### 2011-12-08 docs/HPC_report/finalReportJesse.tex
adding HPC report to docs folder in camellia
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@90 36274a68-8941-4c93-80ef-affaed5139da

\documentclass{article}
\include{jessePreamble} % contains commonly used packages/defined functions
\date{}
\author{Jesse Chan and Nate Roberts}
\title{HPC Final Project: A Parallel Implementation of DPG}

\begin{document}

\maketitle

\section{Introduction to DPG}

The Discontinuous Petrov-Galerkin (DPG) method is a finite element method introduced by Demkowicz and Gopalakrishnan in \cite{DPG1} and \cite{DPG2}. The DPG method was first applied to solve the convection-dominated diffusion equation
\[
\div \left(\beta u - \epsilon\grad u\right) = f,
\]
a prototype for shock and boundary layer problem when $\epsilon \ll 1$, using higher order adaptive meshes in \cite{DPG2} and \cite{DPG3}. It's worth noting that for standard finite element methods, the convection-dominated diffusion problem suffers from large oscillations that grow in amplitude with $\frac{1}{\epsilon}$. This behavior illustrates an example of the \emph{instability} of standard finite element methods when it comes to problems with small parameters.

DPG falls under the class of Discontinuous Galerkin (DG) methods, in that the solution is allowed to be discontinuous across element boundaries, with continuity weakly enforced through numerical fluxes defined on element boundaries. DPG is also a Petrov-Galerkin method, or a finite element method where the test and trial spaces differ. Petrov-Galerkin methods have been successful in demonstrating that a careful selection of test functions improves behavior of the finite element. The Streamline Upwind Petrov-Galerkin method of Hughes and Brooks \cite{SUPG} is an example of such a method, which aims to eliminate the unstable oscillations in the convection-dominated diffusion problem for Continuous Galerkin (CG) methods.

DPG has also been successfully applied to problems in wave propagation and linear elasticity \cite{DPG4}\cite{DPGElas} using the serial Fortran code \verb+hpDPG+. In this report, we demonstrate a parallel implementation of DPG for adaptive meshes, using the convection-dominated diffusion problem as an example.

\subsection{Optimal Test Functions}

The definition of an optimal test function is more rigorously defined in \cite{DPG2}, and has been well-known in the finite element community for some time. However, this idea proved to be impractical, as the cost to computing a single optimal test function was equivalent to the cost of solving the original problem over the entire mesh. The key contribution of DPG has been to note that the global nature of this problem is due to the continuous nature of the trial space. For a Discontinuous Galerkin method, the test space is also necessarily discontinuous, which decouples the global problem into a local problem over each element.

With respect to optimal test functions, a discontinuous test space allows the test functions to be computed \emph{locally}, on an per-element basis. Not only does this decrease the problem size dramatically, it is also intrinsically parallel - the optimal test functions over each element can be computed completely independently of each other.

With DPG, given any basis $\{u_i\}$ for the trial space, we can compute the $i$th optimal test function over an element by solving the auxiliary problem 
\[
(v_i, \delta v)_V = b(u_i,\delta v), \quad \forall \delta v\in V
\]
where $V$ is the space of admissible test functions (with proper regularity) on the element. For a trial function whose support spans multiple elements, the optimal test function is solved for independently over each element, then set as the union of the test functions over each element the trial function spans. In practice, we solve this problem approximately by taking $V$ to be the space of admissible test functions of order $p+\Delta p$, where $p$ is the order of the trial space. This results in a fairly small local system

\subsection{Hybridized DG formulation}

In DG methods, elements are coupled to each other through a numerical flux defined on the boundary; for standard DG methods, this numerical flux is computed using some predetermined function of the finite element solution in the interior. The DPG method is an example of a hybridized DG formulation, where the numerical flux is instead solved for as part of the solution, introducing additional unknowns to the problem (called hybridization).

However, this hybridization produces more loosely coupled blocks in the global stiffness matrix than standard DG methods, which, for certain numerical fluxes, will produce the same coupled sparsity pattern as a CG method. For a hybridized DG formulation, the finite element solution is separated into interior degrees of freedom and boundary/flux degrees of freedom. The interior degrees of freedom (which are usually much more than the boundary degrees of freedom) for each element are completely decoupled from each other, meaning that for global assembly of the stiffness matrices, the amount of data communication needed between different processors is reduced.

\section{Implementation}

\subsection{Camellia/Trilinos implementation}

In this section, we describe the changes that we implemented within Camellia to allow the work to be partitioned and executed efficiently within an MPI environment.

Camellia was originally written to run in serial, so a number of changes were required to allow MPI execution—the most significant of these had to do with element partitioning and partitioning the degree-of-freedom coefficients.  Trilinos's Intrepid routines are designed to execute on batches of cells that are alike in topology and polynomial order.  We allow meshes of non-uniform topology and polynomial order; thus we had implemented an ElementType class which allowed us to identify elements that could be batched.  Our Mesh class maintained data structures such that information pertaining to a particular ElementType could be accessed quickly—for example, Mesh stored a data structure that contained the vertex coordinates belonging for elements of a given ElementType.

The upshot of this design is that mesh information is already, in a sense, partitioned.  However, there is no reason to expect that this will be a good partitioning for dividing up the work of stiffness matrix computation across MPI nodes—for this, we want our mesh partitioning to keep spatially adjacent elements together within a partition to minimize the amount of data that needs to be communicated during global stiffness matrix assembly.

Thus, to maintain both of our desired design features—batching by ElementType and spatially contiguous partitioning across MPI nodes—we require a two-level partitioning; we first divide the elements spatially (the MPI partitions), and then batch together elements of like ElementType within each of these partitions.  (Unfortunately, this is not quite the whole story; because other classes depend on the ElementType division of the whole mesh, we have had to maintain the old lookup tables as well.  We do hope to eliminate these dependencies in the end.)

To facilitate experiments with multiple partitioning strategies (and to maintain separation of concerns), we designed an abstract MeshPartitionPolicy class which, given a Mesh and the number of partitions desired, returns a partition of the elements in the mesh.  The Mesh then uses this to generate a partition of the degree-of-freedom coefficients, which induces a partition of the rows in the stiffness matrix.  The latter partition is used in conjunction with an Epetra FECrsMatrix, a distributed stiffness matrix assembly facility within Trilinos.  The FECrsMatrix allows storage of data not owned by the current MPI node; this data is communicated to the owning MPI node during global assembly of the stiffness matrix.  A convenient consequence of this is that we can separate the cost of global assembly from the cost of local stiffness matrix computations; the latter are independent across MPI nodes, and therefore we expect to see perfect scaling for these.  The scaling of the global assembly will depend on the quality of the partition and the cost of communication between MPI nodes.  We do not hope for perfect scaling here, but we do hope to see a cost per dof per node that does not grow too quickly in the total number of nodes.

\subsection{Partitioning}

Since Camellia is tightly integrated with the Trilinos library already, we use the Zoltan package in Trilinos to generate spatially local partitions of the mesh \cite{ZoltanOverviewArticle}. We interface specifically with the Hilbert Space-filling Curve and Reftree partitioning algorithms in Zoltan, both of which can include parallel implementations.

The Hilbert space-filling curve (HSFC) algorithm works by drawing a curve through the geometric mesh in 2 or 3 dimensional space, then mapping that curve to the interval $[0,1]$. The partitioner then divides up this interval (in an even or weighted manner) into $n$ partitions, and maps each of those partitions back into 2 or 3D. All that's required of the HSFC algorithm is a listing of elements and a geometric identifier associated with a given element. In this case, we use the element centroid as such an identifier.

The Reftree algorithm \cite{REFTREE} adds complexity in that each processor must store information not only about the active nodes, but the ancestors as well. Additionally, Reftree requires that, if you store an ancestor, you must store all its children as well, increasing the amount of redundancy between distributed refinement trees. However, due to Reftree being more agnostic towards element types (quad vs triangle, tetrahedron vs cube), the same algorithm performs similarly for many different types of refined meshes (as opposed to HSFC, which works best for quadrilateral grids, but not for triangular grids).  Additionally, Reftree's algorithm guarantees connected partitions for tetrahedral and triangular grids, and generally performs more robustly on other types of grids as well.

Currently, Reftree has been implemented and tested on local clusters. However, Reftree currently crashes during runs on Lonestar, our HPC architecture for this report. We use the HSFC partitioner for the scaling tests in this report, and hope to fix issues with Reftree in the near future.

\section{Scaling tests}

\section{Future work}

\subsection{$hp$-meshes}
\subsection{Parallel solvers}
\subsubsection{MUMPS}
\subsubsection{Conjugate gradients/static condensation}

One benefit of DPG is that the global stiffness matrices it produces are guaranteed to be symmetric positive-definite, allowing for iterative methods like CG to be used.

Another benefit of the hybridized DG formulation is that the global solve can be statically condensed down to a solve involving only the flux degrees of freedom.

\bibliographystyle{plain}
\bibliography{finalReport}

\end{document}

### 2011-12-08 docs/HPC_report/finalReportJesse.tex
adding notes on scaling to final report
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@91 36274a68-8941-4c93-80ef-affaed5139da
added more lines to hybridized DG formulation
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@92 36274a68-8941-4c93-80ef-affaed5139da

@@
 For a hybridized DG formulation, the finite element solution is separated into interior degrees of freedom and boundary/flux degrees of freedom.
-The interior degrees of freedom (which are usually much more than the boundary degrees of freedom) for each element are completely decoupled from each other, meaning that for global assembly of the stiffness matrices, the amount of data communication needed between different processors is reduced.
+The interior degrees of freedom (which are usually much more than the boundary degrees of freedom) for each element are completely decoupled from each other, implying that, for global assembly of the stiffness matrices, the amount of data communication needed between different processors is reduced.
+Thus, we expect the parallelizability of the assembly process to be fairly high.
 
@@
 
+Handicaps
+- Batch cache size 
+- Using all 12 cores on a single node
+
 \section{Future work}

### 2011-12-08 docs/HPC_report/finalReportJesse.tex
Some edits and additions, particularly to the introduction.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@93 36274a68-8941-4c93-80ef-affaed5139da

@@
 \author{Jesse Chan and Nate Roberts}
-\title{HPC Final Project: A Parallel Implementation of DPG}
+\title{Extending Camellia for Distributed Stiffness Matrix Determination in DPG}
 
@@
 a prototype for shock and boundary layer problem when $\epsilon \ll 1$, using higher order adaptive meshes in \cite{DPG2} and \cite{DPG3}.
-It's worth noting that for standard finite element methods, the convection-dominated diffusion problem suffers from large oscillations that grow in amplitude with $\frac{1}{\epsilon}$.
+For standard finite element methods, the convection-dominated diffusion problem suffers from large oscillations that grow in amplitude with $\frac{1}{\epsilon}$.
 This behavior illustrates an example of the \emph{instability} of standard finite element methods when it comes to problems with small parameters.
 
-DPG falls under the class of Discontinuous Galerkin (DG) methods, in that the solution is allowed to be discontinuous across element boundaries, with continuity weakly enforced through numerical fluxes defined on element boundaries.
-DPG is also a Petrov-Galerkin method, or a finite element method where the test and trial spaces differ.
-Petrov-Galerkin methods have been successful in demonstrating that a careful selection of test functions improves behavior of the finite element.
-The Streamline Upwind Petrov-Galerkin method of Hughes and Brooks \cite{SUPG} is an example of such a method, which aims to eliminate the unstable oscillations in the convection-dominated diffusion problem for Continuous Galerkin (CG) methods.
+DPG is a \emph{discontinuous} Galerkin (DG) method, which means that the solution is allowed to be discontinuous across inter-element boundaries, with continuity weakly enforced through numerical fluxes defined on element boundaries.
+DPG is also a \emph{Petrov}-Galerkin method, a finite element method in which the test and trial spaces are allowed to differ.
+Petrov-Galerkin methods allow selection of test functions that improve the behavior of the finite element.
+The Streamline Upwind Petrov-Galerkin method of Hughes and Brooks \cite{SUPG} is an example of such a method; it aims to eliminate the unstable oscillations in the convection-dominated diffusion problem for Continuous Galerkin (CG) methods.
 
-DPG has also been successfully applied to problems in wave propagation and linear elasticity \cite{DPG4}\cite{DPGElas} using the serial Fortran code \verb+hpDPG+.
-In this report, we demonstrate a parallel implementation of DPG for adaptive meshes, using the convection-dominated diffusion problem as an example.
+DPG has also been successfully applied to problems in wave propagation and linear elasticity \cite{DPG4,DPGElas} using the serial Fortran code \verb+hpDPG+.
+Roberts has recently developed Camellia \cite{Camellia}, a toolbox for solving problems using DPG built atop the Trilinos library of packages.
+Prior to the present work, Camellia supported only serial execution.
+The present work extends Camellia to allow distributed stiffness matrix computation, using the convection-dominated diffusion problem as a testbed.
 
+This report is organized as follows.
+In Section \ref{sec:DPGIntro}, we provide the technical details of DPG that are important to understand the present work.
+In Section \ref{sec:Implementation}, we discuss our extensions to Camellia to support distributed stiffness matrix determination.
+We describe some numerical experiments to examine how well Camellia scales to multiple processors in Section \ref{sec:NumericalExperiments}.
+Finally, in \ref{sec:FutureWork}, we discuss future work that we hope to do in the future to improve Camellia's scalability further.
+
+\section{Introduction to DPG}\label{sec:DPGIntro}
 \subsection{Optimal Test Functions}
 
-The definition of an optimal test function is more rigorously defined in \cite{DPG2}, and has been well-known in the finite element community for some time.
+The definition of an optimal test function is rigorously defined in \cite{DPG2}, and has been well-known in the finite element community for some time.
 However, this idea proved to be impractical, as the cost to computing a single optimal test function was equivalent to the cost of solving the original problem over the entire mesh.
@@
 The interior degrees of freedom (which are usually much more than the boundary degrees of freedom) for each element are completely decoupled from each other, implying that, for global assembly of the stiffness matrices, the amount of data communication needed between different processors is reduced.
-Thus, we expect the parallelizability of the assembly process to be fairly high.
+Thus, we expect the assembly process to scale to large numbers of processors fairly well.
 
-\section{Implementation}
+\section{Implementation}\label{sec:Implementation}
 
@@
 
-Camellia was originally written to run in serial, so a number of changes were required to allow MPI execution—the most significant of these had to do with element partitioning and partitioning the degree-of-freedom coefficients.
+Camellia was originally written to run in serial, so a number of changes were required to allow MPI execution---the most significant of these had to do with element partitioning and partitioning the degree-of-freedom coefficients.
 Trilinos's Intrepid routines are designed to execute on batches of cells that are alike in topology and polynomial order.
 We allow meshes of non-uniform topology and polynomial order; thus we had implemented an ElementType class which allowed us to identify elements that could be batched.
-Our Mesh class maintained data structures such that information pertaining to a particular ElementType could be accessed quickly—for example, Mesh stored a data structure that contained the vertex coordinates belonging for elements of a given ElementType.
+Our Mesh class maintained data structures such that information pertaining to a particular ElementType could be accessed quickly---for example, Mesh stored a data structure that contained the vertex coordinates belonging for elements of a given ElementType.
 
 The upshot of this design is that mesh information is already, in a sense, partitioned.
-However, there is no reason to expect that this will be a good partitioning for dividing up the work of stiffness matrix computation across MPI nodes—for this, we want our mesh partitioning to keep spatially adjacent elements together within a partition to minimize the amount of data that needs to be communicated during global stiffness matrix assembly.
+However, there is no reason to expect that this will be a good partitioning for dividing up the work of stiffness matrix computation across MPI nodes---for this, we want our mesh partitioning to keep spatially adjacent elements together within a partition to minimize the amount of data that needs to be communicated during global stiffness matrix assembly.
 
-Thus, to maintain both of our desired design features—batching by ElementType and spatially contiguous partitioning across MPI nodes—we require a two-level partitioning; we first divide the elements spatially (the MPI partitions), and then batch together elements of like ElementType within each of these partitions.
+Thus, to maintain both of our desired design features---batching by ElementType and spatially contiguous partitioning across MPI nodes---we require a two-level partitioning; we first divide the elements spatially (the MPI partitions), and then batch together elements of like ElementType within each of these partitions.
 (Unfortunately, this is not quite the whole story; because other classes depend on the ElementType division of the whole mesh, we have had to maintain the old lookup tables as well.
@@
 
-\section{Scaling tests}
+\section{Scaling tests}\label{sec:NumericalExperiments}
 
@@
 
-\section{Future work}
+\section{Future work}\label{sec:FutureWork}
 

### 2011-12-08 docs/HPC_report/Extending_Camellia.tex
Renamed tex file.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@95 36274a68-8941-4c93-80ef-affaed5139da

--- 2011-12-08 docs/HPC_report/finalReportJesse.tex
@@
 \date{}
-\author{Jesse Chan and Nate Roberts}
+\author{Jesse Chan and Nathan V. Roberts}
 \title{Extending Camellia for Distributed Stiffness Matrix Determination in DPG}
@@
 DPG has also been successfully applied to problems in wave propagation and linear elasticity \cite{DPG4,DPGElas} using the serial Fortran code \verb+hpDPG+.
-Roberts has recently developed Camellia \cite{Camellia}, a toolbox for solving problems using DPG built atop the Trilinos library of packages.
+Roberts has recently developed Camellia \cite{Camellia}, a toolbox for solving problems using DPG built atop Sandia's Trilinos Project \cite{Trilinos-Overview}.
 Prior to the present work, Camellia supported only serial execution.
@@
 We describe some numerical experiments to examine how well Camellia scales to multiple processors in Section \ref{sec:NumericalExperiments}.
-Finally, in \ref{sec:FutureWork}, we discuss future work that we hope to do in the future to improve Camellia's scalability further.
+Finally, in Section \ref{sec:FutureWork}, we discuss work that we hope to do in the future to improve Camellia's scalability further.
 

### 2011-12-08 docs/HPC_report/Extending_Camellia.tex
finished optimal test function discussion
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@97 36274a68-8941-4c93-80ef-affaed5139da
Added more discussion of extending Camellia, including some design limitations.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@98 36274a68-8941-4c93-80ef-affaed5139da

@@
 
-\section{Introduction to DPG}
+\section{Introduction}
 
-The Discontinuous Petrov-Galerkin (DPG) method is a finite element method introduced by Demkowicz and Gopalakrishnan in \cite{DPG1} and \cite{DPG2}.
-The DPG method was first applied to solve the convection-dominated diffusion equation
+The Discontinuous Petrov-Galerkin (DPG) methodology is a class of finite element methods introduced by Demkowicz and Gopalakrishnan in \cite{DPG1} and \cite{DPG2}.
+DPG was first applied to solve the convection-dominated diffusion equation
 \[
@@
 The Streamline Upwind Petrov-Galerkin method of Hughes and Brooks \cite{SUPG} is an example of such a method; it aims to eliminate the unstable oscillations in the convection-dominated diffusion problem for Continuous Galerkin (CG) methods.
+DPG computes test functions on the fly which are\emph{optimal} in that they deliver the best available approximation to the solution, as measured in an energy norm defined by the problem and a test space which may be chosen by the analyst.
 
@@
 
-\section{Introduction to DPG}\label{sec:DPGIntro}
+\section{DPG: Some Technical Details}\label{sec:DPGIntro}
 \subsection{Optimal Test Functions}
 
-The definition of an optimal test function is rigorously defined in \cite{DPG2}, and has been well-known in the finite element community for some time.
-However, this idea proved to be impractical, as the cost to computing a single optimal test function was equivalent to the cost of solving the original problem over the entire mesh.
+The concept of an optimal test function is rigorously defined in \cite{DPG2}, and has been well-known in the finite element community for some time.
+However, this idea proved to be impractical, as the cost of computing a single optimal test function was equivalent to the cost of solving the original problem over the entire mesh.
 The key contribution of DPG has been to note that the global nature of this problem is due to the continuous nature of the trial space.
@@
 With respect to optimal test functions, a discontinuous test space allows the test functions to be computed \emph{locally}, on an per-element basis.
-Not only does this decrease the problem size dramatically, it is also intrinsically parallel - the optimal test functions over each element can be computed completely independently of each other.
+Not only does this decrease the problem size dramatically, it is also intrinsically parallel---the optimal test functions for each element can be computed completely independently of each other.
 
@@
 In practice, we solve this problem approximately by taking $V$ to be the space of admissible test functions of order $p+\Delta p$, where $p$ is the order of the trial space.
-This results in a fairly small local system
+This results in a small element-local system which is solved to determine a test function corresponding to each degree of freedom on the element.
+$\Delta p$ is taken to be 2 in this report.
 
@@
 
-\subsection{Camellia/Trilinos implementation}
+\subsection{Extending Camellia}
 
-In this section, we describe the changes that we implemented within Camellia to allow the work to be partitioned and executed efficiently within an MPI environment.
+In this section, we describe the changes that we implemented within Camellia to allow the stiffness matrix determination to be executed efficiently within an MPI environment.
 
@@
 The scaling of the global assembly will depend on the quality of the partition and the cost of communication between MPI nodes.
-We do not hope for perfect scaling here, but we do hope to see a cost per dof per node that does not grow too quickly in the total number of nodes.
+We do not hope for perfect scaling here, but we do hope to see a cost per degree of freedom per node that does not grow too quickly in the total number of nodes.
+
+The MeshPartitionPolicy partitions the mesh into sets of elements assigned to an MPI node; for the interface to Epetra, we need a partition of rows of the global stiffness matrix (each of which corresponds to a degree of freedom).
+Degrees of freedom corresponding to numerical fluxes are shared by the elements along whose boundaries they lie.
+We adopt a simple greedy policy for this---shared d.o.f.s are assigned to the element with the smallest global identifier.
+This means that even if the element partitioning were perfectly balanced, some MPI nodes might still have more d.o.f.s assigned to them than others.
+This will not affect the amount of work involved in local stiffness matrix computations, but it may affect MPI communication costs during global assembly.
+
+\subsubsection{Design Limitations: Where Amdahl's Law Might Come to Haunt Us}
+Here, we note a few features of the present design that may become bottlenecks as we scale up to larger problems and larger numbers of MPI nodes.
+
+At present, our global solve is implemented using the KLU implementation provided by the Amesos package within Trilinos.
+This is a direct solve, executed in serial.
+Amesos gathers the global stiffness matrix to rank 0, solves, and then scatters the solution according to the partition we have defined.
+For our serial computations prior to the present work, the cost of the global solve has been dominated by the cost of the local optimal test function determination; however, now that the latter cost has been distributed using MPI and the former has not, we expect the global solve to become a bottleneck, both in terms of overall execution time and in terms of the sizes of problems that can be solved, since the KLU solve must fit into a single node's memory to be practical.
+
+Similarly, at present the entire mesh is determined and stored on every MPI node.
+This has the advantage that no MPI communication is required during mesh construction, but for very large meshes it may become impractical, because the time cost of mesh construction may grow relative to the distributed parts of the computation, and perhaps (for \emph{extremely} large meshes) because the memory required for the mesh may grow too large for storage on a node.
+
+Finally, certain features of the original code depend upon all the solution coefficients being available to the current processor, so for the time being we distribute the entire solution to every MPI node, after KLU has scattered according to the original partitioning.
+We hope to eliminate this dependence on having all solution coefficients available, allowing the solution to be distributed according to the same mapping as was used for the stiffness matrix.
 

### 2011-12-09 docs/HPC_report/Extending_Camellia.tex
adding figs to camellia, adding plotting functions, data, figs to repo
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@99 36274a68-8941-4c93-80ef-affaed5139da

@@
 \documentclass{article}
+\newcommand{\oneFig}{.65}
+\newcommand{\twoFig}{.42}
+\newcommand{\fourFig}{.42}
+
 \include{jessePreamble} % contains commonly used packages/defined functions
@@
 
-\subsubsection{Design Limitations: Where Amdahl's Law Might Come to Haunt Us}
+\subsubsection{Design Limitations: where Amdahl's law might come to haunt us}
 Here, we note a few features of the present design that may become bottlenecks as we scale up to larger problems and larger numbers of MPI nodes.
@@
 
+Describe experimental setup
+\begin{figure}
+\centering
+\subfigure[Cyclic]{
+\includegraphics[scale = \twoFig]{figs/cyclic.pdf}
+}
+\subfigure[HSFC]{
+\includegraphics[scale = \twoFig]{figs/hsfc.pdf}
+}
+\end{figure}
+
+\subsection{Weak scaling}
+
+\begin{figure}
+\centering
+\subfigure[Global stiffness assembly]{
+\includegraphics[scale = \twoFig]{figs/scalingFigs/weakScalingAssembly.pdf}
+}
+\subfigure[Local stiffness computation]{
+\includegraphics[scale = \twoFig]{figs/scalingFigs/weakScalingLocal.pdf}
+}
+\end{figure}
+
+\subsection{Strong scaling}
+\begin{figure}
+\centering
+\subfigure[Global stiffness assembly]{
+\includegraphics[scale = \twoFig]{figs/scalingFigs/hsfcStrongScalingAssembly.pdf}
+}
+\subfigure[Local stiffness computation]{
+\includegraphics[scale = \twoFig]{figs/scalingFigs/hsfcStrongScalingLocal.pdf}
+}
+\caption{Strong scaling statistics for a HSFC (localized) partitioning of the mesh.}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[Global stiffness assembly]{
+\includegraphics[scale = \twoFig]{figs/scalingFigs/cyclicStrongScalingAssembly.pdf}
+}
+\subfigure[Local stiffness computation]{
+\includegraphics[scale = \twoFig]{figs/scalingFigs/cyclicStrongScalingLocal.pdf}
+}
+\caption{Strong scaling statistics for a cyclic (non-localized) partitioning of the mesh.}
+\end{figure}
+
+\subsection{Breakdown of time spent}
+\begin{figure}
+\centering
+\subfigure[202 elements, 13343 dofs]{
+\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref0.pdf}
+}
+\subfigure[808 elements, 52137 dofs ]{
+\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref1.pdf}
+}
+\subfigure[3232 elements, 206081 dofs]{
+\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref2.pdf}
+}
+\subfigure[12928 elements, 819393 dofs]{
+\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref3.pdf}
+}
+\caption{Strong scaling statistics for a cyclic (non-localized) partitioning of the mesh.}
+\end{figure}
+
 Handicaps

### 2011-12-09 docs/HPC_report/plotScalingData.m

@@ -1,0 +1,139 @@
+close all
+clear
+load hsfcMats
+load cyclicMats
+cyclic_assemble = [hsfc_assemble(:,1) cyclic_assemble];
+cyclic_local = [hsfc_local(:,1) cyclic_local];
+cyclic_solve = [hsfc_solve(:,1) cyclic_solve];
+
+%% weak scaling plots
+figure;hold on
+plot(1:length(numMpiProcs),diag(cyclic_assemble),'r*-','linewidth',2)
+plot(1:length(numMpiProcs),diag(hsfc_assemble),'bo-','linewidth',2)
+legend('Cyclic partitioning','HSFC partitioning')
+ylim([0,.7])
+title('Global stiffness matrix assembly time','fontsize',14)
+%set(gca,'XtickLabel',['4^0';'4^1';'4^2';'4^3'])
+xtickVec =['1 ';'  ';' 4';'  ';'16';'  ';'64'];
+set(gca,'XTickLabel',xtickVec)
+xlabel('MPI nodes used','fontsize',14)
+ylabel('Runtime (in seconds)','fontsize',14)
+grid on
+
+figure;hold on
+plot(1:length(numMpiProcs),diag(cyclic_local),'r*-','linewidth',2)
+plot(1:length(numMpiProcs),diag(hsfc_local),'bo-','linewidth',2)
+legend('Cyclic partitioning','HSFC partitioning')
+ylim([0,ceil(max(diag(cyclic_local)))])
+title('Local stiffness matrix computation time','fontsize',14)
+%set(gca,'XTick',numMpiProcs)
+set(gca,'XTickLabel',xtickVec)
+xlabel('MPI nodes used','fontsize',14)
+ylabel('Runtime (in seconds)','fontsize',14)
+
+grid on
+
+%% strong scaling plots
+numInitElems = 202; % from data file
+figure(3);
+figure(4);
+
+figure(5);
+figure(6);
+
+cmat = hsv(4);
+for numUnifRefs = 0:3
+    figure(3)
+    semilogy(1:3,hsfc_assemble(numUnifRefs+1,(2:end)),'*-','color',cmat(numUnifRefs+1,:),'linewidth',2);
+    hold on
+    figure(4)
+    semilogy(1:3,cyclic_assemble(numUnifRefs+1,(2:end)),'*-','color',cmat(numUnifRefs+1,:),'linewidth',2);
+    hold on
+    figure(5)
[…]

### 2011-12-09 docs/HPC_report/Extending_Camellia.tex
added static condensation note at end
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@100 36274a68-8941-4c93-80ef-affaed5139da

@@
 
-Describe experimental setup
+\begin{itemize}
+\item Describe experimental setup
+
+\item Handicaps - batch cache size, using all 12 cores on a single node
+
+\item
+
+\end{itemize}
+
 \begin{figure}
@@
 \subsection{Breakdown of time spent}
+
 \begin{figure}
@@
 }
-\caption{Strong scaling statistics for a cyclic (non-localized) partitioning of the mesh.}
+\caption{Breakdown of time spent in a solve for a series of HSFC-partitioned meshes.}
 \end{figure}
-
-Handicaps
-- Batch cache size 
-- Using all 12 cores on a single node
 
@@
 
-Another benefit of the hybridized DG formulation is that the global solve can be statically condensed down to a solve involving only the flux degrees of freedom.
+Another benefit of the hybridized DG formulation is that the global solve can be reduced down to a solve involving only the flux degrees of freedom.
+Since the interior degrees of freedom are completely decoupled from each other, the system can be reordered to yield
+\[
+\left(\begin{array}{cc}
+A &B\\
+B^T &C
+\end{array}
+\right)
+\left(\begin{array}{c}
+u\\
+f
+\end{array}
+\right) = 
+\left(\begin{array}{c}
+F\\
+G
+\end{array}
+\right)
+\]
+where $A$ is block diagonal. Noting that $u = A^{-1}(F-Bf)$, we can substitute this into the second solution to obtain a problem purely in terms of the flux degrees of freedom
+\[
+(C-B^TA^{-1}B)f = G-B^TA^{-1}F
+\]
+Since $A$ is easy to invert, and $B$ is a much smaller system, this \emph{static condensation} would reduce the cost of the solve.
 

### 2011-12-09 docs/HPC_report/Extending_Camellia.tex
added experimental setup
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@101 36274a68-8941-4c93-80ef-affaed5139da

@@
 Currently, Reftree has been implemented and tested on local clusters.
-However, Reftree currently crashes during runs on Lonestar, our HPC architecture for this report.
+However, Reftree currently crashes during runs on our HPC architecture for this report.
 We use the HSFC partitioner for the scaling tests in this report, and hope to fix issues with Reftree in the near future.
@@
 
-\begin{itemize}
-\item Describe experimental setup
+We tested the scalability of our code on the Lonestar machine at the Texas Advanced Computing Center (TACC), verifying whether or not we observe strong/weak scaling for various parts of the program.
+We solve the convection-diffusion equation on a square mesh, with boundary conditions such that the solution develops a boundary layer (sharp gradient) near the North and East edges of the square.
+We set up our computational experiments by first refining all cells that share an edge with the North and East sides, and repeating this process four times.
+We then construct three additional meshes, by uniformly refining every element in the mesh (quadrupling the number of elements each time).
+For each of these meshes, we solve on Longhorn, using 1, 4, 16, and 64 nodes, tracking the timing of various portions of the code.
+From this data, we extract strong and weak scaling statistics.
 
-\item Handicaps - batch cache size, using all 12 cores on a single node
-
-\item
-
-\end{itemize}
-
-\begin{figure}
-\centering
-\subfigure[Cyclic]{
-\includegraphics[scale = \twoFig]{figs/cyclic.pdf}
-}
-\subfigure[HSFC]{
-\includegraphics[scale = \twoFig]{figs/hsfc.pdf}
-}
-\end{figure}
+It's worth noting that the runtimes reported here do not represent Camellia running at peak efficiency.
+A single Longhorn node contains 12 cores.
+Our experiments here request only one core per node; utilizing all 12 cores on a node would decrease communication costs, as well as allow us to more fully take advantage of the multi-threaded linear algebra libraries used by Trilinos.
+Additionally, there is a parameter within Camellia that controls the batch size for the Trilinos Intrepid batching routines.
+Tuning this parameter based on machine-specific cache sizes should further optimize performance.
 

### 2011-12-09 docs/HPC_report/Extending_Camellia.tex
added figure, more explanation to report
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@105 36274a68-8941-4c93-80ef-affaed5139da

@@
 \documentclass{article}
-\newcommand{\oneFig}{.65}
+\newcommand{\oneFig}{.5}
 \newcommand{\twoFig}{.42}
@@
 We solve the convection-diffusion equation on a square mesh, with boundary conditions such that the solution develops a boundary layer (sharp gradient) near the North and East edges of the square.
+
+\begin{figure}
+\centering
+\includegraphics[scale=\oneFig]{figs/Solution3232nomesh.png}
+\caption{Computed convection-diffusion solution for $\epsilon=1e-2$ using a refined mesh.  $L^2$ error is $O(1e-4)$.}
+\end{figure}
+
 We set up our computational experiments by first refining all cells that share an edge with the North and East sides, and repeating this process four times.
@@
 From this data, we extract strong and weak scaling statistics.
+
+We experimented also with both a localized and non-localized partitioning of each mesh in order to analyze the communication costs in global stiffness matrix assembly.
+For these runs, we created localized partitions of the mesh using a HSFC partitioner.
+For a non-localized partitioner, we chose to use the Zoltan cyclic partitioner, which loops through the list of active elements, sending the first element to the first processor, the next to the next processor, and so on.
+After reaching the last processor, the cyclic partitioner cycles back to the first processor and repeats this process \footnote{Due to the nature of our refinements in this test, a blocked algorithm (equally partitioning the ordered list of active elements by element number) still maintained fairly good locality.}.
+This partitioning is, in some sense, a ``worst case" scenario that maximizes communication between processors.
 
@@
 }
+\caption{Weak scaling results for computation of local stiffness matrices and global stiffness matrix assembly.
+For each run, both the number of MPI nodes and number of elements are increased by a factor of four.}
 \end{figure}
+
+Both localized and non-localized local stiffness computation display weak scalability by maintaining a constant runtime as both the problem size and number of processors are increased.
+Unlike the localized case, non-localized assembly of the global stiffness matrix does not scale weakly.
+It's worth noting, however, that though communication costs grow much faster with a poor partitioning of the mesh, the maximum amount of time spent on assembly is still only a fraction of the time spent on computation of local stiffness matrices.
 

### 2011-12-09 docs/HPC_report/Extending_Camellia.tex
added new figure, more explanation to report
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@106 36274a68-8941-4c93-80ef-affaed5139da

@@
 \documentclass{article}
-\newcommand{\oneFig}{.5}
+\newcommand{\oneFig}{.45}
 \newcommand{\twoFig}{.42}
@@
 \centering
-\includegraphics[scale=\oneFig]{figs/Solution3232nomesh.png}
-\caption{Computed convection-diffusion solution for $\epsilon=1e-2$ using a refined mesh.  $L^2$ error is $O(1e-4)$.}
+\includegraphics[scale=\oneFig]{figs/Solution12928nomesh.png}
+\caption{Computed solution for $\epsilon=1e-2$ using a refined mesh.  $L^2$ error is $O(1e-5)$.}
 \end{figure}
@@
 \subsubsection{MUMPS}
+
 \subsubsection{Conjugate gradients/static condensation}
@@
 \]
-Since $A$ is easy to invert, and $B$ is a much smaller system, this \emph{static condensation} would reduce the cost of the solve.
+Since $A$ is easy to invert, and $B$ is a much smaller system, this static condensation would reduce the cost of the solve.
 

### 2011-12-09 docs/HPC_report/Extending_Camellia.tex
added hp mesh partitioning to further
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@107 36274a68-8941-4c93-80ef-affaed5139da

@@
 \subsection{$hp$-meshes}
+
+The Zoltan partitioner supports a weighted partitioning of a set of objects.
+At the moment, every element is treated with equal weight, under the assumption that each contributes an equal number of degrees of freedom.
+We would like to extend the partitioning to $hp$-adaptive meshes (where the polynomial order $p$ is allowed to vary element by element) by weighting each element by the number of internal degrees of freedom that it holds.
+
 \subsection{Parallel solvers}

### 2011-12-09 docs/HPC_report/Extending_Camellia.tex
fixed typos, added in partitioning figs
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@108 36274a68-8941-4c93-80ef-affaed5139da

@@
 The Streamline Upwind Petrov-Galerkin method of Hughes and Brooks \cite{SUPG} is an example of such a method; it aims to eliminate the unstable oscillations in the convection-dominated diffusion problem for Continuous Galerkin (CG) methods.
-DPG computes test functions on the fly which are\emph{optimal} in that they deliver the best available approximation to the solution, as measured in an energy norm defined by the problem and a test space which may be chosen by the analyst.
+DPG computes test functions on the fly which are \emph{optimal} in that they deliver the best available approximation to the solution, as measured in an energy norm defined by the problem and a test space which may be chosen by the analyst.
 
@@
 \]
-where $V$ is the space of admissible test functions (with proper regularity) on the element.
+where $V$ is the space of admissible test functions (with proper regularity) on the element, and $(v_i,\delta v)_V$ is some inner product on $V$ (choices for this inner product are discussed in \cite{DPG2}, \cite{DPG4}).
 For a trial function whose support spans multiple elements, the optimal test function is solved for independently over each element, then set as the union of the test functions over each element the trial function spans.
 In practice, we solve this problem approximately by taking $V$ to be the space of admissible test functions of order $p+\Delta p$, where $p$ is the order of the trial space.
-This results in a small element-local system which is solved to determine a test function corresponding to each degree of freedom on the element.
+This results in a small local system on each element which is solved to determine a test function corresponding to each degree of freedom on the element.
 $\Delta p$ is taken to be 2 in this report.
@@
 
-\begin{figure}
+\begin{figure}[h!]
 \centering
@@
 
+\begin{figure}[h!]
+\centering
+\subfigure[HSFC partitioning]{
+\includegraphics[scale = \twoFig]{figs/hsfc.pdf}
+}
+\subfigure[Cyclic partitioning]{
+\includegraphics[scale = \twoFig]{figs/cyclic.pdf}
+}
+\caption{Localized and non-localized partitions of the mesh.}
+\end{figure}
+
 It's worth noting that the runtimes reported here do not represent Camellia running at peak efficiency.
@@
 \subsection{Strong scaling}
-\begin{figure}
+\begin{figure}[h!]
 \centering

### 2011-12-09 docs/HPC_report/Extending_Camellia.tex
Edited especially "Scaling tests".  Replaced Solution12928nomesh with slightly higher-resolution version.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@109 36274a68-8941-4c93-80ef-affaed5139da

@@
 We tested the scalability of our code on the Lonestar machine at the Texas Advanced Computing Center (TACC), verifying whether or not we observe strong/weak scaling for various parts of the program.
-We solve the convection-diffusion equation on a square mesh, with boundary conditions such that the solution develops a boundary layer (sharp gradient) near the North and East edges of the square.
+We solve the convection-diffusion equation on a square mesh, with boundary conditions such that the solution develops a boundary layer (sharp gradient) near the north and east edges of the square.
 
@@
 \includegraphics[scale=\oneFig]{figs/Solution12928nomesh.png}
-\caption{Computed solution for $\epsilon=1e-2$ using a refined mesh.  $L^2$ error is $O(1e-5)$.}
+\caption{Computed solution for $\epsilon=10^{-2}$ using a refined mesh.  $L^2$ error is $O(10^{-5})$.}
 \end{figure}
 
-We set up our computational experiments by first refining all cells that share an edge with the North and East sides, and repeating this process four times.
+We set up our computational experiments by first refining all cells that share an edge with the north and east sides, and repeating this process four times.
 We then construct three additional meshes, by uniformly refining every element in the mesh (quadrupling the number of elements each time).
@@
 
-We experimented also with both a localized and non-localized partitioning of each mesh in order to analyze the communication costs in global stiffness matrix assembly.
-For these runs, we created localized partitions of the mesh using a HSFC partitioner.
-For a non-localized partitioner, we chose to use the Zoltan cyclic partitioner, which loops through the list of active elements, sending the first element to the first processor, the next to the next processor, and so on.
-After reaching the last processor, the cyclic partitioner cycles back to the first processor and repeats this process \footnote{Due to the nature of our refinements in this test, a blocked algorithm (equally partitioning the ordered list of active elements by element number) still maintained fairly good locality.}.
-This partitioning is, in some sense, a ``worst case" scenario that maximizes communication between processors.
+We also used contiguous and discontiguous partitions of each mesh to measure the effect of partition quality on the communication costs in global stiffness matrix assembly.
+We created contiguous partitions of the mesh using a HSFC partitioner.
+To create the discontiguous partitioning, we chose to use the Zoltan cyclic partitioner, which loops through the list of active elements, sending the first element to the first processor, the next to the next processor, and so on.
+After reaching the last processor, the cyclic partitioner cycles back to the first processor and repeats this process.\footnote{Due to the nature of our refinements in this test, a blocked partitioner (equally partitioning the ordered list of active elements by element number) happened to produce nearly-contiguous partitions.
+We therefore have omitted this partitioner from our analysis, since we do not believe that its performance here represents its performance in general.}  The cyclic partitioning is a ``worst case" scenario in the sense that each of the current MPI node's elements' neighbors are owned by some other MPI node.
+
+It's worth noting that the runtimes reported here do not represent Camellia running at peak efficiency.
+A single Lonestar node contains 12 cores.
+Because MPI communication has much higher bandwidth intra-node than inter-node, and for analysis we wanted approximately equal bandwidth between MPI processes, we use only one core per node.
+Utilizing all 12 cores on a node would decrease communication costs.
+Additionally, there is a parameter within Camellia that controls the batch size for the Trilinos Intrepid batching routines.
+Tuning this parameter based on machine-specific cache sizes should further improve performance.
 
@@
 }
-\caption{Localized and non-localized partitions of the mesh.}
+\caption{Contiguous and discontiguous partitions of the mesh.}
 \end{figure}
-
-It's worth noting that the runtimes reported here do not represent Camellia running at peak efficiency.
-A single Longhorn node contains 12 cores.
-Our experiments here request only one core per node; utilizing all 12 cores on a node would decrease communication costs, as well as allow us to more fully take advantage of the multi-threaded linear algebra libraries used by Trilinos.
-Additionally, there is a parameter within Camellia that controls the batch size for the Trilinos Intrepid batching routines.
-Tuning this parameter based on machine-specific cache sizes should further optimize performance.
 

### 2011-12-09 docs/HPC_report/Extending_Camellia.tex
Edited weak scaling discussion.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@110 36274a68-8941-4c93-80ef-affaed5139da

@@
 \centering
+\subfigure[Local stiffness computation]{
+\label{fig:weakScalingStiffness}
+\includegraphics[scale = \twoFig]{figs/scalingFigs/weakScalingLocal.pdf}
+}
 \subfigure[Global stiffness assembly]{
+\label{fig:weakScalingAssembly}
 \includegraphics[scale = \twoFig]{figs/scalingFigs/weakScalingAssembly.pdf}
-}
-\subfigure[Local stiffness computation]{
-\includegraphics[scale = \twoFig]{figs/scalingFigs/weakScalingLocal.pdf}
 }
@@
 
-Both localized and non-localized local stiffness computation display weak scalability by maintaining a constant runtime as both the problem size and number of processors are increased.
-Unlike the localized case, non-localized assembly of the global stiffness matrix does not scale weakly.
+The local stiffness computation for both partition types maintain a constant runtime as the problem size and number of processors increase---that is, both achieve weak scalability for this part of the computation, as can be seen in Figure \ref{fig:weakScalingStiffness}.
+Assembly of the global stiffness matrix achieves weak scalability only for the contiguous case, as can be seen in Figure \ref{fig:weakScalingAssembly}.
 It's worth noting, however, that though communication costs grow much faster with a poor partitioning of the mesh, the maximum amount of time spent on assembly is still only a fraction of the time spent on computation of local stiffness matrices.

### 2011-12-09 docs/HPC_report/Extending_Camellia.tex
More revision of weak scaling.  Started on strong scaling.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@111 36274a68-8941-4c93-80ef-affaed5139da

@@
 We set up our computational experiments by first refining all cells that share an edge with the north and east sides, and repeating this process four times.
-We then construct three additional meshes, by uniformly refining every element in the mesh (quadrupling the number of elements each time).
-For each of these meshes, we solve on Longhorn, using 1, 4, 16, and 64 nodes, tracking the timing of various portions of the code.
-From this data, we extract strong and weak scaling statistics.
+We then constructed three additional meshes, by uniformly refining every element in the mesh (quadrupling the number of elements each time).
+For each of these meshes, we solved on Lonestar, using 1, 4, 16, and 64 nodes, tracking the timing of various portions of the code.
+From this data, we extracted strong and weak scaling statistics.
 
@@
 \centering
+\subfigure[Cyclic partitioning]{
+\includegraphics[scale = \twoFig]{figs/cyclic.pdf}
+}
 \subfigure[HSFC partitioning]{
 \includegraphics[scale = \twoFig]{figs/hsfc.pdf}
-}
-\subfigure[Cyclic partitioning]{
-\includegraphics[scale = \twoFig]{figs/cyclic.pdf}
 }
@@
 \subsection{Weak scaling}
+In our weak scaling tests, we aimed to fix the size of the problem \emph{per MPI node}, and examined the runtime of various portions of the execution---we hope to see a constant runtime as the problem size and number of processors increase, and this is what we mean by achieving weak scalability.
 
@@
 \caption{Weak scaling results for computation of local stiffness matrices and global stiffness matrix assembly.
-For each run, both the number of MPI nodes and number of elements are increased by a factor of four.}
+For each run, both the number of MPI nodes and the number of elements increased by a factor of four.}
 \end{figure}
 
-The local stiffness computation for both partition types maintain a constant runtime as the problem size and number of processors increase---that is, both achieve weak scalability for this part of the computation, as can be seen in Figure \ref{fig:weakScalingStiffness}.
+Both partition types achieve weak scalability in the local stiffness matrix computation, as can be seen in Figure \ref{fig:weakScalingStiffness}.
+In fact, we see the total runtime \emph{decrease} slightly as the total workload and number of MPI nodes increase---we are unsure of the reason for this.
+Similarly, although we would expect the partitioning not to affect this portion of the computation at all (since no inter-node communication occurs at this stage), for some reason the HSFC partitioning slightly outperforms the cyclic on each of the multi-node runs.
+
 Assembly of the global stiffness matrix achieves weak scalability only for the contiguous case, as can be seen in Figure \ref{fig:weakScalingAssembly}.
-It's worth noting, however, that though communication costs grow much faster with a poor partitioning of the mesh, the maximum amount of time spent on assembly is still only a fraction of the time spent on computation of local stiffness matrices.
+It's worth noting, however, that though the poor mesh partitioning imposes much higher communication costs than the HSFC partitioning, the maximum amount of time spent on assembly is still only a small fraction of the time spent on computation of local stiffness matrices.
 
 \subsection{Strong scaling}
+In our strong scaling tests, we considered problems of fixed size, distributing the workload for each among increasing numbers of MPI nodes.
+Here, we hope to see runtimes that decrease linearly in the number of MPI nodes---this is what we mean by achieving strong scalability.
 \begin{figure}[h!]
 \centering
-\subfigure[Global stiffness assembly]{
+\subfigure[Local stiffness computation]{\label{fig:strongScalingLocalStiffnessHSFC}
+\includegraphics[scale = \twoFig]{figs/scalingFigs/hsfcStrongScalingLocal.pdf}
+}
+\subfigure[Global stiffness assembly]{\label{fig:strongScalingAssemblyHSFC}
 \includegraphics[scale = \twoFig]{figs/scalingFigs/hsfcStrongScalingAssembly.pdf}
 }
-\subfigure[Local stiffness computation]{
-\includegraphics[scale = \twoFig]{figs/scalingFigs/hsfcStrongScalingLocal.pdf}
-}
-\caption{Strong scaling statistics for a HSFC (localized) partitioning of the mesh.}
+\caption{Strong scaling statistics for a HSFC (contiguous) partitioning of the mesh.}
 \end{figure}
@@
 \centering
-\subfigure[Global stiffness assembly]{
+\subfigure[Local stiffness computation]{\label{fig:strongScalingLocalStiffnessCyclic}
+\includegraphics[scale = \twoFig]{figs/scalingFigs/cyclicStrongScalingLocal.pdf}
+}
+\subfigure[Global stiffness assembly]{\label{fig:strongScalingAssemblyCyclic}
 \includegraphics[scale = \twoFig]{figs/scalingFigs/cyclicStrongScalingAssembly.pdf}
 }
-\subfigure[Local stiffness computation]{
-\includegraphics[scale = \twoFig]{figs/scalingFigs/cyclicStrongScalingLocal.pdf}
-}
-\caption{Strong scaling statistics for a cyclic (non-localized) partitioning of the mesh.}
+\caption{Strong scaling statistics for a cyclic (discontiguous) partitioning of the mesh.}
 \end{figure}

### 2011-12-09 docs/HPC_report/Extending_Camellia.tex
Added strong scaling discussion.  Swapped order of strong and weak scaling.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@112 36274a68-8941-4c93-80ef-affaed5139da

@@
 For each of these meshes, we solved on Lonestar, using 1, 4, 16, and 64 nodes, tracking the timing of various portions of the code.
-From this data, we extracted strong and weak scaling statistics.
+From this data, we extracted strong and weak scaling statistics, discussed below in Sections \ref{sec:strongScaling} and \ref{sec:weakScaling}.
+The runtimes plotted in each of our figures are the mean of the times recorded at each MPI node.
 
@@
 After reaching the last processor, the cyclic partitioner cycles back to the first processor and repeats this process.\footnote{Due to the nature of our refinements in this test, a blocked partitioner (equally partitioning the ordered list of active elements by element number) happened to produce nearly-contiguous partitions.
-We therefore have omitted this partitioner from our analysis, since we do not believe that its performance here represents its performance in general.}  The cyclic partitioning is a ``worst case" scenario in the sense that each of the current MPI node's elements' neighbors are owned by some other MPI node.
+We therefore have omitted this partitioner from our analysis, since we do not believe that its performance here represents its performance in general.}  The cyclic partitioning is a ``worst case" scenario in the sense that each of the current MPI node's elements' neighbors are owned by some other MPI node, with the consequence that information concerning each element boundary must be sent via MPI.
 
@@
 
-\subsection{Weak scaling}
+\subsection{Strong scaling}\label{sec:strongScaling}
+In our strong scaling tests, we considered problems of fixed size, distributing the workload for each among increasing numbers of MPI nodes.
+Here, we hope to see runtimes that decrease linearly in the number of MPI nodes---this is what we mean by achieving strong scalability.
+
+Because the local stiffness computations are entirely independent of each other, requiring no communication among MPI nodes, we expect to see perfect scaling for these.
+As can be seen in Figures \ref{fig:strongScalingLocalStiffnessCyclic} and \ref{fig:strongScalingLocalStiffnessHSFC}, we do achieve something very close to this, although the cyclic partitioning took longer in almost every case, for reasons that are unclear to us.
+It may have something to do with data locality on each node---by the manner of our construction, data concerning contiguous mesh elements is more likely to be close together in memory than the data for mesh elements in the cyclic case.
+
+It is less clear what we should expect for the global stiffness matrix assembly; we expect the HSFC partitioning to outperform the cyclic partitioning, and we would like to see the runtimes for assembly decrease as the number of MPI nodes increases.
+As can be seen in Figures \ref{fig:strongScalingAssemblyCyclic} and \ref{fig:strongScalingAssemblyHSFC}, for the larger problems in both cases, we do have something approaching strong scalability.
+For the 202- and 808-element problems, we see the time cost increase (or fail to decrease, in the case of the 808-element problem for the cyclic partitioner) between 16 and 64 nodes.
+However, it's worth noting that in these cases, the real times involved are small: less than a second in each case.
+If our concern is our ability to scale up to large problems on large numbers of processors, it does not appear that the global assembly will be a bottleneck.
+The HSFC partitioning does show its strength here compared with the cyclic; for the 12,928 mesh on the 4-node run, the cyclic partitioner took an average of 49.1 seconds per node, compared with 1.63 seconds for the HSFC partition.
+
+\begin{figure}[h!]
+\centering
+\subfigure[Cyclic Partitioning]{\label{fig:strongScalingLocalStiffnessCyclic}
+\includegraphics[scale = \twoFig]{figs/scalingFigs/cyclicStrongScalingLocal.pdf}
+}
+\subfigure[HSFC Partitioning]{\label{fig:strongScalingLocalStiffnessHSFC}
+\includegraphics[scale = \twoFig]{figs/scalingFigs/hsfcStrongScalingLocal.pdf}
+}
+\caption{Strong scaling plots for the local stiffness matrix computation.}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\subfigure[Cyclic Partitioning]{\label{fig:strongScalingAssemblyCyclic}
+\includegraphics[scale = \twoFig]{figs/scalingFigs/cyclicStrongScalingAssembly.pdf}
+}
+\subfigure[HSFC Partitioning]{\label{fig:strongScalingAssemblyHSFC}
+\includegraphics[scale = \twoFig]{figs/scalingFigs/hsfcStrongScalingAssembly.pdf}
+}
+\caption{Strong scaling plots for global stiffness matrix assembly.  (Note the differing scales.) }
+\end{figure}
+
+\subsection{Weak scaling}\label{sec:weakScaling}
 In our weak scaling tests, we aimed to fix the size of the problem \emph{per MPI node}, and examined the runtime of various portions of the execution---we hope to see a constant runtime as the problem size and number of processors increase, and this is what we mean by achieving weak scalability.
@@
 It's worth noting, however, that though the poor mesh partitioning imposes much higher communication costs than the HSFC partitioning, the maximum amount of time spent on assembly is still only a small fraction of the time spent on computation of local stiffness matrices.
-
-\subsection{Strong scaling}
-In our strong scaling tests, we considered problems of fixed size, distributing the workload for each among increasing numbers of MPI nodes.
-Here, we hope to see runtimes that decrease linearly in the number of MPI nodes---this is what we mean by achieving strong scalability.
-\begin{figure}[h!]
-\centering
-\subfigure[Local stiffness computation]{\label{fig:strongScalingLocalStiffnessHSFC}
-\includegraphics[scale = \twoFig]{figs/scalingFigs/hsfcStrongScalingLocal.pdf}
-}
-\subfigure[Global stiffness assembly]{\label{fig:strongScalingAssemblyHSFC}
-\includegraphics[scale = \twoFig]{figs/scalingFigs/hsfcStrongScalingAssembly.pdf}
-}
-\caption{Strong scaling statistics for a HSFC (contiguous) partitioning of the mesh.}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\subfigure[Local stiffness computation]{\label{fig:strongScalingLocalStiffnessCyclic}
-\includegraphics[scale = \twoFig]{figs/scalingFigs/cyclicStrongScalingLocal.pdf}
-}
-\subfigure[Global stiffness assembly]{\label{fig:strongScalingAssemblyCyclic}
-\includegraphics[scale = \twoFig]{figs/scalingFigs/cyclicStrongScalingAssembly.pdf}
-}
-\caption{Strong scaling statistics for a cyclic (discontiguous) partitioning of the mesh.}
-\end{figure}
 

### 2011-12-09 docs/HPC_report/Extending_Camellia.tex
A bunch of edits throughout.  I think this may finish it.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@113 36274a68-8941-4c93-80ef-affaed5139da

@@
 \date{}
-\author{Jesse Chan and Nathan V. Roberts}
+\author{Jesse Chan \and Nathan V. Roberts}
 \title{Extending Camellia for Distributed Stiffness Matrix Determination in DPG}
@@
 The concept of an optimal test function is rigorously defined in \cite{DPG2}, and has been well-known in the finite element community for some time.
-However, this idea proved to be impractical, as the cost of computing a single optimal test function was equivalent to the cost of solving the original problem over the entire mesh.
-The key contribution of DPG has been to note that the global nature of this problem is due to the continuous nature of the trial space.
-For a Discontinuous Galerkin method, the test space is also necessarily discontinuous, which decouples the global problem into a local problem over each element.
+However, the idea was considered impractical, as the cost of computing a single optimal test function was equivalent to the cost of solving the original problem over the entire mesh.
+A key contribution of DPG has been to note that the global nature of this problem is due to the continuous nature of the trial space.
+For a discontinuous Galerkin method, the test space is also necessarily discontinuous, which decouples the global problem into element-local problems.
 
-With respect to optimal test functions, a discontinuous test space allows the test functions to be computed \emph{locally}, on an per-element basis.
-Not only does this decrease the problem size dramatically, it is also intrinsically parallel---the optimal test functions for each element can be computed completely independently of each other.
+A discontinuous test space allows the test functions to be computed \emph{locally}, on a per-element basis.
+Not only does this decrease the problem size dramatically, it is also intrinsically parallel---the optimal test functions for each element can be computed independently of each other.
 
@@
 In DG methods, elements are coupled to each other through a numerical flux defined on the boundary; for standard DG methods, this numerical flux is computed using some predetermined function of the finite element solution in the interior.
-The DPG method is an example of a hybridized DG formulation, where the numerical flux is instead solved for as part of the solution, introducing additional unknowns to the problem (called hybridization).
+The DPG method is an example of a hybridized DG formulation, which means that the numerical flux is solved for as part of the solution by introducing additional unknowns to the problem.
 
-However, this hybridization produces more loosely coupled blocks in the global stiffness matrix than standard DG methods, which, for certain numerical fluxes, will produce the same coupled sparsity pattern as a CG method.
+Whereas standard DG methods can (for certain numerical fluxes) produce global stiffness matrices whose elements are as tightly coupled as a CG method would, hybridization produces more loosely coupled blocks in the matrix.
 For a hybridized DG formulation, the finite element solution is separated into interior degrees of freedom and boundary/flux degrees of freedom.
-The interior degrees of freedom (which are usually much more than the boundary degrees of freedom) for each element are completely decoupled from each other, implying that, for global assembly of the stiffness matrices, the amount of data communication needed between different processors is reduced.
-Thus, we expect the assembly process to scale to large numbers of processors fairly well.
+The interior degrees of freedom (of which there are usually many more than boundary degrees of freedom) for each element are decoupled from each other.
+Thus the inter-node communication required during global stiffness matrix assembly is reduced.
+We therefore expect the assembly process to scale to large numbers of processors, particularly if we use a good partitioner.
 
@@
 We allow meshes of non-uniform topology and polynomial order; thus we had implemented an ElementType class which allowed us to identify elements that could be batched.
-Our Mesh class maintained data structures such that information pertaining to a particular ElementType could be accessed quickly---for example, Mesh stored a data structure that contained the vertex coordinates belonging for elements of a given ElementType.
+Our Mesh class maintained data structures such that information pertaining to a particular ElementType could be accessed quickly---for example, Mesh stored a data structure that contained the vertex coordinates belonging to elements of a given ElementType.
 
@@
 The Mesh then uses this to generate a partition of the degree-of-freedom coefficients, which induces a partition of the rows in the stiffness matrix.
-The latter partition is used in conjunction with an Epetra FECrsMatrix, a distributed stiffness matrix assembly facility within Trilinos.
+The latter partition is used in conjunction with an Epetra FECrsMatrix, a distributed stiffness matrix class within Trilinos.
 The FECrsMatrix allows storage of data not owned by the current MPI node; this data is communicated to the owning MPI node during global assembly of the stiffness matrix.
@@
 Degrees of freedom corresponding to numerical fluxes are shared by the elements along whose boundaries they lie.
-We adopt a simple greedy policy for this---shared d.o.f.s are assigned to the element with the smallest global identifier.
+We adopt a simple greedy policy for assignment of these d.o.f.s: shared d.o.f.s are assigned to the element with the smallest global identifier.
 This means that even if the element partitioning were perfectly balanced, some MPI nodes might still have more d.o.f.s assigned to them than others.
@@
 
-Finally, certain features of the original code depend upon all the solution coefficients being available to the current processor, so for the time being we distribute the entire solution to every MPI node, after KLU has scattered according to the original partitioning.
+Finally, certain features of the original code depend upon all the solution coefficients being available to the current processor, so for the time being we distribute the entire solution to every MPI node, after Amesos has scattered according to the original partitioning.
 We hope to eliminate this dependence on having all solution coefficients available, allowing the solution to be distributed according to the same mapping as was used for the stiffness matrix.
@@
 
-The Hilbert space-filling curve (HSFC) algorithm works by drawing a curve through the geometric mesh in 2 or 3 dimensional space, then mapping that curve to the interval $[0,1]$.
-The partitioner then divides up this interval (in an even or weighted manner) into $n$ partitions, and maps each of those partitions back into 2 or 3D.
-All that's required of the HSFC algorithm is a listing of elements and a geometric identifier associated with a given element.
+The Hilbert space-filling curve (HSFC) algorithm works by drawing a curve through the geometric mesh in 2- or 3-dimensional space, then mapping that curve to the interval $[0,1]$.
+The partitioner then divides up this interval (in an even or weighted manner) into $n$ partitions, and uses this partitioning to induce a partition of the mesh.
+All that's required by the HSFC algorithm is a listing of elements and a geometric identifier associated with a given element.
 In this case, we use the element centroid as such an identifier.
@@
 The Reftree algorithm \cite{REFTREE} adds complexity in that each processor must store information not only about the active nodes, but the ancestors as well.
-Additionally, Reftree requires that, if you store an ancestor, you must store all its children as well, increasing the amount of redundancy between distributed refinement trees.
-However, due to Reftree being more agnostic towards element types (quad vs triangle, tetrahedron vs cube), the same algorithm performs similarly for many different types of refined meshes (as opposed to HSFC, which works best for quadrilateral grids, but not for triangular grids).
+Reftree also requires that if you store an ancestor, you also store all its children as well, increasing the amount of redundancy between distributed refinement trees.
+However, since Reftree is not tuned to a particular element types (quad or triangle, tetrahedron or cube), the same algorithm performs similarly for many different types of refined meshes (as opposed to HSFC, which works best for quadrilateral grids, but not for triangular grids).
 Additionally, Reftree's algorithm guarantees connected partitions for tetrahedral and triangular grids, and generally performs more robustly on other types of grids as well.
 
-Currently, Reftree has been implemented and tested on local clusters.
-However, Reftree currently crashes during runs on our HPC architecture for this report.
-We use the HSFC partitioner for the scaling tests in this report, and hope to fix issues with Reftree in the near future.
+Currently, we have implemented and tested a Reftree MeshPartitionPolicy on our workstations.
+However, Reftree currently crashes during runs on Lonestar, our HPC architecture for this report.
+We used the HSFC partitioner for the scaling tests in this report, and hope to fix issues with Reftree in the near future.
 
@@
 We solve the convection-diffusion equation on a square mesh, with boundary conditions such that the solution develops a boundary layer (sharp gradient) near the north and east edges of the square.
+The solution for a refined mesh is shown in Figure \ref{fig:solutionPlot}.
 
@@
 \includegraphics[scale=\oneFig]{figs/Solution12928nomesh.png}
-\caption{Computed solution for $\epsilon=10^{-2}$ using a refined mesh.  $L^2$ error is $O(10^{-5})$.}
+\caption{Computed solution for $\epsilon=10^{-2}$ using a 12,928-element mesh.  $L^2$ error is $O(10^{-5})$.}
+\label{fig:solutionPlot}
 \end{figure}
@@
 We created contiguous partitions of the mesh using a HSFC partitioner.
-To create the discontiguous partitioning, we chose to use the Zoltan cyclic partitioner, which loops through the list of active elements, sending the first element to the first processor, the next to the next processor, and so on.
+To create the discontiguous partitioning, we used the Zoltan cyclic partitioner, which loops through the list of active elements, sending the first element to the first processor, the next to the next processor, and so on.
 After reaching the last processor, the cyclic partitioner cycles back to the first processor and repeats this process.\footnote{Due to the nature of our refinements in this test, a blocked partitioner (equally partitioning the ordered list of active elements by element number) happened to produce nearly-contiguous partitions.
-We therefore have omitted this partitioner from our analysis, since we do not believe that its performance here represents its performance in general.}  The cyclic partitioning is a ``worst case" scenario in the sense that each of the current MPI node's elements' neighbors are owned by some other MPI node, with the consequence that information concerning each element boundary must be sent via MPI.
+We therefore have omitted this partitioner from our analysis, since we do not believe that its performance here accurately predicts its performance in general.}  The cyclic partitioning is a ``worst case" scenario in the sense that each of the current MPI node's elements' neighbors are owned by some other MPI node, with the consequence that information concerning each element boundary must be sent via MPI.
+An example cyclic partitioning can be seen in Figure \ref{fig:cyclicPartition}; Figure \ref{fig:HSFCPartition} shows an HSFC partitioning.
 
@@
 \centering
-\subfigure[Cyclic partitioning]{
+\subfigure[Cyclic partitioning]{\label{fig:cyclicPartition}
 \includegraphics[scale = \twoFig]{figs/cyclic.pdf}
 }
-\subfigure[HSFC partitioning]{
+\subfigure[HSFC partitioning]{\label{fig:HSFCPartition}
 \includegraphics[scale = \twoFig]{figs/hsfc.pdf}
 }
-\caption{Contiguous and discontiguous partitions of the mesh.}
+\caption{Discontiguous and contiguous partitions of the mesh.}
 \end{figure}
@@
 If our concern is our ability to scale up to large problems on large numbers of processors, it does not appear that the global assembly will be a bottleneck.
-The HSFC partitioning does show its strength here compared with the cyclic; for the 12,928 mesh on the 4-node run, the cyclic partitioner took an average of 49.1 seconds per node, compared with 1.63 seconds for the HSFC partition.
+The HSFC partitioning does show its strength here compared with the cyclic; for the 12,928 mesh on the 4-node run, the cyclic partitioning took an average of 49.1 seconds per node, compared with 1.63 seconds for the HSFC partitioning.
 
@@
 In fact, we see the total runtime \emph{decrease} slightly as the total workload and number of MPI nodes increase---we are unsure of the reason for this.
-Similarly, although we would expect the partitioning not to affect this portion of the computation at all (since no inter-node communication occurs at this stage), for some reason the HSFC partitioning slightly outperforms the cyclic on each of the multi-node runs.
+Although we would not expect the partitioning to affect this portion of the computation at all (since no inter-node communication occurs at this stage), for some reason the HSFC partitioning slightly outperforms the cyclic on each of the multi-node runs.
+As with the strong scaling, we speculate that this is due to locality of the owned element data in the case of the HSFC partitioning.
 
 Assembly of the global stiffness matrix achieves weak scalability only for the contiguous case, as can be seen in Figure \ref{fig:weakScalingAssembly}.
-It's worth noting, however, that though the poor mesh partitioning imposes much higher communication costs than the HSFC partitioning, the maximum amount of time spent on assembly is still only a small fraction of the time spent on computation of local stiffness matrices.
+It's worth noting, however, that though the poor mesh partitioning imposes much higher communication costs than the HSFC partitioning, the maximum amount of time spent on assembly is still dominated by the time spent on computation of local stiffness matrices.
 
-\subsection{Breakdown of time spent}
+\subsection{Total runtime analysis}\label{sec:runtimeAnalysis}
+As the final component of our performance analysis, we examine components of the total runtime for each of our four problems using 1, 4, 16, and 64 MPI nodes; here we use the HSFC partitioner.
+This can be seen in Figure \ref{fig:timeBreakdown}.
+We see that for the largest MPI runs the combined time spent on local stiffness computation and global assembly is a small fraction of the total time spent---since these were the targets of the present work, we can count it a success.
+The graphs also show that the cost of the global solve dominates in each of these runs, making this the obvious next target for optimization.
+In the ``Other'' category, the largest cost is the mesh determination.
+In the 12,928-element case, this takes about 5 seconds.
+Thus, a distributed mesh might be our next target after the solve is optimized.
 
@@
 \centering
-\subfigure[202 elements, 13343 dofs]{
+\subfigure[202 elements, 13,343 dofs]{
 \includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref0.pdf}
 }
-\subfigure[808 elements, 52137 dofs ]{
+\subfigure[808 elements, 52,137 dofs ]{
 \includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref1.pdf}
 }
-\subfigure[3232 elements, 206081 dofs]{
+\subfigure[3,232 elements, 206,081 dofs]{
 \includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref2.pdf}
 }
-\subfigure[12928 elements, 819393 dofs]{
+\subfigure[12,928 elements, 819,393 dofs]{
 \includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref3.pdf}
@@
 \caption{Breakdown of time spent in a solve for a series of HSFC-partitioned meshes.}
+\label{fig:timeBreakdown}
 \end{figure}
@@
 \section{Future work}\label{sec:FutureWork}
+There are several ways in which we hope to extend Camellia further to allow it to solve larger problems still; we hope to:
+\begin{itemize}
+\item distribute the solve, using MUMPS or an iterative solver,
+\item improve the load balancing for meshes of variable polynomial order,
+\item distribute mesh construction and storage, and
+\item distribute solution storage.
+\end{itemize}
 
-\subsection{$hp$-meshes}
+As discussed in Section \ref{sec:runtimeAnalysis} above, the lowest-hanging fruit for further improving the performance for the experimental setup considered in the present work is distributing the solve.
+We have already successfully interfaced with MUMPS---a parallel sparse direct solver---on one of our laptops; we expect that getting MUMPS to work on Lonestar will just be a matter of building Trilinos and Camellia with MUMPS there.
+One of the advantages of DPG is that its stiffness matrices are guaranteed to be symmetric positive definite, which opens the door to using iterative methods such as conjugate gradient methods.
+DPG also produces matrices whose entries are coupled only through the flux degrees of freedom; thus static condensation techniques can be used to reduce the size of the global system to be solved.
+(See Appendix \ref{app:staticCondensation} for a brief explanation of what's involved in static condensation.)  We believe that iterative solvers and static condensation would allow us to solve larger problems than MUMPS will allow---we have heard that MUMPS only scales to about 128 processors.
 
-The Zoltan partitioner supports a weighted partitioning of a set of objects.
-At the moment, every element is treated with equal weight, under the assumption that each contributes an equal number of degrees of freedom.
-We would like to extend the partitioning to $hp$-adaptive meshes (where the polynomial order $p$ is allowed to vary element by element) by weighting each element by the number of internal degrees of freedom that it holds.
+In the present work, we considered a mesh of uniform polynomial order and considered all elements to be of equal weight; Camellia supports meshes with variable order, and Zoltan provides facilities for weighting elements differently.
+By taking advantage of this feature of Zoltan (using a weight corresponding to the number of degrees of freedom on each element), we can improve Camellia's load balancing for meshes of variable polynomial order.
+In fact, in doing so, we expect to improve slightly the load balancing for the setup considered here, because elements with hanging nodes do have slightly more degrees of freedom than those without.
 
-\subsection{Parallel solvers}
-\subsubsection{MUMPS}
+At present, the mesh is constructed and stored on each node, as is the solution.
+It should be a relatively small extension to the present work to allow the solution to be distributed.
+Allowing mesh construction to be distributed is a bigger challenge, largely because the nodes must agree on the global stiffness matrix row indices.
+Given that we are working with an adaptive mesh, it will likely make sense to distribute the work of mesh refinement according to the partition of the previous mesh and use Zoltan to do the load rebalancing.
 
-\subsubsection{Conjugate gradients/static condensation}
+In summary, we have achieved good overall speedup for Camellia using a Hilbert space-filling curve partitioner, and have identified the next steps for improving its parallel performance further.
 
-One benefit of DPG is that the global stiffness matrices it produces are guaranteed to be symmetric positive-definite, allowing for iterative methods like CG to be used.
+\bibliographystyle{plain}
+\bibliography{finalReport}
 
-Another benefit of the hybridized DG formulation is that the global solve can be reduced down to a solve involving only the flux degrees of freedom.
+\newpage
+\appendix
+\section{Static Condensation}\label{app:staticCondensation}
+
+One benefit of DPG's hybridized DG formulation is that the global solve can be reduced down to a solve involving only the flux degrees of freedom.
 Since the interior degrees of freedom are completely decoupled from each other, the system can be reordered to yield
@@
 \]
-Since $A$ is easy to invert, and $B$ is a much smaller system, this static condensation would reduce the cost of the solve.
-
-\bibliographystyle{plain}
-\bibliography{finalReport}
+Since $A$ is easy to invert, and $B$ is a much smaller system, this \emph{static condensation} would reduce the cost of the solve.
 

### 2012-01-23 docs/HPC_report/Camellia_update_230112/Camellia_update_230112.tex
Commit of template for today's Camellia update talk.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@155 36274a68-8941-4c93-80ef-affaed5139da

\documentclass[mathserif]{beamer}
\usetheme[secheader]{pecostalk}

\newcommand{\commentout}[1]{}

\newcommand{\cpp}[0]{\texttt{C++}}

\usepackage{accents}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs,showmanualtags}

\definecolor{DarkGreen}{rgb}{0.13,0.55,0.13}

\graphicspath{{./figs/}}

\date{5-6 October 2010}
\author{Nathan V. Roberts}
\institute{Center for Predictive Engineering and Computational Sciences \\
  Institute for Computational Engineering and Sciences \\
  The University of Texas at Austin \\

  Joint work with \\
  Denis Ridzal, Pavel B. Bochev, Kara J. Peterson, Christopher M. Siefert at Sandia, and \\
  Leszek D. Demkowicz at UT Austin
}
\title[DPG: Stokes 2D]{
Application of a Discontinuous Petrov-Galerkin (DPG) Method to the Stokes Equations}
\begin{document}

\section{Introduction}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{Outline}
\tableofcontents
\end{frame}

\begin{frame}
\frametitle{Stokes Formulation}
\end{frame}

\frame{
%\begin{figure}[!htb]
%\center
%\includegraphics[scale=.28]{LDGcomparison.pdf}
%\caption{DPG with quasi-optimal test norm ($\beta=10^{-1}$) versus LDG convergence.}
%\end{figure}
}

\end{document}

### 2012-01-23 docs/HPC_report/Camellia_update_230112/Camellia_update_230112.tex
jesse committing his changes to the update presentation.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@162 36274a68-8941-4c93-80ef-affaed5139da
added detail to a title slide on presentation
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@163 36274a68-8941-4c93-80ef-affaed5139da
Final version of the slides.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@164 36274a68-8941-4c93-80ef-affaed5139da

@@
 \usepackage{mathtools}
+\usepackage{subfigure}
 \mathtoolsset{showonlyrefs,showmanualtags}
@@
 
-\graphicspath{{./figs/}}
+\setbeamercolor{block body}{bg=white}
 
-\date{5-6 October 2010}
-\author{Nathan V. Roberts}
+\graphicspath{{./figs/ ../figs/}}
+
+\date{23 January 2012}
+\author{Jesse Chan, Nathan V. Roberts}
 \institute{Center for Predictive Engineering and Computational Sciences \\
   Institute for Computational Engineering and Sciences \\
-  The University of Texas at Austin \\
-
-  Joint work with \\
-  Denis Ridzal, Pavel B. Bochev, Kara J. Peterson, Christopher M. Siefert at Sandia, and \\
-  Leszek D. Demkowicz at UT Austin
+  The University of Texas at Austin
 }
-\title[DPG: Stokes 2D]{
-Application of a Discontinuous Petrov-Galerkin (DPG) Method to the Stokes Equations}
+\title[Camellia + MPI]{
+Extending Camellia: Distributed Stiffness Matrix Determination with MPI}
 \begin{document}
 
-\section{Introduction}
+\section{Status Update in Brief}
 
@@
 \begin{frame}
-\frametitle{Stokes Formulation}
+\frametitle{What we had in September 2011}
+Support for:
+\begin{itemize}
+\item meshes of arbitrary degree, with arbitrary combinations of triangles and quads
+\item p-refinements
+\item easy-to-specify bilinear forms
+\item easy-to-specify inner products, {\bf including automatically specified mathematician's and optimal inner products}
+\item rudimentary plotting of field variables using MATLAB
+\item all computations done in serial
+\end{itemize}
 \end{frame}
 
-\frame{
+\begin{frame}
+\frametitle{What we've added}
+Support for:
+\begin{itemize}
+\item h-refinements
+\item automatic adaptivity
+\item mesh-dependent inner products
+\item better plotting of fields, plus simultaneous flux plotting, using MATLAB
+\item {\bf distributed optimal test function and stiffness matrix determination using MPI}
+\item next up/underway: work on 2D Burgers' equation (following MIT paper)
+\end{itemize}
+\end{frame}
+
+\section{Extending Camellia for MPI}
+
+\begin{frame}
+\frametitle{Goals for Camellia+MPI}
+Immediately (today):
+\begin{itemize}
+\item distributed optimal test function and stiffness matrix determination
+\item perform timing experiments to measure speedup and determine where the serial bottlenecks are
+\end{itemize}
+Eventually (someday):
+\begin{itemize}
+\item parallel data structures for Mesh, Solution
+\item parallel solver (MUMPS already works on Nate's laptop)
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Distributing Element Computations: Partitioning Strategy}
+To take advantage of MPI, we need to partition the Mesh somehow.  What's a good way to do this?
+\begin{itemize}
+\item Key consideration in designing distributed algorithms: {\bf data locality} and {\bf minimizing inter-node communication}.
+\item In FEM algorithms, data locality generally follows spatial locality---in DPG, we'll have information to communicate about fluxes and traces along each edge shared by two MPI nodes.
+\item We use a Hilbert space-filling curve to determine a spatially-local partition of elements, using Trilinos's Zoltan package.
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Example Partitions}
 %\begin{figure}[!htb]
 %\center
-%\includegraphics[scale=.28]{LDGcomparison.pdf}
-%\caption{DPG with quasi-optimal test norm ($\beta=10^{-1}$) versus LDG convergence.}
+%\includegraphics[scale=.38]{../figs/cyclic.pdf}
+%\caption{}
 %\end{figure}
+\begin{columns}[c]
+\begin{column}{5.5cm}
+\begin{block}{``Cyclic'' partitioning}
+\includegraphics[width=5.5cm]{../figs/cyclic.pdf}
+\end{block}
+\end{column}
+\begin{column}{5.5cm}
+\begin{block}{Hilbert SFC partitioning}
+\includegraphics[width=5.5cm]{../figs/hsfc.pdf}
+\end{block}
+\end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}
+\frametitle{Details of Original Mesh Implementation: ElementType}
+\begin{itemize}
+\item The low-level methods used to do integration, etc. in Trilinos allow {\bf batching} of elements---i.e. computations can be done for several elements at once for better efficiency.
+\item These methods assume that all elements in a batch are of like type.
+\item Camellia's meshes have elements of different types.
+\item Design goal: allow computations to be done on all elements that are of like type.
+\end{itemize}
+
+All of this motivates the introduction of the ElementType class.
+\end{frame}
+
+\begin{frame}
+\frametitle{Details of Original Mesh Implementation: ElementType}
+Camellia's ElementType is determined by the following features of the element:
+\begin{itemize}
+\item trial space (a \emph{DofOrdering} object),
+\item test space (a \emph{DofOrdering} object),
+\item element topology (a Trilinos \emph{CellTopology} object)
+\end{itemize}
+
+All elements of like type can be addressed as a batch.  Supporting this required the creation of a number of structures within Camellia's Mesh class that are indexed by ElementType.
+\end{frame}
+
+\begin{frame}
+\frametitle{Two Element-Partitioning Mechanisms}
+The division of the Mesh into elements of like ElementType can be thought of as a partitioning of the Mesh.  How should this interact with the partitioning provided by the HSFC?
+\begin{itemize}
+\item effectively, want a {\bf two-level} partition: first, apply HSFC, and then use ElementType within an MPI node for batching
+\item this means that each of the Mesh's data structures indexed by ElementType should also be indexed by partitionNumber
+\item unfortunately, we still need to support some mesh-global operations indexed by ElementType: thus we need to duplicate several of our lookups.
+\item the eventual goal: get rid of those mesh-global operations, replacing them with distributed versions.
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Other Code Modifications}
+Changes required outside of Mesh:
+\begin{itemize}
+\item introduce abstract MeshPartitionPolicy class, with concrete HSFC and Cyclic implementations
+\item in Solution, determine dof partitioning, and supply that to the Epetra CrsMatrix
+\item in Solution: after the solve, distribute solution coefficients to all nodes (will not be required once we have a  completely distributed implementation of all methods)
+\end{itemize}
+\end{frame}
+
+\section{Timing Experiments}
+
+\begin{frame}
+\frametitle{Experimental Setup}
+For a convection-dominated diffusion problem, we used four meshes of size varying from 202 elements to 12928 elements, and timed the overall computation, as well as the following individual components on each node:
+\begin{itemize}
+\item local stiffness matrix computation
+\item global stiffness matrix assembly
+\item solve
+\end{itemize}
+We ran this on Lonestar, using between 1 and 64 MPI nodes.  For a cleaner experiment, we only used 1 core from each machine.
+\end{frame}
+
+\begin{frame}
+\frametitle{Strong Scaling}
+Strong scaling: fix the problem size, and distribute the workload across increasing numbers of processors.
+\begin{columns}[c]
+\begin{column}{5.5cm}
+\begin{block}{``Cyclic'' local stiffness computation}
+\includegraphics[width=5.5cm]{../figs/scalingFigs/cyclicStrongScalingLocal.pdf}
+\end{block}
+\end{column}
+\begin{column}{5.5cm}
+\begin{block}{Hilbert SFC local stiffness computation}
+\includegraphics[width=5.5cm]{../figs/scalingFigs/hsfcStrongScalingLocal.pdf}
+\end{block}
+\end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}
+\frametitle{Strong Scaling, Global Assembly}
+\begin{columns}[c]
+\begin{column}{5.5cm}
+\begin{block}{``Cyclic'' global assembly}
+\includegraphics[width=5.5cm]{../figs/scalingFigs/cyclicStrongScalingAssembly.pdf}
+\end{block}
+\end{column}
+\begin{column}{5.5cm}
+\begin{block}{Hilbert SFC global assembly}
+\includegraphics[width=5.5cm]{../figs/scalingFigs/hsfcStrongScalingAssembly.pdf}
+\end{block}
+\end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}
+\frametitle{Weak Scaling}
+Weak scaling: fix the problem size per MPI node, and increase the number of MPI nodes.  Hope to see constant runtime.
+\begin{columns}[c]
+\begin{column}{5.5cm}
+\begin{block}{Local Stiffness}
+\includegraphics[width=5.5cm]{../figs/scalingFigs/weakScalingLocal.pdf}
+\end{block}
+\end{column}
+\begin{column}{5.5cm}
+\begin{block}{Global Assembly}
+\includegraphics[width=5.5cm]{../figs/scalingFigs/weakScalingAssembly.pdf}
+\end{block}
+\end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}
+\frametitle{Total Runtime Analysis}
+Examine the fraction of time spent in various computations as the number of MPI nodes increases.
+\begin{columns}[c]
+\begin{column}{5.5cm}
+\begin{block}{202 elements, 13,343 does}
+\includegraphics[width=5.5cm]{../figs/scalingFigs/bar_ref0.pdf}
+\end{block}
+\end{column}
+\begin{column}{5.5cm}
+\begin{block}{12,928 elements, 819,393 dofs}
+\includegraphics[width=5.5cm]{../figs/scalingFigs/bar_ref3.pdf}
+\end{block}
+\end{column}
+\end{columns}
+\end{frame}
+
+\section{Parallel Adaptivity}
+
+\frame{
+\frametitle{Experiments with parallel adaptivity}
+We have implemented Heuer and Demkowicz's inner product in Camellia
+\[
+\left((\tau,v),(\delta \tau ,\delta v)\right)_V=C(K,\epsilon)\|v\| + \epsilon\| \nabla v\| + \|\beta \cdot \nabla v \|_w + \|\tau \|_w + \|\nabla \cdot \tau \|_w 
+\]
+where $C(K,\epsilon) = \min(\epsilon,|J(K)|)$. 
+\begin{figure}[!h]
+\centering
+\subfigure{
+\includegraphics[scale=.3]{simplePlot.png}
+}
+\subfigure{
+\includegraphics[scale=.3]{simpleFlux.png}
+}
+\end{figure}
 }
 
+\frame{
+\frametitle{For better pictures, $\epsilon = 5e-2$, slightly skew advection.}
+
+\begin{figure}[!h]
+\centering
+\subfigure{
+\includegraphics[scale=.25]{demoFlux.png}
+}
+\subfigure{
+\includegraphics[scale=.25]{demoSolMesh.png}
+}
+\subfigure{
+\includegraphics[scale=.25]{demoSol.png}
+}
+\end{figure}
+}
+
+\frame{
+\frametitle{To make sure we still work at smaller scales, $\epsilon = 1e-3$}
+\begin{figure}[!h]
+\centering
+\subfigure{
+\includegraphics[scale=.35]{denseMesh.png}
+}\subfigure{
+\includegraphics[scale=.35]{errorRate.png}
+}
+\end{figure}
+}
+
+\section{Future Work}
+\begin{frame}
+\frametitle{Future Work}
+We are pretty satisfied, for now, with our parallel performance: we expect that we will be able to do our 2D Navier-Stokes simulations in reasonable time with the code as it stands.
+But there is still significant opportunity to extend Camellia to solve larger problems still:
+\begin{itemize}
+\item distribute the solve using MUMPS or an iterative solver,
+\item improve load balancing for meshes of variable polynomial order,
+\item distribute mesh construction and storage, and
+\item distribute solution storage.
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+\begin{center}
+  \vfill
+  Thank you.
+  \vfill
+  Questions?
+  \vfill
+\end{center}
+\end{frame}
+
 \end{document}

### 2012-03-02 docs/presentations/nate/Rodeo2012/talk.tex
Draft of Rodeo 2012 slides.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@345 36274a68-8941-4c93-80ef-affaed5139da

\documentclass[mathserif]{beamer}
\usetheme[secheader]{pecostalk}
\graphicspath{{figs/}}

\newcommand{\eqdef}{\stackrel{\text{\tiny def}}{=}}

\newcommand{\NVRvect}[1]{\ensuremath\boldsymbol{#1}}
\newcommand{\NVRtensor}[1]{\underline{\NVRvect{#1}}}
\newcommand{\NVRnorm}[1]{\left|\left|#1\right|\right|}
\newcommand{\NVRgrad}{\nabla}
\newcommand{\NVRdiv}{\NVRgrad \cdot}
\newcommand{\NVRpd}[2]{\frac{\partial#1}{\partial#2}}
\newcommand{\NVRpdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
\newcommand{\NVReqdef}{\stackrel{\text{\tiny def}}{=}}

\newcommand{\NVRHgrad}{H(\text{grad})}
\newcommand{\NVRHdiv}{H(\text{div})}
\newcommand{\NVRsumm}[2]{\ensuremath\displaystyle\sum\limits_{#1}^{#2}}

\date{March 2-3, 2012}
\author{Nate Roberts}
\institute{The University of Texas at Austin}
\title[Camellia]{Camellia}
\subtitle{A Discontinuous Petrov-Galerkin Toolbox Using Trilinos}

\begin{document}
\begin{frame}
\begin{center}
\includegraphics[width=.8\linewidth]{grand_logo}\\
\end{center}
\titlepage
\begin{flushright}
\includegraphics[scale=0.1]{asc_logo}\\
\end{flushright}
\end{frame}

%===============================================================================
% ACKNOWLEDGEMENTS
%===============================================================================
\begin{frame}
\frametitle{Acknowledgments}

Collaborators:
\begin{itemize}
\item Leszek Demkowicz (UT/PECOS)
\item Denis Ridzal (Sandia/CSRI)
\item Pavel Bochev (Sandia/CSRI)
\item Jesse Chan (UT/PECOS)
\end{itemize}

Support:
\begin{itemize}
\item Sandia (summer internships)
\item PECOS (GRA funding)
\item ICES (CSEM Fellowship)
\end{itemize}

\end{frame}

%===============================================================================
% OUTLINE
%===============================================================================
\begin{frame}
\frametitle{Outline}

\begin{enumerate}
\item DPG Intro
\item Goals for Camellia
\item Selected Design Ideas within Camellia
\item A Performance Issue, and its Resolution
\item Current and Future Work
\end{enumerate}

\end{frame}

%===============================================================================
% From Strong-Form PDE to DPG Form
%===============================================================================
\begin{frame}                                                                                                                                                                          
\frametitle{From Strong-Form PDE to DPG Form}
\begin{center}
\includegraphics[width=.6\linewidth]{DPGFormCartoon}\\
\end{center}
\end{frame}              
%===============================================================================
% Solving with DPG
%===============================================================================
\begin{frame}                                                                                                                                                                          
\frametitle{Solving with DPG}
\begin{center}
\includegraphics[width=0.9\linewidth]{DPGSolveCartoon}\\
\end{center}
\end{frame}

%===============================================================================
% CAMELLIA GOALS
%===============================================================================
\begin{frame}
\frametitle{Goals for Camellia}
\begin{block}{Goals for Camellia (Achieved)}
\begin{itemize}
\item Define $b(u,v)$ in the \emph{continuous} space (separation of concerns)
\item Arbitrary, hp-adaptive 2D meshes (quads and triangles)
\item ``Reasonable'' speed and scalability
\item Provide prebuilt versions of inner products commonly used in DPG research (mathematician's and quasi-optimal)
\end{itemize}
\end{block}

\vspace{3 mm}

\begin{block}{Goals for Camellia (Aspirational)}
\begin{itemize}
\item Support for nonlinear PDEs (Navier-Stokes in particular)
\item Better scalability
\item Longer term: 3D meshes
\end{itemize}
\end{block}

\end{frame}

%===============================================================================
% WHAT INTREPID (TRILINOS) PROVIDES
%===============================================================================
\begin{frame}
\frametitle{Trilinos Support}
\begin{block}{Provided by Intrepid}
\begin{itemize}
\item Conforming basis functions 
\item Basis value transformations from reference to physical space
\item Numerical integration facilities
\end{itemize}
\end{block}

The Intrepid facilities operate on \emph{batches} of like elements.

\vspace{3 mm}

\begin{block}{Provided by Epetra}
\begin{itemize}
\item Distributed storage types (including Epetra::FECrsMatrix)
\item Abstract linear solver interfaces (easy to switch solvers)
\end{itemize}
\end{block}

\end{frame}

%===============================================================================
% ELEMENT TYPE
%===============================================================================
\begin{frame}
\frametitle{Design Idea: Element Type}

\begin{center}
\includegraphics[width=8.5cm]{ElementType}
\end{center}

To take maximal advantage of Intrepid's support for batches of elements while operating on a non-uniform mesh,
we introduce the notion of the element type.  Elements of the same type agree in terms of their discrete test and trial spaces.

\end{frame}

%===============================================================================
% ELEMENT TYPE
%===============================================================================
\begin{frame}
\frametitle{Design Idea: Discrete Space}

\begin{center}
\includegraphics[width=8.5cm]{DiscreteSpace}
\end{center}

The discrete spaces, in turn, are defined by mappings from variables to the bases used to represent them.

\end{frame}

%===============================================================================
% FACTORY DESIGN PATTERN
%===============================================================================
\begin{frame}
\frametitle{Design Pattern: Factory}

Bases are objects.  So are the discrete spaces and element types.  To minimize memory footprint (among
other considerations), we need a mechanism to guarantee that we only create one copy of each basis, discrete
space, and element type.  This is known as a \emph{Factory} in the design pattern literature.

\begin{block}{Create Factories for:}
\begin{itemize}
\item Basis
\item Discrete Space
\item Element Type
\end{itemize}
\end{block}

\end{frame}

%===============================================================================
% PERFORMANCE ISSUES
%===============================================================================
\begin{frame}
\frametitle{Performance Story: Quasi-Optimal Inner Product}

The ``optimal test norm''---a choice of test space norm that deliver best approximation in $||\cdot||_{U}$---is given by 
\begin{align*}
||v||_{V}\eqdef \sup_{||u||_{U}=1} b(u,v).
\end{align*}
\\
\begin{itemize}
\item When $U=L^{2}$, can determine analytically using Cauchy-Schwarz.
\item Approximate with ``localized'' version, the \emph{quasi-optimal} test norm.
\item Camellia can determine quasi-optimal test norm automatically.
\end{itemize}

However, when I first implemented this and used it in place of the ``mathematician's'' norm, I observed a dramatic reduction in overall speed.  Why?

\end{frame}

\begin{frame}
\frametitle{Performance Story: Quasi-Optimal Inner Product}

The mathematician's norm for my Stokes formulation is:
\begin{align*}
\NVRnorm{(\NVRvect{q}_{1},\NVRvect{q}_{2},v_{1},v_{2},v_{3})}_{V}^{2}  \NVReqdef \NVRsumm{i=1}{2} ||\NVRvect{q}_{i}||_{\NVRHdiv}^{2} + \NVRsumm{i=1}{3} ||v||_{\NVRHgrad}^{2} \label{NVR:eq:genericNorm}\\
\end{align*}

Compare the quasi-optimal test norm:
\begin{align*}
& \NVRnorm{\frac{q_{11}}{2\mu}+\NVRpd{}{x}v_{1}}_{L^2}^{2} + \NVRnorm{\frac{q_{11}}{2\mu}+\frac{q_{22}}{2\mu}}_{L^2}^{2} + \NVRnorm{\frac{q_{12}}{2\mu}+\frac{q_{21}}{2\mu}+\NVRpd{}{y}v_{1}+\NVRpd{}{x}v_{2}}_{L^2}^{2}\\
&\left. + \NVRnorm{\frac{q_{22}}{2\mu}+\NVRpd{}{y}v_{2}}_{L^2}^{2} + \NVRnorm{q_{12}-q_{21}}_{L^2}^{2} + \NVRnorm{\NVRdiv \NVRvect{q}_{1}-\NVRpd{}{x}v_{3}}_{L^2}^{2} \right.\\
&+\NVRsumm{i=1}{2} ||\NVRvect{q}_{i}||_{L^{2}}^{2} + \NVRsumm{i=1}{3} ||v||_{L^{2}}^{2}\\
\end{align*}

\end{frame}

\begin{frame}
\frametitle{Design Idea: BasisCache}

\begin{itemize}
\item Discrete spaces $\implies$ quadrature points.
\item Will use each basis repeatedly---especially in quasi-optimal test norm!---in both reference and physical space.
\end{itemize}

\begin{itemize}
\item Procedural idea: compute these values once, store them, and reuse them.
\item Object-oriented analog: a cache of basis values (lazily computed, with a limited lifespan).
\item Core computational components---BilinearForm, RHS, and InnerProduct---take a BasisCache as an argument.
\end{itemize}

Once implemented, the quasi-optimal test norm was nearly as fast as the mathematician's norm...

\end{frame}

%===============================================================================
% CURRENT AND FUTURE WORK
%===============================================================================
\begin{frame}
\frametitle{Current and Future Work}
\begin{block}{}
\begin{itemize}
\item Nonlinear PDE support
\item MPI---have: distributed stiffness computation and solve (MUMPS); want: distributed storage/mesh
\item Application to Navier-Stokes
\end{itemize}
\end{block}

\begin{columns}[c]
\begin{column}{5.5cm}
\begin{block}{Convection-Diffusion, $\epsilon=10^{-2}$}
\includegraphics[width=5.5cm]{confusionDemo.png}
\end{block}
\end{column}
\begin{column}{5.5cm}
\begin{block}{Burgers', $\epsilon=10^{-4}$}
\includegraphics[width=5.5cm]{burgers1e4.png}
\end{block}
\end{column}
\end{columns}
\end{frame}

%===============================================================================
% NEW SLIDE
%===============================================================================
\begin{frame}
\frametitle{}
\begin{block}{}
\center{Thank you!} \\
\center{Questions?}\\
%For more info:\\
%nroberts@ices.utexas.edu\\
%\url{https://cfwebprod.sandia.gov/cfdocs/CCIM/docs/Roberts_et_al_SAND2011-6678.pdf}
\end{block}

\end{frame}

\end{document}

### 2012-03-03 docs/presentations/nate/Rodeo2012/talk.tex
Final version of FE Rodeo talk.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@353 36274a68-8941-4c93-80ef-affaed5139da

@@
 
-Bases are objects.  So are the discrete spaces and element types.  To minimize memory footprint (among
-other considerations), we need a mechanism to guarantee that we only create one copy of each basis, discrete
+Each element has a type; each type has a pair of discrete spaces; each discrete space is made up of several bases.  How do we keep this design from taking a prohibitive amount of memory?\\
+\vspace{3 mm}
+For this, among other considerations: want a way to guarantee that we only create one copy of each basis, discrete
 space, and element type.  This is known as a \emph{Factory} in the design pattern literature.
@@
 \begin{align*}
-\NVRnorm{(\NVRvect{q}_{1},\NVRvect{q}_{2},v_{1},v_{2},v_{3})}_{V}^{2}  \NVReqdef \NVRsumm{i=1}{2} ||\NVRvect{q}_{i}||_{\NVRHdiv}^{2} + \NVRsumm{i=1}{3} ||v||_{\NVRHgrad}^{2} \label{NVR:eq:genericNorm}\\
+\NVRnorm{(\NVRvect{q}_{1},\NVRvect{q}_{2},v_{1},v_{2},v_{3})}_{V}^{2}  \NVReqdef \NVRsumm{i=1}{2} ||\NVRvect{q}_{i}||_{\NVRHdiv}^{2} + \NVRsumm{i=1}{3} ||v_{i}||_{\NVRHgrad}^{2} \label{NVR:eq:genericNorm}\\
 \end{align*}
@@
 &\left. + \NVRnorm{\frac{q_{22}}{2\mu}+\NVRpd{}{y}v_{2}}_{L^2}^{2} + \NVRnorm{q_{12}-q_{21}}_{L^2}^{2} + \NVRnorm{\NVRdiv \NVRvect{q}_{1}-\NVRpd{}{x}v_{3}}_{L^2}^{2} \right.\\
-&+\NVRsumm{i=1}{2} ||\NVRvect{q}_{i}||_{L^{2}}^{2} + \NVRsumm{i=1}{3} ||v||_{L^{2}}^{2}\\
+&+\NVRsumm{i=1}{2} ||\NVRvect{q}_{i}||_{L^{2}}^{2} + \NVRsumm{i=1}{3} ||v_{i}||_{L^{2}}^{2}\\
 \end{align*}
@@
 \item Nonlinear PDE support
-\item MPI---have: distributed stiffness computation and solve (MUMPS); want: distributed storage/mesh
+\item Better scalability (distributed mesh)
 \item Application to Navier-Stokes

### 2012-03-08 docs/presentations/nate/Proposal/SIAMreport.tex
Initial start on the Proposal.  Just copied and pasted stuff from the Sandia report, mostly.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@371 36274a68-8941-4c93-80ef-affaed5139da

\documentclass{siamltex}

% PACKAGES ---------------------------------------------------------------
\usepackage{amsfonts,amsmath,graphicx,subfigure,xcolor}
\usepackage{listings}
\usepackage{courier}
\definecolor{lightlightgray}{gray}{0.95}
\definecolor{lightlightblue}{rgb}{0.4,0.4,0.95}
\definecolor{lightlightgreen}{rgb}{0.8,1,0.8}
\lstset{language=C++,
           frame=single,
           basicstyle=\ttfamily\footnotesize,
           keywordstyle=\color{black}\textbf,
           backgroundcolor=\color{lightlightgray},
           commentstyle=\color{blue},
           frame=single
           }
% ADD YOUR OWN PACKAGES HERE ---------------------------------------------
%\usepackage{someotherpackage}

% DEFINITIONS ------------------------------------------------------------
% ADD YOUR OWN DEFINITIONS HERE ------------------------------------------
% BE SURE TO PREFACE LABEL WITH YOUR OWN INITIALS (NVR in this example) --
\newcommand{\NVRvect}[1]{\ensuremath\boldsymbol{#1}}
\newcommand{\NVRtensor}[1]{\underline{\NVRvect{#1}}}
\newcommand{\NVRnorm}[1]{\left|\left|#1\right|\right|}
\newcommand{\NVRgrad}{\nabla}
\newcommand{\NVRdiv}{\NVRgrad \cdot}
\newcommand{\NVRpd}[2]{\frac{\partial#1}{\partial#2}}
\newcommand{\NVRpdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
\newcommand{\NVReqdef}{\stackrel{\text{\tiny def}}{=}}

\newcommand{\NVRcurl}{\nabla \times}
\newcommand{\NVRHgrad}{H(\text{grad})}
\newcommand{\NVRHcurl}{H(\text{curl})}
\newcommand{\NVRHdiv}{H(\text{div})}
\newcommand{\NVRsumm}[2]{\ensuremath\displaystyle\sum\limits_{#1}^{#2}}

% This controls the table-of-contents entry in the proceedings. Edit it
% to include your article title followed by the authors' names, as shown.
\addcontentsline{toc}{chapter}{Application of a Discontinuous Petrov-Galerkin Method to the Stokes Equations\\
{\em N.V.\ Roberts, D.\ Ridzal, P.B.\ Bochev, L.D.\ Demkowicz}}

\pagestyle{myheadings}

\thispagestyle{plain}

% This gives the running head. Usually you list a shortened version of
% your article title (unless it's already very short) along with
% the author's names, as shown.
\markboth{DPG Trilinos Toolbox}{N.~V.\ Roberts, D.\ Ridzal, P.~B.\ Bochev, L.~D.\ Demkowicz}

% Put your article title in here
\title{A Toolbox for a Class of Discontinuous
       Petrov-Galerkin Methods Using Trilinos\thanks{Also available as Sandia Report SAND2011-6678.
                 Sandia National Laboratories is a multi-program laboratory
                 managed and operated by Sandia Corporation, a wholly owned subsidiary of
                 Lockheed Martin Corporation, for the U.S. Department of
                 Energy's National Nuclear Security Administration under
                 contract DE-AC04-94AL85000.}}

% List each author, their affiliation, and their e-mail address, as shown.
\author{
Nathan V.\ Roberts\thanks{The University of Texas at Austin,
Institute for Computational Engineering and Science,
201 E 24th St,
Austin, TX 78712. E-mail: nroberts@ices.utexas.edu.  Research sponsored by The Center for Predictive Engineering and COmputational Sciences (PECOS). PECOS is a DOE-funded Center of Excellence within the Institute for Computational Engineering and Sciences (ICES) at The University of Texas at Austin.}
\and
Denis Ridzal\thanks{Optimization and Uncertainty Quantification, MS-1320,
                 Sandia National Laboratories, P.O. Box 5800,
                 Albuquerque, NM 87185-1320.  E-mail: dridzal@sandia.gov.
                 Research sponsored by the Office of Science ASCR program.}
\and
Pavel B.\ Bochev\thanks{Numerical Analysis and Applications, MS-1320,
                 Sandia National Laboratories, P.O. Box 5800,
                 Albuquerque, NM 87185-1320.  E-mail: pbboche@sandia.gov.
                 Research sponsored by the Office of Science ASCR program.}
\and
Leszek D.\ Demkowicz\thanks{The University of Texas at Austin,
Institute for Computational Engineering and Science,
201 E 24th St,
Austin, TX 78712. E-mail: leszek@ices.utexas.edu.. Research sponsored by PECOS.}  }

\begin{document}

\maketitle

% Include your abstract here.
\begin{abstract}
The class of discontinuous Petrov-Galerkin finite element methods (DPG) proposed by L. Demkowicz and J. Gopalakrishnan \cite{DPG1,DPG2} guarantees the optimality of the solution in an energy norm and produces a symmetric positive definite stiffness matrix, among other desirable properties.  In this paper, we describe a toolbox, implemented atop Sandia's Trilinos Project \cite{Trilinos}, for rapid development of solvers for DPG methods.  We use this toolbox to develop solvers for the Poisson and Stokes problems.
\end{abstract}

\input{paper.tex}

\end{document}

### 2012-03-08 docs/presentations/nate/Proposal/paper.tex
Initial start on the Proposal.  Just copied and pasted stuff from the Sandia report, mostly.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@371 36274a68-8941-4c93-80ef-affaed5139da

\section{Abstract Theory}

\section{Analysis of the Stokes Equations}
The strong form of the Stokes problem with which we begin is as follows:

\begin{align}
- \mu \Delta \NVRvect{u} + \NVRgrad p &= \NVRvect{f} & \text{ in } \Omega, \label{NVR:eq:strongfirst1} \\
\NVRdiv \NVRvect{u} &= 0 & \text{ in } \Omega, \\
\NVRvect{u} &= \NVRvect{g_{D}} & \text{ on } \partial\Omega,\label{NVR:eq:stronglast1}
\end{align}
where $\Omega \subset \mathbb{R}^{2}$, $\mu$ is viscosity, $\NVRtensor{\epsilon}=\NVRgrad^{\text{sym}} \NVRvect{u}$ is strain, $p$ is pressure, $u$ velocity, and $\NVRvect{f}$ a vector forcing function.

For DPG, we require a first-order system.  We introduce $\NVRtensor{\sigma}=\mu \NVRgrad \NVRvect{u}$:
\begin{align}
\frac{1}{\mu} \NVRtensor{\sigma} - \NVRgrad \NVRvect{u} &= 0 \\
- \mu \NVRdiv \NVRtensor{\sigma} + \NVRgrad p &= \NVRvect{f} & \text{ in } \Omega, \label{NVR:eq:strongfirst2} \\
\NVRdiv \NVRvect{u} &= 0 & \text{ in } \Omega, \\
\NVRvect{u} &= \NVRvect{g_{D}} & \text{ on } \partial\Omega,\label{NVR:eq:stronglast2}
\end{align}

%% Everything that follows is my write-up from Sandia, Summer 2011.  Kept here for reference and possibly to crib from it later.  (The tutorial-type stuff might make a nice appendix.)

\pagebreak

This page intentionally left blank.  What follows is old material.
\pagebreak

\section{Introduction}\label{NVR:sec:intro}
Recently, L. Demkowicz and J. Gopalakrishnan have proposed a new class of discontinuous Petrov-Galerkin (DPG) methods \cite{DPG1,DPG2,DPG3,DPG4,DPG5}, which compute test functions that are adapted to the problem of interest to produce stable discretization schemes.  An important choice that must be made in the application of the method is the definition of the inner product on the test space.  In this paper, we describe a toolbox for rapid development of solvers for DPG methods, implemented atop Sandia's Trilinos Project \cite{Trilinos}, using especially the Intrepid package of interoperable tools for compatible discretizations \cite{Intrepid}.  We use our DPG toolbox to develop solvers for the Poisson and Stokes problems.

Whereas traditional Galerkin methods use the same space for test and trial spaces, Petrov-Galerkin methods allow the test and trial spaces to differ.  The DPG approach computes test functions that are \emph{optimal}, in a sense that we make precise in Section~\ref{NVR:sec:DPGintro}.  One consequence of this choice of test functions is that the stiffness matrix for a continuous, weakly coercive variational formulation is symmetric (hermitian, for complex-valued problems) and positive definite.  Of course, the determination of test functions is an extra step compared with traditional methods; it is important that these can be determined cheaply.  By using discontinuous Galerkin (DG) formulations, DPG achieves this, reducing the computation of the test functions to a local problem.  Our method bears some resemblance to the MDG method \cite{Hughes} in that a local problem is solved on each element. The key difference with that paper is that in MDG the local problem is restriction of the original equations whereas in DPG the local problem is implied by the selected test space inner product. Furthermore, in MDG the local problem is used to express DG degrees of freedom in terms of continuous degrees of freedom, i.e., to effect static condensation on the element.

We have implemented a toolbox for solving PDEs using DPG.  Our eventual goal is to produce an $hp$-adaptive implementation of DPG which allows implementation of a solver for a new variational formulation with minimal effort.  Currently, $p$-refinements are functional and the code is designed in anticipation of $h$-refinement, although $hp$-adaptivity is not yet completed.  The code supports both triangular and quadrilateral elements of arbitrary order.

The paper is structured as follows.  In Section \ref{NVR:sec:DPGintro}, we give an introduction to the basic features of the DPG method.  In Section \ref{NVR:sec:poissonForm}, we derive the weak formulation of the Poisson problem.  We describe two commonly used test space norms which the code explicitly supports in Section \ref{NVR:sec:testNorms}.  In Section \ref{NVR:sec:codeOverview}, we give a brief overview of the code.  In Section \ref{NVR:sec:poissonImplementation} we give complete details on implementing the Poisson formulation using our toolbox.  We then discuss mesh generation and solving in Section \ref{NVR:sec:meshAndSolve}.  We briefly discuss two Stokes formulations in Section \ref{NVR:sec:stokesForm}.  In Section \ref{NVR:sec:numericalResults} we present some numerical results produced using the code.  We conclude in Section \ref{NVR:sec:conclusion}.

\section{DPG Method}\label{NVR:sec:DPGintro}
Here, we sketch some of the main features of the DPG method.  For details, we refer the reader to a series of papers by Demkowicz et al., in particular the second ICES Report \cite{DPG2}, from which most of this section is derived.  We begin with theoretical definitions and results, and then describe the approach to practical realization.  Consider the abstract variational boundary-value problem:
\begin{align}
\text{Find } u \in U : b(u,v) = l(v) \quad \forall v \in V.\label{NVR:eq:avbvp}
\end{align}
We take $U$ and $V$ to be real Hilbert spaces.  We assume $b(\cdot,\cdot)$ is continuous, i.e.\
\begin{align}
|b(u,v)| \leq M \NVRnorm{u}_{U} \NVRnorm{v}_{V},
\end{align}
for some real $M$. We assume also that $b(\cdot,\cdot)$ is weakly coercive, that is
\begin{align}
\inf_{\NVRnorm{u}_{U}=1} \sup_{\NVRnorm{v}_{V}=1} b(u,v) > \gamma,
\end{align}
for some $\gamma > 0$.  If we additionally assume that
\begin{align}
\{v \in V : b(u,v)=0 \quad \forall u \in U\} = \{0\},
\end{align}
then it is well known that the problem \eqref{NVR:eq:avbvp} has a unique solution provided that $l \in V'$, the dual of $V$.

\subsection{Energy Norm}
We define an alternate norm, called the \emph{energy norm}, on the trial space $U$ by
\begin{equation}\label{NVR:eq:energyNorm}
\NVRnorm{u}_{E} \NVReqdef \sup_{\NVRnorm{v}_{V}=1} b(u,v).
\end{equation}
This norm is the one in which the optimality is guaranteed by the selection of optimal test functions. It is an equivalent norm to the standard norm on $U$, i.e.\
\begin{equation}
\gamma \NVRnorm{u}_{U} \leq \NVRnorm{u}_{E} \leq M \NVRnorm{u}_{U} \quad \forall u \in U.
\end{equation}

\subsection{Optimal Test Functions}
We are now prepared to give a definition of the optimal test functions.  Define a map $T:U \rightarrow V$ from the trial space to the test space by: For $u \in U$, define $Tu$, the \emph{optimal test function} corresponding to $u$, as the unique solution to 
\begin{align*}
(Tu,v)_{V} = b(u,v) \quad \forall v \in V.
\end{align*}
By the Riesz representation theorem, $T$ is well-defined.  Note that 
\begin{align*}
\NVRnorm{u}_{E} = \sup_{\NVRnorm{v}_{V}=1} b(u,v) = \sup_{\NVRnorm{v}_{V}=1} (Tu,v)_{V} = \frac{1}{\NVRnorm{Tu}_{V}} (Tu, Tu)_{V} = \NVRnorm{Tu}_{V}.
\end{align*}
Thus the energy norm is generated by the inner product on $V$, i.e.\ 
\begin{equation}
(u,u)_{E} \NVReqdef (Tu,Tu)_{V}.\label{NVR:eq:ipEqualsEnergy}
\end{equation}
In practice, we approximate $T$ by a discrete operator $T_{n}$, described in Section \ref{NVR:sec:practicalRealization}.
\subsection{Optimal Test Space for $U_{n}$}
Take a finite-dimensional trial space $U_{n} \subset U$.  Define the \emph{optimal test space} for $U_{n}$ as $V_{n} = \text{span} \{Te_{j} : j=1,\cdots,n\}$, where the $e_{j}$ form a basis for $U_{n}$.

Solve the discrete problem
\begin{equation}
\text{Find } u_{n} \in U_{n} : b(u_{n}, v) = l(v) \ \forall v \in V_{n}. \label{NVR:eq:discreteAVBVP}
\end{equation}
Then the error is the best approximation error in the energy norm,
\begin{align}
\NVRnorm{u-u_{n}}_{E} = \inf_{w_{n} \in U_{n}} \NVRnorm{u-w_{n}}_{E},\label{NVR:eq:optimalityEqn}
\end{align}
and this is the sense in which the test space is \emph{optimal}.

\subsection{Practical Realization}\label{NVR:sec:practicalRealization}
The method involves two steps: first, find the optimal test functions; second, use the optimal test functions to solve the discrete problem \ref{NVR:eq:discreteAVBVP}.  The optimal test functions are not in general polynomials.  In practice, we approximate them with an ``enriched'' polynomial space --- a space of polynomials of slightly higher degree than the trial space.  This is done to provide a higher-fidelity approximation to the continuous space of optimal test functions.  The best choice for the amount of ``enrichment'' is determined experimentally for each problem.

In general, we apply the following procedure:
\begin{enumerate}
\sloppy
\item Given a boundary value problem, develop mesh-dependent $b(\cdot,\cdot)$ with test space $V$ that allows inter-element discontinuities (hence \emph{Discontinuous} Petrov-Galerkin).  We develop this in Section \ref{NVR:sec:stokesForm}.
\item Choose trial space $U_{n}$ (in particular the norm of interest in $U_{n}$), and the inner product on $V$, which will be motivated by the choice of trial space.
%We detail this process for the Poisson problem in Section \ref{NVR:sec:innerProductSpecification}.
\item Compute optimal test functions.
Approximate $T$ by $T_{n}: U_{n} \rightarrow \widetilde{V}_{n} \subset V$.  We use an enriched space of piecewise polynomials for $\widetilde{V}_{n}$.  Defining $t_{j} = T_{n} e_{j}$, we solve
\begin{eqnarray*}
(t_{j},\tilde{e}_{i})_{V} = b(e_{j},\tilde{e}_{i})
\end{eqnarray*}
for $t_{j}$, where the $\tilde{e}_{i}$ form the basis for $\widetilde{V}_{n}$.
\item Use the optimal test functions to solve the problem on $U_{n} \times \widetilde{V}_{n}$.  We note that the stiffness matrix here is symmetric positive definite (hermitian, for a complex-valued problem),
\begin{align*}
b(e_{j},t_{i}) &= (T_{n}e_{j}, t_{i})_{V} = (T_{n}e_{j}, T_{n}e_{i})_{V} = \overline{(T_{n}e_{i}, T_{n}e_{j})}_{V} \\
               &= \overline{(T_{n}e_{i}, t_{j})}_{V} = \overline{b(e_{i}, t_{j})}.
\end{align*}
Also, note that this means that we may compute the stiffness matrix in terms of the inner product on the test space $V$, without explicit recourse to the bilinear form.
\end{enumerate}

\section{Poisson Formulation}\label{NVR:sec:poissonForm}
Our general approach to variational formulations in DPG is as follows.  First, rewrite the strong form of the problem as a system of first-order partial differential equations.  Then, multiply by test functions and integrate by parts, moving all derivatives to the test functions, introducing fluxes and traces wherever the trial space variables appear in boundary integrals.  We thus arrive at the \emph{ultra-weak} form of the problem, a formulation in which all solution variables are in $L^{2}$.

We apply the DPG method to the Poisson problem in two dimensions:
\begin{align*}
\nabla \cdot \nabla \phi = f.
\end{align*}
We define $\bf{\psi} = \nabla \phi$ and rewrite as a first-order system:
\begin{align*}
\nabla \phi - \psi &= 0\\
\nabla \cdot \psi &= f.
\end{align*}
Multiply by test functions and integrate:
\begin{align*}
\int_K \nabla \phi \cdot \bf{q} - \int_K \psi \cdot \bf{q} &= 0\\
\int_K \nabla \cdot \psi \: v &= \int_K f v.
\end{align*}
Integrate by parts, introducing flux $\widehat{\psi}_n$ and trace $\widehat{\phi}$ on the boundary:
\begin{align*}
- \int_K \phi \nabla \cdot \bf{q} - \int_K \psi \cdot \bf{q} + \int_{\partial K} \widehat{\phi} \: \bf{q} \cdot \bf{n} &= 0\\
- \int_K \psi \cdot \nabla v + \int_{\partial K} \widehat{\psi}_n \: v &= \int_K f v \,.
\end{align*}

\section{Two Standard Choices for Test Space Norm}\label{NVR:sec:testNorms}
In this section, we describe two commonly used norms on the test space --- recall that the choice of test space norm will determine the energy norm, and thus the sense in which test functions are optimal.  Our implementation makes usage of these norms simple.
\subsection{Mathematician's Norm}
In general, test functions in a variational form each belong to some functional space on which a norm is already defined.  Therefore, a mathematically natural choice for a norm on the test space will be the Euclidean combination of these norms.  In the case of our Poisson formulation, $\NVRvect{q} \in \NVRHdiv$ and $v \in \NVRHgrad$, so define
\begin{align*}
\NVRnorm{(\NVRvect{q},v)}_{V}^{2}  \NVReqdef \int_{\Omega} &\left((\NVRdiv \NVRvect{q})^{2} + \NVRvect{q} \cdot \NVRvect{q} + \NVRgrad v \cdot \NVRgrad v + v^{2}\right)\\
\end{align*}
as the \emph{mathematician's} norm on the test space.

\subsection{Optimal and Quasi-Optimal Test Norms}
We know from the analysis that DPG delivers the best solution in the \emph{energy norm}, and that the choice of norm on the test space determines the energy norm.  We can then ask whether it is possible to select the test space norm in such a way that the energy norm is exactly the norm of interest ($L^{2}$, in our case) --- and the answer is yes; this is given in the abstract setting by 
\begin{align*}
\NVRnorm{v}_{V}\NVReqdef \sup_{\NVRnorm{u}_{U}=1} b(u,v),
\end{align*}
where $\NVRnorm{\cdot}_{U}$ is the norm of interest.  $\NVRnorm{\cdot}_{V}$ is then called the \emph{optimal test norm}.  To determine the optimal test norm, we can collect terms by trial space variable, and then take the supremum using the Cauchy-Schwarz inequality.  When we do so, we will have some element boundary terms arising from the fluxes and traces.  To make the test norm \emph{localizable}, we then replace these terms with $L^{2}$ terms on the element interior, often with some weight $\beta$.  The resultant norm we call the \emph{quasi-optimal test norm}.

\section{Code Overview}\label{NVR:sec:codeOverview}
The directory layout in our code repository is as follows:
\begin{center}
\begin{minipage}{0.4\textwidth}
{\bf
\begin{lstlisting}[backgroundcolor=\color{lightlightgreen}]
 ||-Drivers
 ||---DPGTests
 ||---MultiOrderStudy
 ||---Poisson
 ||---Stokes
 ||-SummerProceedings2011
 ||-build
 ||-presentation
 ||-src
 ||---Basis
 ||---ConvergenceStudy
 ||---DofOrdering
 ||---InnerProduct
 ||---Mesh
 ||---Problem
 ||---Solution
 ||---visualization
\end{lstlisting}
}
\end{minipage}
\end{center}

The core code is in the \verb=src= directory.  Within this, \verb=Basis= contains classes related to basis functions.  \verb=ConvergenceStudy= contains the \verb=HConvergenceStudy= class, discussed below in Section \ref{NVR:sec:HConvergenceStudy}, which provides support for studying convergence rates.  \verb=DofOrdering= contains a utility class for maintaining the ordering of coefficients related to the bases of interest.  \verb=InnerProduct= contains classes related to implementation of the test-space inner product, discussed in detail in Section \ref{NVR:sec:innerProductSpecification}.  \verb=Mesh= contains classes related to meshing and elements; Section \ref{NVR:sec:mesh} details mesh construction.  The \verb=Problem= directory contains classes for the specification of the bilinear form, right hand side, and boundary conditions, discussed in Sections \ref{NVR:sec:poissonBilinearForm}, \ref{NVR:sec:poissonRHS}, and \ref{NVR:sec:poissonBCs}, respectively, using the Poisson problem as a motivating example.  \verb=Solution= contains classes for solving such problems, as well as for the specification of exact (manufactured) solutions; these are discussed in Sections \ref{NVR:sec:ExactSolution} and \ref{NVR:sec:Solution}.  Finally, the \verb=visualization= directory contains a MATLAB script, discussed in Section \ref{NVR:sec:visualization}, for plotting solutions.

Several sample drivers can be found in the \verb=Drivers= directory; \verb=DPGTests= runs a test suite against the core code, \verb=StokesStudy=, \verb=StokesStudyHybridMesh= and \verb=PoissonStudy= are drivers built with the \verb=HConvergenceStudy= class, used to produce the results in Section \ref{NVR:sec:numericalResults}.

The \verb=SummerProceedings2011= directory contains the TeX source files, plots, and raw data used used to produce this document.  The \verb=presentation= directory contains a presentation covering much the same material.

Finally, the \verb=build= directory contains a makefile that can be used to build the core code and the drivers.

\section{Poisson Implementation}\label{NVR:sec:poissonImplementation}
We now detail the implementation of Poisson using the toolbox we have developed.  To specify a PDE to solve, we need to define the following:
\begin{itemize}
\item a bilinear form,
\item a right-hand side, and
\item boundary conditions.
\end{itemize}

Our DPG implementation is intended to make it simple to specify each of these, once a first-order weak formulation has been derived.

\subsection{Poisson Bilinear Form}\label{NVR:sec:poissonBilinearForm}
Our bilinear form is given by
\begin{align*}
b(\cdot,\cdot) = &- \int_K \phi \nabla \cdot \bf{q} - \int_K \psi \cdot \bf{q} + \int_{\partial K} \widehat{\phi} \: \bf{q} \cdot \bf{n}\\
&- \int_K \psi \cdot \nabla v + \int_{\partial K} \widehat{\psi}_n \: v \,.
\end{align*}

Bilinear forms should subclass \verb=BilinearForm=.  This abstract class provides the routines required for the rest of the toolbox to determine the optimal test functions, produce the global stiffness matrix, and solve the system.  The first step in subclassing is to populate two \verb=vector<int>= structures provided by \verb=BilinearForm=, \verb=_trialIDs= and \verb=_testIDs=.  These are simply integer identifiers that the subclass uses for each of the trial and test variables.   A typical approach is to define an enumeration for each of these in the subclass header file, and populate the vectors with these in the subclass constructor.

In the Poisson formulation, we have:
\begin{itemize}
\item two test functions ($\bf{q}$ and $v$),
\item one scalar trial ``field'' variable ($\phi$),
\item one vector trial ``field'' variable ($\bf{\psi}$, which our implementation requires us to split into scalars $\bf{\psi}_{1}$ and $\bf{\psi}_{2}$),
\item one flux ($\widehat{\psi}_n$),
\item and one trace ($\widehat{\phi}$).
\end{itemize}

Here is a snippet, defining the identifiers we wish to use for test and trial functions, from \verb=PoissonBilinearForm.h=:
\begin{lstlisting}
enum ETestIDs {
  Q_1 = 0,
  V_1
};

enum ETrialIDs {
  PHI_HAT = 0,
  PSI_HAT_N,
  PHI,
  PSI_1,
  PSI_2
};
\end{lstlisting}

The constructor for \verb=PoissonBilinearForm= simply populates \verb=_trialIDs= and \verb=_testIDs= with these enumeration values:
\begin{lstlisting}
PoissonBilinearForm::PoissonBilinearForm() {
  _testIDs.push_back(Q_1);
  _testIDs.push_back(V_1);

  _trialIDs.push_back(PHI_HAT);
  _trialIDs.push_back(PSI_HAT_N);
  _trialIDs.push_back(PHI);
  _trialIDs.push_back(PSI_1);
  _trialIDs.push_back(PSI_2);
}
\end{lstlisting}

\verb=BilinearForm= also contains several virtual member functions that subclasses must override:
\begin{enumerate}
\item \verb=const string & testName(int testID)=,
\item \verb=const string & trialName(int trialID)=,
\item \verb=EFunctionSpaceExtended=\\ ${ }\qquad$ \verb=functionSpaceForTest(int testID)=,
\item \verb=EFunctionSpaceExtended=\\ ${ }\qquad$ \verb=functionSpaceForTrial(int trialID)=,
\item \verb=bool isFluxOrTrace(int trialID)=,
\item either \verb=bool trialTestOperator(...)=, or\\
      ${ }\mspace{45mu}$ \verb=void trialTestOperators(...)=,
\item and one of the two forms of \verb=void applyBilinearFormData(...)=.
\end{enumerate}

For \verb=testName()= and \verb=trialName()=, we recommend using LaTeX-compatible strings, because \verb=BilinearForm= can output a TeX-friendly string representation of the bilinear form as implemented, a valuable debugging tool.  Here is a snippet defining these, from \verb=PoissonBilinearForm.cpp=:
\begin{lstlisting}
// trial variable names:
static const string & S_PHI = "\\phi";
static const string & S_PSI_1 = "\\psi_1";
static const string & S_PSI_2 = "\\psi_2";
static const string & S_PHI_HAT = "\\hat{\\phi}";
static const string & S_PSI_HAT_N ="\\hat{\\psi}_n";
static const string & S_DEFAULT_TRIAL = "invalid trial";

// test variable names:
static const string & S_Q_1 = "q_1";
static const string & S_V_1 = "v_1";
static const string & S_DEFAULT_TEST = "invalid test";

const string & PoissonBilinearForm::testName(int testID) {
  switch (testID) {
    case Q_1:
      return S_Q_1;
    break;
    case V_1:
      return S_V_1;
    break;
    default:
      return S_DEFAULT_TEST;
} }

const string & PoissonBilinearForm::trialName(int trialID) {
  switch(trialID) {
    case PHI:
      return S_PHI;
    break;
    case PSI_1:
      return S_PSI_1;
    break;
    case PSI_2:
      return S_PSI_2;
    break;
    case PHI_HAT:
      return S_PHI_HAT;
    break;
    case PSI_HAT_N:
      return S_PSI_HAT_N;
    break;
    default:
      return S_DEFAULT_TRIAL;
} }
\end{lstlisting}

Next, we need to define the continuous spaces to which the test and trial functions belong.  These are defined by enumeration \verb=EFunctionSpaceExtended= in namespace \verb=IntrepidExtendedTypes= (specified in \verb=BilinearForm.h=); this mirrors names and values in \verb=IntrepidTypes::EFunctionSpace=, with the intent of adding spaces to support features such as local conservation.  In general in DPG, trial space functions will be in $L^{2}$, with the exception of traces, which will be in $H^{1}$.  The appropriate test space for a given test function is determined by the derivatives applied to that test function --- thus $\bf{q} \in \NVRHdiv$ and $v \in \NVRHgrad$.  Here is the code for the Poisson bilinear form:
\begin{lstlisting}
EFunctionSpaceExtended
PoissonBilinearForm::functionSpaceForTrial(int trialID) {
  // Field variables, and fluxes, are all L2.
  if (trialID != PHI_HAT) {
    return IntrepidExtendedTypes::FUNCTION_SPACE_HVOL;
  } else {
    return IntrepidExtendedTypes::FUNCTION_SPACE_HGRAD;
} }

EFunctionSpaceExtended
PoissonBilinearForm::functionSpaceForTest(int testID) {
  switch (testID) {
    case Q_1:
      return IntrepidExtendedTypes::FUNCTION_SPACE_HDIV;
    break;
    case V_1:
      return IntrepidExtendedTypes::FUNCTION_SPACE_HGRAD;
    break;
    default:
      throw "Error: unknown testID";
} }
\end{lstlisting}

We also need to specify which of our trial variables are field variables and which are fluxes or traces.  This is accomplished by overriding \verb=isFluxOrTrace()=:
\begin{lstlisting}
bool PoissonBilinearForm::isFluxOrTrace(int trialID) {
  if ((PHI_HAT==trialID) || (PSI_HAT_N==trialID)) {
    return true;
  } else {
    return false;
} }
\end{lstlisting}

We have now entirely defined the variables that enter the bilinear form.  If we now call \verb=BilinearForm='s \verb=printTestTrialInteractions()= method, we get the following output:
\begin{lstlisting}
****** Interactions with test variable q_1 ******* 
\int_{\partial K} \hat{\phi} q_1 - \int_{K} \phi \nabla \cdot q_1
- \int_{K} \psi_1 \bf{i} \cdot q_1 - \int_{K} \psi_2 \bf{j} \cdot q_1

****** Interactions with test variable v_1 ******* 
\int_{\partial K} \hat{\psi}_n v_1 
- \int_{K} \psi_1 \frac{\partial}{\partial x} v_1
- \int_{K} \psi_2 \frac{\partial}{\partial y} v_1
\end{lstlisting}

Each of these lines can be pasted into a TeX document and rendered for comparison with the intended bilinear form.  Note that this method will only work approximately when material data varies in space, but for constant material data, it should provide an exact representation of the bilinear form as implemented.

To complete the specification of the bilinear form, we need to define the way that test and trial variables interact, as well as apply material data.  The former is specified in terms of operators that should be applied a test and trial pair.  In most simple bilinear forms, a given (test, trial) pair will appear only once.  In this case, the single-operator \verb=bool trialTestOperator()= method may be used.  The subclass should return \verb=true= if the pair appears in the bilinear form, and \verb=false= otherwise.  If the pair does appear, then the subclass should set the test and trial operators passed in.  Note that because our approach splits the vector $\psi$ into two scalars $\psi_{1}$ and $\psi_{2}$, the $\psi \cdot \nabla v$ term must be split into $\psi_{1} \NVRpd{}{x} v +  \psi_{2} \NVRpd{}{y} v$.  The code appears below.
\begin{lstlisting}
bool PoissonBilinearForm::trialTestOperator(int trialID, 
                         int testID, 
                         EOperatorExtended &trialOperator, 
                         EOperatorExtended &testOperator) {
 // being DPG, trialOperator will always be OPERATOR_VALUE
 trialOperator = IntrepidExtendedTypes::OPERATOR_VALUE;
 // unless we specify otherwise, 
 // trial and test don't interact:
 bool returnValue = false; 
 switch (testID) {
   case Q_1:
     switch (trialID) {
       case PSI_1:
         returnValue = true;
         // x component of q1 against psi1 (dot product):
         testOperator = IntrepidExtendedTypes::OPERATOR_X;
         break;
       case PSI_2:
         returnValue = true;
         // y component of q1 against psi1 (dot product)
         testOperator = IntrepidExtendedTypes::OPERATOR_Y; 
         break;
       case PHI:
         returnValue = true;
         testOperator = IntrepidExtendedTypes::OPERATOR_DIV;
         break;
       case PHI_HAT:
        returnValue = true;
        testOperator = IntrepidExtendedTypes::OPERATOR_VALUE;
        break;
       default:
         break;
     }
     break;
   case V_1:
     switch (trialID) {
       case PSI_1:
         returnValue = true;
         testOperator = IntrepidExtendedTypes::OPERATOR_DX;
         break;
       case PSI_2:
         returnValue = true;
         testOperator = IntrepidExtendedTypes::OPERATOR_DY;
         break;
       case PSI_HAT_N:
        returnValue = true;
        testOperator = IntrepidExtendedTypes::OPERATOR_VALUE;
        break;
       default:
         break;
     }
   default:
     break;
 }
 return returnValue;    
}
\end{lstlisting}

The multi-operator version is similar, with multiple \verb=EOperatorExtended= values being specified for each test and trial function.

We now specify the material data by overriding \verb=applyBilinearFormData=; there is a variant for both the multi- and single-operator implementations.  This will be called only for (test, trial) pairs that have non-zero interaction in the bilinear form.  The arguments to the single-argument variant of \verb=applyBilinearFormData= are as follows:
\begin{itemize}
\item \verb=int trialID=: the trial variable identifier
\item \verb=int testID=: the test variable identifier
\item \verb=FieldContainer<double> &testTrialValuesAtPoints=:\\
      values to which the material data should be applied 
\item \verb=FieldContainer<double> &points=: the spatial points at which the material data is applied
\end{itemize}

There is a static convenience function, \verb=multiplyFCByWeight()= implemented in \verb=BilinearForm=, which simply multiplies all the values in an Intrepid FieldContainer by a given weight.  This is convenient in a case like our Poisson problem, in which the material data is constant.
\begin{lstlisting}
void PoissonBilinearForm::applyBilinearFormData(int trialID,
            int testID, 
            FieldContainer<double> &testTrialValuesAtPoints, 
            FieldContainer<double> &points) {
  switch (testID) {
    case Q_1:
      // - (phi, div q1)_K + (phi_hat, q_1n)_dK - (psi, q1)
      switch (trialID) {
        case PHI:
          // negate
          multiplyFCByWeight(testTrialValuesAtPoints,-1.0);
        break;
        case PSI_1:
          // negate
          multiplyFCByWeight(testTrialValuesAtPoints,-1.0);
        break;
        case PSI_2:
          // negate
          multiplyFCByWeight(testTrialValuesAtPoints,-1.0);         
        break;
        case PHI_HAT:
          // do nothing -- testTrialValuesAtPoints already
          //               has the right values 
        break;
      }
    break;
    case V_1:
      switch(trialID) {
      // -(psi, grad v1)_K + (psi_hat_n, v1)_dK
        case PHI:
          throw "Error: no (v1, phi) term";
        break;
        case PSI_1:
          // negate
          multiplyFCByWeight(testTrialValuesAtPoints,-1.0);
        break;
        case PSI_2:
          // negate
          multiplyFCByWeight(testTrialValuesAtPoints,-1.0);
        break;
        case PSI_HAT_N:
          // do nothing -- testTrialValuesAtPoints already
          //               has the right values
         break;
      }
    break;
} }
\end{lstlisting}

\subsection{Poisson Right-Hand Side}\label{NVR:sec:poissonRHS}
To specify the right hand side, we subclass \verb=RHS=, overriding two functions:
\begin{enumerate}
\item \verb=bool nonZeroRHS(int testVarID)=, and
\item \verb=void rhs(int testVarID, FC &physicalPoints, FC &values)=.
\end{enumerate}

There are several versions of such implementations for Poisson.  Below, we quote from \verb=PoissonRHSCubic=.  A call to \verb=nonZeroRHS(int testVarID)= should return \verb=true= for any test variable which has a non-zero right-hand side.  For Poisson, the only such test variable is $v$; we integrate a function $f$ against it.  A call to
\verb=rhs(testVarID, physicalPoints, values)=
is responsible for providing the values of the function $f$ at points \verb=physicalPoints= by populating \verb=values=.  Taking an exact solution $\phi=x^{3}+2y^{3}$, we have $f=\nabla \cdot \nabla \phi = 6x+12y$.  Thus our subclass implements the right hand side as follows:
\begin{lstlisting}
bool PoissonRHSCubic::nonZeroRHS(int testVarID) {
  if (testVarID == PoissonBilinearForm::Q_1) { 
    // the vector test function, zero RHS:
    return false;
  } else if (testVarID == PoissonBilinearForm::V_1) {
    return true;
  } else {
    return false; // could throw an exception here
} }

void PoissonRHSCubic::rhs(int testVarID, 
                   FieldContainer<double> &physicalPoints,
                   FieldContainer<double> &values) {
  // for an exact solution of x^3 + 2y^3, f = 6x + 12y
  int numCells = physicalPoints.dimension(0);
  int numPoints = physicalPoints.dimension(1);
  int spaceDim = physicalPoints.dimension(2);
  if (testVarID == PoissonBilinearForm::V_1) {
    values.resize(numCells,numPoints);
    for (int cellIndex=0; cellIndex<numCells; cellIndex++) {
      for (int ptIndex=0; ptIndex<numPoints; ptIndex++) {
        double x = physicalPoints(cellIndex,ptIndex,0);
        double y = physicalPoints(cellIndex,ptIndex,1);
        values(cellIndex,ptIndex) = 6.0*x + 12.0*y;
} } } }
\end{lstlisting}

\subsection{Poisson Boundary Conditions}\label{NVR:sec:poissonBCs}
Because we are interested the Poisson problem as a prototype for Stokes, we would like to apply Dirichlet conditions to $\psi$, leaving $\phi$ to enter the original, strong form of the equation only through a gradient, analogous to the way that pressure enters the Stokes equations.  In DPG, we apply boundary conditions through the fluxes and traces, because these are the only variables formally defined on the boundary.  Thus a boundary condition $\psi \cdot n=g$ on $\partial \Omega$ becomes $\widehat{\psi}_{n}=g$ on $\partial \Omega$.  To make the problem well-posed, we do need to pin down $\phi$.  Two ways of doing this are supported by the code --- first, a single point value can be imposed as a Dirichlet-like condition on a field variable.  This is a discrete trick that may bring some numerical difficulties such as bad conditioning with it --- such has been our experience.  A second way to make the problem well-posed is to impose a zero-mean condition on $\psi$.  This carries with it slightly more computational cost than the other approach, but has better numerical properties.  The implementation for the latter follows the procedure described in \cite{BochevLehoucq}.

All the boundary conditions described above can be defined by subclassing the \verb=BC= class.  The methods available for overriding are:
\begin{itemize}
\item \verb=bool bcsImposed(int varID)=:\\ specifies whether BCs are anywhere imposed for \verb=varID=;
\item \verb=void imposeBC(...)=:\\ requests imposition of BCs at boundary points;
\item \verb=bool singlePointBC(int varID)=:\\ specifies whether to impose a single-point BC on a field variable;
\item \verb=bool imposeZeroMeanConstraint(int varID)=:\\ specifies whether to impose a zero-mean constraint on a field variable.
\end{itemize}
The \verb=imposeBC()= method takes arguments:
\begin{itemize}
\item \verb=int varID=:\\ the variable for which BCs are requested;
\item \verb=FieldContainer<double> &physicalPoints=:\\ the points at which BCs might be imposed,  dimensions are (C,P,D);
\item \verb=FieldContainer<double> &unitNormals=:\\ outward unit normals at the specified points,  dimensions are (C,P,D);
\item \verb=FieldContainer<double> &dirichletValues=:\\ the values to impose at the specified points, dimensions are (C,P);
\item \verb=FieldContainer<bool> &imposeHere=:\\ whether to impose the BC at the specified point, dimensions are (C,P).
\end{itemize}
The final \verb=imposeHere= argument allows boundary conditions to be specified only along part of the boundary.

In the \verb=PoissonBCCubic= class, we take the single-point option for the condition on $\phi$, and impose a Dirichlet condition everywhere along the boundary for $\widehat{\psi}_{n}$.  Since $\phi=x^{3}+2y^{3}$, $\psi=\nabla \phi = {3 x^{2} \choose 6 y^{2}}$, so that $\psi \cdot n = 3x^{2}n_{1} + 6 y^{2} n_{2}$; this is the value we impose on $\widehat{\psi}_{n}$.  The code appears below, somewhat redacted, for space and clarity:
\begin{lstlisting}
bool PoissonBCCubic::bcsImposed(int varID){
  return varID == PoissonBilinearForm::PSI_HAT_N;
}

bool PoissonBCCubic::singlePointBC(int varID) {
  return varID == PoissonBilinearForm::PHI;
}

void PoissonBCCubic::imposeBC(int varID, 
                     FieldContainer<double> &physicalPoints,
                     FieldContainer<double> &unitNormals,
                     FieldContainer<double> &dirichletValues,
                     FieldContainer<bool> &imposeHere) {
  int numCells = physicalPoints.dimension(0);
  int numPoints = physicalPoints.dimension(1);
  int spaceDim = physicalPoints.dimension(2);

  if (varID == PoissonBilinearForm::PHI) {
    for (int cellIndex=0; cellIndex<numCells; cellIndex++) {
      for (int ptIndex=0; ptIndex<numPoints; ptIndex++) {
        double x = physicalPoints(cellIndex,ptIndex,0);
        double y = physicalPoints(cellIndex,ptIndex,1);
        dirichletValues(cellIndex,ptIndex) = x*x*x + 2.0*y*y*y;
        // impose everywhere:
        imposeHere(cellIndex,ptIndex) = true;
      }
    }
  } else if (varID == PoissonBilinearForm::PSI_HAT_N) {
    for (int cellIndex=0; cellIndex<numCells; cellIndex++) {
      for (int ptIndex=0; ptIndex<numPoints; ptIndex++) {
        // value = n1 * (3x^2) + n2 * (6y^2)
        double x = physicalPoints(cellIndex,ptIndex,0);
        double y = physicalPoints(cellIndex,ptIndex,1);
        double n1 = unitNormals(cellIndex,ptIndex,0);
        double n2 = unitNormals(cellIndex,ptIndex,1);
        double value = (3.0*x*x)*n1 + (6.0*y*y)*n2;
        dirichletValues(cellIndex,ptIndex) = value;
        // impose everywhere:
        imposeHere(cellIndex,ptIndex) = true; 
} } } }
\end{lstlisting}

\subsection{Manufactured Solutions}
Using the Sacado package in Trilinos, it is possible to specify exact solutions and apply automatic differentiation to these.  This is an ideal way to implement a class of manufactured solutions for a variational problem.  While a detailed discussion of Sacado is beyond the scope of this paper, there are two example manufactured solutions, \verb=PoissonExactSolution= and \verb=StokesManufacturedSolution=, included with the code.  Each of these uses multiple inheritance to subclass \verb=RHS=, \verb=BC=, as well as \verb=ExactSolution=, an abstract class which provides solution values at a point, and offers facilities for measuring the error in computed solutions.

\subsection{Test Space Inner Product Specification}\label{NVR:sec:innerProductSpecification}
In Section \ref{NVR:sec:testNorms}, we described two standard test norms, the mathematician's norm and the quasi-optimal test norm.  We provide implementations in \verb=MathInnerProduct= and \verb=OptimalInnerProduct=.  The constructors for these simply take a \verb=BilinearForm= object as argument.  The value of $\beta$ in the quasi-optimal test norm is taken to be 1.

If a different test norm is desired, one can subclass \verb=DPGInnerProduct=, and override the \verb=operators()= and \verb=applyInnerProductData()= methods.  The interface is very much like that for the BilinearForm.  One limitation is worth mentioning: at present, \verb=applyInnerProductData()= receives only information about the physical points where the inner product is to be computed; some of our past research has involved inner products that depend on the location relative to an element boundary or the element's size.  Although these are relatively simple extensions, they are not presently supported by the DPG Trilinos toolbox.

\section{Meshing and Solving}\label{NVR:sec:meshAndSolve}
Once we have a bilinear form specified with a test space inner product, we are ready to produce a mesh on which to solve the variational problem, and examine the error of that solution.  There are four classes provided to support this:
\begin{itemize}
\item \verb=Mesh=: defines elements, vertices, and test and trial bases. 
\item \verb=ExactSolution=: defines the exact solution values at a point.
\item \verb=Solution=: solves the linear system and stores solution coefficients.
\item \verb=HConvergenceStudy=: solves the variational problem on a series of meshes, and computes convergence rates for trial space variables.
\end{itemize}
In this section, we discuss each of these in turn.

\subsection{The Mesh Class}\label{NVR:sec:mesh}
The \verb=Mesh= class represents a bilinear form together with a set of quadrilaterals and triangles on which polynomial bases are defined for each test and trial variable.  The basic \verb=Mesh= constructor takes arguments
\begin{itemize}
\item \verb=vector<FieldContainer<double> > &vertices=,
\item \verb=vector< vector<int> > &elementVertices=,
\item \verb=Teuchos::RCP< BilinearForm > bilinearForm=,
\item \verb=int pTrial=, and
\item \verb=int pToAddTest=.
\end{itemize}

The \verb=vertices= vector has FieldContainer entries with dimensions \verb=(spaceDim)=, the spatial dimension of the problem, each of which specifies the physical locations of an element vertex.  Each physical vertex should be listed exactly once.  (We do assume \verb=(spaceDim)= = 2 in a few places in the code, so that is a limitation for the moment.)

The \verb=elementVertices= vector contains a vector of 3 or 4 vertex indices for each element---these are the indices of the element's vertices in the \verb=vertices=  vector, and they should be specified in counterclockwise order (clockwise will work as well, but all elements must be specified in the same order, clockwise or counterclockwise).  The \verb=Mesh= class will automatically determine which element edges lie along the boundary, as well as which edges are shared between elements.

The \verb=bilinearForm= argument is a reference-counted pointer to the bilinear form for the variational problem to be solved.

\verb=pTrial= is the polynomial order of approximation to be used for trial space variables belonging to $H^{1}$ (that is, in function space \verb=FUNCTION_SPACE_HGRAD= --- typically, these are just the traces), and \verb=pToAddToTest= is the polynomial order to add to this to obtain the order for the test space.  Trial space variables in $L^{2}$ (function space \verb=FUNCTION_SPACE_HVOL=, typically field variables and fluxes), then these will have order \verb=pTrial-1=.

In addition to the basic mesh constructor, there are two static constructors to build meshes within an axis-aligned rectangle.  These are \verb=buildQuadMesh= and \verb=buildQuadMeshHybrid=, with the following signatures:
\begin{lstlisting}
Teuchos::RCP<Mesh> buildQuadMesh(
          const FieldContainer<double> &quadBoundaryPoints,
          int horizontalElements, int verticalElements,
          Teuchos::RCP< BilinearForm > bilinearForm, 
          int pTrial, int pTest, bool triangulate=false);
Teuchos::RCP<Mesh> buildQuadMeshHybrid(
          const FieldContainer<double> &quadBoundaryPoints, 
          int horizontalElements, int verticalElements,
          Teuchos::RCP< BilinearForm > bilinearForm, 
          int pTrial, int pTest);
\end{lstlisting}

Both methods will construct a regularly spaced grid of $horizontalElements \times verticalElements$ rectangular elements, with \verb=pToAddTest= = \verb=pTest - pTrial=.  \verb=quadBoundaryPoints= is a FieldContainer with dimensions (4,2) containing four axis-aligned vertices.  (We do hope to relax the axis-alignment constraint in the near future.)  In the first method, if \verb=triangulate= is true, these rectangles are cut along a diagonal to form triangular elements.  In the second method, half of the elements are split; the mesh is thus a ``hybrid'' of triangles and quads.

\subsection{The ExactSolution Class}\label{NVR:sec:ExactSolution}  In order to measure the $L^{2}$ error of a computed solution, we need to know what the exact solution is.  The \verb=ExactSolution= class is a mechanism for defining this.  Subclasses should override the \verb=solutionValue()= methods, which have signatures:
\begin{lstlisting}
double solutionValue(int trialID,
                     FieldContainer<double> &physicalPoint);
double solutionValue(int trialID,
                     FieldContainer<double> &physicalPoint,
                     FieldContainer<double> &unitNormal);
\end{lstlisting}
where \verb=unitNormal= and \verb=physicalPoint= are containers with dimension equal to the spatial dimension (2, for the present).  The \verb=unitNormal= argument is provided in the second method so that fluxes, which depend on the outward normal, may be computed.  As discussed above, the \verb=PoissonExactSolution= class demonstrates an implementation of \verb=ExactSolution= using Sacado for automatic differentiation.

\subsection{The Solution Class}\label{NVR:sec:Solution} A \verb=Solution= object can be constructed and solved as follows:
\begin{lstlisting}
Solution solution(mesh, bc, rhs, innerProduct);
solution.solve();
\end{lstlisting}

At present, the \verb=solve()= method solves using the KLU implementation provided by Trilinos.  The \verb=Solution= class also provides support for computing solution values at points (through the \verb=solutionValues()= methods), as well as outputting a data file representing the mesh solution for a given trial space variable (the \verb=writeToFile()= method).

\subsection{The HConvergenceStudy Class}\label{NVR:sec:HConvergenceStudy}  The \verb=HConvergenceStudy= class provides a simple mechanism for studying convergence rates on the meshes supported by the constructors \verb=buildQuadMesh()= and \verb=buildQuadMeshHybrid()=.  Its constructor interface is as follows:
\begin{lstlisting}
HConvergenceStudy(Teuchos::RCP<ExactSolution> exactSolution,
                  Teuchos::RCP<BilinearForm> bilinearForm,
                  Teuchos::RCP<RHS> rhs,
                  Teuchos::RCP<BC> bc,
                  Teuchos::RCP<DPGInnerProduct> ip, 
                  int minLogElements, int maxLogElements, 
                  int H1Order, int pToAdd, 
                  bool randomRefinements,
                  bool useTriangles, bool useHybrid)
\end{lstlisting}

The logarithms in \verb=minLogElements= and \verb=maxLogElements= are base 2, and the number of elements is measured in one axis direction only --- for example, specifying 0 and 5 will compute solutions for meshes varying in size from $1 \times 1$ to $32 \times 32$.  \verb=H1Order= is the polynomial order for $H^{1}$ space, which is one higher than that used for $L^{2}$.  The \verb=randomRefinements= flag will vary the \verb=H1Order= throughout the mesh; these are not actually randomly chosen --- the flag is meant for exercising $p$-refinements.  The other arguments are self-explanatory.

Calling \verb=solve(quadBoundaryPoints)=, where the \verb=quadBoundaryPoints= argument is such as was used in \verb=buildQuadMesh()=, will compute solutions on a series of meshes.  Calling \verb=writeToFiles(filePathPrefix, trialID)= will print error values and convergence rates for \verb=trialID= to console, and write both the error values and the visualization data for the solution to a set of files starting with \verb=filePathPrefix=.  Example drivers for \verb=HConvergenceStudy= can be found in \verb=PoissonStudy= and \verb=StokesStudy=.

\subsection{Visualization}\label{NVR:sec:visualization}
For visualization in MATLAB, first call the \verb=Solution= object's \verb=writeToFile()= method, passing in the trial variable identifier and the file path as arguments.  Our toolbox provides a MATLAB script, \verb=plotSolution.m=, for displaying the solution.  Calling this is as simple as ensuring that the MATLAB script is in your MATLAB path, and then calling \verb=plotSolution(filePath)= from MATLAB.  The visualization is approximate: at present, we only write out solution values at vertices, and MATLAB is responsible for interpolating between these.  We do hope to provide higher-fidelity visualization soon.

\section{Stokes Formulations}\label{NVR:sec:stokesForm}
In Section \ref{NVR:sec:poissonForm}, we developed an ultra-weak variational formulation for the Poisson problem.  In this section, we do the same for two formulations of the Stokes problem.

\subsection{Stokes Formulation I: VSP Formulation}
We begin with the formulation we have used in previous work, a velocity-stress-pressure (VSP) formulation.  Our past motivation for selecting this one over the velocity-vorticity-pressure (VVP) formulation which we discuss below had to do with details of implementation.  The VVP formulation requires considerably fewer solution variables, so now that we have it implemented, we prefer it.

The strong form of the Stokes problem with which we begin is as follows:

\begin{align}
- 2 \mu \NVRdiv \NVRtensor{\epsilon} + \NVRgrad p &= \NVRvect{f} & \text{ in } \Omega, \label{NVR:eq:strongfirst} \\
\NVRdiv \NVRvect{u} &= 0 & \text{ in } \Omega, \\
\NVRvect{u} &= \NVRvect{g_{D}} & \text{ on } \partial\Omega,\label{NVR:eq:stronglast}
\end{align}
where $\Omega \subset \mathbb{R}^{2}$, $\mu$ is viscosity, $\NVRtensor{\epsilon}=\NVRgrad^{\text{sym}} \NVRvect{u}$ is strain, $p$ is pressure, $u$ velocity, and $\NVRvect{f}$ a vector forcing function.

We introduce stress $\sigma$ and vorticity $\omega$ by
\begin{align*}
\NVRtensor{\sigma} &= 2 \mu \NVRtensor{\epsilon} - p\NVRtensor{I}\\
\NVRtensor{\omega} &= \frac{1}{2}(\NVRgrad \NVRvect{u} - \NVRgrad \NVRvect{u}^{T})
\end{align*}
so that equation \eqref{NVR:eq:strongfirst} becomes simply $-\NVRdiv \NVRtensor{\sigma} = \NVRvect{f}$.
We also have
\begin{align*}
\NVRtensor{\epsilon} &= \frac{1}{2 \mu}(\NVRtensor{\sigma} + p\NVRtensor{I}).
\end{align*}
Since $\NVRtensor{\epsilon} = \NVRgrad^{\text{sym}} \NVRvect{u} = \NVRgrad \NVRvect{u} - \NVRtensor{\omega}$, the entire system is

\begin{align*}
\frac{1}{2 \mu}(\NVRtensor{\sigma} + p\NVRtensor{I}) - \NVRgrad \NVRvect{u} + \NVRtensor{\omega} &= \NVRtensor{0}  & \text{ in } \Omega, \\
- \NVRdiv \NVRtensor{\sigma} &= \NVRvect{f} & \text{ in } \Omega, \\
\NVRdiv \NVRvect{u} &= 0 & \text{ in } \Omega, \\
\NVRvect{u} &= \NVRvect{g_{D}} & \text{ on } \partial\Omega.
\end{align*}
Note that the antisymmetric part of the first equation recovers the definition of $\NVRtensor{\omega}$, so that it need not enter the system separately.
Define scalar $\omega = \omega_{21} = \frac{1}{2}(u_{1,2} - u_{2,1})$.  Our strong formulation is

\begin{align*}
\frac{1}{2 \mu}{\sigma_{11} + p \choose \sigma_{21}} - \NVRgrad u_{1} + {0 \choose \omega} &= \NVRvect{0} & \text{ in } \Omega, \\
\frac{1}{2 \mu}{\sigma_{12} \choose \sigma_{22} + p} - \NVRgrad u_{2} - {\omega \choose 0} &= \NVRvect{0}  & \text{ in } \Omega, \\
-\NVRdiv {\sigma_{11} \choose \sigma_{21}} &= f_{1} & \text{ in } \Omega, \\
-\NVRdiv {\sigma_{12} \choose \sigma_{22}} &= f_{2} & \text{ in } \Omega, \\
\NVRdiv \NVRvect{u} &= 0 & \text{ in } \Omega, \\\
\NVRvect{u} &= \NVRvect{g_{D}} & \text{ on } \partial\Omega.
\end{align*}
Multiplying the first two equations by vector test functions $\NVRvect{q}_{i}$ and the following three by scalar test functions $v_{i}$, and integrating by parts over an element $K$, we obtain

\begin{align*}
\int_{K} \left(\frac{1}{2 \mu}{\sigma_{11} + p \choose \sigma_{21}} + {0 \choose \omega} \right) \cdot \NVRvect{q}_{1} &+ \int_{K} u_{1} \NVRdiv \NVRvect{q_{1}} &-& \int_{\partial K} \widehat{u}_{1} \NVRvect{q_{1}} \cdot n &&=\NVRvect{0} \\
\int_{K} \left(\frac{1}{2 \mu}{\sigma_{12} \choose \sigma_{22} + p} - {\omega \choose 0}\right) \cdot \NVRvect{q}_{2} &+ \int_{K} u_{2} \NVRdiv \NVRvect{q_{2}} &-& \int_{\partial K} \widehat{u}_{2} \NVRvect{q_{2}} \cdot n &&= \NVRvect{0}\\
\int_{K}  {\sigma_{11} \choose \sigma_{21}} \cdot \NVRgrad v_{1} &&-& \int_{\partial K} \widehat{\NVRvect{\sigma}}_{1n} v_{1} &&= \int_{K} f_{1} v_{1} \\
\int_{K} {\sigma_{12} \choose \sigma_{22}} \cdot \NVRgrad v_{2} &&-& \int_{\partial K} \widehat{\NVRvect{\sigma}}_{2n} v_{2}  &&= \int_{K} f_{2} v_{2} \\
-\int_{K} \NVRvect{u} \cdot \NVRgrad v_{3} &&+& \int_{\partial K} \widehat{\NVRvect{u}} v_{3} \cdot n &&= 0,
\end{align*}
where the hatted variables ($\widehat{u}_{1}$, e.g.) are fluxes and traces introduced by relaxing the continuity requirement at element boundaries.  These differ from the \emph{numerical fluxes} that appear in other DG methods, in that they are not constructed a priori, but simply enter the variational problem as additional unknowns. We solve for them at the same time as we solve 
the rest of the unknowns.  As in other DG methods, the fluxes will approach the corresponding unhatted solution variables (which we call \emph{field} variables) as the latter approach the exact solution.

Conceptually, this requires nothing more than the Poisson formulation we described above --- in particular, the test functions $\NVRvect{q}_{i} \in \NVRHdiv$ and $v_{i} \in \NVRHgrad$, so we do not require any test spaces or operators different than discussed above.  An implementation of this bilinear form can be found in \verb=StokesBilinearForm=.

\subsection{Stokes Formulation II: Velocity-Vorticity-Pressure Formulation}  The standard velocity-vorticity-pressure (VVP) Stokes formulation is:
\begin{align*}
\NVRcurl \omega + \NVRgrad P &= \NVRvect{f}\\
\omega - \NVRcurl \NVRvect{u} &= 0\\
\NVRdiv \NVRvect{u} &= 0.
\end{align*}
(Note that the value of $\omega$ here differs by a factor of $-\frac{1}{2}$ from the $\omega$ as defined in the previous formulation.)  Multiplying by test functions, integrating by parts, and substituting fluxes and traces for boundary values, we obtain:

\begin{align*}
\int_{\partial K} \widehat{\omega} \NVRvect{q} \cdot {n_{2} \choose -n_{1}} + \int_{\partial K} \widehat{P} q_{n} -  \int_{K}\omega \NVRcurl \NVRvect{q} -  \int_{K} P \NVRdiv \NVRvect{q} &= \int_{K} \NVRvect{f} \cdot \NVRvect{q}\\
\int_{\partial K} \widehat{u}_{\times \NVRvect{n}}v_{1} -  \int_{K}\NVRvect{u} \cdot (\NVRcurl v_{1}) +  \int_{K} \omega v_{1} &= 0\\
\int_{\partial K} \widehat{u}_{\NVRvect{n}} v_{2} -  \int_{K}\NVRvect{u} \cdot (\NVRgrad v_{2}) &= 0 \,.
\end{align*}
Whereas the original Stokes formulation required 7 field variables, 3 traces, and 2 fluxes, the VVP formulation requires just 4 field, 2 trace, and two flux variables.  However, there are a few new operators and spaces required.  While $v_{i} \in \NVRHgrad$ as before, now we require $\NVRvect{q} \in \NVRHdiv$ \emph{and} $\NVRvect{q} \in \NVRHcurl$.  We can support this by requiring $\NVRvect{q} \in \NVRHgrad \times \NVRHgrad$.  In the code, we define the function space for $\NVRvect{q}$ as \verb=FUNCTION_SPACE_VECTOR_HGRAD=.  The curl operator is given by \verb=OPERATOR_CURL=, and the \[ \displaystyle \cdot {n_{2} \choose -n_{1}}=\times n\] operator is given by \verb=OPERATOR_CROSS_N=.
The implementation for this formulation can be found in \verb=StokesVVPBilinearForm=.

\section{Numerical Results}\label{NVR:sec:numericalResults}
For each of our three formulations --- Poisson, VSP Stokes, and VVP Stokes --- we have run a set of numerical experiments:
\begin{itemize}
\item For $L^{2}$ polynomial orders 1, 2, and 3, run convergence studies on meshes varying from $1 \times 1$ to $32 \times 32$.
\item For a $16 \times 16$ mesh, vary the polynomial orders of the elements across the mesh.
\item For $L^{2}$ polynomial orders 1, 2, and 3, run convergence studies on ``hybrid'' meshes (quads and triangles together) varying in size from $1 \times 1$ to $32 \times 32$.
\end{itemize}

The first two experiments we ran with triangles and quads.  For all of the experiments, we used the zero mean constraint and the domain $(-1,1) \times (-1,1)$, and the mathematician's inner product.  We used the Poisson manufactured solution
\begin{align*}
\phi = e^{x \sin y} - \frac{1}{4} \int_{-1}^{1} \int_{-1}^{1} e^{x \sin y} dx dy,
\end{align*}
where the subtracted integral is chosen to ensure that $\phi$ does indeed have a zero mean.  Following our previous work, the Stokes experiments used a manufactured solution
\begin{align*}
u_{1} &=  -e^{x} ( y \cos y + \sin y )\\
u_{2} &=  e^{x}  y \sin y\\
p &= 2 \mu e^{x} \sin y.
\end{align*}

\subsection{Convergence Studies on Uniform Meshes}
For polynomial order $k$, we expect a convergence rate of $k+1$.  This is indeed what we see in our experiments.  The Poisson convergence studies with triangular elements can be found in Table \ref{NVR:table:poissonTriRates}; with quads, in Table \ref{NVR:table:poissonQuadRates}.  The Stokes VSP studies with triangles can be found in Table \ref{NVR:table:VSPTriRates}; with quads, in Table \ref{NVR:table:VSPQuadRates}.  The VVP studies with triangles are shown in Table \ref{NVR:table:VVPTriRates}; with quads, in Table \ref{NVR:table:VVPQuadRates}.

\subsection{Meshes of Multiple Polynomial Orders}\label{NVR:sec:mixedMeshes}
To confirm that our code works well with meshes that include elements of varying degree, we took a $16 \times 16$ mesh with $L^{2}$ polynomial degree assigned according to the following pattern, repeated 4 times:
\\
\begin{center}
\begin{tabular}{| c | c | c | c || c | c | c | c || c | c | c | c || c | c | c | c |}
\hline
4 &4 &4 &4  &1 &1 &1 &1  &2 &2 &2 &2  &3 &3 &3 &3 \\
\hline
3 &3 &3 &3  &4 &4 &4 &4  &1 &1 &1 &1  &2 &2 &2 &2 \\
\hline
2 &2 &2 &2  &3 &3 &3 &3  &4 &4 &4 &4  &1 &1 &1 &1 \\
\hline
1 &1 &1 &1  &2 &2 &2 &2  &3 &3 &3 &3  &4 &4 &4 &4 \\
\hline
\end{tabular}
\end{center}
\vspace{0.1in}
We hope to see errors as good as, or better than, our first-order $16 \times 16$ mesh for the same problem, although we can perhaps explain a small amount of increased error as due to worse conditioning of the matrices for higher-order polynomials.

The results for Poisson are:
\\
\begin{center}
\begin{tabular}{| c | c | c | c | c | c |}
\hline
\multicolumn{6}{| c |}{Triangles} \\
\hline
\multicolumn{2}{| c |}{$\phi$} & \multicolumn{2}{| c |}{$\psi_{1}$} & \multicolumn{2}{| c |}{$\psi_{2}$} \\
\hline
$k=1$ & mixed $k$ & $k=1$ & mixed $k$ & $k=1$ & mixed $k$ \\
\hline
2.0e-3 & 9.1e-4 & 3.4e-3 & 1.7e-3 & 2.4e-3 & 1.1e-3\\
\hline
\hline
\multicolumn{6}{| c |}{Quads} \\
\hline
\multicolumn{2}{| c |}{$\phi$} & \multicolumn{2}{| c |}{$\psi_{1}$} & \multicolumn{2}{| c |}{$\psi_{2}$} \\
\hline
$k=1$ & mixed $k$ & $k=1$ & mixed $k$ & $k=1$ & mixed $k$ \\
\hline
1.0e-3 & 3.7e-4 & 2.3e-3 & 6.6e-4 & 2.9e-3 &1.2e-3\\
\hline
\end{tabular}
\end{center}
\vspace{0.1in}
For Poisson, the multi-order mesh has lower error than the first-order mesh in every variable, just as we would like.

The results for Stokes VSP are:
\\
\begin{center}
\begin{tabular}{| c | c | c | c | c | c |}
\hline
\multicolumn{6}{| c |}{Triangles} \\
\hline
\multicolumn{2}{| c |}{$p$} & \multicolumn{2}{| c |}{$u_{1}$} & \multicolumn{2}{| c |}{$u_{2}$} \\
\hline
$k=1$ & mixed $k$ & $k=1$ & mixed $k$ & $k=1$ & mixed $k$ \\
\hline
1.6e-2 & 1.4e-2 & 5.1e-3 & 2.4e-3 & 4.4e-3 & 2.1e-3\\
\hline
\hline
\multicolumn{6}{| c |}{Quads} \\
\hline
\multicolumn{2}{| c |}{$p$} & \multicolumn{2}{| c |}{$u_{1}$} & \multicolumn{2}{| c |}{$u_{2}$} \\
\hline
$k=1$ & mixed $k$ & $k=1$ & mixed $k$ & $k=1$ & mixed $k$ \\
\hline
5.3e-3 & 1.0e-2 & 4.9e-3 & 1.6e-3 & 2.5e-3 & 1.3e-3\\
\hline
\end{tabular}
\end{center}
\vspace{0.1in}
For Stokes VSP, the multi-order mesh has lower error than the first-order mesh in every variable, except for pressure in the quad mesh, where the first-order mesh does better by about a factor of 2.

The results for Stokes VVP are:
\\
\begin{center}
\begin{tabular}{| c | c | c | c | c | c |}
\hline
\multicolumn{6}{| c |}{Triangles} \\
\hline
\multicolumn{2}{| c |}{$p$} & \multicolumn{2}{| c |}{$u_{1}$} & \multicolumn{2}{| c |}{$u_{2}$} \\
\hline
$k=1$ & mixed $k$ & $k=1$ & mixed $k$ & $k=1$ & mixed $k$ \\
\hline
6.9e-2 & 5.8e-2 & 6.9e-3 & 3.1e-3 & 6.8e-3 & 2.7e-3\\
\hline
\hline
\multicolumn{6}{| c |}{Quads} \\
\hline
\multicolumn{2}{| c |}{$p$} & \multicolumn{2}{| c |}{$u_{1}$} & \multicolumn{2}{| c |}{$u_{2}$} \\
\hline
$k=1$ & mixed $k$ & $k=1$ & mixed $k$ & $k=1$ & mixed $k$ \\
\hline
8.0e-3 & 2.1e-2 & 3.9e-3 & 1.7e-3 & 3.8e-3 & 1.4e-3\\
\hline
\end{tabular}
\end{center}
\vspace{0.1in}
Again, the behavior is just as we would like, except in the case of pressure for quads, where the error in the first-order mesh is better than that for the multi-order, this time by a factor of about 2.5.  We believe that this is due to round-off error, but we do not at present have a precise explanation.

\subsection{``Hybrid'' Mesh Convergence Studies}

We studied the convergence of the Poisson solution for ``hybrid'' meshes, containing half triangles and half quads, ranging from $1 \times 1$ to $32 \times 32$, with $L^{2}$ polynomial orders $k=1,2,3$.  The results can be seen in Table \ref{NVR:table:PoissonHybridRates}; again, the convergence rates for all variables are optimal. Plots of $\phi$, $\psi_{1}$ and $\psi_{2}$ for the $16 \times 16$ mesh can be found in Figure \ref{NVR:fig:Poisson}.

We studied the same for the VSP and VVP Stokes formulations.  VSP results can be found in Table \ref{NVR:table:VSPHybridRates}; VVP, Table \ref{NVR:table:VVPHybridRates} --- the rates are optimal for $u_{1}$ and $u_{2}$ across the board, but for reasons unknown the $k=1$ VVP pressure is somewhat sub-optimal, while for $k=2$ and 3, the rate is somewhat super-optimal.  Something similar happens in the VSP pressure, although there the effect is considerably less pronounced.  Plots of $P$, $u_{1}$ and $u_{2}$ for the $16 \times 16$ mesh can be found in Figure \ref{NVR:fig:Stokes}.  These were generated using the VVP formulation; the VSP plots are visually identical.

\section{Conclusions and Future Work}\label{NVR:sec:conclusion}
We have implemented a general toolbox for solving DPG problems, together with proof-of-concept implementations of solvers for the Poisson and Stokes problems.  We look forward to extending this further.  Here is a short list of features we would like to add, and experiments we would like to perform, going forward:
\begin{itemize}
\item Quotient space norm computations --- when we impose the pressure at a point rather than imposing a zero-mean condition, the $L^{2}$ norm of the error is not the correct measure.  We need to subtract off the mean value of both the exact solution and that of the computed solution before taking the $L^{2}$ norm of the difference.
\item Support for solving nonlinear problems using Newton-Raphson --- in the end, we hope to use this toolbox to solve the compressible Navier-Stokes equations in two dimensions.
\item $p$-adaptivity --- we have $p$-refinements in place, so this is just a matter of computing the error and refining where the error is highest.
\item $h$-adaptivity --- this will require us to add support for $h$-refinements.  We have a good idea how we will do so.
\item Mesh-dependent inner products --- at present, our inner products are computed without any knowledge of element sizes; in some other DPG explorations, we have used various kinds of weighted inner product, so we would like to support these.
\item Support for 1D computations.  At present, only 2D is supported by the mesh, but it should be a relatively simple matter to add support for 1D.  3D will be more involved, but is tractable.
\item MPI support.  At present, the bulk of the computational cost in our numerical experiments is devoted to computing the optimal test functions.  Because these are local computations, they should scale easily to many processors.
\end{itemize}

\bibliographystyle{siam}
% Edit the line below to be your first and last names.
\bibliography{paper}

\appendix

\clearpage
\section{Results of Convergence Studies on Uniform Meshes}

\vspace{1.59in}

\begin{table}[h!b!p!]
\begin{center}
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
\multicolumn{7}{| c |}{k=1} \\
\hline
Mesh Size & $\phi$ & rate & $\psi_{1}$ & rate &  $\psi_{2}$ & rate \\
\hline
1 $\times$ 1		&4.2e-1	&-	&5.2e-1	&-		&3.4e-1	&-	\\
2 $\times$ 2         	&1.3e-1	&1.71	&2.0e-1	&1.38		&1.5e-1     	&1.24	\\
4 $\times$ 4	        	&3.2e-2	&2.00	&5.2e-2	&1.93		&3.9e-2     	&1.92	\\
8 $\times$ 8         	&8.0e-3	&2.01	&1.3e-2	&1.96		&9.6e-3     	&2.00	\\
16 $\times$ 16         	&2.0e-3	&2.00	&3.4e-3	&1.99		&2.4e-3     	&2.01	\\
32 $\times$ 32         	&5.0e-4	&2.00	&8.4e-4	&1.99		&6.0e-4      	&2.00	\\
\hline
\multicolumn{7}{| c |}{k=2} \\
\hline
Mesh Size & $\phi$ & rate & $\psi_{1}$ & rate &  $\psi_{2}$ & rate \\
\hline
1 $\times$ 1		&7.9e-2	&-	&2.5e-1	&-	&1.4e-1	&-	\\
2 $\times$ 2         	&1.2e-2	&2.77	&3.1e-2	&2.97	&3.6e-2     	&1.96	\\
4 $\times$ 4       	&1.4e-3	&3.00	&4.1e-3	&2.95	&4.9e-3     	&2.86	\\
8 $\times$ 8         	&1.8e-4	&2.99	&5.1e-4	&2.98	&6.0e-4     	&3.02	\\
16 $\times$ 16         	&2.3e-5	&3.00	&6.5e-5	&2.99	&7.5e-5     	&3.01	\\
32 $\times$ 32         	&2.8e-6	&3.00	&8.1e-6	&3.00	&9.3e-6      	&3.01	\\
\hline
\multicolumn{7}{| c |}{k=3} \\
\hline
Mesh Size & $\phi$ & rate & $\psi_{1}$ & rate &  $\psi_{2}$ & rate \\
\hline
1 $\times$ 1		&2.5e-2	&-	&2.9e-2	&-	&4.3e-2	&-	\\
2 $\times$ 2         	&1.5e-3	&3.99	&3.4e-3	&3.09	&5.2e-3     	&3.06	\\
4 $\times$ 4        	&1.1e-4	&3.82	&2.3e-4	&3.92	&3.4e-4     	&3.95	\\
8 $\times$ 8         	&7.1e-6	&3.94	&1.5e-5	&3.99	&2.1e-5     	&3.98	\\
16 $\times$ 16         	&4.5e-7	&3.99	&9.2e-7	&3.99	&1.3e-6     	&4.00	\\
32 $\times$ 32         	&2.8e-8	&4.00	&5.8e-8	&4.00	&8.4e-8      	&4.00	\\
\hline
\end{tabular}
\end{center} 
\caption{Poisson: Triangles, $L^{2}$ Error and $h$-Convergence Rates.  We observe optimal convergence.}
\label{NVR:table:poissonTriRates}
\end{table}

\begin{table}[h!b!p!]
\begin{center}
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
\multicolumn{7}{| c |}{k=1} \\
\hline
Mesh Size & $\phi$ & rate & $\psi_{1}$ & rate &  $\psi_{2}$ & rate \\
\hline
1 $\times$ 1		&1.4e-1	&-	&5.4e-1	&-	&3.8e-1	&-	\\
2 $\times$ 2         	&5.2e-2	&1.41	&1.3e-1	&2.00	&1.4e-1     	&1.41	\\
4 $\times$ 4        	&1.5e-2	&1.77	&3.5e-2	&1.92	&4.3e-2     	&1.70	\\
8 $\times$ 8         	&4.1e-3	&1.93	&9.1e-3	&1.97	&1.2e-2     	&1.91	\\
16 $\times$ 16         	&1.0e-3	&1.98	&2.3e-3	&2.00	&2.9e-3     	&1.98	\\
32 $\times$ 32         	&2.6e-4	&2.00	&5.7e-4	&2.00	&7.3e-4      	&2.00	\\
\hline
\multicolumn{7}{| c |}{k=2} \\
\hline
Mesh Size & $\phi$ & rate & $\psi_{1}$ & rate &  $\psi_{2}$ & rate \\
\hline
1 $\times$ 1		&4.9e-2	&-	&8.5e-2	&-	&1.1e-1	&-	\\
2 $\times$ 2         	&6.6e-3	&2.91	&1.7e-2	&2.34	&1.6e-2     	&2.78	\\
4 $\times$ 4        	&7.8e-4	&3.08	&2.2e-3	&2.90	&1.8e-3     	&3.12	\\
8 $\times$ 8         	&9.3e-5	&3.05	&2.6e-4	&3.11	&2.0e-4     	&3.20	\\
16 $\times$ 16         	&1.2e-5	&3.01	&3.1e-5	&3.06	&2.3e-5     	&3.11	\\
32 $\times$ 32         	&1.4e-6	&3.00	&3.8e-6	&3.03	&2.8e-6      	&3.05	\\
\hline
\multicolumn{7}{| c |}{k=3} \\
\hline
Mesh Size & $\phi$ & rate & $\psi_{1}$ & rate &  $\psi_{2}$ & rate \\
\hline
1 $\times$ 1		&1.2e-2	&-	&3.0e-2	&-	&2.6e-2	&-	\\
2 $\times$ 2         	&6.6e-4	&4.16	&2.6e-3	&3.54	&2.0e-3     	&3.66	\\
4 $\times$ 4        	&3.3e-5	&4.33	&1.2e-4	&4.39	&1.1e-4     	&4.18	\\
8 $\times$ 8         	&2.1e-6	&3.99	&7.3e-6	&4.09	&6.6e-6     	&4.10	\\
16 $\times$ 16         	&1.3e-7	&3.99	&4.4e-7	&4.04	&3.9e-7     	&4.07	\\
32 $\times$ 32         	&8.1e-9	&4.00	&2.7e-8	&4.02	&2.4e-8      	&4.04	\\
\hline
\end{tabular}
\end{center} 
\caption{Poisson: Quads, $L^{2}$ Error and $h$-Convergence Rates.  We observe optimal convergence.}
\label{NVR:table:poissonQuadRates}
\end{table}

\begin{table}[h!b!p!]
\begin{center}
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
\multicolumn{7}{| c |}{k=1} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&3.2e-0	&-	&9.4e-1	&-	&1.6e-0	&-	\\
2 $\times$ 2         	&1.1e-0	& 1.53	&3.1e-1	&1.62	&2.8e-1     	&2.05	\\
4 $\times$ 4        	&3.0e-1	& 1.89	&8.0e-2	&1.94	&7.0e-2     	&1.99	\\
8 $\times$ 8         	&6.9e-2	& 2.11	&2.0e-2	&1.99	&1.8e-2     	&2.00	\\
16 $\times$ 16         	&1.6e-2	& 2.12	&5.1e-3	&2.00	&4.4e-3     	&2.00	\\
32 $\times$ 32         	&3.8e-3	& 2.08	&1.3e-3	&2.00	&1.1e-3      	&2.00	\\
\hline
\multicolumn{7}{| c |}{k=2} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&2.3e-0	&-	&2.6e-1	&-	&4.3e-1	&-	\\
2 $\times$ 2         	&2.8e-1	&3.02	&4.3e-2	&2.63	&5.1e-2     	&3.05	\\
4 $\times$ 4        	&3.4e-2	&3.06	&5.8e-3	&2.88	&6.6e-3     	&2.97	\\
8 $\times$ 8         	&4.0e-3	&3.10	&7.4e-4	&2.97	&8.3e-4     	&2.99	\\
16 $\times$ 16         	&4.7e-4	&3.06	&9.3e-4	&2.99	&1.0e-4     	&3.00	\\
32 $\times$ 32         	&5.8e-5	&3.03	&1.2e-5	&3.00	&1.3e-5      	&3.00	\\
\hline
\multicolumn{7}{| c |}{k=3} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&3.7e-1	&-	&5.0e-2	&-	&3.7e-2	&-	\\
2 $\times$ 2         	&3.4e-2	&3.46	&4.0e-3	&3.66	&3.4e-3     	&3.44	\\
4 $\times$ 4        	&2.6e-3	&3.70	&2.6e-4	&3.95	&2.2e-4     	&3.94	\\
8 $\times$ 8         	&1.9e-4	&3.82	&1.6e-5	&3.99	&1.4e-5     	&4.00	\\
16 $\times$ 16         	&1.1e-5	&4.06	&1.0e-6	&4.00	&8.8e-7     	&4.00	\\
32 $\times$ 32         	&5.8e-7	&4.27	&6.4e-8	&4.00	&5.5e-8      	&4.00	\\
\hline
\end{tabular}
\end{center} 
\caption{Stokes VSP: Triangles, $L^{2}$ Error and $h$-Convergence Rates.  We observe optimal convergence.}
\label{NVR:table:VSPTriRates}
\end{table}

\begin{table}[h!b!p!]
\begin{center}
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
\multicolumn{7}{| c |}{k=1} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&1.1e-0	&-	&4.7e-1	&-	&8.3e-1	&-	\\
2 $\times$ 2         	&6.1e-1	&0.84	&3.0e-1	&0.65	&1.7e-1     	&2.33	\\
4 $\times$ 4        	&1.4e-1	&2.07	&7.8e-2	&1.94	&4.0e-2     	&2.03	\\
8 $\times$ 8         	&2.9e-2	&2.33	&2.0e-2	&1.99	&1.0e-2     	&2.01	\\
16 $\times$ 16         	&5.4e-3	&2.41	&4.9e-3	&2.00	&2.5e-3     	&2.00	\\
32 $\times$ 32         	&1.0e-3	&2.38	&1.2e-3	&2.00	&6.3e-4      	&2.00	\\
\hline
\multicolumn{7}{| c |}{k=2} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&3.3e-1	&-	&3.0e-1	&-	&1.7e-1	&-	\\
2 $\times$ 2         	&1.8e-1	&0.82	&3.2e-2	&3.22	&2.0e-2     	&3.06	\\
4 $\times$ 4        	&1.5e-2	&3.67	&3.9e-3	&3.04	&2.5e-3     	&3.02	\\
8 $\times$ 8         	&1.2e-3	&3.58	&4.8e-4	&3.01	&3.1e-4     	&3.01	\\
16 $\times$ 16         	&1.0e-4	&3.54	&6.0e-5	&3.00	&3.9e-5     	&3.00	\\
32 $\times$ 32         	&9.5e-6	&3.46	&7.6e-6	&3.00	&4.9e-6      	&3.00	\\
\hline
\multicolumn{7}{| c |}{k=3} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&2.7e-1	&-	&1.3e-2	&-	&3.3e-2	&-	\\
2 $\times$ 2         	&2.0e-2	&3.74	&1.7e-3	&2.91	&1.8e-3     	&4.17	\\
4 $\times$ 4       	&1.3e-3	&4.02	&1.1e-4	&3.96	&1.1e-4     	&4.05	\\
8 $\times$ 8         	&7.0e-5	&4.16	&6.8e-6	&3.99	&6.9e-6     	&4.02	\\
16 $\times$ 16         	&3.6e-6	&4.29	&4.3e-7	&4.00	&4.3e-7     	&4.00	\\
32 $\times$ 32         	&1.6e-7	&4.52	&2.7e-8	&4.00	&2.7e-8      	&4.00	\\
\hline
\end{tabular}
\end{center} 
\caption{Stokes VSP: Quads, $L^{2}$ Error and $h$-Convergence Rates.  We observe optimal convergence.}
\label{NVR:table:VSPQuadRates}
\end{table}

\begin{table}[h!b!p!]
\begin{center}
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
\multicolumn{7}{| c |}{k=1} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&3.0e-0	&-	&1.6e-0	&-	&2.0e-0	&-	\\
2 $\times$ 2         	&1.5e-0	&1.00	&4.9e-1	&1.72	&4.2e-1     	&2.23	\\
4 $\times$ 4        	&6.4e-1	&1.23	&1.1e-1	&2.14	&1.1e-1     	&1.90	\\
8 $\times$ 8         	&2.3e-1	&1.51	&2.8e-2	&2.00	&2.8e-2     	&2.02	\\
16 $\times$ 16         	&6.9e-2	&1.70	&6.9e-3	&2.00	&6.8e-3     	&2.02	\\
32 $\times$ 32         	&2.0e-2	&1.77	&1.7e-3	&2.00	&1.7e-3      	&2.01	\\
\hline
\multicolumn{7}{| c |}{k=2} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&2.1e-0	&-	&3.3e-1	&-	&4.6e-1	&-	\\
2 $\times$ 2         	&8.5e-2	&4.65	&5.5e-2	&2.58	&5.6e-2     	&3.04	\\
4 $\times$ 4        	&8.3e-3	&3.35	&7.3e-3	&2.90	&7.7e-3     	&2.85	\\
8 $\times$ 8         	&7.7e-4	&3.44	&9.3e-4	&2.97	&1.0e-3     	&2.96	\\
16 $\times$ 16         	&6.8e-5	&3.51	&1.2e-4	&2.99	&1.3e-4     	&2.99	\\
32 $\times$ 32         	&6.9e-6	&3.30	&1.5e-5	&3.00	&1.6e-5      	&3.00	\\
\hline
\multicolumn{7}{| c |}{k=3} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&1.7e-1	&-	&5.9e-2	&-	&5.4e-2	&-	\\
2 $\times$ 2         	&1.3e-2	&3.74	&4.4e-3	&3.74	&4.2e-3     	&3.68	\\
4 $\times$ 4        	&8.9e-4	&3.83	&2.9e-4	&3.93	&2.7e-4     	&3.96	\\
8 $\times$ 8         	&4.8e-5	&4.22	&1.8e-5	&3.99	&1.7e-5     	&3.99	\\
16 $\times$ 16         	&2.0e-6	&4.60	&1.1e-6	&4.00	&1.1e-6     	&4.00	\\
32 $\times$ 32         	&6.7e-8	&4.89	&7.2e-8	&4.00	&6.4e-8      	&4.00	\\
\hline
\end{tabular}
\end{center} 
\caption{Stokes VVP: Triangles, $L^{2}$ Error and $h$-Convergence Rates.  We observe optimal convergence.}
\label{NVR:table:VVPTriRates}
\end{table}

\begin{table}[h!b!p!]
\begin{center}
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
\multicolumn{7}{| c |}{k=1} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&1.5e-0	&-	&4.9e-1	&-	&1.5e-0	&-	\\
2 $\times$ 2         	&1.5e-0	&0.02	&3.6e-1	&0.45	&3.1e-1     	&2.26	\\
4 $\times$ 4        	&1.0e-1	&3.90	&6.5e-2	&2.45	&6.3e-2     	&2.28	\\
8 $\times$ 8         	&3.0e-2	&1.74	&1.6e-2	&2.05	&1.5e-2     	&2.04	\\
16 $\times$ 16         	&8.0e-3	&1.91	&3.9e-3	&2.01	&3.8e-3     	&2.01	\\
32 $\times$ 32         	&2.0e-3	&1.97	&9.8e-4	&2.00	&9.6e-4      	&2.00	\\
\hline
\multicolumn{7}{| c |}{k=2} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		& 2.1e-0	&-	&3.9e-1	&-	&2.7e-1	&-	\\
2 $\times$ 2         	& 5.1e-2	&5.33	&3.3e-2	&3.56	&2.2e-2     	&3.60	\\
4 $\times$ 4        	& 3.7e-3	&3.80	&3.9e-3	&3.07	&2.6e-3     	&3.06	\\
8 $\times$ 8         	& 3.5e-4	&3.41	&4.9e-4	&3.02	&3.3e-4     	&3.01	\\
16 $\times$ 16         	& 3.8e-5	&3.18	&6.1e-5	&3.00	&4.1e-5     	&3.00	\\
32 $\times$ 32         	& 4.4e-6	&3.12	&7.6e-6	&3.00	&5.1e-6      	&3.00	\\
\hline
\multicolumn{7}{| c |}{k=3} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&1.9e-1	&-	&1.3e-2	&-	&3.7e-2	&-	\\
2 $\times$ 2         	&1.3e-2	&3.82	&1.8e-3	&2.85	&2.0e-3     	&4.23	\\
4 $\times$ 4        	&4.7e-4	&4.83	&1.1e-4	&3.97	&1.1e-4     	&4.11	\\
8 $\times$ 8         	&1.9e-5	&4.59	&7.1e-6	&4.00	&7.1e-6     	&4.02	\\
16 $\times$ 16         	&1.0e-6	&4.24	&4.4e-7	&4.00	&4.4e-7     	&4.00	\\
32 $\times$ 32         	&6.3e-8	&4.04	&2.8e-8	&4.00	&2.8e-8      	&4.00	\\
\hline
\end{tabular}
\end{center} 
\caption{Stokes VVP: Quads, $L^{2}$ Error and $h$-Convergence Rates.  We observe optimal convergence.}
\label{NVR:table:VVPQuadRates}
\end{table}

\clearpage
\section{Results of Convergence Studies on Hybrid Meshes}

\vspace{1.59in}

\begin{table}[h!b!p!]
\begin{center}
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
\multicolumn{7}{| c |}{k=1} \\
\hline
Mesh Size & $\phi$ & rate & $\psi_{1}$ & rate &  $\psi_{2}$ & rate \\
\hline
1 $\times$ 1		&4.2e-1	&-		&5.2e-1	&-		&3.4e-1	&-		\\
2 $\times$ 2         	&9.6e-2	&2.12	&1.7e-1	&1.58	&1.4e-1     	&1.27	\\
4 $\times$ 4        	&2.4e-2	&1.99	&4.5e-2	&1.93	&4.0e-2     	&1.84	\\
8 $\times$ 8         	&6.1e-3	&2.00	&1.2e-2	&1.97	&1.0e-2     	&1.96	\\
16 $\times$ 16         	&1.5e-3	&2.00	&2.9e-3	&1.99	&2.6e-3     	&1.99	\\
32 $\times$ 32         	&3.8e-4	&2.00	&7.3e-4	&2.00	&6.4e-4      	&2.00	\\
\hline
\multicolumn{7}{| c |}{k=2} \\
\hline
Mesh Size & $\phi$ & rate & $\psi_{1}$ & rate &  $\psi_{2}$ & rate \\
\hline
1 $\times$ 1		&7.9e-2	&-	&2.5e-1	&-	&1.4e-1	&-	\\
2 $\times$ 2         	&9.5e-3	&3.06	&2.5e-2	&3.29	&2.8e-2     	&2.33	\\
4 $\times$ 4        	&1.2e-3	&3.03	&3.3e-3	&2.94	&3.7e-3     	&2.90	\\
8 $\times$ 8         	&1.4e-4	&3.01	&4.1e-4	&3.01	&4.5e-4     	&3.04	\\
16 $\times$ 16         	&1.8e-5	&3.00	&5.1e-5	&3.01	&5.5e-5     	&3.02	\\
32 $\times$ 32         	&2.3e-6	&3.00	&6.3e-6	&3.00	&6.9e-6      	&3.01	\\
\hline
\multicolumn{7}{| c |}{k=3} \\
\hline
Mesh Size & $\phi$ & rate & $\psi_{1}$ & rate &  $\psi_{2}$ & rate \\
\hline
1 $\times$ 1		&2.5e-2	&-	&2.9e-2	&-	&4.3e-2		&-		\\
2 $\times$ 2         	&1.2e-3	&4.37	&3.0e-3	&3.27	&4.0e-3     	&3.45	\\
4 $\times$ 4        	&8.1e-5	&3.88	&1.8e-4	&4.05	&2.5e-4     	&3.98	\\
8 $\times$ 8         	&5.2e-6	&3.95	&1.2e-5	&3.99	&1.6e-5     	&3.99	\\
16 $\times$ 16         	&3.3e-7	&3.99	&7.2e-7	&4.00	&9.9e-7     	&4.00	\\
32 $\times$ 32         	&2.1e-8	&4.00	&4.4e-8	&4.00	&6.2e-8      	&4.00	\\
\hline
\end{tabular}
\end{center} 
\caption{Poisson: ``Hybrid'' Mesh, $L^{2}$ Error and $h$-Convergence Rates.  We observe optimal convergence.}
\label{NVR:table:PoissonHybridRates}
\end{table}

\begin{table}[h!b!p!]
\begin{center}
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
\multicolumn{7}{| c |}{k=1} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&3.2e-0	&-	&9.4e-1	&-	&1.2e-0	&-	\\
2 $\times$ 2         	&1.1e-0	&1.58	&3.1e-1	&1.62	&2.7e-1     	&2.10	\\
4 $\times$ 4        	&2.9e-1	&1.88	&8.0e-2	&1.94	&6.8e-2     	&1.99	\\
8 $\times$ 8         	&6.7e-2	&2.12	&2.0e-2	&1.99	&1.7e-2     	&2.00	\\
16 $\times$ 16         	&1.5e-2	&2.14	&5.0e-3	&2.00	&4.2e-3     	&2.00	\\
32 $\times$ 32         	&3.6e-3	&2.09	&1.3e-3	&2.00	&1.1e-3      	&2.00	\\
\hline
\multicolumn{7}{| c |}{k=2} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&2.3e-0	&-	&2.6e-1	&-	&4.3e-1	&-	\\
2 $\times$ 2         	&2.8e-1	&3.02	&4.1e-2	&2.67	&4.9e-2     	&3.12	\\
4 $\times$ 4        	&3.2e-2	&3.13	&5.6e-3	&2.89	&6.3e-3     	&2.98	\\
8 $\times$ 8         	&3.8e-3	&3.11	&7.1e-4	&2.97	&7.9e-4     	&2.99	\\
16 $\times$ 16         	&4.5e-4	&3.07	&9.0e-6	&2.99	&9.9e-5     	&3.00	\\
32 $\times$ 32         	&5.5e-5	&3.03	&1.1e-5	&3.00	&1.2e-5      	&3.00	\\
\hline
\multicolumn{7}{| c |}{k=3} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&3.7e-1	&-	&5.0e-2	&-	&3.7e-2	&-	\\
2 $\times$ 2         	&3.3e-2	&3.51	&3.8e-3	&3.73	&3.3e-3     	&3.50	\\
4 $\times$ 4        	&2.5e-3	&3.69	&2.5e-4	&3.95	&2.1e-4     	&3.94	\\
8 $\times$ 8         	&1.8e-4	&3.80	&1.6e-5	&3.99	&1.3e-5     	&4.00	\\
16 $\times$ 16         	&1.1e-5	&4.06	&9.7e-7	&4.00	&8.4e-7     	&4.00	\\
32 $\times$ 32         	&5.5e-7	&4.30	&6.1e-8	&4.00	&5.2e-8      	&4.00	\\
\hline
\end{tabular}
\end{center} 
\caption{Stokes VSP: ``Hybrid'' Mesh, $L^{2}$ Error and $h$-Convergence Rates.  Rates are
close to optimal.}
\label{NVR:table:VSPHybridRates}
\end{table}

\begin{table}[h!b!p!]
\begin{center}
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
\multicolumn{7}{| c |}{k=1} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&3.0e-0	&-	&1.6e-0	&-	&2.0e-0	&-	\\
2 $\times$ 2         	&1.2e-0	&1.30	&4.6e-1	&1.80	&4.1e-1     	&2.25	\\
4 $\times$ 4        	&6.2e-1	&0.97	&1.1e-1	&2.12	&1.1e-1     	&1.93	\\
8 $\times$ 8         	&2.2e-1	&1.48	&2.7e-2	&1.99	&2.7e-2     	&2.03	\\
16 $\times$ 16         	&6.9e-2	&1.70	&6.6e-3	&2.00	&6.6e-3     	&2.02	\\
32 $\times$ 32         	&2.0e-2	&1.77	&1.7e-3	&2.00	&1.6e-3      	&2.01	\\
\hline
\multicolumn{7}{| c |}{k=2} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&2.1e-0	&-	&3.3e-1	&-	&4.6e-1	&-	\\
2 $\times$ 2         	&8.8e-2	&4.60	&5.2e-2	&2.64	&5.3e-2     	&3.12	\\
4 $\times$ 4        	&8.6e-3	&3.35	&7.0e-3	&2.91	&7.3e-3     	&2.85	\\
8 $\times$ 8         	&7.7e-4	&3.48	&8.9e-4	&2.98	&9.4e-4     	&2.96	\\
16 $\times$ 16         	&6.7e-5	&3.53	&1.1e-4	&2.99	&1.2e-4     	&2.99	\\
32 $\times$ 32         	&6.7e-6	&3.32	&1.4e-5	&3.00	&1.5e-5      	&3.00	\\
\hline
\multicolumn{7}{| c |}{k=3} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&1.7e-1	&-	&5.9e-2	&-	&5.4e-2	&-	\\
2 $\times$ 2         	&1.3e-2	&3.74	&4.2e-3	&3.81	&4.0e-3     	&3.75	\\
4 $\times$ 4        	&8.9e-4	&3.83	&2.8e-4	&3.93	&2.6e-4     	&3.97	\\
8 $\times$ 8         	&4.8e-5	&4.22	&1.7e-5	&3.99	&1.6e-5     	&4.00	\\
16 $\times$ 16         	&2.0e-6	&4.59	&1.1e-6	&4.00	&1.0e-6     	&4.00	\\
32 $\times$ 32         	&6.7e-8	&4.89	&6.8e-8	&4.00	&6.3e-8      	&4.00	\\
\hline
\end{tabular}
\end{center} 
\caption{Stokes VVP: ``Hybrid'' Mesh, $L^{2}$ Error and $h$-Convergence Rates.  Rates are close to optimal.}
\label{NVR:table:VVPHybridRates}
\end{table}

\clearpage

\section{Solution Plots}

\begin{figure}[hbh]
\begin{center}
\includegraphics[height=0.27\textheight]{plots/poissonHybrid/phicubic16x16.pdf}\\
\includegraphics[height=0.27\textheight]{plots/poissonHybrid/psi1cubic16x16.pdf}\\
\includegraphics[height=0.27\textheight]{plots/poissonHybrid/psi2cubic16x16.pdf}
\caption{Solution of Poisson with quads and triangles (cubic elements, $16 \times 16$ mesh):
$\phi$ (top pane),
$\psi_{1}$ (middle pane)
$\psi_{2}$ (bottom pane).}
\label{NVR:fig:Poisson}
\end{center}\end{figure}

\begin{figure}[hbh]
\begin{center}
\includegraphics[height=0.27\textheight]{plots/stokesVVPHybrid/pressurecubic16x16.pdf}
\includegraphics[height=0.27\textheight]{plots/stokesVVPHybrid/u1cubic16x16.pdf}
\includegraphics[height=0.27\textheight]{plots/stokesVVPHybrid/u2cubic16x16.pdf}
\caption{Solution of Stokes (VVP) with quads and triangles (cubic elements, $16 \times 16$ mesh):
$P$ (top pane),
$u_{1}$ (middle pane),
$u_{2}$ (bottom pane).}
\label{NVR:fig:Stokes}
\end{center}\end{figure}

### 2012-03-15 docs/NewBCRobustness_paper/paper.tex
committing new paper
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@376 36274a68-8941-4c93-80ef-affaed5139da

%\documentclass[11pt]{article}
\documentclass[11pt,onecolumn]{scrartcl}
%\documentclass[11pt,onecolumn,fleqn]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
\usepackage[top=2cm,bottom=3cm,left=2.5cm,right=2cm]{geometry}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{array}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{pdfpages}
%\usepackage[textsize=footnotesize,color=green]{todonotes}
\usepackage{algorithm, algorithmic}
\usepackage{tikz}
%\usetikzlibrary{%
%    decorations.pathreplacing,%
%    decorations.pathmorphing%
%}
\usepackage[normalem]{ulem}

\newcommand{\bs}[1]{\boldsymbol{#1}}
\DeclareMathOperator{\diag}{diag}

\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}

\newcommand{\tablab}[1]{\label{tab:#1}}
\newcommand{\tabref}[1]{Table~\ref{tab:#1}}

\newcommand{\theolab}[1]{\label{theo:#1}}
\newcommand{\theoref}[1]{\ref{theo:#1}}
\newcommand{\eqnlab}[1]{\label{eq:#1}}
\newcommand{\eqnref}[1]{\eqref{eq:#1}}
\newcommand{\seclab}[1]{\label{sec:#1}}
\newcommand{\secref}[1]{\ref{sec:#1}}
\newcommand{\lemlab}[1]{\label{lem:#1}}
\newcommand{\lemref}[1]{\ref{lem:#1}}

\newcommand{\mb}[1]{\mathbf{#1}}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\nor}[1]{\left\| #1 \right\|}
\newcommand{\snor}[1]{\left| #1 \right|}
\newcommand{\LRp}[1]{\left( #1 \right)}
\newcommand{\LRs}[1]{\left[ #1 \right]}
\newcommand{\LRa}[1]{\left< #1 \right>}
\newcommand{\LRc}[1]{\left\{ #1 \right\}}
\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
\newcommand{\Grad} {\ensuremath{\nabla}}
\newcommand{\Div} {\ensuremath{\nabla\cdot}}

\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
\newcommand{\tensor}[1]{\underline{\vect{#1}}}
\newcommand{\del}{\Delta}
\newcommand{\grad}{\nabla}
\newcommand{\curl}{\grad \times}
\renewcommand{\div}{\grad \cdot}
\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
\newcommand{\eip}[1]{a\left( #1 \right)}
\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}

\newcommand{\circone}{\ding{192}}
\newcommand{\circtwo}{\ding{193}}
\newcommand{\circthree}{\ding{194}}
\newcommand{\circfour}{\ding{195}}
\newcommand{\circfive}{\ding{196}}

\def\arr#1#2#3#4{\left[
\begin{array}{cc}
#1 & #2\\
#3 & #4\\
\end{array}
\right]}
\def\vecttwo#1#2{\left[
\begin{array}{c}
#1\\
#2\\
\end{array}
\right]}
\def\vectthree#1#2#3{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
\end{array}
\right]}
\def\vectfour#1#2#3#4{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
#4\\
\end{array}
\right]}

\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

\newcommand{\G} {\Gamma}
\newcommand{\Gin} {\Gamma_{in}}
\newcommand{\Gout} {\Gamma_{out}}

\begin{document}

\section{Introduction}

\subsection{Introduction to DPG}
The idea of optimal test functions was introduced by Demkowicz and Gopalakrishnan in \cite{DPG2}.  Conceptually, these optimal test functions are the result of a minimum residual method applied to the operator form of a variational equation.  Given Hilbert spaces $U$ and $V$ and a the variational problem $b(u,v) = l(v)$, $\forall u\in U, v\in V$, we can identify $B:U\rightarrow V'$ and $l \in V'$ 
\[
\left.\begin{array}{c}
b(u_h,v) = \langle Bu_h,v\rangle  \\
l(v) = \langle l,v\rangle
\end{array}\right\}
\Longleftrightarrow Bu_h = l
\]
We seek the minimization of the residual in the dual norm
\[
\min_{u_h\in U_h} J(u_h) = \frac{1}{2}\|Bu_h-l\|_{V'}^2 = \frac{1}{2} \sup_{v\in V} \| b(u_h,v)-l(v)\|_{V}^2
\]
Recall $R_V$, the Riesz operator $\langle R_V v,\delta v\rangle = (v, \delta v)_V$ identifying elements of Hilbert space with elements of the dual.  As $R_V$ and its inverse are isometries, $\|f\|_{V'} = \|R_V^{-1} f\|_V$, and 
\[
\min_{u_h\in U_h} J(u_h) = \frac{1}{2}\|Bu_h-l\|_{V'}^2 =  \frac{1}{2}\|R_V^{-1}(Bu_h-l)\|_V^2
\]
First order optimality conditions require the Gateux derivative to be zero in all directions $u_h \in U_h$.  
\begin{align*}
\left(R_V^{-1}(Bu_h-l),R_V^{-1}B\delta u_h\right)_V &= 0, \quad \forall \delta u_h \in U_h \\
\rightarrow \langle Bu_h-l, v_h\rangle &= 0, \quad v_h = R_V^{-1}B\delta u_h
\end{align*}
which returns a standard variational equation $b(u_h,v_h) - l(v_h) = 0$, for the specific choice of test functions $v_h = R_V^{-1}B\delta u_h$.  We identify the \textit{trial-to-test} operator $T = R_V^{-1}B$, which maps a trial function $u_h$ to its corresponding \textit{optimal} test function $v_h = Tu_h$.  These test functions can be solved for by solving the auxiliary variational problem
\[
\left(v_h,\delta v\right)_V = b(u_h,v)
\]

Finally, while the above variational problem is a global operation for standard continuous test spaces, the use of discontinuous test spaces reduces it to an element-local problem.  In practice, this variational problem can rarely be solved exactly and it is solved approximately using the standard Bubnov-Galerkin method and an ``enriched" subspace of $V$. We assume the corresponding error in approximation of the optimal test functions is negligible for the scope of this paper.  Further work concerning the effect of approximation error in the computation of optimal test functions can be found in \cite{practicalDPG}.

Under the standard conditions for well-posedness of the continuous variational problem, the discrete DPG method delivers the best approximation error in the ``energy norm" $\|u\|_E = \sup \frac{b(u,v)}{\|v\|_V}$.  Additionally, the actual energy error $\|u-u_h\|_E$ is computable through $\|e_h\|_V$, where
\[
\left(e_h,\delta v\right)_V = b(u-u_h,v) = b(u_h,v)-l(v)
\]
This is simply a consequence of the least-squares nature of DPG; the energy error is simply the measure of the residual in the proper norm.

\subsection{Variational form}

The DPG (discontinuous Petrov-Galerkin) method is the combination of the concept of computable optimal test functions with the so-called ``ultra-weak formulation", where every equation is relaxed.  Moreover, to maintain conformity while seeking an $L^2$ setting on interior ``field" variables, boundary terms are identified as additional new unknowns.  The result is a hybrid DG method with locally supported optimal test functions.  For a given operator equation $Au = f$, the ultra-weak formulation is 
\[
b\left(\left(\widehat{u},u\right),v\right) - l(v) = \langle \widehat{u}, v \rangle - (u,A^*v) - (f,v)
\]

\section{Choice of test norm}

Up to now, we've neglected discussion of the proper choice of inner product/norm on the space $V$.  This choice is important, as the choice of norm on $V$ determines the

Under the assumption of injectivity of the adjoint of our variational operator $B$, we can define the optimal test norm 
\[
\|v\|_{\rm opt} = \sup_{u\in U}\frac{b(u,v)}{\|u\|_U}
\]
If the solution is in $U$, then choosing $\|v\|=\|v\|_{\rm opt}$ implies 
\[
\|u\|_E = \sup_{v\in V}\frac{b(u,v)}{\|v\|_V} = \sup_{v\in V}\sup_{w\in V}\frac{b(u,v)}{b(w,v)}\|w\|_U =\sup_{w\in V}\frac{b(u,v^*)}{b(w,v^*)}\|w\|_U = \|u\|_U
\]
FIX ABOVE

This norm is non-localizable, however - even with discontinuous test functions, solving for optimal test functions under this optimal norm will result in global problems as well, due to the coupling given by the boundary terms in our bilinear form.  The ``quasi-optimal" test norm is created by removing such boundary terms and replacing them with scaled $L^2$ norms of the field variables.

\subsection{Singular perturbation problems and robustness}

Standard Bubnov-Galerkin methods tend to perform poorly for the class of partial-differential equations known as singularly perturbed problems, where a given parameter $\epsilon$ may approach either $0$ or $\infty$ in the context of physical problems.  This poor performance is captured by the error bound
\[
\|u-u_h\|_E \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_U
\]
The growth of $C$ with $\epsilon$ is referred to as a loss of robustness, where the bound on the error in the finite element solution by the best approximation error.  Intuitively, as our singular perturbation parameter changes, our finite element error is bounded more and more loosely to the best approximation error, allowing for degradation of the solution

A well-known example is the growth of spurious oscillations in the finite element solution of the 1D convection-diffusion problem $ u'-\epsilon u'' = f$ (with Dirichlet boundary conditions) as $\epsilon\rightarrow 0$.  Another class of examples are wave propagation problems, in which the singular perturbation parameter is the wavenumber, $k\rightarrow \infty$.  The lack of robustness in this case manifests as ``pollution" error, a phenomenon where the finite element solution degrades over many wavelengths (commonly manifesting as a phase error between the FE solution and the exact solution).  The DPG method is currently being analyzed for both acoustic and elastic waves in context of the Helmholtz equation \cite{DPG4} and equations of linear elasticity.  Numerically, DPG appears to yield a ``pollution-free" method for these problems under a specific regularization of the ``quasi-optimal" test norm.

\section{Model problem and robustness using DPG}

We consider the model convection-diffusion problem on domain $\Omega$ with boundary $\Gamma$
\begin{align*}
\div (\beta u - \sigma) &= f \\
\frac{1}{\epsilon}\sigma - \grad u &= 0
\end{align*}
with the corresponding variational form 
\[
b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle + \langle \widehat{f}_n, \left[v\right] \rangle
\]
where the above inner products are taken element-wise over the finite element mesh $\Omega_h$, and the duality pairings are taken on $\Gamma_h$, the mesh ``skeleton", or union of edges of elements $K$ in $\Omega_h$.  The functional setting is now well understood as well (see \cite{analysisDPG} for details) - $u,\sigma \in L^2(\Omega)$, $v \in H^1(\Omega_h)$, $\tau \in H({\rm div},\Omega_h)$, where $H^1(\Omega_h)$ and $H({\rm div},\Omega_h)$ are element-wise ``broken" Sobolev spaces.  By duality, $\widehat{u}$ lives in the trace space of $H^1(\Omega_h)$, while $\widehat{f}_n$ comes from the normal trace space of $H({\rm div},\Omega_h)$.

To analyze the robustness of DPG, we note that 
\[
b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \| u \|^2_{L^2}
\]
for the specific continuous test functions $\tau$ and $v$ satisfying
\begin{align*}
\div \tau - \beta \cdot \grad v &= g \\
\frac{1}{\epsilon}\tau + \grad v &= f
\end{align*}
with boundary conditions such that the boundary terms in the bilinear form vanish.  Then, for the above choice of $\left(\tau, v\right)$, with $g=u$ and $f=0$,
\begin{align*}
\|u\|_{L^2}^2 &= b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right)}{\|\left(\tau, v\right)\|_V}\|\left(\tau, v\right)\|_V \leq \|u\|_E \|\left(\tau, v\right)\|_V
\end{align*}
We will use the notation $\lesssim$ to denote an $\epsilon$-independent bound.  If we can show $\|\left(\tau, v\right)\|_V \lesssim \| u \|_{L^2}$ for any choice of $u \in L^2$, then dividing through by $\|u\|_{L^2}$ gives
\[
\|u\|_{L^2} \lesssim \|u\|_E
\]
which results in in robust control of the $L^2$ error by the error in the energy norm, in which DPG is optimal.  The study of robustness for the DPG method has now been reduced to proving stability estimates for the adjoint problem.

For convection-diffusion, the quasi-optimal norm is 
\[
\|\left(\tau, v\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v \|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 + C_1\|v\|_{L^2} + C_2\|\tau\|_{L^2}
\]
for some choice of constants $C_1$ and $C_2$.  We note that the optimal test norm will automatically guarantee the robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.  However, use of this norm for the convection-diffusion problem is difficult, as the quasi-optimal test norm will induce strong boundary layers of width $\epsilon/h^2$ (in comparison, in wave propagation problems, the mesh size tends to be on the order of the wavelength/singular perturbation parameter, resulting in optimal test functions that are much easier to approximate over an element).  As the relevant range of $\epsilon$ for physical problems is $1e-7$, solving on (at least) partially under-resolved meshes is unavoidable.  Resolving such boundary layers for an underresolved mesh has been investigated numerically using specially designed subgrid meshes by Niemi, Collier, and Calo in \cite{DBLP:journals/procedia/NiemiCC11}.  We approach this from a different perspective, looking instead for a robust test norm which does not induce boundary layers in the approximation of optimal test functions.

\subsection{Boundary conditions}

We split the boundary $\Gamma$ into three portions
\begin{align*}
\Gamma_{-} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\} \quad {\rm (inflow)}\\
\Gamma_{+} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\} \quad {\rm (outflow)}\\
\Gamma_{0} &\coloneqq \{x\in \Gamma; \beta_n(x) = 0\}\\
\end{align*}
Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions everywhere on $\Gamma$, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
\[
\|\left(\tau, v\right)\|_{V,w}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\|_{w+\epsilon} + \| \div \tau\|_{w+\epsilon} + \frac{1}{\epsilon}\|\tau\|_{w+\epsilon}
\]
where $\|\cdot \|_{w+\epsilon}$ is a weighted $L^2$ norm, where the weight $w \in (0,1)$ is required to vanish on $\Gamma_-$.  The need for the weight is intuitively explained by the induced adjoint problem.  The bilinear form for the Dirichlet case is
\[
b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) + \langle \widehat{f}_n, \left[v\right] \rangle
\]
Choosing a continuous conforming test function $v$ removes the contribution of the term $\langle \widehat{f}_n, \left[v\right] \rangle$ on the mesh skeleton; however, it is necessary to assume in addition $v=0$ on $\Gamma$ to have $b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \|u\|_{L^2}^2$.  Intuitively, the adjoint problem is similar to the primal problem with the direction of inflow reversed, such that the inflow becomes the outflow, and outflow inflow.  The need for the weight arises due to the presence of the Dirichlet boundary condition on $v$ near the inflow; this induces strong boundary layers at the inflow such that $\grad v \approx O(\epsilon^{-1})$. It may be of interest to note that, for sufficiently small $\epsilon$, these issues manifest themselves in numerical experiments as additional refinements near the inflow.

We improve upon the result of Demkowicz and Heuer by adopting a new inflow boundary condition, given by Hesthaven et al in \cite{Hesthaven96astable}, where we set
\[
\beta_n u - \sigma_n = f_n = u_0
\]
on $\Gamma_-$, and continue with the wall boundary condition $u=0$ on $\Gamma_+$.  For our model problem, as for most problems of interest in CFD, we expect $\grad u$ to be small near the inflow, and that the solution using $u=u_0$ and $\beta_n u - \sigma_n = f_n = u_0$ should converge to each other for sufficiently small $\epsilon$.

Under the new inflow conditions, the induced bilinear form is now
\[
b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+}
\]
The corresponding adjoint problem now has boundary conditions
\begin{align}
\tau_n &= 0, \quad x\in \Gamma_- \label{eq:adj_bc1}\\
v &= 0, \quad x\in \Gamma_+ \label{eq:adj_bc2}
\end{align}
and it can be shown that DPG is robust using an unweighted version of the test norm in \cite{DPGrobustness}
\[
\|\left(\tau, v\right)\|_{V}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\| + \| \div \tau\| + \frac{1}{\epsilon}\|\tau\|
\]

\subsection{Stability of the adjoint problem (bound from below)}

We reduce the adjoint problem to the scalar second order equation
\begin{equation}
- \epsilon \Delta v - \beta \cdot \grad v = g - \epsilon \div f \label{adjoint}
\end{equation}
with boundary conditions
\begin{align*}
\tau_n = - \epsilon \grad v \cdot n &=f\cdot n, \quad x\in \Gamma_-\\
v &= 0, \quad x\in \Gamma_+ 
\end{align*}
and treat the cases $f=0$, $g=0$ separately.  The above boundary conditions reduce down to \eqref{eq:adj_bc1} and \eqref{eq:adj_bc2} when requesting $L^2$ robustness in $u$ ($f=0$); these more general boundary conditions are necessary for bounds involving $f \neq 0$.

Additionally, the $\div$ operator is understood now in the weak sense, as the dual operator of $-\grad : H_0^1(\Omega) \rightarrow L^2(\Omega)$, such that $\div f \in \left(H_0^1(\Omega)\right)'$.  $f\cdot n$ is understood as a limit; smooth functions are dense in $H^1(\Omega)$, and we define $f\cdot n$ as the limit of $f_i\cdot n$, where $f_i \in C^\infty(\Omega)$, $f_i \rightarrow f$.

For this analysis, it will be necessary to assume conditions on $\beta$.  For each proof, we require $\beta \in C^2(\bar{\Omega})$ and $\beta, \div \beta = O(1)$.  Additionally, we will assume one or both of the following assumptions
\begin{align}
&\curl \beta = 0, \quad 0<C \leq \left | \beta\right |^2 + \frac{1}{2}\div \beta, \quad C = O(1) \label{a_req}\\
&\grad \beta + \grad \beta ^T - \div \beta I = O(1) \label{b_req}
\end{align}

\begin{lemma} 
\label{lemma_1}
Assuming \eqref{a_req} and \eqref{adjoint} hold, for sufficiently small $\epsilon$, 
\[
\epsilon \|\grad v\|^2 + \|v\|^2 \lesssim \|g\| + \epsilon \| f\|
\]
\end{lemma}

\begin{proof}
Since $\curl \beta=0$, and $\Omega$ is simply connected, there exists a scalar potential $\psi$, $\grad \psi = \beta$ such that $e^\psi = O(1)$.  Take the transformed function $w = e^\psi v$; following (2.26) in \cite{DPGrobustness}, we substitute $w$ into the the left hand side of equation \eqref{adjoint}, arriving at the relation  
\[
-\epsilon \Delta w - (1-2\epsilon) \beta \cdot \grad w + \left((1-\epsilon)|\beta|^2 + \epsilon \div \beta\right) w = e^\psi (g-\epsilon \div f)
\]
Multiplying by $w$ and integrating over $\Omega$ gives
\[
-\epsilon \int_\Omega \Delta ww - (1-2\epsilon) \int_\Omega\beta \cdot \grad w w + \int_\Omega\left((1-\epsilon)|\beta|^2 + \epsilon \div \beta\right) w^2 = \int_\Omega e^\psi (g-\epsilon \div f) w
\]
Integrating by parts gives
\[
-\epsilon \int_\Omega \Delta ww - (1-2\epsilon) \int_\Omega\beta \cdot \grad w w = \epsilon \left( \int_\Omega |\grad w|^2- \int_{\Gamma} w \grad w \cdot n  \right) + \frac{(1-2\epsilon) }{2} \left(\int_\Omega \div \beta w^2 - \int_\Gamma\beta_n w^2 \right)
\]
Noting that $w=0$ on $\Gamma_+$ reduces the boundary integrals over $\Gamma$ to just the inflow $\Gamma_-$.  Furthermore, we have the relation $\grad w = e^\psi(\grad v + \beta v)$.  Applying the above and boundary conditions on $\Gamma_-$, the first boundary integral becomes
\[
\int_{\Gamma_-} w \grad w \cdot n = \int_{\Gamma_-} we^\psi(\grad v + \beta v)\cdot n =  \int_{\Gamma_-} we^\psi(f\cdot n + \beta_n v)
\]
Noting $\int_{\Gamma_-}\beta_n w^2 \leq 0$ through $\beta_n<0$ on the inflow gives
\[
\epsilon \int_\Omega |\grad w|^2 + \int_\Omega \left((1-\epsilon)|\beta|^2 + \frac{1}{2} \div \beta \right) w^2 - \epsilon \int_{\Gamma_-} we^\psi f\cdot n \leq \int_\Omega e^\psi (g-\epsilon \div f) w
\]
assuming $\epsilon$ is sufficiently small.  Our assumptions on $\beta$ allow us to bound $\left((1-\epsilon)|\beta|^2 + \frac{1}{2} \div \beta \right) \lesssim 1$ and $e^\psi \lesssim 1$. We can then bound the left hand side from below by
\[
\epsilon \|\grad w\|^2 + \|w\|^2 - \epsilon \int_{\Gamma_-} we^\psi f\cdot n  \lesssim \epsilon \int_\Omega |\grad w|^2 + \int_\Omega \left((1-\epsilon)|\beta|^2 + \frac{1}{2} \div \beta \right) w^2 - \epsilon \int_{\Gamma_-} we^\psi f\cdot n 
\]
Interpreting $\div f$ as a functional, the right hand gives
\begin{align*}
\int_\Omega e^\psi (g-\epsilon \div f) w &= \int_\Omega e^\psi g + \int_\Omega \epsilon f \cdot \grad (e^\psi w) - \int_\Gamma \epsilon f\cdot n e^\psi w\\
\end{align*}
The boundary integral on $\Gamma$ reduces to $\Gamma_-$, which is then nullified by the same term on the left hand side, leaving us with 
\[
\epsilon \|\grad w\|^2 + \|w\|^2 \lesssim \int_\Omega e^\psi g + \int_\Omega \epsilon f \cdot \grad (e^\psi w) = \int_\Omega e^\psi g + \int_\Omega \epsilon f \cdot (\beta w + \grad w)
\]
From here, the proof is identical to \cite{DPGrobustness}; an application of Peter-Paul Young's inequality to the right hand side and bounds on $\|v\|, \|\grad v\|$ by $\|w\|,\|\grad w\|$ complete the estimate.  
%ISSUE: REMOVE BOUNDARY TERM
\end{proof}

\begin{lemma} 
\label{lemma_2}
Assume $v$ satisfies $\eqref{adjoint}$ and $\beta$ satisfies \eqref{a_req} and \eqref{b_req}.  If $\div f = 0$ and $\epsilon$ is sufficiently small, 
\[
\|\beta \cdot \grad v \| \lesssim \| f\|
\]
\end{lemma}

\begin{proof}
Define $v_\beta = \beta\cdot \grad v$.  Multiplying by $v_\beta$ and integrating over $\Omega$ gives
\[
\|v_\beta\|^2 = -\int_\Omega g v_\beta - \epsilon \int_\Omega \Delta v v_\beta
\]
Note that 
\[
-\int_{\Omega} \beta\cdot \grad v \del v = -\int_{\Omega} \beta\cdot \grad v \div \grad v
\]
Integrating this by parts, we get
\[
-\int_{\Omega} \beta\cdot \grad v \div \grad v = \int_{\Omega}\grad (\beta\cdot \grad v) \cdot \grad v  - \int_{\Gamma}n\cdot \grad v \beta\cdot\grad v
\]
Note that 
\[
\grad (\beta \cdot \grad v) = \grad \beta \cdot \grad v + \beta \cdot \grad \grad v
\]
where $\grad \beta$ and $\grad \grad v$ are understood to be tensors. Then, 
\[
\int_{\Omega}\grad (\beta\cdot \grad v) \cdot \grad v = \int_{\Omega}(\grad \beta\cdot \grad v) \cdot \grad v + \int_{\Omega}\beta\cdot \grad\grad v \cdot \grad v 
\]
Noting that $\grad v \cdot \grad \grad v = \grad\frac{1}{2}\left(\grad v\cdot \grad v\right)$, if we integrate by parts again, we get
%\[
%\int_{\Omega}\beta\cdot \grad\grad v \cdot \grad v = \frac{1}{2}\int_{\Omega}\beta\cdot \grad(\grad v \cdot \grad v ) = \frac{1}{2}\int_{\Gamma}\beta_n (\grad v \cdot \grad v ) - \frac{1}{2}\int_{\Omega}\div \beta (\grad v \cdot \grad v )
%\]
%Then, we can combine these terms to get
\begin{align*}
-\int_{\Omega}  \del vv_\beta &= - \int_{\Gamma}n\cdot \grad v \beta\cdot\grad v + \frac{1}{2}\int_{\Gamma}\beta_n (\grad v \cdot \grad v ) - \frac{1}{2}\int_{\Omega}\div \beta (\grad v \cdot \grad v ) + \int_{\Omega}(\grad \beta\cdot \grad v) \cdot \grad v\\
&= - \int_{\Gamma}n\cdot \grad v \beta\cdot\grad v + \frac{1}{2}\int_{\Gamma}\beta_n (\grad v \cdot \grad v ) + \int_{\Omega} \grad v \left(\grad \beta - \frac{1}{2}\div \beta I\right)\grad v
\end{align*}
Finally, substituting this into our adjoint equation multiplied by $v_\beta$, we get
\[
\| v_\beta\|^2 = -\int_{\Omega}g\beta\cdot \grad v +  \epsilon\int_{\Gamma}  \left( -n\cdot \grad v \beta + \frac{1}{2}\beta_n \grad v \right) \cdot \grad v + \epsilon\int_{\Omega} \grad v \left(\grad \beta - \frac{1}{2}\div \beta I\right)\grad v
\]
%The first term on the RHS can be controlled using Young's inequality. 
The last term can be bounded by our assumption on $\|\grad \beta - \frac{1}{2}\div \beta I\|^2 \leq C$.
\[
\epsilon \int_{\Omega} \grad v \left(\grad \beta - \frac{1}{2}\div \beta I\right)\grad v \leq C\frac{\epsilon}{2} \|\grad v\|^2
\]
For the boundary terms, on $\Gamma_-$, $\grad v\cdot n = 0$, reducing the above to $\beta_n|\grad v|^2 \leq 0$.  On $\Gamma_+$, $v=0$ implies $\grad v \cdot \tau = 0$, where $\tau$ is a tangential direction.  An orthogonal decomposition yields $\grad v = (\grad v \cdot n) n$, reducing the above to 
\[
 \epsilon\int_{\Gamma}  -\frac{1}{2}|\beta_n| (\grad v \cdot n)^2 \leq 0
\]
leaving us with the estimate
\[
\|v_\beta\|^2 \leq  -\int_{\Omega}g\beta\cdot \grad v + C\frac{\epsilon}{2} \|\grad v\|^2
\]
Since $C=O(1)$, an application of Young's inequality and Lemma 1 complete the estimate.

\end{proof}

\subsection{Energy norm equivalence (bound from above)}

\section{Numerical experiments}

In our numerical experiments, we will be interested

\subsection{Erickson model problem}

\subsection{Setting just $u_0$, not $u_0-\sigma_n$}

\subsection{Near discontinuous hat}

\section{Conclusions}
\bibliographystyle{plain}
\bibliography{paper}

\end{document}

### 2012-03-19 docs/NewBCRobustness_paper/paper.tex
adding figs and updates to paper
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@377 36274a68-8941-4c93-80ef-affaed5139da

@@
 \usepackage{tikz}
+\usepackage{subfigure}
 %\usetikzlibrary{%
@@
 where the above inner products are taken element-wise over the finite element mesh $\Omega_h$, and the duality pairings are taken on $\Gamma_h$, the mesh ``skeleton", or union of edges of elements $K$ in $\Omega_h$.
+Define the interior skeleton $\Gamma_h^0 = \Gamma_h \setminus \Gamma$.
 The functional setting is now well understood as well (see \cite{analysisDPG} for details) - $u,\sigma \in L^2(\Omega)$, $v \in H^1(\Omega_h)$, $\tau \in H({\rm div},\Omega_h)$, where $H^1(\Omega_h)$ and $H({\rm div},\Omega_h)$ are element-wise ``broken" Sobolev spaces.
@@
 \end{align*}
-with boundary conditions such that the boundary terms in the bilinear form vanish.  Then, for the above choice of $\left(\tau, v\right)$, with $g=u$ and $f=0$,
+with $g=u$ and $f=0$, and with boundary conditions such that the boundary terms in the bilinear form vanish.  Then, for the above choice of $\left(\tau, v\right)$, 
 \begin{align*}
@@
 We note that the optimal test norm will automatically guarantee the robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.
-However, use of this norm for the convection-diffusion problem is difficult, as the quasi-optimal test norm will induce strong boundary layers of width $\epsilon/h^2$ (in comparison, in wave propagation problems, the mesh size tends to be on the order of the wavelength/singular perturbation parameter, resulting in optimal test functions that are much easier to approximate over an element).
-As the relevant range of $\epsilon$ for physical problems is $1e-7$, solving on (at least) partially under-resolved meshes is unavoidable.
+However, use of this norm for the convection-diffusion problem is difficult - the variational problem for optimal test functions using the quasi-optimal test norm is equivalent to a reaction-diffusion system \cite{DBLP:journals/procedia/NiemiCC11}.
+Transforming the problem to the reference element reveals that will induce strong boundary layers of width $\epsilon/h^2$ (in comparison, in wave propagation problems, the mesh size tends to be on the order of the wavelength/singular perturbation parameter, resulting in smooth optimal test functions that are much easier to approximate over the reference element).
+As the relevant range of $\epsilon$ for physical problems is $1e-7$, solving on partially under-resolved meshes is unavoidable.
 Resolving such boundary layers for an underresolved mesh has been investigated numerically using specially designed subgrid meshes by Niemi, Collier, and Calo in \cite{DBLP:journals/procedia/NiemiCC11}.
-We approach this from a different perspective, looking instead for a robust test norm which does not induce boundary layers in the approximation of optimal test functions.
+We approach this from a different perspective, looking instead for robust test norms which do not induce boundary layers in the approximation of optimal test functions.
 
@@
 \]
-Choosing a continuous conforming test function $v$ removes the contribution of the term $\langle \widehat{f}_n, \left[v\right] \rangle$ on the mesh skeleton; however, it is necessary to assume in addition $v=0$ on $\Gamma$ to have $b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \|u\|_{L^2}^2$.
-Intuitively, the adjoint problem is similar to the primal problem with the direction of inflow reversed, such that the inflow becomes the outflow, and outflow inflow.
+Choosing a continuous conforming test function $v$ removes the contribution of the term $\langle \widehat{f}_n, \left[v\right] \rangle$ on the mesh skeleton; however, it is necessary to assume in addition $v=0$ on $\Gamma$ to have
+$$b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \|u\|_{L^2}^2.$$  Intuitively, the adjoint problem is similar to the primal problem with the direction of inflow reversed, such that the inflow becomes the outflow, and outflow inflow.
 The need for the weight arises due to the presence of the Dirichlet boundary condition on $v$ near the inflow; this induces strong boundary layers at the inflow such that $\grad v \approx O(\epsilon^{-1})$.
@@
 \begin{align}
-\tau_n &= 0, \quad x\in \Gamma_- \label{eq:adj_bc1}\\
+\tau_n &= 0, \quad x\in \Gamma_-\cup \Gamma_0 \label{eq:adj_bc1}\\
 v &= 0, \quad x\in \Gamma_+ \label{eq:adj_bc2}
@@
 \end{align}
+The second lemma concerns the robust control of $u$ by the energy error; the first and third concern the robust control of field variable $\sigma$ and flux/trace variables, respectively.
 
@@
 Since $C=O(1)$, an application of Young's inequality and Lemma 1 complete the estimate.
-
 \end{proof}
 
+\begin{lemma}
+\label{lemma_3}
+Let $\beta$ satisfy \eqref{a_req} and $\div \beta = 0$, and $f=g=0$.  Then, there holds
+\[
+\|\grad v\| = \frac{1}{\epsilon}\|\tau\| \lesssim \frac{1}{\epsilon} \| [\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v]\|_{\Gamma_h^0 \cup \Gamma_+}
+\]
+\end{lemma}
+\begin{proof}
+We follow \cite{analysisDPG} and \cite{DPGrobustness} in decomposing $\tau$ into $z\in H({\rm curl},\Omega)$ and $\psi\in H^1(\Omega)$ such that
+\[
+\tau = \left(\epsilon \grad \psi - \beta \psi\right) + \curl z
+\]
+Specifically, $\psi$ is chosen as the solution to 
+\begin{align*}
+-\epsilon \grad \psi + \div \left(\beta \psi\right) &= -\div \tau \\
+\epsilon \grad \psi \cdot n - \beta_n \psi - \tau\cdot n &= 0, \quad x\in \Gamma_-\\
+\psi &= 0, \quad x\in \Gamma_+ 
+\end{align*}
+Since $\div \beta = 0$, we satisfy \eqref{a_req}, and can use Lemma 1 (with $f = \frac{1}{\epsilon}\tau$) to bound
+\[
+\epsilon \|\grad \psi\|^2 + \|\psi \|^2 = \frac{1}{\epsilon}\|\tau\|^2
+\]
+By the above bound and triangle inequality, 
+\[
+\|\curl z \| \leq \epsilon \|\grad \psi\| + \|\beta \psi\| + \|\tau\| \lesssim \frac{1}{\sqrt{\epsilon}}\|\tau\|
+\]
+On the other hand, using the decomposition and boundary conditions directly, we have
+\begin{align*}
+\|\tau\|^2 &= (\tau, \epsilon \grad \psi - \beta \psi + \curl z) = (\tau, \epsilon \grad \psi) - (\tau,\beta \psi) + (\tau,\curl z)  \\
+&=(\tau, \epsilon \grad \psi) + \epsilon(\grad v,\beta \psi) - \epsilon(\grad v,\curl z)  \\
+&=\epsilon \langle [\tau \cdot n],\psi \rangle - \epsilon  \langle n\cdot \curl z, [v]\rangle = \epsilon \langle [\tau \cdot n],\psi \rangle_{\Gamma_h \setminus \Gamma_+} - \epsilon  \langle n\cdot \curl z, [v]\rangle_{\Gamma_h \cup \Gamma_+}\\
+&\lesssim \epsilon \|[\tau \cdot n]\|_{\Gamma_h \setminus \Gamma_+} \|\psi\| + \epsilon \| [v]\|_{\Gamma_h \cup \Gamma_+}\| n\cdot \curl z \| 
+\end{align*}
+by the boundary norms, which are defined by duality
+\begin{align*}
+\|[\tau\cdot n]\|_{\Gamma_h} &\coloneqq \sup_{w\in H^1} \frac{\langle [\tau \cdot n], w\rangle}{\|w\|_{H^1(\Omega)}}\\
+\|[v]\|_{\Gamma_h} &\coloneqq \sup_{\eta\in H({\rm div})} \frac{\langle v, \eta\cdot n\rangle}{\|\eta\|_{H({\rm div},\Omega)}}
+\end{align*}
+Applying the above estimates for $\|\psi\|$ and $\|n\cdot \curl z\|$ and noting that $\|\grad v\| = \frac{1}{\epsilon}\|\tau\|$ completes the proof.
+\end{proof}
 \subsection{Energy norm equivalence (bound from above)}
+
+TODO: FINISH THIS.
 
@@
 
-In our numerical experiments, we will be interested
+In our numerical experiments, we will be interested in the use of the unweighted test norm 
+\[
+\|\left(\tau, v\right)\|_{V}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\| + \| \div \tau\| + \frac{1}{\epsilon}\|\tau\|
+\]
+However, the presence of both $\|v\|$ and $\epsilon\|\grad v\|$ terms, and similarly $\|\div \tau\|$ and $\frac{1}{\epsilon}\|\tau\|$ terms, induces boundary layers in the optimal test functions, though only in the crosswind direction.
+To avoid this effect, we follow \cite{DPGrobustness} in scaling the $L^2$ contributions of $v$ and $\tau$ such that, when transformed to the reference element, both $v$ and $\grad v$ terms are $O(1)$.
+In this paper, we consider only isotropic refinements on quadrilateral elements, such that $h_1 = h_2 = h$, and $|K| = h^2$.
+\[
+\|\left(\tau, v\right)\|_{V}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\| + \| \div \tau\| + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|
+\]
+This modified test norm avoids boundary layers, but for adaptive meshes, provides additional stability in areas of heavy refinement.
+Intuitively, this is justifiable by the fact that best approximation error is typically largest near boundary layers, where refinements tend to aggregate.
+Additionally, test norms that differ from element to element fit cleanly into the DPG framework - as the best approximation error tends to be negligible in areas where the solution is smooth, the finite element error will be small in those areas, even with slightly suboptimal robustness.
 
@@
 
+For the choice of $\Omega = [0,1]^2$ and $\beta = (1,0)^T$, the convection diffusion equation reduces to
+\[
+\pd{u}{x} - \epsilon \left(\pdd{u}{x}+ \pdd{u}{y}\right) = f
+\]
+which, for $f=0$, has an exact solution by separation of variables, allowing us to analyze convergence of DPG for a wide range of $\epsilon$.
+For boundary conditions, we impose $u=0$ on $\Gamma_+$ and $\beta_n u - \sigma_n$ on $\Gamma_-$, which reduces to
+\begin{align*}
+u-\sigma_x &= u_0-\sigma_{x,0}, \quad x=0\\
+\sigma_y &=  0, \quad y=0,1\\
+\end{align*}
+In this case, our exact solution is the series
+\[
+u(x,y) = C_0 + \sum_{n=1}^\infty C_n \frac{\exp(r_2(x-1)-\exp(r_1(x-1)))}{r_1\exp(-r2) - r_2\exp(-r1)}\cos(n\pi y)
+\]
+where
+\begin{align*}
+r_{1,2} &= \frac{1 \pm \sqrt{1 + 4 \epsilon\lambda_n}}{2 \epsilon}\\
+\lambda_n &= n^2\pi^2 \epsilon
+\end{align*}
+The constants $C_n$ depend on a given inflow condition $u_0$ at $x=0$
+\[
+C_n = \int_0^1 u_0(y) \cos(n\pi y)
+\]
+
+\subsection{Solution with $C_1 = 1, C_n = 0, n\neq 1$}
+
+We begin with the solution taken to be the first non-constant mode of the above series.
+We set the inflow boundary condition to be exactly the value of $u-\sigma_x$ corresponding to the exact solution.
+
+\begin{figure}[h]
+\centering
+\subfigure{
+\includegraphics[scale=.37]{figs/wallBC_exact_u.png}
+}
+\subfigure{
+\includegraphics[scale=.37]{figs/wallBC_exact_sigx.png}
+}
+\subfigure{
+\includegraphics[scale=.37]{figs/wallBC_exact_sigy.png}
+}
+\caption{Solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
+\end{figure}
+
+In each case, we begin with a square 4 by 4 mesh of quadrilateral elements with order $p=3$.
+We choose $\Delta p = 5$, though we note that the behavior of DPG is nearly identical for any $\Delta p > 3$.
+$h$-refinements are executed using a greedy refinement algorithm, where element energy error $e_K^2$ is computed for all elements $K$, and elements such that $e_K^2 \leq \alpha \max_K e_K^2$ are refined.
+We make the arbitrary choice of taking $\alpha = .2$ for each of these experiments.
+
+\begin{figure}[h]
+\centering
+\includegraphics[scale=.4]{figs/u_pointdiff_wallBC.png}
+\caption{Adapted mesh and pointwise error for $\epsilon=.01$}
+\end{figure}
+
+We are especially interested in the ratio of energy error and $L^2$ error.
+Stability estimates imply that, using the above test norm, $\|u-u_h\|_{L^2} / \|u-u_h\|_E \sim C$ independent of $\epsilon$.
+Figure~\ref{ratios_simple} seems to imply that, at least for this model problem, $C=O(1)$.
+
+\begin{figure}[h!]
+\centering
+\subfigure{
+\includegraphics[scale=.38]{figs/errorrates_wallBC.png}
+}
+\subfigure{
+\includegraphics[scale=.38]{figs/L2energyratio_wallBC.png}
+}
+\caption{$L^2$ and energy errors, and their ratio for $\epsilon=.01$, $\epsilon=.001$, $\epsilon=.0001$}
+\label{ratios_simple}
+\end{figure}
+
+The effect of the test norm on mesh dependence can be seen in the ratios of $L^2$ to energy error; as the mesh is refined, the constants in front of the $L^2$ terms for $v$ and $\tau$ converge to stationary values, and the ratio of $L^2$ to energy error transitions from a smaller to a larger value.
+The transition point happens later for smaller $\epsilon$, which we expect, since the transition of the ratio corresponds to the introduction of elements of order $\epsilon$ through mesh refinement.
+
 \subsection{Setting just $u_0$, not $u_0-\sigma_n$}
 
+In practice, we will not have prior knowledge of $\sigma_n$ at the inflow, and will have to set $\beta_n u - \sigma_n = u_0$, ignoring the viscous contribution to the boundary condition.
+The hope is that for small $\epsilon$, this omission will be negligible.
+
 \subsection{Near discontinuous hat}
+
+We note also that an additional advantage of selecting this new boundary condition is a relaxation of regularity requirements; strictly discontinuous inflow boundary conditions are no longer ``variational crimes".
 

### 2012-03-19 docs/NewBCRobustness_paper/paper.tex
committing modified changes to paper (adding figs, adding discontinuous inflow section
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@380 36274a68-8941-4c93-80ef-affaed5139da

@@
 
-\subsection{Setting just $u_0$, not $u_0-\sigma_n$}
+\subsection{Neglecting $\sigma_n$}
 
@@
 The hope is that for small $\epsilon$, this omission will be negligible.
+Figure~\ref{ratios_noSigma} indicates that, between $\epsilon = .005$ and $\epsilon = .001$, the omission of $\sigma_n$ in the boundary condition becomes negligible, and both our error rates and ratios of $L^2$ to energy error become identical to the case where $\sigma_n$ is explicitly accounted for, well within the range of $\epsilon$ of physical interest.
+However, even for large $\epsilon = .01$, the $L^2$ error stagnates around $1e-3$, which is only $7%$ relative error.
 
-\subsection{Near discontinuous hat}
+\begin{figure}[h!]
+\centering
+\subfigure{
+\includegraphics[scale=.38]{figs/rates_noSigma.png}
+}
+\subfigure{
+\includegraphics[scale=.38]{figs/ratio_noSigma.png}
+}
+\caption{$L^2$ and energy errors, and their ratio for $\epsilon=.01$, $\epsilon=.005$, $\epsilon=.001$, $\epsilon=.0001$}
+\label{ratios_noSigma}
+\end{figure}
 
-We note also that an additional advantage of selecting this new boundary condition is a relaxation of regularity requirements; strictly discontinuous inflow boundary conditions are no longer ``variational crimes".
+\subsection{Discontinuous inflow data}
+
+We note also that an additional advantage of selecting this new boundary condition is a relaxation of regularity requirements; as $\widehat{f}_n \in H^{-1/2}(\Omega)$, strictly discontinuous inflow boundary conditions are no longer ``variational crimes".
+We use the discontinuous inflow data
+\[
+u_0(y) = \begin{cases}
+(y-1)^2&, \quad y>.5\\
+y^2&, \quad y\leq .5 
+\end{cases}
+\]
 

### 2012-03-20 docs/NewBCRobustness_paper/paper.tex
committing 3/19 changes
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@381 36274a68-8941-4c93-80ef-affaed5139da

@@
 
+\tableofcontents
+
 \section{Introduction}
@@
 \]
-If the solution is in $U$, then choosing $\|v\|=\|v\|_{\rm opt}$ implies 
+If the solution is in $U$, then choosing $\|v\|=\|v\|_{\rm opt}$ implies $\|u\|_E = \|u\|_U$.
+The proof is simple; we have by definition that $b(u,v) \leq \|u\|_U\|v\|_V$.
+The reverse $b(u,v) \leq \|u\|_U\|v\|_V$ is proved by
 \[
-\|u\|_E = \sup_{v\in V}\frac{b(u,v)}{\|v\|_V} = \sup_{v\in V}\sup_{w\in V}\frac{b(u,v)}{b(w,v)}\|w\|_U =\sup_{w\in V}\frac{b(u,v^*)}{b(w,v^*)}\|w\|_U = \|u\|_U
+\inf_{u\in U} \frac{\|u\|_E}{\|u\|_U} = \inf_{u\in U} \sup_{v\in V}\frac{b(u,v)}{\|v\|_V\|u\|_U} = \inf_{v\in V} \sup_{u\in U}\frac{b(u,v)}{\|v\|_V\|u\|_U} = \inf_{v\in V} \frac{\|v\|_V}{\|v\|_V} = 1
 \]
-FIX ABOVE
+where we're able to switch the order of $\inf$ and $\sup$ due to the injectivity of $B$ (see  \cite{BabuskaEquivBrezzi}).
 
@@
 The functional setting is now well understood as well (see \cite{analysisDPG} for details) - $u,\sigma \in L^2(\Omega)$, $v \in H^1(\Omega_h)$, $\tau \in H({\rm div},\Omega_h)$, where $H^1(\Omega_h)$ and $H({\rm div},\Omega_h)$ are element-wise ``broken" Sobolev spaces.
-By duality, $\widehat{u}$ lives in the trace space of $H^1(\Omega_h)$, while $\widehat{f}_n$ comes from the normal trace space of $H({\rm div},\Omega_h)$.
+By duality, $\widehat{u}$ lives in $H^{1/2}(\Gamma_h)$, the trace space of $H^1(\Omega_h)$, while $\widehat{f}_n$ comes from $H^{-1/2}(\Gamma_h)$, the normal trace space of $H({\rm div},\Omega_h)$.
 
@@
 We will use the notation $\lesssim$ to denote an $\epsilon$-independent bound.
-If we can show $\|\left(\tau, v\right)\|_V \lesssim \| u \|_{L^2}$ for any choice of $u \in L^2$, then dividing through by $\|u\|_{L^2}$ gives
+If we can show $\|\left(\tau, v\right)\|_V \lesssim \| g \|_{L^2}$ for any choice of $g \in L^2$, then, for $g=u$, dividing through by $\|u\|_{L^2}$ gives
 \[
@@
 
-\subsection{Boundary conditions}
+\subsection{Boundary conditions and adjoint stability}
 
@@
 \]
-The corresponding adjoint problem now has boundary conditions
+The corresponding adjoint problem for $L^2$ stability of $u$ now has boundary conditions
 \begin{align}
@@
 \end{align}
-and it can be shown that DPG is robust using an unweighted version of the test norm in \cite{DPGrobustness}
+
+\subsection{Norms on $U$}
+
+Given the boundary conditions on $\widehat{u}$ and $\widehat{f}_n$, we can now also define the trace norms as (canonical) minimum energy extension norms 
+\begin{align*}
+\|\widehat{u}\| &= \inf_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+}=0, \left.w\right |_{\Gamma_h\setminus \Gamma_+ } = \widehat{u}} \|w\|_{H^1(\Omega)}\\
+\|\widehat{f}_n\| &= \inf_{q\in H({\rm div},\Omega), \left.q\cdot n\right|_{\Gamma_-}= 0, \left. q\cdot n \right |_{\Gamma_h} = \widehat{f}_n} \|q\|_{H({\rm div},\Omega)}
+\end{align*}
+We will construct norms on $U$ as combinations of norms on each variable
+\[
+\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\|_U = C_1 \|u\|_{L^2} + C_2 \|\sigma\|_{L^2} + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|
+\]
+
+\subsection{Main result}
+
+For this analysis, it will be necessary to assume certain conditions on $\beta$.
+For each proof, we require $\beta \in C^2(\bar{\Omega})$ and $\beta, \div \beta = O(1)$.
+Additionally, we will assume one or both of the following assumptions
+\begin{align}
+&\curl \beta = 0, \quad 0<C \leq \left | \beta\right |^2 + \frac{1}{2}\div \beta, \quad C = O(1) \label{a_req}\\
+&\grad \beta + \grad \beta ^T - \div \beta I = O(1) \label{b_req}\\
+&\div \beta = 0 \label{c_req}
+\end{align}
+
+The primary result of this paper is that, if conditions \ref{a_req},\ref{b_req}, and \ref{c_req} are all satisfied, the DPG method provides robust control over the $L^2$ error 
+\[
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-\left(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h}\right)\right\|_{U_1} \lesssim \inf_{w\in U_h}\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-w_h \right\|_{E}
+\]
+using the unweighted version of the test norm in \cite{DPGrobustness}
 \[
@@
 \]
+where $\|\cdot \|_{U_1}$ is defined as
+\[
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U_1}^2 \coloneqq \|u\|^2 + \|\sigma\|^2 + \epsilon^2\|\widehat{u}\|^2+\epsilon \|\widehat{f}_n\|^2.
+\]
+A second, weaker result is an upper bound on the energy norm
+\[
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-\left(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h}\right)\right\|_{E} \lesssim \inf_{w\in U_h}\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-w_h\right\|_{U_2}
+\]
+where $\|\cdot \|_{U_2}$ is defined as
+\[
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U_2}^2 \coloneqq \|u\|^2 + \frac{1}{\epsilon^2}\|\sigma\|^2 + \frac{1}{\epsilon}\|\widehat{u}\|^2+\frac{1}{\epsilon} \|\widehat{f}_n\|^2.
+\]
+The upper bound on the energy norm appears to depend on $\epsilon^{-1}$, implying that, at most, we have the bound from below $\|u-u_h\|_{U} \geq \epsilon\|u-u_h\|_E$.
+However, numerical experiments demonstrate much better results, and suggest that, at least for our examples, $\|u-u_h\|_E \lesssim \|u-u_h\|_{U}$, implying that the induced energy norm is equivalent to the canonical norms we've chosen on our group variable $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)$.
 
@@
 Additionally, the $\div$ operator is understood now in the weak sense, as the dual operator of $-\grad : H_0^1(\Omega) \rightarrow L^2(\Omega)$, such that $\div f \in \left(H_0^1(\Omega)\right)'$.
-$f\cdot n$ is understood as a limit; smooth functions are dense in $H^1(\Omega)$, and we define $f\cdot n$ as the limit of $f_i\cdot n$, where $f_i \in C^\infty(\Omega)$, $f_i \rightarrow f$.
+The normal trace $f\cdot n$ is understood as a limit; smooth functions are dense in $H^1(\Omega)$, and we define $f\cdot n$ as the limit of $f_i\cdot n$, where $f_i \in C^\infty(\Omega)$, $f_i \rightarrow f$.
 
-For this analysis, it will be necessary to assume conditions on $\beta$.
-For each proof, we require $\beta \in C^2(\bar{\Omega})$ and $\beta, \div \beta = O(1)$.
-Additionally, we will assume one or both of the following assumptions
-\begin{align}
-&\curl \beta = 0, \quad 0<C \leq \left | \beta\right |^2 + \frac{1}{2}\div \beta, \quad C = O(1) \label{a_req}\\
-&\grad \beta + \grad \beta ^T - \div \beta I = O(1) \label{b_req}
-\end{align}
 The second lemma concerns the robust control of $u$ by the energy error; the first and third concern the robust control of field variable $\sigma$ and flux/trace variables, respectively.
@@
 \label{lemma_3}
-Let $\beta$ satisfy \eqref{a_req} and $\div \beta = 0$, and $f=g=0$.  Then, there holds
+Let $\beta$ satisfy \eqref{a_req} and \eqref{c_req}, and let $f=g=0$.  Then, there holds
 \[
@@
 \end{align*}
-by the boundary norms, which are defined by duality
+by the boundary norms for $v$ and $\tau$, which are defined by duality
 \begin{align*}
@@
 \end{proof}
+
 \subsection{Energy norm equivalence (bound from above)}
 
-TODO: FINISH THIS.
+We've shown the robust bound of a norm on $U$ by energy error; for a full equivalence statement between the energy norm and norms on $U$, we require a bound on the energy norm by some norm on $U$.
 
@@
 In this paper, we consider only isotropic refinements on quadrilateral elements, such that $h_1 = h_2 = h$, and $|K| = h^2$.
+Our test norm for an element $K$ is now
 \[
-\|\left(\tau, v\right)\|_{V}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\| + \| \div \tau\| + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|
+\|\left(\tau, v\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\| + \| \div \tau\| + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|
 \]
@@
 Intuitively, this is justifiable by the fact that best approximation error is typically largest near boundary layers, where refinements tend to aggregate.
-Additionally, test norms that differ from element to element fit cleanly into the DPG framework - as the best approximation error tends to be negligible in areas where the solution is smooth, the finite element error will be small in those areas, even with slightly suboptimal robustness.
+%Additionally, test norms that differ from element to element fit cleanly into the DPG framework - as the best approximation error tends to be negligible in areas where the solution is , the finite element error will be small in those areas, even with slightly suboptimal robustness.
 
@@
 
-For the choice of $\Omega = [0,1]^2$ and $\beta = (1,0)^T$, the convection diffusion equation reduces to
+For the choice of $\Omega = (0,1)^2$ and $\beta = (1,0)^T$, the convection diffusion equation reduces to
 \[
@@
 
-\begin{figure}[h]
+\begin{figure}[h!]
 \centering
@@
 \end{figure}
-
 In each case, we begin with a square 4 by 4 mesh of quadrilateral elements with order $p=3$.
@@
 \end{figure}
-
-We are especially interested in the ratio of energy error and $L^2$ error.
+We are especially interested in the ratio of energy error and total $L^2$ error in both $\sigma$ and $u$.
 Stability estimates imply that, using the above test norm, $\|u-u_h\|_{L^2} / \|u-u_h\|_E \sim C$ independent of $\epsilon$.
@@
 \end{figure}
-
-The effect of the test norm on mesh dependence can be seen in the ratios of $L^2$ to energy error; as the mesh is refined, the constants in front of the $L^2$ terms for $v$ and $\tau$ converge to stationary values, and the ratio of $L^2$ to energy error transitions from a smaller to a larger value.
+The effect of a mesh dependent test norm can be seen in the ratios of $L^2$ to energy error; as the mesh is refined, the constants in front of the $L^2$ terms for $v$ and $\tau$ converge to stationary values, and the ratio of $L^2$ to energy error transitions from a smaller to a larger value.
 The transition point happens later for smaller $\epsilon$, which we expect, since the transition of the ratio corresponds to the introduction of elements of order $\epsilon$ through mesh refinement.
@@
 Figure~\ref{ratios_noSigma} indicates that, between $\epsilon = .005$ and $\epsilon = .001$, the omission of $\sigma_n$ in the boundary condition becomes negligible, and both our error rates and ratios of $L^2$ to energy error become identical to the case where $\sigma_n$ is explicitly accounted for, well within the range of $\epsilon$ of physical interest.
-However, even for large $\epsilon = .01$, the $L^2$ error stagnates around $1e-3$, which is only $7%$ relative error.
+For large $\epsilon = .01$, the $L^2$ error stagnates around $1e-3$, or about $7\%$ relative error.
 
@@
 }
-\caption{$L^2$ and energy errors, and their ratio for $\epsilon=.01$, $\epsilon=.005$, $\epsilon=.001$, $\epsilon=.0001$}
+\caption{$L^2$ and energy errors and their ratio when neglecting $\sigma_n$ at the inflow.}
 \label{ratios_noSigma}
@@
 We note also that an additional advantage of selecting this new boundary condition is a relaxation of regularity requirements; as $\widehat{f}_n \in H^{-1/2}(\Omega)$, strictly discontinuous inflow boundary conditions are no longer ``variational crimes".
-We use the discontinuous inflow data
+We consider the discontinuous inflow condition
 \[
@@
 (y-1)^2&, \quad y>.5\\
-y^2&, \quad y\leq .5 
+-y^2&, \quad y\leq .5 
 \end{cases}
 \]
+as an example of a more difficult test case.
+
+\begin{figure}[h!]
+\centering
+\subfigure{
+\includegraphics[scale=.38]{figs/disc_hat.png}
+}
+\subfigure{
+\includegraphics[scale=.38]{figs/disc_hat_surf.png}
+}
+\caption{Solution variables $u$ and $\widehat{u}$ with discontinuous inflow data $u_0$ for $\epsilon = .01$.}
+\label{disc_sol}
+\end{figure}
+Figure~\ref{disc_sol} shows the solution $u$ and overlaid trace variable $\widehat{u}$, which both demonstrate the regularizing effect of viscosity on the discontinuous boundary condition at $x=0$.
+In order to compare with an exact solution, we approximate $u_0$ with 20 terms of a Fourier series, giving a near-discontinuity for $u_0$.
+
+\begin{figure}[h!]
+\centering
+\subfigure{
+\includegraphics[scale=.38]{figs/rates_disc.png}
+}
+\subfigure{
+\includegraphics[scale=.38]{figs/ratio_disc.png}
+}
+\caption{$L^2$ and energy errors, and their ratio for $\epsilon=.01$, $\epsilon=.001$, $\epsilon=.0001$, with discontinuous $u_0$ approximated by a Fourier expansion. }
+\label{disc_sol_fourier}
+\end{figure}
+The ratios of $L^2$ to energy error are now less predictable than for the previous example, due to the ``moving target" nature of the approximation of oscillatory boundary conditions.
+Even so, the ratios remain bounded and close to $1$ for $\epsilon$ varying over two orders of magnitude, as predicted by theory.
 
 \section{Conclusions}
+
 \bibliographystyle{plain}

### 2012-03-21 docs/NewBCRobustness_paper/paper.tex
committing paper changes, resolving conflict
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@382 36274a68-8941-4c93-80ef-affaed5139da

@@
 
-\subsection{Introduction to DPG}
+\subsection{Optimal test functions}
 The idea of optimal test functions was introduced by Demkowicz and Gopalakrishnan in \cite{DPG2}.
@@
 
-\section{Choice of test norm}
+\subsection{Choice of test norm}
 
@@
 
-\section{Model problem and robustness using DPG}
+\section{Model problem and robustness}
 
@@
 We approach this from a different perspective, looking instead for robust test norms which do not induce boundary layers in the approximation of optimal test functions.
+
+The estimates and proofs in this paper are largely based off of techniques and prior work done in \cite{DPGrobustness} and \cite{analysisDPG}; for further details, we encourage readers to consult these two publications as well.
 
@@
 
-\subsection{Main result}
+\subsection{Equivalence of energy and $U$ norms}
 
@@
 The upper bound on the energy norm appears to depend on $\epsilon^{-1}$, implying that, at most, we have the bound from below $\|u-u_h\|_{U} \geq \epsilon\|u-u_h\|_E$.
-However, numerical experiments demonstrate much better results, and suggest that, at least for our examples, $\|u-u_h\|_E \lesssim \|u-u_h\|_{U}$, implying that the induced energy norm is equivalent to the canonical norms we've chosen on our group variable $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)$.
+However, numerical experiments demonstrate much better results, and suggest that, at least for our examples, $\|u-u_h\|_E \lesssim \|u-u_h\|_{U}$, implying that the induced energy norm is equivalent to the canonical norms we've chosen on the group variable $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)$.
 
-\subsection{Stability of the adjoint problem (bound from below)}
+\subsubsection{Stability of the adjoint problem (bound from below)}
 
@@
 \]
-For the boundary terms, on $\Gamma_-$, $\grad v\cdot n = 0$, reducing the above to $\beta_n|\grad v|^2 \leq 0$.
+For the boundary terms, on $\Gamma_-$, $\grad v\cdot n = 0$, reducing the integrand over the boundary to $\beta_n|\grad v|^2 \leq 0$.
 On $\Gamma_+$, $v=0$ implies $\grad v \cdot \tau = 0$, where $\tau$ is a tangential direction.
@@
 \]
-On the other hand, using the decomposition and boundary conditions directly, we have
+On the other hand, using the decomposition and boundary conditions directly, we can integrate by parts to arrive at
 \begin{align*}
@@
 
-\subsection{Energy norm equivalence (bound from above)}
+\subsubsection{Energy norm equivalence (bound from above)}
 
-We've shown the robust bound of a norm on $U$ by energy error; for a full equivalence statement between the energy norm and norms on $U$, we require a bound on the energy norm by some norm on $U$.
+We've shown the robust bound of a norm on $U$ by energy error; for a full equivalence statement, we require a bound on the energy norm by some norm on $U$.
+We do so by taking advantage of the fact that the test norm can be recovered via duality
+\[
+\| \left(\tau,v\right) \|_V = \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E}
+\]
+The proof for this is identical to proving $\|u\|_E = \|u\|_U$ for the choice of the optimal test norm.
+
+In \cite{DPGrobustness}, the quasi-optimal test norm was shown to induce an energy norm that is equivalent from above and below with
 
@@
 \]
-This modified test norm avoids boundary layers, but for adaptive meshes, provides additional stability in areas of heavy refinement.
-Intuitively, this is justifiable by the fact that best approximation error is typically largest near boundary layers, where refinements tend to aggregate.
+This modified test norm avoids boundary layers, but for adaptive meshes, provides additional stability in areas of heavy refinement, where best approximation error tends to be large and stronger robustness is most needed.
+%Intuitively, this is justifiable by the fact that best approximation error is typically only large near where refinements tend to aggregate.
+
 %Additionally, test norms that differ from element to element fit cleanly into the DPG framework - as the best approximation error tends to be negligible in areas where the solution is , the finite element error will be small in those areas, even with slightly suboptimal robustness.
@@
 \[
-\pd{u}{x} - \epsilon \left(\pdd{u}{x}+ \pdd{u}{y}\right) = f
+\pd{u}{x} - \epsilon \left(\pdd{u}{x}+ \pdd{u}{y}\right) = 0
 \]
-which, for $f=0$, has an exact solution by separation of variables, allowing us to analyze convergence of DPG for a wide range of $\epsilon$.
+which has an exact solution by separation of variables, allowing us to analyze convergence of DPG for a wide range of $\epsilon$.
 For boundary conditions, we impose $u=0$ on $\Gamma_+$ and $\beta_n u - \sigma_n$ on $\Gamma_-$, which reduces to
@@
 
-\subsection{Solution with $C_1 = 1, C_n = 0, n\neq 1$}
+\subsubsection{Solution with $C_1 = 1, C_{n\neq 1} = 0$}
 
@@
 
-\subsection{Neglecting $\sigma_n$}
+\subsubsection{Neglecting $\sigma_n$}
 
@@
 
-\subsection{Discontinuous inflow data}
+\subsubsection{Discontinuous inflow data}
 
@@
 u_0(y) = \begin{cases}
-(y-1)^2&, \quad y>.5\\
--y^2&, \quad y\leq .5 
+(y-1)^2, \quad &y>.5\\
+-y^2, \quad &y\leq .5 
 \end{cases}
@@
 
+None yet.  Ideas:
+\begin{itemize}
+\item Explanation of choice of boundary condition and why it impacts stability
+\item Interpretation of weight as allowing diffusion to work on the boundary.  
+\item Note results have worked for Burgers, and expand on how they would apply to Navier-Stokes
+\end{itemize}
+
 \bibliographystyle{plain}

### 2012-03-21 docs/NewBCRobustness_paper/paper.tex
fixed paper so it compiles correctly now
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@383 36274a68-8941-4c93-80ef-affaed5139da

@@
 
-In \cite{DPGrobustness}, the quasi-optimal test norm was shown to induce an energy norm that is equivalent from above and below with
+In \cite{DPGrobustness}, the quasi-optimal test norm was shown to induce an energy norm that is bounded from both above and below by norms on $U$ that do not grow in magnitude with $\epsilon^{-1}$.
 

### 2012-03-23 docs/NewBCRobustness_paper/paper.tex
fixed some mistakes and begun adding last two (main) lemmas to paper.tex
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@386 36274a68-8941-4c93-80ef-affaed5139da

--- 2012-03-21 docs/NewBCRobustness_paper/paper.tex
@@
 \end{align*}
+Additionally, throughout the rest of this work, we denote norms on $u$ and $\sigma$ as
+\begin{align*}
+\|u\| &= \|u\|_{L^2} \\
+\|\sigma\| &= \|\sigma\|_{L^2}
+\end{align*}
 We will construct norms on $U$ as combinations of norms on each variable
 \[
-\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\|_U = C_1 \|u\|_{L^2} + C_2 \|\sigma\|_{L^2} + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = C_1 \|u\| + C_2 \|\sigma\| + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|
 \]
@@
 
+The proof proceeds in two parts; the bound from below is proven by providing stability estimates for the adjoint problem, while the bound from above of the energy norm is proven separately.
+
 \subsubsection{Stability of the adjoint problem (bound from below)}
@@
 with boundary conditions
-\begin{align*}
-\tau_n = - \epsilon \grad v \cdot n &=f\cdot n, \quad x\in \Gamma_-\\
-v &= 0, \quad x\in \Gamma_+ 
-\end{align*}
+\begin{align}
+\tau_n = - \epsilon \grad v \cdot n &=f\cdot n, \quad x\in \Gamma_- \label{bc_1}\\ 
+v &= 0, \quad x\in \Gamma_+ \label{bc_2}
+\end{align}
 and treat the cases $f=0$, $g=0$ separately.
@@
 \label{lemma_1}
-Assuming \eqref{a_req} and \eqref{adjoint} hold, for sufficiently small $\epsilon$, 
+Assume \eqref{a_req} and \eqref{adjoint} hold.  Then, for $v$ satisfying \eqref{bc_1}, \eqref{bc_2} and sufficiently small $\epsilon$, 
 \[
@@
 \label{lemma_2}
-Assume $v$ satisfies $\eqref{adjoint}$ and $\beta$ satisfies \eqref{a_req} and \eqref{b_req}.  If $\div f = 0$ and $\epsilon$ is sufficiently small, 
+Assume $v$ satisfies $\eqref{adjoint}$,\eqref{bc_1}, and \eqref{bc_2}, and $\beta$ satisfies \eqref{a_req} and \eqref{b_req}.  If $\div f = 0$ and $\epsilon$ is sufficiently small, 
 \[
@@
 &=\epsilon \langle [\tau \cdot n],\psi \rangle - \epsilon  \langle n\cdot \curl z, [v]\rangle = \epsilon \langle [\tau \cdot n],\psi \rangle_{\Gamma_h \setminus \Gamma_+} - \epsilon  \langle n\cdot \curl z, [v]\rangle_{\Gamma_h \cup \Gamma_+}\\
-&\lesssim \epsilon \|[\tau \cdot n]\|_{\Gamma_h \setminus \Gamma_+} \|\psi\| + \epsilon \| [v]\|_{\Gamma_h \cup \Gamma_+}\| n\cdot \curl z \| 
+&\lesssim \epsilon \|[\tau \cdot n]\| \|\psi\| + \epsilon \| [v]\|\| n\cdot \curl z \| 
 \end{align*}
-by the boundary norms for $v$ and $\tau$, which are defined by duality
+where the boundary norms for $v$ and $\tau$ are defined by duality
 \begin{align*}
-\|[\tau\cdot n]\|_{\Gamma_h} &\coloneqq \sup_{w\in H^1} \frac{\langle [\tau \cdot n], w\rangle}{\|w\|_{H^1(\Omega)}}\\
-\|[v]\|_{\Gamma_h} &\coloneqq \sup_{\eta\in H({\rm div})} \frac{\langle v, \eta\cdot n\rangle}{\|\eta\|_{H({\rm div},\Omega)}}
+\|[\tau\cdot n]\| &= \|[\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} \coloneqq \sup_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+} = 0} \frac{\langle [\tau \cdot n], w\rangle}{\|w\|_{H^1(\Omega)}}\\
+\|[v]\|&=\|[v]\|_{\Gamma_h^0 \cup \Gamma_+} \coloneqq \sup_{\eta\in H({\rm div};\Omega), \left.\eta\cdot n\right|_{\Gamma_- \cup \Gamma_0} = 0} \frac{\langle v, \eta\cdot n\rangle}{\|\eta\|_{H({\rm div},\Omega)}}
 \end{align*}
 Applying the above estimates for $\|\psi\|$ and $\|n\cdot \curl z\|$ and noting that $\|\grad v\| = \frac{1}{\epsilon}\|\tau\|$ completes the proof.
+\end{proof}
+
+With these three lemmas, we can prove the robust bound of both field variables and fluxes by the energy error.
+In doing so, we take advantage of the fact that, for any choice of energy norm, the test norm $\|v\|_V$ inducing it can be recovered via duality
+\begin{align}
+\| v \|_V = \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_E} \label{norm_duality}
+\end{align}
+%\[
+%\| \left(\tau,v\right) \|_V = \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E}
+%\]
+The proof for this is identical to proving $\|u\|_E = \|u\|_U$ for the choice of the optimal test norm.
+
+As a consequence of \eqref{norm_duality}, assume an energy norm $\left\| u \right\|_{E,1}$ is induced by a given test norm $\| v  \|_{V,1}$.
+To bound $\|\cdot\|_E$ robustly from above or below by a given norm $\left\| u \right\|_{U,2}$ on $U$ now only requires the robust bound in the opposite direction of $\| v \|_{V,1}$ by $\|v\|_{V,2}$.
+
+\begin{lemma}
+(Bound from below) If $\beta$ satisfies \eqref{a_req} and \eqref{b_req}, then for $\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U$,
+\[
+\|u\| + \|\sigma\| + \epsilon\|\widehat{u}\|+ \sqrt{\epsilon}\|\widehat{u}\| \lesssim \left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E
+\]
+\end{lemma}
+\begin{proof}
+By \eqref{norm_duality}, proving the above result is equivalent to showing 
+\begin{align*}
+\|\left(v,\tau\right)\|_V &\lesssim \frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\|u\| + \|\sigma\| + \epsilon\|\widehat{u}\|+ \sqrt{\epsilon}\|\widehat{u}\|}\\
+& \simeq \|g\| + \|f\| + \epsilon^{-1}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle [\tau\cdot n], \widehat{u}\rangle}{\|\widehat{u}\|} + \epsilon^{-1/2}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, [v]\rangle}{\|\widehat{f}\|},
+\end{align*}
+which, by definition of the boundary norms, is 
+\[
+\|\left(v,\tau\right)\|_V \lesssim \|g\| + \|f\| + \epsilon^{-1}\|[\tau\cdot n]\| + \epsilon^{-1/2}\|[v]\|
+\]
+We will bound each term by first decomposing $\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right)$, where $\left(v_1,\tau_1\right)$ satisfies our adjoint equation \eqref{adjoint} with $f = 0, g= \div \tau - \beta\cdot \grad v$, and $\left(v_2,\tau_2\right)$ satisfies \eqref{adjoint} with $g = 0, f= \epsilon^{-1}\tau + \grad v$.
+By construction, $\left(v_0,\tau_0\right)$ must satisfy \eqref{adjoint} with $f=g=0$, and with boundary conditions
+\begin{align*}
+[v_0] &= [v], \quad x\in \Gamma_h \cup \Gamma_+\\
+[\tau_0 \cdot n] &= [\tau \cdot n]-[\tau_2 \cdot n], \quad x\in \Gamma_h\setminus \Gamma_+\\
+\end{align*}
+\textcolor{red}{not done yet}
 \end{proof}
@@
 We've shown the robust bound of a norm on $U$ by energy error; for a full equivalence statement, we require a bound on the energy norm by some norm on $U$.  
-We do so by taking advantage of the fact that the test norm can be recovered via duality
-\[
-\| \left(\tau,v\right) \|_V = \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E}
-\]
-The proof for this is identical to proving $\|u\|_E = \|u\|_U$ for the choice of the optimal test norm.
+\begin{lemma}
+Bound from above \textcolor{red}{not done yet}
+\end{lemma}
+\begin{proof}
+\textcolor{red}{not done yet}
+\end{proof}
 
-In \cite{DPGrobustness}, the quasi-optimal test norm was shown to induce an energy norm that is equivalent from above and below with
+%In \cite{DPGrobustness}, the quasi-optimal test norm was shown to induce an energy norm that is bounded from both above and below by norms on $U$ that do not grow in magnitude with $\epsilon^{-1}$.
 

### 2012-03-23 docs/presentations/nate/Proposal/SIAMreport.tex
Updated Stokes write-up.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@387 36274a68-8941-4c93-80ef-affaed5139da

@@
 % BE SURE TO PREFACE LABEL WITH YOUR OWN INITIALS (NVR in this example) --
-\newcommand{\NVRvect}[1]{\ensuremath\boldsymbol{#1}}
-\newcommand{\NVRtensor}[1]{\underline{\NVRvect{#1}}}
-\newcommand{\NVRnorm}[1]{\left|\left|#1\right|\right|}
+\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
+\newcommand{\NVRtensor}[1]{\underline{\vect{#1}}}
+\newcommand{\norm}[1]{\left|\left|#1\right|\right|}
 \newcommand{\NVRgrad}{\nabla}
@@
 \addcontentsline{toc}{chapter}{Application of a Discontinuous Petrov-Galerkin Method to the Stokes Equations\\
-{\em N.V.\ Roberts, D.\ Ridzal, P.B.\ Bochev, L.D.\ Demkowicz}}
+{\em N.V.\ Roberts}}
 
@@
 % the author's names, as shown.
-\markboth{DPG Trilinos Toolbox}{N.~V.\ Roberts, D.\ Ridzal, P.~B.\ Bochev, L.~D.\ Demkowicz}
+\markboth{Nathan Roberts Thesis Proposal}{N.~V.\ Roberts}
 
 % Put your article title in here
-\title{A Toolbox for a Class of Discontinuous
-       Petrov-Galerkin Methods Using Trilinos\thanks{Also available as Sandia Report SAND2011-6678.
-                 Sandia National Laboratories is a multi-program laboratory
-                 managed and operated by Sandia Corporation, a wholly owned subsidiary of
-                 Lockheed Martin Corporation, for the U.S. Department of
-                 Energy's National Nuclear Security Administration under
-                 contract DE-AC04-94AL85000.}}
+\title{Applying Discontinuous Petrov-Galerkin Methods to Fluid Problems}
 
@@
 Research sponsored by The Center for Predictive Engineering and COmputational Sciences (PECOS).
-PECOS is a DOE-funded Center of Excellence within the Institute for Computational Engineering and Sciences (ICES) at The University of Texas at Austin.}
-\and
-Denis Ridzal\thanks{Optimization and Uncertainty Quantification, MS-1320,
-                 Sandia National Laboratories, P.O. Box 5800,
-                 Albuquerque, NM 87185-1320.  E-mail: dridzal@sandia.gov.
-                 Research sponsored by the Office of Science ASCR program.}
-\and
-Pavel B.\ Bochev\thanks{Numerical Analysis and Applications, MS-1320,
-                 Sandia National Laboratories, P.O. Box 5800,
-                 Albuquerque, NM 87185-1320.  E-mail: pbboche@sandia.gov.
-                 Research sponsored by the Office of Science ASCR program.}
-\and
-Leszek D.\ Demkowicz\thanks{The University of Texas at Austin,
-Institute for Computational Engineering and Science,
-201 E 24th St,
-Austin, TX 78712. E-mail: leszek@ices.utexas.edu.. Research sponsored by PECOS.}  }
+PECOS is a DOE-funded Center of Excellence within the Institute for Computational Engineering and Sciences (ICES) at The University of Texas at Austin.} }
 
@@
 \begin{abstract}
-The class of discontinuous Petrov-Galerkin finite element methods (DPG) proposed by L.
+%The class of discontinuous Petrov-Galerkin finite element methods (DPG) proposed by L.
 Demkowicz and J.
 Gopalakrishnan \cite{DPG1,DPG2} guarantees the optimality of the solution in an energy norm and produces a symmetric positive definite stiffness matrix, among other desirable properties.
-In this paper, we describe a toolbox, implemented atop Sandia's Trilinos Project \cite{Trilinos}, for rapid development of solvers for DPG methods.
-We use this toolbox to develop solvers for the Poisson and Stokes problems.
+In this paper, we describe Camellia, a toolbox for rapid development of solvers for DPG methods, implemented atop Sandia's Trilinos Project \cite{Trilinos}, and its application to several problems in fluid dynamics.
 \end{abstract}

### 2012-03-23 docs/presentations/nate/Proposal/paper.tex
Updated Stokes write-up.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@387 36274a68-8941-4c93-80ef-affaed5139da

@@
 \begin{align}
-- \mu \Delta \NVRvect{u} + \NVRgrad p &= \NVRvect{f} & \text{ in } \Omega, \label{NVR:eq:strongfirst1} \\
-\NVRdiv \NVRvect{u} &= 0 & \text{ in } \Omega, \\
-\NVRvect{u} &= \NVRvect{g_{D}} & \text{ on } \partial\Omega,\label{NVR:eq:stronglast1}
+- \mu \Delta \vect{u} + \NVRgrad p &= \vect{f} & \text{ in } \Omega, \label{NVR:eq:strongfirst1} \\
+\NVRdiv \vect{u} &= 0 & \text{ in } \Omega, \\
+\vect{u} &= \vect{g_{D}} & \text{ on } \partial\Omega,\label{NVR:eq:stronglast1}
 \end{align}
-where $\Omega \subset \mathbb{R}^{2}$, $\mu$ is viscosity, $\NVRtensor{\epsilon}=\NVRgrad^{\text{sym}} \NVRvect{u}$ is strain, $p$ is pressure, $u$ velocity, and $\NVRvect{f}$ a vector forcing function.
-
-For DPG, we require a first-order system.  We introduce $\NVRtensor{\sigma}=\mu \NVRgrad \NVRvect{u}$:
+where $\Omega \subset \mathbb{R}^{2}$, $\mu$ is viscosity, $p$ is pressure, $\vect{u}$ velocity, and $\vect{f}$ a vector forcing function.
+
+For DPG, we require a first-order system.  We introduce $\NVRtensor{\sigma}= \NVRgrad \vect{u}$:
 \begin{align}
-\frac{1}{\mu} \NVRtensor{\sigma} - \NVRgrad \NVRvect{u} &= 0 \\
-- \mu \NVRdiv \NVRtensor{\sigma} + \NVRgrad p &= \NVRvect{f} & \text{ in } \Omega, \label{NVR:eq:strongfirst2} \\
-\NVRdiv \NVRvect{u} &= 0 & \text{ in } \Omega, \\
-\NVRvect{u} &= \NVRvect{g_{D}} & \text{ on } \partial\Omega,\label{NVR:eq:stronglast2}
+- \mu \NVRdiv \NVRtensor{\sigma} + \NVRgrad p &= \vect{f} & \text{ in } \Omega, \label{NVR:eq:strongfirst2} \\
+\NVRdiv \vect{u} &= 0 & \text{ in } \Omega, \\
+\NVRtensor{\sigma} - \NVRgrad \vect{u} &= 0 & \text{ in } \Omega,\\
+\vect{u} &= \vect{g_{D}} & \text{ on } \partial\Omega.\label{NVR:eq:stronglast2}
 \end{align}
+
+Considering the above as a linear operator $A$ operating on a group variable $\tilde{u} = (\vect{u},p,\NVRtensor{\sigma})$, to apply the abstract theory presented above we need to establish that $A$ and $A^{*}$ are injective, and either that $||A \tilde{u}|| \geq \gamma ||\tilde{u}||$ or that $||A^{*} \tilde{v}|| \geq \gamma ||\tilde{v}||$.
+Since the latter two conditions imply the injectivity of the respective operators, it will suffice to prove these.\\
+
+\subsection{$||A \tilde{u}|| \geq \gamma ||\tilde{u}||$}
+Adding right-hand sides $g$ and $\NVRtensor{h}$
+
+\begin{align}
+- \mu \NVRdiv \NVRtensor{\sigma} + \NVRgrad p &= \vect{f} & \text{ in } \Omega, \label{NVR:eq:strongfirst3} \\
+\NVRdiv \vect{u} &= g & \text{ in } \Omega, \\
+\NVRtensor{\sigma} - \NVRgrad \vect{u} &= \NVRtensor{h} & \text{ in } \Omega, \label{NVR:eq:strongsecondtolast3} \\
+\vect{u} &= \vect{g_{D}} & \text{ on } \partial\Omega,\label{NVR:eq:stronglast3}
+\end{align}
+we have that $A \tilde{u} = (\vect{f},g,\NVRtensor{h})$.
+If we can establish bounds for each of the solution variables in terms of norms on $\vect{f},g,$ and $\NVRtensor{h}$, then we will have the required lower bound $|| A \tilde{u} || \geq \gamma || \tilde{u} ||$.
+For the time being we assume that $\vect{g_{D}} = 0$.\\
+
+Note that, by linearity of $A$, it suffices to consider cases in which only one of $\vect{f},g,$ and $\NVRtensor{h}$ is non-zero.\\
+
+\subsubsection{$\vect{f} \neq \vect{0}$}
+In this case, we have exactly the system (\ref{NVR:eq:strongfirst2})-(\ref{NVR:eq:stronglast2}), which reduces (in a distributional sense) to (\ref{NVR:eq:strongfirst1})-(\ref{NVR:eq:stronglast1}).
+Testing the first equation with the velocity $u \in H^{1}_{0}(\Omega)$, we have
+\begin{align*}
+- (\mu \Delta \vect{u}, \vect{u})_{\Omega} + (\NVRgrad p, \vect{u})_{\Omega} &= (\vect{f},\vect{u})_{\Omega}.\\
+\end{align*}
+Integrating by parts, we obtain:
+\begin{align*}
+(\mu \NVRgrad \vect{u}, \NVRgrad \vect{u})_{\Omega} - \langle \NVRgrad \vect{u} \cdot \vect{n}, \vect{u} \rangle_{\partial \Omega} - (p, \NVRdiv u)_{\Omega} + \langle p, \vect{u} \cdot \vect{n} \rangle_{\partial \Omega} &= (\vect{f},\vect{u})_{\Omega}.
+\end{align*}
+
+Noting that $\vect{u} = 0$ on $\partial \Omega$ and that $\NVRdiv \vect{u} = 0 $ in $\Omega$, this reduces to:
+
+\begin{align*}
+\mu (\NVRgrad \vect{u}, \NVRgrad \vect{u})_{\Omega} = ||\NVRgrad \vect{u}||^{2}_{\Omega} = || \NVRtensor{ \sigma }||^{2}_{\Omega} &= (\vect{f},\vect{u})_{\Omega} \\
+&\leq || f ||_{\Omega} || \vect{u} ||_{\Omega}\\
+&\leq C_{P} || f ||_{\Omega} || \NVRgrad \vect{u} ||_{\Omega},
+\end{align*}
+where $C_{P}$ is the Poincare constant.  Thus $ || \NVRtensor{ \sigma }||_{\Omega} \leq \frac{C_{P}}{\mu} || f ||_{\Omega}$, and $|| \vect{u} || \leq \frac{C_{P}^{2}}{\mu} || f ||_{\Omega}$.
+
+To bound the pressure $p$, we require a result by Ladyzhenskaya for $p \in L^{2}_{0}$:
+\begin{align*}
+\sup_{\vect{v} \in H^{1}(\Omega)} \frac{(p, \NVRdiv \vect{v})_{\Omega}}{\norm{ \vect{v} }_{H^{1}(\Omega)} } \geq \beta \norm{p}_{\Omega}
+\end{align*}
+for some constant $\beta > 0$.  Testing equation (\ref{NVR:eq:strongfirst1}) with $\vect{v} \in \vect{H}^{1}_{0}(\Omega)$, we have
+\begin{align*}
+\NVRgrad p \cdot \vect{v} = \vect{f} \cdot \vect{v} + \mu \Delta \vect{u} \cdot \vect{v}.
+\end{align*}
+
+Integrating by parts, dividing by $\norm{ \vect{v} }_{H^{1}(\Omega)}$ and taking the supremum:
+\begin{align*}
+\sup - \frac{(p, \NVRdiv \vect{v})}{\norm{ \vect{v} }_{H^{1}(\Omega)}} &= \sup \left\{\frac{(\vect{f}, \vect{v})}{\norm{ \vect{v} }_{H^{1}(\Omega)}} - \frac{\mu (\NVRgrad \vect{u}, \NVRgrad \vect{v})}{\norm{ \vect{v} }_{H^{1}(\Omega)}}\right\} \\
+&\leq \frac{\norm{\vect{f}} \norm{\vect{v}}_{L^{2}}}{\norm{ \vect{v} }_{H^{1}(\Omega)}} + \mu \norm{\NVRgrad \vect{u}} \leq \norm{\vect{f} } + \mu \frac{C_{P}}{\mu} \norm{\vect{f}} = (1 + C_{P}) \norm{\vect{f}}.
+\end{align*}
+By the Ladyzhenskaya result, we then have $\norm{p} \leq \frac{1 + C_{P}}{\beta} \norm{\vect{f}}$, bounding $p$, as required.
+
+\subsubsection{$ g \neq 0$} In this case, we have
+\begin{align}
+- \mu \NVRdiv \NVRtensor{\sigma} + \NVRgrad p &= \vect{0} & \text{ in } \Omega, \label{NVR:eq:gstrongfirst} \\
+\NVRdiv \vect{u} &= g & \text{ in } \Omega, \\
+\NVRtensor{\sigma} - \NVRgrad \vect{u} &= 0 & \text{ in } \Omega,\\
+\vect{u} &= \vect{0} & \text{ on } \partial\Omega.\label{NVR:eq:gstronglast}
+\end{align}
+
+We must also assume compatibility between $g$ and the boundary condition on $\vect{u}$; that is, that $g$ has zero average on $\Omega$:
+\begin{align*}
+\int_{\Omega} g = \int_{\partial \Omega} \vect{u} \cdot \vect{n} = 0.
+\end{align*}
+
+Now, by surjectivity of $\NVRdiv$, 
+\begin{align*}
+\forall g \in L^{2} \quad \exists \vect{u}_{0} : \NVRdiv \vect{u}_{0} = g.
+\end{align*}
+
+By the Lax-Milgram theorem, we have $\exists !
+\phi \in H^{1}_{0} : \vect{u}_{0} = \NVRgrad \phi$, so that $\Delta \phi = g$ and, assuming that $\Omega$ is convex, then by the Elliptic Regularity theorem (see \cite[p.
+214]{Folland} for a proof), $\phi \in H^{2}$ and:
+\begin{align*}
+\norm{\phi}_{H^{2}} &\leq C \norm{g}\\ % SEE ARBOGAST/BONA, p. 223 (Elliptic Regularity, section 8.5.4, Theorem 8.13)---references [GT] or [Fo] for a proof
+\norm{\NVRgrad \phi}_{H^{1}} &\leq C \norm{g},
+\end{align*}
+for some $C > 0$ independent of $g$ and $\phi$.  That is, in fact $\vect{u}_{0} \in H^{1}$ and $\norm{ \vect{u}_{0} }_{H^{1}} \leq C \norm{g}$. \\
+
+Now, setting $\vect{w} = \vect{u} - \vect{u}_{0}$, we have $\NVRdiv \vect{w} = 0$.  Testing equation (\ref{NVR:eq:strongfirst1}) with $\vect{w}$ and integrating by parts, we obtain:
+\begin{align*}
+\mu (\NVRgrad \vect{u},\NVRgrad \vect{w})_{\Omega} &= 0\\
+\mu (\NVRgrad \vect{w} + \NVRgrad \vect{u}_{0},\NVRgrad \vect{w})_{\Omega} &= 0\\
+\implies \mu \norm{\NVRgrad \vect{w}}^{2} &= -(\NVRgrad \vect{u}_{0}, \NVRgrad \vect{w}) \\
+&\leq \norm{ \NVRgrad \vect{u}_{0} } \norm{ \NVRgrad \vect{w} } \\
+&\leq C \norm{g} \norm{ \NVRgrad \vect{w} },
+\end{align*}
+so that $\norm{ \NVRgrad \vect{w} } \leq  \frac{C}{\mu} \norm{ g }$, and therefore as before we obtain a bound on $\norm{\NVRtensor{\sigma}} = \norm{\NVRgrad \vect{u}} \leq \left( 1 + \frac{1}{\mu} \right) C \norm{g}$, and again by means of the Poincare inequality we may bound $\norm{\vect{u}} \leq C_{P} \norm{\NVRgrad \vect{u}} \leq \frac{C C_{P}}{\mu} \norm{ g }$ as well.\\
+
+The bound on $p$ is established exactly as before, except that now $\vect{f} = \vect{0}$, so that we obtain the bound $\norm{p} \leq \frac{\mu}{\beta} \norm{\NVRgrad \vect{u}}$.
+
+\subsubsection{$ \NVRtensor{h} \neq \NVRtensor{0}$}  In this case, we have
+\begin{align}
+- \mu \NVRdiv \NVRtensor{\sigma} + \NVRgrad p &= \vect{0} & \text{ in } \Omega, \label{NVR:eq:hstrongfirst} \\
+\NVRdiv \vect{u} &= 0 & \text{ in } \Omega, \\
+\NVRtensor{\sigma} - \NVRgrad \vect{u} &= \NVRtensor{h} & \text{ in } \Omega, \\
+\vect{u} &= \vect{0} & \text{ on } \partial\Omega.\label{NVR:eq:hstronglast}
+\end{align}
+
+Then, $\NVRtensor{\sigma} = \NVRgrad \vect{u} + \NVRtensor{h}$, and we have:
+\begin{align*}
+- \mu \NVRdiv \NVRtensor{\sigma} + \NVRgrad p &= - \mu \Delta \vect{u} - \mu \NVRdiv \NVRtensor{h} + \NVRgrad p = \vect{0} \\
+- \mu \Delta \vect{u} + \NVRgrad p &= - \mu  \NVRdiv \NVRtensor{h}
+\end{align*}
+
+in a distributional sense.  Testing with $\vect{u}$, and integrating by parts, again the pressure term vanishes because $\NVRdiv \vect{u} = 0$, so that much as before, we obtain:
+
+\begin{align*}
+\mu (\NVRgrad \vect{u}, \NVRgrad \vect{u})_{\Omega} &= \langle \NVRdiv \NVRtensor{h}, \vect{u} \rangle_{\partial \Omega}\\
+&= -(\NVRtensor{h}, \NVRgrad \vect{u})_{\Omega} \leq \norm{\NVRtensor{h}}_{L^{2}(\Omega)} \norm{ \NVRgrad \vect{u} }_{L^{2}(\Omega)}.
+\end{align*}
+
+So $\norm{\NVRgrad \vect{u}} \leq \frac{1}{\mu} \norm{\NVRtensor{h}}$, and the bounds $\norm{\vect{u} } \leq \frac{C_{P}}{\mu} \norm{\NVRtensor{h}}$ and $\norm{p} \leq \frac{\mu}{\beta}\left( \norm{ \NVRgrad \vect{u} } + \norm{\NVRtensor{h}} \right)$ can be established in a similar fashion as above.
+
+%% ADJOINT %%
+\subsection{$||A^{*} \tilde{v}|| \geq \gamma ||\tilde{v}||$}  If we consider $(A \tilde{u}, \tilde{v})$, where $\tilde{v} = (\NVRtensor{\tau},\vect{q}, v)$, and integrate by parts (ignoring boundary terms for now), we can readily see that the adjoint equation $A^{*} \tilde{v} = \vect{F}$ takes the form:
+\begin{align}
+\NVRdiv \NVRtensor{\tau} - \NVRgrad v &= \vect{f^{*}} & \text{ in } \Omega, \\
+- \NVRdiv \vect{q} &= g^{*} & \text{ in } \Omega, \\
+\NVRtensor{\tau} + \mu \NVRgrad \vect{q} &= \NVRtensor{h^{*}} & \text{ in } \Omega.
+\end{align}
+
+If we then substitute $\NVRtensor{\tau} = - \mu \NVRtensor{\sigma}$ and $v = -p$, we have:
+\begin{align}
+- \mu \NVRdiv \NVRtensor{\sigma} + \NVRgrad p &= \vect{f}^{*} & \text{ in } \Omega, \\
+\NVRdiv \vect{q} &= -g^{*} & \text{ in } \Omega, \\
+\NVRtensor{\sigma} - \NVRgrad \vect{q} &= - \frac{1}{\mu} \NVRtensor{h}^{*} & \text{ in } \Omega,
+\end{align}
+
+so that the adjoint $A^{*}$ takes exactly the same form as the original operator $A$ (compare equations (\ref{NVR:eq:strongfirst3}) - (\ref{NVR:eq:strongsecondtolast3})).
+Thus our argument for $||A \tilde{u}|| \geq \gamma ||\tilde{u}||$ will also work to show that $||A^{*} \tilde{v}|| \geq \gamma ||\tilde{v}||$.
 
@@
 \begin{align}
-|b(u,v)| \leq M \NVRnorm{u}_{U} \NVRnorm{v}_{V},
+|b(u,v)| \leq M \norm{u}_{U} \norm{v}_{V},
 \end{align}
@@
 \begin{align}
-\inf_{\NVRnorm{u}_{U}=1} \sup_{\NVRnorm{v}_{V}=1} b(u,v) > \gamma,
+\inf_{\norm{u}_{U}=1} \sup_{\norm{v}_{V}=1} b(u,v) > \gamma,
 \end{align}
@@
 \begin{equation}\label{NVR:eq:energyNorm}
-\NVRnorm{u}_{E} \NVReqdef \sup_{\NVRnorm{v}_{V}=1} b(u,v).
+\norm{u}_{E} \NVReqdef \sup_{\norm{v}_{V}=1} b(u,v).
 \end{equation}
@@
 \begin{equation}
-\gamma \NVRnorm{u}_{U} \leq \NVRnorm{u}_{E} \leq M \NVRnorm{u}_{U} \quad \forall u \in U.
+\gamma \norm{u}_{U} \leq \norm{u}_{E} \leq M \norm{u}_{U} \quad \forall u \in U.
 \end{equation}
@@
 \begin{align*}
-\NVRnorm{u}_{E} = \sup_{\NVRnorm{v}_{V}=1} b(u,v) = \sup_{\NVRnorm{v}_{V}=1} (Tu,v)_{V} = \frac{1}{\NVRnorm{Tu}_{V}} (Tu, Tu)_{V} = \NVRnorm{Tu}_{V}.
+\norm{u}_{E} = \sup_{\norm{v}_{V}=1} b(u,v) = \sup_{\norm{v}_{V}=1} (Tu,v)_{V} = \frac{1}{\norm{Tu}_{V}} (Tu, Tu)_{V} = \norm{Tu}_{V}.
 \end{align*}
@@
 \begin{align}
-\NVRnorm{u-u_{n}}_{E} = \inf_{w_{n} \in U_{n}} \NVRnorm{u-w_{n}}_{E},\label{NVR:eq:optimalityEqn}
+\norm{u-u_{n}}_{E} = \inf_{w_{n} \in U_{n}} \norm{u-w_{n}}_{E},\label{NVR:eq:optimalityEqn}
 \end{align}
@@
 Therefore, a mathematically natural choice for a norm on the test space will be the Euclidean combination of these norms.
-In the case of our Poisson formulation, $\NVRvect{q} \in \NVRHdiv$ and $v \in \NVRHgrad$, so define
-\begin{align*}
-\NVRnorm{(\NVRvect{q},v)}_{V}^{2}  \NVReqdef \int_{\Omega} &\left((\NVRdiv \NVRvect{q})^{2} + \NVRvect{q} \cdot \NVRvect{q} + \NVRgrad v \cdot \NVRgrad v + v^{2}\right)\\
+In the case of our Poisson formulation, $\vect{q} \in \NVRHdiv$ and $v \in \NVRHgrad$, so define
+\begin{align*}
+\norm{(\vect{q},v)}_{V}^{2}  \NVReqdef \int_{\Omega} &\left((\NVRdiv \vect{q})^{2} + \vect{q} \cdot \vect{q} + \NVRgrad v \cdot \NVRgrad v + v^{2}\right)\\
 \end{align*}
@@
 \begin{align*}
-\NVRnorm{v}_{V}\NVReqdef \sup_{\NVRnorm{u}_{U}=1} b(u,v),
-\end{align*}
-where $\NVRnorm{\cdot}_{U}$ is the norm of interest.
-$\NVRnorm{\cdot}_{V}$ is then called the \emph{optimal test norm}.
+\norm{v}_{V}\NVReqdef \sup_{\norm{u}_{U}=1} b(u,v),
+\end{align*}
+where $\norm{\cdot}_{U}$ is the norm of interest.
+$\norm{\cdot}_{V}$ is then called the \emph{optimal test norm}.
 To determine the optimal test norm, we can collect terms by trial space variable, and then take the supremum using the Cauchy-Schwarz inequality.
@@
 \begin{align}
-- 2 \mu \NVRdiv \NVRtensor{\epsilon} + \NVRgrad p &= \NVRvect{f} & \text{ in } \Omega, \label{NVR:eq:strongfirst} \\
-\NVRdiv \NVRvect{u} &= 0 & \text{ in } \Omega, \\
-\NVRvect{u} &= \NVRvect{g_{D}} & \text{ on } \partial\Omega,\label{NVR:eq:stronglast}
+- 2 \mu \NVRdiv \NVRtensor{\epsilon} + \NVRgrad p &= \vect{f} & \text{ in } \Omega, \label{NVR:eq:strongfirst} \\
+\NVRdiv \vect{u} &= 0 & \text{ in } \Omega, \\
+\vect{u} &= \vect{g_{D}} & \text{ on } \partial\Omega,\label{NVR:eq:stronglast}
 \end{align}
-where $\Omega \subset \mathbb{R}^{2}$, $\mu$ is viscosity, $\NVRtensor{\epsilon}=\NVRgrad^{\text{sym}} \NVRvect{u}$ is strain, $p$ is pressure, $u$ velocity, and $\NVRvect{f}$ a vector forcing function.
+where $\Omega \subset \mathbb{R}^{2}$, $\mu$ is viscosity, $\NVRtensor{\epsilon}=\NVRgrad^{\text{sym}} \vect{u}$ is strain, $p$ is pressure, $u$ velocity, and $\vect{f}$ a vector forcing function.
 
@@
 \NVRtensor{\sigma} &= 2 \mu \NVRtensor{\epsilon} - p\NVRtensor{I}\\
-\NVRtensor{\omega} &= \frac{1}{2}(\NVRgrad \NVRvect{u} - \NVRgrad \NVRvect{u}^{T})
-\end{align*}
-so that equation \eqref{NVR:eq:strongfirst} becomes simply $-\NVRdiv \NVRtensor{\sigma} = \NVRvect{f}$.
+\NVRtensor{\omega} &= \frac{1}{2}(\NVRgrad \vect{u} - \NVRgrad \vect{u}^{T})
+\end{align*}
+so that equation \eqref{NVR:eq:strongfirst} becomes simply $-\NVRdiv \NVRtensor{\sigma} = \vect{f}$.
 We also have
@@
 \end{align*}
-Since $\NVRtensor{\epsilon} = \NVRgrad^{\text{sym}} \NVRvect{u} = \NVRgrad \NVRvect{u} - \NVRtensor{\omega}$, the entire system is
-
-\begin{align*}
-\frac{1}{2 \mu}(\NVRtensor{\sigma} + p\NVRtensor{I}) - \NVRgrad \NVRvect{u} + \NVRtensor{\omega} &= \NVRtensor{0}  & \text{ in } \Omega, \\
-- \NVRdiv \NVRtensor{\sigma} &= \NVRvect{f} & \text{ in } \Omega, \\
-\NVRdiv \NVRvect{u} &= 0 & \text{ in } \Omega, \\
-\NVRvect{u} &= \NVRvect{g_{D}} & \text{ on } \partial\Omega.
+Since $\NVRtensor{\epsilon} = \NVRgrad^{\text{sym}} \vect{u} = \NVRgrad \vect{u} - \NVRtensor{\omega}$, the entire system is
+
+\begin{align*}
+\frac{1}{2 \mu}(\NVRtensor{\sigma} + p\NVRtensor{I}) - \NVRgrad \vect{u} + \NVRtensor{\omega} &= \NVRtensor{0}  & \text{ in } \Omega, \\
+- \NVRdiv \NVRtensor{\sigma} &= \vect{f} & \text{ in } \Omega, \\
+\NVRdiv \vect{u} &= 0 & \text{ in } \Omega, \\
+\vect{u} &= \vect{g_{D}} & \text{ on } \partial\Omega.
 \end{align*}
@@
 \begin{align*}
-\frac{1}{2 \mu}{\sigma_{11} + p \choose \sigma_{21}} - \NVRgrad u_{1} + {0 \choose \omega} &= \NVRvect{0} & \text{ in } \Omega, \\
-\frac{1}{2 \mu}{\sigma_{12} \choose \sigma_{22} + p} - \NVRgrad u_{2} - {\omega \choose 0} &= \NVRvect{0}  & \text{ in } \Omega, \\
+\frac{1}{2 \mu}{\sigma_{11} + p \choose \sigma_{21}} - \NVRgrad u_{1} + {0 \choose \omega} &= \vect{0} & \text{ in } \Omega, \\
+\frac{1}{2 \mu}{\sigma_{12} \choose \sigma_{22} + p} - \NVRgrad u_{2} - {\omega \choose 0} &= \vect{0}  & \text{ in } \Omega, \\
 -\NVRdiv {\sigma_{11} \choose \sigma_{21}} &= f_{1} & \text{ in } \Omega, \\
 -\NVRdiv {\sigma_{12} \choose \sigma_{22}} &= f_{2} & \text{ in } \Omega, \\
-\NVRdiv \NVRvect{u} &= 0 & \text{ in } \Omega, \\\
-\NVRvect{u} &= \NVRvect{g_{D}} & \text{ on } \partial\Omega.
-\end{align*}
-Multiplying the first two equations by vector test functions $\NVRvect{q}_{i}$ and the following three by scalar test functions $v_{i}$, and integrating by parts over an element $K$, we obtain
-
-\begin{align*}
-\int_{K} \left(\frac{1}{2 \mu}{\sigma_{11} + p \choose \sigma_{21}} + {0 \choose \omega} \right) \cdot \NVRvect{q}_{1} &+ \int_{K} u_{1} \NVRdiv \NVRvect{q_{1}} &-& \int_{\partial K} \widehat{u}_{1} \NVRvect{q_{1}} \cdot n &&=\NVRvect{0} \\
-\int_{K} \left(\frac{1}{2 \mu}{\sigma_{12} \choose \sigma_{22} + p} - {\omega \choose 0}\right) \cdot \NVRvect{q}_{2} &+ \int_{K} u_{2} \NVRdiv \NVRvect{q_{2}} &-& \int_{\partial K} \widehat{u}_{2} \NVRvect{q_{2}} \cdot n &&= \NVRvect{0}\\
-\int_{K}  {\sigma_{11} \choose \sigma_{21}} \cdot \NVRgrad v_{1} &&-& \int_{\partial K} \widehat{\NVRvect{\sigma}}_{1n} v_{1} &&= \int_{K} f_{1} v_{1} \\
-\int_{K} {\sigma_{12} \choose \sigma_{22}} \cdot \NVRgrad v_{2} &&-& \int_{\partial K} \widehat{\NVRvect{\sigma}}_{2n} v_{2}  &&= \int_{K} f_{2} v_{2} \\
--\int_{K} \NVRvect{u} \cdot \NVRgrad v_{3} &&+& \int_{\partial K} \widehat{\NVRvect{u}} v_{3} \cdot n &&= 0,
+\NVRdiv \vect{u} &= 0 & \text{ in } \Omega, \\\
+\vect{u} &= \vect{g_{D}} & \text{ on } \partial\Omega.
+\end{align*}
+Multiplying the first two equations by vector test functions $\vect{q}_{i}$ and the following three by scalar test functions $v_{i}$, and integrating by parts over an element $K$, we obtain
+
+\begin{align*}
+\int_{K} \left(\frac{1}{2 \mu}{\sigma_{11} + p \choose \sigma_{21}} + {0 \choose \omega} \right) \cdot \vect{q}_{1} &+ \int_{K} u_{1} \NVRdiv \vect{q_{1}} &-& \int_{\partial K} \widehat{u}_{1} \vect{q_{1}} \cdot n &&=\vect{0} \\
+\int_{K} \left(\frac{1}{2 \mu}{\sigma_{12} \choose \sigma_{22} + p} - {\omega \choose 0}\right) \cdot \vect{q}_{2} &+ \int_{K} u_{2} \NVRdiv \vect{q_{2}} &-& \int_{\partial K} \widehat{u}_{2} \vect{q_{2}} \cdot n &&= \vect{0}\\
+\int_{K}  {\sigma_{11} \choose \sigma_{21}} \cdot \NVRgrad v_{1} &&-& \int_{\partial K} \widehat{\vect{\sigma}}_{1n} v_{1} &&= \int_{K} f_{1} v_{1} \\
+\int_{K} {\sigma_{12} \choose \sigma_{22}} \cdot \NVRgrad v_{2} &&-& \int_{\partial K} \widehat{\vect{\sigma}}_{2n} v_{2}  &&= \int_{K} f_{2} v_{2} \\
+-\int_{K} \vect{u} \cdot \NVRgrad v_{3} &&+& \int_{\partial K} \widehat{\vect{u}} v_{3} \cdot n &&= 0,
 \end{align*}
@@
 
-Conceptually, this requires nothing more than the Poisson formulation we described above --- in particular, the test functions $\NVRvect{q}_{i} \in \NVRHdiv$ and $v_{i} \in \NVRHgrad$, so we do not require any test spaces or operators different than discussed above.
+Conceptually, this requires nothing more than the Poisson formulation we described above --- in particular, the test functions $\vect{q}_{i} \in \NVRHdiv$ and $v_{i} \in \NVRHgrad$, so we do not require any test spaces or operators different than discussed above.
 An implementation of this bilinear form can be found in \verb=StokesBilinearForm=.
@@
 \begin{align*}
-\NVRcurl \omega + \NVRgrad P &= \NVRvect{f}\\
-\omega - \NVRcurl \NVRvect{u} &= 0\\
-\NVRdiv \NVRvect{u} &= 0.
+\NVRcurl \omega + \NVRgrad P &= \vect{f}\\
+\omega - \NVRcurl \vect{u} &= 0\\
+\NVRdiv \vect{u} &= 0.
 \end{align*}
@@
 \begin{align*}
-\int_{\partial K} \widehat{\omega} \NVRvect{q} \cdot {n_{2} \choose -n_{1}} + \int_{\partial K} \widehat{P} q_{n} -  \int_{K}\omega \NVRcurl \NVRvect{q} -  \int_{K} P \NVRdiv \NVRvect{q} &= \int_{K} \NVRvect{f} \cdot \NVRvect{q}\\
-\int_{\partial K} \widehat{u}_{\times \NVRvect{n}}v_{1} -  \int_{K}\NVRvect{u} \cdot (\NVRcurl v_{1}) +  \int_{K} \omega v_{1} &= 0\\
-\int_{\partial K} \widehat{u}_{\NVRvect{n}} v_{2} -  \int_{K}\NVRvect{u} \cdot (\NVRgrad v_{2}) &= 0 \,.
+\int_{\partial K} \widehat{\omega} \vect{q} \cdot {n_{2} \choose -n_{1}} + \int_{\partial K} \widehat{P} q_{n} -  \int_{K}\omega \NVRcurl \vect{q} -  \int_{K} P \NVRdiv \vect{q} &= \int_{K} \vect{f} \cdot \vect{q}\\
+\int_{\partial K} \widehat{u}_{\times \vect{n}}v_{1} -  \int_{K}\vect{u} \cdot (\NVRcurl v_{1}) +  \int_{K} \omega v_{1} &= 0\\
+\int_{\partial K} \widehat{u}_{\vect{n}} v_{2} -  \int_{K}\vect{u} \cdot (\NVRgrad v_{2}) &= 0 \,.
 \end{align*}
@@
 However, there are a few new operators and spaces required.
-While $v_{i} \in \NVRHgrad$ as before, now we require $\NVRvect{q} \in \NVRHdiv$ \emph{and} $\NVRvect{q} \in \NVRHcurl$.
-We can support this by requiring $\NVRvect{q} \in \NVRHgrad \times \NVRHgrad$.
-In the code, we define the function space for $\NVRvect{q}$ as \verb=FUNCTION_SPACE_VECTOR_HGRAD=.
+While $v_{i} \in \NVRHgrad$ as before, now we require $\vect{q} \in \NVRHdiv$ \emph{and} $\vect{q} \in \NVRHcurl$.
+We can support this by requiring $\vect{q} \in \NVRHgrad \times \NVRHgrad$.
+In the code, we define the function space for $\vect{q}$ as \verb=FUNCTION_SPACE_VECTOR_HGRAD=.
 The curl operator is given by \verb=OPERATOR_CURL=, and the \[ \displaystyle \cdot {n_{2} \choose -n_{1}}=\times n\] operator is given by \verb=OPERATOR_CROSS_N=.

### 2012-03-26 docs/NewBCRobustness_paper/paper.tex
committing first draft of paper (minus conclusion)
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@393 36274a68-8941-4c93-80ef-affaed5139da

@@
 
+\author{Tan Bui \and Jesse Chan \and Leszek Demkowicz \and Norbert Heuer}
+\title{Robust DPG stability II}
+\date{}
 \begin{document}
 
-\tableofcontents
+%\tableofcontents
+\maketitle
 
@@
 where the above inner products are taken element-wise over the finite element mesh $\Omega_h$, and the duality pairings are taken on $\Gamma_h$, the mesh ``skeleton", or union of edges of elements $K$ in $\Omega_h$.
+The divergence and gradient operators are likewise understood to be taken element-wise.
+
 Define the interior skeleton $\Gamma_h^0 = \Gamma_h \setminus \Gamma$.
@@
 It may be of interest to note that, for sufficiently small $\epsilon$, these issues manifest themselves in numerical experiments as additional refinements near the inflow.
+The presence of the new boundary condition relaxes the outflow boundary condition for the adjoint/dual problem, resulting in stronger stability for the primal problem.
 
@@
 \[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = C_1 \|u\| + C_2 \|\sigma\| + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = C_1 \|u\| + C_2 \|\sigma\| + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|.
 \]
@@
 \[
-\|\left(\tau, v\right)\|_{V}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\| + \| \div \tau\| + \frac{1}{\epsilon}\|\tau\|
+\|\left(\tau, v\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2
 \]
@@
 \[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U_2}^2 \coloneqq \|u\|^2 + \frac{1}{\epsilon^2}\|\sigma\|^2 + \frac{1}{\epsilon}\|\widehat{u}\|^2+\frac{1}{\epsilon} \|\widehat{f}_n\|^2.
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U_2} \coloneqq \|u\| + \frac{1}{\sqrt{\epsilon}}\left(\|\sigma\|^2 + \|\widehat{u}\|^2+ \|\widehat{f}_n\|^2\right).
 \]
@@
 \begin{align}
-\tau_n = - \epsilon \grad v \cdot n &=f\cdot n, \quad x\in \Gamma_- \label{bc_1}\\ 
+%\tau \cdot n = 
+- \epsilon \grad v \cdot n &=f\cdot n, \quad x\in \Gamma_- \label{bc_1}\\ 
 v &= 0, \quad x\in \Gamma_+ \label{bc_2}
@@
 
+We will denote $\|\cdot \| = \|\cdot\|_{L^2}$ for all functions defined on $\Omega$.  The boundary norms on $\Gamma_h$ for $v$ and $\tau$ are defined by duality from the bilinear form
+\begin{align*}
+\|[\tau\cdot n]\| &= \|[\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} \coloneqq \sup_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+} = 0} \frac{\langle [\tau \cdot n], w\rangle}{\|w\|_{H^1(\Omega)}}\\
+\|[v]\|&=\|[v]\|_{\Gamma_h^0 \cup \Gamma_+} \coloneqq \sup_{\eta\in H({\rm div};\Omega), \left.\eta\cdot n\right|_{\Gamma_- \cup \Gamma_0} = 0} \frac{\langle v, \eta\cdot n\rangle}{\|\eta\|_{H({\rm div},\Omega)}}
+\end{align*}
+
 The second lemma concerns the robust control of $u$ by the energy error; the first and third concern the robust control of field variable $\sigma$ and flux/trace variables, respectively.
@@
 \label{lemma_1}
-Assume \eqref{a_req} and \eqref{adjoint} hold.  Then, for $v$ satisfying \eqref{bc_1}, \eqref{bc_2} and sufficiently small $\epsilon$, 
+Assume \eqref{a_req} holds.  Then, for $v$ satisfying equation \eqref{adjoint} with boundary conditions \eqref{bc_1}, \eqref{bc_2} and sufficiently small $\epsilon$, 
 \[
-\epsilon \|\grad v\|^2 + \|v\|^2 \lesssim \|g\| + \epsilon \| f\|
+\epsilon \|\grad v\|^2 + \|v\|^2 \lesssim \|g\|^2 + \epsilon \| f\|^2
 \]
@@
 \begin{align*}
-\int_\Omega e^\psi (g-\epsilon \div f) w &= \int_\Omega e^\psi g + \int_\Omega \epsilon f \cdot \grad (e^\psi w) - \int_\Gamma \epsilon f\cdot n e^\psi w\\
+\int_\Omega e^\psi (g-\epsilon \div f) w &= \int_\Omega e^\psi g + \int_\Omega \epsilon f \cdot \grad (e^\psi w) - \int_\Gamma \epsilon f\cdot n e^\psi w
 \end{align*}
@@
 \label{lemma_2}
-Assume $v$ satisfies $\eqref{adjoint}$,\eqref{bc_1}, and \eqref{bc_2}, and $\beta$ satisfies \eqref{a_req} and \eqref{b_req}.  If $\div f = 0$ and $\epsilon$ is sufficiently small, 
+Assume $v$ satisfies $\eqref{adjoint}$, with boundary conditions \eqref{bc_1}, and \eqref{bc_2}, and $\beta$ satisfies \eqref{a_req} and \eqref{b_req}.
+If $\div f = 0$ and $\epsilon$ is sufficiently small,
 \[
-\|\beta \cdot \grad v \| \lesssim \| f\|
+\|\beta \cdot \grad v \| \lesssim \| g\|
 \]
@@
 \label{lemma_3}
-Let $\beta$ satisfy \eqref{a_req} and \eqref{c_req}, and let $f=g=0$.  Then, there holds
+Let $\beta$ satisfy \eqref{a_req} and \eqref{c_req}, and let $v$ satisfy \eqref{adjoint} with $f=g=0$, and arbitrary boundary conditions.  Then, there holds
 \[
@@
 \end{align*}
-where the boundary norms for $v$ and $\tau$ are defined by duality
-\begin{align*}
-\|[\tau\cdot n]\| &= \|[\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} \coloneqq \sup_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+} = 0} \frac{\langle [\tau \cdot n], w\rangle}{\|w\|_{H^1(\Omega)}}\\
-\|[v]\|&=\|[v]\|_{\Gamma_h^0 \cup \Gamma_+} \coloneqq \sup_{\eta\in H({\rm div};\Omega), \left.\eta\cdot n\right|_{\Gamma_- \cup \Gamma_0} = 0} \frac{\langle v, \eta\cdot n\rangle}{\|\eta\|_{H({\rm div},\Omega)}}
-\end{align*}
+by definition of the boundary norms on $[\tau\cdot n]$ and $[v]$.
+
 Applying the above estimates for $\|\psi\|$ and $\|n\cdot \curl z\|$ and noting that $\|\grad v\| = \frac{1}{\epsilon}\|\tau\|$ completes the proof.
@@
 \end{align}
-%\[
-%\| \left(\tau,v\right) \|_V = \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E}
-%\]
 The proof for this is identical to proving $\|u\|_E = \|u\|_U$ for the choice of the optimal test norm.
@@
 \]
-We will bound each term by first decomposing $\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right)$, where $\left(v_1,\tau_1\right)$ satisfies our adjoint equation \eqref{adjoint} with $f = 0, g= \div \tau - \beta\cdot \grad v$, and $\left(v_2,\tau_2\right)$ satisfies \eqref{adjoint} with $g = 0, f= \epsilon^{-1}\tau + \grad v$.
-By construction, $\left(v_0,\tau_0\right)$ must satisfy \eqref{adjoint} with $f=g=0$, and with boundary conditions
+We will bound $\|\left(v,\tau\right)\|_V$ for all $\left(v,\tau\right)$ satisfying \eqref{adjoint} by first decomposing $\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right)$, where $\left(v_1,\tau_1\right)$ satisfies our adjoint equation \eqref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and
 \begin{align*}
-[v_0] &= [v], \quad x\in \Gamma_h \cup \Gamma_+\\
-[\tau_0 \cdot n] &= [\tau \cdot n]-[\tau_2 \cdot n], \quad x\in \Gamma_h\setminus \Gamma_+\\
+f &= 0\\
+g&= \div \tau - \beta\cdot \grad v,
 \end{align*} 
-\textcolor{red}{not done yet}
+and $\left(v_2,\tau_2\right)$ satisfies \eqref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and 
+\begin{align*}
+g &= 0\\
+f &= \epsilon^{-1}\tau + \grad v.
+\end{align*}
+We note that, if $v_2$ satisfies $n\cdot \grad v_2 = n\cdot f$, by definition of $f$ and $v_2$,
+\begin{align*}
+\tau_2 \cdot n &= \epsilon n\cdot f - \epsilon n\cdot \grad v_2 = 0, \quad x\in \Gamma_- \cup \Gamma_0
+\end{align*}
+By construction, $\left(v_0,\tau_0\right)$ must satisfy \eqref{adjoint} with $f=g=0$, with jumps
+\begin{align*}
+[v_0] &= [v], \quad x\in \Gamma_h^0\\
+[\tau_0 \cdot n] &= [\tau \cdot n], \quad x\in \Gamma_h^0.
+\end{align*}
+By $\left(v_0,\tau_0\right) = \left(v,\tau\right) - \left(v_1,\tau_1\right) - \left(v_2,\tau_2\right)$, $\left(v_0,\tau_0\right)$ must satisfy boundary conditions
+\begin{align*}
+v_0 &= v, \quad x\in \Gamma_+\\
+\tau_0 \cdot n &= \tau \cdot n, \quad x\in \Gamma_-\cup \Gamma_0.
+\end{align*}
+Robustly bounding $\|\left(v,\tau\right)\|_V$ from above reduces to robustly bounding each component 
+\[
+\|\left(v_{0},\tau_{0}\right)\|_V, \|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|g\| + \|f\| + \epsilon^{-1}\|[\tau\cdot n]\| + \epsilon^{-1/2}\|[v]\|
+\]
+%\begin{align*}
+%\|\left(\tau, v\right)\|_{V}^2 &= \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2 \\
+%& \lesssim \|g\| + \|f\| + \epsilon^{-1}\|[\tau\cdot n]\| + \epsilon^{-1/2}\|[v]\|
+%\end{align*}
+\begin{itemize}
+\item \textbf{Bound on $\|\left(v_{0},\tau_{0}\right)\|_V$}
+
+Lemma 3 gives control over $\epsilon\|\grad v_0\| + \frac{1}{\epsilon}\|\tau_0\|$ through
+\[
+\|\grad v_0\| = \frac{1}{\epsilon}\|\tau_0\| \lesssim \frac{1}{\epsilon} \| [\tau_0\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v_0]\|_{\Gamma_h^0 \cup \Gamma_+} = \frac{1}{\epsilon} \| [\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v]\|_{\Gamma_h^0 \cup \Gamma_+}
+\]
+Lemma 4.2 of \cite{analysisDPG} gives us the Poincare inequality for discontinuous functions
+\[
+\|v_0\| \lesssim \|\grad v_0\| + \|[v]\|
+\]
+%Since $f=0$, by Lemma 2, $\|\beta\cdot \grad v_0\|  \lesssim \|g\| = 0$.  
+Since $g = 0$, $\| \div \tau_0\| = \|\beta\cdot \grad v_0\|\lesssim \|\grad v_0\|$, which we've bounded previously.
+
+\item \textbf{Bound on $\|\left(v_{1},\tau_{1}\right)\|_V$}
+
+%Given $\tau_1 \in H({\rm div};\Omega)$, $v\in H^1(\Omega)$, with boundary conditions \eqref{bc_1} and \eqref{bc_2}, $\frac{1}{\epsilon} \| [\tau_0\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v_0]\|_{\Gamma_h^0 \cup \Gamma_+}=0$.
+With $f = 0$, Lemma 2 provides the bound
+\[
+\|\beta \cdot \grad v_1 \| \lesssim \| g\|
+\]
+Noting that $\div \tau_1 = g+\beta\cdot \grad v_1$ gives $\|\div \tau_1 \| \lesssim \|g\|$ as well.  Lemma 1 gives
+\[
+\epsilon \|\grad v_1\|^2 + \|v_1\|^2 \lesssim \|g\|^2
+\]
+and noting that $\epsilon^{-1/2}\tau_1 = \epsilon^{1/2}v_1$ gives $\epsilon\|\grad v_1\|^2 = \epsilon^{-1}\|\tau_1\|^2 \lesssim \|g\|^2$ as well.
+
+\item \textbf{Bound on $\|\left(v_{2},\tau_{2}\right)\|_V$}
+
+Lemma 1 provides
+\[
+\epsilon \|\grad v\|^2 + \|v\|^2 \lesssim  \epsilon \| f\|^2 \leq \|f\|^2
+\]
+We have $\epsilon^{-1}\tau = f - \grad v$, so $\epsilon^{-1} \|\tau\| \lesssim \|f\| + \|\grad v\|$.
+Lemma 1 implies $\|\grad v\|^2  \lesssim  \| f\|^2$, so for $\epsilon \leq 1$, we control $\epsilon^{-1/2}\|\tau\| \leq \epsilon^{-1}\|\tau\| \lesssim \|f\|$.
+The remaining terms can be bounded by noting that, with $g = 0$, $\|\div \tau_2\| = \|\beta\cdot \grad v_2\| \lesssim \|\grad v_2\| \lesssim \|f\| $.
+\end{itemize}
 \end{proof}
@@
 We've shown the robust bound of a norm on $U$ by energy error; for a full equivalence statement, we require a bound on the energy norm by some norm on $U$.
+By the duality of the energy and test norm, this is equivalent to bounding the test norm from below, using the test norm induced by the norm on $U$ bounding the energy norm.
 \begin{lemma}
-Bound from above \textcolor{red}{not done yet}
+
+(Bound from above) For $\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U$,
+\[
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E \lesssim \|u\| + \frac{1}{\sqrt{\epsilon}}\left(\|\sigma\| + \|\widehat{u}\|+ \|\widehat{u}\|\right)
+\]
+
+%\textcolor{red}{not done yet}
 \end{lemma}
 \begin{proof}
-\textcolor{red}{not done yet}
+For any norm on $U$ of the form
+\[
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,*} = \|u\| + C_2 \|\sigma\| + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|,
+\]
+the induced test norm is  
+\begin{align*}
+\| \left(\tau,v\right) \|_{V,*} &= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E} \\
+& = \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle + \langle \widehat{f}_n, \left[v\right] \rangle
+}{\|u\| + C_2 \|\sigma\| + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|} \\
+&\lesssim \|g\| + \frac{1}{C_2}\|f\| + \sup_{\widehat{u},\widehat{f}_n \neq 0}\frac{\langle \left[\tau_n\right], \widehat{u} \rangle + \langle \widehat{f}_n, \left[v\right] \rangle}{C_3\|\widehat{u}\| + C_4\|\widehat{f}_n\|}
+\end{align*}
+where $f$ and $g$ are again the loads of the adjoint problem \eqref{adjoint}.  By the triangle inequality, 
+\begin{align*}
+\epsilon \|f \|^2 &\leq \epsilon^{-1} \| \tau\|^2 + {\epsilon} \|\grad v\|^2 \lesssim \| \left(\tau,v\right)\|_V^2\\
+\|g \| &\leq \|\div \tau\| +  \|\beta \cdot \grad v\| \lesssim \| \left(\tau,v\right)\|_V
+\end{align*}
+We estimate the supremum by following \cite{DPGrobustness}; we begin by choosing $\eta \in H({\rm div}; \Omega)$, $w\in H^1(\Omega)$, such that $\left.\left(\eta-\beta w \right)\cdot n\right |_{\Gamma_+} = 0$ and $\left.w\right |_{\Gamma_-\cup\Gamma_0} = 0$, and integrating the boundary pairing by parts to get
+\begin{align*}
+\langle [\tau\cdot n],w\rangle + \langle [v],\left(\eta - \beta w\right)\cdot n\rangle &\lesssim \|\left(\tau,v\right)\|_V\frac{1}{\sqrt{\epsilon}}\left(\|\eta\| + \|w\|\right)\\
+%\langle [\tau\cdot n],w\rangle + \langle [v],\left(\eta - \beta w\right)\cdot n\rangle 
+&\lesssim \|\left(\tau,v\right)\|_V\frac{1}{\sqrt{\epsilon}}\left(\|\eta-\beta w\| + \|w\|\right)
+\end{align*}
+since $\|\eta\| = \|\eta - \beta w + \beta w\| \leq \|\eta - \beta w\| + \|\beta w\| \lesssim \|\eta-\beta w\| + \|w\|$.  Dividing through and taking the supremum gives
+\[
+\sup_{w,\eta \neq 0} \frac{\langle[\tau\cdot n],w\rangle + \langle [v],\left(\eta - \beta w\right)\cdot n\rangle}{\left(\|\eta-\beta w\| + \|w\|\right)} \lesssim \|\left(\tau,v\right)\|_V\frac{1}{\sqrt{\epsilon}}
+\]
+To finish the proof, define $\rho \in H^{1/2}(\Gamma_h)$ and $\phi \in H^{-1/2}(\Gamma_h)$ such that $\rho = \left.w\right|_{\Gamma_h}$ and $\phi = \left.(\eta-\beta w)\cdot n\right|_{\Gamma_h}$, and note that
+\begin{align*}
+\sup_{\rho,\phi \neq 0} \frac{\langle [\tau\cdot n],\rho\rangle + \langle [v],\phi \rangle}{\|\rho\|+\|\phi\|} &= \sup_{w,\eta \neq 0} \frac{\langle [\tau\cdot n],w\rangle + \langle [v],\left(\eta - \beta w\right)\cdot n\rangle}{ \|w\|+\|\eta-\beta w\|}
+\end{align*}
+
+Together, the bounds on $\|g\|$ and $\|f\|$ imply $\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{E} \lesssim \left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,*}$ for $C_2 = C_3 = C_4 = \frac{1}{\sqrt{\epsilon}}$.
 \end{proof}
@@
 We are especially interested in the ratio of energy error and total $L^2$ error in both $\sigma$ and $u$.
-Stability estimates imply that, using the above test norm, $\|u-u_h\|_{L^2} / \|u-u_h\|_E \sim C$ independent of $\epsilon$.
+Stability estimates imply that, using the above test norm, $\|u-u_h\|_{L^2} / \|u-u_h\|_E \leq C$ independent of $\epsilon$.
 Figure~\ref{ratios_simple} seems to imply that, at least for this model problem, $C=O(1)$.
+Additionally, while we do not have a robust lower bound (i.e.\ $\|u-u_h\|_{L^2} / \|u-u_h\|_E$ can approach $0$ as $\epsilon \rightarrow 0$), our numerical results present a robust lower bound.
 
@@
 The ratios of $L^2$ to energy error are now less predictable than for the previous example, due to the ``moving target" nature of the approximation of oscillatory boundary conditions.
-Even so, the ratios remain bounded and close to $1$ for $\epsilon$ varying over two orders of magnitude, as predicted by theory.
+The numerical experiments were originally performed by applying boundary conditions via interpolation; the result was that the highly oscillatory inflow boundary condition was not sampled enough to be properly resolved, causing the solution to converge to a solution different than the exact solution.
+The experiments were repeated using the penalty method to enforce inflow conditions; however, we note that the proper way to do so is to use an $L^2$ projection at the boundary.
+When using the penalty method, however, the ratios still remain bounded and close to $1$ for $\epsilon$ varying over two orders of magnitude, as predicted by theory.
 

### 2012-03-26 docs/NewBCRobustness_paper/paper.tex
adding ta few small modifications to paper
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@394 36274a68-8941-4c93-80ef-affaed5139da

@@
 The estimates and proofs in this paper are largely based off of techniques and prior work done in \cite{DPGrobustness} and \cite{analysisDPG}; for further details, we encourage readers to consult these two publications as well.
+The primary contributions in this paper are stability estimates for a new set of boundary conditions and a slightly different test norm.
 
@@
 
+In each numerical experiment, we vary $\epsilon = .01, .001, .0001$ in order to demonstrate robustness over a range of $\epsilon$.
+This is intended to mirror the numerical experiments in \cite{DPGrobustness}; for ``worst-case" linear solvers, such as LU decomposition without pivoting, the effect of roundoff error becomes evident for $\epsilon \leq O(1e-5)$.
+
+\textcolor{red}{Add figure here on convergence for smaller epsilon}
+
 \subsection{Erickson model problem}
@@
 
+\pagebreak
+
 \subsubsection{Discontinuous inflow data}

### 2012-03-27 docs/NewBCRobustness_paper/paper.tex
adding roundoff effects discussion to paper
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@396 36274a68-8941-4c93-80ef-affaed5139da

@@
 In each numerical experiment, we vary $\epsilon = .01, .001, .0001$ in order to demonstrate robustness over a range of $\epsilon$.
-This is intended to mirror the numerical experiments in \cite{DPGrobustness}; for ``worst-case" linear solvers, such as LU decomposition without pivoting, the effect of roundoff error becomes evident for $\epsilon \leq O(1e-5)$.
+This is intended to mirror the numerical experiments in \cite{DPGrobustness}; for ``worst-case" linear solvers, such as LU decomposition without pivoting, the effect of roundoff error becomes evident in the solving of optimal test functions for $\epsilon \leq O(1e-5)$.
+The roundoff itself comes from the Gram matrix under certain test norms; for example, if the weighted $\left(H({\rm div};\Omega), H^1(\Omega)\right)$ norm is used for the test norm $\|\left(\tau,v\right)\|_V$ (as was done in \cite{DPG2}), for an element of size $h$, $\|v\|_{L^2}^2 = O(h)$, while $\|\grad v\|_{L^2}^2 = O(h^{-1})$.
+As $h\rightarrow 0$, the seminorm portion of the test norm dominates the Gram matrix, leading to a near-singular and ill-conditioned system.
+
+The effect of roundoff error is often characterized by an increase in the energy error, which (assuming approximability of test functions) is proven to decrease for any series of refined meshes.
+These roundoff effects are dependent primarily on the mesh, appearing when trying to fully resolve boundary layers for very small $\epsilon$.
 
@@
 
+We examined smaller $\epsilon$ as well.
+In \cite{DPGrobustness}, the smallest resolvable $\epsilon$ using only double precision arithmetic was $1e-4$.
+The solution of optimal test functions is now done using both pivoting and equilibration, improving conditioning.
+Roundoff effects still appear, but at smaller values of $\epsilon$.
+
+\begin{figure}[h!]
+\centering
+\subfigure{
+\includegraphics[scale=.38]{figs/roundoff_rates.png}
+}
+\subfigure{
+\includegraphics[scale=.38]{figs/roundoff_ratio.png}
+}
+\caption{Energy error and $L^2$/energy error ratio for $\epsilon=1e-5$, $\epsilon=1e-6$, $\epsilon=1e-7$.
+Non-monotonic behavior of the energy error indicates conditioning issues and roundoff effects.}
+\label{roundoff_figures}
+\end{figure}
+
+Without anisotropic refinements, it still becomes computationally difficult to fully resolve the solution for smaller $\epsilon$.
+Regardless, for all ranges of $\epsilon$, the robustness of DPG remains constant, as indicted by the rates and ratio between $L^2$ and energy error in Figure~\ref{roundoff_figures}.
+For $\epsilon = 1e-5$, we observe that the ratio of $L^2$ error increases, corresponding to the scaling of the test norm with mesh size (the transition in test norm occurs after 8 refinements, which, for an initial $4\times 4$ mesh, implies a minimum element size of about $1.5e-05$.
+At this point, rescaled test norm allows us to take advantage of the full magnitude of the $L^2$ term for $\|v\|$ and $\|\tau\|$ implied by our adjoint estimates).
+By analogy, for smaller $\epsilon = 1e-6, 1e-7$, the transition period should begin near the 10th and 11th refinement iterations; however, we do not observe such behavior.
+For $\epsilon=1e-6$, the ratio simply remains constant, but for $\epsilon=1e-7$, we observe roundoff effects, as the energy error increases at the 11th refinement.
+Since DPG is optimal in the energy norm for a fixed test norm\footnote{While the test norm changes with the mesh, it increases monotonically.
+A strictly stronger test norm implies $\frac{b(u,v)}{\|v\|_1} \geq \frac{b(u,v)}{\|v\|_2}$ for any $\|v\|_1 \leq \|v\|_2$}}, we expect monotonic decrease of the energy error with mesh refinement.
+Non-monotonic behavior indicates either approximation or roundoff error, and as there was no qualitative difference between using $\Delta p = 5$ and $\Delta p = 6$ for these experiments, we expect that the approximation error is negligible and conclude roundoff effects are at play.
+
 \subsubsection{Neglecting $\sigma_n$}
@@
 \end{figure}
-
-\pagebreak
 

### 2012-03-29 docs/NewBCRobustness_paper/paper.tex
committing mods to paper (reorganization)
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@405 36274a68-8941-4c93-80ef-affaed5139da

@@
 Conceptually, these optimal test functions are the result of a minimum residual method applied to the operator form of a variational equation.
-Given Hilbert spaces $U$ and $V$ and a the variational problem $b(u,v) = l(v)$, $\forall u\in U, v\in V$, we can identify $B:U\rightarrow V'$ and $l \in V'$
+Given Hilbert spaces $U$ and $V$ and a variational problem $b(u,v) = l(v)$, $\forall u\in U, v\in V$, we can identify $B:U\rightarrow V'$ and $l \in V'$
 \[
@@
 \[
-\left(v_h,\delta v\right)_V = b(u_h,v)
+\left(v_h,\delta v\right)_V = b(u_h,\delta v)
 \]
 
-Finally, while the above variational problem is a global operation for standard continuous test spaces, the use of discontinuous test spaces reduces it to an element-local problem.
-In practice, this variational problem can rarely be solved exactly and it is solved approximately using the standard Bubnov-Galerkin method and an ``enriched" subspace of $V$.
+Finally, while the above variational problem is a global operation for standard continuous test spaces, the use of discontinuous test spaces reduces it to a local problem that can be solved in an element-by-element fashion.
+In practice, this variational problem can rarely be solved exactly, but instead is solved approximately using the standard Bubnov-Galerkin method and an ``enriched" subspace of $V$.
 We assume the corresponding error in approximation of the optimal test functions is negligible for the scope of this paper.
@@
 
-The DPG (discontinuous Petrov-Galerkin) method is the combination of the concept of computable optimal test functions with the so-called ``ultra-weak formulation", where every equation is relaxed.
+The DPG (discontinuous Petrov-Galerkin) method is the combination of the concept of computable optimal test functions with the so-called ``ultra-weak formulation", where the regularity requirement on each solution variable is relaxed through integration by parts.
 Moreover, to maintain conformity while seeking an $L^2$ setting on interior ``field" variables, boundary terms are identified as additional new unknowns.
@@
 \]
+where $A^*$ is the formal adjoint resulting from integration by parts.
 
@@
 
-Up to now, we've neglected discussion of the proper choice of inner product/norm on the space $V$.  This choice is important, as the choice of norm on $V$ determines the
+Up to now, we have neglected discussion of the proper choice of inner product/norm on the space $V$.  This choice is important, as the choice of norm on $V$ determines the
 
@@
 
-This norm is non-localizable, however - even with discontinuous test functions, solving for optimal test functions under this optimal norm will result in global problems as well, due to the coupling given by the boundary terms in our bilinear form.
+The norm $\|v\|_{\rm opt}$ is non-localizable, however - even with discontinuous test functions, solving for optimal test functions under this optimal norm will result in global problems as well, due to the coupling given by the boundary terms in our bilinear form.
 The ``quasi-optimal" test norm is created by removing such boundary terms and replacing them with scaled $L^2$ norms of the field variables.
@@
 \]
-The growth of $C$ with $\epsilon$ is referred to as a loss of robustness, where the bound on the error in the finite element solution by the best approximation error.
+The growth of $C$ with $\epsilon$ is referred to as a loss of robustness, where the bound on the error in the finite element solution by the best approximation error increases as $\epsilon\rightarrow 0$.
 Intuitively, as our singular perturbation parameter changes, our finite element error is bounded more and more loosely to the best approximation error, allowing for degradation of the solution
@@
 The lack of robustness in this case manifests as ``pollution" error, a phenomenon where the finite element solution degrades over many wavelengths (commonly manifesting as a phase error between the FE solution and the exact solution).
-The DPG method is currently being analyzed for both acoustic and elastic waves in context of the Helmholtz equation \cite{DPG4} and equations of linear elasticity.
-Numerically, DPG appears to yield a ``pollution-free" method for these problems under a specific regularization of the ``quasi-optimal" test norm.
+The DPG method is currently being analyzed for both acoustic and elastic waves in context of the Helmholtz equation and equations of linear elasticity.
+Numerically, DPG appears to provide a ``pollution-free" method for these problems under a specific regularization of the ``quasi-optimal" test norm \cite{DPG4}.
 
@@
 \]
-where the above inner products are taken element-wise over the finite element mesh $\Omega_h$, and the duality pairings are taken on $\Gamma_h$, the mesh ``skeleton", or union of edges of elements $K$ in $\Omega_h$.
-The divergence and gradient operators are likewise understood to be taken element-wise.
+where $\left[ \tau_n \right]$ and $\left[ v\right]$ denote the jumps in $\tau_n$ and $v$, defined as
+\begin{align*}
+\left[ \tau_n \right] &= \tau^+ \cdot n^+ + \tau^-\cdot n^-\\
+\left[ v\right] &= v^+{\rm sgn}(n^+) - v^-{\rm sgn}(n^-)
+\end{align*}
+Additionally, the inner products are taken element-wise over the finite element mesh $\Omega_h$, and the duality pairings are taken on $\Gamma_h$, the mesh ``skeleton", or union of edges of elements $K$ in $\Omega_h$.
+The divergence and gradient operators are likewise understood to act element-wise.
 
@@
 By duality, $\widehat{u}$ lives in $H^{1/2}(\Gamma_h)$, the trace space of $H^1(\Omega_h)$, while $\widehat{f}_n$ comes from $H^{-1/2}(\Gamma_h)$, the normal trace space of $H({\rm div},\Omega_h)$.
+
+\subsection{\textcolor{red}{Make new subsection on robustness here, reorganize}}
 
@@
 \end{align*}
-Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions everywhere on $\Gamma$, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
+Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
 \[
@@
 on $\Gamma_-$, and continue with the wall boundary condition $u=0$ on $\Gamma_+$.
-For our model problem, as for most problems of interest in CFD, we expect $\grad u$ to be small near the inflow, and that the solution using $u=u_0$ and $\beta_n u - \sigma_n = f_n = u_0$ should converge to each other for sufficiently small $\epsilon$.
+For our model problem, as for most problems of interest in CFD, we expect $\grad u$ to be small near the inflow, and that the solutions to \eqref{primal} using $u=u_0$ and $\beta_n u - \sigma_n = f_n = u_0$ should converge to each other for sufficiently small $\epsilon$.
 
@@
 \[
-b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+}
+b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup \Gamma_h^0}
 \]
@@
 For each proof, we require $\beta \in C^2(\bar{\Omega})$ and $\beta, \div \beta = O(1)$.
-Additionally, we will assume one or both of the following assumptions
+Additionally, we will assume some or all of the following assumptions
 \begin{align}
@@
 
-The primary result of this paper is that, if conditions \ref{a_req},\ref{b_req}, and \ref{c_req} are all satisfied, the DPG method provides robust control over the $L^2$ error 
+The primary result of this paper is that, if conditions \ref{a_req},\ref{b_req}, and \ref{c_req} are all satisfied, the DPG method provides robust control over the $L^2$ error in $u$ and $\sigma$
 \[
@@
 \]
+The choice of test norm \textcolor{red}{should be explained here}.
+
 A second, weaker result is an upper bound on the energy norm
@@
 \[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U_2} \coloneqq \|u\| + \frac{1}{\sqrt{\epsilon}}\left(\|\sigma\|^2 + \|\widehat{u}\|^2+ \|\widehat{f}_n\|^2\right).
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U_2}^2 \coloneqq \|u\|^2 + \frac{1}{\sqrt{\epsilon}}\left(\|\sigma\|^2 + \|\widehat{u}\|^2+ \|\widehat{f}_n\|^2\right).
 \]
-The upper bound on the energy norm appears to depend on $\epsilon^{-1}$, implying that, at most, we have the bound from below $\|u-u_h\|_{U} \geq \epsilon\|u-u_h\|_E$.
-However, numerical experiments demonstrate much better results, and suggest that, at least for our examples, $\|u-u_h\|_E \lesssim \|u-u_h\|_{U}$, implying that the induced energy norm is equivalent to the canonical norms we've chosen on the group variable $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)$.
+The upper bound on the energy norm appears to depend on $\epsilon^{-1/2}$, implying that for very small $\epsilon$, the $L^2$ error may be much smaller than the energy error.
+However, numerical experiments demonstrate much better results, and suggest that, at least for our examples, $\|u-u_h\|_E \sim \|u-u_h\|_{U}$, implying that the induced energy norm is equivalent to the canonical norms we have chosen on the group variable $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)$.
 
-The proof proceeds in two parts; the bound from below is proven by providing stability estimates for the adjoint problem, while the bound from above of the energy norm is proven separately.
+The proof proceeds in two steps; the bound from below is proven by providing stability estimates for the adjoint problem, while the bound from above of the energy norm is proven separately.
 
@@
 and treat the cases $f=0$, $g=0$ separately.
-The above boundary conditions reduce down to \eqref{eq:adj_bc1} and \eqref{eq:adj_bc2} when requesting $L^2$ robustness in $u$ ($f=0$); these more general boundary conditions are necessary for bounds involving $f \neq 0$.
+The above boundary conditions simplify to \eqref{eq:adj_bc1} and \eqref{eq:adj_bc2} when requesting $L^2$ robustness in $u$ ($f=0$); these more general boundary conditions are necessary for bounds involving $f \neq 0$.
 
@@
 
-The second lemma concerns the robust control of $u$ by the energy error; the first and third concern the robust control of field variable $\sigma$ and flux/trace variables, respectively.
+\textcolor{Fix ordering of lemmas} The second lemma concerns the robust control of $u$ by the energy error; the first and third concern the robust control of field variable $\sigma$ and flux/trace variables, respectively.
 
@@
 assuming $\epsilon$ is sufficiently small.
-Our assumptions on $\beta$ allow us to bound $\left((1-\epsilon)|\beta|^2 + \frac{1}{2} \div \beta \right) \lesssim 1$ and $e^\psi \lesssim 1$.
-We can then bound the left hand side from below by
+Our assumptions on $\beta$ implies $\left((1-\epsilon)|\beta|^2 + \frac{1}{2} \div \beta \right) \lesssim 1$ and $e^\psi = O(1)$.
+We can then bound from below
 \[
@@
 \label{lemma_2}
-Assume $v$ satisfies $\eqref{adjoint}$, with boundary conditions \eqref{bc_1}, and \eqref{bc_2}, and $\beta$ satisfies \eqref{a_req} and \eqref{b_req}.
+Assume $v$ satisfies \eqref{adjoint}, with boundary conditions \eqref{bc_1}, and \eqref{bc_2}, and $\beta$ satisfies \eqref{a_req} and \eqref{b_req}.
 If $\div f = 0$ and $\epsilon$ is sufficiently small,
@@
 \begin{proof}
-Define $v_\beta = \beta\cdot \grad v$.  Multiplying by $v_\beta$ and integrating over $\Omega$ gives
+Define $v_\beta = \beta\cdot \grad v$.  Multiplying the adjoint equation \eqref{adjoint} by $v_\beta$ and integrating over $\Omega$ gives
 \[
@@
 %Since $f=0$, by Lemma 2, $\|\beta\cdot \grad v_0\|  \lesssim \|g\| = 0$.  
-Since $g = 0$, $\| \div \tau_0\| = \|\beta\cdot \grad v_0\|\lesssim \|\grad v_0\|$, which we've bounded previously.
+Since $g = 0$, $\| \div \tau_0\| = \|\beta\cdot \grad v_0\|\lesssim \|\grad v_0\|$, which we have bounded previously.
 
@@
 
-We've shown the robust bound of a norm on $U$ by energy error; for a full equivalence statement, we require a bound on the energy norm by some norm on $U$.
+We have shown the robust bound of a norm on $U$ by energy error; for a full equivalence statement, we require a bound on the energy norm by some norm on $U$.
 By the duality of the energy and test norm, this is equivalent to bounding the test norm from below, using the test norm induced by the norm on $U$ bounding the energy norm.

### 2012-03-30 docs/NewBCRobustness_paper/paper.tex
reorganized paper, fixed math typo
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@408 36274a68-8941-4c93-80ef-affaed5139da

@@
 We consider the model convection-diffusion problem on domain $\Omega$ with boundary $\Gamma$
+\begin{align}
+\div (\beta u) - \epsilon\Delta v &= f  \label{primal}
+\end{align}
+in first order form
 \begin{align*}
@@
 with the corresponding variational form 
-\[
+\begin{align*}
 b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle + \langle \widehat{f}_n, \left[v\right] \rangle
-\]
+\end{align*}
 where $\left[ \tau_n \right]$ and $\left[ v\right]$ denote the jumps in $\tau_n$ and $v$, defined as
@@
 \left[ \tau_n \right] &= \tau^+ \cdot n^+ + \tau^-\cdot n^-\\
-\left[ v\right] &= v^+{\rm sgn}(n^+) - v^-{\rm sgn}(n^-)
+\left[ v\right] &= v^+{\rm sgn}(n^+) + v^-{\rm sgn}(n^-)
 \end{align*}
@@
 
-\subsection{\textcolor{red}{Make new subsection on robustness here, reorganize}}
+We split the boundary $\Gamma$ into three portions
+\begin{align*}
+\Gamma_{-} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\} \quad {\rm (inflow)}\\
+\Gamma_{+} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\} \quad {\rm (outflow)}\\
+\Gamma_{0} &\coloneqq \{x\in \Gamma; \beta_n(x) = 0\}
+\end{align*}
+We adopt a new inflow boundary condition, given by Hesthaven et al in \cite{Hesthaven96astable}, where we set
+\[
+\beta_n u - \sigma_n = f_n = u_0
+\]
+on $\Gamma_-$, and continue with the wall boundary condition $u=0$ on $\Gamma_+$.
+For our model problem, as for most problems of interest in CFD, we expect $\grad u$ to be small near the inflow, and that the solutions to \eqref{primal} using $u=u_0$ and $\beta_n u - \sigma_n = f_n = u_0$ should converge to each other for sufficiently small $\epsilon$.
+Under these new boundary conditions, our variational problem $b(u,v) = l(v)$ is now defined by
+\begin{align*}
+b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup \Gamma_h^0} \\
+l\left(\left(\tau,v\right)\right) &= \left(f, v\right) + \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_+} - \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_-} 
+\end{align*}
 
-To analyze the robustness of DPG, we note that 
-\[
-b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \| u \|^2_{L^2}
-\]
-for the specific continuous test functions $\tau$ and $v$ satisfying
-\begin{align*}
-\div \tau - \beta \cdot \grad v &= g \\
-\frac{1}{\epsilon}\tau + \grad v &= f
-\end{align*}
-with $g=u$ and $f=0$, and with boundary conditions such that the boundary terms in the bilinear form vanish.  Then, for the above choice of $\left(\tau, v\right)$, 
-\begin{align*}
-\|u\|_{L^2}^2 &= b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right)}{\|\left(\tau, v\right)\|_V}\|\left(\tau, v\right)\|_V \leq \|u\|_E \|\left(\tau, v\right)\|_V
-\end{align*}
-We will use the notation $\lesssim$ to denote an $\epsilon$-independent bound.
-If we can show $\|\left(\tau, v\right)\|_V \lesssim \| g \|_{L^2}$ for any choice of $g \in L^2$, then, for $g=u$, dividing through by $\|u\|_{L^2}$ gives
-\[
-\|u\|_{L^2} \lesssim \|u\|_E
-\]
-which results in in robust control of the $L^2$ error by the error in the energy norm, in which DPG is optimal.
-The study of robustness for the DPG method has now been reduced to proving stability estimates for the adjoint problem.
+\subsection{Approximability of the quasi-optimal test norm}%\textcolor{red}{Make new subsection on robustness here, reorganize}}
 
@@
 The estimates and proofs in this paper are largely based off of techniques and prior work done in \cite{DPGrobustness} and \cite{analysisDPG}; for further details, we encourage readers to consult these two publications as well.
-The primary contributions in this paper are stability estimates for a new set of boundary conditions and a slightly different test norm.
+The primary contributions in this paper are stronger stability estimates for a new inflow boundary condition and a slightly different test norm.
 
@@
 
-We split the boundary $\Gamma$ into three portions
+To analyze the robustness of DPG, we note that 
 \begin{align*}
-\Gamma_{-} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\} \quad {\rm (inflow)}\\
-\Gamma_{+} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\} \quad {\rm (outflow)}\\
-\Gamma_{0} &\coloneqq \{x\in \Gamma; \beta_n(x) = 0\}\\
+b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup \Gamma_h^0} \\
+&= \| u \|^2_{L^2}
 \end{align*}
+for the specific continuous test functions $\tau$ and $v$ satisfying
+\begin{align*}
+\div \tau - \beta \cdot \grad v &= g \\
+\frac{1}{\epsilon}\tau + \grad v &= f
+\end{align*}
+with $g=u$ and $f=0$, and with boundary conditions
+with boundary conditions
+\begin{align}
+\tau_n &= 0, \quad x\in \Gamma_-\cup \Gamma_0 \label{eq:adj_bc1}\\
+v &= 0, \quad x\in \Gamma_+ \label{eq:adj_bc2}
+\end{align}
+such that the boundary terms in the bilinear form vanish.  Then, for the above choice of $\left(\tau, v\right)$, 
+\begin{align*}
+\|u\|_{L^2}^2 &= b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right)}{\|\left(\tau, v\right)\|_V}\|\left(\tau, v\right)\|_V \leq \|u\|_E \|\left(\tau, v\right)\|_V
+\end{align*}
+We will use the notation $\lesssim$ to denote an $\epsilon$-independent bound.
+If we can show $\|\left(\tau, v\right)\|_V \lesssim \| g \|_{L^2}$ for any choice of $g \in L^2$, then, for $g=u$, dividing through by $\|u\|_{L^2}$ gives
+\[
+\|u\|_{L^2} \lesssim \|u\|_E
+\]
+which results in in robust control of the $L^2$ error by the error in the energy norm, in which DPG is optimal.
+The study of robustness for the DPG method has now been reduced to proving stability estimates for the adjoint problem.
+
 Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
@@
 For our model problem, as for most problems of interest in CFD, we expect $\grad u$ to be small near the inflow, and that the solutions to \eqref{primal} using $u=u_0$ and $\beta_n u - \sigma_n = f_n = u_0$ should converge to each other for sufficiently small $\epsilon$.
-
-Under the new inflow conditions, the induced bilinear form is now
+Using this, we can prove robust control over $\|u\|_{L^2}$ using the using the unweighted version of the test norm in \cite{DPGrobustness}
 \[
-b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup \Gamma_h^0}
+\|\left(\tau, v\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2
 \]
-The corresponding adjoint problem for $L^2$ stability of $u$ now has boundary conditions
-\begin{align}
-\tau_n &= 0, \quad x\in \Gamma_-\cup \Gamma_0 \label{eq:adj_bc1}\\
-v &= 0, \quad x\in \Gamma_+ \label{eq:adj_bc2}
-\end{align}
+This test norm is implied by certain norm ``building blocks"; stability analysis of the adjoint equation allows us to bound from above norms and seminorms on $v$ and $\tau$ by $\|f\|_{L^2}$ and $\|g\|_{L^2}$ in ways that do not grow as $\epsilon \rightarrow 0$, and we assemble the test norm as combinations of such norms and seminorms on $v$ and $\tau$.
 
@@
 \]
-using the unweighted version of the test norm in \cite{DPGrobustness}
+using the test norm
 \[
@@
 \]
-The choice of test norm \textcolor{red}{should be explained here}.
+%\textcolor{red}{should be explained here}.
 
@@
 \end{align*}
-
-\textcolor{Fix ordering of lemmas} The second lemma concerns the robust control of $u$ by the energy error; the first and third concern the robust control of field variable $\sigma$ and flux/trace variables, respectively.
+Lemma \ref{lemma_grad} concerns the robust control of $u$ by the energy error; Lemmas \ref{lemma_stream} and \ref{lemma_boundary} concern the robust control of field variable $\sigma$ and flux/trace variables, respectively.
 
 \begin{lemma} 
-\label{lemma_1}
-Assume \eqref{a_req} holds.  Then, for $v$ satisfying equation \eqref{adjoint} with boundary conditions \eqref{bc_1}, \eqref{bc_2} and sufficiently small $\epsilon$, 
-\[
-\epsilon \|\grad v\|^2 + \|v\|^2 \lesssim \|g\|^2 + \epsilon \| f\|^2
-\]
-\end{lemma}
-
-\begin{proof}
-Since $\curl \beta=0$, and $\Omega$ is simply connected, there exists a scalar potential $\psi$, $\grad \psi = \beta$ such that $e^\psi = O(1)$.
-Take the transformed function $w = e^\psi v$; following (2.26) in \cite{DPGrobustness}, we substitute $w$ into the the left hand side of equation \eqref{adjoint}, arriving at the relation
-\[
--\epsilon \Delta w - (1-2\epsilon) \beta \cdot \grad w + \left((1-\epsilon)|\beta|^2 + \epsilon \div \beta\right) w = e^\psi (g-\epsilon \div f)
-\]
-Multiplying by $w$ and integrating over $\Omega$ gives
-\[
--\epsilon \int_\Omega \Delta ww - (1-2\epsilon) \int_\Omega\beta \cdot \grad w w + \int_\Omega\left((1-\epsilon)|\beta|^2 + \epsilon \div \beta\right) w^2 = \int_\Omega e^\psi (g-\epsilon \div f) w
-\]
-Integrating by parts gives
-\[
--\epsilon \int_\Omega \Delta ww - (1-2\epsilon) \int_\Omega\beta \cdot \grad w w = \epsilon \left( \int_\Omega |\grad w|^2- \int_{\Gamma} w \grad w \cdot n  \right) + \frac{(1-2\epsilon) }{2} \left(\int_\Omega \div \beta w^2 - \int_\Gamma\beta_n w^2 \right)
-\]
-Noting that $w=0$ on $\Gamma_+$ reduces the boundary integrals over $\Gamma$ to just the inflow $\Gamma_-$.
-Furthermore, we have the relation $\grad w = e^\psi(\grad v + \beta v)$.
-Applying the above and boundary conditions on $\Gamma_-$, the first boundary integral becomes
-\[
-\int_{\Gamma_-} w \grad w \cdot n = \int_{\Gamma_-} we^\psi(\grad v + \beta v)\cdot n =  \int_{\Gamma_-} we^\psi(f\cdot n + \beta_n v)
-\]
-Noting $\int_{\Gamma_-}\beta_n w^2 \leq 0$ through $\beta_n<0$ on the inflow gives
-\[
-\epsilon \int_\Omega |\grad w|^2 + \int_\Omega \left((1-\epsilon)|\beta|^2 + \frac{1}{2} \div \beta \right) w^2 - \epsilon \int_{\Gamma_-} we^\psi f\cdot n \leq \int_\Omega e^\psi (g-\epsilon \div f) w
-\]
-assuming $\epsilon$ is sufficiently small.
-Our assumptions on $\beta$ implies $\left((1-\epsilon)|\beta|^2 + \frac{1}{2} \div \beta \right) \lesssim 1$ and $e^\psi = O(1)$.
-We can then bound from below
-\[
-\epsilon \|\grad w\|^2 + \|w\|^2 - \epsilon \int_{\Gamma_-} we^\psi f\cdot n  \lesssim \epsilon \int_\Omega |\grad w|^2 + \int_\Omega \left((1-\epsilon)|\beta|^2 + \frac{1}{2} \div \beta \right) w^2 - \epsilon \int_{\Gamma_-} we^\psi f\cdot n
-\]
-Interpreting $\div f$ as a functional, the right hand gives
-\begin{align*}
-\int_\Omega e^\psi (g-\epsilon \div f) w &= \int_\Omega e^\psi g + \int_\Omega \epsilon f \cdot \grad (e^\psi w) - \int_\Gamma \epsilon f\cdot n e^\psi w
-\end{align*}
-The boundary integral on $\Gamma$ reduces to $\Gamma_-$, which is then nullified by the same term on the left hand side, leaving us with 
-\[
-\epsilon \|\grad w\|^2 + \|w\|^2 \lesssim \int_\Omega e^\psi g + \int_\Omega \epsilon f \cdot \grad (e^\psi w) = \int_\Omega e^\psi g + \int_\Omega \epsilon f \cdot (\beta w + \grad w)
-\]
-From here, the proof is identical to \cite{DPGrobustness}; an application of Peter-Paul Young's inequality to the right hand side and bounds on $\|v\|, \|\grad v\|$ by $\|w\|,\|\grad w\|$ complete the estimate.
-%ISSUE: REMOVE BOUNDARY TERM
-\end{proof}
-
-\begin{lemma} 
-\label{lemma_2}
+\label{lemma_stream}
 Assume $v$ satisfies \eqref{adjoint}, with boundary conditions \eqref{bc_1}, and \eqref{bc_2}, and $\beta$ satisfies \eqref{a_req} and \eqref{b_req}.
@@
 \begin{lemma} 
-\label{lemma_3}
+\label{lemma_grad}
+Assume \eqref{a_req} holds.  Then, for $v$ satisfying equation \eqref{adjoint} with boundary conditions \eqref{bc_1}, \eqref{bc_2} and sufficiently small $\epsilon$, 
+\[
+\epsilon \|\grad v\|^2 + \|v\|^2 \lesssim \|g\|^2 + \epsilon \| f\|^2
+\]
+\end{lemma}
+
+\begin{proof}
+Since $\curl \beta=0$, and $\Omega$ is simply connected, there exists a scalar potential $\psi$, $\grad \psi = \beta$ such that $e^\psi = O(1)$.
+Take the transformed function $w = e^\psi v$; following (2.26) in \cite{DPGrobustness}, we substitute $w$ into the the left hand side of equation \eqref{adjoint}, arriving at the relation
+\[
+-\epsilon \Delta w - (1-2\epsilon) \beta \cdot \grad w + \left((1-\epsilon)|\beta|^2 + \epsilon \div \beta\right) w = e^\psi (g-\epsilon \div f)
+\]
+Multiplying by $w$ and integrating over $\Omega$ gives
+\[
+-\epsilon \int_\Omega \Delta ww - (1-2\epsilon) \int_\Omega\beta \cdot \grad w w + \int_\Omega\left((1-\epsilon)|\beta|^2 + \epsilon \div \beta\right) w^2 = \int_\Omega e^\psi (g-\epsilon \div f) w
+\]
+Integrating by parts gives
+\[
+-\epsilon \int_\Omega \Delta ww - (1-2\epsilon) \int_\Omega\beta \cdot \grad w w = \epsilon \left( \int_\Omega |\grad w|^2- \int_{\Gamma} w \grad w \cdot n  \right) + \frac{(1-2\epsilon) }{2} \left(\int_\Omega \div \beta w^2 - \int_\Gamma\beta_n w^2 \right)
+\]
+Noting that $w=0$ on $\Gamma_+$ reduces the boundary integrals over $\Gamma$ to just the inflow $\Gamma_-$.
+Furthermore, we have the relation $\grad w = e^\psi(\grad v + \beta v)$.
+Applying the above and boundary conditions on $\Gamma_-$, the first boundary integral becomes
+\[
+\int_{\Gamma_-} w \grad w \cdot n = \int_{\Gamma_-} we^\psi(\grad v + \beta v)\cdot n =  \int_{\Gamma_-} we^\psi(f\cdot n + \beta_n v)
+\]
+Noting $\int_{\Gamma_-}\beta_n w^2 \leq 0$ through $\beta_n<0$ on the inflow gives
+\[
+\epsilon \int_\Omega |\grad w|^2 + \int_\Omega \left((1-\epsilon)|\beta|^2 + \frac{1}{2} \div \beta \right) w^2 - \epsilon \int_{\Gamma_-} we^\psi f\cdot n \leq \int_\Omega e^\psi (g-\epsilon \div f) w
+\]
+assuming $\epsilon$ is sufficiently small.
+Our assumptions on $\beta$ implies $\left((1-\epsilon)|\beta|^2 + \frac{1}{2} \div \beta \right) \lesssim 1$ and $e^\psi = O(1)$.
+We can then bound from below
+\[
+\epsilon \|\grad w\|^2 + \|w\|^2 - \epsilon \int_{\Gamma_-} we^\psi f\cdot n  \lesssim \epsilon \int_\Omega |\grad w|^2 + \int_\Omega \left((1-\epsilon)|\beta|^2 + \frac{1}{2} \div \beta \right) w^2 - \epsilon \int_{\Gamma_-} we^\psi f\cdot n
+\]
+Interpreting $\div f$ as a functional, the right hand gives
+\begin{align*}
+\int_\Omega e^\psi (g-\epsilon \div f) w &= \int_\Omega e^\psi g + \int_\Omega \epsilon f \cdot \grad (e^\psi w) - \int_\Gamma \epsilon f\cdot n e^\psi w
+\end{align*}
+The boundary integral on $\Gamma$ reduces to $\Gamma_-$, which is then nullified by the same term on the left hand side, leaving us with 
+\[
+\epsilon \|\grad w\|^2 + \|w\|^2 \lesssim \int_\Omega e^\psi g + \int_\Omega \epsilon f \cdot \grad (e^\psi w) = \int_\Omega e^\psi g + \int_\Omega \epsilon f \cdot (\beta w + \grad w)
+\]
+From here, the proof is identical to \cite{DPGrobustness}; an application of Peter-Paul Young's inequality to the right hand side and bounds on $\|v\|, \|\grad v\|$ by $\|w\|,\|\grad w\|$ complete the estimate.
+%ISSUE: REMOVE BOUNDARY TERM
+\end{proof}
+
+\begin{lemma}
+\label{lemma_boundary}
 Let $\beta$ satisfy \eqref{a_req} and \eqref{c_req}, and let $v$ satisfy \eqref{adjoint} with $f=g=0$, and arbitrary boundary conditions.  Then, there holds
@@
 \begin{align*}
--\epsilon \grad \psi + \div \left(\beta \psi\right) &= -\div \tau \\
+-\epsilon \Delta \psi + \div \left(\beta \psi\right) &= -\div \tau \\
 \epsilon \grad \psi \cdot n - \beta_n \psi - \tau\cdot n &= 0, \quad x\in \Gamma_-\\
@@
 
-%\textcolor{red}{not done yet}
 \end{lemma}
@@
 
-\textcolor{red}{Add figure here on convergence for smaller epsilon}
+%\textcolor{red}{Add figure here on convergence for smaller epsilon}
 
@@
 Since DPG is optimal in the energy norm for a fixed test norm\footnote{While the test norm changes with the mesh, it increases monotonically.
-A strictly stronger test norm implies $\frac{b(u,v)}{\|v\|_1} \geq \frac{b(u,v)}{\|v\|_2}$ for any $\|v\|_1 \leq \|v\|_2$}}, we expect monotonic decrease of the energy error with mesh refinement.
+A strictly stronger test norm implies $\frac{b(u,v)}{\|v\|_1} \geq \frac{b(u,v)}{\|v\|_2}$ for any $\|v\|_1 \leq \|v\|_2$}, we expect monotonic decrease of the energy error with mesh refinement.
 Non-monotonic behavior indicates either approximation or roundoff error, and as there was no qualitative difference between using $\Delta p = 5$ and $\Delta p = 6$ for these experiments, we expect that the approximation error is negligible and conclude roundoff effects are at play.

### 2012-03-30 docs/NewBCRobustness_paper/paper.tex
committing start of modifications to paper
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@411 36274a68-8941-4c93-80ef-affaed5139da

@@
 
-%\tableofcontents
+\tableofcontents
 \maketitle
@@
 \section{Introduction}
+
+\subsection{Singular perturbation problems and robustness}
+
+Standard Bubnov-Galerkin methods tend to perform poorly for the class of partial-differential equations known as singularly perturbed problems, where a given parameter $\epsilon$ may approach either $0$ or $\infty$ in the context of physical problems.
+This poor performance is captured by the error bound
+\[
+\|u-u_h\|_E \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_U
+\]
+The growth of $C$ with $\epsilon$ is referred to as a loss of robustness, where the bound on the error in the finite element solution by the best approximation error increases as $\epsilon\rightarrow 0$.
+Intuitively, as our singular perturbation parameter changes, our finite element error is bounded more and more loosely to the best approximation error, allowing for degradation of the solution
+
+A well-known example is the growth of spurious oscillations in the finite element solution of the 1D convection-diffusion problem $ u'-\epsilon u'' = f$ (with Dirichlet boundary conditions) as $\epsilon\rightarrow 0$.
+Another class of examples are wave propagation problems, in which the singular perturbation parameter is the wavenumber, $k\rightarrow \infty$.
+The lack of robustness in this case manifests as ``pollution" error, a phenomenon where the finite element solution degrades over many wavelengths (commonly manifesting as a phase error between the FE solution and the exact solution).
+
+\textcolor{red}{add bit about residual-based stabilization terms and test functions}
 
@@
 Moreover, to maintain conformity while seeking an $L^2$ setting on interior ``field" variables, boundary terms are identified as additional new unknowns.
-The result is a hybrid DG method with locally supported optimal test functions.
+The result is a hybridized DG method with locally supported optimal test functions.
 For a given operator equation $Au = f$, the ultra-weak formulation is
@@
 
-\subsection{Choice of test norm}
+\subsection{Optimal and quasi-optimal test norms}
 
-Up to now, we have neglected discussion of the proper choice of inner product/norm on the space $V$.  This choice is important, as the choice of norm on $V$ determines the
+Up to now, we have neglected discussion of the proper choice of inner product/norm on the space $V$.
+This choice is important, as the choice of norm on $V$ determines the norm on $U$ in which DPG is optimal.
+Whether a particular choice of norm on $V$ norm is ``good" or not is problem-dependent; however, there is an important canonical choice of test norm for any given variational form.
 
-Under the assumption of injectivity of the adjoint of our variational operator $B$, we can define the optimal test norm 
+Under the assumption of injectivity of the adjoint of our variational operator $B$, we can define the \textit{optimal test norm} 
 \[
@@
 where we're able to switch the order of $\inf$ and $\sup$ due to the injectivity of $B$ (see  \cite{BabuskaEquivBrezzi}).
+This is the ideal test norm; given any particular norm $\|u\|_U$, DPG under the optimal test norm will return the best finite element approximation in that norm.
 
-The norm $\|v\|_{\rm opt}$ is non-localizable, however - even with discontinuous test functions, solving for optimal test functions under this optimal norm will result in global problems as well, due to the coupling given by the boundary terms in our bilinear form.
-The ``quasi-optimal" test norm is created by removing such boundary terms and replacing them with scaled $L^2$ norms of the field variables.
-
-\subsection{Singular perturbation problems and robustness}
-
-Standard Bubnov-Galerkin methods tend to perform poorly for the class of partial-differential equations known as singularly perturbed problems, where a given parameter $\epsilon$ may approach either $0$ or $\infty$ in the context of physical problems.
-This poor performance is captured by the error bound
-\[
-\|u-u_h\|_E \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_U
-\]
-The growth of $C$ with $\epsilon$ is referred to as a loss of robustness, where the bound on the error in the finite element solution by the best approximation error increases as $\epsilon\rightarrow 0$.
-Intuitively, as our singular perturbation parameter changes, our finite element error is bounded more and more loosely to the best approximation error, allowing for degradation of the solution
-
-A well-known example is the growth of spurious oscillations in the finite element solution of the 1D convection-diffusion problem $ u'-\epsilon u'' = f$ (with Dirichlet boundary conditions) as $\epsilon\rightarrow 0$.
-Another class of examples are wave propagation problems, in which the singular perturbation parameter is the wavenumber, $k\rightarrow \infty$.
-The lack of robustness in this case manifests as ``pollution" error, a phenomenon where the finite element solution degrades over many wavelengths (commonly manifesting as a phase error between the FE solution and the exact solution).
+The norm $\|v\|_{\rm opt}$ is non-localizable, however - the inversion of the inner product corresponding to this norm is global, and solving for optimal test functions under this optimal norm will result in global problems as well, due to the coupling given by the boundary terms in our bilinear form.
+In practice, an approximation is made by removing such boundary terms and replacing them with scaled $L^2$ norms of the field variables, producing so-called \textit{quasi-optimal} test norms.
 The DPG method is currently being analyzed for both acoustic and elastic waves in context of the Helmholtz equation and equations of linear elasticity.
-Numerically, DPG appears to provide a ``pollution-free" method for these problems under a specific regularization of the ``quasi-optimal" test norm \cite{DPG4}.
+Numerically, DPG appears to provide a ``pollution-free" method without phase error for these problems under the ``quasi-optimal" test norm with a specific scaling of the regularizing $L^2$ terms \cite{DPG4}.
+Similar results have also been obtained with the quasi-optimal test norm in the context of the elasticity \cite{DPGElas} and linearized Stokes equations \cite{Camellia}.
 
@@
 
-\subsection{Approximability of the quasi-optimal test norm}%\textcolor{red}{Make new subsection on robustness here, reorganize}}
-
-For convection-diffusion, the quasi-optimal norm is 
-\[
-\|\left(\tau, v\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v \|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 + C_1\|v\|_{L^2} + C_2\|\tau\|_{L^2}
-\]
-for some choice of constants $C_1$ and $C_2$.
-We note that the optimal test norm will automatically guarantee the robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.
-However, use of this norm for the convection-diffusion problem is difficult - the variational problem for optimal test functions using the quasi-optimal test norm is equivalent to a reaction-diffusion system \cite{DBLP:journals/procedia/NiemiCC11}.
-Transforming the problem to the reference element reveals that will induce strong boundary layers of width $\epsilon/h^2$ (in comparison, in wave propagation problems, the mesh size tends to be on the order of the wavelength/singular perturbation parameter, resulting in smooth optimal test functions that are much easier to approximate over the reference element).
-As the relevant range of $\epsilon$ for physical problems is $1e-7$, solving on partially under-resolved meshes is unavoidable.
-Resolving such boundary layers for an underresolved mesh has been investigated numerically using specially designed subgrid meshes by Niemi, Collier, and Calo in \cite{DBLP:journals/procedia/NiemiCC11}.
-We approach this from a different perspective, looking instead for robust test norms which do not induce boundary layers in the approximation of optimal test functions.
-
-The estimates and proofs in this paper are largely based off of techniques and prior work done in \cite{DPGrobustness} and \cite{analysisDPG}; for further details, we encourage readers to consult these two publications as well.
-The primary contributions in this paper are stronger stability estimates for a new inflow boundary condition and a slightly different test norm.
-
-\subsection{Boundary conditions and adjoint stability}
-
-To analyze the robustness of DPG, we note that 
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup \Gamma_h^0} \\
-&= \| u \|^2_{L^2}
-\end{align*}
-for the specific continuous test functions $\tau$ and $v$ satisfying
-\begin{align*}
-\div \tau - \beta \cdot \grad v &= g \\
-\frac{1}{\epsilon}\tau + \grad v &= f
-\end{align*}
-with $g=u$ and $f=0$, and with boundary conditions
-with boundary conditions
-\begin{align}
-\tau_n &= 0, \quad x\in \Gamma_-\cup \Gamma_0 \label{eq:adj_bc1}\\
-v &= 0, \quad x\in \Gamma_+ \label{eq:adj_bc2}
-\end{align}
-such that the boundary terms in the bilinear form vanish.  Then, for the above choice of $\left(\tau, v\right)$, 
-\begin{align*}
-\|u\|_{L^2}^2 &= b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right)}{\|\left(\tau, v\right)\|_V}\|\left(\tau, v\right)\|_V \leq \|u\|_E \|\left(\tau, v\right)\|_V
-\end{align*}
-We will use the notation $\lesssim$ to denote an $\epsilon$-independent bound.
-If we can show $\|\left(\tau, v\right)\|_V \lesssim \| g \|_{L^2}$ for any choice of $g \in L^2$, then, for $g=u$, dividing through by $\|u\|_{L^2}$ gives
-\[
-\|u\|_{L^2} \lesssim \|u\|_E
-\]
-which results in in robust control of the $L^2$ error by the error in the energy norm, in which DPG is optimal.
-The study of robustness for the DPG method has now been reduced to proving stability estimates for the adjoint problem.
-
-Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
-\[
-\|\left(\tau, v\right)\|_{V,w}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\|_{w+\epsilon} + \| \div \tau\|_{w+\epsilon} + \frac{1}{\epsilon}\|\tau\|_{w+\epsilon}
-\]
-where $\|\cdot \|_{w+\epsilon}$ is a weighted $L^2$ norm, where the weight $w \in (0,1)$ is required to vanish on $\Gamma_-$.
-The need for the weight is intuitively explained by the induced adjoint problem.
-The bilinear form for the Dirichlet case is
-\[
-b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) + \langle \widehat{f}_n, \left[v\right] \rangle
-\]
-Choosing a continuous conforming test function $v$ removes the contribution of the term $\langle \widehat{f}_n, \left[v\right] \rangle$ on the mesh skeleton; however, it is necessary to assume in addition $v=0$ on $\Gamma$ to have
-$$b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \|u\|_{L^2}^2.$$  Intuitively, the adjoint problem is similar to the primal problem with the direction of inflow reversed, such that the inflow becomes the outflow, and outflow inflow.
-The need for the weight arises due to the presence of the Dirichlet boundary condition on $v$ near the inflow; this induces strong boundary layers at the inflow such that $\grad v \approx O(\epsilon^{-1})$.
-It may be of interest to note that, for sufficiently small $\epsilon$, these issues manifest themselves in numerical experiments as additional refinements near the inflow.
-The presence of the new boundary condition relaxes the outflow boundary condition for the adjoint/dual problem, resulting in stronger stability for the primal problem.
-
-We improve upon the result of Demkowicz and Heuer by adopting a new inflow boundary condition, given by Hesthaven et al in \cite{Hesthaven96astable}, where we set
-\[
-\beta_n u - \sigma_n = f_n = u_0
-\]
-on $\Gamma_-$, and continue with the wall boundary condition $u=0$ on $\Gamma_+$.
-For our model problem, as for most problems of interest in CFD, we expect $\grad u$ to be small near the inflow, and that the solutions to \eqref{primal} using $u=u_0$ and $\beta_n u - \sigma_n = f_n = u_0$ should converge to each other for sufficiently small $\epsilon$.
-Using this, we can prove robust control over $\|u\|_{L^2}$ using the using the unweighted version of the test norm in \cite{DPGrobustness}
-\[
-\|\left(\tau, v\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2
-\]
-This test norm is implied by certain norm ``building blocks"; stability analysis of the adjoint equation allows us to bound from above norms and seminorms on $v$ and $\tau$ by $\|f\|_{L^2}$ and $\|g\|_{L^2}$ in ways that do not grow as $\epsilon \rightarrow 0$, and we assemble the test norm as combinations of such norms and seminorms on $v$ and $\tau$.
-
 \subsection{Norms on $U$}
@@
 \]
+\subsection{Norms on $V$}
+
+%We will denote $\|\cdot \| = \|\cdot\|_{L^2}$ for all functions defined on $\Omega_h$. 
+As $\tau \in H({\rm div},\Omega_h)$ and $v \in H^1(\Omega_h)$, we will construct norms on $v$ and $\tau$ using some combination of terms which are equivalent to the canonical broken $H^1(\Omega_h) \times H({\rm div},\Omega_h)$ norm
+\[
+\|\left(\tau,v\right)\|_{H^1(\Omega_h) \times H({\rm div},\Omega_h)} = \|v\|_{L^2(\Omega_h)}^2 + \|\grad v\|_{L^2(\Omega_h)}^2  + \|\tau\|_{L^2(\Omega_h)}^2 + \|\div \tau\|_{L^2(\Omega_h)}^2
+\]
+The exact norms that we will place on $V$ will be determined later.
+
+The boundary norms on $\Gamma_h$ for $v$ and $\tau$ are defined by duality from the bilinear form
+\begin{align*}
+\|[\tau\cdot n]\| &= \|[\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} \coloneqq \sup_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+} = 0} \frac{\langle [\tau \cdot n], w\rangle}{\|w\|_{H^1(\Omega)}}\\
+\|[v]\|&=\|[v]\|_{\Gamma_h^0 \cup \Gamma_+} \coloneqq \sup_{\eta\in H({\rm div};\Omega), \left.\eta\cdot n\right|_{\Gamma_- \cup \Gamma_0} = 0} \frac{\langle v, \eta\cdot n\rangle}{\|\eta\|_{H({\rm div},\Omega)}}
+\end{align*}
+
+\subsection{Approximability of the quasi-optimal test norm}%\textcolor{red}{Make new subsection on robustness here, reorganize}}
+
+For convection-diffusion, the quasi-optimal norm is 
+\[
+\|\left(\tau, v\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v \|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 + C_1\|v\|_{L^2} + C_2\|\tau\|_{L^2}
+\]
+for some choice of constants $C_1$ and $C_2$.
+We note that the optimal test norm will automatically guarantee the robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.
+However, use of this norm for the convection-diffusion problem is difficult - the variational problem for optimal test functions using the quasi-optimal test norm is equivalent to a reaction-diffusion system \cite{DBLP:journals/procedia/NiemiCC11}.
+Transforming the problem to the reference element reveals that will induce strong boundary layers of width $\epsilon/h^2$ (in comparison, in Helmholtz and wave propagation problems, the mesh size tends to be on the order of the wavelength/singular perturbation parameter, resulting in smooth optimal test functions that are much easier to approximate over the reference element).
+As the relevant range of $\epsilon$ for physical problems is $1e-7$, solving on partially under-resolved meshes is unavoidable.
+
+Resolving such boundary layers for an underresolved mesh has been investigated numerically using specially designed (Shishkin) subgrid meshes by Niemi, Collier, and Calo in \cite{DBLP:journals/procedia/NiemiCC11}.
+However, even with Shishkin meshes, the approximation of optimal test functions under the quasi-optimal norm is difficult and far more expensive than approximation test functions using a simple $p$-enriched space for $V$.
+We approach this from a different perspective, looking instead for robust test norms which do not induce boundary layers in the approximation of optimal test functions, and do so by formulating a general approach to analyzing the behavior of DPG under a given test norm.
+
+The estimates and proofs in this paper are largely based off of techniques and prior work done in \cite{DPGrobustness} and \cite{analysisDPG}; for further details, we encourage readers to consult these two publications as well.
+The primary contributions in this paper are stronger stability estimates for a new inflow boundary condition and a slightly different test norm.
+
+\subsection{Adjoint stability}
+
+\textcolor{red}{introduce the three lemmas}
+An important relationship is the duality of the energy norm and test norm; for any choice of energy norm, the test norm $\|v\|_V$ inducing it can be recovered via duality
+\begin{align}
+\| v \|_V = \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_E} \label{norm_duality}
+\end{align}
+The proof for this is identical to proving $\|u\|_E = \|u\|_U$ for the choice of the optimal test norm.
+
+As a consequence of \eqref{norm_duality}, assume an energy norm $\left\| u \right\|_{E,1}$ is induced by a given test norm $\| v  \|_{V,1}$.
+To bound $\|\cdot\|_E$ robustly from above or below by a given norm $\left\| u \right\|_{U,2}$ on $U$ now only requires the robust bound in the opposite direction of $\| v \|_{V,1}$ by $\|v\|_{V,2}$.
+
+We will use the notation $\lesssim$ to denote an $\epsilon$-independent bound.
+
+\subsubsection{Induced adjoint boundary conditions}
+
+Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
+\[
+\|\left(\tau, v\right)\|_{V,w}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\|_{w+\epsilon} + \| \div \tau\|_{w+\epsilon} + \frac{1}{\epsilon}\|\tau\|_{w+\epsilon}
+\]
+where $\|\cdot \|_{w+\epsilon}$ is a weighted $L^2$ norm, where the weight $w \in (0,1)$ is required to vanish on $\Gamma_-$.
+
+\textcolor{red}{Explain how energy norm convergence in $\|u\| + \epsilon \|u'\|$ returns bad results, and the need for an $O(1)$ term in the test norm.}
+
+The need for the weight is intuitively explained by the induced adjoint problem.  The bilinear form for the Dirichlet case is 
+\[
+b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) + \langle \widehat{f}_n, \left[v\right] \rangle
+\]
+We note that 
+\begin{align*}
+b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup \Gamma_h^0} \\
+&= \| u \|^2_{L^2}
+\end{align*}
+for the specific continuous test functions $\tau$ and $v$ satisfying
+\begin{align*}
+\div \tau - \beta \cdot \grad v &= u \\
+\frac{1}{\epsilon}\tau + \grad v &= 0
+\end{align*}
+with boundary conditions
+\begin{align}
+\tau_n &= 0, \quad x\in \Gamma_-\cup \Gamma_0 \label{eq:adj_bc1}\\
+v &= 0, \quad x\in \Gamma_+ \label{eq:adj_bc2}
+\end{align}
+Choosing a continuous conforming test function $v$ removes the contribution of the term $\langle \widehat{f}_n, \left[v\right] \rangle$ on the mesh skeleton, while the boundary conditions remove the contribution of boundary terms from the bilinear form.
+Then, for this specific choice of $\left(\tau, v\right)$,
+\begin{align*}
+\|u\|_{L^2}^2 &= b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right)}{\|\left(\tau, v\right)\|_V}\|\left(\tau, v\right)\|_V \leq \|u\|_E \|\left(\tau, v\right)\|_V
+\end{align*}
+If we can show $\|\left(\tau, v\right)\|_V \lesssim \| u \|_{L^2}$ for any choice of $u \in L^2$, dividing through by $\|u\|_{L^2}$ gives
+\[
+\|u\|_{L^2} \lesssim \|u\|_E
+\]
+which results in in robust control of the $L^2$ error by the error in the energy norm, in which DPG is optimal.
+
+However, we are unable to prove this in the case of Dirichlet boundary conditions.
+Intuitively, the adjoint problem is similar to the primal problem with the direction of inflow reversed, such that the inflow becomes the outflow, and outflow inflow.
+The need for the weight arises due to the presence of the Dirichlet boundary condition on $v$ near the inflow; this induces strong boundary layers at the inflow such that $\grad v \approx O(\epsilon^{-1})$.
+It may be of interest to note that, for sufficiently small $\epsilon$, these issues manifest themselves in numerical experiments as additional refinements near the inflow.
+The presence of the new boundary condition relaxes the outflow boundary condition for the adjoint/dual problem, resulting in stronger stability for the primal problem.
+
+We improve upon the result of Demkowicz and Heuer not by modifying the test norm, but by adopting a new inflow boundary condition, which changes the stability properties of the corresponding adjoint equation.
+Under these new boundary conditions, we can prove robust control over $\|u\|_{L^2}$ using the unweighted version of the test norm in \cite{DPGrobustness}
+\[
+\|\left(\tau, v\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2
+\]
+This test norm is implied by certain norm ``building blocks"; stability analysis of the adjoint equation allows us to bound from above norms and seminorms on $v$ and $\tau$ by $\|f\|_{L^2}$ and $\|g\|_{L^2}$ in ways that do not grow as $\epsilon \rightarrow 0$, and we assemble the test norm as combinations of such norms and seminorms on $v$ and $\tau$.
 
@@
 
-\subsubsection{Stability of the adjoint problem (bound from below)}
+\subsubsection{Bound from below}
+\textcolor{red}{introduce the three lemmas}
+With these three lemmas, we can prove the robust bound of both field variables and fluxes by the energy error.
+In doing so, we take advantage of the fact that, for any choice of energy norm, the test norm $\|v\|_V$ inducing it can be recovered via duality
+\begin{align}
+\| v \|_V = \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_E} \label{norm_duality}
+\end{align}
+The proof for this is identical to proving $\|u\|_E = \|u\|_U$ for the choice of the optimal test norm.
+
+As a consequence of \eqref{norm_duality}, assume an energy norm $\left\| u \right\|_{E,1}$ is induced by a given test norm $\| v  \|_{V,1}$.
+To bound $\|\cdot\|_E$ robustly from above or below by a given norm $\left\| u \right\|_{U,2}$ on $U$ now only requires the robust bound in the opposite direction of $\| v \|_{V,1}$ by $\|v\|_{V,2}$.
+
+\begin{lemma}
+\label{bound_from_below}
+(Bound from below) If $\beta$ satisfies \eqref{a_req} and \eqref{b_req}, then for $\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U$,
+\[
+\|u\| + \|\sigma\| + \epsilon\|\widehat{u}\|+ \sqrt{\epsilon}\|\widehat{u}\| \lesssim \left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E
+\]
+\end{lemma}
+\begin{proof}
+By \eqref{norm_duality}, proving the above result is equivalent to showing 
+\begin{align*}
+\|\left(v,\tau\right)\|_V &\lesssim \frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\|u\| + \|\sigma\| + \epsilon\|\widehat{u}\|+ \sqrt{\epsilon}\|\widehat{u}\|}\\
+& \simeq \|g\| + \|f\| + \epsilon^{-1}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle [\tau\cdot n], \widehat{u}\rangle}{\|\widehat{u}\|} + \epsilon^{-1/2}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, [v]\rangle}{\|\widehat{f}\|},
+\end{align*}
+which, by definition of the boundary norms, is 
+\[
+\|\left(v,\tau\right)\|_V \lesssim \|g\| + \|f\| + \epsilon^{-1}\|[\tau\cdot n]\| + \epsilon^{-1/2}\|[v]\|
+\]
+We will bound $\|\left(v,\tau\right)\|_V$ for all $\left(v,\tau\right)$ satisfying \eqref{adjoint} by first decomposing $\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right)$, where $\left(v_1,\tau_1\right)$ satisfies our adjoint equation \eqref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and
+\begin{align*}
+f &= 0\\
+g&= \div \tau - \beta\cdot \grad v,
+\end{align*} 
+and $\left(v_2,\tau_2\right)$ satisfies \eqref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and 
+\begin{align*}
+g &= 0\\
+f &= \epsilon^{-1}\tau + \grad v.
+\end{align*}
+We note that, if $v_2$ satisfies $n\cdot \grad v_2 = n\cdot f$, by definition of $f$ and $v_2$,
+\begin{align*}
+\tau_2 \cdot n &= \epsilon n\cdot f - \epsilon n\cdot \grad v_2 = 0, \quad x\in \Gamma_- \cup \Gamma_0
+\end{align*}
+By construction, $\left(v_0,\tau_0\right)$ must satisfy \eqref{adjoint} with $f=g=0$, with jumps
+\begin{align*}
+[v_0] &= [v], \quad x\in \Gamma_h^0\\
+[\tau_0 \cdot n] &= [\tau \cdot n], \quad x\in \Gamma_h^0.
+\end{align*}
+By $\left(v_0,\tau_0\right) = \left(v,\tau\right) - \left(v_1,\tau_1\right) - \left(v_2,\tau_2\right)$, $\left(v_0,\tau_0\right)$ must satisfy boundary conditions
+\begin{align*}
+v_0 &= v, \quad x\in \Gamma_+\\
+\tau_0 \cdot n &= \tau \cdot n, \quad x\in \Gamma_-\cup \Gamma_0.
+\end{align*}
+Robustly bounding $\|\left(v,\tau\right)\|_V$ from above reduces to robustly bounding each component 
+\[
+\|\left(v_{0},\tau_{0}\right)\|_V, \|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|g\| + \|f\| + \epsilon^{-1}\|[\tau\cdot n]\| + \epsilon^{-1/2}\|[v]\|
+\]
+%\begin{align*}
+%\|\left(\tau, v\right)\|_{V}^2 &= \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2 \\
+%& \lesssim \|g\| + \|f\| + \epsilon^{-1}\|[\tau\cdot n]\| + \epsilon^{-1/2}\|[v]\|
+%\end{align*}
+\begin{itemize}
+\item \textbf{Bound on $\|\left(v_{0},\tau_{0}\right)\|_V$}
+
+Lemma \ref{lemma_boundary} gives control over $\epsilon\|\grad v_0\| + \frac{1}{\epsilon}\|\tau_0\|$ through
+\[
+\|\grad v_0\| = \frac{1}{\epsilon}\|\tau_0\| \lesssim \frac{1}{\epsilon} \| [\tau_0\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v_0]\|_{\Gamma_h^0 \cup \Gamma_+} = \frac{1}{\epsilon} \| [\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v]\|_{\Gamma_h^0 \cup \Gamma_+}
+\]
+Lemma 4.2 of \cite{analysisDPG} gives us the Poincare inequality for discontinuous functions
+\[
+\|v_0\| \lesssim \|\grad v_0\| + \|[v]\|
+\]
+%Since $f=0$, by Lemma 2, $\|\beta\cdot \grad v_0\|  \lesssim \|g\| = 0$.  
+Since $g = 0$, $\| \div \tau_0\| = \|\beta\cdot \grad v_0\|\lesssim \|\grad v_0\|$, which we have bounded previously.
+
+\item \textbf{Bound on $\|\left(v_{1},\tau_{1}\right)\|_V$}
+
+%Given $\tau_1 \in H({\rm div};\Omega)$, $v\in H^1(\Omega)$, with boundary conditions \eqref{bc_1} and \eqref{bc_2}, $\frac{1}{\epsilon} \| [\tau_0\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v_0]\|_{\Gamma_h^0 \cup \Gamma_+}=0$.
+With $f = 0$, Lemma \ref{lemma_grad} provides the bound
+\[
+\|\beta \cdot \grad v_1 \| \lesssim \| g\|
+\]
+Noting that $\div \tau_1 = g+\beta\cdot \grad v_1$ gives $\|\div \tau_1 \| \lesssim \|g\|$ as well.  Lemma \ref{lemma_grad} gives
+\[
+\epsilon \|\grad v_1\|^2 + \|v_1\|^2 \lesssim \|g\|^2
+\]
+and noting that $\epsilon^{-1/2}\tau_1 = \epsilon^{1/2}v_1$ gives $\epsilon\|\grad v_1\|^2 = \epsilon^{-1}\|\tau_1\|^2 \lesssim \|g\|^2$ as well.
+
+\item \textbf{Bound on $\|\left(v_{2},\tau_{2}\right)\|_V$}
+
+Lemma \ref{lemma_grad} provides
+\[
+\epsilon \|\grad v\|^2 + \|v\|^2 \lesssim  \epsilon \| f\|^2 \leq \|f\|^2
+\]
+We have $\epsilon^{-1}\tau = f - \grad v$, so $\epsilon^{-1} \|\tau\| \lesssim \|f\| + \|\grad v\|$.
+Lemma 1 implies $\|\grad v\|^2  \lesssim  \| f\|^2$, so for $\epsilon \leq 1$, we control $\epsilon^{-1/2}\|\tau\| \leq \epsilon^{-1}\|\tau\| \lesssim \|f\|$.
+The remaining terms can be bounded by noting that, with $g = 0$, $\|\div \tau_2\| = \|\beta\cdot \grad v_2\| \lesssim \|\grad v_2\| \lesssim \|f\| $.
+\end{itemize}
+\end{proof}
+
+\subsubsection{Bound from above}
+
+We have shown the robust bound of a norm on $U$ by energy error; for a full equivalence statement, we require a bound on the energy norm by some norm on $U$.
+By the duality of the energy and test norm, this is equivalent to bounding the test norm from below, using the test norm induced by the norm on $U$ bounding the energy norm.
+\begin{lemma}
+
+(Bound from above) For $\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U$,
+\[
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E \lesssim \|u\| + \frac{1}{\sqrt{\epsilon}}\left(\|\sigma\| + \|\widehat{u}\|+ \|\widehat{u}\|\right)
+\]
+
+\end{lemma}
+\begin{proof}
+For any norm on $U$ of the form
+\[
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,*} = \|u\| + C_2 \|\sigma\| + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|,
+\]
+the induced test norm is  
+\begin{align*}
+\| \left(\tau,v\right) \|_{V,*} &= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E} \\
+& = \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle + \langle \widehat{f}_n, \left[v\right] \rangle
+}{\|u\| + C_2 \|\sigma\| + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|} \\
+&\lesssim \|g\| + \frac{1}{C_2}\|f\| + \sup_{\widehat{u},\widehat{f}_n \neq 0}\frac{\langle \left[\tau_n\right], \widehat{u} \rangle + \langle \widehat{f}_n, \left[v\right] \rangle}{C_3\|\widehat{u}\| + C_4\|\widehat{f}_n\|}
+\end{align*}
+where $f$ and $g$ are again the loads of the adjoint problem \eqref{adjoint}.  By the triangle inequality, 
+\begin{align*}
+\epsilon \|f \|^2 &\leq \epsilon^{-1} \| \tau\|^2 + {\epsilon} \|\grad v\|^2 \lesssim \| \left(\tau,v\right)\|_V^2\\
+\|g \| &\leq \|\div \tau\| +  \|\beta \cdot \grad v\| \lesssim \| \left(\tau,v\right)\|_V
+\end{align*}
+We estimate the supremum by following \cite{DPGrobustness}; we begin by choosing $\eta \in H({\rm div}; \Omega)$, $w\in H^1(\Omega)$, such that $\left.\left(\eta-\beta w \right)\cdot n\right |_{\Gamma_+} = 0$ and $\left.w\right |_{\Gamma_-\cup\Gamma_0} = 0$, and integrating the boundary pairing by parts to get
+\begin{align*}
+\langle [\tau\cdot n],w\rangle + \langle [v],\left(\eta - \beta w\right)\cdot n\rangle &\lesssim \|\left(\tau,v\right)\|_V\frac{1}{\sqrt{\epsilon}}\left(\|\eta\| + \|w\|\right)\\
+%\langle [\tau\cdot n],w\rangle + \langle [v],\left(\eta - \beta w\right)\cdot n\rangle 
+&\lesssim \|\left(\tau,v\right)\|_V\frac{1}{\sqrt{\epsilon}}\left(\|\eta-\beta w\| + \|w\|\right)
+\end{align*}
+since $\|\eta\| = \|\eta - \beta w + \beta w\| \leq \|\eta - \beta w\| + \|\beta w\| \lesssim \|\eta-\beta w\| + \|w\|$.  Dividing through and taking the supremum gives
+\[
+\sup_{w,\eta \neq 0} \frac{\langle[\tau\cdot n],w\rangle + \langle [v],\left(\eta - \beta w\right)\cdot n\rangle}{\left(\|\eta-\beta w\| + \|w\|\right)} \lesssim \|\left(\tau,v\right)\|_V\frac{1}{\sqrt{\epsilon}}
+\]
+To finish the proof, define $\rho \in H^{1/2}(\Gamma_h)$ and $\phi \in H^{-1/2}(\Gamma_h)$ such that $\rho = \left.w\right|_{\Gamma_h}$ and $\phi = \left.(\eta-\beta w)\cdot n\right|_{\Gamma_h}$, and note that
+\begin{align*}
+\sup_{\rho,\phi \neq 0} \frac{\langle [\tau\cdot n],\rho\rangle + \langle [v],\phi \rangle}{\|\rho\|+\|\phi\|} &= \sup_{w,\eta \neq 0} \frac{\langle [\tau\cdot n],w\rangle + \langle [v],\left(\eta - \beta w\right)\cdot n\rangle}{ \|w\|+\|\eta-\beta w\|}
+\end{align*}
+
+Together, the bounds on $\|g\|$ and $\|f\|$ imply $\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{E} \lesssim \left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,*}$ for $C_2 = C_3 = C_4 = \frac{1}{\sqrt{\epsilon}}$.
+\end{proof}
+
+%In \cite{DPGrobustness}, the quasi-optimal test norm was shown to induce an energy norm that is bounded from both above and below by norms on $U$ that do not grow in magnitude with $\epsilon^{-1}$.
+
+\section{Proof of lemmas/stability of the adjoint problem}
 
@@
 and treat the cases $f=0$, $g=0$ separately.
-The above boundary conditions simplify to \eqref{eq:adj_bc1} and \eqref{eq:adj_bc2} when requesting $L^2$ robustness in $u$ ($f=0$); these more general boundary conditions are necessary for bounds involving $f \neq 0$.
+%The above boundary conditions simplify to \eqref{eq:adj_bc1} and \eqref{eq:adj_bc2} when requesting $L^2$ robustness in $u$ ($f=0$); these more general boundary conditions are necessary for bounds involving $f \neq 0$.
+\textcolor{red}{motivate boundary conditions here}
 
@@
 The normal trace $f\cdot n$ is understood as a limit; smooth functions are dense in $H^1(\Omega)$, and we define $f\cdot n$ as the limit of $f_i\cdot n$, where $f_i \in C^\infty(\Omega)$, $f_i \rightarrow f$.
+\textcolor{red}{clearly define what we mean here with the density argument}
 
-We will denote $\|\cdot \| = \|\cdot\|_{L^2}$ for all functions defined on $\Omega$.  The boundary norms on $\Gamma_h$ for $v$ and $\tau$ are defined by duality from the bilinear form
-\begin{align*}
-\|[\tau\cdot n]\| &= \|[\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} \coloneqq \sup_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+} = 0} \frac{\langle [\tau \cdot n], w\rangle}{\|w\|_{H^1(\Omega)}}\\
-\|[v]\|&=\|[v]\|_{\Gamma_h^0 \cup \Gamma_+} \coloneqq \sup_{\eta\in H({\rm div};\Omega), \left.\eta\cdot n\right|_{\Gamma_- \cup \Gamma_0} = 0} \frac{\langle v, \eta\cdot n\rangle}{\|\eta\|_{H({\rm div},\Omega)}}
-\end{align*}
 Lemma \ref{lemma_grad} concerns the robust control of $u$ by the energy error; Lemmas \ref{lemma_stream} and \ref{lemma_boundary} concern the robust control of field variable $\sigma$ and flux/trace variables, respectively.
@@
 \]
-Since $C=O(1)$, an application of Young's inequality and Lemma 1 complete the estimate.
+Since $C=O(1)$, an application of Young's inequality and Lemma \ref{lemma_grad} complete the estimate.
 \end{proof}
@@
 \end{align*}
-Since $\div \beta = 0$, we satisfy \eqref{a_req}, and can use Lemma 1 (with $f = \frac{1}{\epsilon}\tau$) to bound
+Since $\div \beta = 0$, we satisfy \eqref{a_req}, and can use Lemma \ref{lemma_grad} (with $f = \frac{1}{\epsilon}\tau$) to bound
 \[
@@
 \end{proof}
-
-With these three lemmas, we can prove the robust bound of both field variables and fluxes by the energy error.
-In doing so, we take advantage of the fact that, for any choice of energy norm, the test norm $\|v\|_V$ inducing it can be recovered via duality
-\begin{align}
-\| v \|_V = \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_E} \label{norm_duality}
-\end{align}
-The proof for this is identical to proving $\|u\|_E = \|u\|_U$ for the choice of the optimal test norm.
-
-As a consequence of \eqref{norm_duality}, assume an energy norm $\left\| u \right\|_{E,1}$ is induced by a given test norm $\| v  \|_{V,1}$.
-To bound $\|\cdot\|_E$ robustly from above or below by a given norm $\left\| u \right\|_{U,2}$ on $U$ now only requires the robust bound in the opposite direction of $\| v \|_{V,1}$ by $\|v\|_{V,2}$.
-
-\begin{lemma}
-(Bound from below) If $\beta$ satisfies \eqref{a_req} and \eqref{b_req}, then for $\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U$,
-\[
-\|u\| + \|\sigma\| + \epsilon\|\widehat{u}\|+ \sqrt{\epsilon}\|\widehat{u}\| \lesssim \left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E
-\]
-\end{lemma}
-\begin{proof}
-By \eqref{norm_duality}, proving the above result is equivalent to showing 
-\begin{align*}
-\|\left(v,\tau\right)\|_V &\lesssim \frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\|u\| + \|\sigma\| + \epsilon\|\widehat{u}\|+ \sqrt{\epsilon}\|\widehat{u}\|}\\
-& \simeq \|g\| + \|f\| + \epsilon^{-1}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle [\tau\cdot n], \widehat{u}\rangle}{\|\widehat{u}\|} + \epsilon^{-1/2}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, [v]\rangle}{\|\widehat{f}\|},
-\end{align*}
-which, by definition of the boundary norms, is 
-\[
-\|\left(v,\tau\right)\|_V \lesssim \|g\| + \|f\| + \epsilon^{-1}\|[\tau\cdot n]\| + \epsilon^{-1/2}\|[v]\|
-\]
-We will bound $\|\left(v,\tau\right)\|_V$ for all $\left(v,\tau\right)$ satisfying \eqref{adjoint} by first decomposing $\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right)$, where $\left(v_1,\tau_1\right)$ satisfies our adjoint equation \eqref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and
-\begin{align*}
-f &= 0\\
-g&= \div \tau - \beta\cdot \grad v,
-\end{align*} 
-and $\left(v_2,\tau_2\right)$ satisfies \eqref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and 
-\begin{align*}
-g &= 0\\
-f &= \epsilon^{-1}\tau + \grad v.
-\end{align*}
-We note that, if $v_2$ satisfies $n\cdot \grad v_2 = n\cdot f$, by definition of $f$ and $v_2$,
-\begin{align*}
-\tau_2 \cdot n &= \epsilon n\cdot f - \epsilon n\cdot \grad v_2 = 0, \quad x\in \Gamma_- \cup \Gamma_0
-\end{align*}
-By construction, $\left(v_0,\tau_0\right)$ must satisfy \eqref{adjoint} with $f=g=0$, with jumps
-\begin{align*}
-[v_0] &= [v], \quad x\in \Gamma_h^0\\
-[\tau_0 \cdot n] &= [\tau \cdot n], \quad x\in \Gamma_h^0.
-\end{align*}
-By $\left(v_0,\tau_0\right) = \left(v,\tau\right) - \left(v_1,\tau_1\right) - \left(v_2,\tau_2\right)$, $\left(v_0,\tau_0\right)$ must satisfy boundary conditions
-\begin{align*}
-v_0 &= v, \quad x\in \Gamma_+\\
-\tau_0 \cdot n &= \tau \cdot n, \quad x\in \Gamma_-\cup \Gamma_0.
-\end{align*}
-Robustly bounding $\|\left(v,\tau\right)\|_V$ from above reduces to robustly bounding each component 
-\[
-\|\left(v_{0},\tau_{0}\right)\|_V, \|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|g\| + \|f\| + \epsilon^{-1}\|[\tau\cdot n]\| + \epsilon^{-1/2}\|[v]\|
-\]
-%\begin{align*}
-%\|\left(\tau, v\right)\|_{V}^2 &= \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2 \\
-%& \lesssim \|g\| + \|f\| + \epsilon^{-1}\|[\tau\cdot n]\| + \epsilon^{-1/2}\|[v]\|
-%\end{align*}
-\begin{itemize}
-\item \textbf{Bound on $\|\left(v_{0},\tau_{0}\right)\|_V$}
-
-Lemma 3 gives control over $\epsilon\|\grad v_0\| + \frac{1}{\epsilon}\|\tau_0\|$ through
-\[
-\|\grad v_0\| = \frac{1}{\epsilon}\|\tau_0\| \lesssim \frac{1}{\epsilon} \| [\tau_0\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v_0]\|_{\Gamma_h^0 \cup \Gamma_+} = \frac{1}{\epsilon} \| [\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v]\|_{\Gamma_h^0 \cup \Gamma_+}
-\]
-Lemma 4.2 of \cite{analysisDPG} gives us the Poincare inequality for discontinuous functions
-\[
-\|v_0\| \lesssim \|\grad v_0\| + \|[v]\|
-\]
-%Since $f=0$, by Lemma 2, $\|\beta\cdot \grad v_0\|  \lesssim \|g\| = 0$.  
-Since $g = 0$, $\| \div \tau_0\| = \|\beta\cdot \grad v_0\|\lesssim \|\grad v_0\|$, which we have bounded previously.
-
-\item \textbf{Bound on $\|\left(v_{1},\tau_{1}\right)\|_V$}
-
-%Given $\tau_1 \in H({\rm div};\Omega)$, $v\in H^1(\Omega)$, with boundary conditions \eqref{bc_1} and \eqref{bc_2}, $\frac{1}{\epsilon} \| [\tau_0\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v_0]\|_{\Gamma_h^0 \cup \Gamma_+}=0$.
-With $f = 0$, Lemma 2 provides the bound
-\[
-\|\beta \cdot \grad v_1 \| \lesssim \| g\|
-\]
-Noting that $\div \tau_1 = g+\beta\cdot \grad v_1$ gives $\|\div \tau_1 \| \lesssim \|g\|$ as well.  Lemma 1 gives
-\[
-\epsilon \|\grad v_1\|^2 + \|v_1\|^2 \lesssim \|g\|^2
-\]
-and noting that $\epsilon^{-1/2}\tau_1 = \epsilon^{1/2}v_1$ gives $\epsilon\|\grad v_1\|^2 = \epsilon^{-1}\|\tau_1\|^2 \lesssim \|g\|^2$ as well.
-
-\item \textbf{Bound on $\|\left(v_{2},\tau_{2}\right)\|_V$}
-
-Lemma 1 provides
-\[
-\epsilon \|\grad v\|^2 + \|v\|^2 \lesssim  \epsilon \| f\|^2 \leq \|f\|^2
-\]
-We have $\epsilon^{-1}\tau = f - \grad v$, so $\epsilon^{-1} \|\tau\| \lesssim \|f\| + \|\grad v\|$.
-Lemma 1 implies $\|\grad v\|^2  \lesssim  \| f\|^2$, so for $\epsilon \leq 1$, we control $\epsilon^{-1/2}\|\tau\| \leq \epsilon^{-1}\|\tau\| \lesssim \|f\|$.
-The remaining terms can be bounded by noting that, with $g = 0$, $\|\div \tau_2\| = \|\beta\cdot \grad v_2\| \lesssim \|\grad v_2\| \lesssim \|f\| $.
-\end{itemize}
-\end{proof}
-
-\subsubsection{Energy norm equivalence (bound from above)}
-
-We have shown the robust bound of a norm on $U$ by energy error; for a full equivalence statement, we require a bound on the energy norm by some norm on $U$.
-By the duality of the energy and test norm, this is equivalent to bounding the test norm from below, using the test norm induced by the norm on $U$ bounding the energy norm.
-\begin{lemma}
-
-(Bound from above) For $\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U$,
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E \lesssim \|u\| + \frac{1}{\sqrt{\epsilon}}\left(\|\sigma\| + \|\widehat{u}\|+ \|\widehat{u}\|\right)
-\]
-
-\end{lemma}
-\begin{proof}
-For any norm on $U$ of the form
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,*} = \|u\| + C_2 \|\sigma\| + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|,
-\]
-the induced test norm is  
-\begin{align*}
-\| \left(\tau,v\right) \|_{V,*} &= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E} \\
-& = \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle + \langle \widehat{f}_n, \left[v\right] \rangle
-}{\|u\| + C_2 \|\sigma\| + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|} \\
-&\lesssim \|g\| + \frac{1}{C_2}\|f\| + \sup_{\widehat{u},\widehat{f}_n \neq 0}\frac{\langle \left[\tau_n\right], \widehat{u} \rangle + \langle \widehat{f}_n, \left[v\right] \rangle}{C_3\|\widehat{u}\| + C_4\|\widehat{f}_n\|}
-\end{align*}
-where $f$ and $g$ are again the loads of the adjoint problem \eqref{adjoint}.  By the triangle inequality, 
-\begin{align*}
-\epsilon \|f \|^2 &\leq \epsilon^{-1} \| \tau\|^2 + {\epsilon} \|\grad v\|^2 \lesssim \| \left(\tau,v\right)\|_V^2\\
-\|g \| &\leq \|\div \tau\| +  \|\beta \cdot \grad v\| \lesssim \| \left(\tau,v\right)\|_V
-\end{align*}
-We estimate the supremum by following \cite{DPGrobustness}; we begin by choosing $\eta \in H({\rm div}; \Omega)$, $w\in H^1(\Omega)$, such that $\left.\left(\eta-\beta w \right)\cdot n\right |_{\Gamma_+} = 0$ and $\left.w\right |_{\Gamma_-\cup\Gamma_0} = 0$, and integrating the boundary pairing by parts to get
-\begin{align*}
-\langle [\tau\cdot n],w\rangle + \langle [v],\left(\eta - \beta w\right)\cdot n\rangle &\lesssim \|\left(\tau,v\right)\|_V\frac{1}{\sqrt{\epsilon}}\left(\|\eta\| + \|w\|\right)\\
-%\langle [\tau\cdot n],w\rangle + \langle [v],\left(\eta - \beta w\right)\cdot n\rangle 
-&\lesssim \|\left(\tau,v\right)\|_V\frac{1}{\sqrt{\epsilon}}\left(\|\eta-\beta w\| + \|w\|\right)
-\end{align*}
-since $\|\eta\| = \|\eta - \beta w + \beta w\| \leq \|\eta - \beta w\| + \|\beta w\| \lesssim \|\eta-\beta w\| + \|w\|$.  Dividing through and taking the supremum gives
-\[
-\sup_{w,\eta \neq 0} \frac{\langle[\tau\cdot n],w\rangle + \langle [v],\left(\eta - \beta w\right)\cdot n\rangle}{\left(\|\eta-\beta w\| + \|w\|\right)} \lesssim \|\left(\tau,v\right)\|_V\frac{1}{\sqrt{\epsilon}}
-\]
-To finish the proof, define $\rho \in H^{1/2}(\Gamma_h)$ and $\phi \in H^{-1/2}(\Gamma_h)$ such that $\rho = \left.w\right|_{\Gamma_h}$ and $\phi = \left.(\eta-\beta w)\cdot n\right|_{\Gamma_h}$, and note that
-\begin{align*}
-\sup_{\rho,\phi \neq 0} \frac{\langle [\tau\cdot n],\rho\rangle + \langle [v],\phi \rangle}{\|\rho\|+\|\phi\|} &= \sup_{w,\eta \neq 0} \frac{\langle [\tau\cdot n],w\rangle + \langle [v],\left(\eta - \beta w\right)\cdot n\rangle}{ \|w\|+\|\eta-\beta w\|}
-\end{align*}
-
-Together, the bounds on $\|g\|$ and $\|f\|$ imply $\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{E} \lesssim \left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,*}$ for $C_2 = C_3 = C_4 = \frac{1}{\sqrt{\epsilon}}$.
-\end{proof}
-
-%In \cite{DPGrobustness}, the quasi-optimal test norm was shown to induce an energy norm that is bounded from both above and below by norms on $U$ that do not grow in magnitude with $\epsilon^{-1}$.
 

### 2012-04-02 docs/NewBCRobustness_paper/paper.tex
began restructuring of paper, added to bibliography
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@415 36274a68-8941-4c93-80ef-affaed5139da

@@
 
-\textcolor{red}{add bit about residual-based stabilization terms and test functions}
+Traditionally, instability/loss of robustness has been dealt with using residual-based stabilization.
+Given some variational form $b(u,v) - l(v)=0$, the problem is modified by adding to the bilinear form a factor of the residual $r(v) = b(u,v) - l(v)=0$, scaled by a stabilization constant $\tau$.
+The most well-known example of this is the streamline-upwind Petrov-Galerkin method, which is a stabilized method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.
+
+The addition of residual-based stabilization terms can also be interpreted as a modification of the test functions - in other words, stabilization can be achieved by changing the test space for a given problem.
+This idea can be generalized under the idea of \textit{optimal test functions}.
+
+%\textcolor{red}{add bit about SUPG/residual-based stabilization terms and test functions}
 
@@
 \[
-b\left(\left(\widehat{u},u\right),v\right) - l(v) = \langle \widehat{u}, v \rangle - (u,A^*v) - (f,v)
-\]
-where $A^*$ is the formal adjoint resulting from integration by parts.
-
-\subsection{Optimal and quasi-optimal test norms}
+b\left(\left(\widehat{u},u\right),v\right) - l(v) = \langle \widehat{u}, [v] \rangle - (u,A^*v) - (f,v) = 0
+\]
+where $A^*$ is the formal adjoint resulting from integration by parts, and $[v]$ is the jump of $v$ across element boundaries.
+
+\subsection{Induced norms}
 
@@
 
-Under the assumption of injectivity of the adjoint of our variational operator $B$, we can define the \textit{optimal test norm} 
-\[
-\|v\|_{\rm opt} = \sup_{u\in U}\frac{b(u,v)}{\|u\|_U}
-\]
-If the solution is in $U$, then choosing $\|v\|=\|v\|_{\rm opt}$ implies $\|u\|_E = \|u\|_U$.
-The proof is simple; we have by definition that $b(u,v) \leq \|u\|_U\|v\|_V$.
-The reverse $b(u,v) \leq \|u\|_U\|v\|_V$ is proved by
-\[
-\inf_{u\in U} \frac{\|u\|_E}{\|u\|_U} = \inf_{u\in U} \sup_{v\in V}\frac{b(u,v)}{\|v\|_V\|u\|_U} = \inf_{v\in V} \sup_{u\in U}\frac{b(u,v)}{\|v\|_V\|u\|_U} = \inf_{v\in V} \frac{\|v\|_V}{\|v\|_V} = 1
+An important relationship is the duality of the energy norm and test norm; under the assumption of injectivity of the adjoint of our variational 	operator $B$, for any choice of energy norm on $U$, the test norm $\|v\|_V$ inducing it can be recovered via duality
+\begin{align}
+\| v \|_{V,U} = \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_U} \label{norm_duality}
+\end{align}
+If the solution is in $U$, then choosing $\|v\|=\|v\|_{V,U}$ implies $\|u\|_E = \|u\|_U$.
+The proof is simple; we have by definition that $b(u,v) \leq \|u\|_U\|v\|_{V,U}$.
+The reverse $b(u,v) \leq \|u\|_U\|v\|_{V,U}$ is proved by
+\[
+\inf_{u\in U} \frac{\|u\|_E}{\|u\|_U} = \inf_{u\in U} \sup_{v\in V}\frac{b(u,v)}{\|v\|_{V,U}\|u\|_U} = \inf_{v\in V} \sup_{u\in U}\frac{b(u,v)}{\|v\|_{V,U}\|u\|_U} = \inf_{v\in V} \frac{\|v\|_{V,U}}{\|v\|_{V,U}} = 1
 \]
 where we're able to switch the order of $\inf$ and $\sup$ due to the injectivity of $B$ (see  \cite{BabuskaEquivBrezzi}).
-This is the ideal test norm; given any particular norm $\|u\|_U$, DPG under the optimal test norm will return the best finite element approximation in that norm.
-
-The norm $\|v\|_{\rm opt}$ is non-localizable, however - the inversion of the inner product corresponding to this norm is global, and solving for optimal test functions under this optimal norm will result in global problems as well, due to the coupling given by the boundary terms in our bilinear form.
-In practice, an approximation is made by removing such boundary terms and replacing them with scaled $L^2$ norms of the field variables, producing so-called \textit{quasi-optimal} test norms.
+
+As a consequence of \eqref{norm_duality}, given two norms on $U$, $\|\cdot\|_{U_1}$ and $\|\cdot\|_{U_2}$, if $\|u\|_{U_1} \leq \|u\|_{U_2}$, we have the equivalent statement
+\begin{align*}
+\| v \|_{V,U_1} = \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_{U_1}} \geq  \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_{U_2}} = \| v \|_{V,U_2}
+\end{align*}
+In other words, showing an inequality between two norms on $U$ is equivalent to showing the reverse inequality between the respective induced norms on $V$.
+
+\subsection{Optimal and quasi-optimal test norms}
+
+The duality between test norm and variational form holds for any particular variational form, though it is often difficult to determine analytically the form of $\|v\|_{V,U}$.
+However, for the DPG ultra-weak formulation, there is an important test norm that results from a specific induced norm on $U$.
+Define the norm on $U$
+\[
+\|u\| = C_1\|u\|_{L^2} + C_2\|\widehat{u}\|
+\]
+where the norm on $\widehat{u}$ is taken to be the minimum energy extension norm
+\[
+\|\widehat{u}\| = \inf_{w\in V, \left.w\right|_{\Gamma_h}=\widehat{u}} \|w\|_V
+\]
+Then, the induced test norm is 
+\begin{align*}
+\|v\|_{\rm opt} &= \sup_{u,\widehat{u}} \frac{\langle \widehat{u}, [v] \rangle - (u,A^*v)}{C_1\|u\|_{L^2} + C_2\|\widehat{u}\|} \\
+&\leq \frac{1}{C_1}\sup_{u} \frac{(u,A^*v)}{\|u\|_{L^2}} + \frac{1}{C_2}\sup_{\widehat{u}} \frac{\langle \widehat{u}, [v] \rangle}{\|\widehat{u}\|}\\
+&= \frac{1}{C_1}\|A^*v\|_{L^2} + \frac{1}{C_2}\sup_{\widehat{u}} \frac{\langle \widehat{u}, [v] \rangle}{\|\widehat{u}\|}
+\end{align*}
+where we have used the Cauchy-Schwarz inequality, and eliminated the supremum by noting the inequality is tight.  We define $\|u\|_{\rm opt}$ as such a norm with $C_1=C_2 = 1$,
+\[
+\|u\|_{\rm opt} = \|u\|_{L^2} + \|\widehat{u}\|.
+\]
+This is, in some sense, the ideal or ``optimal" test norm; given any particular norm $\|u\|_U$, DPG under the optimal test norm will return the best finite element approximation in both field and flux variables, independently of any parameters
+
+The norm $\|v\|_{\rm opt}$ is non-localizable, however - the above ``optimal" test norm is induced by an inner product; however, this inner product is a global one due to the presence of the jump terms.
+Solving for optimal test functions under this optimal norm through inversion of this inner product  will result in expensive global problems, making this an impractical norm to work with.
+
+In practice, an approximation is made by removing such boundary terms and replacing them with scaled $L^2$ norms of the field variables, producing so-called \textit{quasi-optimal} test norm
+\[
+\|v\|_{\rm qopt} \coloneqq \|A^*v\|_{L^2} + \alpha \|v\|_{L^2}
+\]
+where $\alpha \in \mathbb{R}$ is chosen to complete the seminorm defined by $\|A^*v\|_{L^2}$.
+This optimal test norm has been shown to induce a well-posed DPG method for any well-posed ultra-weak formulation in the context of Friedrichs' systems of equations \cite{DPGFriedrichs}.
+
 The DPG method is currently being analyzed for both acoustic and elastic waves in context of the Helmholtz equation and equations of linear elasticity.
 Numerically, DPG appears to provide a ``pollution-free" method without phase error for these problems under the ``quasi-optimal" test norm with a specific scaling of the regularizing $L^2$ terms \cite{DPG4}.
-Similar results have also been obtained with the quasi-optimal test norm in the context of the elasticity \cite{DPGElas} and linearized Stokes equations \cite{Camellia}.
+Similar results have also been obtained with the quasi-optimal test norm in the context of the elasticity \cite{DPGElas} and linear Stokes equation \cite{Camellia}.
 
@@
 
+We can now translate the above abstract language to a concrete model problem in computational fluid dynamics.
 We consider the model convection-diffusion problem on domain $\Omega$ with boundary $\Gamma$
@@
 
-Given the boundary conditions on $\widehat{u}$ and $\widehat{f}_n$, we can now also define the trace norms as (canonical) minimum energy extension norms 
+Given the boundary conditions on $\widehat{u}$ and $\widehat{f}_n$, we can now also define the trace norms as (canonical) minimum energy extension norms (taking into account the respective lifts of $\widehat{u}$ and $\widehat{f}_n$ on $\Gamma_+$ and $\Gamma_-$, respectively)
 \begin{align*}
@@
 %We will denote $\|\cdot \| = \|\cdot\|_{L^2}$ for all functions defined on $\Omega_h$. 
-As $\tau \in H({\rm div},\Omega_h)$ and $v \in H^1(\Omega_h)$, we will construct norms on $v$ and $\tau$ using some combination of terms which are equivalent to the canonical broken $H^1(\Omega_h) \times H({\rm div},\Omega_h)$ norm
-\[
-\|\left(\tau,v\right)\|_{H^1(\Omega_h) \times H({\rm div},\Omega_h)} = \|v\|_{L^2(\Omega_h)}^2 + \|\grad v\|_{L^2(\Omega_h)}^2  + \|\tau\|_{L^2(\Omega_h)}^2 + \|\div \tau\|_{L^2(\Omega_h)}^2
-\]
-The exact norms that we will place on $V$ will be determined later.
-
-The boundary norms on $\Gamma_h$ for $v$ and $\tau$ are defined by duality from the bilinear form
+As $\tau \in H({\rm div},\Omega_h)$ and $v \in H^1(\Omega_h)$, we will construct norms on $v$ and $\tau$ using some combination of terms which are equivalent to the canonical $H^1(K) \times H({\rm div},K)$ norm over a single element
+\[
+\|\left(\tau,v\right)\|_{H^1(K) \times H({\rm div},K)} = \|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2  + \|\tau\|_{L^2(K)}^2 + \|\div \tau\|_{L^2(K)}^2
+\]
+The squared norm over the entire triangulation $\Omega_h$ is defined to be the squared sum of contributions from each element.  The exact norms that we will place on $V$ will be determined later.
+
+The norms on the skeleton $\Gamma_h$ for $v$ and $\tau$ are defined by duality from the bilinear form
 \begin{align*}
@@
 
-For convection-diffusion, the quasi-optimal norm is 
+For convection-diffusion, the quasi-optimal test norm is 
 \[
@@
 for some choice of constants $C_1$ and $C_2$.  
-We note that the optimal test norm will automatically guarantee the robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.
+%We note that the optimal test norm will automatically guarantee the robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.  
 However, use of this norm for the convection-diffusion problem is difficult - the variational problem for optimal test functions using the quasi-optimal test norm is equivalent to a reaction-diffusion system \cite{DBLP:journals/procedia/NiemiCC11}.
-Transforming the problem to the reference element reveals that will induce strong boundary layers of width $\epsilon/h^2$ (in comparison, in Helmholtz and wave propagation problems, the mesh size tends to be on the order of the wavelength/singular perturbation parameter, resulting in smooth optimal test functions that are much easier to approximate over the reference element).
-As the relevant range of $\epsilon$ for physical problems is $1e-7$, solving on partially under-resolved meshes is unavoidable.
+Transforming the problem to the reference element reveals that the inversion of the inner product associated with the optimal test norm will induce strong boundary layers of width $\epsilon/h^2$ in the optimal test functions.
+In comparison, in Helmholtz and wave propagation problems, the mesh size tends to be on the order of the wavelength/singular perturbation parameter, resulting in smooth optimal test functions that are much easier to approximate over the reference element.
+As the relevant range of $\epsilon$ for physical problems is $1e-7$, solving on partially under-resolved meshes is unavoidable, and the approximability of the optimal test functions must be addressed to take advantage of the properties of DPG.
+
+In the application of DPG in \cite{DPG1,DPG2,DPG3,DPG4}, the approximation of optimal test functions is done using the enriched test space $V = \cup_{K} P^{p+\Delta p}(K)$, where $p$ is the polynomial order of the trial space on a given element $K$.
+In other words, optimal test functions are approximated element-by-element using polynomials whose order is $\Delta p$ more than the local order of approximation.
+Under this scheme, the approximation of optimal test functions is tied to the effectiveness of the $p$-method.
+Unfortunately, for problems with boundary layers (including the approximation of optimal test functions under the quasi-optimal test norm), the $p$-method performs very poorly.
 
 Resolving such boundary layers for an underresolved mesh has been investigated numerically using specially designed (Shishkin) subgrid meshes by Niemi, Collier, and Calo in \cite{DBLP:journals/procedia/NiemiCC11}.
-However, even with Shishkin meshes, the approximation of optimal test functions under the quasi-optimal norm is difficult and far more expensive than approximation test functions using a simple $p$-enriched space for $V$.
+However, even with Shishkin meshes, the approximation of optimal test functions under the quasi-optimal norm is difficult and far more expensive and complex to implement than approximation of test functions using a simple $p$-enriched space for $V$.
 We approach this from a different perspective, looking instead for robust test norms which do not induce boundary layers in the approximation of optimal test functions, and do so by formulating a general approach to analyzing the behavior of DPG under a given test norm.
@@
 
-\subsection{Adjoint stability}
-
-\textcolor{red}{introduce the three lemmas}
-An important relationship is the duality of the energy norm and test norm; for any choice of energy norm, the test norm $\|v\|_V$ inducing it can be recovered via duality
+\section{Strategy for proving robustness under a given test norm}
+
+The main goal of this paper is to derive a test norm that \textit{does not induce boundary layers in the optimal test functions}, but still induces an energy norm \textit{that does not lose robustness as $\epsilon \rightarrow 0$}.
+The first condition is satisfied by first decoupling norms on $\left(\tau,v\right)$ such that
+\[
+\left\|\left(\tau,v\right)\right\|_V = \|\tau\|_{H({\rm div},\Omega_h)} +  \|v\|_{H^1(\Omega_h)}.
+\]
+Ensuring that each term $\|\tau\|_{H({\rm div},\Omega_h)}$ and $ \|v\|_{H^1(\Omega_h)}$ is of the same order will allow for smooth solutions (under some assumptions on $\beta$).  
+\textcolor{red}{Why are we allowed to have $\beta\cdot \grad v$ of order 1 while we have other terms of order $O({\rm Pe})$?  Why does this term not induce boundary layers?}
+
+Showing the second condition on robustness is equivalent to showing the robust equivalence of the $L^2$ error of the solution in a norm on $U$ (that does not grow as $\epsilon\rightarrow 0$) times the error in the energy norm
+\[
+\left(\|u\| + \|\sigma\| + \|\widehat{u}\| + \|\widehat{f}_n\|\right) \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left(\|u\| + \|\sigma\| + \|\widehat{u}\| + \|\widehat{f}_n\|\right)
+\]
+where $\lesssim$ denotes a bound by a constant that will not grow as $\epsilon \rightarrow 0$.  
+%$\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_U \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E$.  
+Our strategy for proving such a bound is broken down into three parts.
+
+\subsection{Translate equivalence norms on $U$ to norms on $V$}
+
+We begin with a given norm on $U$
+\[
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = C_1 \|u\| + C_2 \|\sigma\| + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|.
+\]
+By \eqref{norm_duality}, the duality of test norm and energy norm, a norm of this form induces the test norm
+\begin{align*}
+\|\left(v,\tau\right)\|_{V,U} &= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{C_1\|u\| + C_2\|\sigma\| + C_3\epsilon\|\widehat{u}\|+ C_4\sqrt{\epsilon}\|\widehat{u}\|}\\
+&= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup \Gamma_h^0}}{C_1\|u\| + C_2\|\sigma\| + C_3\epsilon\|\widehat{u}\|+ C_4\sqrt{\epsilon}\|\widehat{u}\|}\\
+& \leq \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle [\tau\cdot n], \widehat{u}\rangle}{\|\widehat{u}\|} +\frac{1}{C_4}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, [v]\rangle}{\|\widehat{f}\|}
+\end{align*}
+where $f$ and $g$ are defined as 
+\begin{align*}
+g &\coloneqq \div \tau - \beta \cdot \grad v\\
+f &\coloneqq \epsilon^{-1}\tau + \grad v
+\end{align*}
+which, by definition of the boundary norms, gives the characterization of the induced test norm 
+\[
+\|\left(v,\tau\right)\|_{V,U} \leq \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\|[\tau\cdot n]\| + \frac{1}{C_4}\|[v]\|
+\]
+\textcolor{red}{is this an equality?
+Is the inequality attainable, and thus attained in the supremum?} We can now use this relation to compare two different norms on $U$ by comparing their induced norms on $V$.
+Additionally, showing a robust inequality between two norms on $U$ is similarly equivalent to showing the robust reverse inequality in the induced norms on $V$.
+
+\subsection{Decomposition into analyzable components}
+
+After reducing the problem of comparing norms on $U$ to comparing norms on $V$, we break the analysis of $\left(\tau,v\right) \in V$ into the analysis of subproblems.  Define the decomposition
+\[
+\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right),
+\]
+where $\left(v_1,\tau_1\right)$ satisfies 
+\begin{align*}
+\epsilon^{-1}\tau_1 + \grad v_1 &= 0\\
+\div \tau_1 - \beta\cdot \grad v_1 &=  \div \tau - \beta\cdot \grad v = g,
+\end{align*} 
+Likewise, we define $\left(v_2,\tau_2\right)$ as satisfying
+\begin{align*}
+\epsilon^{-1}\tau_2 + \grad v_2 &= \epsilon^{-1}\tau + \grad v = f\\
+\div \tau_2 - \beta\cdot \grad v_2 &= 0
+\end{align*}
+We will additionally require both $\left(\tau_1,v_1\right)$ and $\left(\tau_2,v_2\right)$ to come from $H({\rm div}, \Omega)\times H^1(\Omega)$, and to satisfy boundary conditions
+\begin{align*}
+\tau_i\cdot n &= 0, \quad x \in \Gamma_-\\
+v_i &= 0, \quad x \in \Gamma_+
+\end{align*}
+for $i = 1, 2$.
+The selection of $H({\rm div}, \Omega)\times H^1(\Omega)$ conforming test functions satisfying the specific above boundary conditions removes the contribution of the jump terms over the skeleton $\Gamma_h$ in the bilinear form, allowing us to bound components of the induced test norm separately from each other.
+
+Finally, by construction, $\left(v_0,\tau_0\right)$ must satisfy 
+\begin{align*}
+\epsilon^{-1}\tau_0 + \grad v_0 &= 0\\
+\div \tau_0 - \beta\cdot \grad v_0 &= 0
+\end{align*}
+with jumps
+\begin{align*}
+[v_0] &= [v], \quad x\in \Gamma_h^0\\
+[\tau_0 \cdot n] &= [\tau \cdot n], \quad x\in \Gamma_h^0.
+\end{align*}
+By $\left(v_0,\tau_0\right) = \left(v,\tau\right) - \left(v_1,\tau_1\right) - \left(v_2,\tau_2\right)$, $\left(v_0,\tau_0\right)$ must satisfy boundary conditions
 \begin{align}
-\| v \|_V = \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_E} \label{norm_duality}
+v_0 &= v, \quad x\in \Gamma_+ \label{bc_1}\\
+\tau_0 \cdot n &= \tau \cdot n, \quad x\in \Gamma_-\cup \Gamma_0. \label{bc_2}
 \end{align}
-The proof for this is identical to proving $\|u\|_E = \|u\|_U$ for the choice of the optimal test norm.
-
-As a consequence of \eqref{norm_duality}, assume an energy norm $\left\| u \right\|_{E,1}$ is induced by a given test norm $\| v  \|_{V,1}$.
-To bound $\|\cdot\|_E$ robustly from above or below by a given norm $\left\| u \right\|_{U,2}$ on $U$ now only requires the robust bound in the opposite direction of $\| v \|_{V,1}$ by $\|v\|_{V,2}$.
-
-We will use the notation $\lesssim$ to denote an $\epsilon$-independent bound.
+
+We have now decomposed any arbitrary test function $\left(\tau,v\right)$ into a single discontinuous portion and two conforming portions.
+Showing robust equivalence of $\|\left(v,\tau\right)\|_V$ with another norm $\|\cdot \|_{?}$ on $V$ reduces to showing robust equivalence of each component
+\[
+C_1\|\left(\tau,v\right)\|_{?} \lesssim \|\left(v_{0},\tau_{0}\right)\|_V, \|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim C_2\|\left(\tau,v\right)\|_{?}
+\]
+Bounding $\|\left(\tau_0,v_0\right)\|$ requires the use of techniques and decompositions first developed in \cite{analysisDPG} and adapted to convection-diffusion in \cite{DPGrobustness}.
+However, due to the conforming nature of $\left(\tau_1,v_1\right)$ and $\left(\tau_2,v_2\right)$, the bound from above of test functions $\|\left(\tau_{1,2},v_{1,2}\right)\| \leq C\|g\|$ is reduced to proving classical error estimates for the adjoint equation
+\begin{align*}
+\epsilon^{-1}\tau + \grad v &= f\\
+\div \tau - \beta\cdot \grad v &=  g,
+\end{align*} 
+for data $f, g\in L^2({\Omega_h})$ and boundary conditions $\left.\tau\cdot n\right|_{\Gamma_-} = 0$ and $\left.v\right|_{\Gamma_+} = 0$
+
+\subsection{Deriving adjoint estimates}
+
+The final step to constructing a robust, localizable test norm on $V$ that does not generate boundary layers is to derive adjoint stability estimates on $\tau$ and $v$ in terms of localizable normed quantities.
+These normed quantities will create ``building-blocks" through which we can construct test norms, where each building block will correspond roughly to the control of $\|u\|_{L^2}$, $\|\sigma\|_{L^2}$, $\|\widehat{u}\|$, or $\|\widehat{f}_n\|$.
+
+We introduce first the bounds derived; the proofs will be given later.  Under specific assumptions on $\beta$, we have the robust bounds
+\begin{itemize}
+\item For $f=0$ and $v \in H^1(\Omega_h)$, satisfying boundary conditions \eqref{bc_1} and \eqref{bc_2}
+\begin{align*}
+\|\beta \cdot \grad v \| &\lesssim \| g\| 
+\end{align*}
+\item For $v \in H^1(\Omega_h)$ and satisfying boundary conditions \eqref{bc_1} and \eqref{bc_2}, and for sufficiently small $\epsilon$
+\begin{align*}
+\epsilon \|\grad v\|^2 + \|v\|^2 &\lesssim \|g\|^2 + \epsilon \| f\|^2
+\end{align*}
+\item For $f=g=0$, 
+\begin{align*}
+\|\grad v\| = \frac{1}{\epsilon}\|\tau\| &\lesssim \frac{1}{\epsilon} \| [\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v]\|_{\Gamma_h^0 \cup \Gamma_+}
+\end{align*}
+\end{itemize}
+Together, these estimates will be sufficient to complete the first step and demonstrate bounds on induced test norms for different scalings of norms on $U$.
+
+\section{Actually proving things}
 
@@
 \]
-where $\|\cdot \|_{w+\epsilon}$ is a weighted $L^2$ norm, where the weight $w \in (0,1)$ is required to vanish on $\Gamma_-$.
+where $\|\cdot \|_{w+\epsilon}$ is a weighted $L^2$ norm, where the weight $w \in (0,1)$ is required to vanish on $\Gamma_-$ and satisfy $\grad w = O(1)$.
 
@@
 \end{align*}
-If we can show $\|\left(\tau, v\right)\|_V \lesssim \| u \|_{L^2}$ for any choice of $u \in L^2$, dividing through by $\|u\|_{L^2}$ gives
-\[
-\|u\|_{L^2} \lesssim \|u\|_E
-\]
-which results in in robust control of the $L^2$ error by the error in the energy norm, in which DPG is optimal.
-
+At minimum, we want $\|u\|_{L^2} \lesssim \|u\|_E$, which requires 
+\[
+\|\left(\tau, v\right)\|_V \lesssim \| u \|_{L^2}
+\]
+for any choice of $u \in L^2$ (dividing through by $\|u\|_{L^2}$ gives the desired result).
+This can be considered a ``sanity check"; at the minimum, we at least want control over the behavior of the single field variable $u$.
 However, we are unable to prove this in the case of Dirichlet boundary conditions.
+Consider the convection-diffusion problem in 1D
+
+\textcolor{red}{add 1D issue with control over $\|v'\|$ here}
+
 Intuitively, the adjoint problem is similar to the primal problem with the direction of inflow reversed, such that the inflow becomes the outflow, and outflow inflow.
@@
 This test norm is implied by certain norm ``building blocks"; stability analysis of the adjoint equation allows us to bound from above norms and seminorms on $v$ and $\tau$ by $\|f\|_{L^2}$ and $\|g\|_{L^2}$ in ways that do not grow as $\epsilon \rightarrow 0$, and we assemble the test norm as combinations of such norms and seminorms on $v$ and $\tau$.
+
+\textcolor{red}{Move this to after the proof of the streamline gradient lemma.}
 
@@
 \[
-\|\left(\tau, v\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\| + \| \div \tau\| + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|
+\|\left(\tau, v\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2
 \]

### 2012-04-02 docs/NewBCRobustness_paper/paper.tex
committing rewrite (with notes in red for unfinished portions) of the paper
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@416 36274a68-8941-4c93-80ef-affaed5139da

@@
 \]
-Ensuring that each term $\|\tau\|_{H({\rm div},\Omega_h)}$ and $ \|v\|_{H^1(\Omega_h)}$ is of the same order will allow for smooth solutions (under some assumptions on $\beta$).  
+where $\|\tau\|_{H({\rm div},\Omega_h)}$ and $ \|v\|_{H^1(\Omega_h)}$ are both constructed as the sum of norm and seminorms on each respective space.
+Ensuring that each seminorm/normed term is of the same order will allow for smooth solutions (under some assumptions on $\beta$).
+The avoidance of boundary layers in the test norm will be described in more detail in the section detailing numerical experiments.
 \textcolor{red}{Why are we allowed to have $\beta\cdot \grad v$ of order 1 while we have other terms of order $O({\rm Pe})$?  Why does this term not induce boundary layers?}
 
-Showing the second condition on robustness is equivalent to showing the robust equivalence of the $L^2$ error of the solution in a norm on $U$ (that does not grow as $\epsilon\rightarrow 0$) times the error in the energy norm
-\[
-\left(\|u\| + \|\sigma\| + \|\widehat{u}\| + \|\widehat{f}_n\|\right) \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left(\|u\| + \|\sigma\| + \|\widehat{u}\| + \|\widehat{f}_n\|\right)
+Showing the second condition on robustness is equivalent to showing the robust boundedness of the energy error from above and below by norms on $U$ 
+\[
+\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}
 \]
@@
 
-\subsection{Translate equivalence norms on $U$ to norms on $V$}
-
+\subsection{Equate relations between norms on $U$ and norms on $V$}
+\label{sec:strategy1}
 We begin with a given norm on $U$
@@
 \subsection{Decomposition into analyzable components}
+\label{sec:strategy2}
 
@@
 We will additionally require both $\left(\tau_1,v_1\right)$ and $\left(\tau_2,v_2\right)$ to come from $H({\rm div}, \Omega)\times H^1(\Omega)$, and to satisfy boundary conditions
-\begin{align*}
-\tau_i\cdot n &= 0, \quad x \in \Gamma_-\\
-v_i &= 0, \quad x \in \Gamma_+
-\end{align*}
+\begin{align}
+\tau_i\cdot n &= 0, \quad x \in \Gamma_- \label{bc_1}\\
+v_i &= 0, \quad x \in \Gamma_+ \label{bc_2}
+\end{align}
 for $i = 1, 2$.
@@
 We have now decomposed any arbitrary test function $\left(\tau,v\right)$ into a single discontinuous portion and two conforming portions.
-Showing robust equivalence of $\|\left(v,\tau\right)\|_V$ with another norm $\|\cdot \|_{?}$ on $V$ reduces to showing robust equivalence of each component
-\[
-C_1\|\left(\tau,v\right)\|_{?} \lesssim \|\left(v_{0},\tau_{0}\right)\|_V, \|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim C_2\|\left(\tau,v\right)\|_{?}
+Showing the robust bound of $\|\left(v,\tau\right)\|_V$ from above and below (by norms $\|\cdot \|_{V,1}$ and $\|\cdot \|_{V,2}$ on $V$, respectively) reduces to showing the robust bound of each component
+\[
+\|\left(\tau,v\right)\|_{V,1} \lesssim \|\left(v_{0},\tau_{0}\right)\|_V, \|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|\left(\tau,v\right)\|_{V,2}
 \]
 Bounding $\|\left(\tau_0,v_0\right)\|$ requires the use of techniques and decompositions first developed in \cite{analysisDPG} and adapted to convection-diffusion in \cite{DPGrobustness}.
-However, due to the conforming nature of $\left(\tau_1,v_1\right)$ and $\left(\tau_2,v_2\right)$, the bound from above of test functions $\|\left(\tau_{1,2},v_{1,2}\right)\| \leq C\|g\|$ is reduced to proving classical error estimates for the adjoint equation
-\begin{align*}
-\epsilon^{-1}\tau + \grad v &= f\\
-\div \tau - \beta\cdot \grad v &=  g,
-\end{align*} 
-for data $f, g\in L^2({\Omega_h})$ and boundary conditions $\left.\tau\cdot n\right|_{\Gamma_-} = 0$ and $\left.v\right|_{\Gamma_+} = 0$
+However, due to the conforming nature of $\left(\tau_1,v_1\right)$ and $\left(\tau_2,v_2\right)$, the bound from above of test functions $\|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|g\|$ is reduced to proving classical error estimates for the adjoint equations
+\begin{align}
+\epsilon^{-1}\tau + \grad v &= f \label{adjoint1}\\
+\div \tau - \beta\cdot \grad v &=  g, \label{adjoint2}
+\end{align} 
+for any choice of data $f, g\in L^2({\Omega_h})$ and boundary conditions $\left.\tau\cdot n\right|_{\Gamma_-} = 0$ and $\left.v\right|_{\Gamma_+} = 0$
 
 \subsection{Deriving adjoint estimates}
+\label{sec:strategy3}
 
@@
 
-We introduce first the bounds derived; the proofs will be given later.  Under specific assumptions on $\beta$, we have the robust bounds
-\begin{itemize}
-\item For $f=0$ and $v \in H^1(\Omega_h)$, satisfying boundary conditions \eqref{bc_1} and \eqref{bc_2}
-\begin{align*}
-\|\beta \cdot \grad v \| &\lesssim \| g\| 
-\end{align*}
-\item For $v \in H^1(\Omega_h)$ and satisfying boundary conditions \eqref{bc_1} and \eqref{bc_2}, and for sufficiently small $\epsilon$
-\begin{align*}
-\epsilon \|\grad v\|^2 + \|v\|^2 &\lesssim \|g\|^2 + \epsilon \| f\|^2
-\end{align*}
-\item For $f=g=0$, 
-\begin{align*}
-\|\grad v\| = \frac{1}{\epsilon}\|\tau\| &\lesssim \frac{1}{\epsilon} \| [\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v]\|_{\Gamma_h^0 \cup \Gamma_+}
-\end{align*}
-\end{itemize}
-Together, these estimates will be sufficient to complete the first step and demonstrate bounds on induced test norms for different scalings of norms on $U$.
-
-\section{Actually proving things}
-
-\subsubsection{Induced adjoint boundary conditions}
-
-Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
-\[
-\|\left(\tau, v\right)\|_{V,w}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\|_{w+\epsilon} + \| \div \tau\|_{w+\epsilon} + \frac{1}{\epsilon}\|\tau\|_{w+\epsilon}
-\]
-where $\|\cdot \|_{w+\epsilon}$ is a weighted $L^2$ norm, where the weight $w \in (0,1)$ is required to vanish on $\Gamma_-$ and satisfy $\grad w = O(1)$.
-
-\textcolor{red}{Explain how energy norm convergence in $\|u\| + \epsilon \|u'\|$ returns bad results, and the need for an $O(1)$ term in the test norm.}
-
-The need for the weight is intuitively explained by the induced adjoint problem.  The bilinear form for the Dirichlet case is 
-\[
-b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) + \langle \widehat{f}_n, \left[v\right] \rangle
-\]
-We note that 
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup \Gamma_h^0} \\
-&= \| u \|^2_{L^2}
-\end{align*}
-for the specific continuous test functions $\tau$ and $v$ satisfying
-\begin{align*}
-\div \tau - \beta \cdot \grad v &= u \\
-\frac{1}{\epsilon}\tau + \grad v &= 0
-\end{align*}
-with boundary conditions
-\begin{align}
-\tau_n &= 0, \quad x\in \Gamma_-\cup \Gamma_0 \label{eq:adj_bc1}\\
-v &= 0, \quad x\in \Gamma_+ \label{eq:adj_bc2}
-\end{align}
-Choosing a continuous conforming test function $v$ removes the contribution of the term $\langle \widehat{f}_n, \left[v\right] \rangle$ on the mesh skeleton, while the boundary conditions remove the contribution of boundary terms from the bilinear form.
-Then, for this specific choice of $\left(\tau, v\right)$,
-\begin{align*}
-\|u\|_{L^2}^2 &= b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right)}{\|\left(\tau, v\right)\|_V}\|\left(\tau, v\right)\|_V \leq \|u\|_E \|\left(\tau, v\right)\|_V
-\end{align*}
-At minimum, we want $\|u\|_{L^2} \lesssim \|u\|_E$, which requires 
-\[
-\|\left(\tau, v\right)\|_V \lesssim \| u \|_{L^2}
-\]
-for any choice of $u \in L^2$ (dividing through by $\|u\|_{L^2}$ gives the desired result).
-This can be considered a ``sanity check"; at the minimum, we at least want control over the behavior of the single field variable $u$.
-However, we are unable to prove this in the case of Dirichlet boundary conditions.
-Consider the convection-diffusion problem in 1D
-
-\textcolor{red}{add 1D issue with control over $\|v'\|$ here}
-
-Intuitively, the adjoint problem is similar to the primal problem with the direction of inflow reversed, such that the inflow becomes the outflow, and outflow inflow.
-The need for the weight arises due to the presence of the Dirichlet boundary condition on $v$ near the inflow; this induces strong boundary layers at the inflow such that $\grad v \approx O(\epsilon^{-1})$.
-It may be of interest to note that, for sufficiently small $\epsilon$, these issues manifest themselves in numerical experiments as additional refinements near the inflow.
-The presence of the new boundary condition relaxes the outflow boundary condition for the adjoint/dual problem, resulting in stronger stability for the primal problem.
-
-We improve upon the result of Demkowicz and Heuer not by modifying the test norm, but by adopting a new inflow boundary condition, which changes the stability properties of the corresponding adjoint equation.
-Under these new boundary conditions, we can prove robust control over $\|u\|_{L^2}$ using the unweighted version of the test norm in \cite{DPGrobustness}
-\[
-\|\left(\tau, v\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2
-\]
-This test norm is implied by certain norm ``building blocks"; stability analysis of the adjoint equation allows us to bound from above norms and seminorms on $v$ and $\tau$ by $\|f\|_{L^2}$ and $\|g\|_{L^2}$ in ways that do not grow as $\epsilon \rightarrow 0$, and we assemble the test norm as combinations of such norms and seminorms on $v$ and $\tau$.
-
-\textcolor{red}{Move this to after the proof of the streamline gradient lemma.}
-
-\subsection{Equivalence of energy and $U$ norms}
-
-For this analysis, it will be necessary to assume certain conditions on $\beta$.
+We introduce first the bounds derived; the proofs will be given later.
+For this analysis, it will be necessary to assume certain technical conditions on $\beta$.
 For each proof, we require $\beta \in C^2(\bar{\Omega})$ and $\beta, \div \beta = O(1)$.
-Additionally, we will assume some or all of the following assumptions
+Additionally, we will assume some or all of the following assumptions hold
 \begin{align}
@@
 \end{align}
-
-The primary result of this paper is that, if conditions \ref{a_req},\ref{b_req}, and \ref{c_req} are all satisfied, the DPG method provides robust control over the $L^2$ error in $u$ and $\sigma$
+Additionally, as these results are primarily interested in stability and robustness for $\epsilon \ll 1$, we require $\epsilon$ sufficiently small in Lemma \ref{lemma_grad}.
+
+Under proper assumptions on $\beta$, we have the robust bounds
+\begin{itemize}
+\item \textbf{Lemma \ref{lemma_stream}}: For $\beta$ satisfying \eqref{a_req} and \eqref{b_req}, $f=0$ and $v \in H^1(\Omega_h)$, satisfying boundary conditions \eqref{bc_1} and \eqref{bc_2}
+\begin{align*}
+\|\beta \cdot \grad v \| &\lesssim \| g\| 
+\end{align*}
+Similarly, from $\div \tau - \beta\cdot \grad v = g$, we get $\|\div \tau\| \lesssim \|g\|$ as well.  
+\item \textbf{Lemma \ref{lemma_grad}}: For $\beta$ satisfying \eqref{a_req}, and $v \in H^1(\Omega_h)$ satisfying boundary conditions \eqref{bc_1} and \eqref{bc_2}, and for sufficiently small $\epsilon$
+\begin{align*}
+\epsilon \|\grad v\|^2 + \|v\|^2 &\lesssim \|g\|^2 + \epsilon \| f\|^2
+\end{align*}
+\item \textbf{Lemma \ref{lemma_boundary}}: For $\beta$ satisfying \eqref{a_req}, \eqref{c_req}, and $f=g=0$, 
+\begin{align*}
+\|\grad v\| = \frac{1}{\epsilon}\|\tau\| &\lesssim \frac{1}{\epsilon} \| [\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v]\|_{\Gamma_h^0 \cup \Gamma_+}
+\end{align*}
+\end{itemize}
+Together, these estimates will be sufficient to complete the first step and demonstrate bounds on induced test norms for different scalings of norms on $U$.
+
+\section{Relations between energy and $U$ norms}
+
+The primary result of this paper is that, if $\beta$ satisfies \ref{a_req},\ref{b_req}, and \ref{c_req}, the DPG method provides robust control over the $L^2$ error in $u$ and $\sigma$
 \[
@@
 \[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U_1}^2 \coloneqq \|u\|^2 + \|\sigma\|^2 + \epsilon^2\|\widehat{u}\|^2+\epsilon \|\widehat{f}_n\|^2.
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U_1} \coloneqq \|u\| + \|\sigma\| + \epsilon\|\widehat{u}\|+\sqrt{\epsilon} \|\widehat{f}_n\|.
 \]
@@
 \]
-The upper bound on the energy norm appears to depend on $\epsilon^{-1/2}$, implying that for very small $\epsilon$, the $L^2$ error may be much smaller than the energy error.
-However, numerical experiments demonstrate much better results, and suggest that, at least for our examples, $\|u-u_h\|_E \sim \|u-u_h\|_{U}$, implying that the induced energy norm is equivalent to the canonical norms we have chosen on the group variable $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)$.
-
-The proof proceeds in two steps; the bound from below is proven by providing stability estimates for the adjoint problem, while the bound from above of the energy norm is proven separately.
-
-\subsubsection{Bound from below}
-\textcolor{red}{introduce the three lemmas}
-With these three lemmas, we can prove the robust bound of both field variables and fluxes by the energy error.
-In doing so, we take advantage of the fact that, for any choice of energy norm, the test norm $\|v\|_V$ inducing it can be recovered via duality
-\begin{align}
-\| v \|_V = \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_E} \label{norm_duality}
-\end{align}
-The proof for this is identical to proving $\|u\|_E = \|u\|_U$ for the choice of the optimal test norm.
+While the upper bound is robust, we have derived such a bound only by explicitly accounting for a factor of $\epsilon^{-1/2}$ in the bounding norm $\|\cdot \|_{U_2}$.
+This implying that for very small $\epsilon$, the $L^2$ error may be much smaller than the energy error.
+However, \textcolor{red}{explain why this is OK practically.}
+Additionally, numerical experiments demonstrate much better results, and suggest that, at least for our examples, $\|u-u_h\|_E \sim \|u-u_h\|_{U}$, implying that the induced energy norm is equivalent to the canonical norms we have chosen on the group variable $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)$.
+
+\subsection{Bound from below}
+
+We begin by using the strategy outlined in sections~\ref{sec:strategy1}, ~\ref{sec:strategy2}, and ~\ref{sec:strategy3} to prove the robust bound of the $L^2$ error in the field variables by the energy error.
 
@@
 \|u\| + \|\sigma\| + \epsilon\|\widehat{u}\|+ \sqrt{\epsilon}\|\widehat{u}\| \lesssim \left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E
+%\|u\| + \frac{1}{\sqrt{\epsilon}}\|\sigma\| + \epsilon\|\widehat{u}\|+ \sqrt{\epsilon}\|\widehat{u}\| \lesssim \left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E
 \]
@@
 \begin{proof}
-By \eqref{norm_duality}, proving the above result is equivalent to showing 
-\begin{align*}
-\|\left(v,\tau\right)\|_V &\lesssim \frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\|u\| + \|\sigma\| + \epsilon\|\widehat{u}\|+ \sqrt{\epsilon}\|\widehat{u}\|}\\
-& \simeq \|g\| + \|f\| + \epsilon^{-1}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle [\tau\cdot n], \widehat{u}\rangle}{\|\widehat{u}\|} + \epsilon^{-1/2}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, [v]\rangle}{\|\widehat{f}\|},
+By \eqref{norm_duality}, for 
+\begin{align*}
+f &= \epsilon^{-1}\tau + \grad v  \\
+g &=\div \tau - \beta\cdot \grad v,
+\end{align*} 
+we can characterize the test norm for $\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = C_1\|u\| + C_2\|\sigma\| + C_3\|\widehat{u}\|+ C_4\|\widehat{u}\|$ as
+\begin{align*}
+\|\left(v,\tau\right)\|_V &\lesssim \frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{C_1\|u\| + C_2\|\sigma\| + C_3\|\widehat{u}\|+ C_4\|\widehat{u}\|}\\
+& \simeq \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle [\tau\cdot n], \widehat{u}\rangle}{\|\widehat{u}\|} + \frac{1}{C_4}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, [v]\rangle}{\|\widehat{f}\|},
 \end{align*}
@@
 \[
-\|\left(v,\tau\right)\|_V \lesssim \|g\| + \|f\| + \epsilon^{-1}\|[\tau\cdot n]\| + \epsilon^{-1/2}\|[v]\|
-\]
-We will bound $\|\left(v,\tau\right)\|_V$ for all $\left(v,\tau\right)$ satisfying \eqref{adjoint} by first decomposing $\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right)$, where $\left(v_1,\tau_1\right)$ satisfies our adjoint equation \eqref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and
-\begin{align*}
-f &= 0\\
-g&= \div \tau - \beta\cdot \grad v,
-\end{align*} 
-and $\left(v_2,\tau_2\right)$ satisfies \eqref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and 
-\begin{align*}
-g &= 0\\
-f &= \epsilon^{-1}\tau + \grad v.
-\end{align*}
-We note that, if $v_2$ satisfies $n\cdot \grad v_2 = n\cdot f$, by definition of $f$ and $v_2$,
-\begin{align*}
-\tau_2 \cdot n &= \epsilon n\cdot f - \epsilon n\cdot \grad v_2 = 0, \quad x\in \Gamma_- \cup \Gamma_0
-\end{align*}
-By construction, $\left(v_0,\tau_0\right)$ must satisfy \eqref{adjoint} with $f=g=0$, with jumps
-\begin{align*}
-[v_0] &= [v], \quad x\in \Gamma_h^0\\
-[\tau_0 \cdot n] &= [\tau \cdot n], \quad x\in \Gamma_h^0.
-\end{align*}
-By $\left(v_0,\tau_0\right) = \left(v,\tau\right) - \left(v_1,\tau_1\right) - \left(v_2,\tau_2\right)$, $\left(v_0,\tau_0\right)$ must satisfy boundary conditions
-\begin{align*}
-v_0 &= v, \quad x\in \Gamma_+\\
-\tau_0 \cdot n &= \tau \cdot n, \quad x\in \Gamma_-\cup \Gamma_0.
-\end{align*}
+\|\left(v,\tau\right)\|_V \lesssim \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\|[\tau\cdot n]\| + \frac{1}{C_4}\|[v]\|
+\]
+We will bound $\|\left(v,\tau\right)\|_V$ for all $\left(v,\tau\right)$ satisfying \eqref{adjoint} by decomposing $\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right)$ as described in section~\ref{sec:strategy2}.
+%where $\left(v_1,\tau_1\right)$ satisfies our adjoint equation \eqref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and 
+%\begin{align*}
+%f &= 0\\
+%g&= \div \tau - \beta\cdot \grad v,
+%\end{align*} 
+%and $\left(v_2,\tau_2\right)$ satisfies \eqref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and 
+%\begin{align*}
+%g &= 0\\
+%f &= \epsilon^{-1}\tau + \grad v.
+%\end{align*}
+%We note that, if $v_2$ satisfies $n\cdot \grad v_2 = n\cdot f$, by definition of $f$ and $v_2$,
+%\begin{align*}
+%\tau_2 \cdot n &= \epsilon n\cdot f - \epsilon n\cdot \grad v_2 = 0, \quad x\in \Gamma_- \cup \Gamma_0
+%\end{align*}
+%By construction, $\left(v_0,\tau_0\right)$ satisfies adjoint equations \eqref{adjoint1} and \eqref{adjoint2} with $f=g=0$, with jumps
+%\begin{align*}
+%[v_0] &= [v], \quad x\in \Gamma_h^0\\
+%[\tau_0 \cdot n] &= [\tau \cdot n], \quad x\in \Gamma_h^0.
+%\end{align*}
+%By $\left(v_0,\tau_0\right) = \left(v,\tau\right) - \left(v_1,\tau_1\right) - \left(v_2,\tau_2\right)$, $\left(v_0,\tau_0\right)$ must satisfy boundary conditions
+%\begin{align*}
+%v_0 &= v, \quad x\in \Gamma_+\\
+%\tau_0 \cdot n &= \tau \cdot n, \quad x\in \Gamma_-\cup \Gamma_0.
+%\end{align*}
 Robustly bounding $\|\left(v,\tau\right)\|_V$ from above reduces to robustly bounding each component 
 \[
-\|\left(v_{0},\tau_{0}\right)\|_V, \|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|g\| + \|f\| + \epsilon^{-1}\|[\tau\cdot n]\| + \epsilon^{-1/2}\|[v]\|
+\|\left(v_{0},\tau_{0}\right)\|_V, \|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\|[\tau\cdot n]\| + \frac{1}{C_4}\|[v]\|
 \]
@@
 %Since $f=0$, by Lemma 2, $\|\beta\cdot \grad v_0\|  \lesssim \|g\| = 0$.  
-Since $g = 0$, $\| \div \tau_0\| = \|\beta\cdot \grad v_0\|\lesssim \|\grad v_0\|$, which we have bounded previously.
+Since $g = 0$, $\| \div \tau_0\| = \|\beta\cdot \grad v_0\|\lesssim \|\grad v_0\|$, which we now have control over as well.
 
@@
 We have $\epsilon^{-1}\tau = f - \grad v$, so $\epsilon^{-1} \|\tau\| \lesssim \|f\| + \|\grad v\|$.
-Lemma 1 implies $\|\grad v\|^2  \lesssim  \| f\|^2$, so for $\epsilon \leq 1$, we control $\epsilon^{-1/2}\|\tau\| \leq \epsilon^{-1}\|\tau\| \lesssim \|f\|$.
+Lemma~\ref{lemma_grad} implies $\|\grad v\|^2  \lesssim  \| f\|^2$, so for $\epsilon \leq 1$, we control $\epsilon^{-1/2}\|\tau\| \leq \epsilon^{-1}\|\tau\| \lesssim \|f\|$.
 The remaining terms can be bounded by noting that, with $g = 0$, $\|\div \tau_2\| = \|\beta\cdot \grad v_2\| \lesssim \|\grad v_2\| \lesssim \|f\| $.
 \end{itemize}
+
+With these characterizations, we can conclude that $C_1 = C_2 = 1$, $C_3 = \epsilon$, and $C_4 = \epsilon^{1/2}$.  
 \end{proof}
 
-\subsubsection{Bound from above}
+\subsection{Bound from above}
 
@@
 \end{align*}
-where $f$ and $g$ are again the loads of the adjoint problem \eqref{adjoint}.  By the triangle inequality, 
+where $f$ and $g$ are again the loads of the adjoint problem \eqref{adjoint}.  By the triangle inequality, we have the bounds
 \begin{align*}
@@
 %\tau \cdot n = 
-- \epsilon \grad v \cdot n &=f\cdot n, \quad x\in \Gamma_- \label{bc_1}\\ 
-v &= 0, \quad x\in \Gamma_+ \label{bc_2}
+- \epsilon \grad v \cdot n &=f\cdot n, \quad x\in \Gamma_- \label{reducedbc_1}\\ 
+v &= 0, \quad x\in \Gamma_+ \label{reducedbc_2}
 \end{align}
-and treat the cases $f=0$, $g=0$ separately.
-%The above boundary conditions simplify to \eqref{eq:adj_bc1} and \eqref{eq:adj_bc2} when requesting $L^2$ robustness in $u$ ($f=0$); these more general boundary conditions are necessary for bounds involving $f \neq 0$.
-\textcolor{red}{motivate boundary conditions here}
+and treat the cases $f=0$, $g=0$ separately.  The above boundary conditions are the reduced form of boundary conditions \eqref{bc_1} and \eqref{bc_2}.
 
@@
 
+\subsection{Comparison of boundary conditions}
+
+It's worth addressing the effect of boundary conditions on stability.
+Specifically, a test norm that provides stability for one set of boundary conditions may perform poorly for another set of boundary conditions.
+Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
+\[
+\|\left(\tau, v\right)\|_{V,w}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\|_{w+\epsilon} + \| \div \tau\|_{w+\epsilon} + \frac{1}{\epsilon}\|\tau\|_{w+\epsilon}
+\]
+where $\|\cdot \|_{w+\epsilon}$ is a weighted $L^2$ norm, where the weight $w \in (0,1)$ is required to vanish on $\Gamma_-$ and satisfy $\grad w = O(1)$.
+
+\textcolor{red}{Explain how energy norm convergence in $\|u\| + \epsilon \|u'\|$ returns bad results, and the need for an $O(1)$ term in the test norm.}
+
+The need for the weight is intuitively explained by the induced adjoint problem.  The bilinear form for the Dirichlet case is 
+\[
+b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) + \langle \widehat{f}_n, \left[v\right] \rangle
+\]
+We note that 
+\begin{align*}
+b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_h}
+&= \| u \|^2_{L^2}
+\end{align*}
+for the specific continuous test functions $\tau$ and $v$ satisfying
+\begin{align*}
+\div \tau - \beta \cdot \grad v &= u \\
+\frac{1}{\epsilon}\tau + \grad v &= 0
+\end{align*}
+with boundary condition $\left.v\right|_\Gamma = 0$.
+Choosing a continuous conforming test function $v$ removes the contribution of the term $\langle \widehat{f}_n, \left[v\right] \rangle$ on the mesh skeleton, while the boundary conditions remove the contribution of boundary terms from the bilinear form.
+Then, for this specific choice of $\left(\tau, v\right)$,
+\begin{align*}
+\|u\|_{L^2}^2 &= b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right)}{\|\left(\tau, v\right)\|_V}\|\left(\tau, v\right)\|_V \leq \|u\|_E \|\left(\tau, v\right)\|_V
+\end{align*}
+At minimum, we want $\|u\|_{L^2} \lesssim \|u\|_E$, which requires 
+\[
+\|\left(\tau, v\right)\|_V \lesssim \| u \|_{L^2}
+\]
+for any choice of $u \in L^2$ (dividing through by $\|u\|_{L^2}$ gives the desired result).
+This can be considered a ``sanity check"; at the minimum, we at least want control over the behavior of the single field variable $u$.
+However, we are unable to prove this in the case of Dirichlet boundary conditions.
+Consider the convection-diffusion problem in 1D
+
+\textcolor{red}{add 1D issue with control over $\|v'\|$ here}
+In 1D, the problem reduces to 
+\begin{align*}
+\frac{1}{\epsilon}\sigma - u' &= 0\\
+\left(u - \epsilon \sigma \right)' &=f
+\end{align*}
+with bilinear form
+\begin{align*}
+b\left(\left(u,\sigma,\widehat{u},\widehat{f}\right),\left(\tau,v\right)\right) &= \sum_{k=1}^N \left(\left.\widehat{u}(x) \tau(x)\right |^{x_k}_{x_{k-1}} + \left.\widehat{f}(x) v(x)\right |^{x_k}_{x_{k-1}}\right) \\
+&+ \left(\sigma,\epsilon^{-1}\tau\right)_{\Omega_h} + (u,\tau')_{\Omega_h}- \left(u - \epsilon \sigma,v'\right)_{\Omega_h}
+\end{align*}
+where $\widehat{u}(x), \widehat{f}(x) \in \mathbb{R}$ are now point values defined on mesh points $x_k$ for $k=1,\ldots,N$, where there are $N$ elements.
+A norm for $\|u\|_U = \|u\|_{L^2} + \|\sigma\|_{L^2} + \|\widehat{u}\|+ \|\widehat{f}\|$, as the fluxes are simply point values in 1D.  
+The induced norm $\|\left(\tau,v\right)\|_{V,U}$ is
+\begin{align*}
+\|\left(\tau,v\right)\|_{V,U} &= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}\right)} \frac{ \sum_k \left(\widehat{u}(x_k) [\tau(x_k)] + \widehat{f}(x_k) [v(x_k)]\right)+ \left(\sigma,\epsilon^{-1}\tau + v'\right)_{\Omega_h} + (u,\tau'-v')_{\Omega_h}}{\sum_k \left(|\widehat{u}|+ |\widehat{f}|\right) + \|u\|_{L^2} + \|\sigma\|_{L^2} }
+\end{align*}
+
+Intuitively, the adjoint problem is similar to the primal problem with the direction of inflow reversed, such that the inflow becomes the outflow, and outflow inflow.
+The need for the weight arises due to the presence of the Dirichlet boundary condition on $v$ near the inflow; this induces strong boundary layers at the inflow such that $\grad v \approx O(\epsilon^{-1})$.
+It may be of interest to note that, for sufficiently small $\epsilon$, these issues manifest themselves in numerical experiments as additional refinements near the inflow.
+The presence of the new boundary condition relaxes the outflow boundary condition for the adjoint/dual problem, resulting in stronger stability for the primal problem.
+
+We improve upon the result of Demkowicz and Heuer not by modifying the test norm, but by adopting a new inflow boundary condition, which changes the stability properties of the corresponding adjoint equation.
+Under these new boundary conditions, we can prove robust control over $\|u\|_{L^2}$ using the unweighted version of the test norm in \cite{DPGrobustness}
+\[
+\|\left(\tau, v\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2
+\]
+This test norm is implied by certain norm ``building blocks"; stability analysis of the adjoint equation allows us to bound from above norms and seminorms on $v$ and $\tau$ by $\|f\|_{L^2}$ and $\|g\|_{L^2}$ in ways that do not grow as $\epsilon \rightarrow 0$, and we assemble the test norm as combinations of such norms and seminorms on $v$ and $\tau$.
+
+\textcolor{red}{Move this to after the proof of the streamline gradient lemma.}
+
 \section{Numerical experiments}
@@
 This modified test norm avoids boundary layers, but for adaptive meshes, provides additional stability in areas of heavy refinement, where best approximation error tends to be large and stronger robustness is most needed.
+This leads to a norm which is easily computable, but still provides \textit{asymptotically} the strongest test norm and tightest robustness results in the areas of highest error.
+
 %Intuitively, this is justifiable by the fact that best approximation error is typically only large near where refinements tend to aggregate.

### 2012-04-02 docs/NewBCRobustness_paper/paper.tex
minor rewordings of the paper, removal of one red note
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@417 36274a68-8941-4c93-80ef-affaed5139da

@@
 \end{itemize}
-Together, these estimates will be sufficient to complete the first step and demonstrate bounds on induced test norms for different scalings of norms on $U$.
+Together, these estimates will be sufficient to construct a norm on $V$ and demonstrate bounds on induced test norms for different scalings of norms on $U$.
 
@@
 However, \textcolor{red}{explain why this is OK practically.}
-Additionally, numerical experiments demonstrate much better results, and suggest that, at least for our examples, $\|u-u_h\|_E \sim \|u-u_h\|_{U}$, implying that the induced energy norm is equivalent to the canonical norms we have chosen on the group variable $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)$.
+Additionally, numerical experiments demonstrate much better results, and suggest that, at least for our examples, $\|u-u_h\|_E \sim \|u-u_h\|_{U}$, implying that the induced energy norm is equivalent to a norm on the group variable $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)$ that does not grow with $\epsilon$.
 
@@
 
-\textcolor{red}{Explain how energy norm convergence in $\|u\| + \epsilon \|u'\|$ returns bad results, and the need for an $O(1)$ term in the test norm.}
-
 The need for the weight is intuitively explained by the induced adjoint problem.  The bilinear form for the Dirichlet case is 

### 2012-04-02 docs/NewBCRobustness_paper/paper.tex
addition of 1D illustration of the impact of boundary conditions
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@418 36274a68-8941-4c93-80ef-affaed5139da

@@
 \section{Relations between energy and $U$ norms}
-
+\label{sec:main_bounds}
 The primary result of this paper is that, if $\beta$ satisfies \ref{a_req},\ref{b_req}, and \ref{c_req}, the DPG method provides robust control over the $L^2$ error in $u$ and $\sigma$
@@
 Specifically, a test norm that provides stability for one set of boundary conditions may perform poorly for another set of boundary conditions.
-Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
-\[
-\|\left(\tau, v\right)\|_{V,w}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\|_{w+\epsilon} + \| \div \tau\|_{w+\epsilon} + \frac{1}{\epsilon}\|\tau\|_{w+\epsilon}
-\]
-where $\|\cdot \|_{w+\epsilon}$ is a weighted $L^2$ norm, where the weight $w \in (0,1)$ is required to vanish on $\Gamma_-$ and satisfy $\grad w = O(1)$.
-
-The need for the weight is intuitively explained by the induced adjoint problem.  The bilinear form for the Dirichlet case is 
-\[
-b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) + \langle \widehat{f}_n, \left[v\right] \rangle
-\]
-We note that 
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_h}
-&= \| u \|^2_{L^2}
-\end{align*}
-for the specific continuous test functions $\tau$ and $v$ satisfying
-\begin{align*}
-\div \tau - \beta \cdot \grad v &= u \\
-\frac{1}{\epsilon}\tau + \grad v &= 0
-\end{align*}
-with boundary condition $\left.v\right|_\Gamma = 0$.
+The bilinear form for the case of Dirichlet boundary conditions is
+\[
+b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) + \langle \widehat{u}, \left[\tau \cdot n\right] \rangle_{\Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_h}
+\]
+Notice that the final bilinear form is different; hence, the adjoint problems associated with Section~\ref{sec:strategy3} will now carry different boundary conditions as well.
+The stability properties proven here
+%We note that 
+%\begin{align*}
+%b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_h}
+%&= \| u \|^2_{L^2}
+%\end{align*}
+%for the specific continuous test functions $\tau$ and $v$ satisfying
+%\begin{align*}
+%\div \tau - \beta \cdot \grad v &= u \\
+%\frac{1}{\epsilon}\tau + \grad v &= 0
+%\end{align*}
+%with boundary condition $\left.v\right|_\Gamma = 0$.
 Choosing a continuous conforming test function $v$ removes the contribution of the term $\langle \widehat{f}_n, \left[v\right] \rangle$ on the mesh skeleton, while the boundary conditions remove the contribution of boundary terms from the bilinear form.
 Then, for this specific choice of $\left(\tau, v\right)$,
-\begin{align*}
-\|u\|_{L^2}^2 &= b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right)}{\|\left(\tau, v\right)\|_V}\|\left(\tau, v\right)\|_V \leq \|u\|_E \|\left(\tau, v\right)\|_V
-\end{align*}
-At minimum, we want $\|u\|_{L^2} \lesssim \|u\|_E$, which requires 
-\[
-\|\left(\tau, v\right)\|_V \lesssim \| u \|_{L^2}
-\]
-for any choice of $u \in L^2$ (dividing through by $\|u\|_{L^2}$ gives the desired result).
+%\begin{align*}
+%\|u\|_{L^2}^2 &= b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right)}{\|\left(\tau, v\right)\|_V}\|\left(\tau, v\right)\|_V \leq \|u\|_E \|\left(\tau, v\right)\|_V
+%\end{align*}
+%At minimum, we want $\|u\|_{L^2} \lesssim \|u\|_E$, which requires 
+%\[
+%\|\left(\tau, v\right)\|_V \lesssim \| u \|_{L^2}
+%\]
+%for any choice of $u \in L^2$ (dividing through by $\|u\|_{L^2}$ gives the desired result).
 This can be considered a ``sanity check"; at the minimum, we at least want control over the behavior of the single field variable $u$.
 However, we are unable to prove this in the case of Dirichlet boundary conditions.
-Consider the convection-diffusion problem in 1D
-
-\textcolor{red}{add 1D issue with control over $\|v'\|$ here}
+The robust bounds given in Section~\ref{sec:main_bounds} hold in arbitrary dimension; however, we can show that for the case of Dirichlet boundary conditions, the same results will not hold, even in 1D.
+
 In 1D, the problem reduces to 
@@
 where $\widehat{u}(x), \widehat{f}(x) \in \mathbb{R}$ are now point values defined on mesh points $x_k$ for $k=1,\ldots,N$, where there are $N$ elements.
-A norm for $\|u\|_U = \|u\|_{L^2} + \|\sigma\|_{L^2} + \|\widehat{u}\|+ \|\widehat{f}\|$, as the fluxes are simply point values in 1D.  
+We can assume without loss of generality that $\Omega_h$ is the unit interval $(0,1)$.
+A norm for can be defined through $$\|u\|_U = C_1\|u\|_{L^2} + C_2\|\sigma\|_{L^2} + C_3\sum_k \left(|\widehat{u}|+ |\widehat{f}|\right),$$ as the fluxes are simply point values in 1D.
 The induced norm $\|\left(\tau,v\right)\|_{V,U}$ is
 \begin{align*}
-\|\left(\tau,v\right)\|_{V,U} &= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}\right)} \frac{ \sum_k \left(\widehat{u}(x_k) [\tau(x_k)] + \widehat{f}(x_k) [v(x_k)]\right)+ \left(\sigma,\epsilon^{-1}\tau + v'\right)_{\Omega_h} + (u,\tau'-v')_{\Omega_h}}{\sum_k \left(|\widehat{u}|+ |\widehat{f}|\right) + \|u\|_{L^2} + \|\sigma\|_{L^2} }
-\end{align*}
+\|\left(\tau,v\right)\|_{V,U} &= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}\right)} \frac{ (u,\tau'-v')_{\Omega_h}+ \left(\sigma,\epsilon^{-1}\tau + v'\right)_{\Omega_h}+\sum_k \left(\widehat{u}(x_k) [\tau(x_k)] + \widehat{f}(x_k) [v(x_k)]\right)}{C_1\|u\|_{L^2} + C_2\|\sigma\|_{L^2} + C_3\sum_k \left(|\widehat{u}|+ |\widehat{f}|\right)}\\
+&\leq \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\sum_k \left([\tau(x_k)] +[v(x_k)]\right)
+\end{align*}
+for $f = \epsilon^{-1}\tau + v'$ and $g = \tau'-v'$.
+
+Consider now the 1D analogue of the estimate given by Lemma~\ref{lemma_stream}, which is necessary for robust control over the error in $\|u\|_{L^2}$.
+In 1D, $\|\beta\cdot\grad v\| \lesssim \|g\|$ reduces to the inequality
+\[
+\|v'\|\lesssim \|g\|, \quad g\in L^2{\Omega_h}
+\]
+The adjoint problem corresponding to Lemma~\ref{lemma_stream} in section~\ref{sec:strategy3} is likewise reduced in 1D to the scalar equation
+\begin{align}
+\epsilon v'' + v' &= -g \label{adjoint_1D}
+\end{align}
+with $v\in H^1_0\left((0,1)\right)$.  Multiplying this equation by $v'$ and integrating over $\Omega_h$ gives
+\[
+\int_0^1 \epsilon v''v' + \|v'\|_{L^2}^2 = -\int_0^1 g v'
+\]
+Integrating by parts and Young's inequality give
+\begin{align*}
+-\left.\frac{\epsilon}{2} v'^2\right|_0^1 + \|v'\|_{L^2}^2 &\leq \frac{1}{2}\|g\| + \frac{1}{2}\|v'\|
+\end{align*}
+implying that
+\begin{align*}
+\frac{\epsilon}{2} v'(0)^2 + \|v'\|_{L^2}^2 & \lesssim \|g\| 
+\end{align*}
+Let us restrict ourselves to the cases where $v$ is sufficiently smooth for $v'(0)$ to be well defined.
+Taking $g=1$, we can solve \eqref{adjoint_1D} exactly to see that $\epsilon v'(0)^2 = O(\epsilon^{-1})$, indicating a lack of robustness\footnote{Unlike the case of Dirichlet boundary conditions, the inflow condition on $ \widehat{f} = u(0)-\epsilon u'(0)$ induces an adjoint boundary condition $\tau(0)=0$, or equivalently $v'(0) = 0$, removing the non-robust term from the estimate.}.
 
@@
 The need for the weight arises due to the presence of the Dirichlet boundary condition on $v$ near the inflow; this induces strong boundary layers at the inflow such that $\grad v \approx O(\epsilon^{-1})$.
-It may be of interest to note that, for sufficiently small $\epsilon$, these issues manifest themselves in numerical experiments as additional refinements near the inflow.
-The presence of the new boundary condition relaxes the outflow boundary condition for the adjoint/dual problem, resulting in stronger stability for the primal problem.
-
-We improve upon the result of Demkowicz and Heuer not by modifying the test norm, but by adopting a new inflow boundary condition, which changes the stability properties of the corresponding adjoint equation.
+An interesting phenomenon observed is that, for sufficiently small $\epsilon$, these issues manifest themselves in numerical experiments as additional refinements near the inflow\footnote{Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
+\[
+\|\left(\tau, v\right)\|_{V,w}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\|_{w+\epsilon} + \| \div \tau\|_{w+\epsilon} + \frac{1}{\epsilon}\|\tau\|_{w+\epsilon}
+\]
+where $\|\cdot \|_{w+\epsilon}$ is a weighted $L^2$ norm, where the weight $w \in (0,1)$ is required to vanish on $\Gamma_-$ and satisfy $\grad w = O(1)$.
+The need for the weight is necessary to account for the loss of robustness at the inflow.}.
+The presence of the new boundary condition relaxes the outflow boundary condition for the adjoint/dual problem, resulting in stronger stability estimates for the adjoint, and a better robustness result for the primal problem.
+
+%We improve upon the result of Demkowicz and Heuer not by modifying the test norm, but by adopting a new inflow boundary condition, which changes the stability properties of the corresponding adjoint equation.
 Under these new boundary conditions, we can prove robust control over $\|u\|_{L^2}$ using the unweighted version of the test norm in \cite{DPGrobustness}
-\[
-\|\left(\tau, v\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2
-\]
-This test norm is implied by certain norm ``building blocks"; stability analysis of the adjoint equation allows us to bound from above norms and seminorms on $v$ and $\tau$ by $\|f\|_{L^2}$ and $\|g\|_{L^2}$ in ways that do not grow as $\epsilon \rightarrow 0$, and we assemble the test norm as combinations of such norms and seminorms on $v$ and $\tau$.
-
-\textcolor{red}{Move this to after the proof of the streamline gradient lemma.}
+%\[
+%\|\left(\tau, v\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2
+%\]
+%This test norm is implied by certain norm ``building blocks"; stability analysis of the adjoint equation allows us to bound from above norms and seminorms on $v$ and $\tau$ by $\|f\|_{L^2}$ and $\|g\|_{L^2}$ in ways that do not grow as $\epsilon \rightarrow 0$, and we assemble the test norm as combinations of such norms and seminorms on $v$ and $\tau$.
 

### 2012-04-02 docs/NewBCRobustness_paper/paper.tex
made more changes (proofreading) to paper
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@423 36274a68-8941-4c93-80ef-affaed5139da

@@
 The growth of $C$ with $\epsilon$ is referred to as a loss of robustness, where the bound on the error in the finite element solution by the best approximation error increases as $\epsilon\rightarrow 0$.
-Intuitively, as our singular perturbation parameter changes, our finite element error is bounded more and more loosely to the best approximation error, allowing for degradation of the solution
+Intuitively, as our singular perturbation parameter changes, our finite element error is bounded more and more loosely by the best approximation error, allowing for degradation of the solution for very small $\epsilon$.
 
@@
 Traditionally, instability/loss of robustness has been dealt with using residual-based stabilization.
-Given some variational form $b(u,v) - l(v)=0$, the problem is modified by adding to the bilinear form a factor of the residual $r(v) = b(u,v) - l(v)=0$, scaled by a stabilization constant $\tau$.
+Given some variational form, the problem is modified by adding to the bilinear form a factor of the residual, scaled by a stabilization constant $\tau$.
 The most well-known example of this is the streamline-upwind Petrov-Galerkin method, which is a stabilized method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.
@@
 
-The DPG (discontinuous Petrov-Galerkin) method is the combination of the concept of computable optimal test functions with the so-called ``ultra-weak formulation", where the regularity requirement on each solution variable is relaxed through integration by parts.
+The DPG (discontinuous Petrov-Galerkin) method is the pairing of the concept of computable optimal test functions with the so-called ``ultra-weak formulation", where the regularity requirement on each solution variable is relaxed through integration by parts.
 Moreover, to maintain conformity while seeking an $L^2$ setting on interior ``field" variables, boundary terms are identified as additional new unknowns.
@@
 \begin{align*}
-\|v\|_{\rm opt} &= \sup_{u,\widehat{u}} \frac{\langle \widehat{u}, [v] \rangle - (u,A^*v)}{C_1\|u\|_{L^2} + C_2\|\widehat{u}\|} \\
+\|v\| &= \sup_{u,\widehat{u}} \frac{\langle \widehat{u}, [v] \rangle - (u,A^*v)}{C_1\|u\|_{L^2} + C_2\|\widehat{u}\|} \\
 &\leq \frac{1}{C_1}\sup_{u} \frac{(u,A^*v)}{\|u\|_{L^2}} + \frac{1}{C_2}\sup_{\widehat{u}} \frac{\langle \widehat{u}, [v] \rangle}{\|\widehat{u}\|}\\
@@
 \]
-This is, in some sense, the ideal or ``optimal" test norm; given any particular norm $\|u\|_U$, DPG under the optimal test norm will return the best finite element approximation in both field and flux variables, independently of any parameters
-
-The norm $\|v\|_{\rm opt}$ is non-localizable, however - the above ``optimal" test norm is induced by an inner product; however, this inner product is a global one due to the presence of the jump terms.
-Solving for optimal test functions under this optimal norm through inversion of this inner product  will result in expensive global problems, making this an impractical norm to work with.
+which induces the so-called ``optimal test norm"
+\[
+\|v\|_{\rm opt} = \|A^*v\|_{L^2} + \left(\sup_{\widehat{u}} \frac{\langle \widehat{u}, [v] \rangle}{\|\widehat{u}\|}\right)
+\]
+This is, in some sense, the canonical or ideal test norm; given any well-posed variational problem, DPG under the optimal test norm will return the best finite element approximation in both field and flux variables.
+
+The norm $\|v\|_{\rm opt}$ is non-localizable, however - the optimal test norm is induced by a global inner product due to the presence of the jump terms.
+Solving for optimal test functions under this optimal norm (through inversion of Riesz map correspdongin to this inner product) will result in expensive global problems, making this an impractical norm to work with.
 
@@
 It's worth addressing the effect of boundary conditions on stability.
-Specifically, a test norm that provides stability for one set of boundary conditions may perform poorly for another set of boundary conditions.
+Specifically, a test norm that provides stability for one set of boundary conditions may perform poorly for another set.
+Take, for example, the test norm defined in Section~\ref{sec:main_bounds} and the convection-diffusion problem with Dirichlet boundary conditions.
+
 The bilinear form for the case of Dirichlet boundary conditions is 
@@
 Let us restrict ourselves to the cases where $v$ is sufficiently smooth for $v'(0)$ to be well defined.
-Taking $g=1$, we can solve \eqref{adjoint_1D} exactly to see that $\epsilon v'(0)^2 = O(\epsilon^{-1})$, indicating a lack of robustness\footnote{Unlike the case of Dirichlet boundary conditions, the inflow condition on $ \widehat{f} = u(0)-\epsilon u'(0)$ induces an adjoint boundary condition $\tau(0)=0$, or equivalently $v'(0) = 0$, removing the non-robust term from the estimate.}.
+Taking $g=1$ (corresponding to a piecewise constant approximation) we can solve \eqref{adjoint_1D} exactly to see that
+\[
+v = \frac{e^{-\frac{x}{\epsilon}}}{e^{\frac{1}{\epsilon}}-1}\left(e^{\frac{1}{\epsilon}}\left(e^{\frac{x}{\epsilon}}-1\right) + \left(e^{\frac{1}{\epsilon}}-1\right)e^{\frac{x}{\epsilon}}x\right)
+\]
+Consequently, $\frac{\epsilon}{2} v'(0)^2 \approx \epsilon^{-1}$, indicating already a lack of robustness in the bound of $\|v'\|$ by $\|g\|$ for constant data\footnote{Unlike the case of Dirichlet boundary conditions, the inflow condition on $ \widehat{f} = u(0)-\epsilon u'(0)$ induces an adjoint boundary condition $\tau(0)=0$, or equivalently $v'(0) = 0$, removing the non-robust term from the estimate.}.
+The robust bound from below of $g$ constant corresponds to the robust control of the approximation of field variable $u$ by piecewise constant trial functions.
+More detailed 1D error bounds for Dirichlet boundary conditions are provided in \cite{DPG3}, and also indicate a lack of robustness when using the standard broken Sobolev norm as the test norm on $\tau$ and $v$.
 

### 2012-04-03 docs/NewBCRobustness_paper/paper.tex
made a first draft full edit
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@424 36274a68-8941-4c93-80ef-affaed5139da

@@
 
-Standard Bubnov-Galerkin methods tend to perform poorly for the class of partial-differential equations known as singularly perturbed problems, where a given parameter $\epsilon$ may approach either $0$ or $\infty$ in the context of physical problems.
-This poor performance is captured by the error bound
-\[
-\|u-u_h\|_E \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_U
-\]
-The growth of $C$ with $\epsilon$ is referred to as a loss of robustness, where the bound on the error in the finite element solution by the best approximation error increases as $\epsilon\rightarrow 0$.
-Intuitively, as our singular perturbation parameter changes, our finite element error is bounded more and more loosely by the best approximation error, allowing for degradation of the solution for very small $\epsilon$.
-
-A well-known example is the growth of spurious oscillations in the finite element solution of the 1D convection-diffusion problem $ u'-\epsilon u'' = f$ (with Dirichlet boundary conditions) as $\epsilon\rightarrow 0$.
+The finite element/Galerkin method has been widely utilized in engineering to solve partial differential equations related to simulation of solid mechanics problems.
+For many problems in engineering, the bilinear forms resulting from these partial differential equations are symmetric and coercive (positive-definite), and it is well known that the finite element method produces near-optimal results for such problems.
+However, standard Bubnov-Galerkin methods tend to perform poorly for the class of partial-differential equations known as singularly perturbed problems.
+Singularly perturbed problems are problems where a given parameter may be either very small or very large in the context of physical problems.
+An additional complication of singularly perturbed problems is that very often, in the limiting case of the parameter blowing up or decreasing to zero, the partial differential equation itself will change form.
+A canonical example is the convection-diffusion equation.
+In 1D, this equation is
+\[
+u'-\epsilon u'' = f.
+\]
+The equation represents the change in the concentration of some quantity $u$ in some medium from both convective and diffusive effects.
+The parameter $\epsilon$ represents the diffusivity, and in the limit of an inviscid medium as $\epsilon\rightarrow 0$, the partial differential equation changes types, going from a parabolic to a hyperbolic equation.
+
+The finite element method has notoriously performed poorly for this example, and for many other singularly perturbed equations.
+This poor performance is captured by the error bound for the finite element method applied to convection-diffusion equations
+\[
+\|u-u_h\|_E \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_U,
+\]
+where $C(\epsilon)$ grows as $\epsilon$ approaches its limiting case.
+The growth of $C$ with $\epsilon$ is referred to as a \textit{loss of robustness} in $\epsilon$, where the bound on the error in the finite element solution by the best approximation error increases as $\epsilon\rightarrow 0$.
+Intuitively, as our singular perturbation parameter changes, our finite element error is bounded more and more loosely by the best approximation error, allowing for more and more error in the finite element solution for as $\epsilon$ shrinks.
+
+A well-known example of this loss of robustness is the growth of spurious oscillations in the finite element solution of the 1D convection-diffusion problem $ u'-\epsilon u'' = f$ (with Dirichlet boundary conditions) as $\epsilon\rightarrow 0$.
+For small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation develops oscillations of magnitude $O(\epsilon^{-1})$.
 Another class of examples are wave propagation problems, in which the singular perturbation parameter is the wavenumber, $k\rightarrow \infty$.
-The lack of robustness in this case manifests as ``pollution" error, a phenomenon where the finite element solution degrades over many wavelengths (commonly manifesting as a phase error between the FE solution and the exact solution).
+The lack of robustness in this case manifests as ``pollution" error, a phenomenon where the finite element solution degrades over many wavelengths for high wavenumbers (commonly manifesting as a phase error between the FE solution and the exact solution).
 
@@
 The most well-known example of this is the streamline-upwind Petrov-Galerkin method, which is a stabilized method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.
+\textcolor{red}{TO DO: give motivations for consistency (converges to same solution) of stabilization terms vs artificial diffusion type stabilization and, show how consistency gives a Petrov-Galerkin method}
 
@@
 The idea of optimal test functions was introduced by Demkowicz and Gopalakrishnan in \cite{DPG2}.
-Conceptually, these optimal test functions are the result of a minimum residual method applied to the operator form of a variational equation.
+Conceptually, these optimal test functions are the natural result of the minimumization of a residual corresponding the operator form of a variational equation.
+The connection between stabilization and least squares/minimum residual methods has been observed previously; however, the concept of optimal test functions presents the idea from a different perspective.
+
 Given Hilbert spaces $U$ and $V$ and a variational problem $b(u,v) = l(v)$, $\forall u\in U, v\in V$, we can identify $B:U\rightarrow V'$ and $l \in V'$ 
@@
 We identify the \textit{trial-to-test} operator $T = R_V^{-1}B$, which maps a trial function $u_h$ to its corresponding \textit{optimal} test function $v_h = Tu_h$.
-These test functions can be solved for by solving the auxiliary variational problem
+These test functions can be determined by solving the auxiliary variational problem
 \[
@@
 \]
-
-Finally, while the above variational problem is a global operation for standard continuous test spaces, the use of discontinuous test spaces reduces it to a local problem that can be solved in an element-by-element fashion.
-In practice, this variational problem can rarely be solved exactly, but instead is solved approximately using the standard Bubnov-Galerkin method and an ``enriched" subspace of $V$.
+This concept is not a new one; the idea of optimal testing is a classical one (see \textcolor{red}{find citation}).
+However, for standard conforming finite elements, test functions are continuous over the entire domain, and solving the above variational problem for optimal test functions is a global operation that must be performed once for every approximating function in the trial space, rendering the method impractical.
+The breakthrough came through the development of discontinous Galerkin (DG) methods; specifically, the use of discontinuous test spaces reduces the problem of determining optimal test functions to a local problem that can be solved in an element-by-element fashion.
+
+In practice, this variational problem is difficult to solve exactly, and the solution is instead is approximately using the standard Bubnov-Galerkin method and an ``enriched" subspace of $V$ such that $\dim(V) > \dim(U)$.
 We assume the corresponding error in approximation of the optimal test functions is negligible for the scope of this paper.
@@
 
-Under the standard conditions for well-posedness of the continuous variational problem, the discrete DPG method delivers the best approximation error in the ``energy norm" $\|u\|_E = \sup \frac{b(u,v)}{\|v\|_V}$.
-Additionally, the actual energy error $\|u-u_h\|_E$ is computable through $\|e_h\|_V$, where
+Under the standard conditions for well-posedness of the continuous variational problem, the discrete DPG method delivers the best approximation error in the ``energy norm" 
+\[
+\|u\|_E = \sup \frac{b(u,v)}{\|v\|_V}.
+\]
+The above norm can be determined via $\|u\|_E = \|v_u\|_V$, where $v_u$ solves
+\[
+(v_u,\delta v)_V = b(u,\delta v), \quad \forall v \in V
+\]
+As a consequence of this fact, without knowing the exact solution, the actual energy error $\|u-u_h\|_E$ is computable through $\|e_h\|_V$, where
 \[
@@
 
-The DPG (discontinuous Petrov-Galerkin) method is the pairing of the concept of computable optimal test functions with the so-called ``ultra-weak formulation", where the regularity requirement on each solution variable is relaxed through integration by parts.
+The DPG (discontinuous Petrov-Galerkin) method is the pairing of the concept of locally computable optimal test functions with the so-called ``ultra-weak formulation".
+For a given operator equation $Au = f$, the ultra-weak formulation is
+\[
+b\left(\left(\widehat{u},u\right),v\right) - l(v) = \langle \widehat{u}, [v] \rangle - (u,A^*v) - (f,v) = 0
+\]
+where $A^*$ is the formal adjoint resulting from integration by parts, and $[v]$ is the jump of $v$ across element boundaries.
+Under the ultra-weak formulation, the regularity requirement on each solution variable is relaxed through integration by parts.
 Moreover, to maintain conformity while seeking an $L^2$ setting on interior ``field" variables, boundary terms are identified as additional new unknowns.
 The result is a hybridized DG method with locally supported optimal test functions.
-For a given operator equation $Au = f$, the ultra-weak formulation is
-\[
-b\left(\left(\widehat{u},u\right),v\right) - l(v) = \langle \widehat{u}, [v] \rangle - (u,A^*v) - (f,v) = 0
-\]
-where $A^*$ is the formal adjoint resulting from integration by parts, and $[v]$ is the jump of $v$ across element boundaries.
 
@@
 
-Up to now, we have neglected discussion of the proper choice of inner product/norm on the space $V$.
-This choice is important, as the choice of norm on $V$ determines the norm on $U$ in which DPG is optimal.
-Whether a particular choice of norm on $V$ norm is ``good" or not is problem-dependent; however, there is an important canonical choice of test norm for any given variational form.
+Up to now, we have neglected discussion of the proper choice of inner product/norm on the space $V$.  The energy norm in which DPG is optimal 
+\[
+\|u\|_E = \sup \frac{b(u,v)}{\|v\|_V}.
+\]
+depends heavily on our choice of norm on the test space $\|v\|_V$.
 
@@
 
-As a consequence of \eqref{norm_duality}, given two norms on $U$, $\|\cdot\|_{U_1}$ and $\|\cdot\|_{U_2}$, if $\|u\|_{U_1} \leq \|u\|_{U_2}$, we have the equivalent statement
-\begin{align*}
-\| v \|_{V,U_1} = \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_{U_1}} \geq  \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_{U_2}} = \| v \|_{V,U_2}
+As a consequence of \eqref{norm_duality}, given two norms on $U$, $\|\cdot\|_{U_1}$ and $\|\cdot\|_{U,2}$, if $\|u\|_{U_1} \leq \|u\|_{U,2}$, we have the equivalent statement
+\begin{align*}
+\| v \|_{V,U_1} = \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_{U_1}} \geq  \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_{U,2}} = \| v \|_{V,U,2}
 \end{align*}
@@
 The duality between test norm and variational form holds for any particular variational form, though it is often difficult to determine analytically the form of $\|v\|_{V,U}$.
-However, for the DPG ultra-weak formulation, there is an important test norm that results from a specific induced norm on $U$.
+Whether a particular choice of norm on $V$ norm is ``good" or not is problem-dependent; however, for the DPG ultra-weak formulation, there is an important canonical test norm that results from a specific induced norm on $U$.
+
 Define the norm on $U$
@@
 \end{align*}
-where we have used the Cauchy-Schwarz inequality, and eliminated the supremum by noting the inequality is tight.  We define $\|u\|_{\rm opt}$ as such a norm with $C_1=C_2 = 1$,
+where we have used the Cauchy-Schwarz inequality, and eliminated the supremum by noting that the Cauchy-Schwarz inequality is tight.
+We define the optimal/ideal norm on $U$ as $\|u\|_{\rm opt}$ as such a norm with $C_1=C_2 = 1$,
 \[
@@
 \]
-This is, in some sense, the canonical or ideal test norm; given any well-posed variational problem, DPG under the optimal test norm will return the best finite element approximation in both field and flux variables.
-
-The norm $\|v\|_{\rm opt}$ is non-localizable, however - the optimal test norm is induced by a global inner product due to the presence of the jump terms.
-Solving for optimal test functions under this optimal norm (through inversion of Riesz map correspdongin to this inner product) will result in expensive global problems, making this an impractical norm to work with.
-
+This is, in some sense, the canonical or ideal test norm; given any well-posed variational problem, DPG under the optimal test norm will return the best finite element approximation in a balanced norm on both field and flux variables.
+
+Unfortunately, the norm $\|v\|_{\rm opt}$ is non-localizable, meaning that it cannot be decomposed into the sum of independent contributions over individual elements.
+Consequently, the optimal test norm must be induced by a global inner product due to the presence of the jump terms.
+Solving for optimal test functions under this optimal norm (through inversion of Riesz map corresponding to this inner product) will result in expensive global problems, making this an impractical norm to work with.
 In practice, an approximation is made by removing such boundary terms and replacing them with scaled $L^2$ norms of the field variables, producing so-called \textit{quasi-optimal} test norm
@@
 
-We can now translate the above abstract language to a concrete model problem in computational fluid dynamics.
-We consider the model convection-diffusion problem on domain $\Omega$ with boundary $\Gamma$
+Our aim now is to translate the above abstract language to a concrete model problem in computational fluid dynamics.
+We consider the model convection-diffusion problem on domain $\Omega \in \mathbb{R}^d$ with boundary $\Gamma$
 \begin{align}
@@
 \end{align*}
-with the corresponding variational form 
+with the corresponding variational form (modulo application of boundary conditions)
 \begin{align*}
@@
 \end{align*}
-where $\left[ \tau_n \right]$ and $\left[ v\right]$ denote the jumps in $\tau_n$ and $v$, defined as
+where $\left[ \tau_n \right]$ and $\left[ v\right]$ denote the jumps in $\tau_n$ and $v$ across an element edge, defined as
 \begin{align*}
@@
 \end{align*}
+where $n$ is the outward normal vector to an element edge, and ${\rm sgn}(n)$ is 1 if $n$ aligns with a preset global orientation, and $-1$ otherwise.
+\textcolor{red}{I need to find more simple way to explain sgn}.
+
 Additionally, the inner products are taken element-wise over the finite element mesh $\Omega_h$, and the duality pairings are taken on $\Gamma_h$, the mesh ``skeleton", or union of edges of elements $K$ in $\Omega_h$.
+Similarly, we define the interior skeleton $\Gamma_h^0 = \Gamma_h \setminus \Gamma$.
 The divergence and gradient operators are likewise understood to act element-wise.
 
-Define the interior skeleton $\Gamma_h^0 = \Gamma_h \setminus \Gamma$.
  The functional setting is now well understood as well (see \cite{analysisDPG} for details) - $u,\sigma \in L^2(\Omega)$, $v \in H^1(\Omega_h)$, $\tau \in H({\rm div},\Omega_h)$, where $H^1(\Omega_h)$ and $H({\rm div},\Omega_h)$ are element-wise ``broken" Sobolev spaces.
@@
 
-We split the boundary $\Gamma$ into three portions
+Finally, we split the boundary $\Gamma$ into three portions
 \begin{align*}
@@
 on $\Gamma_-$, and continue with the wall boundary condition $u=0$ on $\Gamma_+$.
-For our model problem, as for most problems of interest in CFD, we expect $\grad u$ to be small near the inflow, and that the solutions to \eqref{primal} using $u=u_0$ and $\beta_n u - \sigma_n = f_n = u_0$ should converge to each other for sufficiently small $\epsilon$.
+For our model problem, as for many problems of interest in computational fluid dynamics, we expect $\grad u$ to be small near the inflow, and that the solutions to \eqref{primal} using $u=u_0$ and $\beta_n u - \sigma_n = f_n = u_0$ should converge to each other for sufficiently small $\epsilon$.
 Under these new boundary conditions, our variational problem $b(u,v) = l(v)$ is now defined by
@@
 
-Given the boundary conditions on $\widehat{u}$ and $\widehat{f}_n$, we can now also define the trace norms as (canonical) minimum energy extension norms (taking into account the respective lifts of $\widehat{u}$ and $\widehat{f}_n$ on $\Gamma_+$ and $\Gamma_-$, respectively)
+Given the boundary conditions on $\widehat{u}$ and $\widehat{f}_n$, we can now also define the trace norms as (canonical) minimum energy extension norms (taking into account the respective lifts/boundary conditions on $\widehat{u}$ and $\widehat{f}_n$ on $\Gamma_+$ and $\Gamma_-$, respectively)
 \begin{align*}
@@
 \end{align*}
-Additionally, throughout the rest of this work, we denote norms on $u$ and $\sigma$ as
-\begin{align*}
-\|u\| &= \|u\|_{L^2} \\
-\|\sigma\| &= \|\sigma\|_{L^2}
-\end{align*}
+%Additionally, throughout the rest of this work, we denote norms on $u$ and $\sigma$ as
+%\begin{align*}
+%\|u\| &= \|u\|_{L^2} \\
+%\|\sigma\| &= \|\sigma\|_{L^2(\Omega_h)}
+%\end{align*}
 We will construct norms on $U$ as combinations of norms on each variable
 \[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = C_1 \|u\| + C_2 \|\sigma\| + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|.
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = C_1 \|u\|_{L^2(\Omega_h)} + C_2 \|\sigma\|_{L^2(\Omega_h)} + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|.
 \]
@@
 \]
-The squared norm over the entire triangulation $\Omega_h$ is defined to be the squared sum of contributions from each element.  The exact norms that we will place on $V$ will be determined later.
+The squared norm over the entire triangulation $\Omega_h$ is defined to be the squared sum of contributions from each element
+\[
+\|\left(\tau,v\right)\|_{H^1(\Omega_h) \times H({\rm div},\Omega_h)} = \sum_{K\in \Omega_h} \|\left(\tau,v\right)\|_{H^1(K) \times H({\rm div},K)}
+\]
+The exact norms that we will specify on $V$ will be determined later.
 
@@
 However, use of this norm for the convection-diffusion problem is difficult - the variational problem for optimal test functions using the quasi-optimal test norm is equivalent to a reaction-diffusion system \cite{DBLP:journals/procedia/NiemiCC11}.
-Transforming the problem to the reference element reveals that the inversion of the inner product associated with the optimal test norm will induce strong boundary layers of width $\epsilon/h^2$ in the optimal test functions.
-In comparison, in Helmholtz and wave propagation problems, the mesh size tends to be on the order of the wavelength/singular perturbation parameter, resulting in smooth optimal test functions that are much easier to approximate over the reference element.
-As the relevant range of $\epsilon$ for physical problems is $1e-7$, solving on partially under-resolved meshes is unavoidable, and the approximability of the optimal test functions must be addressed to take advantage of the properties of DPG.
+Such systems also develop strong boundary layers for small diffusion, and transforming the problem to the reference element reveals that the inversion of the inner product associated with the optimal test norm will induce strong boundary layers of width $\epsilon/h^2$ in the optimal test functions.
+In comparison, the quasi-optimal norm has yielded fantastic results for the Helmholtz equation and other wave propagation problems.
+The difference between the two problems lies in the fact that, for wave propagation problems, the mesh size tends to be on the order of the wavenumber $k$/singular perturbation parameter.
+Transforming the variational problem using the quasi-optimal test norm for wave propagation yields smooth optimal test functions that are much easier to approximate over the reference element.
+Typically, the wavenumbers $k$ of physical interest are $O(100)-O(1000)$ with respect to a unit domain.
+The corresponding finite element problems will typically be solved on meshes containing approximately $O(k^d)$ elements in $\mathbb{R}^d$, well within the range of a computationally tractable simulation.
+However, for convection diffusion problems, the relevant range of $\epsilon$ for physical problems can be as small as $1e-7$.
+Solving on partially under-resolved meshes is thus unavoidable, and the approximability of the optimal test functions must be addressed in order to take advantage of the properties of DPG.
 
@@
 Under this scheme, the approximation of optimal test functions is tied to the effectiveness of the $p$-method.
-Unfortunately, for problems with boundary layers (including the approximation of optimal test functions under the quasi-optimal test norm), the $p$-method performs very poorly.
-
-Resolving such boundary layers for an underresolved mesh has been investigated numerically using specially designed (Shishkin) subgrid meshes by Niemi, Collier, and Calo in \cite{DBLP:journals/procedia/NiemiCC11}.
+Unfortunately, for problems with boundary layers - including the approximation of optimal test functions under the quasi-optimal test norm - the $p$-method performs very poorly.
+
+Resolving such boundary layers present in quasi-optimal test functions has been investigated numerically using specially designed (Shishkin) subgrid meshes by Niemi, Collier, and Calo in \cite{DBLP:journals/procedia/NiemiCC11}.
 However, even with Shishkin meshes, the approximation of optimal test functions under the quasi-optimal norm is difficult and far more expensive and complex to implement than approximation of test functions using a simple $p$-enriched space for $V$.
@@
 
-The estimates and proofs in this paper are largely based off of techniques and prior work done in \cite{DPGrobustness} and \cite{analysisDPG}; for further details, we encourage readers to consult these two publications as well.
-The primary contributions in this paper are stronger stability estimates for a new inflow boundary condition and a slightly different test norm.
+The estimates and proofs in this paper are largely based off of techniques and prior work done in \cite{DPGrobustness} and \cite{analysisDPG}; for further details, we encourage readers to consult these two publications as well\footnote{The primary contributions in this paper are stronger stability estimates for a new inflow boundary condition and a slightly different test norm.}.
 
@@
 The main goal of this paper is to derive a test norm that \textit{does not induce boundary layers in the optimal test functions}, but still induces an energy norm \textit{that does not lose robustness as $\epsilon \rightarrow 0$}.
-The first condition is satisfied by first decoupling norms on $\left(\tau,v\right)$ such that
-\[
-\left\|\left(\tau,v\right)\right\|_V = \|\tau\|_{H({\rm div},\Omega_h)} +  \|v\|_{H^1(\Omega_h)}.
-\]
-where $\|\tau\|_{H({\rm div},\Omega_h)}$ and $ \|v\|_{H^1(\Omega_h)}$ are both constructed as the sum of norm and seminorms on each respective space.
+%The first condition is satisfied by first decoupling norms on $\left(\tau,v\right)$ such that
+%\[
+%\left\|\left(\tau,v\right)\right\|_V = \|\tau\|_{H({\rm div},\Omega_h)} +  \|v\|_{H^1(\Omega_h)}.
+%\]
+%where $\|\tau\|_{H({\rm div},\Omega_h)}$ and $ \|v\|_{H^1(\Omega_h)}$ are both constructed as the sum of norm and seminorms on each respective space.
 Ensuring that each seminorm/normed term is of the same order will allow for smooth solutions (under some assumptions on $\beta$).
 The avoidance of boundary layers in the test norm will be described in more detail in the section detailing numerical experiments.  
-\textcolor{red}{Why are we allowed to have $\beta\cdot \grad v$ of order 1 while we have other terms of order $O({\rm Pe})$?  Why does this term not induce boundary layers?}
-
-Showing the second condition on robustness is equivalent to showing the robust boundedness of the energy error from above and below by norms on $U$ 
+\textcolor{red}{Why are we allowed to have $\beta\cdot \grad v$ of order 1 while we have other terms of order $O({\rm Pe})$?
+Why does this term not induce boundary layers?}.
+We focus first on showing the condition on robustness.
+Such a condition is equivalent to showing the robust boundedness of the energy error from above and below by norms on $U$
 \[
@@
 %$\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_U \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E$.  
-Our strategy for proving such a bound is broken down into three parts.
+\textcolor{red}{Explain in intuitive terms what the bounds above and below mean.}
+Our goal is to explicitly derive the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ that characterize this relation, taking into account the limiting case of $\epsilon \rightarrow 0$. 
+Our strategy for doing so is broken down into three parts.
 
@@
 \end{align*}
-which, by definition of the boundary norms, gives the characterization of the induced test norm 
+which, by definition of the boundary norms on $[\tau\cdot n]$ and $[v]$, gives the characterization of the induced test norm 
 \[
@@
 \textcolor{red}{is this an equality?
-Is the inequality attainable, and thus attained in the supremum?} We can now use this relation to compare two different norms on $U$ by comparing their induced norms on $V$.
-Additionally, showing a robust inequality between two norms on $U$ is similarly equivalent to showing the robust reverse inequality in the induced norms on $V$.
+Is the inequality attainable, and thus attained in the supremum?} We can now use this relation to compare two different norms on $U$ by comparing their induced norms on $V$ - recall that showing a robust inequality between two norms on $U$ is similarly equivalent to showing the robust reverse inequality in the induced norms on $V$.
 
@@
 
-After reducing the problem of comparing norms on $U$ to comparing norms on $V$, we break the analysis of $\left(\tau,v\right) \in V$ into the analysis of subproblems.  Define the decomposition
-\[
-\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right),
+After reducing the problem of comparing norms on $U$ to comparing norms on $V$, we break the analysis of $\left(\tau,v\right) \in V$ into the analysis of three subproblems.  Define the decomposition
+\[
+\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\taU,2\right),
 \]
@@
 \end{align*} 
-Likewise, we define $\left(v_2,\tau_2\right)$ as satisfying
-\begin{align*}
-\epsilon^{-1}\tau_2 + \grad v_2 &= \epsilon^{-1}\tau + \grad v = f\\
-\div \tau_2 - \beta\cdot \grad v_2 &= 0
-\end{align*}
-We will additionally require both $\left(\tau_1,v_1\right)$ and $\left(\tau_2,v_2\right)$ to come from $H({\rm div}, \Omega)\times H^1(\Omega)$, and to satisfy boundary conditions
+Likewise, we define $\left(v_2,\taU,2\right)$ as satisfying
+\begin{align*}
+\epsilon^{-1}\taU,2 + \grad v_2 &= \epsilon^{-1}\tau + \grad v = f\\
+\div \taU,2 - \beta\cdot \grad v_2 &= 0
+\end{align*}
+We will additionally require both $\left(\tau_1,v_1\right)$ and $\left(\taU,2,v_2\right)$ to come from $H({\rm div}, \Omega)\times H^1(\Omega)$, and to satisfy boundary conditions
 \begin{align}
@@
 \end{align*}
-By $\left(v_0,\tau_0\right) = \left(v,\tau\right) - \left(v_1,\tau_1\right) - \left(v_2,\tau_2\right)$, $\left(v_0,\tau_0\right)$ must satisfy boundary conditions
+By $\left(v_0,\tau_0\right) = \left(v,\tau\right) - \left(v_1,\tau_1\right) - \left(v_2,\taU,2\right)$, $\left(v_0,\tau_0\right)$ must satisfy boundary conditions
 \begin{align}
@@
 Bounding $\|\left(\tau_0,v_0\right)\|$ requires the use of techniques and decompositions first developed in \cite{analysisDPG} and adapted to convection-diffusion in \cite{DPGrobustness}.
-However, due to the conforming nature of $\left(\tau_1,v_1\right)$ and $\left(\tau_2,v_2\right)$, the bound from above of test functions $\|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|g\|$ is reduced to proving classical error estimates for the adjoint equations
+However, due to the $H({\rm div}, \Omega)\times H^1(\Omega)$ conforming nature of $\left(\tau_1,v_1\right)$ and $\left(\taU,2,v_2\right)$, the bound from above of test functions $\|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|g\|$ is reduced to proving classical error estimates for the adjoint equations
 \begin{align}
@@
 The final step to constructing a robust, localizable test norm on $V$ that does not generate boundary layers is to derive adjoint stability estimates on $\tau$ and $v$ in terms of localizable normed quantities.
-These normed quantities will create ``building-blocks" through which we can construct test norms, where each building block will correspond roughly to the control of $\|u\|_{L^2}$, $\|\sigma\|_{L^2}$, $\|\widehat{u}\|$, or $\|\widehat{f}_n\|$.
+These normed quantities will create ``building-blocks" through which we can construct test norms, where each building block will correspond roughly to robustness estimates for $\|u\|_{L^2}$, $\|\sigma\|_{L^2}$, $\|\widehat{u}\|$, or $\|\widehat{f}_n\|$.
 
@@
 \end{align}
-Additionally, as these results are primarily interested in stability and robustness for $\epsilon \ll 1$, we require $\epsilon$ sufficiently small in Lemma \ref{lemma_grad}.
+We also require $\epsilon$ sufficiently small in Lemma \ref{lemma_grad}.
 
@@
 \end{itemize}
-Together, these estimates will be sufficient to construct a norm on $V$ and demonstrate bounds on induced test norms for different scalings of norms on $U$.
+Together, these estimates will be sufficient to construct a complete norm on $V$ and demonstrate bounds on induced test norms for different scalings of norms on $U$.
 
@@
 \label{sec:main_bounds}
+
+Let the norm 
+\[
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{E}
+\]
+be defined as the energy norm induced by DPG under the specific test norm
+\[
+\|\left(\tau, v\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2.
+\]
+
 The primary result of this paper is that, if $\beta$ satisfies \ref{a_req},\ref{b_req}, and \ref{c_req}, the DPG method provides robust control over the $L^2$ error in $u$ and $\sigma$
 \[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-\left(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h}\right)\right\|_{U_1} \lesssim \inf_{w\in U_h}\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-w_h \right\|_{E}
-\]
-using the test norm
-\[
-\|\left(\tau, v\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2
-\]
-where $\|\cdot \|_{U_1}$ is defined as
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U_1} \coloneqq \|u\| + \|\sigma\| + \epsilon\|\widehat{u}\|+\sqrt{\epsilon} \|\widehat{f}_n\|.
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-\left(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h}\right)\right\|_{U,1} \lesssim \inf_{w\in U_h}\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-w_h \right\|_{E}
+\]
+where $\|\cdot \|_{U,1}$ is defined as
+\[
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,1} \coloneqq \|u\| + \|\sigma\| + \epsilon\|\widehat{u}\|+\sqrt{\epsilon} \|\widehat{f}_n\|.
 \]
@@
 \[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-\left(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h}\right)\right\|_{E} \lesssim \inf_{w\in U_h}\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-w_h\right\|_{U_2}
-\]
-where $\|\cdot \|_{U_2}$ is defined as
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U_2}^2 \coloneqq \|u\|^2 + \frac{1}{\sqrt{\epsilon}}\left(\|\sigma\|^2 + \|\widehat{u}\|^2+ \|\widehat{f}_n\|^2\right).
-\]
-While the upper bound is robust, we have derived such a bound only by explicitly accounting for a factor of $\epsilon^{-1/2}$ in the bounding norm $\|\cdot \|_{U_2}$.
-This implying that for very small $\epsilon$, the $L^2$ error may be much smaller than the energy error.
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-\left(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h}\right)\right\|_{E} \lesssim \inf_{w\in U_h}\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-w_h\right\|_{U,2}
+\]
+where $\|\cdot \|_{U,2}$ is defined as
+\[
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,2}^2 \coloneqq \|u\|^2 + \frac{1}{\sqrt{\epsilon}}\left(\|\sigma\|^2 + \|\widehat{u}\|^2+ \|\widehat{f}_n\|^2\right).
+\]
+While the upper bound is robust, we have derived such a bound only by explicitly accounting for a factor of $\epsilon^{-1/2}$ in the bounding norm $\|\cdot \|_{U,2}$.
+This implies that for very small $\epsilon$, the $L^2$ error may be much smaller than the energy error.
 However, \textcolor{red}{explain why this is OK practically.}
-Additionally, numerical experiments demonstrate much better results, and suggest that, at least for our examples, $\|u-u_h\|_E \sim \|u-u_h\|_{U}$, implying that the induced energy norm is equivalent to a norm on the group variable $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)$ that does not grow with $\epsilon$.
+Additionally, numerical experiments demonstrate much better results, and suggest that, at least for our example problems, $\|u-u_h\|_E \sim \|u-u_h\|_{U}$, implying that the induced energy norm is equivalent to a norm on the group variable $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)$ that does not grow with $\epsilon$.
 
@@
 
-We begin by using the strategy outlined in sections~\ref{sec:strategy1}, ~\ref{sec:strategy2}, and ~\ref{sec:strategy3} to prove the robust bound of the $L^2$ error in the field variables by the energy error.
-
-As a consequence of \eqref{norm_duality}, assume an energy norm $\left\| u \right\|_{E,1}$ is induced by a given test norm $\| v  \|_{V,1}$.
+We begin by using the strategy outlined in sections~\ref{sec:strategy1},~\ref{sec:strategy2}, and the estimates provided in~\ref{sec:strategy3} to prove the robust bound of the $L^2$ error in the field variables by the energy error.
+
+As a consequence of the duality of norms \eqref{norm_duality}, we know that the norm $\left\| u \right\|_{U,1}$ is induced by a specific test norm $\| v  \|_{V,1}$.
 To bound $\|\cdot\|_E$ robustly from above or below by a given norm $\left\| u \right\|_{U,2}$ on $U$ now only requires the robust bound in the opposite direction of $\| v \|_{V,1}$ by $\|v\|_{V,2}$.
@@
 \begin{proof}
-By \eqref{norm_duality}, for 
+By \eqref{norm_duality}, for $f$ and $g$ defined in \eqref{adjoint1} and \eqref{adjoint2},
 \begin{align*}
@@
 \]
-We will bound $\|\left(v,\tau\right)\|_V$ for all $\left(v,\tau\right)$ satisfying \eqref{adjoint} by decomposing $\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right)$ as described in section~\ref{sec:strategy2}.
-%where $\left(v_1,\tau_1\right)$ satisfies our adjoint equation \eqref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and 
+We will bound $\|\left(v,\tau\right)\|_V$ for all $\left(v,\tau\right)$ satisfying \eqref{adjoint} by decomposing $\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\taU,1\right) + \left(v_2,\taU,2\right)$ as described in section~\ref{sec:strategy2}.
+%where $\left(v_1,\taU,1\right)$ satisfies our adjoint equation \eqref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and 
 %\begin{align*}
@@
 %\end{align*} 
-%and $\left(v_2,\tau_2\right)$ satisfies \eqref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and 
+%and $\left(v_2,\taU,2\right)$ satisfies \eqref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and 
 %\begin{align*}
@@
 %\begin{align*}
-%\tau_2 \cdot n &= \epsilon n\cdot f - \epsilon n\cdot \grad v_2 = 0, \quad x\in \Gamma_- \cup \Gamma_0
+%\taU,2 \cdot n &= \epsilon n\cdot f - \epsilon n\cdot \grad v_2 = 0, \quad x\in \Gamma_- \cup \Gamma_0
 %\end{align*}
@@
 %\end{align*}
-%By $\left(v_0,\tau_0\right) = \left(v,\tau\right) - \left(v_1,\tau_1\right) - \left(v_2,\tau_2\right)$, $\left(v_0,\tau_0\right)$ must satisfy boundary conditions
+%By $\left(v_0,\tau_0\right) = \left(v,\tau\right) - \left(v_1,\taU,1\right) - \left(v_2,\taU,2\right)$, $\left(v_0,\tau_0\right)$ must satisfy boundary conditions
 %\begin{align*}
@@
 %\end{align*}
-Robustly bounding $\|\left(v,\tau\right)\|_V$ from above reduces to robustly bounding each component 
+By the triangle inequality, robustly bounding $\|\left(v,\tau\right)\|_V$ from above reduces to robustly bounding each component 
 \[
@@
 \]
+Roughly speaking, Lemma \ref{lemma_grad} concerns the robust control of $u$ by the energy error; Lemmas \ref{lemma_stream} and \ref{lemma_boundary} concern the robust control of field variable $\sigma$ and flux/trace variables, respectively.
+
 %\begin{align*}
@@
 
-%Given $\tau_1 \in H({\rm div};\Omega)$, $v\in H^1(\Omega)$, with boundary conditions \eqref{bc_1} and \eqref{bc_2}, $\frac{1}{\epsilon} \| [\tau_0\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v_0]\|_{\Gamma_h^0 \cup \Gamma_+}=0$.
+%Given $\taU,1 \in H({\rm div};\Omega)$, $v\in H^1(\Omega)$, with boundary conditions \eqref{bc_1} and \eqref{bc_2}, $\frac{1}{\epsilon} \| [\tau_0\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v_0]\|_{\Gamma_h^0 \cup \Gamma_+}=0$.
 With $f = 0$, Lemma \ref{lemma_grad} provides the bound
@@
 \]
-Noting that $\div \tau_1 = g+\beta\cdot \grad v_1$ gives $\|\div \tau_1 \| \lesssim \|g\|$ as well.  Lemma \ref{lemma_grad} gives
+Noting that $\div \taU,1 = g+\beta\cdot \grad v_1$ gives $\|\div \taU,1 \| \lesssim \|g\|$ as well.  Lemma \ref{lemma_grad} gives
 \[
@@
 \]
-and noting that $\epsilon^{-1/2}\tau_1 = \epsilon^{1/2}v_1$ gives $\epsilon\|\grad v_1\|^2 = \epsilon^{-1}\|\tau_1\|^2 \lesssim \|g\|^2$ as well.
+and noting that $\epsilon^{-1/2}\taU,1 = \epsilon^{1/2}v_1$ gives $\epsilon\|\grad v_1\|^2 = \epsilon^{-1}\|\taU,1\|^2 \lesssim \|g\|^2$ as well.
 
@@
 Lemma~\ref{lemma_grad} implies $\|\grad v\|^2  \lesssim  \| f\|^2$, so for $\epsilon \leq 1$, we control $\epsilon^{-1/2}\|\tau\| \leq \epsilon^{-1}\|\tau\| \lesssim \|f\|$.
-The remaining terms can be bounded by noting that, with $g = 0$, $\|\div \tau_2\| = \|\beta\cdot \grad v_2\| \lesssim \|\grad v_2\| \lesssim \|f\| $.
+The remaining terms can be bounded by noting that, with $g = 0$, $\|\div \taU,2\| = \|\beta\cdot \grad v_2\| \lesssim \|\grad v_2\| \lesssim \|f\| $.
 \end{itemize}
@@
 
-We have shown the robust bound of a norm on $U$ by energy error; for a full equivalence statement, we require a bound on the energy norm by some norm on $U$.
-By the duality of the energy and test norm, this is equivalent to bounding the test norm from below, using the test norm induced by the norm on $U$ bounding the energy norm.
+We have shown the robust bound of the norm $\|\cdot \|_{U,1}$ on $U$ by the energy norm; for a full equivalence statement, we require a bound on the energy norm by the norm $\|\cdot \|_{U,2}$ on $U$.
+By the duality of the energy and test norm, this is equivalent to bounding the test norm from below by the test norm induced by $\|\cdot \|_{U,2}$.
 \begin{lemma}
@@
 \end{align*}
-where $f$ and $g$ are again the loads of the adjoint problem \eqref{adjoint}.  By the triangle inequality, we have the bounds
+where $f$ and $g$ are again the loads of the adjoint problem defined in \eqref{adjoint1}, \eqref{adjoint2}.  By the triangle inequality, we have the bounds
 \begin{align*}
@@
 \end{align}
-and treat the cases $f=0$, $g=0$ separately.  The above boundary conditions are the reduced form of boundary conditions \eqref{bc_1} and \eqref{bc_2}.
+and treat the cases $f=0$, $g=0$ separately.
+The above boundary conditions are the reduced form of boundary conditions \eqref{bc_1} and \eqref{bc_2} corresponding to $\left.\tau\cdot n\right|_{\Gamma_-}=0$ and $\left.v\right|_{\Gamma_+}=0$.
 
@@
 \textcolor{red}{clearly define what we mean here with the density argument}
-
-Lemma \ref{lemma_grad} concerns the robust control of $u$ by the energy error; Lemmas \ref{lemma_stream} and \ref{lemma_boundary} concern the robust control of field variable $\sigma$ and flux/trace variables, respectively.
 
@@
 \]
-From here, the proof is identical to \cite{DPGrobustness}; an application of Peter-Paul Young's inequality to the right hand side and bounds on $\|v\|, \|\grad v\|$ by $\|w\|,\|\grad w\|$ complete the estimate.
+From here, the proof is identical to the final lines of the proof of Lemma 1 in \cite{DPGrobustness}; an application of Young's inequality (with $\delta$) to the right hand side and bounds on $\|v\|, \|\grad v\|$ by $\|w\|,\|\grad w\|$ complete the estimate.
 %ISSUE: REMOVE BOUNDARY TERM
@@
 
-It's worth addressing the effect of boundary conditions on stability.
+It is worth addressing the effect of boundary conditions on stability.
 Specifically, a test norm that provides stability for one set of boundary conditions may perform poorly for another set.
@@
 \]
-Notice that the final bilinear form is different; hence, the adjoint problems associated with Section~\ref{sec:strategy3} will now carry different boundary conditions as well.
-The stability properties proven here
+Notice that the boundary terms in the final bilinear form are different; hence, the adjoint problems associated with Section~\ref{sec:strategy3} will now carry different boundary conditions as well.
+Likewise, the stability properties proven previously will not hold under a different set of boundary conditions.
 %We note that 
@@
 \[
-v = \frac{e^{-\frac{x}{\epsilon}}}{e^{\frac{1}{\epsilon}}-1}\left(e^{\frac{1}{\epsilon}}\left(e^{\frac{x}{\epsilon}}-1\right) + \left(e^{\frac{1}{\epsilon}}-1\right)e^{\frac{x}{\epsilon}}x\right)
-\]
+v(x) = \frac{e^{-\frac{x}{\epsilon}}}{e^{\frac{1}{\epsilon}}-1}\left(e^{\frac{1}{\epsilon}}\left(e^{\frac{x}{\epsilon}}-1\right) + \left(e^{\frac{1}{\epsilon}}-1\right)e^{\frac{x}{\epsilon}}x\right)
+\]
+Plotting the solution shows that $v$ develops strong boundary layers of width $\epsilon$ near the inflow.
 Consequently, $\frac{\epsilon}{2} v'(0)^2 \approx \epsilon^{-1}$, indicating already a lack of robustness in the bound of $\|v'\|$ by $\|g\|$ for constant data\footnote{Unlike the case of Dirichlet boundary conditions, the inflow condition on $ \widehat{f} = u(0)-\epsilon u'(0)$ induces an adjoint boundary condition $\tau(0)=0$, or equivalently $v'(0) = 0$, removing the non-robust term from the estimate.}.
@@
 \]
-This modified test norm avoids boundary layers, but for adaptive meshes, provides additional stability in areas of heavy refinement, where best approximation error tends to be large and stronger robustness is most needed.
-This leads to a norm which is easily computable, but still provides \textit{asymptotically} the strongest test norm and tightest robustness results in the areas of highest error.
+This modified test norm avoids boundary layers, but for adaptive meshes, provides additional stability in areas of heavy refinement, where best approximation error tends to be large and stronger robustness is most necessary.
+This leads to a test norm which produces easily approximable optimal test functions, but still provides \textit{asymptotically} the strongest test norm and tightest robustness results in the areas of highest error.
 
@@
 In each numerical experiment, we vary $\epsilon = .01, .001, .0001$ in order to demonstrate robustness over a range of $\epsilon$.
-This is intended to mirror the numerical experiments in \cite{DPGrobustness}; for ``worst-case" linear solvers, such as LU decomposition without pivoting, the effect of roundoff error becomes evident in the solving of optimal test functions for $\epsilon \leq O(1e-5)$.
-The roundoff itself comes from the Gram matrix under certain test norms; for example, if the weighted $\left(H({\rm div};\Omega), H^1(\Omega)\right)$ norm is used for the test norm $\|\left(\tau,v\right)\|_V$ (as was done in \cite{DPG2}), for an element of size $h$, $\|v\|_{L^2}^2 = O(h)$, while $\|\grad v\|_{L^2}^2 = O(h^{-1})$.
+This is intended to mirror the experience with roundoff effects in numerical experiments \cite{DPGrobustness}; for ``worst-case" linear solvers, such as LU decomposition without pivoting, the effect of roundoff error becomes evident in the solving of optimal test functions for $\epsilon \leq O(1e-5)$.
+The roundoff itself comes from the conditioning of the Gram matrix under certain test norms; for example, if the weighted $\left(H({\rm div};\Omega), H^1(\Omega)\right)$ norm is used for the test norm $\|\left(\tau,v\right)\|_V$ (as was done in \cite{DPG2}), for an element of size $h$, $\|v\|_{L^2}^2 = O(h)$, while $\|\grad v\|_{L^2}^2 = O(h^{-1})$.
 As $h\rightarrow 0$, the seminorm portion of the test norm dominates the Gram matrix, leading to a near-singular and ill-conditioned system.
 
-The effect of roundoff error is often characterized by an increase in the energy error, which (assuming approximability of test functions) is proven to decrease for any series of refined meshes.
+The effect of roundoff error is often characterized by an increase in the energy error, which (assuming perfect approximability of test functions) is proven to decrease for any series of refined meshes.
 These roundoff effects are dependent primarily on the mesh, appearing when trying to fully resolve boundary layers for very small $\epsilon$.
@@
 \sigma_y &=  0, \quad y=0,1\\
+u &= 0, \quad x=1\\
 \end{align*}
@@
 \end{align*}
-The constants $C_n$ depend on a given inflow condition $u_0$ at $x=0$
+The constants $C_n$ depend on a given inflow condition $u_0$ at $x=0$ via the formula
 \[
@@
 \end{figure}
-We are especially interested in the ratio of energy error and total $L^2$ error in both $\sigma$ and $u$.
+We are especially interested in the ratio of energy error and total $L^2$ error in both $\sigma$ and $u$, which we denote as $\|u-u_h\|_{L^2}$.
 Stability estimates imply that, using the above test norm, $\|u-u_h\|_{L^2} / \|u-u_h\|_E \leq C$ independent of $\epsilon$.
-Figure~\ref{ratios_simple} seems to imply that, at least for this model problem, $C=O(1)$.
-Additionally, while we do not have a robust lower bound (i.e.\ $\|u-u_h\|_{L^2} / \|u-u_h\|_E$ can approach $0$ as $\epsilon \rightarrow 0$), our numerical results present a robust lower bound.
+Figure~\ref{ratios_simple}, which plots the ratio of $L^2$ to energy error, seems to imply that (at least for this model problem) $C=O(1)$.
+Additionally, while we do not have a robust lower bound ($\|u-u_h\|_{L^2} / \|u-u_h\|_E$ can approach $0$ as $\epsilon \rightarrow 0$), our numerical results appear to indicate the existence of an $\epsilon$-independent lower bound.
 
@@
 \end{figure}
-The effect of a mesh dependent test norm can be seen in the ratios of $L^2$ to energy error; as the mesh is refined, the constants in front of the $L^2$ terms for $v$ and $\tau$ converge to stationary values, and the ratio of $L^2$ to energy error transitions from a smaller to a larger value.
-The transition point happens later for smaller $\epsilon$, which we expect, since the transition of the ratio corresponds to the introduction of elements of order $\epsilon$ through mesh refinement.
-
-We examined smaller $\epsilon$ as well.
+The effect of a mesh dependent test norm can be seen in the ratios of $L^2$ to energy error; as the mesh is refined, the constants in front of the $L^2$ terms for $v$ and $\tau$ converge to stationary values (providing the full robustness implied by our adjoint energy estimates), and the ratio of $L^2$ to energy error transitions from a smaller to a larger value.
+The transition point happens later for smaller $\epsilon$, which we expect, since the transition of the ratio corresponds to the introduction of elements whose size is of order $\epsilon$ through mesh refinement.
+
+We examined how small $\epsilon$ needed to be in order to encounter roundoff effects as well.
 In \cite{DPGrobustness}, the smallest resolvable $\epsilon$ using only double precision arithmetic was $1e-4$.
@@
 
-Without anisotropic refinements, it still becomes computationally difficult to fully resolve the solution for smaller $\epsilon$.
-Regardless, for all ranges of $\epsilon$, the robustness of DPG remains constant, as indicted by the rates and ratio between $L^2$ and energy error in Figure~\ref{roundoff_figures}.
+Without anisotropic refinements, it still becomes computationally difficult to fully resolve the solution for $\epsilon$ smaller than $1e-5$.
+Regardless, for all ranges of $\epsilon$, DPG does not lose robustness, as indicted by the rates and ratio between $L^2$ and energy error in Figure~\ref{roundoff_figures} remaining bounded from both above and below.
 For $\epsilon = 1e-5$, we observe that the ratio of $L^2$ error increases, corresponding to the scaling of the test norm with mesh size (the transition in test norm occurs after 8 refinements, which, for an initial $4\times 4$ mesh, implies a minimum element size of about $1.5e-05$.
 At this point, rescaled test norm allows us to take advantage of the full magnitude of the $L^2$ term for $\|v\|$ and $\|\tau\|$ implied by our adjoint estimates).
-By analogy, for smaller $\epsilon = 1e-6, 1e-7$, the transition period should begin near the 10th and 11th refinement iterations; however, we do not observe such behavior.
-For $\epsilon=1e-6$, the ratio simply remains constant, but for $\epsilon=1e-7$, we observe roundoff effects, as the energy error increases at the 11th refinement.
+By analogy, for smaller $\epsilon = 1e-6, 1e-7$, the transition period should begin near the 10th and 11th refinement iterations; however, we do not observe such behavior, possibly due to roundoff effects.
+For $\epsilon=1e-6$, the ratio simply remains constant, but for $\epsilon=1e-7$, we observe definite roundoff effects, as the energy error increases at the 11th refinement.
 Since DPG is optimal in the energy norm for a fixed test norm\footnote{While the test norm changes with the mesh, it increases monotonically.
@@
 The hope is that for small $\epsilon$, this omission will be negligible.
-Figure~\ref{ratios_noSigma} indicates that, between $\epsilon = .005$ and $\epsilon = .001$, the omission of $\sigma_n$ in the boundary condition becomes negligible, and both our error rates and ratios of $L^2$ to energy error become identical to the case where $\sigma_n$ is explicitly accounted for, well within the range of $\epsilon$ of physical interest.
+Figure~\ref{ratios_noSigma} indicates that, between $\epsilon = .005$ and $\epsilon = .001$, the omission of $\sigma_n$ in the boundary condition becomes negligible, and both our error rates and ratios of $L^2$ to energy error become identical to the case where $\sigma_n$ is explicitly accounted for in the inflow condition.
 For large $\epsilon = .01$, the $L^2$ error stagnates around $1e-3$, or about $7\%$ relative error.
@@
 Figure~\ref{disc_sol} shows the solution $u$ and overlaid trace variable $\widehat{u}$, which both demonstrate the regularizing effect of viscosity on the discontinuous boundary condition at $x=0$.
-In order to compare with an exact solution, we approximate $u_0$ with 20 terms of a Fourier series, giving a near-discontinuity for $u_0$.
+However, we do not have a closed-form solution with which to compare results for a stricly discontinuous $u_0$.
+In order to analyze convergence, we approximate $u_0$ with 20 terms of a Fourier series, giving a near-discontinuity for $u_0$.
 
@@
 \end{figure}
-The ratios of $L^2$ to energy error are now less predictable than for the previous example, due to the ``moving target" nature of the approximation of oscillatory boundary conditions.
+
+The ratios of $L^2$ to energy error are now less predictable than for the previous example, in part due to the difficulty in approximating highly oscillatory boundary conditions.
 The numerical experiments were originally performed by applying boundary conditions via interpolation; the result was that the highly oscillatory inflow boundary condition was not sampled enough to be properly resolved, causing the solution to converge to a solution different than the exact solution.
 The experiments were repeated using the penalty method to enforce inflow conditions; however, we note that the proper way to do so is to use an $L^2$ projection at the boundary.
-When using the penalty method, however, the ratios still remain bounded and close to $1$ for $\epsilon$ varying over two orders of magnitude, as predicted by theory.
+Even when using the penalty method, however, the ratios still remain bounded and close to $1$ for $\epsilon$ varying over two orders of magnitude, as predicted by theory.
 

### 2012-04-03 docs/NewBCRobustness_paper/paper.tex
fixed a typo
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@426 36274a68-8941-4c93-80ef-affaed5139da

@@
 \[
-\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\taU,2\right),
+\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right),
 \]
@@
 \end{align*} 
-Likewise, we define $\left(v_2,\taU,2\right)$ as satisfying
-\begin{align*}
-\epsilon^{-1}\taU,2 + \grad v_2 &= \epsilon^{-1}\tau + \grad v = f\\
-\div \taU,2 - \beta\cdot \grad v_2 &= 0
-\end{align*}
-We will additionally require both $\left(\tau_1,v_1\right)$ and $\left(\taU,2,v_2\right)$ to come from $H({\rm div}, \Omega)\times H^1(\Omega)$, and to satisfy boundary conditions
+Likewise, we define $\left(v_2,\tau_2\right)$ as satisfying
+\begin{align*}
+\epsilon^{-1}\tau_2 + \grad v_2 &= \epsilon^{-1}\tau + \grad v = f\\
+\div \tau_2 - \beta\cdot \grad v_2 &= 0
+\end{align*}
+We will additionally require both $\left(\tau_1,v_1\right)$ and $\left(\tau_2,v_2\right)$ to come from $H({\rm div}, \Omega)\times H^1(\Omega)$, and to satisfy boundary conditions
 \begin{align}
@@
 \end{align*}
-By $\left(v_0,\tau_0\right) = \left(v,\tau\right) - \left(v_1,\tau_1\right) - \left(v_2,\taU,2\right)$, $\left(v_0,\tau_0\right)$ must satisfy boundary conditions
+By $\left(v_0,\tau_0\right) = \left(v,\tau\right) - \left(v_1,\tau_1\right) - \left(v_2,\tau_2\right)$, $\left(v_0,\tau_0\right)$ must satisfy boundary conditions
 \begin{align}
@@
 Bounding $\|\left(\tau_0,v_0\right)\|$ requires the use of techniques and decompositions first developed in \cite{analysisDPG} and adapted to convection-diffusion in \cite{DPGrobustness}.
-However, due to the $H({\rm div}, \Omega)\times H^1(\Omega)$ conforming nature of $\left(\tau_1,v_1\right)$ and $\left(\taU,2,v_2\right)$, the bound from above of test functions $\|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|g\|$ is reduced to proving classical error estimates for the adjoint equations
+However, due to the $H({\rm div}, \Omega)\times H^1(\Omega)$ conforming nature of $\left(\tau_1,v_1\right)$ and $\left(\tau_2,v_2\right)$, the bound from above of test functions $\|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|g\|$ is reduced to proving classical error estimates for the adjoint equations
 \begin{align}
@@
 \]
-We will bound $\|\left(v,\tau\right)\|_V$ for all $\left(v,\tau\right)$ satisfying \eqref{adjoint} by decomposing $\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\taU,1\right) + \left(v_2,\taU,2\right)$ as described in section~\ref{sec:strategy2}.
-%where $\left(v_1,\taU,1\right)$ satisfies our adjoint equation \eqref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and 
+We will bound $\|\left(v,\tau\right)\|_V$ for all $\left(v,\tau\right)$ satisfying \eqref{adjoint} by decomposing $\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right)$ as described in section~\ref{sec:strategy2}.
+%where $\left(v_1,\tau_1\right)$ satisfies our adjoint equation \eqref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and 
 %\begin{align*}
@@
 %\end{align*} 
-%and $\left(v_2,\taU,2\right)$ satisfies \eqref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and 
+%and $\left(v_2,\tau_2\right)$ satisfies \eqref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and 
 %\begin{align*}
@@
 %\begin{align*}
-%\taU,2 \cdot n &= \epsilon n\cdot f - \epsilon n\cdot \grad v_2 = 0, \quad x\in \Gamma_- \cup \Gamma_0
+%\tau_2 \cdot n &= \epsilon n\cdot f - \epsilon n\cdot \grad v_2 = 0, \quad x\in \Gamma_- \cup \Gamma_0
 %\end{align*}
@@
 %\end{align*}
-%By $\left(v_0,\tau_0\right) = \left(v,\tau\right) - \left(v_1,\taU,1\right) - \left(v_2,\taU,2\right)$, $\left(v_0,\tau_0\right)$ must satisfy boundary conditions
+%By $\left(v_0,\tau_0\right) = \left(v,\tau\right) - \left(v_1,\tau_1\right) - \left(v_2,\tau_2\right)$, $\left(v_0,\tau_0\right)$ must satisfy boundary conditions
 %\begin{align*}
@@
 
-%Given $\taU,1 \in H({\rm div};\Omega)$, $v\in H^1(\Omega)$, with boundary conditions \eqref{bc_1} and \eqref{bc_2}, $\frac{1}{\epsilon} \| [\tau_0\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v_0]\|_{\Gamma_h^0 \cup \Gamma_+}=0$.
+%Given $\tau_1 \in H({\rm div};\Omega)$, $v\in H^1(\Omega)$, with boundary conditions \eqref{bc_1} and \eqref{bc_2}, $\frac{1}{\epsilon} \| [\tau_0\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v_0]\|_{\Gamma_h^0 \cup \Gamma_+}=0$.
 With $f = 0$, Lemma \ref{lemma_grad} provides the bound
@@
 \]
-Noting that $\div \taU,1 = g+\beta\cdot \grad v_1$ gives $\|\div \taU,1 \| \lesssim \|g\|$ as well.  Lemma \ref{lemma_grad} gives
+Noting that $\div \tau_1 = g+\beta\cdot \grad v_1$ gives $\|\div \tau_1 \| \lesssim \|g\|$ as well.  Lemma \ref{lemma_grad} gives
 \[
@@
 \]
-and noting that $\epsilon^{-1/2}\taU,1 = \epsilon^{1/2}v_1$ gives $\epsilon\|\grad v_1\|^2 = \epsilon^{-1}\|\taU,1\|^2 \lesssim \|g\|^2$ as well.
+and noting that $\epsilon^{-1/2}\tau_1 = \epsilon^{1/2}v_1$ gives $\epsilon\|\grad v_1\|^2 = \epsilon^{-1}\|\tau_1\|^2 \lesssim \|g\|^2$ as well.
 
@@
 Lemma~\ref{lemma_grad} implies $\|\grad v\|^2  \lesssim  \| f\|^2$, so for $\epsilon \leq 1$, we control $\epsilon^{-1/2}\|\tau\| \leq \epsilon^{-1}\|\tau\| \lesssim \|f\|$.
-The remaining terms can be bounded by noting that, with $g = 0$, $\|\div \taU,2\| = \|\beta\cdot \grad v_2\| \lesssim \|\grad v_2\| \lesssim \|f\| $.
+The remaining terms can be bounded by noting that, with $g = 0$, $\|\div \tau_2\| = \|\beta\cdot \grad v_2\| \lesssim \|\grad v_2\| \lesssim \|f\| $.
 \end{itemize}

### 2012-04-03 src/Basis/BasisCache.cpp
Implemented prototype for a unified LinearTerm integration method.  Made BF::stiffnessMatrix() use it.  Appears to work.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@427 36274a68-8941-4c93-80ef-affaed5139da

@@ -357,6 +357,14 @@ void BasisCache::setSideNormals(FieldContainer<double> &sideNormals) {
   _sideNormals = sideNormals;
 }
 
+const FieldContainer<double> & BasisCache::getCellSideParities() {
+  return _cellSideParities;
+}
+
+void BasisCache::setCellSideParities(const FieldContainer<double> &cellSideParities) {
+  _cellSideParities = cellSideParities;
+}
+
 void BasisCache::setPhysicalCellNodes(const FieldContainer<double> &physicalCellNodes, 
                                       const vector<int> &cellIDs, bool createSideCacheToo) {
   discardPhysicalNodeInfo(); // necessary to get rid of transformed values, which will no longer be valid

### 2012-04-03 src/ScratchPad/BF.cpp

@@ -57,120 +57,140 @@ void BF::printTrialTestInteractions() {
   cout << "BF::printTrialTestInteractions() not yet implemented.\n";
 }
 
+// new, EXPERIMENTAL stiffnessMatrix implementation
+// using the new, EXPERIMENTAL LinearTerm::integrate() 
 void BF::stiffnessMatrix(FieldContainer<double> &stiffness, Teuchos::RCP<ElementType> elemType,
-                     FieldContainer<double> &cellSideParities, Teuchos::RCP<BasisCache> basisCache) {
+                         FieldContainer<double> &cellSideParities, Teuchos::RCP<BasisCache> basisCache) {
   // stiffness is sized as (C, FTest, FTrial)
-  DofOrderingPtr trialOrdering = elemType->trialOrderPtr;
-  DofOrderingPtr testOrdering = elemType->testOrderPtr;
-  FieldContainer<double> physicalCubaturePoints = basisCache->getPhysicalCubaturePoints();
-  
-  unsigned numCells = physicalCubaturePoints.dimension(0);
-  unsigned numPoints = physicalCubaturePoints.dimension(1);
-  unsigned spaceDim = physicalCubaturePoints.dimension(2);
-  
-  shards::CellTopology cellTopo = basisCache->cellTopology();
-  
-  Teuchos::Array<int> ltValueDim;
-  ltValueDim.push_back(numCells);
-  ltValueDim.push_back(0); // # fields -- empty until we have a particular basis
-  ltValueDim.push_back(numPoints);
-  
   stiffness.initialize(0.0);
+  basisCache->setCellSideParities(cellSideParities);
   
   for ( vector< BilinearTerm >:: iterator btIt = _terms.begin();
        btIt != _terms.end(); btIt++) {
     BilinearTerm bt = *btIt;
     LinearTermPtr trialTerm = btIt->first;
     LinearTermPtr testTerm = btIt->second;
-    set<int> trialIDs = trialTerm->varIDs();
-    set<int> testIDs = testTerm->varIDs();
-    
-    int rank = trialTerm->rank();
-    TEST_FOR_EXCEPTION( rank != testTerm->rank(), std::invalid_argument, "test and trial ranks disagree." );
-    
-    set<int>::iterator trialIt;
-    set<int>::iterator testIt;
-    
-    Teuchos::RCP < Intrepid::Basis<double,FieldContainer<double> > > trialBasis, testBasis;
-    
[…]

### 2012-04-03 src/ScratchPad/LinearTerm.cpp

@@ -91,6 +91,136 @@ VarType LinearTerm::termType() const {
   return _termType; 
 }
 
+void LinearTerm::integrate(FieldContainer<double> &values, DofOrderingPtr thisOrdering, 
+                           LinearTermPtr otherTerm, DofOrderingPtr otherOrdering, 
+                           BasisCachePtr basisCache, bool forceBoundaryTerm) {
+  // values has dimensions (numCells, thisFields, otherFields)
+  
+  int numCells = values.dimension(0);
+  int numPoints = basisCache->getPhysicalCubaturePoints().dimension(1);
+  int spaceDim = basisCache->getPhysicalCubaturePoints().dimension(2);
+  
+  set<int> otherIDs = otherTerm->varIDs();
+  
+  int rank = this->rank();
+  TEST_FOR_EXCEPTION( rank != otherTerm->rank(), std::invalid_argument, "other and this ranks disagree." );
+  
+  set<int>::iterator thisIt;
+  set<int>::iterator otherIt;
+  
+  Teuchos::RCP < Intrepid::Basis<double,FieldContainer<double> > > thisBasis, otherBasis;
+  
+  bool thisFluxOrTrace  = (     this->termType() == FLUX) || (     this->termType() == TRACE);
+  bool otherFluxOrTrace = (otherTerm->termType() == FLUX) || (otherTerm->termType() == TRACE);
+
+  bool boundaryTerm = thisFluxOrTrace || otherFluxOrTrace || forceBoundaryTerm;
+  
+  Teuchos::Array<int> ltValueDim;
+  ltValueDim.push_back(numCells);
+  ltValueDim.push_back(0); // # fields -- empty until we have a particular basis
+  ltValueDim.push_back(numPoints);
+  
+  // num "sides" for volume integral: 1...
+  int numSides = boundaryTerm ? basisCache->cellTopology().getSideCount() : 1;
+  for (int sideIndex = 0; sideIndex < numSides; sideIndex++) {
+    int numPointsSide;
+    if (boundaryTerm) { 
+      numPointsSide = basisCache->getPhysicalCubaturePointsForSide(sideIndex).dimension(1);
+    } else {
+      numPointsSide = -1;      
+    }
+    
+    for (otherIt= otherIDs.begin(); otherIt != otherIDs.end(); otherIt++) {
+      int otherID = *otherIt;
+      otherBasis = otherOrdering->getBasis(otherID);
[…]

### 2012-04-03 src/include/BasisCache.h

@@ -75,6 +75,7 @@ private:
   FieldContainer<double> _cellJacobDet;
   FieldContainer<double> _weightedMeasure;
   FieldContainer<double> _physCubPoints;
+  FieldContainer<double> _cellSideParities;
   
   // eventually, will likely want to have _testOrdering, too--and RCP's would be better than copies (need to change constructors)
   DofOrdering _trialOrdering;
@@ -143,6 +144,7 @@ public:
   
   const FieldContainer<double> & getPhysicalCubaturePoints();
   const FieldContainer<double> & getPhysicalCubaturePointsForSide(int sideOrdinal);
+  const FieldContainer<double> & getCellSideParities();
   
   const FieldContainer<double> & getSideUnitNormals(int sideOrdinal);
   
@@ -154,6 +156,7 @@ public:
   void setRefCellPoints(const FieldContainer<double> &pointsRefCell);
   const FieldContainer<double> & getSideNormals();
   void setSideNormals(FieldContainer<double> &sideNormals);
+  void setCellSideParities(const FieldContainer<double> &cellSideParities);
 };
 
 typedef Teuchos::RCP<BasisCache> BasisCachePtr;

### 2012-04-03 docs/NewBCRobustness_paper/paper.tex
fixed typos
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@428 36274a68-8941-4c93-80ef-affaed5139da

@@
 An additional complication of singularly perturbed problems is that very often, in the limiting case of the parameter blowing up or decreasing to zero, the partial differential equation itself will change form.
-A canonical example is the convection-diffusion equation.
+A canonical example is the convection-diffusion equation with Dirichlet boundary conditions.
 In 1D, this equation is
-\[
-u'-\epsilon u'' = f.
-\]
+\begin{align*}
+u'-\epsilon u'' &= f
+\end{align*}
 The equation represents the change in the concentration of some quantity $u$ in some medium from both convective and diffusive effects.
 The parameter $\epsilon$ represents the diffusivity, and in the limit of an inviscid medium as $\epsilon\rightarrow 0$, the partial differential equation changes types, going from a parabolic to a hyperbolic equation.
-
-The finite element method has notoriously performed poorly for this example, and for many other singularly perturbed equations.
+For Dirichlet boundary conditions $u(0)=u_0$ and $u(1)= u_1$, the solution can develop sharp boundary layers of order $\epsilon$ near the outflow.
+
+The finite element method has notoriously performed poorly for both this example, and for many other singularly perturbed problems.
 This poor performance is captured by the error bound for the finite element method applied to convection-diffusion equations
@@
 Intuitively, as our singular perturbation parameter changes, our finite element error is bounded more and more loosely by the best approximation error, allowing for more and more error in the finite element solution for as $\epsilon$ shrinks.
-
-A well-known example of this loss of robustness is the growth of spurious oscillations in the finite element solution of the 1D convection-diffusion problem $ u'-\epsilon u'' = f$ (with Dirichlet boundary conditions) as $\epsilon\rightarrow 0$.
-For small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation develops oscillations of magnitude $O(\epsilon^{-1})$.
-Another class of examples are wave propagation problems, in which the singular perturbation parameter is the wavenumber, $k\rightarrow \infty$.
-The lack of robustness in this case manifests as ``pollution" error, a phenomenon where the finite element solution degrades over many wavelengths for high wavenumbers (commonly manifesting as a phase error between the FE solution and the exact solution).
+The manifestation of this loss of robustness in the finite element solution of the 1D convection-diffusion problem is the growth of spurious oscillations as $\epsilon\rightarrow 0$.
+For a coarse mesh and small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation develops oscillations of magnitude $O(\epsilon^{-1})$.
+
+Another example of a singular perturbation problem which experiences loss of robustness is high frequency wave propagation problems, in which the singular perturbation parameter is the wavenumber, $k\rightarrow \infty$.
+The loss of robustness in this case manifests as ``pollution" error, a phenomenon where the finite element solution degrades over many wavelengths for high wavenumbers (commonly manifesting as a phase error between the FE solution and the exact solution).
 
@@
 \]
-As a consequence of this fact, without knowing the exact solution, the actual energy error $\|u-u_h\|_E$ is computable through $\|e_h\|_V$, where
-\[
-\left(e_h,\delta v\right)_V = b(u-u_h,v) = b(u_h,v)-l(v)
-\]
-This is simply a consequence of the least-squares nature of DPG; the energy error is simply the measure of the residual in the proper norm.
+Due to the isometry of the Riesz map, this is equivalent to measuring the norm of the functional $b(u,v) = l_u(v)\in V'$ in the dual norm.
+An additional consequence of adopting such an energy norm is that, without knowing the exact solution, the actual energy error $\|u-u_h\|_E$ is computable through $\|e_h\|_V$, where
+\[
+\left(e_h,\delta v\right)_V = b(u-u_h,\delta v) = b(u_h,\delta v)-l(\delta v)
+\]
+This is simply a consequence of the least-squares nature of DPG; the energy error is simply the measure of the residual in the proper norm - the dual norm on $V$.
 
@@
 The DPG (discontinuous Petrov-Galerkin) method is the pairing of the concept of locally computable optimal test functions with the so-called ``ultra-weak formulation".
-For a given operator equation $Au = f$, the ultra-weak formulation is
+For a given operator equation in strong form $Au = f$, the ultra-weak formulation is
 \[
@@
 \]
-where $A^*$ is the formal adjoint resulting from integration by parts, and $[v]$ is the jump of $v$ across element boundaries.
+where $A^*$ is the formal adjoint resulting from integration by parts, and $[v]$ is the jump of the test function $v$ across element boundaries.
+Both the inner product and formal adjoint are understood in an element-wise fashion.
 Under the ultra-weak formulation, the regularity requirement on each solution variable is relaxed through integration by parts.
 Moreover, to maintain conformity while seeking an $L^2$ setting on interior ``field" variables, boundary terms are identified as additional new unknowns.
-The result is a hybridized DG method with locally supported optimal test functions.
+The result is a hybridized DG method with locally supported optimal test functions, with energy setting
+\begin{align*}
+u&\in L^2(\Omega)\\
+v&\in V=D(A^*) \\
+\widehat{u}&\in T(D(A))
+\end{align*}
+where $D(A^*)$ is the domain of the formal adjoint $A^*$, and $T(D(A))$ is the trace space of the domain of the operator $A$ in its strong form.
+A more comprehensive discussion of the abstract setting of DPG, as well as a proof of well-posedness, is developed using the graph norm in \cite{DPGFriedrichs}.
 
@@
 The duality between test norm and variational form holds for any particular variational form, though it is often difficult to determine analytically the form of $\|v\|_{V,U}$.
-Whether a particular choice of norm on $V$ norm is ``good" or not is problem-dependent; however, for the DPG ultra-weak formulation, there is an important canonical test norm that results from a specific induced norm on $U$.
+Whether a particular choice of norm on $V$ norm is ``good" or not is problem-dependent; however, for the DPG ultra-weak formulation, there is an important canonical test norm that is induced by a specific norm on $U$.
 
@@
 \end{align*}
-with the corresponding variational form (modulo application of boundary conditions)
+with the corresponding variational form (prior to the application of boundary conditions)
 \begin{align*}
@@
 %$\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_U \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E$.
+
+Intuitively,
+
 \textcolor{red}{Explain in intuitive terms what the bounds above and below mean.}

### 2012-04-03 docs/NewBCRobustness_paper/paper.tex
added more to singularly perturbed problems, fixed red note areas, added explanation of why beta\cdot \grad doesn't cause boundayr layers
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@429 36274a68-8941-4c93-80ef-affaed5139da

@@
 The most well-known example of this is the streamline-upwind Petrov-Galerkin method, which is a stabilized method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.
-\textcolor{red}{TO DO: give motivations for consistency (converges to same solution) of stabilization terms vs artificial diffusion type stabilization and, show how consistency gives a Petrov-Galerkin method}
+An important difference between residual-based stabilization techniques and other stabilizations is the idea of \textit{consistency} - by adding stabilization terms based on the residual, the exact solution still satisfies the same variational problem (i.e Galerkin orthogonality still holds)\footnote{Contrast this to an artificial diffusion method, where a specific amount of additional viscosity is added based on the interplay between the convection and diffusion terms.
+The exact solution to the original equation no longer satisfies the new stabilized formulation.}.
 
@@
 \end{align*}
-where $n$ is the outward normal vector to an element edge, and ${\rm sgn}(n)$ is 1 if $n$ aligns with a preset global orientation, and $-1$ otherwise.
+where $n$ is the outward normal vector to an element edge, and ${\rm sgn}(n)$ is 1 if $n$ aligns with a given global orientation, and $-1$ otherwise.
 \textcolor{red}{I need to find more simple way to explain sgn}.
@@
 The avoidance of boundary layers in the test norm will be described in more detail in the section detailing numerical experiments.
-\textcolor{red}{Why are we allowed to have $\beta\cdot \grad v$ of order 1 while we have other terms of order $O({\rm Pe})$?
-Why does this term not induce boundary layers?}.
-We focus first on showing the condition on robustness.
+We focus first on quantifying the condition on robustness.
 Such a condition is equivalent to showing the robust boundedness of the energy error from above and below by norms on $U$
@@
 where $\lesssim$ denotes a bound by a constant that will not grow as $\epsilon \rightarrow 0$.
-%$\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_U \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E$.
-
-Intuitively,
-
+%The robust bound on the error in $\|\cdot\|_E$ from below by error in $\|\cdot\|_{U,1}$ is crucial to avoiding the instabilities associated with loss of robustness -
 \textcolor{red}{Explain in intuitive terms what the bounds above and below mean.}
 Our goal is to explicitly derive the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ that characterize this relation, taking into account the limiting case of $\epsilon \rightarrow 0$.
+
 Our strategy for doing so is broken down into three parts.
@@
 While the upper bound is robust, we have derived such a bound only by explicitly accounting for a factor of $\epsilon^{-1/2}$ in the bounding norm $\|\cdot \|_{U,2}$.
-This implies that for very small $\epsilon$, the $L^2$ error may be much smaller than the energy error.
-However, \textcolor{red}{explain why this is OK practically.}
-Additionally, numerical experiments demonstrate much better results, and suggest that, at least for our example problems, $\|u-u_h\|_E \sim \|u-u_h\|_{U}$, implying that the induced energy norm is equivalent to a norm on the group variable $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)$ that does not grow with $\epsilon$.
+This implies that for very small $\epsilon$, the $L^2$ error may be much smaller than the energy error (in this sense, DPG may lose some efficiency for small $\epsilon$, though it is still guaranteed against losing robustness and stability).
+However, numerical experiments demonstrate much better results, and suggest that, at least for our example problems, $\|u-u_h\|_E \sim \|u-u_h\|_{U}$, implying that the induced energy norm may be equivalent to a norm on the group variable $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)$ that does not grow with $\epsilon$.
 
@@
 \]
-Notice that the boundary terms in the final bilinear form are different; hence, the adjoint problems associated with Section~\ref{sec:strategy3} will now carry different boundary conditions as well.
+%Notice that the boundary terms in the final bilinear form are different; hence, the adjoint problems associated with Section~\ref{sec:strategy3} will now carry different boundary conditions as well.
 Likewise, the stability properties proven previously will not hold under a different set of boundary conditions.
@@
 However, we are unable to prove this in the case of Dirichlet boundary conditions.
+
 The robust bounds given in Section~\ref{sec:main_bounds} hold in arbitrary dimension; however, we can show that for the case of Dirichlet boundary conditions, the same results will not hold, even in 1D.
@@
 We can assume without loss of generality that $\Omega_h$ is the unit interval $(0,1)$.
-A norm for can be defined through $$\|u\|_U = C_1\|u\|_{L^2} + C_2\|\sigma\|_{L^2} + C_3\sum_k \left(|\widehat{u}|+ |\widehat{f}|\right),$$ as the fluxes are simply point values in 1D.
-The induced norm $\|\left(\tau,v\right)\|_{V,U}$ is
-\begin{align*}
-\|\left(\tau,v\right)\|_{V,U} &= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}\right)} \frac{ (u,\tau'-v')_{\Omega_h}+ \left(\sigma,\epsilon^{-1}\tau + v'\right)_{\Omega_h}+\sum_k \left(\widehat{u}(x_k) [\tau(x_k)] + \widehat{f}(x_k) [v(x_k)]\right)}{C_1\|u\|_{L^2} + C_2\|\sigma\|_{L^2} + C_3\sum_k \left(|\widehat{u}|+ |\widehat{f}|\right)}\\
-&\leq \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\sum_k \left([\tau(x_k)] +[v(x_k)]\right)
-\end{align*}
-for $f = \epsilon^{-1}\tau + v'$ and $g = \tau'-v'$.
+
+%A norm for can be defined through $$\|u\|_U = C_1\|u\|_{L^2} + C_2\|\sigma\|_{L^2} + C_3\sum_k \left(|\widehat{u}|+ |\widehat{f}|\right),$$ as the fluxes are simply point values in 1D.  
+%The induced norm $\|\left(\tau,v\right)\|_{V,U}$ is
+%\begin{align*}
+%\|\left(\tau,v\right)\|_{V,U} &= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}\right)} \frac{ (u,\tau'-v')_{\Omega_h}+ \left(\sigma,\epsilon^{-1}\tau + v'\right)_{\Omega_h}+\sum_k \left(\widehat{u}(x_k) [\tau(x_k)] + \widehat{f}(x_k) [v(x_k)]\right)}{C_1\|u\|_{L^2} + C_2\|\sigma\|_{L^2} + C_3\sum_k \left(|\widehat{u}|+ |\widehat{f}|\right)}\\
+%&\leq \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\sum_k \left([\tau(x_k)] +[v(x_k)]\right)
+%\end{align*}
+%for $f = \epsilon^{-1}\tau + v'$ and $g = \tau'-v'$.
 
@@
 Intuitively, the adjoint problem is similar to the primal problem with the direction of inflow reversed, such that the inflow becomes the outflow, and outflow inflow.
-The need for the weight arises due to the presence of the Dirichlet boundary condition on $v$ near the inflow; this induces strong boundary layers at the inflow such that $\grad v \approx O(\epsilon^{-1})$.
+The need for the weight arises due to the presence of the Dirichlet boundary condition on $v$ near the inflow; this induces strong boundary layers at the inflow such that $\grad v \approx \epsilon \|\grad v\|^2 \approx O(\epsilon^{-1})$.
 An interesting phenomenon observed is that, for sufficiently small $\epsilon$, these issues manifest themselves in numerical experiments as additional refinements near the inflow\footnote{Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
@@
 \]
-However, the presence of both $\|v\|$ and $\epsilon\|\grad v\|$ terms, and similarly $\|\div \tau\|$ and $\frac{1}{\epsilon}\|\tau\|$ terms, induces boundary layers in the optimal test functions, though only in the crosswind direction.
-To avoid this effect, we follow \cite{DPGrobustness} in scaling the $L^2$ contributions of $v$ and $\tau$ such that, when transformed to the reference element, both $v$ and $\grad v$ terms are $O(1)$.
-In this paper, we consider only isotropic refinements on quadrilateral elements, such that $h_1 = h_2 = h$, and $|K| = h^2$.
+However, the presence of both $\|v\|$ and $\epsilon\|\grad v\|$ terms, and similarly $\|\div \tau\|$ and $\frac{1}{\epsilon}\|\tau\|$ terms, induces boundary layers in the optimal test functions.
+We can see this by recovering the strong form of the variational problem defining test functions.
+Assume first that $\tau = 0$.
+Then, assuming $\div \beta = 0$ for illustrative purposes, we have
+\begin{align*}
+\left(\left(0,v\right),\left(\delta\tau,\delta v\right)\right)_{V} &= (v,\delta v) + \epsilon \left(\grad v,\grad \delta v\right) + \left(\beta \cdot \grad v, \beta \cdot \grad \delta v\right)\\
+&= \left(v - \epsilon \Delta v - \div \left(\left(\beta \otimes \beta\right) \grad v\right), \delta v\right)_{L^2} + \langle \epsilon \grad v\cdot n, \delta v\rangle + \langle n\cdot \left(\beta\otimes\beta\right) \grad v , \delta v\rangle
+\end{align*}
+after integration by parts, recovering the strong form of the operator $L$ inducing such a variational problem 
+\[
+Lv \coloneqq v - \epsilon \Delta v - \div \left(\left(\beta \otimes \beta\right) \grad v\right)
+\]
+The streamline direction $\beta$ induces an anisotropic diffusion, while the $\epsilon\|\grad v\|_{L^2}$ term induces a small isotropic diffusion contribution everywhere.
+Any vector in the cross-stream direction is in the null space of the anisotropic diffusion tensor, such that in the cross-stream directions, the optimal test function is governed only by the cross-stream part of the operator $L$
+\[
+L_{\rm cross} \coloneqq v - \epsilon \Delta v 
+\]
+and may develop boundary layers of width $\epsilon$ in those directions.
+To avoid boundary layers in the optimal test functions, we follow \cite{DPGrobustness} in scaling the $L^2$ contributions of $v$ and $\tau$ such that, when transformed to the reference element, both $v$ and $\grad v$ terms are $O(1)$.
+In this paper, we consider only isotropic refinements on quadrilateral elements in 2D, such that $h_1 = h_2 = h$, and $|K| = h^2$.
 Our test norm for an element $K$ is now

### 2012-04-04 docs/NewBCRobustness_paper/paper.tex
correct my last name
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@435 36274a68-8941-4c93-80ef-affaed5139da
some fast corrections and comments need to be resolved
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@436 36274a68-8941-4c93-80ef-affaed5139da

@@
 
-\author{Tan Bui \and Jesse Chan \and Leszek Demkowicz \and Norbert Heuer}
+\author{Tan Bui-Thanh \and Jesse Chan \and Leszek Demkowicz \and Norbert Heuer}
 \title{Robust DPG stability II}
@@
 
-The DPG (discontinuous Petrov-Galerkin) method is the pairing of the concept of locally computable optimal test functions with the so-called ``ultra-weak formulation".
+The discontinuous Petrov-Galerkin (DPG) method is the pairing of the concept of locally computable optimal test functions with the so-called ``ultra-weak formulation".
 For a given operator equation in strong form $Au = f$, the ultra-weak formulation is
@@
 \]
-where $A^*$ is the formal adjoint resulting from integration by parts, and $[v]$ is the jump of the test function $v$ across element boundaries.
-Both the inner product and formal adjoint are understood in an element-wise fashion.
-Under the ultra-weak formulation, the regularity requirement on each solution variable is relaxed through integration by parts.
-Moreover, to maintain conformity while seeking an $L^2$ setting on interior ``field" variables, boundary terms are identified as additional new unknowns.
-The result is a hybridized DG method with locally supported optimal test functions, with energy setting
+where $A^*$ is the formal adjoint resulting from integration by parts,
+and $[v]$ is the jump of the test function $v$ across element
+boundaries.  Both the inner product and formal adjoint are understood
+in an element-wise fashion. Under the ultra-weak formulation, the
+regularity requirement on each solution variable is relaxed through
+integration by parts.  Moreover, to maintain conformity while seeking
+an $L^2$ setting on interior ``field" variables, boundary terms are
+identified as additional new unknowns.  The result is a hybridized DG \textcolor{blue}{TB: This is not true, the hybridized DG method does not hybridize both traces/fluxes}
+method with locally supported optimal test functions, with energy
+setting
 \begin{align*}
@@
 \[
-\|u\|_E = \sup \frac{b(u,v)}{\|v\|_V}.
-\]
-depends heavily on our choice of norm on the test space $\|v\|_V$.
+\|u\|_E = \sup_{v \in V\setminus \{0\}} \frac{b(u,v)}{\|v\|_{V,E}}.
+\]
+depends heavily on our choice of norm on the test space $\|v\|_{V,E}$.
 
@@
 where $n$ is the outward normal vector to an element edge, and ${\rm sgn}(n)$ is 1 if $n$ aligns with a given global orientation, and $-1$ otherwise.
-\textcolor{red}{I need to find more simple way to explain sgn}.
+\textcolor{red}{I need to find more simple way to explain sgn} \textcolor{blue}{TB: see my DPG Friedrichs paper for the explanation}.
 
@@
 
- The functional setting is now well understood as well (see \cite{analysisDPG} for details) - $u,\sigma \in L^2(\Omega)$, $v \in H^1(\Omega_h)$, $\tau \in H({\rm div},\Omega_h)$, where $H^1(\Omega_h)$ and $H({\rm div},\Omega_h)$ are element-wise ``broken" Sobolev spaces.
+ The functional setting is now well understood as well (see \cite{analysisDPG} for details) - $u,\sigma \in L^2(\Omega)$, $v \in H^1(\Omega_h)$, $\tau \in H({\rm div},\Omega_h)$, where $H^1(\Omega_h)$ and $H({\rm div},\Omega_h)$ are ``broken" Sobolev spaces.
 By duality, $\widehat{u}$ lives in $H^{1/2}(\Gamma_h)$, the trace space of $H^1(\Omega_h)$, while $\widehat{f}_n$ comes from $H^{-1/2}(\Gamma_h)$, the normal trace space of $H({\rm div},\Omega_h)$.
@@
 \]
-on $\Gamma_-$, and continue with the wall boundary condition $u=0$ on $\Gamma_+$.
-For our model problem, as for many problems of interest in computational fluid dynamics, we expect $\grad u$ to be small near the inflow, and that the solutions to \eqref{primal} using $u=u_0$ and $\beta_n u - \sigma_n = f_n = u_0$ should converge to each other for sufficiently small $\epsilon$.
-Under these new boundary conditions, our variational problem $b(u,v) = l(v)$ is now defined by
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup \Gamma_h^0} \\
-l\left(\left(\tau,v\right)\right) &= \left(f, v\right) + \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_+} - \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_-} 
+on $\Gamma_-$, and continue \textcolar{blue}{TB: from where?} with the
+wall boundary condition $u=0$ on $\Gamma_+$.  For our model problem,
+as for many problems of interest in computational fluid dynamics, we
+expect $\grad u$ to be small near the inflow, and that the solutions
+to \eqref{primal} using $\beta_n u - \sigma_n = f_n = u_0$ on $\Gamma_-$
+will converge to that using $u=u_0$ on $\Gamma_-$  for sufficiently small $\epsilon$.
+Under these new boundary conditions, our variational problem $b(u,v) =
+l(v)$ is now defined by
+\begin{align*}
+b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right),
+\left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad
+v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle
+\left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} +
+\langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup
+  \Gamma_h^0} \\ l\left(\left(\tau,v\right)\right) &= \left(f,
+v\right) %+ \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_+}
+- \langle u_0, v \rangle_{\Gamma_-}
 \end{align*}
@@
 
-Given the boundary conditions on $\widehat{u}$ and $\widehat{f}_n$, we can now also define the trace norms as (canonical) minimum energy extension norms (taking into account the respective lifts/boundary conditions on $\widehat{u}$ and $\widehat{f}_n$ on $\Gamma_+$ and $\Gamma_-$, respectively)
-\begin{align*}
-\|\widehat{u}\| &= \inf_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+}=0, \left.w\right |_{\Gamma_h\setminus \Gamma_+ } = \widehat{u}} \|w\|_{H^1(\Omega)}\\
-\|\widehat{f}_n\| &= \inf_{q\in H({\rm div},\Omega), \left.q\cdot n\right|_{\Gamma_-}= 0, \left. q\cdot n \right |_{\Gamma_h} = \widehat{f}_n} \|q\|_{H({\rm div},\Omega)}
+Given the boundary conditions on $\widehat{u}$ and $\widehat{f}_n$, we
+can now also define the trace norms as (canonical) minimum energy
+extension norms (taking into account the respective lifts/boundary
+conditions on $\widehat{u}$ and $\widehat{f}_n$ on $\Gamma_+$ and
+$\Gamma_-$, respectively)
+\begin{align*}
+\|\widehat{u}\| &= \inf_{w\in H^1(\Omega),
+  \left.w\right|_{\Gamma_+}=0, \left.w\right |_{\Gamma_h\setminus
+    \Gamma_+ } = \widehat{u}} \|w\|_{H^1(\Omega)}\\ \|\widehat{f}_n\|
+&= \inf_{q\in H({\rm div},\Omega), \left.q\cdot n\right|_{\Gamma_-}=
+  0, \left. q\cdot n \right |_{\Gamma_h\setminus
+    \Gamma_-} = \widehat{f}_n}
+\|q\|_{H({\rm div},\Omega)}
 \end{align*}
@@
 \[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = C_1 \|u\|_{L^2(\Omega_h)} + C_2 \|\sigma\|_{L^2(\Omega_h)} + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|.
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = C_1
+\|u\|_{L^2(\Omega_h)} + C_2 \|\sigma\|_{L^2(\Omega_h)} + C_3
+\|\widehat{u}\| + C_4 \|\widehat{f}_n\|.
 \]
@@
 %We will denote $\|\cdot \| = \|\cdot\|_{L^2}$ for all functions defined on $\Omega_h$. 
-As $\tau \in H({\rm div},\Omega_h)$ and $v \in H^1(\Omega_h)$, we will construct norms on $v$ and $\tau$ using some combination of terms which are equivalent to the canonical $H^1(K) \times H({\rm div},K)$ norm over a single element
-\[
-\|\left(\tau,v\right)\|_{H^1(K) \times H({\rm div},K)} = \|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2  + \|\tau\|_{L^2(K)}^2 + \|\div \tau\|_{L^2(K)}^2
+As $\tau \in H({\rm div},\Omega_h)$ and $v \in H^1(\Omega_h)$, we will
+construct norms on $v$ and $\tau$ using some combination of terms
+which are equivalent to the canonical $H^1(K) \times H({\rm div},K)$
+norm over a single element
+\[
+\|\left(\tau,v\right)\|_{H^1(K) \times H({\rm div},K)}^2 =
+\|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2 + \|\tau\|_{L^2(K)}^2 +
+\|\div \tau\|_{L^2(K)}^2
 \]
@@
 \[
-\|\left(\tau,v\right)\|_{H^1(\Omega_h) \times H({\rm div},\Omega_h)} = \sum_{K\in \Omega_h} \|\left(\tau,v\right)\|_{H^1(K) \times H({\rm div},K)}
+\|\left(\tau,v\right)\|_{H^1(\Omega_h) \times H({\rm div},\Omega_h)}^2
+= \sum_{K\in \Omega_h} \|\left(\tau,v\right)\|_{H^1(K) \times H({\rm
+    div},K)}^2
 \]
@@
 
-\subsection{Approximability of the quasi-optimal test norm}%\textcolor{red}{Make new subsection on robustness here, reorganize}}
+\subsection{Approximability of the quasi-optimal test norm}
+\textcolor{blue}{need to define what we mean by robustness. perharps the best place is in the introduction}
 
@@
 \[
-\|\left(\tau, v\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v \|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 + C_1\|v\|_{L^2} + C_2\|\tau\|_{L^2}
+\|\left(\tau, v\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v
+\|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 +
+C_1\|v\|_{L^2}^2 + C_2\|\tau\|_{L^2}^2
 \]
 for some choice of constants $C_1$ and $C_2$.  
-%We note that the optimal test norm will automatically guarantee the robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.  
-However, use of this norm for the convection-diffusion problem is difficult - the variational problem for optimal test functions using the quasi-optimal test norm is equivalent to a reaction-diffusion system \cite{DBLP:journals/procedia/NiemiCC11}.
-Such systems also develop strong boundary layers for small diffusion, and transforming the problem to the reference element reveals that the inversion of the inner product associated with the optimal test norm will induce strong boundary layers of width $\epsilon/h^2$ in the optimal test functions.
-In comparison, the quasi-optimal norm has yielded fantastic results for the Helmholtz equation and other wave propagation problems.
-The difference between the two problems lies in the fact that, for wave propagation problems, the mesh size tends to be on the order of the wavenumber $k$/singular perturbation parameter.
-Transforming the variational problem using the quasi-optimal test norm for wave propagation yields smooth optimal test functions that are much easier to approximate over the reference element.
-Typically, the wavenumbers $k$ of physical interest are $O(100)-O(1000)$ with respect to a unit domain.
-The corresponding finite element problems will typically be solved on meshes containing approximately $O(k^d)$ elements in $\mathbb{R}^d$, well within the range of a computationally tractable simulation.
-However, for convection diffusion problems, the relevant range of $\epsilon$ for physical problems can be as small as $1e-7$.
-Solving on partially under-resolved meshes is thus unavoidable, and the approximability of the optimal test functions must be addressed in order to take advantage of the properties of DPG.
+%We note that the optimal test norm will automatically guarantee the
+%robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.
+However, use of this norm for the convection-diffusion problem is
+difficult - the variational problem for optimal test functions using
+the quasi-optimal test norm is equivalent to a reaction-diffusion
+system \cite{DBLP:journals/procedia/NiemiCC11}.  Such systems also
+develop strong boundary layers for small diffusion, and transforming
+the problem to the reference element reveals that the inversion of the
+inner product associated with the optimal test norm will induce strong
+boundary layers of width $\epsilon/h^2$ in the optimal test functions.
+In comparison, the quasi-optimal norm has yielded fantastic
+\textcolor{blue}{we don't use fantastic in technical English, replace
+  it with excellent, for example} results for the Helmholtz equation
+and other wave propagation problems. The difference between the two
+problems lies in the fact that, for wave propagation problems, the
+mesh size tends to be on the order of the wavenumber $k$/singular
+perturbation parameter. Transforming the variational problem using the
+quasi-optimal test norm for wave propagation yields smooth optimal
+test functions that are much easier to approximate over the reference
+element. Typically, the wavenumbers $k$ of physical interest are
+$O(100)-O(1000)$ with respect to a unit domain. The corresponding
+finite element problems will typically be solved on meshes containing
+approximately $O(k^d)$ elements in $\mathbb{R}^d$, well within the
+range of a computationally tractable simulation. However, for
+convection diffusion problems, the relevant range of $\epsilon$ for
+physical problems can be as small as $1e-7$. Solving on partially
+under-resolved meshes is thus unavoidable, and the approximability of
+the optimal test functions must be addressed in order to take
+advantage of the properties of DPG.
 
@@
 
-Resolving such boundary layers present in quasi-optimal test functions has been investigated numerically using specially designed (Shishkin) subgrid meshes by Niemi, Collier, and Calo in \cite{DBLP:journals/procedia/NiemiCC11}.
-However, even with Shishkin meshes, the approximation of optimal test functions under the quasi-optimal norm is difficult and far more expensive and complex to implement than approximation of test functions using a simple $p$-enriched space for $V$.
-We approach this from a different perspective, looking instead for robust test norms which do not induce boundary layers in the approximation of optimal test functions, and do so by formulating a general approach to analyzing the behavior of DPG under a given test norm.
-
-The estimates and proofs in this paper are largely based off of techniques and prior work done in \cite{DPGrobustness} and \cite{analysisDPG}; for further details, we encourage readers to consult these two publications as well\footnote{The primary contributions in this paper are stronger stability estimates for a new inflow boundary condition and a slightly different test norm.}.
+Resolving such boundary layers present in quasi-optimal test functions
+has been investigated numerically using specially designed (Shishkin)
+subgrid meshes by Niemi, Collier, and Calo in
+\cite{DBLP:journals/procedia/NiemiCC11}.  However, even with Shishkin
+meshes, the approximation of optimal test functions under the
+quasi-optimal norm is difficult and far more expensive and complex to
+implement than approximation of test functions using a simple
+$p$-enriched space for $V$. We approach this from a different
+perspective, looking instead for robust test norms which do not induce
+boundary layers in the approximation of optimal test functions, and do
+so by formulating a general approach to analyzing the behavior of DPG
+under a given test norm.
+
+The estimates and proofs in this paper are largely based on previous
+work done in \cite{DPGrobustness} and \cite{analysisDPG}. Our primary
+contributions in this paper are stronger stability estimates for a new
+inflow boundary condition and a slightly different test norm.
 
@@
 \]
+\textcolor{blue}{As a reader, up to this point, I don't understand what robustness means and why the above double inequalities is the condition for robustness?}
 where $\lesssim$ denotes a bound by a constant that will not grow as $\epsilon \rightarrow 0$.

### 2012-04-05 docs/NewBCRobustness_paper/paper.tex
changing bib and tex of paper.  adding new sections on explaining robustness
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@446 36274a68-8941-4c93-80ef-affaed5139da

@@
 Singularly perturbed problems are problems where a given parameter may be either very small or very large in the context of physical problems.
-An additional complication of singularly perturbed problems is that very often, in the limiting case of the parameter blowing up or decreasing to zero, the partial differential equation itself will change form.
+An additional complication of singularly perturbed problems is that very often, in the limiting case of the parameter blowing up or decreasing to zero, the partial differential equation itself will change types (i.e from parabolic to hyperbolic).
 A canonical example is the convection-diffusion equation with Dirichlet boundary conditions.
-In 1D, this equation is
+
+\subsubsection{Convection-diffusion}
+
+In 1D, the convection-diffusion equation is
 \begin{align*}
@@
 The finite element method has notoriously performed poorly for both this example, and for many other singularly perturbed problems.
-This poor performance is captured by the error bound for the finite element method applied to convection-diffusion equations
-\[
-\|u-u_h\|_E \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_U,
-\]
-where $C(\epsilon)$ grows as $\epsilon$ approaches its limiting case.
-The growth of $C$ with $\epsilon$ is referred to as a \textit{loss of robustness} in $\epsilon$, where the bound on the error in the finite element solution by the best approximation error increases as $\epsilon\rightarrow 0$.
-Intuitively, as our singular perturbation parameter changes, our finite element error is bounded more and more loosely by the best approximation error, allowing for more and more error in the finite element solution for as $\epsilon$ shrinks.
-The manifestation of this loss of robustness in the finite element solution of the 1D convection-diffusion problem is the growth of spurious oscillations as $\epsilon\rightarrow 0$.
-For a coarse mesh and small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation develops oscillations of magnitude $O(\epsilon^{-1})$.
+This poor performance is captured by the error bound for the finite element method applied to convection-diffusion equations - for the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}
+\[
+\|u-u_h\|_\epsilon \leq C \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
+\]
+for $C$ independent of $\epsilon$, and for $\|u\|_\epsilon \coloneqq \|u\|_{L^2} + \epsilon \|u'\|_{L^2}$. An alternative formulation of the above bound is 
+\[
+\|u-u_h\|_{H^1(0,1)} \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
+\]
+where $C(\epsilon)$ grows as $\epsilon\rightarrow 0$.
+
+The dependence on $\epsilon$ in the bound of our finite element error by best approximation error is referred to as a \textit{loss of robustness}.
+As our singular perturbation parameter changes, our finite element error is bounded more and more loosely by the best approximation error, allowing for more and more error in the finite element solution for as $\epsilon$ shrinks.
+
+Intuitively, a non-robustness method will perform increasingly worse as $\epsilon$ decreases, independently of the best approximation error.
+For example, for a coarse mesh and small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation with a boundary layer develops spurious oscillations of magnitude $O(\epsilon^{-1})$ everywhere in the domain, even where best approximation error is small.
+
+\subsubsection{Wave propagation}
 
@@
 The loss of robustness in this case manifests as ``pollution" error, a phenomenon where the finite element solution degrades over many wavelengths for high wavenumbers (commonly manifesting as a phase error between the FE solution and the exact solution).
+
+\subsubsection{Stabilization terms}
 
@@
 an $L^2$ setting on interior ``field" variables, boundary terms are
-identified as additional new unknowns.  The result is a hybridized DG \textcolor{blue}{TB: This is not true, the hybridized DG method does not hybridize both traces/fluxes}
-method with locally supported optimal test functions, with energy
-setting
+identified as additional new unknowns.  The result is a DG
+method with locally supported optimal test functions, where both fluxes and traces are hybridized.  The energy setting is
 \begin{align*}
@@
 \end{align*}
-where $n$ is the outward normal vector to an element edge, and ${\rm sgn}(n)$ is 1 if $n$ aligns with a given global orientation, and $-1$ otherwise.
-\textcolor{red}{I need to find more simple way to explain sgn} \textcolor{blue}{TB: see my DPG Friedrichs paper for the explanation}.
+where $n$ is the outward normal vector to an element edge, and ${\rm sgn}(n)$ is 1 if $n$ aligns with a given normal orientation $n_e$ on each edge, and $-1$ otherwise (see Examples in \cite{DPGFriedrichs} for a more detailed explanation).
 
@@
 \]
-on $\Gamma_-$, and continue \textcolar{blue}{TB: from where?} with the
-wall boundary condition $u=0$ on $\Gamma_+$.  For our model problem,
+on $\Gamma_-$, and use the standard wall boundary condition $u=0$ on $\Gamma_+$.  For our model problem,
 as for many problems of interest in computational fluid dynamics, we
@@
 \subsection{Approximability of the quasi-optimal test norm}
-\textcolor{blue}{need to define what we mean by robustness. perharps the best place is in the introduction}
+%\textcolor{blue}{need to define what we mean by robustness. perharps the best place is in the introduction}
+
+An ideal choice for the test norm would be the quasi-optimal norm; however, the form of the optimal test norm for convection-diffusion problems turns out to be quite problematic in the small diffusion limit.
 
@@
 boundary layers of width $\epsilon/h^2$ in the optimal test functions.
-In comparison, the quasi-optimal norm has yielded fantastic
-\textcolor{blue}{we don't use fantastic in technical English, replace
-  it with excellent, for example} results for the Helmholtz equation
+In comparison, the quasi-optimal norm has yielded excellent results for the Helmholtz equation
 and other wave propagation problems. The difference between the two
@@
 $p$-enriched space for $V$. We approach this from a different
-perspective, looking instead for robust test norms which do not induce
-boundary layers in the approximation of optimal test functions, and do
-so by formulating a general approach to analyzing the behavior of DPG
-under a given test norm.
+perspective, aiming instead to design a test norm that does not induce boundary layers, yet still maintains what we will define as \textit{robustness} - approximation properties that do not change over a range of $\epsilon$.
+
+\subsection{Alternatives to the quasi-optimal test norm}
+
+We expect the quasi-optimal test norm to deliver results that are close to the optimal test norm; namely, that the DPG finite element solution minimizes error a norm equivalent to
+\[
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = \|u\|_{L^2(\Omega_h)} + \|\sigma\|_{L^2(\Omega_h)} +
+\|\widehat{u}\| + \|\widehat{f}_n\|.
+\]
+This is an example of a \textit{robust} error bound - under the optimal test norm, we will return the best approximation error in the same norm \textit{independently} of $\epsilon$.
+The precise definition of robustness for singularly perturbed problems can be given as follows - for a problem with singular perturbation parameter $\epsilon\rightarrow 0$ and exact solution $u$, a \textit{robust} method will return a solution $u_h$ such that
+\[
+\|u-u_h\|_U \lesssim  \inf_{w_h\in U}\|u-w_h\|_U
+\]
+where $\|\cdot \|_U$ is some norm and $\lesssim$ is a bound by a constant, both of which are independent of  $\epsilon$.
+
+We expect a similar bound to hold under the quasi-optimal norm; however, it is not clear what to expect for other choices of test norms on $V$.
+In particular, it is not clear whether it is possible to achieve a completely robust bound under alternative norms, especially ones that generate easily approximated test functions.
 
@@
 
-\section{Strategy for proving robustness under a given test norm}
+\section{Strategy for estimating the DPG energy norm}
 
@@
 The avoidance of boundary layers in the test norm will be described in more detail in the section detailing numerical experiments.
-We focus first on quantifying the condition on robustness.
-Such a condition is equivalent to showing the robust boundedness of the energy error from above and below by norms on $U$
-\[
-\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}
-\]
-\textcolor{blue}{As a reader, up to this point, I don't understand what robustness means and why the above double inequalities is the condition for robustness?}
-where $\lesssim$ denotes a bound by a constant that will not grow as $\epsilon \rightarrow 0$.
-%The robust bound on the error in $\|\cdot\|_E$ from below by error in $\|\cdot\|_{U,1}$ is crucial to avoiding the instabilities associated with loss of robustness -
-\textcolor{red}{Explain in intuitive terms what the bounds above and below mean.}
-Our goal is to explicitly derive the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ that characterize this relation, taking into account the limiting case of $\epsilon \rightarrow 0$.
-
+
+Instead, the goal of this paper will to be derive $\epsilon$-explicit bounds on the finite element error by the best approximation error, and to characterize the dependence of such bounds upon the test norm.
+We seek to derive an estimate
+\[
+\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}
+\]
+where both $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ are characterized using
+\[
+\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,i} \coloneqq C_1^i\|u\| + C_2^i\|\sigma\| + C_3^i\|\widehat{u}\| + C_4^i\|\widehat{f}_n\|,\quad i = 1,2
+\]
+As it may not be possible to derive $O(1)$ constants for each $C_j^i$, we will aim instead for a quasi-robust estimate, where some constants are allowed to depend on $\epsilon$.
+\textcolor{red}{Not sure if I need this sentence here.}
+
+To derive the above $\epsilon$-explicit bounds on the finite element error in norm $U,1$ by the best approximation error in norm $U,2$, we need to show that the DPG energy norm (in which our finite element solution is optimal), is bounded from above and below
+\[
+\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}.
+\]
+Our goal is to explicitly derive the constants $C^1_1,\ldots C^1_4$ and $C^2_1,\ldots C^2_4$ that define the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ respectively, taking into account any dependence of such $C^i_j$ on $\epsilon$.
 Our strategy for doing so is broken down into three parts.
@@
 \]
-While the upper bound is robust, we have derived such a bound only by explicitly accounting for a factor of $\epsilon^{-1/2}$ in the bounding norm $\|\cdot \|_{U,2}$.
-This implies that for very small $\epsilon$, the $L^2$ error may be much smaller than the energy error (in this sense, DPG may lose some efficiency for small $\epsilon$, though it is still guaranteed against losing robustness and stability).
+While the second bound is robust, we have derived such a bound only by explicitly accounting for a factor of $\epsilon^{-1/2}$ in the bounding norm $\|\cdot \|_{U,2}$.
+This implies that for very small $\epsilon$, the $L^2$ error may be much smaller than the energy error (in this sense, DPG may lose some efficiency for small $\epsilon$).
 However, numerical experiments demonstrate much better results, and suggest that, at least for our example problems, $\|u-u_h\|_E \sim \|u-u_h\|_{U}$, implying that the induced energy norm may be equivalent to a norm on the group variable $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)$ that does not grow with $\epsilon$.

### 2012-04-05 docs/NewBCRobustness_paper/paper.tex
last mods done
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@447 36274a68-8941-4c93-80ef-affaed5139da

@@
 \author{Tan Bui-Thanh \and Jesse Chan \and Leszek Demkowicz \and Norbert Heuer}
-\title{Robust DPG stability II}
+\title{Robust DPG II}
 \date{}
@@
 
-The main goal of this paper is to derive a test norm that \textit{does not induce boundary layers in the optimal test functions}, but still induces an energy norm \textit{that does not lose robustness as $\epsilon \rightarrow 0$}.
+The main goal of this paper is to derive a test norm that \textit{does not induce boundary layers in the optimal test functions}, but still induces an energy norm performs well for $\epsilon \ll 1$.  
 %The first condition is satisfied by first decoupling norms on $\left(\tau,v\right)$ such that
@@
 \]
-As it may not be possible to derive $O(1)$ constants for each $C_j^i$, we will aim instead for a quasi-robust estimate, where some constants are allowed to depend on $\epsilon$.
+%As it may not be possible to derive $O(1)$ constants for each $C_j^i$, we will aim instead for a quasi-robust estimate, where some constants are allowed to depend on $\epsilon$.
 \textcolor{red}{Not sure if I need this sentence here.}
-
 To derive the above $\epsilon$-explicit bounds on the finite element error in norm $U,1$ by the best approximation error in norm $U,2$, we need to show that the DPG energy norm (in which our finite element solution is optimal), is bounded from above and below
@@
 
-The final step to constructing a robust, localizable test norm on $V$ that does not generate boundary layers is to derive adjoint stability estimates on $\tau$ and $v$ in terms of localizable normed quantities.
-These normed quantities will create ``building-blocks" through which we can construct test norms, where each building block will correspond roughly to robustness estimates for $\|u\|_{L^2}$, $\|\sigma\|_{L^2}$, $\|\widehat{u}\|$, or $\|\widehat{f}_n\|$.
+The final step to estimating the induced norm on $U$ by a given localizable test norm on $V$ is to derive adjoint stability estimates on $\tau$ and $v$ in terms of localizable normed quantities.
+These normed quantities will create ``building-blocks" through which we can construct test norms, where each building block will correspond roughly to estimates for $\|u\|_{L^2}$, $\|\sigma\|_{L^2}$, $\|\widehat{u}\|$, or $\|\widehat{f}_n\|$.
 

### 2012-04-05 docs/NewBCRobustness_paper/paper.tex
fixed typo
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@448 36274a68-8941-4c93-80ef-affaed5139da

@@
 \author{Tan Bui-Thanh \and Jesse Chan \and Leszek Demkowicz \and Norbert Heuer}
-\title{Robust DPG II}
+\title{$\epsilon$-explicit analysis of DPG}
 \date{}
@@
 
-The main goal of this paper is to derive a test norm that \textit{does not induce boundary layers in the optimal test functions}, but still induces an energy norm performs well for $\epsilon \ll 1$.  
 %The first condition is satisfied by first decoupling norms on $\left(\tau,v\right)$ such that
@@
 Ensuring that each seminorm/normed term is of the same order will allow for smooth solutions (under some assumptions on $\beta$).
+The main goal of this paper is to derive a test norm that \textit{does not induce boundary layers in the optimal test functions}, but still induces an energy norm performs well for $\epsilon \ll 1$.
 The avoidance of boundary layers in the test norm will be described in more detail in the section detailing numerical experiments.
-
-Instead, the goal of this paper will to be derive $\epsilon$-explicit bounds on the finite element error by the best approximation error, and to characterize the dependence of such bounds upon the test norm.
+Towards the goal of a well-performing energy norm, we will seek to derive $\epsilon$-explicit bounds on the finite element error by the best approximation error, and to characterize the dependence of such bounds upon the test norm.
 We seek to derive an estimate

### 2012-04-06 docs/NewBCRobustness_paper/paper.tex
added density argument
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@450 36274a68-8941-4c93-80ef-affaed5139da

@@
 \author{Tan Bui-Thanh \and Jesse Chan \and Leszek Demkowicz \and Norbert Heuer}
-\title{$\epsilon$-explicit analysis of DPG}
+\title{$\epsilon$-explicit analysis of DPG for convection-dominated diffusion}
 \date{}
@@
 The above boundary conditions are the reduced form of boundary conditions \eqref{bc_1} and \eqref{bc_2} corresponding to $\left.\tau\cdot n\right|_{\Gamma_-}=0$ and $\left.v\right|_{\Gamma_+}=0$.
-
 Additionally, the $\div$ operator is understood now in the weak sense, as the dual operator of $-\grad : H_0^1(\Omega) \rightarrow L^2(\Omega)$, such that $\div f \in \left(H_0^1(\Omega)\right)'$.
-The normal trace $f\cdot n$ is understood as a limit; smooth functions are dense in $H^1(\Omega)$, and we define $f\cdot n$ as the limit of $f_i\cdot n$, where $f_i \in C^\infty(\Omega)$, $f_i \rightarrow f$.
-\textcolor{red}{clearly define what we mean here with the density argument}
+
+The appearance of the normal trace $f\cdot n$ necessitates the use of a smooth dense subset of $L^2$.
+Formally speaking, we define the adjoint equation \eqref{adjoint} for $f\in C^\infty(\Omega)$.
+In doing so, we are allowed to speak of the normal trace $f\cdot n$ on the boundary.
+We derive inequalities that are independent of $f\cdot n$ and $\div f$ (quantities that are ill-defined for $L^2(\Omega)$ functions), and note that, since smooth functions are dense in $L^2(\Omega)$, we can take any $L^2$ function to be the limit of $C^\infty(\Omega)$ functions.
+Since the inequality holds for all smooth functions and is well-defined for $L^2(\Omega)$ functions, the inequality holds for $L^2(\Omega)$ functions in the limit as well.
 

### 2012-04-10 docs/NewBCRobustness_paper/paper.tex
removed a typo (piecewise constant, when I just meant constant)
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@460 36274a68-8941-4c93-80ef-affaed5139da

@@
 Let us restrict ourselves to the cases where $v$ is sufficiently smooth for $v'(0)$ to be well defined.
-Taking $g=1$ (corresponding to a piecewise constant approximation) we can solve \eqref{adjoint_1D} exactly to see that
+Taking $g=1$ (corresponding to a constant approximation) we can solve \eqref{adjoint_1D} exactly to see that
 \[
@@
 Consequently, $\frac{\epsilon}{2} v'(0)^2 \approx \epsilon^{-1}$, indicating already a lack of robustness in the bound of $\|v'\|$ by $\|g\|$ for constant data\footnote{Unlike the case of Dirichlet boundary conditions, the inflow condition on $ \widehat{f} = u(0)-\epsilon u'(0)$ induces an adjoint boundary condition $\tau(0)=0$, or equivalently $v'(0) = 0$, removing the non-robust term from the estimate.}.
-The robust bound from below of $g$ constant corresponds to the robust control of the approximation of field variable $u$ by piecewise constant trial functions.
+The robust bound from below of $g$ constant corresponds to the robust control of the approximation of field variable $u$ by a constant.
 More detailed 1D error bounds for Dirichlet boundary conditions are provided in \cite{DPG3}, and also indicate a lack of robustness when using the standard broken Sobolev norm as the test norm on $\tau$ and $v$.

### 2012-04-13 docs/NewBCRobustness_paper/paper.tex
fixed most of tan's requested changes
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@472 36274a68-8941-4c93-80ef-affaed5139da

--- 2012-04-06 docs/NewBCRobustness_paper/paper.tex
@@
 \begin{align*}
-\|\left(v,\tau\right)\|_{V,U} &= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{C_1\|u\| + C_2\|\sigma\| + C_3\epsilon\|\widehat{u}\|+ C_4\sqrt{\epsilon}\|\widehat{u}\|}\\
-&= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup \Gamma_h^0}}{C_1\|u\| + C_2\|\sigma\| + C_3\epsilon\|\widehat{u}\|+ C_4\sqrt{\epsilon}\|\widehat{u}\|}\\
+\|\left(v,\tau\right)\|_{V,U} &= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{C_1\|u\| + C_2\|\sigma\| + C_3\|\widehat{u}\|+ C_4\|\widehat{u}\|}\\
+&= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup \Gamma_h^0}}{C_1\|u\| + C_2\|\sigma\| + C_3\|\widehat{u}\|+ C_4\|\widehat{u}\|}\\
 & \leq \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle [\tau\cdot n], \widehat{u}\rangle}{\|\widehat{u}\|} +\frac{1}{C_4}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, [v]\rangle}{\|\widehat{f}\|}
@@
 \]
-\textcolor{red}{is this an equality?
-Is the inequality attainable, and thus attained in the supremum?} We can now use this relation to compare two different norms on $U$ by comparing their induced norms on $V$ - recall that showing a robust inequality between two norms on $U$ is similarly equivalent to showing the robust reverse inequality in the induced norms on $V$.
+We can now use this relation to compare two different norms on $U$ by comparing their induced norms on $V$ - recall that showing a robust inequality between two norms on $U$ is similarly equivalent to showing the robust reverse inequality in the induced norms on $V$.
 
@@
 for $i = 1, 2$.
+\tanbui{}{Need to prove or argue that $(v_i, \tau_i)$ exist}.
 The selection of $H({\rm div}, \Omega)\times H^1(\Omega)$ conforming test functions satisfying the specific above boundary conditions removes the contribution of the jump terms over the skeleton $\Gamma_h$ in the bilinear form, allowing us to bound components of the induced test norm separately from each other.
@@
 Bounding $\|\left(\tau_0,v_0\right)\|$ requires the use of techniques and decompositions first developed in \cite{analysisDPG} and adapted to convection-diffusion in \cite{DPGrobustness}.
-However, due to the $H({\rm div}, \Omega)\times H^1(\Omega)$ conforming nature of $\left(\tau_1,v_1\right)$ and $\left(\tau_2,v_2\right)$, the bound from above of test functions $\|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|g\|$ is reduced to proving classical error estimates for the adjoint equations
+However, due to the $H({\rm div}, \Omega)\times H^1(\Omega)$ conforming nature of $\left(\tau_1,v_1\right)$ and $\left(\tau_2,v_2\right)$, the bound from above of test functions $\|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V$ is reduced to proving classical error estimates for the adjoint equations
 \begin{align}
-\epsilon^{-1}\tau + \grad v &= f \label{adjoint1}\\
-\div \tau - \beta\cdot \grad v &=  g, \label{adjoint2}
+\epsilon^{-1}\tau_1 + \grad {v_1} &= 0 \\
+\div {\tau_1} - \beta\cdot \grad {v_1} &=  g, \label{adjoint2}
 \end{align} 
-for any choice of data $f, g\in L^2({\Omega_h})$ and boundary conditions $\left.\tau\cdot n\right|_{\Gamma_-} = 0$ and $\left.v\right|_{\Gamma_+} = 0$
+and 
+\begin{align}
+\epsilon^{-1}\tau_2 + \grad {v_2} &= f \label{adjoint1}\\
+\div {\tau_2} - \beta\cdot \grad {v_2} &= 0, 
+\end{align} 
+for any choice of data $f, g\in L^2({\Omega})$ and boundary conditions $\left.\tau\cdot n\right|_{\Gamma_-} = 0$ and $\left.v\right|_{\Gamma_+} = 0$.
+In other words, we want to bound the solutions $\|\left(\tau_1,v_1\right)\|_V\lesssim \|g\|_{L^2}$ and $\|\left(\tau_2,v_2\right)\|_V \lesssim \|f\|_{L^2}$.
+
+%\tanbui{}{very confusing to reuse $\tau, v$ notations here.}
 
@@
 \begin{itemize}
-\item \textbf{Lemma \ref{lemma_stream}}: For $\beta$ satisfying \eqref{a_req} and \eqref{b_req}, $f=0$ and $v \in H^1(\Omega_h)$, satisfying boundary conditions \eqref{bc_1} and \eqref{bc_2}
-\begin{align*}
-\|\beta \cdot \grad v \| &\lesssim \| g\| 
-\end{align*}
-Similarly, from $\div \tau - \beta\cdot \grad v = g$, we get $\|\div \tau\| \lesssim \|g\|$ as well.  
-\item \textbf{Lemma \ref{lemma_grad}}: For $\beta$ satisfying \eqref{a_req}, and $v \in H^1(\Omega_h)$ satisfying boundary conditions \eqref{bc_1} and \eqref{bc_2}, and for sufficiently small $\epsilon$
+\item \textbf{Lemma \ref{lemma_stream}}: For $\beta$ satisfying \eqref{a_req} and \eqref{b_req}, %$f=0$ 
+and $v_1 \in H^1(\Omega)$, satisfying boundary conditions \eqref{bc_1} and \eqref{bc_2}
+\begin{align*}
+\|\beta \cdot \grad v_1 \| &\lesssim \| g\| 
+\end{align*}
+Similarly, from $\div \tau_1 - \beta\cdot \grad v_1 = g$, we get $\|\div \tau_1\| \lesssim \|g\|$ as well.  
+\item \textbf{Lemma \ref{lemma_grad}}: For $\beta$ satisfying \eqref{a_req}, and $v_1,v_2 \in H^1(\Omega)$ satisfying boundary conditions \eqref{bc_1} and \eqref{bc_2}, and for sufficiently small $\epsilon$
+\begin{align*}
+\epsilon \|\grad v_1\|^2 + \|v_1\|^2 &\lesssim \|g\|^2\\
+\epsilon \|\grad v_2\|^2 + \|v_2\|^2 &\lesssim \epsilon \| f\|^2.
+\end{align*}
+By the triangle inequality, this implies for $v=v_1+v_2$ that
 \begin{align*}
@@
 \end{align*}
-\item \textbf{Lemma \ref{lemma_boundary}}: For $\beta$ satisfying \eqref{a_req}, \eqref{c_req}, and $f=g=0$, 
-\begin{align*}
-\|\grad v\| = \frac{1}{\epsilon}\|\tau\| &\lesssim \frac{1}{\epsilon} \| [\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v]\|_{\Gamma_h^0 \cup \Gamma_+}
+\item \textbf{Lemma \ref{lemma_boundary}}: For $\beta$ satisfying \eqref{a_req}, \eqref{c_req}, %and $f=g=0$, 
+\begin{align*}
+\|\grad v_0\| = \frac{1}{\epsilon}\|\tau_0\| &\lesssim \frac{1}{\epsilon} \| [\tau_0\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v_0]\|_{\Gamma_h^0 \cup \Gamma_+}
 \end{align*}
@@
 Together, these estimates will be sufficient to construct a complete norm on $V$ and demonstrate bounds on induced test norms for different scalings of norms on $U$.  
+%\tanbui{}{again, using the same notation
+%  $(v, \tau)$ for all three problems is not a good idea. Why don't we
+%  use $(v_i,\tau_i)$ introduced above? Things are much clearer this
+%  way?}
 
@@
 
-The primary result of this paper is that, if $\beta$ satisfies \ref{a_req},\ref{b_req}, and \ref{c_req}, the DPG method provides robust control over the $L^2$ error in $u$ and $\sigma$
+The primary result of this paper is that, if $\beta$ satisfies \eqref{a_req},\eqref{b_req}, and \eqref{c_req}, the DPG method provides robust control over the $L^2$ error in $u$ and $\sigma$
 \[
@@
 This implies that for very small $\epsilon$, the $L^2$ error may be much smaller than the energy error (in this sense, DPG may lose some efficiency for small $\epsilon$).
-However, numerical experiments demonstrate much better results, and suggest that, at least for our example problems, $\|u-u_h\|_E \sim \|u-u_h\|_{U}$, implying that the induced energy norm may be equivalent to a norm on the group variable $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)$ that does not grow with $\epsilon$.
+However, numerical experiments demonstrate much better results, and suggest that, at least for our example problems,
+\[
+\|u-u_h\|_E \sim \|u\|_{L^2}+\|\sigma\|_{L^2} + \|\widehat{u}\| + \|\widehat{f}_n\|
+\]
+In other words, we observe that the induced energy norm may be equivalent to a norm on the group variable $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)$ that does not grow with $\epsilon$.
+%\tanbui{}{What is the norm $\|\cdot\|_U$ here?}
 
@@
 \[
+\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,1} =
 \|u\| + \|\sigma\| + \epsilon\|\widehat{u}\|+ \sqrt{\epsilon}\|\widehat{u}\| \lesssim \left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E
@@
 \begin{align*}
-\|\left(v,\tau\right)\|_V &\lesssim \frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{C_1\|u\| + C_2\|\sigma\| + C_3\|\widehat{u}\|+ C_4\|\widehat{u}\|}\\
-& \simeq \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle [\tau\cdot n], \widehat{u}\rangle}{\|\widehat{u}\|} + \frac{1}{C_4}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, [v]\rangle}{\|\widehat{f}\|},
+\|\left(v,\tau\right)\|_V &= \sup_{u,\sigma,\widehat{u},\widehat{f}_n}\frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{C_1\|u\| + C_2\|\sigma\| + C_3\|\widehat{u}\|+ C_4\|\widehat{u}\|}\\
+& \leq \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle [\tau\cdot n], \widehat{u}\rangle}{\|\widehat{u}\|} + \frac{1}{C_4}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, [v]\rangle}{\|\widehat{f}\|},
 \end{align*}
@@
 \[
-\|\left(v,\tau\right)\|_V \lesssim \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\|[\tau\cdot n]\| + \frac{1}{C_4}\|[v]\|
+\|\left(v,\tau\right)\|_V \leq \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\|[\tau\cdot n]\| + \frac{1}{C_4}\|[v]\|
 \]
 We will bound $\|\left(v,\tau\right)\|_V$ for all $\left(v,\tau\right)$ satisfying \eqref{adjoint} by decomposing $\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right)$ as described in section~\ref{sec:strategy2}.
+tanbui{}{Need to tell
+  the readers where this equation comes from, particularly its boundary
+  conditions}
 %where $\left(v_1,\tau_1\right)$ satisfies our adjoint equation \eqref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and 

### 2012-05-22 docs/NavierStokes/notes.tex

\documentclass{article}

\usepackage{array}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{color}
\usepackage{undertilde}
\usepackage[colorlinks = true, filecolor = red, urlcolor = blue, linkcolor = black]{hyperref}
\usepackage{pdflscape}
\usepackage{pifont}
%\usepackage{fullpage}
\setlength\textwidth{6in}
\setlength\textheight{8in}
\setlength\oddsidemargin{0.25in} % LaTeX adds a default 1in to this!
\setlength\evensidemargin{0.25in}
\setlength\topmargin{-0.0in} % LaTeX adds a default 1in to this!
\setlength\headsep{0in}
\setlength\headheight{0in}
\setlength\footskip{1in}

\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}
\renewcommand{\floatpagefraction}{0.75}

\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
\newcommand{\tensor}[1]{\underline{\vect{#1}}}
\newcommand{\del}{\triangle}
\newcommand{\grad}{\nabla}
\renewcommand{\div}{\grad \cdot}
\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
\newcommand{\eip}[1]{a\left( #1 \right)}
\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}

\newcommand{\circone}{\ding{192}}
\newcommand{\circtwo}{\ding{193}}
\newcommand{\circthree}{\ding{194}}
\newcommand{\circfour}{\ding{195}}
\newcommand{\circfive}{\ding{196}}

\def\arr#1#2#3#4{\left[
\begin{array}{cc}
#1 & #2\\
#3 & #4\\
\end{array}
\right]}
\def\vecttwo#1#2{\left[
\begin{array}{c}
#1\\
#2\\
\end{array}
\right]}
\def\vectthree#1#2#3{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
\end{array}
\right]}
\def\vectfour#1#2#3#4{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
#4\\
\end{array}
\right]}
\date{}
\author{Jesse Chan}
\title{NS notes}

\begin{document}

\section{Intro}

Following Demkowicz and Oden, we seek to solve 
\[
\sum^2_{i=1} G_i\left( U\right)_{,i}=\sum^2_{i=1} V_i\left( U\right)_{,i}
\]
where
\[
V_i = \vectfour{0}{\sigma_{i1}}{\sigma_{i2}}{\sum_{j=1}^2\sigma_{ij}u_j + q_i}
\]
are the viscous fluxes, and 
\[
 G_1 = \vectfour{\rho u_1}{\rho u_1^2+p}{\rho u_1 u_2}{((\rho e)+p)u_1}, \qquad G_2 = \vectfour{\rho u_2}{\rho u_1 u_2}{\rho u_2^2+p}{((\rho e)+p)u_2}
\]
are the Eulerian fluxes.

We also have the constitutive relations 
\begin{align*}
\sigma_{ij} &= \mu(u_{i,j}+u_{j,i}) + \lambda u_{k,k}\delta_{ij}\\
q_i &= \kappa T_{,i}\\
p &= (\gamma-1)\rho\iota\\
\iota &= e-\frac{1}{2}(u_1^2+u_2^2)\\
\iota &= c_vT
\end{align*}
where $e$ and $\iota$ are energy and internal energy per unit mass, respectively.

\section{Symbolic form}
In symbolic form, we can write the Navier Stokes equations as a system of seven first order equations. Let $[u_1,u_2] = [u,v]$.

\subsection{Mass equation}
\[
\div \vecttwo{\rho u }{\rho v} = 0
\]
\subsection{Momentum equations}
\begin{align*}
\div \vecttwo{\rho u^2+p }{\rho u v} &= \div\left(\vec{\sigma_{i1}}\right)\\
\div \vecttwo{\rho u v}{\rho v^2+p } &= \div\left(\vec{\sigma_{i2}}\right)
\end{align*}
\subsection{Energy equation}
Let $\boldsymbol \sigma$ be a tensor whose $ij$th term is $\sigma_{ij}$.  
\[
\div\vecttwo{((\rho e)+p)u}{((\rho e)+p)v} = \div\left[\boldsymbol\sigma U + \vec{q}\right]
\]
\subsection{Newtonian fluid laws}
We represent $\boldsymbol\sigma$ using the Newtonian fluid law
\[
\sigma_{ij} = \mu(u_{i,j} + u_{j,i}) + \lambda u_{k,k} \delta_{ij}
\]
where $\mu$ is viscosity and $\lambda$ is bulk viscosity. 
%Following elasticity, a general formula for the stress tensor is 
%\[
%\sigma_{ij} = 2\mu \epsilon_{ij} + \lambda \epsilon_{kk} \delta_{ij}
%\]
We can invert the stress tensor under isotropic and plane strain assumptions to get
%\[
%\epsilon_{ij} = \frac{1}{2\mu} \sigma_{ij} - \frac{\lambda}{4\mu (\mu + \lambda)} \sigma_{kk}\delta_{ij}
%\] 
%which translates to
\[
\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \frac{1}{2\mu} \sigma_{ij} - \frac{\lambda}{4\mu (\mu + \lambda)} \sigma_{kk}\delta_{ij}
\]
We also have
\[
\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \grad  U - \boldsymbol \omega
\]
where $\boldsymbol \omega$ is the antisymmetric part of the infinitesimal strain tensor:
\[
\boldsymbol \omega = \frac{1}{2}\left(\grad  U - \grad ^T  U\right).
\]
Thus our final form is
\begin{align*}
\grad  U - \boldsymbol \omega = \frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I.
\end{align*}
Notice that $\boldsymbol \omega$ is implicitly defined to be the symmetric part of $\grad u$ by taking the symmetric part of the above equation.

In general, $\mu$ and $\lambda$ are functions of temperature.

\subsection{Fourier's heat conduction law}
\begin{align*}
\vec{q} &= \kappa \grad T
\end{align*}
$\kappa$ is generally a function of temperature, and is often assumed to be proportional to $\mu$.

We introduce here the Prandtl number here as well
\[
{\rm Pr} = \frac{\gamma c_v \mu}{\kappa}
\]
In this case, we assume a constant Prandlt number, implying that viscosity is proportional to conductivity.

\subsection{Classical and momentum variables}

In classical variables, our system of equations is now
\begin{align*}
\div \vecttwo{\rho u }{\rho v} &= 0\\
\div \left(\vecttwo{\rho u^2+p }{\rho u v} - \boldsymbol \sigma_{1}\right) &=0\\
\div \left(\vecttwo{\rho u v}{\rho v^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
\div \left(\vecttwo{((\rho e)+p)u}{((\rho e)+p)v} - \boldsymbol\sigma \mathbf{u} + \vec{q}\right) &=0\\
\frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I &= \grad \mathbf{u} - \boldsymbol \omega\\
\frac{1}{\kappa}\vec{q} &= \grad T
\end{align*}

We strongly enforce symmetry of $\boldsymbol \sigma$ by setting $\sigma_{21} = \sigma_{12}$.

\section{Nondimensionalization}
To nondimensionalize our equations, we introduce nondimensional quantities for length, density, velocity, temperature, and viscosity. 
\[
\boldsymbol x^* = \frac{\boldsymbol x}{L}, \qquad \rho^* = \frac{\rho}{\rho_{\infty}}, \qquad \boldsymbol u^* = \frac{\boldsymbol u}{V_\infty}, \qquad T^* = \frac{T}{T_\infty}, \qquad \mu^* = \frac{\mu}{\mu_\infty}
\]
Momentum, pressure, internal energy, and bulk viscosity are then nondimensionalized with respect to the above variables
\[
\boldsymbol m^* = \frac{\boldsymbol m}{\rho_\infty V_\infty}, \qquad p^* = \frac{p}{\rho_\infty V_\infty^2}, \qquad \iota^* = \frac{\iota}{V_\infty^2}, \qquad \lambda^* = \frac{\lambda}{\mu_\infty}
\]
We introduce, for convenience, the Reynolds number
\[
{\rm Re} = \frac{\rho_\infty V_\infty L}{\mu_\infty} 
\]
and the reference (free stream) Mach number
\[
M_\infty = \frac{V_\infty}{\sqrt{\gamma(\gamma-1)c_vT_\infty}}
\]
Note that 
\[
a = \sqrt{\frac{\gamma p_\infty}{\rho_\infty}} = \sqrt{{\gamma p_\infty}} = \sqrt{\gamma(\gamma-1)c_vT_\infty}
\]
The equations take the same form as before after nondimensionalization, so long as we define new material constants
\[
\tilde{\mu} = \frac{\mu^*}{\rm Re}, \qquad \tilde{\lambda} = \frac{\lambda^*}{\rm Re}, \qquad \tilde{c}_v = \frac{1}{\gamma(\gamma-1)M_\infty^2}, \qquad \tilde{\kappa} = \frac{\gamma\tilde{c}_v\tilde{\mu}}{\rm Pr}
\]
From here on, we drop the $^*$ superscript and adopt the nondimensionalized equations.

\subsection{Linearization}

\subsubsection{Conservation laws}

\begin{align*}
\div \vecttwo{\rho u }{\rho v} &= 0\\
\div \left(\vecttwo{\rho u^2+p }{\rho u v} - \boldsymbol \sigma_{1}\right) &=0\\
\div \left(\vecttwo{\rho u v}{\rho v^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
\div \left(\vecttwo{((\rho e)+p)u}{((\rho e)+p)v} - \boldsymbol \sigma_1 \cdot \boldsymbol u- \boldsymbol \sigma_2 \cdot \boldsymbol u + \vec{q}\right) &=0\\
\end{align*}
or generally, 
\[
\div (F_i(\boldsymbol U)-G_i(\boldsymbol U,\boldsymbol \sigma) = 0, \qquad i = 1,\ldots, 4
\]
The variational form restricted to a single element gives
\[
\langle \widehat{F}_i\cdot n, v\rangle - \int_K  (F(\boldsymbol U)-G_i(\boldsymbol U,\boldsymbol \sigma)) \cdot \grad v_i = 0 , \qquad i = 1,\ldots, 4
\]
and the variational form over the entire domain is given by summing up the element-wise contributions.

The presence of terms such as $\boldsymbol \sigma_i \cdot \boldsymbol u$ means that we will need to linearize in the stress variables $\sigma_ij$ in addition to our Eulerian quantities. Since fluxes and traces are linear, we do not need to linearize them. Instead, fluxes $\widehat{F}_{i,n}$ and traces $\widehat{u},\widehat{v},\widehat{T}$ will represent normal traces and traces of the accumulated nonlinear solution. 
\begin{align*}
\langle \widehat{F}_i\cdot n, v\rangle &- \int_K  \left(F_{i,\boldsymbol U}(\boldsymbol U)\cdot \Delta \boldsymbol U -G_{i,\boldsymbol U}(\boldsymbol U, \boldsymbol \sigma)\cdot \Delta \boldsymbol U - G_{i,\boldsymbol \sigma}(\boldsymbol U, \boldsymbol \sigma)\cdot \Delta \boldsymbol \sigma \right)\cdot \grad v_i \\
&= \int_K  \left(F_i(\boldsymbol U)-G_i(\boldsymbol U)\right) \cdot \grad v_i \\
\qquad i &= 1,\ldots, 4
\end{align*}
where
\begin{align*}
F^1_{1,\boldsymbol U} &= \{u,\rho ,0,0\} \\
F^2_{1,\boldsymbol U} &= \{v,0,\rho ,0\} \\
F^1_{2,\boldsymbol U} &=\left\{c_v T (\gamma -1)+u^2,2 u \rho ,0,c_v (\gamma -1) \rho \right\}\\
F^2_{2,\boldsymbol U} &=\{u v,v \rho ,u \rho ,0\}\\
F^1_{3,\boldsymbol U} &=\{u v,v \rho ,u \rho ,0\}\\
F^2_{3,\boldsymbol U} &=\left\{c_v T (\gamma -1)+v^2,0,2 v \rho ,c_v (\gamma -1) \rho \right\}\\
F^1_{4,\boldsymbol U} &=\left\{\frac{1}{2} u \left(2 c_v T (2 \gamma -1)+u^2+v^2\right),\frac{1}{2} \rho  \left(2 c_v T (2 \gamma -1)+3 u^2+v^2\right),u v \rho ,c_v u (2 \gamma -1) \rho \right\}\\
F^2_{4,\boldsymbol U} &=\left\{\frac{1}{2} v \left(2 c_v T (2 \gamma -1)+u^2+v^2\right),u v \rho ,\frac{1}{2} \rho  \left(2c_v T (2 \gamma -1)+u^2+3 v^2\right),c_v v (2 \gamma -1) \rho \right\}
\end{align*}
The viscous Jacobians become (when linearized with respect to $\{\sigma_{11},\sigma_{12}, \sigma_{22}\}$)
\begin{align*}
G^1_{2,\boldsymbol \sigma} &= \{1,0,0\}\\
G^2_{2,\boldsymbol \sigma} &= \{0,1,0\}\\
G^1_{3,\boldsymbol \sigma} &= \{0,1,0\}\\
G^2_{3,\boldsymbol \sigma} &= \{0,0,1\}\\
G^1_{4,\boldsymbol \sigma} &= \{u_1,u_2,0\}\\
G^2_{4,\boldsymbol \sigma} &= \{0,u_1,u_2\}
\end{align*}
and (when linearized with respect to the Eulerian variables)
\begin{align*}
G^1_{4,\boldsymbol U} &= \{0,\sigma_{11},\sigma_{12},0\}\\
G^2_{4,\boldsymbol U} &= \{0,\sigma_{12},\sigma_{22},0\}
\end{align*}

\subsubsection{Viscous equations}
We have two equations left to linearize - the constitutive laws defining our viscous stresses and heat flux terms. 
\begin{align*}
\frac{1}{2\mu}{\boldsymbol \sigma}- \frac{\lambda}{4\mu(\mu+\lambda)}{\rm tr}({\boldsymbol \sigma}){\boldsymbol I} + {\boldsymbol \omega} &= 
\grad
\left[\begin{array}{c}
u_1\\
u_2
\end{array}
\right]\\
\frac{1}{\kappa}
\left[\begin{array}{c}
q_1\\
q_2
\end{array}\right] &=
\grad T
\end{align*}

We treat the first tensor equation as two vector equations by considering each column:
\begin{align*}
\frac{1}{2\mu} \vecttwo{\sigma_{11}}{\sigma_{12}} - \frac{\lambda}{4\mu(\mu+\lambda)}\vecttwo{\sigma_{11}+\sigma_{22}}{0} + \vecttwo{0}{-\omega} - \grad u_1&= 0 \\
\frac{1}{2\mu} \vecttwo{\sigma_{12}}{\sigma_{22}} - \frac{\lambda}{4\mu(\mu+\lambda)}\vecttwo{0}{\sigma_{11}+\sigma_{22}} + \vecttwo{\omega}{0} - \grad u_2 &= 0
\end{align*}
These equations are linear in $\sigma_{ij}$, so the linearization is simple. 
Since all equations are linear in variables $q_1, q_2, w$ for all combinations of variables, we do not need to linearize any equations in $q_1, q_2, w$.

\subsubsection{Initial guess}

For our initial guesses, we set
\[
\rho = 1,\qquad m_1= 1,\qquad m_2 = 0, \qquad T = 1
\]
which is consistent with what was done in Demkowicz and Oden (find citation).

\section{	Boundary conditions}

\subsection{Carter flat plate}

Our first problem of interest is the Carter flat plate problem. An infinitesmally thin flat plate disrupts a free stream flow and causes a shock to form at the tip of the plate.

\begin{figure}[!h]
\centering
\includegraphics[scale=.5]{flat_plate_BCs.pdf}
\caption{Carter flat plate problem.}
\end{figure}

\begin{itemize}
\item \textbf{Inflow boundary conditions:} free stream conditions are applied here to all four fluxes $\widehat{f}_{i,n}$.
\item \textbf{Symmetry boundary conditions:} $u_n = q_n = \pd{u_s}{n} = 0$. Here, this implies $u_2 = q_2 = \sigma_{12} = 0$. We impose the stress condition by noting that, for the flat plate geometry, if $u_2 = 0$, then at the top and bottom, with $n = (0,1)$, $\widehat{f}_{2,n} = \sigma_{12}$, and $\widehat{f}_{4,n} = q_2$ if $\sigma_{12}$ and $u_2 = 0$. 
\item \textbf{Flat plate boundary conditions:} $u_1 = u_2 = 0$, and $T = T_w = \left[1+(\gamma-1)M_\infty^2/2\right] T_\infty = 2.8T_\infty$ (for Mach 3 flow). We impose these strongly on the trace variables $\widehat{u}_1, \widehat{u}_2, \widehat{T}$. 
\item \textbf{Outflow boundary conditions:} the exact boundary conditions to enforce here are questionable\footnote{Demkowicz et al enforce this boundary condition only in regions where the flow is subsonic.}. Capon et al enforce $\pd{u_1}{n}=\pd{u_2}{n}=0$ and $\pd{T}{n} = 0$. Since $u_1$ and $u_2$ are not expected to be zero at these points, we will set $\widehat{f}_{2,n}$ and $\widehat{f}_{4,n}$ to their represented quantities using either the field variables from the background flow, or (in the case of pseudo-time stepping) the previous timestep's flux and field quantities. 
\end{itemize}

\end{document}

### 2012-06-06 docs/NavierStokes/notes.tex
adding figs and NS notes

@@
 \newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
+\newcommand{\nor}[1]{\left\| #1 \right\|}
 
@@
 \newcommand{\circfive}{\ding{196}}
+
+\newcommand{\Reyn}{\rm Re}
+\newcommand{\Gh}{\Gamma_h}
+\newcommand{\Oh}{\Omega_h}
+\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
+\newcommand{\LRs}[1]{\left[ #1 \right]}
+\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
 
@@
 
-\section{Intro}
+\section{The compressible Navier-Stokes equations}
 
-Following Demkowicz and Oden, we seek to solve 
+Following Demkowicz and Oden \cite{Demkowicz:1990:NFE:112271.112276}, we consider the compressible Navier-Stokes equations
 \[
-\sum^2_{i=1} G_i\left( U\right)_{,i}=\sum^2_{i=1} V_i\left( U\right)_{,i}
+\sum^2_{i=1} F_i\left( U\right)_{,i}=\sum^2_{i=1} G_i\left( U\right)_{,i}
 \]
-where
+where the Eulerian fluxes are given as
 \[
-V_i = \vectfour{0}{\sigma_{i1}}{\sigma_{i2}}{\sum_{j=1}^2\sigma_{ij}u_j + q_i}
+F_1 = \vectfour{\rho u_1}{\rho u_1^2+p}{\rho u_1 u_2}{((\rho e)+p)u_1}, \qquad F_2 = \vectfour{\rho u_2}{\rho u_1 u_2}{\rho u_2^2+p}{((\rho e)+p)u_2},
 \]
-are the viscous fluxes, and 
+and the viscous fluxes are given as
 \[
- G_1 = \vectfour{\rho u_1}{\rho u_1^2+p}{\rho u_1 u_2}{((\rho e)+p)u_1}, \qquad G_2 = \vectfour{\rho u_2}{\rho u_1 u_2}{\rho u_2^2+p}{((\rho e)+p)u_2}
+G_i = \vectfour{0}{\sigma_{i1}}{\sigma_{i2}}{\sum_{j=1}^2\sigma_{ij}u_j + q_i}.
 \]
-are the Eulerian fluxes.
-
-We also have the constitutive relations 
+We have also the constitutive relations 
 \begin{align*}
@@
 \end{align*}
-where $e$ and $\iota$ are energy and internal energy per unit mass, respectively.
-
-\section{Symbolic form}
-In symbolic form, we can write the Navier Stokes equations as a system of seven first order equations. Let $[u_1,u_2] = [u,v]$.
+where $e$ and $\iota$ are energy and internal energy per unit mass, respectively. We write the Navier Stokes equations as a system of seven first order equations. Let $[u_1,u_2] = [u,v]$.
 
@@
 
-In general, $\mu$ and $\lambda$ are functions of temperature.
+We note that, though this is a standard approach in solid mechanics, it is nonstandard compared to the usual finite element and DG approaches to the viscous stresses.
+We adopt such an approach to better mirror our experiences with the convection-diffusion equation \cite{DPGrobustness,DPGrobustness2}.
+
+In general, $\mu$ and $\lambda$ are functions of temperature, obeying the power law
+\[
+\mu = \left(\frac{T}{T_0}\right)^\beta,
+\]
+where $T_0$ is a reference temperature. We choose $\beta = 2/3$ in this case.
 
 \subsection{Fourier's heat conduction law}
+We assume Fourier's law 
 \begin{align*}
-\vec{q} &= \kappa \grad T
+\vec{q} &= \kappa \grad T,
 \end{align*}
-$\kappa$ is generally a function of temperature, and is often assumed to be proportional to $\mu$.
-
-We introduce here the Prandtl number here as well
+where $\kappa$ is generally a function of temperature. We introduce here the Prandtl number here as well
 \[
-{\rm Pr} = \frac{\gamma c_v \mu}{\kappa}
+{\rm Pr} = \frac{\gamma c_v \mu}{\kappa}.
 \]
-In this case, we assume a constant Prandlt number, implying that viscosity is proportional to conductivity.
+In this case, we assume a constant Prandlt number, which implies that the heat conductivity $\kappa$ is proportional to viscosity $\mu$.
 
@@
 
-We strongly enforce symmetry of $\boldsymbol \sigma$ by setting $\sigma_{21} = \sigma_{12}$.
+We strongly enforce symmetry of the stress tensor $\boldsymbol \sigma$ by setting $\sigma_{21} = \sigma_{12}$.
 
@@
 \[
-{\rm Re} = \frac{\rho_\infty V_\infty L}{\mu_\infty} 
+\Reyn = \frac{\rho_\infty V_\infty L}{\mu_\infty} 
 \]
@@
 \[
-\tilde{\mu} = \frac{\mu^*}{\rm Re}, \qquad \tilde{\lambda} = \frac{\lambda^*}{\rm Re}, \qquad \tilde{c}_v = \frac{1}{\gamma(\gamma-1)M_\infty^2}, \qquad \tilde{\kappa} = \frac{\gamma\tilde{c}_v\tilde{\mu}}{\rm Pr}
+\tilde{\mu} = \frac{\mu^*}{\Reyn}, \qquad \tilde{\lambda} = \frac{\lambda^*}{\Reyn}, \qquad \tilde{c}_v = \frac{1}{\gamma(\gamma-1)M_\infty^2}, \qquad \tilde{\kappa} = \frac{\gamma\tilde{c}_v\tilde{\mu}}{\rm Pr}
 \]
-From here on, we drop the $^*$ superscript and adopt the nondimensionalized equations.
+From here on, we drop the $^*$ superscript and assume all variables refer to their nondimensionalized quantities.
 
@@
 
+We do not linearize the viscosities $\mu$ and $\lambda$, but instead set them based on the power law and the solution at the previous timestep for simplicity.
+
 \subsubsection{Initial guess}
@@
 \[
-\rho = 1,\qquad m_1= 1,\qquad m_2 = 0, \qquad T = 1
+\rho = 1,\qquad u_1= 1,\qquad u_2 = 0, \qquad T = 1
 \]
-which is consistent with what was done in Demkowicz and Oden (find citation).
+which is consistent with what was done in Demkowicz and Oden in \cite{Demkowicz:1990:NFE:112271.112276}. Stresses are set uniformly to zero.
 
-\section{	Boundary conditions}
+\section{Test norm}
+
+For the convection-diffusion problem 
+\begin{align*}
+\div \left(\beta u - \sigma\right) &= f\\
+\frac{1}{\epsilon}\sigma - \grad u &= 0
+\end{align*}
+on domain $\Omega$, with mesh $\Oh$ and mesh skeleton $\Gh$, the DPG variational formulation is
+\begin{align*}
+b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
+\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
+v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh} - \LRa{
+\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n,
+  \jump{v} }_{\Gh}.
+\end{align*}
+with $v\in H^1$ and $\tau \in H({\rm div},\Oh)$.
+
+The test norm adopted for convection-diffusion in \cite{DPGrobustness,DPGrobustness2} is defined elementwise on $K$ as
+\[
+\|\left(v,\tau\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
+\]
+This test norm both delivers robust control of the error in the $L^2$ variables $u$ and $\sigma$ and avoids boundary layers in the computation of local test functions.
+
+Our test norm is extrapolated to the Navier-Stokes equations as follows: we denote the vector of $H^1$ test functions as $v=\{v_1,v_2,v_3,v_4\}$, and similarly for $W = \{\tau_1,\tau_2,\tau_3\}$.
+Similarly, we group our Eulerian and stress variables into the vector variables $U$ and $\Sigma$, respectively.
+If $R_{\rm Euler}(U,\Sigma)$ and $R_{\rm visc}(U,\Sigma)$ are Eulerian and viscous nonlinear residuals, our formulation for the linearized Navier-Stokes equations is
+\begin{align*}
+\div \left(A_{\rm Euler}U - A_{\rm visc}\Sigma\right) &= R_{\rm Euler}(U,\Sigma)\\
+E_{\rm visc} \Sigma - \grad U &= R_{\rm visc}(U,\Sigma)
+\end{align*}
+with variational formulation
+\begin{align*}
+\LRa{\widehat{F}_n,V}_{\Gh} + \left(U,\div W - A_{\rm Euler}^T\grad  V\right) + \LRa{\widehat{U},W\cdot n}_{\Gh} + \left(\Sigma,E_{\rm visc}^TW - A_{\rm visc}^T\grad  V\right) &= 0
+\end{align*}
+Identifying vector-valued terms in the Navier-Stokes formulation with equivalent scalar terms in the convection-diffusion equation allows us to extrapolate our test norm to systems of equations
+\[
+\|\left(V,W\right)\|_{V,K}^2 = \min\left\{\frac{\Reyn}{|K|},1\right\}\|v\|^2 + \frac{1}{\Reyn} \|A_{\rm visc}^T\grad v\|^2 + \|A_{\rm Euler}^T \grad v\|^2 + \| \div W\|^2 + \min\left\{\Reyn,\frac{1}{|K|}\right\}\|E_{\rm visc}^T\tau\|^2.
+\]
+An advantage of this extrapolation approach is that the incompletely parabolic nature of the Navier-Stokes equation is taken into account; there is no diffusive term present in the mass conservation equation, and the test norm reflects that by requesting only limited regularity of $v_1$.\footnote{The situation is analagous to using the full $H^1(\Oh)$ norm for the pure convection equation --- the optimal test norm $\nor{v}_V = \nor{\beta\cdot \grad v} + \nor{v}$ implies only streamline regularity, whereas taking $\nor{v}_V = \nor{\grad v} + \nor{v}$ implies stronger regularity on the test space $V$ than the graph norm.
+Consequently, convergence is suboptimal for DPG applied to the convection problem under the $H^1(\Oh)$ test norm.}
+
+\section{Boundary conditions}
+
+As a consequence of the ultra-weak variational formulation, our solution is linear in the flux and trace variables.
+Thus, the nonlinear boundary conditions can be applied directly to our fluxes $\widehat{f}_{i,n}, i = 1,\ldots,4$, and traces $\widehat{u}_1$, $\widehat{u}_2$, and $\widehat{T}$.
+
+Additionally, inflow boundary conditions are applied not directly to the trace variables $\widehat{u}_1$, $\widehat{u}_2$, and $\widehat{T}$, but to the fluxes $\widehat{f}_{i,n}$.
+Extrapolating from the convection-diffusion problem, this allows us to use a stronger test norm without experiencing adverse effects for smaller diffusion/higher Reynolds numbers \cite{DPGrobustness,DPGrobustness2}.
 
@@
 \centering
-\includegraphics[scale=.5]{flat_plate_BCs.pdf}
+\includegraphics[scale=.5]{figs/flat_plate_BCs.pdf}
 \caption{Carter flat plate problem.}
@@
 We impose these strongly on the trace variables $\widehat{u}_1, \widehat{u}_2, \widehat{T}$.
-\item \textbf{Outflow boundary conditions:} the exact boundary conditions to enforce here are questionable\footnote{Demkowicz et al enforce this boundary condition only in regions where the flow is subsonic.}.
-Capon et al enforce $\pd{u_1}{n}=\pd{u_2}{n}=0$ and $\pd{T}{n} = 0$.
-Since $u_1$ and $u_2$ are not expected to be zero at these points, we will set $\widehat{f}_{2,n}$ and $\widehat{f}_{4,n}$ to their represented quantities using either the field variables from the background flow, or (in the case of pseudo-time stepping) the previous timestep's flux and field quantities.
+\item \textbf{Outflow boundary conditions:} the exact boundary conditions to enforce here are not universally agreed on\footnote{Demkowicz et al enforce an outflow boundary condition only in regions where the flow is subsonic.\cite{Demkowicz:1990:NFE:112271.112276}}.
+Many enforce $\pd{u_1}{n}=\pd{u_2}{n}=0$ and $\pd{T}{n} = 0$.
+We adopt a ``no boundary condition'' outflow condition, first introduced in \cite{FLD:FLD1650140506}.
+A mathematical analysis and explanation of this boundary condition for standard $H^1$ elements is given in \cite{FLD:FLD505}.
+
+An alternative boundary condition would be as follows: since $u_1$ and $u_2$ are not expected to be zero at these points, we can set $\widehat{f}_{2,n}$ and $\widehat{f}_{4,n}$ to their represented quantities using either the field variables from the background flow, or (in the case of pseudo-time stepping) the previous timestep's flux and field quantities.
+
 \end{itemize}
 
+\section{Numerical experiments}
+
+For our solver, we use a standard pseudo-time solver and a standard greedy refinement scheme.
+Though we have not yet implemented adaptive timestepping, we are able to take large enough uniform timesteps over a coarse mesh such that convergence is comparable to the convergence of a damped Newton method.
+
+The parameters used are as follows:
+\begin{itemize}
+\item{DPG parameters:} Both $p$ and $\Delta p = 2$ uniformly across the mesh. 
+\item{Adaptivity parameters:} Energy threshold for refinements is $\alpha = .2$ or $\alpha = .15$. 
+\item{Time-stepping parameters:} $\Delta t = .1$, and tolerance for transient residual $\epsilon_t = 5e-7$.
+\end{itemize}
+
+\subsection{Carter plate problem}
+
+For the flat plate problem, we take the domain $\Omega = [0,2]\times[0,1]$. For $\Reyn = 500$, we begin with an initial mesh of 8 by 16 elements. 
+\begin{figure}[!h]
+\centering
+\subfigure{\includegraphics[scale=.5]{figs/rhoRe500.pdf}}
+\subfigure{\includegraphics[scale=.5]{figs/u1Re500.pdf}}
+\subfigure{\includegraphics[scale=.5]{figs/u2Re500.pdf}}
+\subfigure{\includegraphics[scale=.5]{figs/TRe500.pdf}}
+\caption{Solutions after four refinements for $\rho$, $u_1$, $u_2$, and $T$ and $\Reyn = 500$.}
+\label{fig:Re500}
+\end{figure}
+
+For $\Reyn = 1000$, we experimented with both an initial mesh of 4 by 8 and 8 by 16 elements.
+We note that, on a very coarse initial mesh (4 by 8 elements), the convergence of the pseudo-timestep stagnates at around a transient residual of $1e-6$; however, if we lower the tolerance only for the first step and continued with the adaptive algorithm, the solution converges below $\epsilon_t$ for all refined meshes.
+\begin{figure}[!h]
+\centering
+\subfigure{\includegraphics[scale=.5]{figs/rhoRe1000.pdf}}
+\subfigure{\includegraphics[scale=.5]{figs/u1Re1000.pdf}}
+\subfigure{\includegraphics[scale=.5]{figs/u2Re1000.pdf}}
+\subfigure{\includegraphics[scale=.5]{figs/TRe1000.pdf}}
+\caption{Solutions after four refinements for $\rho$, $u_1$, $u_2$, and $T$ and $\Reyn = 500$.}
+\label{fig:Re500}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\subfigure[$\Reyn = 500$]{\includegraphics[scale=.5]{figs/MeshRe500.pdf}}
+\subfigure[$\Reyn = 1000$]{\includegraphics[scale=.5]{figs/MeshRe1000.pdf}}
+\caption{Adaptive mesh after four refinement iterations for $\Reyn = 500$ and $\Reyn = 1000$.}
+\label{fig:MeshRe500}
+\end{figure}
+
+\bibliographystyle{plain}
+\bibliography{notes}
+
 \end{document}

### 2012-06-06 docs/Jesse/Proposal/outline.tex
adding Jesse folder w/proposal outline

--- 2012-05-22 docs/NavierStokes/notes.tex
@@
 \author{Jesse Chan}
-\title{NS notes}
+\title{Proposal outline/notes}
 
@@
 
-\section{Intro}
+\section{Introduction}
 
-Following Demkowicz and Oden, we seek to solve 
-\[
-\sum^2_{i=1} G_i\left( U\right)_{,i}=\sum^2_{i=1} V_i\left( U\right)_{,i}
-\]
-where
-\[
-V_i = \vectfour{0}{\sigma_{i1}}{\sigma_{i2}}{\sum_{j=1}^2\sigma_{ij}u_j + q_i}
-\]
-are the viscous fluxes, and 
-\[
- G_1 = \vectfour{\rho u_1}{\rho u_1^2+p}{\rho u_1 u_2}{((\rho e)+p)u_1}, \qquad G_2 = \vectfour{\rho u_2}{\rho u_1 u_2}{\rho u_2^2+p}{((\rho e)+p)u_2}
-\]
-are the Eulerian fluxes.
+\subsection{Motivation and goal}
 
-We also have the constitutive relations 
-\begin{align*}
-\sigma_{ij} &= \mu(u_{i,j}+u_{j,i}) + \lambda u_{k,k}\delta_{ij}\\
-q_i &= \kappa T_{,i}\\
-p &= (\gamma-1)\rho\iota\\
-\iota &= e-\frac{1}{2}(u_1^2+u_2^2)\\
-\iota &= c_vT
-\end{align*}
-where $e$ and $\iota$ are energy and internal energy per unit mass, respectively.
+\begin{itemize}
+\item Adaptivity and stability for CFD problems are issues - cite David Young.
+\item To develop a stable $hp$-adaptive scheme for the steady laminar Navier-Stokes equations in transonic/supersonic regimes.
+\end{itemize}
 
-\section{Symbolic form}
-In symbolic form, we can write the Navier Stokes equations as a system of seven first order equations. Let $[u_1,u_2] = [u,v]$.
+\subsection{Literature review}
+\begin{enumerate}
+\item Finite difference, finite volumes
+\item Finite elements
 
-\subsection{Mass equation}
-\[
-\div \vecttwo{\rho u }{\rho v} = 0
-\]
-\subsection{Momentum equations}
-\begin{align*}
-\div \vecttwo{\rho u^2+p }{\rho u v} &= \div\left(\vec{\sigma_{i1}}\right)\\
-\div \vecttwo{\rho u v}{\rho v^2+p } &= \div\left(\vec{\sigma_{i2}}\right)
-\end{align*}
-\subsection{Energy equation}
-Let $\boldsymbol \sigma$ be a tensor whose $ij$th term is $\sigma_{ij}$.  
-\[
-\div\vecttwo{((\rho e)+p)u}{((\rho e)+p)v} = \div\left[\boldsymbol\sigma U + \vec{q}\right]
-\]
-\subsection{Newtonian fluid laws}
-We represent $\boldsymbol\sigma$ using the Newtonian fluid law
-\[
-\sigma_{ij} = \mu(u_{i,j} + u_{j,i}) + \lambda u_{k,k} \delta_{ij}
-\]
-where $\mu$ is viscosity and $\lambda$ is bulk viscosity. 
-%Following elasticity, a general formula for the stress tensor is 
-%\[
-%\sigma_{ij} = 2\mu \epsilon_{ij} + \lambda \epsilon_{kk} \delta_{ij}
-%\]
-We can invert the stress tensor under isotropic and plane strain assumptions to get
-%\[
-%\epsilon_{ij} = \frac{1}{2\mu} \sigma_{ij} - \frac{\lambda}{4\mu (\mu + \lambda)} \sigma_{kk}\delta_{ij}
-%\] 
-%which translates to
-\[
-\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \frac{1}{2\mu} \sigma_{ij} - \frac{\lambda}{4\mu (\mu + \lambda)} \sigma_{kk}\delta_{ij}
-\]
-We also have
-\[
-\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \grad  U - \boldsymbol \omega
-\]
-where $\boldsymbol \omega$ is the antisymmetric part of the infinitesimal strain tensor:
-\[
-\boldsymbol \omega = \frac{1}{2}\left(\grad  U - \grad ^T  U\right).
-\]
-Thus our final form is
-\begin{align*}
-\grad  U - \boldsymbol \omega = \frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I.
-\end{align*}
-Notice that $\boldsymbol \omega$ is implicitly defined to be the symmetric part of $\grad u$ by taking the symmetric part of the above equation.
+\begin{itemize}
+\item Taylor-Galerkin, SUPG
+\item Upwind DG, HDG (stabilization?)
+\item DPG
+\end{itemize}
 
-In general, $\mu$ and $\lambda$ are functions of temperature.
+\item Optimization/NL solvers (?)
+\end{enumerate}
 
-\subsection{Fourier's heat conduction law}
-\begin{align*}
-\vec{q} &= \kappa \grad T
-\end{align*}
-$\kappa$ is generally a function of temperature, and is often assumed to be proportional to $\mu$.
-
-We introduce here the Prandtl number here as well
-\[
-{\rm Pr} = \frac{\gamma c_v \mu}{\kappa}
-\]
-In this case, we assume a constant Prandlt number, implying that viscosity is proportional to conductivity.
-
-\subsection{Classical and momentum variables}
-
-In classical variables, our system of equations is now
-\begin{align*}
-\div \vecttwo{\rho u }{\rho v} &= 0\\
-\div \left(\vecttwo{\rho u^2+p }{\rho u v} - \boldsymbol \sigma_{1}\right) &=0\\
-\div \left(\vecttwo{\rho u v}{\rho v^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
-\div \left(\vecttwo{((\rho e)+p)u}{((\rho e)+p)v} - \boldsymbol\sigma \mathbf{u} + \vec{q}\right) &=0\\
-\frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I &= \grad \mathbf{u} - \boldsymbol \omega\\
-\frac{1}{\kappa}\vec{q} &= \grad T
-\end{align*}
-
-We strongly enforce symmetry of $\boldsymbol \sigma$ by setting $\sigma_{21} = \sigma_{12}$.
-
-\section{Nondimensionalization}
-To nondimensionalize our equations, we introduce nondimensional quantities for length, density, velocity, temperature, and viscosity. 
-\[
-\boldsymbol x^* = \frac{\boldsymbol x}{L}, \qquad \rho^* = \frac{\rho}{\rho_{\infty}}, \qquad \boldsymbol u^* = \frac{\boldsymbol u}{V_\infty}, \qquad T^* = \frac{T}{T_\infty}, \qquad \mu^* = \frac{\mu}{\mu_\infty}
-\]
-Momentum, pressure, internal energy, and bulk viscosity are then nondimensionalized with respect to the above variables
-\[
-\boldsymbol m^* = \frac{\boldsymbol m}{\rho_\infty V_\infty}, \qquad p^* = \frac{p}{\rho_\infty V_\infty^2}, \qquad \iota^* = \frac{\iota}{V_\infty^2}, \qquad \lambda^* = \frac{\lambda}{\mu_\infty}
-\]
-We introduce, for convenience, the Reynolds number
-\[
-{\rm Re} = \frac{\rho_\infty V_\infty L}{\mu_\infty} 
-\]
-and the reference (free stream) Mach number
-\[
-M_\infty = \frac{V_\infty}{\sqrt{\gamma(\gamma-1)c_vT_\infty}}
-\]
-Note that 
-\[
-a = \sqrt{\frac{\gamma p_\infty}{\rho_\infty}} = \sqrt{{\gamma p_\infty}} = \sqrt{\gamma(\gamma-1)c_vT_\infty}
-\]
-The equations take the same form as before after nondimensionalization, so long as we define new material constants
-\[
-\tilde{\mu} = \frac{\mu^*}{\rm Re}, \qquad \tilde{\lambda} = \frac{\lambda^*}{\rm Re}, \qquad \tilde{c}_v = \frac{1}{\gamma(\gamma-1)M_\infty^2}, \qquad \tilde{\kappa} = \frac{\gamma\tilde{c}_v\tilde{\mu}}{\rm Pr}
-\]
-From here on, we drop the $^*$ superscript and adopt the nondimensionalized equations.
-
-\subsection{Linearization}
-
-\subsubsection{Conservation laws}
-
-\begin{align*}
-\div \vecttwo{\rho u }{\rho v} &= 0\\
-\div \left(\vecttwo{\rho u^2+p }{\rho u v} - \boldsymbol \sigma_{1}\right) &=0\\
-\div \left(\vecttwo{\rho u v}{\rho v^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
-\div \left(\vecttwo{((\rho e)+p)u}{((\rho e)+p)v} - \boldsymbol \sigma_1 \cdot \boldsymbol u- \boldsymbol \sigma_2 \cdot \boldsymbol u + \vec{q}\right) &=0\\
-\end{align*}
-or generally, 
-\[
-\div (F_i(\boldsymbol U)-G_i(\boldsymbol U,\boldsymbol \sigma) = 0, \qquad i = 1,\ldots, 4
-\]
-The variational form restricted to a single element gives
-\[
-\langle \widehat{F}_i\cdot n, v\rangle - \int_K  (F(\boldsymbol U)-G_i(\boldsymbol U,\boldsymbol \sigma)) \cdot \grad v_i = 0 , \qquad i = 1,\ldots, 4
-\]
-and the variational form over the entire domain is given by summing up the element-wise contributions.
-
-The presence of terms such as $\boldsymbol \sigma_i \cdot \boldsymbol u$ means that we will need to linearize in the stress variables $\sigma_ij$ in addition to our Eulerian quantities.
-Since fluxes and traces are linear, we do not need to linearize them.
-Instead, fluxes $\widehat{F}_{i,n}$ and traces $\widehat{u},\widehat{v},\widehat{T}$ will represent normal traces and traces of the accumulated nonlinear solution.
-\begin{align*}
-\langle \widehat{F}_i\cdot n, v\rangle &- \int_K  \left(F_{i,\boldsymbol U}(\boldsymbol U)\cdot \Delta \boldsymbol U -G_{i,\boldsymbol U}(\boldsymbol U, \boldsymbol \sigma)\cdot \Delta \boldsymbol U - G_{i,\boldsymbol \sigma}(\boldsymbol U, \boldsymbol \sigma)\cdot \Delta \boldsymbol \sigma \right)\cdot \grad v_i \\
-&= \int_K  \left(F_i(\boldsymbol U)-G_i(\boldsymbol U)\right) \cdot \grad v_i \\
-\qquad i &= 1,\ldots, 4
-\end{align*}
-where
-\begin{align*}
-F^1_{1,\boldsymbol U} &= \{u,\rho ,0,0\} \\
-F^2_{1,\boldsymbol U} &= \{v,0,\rho ,0\} \\
-F^1_{2,\boldsymbol U} &=\left\{c_v T (\gamma -1)+u^2,2 u \rho ,0,c_v (\gamma -1) \rho \right\}\\
-F^2_{2,\boldsymbol U} &=\{u v,v \rho ,u \rho ,0\}\\
-F^1_{3,\boldsymbol U} &=\{u v,v \rho ,u \rho ,0\}\\
-F^2_{3,\boldsymbol U} &=\left\{c_v T (\gamma -1)+v^2,0,2 v \rho ,c_v (\gamma -1) \rho \right\}\\
-F^1_{4,\boldsymbol U} &=\left\{\frac{1}{2} u \left(2 c_v T (2 \gamma -1)+u^2+v^2\right),\frac{1}{2} \rho  \left(2 c_v T (2 \gamma -1)+3 u^2+v^2\right),u v \rho ,c_v u (2 \gamma -1) \rho \right\}\\
-F^2_{4,\boldsymbol U} &=\left\{\frac{1}{2} v \left(2 c_v T (2 \gamma -1)+u^2+v^2\right),u v \rho ,\frac{1}{2} \rho  \left(2c_v T (2 \gamma -1)+u^2+3 v^2\right),c_v v (2 \gamma -1) \rho \right\}
-\end{align*}
-The viscous Jacobians become (when linearized with respect to $\{\sigma_{11},\sigma_{12}, \sigma_{22}\}$)
-\begin{align*}
-G^1_{2,\boldsymbol \sigma} &= \{1,0,0\}\\
-G^2_{2,\boldsymbol \sigma} &= \{0,1,0\}\\
-G^1_{3,\boldsymbol \sigma} &= \{0,1,0\}\\
-G^2_{3,\boldsymbol \sigma} &= \{0,0,1\}\\
-G^1_{4,\boldsymbol \sigma} &= \{u_1,u_2,0\}\\
-G^2_{4,\boldsymbol \sigma} &= \{0,u_1,u_2\}
-\end{align*}
-and (when linearized with respect to the Eulerian variables)
-\begin{align*}
-G^1_{4,\boldsymbol U} &= \{0,\sigma_{11},\sigma_{12},0\}\\
-G^2_{4,\boldsymbol U} &= \{0,\sigma_{12},\sigma_{22},0\}
-\end{align*}
-
-\subsubsection{Viscous equations}
-We have two equations left to linearize - the constitutive laws defining our viscous stresses and heat flux terms. 
-\begin{align*}
-\frac{1}{2\mu}{\boldsymbol \sigma}- \frac{\lambda}{4\mu(\mu+\lambda)}{\rm tr}({\boldsymbol \sigma}){\boldsymbol I} + {\boldsymbol \omega} &= 
-\grad
-\left[\begin{array}{c}
-u_1\\
-u_2
-\end{array}
-\right]\\
-\frac{1}{\kappa}
-\left[\begin{array}{c}
-q_1\\
-q_2
-\end{array}\right] &=
-\grad T
-\end{align*}
-
-We treat the first tensor equation as two vector equations by considering each column:
-\begin{align*}
-\frac{1}{2\mu} \vecttwo{\sigma_{11}}{\sigma_{12}} - \frac{\lambda}{4\mu(\mu+\lambda)}\vecttwo{\sigma_{11}+\sigma_{22}}{0} + \vecttwo{0}{-\omega} - \grad u_1&= 0 \\
-\frac{1}{2\mu} \vecttwo{\sigma_{12}}{\sigma_{22}} - \frac{\lambda}{4\mu(\mu+\lambda)}\vecttwo{0}{\sigma_{11}+\sigma_{22}} + \vecttwo{\omega}{0} - \grad u_2 &= 0
-\end{align*}
-These equations are linear in $\sigma_{ij}$, so the linearization is simple. 
-Since all equations are linear in variables $q_1, q_2, w$ for all combinations of variables, we do not need to linearize any equations in $q_1, q_2, w$.
-
-\subsubsection{Initial guess}
-
-For our initial guesses, we set
-\[
-\rho = 1,\qquad m_1= 1,\qquad m_2 = 0, \qquad T = 1
-\]
-which is consistent with what was done in Demkowicz and Oden (find citation).
-
-\section{	Boundary conditions}
-
-\subsection{Carter flat plate}
-
-Our first problem of interest is the Carter flat plate problem. An infinitesmally thin flat plate disrupts a free stream flow and causes a shock to form at the tip of the plate.
+\section{Range of CFD problems}
 
@@
 \centering
-\includegraphics[scale=.5]{flat_plate_BCs.pdf}
-\caption{Carter flat plate problem.}
+\includegraphics[scale=.4]{CFD_tree.pdf}
+\caption{Common CFD problems and their simplifying assumptions.}
 \end{figure}
 
-\begin{itemize}
-\item \textbf{Inflow boundary conditions:} free stream conditions are applied here to all four fluxes $\widehat{f}_{i,n}$.
-\item \textbf{Symmetry boundary conditions:} $u_n = q_n = \pd{u_s}{n} = 0$.
-Here, this implies $u_2 = q_2 = \sigma_{12} = 0$.
-We impose the stress condition by noting that, for the flat plate geometry, if $u_2 = 0$, then at the top and bottom, with $n = (0,1)$, $\widehat{f}_{2,n} = \sigma_{12}$, and $\widehat{f}_{4,n} = q_2$ if $\sigma_{12}$ and $u_2 = 0$.
-\item \textbf{Flat plate boundary conditions:} $u_1 = u_2 = 0$, and $T = T_w = \left[1+(\gamma-1)M_\infty^2/2\right] T_\infty = 2.8T_\infty$ (for Mach 3 flow).
-We impose these strongly on the trace variables $\widehat{u}_1, \widehat{u}_2, \widehat{T}$.
-\item \textbf{Outflow boundary conditions:} the exact boundary conditions to enforce here are questionable\footnote{Demkowicz et al enforce this boundary condition only in regions where the flow is subsonic.}.
-Capon et al enforce $\pd{u_1}{n}=\pd{u_2}{n}=0$ and $\pd{T}{n} = 0$.
-Since $u_1$ and $u_2$ are not expected to be zero at these points, we will set $\widehat{f}_{2,n}$ and $\widehat{f}_{4,n}$ to their represented quantities using either the field variables from the background flow, or (in the case of pseudo-time stepping) the previous timestep's flux and field quantities.
-\end{itemize}
+\section{DPG: a minimum residual method for linear problems}
+
+\section{Robustness for convection-dominated diffusion}
+
+\section{DPG for nonlinear problems}
+
+Introduce nonlinear residual to measure convergence, DPG formulation for nonlinear problems. Discuss solution strategies (pseudo-timestep/damped Newton).
+
+Formulate DPG for Burgers' equation as an example, showing results, then show Navier-Stokes at a broad level.
+
+\section{Proposed work}
+
+\subsection{Area A}
+
+Analysis of (incompletely parabolic?) convection-diffusion systems
+
+\subsection{Area B}
+
+Nonlinear DPG - Hessian adjoint trick, anisotropic refinements, $hp$-adaptivity, distributed static condensation (if it's not implemented by then).
+
+\subsection{Area C}
+
+Ramp, bump, airfoil, Euler with NS regularization?
+
+\bibliographystyle{plain}
+\bibliography{paper,NS}
 

### 2012-06-06 docs/Jesse/Proposal/outline.tex
adding Jesse folder w/proposal outline

@@
 
+\subsection{Optimal test functions}
+
+\subsection{Ultra-weak variational formulation}
+
+\subsection{Test norms}
+
 \section{Robustness for convection-dominated diffusion}
+
+\begin{itemize}
+\item Describe mathematically the issue with standard Galerkin.
+\item Give proofs of robustness and numerical results (from paper)
+\end{itemize}
 
@@
 
-Introduce nonlinear residual to measure convergence, DPG formulation for nonlinear problems. Discuss solution strategies (pseudo-timestep/damped Newton).
-
-Formulate DPG for Burgers' equation as an example, showing results, then show Navier-Stokes at a broad level.
+\begin{itemize}
+\item Introduce nonlinear residual to measure convergence, DPG formulation for nonlinear problems. Briefly discuss solution strategies (pseudo-timestep/damped Newton). 
+\item Formulate DPG for Burgers' equation as an example, show results
+\item Show DPG applied to Navier-Stokes at a broad level, with results
+\end{itemize}
 

### 2012-06-08 docs/Jesse/Proposal/outline.tex
adding stuff to proposal older

@@
-\documentclass{article}
+\documentclass{report}
 
 \usepackage{array}
-\usepackage{amsmath}
-\usepackage{amssymb}
+\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
+\usepackage[utf8]{inputenc}
+\usepackage{listings}
+\usepackage{mathtools}
+\usepackage{dsfont}
+\usepackage{pdfpages}
+\usepackage[textsize=footnotesize,color=green]{todonotes}
+\usepackage{algorithm, algorithmic}
+\usepackage{bm}
+\usepackage{tikz}
+\usepackage[normalem]{ulem}
+
 \usepackage{graphicx}
@@
 \newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
-\newcommand{\nor}[1]{\left\| #1 \right\|}
 
@@
 \newcommand{\Reyn}{\rm Re}
+
+\newcommand{\bs}[1]{\boldsymbol{#1}}
+\DeclareMathOperator{\diag}{diag}
+
+\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}
+
+\newcommand{\tablab}[1]{\label{tab:#1}}
+\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
+
+\newcommand{\theolab}[1]{\label{theo:#1}}
+\newcommand{\theoref}[1]{\ref{theo:#1}}
+\newcommand{\eqnlab}[1]{\label{eq:#1}}
+\newcommand{\eqnref}[1]{\eqref{eq:#1}}
+\newcommand{\seclab}[1]{\label{sec:#1}}
+\newcommand{\secref}[1]{\ref{sec:#1}}
+\newcommand{\lemlab}[1]{\label{lem:#1}}
+\newcommand{\lemref}[1]{\ref{lem:#1}}
+
+\newcommand{\mb}[1]{\mathbf{#1}}
+\newcommand{\mbb}[1]{\mathbb{#1}}
+\newcommand{\mc}[1]{\mathcal{#1}}
+\newcommand{\nor}[1]{\left\| #1 \right\|}
+\newcommand{\snor}[1]{\left| #1 \right|}
+\newcommand{\LRp}[1]{\left( #1 \right)}
+\newcommand{\LRs}[1]{\left[ #1 \right]}
+\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
+\newcommand{\LRc}[1]{\left\{ #1 \right\}}
+\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
+\newcommand{\Grad} {\ensuremath{\nabla}}
+\newcommand{\Div} {\ensuremath{\nabla\cdot}}
+\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
+\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
+\newcommand{\uh}{\widehat{u}}
+\newcommand{\fnh}{\widehat{f}_n}
+\renewcommand{\L}{L^2\LRp{\Omega}}
+\newcommand{\pO}{\partial\Omega}
 \newcommand{\Gh}{\Gamma_h}
+\newcommand{\Gm}{\Gamma_{-}}
+\newcommand{\Gp}{\Gamma_{+}}
+\newcommand{\Go}{\Gamma_0}
 \newcommand{\Oh}{\Omega_h}
-\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
-\newcommand{\LRs}[1]{\left[ #1 \right]}
-\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
+
+\newcommand{\eval}[2][\right]{\relax
+  \ifx#1\right\relax \left.\fi#2#1\rvert}
+
+\def\etal{{\it et al.~}}
 
@@
 
+\newtheorem{proposition}{Proposition}
+\newtheorem{corollary}{Corollary}
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
+
 \begin{document}
 
-\section{Introduction}
+\tableofcontents
+\maketitle
 
-\subsection{Motivation and goal}
+\chapter{Introduction}
 
-\begin{itemize}
-\item Adaptivity and stability for CFD problems are issues - cite David Young.
-\item To develop a stable $hp$-adaptive scheme for the steady laminar Navier-Stokes equations in transonic/supersonic regimes.
-\end{itemize}
+\section{Motivations}
 
-\subsection{Literature review}
-\begin{enumerate}
-\item Finite difference, finite volumes
-\item Finite elements
+Adaptivity and stability for CFD problems are issues for high Reynolds and Mach numbers. 
+\todo{FINISH}
 
-\begin{itemize}
-\item Taylor-Galerkin, SUPG
-\item Upwind DG, HDG (stabilization?)
-\item DPG
-\end{itemize}
+Address the fact that CFD problems have issues of robustness; introduce reasoning that we will study the model problem of convection-diffusion first to better understand this.
 
-\item Optimization/NL solvers (?)
-\end{enumerate}
+\subsection{Singular perturbation problems and robustness}
 
-\section{Range of CFD problems}
+Historically, the Galerkin method has been very successfully applied to a broad range of problems in solid mechanics, for which the variational problems resulting from the PDE are symmetric and coercive (positive-definite).
+It is well known that the finite element method produces optimal or near-optimal results for such problems, with the finite element solution matching or coming close to the best approximation of the solution in the finite element space.
+However, standard Bubnov-Galerkin methods tend to perform poorly for the class of PDEs known as singular perturbation problems.
+These problems are often characterized by a parameter that may be either very small or very large in the context of physical problems.
+An additional complication of singular perturbation problems is that very often, in the limiting case of the parameter blowing up or decreasing to zero, the PDE itself will change types (e.g.\ from elliptic to hyperbolic).
+
+A canonical example of a singularly perturbed problem is the convection-diffusion equation. In 1D, the convection-diffusion equation is
+\begin{align*}
+\beta u'-\epsilon u'' &= f.
+\end{align*}
+The equation represents the change in the concentration $u$ of a quantity in a given medium, taking into account both convective and diffusive effects.
+$\beta$ represents the speed of convection, while the singular perturbation parameter $\epsilon$ represents the diffusivity of the medium.
+In the limit of an inviscid medium as $\epsilon\rightarrow 0$, the equation changes types, from elliptic to hyperbolic, and from second order to first order.
+For Dirichlet boundary conditions $u(0)=u_0$ and $u(1)= u_1$, the solution can develop sharp boundary layers of width $\epsilon$ near the outflow.
 
@@
 \centering
-\includegraphics[scale=.4]{CFD_tree.pdf}
-\caption{Common CFD problems and their simplifying assumptions.}
+\includegraphics[scale=.5]{figs/GalerkinOscTight.png}
+\caption{Oscillations in the finite element solution of the convection-diffusion equation for small diffusion.}
+\label{fig:GalerkinOsc}
 \end{figure}
 
-\section{DPG: a minimum residual method for linear problems}
+The poor performance of the finite element method for this problem is reflected in the bound on the error in the finite element solution --- under the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}:
+\[
+\|u-u_h\|_\epsilon \leq C \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
+\]
+for $\|u\|_\epsilon^2 \coloneqq \|u\|_{L^2}^2 + \epsilon \|u'\|_{L^2}^2$, with $C$ independent of $\epsilon$. An alternative formulation of the above bound is 
+\[
+\|u-u_h\|_{H^1(0,1)} \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
+\]
+where $C(\epsilon)$ grows as $\epsilon\rightarrow 0$.
+The dependence of the constant $C$ on $\epsilon$ is referred to as a \textit{loss of robustness} --- as the singular perturbation parameter $\epsilon$ decreases, our finite element error is bounded more and more loosely by the best approximation error.
+As a consequence, the finite element solution can diverge significantly from the best finite element approximation of the solution for very small values of $\epsilon$.
+For example, Figure~\ref{fig:GalerkinOsc} shows an example of how, on a coarse mesh, and for small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation with a boundary layer develops spurious oscillations everywhere in the domain, even where the best approximation error is small.
+These oscillations grow in magnitude as $\epsilon \rightarrow 0$, eventually polluting the entire solution.
 
-\subsection{Optimal test functions}
+\section{Goal}
 
-\subsection{Ultra-weak variational formulation}
+To develop a robust, stable $hp$-adaptive scheme for the steady compressible laminar Navier-Stokes equations in transonic/supersonic regimes.
+\todo{FINISH}
 
-\subsection{Test norms}
+\section{Literature review}
 
-\section{Robustness for convection-dominated diffusion}
+For the past half-century, problems in computational fluid dynamics (CFD) have been solved using a multitude of methods, many of which are physically motivated, and thus applicable only to a small number of problems and geometries.
+We consider more general methods, whose framework is applicable to different problems in CFD; however, our specific focus will be on the nonlinear shock problems of compressible aerodynamics.
+Broadly speaking, the most popular general methods include (in historical order) finite difference methods, finite volume methods, and finite element methods.
+
+\subsection{Finite difference and finite volume methods}
+
+For linear problems, finite difference (FD) methods approximate derivatives based on interpolation of pointwise values of a function.
+FD methods were popularized first by Lax, who introduced the concepts of the monotone scheme and numerical flux.
+For the conservation laws governing compressible aerodynamics, FD methods approximated the conservation law, using some numerical flux to reconstruct approximations to the derivative at a point.
+Finite volume (FV) methods are similar to finite difference methods, but approximate the integral version of a conservation law as opposed to the differential form.
+FD and FV have roughly the same computational cost/complexity; however, the advantage of FV methods over FD is that FV methods can be used on a much larger class of discretizations than FD methods, which require uniform or smooth meshes.
+
+For nonlinear shock problems, the solution often exhibits sharp gradients or discontinuities, around which the solution would develop spurious Gibbs-type oscillations.
+Several ideas were introduced to deal with oscillations in the solution near a sharp gradient or shock: artificial viscosity parameters, total variation diminishing (TVD) schemes, and slope limiters.
+However, each method had its drawback, either in terms of loss of accuracy, dimensional limitations, or problem-specific parameters to be tuned \cite{Shu:Lectures}.
+Harten, Enquist, Osher and Chakravarthy introduced the essentially non-oscillatory (ENO) scheme in 1987 \cite{ENO}, which was improved upon with the weighted essentially non-oscillatory (WENO) scheme in \cite{WENO}.
+WENO remains a popular choice today for both finite volume and finite difference schemes.
+
+Historically, finite volumes and finite difference methods have been the numerical discretizations of choice for CFD applications; the simplicity of implementation of the finite difference method allows for quick turnaround time, and the finite volume method is appealing due to its locally conservative nature and flexibility.
+More recently, the finite element (FE) method has gained popularity as a discretization method for CFD applications for its stability properties and rigorous mathematical foundations.
+Early pioneers of the finite element method for CFD included Zienkiewicz, Oden, Karniadakis, and Hughes \cite{ChungCFDBook}.
+
+\subsection{Stabilized finite element methods}
+
+The finite element/Galerkin method has been widely utilized in engineering to solve partial differential equations governing the behavior of physical phenomena in engineering problems.
+The method relates the solution of a partial differential equation (PDE) to the solution of a corresponding variational problem.
+The finite element method itself provides several advantages --- a framework for systematic mathematical analysis of the behavior of the method, weaker regularity constraints on the solution than implied by the strong form of the equations, and applicability to very general physical domains and geometries for arbitrary orders of approximation.
+
+Traditionally, instability/loss of robustness in finite element methods has been dealt with using residual-based stabilization techniques.
+Given some variational form, the problem is modified by adding to the bilinear form the strong form of the residual, weighted by a test function and scaled by a stabilization constant $\tau$.
+The most well-known example of this technique is the streamline-upwind Petrov-Galerkin (SUPG) method, which is a stabilized FE method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.
+SUPG stabilization not only removes the spurious oscillations from the finite element solution of the convection-diffusion equation, but delivers the best finite element approximation in the $H^1$ norm.
+
+An important difference between residual-based stabilization techniques and other stabilization methods is the idea of \textit{consistency} --- by adding stabilization terms based on the residual, the exact solution still satisfies the same variational problem (i.e.\ Galerkin orthogonality still holds).
+Contrast this to the artificial viscosity methods in finite difference and finite volume methods, where a specific amount of additional viscosity is added based on the magnitude of the convection and diffusion parameters: unlike residual-based stabilization schemes, the exact solution to the original equation no longer satisfies the new stabilized formulation.
+
+The addition of residual-based stabilization terms can also be interpreted as a modification of the test functions --- in other words, stabilization can be achieved by changing the test space for a given problem.
+We approach the idea of stabilization through the construction of \textit{optimal test functions} to achieve optimal approximation properties.
+
+\subsubsection{SUPG}
+
+\todo{FINISH - add SUPG detailed description and Hughes book diagrams for test functions.}
+
+\subsubsection{DG methods}
+
+Discontinuous Galerkin (DG) methods form a subclass of FEM; first introduced by Reed and Hill in \cite{Reed:73}, these methods were later analyzed by Cockburn and Shu \cite{CockburnShu:DG} and have rapidly gained popularity for CFD problems.
+Rather than having a continuous basis where the basis function support spans several element cells, DG opts instead for a discontinuous, piecewise polynomial basis, where, like FV schemes, a numerical flux facilitates communication between discontinuities (unlike FV methods, however, there is no need for a reconstruction step).
+Advantages of DG methods include easily modified local orders of approximation, easy adaptivity in both $h$ and $p$, and efficient parallelizability.
+
+An additional reason for the popularity of DG methods is that they can be interpreted as stabilized FE methods through appropriate choices of the numerical flux.
+For example, for the pure convection problem, the solution has only regularity in the streamline direction, but is only $L^2$ in the crosswind direction.
+As a consequence, the boundary trace of the solution is defined only in the direction of convection.
+The upwind DG method addresses the above issue by choosing the numerical flux to be the upwind flux; in 1D, this means the numerical flux between two elements is taken to be the left
+
+\todo{Add 1D description and diagrams (Hughes book) of DG formulation for convection with upwind flux.}
+
+In this case, the DG numerical flux can be viewed as imparting additional regularity than is present in the solution \cite{DPG1,DPG3}.
+
+A more recent development in DG methods is the idea of \emph{hybridized} DG (HDG), introduced by Gopalakrishnan and Lazarov \cite{hybridDG}.
+The hybridized DG framework addresses several criticisms of common DG methods (globally coupled degrees of freedom, complicated/inefficient implementation procedures, suboptimal convergence of approximate fluxes) by identifying degrees of freedom with support only on element edges.
+Neighboring elements are coupled together only through these degrees of freedom, which can be interpreted as Lagrange multipliers enforcing weak continuity of the trial space.
+Additionally, HDG methods
+
+\subsubsection{Optimization/NL solvers}
+
+Reference (MIT, Fidkowski)
+
+\todo{Find more nonlinear solvers}
+
+\section{Scope}
+
+This proposal will
+\begin{enumerate}
+\item Introduce DPG
+\item Cover the problem of robustness for model problems
+\item Extend results/formulations to nonlinear problems
+\item Discuss proposed work
+\end{enumerate}
+
+\chapter{Range of CFD problems}
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=.45]{figs/CFD_tree.pdf}
+\caption{A diagram of common CFD problems and their simplifying assumptions.}
+\end{figure}
+
+\begin{itemize}
+\item Discuss full compressible Navier-Stokes with boundary layers
+\item Discuss full compressible Navier-Stokes without boundary layers, connect to Euler (mention Dr Young and Boeing and the IBL connection \cite{BoeingDrela})
+\item Discuss model problems
+\end{itemize}
+
+\chapter{Discontinuous Petrov-Galerkin: a minimum residual method for linear problems}
+
+The Discontinuous Petrov-Galerkin (DPG) method of Demkowicz and Gopalakrishnan was first formulated in \cite{DPG1} for the pure convection problem.
+
+Historically, the name DPG was given by Bottasso, Micheletti, Sacco and Causin to their method for elliptic problems in \cite{BottassoMichelettiSacco02}.
+The method was then extended to other problems, including convection-diffusion, in \cite{BottassoMichelettiSacco05,CausinSacco05,CausinSaccoBottasso05}.
+
+The key point in the method of Bottasso et al.\ was their method of hybridization of fluxes.
+Whereas HDG methods will identify an additional flux unknown on the boundary, the numerical flux coupling neighboring elements together is still typically computed in part using contributions from the field variables.
+In the DPG formulation, all numerical fluxes are declared to be independent unknowns, leaving the interior field degrees of freedom completely uncoupled from element to element.
+\todo{Finish, check if this is true.}
+
+The breakthrough came in \cite{DPG2}, where the concept of locally-computable optimal test functions led to the development of the DPG method in its current form.
+
+\todo{Clean up}
+This DPG method with optimal test functions is better understood in \cite{DPG3,DPG4}, extended to problems in \cite{DPGElas,stokesDPG}, well-posedness theory developed for Poisson and convection-diffusion in \cite{analysisDPG}, extended to large class of Friedrichs systems in \cite{Bui-ThanhDemkowiczGhattas11b}.
+\cite{practicalDPG}.
+
+Optimal order comparison to DG in \cite{DPG1}. Comparisons to other DG methods in \cite{Bui-ThanhDemkowiczGhattas11a,DGDPG}.
+
+\section{Optimal Petrov-Galerkin methods}
+
+\seclab{optimalTest} Petrov-Galerkin methods, in which the test space differs from the trial space, have been explored for over 30 years, beginning with the approximate symmetrization method of Barrett and
+Morton~\cite{BARRETT01101981}.
+The idea was continued with the SUPG method of Hughes, and the characteristic Petrov-Galerkin approach of Demkowicz and Oden~\cite{Demkowicz1986188}, which introduced the
+idea of tailoring the test space to change the norm in which a finite element method would converge.
+
+The idea of optimal test functions was introduced by Demkowicz and Gopalakrishnan in \cite{DPG2}.
+Conceptually, these optimal test functions are the natural result of the minimization of a residual corresponding to the operator form of a variational equation.
+The connection between stabilization and least squares/minimum residual methods has been observed previously \cite{GLS}.
+However, the method in \cite{DPG2} distinguishes itself by measuring the residual of the natural \textit{operator form of the equation}, which is posed in the dual space, and measured with the dual norm, as we now discuss.
+
+Throughout the paper, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U'$ and $V'$ as the respective topological dual spaces.
+Let $U_h \subset U$ and $V_h\subset V$ be finite dimensional subsets.
+We are interested in the following problem
+\begin{equation}
+\eqnlab{variationEq}
+\left\{
+  \begin{array}{l}
+    \text{Given } l \in V', \text{ find } u_h \in U_h  \text{ such that} \\ 
+    b(u_h,v_h) = l(v_h), \quad \forall v_h\in V_h,
+  \end{array}
+  \right.
+\end{equation}
+where $b\LRp{\cdot,\cdot}: U \times V \to \mbb{R}$ is a continuous
+bilinear form.  $U$ is chosen to be some trial space of approximating functions, but $V_h$ is as of yet unspecified.
+
+Throughout the paper, we suppose the variational
+problem \eqnref{variationEq} to be well-posed. In that case, we can
+identify a unique operator $B:U\rightarrow V'$ such that
+\[
+\langle Bu,v\rangle_V \coloneqq b(u,v), \quad u\in U, v\in V
+\]
+with $\LRa{\cdot, \cdot}_V$ denoting the duality pairing between $V'$ and $V$, to obtain the operator form of the continuous variational problem
+\begin{equation}
+\eqnlab{dualEq}
+Bu = l \quad \text{in } V'.
+\end{equation}
+In other words, we can represent the continuous form of our variational equation
+\eqnref{variationEq} equivalently as the operator equation \eqnref{dualEq} with values in the
+dual space $V'$.  This motivates us to consider the conditions under which the solution to \eqnref{variationEq} is the solution to the minimum residual problem in $V'$ 
+\[
+u_h = \underset{u_h\in U_h}{\arg\min}\, J(u_h),
+\]
+where $J(w)$ is defined for $w\in U$ as 
+\[
+J(w) = \frac{1}{2}\|Bw-l\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(w,v)-l(v)|^2}{\nor{v}_V^2}.
+\]
+For convenience in writing, we will abuse the notation $\sup_{v \in V}$ to denote $\sup_{v\in V\setminus\{0\}}$ for the remainder of the paper.
+
+Let us define $R_V: V \to V'$ as the Riesz map, which identifies
+elements of $V$ with elements of $V'$ by 
+\[
+\langle R_V v,\delta
+v\rangle_V \coloneqq(v, \delta v)_V, \quad \forall \delta v \in V.
+\]
+Here, $(\cdot, \cdot)_V$ denotes the
+inner product in $V$. As $R_V$ and its inverse, $R_V^{-1}$, are both
+isometries, e.g.\ $\|f\|_{V'} = \|R_V^{-1} f\|_V, \forall f \in V'$, we
+have
+\begin{equation}
+\eqnlab{minimization}
+\min_{u_h\in U_h} J(u_h) = \frac{1}{2}\left\|Bu_h-l\right\|_{V'}^2 =  \frac{1}{2}\left\|R_V^{-1}(Bu_h-l)\right\|_V^2.
+\end{equation}
+The first order optimality condition for \eqnref{minimization} requires
+the G\^ateaux derivative to be zero in all directions $\delta u \in
+U_h$, i\.e\.,
+\begin{align*}
+\left(R_V^{-1}(Bu_h-l),R_V^{-1}B\delta u\right)_V = 0, \quad \forall \delta u \in U. 
+\end{align*}
+We define, for a given $\delta u \in U$, the corresponding {\em optimal test function} $v_{\delta u}$
+\begin{equation}
+\eqnlab{optv}
+v_{\delta u} \coloneqq R_V^{-1}B\delta u \quad  \text{in } V.
+\end{equation} 
+The optimality condition then becomes
+\[
+ \langle Bu_h-l, v_{\delta u}\rangle_V = 0, \quad \forall \delta u \in U
+\]
+which is exactly the standard variational equation in
+ \eqnref{variationEq} with $v_{\delta u}$ as the test functions.
+We can define the optimal test space $V_{\rm opt} \coloneqq \{v_{\delta u} \text{ s.t.
+} \delta u\in U\}$.
+Thus, the solution of the variational problem \eqnref{variationEq} with test space $V_h = V_{\rm opt}$ minimizes the residual in the dual norm $\nor{Bu_h-l}_{V'}$.
+This is the key idea behind the concept of optimal test functions.
+
+Since $U_h \subset U$ is spanned by a finite number of basis functions $\LRc{\varphi_i}_{i=1}^N$, \eqnref{optv} allows us to compute (for each basis function) a corresponding optimal test function $v_{\varphi_i}$.
+The collection $\LRc{v_{\varphi_i}}_{i = 1}^N$ of optimal test functions then forms a basis for the optimal test space.
+In order to express optimal test functions defined in \eqnref{optv} in a more familiar form, we take  $\delta u = \varphi$, a generic basis function in $U_h$, and rewrite \eqnref{optv} as
+\[
+R_Vv_{\varphi} = B\varphi, \quad \text{in } V',
+\]
+which is, by definition, equivalent to
+\[
+\LRp{v_\varphi,\delta v}_V = \LRa{R_Vv_\varphi,\delta v}_{V}=
+\LRa{B\varphi, \delta v}_V = b\LRp{\varphi,\delta v}, \quad
+\forall \delta v \in V.
+\]
+%% Now, let us define the \textit{trial-to-test} operator $T =
+%% R_V^{-1}B$, which, by \eqnref{optv}, maps a trial function $\delta u$
+%% to its corresponding \textit{optimal} test function $v = T\delta u$.
+%% On the other hand,
+As a result, optimal test functions can be determined by solving the auxiliary
+variational problem
+\begin{equation}
+\eqnlab{optvVar}
+\left(v_\varphi,\delta v\right)_V = b(\varphi,\delta v), \quad \forall
+\delta v \in V.
+\end{equation}
+However, in general, for standard $H^1$ and $H({\rm div})$-conforming finite element methods, test functions are continuous over the entire domain, and hence solving variational problem \eqnref{optvVar} for each optimal test function requires a global operation over the entire mesh, rendering the method impractical.
+A breakthrough came through the development of
+discontinous Galerkin (DG) methods, for which basis functions are
+discontinuous over elements. In particular, the use of discontinuous
+test functions $\delta v$ reduces the problem of determining global 
+optimal test functions
+in \eqnref{optvVar} to local problems that can be solved in an
+element-by-element fashion.
+
+We note that solving \eqnref{optvVar} on each element exactly is
+infeasible since it amounts to inverting the Riesz map $R_V$ exactly.
+Instead, optimal test functions are approximated using the standard
+Bubnov-Galerkin method on an ``enriched" subspace $\tilde{V} \subset
+V$ such that $\dim(\tilde{V}) > \dim(U_h)$ elementwise \cite{DPG1, DPG2}. In this
+paper, we assume the error in approximating the optimal test functions
+is negligible, and refer to the work in \cite{practicalDPG} for
+estimating the effects of approximation error on the performance of DPG.
+
+It is now well known that the DPG method
+delivers the best approximation error in the ``energy norm" --- that is
+\cite{Bui-ThanhDemkowiczGhattas11a, DPG2,DPG4} 
+\begin{equation}
+\eqnlab{optimalError}
+\nor{u-u_h}_{U,E} = \inf_{w\in U_h} \nor{u-w}_{U,E},
+\end{equation}
+where the energy norm $\|\cdot \|_{U,E}$ is defined for a function $\varphi \in U$ as
+\begin{equation}
+\eqnlab{energyNorm} \|\varphi\|_{U,E} \coloneqq \sup_{v\in V}
+\frac{b(\varphi,v)}{\|v\|_V} = \sup_{\nor{v}_V = 1} b(\varphi,v) =
+\sup_{\nor{v}_V = 1} \LRa{B\varphi,v}_V = \nor{B\varphi}_{V'} =
+\nor{v_\varphi}_V,
+\end{equation}
+where the last equality holds due to the isometry of the Riesz map
+$R_V$ (or directly from \eqnref{optvVar} by taking the supremum). An
+additional consequence of adopting such an energy norm is that,
+without knowing the exact solution, the energy error $\|u-u_h\|_{U,E}$ can
+be determined by computing $\|v_{u-u_h}\|_V$ from the following
+identity
+\[
+\left(v_{u-u_h},\delta v\right)_V = b(u-u_h,\delta v) = l\LRp{\delta
+v} - b(u_h,\delta v).
+\]
+This is simply a consequence of the least-squares nature of DPG; the energy error is simply the norm of the  residual in $V'$.
+
+Practically speaking, this implies that the DPG method is discretely stable on any mesh.
+In particular, DPG is unconditionally stable for higher order adaptive meshes, where discrete stability is often an issue.
+
+\section{Ultra-weak variational formulation}
+\seclab{abstractUweak}
+
+The naming of the discontinuous Petrov-Galerkin method refers to the fact that the method is a Petrov-Galerkin method, and that the test functions are specified to be discontinuous across element boundaries.
+There is no specification of the regularity of the trial space, and we stress that the idea of DPG is not inherently tied to a single variational formulation \cite{Bui-ThanhDemkowiczGhattas11a}.
+
+In most of the DPG literature, however, the discontinuous Petrov-Galerkin method refers to the combination of the concept of locally computable optimal test functions in Section \secref{optimalTest} with the so-called ``ultra-weak formulation" \cite{DPG1,DPG2,DPG3,DPG4,DPGElas,DBLP:journals/procedia/NiemiCC11}.
+Unlike the previous two sections in which we studied the general equation \eqnref{variationEq} given by abstract bilinear and linear forms, we now consider a concrete instance of \eqnref{variationEq} resulting from an ultra-weak formulation for an abstract first-order system of PDEs $Au = f$.
+Additionally, from this section onwards, we will refer to DPG as the pairing of the ultra-weak variational formulation with the concept of locally computable optimal test functions.
+
+We begin by partitioning the domain of interest $\Omega$ into $\Nel$ non-overlapping elements $K_j, j = 1,\hdots,\Nel$ such that $\Oh = \cup_{j=1}^\Nel K_j$ and $\overline{\Omega} = \overline{\Omega}_h$.
+Here, $h$ is defined as $h= \max_{j\in \LRc{1,\hdots,\Nel}}\text{diam}\LRp{K_j}$.
+We denote the mesh ``skeleton" by $\Gh = \cup_{j=1}^\Nel \partial K_j$; the set of all faces/edges $e$, each of which comes with a normal vector ${n}_e$.
+The internal skeleton is then defined as $\Gamma^0_h = \Gh \setminus \partial \Omega$.
+If a face/edge $e \in \Gh$ is the intersection of $\partial K_i$ and $\partial K_j$, $i \ne j$, we define the following jumps:
+\[
+\jump{v} = \text{sgn} \LRp{{n}^-}v^- + \text{sgn} \LRp{{n}^+}v^+, \quad
+\jump{\tau \cdot n} = {n}^-\cdot \tau^- + {n}^+\cdot\tau^+,
+\]
+where
+\[
+\text{sgn}\LRp{{n}^{\pm}} =
+\left\{
+\begin{array}{ll}
+1 & \text{if } {n}^{\pm} = {n}_e \\
+-1 & \text{if } {n}^\pm = -{n}_e
+\end{array}
+\right..
+\]
+For $e$ belonging to the domain boundary $\partial \Omega$, we define
+\[
+\jump{v} = v, \quad
+\jump{\tau \cdot n} = {n}_e\cdot \tau.
+\]
+Note that we allow arbitrariness in assigning ``-'' and ``+'' quantities to the adjacent elements $K_i$ and $K_j$.
+%For the rest of the paper, we will use the same notation for both a function and its trace (if it is well-defined) when there is no ambiguity.
+
+The ultra-weak formulation for $Au = f$ on $\Oh$, ignoring boundary
+conditions for now, reads
+\begin{equation}
+\eqnlab{uweak}
+b\left(\left(u, \widehat{u}\right),v\right) \coloneqq \langle \widehat{u}, \jump{v}
+\rangle_{\Gh} - (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh},
+\end{equation}
+where we have denoted $\LRa{\cdot,\cdot}_{\Gh}$ as the duality
+pairing on $\Gh$, $\LRp{\cdot,\cdot}_{\Oh}$ the $L^2$-inner
+product over $\Oh$, and $A_h^*$ the formal adjoint resulting from
+element-wise integration by parts.  Occasionally, for simplicity in
+writing, we will ignore the subscripts in the duality pairing and
+$L^2$-inner product if they are $\Gh$ and $\Oh$. Both the
+inner product and formal adjoint are understood to be taken
+element-wise. Using the ultra-weak formulation, the regularity
+requirement on solution variable $u$ is relaxed, that is, $u$ is now
+square integrable for the ultra-weak formulation \eqnref{uweak} to be
+meaningful, instead of being (weakly) differentiable.  The trade-off
+is that $u$ does not admit a trace on $\Gh$ even though it did
+originally. Consequently, we need to introduce an additional new
+``trace'' variable $\widehat{u}$ in \eqnref{uweak}, that is defined only on
+$\Gh$.
+
+The energy setting is now clear; namely,
+\[
+u\in L^2\LRp{\Oh} \equiv L^2(\Omega), \quad v\in V=D(A^*_h), \quad
+\widehat{u}\in \gamma(D(A)),
+\]
+where $D(A_h^*)$ denotes the broken graph space corresponding to $A_h^*$,
+and $\gamma(D(A))$ the trace space (assumed to exist) of the graph space of
+operator $A$.
+The first discussion of the well-posedness of DPG with the ultra-weak formulation can be found in \cite{analysisDPG}, where the proof is presented for the Poisson and convection-diffusion equations.
+A more comprehensive discussion of the abstract setting for DPG with the ultra-weak formulation using the graph space, as well as a more general proof of well-posedness, can be consulted in \cite{Bui-ThanhDemkowiczGhattas11b}.
+
+\section{Choices of test and trial norms}
+\seclab{energyPair}
+
+A clear property of the energy norm defined by \eqnref{energyNorm} is that the trial norm $\nor{\cdot}_{U,E}$ is induced by a given test norm.
+However, the reverse relationship holds as well; for any trial norm, the test norm that induces such a norm is recoverable through duality.
+We have a result, proved in \cite{Bui-ThanhDemkowiczGhattas11a}: assuming, for simplicity, that the bilinear form $b(u,v)$ is definite, given any norm $\nor{\cdot}_{U}$ on the trial space $U$, for $\varphi \in U$, we can represent $\nor{\varphi}_{U}$ via
+\[
+\nor{\varphi}_{U} = \sup_{v \in V}\frac{b\LRp{w,v}}{\nor{v}_{V,U}}.
+\]
+where $\nor{v}_{V,U}$ is defined through
+\[
+\nor{v}_{V,U} = \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U}}.
+\]
+%In other words, the norm $\nor{\cdot}_V$ in $V$ can be recovered using the energy norm $\nor{\cdot}_{U,E}$ in $U$, and vice versa.
+
+In particular, given two arbitrary norms $\nor{\cdot}_{U,1}$ and $\nor{\cdot}_{U,2}$ in $U$
+such that $\nor{\cdot}_{U,1} \le c \nor{\cdot}_{U,2}$ for some constant
+$c$, they generate two norms $\nor{\cdot}_{V,U,1}$ and
+$\nor{\cdot}_{V,U,2}$ in $V$ defined by
+\[
+\nor{v}_{V,U,1} \coloneqq \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U,1}}, \quad
+\text{and }\nor{v}_{V,U,2} \coloneqq \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U,2}},
+\]
+such that $\nor{\cdot}_{V,U,1}$ and $\nor{\cdot}_{V,U,2}$ induce
+$\nor{\cdot}_{U,1}$ and $\nor{\cdot}_{U,2}$ as energy
+norms in $U$, respectively. That is,
+\[
+\|\varphi\|_{U,1} = \sup_{v\in V}
+\frac{b(\varphi,v)}{\|v\|_{V,U,1}}, \quad \text{and }\|\varphi\|_{U,2} = \sup_{v\in V}
+\frac{b(\varphi,v)}{\|v\|_{V,U,2}}.
+\]
+
+A question that remains to be addressed is to establish the relationship
+between $\nor{\cdot}_{V,U,1}$ and $\nor{\cdot}_{V,U,2}$, given that
+$\nor{\cdot}_{U,1} \le c \nor{\cdot}_{U,2}$. But this is
+straightforward since we have
+\begin{align*}
+ \| v \|_{V,U,2} = \sup_{u \in U} \frac{b\left(w,v\right)}{\left\|
+  w \right\|_{U,2}} \le c\sup_{w \in U} \frac{b\left(w,v\right)}{\left\| w
+  \right\|_{U,1}} = c\| v \|_{V,U,1}.
+\end{align*}
+Consequently, a stronger energy norm in $U$ will generate a weaker
+norm in $V$ and vice versa. In other words, to show that an
+energy norm $\nor{\cdot}_{U,1}$ is weaker than another energy norm
+$\nor{\cdot}_{U,2}$ in $U$, one simply needs to show the reverse inequality on the
+corresponding norms in $V$, that is, $\nor{\cdot}_{V,U,1}$ is stronger
+than $\nor{\cdot}_{V,U,2}$.
+
+From now on, unless otherwise stated, we will refer to $\nor{\cdot}_{V,U}$ as the test norm that induces a given norm $\nor{\cdot}_U$.
+Likewise, we will refer $\nor{\cdot}_{U,V}$ as the trial norm induced by a given test norm $\nor{\cdot}_V$.
+In this paper, for simplicity of exposition, we shall call a pair of norms in $U$ and $V$ that induce each other as an {\em energy norm pairing}.
+
+From the discussion above of energy norm and test norm pairings, we know that specifying either a test norm or trial norm is sufficient to define an energy pairing.
+We now derive and discuss two important energy norm pairings, the first of which begins by specifying the canonical norm in $U$ and inducing a test norm on $V$.
+The second pairing begins instead by specifying the canonical norm on $V$ under the ultra-weak formulation \eqnref{uweak} and inducing an energy norm on the trial space $U$.
+
+We begin first with the canonical norm in $U$. Since $\uh \in \gamma\LRp{D\LRp{A}}$, the standard norm for $\uh$ is
+the so-called minimum energy extension norm defined as
+\begin{equation}
+\eqnlab{MEnorm}
+\|\widehat{u}\| = \inf_{w\in D\LRp{A},
+  \left.w\right|_{\Gh}=\widehat{u}} \|w\|_{D\LRp{A}}.
+\end{equation}
+The canonical norm for the group variable $\LRp{u,\uh}$ is then given by
+\[
+\|\left(u,\widehat{u}\right)\|_U^2 = \|u\|^2_{\L} + \|\widehat{u}\|^2,
+\]
+Applying the Cauchy-Schwarz inequality, we arrive at
+\[
+b\LRp{\LRp{u,\uh},v} \le \nor{\LRp{u,\uh}}_U \nor{v}_{V,U},
+\]
+where
+\[
+\nor{v}_{V,U}^2 = \|A_h^*v\|_{\L}^2
++\left(\sup_{\widehat{u} \in \gamma\LRp{D\LRp{A}}} \frac{\LRa{ \widehat{u},
+  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2.
+\]
+
+On the other hand, since $v \in D\LRp{A^*_h}$, the canonical norm for
+$v$ is the broken graph norm: 
+\[
+\nor{v}_V^2 =  \|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2.
+\]
+Using the Cauchy-Schwarz inequality again, we obtain
+\[
+b\LRp{\LRp{u,\uh},v} \le \nor{\LRp{u,\uh}}_{U,V} \nor{v}_{V},
+\]
+where
+\begin{equation}
+\eqnlab{inducedQuasi}
+\nor{\LRp{u,\uh}}_{U,V}^2 = \nor{u}_{\L}^2
++\sup_{v \in D\LRp{A_h^*}} \frac{\LRa{\widehat{u},
+  \jump{v}}_{\Gh}^2}{\|v\|_V^2},
+\end{equation}
+
+Using the framework developed in \cite{Bui-ThanhDemkowiczGhattas11a},
+one can show that both pairs $\LRp{\nor{\LRp{u,\uh}}_U,
+  \nor{v}_{V,U}}$ and $\LRp{\nor{\LRp{u,\uh}}_{U,V}, \nor{v}_{V}}$ are
+energy norm pairings in the sense discussed in Section
+\secref{energyPair}. That is, the canonical norm $\nor{\LRp{u,\uh}}_U$
+in $U$ induces (generates) the norm $\nor{v}_{V,U}$ in $V$, while the
+canonical norm $\nor{v}_V$ in $V$ induces (generates) the energy norm
+$\nor{\LRp{u,\uh}}_{U,V}$ in $U$. In the DPG literature \cite{DPG4}, $\nor{v}_{V,U}$ is known as the {\em optimal test norm},
+while $\nor{v}_{V}$ is known as the {\em quasi-optimal test norm}.
+
+\begin{figure}[!h]
+\centering
+\begin{tabular}{l c c}
+Trial norm & & Test norm \\
+\hline
+$\boxed{\|u\|^2_{\L} + \|\widehat{u}\|^2}$ & $\Longrightarrow$  & $\|A_h^*v\|_{\L}^2
++\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},
+  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2$ \\
+%\hline
+%Quasi-optimal trial norm & & Canonical test norm \\
+%\hline
+$\nor{u}_{\L}^2+\sup_{v } \left(\frac{\LRa{\widehat{u},
+  \jump{v}}_{\Gh}}{\|v\|_V}\right)^2$ &  $\Longleftarrow$ & $\boxed{\|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2}$
+\end{tabular}
+\caption{A summary of the derivation of test/trial norm pairings; we begin with the boxed norm on either the trial or test space, and induce the norm on the other space through duality.
+The optimal \textit{test} norm is naturally derived by beginning with the canonical norm on the trial space, while the quasi-optimal \textit{trial} norm is derived from beginning with the canonical norm on the test space.}
+\end{figure}
+
+The canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ provides a good
+balance between the standard norms on the field $u$ and the flux
+$\uh$ \cite{DPG4}. As a result, if the induced norm $\nor{v}_{V,U}$ (namely, the
+optimal test norm) is used to compute  optimal test functions in
+\eqnref{optvVar}, the finite element error in the canonical norm is the
+best in the sense of \eqnref{optimalError}.
+
+Unfortunately, the optimal test norm is non-localizable due to the presence of the jump term $\jump{v}$.\footnote{A localizable norm $\nor{v}_{V(\Oh)}$ can be written in the form $\nor{v}_{V(\Oh)} = \sum_{K\in\Oh} \nor{v}_{V(K)},$ where $\nor{v}_{V(K)}$ is a norm over the element $K$.} Since the jump terms couple elements together, the evaluation of the jump terms requires contributions from all the elements in the mesh.
+Consequently, solving for an optimal test function
+amounts to inverting the Riesz map %, defined on the left sideof \eqnref{optvVar}, 
+over the entire mesh $\Oh$, making the optimal test norm impractical.
+
+On the other hand, the quasi-optimal test norm $\nor{v}_V$, namely the canonical norm in $V$, \textit{is} localizable, and hence practical.
+However, it's worth noting the difference between the induced energy norm $\nor{\LRp{u,\uh}}_{U,V}$ and the canonical norm in $U$; under the induced norm $\nor{\LRp{u,\uh}}_{U,V}$ there is no natural interpretation for the norm in which the error in the flux variable $\uh$ is measured.
+
+Using a variant of the quasi-optimal test norm, numerical results show that the DPG method appears to provide a ``pollution-free" method without phase error for the Helmholtz equation \cite{DPG4}, and analysis of the pollution-free nature of DPG is currently under investigation.
+Similar results have also been obtained in the context of elasticity \cite{DPGElas} and the linear Stokes equations \cite{Camellia}.
+On the theoretical side, the quasi-optimal test norm has been shown to yield a well-posed DPG methodology for the Poisson and convection-diffusion equations \cite{analysisDPG}.
+More recently, this theory has been generalized to show the well-posedness of DPG for the large class of PDEs of Friedrichs' type \cite{Bui-ThanhDemkowiczGhattas11b}.
+
+\chapter{A robust DPG method for convection-dominated diffusion}
 
@@
 
-\section{DPG for nonlinear problems}
+\chapter{DPG for nonlinear problems}
 
@@
 
-\section{Proposed work}
+\section{Summary: completed/propsed work}
 
@@
 
-Analysis of (incompletely parabolic?) convection-diffusion systems
+\begin{itemize}
+\item{\textbf{Completed: }} Prove robustness of DPG method for the scalar convection-diffusion problem
+\item Attempt analysis of the linearized Navier-Stokes system
+\end{itemize}
 
@@
 
-Nonlinear DPG - Hessian adjoint trick, anisotropic refinements, $hp$-adaptivity, distributed static condensation (if it's not implemented by then).
+\begin{itemize}
+\item{\textbf{Completed: }} Collaborative work with Nathan Roberts on the higher order parallel adaptive DPG code Camellia.
+\item Nonlinear DPG - Hessian adjoint trick
+\item Adaptivity: anisotropic refinements and $hp$-schemes.
+\item Distributed static condensation
+\end{itemize}
 
@@
 
-Ramp, bump, airfoil, Euler with NS regularization?
+\begin{itemize}
+\item{\textbf{Completed: }} Convection-dominated diffusion, Burgers, and Navier-Stokes. 
+\item Higher Reynolds number, ramp problem, Gaussian bump, airfoil.
+\item Euler with NS regularization?
+\end{itemize}
 
 \bibliographystyle{plain}
-\bibliography{paper,NS}
+\bibliography{CFD_intro,DPG_old,paper,NS}
 

### 2012-06-12 docs/Jesse/Proposal/outline.tex
changes to outline and bib
adding more figs, mod of outline

@@
 
-A canonical example of a singularly perturbed problem is the convection-diffusion equation. In 1D, the convection-diffusion equation is
+A canonical example of a singularly perturbed problem is the convection-diffusion equation on domain $\Omega \in \mathbb{R}^3$,
+\[
+\div \left(\beta u\right) - \epsilon \Delta u = f.
+\]
+The equation represents the change in the scalar quantity $u$, representing the concentration of a quantity in a given medium, taking into account both convective and diffusive effects.
+$\beta \in \mathbb{R}^3$ specifies the direction and magnitude of convection, while the singular perturbation parameter $\epsilon$ represents the diffusivity of the medium.
+In the limit of an inviscid medium as $\epsilon\rightarrow 0$, the equation changes types, from elliptic to hyperbolic, and from second order to first order.
+
+We will illustrate the issues associated with numerical methods for this equation using one dimensional examples.  In 1D, the convection-diffusion equation is
 \begin{align*}
@@
 \end{align*}
-The equation represents the change in the concentration $u$ of a quantity in a given medium, taking into account both convective and diffusive effects.
-$\beta$ represents the speed of convection, while the singular perturbation parameter $\epsilon$ represents the diffusivity of the medium.
-In the limit of an inviscid medium as $\epsilon\rightarrow 0$, the equation changes types, from elliptic to hyperbolic, and from second order to first order.
-For Dirichlet boundary conditions $u(0)=u_0$ and $u(1)= u_1$, the solution can develop sharp boundary layers of width $\epsilon$ near the outflow.
+For Dirichlet boundary conditions $u(0)=u_0$ and $u(1)= u_1$, the solution can develop sharp boundary layers of width $\epsilon$ near the outflow boundary $x=1$.
 
@@
 \centering
-\includegraphics[scale=.5]{figs/GalerkinOscTight.png}
-\caption{Oscillations in the finite element solution of the convection-diffusion equation for small diffusion.}
+\includegraphics[scale=.4]{figs/GalerkinOscTight.png}
+\caption{Oscillations in the 1D finite element solution of the convection-diffusion equation for small diffusion.}
 \label{fig:GalerkinOsc}
@@
 For nonlinear shock problems, the solution often exhibits sharp gradients or discontinuities, around which the solution would develop spurious Gibbs-type oscillations.
-Several ideas were introduced to deal with oscillations in the solution near a sharp gradient or shock: artificial viscosity parameters, total variation diminishing (TVD) schemes, and slope limiters.
+Several ideas were introduced to deal with oscillations in the solution near a sharp gradient or shock: artificial diffusion, total variation diminishing (TVD) schemes, and slope limiters.
 However, each method had its drawback, either in terms of loss of accuracy, dimensional limitations, or problem-specific parameters to be tuned \cite{Shu:Lectures}.
@@
 WENO remains a popular choice today for both finite volume and finite difference schemes.
+Most of these methods can be interpreted as adding some specific artificial diffusion to the given numerical scheme.
+We refer to such schemes as \emph{modified equation} methods, as the exact solution no longer satisfies the discrete system due to the presence of additional artificial diffusion.
 
@@
 
-An important difference between residual-based stabilization techniques and other stabilization methods is the idea of \textit{consistency} --- by adding stabilization terms based on the residual, the exact solution still satisfies the same variational problem (i.e.\ Galerkin orthogonality still holds).
-Contrast this to the artificial viscosity methods in finite difference and finite volume methods, where a specific amount of additional viscosity is added based on the magnitude of the convection and diffusion parameters: unlike residual-based stabilization schemes, the exact solution to the original equation no longer satisfies the new stabilized formulation.
-
-The addition of residual-based stabilization terms can also be interpreted as a modification of the test functions --- in other words, stabilization can be achieved by changing the test space for a given problem.
-We approach the idea of stabilization through the construction of \textit{optimal test functions} to achieve optimal approximation properties.
-
 \subsubsection{SUPG}
 
-\todo{FINISH - add SUPG detailed description and Hughes book diagrams for test functions.}
+The Streamline Upwind Petrov Galerkin (SUPG) method is a stabilization method for $H^1$-conforming finite elements, the idea of which was originally motivated by artificial diffusion techniques in finite differences.
+In particular, for the homogeneous 1D convection-diffusion equation, it is possible to recover, under a finite difference method, the exact solution at nodal points by adding an ``exact" artificial diffusion based on the mesh size $h$ and the magnitudes of the convection $\beta$ and the viscosity $\epsilon$.
+
+The idea of ``exact" artificial viscosity was adapted to finite elements not through the direct modification of the equations, but through the test functions and weighting of the residual.
+In particular, finite element and Galerkin methods are often referred to as ``weighted residual" methods, since the starting point of both is to multiply the residual by a particular test, or weighting, function.
+Standard Galerkin methods, known as Bubnov-Galerkin methods, simply choose these weighting functions to be the same as the the basis functions used to approximate the solution.
+A Petrov-Galerkin method refers to any Galerkin method other than a classical Bubnov-Galerkin method.
+
+We will introduce the SUPG method at an abstract level for illustrative purposes only.
+Further details and perspectives on the SUPG method can be found in \cite{SUPG}, as well as in an upcoming book by Hughes.
+The convection-diffusion equation can be written as follows:
+\[
+Lu = \left(L_{\rm adv} + L_{\rm diff} \right) u = f,
+\]
+where $L_{\rm adv} = \div \left(\beta u\right)$ is the first order advective operator, and $L_{\rm diff} = \epsilon \Delta u$ is the second-order diffusive operator.
+Let us assume $u$ to be a linear combination of piecewise-linear basis functions $\phi_i, i = 0,\ldots,N$.
+The SUPG method is then to solve
+\[
+\int_\Omega L u v + \int_\Omega \tau \left(L_{\rm adv}v\right)\left( L u - f\right) = \int_\Omega f v 
+\]
+for where $\tau$ is the SUPG parameter.
+For uniform meshes in 1D, $\tau$ is chosen such that, for $f=0$, the matrix system resulting from SUPG is exactly equal to the finite difference system under ``exact" artificial diffusion.
+However, unlike the artificial diffusion method, for $f\neq 0$, the SUPG method still delivers optimal stabilization.
+In fact, the SUPG finite element solution in 1D is nothing less than the nodal interpolant and the best $H^1$ approximation of the exact solution, as seen in Figure~\ref{fig:SUPG}.
+
+\begin{figure}[!h]
+\centering
+\subfigure[SUPG and standard FEM solutions]{\includegraphics[scale=.43]{figs/SUPG.png}}
+\subfigure[SUPG test function]{\includegraphics[scale=.22]{figs/SUPGtest.png}}
+\caption{SUPG and standard Bubnov-Galerkin solutions to the 1D convection-dominated diffusion equation, and a modified SUPG test function (in black) corresponding to a linear basis ``hat" function (in red).
+The upwind portion of the element is emphasized, while the downwind portion is decreased.
+The magnitude of the discontinuity between the upwind and downwind portion is controlled by the intrinsic timescale parameter $\tau$.
+}
+\label{fig:SUPG}
+\end{figure}
+
+The idea of emphasizing the upwind portion of a test function is an old idea, introduced in 1977 by Zienkiewicz et al.\ in \cite{zienkUpwind}.
+However, the precise amount of upwinding,\footnote{Insufficient upwinding results in a method which still exhibits oscillations and instabilities, while excessive upwinding leads to an overly diffusive method.} as well as the connection to residual-based stabilization methods, were novel to SUPG.
+To date, the SUPG is still the most popular stabilization method of choice for convection-diffusion type problems, in both academic and industry applications.
+
+An important feature of SUPG and other residual-based stabilization techniques that separates it from modified equation methods is the idea of \textit{consistency} --- by adding stabilization terms based on the residual, the exact solution still satisfies the same variational problem (i.e.\ Galerkin orthogonality still holds).
+Contrast this to the artificial diffusion methods in finite difference and finite volume methods, where a specific amount of additional viscosity is added based on the magnitude of the convection and diffusion parameters: unlike residual-based stabilization schemes, the exact solution to the original equation no longer satisfies the new stabilized formulation.
+
+This addition of residual-based stabilization terms can be interpreted as a modification of the test functions as well.  For SUPG, the formulation can equivalently be written as
+\[
+\int_\Omega\left( Lu-f\right) v_i = \int_\Omega f v_i, \quad i = 0,\ldots,N
+\]
+where $v_i$ is defined as
+\[
+v_i = \phi_i(x) + \tau L_{\rm adv} \phi_i.  
+\]
+In other words, the test function $v_i$ is a perturbation of the basis function $\phi_i$ by a scaled advective operator applied to $\phi_i$.
+For a linear $C^0$ basis function (the ``hat" function), this naturally leads to a bias in the upwind or streamline direction of the flow $\beta$, as seen in Figure~\ref{fig:SUPG}.
+
+An important connection can now be made --- stabilization can be achieved by changing the test space for a given problem.
+We will discuss in Section~\secref{optimalTest} approaching the idea of stabilization through the construction of \textit{optimal test functions} to achieve optimal approximation properties.
 
@@
 As a consequence, the boundary trace of the solution is defined only in the direction of convection.
-The upwind DG method addresses the above issue by choosing the numerical flux to be the upwind flux; in 1D, this means the numerical flux between two elements is taken to be the left
+The upwind DG method addresses the above issue by choosing the numerical flux to be the upwind flux; we will illustrate this with a 1D example.
 
@@
 Neighboring elements are coupled together only through these degrees of freedom, which can be interpreted as Lagrange multipliers enforcing weak continuity of the trial space.
-Additionally, HDG methods
+Additionally, HDG methods \todo{add bit about numerical fluxes still used, stabilization param}
 
@@
 \item Describe mathematically the issue with standard Galerkin.
-\item Give proofs of robustness and numerical results (from paper)
+\item Give proofs of robustness and numerical results (from paper)\cite{ChanHeuerBui-ThanhDemkowicz12}
 \end{itemize}

### 2012-06-12 docs/Jesse/Proposal/outline.tex
finished SUPG section minus a reference

@@
 \]
-where $L_{\rm adv} = \div \left(\beta u\right)$ is the first order advective operator, and $L_{\rm diff} = \epsilon \Delta u$ is the second-order diffusive operator.
+where $L_{\rm adv}u \coloneqq \div \left(\beta u\right)$ is the first order advective operator, and $L_{\rm diff}u \coloneqq \epsilon \Delta u$ is the second-order diffusive operator (then, roughly speaking, $L_{\rm diff} u = 0$).
 Let us assume $u$ to be a linear combination of piecewise-linear basis functions $\phi_i, i = 0,\ldots,N$.
@@
 However, the precise amount of upwinding,\footnote{Insufficient upwinding results in a method which still exhibits oscillations and instabilities, while excessive upwinding leads to an overly diffusive method.} as well as the connection to residual-based stabilization methods, were novel to SUPG.
-To date, the SUPG is still the most popular stabilization method of choice for convection-diffusion type problems, in both academic and industry applications.
+
+The method can be made to ``work" for $p>1$, but the results are not as strong as for linear elements, and there is no clear generalization of SUPG to higher order elements.
+Additionally, the stabilization properties of SUPG are weaker in higher dimensions, and the SUPG solution is no longer the $H^1$ best approximation for 2D and 3D problems \todo{find citation}.
+Despite these caveats, SUPG is still the most popular stabilization method of choice for convection-diffusion type problems, in both academic and industry applications.
 
@@
 Rather than having a continuous basis where the basis function support spans several element cells, DG opts instead for a discontinuous, piecewise polynomial basis, where, like FV schemes, a numerical flux facilitates communication between discontinuities (unlike FV methods, however, there is no need for a reconstruction step).
-Advantages of DG methods include easily modified local orders of approximation, easy adaptivity in both $h$ and $p$, and efficient parallelizability.
+Advantages of DG methods include the local conservation property, easily modified local orders of approximation, easy adaptivity in both $h$ and $p$, and efficient parallelizability.
 
-An additional reason for the popularity of DG methods is that they can be interpreted as stabilized FE methods through appropriate choices of the numerical flux.
-For example, for the pure convection problem, the solution has only regularity in the streamline direction, but is only $L^2$ in the crosswind direction.
-As a consequence, the boundary trace of the solution is defined only in the direction of convection.
-The upwind DG method addresses the above issue by choosing the numerical flux to be the upwind flux; we will illustrate this with a 1D example.
+An additional reason for the popularity of DG methods is that they can be interpreted as stabilized FE methods through appropriate choices of the numerical flux \todo{add Brezzi citation}.
+We will illustrate this with the pure convection equation in 1D.
+
+Local conservation: in 1D, numerical solution at outflow is exact.
 
@@
 
-In this case, the DG numerical flux can be viewed as imparting additional regularity than is present in the solution \cite{DPG1,DPG3}.
+For example, for the pure convection problem, the solution has only regularity in the streamline direction, but is only $L^2$ in the crosswind direction.
+As a consequence, the boundary trace of the solution is defined only in the direction of convection.
+The upwind DG method addresses the above issue by choosing the numerical flux to be the upwind flux; in this case, the DG numerical flux can be viewed as imparting additional regularity than is present in the solution \cite{DPG1,DPG3}.
 

### 2012-06-12 docs/Jesse/Proposal/outline.tex
fixed wording of DG section

@@
 Discontinuous Galerkin (DG) methods form a subclass of FEM; first introduced by Reed and Hill in \cite{Reed:73}, these methods were later analyzed by Cockburn and Shu \cite{CockburnShu:DG} and have rapidly gained popularity for CFD problems.
-Rather than having a continuous basis where the basis function support spans several element cells, DG opts instead for a discontinuous, piecewise polynomial basis, where, like FV schemes, a numerical flux facilitates communication between discontinuities (unlike FV methods, however, there is no need for a reconstruction step).
+Rather than having a continuous basis where the basis function support spans several element cells, DG opts instead for a discontinuous, piecewise polynomial basis, where, like FV schemes, a numerical flux facilitates communication between neighboring elements (unlike FV methods, however, there is no need for a reconstruction step).
 Advantages of DG methods include the local conservation property, easily modified local orders of approximation, easy adaptivity in both $h$ and $p$, and efficient parallelizability.

### 2012-06-13 docs/Jesse/Proposal/outline.tex
adding dg to proposal

@@
 
-An additional reason for the popularity of DG methods is that they can be interpreted as stabilized FE methods through appropriate choices of the numerical flux \todo{add Brezzi citation}.
-We will illustrate this with the pure convection equation in 1D.
-
-Local conservation: in 1D, numerical solution at outflow is exact.
+An additional reason for the popularity of DG methods is that they can be interpreted as stabilized FE methods through appropriate choices of the numerical flux \cite{Brezzi20063293}.
+We will illustrate this with the pure convection equation in 1D ---
+\begin{align*}
+\pd{\left(\beta u\right)}{x} &= f\\
+u(0) &= u_0.
+\end{align*}
+The DG formulation is derived by multiplying by a test function $v$ with support only on a single element $K = [x_K,x_{K+1}]$ and integrating by parts.
+The boundary term is left alone, such that the local formulation is
+\[
+\left.\beta u v\right|_{x_K}^{x_{K+1}} + \int_K -\beta u \pd{v}{x} = \int_K f v,
+\]
+and the global formulation is recovered by summing up all element-wise local formulations.
+However, the boundary term in the local formulation is presently ill-defined, as both $u$ and $v$ are dual-valued over element boundaries.
+Consequently, we make the choice to define the values of $u$ on the boundary (the \emph{traces} of $u$) as
+\begin{align*}
+u(x_K) \coloneqq u(x_K^-), \quad u(x_{K+1}) \coloneqq u(x_{K+1}^-),
+\end{align*}
+where $u(x_K^-)$ is the value of $u$ at $x_K$ as seen from the left, and $u(x_K^+)$ the value as seen from the right. Similarly, the traces of $v$ are defined to be
+\begin{align*}
+v(x_K) \coloneqq v(x_K^+), \quad v(x_{K+1}) \coloneqq v(x_{K+1}^-),
+\end{align*}
+Notice the specific choice of $v(x_K)$ --- we have chosen the value of $v(x_K)$ to be the value in the upwind direction.
 
@@
 
-For example, for the pure convection problem, the solution has only regularity in the streamline direction, but is only $L^2$ in the crosswind direction.
-As a consequence, the boundary trace of the solution is defined only in the direction of convection.
+For example, for the pure convection problem, the solution has a distributional derivative in the streamline direction, but is only $L^2$ in the crosswind direction.
+As a consequence of the regularity of the solution, the boundary trace of the solution is defined only in the direction of convection.
 The upwind DG method addresses the above issue by choosing the numerical flux to be the upwind flux; in this case, the DG numerical flux can be viewed as imparting additional regularity than is present in the solution \cite{DPG1,DPG3}.
@@
 \bibliographystyle{plain}
-\bibliography{CFD_intro,DPG_old,paper,NS}
+\bibliography{CFD_intro,DPG_old,paper,LitRev}
 

### 2012-06-13 docs/Jesse/HeuerPaper/paper.tex
moving paper to Jesse/HeuerPaper

%&pdflatex
\documentclass[11pt,onecolumn]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
\usepackage[top=2cm,bottom=3cm,left=2.5cm,right=2cm]{geometry}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{array}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage[textsize=footnotesize,color=green]{todonotes}
\usepackage{algorithm, algorithmic}
\usepackage{array}
\usepackage{bm}
\usepackage{tikz}
\usepackage{subfigure}
\usepackage[normalem]{ulem}

\newcommand{\bs}[1]{\boldsymbol{#1}}
\DeclareMathOperator{\diag}{diag}

\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}

\newcommand{\tablab}[1]{\label{tab:#1}}
\newcommand{\tabref}[1]{Table~\ref{tab:#1}}

\newcommand{\theolab}[1]{\label{theo:#1}}
\newcommand{\theoref}[1]{\ref{theo:#1}}
\newcommand{\eqnlab}[1]{\label{eq:#1}}
\newcommand{\eqnref}[1]{\eqref{eq:#1}}
\newcommand{\seclab}[1]{\label{sec:#1}}
\newcommand{\secref}[1]{\ref{sec:#1}}
\newcommand{\lemlab}[1]{\label{lem:#1}}
\newcommand{\lemref}[1]{\ref{lem:#1}}

\newcommand{\mb}[1]{\mathbf{#1}}
\newcommand{\mbb}[1]{\mathbb{#1}}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\nor}[1]{\left\| #1 \right\|}
\newcommand{\snor}[1]{\left| #1 \right|}
\newcommand{\LRp}[1]{\left( #1 \right)}
\newcommand{\LRs}[1]{\left[ #1 \right]}
\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
\newcommand{\LRc}[1]{\left\{ #1 \right\}}
\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
\newcommand{\Grad} {\ensuremath{\nabla}}
\newcommand{\Div} {\ensuremath{\nabla\cdot}}
\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
\newcommand{\uh}{\widehat{u}}
\newcommand{\fnh}{\widehat{f}_n}
\renewcommand{\L}{L^2\LRp{\Omega}}
\newcommand{\pO}{\partial\Omega}
\newcommand{\Gh}{\Gamma_h}
\newcommand{\Gm}{\Gamma_{-}}
\newcommand{\Gp}{\Gamma_{+}}
\newcommand{\Go}{\Gamma_0}
\newcommand{\Oh}{\Omega_h}

\newcommand{\eval}[2][\right]{\relax
  \ifx#1\right\relax \left.\fi#2#1\rvert}

\def\etal{{\it et al.~}}

\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
\newcommand{\tensor}[1]{\underline{\vect{#1}}}
\newcommand{\del}{\Delta}
\newcommand{\grad}{\nabla}
\newcommand{\curl}{\grad \times}
\renewcommand{\div}{\grad \cdot}
\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
\newcommand{\eip}[1]{a\left( #1 \right)}
\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}

\newcommand{\circone}{\ding{192}}
\newcommand{\circtwo}{\ding{193}}
\newcommand{\circthree}{\ding{194}}
\newcommand{\circfour}{\ding{195}}
\newcommand{\circfive}{\ding{196}}

\def\arr#1#2#3#4{\left[
\begin{array}{cc}
#1 & #2\\
#3 & #4\\
\end{array}
\right]}
\def\vecttwo#1#2{\left[
\begin{array}{c}
#1\\
#2\\
\end{array}
\right]}
\def\vectthree#1#2#3{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
\end{array}
\right]}
\def\vectfour#1#2#3#4{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
#4\\
\end{array}
\right]}

\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

\newcommand{\G} {\Gamma}
\newcommand{\Gin} {\Gamma_{in}}
\newcommand{\Gout} {\Gamma_{out}}

\author{Jesse Chan\textsuperscript{a}, Norbert Heuer\textsuperscript{b}, Tan Bui-Thanh\textsuperscript{a}, and Leszek Demkowicz\textsuperscript{a}}

%\title{$\epsilon$-explicit analysis of DPG for convection-dominated diffusion}
\title{Robust DPG method for convection-dominated diffusion problems II: a natural inflow condition}
\date{}
\begin{document}

%\tableofcontents
\maketitle
\begin{center}
\textsuperscript{a} Institute for Computational Engineering and Sciences, \\University of Texas at Austin, \\Austin, TX 78712, USA\\
\end{center}

\begin{center}
\textsuperscript{b} Facultad de Matem\'aticas, \\Pontificia Universidad Cat\'olica de Chile,\\
Avenida Vicu\~na Mackenna 4860, Santiago, Chile
\end{center}

\section{Introduction}

\subsection{Singular perturbation problems and robustness}

The finite element/Galerkin method has been widely utilized in engineering to solve partial differential equations governing the behavior of physical phenomena in engineering problems.  The method relates the solution of a partial differential equation (PDE) to the solution of a corresponding variational problem. The finite element method itself provides several advantages --- a framework for systematic mathematical analysis of the behavior of the method, weaker regularity constraints on the solution than implied by the strong form of the equations, and applicability to very general physical domains and geometries.

Historically, the Galerkin method has been very successfully applied to a broad range of problems in solid mechanics, for which the variational problems resulting from the PDE are symmetric and coercive (positive-definite). It is well known that the finite element method produces optimal or near-optimal results for such problems, with the finite element solution matching or coming close to the best approximation of the solution in the finite element space. However, standard Bubnov-Galerkin methods tend to perform poorly for the class of PDEs known as singular perturbation problems. These problems are often characterized by a parameter that may be either very small or very large in the context of physical problems.  An additional complication of singular perturbation problems is that very often, in the limiting case of the parameter blowing up or decreasing to zero, the PDE itself will change types (e.g.\ from elliptic to hyperbolic).

\subsubsection{Convection-diffusion}

A canonical example of a singularly perturbed problem is the convection-diffusion equation.  %The equation models the convection of fluid along a direction $\beta$ with a viscous dissipation of magnitude $\epsilon$.  In the limit as $\epsilon\rightarrow 0$, the convection-diffusion equation transforms from a parabolic to a hyperbolic partial differential equation.  
In 1D, the convection-diffusion equation is
\begin{align*}
\beta u'-\epsilon u'' &= f.
\end{align*}
The equation represents the change in the concentration $u$ of a quantity in a given medium, taking into account both convective and diffusive effects. $\beta$ represents the speed of convection, while the singular perturbation parameter $\epsilon$ represents the diffusivity of the medium. In the limit of an inviscid medium as $\epsilon\rightarrow 0$, the equation changes types, from elliptic to hyperbolic, and from second order to first order. For Dirichlet boundary conditions $u(0)=u_0$ and $u(1)= u_1$, the solution can develop sharp boundary layers of width $\epsilon$ near the outflow.

%The finite element method has performed notoriously poorly for this example, as well as for many other singularly perturbed problems. This poor performance is captured by the error bound for the finite element method applied to the convection-diffusion equation - under the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}
The poor performance of the finite element method for this problem is reflected in the bound on the error in the finite element solution --- under the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}:
\[
\|u-u_h\|_\epsilon \leq C \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
\]
for $\|u\|_\epsilon^2 \coloneqq \|u\|_{L^2}^2 + \epsilon \|u'\|_{L^2}^2$, with $C$ independent of $\epsilon$. An alternative formulation of the above bound is 
\[
\|u-u_h\|_{H^1(0,1)} \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
\]
where $C(\epsilon)$ grows as $\epsilon\rightarrow 0$. The dependence of the constant $C$ on $\epsilon$ is referred to as a \textit{loss of robustness} --- as the singular perturbation parameter $\epsilon$ decreases, our finite element error is bounded more and more loosely by the best approximation error.  As a consequence, the finite element solution can diverge significantly from the best finite element approximation of the solution for very small values of $\epsilon$.  For example, on a coarse mesh, and for small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation with a boundary layer develops spurious oscillations everywhere in the domain, even where the best approximation error is small.  These oscillations grow in magnitude as $\epsilon \rightarrow 0$, eventually polluting the entire solution.

%, allowing for more and more error in the finite element solution for as $\epsilon$ shrinks. 
%Intuitively, a non-robust method will perform increasingly worse as $\epsilon$ decreases.

\subsubsection{Wave propagation}

Another example of a singular perturbation problem which experiences loss of robustness is high frequency wave propagation, in which the singular perturbation parameter is the wavenumber $k$, where $k\rightarrow \infty$. The loss of robustness in this case manifests as ``pollution" error, a phenomenon in which the finite element solution degrades over many wavelengths for high wavenumbers (commonly manifesting as a phase error between the FE solution and the exact solution).

\subsubsection{Stabilization terms}

Traditionally, instability/loss of robustness has been dealt with using residual-based stabilization techniques.  Given some variational form, the problem is modified by adding to the bilinear form the strong form of the residual, weighted by a test function and scaled by a stabilization constant $\tau$.  The most well-known example of this technique is the streamline-upwind Petrov-Galerkin (SUPG) method, which is a stabilized method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.  SUPG stabilization not only removes the spurious oscillations from the finite element solution of the convection-diffusion equation, but delivers the best finite element approximation in the $H^1$ norm.  An important difference between residual-based stabilization techniques and other stabilizations is the idea of \textit{consistency} --- by adding stabilization terms based on the residual, the exact solution still satisfies the same variational problem (i.e.\ Galerkin orthogonality still holds).\footnote{Contrast this to an artificial diffusion method, where a specific amount of additional viscosity is added based on the magnitude of the convection and diffusion parameters. The exact solution to the original equation no longer satisfies the new stabilized formulation.}

The addition of residual-based stabilization terms can also be interpreted as a modification of the test functions --- in other words, stabilization can be achieved by changing the test space for a given problem.  We approach the idea of stabilization through the construction of \textit{optimal test functions} to achieve optimal approximation properties.

%\textcolor{red}{add bit about SUPG/residual-based stabilization terms and test functions}

\subsection{Discontinuous Petrov-Galerkin methods with optimal test functions}
\seclab{optimalTest} Petrov-Galerkin methods, in which the test space
differs from the trial space, have been explored for over 30 years,
beginning with the approximate symmetrization method of Barrett and
Morton~\cite{BARRETT01101981}. The idea was continued with the SUPG
method of Hughes, and the characteristic Petrov-Galerkin approach of
Demkowicz and Oden~\cite{Demkowicz1986188}, which introduced the
idea of tailoring the test space to change the norm in which a finite
element method would converge.

The idea of optimal test functions was introduced by Demkowicz and
Gopalakrishnan in \cite{DPG2}.  Conceptually, these optimal test
functions are the natural result of the minimization of a residual
corresponding to the operator form of a variational equation. The
connection between stabilization and least squares/minimum residual
methods has been observed previously \cite{GLS}. However, the method in \cite{DPG2} distinguishes itself
by measuring the residual of the natural \textit{operator form of the equation}, which is posed in the dual space, and measured with the dual norm, as we now discuss.

Throughout the paper, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U'$ and $V'$ as the respective topological dual spaces. Let $U_h \subset U$ and $V_h\subset V$ be finite dimensional subsets. We are interested in the following problem  
\begin{equation}
\eqnlab{variationEq}
\left\{
  \begin{array}{l}
    \text{Given } l \in V', \text{ find } u_h \in U_h  \text{ such that} \\ 
    b(u_h,v_h) = l(v_h), \quad \forall v_h\in V_h,
  \end{array}
  \right.
\end{equation}
where $b\LRp{\cdot,\cdot}: U \times V \to \mbb{R}$ is a continuous
bilinear form.  $U$ is chosen to be some trial space of approximating functions, but $V_h$ is as of yet unspecified.

Throughout the paper, we suppose the variational
problem \eqnref{variationEq} to be well-posed. In that case, we can
identify a unique operator $B:U\rightarrow V'$ such that
\[
\langle Bu,v\rangle_V \coloneqq b(u,v), \quad u\in U, v\in V
\]
with $\LRa{\cdot, \cdot}_V$ denoting the duality pairing between $V'$ and $V$, to obtain the operator form of the continuous variational problem
\begin{equation}
\eqnlab{dualEq}
Bu = l \quad \text{in } V'.
\end{equation}
In other words, we can represent the continuous form of our variational equation
\eqnref{variationEq} equivalently as the operator equation \eqnref{dualEq} with values in the
dual space $V'$.  This motivates us to consider the conditions under which the solution to \eqnref{variationEq} is the solution to the minimum residual problem in $V'$ 
\[
u_h = \underset{u_h\in U_h}{\arg\min}\, J(u_h),
\]
where $J(w)$ is defined for $w\in U$ as 
\[
J(w) = \frac{1}{2}\|Bw-l\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(w,v)-l(v)|^2}{\nor{v}_V^2}.
\]
For convenience in writing, we will abuse the notation $\sup_{v \in V}$ to denote $\sup_{v\in V\setminus\{0\}}$ for the remainder of the paper.

Let us define $R_V: V \to V'$ as the Riesz map, which identifies
elements of $V$ with elements of $V'$ by 
\[
\langle R_V v,\delta
v\rangle_V \coloneqq(v, \delta v)_V, \quad \forall \delta v \in V.
\]
Here, $(\cdot, \cdot)_V$ denotes the
inner product in $V$. As $R_V$ and its inverse, $R_V^{-1}$, are both
isometries, e.g.\ $\|f\|_{V'} = \|R_V^{-1} f\|_V, \forall f \in V'$, we
have
\begin{equation}
\eqnlab{minimization}
\min_{u_h\in U_h} J(u_h) = \frac{1}{2}\left\|Bu_h-l\right\|_{V'}^2 =  \frac{1}{2}\left\|R_V^{-1}(Bu_h-l)\right\|_V^2.
\end{equation}
The first order optimality condition for \eqnref{minimization} requires
the G\^ateaux derivative to be zero in all directions $\delta u \in
U_h$, i\.e\.,
\begin{align*}
\left(R_V^{-1}(Bu_h-l),R_V^{-1}B\delta u\right)_V = 0, \quad \forall \delta u \in U. 
\end{align*}
We define, for a given $\delta u \in U$, the corresponding {\em optimal test function} $v_{\delta u}$
\begin{equation}
\eqnlab{optv}
v_{\delta u} \coloneqq R_V^{-1}B\delta u \quad  \text{in } V.
\end{equation} 
The optimality condition then becomes
\[
 \langle Bu_h-l, v_{\delta u}\rangle_V = 0, \quad \forall \delta u \in U
\]
which is exactly the standard variational equation in
 \eqnref{variationEq} with $v_{\delta u}$ as the test functions. We can define the optimal test space $V_{\rm opt} \coloneqq \{v_{\delta u} \text{ s.t. } \delta u\in U\}$. Thus, the solution of the variational problem \eqnref{variationEq} with test space $V_h = V_{\rm opt}$ minimizes the residual in the dual norm $\nor{Bu_h-l}_{V'}$. This is the key idea behind the concept of optimal test functions.

Since $U_h \subset U$ is spanned by a finite number of basis functions $\LRc{\varphi_i}_{i=1}^N$, \eqnref{optv} allows us to compute (for each basis function) a corresponding optimal test function $v_{\varphi_i}$. The collection $\LRc{v_{\varphi_i}}_{i = 1}^N$ of optimal test functions then forms a basis for the optimal test space.  In order to express optimal test functions defined in \eqnref{optv} in a more familiar form, we take  $\delta u = \varphi$, a generic basis function in $U_h$, and rewrite \eqnref{optv} as
\[
R_Vv_{\varphi} = B\varphi, \quad \text{in } V',
\]
which is, by definition, equivalent to
\[
\LRp{v_\varphi,\delta v}_V = \LRa{R_Vv_\varphi,\delta v}_{V}=
\LRa{B\varphi, \delta v}_V = b\LRp{\varphi,\delta v}, \quad
\forall \delta v \in V.
\]
%% Now, let us define the \textit{trial-to-test} operator $T =
%% R_V^{-1}B$, which, by \eqnref{optv}, maps a trial function $\delta u$
%% to its corresponding \textit{optimal} test function $v = T\delta u$.
%% On the other hand,
As a result, optimal test functions can be determined by solving the auxiliary
variational problem
\begin{equation}
\eqnlab{optvVar}
\left(v_\varphi,\delta v\right)_V = b(\varphi,\delta v), \quad \forall
\delta v \in V.
\end{equation}
However, in general, for standard $H^1$ and $H({\rm div})$-conforming finite element methods, test functions are continuous over the entire domain, and hence solving variational problem \eqnref{optvVar} for each optimal test function requires a global operation over the entire mesh, rendering the method impractical. A breakthrough came through the development of
discontinous Galerkin (DG) methods, for which basis functions are
discontinuous over elements. In particular, the use of discontinuous
test functions $\delta v$ reduces the problem of determining global 
optimal test functions
in \eqnref{optvVar} to local problems that can be solved in an
element-by-element fashion.

We note that solving \eqnref{optvVar} on each element exactly is
infeasible since it amounts to inverting the Riesz map $R_V$ exactly.
Instead, optimal test functions are approximated using the standard
Bubnov-Galerkin method on an ``enriched" subspace $\tilde{V} \subset
V$ such that $\dim(\tilde{V}) > \dim(U_h)$ elementwise \cite{DPG1, DPG2}. In this
paper, we assume the error in approximating the optimal test functions
is negligible, and refer to the work in \cite{practicalDPG} for
estimating the effects of approximation error on the performance of DPG.

It is now well known that the DPG method
delivers the best approximation error in the ``energy norm" --- that is
\cite{Bui-ThanhDemkowiczGhattas11a, DPG2,DPG4} 
\begin{equation}
\eqnlab{optimalError}
\nor{u-u_h}_{U,E} = \inf_{w\in U_h} \nor{u-w}_{U,E},
\end{equation}
where the energy norm $\|\cdot \|_{U,E}$ is defined for a function $\varphi \in U$ as
\begin{equation}
\eqnlab{energyNorm} \|\varphi\|_{U,E} \coloneqq \sup_{v\in V}
\frac{b(\varphi,v)}{\|v\|_V} = \sup_{\nor{v}_V = 1} b(\varphi,v) =
\sup_{\nor{v}_V = 1} \LRa{B\varphi,v}_V = \nor{B\varphi}_{V'} =
\nor{v_\varphi}_V,
\end{equation}
where the last equality holds due to the isometry of the Riesz map
$R_V$ (or directly from \eqnref{optvVar} by taking the supremum). An
additional consequence of adopting such an energy norm is that,
without knowing the exact solution, the energy error $\|u-u_h\|_{U,E}$ can
be determined by computing $\|v_{u-u_h}\|_V$ from the following
identity
\[
\left(v_{u-u_h},\delta v\right)_V = b(u-u_h,\delta v) = l\LRp{\delta
v} - b(u_h,\delta v).
\]
This is simply a consequence of the least-squares nature of DPG; the energy error is simply the norm of the  residual in $V'$.

Practically speaking, this implies that the DPG method is discretely stable on any mesh. In particular, DPG is unconditionally stable for higher order adaptive meshes, where discrete stability is often an issue.

\subsection{Duality between trial and test norms (energy norm pairings)}
%\subsection{Abstract energy norm pairings}
\seclab{energyPair}
A clear property of the energy norm defined by \eqnref{energyNorm} is that the trial norm $\nor{\cdot}_{U,E}$ is induced by a given test norm. However, the reverse relationship holds as well; for any trial norm, the test norm that induces such a norm is recoverable through duality. We have a result, proved in \cite{Bui-ThanhDemkowiczGhattas11a}: assuming, for simplicity, that the bilinear form $b(u,v)$ is definite, given any norm $\nor{\cdot}_{U}$ on the trial space $U$, for $\varphi \in U$, we can represent $\nor{\varphi}_{U}$ via
\[
\nor{\varphi}_{U} = \sup_{v \in V}\frac{b\LRp{w,v}}{\nor{v}_{V,U}}.
\]
where $\nor{v}_{V,U}$ is defined through
\[
\nor{v}_{V,U} = \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U}}.
\]
%In other words, the norm $\nor{\cdot}_V$ in $V$ can be recovered using the energy norm $\nor{\cdot}_{U,E}$ in $U$, and vice versa.

In particular, given two arbitrary norms $\nor{\cdot}_{U,1}$ and $\nor{\cdot}_{U,2}$ in $U$
such that $\nor{\cdot}_{U,1} \le c \nor{\cdot}_{U,2}$ for some constant
$c$, they generate two norms $\nor{\cdot}_{V,U,1}$ and
$\nor{\cdot}_{V,U,2}$ in $V$ defined by
\[
\nor{v}_{V,U,1} \coloneqq \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U,1}}, \quad
\text{and }\nor{v}_{V,U,2} \coloneqq \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U,2}},
\]
such that $\nor{\cdot}_{V,U,1}$ and $\nor{\cdot}_{V,U,2}$ induce
$\nor{\cdot}_{U,1}$ and $\nor{\cdot}_{U,2}$ as energy
norms in $U$, respectively. That is,
\[
\|\varphi\|_{U,1} = \sup_{v\in V}
\frac{b(\varphi,v)}{\|v\|_{V,U,1}}, \quad \text{and }\|\varphi\|_{U,2} = \sup_{v\in V}
\frac{b(\varphi,v)}{\|v\|_{V,U,2}}.
\]

A question that remains to be addressed is to establish the relationship
between $\nor{\cdot}_{V,U,1}$ and $\nor{\cdot}_{V,U,2}$, given that
$\nor{\cdot}_{U,1} \le c \nor{\cdot}_{U,2}$. But this is
straightforward since we have
\begin{align*}
 \| v \|_{V,U,2} = \sup_{u \in U} \frac{b\left(w,v\right)}{\left\|
  w \right\|_{U,2}} \le c\sup_{w \in U} \frac{b\left(w,v\right)}{\left\| w
  \right\|_{U,1}} = c\| v \|_{V,U,1}.
\end{align*}
Consequently, a stronger energy norm in $U$ will generate a weaker
norm in $V$ and vice versa. In other words, to show that an
energy norm $\nor{\cdot}_{U,1}$ is weaker than another energy norm
$\nor{\cdot}_{U,2}$ in $U$, one simply needs to show the reverse inequality on the
corresponding norms in $V$, that is, $\nor{\cdot}_{V,U,1}$ is stronger
than $\nor{\cdot}_{V,U,2}$.

%From now on, unless otherwise stated, we will refer to  $\nor{\cdot}_{V,U,1}$, $\nor{\cdot}_{V,U,2}$, and $\nor{\cdot}_{V}$ as the test norms which induce $\nor{\cdot}_{U,1}$, $\nor{\cdot}_{U,2}$, and $\nor{\cdot}_{U,E}$ and vice versa, in the sense discussed above. 
From now on, unless otherwise stated, we will refer to $\nor{\cdot}_{V,U}$ as the test norm that induces a given norm $\nor{\cdot}_U$. Likewise, we will refer $\nor{\cdot}_{U,V}$ as the trial norm induced by a given test norm $\nor{\cdot}_V$. In this paper, for simplicity of exposition, we shall call a pair of norms in $U$ and $V$ that induce each other as an {\em energy norm pairing}.

\subsection{Discontinuous Petrov-Galerkin methods with the ultra-weak formulation}
\seclab{abstractUweak}

The naming of the discontinuous Petrov-Galerkin method refers to the fact that the method is a Petrov-Galerkin method, and that the test functions are specified to be discontinuous across element boundaries. There is no specification of the regularity of the trial space, and we stress that the idea of DPG is not inherently tied to a single variational formulation \cite{Bui-ThanhDemkowiczGhattas11a}.

In most of the DPG literature, however, the discontinuous Petrov-Galerkin method refers to the combination of the concept of locally computable optimal test functions in Section \secref{optimalTest} with the so-called ``ultra-weak formulation" \cite{DPG1,DPG2,DPG3,DPG4,DPGElas,DBLP:journals/procedia/NiemiCC11}. Unlike the previous two sections in which we studied the general equation \eqnref{variationEq} given by abstract bilinear and linear forms, we now consider a concrete instance of \eqnref{variationEq} resulting from an ultra-weak formulation for an abstract first-order system of PDEs $Au = f$. Additionally, from this section onwards, we will refer to DPG as the pairing of the ultra-weak variational formulation with the concept of locally computable optimal test functions.

We begin by partitioning the domain of interest $\Omega$ into $\Nel$ non-overlapping elements $K_j, j = 1,\hdots,\Nel$ such that $\Oh = \cup_{j=1}^\Nel K_j$ and $\overline{\Omega} = \overline{\Omega}_h$. Here, $h$ is defined as $h= \max_{j\in \LRc{1,\hdots,\Nel}}\text{diam}\LRp{K_j}$.  We denote the mesh ``skeleton" by $\Gh = \cup_{j=1}^\Nel \partial K_j$; the set of all faces/edges $e$, each of which comes with a normal vector ${n}_e$. The internal skeleton is then defined as $\Gamma^0_h = \Gh \setminus \partial \Omega$. If a face/edge $e \in \Gh$ is the intersection of $\partial K_i$ and $\partial K_j$, $i \ne j$, we define the following jumps:
\[
\jump{v} = \text{sgn} \LRp{{n}^-}v^- + \text{sgn} \LRp{{n}^+}v^+, \quad
\jump{\tau \cdot n} = {n}^-\cdot \tau^- + {n}^+\cdot\tau^+,
\]
where
\[
\text{sgn}\LRp{{n}^{\pm}} =
\left\{
\begin{array}{ll}
1 & \text{if } {n}^{\pm} = {n}_e \\
-1 & \text{if } {n}^\pm = -{n}_e
\end{array}
\right..
\]
For $e$ belonging to the domain boundary $\partial \Omega$, we define
\[
\jump{v} = v, \quad
\jump{\tau \cdot n} = {n}_e\cdot \tau.
\]
Note that we allow arbitrariness in assigning ``-'' and ``+'' quantities to the adjacent elements $K_i$ and $K_j$.
%For the rest of the paper, we will use the same notation for both a function and its trace (if it is well-defined) when there is no ambiguity.

The ultra-weak formulation for $Au = f$ on $\Oh$, ignoring boundary
conditions for now, reads
\begin{equation}
\eqnlab{uweak}
b\left(\left(u, \widehat{u}\right),v\right) \coloneqq \langle \widehat{u}, \jump{v}
\rangle_{\Gh} - (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh},
\end{equation}
where we have denoted $\LRa{\cdot,\cdot}_{\Gh}$ as the duality
pairing on $\Gh$, $\LRp{\cdot,\cdot}_{\Oh}$ the $L^2$-inner
product over $\Oh$, and $A_h^*$ the formal adjoint resulting from
element-wise integration by parts.  Occasionally, for simplicity in
writing, we will ignore the subscripts in the duality pairing and
$L^2$-inner product if they are $\Gh$ and $\Oh$. Both the
inner product and formal adjoint are understood to be taken
element-wise. Using the ultra-weak formulation, the regularity
requirement on solution variable $u$ is relaxed, that is, $u$ is now
square integrable for the ultra-weak formulation \eqnref{uweak} to be
meaningful, instead of being (weakly) differentiable.  The trade-off
is that $u$ does not admit a trace on $\Gh$ even though it did
originally. Consequently, we need to introduce an additional new
``trace'' variable $\widehat{u}$ in \eqnref{uweak}, that is defined only on
$\Gh$.

The energy setting is now clear; namely,
\[
u\in L^2\LRp{\Oh} \equiv L^2(\Omega), \quad v\in V=D(A^*_h), \quad
\widehat{u}\in \gamma(D(A)),
\]
where $D(A_h^*)$ denotes the broken graph space corresponding to $A_h^*$,
and $\gamma(D(A))$ the trace space (assumed to exist) of the graph space of
operator $A$. The first discussion of the well-posedness of DPG with the ultra-weak formulation can be found in \cite{analysisDPG}, where the proof is presented for the Poisson and convection-diffusion equations. A more comprehensive discussion of the abstract setting for DPG with the ultra-weak formulation using the graph space, as well as a more general proof of well-posedness, can be consulted in \cite{Bui-ThanhDemkowiczGhattas11b}.

%\subsection{Optimal and quasi-optimal test norms}
\subsection{Canonical energy norm pairings for ultra-weak formulation}

From the discussion in Section~\secref{energyPair} of energy norm and test norm pairings, we know that specifying either a test norm or trial norm is sufficient to define an energy pairing. In this section, we derive and discuss two important energy norm pairings, the first of which begins by specifying the canonical norm in $U$ and inducing a test norm on $V$. The second pairing begins instead by specifying the canonical norm on $V$ under the ultra-weak formulation \eqnref{uweak} and inducing an energy norm on the trial space $U$.

We begin first with the canonical norm in $U$. Since $\uh \in \gamma\LRp{D\LRp{A}}$, the standard norm for $\uh$ is
the so-called minimum energy extension norm defined as
\begin{equation}
\eqnlab{MEnorm}
\|\widehat{u}\| = \inf_{w\in D\LRp{A},
  \left.w\right|_{\Gh}=\widehat{u}} \|w\|_{D\LRp{A}}.
\end{equation}
The canonical norm for the group variable $\LRp{u,\uh}$ is then given by
\[
\|\left(u,\widehat{u}\right)\|_U^2 = \|u\|^2_{\L} + \|\widehat{u}\|^2,
\]
Applying the Cauchy-Schwarz inequality, we arrive at
\[
b\LRp{\LRp{u,\uh},v} \le \nor{\LRp{u,\uh}}_U \nor{v}_{V,U},
\]
where
\[
\nor{v}_{V,U}^2 = \|A_h^*v\|_{\L}^2
+\left(\sup_{\widehat{u} \in \gamma\LRp{D\LRp{A}}} \frac{\LRa{ \widehat{u},
  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2.
\]

On the other hand, since $v \in D\LRp{A^*_h}$, the canonical norm for
$v$ is the broken graph norm: 
\[
\nor{v}_V^2 =  \|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2.
\]
Using the Cauchy-Schwarz inequality again, we obtain
\[
b\LRp{\LRp{u,\uh},v} \le \nor{\LRp{u,\uh}}_{U,V} \nor{v}_{V},
\]
where
\begin{equation}
\eqnlab{inducedQuasi}
\nor{\LRp{u,\uh}}_{U,V}^2 = \nor{u}_{\L}^2
+\sup_{v \in D\LRp{A_h^*}} \frac{\LRa{\widehat{u},
  \jump{v}}_{\Gh}^2}{\|v\|_V^2},
\end{equation}

Using the framework developed in \cite{Bui-ThanhDemkowiczGhattas11a},
one can show that both pairs $\LRp{\nor{\LRp{u,\uh}}_U,
  \nor{v}_{V,U}}$ and $\LRp{\nor{\LRp{u,\uh}}_{U,V}, \nor{v}_{V}}$ are
energy norm pairings in the sense discussed in Section
\secref{energyPair}. That is, the canonical norm $\nor{\LRp{u,\uh}}_U$
in $U$ induces (generates) the norm $\nor{v}_{V,U}$ in $V$, while the
canonical norm $\nor{v}_V$ in $V$ induces (generates) the energy norm
$\nor{\LRp{u,\uh}}_{U,V}$ in $U$. In the DPG literature \cite{DPG4}, $\nor{v}_{V,U}$ is known as the {\em optimal test norm},
while $\nor{v}_{V}$ is known as the {\em quasi-optimal test norm}.

\begin{figure}[!h]
\centering
\begin{tabular}{l c c}
Trial norm & & Test norm \\
\hline
$\boxed{\|u\|^2_{\L} + \|\widehat{u}\|^2}$ & $\Longrightarrow$  & $\|A_h^*v\|_{\L}^2
+\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},
  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2$ \\
%\hline
%Quasi-optimal trial norm & & Canonical test norm \\
%\hline
$\nor{u}_{\L}^2+\sup_{v } \left(\frac{\LRa{\widehat{u},
  \jump{v}}_{\Gh}}{\|v\|_V}\right)^2$ &  $\Longleftarrow$ & $\boxed{\|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2}$
\end{tabular}
\caption{A summary of the derivation of test/trial norm pairings; we begin with the boxed norm on either the trial or test space, and induce the norm on the other space through duality. The optimal \textit{test} norm is naturally derived by beginning with the canonical norm on the trial space, while the quasi-optimal \textit{trial} norm is derived from beginning with the canonical norm on the test space.}
\end{figure}

The canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ provides a good
balance between the standard norms on the field $u$ and the flux
$\uh$ \cite{DPG4}. As a result, if the induced norm $\nor{v}_{V,U}$ (namely, the
optimal test norm) is used to compute  optimal test functions in
\eqnref{optvVar}, the finite element error in the canonical norm is the
best in the sense of \eqnref{optimalError}.

Unfortunately, the optimal test norm is non-localizable due to the presence of the jump term $\jump{v}$.\footnote{A localizable norm $\nor{v}_{V(\Oh)}$ can be written in the form
$$\nor{v}_{V(\Oh)} = \sum_{K\in\Oh} \nor{v}_{V(K)},$$ where $\nor{v}_{V(K)}$ is a norm over the element $K$.} Since the jump terms couple elements together, the evaluation of the jump terms requires contributions from all the elements in the mesh. Consequently, solving for an optimal test function
amounts to inverting the Riesz map %, defined on the left sideof \eqnref{optvVar}, 
over the entire mesh $\Oh$, making the optimal test norm impractical.

On the other hand, the quasi-optimal test norm $\nor{v}_V$, namely the canonical norm in $V$, \textit{is} localizable, and hence practical. However, it's worth noting the difference between the induced energy norm $\nor{\LRp{u,\uh}}_{U,V}$ and the canonical norm in $U$; under the induced norm $\nor{\LRp{u,\uh}}_{U,V}$ there is no natural interpretation for the norm in which the error in the flux variable $\uh$ is measured.

Using a variant of the quasi-optimal test norm, numerical results show that the DPG method appears to provide a ``pollution-free" method without phase error for the Helmholtz equation \cite{DPG4}, and analysis of the pollution-free nature of DPG is currently under investigation. Similar results have also been obtained in the context of elasticity \cite{DPGElas} and the linear Stokes equations \cite{Camellia}. On the theoretical side, the quasi-optimal test norm has been shown to yield a well-posed DPG methodology for the Poisson and convection-diffusion equations \cite{analysisDPG}. More recently, this theory has been generalized to show the well-posedness of DPG for the large class of PDEs of Friedrichs' type \cite{Bui-ThanhDemkowiczGhattas11b}.

\section{Model problem and robustness}
\seclab{sec:modelSec}
The remainder of the paper focuses on a convection-diffusion model problem using the abstract theory that we
have discussed so far. In particular, we shall use the DPG method based on the ultra-weak formulation with optimal test functions to solve the model problem and analyze its behavior with respect to $\epsilon$. 
Our goal is to show the robustness of the method with respect to $\epsilon$, and demonstrate its usefulness as  a numerical approach to solving singular-perturbed problems.

We consider the following model convection-diffusion problem on a domain
$\Omega \subset \mathbb{R}^d$ with boundary $\pO \equiv \Gamma$
\begin{equation}
\div (\beta u) - \epsilon\Delta u = f  \in \L \label{primal},
\end{equation}
which can be cast into the first order form on the group variable
$\LRp{u,\sigma}$ as
\begin{equation}
\eqnlab{CDstrong}
A \LRp{u,\sigma} \coloneqq \LRs {
\begin{array}{c}
\div (\beta u - \sigma) \\ \frac{1}{\epsilon}\sigma - \grad u
\end{array}} = \LRs{
\begin{array}{c}
f \\ 0
\end{array}
}.
\end{equation}
Using the abstract ultra-weak formulation developed in Section
\secref{abstractUweak} for the first order system of PDEs \eqnref{CDstrong} we
obtain
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh} - \LRa{
\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n,
  \jump{v} }_{\Gh},
\end{align*}
where $\LRp{v, \tau}$ is the group test function. It should be pointed
out that the divergence and gradient operators are understood to act
element-wise on test functions $\LRp{v, \tau}$ in the broken graph
space $ D\LRp{A_h^*} \coloneqq  H^1(\Oh) \times H({\rm div}, \Oh)$, but
globally as usual on conforming test functions, i.e.\ $ \LRp{v, \tau}
\in  H^1(\Omega) \times H({\rm div}, \Omega)$. It follows that the
canonical test norm can be written as
\[
\|\left(v, \tau\right)\|_V^2 = \|\left(v, \tau\right)\|_{H^1(\Oh) \times H({\rm div},\Oh)}^2
= \sum_{K\in \Oh} \|\left(v, \tau\right)\|_{H^1(K) \times H({\rm
    div},K)}^2,
\]
where
\[
\|\left(v, \tau \right)\|_{H^1(K) \times H({\rm div},K)}^2 =
\|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2 + \|\tau\|_{L^2(K)}^2 +
\|\div \tau\|_{L^2(K)}^2.
\]

In order to define the proper norm on the trial space, boundary
conditions need to be specified. We begin by splitting the boundary
$\Gamma$ as follows
\begin{align*}
\Gamma_{-} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\}, \quad {\rm
  (inflow)}\\ \Gamma_{+} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\},
\quad {\rm (outflow)}\\ \Gamma_{0} &\coloneqq \{x\in \Gamma;
\beta_n(x) = 0\},
\end{align*}
where $\beta_n \coloneqq \beta \cdot n$.
Previous work in \cite{DPGrobustness} adopted Dirichlet boundary
conditions everywhere on $\Gamma$.  
%and we could obtain the robustness only with special weighted norms in which the weight varied spatially. 
In this paper, we employ the inflow
condition of Hesthaven \etal \cite{Hesthaven96astable}, where we set
\[
\beta_n u - \sigma_n  = u_0, \quad \text{on } \Gm,
\]
instead of $\beta_n u = u_0$. The former resembles the latter
as $\epsilon$ approaches zero\footnote{For our model problem, as for many problems of interest in computational fluid dynamics, we expect $\grad u$ to be small near the inflow, and that the solutions to \eqref{primal} using $\beta_n u - \sigma_n = f_n = u_0$ on $\Gamma_-$ will converge to that using $u=u_0$ on $\Gamma_-$  for sufficiently small $\epsilon$.}; however, the latter induces a more ``well-behaved" adjoint problem than the former, which, as we will discuss, affects the performance of DPG.

On the outflow boundary, we apply standard homogeneous Dirichlet boundary conditions
\[
u = 0, \quad \text{on } \Gp.
\]
This paper is intended to act as an extension of work presented by Heuer and Demkowicz in \cite{DPGrobustness}. The primary focus of the paper is to analyze the DPG method and extend previous results under this new choice of inflow boundary conditions. The difference in the performance of DPG under both new and old boundary conditions is connected to the difference in the adjoint problems induced under each boundary condition. The secondary contribution of this paper will be to analyze the performance of DPG under a new mesh-dependent test norm.

\subsection{Norms on $U$}

With the above boundary conditions at hand, the ultra-weak formulation
\eqnref{uweak} can be fitted in the abstract form \eqnref{variationEq}
as
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right), \left( v,
\tau\right)\right) &= \left(u,\div \tau - \beta \cdot \grad
v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad
v\right)_{\Oh} \\
&- \LRa{ \jump{\tau\cdot n}, \widehat{u} }_{\Gh
  \setminus \Gp} + \LRa{ \widehat{f}_n, \jump{v} }_{\Gamma_h \setminus
  \Gm} =  \left(f, v\right) -
\LRa{ u_0, v }_{\Gamma_-} = l\left(\left(v, \tau\right)\right),
\end{align*}
which, after using the setting in Section \secref{abstractUweak},
suggests the following trial space (see \cite{analysisDPG, Bui-ThanhDemkowiczGhattas11b} for details):
\begin{align*}
u, \sigma \in \L, \quad \text{and } \LRp{\uh,\fnh} \in
\gamma\LRp{D\LRp{A}} \subset \gamma\LRp{  H^1(\Omega) \times
H({\rm div}, \Omega)} = H^{\frac{1}{2}}\left(\Gh\right) \times H^{-\frac{1}{2}}\left(\Gh\right).
\end{align*}
The space for $u$ and $\sigma$ are simply scalar and vector $L^2$ spaces over $\Omega$, while the space for $\left(\uh,\fnh\right)$ is the trace space of the graph space of the operator $A$ subject to the boundary conditions.

The minimum energy extension norm \eqnref{MEnorm} now reads
\begin{align*}
\|\widehat{u}\| &= \inf_{w\in H^1(\Omega),
  \left.w\right|_{\Gamma_+}=0, \left.w\right |_{\Gh\setminus
    \Gamma_+ } = \widehat{u}} \|w\|_{H^1(\Omega)}, \\ \|\widehat{f}_n\|
&= \inf_{q\in H({\rm div},\Omega), \left.q\cdot n\right|_{\Gamma_-}=
  0, \left. q\cdot n \right |_{\Gh\setminus
    \Gamma_-} = \widehat{f}_n}
\|q\|_{H({\rm div},\Omega)}.
\end{align*}
As a result, the canonical norm on $U$ is given by
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U^2 = 
\|u\|_{L^2(\Oh)}^2 + \|\sigma\|_{L^2(\Oh)}^2 +
\|\widehat{u}\|^2 + \|\widehat{f}_n\|^2.
\]

\subsection{Norms on $V$}

%We will denote $\|\cdot \| = \|\cdot\|_{L^2}$ for all functions defined on $\Oh$. 
As $\tau \in H({\rm div},\Oh)$ and $v \in H^1(\Oh)$, we will
construct norms on $v$ and $\tau$ 
which are equivalent to the canonical $H^1(K) \times H({\rm div},K)$
norm over a single element
\[
\|\left(v,\tau\right)\|_{H^1(K) \times H({\rm div},K)}^2 =
\|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2 + \|\tau\|_{L^2(K)}^2 +
\|\div \tau\|_{L^2(K)}^2.
\]
The squared norm over the entire triangulation $\Oh$ is defined to be the squared sum of contributions from each element
\[
\|\left(v,\tau\right)\|_{H^1(\Oh) \times H({\rm div},\Oh)}^2
= \sum_{K\in \Oh} \|\left(v,\tau\right)\|_{H^1(K) \times H({\rm
    div},K)}^2.
\]
The exact norms that we will specify on $V$ will be determined later.

The norms on the skeleton $\Gh$ for $v$ and $\tau$ are defined by duality from the bilinear form
\begin{align*}
\left\|\jump{\tau\cdot n}\right\| &= \left\|\jump{\tau\cdot n}\right\|_{\Gh \setminus \Gamma_+} \coloneqq \sup_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+} = 0} \frac{\langle \jump{\tau \cdot n}, w\rangle}{\|w\|_{H^1(\Omega)}},\\
\left\|\jump{v}\right\|&=\left\|\jump{v}\right\|_{\Gh^0 \cup \Gamma_+} \coloneqq \sup_{\eta\in H({\rm div},\Omega), \left.\eta\cdot n\right|_{\Gamma_- \cup \Gamma_0} = 0} \frac{\langle \jump{v}, \eta\cdot n\rangle}{\|\eta\|_{H({\rm div},\Omega)}}.
\end{align*}

\subsection{Approximability of the quasi-optimal test norm}
%\textcolor{blue}{need to define what we mean by robustness. perharps the best place is in the introduction}
An obvious choice for the test norm would be the quasi-optimal norm; it is the canonical test norm, and DPG has been shown to be well-posed and robust under such an optimal test norm for a large class of problems \cite{DPGrobustness,Bui-ThanhDemkowiczGhattas11b, stokesDPG}. However, computations with the quasi-optimal test norm for convection-diffusion problems turn out to be quite problematic for small diffusion and coarse meshes.

For convection-diffusion, the quasi-optimal test norm is 
\[
\|\left(v,\tau\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v
\|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 +
\|v\|_{L^2}^2 + \|\tau\|_{L^2}^2.
\]
%We note that the optimal test norm will automatically guarantee the
%robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.
Use of this norm for the convection-diffusion problem is difficult --- since the problem \eqnref{optvVar} for optimal test functions is local, we can transform the problem over a single element $K$ to the reference element $\widehat{K}$ and show that it is equivalent to a reaction-diffusion system, with diffusion parameter $\frac{\epsilon}{|K|}$, where $|K|$ is the element measure \cite{DBLP:journals/procedia/NiemiCC11}. We refer to the inverse of this parameter $\frac{|K|}{\epsilon}$ as the element Peclet number $\rm Pe$. For a coarse mesh and small diffusion parameter $\epsilon$, we will have a large element Peclet number, and optimal test functions under the quasi-optimal test norm will develop strong boundary layers of width $\rm Pe$, as seen in Figure~\ref{fig:optTestBoundary}.

In the application of DPG in \cite{DPG1,DPG2,DPG3,DPG4}, the approximation of optimal test functions is done using polynomial enrichment. We search for the solution to \eqnref{optvVar} in the enriched test space $\tilde{V} \approx \prod_{K} P^{p+\Delta p}(K)$, where $p$ is the polynomial order of the trial space on a given element $K$.\footnote{$V$ is only \emph{approximately} equal to the space $\prod_{K} P^{p+\Delta p}(K)$. In practice, $V$ is constructed using locally $H^1$-conforming and Raviart-Thomas elements of appropriate order.}  In other words, optimal test functions are approximated element-by-element using polynomials whose order is $\Delta p$ more than the local order of approximation.  Under this scheme, the error in approximation of test functions is tied to the effectiveness of the $p$-method.  Unfortunately, for problems with boundary layers --- including the approximation of test functions under the quasi-optimal test norm --- the $p$-method performs very poorly. As a result of this poor approximation, the numerical solutions of the convection-dominated diffusion equation under DPG using the quasi-optimal test norm tend to be of poor quality, and do not exhibit all the proven properties of DPG (for example, the energy error may increase after mesh refinement, even though, by virtue of DPG delivering a best approximation, the energy error for a coarse mesh must be greater than or equal to the energy error for a finer mesh).  We conclude that the error in approximation of optimal test functions using simple polynomial enrichment pollutes and ruins the performance of DPG under the quasi-optimal test norm.

\begin{figure}[!h]
\centering
\includegraphics[scale=.25]{figs/opt.png}
\caption{$v$ and $\tau$ components of the 1D optimal test functions corresponding to the flux $\widehat{f}_n$ on the right-hand side of a unit element for $\epsilon = 0.01$. The solution has been obtained using automatic $hp$-adaptivity driven by the test norm with the error tolerance set at 1\%.}
\label{fig:optTestBoundary}
\end{figure}

The difficulty in using the quasi-optimal test norm for convection-diffusion is perplexing at first, considering that the quasi-optimal norm has yielded excellent results for the Helmholtz equation and other wave propagation problems.  The difference between the two problems lies in the fact that, for wave propagation problems, the mesh size tends to be on the order of the wavenumber $k$ --- the singular perturbation parameter. Transforming the variational problem using the quasi-optimal test norm for wave propagation yields smooth optimal test functions that are approximated much more accurately using only polynomials over the reference element. Typically, the wavenumbers $k$ of physical interest are $O(100)$ with respect to a unit domain. The corresponding finite element problems will typically be solved on meshes containing approximately $O\!\left(k^d\right)$ elements in $\mathbb{R}^d$, well within the range of a computationally tractable simulation. However, for convection diffusion problems, the relevant range of $\epsilon$ for physical problems can be as small as $1e-7$. Solving on under-resolved meshes is thus unavoidable, and the approximability of optimal test functions must be addressed in order to take advantage of the properties of DPG.

Resolving such boundary layers present in test functions under the quasi-optimal test norm has been investigated numerically using specially designed (Shishkin) subgrid meshes by Niemi, Collier, and Calo in
\cite{DBLP:journals/procedia/NiemiCC11}.  However, even with Shishkin meshes, the approximation of optimal test functions under the quasi-optimal norm is far more expensive and complex to implement than approximation of test functions using a simple $p$-enriched space for $V$. We therefore aim instead to design a test norm that does not induce boundary layers, but still delivers good approximation results over a range of $\epsilon$.

\section{Analysis of a DPG test norm}
\seclab{sec:testNormSec}
We are interested in computing DPG optimal test functions for the convection-diffusion equation with very small values of $\epsilon$; due to the difficulty of approximating optimal test functions, we conclude that the use of the quasi-optimal test norm is infeasible towards this goal.

However, if we naively choose a test norm that does not generate boundary layers, the performance of DPG may be adversely affected. For example, if $\|\left(v,\tau\right)\|_V^2 = \|v\|_{H^1(\Omega_h)}^2 + \|\tau\|^2_{H({\rm div},\Omega_h)}$, the $H^1(\Omega_h)\times H({\rm div},\Omega_h)$ norm, then the corresponding test functions will be smooth and free of boundary layers; however, the performance of DPG will provide approximations which worsen in quality as $\epsilon$ becomes very small \cite{DPG3,DPGrobustness}.

Our goal is to construct a test norm that compromises between performance of DPG and approximability of test functions.  This test norm should not produce boundary layers in the optimal test functions, but still induce an energy norm that yields good approximation properties for small $\epsilon$. We note that, even under the quasi-optimal norm, the norms on the flux and trace variables will likely depend on $\epsilon$. Thus, we aim to construct a test norm for which the DPG method will be robust in $\epsilon$ with respect to the \emph{field variables}.

For now, we discuss the steps necessary to analyze the performance of DPG with respect to a non-canonical test norm. We require a priori that the test norm has separable $\tau$ and $v$ components --- in other words, that there are no terms in the test norm that couple $\tau$ and $v$ together. Problem \eqnref{optvVar} then decouples, such that the components of the vector-valued test function $\left(v,\tau\right)$ can be solved for independently of each other. The decoupled variational problems are no longer systems but scalar equations in $\tau$ and $v$, for which it is easier to conclude whether or not there are boundary layers in the solutions (the avoidance of boundary layers in the test norm will be discussed in more detail in Section~\ref{sec:num_exp}, which describes our numerical experiments). \textbf{This will ensure that the resulting DPG method does not suffer from approximation errors in the optimal test functions}.

We begin with the following test norm:
\[
\left\|\left(v,\tau\right)\right\|^2_V \coloneqq \|v\|_{L^2}^2 + \epsilon\|\grad v\|_{L^2}^2 + \|\beta \cdot \grad v\|_{L^2}^2  + \frac{1}{\epsilon}\|\tau\|_{L^2}^2 + \|\div \tau\|_{L^2}^2.
\]
The use of this norm is problematic for practical computations; we will discuss the reasons why and present a modification of it in Section~\secref{sec:meshDep}.

We can see how this norm will differ from the canonical $H^1(\Omega_h)\times H({\rm div},\Omega_h)$ norm: the clearest difference is the fact that the gradient in the streamline direction is $O(1)$, while the full gradient is $O(\sqrt{\epsilon})$, so that, in our test norm, the streamline gradient of $v$ will be emphasized over the full gradient of $v$ for small $\epsilon$.

The choice of this test norm is implied by the mathematics of the adjoint problem. Roughly speaking, necessary conditions for the performance of DPG to not degenerate as $\epsilon \rightarrow 0$ are derived through analysis of specific test functions. For example, if $u$ is the first $L^2$ component of the solution to the variational problem defined in Section~\secref{sec:modelSec}, by choosing $(v,\tau) \in H^1(\Omega) \times H({\rm div},\Omega)$ such that 
\begin{align*}
\div \tau - \beta \cdot \grad v &= u \\
\frac{1}{\epsilon} \tau - \grad v &= 0,
\end{align*}
we have
\[
 \nor{u}_{L^2}^2 = b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(v,\tau\right)\right) \leq \nor{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)}_{U,V} \nor{\left(v,\tau\right)}_V,
\]
and we recover the $L^2$ norm of $u$ from the bilinear form.

Let $\|a\| \lesssim \|b\|$ denote an $\epsilon$-independent bound; specifically, that $\|a\| \leq C\|b\|$ for a constant $C$ independent of $\epsilon$. Consequently, if for any $u\in L^2(\Oh)$, $\nor{\left(v,\tau\right)}_V\lesssim \nor{u}_{L^2}$, then dividing through by $\nor{u}_{L^2}$ gives the bound
\[
 \nor{u}_{L^2} \lesssim \nor{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)}_E.
\]
In other words, there is the guarantee that the $L^2$ error in $u$ is at least robustly bounded from above by the energy error. Then, if the energy error (which DPG minimizes) approaches zero, the $L^2$ error in $u$ will as well. The same exercise can be repeated for the stress $\sigma$, as well as the flux variables $\widehat{u}$, $\widehat{f}_n$.

This methodology gives constraints on the quantities found in the test norm; any quantity present in $\nor{\left(v,\tau\right)}_V$ must be shown to be bounded from above independently of $\epsilon$ by the load of the adjoint problem. However, showing this simply amounts to showing \textit{standard energy estimates} for $H^1$ and $H({\rm div})$-conforming finite elements. A more detailed discussion on the reasoning behind the construction of test norms can be found in \cite{DPGrobustness}.

The second step will be to \textbf{show the equivalence of the energy norm to explicit norms on $U$}. Since we do not generally have a closed form expression for the DPG energy norm, we seek to understand the behavior of DPG by finding a norm on $U$ to which the DPG energy norm is equivalent. Since $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U$ is a group variable from a tensor product space, we construct norms on $U$ through the combination of norms on $u$, $\sigma$, $\widehat{u}$, and $\widehat{f}_n$. Specifically, we use the norm on $U$ 
\begin{equation}
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U}^2 \coloneqq \|u\|^2 + \|\sigma\|^2 + \left\|\widehat{u}\right\|^2 + \left\|\widehat{f}_n\right\|^2.
\end{equation}
For equivalence between norms, two constants are specified. However, since this norm on $U$ is a norm on four separate variables, we can specify not just two but eight equivalence constants.\footnote{Sharper estimates are attainable if these constants are allowed to vary over the mesh $\Oh$. See Section~\ref{sec:main_bounds} for a discussion.} In order to simplify analysis, we phrase this equivalence statement in an alternative form.

Let $\nor{\cdot}_E \coloneqq \nor{\cdot}_{U,V}$, the energy norm induced by the test norm described above. We seek the bound of $\nor{\cdot}_E$ from above and below:
\[
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2},
\]
where both $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ are defined as scaled combinations of the norms on $u, \sigma, \widehat{u}$, and $\widehat{f}_n$
\begin{equation}
\eqnlab{uNorms}
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,i}^2 \coloneqq \left(C_u^i\|u\|\right)^2 + \left(C_\sigma^i\|\sigma\|\right)^2 + \left(C_{\widehat{u}}^i\|\widehat{u}\|\right)^2 + \left(C_{\widehat{f}_n}^i\|\widehat{f}_n\|\right)^2,\quad i = 1,2
\end{equation}
Our goal is to explicitly derive the equivalence constants 
%$C^1_u,\ldots, C^1_{\widehat{f}_n}$ and $C^2_u,\ldots, C^2_{\widehat{f}_n}$ 
that define the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ respectively, taking into account any dependency on $\epsilon$. To do so, we need a relation between trial norms on $U$ and test norms on $V$.

Recall from Section~\secref{energyPair} that every test norm induces a corresponding trial norm, and vice versa. Let $\|\cdot\|_{U,1} \simeq \|\cdot\|_{U,2}$ mean that the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ are equivalent, with equivalence constants independent of $\epsilon$. By equivalence of finite dimensional norms and the discussion in Section~\secref{energyPair} on the duality between test norms/energy norms, the norms \eqnref{uNorms} on $U$ induce the equivalent test norms on $\left(v,\tau\right) \in H^1(\Oh)\times H({\rm div},\Oh)$
\begin{align*}
\left\|\left(v,\tau\right)\right\|_{V,{U,i}} &\simeq \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(v,\tau\right)\right)}{C_u^i\|u\| + C_\sigma^i\|\sigma\| + C_{\widehat{u}}^i\|\widehat{u}\|+ C_{\widehat{f}_n}^i\|\widehat{f}_n\|}\\
&= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \jump{\tau_n}, \widehat{u} \rangle_{\Gamma_-\cup \Gh^0} + \langle \widehat{f}_n, \jump{v} \rangle_{\Gamma_+ \cup \Gh^0}}{C_u^i\|u\| + C_\sigma^i\|\sigma\| + C_{\widehat{u}}^i\|\widehat{u}\|+ C_{\widehat{f}_n}^i\|\widehat{f}_n\|}\\
& \simeq \frac{1}{C_u^i}\|g\| + \frac{1}{C_\sigma^i}\|f\| + \frac{1}{C_{\widehat{u}}^i}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle \jump{\tau\cdot n}, \widehat{u}\rangle}{\|\widehat{u}\|} +\frac{1}{C_{\widehat{f}_n}^i}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, \jump{v}\rangle}{\|\widehat{f}_n\|},
\end{align*}
where $f$ and $g$ are defined element-wise over $\Oh$ as 
\begin{align*}
g &\coloneqq \div \tau - \beta \cdot \grad v\\
f &\coloneqq \epsilon^{-1}\tau + \grad v.
\end{align*}
By definition of the norms on the quantities defined on the skeleton $\Gh$, this gives the characterization of the induced test norm 
\[
\|\left(v,\tau\right)\|_{V,{U,i}} \simeq \frac{1}{C_u^i}\|g\| + \frac{1}{C_\sigma^i}\|f\| + \frac{1}{C_{\widehat{u}}^i}\|\jump{\tau\cdot n}\| + \frac{1}{C_{\widehat{f}_n}^i}\|\jump{v}\|, \quad i = 1,2.
\]
We can now use this relation to compare different norms on $U$ by comparing their induced norms on $V$ (recall that showing a robust inequality between two norms on $U$ is equivalent to showing the robust \textit{reverse} inequality in the induced norms on $V$). Namely, we can show the bound of $\nor{\cdot}_{U,1} \lesssim \nor{\cdot}_E$ by showing the bound $\nor{\left(v,\tau\right)}_{V,U,1} \gtrsim \nor{\left(v,\tau\right)}_{V}$, and likewise for $\nor{\cdot}_E \lesssim \nor{\cdot}_{U,2}$.

Since the techniques used to show such bounds are more involved, we break the procedure up into two steps:
\begin{enumerate}
\item{}Decompose test functions $(v,\tau)$ into three separate, more easily analyzable components (Section~\ref{sec:strategy2}).
\item{}Derive adjoint estimates (Section~\ref{sec:strategy3}).
\end{enumerate}

\subsection{Decomposition into analyzable components}
\label{sec:strategy2}

Having reduced the problem of comparing norms on $U$ to the comparison of norms on $V$, we break the analysis of $\left(v,\tau\right) \in V$ into the analysis of three subproblems.  Define the decomposition
\[
\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right),
\]
where $\left(v_1,\tau_1\right)$ satisfies 
\begin{align*}
\epsilon^{-1}\tau_1 + \grad v_1 &= 0 ,\\
\div \tau_1 - \beta\cdot \grad v_1 &=  \div \tau - \beta\cdot \grad v = g, 
\end{align*} 
and $\left(v_2,\tau_2\right)$ satisfies
\begin{align*}
\epsilon^{-1}\tau_2 + \grad v_2 &= \epsilon^{-1}\tau + \grad v = f, \\
\div \tau_2 - \beta\cdot \grad v_2 &= 0.
\end{align*}
Both $(v_1,\tau_1), (v_2,\tau_2) \in H({\rm div}; \Omega)\times H^1(\Omega)$ are understood to satisfy these relations in a conforming sense over the domain $\Omega$; however, the divergence of $\tau$ and gradient of $v$ on the right hand side are still understood to be taken in an element-wise fashion.

We will additionally require both $\left(v_1,\tau_1\right), \left(v_2,\tau_2\right)$ to satisfy the adjoint homogeneous boundary conditions
\begin{align}
\tau_i\cdot n &= 0, \quad \text{on }\Gamma_- \label{bc_1}\\
v_i &= 0, \quad \text{on } \Gamma_+ \label{bc_2}
\end{align}
for $i = 1, 2$. The selection of $H({\rm div}, \Omega)\times H^1(\Omega)$ conforming test functions satisfying the specific boundary conditions above removes the contribution of the jump terms over the skeleton $\Gh$ in the bilinear form, allowing us to analyze field terms in the induced test norms separately from  the boundary/jump terms.

Finally, by construction, $\left(v_0,\tau_0\right) \in H^1(\Oh) \times H({\rm div},\Oh)$ must satisfy 
\begin{align*}
\epsilon^{-1}\tau_0 + \grad v_0 &= 0\\
\div \tau_0 - \beta\cdot \grad v_0 &= 0
\end{align*}
with jumps
\begin{align*}
\jump{v_0} &= \jump{v}, \quad \text{on }\Gh^0\\
\jump{\tau_0 \cdot n} &= \jump{\tau \cdot n}, \quad \text{on }\Gh^0.
\end{align*}
and boundary conditions
\begin{align*}
v_0 &= v, \quad \text{on } \Gamma_+ \\
\tau_0 \cdot n &= \tau \cdot n, \quad \text{on } \Gamma_-\cup \Gamma_0. 
\end{align*}
Notice that the evaluation the bilinear form $b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(v,\tau\right)\right)$ with each specific test functions returns only one part of the bilinear form. Furthermore, by choosing the proper loads $g = u$ and $f=\sigma$, we can recover from the bilinear form the norms of $u$ and $\sigma$ (as described in Section~\secref{sec:testNormSec}), as well as the norms on $\widehat{u}$, and $\widehat{f}_n$.\footnote{To recover the norms on $\widehat{u}$, and $\widehat{f}_n$, the loads $f$, and $g$ must be zero, and the jumps of the test function $(v,\tau)$ must be chosen specifically.}

We have now decomposed an arbitrary test function $\left(\tau,v\right)$ into a discontinuous contribution and two continuous contributions.  Recall that our goal is to show the robust bound from above and below of the DPG energy norm by $\|\cdot \|_{U,1}$ and $\|\cdot \|_{U,2}$:
\[
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}.
\]

Under the duality of trial and test norms and the decomposition of test functions $\left(\tau,v\right) \in V$ into $\left(\tau_0,v_0\right), \left(\tau_1,v_1\right)$, and $\left(\tau_2,v_2\right)$, the above bound is equivalent to bounding each component 
\begin{align*}
\|\left(v,\tau\right)\|_{V,U,1} &\gtrsim \sum_{i=0}^2\|\left(v_{i},\tau_{i}\right)\|_V \gtrsim \|\left(v,\tau\right)\|_{V,U,2}.
%\|\left(v,\tau\right)\|_{V,1} &\lesssim \|\left(v_{1},\tau_{1}\right)\|_V \lesssim \|\left(v,\tau\right)\|_{V,2}\\
%\|\left(v,\tau\right)\|_{V,1} &\lesssim \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|\left(v,\tau\right)\|_{V,2}
\end{align*}
Bounding $\|\left(v_0,\tau_0\right)\|$ requires the use of techniques first developed in \cite{analysisDPG} and adapted to convection-diffusion in \cite{analysisDPG} and \cite{DPGrobustness}. However, since $\left(\tau,v\right) \in H({\rm div}, \Omega)\times H^1(\Omega)$, the bound from above of test functions $\|\left(v_{1},\tau_{1}\right)\|_V$ and $\|\left(v_{2},\tau_{2}\right)\|_V$ is reduced to proving classical error estimates for the adjoint equations
\begin{align*}
\epsilon^{-1}\tau_1 + \grad {v_1} &= 0 \\
\div {\tau_1} - \beta\cdot \grad {v_1} &=  g, \\
\left.\tau_1\cdot n\right|_{\Gamma_-} &= 0, \\
\left.v_1\right|_{\Gamma_+} &= 0.
\end{align*} 
and 
\begin{align*}
\epsilon^{-1}\tau_2 + \grad {v_2} &= f \\
\div {\tau_2} - \beta\cdot \grad {v_2} &= 0, \\
\left.\tau_2\cdot n\right|_{\Gamma_-} &= 0, \\
\left.v_2\right|_{\Gamma_+} &= 0.
\end{align*} 
More generally, we can analyze the adjoint equations
\begin{align}
\epsilon^{-1}\tau + \grad {v} &= f \label{adjoint1}\\
\div {\tau} - \beta\cdot \grad {v} &= g, \label{adjoint2}
\end{align}
for arbitrary data $f, g\in L^2({\Omega})$ and boundary conditions $\jump{\tau\cdot n}_{\Gamma_-} = 0$ and $\jump{v}_{\Gamma_+} = 0$.  In other words, we want to analyze the stability properties of the adjoint equations by deriving bounds of the form $\|\left(v_1,\tau_1\right)\|_V\lesssim \|g\|_{L^2}$ and $\|\left(v_2,\tau_2\right)\|_V \lesssim \|f\|_{L^2}$.

%An alternate interpretation of the above decomposition is that each component $(v_i,\tau_i)$ of the decomposition corresponds to a term in the bilinear form. For example, . If we evaluating our bilinear form with $(v,\tau) = (v_1,\tau_1)$ delivers
%\[
%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
%\left( v_1, \tau_1 \right)\right) = (u,g)_{L^2} 
%\]
%By choosing $g = u$,

\subsection{Adjoint estimates}
\label{sec:strategy3}

The final step to estimating the induced norm on $U$ by a selected localizable test norm on $V$ is to derive adjoint stability estimates on $\tau$ and $v$ in terms of localizable normed quantities.  We will construct complete test norms on $V$ through combinations of these normed quantities.%, where each normed quantity on $\tau$ or $v$ will correspond roughly to $\|u\|_{L^2}$, $\|\sigma\|_{L^2}$, $\|\widehat{u}\|$, or $\|\widehat{f}_n\|$.

We introduce first the bounds derived; the proofs will be given later. For this analysis, it will be necessary to assume certain technical conditions on $\beta$.  For each proof, we require $\beta \in C^2(\bar{\Omega})$ and $\beta, \div \beta = O(1)$.  Additionally, we will assume that some or all of the following assumptions hold:
\begin{align}
&\curl \beta = 0, \quad 0<C \leq \left | \beta\right |^2 + \frac{1}{2}\div \beta, \quad C = O(1) \label{a_req},\\
&\grad \beta + \grad \beta ^T - \div \beta I = O(1) \label{b_req},\\
&\div \beta = 0 \label{c_req}.
\end{align}
Under proper assumptions on $\beta$, we have the robust bounds, which are proved in the Appendix. 
\begin{itemize}
\item \textbf{Lemma \ref{lemma_stream}}: \textit{For $\beta$ satisfying \eqref{a_req} and \eqref{b_req}, %$f=0$ 
and $v_1 \in H^1(\Omega)$, satisfying equations \eqref{adjoint1} and \eqref{adjoint2} with $f=0$, and with boundary conditions \eqref{bc_1} and \eqref{bc_2}},
\begin{align*}
\|\beta \cdot \grad v_1 \| &\lesssim \| g\|.
\end{align*}
Similarly, from $\div \tau_1 - \beta\cdot \grad v_1 = g$, we get $\|\div \tau_1\| \lesssim \|g\|$ as well.  
\item \textbf{Lemma \ref{lemma_grad}}: \textit{For $\beta$ satisfying \eqref{a_req}, and $v \in H^1(\Omega)$ satisfying equations \eqref{adjoint1} and \eqref{adjoint2} and boundary conditions \eqref{bc_1} and \eqref{bc_2}, and for sufficiently small $\epsilon$},
\[
\epsilon \|\grad v\|^2 + \|v\|^2 \lesssim \|g\|^2 + \epsilon \|f\|^2.
\]
We can characterize both $v_1$ and $v_2$ in the above decompositions using this theorem by setting either $f=0$ or $g=0$. 
%\begin{align*}
%\epsilon \|\grad v_1\|^2 + \|v_1\|^2 &\lesssim \|g\|^2\\
%\epsilon \|\grad v_2\|^2 + \|v_2\|^2 &\lesssim \epsilon \| f\|^2.
%\end{align*}
%By the triangle inequality, this implies for any $w$ of the form $w=v_1+v_2$
%\begin{align*}
%\epsilon \|\grad w\|^2 + \|w\|^2 &\lesssim \|g\|^2 + \epsilon \| f\|^2
%\end{align*}
\item \textbf{Lemma \ref{lemma_boundary}}: \textit{For $\beta$ satisfying \eqref{a_req}, \eqref{c_req}, and solutions $v_0 \in H^1(\Oh)$ and $\tau_0 \in H({\rm div},\Oh)$ of equations \eqref{adjoint1} and \eqref{adjoint2} with $f=g=0$,} 
\begin{align*}
\|\grad v_0\| = \frac{1}{\epsilon}\|\tau_0\| &\lesssim \frac{1}{\epsilon} \| \jump{\tau_0\cdot n}\|_{\Gh \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| \jump{v_0}\|_{\Gh^0 \cup \Gamma_+}.
\end{align*}
\end{itemize}
We are interested in showing the equivalence of the DPG energy norm with norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$, respectively.  We will show this by bounding $\|\cdot \|_V$ from below by $\|\cdot\|_{V,U,1}$ and from above by $\|\cdot\|_{V,U,2}$ (the induced test norms for $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$, respectively).

%We will use Lemmas \ref{lemma_stream}, \ref{lemma_grad}, and \ref{lemma_boundary} to prove such bounds on our yet-unspecified test norm $\|(\tau,v)\|_V$.

%Together, these estimates will be sufficient to construct a complete norm on $V$ and demonstrate bounds on induced test norms for different scalings of norms on $U$.  
%\tanbui{}{again, using the same notation
%  $(v, \tau)$ for all three problems is not a good idea. Why don't we
%  use $(v_i,\tau_i)$ introduced above? Things are much clearer this
%  way?}
\subsection{A mesh-dependent test norm}
\seclab{sec:meshDep}
Ideally, we would be interested in the use of the test norm 
\[
\|\left(v,\tau\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2
\]
for practical computations. However, the presence of the term $\|v\|$ together with $\sqrt{\epsilon}\|\grad v\|$ (and similarly $\|\div \tau\|$ and $\frac{1}{\sqrt{\epsilon}}\|\tau\|$ terms) induces boundary layers in the optimal test functions for under-resolved meshes. We can see this by recovering the strong form of the variational problem defining test functions. We first note that the variational problems for the $v$ and $\tau$ components of optimal test functions decouple from each other under this test norm. Then, examining the variational problem for the $v$ component only of an optimal test function, and assuming $\div \beta = 0$ for illustrative purposes, we have 
\begin{align*}
\left(\left(v,0\right),\left(\delta v,\delta\tau\right)\right)_{V} &= (v,\delta v) + \epsilon \left(\grad v,\grad \delta v\right) + \left(\beta \cdot \grad v, \beta \cdot \grad \delta v\right)\\
&= \left(v - \epsilon \Delta v - \div \left(\left(\beta \otimes \beta\right) \grad v\right), \delta v\right)_{L^2} + \langle \epsilon \grad v\cdot n, \delta v\rangle + \langle n\cdot \left(\beta\otimes\beta\right) \grad v , \delta v\rangle.
\end{align*}
After integration by parts, we recover the strong form of the operator $L$ inducing such a variational problem 
\[
Lv \coloneqq v - \epsilon \Delta v - \div \left(\left(\beta \otimes \beta\right) \grad v\right),
\]
where we neglect the resulting boundary terms from integration by parts for now.

The streamline direction $\beta$ induces an anisotropic diffusion, while the $\sqrt{\epsilon}\|\grad v\|_{L^2}$ term induces a small isotropic diffusion contribution everywhere. Since any vector in the cross-stream direction is in the null space of the anisotropic diffusion tensor, in the cross-stream directions, the optimal test function is governed only by the cross-stream part of the operator $L$
\[
L_{\rm \beta^\perp} \coloneqq v - \epsilon \Delta v,
\]
and can develop boundary layers in those directions. The presence of boundary layers has been verified through numerical computation as well; using an $H^1$-conforming finite element code with $hp$-adaptivity \cite{demkowicz2006computing}, the solution to the variational problem defining the optimal test function under the above test norm was computed. Figure~\ref{fig:boundaryTest} shows the result of such a computation for the $v$ component of an optimal test function under the above test norm. 
\begin{figure}[!h]
\centering
\subfigure{\includegraphics[scale=.22]{figs/mesh1.png}}
\subfigure{\includegraphics[scale=.22]{figs/sol1.png}}
\caption{The $v$ component of the optimal test function corresponding to flux $\widehat{u} = x(1-x)$ on the bottom side of a unit element for $\epsilon = 0.01$. The corresponding $hp$-mesh used to compute the solution is displayed to the left.}
\label{fig:boundaryTest}
\end{figure}
To avoid boundary layers in the optimal test functions, we follow \cite{DPGrobustness} in scaling the $L^2$ contributions of $v$ by $C_v(K)$, such that, when transformed to the reference element, both $C_v(K)\|v\|^2$ and $\epsilon\|\grad v\|^2$ are of the same magnitude. Similarly, we scale the $L^2$ contributions of $\tau$ by $C_\tau(K)$ such that $\frac{C_\tau(K)}{\epsilon} \|\tau\|^2$ and $\|\div \tau\|^2$ are of the same magnitude as well. For this paper, we consider only isotropic refinements on quadrilateral elements in 2D.

Our test norm, as defined over a single element $K$, is now
\[
\|\left(v,\tau\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
\]
This modified test norm avoids boundary layers in the locally computed optimal test functions, but for adaptive meshes, provides additional stability in areas of heavy refinement, where the best approximation error tends to be large and stronger robustness is most necessary.  This leads to a test norm which produces easily approximable optimal test functions, but still provides \textit{asymptotically} the strongest test norm and tightest robustness results in the areas of highest error.

\subsection{Equivalence of energy norm with $\nor{\cdot}_U$}
%\subsection{Relations between trial and test constants}
\label{sec:main_bounds}

The main theoretical result of this paper can now be given:
\begin{lemma}
Under the mesh-dependent test norm
\[
\|\left(v,\tau\right)\|_{V,\Oh}^2 = \|C_vv\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \|C_\tau\tau\|^2,
\]
where $C_v, C_{\tau}\in L^2(\Omega)$ are defined elementwise through
\begin{align*}
\left.C_v\right |_K &= \min\left\{\sqrt{\frac{\epsilon}{|K|}},1\right\}\\
\left.C_{\tau}\right |_K &= \min\left\{\frac{1}{\sqrt{\epsilon}},\frac{1}{\sqrt{|K|}}\right\}.
\end{align*}
If $\beta$ satisfies \eqref{a_req}, \eqref{b_req}, and \eqref{c_req}, the DPG energy norm $\nor{\cdot}_E$ satisfies the following equivalence relations
\begin{align*}
\nor{u}_{L^2} + \nor{\sigma}_{L^2} + \epsilon\nor{\widehat{u}} + \sqrt{\epsilon}\nor{\widehat{f}_n} 
&\lesssim \nor{\left(u,\sigma, \widehat{u},\widehat{f}_n\right)}_E \\ 
%\nor{\left(u,\sigma, \widehat{u},\widehat{f}_n\right)}_E &\lesssim \nor{u}_{L^2} + \nor{C_\sigma \sigma}_{L^2} + \frac{1}{\sqrt{\epsilon}} \left(\nor{\widehat{u}} + \nor{\widehat{f}_n}\right),
\nor{\left(u,\sigma, \widehat{u},\widehat{f}_n\right)}_E &\lesssim \nor{u}_{L^2} + \nor{\frac{1}{\epsilon C_\tau} \sigma}_{L^2} + \frac{1}{\sqrt{\epsilon}} \left(\nor{\widehat{u}} + \nor{\widehat{f}_n}\right).
\end{align*}
%where $C_\sigma \in L^2(\Omega)$ is defined elementwise through $\left.C_\sigma\right|_K  = \max\left\{ \frac{1}{\sqrt{\epsilon}} , \frac{\sqrt{|K|}}{\epsilon} \right\}$.
\end{lemma}

\begin{proof}
We begin by proving the bound from below. As a consequence of the duality of norms discussed in Section~\secref{energyPair}, we know that the norm $\left\| u \right\|_{U,1}$ is induced by a specific test norm $\| v  \|_{V,U,1}$.  To bound $\|\cdot\|_E$ robustly from above or below by a given norm $\left\| u \right\|_{U,2}$ on $U$ now only requires the robust bound in the opposite direction of $\| v \|_{V,U,1}$ by $\|v\|_{V,U,2}$.

For $f$ and $g$ defined in \eqref{adjoint1} and \eqref{adjoint2},
\begin{align*}
f &= \epsilon^{-1}\tau + \grad v  \\
g &=\div \tau - \beta\cdot \grad v,
\end{align*} 
we can characterize the test norm for 
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,1}^2 = \|u\|^2 + \|\sigma\|^2 + \epsilon\|\widehat{u}\|^2+ \sqrt{\epsilon}\|\widehat{u}\|^2
\]
through the equivalence relation
\begin{align*}
\|\left(v,\tau\right)\|_{V,U,1} &\simeq \sup_{u,\sigma,\widehat{u},\widehat{f}_n}\frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\|u\| + \|\sigma\| + \epsilon\|\widehat{u}\|+ \sqrt{\epsilon}\|\widehat{u}\|}\\
& \simeq \|g\| + \|f\| + \frac{1}{\epsilon}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle \jump{\tau\cdot n}, \widehat{u}\rangle}{\|\widehat{u}\|} + \frac{1}{\sqrt{\epsilon}}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, \jump{v}\rangle}{\|\widehat{f}\|},
\end{align*}
which, by definition of the boundary norms, is 
\[
\|\left(v,\tau\right)\|_{V,U,1} \simeq \|g\| + \|f\| + \frac{1}{\epsilon}\|\jump{\tau\cdot n}\| + \frac{1}{\sqrt{\epsilon}}\|\jump{v}\|.
\]
We wish to show the bound
\[
\nor{\left(v,\tau\right)}_{V,\Oh} \lesssim \|g\| + \|f\| + \frac{1}{\epsilon}\|\jump{\tau\cdot n}\| + \frac{1}{\sqrt{\epsilon}}\|\jump{v}\|.
\]
By noting that both 
\begin{align*}
\nor{C_vv_0} &\leq \nor{v_0},\\
\nor{C_\tau\tau_0} &\leq \frac{1}{\sqrt{\epsilon}}\nor{\tau_0},
\end{align*}
we have that $\nor{\left(v,\tau\right)}_{V,\Oh} \leq \nor{\left(v,\tau\right)}_{V}$, so it suffices to prove the bound for the mesh-independent test norm 
\[
\|\left(v,\tau\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2.
\]

We will bound $\|\left(v,\tau\right)\|_V$ for all $\left(v,\tau\right)$ by decomposing $\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right)$ as described in Section~\ref{sec:strategy2}.

By the triangle inequality, robustly bounding $\|\left(v,\tau\right)\|_V$ from above reduces to robustly bounding each component 
\[
\|\left(v_{0},\tau_{0}\right)\|_V, \|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|g\| + \|f\| + \frac{1}{\epsilon}\|\jump{\tau\cdot n}\| + \frac{1}{\sqrt{\epsilon}}\|\jump{v}\|.
\]

%Roughly speaking, Lemma \ref{lemma_grad} concerns the robust control of $u$ by the energy error; Lemmas \ref{lemma_stream} and \ref{lemma_boundary} concern the robust control of field variable $\sigma$ and flux/trace variables, respectively.

\begin{itemize}
\item \textbf{Bound on $\|\left(v_{0},\tau_{0}\right)\|_V$}

Lemma \ref{lemma_boundary} gives control over $\sqrt{\epsilon}\|\grad v_0\| + \frac{1}{\epsilon}\|\tau_0\|$ through
\[
\|\grad v_0\| = \frac{1}{\epsilon}\|\tau_0\| \lesssim \frac{1}{\epsilon} \nor{\jump{\tau_0\cdot n}}_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \nor{\jump{v_0}}_{\Gamma_h^0 \cup \Gamma_+} = \frac{1}{\epsilon} \nor{ \jump{\tau\cdot n}}_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \nor{ \jump{v}}_{\Gamma_h^0 \cup \Gamma_+}.
\]
Lemma 4.2 of \cite{analysisDPG} gives us the Poincare inequality for discontinuous functions
\[
\|v_0\| \lesssim \|\grad v_0\| + \|\jump{v}\|.
\]
%Since $f=0$, by Lemma 2, $\|\beta\cdot \grad v_0\|  \lesssim \|g\| = 0$.  
Since $g = 0$, $\| \div \tau_0\| = \|\beta\cdot \grad v_0\|\lesssim \|\grad v_0\|$, which we now have control over as well.

\item \textbf{Bound on $\|\left(v_{1},\tau_{1}\right)\|_V$}

With $f = 0$, Lemma \ref{lemma_stream} provides the bound
\[
\|\beta \cdot \grad v_1 \| \lesssim \| g\|.
\]
Noting that $\div \tau_1 = g+\beta\cdot \grad v_1$ gives $\|\div \tau_1 \| \lesssim \|g\|$ as well.  Lemma \ref{lemma_grad} gives
\[
\epsilon \|\grad v_1\|^2 + \|v_1\|^2 \lesssim \|g\|^2,
\]
and noting that $\epsilon^{-1/2}\tau_1 = \epsilon^{1/2}\grad v_1$ gives $\epsilon\|\grad v_1\|^2 = \epsilon^{-1}\|\tau_1\|^2 \lesssim \|g\|^2$ as well.

\item \textbf{Bound on $\|\left(v_{2},\tau_{2}\right)\|_V$}

Lemma \ref{lemma_grad} provides, for $\epsilon$ sufficiently small, 
\[
\epsilon \|\grad v_2\|^2 + \|v_2\|^2 \lesssim  \epsilon \| f\|^2 \leq \|f\|^2.
\]
We have $\epsilon^{-1}\tau_2 = f - \grad v_2$, so $\epsilon^{-1} \|\tau_2\| \lesssim \|f\| + \|\grad v_2\|$. Lemma~\ref{lemma_grad} implies $\|\grad v_2\|^2  \lesssim  \| f\|^2$, so for $\epsilon \leq 1$, we have $\epsilon^{-1/2}\|\tau_2\| \leq \epsilon^{-1}\|\tau_2\| \lesssim \|f\|$.  The remaining terms can be bounded by noting that, with $g = 0$, $\|\div \tau_2\| = \|\beta\cdot \grad v_2\| \lesssim \|\grad v_2\| \lesssim \|f\| $.
\end{itemize}

We have shown the robust bound of the norm $\|\cdot \|_{U,1}$ on $U$ by the energy norm; for a full equivalence statement, we require a bound from above on the energy norm by the norm $\|\cdot \|_{U,2}$ on $U$.  By the duality of the energy and test norm, this is equivalent to bounding the test norm from below by the test norm induced by $\|\cdot \|_{U,2}$. 
For a norm on $U$ of the form
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,2}^2 = \|u\|^2 + \nor{C_\sigma \sigma}^2 + \frac{1}{{\epsilon}}\left( \|\widehat{u}\|^2 + \|\widehat{f}_n\|^2\right),
\]
the induced test norm is equivalent to
\begin{align*}
\| \left(\tau,v\right) \|_{V,U,2} &\simeq \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E} \\
&\simeq \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \jump{\tau_n}, \widehat{u} \rangle + \langle \widehat{f}_n, \jump{v} \rangle
}{\|u\| + \nor{\left(\epsilon C_\tau\right)^{-1}\sigma} + \frac{1}{\sqrt{\epsilon}}\left(  \|\widehat{u}\| + \|\widehat{f}_n\| \right)} \\
&\simeq \|g\| + \nor{\epsilon C_\tau f} + {\sqrt{\epsilon}}\left(\sup_{\widehat{u},\widehat{f}_n \neq 0}\frac{\langle \jump{\tau_n}, \widehat{u} \rangle + \langle \widehat{f}_n, \jump{v} \rangle}{\|\widehat{u}\| + \|\widehat{f}_n\|}\right),
\end{align*}
where $f$ and $g$ are 
\begin{align*}
f &= \frac{1}{\epsilon}\tau + \grad v\\
g &= \div \tau - \beta \cdot \grad v,
\end{align*}
the loads of the adjoint problem defined in \eqref{adjoint1}, \eqref{adjoint2}.

Note that $\epsilon C_\tau \leq \sqrt{\epsilon}$. Then, by the triangle inequality, we have the bounds
\begin{align*}
%\sqrt{\epsilon} \|f \| &\leq \epsilon^{-1/2} \| \tau\| + \sqrt{\epsilon} \|\grad v\| \lesssim \|\\
\|\epsilon C_\tau f \| &\leq C_\tau \nor{ \tau} + \epsilon C_\tau \nor{\grad v} \lesssim \| \left(\tau,v\right)\|_{V,\Oh}\\
\|g \| &\leq \|\div \tau\| +  \|\beta \cdot \grad v\| \lesssim \| \left(\tau,v\right)\|_{V,\Oh}
\end{align*}
We estimate the supremum on the jumps of $\left(\tau,v\right)$ by following \cite{DPGrobustness}; we begin by choosing $\eta \in H({\rm div}; \Omega)$, $w\in H^1(\Omega)$, such that $\left.\left(\eta-\beta w \right)\cdot n\right |_{\Gamma_+} = 0$ and $\left.w\right |_{\Gamma_-\cup\Gamma_0} = 0$, and integrating the boundary pairing by parts to get
\begin{align*}
\langle \jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle &= (\tau,\grad w) + (\div \tau, w) + \left(\eta - \beta w, \grad v\right) +  \left(\div \left(\eta - \beta w\right), v\right)\\
&\lesssim \|C_\tau\tau\| \nor{ \frac{1}{C_\tau}\grad w} + \|\div \tau\| \|w\| \\
&\left.\hspace{.3cm}\right. + \sqrt{\epsilon}\| \grad v \|\frac{1}{\sqrt{\epsilon}}\|\eta\| +  \|\beta \cdot \grad v\| \| w\|\\
&\left.\hspace{.3cm}\right. + \|C_vv\|\nor{\frac{1}{C_v}\div \eta} + \| C_vv\| \nor{\frac{1}{C_v}w} \\
&\left.\hspace{.3cm}\right. + \|C_v v\| \nor{\frac{1}{C_v} \grad w},
\end{align*}
where we have used that $\epsilon < 1$, $\div \beta = O(1)$, and that $\|\beta\cdot \grad w\|\lesssim \|\grad w\|$.

Without loss of generality, assume the problem is scaled such that $\max_{K\in\Oh}|K| \leq 1$. Then, $\frac{1}{C_\tau^2}\leq \frac{1}{C_v^2} \leq \frac{1}{\epsilon}$, and an application of discrete Cauchy-Schwarz gives us 
\begin{align*}
\langle \jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle &\lesssim \|\left(\tau,v\right)\|_{V,\Oh}\frac{1}{\sqrt{\epsilon}}\left(\nor{\eta}_{H({\rm div},\Omega)} + \nor{w}_{H^1(\Omega)}\right),\\
&\lesssim \|\left(\tau,v\right)\|_{V,\Oh}\frac{1}{\sqrt{\epsilon}}\left(\nor{\eta-\beta w}_{H({\rm div},\Omega)} + \nor{w}_{H^1(\Omega)}\right),
\end{align*}
since $\|\eta\|_{H({\rm div},\Omega)} = \|\eta - \beta w + \beta w\|_{H({\rm div},\Omega)} \leq \|\eta - \beta w\|_{H({\rm div},\Omega)} + \|\beta w\|_{H({\rm div},\Omega)} \lesssim \|\eta-\beta w\|_{H({\rm div},\Omega)} + \|w\|_{H^1(\Omega)}$.  Dividing through and taking the supremum gives
\[
\sup_{w,\eta \neq 0} \frac{\langle\jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle}{\left(\nor{\eta-\beta w}_{H({\rm div},\Omega)} + \nor{w}_{H^1(\Omega)}\right)} \lesssim \|\left(\tau,v\right)\|_{V,\Oh}\frac{1}{\sqrt{\epsilon}}.
\]
To finish the proof, define $\rho \in H^{1/2}(\Gamma_h)$ and $\phi \in H^{-1/2}(\Gamma_h)$ such that $\rho = \left.w\right|_{\Gamma_h}$ and $\phi = \left.(\eta-\beta w)\cdot n\right|_{\Gamma_h}$, and note that, from \cite{analysisDPG}, by the definition of the trace norms on $\jump{\tau\cdot n}$ and $\jump{v}$ 
\begin{align*}
\sup_{\rho,\phi \neq 0} \frac{\langle \jump{\tau\cdot n},\rho\rangle + \langle \jump{v},\phi \rangle}{\|\rho\|_{H^{1/2}(\Gamma_h)}+\|\phi\|_{H^{-1/2}(\Gamma_h)}} &= \sup_{w,\eta \neq 0} \frac{\langle \jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle}{ \|w\|_{H^1(\Omega)}+\|\eta-\beta w\|_{H({\rm div},\Omega)}}.
\end{align*}
Together, the bounds on the jump terms and the bounds on $\|g\|$ and $\|f\|$ imply $\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{E} \lesssim \left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,2}$.
\end{proof}

\subsection{Comparison of boundary conditions}

It is worth addressing the effect of boundary conditions on stability.  Specifically, a test norm that provides stability for one set of boundary conditions may perform poorly for another set.  Take, for example, the test norm defined in Section~\ref{sec:main_bounds} and the convection-diffusion problem with Dirichlet boundary conditions.

The bilinear form for the case of Dirichlet boundary conditions is 
\[
b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(v,\tau\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) + \langle \widehat{u}, \jump{\tau \cdot n} \rangle_{\Gh^0} + \langle \widehat{f}_n, \jump{v} \rangle_{\Gh}.
\]
Notice that the boundary terms in the final bilinear form are different; hence, the adjoint problems associated with Section~\ref{sec:strategy3} will now carry different boundary conditions as well. Likewise, the stability properties proven previously will not hold under a different set of boundary conditions.  
%We note that 
%\begin{align*}
%b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gh^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gh} 
%&= \| u \|^2_{L^2}
%\end{align*}
%for the specific continuous test functions $\tau$ and $v$ satisfying
%\begin{align*}
%\div \tau - \beta \cdot \grad v &= u \\
%\frac{1}{\epsilon}\tau + \grad v &= 0
%\end{align*}
%with boundary condition $\left.v\right|_\Gamma = 0$. Choosing a continuous conforming test function $v$ removes the contribution of the term $\langle \widehat{f}_n, \left[v\right] \rangle$ on the mesh skeleton, while the boundary conditions remove the contribution of boundary terms from the bilinear form.  Then, for this specific choice of $\left(\tau, v\right)$, 
%\begin{align*}
%\|u\|_{L^2}^2 &= b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right)}{\|\left(\tau, v\right)\|_V}\|\left(\tau, v\right)\|_V \leq \|u\|_E \|\left(\tau, v\right)\|_V
%\end{align*}
%At minimum, we want $\|u\|_{L^2} \lesssim \|u\|_E$, which requires 
%\[
%\|\left(\tau, v\right)\|_V \lesssim \| u \|_{L^2}
%\]
%for any choice of $u \in L^2$ (dividing through by $\|u\|_{L^2}$ gives the desired result).  This can be considered a ``sanity check"; at the minimum, we at least want control over the behavior of the single field variable $u$.  However, we are unable to prove this in the case of Dirichlet boundary conditions.

As it turns out, the robust bounds given in Section~\ref{sec:main_bounds} hold in $\mathbb{R}^d$ for arbitrary $d$; however, we can show that for the case of Dirichlet boundary conditions, the same results do not hold, even in 1D.  
%In 1D, the problem reduces to 
%\begin{align*}
%\frac{1}{\epsilon}\sigma - u' &= 0\\
%\left(u - \epsilon \sigma \right)' &=f
%\end{align*}
%with bilinear form
%\begin{align*}
%b\left(\left(u,\sigma,\widehat{u},\widehat{f}\right),\left(\tau,v\right)\right) &= \sum_{k=1}^N \left(\left.\widehat{u}(x) \tau(x)\right |^{x_k}_{x_{k-1}} + \left.\widehat{f}(x) v(x)\right |^{x_k}_{x_{k-1}}\right) \\
%&+ \left(\sigma,\epsilon^{-1}\tau\right)_{\Oh} + (u,\tau')_{\Oh}- \left(u - \epsilon \sigma,v'\right)_{\Oh}
%\end{align*}
%where $\widehat{u}(x), \widehat{f}(x) \in \mathbb{R}$ are now point values defined on mesh points $x_k$ for $k=1,\ldots,N$, where $N$ is the number of elements.  We can assume without loss of generality that $\Oh$ is the unit interval $(0,1)$.  
%
%Let us first provide an interpretation of Lemma~\ref{lemma_stream}. Recall the bilinear form 
%\begin{align*}
%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
%\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
%v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh} - \LRa{
%\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n,
%  \jump{v} }_{\Gh},
%\end{align*}
%By choosing $(v,\tau)$ such that
%\begin{align*}
%\div \tau - \beta \cdot \grad v &= u \\
%\frac{1}{\epsilon} \tau + \grad v &= 0
%\end{align*}
%we will have 
%\[
%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
%\left( v, \tau \right)\right) =\|u\|_{L^2}^2 
%\]
%Given this, we can use the definition of the energy norm \eqnref{energyNorm} to bound
%\[
%\|u\|_{L^2}^2 = b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
%\left( v, \tau \right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
%\left( v, \tau \right)\right)}{\|(v,\tau)\|_V}\|(v,\tau)\|_V \lesssim \|u\|_E \|(v,\tau)\|_V
%\]
%If we can show that $\|(v,\tau)\|_V \lesssim \|u\|_{L^2}$ for $(v,\tau)$ as defined above, then this implies 
%\[
%\|u\|_{L^2} \lesssim \|u\|_E
%\]
%By the fact that 
Consider now the 1D analogue of the estimate given by Lemma~\ref{lemma_stream}.  In 1D, $\|\beta\cdot\grad v_1\| \lesssim \|g\|$ reduces to the inequality 
\[
\|\beta v_1'\|\lesssim \|g\|, \quad g\in L^2\!\left(\Oh\right).
\]
Without this inequality, we are unable to prove the robust bound on the $L^2$ error $\|u-u_h\|_{L^2} \lesssim \nor{(u,\sigma,\widehat{u},\widehat{f}_n)-(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h})}_E$.

The adjoint problem corresponding to Lemma~\ref{lemma_stream} in Section~\ref{sec:strategy3} is likewise reduced in 1D to the scalar equation
\begin{align}
\epsilon v_1'' + \beta v_1' &= -g \label{adjoint_1D}
\end{align}
with $v_1\in H^1_0\left((0,1)\right)$.  After multiplying this equation by $\beta v_1'$ and integrate by parts over $\Oh$, we can apply Young's inequality to get
%\[
%\int_0^1 \epsilon v_1'' \beta v_1' + \|\beta v_1'\|_{L^2}^2 = -\int_0^1 g \beta v_1'.\
%]
%Integrating by parts and Young's inequality gives
\begin{align*}
\left.\frac{\epsilon}{2} \beta v_1'^2\right|_0^1 + \|\beta v_1'\|_{L^2}^2 &\leq \frac{1}{2}\|g\|^2 + \frac{1}{2}\|\beta v_1'\|^2,
\end{align*}
implying that
\begin{align*}
\|\beta v_1'\|_{L^2}^2 & \lesssim \|g\|^2 + {\beta \epsilon} v_1'(0)^2.
\end{align*}
Let us restrict ourselves to the cases where $v_1$ is sufficiently smooth for $v'(0)$ to be well defined.  Taking $g=1$ (corresponding to a piecewise constant approximation) we can solve \eqref{adjoint_1D} exactly. 
\begin{figure}[!h]
\centering
\includegraphics[scale=.5]{figs/testBoundary1D.png}
\caption{$v_1(x) = \frac{e^{-\frac{x}{\epsilon}}}{e^{\frac{1}{\epsilon}}-1}\left(e^{\frac{1}{\epsilon}}\left(e^{\frac{x}{\epsilon}}-1\right) + \left(e^{\frac{1}{\epsilon}}-1\right)e^{\frac{x}{\epsilon}}x\right)$, the solution to the adjoint equation for $f=0$ and constant $\beta$ and load $g$ for $\epsilon = .01$.}
\label{fig:testBoundary1D}
\end{figure}
The solution $v_1$ is plotted in Figure~\ref{fig:testBoundary1D}, where we can see that $v_1(x)$ develops strong boundary layers of width $\epsilon$ near the inflow boundary $x=0$. Consequently, $\frac{\epsilon}{2} v_1'(0)^2 \approx \epsilon^{-1}$. Thus, we cannot conclude $\|\beta v'\| \lesssim \|g\|$ when $g$ is a constant,\footnote{Unlike the case of Dirichlet boundary conditions, the inflow condition on $ \widehat{f}_n = u(0)-\epsilon u'(0)$ induces an adjoint boundary condition $\tau(0)=0$, or equivalently $v'(0) = 0$, removing the non-robust term from the estimate.} and as a consequence cannot conclude that the robust error bound $\|u-u_h\|_{L^2} \lesssim \|(u,\sigma,\widehat{u},\widehat{f}_n)-(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h})\|_E$ holds for the solution $u_h$.  More detailed 1D error bounds for Dirichlet boundary conditions are provided in \cite{DPG3}, and indicate the same lack of robustness under the test norm derived in this paper.\footnote{Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
\[
\|\left(\tau, v\right)\|_{V,w}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\|_{w+\epsilon} + \| \div \tau\|_{w+\epsilon} + \frac{1}{\epsilon}\|\tau\|_{w+\epsilon}
\]
where $\|\cdot \|_{w+\epsilon}$ is a weighted $L^2$ norm, where the weight $w \in (0,1)$ is required to vanish on $\Gamma_-$ and satisfy $\grad w = O(1)$. The need for this weight is necessary to account for the loss of robustness at the inflow.}

\begin{figure}[h!]
\centering
\subfigure[Primal problem, Dirichlet inflow BC]{\includegraphics[scale=.3]{figs/primalDir.png}}
\subfigure[Adjoint problem, Dirichlet inflow BC]{\includegraphics[scale=.3]{figs/adjointDir.png}}
\subfigure[Primal problem, new inflow BC]{\includegraphics[scale=.3]{figs/primal.png}}
\subfigure[Adjoint problem, new inflow BC]{\includegraphics[scale=.3]{figs/adjoint.png}}
\caption{Comparison of primal and adjoint problems under both the standard Dirichlet and the new inflow boundary condition. The outflow boundary for each problem is denoted in red. For the standard Dirichlet inflow condition, the solution to the adjoint problem can develop strong boundary layers at the outflow of the adjoint problem. Notice, under the new inflow conditions, the relaxation of a wall-stop boundary condition with a zero-stress condition at the outflow boundary of the adjoint problem.}
\end{figure}

In higher dimensions, the adjoint problem is of the same form as the primal problem with the direction of convection reversed. However, the primal problem determines adjoint boundary conditions on $\Gamma_-$ and $\Gamma_+$. Thus, wheareas for the primal problem, data is convected from the inflow to the outflow, in the adjoint problem, data is convected from the outflow to the inflow boundary instead.

We can intuitively explain the loss of robustness under our derived test norm by the presence of the Dirichlet boundary condition on $v$ at the inflow boundary. Since the direction of convection is reversed in the adjoint equation, we can interpret the adjoint as representing the convection of a concentration $v$ from the outflow to the inflow boundary. In the presence of a Dirichlet boundary condition at the inflow, $v$ can develop strong boundary layers at the inflow. As a consequence, the quantities $\|\beta\cdot \grad v\|$ and $\sqrt{\epsilon}\|\grad v\|$ are no longer robustly bounded by $\|f\|$ and $\|g\|$, and we can no longer derive robust bounds on the error $\|u-u_h\|_{L^2}$ by the error in the energy norm.

Recall our strategy for analysis was to decompose of $(v,\tau)$ into continuous and discontinuous portions. Mathematically speaking, the use of Dirichlet boundary conditions on the primal problem introduces strong boundary layers into the solution $v$ of the adjoint equation --- in other words, boundary layers are introduced into the continuous portions of our decomposition of $(v,\tau)$.\footnote{The boundary conditions do not introduce boundary layers into the actual computed test functions. However, an interesting phenomenon observed is that, for small $\epsilon$, a lack of robustness can manifest itself during numerical experiments as additional refinements near the inflow boundary, precisely where the continuous parts of the decomposition of $(v,\tau)$ develop boundary layers.} The new inflow boundary condition on the primal problem relaxes the wall boundary condition induced on the adjoint/dual problem with a boundary condition that does not generate boundary layers, resulting in stronger stability estimates for the adjoint, and a better result for the primal problem.

%\begin{figure}[h]
%\centering
%\subfigure[Primal problem]{\includegraphics[scale=.3]{figs/primal.png}}
%\subfigure[Adjoint problem]{\includegraphics[scale=.3]{figs/adjoint.png}}
%\caption{Comparison of primal and adjoint problems for convection-diffusion under the standard Dirichlet outflow boundary condition and the new inflow boundary condition. Notice the replacement of a wall-stop boundary condition with a Neumann stress boundary condition at the outflow boundary of the adjoint problem. }
%\end{figure}

\section{Numerical experiments}
\label{sec:num_exp}

In each numerical experiment, we vary $\epsilon = .01, .001, .0001$ in order to demonstrate robustness over a range of $\epsilon$.  This is intended to mirror the experience with roundoff effects in numerical experiments \cite{DPGrobustness}; for ``worst-case" linear solvers, such as LU decomposition without pivoting, the effect of roundoff error becomes evident in the solving of optimal test functions for $\epsilon \leq O(1e-5)$.  The roundoff itself comes from the conditioning of the Gram matrix under certain test norms; for example, if the weighted $H({\rm div};\Omega)\times H^1(\Omega)$ norm is used for the test norm $\|\left(\tau,v\right)\|_V$ (as was done in \cite{DPG2}), for an element of size $h$, $\|v\|_{L^2}^2 = O(h)$, while $\|\grad v\|_{L^2}^2 = O(h^{-1})$. As $h\rightarrow 0$, the seminorm portion of the test norm dominates the Gram matrix, leading to a near-singular and ill-conditioned system.

The effect of roundoff error is often characterized by an increase in the energy error, which (assuming negligible error in the approximation of test functions) is proven to decrease for any series of refined meshes. These roundoff effects are dependent primarily on the mesh, appearing when trying to fully resolve very thin boundary layers by introducing elements of size $\epsilon$ through adaptivity. The effects of roundoff error were successfully treated in \cite{DPG3} by dynamically rescaling the test norms based on element size, a practical remedy not covered yet by the present analysis.

\subsection{Eriksson-Johnson model problem}

To confirm our theoretical results, we adopt a modification of a problem first proposed by Eriksson and Johnson in \cite{Eriksson1993}. For the choice of $\Omega = (0,1)^2$, $f=0$, and $\beta = (1,0)^T$, the convection diffusion equation reduces to
\[
\pd{u}{x} - \epsilon \left(\pdd{u}{x}+ \pdd{u}{y}\right) = 0,
\]
which has an exact solution by separation of variables, allowing us to analyze convergence of DPG for a wide range of $\epsilon$.  For boundary conditions, we impose $u=0$ on $\Gamma_+$ and $\beta_n u - \sigma_n$ on $\Gamma_-$, which reduces to
\begin{align*}
u-\sigma_x &= u_0-\sigma_{x,0}, \quad x=0,\\
\sigma_y &=  0, \quad y=0,1,\\
u &= 0, \quad x=1.\\
\end{align*}
In this case, our exact solution is the series
\[
u(x,y) = C_0 + \sum_{n=1}^\infty C_n \frac{\exp(r_2(x-1)-\exp(r_1(x-1)))}{r_1\exp(-r2) - r_2\exp(-r1)}\cos(n\pi y),
\]
where
\begin{align*}
r_{1,2} &= \frac{1 \pm \sqrt{1 + 4 \epsilon\lambda_n}}{2 \epsilon},\\
\lambda_n &= n^2\pi^2 \epsilon.
\end{align*}
The constants $C_n$ depend on a given inflow condition $u_0$ at $x=0$ via the formula
\[
C_n = \int_0^1 u_0(y) \cos(n\pi y).
\]

All computations have been done using the adaptive DPG code Camellia, built on the Sandia toolbox Trilinos \cite{Camellia}.

\subsubsection{Solution with $C_1 = 1, C_{n\neq 1} = 0$}

We begin with the solution taken to be the first non-constant term of the above series.  We set the inflow boundary condition to be exactly the value of $u-\sigma_x$ corresponding to the exact solution.

\begin{figure}[h!]
\centering
\subfigure{
\includegraphics[scale=.37]{figs/wallBC_exact_u.png}
}
\subfigure{
\includegraphics[scale=.37]{figs/wallBC_exact_sigx.png}
}
\subfigure{
\includegraphics[scale=.37]{figs/wallBC_exact_sigy.png}
}
\caption{Solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
\end{figure}
In each case, we begin with a square 4 by 4 mesh of quadrilateral elements with order $p=3$.  We choose $\Delta p = 5$, though we note that the behavior of DPG is nearly identical for any $\Delta p \leq 3$, and qualitatively the same for $\Delta p = 2$.  $h$-refinements are executed using a greedy refinement algorithm, where element energy error $e_K^2$ is computed for all elements $K$, and elements such that $e_K^2 \leq \alpha \max_K e_K^2$ are refined.  We make the arbitrary choice of taking $\alpha = .2$ for each of these experiments.

\begin{figure}[h!]
\centering
\includegraphics[scale=.4]{figs/u_pointdiff_wallBC.png}
\caption{Adapted mesh and pointwise error for $\epsilon=.01$}
\end{figure}
We are especially interested in the ratio of energy error and total $L^2$ error in both $\sigma$ and $u$, which we denote as $\|u-u_h\|_{L^2}$.  The bounds on $\nor{\cdot}_E$ presented in Section~\ref{sec:main_bounds} imply that, using the above test norm, $\|u-u_h\|_{L^2} / \|u-u_h\|_E \leq C$ independent of $\epsilon$.  Figure~\ref{ratios_simple}, which plots the ratio of $L^2$ to energy error, seems to imply that (at least for this model problem) $C=O(1)$.  Additionally, while we do not have a robust lower bound ($\|u-u_h\|_{L^2} / \|u-u_h\|_E$ can approach $0$ as $\epsilon \rightarrow 0$), our numerical results appear to indicate the existence of an $\epsilon$-independent lower bound.

\begin{figure}[h!]
\centering
\subfigure{
\includegraphics[scale=.38]{figs/errorrates_wallBC.png}
}
\subfigure{
\includegraphics[scale=.38]{figs/L2energyratio_wallBC.png}
}
\caption{$L^2$ and energy errors, and their ratio for $\epsilon=.01$, $\epsilon=.001$, $\epsilon=.0001$}
\label{ratios_simple}
\end{figure}
The effect of a mesh dependent scalings on the $\|v\|^2$ and $\|\tau\|^2$ terms in the test norm can be seen in the ratios of $L^2$ to energy error; as the mesh is refined, the constants in front of the $L^2$ terms for $v$ and $\tau$ converge to stationary values (providing the full robustness implied by our adjoint energy estimates), and the ratio of $L^2$ to energy error transitions from a smaller to a larger value.  The transition point happens later for smaller $\epsilon$, which we expect, since the transition of the ratio corresponds to the introduction of elements whose size is of order $\epsilon$ through mesh refinement.

We examined how small $\epsilon$ needed to be in order to encounter roundoff effects as well. In \cite{DPGrobustness}, the smallest resolvable $\epsilon$ using only double precision arithmetic was $1e-4$. The solution of optimal test functions is now done using both pivoting and equilibration, improving conditioning. Roundoff effects still appear, but at smaller values of $\epsilon$.

\begin{figure}[h!]
\centering
\subfigure{
\includegraphics[scale=.38]{figs/roundoff_rates.png}
}
\subfigure{
\includegraphics[scale=.38]{figs/roundoff_ratio.png}
}
\caption{Energy error and $L^2$/energy error ratio for $\epsilon=1e-5$, $\epsilon=1e-6$, $\epsilon=1e-7$. Non-monotonic behavior of the energy error indicates conditioning issues and roundoff effects.}
\label{roundoff_figures}
\end{figure}

Without anisotropic refinements, it still becomes computationally difficult to fully resolve the solution for $\epsilon$ smaller than $1e-5$. Regardless, for all ranges of $\epsilon$, DPG does not lose robustness, as indicated by the rates and ratio between $L^2$ and energy error in Figure~\ref{roundoff_figures} remaining bounded from both above and below. For $\epsilon = 1e-5$, we observe that the ratio of $L^2$ error increases, corresponding to the scaling of the test norm with mesh size (the transition in test norm occurs after 8 refinements, which, for an initial $4\times 4$ mesh, implies a minimum element size of about $1.5e-05$. At this point, rescaled test norm allows us to take advantage of the full magnitude of the $L^2$ term for $\|v\|$ and $\|\tau\|$ implied by our adjoint estimates). By analogy, for smaller $\epsilon = 1e-6, 1e-7$, the transition period should begin near the 10th and 11th refinement iterations; however, we do not observe such behavior, possibly due to roundoff effects. 
For $\epsilon=1e-6$, the ratio simply remains constant, but for $\epsilon=1e-7$, we observe definite roundoff effects, as the energy error increases at the 11th refinement. Since DPG is optimal in the energy norm for a mesh-independent test norm\footnote{While the test norm changes with the mesh, it increases monotonically. A strictly stronger test norm implies $\frac{b(u,v)}{\|v\|_1} \geq \frac{b(u,v)}{\|v\|_2}$ for any $\|v\|_1 \leq \|v\|_2$}, we expect monotonic decrease of the energy error with mesh refinement. Non-monotonic behavior indicates either approximation or roundoff error, and as we observed no qualitative difference between using $\Delta p = 5$ and $\Delta p = 6$ for these experiments, we expect that the approximation error is negligible and conclude roundoff effects are at play when these phenomena are observed.

It is worth noting that for $\epsilon \leq 1e-5$, we do not perform enough refinements to completely resolve the boundary layer, so $|K| \geq \epsilon$ for all $K\in \Oh$. Thus, any roundoff effects observed are not due to the conditioning issues associated with the differing scales of the $\nor{v}_{L^2(K)}$ and $\nor{\grad v}_{L^2(K)}$ terms discussed previously.

\subsubsection{Neglecting $\sigma_n$}

In practice, we will not have prior knowledge of $\sigma_n$ at the inflow, and will have to set $\beta_n u - \sigma_n = u_0$, ignoring the viscous contribution to the boundary condition.  The hope is that for small $\epsilon$, this omission will be negligible. Figure~\ref{ratios_noSigma} indicates that, between $\epsilon = .005$ and $\epsilon = .001$, the omission of $\sigma_n$ in the boundary condition becomes negligible, and both our error rates and ratios of $L^2$ to energy error become identical to the case where $\sigma_n$ is explicitly accounted for in the inflow condition. For large $\epsilon = .01$, the $L^2$ error stagnates around $1e-3$, or about $7\%$ relative error.

\begin{figure}[h!]
\centering
\subfigure{
\includegraphics[scale=.38]{figs/rates_noSigma.png}
}
\subfigure{
\includegraphics[scale=.38]{figs/ratio_noSigma.png}
}
\caption{$L^2$ and energy errors and their ratio when neglecting $\sigma_n$ at the inflow.}
\label{ratios_noSigma}
\end{figure}

\subsubsection{Discontinuous inflow data}

We note also that an additional advantage of selecting this new boundary condition is a relaxation of regularity requirements: as $\widehat{f}_n \in H^{-1/2}(\Gh)$, strictly discontinuous inflow boundary conditions are no longer ``variational crimes".  We consider the discontinuous inflow condition
\[
u_0(y) = \begin{cases}
(y-1)^2, \quad &y>.5\\
-y^2, \quad &y\leq .5 
\end{cases}
\]
as an example of a more difficult test case.

\begin{figure}[h!]
\centering
\subfigure{
\includegraphics[scale=.38]{figs/disc_hat.png}
}
\subfigure{
\includegraphics[scale=.38]{figs/disc_hat_surf.png}
}
\caption{Solution variables $u$ and $\widehat{u}$ with discontinuous inflow data $u_0$ for $\epsilon = .01$.}
\label{disc_sol}
\end{figure}
Figure~\ref{disc_sol} shows the solution $u$ and overlaid trace variable $\widehat{u}$, which both demonstrate the regularizing effect of viscosity on the discontinuous boundary condition at $x=0$. However, we do not have a closed-form solution with which to compare results for a stricly discontinuous $u_0$.  In order to analyze convergence, we approximate $u_0$ with 20 terms of a Fourier series, giving a near-discontinuity for $u_0$.

\begin{figure}[h!]
\centering
\subfigure{
\includegraphics[scale=.38]{figs/rates_disc.png}
}
\subfigure{
\includegraphics[scale=.38]{figs/ratio_disc.png}
}
\caption{$L^2$ and energy errors, and their ratio for $\epsilon=.01$, $\epsilon=.001$, $\epsilon=.0001$, with discontinuous $u_0$ approximated by a Fourier expansion. }
\label{disc_sol_fourier}
\end{figure}

The ratios of $L^2$ to energy error are now less predictable than for the previous example, in part due to the difficulty in approximating highly oscillatory boundary conditions. The numerical experiments were originally performed by applying boundary conditions via interpolation; the result was that the highly oscillatory inflow boundary condition was not sampled enough to be properly resolved, causing the solution to converge to a solution different than the exact solution.  The experiments were repeated using the penalty method to enforce inflow conditions; however, we note that the proper way to do so is to use an $L^2$ projection at the boundary.  Even when using the penalty method, however, the ratios still remain bounded and close to $1$ for $\epsilon$ varying over two orders of magnitude, as predicted by theory.

\section{Conclusions}

We have presented in this paper the analysis of a non-canonical test norm and its corresponding DPG energy norm for the convection-diffusion equation in the small-diffusion limit. Additionally, we have introduced a non-standard inflow boundary condition, and have explored the difference between between this and the standard Dirichlet inflow boundary condition.

Numerical results are presented in order to verify the results derived in this paper. However, at least for our model problem, numerical experiments appear to demonstrate results that are stronger than our proofs indicate, delivering solutions for $u$ and $\sigma$ that are extremely close to their best $L^2$ projections.

The theory presented in this paper have been successfully extrapolated to nonlinear singular perturbation problems and systems of equations, and has been applied in context of the Burgers and Navier-Stokes equations. These results will be presented in an upcoming paper.

\section{Acknowledgements}

The authors would like to acknowledge the help of Nathan Roberts with software development and Dr Robert Moser for fruitful discussions and perspective. Chan and Demkowicz were supported by the Department of Energy [National Nuclear Security Administration] under Award Number [DE-FC52-08NA28615]. Heuer was supported through the project "Fondecyt-Chile 1110324" and by the "J Tinsley Oden Faculty Research Fellowship" of the Institute of Computational Engineering and Sciences (ICES).

%None yet.  Ideas:
%\begin{itemize}
%\item Explanation of choice of boundary condition and why it impacts stability
%\item Interpretation of weight as allowing diffusion to work on the boundary.  
%\item Note results have worked for Burgers, and mention the extension to Navier-Stokes
%\end{itemize}

\bibliographystyle{plain}
\bibliography{paper}

\input{paper_appendix.tex}

\end{document}

### 2012-06-15 docs/Jesse/Proposal/BurgersNotes.tex
put together rough proposal with a few missing sections

\section{The viscous Burgers equation}

We will begin with the viscous Burgers' equation as an example of

\begin{figure}[!h]
\centering
\includegraphics[scale=.5]{figs/burgers1e4.png}
\caption{Shock solution for Burgers' equation with $\epsilon = 10^{-4}$.} 
\end{figure}

### 2012-06-15 docs/Jesse/Proposal/DPGrobustness.tex
put together rough proposal with a few missing sections

--- 2012-06-13 docs/Jesse/HeuerPaper/paper.tex
@@
-%&pdflatex
-\documentclass[11pt,onecolumn]{scrartcl}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
-\usepackage[top=2cm,bottom=3cm,left=2.5cm,right=2cm]{geometry}
-\usepackage{amssymb}
-\usepackage{listings}
-\usepackage{array}
-\usepackage{mathtools}
-\usepackage{dsfont}
-\usepackage{graphicx}
-\usepackage{pdfpages}
-\usepackage[textsize=footnotesize,color=green]{todonotes}
-\usepackage{algorithm, algorithmic}
-\usepackage{array}
-\usepackage{bm}
-\usepackage{tikz}
-\usepackage{subfigure}
-\usepackage[normalem]{ulem}
-
-\newcommand{\bs}[1]{\boldsymbol{#1}}
-\DeclareMathOperator{\diag}{diag}
-
-\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}
-
-\newcommand{\tablab}[1]{\label{tab:#1}}
-\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
-
-\newcommand{\theolab}[1]{\label{theo:#1}}
-\newcommand{\theoref}[1]{\ref{theo:#1}}
-\newcommand{\eqnlab}[1]{\label{eq:#1}}
-\newcommand{\eqnref}[1]{\eqref{eq:#1}}
-\newcommand{\seclab}[1]{\label{sec:#1}}
-\newcommand{\secref}[1]{\ref{sec:#1}}
-\newcommand{\lemlab}[1]{\label{lem:#1}}
-\newcommand{\lemref}[1]{\ref{lem:#1}}
-
-\newcommand{\mb}[1]{\mathbf{#1}}
-\newcommand{\mbb}[1]{\mathbb{#1}}
-\newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\nor}[1]{\left\| #1 \right\|}
-\newcommand{\snor}[1]{\left| #1 \right|}
-\newcommand{\LRp}[1]{\left( #1 \right)}
-\newcommand{\LRs}[1]{\left[ #1 \right]}
-\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
-\newcommand{\LRc}[1]{\left\{ #1 \right\}}
-\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
-\newcommand{\Grad} {\ensuremath{\nabla}}
-\newcommand{\Div} {\ensuremath{\nabla\cdot}}
-\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
-\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
-\newcommand{\uh}{\widehat{u}}
-\newcommand{\fnh}{\widehat{f}_n}
-\renewcommand{\L}{L^2\LRp{\Omega}}
-\newcommand{\pO}{\partial\Omega}
-\newcommand{\Gh}{\Gamma_h}
-\newcommand{\Gm}{\Gamma_{-}}
-\newcommand{\Gp}{\Gamma_{+}}
-\newcommand{\Go}{\Gamma_0}
-\newcommand{\Oh}{\Omega_h}
-
-\newcommand{\eval}[2][\right]{\relax
-  \ifx#1\right\relax \left.\fi#2#1\rvert}
-
-\def\etal{{\it et al.~}}
-
-\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
-\newcommand{\tensor}[1]{\underline{\vect{#1}}}
-\newcommand{\del}{\Delta}
-\newcommand{\grad}{\nabla}
-\newcommand{\curl}{\grad \times}
-\renewcommand{\div}{\grad \cdot}
-\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
-\newcommand{\eip}[1]{a\left( #1 \right)}
-\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
-\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
-
-\newcommand{\circone}{\ding{192}}
-\newcommand{\circtwo}{\ding{193}}
-\newcommand{\circthree}{\ding{194}}
-\newcommand{\circfour}{\ding{195}}
-\newcommand{\circfive}{\ding{196}}
-
-\def\arr#1#2#3#4{\left[
-\begin{array}{cc}
-#1 & #2\\
-#3 & #4\\
-\end{array}
-\right]}
-\def\vecttwo#1#2{\left[
-\begin{array}{c}
-#1\\
-#2\\
-\end{array}
-\right]}
-\def\vectthree#1#2#3{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-\end{array}
-\right]}
-\def\vectfour#1#2#3#4{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-#4\\
-\end{array}
-\right]}
-
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-
-\newcommand{\G} {\Gamma}
-\newcommand{\Gin} {\Gamma_{in}}
-\newcommand{\Gout} {\Gamma_{out}}
-
-\author{Jesse Chan\textsuperscript{a}, Norbert Heuer\textsuperscript{b}, Tan Bui-Thanh\textsuperscript{a}, and Leszek Demkowicz\textsuperscript{a}}
-
-%\title{$\epsilon$-explicit analysis of DPG for convection-dominated diffusion}
-\title{Robust DPG method for convection-dominated diffusion problems II: a natural inflow condition}
-\date{}
-\begin{document}
-
-%\tableofcontents
-\maketitle
-\begin{center}
-\textsuperscript{a} Institute for Computational Engineering and Sciences, \\University of Texas at Austin, \\Austin, TX 78712, USA\\
-\end{center}
-
-\begin{center}
-\textsuperscript{b} Facultad de Matem\'aticas, \\Pontificia Universidad Cat\'olica de Chile,\\
-Avenida Vicu\~na Mackenna 4860, Santiago, Chile
-\end{center}
-
-\section{Introduction}
-
-\subsection{Singular perturbation problems and robustness}
-
-The finite element/Galerkin method has been widely utilized in engineering to solve partial differential equations governing the behavior of physical phenomena in engineering problems.
-The method relates the solution of a partial differential equation (PDE) to the solution of a corresponding variational problem.
-The finite element method itself provides several advantages --- a framework for systematic mathematical analysis of the behavior of the method, weaker regularity constraints on the solution than implied by the strong form of the equations, and applicability to very general physical domains and geometries.
-
-Historically, the Galerkin method has been very successfully applied to a broad range of problems in solid mechanics, for which the variational problems resulting from the PDE are symmetric and coercive (positive-definite).
-It is well known that the finite element method produces optimal or near-optimal results for such problems, with the finite element solution matching or coming close to the best approximation of the solution in the finite element space.
-However, standard Bubnov-Galerkin methods tend to perform poorly for the class of PDEs known as singular perturbation problems.
-These problems are often characterized by a parameter that may be either very small or very large in the context of physical problems.
-An additional complication of singular perturbation problems is that very often, in the limiting case of the parameter blowing up or decreasing to zero, the PDE itself will change types (e.g.\ from elliptic to hyperbolic).
-
-\subsubsection{Convection-diffusion}
-
-A canonical example of a singularly perturbed problem is the convection-diffusion equation.
-%The equation models the convection of fluid along a direction $\beta$ with a viscous dissipation of magnitude $\epsilon$.
-In the limit as $\epsilon\rightarrow 0$, the convection-diffusion equation transforms from a parabolic to a hyperbolic partial differential equation.
-In 1D, the convection-diffusion equation is
-\begin{align*}
-\beta u'-\epsilon u'' &= f.
-\end{align*}
-The equation represents the change in the concentration $u$ of a quantity in a given medium, taking into account both convective and diffusive effects.
-$\beta$ represents the speed of convection, while the singular perturbation parameter $\epsilon$ represents the diffusivity of the medium.
-In the limit of an inviscid medium as $\epsilon\rightarrow 0$, the equation changes types, from elliptic to hyperbolic, and from second order to first order.
-For Dirichlet boundary conditions $u(0)=u_0$ and $u(1)= u_1$, the solution can develop sharp boundary layers of width $\epsilon$ near the outflow.
-
-%The finite element method has performed notoriously poorly for this example, as well as for many other singularly perturbed problems.
-This poor performance is captured by the error bound for the finite element method applied to the convection-diffusion equation - under the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}
-The poor performance of the finite element method for this problem is reflected in the bound on the error in the finite element solution --- under the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}:
-\[
-\|u-u_h\|_\epsilon \leq C \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
-\]
-for $\|u\|_\epsilon^2 \coloneqq \|u\|_{L^2}^2 + \epsilon \|u'\|_{L^2}^2$, with $C$ independent of $\epsilon$. An alternative formulation of the above bound is 
-\[
-\|u-u_h\|_{H^1(0,1)} \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
-\]
-where $C(\epsilon)$ grows as $\epsilon\rightarrow 0$.
-The dependence of the constant $C$ on $\epsilon$ is referred to as a \textit{loss of robustness} --- as the singular perturbation parameter $\epsilon$ decreases, our finite element error is bounded more and more loosely by the best approximation error.
-As a consequence, the finite element solution can diverge significantly from the best finite element approximation of the solution for very small values of $\epsilon$.
-For example, on a coarse mesh, and for small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation with a boundary layer develops spurious oscillations everywhere in the domain, even where the best approximation error is small.
-These oscillations grow in magnitude as $\epsilon \rightarrow 0$, eventually polluting the entire solution.
-
-%, allowing for more and more error in the finite element solution for as $\epsilon$ shrinks. 
-%Intuitively, a non-robust method will perform increasingly worse as $\epsilon$ decreases.
-
-\subsubsection{Wave propagation}
-
-Another example of a singular perturbation problem which experiences loss of robustness is high frequency wave propagation, in which the singular perturbation parameter is the wavenumber $k$, where $k\rightarrow \infty$.
-The loss of robustness in this case manifests as ``pollution" error, a phenomenon in which the finite element solution degrades over many wavelengths for high wavenumbers (commonly manifesting as a phase error between the FE solution and the exact solution).
-
-\subsubsection{Stabilization terms}
-
-Traditionally, instability/loss of robustness has been dealt with using residual-based stabilization techniques.
-Given some variational form, the problem is modified by adding to the bilinear form the strong form of the residual, weighted by a test function and scaled by a stabilization constant $\tau$.
-The most well-known example of this technique is the streamline-upwind Petrov-Galerkin (SUPG) method, which is a stabilized method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.
-SUPG stabilization not only removes the spurious oscillations from the finite element solution of the convection-diffusion equation, but delivers the best finite element approximation in the $H^1$ norm.
-An important difference between residual-based stabilization techniques and other stabilizations is the idea of \textit{consistency} --- by adding stabilization terms based on the residual, the exact solution still satisfies the same variational problem (i.e.\ Galerkin orthogonality still holds).\footnote{Contrast this to an artificial diffusion method, where a specific amount of additional viscosity is added based on the magnitude of the convection and diffusion parameters.
-The exact solution to the original equation no longer satisfies the new stabilized formulation.}
-
-The addition of residual-based stabilization terms can also be interpreted as a modification of the test functions --- in other words, stabilization can be achieved by changing the test space for a given problem.
-We approach the idea of stabilization through the construction of \textit{optimal test functions} to achieve optimal approximation properties.
-
-%\textcolor{red}{add bit about SUPG/residual-based stabilization terms and test functions}
-
-\subsection{Discontinuous Petrov-Galerkin methods with optimal test functions}
-\seclab{optimalTest} Petrov-Galerkin methods, in which the test space
-differs from the trial space, have been explored for over 30 years,
-beginning with the approximate symmetrization method of Barrett and
-Morton~\cite{BARRETT01101981}. The idea was continued with the SUPG
-method of Hughes, and the characteristic Petrov-Galerkin approach of
-Demkowicz and Oden~\cite{Demkowicz1986188}, which introduced the
-idea of tailoring the test space to change the norm in which a finite
-element method would converge.
-
-The idea of optimal test functions was introduced by Demkowicz and
-Gopalakrishnan in \cite{DPG2}.  Conceptually, these optimal test
-functions are the natural result of the minimization of a residual
-corresponding to the operator form of a variational equation. The
-connection between stabilization and least squares/minimum residual
-methods has been observed previously \cite{GLS}. However, the method in \cite{DPG2} distinguishes itself
-by measuring the residual of the natural \textit{operator form of the equation}, which is posed in the dual space, and measured with the dual norm, as we now discuss.
-
-Throughout the paper, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U'$ and $V'$ as the respective topological dual spaces.
-Let $U_h \subset U$ and $V_h\subset V$ be finite dimensional subsets.
-We are interested in the following problem
-\begin{equation}
-\eqnlab{variationEq}
-\left\{
-  \begin{array}{l}
-    \text{Given } l \in V', \text{ find } u_h \in U_h  \text{ such that} \\ 
-    b(u_h,v_h) = l(v_h), \quad \forall v_h\in V_h,
-  \end{array}
-  \right.
-\end{equation}
-where $b\LRp{\cdot,\cdot}: U \times V \to \mbb{R}$ is a continuous
-bilinear form.  $U$ is chosen to be some trial space of approximating functions, but $V_h$ is as of yet unspecified.
-
-Throughout the paper, we suppose the variational
-problem \eqnref{variationEq} to be well-posed. In that case, we can
-identify a unique operator $B:U\rightarrow V'$ such that
-\[
-\langle Bu,v\rangle_V \coloneqq b(u,v), \quad u\in U, v\in V
-\]
-with $\LRa{\cdot, \cdot}_V$ denoting the duality pairing between $V'$ and $V$, to obtain the operator form of the continuous variational problem
-\begin{equation}
-\eqnlab{dualEq}
-Bu = l \quad \text{in } V'.
-\end{equation}
-In other words, we can represent the continuous form of our variational equation
-\eqnref{variationEq} equivalently as the operator equation \eqnref{dualEq} with values in the
-dual space $V'$.  This motivates us to consider the conditions under which the solution to \eqnref{variationEq} is the solution to the minimum residual problem in $V'$ 
-\[
-u_h = \underset{u_h\in U_h}{\arg\min}\, J(u_h),
-\]
-where $J(w)$ is defined for $w\in U$ as 
-\[
-J(w) = \frac{1}{2}\|Bw-l\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(w,v)-l(v)|^2}{\nor{v}_V^2}.
-\]
-For convenience in writing, we will abuse the notation $\sup_{v \in V}$ to denote $\sup_{v\in V\setminus\{0\}}$ for the remainder of the paper.
-
-Let us define $R_V: V \to V'$ as the Riesz map, which identifies
-elements of $V$ with elements of $V'$ by 
-\[
-\langle R_V v,\delta
-v\rangle_V \coloneqq(v, \delta v)_V, \quad \forall \delta v \in V.
-\]
-Here, $(\cdot, \cdot)_V$ denotes the
-inner product in $V$. As $R_V$ and its inverse, $R_V^{-1}$, are both
-isometries, e.g.\ $\|f\|_{V'} = \|R_V^{-1} f\|_V, \forall f \in V'$, we
-have
-\begin{equation}
-\eqnlab{minimization}
-\min_{u_h\in U_h} J(u_h) = \frac{1}{2}\left\|Bu_h-l\right\|_{V'}^2 =  \frac{1}{2}\left\|R_V^{-1}(Bu_h-l)\right\|_V^2.
-\end{equation}
-The first order optimality condition for \eqnref{minimization} requires
-the G\^ateaux derivative to be zero in all directions $\delta u \in
-U_h$, i\.e\.,
-\begin{align*}
-\left(R_V^{-1}(Bu_h-l),R_V^{-1}B\delta u\right)_V = 0, \quad \forall \delta u \in U. 
-\end{align*}
-We define, for a given $\delta u \in U$, the corresponding {\em optimal test function} $v_{\delta u}$
-\begin{equation}
-\eqnlab{optv}
-v_{\delta u} \coloneqq R_V^{-1}B\delta u \quad  \text{in } V.
-\end{equation} 
-The optimality condition then becomes
-\[
- \langle Bu_h-l, v_{\delta u}\rangle_V = 0, \quad \forall \delta u \in U
-\]
-which is exactly the standard variational equation in
- \eqnref{variationEq} with $v_{\delta u}$ as the test functions.
-We can define the optimal test space $V_{\rm opt} \coloneqq \{v_{\delta u} \text{ s.t.
-} \delta u\in U\}$.
-Thus, the solution of the variational problem \eqnref{variationEq} with test space $V_h = V_{\rm opt}$ minimizes the residual in the dual norm $\nor{Bu_h-l}_{V'}$.
-This is the key idea behind the concept of optimal test functions.
-
-Since $U_h \subset U$ is spanned by a finite number of basis functions $\LRc{\varphi_i}_{i=1}^N$, \eqnref{optv} allows us to compute (for each basis function) a corresponding optimal test function $v_{\varphi_i}$.
-The collection $\LRc{v_{\varphi_i}}_{i = 1}^N$ of optimal test functions then forms a basis for the optimal test space.
-In order to express optimal test functions defined in \eqnref{optv} in a more familiar form, we take  $\delta u = \varphi$, a generic basis function in $U_h$, and rewrite \eqnref{optv} as
-\[
-R_Vv_{\varphi} = B\varphi, \quad \text{in } V',
-\]
-which is, by definition, equivalent to
-\[
-\LRp{v_\varphi,\delta v}_V = \LRa{R_Vv_\varphi,\delta v}_{V}=
-\LRa{B\varphi, \delta v}_V = b\LRp{\varphi,\delta v}, \quad
-\forall \delta v \in V.
-\]
-%% Now, let us define the \textit{trial-to-test} operator $T =
-%% R_V^{-1}B$, which, by \eqnref{optv}, maps a trial function $\delta u$
-%% to its corresponding \textit{optimal} test function $v = T\delta u$.
-%% On the other hand,
-As a result, optimal test functions can be determined by solving the auxiliary
-variational problem
-\begin{equation}
-\eqnlab{optvVar}
-\left(v_\varphi,\delta v\right)_V = b(\varphi,\delta v), \quad \forall
-\delta v \in V.
-\end{equation}
-However, in general, for standard $H^1$ and $H({\rm div})$-conforming finite element methods, test functions are continuous over the entire domain, and hence solving variational problem \eqnref{optvVar} for each optimal test function requires a global operation over the entire mesh, rendering the method impractical.
-A breakthrough came through the development of
-discontinous Galerkin (DG) methods, for which basis functions are
-discontinuous over elements. In particular, the use of discontinuous
-test functions $\delta v$ reduces the problem of determining global 
-optimal test functions
-in \eqnref{optvVar} to local problems that can be solved in an
-element-by-element fashion.
-
-We note that solving \eqnref{optvVar} on each element exactly is
-infeasible since it amounts to inverting the Riesz map $R_V$ exactly.
-Instead, optimal test functions are approximated using the standard
-Bubnov-Galerkin method on an ``enriched" subspace $\tilde{V} \subset
-V$ such that $\dim(\tilde{V}) > \dim(U_h)$ elementwise \cite{DPG1, DPG2}. In this
-paper, we assume the error in approximating the optimal test functions
-is negligible, and refer to the work in \cite{practicalDPG} for
-estimating the effects of approximation error on the performance of DPG.
-
-It is now well known that the DPG method
-delivers the best approximation error in the ``energy norm" --- that is
-\cite{Bui-ThanhDemkowiczGhattas11a, DPG2,DPG4} 
-\begin{equation}
-\eqnlab{optimalError}
-\nor{u-u_h}_{U,E} = \inf_{w\in U_h} \nor{u-w}_{U,E},
-\end{equation}
-where the energy norm $\|\cdot \|_{U,E}$ is defined for a function $\varphi \in U$ as
-\begin{equation}
-\eqnlab{energyNorm} \|\varphi\|_{U,E} \coloneqq \sup_{v\in V}
-\frac{b(\varphi,v)}{\|v\|_V} = \sup_{\nor{v}_V = 1} b(\varphi,v) =
-\sup_{\nor{v}_V = 1} \LRa{B\varphi,v}_V = \nor{B\varphi}_{V'} =
-\nor{v_\varphi}_V,
-\end{equation}
-where the last equality holds due to the isometry of the Riesz map
-$R_V$ (or directly from \eqnref{optvVar} by taking the supremum). An
-additional consequence of adopting such an energy norm is that,
-without knowing the exact solution, the energy error $\|u-u_h\|_{U,E}$ can
-be determined by computing $\|v_{u-u_h}\|_V$ from the following
-identity
-\[
-\left(v_{u-u_h},\delta v\right)_V = b(u-u_h,\delta v) = l\LRp{\delta
-v} - b(u_h,\delta v).
-\]
-This is simply a consequence of the least-squares nature of DPG; the energy error is simply the norm of the  residual in $V'$.
-
-Practically speaking, this implies that the DPG method is discretely stable on any mesh.
-In particular, DPG is unconditionally stable for higher order adaptive meshes, where discrete stability is often an issue.
-
-\subsection{Duality between trial and test norms (energy norm pairings)}
-%\subsection{Abstract energy norm pairings}
-\seclab{energyPair}
-A clear property of the energy norm defined by \eqnref{energyNorm} is that the trial norm $\nor{\cdot}_{U,E}$ is induced by a given test norm.
-However, the reverse relationship holds as well; for any trial norm, the test norm that induces such a norm is recoverable through duality.
-We have a result, proved in \cite{Bui-ThanhDemkowiczGhattas11a}: assuming, for simplicity, that the bilinear form $b(u,v)$ is definite, given any norm $\nor{\cdot}_{U}$ on the trial space $U$, for $\varphi \in U$, we can represent $\nor{\varphi}_{U}$ via
-\[
-\nor{\varphi}_{U} = \sup_{v \in V}\frac{b\LRp{w,v}}{\nor{v}_{V,U}}.
-\]
-where $\nor{v}_{V,U}$ is defined through
-\[
-\nor{v}_{V,U} = \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U}}.
-\]
-%In other words, the norm $\nor{\cdot}_V$ in $V$ can be recovered using the energy norm $\nor{\cdot}_{U,E}$ in $U$, and vice versa.
-
-In particular, given two arbitrary norms $\nor{\cdot}_{U,1}$ and $\nor{\cdot}_{U,2}$ in $U$
-such that $\nor{\cdot}_{U,1} \le c \nor{\cdot}_{U,2}$ for some constant
-$c$, they generate two norms $\nor{\cdot}_{V,U,1}$ and
-$\nor{\cdot}_{V,U,2}$ in $V$ defined by
-\[
-\nor{v}_{V,U,1} \coloneqq \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U,1}}, \quad
-\text{and }\nor{v}_{V,U,2} \coloneqq \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U,2}},
-\]
-such that $\nor{\cdot}_{V,U,1}$ and $\nor{\cdot}_{V,U,2}$ induce
-$\nor{\cdot}_{U,1}$ and $\nor{\cdot}_{U,2}$ as energy
-norms in $U$, respectively. That is,
-\[
-\|\varphi\|_{U,1} = \sup_{v\in V}
-\frac{b(\varphi,v)}{\|v\|_{V,U,1}}, \quad \text{and }\|\varphi\|_{U,2} = \sup_{v\in V}
-\frac{b(\varphi,v)}{\|v\|_{V,U,2}}.
-\]
-
-A question that remains to be addressed is to establish the relationship
-between $\nor{\cdot}_{V,U,1}$ and $\nor{\cdot}_{V,U,2}$, given that
-$\nor{\cdot}_{U,1} \le c \nor{\cdot}_{U,2}$. But this is
-straightforward since we have
-\begin{align*}
- \| v \|_{V,U,2} = \sup_{u \in U} \frac{b\left(w,v\right)}{\left\|
-  w \right\|_{U,2}} \le c\sup_{w \in U} \frac{b\left(w,v\right)}{\left\| w
-  \right\|_{U,1}} = c\| v \|_{V,U,1}.
-\end{align*}
-Consequently, a stronger energy norm in $U$ will generate a weaker
-norm in $V$ and vice versa. In other words, to show that an
-energy norm $\nor{\cdot}_{U,1}$ is weaker than another energy norm
-$\nor{\cdot}_{U,2}$ in $U$, one simply needs to show the reverse inequality on the
-corresponding norms in $V$, that is, $\nor{\cdot}_{V,U,1}$ is stronger
-than $\nor{\cdot}_{V,U,2}$.
-
-%From now on, unless otherwise stated, we will refer to  $\nor{\cdot}_{V,U,1}$, $\nor{\cdot}_{V,U,2}$, and $\nor{\cdot}_{V}$ as the test norms which induce $\nor{\cdot}_{U,1}$, $\nor{\cdot}_{U,2}$, and $\nor{\cdot}_{U,E}$ and vice versa, in the sense discussed above.
-From now on, unless otherwise stated, we will refer to $\nor{\cdot}_{V,U}$ as the test norm that induces a given norm $\nor{\cdot}_U$.
-Likewise, we will refer $\nor{\cdot}_{U,V}$ as the trial norm induced by a given test norm $\nor{\cdot}_V$.
-In this paper, for simplicity of exposition, we shall call a pair of norms in $U$ and $V$ that induce each other as an {\em energy norm pairing}.
-
-\subsection{Discontinuous Petrov-Galerkin methods with the ultra-weak formulation}
-\seclab{abstractUweak}
-
-The naming of the discontinuous Petrov-Galerkin method refers to the fact that the method is a Petrov-Galerkin method, and that the test functions are specified to be discontinuous across element boundaries.
-There is no specification of the regularity of the trial space, and we stress that the idea of DPG is not inherently tied to a single variational formulation \cite{Bui-ThanhDemkowiczGhattas11a}.
-
-In most of the DPG literature, however, the discontinuous Petrov-Galerkin method refers to the combination of the concept of locally computable optimal test functions in Section \secref{optimalTest} with the so-called ``ultra-weak formulation" \cite{DPG1,DPG2,DPG3,DPG4,DPGElas,DBLP:journals/procedia/NiemiCC11}.
-Unlike the previous two sections in which we studied the general equation \eqnref{variationEq} given by abstract bilinear and linear forms, we now consider a concrete instance of \eqnref{variationEq} resulting from an ultra-weak formulation for an abstract first-order system of PDEs $Au = f$.
-Additionally, from this section onwards, we will refer to DPG as the pairing of the ultra-weak variational formulation with the concept of locally computable optimal test functions.
-
-We begin by partitioning the domain of interest $\Omega$ into $\Nel$ non-overlapping elements $K_j, j = 1,\hdots,\Nel$ such that $\Oh = \cup_{j=1}^\Nel K_j$ and $\overline{\Omega} = \overline{\Omega}_h$.
-Here, $h$ is defined as $h= \max_{j\in \LRc{1,\hdots,\Nel}}\text{diam}\LRp{K_j}$.
-We denote the mesh ``skeleton" by $\Gh = \cup_{j=1}^\Nel \partial K_j$; the set of all faces/edges $e$, each of which comes with a normal vector ${n}_e$.
-The internal skeleton is then defined as $\Gamma^0_h = \Gh \setminus \partial \Omega$.
-If a face/edge $e \in \Gh$ is the intersection of $\partial K_i$ and $\partial K_j$, $i \ne j$, we define the following jumps:
-\[
-\jump{v} = \text{sgn} \LRp{{n}^-}v^- + \text{sgn} \LRp{{n}^+}v^+, \quad
-\jump{\tau \cdot n} = {n}^-\cdot \tau^- + {n}^+\cdot\tau^+,
-\]
-where
-\[
-\text{sgn}\LRp{{n}^{\pm}} =
-\left\{
-\begin{array}{ll}
-1 & \text{if } {n}^{\pm} = {n}_e \\
--1 & \text{if } {n}^\pm = -{n}_e
-\end{array}
-\right..
-\]
-For $e$ belonging to the domain boundary $\partial \Omega$, we define
-\[
-\jump{v} = v, \quad
-\jump{\tau \cdot n} = {n}_e\cdot \tau.
-\]
-Note that we allow arbitrariness in assigning ``-'' and ``+'' quantities to the adjacent elements $K_i$ and $K_j$.
-%For the rest of the paper, we will use the same notation for both a function and its trace (if it is well-defined) when there is no ambiguity.
-
-The ultra-weak formulation for $Au = f$ on $\Oh$, ignoring boundary
-conditions for now, reads
-\begin{equation}
-\eqnlab{uweak}
-b\left(\left(u, \widehat{u}\right),v\right) \coloneqq \langle \widehat{u}, \jump{v}
-\rangle_{\Gh} - (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh},
-\end{equation}
-where we have denoted $\LRa{\cdot,\cdot}_{\Gh}$ as the duality
-pairing on $\Gh$, $\LRp{\cdot,\cdot}_{\Oh}$ the $L^2$-inner
-product over $\Oh$, and $A_h^*$ the formal adjoint resulting from
-element-wise integration by parts.  Occasionally, for simplicity in
-writing, we will ignore the subscripts in the duality pairing and
-$L^2$-inner product if they are $\Gh$ and $\Oh$. Both the
-inner product and formal adjoint are understood to be taken
-element-wise. Using the ultra-weak formulation, the regularity
-requirement on solution variable $u$ is relaxed, that is, $u$ is now
-square integrable for the ultra-weak formulation \eqnref{uweak} to be
-meaningful, instead of being (weakly) differentiable.  The trade-off
-is that $u$ does not admit a trace on $\Gh$ even though it did
-originally. Consequently, we need to introduce an additional new
-``trace'' variable $\widehat{u}$ in \eqnref{uweak}, that is defined only on
-$\Gh$.
-
-The energy setting is now clear; namely,
-\[
-u\in L^2\LRp{\Oh} \equiv L^2(\Omega), \quad v\in V=D(A^*_h), \quad
-\widehat{u}\in \gamma(D(A)),
-\]
-where $D(A_h^*)$ denotes the broken graph space corresponding to $A_h^*$,
-and $\gamma(D(A))$ the trace space (assumed to exist) of the graph space of
-operator $A$.
-The first discussion of the well-posedness of DPG with the ultra-weak formulation can be found in \cite{analysisDPG}, where the proof is presented for the Poisson and convection-diffusion equations.
-A more comprehensive discussion of the abstract setting for DPG with the ultra-weak formulation using the graph space, as well as a more general proof of well-posedness, can be consulted in \cite{Bui-ThanhDemkowiczGhattas11b}.
-
-%\subsection{Optimal and quasi-optimal test norms}
-\subsection{Canonical energy norm pairings for ultra-weak formulation}
-
-From the discussion in Section~\secref{energyPair} of energy norm and test norm pairings, we know that specifying either a test norm or trial norm is sufficient to define an energy pairing.
-In this section, we derive and discuss two important energy norm pairings, the first of which begins by specifying the canonical norm in $U$ and inducing a test norm on $V$.
-The second pairing begins instead by specifying the canonical norm on $V$ under the ultra-weak formulation \eqnref{uweak} and inducing an energy norm on the trial space $U$.
-
-We begin first with the canonical norm in $U$. Since $\uh \in \gamma\LRp{D\LRp{A}}$, the standard norm for $\uh$ is
-the so-called minimum energy extension norm defined as
-\begin{equation}
-\eqnlab{MEnorm}
-\|\widehat{u}\| = \inf_{w\in D\LRp{A},
-  \left.w\right|_{\Gh}=\widehat{u}} \|w\|_{D\LRp{A}}.
-\end{equation}
-The canonical norm for the group variable $\LRp{u,\uh}$ is then given by
-\[
-\|\left(u,\widehat{u}\right)\|_U^2 = \|u\|^2_{\L} + \|\widehat{u}\|^2,
-\]
-Applying the Cauchy-Schwarz inequality, we arrive at
-\[
-b\LRp{\LRp{u,\uh},v} \le \nor{\LRp{u,\uh}}_U \nor{v}_{V,U},
-\]
-where
-\[
-\nor{v}_{V,U}^2 = \|A_h^*v\|_{\L}^2
-+\left(\sup_{\widehat{u} \in \gamma\LRp{D\LRp{A}}} \frac{\LRa{ \widehat{u},
-  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2.
-\]
-
-On the other hand, since $v \in D\LRp{A^*_h}$, the canonical norm for
-$v$ is the broken graph norm: 
-\[
-\nor{v}_V^2 =  \|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2.
-\]
-Using the Cauchy-Schwarz inequality again, we obtain
-\[
-b\LRp{\LRp{u,\uh},v} \le \nor{\LRp{u,\uh}}_{U,V} \nor{v}_{V},
-\]
-where
-\begin{equation}
-\eqnlab{inducedQuasi}
-\nor{\LRp{u,\uh}}_{U,V}^2 = \nor{u}_{\L}^2
-+\sup_{v \in D\LRp{A_h^*}} \frac{\LRa{\widehat{u},
-  \jump{v}}_{\Gh}^2}{\|v\|_V^2},
-\end{equation}
-
-Using the framework developed in \cite{Bui-ThanhDemkowiczGhattas11a},
-one can show that both pairs $\LRp{\nor{\LRp{u,\uh}}_U,
-  \nor{v}_{V,U}}$ and $\LRp{\nor{\LRp{u,\uh}}_{U,V}, \nor{v}_{V}}$ are
-energy norm pairings in the sense discussed in Section
-\secref{energyPair}. That is, the canonical norm $\nor{\LRp{u,\uh}}_U$
-in $U$ induces (generates) the norm $\nor{v}_{V,U}$ in $V$, while the
-canonical norm $\nor{v}_V$ in $V$ induces (generates) the energy norm
-$\nor{\LRp{u,\uh}}_{U,V}$ in $U$. In the DPG literature \cite{DPG4}, $\nor{v}_{V,U}$ is known as the {\em optimal test norm},
-while $\nor{v}_{V}$ is known as the {\em quasi-optimal test norm}.
-
-\begin{figure}[!h]
-\centering
-\begin{tabular}{l c c}
-Trial norm & & Test norm \\
-\hline
-$\boxed{\|u\|^2_{\L} + \|\widehat{u}\|^2}$ & $\Longrightarrow$  & $\|A_h^*v\|_{\L}^2
-+\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},
-  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2$ \\
-%\hline
-%Quasi-optimal trial norm & & Canonical test norm \\
-%\hline
-$\nor{u}_{\L}^2+\sup_{v } \left(\frac{\LRa{\widehat{u},
-  \jump{v}}_{\Gh}}{\|v\|_V}\right)^2$ &  $\Longleftarrow$ & $\boxed{\|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2}$
-\end{tabular}
-\caption{A summary of the derivation of test/trial norm pairings; we begin with the boxed norm on either the trial or test space, and induce the norm on the other space through duality.
-The optimal \textit{test} norm is naturally derived by beginning with the canonical norm on the trial space, while the quasi-optimal \textit{trial} norm is derived from beginning with the canonical norm on the test space.}
-\end{figure}
-
-The canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ provides a good
-balance between the standard norms on the field $u$ and the flux
-$\uh$ \cite{DPG4}. As a result, if the induced norm $\nor{v}_{V,U}$ (namely, the
-optimal test norm) is used to compute  optimal test functions in
-\eqnref{optvVar}, the finite element error in the canonical norm is the
-best in the sense of \eqnref{optimalError}.
-
-Unfortunately, the optimal test norm is non-localizable due to the presence of the jump term $\jump{v}$.\footnote{A localizable norm $\nor{v}_{V(\Oh)}$ can be written in the form
-$$\nor{v}_{V(\Oh)} = \sum_{K\in\Oh} \nor{v}_{V(K)},$$ where $\nor{v}_{V(K)}$ is a norm over the element $K$.} Since the jump terms couple elements together, the evaluation of the jump terms requires contributions from all the elements in the mesh.
-Consequently, solving for an optimal test function
-amounts to inverting the Riesz map %, defined on the left sideof \eqnref{optvVar}, 
-over the entire mesh $\Oh$, making the optimal test norm impractical.
-
-On the other hand, the quasi-optimal test norm $\nor{v}_V$, namely the canonical norm in $V$, \textit{is} localizable, and hence practical.
-However, it's worth noting the difference between the induced energy norm $\nor{\LRp{u,\uh}}_{U,V}$ and the canonical norm in $U$; under the induced norm $\nor{\LRp{u,\uh}}_{U,V}$ there is no natural interpretation for the norm in which the error in the flux variable $\uh$ is measured.
-
-Using a variant of the quasi-optimal test norm, numerical results show that the DPG method appears to provide a ``pollution-free" method without phase error for the Helmholtz equation \cite{DPG4}, and analysis of the pollution-free nature of DPG is currently under investigation.
-Similar results have also been obtained in the context of elasticity \cite{DPGElas} and the linear Stokes equations \cite{Camellia}.
-On the theoretical side, the quasi-optimal test norm has been shown to yield a well-posed DPG methodology for the Poisson and convection-diffusion equations \cite{analysisDPG}.
-More recently, this theory has been generalized to show the well-posedness of DPG for the large class of PDEs of Friedrichs' type \cite{Bui-ThanhDemkowiczGhattas11b}.
-
 \section{Model problem and robustness}
@@
 Even when using the penalty method, however, the ratios still remain bounded and close to $1$ for $\epsilon$ varying over two orders of magnitude, as predicted by theory.
-
-\section{Conclusions}
-
-We have presented in this paper the analysis of a non-canonical test norm and its corresponding DPG energy norm for the convection-diffusion equation in the small-diffusion limit.
-Additionally, we have introduced a non-standard inflow boundary condition, and have explored the difference between between this and the standard Dirichlet inflow boundary condition.
-
-Numerical results are presented in order to verify the results derived in this paper.
-However, at least for our model problem, numerical experiments appear to demonstrate results that are stronger than our proofs indicate, delivering solutions for $u$ and $\sigma$ that are extremely close to their best $L^2$ projections.
-
-The theory presented in this paper have been successfully extrapolated to nonlinear singular perturbation problems and systems of equations, and has been applied in context of the Burgers and Navier-Stokes equations.
-These results will be presented in an upcoming paper.
-
-\section{Acknowledgements}
-
-The authors would like to acknowledge the help of Nathan Roberts with software development and Dr Robert Moser for fruitful discussions and perspective.
-Chan and Demkowicz were supported by the Department of Energy [National Nuclear Security Administration] under Award Number [DE-FC52-08NA28615].
-Heuer was supported through the project "Fondecyt-Chile 1110324" and by the "J Tinsley Oden Faculty Research Fellowship" of the Institute of Computational Engineering and Sciences (ICES).
-
-%None yet.  Ideas:
-%\begin{itemize}
-%\item Explanation of choice of boundary condition and why it impacts stability
-%\item Interpretation of weight as allowing diffusion to work on the boundary.  
-%\item Note results have worked for Burgers, and mention the extension to Navier-Stokes
-%\end{itemize}
-
-\bibliographystyle{plain}
-\bibliography{paper}
-
-\input{paper_appendix.tex}
-
-\end{document}

### 2012-06-15 docs/Jesse/Proposal/DPGtheory.tex
put together rough proposal with a few missing sections

--- 2012-06-12 docs/Jesse/Proposal/outline.tex
@@
-\documentclass{report}
-
-\usepackage{array}
-\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
-\usepackage[utf8]{inputenc}
-\usepackage{listings}
-\usepackage{mathtools}
-\usepackage{dsfont}
-\usepackage{pdfpages}
-\usepackage[textsize=footnotesize,color=green]{todonotes}
-\usepackage{algorithm, algorithmic}
-\usepackage{bm}
-\usepackage{tikz}
-\usepackage[normalem]{ulem}
-
-\usepackage{graphicx}
-\usepackage{subfigure}
-\usepackage{color}
-\usepackage{undertilde}
-\usepackage[colorlinks = true, filecolor = red, urlcolor = blue, linkcolor = black]{hyperref}
-\usepackage{pdflscape}
-\usepackage{pifont}
-%\usepackage{fullpage}
-\setlength\textwidth{6in}
-\setlength\textheight{8in}
-\setlength\oddsidemargin{0.25in} % LaTeX adds a default 1in to this!
-\setlength\evensidemargin{0.25in}
-\setlength\topmargin{-0.0in} % LaTeX adds a default 1in to this!
-\setlength\headsep{0in}
-\setlength\headheight{0in}
-\setlength\footskip{1in}
-
-\renewcommand{\topfraction}{0.85}
-\renewcommand{\textfraction}{0.1}
-\renewcommand{\floatpagefraction}{0.75}
-
-\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
-\newcommand{\tensor}[1]{\underline{\vect{#1}}}
-\newcommand{\del}{\triangle}
-\newcommand{\grad}{\nabla}
-\renewcommand{\div}{\grad \cdot}
-\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
-\newcommand{\eip}[1]{a\left( #1 \right)}
-\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
-\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
-
-\newcommand{\circone}{\ding{192}}
-\newcommand{\circtwo}{\ding{193}}
-\newcommand{\circthree}{\ding{194}}
-\newcommand{\circfour}{\ding{195}}
-\newcommand{\circfive}{\ding{196}}
-
-\newcommand{\Reyn}{\rm Re}
-
-\newcommand{\bs}[1]{\boldsymbol{#1}}
-\DeclareMathOperator{\diag}{diag}
-
-\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}
-
-\newcommand{\tablab}[1]{\label{tab:#1}}
-\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
-
-\newcommand{\theolab}[1]{\label{theo:#1}}
-\newcommand{\theoref}[1]{\ref{theo:#1}}
-\newcommand{\eqnlab}[1]{\label{eq:#1}}
-\newcommand{\eqnref}[1]{\eqref{eq:#1}}
-\newcommand{\seclab}[1]{\label{sec:#1}}
-\newcommand{\secref}[1]{\ref{sec:#1}}
-\newcommand{\lemlab}[1]{\label{lem:#1}}
-\newcommand{\lemref}[1]{\ref{lem:#1}}
-
-\newcommand{\mb}[1]{\mathbf{#1}}
-\newcommand{\mbb}[1]{\mathbb{#1}}
-\newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\nor}[1]{\left\| #1 \right\|}
-\newcommand{\snor}[1]{\left| #1 \right|}
-\newcommand{\LRp}[1]{\left( #1 \right)}
-\newcommand{\LRs}[1]{\left[ #1 \right]}
-\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
-\newcommand{\LRc}[1]{\left\{ #1 \right\}}
-\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
-\newcommand{\Grad} {\ensuremath{\nabla}}
-\newcommand{\Div} {\ensuremath{\nabla\cdot}}
-\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
-\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
-\newcommand{\uh}{\widehat{u}}
-\newcommand{\fnh}{\widehat{f}_n}
-\renewcommand{\L}{L^2\LRp{\Omega}}
-\newcommand{\pO}{\partial\Omega}
-\newcommand{\Gh}{\Gamma_h}
-\newcommand{\Gm}{\Gamma_{-}}
-\newcommand{\Gp}{\Gamma_{+}}
-\newcommand{\Go}{\Gamma_0}
-\newcommand{\Oh}{\Omega_h}
-
-\newcommand{\eval}[2][\right]{\relax
-  \ifx#1\right\relax \left.\fi#2#1\rvert}
-
-\def\etal{{\it et al.~}}
-
-\def\arr#1#2#3#4{\left[
-\begin{array}{cc}
-#1 & #2\\
-#3 & #4\\
-\end{array}
-\right]}
-\def\vecttwo#1#2{\left[
-\begin{array}{c}
-#1\\
-#2\\
-\end{array}
-\right]}
-\def\vectthree#1#2#3{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-\end{array}
-\right]}
-\def\vectfour#1#2#3#4{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-#4\\
-\end{array}
-\right]}
-\date{}
-\author{Jesse Chan}
-\title{Proposal outline/notes}
-
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-
-\begin{document}
-
-\tableofcontents
-\maketitle
-
-\chapter{Introduction}
-
-\section{Motivations}
-
-Adaptivity and stability for CFD problems are issues for high Reynolds and Mach numbers. 
-\todo{FINISH}
-
-Address the fact that CFD problems have issues of robustness; introduce reasoning that we will study the model problem of convection-diffusion first to better understand this.
-
-\subsection{Singular perturbation problems and robustness}
-
-Historically, the Galerkin method has been very successfully applied to a broad range of problems in solid mechanics, for which the variational problems resulting from the PDE are symmetric and coercive (positive-definite).
-It is well known that the finite element method produces optimal or near-optimal results for such problems, with the finite element solution matching or coming close to the best approximation of the solution in the finite element space.
-However, standard Bubnov-Galerkin methods tend to perform poorly for the class of PDEs known as singular perturbation problems.
-These problems are often characterized by a parameter that may be either very small or very large in the context of physical problems.
-An additional complication of singular perturbation problems is that very often, in the limiting case of the parameter blowing up or decreasing to zero, the PDE itself will change types (e.g.\ from elliptic to hyperbolic).
-
-A canonical example of a singularly perturbed problem is the convection-diffusion equation on domain $\Omega \in \mathbb{R}^3$,
-\[
-\div \left(\beta u\right) - \epsilon \Delta u = f.
-\]
-The equation represents the change in the scalar quantity $u$, representing the concentration of a quantity in a given medium, taking into account both convective and diffusive effects.
-$\beta \in \mathbb{R}^3$ specifies the direction and magnitude of convection, while the singular perturbation parameter $\epsilon$ represents the diffusivity of the medium.
-In the limit of an inviscid medium as $\epsilon\rightarrow 0$, the equation changes types, from elliptic to hyperbolic, and from second order to first order.
-
-We will illustrate the issues associated with numerical methods for this equation using one dimensional examples.  In 1D, the convection-diffusion equation is
-\begin{align*}
-\beta u'-\epsilon u'' &= f.
-\end{align*}
-For Dirichlet boundary conditions $u(0)=u_0$ and $u(1)= u_1$, the solution can develop sharp boundary layers of width $\epsilon$ near the outflow boundary $x=1$.
-
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.4]{figs/GalerkinOscTight.png}
-\caption{Oscillations in the 1D finite element solution of the convection-diffusion equation for small diffusion.}
-\label{fig:GalerkinOsc}
-\end{figure}
-
-The poor performance of the finite element method for this problem is reflected in the bound on the error in the finite element solution --- under the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}:
-\[
-\|u-u_h\|_\epsilon \leq C \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
-\]
-for $\|u\|_\epsilon^2 \coloneqq \|u\|_{L^2}^2 + \epsilon \|u'\|_{L^2}^2$, with $C$ independent of $\epsilon$. An alternative formulation of the above bound is 
-\[
-\|u-u_h\|_{H^1(0,1)} \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
-\]
-where $C(\epsilon)$ grows as $\epsilon\rightarrow 0$.
-The dependence of the constant $C$ on $\epsilon$ is referred to as a \textit{loss of robustness} --- as the singular perturbation parameter $\epsilon$ decreases, our finite element error is bounded more and more loosely by the best approximation error.
-As a consequence, the finite element solution can diverge significantly from the best finite element approximation of the solution for very small values of $\epsilon$.
-For example, Figure~\ref{fig:GalerkinOsc} shows an example of how, on a coarse mesh, and for small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation with a boundary layer develops spurious oscillations everywhere in the domain, even where the best approximation error is small.
-These oscillations grow in magnitude as $\epsilon \rightarrow 0$, eventually polluting the entire solution.
-
-\section{Goal}
-
-To develop a robust, stable $hp$-adaptive scheme for the steady compressible laminar Navier-Stokes equations in transonic/supersonic regimes.
-\todo{FINISH}
-
-\section{Literature review}
-
-For the past half-century, problems in computational fluid dynamics (CFD) have been solved using a multitude of methods, many of which are physically motivated, and thus applicable only to a small number of problems and geometries.
-We consider more general methods, whose framework is applicable to different problems in CFD; however, our specific focus will be on the nonlinear shock problems of compressible aerodynamics.
-Broadly speaking, the most popular general methods include (in historical order) finite difference methods, finite volume methods, and finite element methods.
-
-\subsection{Finite difference and finite volume methods}
-
-For linear problems, finite difference (FD) methods approximate derivatives based on interpolation of pointwise values of a function.
-FD methods were popularized first by Lax, who introduced the concepts of the monotone scheme and numerical flux.
-For the conservation laws governing compressible aerodynamics, FD methods approximated the conservation law, using some numerical flux to reconstruct approximations to the derivative at a point.
-Finite volume (FV) methods are similar to finite difference methods, but approximate the integral version of a conservation law as opposed to the differential form.
-FD and FV have roughly the same computational cost/complexity; however, the advantage of FV methods over FD is that FV methods can be used on a much larger class of discretizations than FD methods, which require uniform or smooth meshes.
-
-For nonlinear shock problems, the solution often exhibits sharp gradients or discontinuities, around which the solution would develop spurious Gibbs-type oscillations.
-Several ideas were introduced to deal with oscillations in the solution near a sharp gradient or shock: artificial diffusion, total variation diminishing (TVD) schemes, and slope limiters.
-However, each method had its drawback, either in terms of loss of accuracy, dimensional limitations, or problem-specific parameters to be tuned \cite{Shu:Lectures}.
-Harten, Enquist, Osher and Chakravarthy introduced the essentially non-oscillatory (ENO) scheme in 1987 \cite{ENO}, which was improved upon with the weighted essentially non-oscillatory (WENO) scheme in \cite{WENO}.
-WENO remains a popular choice today for both finite volume and finite difference schemes.
-Most of these methods can be interpreted as adding some specific artificial diffusion to the given numerical scheme.
-We refer to such schemes as \emph{modified equation} methods, as the exact solution no longer satisfies the discrete system due to the presence of additional artificial diffusion.
-
-Historically, finite volumes and finite difference methods have been the numerical discretizations of choice for CFD applications; the simplicity of implementation of the finite difference method allows for quick turnaround time, and the finite volume method is appealing due to its locally conservative nature and flexibility.
-More recently, the finite element (FE) method has gained popularity as a discretization method for CFD applications for its stability properties and rigorous mathematical foundations.
-Early pioneers of the finite element method for CFD included Zienkiewicz, Oden, Karniadakis, and Hughes \cite{ChungCFDBook}.
-
-\subsection{Stabilized finite element methods}
-
-The finite element/Galerkin method has been widely utilized in engineering to solve partial differential equations governing the behavior of physical phenomena in engineering problems.
-The method relates the solution of a partial differential equation (PDE) to the solution of a corresponding variational problem.
-The finite element method itself provides several advantages --- a framework for systematic mathematical analysis of the behavior of the method, weaker regularity constraints on the solution than implied by the strong form of the equations, and applicability to very general physical domains and geometries for arbitrary orders of approximation.
-
-Traditionally, instability/loss of robustness in finite element methods has been dealt with using residual-based stabilization techniques.
-Given some variational form, the problem is modified by adding to the bilinear form the strong form of the residual, weighted by a test function and scaled by a stabilization constant $\tau$.
-The most well-known example of this technique is the streamline-upwind Petrov-Galerkin (SUPG) method, which is a stabilized FE method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.
-SUPG stabilization not only removes the spurious oscillations from the finite element solution of the convection-diffusion equation, but delivers the best finite element approximation in the $H^1$ norm.
-
-\subsubsection{SUPG}
-
-The Streamline Upwind Petrov Galerkin (SUPG) method is a stabilization method for $H^1$-conforming finite elements, the idea of which was originally motivated by artificial diffusion techniques in finite differences.
-In particular, for the homogeneous 1D convection-diffusion equation, it is possible to recover, under a finite difference method, the exact solution at nodal points by adding an ``exact" artificial diffusion based on the mesh size $h$ and the magnitudes of the convection $\beta$ and the viscosity $\epsilon$.
-
-The idea of ``exact" artificial viscosity was adapted to finite elements not through the direct modification of the equations, but through the test functions and weighting of the residual.
-In particular, finite element and Galerkin methods are often referred to as ``weighted residual" methods, since the starting point of both is to multiply the residual by a particular test, or weighting, function.
-Standard Galerkin methods, known as Bubnov-Galerkin methods, simply choose these weighting functions to be the same as the the basis functions used to approximate the solution.
-A Petrov-Galerkin method refers to any Galerkin method other than a classical Bubnov-Galerkin method.
-
-We will introduce the SUPG method at an abstract level for illustrative purposes only.
-Further details and perspectives on the SUPG method can be found in \cite{SUPG}, as well as in an upcoming book by Hughes.
-The convection-diffusion equation can be written as follows:
-\[
-Lu = \left(L_{\rm adv} + L_{\rm diff} \right) u = f,
-\]
-where $L_{\rm adv}u \coloneqq \div \left(\beta u\right)$ is the first order advective operator, and $L_{\rm diff}u \coloneqq \epsilon \Delta u$ is the second-order diffusive operator (then, roughly speaking, $L_{\rm diff} u = 0$).
-Let us assume $u$ to be a linear combination of piecewise-linear basis functions $\phi_i, i = 0,\ldots,N$.
-The SUPG method is then to solve
-\[
-\int_\Omega L u v + \int_\Omega \tau \left(L_{\rm adv}v\right)\left( L u - f\right) = \int_\Omega f v 
-\]
-for where $\tau$ is the SUPG parameter.
-For uniform meshes in 1D, $\tau$ is chosen such that, for $f=0$, the matrix system resulting from SUPG is exactly equal to the finite difference system under ``exact" artificial diffusion.
-However, unlike the artificial diffusion method, for $f\neq 0$, the SUPG method still delivers optimal stabilization.
-In fact, the SUPG finite element solution in 1D is nothing less than the nodal interpolant and the best $H^1$ approximation of the exact solution, as seen in Figure~\ref{fig:SUPG}.
-
-\begin{figure}[!h]
-\centering
-\subfigure[SUPG and standard FEM solutions]{\includegraphics[scale=.43]{figs/SUPG.png}}
-\subfigure[SUPG test function]{\includegraphics[scale=.22]{figs/SUPGtest.png}}
-\caption{SUPG and standard Bubnov-Galerkin solutions to the 1D convection-dominated diffusion equation, and a modified SUPG test function (in black) corresponding to a linear basis ``hat" function (in red).
-The upwind portion of the element is emphasized, while the downwind portion is decreased.
-The magnitude of the discontinuity between the upwind and downwind portion is controlled by the intrinsic timescale parameter $\tau$.
-}
-\label{fig:SUPG}
-\end{figure}
-
-The idea of emphasizing the upwind portion of a test function is an old idea, introduced in 1977 by Zienkiewicz et al.\ in \cite{zienkUpwind}.
-However, the precise amount of upwinding,\footnote{Insufficient upwinding results in a method which still exhibits oscillations and instabilities, while excessive upwinding leads to an overly diffusive method.} as well as the connection to residual-based stabilization methods, were novel to SUPG.
-
-The method can be made to ``work" for $p>1$, but the results are not as strong as for linear elements, and there is no clear generalization of SUPG to higher order elements.
-Additionally, the stabilization properties of SUPG are weaker in higher dimensions, and the SUPG solution is no longer the $H^1$ best approximation for 2D and 3D problems \todo{find citation}.
-Despite these caveats, SUPG is still the most popular stabilization method of choice for convection-diffusion type problems, in both academic and industry applications.
-
-An important feature of SUPG and other residual-based stabilization techniques that separates it from modified equation methods is the idea of \textit{consistency} --- by adding stabilization terms based on the residual, the exact solution still satisfies the same variational problem (i.e.\ Galerkin orthogonality still holds).
-Contrast this to the artificial diffusion methods in finite difference and finite volume methods, where a specific amount of additional viscosity is added based on the magnitude of the convection and diffusion parameters: unlike residual-based stabilization schemes, the exact solution to the original equation no longer satisfies the new stabilized formulation.
-
-This addition of residual-based stabilization terms can be interpreted as a modification of the test functions as well.  For SUPG, the formulation can equivalently be written as
-\[
-\int_\Omega\left( Lu-f\right) v_i = \int_\Omega f v_i, \quad i = 0,\ldots,N
-\]
-where $v_i$ is defined as
-\[
-v_i = \phi_i(x) + \tau L_{\rm adv} \phi_i.  
-\]
-In other words, the test function $v_i$ is a perturbation of the basis function $\phi_i$ by a scaled advective operator applied to $\phi_i$.
-For a linear $C^0$ basis function (the ``hat" function), this naturally leads to a bias in the upwind or streamline direction of the flow $\beta$, as seen in Figure~\ref{fig:SUPG}.
-
-An important connection can now be made --- stabilization can be achieved by changing the test space for a given problem.
-We will discuss in Section~\secref{optimalTest} approaching the idea of stabilization through the construction of \textit{optimal test functions} to achieve optimal approximation properties.
-
-\subsubsection{DG methods}
-
-Discontinuous Galerkin (DG) methods form a subclass of FEM; first introduced by Reed and Hill in \cite{Reed:73}, these methods were later analyzed by Cockburn and Shu \cite{CockburnShu:DG} and have rapidly gained popularity for CFD problems.
-Rather than having a continuous basis where the basis function support spans several element cells, DG opts instead for a discontinuous, piecewise polynomial basis, where, like FV schemes, a numerical flux facilitates communication between discontinuities (unlike FV methods, however, there is no need for a reconstruction step).
-Advantages of DG methods include the local conservation property, easily modified local orders of approximation, easy adaptivity in both $h$ and $p$, and efficient parallelizability.
-
-An additional reason for the popularity of DG methods is that they can be interpreted as stabilized FE methods through appropriate choices of the numerical flux \todo{add Brezzi citation}.
-We will illustrate this with the pure convection equation in 1D.
-
-Local conservation: in 1D, numerical solution at outflow is exact.
-
-\todo{Add 1D description and diagrams (Hughes book) of DG formulation for convection with upwind flux.}
-
-For example, for the pure convection problem, the solution has only regularity in the streamline direction, but is only $L^2$ in the crosswind direction.
-As a consequence, the boundary trace of the solution is defined only in the direction of convection.
-The upwind DG method addresses the above issue by choosing the numerical flux to be the upwind flux; in this case, the DG numerical flux can be viewed as imparting additional regularity than is present in the solution \cite{DPG1,DPG3}.
-
-A more recent development in DG methods is the idea of \emph{hybridized} DG (HDG), introduced by Gopalakrishnan and Lazarov \cite{hybridDG}.
-The hybridized DG framework addresses several criticisms of common DG methods (globally coupled degrees of freedom, complicated/inefficient implementation procedures, suboptimal convergence of approximate fluxes) by identifying degrees of freedom with support only on element edges.
-Neighboring elements are coupled together only through these degrees of freedom, which can be interpreted as Lagrange multipliers enforcing weak continuity of the trial space.
-Additionally, HDG methods \todo{add bit about numerical fluxes still used, stabilization param}
-
-\subsubsection{Optimization/NL solvers}
-
-Reference (MIT, Fidkowski)
-
-\todo{Find more nonlinear solvers}
-
-\section{Scope}
-
-This proposal will
-\begin{enumerate}
-\item Introduce DPG
-\item Cover the problem of robustness for model problems
-\item Extend results/formulations to nonlinear problems
-\item Discuss proposed work
-\end{enumerate}
-
-\chapter{Range of CFD problems}
-
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.45]{figs/CFD_tree.pdf}
-\caption{A diagram of common CFD problems and their simplifying assumptions.}
-\end{figure}
-
-\begin{itemize}
-\item Discuss full compressible Navier-Stokes with boundary layers
-\item Discuss full compressible Navier-Stokes without boundary layers, connect to Euler (mention Dr Young and Boeing and the IBL connection \cite{BoeingDrela})
-\item Discuss model problems
-\end{itemize}
-
-\chapter{Discontinuous Petrov-Galerkin: a minimum residual method for linear problems}
-
 The Discontinuous Petrov-Galerkin (DPG) method of Demkowicz and Gopalakrishnan was first formulated in \cite{DPG1} for the pure convection problem.
@@
 More recently, this theory has been generalized to show the well-posedness of DPG for the large class of PDEs of Friedrichs' type \cite{Bui-ThanhDemkowiczGhattas11b}.
-
-\chapter{A robust DPG method for convection-dominated diffusion}
-
-\begin{itemize}
-\item Describe mathematically the issue with standard Galerkin.
-\item Give proofs of robustness and numerical results (from paper)\cite{ChanHeuerBui-ThanhDemkowicz12}
-\end{itemize}
-
-\chapter{DPG for nonlinear problems}
-
-\begin{itemize}
-\item Introduce nonlinear residual to measure convergence, DPG formulation for nonlinear problems. Briefly discuss solution strategies (pseudo-timestep/damped Newton). 
-\item Formulate DPG for Burgers' equation as an example, show results
-\item Show DPG applied to Navier-Stokes at a broad level, with results
-\end{itemize}
-
-\section{Summary: completed/propsed work}
-
-\subsection{Area A}
-
-\begin{itemize}
-\item{\textbf{Completed: }} Prove robustness of DPG method for the scalar convection-diffusion problem
-\item Attempt analysis of the linearized Navier-Stokes system
-\end{itemize}
-
-\subsection{Area B}
-
-\begin{itemize}
-\item{\textbf{Completed: }} Collaborative work with Nathan Roberts on the higher order parallel adaptive DPG code Camellia.
-\item Nonlinear DPG - Hessian adjoint trick
-\item Adaptivity: anisotropic refinements and $hp$-schemes.
-\item Distributed static condensation
-\end{itemize}
-
-\subsection{Area C}
-
-\begin{itemize}
-\item{\textbf{Completed: }} Convection-dominated diffusion, Burgers, and Navier-Stokes. 
-\item Higher Reynolds number, ramp problem, Gaussian bump, airfoil.
-\item Euler with NS regularization?
-\end{itemize}
-
-\bibliographystyle{plain}
-\bibliography{CFD_intro,DPG_old,paper,NS}
-
-\end{document}

### 2012-06-15 docs/Jesse/Proposal/NSNotes.tex
put together rough proposal with a few missing sections

--- 2012-06-06 docs/NavierStokes/notes.tex
@@
-\documentclass{article}
-
-\usepackage{array}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage{subfigure}
-\usepackage{color}
-\usepackage{undertilde}
-\usepackage[colorlinks = true, filecolor = red, urlcolor = blue, linkcolor = black]{hyperref}
-\usepackage{pdflscape}
-\usepackage{pifont}
-%\usepackage{fullpage}
-\setlength\textwidth{6in}
-\setlength\textheight{8in}
-\setlength\oddsidemargin{0.25in} % LaTeX adds a default 1in to this!
-\setlength\evensidemargin{0.25in}
-\setlength\topmargin{-0.0in} % LaTeX adds a default 1in to this!
-\setlength\headsep{0in}
-\setlength\headheight{0in}
-\setlength\footskip{1in}
-
-\renewcommand{\topfraction}{0.85}
-\renewcommand{\textfraction}{0.1}
-\renewcommand{\floatpagefraction}{0.75}
-
-\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
-\newcommand{\tensor}[1]{\underline{\vect{#1}}}
-\newcommand{\del}{\triangle}
-\newcommand{\grad}{\nabla}
-\renewcommand{\div}{\grad \cdot}
-\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
-\newcommand{\eip}[1]{a\left( #1 \right)}
-\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
-\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
-\newcommand{\nor}[1]{\left\| #1 \right\|}
-
-\newcommand{\circone}{\ding{192}}
-\newcommand{\circtwo}{\ding{193}}
-\newcommand{\circthree}{\ding{194}}
-\newcommand{\circfour}{\ding{195}}
-\newcommand{\circfive}{\ding{196}}
-
-\newcommand{\Reyn}{\rm Re}
-\newcommand{\Gh}{\Gamma_h}
-\newcommand{\Oh}{\Omega_h}
-\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
-\newcommand{\LRs}[1]{\left[ #1 \right]}
-\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
-
-\def\arr#1#2#3#4{\left[
-\begin{array}{cc}
-#1 & #2\\
-#3 & #4\\
-\end{array}
-\right]}
-\def\vecttwo#1#2{\left[
-\begin{array}{c}
-#1\\
-#2\\
-\end{array}
-\right]}
-\def\vectthree#1#2#3{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-\end{array}
-\right]}
-\def\vectfour#1#2#3#4{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-#4\\
-\end{array}
-\right]}
-\date{}
-\author{Jesse Chan}
-\title{NS notes}
-
-\begin{document}
-
 \section{The compressible Navier-Stokes equations}
@@
 
-\subsection{Mass equation}
+\begin{itemize}
+\item \textbf{Mass equation}
 \[
@@
 \end{align*}
-\subsection{Energy equation}
+
+\item \textbf{Energy equation}
 Let $\boldsymbol \sigma$ be a tensor whose $ij$th term is $\sigma_{ij}$.  
@@
 \]
-\subsection{Newtonian fluid laws}
+
+\item \textbf{Newtonian fluid laws}
 We represent $\boldsymbol\sigma$ using the Newtonian fluid law
@@
 
-\subsection{Fourier's heat conduction law}
+\item \textbf{Fourier's heat conduction law}
 We assume Fourier's law 
@@
 
-\subsection{Classical and momentum variables}
+\end{itemize}
 
-In classical variables, our system of equations is now
+To summarize, our system of equations in the classical variables is now
 \begin{align*}
@@
 
-The test norm adopted for convection-diffusion in \cite{DPGrobustness,DPGrobustness2} is defined elementwise on $K$ as
+The test norm adopted for convection-diffusion in Section~\ref{blah}\todo{get section} and in \cite{DPGrobustness2} is defined elementwise on $K$ as
 \[
@@
 \subfigure{\includegraphics[scale=.5]{figs/TRe1000.pdf}}
-\caption{Solutions after four refinements for $\rho$, $u_1$, $u_2$, and $T$ and $\Reyn = 500$.}
+\caption{Solutions after four refinements for $\rho$, $u_1$, $u_2$, and $T$ and $\Reyn = 1000$.}
 \label{fig:Re500}
@@
 \end{figure}
-
-\bibliographystyle{plain}
-\bibliography{notes}
-
-\end{document}

### 2012-06-15 docs/Jesse/Proposal/paper_appendix.tex
put together rough proposal with a few missing sections

--- 2012-04-10 docs/NewBCRobustness_paper/paper.tex
@@
-%\documentclass[11pt]{article}
-\documentclass[11pt,onecolumn]{scrartcl}
-%\documentclass[11pt,onecolumn,fleqn]{scrartcl}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
-\usepackage[top=2cm,bottom=3cm,left=2.5cm,right=2cm]{geometry}
-\usepackage{amssymb}
-\usepackage{listings}
-\usepackage{array}
-\usepackage{mathtools}
-\usepackage{dsfont}
-\usepackage{graphicx}
-\usepackage{pdfpages}
-%\usepackage[textsize=footnotesize,color=green]{todonotes}
-\usepackage{algorithm, algorithmic}
-\usepackage{tikz}
-\usepackage{subfigure}
-%\usetikzlibrary{%
-%    decorations.pathreplacing,%
-%    decorations.pathmorphing%
-%}
-\usepackage[normalem]{ulem}
-
-\newcommand{\bs}[1]{\boldsymbol{#1}}
-\DeclareMathOperator{\diag}{diag}
-
-\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}
-
-\newcommand{\tablab}[1]{\label{tab:#1}}
-\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
-
-\newcommand{\theolab}[1]{\label{theo:#1}}
-\newcommand{\theoref}[1]{\ref{theo:#1}}
-\newcommand{\eqnlab}[1]{\label{eq:#1}}
-\newcommand{\eqnref}[1]{\eqref{eq:#1}}
-\newcommand{\seclab}[1]{\label{sec:#1}}
-\newcommand{\secref}[1]{\ref{sec:#1}}
-\newcommand{\lemlab}[1]{\label{lem:#1}}
-\newcommand{\lemref}[1]{\ref{lem:#1}}
-
-\newcommand{\mb}[1]{\mathbf{#1}}
-\newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\nor}[1]{\left\| #1 \right\|}
-\newcommand{\snor}[1]{\left| #1 \right|}
-\newcommand{\LRp}[1]{\left( #1 \right)}
-\newcommand{\LRs}[1]{\left[ #1 \right]}
-\newcommand{\LRa}[1]{\left< #1 \right>}
-\newcommand{\LRc}[1]{\left\{ #1 \right\}}
-\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
-\newcommand{\Grad} {\ensuremath{\nabla}}
-\newcommand{\Div} {\ensuremath{\nabla\cdot}}
-
-\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
-\newcommand{\tensor}[1]{\underline{\vect{#1}}}
-\newcommand{\del}{\Delta}
-\newcommand{\grad}{\nabla}
-\newcommand{\curl}{\grad \times}
-\renewcommand{\div}{\grad \cdot}
-\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
-\newcommand{\eip}[1]{a\left( #1 \right)}
-\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
-\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
-
-\newcommand{\circone}{\ding{192}}
-\newcommand{\circtwo}{\ding{193}}
-\newcommand{\circthree}{\ding{194}}
-\newcommand{\circfour}{\ding{195}}
-\newcommand{\circfive}{\ding{196}}
-
-\def\arr#1#2#3#4{\left[
-\begin{array}{cc}
-#1 & #2\\
-#3 & #4\\
-\end{array}
-\right]}
-\def\vecttwo#1#2{\left[
-\begin{array}{c}
-#1\\
-#2\\
-\end{array}
-\right]}
-\def\vectthree#1#2#3{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-\end{array}
-\right]}
-\def\vectfour#1#2#3#4{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-#4\\
-\end{array}
-\right]}
-
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-
-\newcommand{\G} {\Gamma}
-\newcommand{\Gin} {\Gamma_{in}}
-\newcommand{\Gout} {\Gamma_{out}}
-
-\author{Tan Bui-Thanh \and Jesse Chan \and Leszek Demkowicz \and Norbert Heuer}
-\title{$\epsilon$-explicit analysis of DPG for convection-dominated diffusion}
-\date{}
-\begin{document}
-
-\tableofcontents
-\maketitle
-
-\section{Introduction}
-
-\subsection{Singular perturbation problems and robustness}
-
-The finite element/Galerkin method has been widely utilized in engineering to solve partial differential equations related to simulation of solid mechanics problems.
-For many problems in engineering, the bilinear forms resulting from these partial differential equations are symmetric and coercive (positive-definite), and it is well known that the finite element method produces near-optimal results for such problems.
-However, standard Bubnov-Galerkin methods tend to perform poorly for the class of partial-differential equations known as singularly perturbed problems.
-Singularly perturbed problems are problems where a given parameter may be either very small or very large in the context of physical problems.
-An additional complication of singularly perturbed problems is that very often, in the limiting case of the parameter blowing up or decreasing to zero, the partial differential equation itself will change types (i.e from parabolic to hyperbolic).
-A canonical example is the convection-diffusion equation with Dirichlet boundary conditions.
-
-\subsubsection{Convection-diffusion}
-
-In 1D, the convection-diffusion equation is
-\begin{align*}
-u'-\epsilon u'' &= f
-\end{align*}
-The equation represents the change in the concentration of some quantity $u$ in some medium from both convective and diffusive effects.
-The parameter $\epsilon$ represents the diffusivity, and in the limit of an inviscid medium as $\epsilon\rightarrow 0$, the partial differential equation changes types, going from a parabolic to a hyperbolic equation.
-For Dirichlet boundary conditions $u(0)=u_0$ and $u(1)= u_1$, the solution can develop sharp boundary layers of order $\epsilon$ near the outflow.
-
-The finite element method has notoriously performed poorly for both this example, and for many other singularly perturbed problems.
-This poor performance is captured by the error bound for the finite element method applied to convection-diffusion equations - for the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}
-\[
-\|u-u_h\|_\epsilon \leq C \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
-\]
-for $C$ independent of $\epsilon$, and for $\|u\|_\epsilon \coloneqq \|u\|_{L^2} + \epsilon \|u'\|_{L^2}$. An alternative formulation of the above bound is 
-\[
-\|u-u_h\|_{H^1(0,1)} \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
-\]
-where $C(\epsilon)$ grows as $\epsilon\rightarrow 0$.
-
-The dependence on $\epsilon$ in the bound of our finite element error by best approximation error is referred to as a \textit{loss of robustness}.
-As our singular perturbation parameter changes, our finite element error is bounded more and more loosely by the best approximation error, allowing for more and more error in the finite element solution for as $\epsilon$ shrinks.
-
-Intuitively, a non-robustness method will perform increasingly worse as $\epsilon$ decreases, independently of the best approximation error.
-For example, for a coarse mesh and small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation with a boundary layer develops spurious oscillations of magnitude $O(\epsilon^{-1})$ everywhere in the domain, even where best approximation error is small.
-
-\subsubsection{Wave propagation}
-
-Another example of a singular perturbation problem which experiences loss of robustness is high frequency wave propagation problems, in which the singular perturbation parameter is the wavenumber, $k\rightarrow \infty$.
-The loss of robustness in this case manifests as ``pollution" error, a phenomenon where the finite element solution degrades over many wavelengths for high wavenumbers (commonly manifesting as a phase error between the FE solution and the exact solution).
-
-\subsubsection{Stabilization terms}
-
-Traditionally, instability/loss of robustness has been dealt with using residual-based stabilization.
-Given some variational form, the problem is modified by adding to the bilinear form a factor of the residual, scaled by a stabilization constant $\tau$.
-The most well-known example of this is the streamline-upwind Petrov-Galerkin method, which is a stabilized method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.
-An important difference between residual-based stabilization techniques and other stabilizations is the idea of \textit{consistency} - by adding stabilization terms based on the residual, the exact solution still satisfies the same variational problem (i.e Galerkin orthogonality still holds)\footnote{Contrast this to an artificial diffusion method, where a specific amount of additional viscosity is added based on the interplay between the convection and diffusion terms.
-The exact solution to the original equation no longer satisfies the new stabilized formulation.}.
-
-The addition of residual-based stabilization terms can also be interpreted as a modification of the test functions - in other words, stabilization can be achieved by changing the test space for a given problem.
-This idea can be generalized under the idea of \textit{optimal test functions}.
-
-%\textcolor{red}{add bit about SUPG/residual-based stabilization terms and test functions}
-
-\subsection{Optimal test functions}
-The idea of optimal test functions was introduced by Demkowicz and Gopalakrishnan in \cite{DPG2}.
-Conceptually, these optimal test functions are the natural result of the minimumization of a residual corresponding the operator form of a variational equation.
-The connection between stabilization and least squares/minimum residual methods has been observed previously; however, the concept of optimal test functions presents the idea from a different perspective.
-
-Given Hilbert spaces $U$ and $V$ and a variational problem $b(u,v) = l(v)$, $\forall u\in U, v\in V$, we can identify $B:U\rightarrow V'$ and $l \in V'$ 
-\[
-\left.\begin{array}{c}
-b(u_h,v) = \langle Bu_h,v\rangle  \\
-l(v) = \langle l,v\rangle
-\end{array}\right\}
-\Longleftrightarrow Bu_h = l
-\]
-We seek the minimization of the residual in the dual norm
-\[
-\min_{u_h\in U_h} J(u_h) = \frac{1}{2}\|Bu_h-l\|_{V'}^2 = \frac{1}{2} \sup_{v\in V} \| b(u_h,v)-l(v)\|_{V}^2
-\]
-Recall $R_V$, the Riesz operator $\langle R_V v,\delta v\rangle = (v, \delta v)_V$ identifying elements of Hilbert space with elements of the dual.
-As $R_V$ and its inverse are isometries, $\|f\|_{V'} = \|R_V^{-1} f\|_V$, and
-\[
-\min_{u_h\in U_h} J(u_h) = \frac{1}{2}\|Bu_h-l\|_{V'}^2 =  \frac{1}{2}\|R_V^{-1}(Bu_h-l)\|_V^2
-\]
-First order optimality conditions require the Gateux derivative to be zero in all directions $u_h \in U_h$.  
-\begin{align*}
-\left(R_V^{-1}(Bu_h-l),R_V^{-1}B\delta u_h\right)_V &= 0, \quad \forall \delta u_h \in U_h \\
-\rightarrow \langle Bu_h-l, v_h\rangle &= 0, \quad v_h = R_V^{-1}B\delta u_h
-\end{align*}
-which returns a standard variational equation $b(u_h,v_h) - l(v_h) = 0$, for the specific choice of test functions $v_h = R_V^{-1}B\delta u_h$.
-We identify the \textit{trial-to-test} operator $T = R_V^{-1}B$, which maps a trial function $u_h$ to its corresponding \textit{optimal} test function $v_h = Tu_h$.
-These test functions can be determined by solving the auxiliary variational problem
-\[
-\left(v_h,\delta v\right)_V = b(u_h,\delta v)
-\]
-This concept is not a new one; the idea of optimal testing is a classical one (see \textcolor{red}{find citation}).
-However, for standard conforming finite elements, test functions are continuous over the entire domain, and solving the above variational problem for optimal test functions is a global operation that must be performed once for every approximating function in the trial space, rendering the method impractical.
-The breakthrough came through the development of discontinous Galerkin (DG) methods; specifically, the use of discontinuous test spaces reduces the problem of determining optimal test functions to a local problem that can be solved in an element-by-element fashion.
-
-In practice, this variational problem is difficult to solve exactly, and the solution is instead is approximately using the standard Bubnov-Galerkin method and an ``enriched" subspace of $V$ such that $\dim(V) > \dim(U)$.
-We assume the corresponding error in approximation of the optimal test functions is negligible for the scope of this paper.
-Further work concerning the effect of approximation error in the computation of optimal test functions can be found in \cite{practicalDPG}.
-
-Under the standard conditions for well-posedness of the continuous variational problem, the discrete DPG method delivers the best approximation error in the ``energy norm" 
-\[
-\|u\|_E = \sup \frac{b(u,v)}{\|v\|_V}.
-\]
-The above norm can be determined via $\|u\|_E = \|v_u\|_V$, where $v_u$ solves
-\[
-(v_u,\delta v)_V = b(u,\delta v), \quad \forall v \in V
-\]
-Due to the isometry of the Riesz map, this is equivalent to measuring the norm of the functional $b(u,v) = l_u(v)\in V'$ in the dual norm.
-An additional consequence of adopting such an energy norm is that, without knowing the exact solution, the actual energy error $\|u-u_h\|_E$ is computable through $\|e_h\|_V$, where
-\[
-\left(e_h,\delta v\right)_V = b(u-u_h,\delta v) = b(u_h,\delta v)-l(\delta v)
-\]
-This is simply a consequence of the least-squares nature of DPG; the energy error is simply the measure of the residual in the proper norm - the dual norm on $V$.
-
-\subsection{Variational form}
-
-The discontinuous Petrov-Galerkin (DPG) method is the pairing of the concept of locally computable optimal test functions with the so-called ``ultra-weak formulation".
-For a given operator equation in strong form $Au = f$, the ultra-weak formulation is
-\[
-b\left(\left(\widehat{u},u\right),v\right) - l(v) = \langle \widehat{u}, [v] \rangle - (u,A^*v) - (f,v) = 0
-\]
-where $A^*$ is the formal adjoint resulting from integration by parts,
-and $[v]$ is the jump of the test function $v$ across element
-boundaries.  Both the inner product and formal adjoint are understood
-in an element-wise fashion. Under the ultra-weak formulation, the
-regularity requirement on each solution variable is relaxed through
-integration by parts.  Moreover, to maintain conformity while seeking
-an $L^2$ setting on interior ``field" variables, boundary terms are
-identified as additional new unknowns.  The result is a DG
-method with locally supported optimal test functions, where both fluxes and traces are hybridized.  The energy setting is
-\begin{align*}
-u&\in L^2(\Omega)\\
-v&\in V=D(A^*) \\
-\widehat{u}&\in T(D(A))
-\end{align*}
-where $D(A^*)$ is the domain of the formal adjoint $A^*$, and $T(D(A))$ is the trace space of the domain of the operator $A$ in its strong form.
-A more comprehensive discussion of the abstract setting of DPG, as well as a proof of well-posedness, is developed using the graph norm in \cite{DPGFriedrichs}.
-
-\subsection{Induced norms}
-
-Up to now, we have neglected discussion of the proper choice of inner product/norm on the space $V$.  The energy norm in which DPG is optimal 
-\[
-\|u\|_E = \sup_{v \in V\setminus \{0\}} \frac{b(u,v)}{\|v\|_{V,E}}.
-\]
-depends heavily on our choice of norm on the test space $\|v\|_{V,E}$.
-
-An important relationship is the duality of the energy norm and test norm; under the assumption of injectivity of the adjoint of our variational 	operator $B$, for any choice of energy norm on $U$, the test norm $\|v\|_V$ inducing it can be recovered via duality
-\begin{align}
-\| v \|_{V,U} = \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_U} \label{norm_duality}
-\end{align}
-If the solution is in $U$, then choosing $\|v\|=\|v\|_{V,U}$ implies $\|u\|_E = \|u\|_U$.
-The proof is simple; we have by definition that $b(u,v) \leq \|u\|_U\|v\|_{V,U}$.
-The reverse $b(u,v) \leq \|u\|_U\|v\|_{V,U}$ is proved by
-\[
-\inf_{u\in U} \frac{\|u\|_E}{\|u\|_U} = \inf_{u\in U} \sup_{v\in V}\frac{b(u,v)}{\|v\|_{V,U}\|u\|_U} = \inf_{v\in V} \sup_{u\in U}\frac{b(u,v)}{\|v\|_{V,U}\|u\|_U} = \inf_{v\in V} \frac{\|v\|_{V,U}}{\|v\|_{V,U}} = 1
-\]
-where we're able to switch the order of $\inf$ and $\sup$ due to the injectivity of $B$ (see  \cite{BabuskaEquivBrezzi}).
-
-As a consequence of \eqref{norm_duality}, given two norms on $U$, $\|\cdot\|_{U_1}$ and $\|\cdot\|_{U,2}$, if $\|u\|_{U_1} \leq \|u\|_{U,2}$, we have the equivalent statement
-\begin{align*}
-\| v \|_{V,U_1} = \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_{U_1}} \geq  \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_{U,2}} = \| v \|_{V,U,2}
-\end{align*}
-In other words, showing an inequality between two norms on $U$ is equivalent to showing the reverse inequality between the respective induced norms on $V$.
-
-\subsection{Optimal and quasi-optimal test norms}
-
-The duality between test norm and variational form holds for any particular variational form, though it is often difficult to determine analytically the form of $\|v\|_{V,U}$.
-Whether a particular choice of norm on $V$ norm is ``good" or not is problem-dependent; however, for the DPG ultra-weak formulation, there is an important canonical test norm that is induced by a specific norm on $U$.
-
-Define the norm on $U$
-\[
-\|u\| = C_1\|u\|_{L^2} + C_2\|\widehat{u}\|
-\]
-where the norm on $\widehat{u}$ is taken to be the minimum energy extension norm
-\[
-\|\widehat{u}\| = \inf_{w\in V, \left.w\right|_{\Gamma_h}=\widehat{u}} \|w\|_V
-\]
-Then, the induced test norm is 
-\begin{align*}
-\|v\| &= \sup_{u,\widehat{u}} \frac{\langle \widehat{u}, [v] \rangle - (u,A^*v)}{C_1\|u\|_{L^2} + C_2\|\widehat{u}\|} \\
-&\leq \frac{1}{C_1}\sup_{u} \frac{(u,A^*v)}{\|u\|_{L^2}} + \frac{1}{C_2}\sup_{\widehat{u}} \frac{\langle \widehat{u}, [v] \rangle}{\|\widehat{u}\|}\\
-&= \frac{1}{C_1}\|A^*v\|_{L^2} + \frac{1}{C_2}\sup_{\widehat{u}} \frac{\langle \widehat{u}, [v] \rangle}{\|\widehat{u}\|}
-\end{align*}
-where we have used the Cauchy-Schwarz inequality, and eliminated the supremum by noting that the Cauchy-Schwarz inequality is tight.
-We define the optimal/ideal norm on $U$ as $\|u\|_{\rm opt}$ as such a norm with $C_1=C_2 = 1$,
-\[
-\|u\|_{\rm opt} = \|u\|_{L^2} + \|\widehat{u}\|.
-\]
-which induces the so-called ``optimal test norm"
-\[
-\|v\|_{\rm opt} = \|A^*v\|_{L^2} + \left(\sup_{\widehat{u}} \frac{\langle \widehat{u}, [v] \rangle}{\|\widehat{u}\|}\right)
-\]
-This is, in some sense, the canonical or ideal test norm; given any well-posed variational problem, DPG under the optimal test norm will return the best finite element approximation in a balanced norm on both field and flux variables.
-
-Unfortunately, the norm $\|v\|_{\rm opt}$ is non-localizable, meaning that it cannot be decomposed into the sum of independent contributions over individual elements.
-Consequently, the optimal test norm must be induced by a global inner product due to the presence of the jump terms.
-Solving for optimal test functions under this optimal norm (through inversion of Riesz map corresponding to this inner product) will result in expensive global problems, making this an impractical norm to work with.
-In practice, an approximation is made by removing such boundary terms and replacing them with scaled $L^2$ norms of the field variables, producing so-called \textit{quasi-optimal} test norm
-\[
-\|v\|_{\rm qopt} \coloneqq \|A^*v\|_{L^2} + \alpha \|v\|_{L^2}
-\]
-where $\alpha \in \mathbb{R}$ is chosen to complete the seminorm defined by $\|A^*v\|_{L^2}$.
-This optimal test norm has been shown to induce a well-posed DPG method for any well-posed ultra-weak formulation in the context of Friedrichs' systems of equations \cite{DPGFriedrichs}.
-
-The DPG method is currently being analyzed for both acoustic and elastic waves in context of the Helmholtz equation and equations of linear elasticity.
-Numerically, DPG appears to provide a ``pollution-free" method without phase error for these problems under the ``quasi-optimal" test norm with a specific scaling of the regularizing $L^2$ terms \cite{DPG4}.
-Similar results have also been obtained with the quasi-optimal test norm in the context of the elasticity \cite{DPGElas} and linear Stokes equation \cite{Camellia}.
-
-\section{Model problem and robustness}
-
-Our aim now is to translate the above abstract language to a concrete model problem in computational fluid dynamics.
-We consider the model convection-diffusion problem on domain $\Omega \in \mathbb{R}^d$ with boundary $\Gamma$
-\begin{align}
-\div (\beta u) - \epsilon\Delta v &= f  \label{primal}
-\end{align}
-in first order form
-\begin{align*}
-\div (\beta u - \sigma) &= f  \\
-\frac{1}{\epsilon}\sigma - \grad u &= 0
-\end{align*}
-with the corresponding variational form (prior to the application of boundary conditions)
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle + \langle \widehat{f}_n, \left[v\right] \rangle
-\end{align*}
-where $\left[ \tau_n \right]$ and $\left[ v\right]$ denote the jumps in $\tau_n$ and $v$ across an element edge, defined as
-\begin{align*}
-\left[ \tau_n \right] &= \tau^+ \cdot n^+ + \tau^-\cdot n^-\\
-\left[ v\right] &= v^+{\rm sgn}(n^+) + v^-{\rm sgn}(n^-)
-\end{align*}
-where $n$ is the outward normal vector to an element edge, and ${\rm sgn}(n)$ is 1 if $n$ aligns with a given normal orientation $n_e$ on each edge, and $-1$ otherwise (see Examples in \cite{DPGFriedrichs} for a more detailed explanation).
-
-Additionally, the inner products are taken element-wise over the finite element mesh $\Omega_h$, and the duality pairings are taken on $\Gamma_h$, the mesh ``skeleton", or union of edges of elements $K$ in $\Omega_h$.
-Similarly, we define the interior skeleton $\Gamma_h^0 = \Gamma_h \setminus \Gamma$.
-The divergence and gradient operators are likewise understood to act element-wise.
-
- The functional setting is now well understood as well (see \cite{analysisDPG} for details) - $u,\sigma \in L^2(\Omega)$, $v \in H^1(\Omega_h)$, $\tau \in H({\rm div},\Omega_h)$, where $H^1(\Omega_h)$ and $H({\rm div},\Omega_h)$ are ``broken" Sobolev spaces.
-By duality, $\widehat{u}$ lives in $H^{1/2}(\Gamma_h)$, the trace space of $H^1(\Omega_h)$, while $\widehat{f}_n$ comes from $H^{-1/2}(\Gamma_h)$, the normal trace space of $H({\rm div},\Omega_h)$.
-
-Finally, we split the boundary $\Gamma$ into three portions
-\begin{align*}
-\Gamma_{-} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\} \quad {\rm (inflow)}\\
-\Gamma_{+} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\} \quad {\rm (outflow)}\\
-\Gamma_{0} &\coloneqq \{x\in \Gamma; \beta_n(x) = 0\}
-\end{align*}
-We adopt a new inflow boundary condition, given by Hesthaven et al in \cite{Hesthaven96astable}, where we set
-\[
-\beta_n u - \sigma_n = f_n = u_0
-\]
-on $\Gamma_-$, and use the standard wall boundary condition $u=0$ on $\Gamma_+$.  For our model problem,
-as for many problems of interest in computational fluid dynamics, we
-expect $\grad u$ to be small near the inflow, and that the solutions
-to \eqref{primal} using $\beta_n u - \sigma_n = f_n = u_0$ on $\Gamma_-$
-will converge to that using $u=u_0$ on $\Gamma_-$  for sufficiently small $\epsilon$.
-Under these new boundary conditions, our variational problem $b(u,v) =
-l(v)$ is now defined by
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right),
-\left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad
-v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle
-\left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} +
-\langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup
-  \Gamma_h^0} \\ l\left(\left(\tau,v\right)\right) &= \left(f,
-v\right) %+ \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_+}
-- \langle u_0, v \rangle_{\Gamma_-}
-\end{align*}
-
-\subsection{Norms on $U$}
-
-Given the boundary conditions on $\widehat{u}$ and $\widehat{f}_n$, we
-can now also define the trace norms as (canonical) minimum energy
-extension norms (taking into account the respective lifts/boundary
-conditions on $\widehat{u}$ and $\widehat{f}_n$ on $\Gamma_+$ and
-$\Gamma_-$, respectively)
-\begin{align*}
-\|\widehat{u}\| &= \inf_{w\in H^1(\Omega),
-  \left.w\right|_{\Gamma_+}=0, \left.w\right |_{\Gamma_h\setminus
-    \Gamma_+ } = \widehat{u}} \|w\|_{H^1(\Omega)}\\ \|\widehat{f}_n\|
-&= \inf_{q\in H({\rm div},\Omega), \left.q\cdot n\right|_{\Gamma_-}=
-  0, \left. q\cdot n \right |_{\Gamma_h\setminus
-    \Gamma_-} = \widehat{f}_n}
-\|q\|_{H({\rm div},\Omega)}
-\end{align*}
-%Additionally, throughout the rest of this work, we denote norms on $u$ and $\sigma$ as
-%\begin{align*}
-%\|u\| &= \|u\|_{L^2} \\
-%\|\sigma\| &= \|\sigma\|_{L^2(\Omega_h)}
-%\end{align*}
-We will construct norms on $U$ as combinations of norms on each variable
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = C_1
-\|u\|_{L^2(\Omega_h)} + C_2 \|\sigma\|_{L^2(\Omega_h)} + C_3
-\|\widehat{u}\| + C_4 \|\widehat{f}_n\|.
-\]
-\subsection{Norms on $V$}
-
-%We will denote $\|\cdot \| = \|\cdot\|_{L^2}$ for all functions defined on $\Omega_h$. 
-As $\tau \in H({\rm div},\Omega_h)$ and $v \in H^1(\Omega_h)$, we will
-construct norms on $v$ and $\tau$ using some combination of terms
-which are equivalent to the canonical $H^1(K) \times H({\rm div},K)$
-norm over a single element
-\[
-\|\left(\tau,v\right)\|_{H^1(K) \times H({\rm div},K)}^2 =
-\|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2 + \|\tau\|_{L^2(K)}^2 +
-\|\div \tau\|_{L^2(K)}^2
-\]
-The squared norm over the entire triangulation $\Omega_h$ is defined to be the squared sum of contributions from each element
-\[
-\|\left(\tau,v\right)\|_{H^1(\Omega_h) \times H({\rm div},\Omega_h)}^2
-= \sum_{K\in \Omega_h} \|\left(\tau,v\right)\|_{H^1(K) \times H({\rm
-    div},K)}^2
-\]
-The exact norms that we will specify on $V$ will be determined later.
-
-The norms on the skeleton $\Gamma_h$ for $v$ and $\tau$ are defined by duality from the bilinear form
-\begin{align*}
-\|[\tau\cdot n]\| &= \|[\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} \coloneqq \sup_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+} = 0} \frac{\langle [\tau \cdot n], w\rangle}{\|w\|_{H^1(\Omega)}}\\
-\|[v]\|&=\|[v]\|_{\Gamma_h^0 \cup \Gamma_+} \coloneqq \sup_{\eta\in H({\rm div};\Omega), \left.\eta\cdot n\right|_{\Gamma_- \cup \Gamma_0} = 0} \frac{\langle v, \eta\cdot n\rangle}{\|\eta\|_{H({\rm div},\Omega)}}
-\end{align*}
-
-\subsection{Approximability of the quasi-optimal test norm}
-%\textcolor{blue}{need to define what we mean by robustness. perharps the best place is in the introduction}
-
-An ideal choice for the test norm would be the quasi-optimal norm; however, the form of the optimal test norm for convection-diffusion problems turns out to be quite problematic in the small diffusion limit.
-
-For convection-diffusion, the quasi-optimal test norm is 
-\[
-\|\left(\tau, v\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v
-\|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 +
-C_1\|v\|_{L^2}^2 + C_2\|\tau\|_{L^2}^2
-\]
-for some choice of constants $C_1$ and $C_2$.  
-%We note that the optimal test norm will automatically guarantee the
-%robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.
-However, use of this norm for the convection-diffusion problem is
-difficult - the variational problem for optimal test functions using
-the quasi-optimal test norm is equivalent to a reaction-diffusion
-system \cite{DBLP:journals/procedia/NiemiCC11}.  Such systems also
-develop strong boundary layers for small diffusion, and transforming
-the problem to the reference element reveals that the inversion of the
-inner product associated with the optimal test norm will induce strong
-boundary layers of width $\epsilon/h^2$ in the optimal test functions.
-In comparison, the quasi-optimal norm has yielded excellent results for the Helmholtz equation
-and other wave propagation problems. The difference between the two
-problems lies in the fact that, for wave propagation problems, the
-mesh size tends to be on the order of the wavenumber $k$/singular
-perturbation parameter. Transforming the variational problem using the
-quasi-optimal test norm for wave propagation yields smooth optimal
-test functions that are much easier to approximate over the reference
-element. Typically, the wavenumbers $k$ of physical interest are
-$O(100)-O(1000)$ with respect to a unit domain. The corresponding
-finite element problems will typically be solved on meshes containing
-approximately $O(k^d)$ elements in $\mathbb{R}^d$, well within the
-range of a computationally tractable simulation. However, for
-convection diffusion problems, the relevant range of $\epsilon$ for
-physical problems can be as small as $1e-7$. Solving on partially
-under-resolved meshes is thus unavoidable, and the approximability of
-the optimal test functions must be addressed in order to take
-advantage of the properties of DPG.
-
-In the application of DPG in \cite{DPG1,DPG2,DPG3,DPG4}, the approximation of optimal test functions is done using the enriched test space $V = \cup_{K} P^{p+\Delta p}(K)$, where $p$ is the polynomial order of the trial space on a given element $K$.
-In other words, optimal test functions are approximated element-by-element using polynomials whose order is $\Delta p$ more than the local order of approximation.
-Under this scheme, the approximation of optimal test functions is tied to the effectiveness of the $p$-method.
-Unfortunately, for problems with boundary layers - including the approximation of optimal test functions under the quasi-optimal test norm - the $p$-method performs very poorly.
-
-Resolving such boundary layers present in quasi-optimal test functions
-has been investigated numerically using specially designed (Shishkin)
-subgrid meshes by Niemi, Collier, and Calo in
-\cite{DBLP:journals/procedia/NiemiCC11}.  However, even with Shishkin
-meshes, the approximation of optimal test functions under the
-quasi-optimal norm is difficult and far more expensive and complex to
-implement than approximation of test functions using a simple
-$p$-enriched space for $V$. We approach this from a different
-perspective, aiming instead to design a test norm that does not induce boundary layers, yet still maintains what we will define as \textit{robustness} - approximation properties that do not change over a range of $\epsilon$.
-
-\subsection{Alternatives to the quasi-optimal test norm}
-
-We expect the quasi-optimal test norm to deliver results that are close to the optimal test norm; namely, that the DPG finite element solution minimizes error a norm equivalent to
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = \|u\|_{L^2(\Omega_h)} + \|\sigma\|_{L^2(\Omega_h)} +
-\|\widehat{u}\| + \|\widehat{f}_n\|.
-\]
-This is an example of a \textit{robust} error bound - under the optimal test norm, we will return the best approximation error in the same norm \textit{independently} of $\epsilon$.
-The precise definition of robustness for singularly perturbed problems can be given as follows - for a problem with singular perturbation parameter $\epsilon\rightarrow 0$ and exact solution $u$, a \textit{robust} method will return a solution $u_h$ such that
-\[
-\|u-u_h\|_U \lesssim  \inf_{w_h\in U}\|u-w_h\|_U
-\]
-where $\|\cdot \|_U$ is some norm and $\lesssim$ is a bound by a constant, both of which are independent of  $\epsilon$.
-
-We expect a similar bound to hold under the quasi-optimal norm; however, it is not clear what to expect for other choices of test norms on $V$.
-In particular, it is not clear whether it is possible to achieve a completely robust bound under alternative norms, especially ones that generate easily approximated test functions.
-
-The estimates and proofs in this paper are largely based on previous
-work done in \cite{DPGrobustness} and \cite{analysisDPG}. Our primary
-contributions in this paper are stronger stability estimates for a new
-inflow boundary condition and a slightly different test norm.
-
-\section{Strategy for estimating the DPG energy norm}
-
-%The first condition is satisfied by first decoupling norms on $\left(\tau,v\right)$ such that
-%\[
-%\left\|\left(\tau,v\right)\right\|_V = \|\tau\|_{H({\rm div},\Omega_h)} +  \|v\|_{H^1(\Omega_h)}.
-%\]
-%where $\|\tau\|_{H({\rm div},\Omega_h)}$ and $ \|v\|_{H^1(\Omega_h)}$ are both constructed as the sum of norm and seminorms on each respective space.
-Ensuring that each seminorm/normed term is of the same order will allow for smooth solutions (under some assumptions on $\beta$).
-The main goal of this paper is to derive a test norm that \textit{does not induce boundary layers in the optimal test functions}, but still induces an energy norm performs well for $\epsilon \ll 1$.
-The avoidance of boundary layers in the test norm will be described in more detail in the section detailing numerical experiments.
-Towards the goal of a well-performing energy norm, we will seek to derive $\epsilon$-explicit bounds on the finite element error by the best approximation error, and to characterize the dependence of such bounds upon the test norm.
-We seek to derive an estimate
-\[
-\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}
-\]
-where both $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ are characterized using
-\[
-\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,i} \coloneqq C_1^i\|u\| + C_2^i\|\sigma\| + C_3^i\|\widehat{u}\| + C_4^i\|\widehat{f}_n\|,\quad i = 1,2
-\]
-%As it may not be possible to derive $O(1)$ constants for each $C_j^i$, we will aim instead for a quasi-robust estimate, where some constants are allowed to depend on $\epsilon$.
-\textcolor{red}{Not sure if I need this sentence here.}
-To derive the above $\epsilon$-explicit bounds on the finite element error in norm $U,1$ by the best approximation error in norm $U,2$, we need to show that the DPG energy norm (in which our finite element solution is optimal), is bounded from above and below
-\[
-\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}.
-\]
-Our goal is to explicitly derive the constants $C^1_1,\ldots C^1_4$ and $C^2_1,\ldots C^2_4$ that define the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ respectively, taking into account any dependence of such $C^i_j$ on $\epsilon$.
-Our strategy for doing so is broken down into three parts.
-
-\subsection{Equate relations between norms on $U$ and norms on $V$}
-\label{sec:strategy1}
-We begin with a given norm on $U$
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = C_1 \|u\| + C_2 \|\sigma\| + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|.
-\]
-By \eqref{norm_duality}, the duality of test norm and energy norm, a norm of this form induces the test norm
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,U} &= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{C_1\|u\| + C_2\|\sigma\| + C_3\epsilon\|\widehat{u}\|+ C_4\sqrt{\epsilon}\|\widehat{u}\|}\\
-&= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup \Gamma_h^0}}{C_1\|u\| + C_2\|\sigma\| + C_3\epsilon\|\widehat{u}\|+ C_4\sqrt{\epsilon}\|\widehat{u}\|}\\
-& \leq \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle [\tau\cdot n], \widehat{u}\rangle}{\|\widehat{u}\|} +\frac{1}{C_4}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, [v]\rangle}{\|\widehat{f}\|}
-\end{align*}
-where $f$ and $g$ are defined as 
-\begin{align*}
-g &\coloneqq \div \tau - \beta \cdot \grad v\\
-f &\coloneqq \epsilon^{-1}\tau + \grad v
-\end{align*}
-which, by definition of the boundary norms on $[\tau\cdot n]$ and $[v]$, gives the characterization of the induced test norm 
-\[
-\|\left(v,\tau\right)\|_{V,U} \leq \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\|[\tau\cdot n]\| + \frac{1}{C_4}\|[v]\|
-\]
-\textcolor{red}{is this an equality?
-Is the inequality attainable, and thus attained in the supremum?} We can now use this relation to compare two different norms on $U$ by comparing their induced norms on $V$ - recall that showing a robust inequality between two norms on $U$ is similarly equivalent to showing the robust reverse inequality in the induced norms on $V$.
-
-\subsection{Decomposition into analyzable components}
-\label{sec:strategy2}
-
-After reducing the problem of comparing norms on $U$ to comparing norms on $V$, we break the analysis of $\left(\tau,v\right) \in V$ into the analysis of three subproblems.  Define the decomposition
-\[
-\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right),
-\]
-where $\left(v_1,\tau_1\right)$ satisfies 
-\begin{align*}
-\epsilon^{-1}\tau_1 + \grad v_1 &= 0\\
-\div \tau_1 - \beta\cdot \grad v_1 &=  \div \tau - \beta\cdot \grad v = g,
-\end{align*} 
-Likewise, we define $\left(v_2,\tau_2\right)$ as satisfying
-\begin{align*}
-\epsilon^{-1}\tau_2 + \grad v_2 &= \epsilon^{-1}\tau + \grad v = f\\
-\div \tau_2 - \beta\cdot \grad v_2 &= 0
-\end{align*}
-We will additionally require both $\left(\tau_1,v_1\right)$ and $\left(\tau_2,v_2\right)$ to come from $H({\rm div}, \Omega)\times H^1(\Omega)$, and to satisfy boundary conditions
-\begin{align}
-\tau_i\cdot n &= 0, \quad x \in \Gamma_- \label{bc_1}\\
-v_i &= 0, \quad x \in \Gamma_+ \label{bc_2}
-\end{align}
-for $i = 1, 2$.
-The selection of $H({\rm div}, \Omega)\times H^1(\Omega)$ conforming test functions satisfying the specific above boundary conditions removes the contribution of the jump terms over the skeleton $\Gamma_h$ in the bilinear form, allowing us to bound components of the induced test norm separately from each other.
-
-Finally, by construction, $\left(v_0,\tau_0\right)$ must satisfy 
-\begin{align*}
-\epsilon^{-1}\tau_0 + \grad v_0 &= 0\\
-\div \tau_0 - \beta\cdot \grad v_0 &= 0
-\end{align*}
-with jumps
-\begin{align*}
-[v_0] &= [v], \quad x\in \Gamma_h^0\\
-[\tau_0 \cdot n] &= [\tau \cdot n], \quad x\in \Gamma_h^0.
-\end{align*}
-By $\left(v_0,\tau_0\right) = \left(v,\tau\right) - \left(v_1,\tau_1\right) - \left(v_2,\tau_2\right)$, $\left(v_0,\tau_0\right)$ must satisfy boundary conditions
-\begin{align}
-v_0 &= v, \quad x\in \Gamma_+ \label{bc_1}\\
-\tau_0 \cdot n &= \tau \cdot n, \quad x\in \Gamma_-\cup \Gamma_0. \label{bc_2}
-\end{align}
-
-We have now decomposed any arbitrary test function $\left(\tau,v\right)$ into a single discontinuous portion and two conforming portions.
-Showing the robust bound of $\|\left(v,\tau\right)\|_V$ from above and below (by norms $\|\cdot \|_{V,1}$ and $\|\cdot \|_{V,2}$ on $V$, respectively) reduces to showing the robust bound of each component
-\[
-\|\left(\tau,v\right)\|_{V,1} \lesssim \|\left(v_{0},\tau_{0}\right)\|_V, \|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|\left(\tau,v\right)\|_{V,2}
-\]
-Bounding $\|\left(\tau_0,v_0\right)\|$ requires the use of techniques and decompositions first developed in \cite{analysisDPG} and adapted to convection-diffusion in \cite{DPGrobustness}.
-However, due to the $H({\rm div}, \Omega)\times H^1(\Omega)$ conforming nature of $\left(\tau_1,v_1\right)$ and $\left(\tau_2,v_2\right)$, the bound from above of test functions $\|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|g\|$ is reduced to proving classical error estimates for the adjoint equations
-\begin{align}
-\epsilon^{-1}\tau + \grad v &= f \label{adjoint1}\\
-\div \tau - \beta\cdot \grad v &=  g, \label{adjoint2}
-\end{align} 
-for any choice of data $f, g\in L^2({\Omega_h})$ and boundary conditions $\left.\tau\cdot n\right|_{\Gamma_-} = 0$ and $\left.v\right|_{\Gamma_+} = 0$
-
-\subsection{Deriving adjoint estimates}
-\label{sec:strategy3}
-
-The final step to estimating the induced norm on $U$ by a given localizable test norm on $V$ is to derive adjoint stability estimates on $\tau$ and $v$ in terms of localizable normed quantities.
-These normed quantities will create ``building-blocks" through which we can construct test norms, where each building block will correspond roughly to estimates for $\|u\|_{L^2}$, $\|\sigma\|_{L^2}$, $\|\widehat{u}\|$, or $\|\widehat{f}_n\|$.
-
-We introduce first the bounds derived; the proofs will be given later.
-For this analysis, it will be necessary to assume certain technical conditions on $\beta$.
-For each proof, we require $\beta \in C^2(\bar{\Omega})$ and $\beta, \div \beta = O(1)$.
-Additionally, we will assume some or all of the following assumptions hold
-\begin{align}
-&\curl \beta = 0, \quad 0<C \leq \left | \beta\right |^2 + \frac{1}{2}\div \beta, \quad C = O(1) \label{a_req}\\
-&\grad \beta + \grad \beta ^T - \div \beta I = O(1) \label{b_req}\\
-&\div \beta = 0 \label{c_req}
-\end{align}
-We also require $\epsilon$ sufficiently small in Lemma \ref{lemma_grad}.
-
-Under proper assumptions on $\beta$, we have the robust bounds
-\begin{itemize}
-\item \textbf{Lemma \ref{lemma_stream}}: For $\beta$ satisfying \eqref{a_req} and \eqref{b_req}, $f=0$ and $v \in H^1(\Omega_h)$, satisfying boundary conditions \eqref{bc_1} and \eqref{bc_2}
-\begin{align*}
-\|\beta \cdot \grad v \| &\lesssim \| g\| 
-\end{align*}
-Similarly, from $\div \tau - \beta\cdot \grad v = g$, we get $\|\div \tau\| \lesssim \|g\|$ as well.  
-\item \textbf{Lemma \ref{lemma_grad}}: For $\beta$ satisfying \eqref{a_req}, and $v \in H^1(\Omega_h)$ satisfying boundary conditions \eqref{bc_1} and \eqref{bc_2}, and for sufficiently small $\epsilon$
-\begin{align*}
-\epsilon \|\grad v\|^2 + \|v\|^2 &\lesssim \|g\|^2 + \epsilon \| f\|^2
-\end{align*}
-\item \textbf{Lemma \ref{lemma_boundary}}: For $\beta$ satisfying \eqref{a_req}, \eqref{c_req}, and $f=g=0$, 
-\begin{align*}
-\|\grad v\| = \frac{1}{\epsilon}\|\tau\| &\lesssim \frac{1}{\epsilon} \| [\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v]\|_{\Gamma_h^0 \cup \Gamma_+}
-\end{align*}
-\end{itemize}
-Together, these estimates will be sufficient to construct a complete norm on $V$ and demonstrate bounds on induced test norms for different scalings of norms on $U$.
-
-\section{Relations between energy and $U$ norms}
-\label{sec:main_bounds}
-
-Let the norm 
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{E}
-\]
-be defined as the energy norm induced by DPG under the specific test norm
-\[
-\|\left(\tau, v\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2.
-\]
-
-The primary result of this paper is that, if $\beta$ satisfies \ref{a_req},\ref{b_req}, and \ref{c_req}, the DPG method provides robust control over the $L^2$ error in $u$ and $\sigma$
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-\left(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h}\right)\right\|_{U,1} \lesssim \inf_{w\in U_h}\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-w_h \right\|_{E}
-\]
-where $\|\cdot \|_{U,1}$ is defined as
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,1} \coloneqq \|u\| + \|\sigma\| + \epsilon\|\widehat{u}\|+\sqrt{\epsilon} \|\widehat{f}_n\|.
-\]
-%\textcolor{red}{should be explained here}.
-
-A second, weaker result is an upper bound on the energy norm
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-\left(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h}\right)\right\|_{E} \lesssim \inf_{w\in U_h}\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-w_h\right\|_{U,2}
-\]
-where $\|\cdot \|_{U,2}$ is defined as
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,2}^2 \coloneqq \|u\|^2 + \frac{1}{\sqrt{\epsilon}}\left(\|\sigma\|^2 + \|\widehat{u}\|^2+ \|\widehat{f}_n\|^2\right).
-\]
-While the second bound is robust, we have derived such a bound only by explicitly accounting for a factor of $\epsilon^{-1/2}$ in the bounding norm $\|\cdot \|_{U,2}$.
-This implies that for very small $\epsilon$, the $L^2$ error may be much smaller than the energy error (in this sense, DPG may lose some efficiency for small $\epsilon$).
-However, numerical experiments demonstrate much better results, and suggest that, at least for our example problems, $\|u-u_h\|_E \sim \|u-u_h\|_{U}$, implying that the induced energy norm may be equivalent to a norm on the group variable $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)$ that does not grow with $\epsilon$.
-
-\subsection{Bound from below}
-
-We begin by using the strategy outlined in sections~\ref{sec:strategy1},~\ref{sec:strategy2}, and the estimates provided in~\ref{sec:strategy3} to prove the robust bound of the $L^2$ error in the field variables by the energy error.
-
-As a consequence of the duality of norms \eqref{norm_duality}, we know that the norm $\left\| u \right\|_{U,1}$ is induced by a specific test norm $\| v  \|_{V,1}$.
-To bound $\|\cdot\|_E$ robustly from above or below by a given norm $\left\| u \right\|_{U,2}$ on $U$ now only requires the robust bound in the opposite direction of $\| v \|_{V,1}$ by $\|v\|_{V,2}$.
-
-\begin{lemma}
-\label{bound_from_below}
-(Bound from below) If $\beta$ satisfies \eqref{a_req} and \eqref{b_req}, then for $\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U$,
-\[
-\|u\| + \|\sigma\| + \epsilon\|\widehat{u}\|+ \sqrt{\epsilon}\|\widehat{u}\| \lesssim \left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E
-%\|u\| + \frac{1}{\sqrt{\epsilon}}\|\sigma\| + \epsilon\|\widehat{u}\|+ \sqrt{\epsilon}\|\widehat{u}\| \lesssim \left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E
-\]
-\end{lemma}
-\begin{proof}
-By \eqref{norm_duality}, for $f$ and $g$ defined in \eqref{adjoint1} and \eqref{adjoint2},
-\begin{align*}
-f &= \epsilon^{-1}\tau + \grad v  \\
-g &=\div \tau - \beta\cdot \grad v,
-\end{align*} 
-we can characterize the test norm for $\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = C_1\|u\| + C_2\|\sigma\| + C_3\|\widehat{u}\|+ C_4\|\widehat{u}\|$ as
-\begin{align*}
-\|\left(v,\tau\right)\|_V &\lesssim \frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{C_1\|u\| + C_2\|\sigma\| + C_3\|\widehat{u}\|+ C_4\|\widehat{u}\|}\\
-& \simeq \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle [\tau\cdot n], \widehat{u}\rangle}{\|\widehat{u}\|} + \frac{1}{C_4}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, [v]\rangle}{\|\widehat{f}\|},
-\end{align*}
-which, by definition of the boundary norms, is 
-\[
-\|\left(v,\tau\right)\|_V \lesssim \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\|[\tau\cdot n]\| + \frac{1}{C_4}\|[v]\|
-\]
-We will bound $\|\left(v,\tau\right)\|_V$ for all $\left(v,\tau\right)$ satisfying \eqref{adjoint} by decomposing $\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right)$ as described in section~\ref{sec:strategy2}.
-%where $\left(v_1,\tau_1\right)$ satisfies our adjoint equation \eqref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and 
-%\begin{align*}
-%f &= 0\\
-%g&= \div \tau - \beta\cdot \grad v,
-%\end{align*} 
-%and $\left(v_2,\tau_2\right)$ satisfies \eqref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and 
-%\begin{align*}
-%g &= 0\\
-%f &= \epsilon^{-1}\tau + \grad v.
-%\end{align*}
-%We note that, if $v_2$ satisfies $n\cdot \grad v_2 = n\cdot f$, by definition of $f$ and $v_2$,
-%\begin{align*}
-%\tau_2 \cdot n &= \epsilon n\cdot f - \epsilon n\cdot \grad v_2 = 0, \quad x\in \Gamma_- \cup \Gamma_0
-%\end{align*}
-%By construction, $\left(v_0,\tau_0\right)$ satisfies adjoint equations \eqref{adjoint1} and \eqref{adjoint2} with $f=g=0$, with jumps
-%\begin{align*}
-%[v_0] &= [v], \quad x\in \Gamma_h^0\\
-%[\tau_0 \cdot n] &= [\tau \cdot n], \quad x\in \Gamma_h^0.
-%\end{align*}
-%By $\left(v_0,\tau_0\right) = \left(v,\tau\right) - \left(v_1,\tau_1\right) - \left(v_2,\tau_2\right)$, $\left(v_0,\tau_0\right)$ must satisfy boundary conditions
-%\begin{align*}
-%v_0 &= v, \quad x\in \Gamma_+\\
-%\tau_0 \cdot n &= \tau \cdot n, \quad x\in \Gamma_-\cup \Gamma_0.
-%\end{align*}
-By the triangle inequality, robustly bounding $\|\left(v,\tau\right)\|_V$ from above reduces to robustly bounding each component 
-\[
-\|\left(v_{0},\tau_{0}\right)\|_V, \|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\|[\tau\cdot n]\| + \frac{1}{C_4}\|[v]\|
-\]
-Roughly speaking, Lemma \ref{lemma_grad} concerns the robust control of $u$ by the energy error; Lemmas \ref{lemma_stream} and \ref{lemma_boundary} concern the robust control of field variable $\sigma$ and flux/trace variables, respectively.
-
-%\begin{align*}
-%\|\left(\tau, v\right)\|_{V}^2 &= \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2 \\
-%& \lesssim \|g\| + \|f\| + \epsilon^{-1}\|[\tau\cdot n]\| + \epsilon^{-1/2}\|[v]\|
-%\end{align*}
-\begin{itemize}
-\item \textbf{Bound on $\|\left(v_{0},\tau_{0}\right)\|_V$}
-
-Lemma \ref{lemma_boundary} gives control over $\epsilon\|\grad v_0\| + \frac{1}{\epsilon}\|\tau_0\|$ through
-\[
-\|\grad v_0\| = \frac{1}{\epsilon}\|\tau_0\| \lesssim \frac{1}{\epsilon} \| [\tau_0\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v_0]\|_{\Gamma_h^0 \cup \Gamma_+} = \frac{1}{\epsilon} \| [\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v]\|_{\Gamma_h^0 \cup \Gamma_+}
-\]
-Lemma 4.2 of \cite{analysisDPG} gives us the Poincare inequality for discontinuous functions
-\[
-\|v_0\| \lesssim \|\grad v_0\| + \|[v]\|
-\]
-%Since $f=0$, by Lemma 2, $\|\beta\cdot \grad v_0\|  \lesssim \|g\| = 0$.  
-Since $g = 0$, $\| \div \tau_0\| = \|\beta\cdot \grad v_0\|\lesssim \|\grad v_0\|$, which we now have control over as well.
-
-\item \textbf{Bound on $\|\left(v_{1},\tau_{1}\right)\|_V$}
-
-%Given $\tau_1 \in H({\rm div};\Omega)$, $v\in H^1(\Omega)$, with boundary conditions \eqref{bc_1} and \eqref{bc_2}, $\frac{1}{\epsilon} \| [\tau_0\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v_0]\|_{\Gamma_h^0 \cup \Gamma_+}=0$.
-With $f = 0$, Lemma \ref{lemma_grad} provides the bound
-\[
-\|\beta \cdot \grad v_1 \| \lesssim \| g\|
-\]
-Noting that $\div \tau_1 = g+\beta\cdot \grad v_1$ gives $\|\div \tau_1 \| \lesssim \|g\|$ as well.  Lemma \ref{lemma_grad} gives
-\[
-\epsilon \|\grad v_1\|^2 + \|v_1\|^2 \lesssim \|g\|^2
-\]
-and noting that $\epsilon^{-1/2}\tau_1 = \epsilon^{1/2}v_1$ gives $\epsilon\|\grad v_1\|^2 = \epsilon^{-1}\|\tau_1\|^2 \lesssim \|g\|^2$ as well.
-
-\item \textbf{Bound on $\|\left(v_{2},\tau_{2}\right)\|_V$}
-
-Lemma \ref{lemma_grad} provides
-\[
-\epsilon \|\grad v\|^2 + \|v\|^2 \lesssim  \epsilon \| f\|^2 \leq \|f\|^2
-\]
-We have $\epsilon^{-1}\tau = f - \grad v$, so $\epsilon^{-1} \|\tau\| \lesssim \|f\| + \|\grad v\|$.
-Lemma~\ref{lemma_grad} implies $\|\grad v\|^2  \lesssim  \| f\|^2$, so for $\epsilon \leq 1$, we control $\epsilon^{-1/2}\|\tau\| \leq \epsilon^{-1}\|\tau\| \lesssim \|f\|$.
-The remaining terms can be bounded by noting that, with $g = 0$, $\|\div \tau_2\| = \|\beta\cdot \grad v_2\| \lesssim \|\grad v_2\| \lesssim \|f\| $.
-\end{itemize}
-
-With these characterizations, we can conclude that $C_1 = C_2 = 1$, $C_3 = \epsilon$, and $C_4 = \epsilon^{1/2}$.  
-\end{proof}
-
-\subsection{Bound from above}
-
-We have shown the robust bound of the norm $\|\cdot \|_{U,1}$ on $U$ by the energy norm; for a full equivalence statement, we require a bound on the energy norm by the norm $\|\cdot \|_{U,2}$ on $U$.
-By the duality of the energy and test norm, this is equivalent to bounding the test norm from below by the test norm induced by $\|\cdot \|_{U,2}$.
-\begin{lemma}
-
-(Bound from above) For $\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U$,
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E \lesssim \|u\| + \frac{1}{\sqrt{\epsilon}}\left(\|\sigma\| + \|\widehat{u}\|+ \|\widehat{u}\|\right)
-\]
-
-\end{lemma}
-\begin{proof}
-For any norm on $U$ of the form
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,*} = \|u\| + C_2 \|\sigma\| + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|,
-\]
-the induced test norm is  
-\begin{align*}
-\| \left(\tau,v\right) \|_{V,*} &= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E} \\
-& = \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle + \langle \widehat{f}_n, \left[v\right] \rangle
-}{\|u\| + C_2 \|\sigma\| + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|} \\
-&\lesssim \|g\| + \frac{1}{C_2}\|f\| + \sup_{\widehat{u},\widehat{f}_n \neq 0}\frac{\langle \left[\tau_n\right], \widehat{u} \rangle + \langle \widehat{f}_n, \left[v\right] \rangle}{C_3\|\widehat{u}\| + C_4\|\widehat{f}_n\|}
-\end{align*}
-where $f$ and $g$ are again the loads of the adjoint problem defined in \eqref{adjoint1}, \eqref{adjoint2}.  By the triangle inequality, we have the bounds
-\begin{align*}
-\epsilon \|f \|^2 &\leq \epsilon^{-1} \| \tau\|^2 + {\epsilon} \|\grad v\|^2 \lesssim \| \left(\tau,v\right)\|_V^2\\
-\|g \| &\leq \|\div \tau\| +  \|\beta \cdot \grad v\| \lesssim \| \left(\tau,v\right)\|_V
-\end{align*}
-We estimate the supremum by following \cite{DPGrobustness}; we begin by choosing $\eta \in H({\rm div}; \Omega)$, $w\in H^1(\Omega)$, such that $\left.\left(\eta-\beta w \right)\cdot n\right |_{\Gamma_+} = 0$ and $\left.w\right |_{\Gamma_-\cup\Gamma_0} = 0$, and integrating the boundary pairing by parts to get
-\begin{align*}
-\langle [\tau\cdot n],w\rangle + \langle [v],\left(\eta - \beta w\right)\cdot n\rangle &\lesssim \|\left(\tau,v\right)\|_V\frac{1}{\sqrt{\epsilon}}\left(\|\eta\| + \|w\|\right)\\
-%\langle [\tau\cdot n],w\rangle + \langle [v],\left(\eta - \beta w\right)\cdot n\rangle 
-&\lesssim \|\left(\tau,v\right)\|_V\frac{1}{\sqrt{\epsilon}}\left(\|\eta-\beta w\| + \|w\|\right)
-\end{align*}
-since $\|\eta\| = \|\eta - \beta w + \beta w\| \leq \|\eta - \beta w\| + \|\beta w\| \lesssim \|\eta-\beta w\| + \|w\|$.  Dividing through and taking the supremum gives
-\[
-\sup_{w,\eta \neq 0} \frac{\langle[\tau\cdot n],w\rangle + \langle [v],\left(\eta - \beta w\right)\cdot n\rangle}{\left(\|\eta-\beta w\| + \|w\|\right)} \lesssim \|\left(\tau,v\right)\|_V\frac{1}{\sqrt{\epsilon}}
-\]
-To finish the proof, define $\rho \in H^{1/2}(\Gamma_h)$ and $\phi \in H^{-1/2}(\Gamma_h)$ such that $\rho = \left.w\right|_{\Gamma_h}$ and $\phi = \left.(\eta-\beta w)\cdot n\right|_{\Gamma_h}$, and note that
-\begin{align*}
-\sup_{\rho,\phi \neq 0} \frac{\langle [\tau\cdot n],\rho\rangle + \langle [v],\phi \rangle}{\|\rho\|+\|\phi\|} &= \sup_{w,\eta \neq 0} \frac{\langle [\tau\cdot n],w\rangle + \langle [v],\left(\eta - \beta w\right)\cdot n\rangle}{ \|w\|+\|\eta-\beta w\|}
-\end{align*}
-
-Together, the bounds on $\|g\|$ and $\|f\|$ imply $\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{E} \lesssim \left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,*}$ for $C_2 = C_3 = C_4 = \frac{1}{\sqrt{\epsilon}}$.
-\end{proof}
-
-%In \cite{DPGrobustness}, the quasi-optimal test norm was shown to induce an energy norm that is bounded from both above and below by norms on $U$ that do not grow in magnitude with $\epsilon^{-1}$.
-
 \section{Proof of lemmas/stability of the adjoint problem}
 
-We reduce the adjoint problem to the scalar second order equation
-\begin{equation}
-- \epsilon \Delta v - \beta \cdot \grad v = g - \epsilon \div f \label{adjoint}
-\end{equation}
+We present now the proofs of the three lemmas used in this paper to show the equivalence of the DPG energy norm to norms on $U$. We reduce the adjoint problem to the scalar second order equation
+\begin{align}
+- \epsilon \Delta v - \beta \cdot \grad v &= g - \epsilon \div f \eqnlab{adjoint}
+\end{align}
 with boundary conditions
@@
 
-The appearance of the normal trace $f\cdot n$ necessitates the use of a smooth dense subset of $L^2$.
-Formally speaking, we define the adjoint equation \eqref{adjoint} for $f\in C^\infty(\Omega)$.
+The normal trace of $f\cdot n$ is treated using a density argument --- for $f\in C^\infty(\Omega)$, we derive inequalities that are independent of $f\cdot n$ and $\div f$.
+We extend these inequalities to $f\in L^2(\Omega)$ by taking $f$ to be the limit of smooth functions.
+%The appearance of the normal trace $f\cdot n$ necessitates the use of a smooth dense subset of $L^2$.
+Formally speaking, we define the adjoint equation \eqnref{adjoint} for $f\in C^\infty(\Omega)$.
 In doing so, we are allowed to speak of the normal trace $f\cdot n$ on the boundary.
 We derive inequalities that are independent of $f\cdot n$ and $\div f$ (quantities that are ill-defined for $L^2(\Omega)$ functions), and note that, since smooth functions are dense in $L^2(\Omega)$, we can take any $L^2$ function to be the limit of $C^\infty(\Omega)$ functions.
-Since the inequality holds for all smooth functions and is well-defined for $L^2(\Omega)$ functions, the inequality holds for $L^2(\Omega)$ functions in the limit as well.
+Since each inequality will hold for all smooth functions and is well-defined for $L^2(\Omega)$ functions, the same inequality will hold for $L^2(\Omega)$ functions in the limit as well.
 
@@
 \label{lemma_stream}
-Assume $v$ satisfies \eqref{adjoint}, with boundary conditions \eqref{bc_1}, and \eqref{bc_2}, and $\beta$ satisfies \eqref{a_req} and \eqref{b_req}.
-If $\div f = 0$ and $\epsilon$ is sufficiently small,
+Assume $v$ satisfies \eqnref{adjoint}, with boundary conditions \eqref{bc_1} and \eqref{bc_2}, and $\beta$ satisfies \eqref{a_req} and \eqref{b_req}.
+If $\div f = 0$ and $\epsilon$ is sufficiently small, then
 \[
-\|\beta \cdot \grad v \| \lesssim \| g\|
+\|\beta \cdot \grad v \| \lesssim \| g\|.
 \]
@@
 \begin{proof}
-Define $v_\beta = \beta\cdot \grad v$.  Multiplying the adjoint equation \eqref{adjoint} by $v_\beta$ and integrating over $\Omega$ gives
+Define $v_\beta = \beta\cdot \grad v$.  Multiplying the adjoint equation \eqnref{adjoint} by $v_\beta$ and integrating over $\Omega$ gives
 \[
-\|v_\beta\|^2 = -\int_\Omega g v_\beta - \epsilon \int_\Omega \Delta v v_\beta
+\|v_\beta\|^2 = -\int_\Omega g v_\beta - \epsilon \int_\Omega \Delta v v_\beta.
 \]
@@
 \[
--\int_{\Omega} \beta\cdot \grad v \del v = -\int_{\Omega} \beta\cdot \grad v \div \grad v
+-\int_{\Omega} \beta\cdot \grad v \del v = -\int_{\Omega} \beta\cdot \grad v \div \grad v.
 \]
@@
 \[
--\int_{\Omega} \beta\cdot \grad v \div \grad v = \int_{\Omega}\grad (\beta\cdot \grad v) \cdot \grad v  - \int_{\Gamma}n\cdot \grad v \beta\cdot\grad v
+-\int_{\Omega} \beta\cdot \grad v \div \grad v = \int_{\Omega}\grad (\beta\cdot \grad v) \cdot \grad v  - \int_{\Gamma}n\cdot \grad v \beta\cdot\grad v.
 \]
-Note that 
-\[
-\grad (\beta \cdot \grad v) = \grad \beta \cdot \grad v + \beta \cdot \grad \grad v
-\]
-where $\grad \beta$ and $\grad \grad v$ are understood to be tensors. Then, 
+Since $\grad (\beta \cdot \grad v) = \grad \beta \cdot \grad v + \beta \cdot \grad \grad v$, where $\grad \beta$ and $\grad \grad v$ are understood to be tensors, 
 \[
@@
 \]
-Noting that $\grad v \cdot \grad \grad v = \grad\frac{1}{2}\left(\grad v\cdot \grad v\right)$, if we integrate by parts again, we get
+If we integrate by parts again and use that $\grad v \cdot \grad \grad v = \grad\frac{1}{2}\left(\grad v\cdot \grad v\right)$, we get
 %\[
@@
 %The first term on the RHS can be controlled using Young's inequality. 
-The last term can be bounded by our assumption on $\|\grad \beta - \frac{1}{2}\div \beta I\|^2 \leq C$.
+The last term can be bounded by our assumption on $\|\grad \beta - \frac{1}{2}\div \beta I\|^2 \leq C$:
 \[
-\epsilon \int_{\Omega} \grad v \left(\grad \beta - \frac{1}{2}\div \beta I\right)\grad v \leq C\frac{\epsilon}{2} \|\grad v\|^2
+\epsilon \int_{\Omega} \grad v \left(\grad \beta - \frac{1}{2}\div \beta I\right)\grad v \leq C\frac{\epsilon}{2} \|\grad v\|^2.
 \]
 For the boundary terms, on $\Gamma_-$, $\grad v\cdot n = 0$, reducing the integrand over the boundary to $\beta_n|\grad v|^2 \leq 0$.
-On $\Gamma_+$, $v=0$ implies $\grad v \cdot \tau = 0$, where $\tau$ is a tangential direction.
-An orthogonal decomposition yields $\grad v = (\grad v \cdot n) n$, reducing the above to
+On $\Gamma_+$, $v=0$ implies $\grad v \cdot \tau = 0$, where $\tau$ is any tangential direction.
+An orthogonal decomposition in the normal and tangential directions yields $\grad v = (\grad v \cdot n) n$, reducing the above to
 \[
- \epsilon\int_{\Gamma}  -\frac{1}{2}|\beta_n| (\grad v \cdot n)^2 \leq 0
+ \epsilon\int_{\Gamma}  -\frac{1}{2}|\beta_n| (\grad v \cdot n)^2 \leq 0.
 \]
-leaving us with the estimate
+Applying these inequalities to our expression for $\|v_\beta\|^2$ leaves us with the estimate
 \[
-\|v_\beta\|^2 \leq  -\int_{\Omega}g\beta\cdot \grad v + C\frac{\epsilon}{2} \|\grad v\|^2
+\|v_\beta\|^2 \leq  -\int_{\Omega}g\beta\cdot \grad v + C\frac{\epsilon}{2} \|\grad v\|^2.
 \]
@@
 \label{lemma_grad}
-Assume \eqref{a_req} holds.  Then, for $v$ satisfying equation \eqref{adjoint} with boundary conditions \eqref{bc_1}, \eqref{bc_2} and sufficiently small $\epsilon$, 
+Assume $\beta$ satisfies \eqref{a_req}.  Then, for $v$ satisfying equation \eqnref{adjoint} with boundary conditions \eqref{bc_1} and \eqref{bc_2} and sufficiently small $\epsilon$, 
 \[
@@
 \begin{proof}
-Since $\curl \beta=0$, and $\Omega$ is simply connected, there exists a scalar potential $\psi$, $\grad \psi = \beta$ such that $e^\psi = O(1)$.
-Take the transformed function $w = e^\psi v$; following (2.26) in \cite{DPGrobustness}, we substitute $w$ into the the left hand side of equation \eqref{adjoint}, arriving at the relation
+Since $\curl \beta=0$, and $\Omega$ is simply connected, there exists a scalar potential $\psi$, $\grad \psi = \beta$ by properties of the exact sequence.
+The potential is non-unique up to a constant, and we choose the constant such that $e^\psi = O(1)$.
+Take the transformed function $w = e^\psi v$; following (2.26) in \cite{DPGrobustness}, we substitute $w$ into the the left hand side of equation \eqnref{adjoint}, arriving at the relation
 \[
@@
 \]
-Noting that $w=0$ on $\Gamma_+$ reduces the boundary integrals over $\Gamma$ to just the inflow $\Gamma_-$.
-Furthermore, we have the relation $\grad w = e^\psi(\grad v + \beta v)$.
+Note that $w=0$ on $\Gamma_+$ reduces the boundary integrals over $\Gamma$ to just the inflow $\Gamma_-$.
+Furthermore, we have $\grad w = e^\psi(\grad v + \beta v)$.
 Applying the above and boundary conditions on $\Gamma_-$, the first boundary integral becomes
@@
 assuming $\epsilon$ is sufficiently small.
-Our assumptions on $\beta$ implies $\left((1-\epsilon)|\beta|^2 + \frac{1}{2} \div \beta \right) \lesssim 1$ and $e^\psi = O(1)$.
-We can then bound from below
+Our assumptions on $\beta$ imply $\left((1-\epsilon)|\beta|^2 + \frac{1}{2} \div \beta \right) \lesssim 1$ and $e^\psi = O(1)$.
+We can then bound from below:
 \[
@@
 \label{lemma_boundary}
-Let $\beta$ satisfy \eqref{a_req} and \eqref{c_req}, and let $v$ satisfy \eqref{adjoint} with $f=g=0$, and arbitrary boundary conditions.  Then, there holds
+%\todo{Rewrite in two steps - get variational soln to div free portion, then infer existence of curl z, then put together the decomp}
+Let $\beta$ satisfy conditions \eqref{a_req} and \eqref{c_req}, and let $v \in H^1(\Oh)$ , $\tau \in H({\rm div},\Oh)$ satisfy equations \eqref{adjoint1} and \eqref{adjoint2} with $f=g=0$%in a distributional sense, with arbitrary boundary conditions
+. Then
 \[
-\|\grad v\| = \frac{1}{\epsilon}\|\tau\| \lesssim \frac{1}{\epsilon} \| [\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v]\|_{\Gamma_h^0 \cup \Gamma_+}
+\|\grad v\| = \frac{1}{\epsilon}\|\tau\| \lesssim \frac{1}{\epsilon} \| \jump{\tau\cdot n}\|_{\Gh \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| \jump{v}\|_{\Gh^0 \cup \Gamma_+}
 \]
@@
 \begin{proof}
-We follow \cite{analysisDPG} and \cite{DPGrobustness} in decomposing $\tau$ into $z\in H({\rm curl},\Omega)$ and $\psi\in H^1(\Omega)$ such that
+
+We begin by choosing $\psi$ as the unique solution to the following problem
+\begin{align*}
+-\epsilon \Delta \psi + \div \left(\beta \psi\right) &= -\div \tau \\
+\epsilon \grad \psi \cdot n - \beta_n\psi - \tau\cdot n &= 0, \quad x\in \Gamma_-\\
+\psi &= 0, \quad x\in \Gamma_+.
+\end{align*}
+Since $\div \beta = 0$, we can conclude that the bilinear form is coercive and the problem is well posed \cite{DPGrobustness}.
+The well-posedness of the above problem directly implies that $\div \left(\tau-(\epsilon\grad \psi - \beta \psi)\right) = 0$ in a distributional sense, and thus there exists a $z\in H({\rm curl},\Omega)$ such that
 \[
@@
 \]
-Specifically, $\psi$ is chosen as the solution to 
+Since $\div \beta = 0$, we satisfy condition~\eqref{a_req}.
+Noting that the sign on $\beta$ is opposite now of the sign on $\epsilon \Delta \psi$, the problem for $\psi$ matches the adjoint problem \label{adjoint} for $f = \frac{1}{\epsilon}\tau$.
+Given the boundary conditions on $\psi$, we can use a trivial modification of the proof of Lemma \ref{lemma_grad} to bound
+\[
+\epsilon \|\grad \psi\|_{L^2}^2 + \|\psi \|_{L^2}^2 \lesssim \frac{1}{\epsilon}\|\tau\|_{L^2}^2.
+\]
+By the above bound and the triangle inequality, 
+\[
+\|\curl z \|_{L^2} \leq \epsilon \|\grad \psi\|_{L^2} + \|\beta \psi\|_{L^2} + \|\tau\|_{L^2} \lesssim \frac{1}{\sqrt{\epsilon}}\|\tau\|_{L^2}.
+\]
+On the other hand, using the decomposition and boundary conditions directly, we can integrate by parts over $\Oh$ to arrive at
 \begin{align*}
--\epsilon \Delta \psi + \div \left(\beta \psi\right) &= -\div \tau \\
-\epsilon \grad \psi \cdot n - \beta_n \psi - \tau\cdot n &= 0, \quad x\in \Gamma_-\\
-\psi &= 0, \quad x\in \Gamma_+ 
+\|\tau\|_{L^2}^2 &= (\tau, \epsilon \grad \psi - \beta \psi + \curl z)_{\Oh} = (\tau, \epsilon \grad \psi) - (\tau,\beta \psi) + (\tau,\curl z)  \\
+&=(\tau, \epsilon \grad \psi) + \epsilon(\grad v,\beta \psi) - \epsilon(\grad v,\curl z)  \\
+&=\epsilon \langle [\tau \cdot n],\psi \rangle - \epsilon  \langle n\cdot \curl z, \jump{v}\rangle-\epsilon(\div \tau, \psi) + \epsilon(\div \left(\beta v\right), \psi).
 \end{align*}
-Since $\div \beta = 0$, we satisfy \eqref{a_req}, and can use Lemma \ref{lemma_grad} (with $f = \frac{1}{\epsilon}\tau$) to bound
-\[
-\epsilon \|\grad \psi\|^2 + \|\psi \|^2 = \frac{1}{\epsilon}\|\tau\|^2
-\]
-By the above bound and triangle inequality, 
-\[
-\|\curl z \| \leq \epsilon \|\grad \psi\| + \|\beta \psi\| + \|\tau\| \lesssim \frac{1}{\sqrt{\epsilon}}\|\tau\|
-\]
-On the other hand, using the decomposition and boundary conditions directly, we can integrate by parts to arrive at
+Note that $\div(\beta v) - \div \tau = 0$ removes the contribution of the pairings on the domain and leaves us with only boundary pairings.
+By definition of the boundary norms on $\jump{\tau\cdot n}$ and $\jump{v}$ and the fact that $\curl z$ is trivially in $H({\rm div}, \Omega)$,
 \begin{align*}
-\|\tau\|^2 &= (\tau, \epsilon \grad \psi - \beta \psi + \curl z) = (\tau, \epsilon \grad \psi) - (\tau,\beta \psi) + (\tau,\curl z)  \\
-&=(\tau, \epsilon \grad \psi) + \epsilon(\grad v,\beta \psi) - \epsilon(\grad v,\curl z)  \\
-&=\epsilon \langle [\tau \cdot n],\psi \rangle - \epsilon  \langle n\cdot \curl z, [v]\rangle = \epsilon \langle [\tau \cdot n],\psi \rangle_{\Gamma_h \setminus \Gamma_+} - \epsilon  \langle n\cdot \curl z, [v]\rangle_{\Gamma_h \cup \Gamma_+}\\
-&\lesssim \epsilon \|[\tau \cdot n]\| \|\psi\| + \epsilon \| [v]\|\| n\cdot \curl z \| 
+\|\tau\|_{L^2}^2 &=\epsilon \langle [\tau \cdot n],\psi \rangle -
+\epsilon \langle n\cdot \curl z, \jump{v}\rangle = \epsilon \langle [\tau
+  \cdot n],\psi \rangle_{\Gh \setminus \Gamma_+} - \epsilon
+\langle n\cdot \curl z,\jump{v}\rangle_{\Gh \setminus
+  \left(\Gamma_-\cup \Gamma_0\right)}\\ &\lesssim \epsilon \|[\tau
+  \cdot n]\| \|\psi\|_{H^1(\Omega)} + \epsilon \| \jump{v}\|\| \curl z
+\|_{L^2}.
 \end{align*}
-by definition of the boundary norms on $[\tau\cdot n]$ and $[v]$.
-
-Applying the above estimates for $\|\psi\|$ and $\|n\cdot \curl z\|$ and noting that $\|\grad v\| = \frac{1}{\epsilon}\|\tau\|$ completes the proof.
+Applying the bounds $\|\psi\|_{H^1(\Omega)}  \leq \frac{1}{\epsilon}\|\tau\|_{L^2}$ and 
+$\|\curl z\|_{L^2} \lesssim \frac{1}{\sqrt{\epsilon}}\|\tau\|_{L^2}$, and noting that $\|\grad v\| = \frac{1}{\epsilon}\|\tau\|$ completes the proof.
 \end{proof}
-
-\subsection{Comparison of boundary conditions}
-
-It is worth addressing the effect of boundary conditions on stability.
-Specifically, a test norm that provides stability for one set of boundary conditions may perform poorly for another set.
-Take, for example, the test norm defined in Section~\ref{sec:main_bounds} and the convection-diffusion problem with Dirichlet boundary conditions.
-
-The bilinear form for the case of Dirichlet boundary conditions is 
-\[
-b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) + \langle \widehat{u}, \left[\tau \cdot n\right] \rangle_{\Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_h}
-\]
-%Notice that the boundary terms in the final bilinear form are different; hence, the adjoint problems associated with Section~\ref{sec:strategy3} will now carry different boundary conditions as well.
-Likewise, the stability properties proven previously will not hold under a different set of boundary conditions.
-%We note that 
-%\begin{align*}
-%b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_h}
-%&= \| u \|^2_{L^2}
-%\end{align*}
-%for the specific continuous test functions $\tau$ and $v$ satisfying
-%\begin{align*}
-%\div \tau - \beta \cdot \grad v &= u \\
-%\frac{1}{\epsilon}\tau + \grad v &= 0
-%\end{align*}
-%with boundary condition $\left.v\right|_\Gamma = 0$.
-Choosing a continuous conforming test function $v$ removes the contribution of the term $\langle \widehat{f}_n, \left[v\right] \rangle$ on the mesh skeleton, while the boundary conditions remove the contribution of boundary terms from the bilinear form.
-Then, for this specific choice of $\left(\tau, v\right)$,
-%\begin{align*}
-%\|u\|_{L^2}^2 &= b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right)}{\|\left(\tau, v\right)\|_V}\|\left(\tau, v\right)\|_V \leq \|u\|_E \|\left(\tau, v\right)\|_V
-%\end{align*}
-%At minimum, we want $\|u\|_{L^2} \lesssim \|u\|_E$, which requires 
-%\[
-%\|\left(\tau, v\right)\|_V \lesssim \| u \|_{L^2}
-%\]
-%for any choice of $u \in L^2$ (dividing through by $\|u\|_{L^2}$ gives the desired result).
-This can be considered a ``sanity check"; at the minimum, we at least want control over the behavior of the single field variable $u$.
-However, we are unable to prove this in the case of Dirichlet boundary conditions.
-
-The robust bounds given in Section~\ref{sec:main_bounds} hold in arbitrary dimension; however, we can show that for the case of Dirichlet boundary conditions, the same results will not hold, even in 1D.
-
-In 1D, the problem reduces to 
-\begin{align*}
-\frac{1}{\epsilon}\sigma - u' &= 0\\
-\left(u - \epsilon \sigma \right)' &=f
-\end{align*}
-with bilinear form
-\begin{align*}
-b\left(\left(u,\sigma,\widehat{u},\widehat{f}\right),\left(\tau,v\right)\right) &= \sum_{k=1}^N \left(\left.\widehat{u}(x) \tau(x)\right |^{x_k}_{x_{k-1}} + \left.\widehat{f}(x) v(x)\right |^{x_k}_{x_{k-1}}\right) \\
-&+ \left(\sigma,\epsilon^{-1}\tau\right)_{\Omega_h} + (u,\tau')_{\Omega_h}- \left(u - \epsilon \sigma,v'\right)_{\Omega_h}
-\end{align*}
-where $\widehat{u}(x), \widehat{f}(x) \in \mathbb{R}$ are now point values defined on mesh points $x_k$ for $k=1,\ldots,N$, where there are $N$ elements.
-We can assume without loss of generality that $\Omega_h$ is the unit interval $(0,1)$.
-
-%A norm for can be defined through $$\|u\|_U = C_1\|u\|_{L^2} + C_2\|\sigma\|_{L^2} + C_3\sum_k \left(|\widehat{u}|+ |\widehat{f}|\right),$$ as the fluxes are simply point values in 1D.  
-%The induced norm $\|\left(\tau,v\right)\|_{V,U}$ is
-%\begin{align*}
-%\|\left(\tau,v\right)\|_{V,U} &= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}\right)} \frac{ (u,\tau'-v')_{\Omega_h}+ \left(\sigma,\epsilon^{-1}\tau + v'\right)_{\Omega_h}+\sum_k \left(\widehat{u}(x_k) [\tau(x_k)] + \widehat{f}(x_k) [v(x_k)]\right)}{C_1\|u\|_{L^2} + C_2\|\sigma\|_{L^2} + C_3\sum_k \left(|\widehat{u}|+ |\widehat{f}|\right)}\\
-%&\leq \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\sum_k \left([\tau(x_k)] +[v(x_k)]\right)
-%\end{align*}
-%for $f = \epsilon^{-1}\tau + v'$ and $g = \tau'-v'$.
-
-Consider now the 1D analogue of the estimate given by Lemma~\ref{lemma_stream}, which is necessary for robust control over the error in $\|u\|_{L^2}$.
-In 1D, $\|\beta\cdot\grad v\| \lesssim \|g\|$ reduces to the inequality
-\[
-\|v'\|\lesssim \|g\|, \quad g\in L^2{\Omega_h}
-\]
-The adjoint problem corresponding to Lemma~\ref{lemma_stream} in section~\ref{sec:strategy3} is likewise reduced in 1D to the scalar equation
-\begin{align}
-\epsilon v'' + v' &= -g \label{adjoint_1D}
-\end{align}
-with $v\in H^1_0\left((0,1)\right)$.  Multiplying this equation by $v'$ and integrating over $\Omega_h$ gives
-\[
-\int_0^1 \epsilon v''v' + \|v'\|_{L^2}^2 = -\int_0^1 g v'
-\]
-Integrating by parts and Young's inequality give
-\begin{align*}
--\left.\frac{\epsilon}{2} v'^2\right|_0^1 + \|v'\|_{L^2}^2 &\leq \frac{1}{2}\|g\| + \frac{1}{2}\|v'\|
-\end{align*}
-implying that
-\begin{align*}
-\frac{\epsilon}{2} v'(0)^2 + \|v'\|_{L^2}^2 & \lesssim \|g\| 
-\end{align*}
-Let us restrict ourselves to the cases where $v$ is sufficiently smooth for $v'(0)$ to be well defined.
-Taking $g=1$ (corresponding to a constant approximation) we can solve \eqref{adjoint_1D} exactly to see that
-\[
-v(x) = \frac{e^{-\frac{x}{\epsilon}}}{e^{\frac{1}{\epsilon}}-1}\left(e^{\frac{1}{\epsilon}}\left(e^{\frac{x}{\epsilon}}-1\right) + \left(e^{\frac{1}{\epsilon}}-1\right)e^{\frac{x}{\epsilon}}x\right)
-\]
-Plotting the solution shows that $v$ develops strong boundary layers of width $\epsilon$ near the inflow.
-Consequently, $\frac{\epsilon}{2} v'(0)^2 \approx \epsilon^{-1}$, indicating already a lack of robustness in the bound of $\|v'\|$ by $\|g\|$ for constant data\footnote{Unlike the case of Dirichlet boundary conditions, the inflow condition on $ \widehat{f} = u(0)-\epsilon u'(0)$ induces an adjoint boundary condition $\tau(0)=0$, or equivalently $v'(0) = 0$, removing the non-robust term from the estimate.}.
-The robust bound from below of $g$ constant corresponds to the robust control of the approximation of field variable $u$ by a constant.
-More detailed 1D error bounds for Dirichlet boundary conditions are provided in \cite{DPG3}, and also indicate a lack of robustness when using the standard broken Sobolev norm as the test norm on $\tau$ and $v$.
-
-Intuitively, the adjoint problem is similar to the primal problem with the direction of inflow reversed, such that the inflow becomes the outflow, and outflow inflow.
-The need for the weight arises due to the presence of the Dirichlet boundary condition on $v$ near the inflow; this induces strong boundary layers at the inflow such that $\grad v \approx \epsilon \|\grad v\|^2 \approx O(\epsilon^{-1})$.
-An interesting phenomenon observed is that, for sufficiently small $\epsilon$, these issues manifest themselves in numerical experiments as additional refinements near the inflow\footnote{Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
-\[
-\|\left(\tau, v\right)\|_{V,w}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\|_{w+\epsilon} + \| \div \tau\|_{w+\epsilon} + \frac{1}{\epsilon}\|\tau\|_{w+\epsilon}
-\]
-where $\|\cdot \|_{w+\epsilon}$ is a weighted $L^2$ norm, where the weight $w \in (0,1)$ is required to vanish on $\Gamma_-$ and satisfy $\grad w = O(1)$.
-The need for the weight is necessary to account for the loss of robustness at the inflow.}.
-The presence of the new boundary condition relaxes the outflow boundary condition for the adjoint/dual problem, resulting in stronger stability estimates for the adjoint, and a better robustness result for the primal problem.
-
-%We improve upon the result of Demkowicz and Heuer not by modifying the test norm, but by adopting a new inflow boundary condition, which changes the stability properties of the corresponding adjoint equation.
-Under these new boundary conditions, we can prove robust control over $\|u\|_{L^2}$ using the unweighted version of the test norm in \cite{DPGrobustness}
-%\[
-%\|\left(\tau, v\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2
-%\]
-%This test norm is implied by certain norm ``building blocks"; stability analysis of the adjoint equation allows us to bound from above norms and seminorms on $v$ and $\tau$ by $\|f\|_{L^2}$ and $\|g\|_{L^2}$ in ways that do not grow as $\epsilon \rightarrow 0$, and we assemble the test norm as combinations of such norms and seminorms on $v$ and $\tau$.
-
-\section{Numerical experiments}
-
-In our numerical experiments, we will be interested in the use of the unweighted test norm 
-\[
-\|\left(\tau, v\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2
-\]
-However, the presence of both $\|v\|$ and $\epsilon\|\grad v\|$ terms, and similarly $\|\div \tau\|$ and $\frac{1}{\epsilon}\|\tau\|$ terms, induces boundary layers in the optimal test functions.
-We can see this by recovering the strong form of the variational problem defining test functions.
-Assume first that $\tau = 0$.
-Then, assuming $\div \beta = 0$ for illustrative purposes, we have
-\begin{align*}
-\left(\left(0,v\right),\left(\delta\tau,\delta v\right)\right)_{V} &= (v,\delta v) + \epsilon \left(\grad v,\grad \delta v\right) + \left(\beta \cdot \grad v, \beta \cdot \grad \delta v\right)\\
-&= \left(v - \epsilon \Delta v - \div \left(\left(\beta \otimes \beta\right) \grad v\right), \delta v\right)_{L^2} + \langle \epsilon \grad v\cdot n, \delta v\rangle + \langle n\cdot \left(\beta\otimes\beta\right) \grad v , \delta v\rangle
-\end{align*}
-after integration by parts, recovering the strong form of the operator $L$ inducing such a variational problem 
-\[
-Lv \coloneqq v - \epsilon \Delta v - \div \left(\left(\beta \otimes \beta\right) \grad v\right)
-\]
-The streamline direction $\beta$ induces an anisotropic diffusion, while the $\epsilon\|\grad v\|_{L^2}$ term induces a small isotropic diffusion contribution everywhere.
-Any vector in the cross-stream direction is in the null space of the anisotropic diffusion tensor, such that in the cross-stream directions, the optimal test function is governed only by the cross-stream part of the operator $L$
-\[
-L_{\rm cross} \coloneqq v - \epsilon \Delta v 
-\]
-and may develop boundary layers of width $\epsilon$ in those directions.
-To avoid boundary layers in the optimal test functions, we follow \cite{DPGrobustness} in scaling the $L^2$ contributions of $v$ and $\tau$ such that, when transformed to the reference element, both $v$ and $\grad v$ terms are $O(1)$.
-In this paper, we consider only isotropic refinements on quadrilateral elements in 2D, such that $h_1 = h_2 = h$, and $|K| = h^2$.
-Our test norm for an element $K$ is now
-\[
-\|\left(\tau, v\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2
-\]
-This modified test norm avoids boundary layers, but for adaptive meshes, provides additional stability in areas of heavy refinement, where best approximation error tends to be large and stronger robustness is most necessary.
-This leads to a test norm which produces easily approximable optimal test functions, but still provides \textit{asymptotically} the strongest test norm and tightest robustness results in the areas of highest error.
-
-%Intuitively, this is justifiable by the fact that best approximation error is typically only large near where refinements tend to aggregate.
-
-%Additionally, test norms that differ from element to element fit cleanly into the DPG framework - as the best approximation error tends to be negligible in areas where the solution is , the finite element error will be small in those areas, even with slightly suboptimal robustness.
-
-In each numerical experiment, we vary $\epsilon = .01, .001, .0001$ in order to demonstrate robustness over a range of $\epsilon$.
-This is intended to mirror the experience with roundoff effects in numerical experiments \cite{DPGrobustness}; for ``worst-case" linear solvers, such as LU decomposition without pivoting, the effect of roundoff error becomes evident in the solving of optimal test functions for $\epsilon \leq O(1e-5)$.
-The roundoff itself comes from the conditioning of the Gram matrix under certain test norms; for example, if the weighted $\left(H({\rm div};\Omega), H^1(\Omega)\right)$ norm is used for the test norm $\|\left(\tau,v\right)\|_V$ (as was done in \cite{DPG2}), for an element of size $h$, $\|v\|_{L^2}^2 = O(h)$, while $\|\grad v\|_{L^2}^2 = O(h^{-1})$.
-As $h\rightarrow 0$, the seminorm portion of the test norm dominates the Gram matrix, leading to a near-singular and ill-conditioned system.
-
-The effect of roundoff error is often characterized by an increase in the energy error, which (assuming perfect approximability of test functions) is proven to decrease for any series of refined meshes.
-These roundoff effects are dependent primarily on the mesh, appearing when trying to fully resolve boundary layers for very small $\epsilon$.
-
-%\textcolor{red}{Add figure here on convergence for smaller epsilon}
-
-\subsection{Erickson model problem}
-
-For the choice of $\Omega = (0,1)^2$ and $\beta = (1,0)^T$, the convection diffusion equation reduces to
-\[
-\pd{u}{x} - \epsilon \left(\pdd{u}{x}+ \pdd{u}{y}\right) = 0
-\]
-which has an exact solution by separation of variables, allowing us to analyze convergence of DPG for a wide range of $\epsilon$.
-For boundary conditions, we impose $u=0$ on $\Gamma_+$ and $\beta_n u - \sigma_n$ on $\Gamma_-$, which reduces to
-\begin{align*}
-u-\sigma_x &= u_0-\sigma_{x,0}, \quad x=0\\
-\sigma_y &=  0, \quad y=0,1\\
-u &= 0, \quad x=1\\
-\end{align*}
-In this case, our exact solution is the series
-\[
-u(x,y) = C_0 + \sum_{n=1}^\infty C_n \frac{\exp(r_2(x-1)-\exp(r_1(x-1)))}{r_1\exp(-r2) - r_2\exp(-r1)}\cos(n\pi y)
-\]
-where
-\begin{align*}
-r_{1,2} &= \frac{1 \pm \sqrt{1 + 4 \epsilon\lambda_n}}{2 \epsilon}\\
-\lambda_n &= n^2\pi^2 \epsilon
-\end{align*}
-The constants $C_n$ depend on a given inflow condition $u_0$ at $x=0$ via the formula
-\[
-C_n = \int_0^1 u_0(y) \cos(n\pi y)
-\]
-
-\subsubsection{Solution with $C_1 = 1, C_{n\neq 1} = 0$}
-
-We begin with the solution taken to be the first non-constant mode of the above series.
-We set the inflow boundary condition to be exactly the value of $u-\sigma_x$ corresponding to the exact solution.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.37]{figs/wallBC_exact_u.png}
-}
-\subfigure{
-\includegraphics[scale=.37]{figs/wallBC_exact_sigx.png}
-}
-\subfigure{
-\includegraphics[scale=.37]{figs/wallBC_exact_sigy.png}
-}
-\caption{Solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
-\end{figure}
-In each case, we begin with a square 4 by 4 mesh of quadrilateral elements with order $p=3$.
-We choose $\Delta p = 5$, though we note that the behavior of DPG is nearly identical for any $\Delta p > 3$.
-$h$-refinements are executed using a greedy refinement algorithm, where element energy error $e_K^2$ is computed for all elements $K$, and elements such that $e_K^2 \leq \alpha \max_K e_K^2$ are refined.
-We make the arbitrary choice of taking $\alpha = .2$ for each of these experiments.
-
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=.4]{figs/u_pointdiff_wallBC.png}
-\caption{Adapted mesh and pointwise error for $\epsilon=.01$}
-\end{figure}
-We are especially interested in the ratio of energy error and total $L^2$ error in both $\sigma$ and $u$, which we denote as $\|u-u_h\|_{L^2}$.
-Stability estimates imply that, using the above test norm, $\|u-u_h\|_{L^2} / \|u-u_h\|_E \leq C$ independent of $\epsilon$.
-Figure~\ref{ratios_simple}, which plots the ratio of $L^2$ to energy error, seems to imply that (at least for this model problem) $C=O(1)$.
-Additionally, while we do not have a robust lower bound ($\|u-u_h\|_{L^2} / \|u-u_h\|_E$ can approach $0$ as $\epsilon \rightarrow 0$), our numerical results appear to indicate the existence of an $\epsilon$-independent lower bound.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{figs/errorrates_wallBC.png}
-}
-\subfigure{
-\includegraphics[scale=.38]{figs/L2energyratio_wallBC.png}
-}
-\caption{$L^2$ and energy errors, and their ratio for $\epsilon=.01$, $\epsilon=.001$, $\epsilon=.0001$}
-\label{ratios_simple}
-\end{figure}
-The effect of a mesh dependent test norm can be seen in the ratios of $L^2$ to energy error; as the mesh is refined, the constants in front of the $L^2$ terms for $v$ and $\tau$ converge to stationary values (providing the full robustness implied by our adjoint energy estimates), and the ratio of $L^2$ to energy error transitions from a smaller to a larger value.
-The transition point happens later for smaller $\epsilon$, which we expect, since the transition of the ratio corresponds to the introduction of elements whose size is of order $\epsilon$ through mesh refinement.
-
-We examined how small $\epsilon$ needed to be in order to encounter roundoff effects as well.
-In \cite{DPGrobustness}, the smallest resolvable $\epsilon$ using only double precision arithmetic was $1e-4$.
-The solution of optimal test functions is now done using both pivoting and equilibration, improving conditioning.
-Roundoff effects still appear, but at smaller values of $\epsilon$.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{figs/roundoff_rates.png}
-}
-\subfigure{
-\includegraphics[scale=.38]{figs/roundoff_ratio.png}
-}
-\caption{Energy error and $L^2$/energy error ratio for $\epsilon=1e-5$, $\epsilon=1e-6$, $\epsilon=1e-7$.
-Non-monotonic behavior of the energy error indicates conditioning issues and roundoff effects.}
-\label{roundoff_figures}
-\end{figure}
-
-Without anisotropic refinements, it still becomes computationally difficult to fully resolve the solution for $\epsilon$ smaller than $1e-5$.
-Regardless, for all ranges of $\epsilon$, DPG does not lose robustness, as indicted by the rates and ratio between $L^2$ and energy error in Figure~\ref{roundoff_figures} remaining bounded from both above and below.
-For $\epsilon = 1e-5$, we observe that the ratio of $L^2$ error increases, corresponding to the scaling of the test norm with mesh size (the transition in test norm occurs after 8 refinements, which, for an initial $4\times 4$ mesh, implies a minimum element size of about $1.5e-05$.
-At this point, rescaled test norm allows us to take advantage of the full magnitude of the $L^2$ term for $\|v\|$ and $\|\tau\|$ implied by our adjoint estimates).
-By analogy, for smaller $\epsilon = 1e-6, 1e-7$, the transition period should begin near the 10th and 11th refinement iterations; however, we do not observe such behavior, possibly due to roundoff effects.
-For $\epsilon=1e-6$, the ratio simply remains constant, but for $\epsilon=1e-7$, we observe definite roundoff effects, as the energy error increases at the 11th refinement.
-Since DPG is optimal in the energy norm for a fixed test norm\footnote{While the test norm changes with the mesh, it increases monotonically.
-A strictly stronger test norm implies $\frac{b(u,v)}{\|v\|_1} \geq \frac{b(u,v)}{\|v\|_2}$ for any $\|v\|_1 \leq \|v\|_2$}, we expect monotonic decrease of the energy error with mesh refinement.
-Non-monotonic behavior indicates either approximation or roundoff error, and as there was no qualitative difference between using $\Delta p = 5$ and $\Delta p = 6$ for these experiments, we expect that the approximation error is negligible and conclude roundoff effects are at play.
-
-\subsubsection{Neglecting $\sigma_n$}
-
-In practice, we will not have prior knowledge of $\sigma_n$ at the inflow, and will have to set $\beta_n u - \sigma_n = u_0$, ignoring the viscous contribution to the boundary condition.
-The hope is that for small $\epsilon$, this omission will be negligible.
-Figure~\ref{ratios_noSigma} indicates that, between $\epsilon = .005$ and $\epsilon = .001$, the omission of $\sigma_n$ in the boundary condition becomes negligible, and both our error rates and ratios of $L^2$ to energy error become identical to the case where $\sigma_n$ is explicitly accounted for in the inflow condition.
-For large $\epsilon = .01$, the $L^2$ error stagnates around $1e-3$, or about $7\%$ relative error.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{figs/rates_noSigma.png}
-}
-\subfigure{
-\includegraphics[scale=.38]{figs/ratio_noSigma.png}
-}
-\caption{$L^2$ and energy errors and their ratio when neglecting $\sigma_n$ at the inflow.}
-\label{ratios_noSigma}
-\end{figure}
-
-\subsubsection{Discontinuous inflow data}
-
-We note also that an additional advantage of selecting this new boundary condition is a relaxation of regularity requirements; as $\widehat{f}_n \in H^{-1/2}(\Omega)$, strictly discontinuous inflow boundary conditions are no longer ``variational crimes".
-We consider the discontinuous inflow condition
-\[
-u_0(y) = \begin{cases}
-(y-1)^2, \quad &y>.5\\
--y^2, \quad &y\leq .5 
-\end{cases}
-\]
-as an example of a more difficult test case.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{figs/disc_hat.png}
-}
-\subfigure{
-\includegraphics[scale=.38]{figs/disc_hat_surf.png}
-}
-\caption{Solution variables $u$ and $\widehat{u}$ with discontinuous inflow data $u_0$ for $\epsilon = .01$.}
-\label{disc_sol}
-\end{figure}
-Figure~\ref{disc_sol} shows the solution $u$ and overlaid trace variable $\widehat{u}$, which both demonstrate the regularizing effect of viscosity on the discontinuous boundary condition at $x=0$.
-However, we do not have a closed-form solution with which to compare results for a stricly discontinuous $u_0$.
-In order to analyze convergence, we approximate $u_0$ with 20 terms of a Fourier series, giving a near-discontinuity for $u_0$.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{figs/rates_disc.png}
-}
-\subfigure{
-\includegraphics[scale=.38]{figs/ratio_disc.png}
-}
-\caption{$L^2$ and energy errors, and their ratio for $\epsilon=.01$, $\epsilon=.001$, $\epsilon=.0001$, with discontinuous $u_0$ approximated by a Fourier expansion. }
-\label{disc_sol_fourier}
-\end{figure}
-
-The ratios of $L^2$ to energy error are now less predictable than for the previous example, in part due to the difficulty in approximating highly oscillatory boundary conditions.
-The numerical experiments were originally performed by applying boundary conditions via interpolation; the result was that the highly oscillatory inflow boundary condition was not sampled enough to be properly resolved, causing the solution to converge to a solution different than the exact solution.
-The experiments were repeated using the penalty method to enforce inflow conditions; however, we note that the proper way to do so is to use an $L^2$ projection at the boundary.
-Even when using the penalty method, however, the ratios still remain bounded and close to $1$ for $\epsilon$ varying over two orders of magnitude, as predicted by theory.
-
-\section{Conclusions}
-
-None yet.  Ideas:
-\begin{itemize}
-\item Explanation of choice of boundary condition and why it impacts stability
-\item Interpretation of weight as allowing diffusion to work on the boundary.  
-\item Note results have worked for Burgers, and expand on how they would apply to Navier-Stokes
-\end{itemize}
-
-\bibliographystyle{plain}
-\bibliography{paper}
-
-\end{document}

### 2012-06-15 docs/Jesse/Proposal/proposalIntro.tex
put together rough proposal with a few missing sections

--- 2012-06-13 docs/Jesse/Proposal/outline.tex
@@
-\documentclass{report}
-
-\usepackage{array}
-\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
-\usepackage[utf8]{inputenc}
-\usepackage{listings}
-\usepackage{mathtools}
-\usepackage{dsfont}
-\usepackage{pdfpages}
-\usepackage[textsize=footnotesize,color=green]{todonotes}
-\usepackage{algorithm, algorithmic}
-\usepackage{bm}
-\usepackage{tikz}
-\usepackage[normalem]{ulem}
-
-\usepackage{graphicx}
-\usepackage{subfigure}
-\usepackage{color}
-\usepackage{undertilde}
-\usepackage[colorlinks = true, filecolor = red, urlcolor = blue, linkcolor = black]{hyperref}
-\usepackage{pdflscape}
-\usepackage{pifont}
-%\usepackage{fullpage}
-\setlength\textwidth{6in}
-\setlength\textheight{8in}
-\setlength\oddsidemargin{0.25in} % LaTeX adds a default 1in to this!
-\setlength\evensidemargin{0.25in}
-\setlength\topmargin{-0.0in} % LaTeX adds a default 1in to this!
-\setlength\headsep{0in}
-\setlength\headheight{0in}
-\setlength\footskip{1in}
-
-\renewcommand{\topfraction}{0.85}
-\renewcommand{\textfraction}{0.1}
-\renewcommand{\floatpagefraction}{0.75}
-
-\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
-\newcommand{\tensor}[1]{\underline{\vect{#1}}}
-\newcommand{\del}{\triangle}
-\newcommand{\grad}{\nabla}
-\renewcommand{\div}{\grad \cdot}
-\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
-\newcommand{\eip}[1]{a\left( #1 \right)}
-\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
-\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
-
-\newcommand{\circone}{\ding{192}}
-\newcommand{\circtwo}{\ding{193}}
-\newcommand{\circthree}{\ding{194}}
-\newcommand{\circfour}{\ding{195}}
-\newcommand{\circfive}{\ding{196}}
-
-\newcommand{\Reyn}{\rm Re}
-
-\newcommand{\bs}[1]{\boldsymbol{#1}}
-\DeclareMathOperator{\diag}{diag}
-
-\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}
-
-\newcommand{\tablab}[1]{\label{tab:#1}}
-\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
-
-\newcommand{\theolab}[1]{\label{theo:#1}}
-\newcommand{\theoref}[1]{\ref{theo:#1}}
-\newcommand{\eqnlab}[1]{\label{eq:#1}}
-\newcommand{\eqnref}[1]{\eqref{eq:#1}}
-\newcommand{\seclab}[1]{\label{sec:#1}}
-\newcommand{\secref}[1]{\ref{sec:#1}}
-\newcommand{\lemlab}[1]{\label{lem:#1}}
-\newcommand{\lemref}[1]{\ref{lem:#1}}
-
-\newcommand{\mb}[1]{\mathbf{#1}}
-\newcommand{\mbb}[1]{\mathbb{#1}}
-\newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\nor}[1]{\left\| #1 \right\|}
-\newcommand{\snor}[1]{\left| #1 \right|}
-\newcommand{\LRp}[1]{\left( #1 \right)}
-\newcommand{\LRs}[1]{\left[ #1 \right]}
-\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
-\newcommand{\LRc}[1]{\left\{ #1 \right\}}
-\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
-\newcommand{\Grad} {\ensuremath{\nabla}}
-\newcommand{\Div} {\ensuremath{\nabla\cdot}}
-\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
-\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
-\newcommand{\uh}{\widehat{u}}
-\newcommand{\fnh}{\widehat{f}_n}
-\renewcommand{\L}{L^2\LRp{\Omega}}
-\newcommand{\pO}{\partial\Omega}
-\newcommand{\Gh}{\Gamma_h}
-\newcommand{\Gm}{\Gamma_{-}}
-\newcommand{\Gp}{\Gamma_{+}}
-\newcommand{\Go}{\Gamma_0}
-\newcommand{\Oh}{\Omega_h}
-
-\newcommand{\eval}[2][\right]{\relax
-  \ifx#1\right\relax \left.\fi#2#1\rvert}
-
-\def\etal{{\it et al.~}}
-
-\def\arr#1#2#3#4{\left[
-\begin{array}{cc}
-#1 & #2\\
-#3 & #4\\
-\end{array}
-\right]}
-\def\vecttwo#1#2{\left[
-\begin{array}{c}
-#1\\
-#2\\
-\end{array}
-\right]}
-\def\vectthree#1#2#3{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-\end{array}
-\right]}
-\def\vectfour#1#2#3#4{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-#4\\
-\end{array}
-\right]}
-\date{}
-\author{Jesse Chan}
-\title{Proposal outline/notes}
-
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-
-\begin{document}
-
-\tableofcontents
-\maketitle
-
-\chapter{Introduction}
-
 \section{Motivations}
 
-Adaptivity and stability for CFD problems are issues for high Reynolds and Mach numbers. 
-\todo{FINISH}
+Over the last three decades, the use of Computational Fluid Dynamics as an engineering and design tool in design of aircraft has become common.
+Wind tunnel experiments are often complemented by computational simulations, and the simulation of off-design conditions.
+Great advances have been made in the field since its introduction, especially in areas of meshing, computer architecture, and solution strategies.
+Despite this, there still exist many computational limitations in existing CFD methods:
+\begin{itemize}
+\item \textbf{Higher order methods :} Higher order methods stand to offer large computational savings through a more efficient use of discrete degrees of freedom.
+However, there are very few working higher-order CFD codes in existence, and most higher order methods tend to degrade to first-order accuracy near shocks.
+The use of higher order codes to solve the steady state equations is even rarer, where convergence of discrete nonlinear steady equations is a tricky issue \cite{BoeingHigherOrder}.
+\item \textbf{Automatic adaptivity :} The use of adaptive meshes is crucial to many CFD applications, where the solution often exhibits very localized sharp gradients and shocks.
+Good resolution for such problems under uniform meshes is computationally prohibitive and impractical for most physical regimes of interest.
+However, the construction of ``good" meshes is a difficult task, usually requiring a-priori knowledge of the form of the solution.
+An alternative to such is the construction of automatically adaptive schemes; such methods usually begin with a coarse mesh and refine based on the minimization of some error.
+However, this task is difficult, as the convergence of numerical methods for problems in CFD is notoriously sensitive to mesh quality.
+Additionally, the use of adaptivity becomes even more difficult in the context of higher order and $hp$ methods \cite{BoeingHigherOrder}.
+\end{itemize}
+Both of these issues are tied to the notion of \emph{robustness}.  We define robustness loosely as the degradation of solution quality with respect
 
-Address the fact that CFD problems have issues of robustness; introduce reasoning that we will study the model problem of convection-diffusion first to better understand this.
+typical physical conditions of interest for the compressible Navier-Stokes equations involve low viscosity/high Reynolds numbers.
+
+Higher order adaptivity and stability for CFD problems are issues for high Reynolds and Mach numbers. 
+\todo{Address the fact that CFD problems have issues of robustness; introduce reasoning that we will study the model problem of convection-diffusion first to better understand this. }
 
@@
 
-For the past half-century, problems in computational fluid dynamics (CFD) have been solved using a multitude of methods, many of which are physically motivated, and thus applicable only to a small number of problems and geometries.
+For the past half-century, problems in CFD have been solved using a multitude of methods, many of which are physically motivated, and thus applicable only to a small number of problems and geometries.
 We consider more general methods, whose framework is applicable to different problems in CFD; however, our specific focus will be on the nonlinear shock problems of compressible aerodynamics.
@@
 Discontinuous Galerkin (DG) methods form a subclass of FEM; first introduced by Reed and Hill in \cite{Reed:73}, these methods were later analyzed by Cockburn and Shu \cite{CockburnShu:DG} and have rapidly gained popularity for CFD problems.
-Rather than having a continuous basis where the basis function support spans several element cells, DG opts instead for a discontinuous, piecewise polynomial basis, where, like FV schemes, a numerical flux facilitates communication between neighboring elements (unlike FV methods, however, there is no need for a reconstruction step).
 Advantages of DG methods include the local conservation property, easily modified local orders of approximation, easy adaptivity in both $h$ and $p$, and efficient parallelizability.
+Rather than having a continuous basis where the basis function support spans several element cells, DG opts instead for a discontinuous, piecewise polynomial basis, where, like FV schemes, a \emph{numerical flux} facilitates communication between neighboring elements (unlike FV methods, however, there is no need for a reconstruction step).
 
-An additional reason for the popularity of DG methods is that they can be interpreted as stabilized FE methods through appropriate choices of the numerical flux \cite{Brezzi20063293}.
+The formal definition of the numerical flux (attributed to Peter Lax) on an element boundary is some function of the values on the edges of both the neighboring elements.
+An additional reason for the popularity of DG methods is that they can be interpreted as stabilized FE methods through appropriate choices of this numerical flux \cite{Brezzi20063293}.
 We will illustrate this with the pure convection equation in 1D ---
@@
 \end{align*}
-Notice the specific choice of $v(x_K)$ --- we have chosen the value of $v(x_K)$ to be the value in the upwind direction.
+We will refer to $v(x_K^+)$ as the upwind value of $v(x_K)$, and refer to DG under this specific choice of traces as upwind DG.
+This specific choice of $v(x_K)$ as the upwind value is crucial; similarly to SUPG, the upwind DG emphasizes the test function in the direction of convection and changes the way the residual is measured.
+As it turns out, the performance of DG for convection-type problems is closely tied to this upwinding --- choosing the value of $v(x_K)$ to be the downwind value $v(x_K^-)$ leads to an unstable method, while choosing $v(x_K)$ to be the average of the upwind and downwind values leads to a DG method with suboptimal stability properties, similar to an $H^1$-conforming continuous Galerkin approximation\cite{Brezzi20063293}.
 
-\todo{Add 1D description and diagrams (Hughes book) of DG formulation for convection with upwind flux.}
-
+Another perspective on the use of the numerical flux in DG methods is that the selection of specific DG fluxes imparts \emph{additional regularity} where needed.
 For example, for the pure convection problem, the solution has a distributional derivative in the streamline direction, but is only $L^2$ in the crosswind direction.
 As a consequence of the regularity of the solution, the boundary trace of the solution is defined only in the direction of convection.
-The upwind DG method addresses the above issue by choosing the numerical flux to be the upwind flux; in this case, the DG numerical flux can be viewed as imparting additional regularity than is present in the solution \cite{DPG1,DPG3}.
+The upwind DG method addresses the above issue by choosing the numerical flux to be the upwind flux; in this case, the DG numerical flux can be viewed as imparting additional regularity to the discrete solution than is implied by the continuous setting \cite{DPG1,DPG3}.
+
+\subsubsection{HDG}
 
@@
 Neighboring elements are coupled together only through these degrees of freedom, which can be interpreted as Lagrange multipliers enforcing weak continuity of the trial space.
-Additionally, HDG methods \todo{add bit about numerical fluxes still used, stabilization param}
+Additionally, HDG methods \todo{add bit about numerical fluxes still used, stabilization params}
 
@@
 
-\chapter{Range of CFD problems}
+\section{Range of CFD problems}
 
@@
 \end{itemize}
-
-\chapter{Discontinuous Petrov-Galerkin: a minimum residual method for linear problems}
-
-The Discontinuous Petrov-Galerkin (DPG) method of Demkowicz and Gopalakrishnan was first formulated in \cite{DPG1} for the pure convection problem.
-
-Historically, the name DPG was given by Bottasso, Micheletti, Sacco and Causin to their method for elliptic problems in \cite{BottassoMichelettiSacco02}.
-The method was then extended to other problems, including convection-diffusion, in \cite{BottassoMichelettiSacco05,CausinSacco05,CausinSaccoBottasso05}.
-
-The key point in the method of Bottasso et al.\ was their method of hybridization of fluxes.
-Whereas HDG methods will identify an additional flux unknown on the boundary, the numerical flux coupling neighboring elements together is still typically computed in part using contributions from the field variables.
-In the DPG formulation, all numerical fluxes are declared to be independent unknowns, leaving the interior field degrees of freedom completely uncoupled from element to element.
-\todo{Finish, check if this is true.}
-
-The breakthrough came in \cite{DPG2}, where the concept of locally-computable optimal test functions led to the development of the DPG method in its current form.
-
-\todo{Clean up}
-This DPG method with optimal test functions is better understood in \cite{DPG3,DPG4}, extended to problems in \cite{DPGElas,stokesDPG}, well-posedness theory developed for Poisson and convection-diffusion in \cite{analysisDPG}, extended to large class of Friedrichs systems in \cite{Bui-ThanhDemkowiczGhattas11b}.
-\cite{practicalDPG}.
-
-Optimal order comparison to DG in \cite{DPG1}. Comparisons to other DG methods in \cite{Bui-ThanhDemkowiczGhattas11a,DGDPG}.
-
-\section{Optimal Petrov-Galerkin methods}
-
-\seclab{optimalTest} Petrov-Galerkin methods, in which the test space differs from the trial space, have been explored for over 30 years, beginning with the approximate symmetrization method of Barrett and
-Morton~\cite{BARRETT01101981}.
-The idea was continued with the SUPG method of Hughes, and the characteristic Petrov-Galerkin approach of Demkowicz and Oden~\cite{Demkowicz1986188}, which introduced the
-idea of tailoring the test space to change the norm in which a finite element method would converge.
-
-The idea of optimal test functions was introduced by Demkowicz and Gopalakrishnan in \cite{DPG2}.
-Conceptually, these optimal test functions are the natural result of the minimization of a residual corresponding to the operator form of a variational equation.
-The connection between stabilization and least squares/minimum residual methods has been observed previously \cite{GLS}.
-However, the method in \cite{DPG2} distinguishes itself by measuring the residual of the natural \textit{operator form of the equation}, which is posed in the dual space, and measured with the dual norm, as we now discuss.
-
-Throughout the paper, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U'$ and $V'$ as the respective topological dual spaces.
-Let $U_h \subset U$ and $V_h\subset V$ be finite dimensional subsets.
-We are interested in the following problem
-\begin{equation}
-\eqnlab{variationEq}
-\left\{
-  \begin{array}{l}
-    \text{Given } l \in V', \text{ find } u_h \in U_h  \text{ such that} \\ 
-    b(u_h,v_h) = l(v_h), \quad \forall v_h\in V_h,
-  \end{array}
-  \right.
-\end{equation}
-where $b\LRp{\cdot,\cdot}: U \times V \to \mbb{R}$ is a continuous
-bilinear form.  $U$ is chosen to be some trial space of approximating functions, but $V_h$ is as of yet unspecified.
-
-Throughout the paper, we suppose the variational
-problem \eqnref{variationEq} to be well-posed. In that case, we can
-identify a unique operator $B:U\rightarrow V'$ such that
-\[
-\langle Bu,v\rangle_V \coloneqq b(u,v), \quad u\in U, v\in V
-\]
-with $\LRa{\cdot, \cdot}_V$ denoting the duality pairing between $V'$ and $V$, to obtain the operator form of the continuous variational problem
-\begin{equation}
-\eqnlab{dualEq}
-Bu = l \quad \text{in } V'.
-\end{equation}
-In other words, we can represent the continuous form of our variational equation
-\eqnref{variationEq} equivalently as the operator equation \eqnref{dualEq} with values in the
-dual space $V'$.  This motivates us to consider the conditions under which the solution to \eqnref{variationEq} is the solution to the minimum residual problem in $V'$ 
-\[
-u_h = \underset{u_h\in U_h}{\arg\min}\, J(u_h),
-\]
-where $J(w)$ is defined for $w\in U$ as 
-\[
-J(w) = \frac{1}{2}\|Bw-l\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(w,v)-l(v)|^2}{\nor{v}_V^2}.
-\]
-For convenience in writing, we will abuse the notation $\sup_{v \in V}$ to denote $\sup_{v\in V\setminus\{0\}}$ for the remainder of the paper.
-
-Let us define $R_V: V \to V'$ as the Riesz map, which identifies
-elements of $V$ with elements of $V'$ by 
-\[
-\langle R_V v,\delta
-v\rangle_V \coloneqq(v, \delta v)_V, \quad \forall \delta v \in V.
-\]
-Here, $(\cdot, \cdot)_V$ denotes the
-inner product in $V$. As $R_V$ and its inverse, $R_V^{-1}$, are both
-isometries, e.g.\ $\|f\|_{V'} = \|R_V^{-1} f\|_V, \forall f \in V'$, we
-have
-\begin{equation}
-\eqnlab{minimization}
-\min_{u_h\in U_h} J(u_h) = \frac{1}{2}\left\|Bu_h-l\right\|_{V'}^2 =  \frac{1}{2}\left\|R_V^{-1}(Bu_h-l)\right\|_V^2.
-\end{equation}
-The first order optimality condition for \eqnref{minimization} requires
-the G\^ateaux derivative to be zero in all directions $\delta u \in
-U_h$, i\.e\.,
-\begin{align*}
-\left(R_V^{-1}(Bu_h-l),R_V^{-1}B\delta u\right)_V = 0, \quad \forall \delta u \in U. 
-\end{align*}
-We define, for a given $\delta u \in U$, the corresponding {\em optimal test function} $v_{\delta u}$
-\begin{equation}
-\eqnlab{optv}
-v_{\delta u} \coloneqq R_V^{-1}B\delta u \quad  \text{in } V.
-\end{equation} 
-The optimality condition then becomes
-\[
- \langle Bu_h-l, v_{\delta u}\rangle_V = 0, \quad \forall \delta u \in U
-\]
-which is exactly the standard variational equation in
- \eqnref{variationEq} with $v_{\delta u}$ as the test functions.
-We can define the optimal test space $V_{\rm opt} \coloneqq \{v_{\delta u} \text{ s.t.
-} \delta u\in U\}$.
-Thus, the solution of the variational problem \eqnref{variationEq} with test space $V_h = V_{\rm opt}$ minimizes the residual in the dual norm $\nor{Bu_h-l}_{V'}$.
-This is the key idea behind the concept of optimal test functions.
-
-Since $U_h \subset U$ is spanned by a finite number of basis functions $\LRc{\varphi_i}_{i=1}^N$, \eqnref{optv} allows us to compute (for each basis function) a corresponding optimal test function $v_{\varphi_i}$.
-The collection $\LRc{v_{\varphi_i}}_{i = 1}^N$ of optimal test functions then forms a basis for the optimal test space.
-In order to express optimal test functions defined in \eqnref{optv} in a more familiar form, we take  $\delta u = \varphi$, a generic basis function in $U_h$, and rewrite \eqnref{optv} as
-\[
-R_Vv_{\varphi} = B\varphi, \quad \text{in } V',
-\]
-which is, by definition, equivalent to
-\[
-\LRp{v_\varphi,\delta v}_V = \LRa{R_Vv_\varphi,\delta v}_{V}=
-\LRa{B\varphi, \delta v}_V = b\LRp{\varphi,\delta v}, \quad
-\forall \delta v \in V.
-\]
-%% Now, let us define the \textit{trial-to-test} operator $T =
-%% R_V^{-1}B$, which, by \eqnref{optv}, maps a trial function $\delta u$
-%% to its corresponding \textit{optimal} test function $v = T\delta u$.
-%% On the other hand,
-As a result, optimal test functions can be determined by solving the auxiliary
-variational problem
-\begin{equation}
-\eqnlab{optvVar}
-\left(v_\varphi,\delta v\right)_V = b(\varphi,\delta v), \quad \forall
-\delta v \in V.
-\end{equation}
-However, in general, for standard $H^1$ and $H({\rm div})$-conforming finite element methods, test functions are continuous over the entire domain, and hence solving variational problem \eqnref{optvVar} for each optimal test function requires a global operation over the entire mesh, rendering the method impractical.
-A breakthrough came through the development of
-discontinous Galerkin (DG) methods, for which basis functions are
-discontinuous over elements. In particular, the use of discontinuous
-test functions $\delta v$ reduces the problem of determining global 
-optimal test functions
-in \eqnref{optvVar} to local problems that can be solved in an
-element-by-element fashion.
-
-We note that solving \eqnref{optvVar} on each element exactly is
-infeasible since it amounts to inverting the Riesz map $R_V$ exactly.
-Instead, optimal test functions are approximated using the standard
-Bubnov-Galerkin method on an ``enriched" subspace $\tilde{V} \subset
-V$ such that $\dim(\tilde{V}) > \dim(U_h)$ elementwise \cite{DPG1, DPG2}. In this
-paper, we assume the error in approximating the optimal test functions
-is negligible, and refer to the work in \cite{practicalDPG} for
-estimating the effects of approximation error on the performance of DPG.
-
-It is now well known that the DPG method
-delivers the best approximation error in the ``energy norm" --- that is
-\cite{Bui-ThanhDemkowiczGhattas11a, DPG2,DPG4} 
-\begin{equation}
-\eqnlab{optimalError}
-\nor{u-u_h}_{U,E} = \inf_{w\in U_h} \nor{u-w}_{U,E},
-\end{equation}
-where the energy norm $\|\cdot \|_{U,E}$ is defined for a function $\varphi \in U$ as
-\begin{equation}
-\eqnlab{energyNorm} \|\varphi\|_{U,E} \coloneqq \sup_{v\in V}
-\frac{b(\varphi,v)}{\|v\|_V} = \sup_{\nor{v}_V = 1} b(\varphi,v) =
-\sup_{\nor{v}_V = 1} \LRa{B\varphi,v}_V = \nor{B\varphi}_{V'} =
-\nor{v_\varphi}_V,
-\end{equation}
-where the last equality holds due to the isometry of the Riesz map
-$R_V$ (or directly from \eqnref{optvVar} by taking the supremum). An
-additional consequence of adopting such an energy norm is that,
-without knowing the exact solution, the energy error $\|u-u_h\|_{U,E}$ can
-be determined by computing $\|v_{u-u_h}\|_V$ from the following
-identity
-\[
-\left(v_{u-u_h},\delta v\right)_V = b(u-u_h,\delta v) = l\LRp{\delta
-v} - b(u_h,\delta v).
-\]
-This is simply a consequence of the least-squares nature of DPG; the energy error is simply the norm of the  residual in $V'$.
-
-Practically speaking, this implies that the DPG method is discretely stable on any mesh.
-In particular, DPG is unconditionally stable for higher order adaptive meshes, where discrete stability is often an issue.
-
-\section{Ultra-weak variational formulation}
-\seclab{abstractUweak}
-
-The naming of the discontinuous Petrov-Galerkin method refers to the fact that the method is a Petrov-Galerkin method, and that the test functions are specified to be discontinuous across element boundaries.
-There is no specification of the regularity of the trial space, and we stress that the idea of DPG is not inherently tied to a single variational formulation \cite{Bui-ThanhDemkowiczGhattas11a}.
-
-In most of the DPG literature, however, the discontinuous Petrov-Galerkin method refers to the combination of the concept of locally computable optimal test functions in Section \secref{optimalTest} with the so-called ``ultra-weak formulation" \cite{DPG1,DPG2,DPG3,DPG4,DPGElas,DBLP:journals/procedia/NiemiCC11}.
-Unlike the previous two sections in which we studied the general equation \eqnref{variationEq} given by abstract bilinear and linear forms, we now consider a concrete instance of \eqnref{variationEq} resulting from an ultra-weak formulation for an abstract first-order system of PDEs $Au = f$.
-Additionally, from this section onwards, we will refer to DPG as the pairing of the ultra-weak variational formulation with the concept of locally computable optimal test functions.
-
-We begin by partitioning the domain of interest $\Omega$ into $\Nel$ non-overlapping elements $K_j, j = 1,\hdots,\Nel$ such that $\Oh = \cup_{j=1}^\Nel K_j$ and $\overline{\Omega} = \overline{\Omega}_h$.
-Here, $h$ is defined as $h= \max_{j\in \LRc{1,\hdots,\Nel}}\text{diam}\LRp{K_j}$.
-We denote the mesh ``skeleton" by $\Gh = \cup_{j=1}^\Nel \partial K_j$; the set of all faces/edges $e$, each of which comes with a normal vector ${n}_e$.
-The internal skeleton is then defined as $\Gamma^0_h = \Gh \setminus \partial \Omega$.
-If a face/edge $e \in \Gh$ is the intersection of $\partial K_i$ and $\partial K_j$, $i \ne j$, we define the following jumps:
-\[
-\jump{v} = \text{sgn} \LRp{{n}^-}v^- + \text{sgn} \LRp{{n}^+}v^+, \quad
-\jump{\tau \cdot n} = {n}^-\cdot \tau^- + {n}^+\cdot\tau^+,
-\]
-where
-\[
-\text{sgn}\LRp{{n}^{\pm}} =
-\left\{
-\begin{array}{ll}
-1 & \text{if } {n}^{\pm} = {n}_e \\
--1 & \text{if } {n}^\pm = -{n}_e
-\end{array}
-\right..
-\]
-For $e$ belonging to the domain boundary $\partial \Omega$, we define
-\[
-\jump{v} = v, \quad
-\jump{\tau \cdot n} = {n}_e\cdot \tau.
-\]
-Note that we allow arbitrariness in assigning ``-'' and ``+'' quantities to the adjacent elements $K_i$ and $K_j$.
-%For the rest of the paper, we will use the same notation for both a function and its trace (if it is well-defined) when there is no ambiguity.
-
-The ultra-weak formulation for $Au = f$ on $\Oh$, ignoring boundary
-conditions for now, reads
-\begin{equation}
-\eqnlab{uweak}
-b\left(\left(u, \widehat{u}\right),v\right) \coloneqq \langle \widehat{u}, \jump{v}
-\rangle_{\Gh} - (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh},
-\end{equation}
-where we have denoted $\LRa{\cdot,\cdot}_{\Gh}$ as the duality
-pairing on $\Gh$, $\LRp{\cdot,\cdot}_{\Oh}$ the $L^2$-inner
-product over $\Oh$, and $A_h^*$ the formal adjoint resulting from
-element-wise integration by parts.  Occasionally, for simplicity in
-writing, we will ignore the subscripts in the duality pairing and
-$L^2$-inner product if they are $\Gh$ and $\Oh$. Both the
-inner product and formal adjoint are understood to be taken
-element-wise. Using the ultra-weak formulation, the regularity
-requirement on solution variable $u$ is relaxed, that is, $u$ is now
-square integrable for the ultra-weak formulation \eqnref{uweak} to be
-meaningful, instead of being (weakly) differentiable.  The trade-off
-is that $u$ does not admit a trace on $\Gh$ even though it did
-originally. Consequently, we need to introduce an additional new
-``trace'' variable $\widehat{u}$ in \eqnref{uweak}, that is defined only on
-$\Gh$.
-
-The energy setting is now clear; namely,
-\[
-u\in L^2\LRp{\Oh} \equiv L^2(\Omega), \quad v\in V=D(A^*_h), \quad
-\widehat{u}\in \gamma(D(A)),
-\]
-where $D(A_h^*)$ denotes the broken graph space corresponding to $A_h^*$,
-and $\gamma(D(A))$ the trace space (assumed to exist) of the graph space of
-operator $A$.
-The first discussion of the well-posedness of DPG with the ultra-weak formulation can be found in \cite{analysisDPG}, where the proof is presented for the Poisson and convection-diffusion equations.
-A more comprehensive discussion of the abstract setting for DPG with the ultra-weak formulation using the graph space, as well as a more general proof of well-posedness, can be consulted in \cite{Bui-ThanhDemkowiczGhattas11b}.
-
-\section{Choices of test and trial norms}
-\seclab{energyPair}
-
-A clear property of the energy norm defined by \eqnref{energyNorm} is that the trial norm $\nor{\cdot}_{U,E}$ is induced by a given test norm.
-However, the reverse relationship holds as well; for any trial norm, the test norm that induces such a norm is recoverable through duality.
-We have a result, proved in \cite{Bui-ThanhDemkowiczGhattas11a}: assuming, for simplicity, that the bilinear form $b(u,v)$ is definite, given any norm $\nor{\cdot}_{U}$ on the trial space $U$, for $\varphi \in U$, we can represent $\nor{\varphi}_{U}$ via
-\[
-\nor{\varphi}_{U} = \sup_{v \in V}\frac{b\LRp{w,v}}{\nor{v}_{V,U}}.
-\]
-where $\nor{v}_{V,U}$ is defined through
-\[
-\nor{v}_{V,U} = \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U}}.
-\]
-%In other words, the norm $\nor{\cdot}_V$ in $V$ can be recovered using the energy norm $\nor{\cdot}_{U,E}$ in $U$, and vice versa.
-
-In particular, given two arbitrary norms $\nor{\cdot}_{U,1}$ and $\nor{\cdot}_{U,2}$ in $U$
-such that $\nor{\cdot}_{U,1} \le c \nor{\cdot}_{U,2}$ for some constant
-$c$, they generate two norms $\nor{\cdot}_{V,U,1}$ and
-$\nor{\cdot}_{V,U,2}$ in $V$ defined by
-\[
-\nor{v}_{V,U,1} \coloneqq \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U,1}}, \quad
-\text{and }\nor{v}_{V,U,2} \coloneqq \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U,2}},
-\]
-such that $\nor{\cdot}_{V,U,1}$ and $\nor{\cdot}_{V,U,2}$ induce
-$\nor{\cdot}_{U,1}$ and $\nor{\cdot}_{U,2}$ as energy
-norms in $U$, respectively. That is,
-\[
-\|\varphi\|_{U,1} = \sup_{v\in V}
-\frac{b(\varphi,v)}{\|v\|_{V,U,1}}, \quad \text{and }\|\varphi\|_{U,2} = \sup_{v\in V}
-\frac{b(\varphi,v)}{\|v\|_{V,U,2}}.
-\]
-
-A question that remains to be addressed is to establish the relationship
-between $\nor{\cdot}_{V,U,1}$ and $\nor{\cdot}_{V,U,2}$, given that
-$\nor{\cdot}_{U,1} \le c \nor{\cdot}_{U,2}$. But this is
-straightforward since we have
-\begin{align*}
- \| v \|_{V,U,2} = \sup_{u \in U} \frac{b\left(w,v\right)}{\left\|
-  w \right\|_{U,2}} \le c\sup_{w \in U} \frac{b\left(w,v\right)}{\left\| w
-  \right\|_{U,1}} = c\| v \|_{V,U,1}.
-\end{align*}
-Consequently, a stronger energy norm in $U$ will generate a weaker
-norm in $V$ and vice versa. In other words, to show that an
-energy norm $\nor{\cdot}_{U,1}$ is weaker than another energy norm
-$\nor{\cdot}_{U,2}$ in $U$, one simply needs to show the reverse inequality on the
-corresponding norms in $V$, that is, $\nor{\cdot}_{V,U,1}$ is stronger
-than $\nor{\cdot}_{V,U,2}$.
-
-From now on, unless otherwise stated, we will refer to $\nor{\cdot}_{V,U}$ as the test norm that induces a given norm $\nor{\cdot}_U$.
-Likewise, we will refer $\nor{\cdot}_{U,V}$ as the trial norm induced by a given test norm $\nor{\cdot}_V$.
-In this paper, for simplicity of exposition, we shall call a pair of norms in $U$ and $V$ that induce each other as an {\em energy norm pairing}.
-
-From the discussion above of energy norm and test norm pairings, we know that specifying either a test norm or trial norm is sufficient to define an energy pairing.
-We now derive and discuss two important energy norm pairings, the first of which begins by specifying the canonical norm in $U$ and inducing a test norm on $V$.
-The second pairing begins instead by specifying the canonical norm on $V$ under the ultra-weak formulation \eqnref{uweak} and inducing an energy norm on the trial space $U$.
-
-We begin first with the canonical norm in $U$. Since $\uh \in \gamma\LRp{D\LRp{A}}$, the standard norm for $\uh$ is
-the so-called minimum energy extension norm defined as
-\begin{equation}
-\eqnlab{MEnorm}
-\|\widehat{u}\| = \inf_{w\in D\LRp{A},
-  \left.w\right|_{\Gh}=\widehat{u}} \|w\|_{D\LRp{A}}.
-\end{equation}
-The canonical norm for the group variable $\LRp{u,\uh}$ is then given by
-\[
-\|\left(u,\widehat{u}\right)\|_U^2 = \|u\|^2_{\L} + \|\widehat{u}\|^2,
-\]
-Applying the Cauchy-Schwarz inequality, we arrive at
-\[
-b\LRp{\LRp{u,\uh},v} \le \nor{\LRp{u,\uh}}_U \nor{v}_{V,U},
-\]
-where
-\[
-\nor{v}_{V,U}^2 = \|A_h^*v\|_{\L}^2
-+\left(\sup_{\widehat{u} \in \gamma\LRp{D\LRp{A}}} \frac{\LRa{ \widehat{u},
-  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2.
-\]
-
-On the other hand, since $v \in D\LRp{A^*_h}$, the canonical norm for
-$v$ is the broken graph norm: 
-\[
-\nor{v}_V^2 =  \|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2.
-\]
-Using the Cauchy-Schwarz inequality again, we obtain
-\[
-b\LRp{\LRp{u,\uh},v} \le \nor{\LRp{u,\uh}}_{U,V} \nor{v}_{V},
-\]
-where
-\begin{equation}
-\eqnlab{inducedQuasi}
-\nor{\LRp{u,\uh}}_{U,V}^2 = \nor{u}_{\L}^2
-+\sup_{v \in D\LRp{A_h^*}} \frac{\LRa{\widehat{u},
-  \jump{v}}_{\Gh}^2}{\|v\|_V^2},
-\end{equation}
-
-Using the framework developed in \cite{Bui-ThanhDemkowiczGhattas11a},
-one can show that both pairs $\LRp{\nor{\LRp{u,\uh}}_U,
-  \nor{v}_{V,U}}$ and $\LRp{\nor{\LRp{u,\uh}}_{U,V}, \nor{v}_{V}}$ are
-energy norm pairings in the sense discussed in Section
-\secref{energyPair}. That is, the canonical norm $\nor{\LRp{u,\uh}}_U$
-in $U$ induces (generates) the norm $\nor{v}_{V,U}$ in $V$, while the
-canonical norm $\nor{v}_V$ in $V$ induces (generates) the energy norm
-$\nor{\LRp{u,\uh}}_{U,V}$ in $U$. In the DPG literature \cite{DPG4}, $\nor{v}_{V,U}$ is known as the {\em optimal test norm},
-while $\nor{v}_{V}$ is known as the {\em quasi-optimal test norm}.
-
-\begin{figure}[!h]
-\centering
-\begin{tabular}{l c c}
-Trial norm & & Test norm \\
-\hline
-$\boxed{\|u\|^2_{\L} + \|\widehat{u}\|^2}$ & $\Longrightarrow$  & $\|A_h^*v\|_{\L}^2
-+\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},
-  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2$ \\
-%\hline
-%Quasi-optimal trial norm & & Canonical test norm \\
-%\hline
-$\nor{u}_{\L}^2+\sup_{v } \left(\frac{\LRa{\widehat{u},
-  \jump{v}}_{\Gh}}{\|v\|_V}\right)^2$ &  $\Longleftarrow$ & $\boxed{\|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2}$
-\end{tabular}
-\caption{A summary of the derivation of test/trial norm pairings; we begin with the boxed norm on either the trial or test space, and induce the norm on the other space through duality.
-The optimal \textit{test} norm is naturally derived by beginning with the canonical norm on the trial space, while the quasi-optimal \textit{trial} norm is derived from beginning with the canonical norm on the test space.}
-\end{figure}
-
-The canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ provides a good
-balance between the standard norms on the field $u$ and the flux
-$\uh$ \cite{DPG4}. As a result, if the induced norm $\nor{v}_{V,U}$ (namely, the
-optimal test norm) is used to compute  optimal test functions in
-\eqnref{optvVar}, the finite element error in the canonical norm is the
-best in the sense of \eqnref{optimalError}.
-
-Unfortunately, the optimal test norm is non-localizable due to the presence of the jump term $\jump{v}$.\footnote{A localizable norm $\nor{v}_{V(\Oh)}$ can be written in the form $\nor{v}_{V(\Oh)} = \sum_{K\in\Oh} \nor{v}_{V(K)},$ where $\nor{v}_{V(K)}$ is a norm over the element $K$.} Since the jump terms couple elements together, the evaluation of the jump terms requires contributions from all the elements in the mesh.
-Consequently, solving for an optimal test function
-amounts to inverting the Riesz map %, defined on the left sideof \eqnref{optvVar}, 
-over the entire mesh $\Oh$, making the optimal test norm impractical.
-
-On the other hand, the quasi-optimal test norm $\nor{v}_V$, namely the canonical norm in $V$, \textit{is} localizable, and hence practical.
-However, it's worth noting the difference between the induced energy norm $\nor{\LRp{u,\uh}}_{U,V}$ and the canonical norm in $U$; under the induced norm $\nor{\LRp{u,\uh}}_{U,V}$ there is no natural interpretation for the norm in which the error in the flux variable $\uh$ is measured.
-
-Using a variant of the quasi-optimal test norm, numerical results show that the DPG method appears to provide a ``pollution-free" method without phase error for the Helmholtz equation \cite{DPG4}, and analysis of the pollution-free nature of DPG is currently under investigation.
-Similar results have also been obtained in the context of elasticity \cite{DPGElas} and the linear Stokes equations \cite{Camellia}.
-On the theoretical side, the quasi-optimal test norm has been shown to yield a well-posed DPG methodology for the Poisson and convection-diffusion equations \cite{analysisDPG}.
-More recently, this theory has been generalized to show the well-posedness of DPG for the large class of PDEs of Friedrichs' type \cite{Bui-ThanhDemkowiczGhattas11b}.
-
-\chapter{A robust DPG method for convection-dominated diffusion}
-
-\begin{itemize}
-\item Describe mathematically the issue with standard Galerkin.
-\item Give proofs of robustness and numerical results (from paper)\cite{ChanHeuerBui-ThanhDemkowicz12}
-\end{itemize}
-
-\chapter{DPG for nonlinear problems}
-
-\begin{itemize}
-\item Introduce nonlinear residual to measure convergence, DPG formulation for nonlinear problems. Briefly discuss solution strategies (pseudo-timestep/damped Newton). 
-\item Formulate DPG for Burgers' equation as an example, show results
-\item Show DPG applied to Navier-Stokes at a broad level, with results
-\end{itemize}
-
-\section{Summary: completed/propsed work}
-
-\subsection{Area A}
-
-\begin{itemize}
-\item{\textbf{Completed: }} Prove robustness of DPG method for the scalar convection-diffusion problem
-\item Attempt analysis of the linearized Navier-Stokes system
-\end{itemize}
-
-\subsection{Area B}
-
-\begin{itemize}
-\item{\textbf{Completed: }} Collaborative work with Nathan Roberts on the higher order parallel adaptive DPG code Camellia.
-\item Nonlinear DPG - Hessian adjoint trick
-\item Adaptivity: anisotropic refinements and $hp$-schemes.
-\item Distributed static condensation
-\end{itemize}
-
-\subsection{Area C}
-
-\begin{itemize}
-\item{\textbf{Completed: }} Convection-dominated diffusion, Burgers, and Navier-Stokes. 
-\item Higher Reynolds number, ramp problem, Gaussian bump, airfoil.
-\item Euler with NS regularization?
-\end{itemize}
-
-\bibliographystyle{plain}
-\bibliography{CFD_intro,DPG_old,paper,LitRev}
-
-\end{document}

### 2012-06-15 docs/Jesse/Proposal/BurgersNotes.tex
adding more additions (NL DPG) to proposal

@@
 
-We will begin with the viscous Burgers' equation as an example of
+We will illustrate the application of DPG to nonlinear problems using a viscous Burgers' equation on domain $\Omega = [0,1]^2 \in \mathbb{R}^2$
+\[
+\pd{\left(u^2/2\right)}{x} + \pd{u}{y} - \epsilon \Delta u = f.
+\]
+If we remove the viscous term, the above problem reduces to the form of the 1D transient Burgers equation, whose solution we can determine via the method of characteristics.  For boundary conditions 
+\[
+u(x.y) = 1-2x, \quad x = 0, y = 0,
+\]
+the solution forms a shock discontinuity starting at $(x,y) = (.5,.5)$, which then propagates upward in the $y$-direction.
+The addition of the viscous term smears this discontinuity, leading to a solution with a smooth shock of width $\epsilon$.
+
+We begin by writing the equation in a first order system.  Defining $\beta(u) = \LRp{u/2,1}$, the above Burgers equation can be written as
+\begin{align*}
+\div\left(\beta(u)u-\sigma\right) &=f \\
+\frac{1}{\epsilon}\sigma - \grad u &=0.
+\end{align*}
+Analogously to the convection-diffusion problem, the DPG nonlinear variational formulation can then be given
+\[
+b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(v,\tau\right)\right) = \LRp{u,\div \tau - \beta(u) \cdot \grad v} + \LRp{\sigma, \frac{1}{\epsilon}\tau + \grad v} + \LRa{\widehat{u},\tau\cdot n} + \LRa{\widehat{f}_n,v} = \LRp{f,v}
+\]
+Linearizing the above then gives us 
+\begin{align*}
+b_u\left(\left(\Delta u,\sigma,\widehat{u},\widehat{f}_n\right),\left(v,\tau\right)\right) &= \LRp{\Delta u,\div \tau - \vecttwo{u}{1} \cdot \grad v} + \LRp{\sigma, \frac{1}{\epsilon}\tau + \grad v} + \LRa{\widehat{u},\tau\cdot n} + \LRa{\widehat{f}_n,v} \\
+&= \LRp{u,\div \tau - \beta(u)\cdot \grad v} 
+\end{align*}
+Notice that the nonlinear term is only dependent on $u$, and thus there is no need to linearize in the variables $\sigma$, $\widehat{u}$, and $\widehat{f}_n$.
+
+Since the linearized Burgers' equation is of the form of a convection-diffusion problem with non-homogeneous load, we adopt the test norm described in Section~\secref{sec:testNormSec} with convection vector $\beta = (u,1)$.
+
+Recall that we did not linearize in the flux variables $\widehat{u}$ and $\widehat{f}_n$, so we can directly apply the nonlinear boundary conditions to our variational formulation.
+Additionally, since Burgers' equation does not have any physical constraints, we can employ a direct Newton iteration to solve the nonlinear equation.
+The adaptivity algorithm is identical to the greedy algorithm described previously, except that the linear solve is replaced by a nonlinear solve.
+The results of an adaptive simulation are shown in Figure~\ref{fig:BurgersShock} for $\epsilon = 1e-4$.
 
@@
 \caption{Shock solution for Burgers' equation with $\epsilon = 10^{-4}$.} 
+\label{fig:BurgersShock}
 \end{figure}
+\todo{Get mesh and zoomed in plot for Burgers' equation.}

### 2012-06-15 docs/Jesse/Proposal/DPGrobustness.tex
adding more additions (NL DPG) to proposal

@@
-\section{Model problem and robustness}
+\section{DPG formulation for convection-diffusion}
+
 \seclab{sec:modelSec}
-The remainder of the paper focuses on a convection-diffusion model problem using the abstract theory that we
+The remainder of this chapter focuses on the convection-diffusion problem using the abstract theory that we
 have discussed so far.
-In particular, we shall use the DPG method based on the ultra-weak formulation with optimal test functions to solve the model problem and analyze its behavior with respect to $\epsilon$.
+In particular, we shall use the DPG method based on the ultra-weak formulation with optimal test functions to solve this model problem and analyze its behavior with respect to $\epsilon$.
 Our goal is to show the robustness of the method with respect to $\epsilon$, and demonstrate its usefulness as  a numerical approach to solving singular-perturbed problems.
 
-We consider the following model convection-diffusion problem on a domain
+The convection-diffusion problem is given on a domain
 $\Omega \subset \mathbb{R}^d$ with boundary $\pO \equiv \Gamma$
@@
 %and we could obtain the robustness only with special weighted norms in which the weight varied spatially. 
-In this paper, we employ the inflow
+We employ instead the inflow
 condition of Hesthaven \etal \cite{Hesthaven96astable}, where we set
@@
 \]
-This paper is intended to act as an extension of work presented by Heuer and Demkowicz in \cite{DPGrobustness}.
-The primary focus of the paper is to analyze the DPG method and extend previous results under this new choice of inflow boundary conditions.
+This work is intended to act as an extension of work presented by Heuer and Demkowicz in \cite{DPGrobustness}.
+The primary focus of this chapter is to analyze the DPG method and extend previous results under this new choice of inflow boundary conditions.
 The difference in the performance of DPG under both new and old boundary conditions is connected to the difference in the adjoint problems induced under each boundary condition.
-The secondary contribution of this paper will be to analyze the performance of DPG under a new mesh-dependent test norm.
+The secondary contribution of this work will be to analyze the performance of DPG under a new mesh-dependent test norm.
 
@@
 
-\section{Analysis of a DPG test norm}
+\subsection{Analysis of a DPG test norm}
 \seclab{sec:testNormSec}
@@
 
-\subsection{Decomposition into analyzable components}
+\subsubsection{Decomposition into analyzable components}
 \label{sec:strategy2}
@@
 
-\subsection{Adjoint estimates}
+\subsubsection{Adjoint estimates}
 \label{sec:strategy3}
@@
 %  way?}
-\subsection{A mesh-dependent test norm}
+\subsubsection{A mesh-dependent test norm}
 \seclab{sec:meshDep}
@@
 \centering
-\subfigure{\includegraphics[scale=.22]{figs/mesh1.png}}
-\subfigure{\includegraphics[scale=.22]{figs/sol1.png}}
+\subfigure{\includegraphics[scale=.2]{figs/mesh1.png}}
+\subfigure{\includegraphics[scale=.2]{figs/sol1.png}}
 \caption{The $v$ component of the optimal test function corresponding to flux $\widehat{u} = x(1-x)$ on the bottom side of a unit element for $\epsilon = 0.01$.
@@
 Similarly, we scale the $L^2$ contributions of $\tau$ by $C_\tau(K)$ such that $\frac{C_\tau(K)}{\epsilon} \|\tau\|^2$ and $\|\div \tau\|^2$ are of the same magnitude as well.
-For this paper, we consider only isotropic refinements on quadrilateral elements in 2D.
+For this work, we consider only isotropic refinements on quadrilateral elements in 2D.
 
@@
 
-\subsection{Equivalence of energy norm with $\nor{\cdot}_U$}
+\subsubsection{Equivalence of energy norm with $\nor{\cdot}_U$}
 %\subsection{Relations between trial and test constants}
@@
 
-The main theoretical result of this paper can now be given:
+The main theoretical result of this work can now be given:
 \begin{lemma}
@@
 
-\subsection{Comparison of boundary conditions}
+\subsubsection{Comparison of boundary conditions}
 
@@
 Thus, we cannot conclude $\|\beta v'\| \lesssim \|g\|$ when $g$ is a constant,\footnote{Unlike the case of Dirichlet boundary conditions, the inflow condition on $ \widehat{f}_n = u(0)-\epsilon u'(0)$ induces an adjoint boundary condition $\tau(0)=0$, or equivalently $v'(0) = 0$, removing the non-robust term from the estimate.} and as a consequence cannot conclude that the robust error bound $\|u-u_h\|_{L^2} \lesssim \|(u,\sigma,\widehat{u},\widehat{f}_n)-(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h})\|_E$ holds for the solution $u_h$.
-More detailed 1D error bounds for Dirichlet boundary conditions are provided in \cite{DPG3}, and indicate the same lack of robustness under the test norm derived in this paper.\footnote{Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
+More detailed 1D error bounds for Dirichlet boundary conditions are provided in \cite{DPG3}, and indicate the same lack of robustness under the test norm used thus far.\footnote{Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
 \[
@@
 \subfigure{
-\includegraphics[scale=.38]{figs/roundoff_rates.png}
+\includegraphics[scale=.36]{figs/roundoff_rates.png}
 }
 \subfigure{
-\includegraphics[scale=.38]{figs/roundoff_ratio.png}
+\includegraphics[scale=.36]{figs/roundoff_ratio.png}
 }
@@
 \subfigure{
-\includegraphics[scale=.38]{figs/rates_disc.png}
+\includegraphics[scale=.36]{figs/rates_disc.png}
 }
 \subfigure{
-\includegraphics[scale=.38]{figs/ratio_disc.png}
+\includegraphics[scale=.36]{figs/ratio_disc.png}
 }

### 2012-06-15 docs/Jesse/Proposal/NSNotes.tex
adding more additions (NL DPG) to proposal

@@
 \]
-\subsection{Momentum equations}
+\item \textbf{Momentum equations}
 \begin{align*}
@@
 \item \textbf{Energy equation}
+
 Let $\boldsymbol \sigma$ be a tensor whose $ij$th term is $\sigma_{ij}$.  
@@
 \item \textbf{Newtonian fluid laws}
+
 We represent $\boldsymbol\sigma$ using the Newtonian fluid law
@@
 \item \textbf{Fourier's heat conduction law}
+
 We assume Fourier's law 
@@
 
-To summarize, our system of equations in the classical variables is now
-\begin{align*}
-\div \vecttwo{\rho u }{\rho v} &= 0\\
-\div \left(\vecttwo{\rho u^2+p }{\rho u v} - \boldsymbol \sigma_{1}\right) &=0\\
-\div \left(\vecttwo{\rho u v}{\rho v^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
-\div \left(\vecttwo{((\rho e)+p)u}{((\rho e)+p)v} - \boldsymbol\sigma \mathbf{u} + \vec{q}\right) &=0\\
-\frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I &= \grad \mathbf{u} - \boldsymbol \omega\\
-\frac{1}{\kappa}\vec{q} &= \grad T
-\end{align*}
-
-We strongly enforce symmetry of the stress tensor $\boldsymbol \sigma$ by setting $\sigma_{21} = \sigma_{12}$.
-
-\section{Nondimensionalization}
+\subsection{Nondimensionalization}
 To nondimensionalize our equations, we introduce nondimensional quantities for length, density, velocity, temperature, and viscosity. 
@@
 
+To summarize, our system of equations in the classical variables is now
+\begin{align*}
+\div \vecttwo{\rho u }{\rho v} &= 0\\
+\div \left(\vecttwo{\rho u^2+p }{\rho u v} - \boldsymbol \sigma_{1}\right) &=0\\
+\div \left(\vecttwo{\rho u v}{\rho v^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
+\div \left(\vecttwo{((\rho e)+p)u}{((\rho e)+p)v} - \boldsymbol\sigma \mathbf{u} + \vec{q}\right) &=0\\
+\frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I &= \grad \mathbf{u} - \Reyn \, {\boldsymbol \omega}\\
+\frac{1}{\kappa}\vec{q} &= \grad T
+\end{align*}
+We strongly enforce symmetry of the stress tensor $\boldsymbol \sigma$ by setting $\sigma_{21} = \sigma_{12}$.
+Additionally, we have scaled the antisymmetric tensor $\boldsymbol \omega$ by the Reynolds number to ensure that $\boldsymbol \omega = O(1)$ for all ranges of $\Reyn$.
+
 \subsection{Linearization}
@@
 
+The Navier-Stokes conservation laws can be written as 
 \begin{align*}
@@
 Instead, fluxes $\widehat{F}_{i,n}$ and traces $\widehat{u},\widehat{v},\widehat{T}$ will represent normal traces and traces of the accumulated nonlinear solution.
+The linearized variational formulation is thus
 \begin{align*}
@@
 \end{align*}
-where
-\begin{align*}
-F^1_{1,\boldsymbol U} &= \{u,\rho ,0,0\} \\
-F^2_{1,\boldsymbol U} &= \{v,0,\rho ,0\} \\
-F^1_{2,\boldsymbol U} &=\left\{c_v T (\gamma -1)+u^2,2 u \rho ,0,c_v (\gamma -1) \rho \right\}\\
-F^2_{2,\boldsymbol U} &=\{u v,v \rho ,u \rho ,0\}\\
-F^1_{3,\boldsymbol U} &=\{u v,v \rho ,u \rho ,0\}\\
-F^2_{3,\boldsymbol U} &=\left\{c_v T (\gamma -1)+v^2,0,2 v \rho ,c_v (\gamma -1) \rho \right\}\\
-F^1_{4,\boldsymbol U} &=\left\{\frac{1}{2} u \left(2 c_v T (2 \gamma -1)+u^2+v^2\right),\frac{1}{2} \rho  \left(2 c_v T (2 \gamma -1)+3 u^2+v^2\right),u v \rho ,c_v u (2 \gamma -1) \rho \right\}\\
-F^2_{4,\boldsymbol U} &=\left\{\frac{1}{2} v \left(2 c_v T (2 \gamma -1)+u^2+v^2\right),u v \rho ,\frac{1}{2} \rho  \left(2c_v T (2 \gamma -1)+u^2+3 v^2\right),c_v v (2 \gamma -1) \rho \right\}
-\end{align*}
-The viscous Jacobians become (when linearized with respect to $\{\sigma_{11},\sigma_{12}, \sigma_{22}\}$)
-\begin{align*}
-G^1_{2,\boldsymbol \sigma} &= \{1,0,0\}\\
-G^2_{2,\boldsymbol \sigma} &= \{0,1,0\}\\
-G^1_{3,\boldsymbol \sigma} &= \{0,1,0\}\\
-G^2_{3,\boldsymbol \sigma} &= \{0,0,1\}\\
-G^1_{4,\boldsymbol \sigma} &= \{u_1,u_2,0\}\\
-G^2_{4,\boldsymbol \sigma} &= \{0,u_1,u_2\}
-\end{align*}
-and (when linearized with respect to the Eulerian variables)
-\begin{align*}
-G^1_{4,\boldsymbol U} &= \{0,\sigma_{11},\sigma_{12},0\}\\
-G^2_{4,\boldsymbol U} &= \{0,\sigma_{12},\sigma_{22},0\}
-\end{align*}
+where $F^i_{j,\boldsymbol U}$, $G^i_{j,\boldsymbol U}$, and $G^i_{j,\boldsymbol \sigma}$ are the Eulerian and two viscous Jacobians (linearized w.r.t.\ the Eulerian/viscous variables), respectively.
+%where
+%\begin{align*}
+%F^1_{1,\boldsymbol U} &= \{u,\rho ,0,0\} \\
+%F^2_{1,\boldsymbol U} &= \{v,0,\rho ,0\} \\
+%F^1_{2,\boldsymbol U} &=\left\{c_v T (\gamma -1)+u^2,2 u \rho ,0,c_v (\gamma -1) \rho \right\}\\
+%F^2_{2,\boldsymbol U} &=\{u v,v \rho ,u \rho ,0\}\\
+%F^1_{3,\boldsymbol U} &=\{u v,v \rho ,u \rho ,0\}\\
+%F^2_{3,\boldsymbol U} &=\left\{c_v T (\gamma -1)+v^2,0,2 v \rho ,c_v (\gamma -1) \rho \right\}\\
+%F^1_{4,\boldsymbol U} &=\left\{\frac{1}{2} u \left(2 c_v T (2 \gamma -1)+u^2+v^2\right),\frac{1}{2} \rho  \left(2 c_v T (2 \gamma -1)+3 u^2+v^2\right),u v \rho ,c_v u (2 \gamma -1) \rho \right\}\\
+%F^2_{4,\boldsymbol U} &=\left\{\frac{1}{2} v \left(2 c_v T (2 \gamma -1)+u^2+v^2\right),u v \rho ,\frac{1}{2} \rho  \left(2c_v T (2 \gamma -1)+u^2+3 v^2\right),c_v v (2 \gamma -1) \rho \right\}
+%\end{align*}
+%The viscous Jacobians become (when linearized with respect to $\{\sigma_{11},\sigma_{12}, \sigma_{22}\}$)
+%\begin{align*}
+%G^1_{2,\boldsymbol \sigma} &= \{1,0,0\}\\
+%G^2_{2,\boldsymbol \sigma} &= \{0,1,0\}\\
+%G^1_{3,\boldsymbol \sigma} &= \{0,1,0\}\\
+%G^2_{3,\boldsymbol \sigma} &= \{0,0,1\}\\
+%G^1_{4,\boldsymbol \sigma} &= \{u_1,u_2,0\}\\
+%G^2_{4,\boldsymbol \sigma} &= \{0,u_1,u_2\}
+%\end{align*}
+%and (when linearized with respect to the Eulerian variables)
+%\begin{align*}
+%G^1_{4,\boldsymbol U} &= \{0,\sigma_{11},\sigma_{12},0\}\\
+%G^2_{4,\boldsymbol U} &= \{0,\sigma_{12},\sigma_{22},0\}
+%\end{align*}
 
@@
 \begin{align*}
-\frac{1}{2\mu}{\boldsymbol \sigma}- \frac{\lambda}{4\mu(\mu+\lambda)}{\rm tr}({\boldsymbol \sigma}){\boldsymbol I} + {\boldsymbol \omega} &= 
+\frac{1}{2\mu}{\boldsymbol \sigma}- \frac{\lambda}{4\mu(\mu+\lambda)}{\rm tr}({\boldsymbol \sigma}){\boldsymbol I} + \Reyn {\boldsymbol \omega} &= 
 \grad
@@
 \begin{align*}
-\frac{1}{2\mu} \vecttwo{\sigma_{11}}{\sigma_{12}} - \frac{\lambda}{4\mu(\mu+\lambda)}\vecttwo{\sigma_{11}+\sigma_{22}}{0} + \vecttwo{0}{-\omega} - \grad u_1&= 0 \\
-\frac{1}{2\mu} \vecttwo{\sigma_{12}}{\sigma_{22}} - \frac{\lambda}{4\mu(\mu+\lambda)}\vecttwo{0}{\sigma_{11}+\sigma_{22}} + \vecttwo{\omega}{0} - \grad u_2 &= 0
+\frac{1}{2\mu} \vecttwo{\sigma_{11}}{\sigma_{12}} - \frac{\lambda}{4\mu(\mu+\lambda)}\vecttwo{\sigma_{11}+\sigma_{22}}{0} + \Reyn\vecttwo{0}{-\omega} - \grad u_1&= 0 \\
+\frac{1}{2\mu} \vecttwo{\sigma_{12}}{\sigma_{22}} - \frac{\lambda}{4\mu(\mu+\lambda)}\vecttwo{0}{\sigma_{11}+\sigma_{22}} + \Reyn\vecttwo{\omega}{0} - \grad u_2 &= 0
 \end{align*}
-These equations are linear in $\sigma_{ij}$, so the linearization is simple. 
+%These equations are linear in $\sigma_{ij}$, so the linearization is simple. 
 Since all equations are linear in variables $q_1, q_2, w$ for all combinations of variables, we do not need to linearize any equations in $q_1, q_2, w$.
@@
 
-\subsubsection{Initial guess}
+\subsection{Test norm}
 
-For our initial guesses, we set
-\[
-\rho = 1,\qquad u_1= 1,\qquad u_2 = 0, \qquad T = 1
-\]
-which is consistent with what was done in Demkowicz and Oden in \cite{Demkowicz:1990:NFE:112271.112276}. Stresses are set uniformly to zero.
-
-\section{Test norm}
-
-For the convection-diffusion problem 
+Recall the convection-diffusion problem 
 \begin{align*}
 \div \left(\beta u - \sigma\right) &= f\\
-\frac{1}{\epsilon}\sigma - \grad u &= 0
+\frac{1}{\epsilon}\sigma - \grad u &= 0.
 \end{align*}
-on domain $\Omega$, with mesh $\Oh$ and mesh skeleton $\Gh$, the DPG variational formulation is
+On domain $\Omega$, with mesh $\Oh$ and mesh skeleton $\Gh$, the DPG variational formulation is
 \begin{align*}
@@
 \end{align*}
-with $v\in H^1$ and $\tau \in H({\rm div},\Oh)$.
-
-The test norm adopted for convection-diffusion in Section~\ref{blah}\todo{get section} and in \cite{DPGrobustness2} is defined elementwise on $K$ as
+with $v\in H^1$ and $\tau \in H({\rm div},\Oh)$. The test norm adopted for convection-diffusion in Section~\secref{sec:testNormSec} and in \cite{DPGrobustness2} is defined elementwise on $K$ as
 \[
@@
 Similarly, we group our Eulerian and stress variables into the vector variables $U$ and $\Sigma$, respectively.
-If $R_{\rm Euler}(U,\Sigma)$ and $R_{\rm visc}(U,\Sigma)$ are Eulerian and viscous nonlinear residuals, our formulation for the linearized Navier-Stokes equations is
+If $R_{\rm Euler}(U,\Sigma)$ and $R_{\rm visc}(U,\Sigma)$ are Eulerian and viscous nonlinear residuals, our formulation for the linearized Navier-Stokes equations can be written as
 \begin{align*}
@@
 Identifying vector-valued terms in the Navier-Stokes formulation with equivalent scalar terms in the convection-diffusion equation allows us to extrapolate our test norm to systems of equations
-\[
-\|\left(V,W\right)\|_{V,K}^2 = \min\left\{\frac{\Reyn}{|K|},1\right\}\|v\|^2 + \frac{1}{\Reyn} \|A_{\rm visc}^T\grad v\|^2 + \|A_{\rm Euler}^T \grad v\|^2 + \| \div W\|^2 + \min\left\{\Reyn,\frac{1}{|K|}\right\}\|E_{\rm visc}^T\tau\|^2.
-\]
+\begin{align*}
+\|\left(V,W\right)\|_{V,K}^2 =& \min\left\{\frac{\Reyn}{|K|},1\right\}\|v\|^2 + \frac{1}{\Reyn} \|A_{\rm visc}^T\grad v\|^2 + \|A_{\rm Euler}^T \grad v\|^2 \\
+& + \| \div W\|^2 + \min\left\{\Reyn,\frac{1}{|K|}\right\}\|E_{\rm visc}^T\tau\|^2.
+\end{align*}
 An advantage of this extrapolation approach is that the incompletely parabolic nature of the Navier-Stokes equation is taken into account; there is no diffusive term present in the mass conservation equation, and the test norm reflects that by requesting only limited regularity of $v_1$.\footnote{The situation is analagous to using the full $H^1(\Oh)$ norm for the pure convection equation --- the optimal test norm $\nor{v}_V = \nor{\beta\cdot \grad v} + \nor{v}$ implies only streamline regularity, whereas taking $\nor{v}_V = \nor{\grad v} + \nor{v}$ implies stronger regularity on the test space $V$ than the graph norm.
@@
 
-\section{Boundary conditions}
+\subsection{Boundary conditions}
 
@@
 
-\subsection{Carter flat plate}
+\subsection{Numerical experiments}
+
+For our solver, we use a standard pseudo-time solver and a standard greedy refinement scheme.
+Though we have not yet implemented adaptive timestepping, we are able to take large enough uniform timesteps over a coarse mesh such that convergence is comparable to the convergence of a damped Newton method.
+
+The numerical parameters used are as follows:
+\begin{itemize}
+\item{DPG parameters:} Both $p$ and $\Delta p = 2$ uniformly across the mesh. 
+\item{Adaptivity parameters:} Energy threshold for refinements is $\alpha = .2$ or $\alpha = .15$. 
+\item{Time-stepping parameters:} $\Delta t = .1$, and tolerance for transient residual $\epsilon_t = 5e-7$.
+\end{itemize}
+
+\subsubsection{Carter flat plate}
 
@@
 
-\section{Numerical experiments}
+For our initial guesses, we set
+\[
+\rho = 1,\qquad u_1= 1,\qquad u_2 = 0, \qquad T = 1
+\]
+which is consistent with what was done in Demkowicz and Oden in \cite{Demkowicz:1990:NFE:112271.112276}. Stresses are set uniformly to zero.
 
-For our solver, we use a standard pseudo-time solver and a standard greedy refinement scheme.
-Though we have not yet implemented adaptive timestepping, we are able to take large enough uniform timesteps over a coarse mesh such that convergence is comparable to the convergence of a damped Newton method.
-
-The parameters used are as follows:
-\begin{itemize}
-\item{DPG parameters:} Both $p$ and $\Delta p = 2$ uniformly across the mesh. 
-\item{Adaptivity parameters:} Energy threshold for refinements is $\alpha = .2$ or $\alpha = .15$. 
-\item{Time-stepping parameters:} $\Delta t = .1$, and tolerance for transient residual $\epsilon_t = 5e-7$.
-\end{itemize}
-
-\subsection{Carter plate problem}
-
-For the flat plate problem, we take the domain $\Omega = [0,2]\times[0,1]$. For $\Reyn = 500$, we begin with an initial mesh of 8 by 16 elements. 
+We take the computational domain to be $\Omega = [0,2]\times[0,1]$. For $\Reyn = 500$, we begin with an initial mesh of 8 by 16 elements. 
 \begin{figure}[!h]

### 2012-06-15 docs/Jesse/Proposal/NonlinDPG.tex
adding more additions (NL DPG) to proposal

\section{DPG for nonlinear problems}

In this chapter, we extend DPG to the nonlinear setting and apply it to two problems in computational fluid dynamics.  We take as our starting point a nonlinear variational formulation
$b(u,v) = l(v)$, which is linear in $v$, but not in $u$.  An appropriate linearization gives
\[
b_u(\Delta u,v) = l(v) - b(u,v),
\]
where $b_u(\Delta u,v)$ is the linearization of $b(u,v)$ with respect to $u$.  Let $B(u)$ and $B_u\Delta u$ be the variational operators associated with $b(u,v)$ and $b_u(\Delta u,v)$, respectively.  We define two additional measures: 
\begin{align*}
\|\Delta u\|_E \coloneqq &= \nor{B_u\Delta u}_{V'} = \nor{R_V^{-1} B_u\Delta u}_V = \sup_{v\in V} \frac{b_u(\Delta u,v)}{\nor{v}_V}\\
\nor{R(u)}_E \coloneqq &= \nor{B(u)-l}_E = \nor{B(u) - l}_{V'}  = \nor{R_V^{-1} B(u)-l}_V = \sup_{v\in V} \frac{b(u,v)-l(v)}{\nor{v}_V}
\end{align*}
These two quantities are measures of the linearized update $\Delta u$ and the nonlinear residual in the appropriate norm in the dual space $V'$.  The first will be used to measure convergence of a nonlinear solution scheme to a stable discrete solution, while the second will be used to assess the convergence of the discrete solution to the continuous solution.

\subsection{Nonlinear solution strategies}

The solution of a nonlinear problem is most commonly found using an iterative method, where a series of solutions to linear problems is expected to converge to the nonlinear solution.  We use two main methods to iterate to a nonlinear solution.  
\begin{itemize}
\item{} \textbf{(Damped) Newton iteration :} Given the linearized system $b_u(\Delta u,v) = b(u,v)-l(v)$, we begin with some initial guess $u\coloneqq u_0$ and solve for $\Delta u_0$.  The process is then repeated with $u\coloneqq u_{i+1} \coloneqq u_i + \alpha_i \Delta u_i$, where $\alpha_i \in (0,1]$ is some damping parameter that may limit the size of the Newton step in order to optimize the rate of convergence or preserve physicality of the solution.  The solution is considered converged when $\nor{\Delta u}_E \leq tol$.  
\item{} \textbf{Pseudo-time stepping: } An alternative method for the solution of steady-state systems is to use a pseudo-timestepping method.  The most common approach is to discretize the equations in time using a stable, implicit method --- if $Lu = f$ is our nonlinear problem and $L_u$ is the linearization of the nonlinear operator $L$ with respect to $u$, then the pseudo-timestepping method solves at each discrete time $t_{i}$
\[
\pd{u}{t} + Lu = f \rightarrow \frac{u(t_i) - u(t_{i-1})}{\Delta t} + L_{u(t_i)}\Delta u(t_i) = (f - Lu(t_i)).
\]
The solution at the next timestep is then set $u(t_{i+1}) \coloneqq u(t_i) + \Delta u(t_i)$.  This procedure is then repeated for the next timestep $t_{i+1}$ until the transient residual decreases such that $\nor{u(t_i) - u(t_{i-1})}_{L^2(\Omega)} = \nor{\Delta u(t_i)}_{L^2(\Omega)} \leq tol$.\footnote{Strictly speaking, seeking the solution at each timestep involves the solution of a nonlinear problem, requiring a Newton-type iteration to solve for $u(t_i)$.  However, for most applications, it is sufficient to approximate the nonlinear solution using a single Newton solve at each time step.} 
\end{itemize}

In practice, most compressible flow solvers opt for the pseudo-time step method over the direct Newton iteration due to the difficulty of convergence and sensitivity of the Newton iteration to initial guess\cite{libMeshPaper}.  Though the convergence of the pseudo-time step is slower, the addition of the zero-order transient terms ``regularizes" the problem, making it easier to solve.\footnote{The addition of a zero-order term ``regularizes" an equation by adding to it a positive-definite $L^2$ projection operator.  In the limit as $\Delta t\rightarrow 0$, the solution at $t_i$ will simply return the $L^2$ projection of the solution at the previous timestep.}

A second class of nonlinear solvers are optimization methods.  Since DPG allows for the formulation of a discrete nonlinear residual, it is possible to formulate the nonlinear DPG problem as a minimization problem and use an optimization method to solve the discrete nonlinear problem.  This approach has been successfully implemented by Peraire et al\. in solving compressible gas dynamics problems on uniform grids using a modified version of the ultra-weak variational formulation \cite{MITDPG}.  An additional advantage of such an approach would be the more direct enforcement of physical constraints, which are treated in an ad-hoc manner in most compressible Navier-Stokes solvers.

\subsection{DPG as a nonlinear minimum residual method}

\todo{Add adjoint trick stuff}

### 2012-06-15 docs/Jesse/Proposal/outline.tex
adding more additions (NL DPG) to proposal

--- 2012-06-12 docs/Jesse/Proposal/outline.tex
@@
 \documentclass{report}
+
+\usepackage{utdiss2}  		% Dissertation package style file.
 
@@
 \newcommand{\grad}{\nabla}
+\newcommand{\curl}{\grad \times}
 \renewcommand{\div}{\grad \cdot}
@@
 \date{}
-\author{Jesse Chan}
-\title{Proposal outline/notes}
 
@@
 
+\newcommand{\G} {\Gamma}
+\newcommand{\Gin} {\Gamma_{in}}
+\newcommand{\Gout} {\Gamma_{out}}
+
+%%%%%%%%%%%%%%% End def of new commands %%%%%%%%%%%%%%%%%%%
+
+\author{Jesse Chan}
+\address{910 E. 32nd St, Apt.\ 101\\ Austin, Texas 78705}  % Required
+
+\title{Proposal outline/notes for DPG and Compressible Navier-Stokes}
+
+\supervisor
+	[Leszek Demkowicz]
+	{Robert Moser}
+
+\committeemembers
+	[Thomas J. R. Hughes]
+	[Somebody]
+	[Somebody]
+	{Eh}
+
+\previousdegrees{B.A.}
+
+\oneandonehalfspacequote
+
+\topmargin 0.125in
+
+\makeindex
+
+%%%%%%%%%%%%%%% Start of thesis %%%%%%%%%%%%%%%%%%%
+
 \begin{document}
+\copyrightpage          % Produces the copyright page.
+\commcertpage           % Produces the Committee Certification
+\titlepage
 
-\tableofcontents
-\maketitle
+\begin{dedication}
+\index{Dedication@\emph{Dedication}}%
+Dedicated to \ldots
+\end{dedication}
+
+\begin{acknowledgments}		% Optional
+\index{Acknowledgments@\emph{Acknowledgments}}%
+I wish to thank the multitudes of people who helped me. Time would
+fail me to tell of \ldots
+\end{acknowledgments}
+
+\utabstract
+\index{Abstract}%
+\indent
+This document has the form of a ``fake'' doctoral dissertation
+in order to provide an example of such, but it is actually a
+copy of Miguel Lerma's documentation for the Mathematics
+Department Computer Seminar of 25 March 1998 updated in July 2001
+and following by Craig McCluskey to meet the March 2001
+requirements of the Graduate School.
+
+This document and its source file show to write a Doctoral Dissertation using 
+\LaTeX{} and the utdiss2 package.
+
+\tableofcontents   % Table of Contents will be automatically
+                   % generated and placed here.
+
+%\listoftables      % List of Tables and List of Figures will be placed
+%\listoffigures     % here, if applicable.
 
@@
 
-\section{Motivations}
-
-Adaptivity and stability for CFD problems are issues for high Reynolds and Mach numbers. 
-\todo{FINISH}
-
-Address the fact that CFD problems have issues of robustness; introduce reasoning that we will study the model problem of convection-diffusion first to better understand this.
-
-\subsection{Singular perturbation problems and robustness}
-
-Historically, the Galerkin method has been very successfully applied to a broad range of problems in solid mechanics, for which the variational problems resulting from the PDE are symmetric and coercive (positive-definite).
-It is well known that the finite element method produces optimal or near-optimal results for such problems, with the finite element solution matching or coming close to the best approximation of the solution in the finite element space.
-However, standard Bubnov-Galerkin methods tend to perform poorly for the class of PDEs known as singular perturbation problems.
-These problems are often characterized by a parameter that may be either very small or very large in the context of physical problems.
-An additional complication of singular perturbation problems is that very often, in the limiting case of the parameter blowing up or decreasing to zero, the PDE itself will change types (e.g.\ from elliptic to hyperbolic).
-
-A canonical example of a singularly perturbed problem is the convection-diffusion equation on domain $\Omega \in \mathbb{R}^3$,
-\[
-\div \left(\beta u\right) - \epsilon \Delta u = f.
-\]
-The equation represents the change in the scalar quantity $u$, representing the concentration of a quantity in a given medium, taking into account both convective and diffusive effects.
-$\beta \in \mathbb{R}^3$ specifies the direction and magnitude of convection, while the singular perturbation parameter $\epsilon$ represents the diffusivity of the medium.
-In the limit of an inviscid medium as $\epsilon\rightarrow 0$, the equation changes types, from elliptic to hyperbolic, and from second order to first order.
-
-We will illustrate the issues associated with numerical methods for this equation using one dimensional examples.  In 1D, the convection-diffusion equation is
-\begin{align*}
-\beta u'-\epsilon u'' &= f.
-\end{align*}
-For Dirichlet boundary conditions $u(0)=u_0$ and $u(1)= u_1$, the solution can develop sharp boundary layers of width $\epsilon$ near the outflow boundary $x=1$.
-
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.4]{figs/GalerkinOscTight.png}
-\caption{Oscillations in the 1D finite element solution of the convection-diffusion equation for small diffusion.}
-\label{fig:GalerkinOsc}
-\end{figure}
-
-The poor performance of the finite element method for this problem is reflected in the bound on the error in the finite element solution --- under the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}:
-\[
-\|u-u_h\|_\epsilon \leq C \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
-\]
-for $\|u\|_\epsilon^2 \coloneqq \|u\|_{L^2}^2 + \epsilon \|u'\|_{L^2}^2$, with $C$ independent of $\epsilon$. An alternative formulation of the above bound is 
-\[
-\|u-u_h\|_{H^1(0,1)} \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
-\]
-where $C(\epsilon)$ grows as $\epsilon\rightarrow 0$.
-The dependence of the constant $C$ on $\epsilon$ is referred to as a \textit{loss of robustness} --- as the singular perturbation parameter $\epsilon$ decreases, our finite element error is bounded more and more loosely by the best approximation error.
-As a consequence, the finite element solution can diverge significantly from the best finite element approximation of the solution for very small values of $\epsilon$.
-For example, Figure~\ref{fig:GalerkinOsc} shows an example of how, on a coarse mesh, and for small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation with a boundary layer develops spurious oscillations everywhere in the domain, even where the best approximation error is small.
-These oscillations grow in magnitude as $\epsilon \rightarrow 0$, eventually polluting the entire solution.
-
-\section{Goal}
-
-To develop a robust, stable $hp$-adaptive scheme for the steady compressible laminar Navier-Stokes equations in transonic/supersonic regimes.
-\todo{FINISH}
-
-\section{Literature review}
-
-For the past half-century, problems in computational fluid dynamics (CFD) have been solved using a multitude of methods, many of which are physically motivated, and thus applicable only to a small number of problems and geometries.
-We consider more general methods, whose framework is applicable to different problems in CFD; however, our specific focus will be on the nonlinear shock problems of compressible aerodynamics.
-Broadly speaking, the most popular general methods include (in historical order) finite difference methods, finite volume methods, and finite element methods.
-
-\subsection{Finite difference and finite volume methods}
-
-For linear problems, finite difference (FD) methods approximate derivatives based on interpolation of pointwise values of a function.
-FD methods were popularized first by Lax, who introduced the concepts of the monotone scheme and numerical flux.
-For the conservation laws governing compressible aerodynamics, FD methods approximated the conservation law, using some numerical flux to reconstruct approximations to the derivative at a point.
-Finite volume (FV) methods are similar to finite difference methods, but approximate the integral version of a conservation law as opposed to the differential form.
-FD and FV have roughly the same computational cost/complexity; however, the advantage of FV methods over FD is that FV methods can be used on a much larger class of discretizations than FD methods, which require uniform or smooth meshes.
-
-For nonlinear shock problems, the solution often exhibits sharp gradients or discontinuities, around which the solution would develop spurious Gibbs-type oscillations.
-Several ideas were introduced to deal with oscillations in the solution near a sharp gradient or shock: artificial diffusion, total variation diminishing (TVD) schemes, and slope limiters.
-However, each method had its drawback, either in terms of loss of accuracy, dimensional limitations, or problem-specific parameters to be tuned \cite{Shu:Lectures}.
-Harten, Enquist, Osher and Chakravarthy introduced the essentially non-oscillatory (ENO) scheme in 1987 \cite{ENO}, which was improved upon with the weighted essentially non-oscillatory (WENO) scheme in \cite{WENO}.
-WENO remains a popular choice today for both finite volume and finite difference schemes.
-Most of these methods can be interpreted as adding some specific artificial diffusion to the given numerical scheme.
-We refer to such schemes as \emph{modified equation} methods, as the exact solution no longer satisfies the discrete system due to the presence of additional artificial diffusion.
-
-Historically, finite volumes and finite difference methods have been the numerical discretizations of choice for CFD applications; the simplicity of implementation of the finite difference method allows for quick turnaround time, and the finite volume method is appealing due to its locally conservative nature and flexibility.
-More recently, the finite element (FE) method has gained popularity as a discretization method for CFD applications for its stability properties and rigorous mathematical foundations.
-Early pioneers of the finite element method for CFD included Zienkiewicz, Oden, Karniadakis, and Hughes \cite{ChungCFDBook}.
-
-\subsection{Stabilized finite element methods}
-
-The finite element/Galerkin method has been widely utilized in engineering to solve partial differential equations governing the behavior of physical phenomena in engineering problems.
-The method relates the solution of a partial differential equation (PDE) to the solution of a corresponding variational problem.
-The finite element method itself provides several advantages --- a framework for systematic mathematical analysis of the behavior of the method, weaker regularity constraints on the solution than implied by the strong form of the equations, and applicability to very general physical domains and geometries for arbitrary orders of approximation.
-
-Traditionally, instability/loss of robustness in finite element methods has been dealt with using residual-based stabilization techniques.
-Given some variational form, the problem is modified by adding to the bilinear form the strong form of the residual, weighted by a test function and scaled by a stabilization constant $\tau$.
-The most well-known example of this technique is the streamline-upwind Petrov-Galerkin (SUPG) method, which is a stabilized FE method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.
-SUPG stabilization not only removes the spurious oscillations from the finite element solution of the convection-diffusion equation, but delivers the best finite element approximation in the $H^1$ norm.
-
-\subsubsection{SUPG}
-
-The Streamline Upwind Petrov Galerkin (SUPG) method is a stabilization method for $H^1$-conforming finite elements, the idea of which was originally motivated by artificial diffusion techniques in finite differences.
-In particular, for the homogeneous 1D convection-diffusion equation, it is possible to recover, under a finite difference method, the exact solution at nodal points by adding an ``exact" artificial diffusion based on the mesh size $h$ and the magnitudes of the convection $\beta$ and the viscosity $\epsilon$.
-
-The idea of ``exact" artificial viscosity was adapted to finite elements not through the direct modification of the equations, but through the test functions and weighting of the residual.
-In particular, finite element and Galerkin methods are often referred to as ``weighted residual" methods, since the starting point of both is to multiply the residual by a particular test, or weighting, function.
-Standard Galerkin methods, known as Bubnov-Galerkin methods, simply choose these weighting functions to be the same as the the basis functions used to approximate the solution.
-A Petrov-Galerkin method refers to any Galerkin method other than a classical Bubnov-Galerkin method.
-
-We will introduce the SUPG method at an abstract level for illustrative purposes only.
-Further details and perspectives on the SUPG method can be found in \cite{SUPG}, as well as in an upcoming book by Hughes.
-The convection-diffusion equation can be written as follows:
-\[
-Lu = \left(L_{\rm adv} + L_{\rm diff} \right) u = f,
-\]
-where $L_{\rm adv}u \coloneqq \div \left(\beta u\right)$ is the first order advective operator, and $L_{\rm diff}u \coloneqq \epsilon \Delta u$ is the second-order diffusive operator (then, roughly speaking, $L_{\rm diff} u = 0$).
-Let us assume $u$ to be a linear combination of piecewise-linear basis functions $\phi_i, i = 0,\ldots,N$.
-The SUPG method is then to solve
-\[
-\int_\Omega L u v + \int_\Omega \tau \left(L_{\rm adv}v\right)\left( L u - f\right) = \int_\Omega f v 
-\]
-for where $\tau$ is the SUPG parameter.
-For uniform meshes in 1D, $\tau$ is chosen such that, for $f=0$, the matrix system resulting from SUPG is exactly equal to the finite difference system under ``exact" artificial diffusion.
-However, unlike the artificial diffusion method, for $f\neq 0$, the SUPG method still delivers optimal stabilization.
-In fact, the SUPG finite element solution in 1D is nothing less than the nodal interpolant and the best $H^1$ approximation of the exact solution, as seen in Figure~\ref{fig:SUPG}.
-
-\begin{figure}[!h]
-\centering
-\subfigure[SUPG and standard FEM solutions]{\includegraphics[scale=.43]{figs/SUPG.png}}
-\subfigure[SUPG test function]{\includegraphics[scale=.22]{figs/SUPGtest.png}}
-\caption{SUPG and standard Bubnov-Galerkin solutions to the 1D convection-dominated diffusion equation, and a modified SUPG test function (in black) corresponding to a linear basis ``hat" function (in red).
-The upwind portion of the element is emphasized, while the downwind portion is decreased.
-The magnitude of the discontinuity between the upwind and downwind portion is controlled by the intrinsic timescale parameter $\tau$.
-}
-\label{fig:SUPG}
-\end{figure}
-
-The idea of emphasizing the upwind portion of a test function is an old idea, introduced in 1977 by Zienkiewicz et al.\ in \cite{zienkUpwind}.
-However, the precise amount of upwinding,\footnote{Insufficient upwinding results in a method which still exhibits oscillations and instabilities, while excessive upwinding leads to an overly diffusive method.} as well as the connection to residual-based stabilization methods, were novel to SUPG.
-
-The method can be made to ``work" for $p>1$, but the results are not as strong as for linear elements, and there is no clear generalization of SUPG to higher order elements.
-Additionally, the stabilization properties of SUPG are weaker in higher dimensions, and the SUPG solution is no longer the $H^1$ best approximation for 2D and 3D problems \todo{find citation}.
-Despite these caveats, SUPG is still the most popular stabilization method of choice for convection-diffusion type problems, in both academic and industry applications.
-
-An important feature of SUPG and other residual-based stabilization techniques that separates it from modified equation methods is the idea of \textit{consistency} --- by adding stabilization terms based on the residual, the exact solution still satisfies the same variational problem (i.e.\ Galerkin orthogonality still holds).
-Contrast this to the artificial diffusion methods in finite difference and finite volume methods, where a specific amount of additional viscosity is added based on the magnitude of the convection and diffusion parameters: unlike residual-based stabilization schemes, the exact solution to the original equation no longer satisfies the new stabilized formulation.
-
-This addition of residual-based stabilization terms can be interpreted as a modification of the test functions as well.  For SUPG, the formulation can equivalently be written as
-\[
-\int_\Omega\left( Lu-f\right) v_i = \int_\Omega f v_i, \quad i = 0,\ldots,N
-\]
-where $v_i$ is defined as
-\[
-v_i = \phi_i(x) + \tau L_{\rm adv} \phi_i.  
-\]
-In other words, the test function $v_i$ is a perturbation of the basis function $\phi_i$ by a scaled advective operator applied to $\phi_i$.
-For a linear $C^0$ basis function (the ``hat" function), this naturally leads to a bias in the upwind or streamline direction of the flow $\beta$, as seen in Figure~\ref{fig:SUPG}.
-
-An important connection can now be made --- stabilization can be achieved by changing the test space for a given problem.
-We will discuss in Section~\secref{optimalTest} approaching the idea of stabilization through the construction of \textit{optimal test functions} to achieve optimal approximation properties.
-
-\subsubsection{DG methods}
-
-Discontinuous Galerkin (DG) methods form a subclass of FEM; first introduced by Reed and Hill in \cite{Reed:73}, these methods were later analyzed by Cockburn and Shu \cite{CockburnShu:DG} and have rapidly gained popularity for CFD problems.
-Rather than having a continuous basis where the basis function support spans several element cells, DG opts instead for a discontinuous, piecewise polynomial basis, where, like FV schemes, a numerical flux facilitates communication between discontinuities (unlike FV methods, however, there is no need for a reconstruction step).
-Advantages of DG methods include the local conservation property, easily modified local orders of approximation, easy adaptivity in both $h$ and $p$, and efficient parallelizability.
-
-An additional reason for the popularity of DG methods is that they can be interpreted as stabilized FE methods through appropriate choices of the numerical flux \todo{add Brezzi citation}.
-We will illustrate this with the pure convection equation in 1D.
-
-Local conservation: in 1D, numerical solution at outflow is exact.
-
-\todo{Add 1D description and diagrams (Hughes book) of DG formulation for convection with upwind flux.}
-
-For example, for the pure convection problem, the solution has only regularity in the streamline direction, but is only $L^2$ in the crosswind direction.
-As a consequence, the boundary trace of the solution is defined only in the direction of convection.
-The upwind DG method addresses the above issue by choosing the numerical flux to be the upwind flux; in this case, the DG numerical flux can be viewed as imparting additional regularity than is present in the solution \cite{DPG1,DPG3}.
-
-A more recent development in DG methods is the idea of \emph{hybridized} DG (HDG), introduced by Gopalakrishnan and Lazarov \cite{hybridDG}.
-The hybridized DG framework addresses several criticisms of common DG methods (globally coupled degrees of freedom, complicated/inefficient implementation procedures, suboptimal convergence of approximate fluxes) by identifying degrees of freedom with support only on element edges.
-Neighboring elements are coupled together only through these degrees of freedom, which can be interpreted as Lagrange multipliers enforcing weak continuity of the trial space.
-Additionally, HDG methods \todo{add bit about numerical fluxes still used, stabilization param}
-
-\subsubsection{Optimization/NL solvers}
-
-Reference (MIT, Fidkowski)
-
-\todo{Find more nonlinear solvers}
-
-\section{Scope}
-
-This proposal will
-\begin{enumerate}
-\item Introduce DPG
-\item Cover the problem of robustness for model problems
-\item Extend results/formulations to nonlinear problems
-\item Discuss proposed work
-\end{enumerate}
-
-\chapter{Range of CFD problems}
-
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.45]{figs/CFD_tree.pdf}
-\caption{A diagram of common CFD problems and their simplifying assumptions.}
-\end{figure}
-
-\begin{itemize}
-\item Discuss full compressible Navier-Stokes with boundary layers
-\item Discuss full compressible Navier-Stokes without boundary layers, connect to Euler (mention Dr Young and Boeing and the IBL connection \cite{BoeingDrela})
-\item Discuss model problems
-\end{itemize}
+\include{proposalIntro}
 
@@
 
-The Discontinuous Petrov-Galerkin (DPG) method of Demkowicz and Gopalakrishnan was first formulated in \cite{DPG1} for the pure convection problem.
+\include{DPGtheory}
 
-Historically, the name DPG was given by Bottasso, Micheletti, Sacco and Causin to their method for elliptic problems in \cite{BottassoMichelettiSacco02}.
-The method was then extended to other problems, including convection-diffusion, in \cite{BottassoMichelettiSacco05,CausinSacco05,CausinSaccoBottasso05}.
-
-The key point in the method of Bottasso et al.\ was their method of hybridization of fluxes.
-Whereas HDG methods will identify an additional flux unknown on the boundary, the numerical flux coupling neighboring elements together is still typically computed in part using contributions from the field variables.
-In the DPG formulation, all numerical fluxes are declared to be independent unknowns, leaving the interior field degrees of freedom completely uncoupled from element to element.
-\todo{Finish, check if this is true.}
-
-The breakthrough came in \cite{DPG2}, where the concept of locally-computable optimal test functions led to the development of the DPG method in its current form.
-
-\todo{Clean up}
-This DPG method with optimal test functions is better understood in \cite{DPG3,DPG4}, extended to problems in \cite{DPGElas,stokesDPG}, well-posedness theory developed for Poisson and convection-diffusion in \cite{analysisDPG}, extended to large class of Friedrichs systems in \cite{Bui-ThanhDemkowiczGhattas11b}.
-\cite{practicalDPG}.
-
-Optimal order comparison to DG in \cite{DPG1}. Comparisons to other DG methods in \cite{Bui-ThanhDemkowiczGhattas11a,DGDPG}.
-
-\section{Optimal Petrov-Galerkin methods}
-
-\seclab{optimalTest} Petrov-Galerkin methods, in which the test space differs from the trial space, have been explored for over 30 years, beginning with the approximate symmetrization method of Barrett and
-Morton~\cite{BARRETT01101981}.
-The idea was continued with the SUPG method of Hughes, and the characteristic Petrov-Galerkin approach of Demkowicz and Oden~\cite{Demkowicz1986188}, which introduced the
-idea of tailoring the test space to change the norm in which a finite element method would converge.
-
-The idea of optimal test functions was introduced by Demkowicz and Gopalakrishnan in \cite{DPG2}.
-Conceptually, these optimal test functions are the natural result of the minimization of a residual corresponding to the operator form of a variational equation.
-The connection between stabilization and least squares/minimum residual methods has been observed previously \cite{GLS}.
-However, the method in \cite{DPG2} distinguishes itself by measuring the residual of the natural \textit{operator form of the equation}, which is posed in the dual space, and measured with the dual norm, as we now discuss.
-
-Throughout the paper, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U'$ and $V'$ as the respective topological dual spaces.
-Let $U_h \subset U$ and $V_h\subset V$ be finite dimensional subsets.
-We are interested in the following problem
-\begin{equation}
-\eqnlab{variationEq}
-\left\{
-  \begin{array}{l}
-    \text{Given } l \in V', \text{ find } u_h \in U_h  \text{ such that} \\ 
-    b(u_h,v_h) = l(v_h), \quad \forall v_h\in V_h,
-  \end{array}
-  \right.
-\end{equation}
-where $b\LRp{\cdot,\cdot}: U \times V \to \mbb{R}$ is a continuous
-bilinear form.  $U$ is chosen to be some trial space of approximating functions, but $V_h$ is as of yet unspecified.
-
-Throughout the paper, we suppose the variational
-problem \eqnref{variationEq} to be well-posed. In that case, we can
-identify a unique operator $B:U\rightarrow V'$ such that
-\[
-\langle Bu,v\rangle_V \coloneqq b(u,v), \quad u\in U, v\in V
-\]
-with $\LRa{\cdot, \cdot}_V$ denoting the duality pairing between $V'$ and $V$, to obtain the operator form of the continuous variational problem
-\begin{equation}
-\eqnlab{dualEq}
-Bu = l \quad \text{in } V'.
-\end{equation}
-In other words, we can represent the continuous form of our variational equation
-\eqnref{variationEq} equivalently as the operator equation \eqnref{dualEq} with values in the
-dual space $V'$.  This motivates us to consider the conditions under which the solution to \eqnref{variationEq} is the solution to the minimum residual problem in $V'$ 
-\[
-u_h = \underset{u_h\in U_h}{\arg\min}\, J(u_h),
-\]
-where $J(w)$ is defined for $w\in U$ as 
-\[
-J(w) = \frac{1}{2}\|Bw-l\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(w,v)-l(v)|^2}{\nor{v}_V^2}.
-\]
-For convenience in writing, we will abuse the notation $\sup_{v \in V}$ to denote $\sup_{v\in V\setminus\{0\}}$ for the remainder of the paper.
-
-Let us define $R_V: V \to V'$ as the Riesz map, which identifies
-elements of $V$ with elements of $V'$ by 
-\[
-\langle R_V v,\delta
-v\rangle_V \coloneqq(v, \delta v)_V, \quad \forall \delta v \in V.
-\]
-Here, $(\cdot, \cdot)_V$ denotes the
-inner product in $V$. As $R_V$ and its inverse, $R_V^{-1}$, are both
-isometries, e.g.\ $\|f\|_{V'} = \|R_V^{-1} f\|_V, \forall f \in V'$, we
-have
-\begin{equation}
-\eqnlab{minimization}
-\min_{u_h\in U_h} J(u_h) = \frac{1}{2}\left\|Bu_h-l\right\|_{V'}^2 =  \frac{1}{2}\left\|R_V^{-1}(Bu_h-l)\right\|_V^2.
-\end{equation}
-The first order optimality condition for \eqnref{minimization} requires
-the G\^ateaux derivative to be zero in all directions $\delta u \in
-U_h$, i\.e\.,
-\begin{align*}
-\left(R_V^{-1}(Bu_h-l),R_V^{-1}B\delta u\right)_V = 0, \quad \forall \delta u \in U. 
-\end{align*}
-We define, for a given $\delta u \in U$, the corresponding {\em optimal test function} $v_{\delta u}$
-\begin{equation}
-\eqnlab{optv}
-v_{\delta u} \coloneqq R_V^{-1}B\delta u \quad  \text{in } V.
-\end{equation} 
-The optimality condition then becomes
-\[
- \langle Bu_h-l, v_{\delta u}\rangle_V = 0, \quad \forall \delta u \in U
-\]
-which is exactly the standard variational equation in
- \eqnref{variationEq} with $v_{\delta u}$ as the test functions.
-We can define the optimal test space $V_{\rm opt} \coloneqq \{v_{\delta u} \text{ s.t.
-} \delta u\in U\}$.
-Thus, the solution of the variational problem \eqnref{variationEq} with test space $V_h = V_{\rm opt}$ minimizes the residual in the dual norm $\nor{Bu_h-l}_{V'}$.
-This is the key idea behind the concept of optimal test functions.
-
-Since $U_h \subset U$ is spanned by a finite number of basis functions $\LRc{\varphi_i}_{i=1}^N$, \eqnref{optv} allows us to compute (for each basis function) a corresponding optimal test function $v_{\varphi_i}$.
-The collection $\LRc{v_{\varphi_i}}_{i = 1}^N$ of optimal test functions then forms a basis for the optimal test space.
-In order to express optimal test functions defined in \eqnref{optv} in a more familiar form, we take  $\delta u = \varphi$, a generic basis function in $U_h$, and rewrite \eqnref{optv} as
-\[
-R_Vv_{\varphi} = B\varphi, \quad \text{in } V',
-\]
-which is, by definition, equivalent to
-\[
-\LRp{v_\varphi,\delta v}_V = \LRa{R_Vv_\varphi,\delta v}_{V}=
-\LRa{B\varphi, \delta v}_V = b\LRp{\varphi,\delta v}, \quad
-\forall \delta v \in V.
-\]
-%% Now, let us define the \textit{trial-to-test} operator $T =
-%% R_V^{-1}B$, which, by \eqnref{optv}, maps a trial function $\delta u$
-%% to its corresponding \textit{optimal} test function $v = T\delta u$.
-%% On the other hand,
-As a result, optimal test functions can be determined by solving the auxiliary
-variational problem
-\begin{equation}
-\eqnlab{optvVar}
-\left(v_\varphi,\delta v\right)_V = b(\varphi,\delta v), \quad \forall
-\delta v \in V.
-\end{equation}
-However, in general, for standard $H^1$ and $H({\rm div})$-conforming finite element methods, test functions are continuous over the entire domain, and hence solving variational problem \eqnref{optvVar} for each optimal test function requires a global operation over the entire mesh, rendering the method impractical.
-A breakthrough came through the development of
-discontinous Galerkin (DG) methods, for which basis functions are
-discontinuous over elements. In particular, the use of discontinuous
-test functions $\delta v$ reduces the problem of determining global 
-optimal test functions
-in \eqnref{optvVar} to local problems that can be solved in an
-element-by-element fashion.
-
-We note that solving \eqnref{optvVar} on each element exactly is
-infeasible since it amounts to inverting the Riesz map $R_V$ exactly.
-Instead, optimal test functions are approximated using the standard
-Bubnov-Galerkin method on an ``enriched" subspace $\tilde{V} \subset
-V$ such that $\dim(\tilde{V}) > \dim(U_h)$ elementwise \cite{DPG1, DPG2}. In this
-paper, we assume the error in approximating the optimal test functions
-is negligible, and refer to the work in \cite{practicalDPG} for
-estimating the effects of approximation error on the performance of DPG.
-
-It is now well known that the DPG method
-delivers the best approximation error in the ``energy norm" --- that is
-\cite{Bui-ThanhDemkowiczGhattas11a, DPG2,DPG4} 
-\begin{equation}
-\eqnlab{optimalError}
-\nor{u-u_h}_{U,E} = \inf_{w\in U_h} \nor{u-w}_{U,E},
-\end{equation}
-where the energy norm $\|\cdot \|_{U,E}$ is defined for a function $\varphi \in U$ as
-\begin{equation}
-\eqnlab{energyNorm} \|\varphi\|_{U,E} \coloneqq \sup_{v\in V}
-\frac{b(\varphi,v)}{\|v\|_V} = \sup_{\nor{v}_V = 1} b(\varphi,v) =
-\sup_{\nor{v}_V = 1} \LRa{B\varphi,v}_V = \nor{B\varphi}_{V'} =
-\nor{v_\varphi}_V,
-\end{equation}
-where the last equality holds due to the isometry of the Riesz map
-$R_V$ (or directly from \eqnref{optvVar} by taking the supremum). An
-additional consequence of adopting such an energy norm is that,
-without knowing the exact solution, the energy error $\|u-u_h\|_{U,E}$ can
-be determined by computing $\|v_{u-u_h}\|_V$ from the following
-identity
-\[
-\left(v_{u-u_h},\delta v\right)_V = b(u-u_h,\delta v) = l\LRp{\delta
-v} - b(u_h,\delta v).
-\]
-This is simply a consequence of the least-squares nature of DPG; the energy error is simply the norm of the  residual in $V'$.
-
-Practically speaking, this implies that the DPG method is discretely stable on any mesh.
-In particular, DPG is unconditionally stable for higher order adaptive meshes, where discrete stability is often an issue.
-
-\section{Ultra-weak variational formulation}
-\seclab{abstractUweak}
-
-The naming of the discontinuous Petrov-Galerkin method refers to the fact that the method is a Petrov-Galerkin method, and that the test functions are specified to be discontinuous across element boundaries.
-There is no specification of the regularity of the trial space, and we stress that the idea of DPG is not inherently tied to a single variational formulation \cite{Bui-ThanhDemkowiczGhattas11a}.
-
-In most of the DPG literature, however, the discontinuous Petrov-Galerkin method refers to the combination of the concept of locally computable optimal test functions in Section \secref{optimalTest} with the so-called ``ultra-weak formulation" \cite{DPG1,DPG2,DPG3,DPG4,DPGElas,DBLP:journals/procedia/NiemiCC11}.
-Unlike the previous two sections in which we studied the general equation \eqnref{variationEq} given by abstract bilinear and linear forms, we now consider a concrete instance of \eqnref{variationEq} resulting from an ultra-weak formulation for an abstract first-order system of PDEs $Au = f$.
-Additionally, from this section onwards, we will refer to DPG as the pairing of the ultra-weak variational formulation with the concept of locally computable optimal test functions.
-
-We begin by partitioning the domain of interest $\Omega$ into $\Nel$ non-overlapping elements $K_j, j = 1,\hdots,\Nel$ such that $\Oh = \cup_{j=1}^\Nel K_j$ and $\overline{\Omega} = \overline{\Omega}_h$.
-Here, $h$ is defined as $h= \max_{j\in \LRc{1,\hdots,\Nel}}\text{diam}\LRp{K_j}$.
-We denote the mesh ``skeleton" by $\Gh = \cup_{j=1}^\Nel \partial K_j$; the set of all faces/edges $e$, each of which comes with a normal vector ${n}_e$.
-The internal skeleton is then defined as $\Gamma^0_h = \Gh \setminus \partial \Omega$.
-If a face/edge $e \in \Gh$ is the intersection of $\partial K_i$ and $\partial K_j$, $i \ne j$, we define the following jumps:
-\[
-\jump{v} = \text{sgn} \LRp{{n}^-}v^- + \text{sgn} \LRp{{n}^+}v^+, \quad
-\jump{\tau \cdot n} = {n}^-\cdot \tau^- + {n}^+\cdot\tau^+,
-\]
-where
-\[
-\text{sgn}\LRp{{n}^{\pm}} =
-\left\{
-\begin{array}{ll}
-1 & \text{if } {n}^{\pm} = {n}_e \\
--1 & \text{if } {n}^\pm = -{n}_e
-\end{array}
-\right..
-\]
-For $e$ belonging to the domain boundary $\partial \Omega$, we define
-\[
-\jump{v} = v, \quad
-\jump{\tau \cdot n} = {n}_e\cdot \tau.
-\]
-Note that we allow arbitrariness in assigning ``-'' and ``+'' quantities to the adjacent elements $K_i$ and $K_j$.
-%For the rest of the paper, we will use the same notation for both a function and its trace (if it is well-defined) when there is no ambiguity.
-
-The ultra-weak formulation for $Au = f$ on $\Oh$, ignoring boundary
-conditions for now, reads
-\begin{equation}
-\eqnlab{uweak}
-b\left(\left(u, \widehat{u}\right),v\right) \coloneqq \langle \widehat{u}, \jump{v}
-\rangle_{\Gh} - (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh},
-\end{equation}
-where we have denoted $\LRa{\cdot,\cdot}_{\Gh}$ as the duality
-pairing on $\Gh$, $\LRp{\cdot,\cdot}_{\Oh}$ the $L^2$-inner
-product over $\Oh$, and $A_h^*$ the formal adjoint resulting from
-element-wise integration by parts.  Occasionally, for simplicity in
-writing, we will ignore the subscripts in the duality pairing and
-$L^2$-inner product if they are $\Gh$ and $\Oh$. Both the
-inner product and formal adjoint are understood to be taken
-element-wise. Using the ultra-weak formulation, the regularity
-requirement on solution variable $u$ is relaxed, that is, $u$ is now
-square integrable for the ultra-weak formulation \eqnref{uweak} to be
-meaningful, instead of being (weakly) differentiable.  The trade-off
-is that $u$ does not admit a trace on $\Gh$ even though it did
-originally. Consequently, we need to introduce an additional new
-``trace'' variable $\widehat{u}$ in \eqnref{uweak}, that is defined only on
-$\Gh$.
-
-The energy setting is now clear; namely,
-\[
-u\in L^2\LRp{\Oh} \equiv L^2(\Omega), \quad v\in V=D(A^*_h), \quad
-\widehat{u}\in \gamma(D(A)),
-\]
-where $D(A_h^*)$ denotes the broken graph space corresponding to $A_h^*$,
-and $\gamma(D(A))$ the trace space (assumed to exist) of the graph space of
-operator $A$.
-The first discussion of the well-posedness of DPG with the ultra-weak formulation can be found in \cite{analysisDPG}, where the proof is presented for the Poisson and convection-diffusion equations.
-A more comprehensive discussion of the abstract setting for DPG with the ultra-weak formulation using the graph space, as well as a more general proof of well-posedness, can be consulted in \cite{Bui-ThanhDemkowiczGhattas11b}.
-
-\section{Choices of test and trial norms}
-\seclab{energyPair}
-
-A clear property of the energy norm defined by \eqnref{energyNorm} is that the trial norm $\nor{\cdot}_{U,E}$ is induced by a given test norm.
-However, the reverse relationship holds as well; for any trial norm, the test norm that induces such a norm is recoverable through duality.
-We have a result, proved in \cite{Bui-ThanhDemkowiczGhattas11a}: assuming, for simplicity, that the bilinear form $b(u,v)$ is definite, given any norm $\nor{\cdot}_{U}$ on the trial space $U$, for $\varphi \in U$, we can represent $\nor{\varphi}_{U}$ via
-\[
-\nor{\varphi}_{U} = \sup_{v \in V}\frac{b\LRp{w,v}}{\nor{v}_{V,U}}.
-\]
-where $\nor{v}_{V,U}$ is defined through
-\[
-\nor{v}_{V,U} = \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U}}.
-\]
-%In other words, the norm $\nor{\cdot}_V$ in $V$ can be recovered using the energy norm $\nor{\cdot}_{U,E}$ in $U$, and vice versa.
-
-In particular, given two arbitrary norms $\nor{\cdot}_{U,1}$ and $\nor{\cdot}_{U,2}$ in $U$
-such that $\nor{\cdot}_{U,1} \le c \nor{\cdot}_{U,2}$ for some constant
-$c$, they generate two norms $\nor{\cdot}_{V,U,1}$ and
-$\nor{\cdot}_{V,U,2}$ in $V$ defined by
-\[
-\nor{v}_{V,U,1} \coloneqq \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U,1}}, \quad
-\text{and }\nor{v}_{V,U,2} \coloneqq \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U,2}},
-\]
-such that $\nor{\cdot}_{V,U,1}$ and $\nor{\cdot}_{V,U,2}$ induce
-$\nor{\cdot}_{U,1}$ and $\nor{\cdot}_{U,2}$ as energy
-norms in $U$, respectively. That is,
-\[
-\|\varphi\|_{U,1} = \sup_{v\in V}
-\frac{b(\varphi,v)}{\|v\|_{V,U,1}}, \quad \text{and }\|\varphi\|_{U,2} = \sup_{v\in V}
-\frac{b(\varphi,v)}{\|v\|_{V,U,2}}.
-\]
-
-A question that remains to be addressed is to establish the relationship
-between $\nor{\cdot}_{V,U,1}$ and $\nor{\cdot}_{V,U,2}$, given that
-$\nor{\cdot}_{U,1} \le c \nor{\cdot}_{U,2}$. But this is
-straightforward since we have
-\begin{align*}
- \| v \|_{V,U,2} = \sup_{u \in U} \frac{b\left(w,v\right)}{\left\|
-  w \right\|_{U,2}} \le c\sup_{w \in U} \frac{b\left(w,v\right)}{\left\| w
-  \right\|_{U,1}} = c\| v \|_{V,U,1}.
-\end{align*}
-Consequently, a stronger energy norm in $U$ will generate a weaker
-norm in $V$ and vice versa. In other words, to show that an
-energy norm $\nor{\cdot}_{U,1}$ is weaker than another energy norm
-$\nor{\cdot}_{U,2}$ in $U$, one simply needs to show the reverse inequality on the
-corresponding norms in $V$, that is, $\nor{\cdot}_{V,U,1}$ is stronger
-than $\nor{\cdot}_{V,U,2}$.
-
-From now on, unless otherwise stated, we will refer to $\nor{\cdot}_{V,U}$ as the test norm that induces a given norm $\nor{\cdot}_U$.
-Likewise, we will refer $\nor{\cdot}_{U,V}$ as the trial norm induced by a given test norm $\nor{\cdot}_V$.
-In this paper, for simplicity of exposition, we shall call a pair of norms in $U$ and $V$ that induce each other as an {\em energy norm pairing}.
-
-From the discussion above of energy norm and test norm pairings, we know that specifying either a test norm or trial norm is sufficient to define an energy pairing.
-We now derive and discuss two important energy norm pairings, the first of which begins by specifying the canonical norm in $U$ and inducing a test norm on $V$.
-The second pairing begins instead by specifying the canonical norm on $V$ under the ultra-weak formulation \eqnref{uweak} and inducing an energy norm on the trial space $U$.
-
-We begin first with the canonical norm in $U$. Since $\uh \in \gamma\LRp{D\LRp{A}}$, the standard norm for $\uh$ is
-the so-called minimum energy extension norm defined as
-\begin{equation}
-\eqnlab{MEnorm}
-\|\widehat{u}\| = \inf_{w\in D\LRp{A},
-  \left.w\right|_{\Gh}=\widehat{u}} \|w\|_{D\LRp{A}}.
-\end{equation}
-The canonical norm for the group variable $\LRp{u,\uh}$ is then given by
-\[
-\|\left(u,\widehat{u}\right)\|_U^2 = \|u\|^2_{\L} + \|\widehat{u}\|^2,
-\]
-Applying the Cauchy-Schwarz inequality, we arrive at
-\[
-b\LRp{\LRp{u,\uh},v} \le \nor{\LRp{u,\uh}}_U \nor{v}_{V,U},
-\]
-where
-\[
-\nor{v}_{V,U}^2 = \|A_h^*v\|_{\L}^2
-+\left(\sup_{\widehat{u} \in \gamma\LRp{D\LRp{A}}} \frac{\LRa{ \widehat{u},
-  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2.
-\]
-
-On the other hand, since $v \in D\LRp{A^*_h}$, the canonical norm for
-$v$ is the broken graph norm: 
-\[
-\nor{v}_V^2 =  \|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2.
-\]
-Using the Cauchy-Schwarz inequality again, we obtain
-\[
-b\LRp{\LRp{u,\uh},v} \le \nor{\LRp{u,\uh}}_{U,V} \nor{v}_{V},
-\]
-where
-\begin{equation}
-\eqnlab{inducedQuasi}
-\nor{\LRp{u,\uh}}_{U,V}^2 = \nor{u}_{\L}^2
-+\sup_{v \in D\LRp{A_h^*}} \frac{\LRa{\widehat{u},
-  \jump{v}}_{\Gh}^2}{\|v\|_V^2},
-\end{equation}
-
-Using the framework developed in \cite{Bui-ThanhDemkowiczGhattas11a},
-one can show that both pairs $\LRp{\nor{\LRp{u,\uh}}_U,
-  \nor{v}_{V,U}}$ and $\LRp{\nor{\LRp{u,\uh}}_{U,V}, \nor{v}_{V}}$ are
-energy norm pairings in the sense discussed in Section
-\secref{energyPair}. That is, the canonical norm $\nor{\LRp{u,\uh}}_U$
-in $U$ induces (generates) the norm $\nor{v}_{V,U}$ in $V$, while the
-canonical norm $\nor{v}_V$ in $V$ induces (generates) the energy norm
-$\nor{\LRp{u,\uh}}_{U,V}$ in $U$. In the DPG literature \cite{DPG4}, $\nor{v}_{V,U}$ is known as the {\em optimal test norm},
-while $\nor{v}_{V}$ is known as the {\em quasi-optimal test norm}.
-
-\begin{figure}[!h]
-\centering
-\begin{tabular}{l c c}
-Trial norm & & Test norm \\
-\hline
-$\boxed{\|u\|^2_{\L} + \|\widehat{u}\|^2}$ & $\Longrightarrow$  & $\|A_h^*v\|_{\L}^2
-+\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},
-  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2$ \\
-%\hline
-%Quasi-optimal trial norm & & Canonical test norm \\
-%\hline
-$\nor{u}_{\L}^2+\sup_{v } \left(\frac{\LRa{\widehat{u},
-  \jump{v}}_{\Gh}}{\|v\|_V}\right)^2$ &  $\Longleftarrow$ & $\boxed{\|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2}$
-\end{tabular}
-\caption{A summary of the derivation of test/trial norm pairings; we begin with the boxed norm on either the trial or test space, and induce the norm on the other space through duality.
-The optimal \textit{test} norm is naturally derived by beginning with the canonical norm on the trial space, while the quasi-optimal \textit{trial} norm is derived from beginning with the canonical norm on the test space.}
-\end{figure}
-
-The canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ provides a good
-balance between the standard norms on the field $u$ and the flux
-$\uh$ \cite{DPG4}. As a result, if the induced norm $\nor{v}_{V,U}$ (namely, the
-optimal test norm) is used to compute  optimal test functions in
-\eqnref{optvVar}, the finite element error in the canonical norm is the
-best in the sense of \eqnref{optimalError}.
-
-Unfortunately, the optimal test norm is non-localizable due to the presence of the jump term $\jump{v}$.\footnote{A localizable norm $\nor{v}_{V(\Oh)}$ can be written in the form $\nor{v}_{V(\Oh)} = \sum_{K\in\Oh} \nor{v}_{V(K)},$ where $\nor{v}_{V(K)}$ is a norm over the element $K$.} Since the jump terms couple elements together, the evaluation of the jump terms requires contributions from all the elements in the mesh.
-Consequently, solving for an optimal test function
-amounts to inverting the Riesz map %, defined on the left sideof \eqnref{optvVar}, 
-over the entire mesh $\Oh$, making the optimal test norm impractical.
-
-On the other hand, the quasi-optimal test norm $\nor{v}_V$, namely the canonical norm in $V$, \textit{is} localizable, and hence practical.
-However, it's worth noting the difference between the induced energy norm $\nor{\LRp{u,\uh}}_{U,V}$ and the canonical norm in $U$; under the induced norm $\nor{\LRp{u,\uh}}_{U,V}$ there is no natural interpretation for the norm in which the error in the flux variable $\uh$ is measured.
-
-Using a variant of the quasi-optimal test norm, numerical results show that the DPG method appears to provide a ``pollution-free" method without phase error for the Helmholtz equation \cite{DPG4}, and analysis of the pollution-free nature of DPG is currently under investigation.
-Similar results have also been obtained in the context of elasticity \cite{DPGElas} and the linear Stokes equations \cite{Camellia}.
-On the theoretical side, the quasi-optimal test norm has been shown to yield a well-posed DPG methodology for the Poisson and convection-diffusion equations \cite{analysisDPG}.
-More recently, this theory has been generalized to show the well-posedness of DPG for the large class of PDEs of Friedrichs' type \cite{Bui-ThanhDemkowiczGhattas11b}.
-
-\chapter{A robust DPG method for convection-dominated diffusion}
+\chapter{A robust DPG method for convection-diffusion}
 
@@
 \end{itemize}
+\todo{Transition between paper and this bit}
 
-\chapter{DPG for nonlinear problems}
+\include{DPGrobustness}
+
+\chapter{Proposed work}
 
@@
 
-\section{Summary: completed/propsed work}
+\include{NonlinDPG}
+\include{BurgersNotes}
+\include{NSNotes}
+
+\section{Area requirements}
 
@@
 \bibliographystyle{plain}
-\bibliography{CFD_intro,DPG_old,paper,NS}
+\bibliography{CFD_intro,DPG_old,paper,LitRev,NSNotes}
+
+%\chapter{Appendix}
+\appendix
+\input{paper_appendix.tex}
 

### 2012-06-15 docs/Jesse/Proposal/proposalIntro.tex
adding more additions (NL DPG) to proposal

@@
 
-Over the last three decades, the use of Computational Fluid Dynamics as an engineering and design tool in design of aircraft has become common.
-Wind tunnel experiments are often complemented by computational simulations, and the simulation of off-design conditions.
+Over the last three decades, Computational Fluid Dynamics (CFD) simulations have become commonplace as a tool in the engineering and design of high-speed aircraft.
+Wind tunnel experiments are often complemented by computational simulations, and CFD technologies have proved very useful in both the reduction of aircraft development cycles, and in the simulation of conditions difficult to reproduce experimentally.
 Great advances have been made in the field since its introduction, especially in areas of meshing, computer architecture, and solution strategies.
@@
 \end{itemize}
-Both of these issues are tied to the notion of \emph{robustness}.  We define robustness loosely as the degradation of solution quality with respect
+Both of these issues are tied to the notion of \emph{robustness}.
+We define robustness loosely as the degradation of the quality of numerical solutions with respect to a given problem parameter.
+In the context of CFD, the parameter of interest is the Reynolds number (the nondimensional equivalent of viscosity) --- for typical physical conditions of interest for the compressible Navier-Stokes equations, the Reynolds number is extremely high, on the order of 1e7, yielding solutions with two vastly different scales - inviscid phenomena at an $O(1)$ scale, and $O(1e-7)$ viscous phenomena.
 
-typical physical conditions of interest for the compressible Navier-Stokes equations involve low viscosity/high Reynolds numbers.
-
-Higher order adaptivity and stability for CFD problems are issues for high Reynolds and Mach numbers. 
-\todo{Address the fact that CFD problems have issues of robustness; introduce reasoning that we will study the model problem of convection-diffusion first to better understand this. }
+The full Navier-Stokes equations are not well understood in a mathematical sense --- in order to more clearly illustrate the issue of robustness for problems in CFD, we will study first the important model problem of convection-dominated diffusion.
 
@@
 
-Historically, the Galerkin method has been very successfully applied to a broad range of problems in solid mechanics, for which the variational problems resulting from the PDE are symmetric and coercive (positive-definite).
+%Historically, the Galerkin method has been very successfully applied to a broad range of problems in solid mechanics, for which the variational problems resulting from the PDE are symmetric and coercive (positive-definite).
 It is well known that the finite element method produces optimal or near-optimal results for such problems, with the finite element solution matching or coming close to the best approximation of the solution in the finite element space.
-However, standard Bubnov-Galerkin methods tend to perform poorly for the class of PDEs known as singular perturbation problems.
+However,
+
+Standard numerical methods tend to perform poorly across the board for the class of PDEs known as singular perturbation problems.
 These problems are often characterized by a parameter that may be either very small or very large in the context of physical problems.
 An additional complication of singular perturbation problems is that very often, in the limiting case of the parameter blowing up or decreasing to zero, the PDE itself will change types (e.g.\ from elliptic to hyperbolic).
-
 A canonical example of a singularly perturbed problem is the convection-diffusion equation on domain $\Omega \in \mathbb{R}^3$,
@@
 \includegraphics[scale=.4]{figs/GalerkinOscTight.png}
-\caption{Oscillations in the 1D finite element solution of the convection-diffusion equation for small diffusion.}
+\caption{Oscillations in the 1D finite element solution of the convection-diffusion equation for small diffusion \cite{GalerkinOsc}.
+Standard finite volume and finite difference methods exhibit similar behavior.}
 \label{fig:GalerkinOsc}
 \end{figure}
-
+We consider for now the Galerkin finite element method as applied to convection-dominated diffusion.
+Standard finite element methods (as well as standard finite volume and finite difference methods) perform poorly for the case of small $\epsilon$.
 The poor performance of the finite element method for this problem is reflected in the bound on the error in the finite element solution --- under the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}:
@@
 where $C(\epsilon)$ grows as $\epsilon\rightarrow 0$.
-The dependence of the constant $C$ on $\epsilon$ is referred to as a \textit{loss of robustness} --- as the singular perturbation parameter $\epsilon$ decreases, our finite element error is bounded more and more loosely by the best approximation error.
+The dependence of the constant $C$ on $\epsilon$ is what we refer to as a \textit{loss of robustness} --- as the singular perturbation parameter $\epsilon$ decreases, our finite element error is bounded more and more loosely by the best approximation error.
 As a consequence, the finite element solution can diverge significantly from the best finite element approximation of the solution for very small values of $\epsilon$.
@@
 
-To develop a robust, stable $hp$-adaptive scheme for the steady compressible laminar Navier-Stokes equations in transonic/supersonic regimes.
-\todo{FINISH}
+From the perspective of the full Navier-Stokes equations, this loss of robustness is doubly problematic.
+Not only will any nonlinear solution suffer from similar non-physical oscillations, but nonlinear solvers themselves may fail to yield a solution due to such instabilities --- a nonlinear solution is almost always computed by solving a series of linear problems whose solutions will converge to the nonlinear solution under appropriate assumptions, and the presence of such oscillations in each linear problem can cause the solution convergence to slow significantly or even diverge.
+
+Our goal is to develop a \emph{stable, higher order adaptive scheme} for the steady compressible laminar Navier-Stokes equations in transonic/supersonic regimes that is \emph{robust for very small viscosity}.
+In particular, we hope to present a method for which $hp$-adaptivity can be applied to problems in compressible flow.
 
@@
 
+Historically, the Galerkin method has been very successfully applied to a broad range of problems in solid mechanics, for which the variational problems resulting from the PDE are symmetric and coercive (positive-definite).
+It is well known that the finite element method produces optimal or near-optimal results for such problems, with the finite element solution matching or coming close to the best approximation of the solution in the finite element space.
+However, standard Galerkin methods tend to perform poorly for singular perturbation problems, developing instabilities when the singular perturbation parameter is very small.
+
 Traditionally, instability/loss of robustness in finite element methods has been dealt with using residual-based stabilization techniques.
@@
 
+All Galerkin methods involve both trial (approximating) and test (weighting) functions.
+Standard Galerkin methods, where these trial and test functions are taken from the same space, are referred to as Bubnov-Galerkin methods.
+A Petrov-Galerkin method refers to any Galerkin method other than a classical Bubnov-Galerkin method.
 The Streamline Upwind Petrov Galerkin (SUPG) method is a stabilization method for $H^1$-conforming finite elements, the idea of which was originally motivated by artificial diffusion techniques in finite differences.
@@
 In particular, finite element and Galerkin methods are often referred to as ``weighted residual" methods, since the starting point of both is to multiply the residual by a particular test, or weighting, function.
-Standard Galerkin methods, known as Bubnov-Galerkin methods, simply choose these weighting functions to be the same as the the basis functions used to approximate the solution.
-A Petrov-Galerkin method refers to any Galerkin method other than a classical Bubnov-Galerkin method.
+Standard Bubnov-Galerkin methods simply choose these weighting functions to be the same as the the basis functions used to approximate the solution.
 
@@
 This specific choice of $v(x_K)$ as the upwind value is crucial; similarly to SUPG, the upwind DG emphasizes the test function in the direction of convection and changes the way the residual is measured.
-As it turns out, the performance of DG for convection-type problems is closely tied to this upwinding --- choosing the value of $v(x_K)$ to be the downwind value $v(x_K^-)$ leads to an unstable method, while choosing $v(x_K)$ to be the average of the upwind and downwind values leads to a DG method with suboptimal stability properties, similar to an $H^1$-conforming continuous Galerkin approximation\cite{Brezzi20063293}.
+As it turns out, the performance of DG for convection-type problems is closely tied to this upwinding --- choosing the value of $v(x_K)$ to be the downwind value $v(x_K^-)$ leads to an unstable method, while choosing $v(x_K)$ to be the average of the upwind and downwind values leads to a DG method with suboptimal stability properties, similar to an $H^1$-conforming continuous Galerkin approximation\cite{Brezzi20063293}.\footnote{For second-order convection-diffusion problems with small diffusion, the additional regularity imparted by choice of the DG numerical flux is often insufficient, and SUPG-type stabilization is also applied.}
 
@@
 Additionally, HDG methods \todo{add bit about numerical fluxes still used, stabilization params}
-
-\subsubsection{Optimization/NL solvers}
-
-Reference (MIT, Fidkowski)
-
-\todo{Find more nonlinear solvers}
 

### 2012-06-15 docs/Jesse/Proposal/areaReq.tex
adding more figs/tex chapters to proposal

--- 2012-06-15 docs/Jesse/Proposal/outline.tex
@@
-\documentclass{report}
-
-\usepackage{utdiss2}  		% Dissertation package style file.
-
-\usepackage{array}
-\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
-\usepackage[utf8]{inputenc}
-\usepackage{listings}
-\usepackage{mathtools}
-\usepackage{dsfont}
-\usepackage{pdfpages}
-\usepackage[textsize=footnotesize,color=green]{todonotes}
-\usepackage{algorithm, algorithmic}
-\usepackage{bm}
-\usepackage{tikz}
-\usepackage[normalem]{ulem}
-
-\usepackage{graphicx}
-\usepackage{subfigure}
-\usepackage{color}
-\usepackage{undertilde}
-\usepackage[colorlinks = true, filecolor = red, urlcolor = blue, linkcolor = black]{hyperref}
-\usepackage{pdflscape}
-\usepackage{pifont}
-%\usepackage{fullpage}
-\setlength\textwidth{6in}
-\setlength\textheight{8in}
-\setlength\oddsidemargin{0.25in} % LaTeX adds a default 1in to this!
-\setlength\evensidemargin{0.25in}
-\setlength\topmargin{-0.0in} % LaTeX adds a default 1in to this!
-\setlength\headsep{0in}
-\setlength\headheight{0in}
-\setlength\footskip{1in}
-
-\renewcommand{\topfraction}{0.85}
-\renewcommand{\textfraction}{0.1}
-\renewcommand{\floatpagefraction}{0.75}
-
-\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
-\newcommand{\tensor}[1]{\underline{\vect{#1}}}
-\newcommand{\del}{\triangle}
-\newcommand{\grad}{\nabla}
-\newcommand{\curl}{\grad \times}
-\renewcommand{\div}{\grad \cdot}
-\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
-\newcommand{\eip}[1]{a\left( #1 \right)}
-\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
-\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
-
-\newcommand{\circone}{\ding{192}}
-\newcommand{\circtwo}{\ding{193}}
-\newcommand{\circthree}{\ding{194}}
-\newcommand{\circfour}{\ding{195}}
-\newcommand{\circfive}{\ding{196}}
-
-\newcommand{\Reyn}{\rm Re}
-
-\newcommand{\bs}[1]{\boldsymbol{#1}}
-\DeclareMathOperator{\diag}{diag}
-
-\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}
-
-\newcommand{\tablab}[1]{\label{tab:#1}}
-\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
-
-\newcommand{\theolab}[1]{\label{theo:#1}}
-\newcommand{\theoref}[1]{\ref{theo:#1}}
-\newcommand{\eqnlab}[1]{\label{eq:#1}}
-\newcommand{\eqnref}[1]{\eqref{eq:#1}}
-\newcommand{\seclab}[1]{\label{sec:#1}}
-\newcommand{\secref}[1]{\ref{sec:#1}}
-\newcommand{\lemlab}[1]{\label{lem:#1}}
-\newcommand{\lemref}[1]{\ref{lem:#1}}
-
-\newcommand{\mb}[1]{\mathbf{#1}}
-\newcommand{\mbb}[1]{\mathbb{#1}}
-\newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\nor}[1]{\left\| #1 \right\|}
-\newcommand{\snor}[1]{\left| #1 \right|}
-\newcommand{\LRp}[1]{\left( #1 \right)}
-\newcommand{\LRs}[1]{\left[ #1 \right]}
-\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
-\newcommand{\LRc}[1]{\left\{ #1 \right\}}
-\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
-\newcommand{\Grad} {\ensuremath{\nabla}}
-\newcommand{\Div} {\ensuremath{\nabla\cdot}}
-\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
-\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
-\newcommand{\uh}{\widehat{u}}
-\newcommand{\fnh}{\widehat{f}_n}
-\renewcommand{\L}{L^2\LRp{\Omega}}
-\newcommand{\pO}{\partial\Omega}
-\newcommand{\Gh}{\Gamma_h}
-\newcommand{\Gm}{\Gamma_{-}}
-\newcommand{\Gp}{\Gamma_{+}}
-\newcommand{\Go}{\Gamma_0}
-\newcommand{\Oh}{\Omega_h}
-
-\newcommand{\eval}[2][\right]{\relax
-  \ifx#1\right\relax \left.\fi#2#1\rvert}
-
-\def\etal{{\it et al.~}}
-
-\def\arr#1#2#3#4{\left[
-\begin{array}{cc}
-#1 & #2\\
-#3 & #4\\
-\end{array}
-\right]}
-\def\vecttwo#1#2{\left[
-\begin{array}{c}
-#1\\
-#2\\
-\end{array}
-\right]}
-\def\vectthree#1#2#3{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-\end{array}
-\right]}
-\def\vectfour#1#2#3#4{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-#4\\
-\end{array}
-\right]}
-\date{}
-
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-
-\newcommand{\G} {\Gamma}
-\newcommand{\Gin} {\Gamma_{in}}
-\newcommand{\Gout} {\Gamma_{out}}
-
-%%%%%%%%%%%%%%% End def of new commands %%%%%%%%%%%%%%%%%%%
-
-\author{Jesse Chan}
-\address{910 E. 32nd St, Apt.\ 101\\ Austin, Texas 78705}  % Required
-
-\title{Proposal outline/notes for DPG and Compressible Navier-Stokes}
-
-\supervisor
-	[Leszek Demkowicz]
-	{Robert Moser}
-
-\committeemembers
-	[Thomas J. R. Hughes]
-	[Somebody]
-	[Somebody]
-	{Eh}
-
-\previousdegrees{B.A.}
-
-\oneandonehalfspacequote
-
-\topmargin 0.125in
-
-\makeindex
-
-%%%%%%%%%%%%%%% Start of thesis %%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-\copyrightpage          % Produces the copyright page.
-\commcertpage           % Produces the Committee Certification
-\titlepage
-
-\begin{dedication}
-\index{Dedication@\emph{Dedication}}%
-Dedicated to \ldots
-\end{dedication}
-
-\begin{acknowledgments}		% Optional
-\index{Acknowledgments@\emph{Acknowledgments}}%
-I wish to thank the multitudes of people who helped me. Time would
-fail me to tell of \ldots
-\end{acknowledgments}
-
-\utabstract
-\index{Abstract}%
-\indent
-This document has the form of a ``fake'' doctoral dissertation
-in order to provide an example of such, but it is actually a
-copy of Miguel Lerma's documentation for the Mathematics
-Department Computer Seminar of 25 March 1998 updated in July 2001
-and following by Craig McCluskey to meet the March 2001
-requirements of the Graduate School.
-
-This document and its source file show to write a Doctoral Dissertation using 
-\LaTeX{} and the utdiss2 package.
-
-\tableofcontents   % Table of Contents will be automatically
-                   % generated and placed here.
-
-%\listoftables      % List of Tables and List of Figures will be placed
-%\listoffigures     % here, if applicable.
-
-\chapter{Introduction}
-
-\include{proposalIntro}
-
-\chapter{Discontinuous Petrov-Galerkin: a minimum residual method for linear problems}
-
-\include{DPGtheory}
-
-\chapter{A robust DPG method for convection-diffusion}
-
-\begin{itemize}
-\item Describe mathematically the issue with standard Galerkin.
-\item Give proofs of robustness and numerical results (from paper)\cite{ChanHeuerBui-ThanhDemkowicz12}
-\end{itemize}
-\todo{Transition between paper and this bit}
-
-\include{DPGrobustness}
-
-\chapter{Proposed work}
-
-\begin{itemize}
-\item Introduce nonlinear residual to measure convergence, DPG formulation for nonlinear problems. Briefly discuss solution strategies (pseudo-timestep/damped Newton). 
-\item Formulate DPG for Burgers' equation as an example, show results
-\item Show DPG applied to Navier-Stokes at a broad level, with results
-\end{itemize}
-
-\include{NonlinDPG}
-\include{BurgersNotes}
-\include{NSNotes}
-
 \section{Area requirements}
@@
 \end{itemize}
-
-\bibliographystyle{plain}
-\bibliography{CFD_intro,DPG_old,paper,LitRev,NSNotes}
-
-%\chapter{Appendix}
-\appendix
-\input{paper_appendix.tex}
-
-\end{document}

### 2012-06-15 docs/Jesse/Proposal/NSNotes.tex
changed NSNotes to add new Re1000 figs, outline, proposal intro (added HDG), and DPG_old bibliography (added HDG)

@@
 
-We take the computational domain to be $\Omega = [0,2]\times[0,1]$. For $\Reyn = 500$, we begin with an initial mesh of 8 by 16 elements. 
+We take the computational domain to be $\Omega = [0,2]\times[0,1]$.
+For $\Reyn = 1000$, we experimented with initial meshes from size 4 by 8 to 8 by 16 elements.
+We note that, on a very coarse initial mesh (4 by 8 elements), the convergence of the pseudo-timestep stagnates at around a transient residual of $1e-6$; however, if we lower the tolerance only for the first step and continued with the adaptive algorithm, the solution converges below $\epsilon_t$ for all refined meshes.
+
 \begin{figure}[!h]
 \centering
-\subfigure{\includegraphics[scale=.5]{figs/rhoRe500.pdf}}
-\subfigure{\includegraphics[scale=.5]{figs/u1Re500.pdf}}
-\subfigure{\includegraphics[scale=.5]{figs/u2Re500.pdf}}
-\subfigure{\includegraphics[scale=.5]{figs/TRe500.pdf}}
-\caption{Solutions after four refinements for $\rho$, $u_1$, $u_2$, and $T$ and $\Reyn = 500$.}
-\label{fig:Re500}
-\end{figure}
-
-For $\Reyn = 1000$, we experimented with both an initial mesh of 4 by 8 and 8 by 16 elements.
-We note that, on a very coarse initial mesh (4 by 8 elements), the convergence of the pseudo-timestep stagnates at around a transient residual of $1e-6$; however, if we lower the tolerance only for the first step and continued with the adaptive algorithm, the solution converges below $\epsilon_t$ for all refined meshes.
-\begin{figure}[!h]
-\centering
-\subfigure{\includegraphics[scale=.5]{figs/rhoRe1000.pdf}}
-\subfigure{\includegraphics[scale=.5]{figs/u1Re1000.pdf}}
-\subfigure{\includegraphics[scale=.5]{figs/u2Re1000.pdf}}
-\subfigure{\includegraphics[scale=.5]{figs/TRe1000.pdf}}
-\caption{Solutions after four refinements for $\rho$, $u_1$, $u_2$, and $T$ and $\Reyn = 1000$.}
+\subfigure[$\rho$]{\includegraphics[scale=.42]{figs/rho.pdf}}
+\subfigure[$u_1$]{\includegraphics[scale=.42]{figs/u1.pdf}}
+\subfigure[$u_2$]{\includegraphics[scale=.42]{figs/u2.pdf}}
+\subfigure[$T$]{\includegraphics[scale=.42]{figs/T.pdf}}
+\caption{Solutions after six refinements for $\Reyn = 1000$.}
 \label{fig:Re500}
@@
 \centering
-\subfigure[$\Reyn = 500$]{\includegraphics[scale=.5]{figs/MeshRe500.pdf}}
-\subfigure[$\Reyn = 1000$]{\includegraphics[scale=.5]{figs/MeshRe1000.pdf}}
-\caption{Adaptive mesh after four refinement iterations for $\Reyn = 500$ and $\Reyn = 1000$.}
+\subfigure[$\rho$]{\includegraphics[scale=.4]{figs/rhozoom.pdf}}
+\subfigure[$u_1$]{\includegraphics[scale=.4]{figs/u1zoom.pdf}}
+\subfigure[$u_2$]{\includegraphics[scale=.4]{figs/u2zoom.pdf}}
+\subfigure[$T$]{\includegraphics[scale=.4]{figs/Tzoom.pdf}}
+\caption{Zoom of solutions at the beginning of the plate for $\Reyn = 1000$.}
+\label{fig:Re500}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=.75]{figs/mesh.pdf}
+\caption{Adaptive mesh after six refinements for $\Reyn = 1000$.}
 \label{fig:MeshRe500}

### 2012-06-15 docs/Jesse/Proposal/outline.tex
changed NSNotes to add new Re1000 figs, outline, proposal intro (added HDG), and DPG_old bibliography (added HDG)

@@
 
-\begin{itemize}
-\item Introduce nonlinear residual to measure convergence, DPG formulation for nonlinear problems. Briefly discuss solution strategies (pseudo-timestep/damped Newton). 
-\item Formulate DPG for Burgers' equation as an example, show results
-\item Show DPG applied to Navier-Stokes at a broad level, with results
-\end{itemize}
-
 \include{NonlinDPG}
@@
 \include{NSNotes}
-
-\section{Area requirements}
-
-\subsection{Area A}
-
-\begin{itemize}
-\item{\textbf{Completed: }} Prove robustness of DPG method for the scalar convection-diffusion problem
-\item Attempt analysis of the linearized Navier-Stokes system
-\end{itemize}
-
-\subsection{Area B}
-
-\begin{itemize}
-\item{\textbf{Completed: }} Collaborative work with Nathan Roberts on the higher order parallel adaptive DPG code Camellia.
-\item Nonlinear DPG - Hessian adjoint trick
-\item Adaptivity: anisotropic refinements and $hp$-schemes.
-\item Distributed static condensation
-\end{itemize}
-
-\subsection{Area C}
-
-\begin{itemize}
-\item{\textbf{Completed: }} Convection-dominated diffusion, Burgers, and Navier-Stokes. 
-\item Higher Reynolds number, ramp problem, Gaussian bump, airfoil.
-\item Euler with NS regularization?
-\end{itemize}
+\include{areaReq}
 
@@
 %\chapter{Appendix}
-\appendix
+\appendices
 \input{paper_appendix.tex}
+\input{hyperbolicDPG.tex}
 

### 2012-06-15 docs/Jesse/Proposal/proposalIntro.tex
changed NSNotes to add new Re1000 figs, outline, proposal intro (added HDG), and DPG_old bibliography (added HDG)

@@
 A more recent development in DG methods is the idea of \emph{hybridized} DG (HDG), introduced by Gopalakrishnan and Lazarov \cite{hybridDG}.
-The hybridized DG framework addresses several criticisms of common DG methods (globally coupled degrees of freedom, complicated/inefficient implementation procedures, suboptimal convergence of approximate fluxes) by identifying degrees of freedom with support only on element edges.
-Neighboring elements are coupled together only through these degrees of freedom, which can be interpreted as Lagrange multipliers enforcing weak continuity of the trial space.
-Additionally, HDG methods \todo{add bit about numerical fluxes still used, stabilization params}
+The hybridized DG framework addresses several criticisms of common DG methods (globally coupled degrees of freedom, complicated/inefficient implementation procedures, suboptimal convergence of approximate fluxes) by identifying degrees of freedom with support only on element edges, which can be interpreted as Lagrange multipliers enforcing weak continuity of the trial space.
+
+HDG methods treat numerical \emph{traces} and numerical \emph{fluxes} differently depending on the form of the boundary term resulting from integration by parts.
+The numerical trace (the result of integrating by parts the gradient) in HDG methods is chosen to be an unknown, while the numerical flux (the result of integrating by parts the divergence) is chosen to be an appropriate function of both function values on neighboring elements and the numerical trace.
+Note that HDG methods still fall under the category of stabilized methods --- stabilization techniques are employed through the choice of the HDG numerical flux, which involves some stabilization parameter $\tau$.
+
+By a careful choice of the numerical flux, the global HDG formulation can be reduced to a single equation involving only the numerical trace degrees of freedom, referred to as the \emph{global} problem.
+Once the global problem is solved, interior degrees of freedom can be recovered in parallel through so-called \emph{local} problems \cite{HDGprojection}.
 
@@
 
-This proposal will
+This PhD thesis proposal will proceed in four main parts:
 \begin{enumerate}
-\item Introduce DPG
-\item Cover the problem of robustness for model problems
-\item Extend results/formulations to nonlinear problems
-\item Discuss proposed work
+\item Introduce the abstract DPG method as a minimum residual method for linear problems.
+\item Formulate a DPG method addressing the issue of robustness for the model problem of convection-dominated diffusion.
+\item Apply the DPG method to singularly perturbed nonlinear problems in CFD, discussing preliminary results for the Burgers and compressible Navier-Stokes equations. 
+\item Introduce completed and proposed work in concentration areas A, B, and C. 
 \end{enumerate}

### 2012-06-19 docs/Jesse/Proposal/DPGtheory.tex
adding more additions (NL DPG) to proposal
committing changes to proposal tex/bib files

@@
-The Discontinuous Petrov-Galerkin (DPG) method of Demkowicz and Gopalakrishnan was first formulated in \cite{DPG1} for the pure convection problem.
+The Discontinuous Petrov-Galerkin (DPG) method of Demkowicz and Gopalakrishnan was first formulated in \cite{DPG1} as a scheme for the pure convection problem.
+The method demonstrated promise --- in particular, the method was able to achieve optimal convergence rates for the Peterson problem where standard DG methods were suboptimal.
+A breakthrough came in \cite{DPG2}, where the concept of locally-computable optimal test functions led to the development of the DPG method in its current form.
+Soon after, the DPG method was successfully applied to solve the convection-diffusion problem in the small-diffusion limit with $\epsilon = 1e-7$ \cite{DPG2,DPG3}.
 
@@
 The method was then extended to other problems, including convection-diffusion, in \cite{BottassoMichelettiSacco05,CausinSacco05,CausinSaccoBottasso05}.
+The key point in the method of Bottasso et al.\ was their method of hybridization of fluxes.
+Whereas HDG methods identify an additional flux unknown on the boundary, the numerical flux coupling neighboring elements together is still typically computed in part by using contributions from interior degrees of freedom on neighboring elements.
+In the DPG formulation, all numerical fluxes are declared to be independent unknowns, leaving the interior field degrees of freedom completely uncoupled from element to element.
+This formulation is often referred to as the \emph{ultra-weak} variational formulation.
 
-The key point in the method of Bottasso et al.\ was their method of hybridization of fluxes.
-Whereas HDG methods will identify an additional flux unknown on the boundary, the numerical flux coupling neighboring elements together is still typically computed in part using contributions from the field variables.
-In the DPG formulation, all numerical fluxes are declared to be independent unknowns, leaving the interior field degrees of freedom completely uncoupled from element to element.
-\todo{Finish, check if this is true.}
+Since its inception, the DPG method has been applied to a wide range of problems with great success, including elasticity \cite{DPGElasLocking}, thin body shell problems \cite{DPGElas}, the cloacking problem in electromagnetics \cite{DPGcloak}, both Helmholtz and elastic wave propagation problems \cite{DPG4}, and recently, the linear Stokes equation \cite{stokesDPG}.
+DPG has also been shown to be a generalization of several successful finite element methods --- comparisons between DPG and standard DG methods can be found in \cite{DPG1}, and more recently, several existing DG methods have been shown to be derivable using the DPG framework \cite{Bui-ThanhDemkowiczGhattas11a,DGDPG}.
 
-The breakthrough came in \cite{DPG2}, where the concept of locally-computable optimal test functions led to the development of the DPG method in its current form.
+Detailed analysis of the energy setting and well-posedness of DPG has been done for the Poisson and convection-diffusion equations in \cite{analysisDPG}.
+The well-posedness of DPG has also recently been extended to the large class of Friedrichs systems in \cite{Bui-ThanhDemkowiczGhattas11b}.
+Significant efforts have also been made in demonstrating the robustness of the DPG method for singular perturbation problems, both in wave propagation \cite{DPG4,DPGwave} and convection-diffusion problems \cite{DPGrobustness, DPGrobustness2}.
 
-\todo{Clean up}
-This DPG method with optimal test functions is better understood in \cite{DPG3,DPG4}, extended to problems in \cite{DPGElas,stokesDPG}, well-posedness theory developed for Poisson and convection-diffusion in \cite{analysisDPG}, extended to large class of Friedrichs systems in \cite{Bui-ThanhDemkowiczGhattas11b}.
-\cite{practicalDPG}.
-
-Optimal order comparison to DG in \cite{DPG1}. Comparisons to other DG methods in \cite{Bui-ThanhDemkowiczGhattas11a,DGDPG}.
-
-\section{Optimal Petrov-Galerkin methods}
+\subsection{Optimal Petrov-Galerkin methods}
 
@@
 
-\section{Ultra-weak variational formulation}
+\subsection{Ultra-weak variational formulation}
 \seclab{abstractUweak}
@@
 
-\section{Choices of test and trial norms}
+\subsection{Choices of test and trial norms}
 \seclab{energyPair}
@@
 
-Unfortunately, the optimal test norm is non-localizable due to the presence of the jump term $\jump{v}$.\footnote{A localizable norm $\nor{v}_{V(\Oh)}$ can be written in the form $\nor{v}_{V(\Oh)} = \sum_{K\in\Oh} \nor{v}_{V(K)},$ where $\nor{v}_{V(K)}$ is a norm over the element $K$.} Since the jump terms couple elements together, the evaluation of the jump terms requires contributions from all the elements in the mesh.
+Unfortunately, the optimal test norm is non-localizable due to the presence of the jump term $\jump{v}$.\footnote{A localizable norm can be written as $\nor{v}_{V(\Oh)} = \sum_{K\in\Oh} \nor{v}_{V(K)},$ where $\nor{v}_{V(K)}$ is a norm over $K$.} Since the jump terms couple elements together, the evaluation of the jump terms requires contributions from all the elements in the mesh.
 Consequently, solving for an optimal test function

### 2012-06-19 docs/Jesse/Proposal/NSNotes.tex
committing changes to proposal tex/bib files

@@
 
-Following Demkowicz and Oden \cite{Demkowicz:1990:NFE:112271.112276}, we consider the compressible Navier-Stokes equations
-\[
-\sum^2_{i=1} F_i\left( U\right)_{,i}=\sum^2_{i=1} G_i\left( U\right)_{,i}
-\]
-where the Eulerian fluxes are given as
-\[
-F_1 = \vectfour{\rho u_1}{\rho u_1^2+p}{\rho u_1 u_2}{((\rho e)+p)u_1}, \qquad F_2 = \vectfour{\rho u_2}{\rho u_1 u_2}{\rho u_2^2+p}{((\rho e)+p)u_2},
-\]
-and the viscous fluxes are given as
-\[
-G_i = \vectfour{0}{\sigma_{i1}}{\sigma_{i2}}{\sum_{j=1}^2\sigma_{ij}u_j + q_i}.
-\]
-We have also the constitutive relations 
+We briefly review the compressible Navier-Stokes equations, given in Section~\secref{sec:compNS}, and formulate DPG for the nonlinear system. 
+\begin{itemize}
+\item \textbf{Conservation equations}
 \begin{align*}
-\sigma_{ij} &= \mu(u_{i,j}+u_{j,i}) + \lambda u_{k,k}\delta_{ij}\\
-q_i &= \kappa T_{,i}\\
-p &= (\gamma-1)\rho\iota\\
-\iota &= e-\frac{1}{2}(u_1^2+u_2^2)\\
-\iota &= c_vT
+\div \vecttwo{\rho u_1 }{\rho u_2} &= 0\\
+\div \vecttwo{\rho u_1^2+p }{\rho u_1 u_2} &= \div\left(\vec{\sigma_{i1}}\right)\\
+\div \vecttwo{\rho u_1 u_2}{\rho u_2^2+p } &= \div\left(\vec{\sigma_{i2}}\right)\\
+\div\vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2} &= \div\left[\boldsymbol\sigma U + \vec{q}\right],
 \end{align*}
-where $e$ and $\iota$ are energy and internal energy per unit mass, respectively. We write the Navier Stokes equations as a system of seven first order equations. Let $[u_1,u_2] = [u,v]$.
-
-\begin{itemize}
-\item \textbf{Mass equation}
-\[
-\div \vecttwo{\rho u }{\rho v} = 0
-\]
-\item \textbf{Momentum equations}
-\begin{align*}
-\div \vecttwo{\rho u^2+p }{\rho u v} &= \div\left(\vec{\sigma_{i1}}\right)\\
-\div \vecttwo{\rho u v}{\rho v^2+p } &= \div\left(\vec{\sigma_{i2}}\right)
-\end{align*}
-
-\item \textbf{Energy equation}
-
-Let $\boldsymbol \sigma$ be a tensor whose $ij$th term is $\sigma_{ij}$.  
-\[
-\div\vecttwo{((\rho e)+p)u}{((\rho e)+p)v} = \div\left[\boldsymbol\sigma U + \vec{q}\right]
-\]
+where $\boldsymbol \sigma$ is the stress tensor whose $ij$th term is $\sigma_{ij}$.
 
@@
 We can invert the stress tensor under isotropic and plane strain assumptions to get
-%\[
-%\epsilon_{ij} = \frac{1}{2\mu} \sigma_{ij} - \frac{\lambda}{4\mu (\mu + \lambda)} \sigma_{kk}\delta_{ij}
-%\] 
-%which translates to
 \[
@@
 
-In general, $\mu$ and $\lambda$ are functions of temperature, obeying the power law
-\[
-\mu = \left(\frac{T}{T_0}\right)^\beta,
-\]
-where $T_0$ is a reference temperature. We choose $\beta = 2/3$ in this case.
-
 \item \textbf{Fourier's heat conduction law}
@@
 \end{align*}
-where $\kappa$ is generally a function of temperature. We introduce here the Prandtl number here as well
+%where $\kappa$ is generally a function of temperature. 
+We introduce here the Prandtl number here as well
 \[
@@
 \[
-\boldsymbol x^* = \frac{\boldsymbol x}{L}, \qquad \rho^* = \frac{\rho}{\rho_{\infty}}, \qquad \boldsymbol u^* = \frac{\boldsymbol u}{V_\infty}, \qquad T^* = \frac{T}{T_\infty}, \qquad \mu^* = \frac{\mu}{\mu_\infty}
+\boldsymbol x^* = \frac{\boldsymbol x}{L}, \qquad \rho^* = \frac{\rho}{\rho_{\infty}}, \qquad u_1^* = \frac{u_1}{V_\infty}, \qquad u_2^* = \frac{u_2}{V_\infty}, \qquad T^* = \frac{T}{T_\infty}, \qquad \mu^* = \frac{\mu}{\mu_\infty}
 \]
-Momentum, pressure, internal energy, and bulk viscosity are then nondimensionalized with respect to the above variables
+Pressure, internal energy, and bulk viscosity are then nondimensionalized with respect to the above variables
 \[
-\boldsymbol m^* = \frac{\boldsymbol m}{\rho_\infty V_\infty}, \qquad p^* = \frac{p}{\rho_\infty V_\infty^2}, \qquad \iota^* = \frac{\iota}{V_\infty^2}, \qquad \lambda^* = \frac{\lambda}{\mu_\infty}
+p^* = \frac{p}{\rho_\infty V_\infty^2}, \qquad \iota^* = \frac{\iota}{V_\infty^2}, \qquad \lambda^* = \frac{\lambda}{\mu_\infty}
 \]
@@
 \div \left(\vecttwo{\rho u v}{\rho v^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
-\div \left(\vecttwo{((\rho e)+p)u}{((\rho e)+p)v} - \boldsymbol \sigma_1 \cdot \boldsymbol u- \boldsymbol \sigma_2 \cdot \boldsymbol u + \vec{q}\right) &=0\\
+\div \left(\vecttwo{((\rho e)+p)u}{((\rho e)+p)v} - \boldsymbol \sigma_1 \cdot \boldsymbol u- \boldsymbol \sigma_2 \cdot \boldsymbol u + \vec{q}\right) &=0
 \end{align*}
@@
 
-\subsection{Numerical experiments}
+\subsection{Numerical experiments: Carter flat plate}
 
-For our solver, we use a standard pseudo-time solver and a standard greedy refinement scheme.
-Though we have not yet implemented adaptive timestepping, we are able to take large enough uniform timesteps over a coarse mesh such that convergence is comparable to the convergence of a damped Newton method.
+For our solver, we use a standard pseudo-time solver and greedy refinement scheme.
+Though we have not yet implemented adaptive timestepping, we are able to take large enough uniform timesteps over a coarse mesh such that convergence is order-of-magnitude comparable to the convergence of a damped Newton method.
 
@@
 \begin{itemize}
-\item{DPG parameters:} Both $p$ and $\Delta p = 2$ uniformly across the mesh. 
+\item{DPG parameters:} $p = 2$ or $p=3$, and $\Delta p = 2$ uniformly across the mesh. 
 \item{Adaptivity parameters:} Energy threshold for refinements is $\alpha = .2$ or $\alpha = .15$. 
@@
 
-\subsubsection{Carter flat plate}
-
-Our first problem of interest is the Carter flat plate problem. An infinitesmally thin flat plate disrupts a free stream flow and causes a shock to form at the tip of the plate.
+Our problem of interest is the Carter flat plate problem. An infinitesmally thin flat plate disrupts a free stream flow and causes a shock to form at the tip of the plate.
 
@@
 \centering
-\subfigure[$\rho$]{\includegraphics[scale=.42]{figs/rho.pdf}}
-\subfigure[$u_1$]{\includegraphics[scale=.42]{figs/u1.pdf}}
-\subfigure[$u_2$]{\includegraphics[scale=.42]{figs/u2.pdf}}
-\subfigure[$T$]{\includegraphics[scale=.42]{figs/T.pdf}}
-\caption{Solutions after six refinements for $\Reyn = 1000$.}
+\subfigure[$\rho$]{\includegraphics[scale=.42]{figs/Re1000p2/rho.pdf}}
+\subfigure[$u_1$]{\includegraphics[scale=.42]{figs/Re1000p2/u1.pdf}}
+\subfigure[$u_2$]{\includegraphics[scale=.42]{figs/Re1000p2/u2.pdf}}
+\subfigure[$T$]{\includegraphics[scale=.42]{figs/Re1000p2/T.pdf}}
+\caption{Solutions after six refinements for $p=2$ and $\Reyn = 1000$.}
 \label{fig:Re500}
@@
 \centering
-\subfigure[$\rho$]{\includegraphics[scale=.4]{figs/rhozoom.pdf}}
-\subfigure[$u_1$]{\includegraphics[scale=.4]{figs/u1zoom.pdf}}
-\subfigure[$u_2$]{\includegraphics[scale=.4]{figs/u2zoom.pdf}}
-\subfigure[$T$]{\includegraphics[scale=.4]{figs/Tzoom.pdf}}
-\caption{Zoom of solutions at the beginning of the plate for $\Reyn = 1000$.}
+\subfigure[$\rho$]{\includegraphics[scale=.4]{figs/Re1000p2/rhozoom.pdf}}
+\subfigure[$u_1$]{\includegraphics[scale=.4]{figs/Re1000p2/u1zoom.pdf}}
+\subfigure[$u_2$]{\includegraphics[scale=.4]{figs/Re1000p2/u2zoom.pdf}}
+\subfigure[$T$]{\includegraphics[scale=.4]{figs/Re1000p2/Tzoom.pdf}}
+\caption{Zoom of solutions at the beginning of the plate for $p=2$ and $\Reyn = 1000$.}
 \label{fig:Re500}
@@
 
+For $p=2$, after six refinements, the mesh contained 1410 elements and 187605 global dofs, with a total DPG energy error of $5.684e-7$.
+Comparatively, for $p=3$, the mesh contained only 444 elements and 97403 global dofs, with a total DPG eneryg error of 4.57681e-7 after five refinements.
+
 \begin{figure}[!h]
 \centering
-\includegraphics[scale=.75]{figs/mesh.pdf}
-\caption{Adaptive mesh after six refinements for $\Reyn = 1000$.}
+\subfigure[$p=2$]{\includegraphics[scale=.5]{figs/Re1000p2/mesh.pdf}}
+\subfigure[$p=3$]{\includegraphics[scale=.5]{figs/Re1000p3/mesh.pdf}}
+\caption{Adaptive mesh after six refinements for $p=2$ and five refinements for $p=3$ with $\Reyn = 1000$.}
 \label{fig:MeshRe500}

### 2012-06-19 docs/Jesse/Proposal/NonlinDPG.tex
committing changes to proposal tex/bib files

@@
 In practice, most compressible flow solvers opt for the pseudo-time step method over the direct Newton iteration due to the difficulty of convergence and sensitivity of the Newton iteration to initial guess\cite{libMeshPaper}.
-Though the convergence of the pseudo-time step is slower, the addition of the zero-order transient terms ``regularizes" the problem, making it easier to solve.\footnote{The addition of a zero-order term ``regularizes" an equation by adding to it a positive-definite $L^2$ projection operator.
+Though the convergence of the pseudo-time step is slower, the addition of the zero-order transient terms ``regularizes" the problem and makes it less difficult to solve.\footnote{The addition of a zero-order term ``regularizes" an equation by adding to it a positive-definite $L^2$ projection operator.
 In the limit as $\Delta t\rightarrow 0$, the solution at $t_i$ will simply return the $L^2$ projection of the solution at the previous timestep.}
@@
 
-\todo{Add adjoint trick stuff}
+A recent theoretical development is the formulation of a DPG method that aims to minimize a nonlinear residual.
+Given two Hilbert spaces --- a trial space $U$ and test space $V$ --- our nonlinear variational formulation can be written as $b(u,v) = l(v)$, with the corresponding operator form of the formulation in $V'$
+\[
+B(u) = l.
+\]
+We can apply the steps used to derive the DPG method for linear problems to the nonlinear setting as well.
+Given a finite dimensional subspace $U_h \subset U$, we consider the discrete nonlinear residual
+\[
+J(u_h) \coloneqq \frac{1}{2}\nor{R_V^{-1}\left(B(u_h)-l\right)}_V^2.
+\]
+Our goal is to solve
+\[
+u_h = \arg \min_{w_h\in U_h}J(w_h).
+\]
+Similarly to the linear case, we can take the Gate\'aux derivative to arrive at a necessary condition for $u_h$ to minimize $J(u_h)$ 
+\begin{align*}
+\LRa{J'(u_h), \delta u_h} &= \LRp{R_V^{-1}\left(B(u_h)-l\right),R_V^{-1}B'(u_h;\delta u_h)}_V, \quad \delta u_h \in U_h. 
+\end{align*}
+As the above is a nonlinear equation, we seek its solution through linearization. Differentiating a second time in $u$, we arrive at
+\begin{align*}
+\LRa{J''(u_h), \Delta u_h} =& \LRa{B'(u_h;\Delta u_h), B'(u_h;\delta u_h)}_V \\
+& + \LRa{\left(B(u_h)-l\right),B''(u_h;\delta u_h,\Delta u_h)}_V \\
+=& \LRp{R_V^{-1}B'(u_h;\Delta u_h), R_V^{-1}B'(u_h;\delta u_h)}_V \\
+& + \LRp{R_V^{-1}\left(B(u_h)-l\right),R_V^{-1}B''(u_h;\delta u_h,\Delta u_h)}_V 
+\end{align*}
+where $B''(u_h;\delta u_h,\Delta u_h)$ denotes the Hessian of $B(u_h)$, evaluated using both $\delta u_h$ and $\Delta u_h$.
+
+Examining the above formulation, we note that DPG as applied to the linearized problem produces the term $ \LRp{R_V^{-1}B'(u_h;\Delta u_h), R_V^{-1}B'(u_h;\delta u_h)}_V$.
+However, in approaching the nonlinear problem through the minimization of the discrete residual, we gain a second-order term involving the Hessian
+\[
+\LRp{R_V^{-1}\left(B(u_h)-l\right),R_V^{-1}B''(u_h;\delta u_h,\Delta u_h)}_V.
+\] 
+The evaluation of this term can be done in a computationally efficient manner --- if we define the image of the nonlinear residual under the Riesz inverse
+\[
+v_{R(u)} = R_V^{-1}\left(B(u_h)-l\right),
+\]
+then we can compute this additional term through
+\begin{align*}
+\LRp{v_{R(u)},R_V^{-1}B''(u_h;\delta u_h,\Delta u_h)}_V &= \LRa{v_{R(u)},B''(u_h;\delta u_h,\Delta u_h)}_V
+\end{align*}
+which can be computed in the same fashion as a Bubnov-Galerkin stiffness matrix. This addition, though not positive definite, is symmetric due to the nature of second order Ga\^teux derivatives.
+
+We note that we have not implemented this Hessian-based nonlinear solver in the numerical experiments to follow, and instead plan to do so in the proposed work outlined in Section~\secref{sec:proposedWork}.

### 2012-06-19 docs/Jesse/Proposal/areaReq.tex
committing changes to proposal tex/bib files

@@
 \section{Area requirements}
+\seclab{sec:proposedWork}
 
@@
 \begin{itemize}
-\item{\textbf{Completed: }} Prove robustness of DPG method for the scalar convection-diffusion problem
-\item Attempt analysis of the linearized Navier-Stokes system
+\item{\textbf{Completed: Prove robustness of DPG method for the scalar convection-diffusion problem.}}
+
+Analysis has been done in \cite{DPGrobustness2}, extending the results of \cite{DPGrobustness}.
+In particular, we have introduced a test norm under which the DPG method robustly bounds the $L^2$ error in the field variables $u$ and the scaled stress $\sigma$.
+Numerical results confirm the theoretical bounds given.
+
+\item{\textbf{Proposed: Attempt analysis of the linearized Navier-Stokes system.}}
+
+We hope to analyze the linearized Navier-Stokes equations to determine an optimal extrapolation of the test norm for the scalar convection-diffusion problem to systems.
+
 \end{itemize}
@@
 \begin{itemize}
-\item{\textbf{Completed: }} Collaborative work with Nathan Roberts on the higher order parallel adaptive DPG code Camellia.
-\item Nonlinear DPG - Hessian adjoint trick
-\item Adaptivity: anisotropic refinements and $hp$-schemes.
-\item Distributed static condensation
+\item{\textbf{Completed: Collaborative work with Nathan Roberts on the higher order parallel adaptive DPG code Camellia.}}
+
+Most numerical experiments have been done using the higher-order adaptive codebase Camellia, built upon the Trilinos library and designed by Nathan Roberts.
+The library allows for rapid implementation of problems through a symbolic syntax similar to the Fenics project.
+Work has been done to support arbitrary-irregularity refinements in both $h$ and $p$, and the framework for anisotropic refinements is in place as well.
+Similarly, the code is partially parallelized - the determination of the stiffness matrix is perfectly scalable, and we are currently exploring options for more scalable solvers.
+
+\item{\textbf{Proposed: Distributed iterative static condensation.}}
+
+A clear choice for a parallelized solver under the ultra-weak variational formulation is static condensation/the Schur-complement method.
+Given a block matrix structure of a stiffness matrix $K$, we can view the DPG system as
+\[
+Ku = \arr{A}{B}{B^T}{D}\vecttwo{u_{\rm flux}}{u_{\rm field}} = \vecttwo{f}{g} = l
+\]
+where $D$ has a block-diagonal structure, and $A$ and $D$ are both square matrices with $\dim{A} < \dim{D}$. The system can be reduced to yield the condensed system
+\[
+\left(A-B D^{-1} B^T\right)u_{\rm flux} = f - B D^{-1} g
+\]
+where $D^{-1}$ can be inverted block-wise. Once the globally coupled flux degrees of freedom are solved for, the field degrees of freedom can be reconstructed locally.
+
+Additionally, though the Schur complement $A-B D^{-1} B^T$ is generally a dense matrix, it does not have to be explicitly formed, and we can use a matrix-free method to solve the above condensed system.
+The question remains on whether or not the condensed DPG stiffness matrix is well-conditioned.
+It has been shown that, unlike standard least-squares methods, DPG generates for the Poisson matrix a stiffness matrix with condition number $O(h^{-2})$ \cite{practicalDPG}.
+It is well known that, under standard finite element methods, if the condition number of the global stiffness matrix $K$ is $O(h^{-2})$, the condition number of the Schur complement is $O(h^{-1})$.
+Additionally, through either diagonal preconditioning or matrix equilibration, the condition number of the Schur complement can often be made significantly smaller than $O(h^{-1})$.
+
+We hope to implement such a distributed solver and determine the scalability of this solver under DPG.
+
+\item{\textbf{Proposed: a Nonlinear Hessian-based DPG method.}}
+
+We hope to implement the Hessian-based nonlinear DPG approach to the viscous Burgers and compressible Navier-Stokes problems and compare convergence and error rates for each problem after applying this nonlinear strategy.
+
+\item{\textbf{Proposed: Anisotropic refinements and $hp$-schemes.}}
+
+The effectiveness and necessity of anisotropic refinement schemes for problems in CFD has been demonstrated several times in the literature \cite{anisotropy1,anisotropy2}.
+As the error representation function has been shown to yield an effective and natural vector-valued residual with which to drive refinement, we hope to generalize the use of the error representation function to yield anisotropic adaptive schemes.
+Additionally, we hope to explore the possibility of inferring an optimal choice between $h$ and $p$ refinement using the error representation function.
+%\cite{BoeingHigherOrder}.
+
 \end{itemize}
@@
 \begin{itemize}
-\item{\textbf{Completed: }} Convection-dominated diffusion, Burgers, and Navier-Stokes. 
-\item Higher Reynolds number, ramp problem, Gaussian bump, airfoil.
-\item Euler with NS regularization?
+\item{\textbf{Completed: convection-dominated diffusion, Burgers, and a model problem for Navier-Stokes.}} 
+\item{\textbf{Proposed: Higher Reynolds number, ramp problem, Gaussian bump, airfoil.}}
+\item{\textbf{Proposed: regularized Euler.}}
 \end{itemize}

### 2012-06-19 docs/Jesse/Proposal/problemRange.tex
committing changes to proposal tex/bib files

\begin{figure}[!h]
\centering
\includegraphics[scale=.45]{figs/CFD_tree.pdf}
\caption{A diagram of common CFD problems and their simplifying assumptions.}
\end{figure}

\section{The compressible Navier-Stokes equations}
\seclab{sec:compNS}

We consider the transient compressible Navier-Stokes equations. For simplicity, we present them in two spatial dimensions. Each equation of the Navier-Stokes system represents the conservation of some physical quantity in the behavior of a fluid inside a general control volume.\footnote{The derivation of the compressible Navier-Stokes equations is a standard result of the Reynolds transport theorem, and can be found in many elementary fluid dynamics books.}

\begin{itemize}
\item{\textbf{Mass conservation}}
\begin{align*}
\pd{\rho}{t} + \div \vecttwo{\rho u }{\rho v} &= 0
\end{align*}

\item{\textbf{Momentum conservation}}
\begin{align*}
\pd{\rho u_1}{t} + \div \left(\vecttwo{\rho u^2+p }{\rho u v} - \boldsymbol \sigma_{1}\right) &=0\\
\pd{\rho u_2}{t} + \div \left(\vecttwo{\rho u v}{\rho v^2+p } - \boldsymbol \sigma_{2}\right) &=0
\end{align*}

\item{\textbf{Energy conservation}}
\begin{align*}
\pd{\rho e}{t} + \div \left(\vecttwo{((\rho e)+p)u}{((\rho e)+p)v} - \boldsymbol \sigma_1 \cdot \boldsymbol u- \boldsymbol \sigma_2 \cdot \boldsymbol u + \vec{q}\right) &=0
\end{align*}
\end{itemize}

We assume our fluid satisfies standard stress laws for $\boldsymbol \sigma$ and $\boldsymbol q$ as well. For viscous stresses $\boldsymbol \sigma$, we assume a Newtonian fluid
\begin{align*}
\sigma_{ij} &= \mu(u_{i,j}+u_{j,i}) + \lambda u_{k,k}\delta_{ij}.
\end{align*}
The coefficients $\lambda$ and $\mu$ are known as the viscosity and bulk viscosity, respectively. The bulk viscosity is often set implicitly through $2\mu + 3\lambda = 0$, known as Stokes' hypothesis. However, since the effect of bulk viscosity can become important for compressible flows, we treat both coefficients separately. In general, $\mu$ and $\lambda$ are functions of temperature, obeying the power law
\[
\mu = \left(\frac{T}{T_0}\right)^\beta,
\]
where $T_0$ is a reference temperature. We choose $\beta = 2/3$ in this case.

We assume our fluid satisfies Fourier's law, which relates the heat flux $\boldsymbol q$ to the gradient of the temperature through
\begin{align*}
{\boldsymbol q} &= \kappa \grad T,
\end{align*}
where $\kappa$ is generally a function of temperature.

Finally, we assume our fluid is a thermally and calorically perfect ideal gas. Let $c_p$ and $c_v$ be the specific heats at constant pressure and volume, respectively. Then,
\begin{align*}
p &= (\gamma-1)\rho\iota\\
\iota &= e-\frac{1}{2}(u_1^2+u_2^2)\\
\iota &= c_vT
\end{align*}
where $e$ and $\iota$ are energy and internal energy per unit mass, respectively.

\todo{write blurb on how comp NS is used - small Re limit}
\todo{write blurb on turbulence}

\subsection{Incompressibility}

\todo{reference Stokes, cite Nate}
\cite{stokesDPG}

\subsection{The linearized Navier-Stokes equations}

The linearized Navier-Stokes equations are the result of small perturbation assumptions applied to the full Navier-Stokes equations. Under such assumptions, the flow is largely uniform, with slight variations that are small compared to the uniform stream velocity. We are interested in the linearized Navier-Stokes equations mainly for mathematical purposes;

\section{The scalar convection-diffusion equation}

The scalar convection-diffusion problem is the prototypical model problem for solving the full Navier-Stokes equations; most stabilized methods consider first the scalar convection-diffusion equation as a test case before attempting a solution of the full Navier-Stokes equations. As discussed previously, an important feature of the convection-diffusion equation is that solutions can develop  boundary layers, a physical feature found in most applications of interest for compressible flow.

\todo{add perspective on convection-diffusion}

\subsection{Burgers' equation}

The Burgers' equation is physically derived from the incompressible Navier-Stokes equations under the assumption that $\grad p \approx 0$, or that the pressure field is near constant. A feature of the Burgers' equation not present in convection-diffusion is that, due to the presence of the nonlinear term, it can develop shock discontinuities in its solutions in finite time.

The Burgers' equation has also been used to study the phenomenon of turbulence; however, the Burgers equation does not exhibit the chaotic nature and sensitivity to initial conditions that characterizes turbulence as observed in the full and incompressible Navier-Stokes equations. In the scope of this dissertation, Burgers shall be used as to test the extension of our numerical method to nonlinear problems.

\section{The inviscid case}

The Euler equations are a result of neglecting the viscous terms in the Navier-Stokes equations. Physically speaking, these assumptions correspond to the inviscid limit, as well as a particular class of boundary conditions (for example, the wall boundary condition $\boldsymbol u = 0$ does not hold in the inviscid limit).

\todo{express coupling - Drela's IBL work} \cite{BoeingDrela}
\todo{Express that mathematically, the Euler equations are difficult}

### 2012-06-19 docs/Jesse/Proposal/proposalIntro.tex
committing changes to proposal tex/bib files

@@
 Good resolution for such problems under uniform meshes is computationally prohibitive and impractical for most physical regimes of interest.
-However, the construction of ``good" meshes is a difficult task, usually requiring a-priori knowledge of the form of the solution.
+However, the construction of ``good" meshes is a difficult task, usually requiring a-priori knowledge of the form of the solution \cite{andersonCFDBook}.
 An alternative to such is the construction of automatically adaptive schemes; such methods usually begin with a coarse mesh and refine based on the minimization of some error.
@@
 As a consequence, the finite element solution can diverge significantly from the best finite element approximation of the solution for very small values of $\epsilon$.
-For example, Figure~\ref{fig:GalerkinOsc} shows an example of how, on a coarse mesh, and for small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation with a boundary layer develops spurious oscillations everywhere in the domain, even where the best approximation error is small.
+For exam ple, Figure~\ref{fig:GalerkinOsc} shows an example of how, on a coarse mesh, and for small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation with a boundary layer develops spurious oscillations everywhere in the domain, even where the best approximation error is small.
 These oscillations grow in magnitude as $\epsilon \rightarrow 0$, eventually polluting the entire solution.
@@
 An additional reason for the popularity of DG methods is that they can be interpreted as stabilized FE methods through appropriate choices of this numerical flux \cite{Brezzi20063293}.
-We will illustrate this with the pure convection equation in 1D ---
+We will illustrate this with the steady convection equation in 1D ---
 \begin{align*}
-\pd{\left(\beta u\right)}{x} &= f\\
-u(0) &= u_0.
+\pd{\left(\beta(x) u\right)}{x} = f, \quad u(0) &= u_0.
 \end{align*}
@@
 A more recent development in DG methods is the idea of \emph{hybridized} DG (HDG), introduced by Gopalakrishnan and Lazarov \cite{hybridDG}.
-The hybridized DG framework addresses several criticisms of common DG methods (globally coupled degrees of freedom, complicated/inefficient implementation procedures, suboptimal convergence of approximate fluxes) by identifying degrees of freedom with support only on element edges, which can be interpreted as Lagrange multipliers enforcing weak continuity of the trial space.
-
+The hybridized DG framework identifies degrees of freedom with support only on element edges, which can be interpreted as Lagrange multipliers enforcing weak continuity of the trial space.
 HDG methods treat numerical \emph{traces} and numerical \emph{fluxes} differently depending on the form of the boundary term resulting from integration by parts.
 The numerical trace (the result of integrating by parts the gradient) in HDG methods is chosen to be an unknown, while the numerical flux (the result of integrating by parts the divergence) is chosen to be an appropriate function of both function values on neighboring elements and the numerical trace.
-Note that HDG methods still fall under the category of stabilized methods --- stabilization techniques are employed through the choice of the HDG numerical flux, which involves some stabilization parameter $\tau$.
 
@@
 Once the global problem is solved, interior degrees of freedom can be recovered in parallel through so-called \emph{local} problems \cite{HDGprojection}.
+
+HDG methods are an active topic of current research, since they address several criticisms of common DG methods (large number of degrees of freedom, globally coupled degrees of freedom, complicated/inefficient implementation procedures, suboptimal convergence of approximate fluxes).
+Note that HDG methods still fall under the category of stabilized methods --- stabilization techniques are employed through the choice of the HDG numerical flux, which involves some stabilization parameter $\tau$.
 

### 2012-06-19 docs/Jesse/Proposal/DPGtheory.tex
fixing things in proposal

@@
 
-Since its inception, the DPG method has been applied to a wide range of problems with great success, including elasticity \cite{DPGElasLocking}, thin body shell problems \cite{DPGElas}, the cloacking problem in electromagnetics \cite{DPGcloak}, both Helmholtz and elastic wave propagation problems \cite{DPG4}, and recently, the linear Stokes equation \cite{stokesDPG}.
+Since its inception, the DPG method has been applied to a wide range of problems with great success, including elasticity \cite{DPGElasLocking}, thin body shell problems \cite{DPGElas}, the cloaking problem in electromagnetics \cite{DPGcloak}, both Helmholtz and elastic wave propagation problems \cite{DPG4}, and recently, the linear Stokes equation \cite{stokesDPG}.
 DPG has also been shown to be a generalization of several successful finite element methods --- comparisons between DPG and standard DG methods can be found in \cite{DPG1}, and more recently, several existing DG methods have been shown to be derivable using the DPG framework \cite{Bui-ThanhDemkowiczGhattas11a,DGDPG}.

### 2012-06-19 docs/Jesse/Proposal/areaReq.tex
fixing things in proposal

@@
 It is well known that, under standard finite element methods, if the condition number of the global stiffness matrix $K$ is $O(h^{-2})$, the condition number of the Schur complement is $O(h^{-1})$.
-Additionally, through either diagonal preconditioning or matrix equilibration, the condition number of the Schur complement can often be made significantly smaller than $O(h^{-1})$.
+Additionally, through either diagonal preconditioning or matrix equilibration, the condition number of the Schur complement can often be made significantly smaller than $O(h^{-1})$, and the positive-definiteness of the resulting system allows the use of fast iterative solvers in solving the condensed system.
 

### 2012-06-19 docs/Jesse/Proposal/abstract.tex
adding abstract

--- 2012-06-15 docs/Jesse/Proposal/outline.tex
@@
-\documentclass{report}
-
-\usepackage{utdiss2}  		% Dissertation package style file.
+\documentclass[12pt,letterpaper,oneside]{article}
+\usepackage{layout}
+\usepackage{fullpage}
 
@@
 \usepackage{pifont}
+\usepackage{geometry} 
+\geometry{letterpaper} 
+\usepackage{setspace}
 %\usepackage{fullpage}
@@
 
+\renewcommand{\arraystretch}{1.5}
+
 %%%%%%%%%%%%%%% End def of new commands %%%%%%%%%%%%%%%%%%%
 
-\author{Jesse Chan}
-\address{910 E. 32nd St, Apt.\ 101\\ Austin, Texas 78705}  % Required
+\author{Jesse Chan\\Committee: \vspace{-0.4cm}\\Dr. Leszek Demkowicz (co-supervisor), Dr. Robert Moser (co-supervisor),\vspace{-0.4cm}\\ Dr. Tom Hughes}
 
-\title{Proposal outline/notes for DPG and Compressible Navier-Stokes}
-
-\supervisor
-	[Leszek Demkowicz]
-	{Robert Moser}
-
-\committeemembers
-	[Thomas J. R. Hughes]
-	[Somebody]
-	[Somebody]
-	{Eh}
-
-\previousdegrees{B.A.}
-
-\oneandonehalfspacequote
-
-\topmargin 0.125in
-
-\makeindex
-
-%%%%%%%%%%%%%%% Start of thesis %%%%%%%%%%%%%%%%%%%
+\title{A DPG method for compressible flow problems}
 
 \begin{document}
-\copyrightpage          % Produces the copyright page.
-\commcertpage           % Produces the Committee Certification
-\titlepage
+\maketitle
 
-\begin{dedication}
-\index{Dedication@\emph{Dedication}}%
-Dedicated to \ldots
-\end{dedication}
+Over the last three decades, Computational Fluid Dynamics (CFD) simulations have become commonplace as a tool in the engineering and design of high-speed aircraft.
+Wind tunnel experiments are often complemented by computational simulations, and CFD technologies have proved very useful in both the reduction of aircraft development cycles, and in the simulation of conditions difficult to reproduce experimentally.
+Great advances have been made in the field since its introduction, especially in areas of meshing, computer architecture, and solution strategies.
+Despite this, there still exist many computational limitations in existing CFD methods; in particular, reliable higher order and $hp$-adaptive methods.
 
-\begin{acknowledgments}		% Optional
-\index{Acknowledgments@\emph{Acknowledgments}}%
-I wish to thank the multitudes of people who helped me. Time would
-fail me to tell of \ldots
-\end{acknowledgments}
+The use of adaptive meshes is crucial to many CFD applications, where the solution often exhibits very localized sharp gradients and shocks.
+Good resolution for such problems under uniform meshes is computationally prohibitive and impractical for most physical regimes of interest.
+However, the construction of ``good" meshes is a difficult task, usually requiring a-priori knowledge of the form of the solution.
+An alternative to such is the construction of automatically adaptive schemes; such methods begin with a coarse mesh and refine based on the minimization of error.
+However, this task is difficult, as the convergence of numerical methods for problems in CFD is notoriously sensitive to mesh quality.
+Additionally, the use of adaptivity becomes even more difficult in the context of higher order and $hp$ methods \cite{BoeingHigherOrder}.
 
-\utabstract
-\index{Abstract}%
-\indent
-This document has the form of a ``fake'' doctoral dissertation
-in order to provide an example of such, but it is actually a
-copy of Miguel Lerma's documentation for the Mathematics
-Department Computer Seminar of 25 March 1998 updated in July 2001
-and following by Craig McCluskey to meet the March 2001
-requirements of the Graduate School.
+Many of these issues are tied to the notion of \emph{robustness}, which we define loosely for CFD applications as the degradation of the quality of numerical solutions with respect to the Reynolds number, or nondimensional viscosity.
+For typical physical conditions of interest for the compressible Navier-Stokes equations, the Reynolds number is extremely high, on the order of 1e7, yielding solutions with two vastly different scales - inviscid phenomena at an $O(1)$ scale, and $O(1e-7)$ viscous phenomena.
 
-This document and its source file show to write a Doctoral Dissertation using 
-\LaTeX{} and the utdiss2 package.
+%From the perspective of the full Navier-Stokes equations, this loss of robustness is doubly problematic.
+Not only will any nonlinear solution suffer from similar non-physical oscillations, but nonlinear solvers themselves may fail to yield a solution due to such instabilities --- a nonlinear solution is almost always computed by solving a series of linear problems whose solutions will converge to the nonlinear solution under appropriate assumptions, and the presence of such oscillations in each linear problem can cause the solution convergence to slow significantly or even diverge.
 
-\tableofcontents   % Table of Contents will be automatically
-                   % generated and placed here.
+ The issue of robustness for finite element methods was addressed early on by Brooks and Hughes in the SUPG method \cite{SUPG}, which introduced the idea of residual-based stabilization methods.
+Such methods have been widely used in industry; however, these methods are often limited to low-order approximations.
+Additionally, such methods are usually formulated for model problems and then applied to the full Navier-Stokes equations, where the extrapolation step is fairly ad-hoc.
 
-%\listoftables      % List of Tables and List of Figures will be placed
-%\listoffigures     % here, if applicable.
+\todo{finish, add DPG reference}
+Demkowicz and Gopalakrishnan introduced the DPG method with optimal test functions, applying it very early on to the convection and convection-diffusion problems \cite{DPG1,DPG2,DPG3}.
+Since then, the DPG method has been applied to a wide range of problems with great success, including elasticity \cite{DPGElasLocking}, thin body shell problems \cite{DPGElas}, the cloaking problem in electromagnetics \cite{DPGcloak}, both Helmholtz and elastic wave propagation problems \cite{DPG4}, and recently, the linear Stokes equation \cite{stokesDPG}.
 
-\chapter{Introduction}
+\paragraph{Goal:} Our goal is to develop a DPG method and higher order adaptive scheme for the steady compressible laminar Navier-Stokes equations in transonic/supersonic regimes that is robust over a range of Reynolds numbers.
+In particular, we hope to present a method for which automatic $hp$-adaptivity can be applied to problems in compressible flow.
 
-\include{proposalIntro}
+\paragraph{Area A: Applicable Mathematics}
 
-\chapter{Discontinuous Petrov-Galerkin: a minimum residual method for linear problems}
+Analysis of convection-diffusion problem, development of a provably robust DPG method for the prototypical singular perturbation problem convection-diffusion.
 
-\include{DPGtheory}
+\paragraph{Area B: Numerical Analysis and Scientific Computation}
 
-\chapter{A robust DPG method for convection-diffusion}
+Parallel adaptive DPG code, Hessian-based nonlinear DPG, scalable parallel solvers.
 
-\begin{itemize}
-\item Describe mathematically the issue with standard Galerkin.
-\item Give proofs of robustness and numerical results (from paper)\cite{ChanHeuerBui-ThanhDemkowicz12}
-\end{itemize}
-\todo{Transition between paper and this bit}
-
-\include{DPGrobustness}
-
-\chapter{Proposed work}
-
-\include{NonlinDPG}
-\include{BurgersNotes}
-\include{NSNotes}
-\include{areaReq}
+\paragraph{Area C: Mathematical Modeling and Applications}
 
@@
 
-%\chapter{Appendix}
-\appendices
-\input{paper_appendix.tex}
-\input{hyperbolicDPG.tex}
-
 \end{document}

### 2012-06-20 docs/Jesse/Proposal/proposalIntro.tex
adding changes to proposal

@@
 
-\section{Range of CFD problems}
-
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.45]{figs/CFD_tree.pdf}
-\caption{A diagram of common CFD problems and their simplifying assumptions.}
-\end{figure}
-
-\begin{itemize}
-\item Discuss full compressible Navier-Stokes with boundary layers
-\item Discuss full compressible Navier-Stokes without boundary layers, connect to Euler (mention Dr Young and Boeing and the IBL connection \cite{BoeingDrela})
-\item Discuss model problems
-\end{itemize}
+%\section{Range of CFD problems}
+%
+%\begin{figure}[!h]
+%\centering
+%\includegraphics[scale=.45]{figs/CFD_tree.pdf}
+%\caption{A diagram of common CFD problems and their simplifying assumptions.}
+%\end{figure}
+%
+%\begin{itemize}
+%\item Discuss full compressible Navier-Stokes with boundary layers
+%\item Discuss full compressible Navier-Stokes without boundary layers, connect to Euler (mention Dr Young and Boeing and the IBL connection \cite{BoeingDrela})
+%\item Discuss model problems
+%\end{itemize}

### 2012-06-20 docs/Jesse/Proposal/DPGrobustness.tex

@@
+The majority of this chapter will focus on the convection-diffusion problem using the abstract theory that we have discussed in the previous chapter.
+In particular, we shall use the DPG method based on the ultra-weak formulation with optimal test functions to solve this model problem and analyze its behavior as $\epsilon\rightarrow 0$.
+Our goal is to show the robustness of the method with respect to $\epsilon$, and demonstrate its usefulness as a numerical method for solving singular-perturbed problems.
+
 \section{DPG formulation for convection-diffusion}
@@
 \seclab{sec:modelSec}
-The remainder of this chapter focuses on the convection-diffusion problem using the abstract theory that we
-have discussed so far.
-In particular, we shall use the DPG method based on the ultra-weak formulation with optimal test functions to solve this model problem and analyze its behavior with respect to $\epsilon$.
-Our goal is to show the robustness of the method with respect to $\epsilon$, and demonstrate its usefulness as  a numerical approach to solving singular-perturbed problems.
 
@@
 
-\section{Numerical experiments}
+\section{Numerical experiments: Eriksson-Johnson problem}
 \label{sec:num_exp}
@@
 The effects of roundoff error were successfully treated in \cite{DPG3} by dynamically rescaling the test norms based on element size, a practical remedy not covered yet by the present analysis.
-
-\subsection{Eriksson-Johnson model problem}
 
@@
 
-\subsubsection{Solution with $C_1 = 1, C_{n\neq 1} = 0$}
+\subsection{Solution with $C_1 = 1, C_{n\neq 1} = 0$}
 
@@
 
-\subsubsection{Neglecting $\sigma_n$}
+\subsection{Neglecting $\sigma_n$}
 
@@
 
-\subsubsection{Discontinuous inflow data}
+\subsection{Discontinuous inflow data}
 

### 2012-06-20 docs/Jesse/Proposal/DPGtheory.tex

@@
 On the theoretical side, the quasi-optimal test norm has been shown to yield a well-posed DPG methodology for the Poisson and convection-diffusion equations \cite{analysisDPG}.
-More recently, this theory has been generalized to show the well-posedness of DPG for the large class of PDEs of Friedrichs' type \cite{Bui-ThanhDemkowiczGhattas11b}.
+More recently, this theory has been generalized to show the well-posedness of DPG under the quasi-optimal test norm for the large class of Friedrichs' type PDEs \cite{Bui-ThanhDemkowiczGhattas11b}.

### 2012-06-20 docs/Jesse/Proposal/NSNotes.tex

@@
 
-For $p=2$, after six refinements, the mesh contained 1410 elements and 187605 global dofs, with a total DPG energy error of $5.684e-7$.
-Comparatively, for $p=3$, the mesh contained only 444 elements and 97403 global dofs, with a total DPG eneryg error of 4.57681e-7 after five refinements.
+For $p=2$, after six refinements, the mesh contained 1410 elements and 187605 global dofs, with a total DPG energy error of $.000753$.
+Comparatively, for $p=3$, the mesh contained only 444 elements and 97403 global dofs, with a total DPG eneryg error of $0.000676$ after five refinements.
 

### 2012-06-20 docs/Jesse/Proposal/abstract.tex

--- 2012-06-15 docs/Jesse/Proposal/outline.tex
@@
 
+\renewcommand{\arraystretch}{1.5}
+
 %%%%%%%%%%%%%%% End def of new commands %%%%%%%%%%%%%%%%%%%
 
-\author{Jesse Chan}
-\address{910 E. 32nd St, Apt.\ 101\\ Austin, Texas 78705}  % Required
+\author{Jesse Chan\\Committee: \vspace{-0.3cm}\\Dr. Leszek Demkowicz (co-supervisor), Dr. Robert Moser (co-supervisor),\vspace{-0.3cm}\\ Dr. Tom Hughes, Committee Member 2, Committee Member 3}
 
-\title{Proposal outline/notes for DPG and Compressible Navier-Stokes}
-
-\supervisor
-	[Leszek Demkowicz]
-	{Robert Moser}
-
-\committeemembers
-	[Thomas J. R. Hughes]
-	[Somebody]
-	[Somebody]
-	{Eh}
-
-\previousdegrees{B.A.}
-
-\oneandonehalfspacequote
-
-\topmargin 0.125in
-
-\makeindex
-
-%%%%%%%%%%%%%%% Start of thesis %%%%%%%%%%%%%%%%%%%
+\title{A DPG method for compressible flow problems}
 
 \begin{document}
-\copyrightpage          % Produces the copyright page.
-\commcertpage           % Produces the Committee Certification
-\titlepage
+\maketitle
 
-\begin{dedication}
-\index{Dedication@\emph{Dedication}}%
-Dedicated to \ldots
-\end{dedication}
+Over the last three decades, Computational Fluid Dynamics (CFD) simulations have become commonplace as a tool in the engineering and design of high-speed aircraft.
+Experiments are often complemented by computational simulations, and CFD technologies have proved very useful in both the reduction of aircraft development cycles, and in the simulation of conditions difficult to reproduce experimentally.
+Great advances have been made in the field since its introduction, especially in areas of meshing, computer architecture, and solution strategies.
+Despite this, there still exist many computational limitations in existing CFD methods; in particular, reliable higher order and $hp$-adaptive methods for the Navier-Stokes equations that govern compressible flow.
 
-\begin{acknowledgments}		% Optional
-\index{Acknowledgments@\emph{Acknowledgments}}%
-I wish to thank the multitudes of people who helped me. Time would
-fail me to tell of \ldots
-\end{acknowledgments}
+Solutions to the Navier-Stokes equations can display shocks and boundary layers, which are characterized by localized regions of rapid change and high gradients.
+The use of adaptive meshes is crucial in such settings --- good resolution for such problems under uniform meshes is computationally prohibitive and impractical for most physical regimes of interest.
+However, the construction of ``good" meshes is a difficult task, usually requiring a-priori knowledge of the form of the solution.
+An alternative to such is the construction of automatically adaptive schemes; such methods begin with a coarse mesh and refine based on the minimization of error.
+However, this task is difficult, as the convergence of numerical methods for problems in CFD is notoriously sensitive to mesh quality.
+Additionally, the use of adaptivity becomes even more difficult in the context of higher order and $hp$ methods \cite{BoeingHigherOrder}.
 
-\utabstract
-\index{Abstract}%
-\indent
-This document has the form of a ``fake'' doctoral dissertation
-in order to provide an example of such, but it is actually a
-copy of Miguel Lerma's documentation for the Mathematics
-Department Computer Seminar of 25 March 1998 updated in July 2001
-and following by Craig McCluskey to meet the March 2001
-requirements of the Graduate School.
+Many of the above issues are tied to the notion of \emph{robustness}, which we define loosely for CFD applications as the degradation of the quality of numerical solutions on a coarse mesh with respect to the Reynolds number, or nondimensional viscosity.
+For typical physical conditions of interest for the compressible Navier-Stokes equations, the Reynolds number dictates the scale of shock and boundary layer phenomena, and can be extremely high --- on the order of 1e7 in a unit domain.
+For an under-resolved mesh, the Galerkin finite element method develops large oscillations which prevent convergence and pollute the solution.
 
-This document and its source file show to write a Doctoral Dissertation using 
-\LaTeX{} and the utdiss2 package.
+The issue of robustness for finite element methods was addressed early on by Brooks and Hughes in the SUPG method \cite{SUPG}, which introduced the idea of residual-based stabilization to combat such oscillations.
+Such methods have been widely used in industry; however, these methods are limited to low-order approximations.
+Additionally, such methods are typically formulated for model problems and then applied to the Navier-Stokes equations, where the extrapolation can be inexact and ad-hoc.
 
-\tableofcontents   % Table of Contents will be automatically
-                   % generated and placed here.
+Residual-based stabilizations can alternatively be viewed as modifying the standard finite element test space, and consequently the norm in which the finite element method converges.
+Demkowicz and Gopalakrishnan generalized this idea in 2009 by introducing the discontinous Petrov-Galerkin (DPG) method with optimal test functions, where test functions are determined such that they minimize the discrete linear residual in a dual space.
+Under the ultra-weak variational formulation, these test functions can be computed locally to yield a symmetric, positive-definite system.
+The DPG method was quickly used to solve the convection and convection-diffusion problems \cite{DPG1,DPG2,DPG3}, and has recently been shown to yield a robust higher order adaptive method for the convection-diffusion model problem in arbitrary dimensions \cite{DPGrobustness,DPGrobustness2}.
 
-%\listoftables      % List of Tables and List of Figures will be placed
-%\listoffigures     % here, if applicable.
+\paragraph{Goal:} Our goal is to develop a DPG method and higher order adaptive scheme for the steady state compressible laminar Navier-Stokes equations in transonic/supersonic regimes that is robust over a range of Mach and Reynolds numbers.
+In particular, we hope to present a method for which automatic $hp$-adaptivity can be applied to problems in compressible flow.
 
-\chapter{Introduction}
+\subsection*{Area A: Applicable Mathematics}
 
-\include{proposalIntro}
+The main theoretical thrust of this research is to develop a DPG method that is provably robust for singular perturbation problems in CFD, but does not suffer from discretization error in the approximation of test functions \cite{DPGrobustness, DPGrobustness2}.
+I will develop such a method for the prototypical singular perturbation problem of convection-diffusion, demonstrate that the method does not suffer from error in the approximation of test functions, and prove the robust bound of the $L^2$ error by the energy error in which DPG is optimal.
+In doing so, I will employ a new inflow boundary condition which, compared to standard Dirichlet inflow conditions, induces more well-behaved solutions to the adjoint problem, and describe the effect upon the robustness of the DPG method.
+I will then extend this method to the linearized Navier-Stokes equations, and conduct a similar analysis of the robustness of DPG for the linearized Navier-Stokes system.
 
-\chapter{Discontinuous Petrov-Galerkin: a minimum residual method for linear problems}
+\subsection*{Area B: Numerical Analysis and Scientific Computation}
 
-\include{DPGtheory}
+A large thrust of the numerical work here has focused on the development of a 2D compressible flow code under the parallel DPG Camellia codebase, developed by Nathan Roberts at ICES \cite{Camellia}.
+In particular, we have developed a framework allowing for rapid implementation of problems and the easy application of higher order and $hp$-adaptive schemes based on a natural error representation function that stems from the DPG residual \cite{DPG2, DPG3}.
+Additionally, the effectiveness and necessity of anisotropic refinement schemes for problems in CFD has been demonstrated several times in the literature \cite{anisotropy1,anisotropy2}.
+The DPG error representation function has been shown to yield an effective and natural vector-valued residual with which to drive refinement, which we hope to generalize to anisotropic adaptive schemes.
 
-\chapter{A robust DPG method for convection-diffusion}
+A recent theoretical development has been a Hessian-based DPG method that aims to minimize the \emph{nonlinear} residual in the dual space.
+This method will augment the positive definite DPG stiffness matrix with a symmetric update determined by the form of the Hessian and the nonlinear residual.
+I will implement such a nonlinear approach and study its effect on the convergence of the nonlinear steady-state problem and the feasibility of different solvers for the new discrete system.
 
-\begin{itemize}
-\item Describe mathematically the issue with standard Galerkin.
-\item Give proofs of robustness and numerical results (from paper)\cite{ChanHeuerBui-ThanhDemkowicz12}
-\end{itemize}
-\todo{Transition between paper and this bit}
+Finally, the DPG method under the ultra-weak formulation yields itself very naturally to a host of parallelizable solvers.
+In particular, I will implement the distributed Schur complement method and study its scalability.
 
-\include{DPGrobustness}
+\subsection*{Area C: Mathematical Modeling and Applications}
 
-\chapter{Proposed work}
+I will apply the DPG method to a several convection diffusion problems which mimic difficult problems in compressible flow simulations, including boundary layer and closed streamline problems.
+I will also solve a viscous Burgers' equation as an extension of DPG to nonlinear problems.
+Finally, the effectiveness of DPG as a numerical method for compressible flow will be assessed with the application of DPG to common transonic and superonic benchmark problems.
+In particular, I will use DPG to solve the flat plate problem, the ramp problem, flow over a Gaussian bump, and flow over an airfoil over a range of Mach numbers and laminar Reynolds numbers.
 
-\include{NonlinDPG}
-\include{BurgersNotes}
-\include{NSNotes}
-\include{areaReq}
+Time permitting, I will also explore the regularization of the inviscid convection and Euler equations using the full convection-diffusion and Navier-Stokes equations in the small-viscosity limit.
+
+%Additionally, we will seek to pursue the application of DPG to the inviscid Euler equations
 

### 2012-06-20 docs/Jesse/Proposal/problemRange.tex

@@
 Under such assumptions, the flow is largely uniform, with slight variations that are small compared to the uniform stream velocity.
-We are interested in the linearized Navier-Stokes equations mainly for mathematical purposes;
+We are interested in the linearized Navier-Stokes equations mainly for mathematical purposes - as the solution to the full Navier-Stokes equations involves a series of solutions for linearized Navier-Stokes, we wish to investigate the behavior of our numerical method with respect to this system.
 
@@
 A feature of the Burgers' equation not present in convection-diffusion is that, due to the presence of the nonlinear term, it can develop shock discontinuities in its solutions in finite time.
-
 The Burgers' equation has also been used to study the phenomenon of turbulence; however, the Burgers equation does not exhibit the chaotic nature and sensitivity to initial conditions that characterizes turbulence as observed in the full and incompressible Navier-Stokes equations.
-In the scope of this dissertation, Burgers shall be used as to test the extension of our numerical method to nonlinear problems.
+In the scope of this dissertation proposal, Burgers shall be used as to test the extension of our numerical method to nonlinear problems.
 
@@
 
-The Euler equations are a result of neglecting the viscous terms in the Navier-Stokes equations.
-Physically speaking, these assumptions correspond to the inviscid limit, as well as a particular class of boundary conditions (for example, the wall boundary condition $\boldsymbol u = 0$ does not hold in the inviscid limit).
+The pure convection equation is a result of neglecting the viscous term in the convection-diffusion equation.
+Physically speaking, these assumptions correspond to the inviscid limit, as well as a particular class of boundary conditions (for example, the wall boundary condition $u = 0$ and prescribed inflow condition may be incompatible in the inviscid limit).
+The Euler equations are likewise a result of neglecting the viscous terms in the Navier-Stokes equations.
+However, these problems can be ill-posed in the continuous setting.
+Take, for example, the vortex problem in Figure~\ref{fig:convCirc}.
+A feature of the convection equation is that there is no crosswind diffusion - thus, materials do not mix across streamlines.
+However, for the vortex problem, this also implies that the solution on any closed streamline can take any arbitrary value, and is thus undefined.
 
-\todo{express coupling - Drela's IBL work} \cite{BoeingDrela}
-\todo{Express that mathematically, the Euler equations are difficult}
+\begin{figure}[!h]
+\centering
+\includegraphics[scale = .22]{figs/convCirc.png}
+\caption{Setup for the vortex problem.}
+\label{fig:convCirc}
+\end{figure}
+Formally speaking, the solution to the vortex problem is taken to be the solution to the convection-diffusion equation (with appropriate outflow boundary conditions) as the viscosity tends towards zero, in which case, the solution in the interior would be uniformly zero.
+This motivates the need for \emph{artificial viscosity} methods with which to regularize inviscid solutions.
+The topic is expansive, and we direct the reader towards \cite{Barter} for a more detailed discussion of past and present artificial viscosity methods.
+
+There is still much interest in solving the inviscid Euler equations in industry --- the full Navier-Stokes models often prove difficult to solve due to the mathematical nature of the equations, and the coupling of the Euler equations with boundary layer models has been successful in simulating many phenomena in compressible flow \cite{BoeingDrela}.

### 2012-06-20 docs/Jesse/Proposal/NSNotes.tex
modifications to thesis (adding of inviscid/incompressible stuff, mod of area requirement, mod of NS notes

@@
 
-For $p=2$, after six refinements, the mesh contained 1410 elements and 187605 global dofs, with a total DPG energy error of $.000753$.
-Comparatively, for $p=3$, the mesh contained only 444 elements and 97403 global dofs, with a total DPG eneryg error of $0.000676$ after five refinements.
+For $p=2$, after six refinements, the mesh contained 1134 elements and 150489 global dofs, with a total DPG energy error of $.000753$.
 
@@
 \subfigure[$p=2$]{\includegraphics[scale=.5]{figs/Re1000p2/mesh.pdf}}
-\subfigure[$p=3$]{\includegraphics[scale=.5]{figs/Re1000p3/mesh.pdf}}
-\caption{Adaptive mesh after six refinements for $p=2$ and five refinements for $p=3$ with $\Reyn = 1000$.}
+%\subfigure[$p=3$]{\includegraphics[scale=.5]{figs/Re1000p3/mesh.pdf}}
+\caption{Adaptive mesh after six refinements for $p=2$
+% and five refinements for $p=3$ 
+with $\Reyn = 1000$.}
 \label{fig:MeshRe500}

### 2012-06-20 docs/Jesse/Proposal/areaReq.tex
modifications to thesis (adding of inviscid/incompressible stuff, mod of area requirement, mod of NS notes

@@
 \item{\textbf{Completed: convection-dominated diffusion, Burgers, and a model problem for Navier-Stokes.}}
+
+I have applied the DPG method to a several convection diffusion problems which mimic difficult problems in compressible flow simulations, including boundary layer and closed streamline problems.
+I have also solved the viscous Burgers' equation as an extension of DPG to nonlinear problems.
+I have also explored the regularization of the pure convection equation using the full convection-diffusion equation in the small-viscosity limit.
+DPG has also been applied to the Navier-Stokes equations to achieve a solution to the flat plate problem for $\Reyn = 1000$.
+
 \item{\textbf{Proposed: Higher Reynolds number, ramp problem, Gaussian bump, airfoil.}}
+
+The effectiveness of DPG as a numerical method for compressible flow will be assessed with the application of DPG to common transonic and superonic benchmark problems.
+In particular, I will use DPG to solve the flat plate problem, the ramp problem, flow over a Gaussian bump, and flow over an airfoil over a range of Mach numbers and laminar Reynolds numbers.
+
 \item{\textbf{Proposed: regularized Euler.}}
+
+Time permitting, I will also explore the regularization of the Euler equations using the full Navier-Stokes equations in the inviscid limit.
+
 \end{itemize}

### 2012-06-20 docs/Jesse/Proposal/problemRange.tex
modifications to thesis (adding of inviscid/incompressible stuff, mod of area requirement, mod of NS notes

@@
 
-\todo{reference Stokes, cite Nate}
-\cite{stokesDPG}
+Under appropriate assumptions on the behavior of density and temperature, the behavior of the compressible Navier-Stokes equations can be sufficiently represented by the incompressible Navier-Stokes equations for low speed laminar fluid flows.
+
+For viscous ``creeping'' flows, the incompressible Navier-Stokes equations reduce down to the Stokes equations. \cite{stokesDPG}
 
@@
 
+The scalar convection-diffusion equation is also mathematically important
+
 \todo{add perspective on convection-diffusion}
@@
 The Burgers' equation has also been used to study the phenomenon of turbulence; however, the Burgers equation does not exhibit the chaotic nature and sensitivity to initial conditions that characterizes turbulence as observed in the full and incompressible Navier-Stokes equations.
+
+The Burgers' equation is also the simplest nonlinear extension of the linear convection-diffusion equation, and exact solutions can sometimes be found using the method of characteristics.
 In the scope of this dissertation proposal, Burgers shall be used as to test the extension of our numerical method to nonlinear problems.

### 2012-06-25 docs/Jesse/Proposal/abstract.tex
adding stuff to tex files of jesse proposal

@@
 
-\author{Jesse Chan\\Committee: \vspace{-0.3cm}\\Dr. Leszek Demkowicz (co-supervisor), Dr. Robert Moser (co-supervisor),\vspace{-0.3cm}\\ Dr. Tom Hughes, Committee Member 2, Committee Member 3}
+\author{Jesse Chan\\Committee: \vspace{-0.3cm}\\Dr. Leszek Demkowicz (co-supervisor), Dr. Robert Moser (co-supervisor),\vspace{-0.3cm}\\ Dr. Todd Arbogast, Dr. Omar Ghattas, Dr. Venkat Raman}
 
@@
 Residual-based stabilizations can alternatively be viewed as modifying the standard finite element test space, and consequently the norm in which the finite element method converges.
-Demkowicz and Gopalakrishnan generalized this idea in 2009 by introducing the discontinous Petrov-Galerkin (DPG) method with optimal test functions, where test functions are determined such that they minimize the discrete linear residual in a dual space.
+Demkowicz and Gopalakrishnan generalized this idea in 2009 by introducing the Discontinous Petrov-Galerkin (DPG) method with optimal test functions, where test functions are determined such that they minimize the discrete linear residual in a dual space.
 Under the ultra-weak variational formulation, these test functions can be computed locally to yield a symmetric, positive-definite system.
@@
 Additionally, the effectiveness and necessity of anisotropic refinement schemes for problems in CFD has been demonstrated several times in the literature \cite{anisotropy1,anisotropy2}.
-The DPG error representation function has been shown to yield an effective and natural vector-valued residual with which to drive refinement, which we hope to generalize to anisotropic adaptive schemes.
+The DPG error representation function has been shown to yield an effective and natural residual with which to drive refinement, which we hope to generalize to anisotropic adaptive schemes.
 
@@
 Finally, the effectiveness of DPG as a numerical method for compressible flow will be assessed with the application of DPG to common transonic and superonic benchmark problems.
-In particular, I will use DPG to solve the flat plate problem, the ramp problem, flow over a Gaussian bump, and flow over an airfoil over a range of Mach numbers and laminar Reynolds numbers.
+In particular, I will use DPG to solve the flat plate problem, the ramp problem, and flow over a Gaussian bump over a range of Mach numbers and laminar Reynolds numbers.
 
-Time permitting, I will also explore the regularization of the inviscid convection and Euler equations using the full convection-diffusion and Navier-Stokes equations in the small-viscosity limit.
+Time permitting, I will also attempt to simulate flow over an airfoil, and to explore the regularization of the inviscid convection and Euler equations using the full convection-diffusion and Navier-Stokes equations in the small-viscosity limit.
 

### 2012-06-25 docs/Jesse/Proposal/outline.tex
committing changes to proposal tex/bib files
adding stuff to tex files of jesse proposal

@@
 
-\title{Proposal outline/notes for DPG and Compressible Navier-Stokes}
+\title{A DPG method for compressible flow problems}
 
@@
 \committeemembers
-	[Thomas J. R. Hughes]
-	[Somebody]
-	[Somebody]
-	{Eh}
+	[Committee member 1]
+	[Committee member 2]
+	{Committee member 3}
 
@@
 
-\include{proposalIntro}
+\input{proposalIntro}
+
+\chapter{Range of problems}
+
+\input{problemRange}
 
@@
 
-\include{DPGtheory}
+\input{DPGtheory}
 
@@
 
-\begin{itemize}
-\item Describe mathematically the issue with standard Galerkin.
-\item Give proofs of robustness and numerical results (from paper)\cite{ChanHeuerBui-ThanhDemkowicz12}
-\end{itemize}
-\todo{Transition between paper and this bit}
-
-\include{DPGrobustness}
+\input{DPGrobustness}
 
@@
 
-\include{NonlinDPG}
-\include{BurgersNotes}
-\include{NSNotes}
-\include{areaReq}
+\input{NonlinDPG}
+\input{BurgersNotes}
+\input{NSNotes}
+\input{areaReq}
 
@@
 %\chapter{Appendix}
-\appendices
+\appendix
 \input{paper_appendix.tex}
-\input{hyperbolicDPG.tex}
+%\input{hyperbolicDPG.tex}
 

### 2012-06-25 docs/Jesse/Proposal/problemRange.tex
adding stuff to tex files of jesse proposal

@@
 
-\todo{write blurb on how comp NS is used - small Re limit}
-\todo{write blurb on turbulence}
+As mentioned before, the compressible Navier-Stokes equations are especially of interest in the simulation of high-speed air flows.
+In other contexts, however, the compressible Navier-Stokes equations may be simplified based on physical assumptions about the problem at hand.
+We briefly cover several simplifying assumptions common in CFD applications.
 
@@
 Under appropriate assumptions on the behavior of density and temperature, the behavior of the compressible Navier-Stokes equations can be sufficiently represented by the incompressible Navier-Stokes equations for low speed laminar fluid flows.
+The study of the incompressible Navier-Stokes equations is an open area in mathematics, and is one of the most famous Millenium Problems posed by the Clay Mathematics Institute.
+The equations of incompressible flow pose a difficult problem computationally as well, in part due to the problem of the simulation of turbulent phenomena.
 
-For viscous ``creeping'' flows, the incompressible Navier-Stokes equations reduce down to the Stokes equations. \cite{stokesDPG}
+For highly viscous ``creeping'' flows, the incompressible Navier-Stokes equations reduce down to the Stokes equations.
+We remark that determining good finite element spaces for the Stokes problem is still an active area of research.
+\cite{stokesFEM} lists several choices of finite element discretizations suitable for the Stokes equation.
+
+The scope of this dissertation will not deal with these two equations --- the Stokes equations are treated in \cite{stokesDPG}, and the incompressible Navier-Stokes are covered in an upcoming dissertation.
 
@@
 
-The scalar convection-diffusion problem is the prototypical model problem for solving the full Navier-Stokes equations; most stabilized methods consider first the scalar convection-diffusion equation as a test case before attempting a solution of the full Navier-Stokes equations.
-As discussed previously, an important feature of the convection-diffusion equation is that solutions can develop  boundary layers, a physical feature found in most applications of interest for compressible flow.
+The scalar convection-diffusion equation models mathematically the distribution of the concentration $u$ of a substance in a medium due to both convective and diffusive effects.
+The general form of the equation in $\mathbb{R}^n$ is
+\[
+\beta\cdot \grad u - \epsilon \Delta u = f,
+\]
+where $\beta \in \mathbb{R}^n$ is a vector specifying the direction of convection.
 
-The scalar convection-diffusion equation is also mathematically important
-
-\todo{add perspective on convection-diffusion}
+Scalar convection-diffusion has significant historical importance, as it is the prototypical model problem for solving the full Navier-Stokes equations --- most stabilized methods consider first the scalar convection-diffusion equation as a test case before attempting a solution of the full Navier-Stokes equations.
+As discussed previously, an important feature of the convection-diffusion equation is that solutions can develop boundary layers whose thickness depends on the viscosity, a physical feature found in most applications of interest for compressible flow.
 

### 2012-06-26 docs/Jesse/Proposal/areaReq.tex

@@
 
-\subsection{Area A}
+\subsection{Area A: Applicable mathematics}
 
@@
 
-\subsection{Area B}
+\subsection{Area B: Numerical analysis and scientific computation}
 
@@
 Additionally, through either diagonal preconditioning or matrix equilibration, the condition number of the Schur complement can often be made significantly smaller than $O(h^{-1})$, and the positive-definiteness of the resulting system allows the use of fast iterative solvers in solving the condensed system.
-
 We hope to implement such a distributed solver and determine the scalability of this solver under DPG.
@@
 The effectiveness and necessity of anisotropic refinement schemes for problems in CFD has been demonstrated several times in the literature \cite{anisotropy1,anisotropy2}.
-As the error representation function has been shown to yield an effective and natural vector-valued residual with which to drive refinement, we hope to generalize the use of the error representation function to yield anisotropic adaptive schemes.
+As the error representation function has been shown to yield an effective and natural residual with which to drive refinement, we hope to generalize the use of the error representation function to yield anisotropic adaptive schemes.
 Additionally, we hope to explore the possibility of inferring an optimal choice between $h$ and $p$ refinement using the error representation function.
@@
 
-\subsection{Area C}
+\subsection{Area C: Mathematical modeling and applications}
 
@@
 I have also explored the regularization of the pure convection equation using the full convection-diffusion equation in the small-viscosity limit.
-DPG has also been applied to the Navier-Stokes equations to achieve a solution to the flat plate problem for $\Reyn = 1000$.
+A quadratic-order adaptive DPG method has also been applied to the Navier-Stokes equations to achieve a solution to the flat plate problem for $\Reyn = 1000$.
 
@@
 The effectiveness of DPG as a numerical method for compressible flow will be assessed with the application of DPG to common transonic and superonic benchmark problems.
-In particular, I will use DPG to solve the flat plate problem, the ramp problem, flow over a Gaussian bump, and flow over an airfoil over a range of Mach numbers and laminar Reynolds numbers.
+In particular, I will use DPG to solve the flat plate problem, the ramp problem, flow over a Gaussian bump, over a range of Mach numbers and laminar Reynolds numbers.
+Time permitting, I will attempt to also present solutions to flow over an airfoil.
 

### 2012-06-26 docs/Jesse/Proposal/DPGtheory.tex
adding updates to proposal tex files

@@
 
-Throughout the paper, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U'$ and $V'$ as the respective topological dual spaces.
+Throughout this work, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U'$ and $V'$ as the respective topological dual spaces.
 Let $U_h \subset U$ and $V_h\subset V$ be finite dimensional subsets.
-We are interested in the following problem
-\begin{equation}
-\eqnlab{variationEq}
-\left\{
-  \begin{array}{l}
-    \text{Given } l \in V', \text{ find } u_h \in U_h  \text{ such that} \\ 
-    b(u_h,v_h) = l(v_h), \quad \forall v_h\in V_h,
-  \end{array}
-  \right.
-\end{equation}
+We are interested in the following problem: given $l \in V'$, find $u_h \in U_h$  such that
+%\begin{equation}
+%\eqnlab{variationEq}
+%\left\{
+%  \begin{array}{l}
+%    \text{Given } l \in V', \text{ find } u_h \in U_h  \text{ such that} \\ 
+%    b(u_h,v_h) = l(v_h), \quad \forall v_h\in V_h,
+%  \end{array}
+%  \right.
+%\end{equation}
+\begin{align}
+b(u_h,v_h) &= l(v_h), \quad \forall v_h\in V_h, \eqnlab{variationEq}
+\end{align}
 where $b\LRp{\cdot,\cdot}: U \times V \to \mbb{R}$ is a continuous
-bilinear form.  $U$ is chosen to be some trial space of approximating functions, but $V_h$ is as of yet unspecified.
+bilinear form.
+$U$ is chosen to be some trial space of approximating functions, but $V_h$ is as of yet unspecified.
+Throughout this work, we suppose the variational problem \eqnref{variationEq} to be well-posed.
 
-Throughout the paper, we suppose the variational
-problem \eqnref{variationEq} to be well-posed. In that case, we can
-identify a unique operator $B:U\rightarrow V'$ such that
+We can identify a unique operator $B:U\rightarrow V'$ such that
 \[
@@
 \]
-For convenience in writing, we will abuse the notation $\sup_{v \in V}$ to denote $\sup_{v\in V\setminus\{0\}}$ for the remainder of the paper.
+For convenience in writing, we will abuse the notation $\sup_{v \in V}$ to denote $\sup_{v\in V\setminus\{0\}}$ for the remainder of this work.
 
@@
 The first order optimality condition for \eqnref{minimization} requires
-the G\^ateaux derivative to be zero in all directions $\delta u \in
-U_h$, i\.e\.,
+the G\^ateaux derivative to be zero in all directions $\delta u \in U_h$, i.e.,
 \begin{align*}
@@
 V$ such that $\dim(\tilde{V}) > \dim(U_h)$ elementwise \cite{DPG1, DPG2}. In this
-paper, we assume the error in approximating the optimal test functions
+document, we assume the error in approximating the optimal test functions
 is negligible, and refer to the work in \cite{practicalDPG} for
@@
 \]
-This is simply a consequence of the least-squares nature of DPG; the energy error is simply the norm of the  residual in $V'$.
+This is simply a consequence of the minimum-residual nature of DPG; the energy error is simply the norm of the  residual in $V'$.
 
-Practically speaking, this implies that the DPG method is discretely stable on any mesh.
-In particular, DPG is unconditionally stable for higher order adaptive meshes, where discrete stability is often an issue.
+Practically speaking, this implies that the DPG method is not only discretely stable, but delivers the \emph{best approximation in the energy norm} on any mesh.
+In particular, the stability and optimality of DPG apply naturally to higher order adaptive meshes, where discrete stability is often an issue.
 
@@
 Note that we allow arbitrariness in assigning ``-'' and ``+'' quantities to the adjacent elements $K_i$ and $K_j$.
-%For the rest of the paper, we will use the same notation for both a function and its trace (if it is well-defined) when there is no ambiguity.
 
@@
 Likewise, we will refer $\nor{\cdot}_{U,V}$ as the trial norm induced by a given test norm $\nor{\cdot}_V$.
-In this paper, for simplicity of exposition, we shall call a pair of norms in $U$ and $V$ that induce each other as an {\em energy norm pairing}.
+In this work, for simplicity of exposition, we shall call a pair of norms in $U$ and $V$ that induce each other as an {\em energy norm pairing}.
 

### 2012-06-26 docs/Jesse/Proposal/NSNotes.tex
adding updates to proposal tex files

@@
 \end{align*}
-An advantage of this extrapolation approach is that the incompletely parabolic nature of the Navier-Stokes equation is taken into account; there is no diffusive term present in the mass conservation equation, and the test norm reflects that by requesting only limited regularity of $v_1$.\footnote{The situation is analagous to using the full $H^1(\Oh)$ norm for the pure convection equation --- the optimal test norm $\nor{v}_V = \nor{\beta\cdot \grad v} + \nor{v}$ implies only streamline regularity, whereas taking $\nor{v}_V = \nor{\grad v} + \nor{v}$ implies stronger regularity on the test space $V$ than the graph norm.
+An advantage of this extrapolation approach is that the incompletely parabolic nature of the Navier-Stokes equation is taken into account; there is no diffusive term present in the mass conservation equation, and the test norm reflects that by requesting only limited regularity of $v_1$.\footnote{The situation is analogous to using the full $H^1(\Oh)$ norm for the pure convection equation --- the optimal test norm $\nor{v}_V = \nor{\beta\cdot \grad v} + \nor{v}$ implies only streamline regularity, whereas taking $\nor{v}_V = \nor{\grad v} + \nor{v}$ implies stronger regularity on the test space $V$ than the graph norm.
 Consequently, convergence is suboptimal for DPG applied to the convection problem under the $H^1(\Oh)$ test norm.}
@@
 \begin{itemize}
-\item{DPG parameters:} $p = 2$ or $p=3$, and $\Delta p = 2$ uniformly across the mesh. 
+\item{DPG parameters:} $p = 2$ and $\Delta p = 2$ uniformly across the mesh. 
 \item{Adaptivity parameters:} Energy threshold for refinements is $\alpha = .2$ or $\alpha = .15$. 
@@
 We impose these strongly on the trace variables $\widehat{u}_1, \widehat{u}_2, \widehat{T}$.
-\item \textbf{Outflow boundary conditions:} the exact boundary conditions to enforce here are not universally agreed on\footnote{Demkowicz et al enforce an outflow boundary condition only in regions where the flow is subsonic.\cite{Demkowicz:1990:NFE:112271.112276}}.
-Many enforce $\pd{u_1}{n}=\pd{u_2}{n}=0$ and $\pd{T}{n} = 0$.
+\item \textbf{Outflow boundary conditions:} the exact boundary conditions to enforce here are not universally agreed on.
+Many enforce $\pd{u_1}{n}=\pd{u_2}{n}=0$ and $\pd{T}{n} = 0$, while others enforce an outflow boundary condition only in regions where the flow is subsonic.\cite{Demkowicz:1990:NFE:112271.112276}.
 We adopt a ``no boundary condition'' outflow condition, first introduced in \cite{FLD:FLD1650140506}.
@@
 
-An alternative boundary condition would be as follows: since $u_1$ and $u_2$ are not expected to be zero at these points, we can set $\widehat{f}_{2,n}$ and $\widehat{f}_{4,n}$ to their represented quantities using either the field variables from the background flow, or (in the case of pseudo-time stepping) the previous timestep's flux and field quantities.
+%An alternative boundary condition would be as follows: since $u_1$ and $u_2$ are not expected to be zero at these points, we can set $\widehat{f}_{2,n}$ and $\widehat{f}_{4,n}$ to their represented quantities using either the field variables from the background flow, or (in the case of pseudo-time stepping) the previous timestep's flux and field quantities.
 
@@
 
-For our initial guesses, we set
+We initialize our solution to
 \[
@@
 
-For $p=2$, after six refinements, the mesh contained 1134 elements and 150489 global dofs, with a total DPG energy error of $.000753$.
+%For $p=2$, after six refinements, the energy error is 0.000410347. After refinement, mesh has 1083 elements and 143910 global dofs.
 
@@
 \centering
-\subfigure[$p=2$]{\includegraphics[scale=.5]{figs/Re1000p2/mesh.pdf}}
+%\subfigure[$p=2$]{\includegraphics[scale=.5]{figs/Re1000p2/mesh.pdf}}
 %\subfigure[$p=3$]{\includegraphics[scale=.5]{figs/Re1000p3/mesh.pdf}}
+\includegraphics[scale=.55]{figs/Re1000p2/mesh.pdf}
 \caption{Adaptive mesh after six refinements for $p=2$
@@
 with $\Reyn = 1000$.}
-\label{fig:MeshRe500}
+\label{fig:MeshRe1000}
 \end{figure}

### 2012-06-26 docs/Jesse/Proposal/NonlinDPG.tex
adding updates to proposal tex files

@@
 Since DPG allows for the formulation of a discrete nonlinear residual, it is possible to formulate the nonlinear DPG problem as a minimization problem and use an optimization method to solve the discrete nonlinear problem.
-This approach has been successfully implemented by Peraire et al\.
-in solving compressible gas dynamics problems on uniform grids using a modified version of the ultra-weak variational formulation \cite{MITDPG}.
+This approach has been successfully implemented by Peraire et al.\ in solving compressible gas dynamics problems on uniform grids using a modified version of the ultra-weak variational formulation \cite{MITDPG}.
 An additional advantage of such an approach would be the more direct enforcement of physical constraints, which are treated in an ad-hoc manner in most compressible Navier-Stokes solvers.
@@
 \end{align*}
-which can be computed in the same fashion as a Bubnov-Galerkin stiffness matrix. This addition, though not positive definite, is symmetric due to the nature of second order Ga\^teux derivatives.
+which can be computed in the same fashion as a Bubnov-Galerkin stiffness matrix. This addition, though not positive definite, is symmetric due to the nature of second order derivatives.
 

### 2012-06-26 docs/Jesse/Proposal/proposalIntro.tex
adding updates to proposal tex files

@@
 Over the last three decades, Computational Fluid Dynamics (CFD) simulations have become commonplace as a tool in the engineering and design of high-speed aircraft.
-Wind tunnel experiments are often complemented by computational simulations, and CFD technologies have proved very useful in both the reduction of aircraft development cycles, and in the simulation of conditions difficult to reproduce experimentally.
+Wind tunnel experiments are often complemented by computational simulations, and CFD technologies have proved very useful in both the reduction of aircraft development cycles and the simulation of experimentally difficult conditions.
 Great advances have been made in the field since its introduction, especially in areas of meshing, computer architecture, and solution strategies.
@@
 The use of higher order codes to solve the steady state equations is even rarer, where convergence of discrete nonlinear steady equations is a tricky issue \cite{BoeingHigherOrder}.
-\item \textbf{Automatic adaptivity :} The use of adaptive meshes is crucial to many CFD applications, where the solution often exhibits very localized sharp gradients and shocks.
+\item \textbf{Automatic adaptivity :} The use of adaptive meshes is crucial to many CFD applications, where the solution can exhibit very localized sharp gradients and shocks.
 Good resolution for such problems under uniform meshes is computationally prohibitive and impractical for most physical regimes of interest.
 However, the construction of ``good" meshes is a difficult task, usually requiring a-priori knowledge of the form of the solution \cite{andersonCFDBook}.
-An alternative to such is the construction of automatically adaptive schemes; such methods usually begin with a coarse mesh and refine based on the minimization of some error.
+An alternative set of strategies are automatically adaptive schemes; such methods usually begin with a coarse mesh and refine based on the minimization of some error.
 However, this task is difficult, as the convergence of numerical methods for problems in CFD is notoriously sensitive to mesh quality.
@@
 We define robustness loosely as the degradation of the quality of numerical solutions with respect to a given problem parameter.
-In the context of CFD, the parameter of interest is the Reynolds number (the nondimensional equivalent of viscosity) --- for typical physical conditions of interest for the compressible Navier-Stokes equations, the Reynolds number is extremely high, on the order of 1e7, yielding solutions with two vastly different scales - inviscid phenomena at an $O(1)$ scale, and $O(1e-7)$ viscous phenomena.
+In the context of CFD simulations, the parameter of interest is the Reynolds number (the nondimensional equivalent of the inverse of the viscosity) --- for typical physical conditions of interest for the compressible Navier-Stokes equations, the Reynolds number is extremely high, on the order of 1e7, yielding solutions with two vastly different scales - inviscid phenomena at an $O(1)$ scale, and $O(1e-7)$ viscous phenomena.
 
@@
 
-Standard numerical methods tend to perform poorly across the board for the class of PDEs known as singular perturbation problems.
-These problems are often characterized by a parameter that may be either very small or very large in the context of physical problems.
+Standard numerical methods tend to perform poorly across the board for the class of PDEs known as singular perturbation problems; these problems are often characterized by a parameter that may be either very small or very large.
 An additional complication of singular perturbation problems is that very often, in the limiting case of the parameter blowing up or decreasing to zero, the PDE itself will change types (e.g.\ from elliptic to hyperbolic).
-A canonical example of a singularly perturbed problem is the convection-diffusion equation on domain $\Omega \in \mathbb{R}^3$,
+A canonical example of a singularly perturbed problem is the convection-diffusion equation in domain $\Omega \in \mathbb{R}^3$,
 \[
@@
 \]
-The equation represents the change in the scalar quantity $u$, representing the concentration of a quantity in a given medium, taking into account both convective and diffusive effects.
-$\beta \in \mathbb{R}^3$ specifies the direction and magnitude of convection, while the singular perturbation parameter $\epsilon$ represents the diffusivity of the medium.
+The equation models the steady-state distribution of the scalar quantity $u$, representing the concentration of a quantity in a given medium, taking into account both convective and diffusive effects.
+Vector $\beta \in \mathbb{R}^3$ specifies the direction and magnitude of convection, while the singular perturbation parameter $\epsilon$ represents the diffusivity of the medium.
 In the limit of an inviscid medium as $\epsilon\rightarrow 0$, the equation changes types, from elliptic to hyperbolic, and from second order to first order.
@@
 As a consequence, the finite element solution can diverge significantly from the best finite element approximation of the solution for very small values of $\epsilon$.
-For exam ple, Figure~\ref{fig:GalerkinOsc} shows an example of how, on a coarse mesh, and for small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation with a boundary layer develops spurious oscillations everywhere in the domain, even where the best approximation error is small.
-These oscillations grow in magnitude as $\epsilon \rightarrow 0$, eventually polluting the entire solution.
+For example, Figure~\ref{fig:GalerkinOsc} shows an example of how, on a coarse mesh, and for small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation with a boundary layer develops spurious oscillations everywhere in the domain, even where the best approximation error is small.
+These oscillations grow in magnitude as $\epsilon \rightarrow 0$, eventually polluting the entire solution.\footnote{For nonlinear shock problems, the solution often exhibits sharp gradients or discontinuities, around which the solution would develop spurious Gibbs-type oscillations.
+These are a result of underresolution of the solution, and are separate from the oscillations resulting from a lack of robustness.}
 
@@
 From the perspective of the full Navier-Stokes equations, this loss of robustness is doubly problematic.
-Not only will any nonlinear solution suffer from similar non-physical oscillations, but nonlinear solvers themselves may fail to yield a solution due to such instabilities --- a nonlinear solution is almost always computed by solving a series of linear problems whose solutions will converge to the nonlinear solution under appropriate assumptions, and the presence of such oscillations in each linear problem can cause the solution convergence to slow significantly or even diverge.
+Not only will any nonlinear solution suffer from similar non-physical oscillations, but nonlinear solvers themselves may fail to yield a solution due to such instabilities.
+A nonlinear solution is almost always computed by solving a series of linear problems whose solutions will converge to the nonlinear solution under appropriate assumptions, and the presence of such oscillations in each linear problem can cause the solution convergence to slow significantly or even diverge.
 
-Our goal is to develop a \emph{stable, higher order adaptive scheme} for the steady compressible laminar Navier-Stokes equations in transonic/supersonic regimes that is \emph{robust for very small viscosity}.
+Our aim is to develop a \emph{stable, higher order adaptive scheme} for the steady compressible laminar Navier-Stokes equations in transonic/supersonic regimes that is \emph{robust for very small viscosity}.
 In particular, we hope to present a method for which $hp$-adaptivity can be applied to problems in compressible flow.
+The goal of this dissertation will be to develop a mathematical theory demonstrating the robustness in $\epsilon$ of our method for singularly perturbed convection-diffusion problems, and to demonstrate its feasibility as a CFD solver by applying it to several benchmark problems.
+\todo{Check with LD if it's what he's looking for}
 
@@
 For the past half-century, problems in CFD have been solved using a multitude of methods, many of which are physically motivated, and thus applicable only to a small number of problems and geometries.
-We consider more general methods, whose framework is applicable to different problems in CFD; however, our specific focus will be on the nonlinear shock problems of compressible aerodynamics.
+We consider more general methods, whose framework is applicable to a larger set of problems; however, our specific focus will be on the problems of compressible aerodynamics involving small-scale viscous phenomena (i.e.\ boundary layers and, if present, shock waves).
 Broadly speaking, the most popular general methods include (in historical order) finite difference methods, finite volume methods, and finite element methods.
@@
 For linear problems, finite difference (FD) methods approximate derivatives based on interpolation of pointwise values of a function.
-FD methods were popularized first by Lax, who introduced the concepts of the monotone scheme and numerical flux.
-For the conservation laws governing compressible aerodynamics, FD methods approximated the conservation law, using some numerical flux to reconstruct approximations to the derivative at a point.
+In the context of conservation laws, FD methods were popularized first by Lax, who introduced the concepts of the monotone scheme and numerical flux.
+For the conservation laws governing compressible aerodynamics, FD methods approximate the conservation law, using some numerical flux to reconstruct approximations to the derivative at a point.
 Finite volume (FV) methods are similar to finite difference methods, but approximate the integral version of a conservation law as opposed to the differential form.
-FD and FV have roughly the same computational cost/complexity; however, the advantage of FV methods over FD is that FV methods can be used on a much larger class of discretizations than FD methods, which require uniform or smooth meshes.
+FD and FV have roughly the same computational cost/complexity; however, the advantage of FV methods over FD is that FV methods can be used on a much larger class of problems and geometries than FD methods, which require uniform or smooth structured meshes.
 
-For nonlinear shock problems, the solution often exhibits sharp gradients or discontinuities, around which the solution would develop spurious Gibbs-type oscillations.
 Several ideas were introduced to deal with oscillations in the solution near a sharp gradient or shock: artificial diffusion, total variation diminishing (TVD) schemes, and slope limiters.
@@
 Most of these methods can be interpreted as adding some specific artificial diffusion to the given numerical scheme.
-We refer to such schemes as \emph{modified equation} methods, as the exact solution no longer satisfies the discrete system due to the presence of additional artificial diffusion.
+We refer to such schemes as \emph{modified equation} methods, as the exact solution no longer satisfies the discrete system due to the presence of additional artificial diffusion terms.
 
@@
 
-Historically, the Galerkin method has been very successfully applied to a broad range of problems in solid mechanics, for which the variational problems resulting from the PDE are symmetric and coercive (positive-definite).
+Historically, the Galerkin method has been very successfully applied to a broad range of problems in solid mechanics, for which the variational problems resulting from the PDE are often symmetric and coercive (positive-definite).
 It is well known that the finite element method produces optimal or near-optimal results for such problems, with the finite element solution matching or coming close to the best approximation of the solution in the finite element space.
@@
 Standard Galerkin methods, where these trial and test functions are taken from the same space, are referred to as Bubnov-Galerkin methods.
-A Petrov-Galerkin method refers to any Galerkin method other than a classical Bubnov-Galerkin method.
-The Streamline Upwind Petrov Galerkin (SUPG) method is a stabilization method for $H^1$-conforming finite elements, the idea of which was originally motivated by artificial diffusion techniques in finite differences.
+Petrov-Galerkin methods refer most often to methods where test and trial functions \emph{differ}, leading to differing test and trial spaces.\footnote{Hughes takes the more general definition of a Petrov-Galerkin method to be any Galerkin method other than a classical Bubnov-Galerkin method.}  The Streamline Upwind Petrov Galerkin (SUPG) method is a stabilization method for $H^1$-conforming finite elements, the idea of which was originally motivated by artificial diffusion techniques in finite differences.
 In particular, for the homogeneous 1D convection-diffusion equation, it is possible to recover, under a finite difference method, the exact solution at nodal points by adding an ``exact" artificial diffusion based on the mesh size $h$ and the magnitudes of the convection $\beta$ and the viscosity $\epsilon$.
-
-The idea of ``exact" artificial viscosity was adapted to finite elements not through the direct modification of the equations, but through the test functions and weighting of the residual.
-In particular, finite element and Galerkin methods are often referred to as ``weighted residual" methods, since the starting point of both is to multiply the residual by a particular test, or weighting, function.
+The idea of ``exact" artificial viscosity was adapted to finite elements not through the direct modification of the equations, but through the \emph{test} functions and weighting of the residual.
+\footnote{Finite element and Galerkin methods are often referred to as ``weighted residual" methods, since the starting point of both is to multiply the residual by a particular test, or weighting, function.
 Standard Bubnov-Galerkin methods simply choose these weighting functions to be the same as the the basis functions used to approximate the solution.
+}
 
@@
 \]
-where $L_{\rm adv}u \coloneqq \div \left(\beta u\right)$ is the first order advective operator, and $L_{\rm diff}u \coloneqq \epsilon \Delta u$ is the second-order diffusive operator (then, roughly speaking, $L_{\rm diff} u = 0$).
-Let us assume $u$ to be a linear combination of piecewise-linear basis functions $\phi_i, i = 0,\ldots,N$.
+where $L_{\rm adv}u \coloneqq \div \left(\beta u\right)$ is the first order advective operator, and $L_{\rm diff}u \coloneqq \epsilon \Delta u$ is the second-order diffusive operator.
+Let us assume $u$ to be a linear combination of piecewise-linear basis functions $\phi_i, i = 0,\ldots,N$ (then, within each element, $L_{\rm diff} u = 0$).
 The SUPG method is then to solve
@@
 For uniform meshes in 1D, $\tau$ is chosen such that, for $f=0$, the matrix system resulting from SUPG is exactly equal to the finite difference system under ``exact" artificial diffusion.
-However, unlike the artificial diffusion method, for $f\neq 0$, the SUPG method still delivers optimal stabilization.
-In fact, the SUPG finite element solution in 1D is nothing less than the nodal interpolant and the best $H^1$ approximation of the exact solution, as seen in Figure~\ref{fig:SUPG}.
+However, unlike exact artificial diffusion, for $f\neq 0$, the SUPG method still delivers optimal stabilization.
+In fact, the SUPG finite element solution in 1D is nothing less than the nodal interpolant and the best $H^1_0$ approximation of the exact solution, as seen in Figure~\ref{fig:SUPG}.
 
@@
 \]
+\todo{check to make sure this is correct}
 where $v_i$ is defined as
@@
 Discontinuous Galerkin (DG) methods form a subclass of FEM; first introduced by Reed and Hill in \cite{Reed:73}, these methods were later analyzed by Cockburn and Shu \cite{CockburnShu:DG} and have rapidly gained popularity for CFD problems.
-Advantages of DG methods include the local conservation property, easily modified local orders of approximation, easy adaptivity in both $h$ and $p$, and efficient parallelizability.
-Rather than having a continuous basis where the basis function support spans several element cells, DG opts instead for a discontinuous, piecewise polynomial basis, where, like FV schemes, a \emph{numerical flux} facilitates communication between neighboring elements (unlike FV methods, however, there is no need for a reconstruction step).
+Advantages of DG methods include the local conservation property, easily modified local orders of approximation, ease of adaptivity in both $h$ and $p$, and efficient parallelizability.
+Rather than having a continuous basis where the basis function support spans multiple element cells, DG opts instead for a discontinuous, piecewise polynomial basis, where, like FV schemes, a \emph{numerical flux} facilitates communication between neighboring elements (unlike FV methods, however, there is no need for a reconstruction step).
 
@@
 An additional reason for the popularity of DG methods is that they can be interpreted as stabilized FE methods through appropriate choices of this numerical flux \cite{Brezzi20063293}.
-We will illustrate this with the steady convection equation in 1D ---
+We will illustrate this with the steady convection equation in 1D:
 \begin{align*}
@@
 \end{align*}
-We will refer to $v(x_K^+)$ as the upwind value of $v(x_K)$, and refer to DG under this specific choice of traces as upwind DG.
+For $\beta$ positive, $v(x_K^+)$ is the \emph{upwind} value of $v(x_K)$, and we refer to DG under this specific choice of traces as upwind DG.
 This specific choice of $v(x_K)$ as the upwind value is crucial; similarly to SUPG, the upwind DG emphasizes the test function in the direction of convection and changes the way the residual is measured.
@@
 
-HDG methods are an active topic of current research, since they address several criticisms of common DG methods (large number of degrees of freedom, globally coupled degrees of freedom, complicated/inefficient implementation procedures, suboptimal convergence of approximate fluxes).
+HDG methods are an active topic of current research, since they address several criticisms of common DG methods (large number of globally coupled degrees of freedom, complicated/inefficient implementation procedures, suboptimal convergence of approximate fluxes).
 Note that HDG methods still fall under the category of stabilized methods --- stabilization techniques are employed through the choice of the HDG numerical flux, which involves some stabilization parameter $\tau$.
@@
 
-This PhD thesis proposal will proceed in four main parts:
-\begin{enumerate}
-\item Introduce the abstract DPG method as a minimum residual method for linear problems.
-\item Formulate a DPG method addressing the issue of robustness for the model problem of convection-dominated diffusion.
-\item Apply the DPG method to singularly perturbed nonlinear problems in CFD, discussing preliminary results for the Burgers and compressible Navier-Stokes equations. 
-\item Introduce completed and proposed work in concentration areas A, B, and C. 
-\end{enumerate}
+This PhD thesis proposal will proceed in four main parts.
+We will begin by introducing the abstract Discontinuous Petrov-Galerkin (DPG) method as a minimum residual method for linear problems and highlighting some important properties of the method.
+Our next step will be to formulate and prove the robustness of a DPG method (with respect to $\epsilon$) for the model problem of convection-dominated diffusion.
+Finally, we will extend and apply the DPG method to singularly perturbed nonlinear problems in CFD, presenting preliminary results for the Burgers and compressible Navier-Stokes equations.
 

### 2012-07-16 docs/Jesse/Proposal/NSNotes.tex

@@
 For our solver, we use a standard pseudo-time solver and greedy refinement scheme.
-Though we have not yet implemented adaptive timestepping, we are able to take large enough uniform timesteps over a coarse mesh such that convergence is order-of-magnitude comparable to the convergence of a damped Newton method.
+Though we have not yet implemented adaptive timestepping, we are able to take large enough uniform timesteps over a coarse mesh such that convergence occurs sufficiently quickly.
 
@@
 We take the computational domain to be $\Omega = [0,2]\times[0,1]$.
-For $\Reyn = 1000$, we experimented with initial meshes from size 4 by 8 to 8 by 16 elements.
-We note that, on a very coarse initial mesh (4 by 8 elements), the convergence of the pseudo-timestep stagnates at around a transient residual of $1e-6$; however, if we lower the tolerance only for the first step and continued with the adaptive algorithm, the solution converges below $\epsilon_t$ for all refined meshes.
+We begin with a mesh of 8 by 16 elements.
+Under Dirichlet wall boundary conditions for all 3 traces $u_1$, $u_2$, and $T$, the solution develops a singularity in the density $\rho$ at the plate beginning, and both $T$ and $u_1$ form a boundary layer along the leading edge of the plate.
+Due to the presence of the singularity, the solution for $\rho$ is scaled such that the features of the solution away from the singularity are visible in Figure~\ref{fig:rhoScaled}.
 
@@
 \centering
-\subfigure[$\rho$]{\includegraphics[scale=.42]{figs/Re1000p2/rho.pdf}}
-\subfigure[$u_1$]{\includegraphics[scale=.42]{figs/Re1000p2/u1.pdf}}
-\subfigure[$u_2$]{\includegraphics[scale=.42]{figs/Re1000p2/u2.pdf}}
-\subfigure[$T$]{\includegraphics[scale=.42]{figs/Re1000p2/T.pdf}}
-\caption{Solutions after six refinements for $p=2$ and $\Reyn = 1000$.}
+\subfigure[$\rho$]{\includegraphics[scale=.21]{figs/Re1000p2/rhoUnscaled.png}}
+\subfigure[$u_1$]{\includegraphics[scale=.21]{figs/Re1000p2/u1.png}}
+\subfigure[$u_2$]{\includegraphics[scale=.21]{figs/Re1000p2/u2.png}}
+\subfigure[$T$]{\includegraphics[scale=.21]{figs/Re1000p2/T.png}}
+\caption{Solutions after seven refinements for $p=2$ and $\Reyn = 1000$.}
 \label{fig:Re500}
@@
 \centering
-\subfigure[$\rho$]{\includegraphics[scale=.4]{figs/Re1000p2/rhozoom.pdf}}
-\subfigure[$u_1$]{\includegraphics[scale=.4]{figs/Re1000p2/u1zoom.pdf}}
-\subfigure[$u_2$]{\includegraphics[scale=.4]{figs/Re1000p2/u2zoom.pdf}}
-\subfigure[$T$]{\includegraphics[scale=.4]{figs/Re1000p2/Tzoom.pdf}}
-\caption{Zoom of solutions at the beginning of the plate for $p=2$ and $\Reyn = 1000$.}
-\label{fig:Re500}
+\subfigure[$\rho$]{\includegraphics[scale=.25]{figs/Re1000p2/rhoScaled.png}}
+\subfigure[Mesh]{\includegraphics[scale=.57]{figs/Re1000p2/mesh6.png}}
+\caption{Rescaled solution for $\rho$ in the range $[0,3]$ and adaptive mesh after seven refinements.}
+\label{fig:rhoScaled}
 \end{figure}
-
-%For $p=2$, after six refinements, the energy error is 0.000410347. After refinement, mesh has 1083 elements and 143910 global dofs.
 
@@
 \centering
-%\subfigure[$p=2$]{\includegraphics[scale=.5]{figs/Re1000p2/mesh.pdf}}
-%\subfigure[$p=3$]{\includegraphics[scale=.5]{figs/Re1000p3/mesh.pdf}}
-\includegraphics[scale=.55]{figs/Re1000p2/mesh.pdf}
-\caption{Adaptive mesh after six refinements for $p=2$
-% and five refinements for $p=3$ 
-with $\Reyn = 1000$.}
-\label{fig:MeshRe1000}
+\subfigure[$\rho$]{\includegraphics[scale=.23]{figs/Re1000p2/rhoUnscaledzoom.png}}
+\subfigure[$u_1$]{\includegraphics[scale=.23]{figs/Re1000p2/u1zoom.png}}
+\subfigure[$u_2$]{\includegraphics[scale=.23]{figs/Re1000p2/u2zoom.png}}
+\subfigure[$T$]{\includegraphics[scale=.23]{figs/Re1000p2/Tzoom.png}}
+\caption{Zoom of solutions at the beginning of the plate for $p=2$ and $\Reyn = 1000$.}
 \end{figure}
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=.45]{figs/Re1000p2/heatflux.png}
+\caption{Heat flux at the bottom boundary.}
+\end{figure}

### 2012-07-16 docs/Jesse/Proposal/outline.tex
added committee members to outline

@@
 
-\usepackage{utdiss2}  		% Dissertation package style file.
+\usepackage{utproposal}  		% Dissertation package style file.
 
@@
 \committeemembers
-	[Committee member 1]
-	[Committee member 2]
-	{Committee member 3}
+	[Todd Arbogast]
+	[Omar Ghattas]
+	{Venkat Raman}
 
@@
 \begin{document}
-\copyrightpage          % Produces the copyright page.
-\commcertpage           % Produces the Committee Certification
+%\copyrightpage          % Produces the copyright page.
+%\commcertpage           % Produces the Committee Certification
 \titlepage
-
-\begin{dedication}
-\index{Dedication@\emph{Dedication}}%
-Dedicated to \ldots
-\end{dedication}
-
-\begin{acknowledgments}		% Optional
-\index{Acknowledgments@\emph{Acknowledgments}}%
-I wish to thank the multitudes of people who helped me. Time would
-fail me to tell of \ldots
-\end{acknowledgments}
-
-\utabstract
-\index{Abstract}%
-\indent
-This document has the form of a ``fake'' doctoral dissertation
-in order to provide an example of such, but it is actually a
-copy of Miguel Lerma's documentation for the Mathematics
-Department Computer Seminar of 25 March 1998 updated in July 2001
-and following by Craig McCluskey to meet the March 2001
-requirements of the Graduate School.
-
-This document and its source file show to write a Doctoral Dissertation using 
-\LaTeX{} and the utdiss2 package.
 

### 2012-07-16 docs/Jesse/Proposal/proposalPres.tex

\documentclass[compress]{beamer}
\mode<presentation>
\usetheme{Warsaw}
\usecolortheme{seagull}
%\useoutertheme[subsection=false]{smoothbars}
\useoutertheme{infolines}
\useinnertheme{rectangles}

\usepackage{array}
\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{pdfpages}
\usepackage[textsize=footnotesize,color=green]{todonotes}
\usepackage{algorithm, algorithmic}
\usepackage{bm}
\usepackage{tikz}
\usepackage[normalem]{ulem}

\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{color}
\usepackage{undertilde}
\usepackage{pdflscape}
\usepackage{pifont}

\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}
\renewcommand{\floatpagefraction}{0.75}

\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
\newcommand{\tensor}[1]{\underline{\vect{#1}}}
\newcommand{\del}{\triangle}
\newcommand{\grad}{\nabla}
\newcommand{\curl}{\grad \times}
\renewcommand{\div}{\grad \cdot}
\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
\newcommand{\eip}[1]{a\left( #1 \right)}
\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}

\newcommand{\circone}{\ding{192}}
\newcommand{\circtwo}{\ding{193}}
\newcommand{\circthree}{\ding{194}}
\newcommand{\circfour}{\ding{195}}
\newcommand{\circfive}{\ding{196}}

\newcommand{\Reyn}{\rm Re}

\newcommand{\bs}[1]{\boldsymbol{#1}}
\DeclareMathOperator{\diag}{diag}

\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}

\newcommand{\tablab}[1]{\label{tab:#1}}
\newcommand{\tabref}[1]{Table~\ref{tab:#1}}

\newcommand{\theolab}[1]{\label{theo:#1}}
\newcommand{\theoref}[1]{\ref{theo:#1}}
\newcommand{\eqnlab}[1]{\label{eq:#1}}
\newcommand{\eqnref}[1]{\eqref{eq:#1}}
\newcommand{\seclab}[1]{\label{sec:#1}}
\newcommand{\secref}[1]{\ref{sec:#1}}
\newcommand{\lemlab}[1]{\label{lem:#1}}
\newcommand{\lemref}[1]{\ref{lem:#1}}

\newcommand{\mb}[1]{\mathbf{#1}}
\newcommand{\mbb}[1]{\mathbb{#1}}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\nor}[1]{\left\| #1 \right\|}
\newcommand{\snor}[1]{\left| #1 \right|}
\newcommand{\LRp}[1]{\left( #1 \right)}
\newcommand{\LRs}[1]{\left[ #1 \right]}
\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
\newcommand{\LRc}[1]{\left\{ #1 \right\}}
\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
\newcommand{\Grad} {\ensuremath{\nabla}}
\newcommand{\Div} {\ensuremath{\nabla\cdot}}
\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
\newcommand{\uh}{\widehat{u}}
\newcommand{\fnh}{\widehat{f}_n}
\renewcommand{\L}{L^2\LRp{\Omega}}
\newcommand{\pO}{\partial\Omega}
\newcommand{\Gh}{\Gamma_h}
\newcommand{\Gm}{\Gamma_{-}}
\newcommand{\Gp}{\Gamma_{+}}
\newcommand{\Go}{\Gamma_0}
\newcommand{\Oh}{\Omega_h}

\newcommand{\eval}[2][\right]{\relax
  \ifx#1\right\relax \left.\fi#2#1\rvert}

\def\etal{{\it et al.~}}

\def\arr#1#2#3#4{\left[
\begin{array}{cc}
#1 & #2\\
#3 & #4\\
\end{array}
\right]}
\def\vecttwo#1#2{\left[
\begin{array}{c}
#1\\
#2\\
\end{array}
\right]}
\def\vectthree#1#2#3{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
\end{array}
\right]}
\def\vectfour#1#2#3#4{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
#4\\
\end{array}
\right]}

\newcommand{\G} {\Gamma}
\newcommand{\Gin} {\Gamma_{in}}
\newcommand{\Gout} {\Gamma_{out}}

\title{A DPG method for compressible flow problems}
\author{Jesse Chan}

\begin{document}
\begin{frame}
\maketitle
\end{frame}

\section{Introduction/Literature review}
\frame{
\frametitle{Compressible flow problems}
\begin{figure}
\centering
\subfigure[Shock wave]{\includegraphics[scale=.0704]{figs/compFlowPics/bullet_shock.png}}
\subfigure[Boundary layer]{\includegraphics[scale=.16]{figs/compFlowPics/boundary_layer.png}}
%\subfigure{\includegraphics[scale=.15]{figs/compFlowPics/capsule.png}}
\end{figure}
Compressible flow plays an important role in the aerospace and energy industries - supersonic aircraft, combustion engines, etc.

}
\frame{
\frametitle{Goal: Compressible Navier-Stokes equations}
\begin{columns}[c]
\begin{column}{.475\textwidth}
Numerical difficulties:
\begin{itemize}
\item{} Resolving solutions (sharp, localized $O(\Reyn^{-1})$ phenomena)
\begin{itemize}
\item{} Shocks, boundary layers
\item{} Turbulent phenomena
\end{itemize}
\item{} Stability of numerical schemes
\begin{itemize}
\item{} Coarse/adaptive grids
\item{} Higher order
\end{itemize}
\end{itemize}
\end{column}
\begin{column}{.475\textwidth}
\begin{figure}
\centering
\includegraphics[scale = .7]{figs/compFlowPics/airfoil_mesh.png}
\end{figure}
\end{column}
\end{columns}
\vspace{1cm}
\begin{center}
Idea: begin first with the model problem of convection-diffusion.
\end{center}
}
\frame{
\frametitle{Convection-diffusion as a model problem}
\[
\div \left(\beta u\right) - \epsilon \Delta u = f, \quad \text{on }\Omega \in \mathbb{R}^3
\]
}
\frame{
\frametitle{Dealing with stability/robustness}
Convection-diffusion equation in 1D is $\beta u' - \epsilon u'' = f$.
%\vspace{-.5cm}
\begin{columns}[c]
\begin{column}{.49\textwidth}
Standard continuous Galerkin variational formulation: solve
\[
b(u,v) = l(v) 
\]
where
\begin{align*}
b(u,v) &= \int_\Omega -\beta uv' + \epsilon u'v' \\
l(v) &= \int_\Omega f v 
\end{align*}
\end{column}
\begin{column}{.49\textwidth}
\begin{figure}
\centering
\includegraphics[scale=.3]{figs/GalerkinOscTight.png}
\caption{Oscillations in the standard Galerkin method for underresolved meshes and small $\epsilon$.}
\end{figure}
\end{column}
\end{columns}
}
\frame{
Historical stabilization methods: 
\begin{itemize}
\item Artificial diffusion - solve
\[
\beta u' - \tilde{\epsilon} u'' = f
\]
where $\tilde{\epsilon}$ is set depending on $\beta$, $\epsilon$, and the mesh. 
\item Upwind stencils - for positive $\beta$, and uniform grid points $x_A$,
\[
u'(x_A) \approx \frac{u_h(x_A)-u_h(x_{A-1})}{h}
\]
\end{itemize}

Both of these methods introduce additional numerical diffusion, and their effectiveness depends on the forcing $f$ and parameters $h$, $|\beta|$, and $\epsilon$.
}
\frame{
\frametitle{Streamline-upwind Petrov-Galerkin (SUPG)}
SUPG solves $b_{\rm SUPG}(u,v) = l_{\rm SUPG}(v)$, where
\begin{align*}
b_{\rm SUPG}(u,v) &= b(u,v)+ \sum_{K} \int_{K} \tau \LRp{L_{\rm adv} v} L u \\
l_{\rm SUPG}(v) &= l(v) + \sum_{K} \int_{K} \tau \LRp{L_{\rm adv}v} f.
\end{align*}
\vspace{-.5cm}
\begin{columns}[c]
\begin{column}{.47\textwidth}
\vspace{-.5cm}
\begin{itemize}
\item{} $L_{\rm adv}u = \div \left(\beta u\right)$, and $\tau$ is a parameter. 
\item{} Recovers ``exact'' artificial diffusion for $f=0$.
\item{} Effective for $f\neq 0$, unlike ``exact'' artificial diffusion.
\item{} \emph{Residual-based} stabilization. 
\end{itemize}
\end{column}
\begin{column}{.52\textwidth}
\begin{figure}
\centering
\includegraphics[scale=.3]{figs/SUPG.png}
\caption{Exact, FEM, and SUPG solutions.}
\end{figure}
\end{column}
\end{columns}
}

\frame{
Can be interpreted as a \emph{Petrov-Galerkin} method,
\[
b\LRp{u,\tilde{v}_{i}} = l\LRp{\tilde{v}_{i}}, \quad \forall i = 1,\ldots,N-1,
\]
where the SUPG test function $\tilde{v}_{i}$ is defined elementwise as
\[
\tilde{v}_{i} = \phi_i(x) + \tau L_{\rm adv} \phi_i.  
\]
\begin{figure}
\centering
\subfigure{\includegraphics[scale=.185]{figs/SUPGtest.png}}
\caption{SUPG test function $v_i$.}
\end{figure}
}

\section{The DPG Method}
\frame{
\frametitle{Minimum residual methods through optimal testing}
Identify $B:U\rightarrow V'$ such that
\[
\langle Bu,v\rangle_V \coloneqq b(u,v), \quad u\in U, v\in V.
\]
Then, $b(u_h,v) = l(v)$ is equivalent to the equation in $V'$
\[
Bu_h = l
\]
We seek to minimize the functional on $V'$
\[
J(u_h) = \frac{1}{2}\|Bu_h-l\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(u_h,v)-l(v)|^2}{\nor{v}_V^2}.
\]
}

\frame{
Let $R_V: V \to V'$ be the isometric the Riesz map st.\
\[
\langle R_V v,\delta v\rangle_V \coloneqq(v, \delta v)_V, \quad \forall \delta v \in V.
\]
Then, our functional $J(u_h)$ is equal to
\begin{equation*}
\min_{u_h\in U_h} J(u_h) = \frac{1}{2}\left\|Bu_h-l\right\|_{V'}^2 =  \frac{1}{2}\left\|R_V^{-1}(Bu_h-l)\right\|_V^2.
\end{equation*}
First order optimality: G\^ateaux derivative is zero in all directions $\delta u \in U_h$
\begin{align*}
\left(R_V^{-1}(Bu_h-l),R_V^{-1}B\delta u\right)_V = 0, \quad \forall \delta u \in U. 
\end{align*}
}
\frame{
First order optimality: G\^ateaux derivative is zero in all directions $\delta u \in U_h$
\begin{align*}
\left(R_V^{-1}(Bu_h-l),R_V^{-1}B\delta u\right)_V &= 0,\\
\rightarrow \LRa{(Bu_h-l),R_V^{-1}B\delta u} &= 0, \\
\rightarrow b(u_h,R_V^{-1}B\delta u) - l(R_V^{-1}B\delta u) &= 0
\end{align*}
For $\delta u \in U$, we define the {\em optimal test function} $v_{\delta u}$
\begin{equation*}
v_{\delta u} \coloneqq R_V^{-1}B\delta u 
\end{equation*} 
such that $J(u_h)$ is minimized by the solution of
\[
b\LRp{u_h,v_{\delta u}} = l\LRp{v_{\delta u}}, \quad \forall \delta u \in U
\]
}
\frame{
\frametitle{Practical details of DPG}
\begin{itemize}
\item By choosing $V$ as a \emph{broken} test space, test functions can be determined locally.
\item In practice, $V \coloneqq V_h$, where $\dim(V_h) > \dim(U_h)$ elementwise, and test functions are approximated via solving
\[
\LRp{v_{\delta u},\delta v}_V = b(\delta u,\delta v).
\]
\end{itemize}
}

\frame{
\frametitle{Properties of DPG}
\begin{itemize}
\item Symmetric positive-definite stiffness matrix
\item DPG provides best approximation in energy norm 
\[
\|u\|_E = \|Bu\|_{V'} = \sup \frac{b(u,v)}{\nor{v}_V}.
\]
\item Actual energy error is computable through the residual
\[
\nor{u-u_h}_E = \nor{B(u-u_h)}_{V'} = \nor{R_V^{-1}(l-Bu_h)}_V = \nor{e}_V
\]
where $(e,\delta v)_V = l(v)-b(u_h,v)$ for all $v\in V$. 
\end{itemize}
}

%\frame{
%\frametitle{Duality of norms}
%Duality of norms: for any trial norm $\nor{u}_U$,
%\[
%\nor{u}_{U} = \sup_{v \in V}\frac{b\LRp{u,v}}{\nor{v}_{V,U}}, \quad \nor{v}_{V,U} = \sup_{u \in U}\frac%{b\LRp{u,v}}{\nor{u}_{U}}.
%\]
%Likewise, for any test norm $\nor{v}_V$, 
%\[
%\nor{v}_{V} = \sup_{u \in U}\frac{b\LRp{u,v}}{\nor{U}_{U,V}}, \quad \nor{u}_{U,V} = \sup_{v \in V}\frac%{b\LRp{u,v}}{\nor{v}_{V}}.
%\]
%
%}

\frame{
\frametitle{Ultra-weak formulation}
Given a first order system of equations $Au = f$, we identify the \emph{partition} $\Oh$ and \emph{mesh skeleton} $\Gh$
\[
\Oh = \cup_{j=1}^\Nel K_j, \quad \Gh = \cup_{j=1}^\Nel \partial K_j
\]
The ultra-weak formulation for $Au = f$ on $\Oh$ is
\[
b\left(\left(u, \widehat{u}\right),v\right) \coloneqq \langle \widehat{u}, \jump{v}
\rangle_{\Gh} - (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh}.
\]
where
\[
u\in L^2\LRp{\Oh} \equiv L^2(\Omega), \quad v\in V=D(A^*_h), \quad
\widehat{u}\in \gamma(D(A)),
\]
where $D(A_h^*)$ is the broken graph space of $A_h^*$, and $\gamma(D(A))$ the trace space of the graph space of operator $A$.
}

\frame{
\frametitle{Canonical norms for the ultra-weak formulation}
Under the ultra-weak formulation, we have the following relations:
\begin{figure}[!h]
\centering
\begin{tabular}{l c c}
Trial norm & & Test norm \\
\hline
$\boxed{\|u\|^2_{\L} + \|\widehat{u}\|^2}$ & $\Longrightarrow$  & $\|A_h^*v\|_{\L}^2
+\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},
  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2$ \\
%\hline
%Quasi-optimal trial norm & & Canonical test norm \\
%\hline
$\nor{u}_{\L}^2+\sup_{v } \left(\frac{\LRa{\widehat{u},
  \jump{v}}_{\Gh}}{\|v\|_V}\right)^2$ &  $\Longleftarrow$ & $\boxed{\|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2}$
\end{tabular}
\caption{The optimal \textit{test} norm is naturally derived by beginning with the canonical norm on the trial space, while the quasi-optimal \textit{trial} norm is derived from beginning with the canonical norm on the test space.}
\end{figure}
}

\section{A Robust DPG Method}

\frame{
\frametitle{Ultra-weak formulation for convection-diffusion}
In first order form, the convection-diffusion equation is
\[
A \LRp{u,\sigma} \coloneqq 
\LRs {
\begin{array}{c}
\div (\beta u - \sigma) \\ \frac{1}{\epsilon}\sigma - \grad u
\end{array}} = \LRs{
\begin{array}{c}
f \\ 0
\end{array}
}.
\]
The variational formulation is
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh}&\\
 - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n,\jump{v} }_{\Gh}&,
\end{align*}
where $\widehat{f}_n \coloneqq \beta_n u - \sigma_n$. Note that $\div$ and $\grad$ are taken to act elementwise.
}

\frame{
\frametitle{Quasi-optimal norm under convection-diffusion}
For convection-diffusion, the quasi-optimal test norm is 
\[
\|\left(v,\tau\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v
\|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 +
\|v\|_{L^2}^2 + \|\tau\|_{L^2}^2.
\]
Problem with this test norm: approximability of test functions.
\vspace{-.3cm}
\begin{figure}[!h]
\centering
\includegraphics[scale=.175]{figs/opt.png}
\caption{$v$ and $\tau$ components of the 1D optimal test functions for flux $\widehat{f}_n$ on the \emph{right-hand} side of a unit element for $\epsilon = 0.01$. }
\label{fig:optTestBoundary}
\end{figure}
}

\frame{
\frametitle{Determining an alternative test norm}
``Necessary'' conditions for robustness --- let $\boldsymbol U = \LRp{u,\sigma,\widehat{u},\widehat{f}_n}$, then, by choosing specific $\LRp{v,\tau}$, 
\[
\nor{u}^2_{L^2(\Omega)} = b\LRp{{\boldsymbol U},\LRp{v,\tau}} = \frac{b\LRp{{\boldsymbol U},\LRp{v,\tau}}}{\nor{\LRp{v,\tau}}_V} \nor{\LRp{v,\tau}}_V \leq \nor{\boldsymbol U}_E \nor{\LRp{v,\tau}}_V
\]
If $ \nor{\LRp{v,\tau}}_V \lesssim \|u\|_{L^2(\Omega)}$, then we have the robust bound
\[
\nor{u}^2_{L^2(\Omega)} \lesssim \nor{\boldsymbol U}_E
\]
}

\frame{
\frametitle{Bilinear forms and induced adjoints}
Recall 
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh}&\\
 - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n,\jump{v} }_{\Gh}&,
\end{align*}
We recover $\nor{u}_{L^2(\Omega)}$ by choosing continuous $\LRp{v,\tau}$ s.t.\
\begin{align*}
\div\tau - \beta \cdot \grad v   &= u\\
\frac{1}{\epsilon}\tau - \grad v &= 0
\end{align*}
where boundary conditions are s.t.\ $\LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh}$ and $\LRa{ \widehat{f}_n,\jump{v} }_{\Gh}$ vanish. 
}

\frame{
\frametitle{``Building blocks'' norm}
Test norm quantities are robustly bounded from above by $\nor{u}_{L^2(\Omega)}$.  
\[
\|\left(v,\tau\right)\|_{V,K}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2.
\]
Problem: boundary layers in optimal test functions:
\begin{figure}[!h]
\centering
\subfigure{\includegraphics[scale=.15]{figs/mesh1.png}}
\subfigure{\includegraphics[scale=.15]{figs/sol1.png}}
\caption{The $v$ component of the optimal test function corresponding to flux $\widehat{u} = x(1-x)$ on the bottom side of a unit element for $\epsilon = 0.01$.}
\label{fig:boundaryTest}
\end{figure}
}
\frame{
\frametitle{Mesh-scaled test norms}
%To avoid boundary layers in the optimal test functions, we scale the $L^2$ contributions of $v$ by $C_v(K)$, such that, when transformed to the reference element, both $C_v(K)\|v\|^2$ and $\epsilon\|\grad v\|^2$ are of the same magnitude. Similarly, we scale the $L^2$ contributions of $\tau$ by $C_\tau(K)$ such that $\frac{C_\tau(K)}{\epsilon} \|\tau\|^2$ and $\|\div \tau\|^2$ are of the same magnitude as well.

Our test norm, as defined over a single element $K$, is now
\begin{align*}
\|\left(v,\tau\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 +&\\
\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2&.
\end{align*}
%This modified test norm avoids boundary layers in the locally computed optimal test functions, but for adaptive meshes, provides additional stability in areas of heavy refinement, where the best approximation error tends to be large and stronger robustness is most necessary.  This leads to a test norm which produces easily approximable optimal test functions, but still provides \textit{asymptotically} the strongest test norm and tightest robustness results in the areas of highest error.

}

\frame{
\frametitle{Dirichlet inflow boundary condition}
Standard choice of boundary condition: $u = u_0$ on inflow boundary $\Gamma_{\rm in}$. 
\begin{figure}[h!]
\centering
\subfigure[Primal problem]{\includegraphics[scale=.2]{figs/primalDir.png}}
\subfigure[Adjoint problem]{\includegraphics[scale=.2]{figs/adjointDir.png}}
\caption{For the standard Dirichlet inflow condition, the solution to the adjoint problem can develop strong boundary layers at the outflow of the adjoint problem. }
\end{figure}
}

\frame{
\frametitle{New inflow boundary condition on $\widehat{f}_n$}
Non-standard choice of boundary condition: $\widehat{f}_n = \beta_n u_0$ on $\Gamma_{\rm in}$. 
\begin{figure}[h!]
\centering
\subfigure[Primal problem]{\includegraphics[scale=.2]{figs/primal.png}}
\subfigure[Adjoint problem]{\includegraphics[scale=.2]{figs/adjoint.png}}
\caption{Under the new inflow condition, the wall-stop boundary condition is relaxed to a zero-stress condition at the outflow boundary of the adjoint problem.}
\end{figure}
}

\frame{
\frametitle{Test norms and adjoint solutions}
\begin{itemize}
\item Standard choice of boundary condition: $u = u_0$ on inflow boundary $\Gamma_{\rm in}$: induces boundary layers in adjoint problems.
\item Non-standard choice of boundary condition: $\widehat{f}_n = \beta_n u_0$ on $\Gamma_{\rm in}$: induces smoother adjoint problems.
\end{itemize}

\textbf{Intuition:} the effectiveness of DPG under a test norm is governed by how a \textbf{specific test norm} measures the \textbf{solutions of the adjoint problem}. 
}

\frame{
\frametitle{Erickson-Johnson model problem}

}

\frame{
\frametitle{Numerical experiments}

}
\frame{
More regularized solutions. 
}

\section{Proposed Work}
\frame{
\frametitle{DPG for nonlinear problems}

}
\frame{
\frametitle{Burgers' equation as an example}

}
\frame{
Results for Burgers

}

\frame{
\frametitle{Compressible Navier-Stokes equations}
\begin{align*}
\div \vecttwo{\rho u }{\rho v} &= 0\\
\div \left(\vecttwo{\rho u^2+p }{\rho u v} - \boldsymbol \sigma_{1}\right) &=0\\
\div \left(\vecttwo{\rho u v}{\rho v^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
\div \left(\vecttwo{((\rho e)+p)u}{((\rho e)+p)v} - \boldsymbol\sigma \mathbf{u} + \vec{q}\right) &=0\\
\frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I &= \grad \mathbf{u} - \Reyn \, {\boldsymbol \omega}\\
\frac{1}{\kappa}\vec{q} &= \grad T
\end{align*}
}
\frame{
$\boldsymbol\sigma$ is a Newtonian fluid $\sigma_{ij} = \mu(u_{i,j} + u_{j,i}) + \lambda u_{k,k} \delta_{ij}$.
%We can invert the stress tensor under isotropic and plane strain assumptions to get
\[
\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \frac{1}{2\mu} \sigma_{ij} - \frac{\lambda}{4\mu (\mu + \lambda)} \sigma_{kk}\delta_{ij}
\]
We also have
\[
\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \grad  U - \boldsymbol \omega
\]
%where $\boldsymbol \omega$ is the antisymmetric part of the infinitesimal strain tensor:
%\[
%\boldsymbol \omega = \frac{1}{2}\left(\grad  U - \grad ^T  U\right).
%\]
Our final form is
\begin{align*}
\grad  U - \boldsymbol \omega = \frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I.
\end{align*}
Taking the antisymmetric part implicitly defines $\boldsymbol \omega$ to be the antisymmetric part of $\grad u$. 
}

\frame{
\frametitle{Extrapolation of test norms}
%\begin{columns}
%\begin{column}{.48\textwidth}
Convection-diffusion:
\begin{align*}
\div \left(\beta u - \sigma\right) &= f\\
\frac{1}{\epsilon}\sigma - \grad u &= 0.
\end{align*}
Navier-Stokes:%vectors of test functions  $v=\{v_1,v_2,v_3,v_4\}$, $W = \{\tau_1,\tau_2,\tau_3\}$. Similarly, we group our Eulerian and stress variables into the vector variables $U$ and $\Sigma$.  $R_{\rm Euler}(U,\Sigma)$ and $R_{\rm visc}(U,\Sigma)$ are Eulerian and viscous nonlinear residuals, our formulation for the linearized Navier-Stokes equations can be written as
\begin{align*}
\div \left(A_{\rm Euler}U - A_{\rm visc}\Sigma\right) &= R_{\rm Euler}(U,\Sigma)\\
E_{\rm visc} \Sigma - \grad U &= R_{\rm visc}(U,\Sigma)
\end{align*}
}

\frame{
Convection-diffusion:
\begin{align*}
\|\left(v,\tau\right)\|_{V,K}^2 =& \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 \\
&+\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
\end{align*}

Navier-Stokes:
\begin{align*}
\|\left(V,W\right)\|_{V,K}^2 =& \min\left\{\frac{\Reyn}{|K|},1\right\}\|v\|^2 + \frac{1}{\Reyn} \|A_{\rm visc}^T\grad v\|^2 + \|A_{\rm Euler}^T \grad v\|^2 \\
& + \| \div W\|^2 + \min\left\{\Reyn,\frac{1}{|K|}\right\}\|E_{\rm visc}^T\tau\|^2.
\end{align*}
%An advantage of this extrapolation approach is that the incompletely parabolic nature of the Navier-Stokes equation is taken into account; there is no diffusive term present in the mass conservation equation, and the test norm reflects that by requesting only limited regularity of $v_1$.\footnote{The situation is analogous to using the full $H^1(\Oh)$ norm for the pure convection equation --- the optimal test norm $\nor{v}_V = \nor{\beta\cdot \grad v} + \nor{v}$ implies only streamline regularity, whereas taking $\nor{v}_V = \nor{\grad v} + \nor{v}$ implies stronger regularity on the test space $V$ than the graph norm. Consequently, convergence is suboptimal for DPG applied to the convection problem under the $H^1(\Oh)$ test norm.}
%\end{column}
%\end{columns}
}
\frame{
\frametitle{Carter plate and Boundary conditions}

\begin{figure}[!h]
\centering
\includegraphics[scale=.35]{figs/flat_plate_BCs.pdf}
\caption{Carter flat plate problem.}
\end{figure}
\begin{itemize}
\item{} Inflow and stress boundary conditions, momentum flux boundary conditions. 
\item{} No outflow condition set.
\end{itemize}
}
\frame{
\frametitle{Refinement level 0}
\begin{figure}
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/Re1000p2/u10.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/Re1000p2/T0.png}}
\subfigure{\includegraphics[scale = .35]{figs/Re1000p2/mesh0.png}}
\end{figure}
}
\frame{
\frametitle{Refinement level 1}
\begin{figure}
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/Re1000p2/u11.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/Re1000p2/T1.png}}
\subfigure{\includegraphics[scale = .35]{figs/Re1000p2/mesh1.png}}
\end{figure}
}
\frame{
\frametitle{Refinement level 2}
\begin{figure}
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/Re1000p2/u12.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/Re1000p2/T2.png}}
\subfigure{\includegraphics[scale = .35]{figs/Re1000p2/mesh2.png}}
\end{figure}
}
\frame{
\frametitle{Refinement level 3}
\begin{figure}
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/Re1000p2/u13.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/Re1000p2/T3.png}}
\subfigure{\includegraphics[scale = .35]{figs/Re1000p2/mesh3.png}}
\end{figure}
}
\frame{
\frametitle{Refinement level 4}
\begin{figure}
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/Re1000p2/u14.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/Re1000p2/T4.png}}
\subfigure{\includegraphics[scale = .35]{figs/Re1000p2/mesh4.png}}
\end{figure}
}
\frame{
\frametitle{Refinement level 5}
\begin{figure}
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/Re1000p2/u15.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/Re1000p2/T5.png}}
\subfigure{\includegraphics[scale = .35]{figs/Re1000p2/mesh5.png}}
\end{figure}
}
\frame{
\frametitle{Refinement level 6}
\begin{figure}
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/Re1000p2/u16.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/Re1000p2/T6.png}}
\subfigure{\includegraphics[scale = .35]{figs/Re1000p2/mesh6.png}}
\end{figure}
}

\frame{
\frametitle{Proposed work: Area A}

}
\frame{
\frametitle{Proposed work: Area B}

}
\frame{
\frametitle{Proposed work: Area C}

}
\end{document}

### 2012-07-19 docs/Jesse/Proposal/proposalPres.tex
adding proposal changes

@@
 \useinnertheme{rectangles}
+
+\setbeamercovered{dynamic}
 
@@
 \frametitle{Convection-diffusion as a model problem}
+\vspace{-.5cm}
 \[
@@
 \]
-}
-\frame{
-\frametitle{Dealing with stability/robustness}
-Convection-diffusion equation in 1D is $\beta u' - \epsilon u'' = f$.
-%\vspace{-.5cm}
+\vspace{-.5cm}
 \begin{columns}[c]
 \begin{column}{.49\textwidth}
-Standard continuous Galerkin variational formulation: solve
+In 1D: $\beta u' - \epsilon u'' = f$. Standard continuous Galerkin variational formulation: solve
 \[
@@
 \frame{
+\frametitle{Stabilization}
 Historical stabilization methods: 
@@
 \frame{
-\frametitle{Minimum residual methods through optimal testing}
+\frametitle{Minimum residual methods and optimal testing}
 Identify $B:U\rightarrow V'$ such that
@@
 
-\frame{
+\begin{frame}
 Let $R_V: V \to V'$ be the isometric the Riesz map st.\
@@
 \begin{align*}
-\left(R_V^{-1}(Bu_h-l),R_V^{-1}B\delta u\right)_V = 0, \quad \forall \delta u \in U. 
-\end{align*}
-}
-\frame{
-First order optimality: G\^ateaux derivative is zero in all directions $\delta u \in U_h$
-\begin{align*}
-\left(R_V^{-1}(Bu_h-l),R_V^{-1}B\delta u\right)_V &= 0,\\
+\left(R_V^{-1}(Bu_h-l),R_V^{-1}B\delta u\right)_V &= 0, \quad \forall \delta u \in U.\\
 \rightarrow \LRa{(Bu_h-l),R_V^{-1}B\delta u} &= 0, \\
@@
 \end{align*}
+\end{frame}
+
+\frame{
 For $\delta u \in U$, we define the {\em optimal test function} $v_{\delta u}$
@@
 \frame{
-\frametitle{Practical details of DPG}
+\frametitle{Details and properties of DPG}
 \begin{itemize}
@@
 \]
+\item Symmetric positive-definite stiffness matrix: for $B_{ji} = b(u_j,v_i)$, $l_i = l(v_i)$ for $v_i$ spanning $V_h$, DPG solves
+\[
+u^T B^T R_V^{-1}B = l R_V^{-1}B 
+\]
 \end{itemize}
+
 }
@@
 \frame{
-\frametitle{Properties of DPG}
 \begin{itemize}
-\item Symmetric positive-definite stiffness matrix
-\item DPG provides best approximation in energy norm 
+\item DPG provides the best approximation in the energy norm 
 \[
@@
 \]
-\item Actual energy error is computable through the residual
+\item The actual energy error is computable through the residual
 \[
@@
 \frametitle{Ultra-weak formulation}
-Given a first order system of equations $Au = f$, we identify the \emph{partition} $\Oh$ and \emph{mesh skeleton} $\Gh$
-\[
-\Oh = \cup_{j=1}^\Nel K_j, \quad \Gh = \cup_{j=1}^\Nel \partial K_j
-\]
+\vspace{-.75cm}
+\begin{columns}
+\begin{column}{.65\textwidth}
+Given a first order system $Au = f$, we identify the \textbf{\emph{partition}} $\Oh$ and \textbf{\textcolor{red}{mesh skeleton}} \textcolor{red}{$\Gh$}.
+\end{column}
+\begin{column}{.33\textwidth}
+%\[
+%\Oh = \cup_{j=1}^\Nel K_j, \quad \Gh = \cup_{j=1}^\Nel \partial K_j
+%\]
+\begin{figure}[!h]
+\centering
+\includegraphics[scale = .155]{mesh_skel.pdf}
+\end{figure}
+\end{column}
+\end{columns}
+\vspace{-.5cm}
 The ultra-weak formulation for $Au = f$ on $\Oh$ is
@@
 \frame{
-\frametitle{Determining an alternative test norm}
-``Necessary'' conditions for robustness --- let $\boldsymbol U = \LRp{u,\sigma,\widehat{u},\widehat{f}_n}$, then, by choosing specific $\LRp{v,\tau}$, 
-\[
-\nor{u}^2_{L^2(\Omega)} = b\LRp{{\boldsymbol U},\LRp{v,\tau}} = \frac{b\LRp{{\boldsymbol U},\LRp{v,\tau}}}{\nor{\LRp{v,\tau}}_V} \nor{\LRp{v,\tau}}_V \leq \nor{\boldsymbol U}_E \nor{\LRp{v,\tau}}_V
-\]
-If $ \nor{\LRp{v,\tau}}_V \lesssim \|u\|_{L^2(\Omega)}$, then we have the robust bound
-\[
-\nor{u}^2_{L^2(\Omega)} \lesssim \nor{\boldsymbol U}_E
-\]
-}
-
-\frame{
 \frametitle{Bilinear forms and induced adjoints}
-Recall 
+Recall the convection-diffusion bilinear form
 \begin{align*}
@@
 where boundary conditions are s.t.\ $\LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh}$ and $\LRa{ \widehat{f}_n,\jump{v} }_{\Gh}$ vanish. 
+}
+
+\frame{
+\frametitle{Determining an alternative test norm}
+``Necessary'' conditions for robustness --- let $\boldsymbol U = \LRp{u,\sigma,\widehat{u},\widehat{f}_n}$, then, by choosing specific $\LRp{v,\tau}$, 
+\[
+\nor{u}^2_{L^2(\Omega)} = b\LRp{{\boldsymbol U},\LRp{v,\tau}} = \frac{b\LRp{{\boldsymbol U},\LRp{v,\tau}}}{\nor{\LRp{v,\tau}}_V} \nor{\LRp{v,\tau}}_V \leq \nor{\boldsymbol U}_E \nor{\LRp{v,\tau}}_V
+\]
+If $ \nor{\LRp{v,\tau}}_V \lesssim \|u\|_{L^2(\Omega)}$, then we have the robust bound
+\[
+\nor{u}^2_{L^2(\Omega)} \lesssim \nor{\boldsymbol U}_E
+\]
 }
@@
 \end{align*}
+\begin{itemize}
+\item $v$ and $\tau$ decoupled.
+\item Coefficients are $O(1)$ after transforming to the unit element.
+\end{itemize}
 %This modified test norm avoids boundary layers in the locally computed optimal test functions, but for adaptive meshes, provides additional stability in areas of heavy refinement, where the best approximation error tends to be large and stronger robustness is most necessary.
 This leads to a test norm which produces easily approximable optimal test functions, but still provides \textit{asymptotically} the strongest test norm and tightest robustness results in the areas of highest error.
-
 }
@@
 \centering
-\subfigure[Primal problem]{\includegraphics[scale=.2]{figs/primalDir.png}}
-\subfigure[Adjoint problem]{\includegraphics[scale=.2]{figs/adjointDir.png}}
+\subfigure[Primal problem]{\includegraphics[scale=.22]{figs/primalDir.png}}
+\subfigure[Adjoint problem]{\includegraphics[scale=.22]{figs/adjointDir.png}}
 \caption{For the standard Dirichlet inflow condition, the solution to the adjoint problem can develop strong boundary layers at the outflow of the adjoint problem. }
 \end{figure}
+
 }
@@
 \centering
-\subfigure[Primal problem]{\includegraphics[scale=.2]{figs/primal.png}}
-\subfigure[Adjoint problem]{\includegraphics[scale=.2]{figs/adjoint.png}}
+\subfigure[Primal problem]{\includegraphics[scale=.22]{figs/primal.png}}
+\subfigure[Adjoint problem]{\includegraphics[scale=.22]{figs/adjoint.png}}
 \caption{Under the new inflow condition, the wall-stop boundary condition is relaxed to a zero-stress condition at the outflow boundary of the adjoint problem.}
@@
 \end{itemize}
-
 \textbf{Intuition:} the effectiveness of DPG under a test norm is governed by how a \textbf{specific test norm} measures the \textbf{solutions of the adjoint problem}. 
@@
 \frame{
-\frametitle{Erickson-Johnson model problem}
+\frametitle{Erikkson-Johnson model problem}
+
+On domain $\Omega = [0,1]^2$, with $\beta = (1,0)^T$, $ f = 0$ and boundary conditions
+\begin{align*}
+\widehat{\beta_nu - \sigma_n} &= \widehat{f_n} = u_0, \quad \beta_n \leq 0\\
+\widehat{u} &= 0, \quad \beta_n > 0
+\end{align*}
+
+Separation of variables gives an analytic solution. 
+%\[
+%u(x,y) = C_0 + \sum_{n=1}^\infty C_n \frac{\exp(r_2(x-1)-\exp(r_1(x-1)))}{r_1\exp(-r2) - r_2\exp(-r1)}\cos(n\pi y)
+%\]
+\begin{figure}
+\centering
+\subfigure{
+\includegraphics[scale=.24]{figs/wallBC_exact_u.png}
+}
+\subfigure{
+\includegraphics[scale=.24]{figs/wallBC_exact_sigx.png}
+}
+\subfigure{
+\includegraphics[scale=.24]{figs/wallBC_exact_sigy.png}
+}
+\caption{Solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
+\end{figure}
 
@@
 \frame{
-\frametitle{Numerical experiments}
+\frametitle{Error rates}
+\begin{figure}
+\centering
+\subfigure{
+\includegraphics[scale=.23]{figs/errorrates_wallBC.png}
+}
+\subfigure{
+\includegraphics[scale=.23]{figs/L2energyratio_wallBC.png}
+}
+\subfigure{
+\includegraphics[scale=.22]{figs/u_pointdiff_wallBC.png}
+}
+\caption{$L^2$/energy error, their ratio, and pointwise error in $u$ for $\epsilon = .01$.}
+\end{figure}
 
 }
+%\frame{
+%\frametitle{Regularization}
+%Discontinuous inflow conditions on $\widehat{f_n}$, out of alignment with mesh. Boundary condition $\epsilon \grad u \cdot n = 0$ at outflow.
+%\begin{figure}
+%\centering
+%\subfigure{
+%\includegraphics[scale=.33]{figs/discontinuous.png}
+%}
+%\subfigure{
+%\includegraphics[scale=.305]{figs/discontinuousL2rates.png}
+%}
+%\caption{Discontinuous hat inflow data with $\epsilon = 1e-5$, convection solution errors.}
+%\end{figure}
+%}
+
 \frame{
-More regularized solutions. 
+\frametitle{Regularization}
+For $\beta = (-y,x)^T$ on $\Omega = [-1,1]^2$, and zero normal stress outflow conditions. Ill posed in the convection setting. Similar tests have been done with discontinuous data.
+
+\begin{figure}
+\centering
+\subfigure{
+\includegraphics[scale=.34]{figs/vortex.png}
+}
+\subfigure{
+\includegraphics[scale=.34]{figs/vortexMesh.png}
+}
+\caption{Steady-state vortex problem with $\epsilon = 1e-5$.}
+\end{figure}
+\vspace{-.25cm}
 }
@@
 \frametitle{DPG for nonlinear problems}
-
+\textcolor{red}{REWORK. HOW TO DO THIS SECTION?}
+Begin with the nonlinear variational formulation
+$b(u,v) = l(v)$, linear in $v$, but not in $u$.  An appropriate linearization gives
+\[
+b_u(\Delta u,v) = l(v) - b(u,v),
+\]
+Let $B(u)$ and $B_u\Delta u$ be the variational operators associated with $b(u,v)$ and $b_u(\Delta u,v)$. 
+\begin{align*}
+\|\Delta u\|_E &\coloneqq \nor{B_u\Delta u}_{V'} = \nor{R_V^{-1} B_u\Delta u}_V \\
+\nor{R(u)}_E &\coloneqq \nor{B(u)-l}_E = \nor{B(u) - l}_{V'}  = \nor{R_V^{-1} B(u)-l}_V 
+\end{align*}
 }
+%\frame{
+%\frametitle{Burgers' equation as an example}
+%
+%}
 \frame{
-\frametitle{Burgers' equation as an example}
-
-}
-\frame{
-Results for Burgers
-
+\frametitle{Burgers equation}
+\begin{columns}
+\begin{column}{.48\textwidth}
+\vspace{-.5cm}
+\[
+\pd{\left(u^2/2\right)}{x} + \pd{u}{y} + \epsilon \Delta u = f
+\]
+Burgers equation can be written with $\beta(u) = \LRp{u/2,1}$
+\begin{align*}
+\div\left(\beta(u)u-\sigma\right) &=f \\
+\frac{1}{\epsilon}\sigma - \grad u &=0.
+\end{align*}
+i.e.\ nonlinear convection-diffusion.
+\end{column}
+\begin{column}{.48\textwidth}
+\begin{figure}[!h]
+\centering
+\includegraphics[scale = .35]{figs/burgers1e4.png}
+\caption{Shock solution for Burgers' equation, $\epsilon = 1e-4$.}
+\end{figure}
+\end{column}
+\end{columns}
 }
@@
 \end{align*}
+where $R_{\rm Euler}(U,\Sigma)$ and $R_{\rm visc}(U,\Sigma)$ are the Eulerian/viscous residuals.
 }
@@
 
-Navier-Stokes:
+Navier-Stokes: let $V$ and $W$ be vectors of test functions $v_i$ and $\tau_i$.
 \begin{align*}
-\|\left(V,W\right)\|_{V,K}^2 =& \min\left\{\frac{\Reyn}{|K|},1\right\}\|v\|^2 + \frac{1}{\Reyn} \|A_{\rm visc}^T\grad v\|^2 + \|A_{\rm Euler}^T \grad v\|^2 \\
-& + \| \div W\|^2 + \min\left\{\Reyn,\frac{1}{|K|}\right\}\|E_{\rm visc}^T\tau\|^2.
+\|\left(V,W\right)\|_{V,K}^2 =& \min\left\{\frac{1}{\Reyn|K|},1\right\}\nor{V}^2 + \frac{1}{\Reyn} \nor{A_{\rm visc}^T\grad V}^2 + \nor{A_{\rm Euler}^T \grad V}^2 \\
+& + \nor{\div W}^2 + \min\left\{1,\frac{1}{\Reyn|K|}\right\}\nor{E_{\rm visc}^TW}^2.
 \end{align*}
@@
 
+\section{Area A}
 \frame{
 \frametitle{Proposed work: Area A}
+\begin{itemize}
+\item{\textbf{Completed: Prove robustness of DPG method for the scalar convection-diffusion problem.}}
 
+We have introduced a test norm under which the DPG method robustly bounds the $L^2$ error in the field variables $u$ and the scaled stress $\sigma$.
+Numerical results confirm the theoretical bounds given.
+
+\item{\textbf{Proposed: Attempt analysis of the linearized Navier-Stokes system.}}
+
+We hope to analyze the linearized Navier-Stokes equations to determine an optimal extrapolation of the test norm for the scalar convection-diffusion problem to systems.
+
+\end{itemize}
 }
+
+\subsection{Area B}
+
 \frame{
 \frametitle{Proposed work: Area B}
+\begin{itemize}
+\item{\textbf{Completed: Collaborative work with Nathan Roberts on the higher order parallel adaptive DPG code Camellia.}}
 
+Numerical experiments have been done using the higher-order adaptive codebase Camellia, built upon the Trilinos library and designed by Nathan Roberts.
+%The framework for arbitrary-irregularity anisotropic refinements in both $h$ and $p$ is in place, and the code is partially parallelized.
+
+\item{\textbf{Proposed: Anisotropic refinements and $hp$-schemes.}}
+
+The error representation function has been shown to yield an effective and natural residual with which to drive refinement, which we hope to generalize to yield anisotropic adaptive schemes. 
+\textcolor{red}{GET GRAPHICS FOR ANISOTROPY}
+\end{itemize}
 }
+
 \frame{
-\frametitle{Proposed work: Area C}
+\textbf{Proposed: Distributed iterative static condensation.}
+\[
+Ku = \arr{A}{B}{B^T}{D}\vecttwo{u_{\rm flux}}{u_{\rm field}} = \vecttwo{f}{g} = l
+\]
+where $D$ has a block-diagonal structure. The system can be reduced to yield the condensed system
+\[
+\left(A-B D^{-1} B^T\right)u_{\rm flux} = f - B D^{-1} g
+\]
+where $D^{-1}$ can be inverted block-wise. For FE stiffness matrices under the Laplace equation, the Schur complement has reduced condition number of $O(h^{-1})$ as opposed to $O(h^{-2})$. 
+}
 
+\frame{  
+\textbf{Proposed: a Nonlinear Hessian-based DPG method.}
+Given a nonlinear variational problem $b(u,v) = l(v)$, linear in $v$ but not in $u$, beginning with the \textit{nonlinear} dual residual 
+\[
+J(u_h) = \frac{1}{2}\|B(u_h)-l\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(u_h,v)-l(v)|^2}{\nor{v}_V^2}.
+\]
+produces a Hessian-based DPG method 
+\[
+b_u(\Delta u,v) + b''(\Delta u, \delta u, v_{R(u)}) = r(u,v) = l(v) - b(u,v),
+\]
+which aims to minimize the nonlinear dual residual instead of the linearized problem residual. 
+}
+
+\section{Area C}
+\frame{
+\frametitle{Proposed work: Area C}\
+textcolor{red}{GET GRAPHICS FOR EACH}
+\begin{itemize}
+\item{\textbf{Completed: convection-dominated diffusion, Burgers, and a model problem for Navier-Stokes.}} 
+\item{\textbf{Proposed: Range of Reynolds/Mach numbers, ramp problem, Gaussian bump.}}
+\item{\textbf{Proposed: regularized Euler.}}
+\end{itemize}
 }

### 2012-07-24 docs/Jesse/PECOStalk/CFD_intro.tex
adding pecos talk

--- 2012-06-19 docs/Jesse/Proposal/proposalIntro.tex
@@
-\section{Motivations}
-
-Over the last three decades, Computational Fluid Dynamics (CFD) simulations have become commonplace as a tool in the engineering and design of high-speed aircraft.
-Wind tunnel experiments are often complemented by computational simulations, and CFD technologies have proved very useful in both the reduction of aircraft development cycles, and in the simulation of conditions difficult to reproduce experimentally.
-Great advances have been made in the field since its introduction, especially in areas of meshing, computer architecture, and solution strategies.
-Despite this, there still exist many computational limitations in existing CFD methods:
-\begin{itemize}
-\item \textbf{Higher order methods :} Higher order methods stand to offer large computational savings through a more efficient use of discrete degrees of freedom.
-However, there are very few working higher-order CFD codes in existence, and most higher order methods tend to degrade to first-order accuracy near shocks.
-The use of higher order codes to solve the steady state equations is even rarer, where convergence of discrete nonlinear steady equations is a tricky issue \cite{BoeingHigherOrder}.
-\item \textbf{Automatic adaptivity :} The use of adaptive meshes is crucial to many CFD applications, where the solution often exhibits very localized sharp gradients and shocks.
-Good resolution for such problems under uniform meshes is computationally prohibitive and impractical for most physical regimes of interest.
-However, the construction of ``good" meshes is a difficult task, usually requiring a-priori knowledge of the form of the solution \cite{andersonCFDBook}.
-An alternative to such is the construction of automatically adaptive schemes; such methods usually begin with a coarse mesh and refine based on the minimization of some error.
-However, this task is difficult, as the convergence of numerical methods for problems in CFD is notoriously sensitive to mesh quality.
-Additionally, the use of adaptivity becomes even more difficult in the context of higher order and $hp$ methods \cite{BoeingHigherOrder}.
-\end{itemize}
-Both of these issues are tied to the notion of \emph{robustness}.
-We define robustness loosely as the degradation of the quality of numerical solutions with respect to a given problem parameter.
-In the context of CFD, the parameter of interest is the Reynolds number (the nondimensional equivalent of viscosity) --- for typical physical conditions of interest for the compressible Navier-Stokes equations, the Reynolds number is extremely high, on the order of 1e7, yielding solutions with two vastly different scales - inviscid phenomena at an $O(1)$ scale, and $O(1e-7)$ viscous phenomena.
-
-The full Navier-Stokes equations are not well understood in a mathematical sense --- in order to more clearly illustrate the issue of robustness for problems in CFD, we will study first the important model problem of convection-dominated diffusion.
-
-\subsection{Singular perturbation problems and robustness}
-
-%Historically, the Galerkin method has been very successfully applied to a broad range of problems in solid mechanics, for which the variational problems resulting from the PDE are symmetric and coercive (positive-definite).
-It is well known that the finite element method produces optimal or near-optimal results for such problems, with the finite element solution matching or coming close to the best approximation of the solution in the finite element space.
-However,
-
-Standard numerical methods tend to perform poorly across the board for the class of PDEs known as singular perturbation problems.
-These problems are often characterized by a parameter that may be either very small or very large in the context of physical problems.
-An additional complication of singular perturbation problems is that very often, in the limiting case of the parameter blowing up or decreasing to zero, the PDE itself will change types (e.g.\ from elliptic to hyperbolic).
-A canonical example of a singularly perturbed problem is the convection-diffusion equation on domain $\Omega \in \mathbb{R}^3$,
-\[
-\div \left(\beta u\right) - \epsilon \Delta u = f.
-\]
-The equation represents the change in the scalar quantity $u$, representing the concentration of a quantity in a given medium, taking into account both convective and diffusive effects.
-$\beta \in \mathbb{R}^3$ specifies the direction and magnitude of convection, while the singular perturbation parameter $\epsilon$ represents the diffusivity of the medium.
-In the limit of an inviscid medium as $\epsilon\rightarrow 0$, the equation changes types, from elliptic to hyperbolic, and from second order to first order.
-
-We will illustrate the issues associated with numerical methods for this equation using one dimensional examples.  In 1D, the convection-diffusion equation is
-\begin{align*}
-\beta u'-\epsilon u'' &= f.
-\end{align*}
-For Dirichlet boundary conditions $u(0)=u_0$ and $u(1)= u_1$, the solution can develop sharp boundary layers of width $\epsilon$ near the outflow boundary $x=1$.
-
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.4]{figs/GalerkinOscTight.png}
-\caption{Oscillations in the 1D finite element solution of the convection-diffusion equation for small diffusion \cite{GalerkinOsc}.
-Standard finite volume and finite difference methods exhibit similar behavior.}
-\label{fig:GalerkinOsc}
-\end{figure}
-We consider for now the Galerkin finite element method as applied to convection-dominated diffusion.
-Standard finite element methods (as well as standard finite volume and finite difference methods) perform poorly for the case of small $\epsilon$.
-The poor performance of the finite element method for this problem is reflected in the bound on the error in the finite element solution --- under the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}:
-\[
-\|u-u_h\|_\epsilon \leq C \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
-\]
-for $\|u\|_\epsilon^2 \coloneqq \|u\|_{L^2}^2 + \epsilon \|u'\|_{L^2}^2$, with $C$ independent of $\epsilon$. An alternative formulation of the above bound is 
-\[
-\|u-u_h\|_{H^1(0,1)} \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
-\]
-where $C(\epsilon)$ grows as $\epsilon\rightarrow 0$.
-The dependence of the constant $C$ on $\epsilon$ is what we refer to as a \textit{loss of robustness} --- as the singular perturbation parameter $\epsilon$ decreases, our finite element error is bounded more and more loosely by the best approximation error.
-As a consequence, the finite element solution can diverge significantly from the best finite element approximation of the solution for very small values of $\epsilon$.
-For exam ple, Figure~\ref{fig:GalerkinOsc} shows an example of how, on a coarse mesh, and for small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation with a boundary layer develops spurious oscillations everywhere in the domain, even where the best approximation error is small.
-These oscillations grow in magnitude as $\epsilon \rightarrow 0$, eventually polluting the entire solution.
-
-\section{Goal}
-
-From the perspective of the full Navier-Stokes equations, this loss of robustness is doubly problematic.
-Not only will any nonlinear solution suffer from similar non-physical oscillations, but nonlinear solvers themselves may fail to yield a solution due to such instabilities --- a nonlinear solution is almost always computed by solving a series of linear problems whose solutions will converge to the nonlinear solution under appropriate assumptions, and the presence of such oscillations in each linear problem can cause the solution convergence to slow significantly or even diverge.
-
-Our goal is to develop a \emph{stable, higher order adaptive scheme} for the steady compressible laminar Navier-Stokes equations in transonic/supersonic regimes that is \emph{robust for very small viscosity}.
-In particular, we hope to present a method for which $hp$-adaptivity can be applied to problems in compressible flow.
-
-\section{Literature review}
-
-For the past half-century, problems in CFD have been solved using a multitude of methods, many of which are physically motivated, and thus applicable only to a small number of problems and geometries.
-We consider more general methods, whose framework is applicable to different problems in CFD; however, our specific focus will be on the nonlinear shock problems of compressible aerodynamics.
-Broadly speaking, the most popular general methods include (in historical order) finite difference methods, finite volume methods, and finite element methods.
-
-\subsection{Finite difference and finite volume methods}
-
 For linear problems, finite difference (FD) methods approximate derivatives based on interpolation of pointwise values of a function.
@@
 For nonlinear shock problems, the solution often exhibits sharp gradients or discontinuities, around which the solution would develop spurious Gibbs-type oscillations.
-Several ideas were introduced to deal with oscillations in the solution near a sharp gradient or shock: artificial diffusion, total variation diminishing (TVD) schemes, and slope limiters.
+Several ideas were introduced to deal with oscillations in the solution near a sharp gradient or shock: artificial viscosity parameters, total variation diminishing (TVD) schemes, and slope limiters.
 However, each method had its drawback, either in terms of loss of accuracy, dimensional limitations, or problem-specific parameters to be tuned \cite{Shu:Lectures}.
@@
 WENO remains a popular choice today for both finite volume and finite difference schemes.
-Most of these methods can be interpreted as adding some specific artificial diffusion to the given numerical scheme.
-We refer to such schemes as \emph{modified equation} methods, as the exact solution no longer satisfies the discrete system due to the presence of additional artificial diffusion.
 
 Historically, finite volumes and finite difference methods have been the numerical discretizations of choice for CFD applications; the simplicity of implementation of the finite difference method allows for quick turnaround time, and the finite volume method is appealing due to its locally conservative nature and flexibility.
-More recently, the finite element (FE) method has gained popularity as a discretization method for CFD applications for its stability properties and rigorous mathematical foundations.
+More recently, the finite element method (FEM) has gained popularity as a discretization method for CFD applications for its stability properties and rigorous mathematical foundations.
 Early pioneers of the finite element method for CFD included Zienkiewicz, Oden, Karniadakis, and Hughes \cite{ChungCFDBook}.
 
-\subsection{Stabilized finite element methods}
-
-The finite element/Galerkin method has been widely utilized in engineering to solve partial differential equations governing the behavior of physical phenomena in engineering problems.
-The method relates the solution of a partial differential equation (PDE) to the solution of a corresponding variational problem.
-The finite element method itself provides several advantages --- a framework for systematic mathematical analysis of the behavior of the method, weaker regularity constraints on the solution than implied by the strong form of the equations, and applicability to very general physical domains and geometries for arbitrary orders of approximation.
-
-Historically, the Galerkin method has been very successfully applied to a broad range of problems in solid mechanics, for which the variational problems resulting from the PDE are symmetric and coercive (positive-definite).
-It is well known that the finite element method produces optimal or near-optimal results for such problems, with the finite element solution matching or coming close to the best approximation of the solution in the finite element space.
-However, standard Galerkin methods tend to perform poorly for singular perturbation problems, developing instabilities when the singular perturbation parameter is very small.
-
-Traditionally, instability/loss of robustness in finite element methods has been dealt with using residual-based stabilization techniques.
-Given some variational form, the problem is modified by adding to the bilinear form the strong form of the residual, weighted by a test function and scaled by a stabilization constant $\tau$.
-The most well-known example of this technique is the streamline-upwind Petrov-Galerkin (SUPG) method, which is a stabilized FE method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.
-SUPG stabilization not only removes the spurious oscillations from the finite element solution of the convection-diffusion equation, but delivers the best finite element approximation in the $H^1$ norm.
-
-\subsubsection{SUPG}
-
-All Galerkin methods involve both trial (approximating) and test (weighting) functions.
-Standard Galerkin methods, where these trial and test functions are taken from the same space, are referred to as Bubnov-Galerkin methods.
-A Petrov-Galerkin method refers to any Galerkin method other than a classical Bubnov-Galerkin method.
-The Streamline Upwind Petrov Galerkin (SUPG) method is a stabilization method for $H^1$-conforming finite elements, the idea of which was originally motivated by artificial diffusion techniques in finite differences.
-In particular, for the homogeneous 1D convection-diffusion equation, it is possible to recover, under a finite difference method, the exact solution at nodal points by adding an ``exact" artificial diffusion based on the mesh size $h$ and the magnitudes of the convection $\beta$ and the viscosity $\epsilon$.
-
-The idea of ``exact" artificial viscosity was adapted to finite elements not through the direct modification of the equations, but through the test functions and weighting of the residual.
-In particular, finite element and Galerkin methods are often referred to as ``weighted residual" methods, since the starting point of both is to multiply the residual by a particular test, or weighting, function.
-Standard Bubnov-Galerkin methods simply choose these weighting functions to be the same as the the basis functions used to approximate the solution.
-
-We will introduce the SUPG method at an abstract level for illustrative purposes only.
-Further details and perspectives on the SUPG method can be found in \cite{SUPG}, as well as in an upcoming book by Hughes.
-The convection-diffusion equation can be written as follows:
-\[
-Lu = \left(L_{\rm adv} + L_{\rm diff} \right) u = f,
-\]
-where $L_{\rm adv}u \coloneqq \div \left(\beta u\right)$ is the first order advective operator, and $L_{\rm diff}u \coloneqq \epsilon \Delta u$ is the second-order diffusive operator (then, roughly speaking, $L_{\rm diff} u = 0$).
-Let us assume $u$ to be a linear combination of piecewise-linear basis functions $\phi_i, i = 0,\ldots,N$.
-The SUPG method is then to solve
-\[
-\int_\Omega L u v + \int_\Omega \tau \left(L_{\rm adv}v\right)\left( L u - f\right) = \int_\Omega f v 
-\]
-for where $\tau$ is the SUPG parameter.
-For uniform meshes in 1D, $\tau$ is chosen such that, for $f=0$, the matrix system resulting from SUPG is exactly equal to the finite difference system under ``exact" artificial diffusion.
-However, unlike the artificial diffusion method, for $f\neq 0$, the SUPG method still delivers optimal stabilization.
-In fact, the SUPG finite element solution in 1D is nothing less than the nodal interpolant and the best $H^1$ approximation of the exact solution, as seen in Figure~\ref{fig:SUPG}.
-
-\begin{figure}[!h]
-\centering
-\subfigure[SUPG and standard FEM solutions]{\includegraphics[scale=.43]{figs/SUPG.png}}
-\subfigure[SUPG test function]{\includegraphics[scale=.22]{figs/SUPGtest.png}}
-\caption{SUPG and standard Bubnov-Galerkin solutions to the 1D convection-dominated diffusion equation, and a modified SUPG test function (in black) corresponding to a linear basis ``hat" function (in red).
-The upwind portion of the element is emphasized, while the downwind portion is decreased.
-The magnitude of the discontinuity between the upwind and downwind portion is controlled by the intrinsic timescale parameter $\tau$.
-}
-\label{fig:SUPG}
-\end{figure}
-
-The idea of emphasizing the upwind portion of a test function is an old idea, introduced in 1977 by Zienkiewicz et al.\ in \cite{zienkUpwind}.
-However, the precise amount of upwinding,\footnote{Insufficient upwinding results in a method which still exhibits oscillations and instabilities, while excessive upwinding leads to an overly diffusive method.} as well as the connection to residual-based stabilization methods, were novel to SUPG.
-
-The method can be made to ``work" for $p>1$, but the results are not as strong as for linear elements, and there is no clear generalization of SUPG to higher order elements.
-Additionally, the stabilization properties of SUPG are weaker in higher dimensions, and the SUPG solution is no longer the $H^1$ best approximation for 2D and 3D problems \todo{find citation}.
-Despite these caveats, SUPG is still the most popular stabilization method of choice for convection-diffusion type problems, in both academic and industry applications.
-
-An important feature of SUPG and other residual-based stabilization techniques that separates it from modified equation methods is the idea of \textit{consistency} --- by adding stabilization terms based on the residual, the exact solution still satisfies the same variational problem (i.e.\ Galerkin orthogonality still holds).
-Contrast this to the artificial diffusion methods in finite difference and finite volume methods, where a specific amount of additional viscosity is added based on the magnitude of the convection and diffusion parameters: unlike residual-based stabilization schemes, the exact solution to the original equation no longer satisfies the new stabilized formulation.
-
-This addition of residual-based stabilization terms can be interpreted as a modification of the test functions as well.  For SUPG, the formulation can equivalently be written as
-\[
-\int_\Omega\left( Lu-f\right) v_i = \int_\Omega f v_i, \quad i = 0,\ldots,N
-\]
-where $v_i$ is defined as
-\[
-v_i = \phi_i(x) + \tau L_{\rm adv} \phi_i.  
-\]
-In other words, the test function $v_i$ is a perturbation of the basis function $\phi_i$ by a scaled advective operator applied to $\phi_i$.
-For a linear $C^0$ basis function (the ``hat" function), this naturally leads to a bias in the upwind or streamline direction of the flow $\beta$, as seen in Figure~\ref{fig:SUPG}.
-
-An important connection can now be made --- stabilization can be achieved by changing the test space for a given problem.
-We will discuss in Section~\secref{optimalTest} approaching the idea of stabilization through the construction of \textit{optimal test functions} to achieve optimal approximation properties.
-
-\subsubsection{DG methods}
-
-Discontinuous Galerkin (DG) methods form a subclass of FEM; first introduced by Reed and Hill in \cite{Reed:73}, these methods were later analyzed by Cockburn and Shu \cite{CockburnShu:DG} and have rapidly gained popularity for CFD problems.
-Advantages of DG methods include the local conservation property, easily modified local orders of approximation, easy adaptivity in both $h$ and $p$, and efficient parallelizability.
-Rather than having a continuous basis where the basis function support spans several element cells, DG opts instead for a discontinuous, piecewise polynomial basis, where, like FV schemes, a \emph{numerical flux} facilitates communication between neighboring elements (unlike FV methods, however, there is no need for a reconstruction step).
-
-The formal definition of the numerical flux (attributed to Peter Lax) on an element boundary is some function of the values on the edges of both the neighboring elements.
-An additional reason for the popularity of DG methods is that they can be interpreted as stabilized FE methods through appropriate choices of this numerical flux \cite{Brezzi20063293}.
-We will illustrate this with the steady convection equation in 1D ---
-\begin{align*}
-\pd{\left(\beta(x) u\right)}{x} = f, \quad u(0) &= u_0.
-\end{align*}
-The DG formulation is derived by multiplying by a test function $v$ with support only on a single element $K = [x_K,x_{K+1}]$ and integrating by parts.
-The boundary term is left alone, such that the local formulation is
-\[
-\left.\beta u v\right|_{x_K}^{x_{K+1}} + \int_K -\beta u \pd{v}{x} = \int_K f v,
-\]
-and the global formulation is recovered by summing up all element-wise local formulations.
-However, the boundary term in the local formulation is presently ill-defined, as both $u$ and $v$ are dual-valued over element boundaries.
-Consequently, we make the choice to define the values of $u$ on the boundary (the \emph{traces} of $u$) as
-\begin{align*}
-u(x_K) \coloneqq u(x_K^-), \quad u(x_{K+1}) \coloneqq u(x_{K+1}^-),
-\end{align*}
-where $u(x_K^-)$ is the value of $u$ at $x_K$ as seen from the left, and $u(x_K^+)$ the value as seen from the right. Similarly, the traces of $v$ are defined to be
-\begin{align*}
-v(x_K) \coloneqq v(x_K^+), \quad v(x_{K+1}) \coloneqq v(x_{K+1}^-),
-\end{align*}
-We will refer to $v(x_K^+)$ as the upwind value of $v(x_K)$, and refer to DG under this specific choice of traces as upwind DG.
-This specific choice of $v(x_K)$ as the upwind value is crucial; similarly to SUPG, the upwind DG emphasizes the test function in the direction of convection and changes the way the residual is measured.
-As it turns out, the performance of DG for convection-type problems is closely tied to this upwinding --- choosing the value of $v(x_K)$ to be the downwind value $v(x_K^-)$ leads to an unstable method, while choosing $v(x_K)$ to be the average of the upwind and downwind values leads to a DG method with suboptimal stability properties, similar to an $H^1$-conforming continuous Galerkin approximation\cite{Brezzi20063293}.\footnote{For second-order convection-diffusion problems with small diffusion, the additional regularity imparted by choice of the DG numerical flux is often insufficient, and SUPG-type stabilization is also applied.}
-
-Another perspective on the use of the numerical flux in DG methods is that the selection of specific DG fluxes imparts \emph{additional regularity} where needed.
-For example, for the pure convection problem, the solution has a distributional derivative in the streamline direction, but is only $L^2$ in the crosswind direction.
-As a consequence of the regularity of the solution, the boundary trace of the solution is defined only in the direction of convection.
-The upwind DG method addresses the above issue by choosing the numerical flux to be the upwind flux; in this case, the DG numerical flux can be viewed as imparting additional regularity to the discrete solution than is implied by the continuous setting \cite{DPG1,DPG3}.
-
-\subsubsection{HDG}
-
-A more recent development in DG methods is the idea of \emph{hybridized} DG (HDG), introduced by Gopalakrishnan and Lazarov \cite{hybridDG}.
-The hybridized DG framework identifies degrees of freedom with support only on element edges, which can be interpreted as Lagrange multipliers enforcing weak continuity of the trial space.
-HDG methods treat numerical \emph{traces} and numerical \emph{fluxes} differently depending on the form of the boundary term resulting from integration by parts.
-The numerical trace (the result of integrating by parts the gradient) in HDG methods is chosen to be an unknown, while the numerical flux (the result of integrating by parts the divergence) is chosen to be an appropriate function of both function values on neighboring elements and the numerical trace.
-
-By a careful choice of the numerical flux, the global HDG formulation can be reduced to a single equation involving only the numerical trace degrees of freedom, referred to as the \emph{global} problem.
-Once the global problem is solved, interior degrees of freedom can be recovered in parallel through so-called \emph{local} problems \cite{HDGprojection}.
-
-HDG methods are an active topic of current research, since they address several criticisms of common DG methods (large number of degrees of freedom, globally coupled degrees of freedom, complicated/inefficient implementation procedures, suboptimal convergence of approximate fluxes).
-Note that HDG methods still fall under the category of stabilized methods --- stabilization techniques are employed through the choice of the HDG numerical flux, which involves some stabilization parameter $\tau$.
-
-\section{Scope}
-
-This PhD thesis proposal will proceed in four main parts:
-\begin{enumerate}
-\item Introduce the abstract DPG method as a minimum residual method for linear problems.
-\item Formulate a DPG method addressing the issue of robustness for the model problem of convection-dominated diffusion.
-\item Apply the DPG method to singularly perturbed nonlinear problems in CFD, discussing preliminary results for the Burgers and compressible Navier-Stokes equations. 
-\item Introduce completed and proposed work in concentration areas A, B, and C. 
-\end{enumerate}
-
-\section{Range of CFD problems}
-
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.45]{figs/CFD_tree.pdf}
-\caption{A diagram of common CFD problems and their simplifying assumptions.}
-\end{figure}
-
-\begin{itemize}
-\item Discuss full compressible Navier-Stokes with boundary layers
-\item Discuss full compressible Navier-Stokes without boundary layers, connect to Euler (mention Dr Young and Boeing and the IBL connection \cite{BoeingDrela})
-\item Discuss model problems
-\end{itemize}
+%Well-adapted to parabolic PDEs, finite element methods (FEM) gained early acceptance in engineering mechanics problems, though FEM became popular for the hyperbolic problems of CFD later than FD and FV methods.
+Early pioneers of the finite element method for CFD included Zienkiewicz, Oden, Karniadakis, and Hughes \cite{ChungCFDBook}.
+Of special note is the Streamline Upwind Petrov-Galerkin method (SUPG) of Brooks and Hughes \cite{SUPG}, which biases the standard test function by some amount in the direction of convection.
+SUPG is still the most popular FEM stabilization method to date.

### 2012-07-24 docs/Jesse/PECOStalk/proposalPres.tex
adding pecos talk

--- 2012-07-19 docs/Jesse/Proposal/proposalPres.tex
@@
 \usepackage{subfigure}
+%\usepackage{caption}
+%\usepackage{subcaption}
+
 \usepackage{color}
@@
 \frametitle{DPG for nonlinear problems}
-\textcolor{red}{REWORK. HOW TO DO THIS SECTION?}
-Begin with the nonlinear variational formulation
-$b(u,v) = l(v)$, linear in $v$, but not in $u$.  An appropriate linearization gives
+
+Given some linearization technique, we can measure 
+\begin{itemize}
+\item the nonlinear residual 
 \[
-b_u(\Delta u,v) = l(v) - b(u,v),
+\nor{R(u)}_E \coloneqq \nor{B(u)-l}_E = \nor{B(u) - l}_{V'}  = \nor{R_V^{-1} B(u)-l}_V 
 \]
-Let $B(u)$ and $B_u\Delta u$ be the variational operators associated with $b(u,v)$ and $b_u(\Delta u,v)$. 
-\begin{align*}
-\|\Delta u\|_E &\coloneqq \nor{B_u\Delta u}_{V'} = \nor{R_V^{-1} B_u\Delta u}_V \\
-\nor{R(u)}_E &\coloneqq \nor{B(u)-l}_E = \nor{B(u) - l}_{V'}  = \nor{R_V^{-1} B(u)-l}_V 
-\end{align*}
+\item size of the linearized update $\Delta u$
+\[
+\|\Delta u\|_E \coloneqq \nor{B_u\Delta u}_{V'} = \nor{R_V^{-1} B_u\Delta u}_V 
+\]
+\end{itemize}
+
+%\textcolor{red}{REWORK. HOW TO DO THIS SECTION?}
+%Begin with the nonlinear variational formulation
+%$b(u,v) = l(v)$, linear in $v$, but not in $u$.  An appropriate linearization gives
+%\[
+%b_u(\Delta u,v) = l(v) - b(u,v),
+%\]
+%Let $B(u)$ and $B_u\Delta u$ be the variational operators associated with $b(u,v)$ and $b_u(\Delta u,v)$. 
+%\begin{align*}
+%\|\Delta u\|_E &\coloneqq \nor{B_u\Delta u}_{V'} = \nor{R_V^{-1} B_u\Delta u}_V \\
+%\nor{R(u)}_E &\coloneqq \nor{B(u)-l}_E = \nor{B(u) - l}_{V'}  = \nor{R_V^{-1} B(u)-l}_V 
+%\end{align*}
 }
@@
 \frame{
-\frametitle{Burgers equation}
+\frametitle{Test case: Burgers equation}
 \begin{columns}
@@
 }
+\setcounter{subfigure}{0}
+
 \frame{
@@
 }
+\setcounter{subfigure}{0}
 
-\section{Area A}
+\frame{
+\frametitle{Zoomed solutions at the plate edge}
+\begin{figure}
+\subfigure[$\rho$]{\includegraphics[scale = .12]{figs/Re1000p2/rhoUnscaledzoom.png}}
+\subfigure[$u_1$]{\includegraphics[scale = .12]{figs/Re1000p2/u1zoom.png}}
+\subfigure[$u_2$]{\includegraphics[scale = .12]{figs/Re1000p2/u2zoom.png}}
+\subfigure[$T$]{\includegraphics[scale = .12]{figs/Re1000p2/Tzoom.png}}
+\subfigure[$q_n$]{\includegraphics[scale = .23]{figs/Re1000p2/heatflux.png}}
+\end{figure}
+}
+
+\section{Proposed work}
+\subsection{Area A}
 \frame{
@@
 \]
-produces a Hessian-based DPG method 
+produces a Hessian-based DPG method, which solves
 \[
-b_u(\Delta u,v) + b''(\Delta u, \delta u, v_{R(u)}) = r(u,v) = l(v) - b(u,v),
+b_u(\Delta u,v) + b''(\Delta u, \delta u, v_{R(u)}) = l(v) - b(u,v) = r(u,v),
 \]
-which aims to minimize the nonlinear dual residual instead of the linearized problem residual. 
+and aims to minimize the nonlinear dual residual instead of the linearized problem residual. 
 }
@@
 \frame{
-\frametitle{Proposed work: Area C}\
-textcolor{red}{GET GRAPHICS FOR EACH}
+\frametitle{Proposed work: Area C}
 \begin{itemize}
@@
 \item{\textbf{Proposed: regularized Euler.}}
+\textcolor{red}{Graphics?}
 \end{itemize}

### 2012-07-24 docs/Jesse/PECOStalk/utdiss2-05/chapter-appendix2.tex
adding pecos talk

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{My Appendix \#2}
\index{Appendix!My Appendix \#2@\emph{My Appendix \#2}}%
\section{The First Section}
This is the first section.
This is the second appendix.

\section{The Second Section}
This is the second section of the second appendix.

\subsection{The First Subsection of the Second Section}
This is the first subsection of the second section of the second appendix.

\subsection{The Second Subsection of the Second Section}
This is the second subsection of the second section of the second appendix.

\subsubsection{The First Subsubsection of the Second Subsection of
		the Second Section}
This is the first subsubsection of the second subsection of the
second section of the second appendix.

\subsubsection{The Second Subsubsection of the Second Subsection
		of the Second Section}
This is the second subsubsection of the second subsection of the
second section of the second appendix.

### 2012-07-24 docs/Jesse/PECOStalk/utdiss2-05/chapter-makingbib.tex
adding pecos talk

\chapter{Making the Bibliography with BiB\TeX{}}\label{c:bib}
\index{Making the Bibliography with BiBTeX%
@\emph{Making the Bibliography with BiB\TeX{}}}%

BiB\TeX{} 
\index{BiBTeX@BiB\TeX{}}%
allows one to generate automatically the bibliography 
from a database of bibliographic 
items. You need to do the following:

\begin{enumerate}
\item Create the bibliographic database, 
\index{bibliographic database}%
which is a file whose name ends in \texttt{.bib}. 
\index{.bib@\texttt{.bib}}%
Let us call it \texttt{diss.bib}. Entries in this file are like this:
\begin{verbatim}
@BOOK{knuth:tb,
  author = "Donald K. Knuth",
  title = "The \TeXbook",
  publisher = "Addison-Wesley",
  year = "1984",
}
@TECHREPORT{poorten:sp,
  author = "Alf~J.~van der Poorten",
  title = "Some problems of recurrent interest",
  institution = "School of Mathematics and Physics,
                 Macquarie University",
  address = "North Ryde, Australia 2113",
  number = "81-0037",
  month = "August",
  year = "1981",
}
@ARTICLE{erdos:oap,
 author = "Paul Erd{\"o}s and Paul Turan",
 title = "On a problem in the theory of uniform 
          distribution, {I}", 
 journal = "Indag. Math.",
 volume = "10",
 year = "1948",
 pages = "370--378",
}
\end{verbatim}

\item Include a \cn{bibliographystyle} 
\index{commands!bibliographystyle@\cn{bibliographystyle}}%
command in your \LaTeX{} file, say

\cn{bibliographystyle\{plain\}} 
and a \cn{bibliography} 
\index{commands!bibliography@\cn{bibliography}}%
command to load the bibliography, 
in this case \cn{bibliography\{diss\}}, at the point of your 
document where the bibliography should be inserted.

The document at this point will look like this:
\begin{verbatim}
\bibliographystyle{plain}
\bibliography{diss}
\end{verbatim}

\item Run \LaTeX{} on your main file, say \texttt{foo.tex}: 
\texttt{latex foo}. This generates an auxiliary file 
\texttt{foo.aux} with a list of \cn{cite} 
\index{commands!cite@\cn{cite}}
references.

\item Run BiB\TeX{} on your file: \texttt{bibtex foo}. 
BiB\TeX{} reads the auxiliary file, looks up the 
bibliographic database (\texttt{diss.bib}), 
and writes a \texttt{.bbl} 
\index{.bbl@\texttt{.bbl}}%
file with the bibliographic information formated according to
the bibliographic style file (\texttt{.bst}, 
\index{.bst@\texttt{.bst}}%
say \texttt{plain.bst}) 
\index{plain.bst@\texttt{plain.bst}}%
specified.  Messages about resources used and error messages
are written to a \texttt{.blg} 
\index{.blg@\texttt{.blg}}%
file (in the case of this template, disstemplate.blg).

\item Run \LaTeX{} again: \texttt{latex foo}, which now 
reads the \texttt{.bbl} 
\index{.bbl@\texttt{.bbl}}%
reference file.

\item Run \LaTeX{} for a third time: \texttt{latex foo}, 
resolving all references.

\end{enumerate}

This includes all bibliographic items that have been cited 
in the document with a \cn{cite} 
\index{commands!cite@\cn{cite}}%
command. In order to include non cited items in the bibliography,
use the command \cn{nocite}. For example, \cn{nocite\{knuth:tb\}}
anywhere in the document (after \cn{begin\{document\}}) includes 
in the bibliography the item with label \texttt{knuth:tb}. 
In order to include \emph{all} items of the bibliographic 
database, use the command \cn{nocite\{*\}}.
\index{commands!nocite@\cn{nocite}}%

### 2012-07-24 docs/Jesse/PECOStalk/utdiss2-05/chapter-tables+figs.tex
adding pecos talk

\chapter{Making Tables and Including Figures}
\index{Making Tables and Including Figures@\emph{Making Tables
	and Including Figures}}%

The \emph{tabular} 
\index{commands!environments!tabular}%
environment allows us to create complex 
tables and figures, and draw boundaries around and within it.
The following example illustrates this:

\begin{table}[h]
\begin{center}
\caption{An example of a table.}
\vskip 10pt
\begin{tabular}{|ll|l|ll|l|lll|}
\cline{1-2} \cline{4-5} \cline{7-9}
\multicolumn{2}{|c|} {\textsl{Gegenwart}} & &
\multicolumn{2}{|c|} {\textsl{Imperfekt}} & &
\multicolumn{3}{|c|} {\textsl{Perfekt}} \\
\cline{1-2} \cline{4-5} \cline{7-9}
ich & bin  & & ich & war   & & ich & bin  & gewesen \\
du  & bist & & du  & warst & & du  & bist & gewesen \\
er  &      & & er  &       & & er  &      &         \\
sie & ist  & & sie & wart  & & sie & ist  & gewesen \\
es  &      & & es  &       & & es  &      &         \\
\cline{1-2} \cline{4-5} \cline{7-9}
wir & sind & & wir & waren & & wir & sind & gewesen \\
ihr & seid & & ihr & wart  & & ihr & seid & gewesen \\
sie & sind & & sie & waren & & sie & sind & gewesen \\
\cline{1-2} \cline{4-5} \cline{7-9}
Sie & sind & & Sie & waren & & Sie & sind & gewesen \\
\cline{1-2} \cline{4-5} \cline{7-9}
\end{tabular} \\[10pt]
Note: The assistance of Herr Professor Lothar Frommhold \\
in generating this table of German declensions \\
is gratefully acknowledged.
\vskip -20pt
\end{center}
\end{table}
\index{commands!environments!table}%

This table was created with the following sequence 
of commands:
\begin{verbatim}
\begin{table}[h]
\begin{center}
\caption{An example of a table.}
\vskip 10pt
\begin{tabular}{|ll|l|ll|l|lll|}
\cline{1-2} \cline{4-5} \cline{7-9}
\multicolumn{2}{|c|} {\textsl{Gegenwart}} & &
\multicolumn{2}{|c|} {\textsl{Imperfekt}} & &
\multicolumn{3}{|c|} {\textsl{Perfekt}} \\
\cline{1-2} \cline{4-5} \cline{7-9}
ich & bin  & & ich & war   & & ich & bin  & gewesen \\
du  & bist & & du  & warst & & du  & bist & gewesen \\
er  &      & & er  &       & & er  &      &         \\
sie & ist  & & sie & wart  & & sie & ist  & gewesen \\
es  &      & & es  &       & & es  &      &         \\
\cline{1-2} \cline{4-5} \cline{7-9}
wir & sind & & wir & waren & & wir & sind & gewesen \\
ihr & seid & & ihr & wart  & & ihr & seid & gewesen \\
sie & sind & & sie & waren & & sie & sind & gewesen \\
\cline{1-2} \cline{4-5} \cline{7-9}
Sie & sind & & Sie & waren & & Sie & sind & gewesen \\
\cline{1-2} \cline{4-5} \cline{7-9}
\end{tabular} \\[10pt]
Note: The assistance of Herr Professor Lothar Frommhold \\
in generating this table of German declensions \\
is gratefully acknowledged.
\vskip -20pt
\end{center}
\end{table}
\index{commands!environments!table}%
\end{verbatim}

The argument \texttt{h} indicates the position for the 
table, in this case ``here if possible''. Other values
of this argument are:
\texttt{t} (top of the page),
\texttt{b} (bottom of the page),
\texttt{p} (on the page of floats) and 
\texttt{H} (HERE! - requires using the package float.sty.
Note: When this option is used, LaTeX ignores all of its formatting
rules and does what you say, putting the entire float exactly where
it is defined. Check your output to make sure it is what you want!
If you are having trouble with LaTeX wanting to put a figure that's
larger than roughly half-a-page, as well as all of the figures
following it, at the end of a chapter, try using the command
\cn{clearpage} immediately following the large figure --- and maybe
a \cn{newpage} later.)
It is possible to combine several arguments, such as
\texttt{ht} (``here if possible, otherwise on top of
the page''). The default is \texttt{tbp}.

Figure \ref{f:ex} is a typical example of inclusion of a 
figure contained in an encapsulated PostScript file. 
\index{PostScript}%
\index{encapsulated PostScript}%
In order to use it, it is necessary to include the 
command \cn{usepackage\{psfig\}} 
\index{psfig}%
at the beginning of the document.

\begin{figure}[htb] % Imported eps example.
\begin{center}
\ \psfig{file=pup-on-rug.eps,height=1.5in,width=2.0in}
\caption{An example of an imported eps file.}
\label{f:ex}
\end{center}
\end{figure}
\index{commands!environments!figure}%
You can see the commands that generated this
figure in the source file. Look for the line
\cn{begin\{figure\}[htb] \% Imported eps example. }

The command that imports the file is \cn{psfig}, and it also 
controls its size (\texttt{height} and \texttt{width}), and 
can rotate the figure (\texttt{angle}).

Figures can also be drawn by using \LaTeX{} commands. 
Figure \ref{f:circuit} is an example 
(taken from \cite{gms:tlc}).

\begin{figure}[htb] % Picture example.
\begin{center}
   \setlength{\unitlength}{4mm}
   \begin{picture}(12,10)(-2,0)
      \linethickness{0.4pt}
      \qbezier(2.00,6.00)(7.00,6.00)(9.00,3.00)
      \qbezier(2.00,0.00)(7.00,0.00)(9.00,3.00)
      \qbezier(2.00,6.00)(4.00,3.00)(2.00,0.00)
      \qbezier(1.00,6.00)(3.00,3.00)(1.00,0.00)
      \put(9.75,3.00){\circle{1.50}}
      \put(10.50,3.00){\line(1,0){1.50}}
      \put(0.00,5.00){\line(1,0){1.50}}
      \put(0.00,1.00){\line(1,0){1.50}}
   \end{picture}
\caption{An example of a picture}
\label{f:circuit}
\end{center}
\end{figure}
\index{picture}%

The commands that generated this
picture are in the source file following the line
\cn{begin\{figure\}[htb] \% Picture example.  }

The commands used have rather obvious meanings. In particular, 
the command \cn{qbezier} 
\index{commands!qbezier@\cn{qbezier}}%
draws a quadratic Bezier curve, 
defined by its two ending points, and a third point (whose 
coordinates are in the middle) that is used as control point. 
Figure \ref{f:qb} illustrates the effect of the control point:

%\begin{figure}[htb] % Bezier curves example.
\begin{figure}[h] % Bezier curves example.
\begin{center}
   \setlength{\unitlength}{.8mm}
   \begin{picture}(55,55)(-15,0)
      \linethickness{1pt}
      \qbezier(0,0)(-10,30)(50,30)
      \qbezier(0,0)(20,50)(50,30)
      \thinlines
      \put(0,0){\line(-1,3){10}}
      \put(50,30){\line(-1,0){60}}
      \put(0,0){\line(2,5){20}}
      \put(50,30){\line(-3,2){30}}
      \put(0,0){\circle*{1}}
      \put(0,-1){\makebox(0,0)[t]{$A_{0,0}$}}
      \put(-10,30){\circle*{1}}
      \put(-10,31){\makebox(0,0)[b]{$B_{10,30}$}}
      \put(50,30){\circle*{1}}
      \put(58,29){\makebox(0,0)[b]{$C_{50,30}$}}
      \put(20,50){\circle*{1}}
      \put(20,51){\makebox(0,0)[b]{$D_{20,50}$}}
   \end{picture}
\caption{Bezier curves}
\label{f:qb}
\end{center}
\end{figure}
\index{Bezier curves}%

This figure has been generated with the following commands:
\begin{verbatim}
\begin{figure}[htb] % Bezier curves example.
\begin{center}
   \setlength{\unitlength}{.8mm}
   \begin{picture}(55,55)(-15,0)
      \linethickness{1pt}
      \qbezier(0,0)(-10,30)(50,30)
      \qbezier(0,0)(20,50)(50,30)
      \thinlines
      \put(0,0){\line(-1,3){10}}
      \put(50,30){\line(-1,0){60}}
      \put(0,0){\line(2,5){20}}
      \put(50,30){\line(-3,2){30}}
      \put(0,0){\circle*{1}}
      \put(0,-1){\makebox(0,0)[t]{$A_{0,0}$}}
      \put(-10,30){\circle*{1}}
      \put(-10,31){\makebox(0,0)[b]{$B_{10,30}$}}
      \put(50,30){\circle*{1}}
      \put(58,29){\makebox(0,0)[b]{$C_{50,30}$}}
      \put(20,50){\circle*{1}}
      \put(20,51){\makebox(0,0)[b]{$D_{20,50}$}}
   \end{picture}
\caption{Bezier curves}
\label{f:qb}
\end{center}
\end{figure}
\end{verbatim}

### 2012-07-24 docs/Jesse/PECOStalk/proposalIntro.tex

--- 2012-06-26 docs/Jesse/Proposal/proposalIntro.tex
@@
 The goal of this dissertation will be to develop a mathematical theory demonstrating the robustness in $\epsilon$ of our method for singularly perturbed convection-diffusion problems, and to demonstrate its feasibility as a CFD solver by applying it to several benchmark problems.
-\todo{Check with LD if it's what he's looking for}
 
@@
 
-We will introduce the SUPG method at an abstract level for illustrative purposes only.
+We will introduce the SUPG method at the abstract level for illustrative purposes only.
 Further details and perspectives on the SUPG method can be found in \cite{SUPG}, as well as in an upcoming book by Hughes.
@@
 Let us assume $u$ to be a linear combination of piecewise-linear basis functions $\phi_i, i = 0,\ldots,N$ (then, within each element, $L_{\rm diff} u = 0$).
-The SUPG method is then to solve
-\[
-\int_\Omega L u v + \int_\Omega \tau \left(L_{\rm adv}v\right)\left( L u - f\right) = \int_\Omega f v 
-\]
+If $b(u,v)$ and $l(v)$ are the bilinear form and load for the standard Galerkin method (resulting from multiplying by a test function $v$ and integrating both convective and diffusion terms by parts), the SUPG method is then to solve $b_{\rm SUPG}(u,v) = l_{\rm SUPG}(v)$, where $b_{\rm SUPG}(u,v)$ and $l_{\rm SUPG}(v)$ are defined as
+\begin{align*}
+b_{\rm SUPG}(u,v) &= b(u,v)+ \sum_{K} \int_{K} \tau \LRp{L_{\rm adv} v} \LRp{L u - f} \\
+l_{\rm SUPG}(v) &= l(v) + \sum_{K} \int_{K} \tau \LRp{L_{\rm adv}v} f
+\end{align*}
 for where $\tau$ is the SUPG parameter.
@@
 
-The method can be made to ``work" for $p>1$, but the results are not as strong as for linear elements, and there is no clear generalization of SUPG to higher order elements.
-Additionally, the stabilization properties of SUPG are weaker in higher dimensions, and the SUPG solution is no longer the $H^1$ best approximation for 2D and 3D problems \todo{find citation}.
-Despite these caveats, SUPG is still the most popular stabilization method of choice for convection-diffusion type problems, in both academic and industry applications.
+For appropriately chosen $\tau$, the method can be generalized for higher order elements as well.
+In higher dimensions, and the SUPG solution is very close to, but no longer the $H^1_0$ best approximation for 2D and 3D problems \cite{HughesSangalliSUPG}.
+Since its inception, SUPG is and has been the most popular stabilization method of choice for convection-diffusion type problems, in both academic and industry applications.
 
@@
 \[
-\int_\Omega\left( Lu-f\right) v_i = \int_\Omega f v_i, \quad i = 0,\ldots,N
+b\LRp{u,\tilde{v}_{i}} = l\LRp{\tilde{v}_{i}}, \quad \forall i = 1,\ldots,N-1
 \]
-\todo{check to make sure this is correct}
-where $v_i$ is defined as
+where the SUPG test function $\tilde{v}_{i}$ is defined elementwise as
 \[
-v_i = \phi_i(x) + \tau L_{\rm adv} \phi_i.  
+\tilde{v}_{i} = \phi_i(x) + \tau L_{\rm adv} \phi_i.  
 \]
-In other words, the test function $v_i$ is a perturbation of the basis function $\phi_i$ by a scaled advective operator applied to $\phi_i$.
+In other words, the test functions $\tilde{v}_{i}$ is a perturbation of the basis function $\phi_i$ by a scaled advective operator applied to $\phi_i$.
 For a linear $C^0$ basis function (the ``hat" function), this naturally leads to a bias in the upwind or streamline direction of the flow $\beta$, as seen in Figure~\ref{fig:SUPG}.

### 2012-07-24 docs/Jesse/PECOStalk/utdiss2-05/chapter-math.tex

\chapter{An Example of Mathematical Writing}
\index{An Example of Mathematical Writing%
@\emph{An Example of Mathematical Writing}}%

\section{Generalized Fatou's Lemma}
\index{Generalized Fatou's Lemma%
@\emph{Generalized Fatou's Lemma}}%

Here we show an application of the following lemma:

\begin{lem}[Generalized Fatou's Lemma] \label{l:fatou}

Let $A$ be a Dedekind ring and $F$ a rational series 
in $A[[X]]$, i.e., $F = p/q$ for some 
$p, q \in A[X]$. Then there exist two polynomials 
$P, Q \in A[X]$ such that $F = P/Q$, 
where $P$ and $Q$ are relatively prime and 
$Q(0) = 1$.

\end{lem}

\proof
See \cite{bertin:psn}, p.~15, theorem~1.3.
\endproof

\begin{thm} \label{l:req}
Let $\{c_n\}_{n=-\infty}^{\infty}$ a set of 
elements from $K$ such that $c_n \in k'$ for every 
$n \geq n_0$, and verifying the following recurrence 
relation of order M:
\begin{equation}
c_n\ =\ r_1\,c_{n-1} + r_2\,c_{n-2} + \dots + r_M\,c_{n-M}
\end{equation}
for every $n \in \mathbb Z$, where $r_1,r_2,\dots,r_M$ are in 
$K$, $r_M \neq 0$. 
Then:

\item{(i)} The coefficients $r_1,r_2,\dots,r_M$ are in 
$k'$, and for every $n \in \mathbb Z$, $c_n \in k'$.

\item{(ii)} If $c_n \in \mathcal O_{k',v}$ 
for every $n \geq n_0$, then the coefficients 
$r_1,r_2,\dots,r_M$ are all in 
$\mathcal O_{k',v}$.

\end{thm}

\proof

\item{(i)} Let $C_n$ and $R$ be the matrices:

\begin{equation}
C_n\ =
\ \left(
\begin{array}{llll}
              c_n & c_{n+1} & \hdots & c_{n+M-1} \\
              c_{n+1} & c_{n+2} & \hdots  & c_{n+M} \\
              \vdots & \vdots & \ddots & \vdots \\
              c_{n+M-1} & c_{n+M} & \hdots & c_{n+2M-2}
\end{array}
\right)
\end{equation}
and
\begin{equation}
R\ =
\ \left(
\begin{array}{lllll}
              0 & 1 & 0 & \hdots & 0 \\
              0 & 0 & 1 & \hdots & 0 \\
             \vdots & \vdots & \vdots & \ddots & \vdots \\
              0 & 0 & 0 & \hdots & 1 \\
              r_M & r_{M-1} & r_{M-2} & \hdots & r_1 
\end{array}
\right)
\end{equation}

We have that $C_{n+1} = R\,C_n$. Since the recurrence 
relation is of order M, $C_n$ is non singular. 
On the other hand, $R = C_{n+1}\,C_{n}^{-1}$. Since the 
elements of $C_n$ are in $k'$ for $n \geq n_0$, the entries 
of $R$, and those of $R^{-1}$, will be in $k'$. Since 
$C_{n-1} = R^{-1}\,C_n$, we get that the entries of 
$C_n$ will be in $k'$ also for $n < n_0$.

\item{(ii)} For each $t \geq n_0$ define the formal 
power series

\begin{equation}
F_t(X)\ =\ \sum_{n=0}^{\infty} c_{t+n}\,X^n
\end{equation}
which is in $\mathcal O_{k',v}[[X]]$. 
We have $F_t(X) = p_t(X)/q(X)$, 
where $p_t(X),q(X) \in k'[X]$ are the following:
\begin{equation}
p_t(X)\ =\ \sum_{j=0}^{M-1} \Bigl( c_{t+j} - 
                    \sum_{i=1}^{j} r_i\,c_{t+j-i} \Bigr)\,X^j
\end{equation}
\begin{equation}
q(X)\ =\ 1 - r_1\,X - r_2\,X^2 - \dots - r_M\,X^M
\end{equation}
This can be checked by multiplying $F_t(X)$ by $q_t(X)$ 
and using the recurrence relation, which gives 
$F_t(X)\,q(X) = p_t(X)$ (see \cite{poorten:sp}).

Now we will prove that $p_t(X)$ and $q(X)$ are relatively 
prime. To do so, we will see that they cannot have any 
common root (in $\overline {k'}$). In fact, assume 
that $\alpha$ is a common root of $p_{t_0}(X)$ and $q(X)$ 
for some $t_0 \geq n_0$, i.e.: 
$p_{t_0}(\alpha) = q(\alpha) = 0$. 
Since $q(0)=1$, then $\alpha \neq 0$. Now we have:
\begin{equation}
X\,F_{t_0+1}(X) = F_{t_0}(X) - c_{t_0}
\end{equation}
so:
\begin{multline}
X\,p_{t_0+1}(X) = X\,q(X)\,F_{t_0+1}(X) \\
= q(X)\,(F_{t_0}(X) - c_{t_0}) = p_{t_0}(X) - c_{t_0}\,q(X)
\end{multline}
Hence $p_{t_0+1}(\alpha) = 0$, which means that $\alpha$ is 
also a root of $p_{t_0+1}(X)$. By induction we get that 
$p_t(\alpha) = 0$ for every $t \geq t_0$. Grouping the 
terms of $p_t(X)$ with respect to $c_t,c_{t+1},\dots,c_{t+M-1}$, 
we get:
\begin{equation}
p_t(X) = \sum_{j=0}^{M-1} a_j(X)\,c_{t+j}
\end{equation}
where 
\begin{equation}
a_j(X) = X^j\,\Bigl( 1 - \sum_{i=1}^{M-j-1} r_i\,X^i \Bigr)
\end{equation}
Note that $a_0(X),a_1(X),\dots,a_{M-1}(X)$ do not depend on t. 
On the other hand $p_t(\alpha)=0$ implies
\begin{equation}
\label{e:coldep}
\sum_{j=0}^{M-1} a_j(\alpha)\,c_{t+j} = 0
\end{equation}
for every $t \geq t_0$. Note that $a_{M-1}(\alpha)=\alpha^{M-1}
\neq 0$, so $a_0(\alpha),a_1(\alpha),\dots,a_{M-1}(\alpha)$ 
are not all zero, and (\ref{e:coldep}) means that the columns 
of the matrix $C_{t_0}$ are linearly dependent, so 
$\det C_{t_0}=0$, which contradicts the fact that $C_{t_0}$ 
is non singular. Hence, the hypothesis that $p_t(X)$ and 
$q(X)$ have a common root has to be false. This proves that 
$p_t(X)$ and $q(X)$ are relatively prime.

By (generalized Fatou's) lemma~\ref{l:fatou}, 
and taking into account that 
$\mathcal O_{k',v}$ is a Dedekind ring, 
we get that there exist two relatively prime 
polynomials $P_t(X)$ and $Q_t(X)$ in 
$\mathcal O_{k',v}[X]$ such that 
$F_t(X) = P_t(X)/Q_t(X)$ and $Q_t(0)=1$. Hence: 
$p_t(X)\,Q_t(X) = q(X)\,P_t(X)$. By unique factorization 
of polynomials in $k'[X]$, there is a $u \in k'$ such that 
$P_t(X) = u\,p_t(X)$ and $Q_t(X) = u\,q_t(X)$. Since 
$Q_t(0)=q(0)=1$, we get that $u=1$, so 
$P_t(X) = p_t(X)$ and $Q_t(X) = q(X)$. 
Hence, the coefficients of $q(X)$ are in 
$\mathcal O_{k',v}$.

\endproof

\section{Other Examples of Mathematical Writing}

\subsection{An Example of a Commutative Diagram}
\index{An Example of a Commutative Diagram%
@{An Example of a Commutative Diagram}}%

The following is an example of a commutative diagram.
\index{commutative diagram}%
It requires the \texttt{amscd} package.
\index{amscd package@{\texttt{amscd} package}}

\begin{equation*}
\newcommand{\End}{\operatorname{End}}
\begin{CD}
S^{{\mathcal{W}}_\Lambda}\otimes T   @>j>>   T\\
@VVV                                    @VV{\End P}V\\
(S\otimes T)/I                  @=      (Z\otimes T)/J
\end{CD}
\end{equation*}

That diagram has been made with the following commands:

\begin{verbatim}
\newcommand{\End}{\operatorname{End}}
\begin{CD}
S^{{\mathcal{W}}_\Lambda}\otimes T   @>j>>   T\\
@VVV                                    @VV{\End P}V\\
(S\otimes T)/I                  @=      (Z\otimes T)/J
\end{CD}
\end{verbatim}

\subsection{Using AMS Fonts}
\index{Using AMS Fonts@{Using AMS Fonts}}

To use AMS fonts it is necessary to choose from an assortment 
of \LaTeX{} packages. For instance the command 
\cn{usepackage\{amsfonts\}} calls in the \emph{amsfonts} package, 
which provides blackboard bold letters (e.g. $\mathbb{R}$) and 
some math symbols. A superset of that package is 
\emph{amssymb}. Other packages are \emph{eufrak} 
for Frankfurt letters (e.g. $\mathfrak{R}$)
and \emph{eucal} for Euler script 
(e.g. $\mathcal{R}$). 
Consult the \LaTeX{} documentation about this subject 
for additional information.

### 2012-07-30 docs/Jesse/Proposal/proposalPres.tex

@@
 
-\title{A DPG method for compressible flow problems}
-\author{Jesse Chan}
+\title{A Discontinuous Petrov-Galerkin method for compressible flow problems}
+\author{Jesse Chan \\ Supervisors: Leszek Demkowicz, Robert Moser}
 
@@
 \end{figure}
-Compressible flow plays an important role in the aerospace and energy industries - supersonic aircraft, combustion engines, etc.
+Compressible flow plays an important role in the aerospace and energy industries - transonic and supersonic aircraft, combustion engines, etc.
 
@@
 \begin{itemize}
-\item{} Resolving solutions (sharp, localized $O(\Reyn^{-1})$ phenomena)
+\item{} Resolving solution features (sharp, localized $O(\Reyn^{-1})$ phenomena)
 \begin{itemize}
@@
 \end{itemize}
+\item{} Nonlinear convergence and uniqueness of solutions
 \end{itemize}
@@
 \frame{
-\frametitle{Convection-diffusion as a model problem}
+\frametitle{Robustness: convection-diffusion as a model problem}
 \vspace{-.5cm}
@@
 \centering
-\includegraphics[scale=.3]{figs/GalerkinOscTight.png}
-\caption{Oscillations in the standard Galerkin method for underresolved meshes and small $\epsilon$.}
+\includegraphics[scale=.35]{figs/GalerkinOscTight.png}
+\caption{Oscillations in the standard Galerkin for underresolved meshes and small $\epsilon$.}
 \end{figure}
@@
 }
-\frame{
-\frametitle{Stabilization}
-Historical stabilization methods: 
-\begin{itemize}
-\item Artificial diffusion - solve
-\[
-\beta u' - \tilde{\epsilon} u'' = f
-\]
-where $\tilde{\epsilon}$ is set depending on $\beta$, $\epsilon$, and the mesh. 
-\item Upwind stencils - for positive $\beta$, and uniform grid points $x_A$,
-\[
-u'(x_A) \approx \frac{u_h(x_A)-u_h(x_{A-1})}{h}
-\]
-\end{itemize}
-
-Both of these methods introduce additional numerical diffusion, and their effectiveness depends on the forcing $f$ and parameters $h$, $|\beta|$, and $\epsilon$.
-}
+%\frame{
+%\frametitle{Stabilization}
+%Historical stabilization methods: 
+%\begin{itemize}
+%\item Artificial diffusion - solve
+%\[
+%\beta u' - \tilde{\epsilon} u'' = f
+%\]
+%where $\tilde{\epsilon}$ is set depending on $\beta$, $\epsilon$, and the mesh. Can be made ``exact'' for $f=0$. 
+%\item Upwind finite differences - for $\beta > 0$, and uniform grid points $x_A$,
+%\[
+%u'(x_A) \approx \frac{u_h(x_A)-u_h(x_{A-1})}{h}
+%\]
+%\end{itemize}
+%Both of these methods introduce additional numerical diffusion, and their effectiveness depends on the forcing $f$ and parameters $h$, $|\beta|$, and $\epsilon$.
+%}
 \frame{
@@
 \begin{itemize}
-\item{} $L_{\rm adv}u = \div \left(\beta u\right)$, and $\tau$ is a parameter. 
-\item{} Recovers ``exact'' artificial diffusion for $f=0$.
+\item{} $Lu = \div\left(\beta u\right) - \epsilon \triangle u$, $L_{\rm adv}u = \div \left(\beta u\right)$, and $\tau$ is a parameter. 
+%\item{} Recovers ``exact'' artificial diffusion for $f=0$.
 \item{} Effective for $f\neq 0$, unlike ``exact'' artificial diffusion.
@@
 \centering
-\includegraphics[scale=.3]{figs/SUPG.png}
-\caption{Exact, FEM, and SUPG solutions.}
+\includegraphics[scale=.35]{figs/SUPG.png}
+%\caption{Exact, Bubnov-Galerkin, and SUPG solutions.}
 \end{figure}
@@
 \frame{
-\frametitle{Minimum residual methods and optimal testing}
-Identify $B:U\rightarrow V'$ such that
+\frametitle{DPG: a minimum residual method via optimal testing}
+Given
+\[
+b(u,v) = l(v), \quad u\in U, \quad v\in V
+\]
+identify $B:U\rightarrow V'$ such that 
 \[
@@
 \begin{frame}
-Let $R_V: V \to V'$ be the isometric the Riesz map st.\
+Let $R_V: V \to V'$ be the isometric Riesz map st.\
 \[
@@
 \frame{
-For $\delta u \in U$, we define the {\em optimal test function} $v_{\delta u}$
+\frametitle{Minimum residual methods and optimal testing}
+For $\delta u \in U$, define the \textcolor{red}{optimal test function} $v_{\delta u}$. 
 \begin{equation*}
-v_{\delta u} \coloneqq R_V^{-1}B\delta u 
+v_{\delta u} \coloneqq R_V^{-1}B\delta u.
 \end{equation*} 
-such that $J(u_h)$ is minimized by the solution of
+Then, the least-squares residual $J(u_h) = \frac{1}{2}\left\|Bu_h-l\right\|_{V'}^2$ is minimized by the solution of
 \[
@@
 }
+
 \frame{
-\frametitle{Details and properties of DPG}
+\frametitle{Practical details of DPG}
 \begin{itemize}
-\item By choosing $V$ as a \emph{broken} test space, test functions can be determined locally.
-\item In practice, $V \coloneqq V_h$, where $\dim(V_h) > \dim(U_h)$ elementwise, and test functions are approximated via solving
+\item By choosing a \emph{broken} test space $V$ and \textcolor{red}{localizable} norm $\nor{v}_V = \sum_K \nor{v}_{V(K)}$, test functions can be determined locally.
+\item In practice, we use the \textcolor{red}{enriched space} $V \coloneqq V_h$, where $\dim(V_h) > \dim(U_h)$ elementwise, and \textcolor{red}{optimal test functions} are approximated by solving
 \[
-\LRp{v_{\delta u},\delta v}_V = b(\delta u,\delta v).
+\LRp{v_{\delta u},\delta v}_V = b(\delta u,\delta v), \quad \delta u\in U, \quad v_{\delta u},\delta v\in V_h
 \]
-\item Symmetric positive-definite stiffness matrix: for $B_{ji} = b(u_j,v_i)$, $l_i = l(v_i)$ for $v_i$ spanning $V_h$, DPG solves
-\[
-u^T B^T R_V^{-1}B = l R_V^{-1}B 
-\]
+Typically, if $U_h = \mathcal{P}^p(\mathbb{R}^n)$, $V_h = \mathcal{P}^{p+\triangle p}(\mathbb{R}^n)$, where $\triangle p \geq n$. 
 \end{itemize}
-
 }
@@
 \frame{
+\frametitle{Properties of DPG}
+DPG provides a symmetric positive-definite stiffness matrix. Let $\{\phi_j\}_{j=1}^m$ be a basis for $U_h$, and $\{v_i\}_{i=1}^n$ a basis for $V_h$, such that $n>m$. Then, for 
+\begin{align*}
+B_{ji} &= b(\phi_j,v_i),\\
+l_i &= l(v_i),
+\end{align*}
+DPG solves the discrete system
+\begin{align*}
+(B^T R_V^{-1}B) u  &= (B^T R_V^{-1}) l,
+\end{align*}
+where, under a localizable norm and discontinuous test functions, $R_V^{-1}$ is block diagonal.
+}
+
+\frame{
+\frametitle{Properties of DPG}
 \begin{itemize}
-\item DPG provides the best approximation in the energy norm 
+\item DPG provides the best approximation in the \textcolor{red}{energy norm}
 \[
-\|u\|_E = \|Bu\|_{V'} = \sup \frac{b(u,v)}{\nor{v}_V}.
+\|u\|_E = \|Bu\|_{V'} = \sup_{\nor{v}_V=1} \left|b(u,v)\right|.
 \]
-\item The actual energy error is computable through the residual
+\item The energy error is computable through the residual
 \[
@@
 \]
-where $(e,\delta v)_V = l(v)-b(u_h,v)$ for all $v\in V$. 
+where the \textcolor{red}{error representation function} $e$ is defined through $(e,\delta v)_V = l(v)-b(u_h,\delta v)$ for all $\delta v\in V$. 
 \end{itemize}
@@
 \[
-b\left(\left(u, \widehat{u}\right),v\right) \coloneqq \langle \widehat{u}, \jump{v}
-\rangle_{\Gh} - (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh}.
+b\left(\left(u, \widehat{u}\right),v\right) \coloneqq \sum_K\langle \widehat{u},v \rangle_{\delta K} + (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh}.
 \]
-where
+Under proper assumptions, $\sum_K\langle \widehat{u},v \rangle_{\delta K} = \langle \widehat{u}, \jump{v} \rangle_{\Gh}$. The energy setting is
 \[
@@
 \]
-where $D(A_h^*)$ is the broken graph space of $A_h^*$, and $\gamma(D(A))$ the trace space of the graph space of operator $A$.
+where $D(A_h^*)$ is the broken graph space of the formal adjoint $A_h^*$, and $\gamma(D(A))$ the trace space of the graph space of operator $A$.
 }
@@
 \frame{
-\frametitle{Canonical norms for the ultra-weak formulation}
-Under the ultra-weak formulation, we have the following relations:
+\frametitle{Test and trial norms for the ultra-weak formulation}
+Under the ultra-weak formulation, we have the following equivalence relations:
 \begin{figure}[!h]
@@
   \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2$ \\
-%\hline
-%Quasi-optimal trial norm & & Canonical test norm \\
-%\hline
 $\nor{u}_{\L}^2+\sup_{v } \left(\frac{\LRa{\widehat{u},
@@
 \end{tabular}
-\caption{The optimal \textit{test} norm is naturally derived by beginning with the canonical norm on the trial space, while the quasi-optimal \textit{trial} norm is derived from beginning with the canonical norm on the test space.}
+\caption{The optimal \textit{test} norm is naturally derived by beginning with the canonical norm on the trial space, while the quasi-optimal \textit{trial} norm is derived from beginning with the canonical (\emph{graph}) norm on the test space.}
 \end{figure}
@@
 
-\section{A Robust DPG Method}
+%\frame{
+%\frametitle{The canonical test norm}
+%Under the ultra-weak formulation, we have the natural norm
+%\[
+%\nor{\LRp{u,\widehat{u}}} = \|u\|^2_{\L} + \|\widehat{u}\|^2 
+%\]
+%which generates a test norm \emph{equivalent} to 
+%\[
+%\nor{v}_{V_{\rm opt}} \coloneqq \|A_h^*v\|_{\L}^2 +\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},\jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2
+%\]
+%This norm is not localizable, so we instead substitute the jump terms for an $L^2$ term, giving us the \emph{graph norm}
+%\[
+%\nor{v}_V \coloneqq \|A_h^*v\|_{\L}^2 + \nor{v}_{L^2}.
+%\]
+%}
+
+\section{A Robust DPG Method for Convection-Diffusion}
 
@@
 b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh}&\\
+\left( v, \tau \right)\right) = \left(u,\grad_h\cdot \tau - \beta \cdot \grad_h
+v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad_h v\right)_{\Oh}&\\
  - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n,\jump{v} }_{\Gh}&,
 \end{align*}
-where $\widehat{f}_n \coloneqq \beta_n u - \sigma_n$. Note that $\div$ and $\grad$ are taken to act elementwise.
+where $\widehat{f}_n \coloneqq \beta_n u - \sigma_n$, and $\grad_h\cdot$ and $\grad_h$ act elementwise.
 }
@@
 \frame{
-\frametitle{Quasi-optimal norm under convection-diffusion}
-For convection-diffusion, the quasi-optimal test norm is 
+\frametitle{Graph norm under convection-diffusion}
+For convection-diffusion, the quasi-optimal (graph) test norm is 
 \[
@@
 \|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 +
-\|v\|_{L^2}^2 + \|\tau\|_{L^2}^2.
+\|v\|_{L^2}^2.
 \]
@@
 \frame{
-\frametitle{Bilinear forms and induced adjoints}
+\frametitle{Determining an alternative test norm}
 Recall the convection-diffusion bilinear form
@@
 \end{align*}
-We recover $\nor{u}_{L^2(\Omega)}$ by choosing continuous $\LRp{v,\tau}$ s.t.\
+We recover $\nor{u}_{L^2(\Omega)}$ by choosing continuous $\LRp{v,\tau}$ satisfying the \emph{adjoint equations}
 \begin{align*}
 \div\tau - \beta \cdot \grad v   &= u\\
-\frac{1}{\epsilon}\tau - \grad v &= 0
+\frac{1}{\epsilon}\tau + \grad v &= 0
 \end{align*}
@@
 \frame{
-\frametitle{Determining an alternative test norm}
-``Necessary'' conditions for robustness --- let $\boldsymbol U = \LRp{u,\sigma,\widehat{u},\widehat{f}_n}$, then, by choosing specific $\LRp{v,\tau}$, 
+\frametitle{A robust bound}
+``Necessary'' conditions for robustness --- let $\boldsymbol U = \LRp{u,\sigma,\widehat{u},\widehat{f}_n}$, then, by choosing specific $\LRp{v,\tau}$ satisfying the adjoint equations,
 \[
@@
 \[
-\nor{u}^2_{L^2(\Omega)} \lesssim \nor{\boldsymbol U}_E
+\nor{u}_{L^2(\Omega)} \lesssim \nor{\boldsymbol U}_E
 \]
-}
-
-\frame{
-\frametitle{``Building blocks'' norm}
-Test norm quantities are robustly bounded from above by $\nor{u}_{L^2(\Omega)}$.  
-\[
-\|\left(v,\tau\right)\|_{V,K}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2.
-\]
-Problem: boundary layers in optimal test functions:
-\begin{figure}[!h]
-\centering
-\subfigure{\includegraphics[scale=.15]{figs/mesh1.png}}
-\subfigure{\includegraphics[scale=.15]{figs/sol1.png}}
-\caption{The $v$ component of the optimal test function corresponding to flux $\widehat{u} = x(1-x)$ on the bottom side of a unit element for $\epsilon = 0.01$.}
-\label{fig:boundaryTest}
-\end{figure}
+\textbf{Test norm should measure the adjoint solution robustly.}
 }
 \frame{
-\frametitle{Mesh-scaled test norms}
-%To avoid boundary layers in the optimal test functions, we scale the $L^2$ contributions of $v$ by $C_v(K)$, such that, when transformed to the reference element, both $C_v(K)\|v\|^2$ and $\epsilon\|\grad v\|^2$ are of the same magnitude.
-Similarly, we scale the $L^2$ contributions of $\tau$ by $C_\tau(K)$ such that $\frac{C_\tau(K)}{\epsilon} \|\tau\|^2$ and $\|\div \tau\|^2$ are of the same magnitude as well.
-
-Our test norm, as defined over a single element $K$, is now
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 +&\\
-\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2&.
-\end{align*}
-\begin{itemize}
-\item $v$ and $\tau$ decoupled.
-\item Coefficients are $O(1)$ after transforming to the unit element.
-\end{itemize}
-%This modified test norm avoids boundary layers in the locally computed optimal test functions, but for adaptive meshes, provides additional stability in areas of heavy refinement, where the best approximation error tends to be large and stronger robustness is most necessary.
-This leads to a test norm which produces easily approximable optimal test functions, but still provides \textit{asymptotically} the strongest test norm and tightest robustness results in the areas of highest error.
-}
-
-\frame{
 \frametitle{Dirichlet inflow boundary condition}
-Standard choice of boundary condition: $u = u_0$ on inflow boundary $\Gamma_{\rm in}$. 
+Standard choice of boundary condition: $u = u_0$ on inflow boundary $\Gamma_{\rm in}$, induces boundary layers in adjoint problems. 
 \begin{figure}[h!]
 \centering
-\subfigure[Primal problem]{\includegraphics[scale=.22]{figs/primalDir.png}}
-\subfigure[Adjoint problem]{\includegraphics[scale=.22]{figs/adjointDir.png}}
+\subfigure[Primal problem]{\includegraphics[scale=.23]{figs/primalDir.png}}
+\subfigure[Adjoint problem]{\includegraphics[scale=.23]{figs/adjointDir.png}}
 \caption{For the standard Dirichlet inflow condition, the solution to the adjoint problem can develop strong boundary layers at the outflow of the adjoint problem. }
 \end{figure}
-
 }
@@
 \frametitle{New inflow boundary condition on $\widehat{f}_n$}
-Non-standard choice of boundary condition: $\widehat{f}_n = \beta_n u_0$ on $\Gamma_{\rm in}$. 
+Non-standard choice of boundary condition: $\widehat{f}_n = \beta_n u_0$ on $\Gamma_{\rm in}$, induces smoother adjoint problems. 
 \begin{figure}[h!]
 \centering
-\subfigure[Primal problem]{\includegraphics[scale=.22]{figs/primal.png}}
-\subfigure[Adjoint problem]{\includegraphics[scale=.22]{figs/adjoint.png}}
+\subfigure[Primal problem]{\includegraphics[scale=.23]{figs/primal.png}}
+\subfigure[Adjoint problem]{\includegraphics[scale=.23]{figs/adjoint.png}}
 \caption{Under the new inflow condition, the wall-stop boundary condition is relaxed to a zero-stress condition at the outflow boundary of the adjoint problem.}
@@
 \frametitle{Test norms and adjoint solutions}
+\textbf{Intuition:} the effectiveness of DPG under a test norm is governed by how a \textbf{specific test norm} measures the \textbf{solutions of the adjoint problem}.
+
+\begin{figure}[!h]
+\subfigure[Dirichlet inflow]{\includegraphics[scale=.35]{figs/dirichletBC.png}}
+\subfigure[``Convection'' inflow]{\includegraphics[scale=.35]{figs/newBC.png}}
+\caption{DPG solutions to convection-diffusion for both inflow conditions using an $H^1$ test norm.}
+\end{figure}
+}
+
+%\frame{
+%\frametitle{``Building blocks'' norm}
+%Test norm quantities are robustly bounded from above by $\nor{u}_{L^2(\Omega)}$.  
+%\[
+%\|\left(v,\tau\right)\|_{V,K}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2.
+%\]
+%Problem: boundary layers in optimal test functions:
+%\begin{figure}[!h]
+%\centering
+%\subfigure{\includegraphics[scale=.15]{figs/mesh1.png}}
+%\subfigure{\includegraphics[scale=.15]{figs/sol1.png}}
+%\caption{The $v$ component of the optimal test function corresponding to flux $\widehat{u} = x(1-x)$ on the bottom side of a unit element for $\epsilon = 0.01$.}
+%\label{fig:boundaryTest}
+%\end{figure}
+%}
+\frame{
+\frametitle{Adjoint estimates, or ``norm building blocks''}
+For solutions $(v,\tau)$ of the adjoint equations, the following quantities are robustly bounded from above by $\nor{u}_{L^2(\Omega)}$.  
+\begin{align*}
+&\|v\|, \sqrt{\epsilon} \|\grad v\|, \|\beta \cdot \grad v\| \\
+&\| \div \tau\|, \frac{1}{\sqrt{\epsilon}}\|\tau\|.
+\end{align*}
+We will construct a test norm through a combination of the above quantities, such that
 \begin{itemize}
-\item Standard choice of boundary condition: $u = u_0$ on inflow boundary $\Gamma_{\rm in}$: induces boundary layers in adjoint problems.
-\item Non-standard choice of boundary condition: $\widehat{f}_n = \beta_n u_0$ on $\Gamma_{\rm in}$: induces smoother adjoint problems.
+\item $v$ and $\tau$ decoupled (no systems).
+\item Coefficients are of equal order after transforming to the unit element (no boundary layers).
 \end{itemize}
-\textbf{Intuition:} the effectiveness of DPG under a test norm is governed by how a \textbf{specific test norm} measures the \textbf{solutions of the adjoint problem}. 
+}
+\frame{
+\frametitle{Mesh-scaled test norms}
+Our test norm, as defined over a single element $K$, is now
+\begin{align*}
+\|\left(v,\tau\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 +&\\
+\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2&.
+\end{align*}
+which induces the proven \emph{robust} bound 
+\[
+\nor{u}_{L^2(\Omega)}+ \nor{\sigma}_{L^2(\Omega)} + \epsilon\nor{\widehat{u}} + \sqrt{\epsilon} \nor{\widehat{f}_n} \lesssim \nor{\LRp{u,\sigma,\widehat{u},\widehat{f}_n}}_E.
+\]
 }
@@
 \subfigure{
-\includegraphics[scale=.23]{figs/errorrates_wallBC.png}
+\includegraphics[scale=.24]{figs/errorrates_wallBC.png}
 }
 \subfigure{
-\includegraphics[scale=.23]{figs/L2energyratio_wallBC.png}
+\includegraphics[scale=.24]{figs/L2energyratio_wallBC.png}
 }
@@
 \end{figure}
+}
 
-}
 %\frame{
@@
 \frametitle{Regularization}
-For $\beta = (-y,x)^T$ on $\Omega = [-1,1]^2$, and zero normal stress outflow conditions. Ill posed in the convection setting. Similar tests have been done with discontinuous data.
+For $\beta = (.5-y,x-.5)^T$ on $\Omega = [0,1]^2$, and zero normal stress outflow conditions. Ill posed in the convection setting. Similar tests have been done with discontinuous data.
 
@@
 \subfigure{
-\includegraphics[scale=.34]{figs/vortex.png}
+\includegraphics[scale=.35]{figs/vortex.png}
 }
 \subfigure{
-\includegraphics[scale=.34]{figs/vortexMesh.png}
+\includegraphics[scale=.35]{figs/vortexMesh.png}
 }
@@
 
-\section{Proposed Work}
+\section{DPG for nonlinear problems}
 \frame{
 \frametitle{DPG for nonlinear problems}
-\textcolor{red}{REWORK. HOW TO DO THIS SECTION?}
-Begin with the nonlinear variational formulation
-$b(u,v) = l(v)$, linear in $v$, but not in $u$.  An appropriate linearization gives
+
+Given some linearization technique, we can measure 
+\begin{itemize}
+\item size of the linearized update $\Delta u$
 \[
-b_u(\Delta u,v) = l(v) - b(u,v),
+\|\Delta u\|_E \coloneqq \nor{B_u\Delta u}_{V'} = \nor{R_V^{-1} B_u\Delta u}_V 
 \]
-Let $B(u)$ and $B_u\Delta u$ be the variational operators associated with $b(u,v)$ and $b_u(\Delta u,v)$. 
-\begin{align*}
-\|\Delta u\|_E &\coloneqq \nor{B_u\Delta u}_{V'} = \nor{R_V^{-1} B_u\Delta u}_V \\
-\nor{R(u)}_E &\coloneqq \nor{B(u)-l}_E = \nor{B(u) - l}_{V'}  = \nor{R_V^{-1} B(u)-l}_V 
-\end{align*}
+\item the nonlinear residual 
+\[
+\nor{R(u)}_E \coloneqq \nor{B(u)-l}_E = \nor{B(u) - l}_{V'}  = \nor{R_V^{-1}\LRp{B(u)-l}}_V 
+\]
+\end{itemize}
+We will work with either full Newton-Raphson or pseudo-timestepping linearization.
+
+%\textcolor{red}{REWORK. HOW TO DO THIS SECTION?}
+%Begin with the nonlinear variational formulation
+%$b(u,v) = l(v)$, linear in $v$, but not in $u$.  An appropriate linearization gives
+%\[
+%b_u(\Delta u,v) = l(v) - b(u,v),
+%\]
+%Let $B(u)$ and $B_u\Delta u$ be the variational operators associated with $b(u,v)$ and $b_u(\Delta u,v)$. 
+%\begin{align*}
+%\|\Delta u\|_E &\coloneqq \nor{B_u\Delta u}_{V'} = \nor{R_V^{-1} B_u\Delta u}_V \\
+%\nor{R(u)}_E &\coloneqq \nor{B(u)-l}_E = \nor{B(u) - l}_{V'}  = \nor{R_V^{-1} B(u)-l}_V 
+%\end{align*}
 }
@@
 \end{align*}
-i.e.\ nonlinear convection-diffusion.
+i.e.\ nonlinear convection-diffusion. Solution is achieved using Newton-Raphson.
 \end{column}
@@
 \frame{
-\frametitle{Compressible Navier-Stokes equations}
+\frametitle{Compressible Navier-Stokes equations (ideal gas)}
 \begin{align*}
@@
 }
+
 \frame{
@@
 \frame{
-\frametitle{Proposed work: Area B}
+\frametitle{Future work: Area B}
 \begin{itemize}
@@
 
-Numerical experiments have been done using the higher-order adaptive codebase Camellia, built upon the Trilinos library and designed by Nathan Roberts.
+Numerical experiments use the higher-order adaptive codebase Camellia, built upon the Trilinos library by Nathan Roberts.
 %The framework for arbitrary-irregularity anisotropic refinements in both $h$ and $p$ is in place, and the code is partially parallelized.
@@
 
-The error representation function has been shown to yield an effective and natural residual with which to drive refinement, which we hope to generalize to yield anisotropic adaptive schemes. 
-\textcolor{red}{GET GRAPHICS FOR ANISOTROPY}
+The error representation function drives refinement effectively, and we hope to generalize its use to anisotropic adaptive schemes. 
+\begin{figure}
+\subfigure{\includegraphics[scale = .18]{figs/anisotropy/b5.png}}
+\subfigure{\includegraphics[scale = .186]{figs/anisotropy/v6.png}}
+\end{figure}
 \end{itemize}
@@
 \]
-produces a Hessian-based DPG method 
+produces a Hessian-based DPG method, which solves
 \[
-b_u(\Delta u,v) + b''(\Delta u, \delta u, v_{R(u)}) = r(u,v) = l(v) - b(u,v),
+b_u(\Delta u,v) + b''(\Delta u, \delta u, v_{R(u)}) = l(v) - b(u,v) = r(u,v),
 \]
-which aims to minimize the nonlinear dual residual instead of the linearized problem residual. 
+and aims to minimize the nonlinear dual residual instead of the linearized problem residual. 
 }
 
-\section{Area C}
+\subsection{Area C}
 \frame{
-\frametitle{Proposed work: Area C}\
-textcolor{red}{GET GRAPHICS FOR EACH}
+\frametitle{Proposed work: Area C}
 \begin{itemize}
@@
 \item{\textbf{Proposed: regularized Euler.}}
+%\textcolor{red}{Graphics?}
 \end{itemize}

### 2012-08-08 docs/Jesse/Proposal/proposalPres.tex
committing tex and bib files for proposal

@@
 \usepackage{pifont}
+
+\usepackage{bibentry}
+\nobibliography*
+
+%\usepackage[osf]{mathpazo}
+%\usepackage{mathpazo}
+%\renewcommand\rmdefault{ptm}
 
@@
 
-\title{A Discontinuous Petrov-Galerkin method for compressible flow problems}
-\author{Jesse Chan \\ Supervisors: Leszek Demkowicz, Robert Moser}
+% removes nav symbols
+\beamertemplatenavigationsymbolsempty
+
+% defines newblock as null, giving compile issues otherwise
+\let\newblock\relax
+
+\institute[ICES]{Institute for Computational Engineering and Sciences}
+
+\title[A DPG method for Compressible Flow]{A Discontinuous Petrov-Galerkin method for compressible flow problems}
+\date{August 8, 2012}
+\author[J. Chan, L. Demkowicz, R. Moser]{Jesse Chan \\ Supervisors: Leszek Demkowicz, Robert Moser \\ Committee: Todd Arbogast, Omar Ghattas, Venkat Raman}
 
@@
 \frame{
-\frametitle{Compressible flow problems}
+\frametitle{Phenomena in compressible flow}
 \begin{figure}
@@
 \frame{
-\frametitle{Goal: Compressible Navier-Stokes equations}
+\frametitle{Compressible Navier-Stokes equations}
 \begin{columns}[c]
@@
 \begin{itemize}
-\item{} Resolving solution features (sharp, localized $O(\Reyn^{-1})$ phenomena)
-\begin{itemize}
-\item{} Shocks, boundary layers
-\item{} Turbulent phenomena
-\end{itemize}
+\item{} Resolving solution features (sharp, localized viscous-scale phenomena)
+\begin{itemize}
+\item{} Shocks
+\item{} Boundary layers - resolution needed for drag/load
+\item{} Turbulence (non-localized)
+\end{itemize}
+\item{} Nonlinear convergence and uniqueness of solutions
 \item{} Stability of numerical schemes
@@
 \end{itemize}
-\item{} Nonlinear convergence and uniqueness of solutions
 \end{itemize}
@@
 \end{columns}
-\vspace{1cm}
+\vspace{.2cm}
 \begin{center}
@@
 \[
-b(u,v) = l(v) 
+b(u,v) = \ell(v), \quad u,v\in H^1_0([0,1])
 \]
@@
 b(u,v) &= \int_\Omega -\beta uv' + \epsilon u'v' \\
-l(v) &= \int_\Omega f v 
+\ell(v) &= \int_\Omega f v 
 \end{align*}
@@
 \includegraphics[scale=.35]{figs/GalerkinOscTight.png}
-\caption{Oscillations in the standard Galerkin for underresolved meshes and small $\epsilon$.}
+\caption{Solution for $f=1$. Oscillations in the standard Galerkin method for large Peclet numbers ${\rm Pe} \coloneqq \frac{h}{\epsilon}$.}
 \end{figure}
@@
 b_{\rm SUPG}(u,v) &= b(u,v)+ \sum_{K} \int_{K} \tau \LRp{L_{\rm adv} v} L u \\
-l_{\rm SUPG}(v) &= l(v) + \sum_{K} \int_{K} \tau \LRp{L_{\rm adv}v} f.
+l_{\rm SUPG}(v) &= \ell(v) + \sum_{K} \int_{K} \tau \LRp{L_{\rm adv}v} f.
 \end{align*}
@@
 \begin{columns}[c]
-\begin{column}{.47\textwidth}
+\begin{column}{.44\textwidth}
 \vspace{-.5cm}
@@
 %\item{} Recovers ``exact'' artificial diffusion for $f=0$.
-\item{} Effective for $f\neq 0$, unlike ``exact'' artificial diffusion.
+\item{} Effective for $f\neq 0$. %``exact'' artificial diffusion.
 \item{} \emph{Residual-based} stabilization. 
@@
 \end{column}
-\begin{column}{.52\textwidth}
-\begin{figure}
-\centering
-\includegraphics[scale=.35]{figs/SUPG.png}
+\begin{column}{.54\textwidth}
+\begin{figure}
+\centering
+\includegraphics[scale=.38]{figs/SUPG.png}
 %\caption{Exact, Bubnov-Galerkin, and SUPG solutions.}
@@
 \frame{
+\begin{columns}
+\begin{column}{.49\textwidth}
 Can be interpreted as a \emph{Petrov-Galerkin} method,
 \[
-b\LRp{u,\tilde{v}_{i}} = l\LRp{\tilde{v}_{i}}, \quad \forall i = 1,\ldots,N-1,
-\]
-where the SUPG test function $\tilde{v}_{i}$ is defined elementwise as
+b\LRp{u,\tilde{v}_{i}} = \ell\LRp{\tilde{v}_{i}}, \quad \forall i = 1,\ldots,N-1,
+\]
+where the SUPG test function $\tilde{v}_{i}$ is defined elementwise as\footnotemark
 \[
@@
 \]
-\begin{figure}
-\centering
-\subfigure{\includegraphics[scale=.185]{figs/SUPGtest.png}}
+\end{column}
+\begin{column}{.49\textwidth}
+\begin{figure}
+\centering
+\subfigure{\includegraphics[scale=.16]{figs/SUPGtest.png}}
 \caption{SUPG test function $v_i$.}
 \end{figure}
+\end{column}
+\end{columns}
+\footnotetext{\bibentry{SUPG}}
 }
@@
 \frametitle{DPG: a minimum residual method via optimal testing}
-Given
-\[
-b(u,v) = l(v), \quad u\in U, \quad v\in V
-\]
-identify $B:U\rightarrow V'$ such that 
-\[
-\langle Bu,v\rangle_V \coloneqq b(u,v), \quad u\in U, v\in V.
-\]
-Then, $b(u_h,v) = l(v)$ is equivalent to the equation in $V'$
-\[
-Bu_h = l
-\]
-We seek to minimize the functional on $V'$
-\[
-J(u_h) = \frac{1}{2}\|Bu_h-l\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(u_h,v)-l(v)|^2}{\nor{v}_V^2}.
+Given a trial space $U$ and Hilbert test space $V$,
+\[
+b(u,v) = \ell(v), \quad u\in U, \quad v\in V
+\]
+This is equivalent to the operator equation posed in $V'$
+\[
+Bu = \ell
+\]
+if we identify $B:U\rightarrow V'$ and $\ell\in V'$ such that 
+\begin{align*}
+\langle Bu,v\rangle_V &\coloneqq b(u,v), \quad u\in U, v\in V,\\
+\langle \ell,v\rangle_V &\coloneqq \ell(v), \quad v\in V.
+\end{align*}
+We seek to minimize the dual functional over $U_h \subset U$
+\[
+J(u_h) = \frac{1}{2}\|Bu_h-\ell\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(u_h,v)-\ell(v)|^2}{\nor{v}_V^2}.
 \]
@@
 \begin{equation*}
-\min_{u_h\in U_h} J(u_h) = \frac{1}{2}\left\|Bu_h-l\right\|_{V'}^2 =  \frac{1}{2}\left\|R_V^{-1}(Bu_h-l)\right\|_V^2.
+\min_{u_h\in U_h} J(u_h) = \frac{1}{2}\left\|Bu_h-\ell\right\|_{V'}^2 =  \frac{1}{2}\left\|R_V^{-1}(Bu_h-\ell)\right\|_V^2.
 \end{equation*}
@@
 \begin{align*}
-\left(R_V^{-1}(Bu_h-l),R_V^{-1}B\delta u\right)_V &= 0, \quad \forall \delta u \in U.\\
-\rightarrow \LRa{(Bu_h-l),R_V^{-1}B\delta u} &= 0, \\
-\rightarrow b(u_h,R_V^{-1}B\delta u) - l(R_V^{-1}B\delta u) &= 0
+\left(R_V^{-1}(Bu_h-\ell),R_V^{-1}B\delta u\right)_V &= 0, \quad \forall \delta u \in U_h.\\
+\rightarrow \LRa{(Bu_h-\ell),R_V^{-1}B\delta u} &= 0, \\
+\rightarrow b(u_h,R_V^{-1}B\delta u) - \ell(R_V^{-1}B\delta u) &= 0
 \end{align*}
@@
 \frame{
-\frametitle{Minimum residual methods and optimal testing}
-For $\delta u \in U$, define the \textcolor{red}{optimal test function} $v_{\delta u}$. 
+\frametitle{Summary: select test functions to minimize residuals}
+For $\delta u \in U_h$, define the \textcolor{red}{optimal test function} $v_{\delta u}$. 
 \begin{equation*}
@@
 \end{equation*} 
-Then, the least-squares residual $J(u_h) = \frac{1}{2}\left\|Bu_h-l\right\|_{V'}^2$ is minimized by the solution of
-\[
-b\LRp{u_h,v_{\delta u}} = l\LRp{v_{\delta u}}, \quad \forall \delta u \in U
+Then, the residual $J(u_h) = \frac{1}{2}\left\|Bu_h-\ell\right\|_{V'}^2$ is minimized by the solution of
+\[
+b\LRp{u_h,v_{\delta u}} = \ell\LRp{v_{\delta u}}, \quad \forall \delta u \in U_h.
 \]
@@
 \frametitle{Practical details of DPG}
-\begin{itemize}
-\item By choosing a \emph{broken} test space $V$ and \textcolor{red}{localizable} norm $\nor{v}_V = \sum_K \nor{v}_{V(K)}$, test functions can be determined locally.
-\item In practice, we use the \textcolor{red}{enriched space} $V \coloneqq V_h$, where $\dim(V_h) > \dim(U_h)$ elementwise, and \textcolor{red}{optimal test functions} are approximated by solving
-\[
-\LRp{v_{\delta u},\delta v}_V = b(\delta u,\delta v), \quad \delta u\in U, \quad v_{\delta u},\delta v\in V_h
-\]
-Typically, if $U_h = \mathcal{P}^p(\mathbb{R}^n)$, $V_h = \mathcal{P}^{p+\triangle p}(\mathbb{R}^n)$, where $\triangle p \geq n$. 
-\end{itemize}
+Computation of $v_{\delta u} \coloneqq R_V^{-1}B\delta u$ is \textbf{global} and \textbf{infinite-dimensional}.
+\begin{itemize}
+\item By choosing a \textcolor{red}{broken} test space $V$ and \textcolor{red}{localizable} norm $\nor{v}_V^2 = \sum_K \nor{v}_{V(K)}^2$, test functions can be determined locally.
+\item In practice, we use an \textcolor{red}{enriched space} $V_h \subset V$, where $\dim(V_h) > \dim(U_h)$ elementwise, and \textcolor{red}{optimal test functions} are approximated by computing $v_{\delta u} \coloneqq R_{V_h}^{-1}B\delta u \in V_h$ through\footnote{\bibentry{DPG2}}
+\[
+\LRp{v_{\delta u},\delta v}_V = b(\delta u,\delta v), \quad \delta u\in U_h, \quad \forall \delta v\in V_h
+\]
+Typically, if $U_h = \mathcal{P}^p(\mathbb{R}^n)$, $V_h = \mathcal{P}^{p+\triangle p}(\mathbb{R}^n)$, where $\triangle p \geq n$.\footnote{\bibentry{practicalDPG}} 
+\end{itemize}
+%\footnotetext{\bibentry{DPG2}}
 }
@@
 B_{ji} &= b(\phi_j,v_i),\\
-l_i &= l(v_i),
-\end{align*}
-DPG solves the discrete system
-\begin{align*}
-(B^T R_V^{-1}B) u  &= (B^T R_V^{-1}) l,
+l_i &= \ell(v_i),
+\end{align*}
+DPG solves the discrete system for degrees of freedom $u$
+\begin{align*}
+\LRp{B^T R_V^{-1}B} u  &= \LRp{B^T R_V^{-1}} l,
 \end{align*}
@@
 \frametitle{Properties of DPG}
+Additional properties of DPG include\footnotemark
 \begin{itemize}
@@
 \]
-where the \textcolor{red}{error representation function} $e$ is defined through $(e,\delta v)_V = l(v)-b(u_h,\delta v)$ for all $\delta v\in V$. 
-\end{itemize}
+where the \textcolor{red}{error representation function} $e$ is defined through $(e,\delta v)_V = \ell(v)-b(u_h,\delta v)$ for all $\delta v\in V$. 
+\end{itemize}
+\footnotetext{\bibentry{DPG3pub}}
 }
@@
 \begin{columns}
-\begin{column}{.65\textwidth}
+\begin{column}{.64\textwidth}
 Given a first order system $Au = f$, we identify the \textbf{\emph{partition}} $\Oh$ and \textbf{\textcolor{red}{mesh skeleton}} \textcolor{red}{$\Gh$}.
 \end{column}
-\begin{column}{.33\textwidth}
+\begin{column}{.34\textwidth}
 %\[
@@
 \[
-b\left(\left(u, \widehat{u}\right),v\right) \coloneqq \sum_K\langle \widehat{u},v \rangle_{\delta K} + (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh}.
-\]
-Under proper assumptions, $\sum_K\langle \widehat{u},v \rangle_{\delta K} = \langle \widehat{u}, \jump{v} \rangle_{\Gh}$. The energy setting is
+b\left(\left(u, \widehat{u}\right),v\right) \coloneqq \sum_K\langle \widehat{u},v \rangle_{\partial K} + (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh}.
+\]
+Under proper assumptions, $\sum_K\langle \widehat{u},v \rangle_{\partial K} = \langle \widehat{u}, \jump{v} \rangle_{\Gh}$, with energy setting
 \[
@@
 \]
-where $D(A_h^*)$ is the broken graph space of the formal adjoint $A_h^*$, and $\gamma(D(A))$ the trace space of the graph space of operator $A$.
-}
-
-\frame{
-\frametitle{Test and trial norms for the ultra-weak formulation}
-Under the ultra-weak formulation, we have the following equivalence relations:
-\begin{figure}[!h]
-\centering
-\begin{tabular}{l c c}
-Trial norm & & Test norm \\
-\hline
-$\boxed{\|u\|^2_{\L} + \|\widehat{u}\|^2}$ & $\Longrightarrow$  & $\|A_h^*v\|_{\L}^2
-+\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},
-  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2$ \\
-$\nor{u}_{\L}^2+\sup_{v } \left(\frac{\LRa{\widehat{u},
-  \jump{v}}_{\Gh}}{\|v\|_V}\right)^2$ &  $\Longleftarrow$ & $\boxed{\|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2}$
-\end{tabular}
-\caption{The optimal \textit{test} norm is naturally derived by beginning with the canonical norm on the trial space, while the quasi-optimal \textit{trial} norm is derived from beginning with the canonical (\emph{graph}) norm on the test space.}
-\end{figure}
-}
-
-%\frame{
-%\frametitle{The canonical test norm}
-%Under the ultra-weak formulation, we have the natural norm
-%\[
-%\nor{\LRp{u,\widehat{u}}} = \|u\|^2_{\L} + \|\widehat{u}\|^2 
-%\]
-%which generates a test norm \emph{equivalent} to 
-%\[
-%\nor{v}_{V_{\rm opt}} \coloneqq \|A_h^*v\|_{\L}^2 +\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},\jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2
-%\]
-%This norm is not localizable, so we instead substitute the jump terms for an $L^2$ term, giving us the \emph{graph norm}
-%\[
-%\nor{v}_V \coloneqq \|A_h^*v\|_{\L}^2 + \nor{v}_{L^2}.
-%\]
-%}
+where $D(A_h^*)$ is the broken graph space of the formal adjoint $A_h^*$, and $\gamma(D(A))$ the trace space of the graph space of operator $A$.\footnote{\bibentry{analysisDPG}}
+}
+
+\frame{
+\frametitle{The canonical ``graph'' test norm}
+Recall $\nor{u}_E \coloneqq \sup_{v\in V\setminus\{0\}}\frac{b(u,v)}{\nor{v}_V}$. Under the ultra-weak formulation, the trial norm 
+\[
+\nor{\LRp{u,\widehat{u}}}_U \coloneqq \|u\|^2_{\L} + \|\widehat{u}\|^2
+\] 
+generates a test norm \emph{equivalent} to 
+\[
+\nor{v}_{V_{\rm opt}} \coloneqq \|A_h^*v\|_{\L}^2 +\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},\jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2.
+\]
+This norm is not localizable, so we instead substitute the jump terms for an $L^2$ term, giving us the \emph{graph norm}\footnote{\bibentry{Bui-ThanhDemkowiczGhattas11b}}
+\[
+\nor{v}_V \coloneqq \|A_h^*v\|_{\L}^2 + \nor{v}_{L^2}.
+\]
+}
+
+\frame{
+\frametitle{Goal: robust higher order adaptive methods}
+\begin{columns}
+\begin{column}{.45\textwidth}
+Our aim is to design an adaptive method for compressible laminar flows that is 
+\begin{itemize}
+\item robust in Reynolds number
+\item stable for arbitrary elements
+\end{itemize}
+
+This proposal will outline
+\begin{enumerate}
+\item a robust DPG method for convection-diffusion,
+\item extension to nonlinear problems and systems,
+\item proposed work.
+\end{enumerate}
+
+\end{column}
+\begin{column}{.54\textwidth}
+\begin{figure}
+\centering
+\subfigure{\includegraphics[scale=.23]{figs/Re1000p2/u2_full.png}}
+\subfigure{\includegraphics[scale=.37]{figs/Re1000p2/mesh6.png}}
+\caption{$u_2$ and $p=2$ mesh for $\Reyn = 1000$.}
+\end{figure}
+\end{column}
+\end{columns}
+}
 
@@
 v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad_h v\right)_{\Oh}&\\
- - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n,\jump{v} }_{\Gh}&,
-\end{align*}
-where $\widehat{f}_n \coloneqq \beta_n u - \sigma_n$, and $\grad_h\cdot$ and $\grad_h$ act elementwise.
+  - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
+\end{align*}
+where $\widehat{f}_n \coloneqq \beta_n u - \sigma_n$ and $\LRa{\widehat{f}_n,\jump{v} }_{\Gh}$ is defined 
+\[
+\LRa{\widehat{f}_n,\jump{v} }_{\Gh}\coloneqq \sum_K\int_{\partial K}{\rm sgn}(\vec{n}) \, \widehat{f}_n v.
+\]
 }
@@
 \frametitle{Graph norm under convection-diffusion}
-For convection-diffusion, the quasi-optimal (graph) test norm is 
-\[
-\|\left(v,\tau\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v
-\|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 +
-\|v\|_{L^2}^2.
+For convection-diffusion, the graph test norm is defined elementwise
+\[
+\|\left(v,\tau\right)\|_{V(K)}^2 = \| \div \tau - \beta \cdot \grad v
+\|_{L^2(K)}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2(K)}^2 +
+\|v\|_{L^2(K)}^2.
 \]
@@
 v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh}&\\
- - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n,\jump{v} }_{\Gh}&,
-\end{align*}
-We recover $\nor{u}_{L^2(\Omega)}$ by choosing continuous $\LRp{v,\tau}$ satisfying the \emph{adjoint equations}
+ - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
+\end{align*}
+We recover $\nor{u}^2_{L^2(\Omega)}$ by choosing conforming $\LRp{v,\tau}$ satisfying the \emph{adjoint equations}
 \begin{align*}
@@
 \end{align*}
-where boundary conditions are s.t.\ $\LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh}$ and $\LRa{ \widehat{f}_n,\jump{v} }_{\Gh}$ vanish. 
+with boundary conditions s.t.\ $\LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gamma}$ and $\LRa{ \widehat{f}_n,\jump{v} }_{\Gamma}$ vanish.
 }
@@
 \frametitle{A robust bound}
-``Necessary'' conditions for robustness --- let $\boldsymbol U = \LRp{u,\sigma,\widehat{u},\widehat{f}_n}$, then, by choosing specific $\LRp{v,\tau}$ satisfying the adjoint equations,
+``Necessary'' conditions for robustness --- let $\boldsymbol U = \LRp{u,\sigma,\widehat{u},\widehat{f}_n}$. Then, by choosing specific $\LRp{v,\tau}$ satisfying the adjoint equations,
 \[
@@
 \]
-If $ \nor{\LRp{v,\tau}}_V \lesssim \|u\|_{L^2(\Omega)}$, then we have the robust bound
+Let $\lesssim$ denote a robust bound - \textcolor{red}{if $ \nor{\LRp{v,\tau}}_V \lesssim \|u\|_{L^2(\Omega)}$}, then we have that
 \[
@@
 \]
-\textbf{Test norm should measure the adjoint solution robustly.}
-}
+\textbf{Main idea: the \textcolor{red}{test norm} should measure \textcolor{red}{adjoint solutions} robustly.}
+}
+
+\frame{
+\frametitle{Choice of inflow boundary condition}
+
+\begin{columns}
+\begin{column}{.49\textwidth}
+We impose the standard outflow wall boundary condition on $u$. For inflow boundary condition: 
+\begin{itemize}
+\item{} The standard choice of inflow boundary condition: $u = u_0$.
+\item{} We impose the non-standard inflow condition: $\widehat{f}_n \coloneqq \beta_n u - \sigma_n \approx \beta_n u_0$ on $\Gamma_{\rm in}$.
+\end{itemize}
+\end{column}
+
+\begin{column}{.49\textwidth}
+\begin{figure}
+\includegraphics[scale=.23]{figs/primal.png}
+\caption{Non-standard inflow.}
+\end{figure}
+\end{column}
+\end{columns}
+When $\sigma_n \approx 0$ near the inflow, condition on $\widehat{f}_n$ approximates condition on $u$.
+
+}
+
 \frame{
 \frametitle{Dirichlet inflow boundary condition}
-Standard choice of boundary condition: $u = u_0$ on inflow boundary $\Gamma_{\rm in}$, induces boundary layers in adjoint problems. 
+Standard choice of boundary condition: $u = u_0$ on inflow boundary $\Gamma_{\rm in}$, induces boundary layers in adjoint problems, \textcolor{red}{$\nor{\beta\cdot \grad v}_{L^2} = O(\epsilon^{-1})$}.
 \begin{figure}[h!]
@@
 \frametitle{New inflow boundary condition on $\widehat{f}_n$}
-Non-standard choice of boundary condition: $\widehat{f}_n = \beta_n u_0$ on $\Gamma_{\rm in}$, induces smoother adjoint problems. 
+Non-standard choice of boundary condition: $\widehat{f}_n = \beta_n u_0$ on $\Gamma_{\rm in}$, induces smoother adjoint problems, \textcolor{red}{$\nor{\beta\cdot \grad v}_{L^2} = O(1)$}.
 \begin{figure}[h!]
@@
 \begin{figure}[!h]
+\centering
 \subfigure[Dirichlet inflow]{\includegraphics[scale=.35]{figs/dirichletBC.png}}
@@
 \end{align*}
-which induces the proven \emph{robust} bound 
+which induces the proven \emph{robust} bound\footnote{\bibentry{DPGrobustness2}}
 \[
@@
 \begin{align*}
-\widehat{\beta_nu - \sigma_n} &= \widehat{f_n} = u_0, \quad \beta_n \leq 0\\
+\widehat{\beta_nu - \sigma_n} &= \widehat{f}_n = u_0, \quad \beta_n \leq 0\\
 \widehat{u} &= 0, \quad \beta_n > 0
@@
 
-Separation of variables gives an analytic solution. 
+%Separation of variables gives an analytic solution. 
+All numerical experiments done using Camellia codebase.\footnote{\bibentry{Camellia}}
 %\[
@@
 \subfigure{
-\includegraphics[scale=.24]{figs/wallBC_exact_u.png}
+\includegraphics[scale=.23]{figs/wallBC_exact_u.png}
 }
 \subfigure{
-\includegraphics[scale=.24]{figs/wallBC_exact_sigx.png}
+\includegraphics[scale=.23]{figs/wallBC_exact_sigx.png}
 }
 \subfigure{
-\includegraphics[scale=.24]{figs/wallBC_exact_sigy.png}
-}
-\caption{Solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
-\end{figure}
-
+\includegraphics[scale=.23]{figs/wallBC_exact_sigy.png}
+}
+\caption{Exact solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
+\end{figure}
 }
@@
 \subfigure{
-\includegraphics[scale=.24]{figs/errorrates_wallBC.png}
+\includegraphics[scale=.33]{figs/errorrates_wallBC.png}
 }
 \subfigure{
-\includegraphics[scale=.24]{figs/L2energyratio_wallBC.png}
-}
-\subfigure{
-\includegraphics[scale=.22]{figs/u_pointdiff_wallBC.png}
-}
-\caption{$L^2$/energy error, their ratio, and pointwise error in $u$ for $\epsilon = .01$.}
+\includegraphics[scale=.33]{figs/L2energyratio_wallBC.png}
+}
+%\subfigure{
+%\includegraphics[scale=.22]{figs/u_pointdiff_wallBC.png}
+%}
+\caption{$L^2$/energy errors and their ratio for $\epsilon = .01, .001, .0001$.}
 \end{figure}
@@
 \frametitle{Regularization}
-For $\beta = (.5-y,x-.5)^T$ on $\Omega = [0,1]^2$, and zero normal stress outflow conditions. Ill posed in the convection setting. Similar tests have been done with discontinuous data.
+For $\beta = (-y,x)^T$ on $\Omega = [-1,1]^2$. Ill posed in the convection setting. Similar tests have been done with discontinuous data.
 
@@
 \subfigure{
-\includegraphics[scale=.35]{figs/vortex.png}
+\includegraphics[scale=.21]{figs/vortex.png}
 }
 \subfigure{
-\includegraphics[scale=.35]{figs/vortexMesh.png}
-}
-\caption{Steady-state vortex problem with $\epsilon = 1e-5$.}
+\includegraphics[scale=.2015]{figs/vortexMesh.png}
+}
+\caption{Steady vortex problem with $\epsilon = 1e-4$, using a variant of the test norm.}
 \end{figure}
@@
 
-Given some linearization technique, we can measure 
+Given some linearization technique (typically Newton-Raphson and pseudo-timestepping linearization), we measure 
 \begin{itemize}
@@
 \[
-\nor{R(u)}_E \coloneqq \nor{B(u)-l}_E = \nor{B(u) - l}_{V'}  = \nor{R_V^{-1}\LRp{B(u)-l}}_V 
-\]
-\end{itemize}
-We will work with either full Newton-Raphson or pseudo-timestepping linearization.
-
-%\textcolor{red}{REWORK. HOW TO DO THIS SECTION?}
-%Begin with the nonlinear variational formulation
-%$b(u,v) = l(v)$, linear in $v$, but not in $u$.  An appropriate linearization gives
-%\[
-%b_u(\Delta u,v) = l(v) - b(u,v),
-%\]
-%Let $B(u)$ and $B_u\Delta u$ be the variational operators associated with $b(u,v)$ and $b_u(\Delta u,v)$. 
-%\begin{align*}
-%\|\Delta u\|_E &\coloneqq \nor{B_u\Delta u}_{V'} = \nor{R_V^{-1} B_u\Delta u}_V \\
-%\nor{R(u)}_E &\coloneqq \nor{B(u)-l}_E = \nor{B(u) - l}_{V'}  = \nor{R_V^{-1} B(u)-l}_V 
-%\end{align*}
-}
-%\frame{
-%\frametitle{Burgers' equation as an example}
-%
-%}
-\frame{
-\frametitle{Test case: Burgers equation}
+\nor{R(u)}_E \coloneqq \nor{B(u) - \ell}_{V'}  = \nor{R_V^{-1}\LRp{B(u)-\ell}}_V 
+\]
+\end{itemize}
+Preliminary experiments were done in 1D\footnote{\bibentry{DPGNS_1d}} and space-time.\footnote{\bibentry{DPGspacetime}}
+}
+
+\frame{
+\frametitle{2D test case: Burgers equation}
 \begin{columns}
@@
 \end{align*}
-i.e.\ nonlinear convection-diffusion. Solution is achieved using Newton-Raphson.
+i.e.\ nonlinear convection-diffusion on domain $[0,1]^2$.
 \end{column}
@@
 \centering
-\includegraphics[scale = .35]{figs/burgers1e4.png}
-\caption{Shock solution for Burgers' equation, $\epsilon = 1e-4$.}
+\includegraphics[scale = .22]{figs/burgers.png}
+\caption{Shock solution for Burgers' equation, $\epsilon = 1e-4$, using Newton-Raphson.}
 \end{figure}
@@
 }
-
-\frame{
-\frametitle{Compressible Navier-Stokes equations (ideal gas)}
-\begin{align*}
-\div \vecttwo{\rho u }{\rho v} &= 0\\
-\div \left(\vecttwo{\rho u^2+p }{\rho u v} - \boldsymbol \sigma_{1}\right) &=0\\
-\div \left(\vecttwo{\rho u v}{\rho v^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
-\div \left(\vecttwo{((\rho e)+p)u}{((\rho e)+p)v} - \boldsymbol\sigma \mathbf{u} + \vec{q}\right) &=0\\
-\frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I &= \grad \mathbf{u} - \Reyn \, {\boldsymbol \omega}\\
+\frame{
+Adaptivity begins with a cubic $4\times 4$ mesh.
+\begin{figure}[!h]
+\centering
+\subfigure{\includegraphics[scale=.2]{figs/burgersMesh.png}}
+\subfigure{\includegraphics[scale=.2]{figs/burgersZoom.png}}
+\caption{Adaptive mesh after 9 refinements, and zoom view at point (.5,.5) with shock formation and $1e-3$ width line for reference.}
+\end{figure}
+}
+
+\frame{
+\frametitle{2D Compressible Navier-Stokes equations (ideal gas)}
+Given density $\rho$, velocities $\mathbf{u} = \LRp{u_1,u_2}$ and temperature $T$,
+\begin{align*}
+\div \vecttwo{\rho u_1 }{\rho u_2} &= 0\\
+\div \left(\vecttwo{\rho u_1^2+p }{\rho u_1 u_2} - \boldsymbol \sigma_{1}\right) &=0\\
+\div \left(\vecttwo{\rho u_1 u_2}{\rho u_2^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
+\div \left(\vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2} - \boldsymbol\sigma \mathbf{u} + \vec{q}\right) &=0\\
+\frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I &= \grad \mathbf{u} - \Reyn \, \boldsymbol \omega \\
 \frac{1}{\kappa}\vec{q} &= \grad T
@@
 \frame{
-$\boldsymbol\sigma$ is a Newtonian fluid $\sigma_{ij} = \mu(u_{i,j} + u_{j,i}) + \lambda u_{k,k} \delta_{ij}$.
+\frametitle{Stress law}
+$\boldsymbol\sigma$ for a Newtonian fluid: $\sigma_{ij} = \mu(u_{i,j} + u_{j,i}) + \lambda u_{k,k} \delta_{ij}$.
 %We can invert the stress tensor under isotropic and plane strain assumptions to get
@@
 \]
-We also have
+The symmetric part of the gradient is
 \[
@@
 \end{align*}
-Taking the antisymmetric part implicitly defines $\boldsymbol \omega$ to be the antisymmetric part of $\grad u$. 
+By enforcing strong symmetry of $\boldsymbol \sigma$, taking the antisymmetric part implicitly defines $\boldsymbol \omega$ to be the antisymmetric part of $\grad u$. 
 }
@@
 \end{align*}
-Navier-Stokes:%vectors of test functions  $v=\{v_1,v_2,v_3,v_4\}$, $W = \{\tau_1,\tau_2,\tau_3\}$.
-Similarly, we group our Eulerian and stress variables into the vector variables $U$ and $\Sigma$.
-$R_{\rm Euler}(U,\Sigma)$ and $R_{\rm visc}(U,\Sigma)$ are Eulerian and viscous nonlinear residuals, our formulation for the linearized Navier-Stokes equations can be written as
-\begin{align*}
-\div \left(A_{\rm Euler}U - A_{\rm visc}\Sigma\right) &= R_{\rm Euler}(U,\Sigma)\\
-E_{\rm visc} \Sigma - \grad U &= R_{\rm visc}(U,\Sigma)
-\end{align*}
-where $R_{\rm Euler}(U,\Sigma)$ and $R_{\rm visc}(U,\Sigma)$ are the Eulerian/viscous residuals.
-}
-
-\frame{
+Navier-Stokes: defining vector variables $U = \{\rho,u_1,u_2,T\}$ and $\Sigma = \{{\boldsymbol \sigma},\mathbf{q},\omega\}$,
+\begin{align*}
+\div \left(A_{\rm invisc}U - A_{\rm visc}\Sigma\right) &= R_{\rm conserv}(U,\Sigma)\\
+E_{\rm visc} \Sigma - \grad U &= R_{\rm constit}(U,\Sigma)
+\end{align*}
+where $R_{\rm conserv}(U,\Sigma)$ and $R_{\rm constit}(U,\Sigma)$ are the conservation/constitutive residuals.
+}
+
+\frame{
+\frametitle{Test norms over one element}
 Convection-diffusion:
 \begin{align*}
-\|\left(v,\tau\right)\|_{V,K}^2 =& \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 \\
+\|\left(v,\tau\right)\|_{V,K}^2 =& \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \|\beta \cdot \grad v\|^2 + \epsilon \|\grad v\|^2  \\
 &+\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
@@
 \begin{align*}
-\|\left(V,W\right)\|_{V,K}^2 =& \min\left\{\frac{1}{\Reyn|K|},1\right\}\nor{V}^2 + \frac{1}{\Reyn} \nor{A_{\rm visc}^T\grad V}^2 + \nor{A_{\rm Euler}^T \grad V}^2 \\
+\|\left(V,W\right)\|_{V,K}^2 =& \min\left\{\frac{1}{\Reyn|K|},1\right\}\nor{V}^2  + \nor{A_{\rm invisc}^T \grad V}^2 + \frac{1}{\Reyn} \nor{A_{\rm visc}^T\grad V}^2 \\
 & + \nor{\div W}^2 + \min\left\{1,\frac{1}{\Reyn|K|}\right\}\nor{E_{\rm visc}^TW}^2.
 \end{align*}
-%An advantage of this extrapolation approach is that the incompletely parabolic nature of the Navier-Stokes equation is taken into account; there is no diffusive term present in the mass conservation equation, and the test norm reflects that by requesting only limited regularity of $v_1$.\footnote{The situation is analogous to using the full $H^1(\Oh)$ norm for the pure convection equation --- the optimal test norm $\nor{v}_V = \nor{\beta\cdot \grad v} + \nor{v}$ implies only streamline regularity, whereas taking $\nor{v}_V = \nor{\grad v} + \nor{v}$ implies stronger regularity on the test space $V$ than the graph norm.
-Consequently, convergence is suboptimal for DPG applied to the convection problem under the $H^1(\Oh)$ test norm.}
-%\end{column}
-%\end{columns}
-}
-\frame{
-\frametitle{Carter plate and Boundary conditions}
-
+}
+
+\frame{
+\frametitle{Carter's flat plate problem}
+\begin{columns}
+\begin{column}{.49\textwidth}
 \begin{figure}[!h]
 \centering
-\includegraphics[scale=.35]{figs/flat_plate_BCs.pdf}
-\caption{Carter flat plate problem.}
-\end{figure}
-\begin{itemize}
-\item{} Inflow and stress boundary conditions, momentum flux boundary conditions. 
+\includegraphics[scale=.32]{figs/flat_plate_BCs.pdf}
+\caption{Carter flat plate problem on domain $[0,2]\times[0,1]$. Plate begins at $x=1$, ${\rm Re} = 1000$.}
+\end{figure}
+\end{column}
+\begin{column}{.49\textwidth}
+\begin{enumerate}
+\item{} Symmetry boundary conditions.
+\item{} Prescribed temperature and wall stagnation conditions.
+\item{} Symmetry boundary conditions.
+\item{} Inflow: conserved quantities specified using far-field values.
 \item{} No outflow condition set.
-\end{itemize}
+\end{enumerate}
+Stress/heat flux boundary conditions are set in terms of the momentum and energy fluxes. 
+\end{column}
+\end{columns}
 }
@@
 \begin{figure}
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/Re1000p2/u10.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/Re1000p2/T0.png}}
-\subfigure{\includegraphics[scale = .35]{figs/Re1000p2/mesh0.png}}
+\centering
+\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u0.png}}
+\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T0.png}}
+\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh0.png}}
 \end{figure}
@@
 \begin{figure}
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/Re1000p2/u11.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/Re1000p2/T1.png}}
-\subfigure{\includegraphics[scale = .35]{figs/Re1000p2/mesh1.png}}
+\centering
+\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u1.png}}
+\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T1.png}}
+\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh1.png}}
 \end{figure}
@@
 \begin{figure}
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/Re1000p2/u12.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/Re1000p2/T2.png}}
-\subfigure{\includegraphics[scale = .35]{figs/Re1000p2/mesh2.png}}
+\centering
+\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u2.png}}
+\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T2.png}}
+\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh2.png}}
 \end{figure}
@@
 \begin{figure}
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/Re1000p2/u13.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/Re1000p2/T3.png}}
-\subfigure{\includegraphics[scale = .35]{figs/Re1000p2/mesh3.png}}
+\centering
+\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u3.png}}
+\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T3.png}}
+\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh3.png}}
 \end{figure}
@@
 \begin{figure}
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/Re1000p2/u14.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/Re1000p2/T4.png}}
-\subfigure{\includegraphics[scale = .35]{figs/Re1000p2/mesh4.png}}
+\centering
+\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u4.png}}
+\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T4.png}}
+\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh4.png}}
 \end{figure}
@@
 \begin{figure}
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/Re1000p2/u15.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/Re1000p2/T5.png}}
-\subfigure{\includegraphics[scale = .35]{figs/Re1000p2/mesh5.png}}
+\centering
+\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u5.png}}
+\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T5.png}}
+\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh5.png}}
 \end{figure}
@@
 \begin{figure}
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/Re1000p2/u16.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/Re1000p2/T6.png}}
-\subfigure{\includegraphics[scale = .35]{figs/Re1000p2/mesh6.png}}
+\centering
+\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u6.png}}
+\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T6.png}}
+\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh6.png}}
 \end{figure}
@@
 \frame{
-\frametitle{Zoomed solutions at the plate edge}
-\begin{figure}
+\frametitle{Refinement level 7}
+\begin{figure}
+\centering
+\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u7.png}}
+\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T7.png}}
+\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh7.png}}
+\end{figure}
+}
+\setcounter{subfigure}{0}
+
+\frame{
+\frametitle{Refinement level 8}
+\begin{figure}
+\centering
+\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u8.png}}
+\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T8.png}}
+\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh8.png}}
+\end{figure}
+}
+\setcounter{subfigure}{0}
+
+\frame{
+\frametitle{Refinement level 9}
+\begin{figure}
+\centering
+\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u9.png}}
+\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T9.png}}
+\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh9.png}}
+\end{figure}
+}
+\setcounter{subfigure}{0}
+
+\frame{
+\frametitle{Refinement level 10}
+\begin{figure}
+\centering
+\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u10.png}}
+\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T10.png}}
+\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh10.png}}
+\end{figure}
+}
+\setcounter{subfigure}{0}
+
+\frame{
+\frametitle{Zoomed solutions at plate/stagnation point}
+\begin{figure}
+\centering
 \subfigure[$\rho$]{\includegraphics[scale = .12]{figs/Re1000p2/rhoUnscaledzoom.png}}
@@
 
-\item{\textbf{Proposed: Attempt analysis of the linearized Navier-Stokes system.}}
+\item{\textbf{\textcolor{red}{Proposed}: Attempt analysis of the linearized Navier-Stokes system.}}
 
@@
 \frame{
-\frametitle{Future work: Area B}
+\frametitle{Proposed work: Area B}
 \begin{itemize}
@@
 
-Numerical experiments use the higher-order adaptive codebase Camellia, built upon the Trilinos library by Nathan Roberts.
+Numerical experiments use the higher-order adaptive codebase Camellia, built by Nathan Roberts upon the Trilinos library.
 %The framework for arbitrary-irregularity anisotropic refinements in both $h$ and $p$ is in place, and the code is partially parallelized.
 
-\item{\textbf{Proposed: Anisotropic refinements and $hp$-schemes.}}
+\item{\textbf{\textcolor{red}{Proposed}: Anisotropic refinements and $hp$-schemes.}}
 
@@
 \begin{figure}
-\subfigure{\includegraphics[scale = .18]{figs/anisotropy/b5.png}}
-\subfigure{\includegraphics[scale = .186]{figs/anisotropy/v6.png}}
-\end{figure}
-\end{itemize}
-}
-
-\frame{
-\textbf{Proposed: Distributed iterative static condensation.}
+\centering
+\subfigure{\includegraphics[scale = .175]{figs/anisotropy/b5.png}}
+\subfigure{\includegraphics[scale = .18]{figs/anisotropy/v6.png}}
+\caption{Anisotropic mesh for a convection-diffusion boundary layer.}
+\end{figure}
+\end{itemize}
+}
+
+\frame{
+\textbf{\textcolor{red}{Proposed}: Distributed iterative static condensation.}
 \[
@@
 \]
-where $D^{-1}$ can be inverted block-wise. For FE stiffness matrices under the Laplace equation, the Schur complement has reduced condition number of $O(h^{-1})$ as opposed to $O(h^{-2})$. 
-}
-
-\frame{  
-\textbf{Proposed: a Nonlinear Hessian-based DPG method.}
-Given a nonlinear variational problem $b(u,v) = l(v)$, linear in $v$ but not in $u$, beginning with the \textit{nonlinear} dual residual 
-\[
-J(u_h) = \frac{1}{2}\|B(u_h)-l\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(u_h,v)-l(v)|^2}{\nor{v}_V^2}.
+where $D^{-1}$ can be inverted block-wise.
+For FE stiffness matrices under the Laplace equation, the Schur complement has reduced condition number of $O(h^{-1})$ as opposed to $O(h^{-2})$.\footnote{\bibentry{schurComplement}}
+}
+
+\frame{  
+\textbf{\textcolor{red}{Proposed}: a Nonlinear Hessian-based DPG method.}
+Given a nonlinear variational problem $b(u,v) = \ell(v)$, linear in $v$ but not in $u$, beginning with the \textit{nonlinear} dual residual 
+\[
+J(u_h) = \frac{1}{2}\|B(u_h)-\ell\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(u_h,v)-\ell(v)|^2}{\nor{v}_V^2}.
 \]
@@
 \[
-b_u(\Delta u,v) + b''(\Delta u, \delta u, v_{R(u)}) = l(v) - b(u,v) = r(u,v),
+b_u(\Delta u,v) + b''(\Delta u, \delta u, v_{R(u)}) = \ell(v) - b(u,v) = r(u,v),
 \]
@@
 \frametitle{Proposed work: Area C}
+\begin{columns}
+\begin{column}{.48\textwidth}
 \begin{itemize}
 \item{\textbf{Completed: convection-dominated diffusion, Burgers, and a model problem for Navier-Stokes.}}
-\item{\textbf{Proposed: Range of Reynolds/Mach numbers, ramp problem, Gaussian bump.}}
-\item{\textbf{Proposed: regularized Euler.}}
-%\textcolor{red}{Graphics?}
-\end{itemize}
-}
+\item{\textbf{\textcolor{red}{Proposed}: Range of Reynolds/Mach numbers.}}
+\item{\textbf{\textcolor{red}{Proposed}: Flow over a bump, Holden's ramp problem (shock-boundary layer interaction).}}
+\item{\textbf{\textcolor{red}{Proposed (time permitting)}: airfoils, regularized Euler.}}
+\end{itemize}
+\end{column}
+\begin{column}{.5\textwidth}
+\begin{figure}
+\centering
+\includegraphics[scale = .275]{figs/ramp.png}
+\end{figure}
+\end{column}
+\end{columns}
+}
+
+\frame{
+\begin{center}
+Thank you!\\
+\vspace{1cm}
+Questions?
+\end{center}
+}
+
+\section{Extended slides}
+
+\frame{
+\frametitle{Extended literature review}
+\begin{itemize}
+\item Finite difference/volume methods, upwind stencils, monotonicity, ENO/WENO. 
+\item Artificial diffusion, flux limiters/discontinuity-capturing operators.
+\item DG fluxes can be interpreted as residual-based stabilizations similar to SUPG.\footnote{\bibentry{Brezzi20063293}}
+\item Hybridized DG (HDG) methods introduce independent unknowns for numerical traces. Fluxes are defined in terms of DG fluxes and the numerical trace.\footnote{\bibentry{hybridDG}}
+\end{itemize}
+}
+
+\frame{
+\frametitle{Specifics of the ultra-weak formulation}
+
+Given a first order system $Au = f$, multiply by test function $v$ and integrate 
+\[
+\LRp{Au,v} = \LRa{\gamma\LRp{Au},v} + \LRp{u,A^*_hv} = \LRp{f,v}
+\]
+If $u \in L^2\LRp{\Omega}$, the trace of $u$ is undefined, so we identify boundary terms $\LRa{\gamma\LRp{Au},v}_{\Gh} = \LRa{\widehat{u},v}_{\Gh}$ as unknowns $\widehat{u}$ on $\Gh$.
+For convection-diffusion,
+\begin{align*}
+b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
+\left( v, \tau \right)\right) = \left(u,\grad_h\cdot \tau - \beta \cdot \grad_h
+v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad_h v\right)_{\Oh}&\\
+  - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
+\end{align*}
+where 
+\begin{align*}
+\widehat{f}_n \coloneqq \beta_n u - \sigma_n \in H^{-1/2}(\Gh), \quad \widehat{u} \in H^{1/2}(\Gh)
+\end{align*}
+with the minimum energy extension norm on $\Gh$. We note that $H^{\pm 1/2}(\Gh)$ are \emph{closed} subspaces of $\prod_K H^{\pm 1/2}(\partial K)$. 
+}
+
+\frame{
+\frametitle{Inviscid equations}
+Issue: consider pure convection, $\div \beta u = f$. The ultra-weak variational formulation is
+\[
+\LRa{\widehat{f}_n,v}-\LRp{u,\beta\cdot \grad v} = \LRp{f,v},
+\]
+where $\widehat{f}_n \coloneqq \beta_n u$.
+When $\beta_n = 0$, $v$ has only a streamline derivative, and $\widehat{f}_n$ becomes an ill-defined trace in the cross-stream direction.
+For hyperbolic \emph{systems}, this issue manifests as \emph{sonic lines}.
+\begin{figure}
+\centering
+\includegraphics[scale=.25]{figs/sonicLines.pdf}
+\caption{Sonic lines ($u_n - c = 0$) appear for linearized Euler.}
+\end{figure}
+}
+
+\bibliographystyle{plain}
+{\scriptsize
+\bibliography{CFD_intro,DPG_old,paper,LitRev,NSNotes}
+}
+
 \end{document}

### 2012-08-14 docs/Jesse/Proposal/boeingPres.tex
adding boeing presentation to git

--- 2012-08-08 docs/Jesse/Proposal/proposalPres.tex
@@
 \title[A DPG method for Compressible Flow]{A Discontinuous Petrov-Galerkin method for compressible flow problems}
-\date{August 8, 2012}
-\author[J. Chan, L. Demkowicz, R. Moser]{Jesse Chan \\ Supervisors: Leszek Demkowicz, Robert Moser \\ Committee: Todd Arbogast, Omar Ghattas, Venkat Raman}
+\date{August 15, 2012}
+\author[J. Chan, T. Ellis, L. Demkowicz, R. Moser]{Jesse Chan, Truman Ellis \\ Supervisors: Leszek Demkowicz, Robert Moser}
 
@@
 }
-%\frame{
-%\frametitle{Stabilization}
-%Historical stabilization methods: 
-%\begin{itemize}
-%\item Artificial diffusion - solve
-%\[
-%\beta u' - \tilde{\epsilon} u'' = f
-%\]
-%where $\tilde{\epsilon}$ is set depending on $\beta$, $\epsilon$, and the mesh. Can be made ``exact'' for $f=0$. 
-%\item Upwind finite differences - for $\beta > 0$, and uniform grid points $x_A$,
-%\[
-%u'(x_A) \approx \frac{u_h(x_A)-u_h(x_{A-1})}{h}
-%\]
-%\end{itemize}
-%Both of these methods introduce additional numerical diffusion, and their effectiveness depends on the forcing $f$ and parameters $h$, $|\beta|$, and $\epsilon$.
-%}
+
 \frame{
@@
 %}
+\frame{
+\frametitle{Local conservation}
+Given stiffness matrix $K$, can introduce Lagrange multipliers to enforce element-wise constraints, leading to the saddle point problem
+\[
+\arr{K}{B}{B^T}{0}\vecttwo{u}{\lambda} = \vecttwo{f}{c}.
+\]
+where the Lagrange multipliers $\lambda$ can be locally condensed. We use the test norm
+\begin{align*}
+\|\left(v,\tau\right)\|_{V,K}^2 = \left|\int_K v\right|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 +&\\
+\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2&.
+\end{align*}
+}
+
+\frame{
+\frametitle{Additional examples}
+\begin{figure}
+\centering
+\subfigure[Advection skew]{
+\includegraphics[scale = .175]{figs/Conservative/hughes.png}
+}
+\subfigure[Flow over a step]{
+\includegraphics[scale = .175]{figs/Conservative/step.png}
+}
+\subfigure[Double glazing]{
+\includegraphics[scale = .182]{figs/Conservative/doubleGlazing.png}
+}
+\end{figure}
+Locally conservative version of DPG performs very similarly to the standard DPG in all cases.
+}
 
@@
 }
-\caption{Steady vortex problem with $\epsilon = 1e-4$, using a variant of the test norm.}
+\caption{Steady vortex problem with $\epsilon = 1e-4$.}
 \end{figure}
 \vspace{-.25cm}
+}
+
+\frame{
+\frametitle{Current work - Hemker problem}
+
+\begin{figure}
+\centering
+\subfigure{
+\includegraphics[scale = .225]{figs/Conservative/Hemker/WithoutMesh.png}
+}
+\subfigure{
+\includegraphics[scale = .225]{figs/Conservative/Hemker/WithMesh.png}
+}
+\caption{Convection-diffusion solution to the Hemker problem.}
+\end{figure}
+}
+\frame{
+\frametitle{Current work - high-lift airfoil}
+\begin{figure}
+\centering
+\subfigure{
+\includegraphics[scale = .1875]{figs/Conservative/Airfoil-Conservative-1E-3/solution.png}
+}
+\subfigure{
+\includegraphics[scale = .175]{figs/Conservative/Airfoil-Conservative-1E-3/mesh7.png}
+}
+\caption{Convection-diffusion solution over the high-lift airfoil, with advection at an angle, $\epsilon = 1e-3$, with $p=3$. Mesh is generated by \emph{Triangle}.}
+\end{figure}
 }
@@
 
-\section{Proposed work}
-\subsection{Area A}
-\frame{
-\frametitle{Proposed work: Area A}
-\begin{itemize}
-\item{\textbf{Completed: Prove robustness of DPG method for the scalar convection-diffusion problem.}}
-
-We have introduced a test norm under which the DPG method robustly bounds the $L^2$ error in the field variables $u$ and the scaled stress $\sigma$.
+\section{Future work}
+%\subsection{Area A}
+%\frame{
+%\frametitle{Proposed work: Area A}
+%\begin{itemize}
+%\item{\textbf{Completed: Prove robustness of DPG method for the scalar convection-diffusion problem.}}
+%
+%We have introduced a test norm under which the DPG method robustly bounds the $L^2$ error in the field variables $u$ and the scaled stress $\sigma$.
 Numerical results confirm the theoretical bounds given.
-
-\item{\textbf{\textcolor{red}{Proposed}: Attempt analysis of the linearized Navier-Stokes system.}}
-
-We hope to analyze the linearized Navier-Stokes equations to determine an optimal extrapolation of the test norm for the scalar convection-diffusion problem to systems.
-
-\end{itemize}
-}
-
-\subsection{Area B}
-
-\frame{
-\frametitle{Proposed work: Area B}
-\begin{itemize}
-\item{\textbf{Completed: Collaborative work with Nathan Roberts on the higher order parallel adaptive DPG code Camellia.}}
-
-Numerical experiments use the higher-order adaptive codebase Camellia, built by Nathan Roberts upon the Trilinos library.
+%
+%\item{\textbf{\textcolor{red}{Proposed}: Attempt analysis of the linearized Navier-Stokes system.}}
+%
+%We hope to analyze the linearized Navier-Stokes equations to determine an optimal extrapolation of the test norm for the scalar convection-diffusion problem to systems. 
+%
+%\end{itemize}
+%}
+
+%\subsection{Area B}
+%
+\frame{
+%\frametitle{Proposed work: Area B}
+%\item{\textbf{Completed: Collaborative work with Nathan Roberts on the higher order parallel adaptive DPG code Camellia.}}
+%
+%Numerical experiments use the higher-order adaptive codebase Camellia, built by Nathan Roberts upon the Trilinos library.
 %The framework for arbitrary-irregularity anisotropic refinements in both $h$ and $p$ is in place, and the code is partially parallelized.
 
-\item{\textbf{\textcolor{red}{Proposed}: Anisotropic refinements and $hp$-schemes.}}
+\frametitle{Future work: anisotropic refinements and $hp$-schemes.}
 
@@
 \end{figure}
-\end{itemize}
-}
-
-\frame{
-\textbf{\textcolor{red}{Proposed}: Distributed iterative static condensation.}
+}
+
+\frame{
+\frametitle{Future work: distributed iterative static condensation.}
 \[
@@
 \frame{  
-\textbf{\textcolor{red}{Proposed}: a Nonlinear Hessian-based DPG method.}
+\frametitle{Future work: a Nonlinear Hessian-based DPG method.}
 Given a nonlinear variational problem $b(u,v) = \ell(v)$, linear in $v$ but not in $u$, beginning with the \textit{nonlinear} dual residual 
@@
 
-\subsection{Area C}
-\frame{
-\frametitle{Proposed work: Area C}
+\frame{
+\frametitle{Future work: applications}
 \begin{columns}
@@
 \begin{itemize}
-\item{\textbf{Completed: convection-dominated diffusion, Burgers, and a model problem for Navier-Stokes.}}
-\item{\textbf{\textcolor{red}{Proposed}: Range of Reynolds/Mach numbers.}}
-\item{\textbf{\textcolor{red}{Proposed}: Flow over a bump, Holden's ramp problem (shock-boundary layer interaction).}}
-\item{\textbf{\textcolor{red}{Proposed (time permitting)}: airfoils, regularized Euler.}}
+\item{{Solutions for all problems over a range of Reynolds/Mach numbers.}}
+\item{{Flow over a bump, Holden's ramp problem (shock-boundary layer interaction).}}
+\item{{Time permitting: airfoils, regularized Euler.}}
 \end{itemize}

### 2012-08-14 docs/Jesse/Proposal/boeingPres.tex
last mods to boeing pres

@@
 \end{figure}
-Locally conservative version of DPG performs very similarly to the standard DPG in all cases.
+Locally conservative version of DPG performs very similarly to the standard DPG in all cases over a range of $\epsilon$. 
 }
@@
 }
-\caption{Convection-diffusion solution to the Hemker problem.}
+\caption{Convection-diffusion solution to flow over a cylinder at $\epsilon = 1e-4$.}
 \end{figure}

### 2012-09-06 docs/Jesse/Proposal/boeingPres.tex
changes to boeing pres

@@
 
-\section{Introduction/Literature review}
-\frame{
-\frametitle{Phenomena in compressible flow}
-\begin{figure}
-\centering
-\subfigure[Shock wave]{\includegraphics[scale=.0704]{figs/compFlowPics/bullet_shock.png}}
-\subfigure[Boundary layer]{\includegraphics[scale=.16]{figs/compFlowPics/boundary_layer.png}}
-%\subfigure{\includegraphics[scale=.15]{figs/compFlowPics/capsule.png}}
-\end{figure}
-Compressible flow plays an important role in the aerospace and energy industries - transonic and supersonic aircraft, combustion engines, etc.
-
-}
 \frame{
@@
 \div \left(\vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2} - \boldsymbol\sigma \mathbf{u} + \vec{q}\right) &=0\\
-\frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I &= \grad \mathbf{u} - \Reyn \, \boldsymbol \omega \\
+\frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I &= \grad \mathbf{u} - \Reyn \, \boldsymbol w\\
 \frac{1}{\kappa}\vec{q} &= \grad T
@@
 \[
-\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \grad  U - \boldsymbol \omega
-\]
-%where $\boldsymbol \omega$ is the antisymmetric part of the infinitesimal strain tensor:
-%\[
-%\boldsymbol \omega = \frac{1}{2}\left(\grad  U - \grad ^T  U\right).
-%\]
+\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \grad  U - \boldsymbol w
+\]
 Our final form is
 \begin{align*}
-\grad  U - \boldsymbol \omega = \frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I.
-\end{align*}
-By enforcing strong symmetry of $\boldsymbol \sigma$, taking the antisymmetric part implicitly defines $\boldsymbol \omega$ to be the antisymmetric part of $\grad u$. 
+\grad  U - \boldsymbol w= \frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I.
+\end{align*}
+By enforcing strong symmetry of $\boldsymbol \sigma$, taking the antisymmetric part implicitly defines $\boldsymbol w$ to be the antisymmetric part of $\grad u$. 
 }
@@
 \end{align*}
-Navier-Stokes: defining vector variables $U = \{\rho,u_1,u_2,T\}$ and $\Sigma = \{{\boldsymbol \sigma},\mathbf{q},\omega\}$,
+Navier-Stokes: defining vector variables $U = \{\rho,u_1,u_2,T\}$ and $\Sigma = \{{\boldsymbol \sigma},\mathbf{q},w\}$,
 \begin{align*}

### 2012-09-07 docs/Jesse/Vienna/pres.tex

--- 2012-09-06 docs/Jesse/Proposal/boeingPres.tex
@@
 
-\title[A DPG method for Compressible Flow]{A Discontinuous Petrov-Galerkin method for compressible flow problems}
-\date{August 15, 2012}
-\author[J. Chan, T. Ellis, L. Demkowicz, R. Moser]{Jesse Chan, Truman Ellis \\ Supervisors: Leszek Demkowicz, Robert Moser}
+\title[A DPG method for Compressible Flow]{Application of a Discontinuous Petrov-Galerkin method to compressible flow problems}
+\date{Sept 12, 2012}
+\author[J. Chan, L. Demkowicz, R. Moser]{Jesse Chan\\ Supervisors: Leszek Demkowicz, Robert Moser}
 
@@
 \begin{columns}[c]
-\begin{column}{.475\textwidth}
+\begin{column}{.55\textwidth}
 Numerical difficulties:
@@
 \item{} Boundary layers - resolution needed for drag/load
-\item{} Turbulence (non-localized)
 \end{itemize}
-\item{} Nonlinear convergence and uniqueness of solutions
 \item{} Stability of numerical schemes
@@
 \end{itemize}
+\item{} Stabilized methods
+\begin{itemize}
+\item{} Stabilization parameters
+\item{} Higher-order
+\end{itemize}
 \end{itemize}
 \end{column}
-\begin{column}{.475\textwidth}
+\begin{column}{.4\textwidth}
 \begin{figure}
 \centering
-\includegraphics[scale = .7]{figs/compFlowPics/airfoil_mesh.png}
+\subfigure{\includegraphics[scale = .6]{figs/compFlowPics/airfoil_mesh.png}}
+\subfigure{\includegraphics[scale=.3]{figs/SUPG.png}}
 \end{figure}
@@
 \end{columns}
-\vspace{.2cm}
-\begin{center}
-Idea: begin first with the model problem of convection-diffusion.
-\end{center}
-}
-\frame{
-\frametitle{Robustness: convection-diffusion as a model problem}
-\vspace{-.5cm}
-\[
-\div \left(\beta u\right) - \epsilon \Delta u = f, \quad \text{on }\Omega \in \mathbb{R}^3
-\]
-\vspace{-.5cm}
-\begin{columns}[c]
-\begin{column}{.49\textwidth}
-In 1D: $\beta u' - \epsilon u'' = f$. Standard continuous Galerkin variational formulation: solve
-\[
-b(u,v) = \ell(v), \quad u,v\in H^1_0([0,1])
-\]
-where
-\begin{align*}
-b(u,v) &= \int_\Omega -\beta uv' + \epsilon u'v' \\
-\ell(v) &= \int_\Omega f v 
-\end{align*}
-\end{column}
-\begin{column}{.49\textwidth}
-\begin{figure}
-\centering
-\includegraphics[scale=.35]{figs/GalerkinOscTight.png}
-\caption{Solution for $f=1$. Oscillations in the standard Galerkin method for large Peclet numbers ${\rm Pe} \coloneqq \frac{h}{\epsilon}$.}
-\end{figure}
-\end{column}
-\end{columns}
-}
-
-\frame{
-\frametitle{Streamline-upwind Petrov-Galerkin (SUPG)}
-SUPG solves $b_{\rm SUPG}(u,v) = l_{\rm SUPG}(v)$, where
-\begin{align*}
-b_{\rm SUPG}(u,v) &= b(u,v)+ \sum_{K} \int_{K} \tau \LRp{L_{\rm adv} v} L u \\
-l_{\rm SUPG}(v) &= \ell(v) + \sum_{K} \int_{K} \tau \LRp{L_{\rm adv}v} f.
-\end{align*}
-\vspace{-.5cm}
-\begin{columns}[c]
-\begin{column}{.44\textwidth}
-\vspace{-.5cm}
-\begin{itemize}
-\item{} $Lu = \div\left(\beta u\right) - \epsilon \triangle u$, $L_{\rm adv}u = \div \left(\beta u\right)$, and $\tau$ is a parameter. 
-%\item{} Recovers ``exact'' artificial diffusion for $f=0$.
-\item{} Effective for $f\neq 0$. %``exact'' artificial diffusion.
-\item{} \emph{Residual-based} stabilization. 
-\end{itemize}
-\end{column}
-\begin{column}{.54\textwidth}
-\begin{figure}
-\centering
-\includegraphics[scale=.38]{figs/SUPG.png}
-%\caption{Exact, Bubnov-Galerkin, and SUPG solutions.}
-\end{figure}
-\end{column}
-\end{columns}
-}
-
-\frame{
-\begin{columns}
-\begin{column}{.49\textwidth}
-Can be interpreted as a \emph{Petrov-Galerkin} method,
-\[
-b\LRp{u,\tilde{v}_{i}} = \ell\LRp{\tilde{v}_{i}}, \quad \forall i = 1,\ldots,N-1,
-\]
-where the SUPG test function $\tilde{v}_{i}$ is defined elementwise as\footnotemark
-\[
-\tilde{v}_{i} = \phi_i(x) + \tau L_{\rm adv} \phi_i.  
-\]
-\end{column}
-\begin{column}{.49\textwidth}
-\begin{figure}
-\centering
-\subfigure{\includegraphics[scale=.16]{figs/SUPGtest.png}}
-\caption{SUPG test function $v_i$.}
-\end{figure}
-\end{column}
-\end{columns}
-\footnotetext{\bibentry{SUPG}}
 }
@@
 \[
-b(u,v) = \ell(v), \quad u\in U, \quad v\in V
+b(u,v) = \ell(v) \Longleftrightarrow Bu = \ell, \quad 
+\left.\begin{array}{cl}
+\langle Bu,v\rangle_V &\coloneqq b(u,v)\\
+\langle \ell,v\rangle_V &\coloneqq \ell(v).
+\end{array}\right\}
 \]
-This is equivalent to the operator equation posed in $V'$
+We seek to minimize the \textcolor{red}{dual residual} over $U_h \subset U$
 \[
-Bu = \ell
+J(u_h) = \frac{1}{2}\|Bu_h-\ell\|_{V'}^2 = \frac{1}{2}\left\|R_V^{-1}(Bu_h-\ell)\right\|_V^2.
 \]
-if we identify $B:U\rightarrow V'$ and $\ell\in V'$ such that 
-\begin{align*}
-\langle Bu,v\rangle_V &\coloneqq b(u,v), \quad u\in U, v\in V,\\
-\langle \ell,v\rangle_V &\coloneqq \ell(v), \quad v\in V.
-\end{align*}
-We seek to minimize the dual functional over $U_h \subset U$
-\[
-J(u_h) = \frac{1}{2}\|Bu_h-\ell\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(u_h,v)-\ell(v)|^2}{\nor{v}_V^2}.
-\]
-}
-
-\begin{frame}
-Let $R_V: V \to V'$ be the isometric Riesz map st.\
+where $R_V: V \to V'$ is the isometric Riesz map
 \[
@@
 \]
-Then, our functional $J(u_h)$ is equal to
-\begin{equation*}
-\min_{u_h\in U_h} J(u_h) = \frac{1}{2}\left\|Bu_h-\ell\right\|_{V'}^2 =  \frac{1}{2}\left\|R_V^{-1}(Bu_h-\ell)\right\|_V^2.
-\end{equation*}
-First order optimality: G\^ateaux derivative is zero in all directions $\delta u \in U_h$
-\begin{align*}
-\left(R_V^{-1}(Bu_h-\ell),R_V^{-1}B\delta u\right)_V &= 0, \quad \forall \delta u \in U_h.\\
-\rightarrow \LRa{(Bu_h-\ell),R_V^{-1}B\delta u} &= 0, \\
-\rightarrow b(u_h,R_V^{-1}B\delta u) - \ell(R_V^{-1}B\delta u) &= 0
-\end{align*}
-\end{frame}
-
-\frame{
-\frametitle{Summary: select test functions to minimize residuals}
-For $\delta u \in U_h$, define the \textcolor{red}{optimal test function} $v_{\delta u}$. 
-\begin{equation*}
-v_{\delta u} \coloneqq R_V^{-1}B\delta u.
-\end{equation*} 
-Then, the residual $J(u_h) = \frac{1}{2}\left\|Bu_h-\ell\right\|_{V'}^2$ is minimized by the solution of
+Conditions for minimization of the convex functional give
 \[
-b\LRp{u_h,v_{\delta u}} = \ell\LRp{v_{\delta u}}, \quad \forall \delta u \in U_h.
+b(u_h,v_{\delta u}) = \ell(v_{\delta u}), \quad \forall \delta u \in U_h, \quad v_{\delta u} \coloneqq R_V^{-1}B\delta u.
 \]
@@
 \frametitle{Properties of DPG}
-DPG provides a symmetric positive-definite stiffness matrix. Let $\{\phi_j\}_{j=1}^m$ be a basis for $U_h$, and $\{v_i\}_{i=1}^n$ a basis for $V_h$, such that $n>m$. Then, for 
-\begin{align*}
-B_{ji} &= b(\phi_j,v_i),\\
-l_i &= \ell(v_i),
-\end{align*}
-DPG solves the discrete system for degrees of freedom $u$
+%Properties of DPG include\footnotemark
+\begin{itemize}
+\item Stiffness matrices are \textcolor{red}{symmetric positive-definite}.
+For trial/test bases $\{\phi_j\}_{j=1}^m$ and $\{v_i\}_{i=1}^n$, with $B_{ji} = b(\phi_j,v_i)$ and $l_i = \ell(v_i)$.
+DPG solves
 \begin{align*}
@@
 \end{align*}
-where, under a localizable norm and discontinuous test functions, $R_V^{-1}$ is block diagonal.
-}
-
-\frame{
-\frametitle{Properties of DPG}
-Additional properties of DPG include\footnotemark
-\begin{itemize}
+For localizable norms and discontinuous testing, $R_V$ is block diagonal.
 \item DPG provides the best approximation in the \textcolor{red}{energy norm}
@@
 \]
-\item The energy error is computable through the residual
+\item The energy error is computable through the \textcolor{red}{error representation function} $e$ defined through $(e,\delta v)_V = \ell(v)-b(u_h,\delta v)$ for all $\delta v\in V$. 
 \[
@@
 \]
-where the \textcolor{red}{error representation function} $e$ is defined through $(e,\delta v)_V = \ell(v)-b(u_h,\delta v)$ for all $\delta v\in V$. 
 \end{itemize}
-\footnotetext{\bibentry{DPG3pub}}
-}
-
-%\frame{
-%\frametitle{Duality of norms}
-%Duality of norms: for any trial norm $\nor{u}_U$,
-%\[
-%\nor{u}_{U} = \sup_{v \in V}\frac{b\LRp{u,v}}{\nor{v}_{V,U}}, \quad \nor{v}_{V,U} = \sup_{u \in U}\frac%{b\LRp{u,v}}{\nor{u}_{U}}.
-%\]
-%Likewise, for any test norm $\nor{v}_V$, 
-%\[
-%\nor{v}_{V} = \sup_{u \in U}\frac{b\LRp{u,v}}{\nor{U}_{U,V}}, \quad \nor{u}_{U,V} = \sup_{v \in V}\frac%{b\LRp{u,v}}{\nor{v}_{V}}.
-%\]
-%
-%}
-
-\frame{
-\frametitle{Ultra-weak formulation}
-\vspace{-.75cm}
-\begin{columns}
-\begin{column}{.64\textwidth}
-Given a first order system $Au = f$, we identify the \textbf{\emph{partition}} $\Oh$ and \textbf{\textcolor{red}{mesh skeleton}} \textcolor{red}{$\Gh$}.
-\end{column}
-\begin{column}{.34\textwidth}
-%\[
-%\Oh = \cup_{j=1}^\Nel K_j, \quad \Gh = \cup_{j=1}^\Nel \partial K_j
-%\]
-\begin{figure}[!h]
-\centering
-\includegraphics[scale = .155]{mesh_skel.pdf}
-\end{figure}
-\end{column}
-\end{columns}
-\vspace{-.5cm}
-The ultra-weak formulation for $Au = f$ on $\Oh$ is
-\[
-b\left(\left(u, \widehat{u}\right),v\right) \coloneqq \sum_K\langle \widehat{u},v \rangle_{\partial K} + (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh}.
-\]
-Under proper assumptions, $\sum_K\langle \widehat{u},v \rangle_{\partial K} = \langle \widehat{u}, \jump{v} \rangle_{\Gh}$, with energy setting
-\[
-u\in L^2\LRp{\Oh} \equiv L^2(\Omega), \quad v\in V=D(A^*_h), \quad
-\widehat{u}\in \gamma(D(A)),
-\]
-where $D(A_h^*)$ is the broken graph space of the formal adjoint $A_h^*$, and $\gamma(D(A))$ the trace space of the graph space of operator $A$.\footnote{\bibentry{analysisDPG}}
-}
-
-\frame{
-\frametitle{The canonical ``graph'' test norm}
-Recall $\nor{u}_E \coloneqq \sup_{v\in V\setminus\{0\}}\frac{b(u,v)}{\nor{v}_V}$. Under the ultra-weak formulation, the trial norm 
-\[
-\nor{\LRp{u,\widehat{u}}}_U \coloneqq \|u\|^2_{\L} + \|\widehat{u}\|^2
-\] 
-generates a test norm \emph{equivalent} to 
-\[
-\nor{v}_{V_{\rm opt}} \coloneqq \|A_h^*v\|_{\L}^2 +\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},\jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2.
-\]
-This norm is not localizable, so we instead substitute the jump terms for an $L^2$ term, giving us the \emph{graph norm}\footnote{\bibentry{Bui-ThanhDemkowiczGhattas11b}}
-\[
-\nor{v}_V \coloneqq \|A_h^*v\|_{\L}^2 + \nor{v}_{L^2}.
-\]
-}
-
-\frame{
-\frametitle{Goal: robust higher order adaptive methods}
-\begin{columns}
-\begin{column}{.45\textwidth}
-Our aim is to design an adaptive method for compressible laminar flows that is 
-\begin{itemize}
-\item robust in Reynolds number
-\item stable for arbitrary elements
-\end{itemize}
-
-This proposal will outline
-\begin{enumerate}
-\item a robust DPG method for convection-diffusion,
-\item extension to nonlinear problems and systems,
-\item proposed work.
-\end{enumerate}
-
-\end{column}
-\begin{column}{.54\textwidth}
-\begin{figure}
-\centering
-\subfigure{\includegraphics[scale=.23]{figs/Re1000p2/u2_full.png}}
-\subfigure{\includegraphics[scale=.37]{figs/Re1000p2/mesh6.png}}
-\caption{$u_2$ and $p=2$ mesh for $\Reyn = 1000$.}
-\end{figure}
-\end{column}
-\end{columns}
+%\footnotetext{\bibentry{DPG3pub}}
 }
@@
 \frametitle{Ultra-weak formulation for convection-diffusion}
-In first order form, the convection-diffusion equation is
+\begin{columns}
+\begin{column}{.65\textwidth}
+The first order convection-diffusion system:
 \[
@@
 \]
+\end{column}
+
+\begin{column}{.35\textwidth}
+\begin{figure}[!h]
+\centering
+\includegraphics[scale = .15]{figs/mesh_skel.pdf}
+\end{figure}
+\end{column}
+
+\end{columns}
+
 The variational formulation is
@@
 \frametitle{Graph norm under convection-diffusion}
-For convection-diffusion, the graph test norm is defined elementwise
-\[
-\|\left(v,\tau\right)\|_{V(K)}^2 = \| \div \tau - \beta \cdot \grad v
-\|_{L^2(K)}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2(K)}^2 +
+The graph norm\footnote{\bibentry{Bui-ThanhDemkowiczGhattas11b}} for convection-diffusion gives exceptional stability.  %, this norm is defined elementwise
+\begin{align*}
+\|\left(v,\tau\right)\|_{V(K)}^2 =& \| \div \tau - \beta \cdot \grad v\|_{L^2(K)}^2 + 
+\| \epsilon^{-1} \tau + \grad v \|_{L^2(K)}^2 +
 \|v\|_{L^2(K)}^2.
-\]
+\end{align*}
 Problem with this test norm: approximability of test functions.
-\vspace{-.3cm}
 \begin{figure}[!h]
 \centering
-\includegraphics[scale=.175]{figs/opt.png}
-\caption{$v$ and $\tau$ components of the 1D optimal test functions for flux $\widehat{f}_n$ on the \emph{right-hand} side of a unit element for $\epsilon = 0.01$. }
+\includegraphics[scale=.16]{figs/opt.png}
+\caption{Components of optimal test functions for flux $\widehat{f}_n$ on the \emph{right-hand} side of a unit element for $\epsilon = 0.01$. }
 \label{fig:optTestBoundary}
@@
 \frametitle{Determining an alternative test norm}
-Recall the convection-diffusion bilinear form
+%Recall the convection-diffusion bilinear form.  %Let $\boldsymbol U = \LRp{u,\sigma,\widehat{u},\widehat{f}_n}$. 
+\vspace{-.85cm}
+\begin{align*}%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),\left( v, \tau \right)\right) 
+b(\boldsymbol U,\boldsymbol V) = \left(u,\div \tau - \beta \cdot \grad
+v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh} + \text{boundary terms}
+% - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}
+\end{align*}
+Recover $\nor{u}^2_{L^2(\Omega)}$ with conforming $\LRp{v,\tau}$ satisfying the \emph{adjoint equations}
 \begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh}&\\
- - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
-\end{align*}
-We recover $\nor{u}^2_{L^2(\Omega)}$ by choosing conforming $\LRp{v,\tau}$ satisfying the \emph{adjoint equations}
-\begin{align*}
+\left.
+\begin{array}{cl}
 \div\tau - \beta \cdot \grad v   &= u\\
 \frac{1}{\epsilon}\tau + \grad v &= 0
+\end{array}
+\right. ,
+\quad
+\LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gamma}, \LRa{ \widehat{f}_n,\jump{v} }_{\Gamma} = 0
 \end{align*}
-with boundary conditions s.t.\ $\LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gamma}$ and $\LRa{ \widehat{f}_n,\jump{v} }_{\Gamma}$ vanish.
-}
-
-\frame{
-\frametitle{A robust bound}
-``Necessary'' conditions for robustness --- let $\boldsymbol U = \LRp{u,\sigma,\widehat{u},\widehat{f}_n}$. Then, by choosing specific $\LRp{v,\tau}$ satisfying the adjoint equations,
+``Necessary'' conditions for robustness --- 
 \[
@@
 
-\frame{
-\frametitle{Choice of inflow boundary condition}
-
-\begin{columns}
-\begin{column}{.49\textwidth}
-We impose the standard outflow wall boundary condition on $u$. For inflow boundary condition: 
-\begin{itemize}
-\item{} The standard choice of inflow boundary condition: $u = u_0$.
-\item{} We impose the non-standard inflow condition: $\widehat{f}_n \coloneqq \beta_n u - \sigma_n \approx \beta_n u_0$ on $\Gamma_{\rm in}$.
-\end{itemize}
-\end{column}
-
-\begin{column}{.49\textwidth}
-\begin{figure}
-\includegraphics[scale=.23]{figs/primal.png}
-\caption{Non-standard inflow.}
-\end{figure}
-\end{column}
-\end{columns}
-When $\sigma_n \approx 0$ near the inflow, condition on $\widehat{f}_n$ approximates condition on $u$.
-
-}
+%\frame{
+%\frametitle{Choice of inflow boundary condition}
+%
+%\begin{columns}
+%\begin{column}{.49\textwidth}
+%We impose the standard outflow wall boundary condition on $u$. For inflow boundary condition: 
+%\begin{itemize}
+%\item{} The standard choice of inflow boundary condition: $u = u_0$.
+%\item{} We impose the non-standard inflow condition: $\widehat{f}_n \coloneqq \beta_n u - \sigma_n \approx \beta_n u_0$ on $\Gamma_{\rm in}$.
+%\end{itemize}
+%\end{column}
+%
+%\begin{column}{.49\textwidth}
+%\begin{figure}
+%\includegraphics[scale=.23]{figs/primal.png}
+%\caption{Non-standard inflow.}
+%\end{figure}
+%\end{column}
+%\end{columns}
+%When $\sigma_n \approx 0$ near the inflow, condition on $\widehat{f}_n$ approximates condition on $u$. 
+%}
 
 \frame{
-\frametitle{Dirichlet inflow boundary condition}
+\frametitle{Dirichlet inflow condition: issues as $\epsilon \rightarrow 0$}
 Standard choice of boundary condition: $u = u_0$ on inflow boundary $\Gamma_{\rm in}$, induces boundary layers in adjoint problems, \textcolor{red}{$\nor{\beta\cdot \grad v}_{L^2} = O(\epsilon^{-1})$}.
@@
 \frame{
-\frametitle{New inflow boundary condition on $\widehat{f}_n$}
+\frametitle{Solution: New inflow boundary condition on $\widehat{f}_n$}
 Non-standard choice of boundary condition: $\widehat{f}_n = \beta_n u_0$ on $\Gamma_{\rm in}$, induces smoother adjoint problems, \textcolor{red}{$\nor{\beta\cdot \grad v}_{L^2} = O(1)$}.
@@
 
-%\frame{
-%\frametitle{``Building blocks'' norm}
-%Test norm quantities are robustly bounded from above by $\nor{u}_{L^2(\Omega)}$.  
-%\[
-%\|\left(v,\tau\right)\|_{V,K}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2.
-%\]
-%Problem: boundary layers in optimal test functions:
-%\begin{figure}[!h]
-%\centering
-%\subfigure{\includegraphics[scale=.15]{figs/mesh1.png}}
-%\subfigure{\includegraphics[scale=.15]{figs/sol1.png}}
-%\caption{The $v$ component of the optimal test function corresponding to flux $\widehat{u} = x(1-x)$ on the bottom side of a unit element for $\epsilon = 0.01$.}
-%\label{fig:boundaryTest}
-%\end{figure}
-%}
-\frame{
-\frametitle{Adjoint estimates, or ``norm building blocks''}
-For solutions $(v,\tau)$ of the adjoint equations, the following quantities are robustly bounded from above by $\nor{u}_{L^2(\Omega)}$.  
-\begin{align*}
-&\|v\|, \sqrt{\epsilon} \|\grad v\|, \|\beta \cdot \grad v\| \\
-&\| \div \tau\|, \frac{1}{\sqrt{\epsilon}}\|\tau\|.
-\end{align*}
-We will construct a test norm through a combination of the above quantities, such that
-\begin{itemize}
-\item $v$ and $\tau$ decoupled (no systems).
-\item Coefficients are of equal order after transforming to the unit element (no boundary layers).
-\end{itemize}
-}
 \frame{
 \frametitle{Mesh-scaled test norms}
-Our test norm, as defined over a single element $K$, is now
+For solutions $(v,\tau)$ of the adjoint equations, we derive quantities that are robustly bounded from above by $\nor{u}_{L^2(\Omega)}$.  Our test norm, as defined over a single element $K$, is now
 \begin{align*}
@@
 \frame{
-\frametitle{Erikkson-Johnson model problem}
+\frametitle{Numerical verification: Erikkson-Johnson problem}
 
-On domain $\Omega = [0,1]^2$, with $\beta = (1,0)^T$, $ f = 0$ and boundary conditions
-\begin{align*}
-\widehat{\beta_nu - \sigma_n} &= \widehat{f}_n = u_0, \quad \beta_n \leq 0\\
-\widehat{u} &= 0, \quad \beta_n > 0
-\end{align*}
-
-%Separation of variables gives an analytic solution. 
-All numerical experiments done using Camellia codebase.\footnote{\bibentry{Camellia}}
-%\[
-%u(x,y) = C_0 + \sum_{n=1}^\infty C_n \frac{\exp(r_2(x-1)-\exp(r_1(x-1)))}{r_1\exp(-r2) - r_2\exp(-r1)}\cos(n\pi y)
-%\]
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale=.23]{figs/wallBC_exact_u.png}
-}
-\subfigure{
-\includegraphics[scale=.23]{figs/wallBC_exact_sigx.png}
-}
-\subfigure{
-\includegraphics[scale=.23]{figs/wallBC_exact_sigy.png}
-}
-\caption{Exact solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
-\end{figure}
-}
-
-\frame{
-\frametitle{Error rates}
+%On domain $\Omega = [0,1]^2$, with $\beta = (1,0)^T$, $ f = 0$ and boundary conditions
+%\begin{align*}
+%\widehat{\beta_nu - \sigma_n} &= \widehat{f}_n = u_0, \quad \beta_n \leq 0\\
+%\widehat{u} &= 0, \quad \beta_n > 0
+%\end{align*}
+Experiments done using Camellia\footnote{\bibentry{Camellia}} and a boundary layer solution.
+%\begin{figure}
+%\centering
+%\subfigure{
+%\includegraphics[scale=.23]{figs/wallBC_exact_u.png}
+%}
+%\subfigure{
+%\includegraphics[scale=.23]{figs/wallBC_exact_sigx.png}
+%}
+%\subfigure{
+%\includegraphics[scale=.23]{figs/wallBC_exact_sigy.png}
+%}
+%\caption{Exact solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
+%\end{figure}
 \begin{figure}
@@
 
+%\section{DPG for nonlinear problems}
 %\frame{
-%\frametitle{Regularization}
-%Discontinuous inflow conditions on $\widehat{f_n}$, out of alignment with mesh. Boundary condition $\epsilon \grad u \cdot n = 0$ at outflow.
-%\begin{figure}
-%\centering
-%\subfigure{
-%\includegraphics[scale=.33]{figs/discontinuous.png}
+%\frametitle{DPG for nonlinear problems}
+%
+%Given some linearization technique (typically Newton-Raphson and pseudo-timestepping linearization), we measure 
+%\begin{itemize}
+%\item size of the linearized update $\Delta u$
+%\[
+%\|\Delta u\|_E \coloneqq \nor{B_u\Delta u}_{V'} = \nor{R_V^{-1} B_u\Delta u}_V 
+%\]
+%\item the nonlinear residual 
+%\[
+%\nor{R(u)}_E \coloneqq \nor{B(u) - \ell}_{V'}  = \nor{R_V^{-1}\LRp{B(u)-\ell}}_V 
+%\]
+%\end{itemize}
+%Preliminary experiments were done in 1D\footnote{\bibentry{DPGNS_1d}} and space-time.\footnote{\bibentry{DPGspacetime}}
 %}
-%\subfigure{
-%\includegraphics[scale=.305]{figs/discontinuousL2rates.png}
-%}
-%\caption{Discontinuous hat inflow data with $\epsilon = 1e-5$, convection solution errors.}
-%\end{figure}
-%}
-\frame{
-\frametitle{Local conservation}
-Given stiffness matrix $K$, can introduce Lagrange multipliers to enforce element-wise constraints, leading to the saddle point problem
-\[
-\arr{K}{B}{B^T}{0}\vecttwo{u}{\lambda} = \vecttwo{f}{c}.
-\]
-where the Lagrange multipliers $\lambda$ can be locally condensed. We use the test norm
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,K}^2 = \left|\int_K v\right|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 +&\\
-\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2&.
-\end{align*}
-}
-
-\frame{
-\frametitle{Additional examples}
-\begin{figure}
-\centering
-\subfigure[Advection skew]{
-\includegraphics[scale = .175]{figs/Conservative/hughes.png}
-}
-\subfigure[Flow over a step]{
-\includegraphics[scale = .175]{figs/Conservative/step.png}
-}
-\subfigure[Double glazing]{
-\includegraphics[scale = .182]{figs/Conservative/doubleGlazing.png}
-}
-\end{figure}
-Locally conservative version of DPG performs very similarly to the standard DPG in all cases over a range of $\epsilon$. 
-}
-
-\frame{
-\frametitle{Regularization}
-For $\beta = (-y,x)^T$ on $\Omega = [-1,1]^2$. Ill posed in the convection setting. Similar tests have been done with discontinuous data.
-
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale=.21]{figs/vortex.png}
-}
-\subfigure{
-\includegraphics[scale=.2015]{figs/vortexMesh.png}
-}
-\caption{Steady vortex problem with $\epsilon = 1e-4$.}
-\end{figure}
-\vspace{-.25cm}
-}
-
-\frame{
-\frametitle{Current work - Hemker problem}
-
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale = .225]{figs/Conservative/Hemker/WithoutMesh.png}
-}
-\subfigure{
-\includegraphics[scale = .225]{figs/Conservative/Hemker/WithMesh.png}
-}
-\caption{Convection-diffusion solution to flow over a cylinder at $\epsilon = 1e-4$.}
-\end{figure}
-}
-\frame{
-\frametitle{Current work - high-lift airfoil}
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale = .1875]{figs/Conservative/Airfoil-Conservative-1E-3/solution.png}
-}
-\subfigure{
-\includegraphics[scale = .175]{figs/Conservative/Airfoil-Conservative-1E-3/mesh7.png}
-}
-\caption{Convection-diffusion solution over the high-lift airfoil, with advection at an angle, $\epsilon = 1e-3$, with $p=3$. Mesh is generated by \emph{Triangle}.}
-\end{figure}
-}
-
-\section{DPG for nonlinear problems}
-\frame{
-\frametitle{DPG for nonlinear problems}
-
-Given some linearization technique (typically Newton-Raphson and pseudo-timestepping linearization), we measure 
-\begin{itemize}
-\item size of the linearized update $\Delta u$
-\[
-\|\Delta u\|_E \coloneqq \nor{B_u\Delta u}_{V'} = \nor{R_V^{-1} B_u\Delta u}_V 
-\]
-\item the nonlinear residual 
-\[
-\nor{R(u)}_E \coloneqq \nor{B(u) - \ell}_{V'}  = \nor{R_V^{-1}\LRp{B(u)-\ell}}_V 
-\]
-\end{itemize}
-Preliminary experiments were done in 1D\footnote{\bibentry{DPGNS_1d}} and space-time.\footnote{\bibentry{DPGspacetime}}
-}
 
@@
 \begin{align*}
-\div \vecttwo{\rho u_1 }{\rho u_2} &= 0\\
-\div \left(\vecttwo{\rho u_1^2+p }{\rho u_1 u_2} - \boldsymbol \sigma_{1}\right) &=0\\
-\div \left(\vecttwo{\rho u_1 u_2}{\rho u_2^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
-\div \left(\vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2} - \boldsymbol\sigma \mathbf{u} + \vec{q}\right) &=0\\
-\frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I &= \grad \mathbf{u} - \Reyn \, \boldsymbol w\\
-\frac{1}{\kappa}\vec{q} &= \grad T
+\div \vecttwo{\rho u_1 }{\rho u_2} &= 0,\\
+\div \left(\vecttwo{\rho u_1^2+p }{\rho u_1 u_2} - \boldsymbol \sigma_{1}\right) &=0,\\
+\div \left(\vecttwo{\rho u_1 u_2}{\rho u_2^2+p } - \boldsymbol \sigma_{2}\right) &=0,\\
+\div \left(\vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2} - \boldsymbol\sigma \mathbf{u} + \vec{q}\right) &=0,\\
+\frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I &= \grad \mathbf{u} - \Reyn \, \boldsymbol w,\\
+\kappa^{-1}\vec{q} &= \grad T,
 \end{align*}
-}
-
-\frame{
-\frametitle{Stress law}
-$\boldsymbol\sigma$ for a Newtonian fluid: $\sigma_{ij} = \mu(u_{i,j} + u_{j,i}) + \lambda u_{k,k} \delta_{ij}$.
-%We can invert the stress tensor under isotropic and plane strain assumptions to get
-\[
-\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \frac{1}{2\mu} \sigma_{ij} - \frac{\lambda}{4\mu (\mu + \lambda)} \sigma_{kk}\delta_{ij}
-\]
-The symmetric part of the gradient is
-\[
-\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \grad  U - \boldsymbol w
-\]
-Our final form is
-\begin{align*}
-\grad  U - \boldsymbol w= \frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I.
-\end{align*}
-By enforcing strong symmetry of $\boldsymbol \sigma$, taking the antisymmetric part implicitly defines $\boldsymbol w$ to be the antisymmetric part of $\grad u$. 
+where $\boldsymbol w$ represents the antisymmetric part of $\grad u$
 }
@@
 \begin{align*}
-\div \left(\beta u - \sigma\right) &= f\\
-\frac{1}{\epsilon}\sigma - \grad u &= 0.
+\div \left(\textcolor{red}{\beta u} - \textcolor{blue}{\sigma}\right) &= f\\
+\frac{1}{\epsilon}\sigma - {\grad u} &= 0.
 \end{align*}
@@
 \begin{align*}
-\div \left(A_{\rm invisc}U - A_{\rm visc}\Sigma\right) &= R_{\rm conserv}(U,\Sigma)\\
+\div \left(\textcolor{red}{A_{\rm invisc}U} - \textcolor{blue}{A_{\rm visc}\Sigma}\right) &= R_{\rm conserv}(U,\Sigma)\\
 E_{\rm visc} \Sigma - \grad U &= R_{\rm constit}(U,\Sigma)
@@
 }
-
+%\addtocounter{framenumber}{-1}
 \frame{
-\frametitle{Test norms over one element}
+\frametitle{Extrapolation of test norms}
+%\begin{columns}
+%\begin{column}{.48\textwidth}
 Convection-diffusion:
 \begin{align*}
-\|\left(v,\tau\right)\|_{V,K}^2 =& \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \|\beta \cdot \grad v\|^2 + \epsilon \|\grad v\|^2  \\
-&+\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
+\div \left(\beta u - \sigma\right) &= f\\
+\textcolor{red}{\frac{1}{\epsilon}\sigma} - \textcolor{blue}{\grad u} &= 0.
 \end{align*}
-
-Navier-Stokes: let $V$ and $W$ be vectors of test functions $v_i$ and $\tau_i$.
+Navier-Stokes: defining vector variables $U = \{\rho,u_1,u_2,T\}$ and $\Sigma = \{{\boldsymbol \sigma},\mathbf{q},w\}$,
 \begin{align*}
-\|\left(V,W\right)\|_{V,K}^2 =& \min\left\{\frac{1}{\Reyn|K|},1\right\}\nor{V}^2  + \nor{A_{\rm invisc}^T \grad V}^2 + \frac{1}{\Reyn} \nor{A_{\rm visc}^T\grad V}^2 \\
-& + \nor{\div W}^2 + \min\left\{1,\frac{1}{\Reyn|K|}\right\}\nor{E_{\rm visc}^TW}^2.
+\div \left({A_{\rm invisc}U} - {A_{\rm visc}\Sigma}\right) &= R_{\rm conserv}(U,\Sigma)\\
+\textcolor{red}{E_{\rm visc} \Sigma} - \textcolor{blue}{\grad U} &= R_{\rm constit}(U,\Sigma)
 \end{align*}
+where $R_{\rm conserv}(U,\Sigma)$ and $R_{\rm constit}(U,\Sigma)$ are the conservation/constitutive residuals.
 }
@@
 
-\section{Future work}
-%\subsection{Area A}
-%\frame{
-%\frametitle{Proposed work: Area A}
-%\begin{itemize}
-%\item{\textbf{Completed: Prove robustness of DPG method for the scalar convection-diffusion problem.}}
-%
-%We have introduced a test norm under which the DPG method robustly bounds the $L^2$ error in the field variables $u$ and the scaled stress $\sigma$.
-Numerical results confirm the theoretical bounds given.
-%
-%\item{\textbf{\textcolor{red}{Proposed}: Attempt analysis of the linearized Navier-Stokes system.}}
-%
-%We hope to analyze the linearized Navier-Stokes equations to determine an optimal extrapolation of the test norm for the scalar convection-diffusion problem to systems. 
-%
-%\end{itemize}
-%}
-
-%\subsection{Area B}
-%
-\frame{
-%\frametitle{Proposed work: Area B}
-%\item{\textbf{Completed: Collaborative work with Nathan Roberts on the higher order parallel adaptive DPG code Camellia.}}
-%
-%Numerical experiments use the higher-order adaptive codebase Camellia, built by Nathan Roberts upon the Trilinos library.
-%The framework for arbitrary-irregularity anisotropic refinements in both $h$ and $p$ is in place, and the code is partially parallelized.
-
-\frametitle{Future work: anisotropic refinements and $hp$-schemes.}
-
-The error representation function drives refinement effectively, and we hope to generalize its use to anisotropic adaptive schemes. 
-\begin{figure}
-\centering
-\subfigure{\includegraphics[scale = .175]{figs/anisotropy/b5.png}}
-\subfigure{\includegraphics[scale = .18]{figs/anisotropy/v6.png}}
-\caption{Anisotropic mesh for a convection-diffusion boundary layer.}
-\end{figure}
-}
-
-\frame{
-\frametitle{Future work: distributed iterative static condensation.}
-\[
-Ku = \arr{A}{B}{B^T}{D}\vecttwo{u_{\rm flux}}{u_{\rm field}} = \vecttwo{f}{g} = l
-\]
-where $D$ has a block-diagonal structure. The system can be reduced to yield the condensed system
-\[
-\left(A-B D^{-1} B^T\right)u_{\rm flux} = f - B D^{-1} g
-\]
-where $D^{-1}$ can be inverted block-wise.
-For FE stiffness matrices under the Laplace equation, the Schur complement has reduced condition number of $O(h^{-1})$ as opposed to $O(h^{-2})$.\footnote{\bibentry{schurComplement}}
-}
-
-\frame{  
-\frametitle{Future work: a Nonlinear Hessian-based DPG method.}
-Given a nonlinear variational problem $b(u,v) = \ell(v)$, linear in $v$ but not in $u$, beginning with the \textit{nonlinear} dual residual 
-\[
-J(u_h) = \frac{1}{2}\|B(u_h)-\ell\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(u_h,v)-\ell(v)|^2}{\nor{v}_V^2}.
-\]
-produces a Hessian-based DPG method, which solves
-\[
-b_u(\Delta u,v) + b''(\Delta u, \delta u, v_{R(u)}) = \ell(v) - b(u,v) = r(u,v),
-\]
-and aims to minimize the nonlinear dual residual instead of the linearized problem residual. 
-}
-
-\frame{
-\frametitle{Future work: applications}
-\begin{columns}
-\begin{column}{.48\textwidth}
-\begin{itemize}
-\item{{Solutions for all problems over a range of Reynolds/Mach numbers.}}
-\item{{Flow over a bump, Holden's ramp problem (shock-boundary layer interaction).}}
-\item{{Time permitting: airfoils, regularized Euler.}}
-\end{itemize}
-\end{column}
-\begin{column}{.5\textwidth}
-\begin{figure}
-\centering
-\includegraphics[scale = .275]{figs/ramp.png}
-\end{figure}
-\end{column}
-\end{columns}
-}
-
 \frame{
@@
 
-\section{Extended slides}
-
-\frame{
-\frametitle{Extended literature review}
-\begin{itemize}
-\item Finite difference/volume methods, upwind stencils, monotonicity, ENO/WENO. 
-\item Artificial diffusion, flux limiters/discontinuity-capturing operators.
-\item DG fluxes can be interpreted as residual-based stabilizations similar to SUPG.\footnote{\bibentry{Brezzi20063293}}
-\item Hybridized DG (HDG) methods introduce independent unknowns for numerical traces. Fluxes are defined in terms of DG fluxes and the numerical trace.\footnote{\bibentry{hybridDG}}
-\end{itemize}
-}
-
-\frame{
-\frametitle{Specifics of the ultra-weak formulation}
-
-Given a first order system $Au = f$, multiply by test function $v$ and integrate 
-\[
-\LRp{Au,v} = \LRa{\gamma\LRp{Au},v} + \LRp{u,A^*_hv} = \LRp{f,v}
-\]
-If $u \in L^2\LRp{\Omega}$, the trace of $u$ is undefined, so we identify boundary terms $\LRa{\gamma\LRp{Au},v}_{\Gh} = \LRa{\widehat{u},v}_{\Gh}$ as unknowns $\widehat{u}$ on $\Gh$.
-For convection-diffusion,
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-\left( v, \tau \right)\right) = \left(u,\grad_h\cdot \tau - \beta \cdot \grad_h
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad_h v\right)_{\Oh}&\\
-  - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
-\end{align*}
-where 
-\begin{align*}
-\widehat{f}_n \coloneqq \beta_n u - \sigma_n \in H^{-1/2}(\Gh), \quad \widehat{u} \in H^{1/2}(\Gh)
-\end{align*}
-with the minimum energy extension norm on $\Gh$. We note that $H^{\pm 1/2}(\Gh)$ are \emph{closed} subspaces of $\prod_K H^{\pm 1/2}(\partial K)$. 
-}
-
-\frame{
-\frametitle{Inviscid equations}
-Issue: consider pure convection, $\div \beta u = f$. The ultra-weak variational formulation is
-\[
-\LRa{\widehat{f}_n,v}-\LRp{u,\beta\cdot \grad v} = \LRp{f,v},
-\]
-where $\widehat{f}_n \coloneqq \beta_n u$.
-When $\beta_n = 0$, $v$ has only a streamline derivative, and $\widehat{f}_n$ becomes an ill-defined trace in the cross-stream direction.
-For hyperbolic \emph{systems}, this issue manifests as \emph{sonic lines}.
-\begin{figure}
-\centering
-\includegraphics[scale=.25]{figs/sonicLines.pdf}
-\caption{Sonic lines ($u_n - c = 0$) appear for linearized Euler.}
-\end{figure}
-}
+%\input{futureWork}
+%\input{extendedSlides}
 

### 2012-09-07 docs/Jesse/Vienna/extendedSlides.tex

--- 2012-09-06 docs/Jesse/Proposal/boeingPres.tex
@@
-\documentclass[compress]{beamer}
-\mode<presentation>
-\usetheme{Warsaw}
-\usecolortheme{seagull}
-%\useoutertheme[subsection=false]{smoothbars}
-\useoutertheme{infolines}
-\useinnertheme{rectangles}
-
-\setbeamercovered{dynamic}
-
-\usepackage{array}
-\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
-\usepackage[utf8]{inputenc}
-\usepackage{listings}
-\usepackage{mathtools}
-\usepackage{dsfont}
-\usepackage{pdfpages}
-\usepackage[textsize=footnotesize,color=green]{todonotes}
-\usepackage{algorithm, algorithmic}
-\usepackage{bm}
-\usepackage{tikz}
-\usepackage[normalem]{ulem}
-
-\usepackage{graphicx}
-\usepackage{subfigure}
-%\usepackage{caption}
-%\usepackage{subcaption}
-
-\usepackage{color}
-\usepackage{undertilde}
-\usepackage{pdflscape}
-\usepackage{pifont}
-
-\usepackage{bibentry}
-\nobibliography*
-
-%\usepackage[osf]{mathpazo}
-%\usepackage{mathpazo}
-%\renewcommand\rmdefault{ptm}
-
-\renewcommand{\topfraction}{0.85}
-\renewcommand{\textfraction}{0.1}
-\renewcommand{\floatpagefraction}{0.75}
-
-\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
-\newcommand{\tensor}[1]{\underline{\vect{#1}}}
-\newcommand{\del}{\triangle}
-\newcommand{\grad}{\nabla}
-\newcommand{\curl}{\grad \times}
-\renewcommand{\div}{\grad \cdot}
-\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
-\newcommand{\eip}[1]{a\left( #1 \right)}
-\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
-\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
-
-\newcommand{\circone}{\ding{192}}
-\newcommand{\circtwo}{\ding{193}}
-\newcommand{\circthree}{\ding{194}}
-\newcommand{\circfour}{\ding{195}}
-\newcommand{\circfive}{\ding{196}}
-
-\newcommand{\Reyn}{\rm Re}
-
-\newcommand{\bs}[1]{\boldsymbol{#1}}
-\DeclareMathOperator{\diag}{diag}
-
-\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}
-
-\newcommand{\tablab}[1]{\label{tab:#1}}
-\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
-
-\newcommand{\theolab}[1]{\label{theo:#1}}
-\newcommand{\theoref}[1]{\ref{theo:#1}}
-\newcommand{\eqnlab}[1]{\label{eq:#1}}
-\newcommand{\eqnref}[1]{\eqref{eq:#1}}
-\newcommand{\seclab}[1]{\label{sec:#1}}
-\newcommand{\secref}[1]{\ref{sec:#1}}
-\newcommand{\lemlab}[1]{\label{lem:#1}}
-\newcommand{\lemref}[1]{\ref{lem:#1}}
-
-\newcommand{\mb}[1]{\mathbf{#1}}
-\newcommand{\mbb}[1]{\mathbb{#1}}
-\newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\nor}[1]{\left\| #1 \right\|}
-\newcommand{\snor}[1]{\left| #1 \right|}
-\newcommand{\LRp}[1]{\left( #1 \right)}
-\newcommand{\LRs}[1]{\left[ #1 \right]}
-\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
-\newcommand{\LRc}[1]{\left\{ #1 \right\}}
-\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
-\newcommand{\Grad} {\ensuremath{\nabla}}
-\newcommand{\Div} {\ensuremath{\nabla\cdot}}
-\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
-\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
-\newcommand{\uh}{\widehat{u}}
-\newcommand{\fnh}{\widehat{f}_n}
-\renewcommand{\L}{L^2\LRp{\Omega}}
-\newcommand{\pO}{\partial\Omega}
-\newcommand{\Gh}{\Gamma_h}
-\newcommand{\Gm}{\Gamma_{-}}
-\newcommand{\Gp}{\Gamma_{+}}
-\newcommand{\Go}{\Gamma_0}
-\newcommand{\Oh}{\Omega_h}
-
-\newcommand{\eval}[2][\right]{\relax
-  \ifx#1\right\relax \left.\fi#2#1\rvert}
-
-\def\etal{{\it et al.~}}
-
-\def\arr#1#2#3#4{\left[
-\begin{array}{cc}
-#1 & #2\\
-#3 & #4\\
-\end{array}
-\right]}
-\def\vecttwo#1#2{\left[
-\begin{array}{c}
-#1\\
-#2\\
-\end{array}
-\right]}
-\def\vectthree#1#2#3{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-\end{array}
-\right]}
-\def\vectfour#1#2#3#4{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-#4\\
-\end{array}
-\right]}
-
-\newcommand{\G} {\Gamma}
-\newcommand{\Gin} {\Gamma_{in}}
-\newcommand{\Gout} {\Gamma_{out}}
-
-% removes nav symbols
-\beamertemplatenavigationsymbolsempty
-
-% defines newblock as null, giving compile issues otherwise
-\let\newblock\relax
-
-\institute[ICES]{Institute for Computational Engineering and Sciences}
-
-\title[A DPG method for Compressible Flow]{A Discontinuous Petrov-Galerkin method for compressible flow problems}
-\date{August 15, 2012}
-\author[J. Chan, T. Ellis, L. Demkowicz, R. Moser]{Jesse Chan, Truman Ellis \\ Supervisors: Leszek Demkowicz, Robert Moser}
-
-\begin{document}
-\begin{frame}
-\maketitle
-\end{frame}
+\section{Extended slides}
 
 \frame{
-\frametitle{Compressible Navier-Stokes equations}
-\begin{columns}[c]
-\begin{column}{.475\textwidth}
-Numerical difficulties:
-\begin{itemize}
-\item{} Resolving solution features (sharp, localized viscous-scale phenomena)
-\begin{itemize}
-\item{} Shocks
-\item{} Boundary layers - resolution needed for drag/load
-\item{} Turbulence (non-localized)
-\end{itemize}
-\item{} Nonlinear convergence and uniqueness of solutions
-\item{} Stability of numerical schemes
-\begin{itemize}
-\item{} Coarse/adaptive grids
-\item{} Higher order
-\end{itemize}
-\end{itemize}
-\end{column}
-\begin{column}{.475\textwidth}
-\begin{figure}
-\centering
-\includegraphics[scale = .7]{figs/compFlowPics/airfoil_mesh.png}
-\end{figure}
-\end{column}
-\end{columns}
-\vspace{.2cm}
-\begin{center}
-Idea: begin first with the model problem of convection-diffusion.
-\end{center}
-}
-\frame{
-\frametitle{Robustness: convection-diffusion as a model problem}
-\vspace{-.5cm}
+\frametitle{Specifics of the ultra-weak formulation}
+
+Given a first order system $Au = f$, multiply by test function $v$ and integrate 
 \[
-\div \left(\beta u\right) - \epsilon \Delta u = f, \quad \text{on }\Omega \in \mathbb{R}^3
+\LRp{Au,v} = \LRa{\gamma\LRp{Au},v} + \LRp{u,A^*_hv} = \LRp{f,v}
 \]
-\vspace{-.5cm}
-\begin{columns}[c]
-\begin{column}{.49\textwidth}
-In 1D: $\beta u' - \epsilon u'' = f$. Standard continuous Galerkin variational formulation: solve
-\[
-b(u,v) = \ell(v), \quad u,v\in H^1_0([0,1])
-\]
-where
-\begin{align*}
-b(u,v) &= \int_\Omega -\beta uv' + \epsilon u'v' \\
-\ell(v) &= \int_\Omega f v 
-\end{align*}
-\end{column}
-\begin{column}{.49\textwidth}
-\begin{figure}
-\centering
-\includegraphics[scale=.35]{figs/GalerkinOscTight.png}
-\caption{Solution for $f=1$. Oscillations in the standard Galerkin method for large Peclet numbers ${\rm Pe} \coloneqq \frac{h}{\epsilon}$.}
-\end{figure}
-\end{column}
-\end{columns}
-}
-
-\frame{
-\frametitle{Streamline-upwind Petrov-Galerkin (SUPG)}
-SUPG solves $b_{\rm SUPG}(u,v) = l_{\rm SUPG}(v)$, where
-\begin{align*}
-b_{\rm SUPG}(u,v) &= b(u,v)+ \sum_{K} \int_{K} \tau \LRp{L_{\rm adv} v} L u \\
-l_{\rm SUPG}(v) &= \ell(v) + \sum_{K} \int_{K} \tau \LRp{L_{\rm adv}v} f.
-\end{align*}
-\vspace{-.5cm}
-\begin{columns}[c]
-\begin{column}{.44\textwidth}
-\vspace{-.5cm}
-\begin{itemize}
-\item{} $Lu = \div\left(\beta u\right) - \epsilon \triangle u$, $L_{\rm adv}u = \div \left(\beta u\right)$, and $\tau$ is a parameter. 
-%\item{} Recovers ``exact'' artificial diffusion for $f=0$.
-\item{} Effective for $f\neq 0$. %``exact'' artificial diffusion.
-\item{} \emph{Residual-based} stabilization. 
-\end{itemize}
-\end{column}
-\begin{column}{.54\textwidth}
-\begin{figure}
-\centering
-\includegraphics[scale=.38]{figs/SUPG.png}
-%\caption{Exact, Bubnov-Galerkin, and SUPG solutions.}
-\end{figure}
-\end{column}
-\end{columns}
-}
-
-\frame{
-\begin{columns}
-\begin{column}{.49\textwidth}
-Can be interpreted as a \emph{Petrov-Galerkin} method,
-\[
-b\LRp{u,\tilde{v}_{i}} = \ell\LRp{\tilde{v}_{i}}, \quad \forall i = 1,\ldots,N-1,
-\]
-where the SUPG test function $\tilde{v}_{i}$ is defined elementwise as\footnotemark
-\[
-\tilde{v}_{i} = \phi_i(x) + \tau L_{\rm adv} \phi_i.  
-\]
-\end{column}
-\begin{column}{.49\textwidth}
-\begin{figure}
-\centering
-\subfigure{\includegraphics[scale=.16]{figs/SUPGtest.png}}
-\caption{SUPG test function $v_i$.}
-\end{figure}
-\end{column}
-\end{columns}
-\footnotetext{\bibentry{SUPG}}
-}
-
-\section{The DPG Method}
-\frame{
-\frametitle{DPG: a minimum residual method via optimal testing}
-Given a trial space $U$ and Hilbert test space $V$,
-\[
-b(u,v) = \ell(v), \quad u\in U, \quad v\in V
-\]
-This is equivalent to the operator equation posed in $V'$
-\[
-Bu = \ell
-\]
-if we identify $B:U\rightarrow V'$ and $\ell\in V'$ such that 
-\begin{align*}
-\langle Bu,v\rangle_V &\coloneqq b(u,v), \quad u\in U, v\in V,\\
-\langle \ell,v\rangle_V &\coloneqq \ell(v), \quad v\in V.
-\end{align*}
-We seek to minimize the dual functional over $U_h \subset U$
-\[
-J(u_h) = \frac{1}{2}\|Bu_h-\ell\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(u_h,v)-\ell(v)|^2}{\nor{v}_V^2}.
-\]
-}
-
-\begin{frame}
-Let $R_V: V \to V'$ be the isometric Riesz map st.\
-\[
-\langle R_V v,\delta v\rangle_V \coloneqq(v, \delta v)_V, \quad \forall \delta v \in V.
-\]
-Then, our functional $J(u_h)$ is equal to
-\begin{equation*}
-\min_{u_h\in U_h} J(u_h) = \frac{1}{2}\left\|Bu_h-\ell\right\|_{V'}^2 =  \frac{1}{2}\left\|R_V^{-1}(Bu_h-\ell)\right\|_V^2.
-\end{equation*}
-First order optimality: G\^ateaux derivative is zero in all directions $\delta u \in U_h$
-\begin{align*}
-\left(R_V^{-1}(Bu_h-\ell),R_V^{-1}B\delta u\right)_V &= 0, \quad \forall \delta u \in U_h.\\
-\rightarrow \LRa{(Bu_h-\ell),R_V^{-1}B\delta u} &= 0, \\
-\rightarrow b(u_h,R_V^{-1}B\delta u) - \ell(R_V^{-1}B\delta u) &= 0
-\end{align*}
-\end{frame}
-
-\frame{
-\frametitle{Summary: select test functions to minimize residuals}
-For $\delta u \in U_h$, define the \textcolor{red}{optimal test function} $v_{\delta u}$. 
-\begin{equation*}
-v_{\delta u} \coloneqq R_V^{-1}B\delta u.
-\end{equation*} 
-Then, the residual $J(u_h) = \frac{1}{2}\left\|Bu_h-\ell\right\|_{V'}^2$ is minimized by the solution of
-\[
-b\LRp{u_h,v_{\delta u}} = \ell\LRp{v_{\delta u}}, \quad \forall \delta u \in U_h.
-\]
-}
-
-\frame{
-\frametitle{Practical details of DPG}
-Computation of $v_{\delta u} \coloneqq R_V^{-1}B\delta u$ is \textbf{global} and \textbf{infinite-dimensional}.
-\begin{itemize}
-\item By choosing a \textcolor{red}{broken} test space $V$ and \textcolor{red}{localizable} norm $\nor{v}_V^2 = \sum_K \nor{v}_{V(K)}^2$, test functions can be determined locally.
-\item In practice, we use an \textcolor{red}{enriched space} $V_h \subset V$, where $\dim(V_h) > \dim(U_h)$ elementwise, and \textcolor{red}{optimal test functions} are approximated by computing $v_{\delta u} \coloneqq R_{V_h}^{-1}B\delta u \in V_h$ through\footnote{\bibentry{DPG2}}
-\[
-\LRp{v_{\delta u},\delta v}_V = b(\delta u,\delta v), \quad \delta u\in U_h, \quad \forall \delta v\in V_h
-\]
-Typically, if $U_h = \mathcal{P}^p(\mathbb{R}^n)$, $V_h = \mathcal{P}^{p+\triangle p}(\mathbb{R}^n)$, where $\triangle p \geq n$.\footnote{\bibentry{practicalDPG}} 
-\end{itemize}
-%\footnotetext{\bibentry{DPG2}}
-}
-
-\frame{
-\frametitle{Properties of DPG}
-DPG provides a symmetric positive-definite stiffness matrix. Let $\{\phi_j\}_{j=1}^m$ be a basis for $U_h$, and $\{v_i\}_{i=1}^n$ a basis for $V_h$, such that $n>m$. Then, for 
-\begin{align*}
-B_{ji} &= b(\phi_j,v_i),\\
-l_i &= \ell(v_i),
-\end{align*}
-DPG solves the discrete system for degrees of freedom $u$
-\begin{align*}
-\LRp{B^T R_V^{-1}B} u  &= \LRp{B^T R_V^{-1}} l,
-\end{align*}
-where, under a localizable norm and discontinuous test functions, $R_V^{-1}$ is block diagonal.
-}
-
-\frame{
-\frametitle{Properties of DPG}
-Additional properties of DPG include\footnotemark
-\begin{itemize}
-\item DPG provides the best approximation in the \textcolor{red}{energy norm}
-\[
-\|u\|_E = \|Bu\|_{V'} = \sup_{\nor{v}_V=1} \left|b(u,v)\right|.
-\]
-\item The energy error is computable through the residual
-\[
-\nor{u-u_h}_E = \nor{B(u-u_h)}_{V'} = \nor{R_V^{-1}(l-Bu_h)}_V = \nor{e}_V
-\]
-where the \textcolor{red}{error representation function} $e$ is defined through $(e,\delta v)_V = \ell(v)-b(u_h,\delta v)$ for all $\delta v\in V$. 
-\end{itemize}
-\footnotetext{\bibentry{DPG3pub}}
-}
-
-%\frame{
-%\frametitle{Duality of norms}
-%Duality of norms: for any trial norm $\nor{u}_U$,
-%\[
-%\nor{u}_{U} = \sup_{v \in V}\frac{b\LRp{u,v}}{\nor{v}_{V,U}}, \quad \nor{v}_{V,U} = \sup_{u \in U}\frac%{b\LRp{u,v}}{\nor{u}_{U}}.
-%\]
-%Likewise, for any test norm $\nor{v}_V$, 
-%\[
-%\nor{v}_{V} = \sup_{u \in U}\frac{b\LRp{u,v}}{\nor{U}_{U,V}}, \quad \nor{u}_{U,V} = \sup_{v \in V}\frac%{b\LRp{u,v}}{\nor{v}_{V}}.
-%\]
-%
-%}
-
-\frame{
-\frametitle{Ultra-weak formulation}
-\vspace{-.75cm}
-\begin{columns}
-\begin{column}{.64\textwidth}
-Given a first order system $Au = f$, we identify the \textbf{\emph{partition}} $\Oh$ and \textbf{\textcolor{red}{mesh skeleton}} \textcolor{red}{$\Gh$}.
-\end{column}
-\begin{column}{.34\textwidth}
-%\[
-%\Oh = \cup_{j=1}^\Nel K_j, \quad \Gh = \cup_{j=1}^\Nel \partial K_j
-%\]
-\begin{figure}[!h]
-\centering
-\includegraphics[scale = .155]{mesh_skel.pdf}
-\end{figure}
-\end{column}
-\end{columns}
-\vspace{-.5cm}
-The ultra-weak formulation for $Au = f$ on $\Oh$ is
-\[
-b\left(\left(u, \widehat{u}\right),v\right) \coloneqq \sum_K\langle \widehat{u},v \rangle_{\partial K} + (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh}.
-\]
-Under proper assumptions, $\sum_K\langle \widehat{u},v \rangle_{\partial K} = \langle \widehat{u}, \jump{v} \rangle_{\Gh}$, with energy setting
-\[
-u\in L^2\LRp{\Oh} \equiv L^2(\Omega), \quad v\in V=D(A^*_h), \quad
-\widehat{u}\in \gamma(D(A)),
-\]
-where $D(A_h^*)$ is the broken graph space of the formal adjoint $A_h^*$, and $\gamma(D(A))$ the trace space of the graph space of operator $A$.\footnote{\bibentry{analysisDPG}}
-}
-
-\frame{
-\frametitle{The canonical ``graph'' test norm}
-Recall $\nor{u}_E \coloneqq \sup_{v\in V\setminus\{0\}}\frac{b(u,v)}{\nor{v}_V}$. Under the ultra-weak formulation, the trial norm 
-\[
-\nor{\LRp{u,\widehat{u}}}_U \coloneqq \|u\|^2_{\L} + \|\widehat{u}\|^2
-\] 
-generates a test norm \emph{equivalent} to 
-\[
-\nor{v}_{V_{\rm opt}} \coloneqq \|A_h^*v\|_{\L}^2 +\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},\jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2.
-\]
-This norm is not localizable, so we instead substitute the jump terms for an $L^2$ term, giving us the \emph{graph norm}\footnote{\bibentry{Bui-ThanhDemkowiczGhattas11b}}
-\[
-\nor{v}_V \coloneqq \|A_h^*v\|_{\L}^2 + \nor{v}_{L^2}.
-\]
-}
-
-\frame{
-\frametitle{Goal: robust higher order adaptive methods}
-\begin{columns}
-\begin{column}{.45\textwidth}
-Our aim is to design an adaptive method for compressible laminar flows that is 
-\begin{itemize}
-\item robust in Reynolds number
-\item stable for arbitrary elements
-\end{itemize}
-
-This proposal will outline
-\begin{enumerate}
-\item a robust DPG method for convection-diffusion,
-\item extension to nonlinear problems and systems,
-\item proposed work.
-\end{enumerate}
-
-\end{column}
-\begin{column}{.54\textwidth}
-\begin{figure}
-\centering
-\subfigure{\includegraphics[scale=.23]{figs/Re1000p2/u2_full.png}}
-\subfigure{\includegraphics[scale=.37]{figs/Re1000p2/mesh6.png}}
-\caption{$u_2$ and $p=2$ mesh for $\Reyn = 1000$.}
-\end{figure}
-\end{column}
-\end{columns}
-}
-
-\section{A Robust DPG Method for Convection-Diffusion}
-
-\frame{
-\frametitle{Ultra-weak formulation for convection-diffusion}
-In first order form, the convection-diffusion equation is
-\[
-A \LRp{u,\sigma} \coloneqq 
-\LRs {
-\begin{array}{c}
-\div (\beta u - \sigma) \\ \frac{1}{\epsilon}\sigma - \grad u
-\end{array}} = \LRs{
-\begin{array}{c}
-f \\ 0
-\end{array}
-}.
-\]
-The variational formulation is
+If $u \in L^2\LRp{\Omega}$, the trace of $u$ is undefined, so we identify boundary terms $\LRa{\gamma\LRp{Au},v}_{\Gh} = \LRa{\widehat{u},v}_{\Gh}$ as unknowns $\widehat{u}$ on $\Gh$.
+For convection-diffusion,
 \begin{align*}
@@
 \end{align*}
-where $\widehat{f}_n \coloneqq \beta_n u - \sigma_n$ and $\LRa{\widehat{f}_n,\jump{v} }_{\Gh}$ is defined 
-\[
-\LRa{\widehat{f}_n,\jump{v} }_{\Gh}\coloneqq \sum_K\int_{\partial K}{\rm sgn}(\vec{n}) \, \widehat{f}_n v.
-\]
+where 
+\begin{align*}
+\widehat{f}_n \coloneqq \beta_n u - \sigma_n \in H^{-1/2}(\Gh), \quad \widehat{u} \in H^{1/2}(\Gh)
+\end{align*}
+with the minimum energy extension norm on $\Gh$. We note that $H^{\pm 1/2}(\Gh)$ are \emph{closed} subspaces of $\prod_K H^{\pm 1/2}(\partial K)$. 
 }
@@
 \frame{
-\frametitle{Graph norm under convection-diffusion}
-For convection-diffusion, the graph test norm is defined elementwise
+\frametitle{Inviscid equations}
+Issue: consider pure convection, $\div \beta u = f$. The ultra-weak variational formulation is
 \[
-\|\left(v,\tau\right)\|_{V(K)}^2 = \| \div \tau - \beta \cdot \grad v
-\|_{L^2(K)}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2(K)}^2 +
-\|v\|_{L^2(K)}^2.
+\LRa{\widehat{f}_n,v}-\LRp{u,\beta\cdot \grad v} = \LRp{f,v},
 \]
-Problem with this test norm: approximability of test functions.
-\vspace{-.3cm}
-\begin{figure}[!h]
+where $\widehat{f}_n \coloneqq \beta_n u$.
+When $\beta_n = 0$, $v$ has only a streamline derivative, and $\widehat{f}_n$ becomes an ill-defined trace in the cross-stream direction.
+For hyperbolic \emph{systems}, this issue manifests as \emph{sonic lines}.
+\begin{figure}
 \centering
-\includegraphics[scale=.175]{figs/opt.png}
-\caption{$v$ and $\tau$ components of the 1D optimal test functions for flux $\widehat{f}_n$ on the \emph{right-hand} side of a unit element for $\epsilon = 0.01$. }
-\label{fig:optTestBoundary}
+\includegraphics[scale=.25]{figs/sonicLines.pdf}
+\caption{Sonic lines ($u_n - c = 0$) appear for linearized Euler.}
 \end{figure}
@@
 
-\frame{
-\frametitle{Determining an alternative test norm}
-Recall the convection-diffusion bilinear form
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh}&\\
- - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
-\end{align*}
-We recover $\nor{u}^2_{L^2(\Omega)}$ by choosing conforming $\LRp{v,\tau}$ satisfying the \emph{adjoint equations}
-\begin{align*}
-\div\tau - \beta \cdot \grad v   &= u\\
-\frac{1}{\epsilon}\tau + \grad v &= 0
-\end{align*}
-with boundary conditions s.t.\ $\LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gamma}$ and $\LRa{ \widehat{f}_n,\jump{v} }_{\Gamma}$ vanish.
-}
-
-\frame{
-\frametitle{A robust bound}
-``Necessary'' conditions for robustness --- let $\boldsymbol U = \LRp{u,\sigma,\widehat{u},\widehat{f}_n}$. Then, by choosing specific $\LRp{v,\tau}$ satisfying the adjoint equations,
-\[
-\nor{u}^2_{L^2(\Omega)} = b\LRp{{\boldsymbol U},\LRp{v,\tau}} = \frac{b\LRp{{\boldsymbol U},\LRp{v,\tau}}}{\nor{\LRp{v,\tau}}_V} \nor{\LRp{v,\tau}}_V \leq \nor{\boldsymbol U}_E \nor{\LRp{v,\tau}}_V
-\]
-Let $\lesssim$ denote a robust bound - \textcolor{red}{if $ \nor{\LRp{v,\tau}}_V \lesssim \|u\|_{L^2(\Omega)}$}, then we have that
-\[
-\nor{u}_{L^2(\Omega)} \lesssim \nor{\boldsymbol U}_E
-\]
-\textbf{Main idea: the \textcolor{red}{test norm} should measure \textcolor{red}{adjoint solutions} robustly.}
-}
-
-\frame{
-\frametitle{Choice of inflow boundary condition}
-
-\begin{columns}
-\begin{column}{.49\textwidth}
-We impose the standard outflow wall boundary condition on $u$. For inflow boundary condition: 
-\begin{itemize}
-\item{} The standard choice of inflow boundary condition: $u = u_0$.
-\item{} We impose the non-standard inflow condition: $\widehat{f}_n \coloneqq \beta_n u - \sigma_n \approx \beta_n u_0$ on $\Gamma_{\rm in}$.
-\end{itemize}
-\end{column}
-
-\begin{column}{.49\textwidth}
-\begin{figure}
-\includegraphics[scale=.23]{figs/primal.png}
-\caption{Non-standard inflow.}
-\end{figure}
-\end{column}
-\end{columns}
-When $\sigma_n \approx 0$ near the inflow, condition on $\widehat{f}_n$ approximates condition on $u$.
-
-}
-
-\frame{
-\frametitle{Dirichlet inflow boundary condition}
-Standard choice of boundary condition: $u = u_0$ on inflow boundary $\Gamma_{\rm in}$, induces boundary layers in adjoint problems, \textcolor{red}{$\nor{\beta\cdot \grad v}_{L^2} = O(\epsilon^{-1})$}.
-\begin{figure}[h!]
-\centering
-\subfigure[Primal problem]{\includegraphics[scale=.23]{figs/primalDir.png}}
-\subfigure[Adjoint problem]{\includegraphics[scale=.23]{figs/adjointDir.png}}
-\caption{For the standard Dirichlet inflow condition, the solution to the adjoint problem can develop strong boundary layers at the outflow of the adjoint problem. }
-\end{figure}
-}
-
-\frame{
-\frametitle{New inflow boundary condition on $\widehat{f}_n$}
-Non-standard choice of boundary condition: $\widehat{f}_n = \beta_n u_0$ on $\Gamma_{\rm in}$, induces smoother adjoint problems, \textcolor{red}{$\nor{\beta\cdot \grad v}_{L^2} = O(1)$}.
-\begin{figure}[h!]
-\centering
-\subfigure[Primal problem]{\includegraphics[scale=.23]{figs/primal.png}}
-\subfigure[Adjoint problem]{\includegraphics[scale=.23]{figs/adjoint.png}}
-\caption{Under the new inflow condition, the wall-stop boundary condition is relaxed to a zero-stress condition at the outflow boundary of the adjoint problem.}
-\end{figure}
-}
-
-\frame{
-\frametitle{Test norms and adjoint solutions}
-\textbf{Intuition:} the effectiveness of DPG under a test norm is governed by how a \textbf{specific test norm} measures the \textbf{solutions of the adjoint problem}.
-
-\begin{figure}[!h]
-\centering
-\subfigure[Dirichlet inflow]{\includegraphics[scale=.35]{figs/dirichletBC.png}}
-\subfigure[``Convection'' inflow]{\includegraphics[scale=.35]{figs/newBC.png}}
-\caption{DPG solutions to convection-diffusion for both inflow conditions using an $H^1$ test norm.}
-\end{figure}
-}
-
-%\frame{
-%\frametitle{``Building blocks'' norm}
-%Test norm quantities are robustly bounded from above by $\nor{u}_{L^2(\Omega)}$.  
-%\[
-%\|\left(v,\tau\right)\|_{V,K}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2.
-%\]
-%Problem: boundary layers in optimal test functions:
-%\begin{figure}[!h]
-%\centering
-%\subfigure{\includegraphics[scale=.15]{figs/mesh1.png}}
-%\subfigure{\includegraphics[scale=.15]{figs/sol1.png}}
-%\caption{The $v$ component of the optimal test function corresponding to flux $\widehat{u} = x(1-x)$ on the bottom side of a unit element for $\epsilon = 0.01$.}
-%\label{fig:boundaryTest}
-%\end{figure}
-%}
-\frame{
-\frametitle{Adjoint estimates, or ``norm building blocks''}
-For solutions $(v,\tau)$ of the adjoint equations, the following quantities are robustly bounded from above by $\nor{u}_{L^2(\Omega)}$.  
-\begin{align*}
-&\|v\|, \sqrt{\epsilon} \|\grad v\|, \|\beta \cdot \grad v\| \\
-&\| \div \tau\|, \frac{1}{\sqrt{\epsilon}}\|\tau\|.
-\end{align*}
-We will construct a test norm through a combination of the above quantities, such that
-\begin{itemize}
-\item $v$ and $\tau$ decoupled (no systems).
-\item Coefficients are of equal order after transforming to the unit element (no boundary layers).
-\end{itemize}
-}
-\frame{
-\frametitle{Mesh-scaled test norms}
-Our test norm, as defined over a single element $K$, is now
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 +&\\
-\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2&.
-\end{align*}
-which induces the proven \emph{robust} bound\footnote{\bibentry{DPGrobustness2}}
-\[
-\nor{u}_{L^2(\Omega)}+ \nor{\sigma}_{L^2(\Omega)} + \epsilon\nor{\widehat{u}} + \sqrt{\epsilon} \nor{\widehat{f}_n} \lesssim \nor{\LRp{u,\sigma,\widehat{u},\widehat{f}_n}}_E.
-\]
-}
-
-\frame{
-\frametitle{Erikkson-Johnson model problem}
-
-On domain $\Omega = [0,1]^2$, with $\beta = (1,0)^T$, $ f = 0$ and boundary conditions
-\begin{align*}
-\widehat{\beta_nu - \sigma_n} &= \widehat{f}_n = u_0, \quad \beta_n \leq 0\\
-\widehat{u} &= 0, \quad \beta_n > 0
-\end{align*}
-
-%Separation of variables gives an analytic solution. 
-All numerical experiments done using Camellia codebase.\footnote{\bibentry{Camellia}}
-%\[
-%u(x,y) = C_0 + \sum_{n=1}^\infty C_n \frac{\exp(r_2(x-1)-\exp(r_1(x-1)))}{r_1\exp(-r2) - r_2\exp(-r1)}\cos(n\pi y)
-%\]
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale=.23]{figs/wallBC_exact_u.png}
-}
-\subfigure{
-\includegraphics[scale=.23]{figs/wallBC_exact_sigx.png}
-}
-\subfigure{
-\includegraphics[scale=.23]{figs/wallBC_exact_sigy.png}
-}
-\caption{Exact solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
-\end{figure}
-}
-
-\frame{
-\frametitle{Error rates}
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale=.33]{figs/errorrates_wallBC.png}
-}
-\subfigure{
-\includegraphics[scale=.33]{figs/L2energyratio_wallBC.png}
-}
-%\subfigure{
-%\includegraphics[scale=.22]{figs/u_pointdiff_wallBC.png}
-%}
-\caption{$L^2$/energy errors and their ratio for $\epsilon = .01, .001, .0001$.}
-\end{figure}
-}
-
-%\frame{
-%\frametitle{Regularization}
-%Discontinuous inflow conditions on $\widehat{f_n}$, out of alignment with mesh. Boundary condition $\epsilon \grad u \cdot n = 0$ at outflow.
-%\begin{figure}
-%\centering
-%\subfigure{
-%\includegraphics[scale=.33]{figs/discontinuous.png}
-%}
-%\subfigure{
-%\includegraphics[scale=.305]{figs/discontinuousL2rates.png}
-%}
-%\caption{Discontinuous hat inflow data with $\epsilon = 1e-5$, convection solution errors.}
-%\end{figure}
-%}
 \frame{
@@
 }
-
-\section{DPG for nonlinear problems}
-\frame{
-\frametitle{DPG for nonlinear problems}
-
-Given some linearization technique (typically Newton-Raphson and pseudo-timestepping linearization), we measure 
-\begin{itemize}
-\item size of the linearized update $\Delta u$
-\[
-\|\Delta u\|_E \coloneqq \nor{B_u\Delta u}_{V'} = \nor{R_V^{-1} B_u\Delta u}_V 
-\]
-\item the nonlinear residual 
-\[
-\nor{R(u)}_E \coloneqq \nor{B(u) - \ell}_{V'}  = \nor{R_V^{-1}\LRp{B(u)-\ell}}_V 
-\]
-\end{itemize}
-Preliminary experiments were done in 1D\footnote{\bibentry{DPGNS_1d}} and space-time.\footnote{\bibentry{DPGspacetime}}
-}
-
-\frame{
-\frametitle{2D test case: Burgers equation}
-\begin{columns}
-\begin{column}{.48\textwidth}
-\vspace{-.5cm}
-\[
-\pd{\left(u^2/2\right)}{x} + \pd{u}{y} + \epsilon \Delta u = f
-\]
-Burgers equation can be written with $\beta(u) = \LRp{u/2,1}$
-\begin{align*}
-\div\left(\beta(u)u-\sigma\right) &=f \\
-\frac{1}{\epsilon}\sigma - \grad u &=0.
-\end{align*}
-i.e.\ nonlinear convection-diffusion on domain $[0,1]^2$.
-\end{column}
-\begin{column}{.48\textwidth}
-\begin{figure}[!h]
-\centering
-\includegraphics[scale = .22]{figs/burgers.png}
-\caption{Shock solution for Burgers' equation, $\epsilon = 1e-4$, using Newton-Raphson.}
-\end{figure}
-\end{column}
-\end{columns}
-}
-\frame{
-Adaptivity begins with a cubic $4\times 4$ mesh.
-\begin{figure}[!h]
-\centering
-\subfigure{\includegraphics[scale=.2]{figs/burgersMesh.png}}
-\subfigure{\includegraphics[scale=.2]{figs/burgersZoom.png}}
-\caption{Adaptive mesh after 9 refinements, and zoom view at point (.5,.5) with shock formation and $1e-3$ width line for reference.}
-\end{figure}
-}
-
-\frame{
-\frametitle{2D Compressible Navier-Stokes equations (ideal gas)}
-Given density $\rho$, velocities $\mathbf{u} = \LRp{u_1,u_2}$ and temperature $T$,
-\begin{align*}
-\div \vecttwo{\rho u_1 }{\rho u_2} &= 0\\
-\div \left(\vecttwo{\rho u_1^2+p }{\rho u_1 u_2} - \boldsymbol \sigma_{1}\right) &=0\\
-\div \left(\vecttwo{\rho u_1 u_2}{\rho u_2^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
-\div \left(\vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2} - \boldsymbol\sigma \mathbf{u} + \vec{q}\right) &=0\\
-\frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I &= \grad \mathbf{u} - \Reyn \, \boldsymbol w\\
-\frac{1}{\kappa}\vec{q} &= \grad T
-\end{align*}
-}
-
-\frame{
-\frametitle{Stress law}
-$\boldsymbol\sigma$ for a Newtonian fluid: $\sigma_{ij} = \mu(u_{i,j} + u_{j,i}) + \lambda u_{k,k} \delta_{ij}$.
-%We can invert the stress tensor under isotropic and plane strain assumptions to get
-\[
-\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \frac{1}{2\mu} \sigma_{ij} - \frac{\lambda}{4\mu (\mu + \lambda)} \sigma_{kk}\delta_{ij}
-\]
-The symmetric part of the gradient is
-\[
-\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \grad  U - \boldsymbol w
-\]
-Our final form is
-\begin{align*}
-\grad  U - \boldsymbol w= \frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I.
-\end{align*}
-By enforcing strong symmetry of $\boldsymbol \sigma$, taking the antisymmetric part implicitly defines $\boldsymbol w$ to be the antisymmetric part of $\grad u$. 
-}
-
-\frame{
-\frametitle{Extrapolation of test norms}
-%\begin{columns}
-%\begin{column}{.48\textwidth}
-Convection-diffusion:
-\begin{align*}
-\div \left(\beta u - \sigma\right) &= f\\
-\frac{1}{\epsilon}\sigma - \grad u &= 0.
-\end{align*}
-Navier-Stokes: defining vector variables $U = \{\rho,u_1,u_2,T\}$ and $\Sigma = \{{\boldsymbol \sigma},\mathbf{q},w\}$,
-\begin{align*}
-\div \left(A_{\rm invisc}U - A_{\rm visc}\Sigma\right) &= R_{\rm conserv}(U,\Sigma)\\
-E_{\rm visc} \Sigma - \grad U &= R_{\rm constit}(U,\Sigma)
-\end{align*}
-where $R_{\rm conserv}(U,\Sigma)$ and $R_{\rm constit}(U,\Sigma)$ are the conservation/constitutive residuals.
-}
-
-\frame{
-\frametitle{Test norms over one element}
-Convection-diffusion:
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,K}^2 =& \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \|\beta \cdot \grad v\|^2 + \epsilon \|\grad v\|^2  \\
-&+\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
-\end{align*}
-
-Navier-Stokes: let $V$ and $W$ be vectors of test functions $v_i$ and $\tau_i$.
-\begin{align*}
-\|\left(V,W\right)\|_{V,K}^2 =& \min\left\{\frac{1}{\Reyn|K|},1\right\}\nor{V}^2  + \nor{A_{\rm invisc}^T \grad V}^2 + \frac{1}{\Reyn} \nor{A_{\rm visc}^T\grad V}^2 \\
-& + \nor{\div W}^2 + \min\left\{1,\frac{1}{\Reyn|K|}\right\}\nor{E_{\rm visc}^TW}^2.
-\end{align*}
-}
-
-\frame{
-\frametitle{Carter's flat plate problem}
-\begin{columns}
-\begin{column}{.49\textwidth}
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.32]{figs/flat_plate_BCs.pdf}
-\caption{Carter flat plate problem on domain $[0,2]\times[0,1]$. Plate begins at $x=1$, ${\rm Re} = 1000$.}
-\end{figure}
-\end{column}
-\begin{column}{.49\textwidth}
-\begin{enumerate}
-\item{} Symmetry boundary conditions.
-\item{} Prescribed temperature and wall stagnation conditions.
-\item{} Symmetry boundary conditions.
-\item{} Inflow: conserved quantities specified using far-field values.
-\item{} No outflow condition set.
-\end{enumerate}
-Stress/heat flux boundary conditions are set in terms of the momentum and energy fluxes. 
-\end{column}
-\end{columns}
-}
-
-\frame{
-\frametitle{Refinement level 0}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u0.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T0.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh0.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 1}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u1.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T1.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh1.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 2}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u2.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T2.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh2.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 3}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u3.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T3.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh3.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 4}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u4.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T4.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh4.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 5}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u5.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T5.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh5.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 6}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u6.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T6.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh6.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 7}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u7.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T7.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh7.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 8}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u8.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T8.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh8.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 9}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u9.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T9.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh9.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 10}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u10.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T10.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh10.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Zoomed solutions at plate/stagnation point}
-\begin{figure}
-\centering
-\subfigure[$\rho$]{\includegraphics[scale = .12]{figs/Re1000p2/rhoUnscaledzoom.png}}
-\subfigure[$u_1$]{\includegraphics[scale = .12]{figs/Re1000p2/u1zoom.png}}
-\subfigure[$u_2$]{\includegraphics[scale = .12]{figs/Re1000p2/u2zoom.png}}
-\subfigure[$T$]{\includegraphics[scale = .12]{figs/Re1000p2/Tzoom.png}}
-\subfigure[$q_n$]{\includegraphics[scale = .23]{figs/Re1000p2/heatflux.png}}
-\end{figure}
-}
-
-\section{Future work}
-%\subsection{Area A}
-%\frame{
-%\frametitle{Proposed work: Area A}
-%\begin{itemize}
-%\item{\textbf{Completed: Prove robustness of DPG method for the scalar convection-diffusion problem.}}
-%
-%We have introduced a test norm under which the DPG method robustly bounds the $L^2$ error in the field variables $u$ and the scaled stress $\sigma$.
-Numerical results confirm the theoretical bounds given.
-%
-%\item{\textbf{\textcolor{red}{Proposed}: Attempt analysis of the linearized Navier-Stokes system.}}
-%
-%We hope to analyze the linearized Navier-Stokes equations to determine an optimal extrapolation of the test norm for the scalar convection-diffusion problem to systems. 
-%
-%\end{itemize}
-%}
-
-%\subsection{Area B}
-%
-\frame{
-%\frametitle{Proposed work: Area B}
-%\item{\textbf{Completed: Collaborative work with Nathan Roberts on the higher order parallel adaptive DPG code Camellia.}}
-%
-%Numerical experiments use the higher-order adaptive codebase Camellia, built by Nathan Roberts upon the Trilinos library.
-%The framework for arbitrary-irregularity anisotropic refinements in both $h$ and $p$ is in place, and the code is partially parallelized.
-
-\frametitle{Future work: anisotropic refinements and $hp$-schemes.}
-
-The error representation function drives refinement effectively, and we hope to generalize its use to anisotropic adaptive schemes. 
-\begin{figure}
-\centering
-\subfigure{\includegraphics[scale = .175]{figs/anisotropy/b5.png}}
-\subfigure{\includegraphics[scale = .18]{figs/anisotropy/v6.png}}
-\caption{Anisotropic mesh for a convection-diffusion boundary layer.}
-\end{figure}
-}
-
-\frame{
-\frametitle{Future work: distributed iterative static condensation.}
-\[
-Ku = \arr{A}{B}{B^T}{D}\vecttwo{u_{\rm flux}}{u_{\rm field}} = \vecttwo{f}{g} = l
-\]
-where $D$ has a block-diagonal structure. The system can be reduced to yield the condensed system
-\[
-\left(A-B D^{-1} B^T\right)u_{\rm flux} = f - B D^{-1} g
-\]
-where $D^{-1}$ can be inverted block-wise.
-For FE stiffness matrices under the Laplace equation, the Schur complement has reduced condition number of $O(h^{-1})$ as opposed to $O(h^{-2})$.\footnote{\bibentry{schurComplement}}
-}
-
-\frame{  
-\frametitle{Future work: a Nonlinear Hessian-based DPG method.}
-Given a nonlinear variational problem $b(u,v) = \ell(v)$, linear in $v$ but not in $u$, beginning with the \textit{nonlinear} dual residual 
-\[
-J(u_h) = \frac{1}{2}\|B(u_h)-\ell\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(u_h,v)-\ell(v)|^2}{\nor{v}_V^2}.
-\]
-produces a Hessian-based DPG method, which solves
-\[
-b_u(\Delta u,v) + b''(\Delta u, \delta u, v_{R(u)}) = \ell(v) - b(u,v) = r(u,v),
-\]
-and aims to minimize the nonlinear dual residual instead of the linearized problem residual. 
-}
-
-\frame{
-\frametitle{Future work: applications}
-\begin{columns}
-\begin{column}{.48\textwidth}
-\begin{itemize}
-\item{{Solutions for all problems over a range of Reynolds/Mach numbers.}}
-\item{{Flow over a bump, Holden's ramp problem (shock-boundary layer interaction).}}
-\item{{Time permitting: airfoils, regularized Euler.}}
-\end{itemize}
-\end{column}
-\begin{column}{.5\textwidth}
-\begin{figure}
-\centering
-\includegraphics[scale = .275]{figs/ramp.png}
-\end{figure}
-\end{column}
-\end{columns}
-}
-
-\frame{
-\begin{center}
-Thank you!\\
-\vspace{1cm}
-Questions?
-\end{center}
-}
-
-\section{Extended slides}
-
-\frame{
-\frametitle{Extended literature review}
-\begin{itemize}
-\item Finite difference/volume methods, upwind stencils, monotonicity, ENO/WENO. 
-\item Artificial diffusion, flux limiters/discontinuity-capturing operators.
-\item DG fluxes can be interpreted as residual-based stabilizations similar to SUPG.\footnote{\bibentry{Brezzi20063293}}
-\item Hybridized DG (HDG) methods introduce independent unknowns for numerical traces. Fluxes are defined in terms of DG fluxes and the numerical trace.\footnote{\bibentry{hybridDG}}
-\end{itemize}
-}
-
-\frame{
-\frametitle{Specifics of the ultra-weak formulation}
-
-Given a first order system $Au = f$, multiply by test function $v$ and integrate 
-\[
-\LRp{Au,v} = \LRa{\gamma\LRp{Au},v} + \LRp{u,A^*_hv} = \LRp{f,v}
-\]
-If $u \in L^2\LRp{\Omega}$, the trace of $u$ is undefined, so we identify boundary terms $\LRa{\gamma\LRp{Au},v}_{\Gh} = \LRa{\widehat{u},v}_{\Gh}$ as unknowns $\widehat{u}$ on $\Gh$.
-For convection-diffusion,
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-\left( v, \tau \right)\right) = \left(u,\grad_h\cdot \tau - \beta \cdot \grad_h
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad_h v\right)_{\Oh}&\\
-  - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
-\end{align*}
-where 
-\begin{align*}
-\widehat{f}_n \coloneqq \beta_n u - \sigma_n \in H^{-1/2}(\Gh), \quad \widehat{u} \in H^{1/2}(\Gh)
-\end{align*}
-with the minimum energy extension norm on $\Gh$. We note that $H^{\pm 1/2}(\Gh)$ are \emph{closed} subspaces of $\prod_K H^{\pm 1/2}(\partial K)$. 
-}
-
-\frame{
-\frametitle{Inviscid equations}
-Issue: consider pure convection, $\div \beta u = f$. The ultra-weak variational formulation is
-\[
-\LRa{\widehat{f}_n,v}-\LRp{u,\beta\cdot \grad v} = \LRp{f,v},
-\]
-where $\widehat{f}_n \coloneqq \beta_n u$.
-When $\beta_n = 0$, $v$ has only a streamline derivative, and $\widehat{f}_n$ becomes an ill-defined trace in the cross-stream direction.
-For hyperbolic \emph{systems}, this issue manifests as \emph{sonic lines}.
-\begin{figure}
-\centering
-\includegraphics[scale=.25]{figs/sonicLines.pdf}
-\caption{Sonic lines ($u_n - c = 0$) appear for linearized Euler.}
-\end{figure}
-}
-
-\bibliographystyle{plain}
-{\scriptsize
-\bibliography{CFD_intro,DPG_old,paper,LitRev,NSNotes}
-}
-
-\end{document}

### 2012-09-10 docs/Nate/Proposal/CamelliaDetails.tex
Added proposal.

\section{Camellia: Design, Implementation, and Verification of a Toolbox for DPG}
\label{sec:CamelliaDetails}

In this appendix, we describe some details of \emph{Camellia}, a C++ toolbox for rapid development of DPG solvers, implemented atop Sandia's Trilinos library of packages \cite{Trilinos}.  The essential design goal for Camellia is to make DPG research and experimentation as simple as possible, without sacrificing too much by way of performance.  Our ideal is to write code that expresses the DPG formulation---the variational form and the inner product on the test space---in a way that makes the mathematics transparent, and requires minimal overhead beyond this to specify and solve problems.  We aim at excellent software design, following software engineering principles such as encapsulation and using tests and parameter checking to verify the code on an ongoing basis.

Key features of Camellia include:
\begin{itemize}
\item simple implementation of systems of arbitrary first-order PDEs,
\item simple implementation of arbitrary test space inner products,
\item distributed stiffness matrix determination,
\item distributed solve (using MUMPS),
\item automatic $h$- and $p$-adaptivity (no $hp$ yet; we need a way to choose between $h$ and $p$),
\item support for meshes made up of quads and triangles,
\item support for meshes of arbitrary irregularity, and
\item \NVRHgrad-, \NVRHdiv-, and \NVRHcurl-conforming basis functions.
\end{itemize}

The structure of this appendix is as follows.  In Section \ref{sec:overallDesign}, we describe the broad design of Camellia.  To motivate and make concrete some of what follows, we demonstrate the implementation of the velocity-gradient-pressure Stokes formulation in Section \ref{sec:stokesVGP}.  We detail the facilities for simple specification of DPG formulations in Section \ref{sec:selectedDesignDetails}; for a discussion of our \code{BasisCache} class and its facilities for making basis function computations more efficient, as well as a discussion of our treatment of hanging nodes in Camellia, see Section \ref{sec:proposedApproachCamellia}.  In Section \ref{sec:CamelliaVerification}, we describe our approach to verification of the code.  Section \ref{sec:distributingStiffness} discusses our implementation of a distributed stiffness matrix computation, and some performance testing that attended that project.  Finally, we briefly mention Jesse Chan's use of Camellia to solve compressible Navier-Stokes, with some pictorial documentation, in Section \ref{sec:compressibleNS}.

\subsection{Overall Design}\label{sec:overallDesign}
In this subsection, we describe the overall design of the code.  We begin with an edited directory listing of the Camellia source code, followed by a short description of each class.  We then summarize Camellia's reliance on Trilinos, listing the features we use and the Trilinos packages which provide them.  Finally, we note our use of reference-counted pointers and our naming convention for these.

\paragraph{Code Overview.}
The directory layout in our code repository is as follows:
\begin{center}
\begin{minipage}{0.4\textwidth}
{\bf
\begin{lstlisting}[backgroundcolor=\color{lightlightgreen}]
 ||-Drivers
 ||---DPGTests
 ||---MultiOrderStudy
 ||---Poisson
 ||---Stokes
 ||-src
 ||---Basis
 ||---ConvergenceStudy
 ||---DiscreteSpace
 ||---Formulation
 ||---Mesh
 ||---Solution
 ||---visualization
\end{lstlisting}
}
\end{minipage}
\end{center}

The core code is in the \verb=src= directory.  Within this, \verb=Basis= contains classes related to basis functions.  \verb=ConvergenceStudy= contains the \code{HConvergenceStudy} class, which provides support for studying convergence rates.  The \verb=DiscreteSpace= directory contains the \verb=DiscreteSpace= class and a Factory class for creating \verb=DiscreteSpace= objects, which allow trial and test spaces to be defined, and maintain the ordering of coefficients related to the bases of interest.  \verb=Formulation= contains classes supporting the succinct specification of variational formulations, inner products, and boundary conditions; these are discussed in detail in Section \ref{NVR:sec:formulationClasses}.  \verb=Mesh= contains classes related to meshing and elements, including those responsible for mesh partitioning across MPI nodes; for an extended discussion of our partitioning approach, see Section \ref{sec:distributingStiffness}.  \verb=Solution= contains classes for solving a variational formulation on a mesh.  Finally, the \verb=visualization= directory contains some MATLAB scripts for plotting solutions.  (Recently, we have added facilities which output solutions in VTK format.\footnote{Thanks to Truman Ellis for implementing this.})   Section \ref{sec:stokesVGP} walks through an extended example, specifying the velocity-gradient-pressure (VGP) Stokes formulation, creating an initial mesh, specifying a refinement strategy, and solving adaptively.

Several sample drivers can be found in the \verb=Drivers= directory; \verb=DPGTests= runs a test suite against the core code, \verb=StokesStudy=, \verb=StokesStudyHybridMesh= and \verb=PoissonStudy= are drivers built with the \verb=HConvergenceStudy= class, used to produce the results in Section \ref{NVR:sec:numericalResults}.

%\todo{Write about the overall structure of the code, including some collaboration diagrams.  Refer to the early group meeting presentation for some possibilities.}

\paragraph{Reliance on Trilinos.}
In the table below, we list several features Camellia uses, alongside the Trilinos package that provides each.\\
\begin{center}
\begin{tabular}{| l | c |}
\hline
{Feature}			&{Trilinos Package} \\
\hline
OO interface to MUMPS 		&Amesos \\
KLU solver 				&Amesos \\
conforming basis functions	&Intrepid \\
pullbacks/Piola transforms 	&Intrepid \\
smart multidimensional arrays 	&Intrepid \\
distributed compressed row storage matrices and vectors	&Epetra \\
cell topologies 				&Shards \\
reference-counted pointers 				&Teuchos \\
space-filling curves for spatially local mesh partitioning 		&Zoltan \\
\hline
\end{tabular}
\end{center}

\paragraph{Reference-counted pointers.} Throughout the code, and in this appendix, we make liberal use of reference-counted pointers (RCPs, instances of the \code{Teuchos::RCP} template class), which allow us to create objects without much concern about reclaiming the memory allocated for them: when the last reference to the object goes out of scope, the memory will automatically be reclaimed.  Because \code{Teuchos::RCP<\emph{ClassName}>} can be a lot to type, in the code and in this chapter, we adopt a convention that \code{\emph{ClassName}Ptr} will mean the same thing.

%This chapter is organized as follows.  In Section \ref{sec:StokesExample}, we walk through an implementation of our Stokes formulation; this amounts to a brief user's guide for the code.  In Section \ref{sec:DesignOverview}, we discuss the high-level design of Camellia.  In Section \ref{sec:DesignDetails}, we highlight selected details of the design.  Section \ref{sec:Meshing} describes our approach to meshing, solving, and adaptivity.  We describe Camellia's support for nonlinear problems in Section \ref{sec:NonlinearProblems}.  In Section \ref{sec:Deal.II}, we compare our approach to that taken by deal.II \cite{Deal.II}, a popular academic finite element code.  We conclude the chapter in Section \ref{sec:CamelliaConclusion}.

\subsection{Example: Solving the Stokes Problem using Camellia}\label{sec:stokesVGP}
Recall our VGP Stokes formulation:
\begin{align*}
\left({\sigma_{11} - p \choose \sigma_{12}}, \NVRgrad v_{1} \right)_{\Omega} - \left\langle \widehat{t}_{1n}, v_{1} \right\rangle_{\partial \Omega} &= (f_{1}, v_{1} )\\
\left({\sigma_{21} \choose \sigma_{22} - p}, \NVRgrad v_{2} \right)_{\Omega} - \left\langle \widehat{t}_{2n}, v_{2} \right\rangle_{\partial \Omega} &= (f_{2}, v_{2} )\\
\left({u_{1}  \choose u_{2}}, \NVRgrad q \right)_{\Omega} -   \left\langle {\widehat{u}_{1}  \choose \widehat{u}_{2}} \cdot \vect{n}, q \right\rangle_{\partial \Omega} &= 0\\
(u_{1}, \NVRdiv \vect{\tau}_{1})_{\Omega} + \left(\frac{1}{\mu}{\sigma_{11} \choose \sigma_{12}}, \vect{\tau}_{1}\right)_{\Omega} - \langle \widehat{u}_{1}, \vect{\tau}_{1} \cdot \vect{n} \rangle_{\partial \Omega} &= 0 \\
(u_{2}, \NVRdiv \vect{\tau}_{2})_{\Omega} + \left(\frac{1}{\mu}{\sigma_{21} \choose \sigma_{22}}, \vect{\tau}_{2}\right)_{\Omega} - \langle \widehat{u}_{2}, \vect{\tau}_{2} \cdot \vect{n} \rangle_{\partial \Omega} &= 0, \\
\end{align*}
where traction $\widehat{t}_{1n}$ is the flux identified with ${\sigma_{11} - p \choose \sigma_{12}} \cdot \vect{n}$, and $\widehat{t}_{2n}$ is identified with ${\sigma_{21}  \choose \sigma_{22} - p} \cdot \vect{n}$.

The steps to implementing a solver for such a formulation are as follows:
\begin{enumerate}
\item Identify the variables involved: fields, traces, fluxes, and test functions.
\item Implement functions (by extending the \code{Function} class) for any spatially varying material data in the formulation (in our Stokes case, there are none, save possibly for the forcing function $\vect{f}$).
\item Create an instance of \code{BF} (the bilinear form), and add bilinear terms for each of the equations.
\item Create an instance of \code{RHS}, and add linear terms for each of the equations with nonzero right-hand side.
\item Create an instance of \code{IP} (the inner product), and add terms representing the test-space inner product.
\item Create an instance of \code{BC}, and specify boundary conditions and zero-mean constraints.
\item Create an instance of \code{Mesh}, the initial mesh.
\item Create an instance of \code{Solution}, and solve.
\item Optionally, create an instance of \code{RefinementStrategy}, and use this to adaptively refine the mesh.
\end{enumerate}

We treat each of these in turn.
\paragraph{Identify variables involved.}
The Stokes formulation has scalar field variables $u_{1},u_{2},p,\sigma_{11},\sigma_{12},\sigma_{21},\sigma_{22}$, traces $\widehat{u}_{1},\widehat{u}_{2}$, and fluxes $\widehat{t}_{1n}, \widehat{t}_{2n}$.  The test functions are $v_{1},v_{2},q \in H^{1}$ and $\vect{\tau}_{1},\vect{\tau}_{2} \in \NVRHdiv$.  Thus, we create an instance of the \code{VarFactory} class, and ask it to create \code{VarPtr}s corresponding to each of these variables:

\begin{lstlisting}
  VarFactory varFactory; 
  // traces
  VarPtr u1hat = varFactory.traceVar("\\widehat{u}_1");
  VarPtr u2hat = varFactory.traceVar("\\widehat{u}_2");
  // fluxes
  VarPtr t1n = varFactory.fluxVar("\\widehat{t}_{1n}");
  VarPtr t2n = varFactory.fluxVar("\\widehat{t}_{2n}");
  // fields
  VarPtr u1 = varFactory.fieldVar("u_1");
  VarPtr u2 = varFactory.fieldVar("u_2");
  VarPtr sigma11 = varFactory.fieldVar("\\sigma_11");
  VarPtr sigma12 = varFactory.fieldVar("\\sigma_12");
  VarPtr sigma21 = varFactory.fieldVar("\\sigma_21");
  VarPtr sigma22 = varFactory.fieldVar("\\sigma_22");
  VarPtr p = varFactory.fieldVar("p");
  // test functions
  VarPtr tau1 = varFactory.testVar("\\tau_1", HDIV);  // tau_1
  VarPtr tau2 = varFactory.testVar("\\tau_2", HDIV);  // tau_2
  VarPtr v1 = varFactory.testVar("v_1", HGRAD); // v_1
  VarPtr v2 = varFactory.testVar("v_2", HGRAD); // v_2
  VarPtr q = varFactory.testVar("q", HGRAD); // q
\end{lstlisting}

The strings in each variable definition are human- and/or TeX-readable identifiers for each variable, which can be used in debugging output, or to generate, say, TeX tabulations of numerical results.  The \code{Var} class includes a unique ID for each variable, the function space for the variable, and allows various operators to be applied to the variable (first order differential operators and operators involving the unit normal along the element boundary).

\paragraph{Implement functions for spatially-varying data.}
The bilinear form for our Stokes formulation doesn't have any spatially-varying parameters, but the forcing function $\vect{f}$ might vary in space.  Suppose that $\vect{f}= {x \choose y}$.  We can implement functions like this one---functions that depend only on space, and not on mesh-dependent parameters like the element diameter---by extending \code{SimpleFunction}, and overriding its \code{values()} method.  In this case, we implement $\vect{f}$ as two scalar functions, $f_{1}$ and $f_{2}$.
\begin{lstlisting}
class F1 : public SimpleFunction {
public:
  double value(double x, double y) {
    return x;
  }
};
class F2 : public SimpleFunction {
public:
  double value(double x, double y) {
    return y;
  }
};
\end{lstlisting}

\paragraph{Add bilinear terms for each equation.}
When implementing a bilinear form involving vector quantities, the simplest thing is to break it into scalar components.  Thus we consider $(\sigma_{11} - p) \NVRpd{v_{1}}{x} + \sigma_{12} \NVRpd{v_{1}}{y}$ in place of ${\sigma_{11} - p \choose \sigma_{12}} \cdot \NVRgrad v_{1}$.

Notice that bilinear forms can generally be expressed as a sum of $L^{2}$ inner products of linear terms involving the trial space variables in the first argument and test space variables in the second argument.  Because we limit ourselves to first-order ultra-weak formulations, we know that all the derivatives will be first order (and, less importantly for the implementation, that they will all be on the test variables).  Thus Camellia uses a \code{LinearTerm} class as the building block for bilinear forms, test space inner products, and right-hand sides.  \code{LinearTerm}s can involve test or trial space variables with optional first-order differential operators applied, possibly multiplied by a functional weight, a \code{FunctionPtr}.  By means of operator overloading, Camellia makes it possible to express things quite succinctly, and in a way that makes the mathematics transparent.  For example, if we have a scalar weight \code{mu} $= \mu$ and we want a \code{LinearTermPtr} that represents $\mu \nabla v$, we can simply write \code{mu * v->grad()}.

Here, then, is the code for the Stokes bilinear form:
\begin{lstlisting}
  BFPtr stokesBF = Teuchos::rcp( new BF(varFactory) );
  double mu = 1.0;
  // v1 terms:
  stokesBF->addTerm(sigma11 - p, v1->dx()); // (sigma1 - (p,0), grad v1) 
  stokesBF->addTerm(sigma12, v1->dy());
  stokesBF->addTerm( sigma1n, v1);

  // v2:
  stokesBF->addTerm(sigma21, v2->dx());     // (sigma2 - (0,p), grad v2)
  stokesBF->addTerm(sigma22 - p, v2->dy());
  stokesBF->addTerm( sigma2n, v2);

  // q:
  stokesBF->addTerm(-u1, q->dx()); // (-u, grad q)
  stokesBF->addTerm(-u2, q->dy());
  stokesBF->addTerm(u1hat->times_normal_x() + u2hat->times_normal_y(), q);

  // tau1:
  stokesBF->addTerm(u1, tau1->div());
  stokesBF->addTerm(sigma11 / mu, tau1->x()); // (sigma1 / mu, tau1)
  stokesBF->addTerm(sigma12 / mu, tau1->y());
  stokesBF->addTerm(-u1hat, tau1->dot_normal());

  // tau2:
  stokesBF->addTerm(u2, tau2->div());
  stokesBF->addTerm(sigma21 / mu, tau2->x()); // (sigma2 / mu, tau2)
  stokesBF->addTerm(sigma22 / mu, tau2->y());
  stokesBF->addTerm(-u2hat, tau2->dot_normal());
\end{lstlisting} 
Thus, in 23 lines of code, we have implemented the entire bilinear form.  By way of contrast, an earlier version of Camellia---prior to the introduction of \code{LinearTerm}---required over 300 lines of code for the same purpose.

\paragraph{Add linear terms for each nonzero right-hand side.}
Our scalar equations have two nonzero right-hand sides, $(f_{1},v_{1})$ and $(f_{2},v_{2})$.  We need to define $f_{1}$ and $f_{2}$ as instances of \code{F1} and \code{F2}, and add $(f_{1},v_{1}) + (f_{2},v_{2})$ to a new instance of \code{RHS}.

\begin{lstlisting}
  FunctionPtr f1 = Teuchos::rcp( new F1 );
  FunctionPtr f2 = Teuchos::rcp( new F2 );
  RHSPtr rhs = Teuchos::rcp( new RHS );
  rhs->addTerm( f1 * v1 );
  rhs->addTerm( f2 * v2 );
\end{lstlisting}

\paragraph{Define the inner product.}
Camellia's \code{IP} class allows simple definition of inner products, typically used for specifying the test space inner product which is key to the DPG formulation.  Recall that the graph norm for the Stokes VGP formulation is:
\begin{align*}
\norm{(\NVRtensor{\tau},\vect{v}, q)}_{\rm graph}^{2} =& \norm{\NVRdiv \NVRtensor{\tau} - \NVRgrad q}^{2} + \norm{\NVRdiv \vect{v}}^{2} + \norm{ \NVRtensor{\tau} + \NVRgrad{\vect{v}}}^{2} + \norm{\NVRtensor{\tau}}^{2} + \norm{\vect{v}}^{2} + \norm{q}^{2}.
\end{align*}
The \code{IP} class squares each of the terms supplied to it; thus \code{ip->addTerm(q)} adds the term $\norm{q}^{2}$ to the inner product.  Our implementation is thus:

\begin{lstlisting}
  IPPtr ip = Teuchos::rcp(new IP());
  ip->addTerm( tau1->div() - q->dx() ); // u1
  ip->addTerm( tau2->div() - q->dy() ); // u2
  ip->addTerm( v1->dx() + v2->dy() );   // pressure
  ip->addTerm( v1->dx() + tau1->x() );  // sigma11
  ip->addTerm( v1->dy() + tau1->y() );  // sigma12
  ip->addTerm( v2->dx() + tau2->x() );  // sigma21
  ip->addTerm( v2->dy() + tau2->y() );  // sigma22
  ip->addTerm( v1 );
  ip->addTerm( v2 );
  ip->addTerm( q );
  ip->addTerm( tau1 );
  ip->addTerm( tau2 );
\end{lstlisting}

\paragraph{Specify boundary conditions and zero-mean constraints.}
Let us specify boundary conditions for the lid-driven cavity flow problem described in Section \ref{sec:lidDrivenCavityFlow}.  Recall that our implementation of the problem approximates the boundary conditions to make them continuous, introducing a ``ramp'' of width $\epsilon=\frac{1}{64}$.  We require:

\begin{itemize}
\item along the top boundary, $u_{1} = \left\{
\begin{array}{cl}
\frac{x}{\epsilon} 		& \quad x \leq \epsilon \\
1					& \quad \epsilon < x < 1 - \epsilon, \\
\frac{1 - x}{\epsilon}		& \quad 1 - \epsilon \leq x
\end{array}
\right.
$
\item along the left, right, and bottom walls of the cavity, $u_{1} = 0$, and
\item along the entire boundary, $u_{2} = 0$.
\end{itemize}
Furthermore, because the pressure $p$ only enters the formulation through a gradient, it will only be determined up to a constant.  To fix its value, we impose a zero-mean constraint, $\int_{\Omega} p = 0$.

To specify the velocity BCs, we begin by implementing functions defined on the boundary.  Camellia provides a \code{SimpleFunction} class, which is itself a subclass of \code{Function}: both classes define spatially varying functions; \code{SimpleFunction} presents a simpler interface that assumes the functions depend \emph{only} on spatial coordinates.  We define subclasses of \code{SimpleFunction} for the BCs on $u_{1}$ and $u_{2}$.

\begin{lstlisting}
class U1_0 : public SimpleFunction {
  double _eps;
public:
  U1_0(double eps) {
    _eps = eps;
  }
  double value(double x, double y) {
    double tol = 1e-14;
    if (abs(y-1.0) < tol) { // top boundary
      if ( (abs(x) < _eps) ) { // top left
        return x / _eps;
      } else if ( abs(1.0-x) < _eps) { // top right
        return (1.0-x) / _eps;
      } else { // top middle
        return 1;
      }
    } else { // not top boundary: 0.0
      return 0.0;
    }
  }
};

class U2_0 : public SimpleFunction {
public:
  double value(double x, double y) {
    return 0.0;
  }
};
\end{lstlisting}

Next, we need a mechanism to specify the portion of the boundary along which each BC is imposed---for example, some BCs might be imposed along an inflow boundary, while others are imposed only along the outflow boundary.  Camellia allows the boundary to be restricted by means of a \code{SpatialFilter} subclass.  In the case of lid-driven cavity flow, all our BCs are imposed along the entire boundary, so our \code{SpatialFilter} subclass simply matches the entire boundary.

\begin{lstlisting}
class UnitSquareBoundary : public SpatialFilter {
public:
  bool matchesPoint(double x, double y) {
    double tol = 1e-14;
    bool xMatch = (abs(x) < tol) || (abs(x-1.0) < tol);
    bool yMatch = (abs(y) < tol) || (abs(y-1.0) < tol);
    return xMatch || yMatch;
  }
};
\end{lstlisting}

Now, in the main body of the code, we need to create instances of our \code{Function} and \code{SpatialFilter} subclasses, as well as a new \code{BC} object.\footnote{The class we are here, for simplicity of exposition, calling \code{BC} is in fact implemented as \code{BCEasy}, because an earlier abstract superclass already has the name \code{BC}.  We expect to rename the classes to match the exposition at some point in the future; the present \code{BC} class might become \code{AbstractBC}, for example.}  We then add Dirichlet conditions for $\widehat{u}_{1}$ and $\widehat{u}_{2}$, as well as the zero-mean constraint on $p$.

\begin{lstlisting}
  double eps = 1.0 / 64.0;
  BCPtr bc = Teuchos::rcp( new BC );
  SpatialFilterPtr entireBoundary = Teuchos::rcp( new UnitSquareBoundary );
  FunctionPtr u1_0 = Teuchos::rcp( new U1_0(eps) );
  FunctionPtr u2_0 = Teuchos::rcp( new U2_0 );

  bc->addDirichlet(u1hat, entireBoundary, u1_0);
  bc->addDirichlet(u2hat, entireBoundary, u2_0);
  bc->addZeroMeanConstraint(p);
\end{lstlisting}

\paragraph{Create the initial mesh.}
Our philosophy in DPG is to start with a coarse mesh, and allow adaptivity to refine in regions of largest error.  Camellia provides a simple constructor for creating a uniform rectangular, axis-aligned mesh, such as the one we need for lid-driven cavity flow.  There is also a constructor which allows an arbitrary 2D mesh to be specified through element vertices.  (Truman Ellis has also recently added facilities for importing triangular meshes created by the Triangle mesh generator \cite{shewchuk96b}.)  For lid-driven cavity flow, we create a $2 \times 2$ initial quadrilateral mesh with quadratic field variables and quartic test functions using the simple constructor:

\begin{lstlisting}
  int H1Order = 3; // L^2 order plus 1
  int pToAdd = 1;  // enrichment for test function approximation

  // define the problem domain using Intrepid's FieldContainer
  FieldContainer<double> quadPoints(4,2);
  quadPoints(0,0) = 0.0; // x1
  quadPoints(0,1) = 0.0; // y1
  quadPoints(1,0) = 1.0;
  quadPoints(1,1) = 0.0;
  quadPoints(2,0) = 1.0;
  quadPoints(2,1) = 1.0;
  quadPoints(3,0) = 0.0;
  quadPoints(3,1) = 1.0;

  bool useTriangles = false; // don't split quads into triangles
  int horizontalCells = 2, verticalCells = 2;
  MeshPtr mesh = Mesh::buildQuadMesh(quadPoints, horizontalCells, verticalCells,
                                     stokesBF, H1Order, H1Order+pToAdd, useTriangles);
\end{lstlisting}
It is perhaps worth noting that the \code{Mesh} class defines the entire discretization: the geometry, element boundaries, \emph{and} the discrete trial and test spaces on each element.  This is the reason why the \code{stokesBF} argument is required here.  This is something we hope to change in a redesign, as there are many situations in which it is desirable to solve multiple problems on a single mesh, which the present design makes inconvenient.  In lid-driven cavity flow, for example, we solve for streamlines using the solution to the \code{stokesBF} variational form as data.

\paragraph{Solve.}
We now create a \code{Solution} object, which depends on the mesh \code{mesh} (and through it on the bilinear form \code{stokesBF}), the boundary conditions \code{bc}, the right-hand side \code{rhs}, and the test space inner product \code{ip}.  Once this is created, solving using MUMPS is then as simple as calling \code{solve()}:

\begin{lstlisting}
  SolutionPtr solution = Teuchos::rcp( new Solution(mesh, bc, rhs, ip) );
  solution->solve();
\end{lstlisting}

\paragraph{Adaptively refine the mesh.}
As previously discussed in Sections \ref{sec:proposedApproachDPG} and \ref{sec:lidDrivenCavityFlow}, our $h$-refinement strategy is very simple:
\begin{enumerate}
\item Loop through the elements, determining the maximum element error $\norm{e_{K{\rm max}}}_{V}$.
\item Refine all elements with error at least 20\% of the maximum $\norm{e_{K{\rm max}}}_{V}$.
\end{enumerate}
The \code{RefinementStrategy} class implements this strategy, taking the $20\%$ threshold as a construction parameter.  The code to execute seven refinement steps is then simply

\begin{lstlisting}
  double energyThreshold = 0.20; // for mesh refinements
  RefinementStrategyPtr refinementStrategy;
  refinementStrategy = Teuchos::rcp( new RefinementStrategy( solution, 
                                                             energyThreshold ));
  for (int i=0; i<7; i++) {
    refinementStrategy->refine();
    solution->solve();
  }
\end{lstlisting}

\subsection{Selected Design Details}\label{sec:selectedDesignDetails}
\subsubsection{Building Blocks for DPG Formulations: Var, LinearTerm, Function, IP, BF}
\label{NVR:sec:formulationClasses}
In Section \ref{sec:stokesVGP}, we demonstrated Camellia's facilities for rapidly specifying DPG formulations in the context of the VGP Stokes formulation.  Here, we describe in more detail the various components that allow this.

\paragraph{\code{Var}.}  The \code{Var} class identifies a trial or test space variable.  The \code{VarFactory} class manages creation of \code{Var}s, ensuring unique identifiers for each variable, which in turn are used in the ordering of corresponding degree of freedom coefficients in the \code{DiscreteSpace} class.  The \code{Var} class also keeps track of a linear operator applied to the variables---the default is a value operator; first-order differential operators, operators involving unit normals, and operators to select a component of a vector function are also available.  \code{Var}s also have \emph{types}: field, trace, flux, and test types are defined.  Each \code{Var} has a \emph{rank}---0 for scalar, 1 for vector, and so on.

\paragraph{\code{Function}.}  The \code{Function} class defines a function that may vary in space.  The \code{values()} method takes a \code{BasisCache} as an argument; the \code{BasisCache} in turn defines points of interest.  We adopt this approach for several reasons.  First, by operating on batches of points, computations may be more efficient than if we required a function call for each point.  Second, the \code{BasisCache} may contain other contextual information (for example, identifiers for the mesh elements being operated on) on which the \code{Function} instance depends---compared with adding arguments to the \code{values()} for such information, this allows a simple, unified interface for all \code{Function} instances.  Finally, as its name suggests, the \code{BasisCache} caches previously computed basis values, which allows some \code{Function} instances to compute their values more quickly---for instance, \code{PreviousSolutionFunction} uses computed solution coefficients to determine solution values, and this requires summing over various basis functions.  As with \code{Var}, \code{Function} has a rank.

There are many \code{Function} subclasses provided, and each of these can be used for visualization output; here, we name a few representative examples.  The \code{PreviousSolutionFunction} takes as its argument a \code{LinearTermPtr} (see below), so that solution variables may be combined in an arbitrary fashion and used elsewhere.  This is exactly the mechanism by which nonlinear problems are solved in Camellia.  The \code{hFunction} allows simple definition of functions that depend on the diameter of mesh cells.  \code{MeshPolyOrderFunction} has as its value the polynomial order trial space on each cell of the mesh; this is particularly useful for visualization of variable-order meshes.

\paragraph{\code{LinearTerm}.}  The \code{LinearTerm} class represents variational terms that are linear in either trial or test variables.  As such, \code{LinearTerm}s are defined as the product of a \code{Function} and a \code{Var}.  \code{LinearTerm}s have types and ranks determined by their component functions and variables.  Operator overloading allows simple syntax for some commonly used patterns---if \code{f1, f2} are \code{FunctionPtr}s and \code{v1, v2} are test variables, for example, each of the following expressions returns a corresponding \code{LinearTermPtr}:
\begin{itemize}
\item \code{f1 * v1},
\item \code{v1 / f1},
\item \code{f1 / f2 * v1},
\item \code{v1 + v2},
\item \code{ f1 * v1 + f2 * v2},
\item \code{3 * v1 + v2 / 5}, and
\item \code{ - v1}.
\end{itemize}
Moreover, application of differential operators to variables is just a matter of calling the appropriate method on the \code{VarPtr}s; e.g. \code{v1->grad()} means $\NVRgrad v_{1}$.

\paragraph{\code{IP}.}  The \code{IP} class represents an inner product; its primary purpose is to define the test space inner product.  Its \code{addTerm()} method takes a \code{LinearTermPtr} as argument.  The square of the norm generated by the inner product is the sum of the squares of its terms.  For example, the following code will specify an inner product that generates the norm $\left(\norm{v}^{2} + \norm{\NVRgrad v}^{2}\right)^{1/2}$.

\begin{lstlisting}
IPPtr ip =  = Teuchos::rcp(new IP());
ip->addTerm(v);
ip->addTerm(v->grad());
\end{lstlisting}

\paragraph{\code{BF}.} The \code{BF} class represents a bilinear form; its \code{addTerm()} method takes as arguments trial and test space \code{LinearTermPtr}s.  Each term is the $L^{2}$ inner product of its arguments, taken either on the interior of each element (for field variables) or along the element boundary (for fluxes and traces).

%\subsubsection{Meshing and Solving}\label{NVR:sec:meshAndSolve}
%Once we have a bilinear form specified with a test space inner product, we are ready to produce a mesh on which to solve the variational problem, and examine the error of that solution.  There are four classes provided to support this:
%\begin{itemize}
%\item \verb=Mesh=: defines elements, vertices, and test and trial bases. 
%\item \verb=ExactSolution=: defines the exact solution values at a point.
%\item \verb=Solution=: solves the linear system and stores solution coefficients.
%\item \verb=HConvergenceStudy=: solves the variational problem on a series of meshes, and computes convergence rates for trial space variables.
%\end{itemize}
%In this section, we discuss each of these in turn.
%
%\paragraph{The Mesh Class}\label{NVR:sec:mesh}
%The \verb=Mesh= class represents a bilinear form together with a set of quadrilaterals and triangles on which polynomial bases are defined for each test and trial variable.  The basic \verb=Mesh= constructor takes arguments
%\begin{itemize}
%\item \verb=vector<FieldContainer<double> > &vertices=,
%\item \verb=vector< vector<int> > &elementVertices=,
%\item \verb=Teuchos::RCP< BilinearForm > bilinearForm=,
%\item \verb=int pTrial=, and
%\item \verb=int pToAddTest=.
%\end{itemize}
%
%The \verb=vertices= vector has FieldContainer entries with dimensions \verb=(spaceDim)=, the spatial dimension of the problem, each of which specifies the physical locations of an element vertex.  Each physical vertex should be listed exactly once.  (We do assume \verb=(spaceDim)= = 2 in a few places in the code, so that is a limitation for the moment.)
%
%The \verb=elementVertices= vector contains a vector of 3 or 4 vertex indices for each element---these are the indices of the element's vertices in the \verb=vertices=  vector, and they should be specified in counterclockwise order (clockwise will work as well, but all elements must be specified in the same order, clockwise or counterclockwise).  The \verb=Mesh= class will automatically determine which element edges lie along the boundary, as well as which edges are shared between elements.
%
%The \verb=bilinearForm= argument is a reference-counted pointer to the bilinear form for the variational problem to be solved.  
%
%\verb=pTrial= is the polynomial order of approximation to be used for trial space variables belonging to $H^{1}$ (that is, in function space \verb=FUNCTION_SPACE_HGRAD= --- typically, these are just the traces), and \verb=pToAddToTest= is the polynomial order to add to this to obtain the order for the test space.  Trial space variables in $L^{2}$ (function space \verb=FUNCTION_SPACE_HVOL=, typically field variables and fluxes), then these will have order \verb=pTrial-1=.
%
%In addition to the basic mesh constructor, there are two static constructors to build meshes within an axis-aligned rectangle.  These are \verb=buildQuadMesh= and \verb=buildQuadMeshHybrid=, with the following signatures:
%\begin{lstlisting}
%Teuchos::RCP<Mesh> buildQuadMesh(
%          const FieldContainer<double> &quadBoundaryPoints,
%          int horizontalElements, int verticalElements,
%          Teuchos::RCP< BilinearForm > bilinearForm, 
%          int pTrial, int pTest, bool triangulate=false);
%Teuchos::RCP<Mesh> buildQuadMeshHybrid(
%          const FieldContainer<double> &quadBoundaryPoints, 
%          int horizontalElements, int verticalElements,
%          Teuchos::RCP< BilinearForm > bilinearForm, 
%          int pTrial, int pTest);
%\end{lstlisting}
%
%Both methods will construct a regularly spaced grid of $horizontalElements \times verticalElements$ rectangular elements, with \verb=pToAddTest= = \verb=pTest - pTrial=.  \verb=quadBoundaryPoints= is a FieldContainer with dimensions (4,2) containing four axis-aligned vertices.  (We do hope to relax the axis-alignment constraint in the near future.)  In the first method, if \verb=triangulate= is true, these rectangles are cut along a diagonal to form triangular elements.  In the second method, half of the elements are split; the mesh is thus a ``hybrid'' of triangles and quads.
%
%\paragraph{The Solution Class}\label{NVR:sec:Solution} A \verb=Solution= object can be constructed and solved as follows:
%\begin{lstlisting}
%Solution solution(mesh, bc, rhs, innerProduct);
%solution.solve();
%\end{lstlisting}
%
%At present, the \verb=solve()= method solves using the KLU implementation provided by Trilinos.  The \verb=Solution= class also provides support for computing solution values at points (through the \verb=solutionValues()= methods), as well as outputting a data file representing the mesh solution for a given trial space variable (the \verb=writeToFile()= method).
%
%\paragraph{The HConvergenceStudy Class}\label{NVR:sec:HConvergenceStudy}  The \verb=HConvergenceStudy= class provides a simple mechanism for studying convergence rates on the meshes supported by the constructors \verb=buildQuadMesh()= and \verb=buildQuadMeshHybrid()=.  Its constructor interface is as follows:
%\begin{lstlisting}
%HConvergenceStudy(Teuchos::RCP<ExactSolution> exactSolution,
%                  Teuchos::RCP<BilinearForm> bilinearForm,
%                  Teuchos::RCP<RHS> rhs,
%                  Teuchos::RCP<BC> bc,
%                  Teuchos::RCP<DPGInnerProduct> ip, 
%                  int minLogElements, int maxLogElements, 
%                  int H1Order, int pToAdd, 
%                  bool randomRefinements,
%                  bool useTriangles, bool useHybrid)
%\end{lstlisting}
%
%The logarithms in \verb=minLogElements= and \verb=maxLogElements= are base 2, and the number of elements is measured in one axis direction only --- for example, specifying 0 and 5 will compute solutions for meshes varying in size from $1 \times 1$ to $32 \times 32$.  \verb=H1Order= is the polynomial order for $H^{1}$ space, which is one higher than that used for $L^{2}$.  The \verb=randomRefinements= flag will vary the \verb=H1Order= throughout the mesh; these are not actually randomly chosen --- the flag is meant for exercising $p$-refinements.  The other arguments are self-explanatory.
%
%Calling \verb=solve(quadBoundaryPoints)=, where the \verb=quadBoundaryPoints= argument is such as was used in \verb=buildQuadMesh()=, will compute solutions on a series of meshes.  Calling \verb=writeToFiles(filePathPrefix, trialID)= will print error values and convergence rates for \verb=trialID= to console, and write both the error values and the visualization data for the solution to a set of files starting with \verb=filePathPrefix=.  Example drivers for \verb=HConvergenceStudy= can be found in \verb=PoissonStudy= and \verb=StokesStudy=.
%
%\paragraph{Visualization}\label{NVR:sec:visualization}
%For visualization in MATLAB, first call the \verb=Solution= object's \verb=writeToFile()= method, passing in the trial variable identifier and the file path as arguments.  Our toolbox provides a MATLAB script, \verb=plotSolution.m=, for displaying the solution.  Calling this is as simple as ensuring that the MATLAB script is in your MATLAB path, and then calling \verb=plotSolution(filePath)= from MATLAB.  The visualization is approximate: at present, we only write out solution values at vertices, and MATLAB is responsible for interpolating between these.  We do hope to provide higher-fidelity visualization soon.

\subsection{Verification of the Code}\label{sec:CamelliaVerification}
We adopt a multi-pronged approach to verification of the code.  The first line of defense is runtime parameter checking, some of which is provided by Trilinos (e.g. the \code{FieldContainer} multi-dimensional array class checks the rank and bounds of its arguments), and some by Camellia itself (e.g. summing \code{LinearTermPtr}s of unlike type---e.g. test and field variables---causes an exception to be thrown).  We have a growing suite of unit tests which we periodically run during code development.  We have run a variety of tests, documented below, to confirm expected convergence rates.  Finally, we use the code in a variety of research applications---we have used it to solve Poisson, convection-dominated diffusion, Stokes, Burgers, and compressible Navier-Stokes equations; the success of each of these applications acts as one more check of the code's correctness.

\subsubsection{DPG Formulations Used in Code Verification}\label{NVR:sec:stokesForm}
Here, we state a formulation of the Poisson problem, and develop two additional DPG formulations for the Stokes problem, which we use below as part of our verification of the code.

\paragraph{Poisson Formulation.}  The formulation of the Poisson problem used in our verification tests is as follows:
\begin{align*}
b(\cdot,\cdot) = &- \int_K \phi \nabla \cdot \bf{q} - \int_K \psi \cdot \bf{q} + \int_{\partial K} \widehat{\phi} \: \bf{q} \cdot \bf{n}\\
&- \int_K \psi \cdot \nabla v + \int_{\partial K} \widehat{\psi}_n \: v \,.
\end{align*}

\paragraph{Stokes VSP Formulation.}
We begin with the formulation we used in our original work with the Stokes problem, a velocity-stress-pressure (VSP) formulation.  Our original motivation for selecting this one over the velocity-vorticity-pressure (VVP) formulation which we discuss below had to do with details of implementation.  The VVP formulation requires considerably fewer solution variables, so now that it is implemented, we prefer it.

The strong form of the Stokes problem with which we begin is as follows:

\begin{align}
- 2 \mu \NVRdiv \NVRtensor{\epsilon} + \NVRgrad p &= \vect{f} & \text{ in } \Omega, \label{NVR:eq:strongfirst} \\
\NVRdiv \vect{u} &= 0 & \text{ in } \Omega, \\
\vect{u} &= \vect{g_{D}} & \text{ on } \partial\Omega,\label{NVR:eq:stronglast}
\end{align}
where $\Omega \subset \mathbb{R}^{2}$, $\mu$ is viscosity, $\NVRtensor{\epsilon}=\NVRgrad^{\text{sym}} \vect{u}$ is strain, $p$ is pressure, $u$ velocity, and $\vect{f}$ a vector forcing function.

We introduce stress $\sigma$ and vorticity $\omega$ by
\begin{align*}
\NVRtensor{\sigma} &= 2 \mu \NVRtensor{\epsilon} - p\NVRtensor{I}\\
\NVRtensor{\omega} &= \frac{1}{2}(\NVRgrad \vect{u} - \NVRgrad \vect{u}^{T})
\end{align*}
so that equation \eqref{NVR:eq:strongfirst} becomes simply $-\NVRdiv \NVRtensor{\sigma} = \vect{f}$.
We also have
\begin{align*}
\NVRtensor{\epsilon} &= \frac{1}{2 \mu}(\NVRtensor{\sigma} + p\NVRtensor{I}).
\end{align*}
Since $\NVRtensor{\epsilon} = \NVRgrad^{\text{sym}} \vect{u} = \NVRgrad \vect{u} - \NVRtensor{\omega}$, the entire system is

\begin{align*}
\frac{1}{2 \mu}(\NVRtensor{\sigma} + p\NVRtensor{I}) - \NVRgrad \vect{u} + \NVRtensor{\omega} &= \NVRtensor{0}  & \text{ in } \Omega, \\
- \NVRdiv \NVRtensor{\sigma} &= \vect{f} & \text{ in } \Omega, \\
\NVRdiv \vect{u} &= 0 & \text{ in } \Omega, \\
\vect{u} &= \vect{g_{D}} & \text{ on } \partial\Omega.
\end{align*}
Note that the antisymmetric part of the first equation recovers the definition of $\NVRtensor{\omega}$, so that it need not enter the system separately.
Define scalar $\omega = \omega_{21} = \frac{1}{2}(u_{1,2} - u_{2,1})$.  Our strong formulation is

\begin{align*}
\frac{1}{2 \mu}{\sigma_{11} + p \choose \sigma_{21}} - \NVRgrad u_{1} + {0 \choose \omega} &= \vect{0} & \text{ in } \Omega, \\
\frac{1}{2 \mu}{\sigma_{12} \choose \sigma_{22} + p} - \NVRgrad u_{2} - {\omega \choose 0} &= \vect{0}  & \text{ in } \Omega, \\
-\NVRdiv {\sigma_{11} \choose \sigma_{21}} &= f_{1} & \text{ in } \Omega, \\
-\NVRdiv {\sigma_{12} \choose \sigma_{22}} &= f_{2} & \text{ in } \Omega, \\
\NVRdiv \vect{u} &= 0 & \text{ in } \Omega, \\\
\vect{u} &= \vect{g_{D}} & \text{ on } \partial\Omega.
\end{align*}
Multiplying the first two equations by vector test functions $\vect{q}_{i}$ and the following three by scalar test functions $v_{i}$, and integrating by parts over an element $K$, we obtain

\begin{align*}
\int_{K} \left(\frac{1}{2 \mu}{\sigma_{11} + p \choose \sigma_{21}} + {0 \choose \omega} \right) \cdot \vect{q}_{1} &+ \int_{K} u_{1} \NVRdiv \vect{q_{1}} &-& \int_{\partial K} \widehat{u}_{1} \vect{q_{1}} \cdot n &&=\vect{0} \\
\int_{K} \left(\frac{1}{2 \mu}{\sigma_{12} \choose \sigma_{22} + p} - {\omega \choose 0}\right) \cdot \vect{q}_{2} &+ \int_{K} u_{2} \NVRdiv \vect{q_{2}} &-& \int_{\partial K} \widehat{u}_{2} \vect{q_{2}} \cdot n &&= \vect{0}\\
\int_{K}  {\sigma_{11} \choose \sigma_{21}} \cdot \NVRgrad v_{1} &&-& \int_{\partial K} \widehat{\vect{\sigma}}_{1n} v_{1} &&= \int_{K} f_{1} v_{1} \\
\int_{K} {\sigma_{12} \choose \sigma_{22}} \cdot \NVRgrad v_{2} &&-& \int_{\partial K} \widehat{\vect{\sigma}}_{2n} v_{2}  &&= \int_{K} f_{2} v_{2} \\
-\int_{K} \vect{u} \cdot \NVRgrad v_{3} &&+& \int_{\partial K} \widehat{\vect{u}} v_{3} \cdot n &&= 0,
\end{align*}
where the hatted variables ($\widehat{u}_{1}$, e.g.) are fluxes and traces introduced by relaxing the continuity requirement at element boundaries.  These differ from the \emph{numerical fluxes} that appear in other DG methods, in that they are not constructed a priori, but simply enter the variational problem as additional unknowns. We solve for them at the same time as we solve 
the rest of the unknowns.  As in other DG methods, the fluxes will approach the corresponding unhatted solution variables (which we call \emph{field} variables) as the latter approach the exact solution.

\paragraph{Stokes Formulation II: Velocity-Vorticity-Pressure Formulation}  The standard velocity-vorticity-pressure (VVP) Stokes formulation is:
\begin{align*}
\NVRcurl \omega + \NVRgrad p &= \vect{f}\\
\omega - \NVRcurl \vect{u} &= 0\\
\NVRdiv \vect{u} &= 0.
\end{align*}
(Note that the value of $\omega$ here differs by a factor of $-\frac{1}{2}$ from the $\omega$ as defined in the previous formulation.)  Multiplying by test functions, integrating by parts, and substituting fluxes and traces for boundary values, we obtain:

\begin{align*}
\int_{\partial K} \widehat{\omega} \vect{q} \cdot {n_{2} \choose -n_{1}} + \int_{\partial K} \widehat{p} q_{n} -  \int_{K}\omega \NVRcurl \vect{q} -  \int_{K} p \NVRdiv \vect{q} &= \int_{K} \vect{f} \cdot \vect{q}\\
\int_{\partial K} \widehat{u}_{\times \vect{n}}v_{1} -  \int_{K}\vect{u} \cdot (\NVRcurl v_{1}) +  \int_{K} \omega v_{1} &= 0\\
\int_{\partial K} \widehat{u}_{\vect{n}} v_{2} -  \int_{K}\vect{u} \cdot (\NVRgrad v_{2}) &= 0 \,.
\end{align*}
Whereas the original Stokes formulation required 7 field variables, 3 traces, and 2 fluxes, the VVP formulation requires just 4 field, 2 trace, and two flux variables.

\subsubsection{Verification Experiments}\label{NVR:sec:numericalResults}
For each of our three formulations --- Poisson, VSP Stokes, and VVP Stokes --- we have run a set of numerical experiments:
\begin{itemize}
\item For $L^{2}$ polynomial orders 1, 2, and 3, run convergence studies on meshes varying from $1 \times 1$ to $32 \times 32$.
\item For a $16 \times 16$ mesh, vary the polynomial orders of the elements across the mesh.
\item For $L^{2}$ polynomial orders 1, 2, and 3, run convergence studies on ``hybrid'' meshes (quads and triangles together) varying in size from $1 \times 1$ to $32 \times 32$.
\end{itemize}

The first two experiments we ran with triangles and quads.  For all of the experiments, we specified the domain $(-1,1) \times (-1,1)$, imposed a zero-mean constraint, and used the naive test space norm.  As will be clear from the discussion in Appendices \ref{sec:StokesAnalysis} and \ref{sec:StokesNumericalResults}, the naive norm is not likely the ideal norm for our Stokes formulations, as it leads to suboptimal convergence in the pressure; we performed these tests prior to performing that analysis, and in the future we hope to repeat these tests with the graph norms corresponding to the VSP and VVP formulations.  We used the Poisson manufactured solution
\begin{align*}
\phi = e^{x \sin y} - \frac{1}{4} \int_{-1}^{1} \int_{-1}^{1} e^{x \sin y} dx dy,
\end{align*}
where the subtracted integral is chosen to ensure that $\phi$ does indeed have a zero mean.  Following our previous work, the Stokes experiments used a manufactured solution
\begin{align*}
u_{1} &=  -e^{x} ( y \cos y + \sin y )\\
u_{2} &=  e^{x}  y \sin y\\
p &= 2 \mu e^{x} \sin y.
\end{align*}

\paragraph{Convergence Studies on Uniform Meshes}
For polynomial order $k$, we expect a convergence rate of $k+1$.  This is indeed what we see in our experiments.  The Poisson convergence studies with triangular elements can be found in Table \ref{NVR:table:poissonTriRates}; with quads, in Table \ref{NVR:table:poissonQuadRates}.  The Stokes VSP studies with triangles can be found in Table \ref{NVR:table:VSPTriRates}; with quads, in Table \ref{NVR:table:VSPQuadRates}.  The VVP studies with triangles are shown in Table \ref{NVR:table:VVPTriRates}; with quads, in Table \ref{NVR:table:VVPQuadRates}.  It is worth noting that the convergence rates we see with the naive test space norm for the VSP and VVP are better than the rates we saw when using the naive norm with the VGP formulation (see Appendix \ref{sec:StokesNumericalResults}); however, the $L^{2}$ errors in pressure remain significantly larger than the best approximation error.

\paragraph{Meshes of Multiple Polynomial Orders}\label{NVR:sec:mixedMeshes}
To confirm that our code works well with meshes that include elements of varying degree, we took a $16 \times 16$ mesh with $L^{2}$ polynomial degree assigned according to the following pattern, repeated 4 times:
\\
\begin{center}
\begin{tabular}{| c | c | c | c || c | c | c | c || c | c | c | c || c | c | c | c |}
\hline
4 &4 &4 &4  &1 &1 &1 &1  &2 &2 &2 &2  &3 &3 &3 &3 \\
\hline
3 &3 &3 &3  &4 &4 &4 &4  &1 &1 &1 &1  &2 &2 &2 &2 \\
\hline
2 &2 &2 &2  &3 &3 &3 &3  &4 &4 &4 &4  &1 &1 &1 &1 \\
\hline
1 &1 &1 &1  &2 &2 &2 &2  &3 &3 &3 &3  &4 &4 &4 &4 \\
\hline
\end{tabular}
\end{center}
\vspace{0.1in}
We hope to see errors as good as, or better than, our first-order $16 \times 16$ mesh for the same problem, although we can perhaps explain a small amount of increased error as due to worse conditioning of the matrices for higher-order polynomials.

The results for Poisson are:
\\
\begin{center}
\begin{tabular}{| c | c | c | c | c | c |}
\hline
\multicolumn{6}{| c |}{Triangles} \\
\hline
\multicolumn{2}{| c |}{$\phi$} & \multicolumn{2}{| c |}{$\psi_{1}$} & \multicolumn{2}{| c |}{$\psi_{2}$} \\
\hline
$k=1$ & mixed $k$ & $k=1$ & mixed $k$ & $k=1$ & mixed $k$ \\
\hline
2.0e-3 & 9.1e-4 & 3.4e-3 & 1.7e-3 & 2.4e-3 & 1.1e-3\\
\hline
\hline
\multicolumn{6}{| c |}{Quads} \\
\hline
\multicolumn{2}{| c |}{$\phi$} & \multicolumn{2}{| c |}{$\psi_{1}$} & \multicolumn{2}{| c |}{$\psi_{2}$} \\
\hline
$k=1$ & mixed $k$ & $k=1$ & mixed $k$ & $k=1$ & mixed $k$ \\
\hline
1.0e-3 & 3.7e-4 & 2.3e-3 & 6.6e-4 & 2.9e-3 &1.2e-3\\
\hline
\end{tabular}
\end{center}
\vspace{0.1in}
For Poisson, the multi-order mesh has lower error than the first-order mesh in every variable, just as we would like.

The results for Stokes VSP are:
\\
\begin{center}
\begin{tabular}{| c | c | c | c | c | c |}
\hline
\multicolumn{6}{| c |}{Triangles} \\
\hline
\multicolumn{2}{| c |}{$p$} & \multicolumn{2}{| c |}{$u_{1}$} & \multicolumn{2}{| c |}{$u_{2}$} \\
\hline
$k=1$ & mixed $k$ & $k=1$ & mixed $k$ & $k=1$ & mixed $k$ \\
\hline
1.6e-2 & 1.4e-2 & 5.1e-3 & 2.4e-3 & 4.4e-3 & 2.1e-3\\
\hline
\hline
\multicolumn{6}{| c |}{Quads} \\
\hline
\multicolumn{2}{| c |}{$p$} & \multicolumn{2}{| c |}{$u_{1}$} & \multicolumn{2}{| c |}{$u_{2}$} \\
\hline
$k=1$ & mixed $k$ & $k=1$ & mixed $k$ & $k=1$ & mixed $k$ \\
\hline
5.3e-3 & 1.0e-2 & 4.9e-3 & 1.6e-3 & 2.5e-3 & 1.3e-3\\
\hline
\end{tabular}
\end{center}
\vspace{0.1in}
For Stokes VSP, the multi-order mesh has lower error than the first-order mesh in every variable, except for pressure in the quad mesh, where the first-order mesh does better by about a factor of 2.

The results for Stokes VVP are:
\\
\begin{center}
\begin{tabular}{| c | c | c | c | c | c |}
\hline
\multicolumn{6}{| c |}{Triangles} \\
\hline
\multicolumn{2}{| c |}{$p$} & \multicolumn{2}{| c |}{$u_{1}$} & \multicolumn{2}{| c |}{$u_{2}$} \\
\hline
$k=1$ & mixed $k$ & $k=1$ & mixed $k$ & $k=1$ & mixed $k$ \\
\hline
6.9e-2 & 5.8e-2 & 6.9e-3 & 3.1e-3 & 6.8e-3 & 2.7e-3\\
\hline
\hline
\multicolumn{6}{| c |}{Quads} \\
\hline
\multicolumn{2}{| c |}{$p$} & \multicolumn{2}{| c |}{$u_{1}$} & \multicolumn{2}{| c |}{$u_{2}$} \\
\hline
$k=1$ & mixed $k$ & $k=1$ & mixed $k$ & $k=1$ & mixed $k$ \\
\hline
8.0e-3 & 2.1e-2 & 3.9e-3 & 1.7e-3 & 3.8e-3 & 1.4e-3\\
\hline
\end{tabular}
\end{center}
\vspace{0.1in}
Again, the behavior is just as we would like, except in the case of pressure for quads, where the error in the first-order mesh is better than that for the multi-order, this time by a factor of about 2.5.  We believe that this is due to round-off error, but we do not at present have a precise explanation.

\paragraph{``Hybrid'' Mesh Convergence Studies}

We studied the convergence of the Poisson solution for ``hybrid'' meshes, containing half triangles and half quads, ranging from $1 \times 1$ to $32 \times 32$, with $L^{2}$ polynomial orders $k=1,2,3$.  The results can be seen in Table \ref{NVR:table:PoissonHybridRates}; again, the convergence rates for all variables are optimal. Plots of $\phi$, $\psi_{1}$ and $\psi_{2}$ for the $16 \times 16$ mesh can be found in Figure \ref{NVR:fig:Poisson}.

We studied the same for the VSP and VVP Stokes formulations.  VSP results can be found in Table \ref{NVR:table:VSPHybridRates}; VVP, Table \ref{NVR:table:VVPHybridRates} --- the rates are optimal for $u_{1}$ and $u_{2}$ across the board, but for reasons unknown the $k=1$ VVP pressure is somewhat sub-optimal, while for $k=2$ and 3, the rate is somewhat super-optimal.  Something similar happens in the VSP pressure, although there the effect is considerably less pronounced.  Plots of $P$, $u_{1}$ and $u_{2}$ for the $16 \times 16$ mesh can be found in Figure \ref{NVR:fig:Stokes}.  These were generated using the VVP formulation; the VSP plots are visually identical.

\clearpage
\subsubsection{Results of Convergence Studies on Uniform Meshes}

\vspace{1.59in}

\begin{table}[h!b!p!]
\begin{center}
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
\multicolumn{7}{| c |}{k=1} \\
\hline
Mesh Size & $\phi$ & rate & $\psi_{1}$ & rate &  $\psi_{2}$ & rate \\
\hline
1 $\times$ 1		&4.2e-1	&-	&5.2e-1	&-		&3.4e-1	&-	\\
2 $\times$ 2         	&1.3e-1	&1.71	&2.0e-1	&1.38		&1.5e-1     	&1.24	\\
4 $\times$ 4	        	&3.2e-2	&2.00	&5.2e-2	&1.93		&3.9e-2     	&1.92	\\
8 $\times$ 8         	&8.0e-3	&2.01	&1.3e-2	&1.96		&9.6e-3     	&2.00	\\
16 $\times$ 16         	&2.0e-3	&2.00	&3.4e-3	&1.99		&2.4e-3     	&2.01	\\
32 $\times$ 32         	&5.0e-4	&2.00	&8.4e-4	&1.99		&6.0e-4      	&2.00	\\
\hline
\multicolumn{7}{| c |}{k=2} \\
\hline
Mesh Size & $\phi$ & rate & $\psi_{1}$ & rate &  $\psi_{2}$ & rate \\
\hline
1 $\times$ 1		&7.9e-2	&-	&2.5e-1	&-	&1.4e-1	&-	\\
2 $\times$ 2         	&1.2e-2	&2.77	&3.1e-2	&2.97	&3.6e-2     	&1.96	\\
4 $\times$ 4       	&1.4e-3	&3.00	&4.1e-3	&2.95	&4.9e-3     	&2.86	\\
8 $\times$ 8         	&1.8e-4	&2.99	&5.1e-4	&2.98	&6.0e-4     	&3.02	\\
16 $\times$ 16         	&2.3e-5	&3.00	&6.5e-5	&2.99	&7.5e-5     	&3.01	\\
32 $\times$ 32         	&2.8e-6	&3.00	&8.1e-6	&3.00	&9.3e-6      	&3.01	\\
\hline
\multicolumn{7}{| c |}{k=3} \\
\hline
Mesh Size & $\phi$ & rate & $\psi_{1}$ & rate &  $\psi_{2}$ & rate \\
\hline
1 $\times$ 1		&2.5e-2	&-	&2.9e-2	&-	&4.3e-2	&-	\\
2 $\times$ 2         	&1.5e-3	&3.99	&3.4e-3	&3.09	&5.2e-3     	&3.06	\\
4 $\times$ 4        	&1.1e-4	&3.82	&2.3e-4	&3.92	&3.4e-4     	&3.95	\\
8 $\times$ 8         	&7.1e-6	&3.94	&1.5e-5	&3.99	&2.1e-5     	&3.98	\\
16 $\times$ 16         	&4.5e-7	&3.99	&9.2e-7	&3.99	&1.3e-6     	&4.00	\\
32 $\times$ 32         	&2.8e-8	&4.00	&5.8e-8	&4.00	&8.4e-8      	&4.00	\\
\hline
\end{tabular}
\end{center} 
\caption{Poisson: Triangles, $L^{2}$ Error and $h$-Convergence Rates.  We observe optimal convergence.}
\label{NVR:table:poissonTriRates}
\end{table}

\begin{table}[h!b!p!]
\begin{center}
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
\multicolumn{7}{| c |}{k=1} \\
\hline
Mesh Size & $\phi$ & rate & $\psi_{1}$ & rate &  $\psi_{2}$ & rate \\
\hline
1 $\times$ 1		&1.4e-1	&-	&5.4e-1	&-	&3.8e-1	&-	\\
2 $\times$ 2         	&5.2e-2	&1.41	&1.3e-1	&2.00	&1.4e-1     	&1.41	\\
4 $\times$ 4        	&1.5e-2	&1.77	&3.5e-2	&1.92	&4.3e-2     	&1.70	\\
8 $\times$ 8         	&4.1e-3	&1.93	&9.1e-3	&1.97	&1.2e-2     	&1.91	\\
16 $\times$ 16         	&1.0e-3	&1.98	&2.3e-3	&2.00	&2.9e-3     	&1.98	\\
32 $\times$ 32         	&2.6e-4	&2.00	&5.7e-4	&2.00	&7.3e-4      	&2.00	\\
\hline
\multicolumn{7}{| c |}{k=2} \\
\hline
Mesh Size & $\phi$ & rate & $\psi_{1}$ & rate &  $\psi_{2}$ & rate \\
\hline
1 $\times$ 1		&4.9e-2	&-	&8.5e-2	&-	&1.1e-1	&-	\\
2 $\times$ 2         	&6.6e-3	&2.91	&1.7e-2	&2.34	&1.6e-2     	&2.78	\\
4 $\times$ 4        	&7.8e-4	&3.08	&2.2e-3	&2.90	&1.8e-3     	&3.12	\\
8 $\times$ 8         	&9.3e-5	&3.05	&2.6e-4	&3.11	&2.0e-4     	&3.20	\\
16 $\times$ 16         	&1.2e-5	&3.01	&3.1e-5	&3.06	&2.3e-5     	&3.11	\\
32 $\times$ 32         	&1.4e-6	&3.00	&3.8e-6	&3.03	&2.8e-6      	&3.05	\\
\hline
\multicolumn{7}{| c |}{k=3} \\
\hline
Mesh Size & $\phi$ & rate & $\psi_{1}$ & rate &  $\psi_{2}$ & rate \\
\hline
1 $\times$ 1		&1.2e-2	&-	&3.0e-2	&-	&2.6e-2	&-	\\
2 $\times$ 2         	&6.6e-4	&4.16	&2.6e-3	&3.54	&2.0e-3     	&3.66	\\
4 $\times$ 4        	&3.3e-5	&4.33	&1.2e-4	&4.39	&1.1e-4     	&4.18	\\
8 $\times$ 8         	&2.1e-6	&3.99	&7.3e-6	&4.09	&6.6e-6     	&4.10	\\
16 $\times$ 16         	&1.3e-7	&3.99	&4.4e-7	&4.04	&3.9e-7     	&4.07	\\
32 $\times$ 32         	&8.1e-9	&4.00	&2.7e-8	&4.02	&2.4e-8      	&4.04	\\
\hline
\end{tabular}
\end{center} 
\caption{Poisson: Quads, $L^{2}$ Error and $h$-Convergence Rates.  We observe optimal convergence.}
\label{NVR:table:poissonQuadRates}
\end{table}

\begin{table}[h!b!p!]
\begin{center}
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
\multicolumn{7}{| c |}{k=1} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&3.2e-0	&-	&9.4e-1	&-	&1.6e-0	&-	\\
2 $\times$ 2         	&1.1e-0	& 1.53	&3.1e-1	&1.62	&2.8e-1     	&2.05	\\
4 $\times$ 4        	&3.0e-1	& 1.89	&8.0e-2	&1.94	&7.0e-2     	&1.99	\\
8 $\times$ 8         	&6.9e-2	& 2.11	&2.0e-2	&1.99	&1.8e-2     	&2.00	\\
16 $\times$ 16         	&1.6e-2	& 2.12	&5.1e-3	&2.00	&4.4e-3     	&2.00	\\
32 $\times$ 32         	&3.8e-3	& 2.08	&1.3e-3	&2.00	&1.1e-3      	&2.00	\\
\hline
\multicolumn{7}{| c |}{k=2} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&2.3e-0	&-	&2.6e-1	&-	&4.3e-1	&-	\\
2 $\times$ 2         	&2.8e-1	&3.02	&4.3e-2	&2.63	&5.1e-2     	&3.05	\\
4 $\times$ 4        	&3.4e-2	&3.06	&5.8e-3	&2.88	&6.6e-3     	&2.97	\\
8 $\times$ 8         	&4.0e-3	&3.10	&7.4e-4	&2.97	&8.3e-4     	&2.99	\\
16 $\times$ 16         	&4.7e-4	&3.06	&9.3e-4	&2.99	&1.0e-4     	&3.00	\\
32 $\times$ 32         	&5.8e-5	&3.03	&1.2e-5	&3.00	&1.3e-5      	&3.00	\\
\hline
\multicolumn{7}{| c |}{k=3} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&3.7e-1	&-	&5.0e-2	&-	&3.7e-2	&-	\\
2 $\times$ 2         	&3.4e-2	&3.46	&4.0e-3	&3.66	&3.4e-3     	&3.44	\\
4 $\times$ 4        	&2.6e-3	&3.70	&2.6e-4	&3.95	&2.2e-4     	&3.94	\\
8 $\times$ 8         	&1.9e-4	&3.82	&1.6e-5	&3.99	&1.4e-5     	&4.00	\\
16 $\times$ 16         	&1.1e-5	&4.06	&1.0e-6	&4.00	&8.8e-7     	&4.00	\\
32 $\times$ 32         	&5.8e-7	&4.27	&6.4e-8	&4.00	&5.5e-8      	&4.00	\\
\hline
\end{tabular}
\end{center} 
\caption{Stokes VSP: Triangles, $L^{2}$ Error and $h$-Convergence Rates.  We observe optimal convergence rates for the velocity.  The pressure rates are \emph{super}-optimal, which demonstrates that these cannot be the asymptotic values.  We believe the error in the pressure remains larger than the best approximation error due to our poor choice of test space norm (the naive norm).}
\label{NVR:table:VSPTriRates}
\end{table}

\begin{table}[h!b!p!]
\begin{center}
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
\multicolumn{7}{| c |}{k=1} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&1.1e-0	&-	&4.7e-1	&-	&8.3e-1	&-	\\
2 $\times$ 2         	&6.1e-1	&0.84	&3.0e-1	&0.65	&1.7e-1     	&2.33	\\
4 $\times$ 4        	&1.4e-1	&2.07	&7.8e-2	&1.94	&4.0e-2     	&2.03	\\
8 $\times$ 8         	&2.9e-2	&2.33	&2.0e-2	&1.99	&1.0e-2     	&2.01	\\
16 $\times$ 16         	&5.4e-3	&2.41	&4.9e-3	&2.00	&2.5e-3     	&2.00	\\
32 $\times$ 32         	&1.0e-3	&2.38	&1.2e-3	&2.00	&6.3e-4      	&2.00	\\
\hline
\multicolumn{7}{| c |}{k=2} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&3.3e-1	&-	&3.0e-1	&-	&1.7e-1	&-	\\
2 $\times$ 2         	&1.8e-1	&0.82	&3.2e-2	&3.22	&2.0e-2     	&3.06	\\
4 $\times$ 4        	&1.5e-2	&3.67	&3.9e-3	&3.04	&2.5e-3     	&3.02	\\
8 $\times$ 8         	&1.2e-3	&3.58	&4.8e-4	&3.01	&3.1e-4     	&3.01	\\
16 $\times$ 16         	&1.0e-4	&3.54	&6.0e-5	&3.00	&3.9e-5     	&3.00	\\
32 $\times$ 32         	&9.5e-6	&3.46	&7.6e-6	&3.00	&4.9e-6      	&3.00	\\
\hline
\multicolumn{7}{| c |}{k=3} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&2.7e-1	&-	&1.3e-2	&-	&3.3e-2	&-	\\
2 $\times$ 2         	&2.0e-2	&3.74	&1.7e-3	&2.91	&1.8e-3     	&4.17	\\
4 $\times$ 4       	&1.3e-3	&4.02	&1.1e-4	&3.96	&1.1e-4     	&4.05	\\
8 $\times$ 8         	&7.0e-5	&4.16	&6.8e-6	&3.99	&6.9e-6     	&4.02	\\
16 $\times$ 16         	&3.6e-6	&4.29	&4.3e-7	&4.00	&4.3e-7     	&4.00	\\
32 $\times$ 32         	&1.6e-7	&4.52	&2.7e-8	&4.00	&2.7e-8      	&4.00	\\
\hline
\end{tabular}
\end{center} 
\caption{Stokes VSP: Quads, $L^{2}$ Error and $h$-Convergence Rates.  We observe optimal convergence rates for the velocity.  The pressure rates are \emph{super}-optimal, which demonstrates that these cannot be the asymptotic values.  Comparison with the best approximation values determined in our VGP experiments verifies that the error in the pressure is considerably larger than the best approximation error in the discrete space (e.g. for $k=3$ and a $16 \times 16$ mesh, the best approximation error is 6.8e-8, vs. 3.6e-6 here); the larger error in the pressure is almost certainly due to our use of the naive test space norm.}
\label{NVR:table:VSPQuadRates}
\end{table}

\begin{table}[h!b!p!]
\begin{center}
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
\multicolumn{7}{| c |}{k=1} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&3.0e-0	&-	&1.6e-0	&-	&2.0e-0	&-	\\
2 $\times$ 2         	&1.5e-0	&1.00	&4.9e-1	&1.72	&4.2e-1     	&2.23	\\
4 $\times$ 4        	&6.4e-1	&1.23	&1.1e-1	&2.14	&1.1e-1     	&1.90	\\
8 $\times$ 8         	&2.3e-1	&1.51	&2.8e-2	&2.00	&2.8e-2     	&2.02	\\
16 $\times$ 16         	&6.9e-2	&1.70	&6.9e-3	&2.00	&6.8e-3     	&2.02	\\
32 $\times$ 32         	&2.0e-2	&1.77	&1.7e-3	&2.00	&1.7e-3      	&2.01	\\
\hline
\multicolumn{7}{| c |}{k=2} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&2.1e-0	&-	&3.3e-1	&-	&4.6e-1	&-	\\
2 $\times$ 2         	&8.5e-2	&4.65	&5.5e-2	&2.58	&5.6e-2     	&3.04	\\
4 $\times$ 4        	&8.3e-3	&3.35	&7.3e-3	&2.90	&7.7e-3     	&2.85	\\
8 $\times$ 8         	&7.7e-4	&3.44	&9.3e-4	&2.97	&1.0e-3     	&2.96	\\
16 $\times$ 16         	&6.8e-5	&3.51	&1.2e-4	&2.99	&1.3e-4     	&2.99	\\
32 $\times$ 32         	&6.9e-6	&3.30	&1.5e-5	&3.00	&1.6e-5      	&3.00	\\
\hline
\multicolumn{7}{| c |}{k=3} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&1.7e-1	&-	&5.9e-2	&-	&5.4e-2	&-	\\
2 $\times$ 2         	&1.3e-2	&3.74	&4.4e-3	&3.74	&4.2e-3     	&3.68	\\
4 $\times$ 4        	&8.9e-4	&3.83	&2.9e-4	&3.93	&2.7e-4     	&3.96	\\
8 $\times$ 8         	&4.8e-5	&4.22	&1.8e-5	&3.99	&1.7e-5     	&3.99	\\
16 $\times$ 16         	&2.0e-6	&4.60	&1.1e-6	&4.00	&1.1e-6     	&4.00	\\
32 $\times$ 32         	&6.7e-8	&4.89	&7.2e-8	&4.00	&6.4e-8      	&4.00	\\
\hline
\end{tabular}
\end{center} 
\caption{Stokes VVP: Triangles, $L^{2}$ Error and $h$-Convergence Rates.  We observe optimal convergence rates for the velocity.  The pressure rates are \emph{super}-optimal, which demonstrates that these cannot be the asymptotic values.  We believe the error in the pressure remains larger than the best approximation error due to our poor choice of test space norm (the naive norm).}
\label{NVR:table:VVPTriRates}
\end{table}

\begin{table}[h!b!p!]
\begin{center}
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
\multicolumn{7}{| c |}{k=1} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&1.5e-0	&-	&4.9e-1	&-	&1.5e-0	&-	\\
2 $\times$ 2         	&1.5e-0	&0.02	&3.6e-1	&0.45	&3.1e-1     	&2.26	\\
4 $\times$ 4        	&1.0e-1	&3.90	&6.5e-2	&2.45	&6.3e-2     	&2.28	\\
8 $\times$ 8         	&3.0e-2	&1.74	&1.6e-2	&2.05	&1.5e-2     	&2.04	\\
16 $\times$ 16         	&8.0e-3	&1.91	&3.9e-3	&2.01	&3.8e-3     	&2.01	\\
32 $\times$ 32         	&2.0e-3	&1.97	&9.8e-4	&2.00	&9.6e-4      	&2.00	\\
\hline
\multicolumn{7}{| c |}{k=2} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		& 2.1e-0	&-	&3.9e-1	&-	&2.7e-1	&-	\\
2 $\times$ 2         	& 5.1e-2	&5.33	&3.3e-2	&3.56	&2.2e-2     	&3.60	\\
4 $\times$ 4        	& 3.7e-3	&3.80	&3.9e-3	&3.07	&2.6e-3     	&3.06	\\
8 $\times$ 8         	& 3.5e-4	&3.41	&4.9e-4	&3.02	&3.3e-4     	&3.01	\\
16 $\times$ 16         	& 3.8e-5	&3.18	&6.1e-5	&3.00	&4.1e-5     	&3.00	\\
32 $\times$ 32         	& 4.4e-6	&3.12	&7.6e-6	&3.00	&5.1e-6      	&3.00	\\
\hline
\multicolumn{7}{| c |}{k=3} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&1.9e-1	&-	&1.3e-2	&-	&3.7e-2	&-	\\
2 $\times$ 2         	&1.3e-2	&3.82	&1.8e-3	&2.85	&2.0e-3     	&4.23	\\
4 $\times$ 4        	&4.7e-4	&4.83	&1.1e-4	&3.97	&1.1e-4     	&4.11	\\
8 $\times$ 8         	&1.9e-5	&4.59	&7.1e-6	&4.00	&7.1e-6     	&4.02	\\
16 $\times$ 16         	&1.0e-6	&4.24	&4.4e-7	&4.00	&4.4e-7     	&4.00	\\
32 $\times$ 32         	&6.3e-8	&4.04	&2.8e-8	&4.00	&2.8e-8      	&4.00	\\
\hline
\end{tabular}
\end{center} 
\caption{Stokes VVP: Quads, $L^{2}$ Error and $h$-Convergence Rates.  We observe optimal convergence rates for the velocity.  The pressure rates are \emph{super}-optimal, which demonstrates that these cannot be the asymptotic values.  Comparison with the best approximation values determined in our VGP experiments verifies that the error in the pressure is considerably larger than the best approximation error in the discrete space (e.g. for $k=3$ and a $16 \times 16$ mesh, the best approximation error is 6.8e-8, vs. 1.0e-6 here); the larger error in the pressure is almost certainly due to our use of the naive test space norm.}
\label{NVR:table:VVPQuadRates}
\end{table}

\clearpage
\subsubsection{Results of Convergence Studies on Hybrid Meshes}

\vspace{1.59in}

\begin{table}[h!b!p!]
\begin{center}
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
\multicolumn{7}{| c |}{k=1} \\
\hline
Mesh Size & $\phi$ & rate & $\psi_{1}$ & rate &  $\psi_{2}$ & rate \\
\hline
1 $\times$ 1		&4.2e-1	&-		&5.2e-1	&-		&3.4e-1	&-		\\
2 $\times$ 2         	&9.6e-2	&2.12	&1.7e-1	&1.58	&1.4e-1     	&1.27	\\
4 $\times$ 4        	&2.4e-2	&1.99	&4.5e-2	&1.93	&4.0e-2     	&1.84	\\
8 $\times$ 8         	&6.1e-3	&2.00	&1.2e-2	&1.97	&1.0e-2     	&1.96	\\
16 $\times$ 16         	&1.5e-3	&2.00	&2.9e-3	&1.99	&2.6e-3     	&1.99	\\
32 $\times$ 32         	&3.8e-4	&2.00	&7.3e-4	&2.00	&6.4e-4      	&2.00	\\
\hline
\multicolumn{7}{| c |}{k=2} \\
\hline
Mesh Size & $\phi$ & rate & $\psi_{1}$ & rate &  $\psi_{2}$ & rate \\
\hline
1 $\times$ 1		&7.9e-2	&-	&2.5e-1	&-	&1.4e-1	&-	\\
2 $\times$ 2         	&9.5e-3	&3.06	&2.5e-2	&3.29	&2.8e-2     	&2.33	\\
4 $\times$ 4        	&1.2e-3	&3.03	&3.3e-3	&2.94	&3.7e-3     	&2.90	\\
8 $\times$ 8         	&1.4e-4	&3.01	&4.1e-4	&3.01	&4.5e-4     	&3.04	\\
16 $\times$ 16         	&1.8e-5	&3.00	&5.1e-5	&3.01	&5.5e-5     	&3.02	\\
32 $\times$ 32         	&2.3e-6	&3.00	&6.3e-6	&3.00	&6.9e-6      	&3.01	\\
\hline
\multicolumn{7}{| c |}{k=3} \\
\hline
Mesh Size & $\phi$ & rate & $\psi_{1}$ & rate &  $\psi_{2}$ & rate \\
\hline
1 $\times$ 1		&2.5e-2	&-	&2.9e-2	&-	&4.3e-2		&-		\\
2 $\times$ 2         	&1.2e-3	&4.37	&3.0e-3	&3.27	&4.0e-3     	&3.45	\\
4 $\times$ 4        	&8.1e-5	&3.88	&1.8e-4	&4.05	&2.5e-4     	&3.98	\\
8 $\times$ 8         	&5.2e-6	&3.95	&1.2e-5	&3.99	&1.6e-5     	&3.99	\\
16 $\times$ 16         	&3.3e-7	&3.99	&7.2e-7	&4.00	&9.9e-7     	&4.00	\\
32 $\times$ 32         	&2.1e-8	&4.00	&4.4e-8	&4.00	&6.2e-8      	&4.00	\\
\hline
\end{tabular}
\end{center} 
\caption{Poisson: ``Hybrid'' Mesh, $L^{2}$ Error and $h$-Convergence Rates.  We observe optimal convergence.}
\label{NVR:table:PoissonHybridRates}
\end{table}

\begin{table}[h!b!p!]
\begin{center}
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
\multicolumn{7}{| c |}{k=1} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&3.2e-0	&-	&9.4e-1	&-	&1.2e-0	&-	\\
2 $\times$ 2         	&1.1e-0	&1.58	&3.1e-1	&1.62	&2.7e-1     	&2.10	\\
4 $\times$ 4        	&2.9e-1	&1.88	&8.0e-2	&1.94	&6.8e-2     	&1.99	\\
8 $\times$ 8         	&6.7e-2	&2.12	&2.0e-2	&1.99	&1.7e-2     	&2.00	\\
16 $\times$ 16         	&1.5e-2	&2.14	&5.0e-3	&2.00	&4.2e-3     	&2.00	\\
32 $\times$ 32         	&3.6e-3	&2.09	&1.3e-3	&2.00	&1.1e-3      	&2.00	\\
\hline
\multicolumn{7}{| c |}{k=2} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&2.3e-0	&-	&2.6e-1	&-	&4.3e-1	&-	\\
2 $\times$ 2         	&2.8e-1	&3.02	&4.1e-2	&2.67	&4.9e-2     	&3.12	\\
4 $\times$ 4        	&3.2e-2	&3.13	&5.6e-3	&2.89	&6.3e-3     	&2.98	\\
8 $\times$ 8         	&3.8e-3	&3.11	&7.1e-4	&2.97	&7.9e-4     	&2.99	\\
16 $\times$ 16         	&4.5e-4	&3.07	&9.0e-6	&2.99	&9.9e-5     	&3.00	\\
32 $\times$ 32         	&5.5e-5	&3.03	&1.1e-5	&3.00	&1.2e-5      	&3.00	\\
\hline
\multicolumn{7}{| c |}{k=3} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&3.7e-1	&-	&5.0e-2	&-	&3.7e-2	&-	\\
2 $\times$ 2         	&3.3e-2	&3.51	&3.8e-3	&3.73	&3.3e-3     	&3.50	\\
4 $\times$ 4        	&2.5e-3	&3.69	&2.5e-4	&3.95	&2.1e-4     	&3.94	\\
8 $\times$ 8         	&1.8e-4	&3.80	&1.6e-5	&3.99	&1.3e-5     	&4.00	\\
16 $\times$ 16         	&1.1e-5	&4.06	&9.7e-7	&4.00	&8.4e-7     	&4.00	\\
32 $\times$ 32         	&5.5e-7	&4.30	&6.1e-8	&4.00	&5.2e-8      	&4.00	\\
\hline
\end{tabular}
\end{center} 
\caption{Stokes VSP: ``Hybrid'' Mesh, $L^{2}$ Error and $h$-Convergence Rates.  Rates are
close to optimal.}
\label{NVR:table:VSPHybridRates}
\end{table}

\begin{table}[h!b!p!]
\begin{center}
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
\multicolumn{7}{| c |}{k=1} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&3.0e-0	&-	&1.6e-0	&-	&2.0e-0	&-	\\
2 $\times$ 2         	&1.2e-0	&1.30	&4.6e-1	&1.80	&4.1e-1     	&2.25	\\
4 $\times$ 4        	&6.2e-1	&0.97	&1.1e-1	&2.12	&1.1e-1     	&1.93	\\
8 $\times$ 8         	&2.2e-1	&1.48	&2.7e-2	&1.99	&2.7e-2     	&2.03	\\
16 $\times$ 16         	&6.9e-2	&1.70	&6.6e-3	&2.00	&6.6e-3     	&2.02	\\
32 $\times$ 32         	&2.0e-2	&1.77	&1.7e-3	&2.00	&1.6e-3      	&2.01	\\
\hline
\multicolumn{7}{| c |}{k=2} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&2.1e-0	&-	&3.3e-1	&-	&4.6e-1	&-	\\
2 $\times$ 2         	&8.8e-2	&4.60	&5.2e-2	&2.64	&5.3e-2     	&3.12	\\
4 $\times$ 4        	&8.6e-3	&3.35	&7.0e-3	&2.91	&7.3e-3     	&2.85	\\
8 $\times$ 8         	&7.7e-4	&3.48	&8.9e-4	&2.98	&9.4e-4     	&2.96	\\
16 $\times$ 16         	&6.7e-5	&3.53	&1.1e-4	&2.99	&1.2e-4     	&2.99	\\
32 $\times$ 32         	&6.7e-6	&3.32	&1.4e-5	&3.00	&1.5e-5      	&3.00	\\
\hline
\multicolumn{7}{| c |}{k=3} \\
\hline
Mesh Size & $p$ & rate & $u_{1}$ & rate &  $u_{2}$ & rate \\
\hline
1 $\times$ 1		&1.7e-1	&-	&5.9e-2	&-	&5.4e-2	&-	\\
2 $\times$ 2         	&1.3e-2	&3.74	&4.2e-3	&3.81	&4.0e-3     	&3.75	\\
4 $\times$ 4        	&8.9e-4	&3.83	&2.8e-4	&3.93	&2.6e-4     	&3.97	\\
8 $\times$ 8         	&4.8e-5	&4.22	&1.7e-5	&3.99	&1.6e-5     	&4.00	\\
16 $\times$ 16         	&2.0e-6	&4.59	&1.1e-6	&4.00	&1.0e-6     	&4.00	\\
32 $\times$ 32         	&6.7e-8	&4.89	&6.8e-8	&4.00	&6.3e-8      	&4.00	\\
\hline
\end{tabular}
\end{center} 
\caption{Stokes VVP: ``Hybrid'' Mesh, $L^{2}$ Error and $h$-Convergence Rates.  Rates are close to optimal.}
\label{NVR:table:VVPHybridRates}
\end{table}

\pagebreak

\subsubsection{Solution Plots}

\begin{figure}[h!b!h!]
\begin{center}
\includegraphics[height=0.27\textheight]{plots/poissonHybrid/phicubic16x16.pdf}\\
\includegraphics[height=0.27\textheight]{plots/poissonHybrid/psi1cubic16x16.pdf}\\
\includegraphics[height=0.27\textheight]{plots/poissonHybrid/psi2cubic16x16.pdf}
\caption{Solution of Poisson with quads and triangles (cubic elements, $16 \times 16$ mesh):
$\phi$ (top pane),
$\psi_{1}$ (middle pane)
$\psi_{2}$ (bottom pane).}
\label{NVR:fig:Poisson}
\end{center}\end{figure}

\begin{figure}[h!b!h!]
\begin{center}
\includegraphics[height=0.27\textheight]{plots/stokesVVPHybrid/pressurecubic16x16.pdf}
\includegraphics[height=0.27\textheight]{plots/stokesVVPHybrid/u1cubic16x16.pdf}
\includegraphics[height=0.27\textheight]{plots/stokesVVPHybrid/u2cubic16x16.pdf}
\caption{Solution of Stokes (VVP) with quads and triangles (cubic elements, $16 \times 16$ mesh):
$p$ (top pane),
$u_{1}$ (middle pane),
$u_{2}$ (bottom pane).}
\label{NVR:fig:Stokes}
\end{center}\end{figure}

\clearpage

\subsection{Extending Camellia for Distributed Stiffness Matrix Determination}\label{sec:distributingStiffness}
Here, we describe the changes that we implemented within Camellia to allow the stiffness matrix determination to be executed efficiently within an MPI environment.

Camellia was originally written to run in serial, so a number of changes were required to allow MPI execution---the most significant of these had to do with element partitioning and partitioning the degree-of-freedom coefficients.  Trilinos's Intrepid routines are designed to execute on batches of cells that are alike in topology and polynomial order.  We allow meshes of non-uniform topology and polynomial order; thus we had implemented an ElementType class which allowed us to identify elements that could be batched.  Our Mesh class maintained data structures such that information pertaining to a particular ElementType could be accessed quickly---for example, Mesh stored a data structure that contained the vertex coordinates belonging to elements of a given ElementType.

The upshot of this design is that mesh information is already, in a sense, partitioned.  However, there is no reason to expect that this will be a good partitioning for dividing up the work of stiffness matrix computation across MPI nodes---for this, we want our mesh partitioning to keep spatially adjacent elements together within a partition to minimize the amount of data that needs to be communicated during global stiffness matrix assembly.

Thus, to maintain both of our desired design features---batching by ElementType and spatially contiguous partitioning across MPI nodes---we require a two-level partitioning; we first divide the elements spatially (the MPI partitions), and then batch together elements of like ElementType within each of these partitions.  (Unfortunately, this is not quite the whole story; because other classes depend on the ElementType division of the whole mesh, we have had to maintain the old lookup tables as well.  We do hope to eliminate these dependencies in the end.)

To facilitate experiments with multiple partitioning strategies (and to maintain separation of concerns), we designed an abstract MeshPartitionPolicy class which, given a Mesh and the number of partitions desired, returns a partition of the elements in the mesh.  The Mesh then uses this to generate a partition of the degree-of-freedom coefficients, which induces a partition of the rows in the stiffness matrix.  The latter partition is used in conjunction with an Epetra FECrsMatrix, a distributed stiffness matrix class within Trilinos.  The FECrsMatrix allows storage of data not owned by the current MPI node; this data is communicated to the owning MPI node during global assembly of the stiffness matrix.  A convenient consequence of this is that we can separate the cost of global assembly from the cost of local stiffness matrix computations; the latter are independent across MPI nodes, and therefore we expect to see perfect scaling for these.  The scaling of the global assembly will depend on the quality of the partition and the cost of communication between MPI nodes.  We do not hope for perfect scaling here, but we do hope to see a cost per degree of freedom per node that does not grow too quickly in the total number of nodes.

The MeshPartitionPolicy partitions the mesh into sets of elements assigned to an MPI node; for the interface to Epetra, we need a partition of rows of the global stiffness matrix (each of which corresponds to a degree of freedom).  Degrees of freedom corresponding to numerical fluxes are shared by the elements along whose boundaries they lie.  We adopt a simple greedy policy for assignment of these d.o.f.s: shared d.o.f.s are assigned to the element with the smallest global identifier.  This means that even if the element partitioning were perfectly balanced, some MPI nodes might still have more d.o.f.s assigned to them than others.  This will not affect the amount of work involved in local stiffness matrix computations, but it may affect MPI communication costs during global assembly.

\paragraph{Design Limitations: where Amdahl's law might come to haunt us.}
Here, we note a few features of the present design that may become bottlenecks as we scale up to larger problems and larger numbers of MPI nodes.

At present, our global solve is implemented using the KLU implementation provided by the Amesos package within Trilinos.  This is a direct solve, executed in serial.  Amesos gathers the global stiffness matrix to rank 0, solves, and then scatters the solution according to the partition we have defined.  For our serial computations prior to the present work, the cost of the global solve has been dominated by the cost of the local optimal test function determination; however, now that the latter cost has been distributed using MPI and the former has not, we expect the global solve to become a bottleneck, both in terms of overall execution time and in terms of the sizes of problems that can be solved, since the KLU solve must fit into a single node's memory to be practical.

Similarly, at present the entire mesh is determined and stored on every MPI node.  This has the advantage that no MPI communication is required during mesh construction, but for very large meshes it may become impractical, because the time cost of mesh construction may grow relative to the distributed parts of the computation, and perhaps (for \emph{extremely} large meshes) because the memory required for the mesh may grow too large for storage on a node.

Finally, certain features of the original code depend upon all the solution coefficients being available to the current processor, so for the time being we distribute the entire solution to every MPI node, after Amesos has scattered according to the original partitioning.  We hope to eliminate this dependence on having all solution coefficients available, allowing the solution to be distributed according to the same mapping as was used for the stiffness matrix.

\subsubsection{Partitioning}

Since Camellia is tightly integrated with the Trilinos library already, we use the Zoltan package in Trilinos to generate spatially local partitions of the mesh \cite{ZoltanOverviewArticle}. We interface specifically with the Hilbert Space-filling Curve and Reftree partitioning algorithms in Zoltan, both of which can include parallel implementations.

The Hilbert space-filling curve (HSFC) algorithm works by drawing a curve through the geometric mesh in 2- or 3-dimensional space, then mapping that curve to the interval $[0,1]$. The partitioner then divides up this interval (in an even or weighted manner) into $n$ partitions, and uses this partitioning to induce a partition of the mesh. All that's required by the HSFC algorithm is a listing of elements and a geometric identifier associated with a given element. In this case, we use the element centroid as such an identifier.

The Reftree algorithm \cite{REFTREE} adds complexity in that each processor must store information not only about the active nodes, but the ancestors as well. Reftree also requires that if you store an ancestor, you also store all its children as well, increasing the amount of redundancy between distributed refinement trees. However, since Reftree is not tuned to a particular element types (quad or triangle, tetrahedron or cube), the same algorithm performs similarly for many different types of refined meshes (as opposed to HSFC, which works best for quadrilateral grids, but not for triangular grids).  Additionally, Reftree's algorithm guarantees connected partitions for tetrahedral and triangular grids, and generally performs more robustly on other types of grids as well.

Currently, we have implemented and tested a Reftree MeshPartitionPolicy on our workstations. However, Reftree currently crashes during runs on Lonestar, our HPC architecture for this report. We used the HSFC partitioner for the scaling tests in this report, and hope to fix issues with Reftree in the near future.

\subsubsection{Scaling tests}\label{sec:ScalingExperiments}

We tested the scalability of our code on the Lonestar machine at the Texas Advanced Computing Center (TACC), verifying whether or not we observe strong/weak scaling for various parts of the program.  We solve the convection-diffusion equation on a square mesh, with boundary conditions such that the solution develops a boundary layer (sharp gradient) near the north and east edges of the square.  The solution for a refined mesh is shown in Figure \ref{fig:solutionPlot}.

\begin{figure}[h!]
\centering
\includegraphics[scale=0.45]{figs/Solution12928nomesh.png}
\caption{Computed solution for $\epsilon=10^{-2}$ using a 12,928-element mesh.  $L^2$ error is $O(10^{-5})$.}
\label{fig:solutionPlot}
\end{figure}

We set up our computational experiments by first refining all cells that share an edge with the north and east sides, and repeating this process four times.   We then constructed three additional meshes, by uniformly refining every element in the mesh (quadrupling the number of elements each time).  For each of these meshes, we solved on Lonestar, using 1, 4, 16, and 64 nodes, tracking the timing of various portions of the code.  From this data, we extracted strong and weak scaling statistics, discussed below in Sections \ref{sec:strongScaling} and \ref{sec:weakScaling}.  The runtimes plotted in each of our figures are the mean of the times recorded at each MPI node.

We also used contiguous and discontiguous partitions of each mesh to measure the effect of partition quality on the communication costs in global stiffness matrix assembly.  We created contiguous partitions of the mesh using a HSFC partitioner.  To create the discontiguous partitioning, we used the Zoltan cyclic partitioner, which loops through the list of active elements, sending the first element to the first processor, the next to the next processor, and so on.  After reaching the last processor, the cyclic partitioner cycles back to the first processor and repeats this process.\footnote{Due to the nature of our refinements in this test, a blocked partitioner (equally partitioning the ordered list of active elements by element number) happened to produce nearly-contiguous partitions.  We therefore have omitted this partitioner from our analysis, since we do not believe that its performance here accurately predicts its performance in general.}  The cyclic partitioning is a ``worst case" scenario in the sense that each of the current MPI node's elements' neighbors are owned by some other MPI node, with the consequence that information concerning each element boundary must be sent via MPI.  An example cyclic partitioning can be seen in Figure \ref{fig:cyclicPartition}; Figure \ref{fig:HSFCPartition} shows an HSFC partitioning.

It's worth noting that the runtimes reported here do not represent Camellia running at peak efficiency.  A single Lonestar node contains 12 cores.  Because MPI communication has much higher bandwidth intra-node than inter-node, and for analysis we wanted approximately equal bandwidth between MPI processes, we use only one core per node.  Utilizing all 12 cores on a node would decrease communication costs.  Additionally, there is a parameter within Camellia that controls the batch size for the Trilinos Intrepid batching routines.  Tuning this parameter based on machine-specific cache sizes should further improve performance.

\begin{figure}[h!]
\centering
\subfigure[Cyclic partitioning]{\label{fig:cyclicPartition}
\includegraphics[scale = 0.42]{figs/cyclic.pdf}
}
\subfigure[HSFC partitioning]{\label{fig:HSFCPartition}
\includegraphics[scale = 0.42]{figs/hsfc.pdf}
}
\caption{Discontiguous and contiguous partitions of the mesh.}
\end{figure}

\subsubsection{Strong scaling}\label{sec:strongScaling}
In our strong scaling tests, we considered problems of fixed size, distributing the workload for each among increasing numbers of MPI nodes.  Here, we hope to see runtimes that decrease linearly in the number of MPI nodes---this is what we mean by achieving strong scalability.

Because the local stiffness computations are entirely independent of each other, requiring no communication among MPI nodes, we expect to see perfect scaling for these.  As can be seen in Figures \ref{fig:strongScalingLocalStiffnessCyclic} and \ref{fig:strongScalingLocalStiffnessHSFC}, we do achieve something very close to this, although the cyclic partitioning took longer in almost every case, for reasons that are unclear to us.  It may have something to do with data locality on each node---by the manner of our construction, data concerning contiguous mesh elements is more likely to be close together in memory than the data for mesh elements in the cyclic case.

It is less clear what we should expect for the global stiffness matrix assembly; we expect the HSFC partitioning to outperform the cyclic partitioning, and we would like to see the runtimes for assembly decrease as the number of MPI nodes increases.  As can be seen in Figures \ref{fig:strongScalingAssemblyCyclic} and \ref{fig:strongScalingAssemblyHSFC}, for the larger problems in both cases, we do have something approaching strong scalability.  For the 202- and 808-element problems, we see the time cost increase (or fail to decrease, in the case of the 808-element problem for the cyclic partitioner) between 16 and 64 nodes.  However, it's worth noting that in these cases, the real times involved are small: less than a second in each case.  If our concern is our ability to scale up to large problems on large numbers of processors, it does not appear that the global assembly will be a bottleneck.  The HSFC partitioning does show its strength here compared with the cyclic; for the 12,928 mesh on the 4-node run, the cyclic partitioning took an average of 49.1 seconds per node, compared with 1.63 seconds for the HSFC partitioning.

\begin{figure}[h!]
\centering
\subfigure[Cyclic Partitioning]{\label{fig:strongScalingLocalStiffnessCyclic}
\includegraphics[scale = 0.42]{figs/scalingFigs/cyclicStrongScalingLocal.pdf}
}
\subfigure[HSFC Partitioning]{\label{fig:strongScalingLocalStiffnessHSFC}
\includegraphics[scale = 0.42]{figs/scalingFigs/hsfcStrongScalingLocal.pdf}
}
\caption{Strong scaling plots for the local stiffness matrix computation.}
\end{figure}

\begin{figure}[h!]
\centering
\subfigure[Cyclic Partitioning]{\label{fig:strongScalingAssemblyCyclic}
\includegraphics[scale = 0.42]{figs/scalingFigs/cyclicStrongScalingAssembly.pdf}
}
\subfigure[HSFC Partitioning]{\label{fig:strongScalingAssemblyHSFC}
\includegraphics[scale = 0.42]{figs/scalingFigs/hsfcStrongScalingAssembly.pdf}
}
\caption{Strong scaling plots for global stiffness matrix assembly.  (Note the differing scales.) }
\end{figure}

\subsubsection{Weak scaling}\label{sec:weakScaling}
In our weak scaling tests, we aimed to fix the size of the problem \emph{per MPI node}, and examined the runtime of various portions of the execution---we hope to see a constant runtime as the problem size and number of processors increase, and this is what we mean by achieving weak scalability.

\begin{figure}[h!]
\centering
\subfigure[Local stiffness computation]{
\label{fig:weakScalingStiffness}
\includegraphics[scale = 0.42]{figs/scalingFigs/weakScalingLocal.pdf}
}
\subfigure[Global stiffness assembly]{
\label{fig:weakScalingAssembly}
\includegraphics[scale = 0.42]{figs/scalingFigs/weakScalingAssembly.pdf}
}
\caption{Weak scaling results for computation of local stiffness matrices and global stiffness matrix assembly.  For each run, both the number of MPI nodes and the number of elements increased by a factor of four.}
\end{figure}

Both partition types achieve weak scalability in the local stiffness matrix computation, as can be seen in Figure \ref{fig:weakScalingStiffness}.  In fact, we see the total runtime \emph{decrease} slightly as the total workload and number of MPI nodes increase---we are unsure of the reason for this. Although we would not expect the partitioning to affect this portion of the computation at all (since no inter-node communication occurs at this stage), for some reason the HSFC partitioning slightly outperforms the cyclic on each of the multi-node runs.  As with the strong scaling, we speculate that this is due to locality of the owned element data in the case of the HSFC partitioning.

Assembly of the global stiffness matrix achieves weak scalability only for the contiguous case, as can be seen in Figure \ref{fig:weakScalingAssembly}. It's worth noting, however, that though the poor mesh partitioning imposes much higher communication costs than the HSFC partitioning, the maximum amount of time spent on assembly is still dominated by the time spent on computation of local stiffness matrices.

\subsubsection{Total runtime analysis}\label{sec:runtimeAnalysis}
As the final component of our performance analysis, we examine components of the total runtime for each of our four problems using 1, 4, 16, and 64 MPI nodes; here we use the HSFC partitioner.  This can be seen in Figure \ref{fig:timeBreakdown}.  We see that for the largest MPI runs the combined time spent on local stiffness computation and global assembly is a small fraction of the total time spent---since these were the targets of the present work, we can count it a success.  The graphs also show that the cost of the global solve dominates in each of these runs, making this the obvious next target for optimization.  In the ``Other'' category, the largest cost is the mesh determination.  In the 12,928-element case, this takes about 5 seconds.  Thus, a distributed mesh might be our next target after the solve is optimized.

\begin{figure}[h!]
\centering
\subfigure[202 elements, 13,343 dofs]{
\includegraphics[scale = 0.42]{figs/scalingFigs/bar_ref0.pdf}
}
\subfigure[808 elements, 52,137 dofs ]{
\includegraphics[scale = 0.42]{figs/scalingFigs/bar_ref1.pdf}
}
\subfigure[3,232 elements, 206,081 dofs]{
\includegraphics[scale = 0.42]{figs/scalingFigs/bar_ref2.pdf}
}
\subfigure[12,928 elements, 819,393 dofs]{
\includegraphics[scale = 0.42]{figs/scalingFigs/bar_ref3.pdf}
}
\caption{Breakdown of time spent in a solve for a series of HSFC-partitioned meshes.}
\label{fig:timeBreakdown}
\end{figure}

\subsubsection{Future Work for Better Scaling}\label{sec:FutureWork}
There are several ways in which we hope to extend Camellia further to allow it to solve larger problems still; we hope to:
\begin{itemize}
\item distribute the solve, using MUMPS or an iterative solver,
\item improve the load balancing for meshes of variable polynomial order,
\item distribute mesh construction and storage, and
\item distribute solution storage.
\end{itemize}

As discussed in Section \ref{sec:runtimeAnalysis} above, the lowest-hanging fruit for further improving the performance for the experimental setup considered in the present work is distributing the solve.  We have already successfully interfaced with MUMPS---a parallel sparse direct solver---on one of our laptops; we expect that getting MUMPS to work on Lonestar will just be a matter of building Trilinos and Camellia with MUMPS there.  One of the advantages of DPG is that its stiffness matrices are guaranteed to be symmetric positive definite, which opens the door to using iterative methods such as conjugate gradient methods.  DPG also produces matrices whose entries are coupled only through the flux degrees of freedom; thus static condensation techniques can be used to reduce the size of the global system to be solved.  We believe that iterative solvers and static condensation would allow us to solve larger problems than MUMPS will allow---we have heard that MUMPS only scales to about 128 processors.

In the present work, we considered a mesh of uniform polynomial order and considered all elements to be of equal weight; Camellia supports meshes with variable order, and Zoltan provides facilities for weighting elements differently.  By taking advantage of this feature of Zoltan (using a weight corresponding to the number of degrees of freedom on each element), we can improve Camellia's load balancing for meshes of variable polynomial order.  In fact, in doing so, we expect to improve slightly the load balancing for the setup considered here, because elements with hanging nodes do have slightly more degrees of freedom than those without.

At present, the mesh is constructed and stored on each node, as is the solution.  It should be a relatively small extension to the present work to allow the solution to be distributed.  Allowing mesh construction to be distributed is a bigger challenge, largely because the nodes must agree on the global stiffness matrix row indices.  Given that we are working with an adaptive mesh, it will likely make sense to distribute the work of mesh refinement according to the partition of the previous mesh and use Zoltan to do the load rebalancing.

In summary, we have achieved good overall speedup for Camellia using a Hilbert space-filling curve partitioner, and have identified the next steps for improving its parallel performance further.

\subsection{Demonstration of Nonlinear Solution Capabilities: Compressible Navier-Stokes}\label{sec:compressibleNS}
Jesse Chan has applied Camellia's nonlinear solve capabilities to the compressible Navier-Stokes equations in the context of Carter's flat plate problem.  We include here some plots that demonstrate the success of the adaptive mesh (Figure \ref{fig:JCmeshRefinements}), as well as a plot of the final solution for the velocity in the $x$ direction (Figure \ref{fig:JCu1}).  This experiment was performed with a Reynolds number of 1000 and a Mach number of 3.

\begin{figure}[h!]
\centering
\subfigure[i=0]{
\includegraphics[scale = 0.45]{figures/mesh0.png}
}
\subfigure[i=1]{
\includegraphics[scale = 0.45]{figures/mesh1.png}
}
\subfigure[i=2]{
\includegraphics[scale = 0.45]{figures/mesh2.png}
}
\subfigure[i=4]{
\includegraphics[scale = 0.45]{figures/mesh4.png}
}
\subfigure[i=5]{
\includegraphics[scale = 0.45]{figures/mesh5.png}
}
\subfigure[i=6]{
\includegraphics[scale = 0.45]{figures/mesh6.png}
}
\caption{Mesh refinements for compressible Navier-Stokes in Carter's flat plate problem.  The $i$ values are the refinement number (i.e. $i=0$ corresponds to the initial mesh).}
\label{fig:JCmeshRefinements}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[scale = 0.90]{figures/u1.pdf}
\caption{Final solution for the $x$ component of the velocity in Carter's flat plate problem.}
\label{fig:JCu1}
\end{figure}

%\subsection{Meshing, Solving, and Adaptivity}\label{sec:Meshing}   both what's there now, and what we will eventually do.  This is where our idea for the $hp$-decision algorithm should go.
%\subsubsection{Handling Hanging Nodes: MultiBasis and PatchBasis}\label{sec:HangingNodes}
%\subsection{Nonlinear Problems}\label{sec:NonlinearProblems}
%\subsection{Comparison between Camellia and deal.II}\label{sec:Deal.II}
%\subsection{Summary}\label{sec:CamelliaConclusion}

\clearpage

### 2012-09-10 docs/Nate/Proposal/abstract.tex
Added proposal.

%\documentstyle[11pt]{article}
\documentclass[12pt,c]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[english]{babel}
\usepackage{a4wide}
%\usepackage{showlabels}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{pgf}
\usepackage[textsize=footnotesize,color=yellow]{todonotes}
\usepackage{subfigure}

% Latin Modern (similar to CM with more characters)
\usepackage{lmodern} % math, rm, ss, tt
\usepackage[T1]{fontenc}

\input{my_preamble}
\input{nate_commands}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\tanbui}[2]{\textcolor{blue}{\underline{#1}} \textcolor{red}{#2}}
\newcommand{\note}[1]{\noindent\emph{\textcolor{blue}{#1\,}}}
\newcommand{\LRp}[1]{\left( #1 \right)}
\newcommand{\LRs}[1]{\left[ #1 \right]}
\newcommand{\LRa}[1]{\left< #1 \right>}
\newcommand{\LRc}[1]{\left\{ #1 \right\}}

\DeclareMathOperator*{\argmin}{arg\,min}

% COLORS
\def\Reddd{\special{color rgb  1.   0.   0.}} 
\def\Black{\special{color cmyk 0.   0.   0    1.}} 
\let\B\Black   
\let\Rd\Reddd

\catcode`@=12

             \topmargin 0.0in      %(TOP)  1"
             \oddsidemargin 0.0in  %(LEFT) 1"
             \textwidth 6.5in      %(RIGHT)1"
             \textheight 8.5in     %(BOT)  1"
             \headsep 0.0in
             \headheight 0.3in

\DeclareMathOperator{\curl}{curl}

\newcommand{\PT}{{\partial T}}
\def\grad{\nabla}
\def\pa{\partial}
\let\tilde\widetilde

\newcommand{\eqnlab}[1]{\label{eq:#1}}
\newcommand{\eqnref}[1]{\eqref{eq:#1}}
\newcommand{\prolab}[1]{\label{pro:#1}}
\newcommand{\proref}[1]{\ref{pro:#1}}
\newcommand{\theolab}[1]{\label{theo:#1}}
\newcommand{\theoref}[1]{\ref{theo:#1}}
\newcommand{\lemlab}[1]{\label{lem:#1}}
\newcommand{\lemref}[1]{\ref{lem:#1}}
\newcommand{\seclab}[1]{\label{sec:#1}}
\newcommand{\secref}[1]{\ref{sec:#1}}

\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\nor}[1]{\left\| #1 \right\|}
\newcommand{\jump}[1] {\ensuremath{[\![#1]\!]}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\Grad} {\ensuremath{\nabla}}
\newcommand{\Div} {\ensuremath{\nabla\cdot}}
\newcommand{\pO}{\partial \Omega}
\newcommand{\eval}[2][\right]{\relax
  \ifx#1\right\relax \left.\fi#2#1\rvert}

\newcommand{\A}{A}
\newcommand{\As}{A^\ast}
\newcommand{\HA}{H_\A}
\newcommand{\HAs}{H_{\As}}
\newcommand{\T}{T}
\renewcommand{\L}{L^2\LRp{\Omega}}
\newcommand{\Tt}{T^\ast}
\renewcommand{\B}{\mc{B}}
\newcommand{\M}{\mc{M}}
\newcommand{\Bs}{\mc{B}^\ast}
\newcommand{\Ms}{\mc{M}^\ast}
\newcommand{\V}{V}
\newcommand{\Vs}{\V^\ast}

\begin{document}
\baselineskip=16pt
\parskip= 4pt
%*************************************************page 1

%\input{project}
%\bibliography{./DPG,/home/leszek/ices/book3/references/Demkowicz}
%\bibliographystyle{plain}

\newpage

%\vspace*{.5cm}

\begin{center}

{\huge
A Discontinuous Petrov-Galerkin Methodology\\ for Incompressible Flow\\[8pt]
}
{\LARGE
Towards Automatic, Robust Mesh Adaptivity
}
\vspace*{1cm}

\vspace*{.5cm}
{\large

Nathan V. Roberts \\
Committee: Leszek Demkowicz (co-advisor), Robert Moser (co-advisor), \\
Todd Arbogast, George Biros, Thomas Hughes
}
\end{center}

%\begin{abstract}
%We discuss well-posedness and convergence theory for 
%the DPG method applied to a general system of linear Partial Differential
%Equations (PDEs) and specialize it to the classical Stokes problem.  The Stokes problem is an iconic troublemaker for standard Bubnov Galerkin methods; if discretizations are not carefully designed, they may exhibit non-convergence or locking.  By contrast, DPG does not require us to treat the Stokes problem in any special manner.  We illustrate and confirm our theoretical convergence estimates with numerical experiments.
%\end{abstract}

%{\bf Key words:}
%Discontinuous Petrov Galerkin, Stokes problem
%
%{\bf AMS subject classification:} 65N30, 35L15

%\subsection*{Acknowledgment}
%Roberts was supported by the Department of Energy
%[National Nuclear Security Adminis- tration] under Award Number
%[DE-FC52-08NA28615].  We also thank Pavel Bochev and Denis Ridzal for
%hosting and collaborating with Roberts in the summers of 2010 and
%2011, when he was supported by internships at Sandia National
%Laboratories (Albuquerque).

\paragraph{Motivation.} Incompressible flows---flows in which variations in the density of a fluid are not important to the physics---arise in a wide variety of applications, from hydraulics to aerodynamics.  The incompressible Navier-Stokes equations which govern such flows are also of fundamental physical and mathematical interest.  They are believed to hold the key to understanding turbulent phenomena; precise conditions for the existence and uniqueness of solutions remain unknown---and establishing such conditions is the subject of one of the Clay Mathematics Institute's Millennium Prize Problems.

Typical solutions of incompressible flow problems involve both fine- and large-scale phenomena, so that a uniform finite element mesh of sufficient granularity will at best be wasteful of computational resources, and at worst be infeasible because of resource limitations.  Thus adaptive mesh refinements are required.  In industry, the adaptivity schemes used are ad hoc, requiring a domain expert to predict features of the solution.  A badly chosen mesh may cause the code to take considerably longer to converge, or fail to converge altogether.  Typically, the Navier-Stokes solve will be just one component in an optimization loop, which means that any failure requiring human intervention is costly.

\paragraph{Goal.} My aim is to develop a solver for the incompressible Navier-Stokes equations that provides robust adaptivity starting with a coarse mesh.  By robust, I mean both that the solver always converges to a solution in predictable time, and that the adaptive scheme is independent of the problem---no special expertise is required for adaptivity.

The cornerstone of my approach will be the discontinuous Petrov-Galerkin with optimal test functions (DPG) finite element methodology recently developed by Leszek Demkowicz and Jay Gopalakrishnan \cite{DPG1,DPG2}.  Whereas Bubnov-Galerkin methods use the same function space for both test and trial functions, Petrov-Galerkin methods allow the spaces for test and trial functions to differ.  In DPG, the test functions are computed on the fly and are chosen to minimize the residual.  For well-posed problems with sufficiently regular solutions, DPG can be shown to converge at optimal rates---the ``inf sup'' constants governing the convergence are mesh-independent, and of the same order as those governing the continuous problem \cite{DPGStokes}.  DPG also provides an accurate mechanism for \emph{measuring} (not merely estimating) the error, and this can be used to drive adaptive mesh refinements.

Several approximations to Navier-Stokes are of physical interest, and my approach will involve studying each of these in turn, culminating in the study of the 2D incompressible Navier-Stokes equations.  The Stokes equations can be obtained by neglecting the convective term; these are accurate for ``creeping'' viscous flows.  The Oseen equations replace the convective term, which is nonlinear, with a linear approximation.  The steady-state incompressible Navier-Stokes equations are an approximation of the transient equations, obtained by neglecting time variations.

We have studied DPG applied to the Stokes problem in some detail, with theoretical results predicting optimal rates of convergence, and numerical results that appear to show even more: it appears that we asymptotically approach the best approximation error available in the discrete space \cite{DPGStokes}.  Because of this success and the close relationship between the Stokes equations and the incompressible Navier-Stokes equations, I am optimistic that we can achieve good results with the latter as well.

Central to my study of these problems will be the use and further development of \emph{Camellia} \cite{RobertsetAl11}, a toolbox I developed for solving DPG problems which uses Sandia's Trilinos library of packages \cite{Trilinos}.   I began work on Camellia in collaboration with Denis Ridzal and Pavel Bochev during an internship at Sandia.\nocite{RobertsetAl10}  At present, Camellia supports 2D meshes of triangles and quads of variable polynomial order, provides mechanisms for easy specification of DPG variational forms, supports $h$- and $p$- refinements, and supports distributed computation of the stiffness matrix, among other features.  I hope to add support for meshes of arbitrary spatial dimension, support for space-time elements, and support for distributed mesh and solution representation---although it is not yet clear that these will be necessary for the central goal of the dissertation, it is clear that such features will be desirable.

\paragraph{Contributions.} The central contribution of the dissertation will be the design and development of mathematical techniques and software, based on the DPG method, for solving the 2D incompressible Navier-Stokes equations in the laminar regime (Reynolds numbers up to about 1000).  Along the way, I will investigate approximations to these equations---the Stokes equations and the Oseen equations---followed by the steady-state Navier-Stokes equations.  If time allows, I will also solve the transient Navier-Stokes equations.

The study of DPG applied to a system of PDEs has several aspects.  A first-order variational formulation must be derived, including the selection of appropriate test and trial space norms.  The well-posedness of the formulation might be proved.  The formulation can be investigated numerically by means of test problems: convergence can be studied by means of manufactured solutions, and ``real-world'' performance can be studied by means of more physically realistic test problems.  In terms of the CSEM program areas, the derivation of variational formulations and any proofs of their well-posedness belong to Area A, Applicable Mathematics.  The design and development of software for numerical investigations belong to Area B, Numerical Analysis and Scientific Computation.  The study of test problems belongs to Area C, Mathematical Modeling and Applications.  I will briefly describe the specific proposed contributions of this dissertation to each of these in turn.

\paragraph{Area A.}  I will pose several DPG formulations of the Stokes equations---the velocity-gradient-pressure (VGP), velocity-stress-pressure (VSP), and velocity-vorticity-pressure (VVP) formulations.  I will pose DPG formulations of the Oseen equations and the 2D incompressible Navier-Stokes equations.

I will prove the well-posedness of the VGP Stokes formulation for DPG, which has as consequence a guarantee of optimal convergence rates \cite{DPGStokes}; I plan to complete similar proofs for the VSP and VVP formulations.  Time permitting, I would like to prove a similar result for the Oseen equations.  The work on the Oseen equations will include the study of \emph{robustness} for the small-viscosity (high Reynolds number) case, with reference to previous work on convection-dominated diffusion \cite{DPG2,DemkowiczHeuer}.

\paragraph{Area B.} I will design and develop a software toolbox (\emph{Camellia}) for the investigation of DPG problems.  This will support 2D meshes of triangles and quads of variable polynomial order, provide mechanisms for easy specification of DPG variational forms, support $h$- and $p$- refinements, and support distributed computation of the stiffness matrix, among other features.

Time permitting, I hope to add support for meshes of arbitrary spatial dimension, support for space-time elements, and support for distributed mesh and solution representation.

\paragraph{Area C.} I will verify convergence rates for the Stokes, Oseen, and Navier-Stokes equations using manufactured solutions.

I will simulate the classical lid-driven cavity flow and backward-facing step problems using, in turn, the Stokes, Oseen, and Navier-Stokes equations.

I will simulate flow past a cylinder using the steady-state Navier-Stokes equations.  Time permitting, I will do so with the transient equations as well.

\nocite{Chorin68}
\nocite{Rannacher99}

\bibliography{./DPG}
\bibliographystyle{plain}

\end{document}

### 2012-09-10 docs/Nate/Proposal/summary.tex
Added proposal.

%\documentstyle[11pt]{article}
\documentclass[11pt,c]{article}
\usepackage[multiple]{footmisc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[english]{babel}
\usepackage{times}
\usepackage{a4wide}
%\usepackage{showlabels}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{pgf}
\usepackage[textsize=footnotesize,color=yellow]{todonotes}
\usepackage{subfigure}
\usepackage{listings}
\usepackage{courier}
\definecolor{lightlightgray}{gray}{0.95}
\definecolor{lightlightblue}{rgb}{0.4,0.4,0.95}
\definecolor{lightlightgreen}{rgb}{0.8,1,0.8}
\lstset{language=C++,
           frame=single,
           basicstyle=\ttfamily\footnotesize,
           keywordstyle=\color{black}\textbf,
           backgroundcolor=\color{lightlightgray},
           commentstyle=\color{blue},
           frame=single
           }
\usepackage{hyperref}

\setcounter{tocdepth}{2}

\input{my_preamble}
\input{nate_commands}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\tanbui}[2]{\textcolor{blue}{\underline{#1}} \textcolor{red}{#2}}
\newcommand{\note}[1]{\noindent\emph{\textcolor{blue}{#1\,}}}
\newcommand{\LRp}[1]{\left( #1 \right)}
\newcommand{\LRs}[1]{\left[ #1 \right]}
\newcommand{\LRa}[1]{\left< #1 \right>}
\newcommand{\LRc}[1]{\left\{ #1 \right\}}

\newcommand{\pd}[2]{\frac{\partial #1}{\partial #2}}

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\deal}{\code{deal.II}\,}

\DeclareMathOperator*{\argmin}{arg\,min}

% COLORS
\def\Reddd{\special{color rgb  1.   0.   0.}} 
\def\Black{\special{color cmyk 0.   0.   0    1.}} 
\let\B\Black   
\let\Rd\Reddd

\catcode`@=12

             \topmargin 0.0in      %(TOP)  1"
             \oddsidemargin 0.0in  %(LEFT) 1"
             \textwidth 6.5in      %(RIGHT)1"
             \textheight 8.5in     %(BOT)  1"
             \headsep 0.0in
             \headheight 0.3in

\DeclareMathOperator{\curl}{curl}

\newcommand{\PT}{{\partial T}}
\def\grad{\nabla}
\def\pa{\partial}
\let\tilde\widetilde

\newcommand{\eqnlab}[1]{\label{eq:#1}}
\newcommand{\eqnref}[1]{\eqref{eq:#1}}
\newcommand{\prolab}[1]{\label{pro:#1}}
\newcommand{\proref}[1]{\ref{pro:#1}}
\newcommand{\theolab}[1]{\label{theo:#1}}
\newcommand{\theoref}[1]{\ref{theo:#1}}
\newcommand{\lemlab}[1]{\label{lem:#1}}
\newcommand{\lemref}[1]{\ref{lem:#1}}
\newcommand{\seclab}[1]{\label{sec:#1}}
\newcommand{\secref}[1]{\ref{sec:#1}}

\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\nor}[1]{\left\| #1 \right\|}
\newcommand{\jump}[1] {\ensuremath{[\![#1]\!]}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\Grad} {\ensuremath{\nabla}}
\newcommand{\Div} {\ensuremath{\nabla\cdot}}
\newcommand{\pO}{\partial \Omega}
\newcommand{\eval}[2][\right]{\relax
  \ifx#1\right\relax \left.\fi#2#1\rvert}

\newcommand{\A}{A}
\newcommand{\As}{A^\ast}
\newcommand{\HA}{H_\A}
\newcommand{\HAs}{H_{\As}}
\newcommand{\T}{T}
\renewcommand{\L}{L^2\LRp{\Omega}}
\newcommand{\Tt}{T^\ast}
\renewcommand{\B}{\mc{B}}
\newcommand{\M}{\mc{M}}
\newcommand{\Bs}{\mc{B}^\ast}
\newcommand{\Ms}{\mc{M}^\ast}
\newcommand{\V}{V}
\newcommand{\Vs}{\V^\ast}

\begin{document}
\baselineskip=16pt
\parskip= 4pt
%*************************************************page 1

%\input{project}
%\bibliography{./DPG,/home/leszek/ices/book3/references/Demkowicz}
%\bibliographystyle{plain}

\newpage

%\vspace*{.5cm}

\begin{center}

{\huge {\bf
The DPG Method\\[8pt] for Incompressible Flow Problems\\[8pt]
}}
\vspace*{1cm}

\vspace*{.5cm}
{\Large

 Nathan V. Roberts

\vspace*{.5cm}
Institute for
Computational Engineering and Sciences\\
The University of Texas at Austin, Austin, TX 78712, USA\\
}
\end{center}

%\begin{abstract}
%We discuss well-posedness and convergence theory for 
%the DPG method applied to a general system of linear Partial Differential
%Equations (PDEs) and specialize it to the classical Stokes problem.  The Stokes problem is an iconic troublemaker for standard Bubnov Galerkin methods; if discretizations are not carefully designed, they may exhibit non-convergence or locking.  By contrast, DPG does not require us to treat the Stokes problem in any special manner.  We illustrate and confirm our theoretical convergence estimates with numerical experiments.
%\end{abstract}

%{\bf Key words:}
%Discontinuous Petrov Galerkin, Stokes problem
%
%{\bf AMS subject classification:} 65N30, 35L15

\subsection*{Acknowledgments}
I have been supported by the Department of Energy [National Nuclear Security Administration] under Award Number
[DE-FC52-08NA28615].  I would like to thank my advisors, Leszek Demkowicz and Robert Moser, and the rest of my thesis committee---Todd Arbogast, George Biros, Thomas Hughes, and Venkatramanan Raman---for their support and guidance of my work.  I also thank Pavel Bochev and Denis Ridzal for
hosting and collaborating with me in the summers of 2010 and 2011, when I was supported by internships at Sandia National
Laboratories (Albuquerque).  I thank Tan Bui-Thanh and Jesse Chan for their continuing collaboration in various aspects of my research.

\subsection*{Provenance}
Some of the material in this document was originally developed in collaboration with others, some of which has been published in other contexts.  Specifically, the discussion of distributing the stiffness matrix computation in Appendix \ref{sec:CamelliaDetails} was written with Jesse Chan (but not published); portions of Sections \ref{sec:litreviewflow}, \ref{sec:proposedApproachDPG}, and \ref{sec:preliminaryResults} and Appendices \ref{sec:StokesAnalysis} and \ref{sec:StokesNumericalResults} were written with Tan Bui Thanh and Leszek Demkowicz \cite{DPGStokes}; some of the material regarding development and verification of Camellia in Appendix \ref{sec:CamelliaDetails} arose from a collaboration with Denis Ridzal and Pavel Bochev \cite{RobertsetAl11}.

\newpage
\tableofcontents
\newpage

\section{Introduction}
\paragraph{Motivation.} Incompressible flows---flows in which variations in the density of a fluid are not important to the physics---arise in a wide variety of applications, from hydraulics to aerodynamics.  The incompressible Navier-Stokes equations which govern such flows are also of fundamental physical and mathematical interest.  They are believed to hold the key to understanding turbulent phenomena; precise conditions for the existence and uniqueness of solutions remain unknown---and establishing such conditions is the subject of one of the Clay Mathematics Institute's Millennium Prize Problems.

Typical solutions of incompressible flow problems involve both fine- and large-scale phenomena, so that a uniform finite element mesh of sufficient granularity will at best be wasteful of computational resources, and at worst be infeasible because of resource limitations.  Thus adaptive mesh refinements are required.  In industry, the adaptivity schemes used are ad hoc, requiring a domain expert to predict features of the solution.  A badly chosen mesh may cause the code to take considerably longer to converge, or fail to converge altogether.  Typically, the Navier-Stokes solve will be just one component in an optimization loop, which means that any failure requiring human intervention is costly.

\paragraph{Goal.} Our aim is to develop a solver for the incompressible Navier-Stokes equations that provides robust adaptivity starting with a coarse mesh.  By robust, we mean both that the solver always converges to a solution in predictable time, and that the adaptive scheme is independent of the problem---no special expertise is required for adaptivity.

The cornerstone of our approach will be the discontinuous Petrov-Galerkin with optimal test functions (DPG) finite element methodology recently developed by Leszek Demkowicz and Jay Gopalakrishnan \cite{DPG1,DPG2}.  Whereas Bubnov-Galerkin methods use the same function space for both test and trial functions, Petrov-Galerkin methods allow the spaces for test and trial functions to differ.  In DPG, the test functions are computed on the fly and are chosen to minimize the residual.  For well-posed problems with sufficiently regular solutions, DPG can be shown to converge at optimal rates---the ``inf sup'' constants governing the convergence are mesh-independent, and of the same order as those governing the continuous problem \cite{DPGStokes}.  DPG also provides an accurate mechanism for \emph{measuring} (not merely estimating) the error, and this can be used to drive adaptive mesh refinements.

Several approximations to Navier-Stokes are of physical interest, and our approach will involve studying each of these in turn, culminating in the study of the 2D incompressible Navier-Stokes equations.  The Stokes equations can be obtained by neglecting the convective term; these are accurate for ``creeping'' viscous flows.  The Oseen equations replace the convective term, which is nonlinear, with a linear approximation.  The steady-state incompressible Navier-Stokes equations can be obtained by setting the time derivatives in the transient equations to zero.

We have studied DPG applied to the Stokes problem in some detail, with theoretical results predicting optimal rates of convergence, and numerical results that appear to show even more: it appears that we asymptotically approach the best approximation error available in the discrete space \cite{DPGStokes}.  Because of this success and the close relationship between the Stokes equations and the incompressible Navier-Stokes equations, we are optimistic that we can achieve good results with the latter as well.

Central to our study of these problems will be the use and further development of \emph{Camellia} \cite{RobertsetAl11}, a toolbox we developed for solving DPG problems which uses Sandia's Trilinos library of packages \cite{Trilinos}.   I began work on Camellia in collaboration with Denis Ridzal and Pavel Bochev during an internship at Sandia.\nocite{RobertsetAl10}  At present, Camellia supports 2D meshes of triangles and quads of variable polynomial order, provides mechanisms for easy specification of DPG variational forms, supports $h$- and $p$- refinements, and supports distributed computation of the stiffness matrix, among other features.  We hope to add support for meshes of arbitrary spatial dimension, support for space-time elements, and support for distributed mesh and solution representation---although it is not yet clear that these will be necessary for the central goal of the dissertation, it is clear that such features will be desirable.

\paragraph{Structure of the Proposal.} The structure of this document is as follows.  In Section \ref{sec:litreviewflow}, we review some relevant approaches in the literature on incompressible flow; in Section \ref{sec:litreviewFEM}, we discuss three popular FEM codes (\deal, libMesh, and FEniCS), for later comparison and contrast with Camellia.  In Section \ref{sec:proposedApproachDPG}, we describe some features of DPG and how we propose to exploit these in the context of incompressible flow problems.  In Section \ref{sec:proposedApproachCamellia}, we describe the proposed approach to designing FEM software that implements the DPG method (Camellia).  In Section \ref{sec:preliminaryResults}, we summarize the results of these approaches in the context of the Stokes problem.  We conclude in Section \ref{sec:conclusion} with an itemized list of contributions proposed for the dissertation.  Finally, appendices provide details of the work thus far accomplished: Appendix \ref{sec:StokesAnalysis} covers mathematical results for a DPG formulation of the Stokes problem; Appendix \ref{sec:CamelliaDetails} discusses the design, implementation, and verification of Camellia; numerical results for the Stokes problem are detailed in Appendix \ref{sec:StokesNumericalResults}.

\section{Literature Review: Incompressible Flow Problems}
\label{sec:litreviewflow}
In this section, we review the literature regarding numerical solutions of the Stokes, Oseen, and incompressible Navier-Stokes equations.  Some of the principal challenges of solving incompressible Navier-Stokes---in particular, its saddle-point character---can already be seen in the Stokes problem, and finite element discretizations and analysis for the Stokes problem often apply to Navier-Stokes as well.

First, though, we briefly state the incompressible transient Navier-Stokes equations, and each of the approximations to them that we will investigate.  The Navier-Stokes equations are:
\begin{align*}
- \NVRgrad p + \mu \Delta \vect{u} &= \pd{\vect{u}}{t} + \vect{u} \cdot \NVRgrad \vect{u} \\
\NVRdiv \vect{u} &= 0,
\end{align*}
where $p$ is the pressure, $\vect{u}$ is the velocity, and $\mu = \frac{1}{\rm Re}$ is the viscosity, assumed constant.  The first equation corresponds to the conservation of momentum; the second to conservation of mass.  We have neglected gravitational effects, and have taken density $\rho$ to be a constant, non-dimensionalized to equal 1.  These are the transient equations; with the steady-state assumption $\pd{\vect{u}}{t} = 0$ we get the steady equations:
\begin{align*}
- \NVRgrad p + \mu \Delta \vect{u} &= \vect{u} \cdot \NVRgrad \vect{u} \\
\NVRdiv \vect{u} &= 0.
\end{align*}

These are nonlinear thanks to the convective term $\vect{u} \cdot \NVRgrad \vect{u}$; if we approximate this by a linear term $\vect{U} \cdot \NVRgrad \vect{u}$, where $\vect{U}$ is the free-stream velocity, we have
\begin{align*}
- \NVRgrad p + \mu \Delta \vect{u} &= \vect{U} \cdot \NVRgrad \vect{u} \\
\NVRdiv \vect{u} &= 0,
\end{align*}
which are the Oseen equations.  If we neglect the convective term altogether we have
\begin{align*}
- \NVRgrad p + \mu \Delta \vect{u} &= \vect{0} \\
\NVRdiv \vect{u} &= 0,
\end{align*}
the Stokes equations with zero forcing function.

\paragraph{Stokes and Oseen.}
The Stokes equations model incompressible viscous (``creeping'') flow;
they can be derived by neglecting the convective term in the
incompressible Navier-Stokes equations.  Naive discretizations for the
Stokes problem can lead to non-convergence or locking
\cite{BoffiBrezziFortin}.  Of crucial importance for Bubnov-Galerkin
formulations of the Stokes equations---and more generally, of saddle
point problems---is the satisfaction of the two so-called Brezzi
inf-sup conditions \cite{Brezzi74}.  For the Stokes equations, the
first of these, the ``inf-sup in the kernel'' condition, is satisfied
automatically.  If the discrete spaces for velocity $\vect{u}$ and
pressure $p$ are $\vect{V}_{h} \subset \vect{H}^{1}$ and $Q_{h}
\subset L^{2}$, respectively, the second Brezzi condition for Stokes
is then
\[
\inf_{q \in Q_{h}} \sup_{v \in V_{h}} \frac{\left(q, \NVRdiv \vect{v} \right)}{\norm{q}_{L^{2}_{0}} \norm{\vect{v}}_{\vect{H}^{1}}} \geq \gamma_{h} \geq \gamma_{0} > 0.
\]
In the context of Stokes, this condition is often called the
Ladyzhenskaya-Babuska-Brezzi (LBB) condition, because Ladyzhenskaya
first proved the continuous analog of the condition for the Stokes
equations \cite{Ladyzhenskaya}; much of the challenge in solving
Stokes lies in the selection of discrete spaces that satisfy this
condition.

In \cite{BoffiBrezziFortin}, Boffi, Brezzi, and Fortin survey some
choices for finite element discretizations to satisfy the LBB
condition for the Stokes problem, among which are the MINI element,
Crouzeix-Raviart element, and the class of $Q_{k}-P_{k-1}$ elements.
Generalized Hood-Taylor elements can be shown to satisfy the condition
under certain regularity constraints on the mesh.  (Each of these
elements generalizes to three-dimensional spaces as well.)  It is worth
noting that each of these elements uses a polynomial approximation for
pressure of one order lower than that used for velocity, so that the
theoretical optimal convergence rate is lower for the pressure than it
is for the velocity.

Cockburn et al. have applied the local discontinuous Galerkin (LDG)
method \cite{Castillo00} to the Stokes problem
\cite{CockburnKanschatSchotzauSchwab03}; LDG derives its name from the
local elimination of some variables (in the case of Stokes, the
stresses)---by comparison with standard DG methods, the global solve
in LDG involves only about half as many unknowns, a significant
savings.  By means of carefully chosen numerical fluxes, the LDG
method can enforce conservation laws weakly element by element, in a
locally conservative way.  The method also allows one to choose spaces
for the pressure and velocity independently, so that
equal-order approximations can be used, but Cockburn et al. show that the convergence rate
for pressure and stress will be of order one less than that for
velocity.  They numerically compare the efficiency of using
lower-order approximations for pressure and stress with that of
equal-order approximations, and conclude that in most cases the
equal-order approximations are more efficient:
although both choices yield the same \emph{rate} of convergence, the
lower-order approximation requires more degrees of freedom to
achieve the same accuracy.

Cockburn et al. have also applied LDG to the Oseen equations by combining their LDG discretization of Stokes with a classical DG discretization of the convective term, with similarly good results---optimal-order convergence when the pressure space is discretized with polynomials of degree one less than that of the velocity, and the possibility of using equal-order approximations for all variables with improved efficiency \cite{Cockburn2002,LDGOseen}.  Their numerical experiments demonstrate success with Reynolds numbers from 1 to 1000. %It would be worth reading the Cockburn2002 reference in detail; I discovered it late in the game, and it does go into a lot more detail.  Also would be worth reading some of the things they cite in both articles in their literature review.

Building on work begun in Evans's PhD. thesis \cite{EvansThesis}, Evans and Hughes have applied their divergence-free B-splines to the Stokes equations, with excellent results: using equal-order velocity and pressure spaces, local conservation is automatic by virtue of the divergence-free basis used for the velocity, and in their experiments, pressure and velocity both converge at optimal\footnote{Evans and Hughes prove an optimal convergence rate of $k+1$ for the velocity; for the pressure, they prove a rate of at least $k$.  Their experiments show $k+1$ rates for both variables.} rates \cite{EvansHughesStokes}.

%\paragraph{Oseen.}
%LDG for Oseen \cite{LDGOseen}.
%
%Cockburn et al. have applied the LDG method to the Oseen problem as well.  
%
%What else?  (Original paper by Oseen?  I believe this is actually a book, ``Neuere Methoden und Ergebnisse in der Hydrodynamik,'' Leipzig 1927.)
%  
%  I'm a bit stuck finding other good sources.  May want to refer to textbooks, e.g. Panton.  Basic message is that the Oseen equations are linearized Navier-Stokes; they can be seen as a single Newton-Raphson step around a previous solution $\vect{u} = \vect{U}$ (I believe that's correct; I need to double-check it).  (So maybe the right thing is to search for linearized Navier-Stokes; not everyone may refer to Oseen.)
%  
%A mathematical treatment of the (transient!) linearized Navier-Stokes equations can be found here: http://people.oregonstate.edu/~thomanen/spin.pdf.  There is at least mention of Stokes and Oseen as well.

\paragraph{Navier-Stokes.}

In incompressible flows velocity and pressure are coupled by an incompressibility constraint, which leads to a saddle-point system that can be very sensitive to the discretization.  Guermond et al. review \emph{projection} methods for incompressible flows \cite{Guermond06}, which can also be viewed as fractional step methods, in that each time step is broken into partial steps.  These are attractive because they decouple the velocity and the pressure: at each time step, two elliptic equations need to be solved in sequence.  The methods fall into three broad classes: pressure-correction methods (such as that of Chorin \cite{Chorin68} and Temam \cite{Temam69.I,Temam69.II}), velocity-correction methods (such as that of Orszag et al. \cite{OrszagEtAl} or that of Karniadakis et al. \cite{KarniadakisEtAl}), and consistent splitting methods such as that of Guermond and Shen \cite{GuermondShen}.  The pressure- and velocity-correction methods introduce artificial boundary conditions which can induce numerical boundary layers, preventing the schemes from converging at optimal rates.  Consistent splitting schemes are schemes that split the time step in a way that does not introduce such artificial boundary conditions.  Guermond et al. cite numerical evidence indicating that the velocity- and pressure-correction schemes can have order 3 convergence for velocity and order $\frac{5}{2}$ convergence for pressure (measured in the $L^{2}$ norm), for time steps that are not too small relative to the spatial discretization.

Guermond and Minev have recently introduced a new dimensional splitting approach to solving the Navier-Stokes equations \cite{GuermondMinev2011}.  Noting that the Chorin-Temam method can be understood as solving a singular perturbation of the exact equations where the perturbation takes the form $-\epsilon \Delta p$, where $\epsilon$ is the size of the time step, they show that the Chorin-Temam scheme is one of a broad class of schemes that have similar convergence properties.  Another such scheme is the one they present in the paper, which has the advantage of being extremely cheap to compute: remarkably, it only requires solving a series of one-dimensional boundary-value problems.  The approach also is suitable for parallel implementation; in their experiments, they show that their implementation has a speedup close to the ideal one on up to 1000 processors.  As presented, the scheme only applies to simple domains discretized into axis-aligned parallelepipeds, although the authors do note in the conclusion several ideas for extending the scheme to more complex domains.

%Chorin 1968: In 1968, Chorin presented a numerical solution of the Navier-Stokes equations using a finite difference method, a projection method that the FEniCS book says is often referred to as a ``non-incremental pressure correction scheme.''  But Chorin says it's a finite difference method, whereas the FEniCS book seems to be talking about a finite element method.  The latter also attributes the scheme to Temam 1969, so maybe Temam took Chorin's FD method and made a FE method from it.  The key insight has to do with neglecting the pressure until late in the game, I think---maybe it's effectively about the way the system is linearized, so that it applies in both contexts.\footnote{The Temam reference has the title ``Sur l'approximation de la solution des Žquations de Navier-Stokes par la mŽthode des pas fractionnaires (I).''  I haven't found a translation.}  Rannacher has a 1992 paper on the Chorin projection method, with what may be a nice characterization of it (he says that the point is to deal with the saddle-point character arising from the incompressibility constraint).

%Rannacher's overview of Navier-Stokes and FEM.  \red{This may be a good reference to find out about the relationship between Stokes elements and inc. Navier-Stokes elements.  From what I've seen, it looks like the former are used for the latter.  Is there some simple way of seeing why?  Certainly it's clear that the two problems are closely related.}

%Something by Moser?

%Something by Jimenez?

Cockburn et al. have applied their LDG approach to the Navier-Stokes equations \cite{Cockburn2004, Cockburn2007}.  They note that while for many schemes for solving the Stokes and Oseen equations, weakly enforced incompressibility suffices in the proof of stability, the presence of the nonlinear convective term in the Navier-Stokes equations means that weak enforcement is insufficient.  They further note that the standard solution to this problem (due to Temam), which involves a modification of the nonlinearity of the equations, cannot be used in an LDG method because it cannot be rendered in divergence form and therefore would prevent local conservation.  The remedy they propose involves projecting the previous approximate solution for the velocity $\vect{u}_{h}$ into a divergence-free space; they then use this divergence-free velocity $\vect{w}$ as the convective velocity in the nonlinear term.  They thereby recover the previously studied Oseen problem, so that with the addition of an appropriate stabilization function, the stability of the method is guaranteed.  The result is a method that is locally conservative, stable, and converges at optimal rates for polynomial discretizations of arbitrary order.  They perform numerical experiments using a classical analytical solution due to Kovasznay \cite{Kovasznay}.  They report success in numerical experiments solving for an analytical solution with Reynolds numbers between 1 and 100; for Reynolds numbers of 1000, they report that the nonlinear iteration does not converge, and hypothesize that this is due to instability in the stationary problem for such Reynolds numbers.

Evans and Hughes have likewise applied their divergence-free B-splines to the steady and unsteady Navier-Stokes equations \cite{EvansHughesSteadyNavierStokes,EvansHughesUnsteadyNavierStokes}, again with excellent results.  They have successfully applied steady Navier-Stokes to the driven cavity problem at Reynolds numbers up to 1000; they report success in other steady flow computations with Reynolds numbers upwards of 3200.  They argue that the fact that most numerical methods only satisfy the incompressibility constraint approximately means that these do not obey fundamental laws of physics, including energy conservation, the failure of which can be shown to lead to numerical instability.  By contrast, they demonstrate that their discretizations conserve momentum and satisfy balance laws for energy, vorticity, enstrophy, and helicity.

%red{expanded on in \cite{Cockburn2007})}

%There's a nice review of DNS as a research tool for understanding turbulence (Moin and Mahesh 1998).  This may provide a nice skeleton to hang any other literature review on.  But then again, it may be too much about turbulence.  I'm not sure.  It doesn't treat Chorin, e.g.---and every paper cited (it seems) h as to do with turbulent flows.  There are complexities in turbulent flows that may not affect other flows, and I'm only aiming at the laminar regime.  I don't see any reason why I couldn't handle turbulent phenomena as well---not turbulence modeling, but DNS---except maybe computational cost.  But let's get the laminar stuff working first!

% Doering's review of the state of our knowledge of the mathematical structure of the 3D Navier-Stokes equations \cite{Doering2009}.

\section{Three Popular FEM Codes: deal.II, libMesh, and FEniCS}
\label{sec:litreviewFEM}
In this section, we examine three popular object-oriented libraries for doing finite element computations.  We begin with a somewhat extended discussion of \deal \cite{BangerthKanschat99}, because it is similar to our own approach in Camellia (see Section \ref{sec:proposedApproachCamellia}) and because it preceded libMesh and FEniCS.  We then highlight some features of libMesh \cite{Kirk2006} and FEniCS \cite{fenics:book}.

\paragraph{\deal.}
\deal is designed for flexibility, ease of use, efficiency, and safety.  It is flexible in that it is possible, without too much effort, to vary choices for finite element spaces, spatial dimension, variational formulations, and linear solvers.  The ease of use comes largely by virtue of encapsulation: details of complex data storage structures are hidden from the user.  Safety is provided by means of runtime parameter checking, which allows programming errors to be detected early.  \deal also boasts extensive documentation (5000 pages if printed, they claim), with many implementation examples available on the \deal website.\footnote{http://www.dealii.org}

It is worth noting that \deal is quite \emph{mature}; the initial DEAL code was developed between 1993 and 1997; \deal was conceived as a rewrite, begun in 1997, and it has continued to be used, extended, and maintained since then.  The LDG work cited in Section \ref{sec:litreviewflow} (\cite{CockburnKanschatSchotzauSchwab03,LDGOseen,Cockburn2004,Cockburn2007}), for example, uses \deal for its numerical experiments.  Also, it is possible to implement DPG methods using \deal; in our research group, Jamie Bramwell is using it in her work on linear elasticity.

Several of \deal's classes are templated on the spatial dimension, making it a relatively simple matter to write dimensionally-independent code.  \deal supports \emph{hypercube} topologies in 1, 2, and 3 space dimensions: lines, quads, and hexahedra, with a variety of finite elements supported on these: continuous and discontinuous Lagrange elements, as well as Nedelec and Raviart-Thomas elements.  Arbitrary polynomial orders are supported for each of these element types.

\deal allows $h$-, $p$-, and $hp$-adaptive meshes; both anisotropic and isotropic mesh refinements are supported.  The meshes are hierarchical: refined (child) cells are nested inside (parent) cells belonging to the previous mesh.  Recently, support has been added for distributing \deal meshes using \code{p4est} \cite{dealiiwithp4est}, a library for parallel adaptive mesh refinement on forests of octrees \cite{p4est}, which boasts scalability to hundreds of thousands of processor cores.

A consequence of using adaptively refined hierarchical meshes is that refined meshes will usually contain \emph{hanging nodes}---faces where one neighbor has been refined and another has not; see Figure \ref{fig:hangingNode}.  If elements $K_{1}$, $K_{2}$, and $K_{3}$ are all linear Lagrangian elements, then along the shared edge, $K_{2}$ and $K_{3}$ define a space containing all (continuous) functions that are linear along the smaller edges AB and BC, while $K_{1}$ only contains functions that are linear along the larger edge AC.  \deal addresses this by means of constraints on the spaces for $K_{2}$ and $K_{3}$, which are incorporated into the final linear problem in a way that will preserve the symmetry and positivity of the stiffness matrix, if the unconstrained stiffness matrix has those features.

Finite element spaces are represented by the \code{FE} class within \deal---this provides shape functions and their derivatives on the reference cell, when the spaces are defined on a reference cell; otherwise, the functions are provided on physical cells.  The \code{FE} class is, however, not typically used directly by application developers; noting that most finite element developers will only be interested in the \emph{values} of shape functions and their derivatives at particular points (e.g. quadrature points), \deal provides an interface to such values in the \code{FEValues} class.  This class handles the transformation of values from reference to physical space, such as the Piola transform.\footnote{Camellia provides this functionality, among other things, within its \code{BasisCache} class.  See Section \ref{sec:proposedApproachCamellia}.}

\paragraph{libMesh.}  libMesh \cite{Kirk2006} is another finite element library; it was in fact inspired by \deal; as the name suggests, libMesh pays particular attention to the mesh---the \code{Element} class is designed to be subclassed with new elements, and a wide variety of elements are provided.  In 2D, both triangle and quad elements are provided; in 3D, hexahedra, tetrahedra, prisms, and pyramids are provided, as well as a collection of infinite elements.  $hp$-adaptivity is supported for all element types.  Support for distributed stiffness matrix computation and assembly is provided.  At present, a copy of the data structures defining the mesh must be stored on each node; development of a \code{ParallelMesh} class is underway, which will support distributed mesh storage.\footnote{See \url{http://libmesh.sourceforge.net/doxygen/classlibMesh_1_1ParallelMesh.php}.} %I believe only isotropic refinements are supported.  Not sure if that's worth mentioning.

\paragraph{FEniCS.}  The FEniCS project \cite{fenics:book} aims at highly automated solution of finite element problems; the authors emphasize the simplicity with which finite element solvers can be implemented.  The only topologies currently supported are simplices: intervals in 1D, triangles in 2D, and tetrahedra in 3D.  On these topologies, many standard finite element types are supported---most of these support polynomials of arbitrary order.  The DOLFIN library \cite[Chapter 10]{fenics:book} provides the main user interface to FEniCS; this generates C++ code from variational forms specified by the user in the Unified Form Language (UFL) \cite[Chapter 17]{fenics:book}---the developers aim thereby to achieve simplicity of specification while maintaining performance.  Both C++ and Python interfaces are supported; some features are only available using the Python interface.

\section{Proposed Approach: DPG for Incompressible Flow}
\label{sec:proposedApproachDPG}
\paragraph{The Discontinuous Petrov-Galerkin Method with Optimal Test Functions.} We begin with a short historical review of the method.  By a discontinuous Galerkin (DG) method, we mean one that allows test and/or trial functions that are not globally conforming; by a Petrov-Galerkin method, we mean one that allows the test and trial spaces to differ.  In 2002, Bottasso et al. introduced a method \cite{BottassoMichelettiSacco02, BottassoMichelettiSacco05}, also called DPG.  Like our DPG method, theirs used an ``ultra-weak'' variational formulation (moving all derivatives to test functions) and replaced the numerical fluxes used in DG methods to ``glue'' the elements together with new independent unknowns defined on element interfaces.  The idea of optimal testing was introduced by Demkowicz and Gopalakrishnan in 2009 \cite{DPG1}, which is distinguished by an on-the-fly computation of an approximation to a set of test functions that are optimal in the sense that they guarantee minimization of the residual in the dual norm.  In 2009-2010, a flurry of numerical experimentation followed, including applications to convection-dominated diffusion \cite{DPG2}, wave propagation \cite{DPG4}, elasticity \cite{DPG1023}, thin-body (beam and shell) problems \cite{NiemiBramwellDemkowicz10}, and the Stokes problem \cite{RobertsetAl10}.  The wave propagation paper also introduced the concept of an \emph{optimal test norm}, whose selection makes the energy norm identical to the norm of interest on the trial space.  In 2010, Demkowicz and Gopalakrishnan proved the convergence of the method for the Laplace equation \cite{DPG6}, and Demkowicz and Heuer developed a systematic approach to the selection of a test space norm for singularly perturbed problems \cite{DemkowiczHeuer}. In 2011, Bui-Thanh et al. \cite{Bui-ThanhDemkowiczGhattas11b} developed a unified analysis of DPG problems by means of Friedrichs' systems.  Our analysis for the Stokes problem, presented here in Appendix  \ref{sec:StokesAnalysis} builds on the existence of trace spaces and proceeds along a more classical path, connecting to Banach's theory of closed operators.

Some work has been done on nonlinear problems as well.  Very early on, Chan, Demkowicz, and Roberts solved the 1D Burgers and compressible Navier-Stokes equations by applying DPG to the linearized problem \cite{DPG5}.  More recently, Moro et al. have applied their related HDPG method to the 2D Burgers equation; a key difference in their work is that they apply DPG to the \emph{nonlinear} problem, using optimization techniques to minimize the DPG residual.
%---we hope to pursue similar ideas in our own research on nonlinear problems.

Most DPG analysis assumes that the optimal test functions are computed exactly, but in practice we must approximate them.  Gopalakrishnan and Qiu have shown that for the Laplace equation and linear elasticity, for sufficiently high-order approximations\footnote{$k_{\rm test}=k_{\rm trial}+N$, where $N$ is the number of space dimensions, and by $k_{\rm test}$ we mean the polynomial order of the basis functions for the test space, and by $k_{\rm trial}$ we mean the order for the $L^{2}$ bases in the trial space.} of the test space, optimal convergence rates are maintained \cite{GopalakrishnanQiu11}.

We will now briefly derive DPG, motivating it as a minimum residual method.  Suppose that $U$ is the trial space, and $V$ the test space (both Hilbert) for a well-posed variational problem $b(u,v) = l(v)$.  Writing this in the operator form $Bu = l$, where $B : U \rightarrow V'$, we seek to minimize the residual for the discrete space $U_{h} \subset U$:
\begin{align*}
u_{h} = \underset{u_{h} \in U_{h}} \argmin \,\, \frac{1}{2} \norm{Bu_{h}-l}_{V'}^{2}.
\end{align*}
Now, the dual space $V'$ is not especially easy to work with; we would prefer to work with $V$ itself.  Recalling that the Riesz operator $R_{V} : V \rightarrow V'$ defined by 
\begin{align*}
\langle R_{V}v, \delta v\rangle=(v,\delta v)_{V}, \quad \forall \delta v \in V,
\end{align*}
where $\langle \cdot, \cdot \rangle$ denotes the duality pairing
between $V'$ and $V$, is an \emph{isometry}---that is,
$\norm{R_{V}v}_{V'} = \norm{v}_{V}$---we can rewrite the term we want
to minimize as a norm in $V$:
\begin{align} \label{NVR:eqn:resNormSquared}
\frac{1}{2} \norm{Bu_{h}-l}_{V'}^{2} = \frac{1}{2} \norm{R_{V}^{-1}\left(Bu_{h}-l\right)}_{V}^{2} = \frac{1}{2} \left(R_{V}^{-1}\left(Bu_{h}-l\right), R_{V}^{-1}\left(Bu_{h}-l\right) \right)_{V}.
\end{align}
The first-order optimality condition requires that the G\^ateaux derivative of (\ref{NVR:eqn:resNormSquared}) be equal to zero for minimizer $u_{h}$; we have
\begin{align*}
\left(R_{V}^{-1}\left(Bu_{h}-l\right), R_{V}^{-1}B \delta u_{h} \right)_{V} = 0, \quad \forall \delta u_{h} \in U_{h}.
\end{align*}
By the definition of $R_{V}$, the preceding equation is equivalent to
\begin{equation}
\label{eqn:optTest}
\langle Bu_{h} - l, R_{V}^{-1}B \delta u_{h} \rangle = 0 \quad \forall \delta u_{h} \in U_{h}.
\end{equation}
Now, if we identify $v_{\delta u_{h}} = R_{V}^{-1}B \delta u_{h}$ as a test function, we can rewrite \eqref{eqn:optTest} as
\begin{align*}
%\langle Bu_{h} - l, v_{\delta u_{h}} \rangle &= 0 \\
%\langle Bu_{h}, v_{\delta u_{h}} \rangle &= \langle l, v_{\delta u_{h}} \rangle \\
b(u_{h},v_{\delta u_{h}}) &= l(v_{\delta u_{h}}).
\end{align*}
Note that the last equation is exactly the original variational form,
tested with a special function $v_{\delta u_{h}}$ that corresponds to $\delta u_{h} \in
U_{h}$; we call $v_{\delta u_{h}}$ an \emph{optimal test function}. The DPG method
is then to solve the problem $b(u_{h},v_{\delta u_{h}}) = l(v_{\delta
  u_{h}})$ with optimal test functions $v_{\delta u_{h}} \in V$ that solve the
problem
\begin{align}
\label{NVR:eqn:testFunctionProblem}
 (v_{\delta u_{h}}, \delta v)_{V} = \langle R_{V}v_{\delta u_{h}}, \delta v \rangle = \langle B \delta u_{h}, \delta v \rangle =  b(\delta u_{h}, \delta v), \quad \forall \delta v \in V.
\end{align}
In standard conforming methods, test functions are continuous over the
entire domain, which would mean that solving
(\ref{NVR:eqn:testFunctionProblem}) would require computations on the
global mesh, making the method impractical.  In DPG, we use test
functions that are discontinuous across elements, so that
(\ref{NVR:eqn:testFunctionProblem}) becomes a local problem---that is, it can
be solved element-by-element.  Of course,
(\ref{NVR:eqn:testFunctionProblem}) still requires inversion of the
infinite-dimensional Riesz map, and we approximate this by using an
``enriched'' test space $V_{h}$ of polynomial order higher
than that of the trial space $U_{h}$.  Note that the test functions
$v_{\delta u_{h}}$ immediately give rise to a hermitian positive
definite stiffness matrix; if $\{e_{i}\}$ is a basis for $U_{h}$, we
have:
 \begin{align*}
b(e_{i},v_{e_{j}}) = (v_{e_{i}},v_{e_{j}})_{V} =  \overline{(v_{e_{j}}, v_{e_{i}})}_{V} = \overline{b(e_{j},v_{e_{i}})}.
\end{align*}

It should be pointed out that we have not made any assumptions about
the inner product on $V$.  An important point is that by an
appropriate choice of test space inner product, the induced energy
norm on the trial space can be made to coincide with the norm of
interest \cite{DPG4}; DPG then delivers the best approximation error
in that norm.  In practice this optimal test space inner product is
approximated by a ``localizable'' inner product, and DPG delivers the
best approximation error up to a mesh-independent constant.  That is,
\begin{align*}
\norm{u-u_{h}}_{U} \leq \frac{M}{\gamma_{DPG}} \inf_{w_{h} \in U_{h}} \norm{u-w_{h}}_{U},
\end{align*}
where $M=O(1)$ and $\gamma_{DPG}$ is mesh-independent, and $\gamma_{DPG}$ is of the order of inf-sup constants for the strong operator and its adjoint (see Appendix \ref{sec:StokesAnalysis}).  We therefore say that DPG is \emph{automatically stable}, modulo any error in solving for the test functions $v_{\delta u_{h}}$.

It is a relatively simple matter, when desired, to enforce \emph{local conservation}---that is, an element-wise property that corresponds to a (mass) conservation law---by means of Lagrange multipliers.  This was first noted by Moro et al. \cite{MoroNguyenPeraire11}.  This is often useful in the context of practical fluid problems.  We have not yet, however, explored combining DPG with local conservation in any great detail.  In the numerical examples presented in Section \ref{sec:preliminaryResults}, local conservation was not enforced, but it appears from our limited experimentation to have negligible effect in the context of these examples.

\paragraph{Application to Nonlinear Problems.} Here, we develop an abstract formulation for DPG applied to nonlinear problems.  Note that the discussion above through (\ref{NVR:eqn:resNormSquared}) makes no assumption that operator $B$ is linear; for a nonlinear $B$ the first-order optimality condition gives us
\begin{align*}
\left(R_{V}^{-1}\left(Bu_{h}-l\right), R_{V}^{-1}B'(u_{h},\delta u_{h}) \right)_{V} = 0, \quad \forall \delta u_{h} \in U_{h}.
\end{align*}
where $B'(u_{h},\delta u_{h})$ is the G\^ateaux derivative of $B$ at $u_{h}$ in direction $\delta u_{h}$.  Continuing in much the same way as above, we have
\begin{align}
\label{eqn:nonlinearDuality}
\langle Bu_{h} - l, R_{V}^{-1}B'(u_{h},\delta u_{h}) \rangle = 0 \quad \forall \delta u_{h} \in U_{h}.
\end{align}
Now, we can again identify $v_{\delta u_{h}} = R_{V}^{-1}B'(u_{h},\delta u_{h})$ as a test function and note that
\begin{align*}
b(u_{h},v_{\delta u_{h}}) &= l(v_{\delta u_{h}}),
\end{align*}
but notice that now $v_{\delta u_{h}}$ also depends on the solution $u_{h}$.  Linearizing about $u_{h} + \Delta u_{h}$, we have
\begin{align*}
B(u_{h} + \Delta u_{h}) \approx Bu_{h} + B'(u_{h},\Delta u_{h})
\end{align*}
and
\begin{align*}
B'(u_{h} + \Delta u_{h},\delta u_{h}) \approx B'(u_{h},\delta u_{h}) + B''(u_{h},\delta u_{h},\Delta u_{h})
\end{align*}
so that (\ref{eqn:nonlinearDuality}) becomes
\begin{align*}
\langle Bu_{h} + B'(u_{h},\Delta u_{h}) - l, R_{V}^{-1}\left( B'(u_{h},\delta u_{h}) + B''(u_{h},\delta u_{h},\Delta u_{h}) \right)) \rangle = 0 \quad \forall \delta u_{h} \in U_{h}.
\end{align*}
Dropping the terms that are second order in $\Delta u_{h}$ and defining $v_{\delta u_{h}} = R_{V}^{-1}B'(u_{h},\delta u_{h})$, we have
\begin{align*}
\langle Bu_{h} - l, v_{\delta u_{h}} \rangle + \langle Bu_{h} - l, R_{V}^{-1}B''(u_{h},\delta u_{h},\Delta u_{h}) \rangle + \langle B'(u_{h},\Delta u_{h}),  v_{\delta u_{h}} \rangle = 0.
\end{align*}
The term involving $R_{V}^{-1}B''(u_{h},\delta u_{h},\Delta u_{h})$ is awkward, since it involves both the Riesz inversion and the linear unknown $\Delta u_{h}$.  We can rewrite this term, moving the Riesz operator onto the nonlinear residual:
\begin{align*}
\langle Bu_{h} - l, R_{V}^{-1}B''(u_{h},\delta u_{h},\Delta u_{h}) \rangle &= \left( R_{V}^{-1} (Bu_{h} - l), R_{V}^{-1}B''(u_{h},\delta u_{h},\Delta u_{h}) \right)_{V} \\
&= \langle B''(u_{h},\delta u_{h},\Delta u_{h}), R_{V}^{-1} (Bu_{h} - l) \rangle.
\end{align*}
Defining $v_{u_{h}} = R_{V}^{-1} (Bu_{h} - l)$, the linearized problem is then
\begin{align*}
b'(u_{h},\Delta u_{h}; v_{\delta u_{h}}) + b''(u_{h},\delta u_{h}, \Delta u_{h}; v_{u_{h}}) = - b(u_{h}, v_{\delta u_{h}}) + l(v_{\delta u_{h}}).
\end{align*}
It is worth noting that the above is somewhat different from our previous approach to nonlinear problems, in that here we minimize the nonlinear residual instead of the residual of the linearized problem.  The present approach results in the introduction of the hessian term.  Because the nonlinear residual is the one we are actually interested in minimizing, we believe that the new approach will produce better results (faster convergence of the nonlinear iteration) than the old; however, we have not yet used it in any computations.  Also, whereas the previous approach retained a symmetric positive definite stiffness matrix in the linear problem, here the hessian term might make the linear operator non-positive if the nonlinear residual is large (because $v_{u_{h}}$ depends on that); the stability of the linear solve might suffer as a result.

\paragraph{Adaptive Strategy for Linear Problems.}
While other methods typically employ a posteriori error \emph{estimators}, DPG allows the error to be computed precisely.  This makes for a simpler, more efficient and more robust adaptivity strategy.  When refining a mesh, the key question is where in the mesh the greatest error lies.  DPG provides a precise measurement of the error in the dual norm:
\begin{align*}
\norm{Bu_{h}-l}_{V'} = \norm{R_{V}^{-1}(Bu_{h}-l)}_{V}.
\end{align*}
If we then define an error representation function $e=R_{V}^{-1}(Bu_{h}-l) \in V$, we can solve
\begin{align*}
(e,\delta v)_{V} = b(u_{h},\delta v) - l(\delta v), \quad \forall \delta v \in V,
\end{align*}
locally for $e$.  We use $\norm{e_{K}}_{V}=\norm{Bu_{h}-l}_{V'(K)}$ on each element $K$ to drive adaptive mesh refinements.

At present, we use a simple $h$-refinement strategy:
\begin{enumerate}
\item Loop through the elements, determining the maximum element error $\norm{e_{K{\rm max}}}_{V}$.
\item Refine all elements with error at least 20\% of the maximum $\norm{e_{K{\rm max}}}_{V}$.
\end{enumerate}
The analysis and our software implementations support $p$- and $hp$-refinements as well.  $p$-adaptivity can employ a strategy similar to the above.  We do not yet have a well-defined strategy for deciding between $h$- and $p$-refinements once we have decided that a given element should be refined, but in Section \ref{sec:preliminaryResults} we include some results for Stokes flow with the $h$-refinement scheme above as well as an ad hoc $hp$-scheme.

\paragraph{Adaptive Strategies for Nonlinear Problems.}  When using an adaptive mesh for a nonlinear problem, we have two loops: the refinement loop and the nonlinear iteration.  This gives us two basic choices.  We can either hold the mesh fixed and iterate through Newton-Raphson steps, or we can first resolve the linearized problem through mesh refinement and only then proceed to the next Newton-Raphson step.  One can also imagine hybrid choices, in which the requirement for resolution of the linear problem is more relaxed for early Newton-Raphson steps, becoming stricter when the nonlinear problem is nearly resolved.

Some early experiments led us to the conclusion that refining outside the nonlinear iteration is computationally cheaper.  We did not have support for mesh coarsening in the code we were using at the time; having such support could change the balance.  We do not currently have mesh coarsening in Camellia, but we do not believe it will be difficult to add, and it may prove quite useful for nonlinear problems---therefore, we expect to add it in the near future.

\paragraph{Strategy for Transient Problems.} We would like ultimately to apply DPG to the transient Navier-Stokes equations.  The usual practice for transient problems is \emph{time-stepping}, in which first a solution is found at an initial time $t=t_{0}$; the solution at $t=t_{0} + \Delta t$ is then found, via either an implicit or an explicit method, in terms of the solution at the previous time step(s).  One of the questions that must be answered in time-stepping methods is how big a time step to take; implicit methods are generally preferred because they allow accurate results with larger time steps.

%Even for steady-state problems, it can be useful to introduce an artificial transient term and march in time until a steady-state is reached---often such an approach will be less sensitive to the initial guess.

There is no reason that standard time-stepping approaches would not work well with DPG, and these may have practical advantages.  However, for our initial efforts in transient problems, we plan instead to use \emph{space-time} finite elements, in which the time dimension is treated much as the spatial dimensions are---the only difference is that degree of freedom coefficients are only stored for a single ``time slab,'' which keeps the problem size tractable.  The great advantage of this is that the entire DPG apparatus can be brought to bear on the problem as a whole: with a well-chosen test space norm and a well-posed linear problem, we can guarantee optimal convergence rates; for both linear and nonlinear problems, we can measure the error and use this to drive adaptivity in both space and time.  The latter means that the question of time step size will be answered for us automatically, and in a heterogeneous fashion: in areas of small error, the ``time steps'' will remain coarse; in areas with larger error, they will be refined.

%Looking further forward to very large problems, one limitation of time-stepping methods is that they are by their nature \emph{sequential}; the solution at $t=t_{k}$ must be found before it can be found at $t=t_{k+1}$.  Although finding the solution at a given time step may be perfectly scalable, essentially each processor must go through the whole time series, and that cost may become the bottleneck.  By contrast, a space-time approach allows the solution to be computed through the entire time domain at once, so that each processor might be responsible only for a small piece of the time domain.  Thus space-time elements may allow us to take better advantage of growing computational resources.\footnote{Thanks to Jean-Luc Guermond for making this point in a private conversation.}

\section{Proposed Approach: DPG Software Design}
\label{sec:proposedApproachCamellia}

In this section, we describe \emph{Camellia}, a C++ toolbox for rapid development of DPG solvers, implemented atop Sandia's Trilinos library of packages \cite{Trilinos}.  The essential design goal for Camellia is to make DPG research and experimentation as simple as possible, without sacrificing too much by way of performance.  Our ideal is to write code that expresses the DPG formulation---the variational form and the inner product on the test space---in a way that makes the mathematics transparent, and requires minimal overhead beyond this to specify and solve problems.  We aim at excellent software design, following software engineering principles such as encapsulation and using tests and parameter checking to verify the code on an ongoing basis.

The goal of the present section is to provide a broad overview of Camellia, putting it in context by comparison to \deal.  Further details can be found in Appendix \ref{sec:CamelliaDetails}.  We begin with some general comments, and then focus, by way of example, on three specific design details: the use of the Factory design pattern throughout the code, how basis values are treated in Camellia, and how hanging nodes are handled.

\begin{figure}[h]
\centering
\includegraphics[scale=0.75]{./fig/hangingNode.eps}
\caption{Schematic of a hanging node: the element on the right has been refined, resulting in a ``broken'' edge along the right side of the coarse element $K_{1}$.
}
\label{fig:hangingNode}
\end{figure}

Because we focus on implementing DPG solvers, we can make certain simplifying assumptions.  We can assume a first-order system with all derivatives moved onto test functions.  We can assume that trial space variables defined on element interiors are discontinuous across element boundaries; the inter-element ``connectivity'' is limited to fluxes and traces, which are defined only on the element boundaries.  The latter allows some flexibility in dealing with hanging nodes.

Camellia aims at a higher level of abstraction than does \deal; for instance, Camellia does not require the user to write a loop over the elements in the mesh to compute the stiffness matrix.  In fact, the user need not be directly aware of the stiffness matrix at all.  There is a tradeoff here: while this has obvious advantages in that the code is generally simpler and easier to write, if the user wishes to do something special with the stiffness matrix, she might find that it is not as obvious how to do so in Camellia as it is in \deal.  In Camellia, specification of variational forms and test space inner products hews quite closely to the mathematics; for instance, the code snippet below specifies:
\begin{itemize}
\item a field trial variable $u \in L^{2}$,
\item a trace trial variable $\widehat{u} \in H^{1/2}$,
\item a test variable $\vect{v} \in \NVRHdiv$,
\item a bilinear form $b(u,v) = -\int_{\Omega} u \NVRdiv \vect{v} + \int_{\partial \Omega} \widehat{u} \vect{v} \cdot \vect{n} $, and
\item a test space norm $\norm{\vect{v}}_{V}^{2} = \norm{\vect{v}}_{L^{2}}^{2} + \norm{\NVRdiv \vect{v}}_{L^{2}}^{2}$.
 \end{itemize}

\begin{lstlisting}
  VarFactory varFactory; 
  // define field variable u
  VarPtr u = varFactory.fieldVar("u");
  // define flux variable u_hat
  VarPtr u_hat = varFactory.traceVar("\\widehat{u}");
  // define test function v
  VarPtr v = varFactory.testVar("v", HDIV); 
  // create bilinear form
  BFPtr bilinearForm = Teuchos::rcp( new BF(varFactory) );
  // specify field variable term
  bilinearForm->addTerm(-u, v->div());
  // specify flux variable term
  bilinearForm->addTerm(u_hat, v->dot_normal());
  // create test space inner product
  IPPtr innerProduct = Teuchos::rcp(new IP);
  // add L^2 term
  innerProduct->addTerm(v);
  // add divergence term
  innerProduct->addTerm(v->div());
\end{lstlisting}

Our approach in Camellia can perhaps be seen as falling somewhere between \deal and FEniCS---the specification of variational forms is at least vaguely reminiscent of FEniCS's UFL, but we are not going so far as to provide a domain-specific language and C++ code generation for that language.  We do include some basic operator overloading to allow expressions in variational forms such as \code{sinx * u1 + cosy * u2}, where \code{sinx} and \code{cosy} are user-supplied pointers to a \code{Function} class instance.

At present, Camellia supports only two spatial dimensions, and has no direct support for a time domain.  We do hope to add support for one, two, and three space dimensions, as well as extrusion of any of these in a time dimension to create space-time elements.  In 2D, Camellia supports both quads and triangles; our hope is to support at least hexahedra and tetrahedra (and perhaps pyramids and prisms) in 3D.  This is in contrast to \deal, which for the sake of simplicity of the code supports only hypercube elements, and FEniCS, which supports only simplicial elements.

One of the great advantages of DPG is that we can \emph{measure}, not merely estimate, the error in the dual norm $\norm{\cdot}_{V'}$, which is exactly the natural norm from a mathematical point of view (of course it is up to the analyst to specify $\norm{\cdot}_{V}$ well).  We can use this to drive adaptivity, and because this depends simply on the choice of norm $\norm{\cdot}_{V}$, the user need not implement an error indicator.  At present, we support both $h$- and $p$-adaptivity; $hp$-refinements are also possible, although we do not yet have a general strategy for deciding between $h$ and $p$.  Similarly, the infrastructure for refinements could easily be extended to support anisotropic refinements, but we do not yet have a strategy for deciding the best refinement direction.  Some examples using adaptivity are discussed in Section \ref{sec:preliminaryResults} and Appendix \ref{sec:StokesNumericalResults}.

Camellia supports distributed computation of the stiffness matrix; because the computation of optimal test functions is a local problem, this scales perfectly.  We do not yet support distributed storage of the mesh or solution---a copy of each is stored on each processor---although we do hope to add both.  Currently, we use KLU and MUMPS solvers, which are both direct solvers; MUMPS is a parallel solver.  Camellia implements an abstract \code{Solver} interface, by which users can add linear solvers of their own choosing.  (Determining good preconditioners for DPG stiffness matrices is an area of active research.)  Detailed discussion of the distribution of the stiffness matrix and some measurements of the scalability of various parts of the code can be found in Appendix \ref{sec:CamelliaDetails}.

\paragraph{The Factory Design Pattern.}
Camellia represents each basis function that corresponds to a trial or test space variable on a given cell using an instance of Intrepid's \code{Basis} class.  If each cell in the mesh were to store a \code{Basis} object for each basis, that would be a waste both of memory and the time required to construct the objects.  For this reason, we make use of the \emph{Factory} design pattern, which encapsulates object construction---in this instance, we want only to create each basis once on each compute node (to be precise, this is the FlyWeightFactory design pattern \cite[p. 199]{GoFBook}).  When the \code{BasisFactory} receives a request for a basis belonging to a given function space (e.g. \NVRHdiv) on a given cell topology (e.g. a triangle) with a given polynomial order (e.g. 5), it looks up this combination of features in a hash map; if such a basis already exists, a pointer to it is returned; if it does not exist, it is created and stored, and a pointer to it is returned.

Discrete spaces in Camellia are represented by the \code{DofOrdering} class,\footnote{We are considering renaming this class \code{DiscreteSpace}.} and the combination of trial space and test space for an element comprise the \code{ElementType}.  Just as with \code{Basis}, the Factory pattern is applied in \code{DofOrderingFactory} and \code{ElementTypeFactory}.

It is worth noting that the Factory classes will not generally be used directly by users.  Creation of \code{DofOrdering}s and \code{ElementType}s is generally handled by the \code{Mesh} class; \code{Basis} instances are usually requested by the \code{DofOrderingFactory} and assigned to the \code{DofOrdering}.

\paragraph{Basis Values: \deal's \code{FEValues} compared with Camellia's \code{BasisCache}.}
Finite element computations often make use of a \emph{reference} cell; values of shape functions and derivatives are computed on the reference cell and  transformed to appropriate values in physical space.  The values of interest are usually at specific points; most commonly these are quadrature points.  Both \deal and Camellia include classes---\code{FEValues} and \code{BasisCache},\footnote{Because \code{BasisCache} has evolved somewhat to include additional features relating to the computational context---e.g., it can optionally store a list of the cell IDs currently being operated on---we are considering renaming it \code{ContextCache}.} respectively---that take advantage of this fact to reduce development effort and speed execution.

Both classes compute values in reference space and provide transformations into physical space.  Now, not all the basis function values will be of interest for a given computation---derivative values might not be required, for example, and it would be wasteful to compute them in such a case.  \deal allows the user to specify that such values are not required so that they will not be computed.  Camellia's approach is \emph{lazy} computation of all values: the first time, for example, the derivative values for a basis are requested, these will be computed at all the points of interest, and stored.

It is also worth noting that, while \deal's \code{FEValues} class is tied to a particular element type, \code{BasisCache} is a bit more flexible.  \code{BasisCache} will return values for any requested basis; it is possible to do so efficiently because all bases are created using the \code{BasisFactory}, as described above.  \code{BasisCache} uses the memory address of the \code{Basis} object as an index into its lookup tables.  Generally speaking, a \code{BasisCache} instance will be relatively short-lived in Camellia, but many methods do take a \code{BasisCache} pointer as an argument, so that basis values computed in one part of the code might easily be reused in a completely separate part of the code.

\begin{figure}[h!b!p!]
\centering
\includegraphics[scale=0.75]{./fig/hangingNode2irreg.eps}
\caption{Schematic of a 2-irregular mesh.
}
\label{fig:hangingNode2irreg}
\end{figure}

\paragraph{Treatment of Hanging Nodes: \code{MultiBasis}.}
As mentioned in the discussion of \deal in Section \ref{sec:litreviewFEM}, one of the usual complexities of finite element methods has to do with the treatment of \emph{hanging nodes}, element faces in the mesh where an element has been refined and its neighbor along that face has not, as shown in Figure \ref{fig:hangingNode}.  At issue is the relationship of the shape functions discretizing a variable on the coarse element to those discretizing the same variable on the finer neighboring elements.  (When neighboring elements are of the same coarseness and polynomial order, the relationship between shape functions on the neighbors is a simple identification.)

The usual way that hanging nodes are handled in finite elements is by imposing a constraint on the finer elements, so that their shape functions conform to the function space on the coarse element along the shared face.  Such constraints might become complicated to implement if arbitrary refinement patterns are allowed---for this reason, finite element codes sometimes limit the irregularity of the mesh;\footnote{\deal and libMesh both support meshes of arbitrary irregularity, although this is not the default option, and their mechanisms for implementing this necessarily differ from ours.} e.g., the mesh shown in Figure \ref{fig:hangingNode2irreg} is called \emph{2-irregular}, because the coarse neighbor on the right has been refined twice along the shared edge, while the one on the left has not been refined at all.  The usual practice is to enforce 1-irregularity by introducing additional refinements to coarse neighbors; usually this is implemented by means of constraints imposed on the appropriate degrees of freedom to ensure continuity.

Our approach in Camellia differs.  We observe that in DPG the discretizations on element interiors are entirely independent of each other, so that only the flux and trace variables---the ones that are defined along a shared edge---need to be reconciled.  We therefore allow the coarse element ($K_{1}$ in Figure \ref{fig:hangingNode}) to ``borrow'' the appropriate basis from its finer neighbors.  The result is that the coarse element has a basis that is only piecewise polynomial along the shared edge; in the case of fluxes, the basis even allows discontinuity at the hanging node.

To implement this, we define a general basis class, which we call \code{MultiBasis}, which allows a basis to be formed along a broken edge from two arbitrary sub-bases.  Clearly, to avoid introducing quadrature error, the quadrature points for the \code{MultiBasis} must be the union of those for its sub-bases; therefore, \code{MultiBasis} provides these to the \code{BasisCache} when the latter determines quadrature points for an edge.  Because a sub-basis can itself be a \code{MultiBasis}, we have an elegant recursive mechanism by which we can handle meshes of arbitrary irregularity.\footnote{Thus far in practice, we have usually continued to enforce 1-irregularity, but in the instances where we have not enforced it, we have not found any ill effects.}

Dual to the concept of \code{MultiBasis} is that of a \code{PatchBasis}, in which the finer elements ``borrow'' a patch of the coarse neighbor's basis.  An option for \code{PatchBasis} is under development.  The \code{PatchBasis} approach coincides exactly with the standard approach of imposing constraints on the finer elements.

\section{Summary of Preliminary Results}
\label{sec:preliminaryResults}
In this section, we summarize the results we have thus far achieved in the context of the Stokes problem.  The principal theoretical result is the proof of the well-posedness of the velocity-gradient-pressure Stokes formulation (specified below), which implies optimal convergence rates when the \emph{graph norm} is used as the norm on the test space.  Details are provided in Appendix \ref{sec:StokesAnalysis}.

As can be seen by the large body of research discussed in Section \ref{sec:litreviewflow}, finding good discrete spaces for the
Stokes problem is \emph{difficult}---this has been an area of ongoing
research for decades.  Through our analysis and numerical results, we demonstrate that DPG allows
solution of the Stokes problem without any special effort---that is,
the Stokes problem is approached and analyzed with exactly the same
DPG-theoretical tools that we use for other linear problems, and we
can use the same discrete spaces for velocity and pressure. In
particular, we use equal-order spaces for velocity and pressure, and
both pressure and velocity converge at the same rate, a contrast with
LDG \cite{CockburnKanschatSchotzauSchwab03}.  Indeed, one of our
numerical experiments demonstrates not only that the method delivers
the optimal convergence rate, but also that the method provides a solution
close to the $L^{2}$ projection of the exact solution.

Our Stokes work began in collaboration with Pavel Bochev and Denis
Ridzal in the summer of 2010 \cite{RobertsetAl10}, during an
internship at Sandia.  Bochev astutely suggested the Stokes problem as
a good example problem for DPG.  That summer, we were puzzled by the
poor performance of DPG using what we herein refer to as the
\emph{naive} test space norm; the present analysis serves (among other
things) to explain why the naive norm fails to achieve optimal
convergence rates, in contrast to the choice to which our analysis
leads us, which we here call the \emph{adjoint graph} norm.

Our numerical results fall into two categories: convergence studies performed on a manufactured solution to verify the theoretically predicted convergence rates, and adaptivity studies in the context of the lid-driven cavity flow problem.  Further details, including an exploration of how the method can go wrong if the test space norm is naively chosen, can be found in Appendix \ref{sec:StokesNumericalResults}.

\subsection{Velocity-Gradient-Pressure Formulation.} The classical strong form of the Stokes problem in $\Omega \subset
\mathbb{R}^{2}$ is given by
\begin{subequations}
\begin{align}
- \mu \Delta \vect{u} + \NVRgrad p &= \vect{f} & \text{ in } \Omega, \label{NVR:eq:StokesFirstIntro} \\
\NVRdiv \vect{u} &= g & \text{ in } \Omega, \\
\vect{u} &= \vect{u}_D & \text{ on } \partial\Omega,\label{NVR:eq:StokesLastIntro}
\end{align}
\end{subequations}
where $\mu$ is viscosity, $p$ pressure, $\vect{u}$ velocity, and
$\vect{f}$ a vector forcing function.  The first equation corresponds
to conservation of momentum, and the second to conservation of mass.
While the analysis will treat the case where mass can be added or removed
from the system ($g \neq 0$), in practice generally (and in our
numerical experiments) $g = 0$.  Since by appropriate
non-dimensionalization we can eliminate the constant $\mu$, we take
$\mu=1$ throughout.

In order to apply the DPG method, we need to cast the system
\eqref{NVR:eq:StokesFirstIntro}--\eqref{NVR:eq:StokesLastIntro} as a
first-order system.  We introduce $\NVRtensor{\sigma}= \NVRgrad
\vect{u}$:
\begin{subequations}
\begin{align}
- \NVRdiv \NVRtensor{\sigma} + \NVRgrad p &= \vect{f} & \text{ in } \Omega, \\
 \NVRdiv \vect{u} &= g & \text{ in } \Omega, \\
 \NVRtensor{\sigma} - \NVRgrad \vect{u} &= 0 & \text{ in } \Omega,\\ 
\vect{u} &= \vect{u}_D & \text{ on } \partial\Omega.
\end{align}
\end{subequations}

Clearly, the first-order formulation is by no means unique; we have chosen this one for convenience of mathematical analysis
and simplicity of presentation.  Previously, we have experimented with
other formulations; the velocity-stress-pressure (VSP) and the velocity-vorticity-pressure (VVP) formulations \cite{RobertsetAl10,RobertsetAl11}.\footnote{The VSP and VVP Stokes formulations are also detailed and used in Appendix \ref{sec:CamelliaDetails} as part of the verification of Camellia.}  Note also that $\NVRtensor{\sigma}$ in this formulation is \emph{not} the physical stress (the physical stress does enter the VSP formulation).

\subsection{Manufactured Solution.}
To test the method, we use a manufactured solution following Cockburn et al. \cite{CockburnKanschatSchotzauSchwab03}
\begin{align*}
u_{1} &=  -e^{x} ( y \cos y + \sin y )\\
u_{2} &=  e^{x}  y \sin y\\
p &= 2 \mu e^{x} \sin y
\end{align*}
on domain $\Omega = (-1,1)^2$, taking $\mu=1$, with uniform quadrilateral meshes of increasing granularity, and examine convergence rates.  The $L^{2}$ norm of the exact solution for $u_{1}$ is 2.53; for $u_{2}$, 1.07; for $p$, 2.81.

Figure \ref{fig:summary_graph_h} shows $h$-convergence results using the graph norm in the test space, for uniform quadrilateral meshes varying from $k=1$ to 4 in polynomial order, and from $1 \times 1$ to $16 \times 16$ elements.  The dashed lines in the plots show the error of an $L^{2}$ projection of the exact solution (the theoretical best we could achieve)---the lines lie nearly on top of each other.  We not only observe optimal convergence rates, but almost exactly achieve the best approximation error!

\begin{figure}[p]
\centering
\subfigure[$u_{1}$]{
\includegraphics[scale=0.42]{./figures/u1_graph_h.pdf}
\label{fig:u1graph_h}
}
\subfigure[$u_{2}$]{
\includegraphics[scale=0.42]{./figures/u2_graph_h.pdf}
\label{fig:u2graph_h}
}
\subfigure[$p$]{
\includegraphics[scale=0.42]{./figures/pressure_graph_h.pdf}
\label{fig:pressuregraph_h}
}
\caption{$h$-convergence of $u_{1},u_{2}$ and $p$ when using the graph norm for the test space.  We observe optimal convergence rates, and nearly match the $L^{2}$-projection of the exact solution.
}
\label{fig:summary_graph_h}
\end{figure}

\subsection{Lid-Driven Cavity Flow.}\label{sec:lidDrivenCavityFlow}
\begin{figure}[h!b!p!]
\centering
\includegraphics[scale=0.75]{./figures/cavity_flow_cartoon.pdf}
\caption{Sketch of lid-driven cavity flow.
}
\label{fig:summary_cavity_flow_cartoon}
\end{figure}
A classic test case for Stokes flow is the lid-driven cavity flow problem.  Consider a square cavity with an incompressible, viscous fluid, with a lid that moves at a constant rate.  The resulting flow will be vorticular; as sketched in Figure \ref{fig:summary_cavity_flow_cartoon}, there will also be so-called \emph{Moffat eddies} at the corners; in fact, the exact solution  will have an infinite number of such eddies, visible at progressively finer scales \cite{Moffat}.  Note that the problem as described will have a discontinuity in the fluid velocity at the top corners, and hence its solution will not conform to the spaces we used in our analysis; for this reason, in our experiment we approximate the problem by introducing a thin ramp in the boundary conditions---we have chosen a ramp of width $\frac{1}{64}$.  This makes the boundary conditions continuous,\footnote{It is worth noting that these boundary conditions are not exactly representable by many of the coarser meshes used in our experiments.  We interpolate the boundary conditions in the discrete space.} so that the solution conforms to the spaces used in the analysis.
\paragraph{$h$-adaptivity study.}
For $h$-refinements, our strategy---previously discussed in Section \ref{sec:proposedApproachDPG}---is very simple:
\begin{enumerate}
\item Loop through the elements, determining the maximum element error $\norm{e_{K{\rm max}}}_{V}$.
\item Refine all elements with error at least 20\% of the maximum $\norm{e_{K{\rm max}}}_{V}$.
\end{enumerate}

Because the exact solution is unknown, we first solve on an overkill mesh and compare our adaptive solution at each step to the overkill solution.  In this experiment, we used quadratic field variables ($k=2$), a test space enrichment of 1 relative to the $H^{1}$ order (that is, $k_{\rm test} = k + 2 = 4$) for both the adaptive and overkill solutions.  The overkill mesh was $256 \times 256$ elements, with 5,576,706 dofs.

The initial mesh was a $2 \times 2$ square mesh; we ran seven $h$-adaptive refinements.  We stopped after seven steps to ensure that the resulting mesh was nowhere finer than the overkill solution.  At each step, we computed the Euclidean ($\ell_{2}$) norm of the $L^{2}$ norm of each of the seven field variables.  The final adaptive mesh has 124 elements and 11,202 dofs, and combined $L^{2}$ error of $4.4 \times 10^{-4}$ compared with the overkill mesh.  We also ran a few uniform refinements and computed the $L^{2}$ error for these compared with the overkill mesh, to show the comparative efficiency of the adaptive refinements.  The results are plotted in Figure \ref{fig:summary_adaptive_cavity_flow_quadratic_vs_overkill}.
\begin{figure}[h!b!p!]
\centering
\includegraphics[scale=0.60]{./figures/adaptive_cavity_flow_quadratic_vs_overkill.pdf}
\caption{Euclidean norm of $L^{2}$ error in all field variables in $h$-adaptive mesh relative to an overkill mesh with $256 \times 256$ quadratic elements.  The Euclidean norm of all field variables in the exact solution is 6.73.
}
\label{fig:summary_adaptive_cavity_flow_quadratic_vs_overkill}
\end{figure}

We also post-processed the results to solve for the stream function $\phi$, where $\Delta \phi = \NVRcurl \vect{u}$.  The contours of $\phi$ are the streamlines of the flow.  These are plotted for the quadratic adaptive mesh described above in Figure \ref{fig:summary_streamlines_p2}; the first Moffat eddy can be seen clearly in the zoomed-in plot.  This quadratic mesh does not resolve the second Moffat eddy, but if we run 11 adaptive refinements on a cubic mesh, we can see it.  This is shown in Figure \ref{fig:summary_streamlines_p3_r11}.

\begin{figure}[p]
\centering
\subfigure[full cavity]{
\includegraphics[scale=0.42]{./figures/streamlines_p2_r7.pdf}
\label{fig:summary_streamlines_p2_r7}
}
\subfigure[lower-left corner]{
\includegraphics[scale=0.42]{./figures/streamlines_detail_p2_r7.pdf}
\label{fig:summary_streamlines_detail_p2_r7}
}
\caption{Streamlines for the full cavity and for the lower-left corner, on a quadratic mesh after 7 adaptive refinements.  The lower-left corner shows the first Moffat eddy.  The final mesh has 124 elements and 11,202 dofs.}
\label{fig:summary_streamlines_p2}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[scale=0.42]{./figures/streamlines_minute_detail_p3_r11.pdf}
\caption{Streamlines for the lower-left corner on a cubic mesh after 11 adaptive refinements: the second Moffat eddy.  The final mesh has 298 elements and 44,206 dofs.}
\label{fig:summary_streamlines_p3_r11}
\end{figure}

\paragraph{ad hoc $hp$-adaptivity study.}
\begin{figure}[h!b!p!]
\centering
\includegraphics[scale=0.60]{./figures/hp_adaptive_cavity_flow_vs_overkill.pdf}
\caption{Euclidean norm of $L^{2}$ error in all field variables in (ad hoc) $hp$-adaptive mesh relative to an overkill mesh with $64 \times 64$ quintic elements.  The Euclidean norm of all field variables in the exact solution is 6.73; the final mesh has 46 elements and 5,986 dofs.
}
\label{fig:summary_hp_adaptive_cavity_flow_vs_overkill}
\end{figure}
For the $hp$ experiment, we adopt a similar strategy; this time, our overkill mesh contains $64 \times 64$ quintic elements, and our initial mesh has $2 \times 2$ linear elements.  We detail our ad hoc choice between $h$- and $p$-refinement in Appendix \ref{sec:StokesNumericalResults}; here, we simply note that our strategy for making this choice does depend on knowledge of the problem---we aim here simply to demonstrate that the method allows arbitrary meshes of arbitrary, variable polynomial order.

We ran 9 refinement steps.  The final mesh has 46 elements and 5,986 dofs, compared with 1,223,682 dofs in the overkill mesh.  The $L^{2}$ error of the adaptive solution compared with the overkill is $8.0 \times 10^{-4}$.  As in the previous experiment, we also tried running a few uniform $h$-refinements on the same initial mesh, as a baseline for comparison.  The results are plotted in Figure \ref{fig:summary_hp_adaptive_cavity_flow_vs_overkill}.

%pagebreaks provide a ``honeypot'' to keep too many figures from spilling into the conclusion
%\pagebreak

\section{Conclusion and Proposed Contributions}
\label{sec:conclusion}
The central contribution of the dissertation will be the design and development of mathematical techniques and software, based on the DPG method, for solving the 2D incompressible Navier-Stokes equations in the laminar regime (Reynolds numbers up to about 1000).  Along the way, we will investigate approximations to these equations---the Stokes equations and the Oseen equations---followed by the steady-state Navier-Stokes equations.  If time allows, we will also solve the transient Navier-Stokes equations.

The study of DPG applied to a system of PDEs has several aspects.  A first-order variational formulation must be derived, including the selection of appropriate test and trial space norms.  The well-posedness of the formulation might be proved.  The formulation can be investigated numerically by means of test problems: convergence can be studied by means of manufactured solutions, and ``real-world'' performance can be studied by means of more physically realistic test problems.  In terms of the CSEM program areas, the derivation of variational formulations and any proofs of their well-posedness belong to Area A, Applicable Mathematics.  The design and development of software for numerical investigations belong to Area B, Numerical Analysis and Scientific Computation.  The study of test problems belongs to Area C, Mathematical Modeling and Applications.  We will briefly describe the specific proposed contributions of this dissertation to each of these in turn.

\paragraph{Area A.}  We will pose several DPG formulations of the Stokes equations---the velocity-gradient-pressure (VGP), velocity-stress-pressure (VSP), and velocity-vorticity-pressure (VVP) formulations.  We will pose DPG formulations of the Oseen equations and the 2D incompressible Navier-Stokes equations.

We will prove the well-posedness of the VGP Stokes formulation for DPG, which has as consequence a guarantee of optimal convergence rates \cite{DPGStokes}; we plan to complete similar proofs for the VSP and VVP formulations.  Time permitting, we would like to prove a similar result for the Oseen equations.  The work on the Oseen equations will include the study of \emph{robustness} for the small-viscosity (high Reynolds number) case, with reference to previous work on convection-dominated diffusion \cite{DPG2,DemkowiczHeuer}.

\paragraph{Area B.} We will design and develop a software toolbox (\emph{Camellia}) for the investigation of DPG problems.  This will support 2D meshes of triangles and quads of variable polynomial order, provide mechanisms for easy specification of DPG variational forms, support $h$- and $p$- refinements, and support distributed computation of the stiffness matrix, among other features.

Time permitting, we hope to add support for meshes of arbitrary spatial dimension, support for space-time elements, and support for distributed mesh and solution representation.

\paragraph{Area C.} We will verify convergence rates for the Stokes, Oseen, and Navier-Stokes equations using manufactured solutions.

We will simulate the classical lid-driven cavity flow and backward-facing step problems using, in turn, the Stokes, Oseen, and Navier-Stokes equations.

We will simulate flow past a cylinder using the steady-state Navier-Stokes equations.  Time permitting, we will do so with the transient equations as well.

\pagebreak
\appendix
\input{stokesAnalysis.tex}

\pagebreak
\input{CamelliaDetails.tex}

\pagebreak
\input{stokesExperiments.tex}

%\section{Overview of Incompressible Flow}
%Discussion of the full transient, nonlinear problem, plus simplified versions:
%\begin{itemize}
%\item full transient
%\item steady
%\item Oseen
%\item Stokes
%\end{itemize}

\bibliography{./DPG}
\bibliographystyle{plain}

%\pagebreak
%
%\section*{Appendix}
%\input{stokes_bounded_below}

%\input{detailedTables}

\end{document}

### 2012-09-18 docs/Jesse/Vienna/pres.tex

@@
 
-\title[A DPG method for Compressible Flow]{Application of a Discontinuous Petrov-Galerkin method to compressible flow problems}
-\date{Sept 12, 2012}
-\author[J. Chan, L. Demkowicz, R. Moser]{Jesse Chan\\ Supervisors: Leszek Demkowicz, Robert Moser}
+\title[A DPG method for Compressible Flow]{Application of a Discontinuous Petrov-Galerkin method to problems in compressible flow}
+\date{ECCOMAS: Sept 12, 2012}
+\author[J. Chan, N. Roberts, L. Demkowicz, R. Moser]{Jesse Chan, Nathan Roberts\\ Supervisors: Leszek Demkowicz, Robert Moser}
 
@@
 \end{itemize}
-\item{} Stability of numerical schemes
-\begin{itemize}
-\item{} Coarse/adaptive grids
-\item{} Higher order
-\end{itemize}
-\item{} Stabilized methods
-\begin{itemize}
-\item{} Stabilization parameters
-\item{} Higher-order
-\end{itemize}
+%\item{} Stability of numerical schemes 
+%\begin{itemize}
+%\item{} Coarse grids
+%\item{} Higher order
+%\end{itemize}
+\item{} Problems of \emph{discrete coercivity} and \emph{robustness}: 
+\begin{align*}
+b(v,v) &\geq \epsilon\nor{v}_{H^1_0}^2, \quad (\text{if at all}),\\
+\nor{u-u_h} &\leq C_\epsilon \inf_{w_h} \nor{u-w_h}.
+\end{align*}
+\item{} Current fix: stabilization%SUPG aims to solve both simultaneously.
 \end{itemize}
@@
 \langle \ell,v\rangle_V &\coloneqq \ell(v).
-\end{array}\right\}
+\end{array}\right.
 \]
@@
 
+\setcounter{subfigure}{0}
+\frame{
+\frametitle{The graph test norm - near $L^2$ best approx for Stokes.}
+\vspace{-.3cm}
+\begin{figure}
+\centering
+\subfigure[Manufactured soln:\ $u_1$ error]{\includegraphics[scale=.235]{figs/stokes/u1_err.pdf}}
+\subfigure[Manufactured soln:\ $p$ error]{\includegraphics[scale=.235]{figs/stokes/pressure_err.pdf}}
+\subfigure[Cavity flow streamlines]{\includegraphics[scale=.245]{figs/stokes/streamlines.pdf}}
+\subfigure[Second Moffat eddy]{\includegraphics[scale=.245]{figs/stokes/streamlines_zoom.pdf}}
+\end{figure}
+}
+
 \section{A Robust DPG Method for Convection-Diffusion}
@@
 \frame{
-\frametitle{Graph norm under convection-diffusion}
+\frametitle{The graph test norm: problems under convection-diffusion}
 The graph norm\footnote{\bibentry{Bui-ThanhDemkowiczGhattas11b}} for convection-diffusion gives exceptional stability.  %, this norm is defined elementwise
@@
 \quad
-\LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gamma}, \LRa{ \widehat{f}_n,\jump{v} }_{\Gamma} = 0
+\text{boundary terms} = 0%\LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gamma}, \LRa{ \widehat{f}_n,\jump{v} }_{\Gamma} = 0
 \end{align*}
@@
 \centering
-\subfigure[Dirichlet inflow]{\includegraphics[scale=.35]{figs/dirichletBC.png}}
-\subfigure[``Convection'' inflow]{\includegraphics[scale=.35]{figs/newBC.png}}
+\subfigure[Dirichlet inflow $u=u_0$]{\includegraphics[scale=.35]{figs/dirichletBC.png}}
+\subfigure[``Convection'' inflow $u-\epsilon u' \approx u_0$]{\includegraphics[scale=.35]{figs/newBC.png}}
 \caption{DPG solutions to convection-diffusion for both inflow conditions using an $H^1$ test norm.}
@@
 %\end{align*}
-Experiments done using Camellia\footnote{\bibentry{Camellia}} and a boundary layer solution.
+Adaptive refinement using Camellia\footnote{\bibentry{Camellia}} for a boundary layer solution.
 %\begin{figure}
@@
 %\addtocounter{framenumber}{-1}
+\addtocounter{framenumber}{-1}
 \frame{
@@
 }
+\addtocounter{framenumber}{-1}
 \setcounter{subfigure}{0}
@@
 %\input{futureWork}
-%\input{extendedSlides}
+\input{extendedSlides}
 

### 2012-09-18 docs/Nate/Proposal/presentation/talk.tex

\documentclass[mathserif]{beamer}
\usepackage{subfigure}
\usepackage{listings}
\usepackage{courier}
\definecolor{lightlightgray}{gray}{0.95}
\definecolor{lightlightblue}{rgb}{0.4,0.4,0.95}
\definecolor{lightlightgreen}{rgb}{0.8,1,0.8}
\lstset{language=C++,
           frame=single,
           basicstyle=\ttfamily\footnotesize,
           keywordstyle=\color{black}\textbf,
           backgroundcolor=\color{lightlightgray},
           commentstyle=\color{blue},
           frame=single
           }
\usetheme[secheader]{pecostalk}
\usepackage{bibentry}
\nobibliography*
\graphicspath{{figs/}}

% defines newblock as null, giving compile issues otherwise
\let\newblock\relax

\newcommand{\eqdef}{\stackrel{\text{\tiny def}}{=}}

\newcommand{\NVRvect}[1]{\ensuremath\boldsymbol{#1}}
\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
\newcommand{\NVRtensor}[1]{\NVRvect{#1}}
%\newcommand{\NVRtensor}[1]{\underline{\NVRvect{#1}}}
\newcommand{\NVRnorm}[1]{\left|\left|#1\right|\right|}
\newcommand{\norm}[1]{\left|\left|#1\right|\right|}
\newcommand{\NVRgrad}{\nabla}
\newcommand{\NVRdiv}{\NVRgrad \cdot}
\newcommand{\NVRpd}[2]{\frac{\partial#1}{\partial#2}}
\newcommand{\NVRpdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
\newcommand{\NVReqdef}{\stackrel{\text{\tiny def}}{=}}

\newcommand{\NVRHgrad}{H(\text{grad})}
\newcommand{\NVRHdiv}{H(\text{div})}
\newcommand{\NVRsumm}[2]{\ensuremath\displaystyle\sum\limits_{#1}^{#2}}

\newcommand{\NVRcurl}{\nabla \times}
\newcommand{\NVRHcurl}{\ensuremath H(\text{curl})}

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\deal}{\code{deal.II}\,}

\newcommand{\pecosbold}[1]{{\color{pecos2}{#1}}}
\newcommand{\pecosreallybold}[1]{{\color{pecos6}{#1}}}

\newcommand{\FootSize}{\scriptsize}

\DeclareMathOperator*{\argmin}{arg\,min}

\date{August 30, 2012}
\author[Nathan V. Roberts]{Nathan V. Roberts \\
Supervisors: Leszek Demkowicz, Robert Moser \\
Committee: Todd Arbogast, George Biros, Thomas Hughes, Venkatramanan Raman
}
\institute{Institute for Computational and Engineering Sciences\\
The University of Texas at Austin}
\title[DPG for Incompressible Flow]{A Discontinuous Petrov-Galerkin Methodology\\ for Incompressible Flow}
\subtitle{Towards Automatic, Robust Mesh Adaptivity}

\begin{document}
\begin{frame}
%\begin{center}
%\includegraphics[width=.8\linewidth]{grand_logo}\\
%\end{center}
\titlepage
%\begin{flushright}
%\includegraphics[scale=0.1]{asc_logo}\\
%\end{flushright}
\end{frame}

%===============================================================================
% ACKNOWLEDGEMENTS
%===============================================================================
%\begin{frame}
%\frametitle{Acknowledgments}
%
%Collaborators:
%\begin{itemize}
%\item Leszek Demkowicz (UT/PECOS)
%\item Denis Ridzal (Sandia/CSRI)
%\item Pavel Bochev (Sandia/CSRI)
%\item Jesse Chan (UT/PECOS)
%\end{itemize}
%
%Support:
%\begin{itemize}
%\item Sandia (summer internships)
%\item PECOS (GRA funding)
%\item ICES (CSEM Fellowship)
%\end{itemize}
%
%\end{frame}

\begin{frame}
\frametitle{Motivation}

Incompressible flows:
\begin{itemize}
\item arise in a variety of applications, from hydraulics to aerodynamics
\item Navier-Stokes equations are of fundamental physical and mathematical interest:

\begin{itemize}
\item believed to hold the key to understanding turbulence
\item precise conditions for existence and uniqueness of solutions remain unknown (Millennium Prize problem)
\end{itemize}

\end{itemize}
%\hspace{1cm} 
\begin{center}
\includegraphics[width=6cm]{../figures/submarine}
\end{center}
% \hfill \includegraphics{../figures/propeller}\hspace{1cm}
\end{frame}

\begin{frame}
\frametitle{Motivation}

\begin{center}\nocite{Williamson1996}
\includegraphics[scale=.5]{../figures/cylinderWakeRe300Williamson.png}\\
\end{center}

Typical solutions of incompressible flow problems involve both fine- and large-scale phenomena.

\begin{center}
$\implies$
\end{center}

A \pecosbold{uniform} finite element mesh of sufficient granularity is
\begin{itemize}
\item \pecosbold{wasteful} of computational resources, or
\item \pecosbold{infeasible} because of resource limitations.
\end{itemize}

\vspace{3mm}
\begin{center}
Therefore, an \pecosbold{adaptive mesh} is required.
\end{center}

\end{frame}

\begin{frame}
\frametitle{Motivation}
In industry:
\begin{itemize}
\item adaptivity schemes used are ad hoc, requiring a domain expert to predict features of the solution,
\item a badly chosen mesh may take considerably longer to converge or fail to converge, and
\item typically, the Navier-Stokes solve will be just one component in an optimization loop $\implies$ any failure requiring human intervention is costly.
\end{itemize}

\begin{center}
\includegraphics[scale=0.35]{../figures/Jesse/mesh10.png}
\end{center}

\end{frame}

\begin{frame}
\vspace{5mm}
\begin{center}
\pecosbold{Goal}: Develop a solver for the incompressible Navier-Stokes equations that provides \pecosbold{robust adaptivity} starting from a coarse mesh.
\end{center}
\pause
By \pecosbold{robust}, we mean:
\begin{itemize}
\item always \pecosbold{converges} to a solution in predictable time, and
\pause
\item the adaptive scheme is \pecosbold{independent} of the problem: no special expertise required for adaptivity.
\end{itemize}

% Explain here what we mean by robust: solver always converges to a solution in predictable time, and that the adaptive scheme is independent of the problem: no special expertise is required for adaptivity.

\end{frame}

%===============================================================================
% OUTLINE
%===============================================================================

% UNCOMMENT THIS TO ADD AN OUTLINE AT THE TOP OF EACH SECTION...
%\AtBeginSection[]
%{
%  \begin{frame}<beamer>
%    \frametitle{Outline}
%    \tableofcontents[currentsection]
%  \end{frame}
%}

\begin{frame}
\frametitle{Outline}
\tableofcontents
\end{frame}

\section{DPG in Brief} % 5-6 slides
% motivate as a min-residual method
% end with the two flow chart slides
%===============================================================================
% The Abstract Problem and Minimization of the Residual
%===============================================================================
\begin{frame}
\frametitle{The Abstract Problem and Minimization of the Residual}
Take $U,V$ Hilbert.\\
\vspace{5mm}
We seek $u \in U$ such that
\[
b(u,v) = l(v) \quad \forall v \in V,
\]
where $b$ and $l$ are linear in $v$.  Define $B$ by $Bu = b(u,\cdot) \in V'$; $Bu$ is a linear functional on the test space $V$.\\
\vspace{5mm}
We seek to minimize the residual in the discrete space $U_{h} \subset U$:
\begin{align*}
u_{h} = \underset{w_{h} \in U_{h}} \argmin \,\, \frac{1}{2} \norm{Bw_{h}-l}_{V'}^{2}.
\end{align*}
\end{frame}

\begin{frame}
\frametitle{The Abstract Problem and Minimization of the Residual}
\begin{align*}
u_{h} = \underset{w_{h} \in U_{h}} \argmin \,\, \frac{1}{2} \norm{Bw_{h}-l}_{V'}^{2}.
\end{align*}

% PATTER: ``not especially easy to work with'': non-constructive; involves taking a supremum
Now, the dual space $V'$ is not especially easy to work with; we would prefer to work with $V$ itself.  Recalling that the Riesz operator $R_{V} : V \rightarrow V'$ defined by 
\begin{align*}
\langle R_{V}v, \delta v\rangle=(v,\delta v)_{V}, \quad \forall \delta v \in V,
\end{align*}
is an \emph{isometry}---$\norm{R_{V}v}_{V'} = \norm{v}_{V}$---we can rewrite the term we want
to minimize as a norm in $V$:

\begin{align*}
\frac{1}{2} \norm{Bw_{h}-l}_{V'}^{2} &= \frac{1}{2} \norm{R_{V}^{-1}\left(Bw_{h}-l\right)}_{V}^{2}\\
                                                              &= \frac{1}{2} \left(R_{V}^{-1}\left(Bw_{h}-l\right), R_{V}^{-1}\left(Bw_{h}-l\right) \right)_{V}.
\end{align*}
\end{frame}

\begin{frame}
\frametitle{The Abstract Problem and Minimization of the Residual}
We seek to minimize
\begin{align*}
\frac{1}{2} \left(R_{V}^{-1}\left(Bw_{h}-l\right), R_{V}^{-1}\left(Bw_{h}-l\right) \right)_{V}.
\end{align*}
The first-order optimality condition requires that the G\^ateaux derivative be equal to zero for minimizer $u_{h}$; assuming $B$ is linear, we have
\begin{align*}
\left(R_{V}^{-1}\left(Bu_{h}-l\right), R_{V}^{-1}B \delta u_{h} \right)_{V} = 0, \quad \forall \delta u_{h} \in U_{h}.
\end{align*}
By the definition of $R_{V}$, this is equivalent to
\begin{align*} % PATTER: use the phrase ``duality pairing''
\langle Bu_{h} - l, R_{V}^{-1}B \delta u_{h} \rangle = 0 \quad \forall \delta u_{h} \in U_{h}.
\end{align*}

\end{frame}

\begin{frame}
\frametitle{The Abstract Problem and Minimization of the Residual}
We have:
\begin{align*}
\langle Bu_{h} - l, R_{V}^{-1}B \delta u_{h} \rangle = 0 \quad \forall \delta u_{h} \in U_{h}.
\end{align*}
Now, if we identify $v_{\delta u_{h}} = R_{V}^{-1}B \delta u_{h}$ as a test function, we can rewrite this as
\begin{align*}
b(u_{h},v_{\delta u_{h}}) &= l(v_{\delta u_{h}}).
\end{align*}

Thus, the discrete solution that minimizes the residual is exactly attained by testing the original equation with appropriate test functions.  We call these \pecosbold{optimal test functions}.\footnote{\FootSize \bibentry{DPG2}}

\end{frame}

\begin{frame}
\frametitle{Evaluating Error}
The derivation prompts the definition of an \pecosbold{energy norm} on the trial space:
\[
\NVRnorm{u}_{E} \NVReqdef \NVRnorm{Bu}_{V'} = \sup_{v \in V} \frac{b(u,v)}{\NVRnorm{v}_{V}}.
\]
We can use this to define a measure of the error:
\begin{align*}
\NVRnorm{u - u_{h}}_{E} &= \NVRnorm{Bu - Bu_{h}}_{V'} \\
&=  \NVRnorm{l - Bu_{h}}_{V'} \\
&= \NVRnorm{R_{V}^{-1}\left(l - Bu_{h}\right)}_{V}.
\end{align*}
Note that all the terms in the final expression are known, so that we can \pecosbold{evaluate}, not merely estimate, the error.  This drives adaptivity.
\end{frame}

%===============================================================================
% From Strong-Form PDE to DPG Form
%===============================================================================
\begin{frame}                                                                                                                                                                          
\frametitle{From Strong-Form PDE to DPG Form}
\begin{center}
\includegraphics[width=\linewidth]{../figures/DPGFormCartoon}\\
\end{center}
\end{frame}              
%===============================================================================
% Solving with DPG
%===============================================================================
\begin{frame}                                                                                                                                                                          
\frametitle{Solving with DPG}
\begin{center} 
\includegraphics[width=0.9\linewidth]{../figures/DPGSolveCartoonNew}\\
\end{center}
\end{frame}

\begin{frame}
\frametitle{Graph Test Norm}

For a strong operator $A$ with formal adjoint $A^{*}$, the \pecosbold{adjoint graph space} is
\[
H_{A^{*}} = \left\{ v \in L^{2}(\Omega) : A^{*}v \in L^{2}(\Omega) \right\}
\]

and the \pecosbold{(adjoint) graph norm} on the test space $V$ is given by
\[
\NVRnorm{v}_{\rm graph} = \NVRnorm{v}_{H_{A^{*}}} = \left( \NVRnorm{v}^{2} + \NVRnorm{A^{*}v}^{2}\right)^{1/2}.
\]

\vspace{5mm}
\begin{center}
E.g. if $A^{*} = \NVRgrad$, then $H_{A^{*}} = H^{1}$, and $\NVRnorm{v}_{H_{A^{*}}} = \NVRnorm{v}_{H^{1}}$.
\end{center}
\end{frame}

\begin{frame}
\frametitle{Key Result: Well-posedness $\implies$ Optimal Convergence}
Under modest technical assumptions (true for Stokes), we have\footnote{\FootSize \bibentry{DPGStokes}}\\
\[
\NVRnorm{Au} \geq \gamma \NVRnorm{u} \implies \sup_{v \in H_{A^{*}}} \frac{b((u,\widehat{u}),v)}{\NVRnorm{v}_{H_{A^{*}}}} \geq \gamma_{\rm DPG} \left(\NVRnorm{u}^{2} + \NVRnorm{\widehat{u}}^{2}_{\widehat{H}_{A}(\Gamma_{h})}\right)^{1/2}
\]
where $\gamma_{\rm DPG} = O(\gamma)$ is a mesh-independent constant, and $\NVRnorm{\cdot}_{\widehat{H}_{A}(\Gamma_{h})}$ is the minimum energy extension norm.\\
\pause
\vspace{5mm}
By Babu\v{s}ka's Theorem,
\[
\implies \left(\NVRnorm{u - u_{h}}^{2} + \NVRnorm{\widehat{u} - \widehat{u}_{h}}^{2}_{\widehat{H}_{A}(\Gamma_{h})}\right)^{1/2} \leq \frac{M}{\gamma_{\rm DPG}} \left( {\rm B.A.E.} \right).
\]
\pause
Suffices to show that $\NVRnorm{Au} \geq \gamma \NVRnorm{u}$ to prove \pecosbold{optimal} convergence rate!
\end{frame}

\section{Equations for Incompressible Flow}
\begin{frame}
\frametitle{Incompressible Flow Equations}
\begin{center}
\includegraphics[width=0.9\linewidth]{../figures/incFlowEqns}\\
\end{center}
\end{frame}

\section{Stokes} % 10-12 slides
% lit. review (including various classical elements, discussion of locking and non-convergence)
% Stokes analysis, summary results
% Numerical experiments: manufactured solution, lid-driven cavity flow problem
% Probably worth mentioning the naive norm results: drives home why the analysis is valuable, and the fact that the optimal test function lives in a very specific space.
%===============================================================================
% Stokes: Classical Problem
%===============================================================================
\begin{frame}
\frametitle{Classical Stokes Problem}
The classical strong form of the Stokes problem in $\Omega \subset
\mathbb{R}^{2}$ is given by
\begin{align*}
- \mu \Delta \vect{u} + \NVRgrad p &= \vect{f} & \text{ in } \Omega, \\
\NVRdiv \vect{u} &= 0 & \text{ in } \Omega, \\
\vect{u} &= \vect{u}_D & \text{ on } \partial\Omega,
\end{align*}
where $\mu$ is viscosity, $p$ pressure, $\vect{u}$ velocity, and
$\vect{f}$ a vector forcing function.  Since by appropriate
non-dimensionalization we can eliminate the constant $\mu$, we take
$\mu=1$ throughout. 
\end{frame}
%===============================================================================
% Stokes: ``Literature Review:'' What's generally done, etc.
%===============================================================================
\begin{frame}
\frametitle{Stokes: Existing Approaches}

Naive discretizations of Stokes can exhibit \pecosbold{non-convergence} or \pecosbold{locking}.\footnote{\FootSize \bibentry{BoffiBrezziFortin}}
\\
\vspace{5mm}
Standard Galerkin discretizations:
\begin{itemize}
\item need to satisfy the \pecosbold{LBB condition}
\item examples: the MINI element, Crouzeix-Raviart element, the class of $Q_{k}-P_{k-1}$ elements
\item polynomial degree in the pressure discretization one lower than that for velocity $\implies$ pressure converges more slowly
\end{itemize}
%\item When solving saddle-point systems using Bubnov-Galerkin methods, there are two \pecosbold{Brezzi conditions} which must be satisfied.  The challenging one for Stokes is the \pecosbold{LBB condition}---much of the art of solving Stokes is to find discrete spaces that satisfy the LBB condition.%\footnote{\bibentry{BoffiBrezziFortin}}

%\item Some choices that satisfy the LBB condition are the MINI element, Crouzeix-Raviart element, and the class of $Q_{k}-P_{k-1}$ elements.  All of these require a polynomial degree in the pressure discretization one lower than that for velocity (so that pressure converges more slowly).

\end{frame}

\begin{frame}
\frametitle{Stokes: Existing Approaches}
Local discontinuous Galerkin (LDG) method:\footnote{\FootSize \bibentry{CockburnKanschatSchotzauSchwab03}}
\begin{itemize}
\item \pecosbold{locally conservative}
\item allows pressure and velocity spaces to be chosen independently
\item equal-order spaces may be used
\item convergence \emph{rate} for the pressure remains lower than that for the velocity
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Stokes: Existing Approaches}
Divergence-conforming B-splines:\footnote{\FootSize \bibentry{EvansThesis}}
\begin{itemize}
\item pointwise divergence-free space $\implies$ locally conservative
\item equal-order spaces
\item optimal convergence rates for pressure \pecosbold{and} velocity
\item non-conforming for multi-patch domains $\implies$ DG techniques for tangential continuity across patch interfaces
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{DPG Applied to Stokes}

To apply DPG, we need a first-order system.  We introduce $\NVRtensor{\sigma}= \NVRgrad
\vect{u}$:
\begin{align*}
- \NVRdiv \NVRtensor{\sigma} + \NVRgrad p &= \vect{f} & \text{ in } \, \Omega, \\
 \NVRdiv \vect{u} &= 0 & \text{ in } \, \Omega, \\
 \NVRtensor{\sigma} - \NVRgrad \vect{u} &= 0 & \text{ in } \, \Omega.
\end{align*}
Testing with $(\vect{v},q,\vect{\tau})$, and integrating by parts, we have
\begin{align*}
\left(\NVRtensor{\sigma} - p \NVRtensor{I}, \NVRgrad \vect{v} \right)_{\Omega_{h}} - \left\langle \widehat{\vect{t}}_{n}, \vect{v} \right\rangle_{\Gamma_{h}} &= (\vect{f}, \vect{v} )_{\Omega_{h}}\\
\left(\vect{u}, \NVRgrad q \right)_{\Omega_{h}} -  \left\langle \widehat{\vect{u}} \cdot \vect{n}, q  \right\rangle_{\Gamma_{h}} &= 0\\
\left( \NVRtensor{\sigma}, \NVRtensor{\tau} \right)_{\Omega_{h}} + \left( \vect{u}, \NVRdiv \NVRtensor{\tau} \right)_{\Omega_{h}} - \left\langle \widehat{\vect{u}}, \NVRtensor{\tau} \vect{n}  \right\rangle_{\Gamma_{h}} &= \NVRtensor{0},
\end{align*}
where traction $\vect{t}_{n} \eqdef ( \NVRtensor{\sigma} - p \NVRtensor{I} ) \vect{n}$, and the hatted variables $\widehat{\vect{t}}_{n}$ and $\widehat{\vect{u}}$ are new unknowns representing the traces of the corresponding variables at the boundary.

\end{frame}

\begin{frame}
\frametitle{DPG Applied to Stokes}
DPG Formulation:
\begin{align*}
b(u,v) =& \left(\NVRtensor{\sigma} - p \NVRtensor{I}, \NVRgrad \vect{v} \right)_{\Omega_{h}} - \left\langle \widehat{\vect{t}}_{n}, \vect{v} \right\rangle_{\Gamma_{h}}\\
&+\left(\vect{u}, \NVRgrad q \right)_{\Omega_{h}} -  \left\langle \widehat{\vect{u}} \cdot \vect{n}, q  \right\rangle_{\Gamma_{h}}\\
&+ \left( \NVRtensor{\sigma}, \NVRtensor{\tau} \right)_{\Omega_{h}} + \left( \vect{u}, \NVRdiv \NVRtensor{\tau} \right)_{\Omega_{h}} - \left\langle \widehat{\vect{u}}, \NVRtensor{\tau} \vect{n}  \right\rangle_{\Gamma_{h}} = (\vect{f}, \vect{v} )_{\Omega_{h}} = l(v).
\end{align*}
The natural spaces for the trial variables are then:
\begin{itemize}
\item fields: $p \in L^{2}(\Omega), \vect{u} \in \vect{L}^{2}(\Omega), \NVRtensor{\sigma} \in \vect{L}^{2}(\Omega)$,
\item fluxes: $\widehat{\vect{t}}_{n} \in \NVRtensor{H}^{-1/2}(\Gamma_{h})$,
\item traces: $\widehat{\vect{u}} \in \vect{H}^{1/2}(\Gamma_{h})$.
\end{itemize}

The natural norms for fluxes and traces are \emph{minimum energy extension norms}.

\end{frame}

\begin{frame}
\frametitle{Polynomial Space Choices}
How to select polynomial spaces for $u$ and $\widehat{u}$?
\begin{itemize}
\item Graph norm $\implies$ error bounded by best approximation error.
\vspace{3mm} \pause
\item Want all variables to have same B.A.E. convergence rates.
\vspace{3mm} \pause
\item Fix polynomial order $k$ for $L^{2}$ variables.  ($k+1$ rate.)
\vspace{3mm} \pause
\item $\implies$ $k+1$ for $H^{1/2}(\Gamma_{h})$.
\vspace{3mm} \pause
\item $\implies$ $k$ for $H^{-1/2}(\Gamma_{h})$.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Graph Test Norm}
The adjoint graph norm for our Stokes formulation is:\footnote{\FootSize \bibentry{DPGStokes}}
\begin{align*}
\norm{(\NVRtensor{\tau},\vect{v}, q)}_{\rm graph}^{2} =& \norm{\NVRdiv \NVRtensor{\tau} - \NVRgrad q}^{2} + \norm{\NVRdiv \vect{v}}^{2} + \norm{ \NVRtensor{\tau} + \NVRgrad{\vect{v}}}^{2}\\ 
&+ \norm{\NVRtensor{\tau}}^{2} + \norm{\vect{v}}^{2} + \norm{q}^{2}.
\end{align*}

\end{frame}

\begin{frame}
\frametitle{Manufactured Solution}
For our first numerical experiment (and following Cockburn et al.\footnote{\FootSize \bibentry{CockburnKanschatSchotzauSchwab03}}), we consider a manufactured solution
\begin{align*}
u_{1} &=  -e^{x} ( y \cos y + \sin y )\\
u_{2} &=  e^{x}  y \sin y\\
p &= 2 \mu e^{x} \sin y
\end{align*}
on domain $\Omega=(-1,1)^{2}$.  We use this to determine appropriate boundary conditions for the DPG problem.  We also perform an $L^{2}$ projection of the exact solution into the trial space to find the solution with the best approximation error.
\end{frame}

\begin{frame}
\frametitle{Graph Test Norm: $u_{1}$ convergence}
\begin{figure}[!htb]
\center
{\setlength{\fboxsep}{1pt}\colorbox{pecos2}{\includegraphics[scale=.38]{../figures/u1_graph_h.png}}}
\caption{$h$-convergence with the graph norm: $u_{1}$.  Dashed lines: best approximation error.}
\end{figure}
\end{frame}

\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
\begin{frame}
\frametitle{Graph Test Norm: $u_{2}$ convergence}
\begin{figure}[!htb]
\center
{\setlength{\fboxsep}{1pt}\colorbox{pecos2}{\includegraphics[scale=.38]{../figures/u2_graph_h.png}}}
\caption{$h$-convergence with the graph norm: $u_{2}$.  Dashed lines: best approximation error.}
\end{figure}
\end{frame}

\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
\begin{frame}
\frametitle{Graph Test Norm: $p$ convergence}
\begin{figure}[!htb]
\center
{\setlength{\fboxsep}{1pt}\colorbox{pecos2}{\includegraphics[scale=.38]{../figures/pressure_graph_h.png}}}
\caption{$h$-convergence with the graph norm: $p$.  Dashed lines: best approximation error.}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Naive Test Norm\footnote{\FootSize \bibentry{RobertsetAl10}}}
What if we don't use the graph norm, but a naive choice instead?

\begin{align*}
\norm{(\NVRtensor{\tau},\vect{v}, q)}_{\rm naive}^{2} = \norm{\NVRtensor{\tau}}^{2} + \norm{\NVRdiv \NVRtensor{\tau}}^{2} + \norm{\vect{v}}^{2} + \norm{\NVRgrad \vect{v}}^{2} + \norm{q}^{2} + \norm{\NVRgrad q}^{2}.
\end{align*}
\end{frame}

\begin{frame}
\frametitle{Naive Test Norm: $u_{1}$ convergence}
\begin{figure}[!htb]
\center
{\setlength{\fboxsep}{1pt}\colorbox{pecos2}{\includegraphics[scale=.38]{../figures/u1_naive_h.png}}}
\caption{$h$-convergence with the naive norm: $u_{1}$.  Dashed lines: best approximation error.}
\end{figure}
\end{frame}

\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
\begin{frame}
\frametitle{Naive Test Norm: $u_{2}$ convergence}
\begin{figure}[!htb]
\center
{\setlength{\fboxsep}{1pt}\colorbox{pecos2}{\includegraphics[scale=.38]{../figures/u2_naive_h.png}}}
\caption{$h$-convergence with the naive norm: $u_{2}$.  Dashed lines: best approximation error.}
\end{figure}
\end{frame}

\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
\begin{frame}
\frametitle{Naive Test Norm: $p$ convergence}
\begin{figure}[!htb]
\center
{\setlength{\fboxsep}{1pt}\colorbox{pecos2}{\includegraphics[scale=.38]{../figures/pressure_naive_h.png}}}
\caption{$h$-convergence with the naive norm: $p$.  Dashed lines: best approximation error.}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Graph vs. Naive Test Norm}
What's the difference between the two norms?  Why are the results better with the graph norm?

\begin{align*}
\norm{(\NVRtensor{\tau},\vect{v}, q)}_{\rm naive}^{2} =& \norm{\NVRdiv \NVRtensor{\tau}}^{2} + \norm{\NVRdiv \vect{v}}^{2} + \norm{\NVRgrad q}^{2} + \norm{\NVRtensor{\tau}}^{2} + \norm{\vect{v}}^{2} + \norm{q}^{2}\\
\vspace{30mm}
\norm{(\NVRtensor{\tau},\vect{v}, q)}_{\rm graph}^{2} =& \norm{\NVRdiv \NVRtensor{\tau} - \NVRgrad q}^{2} + \norm{\NVRdiv \vect{v}}^{2} + \norm{ \NVRtensor{\tau} + \NVRgrad{\vect{v}}}^{2}\\ 
&+ \norm{\NVRtensor{\tau}}^{2} + \norm{\vect{v}}^{2} + \norm{q}^{2}
\end{align*}
\pause
The naive norm is \pecosbold{stronger}---e.g. it requires $\NVRdiv \NVRtensor{\tau} \in L^{2}$ and $\NVRgrad q \in L^{2}$, whereas the graph norm merely requires that $\NVRdiv \NVRtensor{\tau} - \NVRgrad q \in L^{2}$.

\end{frame}

\begin{frame}
\frametitle{Lid-Driven Cavity Flow Problem}
A classic test case for Stokes flow is the \pecosbold{lid-driven cavity flow problem}.  Consider a square cavity with an incompressible, viscous fluid, with a lid that moves at a constant rate.  The resulting flow will be vorticular; there will be \pecosbold{Moffat eddies} at the corners; in fact, the exact solution will have an infinite number of such eddies, visible at progressively finer scales.\footnote{\FootSize \bibentry{Moffat}}
\begin{center}
{\includegraphics[scale=0.40]{../figures/cavity_flow_cartoon.pdf}}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Lid-Driven Cavity Flow Problem}
\begin{center}
{\includegraphics[scale=0.40]{../figures/cavity_flow_cartoon.pdf}}
\end{center}
\small{Because the BCs for the problem are discontinuous at the top corners, the exact solution lies outside of $H^{1}$.  So we introduce a small ``ramp'' on either side, of width $\epsilon = \frac{1}{64}$.}
\end{frame}

\begin{frame}
\frametitle{Lid-Driven Cavity Flow Problem}
Since the exact solution is unknown, we compare an overkill mesh to a series of adaptive and uniformly refined solutions.\\

\begin{itemize}
\item For all meshes, we use quadratic field variables ($k=2$).
\item Overkill mesh had $256 \times 256$ elements (5,576,706 dofs).
\item Initial adaptive mesh had $2 \times 2$ elements.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Lid-Driven Cavity Flow: $h$-adaptivity}
\begin{figure}[!htb]
\begin{center}
{\setlength{\fboxsep}{1pt}\colorbox{pecos2}{\includegraphics[scale=0.40]{../figures/adaptive_cavity_flow_quadratic_vs_overkill.pdf}}}
\end{center}
\caption{Euclidean norm of $L^{2}$ error in all field variables in $h$-adaptive mesh relative to an overkill mesh with $256 \times 256$ quadratic elements.  The Euclidean norm of the overkill solution is 6.73.}
\end{figure}

\end{frame}

\begin{frame}
\frametitle{Lid-Driven Cavity Flow: Streamlines}
\begin{center}
{\setlength{\fboxsep}{1pt}\colorbox{pecos2}{\includegraphics[scale=0.25]{../figures/streamlines_p2_r7.pdf}}} \hspace{5mm} {\setlength{\fboxsep}{1pt}\colorbox{pecos2}{\includegraphics[scale=0.25]{../figures/streamlines_detail_p2_r7.pdf}}}
\end{center}
Streamlines for the full cavity and for the lower-left corner, on a quadratic mesh after 7 adaptive refinements.  The lower-left corner shows the first Moffat eddy.  The final mesh has 124 elements and 11,202 dofs.
\end{frame}

\begin{frame}
\frametitle{Lid-Driven Cavity Flow: Streamlines}
Using a cubic mesh and running 11 refinement steps, we can resolve the second Moffat eddy:
\begin{center}
{\setlength{\fboxsep}{1pt}\colorbox{pecos2}{\includegraphics[scale=.35]{../figures/streamlines_minute_detail_p3_r11.pdf}}}
\end{center}
Streamlines for the lower-left corner on a cubic mesh after 11 adaptive refinements: the second Moffat eddy.  The final mesh has 298 elements and 44,206 dofs.
\end{frame}

\section{Camellia} % 10-12 slides
% lit. review: deal II, libMesh, FEniCS
% what we do, with a couple selected details
% pretty pictures of solutions produced with Camellia?
\begin{frame}
\frametitle{Camellia}
\pecosbold{Design Goal}: make DPG research and experimentation as simple as possible, without sacrificing too much by way of performance.\\

\begin{block}{Existing FEM Software}
\begin{itemize}
\item \deal\footnotemark
\item libMesh\footnotemark
\item FEniCS\footnotemark
\end{itemize}
\end{block}
\addtocounter{footnote}{-2}
\footnotetext{\FootSize \bibentry{BangerthKanschat99}}
\addtocounter{footnote}{1}
\footnotetext{\FootSize \bibentry{Kirk2006}}
\addtocounter{footnote}{1}
\footnotetext{\FootSize \bibentry{fenics:book}}
\end{frame}

\begin{frame}
\frametitle{FEM Software: \deal features}
\begin{block}{}
\begin{itemize}
\item flexible: possible to vary choices for FE spaces, spatial dimension, var. formulations, and linear solvers without too much effort
\item easy to use through encapsulation: details of complex data structures hidden from user
\item safe: runtime parameter checking allows many errors to be detected early in development
\item extensive documentation
\item \pecosbold{hypercube} topologies (lines, quads, hexahedra) supported (with several element types: CG and DG Lagrange, N\'{e}d\'{e}lec, Raviart-Thomas)
\end{itemize}
\end{block}
\end{frame}

\begin{frame}
\frametitle{FEM Software: \deal features, continued}
\begin{block}{}
\begin{itemize}
\item $h$-, $p$-, and $hp$-adaptivity
\item distributed stiffness matrix computation
\item recently added: distributed mesh storage\footnotemark
\end{itemize}
\end{block}\footnotetext{\FootSize \bibentry{dealiiwithp4est}}
\end{frame}

\begin{frame}
\frametitle{FEM Software: libMesh and FEniCS}
\begin{block}{libMesh features}
\begin{itemize}
\item inspired by \deal
\item \code{Element} class designed for subclassing
\item many topologies provided: triangles, quads, hexahedra, tetrahedra, prisms, and pyramids
\item $h$-, $p$-, and $hp$-adaptivity
\item distributed stiffness matrix computation
\end{itemize}
\end{block}

\begin{block}{FEniCS features}
\begin{itemize}
\item aim: highly automated solution of FE problems
\item emphasis is on simplicity, especially in specification of variational forms
\item simplex topologies (intervals, triangles, tetrahedra) supported
\end{itemize}
\end{block}
\end{frame}

\begin{frame}
\frametitle{Camellia\footnote{\FootSize \bibentry{RobertsetAl11}}}
\pecosbold{Design Goal}: make DPG research and experimentation as simple as possible, without sacrificing too much by way of performance.
\vspace{3mm}
\begin{center}
\includegraphics[scale=.65]{../figures/CamelliaVennDiagram.pdf}
\end{center}
%\begin{block}{}
%\begin{itemize}
%\item Like \deal and libMesh, support $hp$-adaptive hierarchical meshes
%\item Like libMesh, support multiple element types (quads and triangles in 2D)
%\item Like FEniCS, support rapid development of variational forms
%\item Leverage existing software by building atop Trilinos\footnotemark
%\end{itemize}
%\end{block}
\addtocounter{footnote}{1}
\footnotetext{\FootSize \bibentry{TrilinosShortAuthors}}
\end{frame}

%\begin{frame}
%\frametitle{Camellia\footnote{\FootSize \bibentry{RobertsetAl11}}}
%\pecosbold{Design Goal}: make DPG research and experimentation as simple as possible, without sacrificing too much by way of performance.
%\begin{block}{Goals for Camellia (Achieved)}
%\begin{itemize}
%\item Make variational form and inner product easy to specify
%\item Arbitrary, $hp$-adaptive 2D meshes (quads and triangles)---including meshes of arbitrary irregularity
%\item ``Reasonable'' speed and scalability (distributed stiffness matrix computation)
%\item Support for nonlinear problems
%\end{itemize}
%\end{block}
%
%\vspace{3 mm}
%
%%\begin{figure}[h]
%%\centering
%%\includegraphics[scale=0.35]{../fig/hangingNode.eps}
%%\label{fig:hangingNode}
%%\end{figure}
%\end{frame}
%
%\begin{frame}
%\frametitle{Camellia}
%\begin{block}{Goals for Camellia (Aspirational)}
%\begin{itemize}
%\item Support for minimization of a \pecosbold{nonlinear} residual
%\item Support for curvilinear geometries
%\item Better scalability (distributed mesh storage)
%\item Longer term: 3D meshes
%\end{itemize}
%\end{block}
%
%\end{frame}

%===============================================================================
% WHAT INTREPID (TRILINOS) PROVIDES
%===============================================================================
\begin{frame}
\frametitle{Trilinos Support}
\begin{block}{}
\begin{center}
\begin{tabular}{l c}
\pecosbold{Feature}			&\pecosbold{Trilinos Package} \\
OO interface to MUMPS 		&Amesos \\
KLU solver 				&Amesos \\
conforming basis functions	&Intrepid \\
pullbacks/Piola transforms 	&Intrepid \\
smart multidimensional arrays 	&Intrepid \\
distributed compressed row storage matrices	&Epetra \\
cell topologies 				&Shards \\
reference-counted pointers 				&Teuchos \\
space-filling curves for spatially local mesh partitioning 		&Zoltan \\
\end{tabular}
\end{center}
\end{block}
\end{frame}

\begin{frame}
\frametitle{Camellia: Other Users}
\begin{itemize}
\item Jesse Chan: compressible Navier-Stokes
\item Truman Ellis: compressible Navier-Stokes with turbulence
\end{itemize}
\begin{figure}
\centering
\subfigure[Mesh]{\includegraphics[height = 3cm]{../figures/Jesse/Mesh10.png}}
\subfigure[$u_1$]{\includegraphics[height = 3cm]{../figures/Jesse/u10.png}}
\caption{Compressible Navier-Stokes for Carter flat plate problem, ${\rm Re}=1000, {\rm Ma}=3.$}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Camellia: Stiffness Matrix Timing Test}
\begin{itemize}
\item local stiffness matrix computation is \pecosbold{embarrassingly parallel}
\item minimize assembly costs: \pecosbold{spatially local} mesh partitioning
\item timing tests on Lonestar: solve convection-dominated diffusion
\end{itemize}
\vspace{-5mm}
\begin{center}
\includegraphics[scale = 0.40]{../figs/scalingFigs/bar_ref3.pdf}\hspace{1cm}
\end{center}
\begin{itemize}
\vspace{-5mm}
\item collaborators working on parallel solvers: Kyungjoo Kim (shared memory architecture),  Maciej Paszynski (distributed memory)
\end{itemize}

\end{frame}

\begin{frame}[fragile]
\frametitle{Camellia: Rapid Specification of Inner Products}
Suppose we have a problem whose graph norm is
\[
\NVRnorm{(v,\vect{q})}_{\rm graph}^{2} = \NVRnorm{v}^{2} + \NVRnorm{\vect{q}}^{2} + \NVRnorm{\NVRpd{v}{x} - \NVRpd{v}{y} + \NVRdiv \vect{q}}^{2}.
\]
\vspace{2mm}
To specify this in Camellia, simply do:
\begin{lstlisting}
VarFactory varFactory;
VarPtr v = varFactory.testVar("v", HGRAD);
VarPtr q = varFactory.testVar("q", HDIV);
IPPtr ip = Teuchos::rcp( new IP);
ip->addTerm(v);
ip->addTerm(q);
ip->addTerm(v->dx() - v->dy() + q->div());
\end{lstlisting}

The bilinear form can be specified similarly.

\end{frame}

%\begin{frame}
%\frametitle{Camellia Details: Stiffness Matrix Computation}
%Recall the problem we solve for the optimal test functions:\\
%For each $e_{i} \in U_h$, find $v_{e_{i}} \in V : (v_{e_{i}},w)_V = b(e_{i},w) \quad \forall w \in V$.\\
%For each $e_{i} \in U_h$, find $v_{e_{i}} \in V : (v_{e_{i}},e_{j})_V = b(e_{i},e_{j}) \quad \forall e_{j} \in V$.\\
%
%\end{frame}

\section{Navier-Stokes} % 7-8 slides
\begin{frame}
\frametitle{Navier-Stokes}
\begin{block}{}
The structure of Navier-Stokes is similar to Stokes:
\begin{itemize}
\item Naive discretizations have similar issues with non-convergence and locking.
\item Can use same elements as for Stokes, but now need to deal with the nonlinearity.
\end{itemize}
\end{block}
\end{frame}

\begin{frame}
\frametitle{Navier-Stokes}
\begin{block}{Existing approaches}
\begin{itemize}
\item Classical pressure-correction methods (Chorin, Temam), velocity-correction methods (Orszag, Karniadakis), and consistent splitting schemes (Guermond and Shen), all of which split the nonlinear time step into a pair of elliptic equations.\footnotemark
\item Guermond and Minev's dimensional splitting, another projection method, which is cheap to compute, only requiring solution of a series of 1D boundary value problems.  (Limited, for now, to axis-aligned parallelepiped meshes.)\footnotemark
\end{itemize}
\end{block}
\addtocounter{footnote}{-1}
\footnotetext{\FootSize \bibentry{Guermond06}}
\addtocounter{footnote}{1}
\footnotetext{\FootSize \bibentry{GuermondMinev2011}}
\end{frame}

\begin{frame}
\frametitle{Navier-Stokes}
\begin{block}{Existing approaches}
\begin{itemize}
\item Cockburn et al. applied LDG to Navier-Stokes, with success for Reynolds numbers up to 100.\footnotemark
\item Evans and Hughes applied divergence-conforming B-splines to Navier-Stokes, with success e.g. for driven cavity problem with ${\rm Re}$ up to 1000.\footnotemark
\end{itemize}
\end{block}
\addtocounter{footnote}{-1}
\footnotetext{\FootSize \bibentry{Cockburn2004}}
\addtocounter{footnote}{1}
\footnotetext{\FootSize \bibentry{EvansHughesSteadyNavierStokes}}
\nocite{EvansHughesUnsteadyNavierStokes}
\nocite{EvansHughesSteadyNavierStokes}
\end{frame}

\begin{frame}
\frametitle{Backward-facing Step}
A classical test case for incompressible flow problems is the \pecosbold{backward-facing step} problem, which has a recirculation region east of the step.  We plan to perform numerical experiments using Stokes, Oseen, and Navier-Stokes.

\vspace{5mm}

\begin{center}
{\includegraphics[scale=0.30]{../figures/backFacingStep.pdf}}\hspace{2mm}{\includegraphics[scale=0.17]{../figures/backFacingStepStreamFunction.png}}
\end{center}

\end{frame}

\begin{frame}
\frametitle{Flow Around a Cylinder}
A classical test case for incompressible Navier-Stokes problems is the flow around a cylinder.\footnote{\FootSize \bibentry{KovasznayCylinder}}  We plan to perform numerical experiments using steady-state Navier-Stokes.

\vspace{10mm}

\begin{center}
{\includegraphics[scale=0.50]{../figures/flowPastCylinder.pdf}}
\end{center}

\pause
At around ${\rm Re}=6$, the flow separates but there is still a steady solution, with symmetric vortices in the wake of the cylinder.  Somewhere above ${\rm Re}=40$, vortex shedding begins (and therefore there is no steady solution).

\end{frame}

% lit. review
% classical problems
\section{Proposed Work} % 3 slides
\begin{frame}
\frametitle{Proposed Work: Area C}
\begin{block}{}
\begin{itemize}
\item Verify convergence rates for the Stokes, Oseen, and Navier-Stokes equations using manufactured solutions.
\item Simulate the classical lid-driven cavity flow and backward-facing step problems using, in turn, the Stokes, Oseen, and Navier-Stokes equations.
\item Simulate flow past a cylinder using the steady-state Navier-Stokes equations.  Time permitting, we will do so with the transient equations as well.
\end{itemize}
\end{block}

\begin{block}{Completed}
\begin{itemize}
\item Verify convergence rates for the Stokes equations using manufactured solutions.
\item Simulate lid-driven cavity flow using the Stokes equations.
\end{itemize}
\end{block}

\end{frame}

\begin{frame}
\frametitle{Proposed Work: Area B}
Design and develop a software toolbox (\emph{Camellia}) for the investigation of DPG problems, with the following features:
\begin{block}{Camellia Features (Completed)}
\begin{itemize}
\item 2D meshes of triangles and quads of variable polynomial order,
\item mechanisms for easy specification of DPG variational forms,
\item $h$- and $p$- refinements, and
\item distributed computation of the stiffness matrix.
\end{itemize}
\end{block}

\pecosbold{Time permitting}, add the following features:
\begin{block}{}
\begin{itemize}
\item curvilinear elements, 
\item meshes of arbitrary spatial dimension,
\item space-time elements, and
\item distributed mesh and solution representation.
\end{itemize}
\end{block}

\end{frame}

\begin{frame}
\frametitle{Proposed Work: Area A}

\begin{block}{}
\begin{itemize}
\item \pecosbold{Completed:} Pose several DPG formulations of the Stokes equations---the velocity-gradient-pressure (VGP), velocity-stress-pressure (VSP), and velocity-vorticity-pressure (VVP) formulations.
\item Pose DPG formulations of the Oseen equations and the 2D incompressible Navier-Stokes equations.
\item \pecosbold{Completed:} Prove the well-posedness of the VGP Stokes formulation for DPG, which has as consequence a guarantee of optimal convergence rates.
\item Time permitting, complete similar proofs for the VSP and VVP formulations.
\item Time permitting, complete similar proofs for the Oseen equations, including a study of \emph{robustness}---analyzing the effects of an increasing Reynolds number.
\end{itemize}
\end{block}

\end{frame}

%===============================================================================
% THANK YOU
%===============================================================================
\begin{frame}
\frametitle{}
\begin{block}{}
\center{Thank you!} \\
\center{Questions?}\\
%For more info:\\
%nroberts@ices.utexas.edu\\
\end{block}
\end{frame}

\bibliographystyle{plain}
{\scriptsize
\bibliography{../DPG}
}

%FOSLS
\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
\begin{frame}
\frametitle{FOSLS\footnote{\FootSize \bibentry{FOSLS1}.}}\nocite{FOSLS2}
First-Order Systems Least Squares (FOSLS), like DPG:
\begin{itemize}
\item first-order system
\item SPD stiffness matrix
\item no need for stabilization terms or flux limiters
\item discrete space only needs to be conforming (no need to satisfy LBB condition, e.g.)
\item minimum-residual method
\item \emph{a posteriori} error \pecosbold{measure} (not estimator)
\end{itemize}
Like DPG, FOSLS provides optimal convergence rates, but it does so in a different norm (typically, the graph norm on the trial space).  Problem-specific approaches to get optimal rates in the $L^{2}$ norm, which DPG manages by virtue of Riesz inversion and a broken test space.
\end{frame}

%Nonlinear derivation, and the Hessian
\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
\begin{frame}
\frametitle{Minimization of the Nonlinear Residual}
As before, we seek to minimize
\begin{align*}
\frac{1}{2} \left(R_{V}^{-1}\left(Bw_{h}-l\right), R_{V}^{-1}\left(Bw_{h}-l\right) \right)_{V},
\end{align*}
but now we allow $B$ to be nonlinear.  The first-order optimality condition then requires that
\begin{align*}
\left(R_{V}^{-1}\left(Bu_{h}-l\right), R_{V}^{-1}B'(u_{h},\delta u_{h}) \right)_{V} = 0, \quad \forall \delta u_{h} \in U_{h}.
\end{align*}
where $B'(u_{h},\delta u_{h})$ is the G\^ateaux derivative of $B$ at $u_{h}$ in direction $\delta u_{h}$.  Then
\begin{align*}
\langle Bu_{h} - l, R_{V}^{-1}B'(u_{h},\delta u_{h}) \rangle = 0 \quad \forall \delta u_{h} \in U_{h}.
\end{align*}
\end{frame}
\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
\begin{frame}
\frametitle{Minimization of the Nonlinear Residual}
\begin{align*}
\langle Bu_{h} - l, R_{V}^{-1}B'(u_{h},\delta u_{h}) \rangle = 0 \quad \forall \delta u_{h} \in U_{h}.
\end{align*}
Now, we can again identify $v_{\delta u_{h}} = R_{V}^{-1}B'(u_{h},\delta u_{h})$ as a test function and note that
\begin{align*}
b(u_{h},v_{\delta u_{h}}) &= l(v_{\delta u_{h}}),
\end{align*}
but notice that now $v_{\delta u_{h}}$ also depends on the solution $u_{h}$.  Linearizing about $u_{h} + \Delta u_{h}$, we have
\begin{align*}
B(u_{h} + \Delta u_{h}) \approx Bu_{h} + B'(u_{h},\Delta u_{h})
\end{align*}
and
\begin{align*}
B'(u_{h} + \Delta u_{h},\delta u_{h}) \approx B'(u_{h},\delta u_{h}) + B''(u_{h},\delta u_{h},\Delta u_{h})
\end{align*}
so that the optimality condition becomes
\begin{align*}
\langle &Bu_{h} + B'(u_{h},\Delta u_{h}) - l,\\
             &R_{V}^{-1}\left( B'(u_{h},\delta u_{h}) + B''(u_{h},\delta u_{h},\Delta u_{h}) \right)) \rangle = 0 \quad \forall \delta u_{h} \in U_{h}.
\end{align*}
\end{frame}
\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
\begin{frame}
\frametitle{Minimization of the Nonlinear Residual}
\begin{align*}
\langle &Bu_{h} + B'(u_{h},\Delta u_{h}) - l,\\
             &R_{V}^{-1}\left( B'(u_{h},\delta u_{h}) + B''(u_{h},\delta u_{h},\Delta u_{h}) \right)) \rangle = 0 \quad \forall \delta u_{h} \in U_{h}.
\end{align*}
Dropping the terms that are second order in $\Delta u_{h}$ and defining $v_{\delta u_{h}} = R_{V}^{-1}B'(u_{h},\delta u_{h})$, we have
\begin{align*}
&\langle Bu_{h} - l, v_{\delta u_{h}} \rangle\\
 &+ \langle Bu_{h} - l, R_{V}^{-1}B''(u_{h},\delta u_{h},\Delta u_{h}) \rangle \\
 &+ \langle B'(u_{h},\Delta u_{h}),  v_{\delta u_{h}} \rangle = 0.
\end{align*}
Rewrite the second term:
\begin{align*}
&\langle Bu_{h} - l, R_{V}^{-1}B''(u_{h},\delta u_{h},\Delta u_{h}) \rangle\\
 &= \left( R_{V}^{-1} (Bu_{h} - l), R_{V}^{-1}B''(u_{h},\delta u_{h},\Delta u_{h}) \right)_{V} \\
&= \langle B''(u_{h},\delta u_{h},\Delta u_{h}), R_{V}^{-1} (Bu_{h} - l) \rangle.
\end{align*}
\end{frame}
\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
\begin{frame}
\frametitle{Minimization of the Nonlinear Residual}
We then have:
\begin{align*}
&\langle Bu_{h} - l, v_{\delta u_{h}} \rangle\\
 &+ \langle B''(u_{h},\delta u_{h},\Delta u_{h}), R_{V}^{-1} (Bu_{h} - l) \rangle \\
 &+ \langle B'(u_{h},\Delta u_{h}),  v_{\delta u_{h}} \rangle = 0.
\end{align*}
Defining $v_{u_{h}} = R_{V}^{-1} (Bu_{h} - l)$, the linearized problem is then
\begin{align*}
b'(u_{h},\Delta u_{h}; v_{\delta u_{h}}) + b''(u_{h},\delta u_{h}, \Delta u_{h}; v_{u_{h}}) = - b(u_{h}, v_{\delta u_{h}}) + l(v_{\delta u_{h}}).
\end{align*}
The solution to this problem minimizes the nonlinear residual $\NVRnorm{Bu_{h}-l}_{V'}$.
\end{frame}

% Assumptions for the well-posedness theorem
\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
\begin{frame}
\frametitle{Technical Assumptions (true for VGP Stokes)}
Under modest technical assumptions (true for Stokes), we have\footnote{\FootSize \bibentry{DPGStokes}}\\
\[
\NVRnorm{Au} \geq \gamma \NVRnorm{u} \implies \sup_{v \in H_{A^{*}}} \frac{b((u,\widehat{u}),v)}{\NVRnorm{v}_{H_{A^{*}}}} \geq \gamma_{\rm DPG} \left(\NVRnorm{u}^{2} + \NVRnorm{\widehat{u}}^{2}_{\widehat{H}_{A}(\Gamma_{h})}\right)^{1/2}
\]
where $\gamma_{\rm DPG} = O(\gamma)$ is a mesh-independent constant, and $\NVRnorm{\cdot}_{\widehat{H}_{A}(\Gamma_{h})}$ is the minimum energy extension norm.\\
\vspace{5mm}
In the next slides, we detail the assumptions.
\end{frame}
\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
\begin{frame}
\frametitle{Technical Assumptions (true for VGP Stokes)}
\[
\NVRnorm{Au} \geq \gamma \NVRnorm{u} \implies \sup_{v \in H_{A^{*}}} \frac{b((u,\widehat{u}),v)}{\NVRnorm{v}_{H_{A^{*}}}} \geq \gamma_{\rm DPG} \left(\NVRnorm{u}^{2} + \NVRnorm{\widehat{u}}^{2}_{\widehat{H}_{A}(\Gamma_{h})}\right)^{1/2}
\]
Define $C$ as the operator arising from integration by parts:
\[
(Au,v)_{\Omega} = (u, A^{*}v)_{\Omega} + \langle Cu, v \rangle.
\]
We split $C$ into $C_{1}$ and $C_{2}$ such that 
\begin{align*}
\langle Cu, v \rangle &= \langle C_{1}u, v \rangle + \langle C_{2}u, v \rangle \\
&= \langle C_{1}u, v \rangle + \langle u, C_{2}'v \rangle
\end{align*}
where $C_{1}u = f_{D}$ corresponds to the Dirichlet BCs imposed. \\
\end{frame}
\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
\begin{frame}
\frametitle{Technical Assumptions (true for VGP Stokes)}
\[
\NVRnorm{Au} \geq \gamma \NVRnorm{u} \implies \sup_{v \in H_{A^{*}}} \frac{b((u,\widehat{u}),v)}{\NVRnorm{v}_{H_{A^{*}}}} \geq \gamma_{\rm DPG} \left(\NVRnorm{u}^{2} + \NVRnorm{\widehat{u}}^{2}_{\widehat{H}_{A}(\Gamma_{h})}\right)^{1/2}
\]
Assumptions:
\begin{itemize}
\item Theorem Hypothesis: with homogeneous boundary condition $C_{1}u=0$ in place, operator $A$ is bounded below in the $L^{2}$-orthogonal component of its null space.
\item $C_{1}$ and $C_{2}$ are defined in such a way that
\[ \left( \langle u,
  C_2^\prime v\rangle = 0 \quad \forall u \: : C_1 u = 0 \right) \implies
  C_2^\prime v = 0.
\]
\item $A$ and $A^{*}$ are surjective.
\item Both graph spaces $H_{A}(\Omega)$ and $H_{A^{*}}(\Omega)$ admit corresponding trace spaces $\widehat{H}_{A}(\partial \Omega)$ and $\widehat{H}_{A^{*}}(\partial \Omega)$.
\item The boundary term $\langle Cu, v \rangle$ arising from integration by parts is definite.
\end{itemize}

\end{frame}

\end{document}

### 2012-09-19 docs/Nate/Proposal/stokesAnalysis.tex

\section{Analysis of the Velocity-Gradient-Pressure Stokes Formulation}
\label{sec:StokesAnalysis}

The purpose of this appendix is to present a general theory for the DPG
method for linear PDEs and immediately specialize it to the Stokes
problem. The presented theory summarizes results obtained in
\cite{DPG6,BramwellDemkowiczGopalakrishnanQiu11,DemkowiczGopalakrishnanMugaZitelli12}
for particular boundary-value problems and specializes the
general theory for Friedrichs systems, presented in
\cite{Bui-ThanhDemkowiczGhattas11b}, for cases in which the traces of the graph spaces
are available.  As most of the technical results here are classical,
we have chosen a somewhat informal format of presentation.

\subsection{Notation and Definitions\label{section:notation}}

Let $\Omega$ denote a bounded Lipschitz domain in $\doubleIR^n, n=2,3$,\: with boundary
$\Gamma = \ptl \Omega$. We shall use the following standard energy spaces:
\[
\begin{array}{rl}
H^1(\Omega) & := \{ u \in L^2(\Omega) \: : \: \bfnab u \in \bfL^2(\Omega) \}, \\[8pt]
\bfH(\text{div},\Omega) & := \{ \bfsig \in \bfL^2(\Omega) \: : \: \text{div} \bfsig \in L^2(\Omega) \}, 
\end{array}
\]
with the corresponding trace spaces on $\Gamma$:
\[
\begin{array}{rl}
H^{1/2}(\Gamma) & := \{ 
{\hat{u} =} u\vert_{\Gamma}, \: u \in H^1(\Omega) \},
\\[8pt] H^{-1/2}(\Gamma) & := \{ {\hat{\sigma}_{n}} = (\bfsig \cdot
\bfn)\vert_{\Gamma} ,\: \bfsig \in \bfH(\text{div},\Omega) \},
\end{array}
\] 
where $\bfn$ denotes the outward normal unit vector to the boundary
$\Gamma$.  The definition of trace space $H^{1/2}(\Gamma)$ is
classical but far from trivial, see e.g.  \cite[pp. 96]{McLean}.  The
assumption on the regularity of the domain (being Lipschitz) is
essential; domains with ``cracks'' require a special and
non-classical treatment. When necessary, we will formalize the use of
the trace operator by identifying it with a separate symbol, 
\[
\text{tr} \: : \: H^1(\Omega) \ni u \to \text{tr } u = {\hat{u} =} u\vert_{\Gamma}
\in H^{1/2}(\Gamma).  
\] 
The space $H^{-1/2}(\Gamma)$ is the topological
dual of $H^{1/2}(\Gamma)$ and a second trace operator corresponding to it,
\[ \text{tr} \: : \: \bfH(\text{div},\Omega) \ni \bfsig \to \text{tr
} \bfsig = {\hat{\sigma}_n} = (\bfsig \cdot \bfn)\vert_{\Gamma} \in
H^{-1/2}(\Gamma),
\] 
is usually defined by the {\em generalized Green
  Formula}; see e.g. \cite[pp. 61]{Showalter} or
\cite[pp. 530]{FAbook}. Note that, unless otherwise stated, in this
paper we use the same trace notation ``tr'' for functions in both
$H^1(\Omega)$ and $\bfH(\text{div},\Omega)$.

We shall also use group variables consisting of multiple copies of functions from $H^1(\Omega),\bfH(\text{div},\Omega)$, and $H^{1/2}(\Gamma)$ or distributions from $H^{-1/2}(\Gamma)$. We will then switch to boldface notation:
\[
\begin{array}{rl}
\bfH^1(\Omega) & = H^1(\Omega) \times \ldots \times H^1(\Omega),\\[8pt]
\bfH^{1/2}(\Gamma) & = H^{1/2}(\Gamma) \times \ldots \times H^{1/2}(\Gamma), \\[8pt]
\bfH^{-1/2}(\Gamma) & = H^{-1/2}(\Gamma) \times \ldots \times H^{-1/2}(\Gamma),
\end{array}
\]
etc. In the case of tensors, the definitions will be applied row-wise:
$$
\bfsig = (\sigma_{ij}) \in \bfH(\text{\bf div},\Omega) \quad \Longleftrightarrow \quad
(\sigma_{i1},\ldots,\sigma_{in}) \in \bfH(\text{div},\Omega),\: i=1,\ldots,n.
$$

\paragraph*{Broken energy spaces.}

Let $\Omega$ be partitioned into finite elements $K$ such that
\[
  \overline{\Omega} = \bigcup_K  \bar{K},\: \quad K \text { open},
\]
with corresponding {\em skeleton} $\Gamma_h$ and {\em interior
  skeleton} $\Gamma_h^0$,
\[
\Gamma_h := \bigcup_K \ptl K\qquad \Gamma_h^0 := \Gamma_h - \Gamma.
\]
The usual regularity assumptions for the elements can essentially be relaxed. 
The elements may be general polygons in 2D, or polyhedra\footnote{Possibly curvilinear polyhedra.}
 in 3D (with triangular and quadrilateral
faces). Meshes may be {\em irregular}, i.e. with hanging nodes (see e.g. \cite[pp. 211]{hpbook}).
Also, at this point, we do not make any shape regularity assumptions.
By {\em broken} energy spaces we simply mean standard energy spaces defined element-wise:
\[
\begin{array}{rl}
H^1(\Omega_h) & := \prod_K H^1(K), \\[8pt]
\bfH(\text{div},\Omega_h) & := \prod_K \bfH(\text{div},K).
\end{array}
\]
With broken energy spaces, integration by parts is performed element-wise. 
For $\bfsig \in \bfH(\text{div},\Omega_h)$ and $v \in H^1(\Omega)$, we have
\[
\begin{array}{rl}
(\text{div}_h \bfsig, v)_{\Omega_h}  := &\ds \sum_K (\text{div} \bfsig, v)_K \\[8pt]
 = &\ds \sum_K \left( -(\bfsig, \bfnab v)_K 
+ {\langle\hat{\sigma}_n,\hat{v}\rangle _{\ptl K}} \right) \\[8pt]
 = &\ds - (\bfsig, \bfnab v) + {\underbrace{\sum_K 
\langle\hat{\sigma}_n,\hat{v}\rangle_{\ptl K}}
_{=: \langle\hat{\sigma}_n,\hat{v}\rangle_{\Gamma_h}}.}
\end{array}
\]
Here $(\cdot,\cdot)$ and $(\cdot,\cdot)_K$ denote the $L^2$-product over
the whole domain and element $K$, resp., and $\langle\cdot,\cdot\rangle_{\ptl K}$
stands for the duality pairing between $H^{-1/2}(\ptl K)$ and
$H^{1/2}(\ptl K)$.

Integration by parts leads naturally to the concept of the trace space over the skeleton $\Gamma_h$,
\[
H^{1/2}(\Gamma_h) := 
{
\left\{ \hat{v} = \{\hat{v}_K \} \in \prod_K H^{1/2}(\ptl K) \: :
\: \exists v \in H^1(\Omega) : v\vert_{\ptl K} = \hat{v}_K \right\}.}
\]
This is not a trivial definition. First of all, to be more precise, by
${v}\vert_{\ptl K}$ we mean the trace (for element $K)$
of the restriction of ${v}$ to $K$. Secondly,
$H^{1/2}(\Gamma_h)$ is a {\em closed} subspace of $\prod_K
H^{1/2}(\ptl K)$, as we shall show momentarily. For convenience, we
assume that all trace spaces are endowed with {\em minimum-energy
  extension norms}, i.e.,
\[
 \Vert {\hat{u}}\Vert_{H^{1/2}(\ptl K)} :=
\inf_{\substack{
E{\hat{u}} \in H^1(K)\\ 
E{\hat{u}}\vert_{\ptl K} = {\hat{u}}}}
\Vert E{\hat{u}} \Vert_{H^1(K)},
\]
etc. Let 
${\hat{u}}^n = \{ {\hat{u}}^n_K \} $ be a sequence of functions in
$H^{1/2}(\Gamma_h)$ converging in the product space to a limit ${\hat{u}} =
\{{\hat{u}}_K \} $. For each element $K$, ${\hat{u}}^n_K$ 
is the trace of restriction
${u}^n\vert_K$ for some ${u}^n \in H^1(\Omega)$.  By the definition of
norms, ${u}^n\vert_K \stackrel{n \to \infty}{\longrightarrow} 
{u}_K$ in $H^1(K)$, for
each element $K$. The delicate question is whether we can claim that
the union ${u}$ of ${u}_K$ is in $H^1(\Omega)$. But this follows from the
definition of distributional derivatives. Indeed, given a test function $\phi
\in \mathcal{D}(\Omega)$, we have for each $n$,
\[
 \int_\Omega {u}^n \frac{\ptl \phi}{\ptl x_i} = - \int_{\Omega}
\frac{\ptl {u}^n}{\ptl x_i} \phi 
\] 
or 
\[ \sum_K \int_K {u}^n \frac{\ptl
  \phi}{\ptl x_i} = - \sum_K \int_K \frac{\ptl {u}^n}{\ptl x_i} \phi.
\]
Passing to the limit with $n \to \infty$, we get 
\[ \int_\Omega {u}
\frac{\ptl \phi}{\ptl x_i} = - \sum_K \int_K \frac{\ptl {u}_K}{\ptl x_i}
\phi, 
\] 
which proves that the union of element-wise derivatives
$\frac{\ptl {u}_K}{\ptl x_i}$, a function in $L^2(\Omega)$, {\em is} the
distributional derivative of ${u}$. Consequently, ${u} \in H^1(\Omega)$.

Notice that we have not attempted to extend the classical definition
of the trace space $H^{1/2}(\Gamma)$ for Lipschitz boundary $\Gamma$
to a non-Lipschitz skeleton $\Gamma_h$.\footnote{The definition of a
  Lipschitz domain includes the assumption that the domain is on one
  side of its boundary, see \cite[pp. 89]{McLean}.}  This is not
impossible but much more technical (like for domains with cracks).

A similar construction holds for globally conforming $\bfsig \in \bfH(\text{div},\Omega)$
but broken $v \in H^1(\Omega_h)$:
\[
\begin{array}{ll}
(\bfsig, \bfnab_h v)_{\Omega_h} & := \ds \sum_K (\bfsig, \bfnab v)_K \\[8pt]
& \ds = \sum_K \left( - (\text{div} \bfsig, v)_K + \langle{\hat{\sigma}}_n,{\hat{v}}\rangle_{\ptl K} \right) \\[8pt]
& \ds = -(\text{div} \bfsig,v) + \underbrace{\sum_K \langle{\hat{\sigma}}_n,{\hat{v}}\rangle_{\ptl K}}_{=: \langle{\hat{\sigma}}_n, {\hat{v}}\rangle_{\Gamma_h}}.
\end{array}
\]
In this case, we are led to the definition of the trace space $H^{-1/2}(\Gamma_h)$:
\[
H^{-1/2}(\Gamma_h) := \left\{ {\hat{\sigma}}_n = \{ {\hat{\sigma}}_{Kn} \}\in \prod_K H^{-1/2}(\ptl K) \: : \: \exists \bfsig \in \bfH(\text{div},\Omega)
: {\hat{\sigma}}_{Kn} = (\bfsig \cdot \bfn)\vert_{\ptl K} \right\}.
\]
We equip both trace spaces over the mesh skeleton with minimum energy extension norms
\[
\begin{array}{rl}
\Vert {\hat{v}} \Vert_{H^{1/2}(\Gamma_h)} := \ds &\inf_{\substack{{u} \in H^1(\Omega)\\ {u}\vert_{\Gamma_h} = u}} 
\Vert {u} \Vert_{H^1(\Omega)} \quad \text{ and} \\[24pt]
\Vert {\hat{\sigma}}_n \Vert_{H^{-1/2}(\Gamma_h)} := \ds &\inf_{\substack{\text{\bfsig} \in \text{\bfH}(\text{div},\Omega)\\
(\text{\bfsig} \cdot \text{\bfn})\vert_{\Gamma_h} = {\hat{\sigma}}_n}}
\Vert \bfsig \Vert_{\text{$\bfH$}(\text{div},\Omega)}.
\end{array}
\]
We will also need the space of traces on the internal skeleton
\[
\tilde{H}^{1/2}(\Gamma_h) := \left\{ {\hat{v}} = \{{\hat{v}}_K \} \in  \prod_K H^{1/2}(\ptl K) \: : \: \exists {v} \in H^1_0(\Omega) : {v}\vert_{\ptl K} = {\hat{v}}_K \right\},
\]
which we likewise equip with the minimum energy extension norm.

To summarize, we have defined the term $\langle{\hat{\sigma}}_n,{\hat{v}}\rangle_{\Gamma_h}$ when
one of the variables is a trace over the whole skeleton and
the other is the trace of a function from the broken energy
space. Also notice that, for sufficiently regular functions, 
$\langle{\hat{\sigma}}_n,{\hat{v}}\rangle_{\Gamma_h}$ represents either the $L^2(\Gamma_h)$-product
of trace of a conforming $\bfsig$ and inter-element jumps of $v$, or the product
of jumps in $\sigma_n$ and the trace of a globally conforming $v$. This
can be seen by switching from the summation over elements to the
summation over element faces (edges in 2D).

\subsection{Strong and Ultra-Weak Formulations}

\paragraph*{Integration by parts.}

Let $u$ now represent a group variable consisting of functions defined
on the domain $\Omega$, and $A$ be a linear differential operator
corresponding to a system of first order PDEs. We start with an abstract
integration by parts formula,
\be
(Au,v) = (u,A^\ast v) + \langle C u, v\rangle
\label{eq:integration_by_parts_classical}.
\ee
Here $(\cdot,\cdot)$ denotes the $L^2(\Omega)$-inner product, $A^\ast$ is the formal
adjoint operator, $C$ is  a  boundary operator and at this point $\langle\cdot,\cdot\rangle$ 
stands for just the $L^2(\Gamma)$-inner
product on boundary $\Gamma = \ptl \Omega$. Obviously, the formula holds under
appropriate regularity assumptions, e.g. $u,v \in C^1(\overline{\Omega})$, if all
derivatives are understood in the classical sense.

If we assume $u,v \in L^2(\Omega)$ and interpret the derivatives in a distributional sense,
we arrive naturally at the graph energy spaces
\[
\begin{array}{rl}
\ds H_A(\Omega) & \ds := \{ u \in L^2(\Omega) \: : \: A u \in L^2(\Omega) \} \quad \text{ and }\\[8pt]
\ds H_{A^\ast}(\Omega) & \ds := \{ u \in L^2(\Omega) \: : \: A^\ast u \in L^2(\Omega) \}.
\end{array}
\]
{ {\bf Assumption 1:} We take operators $A$ and $A^\ast$ to be surjections; i.e. given $f \in L^2(\Omega)$, we
  can always find $u \in H_A(\Omega)$ and $v \in H_{A^\ast}(\Omega)$
  such that $Au = f$ and $A^\ast v = f$.  Roughly speaking, this
  corresponds to an assumption  that neither $A$ nor $A^\ast$ are, in a sense,
  degenerate.\footnote{Ivo Babu\v{s}ka, private communication.}}

With $u$ and $v$ coming from the energy spaces, the domain integrals $(Au,v)$ and $(u, A^\ast v)$
are well-defined.  We now assume that the graph spaces admit
trace operators
\[
\begin{array}{rlll}
\text{tr}_A &\ds : \: H_A(\Omega) & \twoheadrightarrow  \widehat{H}_A(\Gamma) \quad \text{ and }\\[8pt]
\text{tr}_{A^\ast} &\ds : \: H_{A^\ast}(\Omega) & \twoheadrightarrow  \widehat{H}_{A^\ast}(\Gamma).
\end{array}
\]
The double arrowheads indicate that the trace operators are surjective. We equip the trace
spaces with the minimum energy extension norms
\[
\Vert \hat{u} \Vert_{\widehat{H}_A(\Gamma)} = \inf_{\substack{u \in H_A(\Omega)\\ \text{tr}_A u = \hat{u} }} \Vert u \Vert_{H_A(\Omega)} \quad \text{ and } \quad 
\Vert \hat{v} \Vert_{\widehat{H}_{A^*}(\Gamma)} = \inf_{\substack{v \in H_{A^*}(\Omega)\\ \text{tr}_{A^*} v = \hat{v} }} \Vert v \Vert_{H_{A^*}(\Omega)}.
\]

We now generalize the classical integration by parts 
formula~(\ref{eq:integration_by_parts_classical}) to a more general, distributional case:
\[
(Au,v) = (u,A^\ast v) + c(\text{tr}_A u, \text{tr}_{A^\ast} v),
\label{eq:integration_by_parts}
\]
with $u \in H_A(\Omega), v \in H_{A^\ast}(\Omega)$, and 
\[
c(\hat{u},\hat{v}), \quad \hat{u} \in \widehat{H}_A(\Gamma), \hat{v} \in \widehat{H}_{A^\ast}(\Gamma) 
\]
being a duality
pairing,\footnote{This notion extends the definition of the ``usual'' duality pairing between a space and its
dual.} i.e. a {\em definite} continuous bilinear (sesquilinear) form. Recall that form $c(\hat{u},\hat{v})$
is definite if
\begin{align*}
\left(c(\hat{u},\hat{v})\right. &= \left.0\quad \forall \hat{v} \right) \implies \hat{u} = 0 \quad \text{ and} \\[8pt]
\left(c(\hat{u},\hat{v})\right. &= \left.0\quad \forall \hat{u} \right) \implies \hat{v} = 0.
\end{align*}
Equivalently, the corresponding boundary operator
\[
C \: : \: \widehat{H}_A(\Gamma) \to (\widehat{H}_{A^\ast}(\Gamma))^\prime,\quad
\langle C\hat{u},\hat{v} \rangle = c(\hat{u},\hat{v})
\]
and its adjoint $C'$ are injective and
therefore both $C$
and $C'$ are isomorphisms.\footnote{$\mathcal{R}(A) = \mathcal{N}(C')^\perp$.} Above and in what follows, $\langle \cdot,\cdot\rangle$
denotes the usual duality pairing between a space and its dual.

\paragraph*{Integration by parts for the Stokes problem.}

We verify (and illustrate) our general assumptions for the Stokes problem.
Multiplying equations~(\ref{NVR:eq:StokesFirstIntro}-\ref{NVR:eq:StokesLastIntro}) with test functions $\bfv,q,\bftau$, integrating by parts
and summing up the equations, we obtain
\begin{align*}
(- \text{\bf div} ( \bfsig - p \bfI ),\bfv)+
(\text{div} \bfu,q)+
(\bfsig  - \bfnab \bfu,\bftau)
=& \quad ( \bfsig - p \bfI, \bfnab \bfv) + \langle  (- \bfsig + p \bfI) \bfn, \bfv\rangle\\[8pt] 
&+ (\bfu, - \bfnab q) + \langle  \bfu \cdot \bfn,q\rangle\\[8pt]
&+ (\bfsig,\bftau) + (\bfu, \text{\bf div} \bftau) + \langle \bfu, - \bftau \bfn\rangle\\[8pt] 
=& \quad (\bfu, {\bf div} (\bftau - q \bfI)) + (p, - \text{div} \bfv) + (\bfsig, \bftau + \bfnab \bfv) \\[8pt]
&+ \langle  (- \bfsig + p \bfI) \bfn, \bfv\rangle + \langle \bfu, (-\bftau + q\bfI) \bfn\rangle.
\end{align*}
Thus, comparing with the abstract theory, we have
\[
\begin{array}{rl}
u & = (\bfu,p,\bfsig), \\[8pt]
v & = (\bfv,q,\bftau), \\[8pt]
Au & = (- \text{\bf div} ( \bfsig - p \bfI ),\text{div} \bfu,\bfsig  - \bfnab \bfu), \\[8pt]
A^\ast v & = (\text{\bf div} (\bftau - q \bfI) ,- \text{div} \bfv,\bftau + \bfnab \bfv ).
\end{array}
\]
The operator is not (formally) self-adjoint but the corresponding energy graph spaces are identical,
$H_A(\Omega) = H_{A^\ast}(\Omega)$, where
\[
H_A(\Omega) = \{ (\bfu,p,\bfsig) \: : \: \bfsig - p\bfI \in
\bfH(\text{\bf div},\Omega), \bfu \in \bfH^1(\Omega) \}.
\]
The traces are also the same; that is, $\text{tr}_A = \text{tr}_{A^\ast}$, where 
\[
\text{tr}_A : H_A(\Omega) \ni (\bfu,p,\bfsig) \to ((-\bfsig + p \bfI)
\bfn, \bfu) \in \bfH^{-1/2}(\Gamma) \times \bfH^{1/2}(\Gamma).
\]
The
boundary term, being the sum of standard duality pairings for
respective components of the traces, is definite.

\begin{remark}
The Stokes problem can be framed into a general abstract case
discussed in \cite[Section 6.6]{FAbook}.  The boundary term is
identified as a {\em concominant} of the corresponding
traces. Moreover, the Stokes equation can be cast into a Friedrichs'
system \cite{ErnGuermond08}, and hence can be studied using the
unified DPG framework \cite{Bui-ThanhDemkowiczGhattas11b} which uses
boundary operator and graph spaces. Here, inspired by our previous work
\cite{Bui-ThanhDemkowiczGhattas11b}, we develop an abstract
DPG theory using the trace operators and graph spaces, assuming the existence of
traces, and study the Stokes equation using this framework.
\end{remark}

\paragraph*{Strong formulation with homogeneous BC.}
We now return to our abstract setting and assume that the boundary operator $C$ can be split into two operators $C_1$ and $C_2$ such that
\[
\begin{array}{ll}
\langle C u,v\rangle &= \langle C_1 u,v\rangle + \langle C_2 u,v\rangle \\[5pt]
& = \langle C_1 u,v\rangle + \langle u, C_2^\prime v\rangle;\\[5pt]
\end{array}
\]
we also take $C_{1}$ and $C_{2}$ to be ``reasonable'' in the sense that both have closed range. It should be pointed out that this is analogous to boundary operator splitting due to Friedrichs \cite{Friedrichs58, ErnGuermondCaplain07}.

We are interested in solving a non-homogeneous boundary-value problem
\be
\left\{
\begin{array}{rll}
A u & = f \quad & \mbox{in } \Omega,\\
C_1 u & = f_D & \mbox{on } \Gamma,
\end{array}
\right.
\label{eq:nonhom_BVP}
\ee
with $f \in L^2(\Omega)$ and $ f_D \in \mathcal{R}(C_1)$.

We begin with the homogeneous BC case:
\be
\left\{
\begin{array}{rll}
A u & = f \quad & \mbox{in } \Omega,\\
C_1 u & = 0 & \mbox{on } \Gamma.
\end{array}
\right.
\label{eq:hom_BVP}
\ee
Introducing the spaces
\[
\begin{array}{ll}
U := \{ u \in H_A(\Omega) : & C_1 \: \text{tr}_A u = 0 \} \quad \text{ and } \\[8pt]
V := \{ v \in H_{A^\ast}(\Omega) : & C_2^\prime \: \text{tr}_{A^\ast} v = 0 \},
\end{array}
\]
we see that, if we restrict operators $A$ and $A^\ast$ to $U$ and $V$, the
boundary term vanishes. However, for $A$ and $A^\ast$ to be
$L^2$-adjoint, we have to make an additional technical
assumption.\footnote{The domain of the adjoint operator has to be maximal in the
  sense that it includes {\em all} $v$ for which the boundary term
  vanishes.}\\
{{\bf Assumption 2:} 
\be \left( \langle u,
  C_2^\prime v\rangle = 0 \quad \forall u \: : C_1 u = 0 \right) \implies
  C_2^\prime v = 0.
\label{eq:adjoint_assumption}
\ee } 
The following lemma allows us to use this condition to establish a decomposition of the trace space.
\begin{lemma}
Assume that $C: X \to
Y$ is an isomorphism from Hilbert space $X$ onto a Hilbert space
$Y$. Assume $C$ has been split into $C_1$ and $C_2$ that satisfy
condition~(\ref{eq:adjoint_assumption}).  Each of following conditions is then equivalent to~(\ref{eq:adjoint_assumption}).
\[
\begin{array}{c}
\mathcal{N}(C_1)^\perp \cap \mathcal{R}(C_2^\prime) = \{ 0 \},  \\[8pt]
\mathcal{N}(C_1)^\perp \cap \mathcal{N}(C_2)^\perp = \{ 0 \},  \\[8pt]
\mathcal{N}(C_2) \cap \mathcal{N}(C_1)  = \{ 0 \},  \\[8pt]
X = \mathcal{N}(C_2) \oplus \mathcal{N}(C_1).
\end{array}
%\label{eq:adjoint_assumption_equivalent}
\]
\end{lemma}
\begin{proof} Elementary with an application of the Closed Range Theorem that we recall below. \end{proof}
Condition~(\ref{eq:adjoint_assumption}) thus decomposes the trace
space $\widehat{H}_A(\Gamma)$ into the direct sum of the nullspaces of
operators $C_1$ and $C_2$; \be \widehat{H}_A(\Gamma) = \widehat{H}_A^1(\Gamma)
\oplus \widehat{H}_A^2(\Gamma),
\label{eq:trace_split}
\ee where $\widehat{H}_A^1(\Gamma) = \mathcal{N}(C_2)$ and
$\widehat{H}_A^2(\Gamma) = \mathcal{N}(C_1)$. In other words, for each
$\hat{u} \in \widehat{H}_A(\Gamma)$, there exist unique $ \hat{u}_1 \in
\widehat{H}_A^1(\Gamma)$ and $ \hat{u}_2 \in \widehat{H}_A^2(\Gamma)$ such that
\[
\hat{u} = \hat{u}_1 + \hat{u}_2,
\]
which is analogous to the condition introduced by Friedrichs \cite{Friedrichs58} on his boundary
operator $M$, subsequently generalized in \cite{ErnGuermondCaplain07}, and first used
in the DPG context in \cite{Bui-ThanhDemkowiczGhattas11b}.

Having reduced the problem with homogeneous BCs to the classical theory of
$L^2$-adjoint operators, we now recall the Banach Closed Range
Theorem. Let $T : X \to Y$ be a linear, continuous operator from a
Hilbert space $X$ into a Hilbert space $Y$. Let $\check{T}$ be the
corresponding operator defined on the quotient space
$X/\mathcal{N}(T)$ or, equivalently, the restriction of $T$ to the
$X$-orthogonal complement of null space of operator $T$,
$\mathcal{N}(T)^\perp \subset X$. Let $\check{T}^\ast$ denote the
analogous operator for the adjoint $T^\ast$.  The following
conditions are then equivalent to each other.  
\[
\begin{array}{c}
T \text{ has a closed range }, \\[8pt]
T^\ast \text{ has a closed range }, \\[8pt]
\check{T} \text{ is bounded below, i.e. } 
\Vert T u \Vert \ge \gamma \Vert u \Vert \quad \forall u \in \mathcal{N}(T)^\perp,\\[8pt]
\check{T}^\ast \text{ is bounded below, i.e. } 
\Vert T^\ast v \Vert \ge \gamma \Vert v \Vert \quad \forall v \in \mathcal{N}(T^\ast)^\perp.
\end{array}
%\label{eq:closed_range_conditions}
\]
Note that the (maximal) constant $\gamma$ is the same for $T$ and $T^\ast$.

{{\bf Assumption 3:} The operator $A\vert_U$, restricted to the
  $L^2$-orthogonal complement $\mathcal{N}(A)^\perp$, is bounded
  below.}

The homogeneous problem~(\ref{eq:hom_BVP}) and its adjoint counterpart
are thus well-posed. More precisely, for each data function $f$ which is
$L^2$-orthogonal to the null space of the adjoint operator, a solution
exists, is unique in the orthogonal complement of the null space
of the operator (equivalently, in the quotient space), and
depends continuously on $f$.  The inverse of the maximal constant $\gamma$ is precisely the norm of the inverse
operator from $\mathcal{R}(A)$ into $\mathcal{N}(A)^\perp$ (which is equal to the norm of the solution operator from $\mathcal{R}(A^{\ast})$ into $\mathcal{N}(A^{\ast})^\perp$).

\paragraph*{Strong formulation with homogeneous BC for the Stokes problem.}
We have 
\[
C_1 u = C_1(\bfu,p,\bfsig) = \text{tr } \bfu \quad \text{and} \quad  
C_2^\prime v = C_2^\prime(\bfv,q,\bftau) = \text{tr } \bfv.
\]
Condition~(\ref{eq:adjoint_assumption}) is easily satisfied.
We have $U=V$, where
\[
U = \{ (\bfu,p,\bfsig) \in (\bfL^2(\Omega) \times L^2(\Omega) \times
\bfL^2(\Omega)) \: : \: \bfsig - p\bfI \in \bfH(\text{\bf
  div},\Omega), \bfu \in \bfH^1_0(\Omega) \}.
\]
Both $A$ and $A^\ast$ have non-trivial null space consisting
of constant pressures.  To ensure uniqueness, we have to
restrict ourselves to pressures $p$ and $q$ with zero average;
\[ p,q \in
L^2_{0} := \left\{ q \in L^2(\Omega) \; : \: \int_\Omega q = 0 \right\}.
\]
The proof that $A$ and $A^\ast$ are bounded below involves the
Ladyzenskaya inf-sup condition; for the reader's convenience we reproduce
the classical reasoning in Appendix \ref{sec:boundedness_below}.

\paragraph*{Strong formulation with non-homogeneous BC.}

We are now ready to tackle the case with a non-homogeneous boundary
condition. We have
\[ (Au,v) - \langle C_1 u,v\rangle = (u,A^\ast v) +
\langle u,C_2^\prime v\rangle \quad u \in H_A(\Omega), v \in H_{A^\ast}(\Omega) .
\]
We are interested in the operators 
\[
\begin{array}{rrl}
H_A(\Omega) \ni u \to & (Au,C_1 u) \in & L^2(\Omega) \times (\widehat{H}_{A^\ast}(\Gamma))^\prime \quad \text{ and } \\[8pt]
H_{A^\ast}(\Omega) \ni v \to & (A^\ast v,C_2^\prime v) \in & L^2(\Omega) \times (\widehat{H}_{A}(\Gamma))^\prime.
\end{array}
\label{eq:bounded_below_nhom}
\]
We have the following classical result.
\begin{theorem}
Assume
that data $f \in L^2(\Omega)$ and 
$f_D \in \mathcal{R}(C_1)$ satisfy the compatibility condition
\[
(f,v) - \langle f_D,v\rangle = 0 \quad \forall v : A^\ast v = 0, C_2^\prime v = 0.
\]
Problem~(\ref{eq:nonhom_BVP}) has a unique solution $u$ in $\mathcal{N}(A)^\perp$ that depends
continuously upon the data; i.e. there exists a constant $\tilde{\gamma}>0$, independent of the data, such that
\[
\tilde{\gamma} \Vert u \Vert_{H_A(\Omega)} \leq \left( \Vert f \Vert^2 + \Vert  f_D \Vert^2 \right)^{1/2}.
\]
The analogous result holds for the adjoint operator $(A^\ast, C_2^\prime)$.
%% \tanbui{Same result holds for adjoint operator $A^\ast$}{Here we mean the pair $(A^\ast v,C_2^\prime v)$, should we say ``Similar results hold for the adjoint equation given by $(A^\ast v,C_2^\prime v)$ since the compatibility condition and the operators are different?}.
\label{theorem:strong_nonhom_formulation}
\end{theorem}
\begin{proof}
Let $\bar{C}_1$ denote the restriction of $C_1$ to $\widehat{H}_A^1(\Gamma)$. Since $\bar{C}_1$ is then
injective and has closed range,
it admits a continuous inverse:
\[
\norm{ \hat{u}_1 }_{\widehat{H}_A(\Gamma)} = \norm{ \bar{C}_1^{-1} f_D }_{\widehat{H}_A(\Gamma)} \leq \frac{1}{\delta} \norm{ f_D }_{(\widehat{H}_{A^\ast}(\Gamma))^\prime}.
\]
Let $\hat{u} = \LRp{\hat{u}_1,0}$ and let $\tilde{\hat{u}}$ be the
minimum-energy extension of $\hat{u}$ in $H_A(\Omega)$.  We seek a solution $u$
of the form 
\[ u = u_0 + \tilde{\hat{u}},
\]
where $u_0 \in
\mathcal{N}(A\vert_U)^\perp$ solves the homogeneous BVP~(\ref{eq:hom_BVP})
with the modified right-hand side $f - A \tilde{\hat{u}}$. The load $f - A
\tilde{\hat{u}}$ satisfies the compatibility condition for the
homogeneous case. Indeed, 
\[
\begin{array}{rl}
(f - A \tilde{\hat{u}}, v) & = (f,v) - (A \tilde{\hat{u}},v) \\[8pt]
& = (f,v) - \left( (\tilde{\hat{u}},A^\ast v) - \langle f_D,v\rangle - \langle \tilde{\hat{u}},C_2^\prime v\rangle \right) \\[8pt]
& = (f,v) - \langle f_D,v\rangle = 0,
\end{array}
\]
for each $v$ such that $A^\ast v = 0$ and $C_2^\prime v = 0$.

We now have
\[
\begin{array}{ll}
\Vert u \Vert^2_{H_A} & = \Vert u_0 + \tilde{\hat{u}} \Vert^2_{H_A}\\[8pt]
& \le 2\LRp{\Vert u_0 \Vert^2_{H_A} + \Vert  \tilde{\hat{u}} \Vert^2_{H_A}}.
\end{array}
\]
Now, observe that
\[ \Vert \tilde{\hat{u}} \Vert_{H_A(\Omega)} =
\Vert \hat{u} \Vert_{\widehat{H}_A(\Gamma)} \leq \frac{1}{\delta} \Vert f_D
\Vert_{(\widehat{H}_{A^\ast}(\Gamma))^\prime}
\] 
and that
\[
\begin{array}{ll}
\Vert u_0 \Vert^2_{H_A} & = \Vert u_0 \Vert^2 + \Vert A u_0 \Vert^2 \\[8pt]
&\leq \ds \left(\frac{1}{\gamma^2} + 1 \right) \Vert A u_0 \Vert^2 \\[12pt]
& \ds \leq 2 \left(\frac{1}{\gamma^2} + 1 \right) \left[ \Vert f \Vert^2 + \frac{1}{\delta^2} \Vert f_D \Vert^2 \right].
\end{array}
\]
Combining these results ends the proof with
\[
\frac{1}{\tilde{\gamma}} \le 2\max\LRc{\sqrt{\frac{1}{\gamma^2} + 1}, \frac{1}{\delta}\sqrt{\frac{1}{\gamma^2} + \frac{3}{2}}}.
\]

\end{proof}

%% \begin{corollary}
%% Operators~(\ref{eq:bounded_below_nhom})
%% are bounded below with common constant 
%% \[
%% \tilde{\gamma} \geq (2 (\frac{1}{\gamma^2} + 1 )\max \{ 1, \frac{1}{\delta^2}\} )^{-1/2}.
%% \]
%% \end{corollary}

\paragraph*{Strong formulation with non-homogeneous BCs for the Stokes problem.}
The ranges of operators $C_1$ and $C'_2$ coincide exactly with
$\bfH^{1/2}(\Gamma)$.  The strong formulation for the non-homogeneous
Stokes problem is well-posed, provided the data $g$ and $\bfu_D$ satisfy the
compatibility condition
\[ 
\int_\Omega g = \int_{\Gamma} \bfu_D \cdot
\bfn.
\] 
The analogous conclusion holds for the adjoint operator.

\paragraph{Ultra-weak (variational) formulation.}

We are now ready to formulate the {\em ultra-weak variational
  formulation} for problem~(\ref{eq:nonhom_BVP}).  The steps are as
follows.
\begin{enumerate}
  \item Integrate by parts:
\[
(u,A^\ast v) + \langle C \text{tr}_A u, v\rangle = (f,v).
\]
  \item Split the boundary operator $C$ into $C_1$ and $C_2$ according to the decomposition in ~(\ref{eq:trace_split}):
\[
(u,A^\ast v) + \langle C_1 (\text{tr}_A u)_1, v\rangle   +  \langle C_2 (\text{tr}_A u)_2, v\rangle = (f,v). 
\]
  \item Apply the BC, moving the known term $C_1 (\text{tr}_A u)_1 = f_{D} $ to the right-hand side:
\[
(u,A^\ast v) + \langle (\text{tr}_A u)_2, C_2^\prime v\rangle = (f,v) - \langle f_D,v\rangle.
\]
\item Declare $\hat{u}_2 = (\text{tr}_A u)_2$ to be an independent unknown.  The problem then becomes
\be
\left\{
\begin{array}{ll}
\text{Find } u \in L^2(\Omega), \hat{u}_2 \in \widehat{H}_A^2(\Gamma) \text{ such that} \\[8pt]
(u,A^\ast v) + \langle \hat{u}_2, C_2^\prime v\rangle = (f,v) - \langle f_D,v\rangle \quad \forall v \in H_{A^\ast}(\Omega).
\end{array}
\right.
\label{eq:ultraweak_formulation}
\ee
\end{enumerate}
The bilinear form
\be
b((u,\hat{u}_2),v) := (u,A^\ast v) + \langle \hat{u}_2, C_2^\prime v\rangle
= (u,A^\ast v) + c(\hat{u}_2, v)
\label{eq:bilinear_form_ultraweak_formulation}
\ee
generates two associated operators $B$ and $B^{\prime}$, where
\[
b((u,\hat{u}_2),v) = \langle  B(u,\hat{u}_2),v\rangle = \langle (u,\hat{u}_2),B^\prime v\rangle.
\]
Operator $B'$ corresponds to the strong setting for the adjoint $A^\ast$ with non-homogeneous
BCs;
\[
B' v = (A^\ast v, C_2^\prime v) \in L^2(\Omega) \times
(\widehat{H}_A(\Gamma))^\prime.
\]
In order to determine the null-space of operator $B$, assume that
\[
 b((u,\hat{u}_2),v) = 0 \quad \forall v \in H_{A^\ast}(\Omega).
\]
Testing first with $v \in \mathcal{D}(\Omega)$, we deduce that $A u =
0$. Integrating the first term by parts, and testing with arbitrary
$v$, we learn that $\hat{u}_2 = u$ on $\Gamma$ and
  $C_1 u = 0$.

\begin{theorem}
Problem~(\ref{eq:ultraweak_formulation}) is well-posed. In particular,
for each $f$ and $f_D$ which satisfy the compatibility condition
\be
(f,v) - \langle f_D,v\rangle =0 \quad \forall v \in \mathcal{N}(A^\ast\vert_V),
\label{eq:compatibility_condition_ultraweak}
\ee a solution of (\ref{eq:ultraweak_formulation}) exists which is
unique up to $u \in \mathcal{N}(A\vert_U)$ and corresponding
$\hat{u}_2 \in \widehat{H}_A^2(\Gamma)$ such that $u_2 - \hat{u}_2 \in
{\mathcal{N}(C_1)}$ where $u_2$ is the corresponding component of trace
of $u$ in $\widehat{H}_A^2(\Gamma)$.

The inf-sup constant for bilinear
form~(\ref{eq:bilinear_form_ultraweak_formulation}) is equal to the
inf-sup constant of the adjoint operator  $(A^\ast, C_2^\prime)$ from
Theorem~\ref{theorem:strong_nonhom_formulation}.
\end{theorem}
\begin{proof}
We observe that the conjugate
$B^\prime$ of operator $B$ corresponding to the bilinear
form~(\ref{eq:bilinear_form_ultraweak_formulation}) coincides with the
strong form of operator $(A^\ast, C_2^\prime)$. The result is then a direct consequence of Theorem \ref{theorem:strong_nonhom_formulation}.
\end{proof}

\paragraph{Ultra-weak formulation for the Stokes problem.} 
The Stokes formulation is now just a matter of interpretation. The solution consists of $u = (\bfu,p,\bfsig)$
and unknown traction
\[
\hat{\bft} = (-\bfsig + p \bfI) \bfn
\]
Remember that only for a sufficiently regular\footnote{That is, $u \in H_A(\Omega)$.}
 solution $u$ will $\hat{\bft}$ coincide with
the trace $(-\bfsig + p \bfI) \bfn$. In the ultra-weak formulation, the traction $\hat{\bft}$
appears as an {\em independent} unknown. 
With homogeneous incompressibility constraint, the variational problem reads as follows.
\[
\left\{
\begin{array}{ll}
\text{Find }\bfu \in \bfL^2(\Omega), p \in L^2(\Omega), \bfsig \in \bfL^2(\Omega),
\hat{\bft} \in H^{-1/2}(\Gamma) \text{ such that} \\[8pt]
(\bfu, {\bf div} (\bftau - q \bfI)) + (p, - \text{div} q) + (\bfsig, \bftau + \bfnab \bfv) 
+ \langle \hat{\bft},\bfv\rangle = (\bff,\bfv) - \langle \bfu_D,(-\bftau + q\bfI) \bfn\rangle \\[8pt]
\hfill \forall (\bfv,q,\bftau) \text{ such that } 
\bftau - q\bfI \in \bfH(\text{\bf div},\Omega), \bfv \in \bfH^1(\Omega).
\end{array}
\right.
\]
The load is specified by a body force $\bff \in \bfL^2(\Omega)$ and a velocity $\bfu_D \in \bfH^{1/2}(\Gamma)$
on the boundary with vanishing normal component:
\[
\int_{\Gamma} \bfu_D \cdot \bfn = 0.
\]
The solution is determined up to a constant pressure $p_{0}$
{and corresponding constant traction $\hat{\vect{t}}_{0} = p_{0} \bfn$.}

Notice that there are no boundary conditions imposed on the test functions. This is important
from a practical point of view.

{
\begin{remark}
{\bf Strong versus weak imposition of boundary conditions.}
In classical variational formulations for second order PDEs, we distinguish between {\em strong}
(Dirichlet) BCs and weak (Neumann) BCs. Dirichlet BCs are accounted for by coming up
with a finite-energy lift of the BC data, and looking for a solution to the 
problem with homogeneous BCs and a modified ``load vector'' that includes the action
of the bilinear form on the lift \cite[p. 34]{hpbook}. In practice, the Dirichlet data is first projected
(interpolated) into the trace of FE space and then lifted with FE shape functions.
By contrast to the Dirichlet BC case, Neumann BCs only contribute to the load vector. 
The terms ``strong'' and ``weak'' refer to the fact that, with Dirichlet data in the
FE space, Dirichlet BCs are enforced pointwise, whereas Neumann BCs, in general, are satisfied
only in the limit.
}

{ In an ultra-weak variational formulation, each BC may
  be specified either in a ``strong'' or ``weak'' way. The formulation
  discussed above corresponds to a weak imposition of the BC. Data
  $f_D$ contributes to the load vector and is accounted for on the
  element level, in the integration for the load vector. An alternate,
  strong imposition of the same BC, starts with finding a trace lift
  $\hat{u}_0$ of the BC,
$$
C_1 \hat{u}_0 = f_D.
$$
Notice that the lift may have a non-zero $\widehat{H}_A^2$-component but the final trace will
be equal to the sum of the lift and an unknown component $\hat{u}_2 \in \widehat{H}_A^2$,
$$
\hat{u} = \hat{u}_0 + \hat{u}_2.
$$
The term $\langle f_D,v \rangle$ on the right-hand side of~(\ref{eq:bilinear_form_ultraweak_formulation})
is simply replaced with $c(u_0,v)$. 
The rest of the formulation remains unchanged.
The difference between the two formulations becomes
more visible in context of discontinuous test functions discussed next.
\label{remark:strong_vs_weak_BC}
\end{remark}
}

\subsection{DPG formulation}\label{sec:AnalysisDPGFormulation}

The essence of the DPG formulation lies in extending the concept of the ultra-weak variational
formulation to broken test spaces. We begin by partitioning domain $\Omega$ into finite elements $K$
and integrating by parts on each element:
\[
(Au,v)_{K} = (u,A^\ast v)_{K} + c_{\ptl K}(u,v) \quad u \in H_A(K), v \in H_{A^\ast}(K).
\]
Next, we sum over all elements to obtain
\[
\underbrace{\sum_K (Au,v)_{K}}_{ = (Au,v)}
 = \underbrace{\sum_K (u,A^\ast v)_{K}}_{=: (u,A_h^\ast v)_{h}}
 + \underbrace{\sum_K c_{\ptl K}(u,v)}_{=: c_h(u,v)}
 \quad u \in H_A(\Omega), v \in H_{A^\ast}(\Omega_h).
\]
Here we take $u$ to be globally conforming but allow $v$ to come from the broken graph space
\[
H_{A^\ast}(\Omega_h) := \left\{ v \in L^2(\Omega) \: : \: A^\ast v\vert_K \in L^2(K) \: \forall K\right\}.
\]
The index $h$ on the domain
indicates that the formal adjoint operator is to be
understood element-wise. The boundary term $c_{h}$ now extends to the whole skeleton $\Gamma_h = \cup_K \ptl K$.
For the internal skeleton $\Gamma_h^0 = \Gamma_h - \Gamma$, this term represents the action of traces $\hat{u}$
on the jumps of traces $\hat{v}$. As with $H^{1/2}(\Gamma_h)$ and $H^{-1/2}(\Gamma_h)$,
we introduce a general, abstract space of traces on the skeleton,
\[
\widehat{H}_A(\Gamma_h) := \left\{
\hat{u} = \{ \hat{u}_K \} \in \prod_K \widehat{H}_A(\ptl K) \: : \: \exists u \in H_A(\Omega) : 
\text{tr}_A u\vert_K =  \hat{u}_K \right\},
\]
and the corresponding subspace of traces that vanish on $\Gamma = \ptl \Omega$,
\[
\hat{\tilde{H}}_A(\Gamma_h) := \left\{
\hat{u} = \{ \hat{u}_K \} \in \prod_K \widehat{H}_A(\ptl K) \: : \: \exists u \in \tilde{H}_A(\Omega)
 : 
\text{tr}_A u\vert_K =  \hat{u}_K \right\},
\]
where
\[
\tilde{H}_A(\Omega) = \left\{ u \in H_A(\Omega) \: : \: \text{tr }u = 0 \text{ on } \Gamma \right\}.
\]
As usual, we equip the trace space with the minimum energy extension norm.

Any function $u \in H_A(\Omega)$ can be decomposed into an extension of its trace to $\Gamma$
and a component that vanishes on $\Gamma$:
\[
u = E(\text{tr } u ) + \tilde{u},\quad \tilde{u} \in \tilde{H}_A(\Omega).
\]
If the extension $E(\text{tr } u )$ is the minimum-energy extension, the decomposition above
is $H_A$-orthogonal. This implies a corresponding decomposition for traces $\hat{u}
\in \widehat{H}_A(\Gamma_h)$:
\[
\hat{u} = 
{\hat{E}}\hat{u}_0 + \hat{\tilde{u}},\quad \hat{\tilde{u}} \in \hat{\tilde{H}}_A(\Gamma_h).
\]
Here {
$\hat{u}_0 \in \widehat{H}_A(\Gamma)$ is the restriction of $\hat{u}$ to $\Gamma$ and  
$\hat{E}\hat{u}_0 \in \widehat{H}_A(\Gamma_h)$ is any extension of $\hat{u}_0$ back to the whole
skeleton $\Gamma_h$.}
Again, if we use the minimum-energy extension, the decomposition
is $\widehat{H}_A(\Gamma_h)$-orthogonal. We have
\be
\widehat{H}_A(\Gamma_h) = {\hat{E}} \widehat{H}_A(\Gamma) \oplus \hat{\tilde{H}}_A(\Gamma_h).
\label{eq:trace_decomposition}
\ee

By construction, we have a generalization of the trace operator to the whole skeleton,
\[
\text{tr} : H_A(\Omega) \twoheadrightarrow \widehat{H}_A(\Gamma_h).
\]
The skeleton term
$c_h(\hat{u},\hat{v})$ is well-defined for 
$\hat{u} \in \widehat{H}_A(\Gamma_h)$ and $\hat{v} = \{\hat{v}_K \} \in \prod_K H_{A^\ast}(\ptl K)$.
We also have the condition
\[
\begin{array}{c}
\left((c_h(\hat{u},\hat{v}) = 0 \: \forall \hat{u} \in \hat{\tilde{H}}_A(\Gamma_h) \right)
\Longleftrightarrow v \in H_{A^\ast}(\Omega). \\[8pt]
\end{array}
\]
Indeed, if we restrict ourselves to a globally conforming test function, the skeleton term reduces
to a term that involves only the domain boundary $\Gamma$, where the trace $\hat{u}$ vanishes. The converse follows
from the definition of distributional derivatives. 
Indeed, for any test function $\phi \in \mathcal{D}(\Omega)$,
we have
\[
c_h (\text{tr} \phi, v) = (A \phi,v) - (\phi,A^\ast_h v)_h = 0,
\]
which proves that the union of element-wise values $A^\ast_h v$ (which lives in $L^2(\Omega)$) is
equal to $A^\ast v$ in the sense of distributions.

We now use the decomposition of traces~(\ref{eq:trace_decomposition})
to set up the boundary operators. 
{
Recall that condition~(\ref{eq:adjoint_assumption}) decomposed the
trace space $\widehat{H}_A(\Gamma)$
into  the direct sum of the nullspaces of operators $C_2$ and $C_1$:
\[
\widehat{H}_A(\Gamma) = \widehat{H}_A^1(\Gamma) \oplus \widehat{H}_A^2(\Gamma),
\quad \hat{u} = \hat{u}_1 + \hat{u}_2.
%\label{eq:trace_split_h}
\]
The first term is known from the boundary condition; the second remains as an additional
unknown.
We have
\be
\begin{array}{ll}
c_h(\hat{u},\hat{v}) & = c_h(\hat{E}\hat{u}_0,\hat{v}) + c_h(\hat{\tilde{u}},\hat{v}) \\[8pt]
& 
= c_h(\hat{E} \hat{u}_0^1, \hat{v}) + c_h(\hat{E} \hat{u}_0^2, \hat{v}) 
+  c_h(\hat{\tilde{u}},\hat{v}).
\end{array}
\label{eq:split_ch}
\ee
For conforming test functions $\hat{v} \in \widehat{H}_{A^\ast}(\Gamma_h)$, 
the bilinear form on the skeleton reduces to the
bilinear form on the domain boundary,
$$
c_h(\hat{u},\hat{v}) = c(\hat{u},\hat{v}) = c(\hat{u}_0^1,\hat{v}) + c(\hat{u}_0^2,\hat{v}) 
= \langle f_D, \hat{v} \rangle + c(\hat{u}_0^2,\hat{v}).
$$
In particular, this is independent of the choice of lift $\hat{E}$.
To impose the BC strongly, we need to find a trace lift of the BC data $f_D$,
$$
C_1 \hat{u}_0 = f_D,
$$
move the term with the lift to the right-hand side, and look for the unknown component $\hat{u}_2$
of the trace on $\Gamma$. The final formulation reads as follows.
\[
\left\{
\begin{array}{ll}
u \in L^2(\Omega), \hat{u} \in \hat{E} \widehat{H}_A^2(\Gamma) \oplus \hat{\tilde{H}}_A(\Gamma_h)  \\[8pt]
(u,A^\ast_h v)_h +  c_h(\hat{u},v) = (f,v) - c_h(\hat{E}\hat{u}_0,v)
\quad \forall v \in H_{A^\ast}(\Omega_h)
\end{array}
\right.
%\label{eq:abstract_DPG_formulation_strong}
\]
However, if we decide to enforce the BC in a weak way, we need to replace the first
term on the right-hand side of ~(\ref{eq:split_ch}) with an extension of
known BC data $\langle f,v\rangle$ to discontinuous test functions.
This is always possible as the term $c_h(\hat{E} \hat{u}_0,v)$ provides an example of such an extension.
}

{
The final abstract DPG formulation\footnote{That is, the ultra-weak variational formulation with broken test functions.}
is then
\be
\left\{
\begin{array}{ll}
u \in L^2(\Omega), \hat{u} \in \hat{E} \widehat{H}_A^2(\Gamma) \oplus \hat{\tilde{H}}_A(\Gamma_h)  \\[8pt]
(u,A^\ast_h v)_h +  c_h(\hat{u},v) = (f,v) - \langle f_D, v\rangle_{\Gamma_h} 
\quad \forall v \in H_{A^\ast}(\Omega_h).
\end{array}
\right.
\label{eq:abstract_DPG_formulation}
\ee
}

The bilinear\footnote{Sesquilinear for complex-valued problems.} form corresponding to the formulation 
\[
b((u,\hat{u}),v) := (u,A^\ast_h v)_h  + c_h(\hat{u},v)
\]
generates operators $B$ and $B'$, where
\[
 b((u,\hat{u}),v) = \langle B(u,\hat{u}),v\rangle 
= \langle (u,\hat{u}),B'v\rangle.
\]
The null space of conjugate operator $B'$ coincides with the null space of $A^\ast\vert_V$. Indeed, let
\[
b((u,\hat{u}),v) = 0 \quad \forall (u,\hat{u}).
\label{eq:null_space_conjugate_operator}
\]
Taking arbitrary
$\hat{u} \in \hat{\tilde{H}}_A(\Gamma_h)$, we conclude that $v$ must be globally conforming, 
so the bilinear form in~(\ref{eq:null_space_conjugate_operator}) reduces to 
the bilinear form~(\ref{eq:bilinear_form_ultraweak_formulation}).

The null space of DPG operator $B$ consists of all $(u,\hat{u})$ such that
\[
 b((u,\hat{u}),v) = 0 \quad \forall v \in H_{A^\ast}(\Omega_h).
\]
As with the ultra-weak variational formulation, we first test with
$v \in \mathcal{D}(\Omega)$ to conclude that $A u = 0$. Integrating the first term by parts
and testing with arbitrary $v$, we conclude that $\hat{u} = u$ on $\Gamma_h$. In particular, as
$\hat{u}\vert_\Gamma \in \widehat{H}^2_A(\Gamma)$, this implies that $C_1 u = 0$ on $\Gamma$.

We are in a position to state our main abstract result.
\begin{theorem}
Problem~(\ref{eq:abstract_DPG_formulation}) is well-posed. More precisely, for any 
data $f$ and $f_{D}$ that satisfy the compatibility condition~(\ref{eq:compatibility_condition_ultraweak}), 
the problem has a solution $(u,\hat{u})$ such that $(u,\hat{u}\vert_\Gamma)$
coincides with the solution of~(\ref{eq:ultraweak_formulation}).
The bilinear form satisfies
the inf sup condition
\[
\sup_{v \in H_{A^\ast}(\Omega_h)} 
\frac{\vert (u,A^\ast_h v)_h + c_h(\hat{u},v) \vert}{\Vert v \Vert_{H_{A^\ast}(\Omega_h)}}
\geq \gamma_{DPG} 
\left( \Vert u \Vert_{L^2(\Omega)}^2 + \Vert \hat{u} \Vert_{\widehat{H}_A(\Gamma_h)}^2 \right)^{1/2}
%\sqrt{ \Vert u \Vert_{L^2(\Omega)}^2 + \Vert \hat{u} \Vert_{\widehat{H}_A(\Gamma_h)}^2 }
\]
for all $\hat{u} \in \hat{E} \widehat{H}_A^2(\Gamma) \oplus
 \hat{\tilde{H}}_A(\Gamma_h)$, and $u \in L^2(\Omega)$ {orthogonal to the null space:}
\[
\left\{ (u,\hat{u}) \: : \: u \in \mathcal{N}(A\vert_U) \text{ and } \hat{u} = u \text{ on }\Gamma_h \right\}
\]
The inf-sup constant $\gamma_{DPG}$ is mesh-independent and
$\gamma_{DPG}=$ {$O(\gamma)$ and $O(\tilde{\gamma})$ for the adjoint operator.}
\end{theorem}
\begin{proof}
We will switch the order of spaces in the inf-sup condition and prove that
\be
\sup_{\substack{u \in L^2(\Omega)\\ \hat{u} \in E \widehat{H}_A^2(\Gamma) \oplus
 \hat{\tilde{H}}_A(\Gamma_h)
}} 
\frac{\vert (u,A^\ast_h v)_h + c_h(\hat{u},v) \vert}
%{\sqrt{ \Vert u \Vert_{L^2(\Omega)}^2 + \Vert \hat{u} \Vert_{\widehat{H}_A(\Gamma_h)}^2 }
{\left( \Vert u \Vert_{L^2(\Omega)}^2 + \Vert \hat{u} \Vert_{\widehat{H}_A(\Gamma_h)}^2 \right)^{1/2}
}
\geq \gamma_{DPG} 
\Vert v \Vert_{H_{A^\ast}(\Omega_h)}
\label{eq:inverted_infsup}
\ee
for all $v$ $L^2$-orthogonal to $\mathcal{N}(A^\ast\vert_V)$.

{\bf Step 1:} Consider first a special case when $A^\ast_h v = 0$. Consider a conforming $u \in 
(\mathcal{N}(A\vert_U))^\perp \subset U$ such
that $A u = v$. Since $v \in (\mathcal{N}(A^\ast\vert_V))^\perp$, such a $u$ exists. We then have
\[
\begin{array}{ll}
\Vert v \Vert^2 & \ds = (A u, v) = \underbrace{(u,A^\ast_h v)}_{= 0} + c_h(\text{tr } u,v) \\[12pt]
& \ds \le \frac{\vert  c_h(\text{tr } u,v) \vert}{\Vert \text{tr } u \Vert } \: \Vert \text{tr } u \Vert \\[12pt]
&\ds \leq \sup_{\hat{u}} \frac{\vert  c_h(\hat{u},v) \vert}{\Vert \hat{u} \Vert } \: \Vert u \Vert_{H_A(\Omega)}
\\[12pt]
& \ds \leq \frac{1}{\gamma} \sup_{\hat{u}} \frac{\vert  c_h(\hat{u},v) \vert}{\Vert \hat{u} \Vert } \Vert v \Vert.
\end{array}
\]
Dividing both sides by $\Vert v \Vert$, we get the required inequality.

{\bf Step 2:} Now let $v$ be arbitrary. Consider a conforming $\tilde{v} \in H_{A^\ast}(\Omega)$ such that
$A^\ast \tilde{v} = \ A^\ast_h v$. By {Assumption 1}, such a function always exists and can
be interpreted as a solution to the strong adjoint problem with non-homogeneous BC data $f_{D} = C^\prime_2 \tilde{v}$:
\[
\left\{
\begin{array}{ll}
A^\ast \tilde{v}  = A^\ast_h v \\[8pt]
C^\prime_2 \tilde{v}  = f_{D}.
\end{array}
\right.
\]
To ensure uniqueness and boundedness in the $L^2$-norm, we assume that $\tilde{v}$ is $L^2$-orthogonal
to the null space $\mathcal{N}(A^\ast\vert_V)$.

Now, by construction, $A_h( v - \tilde{v}) = 0$ and 
$v - \tilde{v} \in (\mathcal{N}(A^\ast\vert_V))^\perp$
so, by the Step 1 result,
the difference $ v - \tilde{v}$ is bounded in both $L^2$ and 
$H_{A^\ast}$ norms by the supremum in~(\ref{eq:inverted_infsup}). We thus need only demonstrate that
we can control the norm of the conforming $\tilde{v}$. But, if we restrict ourselves
in~(\ref{eq:inverted_infsup}) to conforming test functions, the bilinear form collapses 
to~(\ref{eq:bilinear_form_ultraweak_formulation}).

This finishes the proof.
\end{proof}

\subsection{DPG formulation for the Stokes problem}

We begin by emphasizing the global character of decomposition of traces in~(\ref{eq:trace_decomposition}).
Velocity trace $\hat{\bfu} \in \bfH^{1/2}(\Gamma_h)$ can be decomposed into 
an extension of the velocity trace on the boundary $\Gamma$
and the trace on the internal skeleton $\Gamma_h^0$:
\[
\hat{\bfu} = \hat{E} \hat{\bfu}_0 + \hat{\tilde{\bfu}}
\]
In FE computations, traces are approximated with functions that are globally continuous
on the skeleton $\Gamma_h$.
The trace $\hat{\bfu}_0$, which is known from the boundary condition, has to be lifted to the whole skeleton.
In computations, we use FE shape functions and lift $\hat{\bfu}_0$ only into the
 layer of elements neighboring $\Gamma$.
The unknown part of velocity trace $\hat{\tilde{\bfu}} \in \tilde{\bfH}^{1/2}(\Gamma^0_h)$ 
lives on the internal skeleton only.

The unknown traction trace $\hat{\bft} \in \bfH^{-1/2}(\Gamma_h)$ lives on the whole skeleton.
On the continuous level, the decomposition of traction into 
a lift of its restriction to $\Gamma$ and the remaining component $\hat{\tilde{\bft}} 
\in \tilde{\bfH}^{-1/2}(\Gamma)$ that lives on the internal skeleton $\Gamma_h^0$ is also global.
In 2D for instance, 
for $\bft$ from a {\em standard} boundary space $\bfH^{-1/2}(\Gamma)$, the corresponding
restriction to an edge $e$ of an element $K$ adjacent to boundary $\Gamma$ lives only in $\bfH^{-1/2}(e)$
and {\em cannot} just be extended by zero to a functional in $\bfH^{-1/2}(\ptl K)$.
However, the conformity present in the definition of space $\bfH^{-1/2}(\Gamma_h)$ is so weak 
that it does
not translate into any global continuity conditions for the approximating polynomial spaces that
are discontinuous from edge to edge.

For the Stokes problem, the boundary operators represent exactly the velocity and traction components
of the solution trace;
\[
C_1 (\hat{\bft},\hat{\bfu}) = \bfu,\quad C_2 (\hat{\bft},\hat{\bfu}) = \hat{\bft}.
\]
{
The difference between the strong and weak imposition of BCs is, in our case, insignificant.
The abstract $\langle f_D,v \rangle$ term corresponds to $\langle\bfu_D,\bfr\rangle_\Gamma$,
where $\bfr$ is the traction component of the test function.
Its extension to discontinuous test functions $v$ is constructed by lifting Dirichlet data $\bfu_D$ to the
whole skeleton. The strong imposition of the BCs is essentially the same. The abstract lift $\hat{u}_0$
of $\bfu_D$ can be selected to be $(\bfu_D,{\bf 0})$ (zero traction) and, if we use the same extension
of $\bfu_D$ to the whole skeleton, the two formulations will be identical. A subtle difference
lies in the way we treat those lifts in FE computations. Assume, e.g., that we approximate
traces with quadratics.
Assume that we have a non-polynomial
data $u_D$. With the strong imposition of BCs, we first interpolate the data with quadratics
and use quadratic shape functions to lift it to the whole skeleton. The contributions
to the load vector will be computed by integrating the quadratic lifts against test functions.
With the weak imposition of the BCs, the non-polynomial $\bfu_D$ on $\Gamma$
will be integrated directly against the test functions and, in general, will yield different
values. Additionally, 
even if we lift the non-polynomial $\bfu_D$ to the whole skeleton
with the same quadratic shape functions, the lifts will differ on the internal skeleton and,
consequently, the resulting approximate traces will differ. In the limit, of course,
the difference will disappear.}

The null space of conjugate operator $B'$ coincides with the null space of adjoint $A^\ast$ with homogeneous
BC $\bfv = {\bf 0}$ on $\Gamma$ and consists of constant pressures
\[
\{ ({\bf 0},c,{\bf 0}) \: : \: c \in \doubleIR \}.
\]
The null space of operator $B$ is the same as that for the operator corresponding to the
ultra-weak formulation,
\[
\{ ((\bfu,p,\bfsig),\hat{\bft}) \: : \: \bfu = {\bf 0}, p = c , \bfsig = {\bf 0}, \hat{\bft} = c \bfn 
\text{ where } c \in \doubleIR \}.
\]
The non-trivial null spaces imply the compatibility condition for the load and non-uniqueness of the solution.
The compatibility condition for the load involves the right-hand side $g$
of the divergence equation\footnote{$g=0$ in practice.} and
the velocity trace BC data $\bfu_D$, and takes the form 
\[
\int_\Omega g = \int_{\Gamma} \bfu_D \cdot \bfn.
\]
This well-known condition can be obtained immediately by integrating the divergence equation
and using the boundary condition on $\bfu$:
\[
\int_\Omega g = \int_\Omega \text{div } \bfu = \int_\Gamma \bfu \cdot \bfn = \int_\Gamma \bfu_D \cdot \bfn.
\]
Assumption 1 thus reduces to the condition that the divergence operator is surjective, a well-known
fact.

With data satisfying the compatibility condition, the solution (pressure and tractions) is determined
up to a constant. In computations, the constant can be fixed by implementing an additional scaling
condition. We can enforce, for instance, zero average pressure in one particular element, or zero
average normal traction on a particular edge. The scaling will affect the ultimate values for pressure
and tractions, but has no effect on the velocity or on its gradient and trace.

\subsection{A summary}

We have presented a general theory on well-posedness for DPG variational formulation for an arbitrary
system of differential operators represented by an abstract operator $A$. 
We have made a number of assumptions, which we now summarize.
\begin{itemize}
  \item Operator $A$ and its formal adjoint $A^\ast$ are surjective ({Assumption 1}).
  \item Both energy graph spaces $H_A(\Omega)$ and $H_{A^\ast}(\Omega)$ admit corresponding
trace spaces $\widehat{H}_A(\ptl \Omega),\widehat{H}_{A^\ast}(\ptl \Omega)$.
  \item The boundary bilinear term $c(u,v)$ resulting from integration by parts is definite. 
  \item Boundary operator $C_1$ has been selected in such a way that {Assumption 2}
 is satisfied.
  \item With homogeneous boundary condition $C_1 u = 0$ in place, operator $A$ is bounded below
in the $L^2$-orthogonal complement of its null space ({Assumption 3}).
\end{itemize}
With these conditions satisfied, the DPG formulation is well-posed. The corresponding inf-sup constant
is mesh-independent.
Sweeping technical details under the carpet, this is the main
take-home message: {\em boundedness below of the strong operator with homogeneous BC implies
the inf-sup condition for the DPG formulation with a mesh-independent constant.}

The general theory is guiding us how to select unknown traces on the skeleton.
The energy setting involves graph norms for both operator $A$ and its formal adjoint $A^{\ast}$. The graph norm
in the test space is equivalent to the {\em optimal test norm} \cite{DPG4} with {\em mesh-independent} 
equivalence constants. The graph norm for $A$ implies the energy setting for unknown traces and
the minimum energy extension norm.

All these conditions are satisfied for the Stokes problem.

\subsection{Boundedness Below of the First-Order Stokes Operator with Homogeneous BCs}
\label{sec:boundedness_below}
Finally, for completeness we show that the operator corresponding to our first-order Stokes problem with homogeneous BCs is bounded below.  While in the above we have taken $\mu=1$, here we consider the more general case of constant $\mu > 0$.

Recall the classical strong form of the Stokes problem:

\begin{align}
- \mu \Delta \vect{u} + \NVRgrad p &= \vect{f} & \text{ in } \Omega, \label{NVR:eq:strongfirst1} \\
\NVRdiv \vect{u} &= 0 & \text{ in } \Omega, \\
\vect{u} &= \vect{u}_D & \text{ on } \partial\Omega.\label{NVR:eq:stronglast1}
\end{align}

Recall also our first-order system for the Stokes equations:
\begin{subequations}
\eqnlab{StokesFirstOrder}
\begin{align}
- \NVRdiv \NVRtensor{\sigma} + \NVRgrad p &= \vect{f} & \text{ in
} \Omega, \label{NVR:eq:strongfirst2} \\ \NVRdiv \vect{u} &=
\NVRtensor{0} & \text{ in } \Omega, \\ \frac{1}{\mu}\NVRtensor{\sigma} - \NVRgrad
\vect{u} &= 0 & \text{ in } \Omega,\\ \vect{u} &= \vect{u}_D & \text{ on
} \partial\Omega.\label{NVR:eq:stronglast2}
\end{align}
\end{subequations}

If we introduce $\A : \HA \rightarrow \L$
with group variable $u = (\vect{u},p,\NVRtensor{\sigma})$,  the Stokes equation in first order form \eqnref{StokesFirstOrder}, ignoring the boundary conditions,
can be written succinctly as
\begin{align}
\A u \NVReqdef \left[\begin{array}{c}
- \NVRdiv \NVRtensor{\sigma} + \NVRgrad p\\
\NVRdiv \vect{u}\\
\frac{1}{\mu}\NVRtensor{\sigma} - \NVRgrad \vect{u}\end{array}\right]
= \left[\begin{array}{c}
\vect{f} \\
0 \\
\NVRtensor{0}
\end{array}\right].\label{NVR:eq:operatorAdefined}
\end{align}

Considering linear operator $\A$ as defined in equation (\ref{NVR:eq:operatorAdefined}) operating on group variable $u = (\vect{u},p,\NVRtensor{\sigma})$, we seek to show that $||\A u||_{L^{2}} \geq \gamma ||u||_{\HA}$.\\

\subsubsection{$||\A u||_{\Omega} \geq \gamma ||u||_{\HA}$}
Adding right-hand sides $g$ and $\NVRtensor{h}$

\begin{align}
-\NVRdiv \NVRtensor{\sigma} + \NVRgrad p &= \vect{f} & \text{ in } \Omega, \label{NVR:eq:strongfirst3} \\
\NVRdiv \vect{u} &= g & \text{ in } \Omega, \\
\frac{1}{\mu}\NVRtensor{\sigma} - \NVRgrad \vect{u} &= \NVRtensor{h} & \text{ in } \Omega, \label{NVR:eq:strongsecondtolast3} \\
\vect{u} &= \vect{0} & \text{ on } \partial\Omega,\label{NVR:eq:stronglast3}
\end{align}
we have that $\A u = (\vect{f},g,\NVRtensor{h})$.  If we can establish bounds for the $L^{2}$ norms of each of the solution variables in terms of $L^{2}$ norms on $\vect{f},g,$ and $\NVRtensor{h}$, then we will have the required lower bound $|| \A u ||_{\Omega} \geq \gamma || u ||_{\HA}$, where $|| u ||_{\HA} \NVReqdef \left( || \A u ||_{\Omega}^{2} + || u ||_{\Omega}^{2}  \right)^{1/2}$.\\

Note that, by linearity of $\A$, it suffices to consider cases in which only one of $\vect{f},g,$ and $\NVRtensor{h}$ is non-zero.  We consider each of these cases in the following three subsections.\\

\subsubsection{$\vect{f} \neq \vect{0},g=0,\NVRtensor{h}=\NVRtensor{0}$}
In this case, we have exactly the system (\ref{NVR:eq:strongfirst2})-(\ref{NVR:eq:stronglast2}), which reduces (in a distributional sense) to (\ref{NVR:eq:strongfirst1})-(\ref{NVR:eq:stronglast1}).  Testing the first equation with the velocity $\vect{u} \in \vect{H}^{1}_{0}(\Omega)$, we have
\begin{align*}
- (\mu \Delta \vect{u}, \vect{u})_{\Omega} + (\NVRgrad p, \vect{u})_{\Omega} &= (\vect{f},\vect{u})_{\Omega}.\\
\end{align*}
Integrating by parts, we obtain:
\begin{align*}
(\mu \NVRgrad \vect{u}, \NVRgrad \vect{u})_{\Omega} - \langle \mu \NVRgrad \vect{u} \cdot \vect{n}, \vect{u} \rangle_{\partial \Omega} - (p, \NVRdiv u)_{\Omega} + \langle p, \vect{u} \cdot \vect{n} \rangle_{\partial \Omega} &= (\vect{f},\vect{u})_{\Omega}.
\end{align*}

Noting that $\vect{u} = 0$ on $\partial \Omega$ and that $\NVRdiv \vect{u} = 0 $ in $\Omega$, this reduces to:

\begin{align*}
\mu (\NVRgrad \vect{u}, \NVRgrad \vect{u})_{\Omega} = \mu ||\NVRgrad \vect{u}||^{2}_{\Omega} = \mu || \NVRtensor{ \sigma }||^{2}_{\Omega} &= (\vect{f},\vect{u})_{\Omega} \\
&\leq || f ||_{\Omega} || \vect{u} ||_{\Omega}\\
&\leq C_{P} || f ||_{\Omega} || \NVRgrad \vect{u} ||_{\Omega},
\end{align*}
where $C_{P}$ is the Poincar\'{e} constant.  Thus $ || \NVRtensor{ \sigma }||_{\Omega} \leq \frac{C_{P}}{\mu} || f ||_{\Omega}$, and $|| \vect{u} || \leq \frac{C_{P}^{2}}{\mu} || f ||_{\Omega}$.

To bound the pressure $p$, we require a result by Ladyzhenskaya \cite{Ladyzhenskaya} for $p \in L^{2}_{0} \NVReqdef \{w \in L^{2}(\Omega) : \int_{\Omega} w = 0 \}$:
\begin{align*}
\sup_{\vect{v} \in \vect{H}^{1}(\Omega)} \frac{(p, \NVRdiv \vect{v})_{\Omega}}{\norm{ \vect{v} }_{H^{1}(\Omega)} } \geq \beta \norm{p}_{\Omega}
\end{align*}
for some constant $\beta > 0$.  Testing equation (\ref{NVR:eq:strongfirst1}) with $\vect{v} \in \vect{H}^{1}_{0}(\Omega)$, we have
\begin{align*}
(\NVRgrad p, \vect{v})_{\Omega} = (\vect{f}, \vect{v})_{\Omega} + (\mu \Delta \vect{u}, \vect{v})_{\Omega}.
\end{align*}

Integrating by parts, dividing by $\norm{ \vect{v} }_{H^{1}(\Omega)}$ and taking the supremum:
\begin{align*}
\sup - \frac{(p, \NVRdiv \vect{v})}{\norm{ \vect{v} }_{H^{1}(\Omega)}} &= \sup \left\{\frac{(\vect{f}, \vect{v})}{\norm{ \vect{v} }_{H^{1}(\Omega)}} - \frac{\mu (\NVRgrad \vect{u}, \NVRgrad \vect{v})}{\norm{ \vect{v} }_{H^{1}(\Omega)}}\right\} \\
&\leq \frac{\norm{\vect{f}} \norm{\vect{v}}_{L^{2}}}{\norm{ \vect{v} }_{H^{1}(\Omega)}} + \mu \norm{\NVRgrad \vect{u}} \leq \norm{\vect{f} } + \mu \frac{C_{P}}{\mu} \norm{\vect{f}} = (1 + C_{P}) \norm{\vect{f}}.
\end{align*}
By the Ladyzhenskaya result, we then have $\norm{p} \leq \frac{1 + C_{P}}{\beta} \norm{\vect{f}}$, bounding $p$, as required.

\subsubsection{$\vect{f} = \vect{0}, g \neq 0,\NVRtensor{h}=\NVRtensor{0}$} In this case, we have
\begin{align}
- \NVRdiv \NVRtensor{\sigma} + \NVRgrad p &= \vect{0} & \text{ in } \Omega, \label{NVR:eq:gstrongfirst} \\
\NVRdiv \vect{u} &= g & \text{ in } \Omega, \\
\frac{1}{\mu} \NVRtensor{\sigma} - \NVRgrad \vect{u} &= 0 & \text{ in } \Omega, \label{NVR:eq:gstrongsigmadef}\\
\vect{u} &= \vect{0} & \text{ on } \partial\Omega.\label{NVR:eq:gstronglast}
\end{align}

We must also assume compatibility between $g$ and the boundary condition on $\vect{u}$; that is, that $g$ has zero average on $\Omega$:
\begin{align*}
\int_{\Omega} g = \int_{\partial \Omega} \vect{u} \cdot \vect{n} = 0.
\end{align*}

Now, by surjectivity of $\NVRdiv : \NVRHdiv \rightarrow L^{2}$, there exists $\vect{u}_{0}$ such that $\NVRdiv \vect{u}_{0} = g$.  By the Lax-Milgram theorem, we have $\exists ! \phi \in H^{1}_{0} : \vect{u}_{0} = \NVRgrad \phi$, so that $\Delta \phi = g$ and, assuming that $\Omega$ is convex, then by the Elliptic Regularity theorem (see \cite[p. 214]{Folland} for a proof), $\phi \in H^{2}$ and:
\begin{align*}
\norm{\phi}_{H^{2}} &\leq C \norm{g}\\ % SEE ARBOGAST/BONA, p. 223 (Elliptic Regularity, section 8.5.4, Theorem 8.13)---references [GT] or [Fo] for a proof
\implies \norm{\NVRgrad \phi}_{H^{1}} &\leq C \norm{g},
\end{align*}
for some $C > 0$ independent of $g$ and $\phi$.  That is, in fact $\vect{u}_{0} \in H^{1}$ and $\norm{ \vect{u}_{0} }_{H^{1}} \leq C \norm{g}$.

Setting $\vect{w} = \vect{u} - \vect{u}_{0}$, we have $\NVRdiv \vect{w} = 0$, and $\vect{w} = 0$ on $\partial \Omega$.  Note that we can recover $-\mu \Delta \vect{u} + \NVRgrad p = 0$ by substituting (\ref{NVR:eq:gstrongsigmadef}) into (\ref{NVR:eq:gstrongfirst}).  Testing this with $\vect{w}$ and integrating by parts, we obtain:
\begin{align*}
\mu (\NVRgrad \vect{u},\NVRgrad \vect{w})_{\Omega} &= 0\\
\mu (\NVRgrad \vect{w} + \NVRgrad \vect{u}_{0},\NVRgrad \vect{w})_{\Omega} &= 0\\
\implies \norm{\NVRgrad \vect{w}}^{2} &= -(\NVRgrad \vect{u}_{0}, \NVRgrad \vect{w}) \\
&\leq \norm{ \NVRgrad \vect{u}_{0} } \norm{ \NVRgrad \vect{w} } \\
&\leq C \norm{g} \norm{ \NVRgrad \vect{w} },
\end{align*}
so that $\norm{ \NVRgrad \vect{w} } \leq  C \norm{ g }$, and therefore as before we obtain a bound on $\norm{\NVRtensor{\sigma}} = \norm{\NVRgrad \vect{u}} \leq 2 C \norm{g}$, and again by means of the Poincar\'{e} inequality we may bound $\norm{\vect{u}} \leq C_{P} \norm{\NVRgrad \vect{u}} \leq 2 C C_{P} \norm{ g }$ as well.

The bound on $p$ is established exactly as before, except that now $\vect{f} = \vect{0}$, so that we obtain the bound $\norm{p} \leq \frac{\mu}{\beta} \norm{\NVRgrad \vect{u}} \leq \frac{2 \mu C C_{P}}{\beta} \norm{ g }$.

\subsubsection{$\vect{f} = \vect{0},g=0,\NVRtensor{h} \neq \NVRtensor{0}$}  In this case, we have
\begin{align}
- \NVRdiv \NVRtensor{\sigma} + \NVRgrad p &= \vect{0} & \text{ in } \Omega, \label{NVR:eq:hstrongfirst} \\
\NVRdiv \vect{u} &= 0 & \text{ in } \Omega, \\
\frac{1}{\mu} \NVRtensor{\sigma} - \NVRgrad \vect{u} &= \NVRtensor{h} & \text{ in } \Omega, \\
\vect{u} &= \vect{0} & \text{ on } \partial\Omega.\label{NVR:eq:hstronglast}
\end{align}
Then, $\NVRtensor{\sigma} = \mu(\NVRgrad \vect{u} + \NVRtensor{h})$, and we have:
\begin{align*}
- \NVRdiv \NVRtensor{\sigma} + \NVRgrad p = - \mu \Delta \vect{u} - \mu \NVRdiv \NVRtensor{h} + \NVRgrad p &= \vect{0},
\end{align*}
so that
\begin{align*} - \mu \Delta \vect{u} + \NVRgrad p &= - \mu  \NVRdiv \NVRtensor{h}
\end{align*}
in a distributional sense.  Testing with $\vect{u}$, and integrating the left hand side by parts, again the pressure term vanishes because $\NVRdiv \vect{u} = 0$, so that much as before, we obtain:
\begin{align*}
\mu (\NVRgrad \vect{u}, \NVRgrad \vect{u})_{\Omega} &= \mu (\NVRdiv \NVRtensor{h}, \vect{u} )_{\Omega}\\
&= - \mu(\NVRtensor{h}, \NVRgrad \vect{u})_{\Omega} \leq \mu \norm{\NVRtensor{h}}_{L^{2}(\Omega)} \norm{ \NVRgrad \vect{u} }_{L^{2}(\Omega)}.
\end{align*}
So $\norm{\NVRgrad \vect{u}} \leq \norm{\NVRtensor{h}}$, and the bounds $\norm{\vect{u} } \leq C_{P} \norm{\NVRtensor{h}}$ and $\norm{p} \leq \frac{\mu}{\beta}\left( \norm{ \NVRgrad \vect{u} } + \norm{\NVRtensor{h}} \right) \leq \frac{2 \mu}{\beta} || \NVRtensor{h} ||$ can be established in a similar fashion as above.

### 2012-09-19 docs/Nate/Proposal/stokesExperiments.tex

\section{Numerical Experiments for the Stokes Equations}
\label{sec:StokesNumericalResults}
To illustrate the theoretical results, we perform three numerical
experiments.  In the first two we use boundary conditions and forcing
function corresponding to a manufactured solution; first showing
optimal convergence using the graph norm arising from the analysis as
the test space norm, then showing sub-optimal convergence when a naive
norm is selected instead.  Finally, we examine the classic lid-driven
cavity flow problem.

We implemented the experiments described below using \emph{Camellia}, a toolbox for DPG developed by Roberts starting at Sandia in summer 2011, in collaboration with Denis Ridzal and Pavel Bochev \cite{RobertsEtAl11}.  Camellia supports 2D meshes of triangles and quads of variable polynomial order, provides mechanisms for easy specification of DPG variational forms, supports $h$- and $p$- refinements, and supports distributed computation of the stiffness matrix, among other features.

Recall that the pressure $p$ in the Stokes problem is only determined up to a constant.  Following a method described by Bochev and Lehoucq \cite{BochevLehoucq}, we add a constraint on the pressure that enforces
\[
\int_{\Omega} p = 0,
\]
thereby determining the solution uniquely.  This constraint is also satisfied by the manufactured solution used in our experiments.

Before turning to the experiments themselves, we briefly note the expected convergence properties and give a few implementation details.  When implementing DPG, we have several choices: what polynomial orders to use for the approximation of fields, traces, and fluxes; how to approximate the optimal test functions, and what norm to use on the test space.  We discuss each of these in turn.

\subsection{Convergence and orders of polynomial approximation}
For a DPG solution $(u_{h},\widehat{u}_{h})$ and exact solution $(u,\widehat{u})$, the analysis in Appendix \ref{sec:StokesAnalysis} gives us
\begin{align}\label{NVR:eqn:gammaBound}
\left(\norm{u-u_{h}}^{2} + \norm{\widehat{u}-\widehat{u}_{h}}_{\hat{H}_A(\Gamma_{h})}^{2}\right)^{1/2} \leq \frac{M}{\gamma_{DPG}} \inf_{(w_{h},\widehat{w}_{h})}\left(\norm{u-w_{h}}^{2} + \norm{\widehat{u}-\widehat{w}_{h}}_{\hat{H}_A(\Gamma_{h})}^{2}  \right)^{1/2},
\end{align}
where $M=O(1)$ and $\gamma_{DPG}=O(\gamma)$ (and for the Stokes problem, $\gamma=O(1)$), the salient point for convergence being that these are mesh-independent constants: for the graph norm presented in the analysis, the method is automatically stable.\footnote{As will be seen in what follows, if we use the naive test norm instead, we do \emph{not} get the optimal convergence rates in the pressure.  We hypothesize that if we performed a similar analysis for the naive norm, $\gamma$ would not be mesh-independent.}

Assuming $u$ is sufficiently smooth, for a discrete $L^2$ space comprised of polynomials of order $k$, we expect best $h$-convergence rates of $k+1$; that is, we have
\begin{align}
\inf_{w_{h} \in U_{h}} \norm{u-w_{h}} \leq C_{1} h^{k+1}.\label{NVR:eqn:hBound}
\end{align}
for some mesh-independent constant $C_{1}$.  It can be shown that, for traces $\widehat{w}_{h}$ whose $H^{-1/2}(\Gamma_{h})$ and $H^{1/2}(\Gamma_{h})$ components are approximated by polynomials of orders $k$ and $k+1$, respectively,
\[
\inf_{\widehat{w}_{h} \in \hat{H}_A(\Gamma_{h})} \norm{\widehat{u}-\widehat{w}_{h}}_{\hat{H}_A(\Gamma_{h})} \leq C_{2} h^{k+1}
\]
for some mesh-independent constant $C_{2}$.  For details and further references, see \cite[pp. 7-8]{DPG6}. Combining this with equations (\ref{NVR:eqn:gammaBound}) and (\ref{NVR:eqn:hBound}), we then have the bound
\[
\norm{u-u_{h}} \leq C h^{k+1}
\]
for $C = \min(C_{1}, C_{2})$.
Assuming negligible error in computing the optimal test functions, for these choices of polynomial order, we expect DPG solutions to converge in $h$ at the optimal rate of $k+1$ for all $L^{2}$ variables.

We can also motivate the choice of polynomial orders for the trial space intuitively from the exact sequence.  If we define $k$ as the polynomial order of approximation of field variables, because these belong to $L^{2}$, it is natural to choose $k+1$ as the $H^{1}$ order.  The traces of $H^{1}$ functions ($\widehat{u}_{1}$ and $\widehat{u}_{2}$) belong to $H^{1/2}$, a stronger space than $L^{2}$, so that $k+1$ is a natural order of approximation for these.  The traces of \NVRHdiv  functions $\left(\widehat{{\sigma_{11} - p \choose \sigma_{12}} \cdot \vect{n}}\right.$ and $\left.\widehat{{\sigma_{21}  \choose \sigma_{22} - p} \cdot \vect{n}}\right)$ belong to $H^{-1/2}$, a weaker space than $L^{2}$, so that $k$ is a natural order of approximation for these.

The exact optimal test functions will not in general be polynomials; we approximate them by using an ``enriched'' space of Lagrange and Raviart-Thomas elements approximating $H^{1}(\Omega_{h})$ and $\vect{H}(\text{\rm div},\Omega_{h})$ components of the test space.  In practice, we experiment with various levels of enrichment, and take the minimum enrichment that yields results nearly as good as higher levels of enrichment.  In the present work, we used 1 as the enrichment order; that is, $k_{\rm test} = k+2$.  As will be seen below, with this, we come extremely close to matching the best approximation error, so that there is no benefit to enriching the test space further.\footnote{For an analysis of the effect of the test space enrichment on rates of convergence in the Laplace problem and linear elasticity, see Gopalakrishnan and Qiu \cite{GopalakrishnanQiu11}.}

Note also that we have made no assumptions about the choice of basis functions.  The present work uses $H^{1}$- and \NVRHdiv-conforming nodal bases provided by the Intrepid package in Trilinos \cite{Trilinos}.

\subsection{Test space norm}
The choice of test norm arising from the above analysis is the (adjoint) graph norm:
\begin{align*}
\norm{(\NVRtensor{\tau},\vect{v}, q)}_{\rm graph}^{2} = \norm{\NVRdiv \NVRtensor{\tau} - \NVRgrad q}^{2} + \norm{\NVRdiv \vect{v}}^{2} + \norm{ \NVRtensor{\tau} + \NVRgrad{\vect{v}}}^{2} + \norm{\NVRtensor{\tau}}^{2} + \norm{\vect{v}}^{2} + \norm{q}^{2}
\end{align*}

We use this norm in our first experiment, and get the optimal convergence rates for the field variables.  In our second experiment, we consider another choice of test norm, which we refer to as the \emph{naive} test space norm:
\begin{align*}
\norm{(\NVRtensor{\tau},\vect{v}, q)}_{\rm naive}^{2} = \norm{\NVRtensor{\tau}}^{2} + \norm{\NVRdiv \NVRtensor{\tau}}^{2} + \norm{\vect{v}}^{2} + \norm{\NVRgrad \vect{v}}^{2} + \norm{q}^{2} + \norm{\NVRgrad q}^{2}.
\end{align*}
Note that this is a \emph{stronger} space than the one generated by the graph norm; that is, if we define
\begin{align*}
\V_{\rm graph} &= \{ (\NVRtensor{\tau},\vect{v}, q) : \norm{(\NVRtensor{\tau},\vect{v}, q)}_{\rm graph} < \infty \}, \text{and} \\
\V_{\rm naive} &= \{ (\NVRtensor{\tau},\vect{v}, q) : \norm{(\NVRtensor{\tau},\vect{v}, q)}_{\rm naive} < \infty \},
\end{align*}
then $V_{\rm naive} \subset V_{\rm graph}$.  Specifically, $V_{\rm graph}$ only requires $\NVRdiv \NVRtensor{\tau} - \NVRgrad q \in \vect{L}^{2}$, while $V_{\rm naive}$ requires $\NVRdiv \NVRtensor{\tau} \in \vect{L}^{2}$ \emph{and} $\NVRgrad q \in \vect{L}^{2}$.

\subsection{Manufactured Solution Experiment with Graph Test Space Norm}
To test the method, we use a manufactured solution following Cockburn et al. \cite{CockburnKanschatSchotzauSchwab03}
\begin{align*}
u_{1} &=  -e^{x} ( y \cos y + \sin y )\\
u_{2} &=  e^{x}  y \sin y\\
p &= 2 \mu e^{x} \sin y
\end{align*}
on domain $\Omega = (-1,1)^2$, taking $\mu=1$, with uniform quadrilateral meshes of increasing granularity, and examine convergence rates.  The $L^{2}$ norm of the exact solution for $u_{1}$ is 2.53; for $u_{2}$, 1.07; for $p$, 2.81.

Figures \ref{fig:graph_h} and \ref{fig:graph_p} show $h$- and $p$-convergence\footnote{In this context, by $p$ we mean polynomial refinements.  We mostly use $k$ for polynomial order, because $p$ is our pressure variable; but a few times in the following pages we will overload $p$ to mean polynomial order as well.} results using the graph norm in the test space, for uniform quadrilateral meshes varying from $k=1$ to 4 in polynomial order, and from $1 \times 1$ to $16 \times 16$ elements.  The dashed lines in the plots show the error of an $L^{2}$ projection of the exact solution (the theoretical best we could achieve)---the lines lie nearly on top of each other.  We not only observe optimal convergence rates, but almost exactly achieve the best approximation error!

\begin{figure}[h!b!p!]
\centering
\subfigure[$u_{1}$]{
\includegraphics[scale=0.42]{./figures/u1_graph_h.pdf}
\label{fig:u1graph_h}
}
\subfigure[$u_{2}$]{
\includegraphics[scale=0.42]{./figures/u2_graph_h.pdf}
\label{fig:u2graph_h}
}
\subfigure[$p$]{
\includegraphics[scale=0.42]{./figures/pressure_graph_h.pdf}
\label{fig:pressuregraph_h}
}
\caption{$h$-convergence of $u_{1},u_{2}$ and $p$ when using the graph norm for the test space.  We observe optimal convergence rates, and nearly match the $L^{2}$-projection of the exact solution.
}
\label{fig:graph_h}
\end{figure}

\begin{figure}[h!b!p!]
\centering
\subfigure[$u_{1}$]{
\includegraphics[scale=0.42]{./figures/u1_graph_p.pdf}
\label{fig:u1graph_p}
}
\subfigure[$u_{2}$]{
\includegraphics[scale=0.42]{./figures/u2_graph_p.pdf}
\label{fig:u2graph_p}
}
\subfigure[$p$]{
\includegraphics[scale=0.42]{./figures/pressure_graph_p.pdf}
\label{fig:pressuregraph_p}
}
\caption{p-convergence of $u_{1},u_{2}$ and $p$ when using the graph norm for the test space.  We observe exponential convergence for the finer meshes, and nearly match the $L^{2}$-projection of the exact solution.
}
\label{fig:graph_p}
\end{figure}

\subsection{Manufactured Solution Experiment with Naive Test Space Norm}
Our second manufactured solution experiment uses the naive norm on the test space.  This was the first norm we used when studying DPG formulations of Stokes \cite{RobertsetAl10}, before we had developed the analysis above, showing why the naive norm might not do as well as the graph norm does.

Figures \ref{fig:naive_h} and \ref{fig:naive_p} show $h$- and $p$-convergence results using the naive norm in the test space, for uniform quadrilateral meshes varying from $k=1$ to 4 in polynomial order, and from $1 \times 1$ to $16 \times 16$ elements; we have again plotted for comparison the error in the $L^{2}$ projection of the exact solution.  As with the graph norm, here we observe optimal convergence rates and almost exactly achieve the best approximation error in velocities $u_{1}$ and $u_{2}$, but in the pressure $p$ we are sub-optimal by up to two orders of magnitude.

Why do we not see optimal convergence for the naive norm?  Recall that this is a stronger norm than the graph norm used in our analysis; thus the test functions that we seek---namely, the ones that will minimize the residual---may not reside within the continuous space represented by the naive norm.  By using the naive norm, we are searching for these test functions inside a smaller space, and we may not find them there.

\begin{figure}[h!b!p!]
\centering
\subfigure[$u_{1}$]{
\includegraphics[scale=0.42]{./figures/u1_naive_h.pdf}
\label{fig:u1naive_h}
}
\subfigure[$u_{2}$]{
\includegraphics[scale=0.42]{./figures/u2_naive_h.pdf}
\label{fig:u2naive_h}
}
\subfigure[$p$]{
\includegraphics[scale=0.42]{./figures/pressure_naive_h.pdf}
\label{fig:pressurenaive_h}
}
\caption{$h$-convergence of $u_{1},u_{2}$ and $p$ when using the naive norm for the test space.  We observe optimal convergence rates (and nearly match the $L^{2}$-projection of the exact solution) for $u_{1}$ and $u_{2}$, but $p$ converges at suboptimal rates.
}
\label{fig:naive_h}
\end{figure}

\begin{figure}[h!b!p!]
\centering
\subfigure[$u_{1}$]{
\includegraphics[scale=0.42]{./figures/u1_naive_p.pdf}
\label{fig:u1naive_p}
}
\subfigure[$u_{2}$]{
\includegraphics[scale=0.42]{./figures/u2_naive_p.pdf}
\label{fig:u2naive_p}
}
\subfigure[$p$]{
\includegraphics[scale=0.42]{./figures/pressure_naive_p.pdf}
\label{fig:pressurenaive_p}
}
\caption{p-convergence of $u_{1},u_{2}$ and $p$ when using the naive norm for the test space.  We observe exponential convergence for the finer meshes, and nearly match the $L^{2}$-projection of the exact solution for $u_{1}$ and $u_{2}$, but see significantly suboptimal solutions in $p$.
}
\label{fig:naive_p}
\end{figure}

\subsection{Lid-Driven Cavity Flow}
A classic test case for Stokes flow is the lid-driven cavity flow problem.  Consider a square cavity with an incompressible, viscous fluid, with a lid that moves at a constant rate.  The resulting flow will be vorticular; as sketched in Figure \ref{fig:cavity_flow_cartoon}, there will also be so-called \emph{Moffat eddies} at the corners; in fact, the exact solution  will have an infinite number of such eddies, visible at progressively finer scales \cite{Moffat}.  Note that the problem as described will have a discontinuity in the fluid velocity at the top corners, and hence its solution will not conform to the spaces we used in our analysis; for this reason, in our experiment we approximate the problem by introducing a thin ramp in the boundary conditions---we have chosen a ramp of width $\frac{1}{64}$.  This makes the boundary conditions continuous,\footnote{It is worth noting that these boundary conditions are not exactly representable by many of the coarser meshes used in our experiments.  We interpolate the boundary conditions in the discrete space.} so that the solution conforms to the spaces used in the analysis.
\begin{figure}[h!b!p!]
\centering
\includegraphics[scale=0.42]{./figures/cavity_flow_cartoon.pdf}
\caption{Sketch of lid-driven cavity flow.
}
\label{fig:cavity_flow_cartoon}
\end{figure}

As described in the introduction, DPG gives us a mechanism for measuring the residual error in the dual norm (the very error we seek to minimize) precisely, and we use this to drive adaptivity, by measuring the error $\norm{e_{K}}_{V}$ for each element $K$.  Both the method and our code allow refinements in $h$ or $p$ or in some combination of $h$ and $p$.  However, we do not yet have a general mechanism for deciding \emph{which} refinement to apply ($h$ or $p$), once we have decided that a given element should be refined.  We run two experiments, one with $h$-adaptivity and one using an ad hoc $hp$-adaptive strategy, described below.

Although it is not required by the code, we enforce \emph{1-irregularity} throughout---that is, before an element can be refined twice along an edge, its neighbor along that edge must be refined once.  In limited comparisons running the same experiments without enforcing 1-irregularity, this did not appear to make much practical difference.

\subsubsection{$h$-refinement strategy}
For $h$-refinements, our strategy is very simple:
\begin{enumerate}
\item Loop through the elements, determining the maximum element error $\norm{e_{K{\rm max}}}_{V}$.
\item Refine all elements with error at least 20\% of the maximum $\norm{e_{K{\rm max}}}_{V}$.
\end{enumerate}

Because the exact solution is unknown, we first solve on an overkill mesh and compare our adaptive solution at each step to the overkill solution.  In this experiment, we used quadratic field variables ($k=2$), a test space enrichment of 1 relative to the $H^{1}$ order (that is, $k_{\rm test} = k + 2 = 4$) for both the adaptive and overkill solutions.  The overkill mesh was $256 \times 256$ elements, with 5,576,706 dofs.

The initial mesh was a $2 \times 2$ square mesh; we ran seven $h$-adaptive refinements.  We stopped after seven steps to ensure that the resulting mesh was nowhere finer than the overkill solution.  At each step, we computed the Euclidean ($\ell_{2}$) norm of the $L^{2}$ norm of each of the seven field variables.  The final adaptive mesh has 124 elements and 11,202 dofs, and combined $L^{2}$ error of $4.4 \times 10^{-4}$ compared with the overkill mesh.  We also ran a few uniform refinements and computed the $L^{2}$ error for these compared with the overkill mesh, to show the comparative efficiency of the adaptive refinements.  The results are plotted in Figure \ref{fig:adaptive_cavity_flow_quadratic_vs_overkill}.
\begin{figure}[h!b!p!]
\centering
\includegraphics[scale=0.60]{./figures/adaptive_cavity_flow_quadratic_vs_overkill.pdf}
\caption{Euclidean norm of $L^{2}$ error in all field variables in $h$-adaptive mesh relative to an overkill mesh with $256 \times 256$ quadratic elements.  The Euclidean norm of all field variables in the exact solution is 6.73.
}
\label{fig:adaptive_cavity_flow_quadratic_vs_overkill}
\end{figure}

We also post-processed the results to solve for the stream function $\phi$, where $\Delta \phi = \NVRcurl \vect{u}$.  The contours of $\phi$ are the streamlines of the flow.  These are plotted for the quadratic adaptive mesh described above in Figure \ref{fig:streamlines_p2}; the first Moffat eddy can be seen clearly in the zoomed-in plot.  This quadratic mesh does not resolve the second Moffat eddy, but if we run 11 adaptive refinements on a cubic mesh, we can see it.  This is shown in Figure \ref{fig:streamlines_p3_r11}.

\begin{figure}[h!b!p!]
\centering
\subfigure[full cavity]{
\includegraphics[scale=0.42]{./figures/streamlines_p2_r7.pdf}
\label{fig:streamlines_p2_r7}
}
\subfigure[lower-left corner]{
\includegraphics[scale=0.42]{./figures/streamlines_detail_p2_r7.pdf}
\label{fig:streamlines_detail_p2_r7}
}
\caption{Streamlines for the full cavity and for the lower-left corner, on a quadratic mesh after 7 adaptive refinements.  The lower-left corner shows the first Moffat eddy.  The final mesh has 124 elements and 11,202 dofs.}
\label{fig:streamlines_p2}
\end{figure}

\begin{figure}[h!b!p!]
\centering
\includegraphics[scale=0.42]{./figures/streamlines_minute_detail_p3_r11.pdf}
\caption{Streamlines for the lower-left corner on a cubic mesh after 11 adaptive refinements: the second Moffat eddy.  The final mesh has 298 elements and 44,206 dofs.}
\label{fig:streamlines_p3_r11}
\end{figure}

\subsubsection{Ad hoc $hp$-refinement strategy}
For the $hp$ experiment, we adopt a similar strategy; this time, our overkill mesh contains $64 \times 64$ quintic elements, and our initial mesh has $2 \times 2$ linear elements.  We know {\it a priori} that we should refine in $h$ at the top corners---if only to fully resolve the boundary condition.  The strategy is again:
\begin{enumerate}
\item Loop through the elements, determining the maximum element error $\norm{e_{K{\rm max}}}_{V}$.
\item Refine all elements with error at least 20\% of the maximum $\norm{e_{K{\rm max}}}_{V}$.
\end{enumerate}
However, this time we must decide whether to refine in $h$ or $p$.  The basic constraints we would like to follow are:
\begin{itemize}
\item the adaptive mesh must be nowhere finer than the overkill mesh (in $h$ or $p$), and
\item prefer $h$-refinements at all corners (top and bottom).
\end{itemize}
So, once the corner elements are as small as the overkill mesh, then they refine in $p$, and all other elements refine in $p$ until they are quintic, after which they may refine in $h$.

The primary purpose of this experiment is to demonstrate that the method allows arbitrary meshes of arbitrary, variable polynomial order.  The strategy described above clearly depends on \emph{a priori} knowledge of the particular problem we are solving; we have yet to determine a good general strategy for deciding between $h$- and $p$-refinements.

We ran 9 refinement steps.  The final mesh has 46 elements and 5,986 dofs, compared with 1,223,682 dofs in the overkill mesh.  The $L^{2}$ error of the adaptive solution compared with the overkill is $8.0 \times 10^{-4}$.  As in the previous experiment, we also tried running a few uniform $h$-refinements on the same initial mesh, as a baseline for comparison.  The results are plotted in Figure \ref{fig:hp_adaptive_cavity_flow_vs_overkill}; the mesh can be seen in Figure \ref{fig:cavityFlowPolyOrder}.

\begin{figure}[h!b!p!]
\centering
\includegraphics[scale=0.60]{./figures/hp_adaptive_cavity_flow_vs_overkill.pdf}
\caption{Euclidean norm of $L^{2}$ error in all field variables in (ad hoc) $hp$-adaptive mesh relative to an overkill mesh with $64 \times 64$ quintic elements.  The Euclidean norm of all field variables in the exact solution is 6.73; the final mesh has 46 elements and 5,986 dofs.
}
\label{fig:hp_adaptive_cavity_flow_vs_overkill}
\end{figure}

\begin{figure}[h!b!p!]
\centering
\includegraphics[scale=0.60]{./figures/cavityFlowPolyOrder.pdf}
\caption{Adaptive mesh for ad hoc $hp$-adaptivity strategy after 9 refinement steps.  The scale represents the polynomial order of the $L^{2}$ variables in the solution.  The final mesh has 46 elements and 5,986 dofs.
}
\label{fig:cavityFlowPolyOrder}
\end{figure}

### 2012-10-08 docs/Nate/Proposal/presentation/tst_2012_talk.tex
Added TST 2012 talk.

--- 2012-09-18 docs/Nate/Proposal/presentation/talk.tex
@@
 
-\date{August 30, 2012}
-\author[Nathan V. Roberts]{Nathan V. Roberts \\
-Supervisors: Leszek Demkowicz, Robert Moser \\
-Committee: Todd Arbogast, George Biros, Thomas Hughes, Venkatramanan Raman
+\date{TST Meeting\\ October 17, 2012}
+\author[Nate Roberts]{Nate Roberts \\
+Collaborators: Leszek Demkowicz, Jesse Chan, Truman Ellis
 }
@@
 The University of Texas at Austin}
-\title[DPG for Incompressible Flow]{A Discontinuous Petrov-Galerkin Methodology\\ for Incompressible Flow}
-\subtitle{Towards Automatic, Robust Mesh Adaptivity}
-
+\title[Camellia: A DPG Toolbox]{Camellia:}
+\subtitle{A Toolbox for a Class of Discontinuous Petrov-Galerkin Methods\\ Using Trilinos}
 \begin{document}
@@
 
-%===============================================================================
-% ACKNOWLEDGEMENTS
-%===============================================================================
-%\begin{frame}
-%\frametitle{Acknowledgments}
-%
-%Collaborators:
-%\begin{itemize}
-%\item Leszek Demkowicz (UT/PECOS)
-%\item Denis Ridzal (Sandia/CSRI)
-%\item Pavel Bochev (Sandia/CSRI)
-%\item Jesse Chan (UT/PECOS)
-%\end{itemize}
-%
-%Support:
-%\begin{itemize}
-%\item Sandia (summer internships)
-%\item PECOS (GRA funding)
-%\item ICES (CSEM Fellowship)
-%\end{itemize}
-%
-%\end{frame}
-
-\begin{frame}
-\frametitle{Motivation}
-
-Incompressible flows:
-\begin{itemize}
-\item arise in a variety of applications, from hydraulics to aerodynamics
-\item Navier-Stokes equations are of fundamental physical and mathematical interest:
-
-\begin{itemize}
-\item believed to hold the key to understanding turbulence
-\item precise conditions for existence and uniqueness of solutions remain unknown (Millennium Prize problem)
-\end{itemize}
-
-\end{itemize}
-%\hspace{1cm} 
-\begin{center}
-\includegraphics[width=6cm]{../figures/submarine}
-\end{center}
-% \hfill \includegraphics{../figures/propeller}\hspace{1cm}
-\end{frame}
-
-\begin{frame}
-\frametitle{Motivation}
-
-\begin{center}\nocite{Williamson1996}
-\includegraphics[scale=.5]{../figures/cylinderWakeRe300Williamson.png}\\
-\end{center}
-
-Typical solutions of incompressible flow problems involve both fine- and large-scale phenomena.
-
-\begin{center}
-$\implies$
-\end{center}
-
-A \pecosbold{uniform} finite element mesh of sufficient granularity is
-\begin{itemize}
-\item \pecosbold{wasteful} of computational resources, or
-\item \pecosbold{infeasible} because of resource limitations.
-\end{itemize}
-
-\vspace{3mm}
-\begin{center}
-Therefore, an \pecosbold{adaptive mesh} is required.
-\end{center}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Motivation}
-In industry:
-\begin{itemize}
-\item adaptivity schemes used are ad hoc, requiring a domain expert to predict features of the solution,
-\item a badly chosen mesh may take considerably longer to converge or fail to converge, and
-\item typically, the Navier-Stokes solve will be just one component in an optimization loop $\implies$ any failure requiring human intervention is costly.
-\end{itemize}
-
-\begin{center}
-\includegraphics[scale=0.35]{../figures/Jesse/mesh10.png}
-\end{center}
-
-\end{frame}
-
-\begin{frame}
-\vspace{5mm}
-\begin{center}
-\pecosbold{Goal}: Develop a solver for the incompressible Navier-Stokes equations that provides \pecosbold{robust adaptivity} starting from a coarse mesh.
-\end{center}
-\pause
-By \pecosbold{robust}, we mean:
-\begin{itemize}
-\item always \pecosbold{converges} to a solution in predictable time, and
-\pause
-\item the adaptive scheme is \pecosbold{independent} of the problem: no special expertise required for adaptivity.
-\end{itemize}
-
-% Explain here what we mean by robust: solver always converges to a solution in predictable time, and that the adaptive scheme is independent of the problem: no special expertise is required for adaptivity.
-
-\end{frame}
-
-%===============================================================================
-% OUTLINE
-%===============================================================================
-
-% UNCOMMENT THIS TO ADD AN OUTLINE AT THE TOP OF EACH SECTION...
-%\AtBeginSection[]
-%{
-%  \begin{frame}<beamer>
-%    \frametitle{Outline}
-%    \tableofcontents[currentsection]
-%  \end{frame}
-%}
-
-\begin{frame}
-\frametitle{Outline}
-\tableofcontents
-\end{frame}
-
-\section{DPG in Brief} % 5-6 slides
+\section{DPG in Brief} % 3-4 slides
 % motivate as a min-residual method
@@
 \begin{frame}
-\frametitle{The Abstract Problem and Minimization of the Residual}
-Take $U,V$ Hilbert.\\
-\vspace{5mm}
-We seek $u \in U$ such that
+\frametitle{The Abstract Problem and Minimization of the Residual}\small
+Take $U,V$ Hilbert.  We seek $u \in U$ such that
 \[
@@
 \]
-where $b$ and $l$ are linear in $v$.  Define $B$ by $Bu = b(u,\cdot) \in V'$; $Bu$ is a linear functional on the test space $V$.\\
+where $b$ is bilinear and $l$ is linear in $v$.  Define $B$ by $Bu = b(u,\cdot) \in V'$.\\
 \vspace{5mm}
@@
 \end{align*}
-\end{frame}
 
-\begin{frame}
-\frametitle{The Abstract Problem and Minimization of the Residual}
+If we use test functions $v_{\delta u_{h}} = R_{V}^{-1}B \delta u_{h}$, then the discrete solution to
 \begin{align*}
-u_{h} = \underset{w_{h} \in U_{h}} \argmin \,\, \frac{1}{2} \norm{Bw_{h}-l}_{V'}^{2}.
+b(u_{h},v_{\delta u_{h}}) &= l(v_{\delta u_{h}}) \forall \delta u_{h} \in U_{h}
 \end{align*}
+minimizes the residual.  We call the $v_{\delta u_{h}}$ \pecosbold{optimal test functions}.\footnote{\FootSize \bibentry{DPG2}}
 
-% PATTER: ``not especially easy to work with'': non-constructive; involves taking a supremum
-Now, the dual space $V'$ is not especially easy to work with; we would prefer to work with $V$ itself.  Recalling that the Riesz operator $R_{V} : V \rightarrow V'$ defined by 
-\begin{align*}
-\langle R_{V}v, \delta v\rangle=(v,\delta v)_{V}, \quad \forall \delta v \in V,
-\end{align*}
-is an \emph{isometry}---$\norm{R_{V}v}_{V'} = \norm{v}_{V}$---we can rewrite the term we want
-to minimize as a norm in $V$:
-
-\begin{align*}
-\frac{1}{2} \norm{Bw_{h}-l}_{V'}^{2} &= \frac{1}{2} \norm{R_{V}^{-1}\left(Bw_{h}-l\right)}_{V}^{2}\\
-                                                              &= \frac{1}{2} \left(R_{V}^{-1}\left(Bw_{h}-l\right), R_{V}^{-1}\left(Bw_{h}-l\right) \right)_{V}.
-\end{align*}
-\end{frame}
-
-\begin{frame}
-\frametitle{The Abstract Problem and Minimization of the Residual}
-We seek to minimize
-\begin{align*}
-\frac{1}{2} \left(R_{V}^{-1}\left(Bw_{h}-l\right), R_{V}^{-1}\left(Bw_{h}-l\right) \right)_{V}.
-\end{align*}
-The first-order optimality condition requires that the G\^ateaux derivative be equal to zero for minimizer $u_{h}$; assuming $B$ is linear, we have
-\begin{align*}
-\left(R_{V}^{-1}\left(Bu_{h}-l\right), R_{V}^{-1}B \delta u_{h} \right)_{V} = 0, \quad \forall \delta u_{h} \in U_{h}.
-\end{align*}
-By the definition of $R_{V}$, this is equivalent to
-\begin{align*} % PATTER: use the phrase ``duality pairing''
-\langle Bu_{h} - l, R_{V}^{-1}B \delta u_{h} \rangle = 0 \quad \forall \delta u_{h} \in U_{h}.
-\end{align*}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{The Abstract Problem and Minimization of the Residual}
-We have:
-\begin{align*}
-\langle Bu_{h} - l, R_{V}^{-1}B \delta u_{h} \rangle = 0 \quad \forall \delta u_{h} \in U_{h}.
-\end{align*}
-Now, if we identify $v_{\delta u_{h}} = R_{V}^{-1}B \delta u_{h}$ as a test function, we can rewrite this as
-\begin{align*}
-b(u_{h},v_{\delta u_{h}}) &= l(v_{\delta u_{h}}).
-\end{align*}
-
-Thus, the discrete solution that minimizes the residual is exactly attained by testing the original equation with appropriate test functions.
-We call these \pecosbold{optimal test functions}.\footnote{\FootSize \bibentry{DPG2}}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Evaluating Error}
-The derivation prompts the definition of an \pecosbold{energy norm} on the trial space:
-\[
-\NVRnorm{u}_{E} \NVReqdef \NVRnorm{Bu}_{V'} = \sup_{v \in V} \frac{b(u,v)}{\NVRnorm{v}_{V}}.
-\]
-We can use this to define a measure of the error:
-\begin{align*}
-\NVRnorm{u - u_{h}}_{E} &= \NVRnorm{Bu - Bu_{h}}_{V'} \\
-&=  \NVRnorm{l - Bu_{h}}_{V'} \\
-&= \NVRnorm{R_{V}^{-1}\left(l - Bu_{h}\right)}_{V}.
-\end{align*}
-Note that all the terms in the final expression are known, so that we can \pecosbold{evaluate}, not merely estimate, the error.  This drives adaptivity.
 \end{frame}
@@
 \begin{frame}
-\frametitle{Graph Test Norm}
-
-For a strong operator $A$ with formal adjoint $A^{*}$, the \pecosbold{adjoint graph space} is
-\[
-H_{A^{*}} = \left\{ v \in L^{2}(\Omega) : A^{*}v \in L^{2}(\Omega) \right\}
-\]
-
-and the \pecosbold{(adjoint) graph norm} on the test space $V$ is given by
+\frametitle{Key Features of DPG}\small
+\begin{itemize}
+\item \pecosbold{guarantees} minimum residual in a norm that depends on the test space, \pecosbold{a free choice}
+\item for non-singularly-perturbed, well-posed linear problems, \pecosbold{provably optimal} convergence rates when the ``adjoint graph norm'' is used for the test space
+\item \pecosbold{SPD} stiffness matrix
+\item discontinuous test space $\implies$ solving for test functions is a \pecosbold{local} operation
+\item nonlinear problems: so far, apply the linear method to the linearized problem
+\item have also derived a method that instead minimizes the nonlinear residual
+\end{itemize}
+\begin{block}{Adjoint Graph Norm}
+For a strong operator $A$ with formal adjoint $A^{*}$, the \pecosbold{adjoint graph norm} on the test space $V$ is given by
 \[
@@
 \]
-
-\vspace{5mm}
-\begin{center}
-E.g. if $A^{*} = \NVRgrad$, then $H_{A^{*}} = H^{1}$, and $\NVRnorm{v}_{H_{A^{*}}} = \NVRnorm{v}_{H^{1}}$.
-\end{center}
-\end{frame}
-
-\begin{frame}
-\frametitle{Key Result: Well-posedness $\implies$ Optimal Convergence}
-Under modest technical assumptions (true for Stokes), we have\footnote{\FootSize \bibentry{DPGStokes}}\\
-\[
-\NVRnorm{Au} \geq \gamma \NVRnorm{u} \implies \sup_{v \in H_{A^{*}}} \frac{b((u,\widehat{u}),v)}{\NVRnorm{v}_{H_{A^{*}}}} \geq \gamma_{\rm DPG} \left(\NVRnorm{u}^{2} + \NVRnorm{\widehat{u}}^{2}_{\widehat{H}_{A}(\Gamma_{h})}\right)^{1/2}
-\]
-where $\gamma_{\rm DPG} = O(\gamma)$ is a mesh-independent constant, and $\NVRnorm{\cdot}_{\widehat{H}_{A}(\Gamma_{h})}$ is the minimum energy extension norm.\\
-\pause
-\vspace{5mm}
-By Babu\v{s}ka's Theorem,
-\[
-\implies \left(\NVRnorm{u - u_{h}}^{2} + \NVRnorm{\widehat{u} - \widehat{u}_{h}}^{2}_{\widehat{H}_{A}(\Gamma_{h})}\right)^{1/2} \leq \frac{M}{\gamma_{\rm DPG}} \left( {\rm B.A.E.} \right).
-\]
-\pause
-Suffices to show that $\NVRnorm{Au} \geq \gamma \NVRnorm{u}$ to prove \pecosbold{optimal} convergence rate!
-\end{frame}
-
-\section{Equations for Incompressible Flow}
-\begin{frame}
-\frametitle{Incompressible Flow Equations}
-\begin{center}
-\includegraphics[width=0.9\linewidth]{../figures/incFlowEqns}\\
-\end{center}
-\end{frame}
-
-\section{Stokes} % 10-12 slides
-% lit. review (including various classical elements, discussion of locking and non-convergence)
-% Stokes analysis, summary results
-% Numerical experiments: manufactured solution, lid-driven cavity flow problem
-% Probably worth mentioning the naive norm results: drives home why the analysis is valuable, and the fact that the optimal test function lives in a very specific space.
-%===============================================================================
-% Stokes: Classical Problem
-%===============================================================================
-\begin{frame}
-\frametitle{Classical Stokes Problem}
-The classical strong form of the Stokes problem in $\Omega \subset
-\mathbb{R}^{2}$ is given by
-\begin{align*}
-- \mu \Delta \vect{u} + \NVRgrad p &= \vect{f} & \text{ in } \Omega, \\
-\NVRdiv \vect{u} &= 0 & \text{ in } \Omega, \\
-\vect{u} &= \vect{u}_D & \text{ on } \partial\Omega,
-\end{align*}
-where $\mu$ is viscosity, $p$ pressure, $\vect{u}$ velocity, and
-$\vect{f}$ a vector forcing function.  Since by appropriate
-non-dimensionalization we can eliminate the constant $\mu$, we take
-$\mu=1$ throughout. 
-\end{frame}
-%===============================================================================
-% Stokes: ``Literature Review:'' What's generally done, etc.
-%===============================================================================
-\begin{frame}
-\frametitle{Stokes: Existing Approaches}
-
-Naive discretizations of Stokes can exhibit \pecosbold{non-convergence} or \pecosbold{locking}.\footnote{\FootSize \bibentry{BoffiBrezziFortin}}
-\\
-\vspace{5mm}
-Standard Galerkin discretizations:
-\begin{itemize}
-\item need to satisfy the \pecosbold{LBB condition}
-\item examples: the MINI element, Crouzeix-Raviart element, the class of $Q_{k}-P_{k-1}$ elements
-\item polynomial degree in the pressure discretization one lower than that for velocity $\implies$ pressure converges more slowly
-\end{itemize}
-%\item When solving saddle-point systems using Bubnov-Galerkin methods, there are two \pecosbold{Brezzi conditions} which must be satisfied.
-The challenging one for Stokes is the \pecosbold{LBB condition}---much of the art of solving Stokes is to find discrete spaces that satisfy the LBB condition.%\footnote{\bibentry{BoffiBrezziFortin}}
-
-%\item Some choices that satisfy the LBB condition are the MINI element, Crouzeix-Raviart element, and the class of $Q_{k}-P_{k-1}$ elements.
-All of these require a polynomial degree in the pressure discretization one lower than that for velocity (so that pressure converges more slowly).
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Stokes: Existing Approaches}
-Local discontinuous Galerkin (LDG) method:\footnote{\FootSize \bibentry{CockburnKanschatSchotzauSchwab03}}
-\begin{itemize}
-\item \pecosbold{locally conservative}
-\item allows pressure and velocity spaces to be chosen independently
-\item equal-order spaces may be used
-\item convergence \emph{rate} for the pressure remains lower than that for the velocity
-\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Stokes: Existing Approaches}
-Divergence-conforming B-splines:\footnote{\FootSize \bibentry{EvansThesis}}
-\begin{itemize}
-\item pointwise divergence-free space $\implies$ locally conservative
-\item equal-order spaces
-\item optimal convergence rates for pressure \pecosbold{and} velocity
-\item non-conforming for multi-patch domains $\implies$ DG techniques for tangential continuity across patch interfaces
-\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{DPG Applied to Stokes}
-
-To apply DPG, we need a first-order system.  We introduce $\NVRtensor{\sigma}= \NVRgrad
-\vect{u}$:
-\begin{align*}
-- \NVRdiv \NVRtensor{\sigma} + \NVRgrad p &= \vect{f} & \text{ in } \, \Omega, \\
- \NVRdiv \vect{u} &= 0 & \text{ in } \, \Omega, \\
- \NVRtensor{\sigma} - \NVRgrad \vect{u} &= 0 & \text{ in } \, \Omega.
-\end{align*}
-Testing with $(\vect{v},q,\vect{\tau})$, and integrating by parts, we have
-\begin{align*}
-\left(\NVRtensor{\sigma} - p \NVRtensor{I}, \NVRgrad \vect{v} \right)_{\Omega_{h}} - \left\langle \widehat{\vect{t}}_{n}, \vect{v} \right\rangle_{\Gamma_{h}} &= (\vect{f}, \vect{v} )_{\Omega_{h}}\\
-\left(\vect{u}, \NVRgrad q \right)_{\Omega_{h}} -  \left\langle \widehat{\vect{u}} \cdot \vect{n}, q  \right\rangle_{\Gamma_{h}} &= 0\\
-\left( \NVRtensor{\sigma}, \NVRtensor{\tau} \right)_{\Omega_{h}} + \left( \vect{u}, \NVRdiv \NVRtensor{\tau} \right)_{\Omega_{h}} - \left\langle \widehat{\vect{u}}, \NVRtensor{\tau} \vect{n}  \right\rangle_{\Gamma_{h}} &= \NVRtensor{0},
-\end{align*}
-where traction $\vect{t}_{n} \eqdef ( \NVRtensor{\sigma} - p \NVRtensor{I} ) \vect{n}$, and the hatted variables $\widehat{\vect{t}}_{n}$ and $\widehat{\vect{u}}$ are new unknowns representing the traces of the corresponding variables at the boundary.
-
-\end{frame}
-
-\begin{frame}
-\frametitle{DPG Applied to Stokes}
-DPG Formulation:
-\begin{align*}
-b(u,v) =& \left(\NVRtensor{\sigma} - p \NVRtensor{I}, \NVRgrad \vect{v} \right)_{\Omega_{h}} - \left\langle \widehat{\vect{t}}_{n}, \vect{v} \right\rangle_{\Gamma_{h}}\\
-&+\left(\vect{u}, \NVRgrad q \right)_{\Omega_{h}} -  \left\langle \widehat{\vect{u}} \cdot \vect{n}, q  \right\rangle_{\Gamma_{h}}\\
-&+ \left( \NVRtensor{\sigma}, \NVRtensor{\tau} \right)_{\Omega_{h}} + \left( \vect{u}, \NVRdiv \NVRtensor{\tau} \right)_{\Omega_{h}} - \left\langle \widehat{\vect{u}}, \NVRtensor{\tau} \vect{n}  \right\rangle_{\Gamma_{h}} = (\vect{f}, \vect{v} )_{\Omega_{h}} = l(v).
-\end{align*}
-The natural spaces for the trial variables are then:
-\begin{itemize}
-\item fields: $p \in L^{2}(\Omega), \vect{u} \in \vect{L}^{2}(\Omega), \NVRtensor{\sigma} \in \vect{L}^{2}(\Omega)$,
-\item fluxes: $\widehat{\vect{t}}_{n} \in \NVRtensor{H}^{-1/2}(\Gamma_{h})$,
-\item traces: $\widehat{\vect{u}} \in \vect{H}^{1/2}(\Gamma_{h})$.
-\end{itemize}
-
-The natural norms for fluxes and traces are \emph{minimum energy extension norms}.
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Polynomial Space Choices}
-How to select polynomial spaces for $u$ and $\widehat{u}$?
-\begin{itemize}
-\item Graph norm $\implies$ error bounded by best approximation error.
-\vspace{3mm} \pause
-\item Want all variables to have same B.A.E. convergence rates.
-\vspace{3mm} \pause
-\item Fix polynomial order $k$ for $L^{2}$ variables.  ($k+1$ rate.)
-\vspace{3mm} \pause
-\item $\implies$ $k+1$ for $H^{1/2}(\Gamma_{h})$.
-\vspace{3mm} \pause
-\item $\implies$ $k$ for $H^{-1/2}(\Gamma_{h})$.
-\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Graph Test Norm}
-The adjoint graph norm for our Stokes formulation is:\footnote{\FootSize \bibentry{DPGStokes}}
-\begin{align*}
-\norm{(\NVRtensor{\tau},\vect{v}, q)}_{\rm graph}^{2} =& \norm{\NVRdiv \NVRtensor{\tau} - \NVRgrad q}^{2} + \norm{\NVRdiv \vect{v}}^{2} + \norm{ \NVRtensor{\tau} + \NVRgrad{\vect{v}}}^{2}\\ 
-&+ \norm{\NVRtensor{\tau}}^{2} + \norm{\vect{v}}^{2} + \norm{q}^{2}.
-\end{align*}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Manufactured Solution}
-For our first numerical experiment (and following Cockburn et al.\footnote{\FootSize \bibentry{CockburnKanschatSchotzauSchwab03}}), we consider a manufactured solution
-\begin{align*}
-u_{1} &=  -e^{x} ( y \cos y + \sin y )\\
-u_{2} &=  e^{x}  y \sin y\\
-p &= 2 \mu e^{x} \sin y
-\end{align*}
-on domain $\Omega=(-1,1)^{2}$.
-We use this to determine appropriate boundary conditions for the DPG problem.
-We also perform an $L^{2}$ projection of the exact solution into the trial space to find the solution with the best approximation error.
-\end{frame}
-
-\begin{frame}
-\frametitle{Graph Test Norm: $u_{1}$ convergence}
-\begin{figure}[!htb]
-\center
-{\setlength{\fboxsep}{1pt}\colorbox{pecos2}{\includegraphics[scale=.38]{../figures/u1_graph_h.png}}}
-\caption{$h$-convergence with the graph norm: $u_{1}$.  Dashed lines: best approximation error.}
-\end{figure}
-\end{frame}
-
-\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
-\begin{frame}
-\frametitle{Graph Test Norm: $u_{2}$ convergence}
-\begin{figure}[!htb]
-\center
-{\setlength{\fboxsep}{1pt}\colorbox{pecos2}{\includegraphics[scale=.38]{../figures/u2_graph_h.png}}}
-\caption{$h$-convergence with the graph norm: $u_{2}$.  Dashed lines: best approximation error.}
-\end{figure}
-\end{frame}
-
-\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
-\begin{frame}
-\frametitle{Graph Test Norm: $p$ convergence}
-\begin{figure}[!htb]
-\center
-{\setlength{\fboxsep}{1pt}\colorbox{pecos2}{\includegraphics[scale=.38]{../figures/pressure_graph_h.png}}}
-\caption{$h$-convergence with the graph norm: $p$.  Dashed lines: best approximation error.}
-\end{figure}
-\end{frame}
-
-\begin{frame}
-\frametitle{Naive Test Norm\footnote{\FootSize \bibentry{RobertsetAl10}}}
-What if we don't use the graph norm, but a naive choice instead?
-
-\begin{align*}
-\norm{(\NVRtensor{\tau},\vect{v}, q)}_{\rm naive}^{2} = \norm{\NVRtensor{\tau}}^{2} + \norm{\NVRdiv \NVRtensor{\tau}}^{2} + \norm{\vect{v}}^{2} + \norm{\NVRgrad \vect{v}}^{2} + \norm{q}^{2} + \norm{\NVRgrad q}^{2}.
-\end{align*}
-\end{frame}
-
-\begin{frame}
-\frametitle{Naive Test Norm: $u_{1}$ convergence}
-\begin{figure}[!htb]
-\center
-{\setlength{\fboxsep}{1pt}\colorbox{pecos2}{\includegraphics[scale=.38]{../figures/u1_naive_h.png}}}
-\caption{$h$-convergence with the naive norm: $u_{1}$.  Dashed lines: best approximation error.}
-\end{figure}
-\end{frame}
-
-\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
-\begin{frame}
-\frametitle{Naive Test Norm: $u_{2}$ convergence}
-\begin{figure}[!htb]
-\center
-{\setlength{\fboxsep}{1pt}\colorbox{pecos2}{\includegraphics[scale=.38]{../figures/u2_naive_h.png}}}
-\caption{$h$-convergence with the naive norm: $u_{2}$.  Dashed lines: best approximation error.}
-\end{figure}
-\end{frame}
-
-\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
-\begin{frame}
-\frametitle{Naive Test Norm: $p$ convergence}
-\begin{figure}[!htb]
-\center
-{\setlength{\fboxsep}{1pt}\colorbox{pecos2}{\includegraphics[scale=.38]{../figures/pressure_naive_h.png}}}
-\caption{$h$-convergence with the naive norm: $p$.  Dashed lines: best approximation error.}
-\end{figure}
-\end{frame}
-
-\begin{frame}
-\frametitle{Graph vs. Naive Test Norm}
-What's the difference between the two norms?  Why are the results better with the graph norm?
-
-\begin{align*}
-\norm{(\NVRtensor{\tau},\vect{v}, q)}_{\rm naive}^{2} =& \norm{\NVRdiv \NVRtensor{\tau}}^{2} + \norm{\NVRdiv \vect{v}}^{2} + \norm{\NVRgrad q}^{2} + \norm{\NVRtensor{\tau}}^{2} + \norm{\vect{v}}^{2} + \norm{q}^{2}\\
-\vspace{30mm}
-\norm{(\NVRtensor{\tau},\vect{v}, q)}_{\rm graph}^{2} =& \norm{\NVRdiv \NVRtensor{\tau} - \NVRgrad q}^{2} + \norm{\NVRdiv \vect{v}}^{2} + \norm{ \NVRtensor{\tau} + \NVRgrad{\vect{v}}}^{2}\\ 
-&+ \norm{\NVRtensor{\tau}}^{2} + \norm{\vect{v}}^{2} + \norm{q}^{2}
-\end{align*}
-\pause
-The naive norm is \pecosbold{stronger}---e.g.
-it requires $\NVRdiv \NVRtensor{\tau} \in L^{2}$ and $\NVRgrad q \in L^{2}$, whereas the graph norm merely requires that $\NVRdiv \NVRtensor{\tau} - \NVRgrad q \in L^{2}$.
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Lid-Driven Cavity Flow Problem}
-A classic test case for Stokes flow is the \pecosbold{lid-driven cavity flow problem}.
-Consider a square cavity with an incompressible, viscous fluid, with a lid that moves at a constant rate.
-The resulting flow will be vorticular; there will be \pecosbold{Moffat eddies} at the corners; in fact, the exact solution will have an infinite number of such eddies, visible at progressively finer scales.\footnote{\FootSize \bibentry{Moffat}}
-\begin{center}
-{\includegraphics[scale=0.40]{../figures/cavity_flow_cartoon.pdf}}
-\end{center}
-\end{frame}
-
-\begin{frame}
-\frametitle{Lid-Driven Cavity Flow Problem}
-\begin{center}
-{\includegraphics[scale=0.40]{../figures/cavity_flow_cartoon.pdf}}
-\end{center}
-\small{Because the BCs for the problem are discontinuous at the top corners, the exact solution lies outside of $H^{1}$.
-So we introduce a small ``ramp'' on either side, of width $\epsilon = \frac{1}{64}$.}
-\end{frame}
-
-\begin{frame}
-\frametitle{Lid-Driven Cavity Flow Problem}
-Since the exact solution is unknown, we compare an overkill mesh to a series of adaptive and uniformly refined solutions.\\
-
-\begin{itemize}
-\item For all meshes, we use quadratic field variables ($k=2$).
-\item Overkill mesh had $256 \times 256$ elements (5,576,706 dofs).
-\item Initial adaptive mesh had $2 \times 2$ elements.
-\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Lid-Driven Cavity Flow: $h$-adaptivity}
-\begin{figure}[!htb]
-\begin{center}
-{\setlength{\fboxsep}{1pt}\colorbox{pecos2}{\includegraphics[scale=0.40]{../figures/adaptive_cavity_flow_quadratic_vs_overkill.pdf}}}
-\end{center}
-\caption{Euclidean norm of $L^{2}$ error in all field variables in $h$-adaptive mesh relative to an overkill mesh with $256 \times 256$ quadratic elements.
-The Euclidean norm of the overkill solution is 6.73.}
-\end{figure}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Lid-Driven Cavity Flow: Streamlines}
-\begin{center}
-{\setlength{\fboxsep}{1pt}\colorbox{pecos2}{\includegraphics[scale=0.25]{../figures/streamlines_p2_r7.pdf}}} \hspace{5mm} {\setlength{\fboxsep}{1pt}\colorbox{pecos2}{\includegraphics[scale=0.25]{../figures/streamlines_detail_p2_r7.pdf}}}
-\end{center}
-Streamlines for the full cavity and for the lower-left corner, on a quadratic mesh after 7 adaptive refinements.
-The lower-left corner shows the first Moffat eddy.
-The final mesh has 124 elements and 11,202 dofs.
-\end{frame}
-
-\begin{frame}
-\frametitle{Lid-Driven Cavity Flow: Streamlines}
-Using a cubic mesh and running 11 refinement steps, we can resolve the second Moffat eddy:
-\begin{center}
-{\setlength{\fboxsep}{1pt}\colorbox{pecos2}{\includegraphics[scale=.35]{../figures/streamlines_minute_detail_p3_r11.pdf}}}
-\end{center}
-Streamlines for the lower-left corner on a cubic mesh after 11 adaptive refinements: the second Moffat eddy.  The final mesh has 298 elements and 44,206 dofs.
+\end{block}
 \end{frame}
@@
 \section{Camellia} % 10-12 slides
-% lit. review: deal II, libMesh, FEniCS
-% what we do, with a couple selected details
-% pretty pictures of solutions produced with Camellia?
-\begin{frame}
-\frametitle{Camellia}
-\pecosbold{Design Goal}: make DPG research and experimentation as simple as possible, without sacrificing too much by way of performance.\\
-
-\begin{block}{Existing FEM Software}
-\begin{itemize}
-\item \deal\footnotemark
-\item libMesh\footnotemark
-\item FEniCS\footnotemark
-\end{itemize}
-\end{block}
-\addtocounter{footnote}{-2}
-\footnotetext{\FootSize \bibentry{BangerthKanschat99}}
-\addtocounter{footnote}{1}
-\footnotetext{\FootSize \bibentry{Kirk2006}}
-\addtocounter{footnote}{1}
-\footnotetext{\FootSize \bibentry{fenics:book}}
-\end{frame}
-
-\begin{frame}
-\frametitle{FEM Software: \deal features}
-\begin{block}{}
-\begin{itemize}
-\item flexible: possible to vary choices for FE spaces, spatial dimension, var. formulations, and linear solvers without too much effort
-\item easy to use through encapsulation: details of complex data structures hidden from user
-\item safe: runtime parameter checking allows many errors to be detected early in development
-\item extensive documentation
-\item \pecosbold{hypercube} topologies (lines, quads, hexahedra) supported (with several element types: CG and DG Lagrange, N\'{e}d\'{e}lec, Raviart-Thomas)
-\end{itemize}
-\end{block}
-\end{frame}
-
-\begin{frame}
-\frametitle{FEM Software: \deal features, continued}
-\begin{block}{}
-\begin{itemize}
-\item $h$-, $p$-, and $hp$-adaptivity
-\item distributed stiffness matrix computation
-\item recently added: distributed mesh storage\footnotemark
-\end{itemize}
-\end{block}\footnotetext{\FootSize \bibentry{dealiiwithp4est}}
-\end{frame}
-
-\begin{frame}
-\frametitle{FEM Software: libMesh and FEniCS}
-\begin{block}{libMesh features}
-\begin{itemize}
-\item inspired by \deal
-\item \code{Element} class designed for subclassing
-\item many topologies provided: triangles, quads, hexahedra, tetrahedra, prisms, and pyramids
-\item $h$-, $p$-, and $hp$-adaptivity
-\item distributed stiffness matrix computation
-\end{itemize}
-\end{block}
-
-\begin{block}{FEniCS features}
-\begin{itemize}
-\item aim: highly automated solution of FE problems
-\item emphasis is on simplicity, especially in specification of variational forms
-\item simplex topologies (intervals, triangles, tetrahedra) supported
-\end{itemize}
-\end{block}
-\end{frame}
-
-\begin{frame}
+\begin{frame}[fragile]
 \frametitle{Camellia\footnote{\FootSize \bibentry{RobertsetAl11}}}
@@
 \end{center}
-%\begin{block}{}
-%\begin{itemize}
-%\item Like \deal and libMesh, support $hp$-adaptive hierarchical meshes
-%\item Like libMesh, support multiple element types (quads and triangles in 2D)
-%\item Like FEniCS, support rapid development of variational forms
-%\item Leverage existing software by building atop Trilinos\footnotemark
-%\end{itemize}
-%\end{block}
 \addtocounter{footnote}{1}
@@
 
-%\begin{frame}
-%\frametitle{Camellia\footnote{\FootSize \bibentry{RobertsetAl11}}}
-%\pecosbold{Design Goal}: make DPG research and experimentation as simple as possible, without sacrificing too much by way of performance.
-%\begin{block}{Goals for Camellia (Achieved)}
-%\begin{itemize}
-%\item Make variational form and inner product easy to specify
-%\item Arbitrary, $hp$-adaptive 2D meshes (quads and triangles)---including meshes of arbitrary irregularity
-%\item ``Reasonable'' speed and scalability (distributed stiffness matrix computation)
-%\item Support for nonlinear problems
-%\end{itemize}
-%\end{block}
-%
-%\vspace{3 mm}
-%
-%%\begin{figure}[h]
-%%\centering
-%%\includegraphics[scale=0.35]{../fig/hangingNode.eps}
-%%\label{fig:hangingNode}
-%%\end{figure}
-%\end{frame}
-%
-%\begin{frame}
-%\frametitle{Camellia}
-%\begin{block}{Goals for Camellia (Aspirational)}
-%\begin{itemize}
-%\item Support for minimization of a \pecosbold{nonlinear} residual
-%\item Support for curvilinear geometries
-%\item Better scalability (distributed mesh storage)
-%\item Longer term: 3D meshes
-%\end{itemize}
-%\end{block}
-%
-%\end{frame}
+\begin{frame}
+\frametitle{Camellia: 2011 Design}
+\begin{itemize}
+\item Camellia defines \pecosbold{abstract classes} for bilinear form, inner product, right-hand side, boundary conditions.
+\item User implements problem-specific code through \pecosbold{subclassing}.
+\item Allows \pecosbold{automatic} definition of adjoint graph norm.
+\end{itemize}
 
-%===============================================================================
-% WHAT INTREPID (TRILINOS) PROVIDES
-%===============================================================================
-\begin{frame}
-\frametitle{Trilinos Support}
-\begin{block}{}
+\begin{table}
 \begin{center}
-\begin{tabular}{l c}
-\pecosbold{Feature}			&\pecosbold{Trilinos Package} \\
-OO interface to MUMPS 		&Amesos \\
-KLU solver 				&Amesos \\
-conforming basis functions	&Intrepid \\
-pullbacks/Piola transforms 	&Intrepid \\
-smart multidimensional arrays 	&Intrepid \\
-distributed compressed row storage matrices	&Epetra \\
-cell topologies 				&Shards \\
-reference-counted pointers 				&Teuchos \\
-space-filling curves for spatially local mesh partitioning 		&Zoltan \\
+\begin{tabular}{| c | c |}
+\hline
+Implementation & Lines of Code\\
+\hline
+Stokes bilinear form & 341 \\
+Stokes RHS and BCs & 251 \\
+Automatic graph norm & 198 \\
+\hline
 \end{tabular}
 \end{center}
-\end{block}
+\end{table}
 \end{frame}
@@
 \begin{frame}
-\frametitle{Camellia: Other Users}
+\frametitle{Camellia: 2012 Design}
 \begin{itemize}
-\item Jesse Chan: compressible Navier-Stokes
-\item Truman Ellis: compressible Navier-Stokes with turbulence
+\item Key observation: bilinear form, inner product, and RHS can all be defined using \pecosbold{linear terms} involving the trial and test space variables.
+\item We can define a linear term as \code{lt = f * v} where \code{f} is a function and \code{v} is a variable.
+\item Functions can depend on spatial coordinates, and may be scalar-, vector-, or tensor-valued.
+\item Variables might be operated on by a linear differential operator.
+\item Using these as primitives, Camellia allows \pecosbold{declarative} specification of bilinear form, inner product, and RHS.
 \end{itemize}
-\begin{figure}
-\centering
-\subfigure[Mesh]{\includegraphics[height = 3cm]{../figures/Jesse/Mesh10.png}}
-\subfigure[$u_1$]{\includegraphics[height = 3cm]{../figures/Jesse/u10.png}}
-\caption{Compressible Navier-Stokes for Carter flat plate problem, ${\rm Re}=1000, {\rm Ma}=3.$}
-\end{figure}
 \end{frame}
 
-\begin{frame}
-\frametitle{Camellia: Stiffness Matrix Timing Test}
-\begin{itemize}
-\item local stiffness matrix computation is \pecosbold{embarrassingly parallel}
-\item minimize assembly costs: \pecosbold{spatially local} mesh partitioning
-\item timing tests on Lonestar: solve convection-dominated diffusion
-\end{itemize}
-\vspace{-5mm}
-\begin{center}
-\includegraphics[scale = 0.40]{../figs/scalingFigs/bar_ref3.pdf}\hspace{1cm}
-\end{center}
-\begin{itemize}
-\vspace{-5mm}
-\item collaborators working on parallel solvers: Kyungjoo Kim (shared memory architecture),  Maciej Paszynski (distributed memory)
-\end{itemize}
+\begin{frame}[fragile]
+\frametitle{Camellia: 2012 Design, Poisson implementation}
+Recall our Poisson formulation:
+\begin{align*}
+\text{``}b(u,v)\text{''} = (\widehat{\psi}_n,v)_{\Gamma_h} - (\vect{\psi}, \nabla v)_{\Omega_h} &\\
++ (\vect{\psi}, \vect{q})_{\Omega_h} + (\widehat{\phi}, \vect{q}  \cdot \vect{n})_{\Gamma_h} - (\phi, \nabla \cdot \vect{q})_{\Omega_h} &= (f,v)_{\Omega_h}.
+\end{align*}
+\begin{lstlisting}
+  VarFactory varFactory; 
+  VarPtr v = varFactory.testVar("v", HGRAD);
+  VarPtr q = varFactory.testVar("q", HDIV);
+
+  VarPtr psi_hat_n = varFactory.fluxVar("\\widehat{\\phi}_n");
+  VarPtr phi_hat = varFactory.traceVar("\\widehat{\\psi}");
+  VarPtr psi = varFactory.fieldVar("\\psi", VECTOR_L2);
+  VarPtr phi = varFactory.fieldVar("\\phi", L2);
+\end{lstlisting}
 
@@
 \begin{frame}[fragile]
-\frametitle{Camellia: Rapid Specification of Inner Products}
-Suppose we have a problem whose graph norm is
-\[
-\NVRnorm{(v,\vect{q})}_{\rm graph}^{2} = \NVRnorm{v}^{2} + \NVRnorm{\vect{q}}^{2} + \NVRnorm{\NVRpd{v}{x} - \NVRpd{v}{y} + \NVRdiv \vect{q}}^{2}.
-\]
-\vspace{2mm}
-To specify this in Camellia, simply do:
+\frametitle{Camellia: 2012 Design, Poisson implementation}
+Recall our Poisson formulation:
+\begin{align*}
+\text{``}b(u,v)\text{''} = (\widehat{\psi}_n,v)_{\Gamma_h} - (\vect{\psi}, \nabla v)_{\Omega_h} &\\
++ (\vect{\psi}, \vect{q})_{\Omega_h} + (\widehat{\phi}, \vect{q}  \cdot \vect{n})_{\Gamma_h} - (\phi, \nabla \cdot \vect{q})_{\Omega_h} &= (f,v)_{\Omega_h}.
+\end{align*}
 \begin{lstlisting}
-VarFactory varFactory;
-VarPtr v = varFactory.testVar("v", HGRAD);
-VarPtr q = varFactory.testVar("q", HDIV);
-IPPtr ip = Teuchos::rcp( new IP);
-ip->addTerm(v);
-ip->addTerm(q);
-ip->addTerm(v->dx() - v->dy() + q->div());
+  BFPtr bf = Teuchos::rcp( new BF(varFactory) );
+
+  bf->addTerm(psi_hat_n, v);
+  bf->addTerm(-psi, v->grad());
+
+  bf->addTerm(psi, q);
+  bf->addTerm(phi_hat, q->dot_normal());
+  bf->addTerm(-phi, q->div());
 \end{lstlisting}
 
-The bilinear form can be specified similarly.
-
-\end{frame}
-
-%\begin{frame}
-%\frametitle{Camellia Details: Stiffness Matrix Computation}
-%Recall the problem we solve for the optimal test functions:\\
-%For each $e_{i} \in U_h$, find $v_{e_{i}} \in V : (v_{e_{i}},w)_V = b(e_{i},w) \quad \forall w \in V$.\\
-%For each $e_{i} \in U_h$, find $v_{e_{i}} \in V : (v_{e_{i}},e_{j})_V = b(e_{i},e_{j}) \quad \forall e_{j} \in V$.\\
-%
-%\end{frame}
-
-\section{Navier-Stokes} % 7-8 slides
-\begin{frame}
-\frametitle{Navier-Stokes}
-\begin{block}{}
-The structure of Navier-Stokes is similar to Stokes:
-\begin{itemize}
-\item Naive discretizations have similar issues with non-convergence and locking.
-\item Can use same elements as for Stokes, but now need to deal with the nonlinearity.
-\end{itemize}
-\end{block}
-\end{frame}
-
-\begin{frame}
-\frametitle{Navier-Stokes}
-\begin{block}{Existing approaches}
-\begin{itemize}
-\item Classical pressure-correction methods (Chorin, Temam), velocity-correction methods (Orszag, Karniadakis), and consistent splitting schemes (Guermond and Shen), all of which split the nonlinear time step into a pair of elliptic equations.\footnotemark
-\item Guermond and Minev's dimensional splitting, another projection method, which is cheap to compute, only requiring solution of a series of 1D boundary value problems.
-(Limited, for now, to axis-aligned parallelepiped meshes.)\footnotemark
-\end{itemize}
-\end{block}
-\addtocounter{footnote}{-1}
-\footnotetext{\FootSize \bibentry{Guermond06}}
-\addtocounter{footnote}{1}
-\footnotetext{\FootSize \bibentry{GuermondMinev2011}}
-\end{frame}
-
-\begin{frame}
-\frametitle{Navier-Stokes}
-\begin{block}{Existing approaches}
-\begin{itemize}
-\item Cockburn et al. applied LDG to Navier-Stokes, with success for Reynolds numbers up to 100.\footnotemark
-\item Evans and Hughes applied divergence-conforming B-splines to Navier-Stokes, with success e.g. for driven cavity problem with ${\rm Re}$ up to 1000.\footnotemark
-\end{itemize}
-\end{block}
-\addtocounter{footnote}{-1}
-\footnotetext{\FootSize \bibentry{Cockburn2004}}
-\addtocounter{footnote}{1}
-\footnotetext{\FootSize \bibentry{EvansHughesSteadyNavierStokes}}
-\nocite{EvansHughesUnsteadyNavierStokes}
-\nocite{EvansHughesSteadyNavierStokes}
-\end{frame}
-
-\begin{frame}
-\frametitle{Backward-facing Step}
-A classical test case for incompressible flow problems is the \pecosbold{backward-facing step} problem, which has a recirculation region east of the step.
-We plan to perform numerical experiments using Stokes, Oseen, and Navier-Stokes.
-
-\vspace{5mm}
-
-\begin{center}
-{\includegraphics[scale=0.30]{../figures/backFacingStep.pdf}}\hspace{2mm}{\includegraphics[scale=0.17]{../figures/backFacingStepStreamFunction.png}}
-\end{center}
+RHS, BCs, and test space norms can be specified in a similar fashion.
 
@@
 \begin{frame}
-\frametitle{Flow Around a Cylinder}
-A classical test case for incompressible Navier-Stokes problems is the flow around a cylinder.\footnote{\FootSize \bibentry{KovasznayCylinder}}  We plan to perform numerical experiments using steady-state Navier-Stokes.
+\frametitle{Camellia: 2012 vs. 2011 Design, Lines of Code}
 
-\vspace{10mm}
+\begin{table}[h!b!p!]
+\begin{center}
+\begin{tabular}{| c | c | c |}
+\hline
+Implementation & Lines of Code, Old & Lines of Code, New\\
+\hline
+Stokes bilinear form & 341 & 50 \\
+Stokes RHS and BCs & 251 & 90\\
+Automatic graph norm & 198 & 36 \\
+\hline
+\end{tabular}
+\end{center}
+\end{table}
 
-\begin{center}
-{\includegraphics[scale=0.50]{../figures/flowPastCylinder.pdf}}
-\end{center}
-
-\pause
-At around ${\rm Re}=6$, the flow separates but there is still a steady solution, with symmetric vortices in the wake of the cylinder.
-Somewhere above ${\rm Re}=40$, vortex shedding begins (and therefore there is no steady solution).
-
-\end{frame}
-
-% lit. review
-% classical problems
-\section{Proposed Work} % 3 slides
-\begin{frame}
-\frametitle{Proposed Work: Area C}
-\begin{block}{}
+\begin{block}{Camellia: Future Work}
 \begin{itemize}
-\item Verify convergence rates for the Stokes, Oseen, and Navier-Stokes equations using manufactured solutions.
-\item Simulate the classical lid-driven cavity flow and backward-facing step problems using, in turn, the Stokes, Oseen, and Navier-Stokes equations.
-\item Simulate flow past a cylinder using the steady-state Navier-Stokes equations.  Time permitting, we will do so with the transient equations as well.
+\item support for curved geometry.
+\item minimize the \emph{nonlinear} residual (adds a hessian term).
+\item in further future: 1D and 3D mesh support, distributed mesh and solution storage.
 \end{itemize}
 \end{block}
-
-\begin{block}{Completed}
-\begin{itemize}
-\item Verify convergence rates for the Stokes equations using manufactured solutions.
-\item Simulate lid-driven cavity flow using the Stokes equations.
-\end{itemize}
-\end{block}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Proposed Work: Area B}
-Design and develop a software toolbox (\emph{Camellia}) for the investigation of DPG problems, with the following features:
-\begin{block}{Camellia Features (Completed)}
-\begin{itemize}
-\item 2D meshes of triangles and quads of variable polynomial order,
-\item mechanisms for easy specification of DPG variational forms,
-\item $h$- and $p$- refinements, and
-\item distributed computation of the stiffness matrix.
-\end{itemize}
-\end{block}
-
-\pecosbold{Time permitting}, add the following features:
-\begin{block}{}
-\begin{itemize}
-\item curvilinear elements, 
-\item meshes of arbitrary spatial dimension,
-\item space-time elements, and
-\item distributed mesh and solution representation.
-\end{itemize}
-\end{block}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Proposed Work: Area A}
-
-\begin{block}{}
-\begin{itemize}
-\item \pecosbold{Completed:} Pose several DPG formulations of the Stokes equations---the velocity-gradient-pressure (VGP), velocity-stress-pressure (VSP), and velocity-vorticity-pressure (VVP) formulations.
-\item Pose DPG formulations of the Oseen equations and the 2D incompressible Navier-Stokes equations.
-\item \pecosbold{Completed:} Prove the well-posedness of the VGP Stokes formulation for DPG, which has as consequence a guarantee of optimal convergence rates.
-\item Time permitting, complete similar proofs for the VSP and VVP formulations.
-\item Time permitting, complete similar proofs for the Oseen equations, including a study of \emph{robustness}---analyzing the effects of an increasing Reynolds number.
-\end{itemize}
-\end{block}
-
 \end{frame}
@@
 \center{Questions?}\\
-%For more info:\\
-%nroberts@ices.utexas.edu\\
 \end{block}
+\vspace{1cm}
+\center{For more info:\\
+nroberts@ices.utexas.edu}\\
 \end{frame}
@@
 
-%FOSLS
-\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
-\begin{frame}
-\frametitle{FOSLS\footnote{\FootSize \bibentry{FOSLS1}.}}\nocite{FOSLS2}
-First-Order Systems Least Squares (FOSLS), like DPG:
-\begin{itemize}
-\item first-order system
-\item SPD stiffness matrix
-\item no need for stabilization terms or flux limiters
-\item discrete space only needs to be conforming (no need to satisfy LBB condition, e.g.)
-\item minimum-residual method
-\item \emph{a posteriori} error \pecosbold{measure} (not estimator)
-\end{itemize}
-Like DPG, FOSLS provides optimal convergence rates, but it does so in a different norm (typically, the graph norm on the trial space).
-Problem-specific approaches to get optimal rates in the $L^{2}$ norm, which DPG manages by virtue of Riesz inversion and a broken test space.
-\end{frame}
-
-%Nonlinear derivation, and the Hessian
-\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
-\begin{frame}
-\frametitle{Minimization of the Nonlinear Residual}
-As before, we seek to minimize
-\begin{align*}
-\frac{1}{2} \left(R_{V}^{-1}\left(Bw_{h}-l\right), R_{V}^{-1}\left(Bw_{h}-l\right) \right)_{V},
-\end{align*}
-but now we allow $B$ to be nonlinear.  The first-order optimality condition then requires that
-\begin{align*}
-\left(R_{V}^{-1}\left(Bu_{h}-l\right), R_{V}^{-1}B'(u_{h},\delta u_{h}) \right)_{V} = 0, \quad \forall \delta u_{h} \in U_{h}.
-\end{align*}
-where $B'(u_{h},\delta u_{h})$ is the G\^ateaux derivative of $B$ at $u_{h}$ in direction $\delta u_{h}$.  Then
-\begin{align*}
-\langle Bu_{h} - l, R_{V}^{-1}B'(u_{h},\delta u_{h}) \rangle = 0 \quad \forall \delta u_{h} \in U_{h}.
-\end{align*}
-\end{frame}
-\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
-\begin{frame}
-\frametitle{Minimization of the Nonlinear Residual}
-\begin{align*}
-\langle Bu_{h} - l, R_{V}^{-1}B'(u_{h},\delta u_{h}) \rangle = 0 \quad \forall \delta u_{h} \in U_{h}.
-\end{align*}
-Now, we can again identify $v_{\delta u_{h}} = R_{V}^{-1}B'(u_{h},\delta u_{h})$ as a test function and note that
-\begin{align*}
-b(u_{h},v_{\delta u_{h}}) &= l(v_{\delta u_{h}}),
-\end{align*}
-but notice that now $v_{\delta u_{h}}$ also depends on the solution $u_{h}$.  Linearizing about $u_{h} + \Delta u_{h}$, we have
-\begin{align*}
-B(u_{h} + \Delta u_{h}) \approx Bu_{h} + B'(u_{h},\Delta u_{h})
-\end{align*}
-and
-\begin{align*}
-B'(u_{h} + \Delta u_{h},\delta u_{h}) \approx B'(u_{h},\delta u_{h}) + B''(u_{h},\delta u_{h},\Delta u_{h})
-\end{align*}
-so that the optimality condition becomes
-\begin{align*}
-\langle &Bu_{h} + B'(u_{h},\Delta u_{h}) - l,\\
-             &R_{V}^{-1}\left( B'(u_{h},\delta u_{h}) + B''(u_{h},\delta u_{h},\Delta u_{h}) \right)) \rangle = 0 \quad \forall \delta u_{h} \in U_{h}.
-\end{align*}
-\end{frame}
-\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
-\begin{frame}
-\frametitle{Minimization of the Nonlinear Residual}
-\begin{align*}
-\langle &Bu_{h} + B'(u_{h},\Delta u_{h}) - l,\\
-             &R_{V}^{-1}\left( B'(u_{h},\delta u_{h}) + B''(u_{h},\delta u_{h},\Delta u_{h}) \right)) \rangle = 0 \quad \forall \delta u_{h} \in U_{h}.
-\end{align*}
-Dropping the terms that are second order in $\Delta u_{h}$ and defining $v_{\delta u_{h}} = R_{V}^{-1}B'(u_{h},\delta u_{h})$, we have
-\begin{align*}
-&\langle Bu_{h} - l, v_{\delta u_{h}} \rangle\\
- &+ \langle Bu_{h} - l, R_{V}^{-1}B''(u_{h},\delta u_{h},\Delta u_{h}) \rangle \\
- &+ \langle B'(u_{h},\Delta u_{h}),  v_{\delta u_{h}} \rangle = 0.
-\end{align*}
-Rewrite the second term:
-\begin{align*}
-&\langle Bu_{h} - l, R_{V}^{-1}B''(u_{h},\delta u_{h},\Delta u_{h}) \rangle\\
- &= \left( R_{V}^{-1} (Bu_{h} - l), R_{V}^{-1}B''(u_{h},\delta u_{h},\Delta u_{h}) \right)_{V} \\
-&= \langle B''(u_{h},\delta u_{h},\Delta u_{h}), R_{V}^{-1} (Bu_{h} - l) \rangle.
-\end{align*}
-\end{frame}
-\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
-\begin{frame}
-\frametitle{Minimization of the Nonlinear Residual}
-We then have:
-\begin{align*}
-&\langle Bu_{h} - l, v_{\delta u_{h}} \rangle\\
- &+ \langle B''(u_{h},\delta u_{h},\Delta u_{h}), R_{V}^{-1} (Bu_{h} - l) \rangle \\
- &+ \langle B'(u_{h},\Delta u_{h}),  v_{\delta u_{h}} \rangle = 0.
-\end{align*}
-Defining $v_{u_{h}} = R_{V}^{-1} (Bu_{h} - l)$, the linearized problem is then
-\begin{align*}
-b'(u_{h},\Delta u_{h}; v_{\delta u_{h}}) + b''(u_{h},\delta u_{h}, \Delta u_{h}; v_{u_{h}}) = - b(u_{h}, v_{\delta u_{h}}) + l(v_{\delta u_{h}}).
-\end{align*}
-The solution to this problem minimizes the nonlinear residual $\NVRnorm{Bu_{h}-l}_{V'}$.
-\end{frame}
-
-% Assumptions for the well-posedness theorem
-\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
-\begin{frame}
-\frametitle{Technical Assumptions (true for VGP Stokes)}
-Under modest technical assumptions (true for Stokes), we have\footnote{\FootSize \bibentry{DPGStokes}}\\
-\[
-\NVRnorm{Au} \geq \gamma \NVRnorm{u} \implies \sup_{v \in H_{A^{*}}} \frac{b((u,\widehat{u}),v)}{\NVRnorm{v}_{H_{A^{*}}}} \geq \gamma_{\rm DPG} \left(\NVRnorm{u}^{2} + \NVRnorm{\widehat{u}}^{2}_{\widehat{H}_{A}(\Gamma_{h})}\right)^{1/2}
-\]
-where $\gamma_{\rm DPG} = O(\gamma)$ is a mesh-independent constant, and $\NVRnorm{\cdot}_{\widehat{H}_{A}(\Gamma_{h})}$ is the minimum energy extension norm.\\
-\vspace{5mm}
-In the next slides, we detail the assumptions.
-\end{frame}
-\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
-\begin{frame}
-\frametitle{Technical Assumptions (true for VGP Stokes)}
-\[
-\NVRnorm{Au} \geq \gamma \NVRnorm{u} \implies \sup_{v \in H_{A^{*}}} \frac{b((u,\widehat{u}),v)}{\NVRnorm{v}_{H_{A^{*}}}} \geq \gamma_{\rm DPG} \left(\NVRnorm{u}^{2} + \NVRnorm{\widehat{u}}^{2}_{\widehat{H}_{A}(\Gamma_{h})}\right)^{1/2}
-\]
-Define $C$ as the operator arising from integration by parts:
-\[
-(Au,v)_{\Omega} = (u, A^{*}v)_{\Omega} + \langle Cu, v \rangle.
-\]
-We split $C$ into $C_{1}$ and $C_{2}$ such that 
-\begin{align*}
-\langle Cu, v \rangle &= \langle C_{1}u, v \rangle + \langle C_{2}u, v \rangle \\
-&= \langle C_{1}u, v \rangle + \langle u, C_{2}'v \rangle
-\end{align*}
-where $C_{1}u = f_{D}$ corresponds to the Dirichlet BCs imposed. \\
-\end{frame}
-\addtocounter{framenumber}{-1} % make the next frame # the same as the previous
-\begin{frame}
-\frametitle{Technical Assumptions (true for VGP Stokes)}
-\[
-\NVRnorm{Au} \geq \gamma \NVRnorm{u} \implies \sup_{v \in H_{A^{*}}} \frac{b((u,\widehat{u}),v)}{\NVRnorm{v}_{H_{A^{*}}}} \geq \gamma_{\rm DPG} \left(\NVRnorm{u}^{2} + \NVRnorm{\widehat{u}}^{2}_{\widehat{H}_{A}(\Gamma_{h})}\right)^{1/2}
-\]
-Assumptions:
-\begin{itemize}
-\item Theorem Hypothesis: with homogeneous boundary condition $C_{1}u=0$ in place, operator $A$ is bounded below in the $L^{2}$-orthogonal component of its null space.
-\item $C_{1}$ and $C_{2}$ are defined in such a way that
-\[ \left( \langle u,
-  C_2^\prime v\rangle = 0 \quad \forall u \: : C_1 u = 0 \right) \implies
-  C_2^\prime v = 0.
-\]
-\item $A$ and $A^{*}$ are surjective.
-\item Both graph spaces $H_{A}(\Omega)$ and $H_{A^{*}}(\Omega)$ admit corresponding trace spaces $\widehat{H}_{A}(\partial \Omega)$ and $\widehat{H}_{A^{*}}(\partial \Omega)$.
-\item The boundary term $\langle Cu, v \rangle$ arising from integration by parts is definite.
-\end{itemize}
-
-\end{frame}
-
 \end{document}

### 2012-10-25 docs/Jesse/GlobalLocalTesting/paper.tex

--- 2012-06-13 docs/Jesse/HeuerPaper/paper.tex
@@
 %\title{$\epsilon$-explicit analysis of DPG for convection-dominated diffusion}
-\title{Robust DPG method for convection-dominated diffusion problems II: a natural inflow condition}
+\title{Globally and locally optimal test functions}
 \date{}
@@
 
-\section{Introduction}
+\section{The ultra-weak variational formulation}
 
-\subsection{Singular perturbation problems and robustness}
+\subsection{The adjoint equation and $L^2$ optimality}
 
-The finite element/Galerkin method has been widely utilized in engineering to solve partial differential equations governing the behavior of physical phenomena in engineering problems.
-The method relates the solution of a partial differential equation (PDE) to the solution of a corresponding variational problem.
-The finite element method itself provides several advantages --- a framework for systematic mathematical analysis of the behavior of the method, weaker regularity constraints on the solution than implied by the strong form of the equations, and applicability to very general physical domains and geometries.
+Assuming boundedness below of $A$, as the extra $L^2$ term disappears, we get $L^2$ optimality. The ultra-weak variational form gives
+\begin{align*}
+b(u_h,v) = \LRp{u_h,A^*v} + \LRa{\widehat{u},v} = \text{load and boundary conds} = b(u,A^*v)
+\end{align*}
+If we use for our test functions solutions of the adjoint equation $A^*v = u$ (with appropriate adjoint boundary conditions), $u_h$ is the best $L^2$ projection of the exact solution $u$ onto $U_h$.
 
-Historically, the Galerkin method has been very successfully applied to a broad range of problems in solid mechanics, for which the variational problems resulting from the PDE are symmetric and coercive (positive-definite).
-It is well known that the finite element method produces optimal or near-optimal results for such problems, with the finite element solution matching or coming close to the best approximation of the solution in the finite element space.
-However, standard Bubnov-Galerkin methods tend to perform poorly for the class of PDEs known as singular perturbation problems.
-These problems are often characterized by a parameter that may be either very small or very large in the context of physical problems.
-An additional complication of singular perturbation problems is that very often, in the limiting case of the parameter blowing up or decreasing to zero, the PDE itself will change types (e.g.\ from elliptic to hyperbolic).
+\section{Test norms for the convection-diffusion problem}
 
-\subsubsection{Convection-diffusion}
+Introduce the graph norm here.
 
-A canonical example of a singularly perturbed problem is the convection-diffusion equation.
-%The equation models the convection of fluid along a direction $\beta$ with a viscous dissipation of magnitude $\epsilon$.
-In the limit as $\epsilon\rightarrow 0$, the convection-diffusion equation transforms from a parabolic to a hyperbolic partial differential equation.
-In 1D, the convection-diffusion equation is
+\subsection{Local and global optimal test functions}
+
+Note that globally optimal test functions only produce boundary layers at the global inflow boundary.
+
+Show representation of global test functions in local test functions using Jay's proof using orthogonal subspaces and flux test functions.
+
+\section{Numerical experiments}
+
+\subsection{The effect of under-resolved boundary layers}
+
+\textcolor{red}{Can we quantify the effect of under-resolving boundary layers?}
+
 \begin{align*}
-\beta u'-\epsilon u'' &= f.
+b\LRp{\LRp{u,\sigma, \uh,\fnh},\LRp{v,\tau}} = \LRp{u, \Grad_h\cdot \tau - \beta\cdot \Grad_h v}_{\Oh} + \LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad_h v}_{\Oh} + \LRa{\uh,\tau_n}_{\Gh} + \LRa{\fnh,v}_{\Gh}
 \end{align*}
-The equation represents the change in the concentration $u$ of a quantity in a given medium, taking into account both convective and diffusive effects.
-$\beta$ represents the speed of convection, while the singular perturbation parameter $\epsilon$ represents the diffusivity of the medium.
-In the limit of an inviscid medium as $\epsilon\rightarrow 0$, the equation changes types, from elliptic to hyperbolic, and from second order to first order.
-For Dirichlet boundary conditions $u(0)=u_0$ and $u(1)= u_1$, the solution can develop sharp boundary layers of width $\epsilon$ near the outflow.
-
-%The finite element method has performed notoriously poorly for this example, as well as for many other singularly perturbed problems.
-This poor performance is captured by the error bound for the finite element method applied to the convection-diffusion equation - under the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}
-The poor performance of the finite element method for this problem is reflected in the bound on the error in the finite element solution --- under the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}:
-\[
-\|u-u_h\|_\epsilon \leq C \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
-\]
-for $\|u\|_\epsilon^2 \coloneqq \|u\|_{L^2}^2 + \epsilon \|u'\|_{L^2}^2$, with $C$ independent of $\epsilon$. An alternative formulation of the above bound is 
-\[
-\|u-u_h\|_{H^1(0,1)} \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
-\]
-where $C(\epsilon)$ grows as $\epsilon\rightarrow 0$.
-The dependence of the constant $C$ on $\epsilon$ is referred to as a \textit{loss of robustness} --- as the singular perturbation parameter $\epsilon$ decreases, our finite element error is bounded more and more loosely by the best approximation error.
-As a consequence, the finite element solution can diverge significantly from the best finite element approximation of the solution for very small values of $\epsilon$.
-For example, on a coarse mesh, and for small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation with a boundary layer develops spurious oscillations everywhere in the domain, even where the best approximation error is small.
-These oscillations grow in magnitude as $\epsilon \rightarrow 0$, eventually polluting the entire solution.
-
-%, allowing for more and more error in the finite element solution for as $\epsilon$ shrinks. 
-%Intuitively, a non-robust method will perform increasingly worse as $\epsilon$ decreases.
-
-\subsubsection{Wave propagation}
-
-Another example of a singular perturbation problem which experiences loss of robustness is high frequency wave propagation, in which the singular perturbation parameter is the wavenumber $k$, where $k\rightarrow \infty$.
-The loss of robustness in this case manifests as ``pollution" error, a phenomenon in which the finite element solution degrades over many wavelengths for high wavenumbers (commonly manifesting as a phase error between the FE solution and the exact solution).
-
-\subsubsection{Stabilization terms}
-
-Traditionally, instability/loss of robustness has been dealt with using residual-based stabilization techniques.
-Given some variational form, the problem is modified by adding to the bilinear form the strong form of the residual, weighted by a test function and scaled by a stabilization constant $\tau$.
-The most well-known example of this technique is the streamline-upwind Petrov-Galerkin (SUPG) method, which is a stabilized method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.
-SUPG stabilization not only removes the spurious oscillations from the finite element solution of the convection-diffusion equation, but delivers the best finite element approximation in the $H^1$ norm.
-An important difference between residual-based stabilization techniques and other stabilizations is the idea of \textit{consistency} --- by adding stabilization terms based on the residual, the exact solution still satisfies the same variational problem (i.e.\ Galerkin orthogonality still holds).\footnote{Contrast this to an artificial diffusion method, where a specific amount of additional viscosity is added based on the magnitude of the convection and diffusion parameters.
-The exact solution to the original equation no longer satisfies the new stabilized formulation.}
-
-The addition of residual-based stabilization terms can also be interpreted as a modification of the test functions --- in other words, stabilization can be achieved by changing the test space for a given problem.
-We approach the idea of stabilization through the construction of \textit{optimal test functions} to achieve optimal approximation properties.
-
-%\textcolor{red}{add bit about SUPG/residual-based stabilization terms and test functions}
-
-\subsection{Discontinuous Petrov-Galerkin methods with optimal test functions}
-\seclab{optimalTest} Petrov-Galerkin methods, in which the test space
-differs from the trial space, have been explored for over 30 years,
-beginning with the approximate symmetrization method of Barrett and
-Morton~\cite{BARRETT01101981}. The idea was continued with the SUPG
-method of Hughes, and the characteristic Petrov-Galerkin approach of
-Demkowicz and Oden~\cite{Demkowicz1986188}, which introduced the
-idea of tailoring the test space to change the norm in which a finite
-element method would converge.
-
-The idea of optimal test functions was introduced by Demkowicz and
-Gopalakrishnan in \cite{DPG2}.  Conceptually, these optimal test
-functions are the natural result of the minimization of a residual
-corresponding to the operator form of a variational equation. The
-connection between stabilization and least squares/minimum residual
-methods has been observed previously \cite{GLS}. However, the method in \cite{DPG2} distinguishes itself
-by measuring the residual of the natural \textit{operator form of the equation}, which is posed in the dual space, and measured with the dual norm, as we now discuss.
-
-Throughout the paper, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U'$ and $V'$ as the respective topological dual spaces.
-Let $U_h \subset U$ and $V_h\subset V$ be finite dimensional subsets.
-We are interested in the following problem
-\begin{equation}
-\eqnlab{variationEq}
-\left\{
-  \begin{array}{l}
-    \text{Given } l \in V', \text{ find } u_h \in U_h  \text{ such that} \\ 
-    b(u_h,v_h) = l(v_h), \quad \forall v_h\in V_h,
-  \end{array}
-  \right.
-\end{equation}
-where $b\LRp{\cdot,\cdot}: U \times V \to \mbb{R}$ is a continuous
-bilinear form.  $U$ is chosen to be some trial space of approximating functions, but $V_h$ is as of yet unspecified.
-
-Throughout the paper, we suppose the variational
-problem \eqnref{variationEq} to be well-posed. In that case, we can
-identify a unique operator $B:U\rightarrow V'$ such that
-\[
-\langle Bu,v\rangle_V \coloneqq b(u,v), \quad u\in U, v\in V
-\]
-with $\LRa{\cdot, \cdot}_V$ denoting the duality pairing between $V'$ and $V$, to obtain the operator form of the continuous variational problem
-\begin{equation}
-\eqnlab{dualEq}
-Bu = l \quad \text{in } V'.
-\end{equation}
-In other words, we can represent the continuous form of our variational equation
-\eqnref{variationEq} equivalently as the operator equation \eqnref{dualEq} with values in the
-dual space $V'$.  This motivates us to consider the conditions under which the solution to \eqnref{variationEq} is the solution to the minimum residual problem in $V'$ 
-\[
-u_h = \underset{u_h\in U_h}{\arg\min}\, J(u_h),
-\]
-where $J(w)$ is defined for $w\in U$ as 
-\[
-J(w) = \frac{1}{2}\|Bw-l\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(w,v)-l(v)|^2}{\nor{v}_V^2}.
-\]
-For convenience in writing, we will abuse the notation $\sup_{v \in V}$ to denote $\sup_{v\in V\setminus\{0\}}$ for the remainder of the paper.
-
-Let us define $R_V: V \to V'$ as the Riesz map, which identifies
-elements of $V$ with elements of $V'$ by 
-\[
-\langle R_V v,\delta
-v\rangle_V \coloneqq(v, \delta v)_V, \quad \forall \delta v \in V.
-\]
-Here, $(\cdot, \cdot)_V$ denotes the
-inner product in $V$. As $R_V$ and its inverse, $R_V^{-1}$, are both
-isometries, e.g.\ $\|f\|_{V'} = \|R_V^{-1} f\|_V, \forall f \in V'$, we
-have
-\begin{equation}
-\eqnlab{minimization}
-\min_{u_h\in U_h} J(u_h) = \frac{1}{2}\left\|Bu_h-l\right\|_{V'}^2 =  \frac{1}{2}\left\|R_V^{-1}(Bu_h-l)\right\|_V^2.
-\end{equation}
-The first order optimality condition for \eqnref{minimization} requires
-the G\^ateaux derivative to be zero in all directions $\delta u \in
-U_h$, i\.e\.,
-\begin{align*}
-\left(R_V^{-1}(Bu_h-l),R_V^{-1}B\delta u\right)_V = 0, \quad \forall \delta u \in U. 
-\end{align*}
-We define, for a given $\delta u \in U$, the corresponding {\em optimal test function} $v_{\delta u}$
-\begin{equation}
-\eqnlab{optv}
-v_{\delta u} \coloneqq R_V^{-1}B\delta u \quad  \text{in } V.
-\end{equation} 
-The optimality condition then becomes
-\[
- \langle Bu_h-l, v_{\delta u}\rangle_V = 0, \quad \forall \delta u \in U
-\]
-which is exactly the standard variational equation in
- \eqnref{variationEq} with $v_{\delta u}$ as the test functions.
-We can define the optimal test space $V_{\rm opt} \coloneqq \{v_{\delta u} \text{ s.t.
-} \delta u\in U\}$.
-Thus, the solution of the variational problem \eqnref{variationEq} with test space $V_h = V_{\rm opt}$ minimizes the residual in the dual norm $\nor{Bu_h-l}_{V'}$.
-This is the key idea behind the concept of optimal test functions.
-
-Since $U_h \subset U$ is spanned by a finite number of basis functions $\LRc{\varphi_i}_{i=1}^N$, \eqnref{optv} allows us to compute (for each basis function) a corresponding optimal test function $v_{\varphi_i}$.
-The collection $\LRc{v_{\varphi_i}}_{i = 1}^N$ of optimal test functions then forms a basis for the optimal test space.
-In order to express optimal test functions defined in \eqnref{optv} in a more familiar form, we take  $\delta u = \varphi$, a generic basis function in $U_h$, and rewrite \eqnref{optv} as
-\[
-R_Vv_{\varphi} = B\varphi, \quad \text{in } V',
-\]
-which is, by definition, equivalent to
-\[
-\LRp{v_\varphi,\delta v}_V = \LRa{R_Vv_\varphi,\delta v}_{V}=
-\LRa{B\varphi, \delta v}_V = b\LRp{\varphi,\delta v}, \quad
-\forall \delta v \in V.
-\]
-%% Now, let us define the \textit{trial-to-test} operator $T =
-%% R_V^{-1}B$, which, by \eqnref{optv}, maps a trial function $\delta u$
-%% to its corresponding \textit{optimal} test function $v = T\delta u$.
-%% On the other hand,
-As a result, optimal test functions can be determined by solving the auxiliary
-variational problem
-\begin{equation}
-\eqnlab{optvVar}
-\left(v_\varphi,\delta v\right)_V = b(\varphi,\delta v), \quad \forall
-\delta v \in V.
-\end{equation}
-However, in general, for standard $H^1$ and $H({\rm div})$-conforming finite element methods, test functions are continuous over the entire domain, and hence solving variational problem \eqnref{optvVar} for each optimal test function requires a global operation over the entire mesh, rendering the method impractical.
-A breakthrough came through the development of
-discontinous Galerkin (DG) methods, for which basis functions are
-discontinuous over elements. In particular, the use of discontinuous
-test functions $\delta v$ reduces the problem of determining global 
-optimal test functions
-in \eqnref{optvVar} to local problems that can be solved in an
-element-by-element fashion.
-
-We note that solving \eqnref{optvVar} on each element exactly is
-infeasible since it amounts to inverting the Riesz map $R_V$ exactly.
-Instead, optimal test functions are approximated using the standard
-Bubnov-Galerkin method on an ``enriched" subspace $\tilde{V} \subset
-V$ such that $\dim(\tilde{V}) > \dim(U_h)$ elementwise \cite{DPG1, DPG2}. In this
-paper, we assume the error in approximating the optimal test functions
-is negligible, and refer to the work in \cite{practicalDPG} for
-estimating the effects of approximation error on the performance of DPG.
-
-It is now well known that the DPG method
-delivers the best approximation error in the ``energy norm" --- that is
-\cite{Bui-ThanhDemkowiczGhattas11a, DPG2,DPG4} 
-\begin{equation}
-\eqnlab{optimalError}
-\nor{u-u_h}_{U,E} = \inf_{w\in U_h} \nor{u-w}_{U,E},
-\end{equation}
-where the energy norm $\|\cdot \|_{U,E}$ is defined for a function $\varphi \in U$ as
-\begin{equation}
-\eqnlab{energyNorm} \|\varphi\|_{U,E} \coloneqq \sup_{v\in V}
-\frac{b(\varphi,v)}{\|v\|_V} = \sup_{\nor{v}_V = 1} b(\varphi,v) =
-\sup_{\nor{v}_V = 1} \LRa{B\varphi,v}_V = \nor{B\varphi}_{V'} =
-\nor{v_\varphi}_V,
-\end{equation}
-where the last equality holds due to the isometry of the Riesz map
-$R_V$ (or directly from \eqnref{optvVar} by taking the supremum). An
-additional consequence of adopting such an energy norm is that,
-without knowing the exact solution, the energy error $\|u-u_h\|_{U,E}$ can
-be determined by computing $\|v_{u-u_h}\|_V$ from the following
-identity
-\[
-\left(v_{u-u_h},\delta v\right)_V = b(u-u_h,\delta v) = l\LRp{\delta
-v} - b(u_h,\delta v).
-\]
-This is simply a consequence of the least-squares nature of DPG; the energy error is simply the norm of the  residual in $V'$.
-
-Practically speaking, this implies that the DPG method is discretely stable on any mesh.
-In particular, DPG is unconditionally stable for higher order adaptive meshes, where discrete stability is often an issue.
-
-\subsection{Duality between trial and test norms (energy norm pairings)}
-%\subsection{Abstract energy norm pairings}
-\seclab{energyPair}
-A clear property of the energy norm defined by \eqnref{energyNorm} is that the trial norm $\nor{\cdot}_{U,E}$ is induced by a given test norm.
-However, the reverse relationship holds as well; for any trial norm, the test norm that induces such a norm is recoverable through duality.
-We have a result, proved in \cite{Bui-ThanhDemkowiczGhattas11a}: assuming, for simplicity, that the bilinear form $b(u,v)$ is definite, given any norm $\nor{\cdot}_{U}$ on the trial space $U$, for $\varphi \in U$, we can represent $\nor{\varphi}_{U}$ via
-\[
-\nor{\varphi}_{U} = \sup_{v \in V}\frac{b\LRp{w,v}}{\nor{v}_{V,U}}.
-\]
-where $\nor{v}_{V,U}$ is defined through
-\[
-\nor{v}_{V,U} = \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U}}.
-\]
-%In other words, the norm $\nor{\cdot}_V$ in $V$ can be recovered using the energy norm $\nor{\cdot}_{U,E}$ in $U$, and vice versa.
-
-In particular, given two arbitrary norms $\nor{\cdot}_{U,1}$ and $\nor{\cdot}_{U,2}$ in $U$
-such that $\nor{\cdot}_{U,1} \le c \nor{\cdot}_{U,2}$ for some constant
-$c$, they generate two norms $\nor{\cdot}_{V,U,1}$ and
-$\nor{\cdot}_{V,U,2}$ in $V$ defined by
-\[
-\nor{v}_{V,U,1} \coloneqq \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U,1}}, \quad
-\text{and }\nor{v}_{V,U,2} \coloneqq \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U,2}},
-\]
-such that $\nor{\cdot}_{V,U,1}$ and $\nor{\cdot}_{V,U,2}$ induce
-$\nor{\cdot}_{U,1}$ and $\nor{\cdot}_{U,2}$ as energy
-norms in $U$, respectively. That is,
-\[
-\|\varphi\|_{U,1} = \sup_{v\in V}
-\frac{b(\varphi,v)}{\|v\|_{V,U,1}}, \quad \text{and }\|\varphi\|_{U,2} = \sup_{v\in V}
-\frac{b(\varphi,v)}{\|v\|_{V,U,2}}.
-\]
-
-A question that remains to be addressed is to establish the relationship
-between $\nor{\cdot}_{V,U,1}$ and $\nor{\cdot}_{V,U,2}$, given that
-$\nor{\cdot}_{U,1} \le c \nor{\cdot}_{U,2}$. But this is
-straightforward since we have
-\begin{align*}
- \| v \|_{V,U,2} = \sup_{u \in U} \frac{b\left(w,v\right)}{\left\|
-  w \right\|_{U,2}} \le c\sup_{w \in U} \frac{b\left(w,v\right)}{\left\| w
-  \right\|_{U,1}} = c\| v \|_{V,U,1}.
-\end{align*}
-Consequently, a stronger energy norm in $U$ will generate a weaker
-norm in $V$ and vice versa. In other words, to show that an
-energy norm $\nor{\cdot}_{U,1}$ is weaker than another energy norm
-$\nor{\cdot}_{U,2}$ in $U$, one simply needs to show the reverse inequality on the
-corresponding norms in $V$, that is, $\nor{\cdot}_{V,U,1}$ is stronger
-than $\nor{\cdot}_{V,U,2}$.
-
-%From now on, unless otherwise stated, we will refer to  $\nor{\cdot}_{V,U,1}$, $\nor{\cdot}_{V,U,2}$, and $\nor{\cdot}_{V}$ as the test norms which induce $\nor{\cdot}_{U,1}$, $\nor{\cdot}_{U,2}$, and $\nor{\cdot}_{U,E}$ and vice versa, in the sense discussed above.
-From now on, unless otherwise stated, we will refer to $\nor{\cdot}_{V,U}$ as the test norm that induces a given norm $\nor{\cdot}_U$.
-Likewise, we will refer $\nor{\cdot}_{U,V}$ as the trial norm induced by a given test norm $\nor{\cdot}_V$.
-In this paper, for simplicity of exposition, we shall call a pair of norms in $U$ and $V$ that induce each other as an {\em energy norm pairing}.
-
-\subsection{Discontinuous Petrov-Galerkin methods with the ultra-weak formulation}
-\seclab{abstractUweak}
-
-The naming of the discontinuous Petrov-Galerkin method refers to the fact that the method is a Petrov-Galerkin method, and that the test functions are specified to be discontinuous across element boundaries.
-There is no specification of the regularity of the trial space, and we stress that the idea of DPG is not inherently tied to a single variational formulation \cite{Bui-ThanhDemkowiczGhattas11a}.
-
-In most of the DPG literature, however, the discontinuous Petrov-Galerkin method refers to the combination of the concept of locally computable optimal test functions in Section \secref{optimalTest} with the so-called ``ultra-weak formulation" \cite{DPG1,DPG2,DPG3,DPG4,DPGElas,DBLP:journals/procedia/NiemiCC11}.
-Unlike the previous two sections in which we studied the general equation \eqnref{variationEq} given by abstract bilinear and linear forms, we now consider a concrete instance of \eqnref{variationEq} resulting from an ultra-weak formulation for an abstract first-order system of PDEs $Au = f$.
-Additionally, from this section onwards, we will refer to DPG as the pairing of the ultra-weak variational formulation with the concept of locally computable optimal test functions.
-
-We begin by partitioning the domain of interest $\Omega$ into $\Nel$ non-overlapping elements $K_j, j = 1,\hdots,\Nel$ such that $\Oh = \cup_{j=1}^\Nel K_j$ and $\overline{\Omega} = \overline{\Omega}_h$.
-Here, $h$ is defined as $h= \max_{j\in \LRc{1,\hdots,\Nel}}\text{diam}\LRp{K_j}$.
-We denote the mesh ``skeleton" by $\Gh = \cup_{j=1}^\Nel \partial K_j$; the set of all faces/edges $e$, each of which comes with a normal vector ${n}_e$.
-The internal skeleton is then defined as $\Gamma^0_h = \Gh \setminus \partial \Omega$.
-If a face/edge $e \in \Gh$ is the intersection of $\partial K_i$ and $\partial K_j$, $i \ne j$, we define the following jumps:
-\[
-\jump{v} = \text{sgn} \LRp{{n}^-}v^- + \text{sgn} \LRp{{n}^+}v^+, \quad
-\jump{\tau \cdot n} = {n}^-\cdot \tau^- + {n}^+\cdot\tau^+,
-\]
-where
-\[
-\text{sgn}\LRp{{n}^{\pm}} =
-\left\{
-\begin{array}{ll}
-1 & \text{if } {n}^{\pm} = {n}_e \\
--1 & \text{if } {n}^\pm = -{n}_e
-\end{array}
-\right..
-\]
-For $e$ belonging to the domain boundary $\partial \Omega$, we define
-\[
-\jump{v} = v, \quad
-\jump{\tau \cdot n} = {n}_e\cdot \tau.
-\]
-Note that we allow arbitrariness in assigning ``-'' and ``+'' quantities to the adjacent elements $K_i$ and $K_j$.
-%For the rest of the paper, we will use the same notation for both a function and its trace (if it is well-defined) when there is no ambiguity.
-
-The ultra-weak formulation for $Au = f$ on $\Oh$, ignoring boundary
-conditions for now, reads
-\begin{equation}
-\eqnlab{uweak}
-b\left(\left(u, \widehat{u}\right),v\right) \coloneqq \langle \widehat{u}, \jump{v}
-\rangle_{\Gh} - (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh},
-\end{equation}
-where we have denoted $\LRa{\cdot,\cdot}_{\Gh}$ as the duality
-pairing on $\Gh$, $\LRp{\cdot,\cdot}_{\Oh}$ the $L^2$-inner
-product over $\Oh$, and $A_h^*$ the formal adjoint resulting from
-element-wise integration by parts.  Occasionally, for simplicity in
-writing, we will ignore the subscripts in the duality pairing and
-$L^2$-inner product if they are $\Gh$ and $\Oh$. Both the
-inner product and formal adjoint are understood to be taken
-element-wise. Using the ultra-weak formulation, the regularity
-requirement on solution variable $u$ is relaxed, that is, $u$ is now
-square integrable for the ultra-weak formulation \eqnref{uweak} to be
-meaningful, instead of being (weakly) differentiable.  The trade-off
-is that $u$ does not admit a trace on $\Gh$ even though it did
-originally. Consequently, we need to introduce an additional new
-``trace'' variable $\widehat{u}$ in \eqnref{uweak}, that is defined only on
-$\Gh$.
-
-The energy setting is now clear; namely,
-\[
-u\in L^2\LRp{\Oh} \equiv L^2(\Omega), \quad v\in V=D(A^*_h), \quad
-\widehat{u}\in \gamma(D(A)),
-\]
-where $D(A_h^*)$ denotes the broken graph space corresponding to $A_h^*$,
-and $\gamma(D(A))$ the trace space (assumed to exist) of the graph space of
-operator $A$.
-The first discussion of the well-posedness of DPG with the ultra-weak formulation can be found in \cite{analysisDPG}, where the proof is presented for the Poisson and convection-diffusion equations.
-A more comprehensive discussion of the abstract setting for DPG with the ultra-weak formulation using the graph space, as well as a more general proof of well-posedness, can be consulted in \cite{Bui-ThanhDemkowiczGhattas11b}.
-
-%\subsection{Optimal and quasi-optimal test norms}
-\subsection{Canonical energy norm pairings for ultra-weak formulation}
-
-From the discussion in Section~\secref{energyPair} of energy norm and test norm pairings, we know that specifying either a test norm or trial norm is sufficient to define an energy pairing.
-In this section, we derive and discuss two important energy norm pairings, the first of which begins by specifying the canonical norm in $U$ and inducing a test norm on $V$.
-The second pairing begins instead by specifying the canonical norm on $V$ under the ultra-weak formulation \eqnref{uweak} and inducing an energy norm on the trial space $U$.
-
-We begin first with the canonical norm in $U$. Since $\uh \in \gamma\LRp{D\LRp{A}}$, the standard norm for $\uh$ is
-the so-called minimum energy extension norm defined as
-\begin{equation}
-\eqnlab{MEnorm}
-\|\widehat{u}\| = \inf_{w\in D\LRp{A},
-  \left.w\right|_{\Gh}=\widehat{u}} \|w\|_{D\LRp{A}}.
-\end{equation}
-The canonical norm for the group variable $\LRp{u,\uh}$ is then given by
-\[
-\|\left(u,\widehat{u}\right)\|_U^2 = \|u\|^2_{\L} + \|\widehat{u}\|^2,
-\]
-Applying the Cauchy-Schwarz inequality, we arrive at
-\[
-b\LRp{\LRp{u,\uh},v} \le \nor{\LRp{u,\uh}}_U \nor{v}_{V,U},
-\]
-where
-\[
-\nor{v}_{V,U}^2 = \|A_h^*v\|_{\L}^2
-+\left(\sup_{\widehat{u} \in \gamma\LRp{D\LRp{A}}} \frac{\LRa{ \widehat{u},
-  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2.
-\]
-
-On the other hand, since $v \in D\LRp{A^*_h}$, the canonical norm for
-$v$ is the broken graph norm: 
-\[
-\nor{v}_V^2 =  \|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2.
-\]
-Using the Cauchy-Schwarz inequality again, we obtain
-\[
-b\LRp{\LRp{u,\uh},v} \le \nor{\LRp{u,\uh}}_{U,V} \nor{v}_{V},
-\]
-where
-\begin{equation}
-\eqnlab{inducedQuasi}
-\nor{\LRp{u,\uh}}_{U,V}^2 = \nor{u}_{\L}^2
-+\sup_{v \in D\LRp{A_h^*}} \frac{\LRa{\widehat{u},
-  \jump{v}}_{\Gh}^2}{\|v\|_V^2},
-\end{equation}
-
-Using the framework developed in \cite{Bui-ThanhDemkowiczGhattas11a},
-one can show that both pairs $\LRp{\nor{\LRp{u,\uh}}_U,
-  \nor{v}_{V,U}}$ and $\LRp{\nor{\LRp{u,\uh}}_{U,V}, \nor{v}_{V}}$ are
-energy norm pairings in the sense discussed in Section
-\secref{energyPair}. That is, the canonical norm $\nor{\LRp{u,\uh}}_U$
-in $U$ induces (generates) the norm $\nor{v}_{V,U}$ in $V$, while the
-canonical norm $\nor{v}_V$ in $V$ induces (generates) the energy norm
-$\nor{\LRp{u,\uh}}_{U,V}$ in $U$. In the DPG literature \cite{DPG4}, $\nor{v}_{V,U}$ is known as the {\em optimal test norm},
-while $\nor{v}_{V}$ is known as the {\em quasi-optimal test norm}.
-
-\begin{figure}[!h]
-\centering
-\begin{tabular}{l c c}
-Trial norm & & Test norm \\
-\hline
-$\boxed{\|u\|^2_{\L} + \|\widehat{u}\|^2}$ & $\Longrightarrow$  & $\|A_h^*v\|_{\L}^2
-+\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},
-  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2$ \\
-%\hline
-%Quasi-optimal trial norm & & Canonical test norm \\
-%\hline
-$\nor{u}_{\L}^2+\sup_{v } \left(\frac{\LRa{\widehat{u},
-  \jump{v}}_{\Gh}}{\|v\|_V}\right)^2$ &  $\Longleftarrow$ & $\boxed{\|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2}$
-\end{tabular}
-\caption{A summary of the derivation of test/trial norm pairings; we begin with the boxed norm on either the trial or test space, and induce the norm on the other space through duality.
-The optimal \textit{test} norm is naturally derived by beginning with the canonical norm on the trial space, while the quasi-optimal \textit{trial} norm is derived from beginning with the canonical norm on the test space.}
-\end{figure}
-
-The canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ provides a good
-balance between the standard norms on the field $u$ and the flux
-$\uh$ \cite{DPG4}. As a result, if the induced norm $\nor{v}_{V,U}$ (namely, the
-optimal test norm) is used to compute  optimal test functions in
-\eqnref{optvVar}, the finite element error in the canonical norm is the
-best in the sense of \eqnref{optimalError}.
-
-Unfortunately, the optimal test norm is non-localizable due to the presence of the jump term $\jump{v}$.\footnote{A localizable norm $\nor{v}_{V(\Oh)}$ can be written in the form
-$$\nor{v}_{V(\Oh)} = \sum_{K\in\Oh} \nor{v}_{V(K)},$$ where $\nor{v}_{V(K)}$ is a norm over the element $K$.} Since the jump terms couple elements together, the evaluation of the jump terms requires contributions from all the elements in the mesh.
-Consequently, solving for an optimal test function
-amounts to inverting the Riesz map %, defined on the left sideof \eqnref{optvVar}, 
-over the entire mesh $\Oh$, making the optimal test norm impractical.
-
-On the other hand, the quasi-optimal test norm $\nor{v}_V$, namely the canonical norm in $V$, \textit{is} localizable, and hence practical.
-However, it's worth noting the difference between the induced energy norm $\nor{\LRp{u,\uh}}_{U,V}$ and the canonical norm in $U$; under the induced norm $\nor{\LRp{u,\uh}}_{U,V}$ there is no natural interpretation for the norm in which the error in the flux variable $\uh$ is measured.
-
-Using a variant of the quasi-optimal test norm, numerical results show that the DPG method appears to provide a ``pollution-free" method without phase error for the Helmholtz equation \cite{DPG4}, and analysis of the pollution-free nature of DPG is currently under investigation.
-Similar results have also been obtained in the context of elasticity \cite{DPGElas} and the linear Stokes equations \cite{Camellia}.
-On the theoretical side, the quasi-optimal test norm has been shown to yield a well-posed DPG methodology for the Poisson and convection-diffusion equations \cite{analysisDPG}.
-More recently, this theory has been generalized to show the well-posedness of DPG for the large class of PDEs of Friedrichs' type \cite{Bui-ThanhDemkowiczGhattas11b}.
-
-\section{Model problem and robustness}
-\seclab{sec:modelSec}
-The remainder of the paper focuses on a convection-diffusion model problem using the abstract theory that we
-have discussed so far.
-In particular, we shall use the DPG method based on the ultra-weak formulation with optimal test functions to solve the model problem and analyze its behavior with respect to $\epsilon$.
-Our goal is to show the robustness of the method with respect to $\epsilon$, and demonstrate its usefulness as  a numerical approach to solving singular-perturbed problems.
-
-We consider the following model convection-diffusion problem on a domain
-$\Omega \subset \mathbb{R}^d$ with boundary $\pO \equiv \Gamma$
-\begin{equation}
-\div (\beta u) - \epsilon\Delta u = f  \in \L \label{primal},
-\end{equation}
-which can be cast into the first order form on the group variable
-$\LRp{u,\sigma}$ as
-\begin{equation}
-\eqnlab{CDstrong}
-A \LRp{u,\sigma} \coloneqq \LRs {
-\begin{array}{c}
-\div (\beta u - \sigma) \\ \frac{1}{\epsilon}\sigma - \grad u
-\end{array}} = \LRs{
-\begin{array}{c}
-f \\ 0
-\end{array}
-}.
-\end{equation}
-Using the abstract ultra-weak formulation developed in Section
-\secref{abstractUweak} for the first order system of PDEs \eqnref{CDstrong} we
-obtain
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh} - \LRa{
-\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n,
-  \jump{v} }_{\Gh},
-\end{align*}
-where $\LRp{v, \tau}$ is the group test function. It should be pointed
-out that the divergence and gradient operators are understood to act
-element-wise on test functions $\LRp{v, \tau}$ in the broken graph
-space $ D\LRp{A_h^*} \coloneqq  H^1(\Oh) \times H({\rm div}, \Oh)$, but
-globally as usual on conforming test functions, i.e.\ $ \LRp{v, \tau}
-\in  H^1(\Omega) \times H({\rm div}, \Omega)$. It follows that the
-canonical test norm can be written as
-\[
-\|\left(v, \tau\right)\|_V^2 = \|\left(v, \tau\right)\|_{H^1(\Oh) \times H({\rm div},\Oh)}^2
-= \sum_{K\in \Oh} \|\left(v, \tau\right)\|_{H^1(K) \times H({\rm
-    div},K)}^2,
-\]
-where
-\[
-\|\left(v, \tau \right)\|_{H^1(K) \times H({\rm div},K)}^2 =
-\|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2 + \|\tau\|_{L^2(K)}^2 +
-\|\div \tau\|_{L^2(K)}^2.
-\]
-
-In order to define the proper norm on the trial space, boundary
-conditions need to be specified. We begin by splitting the boundary
-$\Gamma$ as follows
-\begin{align*}
-\Gamma_{-} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\}, \quad {\rm
-  (inflow)}\\ \Gamma_{+} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\},
-\quad {\rm (outflow)}\\ \Gamma_{0} &\coloneqq \{x\in \Gamma;
-\beta_n(x) = 0\},
-\end{align*}
-where $\beta_n \coloneqq \beta \cdot n$.
-Previous work in \cite{DPGrobustness} adopted Dirichlet boundary
-conditions everywhere on $\Gamma$.  
-%and we could obtain the robustness only with special weighted norms in which the weight varied spatially. 
-In this paper, we employ the inflow
-condition of Hesthaven \etal \cite{Hesthaven96astable}, where we set
-\[
-\beta_n u - \sigma_n  = u_0, \quad \text{on } \Gm,
-\]
-instead of $\beta_n u = u_0$. The former resembles the latter
-as $\epsilon$ approaches zero\footnote{For our model problem, as for many problems of interest in computational fluid dynamics, we expect $\grad u$ to be small near the inflow, and that the solutions to \eqref{primal} using $\beta_n u - \sigma_n = f_n = u_0$ on $\Gamma_-$ will converge to that using $u=u_0$ on $\Gamma_-$  for sufficiently small $\epsilon$.}; however, the latter induces a more ``well-behaved" adjoint problem than the former, which, as we will discuss, affects the performance of DPG.
-
-On the outflow boundary, we apply standard homogeneous Dirichlet boundary conditions
-\[
-u = 0, \quad \text{on } \Gp.
-\]
-This paper is intended to act as an extension of work presented by Heuer and Demkowicz in \cite{DPGrobustness}.
-The primary focus of the paper is to analyze the DPG method and extend previous results under this new choice of inflow boundary conditions.
-The difference in the performance of DPG under both new and old boundary conditions is connected to the difference in the adjoint problems induced under each boundary condition.
-The secondary contribution of this paper will be to analyze the performance of DPG under a new mesh-dependent test norm.
-
-\subsection{Norms on $U$}
-
-With the above boundary conditions at hand, the ultra-weak formulation
-\eqnref{uweak} can be fitted in the abstract form \eqnref{variationEq}
-as
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right), \left( v,
-\tau\right)\right) &= \left(u,\div \tau - \beta \cdot \grad
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad
-v\right)_{\Oh} \\
-&- \LRa{ \jump{\tau\cdot n}, \widehat{u} }_{\Gh
-  \setminus \Gp} + \LRa{ \widehat{f}_n, \jump{v} }_{\Gamma_h \setminus
-  \Gm} =  \left(f, v\right) -
-\LRa{ u_0, v }_{\Gamma_-} = l\left(\left(v, \tau\right)\right),
-\end{align*}
-which, after using the setting in Section \secref{abstractUweak},
-suggests the following trial space (see \cite{analysisDPG, Bui-ThanhDemkowiczGhattas11b} for details):
-\begin{align*}
-u, \sigma \in \L, \quad \text{and } \LRp{\uh,\fnh} \in
-\gamma\LRp{D\LRp{A}} \subset \gamma\LRp{  H^1(\Omega) \times
-H({\rm div}, \Omega)} = H^{\frac{1}{2}}\left(\Gh\right) \times H^{-\frac{1}{2}}\left(\Gh\right).
-\end{align*}
-The space for $u$ and $\sigma$ are simply scalar and vector $L^2$ spaces over $\Omega$, while the space for $\left(\uh,\fnh\right)$ is the trace space of the graph space of the operator $A$ subject to the boundary conditions.
-
-The minimum energy extension norm \eqnref{MEnorm} now reads
-\begin{align*}
-\|\widehat{u}\| &= \inf_{w\in H^1(\Omega),
-  \left.w\right|_{\Gamma_+}=0, \left.w\right |_{\Gh\setminus
-    \Gamma_+ } = \widehat{u}} \|w\|_{H^1(\Omega)}, \\ \|\widehat{f}_n\|
-&= \inf_{q\in H({\rm div},\Omega), \left.q\cdot n\right|_{\Gamma_-}=
-  0, \left. q\cdot n \right |_{\Gh\setminus
-    \Gamma_-} = \widehat{f}_n}
-\|q\|_{H({\rm div},\Omega)}.
-\end{align*}
-As a result, the canonical norm on $U$ is given by
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U^2 = 
-\|u\|_{L^2(\Oh)}^2 + \|\sigma\|_{L^2(\Oh)}^2 +
-\|\widehat{u}\|^2 + \|\widehat{f}_n\|^2.
-\]
-
-\subsection{Norms on $V$}
-
-%We will denote $\|\cdot \| = \|\cdot\|_{L^2}$ for all functions defined on $\Oh$. 
-As $\tau \in H({\rm div},\Oh)$ and $v \in H^1(\Oh)$, we will
-construct norms on $v$ and $\tau$ 
-which are equivalent to the canonical $H^1(K) \times H({\rm div},K)$
-norm over a single element
-\[
-\|\left(v,\tau\right)\|_{H^1(K) \times H({\rm div},K)}^2 =
-\|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2 + \|\tau\|_{L^2(K)}^2 +
-\|\div \tau\|_{L^2(K)}^2.
-\]
-The squared norm over the entire triangulation $\Oh$ is defined to be the squared sum of contributions from each element
-\[
-\|\left(v,\tau\right)\|_{H^1(\Oh) \times H({\rm div},\Oh)}^2
-= \sum_{K\in \Oh} \|\left(v,\tau\right)\|_{H^1(K) \times H({\rm
-    div},K)}^2.
-\]
-The exact norms that we will specify on $V$ will be determined later.
-
-The norms on the skeleton $\Gh$ for $v$ and $\tau$ are defined by duality from the bilinear form
-\begin{align*}
-\left\|\jump{\tau\cdot n}\right\| &= \left\|\jump{\tau\cdot n}\right\|_{\Gh \setminus \Gamma_+} \coloneqq \sup_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+} = 0} \frac{\langle \jump{\tau \cdot n}, w\rangle}{\|w\|_{H^1(\Omega)}},\\
-\left\|\jump{v}\right\|&=\left\|\jump{v}\right\|_{\Gh^0 \cup \Gamma_+} \coloneqq \sup_{\eta\in H({\rm div},\Omega), \left.\eta\cdot n\right|_{\Gamma_- \cup \Gamma_0} = 0} \frac{\langle \jump{v}, \eta\cdot n\rangle}{\|\eta\|_{H({\rm div},\Omega)}}.
-\end{align*}
-
-\subsection{Approximability of the quasi-optimal test norm}
-%\textcolor{blue}{need to define what we mean by robustness. perharps the best place is in the introduction}
-An obvious choice for the test norm would be the quasi-optimal norm; it is the canonical test norm, and DPG has been shown to be well-posed and robust under such an optimal test norm for a large class of problems \cite{DPGrobustness,Bui-ThanhDemkowiczGhattas11b, stokesDPG}.
-However, computations with the quasi-optimal test norm for convection-diffusion problems turn out to be quite problematic for small diffusion and coarse meshes.
-
-For convection-diffusion, the quasi-optimal test norm is 
-\[
-\|\left(v,\tau\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v
-\|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 +
-\|v\|_{L^2}^2 + \|\tau\|_{L^2}^2.
-\]
-%We note that the optimal test norm will automatically guarantee the
-%robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.
-Use of this norm for the convection-diffusion problem is difficult --- since the problem \eqnref{optvVar} for optimal test functions is local, we can transform the problem over a single element $K$ to the reference element $\widehat{K}$ and show that it is equivalent to a reaction-diffusion system, with diffusion parameter $\frac{\epsilon}{|K|}$, where $|K|$ is the element measure \cite{DBLP:journals/procedia/NiemiCC11}.
-We refer to the inverse of this parameter $\frac{|K|}{\epsilon}$ as the element Peclet number $\rm Pe$.
-For a coarse mesh and small diffusion parameter $\epsilon$, we will have a large element Peclet number, and optimal test functions under the quasi-optimal test norm will develop strong boundary layers of width $\rm Pe$, as seen in Figure~\ref{fig:optTestBoundary}.
-
-In the application of DPG in \cite{DPG1,DPG2,DPG3,DPG4}, the approximation of optimal test functions is done using polynomial enrichment.
-We search for the solution to \eqnref{optvVar} in the enriched test space $\tilde{V} \approx \prod_{K} P^{p+\Delta p}(K)$, where $p$ is the polynomial order of the trial space on a given element $K$.\footnote{$V$ is only \emph{approximately} equal to the space $\prod_{K} P^{p+\Delta p}(K)$.
-In practice, $V$ is constructed using locally $H^1$-conforming and Raviart-Thomas elements of appropriate order.}  In other words, optimal test functions are approximated element-by-element using polynomials whose order is $\Delta p$ more than the local order of approximation.
-Under this scheme, the error in approximation of test functions is tied to the effectiveness of the $p$-method.
-Unfortunately, for problems with boundary layers --- including the approximation of test functions under the quasi-optimal test norm --- the $p$-method performs very poorly.
-As a result of this poor approximation, the numerical solutions of the convection-dominated diffusion equation under DPG using the quasi-optimal test norm tend to be of poor quality, and do not exhibit all the proven properties of DPG (for example, the energy error may increase after mesh refinement, even though, by virtue of DPG delivering a best approximation, the energy error for a coarse mesh must be greater than or equal to the energy error for a finer mesh).
-We conclude that the error in approximation of optimal test functions using simple polynomial enrichment pollutes and ruins the performance of DPG under the quasi-optimal test norm.
-
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.25]{figs/opt.png}
-\caption{$v$ and $\tau$ components of the 1D optimal test functions corresponding to the flux $\widehat{f}_n$ on the right-hand side of a unit element for $\epsilon = 0.01$.
-The solution has been obtained using automatic $hp$-adaptivity driven by the test norm with the error tolerance set at 1\%.}
-\label{fig:optTestBoundary}
-\end{figure}
-
-The difficulty in using the quasi-optimal test norm for convection-diffusion is perplexing at first, considering that the quasi-optimal norm has yielded excellent results for the Helmholtz equation and other wave propagation problems.
-The difference between the two problems lies in the fact that, for wave propagation problems, the mesh size tends to be on the order of the wavenumber $k$ --- the singular perturbation parameter.
-Transforming the variational problem using the quasi-optimal test norm for wave propagation yields smooth optimal test functions that are approximated much more accurately using only polynomials over the reference element.
-Typically, the wavenumbers $k$ of physical interest are $O(100)$ with respect to a unit domain.
-The corresponding finite element problems will typically be solved on meshes containing approximately $O\!\left(k^d\right)$ elements in $\mathbb{R}^d$, well within the range of a computationally tractable simulation.
-However, for convection diffusion problems, the relevant range of $\epsilon$ for physical problems can be as small as $1e-7$.
-Solving on under-resolved meshes is thus unavoidable, and the approximability of optimal test functions must be addressed in order to take advantage of the properties of DPG.
-
-Resolving such boundary layers present in test functions under the quasi-optimal test norm has been investigated numerically using specially designed (Shishkin) subgrid meshes by Niemi, Collier, and Calo in
-\cite{DBLP:journals/procedia/NiemiCC11}.
-However, even with Shishkin meshes, the approximation of optimal test functions under the quasi-optimal norm is far more expensive and complex to implement than approximation of test functions using a simple $p$-enriched space for $V$.
-We therefore aim instead to design a test norm that does not induce boundary layers, but still delivers good approximation results over a range of $\epsilon$.
-
-\section{Analysis of a DPG test norm}
-\seclab{sec:testNormSec}
-We are interested in computing DPG optimal test functions for the convection-diffusion equation with very small values of $\epsilon$; due to the difficulty of approximating optimal test functions, we conclude that the use of the quasi-optimal test norm is infeasible towards this goal.
-
-However, if we naively choose a test norm that does not generate boundary layers, the performance of DPG may be adversely affected.
-For example, if $\|\left(v,\tau\right)\|_V^2 = \|v\|_{H^1(\Omega_h)}^2 + \|\tau\|^2_{H({\rm div},\Omega_h)}$, the $H^1(\Omega_h)\times H({\rm div},\Omega_h)$ norm, then the corresponding test functions will be smooth and free of boundary layers; however, the performance of DPG will provide approximations which worsen in quality as $\epsilon$ becomes very small \cite{DPG3,DPGrobustness}.
-
-Our goal is to construct a test norm that compromises between performance of DPG and approximability of test functions.
-This test norm should not produce boundary layers in the optimal test functions, but still induce an energy norm that yields good approximation properties for small $\epsilon$.
-We note that, even under the quasi-optimal norm, the norms on the flux and trace variables will likely depend on $\epsilon$.
-Thus, we aim to construct a test norm for which the DPG method will be robust in $\epsilon$ with respect to the \emph{field variables}.
-
-For now, we discuss the steps necessary to analyze the performance of DPG with respect to a non-canonical test norm.
-We require a priori that the test norm has separable $\tau$ and $v$ components --- in other words, that there are no terms in the test norm that couple $\tau$ and $v$ together.
-Problem \eqnref{optvVar} then decouples, such that the components of the vector-valued test function $\left(v,\tau\right)$ can be solved for independently of each other.
-The decoupled variational problems are no longer systems but scalar equations in $\tau$ and $v$, for which it is easier to conclude whether or not there are boundary layers in the solutions (the avoidance of boundary layers in the test norm will be discussed in more detail in Section~\ref{sec:num_exp}, which describes our numerical experiments).
-\textbf{This will ensure that the resulting DPG method does not suffer from approximation errors in the optimal test functions}.
-
-We begin with the following test norm:
-\[
-\left\|\left(v,\tau\right)\right\|^2_V \coloneqq \|v\|_{L^2}^2 + \epsilon\|\grad v\|_{L^2}^2 + \|\beta \cdot \grad v\|_{L^2}^2  + \frac{1}{\epsilon}\|\tau\|_{L^2}^2 + \|\div \tau\|_{L^2}^2.
-\]
-The use of this norm is problematic for practical computations; we will discuss the reasons why and present a modification of it in Section~\secref{sec:meshDep}.
-
-We can see how this norm will differ from the canonical $H^1(\Omega_h)\times H({\rm div},\Omega_h)$ norm: the clearest difference is the fact that the gradient in the streamline direction is $O(1)$, while the full gradient is $O(\sqrt{\epsilon})$, so that, in our test norm, the streamline gradient of $v$ will be emphasized over the full gradient of $v$ for small $\epsilon$.
-
-The choice of this test norm is implied by the mathematics of the adjoint problem.
-Roughly speaking, necessary conditions for the performance of DPG to not degenerate as $\epsilon \rightarrow 0$ are derived through analysis of specific test functions.
-For example, if $u$ is the first $L^2$ component of the solution to the variational problem defined in Section~\secref{sec:modelSec}, by choosing $(v,\tau) \in H^1(\Omega) \times H({\rm div},\Omega)$ such that
+Let $\boldsymbol U$ denote the trial variables $\{u,\sigma, \uh, \fnh\}$. For robustness in $u$, we can choose for $\LRp{v,\tau}$ the conforming solution to the adjoint equation such that 
 \begin{align*}
 \div \tau - \beta \cdot \grad v &= u \\
-\frac{1}{\epsilon} \tau - \grad v &= 0,
+\frac{1}{\epsilon} \tau - \grad v &= 0. 
 \end{align*}
-we have
+By doing so, we recover the $L^2$ norm of $u$ from the bilinear form, such that
 \[
- \nor{u}_{L^2}^2 = b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(v,\tau\right)\right) \leq \nor{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)}_{U,V} \nor{\left(v,\tau\right)}_V,
+\nor{u}^2_{L^2(\Omega)} = b\LRp{{\boldsymbol U},\LRp{v,\tau}} = \frac{b\LRp{{\boldsymbol U},\LRp{v,\tau}}}{\nor{\LRp{v,\tau}}_V} \nor{\LRp{v,\tau}}_V \leq \nor{\boldsymbol U}_E \nor{\LRp{v,\tau}}_V
 \]
-and we recover the $L^2$ norm of $u$ from the bilinear form.
+Let $\lesssim$ denote a robust bound - if $ \nor{\LRp{v,\tau}}_V \lesssim \|u\|_{L^2(\Omega)}$, then we have that
+\[
+\nor{u}_{L^2(\Omega)} \lesssim \nor{\boldsymbol U}_E
+\]
+In other words, a necessary condition for a robust method is that the test norm measures solutions to the adjoint equations in a robust manner.
 
-Let $\|a\| \lesssim \|b\|$ denote an $\epsilon$-independent bound; specifically, that $\|a\| \leq C\|b\|$ for a constant $C$ independent of $\epsilon$.
-Consequently, if for any $u\in L^2(\Oh)$, $\nor{\left(v,\tau\right)}_V\lesssim \nor{u}_{L^2}$, then dividing through by $\nor{u}_{L^2}$ gives the bound
-\[
- \nor{u}_{L^2} \lesssim \nor{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)}_E.
-\]
-In other words, there is the guarantee that the $L^2$ error in $u$ is at least robustly bounded from above by the energy error.
-Then, if the energy error (which DPG minimizes) approaches zero, the $L^2$ error in $u$ will as well.
-The same exercise can be repeated for the stress $\sigma$, as well as the flux variables $\widehat{u}$, $\widehat{f}_n$.
+\textcolor{red}{Can we conclude that the same thing needs to happen for approximate test functions?}
 
-This methodology gives constraints on the quantities found in the test norm; any quantity present in $\nor{\left(v,\tau\right)}_V$ must be shown to be bounded from above independently of $\epsilon$ by the load of the adjoint problem.
-However, showing this simply amounts to showing \textit{standard energy estimates} for $H^1$ and $H({\rm div})$-conforming finite elements.
-A more detailed discussion on the reasoning behind the construction of test norms can be found in \cite{DPGrobustness}.
-
-The second step will be to \textbf{show the equivalence of the energy norm to explicit norms on $U$}.
-Since we do not generally have a closed form expression for the DPG energy norm, we seek to understand the behavior of DPG by finding a norm on $U$ to which the DPG energy norm is equivalent.
-Since $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U$ is a group variable from a tensor product space, we construct norms on $U$ through the combination of norms on $u$, $\sigma$, $\widehat{u}$, and $\widehat{f}_n$.
-Specifically, we use the norm on $U$
-\begin{equation}
-\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U}^2 \coloneqq \|u\|^2 + \|\sigma\|^2 + \left\|\widehat{u}\right\|^2 + \left\|\widehat{f}_n\right\|^2.
-\end{equation}
-For equivalence between norms, two constants are specified.
-However, since this norm on $U$ is a norm on four separate variables, we can specify not just two but eight equivalence constants.\footnote{Sharper estimates are attainable if these constants are allowed to vary over the mesh $\Oh$.
-See Section~\ref{sec:main_bounds} for a discussion.} In order to simplify analysis, we phrase this equivalence statement in an alternative form.
-
-Let $\nor{\cdot}_E \coloneqq \nor{\cdot}_{U,V}$, the energy norm induced by the test norm described above. We seek the bound of $\nor{\cdot}_E$ from above and below:
-\[
-\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2},
-\]
-where both $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ are defined as scaled combinations of the norms on $u, \sigma, \widehat{u}$, and $\widehat{f}_n$
-\begin{equation}
-\eqnlab{uNorms}
-\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,i}^2 \coloneqq \left(C_u^i\|u\|\right)^2 + \left(C_\sigma^i\|\sigma\|\right)^2 + \left(C_{\widehat{u}}^i\|\widehat{u}\|\right)^2 + \left(C_{\widehat{f}_n}^i\|\widehat{f}_n\|\right)^2,\quad i = 1,2
-\end{equation}
-Our goal is to explicitly derive the equivalence constants 
-%$C^1_u,\ldots, C^1_{\widehat{f}_n}$ and $C^2_u,\ldots, C^2_{\widehat{f}_n}$ 
-that define the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ respectively, taking into account any dependency on $\epsilon$.
-To do so, we need a relation between trial norms on $U$ and test norms on $V$.
-
-Recall from Section~\secref{energyPair} that every test norm induces a corresponding trial norm, and vice versa.
-Let $\|\cdot\|_{U,1} \simeq \|\cdot\|_{U,2}$ mean that the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ are equivalent, with equivalence constants independent of $\epsilon$.
-By equivalence of finite dimensional norms and the discussion in Section~\secref{energyPair} on the duality between test norms/energy norms, the norms \eqnref{uNorms} on $U$ induce the equivalent test norms on $\left(v,\tau\right) \in H^1(\Oh)\times H({\rm div},\Oh)$
+If we assume that an underresolved test function behaves similarly to a test function under a larger viscosity, we expect that the term $\nor{\div \tau - \beta \cdot \grad v}_{L^2}$ still remains relatively bounded uniformly in $\epsilon$.
+However, the term $\nor{\frac{1}{\epsilon}\tau - \grad v}_{L^2}$ does not --- analytical calculations in 1D show that this term grows with the Peclet number in the element at the inflow, where the adjoint solution develops a boundary layer.
+As the boundedness of this term determines the robustness of $\sigma$, our energy norm is
 \begin{align*}
-\left\|\left(v,\tau\right)\right\|_{V,{U,i}} &\simeq \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(v,\tau\right)\right)}{C_u^i\|u\| + C_\sigma^i\|\sigma\| + C_{\widehat{u}}^i\|\widehat{u}\|+ C_{\widehat{f}_n}^i\|\widehat{f}_n\|}\\
-&= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \jump{\tau_n}, \widehat{u} \rangle_{\Gamma_-\cup \Gh^0} + \langle \widehat{f}_n, \jump{v} \rangle_{\Gamma_+ \cup \Gh^0}}{C_u^i\|u\| + C_\sigma^i\|\sigma\| + C_{\widehat{u}}^i\|\widehat{u}\|+ C_{\widehat{f}_n}^i\|\widehat{f}_n\|}\\
-& \simeq \frac{1}{C_u^i}\|g\| + \frac{1}{C_\sigma^i}\|f\| + \frac{1}{C_{\widehat{u}}^i}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle \jump{\tau\cdot n}, \widehat{u}\rangle}{\|\widehat{u}\|} +\frac{1}{C_{\widehat{f}_n}^i}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, \jump{v}\rangle}{\|\widehat{f}_n\|},
+\nor{\boldsymbol U}_E &\coloneqq \sup_{\LRp{v,\tau}}\LRp{\frac{\LRp{u,\Grad_h \cdot \tau - \beta \cdot \Grad_h v}_{\Omega}}{\nor{\LRp{v,\tau}}_V} + \frac{\LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad_h v}_{\Omega}}{\nor{\LRp{v,\tau}}_V} + \frac{\LRa{\fnh,v}_{\Gamma} - \LRa{\uh,\tau_n}_{\Gamma}}{\nor{\LRp{v,\tau}}_V}} \\
+&\approx \nor{u}_{L^2} + F(\text{Pe})\nor{\sigma}_{L^2} + \nor{\LRp{\uh,\fnh}}
 \end{align*}
-where $f$ and $g$ are defined element-wise over $\Oh$ as 
-\begin{align*}
-g &\coloneqq \div \tau - \beta \cdot \grad v\\
-f &\coloneqq \epsilon^{-1}\tau + \grad v.
-\end{align*}
-By definition of the norms on the quantities defined on the skeleton $\Gh$, this gives the characterization of the induced test norm 
-\[
-\|\left(v,\tau\right)\|_{V,{U,i}} \simeq \frac{1}{C_u^i}\|g\| + \frac{1}{C_\sigma^i}\|f\| + \frac{1}{C_{\widehat{u}}^i}\|\jump{\tau\cdot n}\| + \frac{1}{C_{\widehat{f}_n}^i}\|\jump{v}\|, \quad i = 1,2.
-\]
-We can now use this relation to compare different norms on $U$ by comparing their induced norms on $V$ (recall that showing a robust inequality between two norms on $U$ is equivalent to showing the robust \textit{reverse} inequality in the induced norms on $V$).
-Namely, we can show the bound of $\nor{\cdot}_{U,1} \lesssim \nor{\cdot}_E$ by showing the bound $\nor{\left(v,\tau\right)}_{V,U,1} \gtrsim \nor{\left(v,\tau\right)}_{V}$, and likewise for $\nor{\cdot}_E \lesssim \nor{\cdot}_{U,2}$.
-
-Since the techniques used to show such bounds are more involved, we break the procedure up into two steps:
-\begin{enumerate}
-\item{}Decompose test functions $(v,\tau)$ into three separate, more easily analyzable components (Section~\ref{sec:strategy2}).
-\item{}Derive adjoint estimates (Section~\ref{sec:strategy3}).
-\end{enumerate}
-
-\subsection{Decomposition into analyzable components}
-\label{sec:strategy2}
-
-Having reduced the problem of comparing norms on $U$ to the comparison of norms on $V$, we break the analysis of $\left(v,\tau\right) \in V$ into the analysis of three subproblems.
-Define the decomposition
-\[
-\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right),
-\]
-where $\left(v_1,\tau_1\right)$ satisfies 
-\begin{align*}
-\epsilon^{-1}\tau_1 + \grad v_1 &= 0 ,\\
-\div \tau_1 - \beta\cdot \grad v_1 &=  \div \tau - \beta\cdot \grad v = g, 
-\end{align*} 
-and $\left(v_2,\tau_2\right)$ satisfies
-\begin{align*}
-\epsilon^{-1}\tau_2 + \grad v_2 &= \epsilon^{-1}\tau + \grad v = f, \\
-\div \tau_2 - \beta\cdot \grad v_2 &= 0.
-\end{align*}
-Both $(v_1,\tau_1), (v_2,\tau_2) \in H({\rm div}; \Omega)\times H^1(\Omega)$ are understood to satisfy these relations in a conforming sense over the domain $\Omega$; however, the divergence of $\tau$ and gradient of $v$ on the right hand side are still understood to be taken in an element-wise fashion.
-
-We will additionally require both $\left(v_1,\tau_1\right), \left(v_2,\tau_2\right)$ to satisfy the adjoint homogeneous boundary conditions
-\begin{align}
-\tau_i\cdot n &= 0, \quad \text{on }\Gamma_- \label{bc_1}\\
-v_i &= 0, \quad \text{on } \Gamma_+ \label{bc_2}
-\end{align}
-for $i = 1, 2$.
-The selection of $H({\rm div}, \Omega)\times H^1(\Omega)$ conforming test functions satisfying the specific boundary conditions above removes the contribution of the jump terms over the skeleton $\Gh$ in the bilinear form, allowing us to analyze field terms in the induced test norms separately from  the boundary/jump terms.
-
-Finally, by construction, $\left(v_0,\tau_0\right) \in H^1(\Oh) \times H({\rm div},\Oh)$ must satisfy 
-\begin{align*}
-\epsilon^{-1}\tau_0 + \grad v_0 &= 0\\
-\div \tau_0 - \beta\cdot \grad v_0 &= 0
-\end{align*}
-with jumps
-\begin{align*}
-\jump{v_0} &= \jump{v}, \quad \text{on }\Gh^0\\
-\jump{\tau_0 \cdot n} &= \jump{\tau \cdot n}, \quad \text{on }\Gh^0.
-\end{align*}
-and boundary conditions
-\begin{align*}
-v_0 &= v, \quad \text{on } \Gamma_+ \\
-\tau_0 \cdot n &= \tau \cdot n, \quad \text{on } \Gamma_-\cup \Gamma_0. 
-\end{align*}
-Notice that the evaluation the bilinear form $b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(v,\tau\right)\right)$ with each specific test functions returns only one part of the bilinear form.
-Furthermore, by choosing the proper loads $g = u$ and $f=\sigma$, we can recover from the bilinear form the norms of $u$ and $\sigma$ (as described in Section~\secref{sec:testNormSec}), as well as the norms on $\widehat{u}$, and $\widehat{f}_n$.\footnote{To recover the norms on $\widehat{u}$, and $\widehat{f}_n$, the loads $f$, and $g$ must be zero, and the jumps of the test function $(v,\tau)$ must be chosen specifically.}
-
-We have now decomposed an arbitrary test function $\left(\tau,v\right)$ into a discontinuous contribution and two continuous contributions.
-Recall that our goal is to show the robust bound from above and below of the DPG energy norm by $\|\cdot \|_{U,1}$ and $\|\cdot \|_{U,2}$:
-\[
-\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}.
-\]
-
-Under the duality of trial and test norms and the decomposition of test functions $\left(\tau,v\right) \in V$ into $\left(\tau_0,v_0\right), \left(\tau_1,v_1\right)$, and $\left(\tau_2,v_2\right)$, the above bound is equivalent to bounding each component
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,U,1} &\gtrsim \sum_{i=0}^2\|\left(v_{i},\tau_{i}\right)\|_V \gtrsim \|\left(v,\tau\right)\|_{V,U,2}.
-%\|\left(v,\tau\right)\|_{V,1} &\lesssim \|\left(v_{1},\tau_{1}\right)\|_V \lesssim \|\left(v,\tau\right)\|_{V,2}\\
-%\|\left(v,\tau\right)\|_{V,1} &\lesssim \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|\left(v,\tau\right)\|_{V,2}
-\end{align*}
-Bounding $\|\left(v_0,\tau_0\right)\|$ requires the use of techniques first developed in \cite{analysisDPG} and adapted to convection-diffusion in \cite{analysisDPG} and \cite{DPGrobustness}.
-However, since $\left(\tau,v\right) \in H({\rm div}, \Omega)\times H^1(\Omega)$, the bound from above of test functions $\|\left(v_{1},\tau_{1}\right)\|_V$ and $\|\left(v_{2},\tau_{2}\right)\|_V$ is reduced to proving classical error estimates for the adjoint equations
-\begin{align*}
-\epsilon^{-1}\tau_1 + \grad {v_1} &= 0 \\
-\div {\tau_1} - \beta\cdot \grad {v_1} &=  g, \\
-\left.\tau_1\cdot n\right|_{\Gamma_-} &= 0, \\
-\left.v_1\right|_{\Gamma_+} &= 0.
-\end{align*} 
-and 
-\begin{align*}
-\epsilon^{-1}\tau_2 + \grad {v_2} &= f \\
-\div {\tau_2} - \beta\cdot \grad {v_2} &= 0, \\
-\left.\tau_2\cdot n\right|_{\Gamma_-} &= 0, \\
-\left.v_2\right|_{\Gamma_+} &= 0.
-\end{align*} 
-More generally, we can analyze the adjoint equations
-\begin{align}
-\epsilon^{-1}\tau + \grad {v} &= f \label{adjoint1}\\
-\div {\tau} - \beta\cdot \grad {v} &= g, \label{adjoint2}
-\end{align}
-for arbitrary data $f, g\in L^2({\Omega})$ and boundary conditions $\jump{\tau\cdot n}_{\Gamma_-} = 0$ and $\jump{v}_{\Gamma_+} = 0$.
-In other words, we want to analyze the stability properties of the adjoint equations by deriving bounds of the form $\|\left(v_1,\tau_1\right)\|_V\lesssim \|g\|_{L^2}$ and $\|\left(v_2,\tau_2\right)\|_V \lesssim \|f\|_{L^2}$.
-
-%An alternate interpretation of the above decomposition is that each component $(v_i,\tau_i)$ of the decomposition corresponds to a term in the bilinear form.
-For example, .
-If we evaluating our bilinear form with $(v,\tau) = (v_1,\tau_1)$ delivers
-%\[
-%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-%\left( v_1, \tau_1 \right)\right) = (u,g)_{L^2} 
-%\]
-%By choosing $g = u$,
-
-\subsection{Adjoint estimates}
-\label{sec:strategy3}
-
-The final step to estimating the induced norm on $U$ by a selected localizable test norm on $V$ is to derive adjoint stability estimates on $\tau$ and $v$ in terms of localizable normed quantities.
-We will construct complete test norms on $V$ through combinations of these normed quantities.%, where each normed quantity on $\tau$ or $v$ will correspond roughly to $\|u\|_{L^2}$, $\|\sigma\|_{L^2}$, $\|\widehat{u}\|$, or $\|\widehat{f}_n\|$.
-
-We introduce first the bounds derived; the proofs will be given later.
-For this analysis, it will be necessary to assume certain technical conditions on $\beta$.
-For each proof, we require $\beta \in C^2(\bar{\Omega})$ and $\beta, \div \beta = O(1)$.
-Additionally, we will assume that some or all of the following assumptions hold:
-\begin{align}
-&\curl \beta = 0, \quad 0<C \leq \left | \beta\right |^2 + \frac{1}{2}\div \beta, \quad C = O(1) \label{a_req},\\
-&\grad \beta + \grad \beta ^T - \div \beta I = O(1) \label{b_req},\\
-&\div \beta = 0 \label{c_req}.
-\end{align}
-Under proper assumptions on $\beta$, we have the robust bounds, which are proved in the Appendix. 
-\begin{itemize}
-\item \textbf{Lemma \ref{lemma_stream}}: \textit{For $\beta$ satisfying \eqref{a_req} and \eqref{b_req}, %$f=0$ 
-and $v_1 \in H^1(\Omega)$, satisfying equations \eqref{adjoint1} and \eqref{adjoint2} with $f=0$, and with boundary conditions \eqref{bc_1} and \eqref{bc_2}},
-\begin{align*}
-\|\beta \cdot \grad v_1 \| &\lesssim \| g\|.
-\end{align*}
-Similarly, from $\div \tau_1 - \beta\cdot \grad v_1 = g$, we get $\|\div \tau_1\| \lesssim \|g\|$ as well.  
-\item \textbf{Lemma \ref{lemma_grad}}: \textit{For $\beta$ satisfying \eqref{a_req}, and $v \in H^1(\Omega)$ satisfying equations \eqref{adjoint1} and \eqref{adjoint2} and boundary conditions \eqref{bc_1} and \eqref{bc_2}, and for sufficiently small $\epsilon$},
-\[
-\epsilon \|\grad v\|^2 + \|v\|^2 \lesssim \|g\|^2 + \epsilon \|f\|^2.
-\]
-We can characterize both $v_1$ and $v_2$ in the above decompositions using this theorem by setting either $f=0$ or $g=0$. 
-%\begin{align*}
-%\epsilon \|\grad v_1\|^2 + \|v_1\|^2 &\lesssim \|g\|^2\\
-%\epsilon \|\grad v_2\|^2 + \|v_2\|^2 &\lesssim \epsilon \| f\|^2.
-%\end{align*}
-%By the triangle inequality, this implies for any $w$ of the form $w=v_1+v_2$
-%\begin{align*}
-%\epsilon \|\grad w\|^2 + \|w\|^2 &\lesssim \|g\|^2 + \epsilon \| f\|^2
-%\end{align*}
-\item \textbf{Lemma \ref{lemma_boundary}}: \textit{For $\beta$ satisfying \eqref{a_req}, \eqref{c_req}, and solutions $v_0 \in H^1(\Oh)$ and $\tau_0 \in H({\rm div},\Oh)$ of equations \eqref{adjoint1} and \eqref{adjoint2} with $f=g=0$,}
-\begin{align*}
-\|\grad v_0\| = \frac{1}{\epsilon}\|\tau_0\| &\lesssim \frac{1}{\epsilon} \| \jump{\tau_0\cdot n}\|_{\Gh \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| \jump{v_0}\|_{\Gh^0 \cup \Gamma_+}.
-\end{align*}
-\end{itemize}
-We are interested in showing the equivalence of the DPG energy norm with norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$, respectively.
-We will show this by bounding $\|\cdot \|_V$ from below by $\|\cdot\|_{V,U,1}$ and from above by $\|\cdot\|_{V,U,2}$ (the induced test norms for $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$, respectively).
-
-%We will use Lemmas \ref{lemma_stream}, \ref{lemma_grad}, and \ref{lemma_boundary} to prove such bounds on our yet-unspecified test norm $\|(\tau,v)\|_V$.
-
-%Together, these estimates will be sufficient to construct a complete norm on $V$ and demonstrate bounds on induced test norms for different scalings of norms on $U$.  
-%\tanbui{}{again, using the same notation
-%  $(v, \tau)$ for all three problems is not a good idea. Why don't we
-%  use $(v_i,\tau_i)$ introduced above? Things are much clearer this
-%  way?}
-\subsection{A mesh-dependent test norm}
-\seclab{sec:meshDep}
-Ideally, we would be interested in the use of the test norm 
-\[
-\|\left(v,\tau\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2
-\]
-for practical computations.
-However, the presence of the term $\|v\|$ together with $\sqrt{\epsilon}\|\grad v\|$ (and similarly $\|\div \tau\|$ and $\frac{1}{\sqrt{\epsilon}}\|\tau\|$ terms) induces boundary layers in the optimal test functions for under-resolved meshes.
-We can see this by recovering the strong form of the variational problem defining test functions.
-We first note that the variational problems for the $v$ and $\tau$ components of optimal test functions decouple from each other under this test norm.
-Then, examining the variational problem for the $v$ component only of an optimal test function, and assuming $\div \beta = 0$ for illustrative purposes, we have
-\begin{align*}
-\left(\left(v,0\right),\left(\delta v,\delta\tau\right)\right)_{V} &= (v,\delta v) + \epsilon \left(\grad v,\grad \delta v\right) + \left(\beta \cdot \grad v, \beta \cdot \grad \delta v\right)\\
-&= \left(v - \epsilon \Delta v - \div \left(\left(\beta \otimes \beta\right) \grad v\right), \delta v\right)_{L^2} + \langle \epsilon \grad v\cdot n, \delta v\rangle + \langle n\cdot \left(\beta\otimes\beta\right) \grad v , \delta v\rangle.
-\end{align*}
-After integration by parts, we recover the strong form of the operator $L$ inducing such a variational problem 
-\[
-Lv \coloneqq v - \epsilon \Delta v - \div \left(\left(\beta \otimes \beta\right) \grad v\right),
-\]
-where we neglect the resulting boundary terms from integration by parts for now.
-
-The streamline direction $\beta$ induces an anisotropic diffusion, while the $\sqrt{\epsilon}\|\grad v\|_{L^2}$ term induces a small isotropic diffusion contribution everywhere.
-Since any vector in the cross-stream direction is in the null space of the anisotropic diffusion tensor, in the cross-stream directions, the optimal test function is governed only by the cross-stream part of the operator $L$
-\[
-L_{\rm \beta^\perp} \coloneqq v - \epsilon \Delta v,
-\]
-and can develop boundary layers in those directions.
-The presence of boundary layers has been verified through numerical computation as well; using an $H^1$-conforming finite element code with $hp$-adaptivity \cite{demkowicz2006computing}, the solution to the variational problem defining the optimal test function under the above test norm was computed.
-Figure~\ref{fig:boundaryTest} shows the result of such a computation for the $v$ component of an optimal test function under the above test norm.
-\begin{figure}[!h]
-\centering
-\subfigure{\includegraphics[scale=.22]{figs/mesh1.png}}
-\subfigure{\includegraphics[scale=.22]{figs/sol1.png}}
-\caption{The $v$ component of the optimal test function corresponding to flux $\widehat{u} = x(1-x)$ on the bottom side of a unit element for $\epsilon = 0.01$.
-The corresponding $hp$-mesh used to compute the solution is displayed to the left.}
-\label{fig:boundaryTest}
-\end{figure}
-To avoid boundary layers in the optimal test functions, we follow \cite{DPGrobustness} in scaling the $L^2$ contributions of $v$ by $C_v(K)$, such that, when transformed to the reference element, both $C_v(K)\|v\|^2$ and $\epsilon\|\grad v\|^2$ are of the same magnitude.
-Similarly, we scale the $L^2$ contributions of $\tau$ by $C_\tau(K)$ such that $\frac{C_\tau(K)}{\epsilon} \|\tau\|^2$ and $\|\div \tau\|^2$ are of the same magnitude as well.
-For this paper, we consider only isotropic refinements on quadrilateral elements in 2D.
-
-Our test norm, as defined over a single element $K$, is now
-\[
-\|\left(v,\tau\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
-\]
-This modified test norm avoids boundary layers in the locally computed optimal test functions, but for adaptive meshes, provides additional stability in areas of heavy refinement, where the best approximation error tends to be large and stronger robustness is most necessary.
-This leads to a test norm which produces easily approximable optimal test functions, but still provides \textit{asymptotically} the strongest test norm and tightest robustness results in the areas of highest error.
-
-\subsection{Equivalence of energy norm with $\nor{\cdot}_U$}
-%\subsection{Relations between trial and test constants}
-\label{sec:main_bounds}
-
-The main theoretical result of this paper can now be given:
-\begin{lemma}
-Under the mesh-dependent test norm
-\[
-\|\left(v,\tau\right)\|_{V,\Oh}^2 = \|C_vv\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \|C_\tau\tau\|^2,
-\]
-where $C_v, C_{\tau}\in L^2(\Omega)$ are defined elementwise through
-\begin{align*}
-\left.C_v\right |_K &= \min\left\{\sqrt{\frac{\epsilon}{|K|}},1\right\}\\
-\left.C_{\tau}\right |_K &= \min\left\{\frac{1}{\sqrt{\epsilon}},\frac{1}{\sqrt{|K|}}\right\}.
-\end{align*}
-If $\beta$ satisfies \eqref{a_req}, \eqref{b_req}, and \eqref{c_req}, the DPG energy norm $\nor{\cdot}_E$ satisfies the following equivalence relations
-\begin{align*}
-\nor{u}_{L^2} + \nor{\sigma}_{L^2} + \epsilon\nor{\widehat{u}} + \sqrt{\epsilon}\nor{\widehat{f}_n} 
-&\lesssim \nor{\left(u,\sigma, \widehat{u},\widehat{f}_n\right)}_E \\ 
-%\nor{\left(u,\sigma, \widehat{u},\widehat{f}_n\right)}_E &\lesssim \nor{u}_{L^2} + \nor{C_\sigma \sigma}_{L^2} + \frac{1}{\sqrt{\epsilon}} \left(\nor{\widehat{u}} + \nor{\widehat{f}_n}\right),
-\nor{\left(u,\sigma, \widehat{u},\widehat{f}_n\right)}_E &\lesssim \nor{u}_{L^2} + \nor{\frac{1}{\epsilon C_\tau} \sigma}_{L^2} + \frac{1}{\sqrt{\epsilon}} \left(\nor{\widehat{u}} + \nor{\widehat{f}_n}\right).
-\end{align*}
-%where $C_\sigma \in L^2(\Omega)$ is defined elementwise through $\left.C_\sigma\right|_K  = \max\left\{ \frac{1}{\sqrt{\epsilon}} , \frac{\sqrt{|K|}}{\epsilon} \right\}$.
-\end{lemma}
-
-\begin{proof}
-We begin by proving the bound from below.
-As a consequence of the duality of norms discussed in Section~\secref{energyPair}, we know that the norm $\left\| u \right\|_{U,1}$ is induced by a specific test norm $\| v  \|_{V,U,1}$.
-To bound $\|\cdot\|_E$ robustly from above or below by a given norm $\left\| u \right\|_{U,2}$ on $U$ now only requires the robust bound in the opposite direction of $\| v \|_{V,U,1}$ by $\|v\|_{V,U,2}$.
-
-For $f$ and $g$ defined in \eqref{adjoint1} and \eqref{adjoint2},
-\begin{align*}
-f &= \epsilon^{-1}\tau + \grad v  \\
-g &=\div \tau - \beta\cdot \grad v,
-\end{align*} 
-we can characterize the test norm for 
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,1}^2 = \|u\|^2 + \|\sigma\|^2 + \epsilon\|\widehat{u}\|^2+ \sqrt{\epsilon}\|\widehat{u}\|^2
-\]
-through the equivalence relation
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,U,1} &\simeq \sup_{u,\sigma,\widehat{u},\widehat{f}_n}\frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\|u\| + \|\sigma\| + \epsilon\|\widehat{u}\|+ \sqrt{\epsilon}\|\widehat{u}\|}\\
-& \simeq \|g\| + \|f\| + \frac{1}{\epsilon}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle \jump{\tau\cdot n}, \widehat{u}\rangle}{\|\widehat{u}\|} + \frac{1}{\sqrt{\epsilon}}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, \jump{v}\rangle}{\|\widehat{f}\|},
-\end{align*}
-which, by definition of the boundary norms, is 
-\[
-\|\left(v,\tau\right)\|_{V,U,1} \simeq \|g\| + \|f\| + \frac{1}{\epsilon}\|\jump{\tau\cdot n}\| + \frac{1}{\sqrt{\epsilon}}\|\jump{v}\|.
-\]
-We wish to show the bound
-\[
-\nor{\left(v,\tau\right)}_{V,\Oh} \lesssim \|g\| + \|f\| + \frac{1}{\epsilon}\|\jump{\tau\cdot n}\| + \frac{1}{\sqrt{\epsilon}}\|\jump{v}\|.
-\]
-By noting that both 
-\begin{align*}
-\nor{C_vv_0} &\leq \nor{v_0},\\
-\nor{C_\tau\tau_0} &\leq \frac{1}{\sqrt{\epsilon}}\nor{\tau_0},
-\end{align*}
-we have that $\nor{\left(v,\tau\right)}_{V,\Oh} \leq \nor{\left(v,\tau\right)}_{V}$, so it suffices to prove the bound for the mesh-independent test norm 
-\[
-\|\left(v,\tau\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2.
-\]
-
-We will bound $\|\left(v,\tau\right)\|_V$ for all $\left(v,\tau\right)$ by decomposing $\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right)$ as described in Section~\ref{sec:strategy2}.
-
-By the triangle inequality, robustly bounding $\|\left(v,\tau\right)\|_V$ from above reduces to robustly bounding each component 
-\[
-\|\left(v_{0},\tau_{0}\right)\|_V, \|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|g\| + \|f\| + \frac{1}{\epsilon}\|\jump{\tau\cdot n}\| + \frac{1}{\sqrt{\epsilon}}\|\jump{v}\|.
-\]
-
-%Roughly speaking, Lemma \ref{lemma_grad} concerns the robust control of $u$ by the energy error; Lemmas \ref{lemma_stream} and \ref{lemma_boundary} concern the robust control of field variable $\sigma$ and flux/trace variables, respectively.
-
-\begin{itemize}
-\item \textbf{Bound on $\|\left(v_{0},\tau_{0}\right)\|_V$}
-
-Lemma \ref{lemma_boundary} gives control over $\sqrt{\epsilon}\|\grad v_0\| + \frac{1}{\epsilon}\|\tau_0\|$ through
-\[
-\|\grad v_0\| = \frac{1}{\epsilon}\|\tau_0\| \lesssim \frac{1}{\epsilon} \nor{\jump{\tau_0\cdot n}}_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \nor{\jump{v_0}}_{\Gamma_h^0 \cup \Gamma_+} = \frac{1}{\epsilon} \nor{ \jump{\tau\cdot n}}_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \nor{ \jump{v}}_{\Gamma_h^0 \cup \Gamma_+}.
-\]
-Lemma 4.2 of \cite{analysisDPG} gives us the Poincare inequality for discontinuous functions
-\[
-\|v_0\| \lesssim \|\grad v_0\| + \|\jump{v}\|.
-\]
-%Since $f=0$, by Lemma 2, $\|\beta\cdot \grad v_0\|  \lesssim \|g\| = 0$.  
-Since $g = 0$, $\| \div \tau_0\| = \|\beta\cdot \grad v_0\|\lesssim \|\grad v_0\|$, which we now have control over as well.
-
-\item \textbf{Bound on $\|\left(v_{1},\tau_{1}\right)\|_V$}
-
-With $f = 0$, Lemma \ref{lemma_stream} provides the bound
-\[
-\|\beta \cdot \grad v_1 \| \lesssim \| g\|.
-\]
-Noting that $\div \tau_1 = g+\beta\cdot \grad v_1$ gives $\|\div \tau_1 \| \lesssim \|g\|$ as well.  Lemma \ref{lemma_grad} gives
-\[
-\epsilon \|\grad v_1\|^2 + \|v_1\|^2 \lesssim \|g\|^2,
-\]
-and noting that $\epsilon^{-1/2}\tau_1 = \epsilon^{1/2}\grad v_1$ gives $\epsilon\|\grad v_1\|^2 = \epsilon^{-1}\|\tau_1\|^2 \lesssim \|g\|^2$ as well.
-
-\item \textbf{Bound on $\|\left(v_{2},\tau_{2}\right)\|_V$}
-
-Lemma \ref{lemma_grad} provides, for $\epsilon$ sufficiently small, 
-\[
-\epsilon \|\grad v_2\|^2 + \|v_2\|^2 \lesssim  \epsilon \| f\|^2 \leq \|f\|^2.
-\]
-We have $\epsilon^{-1}\tau_2 = f - \grad v_2$, so $\epsilon^{-1} \|\tau_2\| \lesssim \|f\| + \|\grad v_2\|$.
-Lemma~\ref{lemma_grad} implies $\|\grad v_2\|^2  \lesssim  \| f\|^2$, so for $\epsilon \leq 1$, we have $\epsilon^{-1/2}\|\tau_2\| \leq \epsilon^{-1}\|\tau_2\| \lesssim \|f\|$.
-The remaining terms can be bounded by noting that, with $g = 0$, $\|\div \tau_2\| = \|\beta\cdot \grad v_2\| \lesssim \|\grad v_2\| \lesssim \|f\| $.
-\end{itemize}
-
-We have shown the robust bound of the norm $\|\cdot \|_{U,1}$ on $U$ by the energy norm; for a full equivalence statement, we require a bound from above on the energy norm by the norm $\|\cdot \|_{U,2}$ on $U$.
-By the duality of the energy and test norm, this is equivalent to bounding the test norm from below by the test norm induced by $\|\cdot \|_{U,2}$.
-For a norm on $U$ of the form
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,2}^2 = \|u\|^2 + \nor{C_\sigma \sigma}^2 + \frac{1}{{\epsilon}}\left( \|\widehat{u}\|^2 + \|\widehat{f}_n\|^2\right),
-\]
-the induced test norm is equivalent to
-\begin{align*}
-\| \left(\tau,v\right) \|_{V,U,2} &\simeq \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E} \\
-&\simeq \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \jump{\tau_n}, \widehat{u} \rangle + \langle \widehat{f}_n, \jump{v} \rangle
-}{\|u\| + \nor{\left(\epsilon C_\tau\right)^{-1}\sigma} + \frac{1}{\sqrt{\epsilon}}\left(  \|\widehat{u}\| + \|\widehat{f}_n\| \right)} \\
-&\simeq \|g\| + \nor{\epsilon C_\tau f} + {\sqrt{\epsilon}}\left(\sup_{\widehat{u},\widehat{f}_n \neq 0}\frac{\langle \jump{\tau_n}, \widehat{u} \rangle + \langle \widehat{f}_n, \jump{v} \rangle}{\|\widehat{u}\| + \|\widehat{f}_n\|}\right),
-\end{align*}
-where $f$ and $g$ are 
-\begin{align*}
-f &= \frac{1}{\epsilon}\tau + \grad v\\
-g &= \div \tau - \beta \cdot \grad v,
-\end{align*}
-the loads of the adjoint problem defined in \eqref{adjoint1}, \eqref{adjoint2}.
-
-Note that $\epsilon C_\tau \leq \sqrt{\epsilon}$. Then, by the triangle inequality, we have the bounds
-\begin{align*}
-%\sqrt{\epsilon} \|f \| &\leq \epsilon^{-1/2} \| \tau\| + \sqrt{\epsilon} \|\grad v\| \lesssim \|\\
-\|\epsilon C_\tau f \| &\leq C_\tau \nor{ \tau} + \epsilon C_\tau \nor{\grad v} \lesssim \| \left(\tau,v\right)\|_{V,\Oh}\\
-\|g \| &\leq \|\div \tau\| +  \|\beta \cdot \grad v\| \lesssim \| \left(\tau,v\right)\|_{V,\Oh}
-\end{align*}
-We estimate the supremum on the jumps of $\left(\tau,v\right)$ by following \cite{DPGrobustness}; we begin by choosing $\eta \in H({\rm div}; \Omega)$, $w\in H^1(\Omega)$, such that $\left.\left(\eta-\beta w \right)\cdot n\right |_{\Gamma_+} = 0$ and $\left.w\right |_{\Gamma_-\cup\Gamma_0} = 0$, and integrating the boundary pairing by parts to get
-\begin{align*}
-\langle \jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle &= (\tau,\grad w) + (\div \tau, w) + \left(\eta - \beta w, \grad v\right) +  \left(\div \left(\eta - \beta w\right), v\right)\\
-&\lesssim \|C_\tau\tau\| \nor{ \frac{1}{C_\tau}\grad w} + \|\div \tau\| \|w\| \\
-&\left.\hspace{.3cm}\right. + \sqrt{\epsilon}\| \grad v \|\frac{1}{\sqrt{\epsilon}}\|\eta\| +  \|\beta \cdot \grad v\| \| w\|\\
-&\left.\hspace{.3cm}\right. + \|C_vv\|\nor{\frac{1}{C_v}\div \eta} + \| C_vv\| \nor{\frac{1}{C_v}w} \\
-&\left.\hspace{.3cm}\right. + \|C_v v\| \nor{\frac{1}{C_v} \grad w},
-\end{align*}
-where we have used that $\epsilon < 1$, $\div \beta = O(1)$, and that $\|\beta\cdot \grad w\|\lesssim \|\grad w\|$.
-
-Without loss of generality, assume the problem is scaled such that $\max_{K\in\Oh}|K| \leq 1$.
-Then, $\frac{1}{C_\tau^2}\leq \frac{1}{C_v^2} \leq \frac{1}{\epsilon}$, and an application of discrete Cauchy-Schwarz gives us
-\begin{align*}
-\langle \jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle &\lesssim \|\left(\tau,v\right)\|_{V,\Oh}\frac{1}{\sqrt{\epsilon}}\left(\nor{\eta}_{H({\rm div},\Omega)} + \nor{w}_{H^1(\Omega)}\right),\\
-&\lesssim \|\left(\tau,v\right)\|_{V,\Oh}\frac{1}{\sqrt{\epsilon}}\left(\nor{\eta-\beta w}_{H({\rm div},\Omega)} + \nor{w}_{H^1(\Omega)}\right),
-\end{align*}
-since $\|\eta\|_{H({\rm div},\Omega)} = \|\eta - \beta w + \beta w\|_{H({\rm div},\Omega)} \leq \|\eta - \beta w\|_{H({\rm div},\Omega)} + \|\beta w\|_{H({\rm div},\Omega)} \lesssim \|\eta-\beta w\|_{H({\rm div},\Omega)} + \|w\|_{H^1(\Omega)}$.
-Dividing through and taking the supremum gives
-\[
-\sup_{w,\eta \neq 0} \frac{\langle\jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle}{\left(\nor{\eta-\beta w}_{H({\rm div},\Omega)} + \nor{w}_{H^1(\Omega)}\right)} \lesssim \|\left(\tau,v\right)\|_{V,\Oh}\frac{1}{\sqrt{\epsilon}}.
-\]
-To finish the proof, define $\rho \in H^{1/2}(\Gamma_h)$ and $\phi \in H^{-1/2}(\Gamma_h)$ such that $\rho = \left.w\right|_{\Gamma_h}$ and $\phi = \left.(\eta-\beta w)\cdot n\right|_{\Gamma_h}$, and note that, from \cite{analysisDPG}, by the definition of the trace norms on $\jump{\tau\cdot n}$ and $\jump{v}$
-\begin{align*}
-\sup_{\rho,\phi \neq 0} \frac{\langle \jump{\tau\cdot n},\rho\rangle + \langle \jump{v},\phi \rangle}{\|\rho\|_{H^{1/2}(\Gamma_h)}+\|\phi\|_{H^{-1/2}(\Gamma_h)}} &= \sup_{w,\eta \neq 0} \frac{\langle \jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle}{ \|w\|_{H^1(\Omega)}+\|\eta-\beta w\|_{H({\rm div},\Omega)}}.
-\end{align*}
-Together, the bounds on the jump terms and the bounds on $\|g\|$ and $\|f\|$ imply $\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{E} \lesssim \left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,2}$.
-\end{proof}
-
-\subsection{Comparison of boundary conditions}
-
-It is worth addressing the effect of boundary conditions on stability.
-Specifically, a test norm that provides stability for one set of boundary conditions may perform poorly for another set.
-Take, for example, the test norm defined in Section~\ref{sec:main_bounds} and the convection-diffusion problem with Dirichlet boundary conditions.
-
-The bilinear form for the case of Dirichlet boundary conditions is 
-\[
-b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(v,\tau\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) + \langle \widehat{u}, \jump{\tau \cdot n} \rangle_{\Gh^0} + \langle \widehat{f}_n, \jump{v} \rangle_{\Gh}.
-\]
-Notice that the boundary terms in the final bilinear form are different; hence, the adjoint problems associated with Section~\ref{sec:strategy3} will now carry different boundary conditions as well.
-Likewise, the stability properties proven previously will not hold under a different set of boundary conditions.
-%We note that 
-%\begin{align*}
-%b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gh^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gh}
-%&= \| u \|^2_{L^2}
-%\end{align*}
-%for the specific continuous test functions $\tau$ and $v$ satisfying
-%\begin{align*}
-%\div \tau - \beta \cdot \grad v &= u \\
-%\frac{1}{\epsilon}\tau + \grad v &= 0
-%\end{align*}
-%with boundary condition $\left.v\right|_\Gamma = 0$.
-Choosing a continuous conforming test function $v$ removes the contribution of the term $\langle \widehat{f}_n, \left[v\right] \rangle$ on the mesh skeleton, while the boundary conditions remove the contribution of boundary terms from the bilinear form.
-Then, for this specific choice of $\left(\tau, v\right)$,
-%\begin{align*}
-%\|u\|_{L^2}^2 &= b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right)}{\|\left(\tau, v\right)\|_V}\|\left(\tau, v\right)\|_V \leq \|u\|_E \|\left(\tau, v\right)\|_V
-%\end{align*}
-%At minimum, we want $\|u\|_{L^2} \lesssim \|u\|_E$, which requires 
-%\[
-%\|\left(\tau, v\right)\|_V \lesssim \| u \|_{L^2}
-%\]
-%for any choice of $u \in L^2$ (dividing through by $\|u\|_{L^2}$ gives the desired result).
-This can be considered a ``sanity check"; at the minimum, we at least want control over the behavior of the single field variable $u$.
-However, we are unable to prove this in the case of Dirichlet boundary conditions.
-
-As it turns out, the robust bounds given in Section~\ref{sec:main_bounds} hold in $\mathbb{R}^d$ for arbitrary $d$; however, we can show that for the case of Dirichlet boundary conditions, the same results do not hold, even in 1D.
-%In 1D, the problem reduces to 
-%\begin{align*}
-%\frac{1}{\epsilon}\sigma - u' &= 0\\
-%\left(u - \epsilon \sigma \right)' &=f
-%\end{align*}
-%with bilinear form
-%\begin{align*}
-%b\left(\left(u,\sigma,\widehat{u},\widehat{f}\right),\left(\tau,v\right)\right) &= \sum_{k=1}^N \left(\left.\widehat{u}(x) \tau(x)\right |^{x_k}_{x_{k-1}} + \left.\widehat{f}(x) v(x)\right |^{x_k}_{x_{k-1}}\right) \\
-%&+ \left(\sigma,\epsilon^{-1}\tau\right)_{\Oh} + (u,\tau')_{\Oh}- \left(u - \epsilon \sigma,v'\right)_{\Oh}
-%\end{align*}
-%where $\widehat{u}(x), \widehat{f}(x) \in \mathbb{R}$ are now point values defined on mesh points $x_k$ for $k=1,\ldots,N$, where $N$ is the number of elements.
-We can assume without loss of generality that $\Oh$ is the unit interval $(0,1)$.
-%
-%Let us first provide an interpretation of Lemma~\ref{lemma_stream}. Recall the bilinear form 
-%\begin{align*}
-%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-%\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
-%v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh} - \LRa{
-%\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n,
-%  \jump{v} }_{\Gh},
-%\end{align*}
-%By choosing $(v,\tau)$ such that
-%\begin{align*}
-%\div \tau - \beta \cdot \grad v &= u \\
-%\frac{1}{\epsilon} \tau + \grad v &= 0
-%\end{align*}
-%we will have 
-%\[
-%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-%\left( v, \tau \right)\right) =\|u\|_{L^2}^2 
-%\]
-%Given this, we can use the definition of the energy norm \eqnref{energyNorm} to bound
-%\[
-%\|u\|_{L^2}^2 = b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-%\left( v, \tau \right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-%\left( v, \tau \right)\right)}{\|(v,\tau)\|_V}\|(v,\tau)\|_V \lesssim \|u\|_E \|(v,\tau)\|_V
-%\]
-%If we can show that $\|(v,\tau)\|_V \lesssim \|u\|_{L^2}$ for $(v,\tau)$ as defined above, then this implies 
-%\[
-%\|u\|_{L^2} \lesssim \|u\|_E
-%\]
-%By the fact that 
-Consider now the 1D analogue of the estimate given by Lemma~\ref{lemma_stream}.  In 1D, $\|\beta\cdot\grad v_1\| \lesssim \|g\|$ reduces to the inequality 
-\[
-\|\beta v_1'\|\lesssim \|g\|, \quad g\in L^2\!\left(\Oh\right).
-\]
-Without this inequality, we are unable to prove the robust bound on the $L^2$ error $\|u-u_h\|_{L^2} \lesssim \nor{(u,\sigma,\widehat{u},\widehat{f}_n)-(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h})}_E$.
-
-The adjoint problem corresponding to Lemma~\ref{lemma_stream} in Section~\ref{sec:strategy3} is likewise reduced in 1D to the scalar equation
-\begin{align}
-\epsilon v_1'' + \beta v_1' &= -g \label{adjoint_1D}
-\end{align}
-with $v_1\in H^1_0\left((0,1)\right)$.  After multiplying this equation by $\beta v_1'$ and integrate by parts over $\Oh$, we can apply Young's inequality to get
-%\[
-%\int_0^1 \epsilon v_1'' \beta v_1' + \|\beta v_1'\|_{L^2}^2 = -\int_0^1 g \beta v_1'.\
-%]
-%Integrating by parts and Young's inequality gives
-\begin{align*}
-\left.\frac{\epsilon}{2} \beta v_1'^2\right|_0^1 + \|\beta v_1'\|_{L^2}^2 &\leq \frac{1}{2}\|g\|^2 + \frac{1}{2}\|\beta v_1'\|^2,
-\end{align*}
-implying that
-\begin{align*}
-\|\beta v_1'\|_{L^2}^2 & \lesssim \|g\|^2 + {\beta \epsilon} v_1'(0)^2.
-\end{align*}
-Let us restrict ourselves to the cases where $v_1$ is sufficiently smooth for $v'(0)$ to be well defined.
-Taking $g=1$ (corresponding to a piecewise constant approximation) we can solve \eqref{adjoint_1D} exactly.
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.5]{figs/testBoundary1D.png}
-\caption{$v_1(x) = \frac{e^{-\frac{x}{\epsilon}}}{e^{\frac{1}{\epsilon}}-1}\left(e^{\frac{1}{\epsilon}}\left(e^{\frac{x}{\epsilon}}-1\right) + \left(e^{\frac{1}{\epsilon}}-1\right)e^{\frac{x}{\epsilon}}x\right)$, the solution to the adjoint equation for $f=0$ and constant $\beta$ and load $g$ for $\epsilon = .01$.}
-\label{fig:testBoundary1D}
-\end{figure}
-The solution $v_1$ is plotted in Figure~\ref{fig:testBoundary1D}, where we can see that $v_1(x)$ develops strong boundary layers of width $\epsilon$ near the inflow boundary $x=0$.
-Consequently, $\frac{\epsilon}{2} v_1'(0)^2 \approx \epsilon^{-1}$.
-Thus, we cannot conclude $\|\beta v'\| \lesssim \|g\|$ when $g$ is a constant,\footnote{Unlike the case of Dirichlet boundary conditions, the inflow condition on $ \widehat{f}_n = u(0)-\epsilon u'(0)$ induces an adjoint boundary condition $\tau(0)=0$, or equivalently $v'(0) = 0$, removing the non-robust term from the estimate.} and as a consequence cannot conclude that the robust error bound $\|u-u_h\|_{L^2} \lesssim \|(u,\sigma,\widehat{u},\widehat{f}_n)-(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h})\|_E$ holds for the solution $u_h$.
-More detailed 1D error bounds for Dirichlet boundary conditions are provided in \cite{DPG3}, and indicate the same lack of robustness under the test norm derived in this paper.\footnote{Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
-\[
-\|\left(\tau, v\right)\|_{V,w}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\|_{w+\epsilon} + \| \div \tau\|_{w+\epsilon} + \frac{1}{\epsilon}\|\tau\|_{w+\epsilon}
-\]
-where $\|\cdot \|_{w+\epsilon}$ is a weighted $L^2$ norm, where the weight $w \in (0,1)$ is required to vanish on $\Gamma_-$ and satisfy $\grad w = O(1)$.
-The need for this weight is necessary to account for the loss of robustness at the inflow.}
-
-\begin{figure}[h!]
-\centering
-\subfigure[Primal problem, Dirichlet inflow BC]{\includegraphics[scale=.3]{figs/primalDir.png}}
-\subfigure[Adjoint problem, Dirichlet inflow BC]{\includegraphics[scale=.3]{figs/adjointDir.png}}
-\subfigure[Primal problem, new inflow BC]{\includegraphics[scale=.3]{figs/primal.png}}
-\subfigure[Adjoint problem, new inflow BC]{\includegraphics[scale=.3]{figs/adjoint.png}}
-\caption{Comparison of primal and adjoint problems under both the standard Dirichlet and the new inflow boundary condition.
-The outflow boundary for each problem is denoted in red.
-For the standard Dirichlet inflow condition, the solution to the adjoint problem can develop strong boundary layers at the outflow of the adjoint problem.
-Notice, under the new inflow conditions, the relaxation of a wall-stop boundary condition with a zero-stress condition at the outflow boundary of the adjoint problem.}
-\end{figure}
-
-In higher dimensions, the adjoint problem is of the same form as the primal problem with the direction of convection reversed.
-However, the primal problem determines adjoint boundary conditions on $\Gamma_-$ and $\Gamma_+$.
-Thus, wheareas for the primal problem, data is convected from the inflow to the outflow, in the adjoint problem, data is convected from the outflow to the inflow boundary instead.
-
-We can intuitively explain the loss of robustness under our derived test norm by the presence of the Dirichlet boundary condition on $v$ at the inflow boundary.
-Since the direction of convection is reversed in the adjoint equation, we can interpret the adjoint as representing the convection of a concentration $v$ from the outflow to the inflow boundary.
-In the presence of a Dirichlet boundary condition at the inflow, $v$ can develop strong boundary layers at the inflow.
-As a consequence, the quantities $\|\beta\cdot \grad v\|$ and $\sqrt{\epsilon}\|\grad v\|$ are no longer robustly bounded by $\|f\|$ and $\|g\|$, and we can no longer derive robust bounds on the error $\|u-u_h\|_{L^2}$ by the error in the energy norm.
-
-Recall our strategy for analysis was to decompose of $(v,\tau)$ into continuous and discontinuous portions.
-Mathematically speaking, the use of Dirichlet boundary conditions on the primal problem introduces strong boundary layers into the solution $v$ of the adjoint equation --- in other words, boundary layers are introduced into the continuous portions of our decomposition of $(v,\tau)$.\footnote{The boundary conditions do not introduce boundary layers into the actual computed test functions.
-However, an interesting phenomenon observed is that, for small $\epsilon$, a lack of robustness can manifest itself during numerical experiments as additional refinements near the inflow boundary, precisely where the continuous parts of the decomposition of $(v,\tau)$ develop boundary layers.} The new inflow boundary condition on the primal problem relaxes the wall boundary condition induced on the adjoint/dual problem with a boundary condition that does not generate boundary layers, resulting in stronger stability estimates for the adjoint, and a better result for the primal problem.
-
-%\begin{figure}[h]
-%\centering
-%\subfigure[Primal problem]{\includegraphics[scale=.3]{figs/primal.png}}
-%\subfigure[Adjoint problem]{\includegraphics[scale=.3]{figs/adjoint.png}}
-%\caption{Comparison of primal and adjoint problems for convection-diffusion under the standard Dirichlet outflow boundary condition and the new inflow boundary condition.
-Notice the replacement of a wall-stop boundary condition with a Neumann stress boundary condition at the outflow boundary of the adjoint problem.
-}
-%\end{figure}
-
-\section{Numerical experiments}
-\label{sec:num_exp}
-
-In each numerical experiment, we vary $\epsilon = .01, .001, .0001$ in order to demonstrate robustness over a range of $\epsilon$.
-This is intended to mirror the experience with roundoff effects in numerical experiments \cite{DPGrobustness}; for ``worst-case" linear solvers, such as LU decomposition without pivoting, the effect of roundoff error becomes evident in the solving of optimal test functions for $\epsilon \leq O(1e-5)$.
-The roundoff itself comes from the conditioning of the Gram matrix under certain test norms; for example, if the weighted $H({\rm div};\Omega)\times H^1(\Omega)$ norm is used for the test norm $\|\left(\tau,v\right)\|_V$ (as was done in \cite{DPG2}), for an element of size $h$, $\|v\|_{L^2}^2 = O(h)$, while $\|\grad v\|_{L^2}^2 = O(h^{-1})$.
-As $h\rightarrow 0$, the seminorm portion of the test norm dominates the Gram matrix, leading to a near-singular and ill-conditioned system.
-
-The effect of roundoff error is often characterized by an increase in the energy error, which (assuming negligible error in the approximation of test functions) is proven to decrease for any series of refined meshes.
-These roundoff effects are dependent primarily on the mesh, appearing when trying to fully resolve very thin boundary layers by introducing elements of size $\epsilon$ through adaptivity.
-The effects of roundoff error were successfully treated in \cite{DPG3} by dynamically rescaling the test norms based on element size, a practical remedy not covered yet by the present analysis.
-
-\subsection{Eriksson-Johnson model problem}
-
-To confirm our theoretical results, we adopt a modification of a problem first proposed by Eriksson and Johnson in \cite{Eriksson1993}.
-For the choice of $\Omega = (0,1)^2$, $f=0$, and $\beta = (1,0)^T$, the convection diffusion equation reduces to
-\[
-\pd{u}{x} - \epsilon \left(\pdd{u}{x}+ \pdd{u}{y}\right) = 0,
-\]
-which has an exact solution by separation of variables, allowing us to analyze convergence of DPG for a wide range of $\epsilon$.
-For boundary conditions, we impose $u=0$ on $\Gamma_+$ and $\beta_n u - \sigma_n$ on $\Gamma_-$, which reduces to
-\begin{align*}
-u-\sigma_x &= u_0-\sigma_{x,0}, \quad x=0,\\
-\sigma_y &=  0, \quad y=0,1,\\
-u &= 0, \quad x=1.\\
-\end{align*}
-In this case, our exact solution is the series
-\[
-u(x,y) = C_0 + \sum_{n=1}^\infty C_n \frac{\exp(r_2(x-1)-\exp(r_1(x-1)))}{r_1\exp(-r2) - r_2\exp(-r1)}\cos(n\pi y),
-\]
-where
-\begin{align*}
-r_{1,2} &= \frac{1 \pm \sqrt{1 + 4 \epsilon\lambda_n}}{2 \epsilon},\\
-\lambda_n &= n^2\pi^2 \epsilon.
-\end{align*}
-The constants $C_n$ depend on a given inflow condition $u_0$ at $x=0$ via the formula
-\[
-C_n = \int_0^1 u_0(y) \cos(n\pi y).
-\]
-
-All computations have been done using the adaptive DPG code Camellia, built on the Sandia toolbox Trilinos \cite{Camellia}.
-
-\subsubsection{Solution with $C_1 = 1, C_{n\neq 1} = 0$}
-
-We begin with the solution taken to be the first non-constant term of the above series.
-We set the inflow boundary condition to be exactly the value of $u-\sigma_x$ corresponding to the exact solution.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.37]{figs/wallBC_exact_u.png}
-}
-\subfigure{
-\includegraphics[scale=.37]{figs/wallBC_exact_sigx.png}
-}
-\subfigure{
-\includegraphics[scale=.37]{figs/wallBC_exact_sigy.png}
-}
-\caption{Solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
-\end{figure}
-In each case, we begin with a square 4 by 4 mesh of quadrilateral elements with order $p=3$.
-We choose $\Delta p = 5$, though we note that the behavior of DPG is nearly identical for any $\Delta p \leq 3$, and qualitatively the same for $\Delta p = 2$.
-$h$-refinements are executed using a greedy refinement algorithm, where element energy error $e_K^2$ is computed for all elements $K$, and elements such that $e_K^2 \leq \alpha \max_K e_K^2$ are refined.
-We make the arbitrary choice of taking $\alpha = .2$ for each of these experiments.
-
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=.4]{figs/u_pointdiff_wallBC.png}
-\caption{Adapted mesh and pointwise error for $\epsilon=.01$}
-\end{figure}
-We are especially interested in the ratio of energy error and total $L^2$ error in both $\sigma$ and $u$, which we denote as $\|u-u_h\|_{L^2}$.
-The bounds on $\nor{\cdot}_E$ presented in Section~\ref{sec:main_bounds} imply that, using the above test norm, $\|u-u_h\|_{L^2} / \|u-u_h\|_E \leq C$ independent of $\epsilon$.
-Figure~\ref{ratios_simple}, which plots the ratio of $L^2$ to energy error, seems to imply that (at least for this model problem) $C=O(1)$.
-Additionally, while we do not have a robust lower bound ($\|u-u_h\|_{L^2} / \|u-u_h\|_E$ can approach $0$ as $\epsilon \rightarrow 0$), our numerical results appear to indicate the existence of an $\epsilon$-independent lower bound.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{figs/errorrates_wallBC.png}
-}
-\subfigure{
-\includegraphics[scale=.38]{figs/L2energyratio_wallBC.png}
-}
-\caption{$L^2$ and energy errors, and their ratio for $\epsilon=.01$, $\epsilon=.001$, $\epsilon=.0001$}
-\label{ratios_simple}
-\end{figure}
-The effect of a mesh dependent scalings on the $\|v\|^2$ and $\|\tau\|^2$ terms in the test norm can be seen in the ratios of $L^2$ to energy error; as the mesh is refined, the constants in front of the $L^2$ terms for $v$ and $\tau$ converge to stationary values (providing the full robustness implied by our adjoint energy estimates), and the ratio of $L^2$ to energy error transitions from a smaller to a larger value.
-The transition point happens later for smaller $\epsilon$, which we expect, since the transition of the ratio corresponds to the introduction of elements whose size is of order $\epsilon$ through mesh refinement.
-
-We examined how small $\epsilon$ needed to be in order to encounter roundoff effects as well.
-In \cite{DPGrobustness}, the smallest resolvable $\epsilon$ using only double precision arithmetic was $1e-4$.
-The solution of optimal test functions is now done using both pivoting and equilibration, improving conditioning.
-Roundoff effects still appear, but at smaller values of $\epsilon$.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{figs/roundoff_rates.png}
-}
-\subfigure{
-\includegraphics[scale=.38]{figs/roundoff_ratio.png}
-}
-\caption{Energy error and $L^2$/energy error ratio for $\epsilon=1e-5$, $\epsilon=1e-6$, $\epsilon=1e-7$.
-Non-monotonic behavior of the energy error indicates conditioning issues and roundoff effects.}
-\label{roundoff_figures}
-\end{figure}
-
-Without anisotropic refinements, it still becomes computationally difficult to fully resolve the solution for $\epsilon$ smaller than $1e-5$.
-Regardless, for all ranges of $\epsilon$, DPG does not lose robustness, as indicated by the rates and ratio between $L^2$ and energy error in Figure~\ref{roundoff_figures} remaining bounded from both above and below.
-For $\epsilon = 1e-5$, we observe that the ratio of $L^2$ error increases, corresponding to the scaling of the test norm with mesh size (the transition in test norm occurs after 8 refinements, which, for an initial $4\times 4$ mesh, implies a minimum element size of about $1.5e-05$.
-At this point, rescaled test norm allows us to take advantage of the full magnitude of the $L^2$ term for $\|v\|$ and $\|\tau\|$ implied by our adjoint estimates).
-By analogy, for smaller $\epsilon = 1e-6, 1e-7$, the transition period should begin near the 10th and 11th refinement iterations; however, we do not observe such behavior, possibly due to roundoff effects.
-For $\epsilon=1e-6$, the ratio simply remains constant, but for $\epsilon=1e-7$, we observe definite roundoff effects, as the energy error increases at the 11th refinement.
-Since DPG is optimal in the energy norm for a mesh-independent test norm\footnote{While the test norm changes with the mesh, it increases monotonically.
-A strictly stronger test norm implies $\frac{b(u,v)}{\|v\|_1} \geq \frac{b(u,v)}{\|v\|_2}$ for any $\|v\|_1 \leq \|v\|_2$}, we expect monotonic decrease of the energy error with mesh refinement.
-Non-monotonic behavior indicates either approximation or roundoff error, and as we observed no qualitative difference between using $\Delta p = 5$ and $\Delta p = 6$ for these experiments, we expect that the approximation error is negligible and conclude roundoff effects are at play when these phenomena are observed.
-
-It is worth noting that for $\epsilon \leq 1e-5$, we do not perform enough refinements to completely resolve the boundary layer, so $|K| \geq \epsilon$ for all $K\in \Oh$.
-Thus, any roundoff effects observed are not due to the conditioning issues associated with the differing scales of the $\nor{v}_{L^2(K)}$ and $\nor{\grad v}_{L^2(K)}$ terms discussed previously.
-
-\subsubsection{Neglecting $\sigma_n$}
-
-In practice, we will not have prior knowledge of $\sigma_n$ at the inflow, and will have to set $\beta_n u - \sigma_n = u_0$, ignoring the viscous contribution to the boundary condition.
-The hope is that for small $\epsilon$, this omission will be negligible.
-Figure~\ref{ratios_noSigma} indicates that, between $\epsilon = .005$ and $\epsilon = .001$, the omission of $\sigma_n$ in the boundary condition becomes negligible, and both our error rates and ratios of $L^2$ to energy error become identical to the case where $\sigma_n$ is explicitly accounted for in the inflow condition.
-For large $\epsilon = .01$, the $L^2$ error stagnates around $1e-3$, or about $7\%$ relative error.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{figs/rates_noSigma.png}
-}
-\subfigure{
-\includegraphics[scale=.38]{figs/ratio_noSigma.png}
-}
-\caption{$L^2$ and energy errors and their ratio when neglecting $\sigma_n$ at the inflow.}
-\label{ratios_noSigma}
-\end{figure}
-
-\subsubsection{Discontinuous inflow data}
-
-We note also that an additional advantage of selecting this new boundary condition is a relaxation of regularity requirements: as $\widehat{f}_n \in H^{-1/2}(\Gh)$, strictly discontinuous inflow boundary conditions are no longer ``variational crimes".
-We consider the discontinuous inflow condition
-\[
-u_0(y) = \begin{cases}
-(y-1)^2, \quad &y>.5\\
--y^2, \quad &y\leq .5 
-\end{cases}
-\]
-as an example of a more difficult test case.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{figs/disc_hat.png}
-}
-\subfigure{
-\includegraphics[scale=.38]{figs/disc_hat_surf.png}
-}
-\caption{Solution variables $u$ and $\widehat{u}$ with discontinuous inflow data $u_0$ for $\epsilon = .01$.}
-\label{disc_sol}
-\end{figure}
-Figure~\ref{disc_sol} shows the solution $u$ and overlaid trace variable $\widehat{u}$, which both demonstrate the regularizing effect of viscosity on the discontinuous boundary condition at $x=0$.
-However, we do not have a closed-form solution with which to compare results for a stricly discontinuous $u_0$.
-In order to analyze convergence, we approximate $u_0$ with 20 terms of a Fourier series, giving a near-discontinuity for $u_0$.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{figs/rates_disc.png}
-}
-\subfigure{
-\includegraphics[scale=.38]{figs/ratio_disc.png}
-}
-\caption{$L^2$ and energy errors, and their ratio for $\epsilon=.01$, $\epsilon=.001$, $\epsilon=.0001$, with discontinuous $u_0$ approximated by a Fourier expansion. }
-\label{disc_sol_fourier}
-\end{figure}
-
-The ratios of $L^2$ to energy error are now less predictable than for the previous example, in part due to the difficulty in approximating highly oscillatory boundary conditions.
-The numerical experiments were originally performed by applying boundary conditions via interpolation; the result was that the highly oscillatory inflow boundary condition was not sampled enough to be properly resolved, causing the solution to converge to a solution different than the exact solution.
-The experiments were repeated using the penalty method to enforce inflow conditions; however, we note that the proper way to do so is to use an $L^2$ projection at the boundary.
-Even when using the penalty method, however, the ratios still remain bounded and close to $1$ for $\epsilon$ varying over two orders of magnitude, as predicted by theory.
+where $F(\text{Pe})$ is some non-decreasing function of the Peclet number.
+Numerical experiments confirm that, for the quasi-optimal test norm, underresolution of the inflow boundary layer negatively affects only the robustness of $u$.
 
@@
 
-We have presented in this paper the analysis of a non-canonical test norm and its corresponding DPG energy norm for the convection-diffusion equation in the small-diffusion limit.
-Additionally, we have introduced a non-standard inflow boundary condition, and have explored the difference between between this and the standard Dirichlet inflow boundary condition.
+\begin{itemize}
+\item There are three levels at which you should look - the continuous level (the adjoint problem for $L^2$ robustness), the global level (which links the adjoint equation to the test functions), and the localized test norm (which relates local test functions to global test functions).
+\item Your test norm may induce boundary layers even when they're not necessary for adjoint $L^2$ stability.
+\item If your test norm promises global boundary layers (that affect robustness), not approximating them leads to a loss of robustness. 
+\end{itemize}
 
-Numerical results are presented in order to verify the results derived in this paper.
-However, at least for our model problem, numerical experiments appear to demonstrate results that are stronger than our proofs indicate, delivering solutions for $u$ and $\sigma$ that are extremely close to their best $L^2$ projections.
+You have to account for the boundary layer/$\epsilon$ diffusion scale somehow - either by 
+\begin{itemize}
+\item adjusting the test norm to account for robustness (weighted test norm), which pushes the $\epsilon$ into the inflow area, 
+\item removing the continuous adjoint problem (``convection'' inflow boundary condition), which removes the boundary layer for $L^2$ stability altogether, 
+\item resolving the global boundary layers (demonstrated here and in Antii's Shishkin meshes)
+\end{itemize}
+\end{document}
 
-The theory presented in this paper have been successfully extrapolated to nonlinear singular perturbation problems and systems of equations, and has been applied in context of the Burgers and Navier-Stokes equations.
-These results will be presented in an upcoming paper.
-
-\section{Acknowledgements}
-
-The authors would like to acknowledge the help of Nathan Roberts with software development and Dr Robert Moser for fruitful discussions and perspective.
-Chan and Demkowicz were supported by the Department of Energy [National Nuclear Security Administration] under Award Number [DE-FC52-08NA28615].
-Heuer was supported through the project "Fondecyt-Chile 1110324" and by the "J Tinsley Oden Faculty Research Fellowship" of the Institute of Computational Engineering and Sciences (ICES).
-
-%None yet.  Ideas:
-%\begin{itemize}
-%\item Explanation of choice of boundary condition and why it impacts stability
-%\item Interpretation of weight as allowing diffusion to work on the boundary.  
-%\item Note results have worked for Burgers, and mention the extension to Navier-Stokes
-%\end{itemize}
-
-\bibliographystyle{plain}
-\bibliography{paper}
-
-\input{paper_appendix.tex}
-
-\end{document}
+%\subsection{The strong form of the trial-to-test operator}
+%
+%Under the graph test norm 
+%\[
+%\LRp{v,\delta v}_{V(K)} = \LRp{A_h^*v,A_h^*\delta v}_{L^2(K)} + (v,\delta v)_{L^2(K)},
+%\]
+%element-local test functions are induced as solutions of 
+%\[
+%\LRp{v,\delta v}_{V(K)} = (u,A_h^*\delta v)_K + \LRa{\uh,\delta v}_{\partial K}
+%\]
+%Under proper regularity assumptions, this variational problem corresponds to the strong problem
+%\begin{align*}
+%A_hA_h^*v + v &= A_hu, \quad \text{on $K$}\\
+%\gamma\LRp{A_h^*v} &= \uh.
+%\end{align*}

### 2012-10-25 docs/Nate/Proposal/presentation/tst_2012_talk.tex

@@
 \begin{document}
+
+%PATTER: I'm a PhD. candidate in the computational science, engineering, and mathematics program here at UT.
 \begin{frame}
-%\begin{center}
-%\includegraphics[width=.8\linewidth]{grand_logo}\\
-%\end{center}
+\begin{center}
+\includegraphics[width=.6\linewidth]{grand_logo}\\
+\end{center}
 \titlepage
@@
 %===============================================================================
+%\begin{frame}                                                                                                                                                                          
+%\frametitle{Solving with DPG}
+%\begin{center} 
+%\includegraphics[width=0.9\linewidth]{../figures/DPGSolveCartoonNew}\\
+%\end{center}
+%\end{frame}
+
 \begin{frame}                                                                                                                                                                          
 \frametitle{Solving with DPG}
-\begin{center} 
-\includegraphics[width=0.9\linewidth]{../figures/DPGSolveCartoonNew}\\
-\end{center}
+\begin{itemize}
+\item We drive \pecosbold{adaptivity} using an energy norm in which we can precisely determine the error:
+\[
+\NVRnorm{u-u_{h}}_{E} = \NVRnorm{R_{V}^{-1}\left(Bu_{h} - l \right)}_{V}.
+\]
+\item In practice, must \pecosbold{approximate} $R_{V}^{-1}$.  We do this by using ``enriched'' test space $V_{p+\Delta p}$.  ($\Delta p=$ 1 or 2, usually.)
+\item Test functions belong to a \pecosbold{broken} (element-wise conforming) space.
+\item \pecosbold{Discontinuous} test space $\implies$ optimal test functions can be determined element-locally.
+\item The system matrix is symmetric-positive definite:
+\[
+K_{ij} = b(e_{i}, v_{e_{j}}) = (v_{e_{i}}, v_{e_{j}})_{V} = (v_{e_{j}}, v_{e_{i}})_{V} = b(e_{j}, v_{e_{i}}) = K_{ji}
+\]
+\end{itemize}
+
 \end{frame}
@@
 \item for non-singularly-perturbed, well-posed linear problems, \pecosbold{provably optimal} convergence rates when the ``adjoint graph norm'' is used for the test space
-\item \pecosbold{SPD} stiffness matrix
-\item discontinuous test space $\implies$ solving for test functions is a \pecosbold{local} operation
+%\item \pecosbold{SPD} stiffness matrix
 \item nonlinear problems: so far, apply the linear method to the linearized problem
@@
 
-  VarPtr psi_hat_n = varFactory.fluxVar("\\widehat{\\phi}_n");
-  VarPtr phi_hat = varFactory.traceVar("\\widehat{\\psi}");
+  VarPtr psi_hat_n = varFactory.fluxVar("\\widehat{\\psi}_n");
+  VarPtr phi_hat = varFactory.traceVar("\\widehat{\\phi}");
   VarPtr psi = varFactory.fieldVar("\\psi", VECTOR_L2);

### 2012-10-29 docs/Jesse/Small talks/globalLocal/globalLocalTalk.tex
adding small talks folder

--- 2012-09-06 docs/Jesse/Proposal/boeingPres.tex
@@
 
-\title[A DPG method for Compressible Flow]{A Discontinuous Petrov-Galerkin method for compressible flow problems}
-\date{August 15, 2012}
-\author[J. Chan, T. Ellis, L. Demkowicz, R. Moser]{Jesse Chan, Truman Ellis \\ Supervisors: Leszek Demkowicz, Robert Moser}
+\title[Global/local DPG]{Global and local DPG test functions for convection-diffusion}
 
@@
 \frame{
-\frametitle{Compressible Navier-Stokes equations}
-\begin{columns}[c]
-\begin{column}{.475\textwidth}
-Numerical difficulties:
-\begin{itemize}
-\item{} Resolving solution features (sharp, localized viscous-scale phenomena)
-\begin{itemize}
-\item{} Shocks
-\item{} Boundary layers - resolution needed for drag/load
-\item{} Turbulence (non-localized)
-\end{itemize}
-\item{} Nonlinear convergence and uniqueness of solutions
-\item{} Stability of numerical schemes
-\begin{itemize}
-\item{} Coarse/adaptive grids
-\item{} Higher order
-\end{itemize}
-\end{itemize}
-\end{column}
-\begin{column}{.475\textwidth}
-\begin{figure}
-\centering
-\includegraphics[scale = .7]{figs/compFlowPics/airfoil_mesh.png}
-\end{figure}
-\end{column}
-\end{columns}
-\vspace{.2cm}
-\begin{center}
-Idea: begin first with the model problem of convection-diffusion.
-\end{center}
-}
-\frame{
-\frametitle{Robustness: convection-diffusion as a model problem}
-\vspace{-.5cm}
-\[
-\div \left(\beta u\right) - \epsilon \Delta u = f, \quad \text{on }\Omega \in \mathbb{R}^3
-\]
-\vspace{-.5cm}
-\begin{columns}[c]
-\begin{column}{.49\textwidth}
-In 1D: $\beta u' - \epsilon u'' = f$. Standard continuous Galerkin variational formulation: solve
-\[
-b(u,v) = \ell(v), \quad u,v\in H^1_0([0,1])
-\]
-where
-\begin{align*}
-b(u,v) &= \int_\Omega -\beta uv' + \epsilon u'v' \\
-\ell(v) &= \int_\Omega f v 
-\end{align*}
-\end{column}
-\begin{column}{.49\textwidth}
-\begin{figure}
-\centering
-\includegraphics[scale=.35]{figs/GalerkinOscTight.png}
-\caption{Solution for $f=1$. Oscillations in the standard Galerkin method for large Peclet numbers ${\rm Pe} \coloneqq \frac{h}{\epsilon}$.}
-\end{figure}
-\end{column}
-\end{columns}
-}
-
-\frame{
-\frametitle{Streamline-upwind Petrov-Galerkin (SUPG)}
-SUPG solves $b_{\rm SUPG}(u,v) = l_{\rm SUPG}(v)$, where
-\begin{align*}
-b_{\rm SUPG}(u,v) &= b(u,v)+ \sum_{K} \int_{K} \tau \LRp{L_{\rm adv} v} L u \\
-l_{\rm SUPG}(v) &= \ell(v) + \sum_{K} \int_{K} \tau \LRp{L_{\rm adv}v} f.
-\end{align*}
-\vspace{-.5cm}
-\begin{columns}[c]
-\begin{column}{.44\textwidth}
-\vspace{-.5cm}
-\begin{itemize}
-\item{} $Lu = \div\left(\beta u\right) - \epsilon \triangle u$, $L_{\rm adv}u = \div \left(\beta u\right)$, and $\tau$ is a parameter. 
-%\item{} Recovers ``exact'' artificial diffusion for $f=0$.
-\item{} Effective for $f\neq 0$. %``exact'' artificial diffusion.
-\item{} \emph{Residual-based} stabilization. 
-\end{itemize}
-\end{column}
-\begin{column}{.54\textwidth}
-\begin{figure}
-\centering
-\includegraphics[scale=.38]{figs/SUPG.png}
-%\caption{Exact, Bubnov-Galerkin, and SUPG solutions.}
-\end{figure}
-\end{column}
-\end{columns}
-}
-
-\frame{
-\begin{columns}
-\begin{column}{.49\textwidth}
-Can be interpreted as a \emph{Petrov-Galerkin} method,
-\[
-b\LRp{u,\tilde{v}_{i}} = \ell\LRp{\tilde{v}_{i}}, \quad \forall i = 1,\ldots,N-1,
-\]
-where the SUPG test function $\tilde{v}_{i}$ is defined elementwise as\footnotemark
-\[
-\tilde{v}_{i} = \phi_i(x) + \tau L_{\rm adv} \phi_i.  
-\]
-\end{column}
-\begin{column}{.49\textwidth}
-\begin{figure}
-\centering
-\subfigure{\includegraphics[scale=.16]{figs/SUPGtest.png}}
-\caption{SUPG test function $v_i$.}
-\end{figure}
-\end{column}
-\end{columns}
-\footnotetext{\bibentry{SUPG}}
-}
-
-\section{The DPG Method}
-\frame{
-\frametitle{DPG: a minimum residual method via optimal testing}
-Given a trial space $U$ and Hilbert test space $V$,
-\[
-b(u,v) = \ell(v), \quad u\in U, \quad v\in V
-\]
-This is equivalent to the operator equation posed in $V'$
-\[
-Bu = \ell
-\]
-if we identify $B:U\rightarrow V'$ and $\ell\in V'$ such that 
-\begin{align*}
-\langle Bu,v\rangle_V &\coloneqq b(u,v), \quad u\in U, v\in V,\\
-\langle \ell,v\rangle_V &\coloneqq \ell(v), \quad v\in V.
-\end{align*}
-We seek to minimize the dual functional over $U_h \subset U$
-\[
-J(u_h) = \frac{1}{2}\|Bu_h-\ell\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(u_h,v)-\ell(v)|^2}{\nor{v}_V^2}.
-\]
-}
-
-\begin{frame}
-Let $R_V: V \to V'$ be the isometric Riesz map st.\
-\[
-\langle R_V v,\delta v\rangle_V \coloneqq(v, \delta v)_V, \quad \forall \delta v \in V.
-\]
-Then, our functional $J(u_h)$ is equal to
-\begin{equation*}
-\min_{u_h\in U_h} J(u_h) = \frac{1}{2}\left\|Bu_h-\ell\right\|_{V'}^2 =  \frac{1}{2}\left\|R_V^{-1}(Bu_h-\ell)\right\|_V^2.
-\end{equation*}
-First order optimality: G\^ateaux derivative is zero in all directions $\delta u \in U_h$
-\begin{align*}
-\left(R_V^{-1}(Bu_h-\ell),R_V^{-1}B\delta u\right)_V &= 0, \quad \forall \delta u \in U_h.\\
-\rightarrow \LRa{(Bu_h-\ell),R_V^{-1}B\delta u} &= 0, \\
-\rightarrow b(u_h,R_V^{-1}B\delta u) - \ell(R_V^{-1}B\delta u) &= 0
-\end{align*}
-\end{frame}
-
-\frame{
-\frametitle{Summary: select test functions to minimize residuals}
-For $\delta u \in U_h$, define the \textcolor{red}{optimal test function} $v_{\delta u}$. 
-\begin{equation*}
-v_{\delta u} \coloneqq R_V^{-1}B\delta u.
-\end{equation*} 
-Then, the residual $J(u_h) = \frac{1}{2}\left\|Bu_h-\ell\right\|_{V'}^2$ is minimized by the solution of
-\[
-b\LRp{u_h,v_{\delta u}} = \ell\LRp{v_{\delta u}}, \quad \forall \delta u \in U_h.
-\]
-}
-
-\frame{
-\frametitle{Practical details of DPG}
-Computation of $v_{\delta u} \coloneqq R_V^{-1}B\delta u$ is \textbf{global} and \textbf{infinite-dimensional}.
-\begin{itemize}
-\item By choosing a \textcolor{red}{broken} test space $V$ and \textcolor{red}{localizable} norm $\nor{v}_V^2 = \sum_K \nor{v}_{V(K)}^2$, test functions can be determined locally.
-\item In practice, we use an \textcolor{red}{enriched space} $V_h \subset V$, where $\dim(V_h) > \dim(U_h)$ elementwise, and \textcolor{red}{optimal test functions} are approximated by computing $v_{\delta u} \coloneqq R_{V_h}^{-1}B\delta u \in V_h$ through\footnote{\bibentry{DPG2}}
-\[
-\LRp{v_{\delta u},\delta v}_V = b(\delta u,\delta v), \quad \delta u\in U_h, \quad \forall \delta v\in V_h
-\]
-Typically, if $U_h = \mathcal{P}^p(\mathbb{R}^n)$, $V_h = \mathcal{P}^{p+\triangle p}(\mathbb{R}^n)$, where $\triangle p \geq n$.\footnote{\bibentry{practicalDPG}} 
-\end{itemize}
-%\footnotetext{\bibentry{DPG2}}
-}
-
-\frame{
-\frametitle{Properties of DPG}
-DPG provides a symmetric positive-definite stiffness matrix. Let $\{\phi_j\}_{j=1}^m$ be a basis for $U_h$, and $\{v_i\}_{i=1}^n$ a basis for $V_h$, such that $n>m$. Then, for 
-\begin{align*}
-B_{ji} &= b(\phi_j,v_i),\\
-l_i &= \ell(v_i),
-\end{align*}
-DPG solves the discrete system for degrees of freedom $u$
-\begin{align*}
-\LRp{B^T R_V^{-1}B} u  &= \LRp{B^T R_V^{-1}} l,
-\end{align*}
-where, under a localizable norm and discontinuous test functions, $R_V^{-1}$ is block diagonal.
-}
-
-\frame{
-\frametitle{Properties of DPG}
-Additional properties of DPG include\footnotemark
-\begin{itemize}
-\item DPG provides the best approximation in the \textcolor{red}{energy norm}
-\[
-\|u\|_E = \|Bu\|_{V'} = \sup_{\nor{v}_V=1} \left|b(u,v)\right|.
-\]
-\item The energy error is computable through the residual
-\[
-\nor{u-u_h}_E = \nor{B(u-u_h)}_{V'} = \nor{R_V^{-1}(l-Bu_h)}_V = \nor{e}_V
-\]
-where the \textcolor{red}{error representation function} $e$ is defined through $(e,\delta v)_V = \ell(v)-b(u_h,\delta v)$ for all $\delta v\in V$. 
-\end{itemize}
-\footnotetext{\bibentry{DPG3pub}}
-}
-
-%\frame{
-%\frametitle{Duality of norms}
-%Duality of norms: for any trial norm $\nor{u}_U$,
-%\[
-%\nor{u}_{U} = \sup_{v \in V}\frac{b\LRp{u,v}}{\nor{v}_{V,U}}, \quad \nor{v}_{V,U} = \sup_{u \in U}\frac%{b\LRp{u,v}}{\nor{u}_{U}}.
-%\]
-%Likewise, for any test norm $\nor{v}_V$, 
-%\[
-%\nor{v}_{V} = \sup_{u \in U}\frac{b\LRp{u,v}}{\nor{U}_{U,V}}, \quad \nor{u}_{U,V} = \sup_{v \in V}\frac%{b\LRp{u,v}}{\nor{v}_{V}}.
-%\]
-%
-%}
-
-\frame{
 \frametitle{Ultra-weak formulation}
-\vspace{-.75cm}
-\begin{columns}
-\begin{column}{.64\textwidth}
-Given a first order system $Au = f$, we identify the \textbf{\emph{partition}} $\Oh$ and \textbf{\textcolor{red}{mesh skeleton}} \textcolor{red}{$\Gh$}.
-\end{column}
-\begin{column}{.34\textwidth}
-%\[
-%\Oh = \cup_{j=1}^\Nel K_j, \quad \Gh = \cup_{j=1}^\Nel \partial K_j
-%\]
-\begin{figure}[!h]
-\centering
-\includegraphics[scale = .155]{mesh_skel.pdf}
-\end{figure}
-\end{column}
-\end{columns}
-\vspace{-.5cm}
-The ultra-weak formulation for $Au = f$ on $\Oh$ is
-\[
-b\left(\left(u, \widehat{u}\right),v\right) \coloneqq \sum_K\langle \widehat{u},v \rangle_{\partial K} + (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh}.
-\]
-Under proper assumptions, $\sum_K\langle \widehat{u},v \rangle_{\partial K} = \langle \widehat{u}, \jump{v} \rangle_{\Gh}$, with energy setting
-\[
-u\in L^2\LRp{\Oh} \equiv L^2(\Omega), \quad v\in V=D(A^*_h), \quad
-\widehat{u}\in \gamma(D(A)),
-\]
-where $D(A_h^*)$ is the broken graph space of the formal adjoint $A_h^*$, and $\gamma(D(A))$ the trace space of the graph space of operator $A$.\footnote{\bibentry{analysisDPG}}
-}
-
-\frame{
-\frametitle{The canonical ``graph'' test norm}
-Recall $\nor{u}_E \coloneqq \sup_{v\in V\setminus\{0\}}\frac{b(u,v)}{\nor{v}_V}$. Under the ultra-weak formulation, the trial norm 
-\[
-\nor{\LRp{u,\widehat{u}}}_U \coloneqq \|u\|^2_{\L} + \|\widehat{u}\|^2
-\] 
-generates a test norm \emph{equivalent} to 
-\[
-\nor{v}_{V_{\rm opt}} \coloneqq \|A_h^*v\|_{\L}^2 +\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},\jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2.
-\]
-This norm is not localizable, so we instead substitute the jump terms for an $L^2$ term, giving us the \emph{graph norm}\footnote{\bibentry{Bui-ThanhDemkowiczGhattas11b}}
-\[
-\nor{v}_V \coloneqq \|A_h^*v\|_{\L}^2 + \nor{v}_{L^2}.
-\]
-}
-
-\frame{
-\frametitle{Goal: robust higher order adaptive methods}
-\begin{columns}
-\begin{column}{.45\textwidth}
-Our aim is to design an adaptive method for compressible laminar flows that is 
-\begin{itemize}
-\item robust in Reynolds number
-\item stable for arbitrary elements
-\end{itemize}
-
-This proposal will outline
-\begin{enumerate}
-\item a robust DPG method for convection-diffusion,
-\item extension to nonlinear problems and systems,
-\item proposed work.
-\end{enumerate}
-
-\end{column}
-\begin{column}{.54\textwidth}
-\begin{figure}
-\centering
-\subfigure{\includegraphics[scale=.23]{figs/Re1000p2/u2_full.png}}
-\subfigure{\includegraphics[scale=.37]{figs/Re1000p2/mesh6.png}}
-\caption{$u_2$ and $p=2$ mesh for $\Reyn = 1000$.}
-\end{figure}
-\end{column}
-\end{columns}
-}
-
-\section{A Robust DPG Method for Convection-Diffusion}
-
-\frame{
-\frametitle{Ultra-weak formulation for convection-diffusion}
-In first order form, the convection-diffusion equation is
-\[
-A \LRp{u,\sigma} \coloneqq 
-\LRs {
-\begin{array}{c}
-\div (\beta u - \sigma) \\ \frac{1}{\epsilon}\sigma - \grad u
-\end{array}} = \LRs{
-\begin{array}{c}
-f \\ 0
-\end{array}
-}.
-\]
-The variational formulation is
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-\left( v, \tau \right)\right) = \left(u,\grad_h\cdot \tau - \beta \cdot \grad_h
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad_h v\right)_{\Oh}&\\
-  - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
-\end{align*}
-where $\widehat{f}_n \coloneqq \beta_n u - \sigma_n$ and $\LRa{\widehat{f}_n,\jump{v} }_{\Gh}$ is defined 
-\[
-\LRa{\widehat{f}_n,\jump{v} }_{\Gh}\coloneqq \sum_K\int_{\partial K}{\rm sgn}(\vec{n}) \, \widehat{f}_n v.
-\]
-}
-
-\frame{
-\frametitle{Graph norm under convection-diffusion}
-For convection-diffusion, the graph test norm is defined elementwise
-\[
-\|\left(v,\tau\right)\|_{V(K)}^2 = \| \div \tau - \beta \cdot \grad v
-\|_{L^2(K)}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2(K)}^2 +
-\|v\|_{L^2(K)}^2.
-\]
-Problem with this test norm: approximability of test functions.
-\vspace{-.3cm}
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.175]{figs/opt.png}
-\caption{$v$ and $\tau$ components of the 1D optimal test functions for flux $\widehat{f}_n$ on the \emph{right-hand} side of a unit element for $\epsilon = 0.01$. }
-\label{fig:optTestBoundary}
-\end{figure}
-}
-
-\frame{
-\frametitle{Determining an alternative test norm}
-Recall the convection-diffusion bilinear form
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh}&\\
- - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
-\end{align*}
-We recover $\nor{u}^2_{L^2(\Omega)}$ by choosing conforming $\LRp{v,\tau}$ satisfying the \emph{adjoint equations}
-\begin{align*}
-\div\tau - \beta \cdot \grad v   &= u\\
-\frac{1}{\epsilon}\tau + \grad v &= 0
-\end{align*}
-with boundary conditions s.t.\ $\LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gamma}$ and $\LRa{ \widehat{f}_n,\jump{v} }_{\Gamma}$ vanish.
-}
-
-\frame{
-\frametitle{A robust bound}
-``Necessary'' conditions for robustness --- let $\boldsymbol U = \LRp{u,\sigma,\widehat{u},\widehat{f}_n}$. Then, by choosing specific $\LRp{v,\tau}$ satisfying the adjoint equations,
-\[
-\nor{u}^2_{L^2(\Omega)} = b\LRp{{\boldsymbol U},\LRp{v,\tau}} = \frac{b\LRp{{\boldsymbol U},\LRp{v,\tau}}}{\nor{\LRp{v,\tau}}_V} \nor{\LRp{v,\tau}}_V \leq \nor{\boldsymbol U}_E \nor{\LRp{v,\tau}}_V
-\]
-Let $\lesssim$ denote a robust bound - \textcolor{red}{if $ \nor{\LRp{v,\tau}}_V \lesssim \|u\|_{L^2(\Omega)}$}, then we have that
-\[
-\nor{u}_{L^2(\Omega)} \lesssim \nor{\boldsymbol U}_E
-\]
-\textbf{Main idea: the \textcolor{red}{test norm} should measure \textcolor{red}{adjoint solutions} robustly.}
-}
-
-\frame{
-\frametitle{Choice of inflow boundary condition}
-
-\begin{columns}
-\begin{column}{.49\textwidth}
-We impose the standard outflow wall boundary condition on $u$. For inflow boundary condition: 
-\begin{itemize}
-\item{} The standard choice of inflow boundary condition: $u = u_0$.
-\item{} We impose the non-standard inflow condition: $\widehat{f}_n \coloneqq \beta_n u - \sigma_n \approx \beta_n u_0$ on $\Gamma_{\rm in}$.
-\end{itemize}
-\end{column}
-
-\begin{column}{.49\textwidth}
-\begin{figure}
-\includegraphics[scale=.23]{figs/primal.png}
-\caption{Non-standard inflow.}
-\end{figure}
-\end{column}
-\end{columns}
-When $\sigma_n \approx 0$ near the inflow, condition on $\widehat{f}_n$ approximates condition on $u$.
-
-}
-
-\frame{
-\frametitle{Dirichlet inflow boundary condition}
-Standard choice of boundary condition: $u = u_0$ on inflow boundary $\Gamma_{\rm in}$, induces boundary layers in adjoint problems, \textcolor{red}{$\nor{\beta\cdot \grad v}_{L^2} = O(\epsilon^{-1})$}.
-\begin{figure}[h!]
-\centering
-\subfigure[Primal problem]{\includegraphics[scale=.23]{figs/primalDir.png}}
-\subfigure[Adjoint problem]{\includegraphics[scale=.23]{figs/adjointDir.png}}
-\caption{For the standard Dirichlet inflow condition, the solution to the adjoint problem can develop strong boundary layers at the outflow of the adjoint problem. }
-\end{figure}
-}
-
-\frame{
-\frametitle{New inflow boundary condition on $\widehat{f}_n$}
-Non-standard choice of boundary condition: $\widehat{f}_n = \beta_n u_0$ on $\Gamma_{\rm in}$, induces smoother adjoint problems, \textcolor{red}{$\nor{\beta\cdot \grad v}_{L^2} = O(1)$}.
-\begin{figure}[h!]
-\centering
-\subfigure[Primal problem]{\includegraphics[scale=.23]{figs/primal.png}}
-\subfigure[Adjoint problem]{\includegraphics[scale=.23]{figs/adjoint.png}}
-\caption{Under the new inflow condition, the wall-stop boundary condition is relaxed to a zero-stress condition at the outflow boundary of the adjoint problem.}
-\end{figure}
-}
-
-\frame{
-\frametitle{Test norms and adjoint solutions}
-\textbf{Intuition:} the effectiveness of DPG under a test norm is governed by how a \textbf{specific test norm} measures the \textbf{solutions of the adjoint problem}.
-
-\begin{figure}[!h]
-\centering
-\subfigure[Dirichlet inflow]{\includegraphics[scale=.35]{figs/dirichletBC.png}}
-\subfigure[``Convection'' inflow]{\includegraphics[scale=.35]{figs/newBC.png}}
-\caption{DPG solutions to convection-diffusion for both inflow conditions using an $H^1$ test norm.}
-\end{figure}
-}
-
-%\frame{
-%\frametitle{``Building blocks'' norm}
-%Test norm quantities are robustly bounded from above by $\nor{u}_{L^2(\Omega)}$.  
-%\[
-%\|\left(v,\tau\right)\|_{V,K}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2.
-%\]
-%Problem: boundary layers in optimal test functions:
-%\begin{figure}[!h]
-%\centering
-%\subfigure{\includegraphics[scale=.15]{figs/mesh1.png}}
-%\subfigure{\includegraphics[scale=.15]{figs/sol1.png}}
-%\caption{The $v$ component of the optimal test function corresponding to flux $\widehat{u} = x(1-x)$ on the bottom side of a unit element for $\epsilon = 0.01$.}
-%\label{fig:boundaryTest}
-%\end{figure}
-%}
-\frame{
-\frametitle{Adjoint estimates, or ``norm building blocks''}
-For solutions $(v,\tau)$ of the adjoint equations, the following quantities are robustly bounded from above by $\nor{u}_{L^2(\Omega)}$.  
-\begin{align*}
-&\|v\|, \sqrt{\epsilon} \|\grad v\|, \|\beta \cdot \grad v\| \\
-&\| \div \tau\|, \frac{1}{\sqrt{\epsilon}}\|\tau\|.
-\end{align*}
-We will construct a test norm through a combination of the above quantities, such that
-\begin{itemize}
-\item $v$ and $\tau$ decoupled (no systems).
-\item Coefficients are of equal order after transforming to the unit element (no boundary layers).
-\end{itemize}
-}
-\frame{
-\frametitle{Mesh-scaled test norms}
-Our test norm, as defined over a single element $K$, is now
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 +&\\
-\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2&.
-\end{align*}
-which induces the proven \emph{robust} bound\footnote{\bibentry{DPGrobustness2}}
-\[
-\nor{u}_{L^2(\Omega)}+ \nor{\sigma}_{L^2(\Omega)} + \epsilon\nor{\widehat{u}} + \sqrt{\epsilon} \nor{\widehat{f}_n} \lesssim \nor{\LRp{u,\sigma,\widehat{u},\widehat{f}_n}}_E.
-\]
-}
-
-\frame{
-\frametitle{Erikkson-Johnson model problem}
-
-On domain $\Omega = [0,1]^2$, with $\beta = (1,0)^T$, $ f = 0$ and boundary conditions
-\begin{align*}
-\widehat{\beta_nu - \sigma_n} &= \widehat{f}_n = u_0, \quad \beta_n \leq 0\\
-\widehat{u} &= 0, \quad \beta_n > 0
-\end{align*}
-
-%Separation of variables gives an analytic solution. 
-All numerical experiments done using Camellia codebase.\footnote{\bibentry{Camellia}}
-%\[
-%u(x,y) = C_0 + \sum_{n=1}^\infty C_n \frac{\exp(r_2(x-1)-\exp(r_1(x-1)))}{r_1\exp(-r2) - r_2\exp(-r1)}\cos(n\pi y)
-%\]
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale=.23]{figs/wallBC_exact_u.png}
-}
-\subfigure{
-\includegraphics[scale=.23]{figs/wallBC_exact_sigx.png}
-}
-\subfigure{
-\includegraphics[scale=.23]{figs/wallBC_exact_sigy.png}
-}
-\caption{Exact solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
-\end{figure}
-}
-
-\frame{
-\frametitle{Error rates}
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale=.33]{figs/errorrates_wallBC.png}
-}
-\subfigure{
-\includegraphics[scale=.33]{figs/L2energyratio_wallBC.png}
-}
-%\subfigure{
-%\includegraphics[scale=.22]{figs/u_pointdiff_wallBC.png}
-%}
-\caption{$L^2$/energy errors and their ratio for $\epsilon = .01, .001, .0001$.}
-\end{figure}
-}
-
-%\frame{
-%\frametitle{Regularization}
-%Discontinuous inflow conditions on $\widehat{f_n}$, out of alignment with mesh. Boundary condition $\epsilon \grad u \cdot n = 0$ at outflow.
-%\begin{figure}
-%\centering
-%\subfigure{
-%\includegraphics[scale=.33]{figs/discontinuous.png}
-%}
-%\subfigure{
-%\includegraphics[scale=.305]{figs/discontinuousL2rates.png}
-%}
-%\caption{Discontinuous hat inflow data with $\epsilon = 1e-5$, convection solution errors.}
-%\end{figure}
-%}
-\frame{
-\frametitle{Local conservation}
-Given stiffness matrix $K$, can introduce Lagrange multipliers to enforce element-wise constraints, leading to the saddle point problem
-\[
-\arr{K}{B}{B^T}{0}\vecttwo{u}{\lambda} = \vecttwo{f}{c}.
-\]
-where the Lagrange multipliers $\lambda$ can be locally condensed. We use the test norm
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,K}^2 = \left|\int_K v\right|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 +&\\
-\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2&.
-\end{align*}
-}
-
-\frame{
-\frametitle{Additional examples}
-\begin{figure}
-\centering
-\subfigure[Advection skew]{
-\includegraphics[scale = .175]{figs/Conservative/hughes.png}
-}
-\subfigure[Flow over a step]{
-\includegraphics[scale = .175]{figs/Conservative/step.png}
-}
-\subfigure[Double glazing]{
-\includegraphics[scale = .182]{figs/Conservative/doubleGlazing.png}
-}
-\end{figure}
-Locally conservative version of DPG performs very similarly to the standard DPG in all cases over a range of $\epsilon$. 
-}
-
-\frame{
-\frametitle{Regularization}
-For $\beta = (-y,x)^T$ on $\Omega = [-1,1]^2$. Ill posed in the convection setting. Similar tests have been done with discontinuous data.
-
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale=.21]{figs/vortex.png}
-}
-\subfigure{
-\includegraphics[scale=.2015]{figs/vortexMesh.png}
-}
-\caption{Steady vortex problem with $\epsilon = 1e-4$.}
-\end{figure}
-\vspace{-.25cm}
-}
-
-\frame{
-\frametitle{Current work - Hemker problem}
-
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale = .225]{figs/Conservative/Hemker/WithoutMesh.png}
-}
-\subfigure{
-\includegraphics[scale = .225]{figs/Conservative/Hemker/WithMesh.png}
-}
-\caption{Convection-diffusion solution to flow over a cylinder at $\epsilon = 1e-4$.}
-\end{figure}
-}
-\frame{
-\frametitle{Current work - high-lift airfoil}
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale = .1875]{figs/Conservative/Airfoil-Conservative-1E-3/solution.png}
-}
-\subfigure{
-\includegraphics[scale = .175]{figs/Conservative/Airfoil-Conservative-1E-3/mesh7.png}
-}
-\caption{Convection-diffusion solution over the high-lift airfoil, with advection at an angle, $\epsilon = 1e-3$, with $p=3$. Mesh is generated by \emph{Triangle}.}
-\end{figure}
-}
-
-\section{DPG for nonlinear problems}
-\frame{
-\frametitle{DPG for nonlinear problems}
-
-Given some linearization technique (typically Newton-Raphson and pseudo-timestepping linearization), we measure 
-\begin{itemize}
-\item size of the linearized update $\Delta u$
-\[
-\|\Delta u\|_E \coloneqq \nor{B_u\Delta u}_{V'} = \nor{R_V^{-1} B_u\Delta u}_V 
-\]
-\item the nonlinear residual 
-\[
-\nor{R(u)}_E \coloneqq \nor{B(u) - \ell}_{V'}  = \nor{R_V^{-1}\LRp{B(u)-\ell}}_V 
-\]
-\end{itemize}
-Preliminary experiments were done in 1D\footnote{\bibentry{DPGNS_1d}} and space-time.\footnote{\bibentry{DPGspacetime}}
-}
-
-\frame{
-\frametitle{2D test case: Burgers equation}
-\begin{columns}
-\begin{column}{.48\textwidth}
-\vspace{-.5cm}
-\[
-\pd{\left(u^2/2\right)}{x} + \pd{u}{y} + \epsilon \Delta u = f
-\]
-Burgers equation can be written with $\beta(u) = \LRp{u/2,1}$
-\begin{align*}
-\div\left(\beta(u)u-\sigma\right) &=f \\
-\frac{1}{\epsilon}\sigma - \grad u &=0.
-\end{align*}
-i.e.\ nonlinear convection-diffusion on domain $[0,1]^2$.
-\end{column}
-\begin{column}{.48\textwidth}
-\begin{figure}[!h]
-\centering
-\includegraphics[scale = .22]{figs/burgers.png}
-\caption{Shock solution for Burgers' equation, $\epsilon = 1e-4$, using Newton-Raphson.}
-\end{figure}
-\end{column}
-\end{columns}
-}
-\frame{
-Adaptivity begins with a cubic $4\times 4$ mesh.
-\begin{figure}[!h]
-\centering
-\subfigure{\includegraphics[scale=.2]{figs/burgersMesh.png}}
-\subfigure{\includegraphics[scale=.2]{figs/burgersZoom.png}}
-\caption{Adaptive mesh after 9 refinements, and zoom view at point (.5,.5) with shock formation and $1e-3$ width line for reference.}
-\end{figure}
-}
-
-\frame{
-\frametitle{2D Compressible Navier-Stokes equations (ideal gas)}
-Given density $\rho$, velocities $\mathbf{u} = \LRp{u_1,u_2}$ and temperature $T$,
-\begin{align*}
-\div \vecttwo{\rho u_1 }{\rho u_2} &= 0\\
-\div \left(\vecttwo{\rho u_1^2+p }{\rho u_1 u_2} - \boldsymbol \sigma_{1}\right) &=0\\
-\div \left(\vecttwo{\rho u_1 u_2}{\rho u_2^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
-\div \left(\vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2} - \boldsymbol\sigma \mathbf{u} + \vec{q}\right) &=0\\
-\frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I &= \grad \mathbf{u} - \Reyn \, \boldsymbol w\\
-\frac{1}{\kappa}\vec{q} &= \grad T
-\end{align*}
-}
-
-\frame{
-\frametitle{Stress law}
-$\boldsymbol\sigma$ for a Newtonian fluid: $\sigma_{ij} = \mu(u_{i,j} + u_{j,i}) + \lambda u_{k,k} \delta_{ij}$.
-%We can invert the stress tensor under isotropic and plane strain assumptions to get
-\[
-\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \frac{1}{2\mu} \sigma_{ij} - \frac{\lambda}{4\mu (\mu + \lambda)} \sigma_{kk}\delta_{ij}
-\]
-The symmetric part of the gradient is
-\[
-\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \grad  U - \boldsymbol w
-\]
-Our final form is
-\begin{align*}
-\grad  U - \boldsymbol w= \frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I.
-\end{align*}
-By enforcing strong symmetry of $\boldsymbol \sigma$, taking the antisymmetric part implicitly defines $\boldsymbol w$ to be the antisymmetric part of $\grad u$. 
-}
-
-\frame{
-\frametitle{Extrapolation of test norms}
-%\begin{columns}
-%\begin{column}{.48\textwidth}
-Convection-diffusion:
-\begin{align*}
-\div \left(\beta u - \sigma\right) &= f\\
-\frac{1}{\epsilon}\sigma - \grad u &= 0.
-\end{align*}
-Navier-Stokes: defining vector variables $U = \{\rho,u_1,u_2,T\}$ and $\Sigma = \{{\boldsymbol \sigma},\mathbf{q},w\}$,
-\begin{align*}
-\div \left(A_{\rm invisc}U - A_{\rm visc}\Sigma\right) &= R_{\rm conserv}(U,\Sigma)\\
-E_{\rm visc} \Sigma - \grad U &= R_{\rm constit}(U,\Sigma)
-\end{align*}
-where $R_{\rm conserv}(U,\Sigma)$ and $R_{\rm constit}(U,\Sigma)$ are the conservation/constitutive residuals.
-}
-
-\frame{
-\frametitle{Test norms over one element}
-Convection-diffusion:
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,K}^2 =& \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \|\beta \cdot \grad v\|^2 + \epsilon \|\grad v\|^2  \\
-&+\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
-\end{align*}
-
-Navier-Stokes: let $V$ and $W$ be vectors of test functions $v_i$ and $\tau_i$.
-\begin{align*}
-\|\left(V,W\right)\|_{V,K}^2 =& \min\left\{\frac{1}{\Reyn|K|},1\right\}\nor{V}^2  + \nor{A_{\rm invisc}^T \grad V}^2 + \frac{1}{\Reyn} \nor{A_{\rm visc}^T\grad V}^2 \\
-& + \nor{\div W}^2 + \min\left\{1,\frac{1}{\Reyn|K|}\right\}\nor{E_{\rm visc}^TW}^2.
-\end{align*}
-}
-
-\frame{
-\frametitle{Carter's flat plate problem}
-\begin{columns}
-\begin{column}{.49\textwidth}
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.32]{figs/flat_plate_BCs.pdf}
-\caption{Carter flat plate problem on domain $[0,2]\times[0,1]$. Plate begins at $x=1$, ${\rm Re} = 1000$.}
-\end{figure}
-\end{column}
-\begin{column}{.49\textwidth}
-\begin{enumerate}
-\item{} Symmetry boundary conditions.
-\item{} Prescribed temperature and wall stagnation conditions.
-\item{} Symmetry boundary conditions.
-\item{} Inflow: conserved quantities specified using far-field values.
-\item{} No outflow condition set.
-\end{enumerate}
-Stress/heat flux boundary conditions are set in terms of the momentum and energy fluxes. 
-\end{column}
-\end{columns}
-}
-
-\frame{
-\frametitle{Refinement level 0}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u0.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T0.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh0.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 1}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u1.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T1.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh1.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 2}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u2.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T2.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh2.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 3}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u3.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T3.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh3.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 4}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u4.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T4.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh4.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 5}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u5.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T5.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh5.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 6}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u6.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T6.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh6.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 7}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u7.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T7.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh7.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 8}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u8.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T8.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh8.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 9}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u9.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T9.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh9.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 10}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u10.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T10.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh10.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Zoomed solutions at plate/stagnation point}
-\begin{figure}
-\centering
-\subfigure[$\rho$]{\includegraphics[scale = .12]{figs/Re1000p2/rhoUnscaledzoom.png}}
-\subfigure[$u_1$]{\includegraphics[scale = .12]{figs/Re1000p2/u1zoom.png}}
-\subfigure[$u_2$]{\includegraphics[scale = .12]{figs/Re1000p2/u2zoom.png}}
-\subfigure[$T$]{\includegraphics[scale = .12]{figs/Re1000p2/Tzoom.png}}
-\subfigure[$q_n$]{\includegraphics[scale = .23]{figs/Re1000p2/heatflux.png}}
-\end{figure}
-}
-
-\section{Future work}
-%\subsection{Area A}
-%\frame{
-%\frametitle{Proposed work: Area A}
-%\begin{itemize}
-%\item{\textbf{Completed: Prove robustness of DPG method for the scalar convection-diffusion problem.}}
-%
-%We have introduced a test norm under which the DPG method robustly bounds the $L^2$ error in the field variables $u$ and the scaled stress $\sigma$.
-Numerical results confirm the theoretical bounds given.
-%
-%\item{\textbf{\textcolor{red}{Proposed}: Attempt analysis of the linearized Navier-Stokes system.}}
-%
-%We hope to analyze the linearized Navier-Stokes equations to determine an optimal extrapolation of the test norm for the scalar convection-diffusion problem to systems. 
-%
-%\end{itemize}
-%}
-
-%\subsection{Area B}
-%
-\frame{
-%\frametitle{Proposed work: Area B}
-%\item{\textbf{Completed: Collaborative work with Nathan Roberts on the higher order parallel adaptive DPG code Camellia.}}
-%
-%Numerical experiments use the higher-order adaptive codebase Camellia, built by Nathan Roberts upon the Trilinos library.
-%The framework for arbitrary-irregularity anisotropic refinements in both $h$ and $p$ is in place, and the code is partially parallelized.
-
-\frametitle{Future work: anisotropic refinements and $hp$-schemes.}
-
-The error representation function drives refinement effectively, and we hope to generalize its use to anisotropic adaptive schemes. 
-\begin{figure}
-\centering
-\subfigure{\includegraphics[scale = .175]{figs/anisotropy/b5.png}}
-\subfigure{\includegraphics[scale = .18]{figs/anisotropy/v6.png}}
-\caption{Anisotropic mesh for a convection-diffusion boundary layer.}
-\end{figure}
-}
-
-\frame{
-\frametitle{Future work: distributed iterative static condensation.}
-\[
-Ku = \arr{A}{B}{B^T}{D}\vecttwo{u_{\rm flux}}{u_{\rm field}} = \vecttwo{f}{g} = l
-\]
-where $D$ has a block-diagonal structure. The system can be reduced to yield the condensed system
-\[
-\left(A-B D^{-1} B^T\right)u_{\rm flux} = f - B D^{-1} g
-\]
-where $D^{-1}$ can be inverted block-wise.
-For FE stiffness matrices under the Laplace equation, the Schur complement has reduced condition number of $O(h^{-1})$ as opposed to $O(h^{-2})$.\footnote{\bibentry{schurComplement}}
-}
-
-\frame{  
-\frametitle{Future work: a Nonlinear Hessian-based DPG method.}
-Given a nonlinear variational problem $b(u,v) = \ell(v)$, linear in $v$ but not in $u$, beginning with the \textit{nonlinear} dual residual 
-\[
-J(u_h) = \frac{1}{2}\|B(u_h)-\ell\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(u_h,v)-\ell(v)|^2}{\nor{v}_V^2}.
-\]
-produces a Hessian-based DPG method, which solves
-\[
-b_u(\Delta u,v) + b''(\Delta u, \delta u, v_{R(u)}) = \ell(v) - b(u,v) = r(u,v),
-\]
-and aims to minimize the nonlinear dual residual instead of the linearized problem residual. 
-}
-
-\frame{
-\frametitle{Future work: applications}
-\begin{columns}
-\begin{column}{.48\textwidth}
-\begin{itemize}
-\item{{Solutions for all problems over a range of Reynolds/Mach numbers.}}
-\item{{Flow over a bump, Holden's ramp problem (shock-boundary layer interaction).}}
-\item{{Time permitting: airfoils, regularized Euler.}}
-\end{itemize}
-\end{column}
-\begin{column}{.5\textwidth}
-\begin{figure}
-\centering
-\includegraphics[scale = .275]{figs/ramp.png}
-\end{figure}
-\end{column}
-\end{columns}
-}
-
-\frame{
-\begin{center}
-Thank you!\\
-\vspace{1cm}
-Questions?
-\end{center}
-}
-
-\section{Extended slides}
-
-\frame{
-\frametitle{Extended literature review}
-\begin{itemize}
-\item Finite difference/volume methods, upwind stencils, monotonicity, ENO/WENO. 
-\item Artificial diffusion, flux limiters/discontinuity-capturing operators.
-\item DG fluxes can be interpreted as residual-based stabilizations similar to SUPG.\footnote{\bibentry{Brezzi20063293}}
-\item Hybridized DG (HDG) methods introduce independent unknowns for numerical traces. Fluxes are defined in terms of DG fluxes and the numerical trace.\footnote{\bibentry{hybridDG}}
-\end{itemize}
-}
-
-\frame{
-\frametitle{Specifics of the ultra-weak formulation}
 
@@
 \]
-If $u \in L^2\LRp{\Omega}$, the trace of $u$ is undefined, so we identify boundary terms $\LRa{\gamma\LRp{Au},v}_{\Gh} = \LRa{\widehat{u},v}_{\Gh}$ as unknowns $\widehat{u}$ on $\Gh$.
+We identify boundary terms $\LRa{\gamma\LRp{Au},v}_{\Gh} = \LRa{\widehat{u},v}_{\Gh}$ as unknowns $\widehat{u}$ on $\Gh$. This gives us the bilinear form.
+\begin{align*}
+b(\LRp{u,\uh},v) &\coloneqq  \LRa{\uh,v} + \LRp{u,A^*_hv}  \\
+l(v) &\coloneqq \LRp{f,v}
+\end{align*}
+%Let boundary conditions be applied on $\uh$ on $\Gamma_{\rm BC}$.  
+DPG approximates optimal test functions  $v_{\delta u}$ for all $\delta u\in U_h$ by solving on a local level
+\[
+\LRp{v_{\delta u},\delta v} = b(\delta u, \delta v), \quad \delta v\in V_h(K)
+\]
+
+}
+
+\frame{
+\frametitle{$L^2$ best approximations under the ultra-weak formulation}
+If our optimal test functions satisfy for all $\delta u_h \in U_h$ 
+\begin{align*}
+A^*v &= \delta u_h, \quad \text{on } \Omega
+%\gamma\LRp{A^*v} &= 0, \quad \text{on } \Gamma \setminus \Gamma_{\rm BC}  \\
+\end{align*}
+with boundary conditions on $v$ such that the boundary terms disappear, we get back the best $L^2$ approximation by virtue of 
+\begin{align*}
+b(\LRp{u_h,\uh_h},v) = \LRa{\uh_h,v} + \LRp{u_h,A^*v} &= \LRp{u_h,\delta u_h}\\
+\LRp{f,v} = b(\LRp{u,\uh},v) =  \LRa{\uh,v} + \LRp{u,A^*v} &= \LRp{u,\delta u_h}
+\end{align*}
+Corresponds to a graph norm choice of test norm: under assumptions of boundedness below of $B$, for $\delta > 0$, we can define as a DPG test norm
+\[
+\nor{v}_V \coloneqq \nor{A^*v}_{L^2} + \delta \nor{v}_{L^2}
+\]
+which, as $\delta \rightarrow 0$, gives an equivalent result.  
+}
+
+\frame{
+\frametitle{Globally optimal test functions}
+Recall that DPG optimal test functions are from a local inversion of the Riesz operator.  We can choose a \textcolor{red}{conforming} test space and invert the Riesz operator over the entire domain: 
+\begin{align*}
+V_{\rm global} &\coloneqq \{v\in \oplus V_K: \LRa{\uh_h, \jump{v}}_{\Gh^0}, \forall \uh_h \in \widehat{U}_h\} \\
+\LRp{v,\delta v}_{\Omega} &= b(u_h,\delta v), \quad v\in V_{\rm global}
+\end{align*}
+We refer to these as \textit{globally} optimal test functions.\footnote{Selecting these test functions removes internal traces from the big picture!}  The test space resulting from the local inversion of the Riesz operator is related to the \textit{globally} optimal test space through the following lemma:
+\begin{lemma}
+The globally optimal test space is contained in the locally optimal test space.  
+\end{lemma}
+}
+
+\frame{
+\frametitle{Optimal test functions for convection-diffusion}
 For convection-diffusion,
@@
 b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-\left( v, \tau \right)\right) = \left(u,\grad_h\cdot \tau - \beta \cdot \grad_h
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad_h v\right)_{\Oh}&\\
-  - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
+\left( v, \tau \right)\right) = &\left(u,\grad_h\cdot \tau - \beta \cdot \grad_h
+v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad_h v\right)_{\Oh}\\
+  &- \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh},
 \end{align*}
@@
 \end{align*}
-with the minimum energy extension norm on $\Gh$. We note that $H^{\pm 1/2}(\Gh)$ are \emph{closed} subspaces of $\prod_K H^{\pm 1/2}(\partial K)$. 
+The adjoint problem for $L^2$ best optimality under convection diffusion is
+\begin{align*}
+\left.
+\begin{array}{cl}
+\div\tau - \beta \cdot \grad v   &= u\\
+\frac{1}{\epsilon}\tau + \grad v &= 0
+\end{array}
+\right. ,
+\end{align*}
+with boundary condition $v = 0$ on $\Gamma$. \textcolor{red}{A boundary layer forms at the inflow.}
 }
@@
 \frame{
-\frametitle{Inviscid equations}
-Issue: consider pure convection, $\div \beta u = f$. The ultra-weak variational formulation is
-\[
-\LRa{\widehat{f}_n,v}-\LRp{u,\beta\cdot \grad v} = \LRp{f,v},
-\]
-where $\widehat{f}_n \coloneqq \beta_n u$.
-When $\beta_n = 0$, $v$ has only a streamline derivative, and $\widehat{f}_n$ becomes an ill-defined trace in the cross-stream direction.
-For hyperbolic \emph{systems}, this issue manifests as \emph{sonic lines}.
+\frametitle{The graph norm for convection-diffusion}
+The graph norm for convection diffusion forms boundary layers on each element, which are only resolvable using special subgrid meshes.  However, 
+\begin{enumerate}
+\item The globally optimal test functions only have boundary layers at the boundary
+\item The test functions for $L^2$ optimality only have boundary layers at the \textcolor{red}{inflow} boundary
+\end{enumerate}
+Question: do we need to resolve the boundary layers in optimal test functions everywhere?
+}
+\frame{
+\frametitle{Numerical experiment}
+\begin{itemize}
+\item Given the Erikkson-Johnson problem, we use the graph test norm and compute both energy and $L^2$ errors.  
+\item We then refine near the inflow and compare the energy and $L^2$ errors.  
+\end{itemize} 
+Best approximation error is small near the inflow, so changes in energy/$L^2$ error are due to resolution of test functions, not the solution.  
 \begin{figure}
 \centering
-\includegraphics[scale=.25]{figs/sonicLines.pdf}
-\caption{Sonic lines ($u_n - c = 0$) appear for linearized Euler.}
+\subfigure{\includegraphics[scale = .35]{figs/qoptInflowDirichlet.png}}
+\subfigure{\includegraphics[scale=.35]{figs/qoptInflowDirichletRatio.png}}
+%\caption{Energy error and total $L^2$ error and their ratios for different levels of resolution of the inflow layer.}
 \end{figure}
@@
 
-\bibliographystyle{plain}
-{\scriptsize
-\bibliography{CFD_intro,DPG_old,paper,LitRev,NSNotes}
+\frame{
+\frametitle{Distribution of error}
+We expect that the term $\nor{\div \tau - \beta \cdot \grad v}_{L^2}$ is bounded uniformly in $\epsilon$.
+However, the term $\nor{\frac{1}{\epsilon}\tau - \grad v}_{L^2}$ is not.\footnote{Analytical calculations in 1D show that this term grows with the Peclet number in the element at the inflow, where the adjoint solution develops a boundary layer.}
+
+As the boundedness of this term determines the robustness of $\sigma$, our energy norm is
+\begin{align*}
+\nor{\boldsymbol U}_E &\coloneqq \sup_{\LRp{v,\tau}}\LRp{\frac{\LRp{u,\Grad_h \cdot \tau - \beta \cdot \Grad_h v}_{\Omega}}{\nor{\LRp{v,\tau}}_V} + \frac{\LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad_h v}_{\Omega}}{\nor{\LRp{v,\tau}}_V}} + \text{etc} \\
+&\approx \nor{u}_{L^2} + C_{\text{Pe}}\nor{\sigma}_{L^2} + \nor{\LRp{\uh,\fnh}}
+\end{align*}
+where $\text{Pe}$ is the element Peclet number near the inflow.  
+%For the quasi-optimal test norm, underresolution of the inflow boundary layer negatively affects only the robustness of $u$. 
+}
+
+\frame{
+\frametitle{Three levels of test functions}
+\begin{itemize}
+\item $L^2$ optimal test functions resulting from a global adjoint problem,
+\item Global test functions resulting from a global Riesz inversion,
+\item Local test functions resulting from local Riesz inversions.
+\end{itemize}
+
+Thoughts:
+\begin{itemize}
+\item The complete local resolution of test functions may not be necessary
+\item You can have optimal test functions with boundary layers even when there are none in the global adjoint: resolution of these on a global level may still be necessary to maintain robustness.
+\end{itemize}
+
 }

### 2012-11-26 docs/Truman/LocalConservation/paper.tex
Added Local Conservation paper.

\documentclass[letterpaper]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{authblk}

\title{Locally Conservative Discontinuous Petrov-Galerkin Finite Elements for
Fluid Problems}
\author{Truman Ellis} 
\author{Leszek Demkowicz}
\author{Jesse Chan}
\affil{Institute for Computational Engineering and Sciences,\\
The University of Texas at Austin, \\
Austin, TX 78712}
\date{}

\begin{document}
\maketitle

\begin{abstract}
\end{abstract}

\section{Intoduction}
Verteeg and Malalasekera, in \emph{An Introduction to Computational Fluid
Dynamics: The Finite Volume Method}\cite[p. 110-113]{IntroCFD} cite three
characteristics that they consider essential to any numerical discretization
of convection-diffusion type problems: conservativeness, boundedness, and
transportiveness.

Perot\cite{Perot2011} argues
\begin{quote}
Accuracy, stability, and consistency are the mathematical concepts that are
typically used to analyze numerical methods for partial differential equations
(PDEs). These important tools quantify how well the mathematics of a PDE is
represented, but they fail to say anything about how well the physics of the
system is represented by a particular numerical method. In practice, physical
fidelity of a numerical solution can be just as important (perhaps even more
important to a physicist) as these more traditional mathematical concepts. A
numerical solution that violates the underlying physics (destroying mass or
entropy, for example) is in many respects just as flawed as an unstable
solution.
\end{quote}

The discontinuous Petrov-Galerkin finite element method has been described as
least squares finite elements with a twist. The key difference is that least
square methods seek to minimize the residual of the solution in some Hilbert
space norm, while DPG seeks the minimization in a dual norm through the
inverse Riesz map. Exact mass conservation has been an issue that has plagued
least squares finite elements for a long time. Several approaches have been
used to try to adress this. Chang and Nelson\cite{ChangNelson1997} developed
the 'restricted LSFEM'\cite{ChangNelson1997} be augmenting the least squares
equations with a Lagrange multiplier explicitly enforcing mass conservation
element-wise. Our conservative formulation of DPG takes a similar approach and
both methods share similar negative of transforming a minimization method to a
saddle-point problem.

The discontinuous Petrov-Galerkin finite element method has shown a lot of
promise for convection-diffusion type problems including robustness in the
face of singularly perturbed problems.

\section{DPG is a Minimum Residual Method}

\bibliographystyle{plain}
\bibliography{../DPG}
\end{document}

### 2012-11-27 docs/Truman/LocalConservation/paper.tex
Finished brief theory stuff in writeup.

@@
 \usepackage{authblk}
+\usepackage{amsmath, amssymb, amsthm, mathtools}
+\usepackage{graphicx}
+\usepackage{subfigure}
+
+\newcommand{\bs}[1]{\boldsymbol{#1}}
+\DeclareMathOperator{\diag}{diag}
+\DeclareMathOperator*{\argmin}{\arg\,\min}
+
+\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}
+
+\newcommand{\tablab}[1]{\label{tab:#1}}
+\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
+
+\newcommand{\theolab}[1]{\label{theo:#1}}
+\newcommand{\theoref}[1]{\ref{theo:#1}}
+\newcommand{\eqnlab}[1]{\label{eq:#1}}
+\newcommand{\eqnref}[1]{\eqref{eq:#1}}
+\newcommand{\seclab}[1]{\label{sec:#1}}
+\newcommand{\secref}[1]{\ref{sec:#1}}
+\newcommand{\lemlab}[1]{\label{lem:#1}}
+\newcommand{\lemref}[1]{\ref{lem:#1}}
+
+\newcommand{\mb}[1]{\mathbf{#1}}
+\newcommand{\mbb}[1]{\mathbb{#1}}
+\newcommand{\mc}[1]{\mathcal{#1}}
+\newcommand{\nor}[1]{\left\| #1 \right\|}
+\newcommand{\snor}[1]{\left| #1 \right|}
+\newcommand{\LRp}[1]{\left( #1 \right)}
+\newcommand{\LRs}[1]{\left[ #1 \right]}
+\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
+\newcommand{\LRc}[1]{\left\{ #1 \right\}}
+\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
+\newcommand{\Grad} {\ensuremath{\nabla}}
+\newcommand{\Div} {\ensuremath{\nabla\cdot}}
+\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
+\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
+\newcommand{\uh}{\widehat{u}}
+\newcommand{\fnh}{\widehat{f}_n}
+\renewcommand{\L}{L^2\LRp{\Omega}}
+\newcommand{\pO}{\partial\Omega}
+\newcommand{\Gh}{\Gamma_h}
+\newcommand{\Gm}{\Gamma_{-}}
+\newcommand{\Gp}{\Gamma_{+}}
+\newcommand{\Go}{\Gamma_0}
+\newcommand{\Oh}{\Omega_h}
+
+\newcommand{\eval}[2][\right]{\relax
+  \ifx#1\right\relax \left.\fi#2#1\rvert}
+
+\def\etal{{\it et al.~}}
+
+\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
+\newcommand{\tensor}[1]{\underline{\vect{#1}}}
+\newcommand{\del}{\Delta}
+\newcommand{\grad}{\nabla}
+\newcommand{\curl}{\grad \times}
+\renewcommand{\div}{\grad \cdot}
+\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
+\newcommand{\eip}[1]{a\left( #1 \right)}
+\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
+\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
+
+\newcommand{\circone}{\ding{192}}
+\newcommand{\circtwo}{\ding{193}}
+\newcommand{\circthree}{\ding{194}}
+\newcommand{\circfour}{\ding{195}}
+\newcommand{\circfive}{\ding{196}}
+
+\def\arr#1#2#3#4{\left[
+\begin{array}{cc}
+#1 & #2\\
+#3 & #4\\
+\end{array}
+\right]}
+\def\vecttwo#1#2{\left[
+\begin{array}{c}
+#1\\
+#2\\
+\end{array}
+\right]}
+\def\vectthree#1#2#3{\left[
+\begin{array}{c}
+#1\\
+#2\\
+#3\\
+\end{array}
+\right]}
+\def\vectfour#1#2#3#4{\left[
+\begin{array}{c}
+#1\\
+#2\\
+#3\\
+#4\\
+\end{array}
+\right]}
+
+\newtheorem{proposition}{Proposition}
+\newtheorem{corollary}{Corollary}
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
+
+\newcommand{\G} {\Gamma}
+\newcommand{\Gin} {\Gamma_{in}}
+\newcommand{\Gout} {\Gamma_{out}}
 
@@
 \section{DPG is a Minimum Residual Method}
+We now proceed with a abstract derivation of the standard Discontinuous
+Petrov-Galerkin method. Suppose we have two Hilbert spaces, $U$ and $V$, the
+trial and test spaces, respectively. And suppose we are trying to solve a
+well-posed variational problem $b(u,v)=l(v)$. We can rewrite this in operator
+form $Bu=l$, where $B:U\rightarrow V'$, where $V'$ is the dual space to $V$.
+Then, for a discrete subspace $U_h\subset U$, we seek to find $u_h\in U_h$
+that minimizes the error residual:
+\begin{equation}
+u_h=\argmin_{u_h\in U_h}\frac{1}{2}\nor{Bu_h-l}^2_{V'}\,.
+\label{minresidual}
+\end{equation}
+Recalling that the Riesz operator $R_V:V\rightarrow V'$ is an isometry defined
+by
+\[
+\LRa{R_Vv,\delta v}=\LRp{v,\delta v}_V,\quad\forall\delta v\in V,
+\]
+we can use the Riesz inverse to minimize on $V$ rather than its dual:
+\begin{equation}
+\frac{1}{2}\nor{Bu_h-l}^2_{V'}=\frac{1}{2}\nor{R_V^{-1}(Bu_h-l)}_V
+=\frac{1}{2}\LRp{R_V^{-1}(Bu_h-l),R_V^{-1}(Bu_h-l)}_V\,.
+\label{eq:rieszapplied}
+\end{equation}
+The first order optimality condition for \eqnref{rieszapplied} requires
+the G\^ateaux derivative to be zero in all directions $\delta u \in
+U_h$, i.e.,
+\[
+\left(R_V^{-1}(Bu_h-l),R_V^{-1}B\delta u\right)_V = 0, \quad \forall \delta u \in U. 
+\]
+By definition of the Riesz operator, this is equivalent to
+\begin{equation}
+\LRa{Bu_h-l,R_V^{-1}B\delta u_h}=0\quad\forall\delta u_h\in U_h\,.
+\label{eq:DPGbilinearform}
+\end{equation}
+Now, we can identify $v_{\delta u_h}\coloneqq R_V^{-1}B\delta u_h$ as the
+optimal test function for trial function $u_h$ and we can rewrite
+\eqnref{DPGbilinearform} as
+\begin{equation}
+b(u_h,v_{\delta u_h})=l(v_{\delta u_h}).
+\label{eq:DPGmethod}
+\end{equation}
+The DPG method then is to solve \eqnref{DPGmethod} with optimal test functions
+$v_{\delta u_h}\in V$ that solve the auxiliary problem
+\begin{equation}
+\LRp{v_{\delta u_h},\delta v}_V=\LRa{R_Vv_{\delta u_h},\delta v}
+=\LRa{B\delta u_h,\delta v}=b(\delta u_h,\delta v)\,,\quad\forall\delta v\in V.
+\label{eq:optimaltestproblem}
+\end{equation}
+Using a continuous test basis would result in a global solve for every optimal
+test function. Therefore DPG uses a discontinuous test basis which makes each
+solve element-local and much more computationally tractable. Of course,
+\eqnref{optimaltestproblem} still requires the inversion of the
+infinite-dimensional Riesz map, but in approximating the $V$ by finite
+dimensional $V_h$ which is of a higher polynomial degree than $U_h$ (hence
+``enriched space'') works well in practice.
+
+No assumptions have been made so far on the definition of the inner product on
+$V$. In fact, proper choice of $\LRp{\cdot,\cdot}_V$ can make the difference
+between a solid DPG method and one that suffers from robustness issues.
+
+\section{DPG Applied to Convection-Diffusion}
+Now that we have briefly outline the abstract DPG method, let us put it into
+practice with the Convection-Diffusion equation. The strong form of the
+steady Convection-Diffusion equation reads
+\[
+\div(\bs\beta u)-\epsilon\del u=g\,,
+\]
+where $u$ is the property of interest, $\bs\beta$ is the convection vector,
+and $g$ is the source term. Let us write this as an equivalent system of first
+order equations:
+\begin{align*}
+\div(\bs\beta u-\bs\sigma)&=g\\
+\frac{1}{\epsilon}\bs\sigma-\grad u&=\bs0\,.
+\end{align*}
 

### 2012-11-28 docs/Truman/LocalConservation/paper.tex
Finished derivation of convection diffusion.

@@
 \usepackage{subfigure}
+
+\def\btau{\boldsymbol\tau}
+\def\bsigma{\boldsymbol\sigma}
+\def\bbeta{\boldsymbol\beta}
+\def\blambda{\boldsymbol\lambda}
 
@@
 \end{align*}
+If we then multiply the top equation by some scalar test function $v$ and the
+bottom equation by some vector-valued test function $\tau$, we can integrate by
+parts over each element $K$:
+\begin{equation}
+\label{eq:preultraweak}
+\begin{aligned}
+-(\bbeta u-\bsigma,\nabla v)_K+((\bbeta
+u-\bsigma)\cdot\mathbf{n},v)_{\partial K}&=(g,v)_K\\
+\frac{1}{\epsilon}(\bsigma,\btau)_K+(u,\nabla\cdot\btau)_K
+-(u,\tau_n)_{\partial K}&=0\,.
+\end{aligned}
+\end{equation}
+The discontinuous Petrov-Galerkin method refers to the fact that we are using
+discontinuous optimal test functions that come from a space differing from the
+trial space. It does not specify our choice of trial space. Nevertheless, many
+considerations of DPG in the literature \cite{} associate DPG with the
+so-called ``ultra-weak formulation.'' We will follow the same derivation for
+the convection-diffusion equation, but we emphasize that other formulations
+are available. Thus, we seek field variables $u\in L^2(K)$ and
+$\bsigma\in\mb{L^2}(K)$. Mathematically, this leaves their traces on element
+boundaries undefined, and in a manner similar to the hybridized discontinuous
+Galerkin method, we define new unknowns for trace $\hat u$ and flux $\hat f$.
+Applying these definitions to \eqnref{preultraweak} and adding the two
+equations together, we arrive at our desired bilinear form,
+\begin{equation}
+\label{eq:confusionBF}
+-(\bbeta u-\bsigma,\nabla v)_K+(\hat f,v)_{\partial K}
++ \frac{1}{\epsilon}(\bsigma,\btau)_K
++(u,\nabla\cdot\btau)_K
+-(\hat u,\tau_n)_{\partial K}=(g,v)_K\,.
+\end{equation}
+% Function Spaces
+
+Within each element, we perform a Bubnov-Galerkin solve for the optimal test
+functions. %Problem description
+As mentioned earlier the choice of test norm on $V$ can have profound
+influence on the robustness of our method.
 

### 2012-11-29 docs/Truman/LocalConservation/paper.tex
Finished basic theory stuff.

@@
 \newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\nor}[1]{\left\| #1 \right\|}
-\newcommand{\snor}[1]{\left| #1 \right|}
+\newcommand{\norm}[1]{\left\| #1 \right\|}
+\newcommand{\snorm}[1]{\left| #1 \right|}
 \newcommand{\LRp}[1]{\left( #1 \right)}
@@
 \begin{equation}
-u_h=\argmin_{u_h\in U_h}\frac{1}{2}\nor{Bu_h-l}^2_{V'}\,.
+u_h=\argmin_{u_h\in U_h}\frac{1}{2}\norm{Bu_h-l}^2_{V'}\,.
 \label{minresidual}
@@
 \begin{equation}
-\frac{1}{2}\nor{Bu_h-l}^2_{V'}=\frac{1}{2}\nor{R_V^{-1}(Bu_h-l)}_V
+\frac{1}{2}\norm{Bu_h-l}^2_{V'}=\frac{1}{2}\norm{R_V^{-1}(Bu_h-l)}^2_V
 =\frac{1}{2}\LRp{R_V^{-1}(Bu_h-l),R_V^{-1}(Bu_h-l)}_V\,.
@@
 \end{equation}
-% Function Spaces
+A cursory look at \eqnref{confusionBF} tells us which function spaces to look
+in for each variable:
+\[
+\begin{array}{lll}
+u\in L^2(K) \quad& \hat u\in H^1(K)|_{\partial K} \quad& v\in H^1(K)\\
+\bsigma\in \mathbf{L}^2(K) \quad& \hat f\in \bs{H}(\mb{div},K)|_{\partial K} \quad& \btau\in H(div,K)\,.\\
+\end{array}
+\]
 
+%TODO: Define broken Sobolev spaces
+All that is left to pin down this problem is a definition of our test norm so
+we can invert the Riesz operator and calculate our optimal test functions.
 Within each element, we perform a Bubnov-Galerkin solve for the optimal test
-functions. %Problem description
+functions. Define finite-dimensional subspaces
+$\mb{U}_h\subset\mb{U}:=L^2(\Omega_h)\times\mb{L}^2(\Omega_h)\times
+H^{1/2}(\Gamma_h)\times H^{-1/2}(\Gamma_h)$ the trial space and 
+$\mb{V}_h\subset\mb{V}:=H^1(\Omega_h)\times H(div,\Omega_h)$ the ``enriched''
+test space.
+For each $\mathbf{u}=\{u,\bsigma,\hat u,\hat f\}\in\mathbf{U}_h$, find
+$\mathbf{v}_{\mathbf{u}}=\{v_\mathbf{u},\btau_\mathbf{u}\}\in\mathbf{V_h}$ such that
+\[
+(\mathbf{v_u},\mathbf{w})_\mathbf{V}=b(\mathbf{u},\mathbf{w})\quad\forall\mathbf{w}\in\mathbf{V}
+\]
 As mentioned earlier the choice of test norm on $V$ can have profound
-influence on the robustness of our method.
+influence on the robustness of our method. Unfortunately, the structure of the
+optimal test norm makes it non-localizable. For many problems, it suffices to
+use the so-call quasi-optimal test norm which is based on the adjoint of the
+$B$ operator, but for convection-diffusion type equations, the adjoint
+develops boundary layers which make solving for the optimal test functions
+much more difficult for small diffusion. In an earlier consideration of DPG
+for convection-diffusion problems, Chan \etal developed the more robust
+test norm\cite{ChanHeuerThanhDemkowicz2012}, 
+\begin{equation}
+\label{eq:robustNorm}
+\norm{(v,\btau)}^2_{\mathbf{V},\Omega_h}=
+\norm{\nabla\cdot\btau}^2+\norm{\min\left\{\frac{1}{\sqrt{\epsilon}},\frac{1}{\sqrt{|K|}}\right\}\btau}^2
++\epsilon\norm{\nabla v}^2+\norm{\bbeta\cdot\nabla v}^2
++\norm{\min\left\{\sqrt{\frac{\epsilon}{|K|}},1\right\}v^2}\,.
+\end{equation}
+Unfortunately, this test norm also has a few issues. For one, some of the
+assumptions that went into its development break down as the flow field
+degenerates to zero. In such cases the final $L^2$ term on $v$ can register
+higher error levels and trigger unnecessary refinements in smooth regions, see
+ref{}.
+%TODO: have Jesse write about this
+
+\section{Locally Conservative Formulation}
+A simple control volume analysis will tell us that a locally conservative
+method must enforce that
+\begin{equation}
+\int_{\partial K}\hat f=\int_K g\,,\quad\forall K\in\Omega_h\,,
+\label{eq:localconservation}
+\end{equation}
+which is equivalent to having the set
+$\mathbf{v}_K:=\{v,\btau\}=\{1_K,\boldsymbol0\}$ for $K=1,\dots,N$ ($N$ is the
+number of mesh elements)
+in the test space, where each $1_K$ has value one on element $K$ and zero
+elsewhere.  In fact, if we insert this test function into
+\eqnref{confusionBF}, all of the $\tau$ and $\grad v$ terms vanish and we are
+left exactly with this condition.
+Numerical experiments imply that local conservation occurs in one dimension,
+but the standard DPG method is not exactly locally conservative for higher
+dimensional problems.
+
+Following Moro \etal\cite{MoroNguyenPeraire11}, we can explicitly augment our
+test space with constants through the use of Lagrange multipliers. Going back
+to \eqnref{rieszapplied}, we can define our Lagrange function,
+\begin{equation}
+\label{eq:lagrangian}
+L(u_h,\blambda) = \frac{1}{2}\norm{R_V^{-1}(Bu_h-l)}_V^2
+-\sum_K\lambda_K\underbrace{\langle Bu_h-l,\mathbf{v}_K\rangle}_
+{\langle\hat f, 1_K\rangle_{\partial K}-\langle g,1_K\rangle_K}\,,
+\end{equation}
+where $\blambda=\{\lambda_1,\cdots,\lambda_N\}$.
+We then proceed as before and find the critical points of \eqnref{lagrangian},
+\begin{equation}
+\label{eq:modifiedBF}
+\frac{\partial L(u_h,\blambda)}{\partial u_h}=b(u_h,R_V^{-1}B\delta u_h)
+-l(R_V^{-1}B\delta u_h)
+-\sum_K\lambda_K b(\delta
+u_h,\mathbf{v}_K)=0\,,\quad\forall\delta u_h\in U_h
+\end{equation}
+\begin{equation}
+\label{eq:constraint}
+\frac{\partial
+L(u_h,\blambda)}{\partial\lambda_K}=-b(u_h,\mathbf{v}_K)+l(\mathbf{v}_K)=0\,,\quad\forall
+K\,.
+\end{equation}
+Equation \eqnref{modifiedBF} is just \eqnref{DPGmethod} with the extra
+Lagrange terms. As usual, the second equation just enforces the constraint. As
+a consequence, we now explicitly have constants in our test space and should
+enforce local conservation to machine precision. The negative side is that we
+have added an additional unknown associated with every mesh element and turned
+our well-behaved minimization into a saddle point problem.
+
+This change has further consequences to how we compute our optimal test
+functions. Since constants are now explicitly represented in the test space,
+we only need to search for optimal test functions in the orthogonal complement
+of constants. The final term in \eqnref{robustNorm} is somewhat troublesome,
+but becomes unnecessary when solving in the orthogonal complement of
+constants. Instead, we can replace it with a much nicer zero mean term. Thus,
+\eqnref{robustNorm} becomes
+\begin{equation}
+\norm{(v,\btau)}^2_{\mathbf{V},\Omega_h}=
+\norm{\nabla\cdot\btau}^2+\norm{\min\left\{\frac{1}{\sqrt{\epsilon}},\frac{1}{\sqrt{|K|}}\right\}\btau}^2\\
++\epsilon\norm{\nabla v}^2+\norm{\bbeta\cdot\nabla
+v}^2+\left(\int_Kv\right)^2\,.
+\end{equation}
 

### 2012-12-04 docs/Jesse/GlobalLocalTesting/paper.tex

@@
 \newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
-\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
+\newcommand{\jump}[1] {\ensuremath{\LRs{\!\left[#1\right]\!}}}
 \newcommand{\uh}{\widehat{u}}
@@
 
-\author{Jesse Chan\textsuperscript{a}, Norbert Heuer\textsuperscript{b}, Tan Bui-Thanh\textsuperscript{a}, and Leszek Demkowicz\textsuperscript{a}}
+\newtheorem{remark}{Remark}
+
+\author{Jesse Chan\textsuperscript{a}, Jay Gopalakrishnan\textsuperscript{b}, and Leszek Demkowicz\textsuperscript{a}}
 
 %\title{$\epsilon$-explicit analysis of DPG for convection-dominated diffusion}
-\title{Globally and locally optimal test functions}
+\title{Global effects in locally optimal DPG test functions for convection-diffusion problems}
 \date{}
@@
 
-%\tableofcontents
 \maketitle
@@
 \begin{center}
-\textsuperscript{b} Facultad de Matem\'aticas, \\Pontificia Universidad Cat\'olica de Chile,\\
-Avenida Vicu\~na Mackenna 4860, Santiago, Chile
+\textsuperscript{b} Department of Mathematics\\Portland State University, \\
+Portland, OR 97207, USA
+%\textsuperscript{b} Facultad de Matem\'aticas, \\Pontificia Universidad Cat\'olica de Chile,\\
+%Avenida Vicu\~na Mackenna 4860, Santiago, Chile
 \end{center}
 
-\section{The ultra-weak variational formulation}
+\tableofcontents
+
+\section{Introduction to DPG}
+
+The Discontinuous Petrov-Galerkin method was originally introduced by Demkowicz and Gopalakrishnan in 2008 method as a way to attain automatic inf-sup stability for any well-posed variational problem through the construction optimal test functions \cite{DPG2}.
+The method was later shown to be equivalent to the minimum residual method applied to the operator residual corresponding to a variational formulation \cite{DPG2, ChanHeuerBui-ThanhDemkowicz12}.
+
+The derivation of the DPG method can be briefly summarized as follows: we are given a trial space $U$ and discrete trial space $U_h \subset U$, Hilbert test space $V$, and a well-posed variational problem: find $u_h\in U_h$  such that
+\begin{align}
+\label{variational}
+&b(u_h,v) = l(v), \quad \forall v\in V, 
+\end{align}
+where $b(u,v)$ is a bilinear form and $l \in V'$.
+If we identify the variational operator $B: U\rightarrow V'$ such that $\LRa{Bu,v} \coloneqq b(u,v)$, we can write the above variational formulation as an operator equation in $V'$
+\[
+Bu_h = l.
+\]
+Seeking the minimization of the discrete residual $\frac{1}{2} \nor{Bu_h-l}^2_{V'}$, we arrive at the normal equations 
+\[
+\LRp{Bu_h-l,B\delta u}_{V'} = 0, \quad \forall \delta u \in U_h.  
+\]
+Since $V$ is Hilbert, we can introduce the Riesz map $R_V:V \rightarrow V'$, an isometric map such that $\LRa{R_V v,\cdot} = \LRp{v,\cdot}_V$.
+By taking the inverse of the Riesz map, we can transform the normal equations in $V'$ to a set of normal equations in $V$
+\[
+\LRp{R_V^{-1}\LRp{Bu_h-l},R_V^{-1}\LRp{B\delta u}}_{V} = 0, \quad \forall \delta u \in U_h.  
+\]
+Using the definitions of the Riesz map $R_V$ and variational operator $B$, we have that
+\begin{align*}
+\LRp{R_V^{-1}\LRp{Bu_h-l},R_V^{-1}\LRp{B\delta u}}_{V} = 0, \quad \forall \delta u \in U_h \\
+\rightarrow \LRa{Bu_h-l,R_V^{-1}\LRp{B\delta u}}_{V} = 0, \quad \forall \delta u \in U_h \\
+\rightarrow b\LRp{u_h,R_V^{-1} B\delta u} - l\LRp{R_V^{-1} B\delta u} = 0, \quad \forall \delta u \in U_h.
+\end{align*}
+In other words, the minimization of the operator residual associated with a given variational form corresponds directly to a Petrov-Galerkin formulation, where test functions are determined under the so-called \textit{trial-to-test} operator $R_V^{-1}B$, which, given functions in the discrete trial space $U_h$,  returns back corresponding test functions which span the discrete test space.
+
+Solutions $u$ to the above problem enjoy the following properties: 
+\begin{enumerate}
+\item If we define the energy norm 
+\[
+\nor{u}_E = \nor{Bu}_{V'} = \sup_{v\in V\setminus\{0\}}\frac{b(u,v)}{\nor{v}_V},
+\]
+then DPG is optimal in $\nor{u}_E$.  This norm is induced through the energy inner product
+\[
+\LRp{v,w}_E = \LRp{Bv,Bw}_{V'} = \LRp{R_V^{-1}Bv, R_V^{-1}Bw}_V.
+\]
+\item The exact energy error $\nor{u-u_h}_E$ is computable without knowing $u$ explicitly, owing to the fact that
+\[
+\nor{u-u_h}_E = \nor{B(u-u_h)}_{V'} = \nor{l-Bu_h}_{V'} = \sup_{v\in V\setminus\{0\}}\frac{l(v)-b(u,v)}{\nor{v}_V},
+\]
+which can be computed as $\nor{e}_V$, where the \textit{error representation function} $e$ is determined as the solution to 
+\[
+\LRp{e,\delta v}_V = l(\delta v)-b(u,\delta v), \quad \delta v\in V.
+\]
+This property is simply a result of the minimum residual nature of DPG; the energy error is simply the residual, measured in the proper norm. 
+\item Let $\{u_i\}_{i = 0}^{i = N}$ be discrete trial functions and $v_{u_i}$ be the corresponding optimal test functions (solutions of Problem (\ref{aux})).
+The discrete system resulting from DPG is symmetric positive-definite; this can be seen from the identity
+\[
+b(u_i,v_{u_j}) = \LRp{v_{u_i},v_{u_j}}_V = \LRp{v_{u_j},v_{u_i}}_V = b(u_j,v_{u_i}).
+\]
+Positive-definiteness is again a natural consequence of the minimum-residual nature of DPG.  
+\end{enumerate}
+
+\subsection{Broken test spaces}
+
+In practice, it can be very difficult computationally to determine a set of optimal test functions.
+The inverse of the Riesz map $R_V^{-1} B\delta u$ can be computed by solving the auxiliary variational problem
+\begin{equation}
+\label{aux}
+(v,\delta v)_V = b\LRp{\delta u,\delta v}, \quad \forall \delta v\in V.  
+\end{equation}
+However, for a conforming discretization, this amounts to a global problem.
+For example, if $V = H^1(\Omega)$ and $\LRp{\cdot, \cdot }_V$ corresponded to the $H^1$ Sobolev inner product  $\LRp{v,\delta v}_{L^2(\Omega)} + \LRp{\grad v,\grad \delta v}_{L^2(\Omega)}$, solving for a single optimal test function would be computationally equivalent to the solution of the Poisson equation over the entire domain.
+However, we can alleviate this issue by choosing for $V$ a \textit{broken} test space.
+
+We begin by assuming we are given some triangulation $\Omega_h$ of $\Omega$ such that $\Omega = \bigoplus_{K\in \Omega_h}K$.  We can adopt for $V$ the broken test space
+\[
+V(\Oh) = \bigoplus_{K\in \Omega_h}V(K).
+\]
+If we further assume that the inner product and norm on $V$ are localizable\footnote{A localizable norm $\nor{v}_{V(\Oh)}$ can be written in the form 
+$$\nor{v}_{V(\Oh)} = \sum_{K\in\Oh} \nor{v}_{V(K)},$$ where $\nor{v}_{V(K)}$ is a norm over the element $K$.}, the solution to \eqref{aux} (corresponding to the inversion of the Riesz map) can now be determined locally on each element.
+In practice, these solutions are approximated by solving (\ref{aux}) over a locally conforming space $V_h$ over each element $K$, where $\dim(V_h) > \dim(U_h)$ elementwise.
+Typically, if $U_h$ is of order $p$, $V_h$ is chosen to be the corresponding $H^1$ or $H({\rm div})$ conforming space of order $p + \del p$, where $\del p \geq n$, the spatial dimension \cite{practicalDPG}.
+For this reason, we refer to $V_h$ as the \textit{enriched} space.
+We refer to this approximated test space under $V_h$ as the approximate optimal test space $V_{{\rm opt},h}$.
+\begin{remark}
+All properties of DPG carry over if $V=V_h$, the discrete inner product space, and if Problem~(\ref{aux}) is well-approximated under $V_h$, then the solution to our variational problem (\ref{variational}) over the approximate optimal test space will deliver very similar results to the solution of (\ref{variational}) over the exact optimal test space.
+\end{remark}
+
+\subsection{The ultra-weak variational formulation}
+
+Up to now, we've left our specific variational formulation unspecified.
+For several reasons, we've chosen to use the \textit{ultra-weak formulation}, which results from writing the PDE as a first-order system, integrating all derivatives by parts, and identifying boundary traces as independent unknowns.
+The formulation is given as follows: let $$\Gh = \bigcup_{K\in \Oh} \partial K$$ be the \textit{mesh skeleton}, comprising of the union of all element boundaries.
+Let $Au=f$ represents the strong form of a first-order system of PDEs; the ultra-weak formulation is then
+\begin{equation}
+\label{variationalProblem}
+b\LRp{\LRp{u,\uh},v} = \LRp{u,A_h^*v}_{\Oh} + \sum_{K \in \Oh} \LRa{\uh,v}_{\partial K} = \LRp{f,v}_{\Omega},
+\end{equation}
+where $u \in L^2{\Omega}$, and $\uh \in \gamma(D(A))$, the trace space of the domain of the strong operator $A$.
+$A_h^*$ is the formal adjoint of $A$ acting elementwise on a broken test space, and $\LRa{\uh,v}_{\partial K}$ is the duality pairing between the trace unknown $\uh$ and the trace of the test function $v$ on an element boundary.
+Under proper regularity assumptions, we have that
+$$\sum_{K \in \Oh} \LRa{\uh,v}_{\partial K} = \LRa{\uh,\jump{v}}_{\Gh}.$$
+
+Combining this variational formulation with the concept of DPG optimal test functions yields a conforming method for $u$, the field variable, and $\uh$, the trace variable.
+Optimal test functions are all determined locally, and optimal test functions corresponding to traces defined on the element boundary $\partial K$ have support over each element adjacent to $\partial K$.
+The degrees of freedom are thus coupled together globally through the optimal test functions for trace variables.
+
+\begin{remark}
+\label{remarkDahmen}
+It is possible to apply the same minimum-residual method behind DPG in an alternative fashion by casting the normal equations as a saddle-point problem, which is the approach taken by Dahmen et al.\ in \cite{DahmenVariationalStabilization}.
+This method requires the solution of a larger linear system than the DPG method, but can be directly applied to arbitrary variational formulations and conforming discretizations of $V$.
+\end{remark}
+
+\subsection{The graph test norm}
+
+Up to now, the inner product $\LRp{v,\delta v}_V$ (which induces a norm on $V$) has not been specified.
+Here, we derive two important ``canonical" test norms for the ultra-weak variational formulation.
+We begin first with the canonical norm in $U$.
+Since $\uh \in \gamma\LRp{D\LRp{A}}$, the standard norm for $\uh$ is the so-called minimum energy extension norm defined as
+\begin{equation*}
+\|\widehat{u}\| = \inf_{w\in D\LRp{A},
+  \left.w\right|_{\Gh}=\widehat{u}} \|w\|_{D\LRp{A}}.
+\end{equation*}
+The canonical norm for the group variable $\LRp{u,\uh}$ is then given by
+\[
+\|\left(u,\widehat{u}\right)\|_U^2 = \|u\|^2_{\L} + \|\widehat{u}\|^2.
+\]
+It has been shown in \cite{Bui-ThanhDemkowiczGhattas11a, ChanHeuerBui-ThanhDemkowicz12} that the canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ induces (generates) the norm $\nor{v}_{V,U}$ in $V$.
+
+The canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ provides an optimal balance between the standard norms on the field $u$ and the flux $\uh$ \cite{DPG4}.
+As a result, if the induced norm $\nor{v}_{V,U}$ (namely, the optimal test norm) is used to compute optimal test functions in (\ref{aux}), the finite element error in the canonical norm is the best in the norm $\nor{u}_{U}$.
+Unfortunately, the optimal test norm is non-localizable due to the presence of the jump term $\jump{v}$.
+Since the jump terms couple elements together, the evaluation of the jump terms requires contributions from all the elements in the mesh.
+Consequently, solving for an optimal test function amounts to inverting the Riesz map over the entire mesh $\Oh$, making the optimal test norm impractical.
+
+On the other hand, since $v \in D\LRp{A^*_h}$, we can use as a test norm for $v$ the broken graph test norm: 
+\[
+\nor{v}_V^2 =  \|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2.
+\]
+This norm is a localization of $\nor{v}_{V,U}$ to allow for the solution of optimal test functions on an element-by-element basis, and can be considered to be the canonical norm on $V$.
+In the DPG literature \cite{DPG4}, $\nor{v}_{V,U}$ is known as the {\em optimal test norm}, while $\nor{v}_{V}$ is known as the quasi-optimal or {\em graph} test norm.
+The DPG method was first shown to be well-posed under the graph test norm for the Poisson and convection-diffusion equations in \cite{analysisDPG}.
+This analysis was later extended to the large class of Friedrichs' systems in \cite{Bui-ThanhDemkowiczGhattas11b}.
+%Using variants of the quasi-optimal test norm, near-optimal results have also been obtained in the context of elasticity \cite{DPGElas} and the linear Stokes equations \cite{stokesDPG}.
+Numerical results also suggest that the DPG method may provide a ``pollution-free" method without phase error for the Helmholtz equation \cite{DPG4}.
+
+\section{Globally conforming optimal test functions}
+
+Though DPG test functions are determined locally, on an element-by-element basis, it is the global properties of the test space that determine the performance of the method.
+We motivate this statement first by deriving global conditions for the test space under which the ultra-weak variational formulation recovers an $L^2$ optimal solution.
 
@@
 
-Assuming boundedness below of $A$, as the extra $L^2$ term disappears, we get $L^2$ optimality. The ultra-weak variational form gives
+Under the ultra-weak formulation, all boundary conditions are treated as natural boundary conditions.
+For boundary data $\uh_0$ enforced on $\Gamma_0 \subset \Gamma$, our corresponding variational formulation is
+\begin{equation*}
+b\LRp{\LRp{u,\uh},v} = \LRp{u,A_h^*v}_{\Omega} + \LRa{\uh,\jump{v}}_{\Gh \setminus \Gamma_0} = \LRp{f,v}_{\Omega} - \LRa{\widehat{u}_0,v}_{\Gamma_0}.
+\end{equation*}
+Suppose now that our test functions come from a \textit{conforming} space - in other words, that
+\[
+%\LRa{\uh,\jump{v}}_{\Gh^0} = 0, \quad \forall \uh \in \gamma(D(A))
+\LRa{\uh,\jump{v}}_{\Gh\setminus \Gamma_0} = 0, \quad \forall \uh \in \gamma(D(A))
+\]
+%is satisfied over the internal skeleton $\Gh^0 \coloneqq \Gh\setminus\Gamma$.  
+is satisfied over $\Gh\setminus \Gamma_0$.  
+In this case, the inter-element boundary terms vanish, $A^*_h v$ becomes $A^*v$, and the variational formulation becomes
 \begin{align*}
-b(u_h,v) = \LRp{u_h,A^*v} + \LRa{\widehat{u},v} = \text{load and boundary conds} = b(u,A^*v)
+%b\LRp{\LRp{u,\uh},v} = \LRp{u,A^*v}_{\Omega} + \LRa{\uh,\jump{v}}_{\Gamma \setminus \Gamma_0} = \LRp{f,v}_{\Omega} - \LRa{\widehat{u}_0,\jump{v}}_{\Gamma_0}.
+b\LRp{\LRp{u,\uh},v} = \LRp{u,A^*v}_{\Omega} = \LRp{f,v}_{\Omega} - \LRa{\widehat{u}_0,\jump{v}}_{\Gamma_0}.
 \end{align*}
-If we use for our test functions solutions of the adjoint equation $A^*v = u$ (with appropriate adjoint boundary conditions), $u_h$ is the best $L^2$ projection of the exact solution $u$ onto $U_h$.
+Let $\bar{V} = \{\bar{v}\in V: \LRa{\uh,\jump{\bar{v}}}_{\Gh\setminus\Gamma_0} = 0, \forall \LRp{0,\uh}\in U\}$ be the conforming subspace of $V$.
+If we seek $u_h \in U_h$ and if our discrete test space is chosen to be
+\[
+\bar{V}_{\rm opt} = \{\bar{v}_{\delta u} \in \bar{V}: A^*\bar{v}_{\delta u} = \delta u, \forall \delta u \in U_h\},
+\]
+%\[
+%\bar{V}_{\rm opt} = \{\bar{v}_{\delta u} \in \bar{V}: \delta u \in U_h\},
+%\]
+%where each test function $v_{\delta u}$ satisfies the following adjoint equation 
+%\begin{align*}
+%A^*v_{\delta u} &= \delta u, \\
+%\left.v_{\delta u}\right |_{\Gamma\setminus\Gamma_0} &= 0,
+%\end{align*}
+then our variational problem reduces to
+\[
+\LRp{u_h,\delta u}_{\Omega} = \LRp{f,v}_{\Omega} = \LRp{u,\delta u}_{\Omega}, \quad \forall \delta u \in U_h
+\]
+and the solution $u_h$ is the $L^2$ projection of the exact solution $u$ onto $U_h$.
 
-\section{Test norms for the convection-diffusion problem}
+\subsection{Globally conforming DPG test spaces}
 
-Introduce the graph norm here.
+As noted above, $L^2$ optimality is achieved when the test space possesses certain \textit{global} properties.
+An obvious question concerning DPG is how much non-local information can be gleaned from locally generated test spaces.\footnote{Global properties of the test norm are related to the adjoint equation, as shown in \cite{DPGrobustness, ChanHeuerBui-ThanhDemkowicz12}.
+However, global properties of the test space have not been explored specifically in these prior works.}
 
-\subsection{Local and global optimal test functions}
+First, we define the idea of \textit{weakly} conforming spaces.  For discrete trial variables $\LRp{u,\uh} \in U_h$, we denote a test function as weakly conforming if
+\[
+b\LRp{\LRp{0,\uh},v} = \LRa{\uh,\jump{v}}_{\Gh\setminus \Gamma_0} = 0, \quad \forall \LRp{0,\uh} \in U_h.
+\]
+In other words, a test function is weakly conforming if its inter-element jumps are orthogonal to all trace functions in the discrete space $U_h$.
+We refer to the space of these test functions as $\tilde{V} = \{\tilde{v}\in V: \LRa{\uh,\jump{\tilde{v}}}_{\Gh\setminus\Gamma_0} = 0, \forall \LRp{0,\uh_h}\in U_h\}$.
 
-Note that globally optimal test functions only produce boundary layers at the global inflow boundary.
+Let $V_{\rm opt} = \{v_{\delta u} \in V: v_{\delta u}= R_V^{-1}B\delta u, \delta u \in U_h\}$ be the space of locally determined DPG test functions, and let 
+\[
+\tilde{V}_{\rm opt} = \{\tilde{v}_{\delta u} \in \tilde{V}: \tilde{v}_{\delta u} = R_{V}^{-1}B\delta u, \delta u \in U_h\}
+\]
+be the space of optimal test functions determined \textit{globally} over the weakly conforming space $\tilde{V}$.
+In other words, the optimal test functions that span $\tilde{V}_{\rm opt}$ are the result of the inversion of the Riesz operator \textit{globally}, over the entire mesh (the idea is not new - the concept of globally optimal test functions was first introduced in \cite{DPG3pub} to prove mesh-independence).
+We have the following lemma concerning the test space spanned by the locally computed optimal test functions of DPG:
+\begin{lemma}
+\label{lemma1}
+$\tilde{V}_{\rm opt} \subseteq V_{\rm opt}$.
+\end{lemma}
+\begin{proof}
+We note first that, because $V_{\rm opt} \subseteq V$, we can orthogonally decompose $V = V_{\rm opt} \bigoplus V_{\rm opt}^\perp$, where, for any $v_{\rm opt}\in V_{\rm opt}$, $\LRp{v_{\rm opt},v^\perp}_V = 0$ for all $v^\perp \in V_{\rm opt}^\perp$.
+Let us now choose a globally conforming test function $\tilde{v}\in \tilde{V}_{\rm opt}$.
+Since $\tilde{V}_{\rm opt} \subseteq V$, we can decompose $\tilde{v} = v_{\rm opt} + v_{\rm opt}^\perp$.
+Demonstrating that $v_{\rm opt}^\perp = 0$ proves the lemma.
 
-Show representation of global test functions in local test functions using Jay's proof using orthogonal subspaces and flux test functions.
+Let $v_{\uh} \in V_{\rm opt}$ be an optimal test function corresponding to the flux variable $\uh$.
+We can use the fact that $v_{\rm opt}^\perp \in V$ to substitute it into the definition of $v_{\uh}$.
+By definition,
+\[
+\LRp{v_{\uh},v_{\rm opt}^\perp}_{V(K)} = \LRa{\uh,v_{\rm opt}^\perp}_{\partial K} = 0,
+\]
+where $\LRp{\cdot,\cdot}_{V(K)}$ denotes an element-wise inner product, and $\LRa{\cdot,\cdot}_{\partial K}$ denotes the duality pairing between $\uh$ and $v$ over the boundary $\partial K$.
+Summing up over all $K$, we have
+\[
+\LRp{v_{\uh},v_{\rm opt}^\perp}_{V(\Oh)} = \LRa{\uh,\jump{v_{\rm opt}^\perp}}_{\Gh} = 0,
+\]
+Thus, we can conclude that $v_{\rm opt}^\perp \in \tilde{V}$ is weakly conforming.
+Then, by definition of the weakly conforming optimal test space $\tilde{V}_{\rm opt}$, for a conforming optimal test function $\tilde{v}_u$ corresponding to a field variable $u$, we have that
+\[
+\LRp{\tilde{v}_u,v_{\rm opt}^\perp}_{V(\Oh)} = \LRp{u,A^*_h v_{\rm opt}^\perp}_{L^2(\Omega)} = \LRp{v_u, v_{\rm opt}^\perp}_{V(K)} = \LRp{v_u, v_{\rm opt}^\perp}_{V(\Oh)} = 0,
+\]
+where $v_u$ is a non-conforming locally determined test function.  The above orthogonality conditions imply that, for the globally conforming test space $\tilde{V}_{\rm opt}$, 
+\[
+0 = \LRp{\tilde{v},v_{\rm opt}^\perp}_V = \LRp{v_{\rm opt} + v_{\rm opt}^\perp,v_{\rm opt}^\perp}_V = \LRp{v_{\rm opt}^\perp,v_{\rm opt}^\perp}_V = \nor{v_{\rm opt}^\perp}_V^2.
+\]
+\end{proof}
+
+We note that Lemma~\ref{lemma1} still holds in the case where optimal test functions spanning $V_{\rm opt}$ are approximated using $V_h$, the enriched space, so long as $V_h$ is a closed subspace of $V$.
+In other words, the space of globally optimal test functions approximated using a weakly conforming enriched space $\tilde{V}_h$ is contained within the approximate optimal test space $V_{{\rm opt},h}$.
+
+Lemma~\ref{lemma1} has an immediate consequence concerning DPG solutions under weakly conforming test spaces: 
+\begin{lemma}
+\label{remark1}
+Let $\tilde{u}$ be the field component of the DPG solution under a weakly globally conforming optimal test space, and let $u$ be the field component of the standard DPG solution.
+Assuming both problems are uniquely solvable, $u = \tilde{u}$.
+\end{lemma}
+\begin{proof}
+This can be shown by taking the variational problem (\ref{variational}) for $u$ and $\widehat{u}$; since $\tilde{V}_{\rm opt} \subseteq V_{\rm opt}$, we can substitute in for $v$ the weakly conforming optimal test functions spanning $\tilde{V}_{\rm opt}$.
+Doing so reduces (\ref{variational}) to the problem for $\tilde{u}$.
+\end{proof}
+
+\subsection{The graph test norm and globally optimal test functions}
+
+The concept of $L^2$ optimal test functions is connected to DPG through a variant of the graph test norm; if we take for our test norm on $V$
+\[
+\nor{v}_V^2 = \nor{A_h^*v}_{L^2{\Omega}}^2 + \delta \nor{v}_{L^2{\Omega}}^2,
+\]
+and assume boundedness below of the bilinear operator $B$ (see \cite{DPG4} for details), $\nor{v}_V$ remains a norm in the limit as $\delta \rightarrow 0$.
+In this limit, the auxiliary problem \eqref{aux} for optimal test functions corresponding to the field variable $u$ reduces to
+\[
+\LRp{A^*_h v_u, A^*_h \delta v}_{V(K)} = \LRp{u,A^*_h \delta v}_{L^2(K)}, \quad \forall \delta v \in V(K).
+\]
+Recalling Lemma \ref{lemma1}, this implies that weakly conforming optimal test functions satisfy
+\[
+\LRp{A^*_h v_u, A^*_h \delta v}_{V(\Omega)} = \LRp{u,A^*_h \delta v}_{L^2(\Omega)}, \quad \forall \delta v \in V(\Omega),
+\]
+which yields a weakly conforming test subspace that can be characterized as
+\[
+\tilde{V}_{\rm opt} = \{\tilde{v}_{\delta u} \in \tilde{V}: A^*_h \tilde{v}_{\delta u} = {\delta u}, {\delta u} \in U_h\}.
+\]
+In other words, the DPG test space in the limit as $\delta \rightarrow 0$ contains a weakly conforming approximation to the $L^2$-optimal test space $\bar{V}_{\rm opt}$.
+The approximation is due to the fact that strong conformity is not guaranteed; let $\LRp{u,\uh}$ and $\LRp{u_h,\uh_h}$ be the exact and approximate solutions respectively to the variational problem \eqref{variationalProblem} with $V = \tilde{V}_{\rm opt}$.
+We then have globally that
+\[
+b\LRp{\LRp{u-u_h,\uh-\uh_h},\tilde{v}} = \LRp{u-u_h,A^*_h \tilde{v}}_{\Omega} + \LRa{\uh-\uh_h,\jump{\tilde{v}}}_{\Gh} = 0, \quad \forall \tilde{v}\in \tilde{V}_{\rm opt}.
+\]
+If the exact flux $\uh$ is exactly representable by the approximate flux $\uh_h$, we have that 
+\[
+\LRp{u_h-u,\delta u}_{\Oh} = 0
+\]
+for all $\delta u \in U_h$, which we recognize as the condition under which the approximate solution $u_h$ is indeed the best-$L^2$ approximation of the true solution $u$ in $U_h$.
+
+%\textcolor{red}{Flesh this out in more detail - where does the approximation of jump terms come in?
+I.e.
+the proper norm in which to measure flux error is the minimum energy extension norm, but this introduces derivatives, which should introduce a $\epsilon^{-1}$ factor into the norm!
+Why is this not observed for convection-diffusion?!?}
+
+\section{The convection-diffusion problem}
+
+The weakly conforming properties of DPG test spaces proven in Lemma~\ref{lemma1} motivate the question whether the global nature of DPG can be exploited to develop a more efficient method.
+We discuss one particular application of this to the convection-diffusion problem for convection-dominated regimes.
+
+The convection-diffusion problem models the concentration $u$ of some solvent in a convection field $\beta$ subject to diffusion of some magnitude $\epsilon$.  We decompose the boundary as follows:
+\begin{align*}
+\Gamma_{\rm in} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\}, \quad {\rm
+(inflow)}\\ 
+\Gamma_{\rm out} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\},
+\quad {\rm (outflow)}\\
+\Gamma_{0} &\coloneqq \{x\in \Gamma;\beta_n(x) = 0\},
+\end{align*}
+where $\beta_n \coloneqq \beta \cdot n$.
+
+The problem is typically written in second-order form as
+\begin{align*}
+\div\LRp{\beta u - \epsilon \grad u} &= f\\
+u &= u_{0}, \quad \text{on } \Gamma.
+\end{align*}
+The problem is especially of interest as a prototypical problem for boundary layer problems in computational fluid dynamics, as solutions to the convection-diffusion problem can, for certain boundary conditions, develop strong boundary layers of width $\epsilon$ at the outflow boundary $\Gamma_{\rm out}$.
+
+\subsection{The graph test norm for the convection-diffusion problem}
+
+We begin first with the canonical norm for DPG, the graph test norm.  Under the ultra-weak variational formulation, the graph test norm for convection-diffusion is
+\[
+\nor{v}_{V_{\rm graph}}^2 = \nor{\div\tau - \beta \cdot \grad v}_{L^2(\Omega)}^2 + \nor{{\epsilon}^{-1} \tau -  \grad v}_{L^2(\Omega)}^2 + \nor{v}_{L^2(\Omega)}^2
+\]
+where the $L^2$ norm of $\tau$ is neglected as it is not required to preserve positive-definiteness of the norm, and $\grad$ and $\div$ are understood to act elementwise.
+
+Introduce the graph test norm here, as well as alternative test norms and problems of robustness \cite{DPGrobustness}, Denote norms as 
+\begin{itemize}
+\item $\nor{\cdot}_{V_{\rm graph}}$
+\item $\nor{\cdot}_{V_{\rm weight}}$ ??
+\end{itemize}
+
+\subsection{Localization and boundary layers under the graph test norm}
+
+The graph test norm typically delivers near-optimal results - for problems of wave propagation, elasticity, and Stokes flow, DPG under the graph test norm delivers solutions nearly indistinguishable from the $L^2$ projections of the exact solution \cite{DPG4, DPGElas, stokesDPG}.
+However, when applied to the convection-diffusion problem, the graph test norm performed very poorly.
+
+It was determined that the optimal test functions generated under the graph test norm developed strong boundary layers of width $\epsilon$.
+Figure~\ref{fig:optTestBoundary} shows the result of 2D numerical experiments\footnote{All figures of optimal test functions are produced using the FEniCS codebase \cite{LoggMardalEtAl2012a}.} where a fine mesh was used to resolve an optimal test function resulting from (\ref{aux}), demonstrating the presence of strong boundary layers at the element inflow boundary $\partial K_{\rm in}$.
+
+\begin{figure}[!h]
+\centering
+\subfigure[$v$]{\includegraphics[width=5cm]{figs/u_graph_v_K.pdf}}
+\subfigure[$\tau_x$]{\includegraphics[width=5cm]{figs/u_graph_tau_x_K.pdf}}
+\subfigure[$\tau_y$]{\includegraphics[width=5cm]{figs/u_graph_tau_y_K.pdf}}
+\caption{$v$ and $\tau$ components of the 2D optimal test functions corresponding to the basis function $u=1$ on the reference element for $\epsilon = 0.01$.
+The solution has been obtained using a fine $128\times128$ mesh of triangles, with $p = 3$.
+}
+\label{fig:optTestBoundary}
+\end{figure}
+
+Under the graph norm for convection-diffusion, Problem~(\ref{aux}) over a single element is given as
+\begin{align*}
+\LRp{\LRp{v,\tau},\LRp{\delta v,\delta \tau}}_{V_{\rm graph}(K)} &= \LRp{u, \Grad_h\cdot \tau - \beta\cdot \Grad_h v}_{K} + \LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad_h v}_{(K)} \\
+&+ \LRa{\uh,\tau_n}_{\partial K} + \LRa{\fnh,v}_{\partial K}
+\end{align*}
+where $\LRp{\LRp{v,\tau},\LRp{\delta v,\delta \tau}}_{V_{\rm graph}(K)}$ is 
+\begin{align*}
+\LRp{\LRp{v,\tau},\LRp{\delta v,\delta \tau}}_{V_{\rm graph}(K)} =& \LRp{\div\tau - \beta \cdot \grad v,\div\delta \tau - \beta \cdot \grad \delta v}_{L^2(K)} \\
+&+ \LRp{{\epsilon}^{-1} \tau -  \grad v,{\epsilon}^{-1} \delta \tau -  \grad \delta v}_{L^2(K)} + \LRp{v,\delta v}_{L^2(K)} 
+\end{align*}
+
+We can transform the above problem to the reference element.
+Applying this simple scaling argument shows that, for elements of size $h$, we can expect a boundary layer of width $h/\epsilon$ relative to a unit domain.\footnote{This is assuming that the parameter $\epsilon$ dictates the width of expected boundary layers on a unit domain.
+The strong form of the above variational problem corresponds to a reaction-diffusion system, for which we expect this assumption to hold.
+Numerical experiments also appear to confirm that the boundary layer is of width $O(\epsilon)$.}  In other words, the strength of the boundary layer is proportional to the element Peclet number ${\rm Pe} = h/\epsilon$.
+For severely underresolved meshes where $h \gg \epsilon$, this makes the approximation of optimal test functions using a simple $p$-enriched space very difficult, though subgrid meshes have been used to resolve such test functions with some success in \cite{DBLP:journals/procedia/NiemiCC11}.
+The construction of the alternative test norm $\nor{\cdot}_{V_{\rm weight}}$ was motivated by the computational difficulty in applying the graph test norm to heavily convection-dominated regimes where $\epsilon \ll 1$.
+
+Consider now globally optimal test functions under the test norm, where Problem~(\ref{aux}) is solved using the weakly conforming space $\tilde{V}$.
+By the same scaling argument, strong boundary layers appear, but only at the global inflow boundary $\Gamma_{\rm in}$.
+We illustrate this in Figure~\ref{fig:optTestBoundaryGlobal}, where we use an $H^1\times H({\rm div})$-conforming finite element space to approximate the globally conforming test function.
+We note that, by approximating optimal test functions using a conforming test space, our test functions no longer produce boundary layers over every single element.
+However, in return, our optimal test functions now contain non-local information - in particular, boundary layers at the domain inflow boundary $\Gamma_{\rm in}$.
+\begin{figure}[!h]
+\centering
+\subfigure[$v$]{\includegraphics[width=5cm]{figs/u_graph_v.pdf}}
+\subfigure[$\tau_x$]{\includegraphics[width=5cm]{figs/u_graph_tau_x.pdf}}
+\subfigure[$\tau_y$]{\includegraphics[width=5cm]{figs/u_graph_tau_y.pdf}}
+\caption{$v$ and $\tau$ components of the 2D optimal test functions corresponding to the piecewise constant $u=1$ with support on a quad element defined on $[.5,.7]\times[.4,.6]$ for $\epsilon = 0.01$.
+Note the presence of nonlocal behavior in the form of the boundary layer at the inflow boundary.}
+\label{fig:optTestBoundaryGlobal}
+\end{figure}
+One key fact that we can exploit is that, under DPG with the ultra-weak variational formulation, our locally determined test space naturally contains non-local information as well.
+By Lemma~\ref{lemma1}, we know that the globally (weakly) conforming optimal test space is contained within our locally determined optimal test space; by Lemma~\ref{remark1}, we have that the DPG solutions under local and conforming optimal test spaces coincide up to $L^2$ field variables.
+In other words, the approximation of the field solution $u$ is solely determined by the approximation of globally optimal test functions by the weakly conforming space enriched space $\tilde{V}_h$.
+
+%\section{Comparison to Variational Multiscale Methods}
+%
+%Question for John: do the VMS fine-scale Green's functions in \cite{HughesVMS} have boundary layers?
+Can the adjoint be backed out explicitly from the fine scale greens function through the projectors?
+%
+%Answer: the adjoint equation is 
+%
+%Remark: localization is exact (no need for approximation over patches), but the global test space is still approximated through the fluxes coupling elements together (a non-conforming DG method).
+
+\subsection{Interpretation of DPG as a non-conforming method over $V$}
+
+Recall that the motivation behind DPG is the minimization of the dual residual $\nor{Bu-l}_{V'}$, which leads to the dual normal equations
+\begin{equation}
+\label{dualNormal}
+\LRp{l-Bu,B\delta u}_{V'} = 0.
+\end{equation}
+Note that the above pairing is taken through the inner product on the dual space $V'$.
+Since $V'$ is also Hilbert, this inner product exists, but may not have a explicit closed form, and is not readily accessible for computation.
+The DPG method proceeds from here by using the Riesz operator to pose the dual normal equations in the inner product on $V$.
+
+As mentioned in Remark~\ref{remarkDahmen}, work by Dahmen et al.\ in \cite{DahmenVariationalStabilization} uses the same functional setting as DPG; however, their starting point is to view the above problem into a saddle point system.
+Defining the error $e = R_V^{-1}\LRp{l-Bu} \in V'$, Problem (\ref{dualNormal}) can be written as follows: solve for $\LRp{e,u_h}$ such that
+\begin{align*}
+\LRp{e,\delta v}_V + b(u_h,\delta v)&= l(\delta v),\quad \delta v \in V\\
+b(\delta u, e) &= 0, \quad \delta u \in U_h
+\end{align*}
+The first equation defines the error representation function $e$ as the Riesz inversion of the residual; the second equation defines orthogonality of the error in the energy inner product 
+\[
+\begin{dcases}
+b(\delta u, e) = 0\\
+\forall \delta u \in U_h 
+\end{dcases}
+\Longleftrightarrow \LRa{R_V^{-1}\LRp{l-Bu},B\delta u}_{V\times V'} = 0 \Longleftrightarrow \LRp{R_V^{-1}{B\LRp{u-u_h}},R_V^{-1}B\delta u}_{V}= 0,
+\]
+where the last condition is exactly the orthogonality of error $\LRp{B\LRp{u-u_h},B\delta u}_{V'}= 0$ with respect to the dual inner product.
+
+If we use for $b(u,v)$ the ultra-weak variational formulation and use for $\LRp{\cdot,\cdot}_V$ a localizable inner product, we recover the DPG method.
+Under this saddle-point formulation, DPG takes the form
+\begin{align*}
+\LRp{e,\delta v}_{V(K)} + \LRp{u_h,A^*_h\delta v}_{L^2{\Omega}} + \LRa{\uh_h,v}_{\Gh}- l(\delta v) &= 0, \quad \delta v \in V(K),\,\, \quad \forall K\in \Oh\\
+\LRp{\delta u, A_h^*e}_{L^2(K)} &= 0, \quad \LRp{\delta u,0} \in U_h, \quad \forall K\in \Oh\\
+\LRa{\widehat{\delta u}, \jump{e}}_{\Gh} &= 0, \quad \LRp{0,\widehat{\delta u}} \in U_h
+\end{align*}
+If $\widehat{\delta u}$ comes from the space of polynomials of order $p$, then the above problem can be interpreted as a non-conforming DG method for $e$, where elements are coupled together by enforcing that inter-element jumps of the error representation $\jump{e}$ are orthogonal with respect to all polynomials up to order $p$ defined on the element edge.
+It may be worth noting that, under this perspective, the performance of DPG relies on accurate approximation of both the solution and error simultaneously, and the choice of energy setting for the error representation function $e \in V$ has been determined through the energy setting for the trial space $U_h$.
 
@@
 
-\subsection{The effect of under-resolved boundary layers}
+\subsection{Robustness}
+The difficulty encountered by most numerical and finite element methods for boundary layer solutions of convection-diffusion problems is a lack of \textit{robustness} in the diffusion parameter $\epsilon$; in other words, for a fixed resolution/number of degrees of freedom, as $\epsilon$ decreases, the finite element error degrades with respect to the best approximation error.
+This can be seen in typical error bounds for finite element methods; if finite element error is appropriately measured in some norm $\nor{\cdot}_U$, then
+\[
+\frac{\nor{u-u_h}_U}{\inf_{w_h\in U_h}\nor{u-w_h}_U} = O(\epsilon^{-1}).
+\]
+Under naive finite elements, which relies on the coercivity of the bilinear form to provide stability, the dependence of the above ratio on $\epsilon$ can be connected to the discrete coercivity constant, which (for appropriate assumptions on boundary conditions and $\beta$) is $O(\epsilon)$ with respect to the $H^1$ norm or seminorm \cite{roos2008robust}.\footnote{These assumptions can be relaxed in the presence of a first order term \cite{stynesSUPG}.}
+
+%This degeneration of the typically manifests itself as oscillatory behavior, which can be observed in the application of the naive finite element method to the convection-dominated diffusion equation.
+This issue can be slightly alleviated through the use of Shishkin meshes which anticipate the presence of boundary layers.
+However, the most popular method of restoring finite element stability in the convection-dominated regime has been the Streamline Upwind Petrov-Galerkin (SUPG) method, which adds a precise amount of residual-based artificial diffusion in the streamline direction.
+Under the modified SUPG bilinear form, coercivity can be restored with respect to a new norm, though not all provable error estimates converge at an optimal rate \cite{stynesSUPG}.
+Despite its name, the SUPG method is not formally a Petrov-Galerkin method (in that the method can be derived starting from a-priori, but can be interpreted as locally modifying the test space over each element to restore coercivity).
+By limiting the amount of streamline diffusion added, discrete inf-sup stability can also be proven with respect to the streamline diffusion norm.
+
+%The DPG method approaches the problem of stabilization differently; by construction, the method is discretely inf-sup stable with respect to a test norm and an induced energy norm on the trial space $U$.
+However, the norms with which inf-sup stability can be shown may depend on $\epsilon$ and generate poor approximations in our desired norm when $\epsilon \ll 1$.
+We discuss here several choices for the DPG test norm that yield a method that is robust in $\epsilon$.
+
+Under exact solutions for optimal test functions under the graph test norm, we expect the DPG method to be robust in $\epsilon$.  Non-robustness can be attributed then to approximation error.
+
+\subsection{Robustness of the graph norm}
+
+To confirm our theoretical results, we adopt a modification of a problem first proposed by Eriksson and Johnson in \cite{Eriksson1993}.
+For the choice of $\Omega = (0,1)^2$, $f=0$, and $\beta = (1,0)^T$, the convection diffusion equation reduces to
+\[
+\pd{u}{x} - \epsilon \left(\pdd{u}{x}+ \pdd{u}{y}\right) = 0,
+\]
+which has an exact solution by separation of variables, allowing us to analyze convergence of DPG for a wide range of $\epsilon$.
+
+%For boundary conditions, we impose $u=0$ on $\Gamma_+$ and $\beta_n u - \sigma_n$ on $\Gamma_-$, which reduces to
+%\begin{align*}
+%u-\sigma_x &= u_0-\sigma_{x,0}, \quad x=0,\\
+%\sigma_y &=  0, \quad y=0,1,\\
+%u &= 0, \quad x=1.\\
+%\end{align*}
+%In this case, our exact solution is the series
+%\[
+%u(x,y) = C_0 + \sum_{n=1}^\infty C_n \frac{\exp(r_2(x-1)-\exp(r_1(x-1)))}{r_1\exp(-r_2) - r_2\exp(-r_1)}\cos(n\pi y),
+%\]
+%where
+%\begin{align*}
+%r_{1,2} &= \frac{1 \pm \sqrt{1 + 4 \epsilon\lambda_n}}{2 \epsilon},\\
+%\lambda_n &= n^2\pi^2 \epsilon.
+%\end{align*}
+%The constants $C_n$ depend on a given inflow condition $u_0$ at $x=0$ via the formula
+%\[
+%C_n = \int_0^1 u_0(y) \cos(n\pi y).
+%\]
+%We begin with the solution taken to be the first non-constant term of the above series.
+We set the inflow boundary condition to be exactly the value of $u-\sigma_x$ corresponding to the exact solution.
+%
+%\begin{figure}[h!]
+%\centering
+%\subfigure{
+%\includegraphics[scale=.37]{figs/wallBC_exact_u.png}
+%}
+%\subfigure{
+%\includegraphics[scale=.37]{figs/wallBC_exact_sigx.png}
+%}
+%\subfigure{
+%\includegraphics[scale=.37]{figs/wallBC_exact_sigy.png}
+%}
+%\caption{Solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
+%\end{figure}
+
+All computations have been done using the adaptive DPG code Camellia, built on the Sandia toolbox Trilinos \cite{Camellia}.
+
+Cite mesh idea of Schwab and Suri \cite{SchwabBoundaryLayers}.
+The mesh will consist of two elements, one of width $C\epsilon(p+\del p)$, where $C = O(1)$.
+Simpler to implement than Shishkin sub-meshes, which are harder to work with than simple $\del p$ enrichment (submeshes require transformations, assembly, etc).
+\begin{figure}[!h]
+\centering
+\subfigure{\includegraphics[width=5.7cm]{figs/schwabSuriMesh.pdf}}
+\subfigure{\includegraphics[width=9cm]{figs/schwabSuriResults.pdf}}
+\caption{Two-element mesh of Schwab and Suri, tailored to predict boundary layers in conforming test functions, and corresponding ratio of $L^2$ errors for the $L^2$-projected exact solution and the DPG solution, ranging over $\epsilon = 1e-1$ to $\epsilon = 1e-7$ with $C=2$.
+}
+\label{fig:schwabSuriMesh}
+\end{figure}
+
+At $\epsilon = 1e-6$, there is significant roundoff error in the thin element due to conditioning of highly anisotropic (aspect ratio = $\epsilon^{-1} = 1e6$) and high order elements.
+Nevertheless, the solution looks like the $L^2$ solution away from that element.
+
+\textcolor{red}{Todo: test limiting the aspect ratio to see if you can resolve decently for $\epsilon = 1e-6, 1e-7$.
+Try adaptivity as well, and try to explain that $\nor{e}_V$ is far from the actual $L^2$ error due to resolution of test functions but not error rep functions.}
+
+\subsection{Adaptivity with/without boundary layer resolution.}
+
+\subsection{Under-resolution of boundary layers}
+We note that globally optimal test functions only produce boundary layers at the global inflow boundary.
 
@@
 \]
-Let $\lesssim$ denote a robust bound - if $ \nor{\LRp{v,\tau}}_V \lesssim \|u\|_{L^2(\Omega)}$, then we have that
+Let $\lesssim$ denote a robust bound in $\epsilon$
+\footnote{A bound $a \lesssim b$ is considered robust in some parameter $\epsilon$ if $a \leq C b$ for some constant $C$ independent of $\epsilon$.}
+  - if $\nor{\LRp{v,\tau}}_V \lesssim \|u\|_{L^2(\Omega)}$, then we have that
 \[
@@
 \]
-In other words, a necessary condition for a robust method is that the test norm measures solutions to the adjoint equations in a robust manner.
+In other words, a necessary condition for a robust method is that the test norm measures global solutions to the adjoint equations in a robust manner.
 
-\textcolor{red}{Can we conclude that the same thing needs to happen for approximate test functions?}
+The above logic was presented in \cite{DPGrobustness, ChanHeuerBui-ThanhDemkowicz12} in order to motivate necessary conditions with which to construct a test norm for convection-diffusion problems.
+However, the same logic can be applied at the discrete level for approximate test functions.
 
-If we assume that an underresolved test function behaves similarly to a test function under a larger viscosity, we expect that the term $\nor{\div \tau - \beta \cdot \grad v}_{L^2}$ still remains relatively bounded uniformly in $\epsilon$.
-However, the term $\nor{\frac{1}{\epsilon}\tau - \grad v}_{L^2}$ does not --- analytical calculations in 1D show that this term grows with the Peclet number in the element at the inflow, where the adjoint solution develops a boundary layer.
+Include plots of underresolved test functions - show that the inflow boundary layer ``releases" for underresolved approximations.
+
+%If we assume that an underresolved test function behaves similarly to a test function under a larger viscosity, we expect that the term $\nor{\div \tau - \beta \cdot \grad v}_{L^2}$ still remains relatively bounded uniformly in $\epsilon$.
+However, the term $\nor{\frac{1}{\epsilon}\tau + \grad v}_{L^2}$ does not - analytical calculations in 1D show that this term grows with the Peclet number in the element at the inflow, where the adjoint solution develops a boundary layer.
 As the boundedness of this term determines the robustness of $\sigma$, our energy norm is
-\begin{align*}
-\nor{\boldsymbol U}_E &\coloneqq \sup_{\LRp{v,\tau}}\LRp{\frac{\LRp{u,\Grad_h \cdot \tau - \beta \cdot \Grad_h v}_{\Omega}}{\nor{\LRp{v,\tau}}_V} + \frac{\LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad_h v}_{\Omega}}{\nor{\LRp{v,\tau}}_V} + \frac{\LRa{\fnh,v}_{\Gamma} - \LRa{\uh,\tau_n}_{\Gamma}}{\nor{\LRp{v,\tau}}_V}} \\
-&\approx \nor{u}_{L^2} + F(\text{Pe})\nor{\sigma}_{L^2} + \nor{\LRp{\uh,\fnh}}
-\end{align*}
-where $F(\text{Pe})$ is some non-decreasing function of the Peclet number.
-Numerical experiments confirm that, for the quasi-optimal test norm, underresolution of the inflow boundary layer negatively affects only the robustness of $u$.
+%\begin{align*}
+%\nor{\boldsymbol U}_E &\coloneqq \sup_{\LRp{v,\tau}}\LRp{\frac{\LRp{u,\Grad_h \cdot \tau - \beta \cdot \Grad_h v}_{\Omega}}{\nor{\LRp{v,\tau}}_V} + \frac{\LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad_h v}_{\Omega}}{\nor{\LRp{v,\tau}}_V} + \frac{\LRa{\fnh,v}_{\Gamma} - \LRa{\uh,\tau_n}_{\Gamma}}{\nor{\LRp{v,\tau}}_V}} \\
+%&\approx \nor{u}_{L^2} + F(\text{Pe})\nor{\sigma}_{L^2} + \nor{\LRp{\uh,\fnh}}
+%\end{align*}
+%where $F(\text{Pe})$ is some non-decreasing function of the Peclet number.
+Numerical experiments confirm that, for the quasi-optimal test norm, underresolution of the inflow boundary layer negatively affects mainly the robustness of $u$.
+
+\subsection{A modification of the adjoint problem}
+
+Modification of adjoint problem: \cite{ChanHeuerBui-ThanhDemkowicz12}.
+\begin{itemize}
+\item $\nor{\cdot}_{V_{\rm inflow}}$ ??
+\end{itemize}
 
@@
 \end{itemize}
+
+\section{Acknowledgements}
+
+\textcolor{red}{Thanks to John Evans for several helpful discussions.}
+
+\bibliographystyle{plain}
+\bibliography{paper}
+
+\section{Outline}
+
+\begin{enumerate}
+\item \textbf{Introduce DPG}
+\item \textbf{Globally optimal test space}: Introduce globally optimal testing, give proof of weakly-conforming global test space contained in localized test space.
+Make note of the jumps being approximated by the flux/trace space and note that this poses difficulty for different singular perturbation problems like wave propagation.
+\begin{itemize}
+\item Relate globally optimal test functions back to $L^2$ optimal global test functions.  
+\end{itemize}
+\item \textbf{Discuss application to convection-diffusion}: describe issue of resolution of local test functions and the presence of boundary layers that appear on elements that aren't in globally optimal test functions.
+Define \textit{robustness}.
+\begin{itemize}
+\item Discuss the different boundary layers - boundary layers in \textit{local/global DPG test functions}, and boundary layers in \textit{$L^2$ optimal test functions}.
+\item There are two cases: If the $L^2$-optimal test functions produce boundary layers, they must be dealt with
+\begin{itemize}
+\item Test norm - weight the test norm such that it doesn't behave non-robustly in the boundary layer area (give graph test norm example as well)
+\item Discrete approximation - approximate test functions such that they resolve the boundary layer robustly.  
+\end{itemize}
+If the $L^2$-optimal test functions do not produce boundary layers, the story then depends on your test norm.
+\begin{itemize}
+\item Test norm - can use a test norm that doesn't produce BL test functions, i.e. remove the weight.
+\item Discrete approx - if you use the graph test norm, boundary layers are still produced.
+\end{itemize}
+\end{itemize}
+\item \textbf{Numerical experiments}: (energy/$L^2$ error and their ratio as resolution of inflow layer increases), 
+\begin{itemize}
+\item Mention effects of underresolution of boundary layers with the new inflow condition/graph test norm, as well as the robust test norm (i.e.
+underresolution of boundary layer in $v$).
+Plot 5 global optimal test functions each - 1 for u, 2 for sigma, 2 fluxes (streamline/cross-stream),
+\begin{itemize} 
+\item Graph norm 
+\item Weighted norm
+\item Unweighted norm
+\end{itemize}
+\end{itemize}
+\item \textbf{Conclusions}: The behavior of DPG really depends on two things for convection-diffusion: if your discrete test functions are approximated such that they are (globally) robust in your test norm, and if your test norm measures the $L^2$ optimal test functions in a robustly continuous manner.
+
+\end{enumerate}
+
 \end{document}

### 2013-02-01 docs/Truman/LocalConservation/paper.tex

--- 2012-11-28 docs/Truman/LocalConservation/paper.tex
@@
 \newcommand{\Oh}{\Omega_h}
+\newcommand{\ptl}{{\partial}}
+\newcommand{\bfsig}{\mbox{\boldmath $\sigma$}}
+\newcommand{\bfn}{\mbox{\boldmath $n$}}
+\newcommand{\bfH}{\mbox{\boldmath $H$}}
+\newcommand{\HdivK}{\bfH(\text{div},K)}
 
@@
 \section{Intoduction}
-Verteeg and Malalasekera, in \emph{An Introduction to Computational Fluid
-Dynamics: The Finite Volume Method}\cite[p. 110-113]{IntroCFD} cite three
-characteristics that they consider essential to any numerical discretization
-of convection-diffusion type problems: conservativeness, boundedness, and
-transportiveness.
+The discontinuous Petrov-Galerkin (DPG) methd with optimal test functions has
+been under active development for convection-diffusion type systems
+\cite{DPG1, DPG2, DPG3, DPG5, DemkowiczHeuer, ChanHeuerThanhDemkowicz2012,
+MoroNguyenPeraire11}. In this paper, we develop a locally conservative
+formulation of DPG for convection-diffusion type equations and supplement this
+with numerical results.
 
+\subsection{Importance of Local Conservation}
+Locally conservative methods hold a special place for numerical analysts in
+the field of fluid dynamics. 
 Perot\cite{Perot2011} argues
@@
 used to try to adress this. Chang and Nelson\cite{ChangNelson1997} developed
-the 'restricted LSFEM'\cite{ChangNelson1997} be augmenting the least squares
+the 'restricted LSFEM'\cite{ChangNelson1997} by augmenting the least squares
 equations with a Lagrange multiplier explicitly enforcing mass conservation
@@
 
-The discontinuous Petrov-Galerkin finite element method has shown a lot of
-promise for convection-diffusion type problems including robustness in the
-face of singularly perturbed problems.
-
-\section{DPG is a Minimum Residual Method}
-We now proceed with a abstract derivation of the standard Discontinuous
-Petrov-Galerkin method. Suppose we have two Hilbert spaces, $U$ and $V$, the
-trial and test spaces, respectively. And suppose we are trying to solve a
-well-posed variational problem $b(u,v)=l(v)$. We can rewrite this in operator
-form $Bu=l$, where $B:U\rightarrow V'$, where $V'$ is the dual space to $V$.
-Then, for a discrete subspace $U_h\subset U$, we seek to find $u_h\in U_h$
-that minimizes the error residual:
+\subsection{DPG is a Minimum Residual Method}
+Roberts \etal presents a brief history and derivation of DPG with optimal test functions in
+\cite{DPGStokes}. We follow his derivation of the standard DPG method as a
+minumum residual method. Let $U$ be the trial Hilbert space and $V$ the test
+Hilbert space for a well-posed variational problem $b(u,v)=l(v)$. In operator
+form this is $Bu=l$, where $B:U\rightarrow V'$. We seek to minimize the
+residual for the discrete space $U_h\subset U$:
 \begin{equation}
-u_h=\argmin_{u_h\in U_h}\frac{1}{2}\nor{Bu_h-l}^2_{V'}\,.
+u_h=\argmin_{u_h\in U_h}\frac{1}{2}\norm{Bu_h-l}^2_{V'}\,.
 \label{minresidual}
@@
 \eqnref{optimaltestproblem} still requires the inversion of the
-infinite-dimensional Riesz map, but in approximating the $V$ by finite
+infinite-dimensional Riesz map, but approximating $V$ by finite
 dimensional $V_h$ which is of a higher polynomial degree than $U_h$ (hence
@@
 
-\section{DPG Applied to Convection-Diffusion}
-Now that we have briefly outline the abstract DPG method, let us put it into
-practice with the Convection-Diffusion equation. The strong form of the
-steady Convection-Diffusion equation reads
+\section{Analysis}
+We now proceed to develop a locally conservative formulation of DPG for
+convection-diffusion type problems, but there are a few terms that we need to
+define first. If $\Omega$ is our problem domain, then we can partition it into
+finite elements $K$ such that
 \[
-\div(\bs\beta u)-\epsilon\del u=g\,,
+\overline{\Omega} = \bigcup_K  \bar{K},\: \quad K \text { open},
+\]
+with corresponding {\em skeleton} $\Gamma_h$ and {\em interior
+  skeleton} $\Gamma_h^0$,
+\[
+\Gamma_h := \bigcup_K \partial K\qquad \Gamma_h^0 := \Gamma_h - \Gamma.
+\]
+We define broken Sobolev spaces element-wise:
+\[
+\begin{array}{rl}
+H^1(\Omega_h) & := \prod_K H^1(K), \\[8pt]
+\bfH(\text{div},\Omega_h) & := \prod_K \bfH(\text{div},K).
+\end{array}
+\]
+We also need the trace spaces:
+\[
+\begin{array}{rl}
+H^\frac{1}{2}(\Gamma_h) & := \left\{ \hat{v} = \{\hat{v}_K \} \in \prod_K H^{1/2}(\ptl K) \: :
+\: \exists v \in H^1(\Omega) : v\vert_{\ptl K} = \hat{v}_K \right\}, \\[8pt]
+H^{-\frac{1}{2}}(\Gamma_h) & := \left\{ {\hat{\sigma}}_n = \{ {\hat{\sigma}}_{Kn} \}\in \prod_K H^{-1/2}(\ptl K) \: : \: \exists \bfsig \in \bfH(\text{div},\Omega)
+: {\hat{\sigma}}_{Kn} = (\bfsig \cdot \bfn)\vert_{\ptl K} \right\},
+\end{array}
+\]
+which are developed more precisely in \cite{DPGStokes}.
+
+\subsection{Element Conservative Convection-Diffusion}
+Now that we have briefly outlined the abstract DPG method, let us apply it to
+the convection-diffusion equation. The strong form of the steady
+convection-diffusion problem with homogeneous Dirichlet boundary conditions reads
+\[
+\left\{
+\begin{array}[c]{rrl}
+\div(\bs\beta u)-\epsilon\del u & =f & \text{in }\Omega\\
+u & =0 & \text{on }\Gamma\,,
+\end{array}
+\right.
 \]
 where $u$ is the property of interest, $\bs\beta$ is the convection vector,
-and $g$ is the source term. Let us write this as an equivalent system of first
+and $f$ is the source term. Nonhomogeneous Dirichlet and Neumann boundary
+conditions are straightforward but would add technicality to the following
+discussion. Let us write this as an equivalent system of first
 order equations:
 \begin{align*}
-\div(\bs\beta u-\bs\sigma)&=g\\
+\div(\bs\beta u-\bs\sigma)&=f\\
 \frac{1}{\epsilon}\bs\sigma-\grad u&=\bs0\,.
@@
 -(\bbeta u-\bsigma,\nabla v)_K+((\bbeta
-u-\bsigma)\cdot\mathbf{n},v)_{\partial K}&=(g,v)_K\\
+u-\bsigma)\cdot\mathbf{n},v)_{\partial K}&=(f,v)_K\\
 \frac{1}{\epsilon}(\bsigma,\btau)_K+(u,\nabla\cdot\btau)_K
@@
 boundaries undefined, and in a manner similar to the hybridized discontinuous
-Galerkin method, we define new unknowns for trace $\hat u$ and flux $\hat f$.
+Galerkin method, we define new unknowns for trace $\hat u$ and flux $\hat t$.
 Applying these definitions to \eqnref{preultraweak} and adding the two
-equations together, we arrive at our desired bilinear form,
+equations together, we arrive at our desired variational problem.
+
+Find
+$\bs u:=(u,\bsigma,\hat u,\hat t)
+\in\bs U:=L^2(\Omega_h)\times \bs L^2(\Omega_h)\times H^{1/2}(\Gamma_h)\times H^{-1/2}(\Gamma_h)$ 
+such that
 \begin{equation}
 \label{eq:confusionBF}
--(\bbeta u-\bsigma,\nabla v)_K+(\hat f,v)_{\partial K}
+-(\bbeta u-\bsigma,\nabla v)_K+(\hat t,v)_{\partial K}
 + \frac{1}{\epsilon}(\bsigma,\btau)_K
 +(u,\nabla\cdot\btau)_K
--(\hat u,\tau_n)_{\partial K}=(g,v)_K\,.
+-(\hat u,\tau_n)_{\partial K}=(f,v)_K \\
 \end{equation}
-% Function Spaces
+for all $\bs v:=(v,\btau)\in
+\bs V:=H^1(\Omega_h)\times\bfH(\text{div},\Omega_h)$. Thus, our bilinear form
+is $b(\bs u,\bs v)=l(\bs v)$.
 
-Within each element, we perform a Bubnov-Galerkin solve for the optimal test
-functions. %Problem description
-As mentioned earlier the choice of test norm on $V$ can have profound
-influence on the robustness of our method.
+Let $\bs U_h:=U_h\times\bs S_h\times\hat U\times\hat F\subset L^2(\Omega_h)\times\bs
+L^2(\Omega_h)\times H^{\frac{1}{2}}(\Gamma_h)\times H^{-\frac{1}{2}}(\Gamma_h)$
+be a finite-dimensional subspace, and let $\bs u_h:=(u_h.\bsigma_h,\hat
+u_h\hat t_h)\in\bs U_h$ be a group variable. The element conservative DPG scheme is
+derived from the Lagrangian:
+\begin{equation}
+L(\bs u_h,\lambda_k)=\frac{1}{2}\norm{R_V^{-1}(b(\bs
+u_h,\cdot)-(f,\cdot))}^2_{\bs V}-\sum_K\lambda_K(b(\bs u_h,1_K)-l(1_K))\,.
+\label{eq:lagrangian}
+\end{equation}
+
+% A cursory look at \eqnref{confusionBF} tells us which function spaces to look
+% in for each variable:
+% \[
+% \begin{array}{lll}
+% u\in L^2(\Omega_h) \quad& \hat u\in H^{1/2}(\Gamma_h) \quad& v\in H^1(\Omega_h)\\
+% \bsigma\in \mathbf{L}^2(\Omega_h) \quad& \hat t\in H^{-1/2}(\Gamma_h) \quad&
+% \btau\in \bs{H}(\bs{div},\Omega_h)\,.\\
+% \end{array}
+% \]
+
+% All that is left to pin down this problem is a definition of our test norm so
+% we can invert the Riesz operator and calculate our optimal test functions.
+% Within each element, we perform a Bubnov-Galerkin solve for the optimal test
+% functions. Define finite-dimensional subspaces
+% $\mb{U}_h\subset\mb{U}:=L^2(\Omega_h)\times\mb{L}^2(\Omega_h)\times
+% H^{1/2}(\Gamma_h)\times H^{-1/2}(\Gamma_h)$ the trial space and 
+% $\mb{V}_h\subset\mb{V}:=H^1(\Omega_h)\times H(div,\Omega_h)$ the ``enriched''
+% test space.
+% For each $\mathbf{u}=\{u,\bsigma,\hat u,\hat t\}\in\mathbf{U}_h$, find
+% $\mathbf{v}_{\mathbf{u}}=\{v_\mathbf{u},\btau_\mathbf{u}\}\in\mathbf{V_h}$ such that
+% \[
+% (\mathbf{v_u},\mathbf{w})_\mathbf{V}=b(\mathbf{u},\mathbf{w})\quad\forall\mathbf{w}\in\mathbf{V}
+% \]
+% As mentioned earlier the choice of test norm on $V$ can have profound
+% influence on the robustness of our method. Unfortunately, the structure of the
+% optimal test norm makes it non-localizable. For many problems, it suffices to
+% use the so-call quasi-optimal test norm which is based on the adjoint of the
+% $B$ operator, but for convection-diffusion type equations, the adjoint
+% develops boundary layers which make solving for the optimal test functions
+% much more difficult for small diffusion. In an earlier consideration of DPG
+% for convection-diffusion problems, Chan \etal developed the more robust
+% test norm\cite{ChanHeuerThanhDemkowicz2012}, 
+% \begin{equation}
+% \label{eq:robustNorm}
+% \norm{(v,\btau)}^2_{\mathbf{V},\Omega_h}=
+% \norm{\nabla\cdot\btau}^2+\norm{\min\left\{\frac{1}{\sqrt{\epsilon}},\frac{1}{\sqrt{|K|}}\right\}\btau}^2
+% +\epsilon\norm{\nabla v}^2+\norm{\bbeta\cdot\nabla v}^2
+% +\norm{\min\left\{\sqrt{\frac{\epsilon}{|K|}},1\right\}v^2}\,.
+% \end{equation}
+% Unfortunately, this test norm also has a few issues. For one, some of the
+% assumptions that went into its development break down as the flow field
+% degenerates to zero. In such cases the final $L^2$ term on $v$ can register
+% higher error levels and trigger unnecessary refinements in smooth regions, see
+% ref{}.
+%TODO: have Jesse write about this
+
+% \subsection{Locally Conservative Formulation}
+% A simple control volume analysis will tell us that a locally conservative
+% method must enforce that
+% \begin{equation}
+% \int_{\partial K}\hat t=\int_K f\,,\quad\forall K\in\Omega_h\,,
+% \label{eq:localconservation}
+% \end{equation}
+% which is equivalent to having the set
+% $\mathbf{v}_K:=\{v,\btau\}=\{1_K,\boldsymbol0\}$ for $K=1,\dots,N$ ($N$ is the
+% number of mesh elements)
+% in the test space, where each $1_K$ has value one on element $K$ and zero
+% elsewhere.  In fact, if we insert this test function into
+% \eqnref{confusionBF}, all of the $\tau$ and $\grad v$ terms vanish and we are
+% left exactly with this condition.
+% Numerical experiments imply that local conservation occurs in one dimension,
+% but the standard DPG method is not exactly locally conservative for higher
+% dimensional problems.
+% 
+% Following Moro \etal\cite{MoroNguyenPeraire11}, we can explicitly augment our
+% test space with constants through the use of Lagrange multipliers. Going back
+% to \eqnref{rieszapplied}, we can define our Lagrange function,
+% \begin{equation}
+% \label{eq:lagrangian}
+% L(u_h,\blambda) = \frac{1}{2}\norm{R_V^{-1}(Bu_h-l)}_V^2
+% -\sum_K\lambda_K\underbrace{\langle Bu_h-l,\mathbf{v}_K\rangle}_
+% {\langle\hat t, 1_K\rangle_{\partial K}-\langle g,1_K\rangle_K}\,,
+% \end{equation}
+% where $\blambda=\{\lambda_1,\cdots,\lambda_N\}$.
+% We then proceed as before and find the critical points of \eqnref{lagrangian},
+% \begin{equation}
+% \label{eq:modifiedBF}
+% \frac{\partial L(u_h,\blambda)}{\partial u_h}=b(u_h,R_V^{-1}B\delta u_h)
+% -l(R_V^{-1}B\delta u_h)
+% -\sum_K\lambda_K b(\delta
+% u_h,\mathbf{v}_K)=0\,,\quad\forall\delta u_h\in U_h
+% \end{equation}
+% \begin{equation}
+% \label{eq:constraint}
+% \frac{\partial
+% L(u_h,\blambda)}{\partial\lambda_K}=-b(u_h,\mathbf{v}_K)+l(\mathbf{v}_K)=0\,,\quad\forall
+% K\,.
+% \end{equation}
+% Equation \eqnref{modifiedBF} is just \eqnref{DPGmethod} with the extra
+% Lagrange terms. As usual, the second equation just enforces the constraint. As
+% a consequence, we now explicitly have constants in our test space and should
+% enforce local conservation to machine precision. The negative side is that we
+% have added an additional unknown associated with every mesh element and turned
+% our well-behaved minimization into a saddle point problem.
+% 
+% This change has further consequences to how we compute our optimal test
+% functions. Since constants are now explicitly represented in the test space,
+% we only need to search for optimal test functions in the orthogonal complement
+% of constants. The final term in \eqnref{robustNorm} is somewhat troublesome,
+% but becomes unnecessary when solving in the orthogonal complement of
+% constants. Instead, we can replace it with a much nicer zero mean term. Thus,
+% \eqnref{robustNorm} becomes
+% \begin{equation}
+% \norm{(v,\btau)}^2_{\mathbf{V},\Omega_h}=
+% \norm{\nabla\cdot\btau}^2+\norm{\min\left\{\frac{1}{\sqrt{\epsilon}},\frac{1}{\sqrt{|K|}}\right\}\btau}^2\\
+% +\epsilon\norm{\nabla v}^2+\norm{\bbeta\cdot\nabla
+% v}^2+\left(\int_Kv\right)^2\,.
+% \end{equation}
 

### 2013-02-06 docs/Truman/LocalConservation/paper.tex

@@
 \newcommand{\HdivK}{\bfH(\text{div},K)}
+\newcommand{\HOneK}{H^{-1}(K)}
+\newcommand{\HOneOmegah}{H^{-1}(\Omega_h)}
+\newcommand{\HdivOmegah}{\bfH(\text{div},\Omega_h)}
+\newcommand{\vdeltau}{v_{\delta\bs u_h}}
+\newcommand{\taudeltau}{\btau_{\delta\bs u_h}}
 
@@
 \right]}
+
+\renewcommand{\arraystretch}{2.0}
 
@@
 \begin{equation}
-\label{eq:confusionBF}
+\label{eq:variationalFormulation}
 -(\bbeta u-\bsigma,\nabla v)_K+(\hat t,v)_{\partial K}
@@
 \end{equation}
+
+Taking the G\^ateaux derivative as before, we arrive at the following system
+of equations:
+\begin{equation}
+\left\{
+\begin{array}[c]{rll}
+b(\bs u_h,T(\delta\bs u_h))-\sum_K\lambda_K b(\bs u_h,1_K)
+&=(f,T(\delta\bs u_h)) & \forall\delta\bs u_h\in\bs U_h\\
+b(\bs u_h,1_K) &=(f,1_K) & \forall K\,,
+\end{array}
+\right.
+\label{eq:conservativeSystem}
+\end{equation}
+where $T:=R_V^{-1}B:\bs U_h\rightarrow\bs V$ is the trial-to-test operator.
+
+Since the trial-to-test operator selectively produces test functions in
+$H^1(\Omega_h)$ and $\bs H(\text{div},\Omega_h)$, denote the result
+$v_{\delta\bs u_h}$ when $T(\delta u_h)\in H^1(\Omega_h)$ and
+$\btau_{\delta\bs u_h}$ when $T(\delta u_h)\in \bs H(\text{div},\Omega_h)$.
+Then, putting \ref{eq:conservativeSystem} into more concrete terms for
+convection-diffusion, we get:
+\begin{equation}
+\left\{
+\begin{array}[c]{rll}
+-(\bbeta u-\bsigma,\nabla \vdeltau)+\langle\hat t,\vdeltau\rangle
++ \frac{1}{\epsilon}(\bsigma,\taudeltau)
++(u,\nabla\cdot\taudeltau)
+-\langle\hat u,\taudeltau\cdot\bs n\rangle\\
+-\sum_K\lambda_K (\delta\hat t,1_K)
+&=(f,\vdeltau) & \forall\delta\bs u_h\in\bs U_h\\
+b(\bs u_h,1_K) &=(f,1_K) & \forall K\,.
+\end{array}
+\right.
+\label{eq:conservativeConfusionSystem}
+\end{equation}
+
+The optimal test functions are determined by solving local problems determined
+by the choice of test norm. For illustrative purposes we choose the robust
+test norm developed by Chan \etal\cite{ChanHeuerThanhDemkowicz2012}. With this
+choice, we get our local problem:
+
+Find $\vdeltau\in\HOneK,\,\taudeltau\in\HdivK$ such that:
+\begin{align}
+(\nabla\cdot\taudeltau,\nabla\cdot\delta\btau)_K
+&+\min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}(\taudeltau,\delta\btau)_K
++\epsilon(\nabla\vdeltau,\nabla \delta v)_K
++(\bbeta\cdot\nabla\vdeltau,\bbeta\cdot\nabla \delta v)_K\\
+&+\alpha\min\left\{\sqrt{\frac{\epsilon}{|K|}},1\right\}(\vdeltau,\delta v)_K
+\quad\quad\forall\delta v\in\HOneK,\,\delta\btau\in\HdivK\,,
+\label{eq:localSolve}
+\end{align}
+where, typically, $\alpha=1$.
+
+We can decompose the discrete flux space $\hat F_h$ into element conserving
+fluxes and some algebraic complement:
+\begin{equation}
+\hat F_h=\hat F_h^c\oplus\hat F_h^{nc}\,,\quad\hat 
+F_h^{c}:=\{\hat t:\langle\hat t,1_K\rangle=0\quad\forall K\}\,.
+\label{eq:decomposition}
+\end{equation}
+This may be accomplished by employing for fluxes in $\hat F_h^{c}$ traces of
+curls, $\nabla\times\phi$. Restricting ourselves to $\delta\hat t\in\hat
+F_h^{c}$ in \eqref{eq:conservativeConfusionSystem}$_1$, we obtain a system  of
+equations that can be solved for $u_h$, $\bsigma_h$, $\hat u$, and $\hat
+t\in\hat F_h^c$. The remaining fluxes, $\hat t\in\hat F_h^{nc}$ are determined
+from \eqref{eq:conservativeConfusionSystem}$_2$. Finally, testing with $\hat
+t\in\hat F_h^{nc}$ in \eqref{eq:conservativeConfusionSystem}$_1$, we obtain a
+system of equations that can be solved for Lagrange multipliers $\lambda_K$.
+Additionally, we can pass in local problem \eqref{eq:localSolve} with
+$\alpha\rightarrow0$. The fact that the test functions will be determined then
+up to a constant does not matter, for $\delta\hat t\in\hat F_h^c$, equation
+\eqref{eq:conservativeConfusionSystem}$_1$ is orthogonal to constants. 
+It is convenient to be able to take $\alpha\rightarrow0$ as we will see in
+some later numerical experiments.
+
+\subsection{Proof of Convergence}
+We cannot directly use Brezzi's theorem, but we can reproduce his argument.
+First of all, variational formulation \eqref{eq:variationalFormulation} is
+equivalent to:
+
+Find $\bs u\in\bs U$ such that
+\begin{equation}
+b(\bs u,T(\delta\bs u))=(f,T(\delta\bs u))\quad\forall\bs v\in\bs V\,.
+\label{eq:bilinearForm}
+\end{equation}
+This is because the trial-to-test operator $T=R_V^{-1}B$ is an isomorphism.
+
+Restricting ourselves to $\delta\hat t_h\in\hat F_h^c$, and subtracting
+\eqref{eq:bilinearForm} from \eqref{eq:conservativeConfusionSystem}, we have
+the Galerkin orthogonality condition:
+\begin{align}
+\label{eq:galerkinOrthogonality}
+\frac{1}{\epsilon}(\bsigma_h-\bsigma,\taudeltau)
+&+(u_h-u,\nabla\cdot\taudeltau)
+-\langle\hat u_h-\hat u,\taudeltau\cdot\bs n\rangle
+\nonumber\\
+&-(\bbeta(u_h-u)-(\bsigma_h-\bsigma),\nabla\vdeltau)
++\langle\hat t_h-\hat t,\vdeltau\rangle
+\\
+&\hspace{25ex}\forall(\delta u_h,\delta\bsigma_h,\delta\hat u_h,\delta\hat t_h)
+\in U_h\times\bs S_h\times\hat U_h\times\hat F_h^c\,.
+\nonumber
+\end{align}
+
+We begin with an equivalent of Brezzi's \emph{discrete inf-sup in kernel
+condition}.
+\begin{lemma}
+\label{lemma:infsuplemma}
+The following condition holds:
+\begin{align}
+\sup_{\stackrel{
+(\delta u_h,\delta\bsigma_h,\delta\hat u,\delta\hat t)\in}
+{U_h\times\bs S_h\times\hat U_h\times\hat F_h^c}
+}
+\frac{\snorm{
+b((u_h,\bsigma_h,\hat u_h,\hat t_h), (\vdeltau,\taudeltau))
+% \frac{1}{\epsilon}(\bsigma_h,\taudeltau)
+% +(u_h,\nabla \cdot\taudeltau)
+% -\langle\hat u_h,\taudeltau\cdot\bs n\rangle
+% -(\bbeta u_h-\bsigma_h,\nabla\vdeltau)
+% +\langle\hat t_h,\vdeltau\rangle
+}}
+{\norm{(\vdeltau,\taudeltau)}}
+\ge\alpha\norm{(u_h,\bsigma_h,\hat u_h,\hat t_h)}\quad\nonumber\\
+\forall(u_h,\bsigma_h,\hat u_h,\hat t_h)
+\in U_h\times\bs S_h\times\hat U_h\times\hat F_h^c\,.
+\label{eq:infsup}
+\end{align}
+
+\end{lemma}
+\begin{proof}
+By the very construction of the trial-to-test operator, the supremum on the
+left is equal to
+\begin{equation}
+\norm{T(u_h,\bsigma_h,\hat u_h,\hat t_h)}_{V}
+=\norm{R_V^{-1}B(u_h,\bsigma_h,\hat u_h, \hat t_h)}_{V}
+=\norm{B(u_h,\bsigma_h,\hat u_h, \hat t_h)}_{V'}
+\label{eq:infsupproof}
+\end{equation}
+The condition follows now from the fact that operator $B$ is bounded below,
+i.e. bilinear form \linebreak$b((u_h,\bsigma_h,\hat u_h, \hat t_h),(v,\btau))$ satisfies
+the inf-sup condition.
+\end{proof}
+
+Assume additionally that flux decomposition \eqref{eq:decomposition} is
+orthogonal. We begin by decomposing $\hat t_h$,
+\begin{equation}
+\hat t_h=\hat t_h^{c}+\hat t_h^{nc}\,.
+\label{eq:fluxdecomposition}
+\end{equation}
+Next, we use the triangle inequality,
+\begin{align}
+\label{eq:triangle}
+\norm{(u-u_h,\bsigma-\bsigma_h,\hat u-\hat u_h, \hat t-\hat t_h)}&=
+\norm{(u-u_h,\bsigma-\bsigma_h,\hat u-\hat u_h, \hat t-(\hat t_h^c+\hat t_h^{nc}))}\nonumber\\
+&\le\norm{(u-w_h,\bsigma-\bs s_h,\hat u-\hat w_h, \hat t-(\hat r_h^c+\hat t_h^{nc}))}\\
+&\hspace{3ex}+\norm{(w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h, \hat r_h^c-\hat t_h^c)}\nonumber
+\end{align}
+where $w_h\in U_h$, $\bs s_h\in\bs S_h$, $\hat w_h\in\hat U_h$, and $\hat
+r_h^{c}\in\hat F_h$ are arbitrary. The inf-sup in kernel condition now
+implies:
+\begin{align}
+\label{eq:estimate}
+&\norm{(w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h, \hat r_h^c-\hat t_h^c)}\\
+&\hspace{8ex}\le\frac{1}{\alpha}
+\sup_{\stackrel{
+(\delta u_h,\delta\bsigma_h,\delta\hat u,\delta\hat t)\in}
+{U_h\times\bs S_h\times\hat U_h\times\hat F_h^c}
+}
+\frac{\snorm{
+b( (w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h,\hat r_h^c-\hat t_h^c),
+(\vdeltau,\taudeltau))
+}}
+{\norm{(\vdeltau,\taudeltau)}}\nonumber\\
+&\hspace{8ex}\le\frac{1}{\alpha}
+\sup_{\stackrel{
+(\delta u_h,\delta\bsigma_h,\delta\hat u,\delta\hat t)\in}
+{U_h\times\bs S_h\times\hat U_h\times\hat F_h^c}
+}
+\frac{\snorm{
+b( (w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h,\hat r_h^c+\hat t_h^{nc}-\hat t),
+(\vdeltau,\taudeltau))
+}}
+{\norm{(\vdeltau,\taudeltau)}}\nonumber\\
+&\hspace{8ex}\le\frac{1}{\alpha}
+\norm{(w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h,\hat t-(\hat r_h^c+\hat
+t_h^{nc}))}
+\end{align}
+% \frac{1}{\epsilon}(\bs s_h-\bsigma_h,\taudeltau)
+% +(w_h-u_h,\nabla \cdot\taudeltau)
+% -\langle\hat w_h-\hat u_h,\taudeltau\cdot\bs n\rangle
+% -(\bbeta (w_h-u_h)-(\bs s_h-\bsigma_h),\nabla\vdeltau)
+% +\langle\hat r_h^c-\hat t_h^c,\vdeltau\rangle
+where the second step follows from the Galerkin orthogonality condition
+\eqref{eq:galerkinOrthogonality}, and the last step is a consequence of the
+minimum energy extension norm for fluxes. Cobining with \eqref{eq:triangle},
+we get the final stability result:
+\begin{equation}
+\norm{(u-u_h,\bsigma-\bsigma_h,\hat u-\hat u_h,\hat t-\hat t_h)}
+\leq\left(1+\frac{1}{\alpha}\right)
+\inf_{\stackrel{
+(w_h,\bs s_h,\hat w,\hat r_h^c)\in}
+{U_h\times\bs S_h\times\hat U_h\times\hat F_h^c}
+}
+\norm{(u-w_h,\bsigma-\bs s_h,\hat u-\hat w,\hat t-(\hat r_h^c+\hat t_h^{nc}))}
+\,.
+\label{eq:stability}
+\end{equation}
+
+\section{Numerical Experiments}
 

### 2013-02-25 docs/Truman/LocalConservation/paper.tex
Wrote up Erickson and skewed convection-diffusion.

@@
 \usepackage{graphicx}
-\usepackage{subfigure}
+% \usepackage{subfigure}
 
@@
 \section{Numerical Experiments}
+We explore each of the following experiments with two sets of test norms: the
+standard graph norm, and the aforementioned robust norm.
 
-% A cursory look at \eqnref{confusionBF} tells us which function spaces to look
-% in for each variable:
-% \[
-% \begin{array}{lll}
-% u\in L^2(\Omega_h) \quad& \hat u\in H^{1/2}(\Gamma_h) \quad& v\in H^1(\Omega_h)\\
-% \bsigma\in \mathbf{L}^2(\Omega_h) \quad& \hat t\in H^{-1/2}(\Gamma_h) \quad&
-% \btau\in \bs{H}(\bs{div},\Omega_h)\,.\\
-% \end{array}
-% \]
+\subsection{Erickson-Johnson Model Problem}
+The Erickson-Johnson problem is one of the few convection-diffusion problems
+with a known analytical solution. Take a domain $\Omega=[0,1]^2$, with
+$\bbeta=(1,0)^T$, $f=0$ and boundary conditions $\hat t=u_0$ when
+$\beta_n\le0$, and $u_0$ is the trace of the exact solution. For
+$n=1,2,\cdots$, let
+$\lambda_n=n^2*\pi^2*\epsilon$,
+$r_n=\frac{1+\sqrt{1+4\epsilon\lambda_n}}{2\epsilon}$, and 
+$s_n=\frac{1-\sqrt{1+4\epsilon\lambda_n}}{2\epsilon}$, the exact solution
+is
+\begin{equation}
+u(x,y)=C_0+\sum_{n=1}^\infty C_n\frac{\exp(s_n(x-1))-\exp(r_n(x-1))}
+{r_n\exp(-s_n)-s_n\exp(-s_n)}\cos(n\pi y)\,.
+\label{eq:ericksonExact}
+\end{equation}
+Taking $\epsilon=0.01$, $C_1=1$, and $C_{n\neq1}=0$, the exact solution looks
+like Figure \ref{fig:erickson}. We solve this problem with both conservative
+and nonconservative formulations of DPG with both graph and robust test norms.
 
-% All that is left to pin down this problem is a definition of our test norm so
-% we can invert the Riesz operator and calculate our optimal test functions.
-% Within each element, we perform a Bubnov-Galerkin solve for the optimal test
-% functions. Define finite-dimensional subspaces
-% $\mb{U}_h\subset\mb{U}:=L^2(\Omega_h)\times\mb{L}^2(\Omega_h)\times
-% H^{1/2}(\Gamma_h)\times H^{-1/2}(\Gamma_h)$ the trial space and 
-% $\mb{V}_h\subset\mb{V}:=H^1(\Omega_h)\times H(div,\Omega_h)$ the ``enriched''
-% test space.
-% For each $\mathbf{u}=\{u,\bsigma,\hat u,\hat t\}\in\mathbf{U}_h$, find
-% $\mathbf{v}_{\mathbf{u}}=\{v_\mathbf{u},\btau_\mathbf{u}\}\in\mathbf{V_h}$ such that
-% \[
-% (\mathbf{v_u},\mathbf{w})_\mathbf{V}=b(\mathbf{u},\mathbf{w})\quad\forall\mathbf{w}\in\mathbf{V}
-% \]
-% As mentioned earlier the choice of test norm on $V$ can have profound
-% influence on the robustness of our method. Unfortunately, the structure of the
-% optimal test norm makes it non-localizable. For many problems, it suffices to
-% use the so-call quasi-optimal test norm which is based on the adjoint of the
-% $B$ operator, but for convection-diffusion type equations, the adjoint
-% develops boundary layers which make solving for the optimal test functions
-% much more difficult for small diffusion. In an earlier consideration of DPG
-% for convection-diffusion problems, Chan \etal developed the more robust
-% test norm\cite{ChanHeuerThanhDemkowicz2012}, 
-% \begin{equation}
-% \label{eq:robustNorm}
-% \norm{(v,\btau)}^2_{\mathbf{V},\Omega_h}=
-% \norm{\nabla\cdot\btau}^2+\norm{\min\left\{\frac{1}{\sqrt{\epsilon}},\frac{1}{\sqrt{|K|}}\right\}\btau}^2
-% +\epsilon\norm{\nabla v}^2+\norm{\bbeta\cdot\nabla v}^2
-% +\norm{\min\left\{\sqrt{\frac{\epsilon}{|K|}},1\right\}v^2}\,.
-% \end{equation}
-% Unfortunately, this test norm also has a few issues. For one, some of the
-% assumptions that went into its development break down as the flow field
-% degenerates to zero. In such cases the final $L^2$ term on $v$ can register
-% higher error levels and trigger unnecessary refinements in smooth regions, see
-% ref{}.
-%TODO: have Jesse write about this
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.6\textwidth]{figs/Erickson/exact.png}
+\caption{Erickson-Johnson exact solution}
+\label{fig:erickson}
+\end{figure}
 
-% \subsection{Locally Conservative Formulation}
-% A simple control volume analysis will tell us that a locally conservative
-% method must enforce that
-% \begin{equation}
-% \int_{\partial K}\hat t=\int_K f\,,\quad\forall K\in\Omega_h\,,
-% \label{eq:localconservation}
-% \end{equation}
-% which is equivalent to having the set
-% $\mathbf{v}_K:=\{v,\btau\}=\{1_K,\boldsymbol0\}$ for $K=1,\dots,N$ ($N$ is the
-% number of mesh elements)
-% in the test space, where each $1_K$ has value one on element $K$ and zero
-% elsewhere.  In fact, if we insert this test function into
-% \eqnref{confusionBF}, all of the $\tau$ and $\grad v$ terms vanish and we are
-% left exactly with this condition.
-% Numerical experiments imply that local conservation occurs in one dimension,
-% but the standard DPG method is not exactly locally conservative for higher
-% dimensional problems.
-% 
-% Following Moro \etal\cite{MoroNguyenPeraire11}, we can explicitly augment our
-% test space with constants through the use of Lagrange multipliers. Going back
-% to \eqnref{rieszapplied}, we can define our Lagrange function,
-% \begin{equation}
-% \label{eq:lagrangian}
-% L(u_h,\blambda) = \frac{1}{2}\norm{R_V^{-1}(Bu_h-l)}_V^2
-% -\sum_K\lambda_K\underbrace{\langle Bu_h-l,\mathbf{v}_K\rangle}_
-% {\langle\hat t, 1_K\rangle_{\partial K}-\langle g,1_K\rangle_K}\,,
-% \end{equation}
-% where $\blambda=\{\lambda_1,\cdots,\lambda_N\}$.
-% We then proceed as before and find the critical points of \eqnref{lagrangian},
-% \begin{equation}
-% \label{eq:modifiedBF}
-% \frac{\partial L(u_h,\blambda)}{\partial u_h}=b(u_h,R_V^{-1}B\delta u_h)
-% -l(R_V^{-1}B\delta u_h)
-% -\sum_K\lambda_K b(\delta
-% u_h,\mathbf{v}_K)=0\,,\quad\forall\delta u_h\in U_h
-% \end{equation}
-% \begin{equation}
-% \label{eq:constraint}
-% \frac{\partial
-% L(u_h,\blambda)}{\partial\lambda_K}=-b(u_h,\mathbf{v}_K)+l(\mathbf{v}_K)=0\,,\quad\forall
-% K\,.
-% \end{equation}
-% Equation \eqnref{modifiedBF} is just \eqnref{DPGmethod} with the extra
-% Lagrange terms. As usual, the second equation just enforces the constraint. As
-% a consequence, we now explicitly have constants in our test space and should
-% enforce local conservation to machine precision. The negative side is that we
-% have added an additional unknown associated with every mesh element and turned
-% our well-behaved minimization into a saddle point problem.
-% 
-% This change has further consequences to how we compute our optimal test
-% functions. Since constants are now explicitly represented in the test space,
-% we only need to search for optimal test functions in the orthogonal complement
-% of constants. The final term in \eqnref{robustNorm} is somewhat troublesome,
-% but becomes unnecessary when solving in the orthogonal complement of
-% constants. Instead, we can replace it with a much nicer zero mean term. Thus,
-% \eqnref{robustNorm} becomes
-% \begin{equation}
-% \norm{(v,\btau)}^2_{\mathbf{V},\Omega_h}=
-% \norm{\nabla\cdot\btau}^2+\norm{\min\left\{\frac{1}{\sqrt{\epsilon}},\frac{1}{\sqrt{|K|}}\right\}\btau}^2\\
-% +\epsilon\norm{\nabla v}^2+\norm{\bbeta\cdot\nabla
-% v}^2+\left(\int_Kv\right)^2\,.
-% \end{equation}
+We plot the $L^2$ and energy error for the various methods in Figures
+\ref{fig:ericksonGraphError} and \ref{fig:ericksonRobustError}. Encouragingly,
+the conservative and nonconservative plots appear to lay right on top of each
+other. This indicates that the conservative formulation at least doensn't hurt
+our convergence significantly.
+
+\begin{figure}[h!]
+\centering
+\parbox{0.45\textwidth}{
+\includegraphics[width=0.45\textwidth]{figs/Erickson/graphError.pdf}
+\caption{Error in Erickson-Johnson solution with graph norm}
+\label{fig:ericksonGraphError}
+}\quad
+\parbox{0.45\textwidth}{
+\includegraphics[width=0.45\textwidth]{figs/Erickson/robustError.pdf}
+\caption{Error in Erickson-Johnson solution with robust norm}
+\label{fig:ericksonRobustError}
+}
+\end{figure}
+
+We plot the flux imbalance errors in Figures \ref{fig:ericksonGraphFlux} and
+\ref{fig:ericksonRobustFlux}. As expected, the element conservative
+formulation brings these errors to the order of machine precision, but it is
+worth pointing out that the flux imbalances for standard DPG are reasonable,
+especially under refinement.
+
+\begin{figure}[h!]
+\centering
+\parbox{0.45\textwidth}{
+\includegraphics[width=0.45\textwidth]{figs/Erickson/graphFlux.pdf}
+\caption{Flux imbalance in Erickson-Johnson solutions with graph norm}
+\label{fig:ericksonGraphFlux}
+}\quad
+\parbox{0.45\textwidth}{
+\includegraphics[width=0.45\textwidth]{figs/Erickson/robustFlux.pdf}
+\caption{Flux imbalance in Erickson-Johnson solutions with robust norm}
+\label{fig:ericksonRobustFlux}
+}
+\end{figure}
+
+\subsection{Skewed Convection-Diffusion Problem}
+This is a standard convection-diffusion problem with a skewed convection
+vector relative to the mesh. The problem setup is identical to the
+Erickson-Johnson problems except that $\bbeta=(2,1)$. The following results
+are for $\epsilon=10^{-4}$.
+
+On our initial mesh, we see no noticeable difference between conservative and
+nonconservative results, though the choice of test norm affects things
+dramatically. The graph norm produces a solution which is comparable to an L2
+project of the exact solution. In this case, the field variable don't show the
+very small boundary layer along the right and top surfaces, though a
+visualization of the traces would show that the wall boundary condition is in
+fact being enforced. As we refine, the field variables will begin to reflect
+the boundary layer. On the other hand, the robust norm does show a boundary
+layer being formed in the field variables.
+
+\begin{figure}[h!]
+\centering
+\parbox{0.45\textwidth}{
+\includegraphics[width=0.45\textwidth]{figs/Confusion/graph0c.png}
+\caption{Conservative skewed convection-diffusion with graph norm, initial mesh}
+\label{fig:confusionGraph0c}
+}\quad
+\parbox{0.45\textwidth}{
+\includegraphics[width=0.45\textwidth]{figs/Confusion/robust0c.png}
+\caption{Conservative skewed convection-diffusion with robust norm, initial mesh}
+\label{fig:confusionRobust0c}
+}
+\end{figure}
+
+As we refine, the three results, nonconservative with graph or robust norm,
+and conservative with graph norm converge to a an essentially identical
+solution (to the eyeball norm), as represented by
+Figure~\ref{fig:confusionGraph8c}. However, the conservative formulation with
+the robust norm seems to exhibit some noise at the right wall as seen in
+Figure~\ref{fig:confusionRobust8c}.
+
+% \begin{figure}[h!]
+% \centering
+% \parbox{0.45\textwidth}{
+% \includegraphics[width=0.45\textwidth]{figs/Confusion/graph8nc.png}
+% \caption{Nonconservative skewed convection-diffusion with graph norm, after 8
+% refinements}
+% \label{fig:confusionGraph8nc}
+% }\quad
+% \parbox{0.45\textwidth}{
+% \includegraphics[width=0.45\textwidth]{figs/Confusion/robust8nc.png}
+% \caption{Nonconservative skewed convection-diffusion with robust norm, after 8
+% refinements}
+% \label{fig:confusionRobust8nc}
+% }
+% \end{figure}
+
+\begin{figure}[h!]
+\centering
+\parbox{0.45\textwidth}{
+\includegraphics[width=0.45\textwidth]{figs/Confusion/graph8c.png}
+\caption{Conservative skewed convection-diffusion with graph norm, after 8
+refinements}
+\label{fig:confusionGraph8c}
+}\quad
+\parbox{0.45\textwidth}{
+\includegraphics[width=0.45\textwidth]{figs/Confusion/robust8c.png}
+\caption{Conservative skewed convection-diffusion with robust norm, after 8
+refinements}
+\label{fig:confusionRobust8c}
+}
+\end{figure}
+
+If we zoom in on one of the noisy areas, as we do in
+Figure~\ref{fig:confusionRobust8c_zoom}, we see overshoots on the order of 32
+and undershoots on the order of -13, where the exact solution varies between 0
+and 1. The cause of these overshoots and undershoots is a little mystery,
+especially because they don't show up until 8 refinement steps in. We will
+explore this problem a little more when we look at the wedge problem.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.6\textwidth]{figs/Confusion/robust8c_zoom.png}
+\caption{Zoomed in conservative skewed convection-diffusion problem after 8
+refinements}
+\label{fig:confusionRobust8c_zoom}
+\end{figure}
+
+Finally, we plot the flux imbalances for the several methods in
+Figure~\ref{fig:confusionGraphFlux} and Figure~\ref{fig:confusionRobustFlux}.
+Interestingly, it appears the effectiveness of our local conservation
+formulation drops as we refine with the graph norm.
+
+\begin{figure}[h!]
+\centering
+\parbox{0.45\textwidth}{
+\includegraphics[width=0.45\textwidth]{figs/Confusion/graphFlux.pdf}
+\caption{Flux imbalance in skewed confusion solutions with graph norm}
+\label{fig:confusionGraphFlux}
+}\quad
+\parbox{0.45\textwidth}{
+\includegraphics[width=0.45\textwidth]{figs/Confusion/robustFlux.pdf}
+\caption{Flux imbalance in skewed confusion solutions with robust norm}
+\label{fig:confusionRobustFlux}
+}
+\end{figure}
 

### 2013-02-25 drivers/LocalConservation/EricksonDriver.cpp

@@ -57,7 +57,7 @@ public:
   bool matchesPoint(double x, double y) {
     double tol = 1e-14;
     bool topMatch = (abs(y-1.0) < tol);
-    bool bottomMatch = (abs(y-1.0) < tol);
+    bool bottomMatch = (abs(y) < tol);
     return topMatch || bottomMatch;
   }
 };

### 2013-02-26 docs/Truman/LocalConservation/paper.tex
Added figures for double glazing.

@@
 \usepackage{graphicx}
-% \usepackage{subfigure}
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 
-\begin{figure}[h!]
+\begin{figure}
 \centering
-\parbox{0.45\textwidth}{
-\includegraphics[width=0.45\textwidth]{figs/Erickson/graphError.pdf}
-\caption{Error in Erickson-Johnson solution with graph norm}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Erickson/graphError.pdf}
+\caption{With graph norm}
 \label{fig:ericksonGraphError}
-}\quad
-\parbox{0.45\textwidth}{
-\includegraphics[width=0.45\textwidth]{figs/Erickson/robustError.pdf}
-\caption{Error in Erickson-Johnson solution with robust norm}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Erickson/robustError.pdf}
+\caption{With robust norm}
 \label{fig:ericksonRobustError}
-}
+\end{subfigure}
+\caption{Error in Erickson-Johnson solutions}
 \end{figure}
@@
 
-\begin{figure}[h!]
+\begin{figure}
 \centering
-\parbox{0.45\textwidth}{
-\includegraphics[width=0.45\textwidth]{figs/Erickson/graphFlux.pdf}
-\caption{Flux imbalance in Erickson-Johnson solutions with graph norm}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Erickson/graphFlux.pdf}
+\caption{With graph norm}
 \label{fig:ericksonGraphFlux}
-}\quad
-\parbox{0.45\textwidth}{
-\includegraphics[width=0.45\textwidth]{figs/Erickson/robustFlux.pdf}
-\caption{Flux imbalance in Erickson-Johnson solutions with robust norm}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Erickson/robustFlux.pdf}
+\caption{With robust norm}
 \label{fig:ericksonRobustFlux}
-}
+\end{subfigure}
+\caption{Flux imbalance in Erickson-Johnson solutions}
 \end{figure}
@@
 
-\begin{figure}[h!]
+\begin{figure}
 \centering
-\parbox{0.45\textwidth}{
-\includegraphics[width=0.45\textwidth]{figs/Confusion/graph0c.png}
-\caption{Conservative skewed convection-diffusion with graph norm, initial mesh}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Confusion/graph0c.png}
+\caption{Conservative with graph norm}
 \label{fig:confusionGraph0c}
-}\quad
-\parbox{0.45\textwidth}{
-\includegraphics[width=0.45\textwidth]{figs/Confusion/robust0c.png}
-\caption{Conservative skewed convection-diffusion with robust norm, initial mesh}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Confusion/robust0c.png}
+\caption{Conservative with robust norm}
 \label{fig:confusionRobust0c}
-}
+\end{subfigure}
+\caption{Skewed convection-diffusion problem with initial mesh}
 \end{figure}
@@
 
-% \begin{figure}[h!]
-% \centering
-% \parbox{0.45\textwidth}{
-% \includegraphics[width=0.45\textwidth]{figs/Confusion/graph8nc.png}
-% \caption{Nonconservative skewed convection-diffusion with graph norm, after 8
-% refinements}
-% \label{fig:confusionGraph8nc}
-% }\quad
-% \parbox{0.45\textwidth}{
-% \includegraphics[width=0.45\textwidth]{figs/Confusion/robust8nc.png}
-% \caption{Nonconservative skewed convection-diffusion with robust norm, after 8
-% refinements}
-% \label{fig:confusionRobust8nc}
-% }
-% \end{figure}
-
-\begin{figure}[h!]
+\begin{figure}
 \centering
-\parbox{0.45\textwidth}{
-\includegraphics[width=0.45\textwidth]{figs/Confusion/graph8c.png}
-\caption{Conservative skewed convection-diffusion with graph norm, after 8
-refinements}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Confusion/graph8c.png}
+\includegraphics[width=\textwidth]{figs/Confusion/graph8c_mesh.png}
+\caption{Conservative with graph norm}
 \label{fig:confusionGraph8c}
-}\quad
-\parbox{0.45\textwidth}{
-\includegraphics[width=0.45\textwidth]{figs/Confusion/robust8c.png}
-\caption{Conservative skewed convection-diffusion with robust norm, after 8
-refinements}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Confusion/robust8c.png}
+\includegraphics[width=\textwidth]{figs/Confusion/robust8c_mesh.png}
+\caption{Conservative with robust norm}
 \label{fig:confusionRobust8c}
-}
+\end{subfigure}
+\caption{Skewed convection-diffusion problem after 8 refinements}
 \end{figure}
@@
 
-\begin{figure}[h!]
+\begin{figure}
 \centering
-\parbox{0.45\textwidth}{
-\includegraphics[width=0.45\textwidth]{figs/Confusion/graphFlux.pdf}
-\caption{Flux imbalance in skewed confusion solutions with graph norm}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Confusion/graphFlux.pdf}
+\caption{With graph norm}
 \label{fig:confusionGraphFlux}
-}\quad
-\parbox{0.45\textwidth}{
-\includegraphics[width=0.45\textwidth]{figs/Confusion/robustFlux.pdf}
-\caption{Flux imbalance in skewed confusion solutions with robust norm}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Confusion/robustFlux.pdf}
+\caption{With robust norm}
 \label{fig:confusionRobustFlux}
-}
+\end{subfigure}
+\caption{Flux imbalance in skewed confusion solutions}
+\end{figure}
+
+\subsection{Double Glazing Problem}
+
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/DoubleGlazing/graph6c.png}
+\caption{Conservative with graph norm}
+\label{fig:doubleglazingGraph6c}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/DoubleGlazing/robust6c.png}
+\caption{Conservative with robust norm}
+\label{fig:doubleglazingRobust6c}
+\end{subfigure}
+\caption{Double glazing problem after 6 refinements}
+\end{figure}
+
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/DoubleGlazing/graphFlux.pdf}
+\caption{With graph norm}
+\label{fig:doubleglazingGraphFlux}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/DoubleGlazing/robustFlux.pdf}
+\caption{With robust norm}
+\label{fig:doubleglazingRobustFlux}
+\end{subfigure}
+\caption{Flux imbalance in double glazing solutions}
 \end{figure}

### 2013-02-27 docs/Truman/LocalConservation/paper.tex

@@
 \subsection{Double Glazing Problem}
+This nominal problem definition takes the same unit square domain with 
+\[
+\bbeta=\binom{2(2y-1)(1-(2x-1)^2)}{-2(2x-1)(1-(2y-1)^2)}\,;\quad f=0\,;\quad
+\hat u=
+\begin{cases}
+1 & \mbox{on }\Gamma_{right}\\
+0 & \mbox{else }
+\end{cases}\,,
+\]
+except that this definition for the boundary is not legal for $\hat u\in
+H^{\frac{1}{2}}(\Gamma_h)$ which is continuous. Therefore we use a ramp of
+width $\sqrt{\epsilon}$ on the right edge to go from 0 to 1. The following
+results are for $\epsilon=10^{-2}$. Note that $\bbeta=(0,0)^T$ at the center
+of the domain.
+
+The choice of test norm appears to have a small effect on the choice mesh
+refinement choices as shown in Figure~\ref{fig:doubleglazing}. Other than
+that, the conservative and nonconservative solutions behave almost exactly to
+the eye. The flux imbalances in Figure~\ref{fig:doubleglazing_flux} are what
+we would expect. The nonconservative formulation appears to become more
+conservative with refinement.
 
@@
 \caption{Double glazing problem after 6 refinements}
+\label{fig:doubleglazing}
 \end{figure}
@@
 \caption{Flux imbalance in double glazing solutions}
+\label{fig:doubleglazing_flux}
+\end{figure}
+
+\subsection{Vortex Problem}
+This problem models a mildly diffusive vortex convecting fluid in a circle. We
+deal with domain $\Omega=[-1,1]^2$ with $\epsilon=10^{-4}$, $\bbeta=(-y,x)^T$,
+and $f=0$. Note that $\bbeta=0$ at the domain center. We have an inflow
+boundary condition when $\bbeta\cdot\mathbf{n}<0$, in which case we set $\hat
+t=\bbeta\cdot\mathbf{n}\cdot u_0$ where
+$u_0=\frac{\sqrt{x^2+y^2}-1}{\sqrt{2}-1}$ which will vary from 0 at the center
+of boundary edges to 1 at corners. We don't enforce an outflow boundary.
+
+Each of the four methods seems to have it's own specific refinement pattern,
+but in general we can see that the nonconservative formulations seem to place
+much more refinements in the center of the vortex where the solution is
+constant. The conservative formulations seem to recognize that more error is
+concentrated on the edges of the vortex where we have a sharp change from
+constant values to linear growth in terms of radius. Again we see that
+standard DPG appears to approach conservation with refinement, and
+unfortunately the conservative formulation appears to be losing enforcement
+under the robust norm.
+
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Vortex/graph6nc.png}
+\caption{Nonconservative with graph norm}
+\label{fig:vortexGraph6nc}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Vortex/robust6nc.png}
+\caption{Nonconservative with robust norm}
+\label{fig:vortexRobust6nc}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Vortex/graph6c.png}
+\caption{Conservative with graph norm}
+\label{fig:vortexGraph6c}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Vortex/robust6c.png}
+\caption{Conservative with robust norm}
+\label{fig:vortexRobust6c}
+\end{subfigure}
+\caption{Vortex problem after 6 refinements}
+\label{fig:vortex}
+\end{figure}
+
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Vortex/graphFlux.pdf}
+\caption{With graph norm}
+\label{fig:vortexGraphFlux}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Vortex/robustFlux.pdf}
+\caption{With robust norm}
+\label{fig:vortexRobustFlux}
+\end{subfigure}
+\caption{Flux imbalance in vortex solutions}
+\label{fig:vortex_flux}
+\end{figure}
+
+\subsection{Wedge Problem}
+We devised this problem to examine some of the issues we were having blow up
+of the solution under the robust test norm. The domain is a rectangle
+$[-0.5,0.5]\times[-1,0.5]$ where the triangle connecting the bottom edges with
+the origin at $(0,0)$ is removed. The convection vector $\bbeta=(1,0)^T$,
+$\epsilon=10^{-1}$, and we apply boundary conditions $\hat t=0$ on the left
+inflow edge, $\hat u=0$ on the top edge, $\bbeta\cdot\mathbf{n}\cdot\hat
+u-\hat t=\sigma_n=0$ on the right outflow edge, $\hat u=1$ on the leading edge
+of the wedge, and $\hat t=\bbeta\cdot\mathbf{n}\cdot 1$ on the trailing edge
+of the wedge.
+
+When the colorscale is scaled from 0 to 1, the macro view of all of the
+solutions looks nearly identical as seen in Figure~\ref{fig:wedge}. However,
+we start to see some differences in the refinement patterns in
+Figure~\ref{fig:wedge_mesh} indicating that the various methods distribute
+error in different ways. We see more evidence of this when we zoom in on the
+tip of the wedge where we get a change in boundary conditions. The graph norm
+solutions don't exhibit any significant problems here. The nonconservative and
+conservative solutions vary smoothly in the range $(-0.00127, 1.03)$, plus or
+minus some less significant digits. The nonconservative robust solution jumps
+from -19.6 to 20.3 at the tip, though this appears to be a very localized
+phenominon. Adding local conservation appears to exacerbate this situation as
+the solution varies from -20.0 to 23.2 and appears to polute a larger area of
+the problem. We implemented a crude hp-adaptive refinement strategy in order
+to try to resolve any singularities present in the solution. If the cell
+measure dips below $5\times10^{-4}$, we switch from h-adaptivity to
+p-adaptivity. Figure~\ref{fig:wedge_poly} shows the resultant polynomial
+orders after refinement. It really appears that the apparent singularities in
+the robust solutions are not physical phenomena that just need resolution, but
+a weakness in the method with the robust test norm.
+
+We plot the flux imbalances in Figure~\ref{fig:wedge_flux}. Despite the
+extreme overshoots and undershoots in the conservative method with the robust
+test norm, we still appear to maintain acceptable levels of conservation.
+
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.4\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Wedge/graph16nc.png}
+\caption{Nonconservative with graph norm}
+\label{fig:wedgeGraph16nc}
+\end{subfigure}
+\begin{subfigure}[t]{0.4\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Wedge/robust16nc.png}
+\caption{Nonconservative with robust norm}
+\label{fig:wedgeRobust16nc}
+\end{subfigure}
+\begin{subfigure}[t]{0.4\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Wedge/graph16c.png}
+\caption{Conservative with graph norm}
+\label{fig:wedgeGraph16c}
+\end{subfigure}
+\begin{subfigure}[t]{0.4\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Wedge/robust16c.png}
+\caption{Conservative with robust norm}
+\label{fig:wedgeRobust16c}
+\end{subfigure}
+\caption{Wedge problem after 16 refinements}
+\label{fig:wedge}
+\end{figure}
+
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.4\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Wedge/graph16nc_mesh.png}
+\caption{Nonconservative with graph norm}
+\label{fig:wedgeGraph16nc_mesh}
+\end{subfigure}
+\begin{subfigure}[t]{0.4\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Wedge/robust16nc_mesh.png}
+\caption{Nonconservative with robust norm}
+\label{fig:wedgeRobust16nc_mesh}
+\end{subfigure}
+\begin{subfigure}[t]{0.4\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Wedge/graph16c_mesh.png}
+\caption{Conservative with graph norm}
+\label{fig:wedgeGraph16c_mesh}
+\end{subfigure}
+\begin{subfigure}[t]{0.4\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Wedge/robust16c_mesh.png}
+\caption{Conservative with robust norm}
+\label{fig:wedgeRobust16c_mesh}
+\end{subfigure}
+\caption{Wedge problem mesh after 16 refinements}
+\label{fig:wedge_mesh}
+\end{figure}
+
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Wedge/graph16nc_zoom.png}
+\caption{Nonconservative with graph norm}
+\label{fig:wedgeGraph16nc_zoom}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Wedge/robust16nc_zoom.png}
+\caption{Nonconservative with robust norm}
+\label{fig:wedgeRobust16nc_zoom}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Wedge/graph16c_zoom.png}
+\caption{Conservative with graph norm}
+\label{fig:wedgeGraph16c_zoom}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Wedge/robust16c_zoom.png}
+\caption{Conservative with robust norm}
+\label{fig:wedgeRobust16c_zoom}
+\end{subfigure}
+\caption{Wedge problem zoomed in after 16 refinements}
+\label{fig:wedge_zoom}
+\end{figure}
+
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Wedge/graph16nc_poly.png}
+\caption{Nonconservative with graph norm}
+\label{fig:wedgeGraph16nc_poly}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Wedge/robust16nc_poly.png}
+\caption{Nonconservative with robust norm}
+\label{fig:wedgeRobust16nc_poly}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Wedge/graph16c_poly.png}
+\caption{Conservative with graph norm}
+\label{fig:wedgeGraph16c_poly}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Wedge/robust16c_poly.png}
+\caption{Conservative with robust norm}
+\label{fig:wedgeRobust16c_poly}
+\end{subfigure}
+\caption{Wedge problem poly after 16 refinements}
+\label{fig:wedge_poly}
+\end{figure}
+
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Wedge/graphFlux.pdf}
+\caption{With graph norm}
+\label{fig:wedgeGraphFlux}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Wedge/robustFlux.pdf}
+\caption{With robust norm}
+\label{fig:wedgeRobustFlux}
+\end{subfigure}
+\caption{Flux imbalance in wedge solutions}
+\label{fig:wedge_flux}
 \end{figure}

### 2013-02-28 docs/Truman/LocalConservation/paper.tex
Added Hemker results to paper.

@@
 
+\subsection{Hemker Problem}
+The Hemker problem is defined on a domain
+$\Omega=\{[-3,9]\times[-3,3]\}\{(x,y):x^2+y^2<1\}$, essentially a simplified
+model of flow past an infinite cylinder. We start with the initial mesh shown
+in Figure~\ref{fig:hemkerInitial} in which we approximate the circle by 32
+linear segments. Our code does not fully support curvilinear elements at this
+time, so as we refine, we just subdivide the initial linear segments. The
+boundary conditions are $\hat t=\bbeta\cdot\mathbf{n}\cdot 1$ on the left
+inflow boundary, $\bbeta\cdot\mathbf{n}\cdot\hat u-\hat t=\sigma_n=0$ on the
+right outflow boundary, $\hat t=0$ on the top and bottom edges, and $\hat u=1$
+on the cylinder.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/Hemker/initial_mesh.png}
+\caption{Initial mesh for the Hemker problem}
+\label{fig:hemkerInitial}
+\end{figure}
+
+After some early refinement steps in which the graph norm solutions exhibit
+some strange behavior (see Figure~\ref{fig:hemker4}) all four methods appear
+to converge toward a decent solution as shown in Figure~\ref{fig:hemker8}. The
+different methods seem to prioritize different parts of the mesh for
+refinement, but with sufficient refinement, the differences in the actual
+solution are fairly insignificant. TODO: Explain why $\hat u$ boundary is not
+nice on inflow.
+
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Hemker/graph4nc.png}
+\includegraphics[width=\textwidth]{figs/Hemker/graph4nc_mesh.png}
+\caption{Nonconservative with graph norm}
+\label{fig:hemkerGraph14nc}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Hemker/robust4nc.png}
+\includegraphics[width=\textwidth]{figs/Hemker/robust4nc_mesh.png}
+\caption{Nonconservative with robust norm}
+\label{fig:hemkerRobust14nc}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Hemker/graph4c.png}
+\includegraphics[width=\textwidth]{figs/Hemker/graph4c_mesh.png}
+\caption{Conservative with graph norm}
+\label{fig:hemkerGraph14c}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Hemker/robust4c.png}
+\includegraphics[width=\textwidth]{figs/Hemker/robust4c_mesh.png}
+\caption{Conservative with robust norm}
+\label{fig:hemkerRobust14c}
+\end{subfigure}
+\caption{Hemker problem after 4 refinements}
+\label{fig:hemker4}
+\end{figure}
+
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Hemker/graph8nc.png}
+\includegraphics[width=\textwidth]{figs/Hemker/graph8nc_mesh.png}
+\caption{Nonconservative with graph norm}
+\label{fig:hemkerGraph18nc}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Hemker/robust8nc.png}
+\includegraphics[width=\textwidth]{figs/Hemker/robust8nc_mesh.png}
+\caption{Nonconservative with robust norm}
+\label{fig:hemkerRobust18nc}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Hemker/graph8c.png}
+\includegraphics[width=\textwidth]{figs/Hemker/graph8c_mesh.png}
+\caption{Conservative with graph norm}
+\label{fig:hemkerGraph18c}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Hemker/robust8c.png}
+\includegraphics[width=\textwidth]{figs/Hemker/robust8c_mesh.png}
+\caption{Conservative with robust norm}
+\label{fig:hemkerRobust18c}
+\end{subfigure}
+\caption{Hemker problem after 8 refinements}
+\label{fig:hemker8}
+\end{figure}
+
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Hemker/graphFlux.pdf}
+\caption{With graph norm}
+\label{fig:hemkerGraphFlux}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Hemker/robustFlux.pdf}
+\caption{With robust norm}
+\label{fig:hemkerRobustFlux}
+\end{subfigure}
+\caption{Flux imbalance in Hemker solutions}
+\label{fig:hemker_flux}
+\end{figure}
+
 \bibliographystyle{plain}

### 2013-02-28 docs/Truman/LocalConservation/paper.tex
Added inner layer and discontinuous source results.

@@
 
+\subsection{Inner Layer Problem}
+
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/InnerLayer/graph8nc.png}
+\includegraphics[width=\textwidth]{figs/InnerLayer/graph8nc_mesh.png}
+\caption{Nonconservative with graph norm}
+\label{fig:innerlayerGraph18nc}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/InnerLayer/robust8nc.png}
+\includegraphics[width=\textwidth]{figs/InnerLayer/robust8nc_mesh.png}
+\caption{Nonconservative with robust norm}
+\label{fig:innerlayerRobust18nc}
+\end{subfigure}
+\caption{Inner layer problem after 8 refinements}
+\label{fig:innerlayer8nc}
+\end{figure}
+
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/InnerLayer/graph8c.png}
+\includegraphics[width=\textwidth]{figs/InnerLayer/graph8c_mesh.png}
+\caption{Conservative with graph norm}
+\label{fig:innerlayerGraph18c}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/InnerLayer/robust8c.png}
+\includegraphics[width=\textwidth]{figs/InnerLayer/robust8c_mesh.png}
+\caption{Conservative with robust norm}
+\label{fig:innerlayerRobust18c}
+\end{subfigure}
+\caption{Inner layer problem after 8 refinements}
+\label{fig:innerlayer8c}
+\end{figure}
+
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/InnerLayer/graphFlux.pdf}
+\caption{With graph norm}
+\label{fig:innerlayerGraphFlux}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/InnerLayer/robustFlux.pdf}
+\caption{With robust norm}
+\label{fig:innerlayerRobustFlux}
+\end{subfigure}
+\caption{Flux imbalance in inner layer solutions}
+\label{fig:innerlayer_flux}
+\end{figure}
+
+\subsection{Discontinuous Source Problem}
+
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Discontinuous/graph8nc.png}
+\caption{Nonconservative with graph norm}
+\label{fig:discontinuousGraph8nc}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Discontinuous/robust8nc.png}
+\caption{Nonconservative with robust norm}
+\label{fig:discontinuousRobust8nc}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Discontinuous/graph8c.png}
+\caption{Conservative with graph norm}
+\label{fig:discontinuousGraph8c}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Discontinuous/robust8c.png}
+\caption{Conservative with robust norm}
+\label{fig:discontinuousRobust8c}
+\end{subfigure}
+\caption{Discontinuous source problem after 8 refinements}
+\label{fig:discontinuous}
+\end{figure}
+
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Hemker/graphFlux.pdf}
+\caption{With graph norm}
+\label{fig:discontinuousGraphFlux}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Hemker/robustFlux.pdf}
+\caption{With robust norm}
+\label{fig:discontinuousRobustFlux}
+\end{subfigure}
+\caption{Flux imbalance in discontinuous source solutions}
+\label{fig:discontinuous_flux}
+\end{figure}
+
 \subsection{Hemker Problem}
@@
 \caption{Nonconservative with graph norm}
-\label{fig:hemkerGraph14nc}
+\label{fig:hemkerGraph4nc}
 \end{subfigure}
@@
 \caption{Nonconservative with robust norm}
-\label{fig:hemkerRobust14nc}
+\label{fig:hemkerRobust4nc}
 \end{subfigure}
@@
 \caption{Conservative with graph norm}
-\label{fig:hemkerGraph14c}
+\label{fig:hemkerGraph4c}
 \end{subfigure}
@@
 \caption{Conservative with robust norm}
-\label{fig:hemkerRobust14c}
+\label{fig:hemkerRobust4c}
 \end{subfigure}
@@
 \caption{Nonconservative with graph norm}
-\label{fig:hemkerGraph18nc}
+\label{fig:hemkerGraph8nc}
 \end{subfigure}
@@
 \caption{Nonconservative with robust norm}
-\label{fig:hemkerRobust18nc}
+\label{fig:hemkerRobust8nc}
 \end{subfigure}
@@
 \caption{Conservative with graph norm}
-\label{fig:hemkerGraph18c}
+\label{fig:hemkerGraph8c}
 \end{subfigure}
@@
 \caption{Conservative with robust norm}
-\label{fig:hemkerRobust18c}
+\label{fig:hemkerRobust8c}
 \end{subfigure}

### 2013-03-04 docs/Jesse/GlobalLocalTesting/paper.tex

--- 2012-10-25 docs/Jesse/GlobalLocalTesting/paper.tex
@@
 \usepackage{amssymb}
+\usepackage{amscd}
 \usepackage{listings}
@@
 \newcommand{\LRc}[1]{\left\{ #1 \right\}}
+\newcommand{\LRb}[1]{\left| #1 \right|}
+
 \newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
@@
 
-\author{Jesse Chan\textsuperscript{a}, Norbert Heuer\textsuperscript{b}, Tan Bui-Thanh\textsuperscript{a}, and Leszek Demkowicz\textsuperscript{a}}
+\newtheorem{remark}{Remark}
+
+\author{Jesse Chan\textsuperscript{a}, Jay Gopalakrishnan\textsuperscript{b}, and Leszek Demkowicz\textsuperscript{a}}
 
 %\title{$\epsilon$-explicit analysis of DPG for convection-dominated diffusion}
-\title{Globally and locally optimal test functions}
+\title{Global properties of DPG test spaces for convection-diffusion problems}
 \date{}
@@
 \begin{center}
-\textsuperscript{b} Facultad de Matem\'aticas, \\Pontificia Universidad Cat\'olica de Chile,\\
-Avenida Vicu\~na Mackenna 4860, Santiago, Chile
+\textsuperscript{b} Department of Mathematics\\Portland State University, \\
+Portland, OR 97207, USA
+%\textsuperscript{b} Facultad de Matem\'aticas, \\Pontificia Universidad Cat\'olica de Chile,\\
+%Avenida Vicu\~na Mackenna 4860, Santiago, Chile
 \end{center}
 
-\section{The ultra-weak variational formulation}
+%\tableofcontents
 
-\subsection{The adjoint equation and $L^2$ optimality}
+\section{Introduction to DPG}
 
-Assuming boundedness below of $A$, as the extra $L^2$ term disappears, we get $L^2$ optimality. The ultra-weak variational form gives
+The Discontinuous Petrov-Galerkin method was originally introduced by Demkowicz and Gopalakrishnan in 2009 as a way to attain automatic inf-sup stability for any well-posed variational problem through the construction of optimal test functions \cite{DPG2}.
+The method was later shown to be equivalent to the minimum residual method applied to the operator residual corresponding to a variational formulation \cite{DPG2, ChanHeuerBui-ThanhDemkowicz12}.
+A more detailed overview of the current state of DPG is available at \cite{overviewDPG}; we give only a brief introduction here.
+
+The derivation of the DPG method can be briefly summarized as follows: assume we are given a trial space $U$, a discrete trial space $U_h \subset U$, a Hilbert test space $V$, and a well-posed (in the inf-sup sense) variational problem: find $u\in U$  such that
+\begin{align}
+\label{variational}
+&b(u,v) = l(v), \quad \forall v\in V, 
+\end{align}
+where $b(u,v)$ is a bilinear form and $l \in V'$.
+If we identify the variational operator $B: U\rightarrow V'$ such that $\LRa{Bu,v} \coloneqq b(u,v)$, we can write the above variational formulation as an operator equation in $V'$
+\[
+Bu = l,
+\]
+where inf-sup well-posedness of the variational formulation translates to boundedness from above and below of the operator $B$.
+
+Let $u_h \in U_h$ now be a discrete approximation to $u$. Seeking the minimization of the discrete residual $\frac{1}{2} \nor{Bu_h-l}^2_{V'}$, we arrive at the normal equations 
+\begin{equation}
+\label{dualNormal}
+\LRp{Bu_h-l,B\delta u}_{V'} = 0, \quad \forall \delta u \in U_h.  
+\end{equation}
+Since $V$ is Hilbert, we can introduce the Riesz map $R_V:V \rightarrow V'$, an isometric isomorphism such that $\LRa{R_V v,\cdot} = \LRp{v,\cdot}_V$.
+By taking the inverse of the Riesz map, we can transform the normal equations in $V'$ to a set of normal equations in $V$
+\[
+\LRp{R_V^{-1}\LRp{Bu_h-l},R_V^{-1}\LRp{B\delta u}}_{V} = 0, \quad \forall \delta u \in U_h.  
+\]
+Using the definitions of the Riesz map $R_V$ and variational operator $B$, we have that
 \begin{align*}
-b(u_h,v) = \LRp{u_h,A^*v} + \LRa{\widehat{u},v} = \text{load and boundary conds} = b(u,A^*v)
+\LRp{R_V^{-1}\LRp{Bu_h-l},R_V^{-1}\LRp{B\delta u}}_{V} = 0, \quad \forall \delta u \in U_h \\
+\rightarrow \LRa{Bu_h-l,R_V^{-1}\LRp{B\delta u}}_{V} = 0, \quad \forall \delta u \in U_h \\
+\rightarrow b\LRp{u_h,R_V^{-1} B\delta u} - l\LRp{R_V^{-1} B\delta u} = 0, \quad \forall \delta u \in U_h.
 \end{align*}
-If we use for our test functions solutions of the adjoint equation $A^*v = u$ (with appropriate adjoint boundary conditions), $u_h$ is the best $L^2$ projection of the exact solution $u$ onto $U_h$.
+In other words, the minimization of the operator residual associated with a given variational form corresponds directly to a Petrov-Galerkin formulation, where test functions are determined under the so-called \textit{trial-to-test} operator $R_V^{-1}B$, which, given functions in the discrete trial space $U_h$,  returns back corresponding test functions which span the discrete test space.
 
-\section{Test norms for the convection-diffusion problem}
+Solutions $u$ to the above problem enjoy the following properties: 
+\begin{enumerate}
+\item If we define the energy norm 
+\[
+\nor{u}_E = \nor{Bu}_{V'} = \sup_{v\in V\setminus\{0\}}\frac{\LRb{b(u,v)}}{\nor{v}_V},
+\]
+then DPG is optimal in the energy norm $\nor{u}_E$, which is induced through the energy inner product
+\[
+\LRp{v,w}_E = \LRp{Bv,Bw}_{V'} = \LRp{R_V^{-1}Bv, R_V^{-1}Bw}_V.
+\]
+\item The exact energy error $\nor{u-u_h}_E$ is computable without knowing $u$ explicitly, owing to the fact that
+\[
+\nor{u-u_h}_E = \nor{B(u-u_h)}_{V'} = \nor{{l-Bu_h}}_{V'} = \sup_{v\in V\setminus\{0\}}\frac{l(v)-b(u,v)}{\nor{v}_V},
+\]
+which can be computed by first computing an \textit{error representation function} $e$ and then evaluating $\nor{e}_V$.  The error representation function is determined by solving the problem
+\[
+\LRp{e,\delta v}_V = l(\delta v)-b(u,\delta v), \quad \delta v\in V.
+\]
+This property is simply a result of the minimum residual nature of DPG; the energy error is simply the residual, measured in the proper norm.  
+\item Let $\{u_i\}_{i = 0}^{i = N}$ be discrete trial functions and $v_{u_i}$ be the corresponding optimal test functions (solutions of Problem (\ref{aux}) below).
+The discrete system resulting from DPG is symmetric positive-definite; this can be seen from the identity
+\[
+b(u_i,v_{u_j}) = \LRp{v_{u_i},v_{u_j}}_V = \LRp{v_{u_j},v_{u_i}}_V = b(u_j,v_{u_i}).
+\]
+Positive-definiteness is again a natural consequence of the minimum-residual nature of DPG.  
+\end{enumerate}
 
-Introduce the graph norm here.
+\subsection{Broken test spaces}
 
-\subsection{Local and global optimal test functions}
+To determine test functions under DPG, we must invert the Riesz map by determining $R_V^{-1} B\delta u$, which is done by solving the auxiliary variational problem
+\begin{equation}
+\label{aux}
+(v,\delta v)_V = b\LRp{\delta u,\delta v}, \quad \forall \delta v\in V.  
+\end{equation}
+Unfortunately, this amounts to both an infinite-dimensional and global problem if $V$ is not chosen carefully.
+For example, if $V = H^1(\Omega)$ and $\LRp{\cdot, \cdot }_V$ corresponded to the $H^1$ Sobolev inner product  $\LRp{v,\delta v}_{L^2(\Omega)} + \LRp{\grad v,\grad \delta v}_{L^2(\Omega)}$, solving for a single optimal test function would be equivalent to solving the Poisson equation exactly over the entire domain.
+However, we can both localize and make solving Problem~(\ref{aux}) computationally feasible by choosing for $V$ a \textit{broken} test space and by approximating the solution to (\ref{aux}) using a discrete space $V_h\subset V$.
 
-Note that globally optimal test functions only produce boundary layers at the global inflow boundary.
+We begin by assuming we are given some triangulation $\Omega_h$ of $\Omega$ such that $\bar{\Omega} = \bigcup_{K\in \Omega_h}\bar{K}$.  We can adopt for $V$ the broken test space
+\[
+V(\Oh) = \bigoplus_{K\in \Omega_h}V(K).
+\]
+If we further assume that the inner product and norm on $V$ are localizable\footnote{A localizable norm $\nor{v}_{V(\Oh)}$ can be written in the form 
+$$\nor{v}_{V(\Oh)}^2 = \sum_{K\in\Oh} \nor{v}_{V(K)}^2,$$ where $\nor{v}_{V(K)}$ is a norm over the element $K$.}, the solution to \eqref{aux} (corresponding to the inversion of the Riesz map) can now be determined locally over each element.
+In practice, these solutions are approximated by solving (\ref{aux}) over a locally conforming space $V_h$ over each element $K$, where $\dim(V_h) > \dim(U_h)$ elementwise.
+Typically, if $U_h$ is of order $p$, $V_h$ is chosen to be the corresponding $H^1$ or $H({\rm div})$ conforming space of order $p + \del p$, where $\del p \geq n$, the spatial dimension \cite{practicalDPG}.
+For this reason, we refer to $V_h$ as the \textit{enriched} space.
+We refer to this approximated test space under $V_h$ as the approximate optimal test space $V_{{\rm opt},h}$.
+\begin{remark}
+All properties of DPG carry over if $V=V_h$, the discrete inner product space, and if Problem~(\ref{aux}) is well-approximated under $V_h$, then the solution to our variational problem (\ref{variational}) over the approximate optimal test space will deliver very similar results to the solution of (\ref{variational}) over the exact optimal test space.
+\end{remark}
 
-Show representation of global test functions in local test functions using Jay's proof using orthogonal subspaces and flux test functions.
+\subsection{The ultra-weak variational formulation}
 
-\section{Numerical experiments}
+Up to now, the variational formulation has been left unspecified.
+For several reasons, we've chosen to use the \textit{ultra-weak formulation}, which results from writing the PDE as a first-order system, integrating all derivatives by parts, and identifying boundary traces as independent unknowns, similarly to hybridized DG methods.
+The formulation is given as follows: let $$\Gh = \bigcup_{K\in \Oh} \partial K$$ be the \textit{mesh skeleton}, comprising of the union of all element boundaries.
+Let $Au=f$ represents the strong form of a first-order system of PDEs; the ultra-weak formulation is then
+\begin{equation}
+\label{variationalProblem}
+b\LRp{\LRp{u,\uh},v} = \LRp{u,A_h^*v}_{\Oh} + \sum_{K \in \Oh} \LRa{\uh,v}_{\partial K} = \LRp{f,v}_{\Omega},
+\end{equation}
+where $u \in \L$, and $A_h^*$ is the formal adjoint of $A$ acting elementwise on a broken test space, and $\LRa{\uh,v}_{\partial K}$ is the duality pairing between the trace unknown $\uh$ and the trace of the test function $v$ on an element boundary.
+Under proper regularity assumptions, we have that
+$$\sum_{K \in \Oh} \LRa{\uh,v}_{\partial K} = \LRa{\uh,\jump{v}}_{\Gh}.$$    %so $\uh \in \gamma(D\LRp{A})$, the trace space of the domain of the strong operator $A$.  
+Finally, $\uh$ represents the trace of the conforming solution to $Au=f$ on the mesh skeleton $\Gh$; if we define the graph space $H_A \coloneqq \LRc{u \in U: Au\in \L},$ then $\uh$ comes from $ \widehat{H}_A(\Gh)$, the trace space of $H_A$ on $\Gh$
+\[
+\widehat{H}_A(\Gh) \coloneqq \LRc{ \left.u\right|_{\Gh}: u\in H_A}.
+\]
 
-\subsection{The effect of under-resolved boundary layers}
+Combining this variational formulation with the concept of DPG optimal test functions yields a conforming method for $u$, the field variable, and $\uh$, the trace variable.
+Optimal test functions are all determined locally, and optimal test functions corresponding to traces defined on the element boundary $\partial K$ have support over each element adjacent to $\partial K$.
+The degrees of freedom are thus coupled together globally through the optimal test functions for trace variables.
 
-\textcolor{red}{Can we quantify the effect of under-resolving boundary layers?}
+\begin{remark}
+\label{remarkDahmen}
+It is possible to apply the same minimum-residual method behind DPG in an alternative fashion by casting the normal equations as a saddle-point problem, which is the approach taken by Dahmen et al.\ in \cite{DahmenVariationalStabilization}.
+This method requires the solution of a larger global linear system than the DPG method, but can be directly applied to arbitrary variational formulations and conforming discretizations of $V$.
+\end{remark}
 
+\subsection{The graph test norm}
+
+We have not yet specified the inner product $\LRp{v,\delta v}_V$, which induces the norm defining the space $V$.
+Here, we derive two important ``canonical" test norms for the ultra-weak variational formulation.
+We begin first with the canonical norm in $U$.
+Since $\uh \in \widehat{H}_A(\Gh)$, the standard norm for $\uh$ is the so-called minimum energy extension norm defined as
+\begin{equation*}
+\|\widehat{u}\| = \inf_{w\in \widehat{H}_A(\Gamma_h),
+  \left.w\right|_{\Gh}=\widehat{u}} \|w\|_{\widehat{H}_A}.
+\end{equation*}
+The canonical norm for the group variable $\LRp{u,\uh}$ is then given by
+\[
+\|\left(u,\widehat{u}\right)\|_U^2 = \|u\|^2_{\L} + \|\widehat{u}\|^2.
+\]
+If we define the norm $\nor{v}_{V,U}$  through
+\[
+\nor{v}_{V,U}^2 = \|A_h^*v\|_{\L}^2
++\left(\sup_{\widehat{u} \in \widehat{H}_A(\Gamma_h)} \frac{\LRa{ \widehat{u},
+  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2, 
+\]
+it has been shown in \cite{Bui-ThanhDemkowiczGhattas11a, ChanHeuerBui-ThanhDemkowicz12} that the canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ induces (generates) the norm $\nor{v}_{V,U}$ in $V$; in other words, the energy norm in which DPG is optimal is equal to the canonical norm $\nor{\LRp{u,\uh}}_U$ if we choose for a test norm on $\nor{v}_{V,U}$.
+
+The canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ provides an optimal balance between the standard norms on the field $u$ and the flux $\uh$ \cite{DPG4}.
+As a result, if the induced norm $\nor{v}_{V,U}$ (namely, the optimal test norm) is used to compute optimal test functions in (\ref{aux}), the finite element error in the canonical norm is the best in the norm $\nor{u}_{U}$.
+Unfortunately, the optimal test norm is non-localizable due to the presence of the jump term $\jump{v}$.
+Since the jump terms couple elements together, the evaluation of the jump terms requires contributions from all the elements in the mesh.
+Consequently, solving for an optimal test function amounts to inverting the Riesz map over the entire mesh $\Oh$, making the optimal test norm impractical.
+
+On the other hand, since $A^*_h v \in \L$, we can use as a test norm for $v$ the broken graph test norm: 
+\[
+\nor{v}_V^2 =  \|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2,
+\]
+where we have regularized the seminorm $\nor{A_h^*v}_{\L}^2$ by adding to it the $L^2$ norm of $v$.
+
+The norm $\nor{v}_V$ can be considered as a localization of $\nor{v}_{V,U}$ to allow for the solution of optimal test functions on an element-by-element basis, and can be considered to be the canonical norm on $V$.
+In the DPG literature \cite{DPG4}, $\nor{v}_{V,U}$ is known as the {\em optimal test norm}, while $\nor{v}_{V}$ is known as the quasi-optimal or {\em graph} test norm.
+The DPG method was first shown to be well-posed under the graph test norm for the Poisson and convection-diffusion equations in \cite{analysisDPG}.
+This analysis was later extended to the large class of Friedrichs' systems in \cite{Bui-ThanhDemkowiczGhattas11b} and to Stokes in \cite{stokesDPG}.
+
+It has also been shown in \cite{stokesDPG} that $\nor{v}_{V,U}$ and $\nor{v}_V$ are equivalent norms; if the operator $A$ is bounded below such that $\nor{Au}_{\L} \geq \gamma\nor{v}_{\L}$, then the equivalence constants between $\nor{v}_{V,U}$ and $\nor{v}_V$ are $O(\gamma)$.
+This is important in context of \textit{singular perturbation problems}, which typically depend on some parameter $k\rightarrow 0$ or $k\rightarrow \infty$; if the constant $\gamma$ associated with the problem is independent of $k$, then the DPG method under the graph test norm is \textit{robust}, or equivalent to the $\L$-projection with constants independent of $k$.
+Robustness is discussed more in Section~\ref{sec:robust} in context of the convection-diffusion equation.
+
+\section{The ultra-weak formulation and globally conforming test spaces}
+
+Though DPG test functions are determined locally on an element-by-element basis, it is the global properties of the test space that determine the performance of the method.
+We motivate this statement first by deriving global conditions for the test space under which the ultra-weak variational formulation recovers an $L^2$ optimal solution, using the specific example of the convection-diffusion equation.
+
+\subsection{The convection-diffusion equation}
+
+The convection-diffusion problem models the concentration $u$ of some solvent in a convection field $\beta$ subject to diffusion of some magnitude $\epsilon > 0$ in some domain $\Omega$ with boundary $\Gamma$.
+We decompose the boundary as follows:
 \begin{align*}
-b\LRp{\LRp{u,\sigma, \uh,\fnh},\LRp{v,\tau}} = \LRp{u, \Grad_h\cdot \tau - \beta\cdot \Grad_h v}_{\Oh} + \LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad_h v}_{\Oh} + \LRa{\uh,\tau_n}_{\Gh} + \LRa{\fnh,v}_{\Gh}
+\Gamma_{\rm in} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\}, \quad {\rm
+(inflow)}\\ 
+\Gamma_{\rm out} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\},
+\quad {\rm (outflow)}\\
+\Gamma_{0} &\coloneqq \{x\in \Gamma;\beta_n(x) = 0\},
 \end{align*}
-Let $\boldsymbol U$ denote the trial variables $\{u,\sigma, \uh, \fnh\}$. For robustness in $u$, we can choose for $\LRp{v,\tau}$ the conforming solution to the adjoint equation such that 
+where $\beta_n \coloneqq \beta \cdot n$.
+
+The problem is typically written in as
 \begin{align*}
-\div \tau - \beta \cdot \grad v &= u \\
-\frac{1}{\epsilon} \tau - \grad v &= 0. 
+\div\LRp{\beta u - \epsilon \grad u} &= f, \quad \text{in } \Omega \\
+u &= u_{0}, \quad \text{on } \Gamma.
 \end{align*}
-By doing so, we recover the $L^2$ norm of $u$ from the bilinear form, such that
+The problem is especially of interest as a prototypical problem for boundary layer problems in computational fluid dynamics, as solutions to the convection-diffusion problem can, for certain boundary conditions, develop strong boundary layers of width $\epsilon$ at the outflow boundary $\Gamma_{\rm out}$.
+
+We can further write it as a system of first-order equations
+\begin{align*}
+\div\LRp{\beta u - \sigma} &= f\\
+\frac{1}{\epsilon}\sigma - \grad u &= 0.
+\end{align*}
+This first order system is the starting point for the ultra-weak variational formulation, which, under the convection-diffusion equation and prior to the application of boundary data, is given as 
+\begin{align*}
+b\LRp{\LRp{u,\sigma, \uh, \fnh}, \LRp{v,\tau}} &=\LRa{\uh,\tau_n}_{\Gh} + \LRa{\fnh,v}_{\Gh} + \\ & \LRp{u, \Grad_h\cdot \tau - \beta\cdot \Grad_h v}_{\L} + \LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad_h v}_{\L}.
+\end{align*}
+where $\fnh \coloneqq \beta_n u - \sigma_n$.  Trial and test spaces are specified to be 
+\begin{align*}
+\LRp{u,\sigma} \in \L, \fnh \in H^{-1/2}(\Gh), \uh \in H^{1/2}(\Gh)&,\\ 
+v \in H^1(\Oh), \tau \in H\LRp{\rm div, \Oh}&,
+\end{align*}
+where $H^1(\Oh)$ and $H\LRp{\rm div, \Oh}$ represent the broken $H^1$ and $H(\rm div)$ spaces over $\Oh$.
+This is discussed in more detail for the convection-diffusion equation in \cite{DPGrobustness, ChanHeuerBui-ThanhDemkowicz12}.
+
+For the case of boundary data $\uh = u_0$ on the entire boundary $\Gamma$, our variational formulation becomes
+\begin{align*}
+\LRa{\uh,\tau_n}_{\Gh^0} + \LRa{\fnh,v}_{\Gh} + \LRp{u, \Grad_h\cdot \tau - \beta\cdot \Grad_h v} + \LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad_h v} = \LRp{f,v} + \LRa{u_0,\tau_n}_{\Gamma}, 
+\end{align*}
+where $\Gh^0 = \Gh\setminus \Gamma$ is the union of all internal element edges, and is referred to as the internal skeleton, and $\Grad_h$ and $\Grad_h\cdot$ are understood to be the broken gradient and divergence, taken over each individual element.
+We have also dropped the subscript for $\LRp{\cdot,\cdot}_{L^2(\Omega)}$ and, for the rest of the paper, simply refer to the $L^2$ inner product using the notation $\LRp{\cdot,\cdot}$.
+
+For DPG, we must also specify a test norm which defines the test space.  Our focus will be on the graph test norm for convection-diffusion, which, under the ultra-weak variational formulation, 
 \[
-\nor{u}^2_{L^2(\Omega)} = b\LRp{{\boldsymbol U},\LRp{v,\tau}} = \frac{b\LRp{{\boldsymbol U},\LRp{v,\tau}}}{\nor{\LRp{v,\tau}}_V} \nor{\LRp{v,\tau}}_V \leq \nor{\boldsymbol U}_E \nor{\LRp{v,\tau}}_V
+\nor{v}_{V_{\rm graph}}^2 = \nor{\grad_h\cdot\tau - \beta \cdot \grad_h v}_{L^2(\Omega)}^2 + \nor{{\epsilon}^{-1} \tau -  \grad_h v}_{L^2(\Omega)}^2 + \nor{v}_{L^2(\Omega)}^2
 \]
-Let $\lesssim$ denote a robust bound - if $ \nor{\LRp{v,\tau}}_V \lesssim \|u\|_{L^2(\Omega)}$, then we have that
+where $\grad_h$ and $\div_h$ are understood to act elementwise.\footnote{Since $\nor{A^*_hv}$ is not positive definite on its own, we typically add an $L^2$ term for all components of the test function; however, here the $L^2$ norm of $\tau$ is neglected as it is not required to preserve positive-definiteness of the norm.}
+
+Though our focus is on the convection-diffusion equation, we will attempt to relate concepts to a more general framework and notation when possible.
+Overloading the notation $\uh \coloneqq \LRp{\uh,\fnh}$, $u \coloneqq \LRp{u,\sigma}$, and $v \coloneqq \LRp{v,\tau}$, we can define the operator $A_h^*: V(\Oh)\rightarrow \L$ through its action restricted to an individual element $K$
 \[
-\nor{u}_{L^2(\Omega)} \lesssim \nor{\boldsymbol U}_E
+\left.A_h^*v\right|_K = \LRp{\div\tau - \beta \cdot \grad v, {\epsilon}^{-1} \tau -  \grad v}, \quad \text{on } K \in \Oh.
 \]
-In other words, a necessary condition for a robust method is that the test norm measures solutions to the adjoint equations in a robust manner.
+We then have the abstract representation of both the ultra-weak variational formulation and the graph test norm as
+\begin{align*}
+b\LRp{\LRp{u,\uh},v} &\coloneqq \LRa{\uh,v} + \LRp{u,A^*_h v}_{\L} \\
+\nor{v}_V^2 &\coloneqq \nor{A_h^*v}_{\L}^2 + \nor{v}_{\L}^2
+\end{align*}
+From this point onward, we will continue to overload our abstract notation in order to connect more general concepts with the concrete example of the convection-diffusion equation.
 
-\textcolor{red}{Can we conclude that the same thing needs to happen for approximate test functions?}
+\subsection{$L^2$ optimality under the ultra-weak variational formulation}
+We will aim now to define energy settings and test/trial spaces under which the ultra-weak formulation produces $L^2$-optimal solutions for $u,\sigma$.
+Our approach focuses on the convection-diffusion equation, but we will generalize using more abstract notation when possible.
 
-If we assume that an underresolved test function behaves similarly to a test function under a larger viscosity, we expect that the term $\nor{\div \tau - \beta \cdot \grad v}_{L^2}$ still remains relatively bounded uniformly in $\epsilon$.
-However, the term $\nor{\frac{1}{\epsilon}\tau - \grad v}_{L^2}$ does not --- analytical calculations in 1D show that this term grows with the Peclet number in the element at the inflow, where the adjoint solution develops a boundary layer.
-As the boundedness of this term determines the robustness of $\sigma$, our energy norm is
+\subsubsection{Test and trial spaces}
+We begin by defining the spaces
 \begin{align*}
-\nor{\boldsymbol U}_E &\coloneqq \sup_{\LRp{v,\tau}}\LRp{\frac{\LRp{u,\Grad_h \cdot \tau - \beta \cdot \Grad_h v}_{\Omega}}{\nor{\LRp{v,\tau}}_V} + \frac{\LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad_h v}_{\Omega}}{\nor{\LRp{v,\tau}}_V} + \frac{\LRa{\fnh,v}_{\Gamma} - \LRa{\uh,\tau_n}_{\Gamma}}{\nor{\LRp{v,\tau}}_V}} \\
-&\approx \nor{u}_{L^2} + F(\text{Pe})\nor{\sigma}_{L^2} + \nor{\LRp{\uh,\fnh}}
+H_A &= \LRc{\LRp{u, \sigma} \in H^1(\Omega) \times H({\rm div};\Omega): \LRp{\div\LRp{\beta u - \sigma}, \frac{1}{\epsilon}\sigma - \grad u}  \in L^2\LRp{\Omega}}\\
+H_{A^*} &= \LRc{\LRp{v,\tau} \in H^1(\Omega)\times H({\rm div};\Omega): \LRp{\div \tau - \beta\cdot \Grad v, \frac{1}{\epsilon}\tau + \Grad v} \in L^2\LRp{\Omega}}
 \end{align*}
-where $F(\text{Pe})$ is some non-decreasing function of the Peclet number.
-Numerical experiments confirm that, for the quasi-optimal test norm, underresolution of the inflow boundary layer negatively affects only the robustness of $u$.
+Note that in these definitions, we have chosen both trial and test functions from the fully conforming spaces $H({\rm div};\Omega)$ and $H^1(\Omega)$ over $\Omega$.
+Let us define the spaces ${U} = {V} = H^1(\Omega) \times H({\rm div};\Omega)$ as the \textit{conforming} spaces for which the inter-element jumps $\LRa{\uh,\tau_n}_{\Gh^0}$ and $\LRa{\fnh,v}_{\Gh^0}$ both vanish.
+If we again overload notation by defining ${u} \coloneqq \LRp{u,\sigma}^T\in {U}$ and ${v} \coloneqq \LRp{v,\tau} \in {V}$, and define the operator $A$ and its adjoint $A^*$ through
+\[
+A{u} \coloneqq \vecttwo{\div\LRp{\beta u - \sigma}}{\frac{1}{\epsilon}\sigma - \grad u}, \quad A^*{v} \coloneqq \vecttwo{\div \tau - \beta\cdot \Grad v}{\frac{1}{\epsilon}\tau + \Grad v},
+\]
+then we can recognize $H_A$ and $H_{A^*}$ as the \textit{graph spaces} corresponding to the first-order system operator $A$ and its adjoint $A^*$.
+We can now compactly characterize the spaces $H_A$ and $H_{A^*}$
+\[
+H_A = \LRc{{u} \in {U}, A{u} \in L^2\LRp{\Omega}}, \quad H_{A^*} = \LRc{{v} \in  {V}, A^*{v} \in L^2\LRp{\Omega}}.
+\]
+%Under the ultra-weak formulation, we are free to choose $\LRp{u,\sigma} \in L^2(\Omega)$.  
+By choosing $\LRp{v,\tau}\in H_{A^*}$, we can eliminate the inter-element jumps in the ultra-weak variational formulation, such that we are left with
+\begin{align*}
+\LRa{\fnh,v}_{\Gamma} - \LRa{\uh,\tau_n}_{\Gamma} + \LRp{u, \Grad\cdot \tau - \beta\cdot \Grad v} + \LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad v} = \LRp{f,v}
+\end{align*}
+prior to the application of boundary conditions.
+
+Specifying spaces for the trace variables $\fnh$ and $\uh$ is a bit more involved.
+Note that $H_{A}$ and $H_{A^*}$ are dual to each other; denoting the trace space of $H_A$ as $\widehat{H}_A = H^{1/2}(\Gamma) \times H^{-1/2}(\Gamma)$ and defining the traces (again overloading notation) through $\widehat{v} \coloneqq \LRp{\left.v\right|_\Gamma, \left.\tau_n\right|_\Gamma} = \LRp{\widehat{v},\widehat{\tau}}$, $\widehat{u} \coloneqq \LRp{\fnh,\uh} \in \widehat{H}_A$, we are able to characterize the duality pairing over $\Gamma$ as follows: we have
+\[
+\LRa{\fnh,v} + \LRa{\uh,\tau_n} \coloneqq \LRp{\div\LRp{\beta u - \sigma},v} + \LRp{\frac{1}{\epsilon}\sigma - \grad u,\tau} - \LRp{u, \Grad\cdot \tau - \beta\cdot \Grad v} - \LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad v}
+\]
+or, using abstract operator notation
+\[
+\LRa{\widehat{u},\widehat{{v}}} = (A{u},{v})-({u},A^*{v}).
+\]
+An interpretation of the above characterization would be that the trial variables $\fnh$ and $\uh$ represent traces of functions $\LRp{\beta u - \sigma, u} \in H_A$.
+Our trial and test spaces can now be specified
+\[
+\LRp{u,\sigma}\in L^2(\Omega), \LRp{\uh,\fnh}\in H^{1/2}(\Gamma) \times H^{-1/2}(\Gamma), \LRp{v,\tau}\in H_{A^*}
+\]
+or under our more general notation,
+\[
+u\in L^2(\Omega), \widehat{u}\in \widehat{H}_{A}(\Gamma), v\in H_{A^*}
+\]
+where $\widehat{H}_{A}(\Gamma) = \LRc{\left.u\right|_\Gamma, u\in H_A}$ consists of the boundary traces of functions in $H_A$.  
+Thus, while we formally relax regularity constraints on $\LRp{u,\sigma}$ by simply requiring $\LRp{u,\sigma} \in L^2(\Omega)$, we maintain regularity constraints through our choice of spaces for the trace variables.
+
+\subsubsection{Test space boundary conditions}
+\label{L2OptTestBC}
+Having replaced the ultra-weak formulation under a broken test space with the ultra-weak formulation using a globally conforming test space, we now aim to treat boundary conditions.
+Under our model problem, boundary data $u_0$ is applied to $\uh$ on the entirety of $\Gamma$, such that our variational formulation becomes
+\[
+\LRa{\fnh,v}_{\Gamma} + \LRp{u, \Grad\cdot \tau - \beta\cdot \Grad v} + \LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad v} = \LRp{f,v} + \LRa{u_0,\tau_n}_{\Gamma}.
+\]
+We can restrict our test space\footnote{Formally speaking, we require only that $\LRa{\fnh,v}_\Gamma = 0, \forall \fnh\in H^{-1/2}(\Gamma)$.
+However, since $\left.v\right|_\Gamma \in H^{1/2}(\Gamma)$, and since the duality pairing $\LRa{\cdot,\cdot}_{H^{-1/2}(\Gamma)\times H^{1/2}(\Gamma)}$ is definite, this condition is equivalent to $\left.v\right|_\Gamma = 0$.} to $\tilde{H}_{A^*} \coloneqq \LRc{\LRp{v,\tau} \in H_{A^*}, \left.v\right|_\Gamma = 0} \subset H_{A^*}$, which reduces the formulation to
+\begin{align*}
+\LRp{u, \Grad\cdot \tau - \beta\cdot \Grad v} + \LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad v} &= \LRp{f,v} + \LRa{u_0,\tau_n}_{\Gamma}.
+\end{align*}
+If our trial space is now taken to be the discrete trial space ${U}_h$ spanned by trial functions $\phi_i = 1,\ldots,N$, by choosing our discrete test space such that 
+\begin{align*}
+\div \tau - \beta\cdot \Grad v &= u_i\\
+\frac{1}{\epsilon}\tau + \Grad v &= \sigma_i\\
+v &= 0, \quad \text{on } \Gamma,
+\end{align*}
+where $u_i$ and $\sigma_i$ are the $u$ and $\sigma$ components of the $i$th trial function $\phi_i$, then our discrete variational problem for $\LRp{u_h,\sigma_h}$ becomes
+\begin{align*}
+\LRp{u_h,u_i} + \LRp{\sigma_h,\sigma_i}  &= \LRp{u_h, \Grad\cdot \tau - \beta\cdot \Grad v} + \LRp{\sigma_h, \frac{1}{\epsilon}\tau + \Grad v}  \\
+&= \LRp{f,v} + \LRa{u_0,\tau_n}_{\Gamma} \\
+&= \LRp{u,u_i} + \LRp{\sigma,\sigma_i}
+\end{align*}
+and the solutions $u_h,\sigma_h \in {U}_h$ to our discrete variational problem are exactly the best $L^2$-approximations to the $u$ and $\sigma$.
+
+We can frame the above discussion concerning boundary conditions using a more abstract notation as well; let us define an boundary condition operator $C:\widehat{H}_{A} \rightarrow \widehat{H}_{A}$, such that boundary data is applied to the quantity $\LRa{C\widehat{u},\widehat{v}}$.
+For the convection-diffusion equation, $C\widehat{u} = \LRp{\uh,0}$, and $\LRa{C\widehat{u},\widehat{v}} \coloneqq \LRa{\uh,\tau_n}$.
+Due to the definiteness of the duality pairing $\LRa{\cdot,\cdot}$, we have that $\LRa{C\widehat{u},\widehat{v}} = \LRa{\widehat{u},C'\widehat{v}}$, where $C'$ is the conjugate of $C$ with respect to the duality pairing.
+Next, we define the space $\tilde{H}_{A^*}$ as
+\[
+\tilde{H}_{A^*} = \LRc{v\in H_{A^*}, (I-C')\widehat{v} = 0}.
+\]
+We interpret $\tilde{H}_{A^*}$ as being the subspace of $H_{A^*}$, the graph space of conforming test functions, such that the remaining boundary terms vanish after imposition of boundary data.
+
+\begin{remark}
+For non-homogeneous boundary conditions under standard finite element methods, boundary conditions are treated using lift and extension operators.
+In other words, given boundary data $u_0$ on some part of the boundary $\Gamma_0 \subset \Gamma$, then we decompose our solution $u$ into $u = E u_0 + \tilde{u}$, where $\tilde{u}$ comes from a so-called homogeneous space $\tilde{{U}} \coloneqq {U}/Eu_0$, and $Eu_0$ is a non-unique extension of the lift $u_0$ into the interior of the domain $\Omega$.
+Under a Bubnov-Galerkin formulation, the test space is the same as the trial space, and we test with a homogeneous test space $\tilde{{V}}$ as well.
+
+We still utilize the same framework under the ultra-weak formulation: $\tilde{H}_{A^*}$ corresponds to the homogeneous test space, and we still utilize lifts and extension operators in dealing with the boundary data.
+However, an important distinction between standard formulations and the ultra-weak formulation is that, for broken test spaces, the lift extends not onto the domain $\Omega_h$, but onto the internal skeleton $\Gamma_h^0$.
+Choosing globally conforming test spaces removes traces defined on the internal skeleton, and allows us to treat boundary conditions by only considering lifts defined on $\Gamma$.
+\end{remark}
+
+The key step in achieving $L^2$ optimality is to choose test functions from a subspace of $\tilde{H}_{A^*}$: by choosing for the discrete test space $V_h$
+\[
+V_h \coloneqq \LRc{v_i\in \tilde{H}_{A^*}, A^*v_i = \phi_i},
+\]
+our discrete variational problem reduces to 
+\[
+\LRp{U_h,A^*V_i} = \LRp{U_h,\phi_i} = \LRp{f,v} + \LRa{u_0,\tau_n}_{\Gamma} = \LRp{U,\phi_i}, \quad i = 1,\ldots,N,
+\]
+which we recognize as the $L^2$ projection of the solution $U$ onto ${U}_h$.
+In other words, under the ultra-weak variational formulation and a conforming test space, the discrete test space that delivers the best $L^2$-approximation is made up of solutions to the adjoint equation, with the basis functions spanning the trial space acting as loads.
+
+\begin{remark}
+We note that we do not use the space $\tilde{H}_{A^*}$ in practice to approximate test functions, as it would require additional logic differentiating between boundary and interior elements, as well as logic distinguishing between free boundary degrees of freedom and degrees of freedom on which boundary conditions are applied.
+The above discussion is mainly to motivate global features necessary for optimal test spaces.
+\end{remark}
+
+%
+%%For boundary data $\uh_0$ enforced on $\Gamma_0 \subset \Gamma$, our corresponding variational formulation is 
+%\begin{equation*}
+%b\LRp{\LRp{u,\uh},v} = \LRp{u,A_h^*v}_{\Omega} + \LRa{\uh,\jump{v}}_{\Gh} = \LRp{f,v}_{\Omega}.
+%\end{equation*}
+%We introduce the operator $C_{\rm BC}$, which is defined such that $C_{\rm BC}\uh$ is the quantity on which boundary conditions $C_{\rm BC}\uh = Cu_0$ are to be applied.
+We can then define a second operator $C$ such that $\LRa{C\uh,\jump{v}}_{\Gamma} = \LRa{\uh,\jump{v}}_{\Gamma} - \LRa{C_{\rm BC}\uh,\jump{v}}_{\Gamma}$, and our formulation becomes
+%\begin{equation*}
+%b\LRp{\LRp{u,\uh},v} = \LRp{u,A_h^*v}_{\Omega} + \LRa{\uh,\jump{v}}_{\Gh^0} + \LRa{\uh,C'\jump{v}}_{\Gamma}= \LRp{f,v}_{\Omega} - \LRa{Cu_0,v}_{\Gamma}.
+%\end{equation*}
+%where $C'$ is the adjoint of $C$ under the duality pairing $\LRa{\cdot,\cdot}$, and $\Gh^0$ is the internal skeleton, or the mesh skeleton minus the domain boundary.
+The goal of this above notation is to allow for a generalized treatment of boundary conditions, where $\LRa{C_{\rm BC}\uh,\jump{v}}_{\Gamma}$ can represent operations such as the extraction of a component of a vector-valued $\uh$ or the restriction of to a section of the boundary.
+For a more rigorous and detailed exposition of the above notation, see \cite{stokesDPG,overviewDPG}.
+%
+%We define the subspace $V_0 \subset V$ as elements of $V$ for which the remaining boundary term $\LRa{\uh,C'\jump{v}}_{\Gamma}$ vanishes: 
+%\[
+%V_0 = \{v\in V : \LRa{\uh,C'\jump{v}}_{\Gamma}= 0, \forall (\uh,0)\in U\}.
+%\]
+%For standard Galerkin formulations, this space is analogous to the homogenous space (the complement of the lift space) for essential boundary conditions.  
+%
+%Suppose now that our test functions come from a \textit{conforming} subspace of $V_0$ - in other words, that
+%\begin{align*}
+%\LRa{\uh,\jump{v}}_{\Gh^0} &= 0, \quad \forall \uh \in \gamma(D(A))
+%%\LRa{\uh,\jump{v}}_{\Gh\setminus \Gamma_0} = 0, \quad \forall \uh \in \gamma(D(A))
+%\end{align*}
+%is additionally satisfied over the internal skeleton ${\Gh^0}$.  
+%%is satisfied over $\Gh\setminus \Gamma_0$.  
+%In this case, the inter-element boundary terms vanish, $A^*_h v$ becomes $A^*v$, and the variational formulation becomes
+%\begin{align*}
+%%b\LRp{\LRp{u,\uh},v} = \LRp{u,A^*v}_{\Omega} + \LRa{\uh,\jump{v}}_{\Gamma \setminus \Gamma_0} = \LRp{f,v}_{\Omega} - \LRa{\widehat{u}_0,\jump{v}}_{\Gamma_0}.
+%%b\LRp{\LRp{u,\uh},v} = \LRp{u,A^*v}_{\Omega} = \LRp{f,v}_{\Omega} - \LRa{\widehat{u}_0,\jump{v}}_{\Gamma_0}.
+%b\LRp{\LRp{u,\uh},v} = \LRp{u,A^*v}_{\Omega} = \LRp{f,v}_{\Omega}.
+%\end{align*}
+%Let $\bar{V}$ be a conforming subspace of $V_0$ such that 
+%%$\bar{V} = \{\bar{v}\in V: \LRa{\uh,\jump{\bar{v}}}_{\Gh\setminus\Gamma_0} = 0, \forall \LRp{0,\uh}\in U\}$.  
+%$\bar{V} = \{\bar{v}\in V_0: \LRa{\uh,\jump{\bar{v}}}_{\Gh^0} = 0, \forall \LRp{0,\uh}\in U\}$.  
+%If we seek $u_h \in U_h$ and if our discrete test space is chosen to be 
+%\[
+%\bar{V}_{\rm opt} = \{\bar{v}_{\delta u} \in \bar{V}: A^*\bar{v}_{\delta u} = \delta u, \forall \delta u \in U_h\},
+%\]
+%%\[
+%%\bar{V}_{\rm opt} = \{\bar{v}_{\delta u} \in \bar{V}: \delta u \in U_h\},
+%%\]
+%%where each test function $v_{\delta u}$ satisfies the following adjoint equation 
+%%\begin{align*}
+%%A^*v_{\delta u} &= \delta u, \\
+%%\left.v_{\delta u}\right |_{\Gamma\setminus\Gamma_0} &= 0,
+%%\end{align*}
+%then our variational problem reduces to
+%\[
+%\LRp{u_h,\delta u}_{\Omega} = \LRp{f,v}_{\Omega} = \LRp{u,\delta u}_{\Omega}, \quad \forall \delta u \in U_h
+%\]
+%and the solution $u_h$ is the $L^2$ projection of the exact solution $u$ onto $U_h$.
+
+\section{Globally conforming DPG test spaces}
+
+As noted above, $L^2$ optimality is achieved when the test space possesses certain \textit{global} properties.
+An obvious question concerning DPG is how much non-local information can be gleaned from locally generated test spaces.\footnote{Global properties of the test norm are related to the adjoint equation, as shown in \cite{DPGrobustness, ChanHeuerBui-ThanhDemkowicz12}.
+However, global properties of the test space have not been explored specifically in these prior works.}
+
+First, we define the idea of \textit{weakly} conforming spaces.  For discrete trial variables $\LRp{u,\uh} \in U_h$, we denote a test function as weakly conforming if
+\[
+b\LRp{\LRp{0,\uh},v} = \LRa{\uh,\jump{v}}_{\Gh^0} = 0, \quad \forall \LRp{0,\uh} \in U_h.
+\]
+In other words, a test function is weakly conforming if its jumps are orthogonal to all trace functions in the discrete space $U_h$.
+We refer to the space of these test functions as $\tilde{V}(\Oh) = \{\tilde{v}\in V: \LRa{\uh,\jump{\tilde{v}}}_{\Gh^0} = 0, \forall \LRp{0,\uh_h}\in U_h\}$.
+
+Let $V_{\rm opt} = \{v_{\delta u} \in V: v_{\delta u}= R_V^{-1}B\delta u, \delta u \in U_h\}$ be the space of locally determined DPG test functions, and let 
+\[
+\tilde{V}_{\rm opt} = \{\tilde{v}_{\delta u} \in \tilde{V}: \tilde{v}_{\delta u} = R_{V}^{-1}B\delta u, \delta u \in U_h\}
+\]
+be the space of optimal test functions determined \textit{globally} over the weakly conforming space $\tilde{V}$.
+In other words, the optimal test functions that span $\tilde{V}_{\rm opt}$ are the result of the inversion of the Riesz operator \textit{globally}, over the entire mesh (the idea is not new - the concept of globally optimal test functions was first introduced in \cite{DPG3pub} to prove mesh-independence).
+The following lemma concerning the test space spanned by the locally computed optimal test functions of DPG was proven first by Demkowicz and Gopalakrishnan in \cite{overviewDPG}, which we reproduce briefly here:
+\begin{lemma}
+\label{lemma1}
+$\tilde{V}_{\rm opt} \subseteq V_{\rm opt}$.
+\end{lemma}
+\begin{proof}
+We note first that, because $V_{\rm opt} \subseteq V$, we can orthogonally decompose $V = V_{\rm opt} \bigoplus V_{\rm opt}^\perp$, where, for any $v_{\rm opt}\in V_{\rm opt}$, $\LRp{v_{\rm opt},v^\perp}_V = 0$ for all $v^\perp \in V_{\rm opt}^\perp$.
+Let us now choose a globally conforming test function $\tilde{v}\in \tilde{V}_{\rm opt}$.
+Since $\tilde{V}_{\rm opt} \subseteq V$, we can decompose $\tilde{v} = v_{\rm opt} + v_{\rm opt}^\perp$.
+Demonstrating that $v_{\rm opt}^\perp = 0$ proves the lemma.
+
+Let $v_{\uh} \in V_{\rm opt}$ be an optimal test function corresponding to the flux variable $\uh$.
+We can use the fact that $v_{\rm opt}^\perp \in V$ to substitute it into the definition of $v_{\uh}$.
+By definition,
+\[
+\LRp{v_{\uh},v_{\rm opt}^\perp}_{V(K)} = \LRa{\uh,v_{\rm opt}^\perp}_{\partial K} = 0,
+\]
+where $\LRp{\cdot,\cdot}_{V(K)}$ denotes an element-wise inner product, and $\LRa{\cdot,\cdot}_{\partial K}$ denotes the duality pairing between $\uh$ and $v$ over the boundary $\partial K$.
+Summing up over all $K$, we have
+\[
+\LRp{v_{\uh},v_{\rm opt}^\perp}_{V(\Oh)} = \LRa{\uh,\jump{v_{\rm opt}^\perp}}_{\Gh^0} = 0,
+\]
+Thus, we can conclude that $v_{\rm opt}^\perp \in \tilde{V}$ is weakly conforming.
+Then, by definition of the weakly conforming optimal test space $\tilde{V}_{\rm opt}$, for a conforming optimal test function $\tilde{v}_u$ corresponding to a field variable $u$, we have that
+\[
+\LRp{\tilde{v}_u,v_{\rm opt}^\perp}_{V(\Oh)} = \LRp{u,A^*_h v_{\rm opt}^\perp}_{L^2(\Omega)} = \LRp{v_u, v_{\rm opt}^\perp}_{V(K)} = \LRp{v_u, v_{\rm opt}^\perp}_{V(\Oh)} = 0,
+\]
+where $v_u$ is a non-conforming locally determined test function.  The above orthogonality conditions imply that, for the globally conforming test space $\tilde{V}_{\rm opt}$, 
+\[
+0 = \LRp{\tilde{v},v_{\rm opt}^\perp}_V = \LRp{v_{\rm opt} + v_{\rm opt}^\perp,v_{\rm opt}^\perp}_V = \LRp{v_{\rm opt}^\perp,v_{\rm opt}^\perp}_V = \nor{v_{\rm opt}^\perp}_V^2.
+\]
+\end{proof}
+
+We note that Lemma~\ref{lemma1} still holds in the case where optimal test functions spanning $V_{\rm opt}$ are approximated using $V_h$, the enriched space, so long as $V_h$ is a closed subspace of $V$.
+In other words, the space of globally optimal test functions approximated using a weakly conforming enriched space $\tilde{V}_h$ is contained within the approximate optimal test space $V_{{\rm opt},h}$.
+
+Lemma~\ref{lemma1} has an immediate consequence concerning DPG solutions under weakly conforming test spaces: 
+\begin{lemma}
+\label{lemma2}
+Let $\tilde{u}$ be the field component of the DPG solution under a weakly globally conforming optimal test space, and let $u$ be the field component of the standard DPG solution.
+Assuming both problems are uniquely solvable, $u = \tilde{u}$.
+\end{lemma}
+\begin{proof}
+This can be shown by taking the variational problem (\ref{variational}) for $u$ and $\widehat{u}$; since $\tilde{V}_{\rm opt} \subseteq V_{\rm opt}$, we can substitute in for $v$ the weakly conforming optimal test functions spanning $\tilde{V}_{\rm opt}$.
+Doing so reduces (\ref{variational}) to the problem for $\tilde{u}$.
+\end{proof}
+
+\subsection{DPG as a non-conforming method over the test space}
+
+While DPG optimal test functions under the ultra-weak variational formulation are determined locally, Lemma~\ref{lemma1} demonstrates that these test spaces are in fact weakly-conforming approximations to globally determined test spaces.
+These results are summarized in Figure~\ref{fig:diagram}.
+\begin{figure}[!h]
+\centering
+\begin{tabular}{|| c | c ||}
+\hline
+\textbf{DPG: conforming local test spaces}  & 
+\textbf{DPG: nonconforming global approximations}\\
+\hline & \\
+Begin with broken test space $V(\Oh)$ & Begin with conforming test space $V(\Omega)$\\
+$\Downarrow$ & $\Downarrow$\\ 
+Exact locally conforming test functions & Exact globally conforming test functions\\
+$\Downarrow$ & $\Downarrow$\\ 
+Use a locally conforming discretization & Weakly-conforming formulation \\
+$\Downarrow$ & $\Downarrow$  \\ 
+Non-conforming test space &  Discretize weakly-conforming space\\
+$\Downarrow$ & $\Downarrow$  \\ 
+Contains weakly-conforming test functions & Weakly-conforming test functions \\
+& \\ \hline
+\end{tabular}
+\caption{We can interpret DPG as constructing weakly-conforming approximations to globally conforming test spaces by beginning with either broken or globally conforming test spaces. }
+\label{fig:diagram}
+\end{figure}
+
+Furthermore, while Lemma~\ref{lemma1} demonstrates that global properties are present in locally determined DPG test spaces, Lemma~\ref{lemma2} emphasizes that the $L^2$ solution $u$ depends solely on global, and not local, properties of the test space.
+This is due to the fact that we can eliminate the trace component $\uh$ of the solution $\LRp{u,\uh}$ by testing only with weakly conforming global test functions.
+Under this perspective, design of the enriched space $V_h$ should focus not on resolving local but \textit{global} features of test functions.
+
+Finally, DPG can also be viewed as a non-conforming method over $V$ under another perspective: as mentioned in Remark~\ref{remarkDahmen}, work by Dahmen et al.\ in \cite{DahmenVariationalStabilization} uses the same functional setting as DPG; however, their starting point is to view the above problem into a saddle point system.
+Defining the error $e = R_V^{-1}\LRp{l-Bu} \in V'$, Problem (\ref{dualNormal}) can be written as follows: solve for $\LRp{e,u_h}$ such that
+\begin{align*}
+\LRp{e,\delta v}_V + b(u_h,\delta v)&= l(\delta v),\quad \delta v \in V\\
+b(\delta u, e) &= 0, \quad \delta u \in U_h
+\end{align*}
+The first equation defines the error representation function $e$ as the Riesz inversion of the residual; the second equation defines orthogonality of the error in the energy inner product 
+\[
+\begin{dcases}
+b(\delta u, e) = 0\\
+\forall \delta u \in U_h 
+\end{dcases}
+\Longleftrightarrow \LRa{R_V^{-1}\LRp{l-Bu},B\delta u}_{V\times V'} = 0 \Longleftrightarrow \LRp{R_V^{-1}{B\LRp{u-u_h}},R_V^{-1}B\delta u}_{V}= 0,
+\]
+where the last condition is exactly the orthogonality of error $\LRp{B\LRp{u-u_h},B\delta u}_{V'}= 0$ with respect to the dual inner product.
+
+If we use for $b(u,v)$ the ultra-weak variational formulation and use for $\LRp{\cdot,\cdot}_V$ a localizable inner product, we recover the DPG method.
+Under this saddle-point formulation, DPG takes the form
+\begin{align*}
+\LRp{e,\delta v}_{V(K)} + \LRp{u_h,A^*_h\delta v}_{L^2{\Omega}} + \LRa{\uh_h,v}_{\Gh}- l(\delta v) &= 0, \quad \delta v \in V(K),\,\, \quad \forall K\in \Oh\\
+\LRp{\delta u, A_h^*e}_{L^2(K)} &= 0, \quad \LRp{\delta u,0} \in U_h, \quad \forall K\in \Oh\\
+\LRa{\widehat{\delta u}, \jump{e}}_{\Gh} &= 0, \quad \LRp{0,\widehat{\delta u}} \in U_h
+\end{align*}
+If $\widehat{\delta u}$ comes from the space of polynomials of order $p$, then the above problem can be interpreted as a non-conforming DG method for $e$, where elements are coupled together by enforcing that inter-element jumps of the error representation $\jump{e}$ are orthogonal with respect to all polynomials up to order $p$ defined on the element edge.
+
+\subsection{The graph test norm and $L^2$-optimal test functions}
+
+We can connect DPG's weakly-conforming test functions back to the $L^2$-optimal test spaces through a variant of the graph norm.  Under a modification of the graph test norm
+\[
+\nor{v}_{\tilde{H}_{A^*}(\Omega)}^2 = \nor{A^*v}_{\L}^2 + \delta \nor{v}_{\L}^2,
+\]
+a regularizing $L^2$ term of magnitude $\delta$ is added to the seminorm term $\nor{A_h^*v}_{\L}^2$.
+In order to both guarantee positive-definiteness and to produce a localizable test norm, $\delta > 0$ is required.
+As this regularizing factor is removed in the limit $\delta \rightarrow 0$, however, we naturally recover a weakly-conforming approximation to the $L^2$-optimal test space.
+
+Recall that an operator is invertible only if it is bounded below; thus, for our problem $Au=f$ to have a solution, we require $\nor{Au}_{\L} > \gamma\nor{u}_{\L}$ for some constant $\gamma > 0$ and some arbitrary $u$.
+Classical theory gives that the adjoint is bounded below as well with the same constant
+\[
+\nor{A^*v}_{\L} > \gamma\nor{v}_{\L}, \quad v\in \tilde{H}_{A^*}(\Omega).
+\]
+If boundedness below holds, then $\nor{A^*v}_{\L}$ itself is a norm, and is equivalent to $\nor{A^*v}_{\L}^2 + \delta \nor{v}_{\L}^2$ such that
+\[
+\nor{A^*v}_{\L} \leq \nor{v}_{\tilde{H}_{A^*}(\Omega)} \leq \LRp{1+\frac{\delta}{\gamma}}\nor{A^*v}_{\L}.
+\]
+Thus, as $\delta \rightarrow 0$, $\nor{v}_{\tilde{H}_{A^*}(\Omega)}$ converges to $\nor{A^*v}_{\L}$.
+Under the test norm $\nor{A^*v}_{\L}$, globally optimal test functions $v_u$ satisfy the variational problem
+\[
+\LRp{A^* v_u, A^* \delta v}_{V(\Omega)} = \LRp{u,A^* \delta v}_{L^2(\Omega)}, \quad \forall \delta v \in \tilde{H}_{A^*}(\Omega),
+\]
+which is a least-squares formulation of the strong adjoint equation $A^* v_u = u$.  Substituting this into the ultra-weak formulation with $u$ replaced with $u_h\in U_h$ returns
+\[
+\LRp{u-u_h,A^*v_{\delta u}} = \LRp{u-u_h,\delta u} = 0, \quad \delta u \in U_h
+\]
+which we recognize as the condition under which $u_h$ is the best $L^2$-projection of the solution.
+
+In practice, DPG uses the variant on the broken graph test norm
+\[
+\nor{v}_{V}^2 = \nor{A_h^*v}_{\L}^2 + \delta \nor{v}_{\L}^2
+\]
+and approximates optimal test functions using a weakly-conforming discretization.
+We can repeat the above analysis for weakly-conforming test spaces\footnote{The difference between conforming and weakly-conforming approximations lies in the fact that the two generate different discrete boundedness-below constants $\gamma_h$.
+For a conforming method, it is known that $\gamma_h > \gamma$; for the weakly-conforming case, the relationship is less certain.
+An upcoming paper on wave propagation problems will aim to address this in more detail.} to show that, as $\delta \rightarrow 0$, DPG optimal test functions satisfy the variational problem
+\[
+\LRp{A_h^* v_u, A_h^* \delta v}_{V(\Omega_h)} = \LRp{u,A_h^* \delta v}_{L^2(\Omega)}, \quad \forall \delta v \in \tilde{V}(\Oh),
+\]
+which is nothing more than a weakly conforming approximation\footnote{We note that this property holds irregardless of boundary conditions: $L^2$-optimal test spaces satisfy certain boundary conditions that are built into the test space $\tilde{H}_{A^*}$, but a weak satisfaction of these boundary conditions by DPG test functions is automatically achieved by weak conformity.} to the least squares problem for the $L^2$-optimal test space.
+
+%\textcolor{red}{clear up confusion on spaces and $\gamma_h$}. The equivalence relation between the two is now
+%\[
+%\nor{A_h^*v}_{\L} \leq \nor{v}_{V} \leq \LRp{1+\frac{\delta}{\gamma_h}}\nor{A_h^*v}_{\L}, 
+%\]
+%where $\gamma_h \neq \gamma$ due to consistency error in introducing a weakly-conforming discretization.
+
+\section{DPG test functions for the convection-diffusion equation}
+
+The weakly conforming properties of DPG test spaces proven in Lemma~\ref{lemma1} motivate the question of how these global features manifest for specific problems.
+We explore this question in more depth in context of the convection-diffusion equation for convection-dominated regimes
+\begin{align*}
+\div\LRp{\beta u - \epsilon \grad u} &= f, \quad \text{in } \Omega \\
+u &= u_{0}, \quad \text{on } \Gamma, 
+\end{align*}
+where $\LRb{\Omega} = O(1)$, and $\epsilon \ll 1$.  Recall that the ultra-weak variational formulation for the convection-diffusion equation is given as
+\begin{align*}
+b\LRp{\LRp{u,\sigma, \uh, \fnh}, \LRp{v,\tau}} &= \LRa{\uh,\tau_n}_{\Gh} + \LRa{\fnh,v}_{\Gh}+ \\ & \LRp{u, \Grad_h\cdot \tau - \beta\cdot \Grad_h v}_{L^2\LRp{\Omega}} + \LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad_h v}_{L^2\LRp{\Omega}}.
+\end{align*}
+
+%The convection-diffusion problem models the concentration $u$ of some solvent in a convection field $\beta$ subject to diffusion of some magnitude $\epsilon$ in some domain $\Omega$ with boundary $\Gamma$.
+We decompose the boundary as follows:
+%\begin{align*}
+%\Gamma_{\rm in} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\}, \quad {\rm
+%(inflow)}\\ 
+%\Gamma_{\rm out} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\},
+%\quad {\rm (outflow)}\\
+%\Gamma_{0} &\coloneqq \{x\in \Gamma;\beta_n(x) = 0\},
+%\end{align*}
+%where $\beta_n \coloneqq \beta \cdot n$.
+%
+%The problem is typically written in second-order form as
+%\begin{align*}
+%\div\LRp{\beta u - \epsilon \grad u} &= f, \quad \text{in } \Omega \\
+%u &= u_{0}, \quad \text{on } \Gamma.
+%\end{align*}
+%The problem is especially of interest as a prototypical problem for boundary layer problems in computational fluid dynamics, as solutions to the convection-diffusion problem can, for certain boundary conditions, develop strong boundary layers of width $\epsilon$ at the outflow boundary $\Gamma_{\rm out}$.
+
+\subsection{Localization and boundary layers under the graph test norm}
+
+The graph test norm typically delivers near-optimal results - for problems of wave propagation, elasticity, and Stokes flow, DPG under the graph test norm delivers solutions nearly indistinguishable from the $L^2$ projections of the exact solution \cite{DPG4, DPGElas, stokesDPG}.
+However, when applied to the convection-diffusion problem, the graph test norm performed very poorly in comparison.
+
+This poor performance can be explained by the difficulty in approximating optimal test functions using our choice of enriched space $V_h$.
+It can be demonstrated that the optimal test functions generated under the graph test norm for convection-diffusion problems develop strong boundary layers of width $\epsilon$.
+Figure~\ref{fig:optTestBoundary} shows the result of 2D numerical experiments where a fine mesh was used to resolve an optimal test function resulting from (\ref{aux}), demonstrating the presence of strong boundary layers at the element inflow boundary $\partial K_{\rm in}$.
+All figures of optimal test functions are produced using the FEniCS codebase \cite{LoggMardalEtAl2012a}.
+
+\begin{figure}[!h]
+\centering
+\subfigure[$v$]{\includegraphics[width=5cm]{figs/u_graph_v_K.pdf}}
+\subfigure[$\tau_x$]{\includegraphics[width=5cm]{figs/u_graph_tau_x_K.pdf}}
+\subfigure[$\tau_y$]{\includegraphics[width=5cm]{figs/u_graph_tau_y_K.pdf}}
+\caption{$v$ and $\tau$ components of the 2D optimal test functions corresponding to the basis function $u=1$ on the reference element for $\epsilon = 0.01$.
+The solution has been obtained using a fine $128\times128$ mesh of triangles, with $p = 3$.
+}
+\label{fig:optTestBoundary}
+\end{figure}
+
+Under the graph norm for convection-diffusion, Problem~(\ref{aux}) over a single element is given as
+\begin{align*}
+\LRp{\LRp{v,\tau},\LRp{\delta v,\delta \tau}}_{V_{\rm graph}(K)} &= \LRp{u, \Grad_h\cdot \tau - \beta\cdot \Grad_h v}_{K} + \LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad_h v}_{(K)} \\
+&+ \LRa{\uh,\tau_n}_{\partial K} + \LRa{\fnh,v}_{\partial K}
+\end{align*}
+where $\LRp{\LRp{v,\tau},\LRp{\delta v,\delta \tau}}_{V_{\rm graph}(K)}$ is 
+\begin{align*}
+\LRp{\LRp{v,\tau},\LRp{\delta v,\delta \tau}}_{V_{\rm graph}(K)} =& \LRp{\div\tau - \beta \cdot \grad v,\div\delta \tau - \beta \cdot \grad \delta v}_{L^2(K)} \\
+&+ \LRp{{\epsilon}^{-1} \tau -  \grad v,{\epsilon}^{-1} \delta \tau -  \grad \delta v}_{L^2(K)} + \LRp{v,\delta v}_{L^2(K)} 
+\end{align*}
+
+We can transform the above problem to the reference element; applying this simple scaling argument shows that, for elements of size $h$, we can expect a boundary layer of width $h/\epsilon$ relative to a unit domain.\footnote{This is assuming that the parameter $\epsilon$ dictates the width of expected boundary layers on a unit domain.
+The strong form of the above variational problem corresponds to a reaction-diffusion system, for which we expect this assumption to hold.
+Numerical experiments also appear to confirm that the boundary layer is of width $O(\epsilon)$.}  In other words, the strength of the boundary layer is proportional to the element Peclet number ${\rm Pe} = h/\epsilon$.
+For severely underresolved meshes where $h \gg \epsilon$, this makes the approximation of optimal test functions using a simple $p$-enriched space very difficult, though specially designed $hp$-Shishkin subgrid meshes have been used to resolve such test functions with some success in \cite{DBLP:journals/procedia/NiemiCC11} (these are discussed further in Section~\ref{ShishkinSection}).
+The construction of alternative test norms in \cite{DPGrobustness, ChanHeuerBui-ThanhDemkowicz12} was motivated by the computational difficulty in applying the graph test norm to heavily convection-dominated regimes where $\epsilon \ll 1$.
+
+Consider now globally optimal test functions under the test norm, where Problem~(\ref{aux}) is solved using the weakly conforming space $\tilde{V}$.
+By the same scaling argument, strong boundary layers appear, but only at the global inflow boundary $\Gamma_{\rm in}$.
+We illustrate this in Figure~\ref{fig:optTestBoundaryGlobal}, where we use an $H^1\times H({\rm div})$-conforming finite element space to approximate the globally conforming test function.
+We note that, by approximating optimal test functions using a conforming test space, our test functions no longer produce boundary layers over every single element.
+However, in return, our optimal test functions now contain non-local information - in particular, optimal test functions for trial functions with support only in the interior of the domain now contain boundary layers at the domain inflow boundary $\Gamma_{\rm in}$.
+
+\begin{figure}[!h]
+\centering
+\subfigure[$v$]{\includegraphics[width=5cm]{figs/u_graph_v.pdf}}
+\subfigure[$\tau_x$]{\includegraphics[width=5cm]{figs/u_graph_tau_x.pdf}}
+\subfigure[$\tau_y$]{\includegraphics[width=5cm]{figs/u_graph_tau_y.pdf}}
+\caption{$v$ and $\tau$ components of the 2D optimal test functions corresponding to the piecewise constant $u=1$ with support on a quad element defined on $[.5,.7]\times[.4,.6]$ for $\epsilon = 0.01$.
+Note the presence of nonlocal behavior in the form of the boundary layer at the inflow boundary.}
+\label{fig:optTestBoundaryGlobal}
+\end{figure}
+
+In light of the non-local nature of globally optimal test functions, we might exploit the fact that, under DPG with the ultra-weak variational formulation, our locally determined test space naturally contains non-local information as well.
+By Lemma~\ref{lemma1}, we know that the globally (weakly) conforming optimal test space is contained within our locally determined optimal test space; by Lemma~\ref{lemma2}, we have that the DPG solutions under local and conforming optimal test spaces coincide up to $L^2$ field variables.
+In other words, the approximation of the field solution $u$ is solely determined by the approximation of globally optimal test functions by the weakly conforming space enriched space $\tilde{V}_h$.
+
+\section{Global effects in numerical experiments}
+
+We investigate now non-local effects present in the DPG optimal test spaces for convection-diffusion under the test norm.
+In particular, we focus on the resolution of boundary layers in optimal test functions for DPG and their effect on \textit{robustness} of discrete solutions with respect to $\epsilon$.
+Under fully resolved optimal test functions under the graph test norm, we expect the DPG method to be robust in $\epsilon$, and for non-robustness to be attributed to approximation error of test functions.
+
+\subsection{Robustness}
+\label{sec:robust}
+The difficulty encountered by most numerical and finite element methods for boundary layer solutions of convection-diffusion problems is a lack of \textit{robustness} in the diffusion parameter $\epsilon$; in other words, for a fixed resolution/number of degrees of freedom, as $\epsilon$ decreases, the finite element error degrades with respect to the best approximation error.
+This can be seen in typical error bounds for finite element methods; if finite element error is appropriately measured in some norm $\nor{\cdot}_U$, then
+\[
+\frac{\nor{u-u_h}_U}{\inf_{w_h\in U_h}\nor{u-w_h}_U} = O(\epsilon^{-1}).
+\]
+Under naive finite elements, which relies on the coercivity of the bilinear form to provide stability, the dependence of the above ratio on $\epsilon$ can be connected to the discrete coercivity constant, which (for appropriate assumptions on boundary conditions and $\beta$) is $O(\epsilon)$ with respect to the $H^1$ norm or seminorm \cite{roos2008robust}).\footnote{These assumptions can be relaxed slightly in the presence of a first order term \cite{stynesSUPG}.}
+%This degeneration of the typically manifests itself as oscillatory behavior, which can be observed in the application of the naive finite element method to the convection-dominated diffusion equation.
+This issue can be slightly alleviated through the use of Shishkin meshes which anticipate the presence of boundary layers.
+
+\subsection{Adaptivity and adjoint boundary layers}
+
+%\	textcolor{red}{Make note on how refinements are seen at the inflow.
+Cite \cite{DPG3}, \cite{DahmenVariationalStabilization}.
+Make note that the method attempts to approximate the optimal test space even when the test norm is different.}
+
+We adopt a modification of a problem first proposed by Eriksson and Johnson in \cite{Eriksson1993} and later used in \cite{DPGrobustness, ChanHeuerBui-ThanhDemkowicz12} to determine the robustness of DPG with respect to the diffusion parameter $\epsilon$.
+For the choice of $\Omega = (0,1)^2$, $f=0$, and $\beta = (1,0)^T$, the convection diffusion equation reduces to
+\[
+\pd{u}{x} - \epsilon \left(\pdd{u}{x}+ \pdd{u}{y}\right) = 0,
+\]
+which has an exact solution by separation of variables, allowing us to analyze convergence of DPG for a wide range of $\epsilon$.
+The use of adaptive quadrature was used to ensure accurate reporting of errors for solutions with boundary layers, and all computations have been done using the higher-order adaptive DPG codebase Camellia, built on the Sandia toolbox Trilinos \cite{Camellia}.
+
+For boundary conditions, we impose
+\begin{align*}
+u-\sigma_x &= u_0-\sigma_{x,0}, \quad x=0,\\
+\sigma_y &=  0, \quad y=0,1,\\
+u &= 0, \quad x=1.
+\end{align*}
+In this case, our exact solution is the series
+\[
+u(x,y) = C_0 + \sum_{n=1}^\infty C_n \frac{\exp(r_2(x-1)-\exp(r_1(x-1)))}{r_1\exp(-r_2) - r_2\exp(-r_1)}\cos(n\pi y),
+\]
+where
+\begin{align*}
+r_{1,2} &= \frac{1 \pm \sqrt{1 + 4 \epsilon\lambda_n}}{2 \epsilon},\\
+\lambda_n &= n^2\pi^2 \epsilon.
+\end{align*}
+%The constants $C_n$ depend on a given inflow condition $u_0$ at $x=0$ via the formula
+%\[
+%C_n = \int_0^1 u_0(y) \cos(n\pi y).
+%\]
+%We begin with the solution taken to be the first non-constant term of the above series.
+We set the inflow boundary condition to be exactly the value of $u-\sigma_x$ corresponding to the exact solution.
+
+\begin{figure}[h!]
+\centering
+\subfigure{
+\includegraphics[scale=.37]{figs/wallBC_exact_u.png}
+}
+\subfigure{
+\includegraphics[scale=.37]{figs/wallBC_exact_sigx.png}
+}
+\subfigure{
+\includegraphics[scale=.37]{figs/wallBC_exact_sigy.png}
+}
+\caption{Exact solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
+\end{figure}
+
+We begin first by recalling a phenomena observed early on in the application of DPG to convection-dominated diffusion problems.
+Under the functional setting of DPG, the choice of test norm defines the optimal test space, but also defines the norm in which error is measured.
+Early experiments in \cite{DPG3} by Demkowicz, Gopalakrishnan and Niemi demonstrated in computational experiments that, for naively chosen test norms, not only would the solution exhibit degeneration on a fixed mesh as $\epsilon\rightarrow 0$, but under automatic adaptivity based on the error representation function, refined meshes would tend to exhibit strong refinements at the inflow boundary.\footnote{Cohen, Dahmen and Welper reported similar results in \cite{DahmenVariationalStabilization} for a different variational formulation and test norm.
+The missing factor in choosing a well-behaved test norm appears to be the presence of the $O(1)$ streamline derivative term $\nor{\beta \grad v}_{L^2}$.}
+
+Figure~\ref{fig:nonRobustness} shows two numerical solutions of the Erikkson-Johnson problem where the inflow profile $u_{\rm in}(y) = y(1-y)$ along $x=0$ is convected from left to right, terminating with a boundary layer at the outflow $x=1$.
+The left figure shows the trial solution $u$ under a test norm introduced in \cite{DPGrobustness}, which is shown to induce a DPG method whose solutions which do not degenerate as $\epsilon\rightarrow 0$.
+The presence of refinements at the inflow under the naive test norm illuminates an interesting heuristic observation concerning DPG for convection-diffusion problems; if the form of your test norm neglects to account for boundary layers in optimal test functions, their effects will show up in the energy error, and the method will still seek to resolve the optimal test space through minimization of error via adaptive mesh refinement.
+
+\begin{figure}[!h]
+\centering
+\subfigure[Robust test norm]{\includegraphics[width=7.5cm]{figs/robust.png}}
+\subfigure[$H^1 \times H({\rm div})$ test norm]{\includegraphics[width=7.5cm]{figs/nonRobust.png}}
+\caption{An example of automatic mesh refinement under both a robust test norm (left) and a naively chosen non-robust test norm (right).
+The naively chosen test norm exhibits both degeneration of the solution and extraneous refinements at the inflow boundary.
+Both figures are produced after four automatic refinements after beginning on a uniform mesh of 4 quadratic elements with $\Delta p=3$.}
+\label{fig:nonRobustness}
+\end{figure}
+
+Motivated by the phenomena observed in Figure~\ref{fig:nonRobustness}, we tested the effect of resolving the boundary layers in globally optimal test functions through the $h$-refinement of elements adjacent to the inflow boundary.
+Under the graph test norm, we expect such globally determined test functions to exhibit strong boundary layers, but only at the inflow boundary.
+Recalling Lemma~\ref{lemma1}, we have that the weakly conforming globally optimal test space is a proper subset of the direct sum of locally optimal test spaces over each element; thus, \textit{a-priori} refinements of the mesh that anticipate the presence of an inflow boundary layer should allow for a better resolution of the global optimal test space and improve approximation properties.
+Additionally, since the solution is relatively smooth near $x=0$, we do not expect additional mesh resolution near the inflow to significantly affect the best approximation error.
+
+\begin{figure}[!h]
+\centering
+\subfigure{\includegraphics[width=8cm]{figs/errorInflow.png}}
+\subfigure{\includegraphics[width=8cm]{figs/ratioInflow.png}}
+\caption{The effects of increased mesh resolution at the inflow boundary on $L^2$ and energy error (left) and their ratio (right).
+Experiments were done beginning on a uniform mesh of 8-by-8 quadratic elements, with $\Delta p = 3$.}
+\label{fig:robustness}
+\end{figure}
+
+Figure~\ref{fig:robustness} demonstrates the effect of increased mesh resolution at the inflow boundary; under no additional inflow resolution, the ratio of $L^2$ to energy error grows as $\epsilon$ decreases, indicating a loss of robustness as discussed in Section~\ref{sec:robust}.
+However, under increased inflow resolution, the ratio can be driven down to be $O(1)$.
+We expected initially for robustness to be restored under resolution of the diffusion scale; however, for $\epsilon \leq 1e-3$, achieving an $O(1)$ ratio required an order of magnitude finer resolution than the $h = O(\epsilon)$.
+The reasons for this may lie in the difference between boundary layers in optimal test functions for field and flux variables and optimal test functions for trace variables.
+
+\subsection{Under-resolution of boundary layers in optimal test functions}
+\label{ShishkinSection}
+We note that globally optimal test functions produce strong boundary layers at the global inflow boundary.
+However, numerical experiments appear to indicate that the boundary layers in test functions for trace variables are stronger than layers in test functions for field and flux variables.
+Note that the auxiliary problem for test functions under the abstract graph test norm is
+\[
+\LRp{v,\delta v}_{V_{\rm graph}} = \LRp{A^*_h v, A^*_h \delta v}_{L^2} + \LRp{v,\delta v}_{L^2} = \LRp{u,A^*_h v} + \LRa{\uh, v}
+\]
+induces a strong problem with boundary conditions $\gamma(A^*_h v) = \LRa{\uh, v}$, where $\gamma(A^*_hv)$ is the trace resulting from integration by parts of the operator $A^*_h$.
+For the convection-diffusion equation, this translates to a boundary condition of
+\begin{align*}
+\tau_n - \beta_n v  &= \fnh\\
+\frac{1}{\epsilon}\tau_n + \pd{v}{n} &= \uh.
+\end{align*}
+where $\fnh$ and $\uh$ are the trace and flux variables for the convection-diffusion equation under the ultra-weak variational formulation.
+The presence of the $\frac{1}{\epsilon}$ term in the boundary condition further increases the strength of the boundary layer when the auxiliary problem~(\ref{aux}) is loaded with a non-zero $\uh$.
+
+Figure~\ref{fig:bl_underresolution} shows the magnitude of the $\tau$ component of optimal test functions for a trace loaded on the inflow boundary for quadratic meshes with increasing anisotropic resolution in the $x$-direction.
+Even between the over-resolved cases $h_x \approx \epsilon$, $h_x \approx 2^{-1}\epsilon$, and $h_x \approx 2^{-2}\epsilon$, the observed boundary layer in the optimal test functions continues to grow in magnitude (as evidenced by Table~\ref{table:magnitudes}, implying that mesh resolution at the diffusion scale is still insufficient to resolve these features.
+
+\begin{figure}[!h]
+\centering
+\subfigure[$128\times 128$ mesh]{\includegraphics[height=4.7cm]{figs/uhat_graph_tau_128.pdf}}
+\subfigure[$256 \times 128$ mesh]{\includegraphics[height=4.7cm]{figs/uhat_graph_tau_256.pdf}}
+\subfigure[$512\times 128$ mesh]{\includegraphics[height=4.7cm]{figs/uhat_graph_tau_512.pdf}}
+\caption{Magnitudes of the vector-valued component $\tau$ of the optimal test functions corresponding to the flux $\widehat{u}=y(1-y)$ on the boundary $x = 0$ for $\epsilon = 0.01$ over the reference element.
+}
+\label{fig:bl_underresolution}
+\end{figure}
+
+This phenomena was observed also in \cite{shishkinDPG}, where $hp$-Shishkin submeshes (discussed in \cite{SchwabBoundaryLayers}) were used to resolve optimal test functions locally over an element.
+In 1D, these meshes consist of a two small ``needle" elements of size $h=p \epsilon$, where $p$ is the polynomial order of the approximating functions (the 2D extension for quadrilateral elements in 2D is straightforward, and is given in detail in \cite{shishkinDPG}).
+Experiments using $p$-refined Shishkin subgrid meshes indicated that the relative error in the approximation of optimal test functions for traces $\uh$ on the inflow boundary did not converge to zero as the dimension of the enriched space $V_h$ was increased (unlike the relative error for optimal test functions for field variables $u$, $\sigma$, and flux $\fnh$), and it was concluded that the use of Shishkin meshes was insufficient to resolve the boundary layers present in optimal test functions for traces over inflow edges for sufficiently small $\epsilon$.
+
+\begin{table}
+  \label{table:magnitudes}
+  \begin{center}
+  \begin{tabular}{|| l || c || r   }
+    \hline
+    Mesh & Maximum value of $| \tau_{\uh} |$ for $\epsilon=.01$ \\ \hline
+    $128\times 128$ & 8.6510571  \\ \hline
+    $256\times 128$ & 38.794881  \\ \hline
+    $512\times 128$ & 50.313599  \\
+    \hline
+  \end{tabular}
+\end{center}
+\caption{Maximum magnitudes of the $\tau$ component of the optimal test functions corresponding to the flux $\widehat{u}=y(1-y)$ on the boundary $x = 0$ for $\epsilon = 0.01$ over the reference element.
+}
+\end{table}
+
+The result of this under-resolution of optimal test functions having to do with traces on the inflow boundary is an underestimation of the inflow boundary term $\LRa{\uh,\jump{v}}_{\Gamma_{\rm in}}$, which leads to the underestimation of the solution in experiments \cite{shishkinDPG}, and explains the fine mesh resolution on the inflow boundary necessary to restore robustness to the DPG method in Figure~\ref{fig:robustness}.
 
@@
 
-\begin{itemize}
-\item There are three levels at which you should look - the continuous level (the adjoint problem for $L^2$ robustness), the global level (which links the adjoint equation to the test functions), and the localized test norm (which relates local test functions to global test functions).
-\item Your test norm may induce boundary layers even when they're not necessary for adjoint $L^2$ stability.
-\item If your test norm promises global boundary layers (that affect robustness), not approximating them leads to a loss of robustness. 
-\end{itemize}
+In this paper, we show how DPG's locally constructed test space can be interpreted as a non-conforming approximation of a weakly-conforming global test space.
+Furthermore, the field solutions and trace solutions on the boundary $\Gamma$ are shown to depend \textit{only} upon properties of the non-conforming global test space; thus, when considering approximation error in test functions, resolution of global approximation error (as opposed to local approximation error) can be sufficient to produce a stable method.
 
-You have to account for the boundary layer/$\epsilon$ diffusion scale somehow - either by 
-\begin{itemize}
-\item adjusting the test norm to account for robustness (weighted test norm), which pushes the $\epsilon$ into the inflow area, 
-\item removing the continuous adjoint problem (``convection'' inflow boundary condition), which removes the boundary layer for $L^2$ stability altogether, 
-\item resolving the global boundary layers (demonstrated here and in Antii's Shishkin meshes)
-\end{itemize}
+Additionally, global properties of test spaces are given under which the ultra-weak formulation delivers the best $L^2$-approximation to the exact solution.
+A connection is made to DPG through the graph test norm, which can be viewed as a regularization of the graph seminorm through the addition of an $L^2$ term of magnitude $\delta$.
+As the regularization parameter $\delta \rightarrow 0$, DPG under this version of the graph test norm is shown to converge to a weakly-conforming approximation to the $L^2$-optimal test space.
+
+Finally, viewing DPG as an approximation to globally optimal test functions allows the construction of test spaces that focus on resolution of global features as opposed to local features.
+We illustrate this with the convection-diffusion problem, where we show that it is possible to restore robustness with respect to the diffusion parameter $\epsilon$ by neglecting the resolution of boundary layers on the element-local level and focusing on the resolution of global boundary layers in optimal test spaces.
+
+%\section{Acknowledgements}
+%
+%The authors thanks John Evans for several helpful discussions on the ideas and philosophy behind Variational Multiscale finite element methods.
+
+\bibliographystyle{plain}
+\bibliography{paper}
+
 \end{document}

### 2013-03-05 docs/Truman/LocalConservation/talk.tex
Added local conservation talk.

\documentclass[mathserif]{beamer}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{listings}
\usepackage{courier}
\usepackage{bibentry}
\usepackage{comment}
\usepackage{multirow}
\nobibliography*
\definecolor{lightlightgray}{gray}{0.95}
\definecolor{lightlightblue}{rgb}{0.4,0.4,0.95}
\definecolor{lightlightgreen}{rgb}{0.8,1,0.8}
\usetheme[secheader]{pecostalk}
\graphicspath{{figs/}}

\date{October 17-18, 2012}
% \author[T. E. Ellis]{Truman E. Ellis\\\medskip
% \small{Advisors: Leszek Demkowicz, Robert Moser\\
% Collaborators: Jesse Chan, Nate Roberts}}
\institute{The University of Texas at Austin}
\title[Locally Conservative DPG]{Locally Conservative Discontinuous 
Petrov-Galerkin for Convection-Diffusion}
% \\subtitle{With A Subtitle If Necessary}

\def\btau{\boldsymbol\tau}
\def\bsigma{\boldsymbol\sigma}
\def\bbeta{\boldsymbol\beta}
\def\blambda{\boldsymbol\lambda}

% defines newblock as null, giving compile issues otherwise
\let\newblock\relax

\newcommand{\eqdef}{\stackrel{\text{\tiny def}}{=}}

\newcommand{\NVRvect}[1]{\ensuremath\boldsymbol{#1}}
\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
\newcommand{\NVRtensor}[1]{\NVRvect{#1}}
%\newcommand{\NVRtensor}[1]{\underline{\NVRvect{#1}}}
\newcommand{\NVRnorm}[1]{\left|\left|#1\right|\right|}
\newcommand{\norm}[1]{\left|\left|#1\right|\right|}
\newcommand{\NVRgrad}{\nabla}
\newcommand{\NVRdiv}{\NVRgrad \cdot}
\newcommand{\NVRpd}[2]{\frac{\partial#1}{\partial#2}}
\newcommand{\NVRpdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
\newcommand{\NVReqdef}{\stackrel{\text{\tiny def}}{=}}

\newcommand{\NVRHgrad}{H(\text{grad})}
\newcommand{\NVRHdiv}{H(\text{div})}
\newcommand{\NVRsumm}[2]{\ensuremath\displaystyle\sum\limits_{#1}^{#2}}

\newcommand{\NVRcurl}{\nabla \times}
\newcommand{\NVRHcurl}{\ensuremath H(\text{curl})}

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\deal}{\code{deal.II}\,}

\newcommand{\pecosbold}[1]{{\color{pecos2}{#1}}}
\newcommand{\pecosreallybold}[1]{{\color{pecos6}{#1}}}

\newcommand{\FootSize}{\scriptsize}

\DeclareMathOperator*{\argmin}{arg\,min}

\renewcommand{\arraystretch}{1.2}

\begin{document}
\begin{frame}
\begin{center}
\includegraphics[width=.8\linewidth]{grand_logo}\\
\end{center}
\titlepage
\begin{flushright}
\includegraphics[scale=0.1]{asc_logo}\\
\end{flushright}
\end{frame}
\begin{comment}
My name is Truman Ellis, and I am also working in Dr. Demkowicz's group on the
discontinuous Petrov-Galerkin method. My background is in aerospace
engineering and CFD, and my goal is to help develop DPG into an attractive
method for realistic problems in computational fluid dynamics. So the goal is
to work on the Euler equations and then build on Nate and Jesse's work on
laminar Navier-Stokes with some turbulence modeling.  But before I got into
that, we thought it would be useful to study a topic that keeps coming up from
the CFD community. Is DPG locally conservative?

This is a numerical characteristic close to the heart of many CFD
practitioners, and in order for DPG to gain a certain level of acceptance
among these circles, we need to address some of these concerns. There are also
some mathematically attractive reasons to pursue local conservation. The
Lax-Wendroff theorem guarantees that a convergent numerical solution to a
system of hyperbolic conservation laws will converge to the correct weak
solution. Also, we are focusing on local conservation on the
convection-diffusion equation as a proof of concept. We are working on
extending this work to more realistic flow simulations.
\end{comment}

%===============================================================================
% NEW SLIDE
%===============================================================================
\begin{frame}
\frametitle{A Summary of DPG}
Overview of Features
\begin{itemize}
\item Robust for singularly perturbed problems
\item Stable in the preasymptotic regime
\item Designed for adaptive mesh refinement
\end{itemize}
\bigskip

DPG is a minimum residual method:
\[
u_{h} = \underset{w_{h} \in U_{h}} \argmin \,\, \frac{1}{2} 
\norm{Bw_{h}-l}_{V'}^{2}
\]
\vspace{-1em}
\[
\scalebox{1.8}{\ensuremath{\Updownarrow}}
\]
\vspace{-1em}
\[
b(u_h,R_V^{-1}B\delta u_h)
=l(R_V^{-1}B\delta u_h)
\quad\forall\delta u_h\in U_h
\]
where $v_{\delta u_h}:=R_V^{-1}B\delta u_h$ are the 
\pecosbold{optimal test functions}.
\end{frame}
\begin{comment}
For the sake of avoiding a lot of repetition and making sure we all finish on
time, I'm going to offer an extremely condensed summary of DPG. Nate and Jesse
already covered this stuff with more rigor. So what are DPG's main selling
points? Why are we interested in applying it to complicated fluid problems
(eventually). 
For one, DPG has proven very robust in the face of singularly
perturbed problems which holds promise for high Reynolds number flows.
You do not need a domain expert to craft well designed meshes for each new
problem. We are mathematically guaranteed to remain stable under very coarse
meshes while adaptively refining toward a solution.

And mathematically, how can we classify DPG? By derivations, it is a minimum
residual method. This means that through the choice of specific optimal test
functions we automatically minimize the residual in the dual norm of a
Hilbert space V. We also have a well-defined process to generate the optimal
test functions which is computationally feasible.
\end{comment}

%===============================================================================
% NEW SLIDE
%===============================================================================
\begin{frame}
\frametitle{DPG for Convection-Diffusion}
Start with the strong-form PDE.
\[
\nabla\cdot(\bbeta u)-\epsilon\Delta u = g
\]
Rewrite as a system of first-order equations.
\begin{align*}
\nabla\cdot(\bbeta u-\bsigma)&=g\\
\frac{1}{\epsilon}\bsigma-\nabla u&=\boldsymbol0
\end{align*}
Multiply by test functions and integrate by parts over each element, $K$.
\begin{align*}
-(\bbeta u-\bsigma,\nabla v)_K+((\bbeta
u-\bsigma)\cdot\mathbf{n},v)_{\partial K}&=(g,v)_K\\
\frac{1}{\epsilon}(\bsigma,\btau)_K+(u,\nabla\cdot\btau)_K
-(u,\tau_n)_{\partial K}&=0
\end{align*}
Use the ultraweak (DPG) formulation to obtain bilinear form $b(u,v)=l(v)$.
\begin{align*}
-(\bbeta u-\bsigma,\nabla v)_K&+(\hat f,v)_{\partial K}
+ \frac{1}{\epsilon}(\bsigma,\btau)_K\\
&+(u,\nabla\cdot\btau)_K
-(\hat u,\tau_n)_{\partial K}=(g,v)_K
\end{align*}
\end{frame}
\begin{comment}
With that ultra-brief refresher, we can now apply DPG to the
convection-diffusion equation. We prefer to work with systems of first order
equations. Then, multiplying the top equation by a scalar valued test
function, v, and the second by a vector valued test function tau, we can
integrate by parts over each element, K. Combining the two equations, we get
our bilinear form for convection diffusion. We seek the field variable, u and
sigma in L2, but that leaves their traces undefined. So, in a manner similar
to the hybridized DG method, we define new unknowns for our traces and fluxes,
u hat and f hat.
\end{comment}

%===============================================================================
% NEW SLIDE
%===============================================================================
\begin{frame}
\frametitle{Local Conservation}
The local conservation law in convection diffusion is 
\[
\int_{\partial K}\hat f=\int_K g\,,
\]
which is equivalent to having $\mathbf{v}_K:=\{v,\btau\}=\{1_K,\boldsymbol0\}$ in the test space.
In general, this is not satisfied by the optimal test functions. 
Following Moro et al\footnote{\FootSize \bibentry{MoroNguyenPeraire11}}, we
can enforce this condition with Lagrange multipliers:
\begin{align*}
L(u_h,\blambda) = \frac{1}{2}\norm{R_V^{-1}(Bu_h-l)}_V^2
-\sum_K\lambda_K\underbrace{\langle Bu_h-l,\mathbf{v}_K\rangle}_
{\langle\hat f, 1_K\rangle_{\partial K}-\langle g,1_K\rangle_K}\,,
\end{align*}
where $\blambda=\{\lambda_1,\cdots,\lambda_N\}$. 
\end{frame}
\begin{comment}
So what does local conservation mean for the convection-diffusion equation. We
want the integral of our fluxes over the element faces to be balanced by any
source terms in the RHS. This is equivalent to having one in the test space.
You can see this if you look at the bilinear form on the previous slide and
plug one and zero in as test functions. Unfortunately the optimal test
functions do not always span constants. It turns out we can augment our test
space with constants through the use of Lagrange multipliers. So taking a
couple of steps backward in the abstract form, we can augment our system with
the Lagrange multipliers enforcing local conservation.
\end{comment}

%===============================================================================
% NEW SLIDE
%===============================================================================
\begin{frame}
\frametitle{Local Conservation}
Finding the critical points of $L(u,\blambda)$, we get the following
equations.
\begin{align*}
\frac{\partial L(u_h,\blambda)}{\partial u_h}&=b(u_h,R_V^{-1}B\delta u_h)
-l(R_V^{-1}B\delta u_h)\\
&{\color{red}-\sum_K\lambda_K b(\delta
u_h,\mathbf{v}_K)}=0\quad\forall\delta u_h\in U_h
\end{align*}
\[
\frac{\partial
L(u_h,\blambda)}{\partial\lambda_K}=-b(u_h,\mathbf{v}_K)+l(\mathbf{v}_K)=0\quad\forall
K
\]
A few consequences:
\begin{itemize}
\item We've turned our minimization problem into a saddlepoint problem.
% \item New $\lambda_K$ DOFs can be statically condensed out.
\item Only need to find the optimal test function in the orthogonal complement
of constants. % Backup slide
\end{itemize}
\end{frame}
\begin{comment}
Now, proceeding forward again and setting the derivatives to zero, we have
turned our minimization problem into a saddle point problem. Note that we have
added extra DOFs equal to the number of mesh elements, but the structure of
the problem allows these to be statically condensed out. The most interesting
consequence of this modification (apart from enforcing local conservation) is
that we can modify the search space for our optimal test functions to be
the orthogonal complement of constants.

?? Is there a modified source term?
\end{comment}

%===============================================================================
% NEW SLIDE
%===============================================================================
\begin{frame}
\frametitle{Optimal Test Functions}
For each $\mathbf{u}=\{u,\bsigma,\hat u,\hat f\}\in\mathbf{U}_h$, find
$\mathbf{v}_{\mathbf{u}}=\{v_\mathbf{u},\btau_\mathbf{u}\}\in\mathbf{V}$ such that
\[
(\mathbf{v_u},\mathbf{w})_\mathbf{V}=b(\mathbf{u},\mathbf{w})\quad\forall\mathbf{w}\in\mathbf{V}
\]
where $\mathbf{V}$ becomes $\mathbf{V}_{p+\Delta p}$ in order to make this
computationally tractable.

Chan et al\footnote{\FootSize \bibentry{ChanHeuerThanhDemkowicz2012}}
developed the following robust norm for convection-diffusion.
\begin{minipage}[t][1.5in]{\textwidth}
\begin{align*}
\norm{(v,\btau)}^2_{\mathbf{V},\Omega_h}&=
\norm{\nabla\cdot\btau}^2+\norm{\min\left\{\frac{1}{\sqrt{\epsilon}},\frac{1}{\sqrt{|K|}}\right\}\btau}^2\\
&+\epsilon\norm{\nabla v}^2+\norm{\bbeta\cdot\nabla v}^2
\makebox[1.5in][l]{$
\only<1>{\underbrace{\color{red}{
+\norm{\min\left\{\sqrt{\frac{\epsilon}{|K|}},1\right\}v}^2
}}_{\text{no longer necessary to make this a norm}}}
\only<2>{\underbrace{\color{red}{
+\left(\int_Kv\right)^2
}}_{\text{zero mean term}}}
$}
\end{align*}
\end{minipage}
\end{frame}
\begin{comment}
So how does this affect our search for optimal test functions? The process to
compute optimal test functions is as follows. For each trial function we are
considering, we want to find the test function in an enriched space that
satisfies the following relation - that the inner product of vu with w equals
the bilinear form acting on u and w for all w in V.

The choice of norm on V can significantly affect the robustness of the
solution. Unfortunately, the optimal test norm is not localizable, and for
convection diffusion, the quasi-optimal test norm has boundary layers arising
from the adjoint and thus has approximability issues. Fortunately a
couple of collaborators developed a robust test norm for convection-diffusion.
Sadly, this norm also has its issues as the final zero order term in the
expression is somewhat troublesome. (???)

Why can we replace the L2 term with the zero mean term?
Why is zero mean more friendly than L2?
- Not mesh dependent
- No boundary layers
\end{comment}

%===============================================================================
% NEW SLIDE
%===============================================================================
\begin{frame}
\frametitle{Vortex Problem}
Does enforcing local conservation make a difference?
\begin{columns}[b]
\begin{column}{0.5\textwidth}
\begin{figure}[t]
\centering
\includegraphics<1>[width=1.0\textwidth]{rawfigs/nl_vortex_c0.png}
\includegraphics<2>[width=1.0\textwidth]{rawfigs/nl_vortex_c1.png}
\includegraphics<3>[width=1.0\textwidth]{rawfigs/nl_vortex_c2.png}
\includegraphics<4>[width=1.0\textwidth]{rawfigs/nl_vortex_c3.png}
\includegraphics<5>[width=1.0\textwidth]{rawfigs/nl_vortex_c4.png}

With Local Conservation
\end{figure}
\end{column}
\begin{column}{0.5\textwidth}
\begin{figure}[t]
\centering
\includegraphics<1>[width=1.0\textwidth]{rawfigs/nl_vortex_nc0.png}
\includegraphics<2>[width=1.0\textwidth]{rawfigs/nl_vortex_nc1.png}
\includegraphics<3>[width=1.0\textwidth]{rawfigs/nl_vortex_nc2.png}
\includegraphics<4>[width=1.0\textwidth]{rawfigs/nl_vortex_nc3.png}
\includegraphics<5>[width=1.0\textwidth]{rawfigs/nl_vortex_nc4.png}

Without Local Conservation
\end{figure}
\end{column}
\end{columns}
\end{frame}
\begin{comment}
We have some promising theoretical reasons to explicitly enforce local
conservation, but does it really make a difference in numerical experiments?
This is a vortex problem with rotating flow. The inside is relatively
constant, so we shouldn't expect the refinement routine to focus too much on
this region. 
However, without strict enforcement of local conservation, the zero order term
in the test norm causes almost uniform refinements to happen in this region.
We expect this happens because beta decays to zero in the center.

Explain theory???
\end{comment}

%===============================================================================
% NEW SLIDE
%===============================================================================
\begin{frame}
\frametitle{Hemker Problem}
\begin{columns}[b]
\begin{column}{0.5\textwidth}
\begin{figure}[t]
\centering
\includegraphics<1>[width=1.0\textwidth]{rawfigs/hemker_c0.png}
\includegraphics<2>[width=1.0\textwidth]{rawfigs/hemker_c1.png}
\includegraphics<3>[width=1.0\textwidth]{rawfigs/hemker_c2.png}
\includegraphics<4>[width=1.0\textwidth]{rawfigs/hemker_c3.png}
\includegraphics<5>[width=1.0\textwidth]{rawfigs/hemker_c4.png}
\end{figure}
\vspace{-1em}
\begin{figure}[t]
\includegraphics<1>[width=1.0\textwidth]{rawfigs/hemkermesh_c0.png}
\includegraphics<2>[width=1.0\textwidth]{rawfigs/hemkermesh_c1.png}
\includegraphics<3>[width=1.0\textwidth]{rawfigs/hemkermesh_c2.png}
\includegraphics<4>[width=1.0\textwidth]{rawfigs/hemkermesh_c3.png}
\includegraphics<5>[width=1.0\textwidth]{rawfigs/hemkermesh_c4.png}

With Local Conservation
\end{figure}
\end{column}
\begin{column}{0.5\textwidth}
\begin{figure}[t]
\centering
\includegraphics<1>[width=1.0\textwidth]{rawfigs/hemker_nc0.png}
\includegraphics<2>[width=1.0\textwidth]{rawfigs/hemker_nc1.png}
\includegraphics<3>[width=1.0\textwidth]{rawfigs/hemker_nc2.png}
\includegraphics<4>[width=1.0\textwidth]{rawfigs/hemker_nc3.png}
\includegraphics<5>[width=1.0\textwidth]{rawfigs/hemker_nc4.png}
\end{figure}
\vspace{-1em}
\begin{figure}[t]
\includegraphics<1>[width=1.0\textwidth]{rawfigs/hemkermesh_nc0.png}
\includegraphics<2>[width=1.0\textwidth]{rawfigs/hemkermesh_nc1.png}
\includegraphics<3>[width=1.0\textwidth]{rawfigs/hemkermesh_nc2.png}
\includegraphics<4>[width=1.0\textwidth]{rawfigs/hemkermesh_nc3.png}
\includegraphics<5>[width=1.0\textwidth]{rawfigs/hemkermesh_nc4.png}

Without Local Conservation
\end{figure}
\end{column}
\end{columns}
\end{frame}
\begin{comment}
This is the Hemker problem. We have a circle with a boundary condition of u=1
and a flow field which convects downstream. You will notice that we are able
to achieve a pretty decent solution with a very coarse mesh. However, as we
refine, we don't see any visible difference between standard DPG and the
locally conservative version. In fact, if you look at error outputs, the
locally conservative version registers higher absolute error at each
refinement step which reflects the fact that we are now minimizing the
residual with constraints rather than purely minimizing.
\end{comment}

%===============================================================================
% NEW SLIDE
%===============================================================================
\begin{frame}
\frametitle{High Lift Airfoil}
\begin{columns}[b]
\begin{column}{0.5\textwidth}
\begin{figure}[t]
\centering
\includegraphics<1>[width=0.85\textwidth]{rawfigs/highlift_c0.png}
\includegraphics<2>[width=0.85\textwidth]{rawfigs/highlift_c1.png}
\includegraphics<3>[width=0.85\textwidth]{rawfigs/highlift_c2.png}
\includegraphics<4>[width=0.85\textwidth]{rawfigs/highlift_c3.png}
\includegraphics<5>[width=0.85\textwidth]{rawfigs/highlift_c4.png}
\includegraphics<6>[width=0.85\textwidth]{rawfigs/highlift_c5.png}
\includegraphics<7>[width=0.85\textwidth]{rawfigs/highlift_c6.png}
\end{figure}
\vspace{-2em}
\begin{figure}[t]
\includegraphics<1>[width=0.85\textwidth]{rawfigs/highlift_mesh_c0.png}
\includegraphics<2>[width=0.85\textwidth]{rawfigs/highlift_mesh_c1.png}
\includegraphics<3>[width=0.85\textwidth]{rawfigs/highlift_mesh_c2.png}
\includegraphics<4>[width=0.85\textwidth]{rawfigs/highlift_mesh_c3.png}
\includegraphics<5>[width=0.85\textwidth]{rawfigs/highlift_mesh_c4.png}
\includegraphics<6>[width=0.85\textwidth]{rawfigs/highlift_mesh_c5.png}
\includegraphics<7>[width=0.85\textwidth]{rawfigs/highlift_mesh_c6.png}

With Local Conservation
\end{figure}
\end{column}
\begin{column}{0.5\textwidth}
\begin{figure}[t]
\centering
\includegraphics<1>[width=0.85\textwidth]{rawfigs/highlift_nc0.png}
\includegraphics<2>[width=0.85\textwidth]{rawfigs/highlift_nc1.png}
\includegraphics<3>[width=0.85\textwidth]{rawfigs/highlift_nc2.png}
\includegraphics<4>[width=0.85\textwidth]{rawfigs/highlift_nc3.png}
\includegraphics<5>[width=0.85\textwidth]{rawfigs/highlift_nc4.png}
\includegraphics<6>[width=0.85\textwidth]{rawfigs/highlift_nc5.png}
\includegraphics<7>[width=0.85\textwidth]{rawfigs/highlift_nc6.png}
\end{figure}
\vspace{-2em}
\begin{figure}[t]
\includegraphics<1>[width=0.85\textwidth]{rawfigs/highlift_mesh_nc0.png}
\includegraphics<2>[width=0.85\textwidth]{rawfigs/highlift_mesh_nc1.png}
\includegraphics<3>[width=0.85\textwidth]{rawfigs/highlift_mesh_nc2.png}
\includegraphics<4>[width=0.85\textwidth]{rawfigs/highlift_mesh_nc3.png}
\includegraphics<5>[width=0.85\textwidth]{rawfigs/highlift_mesh_nc4.png}
\includegraphics<6>[width=0.85\textwidth]{rawfigs/highlift_mesh_nc5.png}
\includegraphics<7>[width=0.85\textwidth]{rawfigs/highlift_mesh_nc6.png}

Without Local Conservation
\end{figure}
\end{column}
\end{columns}
\end{frame}
\begin{comment}
This is a problem that I initially started working on for fun. I had just
finished writing a triangular mesh reader and I was homesick for airfoil
problems. So we got this high lift airfoil profile from some folks at Boeing
and I thought I would mesh it up and just run it as a variation of the Hemker
problem. I know this is not a very realistic problem since there is no
interaction between the geometry and the flow field, but I noticed an
interesting difference between the conservative and nonconservative solutions
that was worth pointing out.
It appears that the locally conservative method is much more reluctant to
apply refinements. We use a greedy refinement algorithm which means we tag the
element with the highest energy error and refine all elements within say 20\%
of this error. This means that we can not do a DOF comparison between these
two plots. It is very obvious by the end that the nonconservative version has
a lot much nicer solution after 6 refinement steps but clearly a much greater
number of DOFs as well. It appears that the locally conservative version
interprets the maximum error element to be much higher than any surrounding
elements and thus fewer elements fall under the selection threshold. 
\end{comment}

%===============================================================================
% NEW SLIDE
%===============================================================================
\begin{frame}
\frametitle{Double Glazing Problem}
\begin{columns}[b]
\begin{column}{0.5\textwidth}
\begin{figure}[t]
\centering
\includegraphics<1>[width=1.0\textwidth]{rawfigs/doubleglazing_c0.png}
\includegraphics<2>[width=1.0\textwidth]{rawfigs/doubleglazing_c1.png}
\includegraphics<3>[width=1.0\textwidth]{rawfigs/doubleglazing_c2.png}
\includegraphics<4>[width=1.0\textwidth]{rawfigs/doubleglazing_c3.png}
\includegraphics<5>[width=1.0\textwidth]{rawfigs/doubleglazing_c4.png}
\includegraphics<6>[width=1.0\textwidth]{rawfigs/doubleglazing_c5.png}
\includegraphics<7>[width=1.0\textwidth]{rawfigs/doubleglazing_c6.png}
\includegraphics<8>[width=1.0\textwidth]{rawfigs/doubleglazing_c7.png}
\includegraphics<9>[width=1.0\textwidth]{rawfigs/doubleglazing_c8.png}

With Local Conservation
\end{figure}
\end{column}
\begin{column}{0.5\textwidth}
\begin{figure}[t]
\centering
\includegraphics<1>[width=1.0\textwidth]{rawfigs/doubleglazing_nc0.png}
\includegraphics<2>[width=1.0\textwidth]{rawfigs/doubleglazing_nc1.png}
\includegraphics<3>[width=1.0\textwidth]{rawfigs/doubleglazing_nc2.png}
\includegraphics<4>[width=1.0\textwidth]{rawfigs/doubleglazing_nc3.png}
\includegraphics<5>[width=1.0\textwidth]{rawfigs/doubleglazing_nc4.png}
\includegraphics<6>[width=1.0\textwidth]{rawfigs/doubleglazing_nc5.png}
\includegraphics<7>[width=1.0\textwidth]{rawfigs/doubleglazing_nc6.png}
\includegraphics<8>[width=1.0\textwidth]{rawfigs/doubleglazing_nc7.png}
\includegraphics<9>[width=1.0\textwidth]{rawfigs/doubleglazing_nc8.png}

Without Local Conservation
\end{figure}
\end{column}
\end{columns}
\end{frame}
\begin{comment}
Finally, we have the double glazing problem. We are starting with a single
element because we can. There are slight differences in refinement pattern
between the two options, but not very significant.
\end{comment}

%===============================================================================
% NEW SLIDE
%===============================================================================
\begin{frame}
\frametitle{Inviscid Burgers' Equation}
\vspace{-0.5em}
\[
\frac{\partial u}{\partial t}+u\frac{\partial u}{\partial
x}=0
\quad\Leftrightarrow\quad
\nabla_{x,t}\cdot\left(\begin{array}{c}
\frac{u^2}{2}\\
u
\end{array}\right)=0
\]
\vspace{-1.5em}
\begin{columns}[b]
\begin{column}{0.5\textwidth}
\begin{figure}[t]
\centering
\includegraphics<1>[width=1.0\textwidth]{rawfigs/inviscidburgers_c0.png}
\includegraphics<2>[width=1.0\textwidth]{rawfigs/inviscidburgers_c1.png}
\includegraphics<3>[width=1.0\textwidth]{rawfigs/inviscidburgers_c2.png}
\includegraphics<4>[width=1.0\textwidth]{rawfigs/inviscidburgers_c3.png}
\includegraphics<5>[width=1.0\textwidth]{rawfigs/inviscidburgers_c4.png}
\includegraphics<6>[width=1.0\textwidth]{rawfigs/inviscidburgers_c5.png}
\includegraphics<7>[width=1.0\textwidth]{rawfigs/inviscidburgers_c6.png}
\includegraphics<8>[width=1.0\textwidth]{rawfigs/inviscidburgers_c7.png}
\includegraphics<9>[width=1.0\textwidth]{rawfigs/inviscidburgers_c8.png}

With Local Conservation
\end{figure}
\end{column}
\begin{column}{0.5\textwidth}
\begin{figure}[t]
\centering
\includegraphics<1>[width=1.0\textwidth]{rawfigs/inviscidburgers_nc0.png}
\includegraphics<2>[width=1.0\textwidth]{rawfigs/inviscidburgers_nc1.png}
\includegraphics<3>[width=1.0\textwidth]{rawfigs/inviscidburgers_nc2.png}
\includegraphics<4>[width=1.0\textwidth]{rawfigs/inviscidburgers_nc3.png}
\includegraphics<5>[width=1.0\textwidth]{rawfigs/inviscidburgers_nc4.png}
\includegraphics<6>[width=1.0\textwidth]{rawfigs/inviscidburgers_nc5.png}
\includegraphics<7>[width=1.0\textwidth]{rawfigs/inviscidburgers_nc6.png}
\includegraphics<8>[width=1.0\textwidth]{rawfigs/inviscidburgers_nc7.png}
\includegraphics<9>[width=1.0\textwidth]{rawfigs/inviscidburgers_nc8.png}

Without Local Conservation
\end{figure}
\end{column}
\end{columns}
\end{frame}
\begin{comment}
This problem is slightly off-topic in that we are no longer dealing with the
convection-diffusion equation. Instead we consider the inviscid Burgers
equation which can be formulated as a nonlinear hyperbolic conservation law,
letting us relate directly to the Lax-Wendroff theorem. A common argument for
local conservation is that shock speed can be off if we don't have a
conservative method, and the Burgers' equation is often given as an example.
We choose to work with a space-time formulation where x follows the x axis and
time the y. So without going through the DPG derivation, let's just see how
our two methods behave. Apart from some slight differences in refinement
pattern, the two methods appear nearly identical.
\end{comment}

%===============================================================================
% NEW SLIDE
%===============================================================================
\begin{frame}
\frametitle{Summary}
What have we done?
\begin{itemize}
\item We've turned our minimization problem into a saddlepoint problem.
\item The change is computationally feasible.
\item Mathematically, it gets rid of troublesome term.
\end{itemize}
Does it make a difference?
\begin{itemize}
\item Enforcement changes refinement strategy.
\item Standard DPG is nearly conservative in practice.
\begin{table}
\centering
\footnotesize
\begin{tabular}{l|c|c|c|c|}
\cline{2-5}
~ & \multicolumn{2}{|c|}{Local Flux Imbalance} & \multicolumn{2}{|c|}{Global Flux Imbalance} \\
\cline{2-5}
~ & Before & After & Before & After \\
\hline
\multicolumn{1}{|c|}{Vortex} & $10^{-8}$ & $10^{-15}$ & $10^{-5}$ & $10^{-16}$ \\
\hline
\multicolumn{1}{|c|}{Hemker} & $10^{-6}$ & $10^{-14}$ & $10^{-4}$ & $10^{-14}$ \\
\hline
\multicolumn{1}{|c|}{High Lift Airfoil} & $10^{-7}$ & $10^{-14}$ & $10^{-5}$ & $10^{-14}$ \\
\hline
\multicolumn{1}{|c|}{Double Glazing} & $10^{-8}$ & $10^{-15}$ & $10^{-9}$ & $10^{-15}$ \\
\hline
\multicolumn{1}{|c|}{Inviscid Burgers} & $10^{-7}$ & $10^{-17}$ & $10^{-6}$ & $10^{-16}$ \\
\hline
\end{tabular}
\end{table}
% \begin{itemize}
% \item Hemker gives maximum flux inbalance of order $10^{-6}$ in a single
% element and $10^{-4}$ globally.
% \end{itemize}
\end{itemize}
\visible<2->{\pecosbold{We need to study the effect on real fluid dynamics.}}
\end{frame}

%===============================================================================
% NEW SLIDE
%===============================================================================
\begin{frame}
\frametitle{Questions?}
% \begin{block}{}
% \center{Thank you!} \\
% \center{Questions?}
% \end{block}
\begin{figure}
\centering
% \includegraphics<1>[width=0.8\textwidth]{rawfigs/highlift_black_nc6.png}
\includegraphics<1>[width=1.0\textwidth]{rawfigs/highlift_gray_nc6.png}
\end{figure}
\end{frame}

\bibliographystyle{plain}
{\scriptsize
\bibliography{DPG}
}

\end{document}

### 2013-03-06 docs/Truman/LocalConservation/paper.tex
Fixed results with robust norm and conservation.

@@
 solution (to the eyeball norm), as represented by
-Figure~\ref{fig:confusionGraph8c}. However, the conservative formulation with
-the robust norm seems to exhibit some noise at the right wall as seen in
-Figure~\ref{fig:confusionRobust8c}.
+Figure~\ref{fig:confusionGraph8c}.
+
+% However, the conservative formulation with
+% the robust norm seems to exhibit some noise at the right wall as seen in
+% Figure~\ref{fig:confusionRobust8c}.
 
@@
 
-If we zoom in on one of the noisy areas, as we do in
-Figure~\ref{fig:confusionRobust8c_zoom}, we see overshoots on the order of 32
-and undershoots on the order of -13, where the exact solution varies between 0
-and 1. The cause of these overshoots and undershoots is a little mystery,
-especially because they don't show up until 8 refinement steps in. We will
-explore this problem a little more when we look at the wedge problem.
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=0.6\textwidth]{figs/Confusion/robust8c_zoom.png}
-\caption{Zoomed in conservative skewed convection-diffusion problem after 8
-refinements}
-\label{fig:confusionRobust8c_zoom}
-\end{figure}
+% If we zoom in on one of the noisy areas, as we do in
+% Figure~\ref{fig:confusionRobust8c_zoom}, we see overshoots on the order of 32
+% and undershoots on the order of -13, where the exact solution varies between 0
+% and 1. The cause of these overshoots and undershoots is a little mystery,
+% especially because they don't show up until 8 refinement steps in. We will
+% explore this problem a little more when we look at the wedge problem.
+% 
+% \begin{figure}[h!]
+% \centering
+% \includegraphics[width=0.6\textwidth]{figs/Confusion/robust8c_zoom.png}
+% \caption{Zoomed in conservative skewed convection-diffusion problem after 8
+% refinements}
+% \label{fig:confusionRobust8c_zoom}
+% \end{figure}
 
@@
 \centering
-\includegraphics[width=\textwidth]{figs/Hemker/graphFlux.pdf}
+\includegraphics[width=\textwidth]{figs/Discontinuous/graphFlux.pdf}
 \caption{With graph norm}
@@
 \centering
-\includegraphics[width=\textwidth]{figs/Hemker/robustFlux.pdf}
+\includegraphics[width=\textwidth]{figs/Discontinuous/robustFlux.pdf}
 \caption{With robust norm}

### 2013-03-06 docs/Truman/LocalConservation/talk/oldSlides.tex

 %===============================================================================
 % NEW SLIDE
 %===============================================================================
 \begin{frame}
 \frametitle{Motivation}
 Why DPG?
 \begin{itemize}
 \item Robust for singularly perturbed problems.
 \item Stable in the preasymptotic regime.
 \item Perfect for adaptive mesh refinement.
 \end{itemize}
 \bigskip

 Why local conservation?
 \begin{itemize}
 \item Local conservation is a priority for the CFD community.
 \item For a system of hyperbolic conservation laws, the Lax-Wendroff theorem
 guarantees that a convergent, locally conservative numerical method converges
 to the correct weak solution.
 \end{itemize}
 \bigskip

 Why convection-diffusion?
 \begin{itemize}
 \item Model problem for Navier-Stokes.
 \end{itemize}
 \end{frame}
 \begin{comment}
 Hopefully Nate and Jesse's talks explained some of the attractions of
 developing the discontinuous Petrov-Galkerin method for fluid problems, but
 here are a couple key points.
 DPG has proved robust in the face of singularly perturbed problems which holds
 promise for high Reynold's number flows.
 You do not need a domain expert to craft well designed meshes for each new
 problem. We are mathematically guaranteed to remain stable under very coarse
 meshes while adaptively refining toward a solution.

 But if we are concerned with realistic flows, why are we worried about local
 conservation in the convection-diffusion equation. First of all, in order for
 DPG to be accepted by the CFD community, we need to pacify some of their
 concerns about local conservation - a very weighty issue among CFD
 practitioners. There are also some attractive reasons, mathematically to
 develop a locally conservative method, such as the Lax-Wendroff theorem which
 uses local conservation as one of two conditions to guarantee that a numerical
 solution converges to the weak solution of a system of hyperbolic conservation
 laws. But before we jump in and start trying to enforce local conservation in
 our solutions to the Navier-Stokes equations, we are starting with something a
 little simpler, the convection-diffusion equation.
 \end{comment}

 %===============================================================================
 % The Abstract Problem and Minimization of the Residual
 %===============================================================================
 %===============================================================================
 % NEW SLIDE
 %===============================================================================
 \begin{frame}
 \frametitle{The Abstract Problem and Minimization of the Residual}
 Take $U,V$ Hilbert.\\
 \vspace{5mm}
 We seek $u \in U$ such that
 \[
 b(u,v) = l(v) \quad \forall v \in V,
 \]
 where $b$ and $l$ are linear in $v$.  Define $B$ by $Bu = b(u,\cdot) \in V'$; $Bu$ is a linear functional on the test space $V$.\\
 \vspace{5mm}
 We seek to minimize the residual in the discrete space $U_{h} \subset U$:
 \begin{align*}
 u_{h} = \underset{w_{h} \in U_{h}} \argmin \,\, \frac{1}{2} \norm{Bw_{h}-l}_{V'}^{2}.
 \end{align*}
 \end{frame}
 \begin{comment}
 Let's first develop the abstract theory of DPG before applying it to the
 convection diffusion equation and then modifying it to enforce local
 conservation. These next couple slides should look familiar, I borrowed them
 from Nate.

 Start with two Hilbert spaces. Our problem seeks a solution u in Hilbert space
 U that satisfies this bilinear form for all test functions in V. Now define
 operator B: U -> V' through the bilinear form. Our problem can then be
 thought of as minimizing a residual in the dual space of V.
 \end{comment}

 %===============================================================================
 % NEW SLIDE
 %===============================================================================
 \begin{frame}
 \frametitle{The Abstract Problem and Minimization of the Residual}
 \begin{align*}
 u_{h} = \underset{w_{h} \in U_{h}} \argmin \,\, \frac{1}{2} \norm{Bw_{h}-l}_{V'}^{2}.
 \end{align*}

 % PATTER: ``not especially easy to work with'': non-constructive; involves taking a supremum
 Now, the dual space $V'$ is not especially easy to work with; we would prefer to work with $V$ itself.  Recalling that the Riesz operator $R_{V} : V \rightarrow V'$ defined by 
 \begin{align*}
 \langle R_{V}v, \delta v\rangle=(v,\delta v)_{V}, \quad \forall \delta v \in V,
 \end{align*}
 is an \emph{isometry}---$\norm{R_{V}v}_{V'} = \norm{v}_{V}$---we can rewrite the term we want
 to minimize as a norm in $V$:

 \begin{align*}
 \frac{1}{2} \norm{Bw_{h}-l}_{V'}^{2} &= \frac{1}{2} \norm{R_{V}^{-1}\left(Bw_{h}-l\right)}_{V}^{2}\\
                                                               &= \frac{1}{2} \left(R_{V}^{-1}\left(Bw_{h}-l\right), R_{V}^{-1}\left(Bw_{h}-l\right) \right)_{V}.
 \end{align*}
 \end{frame}
 \begin{comment}
 Working in the dual space is not especially conducive to developing a
 numerical method, but through the Riesz representation theorem, we can
 associate every member of the dual space with a member of V through the Riesz
 map which is defined by the choice of norm on V. This is an isometry, meaning
 that norms are preserved after the map.

 Now, using the inverse Riesz map, we can reframe our problem as an inner
 product on the V space.
 \end{comment}

 %===============================================================================
 % NEW SLIDE
 %===============================================================================
 \begin{frame}
 \frametitle{The Abstract Problem and Minimization of the Residual}
 We seek to minimize
 \begin{align*}
 \frac{1}{2} \left(R_{V}^{-1}\left(Bw_{h}-l\right), R_{V}^{-1}\left(Bw_{h}-l\right) \right)_{V}.
 \end{align*}
 The first-order optimality condition requires that the G\^ateaux derivative be equal to zero for minimizer $u_{h}$; assuming $B$ is linear, we have
 \begin{align*}
 \left(R_{V}^{-1}\left(Bu_{h}-l\right), R_{V}^{-1}B \delta u_{h} \right)_{V} = 0, \quad \forall \delta u_{h} \in U_{h}.
 \end{align*}
 By the definition of $R_{V}$, this is equivalent to
 \begin{align*} % PATTER: use the phrase ``duality pairing''
 \langle Bu_{h} - l, R_{V}^{-1}B \delta u_{h} \rangle = 0 \quad \forall \delta u_{h} \in U_{h}.
 \end{align*}
 \end{frame}
 \begin{comment}
 So the goal is to minimize this inner product. Obviously, the Gateaux
 derivative will be zero at the minimizer. And by definition of the Riesz
 map, we can turn this inner product into a duality pairing.
 \end{comment}

 %===============================================================================
 % NEW SLIDE
 %===============================================================================
 \begin{frame}
 \frametitle{The Abstract Problem and Minimization of the Residual}
 We have:
 \begin{align*}
 \langle Bu_{h} - l, R_{V}^{-1}B \delta u_{h} \rangle = 0 \quad \forall \delta u_{h} \in U_{h}.
 \end{align*}
 Now, if we identify $v_{\delta u_{h}} = R_{V}^{-1}B \delta u_{h}$ as a test function, we can rewrite this as
 \begin{align*}
 b(u_{h},v_{\delta u_{h}}) &= l(v_{\delta u_{h}}).
 \end{align*}

 Thus, the discrete solution that minimizes the residual is exactly attained by
 testing the original equation with appropriate test functions.  We call these
 \pecosbold{optimal test functions}.\footnote{\FootSize \bibentry{DPG2}}
 \end{frame}
 \begin{comment}
 We are getting close to a recognizable bilinear form again. If we now identify
 our test function as the inverse Riesz map applied to B applied to delta uh,
 we get a bilinear form with a very specific test function that minimizes the
 residual. We call these optimal test functions.
 \end{comment}

 %===============================================================================
 % NEW SLIDE
 %===============================================================================
 \begin{frame}
 \frametitle{DPG for Convection-Diffusion}
 Combining the two equations, we arrive at the bilinear form.
 \bigskip

 Find $\mathbf{u}=\{u,\bsigma,\hat u,\hat f\}\in\mathbf{U}$
 such that
 \[
 b(\mathbf{u},\mathbf{v}) =
 l(\mathbf{v})\quad\forall\mathbf{v}=\{v,\btau\}\in\mathbf{V}
 \]
 where $b$ and $l$ are linear in $\mathbf{v}$ and
 \[
 b(\mathbf{u},\mathbf{v}) =
 \int_K-(\bbeta u-\bsigma)\cdot\nabla v+\frac{1}{\epsilon}\bsigma\cdot\btau+u\nabla\cdot\btau
 +\int_{\partial K}\hat f v-\hat u\btau\cdot n\,,
 \]
 \[
 l(\mathbf{v})=\int_K gv\,,
 \]
 \[
 \begin{array}{lll}
 u\in L^2(K) & \hat u\in H^1(K)|_{\partial K} & v\in H^1(K)\\
 \bsigma\in \mathbf{L}^2(K) & \hat f\in H(div,K)|_{\partial K} & \btau\in H(div,K)\\
 \end{array}\,.
 \]
 Define $B$ by $B\mathbf{u}=b(\mathbf{u},\cdot)\in\mathbf{V}'$.
 \end{frame}

### 2013-04-15 docs/Truman/LocalConservation/paper/paper.tex
Added Intro to Turbulence Talk

--- 2013-03-06 docs/Truman/LocalConservation/paper.tex
@@
 \section{Intoduction}
-The discontinuous Petrov-Galerkin (DPG) methd with optimal test functions has
+The discontinuous Petrov-Galerkin (DPG) method with optimal test functions has
 been under active development for convection-diffusion type systems
 \cite{DPG1, DPG2, DPG3, DPG5, DemkowiczHeuer, ChanHeuerThanhDemkowicz2012,
-MoroNguyenPeraire11}. In this paper, we develop a locally conservative
+MoroNguyenPeraire11}. In this paper, we develop a theory for the locally conservative
 formulation of DPG for convection-diffusion type equations and supplement this
-with numerical results.
+with extensive numerical results.
 
@@
 least squares finite elements with a twist. The key difference is that least
-square methods seek to minimize the residual of the solution in some Hilbert
-space norm, while DPG seeks the minimization in a dual norm through the
+square methods seek to minimize the residual of the solution in the $L^2$
+norm, while DPG seeks the minimization in a dual norm realized through the
 inverse Riesz map. Exact mass conservation has been an issue that has plagued
@@
 used to try to adress this. Chang and Nelson\cite{ChangNelson1997} developed
-the 'restricted LSFEM'\cite{ChangNelson1997} by augmenting the least squares
+the \emph{restricted LSFEM}\cite{ChangNelson1997} by augmenting the least squares
 equations with a Lagrange multiplier explicitly enforcing mass conservation
@@
 \]
-we can use the Riesz inverse to minimize on $V$ rather than its dual:
+we can use the Riesz inverse to minimize in the $V$-norm rather than its dual:
 \begin{equation}
@@
 Now, we can identify $v_{\delta u_h}\coloneqq R_V^{-1}B\delta u_h$ as the
-optimal test function for trial function $u_h$ and we can rewrite
+optimal test function for trial function $\delta u_h$. Define $T:=R_V^{-1}B:U_h\rightarrow V$ as the trial-to-test operator. Now we can rewrite
 \eqnref{DPGbilinearform} as
@@
 \eqnref{optimaltestproblem} still requires the inversion of the
-infinite-dimensional Riesz map, but approximating $V$ by finite
+infinite-dimensional Riesz map, but approximating $V$ by a finite
 dimensional $V_h$ which is of a higher polynomial degree than $U_h$ (hence
@@
 such that
-\begin{equation}
+\begin{align}
 \label{eq:variationalFormulation}
--(\bbeta u-\bsigma,\nabla v)_K+(\hat t,v)_{\partial K}
+\underbrace{-(\bbeta u-\bsigma,\nabla v)_K+(\hat t,v)_{\partial K}
 + \frac{1}{\epsilon}(\bsigma,\btau)_K
 +(u,\nabla\cdot\btau)_K
--(\hat u,\tau_n)_{\partial K}=(f,v)_K \\
-\end{equation}
+-(\hat u,\tau_n)_{\partial K}}_{b(\mathbf{u}, \mathbf{v})}
+&=\underbrace{\:(f,v)_K\genfrac{}{}{0pt}{}{}{}}_{l(\mathbf{v})} &\text{in }\Omega \\
+u&=0 &\text{on }\Gamma\\
+\end{align}
 for all $\bs v:=(v,\btau)\in
-\bs V:=H^1(\Omega_h)\times\bfH(\text{div},\Omega_h)$. Thus, our bilinear form
-is $b(\bs u,\bs v)=l(\bs v)$.
-
-Let $\bs U_h:=U_h\times\bs S_h\times\hat U\times\hat F\subset L^2(\Omega_h)\times\bs
+\bs V:=H^1(\Omega_h)\times\bfH(\text{div},\Omega_h)$.
+
+Let $\bs U_h:=U_h\times\bs S_h\times\hat U_h\times\hat F_h\subset L^2(\Omega_h)\times\bs
 L^2(\Omega_h)\times H^{\frac{1}{2}}(\Gamma_h)\times H^{-\frac{1}{2}}(\Gamma_h)$
@@
 L(\bs u_h,\lambda_k)=\frac{1}{2}\norm{R_V^{-1}(b(\bs
-u_h,\cdot)-(f,\cdot))}^2_{\bs V}-\sum_K\lambda_K(b(\bs u_h,1_K)-l(1_K))\,.
+u_h,\cdot)-(f,\cdot))}^2_{\bs V}-\sum_K\lambda_K(b(\bs u_h,(1_K,\bs0))-l((1_K,\bs0)))\,,
 \label{eq:lagrangian}
 \end{equation}
-
-Taking the G\^ateaux derivative as before, we arrive at the following system
+where $(1_K,\bs0)$ is the test function in which $v=1$ on element $K$ and 0 elsewhere and $\btau=\bs0$ everywhere.
+
+Taking the G\^ateaux derivatives as before, we arrive at the following system
 of equations:
@@
 \begin{array}[c]{rll}
-b(\bs u_h,T(\delta\bs u_h))-\sum_K\lambda_K b(\bs u_h,1_K)
+b(\bs u_h,T(\delta\bs u_h))-\sum_K\lambda_K b(\bs u_h,(1_K,\bs0))
 &=(f,T(\delta\bs u_h)) & \forall\delta\bs u_h\in\bs U_h\\
-b(\bs u_h,1_K) &=(f,1_K) & \forall K\,,
+b(\bs u_h,(1_K,\bs0)) &=(f,(1_K,\bs0)) & \forall K\,,
 \end{array}
@@
 \end{equation}
-where $T:=R_V^{-1}B:\bs U_h\rightarrow\bs V$ is the trial-to-test operator.
+where $T:=R_V^{-1}B:\bs U_h\rightarrow\bs V$ is the same trial-to-test operator as in the original formulation.
 
@@
 $\btau_{\delta\bs u_h}$ when $T(\delta u_h)\in \bs H(\text{div},\Omega_h)$.
-Then, putting \ref{eq:conservativeSystem} into more concrete terms for
+Then, putting \eqref{eq:conservativeSystem} into more concrete terms for
 convection-diffusion, we get:
@@
 -\langle\hat u,\taudeltau\cdot\bs n\rangle\\
--\sum_K\lambda_K (\delta\hat t,1_K)
+-\sum_K\lambda_K (\delta\hat t,(1_K,\bs0))
 &=(f,\vdeltau) & \forall\delta\bs u_h\in\bs U_h\\
-b(\bs u_h,1_K) &=(f,1_K) & \forall K\,.
+\langle\hat t,(1_K,\bs0)\rangle &=(f,(1_K,\bs0)) & \forall K\,.
 \end{array}
@@
 \begin{align}
-(\nabla\cdot\taudeltau,\nabla\cdot\delta\btau)_K
-&+\min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}(\taudeltau,\delta\btau)_K
+(\nabla\cdot\taudeltau,&\nabla\cdot\delta\btau)_K
++\min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}(\taudeltau,\delta\btau)_K
 +\epsilon(\nabla\vdeltau,\nabla \delta v)_K
-+(\bbeta\cdot\nabla\vdeltau,\bbeta\cdot\nabla \delta v)_K\\
++(\bbeta\cdot\nabla\vdeltau,\bbeta\cdot\nabla \delta v)_K\nonumber\\
 &+\alpha\min\left\{\sqrt{\frac{\epsilon}{|K|}},1\right\}(\vdeltau,\delta v)_K
+=b(\delta\bs u_h,(\delta v,\delta\btau))
 \quad\quad\forall\delta v\in\HOneK,\,\delta\btau\in\HdivK\,,
@@
 \hat F_h=\hat F_h^c\oplus\hat F_h^{nc}\,,\quad\hat 
-F_h^{c}:=\{\hat t:\langle\hat t,1_K\rangle=0\quad\forall K\}\,.
+F_h^{c}:=\{\hat t:\langle\hat t,(1_K,\bs0)\rangle=0\quad\forall K\}\,.
 \label{eq:decomposition}
@@
 This may be accomplished by employing for fluxes in $\hat F_h^{c}$ traces of
-curls, $\nabla\times\phi$. Restricting ourselves to $\delta\hat t\in\hat
+curls, $\nabla\times\phi$.
+
+In practice, we solve \eqref{eq:conservativeConfusionSystem} as a fully 
+coupled system of equations, but for didactic purposes, we can examine it 
+one piece at a time. If we restrict \eqref{eq:conservativeConfusionSystem}$_1$
+to $\delta\hat t\in\hat F_h^{nc}$, the Lagrange multiplier term drops out and we 
+left with a system that we can solve for $u_h$, $\bsigma_h$, $\hat u_h$, and 
+$\hat t_h^c\in\hat F^c_h$.
+
+Restricting ourselves to $\delta\hat t\in\hat
 F_h^{c}$ in \eqref{eq:conservativeConfusionSystem}$_1$, we obtain a system  of
@@
 system of equations that can be solved for Lagrange multipliers $\lambda_K$.
+
 Additionally, we can pass in local problem \eqref{eq:localSolve} with
@@
 \eqref{eq:conservativeConfusionSystem}$_1$ is orthogonal to constants. 
+Mathematically, we are dealing with equivalence classes of functions, but in order 
+to obtain a single function that we can deal with numerically, we replace the alpha 
+term with a zero mean scaling condition to obtain the new test norm,
+\begin{align}
+(\nabla\cdot\taudeltau,&\nabla\cdot\delta\btau)_K
++\min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}(\taudeltau,\delta\btau)_K
+\nonumber\\
+&+\epsilon(\nabla\vdeltau,\nabla \delta v)_K
++(\bbeta\cdot\nabla\vdeltau,\bbeta\cdot\nabla \delta v)_K
++\frac{1}{|K|^2}\int_K\vdeltau\delta v\,,
+\label{eq:localSolveMod}
+\end{align}
+where the $\frac{1}{|K|^2}$ coefficient is needed to make the zero mean term 
+scale correctly with $h$. Numerically this helps a good deal with the condition
+numbers of the local solve.
+
 It is convenient to be able to take $\alpha\rightarrow0$ as we will see in
@@
 \bibliographystyle{plain}
-\bibliography{../DPG}
+\bibliography{../../DPG}
 \end{document}

### 2013-04-29 docs/Jesse/SIAM CSE13/travelReport.tex
adding siam/rice talks

\documentclass[letterpaper,10pt]{article}

% last updated 1/14/07
\begin{document}
\author{Jesse Chan}
\title{Professional development travel report}
\maketitle

The SIAM CSE-13 conference is a conference held by the Society of Industrial and Applied Mathematics every two years, and seeks to enable in-depth discussions on a variety of computational efforts on problems in science and engineering.  The conference also seeks to foster the interdisciplinary culture required to meet large-scale challenges, and promote the training of the next generation of computational scientists.

Attending the 2013 SIAM CSE conference has benefited me professionally in several ways.  I attended a Student Career seminar, where I was able to ask four panelists (representing industry, academia, and the National Laboratories) several questions about careers in the computational sciences.  In particular, I was able to gain a better understanding of both the strengths and weaknesses of having a strongly interdisciplinary degree, as well as how to overcome those weaknesses in applications (particularly to academia and industry).

I was able to hold in-depth discussions with several previous graduate students on the current state of their industry and company.  In particular, I was able to gauge the effect of recent policy changes in the DOE (concerning austerity measures and budget cuts that affect research grants to new and innovative small businesses) that may affect several companies in the upcoming years.

Finally, I was able to form new connections and be exposed to a broader set of research topics at the National Laboratories by giving a talk during a minisymposium session.  The session was organized primarily by research staff at Sandia National Laboratories, and the talks given were focused largely on problems of transport, rather than my standard area of high-order finite element methods.  In this way, I was able to both converse with other researchers on the applicability of my own method to problems of interest at the national and industrial level.

The author would like to thank the CSEM Program for their Graduate School Professional Development Award that helped make this possible.

\end{document}

### 2013-04-29 docs/Jesse/HeuerPaper/responseForReviewers.tex
updating heuer paper

%\documentclass[11pt,onecolumn]{scrartcl}
\documentclass{letter}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
\usepackage[top=2cm,bottom=3cm,left=2.5cm,right=2cm]{geometry}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{array}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage[textsize=footnotesize,color=green]{todonotes}
\usepackage{algorithm, algorithmic}
\usepackage{array}
\usepackage{bm}
\usepackage{letterbib}
\usepackage{tikz}
%\usepackage{subfigure}
\usepackage[normalem]{ulem}

\newcommand{\bs}[1]{\boldsymbol{#1}}
\DeclareMathOperator{\diag}{diag}

\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}

\newcommand{\tablab}[1]{\label{tab:#1}}
\newcommand{\tabref}[1]{Table~\ref{tab:#1}}

\newcommand{\theolab}[1]{\label{theo:#1}}
\newcommand{\theoref}[1]{\ref{theo:#1}}
\newcommand{\eqnlab}[1]{\label{eq:#1}}
\newcommand{\eqnref}[1]{\eqref{eq:#1}}
\newcommand{\seclab}[1]{\label{sec:#1}}
\newcommand{\secref}[1]{\ref{sec:#1}}
\newcommand{\lemlab}[1]{\label{lem:#1}}
\newcommand{\lemref}[1]{\ref{lem:#1}}

\newcommand{\mb}[1]{\mathbf{#1}}
\newcommand{\mbb}[1]{\mathbb{#1}}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\nor}[1]{\left\| #1 \right\|}
\newcommand{\snor}[1]{\left| #1 \right|}
\newcommand{\LRp}[1]{\left( #1 \right)}
\newcommand{\LRs}[1]{\left[ #1 \right]}
\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
\newcommand{\LRc}[1]{\left\{ #1 \right\}}
\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
\newcommand{\Grad} {\ensuremath{\nabla}}
\newcommand{\Div} {\ensuremath{\nabla\cdot}}
\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
\newcommand{\uh}{\widehat{u}}
\newcommand{\fnh}{\widehat{f}_n}
\renewcommand{\L}{L^2\LRp{\Omega}}
\newcommand{\pO}{\partial\Omega}
\newcommand{\Gh}{\Gamma_h}
\newcommand{\Gm}{\Gamma_{-}}
\newcommand{\Gp}{\Gamma_{+}}
\newcommand{\Go}{\Gamma_0}
\newcommand{\Oh}{\Omega_h}

\newcommand{\eval}[2][\right]{\relax
  \ifx#1\right\relax \left.\fi#2#1\rvert}

\def\etal{{\it et al.~}}

\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
\newcommand{\tensor}[1]{\underline{\vect{#1}}}
\newcommand{\del}{\Delta}
\newcommand{\grad}{\nabla}
\newcommand{\curl}{\grad \times}
\renewcommand{\div}{\grad \cdot}
\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
\newcommand{\eip}[1]{a\left( #1 \right)}
\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}

\newcommand{\circone}{\ding{192}}
\newcommand{\circtwo}{\ding{193}}
\newcommand{\circthree}{\ding{194}}
\newcommand{\circfour}{\ding{195}}
\newcommand{\circfive}{\ding{196}}

\def\arr#1#2#3#4{\left[
\begin{array}{cc}
#1 & #2\\
#3 & #4\\
\end{array}
\right]}
\def\vecttwo#1#2{\left[
\begin{array}{c}
#1\\
#2\\
\end{array}
\right]}
\def\vectthree#1#2#3{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
\end{array}
\right]}
\def\vectfour#1#2#3#4{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
#4\\
\end{array}
\right]}

\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

\newcommand{\G} {\Gamma}
\newcommand{\Gin} {\Gamma_{in}}
\newcommand{\Gout} {\Gamma_{out}}

\signature{Jesse Chan, Norbert Heuer, Tan Bui-Thanh, and Leszek Demkowicz}
\address{201 East 24th St, Stop C0200\\
Austin, Texas 78712-1229}
\begin{document}
\begin{letter}{Dr Alexey Chernov\\CAMWA Guest Editor\\Special Issue: HONAPDE 2012}

%\tableofcontents
%\maketitle

\opening{Dear Dr Chernov,}

The authors are very grateful for the feedback, comments and suggestions provided by both reviewers.  Please accept the attached revised version of our paper:

\begin{center}
Jesse Chan, Norbert Heuer, Tan Bui-Thanh, and Leszek Demkowicz\\
\textit{A robust DPG method for convection-dominated diffusion problems II: adjoint boundary conditions and mesh-dependent test norms.}
\end{center}

In addition to the changes requested by the reviewers, we have made a few additional corrections in the manuscript.  The title has been changed to match the submitted title, and a citation has been added in Section 1.4 for Dr Wolfgang Dahmen's work, which we discovered after submission.  His work is equivalent to the DPG method for alternative variational formulations.  Additionally, the following changes have been made to the manuscript
\begin{enumerate}
\item On page 2, the SUPG method is mentioned to be $H^1$ optimal.  We have added the specification ``in the 1D case", as this claim does not hold in 2 and 3 dimensions.
\item We have removed part of Section 1.5, previously titled ``Canonical energy norm pairings for the ultra-weak formulation".  Previously, the quasi-optimal/graph test norm was stated to induce a norm on the trial space $U$ of a specific form; it was discovered that this proof was incorrect, and the exact form of the induced energy norm under the graph test norm is unknown.  The section has been rewritten to correct this.  Figure 1 was also removed.  
\item In Section 2 near the second half of page 8, we have changed the description of the broken $H^1\times H({\rm div})$ test norm to be the ``canonical norm on this test space" as opposed to simply ``the canonical test norm", which could be confused with the \textit{quasi-optimal/graph test norm} described as the canonical norm in the previous section.  
\item In Section 3.5, in replacing the image with a higher quality eps version, we plot a solution to the 1D adjoint equation with a given load.  The function plotted was inconsistent with the load described; this is fixed.  
\item In Section 4.1 and onwards, some images have been replaced with higher quality image files.  A typo is corrected on p24, concerning the greedy adaptive strategy used (we refine elements who satisfy $e_K^2 \leq \alpha^2 \max e_K^2$, but had neglected to square the factor $\alpha$ in the original manuscript).

\end{enumerate}

We thank the reviewers for their insightful comments, recommendations, and favorable reviews.  Attached are details on the revisions made as requested from each reviewer, as well as the authors responses to each revision request.

\textbf{Reviewer 1}

%The paper is concerned with DGP methods applied to linear convection-diffusion equations in the small-diffusion limit for the inflow boundary conditions of [13]. The authors identify a non-canonical and mesh-dependent test norm, which is explicitly computable and uniformly equivalent to the energy norm (cf. Lemma 1). The performance of the methods is then tested in a set of numerical examples using h-adaptivity. The tests confirm the robustness of the methods, as expected. Additionally, it is observed that the ratios of $L^2$ errors and energy errors are uniformly bounded in the Peclet number.
%
%Assessment:
%DGP methods have emerged as robust discretization methods for convection-diffusion problems (as well as for other singularly perturbed problems). They are based on the local computation of so-called optimal test functions, which by construction yield stability and quasi-optimality in the norms considered. In this paper, DGP methods are extended to the inflow conditions of [13] while earlier papers address only Dirichlet conditions. It turns out that the effects of the different boundary conditions may be quite dramatic due to the different structure of the adjoint problems, and indeed require different test norms, as illustrated in Section 3.5. As such, this is an interesting contribution to the theory of DGP methods.

%Although I didn't check all details, the results of the paper appear correct and new. The paper is well written; its introduction also nicely surveys the main ideas of DGP methods. I recommend the paper for publication in CAMWA.

%However, I would like to authors to address the following minor suggestions/comments/typos:
\begin{enumerate}
\item \textcolor{red}{After equation (1): $U$ should be $U_h$.}  Corrected.

\item \textcolor{red}{Page 7, last line: A period is missing at the end of the last sentence.}   We fixed the issue on equation (10), where there was a comma instead of a period, but I could not find this typo.

\item \textcolor{red}{The new boundary conditions should be discussed in a few more details. What do they model physically? What happens on $\Gamma_0$? Discussion of weak formulation and well-posedness of the continuous problem?}.  Certainly - we've added a short explanation.  In summary, the boundary condition models physically the conserved flux corresponding to the conservation law.  However, though the boundary condition holds physical meaning, this boundary condition is chosen instead because it approximates, for small enough $\epsilon$ and $\beta_n > 0$ on $\Gamma_0$, the standard boundary condition $u = u_0$ on $\Gamma_0$.

Due to the nature of the ultra-weak variational formulation, the weak formulation for both standard boundary conditions on $u$ and the new boundary condition on $\Gamma_0$ are the same.  For convection-diffusion, the variational form is
\[
b\LRp{\LRp{u,\sigma,\uh,\fnh},\LRp{v,\tau}} = \LRa{\fnh,v} - \LRa{\uh,\tau_n} + \text{field/interior terms}
\]

The application of boundary conditions is equivalent to the imposition of a natural boundary condition in both cases, where either $\LRa{\fnh,v}_{\Gamma_0}$ or $\LRa{\uh,\tau_n}_{\Gamma_0}$ are given data and become forcing terms.

Regarding the well-posedness of the variational problem, we refer the reviewer to \cite{analysisDPG}, whose analysis also covers the case of these boundary conditions (assuming well-posedness of the continuous problem), or \cite{Bui-ThanhDemkowiczGhattas11b}, where both the standard inflow boundary condition on $u$ and the proposed Robin boundary condition can be analyzed in the framework of Friedrichs systems.

Regarding the well-posedness of the continuous problem, we refer the reviewer to \cite{Hesthaven96astable}, the paper of Dr Jan Hesthaven, where he proves well-posedness of both the transient case and the case as $\epsilon \rightarrow 0$.

\item \textcolor{red}{Page 10, mid page: There is a latex error regarding the reference to Figure 2, and the label in Figure 2 needs to be fixed.}  Corrected.

\item \textcolor{red}{Page 12: Several sentences are in boldface, for no obvious reasons. This should be changed. }  Corrected.

\item \textcolor{red}{Assumptions (19)-(21): It should be discussed how restrictive these assumptions are.} Corrected; a footnote has been added discussing the physical interpretation of such assumptions.

A few comments on the assumptions: 
\begin{enumerate}
\item These assumptions are only sufficient conditions - these conditions have been introduced only to ensure a robust bound exists for solutions to the adjoint equations.  For example, the condition $\div \beta = 0$ is only a sufficient condition to ensure the well-posedness of an auxiliary problem related to the proof of a lemma.  The lemma can still hold without this condition
\item These assumptions are strictly for the steady-state case with no first-order term.  In the case when there is a first-order term, it is easy to prove Lemma 3 without the aid of the condition $\curl \beta = 0$.  
\item Several numerical experiments (to be reported in an upcoming report on locally-conservative DPG) do not indicate a loss of robustness even when these conditions are violated.  For example, experiments with the viscous Burgers' equation 
\[
u_{,t} + \LRp{\frac{u^2}{2}}_{,x} - \epsilon \nabla u = 0
\]
yield a solution with a shock from $(x,y) = (.5,.5)$ to $(.5,1)$ for initial condition $u(x,0) = 1-2x$.  The linearized equation is a convection-diffusion equation with $\beta = (u,1)$.  When $u$ has a shock, $\grad \beta + \grad \beta^T - \div \beta I = O(\epsilon^{-1})$, and condition (19) is violated, but there was no observable degeneration in solution quality as $\epsilon$ decreased.  
\end{enumerate}

\item \textcolor{red}{Page 15, last line: change "proper" to "these", "the robust bounds" to "the following robust bounds".}  Corrected.

\item \textcolor{red}{Lemma 1: the equivalence bounds appear not be p-robust. These should be mentioned explicitly in the statement of the lemma.}  The bounds in Lemma 1 should hold under any mesh and arbitrary $p$ - there were only regularity assumptions made in the proof.  Could we request a more detailed explanation into why the bounds appear to not be $p$-robust?

\item \textcolor{red}{Shouldn't the curves in Figure 8 (left) be on top of each other to indicate robustness? Please comment. Also: Please indicate the orders of the convergence which are observed?} Noted - we have expanded the paragraph discussing Figures 7 and 11, (the figures have been renumbered).

As both reviewers have expressed concern over the ratio curves in Figure 8, I have discussed this in a section at the end of this letter explaining the interpretation of the ratio curves for various values of $\epsilon$.

Concerning the orders of convergence - 
\begin{enumerate}
\item We are mostly in the pre-asymptotic range for most of our problems, and thus do not expect to observe optimal rates in our setup for small values of $\epsilon$.  For this reason, we believe that reporting convergence rates would not add much meaningful information.  
\item We have verified that we do indeed achieve optimal rates asymptotically under uniform refinements for $\epsilon = 1$, $1e-1$, and $1e-2$.  However, the mesh size at which the optimal rate is achieved becomes smaller and smaller as $\epsilon$ shrinks; we reach the optimal rate immediately for $\epsilon = 1$, but for $\epsilon = 1e-2$, our rates of convergence between $h = 1/128$ and $h = 256$ changed from 2.5255 to 2.8292.  We expect an optimal rate of $3$, but as this example shows, it may not be computationally feasible to get to that asymptotic range and demonstrate robustness for very small $\epsilon$ at the same time.  
\item Adaptivity should restore the optimal rate of convergence with respect to degrees of freedom; however, for strongly anisotropic solutions (such as boundary layer solutions), this optimal rate is achieved only through the use of anisotropic refinements, which we have not yet implemented.  
\end{enumerate}

\item \textcolor{red}{Page 24: How is the estimator $e_K^2$ defined? Please provide some details.}  Corrected.

Specifically, at the top of page 5, a paragraph is dedicated to the definition of the \textit{error representation function}, which is the inverse Riesz image of the residual of the variational equation (in $V'$) - in other words, the solution of
\[
(e,\delta v)_V = l(\delta v) - b(u_h,\delta v), \quad \forall v\in V.
\]
Under this, $\nor{e}_V = \nor{Bu-Bu_h}_{V'} = \nor{u-u_h}_E$ - the norm of the error representation function returns the norm of the error in the energy norm.  We note that, under a localizable norm and discontinuous test basis, this error representation function can be computed locally and used as a local error indicator.  $e_K^2$ is defined to be the squared energy norm of the error representation function over a single element $\nor{e}_{V(K)}^2$.  Summing together these elementwise contributions recovers the actual squared energy error over the domain.

\end{enumerate}

\textbf{Reviewer 2}

%The authors continue the analysis of the Discontinuous Petrov-Galerkin method for a singularly perturbed convection-diffusion problem initiated in [10].  The paper starts with an introduction to the abstract setting of the DPG. The core of the paper studies the DPG for the (scalar) convection-diffusion problem. Two issues are studied: first, the choice of the norm on the test space and second the impact of this choice on the ``energy norm", i.e., the norm on the trial space. The norm on the test space should fulfill several requirements: firstly, it should be localizable so that the test functions (which have to be computed) can be computed locally and secondly it should avoid test functions that have boundary layers, which are difficult to resolve. In this paper, these two issues are addressed by using the mesh-dependent norm given in Lemma 1 on p. 17. Lemma 1 also shows that the ``energy norm" induced by this norm on the test space allows for control of the field variables, in particular, the primal variable u.
%
%The paper reads very well, is of topical interest and very well suited for CAMWA. The referee recommends publication after the following issues are addressed.

\begin{enumerate}
\item \textcolor{red}{The authors are encouraged to carefully proof-read the proof of Lemma 1.}  Noted.  Shortly after submitting, the authors did go through the proof of Lemma 1 again with a careful read-through.
\item \textcolor{red}{The notation $\nor{\cdot}_{V,K}$ is used in the proof of Lemma 1 repeatedly and the referee did not find a definition.}  Corrected.  The definition of $\nor{\cdot}_{V,K}$ is included on the end of page 4 in the footnote on localizable norms, as well as on p18, right before the definition is used.  Additionally, to be consistent with the notation $L^2(K)$, we have changed the notation from $\nor{\cdot}_{V,K}$ to $\nor{\cdot}_{V(K)}$ 
\item \textcolor{red}{Towards the end of the proof of Lemma 1, the notation $\nor{\eta} + \nor{w}$ appears. The context suggest that $\eta$ and $w$ are measured in the $L^2$-norm, but $H^1$ and $H({\rm div})$ seem more likely from the context.}  Corrected.  The reviewer is correct, the proper setting was indeed $H^1$/$H({\rm div})$.  
\item \textcolor{red}{The numerical results show an $\epsilon$-dependence in the approximation (cf. Figs. 8, 10, 12) although the error measure is rather weak (the $L^2$-norm of the field variable $u$ doesn't ``see" the boundary layer). The referee feels that the readers would appreciate some comments.}  Additional comments describing the ratios have been added on p25.  Figure 10 (now Figure 9) largely addresses the issue of modeling error in the inflow condition.

As both reviewers have expressed concern over the ratio curves in Figure 8, please see the section below on the interpretation of the ratio curves for various values of $\epsilon$.

\item \textcolor{red}{p. 21, just below (22): integrate $\rightarrow$ integrating}.  Corrected.
\item \textcolor{red}{p. 23, last formula: $r2 \rightarrow r_2$}.  Corrected.  There was also the same error in $r1$, which was also corrected.
\end{enumerate}

\textbf{Author remark: on the ratio curves for various values of $\epsilon$}

A few reasons why the curves in these figures are not guaranteed to lie on top of each other 
\begin{enumerate}
\item The proofs only guarantee that the ratio of $L^2$ to energy error is bounded by some constant independent of $\epsilon$.  Changing $\epsilon$ changes the problem, and the curves are not guaranteed to be similar.  The curves are not guaranteed even to be bounded away from zero; this is simply an observed phenomenon.  
\item The test norm used is mesh-dependent.  In this work, the constants placed in front of the $L^2$ portions of the test functions $v$ and $\tau$ are scaled by a mesh-dependent value, which takes two asymptotic values.  In the far-underresolved limit $h \gg \epsilon$, this value is $\epsilon$ for $\nor{v}_{L^2}$ and $1$ for $\nor{\tau}_{L^2}$ - these help guarantee that the optimal test functions do not contain boundary layers, which may introduce approximation error, which our analysis does not account for.  In the fully-resolved limit $h\approx \epsilon$, the values in front of $\nor{v}_{L^2}$ and $\nor{\tau}_{L^2}$ are $1$ and $\epsilon^{-1}$, respectively.  These are to help account for the fact that the $\nor{v}$ and $\nor{\tau}$ scale differently from $\nor{\grad v}$ and $\nor{\div \tau}$.

For the first example, the ratio curves each have a clear ``transition point", where the mesh introduces elements where $h \approx \epsilon$.  This transition occurs later as $\epsilon$ shrinks, simply due to the fact that it takes more degrees of freedom to introduce elements of size $\epsilon$ on a 1-irregular constrained mesh.

In the second example, a discontinuous boundary condition is approximated by a 20 term Fourier series.  As refinements are introduced, the problem itself changes due to the improved resolution of the boundary condition at the inflow (the ``moving target" issue).  This further complicates the matter, and the ratio is consequentially more ``messy"; however, it is still very close to 1 for every $\epsilon$ we tested.  
\item The scale can be misleading; we show the $y$-axis from $0$ to $2$.  In cases where there is \textit{not} a robust bound, these ratios scale with $\epsilon^{-1}$ - in other words, to show the ratios for $\epsilon$ up to $1e-4$, we would require a scale with $y \in [0,1e4]$, or a logarithmic scale from $0$ to $1e4$.  Under these scales, the curves would appear to lie more on top of one another.
\end{enumerate}

\closing{Best regards}

\bibliographystyle{plain}
\bibliography{paper}

\end{letter}
\end{document}

### 2013-04-29 docs/Jesse/HeuerPaper/paperForCAMWA.tex
updating heuer paper

--- 2012-06-13 docs/Jesse/HeuerPaper/paper.tex
@@
 \usepackage[normalem]{ulem}
+\usepackage{epstopdf}
 
@@
 %\title{$\epsilon$-explicit analysis of DPG for convection-dominated diffusion}
-\title{Robust DPG method for convection-dominated diffusion problems II: a natural inflow condition}
+\title{A robust DPG method for convection-dominated diffusion problems II: adjoint boundary conditions and mesh-dependent test norms.}
 \date{}
@@
 The most well-known example of this technique is the streamline-upwind Petrov-Galerkin (SUPG) method, which is a stabilized method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.
-SUPG stabilization not only removes the spurious oscillations from the finite element solution of the convection-diffusion equation, but delivers the best finite element approximation in the $H^1$ norm.
+In the 1D case, SUPG stabilization not only removes the spurious oscillations from the finite element solution of the convection-diffusion equation, but delivers the best finite element approximation in the $H^1$ norm.
 An important difference between residual-based stabilization techniques and other stabilizations is the idea of \textit{consistency} --- by adding stabilization terms based on the residual, the exact solution still satisfies the same variational problem (i.e.\ Galerkin orthogonality still holds).\footnote{Contrast this to an artificial diffusion method, where a specific amount of additional viscosity is added based on the magnitude of the convection and diffusion parameters.
@@
 
-The addition of residual-based stabilization terms can also be interpreted as a modification of the test functions --- in other words, stabilization can be achieved by changing the test space for a given problem.
+The addition of residual-based stabilization terms has also been interpreted as a modification of the test functions --- in other words, stabilization can be achieved by changing the test space for a given problem.
 We approach the idea of stabilization through the construction of \textit{optimal test functions} to achieve optimal approximation properties.
@@
 where $b\LRp{\cdot,\cdot}: U \times V \to \mbb{R}$ is a continuous
-bilinear form.  $U$ is chosen to be some trial space of approximating functions, but $V_h$ is as of yet unspecified.
+bilinear form.  $U_h$ is chosen to be some trial space of approximating functions, but $V_h$ is as of yet unspecified.
 
@@
 However, in general, for standard $H^1$ and $H({\rm div})$-conforming finite element methods, test functions are continuous over the entire domain, and hence solving variational problem \eqnref{optvVar} for each optimal test function requires a global operation over the entire mesh, rendering the method impractical.
-A breakthrough came through the development of
-discontinous Galerkin (DG) methods, for which basis functions are
-discontinuous over elements. In particular, the use of discontinuous
-test functions $\delta v$ reduces the problem of determining global 
-optimal test functions
-in \eqnref{optvVar} to local problems that can be solved in an
-element-by-element fashion.
-
-We note that solving \eqnref{optvVar} on each element exactly is
-infeasible since it amounts to inverting the Riesz map $R_V$ exactly.
-Instead, optimal test functions are approximated using the standard
-Bubnov-Galerkin method on an ``enriched" subspace $\tilde{V} \subset
-V$ such that $\dim(\tilde{V}) > \dim(U_h)$ elementwise \cite{DPG1, DPG2}. In this
-paper, we assume the error in approximating the optimal test functions
-is negligible, and refer to the work in \cite{practicalDPG} for
-estimating the effects of approximation error on the performance of DPG.
-
-It is now well known that the DPG method
-delivers the best approximation error in the ``energy norm" --- that is
-\cite{Bui-ThanhDemkowiczGhattas11a, DPG2,DPG4} 
+A breakthrough came through the development of discontinous Galerkin (DG) methods, for which basis functions are discontinuous over elements.
+In particular, the use of discontinuous test functions $\delta v$ and a \textit{localizable} norm $\nor{\cdot}_V$\footnote{A localizable norm $\nor{v}_{V(\Oh)}$ can be written in the form
+$$\nor{v}_{V(\Oh)}^2 = \sum_{K\in\Oh} \nor{v}_{V(K)}^2,$$ where $\nor{v}_{V(K)}$ is a norm over the element $K$.} reduces the problem of determining global optimal test functions in \eqnref{optvVar} to local problems that can be solved in an element-by-element fashion.
+
+We note that solving \eqnref{optvVar} on each element exactly is infeasible since it amounts to inverting the Riesz map $R_V$ exactly.
+Instead, optimal test functions are approximated using the standard Bubnov-Galerkin method on an ``enriched" subspace $\tilde{V} \subset V$ such that $\dim(\tilde{V}) > \dim(U_h)$ elementwise \cite{DPG1, DPG2}.
+In this paper, we assume the error in approximating the optimal test functions is negligible, and refer to the work in \cite{practicalDPG} for estimating the effects of approximation error on the performance of DPG.
+
+It is now well known that the DPG method delivers the best approximation error in the ``energy norm" --- that is \cite{Bui-ThanhDemkowiczGhattas11a, DPG2,DPG4} 
 \begin{equation}
@@
 additional consequence of adopting such an energy norm is that,
-without knowing the exact solution, the energy error $\|u-u_h\|_{U,E}$ can
-be determined by computing $\|v_{u-u_h}\|_V$ from the following
-identity
-\[
-\left(v_{u-u_h},\delta v\right)_V = b(u-u_h,\delta v) = l\LRp{\delta
-v} - b(u_h,\delta v).
-\]
+without knowing the exact solution, the energy error $\|u-u_h\|_{U,E}  = \nor{Bu - Bu_h}_{V'} = \nor{R_V^{-1}\LRp{l-Bu_h}}_{V}$ can
+be determined by computing the \textit{error representation function} $e \coloneqq R_V^{-1}\LRp{l-Bu_h}$ through
+\[
+\left(e,\delta v\right)_V = b(u-u_h,\delta v) = l\LRp{\delta v} - b(u_h,\delta v)
+\]
+and measuring its norm $\|e\|_V$.
 This is simply a consequence of the least-squares nature of DPG; the energy error is simply the norm of the residual in $V'$.
+Under the assumption of a localizable norm on $V$, we can compute the squared norm over the entire domain $\nor{e}_{V(\Oh)}^2$ as the sum of individual element contributions $\sum_{K\in \Oh} \nor{e}_{V(K)}^2$.
+We define $e_K^2 \coloneqq \nor{e}_{V(K)}^2$ as a local error indicator with which we can drive adaptive mesh refinement.
 
@@
 However, the reverse relationship holds as well; for any trial norm, the test norm that induces such a norm is recoverable through duality.
-We have a result, proved in \cite{Bui-ThanhDemkowiczGhattas11a}: assuming, for simplicity, that the bilinear form $b(u,v)$ is definite, given any norm $\nor{\cdot}_{U}$ on the trial space $U$, for $\varphi \in U$, we can represent $\nor{\varphi}_{U}$ via
+We have a result, Lemma 2.5 in \cite{Bui-ThanhDemkowiczGhattas11a}: assuming, for simplicity, that the bilinear form $b(u,v)$ is definite\footnote{By definite, we mean that \begin{align*}b(u,v) &= 0, \forall v\in V \Rightarrow u = 0\\ b(u,v)&=0, \forall u\in U \Rightarrow v = 0,\end{align*}  which imply injectivity of the bilinear operator $B$ and its transpose $B'$, defined such that $\LRa{Bu,v} = \LRa{u,B'v}$.
+These conditions imply solvability of the variational problem.}, given any norm $\nor{\cdot}_{U}$ on the trial space $U$, for $\varphi \in U$, we can represent $\nor{\varphi}_{U}$ via
 \[
@@
 There is no specification of the regularity of the trial space, and we stress that the idea of DPG is not inherently tied to a single variational formulation \cite{Bui-ThanhDemkowiczGhattas11a}.
+Additionally, Cohen, Dahmen and Welper simultaneously extend the minimum residual concept behind DPG to general variational settings and avoid the use of discontinuous test functions by formulating the minimum residual method as a saddle-point problem \cite{DahmenVariationalStabilization}.
 
@@
 %\subsection{Optimal and quasi-optimal test norms}
-\subsection{Canonical energy norm pairings for ultra-weak formulation}
+\subsection{A canonical energy norm pairing for ultra-weak formulation}
 
 From the discussion in Section~\secref{energyPair} of energy norm and test norm pairings, we know that specifying either a test norm or trial norm is sufficient to define an energy pairing.
-In this section, we derive and discuss two important energy norm pairings, the first of which begins by specifying the canonical norm in $U$ and inducing a test norm on $V$.
+%In this section, we derive and discuss two important energy norm pairings, the first of which begins by specifying the canonical norm in $U$ and inducing a test norm on $V$.
 The second pairing begins instead by specifying the canonical norm on $V$ under the ultra-weak formulation \eqnref{uweak} and inducing an energy norm on the trial space $U$.
+In this section, we derive and discuss an important energy norm pairing which specifies the canonical norm in $U$ and induces a test norm on $V$.
+%The second pairing begins instead by specifying the canonical norm on $V$ under the ultra-weak formulation \eqnref{uweak} and inducing an energy norm on the trial space $U$.
 
@@
 \[
-\|\left(u,\widehat{u}\right)\|_U^2 = \|u\|^2_{\L} + \|\widehat{u}\|^2,
+\|\left(u,\widehat{u}\right)\|_U^2 = \|u\|^2_{\L} + \|\widehat{u}\|^2.
 \]
@@
 
-On the other hand, since $v \in D\LRp{A^*_h}$, the canonical norm for
-$v$ is the broken graph norm: 
+%On the other hand, since $v \in D\LRp{A^*_h}$, the canonical norm for
+%$v$ is the broken graph norm: 
+%\[
+%\nor{v}_V^2 =  \|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2.
+%\]
+%Using the Cauchy-Schwarz inequality again, we obtain
+%\[
+%b\LRp{\LRp{u,\uh},v} \le \nor{\LRp{u,\uh}}_{U,V} \nor{v}_{V},
+%\]
+%where
+%\begin{equation}
+%\eqnlab{inducedQuasi}
+%\nor{\LRp{u,\uh}}_{U,V}^2 = \nor{u}_{\L}^2
+%+\sup_{v \in D\LRp{A_h^*}} \frac{\LRa{\widehat{u},
+%  \jump{v}}_{\Gh}^2}{\|v\|_V^2},
+%\end{equation}
+
+Using the framework developed in \cite{Bui-ThanhDemkowiczGhattas11a}, one can show that $\LRp{\nor{\LRp{u,\uh}}_U,  \nor{v}_{V,U}}$ is an energy norm pairing in the sense discussed in Section \secref{energyPair}.
+That is, the canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ induces (generates) the norm $\nor{v}_{V,U}$ in $V$.
+
+The canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ provides an optimal balance between the standard norms on the field $u$ and the flux $\uh$ \cite{DPG4}.
+As a result, if the induced norm $\nor{v}_{V,U}$ (namely, the optimal test norm) is used to compute  optimal test functions in \eqnref{optvVar}, the finite element error in the canonical norm is the best in the sense of \eqnref{optimalError}.
+Unfortunately, the optimal test norm is non-localizable due to the presence of the jump term $\jump{v}$.
+Since the jump terms couple elements together, the evaluation of the jump terms requires contributions from all the elements in the mesh.
+Consequently, solving for an optimal test function amounts to inverting the Riesz map over the entire mesh $\Oh$, making the optimal test norm impractical.
+
+On the other hand, since $v \in D\LRp{A^*_h}$, we can use as a test norm for $v$ the broken graph norm: 
 \[
@@
 \]
-Using the Cauchy-Schwarz inequality again, we obtain
-\[
-b\LRp{\LRp{u,\uh},v} \le \nor{\LRp{u,\uh}}_{U,V} \nor{v}_{V},
-\]
-where
-\begin{equation}
-\eqnlab{inducedQuasi}
-\nor{\LRp{u,\uh}}_{U,V}^2 = \nor{u}_{\L}^2
-+\sup_{v \in D\LRp{A_h^*}} \frac{\LRa{\widehat{u},
-  \jump{v}}_{\Gh}^2}{\|v\|_V^2},
-\end{equation}
-
-Using the framework developed in \cite{Bui-ThanhDemkowiczGhattas11a},
-one can show that both pairs $\LRp{\nor{\LRp{u,\uh}}_U,
-  \nor{v}_{V,U}}$ and $\LRp{\nor{\LRp{u,\uh}}_{U,V}, \nor{v}_{V}}$ are
-energy norm pairings in the sense discussed in Section
-\secref{energyPair}. That is, the canonical norm $\nor{\LRp{u,\uh}}_U$
-in $U$ induces (generates) the norm $\nor{v}_{V,U}$ in $V$, while the
-canonical norm $\nor{v}_V$ in $V$ induces (generates) the energy norm
-$\nor{\LRp{u,\uh}}_{U,V}$ in $U$. In the DPG literature \cite{DPG4}, $\nor{v}_{V,U}$ is known as the {\em optimal test norm},
-while $\nor{v}_{V}$ is known as the {\em quasi-optimal test norm}.
-
-\begin{figure}[!h]
-\centering
-\begin{tabular}{l c c}
-Trial norm & & Test norm \\
-\hline
-$\boxed{\|u\|^2_{\L} + \|\widehat{u}\|^2}$ & $\Longrightarrow$  & $\|A_h^*v\|_{\L}^2
-+\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},
-  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2$ \\
+This norm is a localization of $\nor{v}_{V,U}$ to allow for the solution of optimal test functions on an element-by-element basis, and is considered to be the canonical norm on $V$.
+In the DPG literature \cite{DPG4}, $\nor{v}_{V,U}$ is known as the {\em optimal test norm}, while $\nor{v}_{V}$ is known as the {\em quasi-optimal} or {\em graph test norm}.
+
+%Using the framework developed in \cite{Bui-ThanhDemkowiczGhattas11a}, one can show that both pairs $\LRp{\nor{\LRp{u,\uh}}_U,  \nor{v}_{V,U}}$ and $\LRp{\nor{\LRp{u,\uh}}_{U,V}, \nor{v}_{V}}$ are energy norm pairings in the sense discussed in Section \secref{energyPair}.
+That is, the canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ induces (generates) the norm $\nor{v}_{V,U}$ in $V$, while the canonical norm $\nor{v}_V$ in $V$ induces (generates) the energy norm $\nor{\LRp{u,\uh}}_{U,V}$ in $U$.
+In the DPG literature \cite{DPG4}, $\nor{v}_{V,U}$ is known as the {\em optimal test norm}, while $\nor{v}_{V}$ is known as the {\em quasi-optimal test norm}.
+
+%\begin{figure}[!h]
+%\centering
+%\begin{tabular}{l c c}
+%Trial norm & & Test norm \\
 %\hline
-%Quasi-optimal trial norm & & Canonical test norm \\
-%\hline
-$\nor{u}_{\L}^2+\sup_{v } \left(\frac{\LRa{\widehat{u},
-  \jump{v}}_{\Gh}}{\|v\|_V}\right)^2$ &  $\Longleftarrow$ & $\boxed{\|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2}$
-\end{tabular}
-\caption{A summary of the derivation of test/trial norm pairings; we begin with the boxed norm on either the trial or test space, and induce the norm on the other space through duality.
+%$\boxed{\|u\|^2_{\L} + \|\widehat{u}\|^2}$ & $\Longrightarrow$  & $\|A_h^*v\|_{\L}^2
+%+\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},
+%  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2$ \\
+%%\hline
+%%Quasi-optimal trial norm & & Canonical test norm \\
+%%\hline
+%$\nor{u}_{\L}^2+\sup_{v } \left(\frac{\LRa{\widehat{u},
+%  \jump{v}}_{\Gh}}{\|v\|_V}\right)^2$ &  $\Longleftarrow$ & $\boxed{\|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2}$
+%\end{tabular}
+%\caption{A summary of the derivation of test/trial norm pairings; we begin with the boxed norm on either the trial or test space, and induce the norm on the other space through duality.
 The optimal \textit{test} norm is naturally derived by beginning with the canonical norm on the trial space, while the quasi-optimal \textit{trial} norm is derived from beginning with the canonical norm on the test space.}
-\end{figure}
-
-The canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ provides a good
-balance between the standard norms on the field $u$ and the flux
-$\uh$ \cite{DPG4}. As a result, if the induced norm $\nor{v}_{V,U}$ (namely, the
-optimal test norm) is used to compute  optimal test functions in
-\eqnref{optvVar}, the finite element error in the canonical norm is the
-best in the sense of \eqnref{optimalError}.
-
-Unfortunately, the optimal test norm is non-localizable due to the presence of the jump term $\jump{v}$.\footnote{A localizable norm $\nor{v}_{V(\Oh)}$ can be written in the form
-$$\nor{v}_{V(\Oh)} = \sum_{K\in\Oh} \nor{v}_{V(K)},$$ where $\nor{v}_{V(K)}$ is a norm over the element $K$.} Since the jump terms couple elements together, the evaluation of the jump terms requires contributions from all the elements in the mesh.
-Consequently, solving for an optimal test function
-amounts to inverting the Riesz map %, defined on the left sideof \eqnref{optvVar}, 
-over the entire mesh $\Oh$, making the optimal test norm impractical.
-
-On the other hand, the quasi-optimal test norm $\nor{v}_V$, namely the canonical norm in $V$, \textit{is} localizable, and hence practical.
+%\end{figure}
+
+%The canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ provides an optimal balance between the standard norms on the field $u$ and the flux $\uh$ \cite{DPG4}.
+As a result, if the induced norm $\nor{v}_{V,U}$ (namely, the optimal test norm) is used to compute  optimal test functions in \eqnref{optvVar}, the finite element error in the canonical norm is the best in the sense of \eqnref{optimalError}.
+%
+%Unfortunately, the optimal test norm is non-localizable due to the presence of the jump term $\jump{v}$.
+Since the jump terms couple elements together, the evaluation of the jump terms requires contributions from all the elements in the mesh.
+Consequently, solving for an optimal test function amounts to inverting the Riesz map over the entire mesh $\Oh$, making the optimal test norm impractical.
+
+%On the other hand, the quasi-optimal test norm $\nor{v}_V$, namely the canonical norm in $V$, \textit{is} localizable, and hence practical.
 However, it's worth noting the difference between the induced energy norm $\nor{\LRp{u,\uh}}_{U,V}$ and the canonical norm in $U$; under the induced norm $\nor{\LRp{u,\uh}}_{U,V}$ there is no natural interpretation for the norm in which the error in the flux variable $\uh$ is measured.
 
-Using a variant of the quasi-optimal test norm, numerical results show that the DPG method appears to provide a ``pollution-free" method without phase error for the Helmholtz equation \cite{DPG4}, and analysis of the pollution-free nature of DPG is currently under investigation.
+Using variants of the quasi-optimal test norm, numerical results show that the DPG method appears to provide a ``pollution-free" method without phase error for the Helmholtz equation \cite{DPG4}, and analysis of the pollution-free nature of DPG is currently under investigation.
 Similar results have also been obtained in the context of elasticity \cite{DPGElas} and the linear Stokes equations \cite{Camellia}.
@@
 \in  H^1(\Omega) \times H({\rm div}, \Omega)$. It follows that the
-canonical test norm can be written as
+canonical norm on this test space can be written as
 \[
@@
 \]
-instead of $\beta_n u = u_0$. The former resembles the latter
-as $\epsilon$ approaches zero\footnote{For our model problem, as for many problems of interest in computational fluid dynamics, we expect $\grad u$ to be small near the inflow, and that the solutions to \eqref{primal} using $\beta_n u - \sigma_n = f_n = u_0$ on $\Gamma_-$ will converge to that using $u=u_0$ on $\Gamma_-$  for sufficiently small $\epsilon$.}; however, the latter induces a more ``well-behaved" adjoint problem than the former, which, as we will discuss, affects the performance of DPG.
+instead of $\beta_n u = u_0$.
+The former resembles the latter as $\epsilon$ approaches zero\footnote{For our model problem, as for many problems of interest in computational fluid dynamics, we expect $\grad u$ to be small near the inflow, and that the solutions to \eqref{primal} using $\beta_n u - \sigma_n = f_n = u_0$ on $\Gamma_-$ will converge to that using $u=u_0$ on $\Gamma_-$  for sufficiently small $\epsilon$.}; however, the latter induces a more ``well-behaved" adjoint problem than the former, which, as we will discuss, affects the performance of DPG.
+Physically speaking, as the above boundary condition corresponds to the integration by parts of the conservation equation, a boundary condition on $\beta_n u - \sigma_n$ models a boundary condition on the conserved flux.
 
@@
 \centering
-\includegraphics[scale=.25]{figs/opt.png}
+\includegraphics[scale=.25]{opt.png}
 \caption{$v$ and $\tau$ components of the 1D optimal test functions corresponding to the flux $\widehat{f}_n$ on the right-hand side of a unit element for $\epsilon = 0.01$.
@@
 The decoupled variational problems are no longer systems but scalar equations in $\tau$ and $v$, for which it is easier to conclude whether or not there are boundary layers in the solutions (the avoidance of boundary layers in the test norm will be discussed in more detail in Section~\ref{sec:num_exp}, which describes our numerical experiments).
-\textbf{This will ensure that the resulting DPG method does not suffer from approximation errors in the optimal test functions}.
+This will ensure that the resulting DPG method does not suffer from approximation errors in the optimal test functions.
 
@@
 
-The second step will be to \textbf{show the equivalence of the energy norm to explicit norms on $U$}.
+The second step will be to show the equivalence of the energy norm to explicit norms on $U$.
 Since we do not generally have a closed form expression for the DPG energy norm, we seek to understand the behavior of DPG by finding a norm on $U$ to which the DPG energy norm is equivalent.
@@
 For each proof, we require $\beta \in C^2(\bar{\Omega})$ and $\beta, \div \beta = O(1)$.
-Additionally, we will assume that some or all of the following assumptions hold:
+Additionally, we will assume that some or all of the following assumptions hold
+\footnote{These assumptions correspond to convection fields which are divergence-free \eqref{c_req}, curl-free \eqref{a_req}, bounded away from zero \eqref{a_req}, and of bounded variation \eqref{b_req}.
+However, these are merely sufficient conditions; numerical experiments indicate that they may not be strictly necessary.}
+:
 \begin{align}
@@
 \end{align}
-Under proper assumptions on $\beta$, we have the robust bounds, which are proved in the Appendix. 
+
+Under these assumptions on $\beta$, we have the following robust bounds, which are proved in the Appendix. 
 \begin{itemize}
@@
 \centering
-\subfigure{\includegraphics[scale=.22]{figs/mesh1.png}}
-\subfigure{\includegraphics[scale=.22]{figs/sol1.png}}
+\subfigure{\includegraphics[scale=.22]{mesh1.png}}
+\subfigure{\includegraphics[scale=.22]{sol1.png}}
 \caption{The $v$ component of the optimal test function corresponding to flux $\widehat{u} = x(1-x)$ on the bottom side of a unit element for $\epsilon = 0.01$.
@@
 
-Our test norm, as defined over a single element $K$, is now
-\[
-\|\left(v,\tau\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
+We can now define $\nor{\LRp{v,\tau}}_{V(K)}$, our test norm over a single element $K$, as 
+\[
+\|\left(v,\tau\right)\|_{V(K)}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
 \]
@@
 \[
-\|\left(v,\tau\right)\|_{V,\Oh}^2 = \|C_vv\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \|C_\tau\tau\|^2,
+\|\left(v,\tau\right)\|_{V(\Oh)}^2 = \|C_vv\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \|C_\tau\tau\|^2,
 \]
@@
 \[
-\nor{\left(v,\tau\right)}_{V,\Oh} \lesssim \|g\| + \|f\| + \frac{1}{\epsilon}\|\jump{\tau\cdot n}\| + \frac{1}{\sqrt{\epsilon}}\|\jump{v}\|.
+\nor{\left(v,\tau\right)}_{V(\Oh)} \lesssim \|g\| + \|f\| + \frac{1}{\epsilon}\|\jump{\tau\cdot n}\| + \frac{1}{\sqrt{\epsilon}}\|\jump{v}\|.
 \]
@@
 \end{align*}
-we have that $\nor{\left(v,\tau\right)}_{V,\Oh} \leq \nor{\left(v,\tau\right)}_{V}$, so it suffices to prove the bound for the mesh-independent test norm 
+we have that $\nor{\left(v,\tau\right)}_{V(\Oh)} \leq \nor{\left(v,\tau\right)}_{V}$, so it suffices to prove the bound for the mesh-independent test norm 
 \[
@@
 %\sqrt{\epsilon} \|f \| &\leq \epsilon^{-1/2} \| \tau\| + \sqrt{\epsilon} \|\grad v\| \lesssim \|\\
-\|\epsilon C_\tau f \| &\leq C_\tau \nor{ \tau} + \epsilon C_\tau \nor{\grad v} \lesssim \| \left(\tau,v\right)\|_{V,\Oh}\\
-\|g \| &\leq \|\div \tau\| +  \|\beta \cdot \grad v\| \lesssim \| \left(\tau,v\right)\|_{V,\Oh}
+\|\epsilon C_\tau f \| &\leq C_\tau \nor{ \tau} + \epsilon C_\tau \nor{\grad v} \lesssim \| \left(\tau,v\right)\|_{V(\Oh)}\\
+\|g \| &\leq \|\div \tau\| +  \|\beta \cdot \grad v\| \lesssim \| \left(\tau,v\right)\|_{V(\Oh)}
 \end{align*}
@@
 \begin{align*}
-\langle \jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle &\lesssim \|\left(\tau,v\right)\|_{V,\Oh}\frac{1}{\sqrt{\epsilon}}\left(\nor{\eta}_{H({\rm div},\Omega)} + \nor{w}_{H^1(\Omega)}\right),\\
-&\lesssim \|\left(\tau,v\right)\|_{V,\Oh}\frac{1}{\sqrt{\epsilon}}\left(\nor{\eta-\beta w}_{H({\rm div},\Omega)} + \nor{w}_{H^1(\Omega)}\right),
+\langle \jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle &\lesssim \|\left(\tau,v\right)\|_{V(\Oh)}\frac{1}{\sqrt{\epsilon}}\left(\nor{\eta}_{H({\rm div},\Omega)} + \nor{w}_{H^1(\Omega)}\right),\\
+&\lesssim \|\left(\tau,v\right)\|_{V(\Oh)}\frac{1}{\sqrt{\epsilon}}\left(\nor{\eta-\beta w}_{H({\rm div},\Omega)} + \nor{w}_{H^1(\Omega)}\right),
 \end{align*}
@@
 \[
-\sup_{w,\eta \neq 0} \frac{\langle\jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle}{\left(\nor{\eta-\beta w}_{H({\rm div},\Omega)} + \nor{w}_{H^1(\Omega)}\right)} \lesssim \|\left(\tau,v\right)\|_{V,\Oh}\frac{1}{\sqrt{\epsilon}}.
+\sup_{w,\eta \neq 0} \frac{\langle\jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle}{\left(\nor{\eta-\beta w}_{H({\rm div},\Omega)} + \nor{w}_{H^1(\Omega)}\right)} \lesssim \|\left(\tau,v\right)\|_{V(\Oh)}\frac{1}{\sqrt{\epsilon}}.
 \]
@@
 
-As it turns out, the robust bounds given in Section~\ref{sec:main_bounds} hold in $\mathbb{R}^d$ for arbitrary $d$; however, we can show that for the case of Dirichlet boundary conditions, the same results do not hold, even in 1D.
+As it turns out, the robust bounds given in Section~\ref{sec:main_bounds} hold in $\mathbb{R}^d$ for arbitrary $d$; however, we can show that for Dirichlet boundary conditions, the same results do not hold even in 1D.
 %In 1D, the problem reduces to 
@@
 %By the fact that 
-Consider now the 1D analogue of the estimate given by Lemma~\ref{lemma_stream}.  In 1D, $\|\beta\cdot\grad v_1\| \lesssim \|g\|$ reduces to the inequality 
+Consider the 1D analogue of the estimate given by Lemma~\ref{lemma_stream}.  In 1D, $\|\beta\cdot\grad v_1\| \lesssim \|g\|$ reduces to the inequality 
 \[
@@
 \end{align}
-with $v_1\in H^1_0\left((0,1)\right)$.  After multiplying this equation by $\beta v_1'$ and integrate by parts over $\Oh$, we can apply Young's inequality to get
+with $v_1\in H^1_0\left((0,1)\right)$.  After multiplying this equation by $\beta v_1'$ and integrating by parts over $\Oh$, we can apply Young's inequality to get
 %\[
@@
 Taking $g=1$ (corresponding to a piecewise constant approximation) we can solve \eqref{adjoint_1D} exactly.
-\begin{figure}[!h]
+\begin{figure}
 \centering
-\includegraphics[scale=.5]{figs/testBoundary1D.png}
+\includegraphics[scale=.5]{testBoundary1D.pdf}
 \caption{$v_1(x) = \frac{e^{-\frac{x}{\epsilon}}}{e^{\frac{1}{\epsilon}}-1}\left(e^{\frac{1}{\epsilon}}\left(e^{\frac{x}{\epsilon}}-1\right) + \left(e^{\frac{1}{\epsilon}}-1\right)e^{\frac{x}{\epsilon}}x\right)$, the solution to the adjoint equation for $f=0$ and constant $\beta$ and load $g$ for $\epsilon = .01$.}
@@
 \end{figure}
+
 The solution $v_1$ is plotted in Figure~\ref{fig:testBoundary1D}, where we can see that $v_1(x)$ develops strong boundary layers of width $\epsilon$ near the inflow boundary $x=0$.
@@
 
-\begin{figure}[h!]
+\begin{figure}
 \centering
-\subfigure[Primal problem, Dirichlet inflow BC]{\includegraphics[scale=.3]{figs/primalDir.png}}
-\subfigure[Adjoint problem, Dirichlet inflow BC]{\includegraphics[scale=.3]{figs/adjointDir.png}}
-\subfigure[Primal problem, new inflow BC]{\includegraphics[scale=.3]{figs/primal.png}}
-\subfigure[Adjoint problem, new inflow BC]{\includegraphics[scale=.3]{figs/adjoint.png}}
+\subfigure[Primal problem, Dirichlet inflow BC]{\includegraphics[scale=.375]{primalDir.pdf}}
+\subfigure[Adjoint problem, Dirichlet inflow BC]{\includegraphics[scale=.375]{adjointDir.pdf}}
+\subfigure[Primal problem, new inflow BC]{\includegraphics[scale=.375]{primal.pdf}}
+\subfigure[Adjoint problem, new inflow BC]{\includegraphics[scale=.375]{adjoint.pdf}}
 \caption{Comparison of primal and adjoint problems under both the standard Dirichlet and the new inflow boundary condition.
 The outflow boundary for each problem is denoted in red.
-For the standard Dirichlet inflow condition, the solution to the adjoint problem can develop strong boundary layers at the outflow of the adjoint problem.
-Notice, under the new inflow conditions, the relaxation of a wall-stop boundary condition with a zero-stress condition at the outflow boundary of the adjoint problem.}
+For the Dirichlet inflow condition, adjoint solutions can develop boundary layers at the outflow of the adjoint problem.
+Under the new inflow conditions, the wall-stop boundary condition is relaxed to a zero-stress condition at the adjoint outflow.}
 \end{figure}
@@
 %\centering
-%\subfigure[Primal problem]{\includegraphics[scale=.3]{figs/primal.png}}
-%\subfigure[Adjoint problem]{\includegraphics[scale=.3]{figs/adjoint.png}}
+%\subfigure[Primal problem]{\includegraphics[scale=.3]{primal.png}}
+%\subfigure[Adjoint problem]{\includegraphics[scale=.3]{adjoint.png}}
 %\caption{Comparison of primal and adjoint problems for convection-diffusion under the standard Dirichlet outflow boundary condition and the new inflow boundary condition.
@@
 \[
-u(x,y) = C_0 + \sum_{n=1}^\infty C_n \frac{\exp(r_2(x-1)-\exp(r_1(x-1)))}{r_1\exp(-r2) - r_2\exp(-r1)}\cos(n\pi y),
+u(x,y) = C_0 + \sum_{n=1}^\infty C_n \frac{\exp(r_2(x-1)-\exp(r_1(x-1)))}{r_1\exp(-r_2) - r_2\exp(-r_1)}\cos(n\pi y),
 \]
@@
 \subfigure{
-\includegraphics[scale=.37]{figs/wallBC_exact_u.png}
+\includegraphics[scale=.37]{wallBC_exact_u.png}
 }
 \subfigure{
-\includegraphics[scale=.37]{figs/wallBC_exact_sigx.png}
+\includegraphics[scale=.37]{wallBC_exact_sigx.png}
 }
 \subfigure{
-\includegraphics[scale=.37]{figs/wallBC_exact_sigy.png}
+\includegraphics[scale=.37]{wallBC_exact_sigy.png}
 }
@@
 \end{figure}
-In each case, we begin with a square 4 by 4 mesh of quadrilateral elements with order $p=3$.
+In each case, we begin with a square 2 by 2 mesh of quadrilateral elements with order $p=3$.
 We choose $\Delta p = 5$, though we note that the behavior of DPG is nearly identical for any $\Delta p \leq 3$, and qualitatively the same for $\Delta p = 2$.
-$h$-refinements are executed using a greedy refinement algorithm, where element energy error $e_K^2$ is computed for all elements $K$, and elements such that $e_K^2 \leq \alpha \max_K e_K^2$ are refined.
+$h$-refinements are executed using a greedy refinement algorithm, where the element energy error $e_K^2$ is computed for all elements $K$, and elements such that $e_K^2 \leq \alpha^2 \max_K e_K^2$ are refined.
 We make the arbitrary choice of taking $\alpha = .2$ for each of these experiments.
@@
 \centering
-\includegraphics[scale=.4]{figs/u_pointdiff_wallBC.png}
+\includegraphics[scale=.4]{u_pointdiff_wallBC.png}
 \caption{Adapted mesh and pointwise error for $\epsilon=.01$}
@@
 \subfigure{
-\includegraphics[scale=.38]{figs/errorrates_wallBC.png}
+\includegraphics[scale=.38]{errorrates_wallBC.pdf}
 }
 \subfigure{
-\includegraphics[scale=.38]{figs/L2energyratio_wallBC.png}
+\includegraphics[scale=.38]{L2energyratio_wallBC.pdf}
 }
@@
 The transition point happens later for smaller $\epsilon$, which we expect, since the transition of the ratio corresponds to the introduction of elements whose size is of order $\epsilon$ through mesh refinement.
+For this reason, the ratios of $L^2$ to energy error do not overlap perfectly with each other.
+We note that the introduction of anisotropic refinements appears to mitigate this effect slightly \cite{DPGrobustness}.
 
@@
 \subfigure{
-\includegraphics[scale=.38]{figs/roundoff_rates.png}
+\includegraphics[scale=.38]{roundoff_rates.pdf}
 }
 \subfigure{
-\includegraphics[scale=.38]{figs/roundoff_ratio.png}
+\includegraphics[scale=.38]{roundoff_ratio.pdf}
 }
@@
 
-It is worth noting that for $\epsilon \leq 1e-5$, we do not perform enough refinements to completely resolve the boundary layer, so $|K| \geq \epsilon$ for all $K\in \Oh$.
+%It is worth noting that for $\epsilon \leq 1e-6$, we do not perform enough refinements to completely resolve the boundary layer, so $|K| \geq \epsilon$ for all $K\in \Oh$.
 Thus, any roundoff effects observed are not due to the conditioning issues associated with the differing scales of the $\nor{v}_{L^2(K)}$ and $\nor{\grad v}_{L^2(K)}$ terms discussed previously.
@@
 \subfigure{
-\includegraphics[scale=.38]{figs/rates_noSigma.png}
+\includegraphics[scale=.38]{rates_noSigma.pdf}
 }
 \subfigure{
-\includegraphics[scale=.38]{figs/ratio_noSigma.png}
+\includegraphics[scale=.38]{ratio_noSigma.pdf}
 }
@@
 \subfigure{
-\includegraphics[scale=.38]{figs/disc_hat.png}
+\includegraphics[scale=.38]{disc_hat.png}
 }
 \subfigure{
-\includegraphics[scale=.38]{figs/disc_hat_surf.png}
+\includegraphics[scale=.38]{disc_hat_surf.png}
 }
@@
 \subfigure{
-\includegraphics[scale=.38]{figs/rates_disc.png}
+\includegraphics[scale=.38]{rates_disc.pdf}
 }
 \subfigure{
-\includegraphics[scale=.38]{figs/ratio_disc.png}
+\includegraphics[scale=.38]{ratio_disc.pdf}
 }
@@
 The ratios of $L^2$ to energy error are now less predictable than for the previous example, in part due to the difficulty in approximating highly oscillatory boundary conditions.
-The numerical experiments were originally performed by applying boundary conditions via interpolation; the result was that the highly oscillatory inflow boundary condition was not sampled enough to be properly resolved, causing the solution to converge to a solution different than the exact solution.
-The experiments were repeated using the penalty method to enforce inflow conditions; however, we note that the proper way to do so is to use an $L^2$ projection at the boundary.
-Even when using the penalty method, however, the ratios still remain bounded and close to $1$ for $\epsilon$ varying over two orders of magnitude, as predicted by theory.
+However, the ratios still remain bounded as predicted by theory, and similarly to the previous problem with a smooth inflow condition, the ratios are close to $1$ for $\epsilon$ varying over two orders of magnitude.
 

### 2013-04-29 docs/Jesse/NavierStokes notes/notes.tex
adding one more heuer paper .sty file and adding NS/confusion notes

%&pdflatex
\documentclass[11pt,onecolumn]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
\usepackage[top=2cm,bottom=3cm,left=2.5cm,right=2cm]{geometry}
\usepackage{amssymb}
\usepackage{amscd}
\usepackage{listings}
\usepackage{array}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage[textsize=footnotesize,color=green]{todonotes}
\usepackage{algorithm, algorithmic}
\usepackage{array}
\usepackage{bm}
\usepackage{tikz}
\usepackage{subfigure}
\usepackage[normalem]{ulem}

\newcommand{\bs}[1]{\boldsymbol{#1}}
\DeclareMathOperator{\diag}{diag}

\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}

\newcommand{\tablab}[1]{\label{tab:#1}}
\newcommand{\tabref}[1]{Table~\ref{tab:#1}}

\newcommand{\theolab}[1]{\label{theo:#1}}
\newcommand{\theoref}[1]{\ref{theo:#1}}
\newcommand{\eqnlab}[1]{\label{eq:#1}}
\newcommand{\eqnref}[1]{\eqref{eq:#1}}
\newcommand{\seclab}[1]{\label{sec:#1}}
\newcommand{\secref}[1]{\ref{sec:#1}}
\newcommand{\lemlab}[1]{\label{lem:#1}}
\newcommand{\lemref}[1]{\ref{lem:#1}}

\newcommand{\mb}[1]{\mathbf{#1}}
\newcommand{\mbb}[1]{\mathbb{#1}}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\nor}[1]{\left\| #1 \right\|}
\newcommand{\snor}[1]{\left| #1 \right|}
\newcommand{\LRp}[1]{\left( #1 \right)}
\newcommand{\LRs}[1]{\left[ #1 \right]}
\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
\newcommand{\LRc}[1]{\left\{ #1 \right\}}
\newcommand{\LRb}[1]{\left| #1 \right|}

\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
\newcommand{\Grad} {\ensuremath{\nabla}}
\newcommand{\Div} {\ensuremath{\nabla\cdot}}
\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
\newcommand{\jump}[1] {\ensuremath{\LRs{\!\left[#1\right]\!}}}
\newcommand{\uh}{\widehat{u}}
\newcommand{\fnh}{\widehat{f}_n}
\renewcommand{\L}{L^2\LRp{\Omega}}
\newcommand{\pO}{\partial\Omega}
\newcommand{\Gh}{\Gamma_h}
\newcommand{\Gm}{\Gamma_{-}}
\newcommand{\Gp}{\Gamma_{+}}
\newcommand{\Go}{\Gamma_0}
\newcommand{\Oh}{\Omega_h}

\newcommand{\eval}[2][\right]{\relax
  \ifx#1\right\relax \left.\fi#2#1\rvert}

\def\etal{{\it et al.~}}

\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
\newcommand{\tensor}[1]{\underline{\vect{#1}}}
\newcommand{\del}{\Delta}
\newcommand{\grad}{\nabla}
\newcommand{\curl}{\grad \times}
\renewcommand{\div}{\grad \cdot}
\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
\newcommand{\eip}[1]{a\left( #1 \right)}
\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}

\newcommand{\circone}{\ding{192}}
\newcommand{\circtwo}{\ding{193}}
\newcommand{\circthree}{\ding{194}}
\newcommand{\circfour}{\ding{195}}
\newcommand{\circfive}{\ding{196}}

\def\arr#1#2#3#4{\left[
\begin{array}{cc}
#1 & #2\\
#3 & #4\\
\end{array}
\right]}
\def\vecttwo#1#2{\left[
\begin{array}{c}
#1\\
#2\\
\end{array}
\right]}
\def\vectthree#1#2#3{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
\end{array}
\right]}
\def\vectfour#1#2#3#4{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
#4\\
\end{array}
\right]}

\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

\newcommand{\G} {\Gamma}
\newcommand{\Gin} {\Gamma_{in}}
\newcommand{\Gout} {\Gamma_{out}}

\newtheorem{remark}{Remark}

%\title{$\epsilon$-explicit analysis of DPG for convection-dominated diffusion}
\title{Notes on the solution of the Navier-Stokes equations using DPG}
\date{}
\begin{document}

\maketitle

\section{Linearized Navier-Stokes equations}

Our approach in applying DPG to the Navier-Stokes equations is to linearize, and then extrapolate DPG to the linearized equations.  The Navier-Stokes equations can be written in terms of the Euler variables $U$ and viscous stresses $\Sigma$ as
\begin{align*}
\div\LRp{F(U)-G(U,\Sigma)}&=0\\
E\Sigma - \grad U&=0.
\end{align*}
The linearized Navier-Stokes equations can be written
\begin{align*}
\div\LRp{\LRp{F_{,U}(U)-G_{,U}(U,\Sigma)}dU-G_{,\Sigma}(U,\Sigma)d\Sigma}&=\text{conservation law residual}\\
E\Sigma - \grad U&= \text{stress law residual}.
\end{align*}
We test the conservation laws with test functions $V$ and stress laws with test functions $V$.  The test norm is extrapolated by identifying like terms with convection-diffusion and extrapolating test norms for groups of variables
\begin{align*}
\nor{\LRp{V,W}}_V^2 =& \nor{V}^2+ \nor{\LRp{F_{,U}(U)-G_{,U}(U,\Sigma)}^TV}^2 + \frac{1}{\rm Re}\nor{G_{,\Sigma}(U,\Sigma)^T\grad V}^2 \\
&+ \min\LRc{{\rm Re},\frac{1}{\LRb{K}}}\nor{W}^2 + \nor{\div W}^2
\end{align*}

\section{Conditioning of local problems}

Notice that, under the above test norm, $V$ and $W$ are decoupled.  Likewise, our local problem decouples into three local problems with submatrices $A_1, A_2, A_3$, where $A_1$ is $\tau_1$ and $\tau_2$, coupled together by the stress equation.  $A_2$ has to do with $\tau_3$, which is decoupled from $\tau_1,\tau_2$ by merit that temperature $T$ and heat flux $q$ do not show up in the stress equations.  $A_3$ is related to $v_1,\ldots, v_4$, and is the main cause of conditioning problems.

\begin{figure}[!h]
\centering
\includegraphics[scale=.75]{figs/GramMatrixSpy.png}
%\subfigure[$\alpha = 1$]{\includegraphics[scale=.475]{figs/aOneConstant.png}}
\caption{Spy plot of the Riesz operator under the robust test norm for Navier-Stokes.}
\end{figure}

We use ${\rm Re} = 100$ to eliminate robustness issues.  After 7 refinements, we have $h_{\rm min} \approx .002$.  The magnitude of the $\L$ term on $v$ is proportional to $dt^{-1}$, and with $dt = .1$, we have a condition number of $\kappa(A_3) = O(1e8)$.

\begin{figure}[!h]
\centering
\includegraphics[scale=.8]{figs/NSConditionNumbers.png}
\caption{Transient residual behavior under poor conditioning.  The condition number estimate is for the entire system; the individual decoupled blocks have significantly lower condition number estimates.}
\end{figure}

Our condition number is now of the order of single precision arithmetic, and we begin to see either divergence or non-monotonic convergence of the transient residual.  Since condition numbers can be misleading, we computed a discrete residual for 100 random loads and averaged them to confirm that the error in our approximation is indeed $O(\kappa(A_3))$.

\begin{figure}[!h]
\centering
\includegraphics[scale=.8]{figs/NSResidualCondition.png}
\caption{Average discrete residual $\nor{b-Ax}_2$.  Convergence of the pseudo-time iteration stalls after the 8th refinement step due to conditioning issues.}
\end{figure}

\subsection{ Cholesky stability}

We found that Cholesky decompositions of the matrices led to factorizations with more diagonally dominant terms when compared to LU factorizations.  Additionally, the failure of Cholesky due to numerical indefiniteness signals a clear stopping point for the method due to roundoff effects.

\section{Singularity in $\rho$}

The singularity in $\rho$ at the plate edge is independent of the Reynolds number and appears to be unbounded.  For $Re = 100$, the singularity continues to grow in magnitude despite the mesh having resolved the diffusive length scale.

\section{Solution strategy}

Specify parameters and motivation, pseudo-time step and inner Newton iteration.

\subsection{Nested solves}

For the compressible Navier-Stokes equations, density $\rho$ and temperature $T$ must both be guaranteed positive to have a physically realistic solution.  Numerically, non-positivity of $\rho$ and $T$ can cause non-convergence of our nonlinear iteration, and in some cases, solution blowup.  In order to ensure positivity of $\rho$ and $T$ for these simulations, during each timestep, we apply a Newton-Raphson with line search to ensure that 
\begin{align*}
\rho + \triangle \rho &> 0\\
T + \triangle T &> 0,
\end{align*}
where $\triangle \rho$ and $\triangle T$ are the Newton-Raphson updates to the solution at each step.  In similar applications, multiple Newton steps per timestep have been shown to accelerate convergence of the pseudo-time algorithm \cite{kirkThesis}.

\subsection{Adaptive time tolerance}

A common technique in the solution of the steady-state Navier-Stokes equations under implicit time discretizations is the use of variable time-stepping.  Typically, these schemes can be expressed as such: at a timestep $i$, the next time step can be expressed as a scaling of the timestep $k$ steps ago
\[
dt_{i+1} = dt_{i-k} \LRp{\frac{R_{i-k}}{R_i}}^r,
\]
where $R_{i-k}$ and $R_i$ are the transient residuals at the $i$th and $(i-k)$th timesteps.  The intuition behind this algorithm is that as transient behavior dies out, we can take larger and larger timesteps, thus accelerating our convergence to steady state.

\textcolor{red}{Talk about DPG and ``changing targets" with variable timestep.}

\bibliographystyle{plain}
\bibliography{paper}

\end{document}

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/data/blender/runner.py

@@ -1,0 +1,103 @@
+# -*- coding: utf-8 -*-
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Follows PEP8
+
+import imp
+import os
+import re
+import sys
+from Blender import Scene
+
+
+class BlenderScript(object):
+
+    def __init__(self):
+        self.args = Arguments()
+        self.render_path = os.path.dirname(self.args['render_path'])
+
+    def render(self):
+        scene = Scene.GetCurrent()
+
+        script = imp.load_source(self.args['script'], self.args['script_path'])
+        blender_initializer = script.BlenderInitializer()
+        blender_initializer.set_up_render(self.args, scene)
+
+        self.set_up_render_context(scene)
+
+        blender_initializer.clean_up()
+
+    def set_up_render_context(self, scene):
+        context = scene.getRenderingContext()
+
+        context.sFrame = 1
+        context.eFrame = 1
+
+        context.imageSizeX(int(self.args['render_width']))
+        context.imageSizeY(int(self.args['render_height']))
+        context.setRenderWinSize(100)
+
+        context.oversampling = True
+        context.OSALevel = 5
+
+        if self.args['alpha']:
+            context.alphaMode = 1
+            context.enableRGBAColor()
+        else:
+            context.alphaMode = 0
+            context.enableRGBColor()
+
+        context.renderPath = self.render_path + os.path.sep
+        context.renderAnim()
+
+
+class Arguments(dict):
+
+    def __init__(self):
+        args = sys.argv[sys.argv.index('--') + 1:]
+        for arg in args:
+            parts = arg.split(':', 1)
+
+            if len(parts) < 2:
+                continue
+
+            key, value = parts[0], parts[1]
+
+            if re.search('^#[0-9A-Fa-f]{6}$', value):
+                self[key] = color(value)
+            elif value.lower() in ('no', 'false'):
+                self[key] = False
+            else:
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/docs/source/conf.py

@@ -1,0 +1,220 @@
+# -*- coding: utf-8 -*-
+#
+# Phatch documentation build configuration file, created by
+# sphinx-quickstart on Thu Aug 27 17:12:37 2009.
+#
+# This file is execfile()d with the current directory set
+# to its containing dir.
+#
+# Note that not all possible configuration values are present in this
+# autogenerated file.
+#
+# All configuration values have a default; values that are commented out
+# serve to show the default.
+#
+# Follows PEP8
+
+import sys
+import os
+
+# If extensions (or modules to document with autodoc) are in another directory,
+# add these directories to sys.path here. If the directory is relative to the
+# documentation root, use os.path.abspath to make it absolute, like shown here.
+sys.path.append(os.path.abspath('../../phatch'))
+
+# -- General configuration ---------------------------------------------------
+
+# Add any Sphinx extension module names here, as strings.
+# They can be extensions
+# coming with Sphinx (named 'sphinx.ext.*') or your custom ones.
+extensions = ['sphinx.ext.autodoc', 'sphinx.ext.doctest', 'sphinx.ext.todo', \
+'sphinx.ext.coverage', 'sphinx.ext.ifconfig']
+
+# Add any paths that contain templates here, relative to this directory.
+templates_path = ['_templates']
+
+# The suffix of source filenames.
+source_suffix = '.rst'
+
+# The encoding of source files.
+#source_encoding = 'utf-8'
+
+# The master toctree document.
+master_doc = 'index'
+
+# General information about the project.
+project = u'Phatch'
+copyright = u'2009, www.stani.be'
+
+# The version info for the project you're documenting, acts as replacement for
+# |version| and |release|, also used in various other places throughout the
+# built documents.
+#
+# The short X.Y version.
+version = '0.2'
+# The full version, including alpha/beta/rc tags.
+release = '0.2'
+
+# The language for content autogenerated by Sphinx. Refer to documentation
+# for a list of supported languages.
+#language = None
+
+# There are two options for replacing |today|: either, you set today to some
+# non-false value, then it is used:
+#today = ''
+# Else, today_fmt is used as the format for a strftime call.
+#today_fmt = '%B %d, %Y'
+
+# List of documents that shouldn't be included in the build.
+#unused_docs = []
+
+# List of directories, relative to source directory, that shouldn't be searched
+# for source files.
+exclude_trees = []
+
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/docs/update.py

@@ -1,0 +1,227 @@
+#!/usr/bin/python
+
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Follows PEP8
+
+import glob
+import os
+from subprocess import call
+
+TOC = '''
+.. toctree::
+   :maxdepth: 2
+
+%s
+
+'''
+
+AUTO = '''
+.. automodule:: %s
+   :members:
+   :undoc-members:
+   :show-inheritance:
+'''
+
+
+def title(header):
+    """Formats a header title.
+
+    :param header: header text
+    :type header: str
+    :returns: header text
+    :rtype: str
+
+    >>> title('header')
+    'header\\n******\\n'
+    """
+    return '%s\n%s\n' % (header, '*' * len(header))
+
+
+def auto(module):
+    """Returns sphinx code to automatically document the module.
+
+    :param module: module name
+    :type module: str
+    :returns: sphinx code
+    :rtype: str
+
+    >>> print(auto('module'))
+    <BLANKLINE>
+    .. automodule:: module
+       :members:
+       :undoc-members:
+       :show-inheritance:
+    <BLANKLINE>
+    """
+    return AUTO % module
+
+
+def toc(modules):
+    """Return sphinx code for module table of contents
+
+    :param modules: module names
+    :type modules: list of str
+    :returns: sphinx code
+    :rtype: str
+
+    >>> toc([])
+    ''
+    >>> print(toc(['foo', 'bar']))
+    <BLANKLINE>
+    .. toctree::
+       :maxdepth: 2
+    <BLANKLINE>
+       bar
+       foo
+    <BLANKLINE>
+    <BLANKLINE>
+    """
+    modules.sort()
+    if not modules:
+        return ''
+    contents = '\n'.join(['   ' + m for m in modules])
+    return TOC % contents
+
+
+def write(filename, module, children):
+    """Write sphinx code for auto documented module to a file
+
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/autocontrast.py

@@ -1,0 +1,185 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+
+# Embedded icon is taken from www.openclipart.org (public domain)
+
+# Follows PEP8
+
+from core import models
+from lib.reverse_translation import _t
+
+#---PIL
+
+
+def init():
+    global Image, ImageOps, imtools
+    import Image
+    import ImageOps
+    from lib import imtools
+
+
+def autocontrast(image, amount=100.0, cutoff=0):
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/border.py

@@ -1,0 +1,256 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+
+# Embedded icon is taken from www.openclipart.org (public domain)
+
+# Follows PEP8
+
+from core import models
+from lib.reverse_translation import _t
+from lib.imtools import has_transparency, has_alpha, get_alpha, \
+    convert_safe_mode, paste
+
+#---PIL
+
+
+def init():
+    global Image, ImageDraw
+    import Image
+    import ImageDraw
+
+OPTIONS = [_t('Equal for all sides'), _t('Different for each side')]
+
+
+def border(image, method, border_width=0, left=0, right=0, top=0, bottom=0,
+        color=0, opacity=100):
+    """
+
+    """
+    #set up sizes, and make the target img
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/brightness.py

@@ -1,0 +1,193 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+
+# Embedded icon is designed by Igor Kekeljevic (http://www.admiror-ns.co.yu).
+
+# Follows PEP8
+
+from core import models
+from lib.reverse_translation import _t
+
+#---PIL
+
+
+def init():
+    global Image, ImageColor, imtools
+    import Image
+    import ImageColor
+    from lib import imtools
+
+
+def brightness(image, amount=50):
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/colorize.py

@@ -1,0 +1,150 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+
+# Embedded icon is designed by Igor Kekeljevic (http://www.admiror-ns.co.yu).
+
+# Follows PEP8
+
+from core import models
+from lib.reverse_translation import _t
+
+#---PIL
+
+
+def init():
+    global Image, ImageOps, imtools
+    import Image
+    import ImageOps
+    from lib import imtools
+
+
+def colorize(image, black, white, amount=100):
+    """Apply a filter
+    - amount: 0-1"""
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/contour.py

@@ -1,0 +1,215 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+#
+# Follows PEP8
+
+# Embedded icon is taken from www.openclipart.org (public domain)
+
+from core import models
+from lib.reverse_translation import _t
+from lib.imtools import has_transparency, paste
+
+#---PIL
+
+
+def init():
+    global Image, ImageOps, imtools
+    import Image
+    import ImageOps
+    from lib import imtools
+    global HTMLColorToRGBA
+    from lib.colors import HTMLColorToRGBA
+
+
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/contrast.py

@@ -1,0 +1,168 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+
+# Embedded icon is taken from www.openclipart.org (public domain)
+
+# Follows PEP8
+
+from core import models
+from lib.reverse_translation import _t
+
+#---PIL
+
+
+def init():
+    global Image, ImageColor, imtools
+    import Image
+    import ImageColor
+    from lib import imtools
+
+
+def contrast(image, amount=50):
+    """Adjust brightness from black to white
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/copy.py

@@ -1,0 +1,215 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+
+# Embedded icon is designed by Igor Kekeljevic (http://www.admiror-ns.co.yu).
+#
+# Follows PEP8
+
+
+from core import ct, models
+from lib.reverse_translation import _t
+
+#no need to lazily import these as they are always imported
+import os
+import shutil
+
+
+class Action(models.Action):
+    """Defined variables: <filename> <type> <folder> <width> <height>"""
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/crop.py

@@ -1,0 +1,156 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+#
+# Follows PEP8
+
+# Embedded icon is taken from www.openclipart.org (public domain)
+
+from core import models
+from lib.reverse_translation import _t
+from lib.imtools import auto_crop
+
+#---PIL
+
+
+def init():
+    global Image, ImageOps
+    import Image
+    import ImageOps
+
+
+def crop(image, mode=None, all=0, left=0, right=0, top=0, bottom=0):
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/delete_tags.py

@@ -1,0 +1,207 @@
+# -*- coding: utf-8 -*-
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+
+# Embedded icon is designed by Alexandre Moore (http://nuovext.pwsp.net/).
+
+# Follows PEP8
+
+from core import ct, models
+from lib.reverse_translation import _t
+
+#no need to lazily import these as they are always imported
+import re
+
+METHODS = [_t('All'), 'Exif', 'Iptc', _t('One')]
+
+
+class Action(models.Action):
+    label = _t('Delete Tags')
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/desaturate.py

@@ -1,0 +1,189 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Embedded icon is designed by Igor Kekeljevic (http://www.admiror-ns.co.yu).
+
+# Follows PEP8
+
+from core import models
+from lib.reverse_translation import _t
+
+#--- PIL function
+
+
+def init():
+    #lazy import
+    global Image, ImageOps, imtools
+    import Image
+    import ImageOps
+    from lib import imtools
+
+
+def grayscale(image, amount=100):
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/fit.py

@@ -1,0 +1,234 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Embedded icon is taken from www.openclipart.org (public domain)
+
+# Follows PEP8
+
+from core import models
+from lib.reverse_translation import _t
+
+#---PIL
+
+
+def init():
+    global Image, ImageOps
+    import Image
+    import ImageOps
+    global HTMLColorToRGBA
+    from lib.colors import HTMLColorToRGBA
+
+
+def fit(image, size, method, bleed, centering):
+    return ImageOps.fit(image, size, method, bleed, centering)
+
+#---Phatch
+
+
+class Action(models.Action):
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/geek.py

@@ -1,0 +1,177 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python.
+
+# Embedded icon is designed by Alexandre Moore (http://nuovext.pwsp.net/).
+
+# Follows PEP8
+
+import os
+
+from core import config
+from core import ct, models
+from lib.reverse_translation import _t
+from lib import system
+
+COMMANDS = [
+    'convert file_in.tif -bordercolor snow -background black '\
+        + '+polaroid file_out.png',
+    'convert -blur 0x5 file_in.tif file_out.png']
+
+try:
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/geotag.py

@@ -1,0 +1,226 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+#
+# The beautiful icon is thanks to the work of the Geotag Icon Project
+# http://www.geotagicons.com/
+#
+# Follows PEP8
+
+from core import ct, models
+from lib.reverse_translation import _t
+
+
+def init():
+    global gps
+    from lib import gps
+
+
+class Action(models.Action):
+    """Defined variables: <filename> <type> <folder> <width> <height>"""
+
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/highlight.py

@@ -1,0 +1,232 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be)
+# for editing python files.
+
+# Embedded icon is taken from www.openclipart.org (public domain)
+
+# Follows PEP8
+
+from core import models
+from lib.reverse_translation import _t
+from lib.openImage import open as open_image
+from lib.imtools import has_transparency, paste
+
+#---Pil
+
+
+def init():
+    global Image, ImageMath, imtools
+    import Image
+    import ImageMath
+    from lib import imtools
+
+
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/mask.py

@@ -1,0 +1,162 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+
+# Embedded icon is taken from www.openclipart.org (public domain)
+
+# Follows PEP8
+
+from core import models
+from lib.reverse_translation import _t
+from lib.openImage import open as open_image
+from lib.imtools import has_transparency
+
+MASK = 'http://photobatch.wikidot.com/local--files/action-mask/mask_torn.png'
+MASKS = [MASK]
+#---Pil
+
+
+def init():
+    global Image, ImageMath, imtools
+    import Image
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/maximum.py

@@ -1,0 +1,150 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+
+# Embedded icon is taken from www.openclipart.org (public domain)
+
+# Follows PEP8
+
+from core import models
+from lib.reverse_translation import _t
+
+#---PIL
+
+
+def init():
+    global Image, ImageFilter, imtools
+    import Image
+    import ImageFilter
+    from lib import imtools
+
+
+def maximum(image, radius, amount=100):
+    """Apply a filter
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/mirror.py

@@ -1,0 +1,261 @@
+# -*- coding: utf-8 -*-
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+
+# Embedded icon is designed by Arielle B Cruz (http://www.abcruz.com/)
+
+#Follows PEP8
+
+from core import models
+from lib.reverse_translation import _t
+from lib.imtools import convert_safe_mode, paste
+
+#---PIL
+
+
+def init():
+    global Image
+    import Image
+
+# Declare constants here
+
+BOTH = _t('Both')
+HORIZONTAL = _t('Horizontal')
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/offset.py

@@ -1,0 +1,121 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+
+# Embedded icon is taken from www.openclipart.org (public domain)
+
+# Follows PEP8
+
+from core import models
+from lib.reverse_translation import _t
+
+#---PIL
+
+
+def init():
+    global ImageChops
+    import ImageChops
+
+
+def offset(image, horizontal_offset, vertical_offset=None):
+    return ImageChops.offset(image, horizontal_offset, vertical_offset)
+
+#---Phatch
+
+
+class Action(models.Action):
+    label = _t('Offset')
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/save_metadata.py

@@ -1,0 +1,221 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+
+# Embedded icon is designed by Igor Kekeljevic (http://www.admiror-ns.co.yu).
+
+# Follows PEP8
+
+from core import ct, models, pil
+from lib.reverse_translation import _t
+
+#no need to lazily import these as they are always imported
+import shutil
+import os
+
+
+class Action(models.LosslessSaveMixin, models.Action):
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/scale.py

@@ -1,0 +1,234 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Embedded icon is designed by Igor Kekeljevic (http://www.admiror-ns.co.yu).
+
+# Follows PEP8
+
+from core import models
+from lib.reverse_translation import _t
+
+
+def init():
+    global Image
+    import Image
+
+
+def preserve_proportions(x0, y0, x1, y1):
+    scaleX = float(x1) / x0
+    scaleY = float(y1) / y0
+    if scaleX < scaleY:
+        y1 = int(round(y0 * scaleX))
+    else:
+        x1 = int(round(x0 * scaleY))
+    return x1, y1
+
+
+class Action(models.Action):
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/shadow.py

@@ -1,0 +1,319 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+#
+# Follows PEP8
+
+# Embedded icon is taken from www.openclipart.org (public domain)
+
+from core import models
+from lib.reverse_translation import _t
+from lib.imtools import has_transparency, paste
+
+#---PIL
+
+
+def init():
+    #lazily import
+    global Image, ImageChops, ImageFilter, imtools
+    import Image
+    import ImageChops
+    import ImageFilter
+    from lib import imtools
+
+
+def drop_shadow(image, horizontal_offset=5, vertical_offset=5,
+        background_color=(255, 255, 255, 0), shadow_color=0x444444,
+        border=8, shadow_blur=3, force_background_color=False, cache=None):
+    """Add a gaussian blur drop shadow to an image.
+
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/sketch.py

@@ -1,0 +1,159 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+
+# Embedded icon is taken from
+# http://www.tutorial9.net/resources/free-icon-pack-web-injection/
+# by designer Jonatan Castro Fernandez.
+
+# Follows PEP8
+
+from core import models
+from lib.reverse_translation import _t
+
+#---Pil
+
+
+def init():
+    global Image, ImageMath, ImageOps, ImageFilter
+    import Image
+    import ImageMath
+    import ImageOps
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/text.py

@@ -1,0 +1,146 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python.
+
+# Embedded icon is taken from www.openclipart.org (public domain)
+
+# Follows PEP8
+
+from core import models
+from lib.reverse_translation import _t
+
+
+def init():
+    global Image, ImageDraw, ImageFont
+    import Image
+    import ImageDraw
+    import ImageFont
+    global calculate_location, convert_safe_mode
+    from lib.imtools import calculate_location, convert_safe_mode
+
+
+def draw_text(image, text, horizontal_offset, vertical_offset,
+              horizontal_justification, vertical_justification, size,
+              color='#FFFFFF', orientation=None, font=None):
+    """Draws text on an image."""
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/transpose.py

@@ -1,0 +1,171 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+
+# Embedded icon is taken from www.openclipart.org (public domain)
+
+# Follows PEP8
+
+from core import models
+from lib.reverse_translation import _t
+
+#---PIL
+
+
+def init():
+    global Image, imtools
+    import Image
+    from lib import imtools
+
+
+def transpose(image, method, amount=100):
+    transposed = image.transpose(getattr(Image, method))
+    if amount < 100:
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/warm_up.py

@@ -1,0 +1,199 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2010 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+
+# Embedded icon is created by Stani, but derived
+# from Igor Kekeljevic (http://www.admiror-ns.co.yu).
+
+# Based on Stani's colorize
+# Copyright (C) 2010 by Pawel T. Jochym <jochym@gmail.com>, www.stani.be
+
+# Make a colorized version of the image with midtone shifted to
+# prescribed color value.
+
+# Follows PEP8
+
+from core import models
+from core.translation import _t
+
+
+#---PIL
+def init():
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/actions/watermark.py

@@ -1,0 +1,164 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python.
+
+# Embedded icon is taken from www.openclipart.org (public domain)
+
+# Follows PEP8
+
+from core import models
+from lib.reverse_translation import _t
+from lib.imtools import convert_safe_mode
+
+
+def init():
+    #lazily import
+    global Image
+    import Image
+    global generate_layer
+    from lib.imtools import generate_layer
+
+
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/app.py

@@ -1,0 +1,234 @@
+# -*- coding: UTF-8 -*-
+
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008  www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Follows PEP8
+
+import os
+import optparse
+import sys
+import urllib
+
+from data.info import INFO
+from core import config
+
+VERSION = "%(name)s %(version)s" % INFO
+
+
+def fix_path(path):
+    #TODO: move me to lib/system.py
+    if path.startswith('file://'):
+        return urllib.unquote(path[7:])
+    return path
+
+
+def parse_locale(config_paths):
+    if '-l' in sys.argv:
+        index = sys.argv.index('-l') + 1
+        if index >= len(sys.argv):
+            sys.exit('Please specify locale language after "-l".')
+        canonical = sys.argv[index]
+    else:
+        canonical = 'default'
+    config.load_locale('phatch', config_paths["PHATCH_LOCALE_PATH"], canonical)
+
+
+def parse_options():
+
+    parser = optparse.OptionParser(
+        usage="""
+  %(name)s [actionlist]
+  %(name)s [options] [actionlist] [image folders/files/urls]
+  %(name)s --inspect [image files/urls]
+  %(name)s --droplet [actionlist/recent] [image files/urls]""" % INFO + """
+
+%s:
+  phatch action_list.phatch
+  phatch --verbose --recursive action_list.phatch image_file.png image_folder
+  phatch --inspect image_file.jpg
+  phatch --droplet recent""" % _('Examples'),
+        version=VERSION,
+    )
+    parser.add_option("-c", "--console", action="store_true",
+        dest="console",
+        default=False,
+        help=_("Run %s as console program without a gui") % INFO['name'])
+    parser.add_option("-d", "--droplet", action="store_true",
+        dest="droplet",
+        default=False,
+        help=_("Run %s as a gui droplet") % INFO['name'])
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/console/__init__.py

@@ -1,0 +1,19 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatchrecommends SPE (http://pythonide.stani.be) for editing python files.
+#
+# Follows PEP8

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/console/console.py

@@ -1,0 +1,203 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+#
+# Follows PEP8
+
+
+#---import modules
+
+#standard library
+import os
+import sys
+
+if __name__ == '__main__':
+    sys.path.insert(0, '../..')
+    from phatch.phatch import init_config_paths
+    init_config_paths()
+
+#gui-independent
+from core import api, ct
+from core.message import FrameReceiver, ProgressReceiver
+from lib import formField
+from lib import safe
+from lib.unicoding import ENCODING
+
+#api.init()
+
+#---functions
+
+
+def u(txt):
+    return txt.encode(ENCODING, 'replace')
+
+
+def ask(message, answers):
+    answer = None
+    while not(answer in answers):
+        answer = raw_input(u(message)).strip().lower()
+    return answer
+
+
+def ask_yes_no(message):
+    return ask(message, [_('yes'), _('no')]) == _('yes')
+
+#---classes
+
+
+class CliMixin:
+    def show_error(self, message, exit=True):
+        self.show_message(u'\n%s: %s' % (_('Error'), message))
+        if exit:
+            self.exit()
+
+    def show_message(self, *messages):
+        self.write(u'\n'.join(messages) + '\n')
+
+    def show_notification(self, message, *args, **keyw):
+        self.show_message(message)
+
+    def write(self, message):
+        if self.verbose:
+            self.output.write(u(message))
+            self.output.flush()
+
+    def exit(self):
+        sys.exit()
+
+    show_info = show_message
+
+
+class Progress(CliMixin, ProgressReceiver):
+    def __init__(self, title, parent_max, child_max, verbose, output, \
+                                    message=''):
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/core/api.py

@@ -1,0 +1,935 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2009 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+
+# Follows PEP8
+
+try:
+    _
+except NameError:
+    __builtins__['_'] = unicode
+
+#---import modules
+
+#standard library
+import codecs
+import glob
+import operator
+import os
+import pprint
+import string
+import time
+import traceback
+from cStringIO import StringIO
+from datetime import timedelta
+
+#gui-independent
+from data.version import VERSION
+from lib import formField
+from lib import metadata
+from lib import openImage
+from lib import safe
+from lib.odict import ReadOnlyDict
+from lib.unicoding import ensure_unicode, exception_to_unicode, ENCODING
+
+import ct
+import pil
+from message import send
+
+#---constants
+PROGRESS_MESSAGE = 'In: %s%s\nFile' % (' ' * 100, '.')
+SEE_LOG = _('See "%s" for more details.') % _('Show Log')
+TREE_HEADERS = ['filename', 'type', 'folder', 'subfolder', 'root',
+    'foldername']
+TREE_VARS = set(TREE_HEADERS).union(pil.BASE_VARS)
+TREE_HEADERS += ['index', 'folderindex']
+ERROR_INCOMPATIBLE_ACTIONLIST = \
+_('Sorry, the action list seems incompatible with %(name)s %(version)s.')
+
+ERROR_UNSAFE_ACTIONLIST_INTRO = _('This action list is unsafe:')
+ERROR_UNSAFE_ACTIONLIST_DISABLE_SAFE = \
+_('Disable Safe Mode in the Tools menu if you trust this action list.')
+ERROR_UNSAFE_ACTIONLIST_ACCEPT = \
+_("Never run action lists from untrusted sources.") + ' ' +\
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/core/config.py

@@ -1,0 +1,247 @@
+# -*- coding: UTF-8 -*-
+
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008  www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Follows PEP8
+
+import gettext
+import glob
+import locale
+import os
+import subprocess
+import shutil
+import sys
+
+from lib import desktop
+from lib import system
+from lib.unicoding import ensure_unicode
+
+#-- nosetests
+
+
+class Paths:
+
+    def __getitem__(self, key):
+        return 'path'
+
+USER_PATH = desktop.USER_FOLDER
+PATHS = Paths()
+PHATCH_ACTIONLISTS_PATH = '.'
+
+
+def _wrap(path):
+    return os.path.join(path, 'phatch')
+
+
+USER_CACHE_PATH = _wrap(desktop.USER_CACHE_FOLDER)
+USER_FONTS_CACHE_PATH = os.path.join(USER_CACHE_PATH, 'fonts.cache')
+USER_LOG_PATH = os.path.join(USER_CACHE_PATH, 'log')
+USER_PREVIEW_PATH = os.path.join(USER_CACHE_PATH, 'preview')
+
+USER_CONFIG_PATH = _wrap(desktop.USER_CONFIG_FOLDER)
+USER_SETTINGS_PATH = os.path.join(USER_CONFIG_PATH, 'settings.py')
+
+USER_DATA_PATH = _wrap(desktop.USER_DATA_FOLDER)
+USER_ACTIONS_PATH = os.path.join(USER_DATA_PATH, 'actions')
+USER_ACTIONLISTS_PATH = os.path.join(USER_DATA_PATH, 'actionlists')
+USER_BIN_PATH = os.path.join(USER_DATA_PATH, 'bin')
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/core/ct.py

@@ -1,0 +1,131 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Follows PEP8
+
+try:
+    _
+except NameError:
+    _ = unicode
+
+import os
+import sys
+from data import license
+from data.info import INFO
+from lib.reverse_translation import _t
+from config import USER_PATH, USER_DATA_PATH, USER_CONFIG_PATH,\
+    USER_CACHE_PATH, USER_ACTIONLISTS_PATH, USER_ACTIONS_PATH,\
+    USER_BIN_PATH, USER_FONTS_PATH, USER_HIGHLIGHTS_PATH, \
+    USER_LOG_PATH, USER_MASKS_PATH, USER_SETTINGS_PATH, \
+    USER_WATERMARKS_PATH
+
+#---description
+DESKTOP_ENTRY_COMMENT = _('Easily batch process images and edit metadata')
+DESCRIPTION = _('Photo Batch Processor')
+LICENSE = license.GPL
+CONTACT = '%(author)s <%(author_email)s>' % INFO
+
+TITLE = '%(name)s' % INFO
+COPYRIGHT = '%(copyright)s (%(url)s)' % INFO
+EXTENSION = '%(extension)s' % INFO
+FRAME_TITLE = '%%s%%s - %s' % TITLE
+SEND_MAIL = 'mailto:%(author_email)s?subject=%%s&body=%%s' % INFO
+
+PLATFORM = sys.platform
+
+if PLATFORM.startswith('darwin'):
+    LINUX, WINDOWS, MAC = False, False, True
+    PLATFORM = 'mac'
+elif PLATFORM.startswith('win'):
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/core/message.py

@@ -1,0 +1,117 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+
+# Follows PEP8
+
+#---import modules
+
+#gui-independent
+import os
+from lib.events import send, Receiver  # send is used when message is imported
+from lib.unicoding import ensure_unicode
+
+#---classes
+
+
+class FrameReceiver(Receiver):
+    #---pubsub
+    def _pubsub(self):
+        Receiver.__init__(self, 'frame')
+        #Pubsub events
+        self.subscribe('append_save_action')
+        self.subscribe('show_execute_dialog')
+        self.subscribe('show_error')
+        self.subscribe('show_files_message')
+        self.subscribe('show_info')
+        self.subscribe('show_message')
+        self.subscribe('show_notification')
+        self.subscribe('show_progress')
+        self.subscribe('show_progress_error')
+        self.subscribe('show_scrolled_message')
+        self.subscribe('show_image_tree')
+        self.subscribe('show_status')
+
+    def append_save_action(self, actions):
+        """To be overwritten."""
+        pass
+
+    def show_execute_dialog(self, result, settings, files=None):
+        """To be overwritten."""
+        pass
+
+    def show_error(self, message):
+        """To be overwritten."""
+        pass
+
+    def show_files_message(self, result, message, title, files):
+        """To be overwritten."""
+        pass
+
+    def show_progress(self, title, parent_max, child_max, message=''):
+        """To be overwritten.
+        parent_max -> parent loop, eg images
+        child_max  -> child loop, eg actions & open"""
+        pass
+
+    def show_progress_error(self, result, message, ignore=True):
+        """To be overwritten."""
+        pass
+
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/core/pil.py

@@ -1,0 +1,736 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2009 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+
+# Follows PEP8
+
+"""All PIL related issues."""
+
+#FIXME:
+# - info should be defined on layer level
+#   -> move call afterwards also to layer level
+#   -> adapt image inspector
+
+import datetime
+import os
+import re
+import types
+
+import Image
+
+#todo make this lazy
+from lib import formField
+from lib import imtools
+from lib import metadata
+from lib import openImage
+from lib import system
+from lib import thumbnail
+from lib import unicoding
+from lib.reverse_translation import _t
+from lib.formField import RE_FILE_IN, RE_FILE_OUT
+
+from ct import TITLE
+from config import USER_BIN_PATH
+
+#from other import EXIF
+
+system.set_bin_paths([USER_BIN_PATH])
+
+try:
+    import pyexiv2
+    from lib import _pyexiv2 as exif
+except:
+    pyexiv2 = None
+    exif = False
+WWW_PYEXIV2 = 'http://tilloy.net/dev/pyexiv2/'
+NEEDS_PYEXIV2 = _('pyexiv2 needs to be installed') + ' (%s)' % WWW_PYEXIV2
+
+CONVERTED_MODE = \
+_('%(mode)s has been converted to %(mode_copy)s to save as %(format)s.')
+
+DYNAMIC_VARS = set(('width', 'height', 'size', 'mode', 'transparency'))
+IMAGE_DEFAULT_DPI = 72
+SEPARATOR = '_'  # should be same as in core.translations
+MONTHS = (_t('January'), _t('February'), _t('March'), _t('April'),
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/core/preview.py

@@ -1,0 +1,55 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+
+# Follows PEP8
+
+if __name__ == '__main__':
+    import sys
+    sys.path.insert(0, '../..')
+    from phatch.phatch import init_config_paths
+    init_config_paths()
+
+import os
+import Image
+import api
+from config import USER_PREVIEW_PATH
+from lib import openImage
+from lib.system import ensure_path
+
+
+def generate(source, size=(48, 48), path=USER_PREVIEW_PATH, force=True):
+    source_image = openImage.open(source)
+    source_image.thumbnail(
+        (min(source_image.size[0], size[0] * 1),
+        min(source_image.size[0], size[0] * 1)),
+        Image.ANTIALIAS)
+    ensure_path(path)
+    for Action in api.ACTIONS.values():
+        action = Action()
+        filename = os.path.join(path, action.label + '.png')
+        if os.path.exists(filename) and not force:
+            continue
+        action.init()
+        result = action.apply_pil(source_image.copy())
+        result.thumbnail(size, Image.ANTIALIAS)
+        result.save(filename)
+
+
+if __name__ == '__main__':
+    api.init()
+    generate('/home/stani/sync/python/phatch/icons/lenna/lenna_new.png')

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/core/safeGlobals.py

@@ -1,0 +1,60 @@
+# -*- coding: UTF-8 -*-
+
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for python editing.
+
+# Follows PEP8
+
+import math
+import random
+
+from lib.metadata import now
+
+
+def allow(key):
+    return key[0] != '_'
+
+
+def add_dictionary(namespace, dictionary):
+    for key, value in dictionary.items():
+        if allow(key):
+            namespace[key] = value
+
+
+def add_module(namespace, module):
+    """Add module dictionary to the ``namespace``. This is the equivalent
+    for::
+
+        from module import *
+
+    This used for the GLOBALS variable.
+
+    :param namespace: namespace
+    :type namespace: dict
+    :param module_dict: module
+    :type module_dict: module
+    """
+    add_dictionary(namespace, module.__dict__)
+
+
+def safe_globals():
+    GLOBALS = {}
+    add_module(GLOBALS, math)
+    add_module(GLOBALS, random)
+    GLOBALS['now'] = now
+    return GLOBALS

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/data/info.py

@@ -1,0 +1,515 @@
+# -*- coding: UTF-8 -*-
+
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for python editing.
+
+"""Important: Run this file everytime info is changed."""
+
+
+import codecs
+import sys
+import time
+
+
+#constants
+NAME = 'Phatch'
+AUTHOR = 'Stani'
+AUTHOR_EMAIL = 'spe.stani.be@gmail.com'
+GPL_VERSION = '3'
+STANI = {
+    'name': AUTHOR,
+    'email': AUTHOR_EMAIL,
+    'url': 'www.stani.be',
+}
+NADIA = {
+    'name': 'Nadia Alramli',
+    'email': 'mail@nadiana.com',
+    'url': 'http://nadiana.com',
+}
+
+SUPPORTED_LANGUAGES = ['Dutch', 'English']
+
+
+from version import VERSION, DATE
+
+#credits
+CREDITS = {
+    'code': [
+        STANI,
+        NADIA,
+        {'name': u'Erich Heine',
+            'email':'sophacles@gmail.com'},
+        {'name': u'Juho Vepsäläinen',
+            'email':'bebraw@gmail.com'},
+        {'name': u'Robin Mills',
+            'email': 'robin@clanmills.com'},
+        {'name': 'Bas van Oostveen',
+            'email': 'v.oostveen@gmail.com'},
+        {'name': 'Pawel T. Jochym',
+            'email': 'jochym@gmail.com'},
+                    ],
+    'documentation': [
+        STANI,
+        {'name': u'Frédéric Mantegazza',
+        'email': 'frederic.mantegazza@gbiloba.org',
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/data/version.py

@@ -1,0 +1,19 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2009  www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+BASE = "0.2.7"
+VERSION = "0.2.7"
+DATE = "Wed, 10 Mar 2010 18:49:51"

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/colors.py

@@ -1,0 +1,69 @@
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Follows PEP8
+
+
+def RGBToHTMLColor(rgb_tuple):
+    """ convert an (R, G, B) tuple to #RRGGBB """
+    hexcolor = '#%02x%02x%02x' % rgb_tuple
+    # that's it! '%02x' means zero-padded, 2-digit hex values
+    return hexcolor
+
+
+def HTMLColorToRGB(colorstring):
+    """ convert #RRGGBB to an (R, G, B) tuple """
+    colorstring = colorstring.strip()
+    if colorstring[0] == '#':
+        colorstring = colorstring[1:]
+    if len(colorstring) != 6:
+        raise ValueError("input #%s is not in #RRGGBB format" % colorstring)
+    r, g, b = colorstring[:2], colorstring[2:4], colorstring[4:]
+    r, g, b = [int(n, 16) for n in (r, g, b)]
+    return (r, g, b)
+
+
+def HTMLColorToRGBA(colorstring, opacity):
+    r, g, b = HTMLColorToRGB(colorstring)
+    return (r, g, b, opacity)
+
+
+def HTMLColorToPILColor(colorstring):
+    """ converts #RRGGBB to PIL-compatible integers"""
+    colorstring = colorstring.strip()
+    while colorstring[0] == '#':
+        colorstring = colorstring[1:]
+    # get bytes in reverse order to deal with PIL quirk
+    colorstring = colorstring[-2:] + colorstring[2:4] + colorstring[:2]
+    # finally, make it numeric
+    color = int(colorstring, 16)
+    return color
+
+
+def PILColorToRGB(pil_color):
+    """ convert a PIL-compatible integer into an (r, g, b) tuple """
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/fonts.py

@@ -1,0 +1,262 @@
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Follows PEP8
+
+import glob
+import os
+import re
+import subprocess
+import sys
+import system
+
+from lib import safe
+
+USER_FONTS_CACHE_PATH = None
+ROOT_FONTS_CACHE_PATH = None
+WRITABLE_FONTS_CACHE_PATH = None
+
+_FONT_DICTIONARY = None
+_FONT_NAMES = None
+
+re_WORD = re.compile('([A-Z0-9]+[^A-Z0-9]*)', re.UNICODE)
+re_SPACE = re.compile('_|\W+', re.UNICODE)
+LOCATE = [
+    ['locate', '-i', '.ttf', '.otf'],
+    ['find', '/', '-iname', '*.ttf', '-o', '-name', '*.otf'],
+]
+
+#collect_fonts (system dependent)
+if sys.platform.startswith('win'):
+    #3thrd party module in other
+    from other.findsystem import findFonts
+
+    def collect_fonts():
+        """Collect a list of all font filenames."""
+        return findFonts()
+else:
+    #better unix alternative for collect_fonts/findFonts
+    #presume findutils are present
+    if not system.find_exe('locate'):
+        sys.exit(_('Please install "%s" first.') % 'locate')
+
+    def locate_files(command):
+        return subprocess.Popen(command,
+            stdout=subprocess.PIPE).stdout.read().splitlines()
+
+    def collect_fonts():
+        """Collect a list of all font filenames."""
+        #try first with locate otherwise with find
+        for command in LOCATE:
+            try:
+                if system.find_exe(command[0]):
+                    output = locate_files(command)
+                    files = [line for line in output
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/gps.py

@@ -1,0 +1,244 @@
+# Copyright (C) 2009 Robin Mills, San Jose, California, www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# All rights donated to the open source project Phatch. This code may
+# be published using a license acceptable to project Phatch.
+
+# Follows PEP8
+
+import os
+import datetime
+import xml.dom.minidom
+
+from other import surd
+
+try:
+    import pyexiv2
+except ImportError:
+    pyexiv2 = None
+
+# Rational number support
+
+
+def r(f):
+    """r(float) - get a Rational number for a float"""
+    s = surd.surd(float(f))
+    return pyexiv2.Rational(s.num, s.denom)
+
+
+def d(angle):
+    """d(any) - get degrees from a number :eg d(33.41) -> 33"""
+    return int(angle)
+
+
+def m(angle):
+    """m(any) - get minutes from a number :eg d(33.41) -> 24"""
+    return int(angle * 60 - d(angle) * 60)
+
+
+def s(angle):
+    """s(any) - get seconds from a number :eg s(33.41) -> 36"""
+    return int(angle * 3600 - d(angle) * 3600 - m(angle) * 60)
+
+
+# dictionary search (closest match)
+def search(dict, target):
+    """search(dict,taget) - search for closest match"""
+    s = sorted(dict.keys())
+    N = len(s)
+    low = 0
+    high = N - 1
+
+    while low < high:
+        mid = (low + high) / 2
+        if s[mid] < target:
+            low = mid + 1
+        else:
+            high = mid
+    return s[low]
+
+
+# XML functions
+def get_xml_timez(phototime, timeshift):
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/imageTable.py

@@ -1,0 +1,436 @@
+# -*- coding: UTF-8 -*-
+
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for python editing.
+
+# Follows PEP8
+
+if __name__ == '__main__':
+    import gettext
+    gettext.install('test')
+
+import glob
+import os
+import re
+
+import metadata
+import openImage
+import unicoding
+
+try:
+    import pyexiv2
+except ImportError:
+    pyexiv2 = None
+
+SEPARATOR = '_'
+
+ALL = _('All')
+SELECT = _('Select')
+RE_TAG_LAST = re.compile('[.](Canon|Sony|Nikon|Leica|Panasonic)')
+RE_TAG_ERROR = _('''\
+The tag "%s" is not valid.
+It should follow the syntax: Exif_* or Iptc_*\
+''')
+RE_TAG_SELECT_NOT = re.compile('[%s]|exif|iptc|#' % SEPARATOR)
+
+MARKUP = '**%s**'
+NONE = ''
+THUMB_SIZE = (128, 128)
+
+
+class TableImage:
+
+    def __init__(self, filename, thumb_size=THUMB_SIZE):
+        """For every image one TableImage is created. It is a helper
+        class to display the metadata in a grid.
+
+        :param filename: image filename
+        :type filename: string
+        :param thumb_size: size of the thumbnail
+        :type thumb_size: tuple of int
+        """
+        self.filename = filename
+        self.thumb_size = thumb_size
+        self.update()
+
+    def update(self):
+        """Update the table from the image source file."""
+        self.label = os.path.basename(self.filename)
+        self.thumb = openImage.open_thumb(self.filename, size=THUMB_SIZE)
+        info = metadata.InfoExtract(self.filename)
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/imtools.py

@@ -1,0 +1,1125 @@
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Follows PEP8
+
+import os
+from cStringIO import StringIO
+from itertools import cycle
+from urllib import urlopen
+
+import Image
+import ImageDraw
+import ImageEnhance
+import ImageOps
+
+import system
+
+ALL_PALETTE_INDICES = set(range(256))
+CHECKBOARD = {}
+COLOR_MAP = [255] * 128 + [0] * 128
+WWW_CACHE = {}
+
+EXT_BY_FORMATS = {
+    'JPEG': ['JPG', 'JPEG', 'JPE'],
+    'TIFF': ['TIF', 'TIFF'],
+    'SVG': ['SVG', 'SVGZ'],
+}
+FORMATS_BY_EXT = {}
+for format, exts in EXT_BY_FORMATS.items():
+    for ext in exts:
+        FORMATS_BY_EXT[ext] = format
+
+
+class InvalidWriteFormatError(Exception):
+    pass
+
+
+def get_format(ext):
+    """Guess the image format by the file extension.
+
+    :param ext: file extension
+    :type ext: string
+    :returns: image format
+    :rtype: string
+
+    .. warning::
+
+        This is only meant to check before saving files. For existing files
+        open the image with PIL and check its format attribute.
+
+    >>> get_format('jpg')
+    'JPEG'
+    """
+    ext = ext.lstrip('.').upper()
+    return FORMATS_BY_EXT.get(ext, ext)
+
+
+def get_format_filename(filename):
+    """Guess the image format by the filename.
+
+    :param filename: filename
+    :type filename: string
+    :returns: image format
+    :rtype: string
+
+    .. warning::
+
+        This is only meant to check before saving files. For existing files
+        open the image with PIL and check its format attribute.
+
+    >>> get_format_filename('test.tif')
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/linux/nautilusExtension.py

@@ -1,0 +1,78 @@
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Follows PEP8
+
+import codecs
+import os
+from core.ct import USER_PATH
+from lib.unicoding import ENCODING
+
+TEMPLATE = """
+from urllib import unquote
+from subprocess import call
+import nautilus
+%(preload)s
+
+class %(name)s_extension(nautilus.MenuProvider):
+    def __init__(self):
+        pass
+
+    def menu_activate_cb(self, menu, files):
+        for file in files:
+            if file.is_gone():
+                return
+        files = ["'%%s'"%%unquote(file.get_uri()[7:]) for file in files]
+        call('%(command)s'%%' '.join(files),shell=True)
+
+    def get_file_items(self, window, files):
+        #only directories and readable image files are accepted
+        files = [file for file in files \
+            if (file.get_uri_scheme() == 'file' and
+            file.get_mime_type() in %(mimetypes)s)]
+        #return if nothing to do
+        if not files: return
+        #install menu
+        item = nautilus.MenuItem('NautilusPython::%(name)s',
+                                 %(label)s,
+                                 %(tooltip)s)
+        #bind/connect menu item with method
+        item.connect('activate', self.menu_activate_cb, files)
+        #return menu item
+        return item,
+"""
+
+NAUTILUS_USER_PYTHON_EXTENSIONS = os.path.join(USER_PATH, '.nautilus',
+    'python-extensions')
+
+
+def nautilus_exists():
+    return os.path.isdir(NAUTILUS_USER_PYTHON_EXTENSIONS)
+
+
+def create_nautilus_extension(name, label, command, mimetypes, tooltip='',
+        preload='', encoding=ENCODING):
+    params = {
+        'name': name,
+        'label': label,
+        'command': command,
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/metadata.py

@@ -1,0 +1,2181 @@
+# -*- coding: UTF-8 -*-
+
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for python editing.
+
+# Follows PEP8
+
+
+# import rpdb2; rpdb2.start_embedded_debugger('x')
+
+#TODO: PROVIDE THESE AS EXTRACT METHOD, exif rotation
+#synchronize between exif automatically? pil manual
+#sphinx doc everything
+
+import datetime
+import os
+import re
+import time
+
+try:
+    import pyexiv2
+    import _pyexiv2
+except ImportError:
+    pyexiv2 = None
+    _pyexiv2 = None
+
+import imtools
+import odict
+import unicoding
+from desktop import DESKTOP_FOLDER
+from metadataTest import DateTime, INFO_TEST, is_string, MONTHS, now, WEEKDAYS
+from reverse_translation import _t
+
+RE_VAR = re.compile('<.+?>')
+
+
+DATETIME_KEYS = ['year', 'month', 'day', 'hour', 'minute', 'second']
+RE_DATETIME_KEYS = re.compile('(%s)$' % ('|'.join(['[.]' + key
+    for key in DATETIME_KEYS])))
+
+RE_PYEXIV2_TAG = re.compile('^(Exif|Iptc)_.+')
+RE_PYEXIV2_TAG_EDITABLE = re.compile('^(Exif|Iptc)_\w+$')
+
+ORIENTATION_TAGS = ['orientation', 'Pexif_Orientation', 'Zexif_Orientation']
+WRITABLE_TAGS = ['dpi', 'transparency'] + ORIENTATION_TAGS
+
+
+def is_editable_tag(tag):
+    if RE_PYEXIV2_TAG_EDITABLE.match(tag):
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/odict.py

@@ -1,0 +1,109 @@
+# -*- coding: utf-8 -*-
+
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Follows PEP8
+
+
+class odict(dict):
+    """This one uses generators in places where it can, and plays nicely
+    with deepcopy."""
+
+    def __init__(self, d=None):
+        if d is None:
+            d = {}
+        self._keys = d.keys()
+        dict.__init__(self, d)
+
+    def __delitem__(self, key):
+        dict.__delitem__(self, key)
+        self._keys.remove(key)
+
+    def __setitem__(self, key, item):
+        dict.__setitem__(self, key, item)
+        # a peculiar sharp edge from copy.deepcopy
+        # we'll have our set item called without __init__
+        if not hasattr(self, '_keys'):
+            self._keys = [key, ]
+        if key not in self._keys:
+            self._keys.append(key)
+
+    def clear(self):
+        dict.clear(self)
+        self._keys = []
+
+    def items(self):
+        for i in self._keys:
+            yield i, self[i]
+
+    def keys(self):
+        return self._keys
+
+    def popitem(self):
+        if len(self._keys) == 0:
+            raise KeyError('dictionary is empty')
+        else:
+            key = self._keys[-1]
+            val = self[key]
+            del self[key]
+            return key, val
+
+    def setdefault(self, key, failobj=None):
+        dict.setdefault(self, key, failobj)
+        if key not in self._keys:
+            self._keys.append(key)
+
+    def update(self, d):
+        for key in d.keys():
+            if key not in self:
+                self._keys.append(key)
+        dict.update(self, d)
+
+    def values(self):
+        for i in self._keys:
+            yield self[i]
+
+    def move(self, key, index):
+
+        """ Move the specified to key to *before* the specified index. """
+
+        try:
+            cur = self._keys.index(key)
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/pyWx/__init__.py

@@ -1,0 +1,16 @@
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Follow PEP8

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/pyWx/about.py

@@ -1,0 +1,261 @@
+# -*- coding: UTF-8 -*-
+
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# generated by wxGlade 0.4.1cvs on Thu Jun  7 21:24:31 2007 from /home/stani/sync/python/convert/trunk/about.wxg
+
+# auto generated so no pep 8
+
+import sys
+import wx
+import wx.lib.hyperlink as hl
+
+if sys.platform.startswith('win'):
+    class TransparentBitmap(wx.Panel):
+        def __init__(self,parent,id,bitmap=wx.NullBitmap,*args,**keyw):
+            super(TransparentBitmap,self).__init__(parent,id,*args,**keyw)
+            self.SetBitmap(bitmap)
+            self.Bind(wx.EVT_PAINT, self.OnPaint)
+
+        def SetBitmap(self,bitmap):
+            self._bitmap    = bitmap
+            size            = self._bitmap.GetSize()
+            self.SetSize(size)
+            self.SetMinSize(size)
+            self.GetParent().Layout()
+
+        def OnPaint(self, evt):
+            dc = wx.PaintDC(self)
+            dc.SetBackground(wx.Brush(
+                self.GetParent().GetBackgroundColour()))
+            dc.Clear()
+            dc.DrawBitmap(self._bitmap, 0,0, True)
+else:
+    TransparentBitmap   = wx.StaticBitmap
+
+class wxgAboutDialog(wx.Dialog):
+    def __init__(self, *args, **kwds):
+        # begin wxGlade: wxgAboutDialog.__init__
+        kwds["style"] = wx.DEFAULT_DIALOG_STYLE
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/pyWx/autoCompleteCtrls.py

@@ -1,0 +1,255 @@
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Follows PEP8
+
+import locale
+import sys
+import wx
+import graphics
+from other.pyWx.TextCtrlAutoComplete import TextCtrlAutoComplete
+
+if hasattr(wx, "PopupWindow"):
+
+    class AutoCompleteTextCtrl(TextCtrlAutoComplete):
+        def __init__(self, parent, id, value, style, choices):
+            #ignore style
+            TextCtrlAutoComplete.__init__(self, parent, choices=choices)
+            self.initialize(value, choices)
+
+        def initialize(self, value, choices):
+            self.all_choices = choices
+            self.SetValue(value)
+            self.SetEntryCallback(self.setDynamicChoices)
+            self.SetMatchFunction(self.match)
+            self.setDynamicChoices()
+            wx.CallAfter(self._showDropDown)
+
+        def match(self, text, choice):
+            '''
+            Demonstrate "smart" matching feature,
+            by ignoring http:// and www. when doing matches.
+            '''
+            t = text.strip().lower()
+            c = choice.lower()
+            if c.startswith(t):
+                return True
+            if c.startswith(r'http://'):
+                c = c[7:]
+            if c.startswith(t):
+                return True
+            if c.startswith('www.'):
+                c = c[4:]
+            return c.startswith(t)
+
+        def setDynamicChoices(self):
+            text = self.GetValue().lower()
+            current_choices = self.GetChoices()
+            choices = [choice for choice in self.all_choices
+                if self.match(text, choice)]
+            if choices != current_choices:
+                self.SetChoices(choices)
+
+        def _showDropDown(self, state=True):
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/pyWx/clipboard.py

@@ -1,0 +1,48 @@
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Follows PEP8
+
+import wx
+
+
+def copy_text(text):
+    """Copies text to the clipboard.
+
+    :param text: text to copy
+    :type text: string
+    :returns: if the operation was succesfull
+    :rtype: bool
+    """
+    if wx.TheClipboard.Open():
+        text_data = wx.TextDataObject(text)
+        wx.TheClipboard.SetData(text_data)
+        wx.TheClipboard.Close()
+        return True
+    return False
+
+
+def get_text():
+    """Gets text from the clipboard.
+
+    :returns: text from the clipboard or an empty string
+    :rtype: string
+    """
+    if wx.TheClipboard.Open():
+        text_data = wx.TextDataObject()
+        wx.TheClipboard.GetData(text_data)
+        wx.TheClipboard.Close()
+        return text_data.GetText()
+    return ''

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/pyWx/dialogsInspector.py

@@ -1,0 +1,83 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+# generated by wxGlade 0.6.3 on Sun Jun 28 16:06:30 2009
+# NO PEP 8
+
+import wx
+
+# begin wxGlade: extracode
+# end wxGlade
+
+class AddTagDialog(wx.Dialog):
+    def __init__(self, *args, **kwds):
+        # begin wxGlade: AddTagDialog.__init__
+        kwds["style"] = wx.DEFAULT_DIALOG_STYLE
+        wx.Dialog.__init__(self, *args, **kwds)
+        self.tag_label = wx.StaticText(self, -1, _("Tag"))
+        self.tag = wx.ComboBox(self, -1, choices=[_("Exif_Photo_UserComment")], style=wx.CB_DROPDOWN | wx.CB_DROPDOWN | wx.CB_SORT)
+        self.value_label = wx.StaticText(self, -1, _("Value"))
+        self.value = wx.TextCtrl(self, -1, "")
+        self.warning = wx.StaticText(self, -1, _("warning"))
+        self.panel_2 = wx.Panel(self, -1)
+        self.cancel = wx.Button(self, wx.ID_CANCEL, "")
+        self.add = wx.Button(self, wx.ID_ADD, "")
+
+        self.__set_properties()
+        self.__do_layout()
+
+        self.Bind(wx.EVT_TEXT, self.OnTagText, self.tag)
+        self.Bind(wx.EVT_BUTTON, self.OnAdd, self.add)
+        # end wxGlade
+
+    def __set_properties(self):
+        # begin wxGlade: AddTagDialog.__set_properties
+        self.SetTitle(_("Add Tag"))
+        self.tag.SetMinSize((300,-1))
+        self.tag.SetSelection(0)
+        self.value.SetMinSize((100,-1))
+        self.warning.Enable(False)
+        self.add.SetDefault()
+        # end wxGlade
+
+    def __do_layout(self):
+        # begin wxGlade: AddTagDialog.__do_layout
+        sizer_14 = wx.BoxSizer(wx.VERTICAL)
+        sizer_16 = wx.BoxSizer(wx.HORIZONTAL)
+        grid_sizer_1 = wx.FlexGridSizer(2, 2, 4, 4)
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/pyWx/droplet.py

@@ -1,0 +1,150 @@
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Follows PEP8
+
+#standard modules
+import types
+
+#gui-dependent
+import wx
+
+
+def fix_paths(paths):
+    if isinstance(paths, (types.ListType, types.TupleType)) \
+        and len(paths) == 1:
+        paths = paths[0]
+    if isinstance(paths, types.StringTypes):
+        paths = paths.strip().split('\n')
+    for index, path in enumerate(paths):
+        if path.startswith('file://'):
+            paths[index] = path[7:]
+    return paths
+
+
+class FileDropTarget(wx.FileDropTarget):
+    def __init__(self, method):
+        super(FileDropTarget, self).__init__()
+        self.method = method
+
+    def OnDropFiles(self, x, y, filenames):
+        self.method(fix_paths(filenames), x, y)
+
+
+class Mixin:
+    def SetAsFileDropTarget(self, object, method):
+        dt = FileDropTarget(method)
+        object.SetDropTarget(dt)
+
+
+class Frame(Mixin, wx.Frame):
+    def __init__(self, parent, title, bitmap, method=None, label='',
+            label_color=wx.BLACK, label_angle=0, label_pos=(0, 0), auto=False,
+            pos=(0, 0), OnShow=None, splash=False, tooltip=''):
+        wx.Frame.__init__(self, parent, -1, title,
+            pos=pos,
+            style=wx.FRAME_SHAPED | wx.SIMPLE_BORDER | wx.FRAME_NO_TASKBAR \
+                | wx.STAY_ON_TOP)
+
+        self.label = label
+        self.label_color = label_color
+        self.label_x, self.label_y = label_pos
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/pyWx/imageFileBrowser.py

@@ -1,0 +1,196 @@
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Follows PEP8
+
+import os
+import sys
+
+import wx
+
+if __name__ == '__main__':
+    _ = unicode
+    sys.path.insert(0, '..')
+    sys.path.insert(0, '../..')
+
+from lib.openImage import open_thumb
+from lib.formField import IMAGE_READ_EXTENSIONS
+
+import popup
+from wxPil import pil_wxBitmap
+
+ICON_SIZE = (64, 64)
+
+
+def truncate(content, length=100, suffix='...'):
+    if len(content) <= length:
+        return content
+    else:
+        return content[:length].rsplit(' ', 1)[0] + suffix
+
+
+class ListCtrl(wx.ListCtrl):
+    def __init__(self, parent, files, icon_size=ICON_SIZE,
+            checkboard=False, **keyw):
+        super(ListCtrl, self).__init__(parent, -1,
+            style=wx.LC_ICON | wx.LC_SINGLE_SEL, **keyw)
+        #create image list
+        self.image_list = wx.ImageList(*icon_size)
+        self.icons = {}
+        for file in files.values():
+            self.icons[file] = self.image_list.Add(
+                pil_wxBitmap(open_thumb(file, size=icon_size)))
+        self.SetImageList(self.image_list, wx.IMAGE_LIST_NORMAL)
+        #populate
+        n = 10
+        if type(files) is dict:
+            labels_files = files.items()
+            #labels_files = [(truncate(label,n),file)
+             #   for label, file in files.items()]
+        labels_files.sort()
+        self._labels = [label for label, file in labels_files]
+        self._files = [file for label, file in labels_files]
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/pyWx/imageInspector.py

@@ -1,0 +1,972 @@
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Follows PEP8
+
+if __name__ == '__main__':
+    #add phatch to sys.path
+    import sys
+    sys.path.insert(0, '..')
+    import gettext
+    gettext.install('test')
+
+#---modules
+import cStringIO
+import os
+import zlib
+
+import wx
+import wx.grid as gridlib
+
+import  wx.lib.newevent
+UpdateEvent, UPDATE_EVENT = wx.lib.newevent.NewEvent()
+
+from lib import imageTable
+from lib import formField
+from lib import metadata
+from lib import system
+
+import clipboard
+import droplet
+import graphics
+import tag
+import wildcard
+import wxPil
+import dialogsInspector
+
+try:
+    import pyexiv2
+except ImportError:
+    pyexiv2 = None
+
+#---constants
+ALL = _('All')
+ALTERNATE_COLORS = (wx.Colour(254, 255, 255), wx.Colour(250, 250, 250))
+COL_WIDTH = 140
+CONFIRM_DELETE_TAG = \
+    _('Are you sure you want to delete this tag from "%s"?')
+CONFIRM_DELETE_TAG_ALL = \
+    _('Are you sure you want to delete this tag from all images?')
+FILENAME = '/home/stani/sync/Afbeeldingen/ubuntu_dog_1600x1200_3d.png'
+#FILENAME = ''
+GRAY = wx.Colour(112, 112, 112)
+RED = wx.Colour(255, 230, 230)
+SELECT = _('Select')
+SIZE = (450, 510)
+THUMB_SIZE = (128, 128)
+TAGS = [SELECT, ALL, 'Pil']
+if pyexiv2:
+    TAGS.extend(['Exif', 'Iptc'])
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/pyWx/inspectorTag.py

@@ -1,0 +1,152 @@
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Follow PEP8
+
+
+import wx
+import inspector
+from tag import Browser, ContentMixin, extract_tags
+
+TEST_DATA = {
+    'decimal':   [[str((row, col)) for col in range(inspector.NUMBER_COLS)]
+                        for row in range(100)],
+    'hexadecimal':  [[str((hex(row), hex(col))) for col in \
+                                    range(inspector.NUMBER_COLS)]
+                        for row in range(100)],
+}
+
+
+class Grid(ContentMixin, inspector.Grid):
+    def SetData(self, data, tag):
+        self.all_data = data
+        self.SetTag(tag)
+
+    def IsEmpty(self):
+        return not self.data
+
+
+class TestContentGrid(Grid):
+    def SetTag(self, tag, filter=None):
+        self.tag_data = self.all_data[tag]
+        self.SetFilter()
+
+    def SetFilter(self, filter=None):
+        if filter is None:
+            filter = self.GetFilter().GetValue()
+        if filter.strip():
+            self.data = [row for row in self.tag_data
+                            if filter in unicode(row)]
+        else:
+            self.data = self.tag_data
+        if not self.CheckEmpty():
+            self.RefreshAll()
+
+    def SetData(self, data):
+        self.all_data = data
+        self.SetTag(_('decimal'))
+
+
+class TestBrowser(Browser):
+    ContentCtrl = TestContentGrid
+
+    paint_message = "nothing found"
+
+    def _init(self):
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/pyWx/paint.py

@@ -1,0 +1,129 @@
+# -*- coding: UTF-8 -*-
+
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Follow PEP8
+
+import wx
+from compatible import GCDC, FONT_SIZE
+import graphics
+MARGIN = 2 * 10
+
+
+class Mixin:
+    paint_message = ''
+    paint_logo = None
+    paint_color = wx.Colour(60, 60, 60)  # ,200)
+    paint_border_color = None
+    paint_opacity = 200
+    paint_radius = 8
+
+    def OnEraseBackground(self, event=None, paint_object=None):
+        paint_object = event.GetEventObject()
+        if not paint_object.IsShown():
+            return
+        _dc = event.GetDC()
+        if not _dc:
+            _dc = wx.ClientDC(paint_object)
+            rect = paint_object.GetUpdateRegion().GetBox()
+            _dc.SetClippingRect(rect)
+        dc = GCDC(_dc)
+        dc.Clear()
+        # Calculate text extents.
+        paint_message = self.GetPaintMessage()
+        if paint_message:
+            tw, th = self.GetClientSize()
+            cw, ch = tw - MARGIN, th - MARGIN
+            font_size = FONT_SIZE + 1
+            while (tw >= cw or th >= ch) and font_size > 5:
+                font_size -= 1
+                font = wx.Font(font_size, wx.FONTFAMILY_SWISS,
+                                wx.FONTSTYLE_NORMAL, wx.FONTSTYLE_NORMAL,
+                                encoding=wx.FONTENCODING_SYSTEM)
+                dc.SetFont(font)
+                tw, th = dc.GetTextExtent(paint_message)
+            td = font_size / 2
+            twd = tw + 2 * td
+            thd = th + 2 * td
+        else:
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/pyWx/shell.py

@@ -1,0 +1,61 @@
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Follow PEP8
+
+try:
+    _
+except NameError:
+    _ = unicode
+
+import time
+
+import __main__
+
+import wx
+import wx.py
+
+TRANSLATE = _
+
+
+class Frame(wx.Frame):
+    def __init__(self, parent, title='Shell', intro='', values={}, icon=None,
+            **kw):
+        wx.Frame.__init__(self, parent, -1, title=title, **kw)
+        self.shell = wx.py.crust.Crust(self, -1, intro=intro)
+        pp = self.shell.shell.interp.locals['pp']
+        self.shell.shell.interp.locals.clear()
+        self.shell.shell.interp.locals.update(values)
+        self.shell.shell.interp.locals['pp'] = pp
+        if icon:
+            self.SetIcon(icon)
+        self.Bind(wx.EVT_CLOSE, self.on_close, self)
+
+        shell = self.shell.shell
+        shell.Unbind(wx.EVT_IDLE)
+        shell.Bind(wx.EVT_IDLE, self.OnIdle)
+
+    def OnIdle(self, event):
+        """Free the CPU to do other things."""
+        __main__._ = TRANSLATE
+        event.Skip()
+        if self.shell.shell.waiting:
+            time.sleep(0.05)
+
+    def on_close(self, event):
+        parent = self.GetParent()
+        parent.menu_tools.Check(parent.menu_tools_python_shell.GetId(), False)
+        parent.shell = None
+        event.Skip()

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/pyWx/treeEdit.py

@@ -1,0 +1,702 @@
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Follow PEP8
+
+# ---import modules
+
+# gui-indepedent
+if __name__ == '__main__':
+    import sys
+    sys.path.insert(0, '..')
+
+from lib import formField
+from lib import metadata
+
+# gui-dependent
+import wx
+import graphics
+import popup
+import treeDragDrop
+
+if __name__ == '__main__':
+    sys.path.insert(0, '../..')
+
+from lib.unicoding import exception_to_unicode
+
+FIELD_DELIMITER = ': '
+WX_ENCODING = wx.GetDefaultPyEncoding()
+IMAGE_TEST_INFO = metadata.InfoTest()
+
+# ---functions
+
+# ---tree
+ITEM_HEIGHT = 28
+ICON_SIZE = (ITEM_HEIGHT, ITEM_HEIGHT)
+TR_DEFAULT_STYLE = wx.TR_HAS_BUTTONS | wx.TR_NO_LINES | \
+            wx.TR_FULL_ROW_HIGHLIGHT | wx.TR_HIDE_ROOT | \
+            wx.TR_DEFAULT_STYLE | wx.SUNKEN_BORDER
+
+
+def _do_nothing(*args, **keyw):
+    pass
+
+
+def rescale(image, x, y, filter=None):
+    """For compatibility with wxPython 2.6"""
+    if filter is None and hasattr(wx, 'IMAGE_QUALITY_HIGH'):
+        filter = wx.IMAGE_QUALITY_HIGH
+    if filter is None:
+        image.Rescale(x, y)
+    else:
+        image.Rescale(x, y, filter)
+
+
+def get_index(li, index, n=3):
+    try:
+        return li[index]
+    except IndexError:
+        return (None, ) * n
+
+
+class TreeMixin(treeDragDrop.Mixin):
+    """
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/pyWx/vlist.py

@@ -1,0 +1,190 @@
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Follow PEP8
+
+import wx
+
+ICON_SIZE = (48, 48)
+
+# ---vlist
+
+
+class Box(wx.VListBox):
+    """Default Icon Size is ICON_SIZE (48)."""
+    def __init__(self, parent, *args, **kwds):
+        super(Box, self).__init__(parent, *args, **kwds)
+        self.SetIconSize(ICON_SIZE)
+        self.SetVerticalGradient()
+        if wx.Platform == '__WXGTK__':
+            self.SetTheme('default')
+        else:
+            self.SetTheme('light_blue')
+        self._events()
+        wx.CallAfter(self.SetSelection, 0)
+
+    def _events(self):
+        """Can be overwritten."""
+        pass
+
+    def GradientColour(self, color):
+        rgb = r, g, b = color.Red(), color.Green(), color.Blue()  # wx2.6
+        m = max(rgb)
+        rgb_without_max = [x for x in rgb if x != m]
+        if not rgb_without_max:
+            return wx.Colour(128, 128, 128)
+        n = max(rgb_without_max)
+        keyw = {}
+        for c in ('Red', 'Green', 'Blue'):
+            x = getattr(color, c)()
+            if x == m:
+                keyw[c.lower()] = x
+            elif x == n:
+                keyw[c.lower()] = x / 2
+            else:
+                keyw[c.lower()] = x / 8
+        return wx.Colour(**keyw)
+
+    def SetTheme(self, theme='default'):
+        self._theme = theme
+        if theme == 'light_blue':
+            # mozilla like
+            self._color_from = wx.Colour(180, 197, 214)
+            self._color_to = wx.Colour(217, 226, 234)
+        else:
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/pyWx/vlistTag.py

@@ -1,0 +1,125 @@
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Follows PEP8
+
+"""Wraps vlist in a tag browser jacket."""
+
+import wx
+from vlist import Box
+from tag import Browser, ContentMixin, extract_tags  # imported by dialogs.py
+
+
+#---Test case
+class TestContentBox(ContentMixin, Box):
+    def SetTag(self, tag):
+        self.SetVerticalGradient(tag == 'vertical')
+        self.Refresh()
+
+    def SetFilter(self, filter):
+        try:
+            n = int(filter)
+        except ValueError:
+            n = 0
+        self.SetItemCount(n)
+        if not self.CheckEmpty():
+            self.RefreshAll()
+
+    def IsEmpty(self):
+        return not self.GetItemCount()
+
+
+class TestBrowser(Browser):
+    ContentCtrl = TestContentBox
+
+    paint_message = "type a number"
+
+    def _init(self):
+        """Normally overwrite this."""
+        self.CheckEmpty()
+
+
+class TestFrame(wx.Frame):
+    def __init__(self, parent):
+        wx.Frame.__init__(self, parent, -1, "Test Tag Browser",
+            size=(640, 480))
+        browser = TestBrowser(self, ['vertical', 'horizontal'], {})
+        browser.EnableResize()
+
+
+class Dialog(wx.Dialog):
+    ContentBrowser = TestBrowser
+
+    def __init__(self, parent, tags, *args, **kwds):
+        kwds["style"] = wx.DEFAULT_DIALOG_STYLE | wx.RESIZE_BORDER
+        super(Dialog, self).__init__(parent, *args, **kwds)
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/pyWx/wildcard.py

@@ -1,0 +1,32 @@
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Follow PEP8
+import sys
+
+
+def wildcard_list(name, extensions):
+    return '%s|%s' % (name,
+        ';'.join([_wildcard_extension(ext) for ext in extensions]))
+
+if sys.platform.startswith('win'):
+    #Windows is case insensitive
+
+    def _wildcard_extension(ext):
+        return '*.%s' % (ext, )
+else:
+
+    def _wildcard_extension(ext):
+        return '*.%s;*.%s;*.%s' % (ext, ext.upper(), ext.capitalize())

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/pyWx/wxcheck.py

@@ -1,0 +1,84 @@
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Follow PEP8
+
+import os
+import sys
+from subprocess import call
+from lib.unicoding import ENCODING
+
+
+def _t(x):
+    return _(x).encode(ENCODING, 'replace')
+
+
+def ensure(recommended, minimal):
+    """Ensures the minimal version of wxPython is installed.
+    - minimal: as string (eg. '2.6')"""
+
+    #wxversion
+    try:
+        import wxversion
+        if wxversion.checkInstalled(recommended):
+            wxversion.select(recommended)
+        else:
+            wxversion.ensureMinimal(minimal)
+        import wx
+        return wx
+    except ImportError:
+        sys.stdout.write(_t('Warning: python-wxversion is not installed.\n'))
+
+    #wxversion failed, import wx anyway
+    params = {'recommended': recommended, 'minimal': minimal}
+    try:
+        import wx
+    except ImportError:
+        message = _t('Error: wxPython %(recommended)s' \
+                                ' (or at least %(minimal)s) can not' \
+                                ' be found, but is required.'
+                            ) % params +\
+            '\n\n' + _t('Please (re)install it.')
+        sys.stderr.write(message)
+        if sys.platform.startswith('linux') and \
+                os.path.exists('/usr/bin/zenity'):
+            call('''zenity --error --text="%s"\n\n''' % message + \
+                _t("This application needs 'python-wxversion' " \
+                    "and 'python-wxgtk%(recommended)s' " \
+                    "(or at least 'python-wxgtk%(minimal)s')."
+                    ) % params, shell=True)
+        sys.exit()
+
+    #wxversion failed but wx is available, check version again
+    params['version'] = wx.VERSION_STRING
+    if wx.VERSION_STRING < minimal:
+
+        class MyApp(wx.App):
+            def OnInit(self):
+                result = wx.MessageBox(
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/reverse_translation.py

@@ -1,0 +1,32 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+
+# Follows PEP8
+
+import gettextFix  # otherwise doctests will fail unfortunately
+
+REVERSE = {}
+
+
+def _t(phrase):
+    REVERSE[_(phrase)] = phrase
+    return phrase
+
+
+def _r(phrase):
+    return REVERSE.get(phrase, phrase)

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/safe.py

@@ -1,0 +1,219 @@
+# Copyright (C) 2009 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Follows PEP8
+
+#import rpdb2;rpdb2.start_embedded_debugger('x')
+
+import operator
+import re
+
+SAFE = {
+    'int': ['abs', 'int', 'min', 'max', 'pow', 'sum'],
+    'str': ['chr', 'lower', 'str', 'title', 'upper'],
+    'bool': ['True', 'False'],
+    'datetime': ['day', 'hour', 'microsecond', 'minute', 'month',
+        'monthname', 'second', 'weekday', 'weekdayname', 'year'],
+    'rational': ['denominator', 'numerator'],
+}
+SAFE['all'] = reduce(operator.add, SAFE.values())
+
+
+"""Todo: alleen format ### moet vervangen worden, daarna gewoon
+eval met locals (incl indices) en globals.
+
+<x>_<y> wordt '%s_%s'(eval(x),eval(y)) '"""
+
+RE_EXPR = re.compile('<([^<>]+?)>', re.UNICODE)
+RE_FORMAT = re.compile('#+')
+RE_VAR = re.compile('(?P<var>[A-Za-z]\w*)(?P<attr>([.]\w(\w|[.])+)?)',
+    re.UNICODE)
+
+
+class UnsafeError(Exception):
+    pass
+
+
+def _format_int(match):
+    """Converts a ``####`` string into a formating string.
+
+    Helper function for :func:`format_expr`.
+
+    :param match: match for a ``##``-string
+    :type match: regular expression match
+    :returns: interpolation format
+    :rtype: string
+
+    >>> f = _format_int(RE_FORMAT.search('####'))
+    >>> f
+    '"%04d"%'
+    >>> eval(f + '5')
+    '0005'
+    """
+    return '"%%0%dd"%%' % len(match.group(0))
+
+
+def format_expr(s):
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/thumbnail.py

@@ -1,0 +1,433 @@
+# Copyright (C) 2009 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Follows PEP8
+
+"""The most important functions of this module are
+``open`` and ``save_to_cache``.
+
+For the freedesktop specifications, it follows:
+http://jens.triq.net/thumbnail-spec/index.html
+"""
+
+import hashlib
+import os
+import stat
+import tempfile
+import urllib
+
+import Image
+
+import imtools
+import system
+
+
+def ensure_path(*paths):
+    path = os.path.join(*paths)
+    if not os.path.exists(path):
+        os.mkdir(path)
+    return path
+
+CHECKBOARD = {}
+FREEDESKTOP = True  # os.path.exists(FREEDESKTOP_PATH)
+THUMB_INFO = {'software': 'Phatch'}
+
+
+def get_mtime(filename, file_stat=None):
+    if file_stat is None:
+        file_stat = os.stat(filename)
+    return file_stat[stat.ST_MTIME]
+
+
+def get_filesize(filename, file_stat=None):
+    if file_stat is None:
+        file_stat = os.stat(filename)
+    return file_stat[stat.ST_SIZE]
+
+
+if FREEDESKTOP:
+
+    import PngImagePlugin
+
+    FREEDESKTOP_SIZE = {
+        'normal': (128, 128),
+        'large': (256, 256)}
+    SIZE = FREEDESKTOP_SIZE['normal']
+
+    FREEDESKTOP_PATH = {
+        'normal': os.path.expanduser('~/.thumbnails/normal'),
+        'large': os.path.expanduser('~/.thumbnails/large')}
+    if os.path.exists(FREEDESKTOP_PATH['normal']):
+        ensure_path(FREEDESKTOP_PATH['large'])
+    else:
+        #simulate freedesktop with a temp dir
+        thumb_path = ensure_path(tempfile.gettempdir(), 'thumbnails')
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/unicoding.py

@@ -1,0 +1,71 @@
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Follows PEP8
+
+import codecs
+import locale
+import system
+
+ENCODING = locale.getdefaultlocale()[1]
+
+try:
+    codecs.lookup(ENCODING)
+except:
+    ENCODING = locale.getpreferredencoding()
+    try:
+        codecs.lookup(ENCODING)
+    except:
+        ENCODING = 'utf-8'
+
+
+def ensure_unicode(x, encoding=ENCODING, errors='replace'):
+    if type(x) is unicode:
+        return x
+    try:
+        return unicode(x)
+    except UnicodeDecodeError:
+        return unicode(x, encoding, errors)
+
+
+def exception_to_unicode(x, encoding=ENCODING, errors='replace'):
+##    #python2.5
+##    if hasattr(x, 'message'):
+##        return ensure_unicode(x.message, encoding, errors)
+    #python2.4
+    try:
+        return ensure_unicode(x, encoding, errors)
+    except:
+        try:
+            return ensure_unicode(str(x), encoding, errors)
+        except:
+            return u'?'
+
+
+def fix_filename(f, encoding=None):
+    if system.is_file(f):
+        return f
+    if type(f) is unicode:
+        encodings = ['latin1', 'utf-8', ENCODING]
+        if encoding:
+            encodings = [encoding] + encodings
+        for encoding in encodings:
+            try:
+                f = f.encode(encoding)
+                if system.is_file(f):
+                    return f
+            except UnicodeEncodeError:
+                pass
+    return None

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/windows/__init__.py

@@ -1,0 +1,16 @@
+# Copyright (C) 2007-2008  www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Follows PEP8

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/windows/locate.py

@@ -1,0 +1,72 @@
+# Copyright (C) 2007-2008  www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+
+# Follows PEP8
+
+try:
+    import _winreg
+except ImportError:
+    _winreg = None
+
+
+class RegistryApplication:
+    name = ''
+    filename = ''
+
+    def get_path(self, reg):
+        pass
+
+
+class Blender(RegistryApplication):
+    name = 'blender'
+    filename = 'blendfile'
+
+    def get_path(self, reg):
+        return _winreg.QueryValue(reg, 'DefaultIcon').rsplit(',', 1)[0]
+
+
+class Inkscape(RegistryApplication):
+    name = 'inkscape'
+    filename = 'svgfile\\shell\edit'
+
+    def get_path(self, reg):
+        return _winreg.QueryValue(reg, 'command').rsplit(' ', 1)[0].strip('"')
+
+
+class Applications(dict):
+
+    def __init__(self):
+        apps = (Blender(), Inkscape())
+
+        for app in apps:
+            self[app.name] = app
+
+
+apps = Applications()
+
+
+def find_exe(app_name):
+    if app_name in apps:
+        app = apps[app_name]
+
+        try:
+            reg = _winreg.OpenKey(_winreg.HKEY_CLASSES_ROOT, app.filename)
+            value = app.get_path(reg)
+            _winreg.CloseKey(reg)
+
+            return value
+        except:
+            pass
+    return None

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/windows/register.py

@@ -1,0 +1,130 @@
+# Copyright (C) 2007-2008  www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Follows PEP8
+
+
+import os
+import sys
+import _winreg
+
+PYTHONW = os.path.join(sys.prefix, 'pythonw.exe')
+PY = 'Python.File'
+PYW = 'Python.NoConFile'
+
+
+def fix_label(x):
+    return x.title().replace(' ', '').encode('ascii', 'ignore')
+
+
+def getFiletype(extension):
+    return _winreg.QueryValue(_winreg.HKEY_CLASSES_ROOT, extension)
+
+#---register
+
+
+def register(label, action, filetype='Python.File', suffix='"%1"'):
+    try:
+        k = '%s\\shell\\%s' % (filetype, label)
+        key = _winreg.CreateKey(_winreg.HKEY_CLASSES_ROOT, k)
+    except:
+        pass
+    try:
+        command = '%s %s' % (action, suffix)
+        _winreg.SetValue(key, "command", _winreg.REG_SZ, command)
+        return key
+    except:
+        return False
+
+
+def register_extension(label, action, extension, suffix='"%1"'):
+    "Registering action for extension in windows explorer context menu."
+    try:
+        filetype = getFiletype(extension)
+    except:
+        return False
+    return register(
+        label=label,
+        action='"%s" %s' % (PYTHONW, action),
+        filetype=filetype,
+        suffix=suffix,
+    )
+
+
+def register_extensions(label, action, extensions, folder=False,
+        suffix='"%1"'):
+    "Registering action for extensions in windows explorer context menu."
+    result = []
+    if folder:
+        if register(label, action, 'Folder', suffix):
+            result.append('folder')
+    for extension in extensions:
+        if register_extension(label, action, extension, suffix):
+            result.append(extension)
+    return result
+
+
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/lib/windows/shortcut.py

@@ -1,0 +1,36 @@
+# Copyright (C) 2007-2008  www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Follows PEP8
+
+import win32com.client
+
+
+def create(save_as, path, arguments="", working_dir="",
+        description="", icon_path=None, icon_index=0):
+    # initialize shortcut
+    shell = win32com.client.Dispatch("WScript.Shell")
+    shortcut = shell.CreateShortCut(save_as)
+
+    # set shortcut parameters
+    shortcut.Targetpath = path
+    shortcut.Arguments = arguments
+    shortcut.WorkingDirectory = working_dir
+    shortcut.Description = description
+    if icon_path:
+        shortcut.IconLocation = icon_path
+
+    # save shortcut
+    shortcut.save()

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/linux/__init__.py

@@ -1,0 +1,19 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+#
+# Follows PEP8

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/other/findsystem.py

@@ -1,0 +1,174 @@
+##THIS SOFTWARE IS NOT FAULT TOLERANT AND SHOULD NOT BE USED IN ANY
+##SITUATION ENDANGERING HUMAN LIFE OR PROPERTY.
+##
+##TTFQuery License
+##
+##	Copyright (c) 2003, Michael C. Fletcher and Contributors
+##	All rights reserved.
+##	
+##	Redistribution and use in source and binary forms, with or without
+##	modification, are permitted provided that the following conditions
+##	are met:
+##	
+##		Redistributions of source code must retain the above copyright
+##		notice, this list of conditions and the following disclaimer.
+##	
+##		Redistributions in binary form must reproduce the above
+##		copyright notice, this list of conditions and the following
+##		disclaimer in the documentation and/or other materials
+##		provided with the distribution.
+##	
+##		The name of Michael C. Fletcher, or the name of any Contributor,
+##		may not be used to endorse or promote products derived from this 
+##		software without specific prior written permission.
+##	
+##	THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
+##	``AS IS'' AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
+##	LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS
+##	FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE
+##	COPYRIGHT HOLDERS AND CONTRIBUTORS BE LIABLE FOR ANY DIRECT,
+##	INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+##	(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
+##	SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
+##	HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT,
+##	STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE)
+##	ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED
+##	OF THE POSSIBILITY OF SUCH DAMAGE. 
+
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/other/pil_1_1_6/JpegImagePlugin.py

@@ -1,0 +1,473 @@
+# This file has been patched to be included with Phatch to fix the handling of
+# CMYK jpg images. It is based on the patch proposed by Kevin Cazabon on the 
+# python image sig mailing list:
+# http://www.mail-archive.com/image-sig@python.org/msg00800.html
+
+# The Python Imaging Library (PIL) is
+#
+#    Copyright (c) 1997-2006 by Secret Labs AB
+#    Copyright (c) 1995-2006 by Fredrik Lundh
+#
+# By obtaining, using, and/or copying this software and/or its associated 
+# documentation, you agree that you have read, understood, and will comply with
+# the following terms and conditions:
+# 
+# Permission to use, copy, modify, and distribute this software and its 
+# associated documentation for any purpose and without fee is hereby granted, 
+# provided that the above copyright notice appears in all copies, and that both
+# that copyright notice and this permission notice appear in supporting 
+# documentation, and that the name of Secret Labs AB or the author not be used
+# in advertising or publicity pertaining to distribution of the software
+# without specific, written prior permission.
+# 
+# SECRET LABS AB AND THE AUTHOR DISCLAIMS ALL WARRANTIES WITH REGARD TO THIS 
+# SOFTWARE, INCLUDING ALL IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS. 
+# IN NO EVENT SHALL SECRET LABS AB OR THE AUTHOR BE LIABLE FOR ANY SPECIAL, 
+# INDIRECT OR CONSEQUENTIAL DAMAGES OR ANY DAMAGES WHATSOEVER RESULTING FROM 
+# LOSS OF USE, DATA OR PROFITS, WHETHER IN AN ACTION OF CONTRACT, NEGLIGENCE 
+# OR OTHER TORTIOUS ACTION, ARISING OUT OF OR IN CONNECTION WITH THE USE OR 
+# PERFORMANCE OF THIS SOFTWARE.
+# 
+# http://www.pythonware.com/products/pil/license.htm
+
+# The Python Imaging Library.
+# $Id: JpegImagePlugin.py 2199 2004-12-18 08:49:05Z fredrik $
+#
+# JPEG (JFIF) file handling
+#
+# See "Digital Compression and Coding of Continous-Tone Still Images,
+# Part 1, Requirements and Guidelines" (CCITT T.81 / ISO 10918-1)
+#
+# History:
+# 1995-09-09 fl   Created
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/other/pil_1_1_6/TiffImagePlugin.py

@@ -1,0 +1,803 @@
+# Patched version to fix dpi problem, see the python image-sig mailing list:
+# http://www.mail-archive.com/image-sig@python.org/msg01572.html
+# Two patches: see line 580 & 732
+
+# The Python Imaging Library (PIL) is
+#
+#    Copyright (c) 1997-2006 by Secret Labs AB
+#    Copyright (c) 1995-2006 by Fredrik Lundh
+#
+# By obtaining, using, and/or copying this software and/or its associated 
+# documentation, you agree that you have read, understood, and will comply with
+# the following terms and conditions:
+# 
+# Permission to use, copy, modify, and distribute this software and its 
+# associated documentation for any purpose and without fee is hereby granted, 
+# provided that the above copyright notice appears in all copies, and that both
+# that copyright notice and this permission notice appear in supporting 
+# documentation, and that the name of Secret Labs AB or the author not be used
+# in advertising or publicity pertaining to distribution of the software
+# without specific, written prior permission.
+# 
+# SECRET LABS AB AND THE AUTHOR DISCLAIMS ALL WARRANTIES WITH REGARD TO THIS 
+# SOFTWARE, INCLUDING ALL IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS. 
+# IN NO EVENT SHALL SECRET LABS AB OR THE AUTHOR BE LIABLE FOR ANY SPECIAL, 
+# INDIRECT OR CONSEQUENTIAL DAMAGES OR ANY DAMAGES WHATSOEVER RESULTING FROM 
+# LOSS OF USE, DATA OR PROFITS, WHETHER IN AN ACTION OF CONTRACT, NEGLIGENCE 
+# OR OTHER TORTIOUS ACTION, ARISING OUT OF OR IN CONNECTION WITH THE USE OR 
+# PERFORMANCE OF THIS SOFTWARE.
+# 
+# http://www.pythonware.com/products/pil/license.htm
+
+# The Python Imaging Library.
+# $Id: TiffImagePlugin.py 2803 2006-07-31 19:18:57Z fredrik $
+#
+# TIFF file handling
+#
+# TIFF is a flexible, if somewhat aged, image file format originally
+# defined by Aldus.  Although TIFF supports a wide variety of pixel
+# layouts and compression methods, the name doesn't really stand for
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/other/pubsub.py

@@ -1,0 +1,1245 @@
+# Copyright: (c) 2004 Oliver Schoenborn
+# License: wxWidgets(based on LGPL,http://www.wxwidgets.org/about/newlicen.htm)
+
+#---------------------------------------------------------------------------
+"""
+This module provides a publish-subscribe component that allows
+listeners to subcribe to messages of a given topic. Contrary to the
+original wxPython.lib.pubsub module (which it is based on), it uses 
+weak referencing to the subscribers so the lifetime of subscribers 
+is not affected by Publisher. Also, callable objects can be used in 
+addition to functions and bound methods. See Publisher class docs for 
+more details. 
+
+Thanks to Robb Shecter and Robin Dunn for having provided 
+the basis for this module (which now shares most of the concepts but
+very little design or implementation with the original 
+wxPython.lib.pubsub).
+
+The publisher is a singleton instance of the PublisherClass class. You 
+access the instance via the Publisher object available from the module::
+
+    from wx.lib.pubsub import Publisher
+    Publisher().subscribe(...)
+    Publisher().sendMessage(...)
+    ...
+
+:Author:      Oliver Schoenborn
+:Since:       Apr 2004
+:Version:     $Id: pubsub.py,v 1.8 2006/06/11 00:12:59 RD Exp $
+:Copyright:   \(c) 2004 Oliver Schoenborn
+:License:     wxWidgets
+"""
+
+_implNotes = """
+Implementation notes
+--------------------
+
+In class Publisher, I represent the topics-listener set as a tree
+where each node is a topic, and contains a list of listeners of that
+topic, and a dictionary of subtopics of that topic. When the Publisher
+is told to send a message for a given topic, it traverses the tree
+down to the topic for which a message is being generated, all
+listeners on the way get sent the message.
+
+Publisher currently uses a weak listener topic tree to store the
+topics for each listener, and if a listener dies before being
+unsubscribed, the tree is notified, and the tree eliminates the
+listener from itself.
+
+Ideally, _TopicTreeNode would be a generic _TreeNode with named
+subnodes, and _TopicTreeRoot would be a generic _Tree with named
+nodes, and Publisher would store listeners in each node and a topic
+tuple would be converted to a path in the tree.  This would lead to a
+much cleaner separation of concerns. But time is over, time to move on.
+"""
+#---------------------------------------------------------------------------
+
+# for function and method parameter counting:
+from types   import InstanceType
+from inspect import getargspec, ismethod, isfunction
+# for weakly bound methods:
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/other/pyWx/TextCtrlAutoComplete.py

@@ -1,0 +1,596 @@
+# Copyright: (c) 2006 CDF Inc. ( http://www.cdf-imaging.com )
+# License: wxWidgets(based on LGPL,http://www.wxwidgets.org/about/newlicen.htm)
+# Website: http://wiki.wxpython.org/TextCtrlAutoComplete
+
+'''
+
+wxPython Custom Widget Collection 20060207
+Written By: Edward Flick (eddy -=at=- cdf-imaging -=dot=- com)
+            Michele Petrazzo (michele -=dot=- petrazzo -=at=- unipex -=dot=- it)
+            Will Sadkin (wsadkin-=at=- nameconnector -=dot=- com)
+Copyright 2006 (c) CDF Inc. ( http://www.cdf-imaging.com )
+Contributed to the wxPython project under the wxPython project's license.
+
+This was slightly adapted by Stani for Phatch:
+- disable the parent event binding
+- change styles of the popup and listctrl
+'''
+
+import locale, wx, sys, cStringIO
+
+import  wx.lib.mixins.listctrl  as  listmix
+
+from wx import ImageFromStream, BitmapFromImage
+#----------------------------------------------------------------------
+def getSmallUpArrowData():
+    return \
+'\x89PNG\r\n\x1a\n\x00\x00\x00\rIHDR\x00\x00\x00\x10\x00\x00\x00\x10\x08\x06\
+\x00\x00\x00\x1f\xf3\xffa\x00\x00\x00\x04sBIT\x08\x08\x08\x08|\x08d\x88\x00\
+\x00\x00<IDAT8\x8dcddbf\xa0\x040Q\xa4{h\x18\xf0\xff\xdf\xdf\xffd\x1b\x00\xd3\
+\x8c\xcf\x10\x9c\x06\xa0k\xc2e\x08m\xc2\x00\x97m\xd8\xc41\x0c \x14h\xe8\xf2\
+\x8c\xa3)q\x10\x18\x00\x00R\xd8#\xec\xb2\xcd\xc1Y\x00\x00\x00\x00IEND\xaeB`\
+\x82'
+
+def getSmallUpArrowBitmap():
+    return BitmapFromImage(getSmallUpArrowImage())
+
+def getSmallUpArrowImage():
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/other/pyWx/toasterbox.py

@@ -1,0 +1,804 @@
+# --------------------------------------------------------------------------- #
+# TOASTERBOX wxPython IMPLEMENTATION
+# Ported And Enhanced From wxWidgets Contribution (Aj Bommarito) By:
+#
+# Andrea Gavana, @ 16 September 2005
+# Latest Revision: 29 May 2009, 09.00 GMT
+#
+#
+# TODO/Caveats List
+#
+# 1. Any Idea?
+#
+#
+# For All Kind Of Problems, Requests Of Enhancements And Bug Reports, Please
+# Write To Me At:
+#
+# andrea.gavana@gmail.com
+# gavana@kpo.kz
+#
+# Or, Obviously, To The wxPython Mailing List!!!
+#
+#
+# End Of Comments
+# --------------------------------------------------------------------------- #
+
+
+"""
+ToasterBox is a cross-platform widget to make the creation of MSN style "toaster"
+popups easier.
+
+
+Description
+===========
+
+ToasterBox is a cross-platform widget to make the creation of MSN style "toaster"
+popups easier. The syntax is really easy especially if you are familiar with the
+syntax of wxPython.
+
+It has 2 main styles:
+
+- TB_SIMPLE: using this style, you will be able to specify a background image for
+             ToasterBox, text properties as text colour, font and label.
+
+- TB_COMPLEX: this style will allow you to put almost any control inside a
+              ToasterBox. You can add a panel in which you can put all the controls
+              you like.
+
+Both styles support the setting of ToasterBox position (on screen coordinates),
+size, the time after which the ToasterBox is destroyed (linger), and the scroll
+speed of ToasterBox.
+
+
+Supported Platforms
+===================
+
+ToasterBox has been tested on the following platforms:
+
+- Windows (verified on Windows XP, 2000)
+- Linux
+- Mac
+
+
+License And Version
+===================
+
+ToasterBox is freeware and distributed under the wxPython license.
+
+Latest revision: Andrea Gavana @ 29 May 2009, 09.00 GMT
+Version 0.2
+
+"""
+
+import textwrap
+import wx
+
+from wx.lib.statbmp import GenStaticBitmap as StaticBitmap
+
+# Define Window List, We Use It Globally
+winlist = []
+
+TB_SIMPLE = 1
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/pyWx/nuovext.py

@@ -1,0 +1,719 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008  www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Embedded icons (48x48) are from NuoveXt 1.6:
+# - Author: Alexandre Moore
+# - Author website: http://nuovext.pwsp.net/
+# - Icon website: http://www.gnome-look.org/content/show.php?content=26448
+# - Icon download: http://www.gnome-look.org/content/download.php?
+# content=26448&id=1&tan=15504822&PHPSESSID=34ec3de1af33e253ee03357a124bfbeb
+# - License: GPL
+#
+# Follow PEP8
+
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/pyWx/plugin.py

@@ -1,0 +1,39 @@
+# -*- coding: UTF-8 -*-
+#
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+#
+# Follow PEP8
+
+import wx
+from core import ct
+from core.api import import_module
+
+ID_droplet = wx.ID_FORWARD
+
+
+def install_frame(frame):
+    try:
+        # os.path.join('lib', ct.PLATFORM))
+        droplet = import_module('droplet', ct.PLATFORM)
+    except:
+        droplet = None
+    if droplet:
+        droplet.install(frame)
+    else:
+        pass

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/pyWx/wxGlade/__init__.py

@@ -1,0 +1,19 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2007-2008 www.stani.be
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+#
+# Follow PEP8

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/phatch/pyWx/wxGlade/dialogs.py

@@ -1,0 +1,376 @@
+# -*- coding: utf-8 -*-
+
+# generated by wxGlade 0.5.1cvs on Thu Jun 14 14:07:44 2007 from /home/stani/sync/python/convert/trunk/gui/wxGlade/dialogs.wxg
+
+import wx
+from lib.pyWx import folderFileBrowser as ffb
+from lib.desktop import USER_FOLDER
+
+class StatusDialog(wx.Dialog):
+    def __init__(self, *args, **kwds):
+        # begin wxGlade: StatusDialog.__init__
+        kwds["style"] = wx.DEFAULT_DIALOG_STYLE
+        wx.Dialog.__init__(self, *args, **kwds)
+        self.panel_1 = wx.Panel(self, -1)
+        self.message = wx.StaticText(self.panel_1, -1, _("Done"))
+        self.log = wx.Button(self.panel_1, -1, _("Show &Log"))
+        self.report = wx.Button(self.panel_1, -1, _("Show &Images"))
+        self.ok = wx.Button(self.panel_1, wx.ID_OK, "")
+
+        self.__set_properties()
+        self.__do_layout()
+
+        self.Bind(wx.EVT_BUTTON, self.on_button_log, self.log)
+        self.Bind(wx.EVT_BUTTON, self.on_button_report, self.report)
+        # end wxGlade
+
+    def __set_properties(self):
+        # begin wxGlade: StatusDialog.__set_properties
+        self.SetTitle(_("Ready!"))
+        # end wxGlade
+
+    def __do_layout(self):
+        # begin wxGlade: StatusDialog.__do_layout
+        sizer_18 = wx.BoxSizer(wx.HORIZONTAL)
+        sizer_19 = wx.BoxSizer(wx.VERTICAL)
+        sizer_20 = wx.BoxSizer(wx.HORIZONTAL)
+        sizer_19.Add(self.message, 1, wx.ALL|wx.EXPAND|wx.ALIGN_CENTER_HORIZONTAL|wx.ALIGN_CENTER_VERTICAL, 6)
+        sizer_20.Add(self.log, 0, wx.ALL|wx.ALIGN_CENTER_VERTICAL, 6)
+        sizer_20.Add(self.report, 0, wx.ALL|wx.ALIGN_CENTER_VERTICAL, 6)
+        sizer_20.Add(self.ok, 0, wx.ALL|wx.ALIGN_CENTER_VERTICAL, 6)
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/tests/acceptance_test.py

@@ -1,0 +1,274 @@
+#!/usr/bin/python
+
+# Phatch - Photo Batch Processor
+# Copyright (C) 2009 Nadia Alramli, Stani (www.stani.be)
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+#
+# Follows PEP8
+
+import logging
+import time
+import optparse
+import sys
+import os
+
+from test_suite import config, utils, phatchtools
+
+report = logging.getLogger('report')
+
+
+def clean():
+    """Clean generated files from previous run"""
+    utils.remove_path(options.output)
+    utils.remove_path(config.OUT_ACTIONLISTS_PATH)
+    utils.remove_path(config.OUT_DIFF)
+    utils.create_path(options.output)
+    utils.create_path(config.OUT_ACTIONLISTS_PATH)
+
+
+def set_logger(log_path):
+    """Setup logging"""
+    logging.basicConfig(
+        level=logging.INFO,
+        format='%(message)s',
+    )
+    #console = logging.StreamHandler()
+    #console.setLevel(logging.INFO)
+    #logging.getLogger('').addHandler(console)
+
+    error_handler = logging.FileHandler(options.log, mode='w')
+    error_handler.setLevel(logging.ERROR)
+    logging.getLogger('').addHandler(error_handler)
+
+    report_handler = logging.FileHandler(options.report, mode='w')
+    report.addHandler(report_handler)
+
+
+if __name__ == '__main__':
+    # Option parser
+    parser = optparse.OptionParser()
+    tags = sorted(phatchtools.get_action_tags().keys() + ['library', 'save'])
+    parser.add_option(
+        '-t', '--tag',
+        default=None,
+        choices=tags,
+        help='Generate tests by tag',
+    )
+    actions = sorted(phatchtools.get_actions().keys())
+    parser.add_option(
+        '-s', '--select',
+        action="append",
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/tests/doc_test.py

@@ -1,0 +1,56 @@
+#!/usr/bin/python
+# -*- coding: utf-8 -*-
+# Copyright (C) 2007-2008  www.stani.be
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Follows PEP8
+
+import os
+import subprocess
+import sys
+
+
+COMMAND = [
+    'nosetests',
+    '--with-doctest',
+    '--noexe',  # DO NOT look for tests in python modules that are executable.
+    '-P',  # --no-path-adjustment
+    '-q',  # --quiet
+]
+MODULES = ['actions', 'console', 'core', 'data', 'lib', 'pyWx']
+
+
+def main(COMMAND, MODULES):
+    if sys.platform.startswith('win'):
+        # windows
+        args = COMMAND + ['-e', 'linux'] + MODULES
+    elif sys.platform.startswith('darwin'):
+        # mac
+        args = COMMAND + ['-e', 'linux|windows'] + MODULES
+    else:
+        # linux
+        args = COMMAND + ['-e', 'windows'] + MODULES + ['linux']
+    os.chdir('../phatch')
+    # The commented lines might be necessary for windows?!
+    #os.rename('__init__.py', '__init__.py.test')
+    #if os.path.exists('__init__.py'):
+    #    os.remove('__init__.py')
+    result = subprocess.call(args)
+    #os.rename('__init__.py.test', '__init__.py')
+    os.chdir('../tests')
+    return result
+
+
+if __name__ == '__main__':
+    sys.exit(main(COMMAND, MODULES))

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/tests/license_test.py

@@ -1,0 +1,76 @@
+#!/usr/bin/python
+# -*- coding: utf-8 -*-
+# Copyright (C) 2007-2010  www.stani.be
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# You need to have licensecheck installed:
+#   sudo apt-get install devscripts
+
+
+import os
+import re
+import sys
+import time
+sys.path.insert(0, os.path.join('..', 'phatch'))
+
+
+try:
+    from lib import system
+except ImportError:
+    print("You need to run this script from the 'tests' directory.")
+    sys.exit(1)
+
+RE_FILE = re.compile('(?P<filename>.+?):\s(?P<license>.+?)\s*'\
+    '\n(\s+\[(?P<copyright>.+?)\])?')
+
+
+def get_error(d):
+    if 'GENERATED' in d['license']:
+        return None
+    if d['license'] != 'GPL (v3 or later)':
+        return 'License should be "GPL (v3 or later)".'
+    if d['copyright'] is None:
+        return 'Copyright is missing (needs to include www.stani.be).'
+    if not('www.stani.be' in d['copyright']):
+        return "Copyright doesn't include 'www.stani.be'"
+
+
+def check():
+    time_start = time.time()
+    error = 0
+    total = 0
+    cur_dir = os.getcwd()
+    stdout, stderr = system.shell(['licensecheck',
+        '--recursive',
+        '--copyright',
+        '--ignore', 'phatch/other|wxGlade|license',
+        os.path.abspath('..'),
+    ])
+    for match in RE_FILE.finditer(stdout):
+        d = match.groupdict()
+        d['error'] = get_error(d)
+        if d['error'] and not('api.py' in d['filename']):
+            print('%(filename)s:\n'\
+                '- %(error)s\n'\
+                '- license: %(license)s\n'\
+                '- copyright: %(copyright)s\n' % d)
+            error += 1
+        total += 1
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/tests/pep8_test.py

@@ -1,0 +1,120 @@
+#!/usr/bin/python
+# -*- coding: utf-8 -*-
+# Copyright (C) 2007-2010  www.stani.be
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Follows PEP8
+
+
+import os
+import pickle
+import time
+import shelve
+import sys
+sys.path.insert(0, os.path.join('..', 'phatch'))
+
+
+try:
+    from other import pep8
+except ImportError:
+    print("You need to run this script from the 'tests' directory.")
+    sys.exit(1)
+
+
+ERROR_HEADER = "Shame on you! These file(s) don't follow PEP8:\n%s\n"
+PEP8_APP = os.path.join('..', 'phatch', 'other', 'pep8.py')
+PEP8_ARGS = ['python', PEP8_APP, '--show-source', '--repeat', '--count']
+WXGLADE = 'wxGlade'
+OTHER = os.path.join('phatch', 'other')
+OUTPUT = os.path.join('tests', 'output')
+
+ERROR_MESSAGE = ''
+
+
+def message(x):
+    global ERROR_MESSAGE
+    print(x)
+    ERROR_MESSAGE += '%s\n' % x
+
+pep8.process_options(PEP8_ARGS)
+pep8.message = message
+
+BLACK_LIST = [
+    os.path.join('phatch', 'lib', 'metadataTest.py'),
+    os.path.join('phatch', 'lib', 'pyWx', 'about.py'),
+    os.path.join('phatch', 'lib', 'pyWx', 'dialogsInspector.py'),
+    os.path.join('phatch', 'lib', 'pyWx', 'folderFileBrowser.py'),
+]
+
+
+def test(dirname='..'):
+    global ERROR_MESSAGE
+
+    def needs_pep8(filename):
+        key = os.path.abspath(filename)[n:]
+        return filename.endswith('.py') and not (
+            OTHER in filename
+            or OUTPUT in filename
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/tests/test_suite/defaults.py

@@ -1,0 +1,27 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2009 Nadia Alramli, Stani (www.stani.be)
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+#
+# Follows PEP8
+
+blender = {
+    'Render Width': '128px',
+    'Render Height': '128px'}
+
+#geotag = {
+#    'GPS Data': ''
+#}

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/tests/test_suite/phatchtools.py

@@ -1,0 +1,401 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2009 Nadia Alramli, Stani (www.stani.be)
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+#
+# Follows PEP8
+
+import re
+import glob
+import os.path
+import sys
+import logging
+import subprocess
+
+# Test suite modules
+import utils
+import config
+import defaults
+import gettext
+gettext.install('_')
+
+# Phatch modules
+from lib.safe import eval_safe
+
+#################################
+#   Building Actions Hashtable  #
+#################################
+__DEFAULTS = {}
+
+
+def get_defaults():
+    """Get actions custom defaults
+    Returns a dictionary that maps action names to defaults"""
+    global __DEFAULTS
+    if __DEFAULTS:
+        return __DEFAULTS
+    __DEFAULTS = dict(
+        (action, getattr(defaults, action))
+        for action in dir(defaults)
+        if not action.startswith('__'))
+    return __DEFAULTS
+
+
+__ACTIONS = {}
+
+
+def get_actions():
+    """Get phatch actions
+    Returns a dictionary that maps action names to objects"""
+    global __ACTIONS
+    if __ACTIONS:
+        return __ACTIONS
+    action_names = [utils.file_name(action_file) for action_file in
+            glob.glob(os.path.join(config.PHATCH_ACTIONS_PATH, '*.py'))]
+    default_values = get_defaults()
+    __ACTIONS = dict(
+        (
+            name,
+            __import__(
+                'actions.%s' % name,
+                name,
+                fromlist=['actions']).Action())
+        for name in action_names
+        if name != '__init__')
+    for name, fields in default_values.iteritems():
+        set_action_fields(__ACTIONS[name], fields)
+    return __ACTIONS
+
+
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/tests/test_suite/utils.py

@@ -1,0 +1,209 @@
+# Phatch - Photo Batch Processor
+# Copyright (C) 2009 Nadia Alramli, Stani (www.stani.be)
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Phatch recommends SPE (http://pythonide.stani.be) for editing python files.
+#
+# Follows PEP8
+
+import filecmp
+import os
+import shutil
+
+
+def system_path(path):
+    """Convert a path string into the correct form"""
+    return os.path.abspath(os.path.normpath(path))
+
+
+def create_path(path):
+    """Create a path if it doesn't already exist"""
+    if not os.path.exists(path):
+        os.makedirs(path)
+
+
+def remove_path(path):
+    """Delete a file or a direcotry"""
+    if os.path.isdir(path):
+        shutil.rmtree(path)
+    elif os.path.exists(path):
+        os.remove(path)
+
+
+def replace_all(input, replace_map):
+    """Replace multiple words in a string"""
+    for key, value in replace_map:
+        input = input.replace(key, value)
+    return input
+
+
+def write_file(path, data):
+    """Write to a file"""
+    f = open(path, 'w')
+    f.write(data)
+    f.close()
+
+
+def file_name(path):
+    """Get the file name from path without its extension"""
+    if os.path.isdir(path):
+        return ''
+    return os.path.basename(path).partition('.')[0]
+
+
+def file_extension(path):
+    """Get the file extension for path"""
+    if os.path.isdir(path):
+        return ''
+    return os.path.basename(path).partition('.')[-1]
+
+
+def indexed_name(name, index):
+    """Return an indexed name"""
+    if index:
+        return '%s_%s' % (name, index)
+    return name
+
+
+def compare(file1, file2):
+    """Compare two files"""
+    return filecmp.cmp(file1, file2)
+
+
+def analyze(original, other):
+    """Analyze the difference between the two images"""
[…]

### 2013-04-29 docs/Jesse/Confusion Notes/figs/phatch-0.2.7/tools/change_tags.py

@@ -1,0 +1,68 @@
+#!/usr/bin/python
+# Copyright (C) 2009 Nadia Alramli, Stani (www.stani.be)
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see http://www.gnu.org/licenses/
+#
+# Follows PEP8
+
+# A script to modify action tags
+import pprint
+import re
+import glob
+import os.path
+import sys
+
+ACTIONS_PATH = os.path.normpath('../phatch/actions')
+reg = re.compile(r'(\s*tags\s*=\s*).+')
+
+
+def parse_tags(tag_file):
+    data = open(tag_file).read().split('\n\n')
+    tag_lists = [map(str.strip, tags.split()) for tags in data]
+    tags = {}
+    for tag_list in tag_lists:
+        for action in tag_list[1:]:
+            if action in tags:
+                tags[action].append(tag_list[0])
+            else:
+                tags[action] = [tag_list[0]]
+    return tags
+
+
+def tag_string(tags):
+    return '[%s]' % ', '.join("_t('%s')" % tag.lower() for tag in tags)
+
+if __name__ == '__main__':
+    if len(sys.argv) == 2:
+        tag_file = sys.argv[1]
+    else:
+        tag_file = 'tag_list'
+
+    tags = parse_tags(tag_file)
+
+    actions = [
+        action
+        for action in glob.glob(os.path.join(ACTIONS_PATH, '*.py'))
+        if action != '__init__'
+    ]
+    for action in actions:
+        data = open(action).read()
+        name = os.path.basename(action)
+
+        def replace_tags(match):
+            return match.group(1) + tag_string(tags[name])
+        data = reg.sub(replace_tags, data)
+        f = open(action, 'w')
+        f.write(data)
+        f.close()

### 2013-04-29 docs/Nate/Proposal/presentation/talk.tex

@@
 Consider a square cavity with an incompressible, viscous fluid, with a lid that moves at a constant rate.
-The resulting flow will be vorticular; there will be \pecosbold{Moffat eddies} at the corners; in fact, the exact solution will have an infinite number of such eddies, visible at progressively finer scales.\footnote{\FootSize \bibentry{Moffat}}
+The resulting flow will be vorticular; there will be \pecosbold{Moffatt eddies} at the corners; in fact, the exact solution will have an infinite number of such eddies, visible at progressively finer scales.\footnote{\FootSize \bibentry{Moffatt}}
 \begin{center}
@@
 Streamlines for the full cavity and for the lower-left corner, on a quadratic mesh after 7 adaptive refinements.
-The lower-left corner shows the first Moffat eddy.
+The lower-left corner shows the first Moffatt eddy.
 The final mesh has 124 elements and 11,202 dofs.
@@
 \frametitle{Lid-Driven Cavity Flow: Streamlines}
-Using a cubic mesh and running 11 refinement steps, we can resolve the second Moffat eddy:
+Using a cubic mesh and running 11 refinement steps, we can resolve the second Moffatt eddy:
 \begin{center}
@@
 \end{center}
-Streamlines for the lower-left corner on a cubic mesh after 11 adaptive refinements: the second Moffat eddy.  The final mesh has 298 elements and 44,206 dofs.
+Streamlines for the lower-left corner on a cubic mesh after 11 adaptive refinements: the second Moffatt eddy.  The final mesh has 298 elements and 44,206 dofs.
 \end{frame}

### 2013-05-01 docs/Jesse/HeuerPaper/responseForReviewers2.tex

--- 2013-04-29 docs/Jesse/HeuerPaper/responseForReviewers.tex
@@
 
-The authors are very grateful for the feedback, comments and suggestions provided by both reviewers.  Please accept the attached revised version of our paper:
-
-\begin{center}
-Jesse Chan, Norbert Heuer, Tan Bui-Thanh, and Leszek Demkowicz\\
-\textit{A robust DPG method for convection-dominated diffusion problems II: adjoint boundary conditions and mesh-dependent test norms.}
-\end{center}
-
-In addition to the changes requested by the reviewers, we have made a few additional corrections in the manuscript.
-The title has been changed to match the submitted title, and a citation has been added in Section 1.4 for Dr Wolfgang Dahmen's work, which we discovered after submission.
-His work is equivalent to the DPG method for alternative variational formulations.
-Additionally, the following changes have been made to the manuscript
-\begin{enumerate}
-\item On page 2, the SUPG method is mentioned to be $H^1$ optimal.  We have added the specification ``in the 1D case", as this claim does not hold in 2 and 3 dimensions.
-\item We have removed part of Section 1.5, previously titled ``Canonical energy norm pairings for the ultra-weak formulation".
-Previously, the quasi-optimal/graph test norm was stated to induce a norm on the trial space $U$ of a specific form; it was discovered that this proof was incorrect, and the exact form of the induced energy norm under the graph test norm is unknown.
-The section has been rewritten to correct this.
-Figure 1 was also removed.
-\item In Section 2 near the second half of page 8, we have changed the description of the broken $H^1\times H({\rm div})$ test norm to be the ``canonical norm on this test space" as opposed to simply ``the canonical test norm", which could be confused with the \textit{quasi-optimal/graph test norm} described as the canonical norm in the previous section.
-\item In Section 3.5, in replacing the image with a higher quality eps version, we plot a solution to the 1D adjoint equation with a given load.
-The function plotted was inconsistent with the load described; this is fixed.
-\item In Section 4.1 and onwards, some images have been replaced with higher quality image files.
-A typo is corrected on p24, concerning the greedy adaptive strategy used (we refine elements who satisfy $e_K^2 \leq \alpha^2 \max e_K^2$, but had neglected to square the factor $\alpha$ in the original manuscript).
-
-\end{enumerate}
-
-We thank the reviewers for their insightful comments, recommendations, and favorable reviews.
-Attached are details on the revisions made as requested from each reviewer, as well as the authors responses to each revision request.
-
-\textbf{Reviewer 1}
-
-%The paper is concerned with DGP methods applied to linear convection-diffusion equations in the small-diffusion limit for the inflow boundary conditions of [13].
-The authors identify a non-canonical and mesh-dependent test norm, which is explicitly computable and uniformly equivalent to the energy norm (cf.
-Lemma 1).
-The performance of the methods is then tested in a set of numerical examples using h-adaptivity.
-The tests confirm the robustness of the methods, as expected.
-Additionally, it is observed that the ratios of $L^2$ errors and energy errors are uniformly bounded in the Peclet number.
-%
-%Assessment:
-%DGP methods have emerged as robust discretization methods for convection-diffusion problems (as well as for other singularly perturbed problems).
-They are based on the local computation of so-called optimal test functions, which by construction yield stability and quasi-optimality in the norms considered.
-In this paper, DGP methods are extended to the inflow conditions of [13] while earlier papers address only Dirichlet conditions.
-It turns out that the effects of the different boundary conditions may be quite dramatic due to the different structure of the adjoint problems, and indeed require different test norms, as illustrated in Section 3.5.
-As such, this is an interesting contribution to the theory of DGP methods.
-
-%Although I didn't check all details, the results of the paper appear correct and new.
-The paper is well written; its introduction also nicely surveys the main ideas of DGP methods.
-I recommend the paper for publication in CAMWA.
-
-%However, I would like to authors to address the following minor suggestions/comments/typos:
-\begin{enumerate}
-\item \textcolor{red}{After equation (1): $U$ should be $U_h$.}  Corrected.
-
-\item \textcolor{red}{Page 7, last line: A period is missing at the end of the last sentence.}   We fixed the issue on equation (10), where there was a comma instead of a period, but I could not find this typo.
-
-\item \textcolor{red}{The new boundary conditions should be discussed in a few more details.
-What do they model physically?
-What happens on $\Gamma_0$?
-Discussion of weak formulation and well-posedness of the continuous problem?}.
-Certainly - we've added a short explanation.
-In summary, the boundary condition models physically the conserved flux corresponding to the conservation law.
-However, though the boundary condition holds physical meaning, this boundary condition is chosen instead because it approximates, for small enough $\epsilon$ and $\beta_n > 0$ on $\Gamma_0$, the standard boundary condition $u = u_0$ on $\Gamma_0$.
-
-Due to the nature of the ultra-weak variational formulation, the weak formulation for both standard boundary conditions on $u$ and the new boundary condition on $\Gamma_0$ are the same.
-For convection-diffusion, the variational form is
-\[
-b\LRp{\LRp{u,\sigma,\uh,\fnh},\LRp{v,\tau}} = \LRa{\fnh,v} - \LRa{\uh,\tau_n} + \text{field/interior terms}
-\]
-
-The application of boundary conditions is equivalent to the imposition of a natural boundary condition in both cases, where either $\LRa{\fnh,v}_{\Gamma_0}$ or $\LRa{\uh,\tau_n}_{\Gamma_0}$ are given data and become forcing terms.
-
-Regarding the well-posedness of the variational problem, we refer the reviewer to \cite{analysisDPG}, whose analysis also covers the case of these boundary conditions (assuming well-posedness of the continuous problem), or \cite{Bui-ThanhDemkowiczGhattas11b}, where both the standard inflow boundary condition on $u$ and the proposed Robin boundary condition can be analyzed in the framework of Friedrichs systems.
-
-Regarding the well-posedness of the continuous problem, we refer the reviewer to \cite{Hesthaven96astable}, the paper of Dr Jan Hesthaven, where he proves well-posedness of both the transient case and the case as $\epsilon \rightarrow 0$.
-
-\item \textcolor{red}{Page 10, mid page: There is a latex error regarding the reference to Figure 2, and the label in Figure 2 needs to be fixed.}  Corrected.
-
-\item \textcolor{red}{Page 12: Several sentences are in boldface, for no obvious reasons. This should be changed. }  Corrected.
-
-\item \textcolor{red}{Assumptions (19)-(21): It should be discussed how restrictive these assumptions are.} Corrected; a footnote has been added discussing the physical interpretation of such assumptions.
-
-A few comments on the assumptions: 
-\begin{enumerate}
-\item These assumptions are only sufficient conditions - these conditions have been introduced only to ensure a robust bound exists for solutions to the adjoint equations.
-For example, the condition $\div \beta = 0$ is only a sufficient condition to ensure the well-posedness of an auxiliary problem related to the proof of a lemma.
-The lemma can still hold without this condition
-\item These assumptions are strictly for the steady-state case with no first-order term.
-In the case when there is a first-order term, it is easy to prove Lemma 3 without the aid of the condition $\curl \beta = 0$.
-\item Several numerical experiments (to be reported in an upcoming report on locally-conservative DPG) do not indicate a loss of robustness even when these conditions are violated.
-For example, experiments with the viscous Burgers' equation
-\[
-u_{,t} + \LRp{\frac{u^2}{2}}_{,x} - \epsilon \nabla u = 0
-\]
-yield a solution with a shock from $(x,y) = (.5,.5)$ to $(.5,1)$ for initial condition $u(x,0) = 1-2x$.
-The linearized equation is a convection-diffusion equation with $\beta = (u,1)$.
-When $u$ has a shock, $\grad \beta + \grad \beta^T - \div \beta I = O(\epsilon^{-1})$, and condition (19) is violated, but there was no observable degeneration in solution quality as $\epsilon$ decreased.
-\end{enumerate}
-
-\item \textcolor{red}{Page 15, last line: change "proper" to "these", "the robust bounds" to "the following robust bounds".}  Corrected.
-
-\item \textcolor{red}{Lemma 1: the equivalence bounds appear not be p-robust.
-These should be mentioned explicitly in the statement of the lemma.}  The bounds in Lemma 1 should hold under any mesh and arbitrary $p$ - there were only regularity assumptions made in the proof.
-Could we request a more detailed explanation into why the bounds appear to not be $p$-robust?
-
-\item \textcolor{red}{Shouldn't the curves in Figure 8 (left) be on top of each other to indicate robustness?
-Please comment.
-Also: Please indicate the orders of the convergence which are observed?} Noted - we have expanded the paragraph discussing Figures 7 and 11, (the figures have been renumbered).
-
-As both reviewers have expressed concern over the ratio curves in Figure 8, I have discussed this in a section at the end of this letter explaining the interpretation of the ratio curves for various values of $\epsilon$.
-
-Concerning the orders of convergence - 
-\begin{enumerate}
-\item We are mostly in the pre-asymptotic range for most of our problems, and thus do not expect to observe optimal rates in our setup for small values of $\epsilon$.
-For this reason, we believe that reporting convergence rates would not add much meaningful information.
-\item We have verified that we do indeed achieve optimal rates asymptotically under uniform refinements for $\epsilon = 1$, $1e-1$, and $1e-2$.
-However, the mesh size at which the optimal rate is achieved becomes smaller and smaller as $\epsilon$ shrinks; we reach the optimal rate immediately for $\epsilon = 1$, but for $\epsilon = 1e-2$, our rates of convergence between $h = 1/128$ and $h = 256$ changed from 2.5255 to 2.8292.
-We expect an optimal rate of $3$, but as this example shows, it may not be computationally feasible to get to that asymptotic range and demonstrate robustness for very small $\epsilon$ at the same time.
-\item Adaptivity should restore the optimal rate of convergence with respect to degrees of freedom; however, for strongly anisotropic solutions (such as boundary layer solutions), this optimal rate is achieved only through the use of anisotropic refinements, which we have not yet implemented.
-\end{enumerate}
-
-\item \textcolor{red}{Page 24: How is the estimator $e_K^2$ defined? Please provide some details.}  Corrected.
-
-Specifically, at the top of page 5, a paragraph is dedicated to the definition of the \textit{error representation function}, which is the inverse Riesz image of the residual of the variational equation (in $V'$) - in other words, the solution of
-\[
-(e,\delta v)_V = l(\delta v) - b(u_h,\delta v), \quad \forall v\in V.
-\]
-Under this, $\nor{e}_V = \nor{Bu-Bu_h}_{V'} = \nor{u-u_h}_E$ - the norm of the error representation function returns the norm of the error in the energy norm.
-We note that, under a localizable norm and discontinuous test basis, this error representation function can be computed locally and used as a local error indicator.
-$e_K^2$ is defined to be the squared energy norm of the error representation function over a single element $\nor{e}_{V(K)}^2$.
-Summing together these elementwise contributions recovers the actual squared energy error over the domain.
-
-\end{enumerate}
+The authors are very grateful for the feedback, comments and suggestions provided by both reviewers in this revision.  Please accept the attached second revised version of our paper.
 
@@
 
-%The authors continue the analysis of the Discontinuous Petrov-Galerkin method for a singularly perturbed convection-diffusion problem initiated in [10].
-The paper starts with an introduction to the abstract setting of the DPG.
-The core of the paper studies the DPG for the (scalar) convection-diffusion problem.
-Two issues are studied: first, the choice of the norm on the test space and second the impact of this choice on the ``energy norm", i.e., the norm on the trial space.
-The norm on the test space should fulfill several requirements: firstly, it should be localizable so that the test functions (which have to be computed) can be computed locally and secondly it should avoid test functions that have boundary layers, which are difficult to resolve.
-In this paper, these two issues are addressed by using the mesh-dependent norm given in Lemma 1 on p.
-17.
-Lemma 1 also shows that the ``energy norm" induced by this norm on the test space allows for control of the field variables, in particular, the primal variable u.
-%
-%The paper reads very well, is of topical interest and very well suited for CAMWA. The referee recommends publication after the following issues are addressed.
+\begin{enumerate}
+\item \textcolor{red}{p.
+4, footnote: given that the authors are in a Hilbert space setting, the authors probably mean $\nor{v}_{V(\Oh)}^2 = \sum_{K\in \Oh} \nor{v}_{V(K)}^2$.}  Corrected -- the authors thank the reviewer for noting this.
+\item \textcolor{red}{Section 1.3: the claim about the relation between the norms $\nor{\cdot}_U$ and $\nor{\cdot}_{V,U}$ is not completely clear to the referee--the authors are encouraged to add a few clarifying words:}
+\begin{enumerate}
+\item \textcolor{red}{please give a precise reference to a theorem in [5].} Clarified.  The theorem is specified to be Lemma 2.5 in \cite{Bui-ThanhDemkowiczGhattas11a}.  
+\item \textcolor{red}{please be more specific as to what ``definite" means for the bilinear form.} Clarified.  We have added a footnote clarifying the ``definiteness" of the bilinear form as meaning 
+\[
+b(u,v) = 0, \forall v\in V \Rightarrow u = 0
+\]
+and
+\[
+b(u,v)=0, \forall u\in U \Rightarrow v = 0,
+\]
+ which imply injectivity of the bilinear operator $B$ and its transpose $B'$, defined such that $\LRa{Bu,v} = \LRa{u,B'v}.$  These conditions in turn guarantee (through the Banach closed range theorem) solvability of the variational problem.
+\item \textcolor{red}{the discussion in Section $1.3$ suggests that for any norm $\nor{\cdot}_U$ one has an induced norm $\nor{\cdot}_{V,U}$ on $V$ .
+The referee doesn't see this.
+For example, taking $U = V = H_0^1(\Omega)$ and $b(u, v) \coloneqq \LRp{\grad u,\grad v}_{L^2(\Omega)}$ but equipping $U$ with $\nor{\cdot}_U \coloneqq \nor{\cdot}_{L^2(\Omega)}$ does not lead to a norm on $V$ via $\nor{\cdot}_{V,U}$ , since for smooth $v$ one obtains $\nor{v}_{V,U} = \nor{\del v}_{L^2(\Omega)}$.}
+\begin{enumerate}
+\item At a very broad level, from Lemma 2.5 in \cite{Bui-ThanhDemkowiczGhattas11a}, the duality between trial and test norms is a consequence of $M/\gamma = 1$, where $M$ is the continuity constant such that $b(u,v)\leq M \nor{u}_U\nor{v}_V$, and $\gamma$ is the inf-sup/boundedness below constant such that
+\[
+0<\gamma \leq \inf_{u\in U}\sup_{v\in V}\frac{b(u,v)}{\nor{u}_U\nor{v}_V}.
+\]
+If the problem is posed such that $U = H_0^1$ but $\nor{\cdot}_U = \nor{\cdot}_{\L}$, then this problem is ill-posed and we no longer have duality between trial and test norms.
 
-\begin{enumerate}
-\item \textcolor{red}{The authors are encouraged to carefully proof-read the proof of Lemma 1.}  Noted.
-Shortly after submitting, the authors did go through the proof of Lemma 1 again with a careful read-through.
-\item \textcolor{red}{The notation $\nor{\cdot}_{V,K}$ is used in the proof of Lemma 1 repeatedly and the referee did not find a definition.}  Corrected.
-The definition of $\nor{\cdot}_{V,K}$ is included on the end of page 4 in the footnote on localizable norms, as well as on p18, right before the definition is used.
-Additionally, to be consistent with the notation $L^2(K)$, we have changed the notation from $\nor{\cdot}_{V,K}$ to $\nor{\cdot}_{V(K)}$
-\item \textcolor{red}{Towards the end of the proof of Lemma 1, the notation $\nor{\eta} + \nor{w}$ appears.
-The context suggest that $\eta$ and $w$ are measured in the $L^2$-norm, but $H^1$ and $H({\rm div})$ seem more likely from the context.}  Corrected.
-The reviewer is correct, the proper setting was indeed $H^1$/$H({\rm div})$.
-\item \textcolor{red}{The numerical results show an $\epsilon$-dependence in the approximation (cf.
-Figs.
-8, 10, 12) although the error measure is rather weak (the $L^2$-norm of the field variable $u$ doesn't ``see" the boundary layer).
-The referee feels that the readers would appreciate some comments.}  Additional comments describing the ratios have been added on p25.
-Figure 10 (now Figure 9) largely addresses the issue of modeling error in the inflow condition.
+\item The reason for the loss of well-posedness if we choose $U = H_0^1$ and $\nor{\cdot}_U = \nor{\cdot}_{\L}$ is that the space $U = H_0^1$ is not complete under the norm $\nor{\cdot}_U = \nor{\cdot}_{\L}$.
+In other words, the space $U$ is smaller than the $\L$ norm would imply - a weaker norm $\nor{\cdot}_U$ implies a large space $U$.
+Under the perspective that the spaces $U$ and $V$ are defined by their respective norms, if we set $\nor{\cdot}_U = \nor{\cdot}_{\L}$, this would imply $U = \L$.
+Since the definitions of the spaces $U$ and $V$ are incorporated in the definition of definiteness of $b(u,v)$, we would lose definiteness of the bilinear form as well, a prerequisite for Lemma 2.5.
+\item We note that it is still possible to specify $\nor{\cdot}_U = \nor{\cdot}_{\L}$.
+If we do not require $U = V = H_0^1$, and simply specify $\nor{\cdot}_U = \nor{\cdot}_{\L}$, then the space induced by $\nor{\cdot}_U$ is $U = \L$.
+If, then, we rewrite the bilinear form such that $b(u,v) = -\LRp{u,\del v}_{\L}$ (to satisfy regularity constraints), then we do indeed induce the norm $\nor{v}_V \coloneqq \nor{\del v}_{\L}$, which then induces the definition of the test space $V = \LRc{v\in \L, \del v\in \L}$.
+Under these conditions, we can show that both well-posedness and duality of norms hold.
 
-As both reviewers have expressed concern over the ratio curves in Figure 8, please see the section below on the interpretation of the ratio curves for various values of $\epsilon$.
+\end{enumerate}
+There are two main responses to this question - the first is that the definition of a space cannot be divorced from the definition of the norm on the space (by choosing a norm on $U$, we are simultaneously choosing the space $U$).
+The second Lemma 2.5 in \cite{Bui-ThanhDemkowiczGhattas11a} gives that three conditions are equivalent -
+\begin{itemize}
+\item $\frac{M}{\gamma} = 1$
+\item $\nor{\cdot}_U = \sup_{v\in V}\frac{b(u,v)}{\nor{v}_V}$
+\item $\nor{\cdot}_{V,U} = \sup_{u\in U}\frac{b(u,v)}{\nor{u}_U}$.
+\end{itemize}
+These three conditions are all related to the inf-sup condition.
+The starting point of DPG is to require from the start that $\frac{M}{\gamma} = 1$.
+By specifying a test norm, the trial norm  (and consequentially the space $U$) are defined such that we can guarantee that $\frac{M}{\gamma} = 1$ by construction.
 
-\item \textcolor{red}{p. 21, just below (22): integrate $\rightarrow$ integrating}.  Corrected.
-\item \textcolor{red}{p. 23, last formula: $r2 \rightarrow r_2$}.  Corrected.  There was also the same error in $r1$, which was also corrected.
 \end{enumerate}
-
-\textbf{Author remark: on the ratio curves for various values of $\epsilon$}
-
-A few reasons why the curves in these figures are not guaranteed to lie on top of each other 
-\begin{enumerate}
-\item The proofs only guarantee that the ratio of $L^2$ to energy error is bounded by some constant independent of $\epsilon$.
-Changing $\epsilon$ changes the problem, and the curves are not guaranteed to be similar.
-The curves are not guaranteed even to be bounded away from zero; this is simply an observed phenomenon.
-\item The test norm used is mesh-dependent.
-In this work, the constants placed in front of the $L^2$ portions of the test functions $v$ and $\tau$ are scaled by a mesh-dependent value, which takes two asymptotic values.
-In the far-underresolved limit $h \gg \epsilon$, this value is $\epsilon$ for $\nor{v}_{L^2}$ and $1$ for $\nor{\tau}_{L^2}$ - these help guarantee that the optimal test functions do not contain boundary layers, which may introduce approximation error, which our analysis does not account for.
-In the fully-resolved limit $h\approx \epsilon$, the values in front of $\nor{v}_{L^2}$ and $\nor{\tau}_{L^2}$ are $1$ and $\epsilon^{-1}$, respectively.
-These are to help account for the fact that the $\nor{v}$ and $\nor{\tau}$ scale differently from $\nor{\grad v}$ and $\nor{\div \tau}$.
-
-For the first example, the ratio curves each have a clear ``transition point", where the mesh introduces elements where $h \approx \epsilon$.
-This transition occurs later as $\epsilon$ shrinks, simply due to the fact that it takes more degrees of freedom to introduce elements of size $\epsilon$ on a 1-irregular constrained mesh.
-
-In the second example, a discontinuous boundary condition is approximated by a 20 term Fourier series.
-As refinements are introduced, the problem itself changes due to the improved resolution of the boundary condition at the inflow (the ``moving target" issue).
-This further complicates the matter, and the ratio is consequentially more ``messy"; however, it is still very close to 1 for every $\epsilon$ we tested.
-\item The scale can be misleading; we show the $y$-axis from $0$ to $2$.
-In cases where there is \textit{not} a robust bound, these ratios scale with $\epsilon^{-1}$ - in other words, to show the ratios for $\epsilon$ up to $1e-4$, we would require a scale with $y \in [0,1e4]$, or a logarithmic scale from $0$ to $1e4$.
-Under these scales, the curves would appear to lie more on top of one another.
 \end{enumerate}
-
 \closing{Best regards}

### 2013-05-01 docs/Jesse/Confusion Notes/notes.tex

%&pdflatex
\documentclass[11pt,onecolumn]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
\usepackage[top=2cm,bottom=3cm,left=2.5cm,right=2cm]{geometry}
\usepackage{amssymb}
\usepackage{amscd}
\usepackage{listings}
\usepackage{array}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage[textsize=footnotesize,color=green]{todonotes}
\usepackage{algorithm, algorithmic}
\usepackage{array}
\usepackage{bm}
\usepackage{tikz}
\usepackage{subfigure}
\usepackage[normalem]{ulem}

\newcommand{\bs}[1]{\boldsymbol{#1}}
\DeclareMathOperator{\diag}{diag}

\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}

\newcommand{\tablab}[1]{\label{tab:#1}}
\newcommand{\tabref}[1]{Table~\ref{tab:#1}}

\newcommand{\theolab}[1]{\label{theo:#1}}
\newcommand{\theoref}[1]{\ref{theo:#1}}
\newcommand{\eqnlab}[1]{\label{eq:#1}}
\newcommand{\eqnref}[1]{\eqref{eq:#1}}
\newcommand{\seclab}[1]{\label{sec:#1}}
\newcommand{\secref}[1]{\ref{sec:#1}}
\newcommand{\lemlab}[1]{\label{lem:#1}}
\newcommand{\lemref}[1]{\ref{lem:#1}}

\newcommand{\mb}[1]{\mathbf{#1}}
\newcommand{\mbb}[1]{\mathbb{#1}}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\nor}[1]{\left\| #1 \right\|}
\newcommand{\snor}[1]{\left| #1 \right|}
\newcommand{\LRp}[1]{\left( #1 \right)}
\newcommand{\LRs}[1]{\left[ #1 \right]}
\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
\newcommand{\LRc}[1]{\left\{ #1 \right\}}
\newcommand{\LRb}[1]{\left| #1 \right|}

\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
\newcommand{\Grad} {\ensuremath{\nabla}}
\newcommand{\Div} {\ensuremath{\nabla\cdot}}
\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
\newcommand{\jump}[1] {\ensuremath{\LRs{\!\left[#1\right]\!}}}
\newcommand{\uh}{\widehat{u}}
\newcommand{\fnh}{\widehat{f}_n}
\renewcommand{\L}{L^2\LRp{\Omega}}
\newcommand{\pO}{\partial\Omega}
\newcommand{\Gh}{\Gamma_h}
\newcommand{\Gm}{\Gamma_{-}}
\newcommand{\Gp}{\Gamma_{+}}
\newcommand{\Go}{\Gamma_0}
\newcommand{\Oh}{\Omega_h}

\newcommand{\eval}[2][\right]{\relax
  \ifx#1\right\relax \left.\fi#2#1\rvert}

\def\etal{{\it et al.~}}

\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
\newcommand{\tensor}[1]{\underline{\vect{#1}}}
\newcommand{\del}{\Delta}
\newcommand{\grad}{\nabla}
\newcommand{\curl}{\grad \times}
\renewcommand{\div}{\grad \cdot}
\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
\newcommand{\eip}[1]{a\left( #1 \right)}
\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}

\newcommand{\circone}{\ding{192}}
\newcommand{\circtwo}{\ding{193}}
\newcommand{\circthree}{\ding{194}}
\newcommand{\circfour}{\ding{195}}
\newcommand{\circfive}{\ding{196}}

\def\arr#1#2#3#4{\left[
\begin{array}{cc}
#1 & #2\\
#3 & #4\\
\end{array}
\right]}
\def\vecttwo#1#2{\left[
\begin{array}{c}
#1\\
#2\\
\end{array}
\right]}
\def\vectthree#1#2#3{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
\end{array}
\right]}
\def\vectfour#1#2#3#4{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
#4\\
\end{array}
\right]}

\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

\newcommand{\G} {\Gamma}
\newcommand{\Gin} {\Gamma_{in}}
\newcommand{\Gout} {\Gamma_{out}}

\newtheorem{remark}{Remark}

%\title{$\epsilon$-explicit analysis of DPG for convection-dominated diffusion}
\title{Notes on convection-diffusion}
\date{}
\begin{document}

\maketitle

\section{Boundary layers in robust norm test functions and global/local test spaces}

In \cite{DPGrobustness, ChanHeuerBui-ThanhDemkowicz12}, we introduced the test norm
\[
\nor{v,\tau}_V^2 \coloneqq \alpha\nor{v}_{\L}^2 + \nor{\beta\grad v}_{\L}^2 + \epsilon \nor{\grad v}_{\L}^2 + {\min}\LRc{\frac{1}{\epsilon},\frac{1}{\LRb{K}}}\nor{\tau}_{\L}^2 + \nor{\div \tau}_{\L}^2
\]
where $\alpha \in [\epsilon,1]$ was selected in such a way that optimal test functions over a single element did not contain boundary layers\footnote{Boundary layers can appear in the cross-stream direction if $\alpha$ is not the same order as $\epsilon/h^2$, where $h$ is the element size.  This is explained in more detail in \cite{ChanHeuerBui-ThanhDemkowicz12}} which are difficult to approximate using our enriched space.

However, in \cite{globalLocalDPG}, it was shown that the global test space made up of the union of local test spaces contains the test subspace of weakly conforming test functions that are the result of solving for optimal test functions globally using a weakly conforming enriched space (which we refer to as the \textit{global test space}).  Furthermore, the field solutions for the DPG method are dependent only upon the properties of the global test space.

In other words, the resolution of boundary layers that occur at element boundaries is not important unless these boundary layers appear in globally determined test functions too (boundary layers that appear on element boundaries but not at a global level can be considered a negligible side-effect of the ``localization" of problems for optimal test functions).  Numerical experiments indicate

For these problems, we consider the Erikkson-Johnson model problem setup - the domain is a unit square in 2D, with $\beta = \LRp{1,0}$.  We computed global test functions corresponding to global field basis functions $1, xy, x(1-x)y(1-y)$ - a constant basis function, a bilinear basis function, and a quadratic bubble - as well as basis functions restricted to a small element in the middle of the domain for both $\alpha = \epsilon$ (where $\epsilon = .01$) and $\alpha = 1$.  No boundary layers were observed in either case, and the test functions under both test norms are very similar.

\begin{figure}
\centering
\subfigure[$\alpha = \epsilon$]{\includegraphics[scale=.475]{figs/aEpsConstant.png}}
\subfigure[$\alpha = 1$]{\includegraphics[scale=.475]{figs/aOneConstant.png}}
\caption{Optimal test functions for a $u=1$.}
\end{figure}

\begin{figure}
\centering
\subfigure[$\alpha = \epsilon$]{\includegraphics[scale=.475]{figs/aEpsBilinear.png}}
\subfigure[$\alpha = 1$]{\includegraphics[scale=.475]{figs/aOneBilinear.png}}
\caption{Optimal test functions for a $u=xy$.}
\end{figure}

\begin{figure}
\centering
\subfigure[$\alpha = \epsilon$]{\includegraphics[scale=.475]{figs/aEpsBubble.png}}
\subfigure[$\alpha = 1$]{\includegraphics[scale=.475]{figs/aOneBubble.png}}
\caption{Optimal test functions for a $u=x(1-x)y(1-y)$.}
\end{figure}

\begin{figure}
\centering
\subfigure[$\alpha = \epsilon$]{\includegraphics[scale=.475]{figs/aEpsElement.png}}
\subfigure[$\alpha = 1$]{\includegraphics[scale=.475]{figs/aOneElement.png}}
\caption{Optimal test functions for a $u=\left.1\right|_K$, where $K = [.5,.7]\times[.4,.6]$.}
\end{figure}
\newpage
\section{Convection-diffusion equation with first-order term}

Very often, the convection-diffusion equation includes a first-order term, such that the form of the equation is
\[
\div\LRp{\beta u - \epsilon \grad u} + \alpha v = f
\]
where $\alpha$ is some constant or function.
%The form of the first order system is 
%\begin{align*}
%\div\LRp{\beta u - \sigma} + \alpha v &= f\\
%\frac{1}{\epsilon}\tau - \grad u &= 0.
%\end{align*}
This first-order term represents a reaction term, modeling production of the solvent $u$.  Most commonly, however, this first order term appears in context of implicit time-stepping methods for the transient convection-diffusion equation
\[
\pd{u}{t}+\div\LRp{\beta u - \epsilon \grad u} = f.
\]
For implicit time-stepping methods, we solve for the solution at the current timestep $u_{t_i} \coloneqq u$ under some approximation of the time derivative: for example, implict Euler uses the first order approximation $\pd{u}{t} \approx \frac{u-u_{t_{i-1}}}{dt}$, introducing a reaction term $u/dt$
\[
\frac{u}{dt}+\div\LRp{\beta u - \epsilon \grad u} = f + \frac{u_{t_{i-1}}}{dt}.
\]
Under this version of the convection-diffusion equation, we modify our test norm to match the magnitude of the first order term $u/dt$
\[
\nor{v,\tau}_V^2 \coloneqq \frac{1}{dt}\nor{v}_{\L}^2 + \nor{\beta\grad v}_{\L}^2 + \epsilon \nor{\grad v}_{\L}^2 + \nor{\tau}_{\L}^2 + \nor{\div \tau}_{\L}^2.
\]
Noting that, according to the previous numerical experiments, the magnitude of the $\L$ term does not appear to create boundary layers in test functions for field variables.  Thus, so long as the $\frac{1}{dt}$ is $O(h)$, the mesh size, we should expect (by a transformation to the unit element) optimal test functions to be locally resolvable using our enriched space.

Recall that proving robustness involves showing energy estimates on the following adjoint equation
\[
\frac{1}{dt}v - \beta\cdot \grad v - \epsilon\del v = u - \epsilon\div \sigma
\]
where $u, \sigma \in \L$ represent functions from the trial space.  
\begin{lemma}
$\frac{1}{dt}\nor{v}_{\L}^2 + \epsilon \nor{\grad v}_{\L}^2 \lesssim \nor{u}_{\L}^2 + \nor{\sigma}_{\L}^2.$
\end{lemma}
\begin{proof}
Multiplying the equation by $v$ and integrating gives
\[
\int \frac{1}{dt} v^2 - \int \beta \cdot \grad v v -  \int \epsilon \del v v = \int u v -  \int \epsilon \div \sigma v.
\]
Integration by parts gives
\[
\frac{1}{dt} \nor{v}^2 + \int \frac{\div \beta}{2} v^2 - \int_\Gamma \frac{\beta_n}{2}v^2 + \epsilon \nor{\grad v}^2 - \epsilon \int_\Gamma v\pd{v}{n}  = \int uv + \int \sigma \epsilon \grad v  - \epsilon \int_\Gamma \sigma_n v
\]
Applying adjoint boundary conditions 
\begin{align*}
v &= 0, \quad \text{on } \Gamma_{\rm out}\\
\pd{v}{n} &= \sigma_n, \quad \text{on } \Gamma_{\rm in}
\end{align*}
reduces this to
\[
\frac{1}{dt} \nor{v}^2 + \int \frac{\div \beta}{2} v^2 + \int_{\Gamma_{\rm in}} \frac{|\beta_n|}{2}v^2 + \epsilon \nor{\grad v}^2 = \int uv + \int \sigma \epsilon \grad v.
\]
An application of Young's inequality on the right hand side completes the proof.  
\end{proof}
If we multiply by $\frac{1}{dt}v$ instead of $v$, we can derive a slightly different bound
\begin{lemma}
$\nor{\frac{1}{dt}v}_{\L}^2 + \frac{\epsilon}{dt} \nor{\grad v}_{\L}^2 \lesssim \nor{u}_{\L}^2 + \nor{\sigma}_{\L}^2$.
\end{lemma}
\begin{proof}
The proof is very similar to the above case. 
\end{proof}
\section{Non-robustness in traces}

In \cite{DPGrobustness}, both the graph norm and the constructed test norm (which we refer to as the \textit{robust} test norm) are shown to satisfy the robust bound
\[
\LRp{\nor{u}_{\L}^2 + \nor{\sigma}_{\L}^2 + \epsilon^2\nor{\uh}_{H^{1/2}(\Gh)} + \epsilon\nor{\fnh}_{H^{-1/2}(\Gh)}}^{1/2} \lesssim \nor{\LRp{u,\sigma,\uh,\fnh}}_E
\]
where $\nor{\cdot}_E$ is the energy norm in which DPG is optimal.  The focus of this bound is the $\epsilon$ independence of the $\L$ norms on $u$ and $\sigma$; however, we have not addressed the issue of robustness of the traces $\uh$ and flux $\fnh$ and how it manifests in practice.

We examine a test problem, with $\Omega = [0,1]^2$.  Inflow conditions\footnote{$u-\epsilon\pd{u}{n}$ approximates $u$ for $\epsilon\ll 1$.  These conditions are set such that we are able to use the robust test norm described in \cite{ChanHeuerBui-ThanhDemkowicz12}.} are set such that
\begin{align*}
u \approx u-\epsilon\pd{u}{n} &= 0,\quad x = 0,\quad y \in [0,1],
\end{align*}
and wall boundary conditions are set to mimic a flat plate problem such that
\begin{align*}
%u &= 0,\quad x = 1,\quad y \in [.5,1],\\
u &= 0,\quad y = 0,\quad x \in [.5,1].
\end{align*}
Boundary conditions in the rest of the domain are set such that
\begin{align*}
\pd{u}{n} &= 0,\quad y = 1,\\
\pd{u}{n} &= 0,\quad y = 0,\quad x \in [0,.5].
\end{align*}
We examine the traces along $y=0$.  Recall that traces are discretized as traces of $H^1$-conforming trial functions; thus, whereas we expect convergence in the $\L$ norm for field variables, this is not true for the traces.  In particular, we observe, in the propagation of error, evidence of non-robustness in the trace variables.  
\begin{figure}
\centering
\includegraphics[scale=.4]{figs/CrossTraces.png}
%\subfigure[Cross-stream traces]{\includegraphics[scale=.3]{figs/CrossTraces.png}}
%\subfigure[Outflow traces]{\includegraphics[scale=.3]{figs/OutflowTraces.png}}
%\caption{Difference between outflow and cross-stream traces.}
\caption{$H^1$-type propagation of error along $y = 0$.}
\end{figure}

\section{Zero-mean scaling}

In \cite{DPGrobustness, ChanHeuerBui-ThanhDemkowicz12}, we proved the energy estimate
\[
\nor{v}^2_{\L} \lesssim \nor{u}^2_{\L} + \nor{\sigma}^2_{\L}
\]
which implied that including $\nor{v}$ could be included in the test norm $\nor{v,\tau}_V$ and produce a robust DPG method for convection-diffusion.  However, it is also possible to replace the $\L$ term with the first-order term 
\[
\frac{1}{h^2}\LRb{\int_K v}^2
\]
which is a scaled measure of the average of $v$ over an element.  By Holder's inequality, we have that 
\[
\LRb{\int_K v} \leq \LRb{\int_K v^2}^{\frac{1}{2}} \LRb{h^2}^{\frac{1}{2}}, 
\]
implying that 
\[
\frac{1}{h^2}\LRb{\int_K v}^2 \leq \nor{v}^2_{\L}
\]
For the locally conservative version of DPG, we were able to replace $\nor{v}^2_{\L}$ in the test norm with $\frac{1}{h^4}\LRb{\int_K v}^2$, because in context of local conservation (enforced by Lagrange multipliers), elementwise constants are already enforced to be in the test space, so the addition of the mean-squared term to the test norm is solely to enforce a scaling condition enforcing a zero-mean condition on the remainder of the test functions.

\section{Anisotropic refinement}

Isotropic adaptive mesh refinement has shown itself to be an effective way to resolve isolated solution features with large gradients, such as point singularities \cite{FindBabuskaPaper}; however, for the resolution of phenomena such as shocks or boundary layers, anisotropic mesh refinement can resolve solution features for a much lower cost per degree-of-freedom, due to the fact that boundary layers in $n$-dimensions are primarily phenomena supported over $n-1$ dimensions.

As a least squares method, DPG already includes a natural error indicator with which to drive adaptive mesh refinement.  To introduce anisotropic refinements, we need to introduce an anisotropy indicator in order to detect in which direction solution features are aligned.  In general, a test norm can be expressed as the sum of normed quantities, both scalar and vector valued.  If we restrict ourselves to quadrilateral elements for the moment, a general anisotropy indicator for DPG can be constructed by evaluating the $\L$ norms of the individual components of vector valued terms in the test norm.

Under the test norm discussed in \cite{ChanHeuerBui-ThanhDemkowicz12} for the convection-dominated diffusion problem, we can define $x$ and $y$ error contributions over a single element
\begin{align*}
e_{x,K} &= \epsilon \nor{\pd{v}{x}}_{L^2(K)}^2 + \nor{\tau_x}_{L^2(K)}^2 \\
e_{y,K} &= \epsilon \nor{\pd{v}{y}}_{L^2(K)}^2 + \nor{\tau_y}_{L^2(K)}^2.
\end{align*}
We define the anisotropy indicator as the ratio $r_K = \frac{e_{x,K}}{e_{y,K}}$, and implement a simple refinement scheme following \cite{DPG3}.  Given some anisotropic threshold $\epsilon_r$, if $r_K>\epsilon_r$, then we can conclude that the error in the $x$ direction is large compared to the $y$ direction, and we anisotropically refine the element along the $x$-axis.  Likewise, if $r_K < \frac{1}{\epsilon_r}$, this implies that the opposite is true, and we refine the element anisotropically along the $y$-axis.

We note that it is possible to compute the discrete system without needing much additional integration.  Recall that if we let $G$ be the SPD Gram matrix representing the inner product $\LRp{v,\delta v}_V$ on $V_h$, we solve for degrees of freedom $c_e$ representing our error representation function $e$.

For both the graph and robust test norms, we can decompose the inner product that induces the test norm into 
\[
\LRp{v,\delta v}_V = \sum_i \LRp{v,\delta v}_{V,x_i} + \LRp{v,\delta v}_{V,{\rm scalar}}
\]
such that $\LRp{v,\delta v}_{V,x_i}$ is a seminorm containing the $i$th coordinate component of a vector-valued test term, and $\LRp{v,\delta v}_{V,{\rm scalar}}$ is simply the non-vector portions of the test norm.  For example, if we take the $H^1(\Omega)$ Sobolev norm
\[
\LRp{v,\delta v}_V = \LRp{v,\delta v}_{\L} + \LRp{\grad v,\grad \delta v}_{\L}
\]
then $\LRp{v,\delta v}_{V,x_i} = \LRp{\pd{v}{x_i},\pd{\delta v}{x_i}}_{\L}$, and $\LRp{v,\delta v}_{V,{\rm scalar}} = \LRp{v,\delta v}_{\L}$.  Each bilinear term $\LRp{v,\delta v}_{V,x_i}$ induces a symmetric positive-semidefinite matrix $G_{x_i}$, such that 
\[
c_e^TG_{x_i}c_e = \nor{e}^2_{V,x_i}.
\]
By storing $G$ as the sum of $G_{\rm scalar}$ and $G_{x_i}$, we can then cheaply compute the anisotropic error indicators once we have the degrees of freedom corresponding to our error representation function.

%\section{Conditioning}
%
%Our test norm for convection-diffusion has been
%\[
%\nor{v,\tau}_V^2 \coloneqq \alpha\nor{v}_{\L}^2 + \nor{\beta\grad v}_{\L}^2 + \epsilon \nor{\grad v}_{\L}^2 + {\min}\LRc{\frac{1}{\epsilon},\frac{1}{\LRb{K}}}\nor{\tau}_{\L}^2 + \nor{\div \tau}_{\L}^2
%\]
%We can see that, when forming the Gram matrix (the discrete Riesz operator) associated with the inner product generating this norm, the $v$ and $\tau$ terms decouple.  
%\begin{align*}
%\nor{v}_V^2 &\coloneqq \alpha\nor{v}_{\L}^2 + \nor{\beta\grad v}_{\L}^2 + \epsilon \nor{\grad v}_{\L}^2 = O(h) + O(1) + O(\epsilon)\\
%\nor{\tau}_V^2 &\coloneqq{\min}\LRc{\frac{1}{\epsilon},\frac{1}{\LRb{K}}}\nor{\tau}_{\L}^2 + \nor{\div \tau}_{\L}^2 = O(
%\end{align*}

\section{Plate problem}
\begin{itemize}
\item Non-local behavior: refinements away from plate edge affect downstream values
\item Singularities under robust norm: at $h = O(\epsilon)$, for smaller $\epsilon$, singularities in the field variables (even for $u$) develop at the plate edge (loss of control over $\sigma$?)  
\item Graph norm avoids the above issues with singularity in field solutions.  
\item Can we mix graph norm + robust norm somehow?  Maybe smoothly mix as $h\rightarrow h_{\min}$?
\item Flux limiters at singularity?
\end{itemize}

\bibliographystyle{plain}
\bibliography{paper}

\end{document}

### 2013-05-01 docs/Jesse/HeuerPaper/paper.tex

@@
-%&pdflatex
 \documentclass[11pt,onecolumn]{scrartcl}
@@
 Taking $g=1$ (corresponding to a piecewise constant approximation) we can solve \eqref{adjoint_1D} exactly.
-\begin{figure}[!h]
+\begin{figure}
 \centering
-\includegraphics[scale=.5]{figs/testBoundary1D.png}
+\includegraphics[scale=.5]{figs/testBoundary1D.eps}
 \caption{$v_1(x) = \frac{e^{-\frac{x}{\epsilon}}}{e^{\frac{1}{\epsilon}}-1}\left(e^{\frac{1}{\epsilon}}\left(e^{\frac{x}{\epsilon}}-1\right) + \left(e^{\frac{1}{\epsilon}}-1\right)e^{\frac{x}{\epsilon}}x\right)$, the solution to the adjoint equation for $f=0$ and constant $\beta$ and load $g$ for $\epsilon = .01$.}
@@
 
-\begin{figure}[h!]
+\begin{figure}
 \centering
-\subfigure[Primal problem, Dirichlet inflow BC]{\includegraphics[scale=.3]{figs/primalDir.png}}
-\subfigure[Adjoint problem, Dirichlet inflow BC]{\includegraphics[scale=.3]{figs/adjointDir.png}}
-\subfigure[Primal problem, new inflow BC]{\includegraphics[scale=.3]{figs/primal.png}}
-\subfigure[Adjoint problem, new inflow BC]{\includegraphics[scale=.3]{figs/adjoint.png}}
+\subfigure[Primal problem, Dirichlet inflow BC]{\includegraphics[scale=.375]{figs/primalDir.eps}}
+\subfigure[Adjoint problem, Dirichlet inflow BC]{\includegraphics[scale=.375]{figs/adjointDir.eps}}
+\subfigure[Primal problem, new inflow BC]{\includegraphics[scale=.375]{figs/primal.eps}}
+\subfigure[Adjoint problem, new inflow BC]{\includegraphics[scale=.375]{figs/adjoint.eps}}
 \caption{Comparison of primal and adjoint problems under both the standard Dirichlet and the new inflow boundary condition.
 The outflow boundary for each problem is denoted in red.
-For the standard Dirichlet inflow condition, the solution to the adjoint problem can develop strong boundary layers at the outflow of the adjoint problem.
-Notice, under the new inflow conditions, the relaxation of a wall-stop boundary condition with a zero-stress condition at the outflow boundary of the adjoint problem.}
+For the Dirichlet inflow condition, adjoint solutions can develop boundary layers at the outflow of the adjoint problem.
+Under the new inflow conditions, the wall-stop boundary condition is relaxed to a zero-stress condition at the adjoint outflow.}
 \end{figure}
@@
 \subfigure{
-\includegraphics[scale=.38]{figs/errorrates_wallBC.png}
+\includegraphics[scale=.38]{figs/errorrates_wallBC.eps}
 }
 \subfigure{
-\includegraphics[scale=.38]{figs/L2energyratio_wallBC.png}
+\includegraphics[scale=.38]{figs/L2energyratio_wallBC.eps}
 }
@@
 \subfigure{
-\includegraphics[scale=.38]{figs/roundoff_rates.png}
+\includegraphics[scale=.38]{figs/roundoff_rates.eps}
 }
 \subfigure{
-\includegraphics[scale=.38]{figs/roundoff_ratio.png}
+\includegraphics[scale=.38]{figs/roundoff_ratio.eps}
 }
@@
 \subfigure{
-\includegraphics[scale=.38]{figs/rates_noSigma.png}
+\includegraphics[scale=.38]{figs/rates_noSigma.eps}
 }
 \subfigure{
-\includegraphics[scale=.38]{figs/ratio_noSigma.png}
+\includegraphics[scale=.38]{figs/ratio_noSigma.eps}
 }
@@
 \subfigure{
-\includegraphics[scale=.38]{figs/rates_disc.png}
+\includegraphics[scale=.38]{figs/rates_disc.eps}
 }
 \subfigure{
-\includegraphics[scale=.38]{figs/ratio_disc.png}
+\includegraphics[scale=.38]{figs/ratio_disc.eps}
 }

### 2013-05-01 docs/Jesse/Rice talk/extendedSlides.tex

--- 2012-09-06 docs/Jesse/Proposal/boeingPres.tex
@@
-\documentclass[compress]{beamer}
-\mode<presentation>
-\usetheme{Warsaw}
-\usecolortheme{seagull}
-%\useoutertheme[subsection=false]{smoothbars}
-\useoutertheme{infolines}
-\useinnertheme{rectangles}
-
-\setbeamercovered{dynamic}
-
-\usepackage{array}
-\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
-\usepackage[utf8]{inputenc}
-\usepackage{listings}
-\usepackage{mathtools}
-\usepackage{dsfont}
-\usepackage{pdfpages}
-\usepackage[textsize=footnotesize,color=green]{todonotes}
-\usepackage{algorithm, algorithmic}
-\usepackage{bm}
-\usepackage{tikz}
-\usepackage[normalem]{ulem}
-
-\usepackage{graphicx}
-\usepackage{subfigure}
-%\usepackage{caption}
-%\usepackage{subcaption}
-
-\usepackage{color}
-\usepackage{undertilde}
-\usepackage{pdflscape}
-\usepackage{pifont}
-
-\usepackage{bibentry}
-\nobibliography*
-
-%\usepackage[osf]{mathpazo}
-%\usepackage{mathpazo}
-%\renewcommand\rmdefault{ptm}
-
-\renewcommand{\topfraction}{0.85}
-\renewcommand{\textfraction}{0.1}
-\renewcommand{\floatpagefraction}{0.75}
-
-\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
-\newcommand{\tensor}[1]{\underline{\vect{#1}}}
-\newcommand{\del}{\triangle}
-\newcommand{\grad}{\nabla}
-\newcommand{\curl}{\grad \times}
-\renewcommand{\div}{\grad \cdot}
-\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
-\newcommand{\eip}[1]{a\left( #1 \right)}
-\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
-\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
-
-\newcommand{\circone}{\ding{192}}
-\newcommand{\circtwo}{\ding{193}}
-\newcommand{\circthree}{\ding{194}}
-\newcommand{\circfour}{\ding{195}}
-\newcommand{\circfive}{\ding{196}}
-
-\newcommand{\Reyn}{\rm Re}
-
-\newcommand{\bs}[1]{\boldsymbol{#1}}
-\DeclareMathOperator{\diag}{diag}
-
-\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}
-
-\newcommand{\tablab}[1]{\label{tab:#1}}
-\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
-
-\newcommand{\theolab}[1]{\label{theo:#1}}
-\newcommand{\theoref}[1]{\ref{theo:#1}}
-\newcommand{\eqnlab}[1]{\label{eq:#1}}
-\newcommand{\eqnref}[1]{\eqref{eq:#1}}
-\newcommand{\seclab}[1]{\label{sec:#1}}
-\newcommand{\secref}[1]{\ref{sec:#1}}
-\newcommand{\lemlab}[1]{\label{lem:#1}}
-\newcommand{\lemref}[1]{\ref{lem:#1}}
-
-\newcommand{\mb}[1]{\mathbf{#1}}
-\newcommand{\mbb}[1]{\mathbb{#1}}
-\newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\nor}[1]{\left\| #1 \right\|}
-\newcommand{\snor}[1]{\left| #1 \right|}
-\newcommand{\LRp}[1]{\left( #1 \right)}
-\newcommand{\LRs}[1]{\left[ #1 \right]}
-\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
-\newcommand{\LRc}[1]{\left\{ #1 \right\}}
-\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
-\newcommand{\Grad} {\ensuremath{\nabla}}
-\newcommand{\Div} {\ensuremath{\nabla\cdot}}
-\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
-\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
-\newcommand{\uh}{\widehat{u}}
-\newcommand{\fnh}{\widehat{f}_n}
-\renewcommand{\L}{L^2\LRp{\Omega}}
-\newcommand{\pO}{\partial\Omega}
-\newcommand{\Gh}{\Gamma_h}
-\newcommand{\Gm}{\Gamma_{-}}
-\newcommand{\Gp}{\Gamma_{+}}
-\newcommand{\Go}{\Gamma_0}
-\newcommand{\Oh}{\Omega_h}
-
-\newcommand{\eval}[2][\right]{\relax
-  \ifx#1\right\relax \left.\fi#2#1\rvert}
-
-\def\etal{{\it et al.~}}
-
-\def\arr#1#2#3#4{\left[
-\begin{array}{cc}
-#1 & #2\\
-#3 & #4\\
-\end{array}
-\right]}
-\def\vecttwo#1#2{\left[
-\begin{array}{c}
-#1\\
-#2\\
-\end{array}
-\right]}
-\def\vectthree#1#2#3{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-\end{array}
-\right]}
-\def\vectfour#1#2#3#4{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-#4\\
-\end{array}
-\right]}
-
-\newcommand{\G} {\Gamma}
-\newcommand{\Gin} {\Gamma_{in}}
-\newcommand{\Gout} {\Gamma_{out}}
-
-% removes nav symbols
-\beamertemplatenavigationsymbolsempty
-
-% defines newblock as null, giving compile issues otherwise
-\let\newblock\relax
-
-\institute[ICES]{Institute for Computational Engineering and Sciences}
-
-\title[A DPG method for Compressible Flow]{A Discontinuous Petrov-Galerkin method for compressible flow problems}
-\date{August 15, 2012}
-\author[J. Chan, T. Ellis, L. Demkowicz, R. Moser]{Jesse Chan, Truman Ellis \\ Supervisors: Leszek Demkowicz, Robert Moser}
-
-\begin{document}
-\begin{frame}
-\maketitle
-\end{frame}
-
-\frame{
-\frametitle{Compressible Navier-Stokes equations}
-\begin{columns}[c]
-\begin{column}{.475\textwidth}
-Numerical difficulties:
-\begin{itemize}
-\item{} Resolving solution features (sharp, localized viscous-scale phenomena)
-\begin{itemize}
-\item{} Shocks
-\item{} Boundary layers - resolution needed for drag/load
-\item{} Turbulence (non-localized)
-\end{itemize}
-\item{} Nonlinear convergence and uniqueness of solutions
-\item{} Stability of numerical schemes
-\begin{itemize}
-\item{} Coarse/adaptive grids
-\item{} Higher order
-\end{itemize}
-\end{itemize}
-\end{column}
-\begin{column}{.475\textwidth}
-\begin{figure}
-\centering
-\includegraphics[scale = .7]{figs/compFlowPics/airfoil_mesh.png}
-\end{figure}
-\end{column}
-\end{columns}
-\vspace{.2cm}
-\begin{center}
-Idea: begin first with the model problem of convection-diffusion.
-\end{center}
-}
-\frame{
-\frametitle{Robustness: convection-diffusion as a model problem}
-\vspace{-.5cm}
-\[
-\div \left(\beta u\right) - \epsilon \Delta u = f, \quad \text{on }\Omega \in \mathbb{R}^3
-\]
-\vspace{-.5cm}
-\begin{columns}[c]
-\begin{column}{.49\textwidth}
-In 1D: $\beta u' - \epsilon u'' = f$. Standard continuous Galerkin variational formulation: solve
-\[
-b(u,v) = \ell(v), \quad u,v\in H^1_0([0,1])
-\]
-where
-\begin{align*}
-b(u,v) &= \int_\Omega -\beta uv' + \epsilon u'v' \\
-\ell(v) &= \int_\Omega f v 
-\end{align*}
-\end{column}
-\begin{column}{.49\textwidth}
-\begin{figure}
-\centering
-\includegraphics[scale=.35]{figs/GalerkinOscTight.png}
-\caption{Solution for $f=1$. Oscillations in the standard Galerkin method for large Peclet numbers ${\rm Pe} \coloneqq \frac{h}{\epsilon}$.}
-\end{figure}
-\end{column}
-\end{columns}
-}
-
-\frame{
-\frametitle{Streamline-upwind Petrov-Galerkin (SUPG)}
-SUPG solves $b_{\rm SUPG}(u,v) = l_{\rm SUPG}(v)$, where
-\begin{align*}
-b_{\rm SUPG}(u,v) &= b(u,v)+ \sum_{K} \int_{K} \tau \LRp{L_{\rm adv} v} L u \\
-l_{\rm SUPG}(v) &= \ell(v) + \sum_{K} \int_{K} \tau \LRp{L_{\rm adv}v} f.
-\end{align*}
-\vspace{-.5cm}
-\begin{columns}[c]
-\begin{column}{.44\textwidth}
-\vspace{-.5cm}
-\begin{itemize}
-\item{} $Lu = \div\left(\beta u\right) - \epsilon \triangle u$, $L_{\rm adv}u = \div \left(\beta u\right)$, and $\tau$ is a parameter. 
-%\item{} Recovers ``exact'' artificial diffusion for $f=0$.
-\item{} Effective for $f\neq 0$. %``exact'' artificial diffusion.
-\item{} \emph{Residual-based} stabilization. 
-\end{itemize}
-\end{column}
-\begin{column}{.54\textwidth}
-\begin{figure}
-\centering
-\includegraphics[scale=.38]{figs/SUPG.png}
-%\caption{Exact, Bubnov-Galerkin, and SUPG solutions.}
-\end{figure}
-\end{column}
-\end{columns}
-}
-
-\frame{
-\begin{columns}
-\begin{column}{.49\textwidth}
-Can be interpreted as a \emph{Petrov-Galerkin} method,
-\[
-b\LRp{u,\tilde{v}_{i}} = \ell\LRp{\tilde{v}_{i}}, \quad \forall i = 1,\ldots,N-1,
-\]
-where the SUPG test function $\tilde{v}_{i}$ is defined elementwise as\footnotemark
-\[
-\tilde{v}_{i} = \phi_i(x) + \tau L_{\rm adv} \phi_i.  
-\]
-\end{column}
-\begin{column}{.49\textwidth}
-\begin{figure}
-\centering
-\subfigure{\includegraphics[scale=.16]{figs/SUPGtest.png}}
-\caption{SUPG test function $v_i$.}
-\end{figure}
-\end{column}
-\end{columns}
-\footnotetext{\bibentry{SUPG}}
-}
-
-\section{The DPG Method}
-\frame{
-\frametitle{DPG: a minimum residual method via optimal testing}
-Given a trial space $U$ and Hilbert test space $V$,
-\[
-b(u,v) = \ell(v), \quad u\in U, \quad v\in V
-\]
-This is equivalent to the operator equation posed in $V'$
-\[
-Bu = \ell
-\]
-if we identify $B:U\rightarrow V'$ and $\ell\in V'$ such that 
-\begin{align*}
-\langle Bu,v\rangle_V &\coloneqq b(u,v), \quad u\in U, v\in V,\\
-\langle \ell,v\rangle_V &\coloneqq \ell(v), \quad v\in V.
-\end{align*}
-We seek to minimize the dual functional over $U_h \subset U$
-\[
-J(u_h) = \frac{1}{2}\|Bu_h-\ell\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(u_h,v)-\ell(v)|^2}{\nor{v}_V^2}.
-\]
-}
-
-\begin{frame}
-Let $R_V: V \to V'$ be the isometric Riesz map st.\
-\[
-\langle R_V v,\delta v\rangle_V \coloneqq(v, \delta v)_V, \quad \forall \delta v \in V.
-\]
-Then, our functional $J(u_h)$ is equal to
-\begin{equation*}
-\min_{u_h\in U_h} J(u_h) = \frac{1}{2}\left\|Bu_h-\ell\right\|_{V'}^2 =  \frac{1}{2}\left\|R_V^{-1}(Bu_h-\ell)\right\|_V^2.
-\end{equation*}
-First order optimality: G\^ateaux derivative is zero in all directions $\delta u \in U_h$
-\begin{align*}
-\left(R_V^{-1}(Bu_h-\ell),R_V^{-1}B\delta u\right)_V &= 0, \quad \forall \delta u \in U_h.\\
-\rightarrow \LRa{(Bu_h-\ell),R_V^{-1}B\delta u} &= 0, \\
-\rightarrow b(u_h,R_V^{-1}B\delta u) - \ell(R_V^{-1}B\delta u) &= 0
-\end{align*}
-\end{frame}
-
-\frame{
-\frametitle{Summary: select test functions to minimize residuals}
-For $\delta u \in U_h$, define the \textcolor{red}{optimal test function} $v_{\delta u}$. 
-\begin{equation*}
-v_{\delta u} \coloneqq R_V^{-1}B\delta u.
-\end{equation*} 
-Then, the residual $J(u_h) = \frac{1}{2}\left\|Bu_h-\ell\right\|_{V'}^2$ is minimized by the solution of
-\[
-b\LRp{u_h,v_{\delta u}} = \ell\LRp{v_{\delta u}}, \quad \forall \delta u \in U_h.
-\]
-}
-
-\frame{
-\frametitle{Practical details of DPG}
-Computation of $v_{\delta u} \coloneqq R_V^{-1}B\delta u$ is \textbf{global} and \textbf{infinite-dimensional}.
-\begin{itemize}
-\item By choosing a \textcolor{red}{broken} test space $V$ and \textcolor{red}{localizable} norm $\nor{v}_V^2 = \sum_K \nor{v}_{V(K)}^2$, test functions can be determined locally.
-\item In practice, we use an \textcolor{red}{enriched space} $V_h \subset V$, where $\dim(V_h) > \dim(U_h)$ elementwise, and \textcolor{red}{optimal test functions} are approximated by computing $v_{\delta u} \coloneqq R_{V_h}^{-1}B\delta u \in V_h$ through\footnote{\bibentry{DPG2}}
-\[
-\LRp{v_{\delta u},\delta v}_V = b(\delta u,\delta v), \quad \delta u\in U_h, \quad \forall \delta v\in V_h
-\]
-Typically, if $U_h = \mathcal{P}^p(\mathbb{R}^n)$, $V_h = \mathcal{P}^{p+\triangle p}(\mathbb{R}^n)$, where $\triangle p \geq n$.\footnote{\bibentry{practicalDPG}} 
-\end{itemize}
-%\footnotetext{\bibentry{DPG2}}
-}
-
-\frame{
-\frametitle{Properties of DPG}
-DPG provides a symmetric positive-definite stiffness matrix. Let $\{\phi_j\}_{j=1}^m$ be a basis for $U_h$, and $\{v_i\}_{i=1}^n$ a basis for $V_h$, such that $n>m$. Then, for 
-\begin{align*}
-B_{ji} &= b(\phi_j,v_i),\\
-l_i &= \ell(v_i),
-\end{align*}
-DPG solves the discrete system for degrees of freedom $u$
-\begin{align*}
-\LRp{B^T R_V^{-1}B} u  &= \LRp{B^T R_V^{-1}} l,
-\end{align*}
-where, under a localizable norm and discontinuous test functions, $R_V^{-1}$ is block diagonal.
-}
-
-\frame{
-\frametitle{Properties of DPG}
-Additional properties of DPG include\footnotemark
-\begin{itemize}
-\item DPG provides the best approximation in the \textcolor{red}{energy norm}
-\[
-\|u\|_E = \|Bu\|_{V'} = \sup_{\nor{v}_V=1} \left|b(u,v)\right|.
-\]
-\item The energy error is computable through the residual
-\[
-\nor{u-u_h}_E = \nor{B(u-u_h)}_{V'} = \nor{R_V^{-1}(l-Bu_h)}_V = \nor{e}_V
-\]
-where the \textcolor{red}{error representation function} $e$ is defined through $(e,\delta v)_V = \ell(v)-b(u_h,\delta v)$ for all $\delta v\in V$. 
-\end{itemize}
-\footnotetext{\bibentry{DPG3pub}}
-}
+\section{Extended slides}
 
 %\frame{
-%\frametitle{Duality of norms}
-%Duality of norms: for any trial norm $\nor{u}_U$,
+%\frametitle{Specifics of the ultra-weak formulation}
+%
+%Given a first order system $Au = f$, multiply by test function $v$ and integrate 
 %\[
-%\nor{u}_{U} = \sup_{v \in V}\frac{b\LRp{u,v}}{\nor{v}_{V,U}}, \quad \nor{v}_{V,U} = \sup_{u \in U}\frac%{b\LRp{u,v}}{\nor{u}_{U}}.
+%\LRp{Au,v} = \LRa{\gamma\LRp{Au},v} + \LRp{u,A^*_hv} = \LRp{f,v}
 %\]
-%Likewise, for any test norm $\nor{v}_V$, 
-%\[
-%\nor{v}_{V} = \sup_{u \in U}\frac{b\LRp{u,v}}{\nor{U}_{U,V}}, \quad \nor{u}_{U,V} = \sup_{v \in V}\frac%{b\LRp{u,v}}{\nor{v}_{V}}.
-%\]
-%
-%}
-
-\frame{
-\frametitle{Ultra-weak formulation}
-\vspace{-.75cm}
-\begin{columns}
-\begin{column}{.64\textwidth}
-Given a first order system $Au = f$, we identify the \textbf{\emph{partition}} $\Oh$ and \textbf{\textcolor{red}{mesh skeleton}} \textcolor{red}{$\Gh$}.
-\end{column}
-\begin{column}{.34\textwidth}
-%\[
-%\Oh = \cup_{j=1}^\Nel K_j, \quad \Gh = \cup_{j=1}^\Nel \partial K_j
-%\]
-\begin{figure}[!h]
-\centering
-\includegraphics[scale = .155]{mesh_skel.pdf}
-\end{figure}
-\end{column}
-\end{columns}
-\vspace{-.5cm}
-The ultra-weak formulation for $Au = f$ on $\Oh$ is
-\[
-b\left(\left(u, \widehat{u}\right),v\right) \coloneqq \sum_K\langle \widehat{u},v \rangle_{\partial K} + (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh}.
-\]
-Under proper assumptions, $\sum_K\langle \widehat{u},v \rangle_{\partial K} = \langle \widehat{u}, \jump{v} \rangle_{\Gh}$, with energy setting
-\[
-u\in L^2\LRp{\Oh} \equiv L^2(\Omega), \quad v\in V=D(A^*_h), \quad
-\widehat{u}\in \gamma(D(A)),
-\]
-where $D(A_h^*)$ is the broken graph space of the formal adjoint $A_h^*$, and $\gamma(D(A))$ the trace space of the graph space of operator $A$.\footnote{\bibentry{analysisDPG}}
-}
-
-\frame{
-\frametitle{The canonical ``graph'' test norm}
-Recall $\nor{u}_E \coloneqq \sup_{v\in V\setminus\{0\}}\frac{b(u,v)}{\nor{v}_V}$. Under the ultra-weak formulation, the trial norm 
-\[
-\nor{\LRp{u,\widehat{u}}}_U \coloneqq \|u\|^2_{\L} + \|\widehat{u}\|^2
-\] 
-generates a test norm \emph{equivalent} to 
-\[
-\nor{v}_{V_{\rm opt}} \coloneqq \|A_h^*v\|_{\L}^2 +\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},\jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2.
-\]
-This norm is not localizable, so we instead substitute the jump terms for an $L^2$ term, giving us the \emph{graph norm}\footnote{\bibentry{Bui-ThanhDemkowiczGhattas11b}}
-\[
-\nor{v}_V \coloneqq \|A_h^*v\|_{\L}^2 + \nor{v}_{L^2}.
-\]
-}
-
-\frame{
-\frametitle{Goal: robust higher order adaptive methods}
-\begin{columns}
-\begin{column}{.45\textwidth}
-Our aim is to design an adaptive method for compressible laminar flows that is 
-\begin{itemize}
-\item robust in Reynolds number
-\item stable for arbitrary elements
-\end{itemize}
-
-This proposal will outline
-\begin{enumerate}
-\item a robust DPG method for convection-diffusion,
-\item extension to nonlinear problems and systems,
-\item proposed work.
-\end{enumerate}
-
-\end{column}
-\begin{column}{.54\textwidth}
-\begin{figure}
-\centering
-\subfigure{\includegraphics[scale=.23]{figs/Re1000p2/u2_full.png}}
-\subfigure{\includegraphics[scale=.37]{figs/Re1000p2/mesh6.png}}
-\caption{$u_2$ and $p=2$ mesh for $\Reyn = 1000$.}
-\end{figure}
-\end{column}
-\end{columns}
-}
-
-\section{A Robust DPG Method for Convection-Diffusion}
-
-\frame{
-\frametitle{Ultra-weak formulation for convection-diffusion}
-In first order form, the convection-diffusion equation is
-\[
-A \LRp{u,\sigma} \coloneqq 
-\LRs {
-\begin{array}{c}
-\div (\beta u - \sigma) \\ \frac{1}{\epsilon}\sigma - \grad u
-\end{array}} = \LRs{
-\begin{array}{c}
-f \\ 0
-\end{array}
-}.
-\]
-The variational formulation is
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-\left( v, \tau \right)\right) = \left(u,\grad_h\cdot \tau - \beta \cdot \grad_h
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad_h v\right)_{\Oh}&\\
-  - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
-\end{align*}
-where $\widehat{f}_n \coloneqq \beta_n u - \sigma_n$ and $\LRa{\widehat{f}_n,\jump{v} }_{\Gh}$ is defined 
-\[
-\LRa{\widehat{f}_n,\jump{v} }_{\Gh}\coloneqq \sum_K\int_{\partial K}{\rm sgn}(\vec{n}) \, \widehat{f}_n v.
-\]
-}
-
-\frame{
-\frametitle{Graph norm under convection-diffusion}
-For convection-diffusion, the graph test norm is defined elementwise
-\[
-\|\left(v,\tau\right)\|_{V(K)}^2 = \| \div \tau - \beta \cdot \grad v
-\|_{L^2(K)}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2(K)}^2 +
-\|v\|_{L^2(K)}^2.
-\]
-Problem with this test norm: approximability of test functions.
-\vspace{-.3cm}
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.175]{figs/opt.png}
-\caption{$v$ and $\tau$ components of the 1D optimal test functions for flux $\widehat{f}_n$ on the \emph{right-hand} side of a unit element for $\epsilon = 0.01$. }
-\label{fig:optTestBoundary}
-\end{figure}
-}
-
-\frame{
-\frametitle{Determining an alternative test norm}
-Recall the convection-diffusion bilinear form
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh}&\\
- - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
-\end{align*}
-We recover $\nor{u}^2_{L^2(\Omega)}$ by choosing conforming $\LRp{v,\tau}$ satisfying the \emph{adjoint equations}
-\begin{align*}
-\div\tau - \beta \cdot \grad v   &= u\\
-\frac{1}{\epsilon}\tau + \grad v &= 0
-\end{align*}
-with boundary conditions s.t.\ $\LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gamma}$ and $\LRa{ \widehat{f}_n,\jump{v} }_{\Gamma}$ vanish.
-}
-
-\frame{
-\frametitle{A robust bound}
-``Necessary'' conditions for robustness --- let $\boldsymbol U = \LRp{u,\sigma,\widehat{u},\widehat{f}_n}$. Then, by choosing specific $\LRp{v,\tau}$ satisfying the adjoint equations,
-\[
-\nor{u}^2_{L^2(\Omega)} = b\LRp{{\boldsymbol U},\LRp{v,\tau}} = \frac{b\LRp{{\boldsymbol U},\LRp{v,\tau}}}{\nor{\LRp{v,\tau}}_V} \nor{\LRp{v,\tau}}_V \leq \nor{\boldsymbol U}_E \nor{\LRp{v,\tau}}_V
-\]
-Let $\lesssim$ denote a robust bound - \textcolor{red}{if $ \nor{\LRp{v,\tau}}_V \lesssim \|u\|_{L^2(\Omega)}$}, then we have that
-\[
-\nor{u}_{L^2(\Omega)} \lesssim \nor{\boldsymbol U}_E
-\]
-\textbf{Main idea: the \textcolor{red}{test norm} should measure \textcolor{red}{adjoint solutions} robustly.}
-}
-
-\frame{
-\frametitle{Choice of inflow boundary condition}
-
-\begin{columns}
-\begin{column}{.49\textwidth}
-We impose the standard outflow wall boundary condition on $u$. For inflow boundary condition: 
-\begin{itemize}
-\item{} The standard choice of inflow boundary condition: $u = u_0$.
-\item{} We impose the non-standard inflow condition: $\widehat{f}_n \coloneqq \beta_n u - \sigma_n \approx \beta_n u_0$ on $\Gamma_{\rm in}$.
-\end{itemize}
-\end{column}
-
-\begin{column}{.49\textwidth}
-\begin{figure}
-\includegraphics[scale=.23]{figs/primal.png}
-\caption{Non-standard inflow.}
-\end{figure}
-\end{column}
-\end{columns}
-When $\sigma_n \approx 0$ near the inflow, condition on $\widehat{f}_n$ approximates condition on $u$.
-
-}
-
-\frame{
-\frametitle{Dirichlet inflow boundary condition}
-Standard choice of boundary condition: $u = u_0$ on inflow boundary $\Gamma_{\rm in}$, induces boundary layers in adjoint problems, \textcolor{red}{$\nor{\beta\cdot \grad v}_{L^2} = O(\epsilon^{-1})$}.
-\begin{figure}[h!]
-\centering
-\subfigure[Primal problem]{\includegraphics[scale=.23]{figs/primalDir.png}}
-\subfigure[Adjoint problem]{\includegraphics[scale=.23]{figs/adjointDir.png}}
-\caption{For the standard Dirichlet inflow condition, the solution to the adjoint problem can develop strong boundary layers at the outflow of the adjoint problem. }
-\end{figure}
-}
-
-\frame{
-\frametitle{New inflow boundary condition on $\widehat{f}_n$}
-Non-standard choice of boundary condition: $\widehat{f}_n = \beta_n u_0$ on $\Gamma_{\rm in}$, induces smoother adjoint problems, \textcolor{red}{$\nor{\beta\cdot \grad v}_{L^2} = O(1)$}.
-\begin{figure}[h!]
-\centering
-\subfigure[Primal problem]{\includegraphics[scale=.23]{figs/primal.png}}
-\subfigure[Adjoint problem]{\includegraphics[scale=.23]{figs/adjoint.png}}
-\caption{Under the new inflow condition, the wall-stop boundary condition is relaxed to a zero-stress condition at the outflow boundary of the adjoint problem.}
-\end{figure}
-}
-
-\frame{
-\frametitle{Test norms and adjoint solutions}
-\textbf{Intuition:} the effectiveness of DPG under a test norm is governed by how a \textbf{specific test norm} measures the \textbf{solutions of the adjoint problem}.
-
-\begin{figure}[!h]
-\centering
-\subfigure[Dirichlet inflow]{\includegraphics[scale=.35]{figs/dirichletBC.png}}
-\subfigure[``Convection'' inflow]{\includegraphics[scale=.35]{figs/newBC.png}}
-\caption{DPG solutions to convection-diffusion for both inflow conditions using an $H^1$ test norm.}
-\end{figure}
-}
-
-%\frame{
-%\frametitle{``Building blocks'' norm}
-%Test norm quantities are robustly bounded from above by $\nor{u}_{L^2(\Omega)}$.  
-%\[
-%\|\left(v,\tau\right)\|_{V,K}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2.
-%\]
-%Problem: boundary layers in optimal test functions:
-%\begin{figure}[!h]
-%\centering
-%\subfigure{\includegraphics[scale=.15]{figs/mesh1.png}}
-%\subfigure{\includegraphics[scale=.15]{figs/sol1.png}}
-%\caption{The $v$ component of the optimal test function corresponding to flux $\widehat{u} = x(1-x)$ on the bottom side of a unit element for $\epsilon = 0.01$.}
-%\label{fig:boundaryTest}
-%\end{figure}
-%}
-\frame{
-\frametitle{Adjoint estimates, or ``norm building blocks''}
-For solutions $(v,\tau)$ of the adjoint equations, the following quantities are robustly bounded from above by $\nor{u}_{L^2(\Omega)}$.  
-\begin{align*}
-&\|v\|, \sqrt{\epsilon} \|\grad v\|, \|\beta \cdot \grad v\| \\
-&\| \div \tau\|, \frac{1}{\sqrt{\epsilon}}\|\tau\|.
-\end{align*}
-We will construct a test norm through a combination of the above quantities, such that
-\begin{itemize}
-\item $v$ and $\tau$ decoupled (no systems).
-\item Coefficients are of equal order after transforming to the unit element (no boundary layers).
-\end{itemize}
-}
-\frame{
-\frametitle{Mesh-scaled test norms}
-Our test norm, as defined over a single element $K$, is now
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 +&\\
-\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2&.
-\end{align*}
-which induces the proven \emph{robust} bound\footnote{\bibentry{DPGrobustness2}}
-\[
-\nor{u}_{L^2(\Omega)}+ \nor{\sigma}_{L^2(\Omega)} + \epsilon\nor{\widehat{u}} + \sqrt{\epsilon} \nor{\widehat{f}_n} \lesssim \nor{\LRp{u,\sigma,\widehat{u},\widehat{f}_n}}_E.
-\]
-}
-
-\frame{
-\frametitle{Erikkson-Johnson model problem}
-
-On domain $\Omega = [0,1]^2$, with $\beta = (1,0)^T$, $ f = 0$ and boundary conditions
-\begin{align*}
-\widehat{\beta_nu - \sigma_n} &= \widehat{f}_n = u_0, \quad \beta_n \leq 0\\
-\widehat{u} &= 0, \quad \beta_n > 0
-\end{align*}
-
-%Separation of variables gives an analytic solution. 
-All numerical experiments done using Camellia codebase.\footnote{\bibentry{Camellia}}
-%\[
-%u(x,y) = C_0 + \sum_{n=1}^\infty C_n \frac{\exp(r_2(x-1)-\exp(r_1(x-1)))}{r_1\exp(-r2) - r_2\exp(-r1)}\cos(n\pi y)
-%\]
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale=.23]{figs/wallBC_exact_u.png}
-}
-\subfigure{
-\includegraphics[scale=.23]{figs/wallBC_exact_sigx.png}
-}
-\subfigure{
-\includegraphics[scale=.23]{figs/wallBC_exact_sigy.png}
-}
-\caption{Exact solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
-\end{figure}
-}
-
-\frame{
-\frametitle{Error rates}
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale=.33]{figs/errorrates_wallBC.png}
-}
-\subfigure{
-\includegraphics[scale=.33]{figs/L2energyratio_wallBC.png}
-}
-%\subfigure{
-%\includegraphics[scale=.22]{figs/u_pointdiff_wallBC.png}
-%}
-\caption{$L^2$/energy errors and their ratio for $\epsilon = .01, .001, .0001$.}
-\end{figure}
-}
-
-%\frame{
-%\frametitle{Regularization}
-%Discontinuous inflow conditions on $\widehat{f_n}$, out of alignment with mesh. Boundary condition $\epsilon \grad u \cdot n = 0$ at outflow.
-%\begin{figure}
-%\centering
-%\subfigure{
-%\includegraphics[scale=.33]{figs/discontinuous.png}
-%}
-%\subfigure{
-%\includegraphics[scale=.305]{figs/discontinuousL2rates.png}
-%}
-%\caption{Discontinuous hat inflow data with $\epsilon = 1e-5$, convection solution errors.}
-%\end{figure}
+%If $u \in L^2\LRp{\Omega}$, the trace of $u$ is undefined, so we identify boundary terms $\LRa{\gamma\LRp{Au},v}_{\Gh} = \LRa{\widehat{u},v}_{\Gh}$ as unknowns $\widehat{u}$ on $\Gh$.
+For convection-diffusion,
+%\begin{align*}
+%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
+%\left( v, \tau \right)\right) = \left(u,\grad_h\cdot \tau - \beta \cdot \grad_h
+%v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad_h v\right)_{\Oh}&\\
+%  - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
+%\end{align*}
+%where 
+%\begin{align*}
+%\widehat{f}_n \coloneqq \beta_n u - \sigma_n \in H^{-1/2}(\Gh), \quad \widehat{u} \in H^{1/2}(\Gh)
+%\end{align*}
+%with the minimum energy extension norm on $\Gh$. We note that $H^{\pm 1/2}(\Gh)$ are \emph{closed} subspaces of $\prod_K H^{\pm 1/2}(\partial K)$. 
 %}
@@
 \frametitle{Local conservation}
-Given stiffness matrix $K$, can introduce Lagrange multipliers to enforce element-wise constraints, leading to the saddle point problem
+Given stiffness matrix $K$, can introduce Lagrange multipliers $\lambda$ to enforce element-wise constraints, leading to the saddle point problem\bibfoot{conservativeDPG} 
 \[
@@
 \]
-where the Lagrange multipliers $\lambda$ can be locally condensed. We use the test norm
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,K}^2 = \left|\int_K v\right|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 +&\\
-\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2&.
-\end{align*}
-}
-
-\frame{
-\frametitle{Additional examples}
+%Conservative DPG performs very similarly to standard DPG over a range of $\epsilon$.
 \begin{figure}
@@
 \end{figure}
-Locally conservative version of DPG performs very similarly to the standard DPG in all cases over a range of $\epsilon$. 
+}
+
+\frame{
+\frametitle{Inviscid equations}
+Issue: consider pure convection, $\div \beta u = f$. The ultra-weak variational formulation is
+\[
+\LRa{\widehat{f}_n,v}-\LRp{u,\beta\cdot \grad v} = \LRp{f,v},
+\]
+where $\widehat{f}_n \coloneqq \beta_n u$.
+When $\beta_n = 0$, $v$ has only a streamline derivative, and $\widehat{f}_n$ becomes an ill-defined trace in the cross-stream direction.
+For hyperbolic \emph{systems}, this issue manifests as \emph{sonic lines}.
+\begin{figure}
+\centering
+\includegraphics[scale=.25]{figs/sonicLines.pdf}
+\caption{Sonic lines ($u_n - c = 0$) appear for linearized Euler.}
+\end{figure}
 }
@@
 \frame{
-\frametitle{Current work - Hemker problem}
-
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale = .225]{figs/Conservative/Hemker/WithoutMesh.png}
+\frametitle{Anisotropic refinement scheme}
 }
-\subfigure{
-\includegraphics[scale = .225]{figs/Conservative/Hemker/WithMesh.png}
-}
-\caption{Convection-diffusion solution to flow over a cylinder at $\epsilon = 1e-4$.}
-\end{figure}
-}
-\frame{
-\frametitle{Current work - high-lift airfoil}
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale = .1875]{figs/Conservative/Airfoil-Conservative-1E-3/solution.png}
-}
-\subfigure{
-\includegraphics[scale = .175]{figs/Conservative/Airfoil-Conservative-1E-3/mesh7.png}
-}
-\caption{Convection-diffusion solution over the high-lift airfoil, with advection at an angle, $\epsilon = 1e-3$, with $p=3$. Mesh is generated by \emph{Triangle}.}
-\end{figure}
-}
-
-\section{DPG for nonlinear problems}
-\frame{
-\frametitle{DPG for nonlinear problems}
-
-Given some linearization technique (typically Newton-Raphson and pseudo-timestepping linearization), we measure 
-\begin{itemize}
-\item size of the linearized update $\Delta u$
-\[
-\|\Delta u\|_E \coloneqq \nor{B_u\Delta u}_{V'} = \nor{R_V^{-1} B_u\Delta u}_V 
-\]
-\item the nonlinear residual 
-\[
-\nor{R(u)}_E \coloneqq \nor{B(u) - \ell}_{V'}  = \nor{R_V^{-1}\LRp{B(u)-\ell}}_V 
-\]
-\end{itemize}
-Preliminary experiments were done in 1D\footnote{\bibentry{DPGNS_1d}} and space-time.\footnote{\bibentry{DPGspacetime}}
-}
-
-\frame{
-\frametitle{2D test case: Burgers equation}
-\begin{columns}
-\begin{column}{.48\textwidth}
-\vspace{-.5cm}
-\[
-\pd{\left(u^2/2\right)}{x} + \pd{u}{y} + \epsilon \Delta u = f
-\]
-Burgers equation can be written with $\beta(u) = \LRp{u/2,1}$
-\begin{align*}
-\div\left(\beta(u)u-\sigma\right) &=f \\
-\frac{1}{\epsilon}\sigma - \grad u &=0.
-\end{align*}
-i.e.\ nonlinear convection-diffusion on domain $[0,1]^2$.
-\end{column}
-\begin{column}{.48\textwidth}
-\begin{figure}[!h]
-\centering
-\includegraphics[scale = .22]{figs/burgers.png}
-\caption{Shock solution for Burgers' equation, $\epsilon = 1e-4$, using Newton-Raphson.}
-\end{figure}
-\end{column}
-\end{columns}
-}
-\frame{
-Adaptivity begins with a cubic $4\times 4$ mesh.
-\begin{figure}[!h]
-\centering
-\subfigure{\includegraphics[scale=.2]{figs/burgersMesh.png}}
-\subfigure{\includegraphics[scale=.2]{figs/burgersZoom.png}}
-\caption{Adaptive mesh after 9 refinements, and zoom view at point (.5,.5) with shock formation and $1e-3$ width line for reference.}
-\end{figure}
-}
-
-\frame{
-\frametitle{2D Compressible Navier-Stokes equations (ideal gas)}
-Given density $\rho$, velocities $\mathbf{u} = \LRp{u_1,u_2}$ and temperature $T$,
-\begin{align*}
-\div \vecttwo{\rho u_1 }{\rho u_2} &= 0\\
-\div \left(\vecttwo{\rho u_1^2+p }{\rho u_1 u_2} - \boldsymbol \sigma_{1}\right) &=0\\
-\div \left(\vecttwo{\rho u_1 u_2}{\rho u_2^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
-\div \left(\vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2} - \boldsymbol\sigma \mathbf{u} + \vec{q}\right) &=0\\
-\frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I &= \grad \mathbf{u} - \Reyn \, \boldsymbol w\\
-\frac{1}{\kappa}\vec{q} &= \grad T
-\end{align*}
-}
-
-\frame{
-\frametitle{Stress law}
-$\boldsymbol\sigma$ for a Newtonian fluid: $\sigma_{ij} = \mu(u_{i,j} + u_{j,i}) + \lambda u_{k,k} \delta_{ij}$.
-%We can invert the stress tensor under isotropic and plane strain assumptions to get
-\[
-\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \frac{1}{2\mu} \sigma_{ij} - \frac{\lambda}{4\mu (\mu + \lambda)} \sigma_{kk}\delta_{ij}
-\]
-The symmetric part of the gradient is
-\[
-\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \grad  U - \boldsymbol w
-\]
-Our final form is
-\begin{align*}
-\grad  U - \boldsymbol w= \frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I.
-\end{align*}
-By enforcing strong symmetry of $\boldsymbol \sigma$, taking the antisymmetric part implicitly defines $\boldsymbol w$ to be the antisymmetric part of $\grad u$. 
-}
-
-\frame{
-\frametitle{Extrapolation of test norms}
-%\begin{columns}
-%\begin{column}{.48\textwidth}
-Convection-diffusion:
-\begin{align*}
-\div \left(\beta u - \sigma\right) &= f\\
-\frac{1}{\epsilon}\sigma - \grad u &= 0.
-\end{align*}
-Navier-Stokes: defining vector variables $U = \{\rho,u_1,u_2,T\}$ and $\Sigma = \{{\boldsymbol \sigma},\mathbf{q},w\}$,
-\begin{align*}
-\div \left(A_{\rm invisc}U - A_{\rm visc}\Sigma\right) &= R_{\rm conserv}(U,\Sigma)\\
-E_{\rm visc} \Sigma - \grad U &= R_{\rm constit}(U,\Sigma)
-\end{align*}
-where $R_{\rm conserv}(U,\Sigma)$ and $R_{\rm constit}(U,\Sigma)$ are the conservation/constitutive residuals.
-}
-
-\frame{
-\frametitle{Test norms over one element}
-Convection-diffusion:
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,K}^2 =& \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \|\beta \cdot \grad v\|^2 + \epsilon \|\grad v\|^2  \\
-&+\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
-\end{align*}
-
-Navier-Stokes: let $V$ and $W$ be vectors of test functions $v_i$ and $\tau_i$.
-\begin{align*}
-\|\left(V,W\right)\|_{V,K}^2 =& \min\left\{\frac{1}{\Reyn|K|},1\right\}\nor{V}^2  + \nor{A_{\rm invisc}^T \grad V}^2 + \frac{1}{\Reyn} \nor{A_{\rm visc}^T\grad V}^2 \\
-& + \nor{\div W}^2 + \min\left\{1,\frac{1}{\Reyn|K|}\right\}\nor{E_{\rm visc}^TW}^2.
-\end{align*}
-}
-
-\frame{
-\frametitle{Carter's flat plate problem}
-\begin{columns}
-\begin{column}{.49\textwidth}
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.32]{figs/flat_plate_BCs.pdf}
-\caption{Carter flat plate problem on domain $[0,2]\times[0,1]$. Plate begins at $x=1$, ${\rm Re} = 1000$.}
-\end{figure}
-\end{column}
-\begin{column}{.49\textwidth}
-\begin{enumerate}
-\item{} Symmetry boundary conditions.
-\item{} Prescribed temperature and wall stagnation conditions.
-\item{} Symmetry boundary conditions.
-\item{} Inflow: conserved quantities specified using far-field values.
-\item{} No outflow condition set.
-\end{enumerate}
-Stress/heat flux boundary conditions are set in terms of the momentum and energy fluxes. 
-\end{column}
-\end{columns}
-}
-
-\frame{
-\frametitle{Refinement level 0}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u0.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T0.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh0.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 1}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u1.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T1.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh1.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 2}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u2.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T2.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh2.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 3}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u3.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T3.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh3.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 4}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u4.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T4.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh4.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 5}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u5.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T5.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh5.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 6}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u6.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T6.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh6.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 7}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u7.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T7.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh7.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 8}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u8.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T8.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh8.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 9}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u9.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T9.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh9.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 10}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u10.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T10.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh10.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Zoomed solutions at plate/stagnation point}
-\begin{figure}
-\centering
-\subfigure[$\rho$]{\includegraphics[scale = .12]{figs/Re1000p2/rhoUnscaledzoom.png}}
-\subfigure[$u_1$]{\includegraphics[scale = .12]{figs/Re1000p2/u1zoom.png}}
-\subfigure[$u_2$]{\includegraphics[scale = .12]{figs/Re1000p2/u2zoom.png}}
-\subfigure[$T$]{\includegraphics[scale = .12]{figs/Re1000p2/Tzoom.png}}
-\subfigure[$q_n$]{\includegraphics[scale = .23]{figs/Re1000p2/heatflux.png}}
-\end{figure}
-}
-
-\section{Future work}
-%\subsection{Area A}
-%\frame{
-%\frametitle{Proposed work: Area A}
-%\begin{itemize}
-%\item{\textbf{Completed: Prove robustness of DPG method for the scalar convection-diffusion problem.}}
-%
-%We have introduced a test norm under which the DPG method robustly bounds the $L^2$ error in the field variables $u$ and the scaled stress $\sigma$.
-Numerical results confirm the theoretical bounds given.
-%
-%\item{\textbf{\textcolor{red}{Proposed}: Attempt analysis of the linearized Navier-Stokes system.}}
-%
-%We hope to analyze the linearized Navier-Stokes equations to determine an optimal extrapolation of the test norm for the scalar convection-diffusion problem to systems. 
-%
-%\end{itemize}
-%}
-
-%\subsection{Area B}
-%
-\frame{
-%\frametitle{Proposed work: Area B}
-%\item{\textbf{Completed: Collaborative work with Nathan Roberts on the higher order parallel adaptive DPG code Camellia.}}
-%
-%Numerical experiments use the higher-order adaptive codebase Camellia, built by Nathan Roberts upon the Trilinos library.
-%The framework for arbitrary-irregularity anisotropic refinements in both $h$ and $p$ is in place, and the code is partially parallelized.
-
-\frametitle{Future work: anisotropic refinements and $hp$-schemes.}
-
-The error representation function drives refinement effectively, and we hope to generalize its use to anisotropic adaptive schemes. 
-\begin{figure}
-\centering
-\subfigure{\includegraphics[scale = .175]{figs/anisotropy/b5.png}}
-\subfigure{\includegraphics[scale = .18]{figs/anisotropy/v6.png}}
-\caption{Anisotropic mesh for a convection-diffusion boundary layer.}
-\end{figure}
-}
-
-\frame{
-\frametitle{Future work: distributed iterative static condensation.}
-\[
-Ku = \arr{A}{B}{B^T}{D}\vecttwo{u_{\rm flux}}{u_{\rm field}} = \vecttwo{f}{g} = l
-\]
-where $D$ has a block-diagonal structure. The system can be reduced to yield the condensed system
-\[
-\left(A-B D^{-1} B^T\right)u_{\rm flux} = f - B D^{-1} g
-\]
-where $D^{-1}$ can be inverted block-wise.
-For FE stiffness matrices under the Laplace equation, the Schur complement has reduced condition number of $O(h^{-1})$ as opposed to $O(h^{-2})$.\footnote{\bibentry{schurComplement}}
-}
-
-\frame{  
-\frametitle{Future work: a Nonlinear Hessian-based DPG method.}
-Given a nonlinear variational problem $b(u,v) = \ell(v)$, linear in $v$ but not in $u$, beginning with the \textit{nonlinear} dual residual 
-\[
-J(u_h) = \frac{1}{2}\|B(u_h)-\ell\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(u_h,v)-\ell(v)|^2}{\nor{v}_V^2}.
-\]
-produces a Hessian-based DPG method, which solves
-\[
-b_u(\Delta u,v) + b''(\Delta u, \delta u, v_{R(u)}) = \ell(v) - b(u,v) = r(u,v),
-\]
-and aims to minimize the nonlinear dual residual instead of the linearized problem residual. 
-}
-
-\frame{
-\frametitle{Future work: applications}
-\begin{columns}
-\begin{column}{.48\textwidth}
-\begin{itemize}
-\item{{Solutions for all problems over a range of Reynolds/Mach numbers.}}
-\item{{Flow over a bump, Holden's ramp problem (shock-boundary layer interaction).}}
-\item{{Time permitting: airfoils, regularized Euler.}}
-\end{itemize}
-\end{column}
-\begin{column}{.5\textwidth}
-\begin{figure}
-\centering
-\includegraphics[scale = .275]{figs/ramp.png}
-\end{figure}
-\end{column}
-\end{columns}
-}
-
-\frame{
-\begin{center}
-Thank you!\\
-\vspace{1cm}
-Questions?
-\end{center}
-}
-
-\section{Extended slides}
-
-\frame{
-\frametitle{Extended literature review}
-\begin{itemize}
-\item Finite difference/volume methods, upwind stencils, monotonicity, ENO/WENO. 
-\item Artificial diffusion, flux limiters/discontinuity-capturing operators.
-\item DG fluxes can be interpreted as residual-based stabilizations similar to SUPG.\footnote{\bibentry{Brezzi20063293}}
-\item Hybridized DG (HDG) methods introduce independent unknowns for numerical traces. Fluxes are defined in terms of DG fluxes and the numerical trace.\footnote{\bibentry{hybridDG}}
-\end{itemize}
-}
-
-\frame{
-\frametitle{Specifics of the ultra-weak formulation}
-
-Given a first order system $Au = f$, multiply by test function $v$ and integrate 
-\[
-\LRp{Au,v} = \LRa{\gamma\LRp{Au},v} + \LRp{u,A^*_hv} = \LRp{f,v}
-\]
-If $u \in L^2\LRp{\Omega}$, the trace of $u$ is undefined, so we identify boundary terms $\LRa{\gamma\LRp{Au},v}_{\Gh} = \LRa{\widehat{u},v}_{\Gh}$ as unknowns $\widehat{u}$ on $\Gh$.
-For convection-diffusion,
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-\left( v, \tau \right)\right) = \left(u,\grad_h\cdot \tau - \beta \cdot \grad_h
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad_h v\right)_{\Oh}&\\
-  - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
-\end{align*}
-where 
-\begin{align*}
-\widehat{f}_n \coloneqq \beta_n u - \sigma_n \in H^{-1/2}(\Gh), \quad \widehat{u} \in H^{1/2}(\Gh)
-\end{align*}
-with the minimum energy extension norm on $\Gh$. We note that $H^{\pm 1/2}(\Gh)$ are \emph{closed} subspaces of $\prod_K H^{\pm 1/2}(\partial K)$. 
-}
-
-\frame{
-\frametitle{Inviscid equations}
-Issue: consider pure convection, $\div \beta u = f$. The ultra-weak variational formulation is
-\[
-\LRa{\widehat{f}_n,v}-\LRp{u,\beta\cdot \grad v} = \LRp{f,v},
-\]
-where $\widehat{f}_n \coloneqq \beta_n u$.
-When $\beta_n = 0$, $v$ has only a streamline derivative, and $\widehat{f}_n$ becomes an ill-defined trace in the cross-stream direction.
-For hyperbolic \emph{systems}, this issue manifests as \emph{sonic lines}.
-\begin{figure}
-\centering
-\includegraphics[scale=.25]{figs/sonicLines.pdf}
-\caption{Sonic lines ($u_n - c = 0$) appear for linearized Euler.}
-\end{figure}
-}
-
-\bibliographystyle{plain}
-{\scriptsize
-\bibliography{CFD_intro,DPG_old,paper,LitRev,NSNotes}
-}
-
-\end{document}

### 2013-05-01 docs/Jesse/Rice talk/futureWork.tex

--- 2012-09-06 docs/Jesse/Proposal/boeingPres.tex
@@
-\documentclass[compress]{beamer}
-\mode<presentation>
-\usetheme{Warsaw}
-\usecolortheme{seagull}
-%\useoutertheme[subsection=false]{smoothbars}
-\useoutertheme{infolines}
-\useinnertheme{rectangles}
-
-\setbeamercovered{dynamic}
-
-\usepackage{array}
-\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
-\usepackage[utf8]{inputenc}
-\usepackage{listings}
-\usepackage{mathtools}
-\usepackage{dsfont}
-\usepackage{pdfpages}
-\usepackage[textsize=footnotesize,color=green]{todonotes}
-\usepackage{algorithm, algorithmic}
-\usepackage{bm}
-\usepackage{tikz}
-\usepackage[normalem]{ulem}
-
-\usepackage{graphicx}
-\usepackage{subfigure}
-%\usepackage{caption}
-%\usepackage{subcaption}
-
-\usepackage{color}
-\usepackage{undertilde}
-\usepackage{pdflscape}
-\usepackage{pifont}
-
-\usepackage{bibentry}
-\nobibliography*
-
-%\usepackage[osf]{mathpazo}
-%\usepackage{mathpazo}
-%\renewcommand\rmdefault{ptm}
-
-\renewcommand{\topfraction}{0.85}
-\renewcommand{\textfraction}{0.1}
-\renewcommand{\floatpagefraction}{0.75}
-
-\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
-\newcommand{\tensor}[1]{\underline{\vect{#1}}}
-\newcommand{\del}{\triangle}
-\newcommand{\grad}{\nabla}
-\newcommand{\curl}{\grad \times}
-\renewcommand{\div}{\grad \cdot}
-\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
-\newcommand{\eip}[1]{a\left( #1 \right)}
-\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
-\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
-
-\newcommand{\circone}{\ding{192}}
-\newcommand{\circtwo}{\ding{193}}
-\newcommand{\circthree}{\ding{194}}
-\newcommand{\circfour}{\ding{195}}
-\newcommand{\circfive}{\ding{196}}
-
-\newcommand{\Reyn}{\rm Re}
-
-\newcommand{\bs}[1]{\boldsymbol{#1}}
-\DeclareMathOperator{\diag}{diag}
-
-\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}
-
-\newcommand{\tablab}[1]{\label{tab:#1}}
-\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
-
-\newcommand{\theolab}[1]{\label{theo:#1}}
-\newcommand{\theoref}[1]{\ref{theo:#1}}
-\newcommand{\eqnlab}[1]{\label{eq:#1}}
-\newcommand{\eqnref}[1]{\eqref{eq:#1}}
-\newcommand{\seclab}[1]{\label{sec:#1}}
-\newcommand{\secref}[1]{\ref{sec:#1}}
-\newcommand{\lemlab}[1]{\label{lem:#1}}
-\newcommand{\lemref}[1]{\ref{lem:#1}}
-
-\newcommand{\mb}[1]{\mathbf{#1}}
-\newcommand{\mbb}[1]{\mathbb{#1}}
-\newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\nor}[1]{\left\| #1 \right\|}
-\newcommand{\snor}[1]{\left| #1 \right|}
-\newcommand{\LRp}[1]{\left( #1 \right)}
-\newcommand{\LRs}[1]{\left[ #1 \right]}
-\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
-\newcommand{\LRc}[1]{\left\{ #1 \right\}}
-\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
-\newcommand{\Grad} {\ensuremath{\nabla}}
-\newcommand{\Div} {\ensuremath{\nabla\cdot}}
-\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
-\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
-\newcommand{\uh}{\widehat{u}}
-\newcommand{\fnh}{\widehat{f}_n}
-\renewcommand{\L}{L^2\LRp{\Omega}}
-\newcommand{\pO}{\partial\Omega}
-\newcommand{\Gh}{\Gamma_h}
-\newcommand{\Gm}{\Gamma_{-}}
-\newcommand{\Gp}{\Gamma_{+}}
-\newcommand{\Go}{\Gamma_0}
-\newcommand{\Oh}{\Omega_h}
-
-\newcommand{\eval}[2][\right]{\relax
-  \ifx#1\right\relax \left.\fi#2#1\rvert}
-
-\def\etal{{\it et al.~}}
-
-\def\arr#1#2#3#4{\left[
-\begin{array}{cc}
-#1 & #2\\
-#3 & #4\\
-\end{array}
-\right]}
-\def\vecttwo#1#2{\left[
-\begin{array}{c}
-#1\\
-#2\\
-\end{array}
-\right]}
-\def\vectthree#1#2#3{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-\end{array}
-\right]}
-\def\vectfour#1#2#3#4{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-#4\\
-\end{array}
-\right]}
-
-\newcommand{\G} {\Gamma}
-\newcommand{\Gin} {\Gamma_{in}}
-\newcommand{\Gout} {\Gamma_{out}}
-
-% removes nav symbols
-\beamertemplatenavigationsymbolsempty
-
-% defines newblock as null, giving compile issues otherwise
-\let\newblock\relax
-
-\institute[ICES]{Institute for Computational Engineering and Sciences}
-
-\title[A DPG method for Compressible Flow]{A Discontinuous Petrov-Galerkin method for compressible flow problems}
-\date{August 15, 2012}
-\author[J. Chan, T. Ellis, L. Demkowicz, R. Moser]{Jesse Chan, Truman Ellis \\ Supervisors: Leszek Demkowicz, Robert Moser}
-
-\begin{document}
-\begin{frame}
-\maketitle
-\end{frame}
-
-\frame{
-\frametitle{Compressible Navier-Stokes equations}
-\begin{columns}[c]
-\begin{column}{.475\textwidth}
-Numerical difficulties:
-\begin{itemize}
-\item{} Resolving solution features (sharp, localized viscous-scale phenomena)
-\begin{itemize}
-\item{} Shocks
-\item{} Boundary layers - resolution needed for drag/load
-\item{} Turbulence (non-localized)
-\end{itemize}
-\item{} Nonlinear convergence and uniqueness of solutions
-\item{} Stability of numerical schemes
-\begin{itemize}
-\item{} Coarse/adaptive grids
-\item{} Higher order
-\end{itemize}
-\end{itemize}
-\end{column}
-\begin{column}{.475\textwidth}
-\begin{figure}
-\centering
-\includegraphics[scale = .7]{figs/compFlowPics/airfoil_mesh.png}
-\end{figure}
-\end{column}
-\end{columns}
-\vspace{.2cm}
-\begin{center}
-Idea: begin first with the model problem of convection-diffusion.
-\end{center}
-}
-\frame{
-\frametitle{Robustness: convection-diffusion as a model problem}
-\vspace{-.5cm}
-\[
-\div \left(\beta u\right) - \epsilon \Delta u = f, \quad \text{on }\Omega \in \mathbb{R}^3
-\]
-\vspace{-.5cm}
-\begin{columns}[c]
-\begin{column}{.49\textwidth}
-In 1D: $\beta u' - \epsilon u'' = f$. Standard continuous Galerkin variational formulation: solve
-\[
-b(u,v) = \ell(v), \quad u,v\in H^1_0([0,1])
-\]
-where
-\begin{align*}
-b(u,v) &= \int_\Omega -\beta uv' + \epsilon u'v' \\
-\ell(v) &= \int_\Omega f v 
-\end{align*}
-\end{column}
-\begin{column}{.49\textwidth}
-\begin{figure}
-\centering
-\includegraphics[scale=.35]{figs/GalerkinOscTight.png}
-\caption{Solution for $f=1$. Oscillations in the standard Galerkin method for large Peclet numbers ${\rm Pe} \coloneqq \frac{h}{\epsilon}$.}
-\end{figure}
-\end{column}
-\end{columns}
-}
-
-\frame{
-\frametitle{Streamline-upwind Petrov-Galerkin (SUPG)}
-SUPG solves $b_{\rm SUPG}(u,v) = l_{\rm SUPG}(v)$, where
-\begin{align*}
-b_{\rm SUPG}(u,v) &= b(u,v)+ \sum_{K} \int_{K} \tau \LRp{L_{\rm adv} v} L u \\
-l_{\rm SUPG}(v) &= \ell(v) + \sum_{K} \int_{K} \tau \LRp{L_{\rm adv}v} f.
-\end{align*}
-\vspace{-.5cm}
-\begin{columns}[c]
-\begin{column}{.44\textwidth}
-\vspace{-.5cm}
-\begin{itemize}
-\item{} $Lu = \div\left(\beta u\right) - \epsilon \triangle u$, $L_{\rm adv}u = \div \left(\beta u\right)$, and $\tau$ is a parameter. 
-%\item{} Recovers ``exact'' artificial diffusion for $f=0$.
-\item{} Effective for $f\neq 0$. %``exact'' artificial diffusion.
-\item{} \emph{Residual-based} stabilization. 
-\end{itemize}
-\end{column}
-\begin{column}{.54\textwidth}
-\begin{figure}
-\centering
-\includegraphics[scale=.38]{figs/SUPG.png}
-%\caption{Exact, Bubnov-Galerkin, and SUPG solutions.}
-\end{figure}
-\end{column}
-\end{columns}
-}
-
-\frame{
-\begin{columns}
-\begin{column}{.49\textwidth}
-Can be interpreted as a \emph{Petrov-Galerkin} method,
-\[
-b\LRp{u,\tilde{v}_{i}} = \ell\LRp{\tilde{v}_{i}}, \quad \forall i = 1,\ldots,N-1,
-\]
-where the SUPG test function $\tilde{v}_{i}$ is defined elementwise as\footnotemark
-\[
-\tilde{v}_{i} = \phi_i(x) + \tau L_{\rm adv} \phi_i.  
-\]
-\end{column}
-\begin{column}{.49\textwidth}
-\begin{figure}
-\centering
-\subfigure{\includegraphics[scale=.16]{figs/SUPGtest.png}}
-\caption{SUPG test function $v_i$.}
-\end{figure}
-\end{column}
-\end{columns}
-\footnotetext{\bibentry{SUPG}}
-}
-
-\section{The DPG Method}
-\frame{
-\frametitle{DPG: a minimum residual method via optimal testing}
-Given a trial space $U$ and Hilbert test space $V$,
-\[
-b(u,v) = \ell(v), \quad u\in U, \quad v\in V
-\]
-This is equivalent to the operator equation posed in $V'$
-\[
-Bu = \ell
-\]
-if we identify $B:U\rightarrow V'$ and $\ell\in V'$ such that 
-\begin{align*}
-\langle Bu,v\rangle_V &\coloneqq b(u,v), \quad u\in U, v\in V,\\
-\langle \ell,v\rangle_V &\coloneqq \ell(v), \quad v\in V.
-\end{align*}
-We seek to minimize the dual functional over $U_h \subset U$
-\[
-J(u_h) = \frac{1}{2}\|Bu_h-\ell\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(u_h,v)-\ell(v)|^2}{\nor{v}_V^2}.
-\]
-}
-
-\begin{frame}
-Let $R_V: V \to V'$ be the isometric Riesz map st.\
-\[
-\langle R_V v,\delta v\rangle_V \coloneqq(v, \delta v)_V, \quad \forall \delta v \in V.
-\]
-Then, our functional $J(u_h)$ is equal to
-\begin{equation*}
-\min_{u_h\in U_h} J(u_h) = \frac{1}{2}\left\|Bu_h-\ell\right\|_{V'}^2 =  \frac{1}{2}\left\|R_V^{-1}(Bu_h-\ell)\right\|_V^2.
-\end{equation*}
-First order optimality: G\^ateaux derivative is zero in all directions $\delta u \in U_h$
-\begin{align*}
-\left(R_V^{-1}(Bu_h-\ell),R_V^{-1}B\delta u\right)_V &= 0, \quad \forall \delta u \in U_h.\\
-\rightarrow \LRa{(Bu_h-\ell),R_V^{-1}B\delta u} &= 0, \\
-\rightarrow b(u_h,R_V^{-1}B\delta u) - \ell(R_V^{-1}B\delta u) &= 0
-\end{align*}
-\end{frame}
-
-\frame{
-\frametitle{Summary: select test functions to minimize residuals}
-For $\delta u \in U_h$, define the \textcolor{red}{optimal test function} $v_{\delta u}$. 
-\begin{equation*}
-v_{\delta u} \coloneqq R_V^{-1}B\delta u.
-\end{equation*} 
-Then, the residual $J(u_h) = \frac{1}{2}\left\|Bu_h-\ell\right\|_{V'}^2$ is minimized by the solution of
-\[
-b\LRp{u_h,v_{\delta u}} = \ell\LRp{v_{\delta u}}, \quad \forall \delta u \in U_h.
-\]
-}
-
-\frame{
-\frametitle{Practical details of DPG}
-Computation of $v_{\delta u} \coloneqq R_V^{-1}B\delta u$ is \textbf{global} and \textbf{infinite-dimensional}.
-\begin{itemize}
-\item By choosing a \textcolor{red}{broken} test space $V$ and \textcolor{red}{localizable} norm $\nor{v}_V^2 = \sum_K \nor{v}_{V(K)}^2$, test functions can be determined locally.
-\item In practice, we use an \textcolor{red}{enriched space} $V_h \subset V$, where $\dim(V_h) > \dim(U_h)$ elementwise, and \textcolor{red}{optimal test functions} are approximated by computing $v_{\delta u} \coloneqq R_{V_h}^{-1}B\delta u \in V_h$ through\footnote{\bibentry{DPG2}}
-\[
-\LRp{v_{\delta u},\delta v}_V = b(\delta u,\delta v), \quad \delta u\in U_h, \quad \forall \delta v\in V_h
-\]
-Typically, if $U_h = \mathcal{P}^p(\mathbb{R}^n)$, $V_h = \mathcal{P}^{p+\triangle p}(\mathbb{R}^n)$, where $\triangle p \geq n$.\footnote{\bibentry{practicalDPG}} 
-\end{itemize}
-%\footnotetext{\bibentry{DPG2}}
-}
-
-\frame{
-\frametitle{Properties of DPG}
-DPG provides a symmetric positive-definite stiffness matrix. Let $\{\phi_j\}_{j=1}^m$ be a basis for $U_h$, and $\{v_i\}_{i=1}^n$ a basis for $V_h$, such that $n>m$. Then, for 
-\begin{align*}
-B_{ji} &= b(\phi_j,v_i),\\
-l_i &= \ell(v_i),
-\end{align*}
-DPG solves the discrete system for degrees of freedom $u$
-\begin{align*}
-\LRp{B^T R_V^{-1}B} u  &= \LRp{B^T R_V^{-1}} l,
-\end{align*}
-where, under a localizable norm and discontinuous test functions, $R_V^{-1}$ is block diagonal.
-}
-
-\frame{
-\frametitle{Properties of DPG}
-Additional properties of DPG include\footnotemark
-\begin{itemize}
-\item DPG provides the best approximation in the \textcolor{red}{energy norm}
-\[
-\|u\|_E = \|Bu\|_{V'} = \sup_{\nor{v}_V=1} \left|b(u,v)\right|.
-\]
-\item The energy error is computable through the residual
-\[
-\nor{u-u_h}_E = \nor{B(u-u_h)}_{V'} = \nor{R_V^{-1}(l-Bu_h)}_V = \nor{e}_V
-\]
-where the \textcolor{red}{error representation function} $e$ is defined through $(e,\delta v)_V = \ell(v)-b(u_h,\delta v)$ for all $\delta v\in V$. 
-\end{itemize}
-\footnotetext{\bibentry{DPG3pub}}
-}
-
-%\frame{
-%\frametitle{Duality of norms}
-%Duality of norms: for any trial norm $\nor{u}_U$,
-%\[
-%\nor{u}_{U} = \sup_{v \in V}\frac{b\LRp{u,v}}{\nor{v}_{V,U}}, \quad \nor{v}_{V,U} = \sup_{u \in U}\frac%{b\LRp{u,v}}{\nor{u}_{U}}.
-%\]
-%Likewise, for any test norm $\nor{v}_V$, 
-%\[
-%\nor{v}_{V} = \sup_{u \in U}\frac{b\LRp{u,v}}{\nor{U}_{U,V}}, \quad \nor{u}_{U,V} = \sup_{v \in V}\frac%{b\LRp{u,v}}{\nor{v}_{V}}.
-%\]
-%
-%}
-
-\frame{
-\frametitle{Ultra-weak formulation}
-\vspace{-.75cm}
-\begin{columns}
-\begin{column}{.64\textwidth}
-Given a first order system $Au = f$, we identify the \textbf{\emph{partition}} $\Oh$ and \textbf{\textcolor{red}{mesh skeleton}} \textcolor{red}{$\Gh$}.
-\end{column}
-\begin{column}{.34\textwidth}
-%\[
-%\Oh = \cup_{j=1}^\Nel K_j, \quad \Gh = \cup_{j=1}^\Nel \partial K_j
-%\]
-\begin{figure}[!h]
-\centering
-\includegraphics[scale = .155]{mesh_skel.pdf}
-\end{figure}
-\end{column}
-\end{columns}
-\vspace{-.5cm}
-The ultra-weak formulation for $Au = f$ on $\Oh$ is
-\[
-b\left(\left(u, \widehat{u}\right),v\right) \coloneqq \sum_K\langle \widehat{u},v \rangle_{\partial K} + (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh}.
-\]
-Under proper assumptions, $\sum_K\langle \widehat{u},v \rangle_{\partial K} = \langle \widehat{u}, \jump{v} \rangle_{\Gh}$, with energy setting
-\[
-u\in L^2\LRp{\Oh} \equiv L^2(\Omega), \quad v\in V=D(A^*_h), \quad
-\widehat{u}\in \gamma(D(A)),
-\]
-where $D(A_h^*)$ is the broken graph space of the formal adjoint $A_h^*$, and $\gamma(D(A))$ the trace space of the graph space of operator $A$.\footnote{\bibentry{analysisDPG}}
-}
-
-\frame{
-\frametitle{The canonical ``graph'' test norm}
-Recall $\nor{u}_E \coloneqq \sup_{v\in V\setminus\{0\}}\frac{b(u,v)}{\nor{v}_V}$. Under the ultra-weak formulation, the trial norm 
-\[
-\nor{\LRp{u,\widehat{u}}}_U \coloneqq \|u\|^2_{\L} + \|\widehat{u}\|^2
-\] 
-generates a test norm \emph{equivalent} to 
-\[
-\nor{v}_{V_{\rm opt}} \coloneqq \|A_h^*v\|_{\L}^2 +\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},\jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2.
-\]
-This norm is not localizable, so we instead substitute the jump terms for an $L^2$ term, giving us the \emph{graph norm}\footnote{\bibentry{Bui-ThanhDemkowiczGhattas11b}}
-\[
-\nor{v}_V \coloneqq \|A_h^*v\|_{\L}^2 + \nor{v}_{L^2}.
-\]
-}
-
-\frame{
-\frametitle{Goal: robust higher order adaptive methods}
-\begin{columns}
-\begin{column}{.45\textwidth}
-Our aim is to design an adaptive method for compressible laminar flows that is 
-\begin{itemize}
-\item robust in Reynolds number
-\item stable for arbitrary elements
-\end{itemize}
-
-This proposal will outline
-\begin{enumerate}
-\item a robust DPG method for convection-diffusion,
-\item extension to nonlinear problems and systems,
-\item proposed work.
-\end{enumerate}
-
-\end{column}
-\begin{column}{.54\textwidth}
-\begin{figure}
-\centering
-\subfigure{\includegraphics[scale=.23]{figs/Re1000p2/u2_full.png}}
-\subfigure{\includegraphics[scale=.37]{figs/Re1000p2/mesh6.png}}
-\caption{$u_2$ and $p=2$ mesh for $\Reyn = 1000$.}
-\end{figure}
-\end{column}
-\end{columns}
-}
-
-\section{A Robust DPG Method for Convection-Diffusion}
-
-\frame{
-\frametitle{Ultra-weak formulation for convection-diffusion}
-In first order form, the convection-diffusion equation is
-\[
-A \LRp{u,\sigma} \coloneqq 
-\LRs {
-\begin{array}{c}
-\div (\beta u - \sigma) \\ \frac{1}{\epsilon}\sigma - \grad u
-\end{array}} = \LRs{
-\begin{array}{c}
-f \\ 0
-\end{array}
-}.
-\]
-The variational formulation is
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-\left( v, \tau \right)\right) = \left(u,\grad_h\cdot \tau - \beta \cdot \grad_h
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad_h v\right)_{\Oh}&\\
-  - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
-\end{align*}
-where $\widehat{f}_n \coloneqq \beta_n u - \sigma_n$ and $\LRa{\widehat{f}_n,\jump{v} }_{\Gh}$ is defined 
-\[
-\LRa{\widehat{f}_n,\jump{v} }_{\Gh}\coloneqq \sum_K\int_{\partial K}{\rm sgn}(\vec{n}) \, \widehat{f}_n v.
-\]
-}
-
-\frame{
-\frametitle{Graph norm under convection-diffusion}
-For convection-diffusion, the graph test norm is defined elementwise
-\[
-\|\left(v,\tau\right)\|_{V(K)}^2 = \| \div \tau - \beta \cdot \grad v
-\|_{L^2(K)}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2(K)}^2 +
-\|v\|_{L^2(K)}^2.
-\]
-Problem with this test norm: approximability of test functions.
-\vspace{-.3cm}
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.175]{figs/opt.png}
-\caption{$v$ and $\tau$ components of the 1D optimal test functions for flux $\widehat{f}_n$ on the \emph{right-hand} side of a unit element for $\epsilon = 0.01$. }
-\label{fig:optTestBoundary}
-\end{figure}
-}
-
-\frame{
-\frametitle{Determining an alternative test norm}
-Recall the convection-diffusion bilinear form
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh}&\\
- - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
-\end{align*}
-We recover $\nor{u}^2_{L^2(\Omega)}$ by choosing conforming $\LRp{v,\tau}$ satisfying the \emph{adjoint equations}
-\begin{align*}
-\div\tau - \beta \cdot \grad v   &= u\\
-\frac{1}{\epsilon}\tau + \grad v &= 0
-\end{align*}
-with boundary conditions s.t.\ $\LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gamma}$ and $\LRa{ \widehat{f}_n,\jump{v} }_{\Gamma}$ vanish.
-}
-
-\frame{
-\frametitle{A robust bound}
-``Necessary'' conditions for robustness --- let $\boldsymbol U = \LRp{u,\sigma,\widehat{u},\widehat{f}_n}$. Then, by choosing specific $\LRp{v,\tau}$ satisfying the adjoint equations,
-\[
-\nor{u}^2_{L^2(\Omega)} = b\LRp{{\boldsymbol U},\LRp{v,\tau}} = \frac{b\LRp{{\boldsymbol U},\LRp{v,\tau}}}{\nor{\LRp{v,\tau}}_V} \nor{\LRp{v,\tau}}_V \leq \nor{\boldsymbol U}_E \nor{\LRp{v,\tau}}_V
-\]
-Let $\lesssim$ denote a robust bound - \textcolor{red}{if $ \nor{\LRp{v,\tau}}_V \lesssim \|u\|_{L^2(\Omega)}$}, then we have that
-\[
-\nor{u}_{L^2(\Omega)} \lesssim \nor{\boldsymbol U}_E
-\]
-\textbf{Main idea: the \textcolor{red}{test norm} should measure \textcolor{red}{adjoint solutions} robustly.}
-}
-
-\frame{
-\frametitle{Choice of inflow boundary condition}
-
-\begin{columns}
-\begin{column}{.49\textwidth}
-We impose the standard outflow wall boundary condition on $u$. For inflow boundary condition: 
-\begin{itemize}
-\item{} The standard choice of inflow boundary condition: $u = u_0$.
-\item{} We impose the non-standard inflow condition: $\widehat{f}_n \coloneqq \beta_n u - \sigma_n \approx \beta_n u_0$ on $\Gamma_{\rm in}$.
-\end{itemize}
-\end{column}
-
-\begin{column}{.49\textwidth}
-\begin{figure}
-\includegraphics[scale=.23]{figs/primal.png}
-\caption{Non-standard inflow.}
-\end{figure}
-\end{column}
-\end{columns}
-When $\sigma_n \approx 0$ near the inflow, condition on $\widehat{f}_n$ approximates condition on $u$.
-
-}
-
-\frame{
-\frametitle{Dirichlet inflow boundary condition}
-Standard choice of boundary condition: $u = u_0$ on inflow boundary $\Gamma_{\rm in}$, induces boundary layers in adjoint problems, \textcolor{red}{$\nor{\beta\cdot \grad v}_{L^2} = O(\epsilon^{-1})$}.
-\begin{figure}[h!]
-\centering
-\subfigure[Primal problem]{\includegraphics[scale=.23]{figs/primalDir.png}}
-\subfigure[Adjoint problem]{\includegraphics[scale=.23]{figs/adjointDir.png}}
-\caption{For the standard Dirichlet inflow condition, the solution to the adjoint problem can develop strong boundary layers at the outflow of the adjoint problem. }
-\end{figure}
-}
-
-\frame{
-\frametitle{New inflow boundary condition on $\widehat{f}_n$}
-Non-standard choice of boundary condition: $\widehat{f}_n = \beta_n u_0$ on $\Gamma_{\rm in}$, induces smoother adjoint problems, \textcolor{red}{$\nor{\beta\cdot \grad v}_{L^2} = O(1)$}.
-\begin{figure}[h!]
-\centering
-\subfigure[Primal problem]{\includegraphics[scale=.23]{figs/primal.png}}
-\subfigure[Adjoint problem]{\includegraphics[scale=.23]{figs/adjoint.png}}
-\caption{Under the new inflow condition, the wall-stop boundary condition is relaxed to a zero-stress condition at the outflow boundary of the adjoint problem.}
-\end{figure}
-}
-
-\frame{
-\frametitle{Test norms and adjoint solutions}
-\textbf{Intuition:} the effectiveness of DPG under a test norm is governed by how a \textbf{specific test norm} measures the \textbf{solutions of the adjoint problem}.
-
-\begin{figure}[!h]
-\centering
-\subfigure[Dirichlet inflow]{\includegraphics[scale=.35]{figs/dirichletBC.png}}
-\subfigure[``Convection'' inflow]{\includegraphics[scale=.35]{figs/newBC.png}}
-\caption{DPG solutions to convection-diffusion for both inflow conditions using an $H^1$ test norm.}
-\end{figure}
-}
-
-%\frame{
-%\frametitle{``Building blocks'' norm}
-%Test norm quantities are robustly bounded from above by $\nor{u}_{L^2(\Omega)}$.  
-%\[
-%\|\left(v,\tau\right)\|_{V,K}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2.
-%\]
-%Problem: boundary layers in optimal test functions:
-%\begin{figure}[!h]
-%\centering
-%\subfigure{\includegraphics[scale=.15]{figs/mesh1.png}}
-%\subfigure{\includegraphics[scale=.15]{figs/sol1.png}}
-%\caption{The $v$ component of the optimal test function corresponding to flux $\widehat{u} = x(1-x)$ on the bottom side of a unit element for $\epsilon = 0.01$.}
-%\label{fig:boundaryTest}
-%\end{figure}
-%}
-\frame{
-\frametitle{Adjoint estimates, or ``norm building blocks''}
-For solutions $(v,\tau)$ of the adjoint equations, the following quantities are robustly bounded from above by $\nor{u}_{L^2(\Omega)}$.  
-\begin{align*}
-&\|v\|, \sqrt{\epsilon} \|\grad v\|, \|\beta \cdot \grad v\| \\
-&\| \div \tau\|, \frac{1}{\sqrt{\epsilon}}\|\tau\|.
-\end{align*}
-We will construct a test norm through a combination of the above quantities, such that
-\begin{itemize}
-\item $v$ and $\tau$ decoupled (no systems).
-\item Coefficients are of equal order after transforming to the unit element (no boundary layers).
-\end{itemize}
-}
-\frame{
-\frametitle{Mesh-scaled test norms}
-Our test norm, as defined over a single element $K$, is now
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 +&\\
-\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2&.
-\end{align*}
-which induces the proven \emph{robust} bound\footnote{\bibentry{DPGrobustness2}}
-\[
-\nor{u}_{L^2(\Omega)}+ \nor{\sigma}_{L^2(\Omega)} + \epsilon\nor{\widehat{u}} + \sqrt{\epsilon} \nor{\widehat{f}_n} \lesssim \nor{\LRp{u,\sigma,\widehat{u},\widehat{f}_n}}_E.
-\]
-}
-
-\frame{
-\frametitle{Erikkson-Johnson model problem}
-
-On domain $\Omega = [0,1]^2$, with $\beta = (1,0)^T$, $ f = 0$ and boundary conditions
-\begin{align*}
-\widehat{\beta_nu - \sigma_n} &= \widehat{f}_n = u_0, \quad \beta_n \leq 0\\
-\widehat{u} &= 0, \quad \beta_n > 0
-\end{align*}
-
-%Separation of variables gives an analytic solution. 
-All numerical experiments done using Camellia codebase.\footnote{\bibentry{Camellia}}
-%\[
-%u(x,y) = C_0 + \sum_{n=1}^\infty C_n \frac{\exp(r_2(x-1)-\exp(r_1(x-1)))}{r_1\exp(-r2) - r_2\exp(-r1)}\cos(n\pi y)
-%\]
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale=.23]{figs/wallBC_exact_u.png}
-}
-\subfigure{
-\includegraphics[scale=.23]{figs/wallBC_exact_sigx.png}
-}
-\subfigure{
-\includegraphics[scale=.23]{figs/wallBC_exact_sigy.png}
-}
-\caption{Exact solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
-\end{figure}
-}
-
-\frame{
-\frametitle{Error rates}
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale=.33]{figs/errorrates_wallBC.png}
-}
-\subfigure{
-\includegraphics[scale=.33]{figs/L2energyratio_wallBC.png}
-}
-%\subfigure{
-%\includegraphics[scale=.22]{figs/u_pointdiff_wallBC.png}
-%}
-\caption{$L^2$/energy errors and their ratio for $\epsilon = .01, .001, .0001$.}
-\end{figure}
-}
-
-%\frame{
-%\frametitle{Regularization}
-%Discontinuous inflow conditions on $\widehat{f_n}$, out of alignment with mesh. Boundary condition $\epsilon \grad u \cdot n = 0$ at outflow.
-%\begin{figure}
-%\centering
-%\subfigure{
-%\includegraphics[scale=.33]{figs/discontinuous.png}
-%}
-%\subfigure{
-%\includegraphics[scale=.305]{figs/discontinuousL2rates.png}
-%}
-%\caption{Discontinuous hat inflow data with $\epsilon = 1e-5$, convection solution errors.}
-%\end{figure}
-%}
-\frame{
-\frametitle{Local conservation}
-Given stiffness matrix $K$, can introduce Lagrange multipliers to enforce element-wise constraints, leading to the saddle point problem
-\[
-\arr{K}{B}{B^T}{0}\vecttwo{u}{\lambda} = \vecttwo{f}{c}.
-\]
-where the Lagrange multipliers $\lambda$ can be locally condensed. We use the test norm
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,K}^2 = \left|\int_K v\right|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 +&\\
-\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2&.
-\end{align*}
-}
-
-\frame{
-\frametitle{Additional examples}
-\begin{figure}
-\centering
-\subfigure[Advection skew]{
-\includegraphics[scale = .175]{figs/Conservative/hughes.png}
-}
-\subfigure[Flow over a step]{
-\includegraphics[scale = .175]{figs/Conservative/step.png}
-}
-\subfigure[Double glazing]{
-\includegraphics[scale = .182]{figs/Conservative/doubleGlazing.png}
-}
-\end{figure}
-Locally conservative version of DPG performs very similarly to the standard DPG in all cases over a range of $\epsilon$. 
-}
-
-\frame{
-\frametitle{Regularization}
-For $\beta = (-y,x)^T$ on $\Omega = [-1,1]^2$. Ill posed in the convection setting. Similar tests have been done with discontinuous data.
-
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale=.21]{figs/vortex.png}
-}
-\subfigure{
-\includegraphics[scale=.2015]{figs/vortexMesh.png}
-}
-\caption{Steady vortex problem with $\epsilon = 1e-4$.}
-\end{figure}
-\vspace{-.25cm}
-}
-
-\frame{
-\frametitle{Current work - Hemker problem}
-
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale = .225]{figs/Conservative/Hemker/WithoutMesh.png}
-}
-\subfigure{
-\includegraphics[scale = .225]{figs/Conservative/Hemker/WithMesh.png}
-}
-\caption{Convection-diffusion solution to flow over a cylinder at $\epsilon = 1e-4$.}
-\end{figure}
-}
-\frame{
-\frametitle{Current work - high-lift airfoil}
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale = .1875]{figs/Conservative/Airfoil-Conservative-1E-3/solution.png}
-}
-\subfigure{
-\includegraphics[scale = .175]{figs/Conservative/Airfoil-Conservative-1E-3/mesh7.png}
-}
-\caption{Convection-diffusion solution over the high-lift airfoil, with advection at an angle, $\epsilon = 1e-3$, with $p=3$. Mesh is generated by \emph{Triangle}.}
-\end{figure}
-}
-
-\section{DPG for nonlinear problems}
-\frame{
-\frametitle{DPG for nonlinear problems}
-
-Given some linearization technique (typically Newton-Raphson and pseudo-timestepping linearization), we measure 
-\begin{itemize}
-\item size of the linearized update $\Delta u$
-\[
-\|\Delta u\|_E \coloneqq \nor{B_u\Delta u}_{V'} = \nor{R_V^{-1} B_u\Delta u}_V 
-\]
-\item the nonlinear residual 
-\[
-\nor{R(u)}_E \coloneqq \nor{B(u) - \ell}_{V'}  = \nor{R_V^{-1}\LRp{B(u)-\ell}}_V 
-\]
-\end{itemize}
-Preliminary experiments were done in 1D\footnote{\bibentry{DPGNS_1d}} and space-time.\footnote{\bibentry{DPGspacetime}}
-}
-
-\frame{
-\frametitle{2D test case: Burgers equation}
-\begin{columns}
-\begin{column}{.48\textwidth}
-\vspace{-.5cm}
-\[
-\pd{\left(u^2/2\right)}{x} + \pd{u}{y} + \epsilon \Delta u = f
-\]
-Burgers equation can be written with $\beta(u) = \LRp{u/2,1}$
-\begin{align*}
-\div\left(\beta(u)u-\sigma\right) &=f \\
-\frac{1}{\epsilon}\sigma - \grad u &=0.
-\end{align*}
-i.e.\ nonlinear convection-diffusion on domain $[0,1]^2$.
-\end{column}
-\begin{column}{.48\textwidth}
-\begin{figure}[!h]
-\centering
-\includegraphics[scale = .22]{figs/burgers.png}
-\caption{Shock solution for Burgers' equation, $\epsilon = 1e-4$, using Newton-Raphson.}
-\end{figure}
-\end{column}
-\end{columns}
-}
-\frame{
-Adaptivity begins with a cubic $4\times 4$ mesh.
-\begin{figure}[!h]
-\centering
-\subfigure{\includegraphics[scale=.2]{figs/burgersMesh.png}}
-\subfigure{\includegraphics[scale=.2]{figs/burgersZoom.png}}
-\caption{Adaptive mesh after 9 refinements, and zoom view at point (.5,.5) with shock formation and $1e-3$ width line for reference.}
-\end{figure}
-}
-
-\frame{
-\frametitle{2D Compressible Navier-Stokes equations (ideal gas)}
-Given density $\rho$, velocities $\mathbf{u} = \LRp{u_1,u_2}$ and temperature $T$,
-\begin{align*}
-\div \vecttwo{\rho u_1 }{\rho u_2} &= 0\\
-\div \left(\vecttwo{\rho u_1^2+p }{\rho u_1 u_2} - \boldsymbol \sigma_{1}\right) &=0\\
-\div \left(\vecttwo{\rho u_1 u_2}{\rho u_2^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
-\div \left(\vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2} - \boldsymbol\sigma \mathbf{u} + \vec{q}\right) &=0\\
-\frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I &= \grad \mathbf{u} - \Reyn \, \boldsymbol w\\
-\frac{1}{\kappa}\vec{q} &= \grad T
-\end{align*}
-}
-
-\frame{
-\frametitle{Stress law}
-$\boldsymbol\sigma$ for a Newtonian fluid: $\sigma_{ij} = \mu(u_{i,j} + u_{j,i}) + \lambda u_{k,k} \delta_{ij}$.
-%We can invert the stress tensor under isotropic and plane strain assumptions to get
-\[
-\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \frac{1}{2\mu} \sigma_{ij} - \frac{\lambda}{4\mu (\mu + \lambda)} \sigma_{kk}\delta_{ij}
-\]
-The symmetric part of the gradient is
-\[
-\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \grad  U - \boldsymbol w
-\]
-Our final form is
-\begin{align*}
-\grad  U - \boldsymbol w= \frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I.
-\end{align*}
-By enforcing strong symmetry of $\boldsymbol \sigma$, taking the antisymmetric part implicitly defines $\boldsymbol w$ to be the antisymmetric part of $\grad u$. 
-}
-
-\frame{
-\frametitle{Extrapolation of test norms}
-%\begin{columns}
-%\begin{column}{.48\textwidth}
-Convection-diffusion:
-\begin{align*}
-\div \left(\beta u - \sigma\right) &= f\\
-\frac{1}{\epsilon}\sigma - \grad u &= 0.
-\end{align*}
-Navier-Stokes: defining vector variables $U = \{\rho,u_1,u_2,T\}$ and $\Sigma = \{{\boldsymbol \sigma},\mathbf{q},w\}$,
-\begin{align*}
-\div \left(A_{\rm invisc}U - A_{\rm visc}\Sigma\right) &= R_{\rm conserv}(U,\Sigma)\\
-E_{\rm visc} \Sigma - \grad U &= R_{\rm constit}(U,\Sigma)
-\end{align*}
-where $R_{\rm conserv}(U,\Sigma)$ and $R_{\rm constit}(U,\Sigma)$ are the conservation/constitutive residuals.
-}
-
-\frame{
-\frametitle{Test norms over one element}
-Convection-diffusion:
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,K}^2 =& \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \|\beta \cdot \grad v\|^2 + \epsilon \|\grad v\|^2  \\
-&+\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
-\end{align*}
-
-Navier-Stokes: let $V$ and $W$ be vectors of test functions $v_i$ and $\tau_i$.
-\begin{align*}
-\|\left(V,W\right)\|_{V,K}^2 =& \min\left\{\frac{1}{\Reyn|K|},1\right\}\nor{V}^2  + \nor{A_{\rm invisc}^T \grad V}^2 + \frac{1}{\Reyn} \nor{A_{\rm visc}^T\grad V}^2 \\
-& + \nor{\div W}^2 + \min\left\{1,\frac{1}{\Reyn|K|}\right\}\nor{E_{\rm visc}^TW}^2.
-\end{align*}
-}
-
-\frame{
-\frametitle{Carter's flat plate problem}
-\begin{columns}
-\begin{column}{.49\textwidth}
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.32]{figs/flat_plate_BCs.pdf}
-\caption{Carter flat plate problem on domain $[0,2]\times[0,1]$. Plate begins at $x=1$, ${\rm Re} = 1000$.}
-\end{figure}
-\end{column}
-\begin{column}{.49\textwidth}
-\begin{enumerate}
-\item{} Symmetry boundary conditions.
-\item{} Prescribed temperature and wall stagnation conditions.
-\item{} Symmetry boundary conditions.
-\item{} Inflow: conserved quantities specified using far-field values.
-\item{} No outflow condition set.
-\end{enumerate}
-Stress/heat flux boundary conditions are set in terms of the momentum and energy fluxes. 
-\end{column}
-\end{columns}
-}
-
-\frame{
-\frametitle{Refinement level 0}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u0.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T0.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh0.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 1}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u1.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T1.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh1.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 2}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u2.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T2.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh2.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 3}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u3.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T3.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh3.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 4}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u4.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T4.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh4.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 5}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u5.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T5.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh5.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 6}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u6.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T6.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh6.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 7}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u7.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T7.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh7.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 8}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u8.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T8.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh8.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 9}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u9.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T9.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh9.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 10}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u10.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T10.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh10.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Zoomed solutions at plate/stagnation point}
-\begin{figure}
-\centering
-\subfigure[$\rho$]{\includegraphics[scale = .12]{figs/Re1000p2/rhoUnscaledzoom.png}}
-\subfigure[$u_1$]{\includegraphics[scale = .12]{figs/Re1000p2/u1zoom.png}}
-\subfigure[$u_2$]{\includegraphics[scale = .12]{figs/Re1000p2/u2zoom.png}}
-\subfigure[$T$]{\includegraphics[scale = .12]{figs/Re1000p2/Tzoom.png}}
-\subfigure[$q_n$]{\includegraphics[scale = .23]{figs/Re1000p2/heatflux.png}}
-\end{figure}
-}
-
 \section{Future work}
@@
 }
-
-\frame{
-\begin{center}
-Thank you!\\
-\vspace{1cm}
-Questions?
-\end{center}
-}
-
-\section{Extended slides}
-
-\frame{
-\frametitle{Extended literature review}
-\begin{itemize}
-\item Finite difference/volume methods, upwind stencils, monotonicity, ENO/WENO. 
-\item Artificial diffusion, flux limiters/discontinuity-capturing operators.
-\item DG fluxes can be interpreted as residual-based stabilizations similar to SUPG.\footnote{\bibentry{Brezzi20063293}}
-\item Hybridized DG (HDG) methods introduce independent unknowns for numerical traces. Fluxes are defined in terms of DG fluxes and the numerical trace.\footnote{\bibentry{hybridDG}}
-\end{itemize}
-}
-
-\frame{
-\frametitle{Specifics of the ultra-weak formulation}
-
-Given a first order system $Au = f$, multiply by test function $v$ and integrate 
-\[
-\LRp{Au,v} = \LRa{\gamma\LRp{Au},v} + \LRp{u,A^*_hv} = \LRp{f,v}
-\]
-If $u \in L^2\LRp{\Omega}$, the trace of $u$ is undefined, so we identify boundary terms $\LRa{\gamma\LRp{Au},v}_{\Gh} = \LRa{\widehat{u},v}_{\Gh}$ as unknowns $\widehat{u}$ on $\Gh$.
-For convection-diffusion,
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-\left( v, \tau \right)\right) = \left(u,\grad_h\cdot \tau - \beta \cdot \grad_h
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad_h v\right)_{\Oh}&\\
-  - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
-\end{align*}
-where 
-\begin{align*}
-\widehat{f}_n \coloneqq \beta_n u - \sigma_n \in H^{-1/2}(\Gh), \quad \widehat{u} \in H^{1/2}(\Gh)
-\end{align*}
-with the minimum energy extension norm on $\Gh$. We note that $H^{\pm 1/2}(\Gh)$ are \emph{closed} subspaces of $\prod_K H^{\pm 1/2}(\partial K)$. 
-}
-
-\frame{
-\frametitle{Inviscid equations}
-Issue: consider pure convection, $\div \beta u = f$. The ultra-weak variational formulation is
-\[
-\LRa{\widehat{f}_n,v}-\LRp{u,\beta\cdot \grad v} = \LRp{f,v},
-\]
-where $\widehat{f}_n \coloneqq \beta_n u$.
-When $\beta_n = 0$, $v$ has only a streamline derivative, and $\widehat{f}_n$ becomes an ill-defined trace in the cross-stream direction.
-For hyperbolic \emph{systems}, this issue manifests as \emph{sonic lines}.
-\begin{figure}
-\centering
-\includegraphics[scale=.25]{figs/sonicLines.pdf}
-\caption{Sonic lines ($u_n - c = 0$) appear for linearized Euler.}
-\end{figure}
-}
-
-\bibliographystyle{plain}
-{\scriptsize
-\bibliography{CFD_intro,DPG_old,paper,LitRev,NSNotes}
-}
-
-\end{document}

### 2013-05-01 docs/Jesse/Rice talk/pres.tex

--- 2012-08-08 docs/Jesse/Proposal/proposalPres.tex
@@
 \newcommand{\Oh}{\Omega_h}
+
+\newcommand{\bibfoot}[1]{\footnote{\tiny\bibentry{#1}}}
 
@@
 
-\title[A DPG method for Compressible Flow]{A Discontinuous Petrov-Galerkin method for compressible flow problems}
-\date{August 8, 2012}
-\author[J. Chan, L. Demkowicz, R. Moser]{Jesse Chan \\ Supervisors: Leszek Demkowicz, Robert Moser \\ Committee: Todd Arbogast, Omar Ghattas, Venkat Raman}
+\title[DPG methods for convective-diffusive problems]{A higher-order adaptive DPG method for compressible flow problems}
+%\title[A DPG method for Compressible Flow]{Application of a Discontinuous Petrov-Galerkin method to problems in compressible flow}
+\date{April 19, 2013}
+\author[J. Chan, L. Demkowicz, R. Moser]{Jesse Chan\\ Supervisors: Leszek Demkowicz, Robert Moser}
 
@@
 
-\section{Introduction/Literature review}
+\section{Motivation}
 \frame{
@@
 Compressible flow plays an important role in the aerospace and energy industries - transonic and supersonic aircraft, combustion engines, etc. 
-
-}
+}
+
 \frame{
@@
 \item{} Boundary layers - resolution needed for drag/load
-\item{} Turbulence (non-localized)
+\item{} Turbulence 
 \end{itemize}
@@
 %\item{} Recovers ``exact'' artificial diffusion for $f=0$.
+\item{} Restores discrete coercivity.
 \item{} Effective for $f\neq 0$. %``exact'' artificial diffusion.
-\item{} \emph{Residual-based} stabilization. 
+\item{} \textcolor{red}{Residual-based} stabilization. 
 \end{itemize}
@@
 \begin{column}{.49\textwidth}
-Can be interpreted as a \emph{Petrov-Galerkin} method,
+Can be ``interpreted'' as a \textcolor{red}{Petrov-Galerkin} method,
 \[
@@
 \end{columns}
-\footnotetext{\bibentry{SUPG}}
-}
+\footnotetext{\tiny\bibentry{SUPG}}
+}
+
+%\section{The DPG Method}
+%\frame{
+%\frametitle{DPG: a minimum residual method via optimal testing}
+%Given a trial space $U$ and Hilbert test space $V$,
+%\[
+%b(u,v) = \ell(v) \Longleftrightarrow Bu = \ell, \quad 
+%\left.\begin{array}{cl}
+%\langle Bu,v\rangle_V &\coloneqq b(u,v)\\
+%\langle \ell,v\rangle_V &\coloneqq \ell(v).
+%\end{array}\right.
+%\]
+%We seek to minimize the \textcolor{red}{dual residual} over $U_h \subset U$
+%\[
+%J(u_h) = \frac{1}{2}\|Bu_h-\ell\|_{V'}^2 = \frac{1}{2}\left\|R_V^{-1}(Bu_h-\ell)\right\|_V^2.
+%\]
+%where $R_V: V \to V'$ is the isometric Riesz map
+%\[
+%\langle R_V v,\delta v\rangle_V \coloneqq(v, \delta v)_V, \quad \forall \delta v \in V.
+%\]
+%Conditions for minimization of the convex functional give
+%\[
+%b(u_h,v_{\delta u}) = \ell(v_{\delta u}), \quad \forall \delta u \in U_h, \quad v_{\delta u} \coloneqq R_V^{-1}B\delta u.
+%\]
+%}
 
@@
 \end{align*}
-We seek to minimize the dual functional over $U_h \subset U$
+We seek to minimize the \textcolor{red}{dual residual} over $U_h \subset U$
 \[
@@
 \]
-Then, our functional $J(u_h)$ is equal to
+Then, our residual $J(u_h)$ is equal to
 \begin{equation*}
@@
 \frametitle{Summary: select test functions to minimize residuals}
-For $\delta u \in U_h$, define the \textcolor{red}{optimal test function} $v_{\delta u}$. 
-\begin{equation*}
-v_{\delta u} \coloneqq R_V^{-1}B\delta u.
-\end{equation*} 
+For $\delta u \in U_h$, define \textcolor{red}{optimal test functions} $v_{\delta u}\coloneqq R_V^{-1}B\delta u$ as solutions to
+\[
+\LRp{v_{\delta u},\delta v}_V = b({\delta u},\delta v), \quad \forall \delta v \in V.
+\]
+The \textcolor{red}{optimal test space} $V_{\rm opt}$
+\[
+V_{\rm opt} \coloneqq \LRc{v_{\delta u}: \delta u\in U_h}.
+\]
 Then, the residual $J(u_h) = \frac{1}{2}\left\|Bu_h-\ell\right\|_{V'}^2$ is minimized by the solution of
 \[
-b\LRp{u_h,v_{\delta u}} = \ell\LRp{v_{\delta u}}, \quad \forall \delta u \in U_h.
+b\LRp{u_h,v} = \ell\LRp{v}, \quad \forall v \in V_{\rm opt}.
 \]
@@
 \item By choosing a \textcolor{red}{broken} test space $V$ and \textcolor{red}{localizable} norm $\nor{v}_V^2 = \sum_K \nor{v}_{V(K)}^2$, test functions can be determined locally.
-\item In practice, we use an \textcolor{red}{enriched space} $V_h \subset V$, where $\dim(V_h) > \dim(U_h)$ elementwise, and \textcolor{red}{optimal test functions} are approximated by computing $v_{\delta u} \coloneqq R_{V_h}^{-1}B\delta u \in V_h$ through\footnote{\bibentry{DPG2}}
+\item In practice, we use an \textcolor{red}{enriched space} $V_h \subset V$, where $\dim(V_h) > \dim(U_h)$ elementwise, and \textcolor{red}{optimal test functions} are approximated by computing $v_{\delta u} \coloneqq R_{V_h}^{-1}B\delta u \in V_h$ through{\bibfoot{DPG2}}
 \[
@@
 \]
-Typically, if $U_h = \mathcal{P}^p(\mathbb{R}^n)$, $V_h = \mathcal{P}^{p+\triangle p}(\mathbb{R}^n)$, where $\triangle p \geq n$.\footnote{\bibentry{practicalDPG}} 
+Typically, if $U_h = \mathcal{P}^p(\mathbb{R}^n)$, $V_h = \mathcal{P}^{p+\triangle p}(\mathbb{R}^n)$, where $\triangle p \geq n$.{\bibfoot{practicalDPG}} 
 \end{itemize}
-%\footnotetext{\bibentry{DPG2}}
 }
@@
 \frametitle{Properties of DPG}
-DPG provides a symmetric positive-definite stiffness matrix. Let $\{\phi_j\}_{j=1}^m$ be a basis for $U_h$, and $\{v_i\}_{i=1}^n$ a basis for $V_h$, such that $n>m$. Then, for 
-\begin{align*}
-B_{ji} &= b(\phi_j,v_i),\\
+DPG provides a \textcolor{red}{symmetric positive-definite} stiffness matrix. Let $\{\phi_j\}_{j=1}^m$ be a basis for $U_h$, and $\{v_i\}_{i=1}^n$ a basis for $V_h$, such that $n>m$. Then, for 
+\begin{align*}
+B_{ij} &= b(\phi_j,v_i),\\
 l_i &= \ell(v_i),
@@
 where the \textcolor{red}{error representation function} $e$ is defined through $(e,\delta v)_V = \ell(v)-b(u_h,\delta v)$ for all $\delta v\in V$. 
+\item Adaptivity driven by local error indicator $\nor{e}_{V(K)}^2$
 \end{itemize}
-\footnotetext{\bibentry{DPG3pub}}
+\footnotetext{\tiny\bibentry{DPG3pub}}
 }
@@
 %\frame{
-%\frametitle{Duality of norms}
-%Duality of norms: for any trial norm $\nor{u}_U$,
-%\[
-%\nor{u}_{U} = \sup_{v \in V}\frac{b\LRp{u,v}}{\nor{v}_{V,U}}, \quad \nor{v}_{V,U} = \sup_{u \in U}\frac%{b\LRp{u,v}}{\nor{u}_{U}}.
-%\]
-%Likewise, for any test norm $\nor{v}_V$, 
-%\[
-%\nor{v}_{V} = \sup_{u \in U}\frac{b\LRp{u,v}}{\nor{U}_{U,V}}, \quad \nor{u}_{U,V} = \sup_{v \in V}\frac%{b\LRp{u,v}}{\nor{v}_{V}}.
-%\]
-%
+%\frametitle{Alternative interpretations of DPG}
+%DPG has been referred to as ``least-squares (with a twist)".  Recall that, given trial and test spaces $U$ and $V$, least-squares orthogonality of error is
+%\begin{align*}
+%\min_{u_h\in U_h}\frac{1}{2}\|Bu_h-\ell\|_{V'}^2 \Rightarrow \left(R_V^{-1}(Bu_h-\ell),R_V^{-1}B\delta u\right)_V = 0, \quad \forall \delta u \in U_h.
+%\end{align*}
+%By undoing the Riesz operator on the \textcolor{red}{left}, we arrive at optimal test functions 
+%\begin{align*}
+%\LRa{Bu_h-\ell,R_V^{-1}B\delta u} = b(u,R_V^{-1}B\delta u)-l(R_V^{-1}B\delta u) = 0, \quad \forall \delta u \in U_h
+%\end{align*}
 %}
+
+\frame{
+\frametitle{Residual-based stabilization (with a twist)}
+Can rewrite least-squares minimization as a \textcolor{red}{saddle point problem}.\bibfoot{DahmenVariationalStabilization}
+%\begin{align*}
+%\min_{u_h\in U_h}\frac{1}{2}\|Bu_h-\ell\|_{V'}^2 \Rightarrow \left(R_V^{-1}(Bu_h-\ell),R_V^{-1}B\delta u\right)_V = 0, \quad \forall \delta u \in U_h.
+%\end{align*}
+Define 
+$$R_V^{-1}(Bu-l)  = e \in V.$$ 
+Undoing the \textcolor{red}{right} Riesz operator leads to the Galerkin orthogonality condition
+\[
+\LRp{e,R_V^{-1}B\delta u}_V = \LRa{e,B\delta u} = b(\delta u, e) = 0, \quad \forall \delta u \in U_h
+\]
+which gives the system for $\LRp{u,e} \in U\times V$
+\begin{align*}
+b(u,v) + \LRp{e,v}_V &= l(v), \quad \forall v \in V\\
+b(\delta u, e) &= 0, \quad \forall \delta u \in U_h
+\end{align*}
+\vspace{-.2cm}
+%\begin{itemize}
+%\item $\LRp{e,v}_V$ can be interpreted as a VMS-type contribution.
+%\item Can be extended to arbitrary variational formulations.
+%\end{itemize}
+}
 
@@
 \centering
-\includegraphics[scale = .155]{mesh_skel.pdf}
+\includegraphics[scale = .155]{figs/mesh_skel.pdf}
 \end{figure}
@@
 \]
-where $D(A_h^*)$ is the broken graph space of the formal adjoint $A_h^*$, and $\gamma(D(A))$ the trace space of the graph space of operator $A$.\footnote{\bibentry{analysisDPG}}
-}
+where $D(A_h^*)$ is the broken graph space of the formal adjoint $A_h^*$, and $\gamma(D(A))$ the trace space of the graph space of operator $A$.\bibfoot{analysisDPG}
+}
+
+\section{Test norms for DPG}
 
@@
 \[
-\nor{\LRp{u,\widehat{u}}}_U \coloneqq \|u\|^2_{\L} + \|\widehat{u}\|^2
+\nor{\LRp{u,\widehat{u}}}_U^2 \coloneqq \|u\|^2_{\L} + \|\widehat{u}\|^2
 \] 
@@
 \[
-\nor{v}_{V_{\rm opt}} \coloneqq \|A_h^*v\|_{\L}^2 +\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},\jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2.
-\]
-This norm is not localizable, so we instead substitute the jump terms for an $L^2$ term, giving us the \emph{graph norm}\footnote{\bibentry{Bui-ThanhDemkowiczGhattas11b}}
-\[
-\nor{v}_V \coloneqq \|A_h^*v\|_{\L}^2 + \nor{v}_{L^2}.
-\]
-}
-
-\frame{
-\frametitle{Goal: robust higher order adaptive methods}
+\|A_h^*v\|_{\L}^2 +\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},\jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2.
+\]
+This norm is not localizable, so we instead substitute the jump terms for an $L^2$ term, giving us the \textcolor{red}{graph norm}{\bibfoot{Bui-ThanhDemkowiczGhattas11b}}
+\[
+\nor{v}_V^2 \coloneqq \|A_h^*v\|_{\L}^2 + \nor{v}_{L^2}^2.
+\]
+}
+
+\setcounter{subfigure}{0}
+\frame{
+\frametitle{The graph test norm - near $L^2$ best approx for Stokes.}
+\vspace{-.3cm}
+\begin{figure}
+\centering
+\subfigure[Manufactured solution:\ $u_1$ error]{\includegraphics[scale=.3]{figs/stokes/u1_err.pdf}}
+\subfigure[Manufactured solution:\ $p$ error]{\includegraphics[scale=.3]{figs/stokes/pressure_err.pdf}}
+\caption{Results under the graph norm for Stokes flow.{\bibfoot{stokesDPG}}}
+\end{figure}
+}
+\frame{
+\frametitle{The graph test norm - Stokes lid-driven cavity flow.}
+\vspace{-.3cm}
+\begin{figure}
+\centering
+\subfigure[Cavity flow streamlines]{\includegraphics[scale=.3]{figs/stokes/streamlines.pdf}}
+\subfigure[Second Moffat eddy]{\includegraphics[scale=.3]{figs/stokes/streamlines_zoom.pdf}}
+\end{figure}
+\vspace{-.3cm}
+Similar results for elasticity, electromagnetics, and wave propagation{\bibfoot{DPG4}}.
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\frame{
+\frametitle{DPG as a non-conforming DG method on $V$}
+For DPG using the ultra-weak variational formulation
+\[
+b\left(\left(u, \widehat{u}\right),v\right) \coloneqq \LRa{\widehat{u},\jump{v}}_{\Gh} + (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh},
+\]
+the saddle point problem is
+\begin{align*}
+\LRp{e,v}_V &= l(v)-b\LRp{\LRp{u,\uh},v}, \quad \forall v \in V(\Oh)\\
+(\delta u, A^*_he)_{\L} &= 0, \quad \forall (\delta u, 0) \in U_h\\
+\LRa{\widehat{\delta u},\jump{e}}_{\Gh} &= \int_{\Gh} \widehat{\delta u} \jump{e} =  0, \quad \forall \LRp{0,\widehat{\delta u}} \in U_h,
+\end{align*}
+This implies $e\in \tilde{V}$, the \emph{weakly conforming} space 
+\[
+\tilde{V} = \LRc{v \in V(\Oh): \LRa{\uh,\jump{v}}_{\Gh} = 0, \quad \forall \LRp{0,\widehat{\delta u}} \in U_h}.
+\]
+}
+
+\frame{
+\frametitle{Global properties of DPG test spaces}
+If we define $\tilde{V}_{\rm opt}$ as the optimal test space constructed using $\tilde{V}$
+\[
+\tilde{V}_{\rm opt} = \LRc{ R_{\tilde V}^{-1}B \delta u, \quad \forall \delta u \in U_h},
+\]
+we have the following theorem\bibfoot{globalDPG}  
+\begin{theorem}
+$\tilde{V}_{\rm opt} \subset V_{\rm opt}$.  Furthermore, the $L^2$/interior solutions of $b(u,v)=l(v)$ over $V_{\rm opt}$ and $\tilde{V}_{\rm opt}$ coincide.
+\end{theorem}
+\begin{itemize}
+\item The locally determined optimal test functions approximate globally optimal test functions.
+\item Under a variant of the graph norm, DPG approximates test functions which deliver $L^2$ optimality.
+\end{itemize}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{A Robust DPG Method for Convection-Diffusion}
+
+\frame{
+\frametitle{Ultra-weak formulation for convection-diffusion}
 \begin{columns}
-\begin{column}{.45\textwidth}
-Our aim is to design an adaptive method for compressible laminar flows that is 
-\begin{itemize}
-\item robust in Reynolds number
-\item stable for arbitrary elements
-\end{itemize}
-
-This proposal will outline
-\begin{enumerate}
-\item a robust DPG method for convection-diffusion,
-\item extension to nonlinear problems and systems,
-\item proposed work.
-\end{enumerate}
-
-\end{column}
-\begin{column}{.54\textwidth}
-\begin{figure}
-\centering
-\subfigure{\includegraphics[scale=.23]{figs/Re1000p2/u2_full.png}}
-\subfigure{\includegraphics[scale=.37]{figs/Re1000p2/mesh6.png}}
-\caption{$u_2$ and $p=2$ mesh for $\Reyn = 1000$.}
-\end{figure}
-\end{column}
-\end{columns}
-}
-
-\section{A Robust DPG Method for Convection-Diffusion}
-
-\frame{
-\frametitle{Ultra-weak formulation for convection-diffusion}
-In first order form, the convection-diffusion equation is
+\begin{column}{.65\textwidth}
+The first order convection-diffusion system:
 \[
@@
 \]
+\end{column}
+
+\begin{column}{.35\textwidth}
+\begin{figure}[!h]
+\centering
+\includegraphics[scale = 1.0]{figs/hybridDGNodes.pdf}
+\end{figure}
+\end{column}
+
+\end{columns}
+
 The variational formulation is
@@
 \frame{
-\frametitle{Graph norm under convection-diffusion}
-For convection-diffusion, the graph test norm is defined elementwise
-\[
-\|\left(v,\tau\right)\|_{V(K)}^2 = \| \div \tau - \beta \cdot \grad v
-\|_{L^2(K)}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2(K)}^2 +
+\frametitle{The graph test norm: problems under convection-diffusion}
+The graph norm{\bibfoot{Bui-ThanhDemkowiczGhattas11b}} for convection-diffusion gives exceptional stability.  %, this norm is defined elementwise
+\begin{align*}
+\|\left(v,\tau\right)\|_{V(K)}^2 =& \| \div \tau - \beta \cdot \grad v\|_{L^2(K)}^2 + 
+\| \epsilon^{-1} \tau + \grad v \|_{L^2(K)}^2 +
 \|v\|_{L^2(K)}^2.
-\]
+\end{align*}
 Problem with this test norm: approximability of test functions.
-\vspace{-.3cm}
 \begin{figure}[!h]
 \centering
-\includegraphics[scale=.175]{figs/opt.png}
-\caption{$v$ and $\tau$ components of the 1D optimal test functions for flux $\widehat{f}_n$ on the \emph{right-hand} side of a unit element for $\epsilon = 0.01$. }
+\includegraphics[scale=.16]{figs/opt.png}
+\caption{Components of optimal test functions for flux $\widehat{f}_n$ on the \emph{right-hand} side of a unit element for $\epsilon = 0.01$. }
 \label{fig:optTestBoundary}
@@
 
+%\frame{
+%\frametitle{Determining an alternative test norm}
+%Recall the convection-diffusion bilinear form
+%\begin{align*}
+%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
+%\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
+%v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh}&\\
+% - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
+%\end{align*}
+%We recover $\nor{u}^2_{L^2(\Omega)}$ by choosing conforming $\LRp{v,\tau}$ satisfying the \textcolor{red}{adjoint equations}
+%\begin{align*}
+%\div\tau - \beta \cdot \grad v   &= u\\
+%\frac{1}{\epsilon}\tau + \grad v &= 0
+%\end{align*}
+%with boundary conditions s.t.\ $\LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gamma}$ and $\LRa{ \widehat{f}_n,\jump{v} }_{\Gamma}$ vanish.
+%}
+%
+%\frame{
+%\frametitle{A robust bound}
+%``Necessary'' conditions for robustness --- let $\boldsymbol U = \LRp{u,\sigma,\widehat{u},\widehat{f}_n}$. Then, by choosing specific $\LRp{v,\tau}$ satisfying the adjoint equations,
+%\[
+%\nor{u}^2_{L^2(\Omega)} = b\LRp{{\boldsymbol U},\LRp{v,\tau}} = \frac{b\LRp{{\boldsymbol U},\LRp{v,\tau}}}{\nor{\LRp{v,\tau}}_V} \nor{\LRp{v,\tau}}_V \leq \nor{\boldsymbol U}_E \nor{\LRp{v,\tau}}_V
+%\]
+%Let $\lesssim$ denote a robust bound - \textcolor{red}{if $ \nor{\LRp{v,\tau}}_V \lesssim \|u\|_{L^2(\Omega)}$}, then we have that
+%\[
+%\nor{u}_{L^2(\Omega)} \lesssim \nor{\boldsymbol U}_E
+%\]
+%\textbf{Main idea: the \textcolor{red}{test norm} should measure \textcolor{red}{adjoint solutions} robustly.}
+%}
+
 \frame{
 \frametitle{Determining an alternative test norm}
-Recall the convection-diffusion bilinear form
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh}&\\
- - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
-\end{align*}
-We recover $\nor{u}^2_{L^2(\Omega)}$ by choosing conforming $\LRp{v,\tau}$ satisfying the \emph{adjoint equations}
-\begin{align*}
+%Recall the convection-diffusion bilinear form.  %Let $\boldsymbol U = \LRp{u,\sigma,\widehat{u},\widehat{f}_n}$. 
+\vspace{-.85cm}
+\begin{align*}%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),\left( v, \tau \right)\right) 
+b(\boldsymbol U,\boldsymbol V) = \left(u,\div \tau - \beta \cdot \grad
+v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh} + \text{boundary terms}
+% - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}
+\end{align*}
+Recover $\nor{u}^2_{L^2(\Omega)}$ with conforming $\LRp{v,\tau}$ satisfying the \emph{adjoint equations}
+\begin{align*}
+\left.
+\begin{array}{cl}
 \div\tau - \beta \cdot \grad v   &= u\\
 \frac{1}{\epsilon}\tau + \grad v &= 0
-\end{align*}
-with boundary conditions s.t.\ $\LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gamma}$ and $\LRa{ \widehat{f}_n,\jump{v} }_{\Gamma}$ vanish.
-}
-
-\frame{
-\frametitle{A robust bound}
-``Necessary'' conditions for robustness --- let $\boldsymbol U = \LRp{u,\sigma,\widehat{u},\widehat{f}_n}$. Then, by choosing specific $\LRp{v,\tau}$ satisfying the adjoint equations,
+\end{array}
+\right. ,
+\quad
+\text{boundary terms} = 0%\LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gamma}, \LRa{ \widehat{f}_n,\jump{v} }_{\Gamma} = 0
+\end{align*}
+``Necessary'' conditions for robustness --- 
 \[
@@
 When $\sigma_n \approx 0$ near the inflow, condition on $\widehat{f}_n$ approximates condition on $u$. 
-
-}
-
-\frame{
-\frametitle{Dirichlet inflow boundary condition}
+}
+
+\frame{
+\frametitle{Dirichlet inflow condition: issues as $\epsilon \rightarrow 0$}
 Standard choice of boundary condition: $u = u_0$ on inflow boundary $\Gamma_{\rm in}$, induces boundary layers in adjoint problems, \textcolor{red}{$\nor{\beta\cdot \grad v}_{L^2} = O(\epsilon^{-1})$}.
@@
 
-%\frame{
-%\frametitle{``Building blocks'' norm}
-%Test norm quantities are robustly bounded from above by $\nor{u}_{L^2(\Omega)}$.  
-%\[
-%\|\left(v,\tau\right)\|_{V,K}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2.
-%\]
-%Problem: boundary layers in optimal test functions:
-%\begin{figure}[!h]
-%\centering
-%\subfigure{\includegraphics[scale=.15]{figs/mesh1.png}}
-%\subfigure{\includegraphics[scale=.15]{figs/sol1.png}}
-%\caption{The $v$ component of the optimal test function corresponding to flux $\widehat{u} = x(1-x)$ on the bottom side of a unit element for $\epsilon = 0.01$.}
-%\label{fig:boundaryTest}
-%\end{figure}
-%}
 \frame{
 \frametitle{Adjoint estimates, or ``norm building blocks''}
-For solutions $(v,\tau)$ of the adjoint equations, the following quantities are robustly bounded from above by $\nor{u}_{L^2(\Omega)}$.  
+For solutions $(v,\tau)$ of the adjoint equations, the following quantities are robustly bounded from above by $\nor{\LRp{u,\sigma}}_{L^2(\Omega)}$.  
 \begin{align*}
@@
 }
+
 \frame{
 \frametitle{Mesh-scaled test norms}
+%For solutions $(v,\tau)$ of the adjoint equations, we derive quantities that are robustly bounded from above by $\nor{\LRp{u,\sigma}}_{L^2(\Omega)}$.  
 Our test norm, as defined over a single element $K$, is now
 \begin{align*}
-\|\left(v,\tau\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 +&\\
+\|\left(v,\tau\right)\|_{V,K}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 +&\\
 \| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2&.
 \end{align*}
-which induces the proven \emph{robust} bound\footnote{\bibentry{DPGrobustness2}}
+Defining $\nor{\LRp{v,\tau}}_{V,\Oh} = \sum_{K\in \Oh} \nor{\LRp{v,\tau}}_{V,K}$ induces the \textcolor{red}{robust} bound{\bibfoot{DPGrobustness2}}
+\begin{theorem}
+Under the test norm $\|\left(v,\tau\right)\|_{V,\Oh}$, the energy norm for DPG satisfies
 \[
@@
 \]
+\end{theorem}
 }
@@
 \begin{align*}
-\widehat{\beta_nu - \sigma_n} &= \widehat{f}_n = u_0, \quad \beta_n \leq 0\\
+\widehat{\beta_nu - \sigma_n} &= \widehat{f}_n = u_0 - \epsilon \pd{u}{n}, \quad \beta_n \leq 0\\
 \widehat{u} &= 0, \quad \beta_n > 0
 \end{align*}
-
-%Separation of variables gives an analytic solution. 
-All numerical experiments done using Camellia codebase.\footnote{\bibentry{Camellia}}
-%\[
-%u(x,y) = C_0 + \sum_{n=1}^\infty C_n \frac{\exp(r_2(x-1)-\exp(r_1(x-1)))}{r_1\exp(-r2) - r_2\exp(-r1)}\cos(n\pi y)
-%\]
+Separation of variables yields a boundary layer solution.\bibfoot{DPGrobustness}  
 \begin{figure}
@@
 \subfigure{
-\includegraphics[scale=.23]{figs/wallBC_exact_u.png}
+\includegraphics[scale=.25]{figs/wallBC_exact_u.png}
 }
 \subfigure{
-\includegraphics[scale=.23]{figs/wallBC_exact_sigx.png}
+\includegraphics[scale=.25]{figs/wallBC_exact_sigx.png}
 }
 \subfigure{
-\includegraphics[scale=.23]{figs/wallBC_exact_sigy.png}
+\includegraphics[scale=.25]{figs/wallBC_exact_sigy.png}
 }
@@
 \frame{
-\frametitle{Error rates}
+\frametitle{Numerical verification: Erikkson-Johnson problem}
+
+%On domain $\Omega = [0,1]^2$, with $\beta = (1,0)^T$, $ f = 0$ and boundary conditions
+%\begin{align*}
+%\widehat{\beta_nu - \sigma_n} &= \widehat{f}_n = u_0, \quad \beta_n \leq 0\\
+%\widehat{u} &= 0, \quad \beta_n > 0
+%\end{align*}
+Numerical experiments done using the Camellia{\bibfoot{Camellia}} codebase.
+%\begin{figure}
+%\centering
+%\subfigure{
+%\includegraphics[scale=.23]{figs/wallBC_exact_u.png}
+%}
+%\subfigure{
+%\includegraphics[scale=.23]{figs/wallBC_exact_sigx.png}
+%}
+%\subfigure{
+%\includegraphics[scale=.23]{figs/wallBC_exact_sigy.png}
+%}
+%\caption{Exact solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
+%\end{figure}
 \begin{figure}
@@
 \subfigure{
-\includegraphics[scale=.33]{figs/errorrates_wallBC.png}
+\includegraphics[scale=.31]{figs/errorrates_wallBC.pdf}
 }
 \subfigure{
-\includegraphics[scale=.33]{figs/L2energyratio_wallBC.png}
+\includegraphics[scale=.31]{figs/L2energyratio_wallBC.pdf}
 }
@@
 
-%\frame{
-%\frametitle{Regularization}
-%Discontinuous inflow conditions on $\widehat{f_n}$, out of alignment with mesh. Boundary condition $\epsilon \grad u \cdot n = 0$ at outflow.
-%\begin{figure}
-%\centering
-%\subfigure{
-%\includegraphics[scale=.33]{figs/discontinuous.png}
-%}
-%\subfigure{
-%\includegraphics[scale=.305]{figs/discontinuousL2rates.png}
-%}
-%\caption{Discontinuous hat inflow data with $\epsilon = 1e-5$, convection solution errors.}
-%\end{figure}
-%}
-
-\frame{
-\frametitle{Regularization}
-For $\beta = (-y,x)^T$ on $\Omega = [-1,1]^2$. Ill posed in the convection setting. Similar tests have been done with discontinuous data.
-
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale=.21]{figs/vortex.png}
-}
-\subfigure{
-\includegraphics[scale=.2015]{figs/vortexMesh.png}
-}
-\caption{Steady vortex problem with $\epsilon = 1e-4$, using a variant of the test norm.}
-\end{figure}
-\vspace{-.25cm}
-}
-
 \section{DPG for nonlinear problems}
@@
 \frametitle{DPG for nonlinear problems}
-
-Given some linearization technique (typically Newton-Raphson and pseudo-timestepping linearization), we measure 
+\begin{itemize}
+\item DPG applied to linearized problem; equivalent to Gauss-Newton 
+\item Given some linearization (Newton-Raphson, pseudo-timestepping	), we measure 
 \begin{itemize}
@@
 \end{itemize}
-Preliminary experiments were done in 1D\footnote{\bibentry{DPGNS_1d}} and space-time.\footnote{\bibentry{DPGspacetime}}
+\end{itemize}
+Preliminary experiments were done in 1D\bibfoot{DPGNS_1d} and space-time.\bibfoot{DPGspacetime}
 }
@@
 \begin{align*}
-\div \vecttwo{\rho u_1 }{\rho u_2} &= 0\\
-\div \left(\vecttwo{\rho u_1^2+p }{\rho u_1 u_2} - \boldsymbol \sigma_{1}\right) &=0\\
-\div \left(\vecttwo{\rho u_1 u_2}{\rho u_2^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
-\div \left(\vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2} - \boldsymbol\sigma \mathbf{u} + \vec{q}\right) &=0\\
-\frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I &= \grad \mathbf{u} - \Reyn \, \boldsymbol \omega \\
-\frac{1}{\kappa}\vec{q} &= \grad T
-\end{align*}
-}
-
-\frame{
-\frametitle{Stress law}
-$\boldsymbol\sigma$ for a Newtonian fluid: $\sigma_{ij} = \mu(u_{i,j} + u_{j,i}) + \lambda u_{k,k} \delta_{ij}$.
-%We can invert the stress tensor under isotropic and plane strain assumptions to get
-\[
-\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \frac{1}{2\mu} \sigma_{ij} - \frac{\lambda}{4\mu (\mu + \lambda)} \sigma_{kk}\delta_{ij}
-\]
-The symmetric part of the gradient is
-\[
-\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \grad  U - \boldsymbol \omega
-\]
-%where $\boldsymbol \omega$ is the antisymmetric part of the infinitesimal strain tensor:
+\div \vecttwo{\rho u_1 }{\rho u_2} &= 0,\\
+\div \left(\vecttwo{\rho u_1^2+p }{\rho u_1 u_2} - \boldsymbol \sigma_{1}\right) &=0,\\
+\div \left(\vecttwo{\rho u_1 u_2}{\rho u_2^2+p } - \boldsymbol \sigma_{2}\right) &=0,\\
+\div \left(\vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2} - \boldsymbol\sigma \mathbf{u} + \vec{q}\right) &=0,\\
+\frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I &= \grad \mathbf{u} - \Reyn \, \boldsymbol w,\\
+\kappa^{-1}\vec{q} &= \grad T,
+\end{align*}
+where $\boldsymbol w$ represents the antisymmetric part of $\grad u$
+}
+
+%\frame{
+%\frametitle{Stress law}
+%$\boldsymbol\sigma$ for a Newtonian fluid: $\sigma_{ij} = \mu(u_{i,j} + u_{j,i}) + \lambda u_{k,k} \delta_{ij}$.
+%%We can invert the stress tensor under isotropic and plane strain assumptions to get
 %\[
-%\boldsymbol \omega = \frac{1}{2}\left(\grad  U - \grad ^T  U\right).
+%\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \frac{1}{2\mu} \sigma_{ij} - \frac{\lambda}{4\mu (\mu + \lambda)} \sigma_{kk}\delta_{ij}
 %\]
-Our final form is
-\begin{align*}
-\grad  U - \boldsymbol \omega = \frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I.
-\end{align*}
-By enforcing strong symmetry of $\boldsymbol \sigma$, taking the antisymmetric part implicitly defines $\boldsymbol \omega$ to be the antisymmetric part of $\grad u$. 
-}
+%The symmetric part of the gradient is
+%\[
+%\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \grad  U - \boldsymbol w
+%\]
+%Our final form is
+%\begin{align*}
+%\grad  U - \boldsymbol w= \frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I.
+%\end{align*}
+%By enforcing strong symmetry of $\boldsymbol \sigma$, taking the antisymmetric part implicitly defines $\boldsymbol w$ to be the antisymmetric part of $\grad u$. 
+%}
 
@@
 \begin{align*}
+\div \left(\textcolor{red}{\beta u} - \textcolor{blue}{\sigma}\right) &= f\\
+\frac{1}{\epsilon}\sigma - {\grad u} &= 0.
+\end{align*}
+Navier-Stokes: defining vector variables $U = \{\rho,u_1,u_2,T\}$ and $\Sigma = \{{\boldsymbol \sigma},\mathbf{q},w\}$,
+\begin{align*}
+\div \left(\textcolor{red}{A_{\rm invisc}U} - \textcolor{blue}{A_{\rm visc}\Sigma}\right) &= R_{\rm conserv}(U,\Sigma)\\
+E_{\rm visc} \Sigma - \grad U &= R_{\rm constit}(U,\Sigma)
+\end{align*}
+where $R_{\rm conserv}(U,\Sigma)$ and $R_{\rm constit}(U,\Sigma)$ are the conservation/constitutive residuals.
+}
+%\addtocounter{framenumber}{-1}
+\addtocounter{framenumber}{-1}
+\frame{
+\frametitle{Extrapolation of test norms}
+%\begin{columns}
+%\begin{column}{.48\textwidth}
+Convection-diffusion:
+\begin{align*}
 \div \left(\beta u - \sigma\right) &= f\\
-\frac{1}{\epsilon}\sigma - \grad u &= 0.
-\end{align*}
-Navier-Stokes: defining vector variables $U = \{\rho,u_1,u_2,T\}$ and $\Sigma = \{{\boldsymbol \sigma},\mathbf{q},\omega\}$,
-\begin{align*}
-\div \left(A_{\rm invisc}U - A_{\rm visc}\Sigma\right) &= R_{\rm conserv}(U,\Sigma)\\
-E_{\rm visc} \Sigma - \grad U &= R_{\rm constit}(U,\Sigma)
+\textcolor{red}{\frac{1}{\epsilon}\sigma} - \textcolor{blue}{\grad u} &= 0.
+\end{align*}
+Navier-Stokes: defining vector variables $U = \{\rho,u_1,u_2,T\}$ and $\Sigma = \{{\boldsymbol \sigma},\mathbf{q},w\}$,
+\begin{align*}
+\div \left({A_{\rm invisc}U} - {A_{\rm visc}\Sigma}\right) &= R_{\rm conserv}(U,\Sigma)\\
+\textcolor{red}{E_{\rm visc} \Sigma} - \textcolor{blue}{\grad U} &= R_{\rm constit}(U,\Sigma)
 \end{align*}
@@
 \begin{align*}
-\|\left(v,\tau\right)\|_{V,K}^2 =& \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \|\beta \cdot \grad v\|^2 + \epsilon \|\grad v\|^2  \\
+\|\left(v,\tau\right)\|_{V,K}^2 =& \|v\|^2 + \|\beta \cdot \grad v\|^2 + \epsilon \|\grad v\|^2  \\
 &+\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
@@
 \begin{align*}
-\|\left(V,W\right)\|_{V,K}^2 =& \min\left\{\frac{1}{\Reyn|K|},1\right\}\nor{V}^2  + \nor{A_{\rm invisc}^T \grad V}^2 + \frac{1}{\Reyn} \nor{A_{\rm visc}^T\grad V}^2 \\
+\|\left(V,W\right)\|_{V,K}^2 =& \nor{V}^2  + \nor{A_{\rm invisc}^T \grad V}^2 + \frac{1}{\Reyn} \nor{A_{\rm visc}^T\grad V}^2 \\
 & + \nor{\div W}^2 + \min\left\{1,\frac{1}{\Reyn|K|}\right\}\nor{E_{\rm visc}^TW}^2.
@@
 
-\section{Proposed work}
-\subsection{Area A}
-\frame{
-\frametitle{Proposed work: Area A}
-\begin{itemize}
-\item{\textbf{Completed: Prove robustness of DPG method for the scalar convection-diffusion problem.}}
-
-We have introduced a test norm under which the DPG method robustly bounds the $L^2$ error in the field variables $u$ and the scaled stress $\sigma$.
-Numerical results confirm the theoretical bounds given.
-
-\item{\textbf{\textcolor{red}{Proposed}: Attempt analysis of the linearized Navier-Stokes system.}}
-
-We hope to analyze the linearized Navier-Stokes equations to determine an optimal extrapolation of the test norm for the scalar convection-diffusion problem to systems.
-
-\end{itemize}
-}
-
-\subsection{Area B}
-
-\frame{
-\frametitle{Proposed work: Area B}
-\begin{itemize}
-\item{\textbf{Completed: Collaborative work with Nathan Roberts on the higher order parallel adaptive DPG code Camellia.}}
-
-Numerical experiments use the higher-order adaptive codebase Camellia, built by Nathan Roberts upon the Trilinos library.
-%The framework for arbitrary-irregularity anisotropic refinements in both $h$ and $p$ is in place, and the code is partially parallelized.
-
-\item{\textbf{\textcolor{red}{Proposed}: Anisotropic refinements and $hp$-schemes.}}
-
-The error representation function drives refinement effectively, and we hope to generalize its use to anisotropic adaptive schemes. 
-\begin{figure}
-\centering
-\subfigure{\includegraphics[scale = .175]{figs/anisotropy/b5.png}}
-\subfigure{\includegraphics[scale = .18]{figs/anisotropy/v6.png}}
-\caption{Anisotropic mesh for a convection-diffusion boundary layer.}
-\end{figure}
-\end{itemize}
-}
-
-\frame{
-\textbf{\textcolor{red}{Proposed}: Distributed iterative static condensation.}
-\[
-Ku = \arr{A}{B}{B^T}{D}\vecttwo{u_{\rm flux}}{u_{\rm field}} = \vecttwo{f}{g} = l
-\]
-where $D$ has a block-diagonal structure. The system can be reduced to yield the condensed system
-\[
-\left(A-B D^{-1} B^T\right)u_{\rm flux} = f - B D^{-1} g
-\]
-where $D^{-1}$ can be inverted block-wise.
-For FE stiffness matrices under the Laplace equation, the Schur complement has reduced condition number of $O(h^{-1})$ as opposed to $O(h^{-2})$.\footnote{\bibentry{schurComplement}}
-}
-
-\frame{  
-\textbf{\textcolor{red}{Proposed}: a Nonlinear Hessian-based DPG method.}
-Given a nonlinear variational problem $b(u,v) = \ell(v)$, linear in $v$ but not in $u$, beginning with the \textit{nonlinear} dual residual 
-\[
-J(u_h) = \frac{1}{2}\|B(u_h)-\ell\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(u_h,v)-\ell(v)|^2}{\nor{v}_V^2}.
-\]
-produces a Hessian-based DPG method, which solves
-\[
-b_u(\Delta u,v) + b''(\Delta u, \delta u, v_{R(u)}) = \ell(v) - b(u,v) = r(u,v),
-\]
-and aims to minimize the nonlinear dual residual instead of the linearized problem residual. 
-}
-
-\subsection{Area C}
-\frame{
-\frametitle{Proposed work: Area C}
-\begin{columns}
-\begin{column}{.48\textwidth}
-\begin{itemize}
-\item{\textbf{Completed: convection-dominated diffusion, Burgers, and a model problem for Navier-Stokes.}}
-\item{\textbf{\textcolor{red}{Proposed}: Range of Reynolds/Mach numbers.}}
-\item{\textbf{\textcolor{red}{Proposed}: Flow over a bump, Holden's ramp problem (shock-boundary layer interaction).}}
-\item{\textbf{\textcolor{red}{Proposed (time permitting)}: airfoils, regularized Euler.}}
-\end{itemize}
-\end{column}
-\begin{column}{.5\textwidth}
-\begin{figure}
-\centering
-\includegraphics[scale = .275]{figs/ramp.png}
-\end{figure}
-\end{column}
-\end{columns}
+\frame{
+\frametitle{Automatic extension to anisotropic/$hp$ meshes}
+\begin{figure}
+\centering
+\includegraphics[scale=.4]{figs/aniso_white.png}
+\caption{Trace $\widehat{T}$ for ${\rm Re} =1000$ using an anisotropic refinement scheme.}
+\end{figure}
+}
+
+\frame{
+\frametitle{Preliminary results for ${\rm Re} =10000$.}
+\begin{figure}
+\centering
+\subfigure[Temperature]{\includegraphics[scale=.145]{figs/T.png}}
+\subfigure[$T$ at stagnation]{\includegraphics[scale=.13]{figs/TZ.png}}
+\subfigure[$\rho$ at stagnation]{\includegraphics[scale=.13]{figs/rhoZ.png}}
+\subfigure[Heat flux at plate]{\includegraphics[scale=.12]{figs/qn.png}}
+\end{figure}
 }
@@
 
-\section{Extended slides}
-
-\frame{
-\frametitle{Extended literature review}
-\begin{itemize}
-\item Finite difference/volume methods, upwind stencils, monotonicity, ENO/WENO. 
-\item Artificial diffusion, flux limiters/discontinuity-capturing operators.
-\item DG fluxes can be interpreted as residual-based stabilizations similar to SUPG.\footnote{\bibentry{Brezzi20063293}}
-\item Hybridized DG (HDG) methods introduce independent unknowns for numerical traces. Fluxes are defined in terms of DG fluxes and the numerical trace.\footnote{\bibentry{hybridDG}}
-\end{itemize}
-}
-
-\frame{
-\frametitle{Specifics of the ultra-weak formulation}
-
-Given a first order system $Au = f$, multiply by test function $v$ and integrate 
-\[
-\LRp{Au,v} = \LRa{\gamma\LRp{Au},v} + \LRp{u,A^*_hv} = \LRp{f,v}
-\]
-If $u \in L^2\LRp{\Omega}$, the trace of $u$ is undefined, so we identify boundary terms $\LRa{\gamma\LRp{Au},v}_{\Gh} = \LRa{\widehat{u},v}_{\Gh}$ as unknowns $\widehat{u}$ on $\Gh$.
-For convection-diffusion,
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-\left( v, \tau \right)\right) = \left(u,\grad_h\cdot \tau - \beta \cdot \grad_h
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad_h v\right)_{\Oh}&\\
-  - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
-\end{align*}
-where 
-\begin{align*}
-\widehat{f}_n \coloneqq \beta_n u - \sigma_n \in H^{-1/2}(\Gh), \quad \widehat{u} \in H^{1/2}(\Gh)
-\end{align*}
-with the minimum energy extension norm on $\Gh$. We note that $H^{\pm 1/2}(\Gh)$ are \emph{closed} subspaces of $\prod_K H^{\pm 1/2}(\partial K)$. 
-}
-
-\frame{
-\frametitle{Inviscid equations}
-Issue: consider pure convection, $\div \beta u = f$. The ultra-weak variational formulation is
-\[
-\LRa{\widehat{f}_n,v}-\LRp{u,\beta\cdot \grad v} = \LRp{f,v},
-\]
-where $\widehat{f}_n \coloneqq \beta_n u$.
-When $\beta_n = 0$, $v$ has only a streamline derivative, and $\widehat{f}_n$ becomes an ill-defined trace in the cross-stream direction.
-For hyperbolic \emph{systems}, this issue manifests as \emph{sonic lines}.
-\begin{figure}
-\centering
-\includegraphics[scale=.25]{figs/sonicLines.pdf}
-\caption{Sonic lines ($u_n - c = 0$) appear for linearized Euler.}
-\end{figure}
-}
+%\input{futureWork}
+\input{extendedSlides}
 

### 2013-05-15 docs/Jesse/Confusion Notes/siamltex/lexample.tex
adding dissertation and H1DPG paper to repo

%%
%% This is file `lexample.tex', 
%% Sample file for siam macros for use with LaTeX 2e
%% 
%% October 1, 1995
%%
%% Version 1.0
%% 
%% You are not allowed to change this file. 
%% 
%% You are allowed to distribute this file under the condition that 
%% it is distributed together with all of the files in the siam macro 
%% distribution. These are:
%%
%%  siamltex.cls (main LaTeX macro file for SIAM)
%%  siamltex.sty (includes siamltex.cls for compatibility mode)
%%  siam10.clo   (size option for 10pt papers)
%%  subeqn.clo   (allows equation numbners with lettered subelements)
%%  siam.bst     (bibliographic style file for BibTeX)
%%  docultex.tex (documentation file)
%%  lexample.tex (this file)
%%
%% If you receive only some of these files from someone, complain! 
%% 
%% You are NOT ALLOWED to distribute this file alone. You are NOT 
%% ALLOWED to take money for the distribution or use of either this 
%% file or a changed version, except for a nominal charge for copying 
%% etc. 
%% \CharacterTable
%%  {Upper-case    \A\B\C\D\E\F\G\H\I\J\K\L\M\N\O\P\Q\R\S\T\U\V\W\X\Y\Z
%%   Lower-case    \a\b\c\d\e\f\g\h\i\j\k\l\m\n\o\p\q\r\s\t\u\v\w\x\y\z
%%   Digits        \0\1\2\3\4\5\6\7\8\9
%%   Exclamation   \!     Double quote  \"     Hash (number) \#
%%   Dollar        \$     Percent       \%     Ampersand     \&
%%   Acute accent  \'     Left paren    \(     Right paren   \)
%%   Asterisk      \*     Plus          \+     Comma         \,
%%   Minus         \-     Point         \.     Solidus       \/
%%   Colon         \:     Semicolon     \;     Less than     \<
%%   Equals        \=     Greater than  \>     Question mark \?
%%   Commercial at \@     Left bracket  \[     Backslash     \\
%%   Right bracket \]     Circumflex    \^     Underscore    \_
%%   Grave accent  \`     Left brace    \{     Vertical bar  \|
%%   Right brace   \}     Tilde         \~}

\documentclass[final,leqno]{siamltex}

% definitions used by included articles, reproduced here for 
% educational benefit, and to minimize alterations needed to be made
% in developing this sample file.

\newcommand{\pe}{\psi}
\def\d{\delta} 
\def\ds{\displaystyle} 
\def\e{{\epsilon}} 
\def\eb{\bar{\eta}}  
\def\enorm#1{\|#1\|_2} 
\def\Fp{F^\prime}  
\def\fishpack{{FISHPACK}} 
\def\fortran{{FORTRAN}} 
\def\gmres{{GMRES}} 
\def\gmresm{{\rm GMRES($m$)}} 
\def\Kc{{\cal K}} 
\def\norm#1{\|#1\|} 
\def\wb{{\bar w}} 
\def\zb{{\bar z}}

% some definitions of bold math italics to make typing easier.
% They are used in the corollary.

\def\bfE{\mbox{\boldmath$E$}}
\def\bfG{\mbox{\boldmath$G$}}

\title{Sample file for SIAM \LaTeX\ macro package\thanks{This 
        work was supported by the Society for Industrial and
        Applied Mathematics, Philadelphia, Pennsylvania.}}

% The thanks line in the title should be filled in if there is
% any support acknowledgement for the overall work to be included
% This \thanks is also used for the received by date info, but
% authors are not expected to provide this.

\author{TeX Production\thanks{Composition Department, Society
        for Industrial and Applied Mathematics, 3600 Univeristy 
        City Science Center, Philadelphia, Pennsylvania, 
        19104-2688 ({\tt tex@siam.org}).}
        \and Various A.~U. Thors\thanks{Various Affiliations, 
        supported by various foundation grants.}}

\begin{document}

\maketitle

\begin{abstract}
An example of SIAM \LaTeX\ macros is presented. Various
aspects of composing manuscripts for SIAM's journal series
are illustrated with actual examples from accepted
manuscripts. SIAM's stylistic standards are adhered to
throughout, and illustrated.
\end{abstract}

\begin{keywords} 
sign-nonsingular matrix, LU-factorization, indicator
polynomial 
\end{keywords}

\begin{AMS}
15A15, 15A09, 15A23
\end{AMS}

\pagestyle{myheadings}
\thispagestyle{plain}
\markboth{TEX PRODUCTION AND V. A. U. THORS}{SIAM MACRO EXAMPLES}

\section{Introduction and examples}
This paper presents a sample file for the use of SIAM's
\LaTeX\ macro package. It illustrates the features of the
macro package, using actual examples culled from various
papers published in SIAM's journals. It is to be expected
that this sample will provide examples of how to use the
macros to generate standard elements of journal papers,
e.g., theorems, definitions, or figures. This paper also
serves as an example of SIAM's stylistic preferences for
the formatting of such elements as bibliographic references,
displayed equations, and equation arrays, among others.
Some special circumstances are not dealt with in this
sample file; for such information one should see the
included documentation file.

{\em Note:} This paper is not to be read in any form for content. 
The conglomeration of equations, lemmas, and other text elements were 
put together solely for typographic illustrative purposes and don't 
make any sense as lemmas, equations, etc.

\subsection{Sample text}
Let $S=[s_{ij}]$ ($1\leq i,j\leq n$) be a $(0,1,-1)$-matrix
of order $n$. Then $S$ is a {\em sign-nonsingular matrix}
(SNS-matrix) provided that each real matrix with the same
sign pattern as $S$ is nonsingular. There has been
considerable recent interest in constructing and
characterizing SNS-matrices \cite{bs}, \cite{klm}. There
has also been interest in strong forms of
sign-nonsingularity \cite{djd}. In this paper we give a new
generalization of SNS-matrices and investigate some of
their basic properties.

Let $S=[s_{ij}]$ be a $(0,1,-1)$-matrix of order $n$ and
let $C=[c_{ij}]$ be a real matrix of order $n$. The pair
$(S,C)$ is called a {\em matrix pair of order} $n$.
Throughout, $X=[x_{ij}]$ denotes a matrix of order $n$
whose entries are algebraically independent indeterminates
over the real field. Let $S\circ X$ denote the Hadamard
product (entrywise product) of $S$ and $X$. We say that the
pair $(S,C)$ is a {\em sign-nonsingular matrix pair of
order} $n$, abbreviated SNS-{\em matrix pair of order} $n$,
provided that the matrix \[A=S\circ X+C\] is nonsingular
for all positive real values of the $x_{ij}$.  If $C=O$
then the pair $(S,O)$ is a SNS-matrix pair if and only if
$S$ is a SNS-matrix.  If $S=O$ then the pair $(O,C)$ is a
SNS-matrix pair if and only if $C$ is nonsingular. Thus
SNS-matrix pairs include both nonsingular matrices and
sign-nonsingular matrices as special cases.

The pairs $(S,C)$ with
\[S=\left[\begin{array}{cc}1&0\\0&0\end{array}\right],\qquad 
C=\left[\begin{array}{cc}1&1\\1&1\end{array}\right]\] and 
\[S=\left[\begin{array}{ccc}1&1&0\\1&1&0\\0&0&0\end{array}\right],\qquad 
C=\left[\begin{array}{ccc}0&0&1\\0&2&0\\
3&0&0\end{array}\right]\] are examples of SNS-matrix pairs.

\subsection{A remuneration list}
In this paper we consider the evaluation of integrals of the 
following forms:
\begin{equation}
\int_a^b \left( \sum_i E_i B_{i,k,x}(t) \right)
         \left( \sum_j F_j B_{j,l,y}(t) \right) dt,\label{problem}
\end{equation}
\begin{equation}
\int_a^b f(t) \left( \sum_i E_i B_{i,k,x}(t) \right) dt,\label{problem2}
\end{equation}
where $B_{i,k,x}$ is the $i$th B-spline of order $k$ defined over the
knots $x_i, x_{i+1}, \ldots, x_{i+k}$.
We will consider B-splines normalized so that their integral is one.
The splines may be of different orders and
defined on different knot sequences $x$ and $y$.
Often the limits of integration will be the entire real line, $-\infty$
to $+\infty$. Note that (\ref{problem}) is a special case of (\ref{problem2})
where $f(t)$ is a spline.

There are five different methods for calculating (\ref{problem})
that will be considered:
\begin{remunerate}
\item Use Gauss quadrature on each interval.
\item Convert the integral to a linear combination of
      integrals of products of B-splines and provide a recurrence for
      integrating the product of a pair of B-splines.
\item Convert the sums of B-splines to piecewise
      B\'{e}zier format and integrate segment
      by segment using the properties of the Bernstein polynomials.
\item Express the product of a pair of B-splines as a linear combination
      of B-splines.
      Use this to reformulate the integrand as a linear combination
      of B-splines, and integrate term by term.
\item Integrate by parts.
\end{remunerate}
Of these five, only methods 1 and 5 are suitable for calculating 
(\ref{problem2}). The first four methods will be touched on and the 
last will be discussed at length.

\subsection{Some displayed equations and \{{\tt eqnarray}\}s}
     By introducing the product topology on  $R^{m \times m} \times
R^{n \times n}$  with the induced inner product
\begin{equation}
\langle (A_{1},B_{1}), (A_{2},B_{2})\rangle := \langle A_{1},A_{2}\rangle 
+ \langle B_{1},B_{2}\rangle,\label{eq2.10}
\end{equation}
we calculate the Fr\'{e}chet derivative of  $F$  as follows:
\begin{eqnarray}
 F'(U,V)(H,K) &=& \langle R(U,V),H\Sigma V^{T} + U\Sigma K^{T} -
P(H\Sigma V^{T} + U\Sigma K^{T})\rangle \nonumber \\
         &=& \langle R(U,V),H\Sigma V^{T} + U\Sigma K^{T}\rangle \label{eq2.11} \\
&=& \langle R(U,V)V\Sigma^{T},H\rangle + \langle \Sigma^{T}U^{T}R(U,V),K^{T}\rangle.     \nonumber
\end{eqnarray}
In the middle line of (\ref{eq2.11}) we have used the fact that the range of
$R$ is always perpendicular to the range of $P$.  The gradient $\nabla F$  of
$F$, therefore,  may be interpreted as the
pair of matrices:
\begin{equation}
 \nabla F(U,V) = (R(U,V)V\Sigma^{T},R(U,V)^{T}U\Sigma ) \in
R^{m \times m} \times R^{n \times n}.       			\label{eq2.12}
\end{equation}
Because of the product topology, we know
\begin{equation}
 {\cal T}_{(U,V)}({\cal O} (m) \times {\cal O} (n)) =
{\cal T}_{U}{\cal O} (m) \times {\cal T}_{V}{\cal O} (n),  		\label{eq2.13}
\end{equation}
where  ${\cal T}_{(U,V)}({\cal O} (m) \times {\cal O} (n))$  stands for the
tangent space to the manifold  ${\cal O} (m) \times {\cal O} (n)$  at  $(U,V)
\in {\cal O} (m) \times {\cal O} (n)$  and so on.  The projection of
$\nabla F(U,V)$  onto  ${\cal T}_{(U,V)}({\cal O} (m) \times {\cal O} (n))$,
therefore, is the product of the projection of the first component of
$\nabla F(U,V)$  onto  ${\cal T}_{U}{\cal O} (m)$  and the projection of the
second component of  $\nabla F(U,V)$  onto  ${\cal T}_{V}{\cal O} (n)$. 
In particular, we claim that the
projection $ g(U,V)$  of the gradient  $\nabla F(U,V)$  onto
${\cal T}_{(U,V)}({\cal O} (m) \times {\cal O} (n))$  is given by the pair of
matrices:
\begin{eqnarray}
g(U,V) = && \left( \frac{R(U,V)V\Sigma^{T}U^{T}-U\Sigma V^{T}R(U,V)^{T}}{2}U,
\right.			\nonumber \\[-1.5ex]
\label{eq2.14}\\[-1.5ex]
&&\quad \left. \frac{R(U,V)^{T}U\Sigma V^{T}-V
   \Sigma^{T}U^{T}R(U,V)}{2}V \right).\nonumber
\end{eqnarray}
Thus, the vector field
\begin{equation}
\frac{d(U,V)}{dt} = -g(U,V) 	\label{eq2.15}
\end{equation}
defines a steepest descent flow on the manifold  ${\cal O} (m) \times
{\cal O} (n)$ for the objective function  $F(U,V)$.

\section{Main results}

Let $(S,C)$ be a matrix pair of order $n$.  The determinant
\[\det (S\circ X+C)\] 
is a polynomial in the indeterminates of $X$ of degree at
most $n$ over the real field. We call this polynomial the
{\em indicator polynomial} of the matrix pair $(S,C)$
because of the following proposition.

\begin{theorem} 
\label{th:prop} 
The matrix pair $(S,C)$ is a {\rm SNS}-matrix pair if and
only if all the nonzero coefficients in its indicator
polynomial have the same sign and there is at least one
nonzero coefficient.
\end{theorem}

\begin{proof}
Assume that $(S,C)$ is a SNS-matrix pair.  Clearly the
indicator polynomial has a nonzero coefficient.  Consider a
monomial
\begin{equation} 
\label{eq:mono} 
b_{i_{1},\ldots,i_{k};j_{1},\ldots,j_{k}}x_{i_{1}j_{1}}\cdots
x_{i_{k}j_{k}}
\end{equation} 
occurring in the indicator polynomial with a nonzero
coefficient.  By taking the $x_{ij}$ that occur in
(\ref{eq:mono}) large and all others small, we see that any
monomial that occurs in the indicator polynomial with a
nonzero coefficient can be made to dominate all others.
Hence all the nonzero coefficients have the same sign. The
converse is im-\linebreak mediate. \qquad\end{proof}

For SNS-matrix pairs $(S,C)$ with $C=O$ the indicator
polynomial is a homogeneous polynomial of degree $n$. In
this case Theorem \ref{th:prop} is a standard fact about
SNS-matrices.

\begin{lemma}[{\rm Stability}]
\label{stability}
Given $T>0$, suppose that $\| \epsilon (t) \|_{1,2} \leq h^{q-2}$
for $0 \leq t \leq T$ and $q \geq 6$. 
Then there exists a positive number $B$ that depends on
$T$ and the exact solution $\pe$ only such that for all $0 \leq t \leq T$,
\begin{equation}
\label{Gron}
\frac {d}{dt} \| \epsilon (t) \| _{1,2}  \leq B
   ( h^{q-3/2} + \| \epsilon (t) \|_{1,2})\;.
\end{equation}
The function $B(T)$ can be chosen to be nondecreasing in time.
\end{lemma}

\begin{theorem} 
\label{th:gibson} 
The maximum number of nonzero entries in a {\rm SNS}-matrix
$S$ of order $n$ equals \[\frac{n^{2}+3n-2}{2}\] with
equality if and only if there exist permutation matrices
such that $P|S|Q=T_{n}$ where
\begin{equation} 
\label{eq:gibson} 
T_{n}=\left[\begin{array}{cccccc} 1&1&\cdots&1&1&1\\
1&1&\cdots&1&1&1\\ 0&1&\cdots&1&1&1\\ 
\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\ 
0&0&\cdots&1&1&1\\ 0&0&\cdots&0&1&1\end{array}\right]. 
\end{equation} 
\end{theorem}

We note for later use that each submatrix of $T_{n}$ of
order $n-1$ has all 1s on its main diagonal.

We now obtain a bound on the number of nonzero entries of
$S$ in a SNS-matrix pair $(S,C)$ in terms of the degree of
the indicator polynomial. We denote the strictly upper
triangular (0,1)-matrix of order $m$ with all 1s above the
main diagonal by $U_{m}$. The all 1s matrix of size $m$ by
$p$ is denoted by $J_{m,p}$.

\begin{proposition}[{\rm Convolution theorem}]
\label{pro:2.1}  Let
\begin{eqnarray*}
a\ast u(t) = \int_0^t a(t- \tau) u(\tau) d\tau, \hspace{.2in} t \in
(0, \infty).
\end{eqnarray*}
Then
\begin{eqnarray*}
\widehat{a\ast u}(s) = \widehat{a}(s)\widehat{u}(s).
\end{eqnarray*}
\end{proposition}

\begin{lemma}
\label{lem:3.1}
For $s_0 >0$, if
$$
\int_0^{\infty} e^{-2s_0 t}v^{(1)}(t) v(t) dt \; \leq 0 \;,
$$
then
\begin{eqnarray*}
\int_0^{\infty} e^{-2s_0 t} v^2(t) dt \; \leq \; \frac{1}{2s_0} v^2(0).
\end{eqnarray*}
\end{lemma}

{\em Proof}. Applying integration by parts, we obtain
\begin{eqnarray*}
\int_0^{\infty} e^{-2s_0 t} [v^2(t)-v^2(0)] dt
&=&\lim_{t\rightarrow \infty}\left (
-\frac{1}{2s_0}e^{-2s_0 t}v^2(t) \right ) +\frac{1}{s_0}
\int_0^{\infty} e^{-2s_0 t}v^{(1)}(t)v(t)dt\\
&\leq& \frac{1}{s_0} \int_0^{\infty} e^{-2s_0 t} v^{(1)}(t)v(t) dt \;\;
\leq \;\; 0.
\end{eqnarray*}
Thus
$$
\int_0^{\infty} e^{-2s_0 t} v^2(t) dt \;\;\leq v^2(0) \int_0^{\infty}
\;\;e^{-2s_0 t} dt\;\;=\;\;\frac{1}{2s_0} v^2(0).\eqno\endproof
$$

\begin{corollary}\label{c4.1}
Let $ \bfE $ satisfy $(5)$--$(6)$ and
suppose $ \bfE^h $ satisfies $(7)$ and $(8)$
with a general $ \bfG $.  Let $ \bfG= \nabla \times {\bf \Phi} + \nabla p,$
$p \in H_0^1 (\Omega) $. Suppose that $\nabla p$ and $ \nabla \times 
{\bf \Phi} $ satisfy all the assumptions of Theorems $4.1$ and  
$4.2$, respectively. In addition suppose all the regularity
assumptions of Theorems $4.1$--$4.2$ are satisfied.  Then 
for $ 0 \le t \le T $ and $ 0 < \epsilon \le \epsilon_0 $ there exists a 
constant $ C = C(\epsilon, T) $ such that
$$
\Vert (\bfE - \bfE^h)(t) \Vert_0 \le C h^{k+1- \epsilon},
$$
where $ C $ also depends on the constants given in Theorems 
$4.1$ and $4.2$.
\end{corollary}

\begin{definition}
Let $S$ be an isolated invariant set with isolating neighborhood $N$.
An {\em index pair} for $S$ is a pair of compact sets $(N_{1},N_{0})$
with $N_{0} \subset N_{1} \subset N$ such that:
\begin{romannum}
\item $cl(N_{1} \backslash N_{0})$
is an isolating neighborhood for $S$.
\item $N_{i}$ is positively invariant relative to $N$ for $i=0,1$,
i.e., given
$x \in N_{i}$ and $x \cdot [0,t] \subset N$, then $x \cdot [0,t] \subset
N_{i}$.
\item $N_{0}$ is an exit set for $N_{1}$, i.e. if $x \in N_{1}$,
$x \cdot [0, \infty ) \not\subset N_{1}$, then there is a $T \geq 0$ such
that $x \cdot [0,T] \subset N_{1}$ and $x \cdot T \in N_{0}$.
\end{romannum}
\end{definition}

\subsection{Numerical experiments} We conducted numerical experiments 
in computing inexact Newton steps for discretizations of a  
{\em modified Bratu problem}, given by  
\begin{eqnarray} 
{\ds \Delta w + c e^w + d{ {\partial w}\over{\partial x} } } 
&=&{\ds f \quad {\rm in}\ D, }\nonumber\\[-1.5ex]
\label{bratu} \\[-1.5ex]
{\ds w }&=&{\ds 0 \quad {\rm on}\ \partial D , } \nonumber
\end{eqnarray} 
where $c$ and $d$ are constants. The actual Bratu problem has $d=0$ and  
$f \equiv0$. It provides a simplified model of nonlinear diffusion  
phenomena, e.g., in combustion and semiconductors, and has been 
considered by Glowinski, Keller, and Rheinhardt \cite{GloKR85}, 
as well as by a number of other investigators; see \cite{GloKR85} 
and the references therein. See also problem 3 by Glowinski and  Keller  
and problem 7 by Mittelmann in the collection of nonlinear model 
problems assembled by Mor\'e \cite{More}. The modified problem  
(\ref{bratu}) has been used as a test problem for inexact Newton 
methods by Brown and Saad \cite{Brown-Saad1}.

In our experiments, we took $D = [0,1]\times[0,1]$, $f \equiv0$, 
$c=d=10$, and discretized (\ref{bratu}) using the usual second-order 
centered differences over a $100\times100$ mesh of equally 
spaced points in $D$. In \gmres($m$), we took $m=10$ and used fast  
Poisson right preconditioning as in the experiments in \S2. The computing  
environment was as described in \S2. All computing was done  
in double precision.

\begin{figure}[ht] 
\vspace{2.5in}
\caption{{\rm Log}$_{10}$ of the residual norm versus the number of
{\rm GMRES$(m)$} iterations for the finite difference methods.} 
\label{diff} 
\end{figure}

In the first set of experiments, we allowed each method to  
run for $40$ {\gmresm} iterations, starting with zero as the initial  
approximate solution, after which the limit of residual norm  
reduction had been reached. The results are shown in Fig.~\ref{diff}.  
In Fig.~\ref{diff}, the top curve was produced by method FD1. 
The second curve from the top is actually a superposition of  
the curves produced by methods EHA2 and FD2; the two curves are 
visually indistinguishable. Similarly, the third curve from  
the top is a superposition of the curves produced by methods EHA4 
and FD4, and the fourth curve from the top, which lies barely above  
the bottom curve, is a superposition of the curves produced by  
methods EHA6 and FD6. The bottom curve was produced by method A.

In the second set of experiments, our purpose was to assess the 
relative amount of computational work required by the methods  
which use higher-order differencing to reach comparable levels  
of residual norm reduction. We compared pairs of methods EHA2  
and FD2, EHA4 and FD4, and EHA6 and FD6 by observing in each of 
20 trials the number of {\gmresm} iterations, number of $F$-evaluations,  
and run time required by each method to reduce the residual norm 
by a factor of $\e$, where for each pair of methods $\e$ was chosen  
to be somewhat greater than the limiting ratio of final to  
initial residual norms obtainable by the methods. In these trials,  
the initial approximate solutions were obtained by generating random  
components as in the similar experiments in \S2. We note that for every  
method, the numbers of {\gmresm} iterations and $F$-evaluations required  
before termination did not vary at all over the 20 trials. The {\gmresm}
iteration counts, numbers of $F$-evaluations, and means and standard  
deviations of the run times are given in Table \ref{diffstats}.

\begin{table}
\caption{Statistics over $20$ trials of {\rm GMRES$(m)$} iteration numbers,  
$F$-evaluations, and run times required to reduce the residual norm by  
a factor of $\e$. For each method, the number of {\rm GMRES$(m)$} iterations  
and $F$-evaluations was the same in every trial.}

\begin{center} \footnotesize
\begin{tabular}{|c|c|c|c|c|c|} \hline  
&& Number of & Number of & Mean Run Time & Standard \\ 
Method & $\e$ & Iterations & $F$-Evaluations& (Seconds) & Deviation \\ \hline 
\lower.3ex\hbox{EHA2} & \lower.3ex\hbox{$10^{-10}$} & \lower.3ex\hbox{26} &  
\lower.3ex\hbox{32} & \lower.3ex\hbox{47.12} & \lower.3ex\hbox{.1048} \\ 
FD2 & $10^{-10}$ & 26 & 58 & 53.79 & .1829 \\ \hline  
\lower.3ex\hbox{EHA4} & \lower.3ex\hbox{$10^{-12}$} & \lower.3ex\hbox{30} &  
\lower.3ex\hbox{42} & \lower.3ex\hbox{56.76} & \lower.3ex\hbox{.1855} \\  
FD4 & $10^{-12}$ & 30 & 132 & 81.35 & .3730 \\ \hline  
\lower.3ex\hbox{EHA6} & \lower.3ex\hbox{$10^{-12}$} & \lower.3ex\hbox{30} &  
\lower.3ex\hbox{48} & \lower.3ex\hbox{58.56} & \lower.3ex\hbox{.1952} \\ 
FD6 & $10^{-12}$ & 30 & 198 & 100.6 & .3278 \\ \hline  
\end{tabular}
\end{center} 
\label{diffstats} 
\end{table}

In our first set of experiments, we took $c=d=10$ and used right 
preconditioning with a fast Poisson solver from {\fishpack}  
\cite{Swarztrauber-Sweet}, which is very effective for these  
fairly small values of $c$ and $d$. We first started each method 
with zero as the initial approximate solution and allowed it  
to run for 40 {\gmresm} iterations, after which the limit of residual  
norm reduction had been reached. Figure \ref{pdep} shows plots  
of the logarithm of the Euclidean norm of the residual versus  
the number of {\gmresm} iterations for the three methods. We note
that in  Fig.~\ref{pdep} and in all other figures below, the plotted
residual norms were not the values maintained by {\gmresm}, but rather
were computed as accurately as possible ``from scratch.''  That is, 
at each {\gmresm} iteration, the current approximate solution was 
formed and its product with the coefficient matrix was subtracted 
from the right-hand side, all in double precision.  
It was important to compute the residual norms in this way because  
the values maintained by {\gmresm} become increasingly untrustworthy  
as the limits of residual norm reduction are neared; see \cite{Walker88}.  
It is seen in Fig.~\ref{pdep} that Algorithm EHA achieved  
the same ultimate level of residual norm reduction as the FDP  
method and required only a few more {\gmresm} iterations to do
so.

\begin{figure}[t] 
\vspace{3in}
\caption{{\rm Log}$_{10}$ of the residual norm versus the number of 
{\rm GMRES}$(m)$ iterations for $c=d=10$ with fast Poisson
preconditioning. Solid curve: Algorithm {\rm EHA}; dotted 
curve: {\rm FDP} method; dashed curve: {\rm FSP} method.} 
\label{pdep} 
\end{figure}

In our second set of experiments, we took $c=d=100$ and carried out  
trials analogous to those in the first set above. No preconditioning  
was used in these experiments, both because we wanted to compare 
the methods without preconditioning and because the fast  
Poisson preconditioning used in the first set of experiments is 
not cost effective for these large values of $c$ and $d$. We first  
allowed each method to run for 600 {\gmresm} iterations, 
starting with zero as the initial approximate solution, after which  
the limit of residual norm reduction had been reached.

\section*{Acknowledgments}
The author thanks the anonymous authors whose work largely
constitutes this sample file. He also thanks the INFO-TeX mailing
list for the valuable indirect assistance he received.

\begin{thebibliography}{10} 
\bibitem{bs} {\sc R.~A. Brualdi and B.~L. Shader}, 
{\em On sign-nonsingular matrices and the conversion of the
permanent into the determinant}, in Applied Geometry and
Discrete Mathematics, The Victor Klee Festschrift, P.
Gritzmann and B. Sturmfels, eds., American Mathematical
Society, Providence, RI, 1991, pp. 117--134.

\bibitem{djd} {\sc J. Drew, C.~R. Johnson, and P. van den Driessche}, 
{\em Strong forms of nonsingularity}, Linear Algebra Appl.,
162 (1992), to appear.

\bibitem{g} {\sc P.~M. Gibson}, {\em Conversion of the permanent into the 
determinant}, Proc. Amer. Math. Soc., 27 (1971),
pp.~471--476.

\bibitem{klm} 
{\sc V.~Klee, R.~Ladner, and R.~Manber}, {\it
Signsolvability revisited}, Linear Algebra Appl., 59
(1984), pp.~131--157.

\bibitem{m} 
{\sc K. Murota}, LU-{\em decomposition of a matrix with
entries of different kinds}, Linear Algebra Appl., 49
(1983), pp.~275--283.

\bibitem{Axelsson}
{\sc O.~Axelsson}, {\em Conjugate gradient type methods for unsymmetric and
  inconsistent systems of linear equations}, Linear Algebra Appl., 29 (1980),
  pp.~1--16.

\bibitem{Brown-Saad1}
{\sc P.~N. Brown and Y.~Saad}, {\em Hybrid {K}rylov methods for nonlinear
  systems of equations}, SIAM J. Sci. Statist. Comput., 11 (1990), 
  pp.~450--481.

\bibitem{DES}
{\sc R.~S. Dembo, S.~C. Eisenstat, and T.~Steihaug}, {\em Inexact {N}ewton
  methods}, SIAM J. Numer. Anal., 19 (1982), pp.~400--408.

\bibitem{EES}
{\sc S.~C. Eisenstat, H.~C. Elman, and M.~H. Schultz}, {\em Variational
  iterative methods for nonsymmetric systems of linear equations}, SIAM J.
  Numer. Anal., 20 (1983), pp.~345--357.

\bibitem{Elman}
{\sc H.~C. Elman}, {\em Iterative methods for large, sparse, nonsymmetric
  systems of linear equations}, Ph.D. thesis, Department of Computer
  Science, Yale University, New Haven, CT, 1982.

\bibitem{GloKR85}
{\sc R.~Glowinski, H.~B. Keller, and L.~Rheinhart}, {\em Continuation-conjugate
  gradient methods for the least-squares solution of nonlinear boundary value
  problems}, SIAM J. Sci. Statist. Comput., 6 (1985), pp.~793--832.

\bibitem{Golub-VanLoan}
{\sc G.~H. Golub and C.~F. Van~Loan}, {\em Matrix Computations}, 
  Second ed., The Johns  Hopkins University Press, Baltimore, MD,  1989.

\bibitem{More}
{\sc J.~J. Mor\'e}, {\em A collection of nonlinear model problems}, in
  Computational Solutions of Nonlinear Systems of Equations, E.~L. Allgower and
  K.~Georg, eds., Lectures in Applied Mathematics, Vol. 26, American
  Mathematical Society, Providence, RI, 1990, pp.~723--762.

\bibitem{Saad}
{\sc Y.~Saad}, {\em Krylov subspace methods for solving large unsymmetric
  linear systems}, Math. Comp., 37 (1981), pp.~105--126.

\bibitem{Saad-Schultz}
{\sc Y.~Saad and M.~H. Schultz}, {\em {\rm GMRES}: A generalized minimal
  residual method for solving nonsymmetric linear systems}, SIAM J. Sci. Statist.
  Comput., 7 (1986), pp.~856--869.

\bibitem{Swarztrauber-Sweet}
{\sc P.~N. Swarztrauber and R.~A. Sweet}, {\em Efficient {\rm FORTRAN}
  subprograms for the solution of elliptic partial differential equations}, ACM
  Trans. Math. Software, 5 (1979), pp.~352--364.

\bibitem{Walker88}
{\sc H.~F. Walker}, {\em Implementation of the {\rm GMRES} method using
  {H}ouseholder transformations}, SIAM J. Sci. Statist. Comput., 9 (1988),
  pp.~152--163.

\bibitem{Walker89}
\sameauthor, {\em Implementations of
  the {\rm GMRES} method}, Computer Phys. Comm., 53 (1989),  pp.~311--320.

\end{thebibliography}

\end{document}

### 2013-05-15 docs/Jesse/Dissertation/BurgersNotes.tex
adding dissertation and H1DPG paper to repo

--- 2012-06-15 docs/Jesse/Proposal/BurgersNotes.tex
@@
 
-We will illustrate the application of DPG to nonlinear problems using a viscous Burgers' equation on domain $\Omega = [0,1]^2 \in \mathbb{R}^2$
+We will illustrate the application of DPG to nonlinear problems using a viscous Burgers' equation on domain $\Omega = [0,1]^2 \in \mathbb{R}^2$ \cite{MITDPG}
 \[
@@
 \[
-u(x.y) = 1-2x, \quad x = 0, y = 0,
+u(x,y) = 1-2x, \quad x = 0, y = 0,
 \]
@@
 
-We begin by writing the equation in a first order system.  Defining $\beta(u) = \LRp{u/2,1}$, the above Burgers equation can be written as
+We begin by writing the equation as a first order system.  Defining $\beta(u) = \LRp{u/2,1}$, the above Burgers equation can be written as 
 \begin{align*}
@@
 The results of an adaptive simulation are shown in Figure~\ref{fig:BurgersShock} for $\epsilon = 1e-4$.
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=.4]{figs/burgers.png}
+\caption{Shock solution for Burgers' equation with $\epsilon = 10^{-4}$.} 
+\label{fig:BurgersShock}
+\end{figure}
+
+For the solution of Burgers' equation, adaptivity began on a cubic $4\times 4$ mesh.
+9 iterations of adaptive mesh refinement were performed, and the resulting mesh and zoomed solution are displayed in Figure~\ref{fig:BurgersShockZoom}, demonstrating a fully resolved smooth transition of the solution into a smeared shock.
 
@@
 \centering
-\includegraphics[scale=.5]{figs/burgers1e4.png}
-\caption{Shock solution for Burgers' equation with $\epsilon = 10^{-4}$.} 
-\label{fig:BurgersShock}
+\subfigure{\includegraphics[scale=.275]{figs/burgersZoom.png}}
+\subfigure{\includegraphics[scale=.275]{figs/burgersMesh.png}}
+\caption{Adaptive mesh after 9 refinements, and zoom view at point (.5,.5) with shock formation and $1e-3$ width line for reference.}
+\label{fig:BurgersShockZoom}
 \end{figure}
-\todo{Get mesh and zoomed in plot for Burgers' equation.}

### 2013-05-15 docs/Jesse/Dissertation/utdiss2-05/chapter-instructions.tex
adding dissertation and H1DPG paper to repo

\chapter{Instructions for Preparing Dissertations, Theses, and Reports}
\index{Instructions for Preparing Dissertations, Theses, and Reports%
@\emph{Instructions for Preparing Dissertations, Theses, and Reports}}%

We are not going to look at the complete set of instructions contained
in \emph{Instructions for Preparation of Doctoral Dissertations and
Dissertation Abstracts} or \emph{Format For The Master's Thesis and Report}
which can be obtained from the Office of Graduate Studies (OGS)
\index{Office of Graduate Studies}%
or on their web page,
\index{Office of Graduate Studies web page}%
\url{http://www.utexas.edu/ogs}.
The doctoral Instructions I am using are dated March, 2001.
The master's Format I am using is dated May, 2001.

Here we will look at a few instructions related to the arrangement of the
dissertation, thesis, or report and a few other ``technical'' details,
providing some examples of common \LaTeX\ usage and some examples of
not-so-common \LaTeX\ usage.

The following are just a couple of tests for the ``quote''
and ``quotation'' environments. The following paragraph is a quote.
\begin{quote}
\index{quote}%
This template package is provided and licensed
``as is'' without warranty of any kind, either expressed or
implied, including, but not limited to, the implied warranties
of merchantability and fitness for a particular purpose.
\end{quote}
The following paragraph is a quotation.
\begin{quotation}
\index{quotation}%
This template package is provided and licensed
``as is'' without warranty of any kind, either expressed or
implied, including, but not limited to, the implied warranties
of merchantability and fitness for a particular purpose.
\end{quotation}

The OGS Instructions say prose quotations over four lines
should be indented on the left. The Doctoral Degree Evaluator says
the quote environment is the correct one to use.

\section{Arrangement of Dissertation}
\index{Arrangement of Dissertation@\emph{Arrangement of Dissertation}}%

Always remember that this ``fake'' dissertation 
\index{fake dissertation}%
is only intended to be a template for writing your own. Since the ultimate
responsibility of making sure your dissertation meets the Graduate School's
requirements, however, lies only with you, you \textbf{\textit{must}} get
the current \emph{Instructions for Preparation of Doctoral Dissertations and
Dissertation Abstracts} from the Office of Graduate Studies or their web
page and check everything yourself. If you don't, you may have a very
rude awakening from the Lynn Renegar, Doctoral Degree Evaluator (aka,
``The Ruler Lady'') at a most inopportune time.

Arrange your dissertation as follows (all sections are required 
unless said otherwise.

\begin{enumerate}

\item Fly Page 
\index{Fly Page}%
(blank protective page). This page is \textbf{not} counted in the numbering.
\textbf{Note:} This template does not insert a Fly Page; if you are printing
an official copy, you must manually insert a blank piece of paper on your own.
Electronic documents do not need a fly page.

\item Copyright Legend 
\index{Copyright Legend}%
(optional) - See OGS Instructions Sample Form A.
Begin counting \textbf{pretext} pages here, but \textbf{do not
place a number on this page.}

\item Committee Certification of Approved Version.
\index{Committee Certification of Approved Version}%
See OGS Instructions Sample Form B. This page is included in the
pretext count, but there should be no page number on the page.

\item Title Page - 
\index{Title Page}%
See OGS Instructions Sample Form C.
This page is counted, but there should not be a page number on this page.

\item Dedication 
\index{Dedication}%
and/or Epigraph (optional). 
\index{Epigraph}%
Included in count, but not numbered.

\item Acknowledgments
\index{Acknowledgments}%
or Preface 
\index{Preface}%
(optional) - Begin showing \textbf{pretext} page numbers with \textbf{lower
case Roman numerals} at bottom of page.

\item Abstract 
\index{Abstract}%
(optional) - See OGS Instructions Sample Form D.

\item Table of contents -
\index{Table of contents}%
List ALL sections which follow it. There are too may different ways a table
of contents may be done for the OGS to give examples in their Instructions
booklet, but do be sure there is agreement between the major headings in
your text and their designations in the Table of Contents (fortunately \LaTeX{}
does this for you automatically). Please ask the Doctoral Degree Evaluator
for assistance if necessary.

\item List of Tables,
\index{List of Tables}%
List of Figures,
\index{List of figures}%
List of Illustrations, 
\index{List of Illustrations}% 
Nomenclature,
\index{Nomenclature}%
List of Supplemental Files (such as multimedia files)
(optional).

\item Text. 
\index{Text}%
The text should be divided into chapters, books or sections. The first page
is Arabic numeral \textbf{``1''}. All sections, \textbf{from the first page
of text through Vita,} should be numbered consecutively.

\item If you group all Tables, 
\index{Tables}%
Figures, 
\index{Figures}%
or Illustrations 
\index{Illustrations}%
in one place in your dissertation, the section should be placed 
here, immediately after the text and before any appendices 
(optional).

\item Appendix or Appendices 
\index{Appendix}%
\index{Appendices}%
(optional).

\item Glossary 
\index{Glossary}%
(optional) - this section may be placed either here or after the Table
of Contents, in the area with List of Tables, List of Figures...

\item Bibliography
\index{Bibliography}%
- consult your supervisor about which recognized style to use.

\item Index
\index{Index}%
(optional).

\item Vita -
\index{Vita}%
This should be a brief biographical sketch of the author. List in the
Table of Contents. See OGS Instructions Sample Form E.

\end{enumerate}

\section{Other Requirements}
\index{Other Requirements@\emph{Other Requirements}}%

\subsection{Margins}
\index{Margins@\emph{Margins}}%

The dissertation, after printing, should have left and top margins of
1~1/2 inches, and the right and bottom margins should be 1~1/4 inches.
These margins should be consistent throughout the dissertation - including
all pages in the appendix. \textbf{All page numbers must be \textit{at
least} one inch from the edges of the page}. Headers are rarely used in
dissertations; if you are considering using them, check with the Doctoral
Degree Evaluator first to be sure they will be accepted.

\subsection{Spacing and Page Arrangement}
\index{Spacing and Page Arrangement@\emph{Spacing and Page Arrangement}}
\index{Spacing}%
\index{Page Arrangement}%

The document should be double-spaced or space-and-a-half. 
Exceptions to double-spacing are: the Table of Contents, Lists of Tables, 
Tables, Figures, Graphs, Captions, Footnotes, Endnotes, 
Appendices, Glossary, Bibliography and Index; these may 
be single-spaced. Paragraph indentations are usually five to ten 
spaces. Prose quotations over four lines should be in 
block quote (double or single spaced, indented on the left). 
Do not use quotation marks if the quotation is indented except for
quotations within the block quote. Please refer to a style manual for
more detailed instructions.

Be sure that each new chapter or major section (i.e., Appendix, Bibliography,
Vita) begins on a new page.

\section{Master's Theses and Reports}

Always remember that this ``fake'' thesis or report 
\index{fake thesis or report}%
--- assuming you have followed the instructions in the next chapter about
how to format it as such --- is only intended to be a template for writing
your own. Since the ultimate responsibility of making sure your thesis or
report meets the Graduate School's requirements, however, lies only with
you, you \textbf{\textit{must}} get the current \emph{Format For The
Master's Thesis and Report} from the Office of Graduate Studies or their web
page and check everything yourself. If you don't, you may have a very
rude awakening from the Mike Feissli, Master's Degree Evaluator at a most
inopportune time.

That said, the formatting requirements for Dissertations and Reports and
Theses are very similar. They are, however, \textbf{\textit{not}} identical.
The primary differences are in the ordering of the title and signature
pages and where the optional index is inserted. For Master's Theses
and Reports, the Title Page must be in front of the Signature Page. For
Master's Theses and Reports, \textbf{\textit{nothing}} is permitted to
come between the bibliography and the vita; the index, if used, must be
before the bibliography. If you want to use an index, talk with Mike
Feissli before your deadline to verify that its inclusion is
acceptable. The index can be removed by commenting out one line with a
percent sign, if necessary, for producing the ``official'' copy of your
thesis or report, and then inserted for copies for your advisor and
you by removing the percent sign.

### 2013-05-15 docs/Truman/IntroLES/talk.tex
Added intro to LES talk.

\documentclass{beamer}
\input{../preamble.tex}
\usetheme[secheader]{pecostalk}

\author[Truman E. Ellis]{Truman E. Ellis}
\title[Intro to LES]{Introduction to Large Eddy Simulation}
\institute{Institute for Computational and Engineering Sciences\\
The University of Texas at Austin}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}\frametitle{Filtered Navier-Stokes}
For filter kernel $G$,
\[
\overline{u}(x)=\int_\Omega G(x,x')u(x')dx'
\]
Filtering the incompressible Navier-Stokes equations:
\[
\pd{\overline{u_i}}{t}=-\overline{\pd{u_iu_j}{x_j}}-\overline{\pd{p}{x_i}}
+\nu\overline{\pdd{u_i}{x_j}{x_j}}
\]
If $G(x,x')=G(x-x')$, we can commute differentiation and filtering
\[
\pd{\overline{u_i}}{t}=-\pd{\overline{u_iu_j}}{x_j}-\pd{\overline{p}}{x_i}
+\nu\pdd{\overline{u_i}}{x_j}{x_j}
\]
Identify ``sub-grid stress'' analogous to Reynolds stress,
\[
\tau_{ij}=\overline{u_iu_j}-\bar{u_i}\bar{u_j}
\]
\end{frame}

\begin{frame}\frametitle{Common Filters}
Explicit Filters:
\begin{itemize}
\item Fourier cut-off filter
\[
\hat G(k) = \begin{cases}
1 & |k| < k_c \\
0 & |k| > k_c \\
\end{cases}
\]
Filter width $\Delta=\pi/k_c$.
\item Top-hat filter
\[
G(x) = \begin{cases}
1/\Delta & |x| < \Delta/2\\
0 & |x| > \Delta/2
\end{cases}
\]
\item Gaussian filter
\[
G(x)=\frac{e^{-x^2/2\Delta^2}}{\Delta\sqrt{2\pi}}
\]
\end{itemize}
Implicit Filters:
\begin{itemize}
\item The numerical method is the filter -- very common, but suspect
\item Define your filter as some projection of the Navier-Stokes solution onto
some finite dimensional function space
\end{itemize}
\end{frame}

\begin{frame}\frametitle{The Closure Problem}
\begin{block}{Filtered Navier-Stokes}
\[
\pd{\overline{u_i}}{t}+\pd{\bar{u_i}\bar{u_j}}{x_j}=-\pd{\overline{p}}{x_i}
+\nu\pdd{\overline{u_i}}{x_j}{x_j}-\pd{\tau_{ij}}{x_j}
\]
\end{block}
\begin{columns}[c]
\begin{column}{0.6\textwidth}
\begin{itemize}
\item Smaller scales can be modeled as isotropic homogeneous
\item Homogeneous isotropic turbulence is \textbf{much} easier to model
\item Primarily need to capture energy cascade effect with extra dissipation
\item Smagorinsky model
\[
\tau_{ij}=-(C_s\Delta)^2(2\overline{S}_{lm}\overline{S}_{lm})^{1/2}\overline{S}_{ij}
+\frac{1}{3}\tau_{kk}\delta_{ij}
\]
\end{itemize}
\end{column}
\begin{column}{0.4\textwidth}
\begin{figure}[t]
	\begin{center}
		\includegraphics[width=\textwidth]{spectrum.png}
	\end{center}
\end{figure}
\end{column}
\end{columns}
\end{frame}

\begin{frame}\frametitle{The Dynamic Model}
Let $C=\sqrt{2}C_s^2$, then Germano's identity gives a process by which to
solve for $C$. Least squares solution gives
\[
C=\frac{\mathcal{L}_{ij}M_{ij}}{M_{kl}M_{kl}}
\]
where 
\[
M_{ij}=\Delta^2\LRp{\widetilde{|\overline{S}|\overline{S}_{ij}}-\alpha^2|\tilde{\overline S}|\tilde{\overline S}_{ij}}
\]
This fixed several longstanding issues with LES
\begin{itemize}
\item Adjustable constants are eliminated.
\item The model turns off (i.e. $C=0$) in well resolved or laminar regions.
\item The need for damping near the wall is eliminated.
\end{itemize}
\end{frame}

\begin{frame}\frametitle{Outstanding Problems -- Wall Modeling}
Near the wall, the ``large'' dynamicly important scales of turbulence are
actually quite small. Thus, to resolve the large scales, the LES must resolve
these small structures, and these structures get smaller relative to the
thickness of the shear layer as the Reynolds number increases. This makes LES
increasingly expensive with increasing Reynolds number. Wall modeling
techniques that do not require the near-wall structures to be resolved are
needed if LES is to be useful at high Reynolds number.
\end{frame}

\begin{frame}\frametitle{Outstanding Problems -- Numerical Errors}
It is common practice in LES for the filter width $\Delta$ to be the grid size
in the numerical simulation. The dynamic procedure uses the behavior of scales
between $\alpha\Delta$ and $\Delta$ is size to set the constants, but these
scales near the grid size have large numerical errors. Thus, the dynamic model
is working on data that is polluted by numerical errors. In fact, Ghosal
showed that even with high order numerical methods, the numerical truncation
errors can be much larger than the subgrid terms. There are three possible
solutions to this problem:
\begin{itemize}
\item Make $\Delta$ much larger than the grid size (expensive).
\item Use exceptionally accurate numerics, i.e. spectral methods (not
generally applicable).
\item Account for the numerical error in the formulation of the LES models (no
one knows how to do this).
\end{itemize}
\end{frame}

\begin{frame}\frametitle{Outstanding Problems -- Embedded laminar features}
In some flows, not everything is turbulent, and the features of the laminar
flow can be too small to resolve. Good examples of this are the separation
shear layers in the cross flow past a circular cylinder. These laminar
features cannot be resolved, but the models are not valid for them either.
\end{frame}

\begin{frame}\frametitle{Outstanding Problems -- What did you compute?}
In an LES, one does not compute the velocity field, rather one computes a
filtered velocity, and therefore one needs to be careful in interpreting the
results. For example, if one is interested in the statistical quantity
$\langle u^2\rangle$, one cannot determine this exactly from the LES. In the
LES, one can only determine $\LRa{\overline{u}^2}\neq\LRa{u^2}$, unless the
energy in the subgrid turbulence is negligible. In general one can expect to
estimate such statistical quantities as $\LRa{u_i(x+r)u_j(x)}$ accurately
provided $|r|\gg\Delta$. However, since the vorticity is strictly a
small-scale quantity (the subgrid contribution to enstrophy is not small), one
cannot expect to reproduce vorticity statistics in an LES.
\end{frame}

\begin{frame}\frametitle{Outstanding Problems -- Commutation Error}
Filters that are used in actual LES simulations are not generally homogeneous,
that is $G(x,x')\neq G(x-x')$, so that filtering no longer commutes with
differentiation. Then, most significantly,
\[
\overline{\pd{u_iu_j}{x_j}}\neq\pd{\overline{u_iu_j}}{x_j}\,,
\]
and the difference between these two terms is generally called the commutation
error. This commutation error plays an important role in the equations.
Suppose that a flow domain is divided into two regions, one in which the
filter scale $\Delta$ is larger than in the other region. If trubulence passes
from the small filter scale region to the large, then not all the scales of
the turbulence that could be represented in the finer region can be
represented in the coarser region. Therefore, some of the smaller scales must
be removed as the turbulence passes from one region to the other. When
turbulence is passing the the opposite direction, scales that were not
represented become representable, and must be added to the LES solution. 
\end{frame}

\begin{frame}\frametitle{Variational Multiscale LES}
\begin{itemize}
\item Use variational projections in place of the traditional filtered
equations
\item Focus on modeling the fine-scale equations
\item Avoids filters eliminates:
\begin{itemize}
\item Inhomogeneous non-commutative filters necessary for wall-bounded flows
\item Use of complex filtered quantities in compressible flows
\end{itemize}
\item Retains numerical consistency in the coarse-scale equations permitting
full rate-of-convergence
\item Newer approaches attempt to capture all scales consistently and to avoid use of eddy
viscosities altogether
\end{itemize}
\end{frame}

\end{document}

### 2013-05-15 docs/Jesse/Dissertation/DPGintro.tex

--- 2012-06-19 docs/Jesse/Proposal/proposalIntro.tex
@@
 
-Over the last three decades, Computational Fluid Dynamics (CFD) simulations have become commonplace as a tool in the engineering and design of high-speed aircraft.
-Wind tunnel experiments are often complemented by computational simulations, and CFD technologies have proved very useful in both the reduction of aircraft development cycles, and in the simulation of conditions difficult to reproduce experimentally.
-Great advances have been made in the field since its introduction, especially in areas of meshing, computer architecture, and solution strategies.
-Despite this, there still exist many computational limitations in existing CFD methods:
-\begin{itemize}
-\item \textbf{Higher order methods :} Higher order methods stand to offer large computational savings through a more efficient use of discrete degrees of freedom.
-However, there are very few working higher-order CFD codes in existence, and most higher order methods tend to degrade to first-order accuracy near shocks.
-The use of higher order codes to solve the steady state equations is even rarer, where convergence of discrete nonlinear steady equations is a tricky issue \cite{BoeingHigherOrder}.
-\item \textbf{Automatic adaptivity :} The use of adaptive meshes is crucial to many CFD applications, where the solution often exhibits very localized sharp gradients and shocks.
-Good resolution for such problems under uniform meshes is computationally prohibitive and impractical for most physical regimes of interest.
-However, the construction of ``good" meshes is a difficult task, usually requiring a-priori knowledge of the form of the solution \cite{andersonCFDBook}.
-An alternative to such is the construction of automatically adaptive schemes; such methods usually begin with a coarse mesh and refine based on the minimization of some error.
-However, this task is difficult, as the convergence of numerical methods for problems in CFD is notoriously sensitive to mesh quality.
-Additionally, the use of adaptivity becomes even more difficult in the context of higher order and $hp$ methods \cite{BoeingHigherOrder}.
-\end{itemize}
-Both of these issues are tied to the notion of \emph{robustness}.
-We define robustness loosely as the degradation of the quality of numerical solutions with respect to a given problem parameter.
-In the context of CFD, the parameter of interest is the Reynolds number (the nondimensional equivalent of viscosity) --- for typical physical conditions of interest for the compressible Navier-Stokes equations, the Reynolds number is extremely high, on the order of 1e7, yielding solutions with two vastly different scales - inviscid phenomena at an $O(1)$ scale, and $O(1e-7)$ viscous phenomena.
-
-The full Navier-Stokes equations are not well understood in a mathematical sense --- in order to more clearly illustrate the issue of robustness for problems in CFD, we will study first the important model problem of convection-dominated diffusion.
+Higher order adaptivity and stability for CFD problems are issues for high Reynolds and Mach numbers. 
+\todo{Address the fact that CFD problems have issues of robustness; introduce reasoning that we will study the model problem of convection-diffusion first to better understand this. }
 
@@
 
-%Historically, the Galerkin method has been very successfully applied to a broad range of problems in solid mechanics, for which the variational problems resulting from the PDE are symmetric and coercive (positive-definite).
+Historically, the Galerkin method has been very successfully applied to a broad range of problems in solid mechanics, for which the variational problems resulting from the PDE are symmetric and coercive (positive-definite).
 It is well known that the finite element method produces optimal or near-optimal results for such problems, with the finite element solution matching or coming close to the best approximation of the solution in the finite element space.
-However,
-
-Standard numerical methods tend to perform poorly across the board for the class of PDEs known as singular perturbation problems.
+However, standard Bubnov-Galerkin methods tend to perform poorly for the class of PDEs known as singular perturbation problems.
 These problems are often characterized by a parameter that may be either very small or very large in the context of physical problems.
 An additional complication of singular perturbation problems is that very often, in the limiting case of the parameter blowing up or decreasing to zero, the PDE itself will change types (e.g.\ from elliptic to hyperbolic).
+
 A canonical example of a singularly perturbed problem is the convection-diffusion equation on domain $\Omega \in \mathbb{R}^3$,
@@
 \includegraphics[scale=.4]{figs/GalerkinOscTight.png}
-\caption{Oscillations in the 1D finite element solution of the convection-diffusion equation for small diffusion \cite{GalerkinOsc}.
-Standard finite volume and finite difference methods exhibit similar behavior.}
+\caption{Oscillations in the 1D finite element solution of the convection-diffusion equation for small diffusion.}
 \label{fig:GalerkinOsc}
 \end{figure}
-We consider for now the Galerkin finite element method as applied to convection-dominated diffusion.
-Standard finite element methods (as well as standard finite volume and finite difference methods) perform poorly for the case of small $\epsilon$.
+
 The poor performance of the finite element method for this problem is reflected in the bound on the error in the finite element solution --- under the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}:
@@
 where $C(\epsilon)$ grows as $\epsilon\rightarrow 0$.
-The dependence of the constant $C$ on $\epsilon$ is what we refer to as a \textit{loss of robustness} --- as the singular perturbation parameter $\epsilon$ decreases, our finite element error is bounded more and more loosely by the best approximation error.
+The dependence of the constant $C$ on $\epsilon$ is referred to as a \textit{loss of robustness} --- as the singular perturbation parameter $\epsilon$ decreases, our finite element error is bounded more and more loosely by the best approximation error.
 As a consequence, the finite element solution can diverge significantly from the best finite element approximation of the solution for very small values of $\epsilon$.
-For exam ple, Figure~\ref{fig:GalerkinOsc} shows an example of how, on a coarse mesh, and for small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation with a boundary layer develops spurious oscillations everywhere in the domain, even where the best approximation error is small.
+For example, Figure~\ref{fig:GalerkinOsc} shows an example of how, on a coarse mesh, and for small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation with a boundary layer develops spurious oscillations everywhere in the domain, even where the best approximation error is small.
 These oscillations grow in magnitude as $\epsilon \rightarrow 0$, eventually polluting the entire solution.
@@
 
-From the perspective of the full Navier-Stokes equations, this loss of robustness is doubly problematic.
-Not only will any nonlinear solution suffer from similar non-physical oscillations, but nonlinear solvers themselves may fail to yield a solution due to such instabilities --- a nonlinear solution is almost always computed by solving a series of linear problems whose solutions will converge to the nonlinear solution under appropriate assumptions, and the presence of such oscillations in each linear problem can cause the solution convergence to slow significantly or even diverge.
-
-Our goal is to develop a \emph{stable, higher order adaptive scheme} for the steady compressible laminar Navier-Stokes equations in transonic/supersonic regimes that is \emph{robust for very small viscosity}.
-In particular, we hope to present a method for which $hp$-adaptivity can be applied to problems in compressible flow.
+To develop a robust, stable $hp$-adaptive scheme for the steady compressible laminar Navier-Stokes equations in transonic/supersonic regimes.
+\todo{FINISH}
 
@@
 
-For the past half-century, problems in CFD have been solved using a multitude of methods, many of which are physically motivated, and thus applicable only to a small number of problems and geometries.
+For the past half-century, problems in computational fluid dynamics (CFD) have been solved using a multitude of methods, many of which are physically motivated, and thus applicable only to a small number of problems and geometries.
 We consider more general methods, whose framework is applicable to different problems in CFD; however, our specific focus will be on the nonlinear shock problems of compressible aerodynamics.
@@
 
-Historically, the Galerkin method has been very successfully applied to a broad range of problems in solid mechanics, for which the variational problems resulting from the PDE are symmetric and coercive (positive-definite).
-It is well known that the finite element method produces optimal or near-optimal results for such problems, with the finite element solution matching or coming close to the best approximation of the solution in the finite element space.
-However, standard Galerkin methods tend to perform poorly for singular perturbation problems, developing instabilities when the singular perturbation parameter is very small.
-
 Traditionally, instability/loss of robustness in finite element methods has been dealt with using residual-based stabilization techniques.
@@
 
-All Galerkin methods involve both trial (approximating) and test (weighting) functions.
-Standard Galerkin methods, where these trial and test functions are taken from the same space, are referred to as Bubnov-Galerkin methods.
-A Petrov-Galerkin method refers to any Galerkin method other than a classical Bubnov-Galerkin method.
 The Streamline Upwind Petrov Galerkin (SUPG) method is a stabilization method for $H^1$-conforming finite elements, the idea of which was originally motivated by artificial diffusion techniques in finite differences.
@@
 In particular, finite element and Galerkin methods are often referred to as ``weighted residual" methods, since the starting point of both is to multiply the residual by a particular test, or weighting, function.
-Standard Bubnov-Galerkin methods simply choose these weighting functions to be the same as the the basis functions used to approximate the solution.
+Standard Galerkin methods, known as Bubnov-Galerkin methods, simply choose these weighting functions to be the same as the the basis functions used to approximate the solution.
+A Petrov-Galerkin method refers to any Galerkin method other than a classical Bubnov-Galerkin method.
 
@@
 An additional reason for the popularity of DG methods is that they can be interpreted as stabilized FE methods through appropriate choices of this numerical flux \cite{Brezzi20063293}.
-We will illustrate this with the steady convection equation in 1D ---
+We will illustrate this with the pure convection equation in 1D ---
 \begin{align*}
-\pd{\left(\beta(x) u\right)}{x} = f, \quad u(0) &= u_0.
+\pd{\left(\beta u\right)}{x} &= f\\
+u(0) &= u_0.
 \end{align*}
@@
 This specific choice of $v(x_K)$ as the upwind value is crucial; similarly to SUPG, the upwind DG emphasizes the test function in the direction of convection and changes the way the residual is measured.
-As it turns out, the performance of DG for convection-type problems is closely tied to this upwinding --- choosing the value of $v(x_K)$ to be the downwind value $v(x_K^-)$ leads to an unstable method, while choosing $v(x_K)$ to be the average of the upwind and downwind values leads to a DG method with suboptimal stability properties, similar to an $H^1$-conforming continuous Galerkin approximation\cite{Brezzi20063293}.\footnote{For second-order convection-diffusion problems with small diffusion, the additional regularity imparted by choice of the DG numerical flux is often insufficient, and SUPG-type stabilization is also applied.}
+As it turns out, the performance of DG for convection-type problems is closely tied to this upwinding --- choosing the value of $v(x_K)$ to be the downwind value $v(x_K^-)$ leads to an unstable method, while choosing $v(x_K)$ to be the average of the upwind and downwind values leads to a DG method with suboptimal stability properties, similar to an $H^1$-conforming continuous Galerkin approximation\cite{Brezzi20063293}.
 
@@
 A more recent development in DG methods is the idea of \emph{hybridized} DG (HDG), introduced by Gopalakrishnan and Lazarov \cite{hybridDG}.
-The hybridized DG framework identifies degrees of freedom with support only on element edges, which can be interpreted as Lagrange multipliers enforcing weak continuity of the trial space.
-HDG methods treat numerical \emph{traces} and numerical \emph{fluxes} differently depending on the form of the boundary term resulting from integration by parts.
-The numerical trace (the result of integrating by parts the gradient) in HDG methods is chosen to be an unknown, while the numerical flux (the result of integrating by parts the divergence) is chosen to be an appropriate function of both function values on neighboring elements and the numerical trace.
+The hybridized DG framework addresses several criticisms of common DG methods (globally coupled degrees of freedom, complicated/inefficient implementation procedures, suboptimal convergence of approximate fluxes) by identifying degrees of freedom with support only on element edges.
+Neighboring elements are coupled together only through these degrees of freedom, which can be interpreted as Lagrange multipliers enforcing weak continuity of the trial space.
+Additionally, HDG methods \todo{add bit about numerical fluxes still used, stabilization params}
 
-By a careful choice of the numerical flux, the global HDG formulation can be reduced to a single equation involving only the numerical trace degrees of freedom, referred to as the \emph{global} problem.
-Once the global problem is solved, interior degrees of freedom can be recovered in parallel through so-called \emph{local} problems \cite{HDGprojection}.
+\subsubsection{Optimization/NL solvers}
 
-HDG methods are an active topic of current research, since they address several criticisms of common DG methods (large number of degrees of freedom, globally coupled degrees of freedom, complicated/inefficient implementation procedures, suboptimal convergence of approximate fluxes).
-Note that HDG methods still fall under the category of stabilized methods --- stabilization techniques are employed through the choice of the HDG numerical flux, which involves some stabilization parameter $\tau$.
+Reference (MIT, Fidkowski)
+
+\todo{Find more nonlinear solvers}
 
@@
 
-This PhD thesis proposal will proceed in four main parts:
+This proposal will
 \begin{enumerate}
-\item Introduce the abstract DPG method as a minimum residual method for linear problems.
-\item Formulate a DPG method addressing the issue of robustness for the model problem of convection-dominated diffusion.
-\item Apply the DPG method to singularly perturbed nonlinear problems in CFD, discussing preliminary results for the Burgers and compressible Navier-Stokes equations. 
-\item Introduce completed and proposed work in concentration areas A, B, and C. 
+\item Introduce DPG
+\item Cover the problem of robustness for model problems
+\item Extend results/formulations to nonlinear problems
+\item Discuss proposed work
 \end{enumerate}

### 2013-05-15 docs/Jesse/Dissertation/NonlinDPG.tex

--- 2012-06-26 docs/Jesse/Proposal/NonlinDPG.tex
@@
 \begin{align*}
-\|\Delta u\|_E \coloneqq &= \nor{B_u\Delta u}_{V'} = \nor{R_V^{-1} B_u\Delta u}_V = \sup_{v\in V} \frac{b_u(\Delta u,v)}{\nor{v}_V}\\
-\nor{R(u)}_E \coloneqq &= \nor{B(u)-l}_E = \nor{B(u) - l}_{V'}  = \nor{R_V^{-1} B(u)-l}_V = \sup_{v\in V} \frac{b(u,v)-l(v)}{\nor{v}_V}
+\|\Delta u\|_E \coloneqq & \nor{B_u\Delta u}_{V'} = \nor{R_V^{-1} B_u\Delta u}_V = \sup_{v\in V} \frac{b_u(\Delta u,v)}{\nor{v}_V}\\
+\nor{R(u)}_E \coloneqq & \nor{B(u)-l}_E = \nor{B(u) - l}_{V'}  = \nor{R_V^{-1} B(u)-l}_V = \sup_{v\in V} \frac{b(u,v)-l(v)}{\nor{v}_V}
 \end{align*}
@@
 
-We note that we have not implemented this Hessian-based nonlinear solver in the numerical experiments to follow, and instead plan to do so in the proposed work outlined in Section~\secref{sec:proposedWork}.
+We note that we have not implemented this Hessian-based nonlinear solver in the numerical experiments to follow, and instead plan to do so in future work.

### 2013-05-15 docs/Jesse/Dissertation/hyperbolicDPG.tex

\chapter{DPG and hyperbolic systems}

It is well-known that solutions to the pure convection equation
\[
\div \LRp{\beta u} = f
\]
are continuous in the distributional sense \emph{only along the streamline $\beta$}. As a consequence, several common physical phenomena that are commonly modeled using the convection equation are ill-posed, mathematically speaking.

\section{Convection}
\seclab{sec:convDPG}

A common test problem with convection codes is $\beta = (-y,x)^T$, or the vortex problem described by Figure~\ref{fig:convCirc}. A rotating streamline convects material in a circular manner from the inflow boundaries around a square domain. However, along any \emph{closed loop} streamline, the solution is undefined, as there is no

\begin{figure}[!h]
\centering
\includegraphics[scale = .25]{figs/convCirc.png}
\caption{Setup for the vortex problem.}
\label{fig:convCirc}
\end{figure}

\begin{figure}[!h]
\centering
\subfigure[Solution]{\includegraphics[scale = .35]{figs/vortex.png}}
\subfigure[Mesh]{\includegraphics[scale = .35]{figs/vortexMesh.png}}
\caption{Regularized solution and mesh for the vortex problem.}
\label{fig:convCircResults}
\end{figure}

\subsection{Ill-posedness of fluxes}

Another issue with the discrete ultra-weak formulation is the ill-posedness of the fluxes on the mesh skeleton. Recall that the DPG formulation for convection is
\[
b(u,v) = \LRa{\widehat{f}_n, v} - \LRp{u,\beta\cdot \grad v} = \LRp{f,v}
\]
where $\widehat{f}_n$ represents the quantity $\beta_n u$. Since there is no small parameter $\epsilon$, as with convection-diffusion, we can use the quasi-optimal test norm 
\[
\nor{v}_V = \nor{\beta\cdot \grad v} + \nor{v}
\]
without worrying about approximability of test functions under this test norm.

However, in directions orthogonal to the streamline, $\beta_n = 0$. Under the quasi-optimal test norm, there is no trace defined in the crossstream direction --- in other words, the flux $\widehat{f}_n$ is undefined on element edges such that $\beta_n = 0$.

In numerical experiments, we took $\beta = (1,0)$, with a uniform mesh on $\Omega = [0,1]^2$. We took an inflow condition $u_0$ such that the best approximation error in the trial space was zero. The result of the ill-posedness of the ultra-weak formulation was that the error in the fluxes was $O(1e-8)$, whereas the error in the fluxes for exactly representable solutions to well-posed problems has typically been $O(1e-12)$ to $O(1e-14)$.

\section{Linearized Euler}
\seclab{sec:eulerDPG}
The effect of the ill-posedness of fluxes can be seen more clearly for systems of hyperbolic equations. We take the linearized Euler equations as an example to illustrate such effects.

The homogeneous Euler equations can be written in the form
\[
F_i(U)_{,i} = 0.
\]
Linearizing around constant $U_i$, $k = \ldots 4$, we arrive at the linearized Euler equations 
\[
\left(A_i(U)\Delta U\right)_{,i} = 0
\]
where $A_i(U)$ are the Euler Jacobian matrices. The exact solution to the above linearized Euler equations is illustrated in Figure~\ref{fig:linEulerExact}. \todo{explain why its exact sol}

\begin{figure}[!h]
\centering
\includegraphics[scale = .5]{figs/linEulerExact.pdf}
\caption{Exact solution to linearized Euler for constant background flow.}
\label{fig:linEulerExact}
\end{figure}

In index notation, the linearized Euler equations can be written as
\[
\left(A_{i}(U)_{jk}\Delta U_k\right)_{,i} = 0
\]
Then, for test functions $V_j$, $j = 1,\ldots, 4$, the DPG formulation for the linearized Euler equations is 
\[
b(U,V) = \LRa{\widehat{f}_{j,n}, V_j} - \LRp{U_k,A_{i}(U)_{jk} V_{j,i}} = \LRp{f,v}
\]
where $f_{j,n}$ represents the quantity $A_n u_k$, where $A_n(U) = A_i(U)_{jk}n_i$ is the normal Euler Jacobian.

It is well-known that the normal Euler Jacobian\todo{finish}

\begin{figure}[!h]
\centering
\includegraphics[scale = .5]{figs/sonicLines.pdf}
\caption{Sonic lines in the solution of the linearized Euler equations.}
\label{fig:linEulerResults}
\end{figure}

### 2013-05-15 docs/Jesse/Dissertation/problemRange.tex

--- 2012-06-25 docs/Jesse/Proposal/problemRange.tex
@@
 For simplicity, we present them in two spatial dimensions.
-Each equation of the Navier-Stokes system represents the conservation of some physical quantity in the behavior of a fluid inside a general control volume.\footnote{The derivation of the compressible Navier-Stokes equations is a standard result of the Reynolds transport theorem, and can be found in many elementary fluid dynamics books.}
+Each equation of the Navier-Stokes system represents the conservation of some physical quantity in the behavior of a fluid inside a general control volume.\footnote{The derivation of the compressible Navier-Stokes equations is a standard result of the Reynolds transport theorem, and can be found in many elementary fluid dynamics books.
+See \cite{Emanuel:994127} for one example.}
 
+In 2D, the classical form of the Navier-Stokes equations involve the fluid density $\rho$, velocity in the $x$ and $y$ directions $u$ and $v$ (or $u_1$ and $u_2$), respectively, temperature $T$, energy per unit mass $e$, and stress and heat flux vectors $\boldsymbol \sigma_i$ and $\vec{q}$.
+The equations are as follows:
 \begin{itemize}
@@
 \end{align*}
-The coefficients $\lambda$ and $\mu$ are known as the viscosity and bulk viscosity, respectively.
+The coefficients $\lambda$ and $\mu$ are the viscosity and bulk viscosity, respectively.
 The bulk viscosity is often set implicitly through $2\mu + 3\lambda = 0$, known as Stokes' hypothesis.
@@
 \end{align*}
-where $\kappa$ is generally a function of temperature.
+where $\kappa$, the coefficient of heat conductivity, is generally a function of temperature.
 
@@
 
-Under appropriate assumptions on the behavior of density and temperature, the behavior of the compressible Navier-Stokes equations can be sufficiently represented by the incompressible Navier-Stokes equations for low speed laminar fluid flows.
+Under appropriate assumptions on the behavior of density and temperature, the behavior of the compressible Navier-Stokes equations can be sufficiently represented by the incompressible Navier-Stokes equations for some fluid flows.
+For example, the incompressible Navier-Stokes equations accurately model nearly incompressible mediums such as water, as well as low Mach number flows of compressible fluids.
 The study of the incompressible Navier-Stokes equations is an open area in mathematics, and is one of the most famous Millenium Problems posed by the Clay Mathematics Institute.
@@
 The linearized Navier-Stokes equations are the result of small perturbation assumptions applied to the full Navier-Stokes equations.
-Under such assumptions, the flow is largely uniform, with slight variations that are small compared to the uniform stream velocity.
+Under such assumptions, the flow in a domain consists only of slight variations (to a given background flow) that are small compared to the magnitude of the free stream velocity.
+Mathematically speaking, the linearized Navier-Stokes equations are the results of the linearization of the full equations with respect to a specific background flow.
+The linearized NS equations are frequently referred to as an ``acoustic problem'', as they are used to study sound propagation.
+
 We are interested in the linearized Navier-Stokes equations mainly for mathematical purposes - as the solution to the full Navier-Stokes equations involves a series of solutions for linearized Navier-Stokes, we wish to investigate the behavior of our numerical method with respect to this system.
@@
 
-The scalar convection-diffusion equation models mathematically the distribution of the concentration $u$ of a substance in a medium due to both convective and diffusive effects.
-The general form of the equation in $\mathbb{R}^n$ is
-\[
-\beta\cdot \grad u - \epsilon \Delta u = f,
-\]
-where $\beta \in \mathbb{R}^n$ is a vector specifying the direction of convection.
-
+Recall that the scalar convection-diffusion equation models mathematically the distribution of the concentration $u$ of a substance in a medium due to both convective and diffusive effects. 
+%The general form of the equation in $\mathbb{R}^n$ is 
+%\[
+%\beta\cdot \grad u - \epsilon \Delta u = f,
+%\]
+%where $\beta \in \mathbb{R}^n$ is a vector specifying the direction of convection.
 Scalar convection-diffusion has significant historical importance, as it is the prototypical model problem for solving the full Navier-Stokes equations --- most stabilized methods consider first the scalar convection-diffusion equation as a test case before attempting a solution of the full Navier-Stokes equations.
@@
 The pure convection equation is a result of neglecting the viscous term in the convection-diffusion equation.
-Physically speaking, these assumptions correspond to the inviscid limit, as well as a particular class of boundary conditions (for example, the wall boundary condition $u = 0$ and prescribed inflow condition may be incompatible in the inviscid limit).
+Physically speaking, these assumptions correspond to the inviscid limit, as well as a particular class of boundary conditions (for example, a prescribed inflow condition may be incompatible with the wall boundary condition $u = 0$ in the inviscid limit).
 The Euler equations are likewise a result of neglecting the viscous terms in the Navier-Stokes equations.
@@
 \end{figure}
-Formally speaking, the solution to the vortex problem is taken to be the solution to the convection-diffusion equation (with appropriate outflow boundary conditions) as the viscosity tends towards zero, in which case, the solution in the interior would be uniformly zero.
+Formally speaking, the solution to the vortex problem is taken to be the solution to the convection-diffusion equation (with appropriate outflow boundary conditions) as the viscosity tends towards zero, in which case, the solution in the interior would be uniformly zero (this technique is referred to in mathematical literature as the ``vanishing viscosity" method, and is used to define unique solutions in the inviscid limit).
 This motivates the need for \emph{artificial viscosity} methods with which to regularize inviscid solutions.
@@
 
-There is still much interest in solving the inviscid Euler equations in industry --- the full Navier-Stokes models often prove difficult to solve due to the mathematical nature of the equations, and the coupling of the Euler equations with boundary layer models has been successful in simulating many phenomena in compressible flow \cite{BoeingDrela}.
+The full Navier-Stokes models have proven difficult to solve due to the mathematical nature of the equations --- due to the lack of robustness of most methods, solving the Navier-Stokes for high Reynolds numbers requires very fine meshes and is an incredibly expensive task.
+Additionally, the problem of turbulence for high Reynolds numbers further complicates the Navier-Stokes solutions for high speed compressible flow.
+Without turbulence models, turbulent effects can prevent convergence to a solution.
+However, common turbulence models, such as Reynolds Averaged Navier-Stokes (RANS), can lead to nonphysical solutions, such as the existence of a steady-state solution when there is none.
+
+In comparison, the coupling of the inviscid Euler equations with boundary layer models has been successful in simulating many phenomena in compressible flow at a computational cost orders of magnitude below that of the full Navier-Stokes equations \cite{BoeingDrela}.
+The method has been extended to a wide array of physical conditions, and is an active area of current research in both industry and academia.

### 2013-05-15 docs/Jesse/Dissertation/utdiss2-05/chapter-introduction.tex

\chapter{Introduction}
\index{Introduction@\emph{Introduction}}%

This document deals with how to write a doctoral dissertation 
using \LaTeX{}, and how to use the \texttt{utdiss2} package. 
\index{utdiss2 package@{\texttt{utdiss2} package}}%

The latest version of this document/package can be obtained from
\url{http://www.ph.utexas.edu/~laser/craigs_stuff/LaTeX/}.\footnote{I
will be transferring this page to the Office of Graduate
Studies when I graduate. The new URL isn't defined yet, but I will
place a ``redirect'' at this URL to send your browser to the correct
location when the transition occurs.}
If your installation of LaTeX is missing any style files used in this
document (most likely with a \cn{usepackage\{package-name.sty\}}
command at the beginning of disstemplate.tex), take a look at the link
on this page to ``Frequently Requested Style Files'' or on the
Comprehensive TeX Archive Network, \url{http://www.ctan.org}.

In case of any confict between the requirements of the Office of Graduate
Studies and what this document says to do, the requirements of the Office
of Graduate Studies prevail.

\section{History of This Package}
\index{History of This Package@\emph{History of This Package}}%

In 1991 the \texttt{utdiss} package was written by Young U. Ryu 
\index{Young U. Ryu}%
in order to be used in the preamble of \LaTeX{} doctoral dissertation
files at the University of Texas at Austin. 
\index{University of Texas at Austin}%
Since then some changes have occured, the most important one
being the introduction of a new version of \LaTeX{} 
\index{LaTeX@{\LaTeX{}}}%
called \LaTeXe{}. 
\index{LaTeX2e@{\LaTeXe{}}}%

In order to partially adapt the utdiss package to this new version
of \LaTeX{}, Miguel Lerma introduced a few modifications in it,
and his document, \textit{How to Write a Doctoral Dissertation
with \LaTeX{}}, served as a test for it. His new package was
called \texttt{utdiss1}.
\index{utdiss1@\texttt{utdiss1}}%

With the significant changes in style introduced by the Graduate
School in the Spring of 2001, as well as  my need to write a
dissertation myself, I extended Miguel Lerma's package to meet
these new requirements. As in Miguel Lerma's case, this document
serves as a test for it, but it is, in addition, intended as a
template for others to use in writing their own dissertations.
The new package is called \texttt{utdiss2}.
\index{utdiss2@\texttt{utdiss2}}%

\section{Revised Philosophy for This Package}
\index{Revised Philosophy for This Package@\emph{Revised Philosophy
	for This Package}}%

Since the source file of this document is intended to be used by students
writing their own dissertations, this document does not display all of the
comments regarding usage of previous versions. It has, instead, transferred
these comments to their respective places in the source file so someone
editing their own copy of the source file to produce their own dissertation
will see the comments where they are needed. It may be helpful to print out
a copy of the source file along with the PostScript version of the document
so the two can be studied side-by-side.

\textbf{Note:} In spite of the effort to accommodate the package to
the requirements of the University, it is not possible to guarantee
that it will always work, and the author of the dissertation remains
responsible for checking that such requirements are actually fulfilled
by his/her final work.

The standard caveat applies:

\begin{quote}
\index{guarantee}%
This template package is provided and licensed ``as is'' without warranty
of any kind, either expressed or implied, including, but not limited to,
the implied warranties of merchantability and fitness for a particular
purpose. Yadda, yadda, yadda, \ldots
\end{quote}

In case of any problem with the use of \texttt{utdiss2}, send me email
at \url{mccluskey@mail.utexas.edu}.

### 2013-05-17 docs/Jesse/Confusion Notes/H1DPG.tex

%&pdflatex
\documentclass[final,leqno]{siamltex}
%\documentclass[10pt,onecolumn]{article}
\usepackage[top=2cm,bottom=3cm,left=3.5cm,right=3.5cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsfonts,mathrsfs}
\let\proof\relax 
\let\endproof\relax
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amscd}
\usepackage{listings}
\usepackage{array}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage[textsize=footnotesize,color=green]{todonotes}
\usepackage{algorithm, algorithmic}
\usepackage{array}
\usepackage{bm}
\usepackage{tikz}
\usepackage{subfigure}
\usepackage[normalem]{ulem}

\newcommand{\bs}[1]{\boldsymbol{#1}}

\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}

\newcommand{\tablab}[1]{\label{tab:#1}}
\newcommand{\tabref}[1]{Table~\ref{tab:#1}}

\newcommand{\theolab}[1]{\label{theo:#1}}
\newcommand{\theoref}[1]{\ref{theo:#1}}
\newcommand{\eqnlab}[1]{\label{eq:#1}}
\newcommand{\eqnref}[1]{\eqref{eq:#1}}
\newcommand{\seclab}[1]{\label{sec:#1}}
\newcommand{\secref}[1]{\ref{sec:#1}}
\newcommand{\lemlab}[1]{\label{lem:#1}}
\newcommand{\lemref}[1]{\ref{lem:#1}}

\newcommand{\mb}[1]{\mathbf{#1}}
\newcommand{\mbb}[1]{\mathbb{#1}}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\nor}[1]{\left\| #1 \right\|}
\newcommand{\snor}[1]{\left| #1 \right|}
\newcommand{\LRp}[1]{\left( #1 \right)}
\newcommand{\LRs}[1]{\left[ #1 \right]}
\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
\newcommand{\LRc}[1]{\left\{ #1 \right\}}
\newcommand{\LRb}[1]{\left| #1 \right|}

\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
\newcommand{\Grad} {\ensuremath{\nabla}}
\newcommand{\Div} {\ensuremath{\nabla\cdot}}
\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
\newcommand{\jump}[1] {\ensuremath{\LRs{\!\left[#1\right]\!}}}
\newcommand{\uh}{\widehat{u}}
\newcommand{\fnh}{\widehat{f}_n}
\renewcommand{\L}{L^2\LRp{\Omega}}
\newcommand{\pO}{\partial\Omega}
\newcommand{\Gh}{\Gamma_h}
\newcommand{\Gm}{\Gamma_{-}}
\newcommand{\Gp}{\Gamma_{+}}
\newcommand{\Go}{\Gamma_0}
\newcommand{\Oh}{\Omega_h}

\newcommand{\eval}[2][\right]{\relax
  \ifx#1\right\relax \left.\fi#2#1\rvert}

\def\etal{{\it et al.~}}

\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
\newcommand{\tensor}[1]{\underline{\vect{#1}}}
\newcommand{\del}{\Delta}
\let\grad\relax
\newcommand{\grad}{\nabla}
\newcommand{\curl}{\grad \times}
\renewcommand{\div}{\grad \cdot}
\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
\newcommand{\eip}[1]{a\left( #1 \right)}
\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}

\newcommand{\circone}{\ding{192}}
\newcommand{\circtwo}{\ding{193}}
\newcommand{\circthree}{\ding{194}}
\newcommand{\circfour}{\ding{195}}
\newcommand{\circfive}{\ding{196}}

\def\arr#1#2#3#4{\left[
\begin{array}{cc}
#1 & #2\\
#3 & #4\\
\end{array}
\right]}
\def\vecttwo#1#2{\left[
\begin{array}{c}
#1\\
#2\\
\end{array}
\right]}
\def\vectthree#1#2#3{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
\end{array}
\right]}
\def\vectfour#1#2#3#4{\left[
\begin{array}{c}
#1\\
#2\\
#3\\
#4\\
\end{array}
\right]}

%\newtheorem{proposition}{Proposition}
%\newtheorem{corollary}{Corollary}
%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}{Lemma}

\newcommand{\G} {\Gamma}
\newcommand{\Gin} {\Gamma_{in}}
\newcommand{\Gout} {\Gamma_{out}}

\newtheorem{remark}{Remark}

\title{A minimum-residual finite element method for the convection-dominated diffusion equation}
\author{Jesse Chan, John A. Evans}
\date{}
\begin{document}

\maketitle

\begin{abstract}
We present a minimum-residual finite element method for convection-dominated diffusion problems in a higher order, adaptive, continuous Galerkin setting.  The method borrows concepts from both the Discontinuous Petrov-Galerkin (DPG) method by Demkowicz et al.\ \cite{DPG2} and the method of variational stabilization by Dahmen et al.\ \cite{DahmenVariationalStabilization}, and it can also be interpreted as a variational multiscale method in which the fine-scales are defined through a dual-orthogonality condition.  A key ingredient in the method is the proper choice of norm used to measure the residual, and we present two alternatives which are observed to be robust in both convection and diffusion-dominated regimes.  Numerically obtained convergence rates are given in 2D, and benchmark numerical examples in all space dimensions are shown to illustrate the behavior of the method.
\end{abstract}

%\tableofcontents
%\begin{keywords}\end{keywords}
%\begin{AMS}\end{AMS}

\section{Introduction}

It is well known that the standard Galerkin finite element method performs very poorly for the convection-diffusion equation -- in the convection-dominated case, it experiences spurious oscillations in the solution that grow as $\epsilon \rightarrow 0$.  The problem is connected back to a loss of discrete coercivity with respect to the standard $H^1$ norm \cite{roos2008robust}.  The concept of \textit{stabilized} methods was introduced in order to combat such oscillations, the most popular of which is the Streamline Upwind Petrov-Galerkin (SUPG) method \cite{SUPG}.  The method can be interpreted as adding a sufficient amount of artificial viscosity in the streamline direction in order to restore discrete coercivity with respect to a new ``streamline-diffusion'' norm \cite{johnsonCrosswind}.  SUPG is also an example of a residual-based stabilization, where the stabilization mechanism disappears as the strong residual of the equation is satisfied.

A connection can be drawn between residual-based stabilized methods and Petrov-Galerkin schemes, where the trial (approximating) functions and test (weighting) functions are allowed to differ.  Specifically, the SUPG method can be interpreted as a modification of standard test functions\footnote{We note that one cannot recover the SUPG formulation beginning with the strong form of the equations and the SUPG test functions; the interpretation of SUPG as a Petrov-Galerkin scheme holds only locally, on element interiors.}, biasing them in the upwind direction based on mesh size, order of polynomial approximation, the magnitude of convection, and the diffusion parameter.  More recently, the concept of Petrov-Galerkin methods has been connected to a novel \textit{minimum residual} framework -- it is shown that the minimization of a specific residual corresponding to a variational formulation naturally leads to the concept of optimal test functions \cite{overviewDPG}.

Optimal test functions resulting from residual minimization were first implemented by Demkowicz and Gopalakrishnan in \cite{DPG2,DPG1}.  The connection between stabilization and least squares/minimum residual methods has been observed previously \cite{GLS}; however, the DPG method distinguishes itself by measuring the residual of the operator form of the equation, which is posed in the dual space.  Soon after, Cohen, Dahmen and Welper introduced an alternative saddle-point formulation of such a minimum residual method in \cite{DahmenVariationalStabilization}, which alluded to a Variational Multiscale (VMS) perspective \cite{VMS1,VMS2,HughesVMS}.

The goal of this paper is three-fold.  The first is to present a method which borrows concepts from each of these recent works and to derive a more detailed connection between the Petrov-Galerkin, stabilized, and VMS perspectives of minimum-residual methods.  The second is to demonstrate that the proposed method is robust in both convection and diffusion-dominated regimes provided the dual norm used to measure the residual is chosen intelligently.  The last goal is to show that the method is stable for arbitrary higher order and adaptive meshes, easily implemented using existing finite element codes and technologies, and extendable to three-dimensional convection-diffusion problems.

\section{A minimum-residual method}

Our starting point is the minimization of some measure of error over a finite-dimensional space.  We begin by first introducing an abstract variational formulation 
\begin{equation}
\eqnlab{variationEq}
\left\{
  \begin{array}{l}
    \text{Given } l \in V', \text{ find } u \in U  \text{ such that} \\ 
    b(u,v) = l(v), \quad \forall v\in V,
  \end{array}
  \right.
\end{equation}
where $b\LRp{\cdot,\cdot}: U \times V \to \mbb{R}$ is a continuous bilinear form.  Throughout the paper, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U'$ and $V'$ as the respective topological dual spaces.  Throughout the paper, we suppose the variational problem \eqnref{variationEq} to be well-posed in the inf-sup sense. We can then identify a unique operator $B:U\rightarrow V'$ such that 
\[
\langle Bu,v\rangle_V \coloneqq b(u,v), \quad u\in U, v\in V
\]
with $\LRa{\cdot, \cdot}_V$ denoting the duality pairing between $V'$ and $V$, to obtain the operator form of the our variational problem
\begin{equation}
\eqnlab{dualEq}
Bu = l \quad \text{in } V'.
\end{equation}
We are interested in minimizing the residual over the discrete approximating subspace $U_h \subset U$
\[
u_h = \underset{u_h\in U_h}{\arg\min}\, J(u_h) \coloneqq \frac{1}{2}\|l-Bu_h\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| l(v)- b(u_h,v)|^2}{\nor{v}_V^2}.
\]
For convenience in writing, we will abuse the notation $\sup_{v \in V}$ to denote $\sup_{v\in V\setminus\{0\}}$ for the remainder of the paper.  If we define the problem-dependent \textit{energy norm} 
\[
\nor{u}_E \coloneqq \nor{Bu}_{V'},
\]
then we can equate the minimization of $J(u_h)$ with the minimization of error in $\nor{\cdot}_E$.

The first order optimality condition for minimization of the quadratic functional $J(u_h)$ requires the G\^ateaux derivative to be zero in all directions $\delta u \in U_h$,
\begin{align}
\left(l-Bu_h,B\delta u\right)_{V'} = 0, \quad \forall \delta u \in U,
\label{orthog}
\end{align}
which is nothing more than the least-squares condition enforcing orthogonality of error with respect to the inner product on $V$.

The difficulty in working with the first-order optimality condition~\eqref{orthog} is that the inner product $\LRp{\cdot,\cdot}_{V'}$ cannot be evaluated explicitly.  However, we have that 
\begin{align}
\left(l-Bu_h,B\delta u\right)_{V'} = \left(R_V^{-1}(l-Bu_h),R_V^{-1}B\delta u\right)_{V},
\label{rieszOrthog}
\end{align}
where $R_V: V\rightarrow V'$ is the Riesz map mapping elements of a Hilbert space $V$ to elements of the dual $V'$ defined by
\[
\LRa{R_Vv,\delta v}_{V\times V'} \coloneqq \LRp{v,\delta v}_V.
\]
Furthermore, the Riesz operator is an isometry, such that $J(u_h) = \frac{1}{2}\nor{l-Bu_h}^2_{V'} = \frac{1}{2}\nor{R_V^{-1}(l-Bu_h)}^2_{V}$.  Thus, satisfaction of~\eqref{rieszOrthog} is exactly equivalent to satisfaction of the original optimality conditions~\eqref{orthog}.

\subsection{Saddle point formulation}
\label{sec:saddlePoint}
We can translate the optimality conditions~\eqref{rieszOrthog} into a more standard variational problem.  First, given some finite dimensional solution $u_h\in U_h$, we define the \textit{error representation function} $e$ such that
\[
\LRp{e,v}_V = l(v)-b(u_h,v), \quad \forall v\in V.
\]
We recognize this condition as defining $R_V e = l-Bu_h$; inversion of the Riesz map gives us 
\[
e = R_V^{-1}\LRp{l-Bu_h} = R_V^{-1}B\LRp{u-u_h},
\]
from which we can see that $\nor{e}_V = \nor{u-u_h}_E$.

Secondly, we need to enforce the orthogonality of the error in equation~\eqref{rieszOrthog}, which becomes
\begin{align*}
\LRp{e,R_V^{-1}B\delta u}_V &= 0, \quad \forall \delta u \in U_h\\
\Rightarrow \LRa{e,B\delta u}_{V\times V'} &= b(\delta u, e) = 0.
\end{align*}
Putting these two conditions returns the symmetric saddle-point problem for $\LRp{e,u_h} \in V\times U_h$
\begin{align*}
\LRp{e,v}_V + b(u_h,v) &= l(v), \quad \forall v\in V\\
b(\delta u, e) &= 0, \quad \forall \delta u \in U_h.
\end{align*}
We note that, under the perspective of the minimization of $J(u_h)$, this system can be viewed as a constrained optimization problem for $e$, where $u_h$ are Lagrange multipliers enforcing satisfaction of the variational problem.

At the moment, $V$ remains an infinite-dimensional space, and will have to be discretized by some $V_h\subset V$ in order to yield a solution.  Under this infinite dimensional setting, the choice of discretization for $V$ will determine how effectively the solution of the discrete problem will minimize $J(u_h)$ -- inadequate resolution of $V_h$ may result in a solution which is far from the true minimizer.

\begin{figure}[!h]
\centering
\includegraphics[scale=.3]{figs/saddlePoint.pdf}
\caption{Saddle point system for minimization of $J(u_h)$; the Schur complement eliminating degrees of freedom for $e$ returns the system resulting from optimal test functions.}
\end{figure}

This formulation was first introduced by Dahmen et al.\ in \cite{DahmenVariationalStabilization}, where $V_h$ was determined adaptively.  The method proceeded in two steps -- first, $V_h$ was set equal to $U_h$ on what we will define as the \textit{coarse mesh}.  Next, \textit{a posteriori} error estimators for $e$ (based on a specific choice of inner product $\LRp{\cdot,\cdot}_V$) were used to drive adaptivity to determine a fine-scale mesh on which $V_h$ was supported.  We choose a simpler representation -- if $U_h$ is represented by polynomials of order $p$, we set $V_h = P^{p+\triangle p}$ globally.  We note that these two choices of discretization for $V$ are not mutually exclusive, and that novel choices for $V_h$ are likely the key to yielding computationally effective methods under this framework.  
\subsection{DPG optimal test function framework}

The DPG method was introduced by Demkowicz and Gopalakrishnan in 2009, and rapidly applied to a series of problems in computational mechanics \cite{DPG2,DPG3,DPG4,maxwellDPG,stokesDPG}.  Though the DPG method shares the same variational setting as Dahmen et al.\, each method followed very different approaches in implementation.  Recall the orthogonality of error~\eqref{rieszOrthog}; by defining the error representation function $e$ and undoing the Riesz map acting on $B\delta u$, we recovered a saddle point formulation.  However, it is possible to instead undo the Riesz map acting on the residual instead, to recover
\begin{align*}
\LRp{R_V^{-1}\LRp{l-Bu_h},R_V^{-1}B\delta u}_V &= 0, \quad \forall \delta u \in U_h\\
\Rightarrow \LRa{\LRp{l-Bu_h},R_V^{-1}B\delta u}_{V\times V'} &= 0\\
\Rightarrow l\LRp{R_V^{-1}B\delta u}-b\LRp{u_h,R_V^{-1}B\delta u} &= 0
\end{align*}
If we define $v_{\delta u} \coloneqq R_V^{-1}B\delta u$, then we recover the original variational formulation with a nonstandard test space
\[
b(u_h,v_{\delta u}) = l(v_{\delta u}), \quad \forall \delta u \in U_h.
\]
The DPG method with optimal test functions was constructed under this perspective of minimization of $J(u_h)$.  While $v_{\delta u} \in V$ must still be solved for approximately, under the assumption of discontinuous test functions, this solve can be localized to a single element.\footnote{In practice, if $U_h(K) = P^p(K)$ is the space of polynomials of order $p$ over the element $K$, then the enriched space $V_h \subset V$ is chosen to be $V_h(K) = P^{p+\triangle p}(K)$, where $\triangle p \geq n$, and $d$ is the spatial dimension.}

We can draw yet another connection to the DPG method by considering the discrete problem which arises from the saddle point formulation.  Our discrete saddle point system is
\[
\left[\begin{array}{cc} \bs{A} &\bs{B}\\ \bs{B}^T&{0}\end{array}\right]\left[\begin{array}{c}\bs{e}\\ \bs{u}\end{array}\right] = \left[\begin{array}{c}\bs{f}\\ 0\end{array}\right],
\]
where, for $u_j\in U_h$ and $v_i,v_j\in V_h$, 
\[
\bs{A}_{ij} \coloneqq \LRp{v_i,v_j}_V, \quad \bs{B}_{ij} \coloneqq b\LRp{u_j,v_i},
\]
such that $\bs{A}$ is a square matrix and $\bs{B}$ is an overdetermined rectangular matrix.  Expressing $\bs{e} = \bs{A}^{-1}\LRp{\bs{f}-\bs{B}\bs{u}}$ allows us to statically condense out the degrees of freedom $\bs{e}$ to form the Schur complement
\[
\bs{B}^T \bs{A}^{-1}\bs{B} \bs{u} = \bs{B}^T \bs{A}^{-1}\bs{f}.
\]
The above system is essentially an algebraic least squares system, but preconditioned on the inside with the positive-definite operator $\bs{A}$, which is precisely the discrete system that arises under the optimal test function framework of DPG.  We can see this further by noting that 
\[
\LRp{\bs{A}^{-1}\bs{B}}^T\bs{B} \bs{u} = \LRp{\bs{A}^{-1}\bs{B}}^T\bs{f} 
\]
is equivalent to 
\[
b\LRp{u_h, \sum_k^{\dim{V_h}} v_{ik}\phi_k} = l\LRp{\sum_k^{\dim{V_h}} v_{ik}\phi_k}, \quad i = 1,\ldots,\dim(U_h)
\]
where $v_{ik} = \LRp{\bs{A}^{-1}\bs{B}}_{ik}$ are the degrees of freedom associated with the $i$th approximated optimal test function.

The efficiency of the DPG method lies in that, under the assumption of a localizable norm and optimal test functions, $\bs{A}$ is block diagonal and can be inverted locally \cite{overviewDPG}.  Under the ultra-weak formulation of DPG, one can show that this corresponds exactly to choosing a non-conforming DG space for $V$, where continuity is enforced weakly at element interfaces by requiring that the jump be orthogonal to polynomials of order $p$ \cite{globalLocalDPG}.\footnote{Such a weakly conforming method was first introduced in \cite{brenner2008mathematical}, where optimal rates of convergence were proved under the assumption that the DG space is at most of order $p+1$ .}

\subsection{Variational Multiscale Framework}

The above saddle point system can also be directly derived from variational multiscale (VMS) principles \cite{VMS1,VMS2}.  The key difference between this and standard multiscale methods is the way in which the fine scales influence the coarse; approximating the fine-scale problem is as difficult as approximating the original equation, so analytic approximations or assumptions must typically be made.  However, through the proper change of variables, this method converts the fine-scale problem into a symmetric-positive definite one, allowing for a well-behaved subgrid model of fine scale behavior.

We begin again with the variational problem
\[
\LRa{Bu,v}_{V'\times V} = \LRa{l,v}_{V'\times V},
\]
where, as before, $B: U\rightarrow V'$ is the operator form of $b(u,v)$, and $l \in V'$ is the load.  Standard VMS techniques then decompose $U$ into a \textit{coarse scale} space $U_h$ and \textit{fine scale} space $U'$, such that the coarse and fine scales $u_h \in U_h \subset U$ and $u' \in U'$ are related through some yet-unspecified orthogonality condition.  Decomposing $u = u_h + u'$ gives 
\begin{align*}
u_h \in U_h, u' \in U\setminus U_h, v \in V\\
\LRa{Bu_h,v}_{V'\times V} + \LRa{Bu',v}_{V'\times V} = \LRa{l,v}_{V'\times V}
\end{align*}
We can now explicitly choose our orthogonality condition defining the fine scales and rewrite the above problem as 
\begin{align*}
u_h \in U_h, u' \in U, v \in V\\
\LRa{Bu_h,v}_{V'\times V} + \LRa{Bu',v}_{V'\times V} &= \LRa{l,v}_{V'\times V}\\
\LRp{u',\bar{w}}_E &= 0, \quad \forall \bar{w} \in U_h,
\end{align*}
where $\LRp{u',\bar{w}}_E$ is defined through
\begin{align*}
\LRp{u',\bar{w}}_E = \LRp{Tu',T\bar{w}}_V\\
T:U\rightarrow V, \quad T \coloneqq R_V^{-1} B
\end{align*}
where $\LRp{v,\delta v}_V$ is an inner product on $V$ and $R_V$ is the Riesz map associated with this inner product.  DPG literature refer to $T$ as the \textit{trial-to-test} operator, which, given a basis function $\phi_i \in U_h$, returns the optimal test function for $\phi_i$ \cite{DPG2}.

If we define our fine-scale using the above orthogonality condition, we have that
\begin{align*}
\LRp{Tu',v}_V = \LRp{R_V^{-1}Bu',v}_V = \LRa{Bu',v}_{V'\times V}\\
\LRp{u',\bar{w}}_E = \LRp{Tu',R_V^{-1}B\bar{w}}_V = \LRa{Tu',B\bar{w}}_{V\times V'}
\end{align*}
and can now rewrite our above VMS formulation as 
\begin{align*}
u_h \in U_h, u' \in U, v \in V\\
\LRa{Bu_h,v}_{V'\times V} + \LRp{Tu',v}_{V} &= \LRa{l,v}_{V'\times V}\\
\LRp{Tu',B\bar{w}}_{V\times V'} &= 0, \quad \forall \bar{w} \in U_h.
\end{align*}
The saddle point formulation of Section~\ref{sec:saddlePoint} can be interpreted as solving not for $u'$, but for $e\coloneqq Tu'$.  The discrete approximation then follows directly from setting $V \coloneqq V_h$, some finite-dimensional enriched space, which impacts the method only through the approximation of $Tu'$ and the construction of the Riesz map $R_V^{-1}$.

To summarize, the minimum-residual framework motivating both Dahmen's variational stabilization and Demkowicz's DPG method can be characterized as a VMS method under which 
\begin{itemize}
\item Orthogonality of $U_h$ and $U'$ is defined through a nonstandard \textit{energy inner product} (i.\ e.\ $\LRp{u',u_h}_E = 0$), and
\item A change of variables (i.\ e.\ solving for $Tu'$ instead of $u'$) symmetrizes the fine-scale contribution and overall system.
\end{itemize}

\section{Choices for test norms}

As with the DPG method, the primary theoretical difficulty is in defining the norm $\nor{v}_V$ such that the method returns good results.  This choice of norm defines the measure of the residual which we minimize or the orthogonality condition defining the separation of coarse and fine scales, depending upon whether you adopt the minimum-residual or VMS perspective.

From this point on, we will focus specifically on $H^1$ standard Galerkin formulation for the scalar convection-diffusion problem on domain $\Omega$
\[
\div(\beta u) - \epsilon \del u = f,
\]
which represents the convection of some quantity $u$ subject to a convection field $\beta \in R^n$ and diffusion of magnitude $\epsilon \in \mathbb{R}$, where $\epsilon > 0$.  We impose inflow and outflow boundary conditions
\begin{align*}
\left.u\right|_{\Gamma_{\rm in}} &= u_{\rm in}\\
\left.u\right|_{\Gamma_{\rm out}} &= u_{\rm out}
\end{align*}
where the following boundaries are defined as 
\begin{align*}
\Gamma_{\rm in}\coloneqq \LRc{x\in \partial \Omega s.\ t.\ \beta\cdot\vec{n}(x) < 0}\\
\Gamma_{\rm out}\coloneqq \LRc{x\in \partial \Omega s.\ t.\ \beta\cdot\vec{n}(x) > 0}
\end{align*}
where $\vec{n}(x)$ is the outward normal at a point on the boundary $\partial \Omega$.  If it is non-empty, we may also define $\Gamma_{0}\coloneqq \LRc{x\in \partial \Omega s.\ t.\ \beta\cdot\vec{n}(x) = 0}$ as the boundary with outward normal orthogonal to the streamline.

Under $u,v \in H^1_0(\Omega)$, Our weak formulation becomes
\[
\LRp{\Grad u,\beta v + \epsilon \Grad v}_{\L} = \LRp{f,v}_{\L}.
\]
A norm based on the symmetric part of the bilinear form was explored in \cite{DahmenVariationalStabilization}, but yielded approximations which degnerated in $\epsilon$.  We present here two different methods based on alternative choices for test norms on $V$ for the convection-diffusion equation that both yield good results as $\epsilon\rightarrow 0$.

\subsection{Weighted streamline diffusion norm}

Our first method is motivated by previous results for the DPG method in \cite{DPGrobustness}, which achieved good results through a modification of the test norm.  We set
\[
\nor{v}_{V,w}^2 \coloneqq \frac{L}{\LRb{\beta}}\nor{\sqrt{w}\beta\cdot \Grad v}_{\L}^2 + \epsilon\nor{\Grad v}_{\L}^2 + \alpha\nor{v}_{\L}^2,
\]
where $L = \LRb{\Omega}^{\frac{1}{d}}$ is the length measure of $\Omega$ in $d$ spatial dimensions, $\LRb{\beta} = \max_\Omega \nor{\beta}_{l^2}$, and we have introduced the scaling $\frac{L}{\LRb{\beta}}$ on the streamline diffusion term for unit consistency\footnote{In all problems considered, $\frac{L}{\LRb{\beta}} = O(1)$}. $\alpha \geq 0$ is a user-specified constant with units of inverse time\footnote{In the case where $\alpha = 0$, the seminorm remains a norm due to equivalence with the $H^1$ seminorm, which is norm on $H^1_0$.  Specifying $\alpha > 0$ does not change the results dramatically; however, it does appear to improve conditioning of $\bs{A}$.}, and $w(x)$ is some smoothly varying positive weighting function.  Specifically, we require $\LRb{w(x)}$ to be of magnitude $O(\epsilon)$ for $x\in \Gamma_{\rm in}$, but $O(1)$ away from the inflow boundary.  Specific restrictions on $w$ are derived in \cite{DPGrobustness} in context of the DPG method.

A second motivation behind the weighting function can also be found in \cite{stynesSUPG, roos2008robust, johnsonCrosswind}, which refer to $w(x)$ as a cut-off function.  A theoretical issue with the convection-diffusion problem is that $\nor{u}_{H^1_0}$ and $\nor{u-u_h}_{H^1_0}$ do not remain bounded as $\epsilon\rightarrow 0$, due to the fact that $u' = O(\epsilon^{-1})$ in the region of boundary or internal layers.  These cut-off functions were introduced in order to yield $\epsilon$-independent bounds on the error by localizing error estimates away from layers.

We can demonstrate the need for the weight/cut-off function $w(x)$ in the test norm -- Figure~\ref{fig:comparison1D} shows the result of two simulations on a uniform 16 element piecewise-linear mesh. The error representation $e$ is approximated by quadratics over the same mesh.  Without the weight, the solution degenerates near the inflow; a similar phenomenon was observed in \cite{DahmenVariationalStabilization, DPG2, globalLocalDPG}.  
\begin{figure}[!h]
\centering
\subfigure[Solution $u$]{\includegraphics[scale=.22]{figs/weightedComparison1D.png}}
\subfigure[Fine-scales $e$]{\includegraphics[scale=.22]{figs/weightedErrorComparison1D.png}}
\caption{Comparisons of $u$ and $e$ for $\epsilon = 10^{-3}$, $f=1$ and $\alpha = 0$. The solution when $w = 1$ is in red, and the solution for when $w = x+\epsilon$ is given in blue.  The exact solution is given in black.}
\label{fig:comparison1D}
\end{figure}

Physically speaking, the weight can be interpreted as a cutoff function for the adjoint solution \cite{DPGrobustness2}, which displays a boundary layer at the inflow due to the fact that the direction of convection is reversed for the adjoint equation.  Mathematically speaking, it can also be interpreted as restoring a sense of directionality to the test norm (which is  sign of $\beta$).

\subsection{Streamline norm with weak boundary conditions on $e$}

While the above norm appears to give improved results, the issue of constructing a weighting function for complex geometries in higher dimensions can be fairly nontrivial.  One possibility would be to solve a Laplace's equation for $w$ on the domain, enforcing that $w(x) = \epsilon$ at inflow boundaries; however, the behavior of such a computationally determined weight has not been examined, and incurs additional complexity that is avoided by other methods.

Under this saddle-point framework, however, it is possible to avoid the use of a weight altogether.  Currently, we seek $v,e\in H^1_0(\Omega)$; however, if we seek instead 
\[
v,e\in H^1_{\rm out}(\Omega) \coloneqq \LRc{v\in H^1(\Omega) s.\ t.\ \left.v\right|_{\Gamma_{out}} = 0},
\]
we modify our variational formulation to be
\[
\LRp{\Grad u,\beta v + \epsilon \Grad v}_{\L} - \epsilon\int_{\Gamma_{\rm in}} \pd{u}{n}v = \LRp{f,v}_{\L}.
\]
Under this modification of the variational formulation, we can set $w=1$ and use the test norm
\[
\nor{v}_{V}^2 \coloneqq \frac{L}{\LRb{\beta}}\nor{\beta\cdot \Grad v}_{\L}^2 + \epsilon\nor{\Grad v}_{\L}^2 + \alpha\nor{v}_{\L}^2
\]
without experiencing the issues displayed for $e\in H^1_0(\Omega)$ in Figure~\ref{fig:comparison1D}.

Physically speaking, the replacement of $H^1_0(\Omega)$ with $H^1_{\rm out}(\Omega)$ can be viewed as releasing the strong imposition of a boundary condition at the inflow.  
%If $\alpha > 0$, then $\nor{v}_V^2$ defines an inner product $H^1(\Omega)$ and can be inverted without the application of boundary conditions.  If we ignore regularity restrictions on $u$ momentarily, the inversion of $\LRp{e,v}_V$ over $H^1_{\rm out}$ then corresponds to the strong problem
%\begin{align*}
%\alpha e - \Div \LRp{\LRp{\beta \otimes \beta + \epsilon I}\Grad e} &= f- \LRp{\beta\cdot \Grad u - \epsilon \del u}\\
%\vec{n}\cdot \LRp{\beta \otimes \beta + \epsilon I} \Grad e - \epsilon \vec{n}\cdot\Grad u &= 0, \quad \text{on }\Gamma_{\rm in}\\
%e &= 0, \quad \text{on }\Gamma_{\rm out}
%\end{align*}
%In other words, the Dirichlet boundary condition at $\Gamma_{\rm in}$ is replaced by a stress boundary condition, releasing the presence of a boundary layer at the inflow.  
The addition of the term $\epsilon\int_{\Gamma_{\rm in}} \pd{u}{n}v$ is akin to a penalty term that weakly enforces a homogeneous boundary condition on $e$ at the inflow; the orthogonality condition for $e$ under this additional term is
\[
(\Grad \delta u, \beta e + \epsilon \Grad e)_{\L} - \epsilon\int_{\Gamma_{\rm in}} \pd{\delta u}{n}e = 0, \quad \forall \delta u \in U_h
\]
If $U_h$ is taken to be a polynomial space of order $p$, the first term enforces orthogonality of $\beta e + \epsilon \Grad e$ to polynomials of order $p-1$ on the interior, while the second term enforces orthogonality of $e$ to polynomials of order $p-1$ on the subset of the boundary $\Gamma_{\rm in}$.  If $e$ is represented by a polynomial of order $p-1$, then this condition reduces to strong enforcement of $\left. e\right|_{\Gamma_{\rm in}}=0$ \cite{brenner2008mathematical}.  This boundary condition is released in the limit as $\epsilon \rightarrow 0$; as a result, for small $\epsilon$, the contribution $\LRp{e,v}_V$ no longer provides an extraneous stabilization at the inflow for under-resolved meshes, improving the resulting solution $u$.  However, for large $\epsilon$, the boundary condition activates and $e$ recovers homogeneous boundary conditions over the entire space $V$.  The choice of weight $w(x)$ in the previous section can be seen as similarly removing the contribution of $e$ near the inflow for small $\epsilon$, but allowing it to return for large $\epsilon$.

A comparison between the weighted norm $\nor{v}_{V,w}$ with $e\in H^1_0(\Omega)$ and unweighted norm with $e\in H^1_{\rm out}$ in one dimension is given in Figure~\ref{fig:robustComparison1D}.  
\begin{figure}[!h]
\centering
\subfigure[Solution $u$]{\includegraphics[scale=.22]{figs/robustComparison1D.png}}
\subfigure[Fine-scales $e$]{\includegraphics[scale=.22]{figs/robustErrorComparison1D.png}}
\caption{Comparisons of $u$ and $e$ for $\epsilon = 10^{-3}$, $f=1$ and $\alpha = 0$. The solution when $w = 1$ and $e\in H^1_{\rm out}(\Omega)$ is in red, and the solution for when $w = x+\epsilon$ is given in blue.  The exact solution is given in black.}
\label{fig:robustComparison1D}
\end{figure}

\begin{remark}
We remark that this inclusion of $\epsilon\int_{\Gamma_{\rm in}} \pd{u}{n}v$ is a variational crime under the assumption that $u \in H^1_0(\Omega)$; the proper way to include such a term in a conforming manner (without introducing additional regularity assumptions on $u$) would be to introduce $\epsilon \pd{u}{n}$ as an additional unknown on the boundary, similar to the work done using DPG under the ultra-weak formulation \cite{DPG2,analysisDPG}.  We note that Broersen and Stevenson have also achieved good results by making use of the space $H^1_{\rm out}(\Omega)$ in their application of the DPG method to the mixed mild-weak formulation for convection-diffusion \cite{broersenStevenson}.  The mild-weak formulation effectively enforces the orthogonality of $e$ to polynomials of lower order on $\Gamma_{\rm in}$ in a conforming manner, by introducing an additional flux unknown representing $\epsilon \pd{u}{n}$.

For many flow problems, activity near the inflow is typically very smooth and can thus be represented using a minimal number of elements under an effective adaptive mesh refinement scheme, implying that the cost of introducing such additional unknowns on $\Gamma_{\rm in}$ can be minimized.  However, since the codebase we currently use does not support unknowns with support only on element edges/faces, we continue to operate under this variational crime, in hopes that we can implement a conforming version in the near future.  Another way to properly include the term $\epsilon \pd{u}{n}$ in the variational formulation would be to work with higher continuity trial spaces that admit a normal trace of the derivative on the boundary \cite{nurbsTrace, NURBSorig}.  
\end{remark}
\begin{remark}
Various other methods of implementing a weak boundary condition on $e$ at the inflow $\Gamma_{\rm in}$ were implemented; for example, the inner product $\LRp{e,v}_V$ was modified by adding the a weak penalization term $$\epsilon C(h,p+\triangle p)\int_{\Gamma_{\rm in}}ev $$ to enforce the boundary condition at $\left.e\right |_{\Gamma_{\rm in}}$, where $C(h,p+\triangle p) = p^2/h$, which is a common choice of penalization parameter in high order finite element literature \cite{nurbsTrace,Warburton20032765}. However, the inclusion of the nonconforming term $\epsilon\int_{\Gamma_{\rm in}} \pd{u}{n}v$ in the bilinear form still resulted in the best solutions for all our numerical tests.  
\end{remark}

%\subset H^1_0(\Omega) \cap \LRc{w\in H^{\frac{3}{2}+\delta}(\Omega): \left.\pd{w}{n}\right|_{\Gamma_{\rm in}} \in H^{\frac{1}{2}}(\Gamma_{\rm in})}
Thus, the full formal characterization of the second method can be given as follows - solve for $u\in U_h \subset H^1_0(\Omega)\cap H^{\frac{3}{2}+\delta}(\Omega)$ (where $\delta$ is an positive real number), $e\in V_h\subset H^1_{\rm out}(\Omega)$ such that
\begin{align*}
\LRp{e,v}_V + (\Grad u, \beta v + \epsilon \Grad v)_{\L} - \epsilon\int_{\Gamma_{\rm in}} \pd{u}{n}v &= (f,v)_{\L}, \quad \forall v \in V_h\\
(\Grad \delta u, \beta e + \epsilon \Grad e)_{\L} - \epsilon\int_{\Gamma_{\rm in}} \pd{\delta u}{n}e &= 0, \quad \forall \delta u \in U_h
\end{align*}
where
\begin{align*}
\LRp{e,v}_V \coloneqq \LRp{\beta\cdot \Grad e,\beta\cdot \Grad v}_{\L} + \epsilon \LRp{e,\Grad v}_{\L}.
\end{align*}
We will utilize this second version of the method for all following numerical examples.

\begin{remark}
We note that, for $\epsilon \ll L$, where $L$ is the length scale of the problem, the boundary term $\epsilon\int_{\Gamma_{\rm in}} \pd{u}{n}v$ effectively disappears, and numerically speaking, we can use $e,v\in H^1_{\rm out}(\Omega)$ without including the additional boundary term in the variational formulation.  
\end{remark}

\section{Numerical examples}

We present several numerical examples, demonstrating rates of convergence and performance of the method on several benchmark problems in 2D.  All numerical examples were implemented in the Python-based FEniCS codebase \cite{LoggMardalEtAl2012a} to demonstrate that, unlike previous methods based upon the minimization of dual residuals, this method is easily implemented in most standard high-order finite element codes.

A remaining choice to be specified is the discretization of $V_h$: if $U_h$ is given to be polynomials of order $p$, the enriched space $V_h$ under which the fine-scales are approximated is set to be polynomials of order $p+\triangle p$ -- in other words, we use a simple polynomial enrichment scheme over a fixed mesh to approximate the fine-scale error representation function $e$.  In all experiments, $\triangle p = 1$ has been found to be sufficient, and larger $\triangle p$ has not been found to have a significant effect on the behavior of the method.  This is in contrast to the original DPG method, which also adopts a polynomial enriched space (where enrichment is done locally over each element) -- results by Gopalakrishnan and Qiu in \cite{practicalDPG} suggest that only $\triangle p \geq d$, where $d$ is spatial dimension, is guaranteed to yield optimal convergence rates for Laplace's equation.

We report only $L^2$ errors for each example, due to the fact that $H^1$ error is not a well-defined quantity as $\epsilon \rightarrow 0$.  As a consequence, during adaptive refinement, the error does not always monotonically decrease or behave as expected, since adaptive refinement is driven by the the quantity $\nor{u-u_h}_E = \nor{e}_V$, which we expect to be equivalent (possibly with equivalence constants depending on $\epsilon$) to the $H^1$ norm.  We do expect $\nor{u-u_h}_E$ to decrease monotonically for all $\epsilon$ (though not uniformly in $\epsilon$) due to the minimum-residual nature of our method.

\subsection{Erikkson-Johnson model problem}

We adopt a problem first proposed by Eriksson and Johnson in \cite{Eriksson1993} and later used in \cite{DPGrobustness, DPGrobustness2} to determine the robustness of DPG with respect to the diffusion parameter $\epsilon$. For the choice of $\Omega = (0,1)^2$, $f=0$, and $\beta = (1,0)^T$, the convection diffusion equation reduces to
\[
\pd{u}{x} - \epsilon \left(\pdd{u}{x}+ \pdd{u}{y}\right) = 0,
\]
which has an exact solution by separation of variables, allowing us to analyze convergence of DPG for a wide range of $\epsilon$. For boundary conditions, we impose
\begin{align*}
u &= u_0, \quad x=0,\\
u &= 0, \quad x=1, y = 0,1
\end{align*}
In this case, our exact solution is the series
\[
u(x,y) = \sum_{n=0}^\infty C_n \frac{e^{r_{1,n}(x-1)} - e^{r_{2,n}(x-1)}}{e^{-r_{1,n}} - e^{-r_{2,n}}} \sin (n\pi y)
\]
where
\begin{align*}
r_{1,2,n} &= \frac{1 \pm \sqrt{1 + 4 \lambda_n}}{2 \epsilon},\\
\lambda_n &= n^2\pi^2 \epsilon.
\end{align*}
We take for the exact solution the first mode, such that $C_0 = 1$, and $C_n = 0$ for $n\neq 1$.  
\begin{align*}
u(x,y) &= \frac{e^{r_{1}(x-1)} - e^{r_{2}(x-1)}}{e^{-r_{1}} - e^{-r_{2}}} \sin (\pi y)\\
r_{1,2} &= \frac{1 \pm \sqrt{1 + 4 \epsilon^2 \pi^2}}{2 \epsilon},
\end{align*}
The problem is driven solely by inflow boundary conditions, and develops a boundary layer of width $\epsilon$ at the outflow $x = 1$.  The resulting solution is shown in Figure~\ref{fig:erikkson} for $\epsilon = 10^{-2}$, along with convergence rates of $\L$ error under uniform mesh refinement for both $p=1$ and $p=2$.  
\begin{figure}[!h]
\centering
\subfigure[Exact solution for $u$]{\includegraphics[scale = .3]{figs/erikksonExact.png}}
\subfigure[Convergence rates for $\epsilon = 10^{-2}$]{\includegraphics[scale = .41]{figs/rates/eps1e2Rates.eps}}
\caption{Erikkson-Johnson model problem for $\epsilon = 10^{-2}$, along with convergence rates under uniform refinement.}
\label{fig:erikkson}
\end{figure}
Optimal rates of convergence are not expected due to the pre-asymptotic nature of the mesh relative to the solution -- typically, $h$ must be $O(\epsilon)$ in order to observe optimal rates of convergence \cite{SchwabBoundaryLayers}.

For large diffusion -- $\epsilon = 1.0$, we do observe optimal $p+1$ rates of convergence in Figure~\ref{fig:erikkson2}.  Likewise, when $\epsilon \ll h$, we observe a sub-optimal rate of $\frac{1}{2}$, the same as the rate suggested by theory and observed numerically in \cite{broersenStevenson} due to the strong boundary layer present under small $\epsilon$.  
\begin{figure}[!h]
\centering
\subfigure[$\epsilon = 1$]{\includegraphics[scale = .4]{figs/rates/eps1e0Rates.eps}}
\subfigure[$\epsilon = 10^{-4}$]{\includegraphics[scale = .4]{figs/rates/eps1e4Rates.eps}}
\caption{Erikkson-Johnson model problem for $\epsilon = 1$ and $\epsilon = 10^{-4}$, along with convergence rates under uniform refinement.}
\label{fig:erikkson2}
\end{figure}

\section{Adaptive mesh refinement}

We experimented also with an adaptive refinement scheme.  Since $\nor{e}_V$ is localizable\footnote{A localizable norm $\nor{v}_{V(\Omega)}$ can be written in the form 
$$\nor{v}_{V(\Omega)}^2 = \sum_{K\in \Oh} \nor{v}_{V(K)}^2,$$ where $\nor{v}_{V(K)}$ is a norm over each element $K$ in the mesh $\Oh$.}, we can evaluate it element-wise to get element error indicators $e_K \coloneqq \nor{e}_{V(K)}$.  We implemented a bulk-chasing refinement strategy, where, given some factor $\theta \in [0,1]$, we refine the top $\lceil{\theta N}\rceil$ elements with the largest error indicators $e_K$.  A greedy refinement scheme was also implemented, where all elements with $e_K > \theta \max_K e_K$ are refined; however, this refinement scheme tended to place refinements more conservatively, requiring many more refinement iterations to achieve a qualitatively good resolution.  In all following experiments, $\theta$ is set to be $.25$.

\subsection{Erikkson-Johnson model problem}

We continue to verify our method using the Erikkson-Johnson with $\epsilon = 10^{-3}$.  The solution $u$ and the convergence/rates of $\L$ error under adaptive mesh refinement for $p=2$ are given in Figure~\ref{fig:erikksonAdapt}.  The energy error $\nor{u-u_h}_E$ is also displayed for comparison.  
\begin{figure}[!h]
\centering
\subfigure{\includegraphics[scale=.39]{figs/erikkson1e3.png}}
\subfigure{\includegraphics[scale=.445]{figs/rates/eps1e3RatesL2.eps}}
\caption{Erikkson-Johnson problem with $\epsilon = 10^{-3}$ under 16 refinements.}
\label{fig:erikksonAdapt}
\end{figure}

As a result of the saddle point formulation, we can also examine the fine-scale error representation function $e$.  Figure~\ref{fig:erikksonError} displays a comparison between the error representation function after the first iteration of adaptive mesh refinement and the 16th iteration.  Recall that the main contribution to the energy error is the streamline derivative of $e$; $\nor{u-u_h}_E^2 = \nor{e}_V^2 = \nor{\beta \cdot \Grad e}_{\L}^2 + \epsilon\nor{\Grad e}_{\L}^2$. Thus, variation in the streamline direction is picked up by $\nor{\beta\cdot \Grad e}_{\L}^2$ and is the primary contribution to the total error.  After sufficient refinement and resolution of the outflow layer, the error representation function becomes smooth in the region of the boundary layer, and refinements will be placed according to the viscous error $\epsilon\nor{\Grad e}_{\L}^2$.

\begin{figure}[!h]
\centering
\subfigure{\includegraphics[scale=.345]{figs/erikkson1e3ErrUnif.png}}
\subfigure{\includegraphics[scale=.345]{figs/erikkson1e3Err.png}}
\caption{Comparison of the fine scale error representation $e$ under the Erikkson-Johnson problem with $\epsilon = 10^{-3}$ for the mesh at the first and $16$th refinement steps.}
\label{fig:erikksonError}
\end{figure}

One open question concerning this method is the energy norm $\nor{u}_E$ which is induced by our choice of bilinear form and inner product on our choice of test space $V = H^1_{\rm out}$.  Figure~\ref{fig:erikksonEpsComparison} displays both $L^2$ and energy errors over a range of $\epsilon$.  We observe that the energy error appears to be, like the $\L$ error (but unlike $H^1(\Omega)$ or error in the streamline diffusion norm), independent of $\epsilon$ -- convergence does not appear to be in a norm that is equivalent to the $H^1$ norm with constants independent of $\epsilon$.

Numerical experiments indicate that the measure of energy error is fairly insensitive to the degree of enrichment of $V_h$, so we expect that only a moderately finer resolution of $V_h$ with respect to $U_h$ is sufficient to capture fine-scale effects.  More investigation is necessary to determine the nature of the energy norm induced by this method.

\begin{figure}[!h]
\centering
\includegraphics[scale=.6]{figs/rates/epsRangeComparison.eps}
\caption{Comparison of $\L$ and energy error convergences under adaptive refinement for the Erikkson-Johnson problem for $\epsilon = 10^{-3}, 10^{-4}, 10^{-5}, 10^{-6}$.}
\label{fig:erikksonEpsComparison}
\end{figure}

\subsection{Discontinuous forcing and advection skew to mesh}

We consider next a slight variant of a model problem introduced by Hughes and Sangalli in \cite{HughesVMS}.  The domain $\Omega$ is again taken to be the unit square, $\beta$ is taken to be $\beta = [.5,1]$, and $\epsilon = 10^{-3}$.  Homogeneous Dirichlet boundary conditions are taken over the entire boundary, and the problem is driven by a discontinuous forcing term $f(x,y)$, where
\[
f(x,y) = \begin{cases}
1 \text{ if } y > 2x \\
0 \text{ otherwise}.
\end{cases}
\]
Under such an example, a boundary layer develops at the outflow boundaries $x,y = 1$, and an internal layer develops due to the fact that the discontinuity in $f$ is parallel to the streamline.  Figure~\ref{fig:discForcing} displays the solution and mesh resulting from 16 automatic mesh refinement iterations.  
\begin{figure}[!h]
\centering
\subfigure{\includegraphics[scale=.43]{figs/DiscontinuousForcing.png}}
\subfigure{\includegraphics[scale=.43]{figs/DiscontinuousForcingMesh.png}}
\caption{Model problem with $\epsilon = 10^{-3}$ and discontinuous forcing $f$.}
\label{fig:discForcing}
\end{figure}
Figure~\ref{fig:discForcing2} displays a zoom of the solution and convergence history of the energy error.
\begin{figure}[!h]
\centering
\subfigure{\includegraphics[scale=.357]{figs/DiscontinuousForcingZoom.png}}
\subfigure{\includegraphics[scale=.45]{figs/rates/eps1e3DiscontinuousForcing.eps}}
\caption{Zoom on the upper right-hand corner of the mesh for $f$ discontinuous, along with convergence of energy error $\nor{u-u_h}_E$.}
\label{fig:discForcing2}
\end{figure}

We can similarly examine advection skew to the mesh, another common benchmark problem for convection-diffusion.  We adopt a modification of the standard problem parameters -- here, $\epsilon = 10^{-7}$, $\beta = [.5,1]$, and $f=0$.  Boundary conditions are set such that
\[
u = \begin{cases}
1 \text{ if } y = 0, x< .5\\
1-y \text{ if } x = 0\\
0 \text{ otherwise}.
\end{cases}
\]
Mathematically speaking, the considered problem is ill-posed for the standard Galerkin method in the continuous setting -- the boundary condition implies a discontinuity in $u$, such that the solution cannot lie in $H^1$.  The boundary condition is then convected in a manner that is skew to the mesh and forms a boundary layer on part of the outflow.

\begin{figure}[!h]
\centering
\subfigure[Solution $u$]{\includegraphics[scale=.3]{figs/skewToMesh.png}}
\subfigure[$u$]{\includegraphics[scale=.313]{figs/skewToMesh3D.png}}
\subfigure[Error representation $e$]{\includegraphics[scale=.29]{figs/skewToMeshE.png}}
\caption{Advection skew to mesh on a uniform quadratic $32\times 32$ grid of triangles.  The fine scale error representation function $e$ is also shown; note that the multiscale contribution of $e$ is dependent on the form of $\LRp{e,v}_V$, which involves streamline derivatives.}
\end{figure}

\begin{figure}[!h]
\centering
\subfigure{\includegraphics[scale=.43]{figs/skewToMeshAdapt.png}}
\subfigure{\includegraphics[scale=.43]{figs/skewToMeshAdaptMesh.png}}
\caption{Advection skew to mesh after iterations 18 of adaptive mesh refinement.}
\end{figure}

\begin{figure}[!h]
\centering
\includegraphics[scale=.45]{figs/rates/eps5e7SkewToMesh.eps}
\caption{Energy error for advection skew to mesh over 18 iterations of adaptive mesh refinement.}
\end{figure}

We note that the standard boundary condition for advection skew to the mesh is 
\[
u = \begin{cases}
1 \text{ if } x = 0 \text{ or } y = 0 \text{ and } x< .5\\
0 \text{ otherwise},
\end{cases}
\]
which produces a discontinuity at the upper left hand corner as well.  However, under automatic mesh refinement, extraneous refinements are placed at this corner's discontinuity.  It is possible to avoid such an issue either by tailoring a mesh refinement scheme to avoid the corner or by adopting a regularized boundary condition by introducing a mesh-dependent ``ramped'' boundary condition which approximates the discontinuity.  This was done for for the lid-driven cavity flow problem under Stokes flow in \cite{stokesDPG}.

We avoid both the above ``fixes'' in order to more cleanly demonstrate the behavior of automatic adaptive mesh refinement; however, we note that under the uniform meshes in Figure~\ref{fig:skewUnif}, or under adaptive refinement schemes that avoids the corner singularity, the method appears to deliver similar results to SUPG.  
\begin{figure}[!h]
\centering
\subfigure[$p=1$]{\includegraphics[scale=.43]{figs/skewToMeshP1Unif.png}}
\subfigure[$p=2$]{\includegraphics[scale=.43]{figs/skewToMeshP2Unif.png}}
\caption{Solution $u$ for advection skew to mesh with the upper-left hand corner discontinuity under both linear and quadratic uniform meshes.}
\label{fig:skewUnif}
\end{figure}

\subsection{A 3D model problem}

We conclude by applying the method to a simple model problem in 3 space dimensions.  We solve on the unit cube $\Omega = [0,1]^3$ with $\beta = [1,1,1]$, $f=1$ and $u=0$ on $\partial \Omega$.  A boundary layer develops on the outflow boundaries $x,y,z = 1$.  Figure~\ref{fig:3D5e2} displays slices of the domain along the streamline direction to illustrate the formation of such a boundary layer.

\begin{figure}[!h]
\centering
\subfigure{\includegraphics[scale=.44]{figs/3DSlices5e2.png}}
\caption{3D Model problem with $\epsilon = 5e-2$.}
\label{fig:3D5e2}
\end{figure}

We examined the behavior of the method with respect to a small $\epsilon$, in this case $\epsilon = 10^{-6}$.  8 adaptive refinements were done beginning with a uniform linear mesh of 8 elements per side; Figure~\ref{fig:3D1e6} shows the resulting solution and mesh along a cut orthogonal to the streamline direction.  All experiments indicate that the method appears to behave qualitatively the same as in 2 dimensions, modulo increased computational cost.

\begin{figure}[!h]
\centering
%\subfigure{\includegraphics[scale=.25]{figs/3DMesh.png}}
\subfigure{\includegraphics[scale=.4]{figs/3DSlice.png}}
\subfigure{\includegraphics[scale=.4]{figs/3DMeshSlice.png}}
\caption{3D Model problem with $\epsilon = 10^{-6}$ after 8 refinements.  The cube is sliced along a plane with normal direction orthogonal to the streamline in order to illustrate the clustering of refinements in the interior of the domain.}
\label{fig:3D1e6}
\end{figure}

%\textcolor{red}{Does Hughes have a reference for the weakening of divergence in higher dimensions?}.

\section{Conclusions and future direction}

We have presented a higher order adaptive $H^1$-conforming method for convection-diffusion problems for very small $\epsilon$, and have made connections to both the DPG method as well as the method of Cohen, Dahmen and Welper.  The method has also been shown to be derivable in the Variational Multiscale framework as well, and is distinguished from traditional VMS methods in its definition of the fine-scale space and problem.  Unlike standard stabilized $H^1$ methods, there are no stabilization parameters.  However, unlike the DPG methods of both Demkowicz et.\ al.\ and Broersen and Stevenson, this method is easily implementable within current finite element codes in arbitrary spatial dimensions.

We note that, while the method displays similarities to SUPG, we do not observe nodal exactness in 1D.  The two methods differ in that we do not work directly with coarse scales defined by the $H^1$ inner product; unless we can induce an energy inner product such that $\LRp{u_h,u'}_E = \LRp{u_h,u'}_{H^1_0}$, then we should not expect nodal exactness in 1D.  However, in higher space dimensions, the behavior of the method is qualitatively very similar to SUPG.

We hope to explore in future research both additional improvements on the method and the application of this method to other problem frameworks and settings, a few of which are described in the following sections.

\subsection{$hpr$-refinement}

Since this method is derived from the same variational principles as DPG, it should likewise be automatically inf-sup stable for arbitrary $hp$ meshes as well.  $hp$-refinement is of interest due to the fact that, under proper choices between $h$ and $p$ refinement, exponential convergence rates are possible, and have been observed for several model problems \cite{demkowicz2006computing}.  Intelligent $hp$-adaptive strategies could also offer more mathematically motivated alternatives to CFD approaches such as flux limiters, which effectively limit the order of approximation in areas of singularities and high gradients.

Additionally, the method automatically extends to incorporate anisotropic elements and $r$-refinement as well, similar to ALE methods.  The combination of these two methods has been shown to produce very fine-resolution results at a competitive computational cost for flow problems with very small viscosity \cite{AlmeidaAnisotropy}.

\subsection{Computational feasibility}

The main obstacle to making this method computationally competitive is the doubling of the number of fully coupled degrees of freedom in solving the problem in saddle point system formulation.  While a larger number of degrees of freedom is often cited as a detriment, it is often accompanied by an advantageous underlying structure -- for example, discontinuous Galerkin methods are also often criticized for their ``explosion of degrees of freedom'' compared to continuous Galerkin methods \cite{cottrell2007isogeometric}, but their local nature aids significantly in parallelization, adaptivity, and explicit time integration, as opposed to methods based on continuous discretizations.

The cost of explicitly discretizing the fine scale error representation $e\in V_h$ roughly amounts to the cost of discretizing an additional coupled PDE under a higher resolution.   The idea of solving an additional PDE for the purposes of stabilization is not unheard of \cite{Barter}; however, the additional discretization cost must be minimized.  We propose several preliminary ideas for doing so: 
\begin{itemize}
\item Recall in Section~\ref{sec:saddlePoint} that the saddle point system is reducible to 
\[
\bs{B}^T \bs{A}^{-1}\bs{B} \bs{u} = \bs{B}^T \bs{A}^{-1}\bs{f}.
\]
where $f$ and $B$ are the load and overdetermined stiffness matrix under $V_h$, and $A$ is the Gram matrix/discrete Riesz map associated with the inner product $\LRp{v,\delta v}_V$.  One approach is to explore possibilities for rapid inversion of $A$.  For example, it is possible to choose $V_h$ to simply be the space of piecewise linears enriched with bubbles -- higher order degrees of freedom could be condensed out, resulting in a system for $e$ with the same number of unknowns as $u$.  The resulting matrix-vector products required to form the Schur complement could be parallelized as well.

One additional possibility would be the exploration of iterative methods for the Schur complement -- the matrix is positive definite, and assembling a matrix-vector product could be done efficiently under a good preconditioner for the symmetric positive-definite matrix $\bs{A}^{-1}$.  Preliminary results demonstrate effective speedup for uniform meshes of piecewise linears in 2D using standard preconditioners (ILU, block Jacobi, AMG), and suggest that a discretization of $V_h$ using a $h$-refined fine mesh could be possible; however, more work would be required to develop preconditioners for high order adaptive meshes.  
\item Another possibility would be to solve the saddle point problem using an Uzawa method \cite{uzawa}, which would decouple the saddle point system into two problems, each involving only degrees of freedom for $e$ or for $u$.  The solution of these two problems feeds an iterative procedure which can converge to the solution of the saddle point problem.  Again, effective use of an Uzawa algorithm would require a good preconditioner for $\bs{A}$ under high-order refined meshes.
\item We hope to explore alternative discretizations for both $U_h$ and $V_h$ in order to minimize degrees of freedom or solution for in the overall system.  A few examples of nonstandard discretizations include higher order continuity basis functions (splines and NURBS \cite{NURBSorig}), and discontinuous functions (DG).  We hope to also explore intelligent mixing of discretizations for $U_h$ and $V_h$.  
\item The DPG method achieves computational efficiency by block-diagonalizing $\bs{A}$ using discontinuous test functions.  The same method could be applied to the $H^1$ setting for convection-diffusion problems at the cost of introducing inter-element fluxes representing the trace on the boundary of an element resulting from integration by parts of the viscous term.  An alternative along the same lines would be to consider block diagonalization of $\bs{A}$ under a patch-based decomposition, such as FETI or one of its variants \cite{FETI1,FETI2}.  
\end{itemize}
\newpage
\bibliographystyle{unsrt}
\bibliography{paper}

\end{document}

### 2013-05-17 docs/Jesse/Confusion Notes/siamltex/docultex.tex

%%
%% This is file `docultex.tex', 
%% Documentation for siam macros for use with LaTeX 2e
%% 
%% August 1, 1995
%%
%% Version 1.1a
%% 
%% You are not allowed to change this file. 
%% 
%% You are allowed to distribute this file under the condition that 
%% it is distributed together with all of the files in the siam macro 
%% distribution. These are:
%%
%%  siamltex.cls (main LaTeX macro for SIAM)
%%  siamltex.sty (includes siamltex.cls for compatibility mode)
%%  siam10.clo   (size option for 10pt papers)
%%  subeqn.clo   (allows equation numbners with lettered subelements)
%%  siam.bst     (bibliographic style file for BibTeX)
%%  docultex.tex (this file)
%%  lexample.tex (example file for latex macro)
%%
%% If you receive only some of these files from someone, complain! 
%% 
%% You are NOT ALLOWED to distribute this file alone. You are NOT 
%% ALLOWED to take money for the distribution or use of either this 
%% file or a changed version, except for a nominal charge for copying 
%% etc. 
%% \CharacterTable
%%  {Upper-case    \A\B\C\D\E\F\G\H\I\J\K\L\M\N\O\P\Q\R\S\T\U\V\W\X\Y\Z
%%   Lower-case    \a\b\c\d\e\f\g\h\i\j\k\l\m\n\o\p\q\r\s\t\u\v\w\x\y\z
%%   Digits        \0\1\2\3\4\5\6\7\8\9
%%   Exclamation   \!     Double quote  \"     Hash (number) \#
%%   Dollar        \$     Percent       \%     Ampersand     \&
%%   Acute accent  \'     Left paren    \(     Right paren   \)
%%   Asterisk      \*     Plus          \+     Comma         \,
%%   Minus         \-     Point         \.     Solidus       \/
%%   Colon         \:     Semicolon     \;     Less than     \<
%%   Equals        \=     Greater than  \>     Question mark \?
%%   Commercial at \@     Left bracket  \[     Backslash     \\
%%   Right bracket \]     Circumflex    \^     Underscore    \_
%%   Grave accent  \`     Left brace    \{     Vertical bar  \|
%%   Right brace   \}     Tilde         \~}

\documentclass[final,leqno]{siamltex}

\title{USING SIAM'S \LaTeX\ MACROS\thanks{This work was
supported by the Society for Industrial and Applied
Mathematics}}

\author{TeX Production\thanks{Society for Industrial and
Applied Mathematics, Philadelphia, Pennsylvania. 
(tex@siam. org). Questions, comments, or corrections
to this document may be directed to that email address.}}

\begin{document}
\maketitle

\begin{abstract}
Documentation is given for use of the SIAM \LaTeX\ macros. These
macros are now compatible with \LaTeX$2_{\varepsilon}$.
Instructions and suggestions for compliance with SIAM style
standards are also included. Familiarity with standard \LaTeX\ commands
is assumed.
\end{abstract}

\begin{keywords}\end{keywords}

\begin{AMS}\end{AMS}

\pagestyle{myheadings}
\thispagestyle{plain}
\markboth{TEX PRODUCTION}{USING SIAM'S \LaTeX\ MACROS}

\section{Introduction}

This file is documentation for the SIAM \LaTeX\ macros, and
provides instruction for submission of your files.

To accommodate authors who electronically typeset their manuscripts,
SIAM supports the use of \LaTeX. To ensure quality typesetting according
to SIAM style standards, SIAM provides a \LaTeX\ macro style file.
Using \LaTeX\ to format a manuscript should simplify the editorial process
and lessen the author's proofreading burden. However,
it is still necessary to proofread the galley proofs with care.

Electronic files should not be submitted until the paper has been
accepted, and then not until requested to do so by someone in the SIAM
office. Once an article is slated for an issue,
someone from the SIAM office will contact the author about any or all
of the following: editorial and stylistic queries, 
supplying the source files (and any supplementary macros)
for the properly formatted article, and handling figures.

When submitting electronic files  (electronic submissions) 
(to {\tt tex@siam.org}) include  the journal, issue, and author's
name in the subject line of the message. 
Authors are responsible for ensuring  that the paper generated 
from the source files exactly matches the paper that
was accepted for publication by the review editor. If it does not,
information on how it differs should be indicated in the transmission 
of the file. When submitting a file, please be sure to include any 
additional macros (other than those provided by SIAM) that will be 
needed to run the paper.

SIAM uses MS-DOS-based computers for \LaTeX\ processing. Therefore
all filenames should be restricted to eight characters or less,
plus a three character extension.

Once the files are corrected here at SIAM, we will mail the revised 
proofs to be read against the original edited hardcopy 
manuscript. We are not
set up to shuttle back and forth varying electronic versions of each
paper, so we must rely on hard copy of the galleys. The author's proofreading
is an important but easily overlooked step. Even if SIAM were not
to introduce a single editorial change into your manuscript, there
would still be a need to check, because electronic transmission
can introduce errors.

The distribution contains the following items: {\tt
siamltex.cls}, the main macro package based on {\tt
article.cls}; {\tt siam10.clo}, for the ten-point size option;\linebreak 
{\tt subeqn.clo}, a style option for equation numbering (see \S3 for
an explanation); and  {\tt siam.bst},
 the style file for use with {\sc Bib}\TeX. Also included are this
file {\tt docultex.tex} and a sample file {\tt lexample.tex}.
The sample file represents a standard application of 
the macros. The rest of this paper will highlight
some keys to effective macro use, as well as point out options and
special cases, and describe SIAM style standards to which
authors should conform.

\section{Headings}
The top matter of a journal paper falls into a standard
format. It begins of course with the \verb|\documentclass| command

\begin{verbatim}

\documentclass{siamltex}

\end{verbatim}

Other class options  can be included
in the bracketed argument of the command, separated by commas.

Optional arguments include:
\begin{description}
\item[final] Without this option, lines which extend past the
margin will have black boxes next to them to help authors identify
lines that they need to fix, by re-writing or inserting breaks. \verb|final|
turns these boxes off, so that very small margin breaks which are not
noticible will not cause boxes to be generated.

\item[oneeqnum] Normally \verb|siamltex.cls| numbers equations,
tables, figures, and theorem environments with a decimal number, 
composed of the section of the paper, a period, and the number of
the enumerated object (example: 1.2). The sequence of numbering
is also restarted with each new section, so that, for example, the last
equation of section 3 may be 3.10, but the first equation of section
4 would be 4.1. Using \verb|oneeqnum| numbers all equations consecutively
throughout a paper with a single digit.

\item[onethmnum] Using \verb|onethmnum| numbers all theorem-like
environments consecutively throughout a paper with a single digit.

\item[onefignum] Using \verb|onethmnum| numbers all figures
 consecutively throughout a paper with a single digit.

\item[onetabnum] Using \verb|onethmnum| numbers all tables
 consecutively throughout a paper with a single digit.
\end{description}

The title and author parts are formatted using the
\verb|\title| and \verb|\author| commands as described in Lamport
\cite{Lamport}. The \verb|\date|
command is not used. \verb|\maketitle| produces the actual
output of the commands.

The addresses and support acknowledgments are put into the
\verb|\author| commands via \verb|\thanks|. If support is
overall for the authors, the support acknowledgment should
be put in a \verb|\thanks| command in the \verb|\title|.
Specific support should go following the addresses of the
individual authors in the same \verb|\thanks| command.

Sometimes authors have support or addresses in common which
necessitates having multiple \verb|\thanks| commands for
each author. Unfortunately \LaTeX\ does not normally allow this, 
so a special procedure must be used. An example of this procedure
follows. Grant information can also be run into both authors' 
footnotes.

\begin{verbatim}

\title{TITLE OF PAPER}

\author{A.~U. Thorone\footnotemark[2]\ \footnotemark[5]
\and A.~U. Thortwo\footnotemark[3]\ \footnotemark[5]
\and A.~U. Thorthree\footnotemark[4]}

\begin{document}
\maketitle

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\footnotetext[2]{Address of A.~U. Thorone}
\footnotetext[3]{Address of A.~U. Thortwo}
\footnotetext[4]{Address of A.~U. Thorthree}
\footnotetext[5]{Support in common for the first and second
authors.}

\renewcommand{\thefootnote}{\arabic{footnote}}

\end{verbatim}

Notice that the footnote marks begin with {\tt [2]}
because the first mark (the asterisk) will be used in the
title for date-received information by SIAM, even if not
already used for support data. This is just one example;
other situations follow a similar pattern.

Following the author and title is the abstract, key words
listing, and AMS subject classification number(s),
designated using the \verb|{abstract}|, \verb|{keywords}|,
and \verb|{AMS}| environments. If
there is only one AMS number, the commands
\verb|\begin{AM}| and \verb|\end{AM}| are used
instead of \verb|{AMS}|. This causes the heading to be
in the singular. Authors are responsible for providing AMS numbers.
They can be found in the Annual Index of Math Reviews, or
through {\tt e-Math} ({\tt telnet e-math.ams.com}; login
and password are both {\tt e-math}).

Left and right running heads should be provided in the
following way.

\begin{verbatim}

\pagestyle{myheadings}
\thispagestyle{plain}
\markboth{A.~U. THORONE AND A.~U. THORTWO}{SHORTER PAPER
TITLE}

\end{verbatim}

\section{Equations and mathematics}

One advantage of \LaTeX\ is that it can automatically number
equations and refer to these equation numbers in text. While plain \TeX's
method of equation numbering (explicit numbering using
\verb|\leqno|) works in the SIAM macro, it is not preferred
except in certain cases. SIAM style guidelines call for
aligned equations in many circumstances, and \LaTeX's 
\verb|{eqnarray}| environment is not compatible with
\verb|\leqno| and \LaTeX\ is not compatible with the plain
\TeX\ command \verb|\eqalign| and \verb|\leqalignno|. Since
SIAM may have to alter or realign certain groups of
equations, it is necessary to use the \LaTeX\ system of
automatic numbering.

Sometimes it is desirable to designate subequations of a larger
equation number. The subequations are designated with
(roman font) letters appended after the number. SIAM has
supplemented its macros with the {\tt subeqn.clo} option which
defines the environment \verb|{subequations}|.

\begin{verbatim}

\begin{subequations}\label{EKx}
\begin{equation}
 y_k =  B  y_{k-1} +  f, \qquad k=1,2,3,\ldots  
\end{equation}
for  any initial vector $ y_0$.   Then 
\begin{equation}
 y_k\rightarrow  u \mbox{\quad iff\quad} \rho( B)<1.
\end{equation}
\end{subequations}

\end{verbatim}

All equations within the \verb|{subequations}| environment
will keep the same overall number, but the letter
designation will increase.

Clear equation formatting using \TeX\ can be challenging. Aside from
the regular \TeX\ documentation, authors will find Nicholas 
J. Higham's book {\em Handbook of Writing for the Mathematical
Sciences\/} \cite{Higham} useful for guidelines and tips on 
formatting with \TeX. The book covers many other topics related 
to article writing as well.

Authors commonly make mistakes by using
 \verb|<|, \verb|>|, \verb|\mid|, and 
\verb|\parallel| as delimiters, instead of 
\verb|\langle|, \verb|\rangle|, \verb:|:,
and \verb:\|:. The incorrect symbols have particular 
meanings distinct from the correct ones and should not be confused.

\begin{table}[htbp]
\caption{Illustration of incorrect delimiter use.}
\begin{center}\footnotesize
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{|ll|ll|}\hline
\multicolumn{2}{|c|}{{\bf Wrong}} & \multicolumn{2}{c|}{{\bf Right}}\\ \hline
\verb|<x, y>| & $<x, y>$   &  \verb|\langle x, y\rangle| & $\langle x, y\rangle$\\
\verb|5 < \mid A \mid| &  $5 < \mid A \mid$ & \verb:5 < |A|: &  $5 < |A|$\\
\verb|6x = \parallel x|&&&\\ 
\verb|    - 1\parallel_{i}| & $6x = \parallel x - 1\parallel_{i}$ &
   \verb:6x = \|x - 1\|_{i}: & $6x = \| x - 1\|_{i}$\\ \hline
\end{tabular}
\end{center}
\end{table}

Another common author error is to put large (and even medium sized)
matrices in-line with the text, rather than displaying them. This
creates unattractive line spacing problems, and should be assiduously
avoided. Text-sized matrices (like $({a \atop b} {b \atop c})$) might
be used but anything much more complex than the example cited will
not be easy to read and should be displayed.

More information on the formatting of equations and aligned
equations is found in Lamport \cite{Lamport}. Authors bear 
primary responsibility for formatting their equations within 
margins and in an aesthetically pleasing and informative manner.

The SIAM macros include additional roman math words, or ``log-like"
functions, to those provided in standard \TeX.  The following
commands are added: \verb:\const:, \verb:\diag:, \verb:\grad:,
\verb:\Range:, \verb:\rank:, and \verb:\supp:.
These commands produce the same word as the command name
in math mode, in upright type.

\section{Special fonts}

SIAM supports the use of the AMS-\TeX\ fonts (version 2.0
and later). The package \verb|amsfonts| can be included with
the command\linebreak \verb|\usepackage{amsfonts}|. This package
is part of the AMS-\LaTeX distribution, available
from the AMS or from the Comprehensive TeX Archive
Network (anonymous ftp to ftp.shsu.edu). The blackboard bold font in this
font package can be used for designating number sets. 
This is preferable to other methods of combining letters
(such as I and R for the real numbers) to produce pseudo-bold
letters but this is tolerable as well. Typographically speaking,
number sets may simply be designated using regular bold letters; 
the blackboard bold typeface was designed to fulfil a desire
to simulate the limitations of a chalk board in printed type.

\subsection{Punctuation}
All standard punctuation and all numerals should be set in roman type
(upright) even within italic text. The only exceptions are periods and 
commas. They may be set to match the surrounding text.

References to sections should use the symbol \S, generated by
\verb|\S|. (If the reference begins a sentence, the term ``Section''
should be spelled out in full.) Authors should not redefine
\verb|\S|, say, to be a calligraphic S, because \verb|\S|
must be reserved for use as the section symbol.

Authors sometimes confuse the use of various types of dashes.
Hyphens (\verb|-|, -) are used for some compound words (many
such words should have no hyphen but must be run together, 
like ``nonzero,'' or split apart, like ``well defined''). 
Minus signs (\verb|$-$|, $-$)
should be used in math to represent subtraction or negative numbers.
En dashes (\verb|--|, --) are used for ranges (like 3--5, 
June--August), or for joined names (like Runge--Kutta). Em dashes
(\verb|---|, ---) are used to set off a clause---such as this 
one---from the rest of the sentence.

\subsection{Text formatting}

SIAM style preferences do not make regular use of the \verb|{enumerate}|
and \verb|{itemize}| environments. Instead,
{\tt siamltex.cls} includes definitions of two alternate list
environments, \verb|{remunerate}| and \verb|{romannum}|.
Unlike the standard itemized lists, these environments do
not indent the secondary lines of text. The labels, whether
defaults or the optional user-defined, are always aligned
flush right.

The \verb|{remunerate}| environment consecutively numbers
each item with an arabic numeral followed by a period. This
number is always upright, even in slanted
environments. (For those wondering at the unusual
naming of this environment, it comes from Seroul and Levy's
\cite{SerLev} definition of a similar macro for plain \TeX: 
%{\tt \char"5C meti} 
\verb|\meti| which is
% {\tt \char"5C item}
\protect\verb|\item|  spelled backwards. Thus
%{\tt \{remunerate\}}, 
\verb|{remunerate}|
a portion of 
%{\tt \{enumerate\}}
\verb|{enumerate}|
spelled backwards.)

The \verb|{romannum}| environment consecutively numbers
each item with a lower-case roman numeral enclosed in
parentheses. This number will always be upright within
slanted environments (as in theorems).

\section{Theorems and Lemmas}
Theorems, lemmas, corollaries, definitions, and propositions are covered
in the SIAM macros by the theorem-environments
\verb|{theorem}|, \verb|{lemma}|, \verb|{corollary}|,
\verb|{definition}| and \verb|{proposition}|. These are all
numbered in the same sequence and produce labels in small 
caps with an italic body. Other environments may be specified by the
\verb|\newtheorem| command. SIAM's style is for Remarks and Examples
to appear with italic labels and an upright roman body.

\begin{verbatim}

\begin{theorem}
Sample theorem included for illustration.  
Numbers and parentheses, like equation $(3.2)$, should be set 
in roman type.  Note that words (as opposed to ``log-like''
functions) in displayed equations, such as
$$ x^2 = Y^2 \sin z^2 \mbox{ for all } x $$
will appear in italic type in a theorem, though normally
they should appear in roman.\end{theorem}

\end{verbatim}

This sample produces Theorem 4.1 below.

\begin{theorem}
Sample theorem included for illustration.  
Numbers and parentheses, like equation $(3.2)$, should be set 
in roman type.  Note that words (as opposed to ``log-like''
functions) in displayed equations, such as
$$ x^2 = Y^2 \sin z^2 \mbox{ for all } x $$
will appear in italic type in a theorem, though normally
they should appear in roman.
\end{theorem}

Proofs are handled with the \verb|\begin{proof}|
\verb|\end{proof}| environment. A ``QED'' box \endproof\ is created
automatically by \verb|\end{proof}|, but this should be
preceded with a \verb|\qquad|.

Named proofs, if used, must be done independently by the
authors. SIAM style specifies that proofs which end with
displayed equations should have the QED box two ems (\verb|\qquad|)
from the end of the equation on line with it horizontally.
Below is an example of how this can be done:

\begin{verbatim}

{\em Proof}. Proof of the previous theorem 
                .
                .
                .
thus,
$$
a^2 + b^2 = c^2 \qquad\endproof
$$

\end{verbatim}

\section{Figures and tables}
Figures and tables sometimes require special consideration.
Tables in SIAM style are need to be set in eight point size
by using the \verb|\footnotesize| command inside the 
\verb|\begin{table}| environment. Also, they should be designed 
so that they do not extend beyond the text margins.

SIAM style requires that no figures or tables  appear in the
references section of the paper. \LaTeX\ is notorious for
making figure placement difficult, so it is important to
pay particular attention to figure placement near the
references in the text. All figures and tables should
be referred to in the text.

SIAM supports the use of {\tt epsfig} for including {\sc PostScript}
figures. All {\sc Post\-Script} figures should be sent in separate
files. See the {\tt epsfig} documentation (available via
anonymous ftp from CTAN: ftp.shsu.edu) for more details on the use
of this style option. It is a good idea to submit high-quality
hardcopy of all {\sc Post\-Script} figures just in case there 
is difficulty in the reproduction of the figure. Figures produced 
by other non-\TeX\ methods should be included as high-quality 
hardcopy when  the manuscript is submitted.

{\sc PostScript} figures that are sent should be generated with
sufficient line thickness. Some past figures authors have sent
had their line widths become very faint when SIAM set the papers
using a high-quality 1200dpi printer.

Hardcopy for non-{\sc PostScript} figures should be included in
the submission of the hardcopy of the manuscript. Space
should be left in the \verb|{figure}| command for the
hardcopy to be inserted in production.

\section{Bibliography and Bib\TeX}

If using {\sc Bib}\TeX, authors need not submit the {\tt .bib} file for
their papers. Merely submit the completed {\tt .bbl} file, having used
{\tt siam.bst} as their bibliographic style file. {\tt siam.bst}
only works with Bib\TeX\ version 99i and later. The use of
Bib\TeX\ and the preparation of a {\tt .bib} file is
described in greater detail in \cite{Lamport}.

If not using Bib\TeX, SIAM bibliographic references follow
the format of the following examples:

\begin{verbatim}

\bibitem{Ri} {\sc W. Riter},
{\em Title of a paper appearing in a book}, in The Book 
Title, E.~D. One, E.~D. Two, and A.~N. Othereditor, eds., 
Publisher, Location, 1992, pp.~000--000.

\bibitem{AuTh1} {\sc A.~U. Thorone}, {\em Title of paper
with lower case letters}, SIAM J. Abbrev. Correctly, 2
(1992), pp.~000--000.

\bibitem{A1A2} {\sc A.~U. Thorone and A.~U. Thortwo}, {\em
Title of paper appearing in book}, in Book Title: With All
Initial Caps, Publisher, Location, 1992.

\bibitem{A1A22} \sameauthor, % generates the 3 em rule
{\em Title of Book{\rm :} Note Initial Caps and {\rm ROMAN
TYPE} for Punctuation and Acronyms}, Publisher,
Location, pp.~000--000, 1992.

\bibitem{AuTh3} {\sc A.~U. Thorthree}, {\em Title of paper
that's not published yet}, SIAM. J. Abbrev. Correctly, to appear.

\end{verbatim}

Other types of references fall into the same general
pattern. See the sample file or any SIAM journal for other
examples. Authors must correctly format their bibliography to
be considered as having used the macros correctly. An incorrectly 
formatted bibliography is not only time-consuming for SIAM to
process but it is possible that errors may be introduced into 
it by keyboarders/copy editors.

As an alternative to the above style of reference, an alphanumeric
code may be used in place of the number (e.g., [AUTh90]). The same
commands are used, but \verb|\bibitem| takes an optional argument
containing the desired alphanumeric code.

Another alternative is no number, simply the authors' names and
the year of publication following in parentheses. The rest of the
format is identical. The macros do not support this alternative
directly, but modifications to the macro definition are possible
if this reference style is preferred.

\section{Conclusion} Many other style suggestions and tips
could be given to help authors but are beyond the scope of this
document. Simple mistakes can be avoided by increasing your familiarity
with how \LaTeX\ functions. The books referred to throughout this document
are also useful to the author who wants clear, beautiful typography
with minimal mistakes.

\Appendix
\section{The use of appendices}
The \verb|\appendix| command may be used before the final sections
of a paper to designate them as appendices. Once \verb|\appendix|
is called, all subsequent sections will appear as

\appendix
\section{Title of appendix} Each one will be sequentially lettered
instead of numbered. Theorem-like environments, subsections,
and equations will also have the section number changed to a letter.

If there is only {\em one} appendix, however, the \verb|\Appendix|
(with a capital letter) should be used instead. This produces only 
the word {\bf Appendix} in the section title, and does not add a letter.
Equation numbers, theorem numbers and subsections of the appendix
will have the letter ``A''  designating the section number.

If you don't want to title your appendix, and just call it
{\bf Appendix A.} for example, use \verb|\appendix\section*{}| 
and don't include anything in the title field. This works
opposite to the way \verb|\section*| usually works, by including the
section number, but not using a title.

Appendices should appear before the bibliography section, not after,
and any acknowledgments should be placed after the appendices and before
the bibliography.

\begin{thebibliography}{1}
\bibitem{GoMiSa} {\sc M. Goossens, F. Mittelbach, and A. Samarin},
{\em The} \LaTeX\ {\em Companion}, Addison-Wesley, Reading, MA, 1994.

\bibitem{Higham} {\sc N.~J. Higham}, {\em Handbook of Writing for
the Mathematical Sciences}, Society for Industrial and Applied
Mathematics, Philadelphia, PA, 1993.

\bibitem{Lamport} {\sc L. Lamport}, \LaTeX: {\em A Document
Preparation System}, Addison-Wesley, Reading, MA, 1986.

\bibitem{SerLev} {\sc R. Seroul and S. Levy}, {\em A
Beginner's Book of} \TeX, Springer-Verlag, Berlin, New
York, 1991.
\end{thebibliography}

\end{document}
%% end of file `docultex.tex'

### 2013-05-17 docs/Jesse/Dissertation/utdiss2-05/chapter-howtouse.tex

\chapter{How to Use the utdiss2 Package}
\index{How to Use the utdiss2 Package%
@\emph{How to Use the utdiss2 Package}}%

\section{Preamble}
\index{Preamble@\emph{Preamble}}%

The preamble of the document starts like this:
\begin{verbatim}
     \documentclass[12pt]{report}
     \usepackage{utdiss2}
\end{verbatim}
\index{commands!documentclass@\cn{documentclass}}%
\index{commands!usepackage@\cn{usepackage}}%

The first line declares ``\texttt{report}'' as the document 
class, 
\index{document class}%
with an option of 12pt for the character size, 
which is slightly greater that usual (the default is 10pt), but is
what the Office of the Graduate School (OGS) recommends.
You may include other options, as in any other \LaTeX{} document.

The second line loads the \texttt{utdiss2} package, 
\index{utdiss2 package@{\texttt{utdiss2} package}}%
which contains a set of commands intended to produce a document fulfilling
the official requirements for a doctoral dissertation or master's thesis or
report. Besides that, you may include other packages. 
For instance:
\begin{verbatim}
     \usepackage{amsmath,amsthm,amsfonts,amscd}
\end{verbatim}
for mathematical symbols, or,
\begin{verbatim}
     \usepackage{draftcopy}
\end{verbatim}
to have a large ``watermark'' across each page of your document that
says, ``DRAFT.''

The next few commands in the preamble are required.

\cn{author\{Craig William McCluskey\}}
\index{commands!author@\cn{author}}%
Replace my name in the command by your
full, official University name.  Make it combination of lower and uppercases.

\cn{address\{9905 Chukar Circle\bslash\bslash\ Austin, Texas 78758\}}
\index{commands!address@\cn{address}}%
Replace my address with your *permanent* (not local) address. Use
\texttt{\bslash\bslash} to separate address lines.

\cn{title\{Writing a Doctoral Dissertation with \cn{LaTeX\{\}} at
the University of Texas at Austin\} }
\index{commands!title@\cn{title}}%
Replace the name of this document
in this command by your dissertation title. If the title consists of more
than one line, it should be in inverted pyramid form. You may have to specify
the line breakings by \texttt{\bslash\bslash} commands.

\cn{supervisor[Isaac Newton]\{Johannes Kepler\} }
\index{commands!supervisor@\cn{supervisor}}%
This document has two supervisors listed. See the source file
(disstemplate.tex) for information on how to have only one supervisor.
This command can be broken across lines as it is in the source file and
as the \cn{committeemembers} command is shown below.

\begin{verbatim}
\committeemembers
        [Erwin Schr\"odinger]
        [Albert Einstein]
        [Charles Townes]
        {Arthur Schawlow}
\end{verbatim}
\index{commands!committeemembers@\cn{committeemembers}}%
This document shows four non-supervisor committee members. See the source
file (disstemplate.tex) for information on how to have a different number.

\cn{previousdegrees\{B.S.\} } Replace B.S. with your previous degree.

The next few commands in the preamble are optional.
\begin{verbatim}
%\graduationmonth{...}
%\graduationyear{...}
%\typist{...}
\end{verbatim}
Their use is documented in the source file.

At this point, if you are writing a master thesis or report
you must use the optional \cn{degree} and \cn{degreeabbr} commands
and specify
\index{master}
\index{master!master thesis}
\index{commands!masterthesis@\cn{masterthesis}}
\index{master!master report}
\index{commands!masterreport@\cn{masterreport}}
\begin{verbatim}
%\degree{MASTER OF ARTS}
%\degreeabbr{M.A.}
%\masterreport
%\masterthesis
\end{verbatim}
as documented in the source file. By default the document is formated
as a \emph{dissertation}%
\footnote{The command \cn{dissertation} is also provided for symmetry.}%
\index{commands!dissertation@\cn{dissertation}}

The default spacing for both text and quoted text is doublespaced.
That can be changed with the following self-explanatory commands: 
\begin{verbatim}
\oneandonehalfspacing 
\singlespacing
\oneandonehalfspacequote
\singlespacequote
\end{verbatim}
\index{commands!oneandonehalfspacing@\cn{oneandonehalfspacing}}%
\index{commands!singlespacing@\cn{singlespacing}}%
\index{commands!oneandonehalfspacequote@\cn{oneandonehalfspacequote}}%
\index{commands!singlespacequote@\cn{singlespacequote}}%

Some versions of LaTeX in combination with some types of printers
produce printed output that has incorrect vertical margins.
The command \cn{topmargin 0.125} is provided to allow easy adjustment
if it's needed.

If there are 10 or more sections, 10 or more subsections for a section,
etc., you need to make an adjustment to the Table of Contents with the
command \cn{longtocentry}.
\index{commands!longtocentry@\cn{longtocentry}}%
This command allocates the proper horizontal space for double-digit
numbers.

\section{Document}
\index{Document@\emph{Document}}%

Next comes the actual text. It could be a sequence of chapters divided
into sections, subsections, etc., all in the main file:
\begin{verbatim}
\chapter{...}     % The first chapter. The
                  % \chapter command is of the form
                  % \chapter[..]{..} or \chapter{..} where
    ... text ...  % [...] is the entry in table of contents
                  % and {...} is the chapter heading printed
                  % in the body of the document.
\section{...}     %
                  % IMPORTANT: If your chapter heading consists
                  % of more than one line, it will be auto-
    ... text ...  % matically broken into separate lines.
                  % If you don't like the way LaTeX breaks the
                  % chapter heading into lines, however, use
\section{...}     % `\newheadline' command to break lines.
                  % NEVER USE \\ IN SECTIONAL (E.G., CHAPTER,
    ... text ...  % SECTION, SUBSECTION, SUBSUBSECTION) HEADINGS!
                  %
\chapter{...}     % This is Chapter 2.
    ... text ...
\section{...}
    ... text...
\subsection{...}
    ... more text ...
\subsubsection{...}
    ... more text ...
\appendix         % The appendix begins here.
% \appendices     % If more than one appendix chapters,
                  % use \appendices instead of \appendix
\chapter{...}     % First appendix chapter, i.e., Appendix A.
\section{...}     % This is appendix section A.1.
    .................
\end{verbatim}
\index{commands!chapter@\cn{chapter}}%
\index{commands!section@\cn{section}}%
\index{commands!subsection@\cn{subsection}}%
\index{commands!appendix@\cn{appendix}}%
\index{commands!appendices@\cn{appendices}}%

Or, the chapters can be written in different files like this document
and be loaded by \cn{include} commands:
\begin{verbatim}
\include{chapter-introduction}
\include{chapter-instructions}
\include{chapter-howtouse}
\include{chapter-makingbib}
\include{chapter-tables+figs}
\include{chapter-math}
\appendices
\index{Appendices@\emph{Appendices}}%
\include{chapter-appendix1}
\include{chapter-appendix2}
\include{chapter-appendix3}
\end{verbatim}
\index{commands!include@\cn{include}}%
Having the chapters in separate files makes the main .tex file simpler
and allows chapters to be easily re-ordered (just swap the order of the
include commands) or left (commented) out for draft copies.

Note: If you have only one appendix, in addition to using
\cn{appendix} instead of \cn{appendices}, you must leave out the
\cn{chapter} definition at the start of the appendix's text. Putting
it in will cause the insertion of an extra page with only the word
Appendix on it and will cause the appendix to be labeled Appendix 1,
both of which are poor form if there is only one appendix.

If you are writing a short dissertation 
\index{short dissertation}%
that does not require 
chapters, you need to use the command \cn{nochapters} 
\index{commands!nochapters@\cn{nochapters}}%
just before the first section:

\begin{verbatim}
\nochapters

\section{...}     % First section.
    ... text ... 
\section{...}     % Second section.
    ... text ... 
        (...)
\end{verbatim}

Next comes the bibliography.
\index{bibliography}%
It can be made by hand like this:
\begin{verbatim}
\begin{thebibliography}{foo}
\bibitem ...   
\end{thebibliography}
\end{verbatim}
\index{commands!environments!thebibliography}%
Or it can also be generated with BiB\TeX{}, 
\index{BiBTeX@BiB\TeX{}}%
as explained in chapter \ref{c:bib}.

Finally the vita is produced like this:
\begin{verbatim}
\begin{vita}
     % Insert your brief biographical sketch here. 
     % Your permanent address and the name of the 
     % typist(s) are generated automatically.
\end{vita}

\end{verbatim}

### 2013-06-04 docs/Jesse/Dissertation/DPGtheory.tex

--- 2013-04-29 docs/Jesse/HeuerPaper/paperForCAMWA.tex
@@
-%&pdflatex
-\documentclass[11pt,onecolumn]{scrartcl}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
-\usepackage[top=2cm,bottom=3cm,left=2.5cm,right=2cm]{geometry}
-\usepackage{amssymb}
-\usepackage{listings}
-\usepackage{array}
-\usepackage{mathtools}
-\usepackage{dsfont}
-\usepackage{graphicx}
-\usepackage{pdfpages}
-\usepackage[textsize=footnotesize,color=green]{todonotes}
-\usepackage{algorithm, algorithmic}
-\usepackage{array}
-\usepackage{bm}
-\usepackage{tikz}
-\usepackage{subfigure}
-\usepackage[normalem]{ulem}
-\usepackage{epstopdf}
-
-\newcommand{\bs}[1]{\boldsymbol{#1}}
-\DeclareMathOperator{\diag}{diag}
-
-\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}
-
-\newcommand{\tablab}[1]{\label{tab:#1}}
-\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
-
-\newcommand{\theolab}[1]{\label{theo:#1}}
-\newcommand{\theoref}[1]{\ref{theo:#1}}
-\newcommand{\eqnlab}[1]{\label{eq:#1}}
-\newcommand{\eqnref}[1]{\eqref{eq:#1}}
-\newcommand{\seclab}[1]{\label{sec:#1}}
-\newcommand{\secref}[1]{\ref{sec:#1}}
-\newcommand{\lemlab}[1]{\label{lem:#1}}
-\newcommand{\lemref}[1]{\ref{lem:#1}}
-
-\newcommand{\mb}[1]{\mathbf{#1}}
-\newcommand{\mbb}[1]{\mathbb{#1}}
-\newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\nor}[1]{\left\| #1 \right\|}
-\newcommand{\snor}[1]{\left| #1 \right|}
-\newcommand{\LRp}[1]{\left( #1 \right)}
-\newcommand{\LRs}[1]{\left[ #1 \right]}
-\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
-\newcommand{\LRc}[1]{\left\{ #1 \right\}}
-\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
-\newcommand{\Grad} {\ensuremath{\nabla}}
-\newcommand{\Div} {\ensuremath{\nabla\cdot}}
-\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
-\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
-\newcommand{\uh}{\widehat{u}}
-\newcommand{\fnh}{\widehat{f}_n}
-\renewcommand{\L}{L^2\LRp{\Omega}}
-\newcommand{\pO}{\partial\Omega}
-\newcommand{\Gh}{\Gamma_h}
-\newcommand{\Gm}{\Gamma_{-}}
-\newcommand{\Gp}{\Gamma_{+}}
-\newcommand{\Go}{\Gamma_0}
-\newcommand{\Oh}{\Omega_h}
-
-\newcommand{\eval}[2][\right]{\relax
-  \ifx#1\right\relax \left.\fi#2#1\rvert}
-
-\def\etal{{\it et al.~}}
-
-\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
-\newcommand{\tensor}[1]{\underline{\vect{#1}}}
-\newcommand{\del}{\Delta}
-\newcommand{\grad}{\nabla}
-\newcommand{\curl}{\grad \times}
-\renewcommand{\div}{\grad \cdot}
-\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
-\newcommand{\eip}[1]{a\left( #1 \right)}
-\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
-\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
-
-\newcommand{\circone}{\ding{192}}
-\newcommand{\circtwo}{\ding{193}}
-\newcommand{\circthree}{\ding{194}}
-\newcommand{\circfour}{\ding{195}}
-\newcommand{\circfive}{\ding{196}}
-
-\def\arr#1#2#3#4{\left[
-\begin{array}{cc}
-#1 & #2\\
-#3 & #4\\
-\end{array}
-\right]}
-\def\vecttwo#1#2{\left[
-\begin{array}{c}
-#1\\
-#2\\
-\end{array}
-\right]}
-\def\vectthree#1#2#3{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-\end{array}
-\right]}
-\def\vectfour#1#2#3#4{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-#4\\
-\end{array}
-\right]}
-
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-
-\newcommand{\G} {\Gamma}
-\newcommand{\Gin} {\Gamma_{in}}
-\newcommand{\Gout} {\Gamma_{out}}
-
-\author{Jesse Chan\textsuperscript{a}, Norbert Heuer\textsuperscript{b}, Tan Bui-Thanh\textsuperscript{a}, and Leszek Demkowicz\textsuperscript{a}}
-
-%\title{$\epsilon$-explicit analysis of DPG for convection-dominated diffusion}
-\title{A robust DPG method for convection-dominated diffusion problems II: adjoint boundary conditions and mesh-dependent test norms.}
-\date{}
-\begin{document}
-
-%\tableofcontents
-\maketitle
-\begin{center}
-\textsuperscript{a} Institute for Computational Engineering and Sciences, \\University of Texas at Austin, \\Austin, TX 78712, USA\\
-\end{center}
-
-\begin{center}
-\textsuperscript{b} Facultad de Matem\'aticas, \\Pontificia Universidad Cat\'olica de Chile,\\
-Avenida Vicu\~na Mackenna 4860, Santiago, Chile
-\end{center}
-
-\section{Introduction}
-
-\subsection{Singular perturbation problems and robustness}
-
-The finite element/Galerkin method has been widely utilized in engineering to solve partial differential equations governing the behavior of physical phenomena in engineering problems.
-The method relates the solution of a partial differential equation (PDE) to the solution of a corresponding variational problem.
-The finite element method itself provides several advantages --- a framework for systematic mathematical analysis of the behavior of the method, weaker regularity constraints on the solution than implied by the strong form of the equations, and applicability to very general physical domains and geometries.
-
-Historically, the Galerkin method has been very successfully applied to a broad range of problems in solid mechanics, for which the variational problems resulting from the PDE are symmetric and coercive (positive-definite).
-It is well known that the finite element method produces optimal or near-optimal results for such problems, with the finite element solution matching or coming close to the best approximation of the solution in the finite element space.
-However, standard Bubnov-Galerkin methods tend to perform poorly for the class of PDEs known as singular perturbation problems.
-These problems are often characterized by a parameter that may be either very small or very large in the context of physical problems.
-An additional complication of singular perturbation problems is that very often, in the limiting case of the parameter blowing up or decreasing to zero, the PDE itself will change types (e.g.\ from elliptic to hyperbolic).
-
-\subsubsection{Convection-diffusion}
-
-A canonical example of a singularly perturbed problem is the convection-diffusion equation.
-%The equation models the convection of fluid along a direction $\beta$ with a viscous dissipation of magnitude $\epsilon$.
-In the limit as $\epsilon\rightarrow 0$, the convection-diffusion equation transforms from a parabolic to a hyperbolic partial differential equation.
-In 1D, the convection-diffusion equation is
-\begin{align*}
-\beta u'-\epsilon u'' &= f.
-\end{align*}
-The equation represents the change in the concentration $u$ of a quantity in a given medium, taking into account both convective and diffusive effects.
-$\beta$ represents the speed of convection, while the singular perturbation parameter $\epsilon$ represents the diffusivity of the medium.
-In the limit of an inviscid medium as $\epsilon\rightarrow 0$, the equation changes types, from elliptic to hyperbolic, and from second order to first order.
-For Dirichlet boundary conditions $u(0)=u_0$ and $u(1)= u_1$, the solution can develop sharp boundary layers of width $\epsilon$ near the outflow.
-
-%The finite element method has performed notoriously poorly for this example, as well as for many other singularly perturbed problems.
-This poor performance is captured by the error bound for the finite element method applied to the convection-diffusion equation - under the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}
-The poor performance of the finite element method for this problem is reflected in the bound on the error in the finite element solution --- under the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}:
-\[
-\|u-u_h\|_\epsilon \leq C \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
-\]
-for $\|u\|_\epsilon^2 \coloneqq \|u\|_{L^2}^2 + \epsilon \|u'\|_{L^2}^2$, with $C$ independent of $\epsilon$. An alternative formulation of the above bound is 
-\[
-\|u-u_h\|_{H^1(0,1)} \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
-\]
-where $C(\epsilon)$ grows as $\epsilon\rightarrow 0$.
-The dependence of the constant $C$ on $\epsilon$ is referred to as a \textit{loss of robustness} --- as the singular perturbation parameter $\epsilon$ decreases, our finite element error is bounded more and more loosely by the best approximation error.
-As a consequence, the finite element solution can diverge significantly from the best finite element approximation of the solution for very small values of $\epsilon$.
-For example, on a coarse mesh, and for small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation with a boundary layer develops spurious oscillations everywhere in the domain, even where the best approximation error is small.
-These oscillations grow in magnitude as $\epsilon \rightarrow 0$, eventually polluting the entire solution.
-
-%, allowing for more and more error in the finite element solution for as $\epsilon$ shrinks. 
-%Intuitively, a non-robust method will perform increasingly worse as $\epsilon$ decreases.
-
-\subsubsection{Wave propagation}
-
-Another example of a singular perturbation problem which experiences loss of robustness is high frequency wave propagation, in which the singular perturbation parameter is the wavenumber $k$, where $k\rightarrow \infty$.
-The loss of robustness in this case manifests as ``pollution" error, a phenomenon in which the finite element solution degrades over many wavelengths for high wavenumbers (commonly manifesting as a phase error between the FE solution and the exact solution).
-
-\subsubsection{Stabilization terms}
-
-Traditionally, instability/loss of robustness has been dealt with using residual-based stabilization techniques.
-Given some variational form, the problem is modified by adding to the bilinear form the strong form of the residual, weighted by a test function and scaled by a stabilization constant $\tau$.
-The most well-known example of this technique is the streamline-upwind Petrov-Galerkin (SUPG) method, which is a stabilized method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.
-In the 1D case, SUPG stabilization not only removes the spurious oscillations from the finite element solution of the convection-diffusion equation, but delivers the best finite element approximation in the $H^1$ norm.
-An important difference between residual-based stabilization techniques and other stabilizations is the idea of \textit{consistency} --- by adding stabilization terms based on the residual, the exact solution still satisfies the same variational problem (i.e.\ Galerkin orthogonality still holds).\footnote{Contrast this to an artificial diffusion method, where a specific amount of additional viscosity is added based on the magnitude of the convection and diffusion parameters.
-The exact solution to the original equation no longer satisfies the new stabilized formulation.}
-
-The addition of residual-based stabilization terms has also been interpreted as a modification of the test functions --- in other words, stabilization can be achieved by changing the test space for a given problem.
-We approach the idea of stabilization through the construction of \textit{optimal test functions} to achieve optimal approximation properties.
-
-%\textcolor{red}{add bit about SUPG/residual-based stabilization terms and test functions}
-
 \subsection{Discontinuous Petrov-Galerkin methods with optimal test functions}
@@
 
-Throughout the paper, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U'$ and $V'$ as the respective topological dual spaces.
+Throughout this dissertation, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U'$ and $V'$ as the respective topological dual spaces.
 Let $U_h \subset U$ and $V_h\subset V$ be finite dimensional subsets.
@@
 More recently, this theory has been generalized to show the well-posedness of DPG for the large class of PDEs of Friedrichs' type \cite{Bui-ThanhDemkowiczGhattas11b}.
-
-\section{Model problem and robustness}
-\seclab{sec:modelSec}
-The remainder of the paper focuses on a convection-diffusion model problem using the abstract theory that we
-have discussed so far.
-In particular, we shall use the DPG method based on the ultra-weak formulation with optimal test functions to solve the model problem and analyze its behavior with respect to $\epsilon$.
-Our goal is to show the robustness of the method with respect to $\epsilon$, and demonstrate its usefulness as  a numerical approach to solving singular-perturbed problems.
-
-We consider the following model convection-diffusion problem on a domain
-$\Omega \subset \mathbb{R}^d$ with boundary $\pO \equiv \Gamma$
-\begin{equation}
-\div (\beta u) - \epsilon\Delta u = f  \in \L \label{primal},
-\end{equation}
-which can be cast into the first order form on the group variable
-$\LRp{u,\sigma}$ as
-\begin{equation}
-\eqnlab{CDstrong}
-A \LRp{u,\sigma} \coloneqq \LRs {
-\begin{array}{c}
-\div (\beta u - \sigma) \\ \frac{1}{\epsilon}\sigma - \grad u
-\end{array}} = \LRs{
-\begin{array}{c}
-f \\ 0
-\end{array}
-}.
-\end{equation}
-Using the abstract ultra-weak formulation developed in Section
-\secref{abstractUweak} for the first order system of PDEs \eqnref{CDstrong} we
-obtain
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh} - \LRa{
-\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n,
-  \jump{v} }_{\Gh},
-\end{align*}
-where $\LRp{v, \tau}$ is the group test function. It should be pointed
-out that the divergence and gradient operators are understood to act
-element-wise on test functions $\LRp{v, \tau}$ in the broken graph
-space $ D\LRp{A_h^*} \coloneqq  H^1(\Oh) \times H({\rm div}, \Oh)$, but
-globally as usual on conforming test functions, i.e.\ $ \LRp{v, \tau}
-\in  H^1(\Omega) \times H({\rm div}, \Omega)$. It follows that the
-canonical norm on this test space can be written as
-\[
-\|\left(v, \tau\right)\|_V^2 = \|\left(v, \tau\right)\|_{H^1(\Oh) \times H({\rm div},\Oh)}^2
-= \sum_{K\in \Oh} \|\left(v, \tau\right)\|_{H^1(K) \times H({\rm
-    div},K)}^2,
-\]
-where
-\[
-\|\left(v, \tau \right)\|_{H^1(K) \times H({\rm div},K)}^2 =
-\|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2 + \|\tau\|_{L^2(K)}^2 +
-\|\div \tau\|_{L^2(K)}^2.
-\]
-
-In order to define the proper norm on the trial space, boundary
-conditions need to be specified. We begin by splitting the boundary
-$\Gamma$ as follows
-\begin{align*}
-\Gamma_{-} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\}, \quad {\rm
-  (inflow)}\\ \Gamma_{+} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\},
-\quad {\rm (outflow)}\\ \Gamma_{0} &\coloneqq \{x\in \Gamma;
-\beta_n(x) = 0\},
-\end{align*}
-where $\beta_n \coloneqq \beta \cdot n$.
-Previous work in \cite{DPGrobustness} adopted Dirichlet boundary
-conditions everywhere on $\Gamma$.  
-%and we could obtain the robustness only with special weighted norms in which the weight varied spatially. 
-In this paper, we employ the inflow
-condition of Hesthaven \etal \cite{Hesthaven96astable}, where we set
-\[
-\beta_n u - \sigma_n  = u_0, \quad \text{on } \Gm,
-\]
-instead of $\beta_n u = u_0$.
-The former resembles the latter as $\epsilon$ approaches zero\footnote{For our model problem, as for many problems of interest in computational fluid dynamics, we expect $\grad u$ to be small near the inflow, and that the solutions to \eqref{primal} using $\beta_n u - \sigma_n = f_n = u_0$ on $\Gamma_-$ will converge to that using $u=u_0$ on $\Gamma_-$  for sufficiently small $\epsilon$.}; however, the latter induces a more ``well-behaved" adjoint problem than the former, which, as we will discuss, affects the performance of DPG.
-Physically speaking, as the above boundary condition corresponds to the integration by parts of the conservation equation, a boundary condition on $\beta_n u - \sigma_n$ models a boundary condition on the conserved flux.
-
-On the outflow boundary, we apply standard homogeneous Dirichlet boundary conditions
-\[
-u = 0, \quad \text{on } \Gp.
-\]
-This paper is intended to act as an extension of work presented by Heuer and Demkowicz in \cite{DPGrobustness}.
-The primary focus of the paper is to analyze the DPG method and extend previous results under this new choice of inflow boundary conditions.
-The difference in the performance of DPG under both new and old boundary conditions is connected to the difference in the adjoint problems induced under each boundary condition.
-The secondary contribution of this paper will be to analyze the performance of DPG under a new mesh-dependent test norm.
-
-\subsection{Norms on $U$}
-
-With the above boundary conditions at hand, the ultra-weak formulation
-\eqnref{uweak} can be fitted in the abstract form \eqnref{variationEq}
-as
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right), \left( v,
-\tau\right)\right) &= \left(u,\div \tau - \beta \cdot \grad
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad
-v\right)_{\Oh} \\
-&- \LRa{ \jump{\tau\cdot n}, \widehat{u} }_{\Gh
-  \setminus \Gp} + \LRa{ \widehat{f}_n, \jump{v} }_{\Gamma_h \setminus
-  \Gm} =  \left(f, v\right) -
-\LRa{ u_0, v }_{\Gamma_-} = l\left(\left(v, \tau\right)\right),
-\end{align*}
-which, after using the setting in Section \secref{abstractUweak},
-suggests the following trial space (see \cite{analysisDPG, Bui-ThanhDemkowiczGhattas11b} for details):
-\begin{align*}
-u, \sigma \in \L, \quad \text{and } \LRp{\uh,\fnh} \in
-\gamma\LRp{D\LRp{A}} \subset \gamma\LRp{  H^1(\Omega) \times
-H({\rm div}, \Omega)} = H^{\frac{1}{2}}\left(\Gh\right) \times H^{-\frac{1}{2}}\left(\Gh\right).
-\end{align*}
-The space for $u$ and $\sigma$ are simply scalar and vector $L^2$ spaces over $\Omega$, while the space for $\left(\uh,\fnh\right)$ is the trace space of the graph space of the operator $A$ subject to the boundary conditions.
-
-The minimum energy extension norm \eqnref{MEnorm} now reads
-\begin{align*}
-\|\widehat{u}\| &= \inf_{w\in H^1(\Omega),
-  \left.w\right|_{\Gamma_+}=0, \left.w\right |_{\Gh\setminus
-    \Gamma_+ } = \widehat{u}} \|w\|_{H^1(\Omega)}, \\ \|\widehat{f}_n\|
-&= \inf_{q\in H({\rm div},\Omega), \left.q\cdot n\right|_{\Gamma_-}=
-  0, \left. q\cdot n \right |_{\Gh\setminus
-    \Gamma_-} = \widehat{f}_n}
-\|q\|_{H({\rm div},\Omega)}.
-\end{align*}
-As a result, the canonical norm on $U$ is given by
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U^2 = 
-\|u\|_{L^2(\Oh)}^2 + \|\sigma\|_{L^2(\Oh)}^2 +
-\|\widehat{u}\|^2 + \|\widehat{f}_n\|^2.
-\]
-
-\subsection{Norms on $V$}
-
-%We will denote $\|\cdot \| = \|\cdot\|_{L^2}$ for all functions defined on $\Oh$. 
-As $\tau \in H({\rm div},\Oh)$ and $v \in H^1(\Oh)$, we will
-construct norms on $v$ and $\tau$ 
-which are equivalent to the canonical $H^1(K) \times H({\rm div},K)$
-norm over a single element
-\[
-\|\left(v,\tau\right)\|_{H^1(K) \times H({\rm div},K)}^2 =
-\|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2 + \|\tau\|_{L^2(K)}^2 +
-\|\div \tau\|_{L^2(K)}^2.
-\]
-The squared norm over the entire triangulation $\Oh$ is defined to be the squared sum of contributions from each element
-\[
-\|\left(v,\tau\right)\|_{H^1(\Oh) \times H({\rm div},\Oh)}^2
-= \sum_{K\in \Oh} \|\left(v,\tau\right)\|_{H^1(K) \times H({\rm
-    div},K)}^2.
-\]
-The exact norms that we will specify on $V$ will be determined later.
-
-The norms on the skeleton $\Gh$ for $v$ and $\tau$ are defined by duality from the bilinear form
-\begin{align*}
-\left\|\jump{\tau\cdot n}\right\| &= \left\|\jump{\tau\cdot n}\right\|_{\Gh \setminus \Gamma_+} \coloneqq \sup_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+} = 0} \frac{\langle \jump{\tau \cdot n}, w\rangle}{\|w\|_{H^1(\Omega)}},\\
-\left\|\jump{v}\right\|&=\left\|\jump{v}\right\|_{\Gh^0 \cup \Gamma_+} \coloneqq \sup_{\eta\in H({\rm div},\Omega), \left.\eta\cdot n\right|_{\Gamma_- \cup \Gamma_0} = 0} \frac{\langle \jump{v}, \eta\cdot n\rangle}{\|\eta\|_{H({\rm div},\Omega)}}.
-\end{align*}
-
-\subsection{Approximability of the quasi-optimal test norm}
-%\textcolor{blue}{need to define what we mean by robustness. perharps the best place is in the introduction}
-An obvious choice for the test norm would be the quasi-optimal norm; it is the canonical test norm, and DPG has been shown to be well-posed and robust under such an optimal test norm for a large class of problems \cite{DPGrobustness,Bui-ThanhDemkowiczGhattas11b, stokesDPG}.
-However, computations with the quasi-optimal test norm for convection-diffusion problems turn out to be quite problematic for small diffusion and coarse meshes.
-
-For convection-diffusion, the quasi-optimal test norm is 
-\[
-\|\left(v,\tau\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v
-\|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 +
-\|v\|_{L^2}^2 + \|\tau\|_{L^2}^2.
-\]
-%We note that the optimal test norm will automatically guarantee the
-%robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.
-Use of this norm for the convection-diffusion problem is difficult --- since the problem \eqnref{optvVar} for optimal test functions is local, we can transform the problem over a single element $K$ to the reference element $\widehat{K}$ and show that it is equivalent to a reaction-diffusion system, with diffusion parameter $\frac{\epsilon}{|K|}$, where $|K|$ is the element measure \cite{DBLP:journals/procedia/NiemiCC11}.
-We refer to the inverse of this parameter $\frac{|K|}{\epsilon}$ as the element Peclet number $\rm Pe$.
-For a coarse mesh and small diffusion parameter $\epsilon$, we will have a large element Peclet number, and optimal test functions under the quasi-optimal test norm will develop strong boundary layers of width $\rm Pe$, as seen in Figure~\ref{fig:optTestBoundary}.
-
-In the application of DPG in \cite{DPG1,DPG2,DPG3,DPG4}, the approximation of optimal test functions is done using polynomial enrichment.
-We search for the solution to \eqnref{optvVar} in the enriched test space $\tilde{V} \approx \prod_{K} P^{p+\Delta p}(K)$, where $p$ is the polynomial order of the trial space on a given element $K$.\footnote{$V$ is only \emph{approximately} equal to the space $\prod_{K} P^{p+\Delta p}(K)$.
-In practice, $V$ is constructed using locally $H^1$-conforming and Raviart-Thomas elements of appropriate order.}  In other words, optimal test functions are approximated element-by-element using polynomials whose order is $\Delta p$ more than the local order of approximation.
-Under this scheme, the error in approximation of test functions is tied to the effectiveness of the $p$-method.
-Unfortunately, for problems with boundary layers --- including the approximation of test functions under the quasi-optimal test norm --- the $p$-method performs very poorly.
-As a result of this poor approximation, the numerical solutions of the convection-dominated diffusion equation under DPG using the quasi-optimal test norm tend to be of poor quality, and do not exhibit all the proven properties of DPG (for example, the energy error may increase after mesh refinement, even though, by virtue of DPG delivering a best approximation, the energy error for a coarse mesh must be greater than or equal to the energy error for a finer mesh).
-We conclude that the error in approximation of optimal test functions using simple polynomial enrichment pollutes and ruins the performance of DPG under the quasi-optimal test norm.
-
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.25]{opt.png}
-\caption{$v$ and $\tau$ components of the 1D optimal test functions corresponding to the flux $\widehat{f}_n$ on the right-hand side of a unit element for $\epsilon = 0.01$.
-The solution has been obtained using automatic $hp$-adaptivity driven by the test norm with the error tolerance set at 1\%.}
-\label{fig:optTestBoundary}
-\end{figure}
-
-The difficulty in using the quasi-optimal test norm for convection-diffusion is perplexing at first, considering that the quasi-optimal norm has yielded excellent results for the Helmholtz equation and other wave propagation problems.
-The difference between the two problems lies in the fact that, for wave propagation problems, the mesh size tends to be on the order of the wavenumber $k$ --- the singular perturbation parameter.
-Transforming the variational problem using the quasi-optimal test norm for wave propagation yields smooth optimal test functions that are approximated much more accurately using only polynomials over the reference element.
-Typically, the wavenumbers $k$ of physical interest are $O(100)$ with respect to a unit domain.
-The corresponding finite element problems will typically be solved on meshes containing approximately $O\!\left(k^d\right)$ elements in $\mathbb{R}^d$, well within the range of a computationally tractable simulation.
-However, for convection diffusion problems, the relevant range of $\epsilon$ for physical problems can be as small as $1e-7$.
-Solving on under-resolved meshes is thus unavoidable, and the approximability of optimal test functions must be addressed in order to take advantage of the properties of DPG.
-
-Resolving such boundary layers present in test functions under the quasi-optimal test norm has been investigated numerically using specially designed (Shishkin) subgrid meshes by Niemi, Collier, and Calo in
-\cite{DBLP:journals/procedia/NiemiCC11}.
-However, even with Shishkin meshes, the approximation of optimal test functions under the quasi-optimal norm is far more expensive and complex to implement than approximation of test functions using a simple $p$-enriched space for $V$.
-We therefore aim instead to design a test norm that does not induce boundary layers, but still delivers good approximation results over a range of $\epsilon$.
-
-\section{Analysis of a DPG test norm}
-\seclab{sec:testNormSec}
-We are interested in computing DPG optimal test functions for the convection-diffusion equation with very small values of $\epsilon$; due to the difficulty of approximating optimal test functions, we conclude that the use of the quasi-optimal test norm is infeasible towards this goal.
-
-However, if we naively choose a test norm that does not generate boundary layers, the performance of DPG may be adversely affected.
-For example, if $\|\left(v,\tau\right)\|_V^2 = \|v\|_{H^1(\Omega_h)}^2 + \|\tau\|^2_{H({\rm div},\Omega_h)}$, the $H^1(\Omega_h)\times H({\rm div},\Omega_h)$ norm, then the corresponding test functions will be smooth and free of boundary layers; however, the performance of DPG will provide approximations which worsen in quality as $\epsilon$ becomes very small \cite{DPG3,DPGrobustness}.
-
-Our goal is to construct a test norm that compromises between performance of DPG and approximability of test functions.
-This test norm should not produce boundary layers in the optimal test functions, but still induce an energy norm that yields good approximation properties for small $\epsilon$.
-We note that, even under the quasi-optimal norm, the norms on the flux and trace variables will likely depend on $\epsilon$.
-Thus, we aim to construct a test norm for which the DPG method will be robust in $\epsilon$ with respect to the \emph{field variables}.
-
-For now, we discuss the steps necessary to analyze the performance of DPG with respect to a non-canonical test norm.
-We require a priori that the test norm has separable $\tau$ and $v$ components --- in other words, that there are no terms in the test norm that couple $\tau$ and $v$ together.
-Problem \eqnref{optvVar} then decouples, such that the components of the vector-valued test function $\left(v,\tau\right)$ can be solved for independently of each other.
-The decoupled variational problems are no longer systems but scalar equations in $\tau$ and $v$, for which it is easier to conclude whether or not there are boundary layers in the solutions (the avoidance of boundary layers in the test norm will be discussed in more detail in Section~\ref{sec:num_exp}, which describes our numerical experiments).
-This will ensure that the resulting DPG method does not suffer from approximation errors in the optimal test functions.
-
-We begin with the following test norm:
-\[
-\left\|\left(v,\tau\right)\right\|^2_V \coloneqq \|v\|_{L^2}^2 + \epsilon\|\grad v\|_{L^2}^2 + \|\beta \cdot \grad v\|_{L^2}^2  + \frac{1}{\epsilon}\|\tau\|_{L^2}^2 + \|\div \tau\|_{L^2}^2.
-\]
-The use of this norm is problematic for practical computations; we will discuss the reasons why and present a modification of it in Section~\secref{sec:meshDep}.
-
-We can see how this norm will differ from the canonical $H^1(\Omega_h)\times H({\rm div},\Omega_h)$ norm: the clearest difference is the fact that the gradient in the streamline direction is $O(1)$, while the full gradient is $O(\sqrt{\epsilon})$, so that, in our test norm, the streamline gradient of $v$ will be emphasized over the full gradient of $v$ for small $\epsilon$.
-
-The choice of this test norm is implied by the mathematics of the adjoint problem.
-Roughly speaking, necessary conditions for the performance of DPG to not degenerate as $\epsilon \rightarrow 0$ are derived through analysis of specific test functions.
-For example, if $u$ is the first $L^2$ component of the solution to the variational problem defined in Section~\secref{sec:modelSec}, by choosing $(v,\tau) \in H^1(\Omega) \times H({\rm div},\Omega)$ such that
-\begin{align*}
-\div \tau - \beta \cdot \grad v &= u \\
-\frac{1}{\epsilon} \tau - \grad v &= 0,
-\end{align*}
-we have
-\[
- \nor{u}_{L^2}^2 = b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(v,\tau\right)\right) \leq \nor{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)}_{U,V} \nor{\left(v,\tau\right)}_V,
-\]
-and we recover the $L^2$ norm of $u$ from the bilinear form.
-
-Let $\|a\| \lesssim \|b\|$ denote an $\epsilon$-independent bound; specifically, that $\|a\| \leq C\|b\|$ for a constant $C$ independent of $\epsilon$.
-Consequently, if for any $u\in L^2(\Oh)$, $\nor{\left(v,\tau\right)}_V\lesssim \nor{u}_{L^2}$, then dividing through by $\nor{u}_{L^2}$ gives the bound
-\[
- \nor{u}_{L^2} \lesssim \nor{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)}_E.
-\]
-In other words, there is the guarantee that the $L^2$ error in $u$ is at least robustly bounded from above by the energy error.
-Then, if the energy error (which DPG minimizes) approaches zero, the $L^2$ error in $u$ will as well.
-The same exercise can be repeated for the stress $\sigma$, as well as the flux variables $\widehat{u}$, $\widehat{f}_n$.
-
-This methodology gives constraints on the quantities found in the test norm; any quantity present in $\nor{\left(v,\tau\right)}_V$ must be shown to be bounded from above independently of $\epsilon$ by the load of the adjoint problem.
-However, showing this simply amounts to showing \textit{standard energy estimates} for $H^1$ and $H({\rm div})$-conforming finite elements.
-A more detailed discussion on the reasoning behind the construction of test norms can be found in \cite{DPGrobustness}.
-
-The second step will be to show the equivalence of the energy norm to explicit norms on $U$.
-Since we do not generally have a closed form expression for the DPG energy norm, we seek to understand the behavior of DPG by finding a norm on $U$ to which the DPG energy norm is equivalent.
-Since $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U$ is a group variable from a tensor product space, we construct norms on $U$ through the combination of norms on $u$, $\sigma$, $\widehat{u}$, and $\widehat{f}_n$.
-Specifically, we use the norm on $U$
-\begin{equation}
-\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U}^2 \coloneqq \|u\|^2 + \|\sigma\|^2 + \left\|\widehat{u}\right\|^2 + \left\|\widehat{f}_n\right\|^2.
-\end{equation}
-For equivalence between norms, two constants are specified.
-However, since this norm on $U$ is a norm on four separate variables, we can specify not just two but eight equivalence constants.\footnote{Sharper estimates are attainable if these constants are allowed to vary over the mesh $\Oh$.
-See Section~\ref{sec:main_bounds} for a discussion.} In order to simplify analysis, we phrase this equivalence statement in an alternative form.
-
-Let $\nor{\cdot}_E \coloneqq \nor{\cdot}_{U,V}$, the energy norm induced by the test norm described above. We seek the bound of $\nor{\cdot}_E$ from above and below:
-\[
-\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2},
-\]
-where both $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ are defined as scaled combinations of the norms on $u, \sigma, \widehat{u}$, and $\widehat{f}_n$
-\begin{equation}
-\eqnlab{uNorms}
-\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,i}^2 \coloneqq \left(C_u^i\|u\|\right)^2 + \left(C_\sigma^i\|\sigma\|\right)^2 + \left(C_{\widehat{u}}^i\|\widehat{u}\|\right)^2 + \left(C_{\widehat{f}_n}^i\|\widehat{f}_n\|\right)^2,\quad i = 1,2
-\end{equation}
-Our goal is to explicitly derive the equivalence constants 
-%$C^1_u,\ldots, C^1_{\widehat{f}_n}$ and $C^2_u,\ldots, C^2_{\widehat{f}_n}$ 
-that define the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ respectively, taking into account any dependency on $\epsilon$.
-To do so, we need a relation between trial norms on $U$ and test norms on $V$.
-
-Recall from Section~\secref{energyPair} that every test norm induces a corresponding trial norm, and vice versa.
-Let $\|\cdot\|_{U,1} \simeq \|\cdot\|_{U,2}$ mean that the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ are equivalent, with equivalence constants independent of $\epsilon$.
-By equivalence of finite dimensional norms and the discussion in Section~\secref{energyPair} on the duality between test norms/energy norms, the norms \eqnref{uNorms} on $U$ induce the equivalent test norms on $\left(v,\tau\right) \in H^1(\Oh)\times H({\rm div},\Oh)$
-\begin{align*}
-\left\|\left(v,\tau\right)\right\|_{V,{U,i}} &\simeq \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(v,\tau\right)\right)}{C_u^i\|u\| + C_\sigma^i\|\sigma\| + C_{\widehat{u}}^i\|\widehat{u}\|+ C_{\widehat{f}_n}^i\|\widehat{f}_n\|}\\
-&= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \jump{\tau_n}, \widehat{u} \rangle_{\Gamma_-\cup \Gh^0} + \langle \widehat{f}_n, \jump{v} \rangle_{\Gamma_+ \cup \Gh^0}}{C_u^i\|u\| + C_\sigma^i\|\sigma\| + C_{\widehat{u}}^i\|\widehat{u}\|+ C_{\widehat{f}_n}^i\|\widehat{f}_n\|}\\
-& \simeq \frac{1}{C_u^i}\|g\| + \frac{1}{C_\sigma^i}\|f\| + \frac{1}{C_{\widehat{u}}^i}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle \jump{\tau\cdot n}, \widehat{u}\rangle}{\|\widehat{u}\|} +\frac{1}{C_{\widehat{f}_n}^i}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, \jump{v}\rangle}{\|\widehat{f}_n\|},
-\end{align*}
-where $f$ and $g$ are defined element-wise over $\Oh$ as 
-\begin{align*}
-g &\coloneqq \div \tau - \beta \cdot \grad v\\
-f &\coloneqq \epsilon^{-1}\tau + \grad v.
-\end{align*}
-By definition of the norms on the quantities defined on the skeleton $\Gh$, this gives the characterization of the induced test norm 
-\[
-\|\left(v,\tau\right)\|_{V,{U,i}} \simeq \frac{1}{C_u^i}\|g\| + \frac{1}{C_\sigma^i}\|f\| + \frac{1}{C_{\widehat{u}}^i}\|\jump{\tau\cdot n}\| + \frac{1}{C_{\widehat{f}_n}^i}\|\jump{v}\|, \quad i = 1,2.
-\]
-We can now use this relation to compare different norms on $U$ by comparing their induced norms on $V$ (recall that showing a robust inequality between two norms on $U$ is equivalent to showing the robust \textit{reverse} inequality in the induced norms on $V$).
-Namely, we can show the bound of $\nor{\cdot}_{U,1} \lesssim \nor{\cdot}_E$ by showing the bound $\nor{\left(v,\tau\right)}_{V,U,1} \gtrsim \nor{\left(v,\tau\right)}_{V}$, and likewise for $\nor{\cdot}_E \lesssim \nor{\cdot}_{U,2}$.
-
-Since the techniques used to show such bounds are more involved, we break the procedure up into two steps:
-\begin{enumerate}
-\item{}Decompose test functions $(v,\tau)$ into three separate, more easily analyzable components (Section~\ref{sec:strategy2}).
-\item{}Derive adjoint estimates (Section~\ref{sec:strategy3}).
-\end{enumerate}
-
-\subsection{Decomposition into analyzable components}
-\label{sec:strategy2}
-
-Having reduced the problem of comparing norms on $U$ to the comparison of norms on $V$, we break the analysis of $\left(v,\tau\right) \in V$ into the analysis of three subproblems.
-Define the decomposition
-\[
-\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right),
-\]
-where $\left(v_1,\tau_1\right)$ satisfies 
-\begin{align*}
-\epsilon^{-1}\tau_1 + \grad v_1 &= 0 ,\\
-\div \tau_1 - \beta\cdot \grad v_1 &=  \div \tau - \beta\cdot \grad v = g, 
-\end{align*} 
-and $\left(v_2,\tau_2\right)$ satisfies
-\begin{align*}
-\epsilon^{-1}\tau_2 + \grad v_2 &= \epsilon^{-1}\tau + \grad v = f, \\
-\div \tau_2 - \beta\cdot \grad v_2 &= 0.
-\end{align*}
-Both $(v_1,\tau_1), (v_2,\tau_2) \in H({\rm div}; \Omega)\times H^1(\Omega)$ are understood to satisfy these relations in a conforming sense over the domain $\Omega$; however, the divergence of $\tau$ and gradient of $v$ on the right hand side are still understood to be taken in an element-wise fashion.
-
-We will additionally require both $\left(v_1,\tau_1\right), \left(v_2,\tau_2\right)$ to satisfy the adjoint homogeneous boundary conditions
-\begin{align}
-\tau_i\cdot n &= 0, \quad \text{on }\Gamma_- \label{bc_1}\\
-v_i &= 0, \quad \text{on } \Gamma_+ \label{bc_2}
-\end{align}
-for $i = 1, 2$.
-The selection of $H({\rm div}, \Omega)\times H^1(\Omega)$ conforming test functions satisfying the specific boundary conditions above removes the contribution of the jump terms over the skeleton $\Gh$ in the bilinear form, allowing us to analyze field terms in the induced test norms separately from  the boundary/jump terms.
-
-Finally, by construction, $\left(v_0,\tau_0\right) \in H^1(\Oh) \times H({\rm div},\Oh)$ must satisfy 
-\begin{align*}
-\epsilon^{-1}\tau_0 + \grad v_0 &= 0\\
-\div \tau_0 - \beta\cdot \grad v_0 &= 0
-\end{align*}
-with jumps
-\begin{align*}
-\jump{v_0} &= \jump{v}, \quad \text{on }\Gh^0\\
-\jump{\tau_0 \cdot n} &= \jump{\tau \cdot n}, \quad \text{on }\Gh^0.
-\end{align*}
-and boundary conditions
-\begin{align*}
-v_0 &= v, \quad \text{on } \Gamma_+ \\
-\tau_0 \cdot n &= \tau \cdot n, \quad \text{on } \Gamma_-\cup \Gamma_0. 
-\end{align*}
-Notice that the evaluation the bilinear form $b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(v,\tau\right)\right)$ with each specific test functions returns only one part of the bilinear form.
-Furthermore, by choosing the proper loads $g = u$ and $f=\sigma$, we can recover from the bilinear form the norms of $u$ and $\sigma$ (as described in Section~\secref{sec:testNormSec}), as well as the norms on $\widehat{u}$, and $\widehat{f}_n$.\footnote{To recover the norms on $\widehat{u}$, and $\widehat{f}_n$, the loads $f$, and $g$ must be zero, and the jumps of the test function $(v,\tau)$ must be chosen specifically.}
-
-We have now decomposed an arbitrary test function $\left(\tau,v\right)$ into a discontinuous contribution and two continuous contributions.
-Recall that our goal is to show the robust bound from above and below of the DPG energy norm by $\|\cdot \|_{U,1}$ and $\|\cdot \|_{U,2}$:
-\[
-\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}.
-\]
-
-Under the duality of trial and test norms and the decomposition of test functions $\left(\tau,v\right) \in V$ into $\left(\tau_0,v_0\right), \left(\tau_1,v_1\right)$, and $\left(\tau_2,v_2\right)$, the above bound is equivalent to bounding each component
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,U,1} &\gtrsim \sum_{i=0}^2\|\left(v_{i},\tau_{i}\right)\|_V \gtrsim \|\left(v,\tau\right)\|_{V,U,2}.
-%\|\left(v,\tau\right)\|_{V,1} &\lesssim \|\left(v_{1},\tau_{1}\right)\|_V \lesssim \|\left(v,\tau\right)\|_{V,2}\\
-%\|\left(v,\tau\right)\|_{V,1} &\lesssim \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|\left(v,\tau\right)\|_{V,2}
-\end{align*}
-Bounding $\|\left(v_0,\tau_0\right)\|$ requires the use of techniques first developed in \cite{analysisDPG} and adapted to convection-diffusion in \cite{analysisDPG} and \cite{DPGrobustness}.
-However, since $\left(\tau,v\right) \in H({\rm div}, \Omega)\times H^1(\Omega)$, the bound from above of test functions $\|\left(v_{1},\tau_{1}\right)\|_V$ and $\|\left(v_{2},\tau_{2}\right)\|_V$ is reduced to proving classical error estimates for the adjoint equations
-\begin{align*}
-\epsilon^{-1}\tau_1 + \grad {v_1} &= 0 \\
-\div {\tau_1} - \beta\cdot \grad {v_1} &=  g, \\
-\left.\tau_1\cdot n\right|_{\Gamma_-} &= 0, \\
-\left.v_1\right|_{\Gamma_+} &= 0.
-\end{align*} 
-and 
-\begin{align*}
-\epsilon^{-1}\tau_2 + \grad {v_2} &= f \\
-\div {\tau_2} - \beta\cdot \grad {v_2} &= 0, \\
-\left.\tau_2\cdot n\right|_{\Gamma_-} &= 0, \\
-\left.v_2\right|_{\Gamma_+} &= 0.
-\end{align*} 
-More generally, we can analyze the adjoint equations
-\begin{align}
-\epsilon^{-1}\tau + \grad {v} &= f \label{adjoint1}\\
-\div {\tau} - \beta\cdot \grad {v} &= g, \label{adjoint2}
-\end{align}
-for arbitrary data $f, g\in L^2({\Omega})$ and boundary conditions $\jump{\tau\cdot n}_{\Gamma_-} = 0$ and $\jump{v}_{\Gamma_+} = 0$.
-In other words, we want to analyze the stability properties of the adjoint equations by deriving bounds of the form $\|\left(v_1,\tau_1\right)\|_V\lesssim \|g\|_{L^2}$ and $\|\left(v_2,\tau_2\right)\|_V \lesssim \|f\|_{L^2}$.
-
-%An alternate interpretation of the above decomposition is that each component $(v_i,\tau_i)$ of the decomposition corresponds to a term in the bilinear form.
-For example, .
-If we evaluating our bilinear form with $(v,\tau) = (v_1,\tau_1)$ delivers
-%\[
-%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-%\left( v_1, \tau_1 \right)\right) = (u,g)_{L^2} 
-%\]
-%By choosing $g = u$,
-
-\subsection{Adjoint estimates}
-\label{sec:strategy3}
-
-The final step to estimating the induced norm on $U$ by a selected localizable test norm on $V$ is to derive adjoint stability estimates on $\tau$ and $v$ in terms of localizable normed quantities.
-We will construct complete test norms on $V$ through combinations of these normed quantities.%, where each normed quantity on $\tau$ or $v$ will correspond roughly to $\|u\|_{L^2}$, $\|\sigma\|_{L^2}$, $\|\widehat{u}\|$, or $\|\widehat{f}_n\|$.
-
-We introduce first the bounds derived; the proofs will be given later.
-For this analysis, it will be necessary to assume certain technical conditions on $\beta$.
-For each proof, we require $\beta \in C^2(\bar{\Omega})$ and $\beta, \div \beta = O(1)$.
-Additionally, we will assume that some or all of the following assumptions hold
-\footnote{These assumptions correspond to convection fields which are divergence-free \eqref{c_req}, curl-free \eqref{a_req}, bounded away from zero \eqref{a_req}, and of bounded variation \eqref{b_req}.
-However, these are merely sufficient conditions; numerical experiments indicate that they may not be strictly necessary.}
-:
-\begin{align}
-&\curl \beta = 0, \quad 0<C \leq \left | \beta\right |^2 + \frac{1}{2}\div \beta, \quad C = O(1) \label{a_req},\\
-&\grad \beta + \grad \beta ^T - \div \beta I = O(1) \label{b_req},\\
-&\div \beta = 0 \label{c_req}.
-\end{align}
-
-Under these assumptions on $\beta$, we have the following robust bounds, which are proved in the Appendix. 
-\begin{itemize}
-\item \textbf{Lemma \ref{lemma_stream}}: \textit{For $\beta$ satisfying \eqref{a_req} and \eqref{b_req}, %$f=0$ 
-and $v_1 \in H^1(\Omega)$, satisfying equations \eqref{adjoint1} and \eqref{adjoint2} with $f=0$, and with boundary conditions \eqref{bc_1} and \eqref{bc_2}},
-\begin{align*}
-\|\beta \cdot \grad v_1 \| &\lesssim \| g\|.
-\end{align*}
-Similarly, from $\div \tau_1 - \beta\cdot \grad v_1 = g$, we get $\|\div \tau_1\| \lesssim \|g\|$ as well.  
-\item \textbf{Lemma \ref{lemma_grad}}: \textit{For $\beta$ satisfying \eqref{a_req}, and $v \in H^1(\Omega)$ satisfying equations \eqref{adjoint1} and \eqref{adjoint2} and boundary conditions \eqref{bc_1} and \eqref{bc_2}, and for sufficiently small $\epsilon$},
-\[
-\epsilon \|\grad v\|^2 + \|v\|^2 \lesssim \|g\|^2 + \epsilon \|f\|^2.
-\]
-We can characterize both $v_1$ and $v_2$ in the above decompositions using this theorem by setting either $f=0$ or $g=0$. 
-%\begin{align*}
-%\epsilon \|\grad v_1\|^2 + \|v_1\|^2 &\lesssim \|g\|^2\\
-%\epsilon \|\grad v_2\|^2 + \|v_2\|^2 &\lesssim \epsilon \| f\|^2.
-%\end{align*}
-%By the triangle inequality, this implies for any $w$ of the form $w=v_1+v_2$
-%\begin{align*}
-%\epsilon \|\grad w\|^2 + \|w\|^2 &\lesssim \|g\|^2 + \epsilon \| f\|^2
-%\end{align*}
-\item \textbf{Lemma \ref{lemma_boundary}}: \textit{For $\beta$ satisfying \eqref{a_req}, \eqref{c_req}, and solutions $v_0 \in H^1(\Oh)$ and $\tau_0 \in H({\rm div},\Oh)$ of equations \eqref{adjoint1} and \eqref{adjoint2} with $f=g=0$,}
-\begin{align*}
-\|\grad v_0\| = \frac{1}{\epsilon}\|\tau_0\| &\lesssim \frac{1}{\epsilon} \| \jump{\tau_0\cdot n}\|_{\Gh \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| \jump{v_0}\|_{\Gh^0 \cup \Gamma_+}.
-\end{align*}
-\end{itemize}
-We are interested in showing the equivalence of the DPG energy norm with norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$, respectively.
-We will show this by bounding $\|\cdot \|_V$ from below by $\|\cdot\|_{V,U,1}$ and from above by $\|\cdot\|_{V,U,2}$ (the induced test norms for $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$, respectively).
-
-%We will use Lemmas \ref{lemma_stream}, \ref{lemma_grad}, and \ref{lemma_boundary} to prove such bounds on our yet-unspecified test norm $\|(\tau,v)\|_V$.
-
-%Together, these estimates will be sufficient to construct a complete norm on $V$ and demonstrate bounds on induced test norms for different scalings of norms on $U$.  
-%\tanbui{}{again, using the same notation
-%  $(v, \tau)$ for all three problems is not a good idea. Why don't we
-%  use $(v_i,\tau_i)$ introduced above? Things are much clearer this
-%  way?}
-\subsection{A mesh-dependent test norm}
-\seclab{sec:meshDep}
-Ideally, we would be interested in the use of the test norm 
-\[
-\|\left(v,\tau\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2
-\]
-for practical computations.
-However, the presence of the term $\|v\|$ together with $\sqrt{\epsilon}\|\grad v\|$ (and similarly $\|\div \tau\|$ and $\frac{1}{\sqrt{\epsilon}}\|\tau\|$ terms) induces boundary layers in the optimal test functions for under-resolved meshes.
-We can see this by recovering the strong form of the variational problem defining test functions.
-We first note that the variational problems for the $v$ and $\tau$ components of optimal test functions decouple from each other under this test norm.
-Then, examining the variational problem for the $v$ component only of an optimal test function, and assuming $\div \beta = 0$ for illustrative purposes, we have
-\begin{align*}
-\left(\left(v,0\right),\left(\delta v,\delta\tau\right)\right)_{V} &= (v,\delta v) + \epsilon \left(\grad v,\grad \delta v\right) + \left(\beta \cdot \grad v, \beta \cdot \grad \delta v\right)\\
-&= \left(v - \epsilon \Delta v - \div \left(\left(\beta \otimes \beta\right) \grad v\right), \delta v\right)_{L^2} + \langle \epsilon \grad v\cdot n, \delta v\rangle + \langle n\cdot \left(\beta\otimes\beta\right) \grad v , \delta v\rangle.
-\end{align*}
-After integration by parts, we recover the strong form of the operator $L$ inducing such a variational problem 
-\[
-Lv \coloneqq v - \epsilon \Delta v - \div \left(\left(\beta \otimes \beta\right) \grad v\right),
-\]
-where we neglect the resulting boundary terms from integration by parts for now.
-
-The streamline direction $\beta$ induces an anisotropic diffusion, while the $\sqrt{\epsilon}\|\grad v\|_{L^2}$ term induces a small isotropic diffusion contribution everywhere.
-Since any vector in the cross-stream direction is in the null space of the anisotropic diffusion tensor, in the cross-stream directions, the optimal test function is governed only by the cross-stream part of the operator $L$
-\[
-L_{\rm \beta^\perp} \coloneqq v - \epsilon \Delta v,
-\]
-and can develop boundary layers in those directions.
-The presence of boundary layers has been verified through numerical computation as well; using an $H^1$-conforming finite element code with $hp$-adaptivity \cite{demkowicz2006computing}, the solution to the variational problem defining the optimal test function under the above test norm was computed.
-Figure~\ref{fig:boundaryTest} shows the result of such a computation for the $v$ component of an optimal test function under the above test norm.
-\begin{figure}[!h]
-\centering
-\subfigure{\includegraphics[scale=.22]{mesh1.png}}
-\subfigure{\includegraphics[scale=.22]{sol1.png}}
-\caption{The $v$ component of the optimal test function corresponding to flux $\widehat{u} = x(1-x)$ on the bottom side of a unit element for $\epsilon = 0.01$.
-The corresponding $hp$-mesh used to compute the solution is displayed to the left.}
-\label{fig:boundaryTest}
-\end{figure}
-To avoid boundary layers in the optimal test functions, we follow \cite{DPGrobustness} in scaling the $L^2$ contributions of $v$ by $C_v(K)$, such that, when transformed to the reference element, both $C_v(K)\|v\|^2$ and $\epsilon\|\grad v\|^2$ are of the same magnitude.
-Similarly, we scale the $L^2$ contributions of $\tau$ by $C_\tau(K)$ such that $\frac{C_\tau(K)}{\epsilon} \|\tau\|^2$ and $\|\div \tau\|^2$ are of the same magnitude as well.
-For this paper, we consider only isotropic refinements on quadrilateral elements in 2D.
-
-We can now define $\nor{\LRp{v,\tau}}_{V(K)}$, our test norm over a single element $K$, as 
-\[
-\|\left(v,\tau\right)\|_{V(K)}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
-\]
-This modified test norm avoids boundary layers in the locally computed optimal test functions, but for adaptive meshes, provides additional stability in areas of heavy refinement, where the best approximation error tends to be large and stronger robustness is most necessary.
-This leads to a test norm which produces easily approximable optimal test functions, but still provides \textit{asymptotically} the strongest test norm and tightest robustness results in the areas of highest error.
-
-\subsection{Equivalence of energy norm with $\nor{\cdot}_U$}
-%\subsection{Relations between trial and test constants}
-\label{sec:main_bounds}
-
-The main theoretical result of this paper can now be given:
-\begin{lemma}
-Under the mesh-dependent test norm
-\[
-\|\left(v,\tau\right)\|_{V(\Oh)}^2 = \|C_vv\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \|C_\tau\tau\|^2,
-\]
-where $C_v, C_{\tau}\in L^2(\Omega)$ are defined elementwise through
-\begin{align*}
-\left.C_v\right |_K &= \min\left\{\sqrt{\frac{\epsilon}{|K|}},1\right\}\\
-\left.C_{\tau}\right |_K &= \min\left\{\frac{1}{\sqrt{\epsilon}},\frac{1}{\sqrt{|K|}}\right\}.
-\end{align*}
-If $\beta$ satisfies \eqref{a_req}, \eqref{b_req}, and \eqref{c_req}, the DPG energy norm $\nor{\cdot}_E$ satisfies the following equivalence relations
-\begin{align*}
-\nor{u}_{L^2} + \nor{\sigma}_{L^2} + \epsilon\nor{\widehat{u}} + \sqrt{\epsilon}\nor{\widehat{f}_n} 
-&\lesssim \nor{\left(u,\sigma, \widehat{u},\widehat{f}_n\right)}_E \\ 
-%\nor{\left(u,\sigma, \widehat{u},\widehat{f}_n\right)}_E &\lesssim \nor{u}_{L^2} + \nor{C_\sigma \sigma}_{L^2} + \frac{1}{\sqrt{\epsilon}} \left(\nor{\widehat{u}} + \nor{\widehat{f}_n}\right),
-\nor{\left(u,\sigma, \widehat{u},\widehat{f}_n\right)}_E &\lesssim \nor{u}_{L^2} + \nor{\frac{1}{\epsilon C_\tau} \sigma}_{L^2} + \frac{1}{\sqrt{\epsilon}} \left(\nor{\widehat{u}} + \nor{\widehat{f}_n}\right).
-\end{align*}
-%where $C_\sigma \in L^2(\Omega)$ is defined elementwise through $\left.C_\sigma\right|_K  = \max\left\{ \frac{1}{\sqrt{\epsilon}} , \frac{\sqrt{|K|}}{\epsilon} \right\}$.
-\end{lemma}
-
-\begin{proof}
-We begin by proving the bound from below.
-As a consequence of the duality of norms discussed in Section~\secref{energyPair}, we know that the norm $\left\| u \right\|_{U,1}$ is induced by a specific test norm $\| v  \|_{V,U,1}$.
-To bound $\|\cdot\|_E$ robustly from above or below by a given norm $\left\| u \right\|_{U,2}$ on $U$ now only requires the robust bound in the opposite direction of $\| v \|_{V,U,1}$ by $\|v\|_{V,U,2}$.
-
-For $f$ and $g$ defined in \eqref{adjoint1} and \eqref{adjoint2},
-\begin{align*}
-f &= \epsilon^{-1}\tau + \grad v  \\
-g &=\div \tau - \beta\cdot \grad v,
-\end{align*} 
-we can characterize the test norm for 
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,1}^2 = \|u\|^2 + \|\sigma\|^2 + \epsilon\|\widehat{u}\|^2+ \sqrt{\epsilon}\|\widehat{u}\|^2
-\]
-through the equivalence relation
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,U,1} &\simeq \sup_{u,\sigma,\widehat{u},\widehat{f}_n}\frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\|u\| + \|\sigma\| + \epsilon\|\widehat{u}\|+ \sqrt{\epsilon}\|\widehat{u}\|}\\
-& \simeq \|g\| + \|f\| + \frac{1}{\epsilon}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle \jump{\tau\cdot n}, \widehat{u}\rangle}{\|\widehat{u}\|} + \frac{1}{\sqrt{\epsilon}}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, \jump{v}\rangle}{\|\widehat{f}\|},
-\end{align*}
-which, by definition of the boundary norms, is 
-\[
-\|\left(v,\tau\right)\|_{V,U,1} \simeq \|g\| + \|f\| + \frac{1}{\epsilon}\|\jump{\tau\cdot n}\| + \frac{1}{\sqrt{\epsilon}}\|\jump{v}\|.
-\]
-We wish to show the bound
-\[
-\nor{\left(v,\tau\right)}_{V(\Oh)} \lesssim \|g\| + \|f\| + \frac{1}{\epsilon}\|\jump{\tau\cdot n}\| + \frac{1}{\sqrt{\epsilon}}\|\jump{v}\|.
-\]
-By noting that both 
-\begin{align*}
-\nor{C_vv_0} &\leq \nor{v_0},\\
-\nor{C_\tau\tau_0} &\leq \frac{1}{\sqrt{\epsilon}}\nor{\tau_0},
-\end{align*}
-we have that $\nor{\left(v,\tau\right)}_{V(\Oh)} \leq \nor{\left(v,\tau\right)}_{V}$, so it suffices to prove the bound for the mesh-independent test norm 
-\[
-\|\left(v,\tau\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2.
-\]
-
-We will bound $\|\left(v,\tau\right)\|_V$ for all $\left(v,\tau\right)$ by decomposing $\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right)$ as described in Section~\ref{sec:strategy2}.
-
-By the triangle inequality, robustly bounding $\|\left(v,\tau\right)\|_V$ from above reduces to robustly bounding each component 
-\[
-\|\left(v_{0},\tau_{0}\right)\|_V, \|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|g\| + \|f\| + \frac{1}{\epsilon}\|\jump{\tau\cdot n}\| + \frac{1}{\sqrt{\epsilon}}\|\jump{v}\|.
-\]
-
-%Roughly speaking, Lemma \ref{lemma_grad} concerns the robust control of $u$ by the energy error; Lemmas \ref{lemma_stream} and \ref{lemma_boundary} concern the robust control of field variable $\sigma$ and flux/trace variables, respectively.
-
-\begin{itemize}
-\item \textbf{Bound on $\|\left(v_{0},\tau_{0}\right)\|_V$}
-
-Lemma \ref{lemma_boundary} gives control over $\sqrt{\epsilon}\|\grad v_0\| + \frac{1}{\epsilon}\|\tau_0\|$ through
-\[
-\|\grad v_0\| = \frac{1}{\epsilon}\|\tau_0\| \lesssim \frac{1}{\epsilon} \nor{\jump{\tau_0\cdot n}}_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \nor{\jump{v_0}}_{\Gamma_h^0 \cup \Gamma_+} = \frac{1}{\epsilon} \nor{ \jump{\tau\cdot n}}_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \nor{ \jump{v}}_{\Gamma_h^0 \cup \Gamma_+}.
-\]
-Lemma 4.2 of \cite{analysisDPG} gives us the Poincare inequality for discontinuous functions
-\[
-\|v_0\| \lesssim \|\grad v_0\| + \|\jump{v}\|.
-\]
-%Since $f=0$, by Lemma 2, $\|\beta\cdot \grad v_0\|  \lesssim \|g\| = 0$.  
-Since $g = 0$, $\| \div \tau_0\| = \|\beta\cdot \grad v_0\|\lesssim \|\grad v_0\|$, which we now have control over as well.
-
-\item \textbf{Bound on $\|\left(v_{1},\tau_{1}\right)\|_V$}
-
-With $f = 0$, Lemma \ref{lemma_stream} provides the bound
-\[
-\|\beta \cdot \grad v_1 \| \lesssim \| g\|.
-\]
-Noting that $\div \tau_1 = g+\beta\cdot \grad v_1$ gives $\|\div \tau_1 \| \lesssim \|g\|$ as well.  Lemma \ref{lemma_grad} gives
-\[
-\epsilon \|\grad v_1\|^2 + \|v_1\|^2 \lesssim \|g\|^2,
-\]
-and noting that $\epsilon^{-1/2}\tau_1 = \epsilon^{1/2}\grad v_1$ gives $\epsilon\|\grad v_1\|^2 = \epsilon^{-1}\|\tau_1\|^2 \lesssim \|g\|^2$ as well.
-
-\item \textbf{Bound on $\|\left(v_{2},\tau_{2}\right)\|_V$}
-
-Lemma \ref{lemma_grad} provides, for $\epsilon$ sufficiently small, 
-\[
-\epsilon \|\grad v_2\|^2 + \|v_2\|^2 \lesssim  \epsilon \| f\|^2 \leq \|f\|^2.
-\]
-We have $\epsilon^{-1}\tau_2 = f - \grad v_2$, so $\epsilon^{-1} \|\tau_2\| \lesssim \|f\| + \|\grad v_2\|$.
-Lemma~\ref{lemma_grad} implies $\|\grad v_2\|^2  \lesssim  \| f\|^2$, so for $\epsilon \leq 1$, we have $\epsilon^{-1/2}\|\tau_2\| \leq \epsilon^{-1}\|\tau_2\| \lesssim \|f\|$.
-The remaining terms can be bounded by noting that, with $g = 0$, $\|\div \tau_2\| = \|\beta\cdot \grad v_2\| \lesssim \|\grad v_2\| \lesssim \|f\| $.
-\end{itemize}
-
-We have shown the robust bound of the norm $\|\cdot \|_{U,1}$ on $U$ by the energy norm; for a full equivalence statement, we require a bound from above on the energy norm by the norm $\|\cdot \|_{U,2}$ on $U$.
-By the duality of the energy and test norm, this is equivalent to bounding the test norm from below by the test norm induced by $\|\cdot \|_{U,2}$.
-For a norm on $U$ of the form
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,2}^2 = \|u\|^2 + \nor{C_\sigma \sigma}^2 + \frac{1}{{\epsilon}}\left( \|\widehat{u}\|^2 + \|\widehat{f}_n\|^2\right),
-\]
-the induced test norm is equivalent to
-\begin{align*}
-\| \left(\tau,v\right) \|_{V,U,2} &\simeq \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E} \\
-&\simeq \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \jump{\tau_n}, \widehat{u} \rangle + \langle \widehat{f}_n, \jump{v} \rangle
-}{\|u\| + \nor{\left(\epsilon C_\tau\right)^{-1}\sigma} + \frac{1}{\sqrt{\epsilon}}\left(  \|\widehat{u}\| + \|\widehat{f}_n\| \right)} \\
-&\simeq \|g\| + \nor{\epsilon C_\tau f} + {\sqrt{\epsilon}}\left(\sup_{\widehat{u},\widehat{f}_n \neq 0}\frac{\langle \jump{\tau_n}, \widehat{u} \rangle + \langle \widehat{f}_n, \jump{v} \rangle}{\|\widehat{u}\| + \|\widehat{f}_n\|}\right),
-\end{align*}
-where $f$ and $g$ are 
-\begin{align*}
-f &= \frac{1}{\epsilon}\tau + \grad v\\
-g &= \div \tau - \beta \cdot \grad v,
-\end{align*}
-the loads of the adjoint problem defined in \eqref{adjoint1}, \eqref{adjoint2}.
-
-Note that $\epsilon C_\tau \leq \sqrt{\epsilon}$. Then, by the triangle inequality, we have the bounds
-\begin{align*}
-%\sqrt{\epsilon} \|f \| &\leq \epsilon^{-1/2} \| \tau\| + \sqrt{\epsilon} \|\grad v\| \lesssim \|\\
-\|\epsilon C_\tau f \| &\leq C_\tau \nor{ \tau} + \epsilon C_\tau \nor{\grad v} \lesssim \| \left(\tau,v\right)\|_{V(\Oh)}\\
-\|g \| &\leq \|\div \tau\| +  \|\beta \cdot \grad v\| \lesssim \| \left(\tau,v\right)\|_{V(\Oh)}
-\end{align*}
-We estimate the supremum on the jumps of $\left(\tau,v\right)$ by following \cite{DPGrobustness}; we begin by choosing $\eta \in H({\rm div}; \Omega)$, $w\in H^1(\Omega)$, such that $\left.\left(\eta-\beta w \right)\cdot n\right |_{\Gamma_+} = 0$ and $\left.w\right |_{\Gamma_-\cup\Gamma_0} = 0$, and integrating the boundary pairing by parts to get
-\begin{align*}
-\langle \jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle &= (\tau,\grad w) + (\div \tau, w) + \left(\eta - \beta w, \grad v\right) +  \left(\div \left(\eta - \beta w\right), v\right)\\
-&\lesssim \|C_\tau\tau\| \nor{ \frac{1}{C_\tau}\grad w} + \|\div \tau\| \|w\| \\
-&\left.\hspace{.3cm}\right. + \sqrt{\epsilon}\| \grad v \|\frac{1}{\sqrt{\epsilon}}\|\eta\| +  \|\beta \cdot \grad v\| \| w\|\\
-&\left.\hspace{.3cm}\right. + \|C_vv\|\nor{\frac{1}{C_v}\div \eta} + \| C_vv\| \nor{\frac{1}{C_v}w} \\
-&\left.\hspace{.3cm}\right. + \|C_v v\| \nor{\frac{1}{C_v} \grad w},
-\end{align*}
-where we have used that $\epsilon < 1$, $\div \beta = O(1)$, and that $\|\beta\cdot \grad w\|\lesssim \|\grad w\|$.
-
-Without loss of generality, assume the problem is scaled such that $\max_{K\in\Oh}|K| \leq 1$.
-Then, $\frac{1}{C_\tau^2}\leq \frac{1}{C_v^2} \leq \frac{1}{\epsilon}$, and an application of discrete Cauchy-Schwarz gives us
-\begin{align*}
-\langle \jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle &\lesssim \|\left(\tau,v\right)\|_{V(\Oh)}\frac{1}{\sqrt{\epsilon}}\left(\nor{\eta}_{H({\rm div},\Omega)} + \nor{w}_{H^1(\Omega)}\right),\\
-&\lesssim \|\left(\tau,v\right)\|_{V(\Oh)}\frac{1}{\sqrt{\epsilon}}\left(\nor{\eta-\beta w}_{H({\rm div},\Omega)} + \nor{w}_{H^1(\Omega)}\right),
-\end{align*}
-since $\|\eta\|_{H({\rm div},\Omega)} = \|\eta - \beta w + \beta w\|_{H({\rm div},\Omega)} \leq \|\eta - \beta w\|_{H({\rm div},\Omega)} + \|\beta w\|_{H({\rm div},\Omega)} \lesssim \|\eta-\beta w\|_{H({\rm div},\Omega)} + \|w\|_{H^1(\Omega)}$.
-Dividing through and taking the supremum gives
-\[
-\sup_{w,\eta \neq 0} \frac{\langle\jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle}{\left(\nor{\eta-\beta w}_{H({\rm div},\Omega)} + \nor{w}_{H^1(\Omega)}\right)} \lesssim \|\left(\tau,v\right)\|_{V(\Oh)}\frac{1}{\sqrt{\epsilon}}.
-\]
-To finish the proof, define $\rho \in H^{1/2}(\Gamma_h)$ and $\phi \in H^{-1/2}(\Gamma_h)$ such that $\rho = \left.w\right|_{\Gamma_h}$ and $\phi = \left.(\eta-\beta w)\cdot n\right|_{\Gamma_h}$, and note that, from \cite{analysisDPG}, by the definition of the trace norms on $\jump{\tau\cdot n}$ and $\jump{v}$
-\begin{align*}
-\sup_{\rho,\phi \neq 0} \frac{\langle \jump{\tau\cdot n},\rho\rangle + \langle \jump{v},\phi \rangle}{\|\rho\|_{H^{1/2}(\Gamma_h)}+\|\phi\|_{H^{-1/2}(\Gamma_h)}} &= \sup_{w,\eta \neq 0} \frac{\langle \jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle}{ \|w\|_{H^1(\Omega)}+\|\eta-\beta w\|_{H({\rm div},\Omega)}}.
-\end{align*}
-Together, the bounds on the jump terms and the bounds on $\|g\|$ and $\|f\|$ imply $\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{E} \lesssim \left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,2}$.
-\end{proof}
-
-\subsection{Comparison of boundary conditions}
-
-It is worth addressing the effect of boundary conditions on stability.
-Specifically, a test norm that provides stability for one set of boundary conditions may perform poorly for another set.
-Take, for example, the test norm defined in Section~\ref{sec:main_bounds} and the convection-diffusion problem with Dirichlet boundary conditions.
-
-The bilinear form for the case of Dirichlet boundary conditions is 
-\[
-b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(v,\tau\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) + \langle \widehat{u}, \jump{\tau \cdot n} \rangle_{\Gh^0} + \langle \widehat{f}_n, \jump{v} \rangle_{\Gh}.
-\]
-Notice that the boundary terms in the final bilinear form are different; hence, the adjoint problems associated with Section~\ref{sec:strategy3} will now carry different boundary conditions as well.
-Likewise, the stability properties proven previously will not hold under a different set of boundary conditions.
-%We note that 
-%\begin{align*}
-%b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gh^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gh}
-%&= \| u \|^2_{L^2}
-%\end{align*}
-%for the specific continuous test functions $\tau$ and $v$ satisfying
-%\begin{align*}
-%\div \tau - \beta \cdot \grad v &= u \\
-%\frac{1}{\epsilon}\tau + \grad v &= 0
-%\end{align*}
-%with boundary condition $\left.v\right|_\Gamma = 0$.
-Choosing a continuous conforming test function $v$ removes the contribution of the term $\langle \widehat{f}_n, \left[v\right] \rangle$ on the mesh skeleton, while the boundary conditions remove the contribution of boundary terms from the bilinear form.
-Then, for this specific choice of $\left(\tau, v\right)$,
-%\begin{align*}
-%\|u\|_{L^2}^2 &= b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right)}{\|\left(\tau, v\right)\|_V}\|\left(\tau, v\right)\|_V \leq \|u\|_E \|\left(\tau, v\right)\|_V
-%\end{align*}
-%At minimum, we want $\|u\|_{L^2} \lesssim \|u\|_E$, which requires 
-%\[
-%\|\left(\tau, v\right)\|_V \lesssim \| u \|_{L^2}
-%\]
-%for any choice of $u \in L^2$ (dividing through by $\|u\|_{L^2}$ gives the desired result).
-This can be considered a ``sanity check"; at the minimum, we at least want control over the behavior of the single field variable $u$.
-However, we are unable to prove this in the case of Dirichlet boundary conditions.
-
-As it turns out, the robust bounds given in Section~\ref{sec:main_bounds} hold in $\mathbb{R}^d$ for arbitrary $d$; however, we can show that for Dirichlet boundary conditions, the same results do not hold even in 1D.
-%In 1D, the problem reduces to 
-%\begin{align*}
-%\frac{1}{\epsilon}\sigma - u' &= 0\\
-%\left(u - \epsilon \sigma \right)' &=f
-%\end{align*}
-%with bilinear form
-%\begin{align*}
-%b\left(\left(u,\sigma,\widehat{u},\widehat{f}\right),\left(\tau,v\right)\right) &= \sum_{k=1}^N \left(\left.\widehat{u}(x) \tau(x)\right |^{x_k}_{x_{k-1}} + \left.\widehat{f}(x) v(x)\right |^{x_k}_{x_{k-1}}\right) \\
-%&+ \left(\sigma,\epsilon^{-1}\tau\right)_{\Oh} + (u,\tau')_{\Oh}- \left(u - \epsilon \sigma,v'\right)_{\Oh}
-%\end{align*}
-%where $\widehat{u}(x), \widehat{f}(x) \in \mathbb{R}$ are now point values defined on mesh points $x_k$ for $k=1,\ldots,N$, where $N$ is the number of elements.
-We can assume without loss of generality that $\Oh$ is the unit interval $(0,1)$.
-%
-%Let us first provide an interpretation of Lemma~\ref{lemma_stream}. Recall the bilinear form 
-%\begin{align*}
-%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-%\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
-%v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh} - \LRa{
-%\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n,
-%  \jump{v} }_{\Gh},
-%\end{align*}
-%By choosing $(v,\tau)$ such that
-%\begin{align*}
-%\div \tau - \beta \cdot \grad v &= u \\
-%\frac{1}{\epsilon} \tau + \grad v &= 0
-%\end{align*}
-%we will have 
-%\[
-%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-%\left( v, \tau \right)\right) =\|u\|_{L^2}^2 
-%\]
-%Given this, we can use the definition of the energy norm \eqnref{energyNorm} to bound
-%\[
-%\|u\|_{L^2}^2 = b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-%\left( v, \tau \right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-%\left( v, \tau \right)\right)}{\|(v,\tau)\|_V}\|(v,\tau)\|_V \lesssim \|u\|_E \|(v,\tau)\|_V
-%\]
-%If we can show that $\|(v,\tau)\|_V \lesssim \|u\|_{L^2}$ for $(v,\tau)$ as defined above, then this implies 
-%\[
-%\|u\|_{L^2} \lesssim \|u\|_E
-%\]
-%By the fact that 
-Consider the 1D analogue of the estimate given by Lemma~\ref{lemma_stream}.  In 1D, $\|\beta\cdot\grad v_1\| \lesssim \|g\|$ reduces to the inequality 
-\[
-\|\beta v_1'\|\lesssim \|g\|, \quad g\in L^2\!\left(\Oh\right).
-\]
-Without this inequality, we are unable to prove the robust bound on the $L^2$ error $\|u-u_h\|_{L^2} \lesssim \nor{(u,\sigma,\widehat{u},\widehat{f}_n)-(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h})}_E$.
-
-The adjoint problem corresponding to Lemma~\ref{lemma_stream} in Section~\ref{sec:strategy3} is likewise reduced in 1D to the scalar equation
-\begin{align}
-\epsilon v_1'' + \beta v_1' &= -g \label{adjoint_1D}
-\end{align}
-with $v_1\in H^1_0\left((0,1)\right)$.  After multiplying this equation by $\beta v_1'$ and integrating by parts over $\Oh$, we can apply Young's inequality to get
-%\[
-%\int_0^1 \epsilon v_1'' \beta v_1' + \|\beta v_1'\|_{L^2}^2 = -\int_0^1 g \beta v_1'.\
-%]
-%Integrating by parts and Young's inequality gives
-\begin{align*}
-\left.\frac{\epsilon}{2} \beta v_1'^2\right|_0^1 + \|\beta v_1'\|_{L^2}^2 &\leq \frac{1}{2}\|g\|^2 + \frac{1}{2}\|\beta v_1'\|^2,
-\end{align*}
-implying that
-\begin{align*}
-\|\beta v_1'\|_{L^2}^2 & \lesssim \|g\|^2 + {\beta \epsilon} v_1'(0)^2.
-\end{align*}
-Let us restrict ourselves to the cases where $v_1$ is sufficiently smooth for $v'(0)$ to be well defined.
-Taking $g=1$ (corresponding to a piecewise constant approximation) we can solve \eqref{adjoint_1D} exactly.
-\begin{figure}
-\centering
-\includegraphics[scale=.5]{testBoundary1D.pdf}
-\caption{$v_1(x) = \frac{e^{-\frac{x}{\epsilon}}}{e^{\frac{1}{\epsilon}}-1}\left(e^{\frac{1}{\epsilon}}\left(e^{\frac{x}{\epsilon}}-1\right) + \left(e^{\frac{1}{\epsilon}}-1\right)e^{\frac{x}{\epsilon}}x\right)$, the solution to the adjoint equation for $f=0$ and constant $\beta$ and load $g$ for $\epsilon = .01$.}
-\label{fig:testBoundary1D}
-\end{figure}
-
-The solution $v_1$ is plotted in Figure~\ref{fig:testBoundary1D}, where we can see that $v_1(x)$ develops strong boundary layers of width $\epsilon$ near the inflow boundary $x=0$.
-Consequently, $\frac{\epsilon}{2} v_1'(0)^2 \approx \epsilon^{-1}$.
-Thus, we cannot conclude $\|\beta v'\| \lesssim \|g\|$ when $g$ is a constant,\footnote{Unlike the case of Dirichlet boundary conditions, the inflow condition on $ \widehat{f}_n = u(0)-\epsilon u'(0)$ induces an adjoint boundary condition $\tau(0)=0$, or equivalently $v'(0) = 0$, removing the non-robust term from the estimate.} and as a consequence cannot conclude that the robust error bound $\|u-u_h\|_{L^2} \lesssim \|(u,\sigma,\widehat{u},\widehat{f}_n)-(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h})\|_E$ holds for the solution $u_h$.
-More detailed 1D error bounds for Dirichlet boundary conditions are provided in \cite{DPG3}, and indicate the same lack of robustness under the test norm derived in this paper.\footnote{Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
-\[
-\|\left(\tau, v\right)\|_{V,w}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\|_{w+\epsilon} + \| \div \tau\|_{w+\epsilon} + \frac{1}{\epsilon}\|\tau\|_{w+\epsilon}
-\]
-where $\|\cdot \|_{w+\epsilon}$ is a weighted $L^2$ norm, where the weight $w \in (0,1)$ is required to vanish on $\Gamma_-$ and satisfy $\grad w = O(1)$.
-The need for this weight is necessary to account for the loss of robustness at the inflow.}
-
-\begin{figure}
-\centering
-\subfigure[Primal problem, Dirichlet inflow BC]{\includegraphics[scale=.375]{primalDir.pdf}}
-\subfigure[Adjoint problem, Dirichlet inflow BC]{\includegraphics[scale=.375]{adjointDir.pdf}}
-\subfigure[Primal problem, new inflow BC]{\includegraphics[scale=.375]{primal.pdf}}
-\subfigure[Adjoint problem, new inflow BC]{\includegraphics[scale=.375]{adjoint.pdf}}
-\caption{Comparison of primal and adjoint problems under both the standard Dirichlet and the new inflow boundary condition.
-The outflow boundary for each problem is denoted in red.
-For the Dirichlet inflow condition, adjoint solutions can develop boundary layers at the outflow of the adjoint problem.
-Under the new inflow conditions, the wall-stop boundary condition is relaxed to a zero-stress condition at the adjoint outflow.}
-\end{figure}
-
-In higher dimensions, the adjoint problem is of the same form as the primal problem with the direction of convection reversed.
-However, the primal problem determines adjoint boundary conditions on $\Gamma_-$ and $\Gamma_+$.
-Thus, wheareas for the primal problem, data is convected from the inflow to the outflow, in the adjoint problem, data is convected from the outflow to the inflow boundary instead.
-
-We can intuitively explain the loss of robustness under our derived test norm by the presence of the Dirichlet boundary condition on $v$ at the inflow boundary.
-Since the direction of convection is reversed in the adjoint equation, we can interpret the adjoint as representing the convection of a concentration $v$ from the outflow to the inflow boundary.
-In the presence of a Dirichlet boundary condition at the inflow, $v$ can develop strong boundary layers at the inflow.
-As a consequence, the quantities $\|\beta\cdot \grad v\|$ and $\sqrt{\epsilon}\|\grad v\|$ are no longer robustly bounded by $\|f\|$ and $\|g\|$, and we can no longer derive robust bounds on the error $\|u-u_h\|_{L^2}$ by the error in the energy norm.
-
-Recall our strategy for analysis was to decompose of $(v,\tau)$ into continuous and discontinuous portions.
-Mathematically speaking, the use of Dirichlet boundary conditions on the primal problem introduces strong boundary layers into the solution $v$ of the adjoint equation --- in other words, boundary layers are introduced into the continuous portions of our decomposition of $(v,\tau)$.\footnote{The boundary conditions do not introduce boundary layers into the actual computed test functions.
-However, an interesting phenomenon observed is that, for small $\epsilon$, a lack of robustness can manifest itself during numerical experiments as additional refinements near the inflow boundary, precisely where the continuous parts of the decomposition of $(v,\tau)$ develop boundary layers.} The new inflow boundary condition on the primal problem relaxes the wall boundary condition induced on the adjoint/dual problem with a boundary condition that does not generate boundary layers, resulting in stronger stability estimates for the adjoint, and a better result for the primal problem.
-
-%\begin{figure}[h]
-%\centering
-%\subfigure[Primal problem]{\includegraphics[scale=.3]{primal.png}}
-%\subfigure[Adjoint problem]{\includegraphics[scale=.3]{adjoint.png}}
-%\caption{Comparison of primal and adjoint problems for convection-diffusion under the standard Dirichlet outflow boundary condition and the new inflow boundary condition.
-Notice the replacement of a wall-stop boundary condition with a Neumann stress boundary condition at the outflow boundary of the adjoint problem.
-}
-%\end{figure}
-
-\section{Numerical experiments}
-\label{sec:num_exp}
-
-In each numerical experiment, we vary $\epsilon = .01, .001, .0001$ in order to demonstrate robustness over a range of $\epsilon$.
-This is intended to mirror the experience with roundoff effects in numerical experiments \cite{DPGrobustness}; for ``worst-case" linear solvers, such as LU decomposition without pivoting, the effect of roundoff error becomes evident in the solving of optimal test functions for $\epsilon \leq O(1e-5)$.
-The roundoff itself comes from the conditioning of the Gram matrix under certain test norms; for example, if the weighted $H({\rm div};\Omega)\times H^1(\Omega)$ norm is used for the test norm $\|\left(\tau,v\right)\|_V$ (as was done in \cite{DPG2}), for an element of size $h$, $\|v\|_{L^2}^2 = O(h)$, while $\|\grad v\|_{L^2}^2 = O(h^{-1})$.
-As $h\rightarrow 0$, the seminorm portion of the test norm dominates the Gram matrix, leading to a near-singular and ill-conditioned system.
-
-The effect of roundoff error is often characterized by an increase in the energy error, which (assuming negligible error in the approximation of test functions) is proven to decrease for any series of refined meshes.
-These roundoff effects are dependent primarily on the mesh, appearing when trying to fully resolve very thin boundary layers by introducing elements of size $\epsilon$ through adaptivity.
-The effects of roundoff error were successfully treated in \cite{DPG3} by dynamically rescaling the test norms based on element size, a practical remedy not covered yet by the present analysis.
-
-\subsection{Eriksson-Johnson model problem}
-
-To confirm our theoretical results, we adopt a modification of a problem first proposed by Eriksson and Johnson in \cite{Eriksson1993}.
-For the choice of $\Omega = (0,1)^2$, $f=0$, and $\beta = (1,0)^T$, the convection diffusion equation reduces to
-\[
-\pd{u}{x} - \epsilon \left(\pdd{u}{x}+ \pdd{u}{y}\right) = 0,
-\]
-which has an exact solution by separation of variables, allowing us to analyze convergence of DPG for a wide range of $\epsilon$.
-For boundary conditions, we impose $u=0$ on $\Gamma_+$ and $\beta_n u - \sigma_n$ on $\Gamma_-$, which reduces to
-\begin{align*}
-u-\sigma_x &= u_0-\sigma_{x,0}, \quad x=0,\\
-\sigma_y &=  0, \quad y=0,1,\\
-u &= 0, \quad x=1.\\
-\end{align*}
-In this case, our exact solution is the series
-\[
-u(x,y) = C_0 + \sum_{n=1}^\infty C_n \frac{\exp(r_2(x-1)-\exp(r_1(x-1)))}{r_1\exp(-r_2) - r_2\exp(-r_1)}\cos(n\pi y),
-\]
-where
-\begin{align*}
-r_{1,2} &= \frac{1 \pm \sqrt{1 + 4 \epsilon\lambda_n}}{2 \epsilon},\\
-\lambda_n &= n^2\pi^2 \epsilon.
-\end{align*}
-The constants $C_n$ depend on a given inflow condition $u_0$ at $x=0$ via the formula
-\[
-C_n = \int_0^1 u_0(y) \cos(n\pi y).
-\]
-
-All computations have been done using the adaptive DPG code Camellia, built on the Sandia toolbox Trilinos \cite{Camellia}.
-
-\subsubsection{Solution with $C_1 = 1, C_{n\neq 1} = 0$}
-
-We begin with the solution taken to be the first non-constant term of the above series.
-We set the inflow boundary condition to be exactly the value of $u-\sigma_x$ corresponding to the exact solution.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.37]{wallBC_exact_u.png}
-}
-\subfigure{
-\includegraphics[scale=.37]{wallBC_exact_sigx.png}
-}
-\subfigure{
-\includegraphics[scale=.37]{wallBC_exact_sigy.png}
-}
-\caption{Solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
-\end{figure}
-In each case, we begin with a square 2 by 2 mesh of quadrilateral elements with order $p=3$.
-We choose $\Delta p = 5$, though we note that the behavior of DPG is nearly identical for any $\Delta p \leq 3$, and qualitatively the same for $\Delta p = 2$.
-$h$-refinements are executed using a greedy refinement algorithm, where the element energy error $e_K^2$ is computed for all elements $K$, and elements such that $e_K^2 \leq \alpha^2 \max_K e_K^2$ are refined.
-We make the arbitrary choice of taking $\alpha = .2$ for each of these experiments.
-
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=.4]{u_pointdiff_wallBC.png}
-\caption{Adapted mesh and pointwise error for $\epsilon=.01$}
-\end{figure}
-We are especially interested in the ratio of energy error and total $L^2$ error in both $\sigma$ and $u$, which we denote as $\|u-u_h\|_{L^2}$.
-The bounds on $\nor{\cdot}_E$ presented in Section~\ref{sec:main_bounds} imply that, using the above test norm, $\|u-u_h\|_{L^2} / \|u-u_h\|_E \leq C$ independent of $\epsilon$.
-Figure~\ref{ratios_simple}, which plots the ratio of $L^2$ to energy error, seems to imply that (at least for this model problem) $C=O(1)$.
-Additionally, while we do not have a robust lower bound ($\|u-u_h\|_{L^2} / \|u-u_h\|_E$ can approach $0$ as $\epsilon \rightarrow 0$), our numerical results appear to indicate the existence of an $\epsilon$-independent lower bound.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{errorrates_wallBC.pdf}
-}
-\subfigure{
-\includegraphics[scale=.38]{L2energyratio_wallBC.pdf}
-}
-\caption{$L^2$ and energy errors, and their ratio for $\epsilon=.01$, $\epsilon=.001$, $\epsilon=.0001$}
-\label{ratios_simple}
-\end{figure}
-The effect of a mesh dependent scalings on the $\|v\|^2$ and $\|\tau\|^2$ terms in the test norm can be seen in the ratios of $L^2$ to energy error; as the mesh is refined, the constants in front of the $L^2$ terms for $v$ and $\tau$ converge to stationary values (providing the full robustness implied by our adjoint energy estimates), and the ratio of $L^2$ to energy error transitions from a smaller to a larger value.
-The transition point happens later for smaller $\epsilon$, which we expect, since the transition of the ratio corresponds to the introduction of elements whose size is of order $\epsilon$ through mesh refinement.
-For this reason, the ratios of $L^2$ to energy error do not overlap perfectly with each other.
-We note that the introduction of anisotropic refinements appears to mitigate this effect slightly \cite{DPGrobustness}.
-
-We examined how small $\epsilon$ needed to be in order to encounter roundoff effects as well.
-In \cite{DPGrobustness}, the smallest resolvable $\epsilon$ using only double precision arithmetic was $1e-4$.
-The solution of optimal test functions is now done using both pivoting and equilibration, improving conditioning.
-Roundoff effects still appear, but at smaller values of $\epsilon$.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{roundoff_rates.pdf}
-}
-\subfigure{
-\includegraphics[scale=.38]{roundoff_ratio.pdf}
-}
-\caption{Energy error and $L^2$/energy error ratio for $\epsilon=1e-5$, $\epsilon=1e-6$, $\epsilon=1e-7$.
-Non-monotonic behavior of the energy error indicates conditioning issues and roundoff effects.}
-\label{roundoff_figures}
-\end{figure}
-
-Without anisotropic refinements, it still becomes computationally difficult to fully resolve the solution for $\epsilon$ smaller than $1e-5$.
-Regardless, for all ranges of $\epsilon$, DPG does not lose robustness, as indicated by the rates and ratio between $L^2$ and energy error in Figure~\ref{roundoff_figures} remaining bounded from both above and below.
-For $\epsilon = 1e-5$, we observe that the ratio of $L^2$ error increases, corresponding to the scaling of the test norm with mesh size (the transition in test norm occurs after 8 refinements, which, for an initial $4\times 4$ mesh, implies a minimum element size of about $1.5e-05$.
-At this point, rescaled test norm allows us to take advantage of the full magnitude of the $L^2$ term for $\|v\|$ and $\|\tau\|$ implied by our adjoint estimates).
-By analogy, for smaller $\epsilon = 1e-6, 1e-7$, the transition period should begin near the 10th and 11th refinement iterations; however, we do not observe such behavior, possibly due to roundoff effects.
-For $\epsilon=1e-6$, the ratio simply remains constant, but for $\epsilon=1e-7$, we observe definite roundoff effects, as the energy error increases at the 11th refinement.
-Since DPG is optimal in the energy norm for a mesh-independent test norm\footnote{While the test norm changes with the mesh, it increases monotonically.
-A strictly stronger test norm implies $\frac{b(u,v)}{\|v\|_1} \geq \frac{b(u,v)}{\|v\|_2}$ for any $\|v\|_1 \leq \|v\|_2$}, we expect monotonic decrease of the energy error with mesh refinement.
-Non-monotonic behavior indicates either approximation or roundoff error, and as we observed no qualitative difference between using $\Delta p = 5$ and $\Delta p = 6$ for these experiments, we expect that the approximation error is negligible and conclude roundoff effects are at play when these phenomena are observed.
-
-%It is worth noting that for $\epsilon \leq 1e-6$, we do not perform enough refinements to completely resolve the boundary layer, so $|K| \geq \epsilon$ for all $K\in \Oh$.
-Thus, any roundoff effects observed are not due to the conditioning issues associated with the differing scales of the $\nor{v}_{L^2(K)}$ and $\nor{\grad v}_{L^2(K)}$ terms discussed previously.
-
-\subsubsection{Neglecting $\sigma_n$}
-
-In practice, we will not have prior knowledge of $\sigma_n$ at the inflow, and will have to set $\beta_n u - \sigma_n = u_0$, ignoring the viscous contribution to the boundary condition.
-The hope is that for small $\epsilon$, this omission will be negligible.
-Figure~\ref{ratios_noSigma} indicates that, between $\epsilon = .005$ and $\epsilon = .001$, the omission of $\sigma_n$ in the boundary condition becomes negligible, and both our error rates and ratios of $L^2$ to energy error become identical to the case where $\sigma_n$ is explicitly accounted for in the inflow condition.
-For large $\epsilon = .01$, the $L^2$ error stagnates around $1e-3$, or about $7\%$ relative error.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{rates_noSigma.pdf}
-}
-\subfigure{
-\includegraphics[scale=.38]{ratio_noSigma.pdf}
-}
-\caption{$L^2$ and energy errors and their ratio when neglecting $\sigma_n$ at the inflow.}
-\label{ratios_noSigma}
-\end{figure}
-
-\subsubsection{Discontinuous inflow data}
-
-We note also that an additional advantage of selecting this new boundary condition is a relaxation of regularity requirements: as $\widehat{f}_n \in H^{-1/2}(\Gh)$, strictly discontinuous inflow boundary conditions are no longer ``variational crimes".
-We consider the discontinuous inflow condition
-\[
-u_0(y) = \begin{cases}
-(y-1)^2, \quad &y>.5\\
--y^2, \quad &y\leq .5 
-\end{cases}
-\]
-as an example of a more difficult test case.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{disc_hat.png}
-}
-\subfigure{
-\includegraphics[scale=.38]{disc_hat_surf.png}
-}
-\caption{Solution variables $u$ and $\widehat{u}$ with discontinuous inflow data $u_0$ for $\epsilon = .01$.}
-\label{disc_sol}
-\end{figure}
-Figure~\ref{disc_sol} shows the solution $u$ and overlaid trace variable $\widehat{u}$, which both demonstrate the regularizing effect of viscosity on the discontinuous boundary condition at $x=0$.
-However, we do not have a closed-form solution with which to compare results for a stricly discontinuous $u_0$.
-In order to analyze convergence, we approximate $u_0$ with 20 terms of a Fourier series, giving a near-discontinuity for $u_0$.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{rates_disc.pdf}
-}
-\subfigure{
-\includegraphics[scale=.38]{ratio_disc.pdf}
-}
-\caption{$L^2$ and energy errors, and their ratio for $\epsilon=.01$, $\epsilon=.001$, $\epsilon=.0001$, with discontinuous $u_0$ approximated by a Fourier expansion. }
-\label{disc_sol_fourier}
-\end{figure}
-
-The ratios of $L^2$ to energy error are now less predictable than for the previous example, in part due to the difficulty in approximating highly oscillatory boundary conditions.
-However, the ratios still remain bounded as predicted by theory, and similarly to the previous problem with a smooth inflow condition, the ratios are close to $1$ for $\epsilon$ varying over two orders of magnitude.
-
-\section{Conclusions}
-
-We have presented in this paper the analysis of a non-canonical test norm and its corresponding DPG energy norm for the convection-diffusion equation in the small-diffusion limit.
-Additionally, we have introduced a non-standard inflow boundary condition, and have explored the difference between between this and the standard Dirichlet inflow boundary condition.
-
-Numerical results are presented in order to verify the results derived in this paper.
-However, at least for our model problem, numerical experiments appear to demonstrate results that are stronger than our proofs indicate, delivering solutions for $u$ and $\sigma$ that are extremely close to their best $L^2$ projections.
-
-The theory presented in this paper have been successfully extrapolated to nonlinear singular perturbation problems and systems of equations, and has been applied in context of the Burgers and Navier-Stokes equations.
-These results will be presented in an upcoming paper.
-
-\section{Acknowledgements}
-
-The authors would like to acknowledge the help of Nathan Roberts with software development and Dr Robert Moser for fruitful discussions and perspective.
-Chan and Demkowicz were supported by the Department of Energy [National Nuclear Security Administration] under Award Number [DE-FC52-08NA28615].
-Heuer was supported through the project "Fondecyt-Chile 1110324" and by the "J Tinsley Oden Faculty Research Fellowship" of the Institute of Computational Engineering and Sciences (ICES).
-
-%None yet.  Ideas:
-%\begin{itemize}
-%\item Explanation of choice of boundary condition and why it impacts stability
-%\item Interpretation of weight as allowing diffusion to work on the boundary.  
-%\item Note results have worked for Burgers, and mention the extension to Navier-Stokes
-%\end{itemize}
-
-\bibliographystyle{plain}
-\bibliography{paper}
-
-\input{paper_appendix.tex}
-
-\end{document}

### 2013-06-04 docs/Jesse/Dissertation/paper_appendix.tex

--- 2012-06-15 docs/Jesse/Proposal/paper_appendix.tex
@@
-\section{Proof of lemmas/stability of the adjoint problem}
+\chapter{Proof of lemmas/stability of the adjoint problem}
 
-We present now the proofs of the three lemmas used in this paper to show the equivalence of the DPG energy norm to norms on $U$. We reduce the adjoint problem to the scalar second order equation
+We present now the proofs of the three lemmas used in Section~\ref{sec:strategy3} to show the equivalence of the DPG energy norm to norms on $U$.
+We reduce the adjoint problem to the scalar second order equation
 \begin{align}

### 2013-06-07 docs/Truman/LocalConservation/paper/paper.tex
Rewrite of results for Local Conservation paper.

@@
 
+\subsection{Local Problem}
 The optimal test functions are determined by solving local problems determined
-by the choice of test norm. For illustrative purposes we choose the robust
+by the choice of test norm. We consider several options for the test norm.
+The graph norm \cite{DPGOverview} is one of the most natural norms to consider
+as it is derived directly from the adjoint of the problem supplemented with
+(possibly scaled) $L^2$ field terms to upgrade it from a semi-norm. 
+Chan \etal\cite{ChanHeuerThanhDemkowicz2012} derived a more robust alternative
+norm for convection diffusion (dubbed the robust norm). We recently
+developed a modification of the robust norm that appears to produce better
+results in the presence of singularities.
+
+\subsubsection{Robust Norm}
+For illustrative purposes we choose the robust
 test norm developed by Chan \etal\cite{ChanHeuerThanhDemkowicz2012}. With this
@@
 \section{Numerical Experiments}
-We explore each of the following experiments with two sets of test norms: the
-standard graph norm, and the aforementioned robust norm.
-
-\subsection{Erickson-Johnson Model Problem}
+In \ref{sec:problemDescriptions} we define each numerical experiment, and in
+\ref{sec:problemAnalysis} we discuss the solution properties in general. We
+solve with second order field variables and flux ($u$, $\bsigma$, and $\hat
+t$), third order traces ($\hat t$), and fifth order test functions ($v$ and
+$\btau$).
+
+Describe how we check local conservation.
+
+\subsection{Description of Problems}\label{sec:problemDescriptions}
+Unless otherwise noted, the problem domain is $\Omega=[0,1]^2$ and $f=0$. Also
+note that except for the discontinuous source problem, blue corresponds to
+$u=0$ and red to $u=1$ with a linear scaling in between.
+
+\subsubsection{Erickson-Johnson Model Problem}
 The Erickson-Johnson problem is one of the few convection-diffusion problems
-with a known analytical solution. Take a domain $\Omega=[0,1]^2$, with
-$\bbeta=(1,0)^T$, $f=0$ and boundary conditions $\hat t=u_0$ when
-$\beta_n\le0$, and $u_0$ is the trace of the exact solution. For
+with a known analytical solution. Take 
+$\bbeta=(1,0)^T$ and boundary conditions $\hat t=\bbeta\cdot\mathbf{n} u_0$ when
+$\beta_n\le0$, where $u_0$ is the trace of the exact solution, and $\hat u=0$
+when $\beta_n>0$. For
 $n=1,2,\cdots$, let
-$\lambda_n=n^2*\pi^2*\epsilon$,
+$\lambda_n=n^2\pi^2\epsilon$,
 $r_n=\frac{1+\sqrt{1+4\epsilon\lambda_n}}{2\epsilon}$, and 
-$s_n=\frac{1-\sqrt{1+4\epsilon\lambda_n}}{2\epsilon}$, the exact solution
+$s_n=\frac{1-\sqrt{1+4\epsilon\lambda_n}}{2\epsilon}$. The exact solution
 is
@@
 \end{equation}
-Taking $\epsilon=0.01$, $C_1=1$, and $C_{n\neq1}=0$, the exact solution looks
-like Figure \ref{fig:erickson}. We solve this problem with both conservative
-and nonconservative formulations of DPG with both graph and robust test norms.
-
-\begin{figure}[h!]
+Taking $\epsilon=10^{-2}$, $C_1=1$, and $C_{n\neq1}=0$, the exact solution looks
+like Figure \ref{fig:erickson}.
+
+\begin{figure}[p]
 \centering
@@
 
-We plot the $L^2$ and energy error for the various methods in Figures
-\ref{fig:ericksonGraphError} and \ref{fig:ericksonRobustError}. Encouragingly,
-the conservative and nonconservative plots appear to lay right on top of each
-other. This indicates that the conservative formulation at least doensn't hurt
-our convergence significantly.
-
-\begin{figure}
+\begin{figure}[p]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/Erickson/modifiedError.pdf}
+\caption{Error in Erickson-Johnson solutions}
+\label{fig:ericksonError}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/Erickson/graphFlux.pdf}
+\caption{Flux imbalance in Erickson-Johnson solutions}
+\label{ericksonFlux}
+\end{figure}
+
+\subsubsection{Skewed Convection-Diffusion Problem}
+This is a standard convection-diffusion problem with a skewed convection
+vector relative to the mesh. We take $\bbeta=(2,1)$, and on the left and
+bottom inflow boundaries we impose $\hat t=1-x-y$ while the right and top
+boundaries have $\hat u=0$. We solve for $\epsilon=10^{-4}$.
+
+\begin{figure}[p]
 \centering
@@
 \centering
-\includegraphics[width=\textwidth]{figs/Erickson/graphError.pdf}
-\caption{With graph norm}
-\label{fig:ericksonGraphError}
+\includegraphics[width=\textwidth]{figs/Confusion/modified8nc.png}
+\includegraphics[width=\textwidth]{figs/Confusion/modified8nc_mesh.png}
+\caption{Nonconservative}
+\label{fig:confusionModified8nc}
 \end{subfigure}
@@
 \centering
-\includegraphics[width=\textwidth]{figs/Erickson/robustError.pdf}
-\caption{With robust norm}
-\label{fig:ericksonRobustError}
-\end{subfigure}
-\caption{Error in Erickson-Johnson solutions}
-\end{figure}
-
-We plot the flux imbalance errors in Figures \ref{fig:ericksonGraphFlux} and
-\ref{fig:ericksonRobustFlux}. As expected, the element conservative
-formulation brings these errors to the order of machine precision, but it is
-worth pointing out that the flux imbalances for standard DPG are reasonable,
-especially under refinement.
-
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Erickson/graphFlux.pdf}
-\caption{With graph norm}
-\label{fig:ericksonGraphFlux}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Erickson/robustFlux.pdf}
-\caption{With robust norm}
-\label{fig:ericksonRobustFlux}
-\end{subfigure}
-\caption{Flux imbalance in Erickson-Johnson solutions}
-\end{figure}
-
-\subsection{Skewed Convection-Diffusion Problem}
-This is a standard convection-diffusion problem with a skewed convection
-vector relative to the mesh. The problem setup is identical to the
-Erickson-Johnson problems except that $\bbeta=(2,1)$. The following results
-are for $\epsilon=10^{-4}$.
-
-On our initial mesh, we see no noticeable difference between conservative and
-nonconservative results, though the choice of test norm affects things
-dramatically. The graph norm produces a solution which is comparable to an L2
-project of the exact solution. In this case, the field variable don't show the
-very small boundary layer along the right and top surfaces, though a
-visualization of the traces would show that the wall boundary condition is in
-fact being enforced. As we refine, the field variables will begin to reflect
-the boundary layer. On the other hand, the robust norm does show a boundary
-layer being formed in the field variables.
-
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Confusion/graph0c.png}
-\caption{Conservative with graph norm}
-\label{fig:confusionGraph0c}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Confusion/robust0c.png}
-\caption{Conservative with robust norm}
-\label{fig:confusionRobust0c}
-\end{subfigure}
-\caption{Skewed convection-diffusion problem with initial mesh}
-\end{figure}
-
-As we refine, the three results, nonconservative with graph or robust norm,
-and conservative with graph norm converge to a an essentially identical
-solution (to the eyeball norm), as represented by
-Figure~\ref{fig:confusionGraph8c}.
-
-% However, the conservative formulation with
-% the robust norm seems to exhibit some noise at the right wall as seen in
-% Figure~\ref{fig:confusionRobust8c}.
-
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Confusion/graph8c.png}
-\includegraphics[width=\textwidth]{figs/Confusion/graph8c_mesh.png}
-\caption{Conservative with graph norm}
-\label{fig:confusionGraph8c}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Confusion/robust8c.png}
-\includegraphics[width=\textwidth]{figs/Confusion/robust8c_mesh.png}
-\caption{Conservative with robust norm}
-\label{fig:confusionRobust8c}
+\includegraphics[width=\textwidth]{figs/Confusion/modified8c.png}
+\includegraphics[width=\textwidth]{figs/Confusion/modified8c_mesh.png}
+\caption{Conservative}
+\label{fig:confusionModified8c}
 \end{subfigure}
 \caption{Skewed convection-diffusion problem after 8 refinements}
-\end{figure}
-
-% If we zoom in on one of the noisy areas, as we do in
-% Figure~\ref{fig:confusionRobust8c_zoom}, we see overshoots on the order of 32
-% and undershoots on the order of -13, where the exact solution varies between 0
-% and 1. The cause of these overshoots and undershoots is a little mystery,
-% especially because they don't show up until 8 refinement steps in. We will
-% explore this problem a little more when we look at the wedge problem.
-% 
-% \begin{figure}[h!]
-% \centering
-% \includegraphics[width=0.6\textwidth]{figs/Confusion/robust8c_zoom.png}
-% \caption{Zoomed in conservative skewed convection-diffusion problem after 8
-% refinements}
-% \label{fig:confusionRobust8c_zoom}
-% \end{figure}
-
-Finally, we plot the flux imbalances for the several methods in
-Figure~\ref{fig:confusionGraphFlux} and Figure~\ref{fig:confusionRobustFlux}.
-Interestingly, it appears the effectiveness of our local conservation
-formulation drops as we refine with the graph norm.
-
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Confusion/graphFlux.pdf}
-\caption{With graph norm}
-\label{fig:confusionGraphFlux}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Confusion/robustFlux.pdf}
-\caption{With robust norm}
-\label{fig:confusionRobustFlux}
-\end{subfigure}
-\caption{Flux imbalance in skewed confusion solutions}
-\end{figure}
-
-\subsection{Double Glazing Problem}
+\label{fig:confusion}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/Confusion/modifiedFlux.pdf}
+\caption{Flux imbalance in skewed convection-diffusion solutions}
+\label{fig:confusionFlux}
+\end{figure}
+
+\subsubsection{Double Glazing Problem}
 This nominal problem definition takes the same unit square domain with 
 \[
-\bbeta=\binom{2(2y-1)(1-(2x-1)^2)}{-2(2x-1)(1-(2y-1)^2)}\,;\quad f=0\,;\quad
+\bbeta=\binom{2(2y-1)(1-(2x-1)^2)}{-2(2x-1)(1-(2y-1)^2)}\,;\quad
 \hat u=
@@
 H^{\frac{1}{2}}(\Gamma_h)$ which is continuous. Therefore we use a ramp of
-width $\sqrt{\epsilon}$ on the right edge to go from 0 to 1. The following
-results are for $\epsilon=10^{-2}$. Note that $\bbeta=(0,0)^T$ at the center
-of the domain.
-
-The choice of test norm appears to have a small effect on the choice mesh
-refinement choices as shown in Figure~\ref{fig:doubleglazing}. Other than
-that, the conservative and nonconservative solutions behave almost exactly to
-the eye. The flux imbalances in Figure~\ref{fig:doubleglazing_flux} are what
-we would expect. The nonconservative formulation appears to become more
-conservative with refinement.
-
-\begin{figure}
+width $\sqrt{\epsilon}$ on the right edge to go from 0 to 1. The 
+results are for $\epsilon=10^{-2}$.
+
+\begin{figure}[p]
 \centering
@@
 \centering
-\includegraphics[width=\textwidth]{figs/DoubleGlazing/graph6c.png}
-\caption{Conservative with graph norm}
+\includegraphics[width=\textwidth]{figs/DoubleGlazing/modified5nc.png}
+\caption{Nonconservative}
 \label{fig:doubleglazingGraph6c}
@@
 \centering
-\includegraphics[width=\textwidth]{figs/DoubleGlazing/robust6c.png}
-\caption{Conservative with robust norm}
+\includegraphics[width=\textwidth]{figs/DoubleGlazing/modified5c.png}
+\caption{Conservative}
 \label{fig:doubleglazingRobust6c}
 \end{subfigure}
-\caption{Double glazing problem after 6 refinements}
+\caption{Double glazing problem after 5 refinements}
 \label{fig:doubleglazing}
@@
 
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/DoubleGlazing/graphFlux.pdf}
-\caption{With graph norm}
-\label{fig:doubleglazingGraphFlux}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/DoubleGlazing/robustFlux.pdf}
-\caption{With robust norm}
-\label{fig:doubleglazingRobustFlux}
-\end{subfigure}
-\caption{Flux imbalance in double glazing solutions}
-\label{fig:doubleglazing_flux}
-\end{figure}
-
-\subsection{Vortex Problem}
+\begin{figure}[p]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/DoubleGlazing/modifiedFlux.pdf}
+\caption{Flux imbalance in double glazing problem}
+\label{fig:doubleglazingFlux}
+\end{figure}
+
+\subsubsection{Vortex Problem}
 This problem models a mildly diffusive vortex convecting fluid in a circle. We
-deal with domain $\Omega=[-1,1]^2$ with $\epsilon=10^{-4}$, $\bbeta=(-y,x)^T$,
-and $f=0$. Note that $\bbeta=0$ at the domain center. We have an inflow
-boundary condition when $\bbeta\cdot\mathbf{n}<0$, in which case we set $\hat
-t=\bbeta\cdot\mathbf{n}\cdot u_0$ where
+deal with domain $\Omega=[-1,1]^2$, with $\epsilon=10^{-4}$, and
+$\bbeta=(-y,x)^T$. Note that $\bbeta=\mathbf{0}$ at the domain center. We have an
+inflow boundary condition when $\bbeta\cdot\mathbf{n}<0$, in which case we set
+$\hat t=\bbeta\cdot\mathbf{n}\cdot u_0$ where
 $u_0=\frac{\sqrt{x^2+y^2}-1}{\sqrt{2}-1}$ which will vary from 0 at the center
@@
 
-Each of the four methods seems to have it's own specific refinement pattern,
-but in general we can see that the nonconservative formulations seem to place
-much more refinements in the center of the vortex where the solution is
-constant. The conservative formulations seem to recognize that more error is
-concentrated on the edges of the vortex where we have a sharp change from
-constant values to linear growth in terms of radius. Again we see that
-standard DPG appears to approach conservation with refinement, and
-unfortunately the conservative formulation appears to be losing enforcement
-under the robust norm.
-
-\begin{figure}
+\begin{figure}[p]
 \centering
@@
 \centering
-\includegraphics[width=\textwidth]{figs/Vortex/graph6nc.png}
-\caption{Nonconservative with graph norm}
-\label{fig:vortexGraph6nc}
+\includegraphics[width=\textwidth]{figs/Vortex/modified6nc.png}
+\caption{Nonconservative}
+\label{fig:vortexModified6nc}
 \end{subfigure}
@@
 \centering
-\includegraphics[width=\textwidth]{figs/Vortex/robust6nc.png}
-\caption{Nonconservative with robust norm}
-\label{fig:vortexRobust6nc}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Vortex/graph6c.png}
-\caption{Conservative with graph norm}
-\label{fig:vortexGraph6c}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Vortex/robust6c.png}
-\caption{Conservative with robust norm}
-\label{fig:vortexRobust6c}
+\includegraphics[width=\textwidth]{figs/Vortex/modified6c.png}
+\caption{Conservative}
+\label{fig:vortexModified6c}
 \end{subfigure}
@@
 
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Vortex/graphFlux.pdf}
-\caption{With graph norm}
-\label{fig:vortexGraphFlux}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Vortex/robustFlux.pdf}
-\caption{With robust norm}
-\label{fig:vortexRobustFlux}
-\end{subfigure}
+\begin{figure}[p]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/Vortex/modifiedFlux.pdf}
 \caption{Flux imbalance in vortex solutions}
@@
 
-\subsection{Wedge Problem}
+\subsubsection{Wedge Problem}
 We devised this problem to examine some of the issues we were having blow up
@@
 
-When the colorscale is scaled from 0 to 1, the macro view of all of the
-solutions looks nearly identical as seen in Figure~\ref{fig:wedge}. However,
-we start to see some differences in the refinement patterns in
-Figure~\ref{fig:wedge_mesh} indicating that the various methods distribute
-error in different ways. We see more evidence of this when we zoom in on the
-tip of the wedge where we get a change in boundary conditions. The graph norm
-solutions don't exhibit any significant problems here. The nonconservative and
-conservative solutions vary smoothly in the range $(-0.00127, 1.03)$, plus or
-minus some less significant digits. The nonconservative robust solution jumps
-from -19.6 to 20.3 at the tip, though this appears to be a very localized
-phenominon. Adding local conservation appears to exacerbate this situation as
-the solution varies from -20.0 to 23.2 and appears to polute a larger area of
-the problem. We implemented a crude hp-adaptive refinement strategy in order
-to try to resolve any singularities present in the solution. If the cell
-measure dips below $5\times10^{-4}$, we switch from h-adaptivity to
-p-adaptivity. Figure~\ref{fig:wedge_poly} shows the resultant polynomial
-orders after refinement. It really appears that the apparent singularities in
-the robust solutions are not physical phenomena that just need resolution, but
-a weakness in the method with the robust test norm.
-
-We plot the flux imbalances in Figure~\ref{fig:wedge_flux}. Despite the
-extreme overshoots and undershoots in the conservative method with the robust
-test norm, we still appear to maintain acceptable levels of conservation.
-
-\begin{figure}
+\begin{figure}[p]
 \centering
@@
 \centering
-\includegraphics[width=\textwidth]{figs/Wedge/graph16nc.png}
-\caption{Nonconservative with graph norm}
+\includegraphics[width=\textwidth]{figs/Wedge/modified16nc.png}
+\includegraphics[width=\textwidth]{figs/Wedge/modified16nc_mesh.png}
+\caption{Nonconservative}
 \label{fig:wedgeGraph16nc}
@@
 \centering
-\includegraphics[width=\textwidth]{figs/Wedge/robust16nc.png}
-\caption{Nonconservative with robust norm}
+\includegraphics[width=\textwidth]{figs/Wedge/modified16c.png}
+\includegraphics[width=\textwidth]{figs/Wedge/modified16c_mesh.png}
+\caption{Conservative}
 \label{fig:wedgeRobust16nc}
-\end{subfigure}
-\begin{subfigure}[t]{0.4\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Wedge/graph16c.png}
-\caption{Conservative with graph norm}
-\label{fig:wedgeGraph16c}
-\end{subfigure}
-\begin{subfigure}[t]{0.4\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Wedge/robust16c.png}
-\caption{Conservative with robust norm}
-\label{fig:wedgeRobust16c}
 \end{subfigure}
@@
 
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.4\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Wedge/graph16nc_mesh.png}
-\caption{Nonconservative with graph norm}
-\label{fig:wedgeGraph16nc_mesh}
-\end{subfigure}
-\begin{subfigure}[t]{0.4\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Wedge/robust16nc_mesh.png}
-\caption{Nonconservative with robust norm}
-\label{fig:wedgeRobust16nc_mesh}
-\end{subfigure}
-\begin{subfigure}[t]{0.4\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Wedge/graph16c_mesh.png}
-\caption{Conservative with graph norm}
-\label{fig:wedgeGraph16c_mesh}
-\end{subfigure}
-\begin{subfigure}[t]{0.4\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Wedge/robust16c_mesh.png}
-\caption{Conservative with robust norm}
-\label{fig:wedgeRobust16c_mesh}
-\end{subfigure}
-\caption{Wedge problem mesh after 16 refinements}
-\label{fig:wedge_mesh}
-\end{figure}
-
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Wedge/graph16nc_zoom.png}
-\caption{Nonconservative with graph norm}
-\label{fig:wedgeGraph16nc_zoom}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Wedge/robust16nc_zoom.png}
-\caption{Nonconservative with robust norm}
-\label{fig:wedgeRobust16nc_zoom}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Wedge/graph16c_zoom.png}
-\caption{Conservative with graph norm}
-\label{fig:wedgeGraph16c_zoom}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Wedge/robust16c_zoom.png}
-\caption{Conservative with robust norm}
-\label{fig:wedgeRobust16c_zoom}
-\end{subfigure}
-\caption{Wedge problem zoomed in after 16 refinements}
-\label{fig:wedge_zoom}
-\end{figure}
-
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Wedge/graph16nc_poly.png}
-\caption{Nonconservative with graph norm}
-\label{fig:wedgeGraph16nc_poly}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Wedge/robust16nc_poly.png}
-\caption{Nonconservative with robust norm}
-\label{fig:wedgeRobust16nc_poly}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Wedge/graph16c_poly.png}
-\caption{Conservative with graph norm}
-\label{fig:wedgeGraph16c_poly}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Wedge/robust16c_poly.png}
-\caption{Conservative with robust norm}
-\label{fig:wedgeRobust16c_poly}
-\end{subfigure}
-\caption{Wedge problem poly after 16 refinements}
-\label{fig:wedge_poly}
-\end{figure}
-
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Wedge/graphFlux.pdf}
-\caption{With graph norm}
-\label{fig:wedgeGraphFlux}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Wedge/robustFlux.pdf}
-\caption{With robust norm}
-\label{fig:wedgeRobustFlux}
-\end{subfigure}
+\begin{figure}[p]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/Wedge/modifiedFlux.pdf}
 \caption{Flux imbalance in wedge solutions}
@@
 
-\subsection{Inner Layer Problem}
-
-\begin{figure}
+\subsubsection{Inner Layer Problem}
+In this problem, $\bbeta=(\frac{\sqrt{3}}{2},\frac{1}{2})^T$ and we have a
+discontinuous flux inflow condition where $\hat t=0$ if $y\le0.2$ and $\hat
+t=\bbeta\cdot\mathbf{n}$ if $y>0.2$. On the outflow, $\hat u=0$. We use a very
+small diffusion scale of $\epsilon=10^{-6}$ which creates a very thin inner
+layer.
+% Nonconservative solution in range $[-0.38, 1.34]$.
+% Conservative solution in range $[-0.39, 1.38]$.
+
+\begin{figure}[p]
 \centering
@@
 \centering
-\includegraphics[width=\textwidth]{figs/InnerLayer/graph8nc.png}
-\includegraphics[width=\textwidth]{figs/InnerLayer/graph8nc_mesh.png}
-\caption{Nonconservative with graph norm}
-\label{fig:innerlayerGraph18nc}
+\includegraphics[width=\textwidth]{figs/InnerLayer/modified8nc.png}
+\includegraphics[width=\textwidth]{figs/InnerLayer/modified8nc_mesh.png}
+\caption{Nonconservative}
+\label{fig:innerlayer8nc}
 \end{subfigure}
@@
 \centering
-\includegraphics[width=\textwidth]{figs/InnerLayer/robust8nc.png}
-\includegraphics[width=\textwidth]{figs/InnerLayer/robust8nc_mesh.png}
-\caption{Nonconservative with robust norm}
-\label{fig:innerlayerRobust18nc}
+\includegraphics[width=\textwidth]{figs/InnerLayer/modified8c.png}
+\includegraphics[width=\textwidth]{figs/InnerLayer/modified8c_mesh.png}
+\caption{Conservative}
+\label{fig:innerlayer8c}
 \end{subfigure}
 \caption{Inner layer problem after 8 refinements}
-\label{fig:innerlayer8nc}
-\end{figure}
-
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/InnerLayer/graph8c.png}
-\includegraphics[width=\textwidth]{figs/InnerLayer/graph8c_mesh.png}
-\caption{Conservative with graph norm}
-\label{fig:innerlayerGraph18c}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/InnerLayer/robust8c.png}
-\includegraphics[width=\textwidth]{figs/InnerLayer/robust8c_mesh.png}
-\caption{Conservative with robust norm}
-\label{fig:innerlayerRobust18c}
-\end{subfigure}
-\caption{Inner layer problem after 8 refinements}
-\label{fig:innerlayer8c}
-\end{figure}
-
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/InnerLayer/graphFlux.pdf}
-\caption{With graph norm}
-\label{fig:innerlayerGraphFlux}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/InnerLayer/robustFlux.pdf}
-\caption{With robust norm}
-\label{fig:innerlayerRobustFlux}
-\end{subfigure}
+\label{fig:innerlayer}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/InnerLayer/modifiedFlux.pdf}
 \caption{Flux imbalance in inner layer solutions}
@@
 
-\subsection{Discontinuous Source Problem}
-
-\begin{figure}
+\subsubsection{Discontinuous Source Problem}
+Here, $\bbeta=(0.5,1)^T/\sqrt{1.25}$, and we have a discontinuous source term
+such that $f=1$ when $y\ge2x$ and $f=-1$ when $y<2x$. We apply boundary
+conditions of $\hat t=0$ on the inflow and $\hat u=0$ on the outflow. Contrary
+to the other problems discussed, the solution for this problem does not range
+from 0 to one. Rather, the colorbar in Figure \ref{fig:discontinuous} is
+scaled to  $[-1.110,0.889]$.
+
+\begin{figure}[p]
 \centering
@@
 \includegraphics[width=\textwidth]{figs/Discontinuous/graph8nc.png}
-\caption{Nonconservative with graph norm}
-\label{fig:discontinuousGraph8nc}
+\caption{Nonconservative}
+\label{fig:discontinuousModified8nc}
 \end{subfigure}
@@
 \includegraphics[width=\textwidth]{figs/Discontinuous/robust8nc.png}
-\caption{Nonconservative with robust norm}
-\label{fig:discontinuousRobust8nc}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Discontinuous/graph8c.png}
-\caption{Conservative with graph norm}
-\label{fig:discontinuousGraph8c}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Discontinuous/robust8c.png}
-\caption{Conservative with robust norm}
-\label{fig:discontinuousRobust8c}
+\caption{Conservative}
+\label{fig:discontinuousModified8c}
 \end{subfigure}
@@
 
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Discontinuous/graphFlux.pdf}
-\caption{With graph norm}
-\label{fig:discontinuousGraphFlux}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Discontinuous/robustFlux.pdf}
-\caption{With robust norm}
-\label{fig:discontinuousRobustFlux}
-\end{subfigure}
+\begin{figure}[p]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/Discontinuous/modifiedFlux.pdf}
 \caption{Flux imbalance in discontinuous source solutions}
@@
 
-\subsection{Hemker Problem}
+\subsubsection{Hemker Problem}
 The Hemker problem is defined on a domain
-$\Omega=\{[-3,9]\times[-3,3]\}\{(x,y):x^2+y^2<1\}$, essentially a simplified
+$\Omega=\{[-3,9]\times[-3,3]\}\setminus\{(x,y):x^2+y^2<1\}$, essentially a simplified
 model of flow past an infinite cylinder. We start with the initial mesh shown
-in Figure~\ref{fig:hemkerInitial} in which we approximate the circle by 32
-linear segments. Our code does not fully support curvilinear elements at this
-time, so as we refine, we just subdivide the initial linear segments. The
-boundary conditions are $\hat t=\bbeta\cdot\mathbf{n}\cdot 1$ on the left
-inflow boundary, $\bbeta\cdot\mathbf{n}\cdot\hat u-\hat t=\sigma_n=0$ on the
-right outflow boundary, $\hat t=0$ on the top and bottom edges, and $\hat u=1$
-on the cylinder.
-
-\begin{figure}[h!]
+in Figure~\ref{fig:hemkerInitial} in which we approximate the circle by 8
+fourth order curvilinear polynomial segments. As we refine, the new elements are
+fitted to better approximate an exact circle.The boundary conditions are $\hat
+t=\bbeta\cdot\mathbf{n}\cdot 1$ on the left inflow boundary,
+$\bbeta\cdot\mathbf{n}\cdot\hat u-\hat t=\sigma_n=0$ on the right outflow
+boundary, $\hat t=0$ on the top and bottom edges, and $\hat u=1$ on the
+cylinder.
+
+\begin{figure}[p]
 \centering
@@
 
-After some early refinement steps in which the graph norm solutions exhibit
-some strange behavior (see Figure~\ref{fig:hemker4}) all four methods appear
-to converge toward a decent solution as shown in Figure~\ref{fig:hemker8}. The
-different methods seem to prioritize different parts of the mesh for
-refinement, but with sufficient refinement, the differences in the actual
-solution are fairly insignificant. TODO: Explain why $\hat u$ boundary is not
-nice on inflow.
-
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Hemker/graph4nc.png}
-\includegraphics[width=\textwidth]{figs/Hemker/graph4nc_mesh.png}
-\caption{Nonconservative with graph norm}
-\label{fig:hemkerGraph4nc}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Hemker/robust4nc.png}
-\includegraphics[width=\textwidth]{figs/Hemker/robust4nc_mesh.png}
-\caption{Nonconservative with robust norm}
-\label{fig:hemkerRobust4nc}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Hemker/graph4c.png}
-\includegraphics[width=\textwidth]{figs/Hemker/graph4c_mesh.png}
-\caption{Conservative with graph norm}
-\label{fig:hemkerGraph4c}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Hemker/robust4c.png}
-\includegraphics[width=\textwidth]{figs/Hemker/robust4c_mesh.png}
-\caption{Conservative with robust norm}
-\label{fig:hemkerRobust4c}
-\end{subfigure}
-\caption{Hemker problem after 4 refinements}
-\label{fig:hemker4}
-\end{figure}
-
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Hemker/graph8nc.png}
-\includegraphics[width=\textwidth]{figs/Hemker/graph8nc_mesh.png}
-\caption{Nonconservative with graph norm}
-\label{fig:hemkerGraph8nc}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Hemker/robust8nc.png}
-\includegraphics[width=\textwidth]{figs/Hemker/robust8nc_mesh.png}
-\caption{Nonconservative with robust norm}
-\label{fig:hemkerRobust8nc}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Hemker/graph8c.png}
-\includegraphics[width=\textwidth]{figs/Hemker/graph8c_mesh.png}
-\caption{Conservative with graph norm}
-\label{fig:hemkerGraph8c}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Hemker/robust8c.png}
-\includegraphics[width=\textwidth]{figs/Hemker/robust8c_mesh.png}
-\caption{Conservative with robust norm}
-\label{fig:hemkerRobust8c}
+\begin{figure}[p]
+\centering
+\begin{subfigure}[t]{0.6\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Hemker/modified8nc.png}
+\end{subfigure}
+\begin{subfigure}[t]{0.6\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Hemker/modified8nc_mesh.png}
+\caption{Nonconservative}
+\label{fig:hemkerModified8nc}
+\end{subfigure}
+\begin{subfigure}[t]{0.6\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Hemker/modified8c.png}
+\end{subfigure}
+\begin{subfigure}[t]{0.6\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Hemker/modified8c_mesh.png}
+\caption{Conservative}
+\label{fig:hemkerModified8c}
 \end{subfigure}
@@
 
-\begin{figure}
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Hemker/graphFlux.pdf}
-\caption{With graph norm}
-\label{fig:hemkerGraphFlux}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Hemker/robustFlux.pdf}
-\caption{With robust norm}
-\label{fig:hemkerRobustFlux}
-\end{subfigure}
-\caption{Flux imbalance in Hemker solutions}
-\label{fig:hemker_flux}
-\end{figure}
+\begin{figure}[p]
+\centering
+\centering
+\includegraphics[width=0.8\textwidth]{figs/Hemker/modifiedFlux.pdf}
+\caption{Flux imbalance in Hemker problem}
+\label{fig:hemkerFlux}
+\end{figure}
+
+\subsection{Analysis of Results}\label{sec:problemAnalysis}
+% Solution quality
+The general trend we see looking at the results is that the solution quality
+of the conservative and conconservative formulations is nearly identical. This
+is ideal, as we wish to preserve the attractive features of DPG --
+namely that it minimizes error in the energy norm. In particular, when we
+examine the error convergence plots for the Erickson-Johnson problem, the
+energy levels for the two methods lie nearly right on top of each other. This
+seems to indicate at the least that enforcing local conservation doesn't hurt
+DPG too much.
+
+% Overshoots/undershoots
+Another measure of solution quality is to look at the magnitude of overshoots
+and undershoots in the solution. In most of the problems considered (barring
+the discontinuous source problem) the exact solution would range exactly
+between 0 and 1. The the resolved solutions, the divergence from these values
+would be negligible, but for the inner layer, in which $\epsilon=10^{-6}$, we
+get overshoots and undershoots along the separation line. For the
+nonconservative formulation, the solution range for $u$ was $[-0.392,1.342]$,
+while the conservative solution range was $[0.389,1.378]$. This difference is
+easily accounted for by the differences in refinement patterns between the two
+methods.
+
+% Mesh refinements
+It is clear when comparing the refinement patterns that the two methods appear
+to calculate slightly different error representation functions (which
+determine which elements to adaptively refine). Standard DPG minimizes the
+error in the energy norm, but the Lagrange multipliers in the conservative
+formulation shift the solution slightly. So we should see somewhat higher
+error and different elements will get chosen for refinement. The choice of
+test norm also plays into this calculation of the error representation
+function. As discussed earlier, the conservative formulation allows us to
+throw away the $L^2$ term on $v$. The inclusion of this term required certain
+assumptions on $\bbeta$ \cite{ChanHeuerThanhDemkowicz2012} that break down for
+the vortex problem. Here we see the nonconservative method needlessly refine
+in the center of the domain where the solution is constant. The conservative
+scheme is more discerning about refinements and focuses refinements where
+solution features are changing. In general, though, both methods appear to
+follow very similar refinement patterns.
+
+% Mass conservation
+It shouldn't come as a surprise that the conservative and nonconservative
+solutions match each other so closely. The conservative formulation
+enforces local conservation more strictly, but if we examine the flux
+imbalance plots, the nonconservative formulation is nearly conservative on its
+own -- and appears to become more conservative with refinement. The flux
+imbalance of the conservative methods appears to bounce around close to the
+machine epsilon (plus a few orders of magnitude). The level of enforcement
+appears to creep up with more degrees of freedom, indicating possible
+accruement of numerical error.
 

### 2013-06-07 docs/Truman/LocalConservation/paper/paper.tex
Added Jesse's content to local conservation paper.

@@
 \usepackage{caption}
+\usepackage{color}
 \usepackage{subcaption}
@@
 
+\section{A coupled, robust test norm}
+In the course of our numerical experiments, we encountered unforseen
+difficulties for certain problems under our current robust test norm.  We
+illustrate in this section the observed issue using a second model problem
+with a singular solution, offer possible explanations for the phenomena
+observed, and propose a modification of the robust test norm presented
+previously, which we demonstrate eliminates the issues observed in numerical
+experiments.
+
+\subsection{A second model problem}
+\seclab{sec:confusionPlate}
+We begin by first examining a different problem than convection-diffusion --
+we examine admissible solutions for the homogeneous Laplace's equation over
+the $y > 0$ half-plane under boundary conditions 
+\begin{align*}
+u &= 0 \text{ on } x > 0\\
+\pd{u}{n} &= 0 \text{ on } x < 0.
+\end{align*}
+Let us consider the 2D case - a simple separation of variables argument in
+polar coordinates shows that the solution is of the form
+\[
+u(r,\theta) = \sum_{n=0}^\infty R_n(r) \sin(\lambda_n \theta),
+\]
+where $\lambda_n = n + \frac{1}{2}$, and $R_n(r) = C_{1,n}x^{\lambda_n} + C_{2,n}x^{-\lambda_n}$.
+By requiring $u(0,\theta) < \infty$, we have $R_n(r) = C_n x^{\lambda_n}$.
+We have now that solutions to this problem include $u$ of the form
+\[
+u = \sum_{n=0} x^{n+\frac{1}{2}} \sin\LRp{\LRp{n+\frac{1}{2}}\theta}.
+\]
+Note that even in the lowest-order term, the gradient of $u$ displays a
+singularity at $r = 0$.  \textcolor{red}{Find reference in that solutions to
+Laplace's equation always can be split into smooth and singular parts on
+similar domains.}
+
+Consider now Laplace's equation $\del u = f$ on the box domain $\Omega =
+[0,1]^2$ with boundary conditions
+\begin{align*}
+u &= 0 \text{ on } x > .5\\
+\pd{u}{n} &= 0 \text{ on } x < .5.
+\end{align*}
+with forcing term $f=1$.  
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=.375]{figs/LaplaceFigs/LaplacePlate.png}
+\caption{Solution of Laplace's equation on the unit quad with $f=1$.}
+\label{fig:laplace}
+\end{figure}
+Extrapolating the results from the half-plane example to a finite domain, we
+expect the solution of Laplace's equation to be bounded, but to have a
+singularity in its gradient.  Figures~\ref{fig:laplace} and
+\ref{fig:laplaceStresses} are finite element solutions of the above problem
+under a quadratic $h$-refined mesh.  Figure~\ref{fig:laplace} confirms that
+$u$ is bounded, while Figure~\ref{fig:laplaceStresses} confirms that
+singularities in the gradient appear at the point $(.5,0)$, where the boundary
+condition changes from Neumann to Dirichlet.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=.275]{figs/LaplaceFigs/LaplacePlateSigma1.png}
+\includegraphics[scale=.275]{figs/LaplaceFigs/LaplacePlateSigma2.png}
+\caption{$x$ and $y$ components of the $\Grad u$ for $u$ solving Laplace's equation with a change in boundary conditions.
+Both components develop singularities at the point where the boundary condition changes type.}
+\label{fig:laplaceStresses}
+\end{figure}
+
+We consider now the convection-diffusion problem, under a similar setup as
+before.  We consider the domain $\Omega = [0,1]^2$, with boundary conditions
+\begin{align*}
+u &= 0,\quad \text{ on } x = 0\\
+\pd{u}{n} &= 0,\quad \text{ on } x = 1, y = 1, \text{ and } y = 0, x < .5\\
+u &= 1,\quad \text{ on } .5 < x \leq 1.
+\end{align*}
+The problem is meant to simulate the transport of $u$ over a domain with a
+``plate'' boundary $x \in [.5,1]$.  For small $\epsilon$, the problem develops
+a boundary layer over the plate, as well as a singularity at the plate tip
+$(x,y) = (.5,0)$.\footnote{This problem is meant to mimic the Carter flat
+plate problem -- a common early benchmark problem in viscous compressible flow
+problems -- which can be shown to also exhibit a singularity in stress at the
+point $(.5,0)$.}  Unlike the Laplace example, we swap the Dirichlet boundary
+condition at the outflow $x=1$ with an outflow boundary
+condition.\footnote{The outflow ``boundary condition'' is simply the absence
+of an applied boundary condition, and is analyzed in more detail in
+\cite{FLD:FLD505}.  This outflow condition appears to work well for
+convection-diffusion problems in the convective regime, and is the outflow
+condition we will use in our extension of DPG to a model problem in viscous
+compressible flow.  Though the well-posedness of the problem under this
+boundary condition is questionable, we can still effectively illustrate the
+issues present under the robust test norm using this problem setup.  }
+
+The above convection-diffusion problem is related back to the earlier
+Laplace/diffusion problem with a singularity -- in most of the domain,
+convective effects dominate; however, if we  localizing the behavior of
+Laplace's equation to a circle of $\epsilon$ around $(.5,0)$, then we again
+see a discontinuity in the stresses.  Asymptotic expansion techniques indicate
+that singularities in solutions are determined primarily by the highest order
+differential operator present in the equation -- in other words, the addition
+of a convective term to a scaled Laplacian (to recover the
+convection-diffusion equation) will not alter the presence of a singularity in
+the solution \cite{roos2008robust}.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=.275]{figs/LaplaceFigs/confusion1e2h1e2.png}
+\includegraphics[scale=.275]{figs/LaplaceFigs/confusion1e2h1e3.png}
+\caption{Solution $u$ for $\epsilon = .01$ under the robust test norm.
+The solution oscillates strongly at the plate edge, growing in magnitude under additional refinements despite the absence of a singularity in $u$ at that point.}
+\label{fig:plateOsc}
+\end{figure}
+
+Figures~\ref{fig:plateOsc} and \ref{fig:plateOscZoom} demonstrate the behavior
+of the DPG method under the robust test norm for the plate problem.  The
+diffusion is taken to be fairly large ($\epsilon = 10^{-2}$), and automatic
+refinements are done until the element size $h$ is at or below the diffusion
+scale.  Due to the singular nature of the solution, refinements are clustered
+around $(.5,0)$, and the order is set to be uniform with $p=2$.  While there
+should be no singularity in $u$, the magnitude of $u$ grows as $h \rightarrow
+0$, so long as $h\leq \epsilon$.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=.375]{figs/LaplaceFigs/confusion1e2h1e3uZoom.png}
+\caption{Zoomed solution $u$ and adaptive mesh for $\epsilon = .01$ after over-resolution of the diffusion scale. }
+\label{fig:plateOscZoom}
+\end{figure}
+
+We note that the appearance of this non-physical singularity in $u$ is allowed
+under the theory underlying the robust test norm; the error in the $\L$-norm
+of the solution is guaranteed to be robustly bounded; however, the $\L$ norm
+does allow for the presence of weak singularities (singularities of order
+$x^{-\frac{1}{2}}$).  Apart from the oscillation of $u$ at the singular point,
+the solution is well-behaved, and the stress $\sigma = \epsilon \Grad u$ is
+very well represented, as indicated in Figure~\ref{fig:plateStresses}.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=.275]{figs/LaplaceFigs/confusion1e2h1e3Sigma1.png}
+\includegraphics[scale=.275]{figs/LaplaceFigs/confusion1e2h1e3Sigma2.png}
+\caption{Viscous stresses for the plate problem.  }
+\label{fig:plateStresses}
+\end{figure}
+
+\subsection{A modification of the robust test norm}
+
+While oscillations of this sort in a solution near a singular point may be
+acceptable in certain simulations, it is a large problem for the methods in
+compressible flow simulations -- physical constraints require several solution
+variables to remain positive throughout simulation.\footnote{Apart from
+returning a non-physical solution, the violation of positivity constraints
+typically results in non-convergence of nonlinear solvers.}  We propose a
+modification of the robust test norm that appears to remedy this issue, which
+we refer to as 
+\[
+\norm{\LRp{v,\tau}}_V^2 \coloneqq \norm{v}^2_{\L} + \norm{\beta\cdot \Grad v}_{\L}^2 + \norm{\div \tau - \beta\cdot\Grad v}_{\L}^2 + \norm{C_\tau\tau}_{\L}^2,
+\]
+where $C_\tau$ is defined as before.
+\footnote{
+We note that we have dropped the
+mesh-dependent scaling on $\norm{v}_{\L}$ from the robust norm; this is related
+to recent insights into the nature of DPG test spaces and explained in more
+detail in %Appendix~\secref{appendix:globalLocal}.
+}  
+We note that, under the
+theory developed in 
+% Section~\secref{sec:testNormSec}, 
+the above test norm is
+trivially provably robust using the same theory.
+\footnote{This is due to the
+fact that $\norm{\div \tau - \beta\cdot\Grad v}_{\L}^2$ is robustly bounded by
+$\norm{\div \tau}_{\L}$ and $\norm{\beta\cdot\Grad v}_{\L}$.  Alternatively, we
+can note that $\norm{\div \tau - \beta\cdot\Grad v}_{\L}^2 = \norm{g}_{\L}^2$,
+where $g$ is a load of the adjoint problem related to robustness described in
+% Section~\secref{sec:testNormSec}.
+}
+
+While not rigorously understood, the author believes the issues related to the
+appearance of non-physical singularities to be related to the uncoupled nature
+of the test norm.  Previous example problems exhibited boundary layers and
+sharp gradients in the stress $\sigma$, but not singularities, which
+contribute significantly more error.  We expect that the oscillations observed
+in $u$ are a sort of \textit{pollution error}, where error in $u$ is tied to
+error in $\sigma$.  If we consider the ultra-weak variational formulation for
+convection-diffusion
+\[
+\LRp{u,\div \tau - \beta\cdot \grad v}_{\L} + \LRp{\sigma,\frac{1}{\epsilon} \tau + \grad v}_{\L} + \ldots,
+\]
+we can see that it is a combination of test functions that corresponds to both
+$u$ and $\sigma$.  Recall from the previous section that, by choosing $\tau$
+and $v$ such that they satisfy the adjoint equation with forcing terms $u$ and
+$\sigma$, we recover the best $L^2$ approximation.  In other words, achieving
+optimality in the $L^2$ norm requires coupling between $v$ and $\tau$, which
+is achieved under the graph norm, but not the robust norm derived in the
+previous section.  If coupling of the test terms , we expect that decoupling
+$v$ and $\tau$ from each other in a test norm from each other will have the
+effect of coupling error in $\sigma$ to error in $u$, which would explain the
+spurious oscillations in $u$ in the presence of singularities in $\sigma$.
+Similar results have been observed in the Stokes equations, where error in $u$
+is coupled to the behavior of the pressure variable \cite{FLD:FLD582}.
+
+The drawback to using the above test norm is that the resulting local system
+for test functions is now completely coupled, whereas using the previous test
+norm, the system was block diagonal due to the decoupling in $v$ and $\tau$
+and could be constructed and inverted more efficiently.  We hope to explore
+the difference between these two norms in more rigor and detail in the
+future.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=.275]{figs/LaplaceFigs/coupled1e2h1e2.png}
+\includegraphics[scale=.275]{figs/LaplaceFigs/coupled1e2h1e3.png}
+\caption{$\epsilon = 10^{-2}$ without $h$-resolving diffusion scale, and with $h$-resolution of diffusion scale.}
+\label{fig:newNorm}
+\end{figure}
+
+Figure~\ref{fig:newNorm} shows the solution for $\epsilon = .01$, where the
+diffusion scale is both underresolved and resolved by $h$-adaptivity.  In both
+cases, there are no additional oscillations near the plate tip --
+Figure~\ref{fig:newNormZoom} shows a zoomed image of the solution $u$ at the
+point $(.5,0)$.  The stress is resolved similarly to the previous case;
+however, the solution $u$ does not display spurious oscillations in either the
+underresolved or resolved cases.  Figure~\ref{fig:newNormSmallEps} displays
+the same quantities, but for $\epsilon = 10^{-4}$, in order to demonstrate
+that the new test norm removes spurious oscillations in $u$ (in the presence
+of singularities in $\sigma$) independently of $\epsilon$.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=.3]{figs/LaplaceFigs/coupled1e2h1e3uZoom.png}
+\caption{Zoom of solution $u$ at the plate tip for $\epsilon = 10^{-2}$.}
+\label{fig:newNormZoom}
+\end{figure}
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=.25]{figs/LaplaceFigs/coupled1e4h1e5.png}
+\includegraphics[scale=.227]{figs/LaplaceFigs/coupled1e4h1e5Zoom.png}
+\caption{14 refinements for $\epsilon = 10^{-4}$, min $h$ is $O(10^{-5})$.}
+\label{fig:newNormSmallEps}
+\end{figure}
+
 \bibliographystyle{plain} 

### 2013-06-10 docs/Truman/LocalConservation/paper/paper.tex
Updated structure of local conservation paper.

@@
 
-\section{Analysis}
+\section{Element Conservative Convection-Diffusion}
 We now proceed to develop a locally conservative formulation of DPG for
@@
 
-\subsection{Element Conservative Convection-Diffusion}
+\subsection{Derivation}
 Now that we have briefly outlined the abstract DPG method, let us apply it to
@@
 trial space. It does not specify our choice of trial space. Nevertheless, many
-considerations of DPG in the literature \cite{} associate DPG with the
-so-called ``ultra-weak formulation.'' We will follow the same derivation for
-the convection-diffusion equation, but we emphasize that other formulations
-are available. Thus, we seek field variables $u\in L^2(K)$ and
-$\bsigma\in\mb{L^2}(K)$. Mathematically, this leaves their traces on element
-boundaries undefined, and in a manner similar to the hybridized discontinuous
-Galerkin method, we define new unknowns for trace $\hat u$ and flux $\hat t$.
-Applying these definitions to \eqnref{preultraweak} and adding the two
-equations together, we arrive at our desired variational problem.
+considerations of DPG in the literature (convection-diffusion \cite{DPG6},
+linear elasticity \cite{BramwellDemkowiczGopalakrishnanQiu11}, linear
+acoustics \cite{DemkowiczGopalakrishnanMugaZitelli12}, Stokes
+\cite{DPGStokes})
+associate DPG with the so-called ``ultra-weak formulation.'' We will follow
+the same derivation for the convection-diffusion equation, but we emphasize
+that other formulations are available. Thus, we seek field variables $u\in
+L^2(K)$ and $\bsigma\in\mb{L^2}(K)$. Mathematically, this leaves their traces
+on element boundaries undefined, and in a manner similar to the hybridized
+discontinuous Galerkin method, we define new unknowns for trace $\hat u$ and
+flux $\hat t$.  Applying these definitions to \eqnref{preultraweak} and adding
+the two equations together, we arrive at our desired variational problem.
 
@@
 \end{equation}
-
-\subsection{Local Problem}
-The optimal test functions are determined by solving local problems determined
-by the choice of test norm. We consider several options for the test norm.
-The graph norm \cite{DPGOverview} is one of the most natural norms to consider
-as it is derived directly from the adjoint of the problem supplemented with
-(possibly scaled) $L^2$ field terms to upgrade it from a semi-norm. 
-Chan \etal\cite{ChanHeuerThanhDemkowicz2012} derived a more robust alternative
-norm for convection diffusion (dubbed the robust norm). We recently
-developed a modification of the robust norm that appears to produce better
-results in the presence of singularities.
-
-\subsubsection{Robust Norm}
-For illustrative purposes we choose the robust
-test norm developed by Chan \etal\cite{ChanHeuerThanhDemkowicz2012}. With this
-choice, we get our local problem:
-
-Find $\vdeltau\in\HOneK,\,\taudeltau\in\HdivK$ such that:
-\begin{align}
-(\nabla\cdot\taudeltau,&\nabla\cdot\delta\btau)_K
-+\min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}(\taudeltau,\delta\btau)_K
-+\epsilon(\nabla\vdeltau,\nabla \delta v)_K
-+(\bbeta\cdot\nabla\vdeltau,\bbeta\cdot\nabla \delta v)_K\nonumber\\
-&+\alpha\min\left\{\sqrt{\frac{\epsilon}{|K|}},1\right\}(\vdeltau,\delta v)_K
-=b(\delta\bs u_h,(\delta v,\delta\btau))
-\quad\quad\forall\delta v\in\HOneK,\,\delta\btau\in\HdivK\,,
-\label{eq:localSolve}
-\end{align}
-where, typically, $\alpha=1$.
-
-We can decompose the discrete flux space $\hat F_h$ into element conserving
-fluxes and some algebraic complement:
-\begin{equation}
-\hat F_h=\hat F_h^c\oplus\hat F_h^{nc}\,,\quad\hat 
-F_h^{c}:=\{\hat t:\langle\hat t,(1_K,\bs0)\rangle=0\quad\forall K\}\,.
-\label{eq:decomposition}
-\end{equation}
-This may be accomplished by employing for fluxes in $\hat F_h^{c}$ traces of
-curls, $\nabla\times\phi$.
-
-In practice, we solve \eqref{eq:conservativeConfusionSystem} as a fully 
-coupled system of equations, but for didactic purposes, we can examine it 
-one piece at a time. If we restrict \eqref{eq:conservativeConfusionSystem}$_1$
-to $\delta\hat t\in\hat F_h^{nc}$, the Lagrange multiplier term drops out and we 
-left with a system that we can solve for $u_h$, $\bsigma_h$, $\hat u_h$, and 
-$\hat t_h^c\in\hat F^c_h$.
-
-Restricting ourselves to $\delta\hat t\in\hat
-F_h^{c}$ in \eqref{eq:conservativeConfusionSystem}$_1$, we obtain a system  of
-equations that can be solved for $u_h$, $\bsigma_h$, $\hat u$, and $\hat
-t\in\hat F_h^c$. The remaining fluxes, $\hat t\in\hat F_h^{nc}$ are determined
-from \eqref{eq:conservativeConfusionSystem}$_2$. Finally, testing with $\hat
-t\in\hat F_h^{nc}$ in \eqref{eq:conservativeConfusionSystem}$_1$, we obtain a
-system of equations that can be solved for Lagrange multipliers $\lambda_K$.
-
-Additionally, we can pass in local problem \eqref{eq:localSolve} with
-$\alpha\rightarrow0$. The fact that the test functions will be determined then
-up to a constant does not matter, for $\delta\hat t\in\hat F_h^c$, equation
-\eqref{eq:conservativeConfusionSystem}$_1$ is orthogonal to constants. 
-Mathematically, we are dealing with equivalence classes of functions, but in order 
-to obtain a single function that we can deal with numerically, we replace the alpha 
-term with a zero mean scaling condition to obtain the new test norm,
-\begin{align}
-(\nabla\cdot\taudeltau,&\nabla\cdot\delta\btau)_K
-+\min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}(\taudeltau,\delta\btau)_K
-\nonumber\\
-&+\epsilon(\nabla\vdeltau,\nabla \delta v)_K
-+(\bbeta\cdot\nabla\vdeltau,\bbeta\cdot\nabla \delta v)_K
-+\frac{1}{|K|^2}\int_K\vdeltau\delta v\,,
-\label{eq:localSolveMod}
-\end{align}
-where the $\frac{1}{|K|^2}$ coefficient is needed to make the zero mean term 
-scale correctly with $h$. Numerically this helps a good deal with the condition
-numbers of the local solve.
-
-It is convenient to be able to take $\alpha\rightarrow0$ as we will see in
-some later numerical experiments.
 
@@
 
-\section{Numerical Experiments}
-In \ref{sec:problemDescriptions} we define each numerical experiment, and in
-\ref{sec:problemAnalysis} we discuss the solution properties in general. We
-solve with second order field variables and flux ($u$, $\bsigma$, and $\hat
-t$), third order traces ($\hat t$), and fifth order test functions ($v$ and
-$\btau$).
-
-Describe how we check local conservation.
-
-\subsection{Description of Problems}\label{sec:problemDescriptions}
-Unless otherwise noted, the problem domain is $\Omega=[0,1]^2$ and $f=0$. Also
-note that except for the discontinuous source problem, blue corresponds to
-$u=0$ and red to $u=1$ with a linear scaling in between.
-
-\subsubsection{Erickson-Johnson Model Problem}
-The Erickson-Johnson problem is one of the few convection-diffusion problems
-with a known analytical solution. Take 
-$\bbeta=(1,0)^T$ and boundary conditions $\hat t=\bbeta\cdot\mathbf{n} u_0$ when
-$\beta_n\le0$, where $u_0$ is the trace of the exact solution, and $\hat u=0$
-when $\beta_n>0$. For
-$n=1,2,\cdots$, let
-$\lambda_n=n^2\pi^2\epsilon$,
-$r_n=\frac{1+\sqrt{1+4\epsilon\lambda_n}}{2\epsilon}$, and 
-$s_n=\frac{1-\sqrt{1+4\epsilon\lambda_n}}{2\epsilon}$. The exact solution
-is
-\begin{equation}
-u(x,y)=C_0+\sum_{n=1}^\infty C_n\frac{\exp(s_n(x-1))-\exp(r_n(x-1))}
-{r_n\exp(-s_n)-s_n\exp(-s_n)}\cos(n\pi y)\,.
-\label{eq:ericksonExact}
-\end{equation}
-Taking $\epsilon=10^{-2}$, $C_1=1$, and $C_{n\neq1}=0$, the exact solution looks
-like Figure \ref{fig:erickson}.
-
-\begin{figure}[p]
-\centering
-\includegraphics[width=0.6\textwidth]{figs/Erickson/exact.png}
-\caption{Erickson-Johnson exact solution}
-\label{fig:erickson}
-\end{figure}
-
-\begin{figure}[p]
-\centering
-\includegraphics[width=0.8\textwidth]{figs/Erickson/modifiedError.pdf}
-\caption{Error in Erickson-Johnson solutions}
-\label{fig:ericksonError}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=0.8\textwidth]{figs/Erickson/graphFlux.pdf}
-\caption{Flux imbalance in Erickson-Johnson solutions}
-\label{ericksonFlux}
-\end{figure}
-
-\subsubsection{Skewed Convection-Diffusion Problem}
-This is a standard convection-diffusion problem with a skewed convection
-vector relative to the mesh. We take $\bbeta=(2,1)$, and on the left and
-bottom inflow boundaries we impose $\hat t=1-x-y$ while the right and top
-boundaries have $\hat u=0$. We solve for $\epsilon=10^{-4}$.
-
-\begin{figure}[p]
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Confusion/modified8nc.png}
-\includegraphics[width=\textwidth]{figs/Confusion/modified8nc_mesh.png}
-\caption{Nonconservative}
-\label{fig:confusionModified8nc}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Confusion/modified8c.png}
-\includegraphics[width=\textwidth]{figs/Confusion/modified8c_mesh.png}
-\caption{Conservative}
-\label{fig:confusionModified8c}
-\end{subfigure}
-\caption{Skewed convection-diffusion problem after 8 refinements}
-\label{fig:confusion}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=0.8\textwidth]{figs/Confusion/modifiedFlux.pdf}
-\caption{Flux imbalance in skewed convection-diffusion solutions}
-\label{fig:confusionFlux}
-\end{figure}
-
-\subsubsection{Double Glazing Problem}
-This nominal problem definition takes the same unit square domain with 
-\[
-\bbeta=\binom{2(2y-1)(1-(2x-1)^2)}{-2(2x-1)(1-(2y-1)^2)}\,;\quad
-\hat u=
-\begin{cases}
-1 & \mbox{on }\Gamma_{right}\\
-0 & \mbox{else }
-\end{cases}\,,
-\]
-except that this definition for the boundary is not legal for $\hat u\in
-H^{\frac{1}{2}}(\Gamma_h)$ which is continuous. Therefore we use a ramp of
-width $\sqrt{\epsilon}$ on the right edge to go from 0 to 1. The 
-results are for $\epsilon=10^{-2}$.
-
-\begin{figure}[p]
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/DoubleGlazing/modified5nc.png}
-\caption{Nonconservative}
-\label{fig:doubleglazingGraph6c}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/DoubleGlazing/modified5c.png}
-\caption{Conservative}
-\label{fig:doubleglazingRobust6c}
-\end{subfigure}
-\caption{Double glazing problem after 5 refinements}
-\label{fig:doubleglazing}
-\end{figure}
-
-\begin{figure}[p]
-\centering
-\includegraphics[width=0.8\textwidth]{figs/DoubleGlazing/modifiedFlux.pdf}
-\caption{Flux imbalance in double glazing problem}
-\label{fig:doubleglazingFlux}
-\end{figure}
-
-\subsubsection{Vortex Problem}
-This problem models a mildly diffusive vortex convecting fluid in a circle. We
-deal with domain $\Omega=[-1,1]^2$, with $\epsilon=10^{-4}$, and
-$\bbeta=(-y,x)^T$. Note that $\bbeta=\mathbf{0}$ at the domain center. We have an
-inflow boundary condition when $\bbeta\cdot\mathbf{n}<0$, in which case we set
-$\hat t=\bbeta\cdot\mathbf{n}\cdot u_0$ where
-$u_0=\frac{\sqrt{x^2+y^2}-1}{\sqrt{2}-1}$ which will vary from 0 at the center
-of boundary edges to 1 at corners. We don't enforce an outflow boundary.
-
-\begin{figure}[p]
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Vortex/modified6nc.png}
-\caption{Nonconservative}
-\label{fig:vortexModified6nc}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Vortex/modified6c.png}
-\caption{Conservative}
-\label{fig:vortexModified6c}
-\end{subfigure}
-\caption{Vortex problem after 6 refinements}
-\label{fig:vortex}
-\end{figure}
-
-\begin{figure}[p]
-\centering
-\includegraphics[width=0.8\textwidth]{figs/Vortex/modifiedFlux.pdf}
-\caption{Flux imbalance in vortex solutions}
-\label{fig:vortex_flux}
-\end{figure}
-
-\subsubsection{Wedge Problem}
-We devised this problem to examine some of the issues we were having blow up
-of the solution under the robust test norm. The domain is a rectangle
-$[-0.5,0.5]\times[-1,0.5]$ where the triangle connecting the bottom edges with
-the origin at $(0,0)$ is removed. The convection vector $\bbeta=(1,0)^T$,
-$\epsilon=10^{-1}$, and we apply boundary conditions $\hat t=0$ on the left
-inflow edge, $\hat u=0$ on the top edge, $\bbeta\cdot\mathbf{n}\cdot\hat
-u-\hat t=\sigma_n=0$ on the right outflow edge, $\hat u=1$ on the leading edge
-of the wedge, and $\hat t=\bbeta\cdot\mathbf{n}\cdot 1$ on the trailing edge
-of the wedge.
-
-\begin{figure}[p]
-\centering
-\begin{subfigure}[t]{0.4\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Wedge/modified16nc.png}
-\includegraphics[width=\textwidth]{figs/Wedge/modified16nc_mesh.png}
-\caption{Nonconservative}
-\label{fig:wedgeGraph16nc}
-\end{subfigure}
-\begin{subfigure}[t]{0.4\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Wedge/modified16c.png}
-\includegraphics[width=\textwidth]{figs/Wedge/modified16c_mesh.png}
-\caption{Conservative}
-\label{fig:wedgeRobust16nc}
-\end{subfigure}
-\caption{Wedge problem after 16 refinements}
-\label{fig:wedge}
-\end{figure}
-
-\begin{figure}[p]
-\centering
-\includegraphics[width=0.8\textwidth]{figs/Wedge/modifiedFlux.pdf}
-\caption{Flux imbalance in wedge solutions}
-\label{fig:wedge_flux}
-\end{figure}
-
-\subsubsection{Inner Layer Problem}
-In this problem, $\bbeta=(\frac{\sqrt{3}}{2},\frac{1}{2})^T$ and we have a
-discontinuous flux inflow condition where $\hat t=0$ if $y\le0.2$ and $\hat
-t=\bbeta\cdot\mathbf{n}$ if $y>0.2$. On the outflow, $\hat u=0$. We use a very
-small diffusion scale of $\epsilon=10^{-6}$ which creates a very thin inner
-layer.
-% Nonconservative solution in range $[-0.38, 1.34]$.
-% Conservative solution in range $[-0.39, 1.38]$.
-
-\begin{figure}[p]
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/InnerLayer/modified8nc.png}
-\includegraphics[width=\textwidth]{figs/InnerLayer/modified8nc_mesh.png}
-\caption{Nonconservative}
-\label{fig:innerlayer8nc}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/InnerLayer/modified8c.png}
-\includegraphics[width=\textwidth]{figs/InnerLayer/modified8c_mesh.png}
-\caption{Conservative}
-\label{fig:innerlayer8c}
-\end{subfigure}
-\caption{Inner layer problem after 8 refinements}
-\label{fig:innerlayer}
-\end{figure}
-
-\begin{figure}[p]
-\centering
-\includegraphics[width=0.8\textwidth]{figs/InnerLayer/modifiedFlux.pdf}
-\caption{Flux imbalance in inner layer solutions}
-\label{fig:innerlayer_flux}
-\end{figure}
-
-\subsubsection{Discontinuous Source Problem}
-Here, $\bbeta=(0.5,1)^T/\sqrt{1.25}$, and we have a discontinuous source term
-such that $f=1$ when $y\ge2x$ and $f=-1$ when $y<2x$. We apply boundary
-conditions of $\hat t=0$ on the inflow and $\hat u=0$ on the outflow. Contrary
-to the other problems discussed, the solution for this problem does not range
-from 0 to one. Rather, the colorbar in Figure \ref{fig:discontinuous} is
-scaled to  $[-1.110,0.889]$.
-
-\begin{figure}[p]
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Discontinuous/graph8nc.png}
-\caption{Nonconservative}
-\label{fig:discontinuousModified8nc}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Discontinuous/robust8nc.png}
-\caption{Conservative}
-\label{fig:discontinuousModified8c}
-\end{subfigure}
-\caption{Discontinuous source problem after 8 refinements}
-\label{fig:discontinuous}
-\end{figure}
-
-\begin{figure}[p]
-\centering
-\includegraphics[width=0.8\textwidth]{figs/Discontinuous/modifiedFlux.pdf}
-\caption{Flux imbalance in discontinuous source solutions}
-\label{fig:discontinuous_flux}
-\end{figure}
-
-\subsubsection{Hemker Problem}
-The Hemker problem is defined on a domain
-$\Omega=\{[-3,9]\times[-3,3]\}\setminus\{(x,y):x^2+y^2<1\}$, essentially a simplified
-model of flow past an infinite cylinder. We start with the initial mesh shown
-in Figure~\ref{fig:hemkerInitial} in which we approximate the circle by 8
-fourth order curvilinear polynomial segments. As we refine, the new elements are
-fitted to better approximate an exact circle.The boundary conditions are $\hat
-t=\bbeta\cdot\mathbf{n}\cdot 1$ on the left inflow boundary,
-$\bbeta\cdot\mathbf{n}\cdot\hat u-\hat t=\sigma_n=0$ on the right outflow
-boundary, $\hat t=0$ on the top and bottom edges, and $\hat u=1$ on the
-cylinder.
-
-\begin{figure}[p]
-\centering
-\includegraphics[width=0.8\textwidth]{figs/Hemker/initial_mesh.png}
-\caption{Initial mesh for the Hemker problem}
-\label{fig:hemkerInitial}
-\end{figure}
-
-\begin{figure}[p]
-\centering
-\begin{subfigure}[t]{0.6\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Hemker/modified8nc.png}
-\end{subfigure}
-\begin{subfigure}[t]{0.6\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Hemker/modified8nc_mesh.png}
-\caption{Nonconservative}
-\label{fig:hemkerModified8nc}
-\end{subfigure}
-\begin{subfigure}[t]{0.6\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Hemker/modified8c.png}
-\end{subfigure}
-\begin{subfigure}[t]{0.6\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Hemker/modified8c_mesh.png}
-\caption{Conservative}
-\label{fig:hemkerModified8c}
-\end{subfigure}
-\caption{Hemker problem after 8 refinements}
-\label{fig:hemker8}
-\end{figure}
-
-\begin{figure}[p]
-\centering
-\centering
-\includegraphics[width=0.8\textwidth]{figs/Hemker/modifiedFlux.pdf}
-\caption{Flux imbalance in Hemker problem}
-\label{fig:hemkerFlux}
-\end{figure}
-
-\subsection{Analysis of Results}\label{sec:problemAnalysis}
-% Solution quality
-The general trend we see looking at the results is that the solution quality
-of the conservative and conconservative formulations is nearly identical. This
-is ideal, as we wish to preserve the attractive features of DPG --
-namely that it minimizes error in the energy norm. In particular, when we
-examine the error convergence plots for the Erickson-Johnson problem, the
-energy levels for the two methods lie nearly right on top of each other. This
-seems to indicate at the least that enforcing local conservation doesn't hurt
-DPG too much.
-
-% Overshoots/undershoots
-Another measure of solution quality is to look at the magnitude of overshoots
-and undershoots in the solution. In most of the problems considered (barring
-the discontinuous source problem) the exact solution would range exactly
-between 0 and 1. The the resolved solutions, the divergence from these values
-would be negligible, but for the inner layer, in which $\epsilon=10^{-6}$, we
-get overshoots and undershoots along the separation line. For the
-nonconservative formulation, the solution range for $u$ was $[-0.392,1.342]$,
-while the conservative solution range was $[0.389,1.378]$. This difference is
-easily accounted for by the differences in refinement patterns between the two
-methods.
-
-% Mesh refinements
-It is clear when comparing the refinement patterns that the two methods appear
-to calculate slightly different error representation functions (which
-determine which elements to adaptively refine). Standard DPG minimizes the
-error in the energy norm, but the Lagrange multipliers in the conservative
-formulation shift the solution slightly. So we should see somewhat higher
-error and different elements will get chosen for refinement. The choice of
-test norm also plays into this calculation of the error representation
-function. As discussed earlier, the conservative formulation allows us to
-throw away the $L^2$ term on $v$. The inclusion of this term required certain
-assumptions on $\bbeta$ \cite{ChanHeuerThanhDemkowicz2012} that break down for
-the vortex problem. Here we see the nonconservative method needlessly refine
-in the center of the domain where the solution is constant. The conservative
-scheme is more discerning about refinements and focuses refinements where
-solution features are changing. In general, though, both methods appear to
-follow very similar refinement patterns.
-
-% Mass conservation
-It shouldn't come as a surprise that the conservative and nonconservative
-solutions match each other so closely. The conservative formulation
-enforces local conservation more strictly, but if we examine the flux
-imbalance plots, the nonconservative formulation is nearly conservative on its
-own -- and appears to become more conservative with refinement. The flux
-imbalance of the conservative methods appears to bounce around close to the
-machine epsilon (plus a few orders of magnitude). The level of enforcement
-appears to creep up with more degrees of freedom, indicating possible
-accruement of numerical error.
+\subsection{Local Problem}
+The optimal test functions are determined by solving local problems determined
+by the choice of test norm. There are several options to consider.
+The graph norm \cite{DPGOverview} is one of the most natural norms to consider
+as it is derived directly from the adjoint of the problem supplemented with
+(possibly scaled) $L^2$ field terms to upgrade it from a semi-norm. 
+Chan \etal\cite{ChanHeuerThanhDemkowicz2012} derived a more robust alternative
+norm for convection diffusion (dubbed the robust norm). We recently
+developed a modification of the robust norm that appears to produce better
+results in the presence of singularities.
 
@@
 
+\subsubsection{Robust Norm}
+For illustrative purposes we choose the robust
+test norm developed by Chan \etal\cite{ChanHeuerThanhDemkowicz2012}. With this
+choice, we get our local problem:
+
+Find $\vdeltau\in\HOneK,\,\taudeltau\in\HdivK$ such that:
+\begin{align}
+(\nabla\cdot\taudeltau,&\nabla\cdot\delta\btau)_K
++\min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}(\taudeltau,\delta\btau)_K
++\epsilon(\nabla\vdeltau,\nabla \delta v)_K
++(\bbeta\cdot\nabla\vdeltau,\bbeta\cdot\nabla \delta v)_K\nonumber\\
+&+\alpha\min\left\{\sqrt{\frac{\epsilon}{|K|}},1\right\}(\vdeltau,\delta v)_K
+=b(\delta\bs u_h,(\delta v,\delta\btau))
+\quad\quad\forall\delta v\in\HOneK,\,\delta\btau\in\HdivK\,,
+\label{eq:localSolve}
+\end{align}
+where, typically, $\alpha=1$.
+
+We can decompose the discrete flux space $\hat F_h$ into element conserving
+fluxes and some algebraic complement:
+\begin{equation}
+\hat F_h=\hat F_h^c\oplus\hat F_h^{nc}\,,\quad\hat 
+F_h^{c}:=\{\hat t:\langle\hat t,(1_K,\bs0)\rangle=0\quad\forall K\}\,.
+\label{eq:decomposition}
+\end{equation}
+This may be accomplished by employing for fluxes in $\hat F_h^{c}$ traces of
+curls, $\nabla\times\phi$.
+
+In practice, we solve \eqref{eq:conservativeConfusionSystem} as a fully 
+coupled system of equations, but for didactic purposes, we can examine it 
+one piece at a time. If we restrict \eqref{eq:conservativeConfusionSystem}$_1$
+to $\delta\hat t\in\hat F_h^{nc}$, the Lagrange multiplier term drops out and we 
+left with a system that we can solve for $u_h$, $\bsigma_h$, $\hat u_h$, and 
+$\hat t_h^c\in\hat F^c_h$.
+
+Restricting ourselves to $\delta\hat t\in\hat
+F_h^{c}$ in \eqref{eq:conservativeConfusionSystem}$_1$, we obtain a system  of
+equations that can be solved for $u_h$, $\bsigma_h$, $\hat u$, and $\hat
+t\in\hat F_h^c$. The remaining fluxes, $\hat t\in\hat F_h^{nc}$ are determined
+from \eqref{eq:conservativeConfusionSystem}$_2$. Finally, testing with $\hat
+t\in\hat F_h^{nc}$ in \eqref{eq:conservativeConfusionSystem}$_1$, we obtain a
+system of equations that can be solved for Lagrange multipliers $\lambda_K$.
+
+Additionally, we can pass in local problem \eqref{eq:localSolve} with
+$\alpha\rightarrow0$. The fact that the test functions will be determined then
+up to a constant does not matter, for $\delta\hat t\in\hat F_h^c$, equation
+\eqref{eq:conservativeConfusionSystem}$_1$ is orthogonal to constants. 
+Mathematically, we are dealing with equivalence classes of functions, but in order 
+to obtain a single function that we can deal with numerically, we replace the alpha 
+term with a zero mean scaling condition to obtain the new test norm,
+\begin{align}
+(\nabla\cdot\taudeltau,&\nabla\cdot\delta\btau)_K
++\min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}(\taudeltau,\delta\btau)_K
+\nonumber\\
+&+\epsilon(\nabla\vdeltau,\nabla \delta v)_K
++(\bbeta\cdot\nabla\vdeltau,\bbeta\cdot\nabla \delta v)_K
++\frac{1}{|K|^2}\int_K\vdeltau\delta v\,,
+\label{eq:localSolveMod}
+\end{align}
+where the $\frac{1}{|K|^2}$ coefficient is needed to make the zero mean term 
+scale correctly with $h$. Numerically this helps a good deal with the condition
+numbers of the local solve.
+
+It is convenient to be able to take $\alpha\rightarrow0$ as we will see in
+some later numerical experiments.
+
+\section{Numerical Experiments}
+In \ref{sec:problemDescriptions} we define each numerical experiment, and in
+\ref{sec:problemAnalysis} we discuss the solution properties in general. We
+solve with second order field variables and flux ($u$, $\bsigma$, and $\hat
+t$), third order traces ($\hat t$), and fifth order test functions ($v$ and
+$\btau$).
+
+Describe how we check local conservation.
+
+\subsection{Description of Problems}\label{sec:problemDescriptions}
+Unless otherwise noted, the problem domain is $\Omega=[0,1]^2$ and $f=0$. Also
+note that except for the discontinuous source problem, blue corresponds to
+$u=0$ and red to $u=1$ with a linear scaling in between.
+
+\subsubsection{Erickson-Johnson Model Problem}
+The Erickson-Johnson problem is one of the few convection-diffusion problems
+with a known analytical solution. Take 
+$\bbeta=(1,0)^T$ and boundary conditions $\hat t=\bbeta\cdot\mathbf{n} u_0$ when
+$\beta_n\le0$, where $u_0$ is the trace of the exact solution, and $\hat u=0$
+when $\beta_n>0$. For
+$n=1,2,\cdots$, let
+$\lambda_n=n^2\pi^2\epsilon$,
+$r_n=\frac{1+\sqrt{1+4\epsilon\lambda_n}}{2\epsilon}$, and 
+$s_n=\frac{1-\sqrt{1+4\epsilon\lambda_n}}{2\epsilon}$. The exact solution
+is
+\begin{equation}
+u(x,y)=C_0+\sum_{n=1}^\infty C_n\frac{\exp(s_n(x-1))-\exp(r_n(x-1))}
+{r_n\exp(-s_n)-s_n\exp(-s_n)}\cos(n\pi y)\,.
+\label{eq:ericksonExact}
+\end{equation}
+Taking $\epsilon=10^{-2}$, $C_1=1$, and $C_{n\neq1}=0$, the exact solution looks
+like Figure \ref{fig:erickson}.
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=0.6\textwidth]{figs/Erickson/exact.png}
+\caption{Erickson-Johnson exact solution}
+\label{fig:erickson}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/Erickson/modifiedError.pdf}
+\caption{Error in Erickson-Johnson solutions}
+\label{fig:ericksonError}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/Erickson/graphFlux.pdf}
+\caption{Flux imbalance in Erickson-Johnson solutions}
+\label{ericksonFlux}
+\end{figure}
+
+\subsubsection{Skewed Convection-Diffusion Problem}
+This is a standard convection-diffusion problem with a skewed convection
+vector relative to the mesh. We take $\bbeta=(2,1)$, and on the left and
+bottom inflow boundaries we impose $\hat t=1-x-y$ while the right and top
+boundaries have $\hat u=0$. We solve for $\epsilon=10^{-4}$.
+
+\begin{figure}[p]
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Confusion/modified8nc.png}
+\includegraphics[width=\textwidth]{figs/Confusion/modified8nc_mesh.png}
+\caption{Nonconservative}
+\label{fig:confusionModified8nc}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Confusion/modified8c.png}
+\includegraphics[width=\textwidth]{figs/Confusion/modified8c_mesh.png}
+\caption{Conservative}
+\label{fig:confusionModified8c}
+\end{subfigure}
+\caption{Skewed convection-diffusion problem after 8 refinements}
+\label{fig:confusion}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/Confusion/modifiedFlux.pdf}
+\caption{Flux imbalance in skewed convection-diffusion solutions}
+\label{fig:confusionFlux}
+\end{figure}
+
+\subsubsection{Double Glazing Problem}
+This nominal problem definition takes the same unit square domain with 
+\[
+\bbeta=\binom{2(2y-1)(1-(2x-1)^2)}{-2(2x-1)(1-(2y-1)^2)}\,;\quad
+\hat u=
+\begin{cases}
+1 & \mbox{on }\Gamma_{right}\\
+0 & \mbox{else }
+\end{cases}\,,
+\]
+except that this definition for the boundary is not legal for $\hat u\in
+H^{\frac{1}{2}}(\Gamma_h)$ which is continuous. Therefore we use a ramp of
+width $\sqrt{\epsilon}$ on the right edge to go from 0 to 1. The 
+results are for $\epsilon=10^{-2}$.
+
+\begin{figure}[p]
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/DoubleGlazing/modified5nc.png}
+\caption{Nonconservative}
+\label{fig:doubleglazingGraph6c}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/DoubleGlazing/modified5c.png}
+\caption{Conservative}
+\label{fig:doubleglazingRobust6c}
+\end{subfigure}
+\caption{Double glazing problem after 5 refinements}
+\label{fig:doubleglazing}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/DoubleGlazing/modifiedFlux.pdf}
+\caption{Flux imbalance in double glazing problem}
+\label{fig:doubleglazingFlux}
+\end{figure}
+
+\subsubsection{Vortex Problem}
+This problem models a mildly diffusive vortex convecting fluid in a circle. We
+deal with domain $\Omega=[-1,1]^2$, with $\epsilon=10^{-4}$, and
+$\bbeta=(-y,x)^T$. Note that $\bbeta=\mathbf{0}$ at the domain center. We have an
+inflow boundary condition when $\bbeta\cdot\mathbf{n}<0$, in which case we set
+$\hat t=\bbeta\cdot\mathbf{n}\cdot u_0$ where
+$u_0=\frac{\sqrt{x^2+y^2}-1}{\sqrt{2}-1}$ which will vary from 0 at the center
+of boundary edges to 1 at corners. We don't enforce an outflow boundary.
+
+\begin{figure}[p]
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Vortex/modified6nc.png}
+\caption{Nonconservative}
+\label{fig:vortexModified6nc}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Vortex/modified6c.png}
+\caption{Conservative}
+\label{fig:vortexModified6c}
+\end{subfigure}
+\caption{Vortex problem after 6 refinements}
+\label{fig:vortex}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/Vortex/modifiedFlux.pdf}
+\caption{Flux imbalance in vortex solutions}
+\label{fig:vortex_flux}
+\end{figure}
+
+\subsubsection{Wedge Problem}
+We devised this problem to examine some of the issues we were having blow up
+of the solution under the robust test norm. The domain is a rectangle
+$[-0.5,0.5]\times[-1,0.5]$ where the triangle connecting the bottom edges with
+the origin at $(0,0)$ is removed. The convection vector $\bbeta=(1,0)^T$,
+$\epsilon=10^{-1}$, and we apply boundary conditions $\hat t=0$ on the left
+inflow edge, $\hat u=0$ on the top edge, $\bbeta\cdot\mathbf{n}\cdot\hat
+u-\hat t=\sigma_n=0$ on the right outflow edge, $\hat u=1$ on the leading edge
+of the wedge, and $\hat t=\bbeta\cdot\mathbf{n}\cdot 1$ on the trailing edge
+of the wedge.
+
+\begin{figure}[p]
+\centering
+\begin{subfigure}[t]{0.4\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Wedge/modified16nc.png}
+\includegraphics[width=\textwidth]{figs/Wedge/modified16nc_mesh.png}
+\caption{Nonconservative}
+\label{fig:wedgeGraph16nc}
+\end{subfigure}
+\begin{subfigure}[t]{0.4\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Wedge/modified16c.png}
+\includegraphics[width=\textwidth]{figs/Wedge/modified16c_mesh.png}
+\caption{Conservative}
+\label{fig:wedgeRobust16nc}
+\end{subfigure}
+\caption{Wedge problem after 16 refinements}
+\label{fig:wedge}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/Wedge/modifiedFlux.pdf}
+\caption{Flux imbalance in wedge solutions}
+\label{fig:wedge_flux}
+\end{figure}
+
+\subsubsection{Inner Layer Problem}
+In this problem, $\bbeta=(\frac{\sqrt{3}}{2},\frac{1}{2})^T$ and we have a
+discontinuous flux inflow condition where $\hat t=0$ if $y\le0.2$ and $\hat
+t=\bbeta\cdot\mathbf{n}$ if $y>0.2$. On the outflow, $\hat u=0$. We use a very
+small diffusion scale of $\epsilon=10^{-6}$ which creates a very thin inner
+layer.
+% Nonconservative solution in range $[-0.38, 1.34]$.
+% Conservative solution in range $[-0.39, 1.38]$.
+
+\begin{figure}[p]
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/InnerLayer/modified8nc.png}
+\includegraphics[width=\textwidth]{figs/InnerLayer/modified8nc_mesh.png}
+\caption{Nonconservative}
+\label{fig:innerlayer8nc}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/InnerLayer/modified8c.png}
+\includegraphics[width=\textwidth]{figs/InnerLayer/modified8c_mesh.png}
+\caption{Conservative}
+\label{fig:innerlayer8c}
+\end{subfigure}
+\caption{Inner layer problem after 8 refinements}
+\label{fig:innerlayer}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/InnerLayer/modifiedFlux.pdf}
+\caption{Flux imbalance in inner layer solutions}
+\label{fig:innerlayer_flux}
+\end{figure}
+
+\subsubsection{Discontinuous Source Problem}
+Here, $\bbeta=(0.5,1)^T/\sqrt{1.25}$, and we have a discontinuous source term
+such that $f=1$ when $y\ge2x$ and $f=-1$ when $y<2x$. We apply boundary
+conditions of $\hat t=0$ on the inflow and $\hat u=0$ on the outflow. Contrary
+to the other problems discussed, the solution for this problem does not range
+from 0 to one. Rather, the colorbar in Figure \ref{fig:discontinuous} is
+scaled to  $[-1.110,0.889]$.
+
+\begin{figure}[p]
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Discontinuous/graph8nc.png}
+\caption{Nonconservative}
+\label{fig:discontinuousModified8nc}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Discontinuous/robust8nc.png}
+\caption{Conservative}
+\label{fig:discontinuousModified8c}
+\end{subfigure}
+\caption{Discontinuous source problem after 8 refinements}
+\label{fig:discontinuous}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/Discontinuous/modifiedFlux.pdf}
+\caption{Flux imbalance in discontinuous source solutions}
+\label{fig:discontinuous_flux}
+\end{figure}
+
+\subsubsection{Hemker Problem}
+The Hemker problem is defined on a domain
+$\Omega=\{[-3,9]\times[-3,3]\}\setminus\{(x,y):x^2+y^2<1\}$, essentially a simplified
+model of flow past an infinite cylinder. We start with the initial mesh shown
+in Figure~\ref{fig:hemkerInitial} in which we approximate the circle by 8
+fourth order curvilinear polynomial segments. As we refine, the new elements are
+fitted to better approximate an exact circle.The boundary conditions are $\hat
+t=\bbeta\cdot\mathbf{n}\cdot 1$ on the left inflow boundary,
+$\bbeta\cdot\mathbf{n}\cdot\hat u-\hat t=\sigma_n=0$ on the right outflow
+boundary, $\hat t=0$ on the top and bottom edges, and $\hat u=1$ on the
+cylinder.
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/Hemker/initial_mesh.png}
+\caption{Initial mesh for the Hemker problem}
+\label{fig:hemkerInitial}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\begin{subfigure}[t]{0.6\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Hemker/modified8nc.png}
+\end{subfigure}
+\begin{subfigure}[t]{0.6\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Hemker/modified8nc_mesh.png}
+\caption{Nonconservative}
+\label{fig:hemkerModified8nc}
+\end{subfigure}
+\begin{subfigure}[t]{0.6\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Hemker/modified8c.png}
+\end{subfigure}
+\begin{subfigure}[t]{0.6\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Hemker/modified8c_mesh.png}
+\caption{Conservative}
+\label{fig:hemkerModified8c}
+\end{subfigure}
+\caption{Hemker problem after 8 refinements}
+\label{fig:hemker8}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\centering
+\includegraphics[width=0.8\textwidth]{figs/Hemker/modifiedFlux.pdf}
+\caption{Flux imbalance in Hemker problem}
+\label{fig:hemkerFlux}
+\end{figure}
+
+\subsection{Analysis of Results}\label{sec:problemAnalysis}
+% Solution quality
+The general trend we see looking at the results is that the solution quality
+of the conservative and conconservative formulations is nearly identical. This
+is ideal, as we wish to preserve the attractive features of DPG --
+namely that it minimizes error in the energy norm. In particular, when we
+examine the error convergence plots for the Erickson-Johnson problem, the
+energy levels for the two methods lie nearly right on top of each other. This
+seems to indicate at the least that enforcing local conservation doesn't hurt
+DPG too much.
+
+% Overshoots/undershoots
+Another measure of solution quality is to look at the magnitude of overshoots
+and undershoots in the solution. In most of the problems considered (barring
+the discontinuous source problem) the exact solution would range exactly
+between 0 and 1. The the resolved solutions, the divergence from these values
+would be negligible, but for the inner layer, in which $\epsilon=10^{-6}$, we
+get overshoots and undershoots along the separation line. For the
+nonconservative formulation, the solution range for $u$ was $[-0.392,1.342]$,
+while the conservative solution range was $[0.389,1.378]$. This difference is
+easily accounted for by the differences in refinement patterns between the two
+methods.
+
+% Mesh refinements
+It is clear when comparing the refinement patterns that the two methods appear
+to calculate slightly different error representation functions (which
+determine which elements to adaptively refine). Standard DPG minimizes the
+error in the energy norm, but the Lagrange multipliers in the conservative
+formulation shift the solution slightly. So we should see somewhat higher
+error and different elements will get chosen for refinement. The choice of
+test norm also plays into this calculation of the error representation
+function. As discussed earlier, the conservative formulation allows us to
+throw away the $L^2$ term on $v$. The inclusion of this term required certain
+assumptions on $\bbeta$ \cite{ChanHeuerThanhDemkowicz2012} that break down for
+the vortex problem. Here we see the nonconservative method needlessly refine
+in the center of the domain where the solution is constant. The conservative
+scheme is more discerning about refinements and focuses refinements where
+solution features are changing. In general, though, both methods appear to
+follow very similar refinement patterns.
+
+% Mass conservation
+It shouldn't come as a surprise that the conservative and nonconservative
+solutions match each other so closely. The conservative formulation
+enforces local conservation more strictly, but if we examine the flux
+imbalance plots, the nonconservative formulation is nearly conservative on its
+own -- and appears to become more conservative with refinement. The flux
+imbalance of the conservative methods appears to bounce around close to the
+machine epsilon (plus a few orders of magnitude). The level of enforcement
+appears to creep up with more degrees of freedom, indicating possible
+accruement of numerical error.
+
 \bibliographystyle{plain} 

### 2013-06-11 docs/Truman/LocalConservation/paper/paper.tex
Polished things up in local conservation paper.

@@
 \newcommand{\HdivK}{\bfH(\text{div},K)}
-\newcommand{\HOneK}{H^{-1}(K)}
+\newcommand{\HOneK}{H^{1}(K)}
 \newcommand{\HOneOmegah}{H^{-1}(\Omega_h)}
@@
 \begin{abstract}
+We develop a locally conservative formulation of the discontinuous
+Petrov-Galerkin finite element method (DPG) for convection-diffusion type
+problems using Lagrange multipliers to exactly enforce conservation over each
+element. We provide a proof of convergence as well as extensive numerical
+experiments showing that the method is indeed locally conservative. We also
+show that standard DPG, while not guaranteed to be conservative, is nearly
+conservative for the benchmarks considered. The new method preserves many of
+the attractive features of DPG, but turns the normally symmetric
+positive-difinite DPG system into a saddlepoint problem.
 \end{abstract}
@@
 least squares finite elements with a twist. The key difference is that least
-square methods seek to minimize the residual of the solution in the $L^2$
+squares methods seek to minimize the residual of the solution in the $L^2$
 norm, while DPG seeks the minimization in a dual norm realized through the
@@
 least squares finite elements for a long time. Several approaches have been
-used to try to adress this. Chang and Nelson\cite{ChangNelson1997} developed
-the \emph{restricted LSFEM}\cite{ChangNelson1997} by augmenting the least squares
+used to try to adress this. Bochev \etal\cite{Bochev2010} accomplish local
+conservation by using a pointwise divergence free velocity space in the Stokes
+formulation.  Chang and Nelson\cite{ChangNelson1997} developed the
+\emph{restricted LSFEM}\cite{ChangNelson1997} by augmenting the least squares
 equations with a Lagrange multiplier explicitly enforcing mass conservation
@@
 If we then multiply the top equation by some scalar test function $v$ and the
-bottom equation by some vector-valued test function $\tau$, we can integrate by
+bottom equation by some vector-valued test function $\btau$, we can integrate by
 parts over each element $K$:
@@
 
-\subsection{Proof of Convergence}
+\subsection{\textcolor{red}{Proof of Convergence}}
 We cannot directly use Brezzi's theorem, but we can reproduce his argument.
@@
 
-\subsection{Local Problem}
+\section{A coupled, robust test norm}
 The optimal test functions are determined by solving local problems determined
@@
 developed a modification of the robust norm that appears to produce better
-results in the presence of singularities.
-
-\section{A coupled, robust test norm}
-In the course of our numerical experiments, we encountered unforseen
-difficulties for certain problems under our current robust test norm.  We
-illustrate in this section the observed issue using a second model problem
-with a singular solution, offer possible explanations for the phenomena
-observed, and propose a modification of the robust test norm presented
-previously, which we demonstrate eliminates the issues observed in numerical
-experiments.
+results in the presence of singularities. In this section we illustrate the
+singularity issues with the Laplace equation, offer possible explanations for
+the phenomena observed, and propose a modification of the robust test norm,
+which we demonstrate eliminates the issues observed in numerical experiments.
 
@@
 \seclab{sec:confusionPlate}
-We begin by first examining a different problem than convection-diffusion --
-we examine admissible solutions for the homogeneous Laplace's equation over
+We begin by first examining a different problem than convection-diffusion.
+We look at admissible solutions for the homogeneous Laplace's equation over
 the $y > 0$ half-plane under boundary conditions 
@@
 \]
-where $\lambda_n = n + \frac{1}{2}$, and $R_n(r) = C_{1,n}x^{\lambda_n} + C_{2,n}x^{-\lambda_n}$.
-By requiring $u(0,\theta) < \infty$, we have $R_n(r) = C_n x^{\lambda_n}$.
-We have now that solutions to this problem include $u$ of the form
+where $\lambda_n = n + \frac{1}{2}$, and $R_n(r) = C_{1,n}x^{\lambda_n} +
+C_{2,n}x^{-\lambda_n}$.  By requiring $u(0,\theta) < \infty$, we have $R_n(r)
+= C_n x^{\lambda_n}$.  We have now that solutions to this problem include $u$
+of the form
 \[
@@
 Note that even in the lowest-order term, the gradient of $u$ displays a
-singularity at $r = 0$.  \textcolor{red}{Find reference in that solutions to
-Laplace's equation always can be split into smooth and singular parts on
-similar domains.}
+singularity at $r = 0$. It is well known that, for smooth boundary data,
+solutions to Laplace’s equation can be decomposed into the linear combination
+of smooth and singular contributions; the above analysis implies that, when
+boundary conditions change from Dirichlet to Neumann on the half-plane, the
+Laplace’s equation will always develop a singularity in the stresses.
 
@@
 \includegraphics[scale=.275]{figs/LaplaceFigs/LaplacePlateSigma2.png}
-\caption{$x$ and $y$ components of the $\Grad u$ for $u$ solving Laplace's equation with a change in boundary conditions.
-Both components develop singularities at the point where the boundary condition changes type.}
+\caption{$x$ and $y$ components of the $\Grad u$ for $u$ solving Laplace's
+equation with a change in boundary conditions.  Both components develop
+singularities at the point where the boundary condition changes type.}
 \label{fig:laplaceStresses}
@@
 \includegraphics[scale=.275]{figs/LaplaceFigs/confusion1e2h1e3.png}
-\caption{Solution $u$ for $\epsilon = .01$ under the robust test norm.
-The solution oscillates strongly at the plate edge, growing in magnitude under additional refinements despite the absence of a singularity in $u$ at that point.}
+\caption{Solution $u$ for $\epsilon = .01$ under the robust test norm.  The
+solution oscillates strongly at the plate edge, growing in magnitude under
+additional refinements despite the absence of a singularity in $u$ at that
+point.}
 \label{fig:plateOsc}
@@
 $x^{-\frac{1}{2}}$).  Apart from the oscillation of $u$ at the singular point,
-the solution is well-behaved, and the stress $\sigma = \epsilon \Grad u$ is
+the solution is well-behaved, and the stress $\bsigma = \epsilon \Grad u$ is
 very well represented, as indicated in Figure~\ref{fig:plateStresses}.
@@
 While oscillations of this sort in a solution near a singular point may be
-acceptable in certain simulations, it is a large problem for the methods in
+acceptable in certain simulations, it is a big problem for the methods in
 compressible flow simulations -- physical constraints require several solution
@@
 modification of the robust test norm that appears to remedy this issue, which
-we refer to as 
-\[
-\norm{\LRp{v,\tau}}_V^2 \coloneqq \norm{v}^2_{\L} + \norm{\beta\cdot \Grad v}_{\L}^2 + \norm{\div \tau - \beta\cdot\Grad v}_{\L}^2 + \norm{C_\tau\tau}_{\L}^2,
-\]
-where $C_\tau$ is defined as before.
-\footnote{
+we refer to as the coupled robust test norm:
+\begin{align}
+\norm{\LRp{v,\btau}}_{V,K}^2 &\coloneqq 
+\min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\norm{\btau}_K^2,
++ \norm{\div \btau - \bbeta\cdot\Grad v}_K^2 \\
+&+\norm{\bbeta\cdot \Grad v}_K^2 
++ \epsilon\norm{\Grad v}_K^2 
++ \norm{v}^2_K
+\end{align}
+where $||\cdot||_K$ signifies the $L^2$ norm over element $K$.\footnote{
 We note that we have dropped the
 mesh-dependent scaling on $\norm{v}_{\L}$ from the robust norm; this is related
-to recent insights into the nature of DPG test spaces and explained in more
-detail in %Appendix~\secref{appendix:globalLocal}.
+to recent insights into the nature of DPG test spaces as discussed in
+\cite{Chan2013}.
 }  
 We note that, under the
-theory developed in 
-% Section~\secref{sec:testNormSec}, 
+theory developed in \cite{ChanHeuerThanhDemkowicz2012}
 the above test norm is
-trivially provably robust using the same theory.
-\footnote{This is due to the
-fact that $\norm{\div \tau - \beta\cdot\Grad v}_{\L}^2$ is robustly bounded by
-$\norm{\div \tau}_{\L}$ and $\norm{\beta\cdot\Grad v}_{\L}$.  Alternatively, we
-can note that $\norm{\div \tau - \beta\cdot\Grad v}_{\L}^2 = \norm{g}_{\L}^2$,
+trivially provably robust using the same ideas.\footnote{This is due to the
+fact that $\norm{\div \btau - \bbeta\cdot\Grad v}_{\L}^2$ is robustly bounded by
+$\norm{\div \btau}_{\L}$ and $\norm{\bbeta\cdot\Grad v}_{\L}$.  Alternatively, we
+can note that $\norm{\div \btau - \bbeta\cdot\Grad v}_{\L}^2 = \norm{g}_{\L}^2$,
 where $g$ is a load of the adjoint problem related to robustness described in
-% Section~\secref{sec:testNormSec}.
+\cite{ChanHeuerThanhDemkowicz2012}.
 }
 
-While not rigorously understood, the author believes the issues related to the
+While not rigorously understood, we believe the issues related to the
 appearance of non-physical singularities to be related to the uncoupled nature
 of the test norm.  Previous example problems exhibited boundary layers and
-sharp gradients in the stress $\sigma$, but not singularities, which
+sharp gradients in the stress $\bsigma$, but not singularities, which
 contribute significantly more error.  We expect that the oscillations observed
 in $u$ are a sort of \textit{pollution error}, where error in $u$ is tied to
-error in $\sigma$.  If we consider the ultra-weak variational formulation for
+error in $\bsigma$.  If we consider the ultra-weak variational formulation for
 convection-diffusion
 \[
-\LRp{u,\div \tau - \beta\cdot \grad v}_{\L} + \LRp{\sigma,\frac{1}{\epsilon} \tau + \grad v}_{\L} + \ldots,
+\LRp{u,\div \btau - \bbeta\cdot \grad v}_{\L} + \LRp{\bsigma,\frac{1}{\epsilon}
+\btau + \grad v}_{\L} + \ldots,
 \]
 we can see that it is a combination of test functions that corresponds to both
-$u$ and $\sigma$.  Recall from the previous section that, by choosing $\tau$
+$u$ and $\bsigma$.  Referring to \cite{ChanHeuerThanhDemkowicz2012}, we note
+that, by choosing $\btau$
 and $v$ such that they satisfy the adjoint equation with forcing terms $u$ and
-$\sigma$, we recover the best $L^2$ approximation.  In other words, achieving
-optimality in the $L^2$ norm requires coupling between $v$ and $\tau$, which
+$\bsigma$, we recover the best $L^2$ approximation.  In other words, achieving
+optimality in the $L^2$ norm requires coupling between $v$ and $\btau$, which
 is achieved under the graph norm, but not the robust norm derived in the
-previous section.  If coupling of the test terms , we expect that decoupling
-$v$ and $\tau$ from each other in a test norm from each other will have the
-effect of coupling error in $\sigma$ to error in $u$, which would explain the
-spurious oscillations in $u$ in the presence of singularities in $\sigma$.
+previous section.  
+If coupling of the test terms delivers optimality in $u$ and $\bsigma$
+independently, we expect that decoupling
+$v$ and $\btau$ from each other in a test norm will have the
+effect of coupling error in $\bsigma$ to error in $u$, which would explain the
+spurious oscillations in $u$ in the presence of singularities in $\bsigma$.
 Similar results have been observed in the Stokes equations, where error in $u$
@@
 The drawback to using the above test norm is that the resulting local system
-for test functions is now completely coupled, whereas using the previous test
-norm, the system was block diagonal due to the decoupling in $v$ and $\tau$
+for test functions is now completely coupled, whereas using the robust test
+norm, the system was block diagonal due to the decoupling in $v$ and $\btau$
 and could be constructed and inverted more efficiently.  We hope to explore
@@
 diffusion scale is both underresolved and resolved by $h$-adaptivity.  In both
-cases, there are no additional oscillations near the plate tip --
+cases, there are no oscillations near the plate tip --
 Figure~\ref{fig:newNormZoom} shows a zoomed image of the solution $u$ at the
@@
 that the new test norm removes spurious oscillations in $u$ (in the presence
-of singularities in $\sigma$) independently of $\epsilon$.
+of singularities in $\bsigma$) independently of $\epsilon$.
 
@@
 
-\subsubsection{Robust Norm}
-For illustrative purposes we choose the robust
-test norm developed by Chan \etal\cite{ChanHeuerThanhDemkowicz2012}. With this
-choice, we get our local problem:
+\subsection{Adaptation for a Locally Conservative Formulation}
+With this choice of test norm, our local problem now becomes:
 
@@
 \begin{align}
-(\nabla\cdot\taudeltau,&\nabla\cdot\delta\btau)_K
-+\min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}(\taudeltau,\delta\btau)_K
-+\epsilon(\nabla\vdeltau,\nabla \delta v)_K
+\min&\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}(\taudeltau,\delta\btau)_K
++(\nabla\cdot\taudeltau-\bbeta\cdot\nabla
+v,\nabla\cdot\delta\btau-\bbeta\cdot\nabla v)_K
 +(\bbeta\cdot\nabla\vdeltau,\bbeta\cdot\nabla \delta v)_K\nonumber\\
-&+\alpha\min\left\{\sqrt{\frac{\epsilon}{|K|}},1\right\}(\vdeltau,\delta v)_K
+&+\epsilon(\nabla\vdeltau,\nabla \delta v)_K
++\alpha(\vdeltau,\delta v)_K
 =b(\delta\bs u_h,(\delta v,\delta\btau))
@@
 
+\textcolor{red}{
 In practice, we solve \eqref{eq:conservativeConfusionSystem} as a fully 
@@
 $\hat t_h^c\in\hat F^c_h$.
-
+}
+
+\textcolor{red}{
 Restricting ourselves to $\delta\hat t\in\hat
@@
 system of equations that can be solved for Lagrange multipliers $\lambda_K$.
+}
 
@@
 \begin{align}
-(\nabla\cdot\taudeltau,&\nabla\cdot\delta\btau)_K
-+\min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}(\taudeltau,\delta\btau)_K
-\nonumber\\
-&+\epsilon(\nabla\vdeltau,\nabla \delta v)_K
-+(\bbeta\cdot\nabla\vdeltau,\bbeta\cdot\nabla \delta v)_K
-+\frac{1}{|K|^2}\int_K\vdeltau\delta v\,,
+\min&\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}(\taudeltau,\delta\btau)_K
++(\nabla\cdot\taudeltau-\bbeta\cdot\nabla
+v,\nabla\cdot\delta\btau-\bbeta\cdot\nabla v)_K\\
+&+(\bbeta\cdot\nabla\vdeltau,\bbeta\cdot\nabla \delta v)_K\nonumber
++\epsilon(\nabla\vdeltau,\nabla \delta v)_K
++\frac{1}{|K|}\int_K\vdeltau\int_K\delta v
 \label{eq:localSolveMod}
 \end{align}
+% \begin{align}
+% (\nabla\cdot\taudeltau,&\nabla\cdot\delta\btau)_K
+% +\min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}(\taudeltau,\delta\btau)_K
+% \nonumber\\
+% &+\epsilon(\nabla\vdeltau,\nabla \delta v)_K
+% +(\bbeta\cdot\nabla\vdeltau,\bbeta\cdot\nabla \delta v)_K
+% +\frac{1}{|K|^2}\int_K\vdeltau\delta v\,,
+% \label{eq:localSolveMod}
+% \end{align}
 where the $\frac{1}{|K|^2}$ coefficient is needed to make the zero mean term 
-scale correctly with $h$. Numerically this helps a good deal with the condition
+scale correctly with $h$. Numerically this helps with the condition
 numbers of the local solve.
-
 It is convenient to be able to take $\alpha\rightarrow0$ as we will see in
@@
 
-Describe how we check local conservation.
+We measure flux imbalance by looping over each element in the mesh and
+integrating the flux over each side and summing them together. We then
+integrate the source term over the volume of the element. The two should match
+each other, and the remainder is the flux imbalance. We get the net global
+flux imbalance by summing these quantities and taking the absolute value. The
+max local flux imbalance is the maximum absolute value of these flux
+imbalances.
 
@@
 Unless otherwise noted, the problem domain is $\Omega=[0,1]^2$ and $f=0$. Also
-note that except for the discontinuous source problem, blue corresponds to
-$u=0$ and red to $u=1$ with a linear scaling in between.
+note that except for the discontinuous source problem, for all of the
+pseudo-color plots, blue corresponds to $0$ and red to $1$ with a linear
+scaling in between. Also, all plots are of the field variable $u$.
 
@@
 
-\begin{figure}[p]
+\begin{figure}[h!]
 \centering
@@
 \centering
+\centering
+\includegraphics[width=0.8\textwidth]{figs/Hemker/modifiedFlux.pdf}
+\caption{Flux imbalance in Hemker problem}
+\label{fig:hemkerFlux}
+\end{figure}
+
+\begin{figure}[p]
+\centering
 \begin{subfigure}[t]{0.6\textwidth}
@@
 
-\begin{figure}[p]
-\centering
-\centering
-\includegraphics[width=0.8\textwidth]{figs/Hemker/modifiedFlux.pdf}
-\caption{Flux imbalance in Hemker problem}
-\label{fig:hemkerFlux}
-\end{figure}
-
 \subsection{Analysis of Results}\label{sec:problemAnalysis}
@@
 The general trend we see looking at the results is that the solution quality
-of the conservative and conconservative formulations is nearly identical. This
+of the conservative and nonconservative formulations is nearly identical. This
 is ideal, as we wish to preserve the attractive features of DPG --
@@
 the discontinuous source problem) the exact solution would range exactly
-between 0 and 1. The the resolved solutions, the divergence from these values
+between 0 and 1. In the resolved solutions, the divergence from these values
 would be negligible, but for the inner layer, in which $\epsilon=10^{-6}$, we
@@
 assumptions on $\bbeta$ \cite{ChanHeuerThanhDemkowicz2012} that break down for
-the vortex problem. Here we see the nonconservative method needlessly refine
+the vortex problem. Here we see the nonconservative method needlessly refines
 in the center of the domain where the solution is constant. The conservative
-scheme is more discerning about refinements and focuses refinements where
+scheme is more discerning about refinements and focuses them where
 solution features are changing. In general, though, both methods appear to
@@
 enforces local conservation more strictly, but if we examine the flux
-imbalance plots, the nonconservative formulation is nearly conservative on its
+imbalance plots, the standard DPG formulation is nearly conservative on its
 own -- and appears to become more conservative with refinement. The flux
@@
 
+\section{Conclusions}
+We've developed a locally conservative formulation of DPG by leveraging
+Lagrange multipliers. While the formulation is provably convergent, it does
+increase the number of unkowns in the system and changes the structure from
+symmetric positive-definite to a saddlepoint problem. Numerical results
+indicate that the method delivers what it promises with local flux imbalances
+hovering close to machine precision, but they also indicate that for the
+problems considered, standard DPG is close to conservative and becomes more so
+with refinements. Probably the most encouraging result of these experiments is
+that enforcing local conservation did not change the nature of the solutions
+too significantly. Standard DPG has a lot of attractive features, and we wish
+to preserve thoes.
+
+Mass conservation is probably the foremost issue facing the class of Least
+Squares Finite Element Methods. And there are several benchmark problems in the
+literature where these methods have performed very poorly, particularly Stokes
+flow over a cylinder and the backward facing step problem. Extending our locally
+conservative formulation of DPG to these kinds of problems should be
+relatively straightforward. The real test of whether local conservation is
+worth it for DPG will come when we start doing more realistic problems.
+
 \bibliographystyle{plain} 

### 2013-06-12 docs/Truman/LocalConservation/paper/paper.tex
Fixed some ordering in local conservation paper.

@@
 acoustics \cite{DemkowiczGopalakrishnanMugaZitelli12}, Stokes
-\cite{DPGStokes})
-associate DPG with the so-called ``ultra-weak formulation.'' We will follow
-the same derivation for the convection-diffusion equation, but we emphasize
-that other formulations are available. Thus, we seek field variables $u\in
-L^2(K)$ and $\bsigma\in\mb{L^2}(K)$. Mathematically, this leaves their traces
-on element boundaries undefined, and in a manner similar to the hybridized
-discontinuous Galerkin method, we define new unknowns for trace $\hat u$ and
-flux $\hat t$.  Applying these definitions to \eqnref{preultraweak} and adding
-the two equations together, we arrive at our desired variational problem.
+\cite{DPGStokes}) associate DPG with the so-called ``ultra-weak formulation.''
+We will follow the same derivation for the convection-diffusion equation, but
+we emphasize that other formulations are available (in particular, the
+Primal DPG\cite{PrimalDPG} method presents an alternative with
+continuous test functions). Thus, we seek field variables $u\in L^2(K)$ and
+$\bsigma\in\mb{L^2}(K)$. Mathematically, this leaves their traces on element
+boundaries undefined, and in a manner similar to the hybridized discontinuous
+Galerkin method, we define new unknowns for trace $\hat u$ and flux $\hat t$.
+Applying these definitions to \eqnref{preultraweak} and adding the two
+equations together, we arrive at our desired variational problem.
 
@@
 &=\underbrace{\:(f,v)_K\genfrac{}{}{0pt}{}{}{}}_{l(\mathbf{v})} &\text{in }\Omega \\
-u&=0 &\text{on }\Gamma\\
+u&=0 &\text{on }\Gamma
 \end{align}
@@
 
+We can decompose the discrete flux space $\hat F_h$ into equilibriated fluxes
+(zero net flux over each element) and some algebraic complement:
+\begin{equation}
+\hat F_h=\hat F_h^e\oplus\hat F_h^{ne}\,,\quad\hat 
+F_h^{e}:=\{\hat t:\langle\hat t,(1_K,\bs0)\rangle=0\quad\forall K\}\,.
+\label{eq:decomposition}
+\end{equation}
+In theory, we could accomplish this by employing for fluxes in $\hat F_h^{e}$
+traces of curls, $\nabla\times\phi$, but we don't do this in practice.
+
+\textcolor{red}{
+In practice, we solve \eqref{eq:conservativeConfusionSystem} as a fully
+coupled system of equations, but for didactic purposes, we can examine it one
+piece at a time. If we restrict \eqref{eq:conservativeConfusionSystem}$_1$ to
+$\delta\hat t\in\hat F_h^{ne}$, the Lagrange multiplier term drops out and we
+are left with a system that we can solve for $u_h$, $\bsigma_h$, $\hat u_h$,
+and $\hat t_h^e\in\hat F^e_h$.
+}
+
+\textcolor{red}{
+Restricting ourselves to $\delta\hat t\in\hat
+F_h^{e}$ in \eqref{eq:conservativeConfusionSystem}$_1$, we obtain a system  of
+equations that can be solved for $u_h$, $\bsigma_h$, $\hat u$, and $\hat
+t\in\hat F_h^e$. The remaining fluxes, $\hat t\in\hat F_h^{ne}$ are determined
+from \eqref{eq:conservativeConfusionSystem}$_2$. Finally, testing with $\hat
+t\in\hat F_h^{ne}$ in \eqref{eq:conservativeConfusionSystem}$_1$, we obtain a
+system of equations that can be solved for Lagrange multipliers $\lambda_K$.
+}
+
 \subsection{\textcolor{red}{Proof of Convergence}}
+In the following discussion, we do not account for the error in approximating
+the optimal test functions because $\dots$ (Need explanation).
 We cannot directly use Brezzi's theorem, but we can reproduce his argument.
@@
 
-Restricting ourselves to $\delta\hat t_h\in\hat F_h^c$, and subtracting
+Restricting ourselves to $\delta\hat t_h\in\hat F_h^e$, and subtracting
 \eqref{eq:bilinearForm} from \eqref{eq:conservativeConfusionSystem}, we have
@@
 &\hspace{25ex}\forall(\delta u_h,\delta\bsigma_h,\delta\hat u_h,\delta\hat t_h)
-\in U_h\times\bs S_h\times\hat U_h\times\hat F_h^c\,.
+\in U_h\times\bs S_h\times\hat U_h\times\hat F_h^e\,.
 \nonumber
@@
 (\delta u_h,\delta\bsigma_h,\delta\hat u,\delta\hat t)\in}
-{U_h\times\bs S_h\times\hat U_h\times\hat F_h^c}
+{U_h\times\bs S_h\times\hat U_h\times\hat F_h^e}
 }
@@
 \forall(u_h,\bsigma_h,\hat u_h,\hat t_h)
-\in U_h\times\bs S_h\times\hat U_h\times\hat F_h^c\,.
+\in U_h\times\bs S_h\times\hat U_h\times\hat F_h^e\,.
 \label{eq:infsup}
@@
 \begin{equation}
-\hat t_h=\hat t_h^{c}+\hat t_h^{nc}\,.
+\hat t_h=\hat t_h^{e}+\hat t_h^{ne}\,.
 \label{eq:fluxdecomposition}
@@
 \norm{(u-u_h,\bsigma-\bsigma_h,\hat u-\hat u_h, \hat t-\hat t_h)}&=
-\norm{(u-u_h,\bsigma-\bsigma_h,\hat u-\hat u_h, \hat t-(\hat t_h^c+\hat t_h^{nc}))}\nonumber\\
-&\le\norm{(u-w_h,\bsigma-\bs s_h,\hat u-\hat w_h, \hat t-(\hat r_h^c+\hat t_h^{nc}))}\\
-&\hspace{3ex}+\norm{(w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h, \hat r_h^c-\hat t_h^c)}\nonumber
+\norm{(u-u_h,\bsigma-\bsigma_h,\hat u-\hat u_h, \hat t-(\hat t_h^e+\hat t_h^{ne}))}\nonumber\\
+&\le\norm{(u-w_h,\bsigma-\bs s_h,\hat u-\hat w_h, \hat t-(\hat r_h^e+\hat t_h^{ne}))}\\
+&\hspace{3ex}+\norm{(w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h, \hat r_h^e-\hat t_h^e)}\nonumber
 \end{align}
 where $w_h\in U_h$, $\bs s_h\in\bs S_h$, $\hat w_h\in\hat U_h$, and $\hat
-r_h^{c}\in\hat F_h$ are arbitrary. The inf-sup in kernel condition now
+r_h^{e}\in\hat F_h$ are arbitrary. The inf-sup in kernel condition now
 implies:
@@
 \label{eq:estimate}
-&\norm{(w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h, \hat r_h^c-\hat t_h^c)}\\
+&\norm{(w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h, \hat r_h^e-\hat t_h^e)}\\
 &\hspace{8ex}\le\frac{1}{\alpha}
@@
 (\delta u_h,\delta\bsigma_h,\delta\hat u,\delta\hat t)\in}
-{U_h\times\bs S_h\times\hat U_h\times\hat F_h^c}
+{U_h\times\bs S_h\times\hat U_h\times\hat F_h^e}
 }
 \frac{\snorm{
-b( (w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h,\hat r_h^c-\hat t_h^c),
+b( (w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h,\hat r_h^e-\hat t_h^e),
 (\vdeltau,\taudeltau))
@@
 (\delta u_h,\delta\bsigma_h,\delta\hat u,\delta\hat t)\in}
-{U_h\times\bs S_h\times\hat U_h\times\hat F_h^c}
+{U_h\times\bs S_h\times\hat U_h\times\hat F_h^e}
 }
 \frac{\snorm{
-b( (w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h,\hat r_h^c+\hat t_h^{nc}-\hat t),
+b( (w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h,\hat r_h^e+\hat t_h^{ne}-\hat t),
 (\vdeltau,\taudeltau))
@@
 &\hspace{8ex}\le\frac{1}{\alpha}
-\norm{(w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h,\hat t-(\hat r_h^c+\hat
-t_h^{nc}))}
+\norm{(w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h,\hat t-(\hat r_h^e+\hat
+t_h^{ne}))}
 \end{align}
@@
 % -(\bbeta (w_h-u_h)-(\bs s_h-\bsigma_h),\nabla\vdeltau)
-% +\langle\hat r_h^c-\hat t_h^c,\vdeltau\rangle
+% +\langle\hat r_h^e-\hat t_h^e,\vdeltau\rangle
 where the second step follows from the Galerkin orthogonality condition
 \eqref{eq:galerkinOrthogonality}, and the last step is a consequence of the
-minimum energy extension norm for fluxes. Cobining with \eqref{eq:triangle},
+minimum energy extension norm for fluxes. Combining with \eqref{eq:triangle},
 we get the final stability result:
@@
 \inf_{\stackrel{
-(w_h,\bs s_h,\hat w,\hat r_h^c)\in}
-{U_h\times\bs S_h\times\hat U_h\times\hat F_h^c}
+(w_h,\bs s_h,\hat w,\hat r_h^e)\in}
+{U_h\times\bs S_h\times\hat U_h\times\hat F_h^e}
 }
-\norm{(u-w_h,\bsigma-\bs s_h,\hat u-\hat w,\hat t-(\hat r_h^c+\hat t_h^{nc}))}
+\norm{(u-w_h,\bsigma-\bs s_h,\hat u-\hat w,\hat t-(\hat r_h^e+\hat t_h^{ne}))}
 \,.
@@
 
-We can decompose the discrete flux space $\hat F_h$ into element conserving
-fluxes and some algebraic complement:
-\begin{equation}
-\hat F_h=\hat F_h^c\oplus\hat F_h^{nc}\,,\quad\hat 
-F_h^{c}:=\{\hat t:\langle\hat t,(1_K,\bs0)\rangle=0\quad\forall K\}\,.
-\label{eq:decomposition}
-\end{equation}
-This may be accomplished by employing for fluxes in $\hat F_h^{c}$ traces of
-curls, $\nabla\times\phi$.
-
-\textcolor{red}{
-In practice, we solve \eqref{eq:conservativeConfusionSystem} as a fully 
-coupled system of equations, but for didactic purposes, we can examine it 
-one piece at a time. If we restrict \eqref{eq:conservativeConfusionSystem}$_1$
-to $\delta\hat t\in\hat F_h^{nc}$, the Lagrange multiplier term drops out and we 
-left with a system that we can solve for $u_h$, $\bsigma_h$, $\hat u_h$, and 
-$\hat t_h^c\in\hat F^c_h$.
-}
-
-\textcolor{red}{
-Restricting ourselves to $\delta\hat t\in\hat
-F_h^{c}$ in \eqref{eq:conservativeConfusionSystem}$_1$, we obtain a system  of
-equations that can be solved for $u_h$, $\bsigma_h$, $\hat u$, and $\hat
-t\in\hat F_h^c$. The remaining fluxes, $\hat t\in\hat F_h^{nc}$ are determined
-from \eqref{eq:conservativeConfusionSystem}$_2$. Finally, testing with $\hat
-t\in\hat F_h^{nc}$ in \eqref{eq:conservativeConfusionSystem}$_1$, we obtain a
-system of equations that can be solved for Lagrange multipliers $\lambda_K$.
-}
-
-Additionally, we can pass in local problem \eqref{eq:localSolve} with
-$\alpha\rightarrow0$. The fact that the test functions will be determined then
-up to a constant does not matter, for $\delta\hat t\in\hat F_h^c$, equation
+With a locally conservative formulation, we can pass in local problem
+\eqref{eq:localSolve} with $\alpha\rightarrow0$. The fact that the test
+functions will be determined then up to a constant does not matter, for
+$\delta\hat t\in\hat F_h^e$, equation
 \eqref{eq:conservativeConfusionSystem}$_1$ is orthogonal to constants.
-Mathematically, we are dealing with equivalence classes of functions, but in order 
-to obtain a single function that we can deal with numerically, we replace the alpha 
-term with a zero mean scaling condition to obtain the new test norm,
+Mathematically, we are dealing with equivalence classes of functions, but in
+order to obtain a single function that we can deal with numerically, we
+replace the alpha term with a zero mean scaling condition to obtain the new
+test norm,
 \begin{align}
@@
 \end{align}
-% \begin{align}
-% (\nabla\cdot\taudeltau,&\nabla\cdot\delta\btau)_K
-% +\min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}(\taudeltau,\delta\btau)_K
-% \nonumber\\
-% &+\epsilon(\nabla\vdeltau,\nabla \delta v)_K
-% +(\bbeta\cdot\nabla\vdeltau,\bbeta\cdot\nabla \delta v)_K
-% +\frac{1}{|K|^2}\int_K\vdeltau\delta v\,,
-% \label{eq:localSolveMod}
-% \end{align}
 where the $\frac{1}{|K|^2}$ coefficient is needed to make the zero mean term 
@@
 in Figure~\ref{fig:hemkerInitial} in which we approximate the circle by 8
-fourth order curvilinear polynomial segments. As we refine, the new elements are
+fifth order curvilinear polynomial segments. As we refine, the new elements are
 fitted to better approximate an exact circle.The boundary conditions are $\hat

### 2013-07-22 docs/Jesse/HeuerPaper/responseForReviewers3.tex
updating Heuer paper docs

--- 2013-05-01 docs/Jesse/HeuerPaper/responseForReviewers2.tex
@@
 
-The authors are very grateful for the feedback, comments and suggestions provided by both reviewers in this revision.  Please accept the attached second revised version of our paper.
+The authors are very grateful for the feedback, comment and suggestion provided by reviewer 2 in this revision.  Please accept the attached third revised version of our paper.
 
@@
 \begin{enumerate}
-\item \textcolor{red}{p.
-4, footnote: given that the authors are in a Hilbert space setting, the authors probably mean $\nor{v}_{V(\Oh)}^2 = \sum_{K\in \Oh} \nor{v}_{V(K)}^2$.}  Corrected -- the authors thank the reviewer for noting this.
-\item \textcolor{red}{Section 1.3: the claim about the relation between the norms $\nor{\cdot}_U$ and $\nor{\cdot}_{V,U}$ is not completely clear to the referee--the authors are encouraged to add a few clarifying words:}
-\begin{enumerate}
-\item \textcolor{red}{please give a precise reference to a theorem in [5].} Clarified.  The theorem is specified to be Lemma 2.5 in \cite{Bui-ThanhDemkowiczGhattas11a}.  
-\item \textcolor{red}{please be more specific as to what ``definite" means for the bilinear form.} Clarified.  We have added a footnote clarifying the ``definiteness" of the bilinear form as meaning 
-\[
-b(u,v) = 0, \forall v\in V \Rightarrow u = 0
-\]
-and
-\[
-b(u,v)=0, \forall u\in U \Rightarrow v = 0,
-\]
- which imply injectivity of the bilinear operator $B$ and its transpose $B'$, defined such that $\LRa{Bu,v} = \LRa{u,B'v}.$  These conditions in turn guarantee (through the Banach closed range theorem) solvability of the variational problem.
-\item \textcolor{red}{the discussion in Section $1.3$ suggests that for any norm $\nor{\cdot}_U$ one has an induced norm $\nor{\cdot}_{V,U}$ on $V$ .
-The referee doesn't see this.
-For example, taking $U = V = H_0^1(\Omega)$ and $b(u, v) \coloneqq \LRp{\grad u,\grad v}_{L^2(\Omega)}$ but equipping $U$ with $\nor{\cdot}_U \coloneqq \nor{\cdot}_{L^2(\Omega)}$ does not lead to a norm on $V$ via $\nor{\cdot}_{V,U}$ , since for smooth $v$ one obtains $\nor{v}_{V,U} = \nor{\del v}_{L^2(\Omega)}$.}
-\begin{enumerate}
-\item At a very broad level, from Lemma 2.5 in \cite{Bui-ThanhDemkowiczGhattas11a}, the duality between trial and test norms is a consequence of $M/\gamma = 1$, where $M$ is the continuity constant such that $b(u,v)\leq M \nor{u}_U\nor{v}_V$, and $\gamma$ is the inf-sup/boundedness below constant such that
-\[
-0<\gamma \leq \inf_{u\in U}\sup_{v\in V}\frac{b(u,v)}{\nor{u}_U\nor{v}_V}.
-\]
-If the problem is posed such that $U = H_0^1$ but $\nor{\cdot}_U = \nor{\cdot}_{\L}$, then this problem is ill-posed and we no longer have duality between trial and test norms.
-
-\item The reason for the loss of well-posedness if we choose $U = H_0^1$ and $\nor{\cdot}_U = \nor{\cdot}_{\L}$ is that the space $U = H_0^1$ is not complete under the norm $\nor{\cdot}_U = \nor{\cdot}_{\L}$.
-In other words, the space $U$ is smaller than the $\L$ norm would imply - a weaker norm $\nor{\cdot}_U$ implies a large space $U$.
-Under the perspective that the spaces $U$ and $V$ are defined by their respective norms, if we set $\nor{\cdot}_U = \nor{\cdot}_{\L}$, this would imply $U = \L$.
-Since the definitions of the spaces $U$ and $V$ are incorporated in the definition of definiteness of $b(u,v)$, we would lose definiteness of the bilinear form as well, a prerequisite for Lemma 2.5.
-\item We note that it is still possible to specify $\nor{\cdot}_U = \nor{\cdot}_{\L}$.
-If we do not require $U = V = H_0^1$, and simply specify $\nor{\cdot}_U = \nor{\cdot}_{\L}$, then the space induced by $\nor{\cdot}_U$ is $U = \L$.
-If, then, we rewrite the bilinear form such that $b(u,v) = -\LRp{u,\del v}_{\L}$ (to satisfy regularity constraints), then we do indeed induce the norm $\nor{v}_V \coloneqq \nor{\del v}_{\L}$, which then induces the definition of the test space $V = \LRc{v\in \L, \del v\in \L}$.
-Under these conditions, we can show that both well-posedness and duality of norms hold.
-
-\end{enumerate}
-There are two main responses to this question - the first is that the definition of a space cannot be divorced from the definition of the norm on the space (by choosing a norm on $U$, we are simultaneously choosing the space $U$).
-The second Lemma 2.5 in \cite{Bui-ThanhDemkowiczGhattas11a} gives that three conditions are equivalent -
-\begin{itemize}
-\item $\frac{M}{\gamma} = 1$
-\item $\nor{\cdot}_U = \sup_{v\in V}\frac{b(u,v)}{\nor{v}_V}$
-\item $\nor{\cdot}_{V,U} = \sup_{u\in U}\frac{b(u,v)}{\nor{u}_U}$.
-\end{itemize}
-These three conditions are all related to the inf-sup condition.
-The starting point of DPG is to require from the start that $\frac{M}{\gamma} = 1$.
-By specifying a test norm, the trial norm  (and consequentially the space $U$) are defined such that we can guarantee that $\frac{M}{\gamma} = 1$ by construction.
-
-\end{enumerate}
+\item \textcolor{red}{
+While the authors have answered the referee's questions in their response, the referee feels that it would be advantagenous for the readers if some of these answers were included in Section 1.3.
+As the authors point out in their response, the norms and the spaces are not completely independent.
+However, the wording in Section~{1.3} is not very clear on that point.
+As written, the reader may think that the {\em sets/linear spaces} $U$ and $V$ are given and he is free to choose {\em any} norm $\|\cdot\|_U$ on $U$ (as in my last example with $U = H^1_0$ equipped with the $L^2$-norm).
+However, as pointed out by the authors in their response, this is not what is meant.
+Likewise, the wording
+\begin{quote}
+In particular, given two {\em arbitrary} norms $\|\cdot\|_{U,1}$,
+$\|\cdot\|_{U,2}$ on $U$ such that $\|\cdot\|_{U,1} \leq c \|\cdot\|_{U,2}$
+\end{quote}
+suggests more freedom in the choice of the norm than is intended by the authors.
+.}  The authors agree, and have added an extra sentence and footnote on page 5 to caution readers against thinking so.
+We have included specifically the example that the reviewer had mentioned, where it is shown that, for the standard Laplace problem with trial and test spaces in $H^1_0$, choosing for a trial norm $\nor{u}_{\L}$ (under which $H^1_0$ is not complete) leads to a test norm that is not well defined for insufficiently smooth $v\in H^1_0$.
+We thank the reviewer for providing this example, which we believe illustrates the need to constrain choices of norms on test/trial spaces in a familiar and clear way to readers.
 \end{enumerate}

### 2013-07-22 docs/Jesse/Confusion Notes/H1DPG.tex
adding Confusion notes changes (h1 paper and bib)

@@
 
-\title{A minimum-residual finite element method for the convection-dominated diffusion equation}
+\title{A minimum-residual finite element method for the convection-diffusion equation}
 \author{Jesse Chan, John A. Evans}
@@
 \begin{abstract}
-We present a minimum-residual finite element method for convection-dominated diffusion problems in a higher order, adaptive, continuous Galerkin setting.
-The method borrows concepts from both the Discontinuous Petrov-Galerkin (DPG) method by Demkowicz et al.\ \cite{DPG2} and the method of variational stabilization by Dahmen et al.\ \cite{DahmenVariationalStabilization}, and it can also be interpreted as a variational multiscale method in which the fine-scales are defined through a dual-orthogonality condition.
+We present a minimum-residual finite element method for convection-diffusion problems in a higher order, adaptive, continuous Galerkin setting.
+The method borrows concepts from both the Discontinuous Petrov-Galerkin (DPG) method by Demkowicz and Gopalakrishnan \cite{DPG2} and the method of variational stabilization by Dahmen et al.\ \cite{DahmenVariationalStabilization}, and it can also be interpreted as a variational multiscale method in which the fine-scales are defined through a dual-orthogonality condition.
 A key ingredient in the method is the proper choice of norm used to measure the residual, and we present two alternatives which are observed to be robust in both convection and diffusion-dominated regimes.
@@
   \begin{array}{l}
-    \text{Given } l \in V', \text{ find } u \in U  \text{ such that} \\ 
+    \text{Given } l \in V^*, \text{ find } u \in U  \text{ such that} \\ 
     b(u,v) = l(v), \quad \forall v\in V,
@@
 where $b\LRp{\cdot,\cdot}: U \times V \to \mbb{R}$ is a continuous bilinear form.
-Throughout the paper, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U'$ and $V'$ as the respective topological dual spaces.
+Throughout the paper, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U^*$ and $V^*$ as the respective topological dual spaces.
 Throughout the paper, we suppose the variational problem \eqnref{variationEq} to be well-posed in the inf-sup sense.
-We can then identify a unique operator $B:U\rightarrow V'$ such that
+We can then identify a unique operator $B:U\rightarrow V^*$ such that
 \[
-\langle Bu,v\rangle_V \coloneqq b(u,v), \quad u\in U, v\in V
+\langle Bu,v\rangle_{V^* \times V} \coloneqq b(u,v), \quad u\in U, v\in V
 \]
-with $\LRa{\cdot, \cdot}_V$ denoting the duality pairing between $V'$ and $V$, to obtain the operator form of the our variational problem
+with $\LRa{\cdot, \cdot}_{V^*\times V}$ denoting the duality pairing between $V^*$ and $V$, to obtain the operator form of the our variational problem
 \begin{equation}
 \eqnlab{dualEq}
-Bu = l \quad \text{in } V'.
+Bu = l \quad \text{in } V^*.
 \end{equation}
@@
 \[
-u_h = \underset{u_h\in U_h}{\arg\min}\, J(u_h) \coloneqq \frac{1}{2}\|l-Bu_h\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| l(v)- b(u_h,v)|^2}{\nor{v}_V^2}.
+u_h = \underset{u_h\in U_h}{\arg\min}\, J(u_h) \coloneqq \frac{1}{2}\|l-Bu_h\|_{V^*}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| l(v)- b(u_h,v)|^2}{\nor{v}_V^2}.
 \]
@@
 \[
-\nor{u}_E \coloneqq \nor{Bu}_{V'},
+\nor{u}_E \coloneqq \nor{Bu}_{V^*},
 \]
@@
 \begin{align}
-\left(l-Bu_h,B\delta u\right)_{V'} = 0, \quad \forall \delta u \in U,
+\left(l-Bu_h,B\delta u\right)_{V^*} = 0, \quad \forall \delta u \in U,
 \label{orthog}
@@
 
-The difficulty in working with the first-order optimality condition~\eqref{orthog} is that the inner product $\LRp{\cdot,\cdot}_{V'}$ cannot be evaluated explicitly.  However, we have that 
+The difficulty in working with the first-order optimality condition~\eqref{orthog} is that the inner product $\LRp{\cdot,\cdot}_{V^*}$ cannot be evaluated explicitly.  However, we have that 
 \begin{align}
-\left(l-Bu_h,B\delta u\right)_{V'} = \left(R_V^{-1}(l-Bu_h),R_V^{-1}B\delta u\right)_{V},
+\left(l-Bu_h,B\delta u\right)_{V^*} = \left(R_V^{-1}(l-Bu_h),R_V^{-1}B\delta u\right)_{V},
 \label{rieszOrthog}
 \end{align}
-where $R_V: V\rightarrow V'$ is the Riesz map mapping elements of a Hilbert space $V$ to elements of the dual $V'$ defined by
+where $R_V: V\rightarrow V^*$ is the Riesz map mapping elements of a Hilbert space $V$ to elements of the dual $V^*$ defined by
 \[
-\LRa{R_Vv,\delta v}_{V\times V'} \coloneqq \LRp{v,\delta v}_V.
+\LRa{R_Vv,\delta v}_{V^*\times V} \coloneqq \LRp{v,\delta v}_V.
 \]
-Furthermore, the Riesz operator is an isometry, such that $J(u_h) = \frac{1}{2}\nor{l-Bu_h}^2_{V'} = \frac{1}{2}\nor{R_V^{-1}(l-Bu_h)}^2_{V}$.
+Furthermore, the Riesz operator is an isometry, such that $J(u_h) = \frac{1}{2}\nor{l-Bu_h}^2_{V^*} = \frac{1}{2}\nor{R_V^{-1}(l-Bu_h)}^2_{V}$.
 Thus, satisfaction of~\eqref{rieszOrthog} is exactly equivalent to satisfaction of the original optimality conditions~\eqref{orthog}.
@@
 \LRp{e,R_V^{-1}B\delta u}_V &= 0, \quad \forall \delta u \in U_h\\
-\Rightarrow \LRa{e,B\delta u}_{V\times V'} &= b(\delta u, e) = 0.
+\Rightarrow \LRa{e,B\delta u}_{V\times V^*} &= b(\delta u, e) = 0.
 \end{align*}
@@
 Next, \textit{a posteriori} error estimators for $e$ (based on a specific choice of inner product $\LRp{\cdot,\cdot}_V$) were used to drive adaptivity to determine a fine-scale mesh on which $V_h$ was supported.
-We choose a simpler representation -- if $U_h$ is represented by polynomials of order $p$, we set $V_h = P^{p+\triangle p}$ globally.
+We choose a simpler representation -- if $U_h$ is represented by piecewise polynomials of order $p$, we set $V_h$ to be piecewise polynomials of order $p+\triangle p$.
 We note that these two choices of discretization for $V$ are not mutually exclusive, and that novel choices for $V_h$ are likely the key to yielding computationally effective methods under this framework.
@@
 \LRp{R_V^{-1}\LRp{l-Bu_h},R_V^{-1}B\delta u}_V &= 0, \quad \forall \delta u \in U_h\\
-\Rightarrow \LRa{\LRp{l-Bu_h},R_V^{-1}B\delta u}_{V\times V'} &= 0\\
+\Rightarrow \LRa{\LRp{l-Bu_h},R_V^{-1}B\delta u}_{V^*\times V} &= 0\\
 \Rightarrow l\LRp{R_V^{-1}B\delta u}-b\LRp{u_h,R_V^{-1}B\delta u} &= 0
@@
 \[
-\LRa{Bu,v}_{V'\times V} = \LRa{l,v}_{V'\times V},
+\LRa{Bu,v}_{V^*\times V} = \LRa{l,v}_{V^*\times V},
 \]
-where, as before, $B: U\rightarrow V'$ is the operator form of $b(u,v)$, and $l \in V'$ is the load.
+where, as before, $B: U\rightarrow V^*$ is the operator form of $b(u,v)$, and $l \in V^*$ is the load.
 Standard VMS techniques then decompose $U$ into a \textit{coarse scale} space $U_h$ and \textit{fine scale} space $U'$, such that the coarse and fine scales $u_h \in U_h \subset U$ and $u' \in U'$ are related through some yet-unspecified orthogonality condition.
@@
 \begin{align*}
-u_h \in U_h, u' \in U\setminus U_h, v \in V\\
-\LRa{Bu_h,v}_{V'\times V} + \LRa{Bu',v}_{V'\times V} = \LRa{l,v}_{V'\times V}
+u_h \in U_h, u' \in U', v \in V\\
+\LRa{Bu_h,v}_{V^*\times V} + \LRa{Bu',v}_{V^*\times V} = \LRa{l,v}_{V^*\times V}
 \end{align*}
-We can now explicitly choose our orthogonality condition defining the fine scales and rewrite the above problem as 
+where $U = U_h\oplus U'$.  We can now explicitly choose our orthogonality condition defining the fine scales and rewrite the above problem as 
 \begin{align*}
 u_h \in U_h, u' \in U, v \in V\\
-\LRa{Bu_h,v}_{V'\times V} + \LRa{Bu',v}_{V'\times V} &= \LRa{l,v}_{V'\times V}\\
+\LRa{Bu_h,v}_{V^*\times V} + \LRa{Bu',v}_{V^*\times V} &= \LRa{l,v}_{V^*\times V}\\
 \LRp{u',\bar{w}}_E &= 0, \quad \forall \bar{w} \in U_h,
@@
 \begin{align*}
-\LRp{Tu',v}_V = \LRp{R_V^{-1}Bu',v}_V = \LRa{Bu',v}_{V'\times V}\\
-\LRp{u',\bar{w}}_E = \LRp{Tu',R_V^{-1}B\bar{w}}_V = \LRa{Tu',B\bar{w}}_{V\times V'}
+\LRp{Tu',v}_V = \LRp{R_V^{-1}Bu',v}_V = \LRa{Bu',v}_{V^*\times V}\\
+\LRp{u',\bar{w}}_E = \LRp{Tu',R_V^{-1}B\bar{w}}_V = \LRa{Tu',B\bar{w}}_{V\times V^*}
 \end{align*}
@@
 u_h \in U_h, u' \in U, v \in V\\
-\LRa{Bu_h,v}_{V'\times V} + \LRp{Tu',v}_{V} &= \LRa{l,v}_{V'\times V}\\
-\LRp{Tu',B\bar{w}}_{V\times V'} &= 0, \quad \forall \bar{w} \in U_h.
+\LRa{Bu_h,v}_{V^*\times V} + \LRp{Tu',v}_{V} &= \LRa{l,v}_{V^*\times V}\\
+\LRp{Tu',B\bar{w}}_{V\times V^*} &= 0, \quad \forall \bar{w} \in U_h.
 \end{align*}
@@
 
-To summarize, the minimum-residual framework motivating both Dahmen's variational stabilization and Demkowicz's DPG method can be characterized as a VMS method under which 
+To summarize, the minimum-residual framework motivating both Dahmen's variational stabilization and Demkowicz and Gopalakrishnan's DPG method can be characterized as a VMS method under which 
 \begin{itemize}
@@
 \]
-where $L = \LRb{\Omega}^{\frac{1}{d}}$ is the length measure of $\Omega$ in $d$ spatial dimensions, $\LRb{\beta} = \max_\Omega \nor{\beta}_{l^2}$, and we have introduced the scaling $\frac{L}{\LRb{\beta}}$ on the streamline diffusion term for unit consistency\footnote{In all problems considered, $\frac{L}{\LRb{\beta}} = O(1)$}.
+where $L = \LRb{\Omega}^{\frac{1}{d}}$ is the length measure of $\Omega$ in $d$ spatial dimensions, $\LRb{\beta} = \max_\Omega \nor{\beta}_{l^2}$, and we have introduced the scaling $\frac{L}{\LRb{\beta}}$ on the streamline diffusion term for unit consistency\footnote{In all problems considered, $\frac{L}{\LRb{\beta}} = O(1)$.}.
 $\alpha \geq 0$ is a user-specified constant with units of inverse time\footnote{In the case where $\alpha = 0$, the seminorm remains a norm due to equivalence with the $H^1$ seminorm, which is norm on $H^1_0$.
 Specifying $\alpha > 0$ does not change the results dramatically; however, it does appear to improve conditioning of $\bs{A}$.}, and $w(x)$ is some smoothly varying positive weighting function.
-Specifically, we require $\LRb{w(x)}$ to be of magnitude $O(\epsilon)$ for $x\in \Gamma_{\rm in}$, but $O(1)$ away from the inflow boundary.
-Specific restrictions on $w$ are derived in \cite{DPGrobustness} in context of the DPG method.
+Specifically, we require $\LRb{w(x)}$ to be of magnitude $O(\epsilon)$ for $x\in \Gamma_{\rm in}$, but $O(1)$ away from the inflow boundary.\footnote{Specific restrictions on $w$ are derived in \cite{DPGrobustness} in context of the DPG method.}
 
@@
 We remark that this inclusion of $\epsilon\int_{\Gamma_{\rm in}} \pd{u}{n}v$ is a variational crime under the assumption that $u \in H^1_0(\Omega)$; the proper way to include such a term in a conforming manner (without introducing additional regularity assumptions on $u$) would be to introduce $\epsilon \pd{u}{n}$ as an additional unknown on the boundary, similar to the work done using DPG under the ultra-weak formulation \cite{DPG2,analysisDPG}.
+However, we have found that doing so does not remove the boundary layer in the residual at the inflow, and numerical results appear to degenerate in quality as $\epsilon$ grows smaller and smaller.
+We believe this is due to the fact that, by decoupling $\epsilon \pd{u}{n}$ as an additional unknown, the orthogonality boundary condition $\int_{\Gamma_{\rm in}} \pd{u}{n} e = 0$ is decoupled from the interior integrals and enforced strongly.\footnote{The same situation occurs when $\pd{u}{n}$ is declared as an additional unknown and when $\epsilon > 0$.}
+
 We note that Broersen and Stevenson have also achieved good results by making use of the space $H^1_{\rm out}(\Omega)$ in their application of the DPG method to the mixed mild-weak formulation for convection-diffusion \cite{broersenStevenson}.
@@
 
-For many flow problems, activity near the inflow is typically very smooth and can thus be represented using a minimal number of elements under an effective adaptive mesh refinement scheme, implying that the cost of introducing such additional unknowns on $\Gamma_{\rm in}$ can be minimized.
-However, since the codebase we currently use does not support unknowns with support only on element edges/faces, we continue to operate under this variational crime, in hopes that we can implement a conforming version in the near future.
-Another way to properly include the term $\epsilon \pd{u}{n}$ in the variational formulation would be to work with higher continuity trial spaces that admit a normal trace of the derivative on the boundary \cite{nurbsTrace, NURBSorig}.
+%For many flow problems, activity near the inflow is typically very smooth and can thus be represented using a minimal number of elements under an effective adaptive mesh refinement scheme, implying that the cost of introducing such additional unknowns on $\Gamma_{\rm in}$ can be minimized.
+However, since the codebase we currently use does not feature unknowns with support only on element edges/faces, we continue to operate under this variational crime, in hopes that we can implement a conforming version in the near future.
+%Another way to properly include the term $\epsilon \pd{u}{n}$ in the variational formulation would be to work with higher continuity trial spaces that admit a normal trace of the derivative on the boundary \cite{nurbsTrace, NURBSorig}.
 \end{remark}
@@
 \begin{remark}
-We note that, for $\epsilon \ll L$, where $L$ is the length scale of the problem, the boundary term $\epsilon\int_{\Gamma_{\rm in}} \pd{u}{n}v$ effectively disappears, and numerically speaking, we can use $e,v\in H^1_{\rm out}(\Omega)$ without including the additional boundary term in the variational formulation.
+We note that, when the Peclet number ${\rm Pe} = \frac{\LRb{\beta} L}{\epsilon} \gg 1$, the boundary term $\epsilon\int_{\Gamma_{\rm in}} \pd{u}{n}v$ effectively disappears, and numerically speaking, we can use $e,v\in H^1_{\rm out}(\Omega)$ without including the additional boundary term in the variational formulation.
 \end{remark}
@@
 Unlike standard stabilized $H^1$ methods, there are no stabilization parameters.
-However, unlike the DPG methods of both Demkowicz et.\ al.\ and Broersen and Stevenson, this method is easily implementable within current finite element codes in arbitrary spatial dimensions.
+However, unlike the DPG methods of both Demkowicz and Gopalakrishnan, as well as the method of Broersen and Stevenson, this method is easily implementable within current finite element codes in arbitrary spatial dimensions.
 
@@
 A few examples of nonstandard discretizations include higher order continuity basis functions (splines and NURBS \cite{NURBSorig}), and discontinuous functions (DG).
-We hope to also explore intelligent mixing of discretizations for $U_h$ and $V_h$.
+Preliminary experiments have yielded promising results in 1D under the combination of higher-continuity and $C_0$ bases for $U_h$ and $V_h$, respectively.
+We hope to further explore intelligent mixing of discretizations for trial and test spaces in future experiments.
 \item The DPG method achieves computational efficiency by block-diagonalizing $\bs{A}$ using discontinuous test functions.
@@
 \end{itemize}
-\newpage
+
+\section{Acknowledgements}
+
+The authors would like to acknowledge the help of Truman Ellis and Dr.\ Leszek Demkowicz for fruitful discussions and perspective.
+Jesse Chan was supported by the Department of Energy [National Nuclear Security Administration] under Award Number [DE- FC52-08NA28615].
+John A.\ Evans was partially supported by the ICES Postdoctoral Fellowship at the Institute for Computational Engineering and Sciences, and by a grant from the Office of Naval Research [N00014-08-1-0992].
+
 \bibliographystyle{unsrt}

### 2013-07-22 docs/Jesse/Dissertation/DPGtheory.tex
updating diss files

@@
-\subsection{Discontinuous Petrov-Galerkin methods with optimal test functions}
+\section{Discontinuous Petrov-Galerkin methods with optimal test functions}
 \seclab{optimalTest} Petrov-Galerkin methods, in which the test space
@@
 Throughout this dissertation, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U'$ and $V'$ as the respective topological dual spaces.
-Let $U_h \subset U$ and $V_h\subset V$ be finite dimensional subsets.
+Let $U_h \subset U$ and $V_h\subset V$ be finite dimensional subspaces.
 We are interested in the following problem
@@
 
-Throughout the paper, we suppose the variational
+Throughout the dissertation, we suppose the variational
 problem \eqnref{variationEq} to be well-posed. In that case, we can
@@
 \]
-For convenience in writing, we will abuse the notation $\sup_{v \in V}$ to denote $\sup_{v\in V\setminus\{0\}}$ for the remainder of the paper.
+For convenience in writing, we will abuse the notation $\sup_{v \in V}$ to denote $\sup_{v\in V\setminus\{0\}}$ for the remainder of the dissertation.
 
@@
 
-We note that solving \eqnref{optvVar} on each element exactly is infeasible since it amounts to inverting the Riesz map $R_V$ exactly.
+We note that solving \eqnref{optvVar} on each element exactly is still infeasible since it amounts to inverting the Riesz map $R_V$ exactly.
 Instead, optimal test functions are approximated using the standard Bubnov-Galerkin method on an ``enriched" subspace $\tilde{V} \subset V$ such that $\dim(\tilde{V}) > \dim(U_h)$ elementwise \cite{DPG1, DPG2}.
-In this paper, we assume the error in approximating the optimal test functions is negligible, and refer to the work in \cite{practicalDPG} for estimating the effects of approximation error on the performance of DPG.
+In this dissertation, we assume the error in approximating the optimal test functions is negligible, and refer to the work in \cite{practicalDPG} for estimating the effects of approximation error on the performance of DPG.
 
@@
 
-\subsection{Duality between trial and test norms (energy norm pairings)}
-%\subsection{Abstract energy norm pairings}
+\section{Duality between trial and test norms (energy norm pairings)}
+
 \seclab{energyPair}
@@
 \[
-\nor{\varphi}_{U} = \sup_{v \in V}\frac{b\LRp{w,v}}{\nor{v}_{V,U}}.
+\nor{\varphi}_{U} = \sup_{v \in V}\frac{b\LRp{\varphi,v}}{\nor{v}_{V,U}},
 \]
@@
 Likewise, we will refer $\nor{\cdot}_{U,V}$ as the trial norm induced by a given test norm $\nor{\cdot}_V$.
-In this paper, for simplicity of exposition, we shall call a pair of norms in $U$ and $V$ that induce each other as an {\em energy norm pairing}.
+In this dissertation, for simplicity of exposition, we shall call a pair of norms in $U$ and $V$ that induce each other as an {\em energy norm pairing}.
 
-\subsection{Discontinuous Petrov-Galerkin methods with the ultra-weak formulation}
+\section{Discontinuous Petrov-Galerkin methods with the ultra-weak formulation}
 \seclab{abstractUweak}
 
-The naming of the discontinuous Petrov-Galerkin method refers to the fact that the method is a Petrov-Galerkin method, and that the test functions are specified to be discontinuous across element boundaries.
+The name of the discontinuous Petrov-Galerkin method refers to the fact that the method is a Petrov-Galerkin method, and that the test functions are specified to be discontinuous across element boundaries.
 There is no specification of the regularity of the trial space, and we stress that the idea of DPG is not inherently tied to a single variational formulation \cite{Bui-ThanhDemkowiczGhattas11a}.
-Additionally, Cohen, Dahmen and Welper simultaneously extend the minimum residual concept behind DPG to general variational settings and avoid the use of discontinuous test functions by formulating the minimum residual method as a saddle-point problem \cite{DahmenVariationalStabilization}.
+Additionally, Cohen, Dahmen and Welper simultaneously extended the minimum residual concept behind DPG to general variational settings and avoid the use of discontinuous test functions by formulating the minimum residual method as a saddle-point problem \cite{DahmenVariationalStabilization}.
 
-In most of the DPG literature, however, the discontinuous Petrov-Galerkin method refers to the combination of the concept of locally computable optimal test functions in Section \secref{optimalTest} with the so-called ``ultra-weak formulation" \cite{DPG1,DPG2,DPG3,DPG4,DPGElas,DBLP:journals/procedia/NiemiCC11}.
+In most of the DPG literature, however, the discontinuous Petrov-Galerkin method refers to the combination of the concept of locally computable optimal test functions introduced in Section \secref{optimalTest} with the so-called ``ultra-weak formulation" \cite{DPG1,DPG2,DPG3,DPG4,DPGElas,DBLP:journals/procedia/NiemiCC11}.
 Unlike the previous two sections in which we studied the general equation \eqnref{variationEq} given by abstract bilinear and linear forms, we now consider a concrete instance of \eqnref{variationEq} resulting from an ultra-weak formulation for an abstract first-order system of PDEs $Au = f$.
@@
 Here, $h$ is defined as $h= \max_{j\in \LRc{1,\hdots,\Nel}}\text{diam}\LRp{K_j}$.
-We denote the mesh ``skeleton" by $\Gh = \cup_{j=1}^\Nel \partial K_j$; the set of all faces/edges $e$, each of which comes with a normal vector ${n}_e$.
+We denote the mesh ``skeleton" by $\Gh = \cup_{j=1}^\Nel \partial K_j$; the set of all faces/edges $e$, each of which come with a normal vector ${n}_e$.
 The internal skeleton is then defined as $\Gamma^0_h = \Gh \setminus \partial \Omega$.
@@
 \]
-Note that we allow arbitrariness in assigning ``-'' and ``+'' quantities to the adjacent elements $K_i$ and $K_j$.
+Note that we allow arbitrariness in assigning ``$-$'' and ``$+$'' quantities to the adjacent elements $K_i$ and $K_j$.
 %For the rest of the paper, we will use the same notation for both a function and its trace (if it is well-defined) when there is no ambiguity.
@@
 product over $\Oh$, and $A_h^*$ the formal adjoint resulting from
-element-wise integration by parts.  Occasionally, for simplicity in
+element-wise integration by parts.\footnote{We note that $\jump{v}$ refers to the jump of the trace of the test function across an edge; for example, for vector valued test functions $\tau$, $\jump{\tau}$ corresponds to the jump of the normal component.
+We will continue to use this notation in following chapters.}
+Occasionally, for simplicity in
 writing, we will ignore the subscripts in the duality pairing and
@@
 %\subsection{Optimal and quasi-optimal test norms}
-\subsection{A canonical energy norm pairing for ultra-weak formulation}
+\section{A canonical energy norm pairing for ultra-weak formulation}
 
@@
 
-Using variants of the quasi-optimal test norm, numerical results show that the DPG method appears to provide a ``pollution-free" method without phase error for the Helmholtz equation \cite{DPG4}, and analysis of the pollution-free nature of DPG is currently under investigation.
+Using variants of the graph test norm, numerical results show that the DPG method appears to provide a ``pollution-free" method without phase error for the Helmholtz equation \cite{DPG4}, and analysis of the pollution-free nature of DPG is currently under investigation.
 Similar results have also been obtained in the context of elasticity \cite{DPGElas} and the linear Stokes equations \cite{Camellia}.
-On the theoretical side, the quasi-optimal test norm has been shown to yield a well-posed DPG methodology for the Poisson and convection-diffusion equations \cite{analysisDPG}.
+On the theoretical side, the graph test norm has been shown to yield a well-posed DPG methodology for the Poisson and convection-diffusion equations \cite{analysisDPG}.
 More recently, this theory has been generalized to show the well-posedness of DPG for the large class of PDEs of Friedrichs' type \cite{Bui-ThanhDemkowiczGhattas11b}.

### 2013-07-22 docs/Jesse/Dissertation/proposalIntro.tex
updating diss files

--- 2012-07-24 docs/Jesse/PECOStalk/proposalIntro.tex
@@
 An additional complication of singular perturbation problems is that very often, in the limiting case of the parameter blowing up or decreasing to zero, the PDE itself will change types (e.g.\ from elliptic to hyperbolic).
-A canonical example of a singularly perturbed problem is the convection-diffusion equation in domain $\Omega \in \mathbb{R}^3$,
+A canonical example of a singularly perturbed problem is the convection-diffusion equation in domain $\Omega \subset \mathbb{R}^3$,
 \[
@@
 \centering
-\includegraphics[scale=.4]{figs/GalerkinOscTight.png}
+\includegraphics[scale=.5]{figs/GalerkinOscTight.png}
 \caption{Oscillations in the 1D finite element solution of the convection-diffusion equation for small diffusion \cite{GalerkinOsc}.
@@
 
-From the perspective of the full Navier-Stokes equations, this loss of robustness is doubly problematic.
+From the perspective of the compressible Navier-Stokes equations, this loss of robustness is doubly problematic.
+Not only will any nonlinear solution suffer from similar unstable oscillations, but nonlinear solvers themselves may fail to yield a solution due to such instabilities.
+A nonlinear solution is almost always computed by solving a series of linear problems whose solutions will converge to the nonlinear solution under appropriate assumptions, and the presence of such oscillations in each linear problem can cause the solution convergence to slow significantly or even diverge.
+Artificial viscosity and shock capturing methods have been used to suppress such oscillations and regularize the problem.
+While these methods will usually yield smooth and qualitatively resolved solutions, these methods are often overly diffusive, yielding results which are poor approximations of the true solution \cite{Gresho1981223}, though modern artificial viscosity and shock capturing schemes have improved greatly in recent years \cite{Barter,Guermond20114248}.
+We have taken an alternative approach in this work, avoiding artificial diffusion and shock capturing for the moment.
+
+Our aim is to develop a stable, higher order scheme for the steady compressible laminar Navier-Stokes equations in transonic/supersonic regimes that is automatically adaptive beginning with very coarse meshes.
+This requires that both the method and the refinement scheme to perform adequately on coarse meshes with high Peclet numbers -- in other words, that the adaptive method is robust in the diffusion parameter.
+We construct such a method in this work -- in particular, we present a method for which automatic adaptivity can be applied to problems in compressible flow, beginning with very coarse meshes which do not reflect additional knowledge about the problem.
+The goal of this dissertation will be to develop a mathematical theory demonstrating the robustness in $\epsilon$ of our method for singularly perturbed convection-diffusion problems, and to demonstrate its feasibility as a CFD solver by applying it to several benchmark problems.
+
+%We construct such a method in this paper as follows: we begin by deriving the DPG method for linear problems, then constructing a DPG method for the scalar convection-diffusion equation that is robust for very small viscosities.
+Unlike common adaptive methods in computational fluid dynamics, which often refine based on physical features (such as high gradients in the solution), adaptivity under this method is driven by the minimization of a residual, which measures error accurately even for highly underresolved meshes.
+The DPG method for scalar convection-diffusion is then extrapolated to systems of nonlinear equations, and applied to the compressible Navier-Stokes equations.
+Numerical experiments are given, demonstrating the robustness of the method and the effectiveness of automatic adaptivity for two model problems in viscous compressible flow.
+
+%From the perspective of the full Navier-Stokes equations, this loss of robustness is doubly problematic.
 Not only will any nonlinear solution suffer from similar non-physical oscillations, but nonlinear solvers themselves may fail to yield a solution due to such instabilities.
 A nonlinear solution is almost always computed by solving a series of linear problems whose solutions will converge to the nonlinear solution under appropriate assumptions, and the presence of such oscillations in each linear problem can cause the solution convergence to slow significantly or even diverge.
-
-Our aim is to develop a \emph{stable, higher order adaptive scheme} for the steady compressible laminar Navier-Stokes equations in transonic/supersonic regimes that is \emph{robust for very small viscosity}.
-In particular, we hope to present a method for which $hp$-adaptivity can be applied to problems in compressible flow.
+%
+%Our aim is to develop a \emph{stable, higher order, automatically adaptive scheme} for the steady compressible laminar Navier-Stokes equations in transonic/supersonic regimes that is \emph{robust for very small viscosity}.
+In particular, we hope to present a method for which automatic adaptivity can be applied to problems in compressible flow, beginning with very coarse meshes which do not reflect additional knowledge about the problem.
 The goal of this dissertation will be to develop a mathematical theory demonstrating the robustness in $\epsilon$ of our method for singularly perturbed convection-diffusion problems, and to demonstrate its feasibility as a CFD solver by applying it to several benchmark problems.
@@
 WENO remains a popular choice today for both finite volume and finite difference schemes.
-Most of these methods can be interpreted as adding some specific artificial diffusion to the given numerical scheme.
-We refer to such schemes as \emph{modified equation} methods, as the exact solution no longer satisfies the discrete system due to the presence of additional artificial diffusion terms.
+Most of these methods can be interpreted as adding some specific artificial diffusion to the given numerical scheme, which vanishes as the mesh size $h\rightarrow 0$.
+%We refer to such schemes as \emph{modified equation} methods, as the exact solution no longer satisfies the discrete system due to the presence of additional artificial diffusion terms.
 
@@
 The most well-known example of this technique is the streamline-upwind Petrov-Galerkin (SUPG) method, which is a stabilized FE method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.
-SUPG stabilization not only removes the spurious oscillations from the finite element solution of the convection-diffusion equation, but delivers the best finite element approximation in the $H^1$ norm.
+SUPG stabilization not only removes the spurious oscillations from the finite element solution of the convection-diffusion equation, but delivers the best finite element approximation in the $H^1$ norm in 1D.
 
@@
 \centering
-\subfigure[SUPG and standard FEM solutions]{\includegraphics[scale=.43]{figs/SUPG.png}}
-\subfigure[SUPG test function]{\includegraphics[scale=.22]{figs/SUPGtest.png}}
+\subfigure[SUPG and standard FEM solutions]{\includegraphics[scale=.475]{figs/SUPG.png}}
+\subfigure[SUPG test function]{\includegraphics[scale=.25]{figs/SUPGtest.png}}
 \caption{SUPG and standard Bubnov-Galerkin solutions to the 1D convection-dominated diffusion equation, and a modified SUPG test function (in black) corresponding to a linear basis ``hat" function (in red).
@@
 
-The idea of emphasizing the upwind portion of a test function is an old idea, introduced in 1977 by Zienkiewicz et al.\ in \cite{zienkUpwind}.
+The idea of emphasizing the upwind portion of a test function is an older idea, introduced in 1977 by Zienkiewicz et al.\ in \cite{zienkUpwind}.
 However, the precise amount of upwinding,\footnote{Insufficient upwinding results in a method which still exhibits oscillations and instabilities, while excessive upwinding leads to an overly diffusive method.} as well as the connection to residual-based stabilization methods, were novel to SUPG.
@@
 For appropriately chosen $\tau$, the method can be generalized for higher order elements as well.
-In higher dimensions, and the SUPG solution is very close to, but no longer the $H^1_0$ best approximation for 2D and 3D problems \cite{HughesSangalliSUPG}.
+In higher dimensions, the SUPG solution is very close to, but no longer the $H^1_0$ best approximation for 2D and 3D problems \cite{HughesSangalliSUPG}.
 Since its inception, SUPG is and has been the most popular stabilization method of choice for convection-diffusion type problems, in both academic and industry applications.
 
-An important feature of SUPG and other residual-based stabilization techniques that separates it from modified equation methods is the idea of \textit{consistency} --- by adding stabilization terms based on the residual, the exact solution still satisfies the same variational problem (i.e.\ Galerkin orthogonality still holds).
-Contrast this to the artificial diffusion methods in finite difference and finite volume methods, where a specific amount of additional viscosity is added based on the magnitude of the convection and diffusion parameters: unlike residual-based stabilization schemes, the exact solution to the original equation no longer satisfies the new stabilized formulation.
-
-This addition of residual-based stabilization terms can be interpreted as a modification of the test functions as well.  For SUPG, the formulation can equivalently be written as
+An important feature of SUPG and other residual-based stabilization techniques that separates it from modified equation methods is the idea of \textit{consistency} --- by adding stabilization terms based on the residual, the exact solution still satisfies the same variational problem (i.e.\ Galerkin orthogonality still holds with $b(u-u_h,v) = 0$ for all $v\in V$).
+This addition of residual-based stabilization can be interpreted as a modification of the test functions.
+For SUPG, the formulation can equivalently be written as
 \[
@@
 
-Discontinuous Galerkin (DG) methods form a subclass of FEM; first introduced by Reed and Hill in \cite{Reed:73}, these methods were later analyzed by Cockburn and Shu \cite{CockburnShu:DG} and have rapidly gained popularity for CFD problems.
+Discontinuous Galerkin (DG) methods form a subclass of FEM; first introduced by Reed and Hill in \cite{Reed:73}.
+These methods were later analyzed Raviart et al \cite{DGRaviart} and later by Johnson et al \cite{DGJohnson}, who contributed a mathematical analysis of the original method of Reed and Hill, as well as by Cockburn and Shu \cite{CockburnShu:DG}, who solved the Euler equations by applying concept of Lax's numerical flux within the context of DG.
+
 Advantages of DG methods include the local conservation property, easily modified local orders of approximation, ease of adaptivity in both $h$ and $p$, and efficient parallelizability.
@@
 The formal definition of the numerical flux (attributed to Peter Lax) on an element boundary is some function of the values on the edges of both the neighboring elements.
-An additional reason for the popularity of DG methods is that they can be interpreted as stabilized FE methods through appropriate choices of this numerical flux \cite{Brezzi20063293}.
+An additional reason for the popularity of DG methods is that they can be interpreted as stabilized FE methods (and vice versa) through appropriate choices of this numerical flux \cite{Brezzi20063293}.
 We will illustrate this with the steady convection equation in 1D:
@@
 
-A more recent development in DG methods is the idea of \emph{hybridized} DG (HDG), introduced by Gopalakrishnan and Lazarov \cite{hybridDG}.
+A more recent development in DG methods is the idea of \emph{hybridized} DG (HDG), introduced by Cockburn, Gopalakrishnan and Lazarov \cite{hybridDG}.
 The hybridized DG framework identifies degrees of freedom with support only on element edges, which can be interpreted as Lagrange multipliers enforcing weak continuity of the trial space.
@@
 
-This PhD thesis proposal will proceed in four main parts.
+This dissertation will proceed in four main parts.
 We will begin by introducing the abstract Discontinuous Petrov-Galerkin (DPG) method as a minimum residual method for linear problems and highlighting some important properties of the method.
 Our next step will be to formulate and prove the robustness of a DPG method (with respect to $\epsilon$) for the model problem of convection-dominated diffusion.
-Finally, we will extend and apply the DPG method to singularly perturbed nonlinear problems in CFD, presenting preliminary results for the Burgers and compressible Navier-Stokes equations.
-
-%\section{Range of CFD problems}
-%
-%\begin{figure}[!h]
-%\centering
-%\includegraphics[scale=.45]{figs/CFD_tree.pdf}
-%\caption{A diagram of common CFD problems and their simplifying assumptions.}
-%\end{figure}
-%
-%\begin{itemize}
-%\item Discuss full compressible Navier-Stokes with boundary layers
-%\item Discuss full compressible Navier-Stokes without boundary layers, connect to Euler (mention Dr Young and Boeing and the IBL connection \cite{BoeingDrela})
-%\item Discuss model problems
-%\end{itemize}
+Finally, we will extend and apply the DPG method to singularly perturbed nonlinear problems in CFD, presenting results for the Burgers and compressible Navier-Stokes equations.

### 2013-07-22 docs/Jesse/Dissertation/confusionAppendix.tex
updating dissertation

--- 2013-05-01 docs/Jesse/Confusion Notes/notes.tex
@@
-%&pdflatex
-\documentclass[11pt,onecolumn]{scrartcl}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
-\usepackage[top=2cm,bottom=3cm,left=2.5cm,right=2cm]{geometry}
-\usepackage{amssymb}
-\usepackage{amscd}
-\usepackage{listings}
-\usepackage{array}
-\usepackage{mathtools}
-\usepackage{dsfont}
-\usepackage{graphicx}
-\usepackage{pdfpages}
-\usepackage[textsize=footnotesize,color=green]{todonotes}
-\usepackage{algorithm, algorithmic}
-\usepackage{array}
-\usepackage{bm}
-\usepackage{tikz}
-\usepackage{subfigure}
-\usepackage[normalem]{ulem}
-
-\newcommand{\bs}[1]{\boldsymbol{#1}}
-\DeclareMathOperator{\diag}{diag}
-
-\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}
-
-\newcommand{\tablab}[1]{\label{tab:#1}}
-\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
-
-\newcommand{\theolab}[1]{\label{theo:#1}}
-\newcommand{\theoref}[1]{\ref{theo:#1}}
-\newcommand{\eqnlab}[1]{\label{eq:#1}}
-\newcommand{\eqnref}[1]{\eqref{eq:#1}}
-\newcommand{\seclab}[1]{\label{sec:#1}}
-\newcommand{\secref}[1]{\ref{sec:#1}}
-\newcommand{\lemlab}[1]{\label{lem:#1}}
-\newcommand{\lemref}[1]{\ref{lem:#1}}
-
-\newcommand{\mb}[1]{\mathbf{#1}}
-\newcommand{\mbb}[1]{\mathbb{#1}}
-\newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\nor}[1]{\left\| #1 \right\|}
-\newcommand{\snor}[1]{\left| #1 \right|}
-\newcommand{\LRp}[1]{\left( #1 \right)}
-\newcommand{\LRs}[1]{\left[ #1 \right]}
-\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
-\newcommand{\LRc}[1]{\left\{ #1 \right\}}
-\newcommand{\LRb}[1]{\left| #1 \right|}
-
-\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
-\newcommand{\Grad} {\ensuremath{\nabla}}
-\newcommand{\Div} {\ensuremath{\nabla\cdot}}
-\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
-\newcommand{\jump}[1] {\ensuremath{\LRs{\!\left[#1\right]\!}}}
-\newcommand{\uh}{\widehat{u}}
-\newcommand{\fnh}{\widehat{f}_n}
-\renewcommand{\L}{L^2\LRp{\Omega}}
-\newcommand{\pO}{\partial\Omega}
-\newcommand{\Gh}{\Gamma_h}
-\newcommand{\Gm}{\Gamma_{-}}
-\newcommand{\Gp}{\Gamma_{+}}
-\newcommand{\Go}{\Gamma_0}
-\newcommand{\Oh}{\Omega_h}
-
-\newcommand{\eval}[2][\right]{\relax
-  \ifx#1\right\relax \left.\fi#2#1\rvert}
-
-\def\etal{{\it et al.~}}
-
-\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
-\newcommand{\tensor}[1]{\underline{\vect{#1}}}
-\newcommand{\del}{\Delta}
-\newcommand{\grad}{\nabla}
-\newcommand{\curl}{\grad \times}
-\renewcommand{\div}{\grad \cdot}
-\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
-\newcommand{\eip}[1]{a\left( #1 \right)}
-\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
-\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
-
-\newcommand{\circone}{\ding{192}}
-\newcommand{\circtwo}{\ding{193}}
-\newcommand{\circthree}{\ding{194}}
-\newcommand{\circfour}{\ding{195}}
-\newcommand{\circfive}{\ding{196}}
-
-\def\arr#1#2#3#4{\left[
-\begin{array}{cc}
-#1 & #2\\
-#3 & #4\\
-\end{array}
-\right]}
-\def\vecttwo#1#2{\left[
-\begin{array}{c}
-#1\\
-#2\\
-\end{array}
-\right]}
-\def\vectthree#1#2#3{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-\end{array}
-\right]}
-\def\vectfour#1#2#3#4{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-#4\\
-\end{array}
-\right]}
-
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-
-\newcommand{\G} {\Gamma}
-\newcommand{\Gin} {\Gamma_{in}}
-\newcommand{\Gout} {\Gamma_{out}}
-
-\newtheorem{remark}{Remark}
-
-%\title{$\epsilon$-explicit analysis of DPG for convection-dominated diffusion}
-\title{Notes on convection-diffusion}
-\date{}
-\begin{document}
-
-\maketitle
+\chapter{Additional notes on convection-diffusion}
 
 \section{Boundary layers in robust norm test functions and global/local test spaces}
+\seclab{appendix:globalLocal}
 
-In \cite{DPGrobustness, ChanHeuerBui-ThanhDemkowicz12}, we introduced the test norm
+In Section~\secref{sec:testNormSec}, we introduced the test norm
 \[
@@
 where $\alpha \in [\epsilon,1]$ was selected in such a way that optimal test functions over a single element did not contain boundary layers\footnote{Boundary layers can appear in the cross-stream direction if $\alpha$ is not the same order as $\epsilon/h^2$, where $h$ is the element size.
-This is explained in more detail in \cite{ChanHeuerBui-ThanhDemkowicz12}} which are difficult to approximate using our enriched space.
+This is explained in more detail in \cite{DPGrobustness2}} which are difficult to approximate using our enriched space.
 
@@
 In other words, the resolution of boundary layers that occur at element boundaries is not important unless these boundary layers appear in globally determined test functions too (boundary layers that appear on element boundaries but not at a global level can be considered a negligible side-effect of the ``localization" of problems for optimal test functions).
-Numerical experiments indicate
 
 For these problems, we consider the Erikkson-Johnson model problem setup - the domain is a unit square in 2D, with $\beta = \LRp{1,0}$.
-We computed global test functions corresponding to global field basis functions $1, xy, x(1-x)y(1-y)$ - a constant basis function, a bilinear basis function, and a quadratic bubble - as well as basis functions restricted to a small element in the middle of the domain for both $\alpha = \epsilon$ (where $\epsilon = .01$) and $\alpha = 1$.
+We computed global test functions corresponding to global field basis functions $1, xy, x(1-x)y(1-y)$ -- a constant basis function, a bilinear basis function, and a quadratic bubble -- as well as basis functions restricted to a small element in the middle of the domain for both $\alpha = \epsilon$ (where $\epsilon = .01$) and $\alpha = 1$.
 No boundary layers were observed in either case, and the test functions under both test norms are very similar.
@@
 \centering
-\subfigure[$\alpha = \epsilon$]{\includegraphics[scale=.475]{figs/aEpsConstant.png}}
-\subfigure[$\alpha = 1$]{\includegraphics[scale=.475]{figs/aOneConstant.png}}
+\subfigure[$\alpha = \epsilon$]{\includegraphics[scale=.425]{figs/aEpsConstant.png}}
+\subfigure[$\alpha = 1$]{\includegraphics[scale=.425]{figs/aOneConstant.png}}
 \caption{Optimal test functions for a $u=1$.}
@@
 \centering
-\subfigure[$\alpha = \epsilon$]{\includegraphics[scale=.475]{figs/aEpsBilinear.png}}
-\subfigure[$\alpha = 1$]{\includegraphics[scale=.475]{figs/aOneBilinear.png}}
+\subfigure[$\alpha = \epsilon$]{\includegraphics[scale=.425]{figs/aEpsBilinear.png}}
+\subfigure[$\alpha = 1$]{\includegraphics[scale=.425]{figs/aOneBilinear.png}}
 \caption{Optimal test functions for a $u=xy$.}
@@
 \centering
-\subfigure[$\alpha = \epsilon$]{\includegraphics[scale=.475]{figs/aEpsBubble.png}}
-\subfigure[$\alpha = 1$]{\includegraphics[scale=.475]{figs/aOneBubble.png}}
+\subfigure[$\alpha = \epsilon$]{\includegraphics[scale=.425]{figs/aEpsBubble.png}}
+\subfigure[$\alpha = 1$]{\includegraphics[scale=.425]{figs/aOneBubble.png}}
 \caption{Optimal test functions for a $u=x(1-x)y(1-y)$.}
@@
 \centering
-\subfigure[$\alpha = \epsilon$]{\includegraphics[scale=.475]{figs/aEpsElement.png}}
-\subfigure[$\alpha = 1$]{\includegraphics[scale=.475]{figs/aOneElement.png}}
+\subfigure[$\alpha = \epsilon$]{\includegraphics[scale=.425]{figs/aEpsElement.png}}
+\subfigure[$\alpha = 1$]{\includegraphics[scale=.425]{figs/aOneElement.png}}
 \caption{Optimal test functions for a $u=\left.1\right|_K$, where $K = [.5,.7]\times[.4,.6]$.}
 \end{figure}
-\newpage
-\section{Convection-diffusion equation with first-order term}
+
+\section{Test norms for the convection-diffusion equation with first-order term}
+\seclab{appendix:timesteppingConfusion}
 
@@
 \end{proof}
-\section{Non-robustness in traces}
+
+%\section{Conditioning of local matrices}
+
+\section{Error propagation in traces}
 
@@
 Inflow conditions\footnote{$u-\epsilon\pd{u}{n}$ approximates $u$ for $\epsilon\ll 1$.
-These conditions are set such that we are able to use the robust test norm described in \cite{ChanHeuerBui-ThanhDemkowicz12}.} are set such that
+These conditions are set such that we are able to use the robust test norm described in \cite{DPGrobustness2}.} are set such that
 \begin{align*}
@@
 Recall that traces are discretized as traces of $H^1$-conforming trial functions; thus, whereas we expect convergence in the $\L$ norm for field variables, this is not true for the traces.
-In particular, we observe, in the propagation of error, evidence of non-robustness in the trace variables.
+In particular, we observe a Gibbs-type phenomena in the propagation of error for traces in Figure~\ref{fig:traceErrors}.
+Unlike the field variables, Gibbs-type overshoots and undershoots in the solution are not localized to a single element.
+This is due to the increased stencil size for traces, which are not locally supported over one element the way field and flux variables are.
 \begin{figure}
@@
 \caption{$H^1$-type propagation of error along $y = 0$.}
+\label{fig:traceErrors}
 \end{figure}
@@
 
-In \cite{DPGrobustness, ChanHeuerBui-ThanhDemkowicz12}, we proved the energy estimate
+In \cite{DPGrobustness, DPGrobustness2}, we proved the energy estimate
 \[
@@
 \]
-which is a scaled measure of the average of $v$ over an element.  By Holder's inequality, we have that 
+which is a scaled measure of the average of $v$ over an element.  By H\"{o}lder's inequality, we have that 
 \[
@@
 For the locally conservative version of DPG, we were able to replace $\nor{v}^2_{\L}$ in the test norm with $\frac{1}{h^4}\LRb{\int_K v}^2$, because in context of local conservation (enforced by Lagrange multipliers), elementwise constants are already enforced to be in the test space, so the addition of the mean-squared term to the test norm is solely to enforce a scaling condition enforcing a zero-mean condition on the remainder of the test functions.
-
-\section{Anisotropic refinement}
-
-Isotropic adaptive mesh refinement has shown itself to be an effective way to resolve isolated solution features with large gradients, such as point singularities \cite{FindBabuskaPaper}; however, for the resolution of phenomena such as shocks or boundary layers, anisotropic mesh refinement can resolve solution features for a much lower cost per degree-of-freedom, due to the fact that boundary layers in $n$-dimensions are primarily phenomena supported over $n-1$ dimensions.
-
-As a least squares method, DPG already includes a natural error indicator with which to drive adaptive mesh refinement.
-To introduce anisotropic refinements, we need to introduce an anisotropy indicator in order to detect in which direction solution features are aligned.
-In general, a test norm can be expressed as the sum of normed quantities, both scalar and vector valued.
-If we restrict ourselves to quadrilateral elements for the moment, a general anisotropy indicator for DPG can be constructed by evaluating the $\L$ norms of the individual components of vector valued terms in the test norm.
-
-Under the test norm discussed in \cite{ChanHeuerBui-ThanhDemkowicz12} for the convection-dominated diffusion problem, we can define $x$ and $y$ error contributions over a single element
-\begin{align*}
-e_{x,K} &= \epsilon \nor{\pd{v}{x}}_{L^2(K)}^2 + \nor{\tau_x}_{L^2(K)}^2 \\
-e_{y,K} &= \epsilon \nor{\pd{v}{y}}_{L^2(K)}^2 + \nor{\tau_y}_{L^2(K)}^2.
-\end{align*}
-We define the anisotropy indicator as the ratio $r_K = \frac{e_{x,K}}{e_{y,K}}$, and implement a simple refinement scheme following \cite{DPG3}.
-Given some anisotropic threshold $\epsilon_r$, if $r_K>\epsilon_r$, then we can conclude that the error in the $x$ direction is large compared to the $y$ direction, and we anisotropically refine the element along the $x$-axis.
-Likewise, if $r_K < \frac{1}{\epsilon_r}$, this implies that the opposite is true, and we refine the element anisotropically along the $y$-axis.
-
-We note that it is possible to compute the discrete system without needing much additional integration.
-Recall that if we let $G$ be the SPD Gram matrix representing the inner product $\LRp{v,\delta v}_V$ on $V_h$, we solve for degrees of freedom $c_e$ representing our error representation function $e$.
-
-For both the graph and robust test norms, we can decompose the inner product that induces the test norm into 
-\[
-\LRp{v,\delta v}_V = \sum_i \LRp{v,\delta v}_{V,x_i} + \LRp{v,\delta v}_{V,{\rm scalar}}
-\]
-such that $\LRp{v,\delta v}_{V,x_i}$ is a seminorm containing the $i$th coordinate component of a vector-valued test term, and $\LRp{v,\delta v}_{V,{\rm scalar}}$ is simply the non-vector portions of the test norm.
-For example, if we take the $H^1(\Omega)$ Sobolev norm
-\[
-\LRp{v,\delta v}_V = \LRp{v,\delta v}_{\L} + \LRp{\grad v,\grad \delta v}_{\L}
-\]
-then $\LRp{v,\delta v}_{V,x_i} = \LRp{\pd{v}{x_i},\pd{\delta v}{x_i}}_{\L}$, and $\LRp{v,\delta v}_{V,{\rm scalar}} = \LRp{v,\delta v}_{\L}$.
-Each bilinear term $\LRp{v,\delta v}_{V,x_i}$ induces a symmetric positive-semidefinite matrix $G_{x_i}$, such that
-\[
-c_e^TG_{x_i}c_e = \nor{e}^2_{V,x_i}.
-\]
-By storing $G$ as the sum of $G_{\rm scalar}$ and $G_{x_i}$, we can then cheaply compute the anisotropic error indicators once we have the degrees of freedom corresponding to our error representation function.
-
-%\section{Conditioning}
-%
-%Our test norm for convection-diffusion has been
-%\[
-%\nor{v,\tau}_V^2 \coloneqq \alpha\nor{v}_{\L}^2 + \nor{\beta\grad v}_{\L}^2 + \epsilon \nor{\grad v}_{\L}^2 + {\min}\LRc{\frac{1}{\epsilon},\frac{1}{\LRb{K}}}\nor{\tau}_{\L}^2 + \nor{\div \tau}_{\L}^2
-%\]
-%We can see that, when forming the Gram matrix (the discrete Riesz operator) associated with the inner product generating this norm, the $v$ and $\tau$ terms decouple.  
-%\begin{align*}
-%\nor{v}_V^2 &\coloneqq \alpha\nor{v}_{\L}^2 + \nor{\beta\grad v}_{\L}^2 + \epsilon \nor{\grad v}_{\L}^2 = O(h) + O(1) + O(\epsilon)\\
-%\nor{\tau}_V^2 &\coloneqq{\min}\LRc{\frac{1}{\epsilon},\frac{1}{\LRb{K}}}\nor{\tau}_{\L}^2 + \nor{\div \tau}_{\L}^2 = O(
-%\end{align*}
-
-\section{Plate problem}
-\begin{itemize}
-\item Non-local behavior: refinements away from plate edge affect downstream values
-\item Singularities under robust norm: at $h = O(\epsilon)$, for smaller $\epsilon$, singularities in the field variables (even for $u$) develop at the plate edge (loss of control over $\sigma$?)  
-\item Graph norm avoids the above issues with singularity in field solutions.  
-\item Can we mix graph norm + robust norm somehow?  Maybe smoothly mix as $h\rightarrow h_{\min}$?
-\item Flux limiters at singularity?
-\end{itemize}
-
-\bibliographystyle{plain}
-\bibliography{paper}
-
-\end{document}

### 2013-07-22 docs/Jesse/Dissertation/dissAbstract.tex
updating dissertation

%Convection-diffusion problems are problems in which the two transport phenomena convection and diffusion are both present.  Convection is, broadly speaking, the transport of substances or information driven by fluid motion -- for example, the convection of heat via air currents.  Diffusion, in contrast, is the transport of substances or information driven by primarily by concentration gradients -- for example, the diffusion of heat in water is the flow of heat from areas of higher temperature to areas of lower temperature, independent of fluid motion.  Early numerical methods for transport were typically designed for either convection of diffusion in a mutually exclusive manner -- methods for solving a convection problem were typically unstable when solving a diffusion problem, and vice-versa.  Finite element methods in particular, while well-suited to diffusion problems, proved to be ill-suited and unstable for convection problems and convection-dominated diffusion problems.  To address this issue, stabilization terms were introduced to remedy issues with standard finite element methods in the convective regime.  In particular, the SUPG method of Brooks and Hughes \cite{SUPG} introduced the notion of residual-based stabilization to combat such oscillations, and remains one of the most successful methods for solving convection-diffusion problems in the convection-dominated regime.

%The method of focus is the Discontinuous Petrov-Galerkin method, a method introduced in 2009 by Leszek Demkowicz and Jay Gopalakrishnan.  This method falls under the larger class of Dual Petrov-Galerkin methods, in which the minimization of a specific residual (posed in a dual norm) leads naturally to a Petrov-Galerkin formulation, where test functions are automatically tailored in a problem-specific manner.  In particular, the subject of this work is the application and mathematical analysis of DPG as a stable, automatically adaptive higher order finite element method to problems in Computational Fluid Dynamics (CFD).

Over the last three decades, CFD simulations have become commonplace as a tool in the engineering and design of high-speed aircraft.  Experiments are often complemented by computational simulations, and CFD technologies have proved very useful in both the reduction of aircraft development cycles, and in the simulation of conditions difficult to reproduce experimentally.  Great advances have been made in the field since its introduction, especially in areas of meshing, computer architecture, and solution strategies.  Despite this, there still exist many computational limitations in existing CFD methods; in particular, reliable higher order and $hp$-adaptive methods for the Navier-Stokes equations that govern viscous compressible flow.

Solutions to the equations of viscous flow can display shocks and boundary layers, which are characterized by localized regions of rapid change and high gradients.  The use of adaptive meshes is crucial in such settings --- good resolution for such problems under uniform meshes is computationally prohibitive and impractical for most physical regimes of interest.  However, the construction of ``good" meshes is a difficult task, usually requiring a-priori knowledge of the form of the solution.  An alternative to such is the construction of automatically adaptive schemes; such methods begin with a coarse mesh and refine based on the minimization of error.  However, this task is difficult, as the convergence of numerical methods for problems in CFD is notoriously sensitive to mesh quality.  Additionally, the use of adaptivity becomes more difficult in the context of higher order and $hp$ methods \cite{BoeingHigherOrder}.

Many of the above issues are tied to the notion of \emph{robustness}, which we define loosely for CFD applications as the degradation of the quality of numerical solutions on a coarse mesh with respect to the Reynolds number, or nondimensional viscosity. For typical physical conditions of interest for the compressible Navier-Stokes equations, the Reynolds number dictates the scale of shock and boundary layer phenomena, and can be extremely high --- on the order of $10^7$ in a unit domain.  For an under-resolved mesh, the Galerkin finite element method develops large oscillations which prevent convergence and pollute the solution.

The issue of robustness for finite element methods was addressed early on by Brooks and Hughes in the SUPG method \cite{SUPG}, which introduced the idea of residual-based stabilization to combat such oscillations. Residual-based stabilizations can alternatively be viewed as modifying the standard finite element test space, and consequently the norm in which the finite element method converges. Demkowicz and Gopalakrishnan generalized this idea in 2009 by introducing the Discontinous Petrov-Galerkin (DPG) method with optimal test functions, where test functions are determined such that they minimize the discrete linear residual in a dual space.  Under the ultra-weak variational formulation, these test functions can be computed locally to yield a symmetric, positive-definite system.  %The DPG method was quickly used to solve the convection and convection-diffusion problems \cite{DPG1,DPG2,DPG3}, and has recently been shown to yield a robust higher order adaptive method for the convection-diffusion model problem in arbitrary dimensions \cite{DPGrobustness,DPGrobustness2}.

The main theoretical thrust of this research is to develop a DPG method that is provably robust for singular perturbation problems in CFD, but does not suffer from discretization error in the approximation of test functions \cite{DPGrobustness, DPGrobustness2}.  Such a method is developed for the prototypical singular perturbation problem of convection-diffusion, where it is demonstrated that the method does not suffer from error in the approximation of test functions, and that the $L^2$ error is robustly bounded by the energy error in which DPG is optimal -- in other words, as the energy error decreases, the $L^2$ error of the solution is guaranteed to decrease as well.  The method is then extended to the linearized Navier-Stokes equations, and applied to the solution of the nonlinear compressible Navier-Stokes equations.

The numerical work in this dissertation has focused on the development of a 2D compressible flow code under the Camellia library, developed and maintained by Nathan Roberts at ICES \cite{Camellia}.  In particular, we have developed a framework allowing for rapid implementation of problems and the easy application of higher order and $hp$-adaptive schemes based on a natural error representation function that stems from the DPG residual \cite{DPG2, DPG3}.

Finally, the DPG method is applied to several convection diffusion problems which mimic difficult problems in compressible flow simulations, including problems exhibiting both boundary layers and singularities in stresses.  A viscous Burgers' equation is solved as an extension of DPG to nonlinear problems, and the effectiveness of DPG as a numerical method for compressible flow is assessed with the application of DPG to two benchmark problems in supersonic flow.  In particular, DPG is used to solve the Carter flat plate problem and the Holden compression corner problem over a range of Mach numbers and laminar Reynolds numbers using automatically adaptive schemes, beginning with very under-resolved/coarse initial meshes.

### 2013-07-22 docs/Jesse/Dissertation/globalLocalDPG.tex
updating diss figs

--- 2013-03-04 docs/Jesse/GlobalLocalTesting/paper.tex
@@
-%&pdflatex
-\documentclass[11pt,onecolumn]{scrartcl}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
-\usepackage[top=2cm,bottom=3cm,left=2.5cm,right=2cm]{geometry}
-\usepackage{amssymb}
-\usepackage{amscd}
-\usepackage{listings}
-\usepackage{array}
-\usepackage{mathtools}
-\usepackage{dsfont}
-\usepackage{graphicx}
-\usepackage{pdfpages}
-\usepackage[textsize=footnotesize,color=green]{todonotes}
-\usepackage{algorithm, algorithmic}
-\usepackage{array}
-\usepackage{bm}
-\usepackage{tikz}
-\usepackage{subfigure}
-\usepackage[normalem]{ulem}
-
-\newcommand{\bs}[1]{\boldsymbol{#1}}
-\DeclareMathOperator{\diag}{diag}
-
-\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}
-
-\newcommand{\tablab}[1]{\label{tab:#1}}
-\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
-
-\newcommand{\theolab}[1]{\label{theo:#1}}
-\newcommand{\theoref}[1]{\ref{theo:#1}}
-\newcommand{\eqnlab}[1]{\label{eq:#1}}
-\newcommand{\eqnref}[1]{\eqref{eq:#1}}
-\newcommand{\seclab}[1]{\label{sec:#1}}
-\newcommand{\secref}[1]{\ref{sec:#1}}
-\newcommand{\lemlab}[1]{\label{lem:#1}}
-\newcommand{\lemref}[1]{\ref{lem:#1}}
-
-\newcommand{\mb}[1]{\mathbf{#1}}
-\newcommand{\mbb}[1]{\mathbb{#1}}
-\newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\nor}[1]{\left\| #1 \right\|}
-\newcommand{\snor}[1]{\left| #1 \right|}
-\newcommand{\LRp}[1]{\left( #1 \right)}
-\newcommand{\LRs}[1]{\left[ #1 \right]}
-\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
-\newcommand{\LRc}[1]{\left\{ #1 \right\}}
-\newcommand{\LRb}[1]{\left| #1 \right|}
-
-\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
-\newcommand{\Grad} {\ensuremath{\nabla}}
-\newcommand{\Div} {\ensuremath{\nabla\cdot}}
-\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
-\newcommand{\jump}[1] {\ensuremath{\LRs{\!\left[#1\right]\!}}}
-\newcommand{\uh}{\widehat{u}}
-\newcommand{\fnh}{\widehat{f}_n}
-\renewcommand{\L}{L^2\LRp{\Omega}}
-\newcommand{\pO}{\partial\Omega}
-\newcommand{\Gh}{\Gamma_h}
-\newcommand{\Gm}{\Gamma_{-}}
-\newcommand{\Gp}{\Gamma_{+}}
-\newcommand{\Go}{\Gamma_0}
-\newcommand{\Oh}{\Omega_h}
-
-\newcommand{\eval}[2][\right]{\relax
-  \ifx#1\right\relax \left.\fi#2#1\rvert}
-
-\def\etal{{\it et al.~}}
-
-\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
-\newcommand{\tensor}[1]{\underline{\vect{#1}}}
-\newcommand{\del}{\Delta}
-\newcommand{\grad}{\nabla}
-\newcommand{\curl}{\grad \times}
-\renewcommand{\div}{\grad \cdot}
-\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
-\newcommand{\eip}[1]{a\left( #1 \right)}
-\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
-\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
-
-\newcommand{\circone}{\ding{192}}
-\newcommand{\circtwo}{\ding{193}}
-\newcommand{\circthree}{\ding{194}}
-\newcommand{\circfour}{\ding{195}}
-\newcommand{\circfive}{\ding{196}}
-
-\def\arr#1#2#3#4{\left[
-\begin{array}{cc}
-#1 & #2\\
-#3 & #4\\
-\end{array}
-\right]}
-\def\vecttwo#1#2{\left[
-\begin{array}{c}
-#1\\
-#2\\
-\end{array}
-\right]}
-\def\vectthree#1#2#3{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-\end{array}
-\right]}
-\def\vectfour#1#2#3#4{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-#4\\
-\end{array}
-\right]}
-
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-
-\newcommand{\G} {\Gamma}
-\newcommand{\Gin} {\Gamma_{in}}
-\newcommand{\Gout} {\Gamma_{out}}
-
-\newtheorem{remark}{Remark}
-
-\author{Jesse Chan\textsuperscript{a}, Jay Gopalakrishnan\textsuperscript{b}, and Leszek Demkowicz\textsuperscript{a}}
-
-%\title{$\epsilon$-explicit analysis of DPG for convection-dominated diffusion}
-\title{Global properties of DPG test spaces for convection-diffusion problems}
-\date{}
-\begin{document}
-
-\maketitle
-\begin{center}
-\textsuperscript{a} Institute for Computational Engineering and Sciences, \\University of Texas at Austin, \\Austin, TX 78712, USA\\
-\end{center}
-
-\begin{center}
-\textsuperscript{b} Department of Mathematics\\Portland State University, \\
-Portland, OR 97207, USA
-%\textsuperscript{b} Facultad de Matem\'aticas, \\Pontificia Universidad Cat\'olica de Chile,\\
-%Avenida Vicu\~na Mackenna 4860, Santiago, Chile
-\end{center}
-
-%\tableofcontents
-
-\section{Introduction to DPG}
-
-The Discontinuous Petrov-Galerkin method was originally introduced by Demkowicz and Gopalakrishnan in 2009 as a way to attain automatic inf-sup stability for any well-posed variational problem through the construction of optimal test functions \cite{DPG2}.
-The method was later shown to be equivalent to the minimum residual method applied to the operator residual corresponding to a variational formulation \cite{DPG2, ChanHeuerBui-ThanhDemkowicz12}.
-A more detailed overview of the current state of DPG is available at \cite{overviewDPG}; we give only a brief introduction here.
-
-The derivation of the DPG method can be briefly summarized as follows: assume we are given a trial space $U$, a discrete trial space $U_h \subset U$, a Hilbert test space $V$, and a well-posed (in the inf-sup sense) variational problem: find $u\in U$  such that
-\begin{align}
-\label{variational}
-&b(u,v) = l(v), \quad \forall v\in V, 
-\end{align}
-where $b(u,v)$ is a bilinear form and $l \in V'$.
-If we identify the variational operator $B: U\rightarrow V'$ such that $\LRa{Bu,v} \coloneqq b(u,v)$, we can write the above variational formulation as an operator equation in $V'$
-\[
-Bu = l,
-\]
-where inf-sup well-posedness of the variational formulation translates to boundedness from above and below of the operator $B$.
-
-Let $u_h \in U_h$ now be a discrete approximation to $u$. Seeking the minimization of the discrete residual $\frac{1}{2} \nor{Bu_h-l}^2_{V'}$, we arrive at the normal equations 
-\begin{equation}
-\label{dualNormal}
-\LRp{Bu_h-l,B\delta u}_{V'} = 0, \quad \forall \delta u \in U_h.  
-\end{equation}
-Since $V$ is Hilbert, we can introduce the Riesz map $R_V:V \rightarrow V'$, an isometric isomorphism such that $\LRa{R_V v,\cdot} = \LRp{v,\cdot}_V$.
-By taking the inverse of the Riesz map, we can transform the normal equations in $V'$ to a set of normal equations in $V$
-\[
-\LRp{R_V^{-1}\LRp{Bu_h-l},R_V^{-1}\LRp{B\delta u}}_{V} = 0, \quad \forall \delta u \in U_h.  
-\]
-Using the definitions of the Riesz map $R_V$ and variational operator $B$, we have that
-\begin{align*}
-\LRp{R_V^{-1}\LRp{Bu_h-l},R_V^{-1}\LRp{B\delta u}}_{V} = 0, \quad \forall \delta u \in U_h \\
-\rightarrow \LRa{Bu_h-l,R_V^{-1}\LRp{B\delta u}}_{V} = 0, \quad \forall \delta u \in U_h \\
-\rightarrow b\LRp{u_h,R_V^{-1} B\delta u} - l\LRp{R_V^{-1} B\delta u} = 0, \quad \forall \delta u \in U_h.
-\end{align*}
-In other words, the minimization of the operator residual associated with a given variational form corresponds directly to a Petrov-Galerkin formulation, where test functions are determined under the so-called \textit{trial-to-test} operator $R_V^{-1}B$, which, given functions in the discrete trial space $U_h$,  returns back corresponding test functions which span the discrete test space.
-
-Solutions $u$ to the above problem enjoy the following properties: 
-\begin{enumerate}
-\item If we define the energy norm 
-\[
-\nor{u}_E = \nor{Bu}_{V'} = \sup_{v\in V\setminus\{0\}}\frac{\LRb{b(u,v)}}{\nor{v}_V},
-\]
-then DPG is optimal in the energy norm $\nor{u}_E$, which is induced through the energy inner product
-\[
-\LRp{v,w}_E = \LRp{Bv,Bw}_{V'} = \LRp{R_V^{-1}Bv, R_V^{-1}Bw}_V.
-\]
-\item The exact energy error $\nor{u-u_h}_E$ is computable without knowing $u$ explicitly, owing to the fact that
-\[
-\nor{u-u_h}_E = \nor{B(u-u_h)}_{V'} = \nor{{l-Bu_h}}_{V'} = \sup_{v\in V\setminus\{0\}}\frac{l(v)-b(u,v)}{\nor{v}_V},
-\]
-which can be computed by first computing an \textit{error representation function} $e$ and then evaluating $\nor{e}_V$.  The error representation function is determined by solving the problem
-\[
-\LRp{e,\delta v}_V = l(\delta v)-b(u,\delta v), \quad \delta v\in V.
-\]
-This property is simply a result of the minimum residual nature of DPG; the energy error is simply the residual, measured in the proper norm.  
-\item Let $\{u_i\}_{i = 0}^{i = N}$ be discrete trial functions and $v_{u_i}$ be the corresponding optimal test functions (solutions of Problem (\ref{aux}) below).
-The discrete system resulting from DPG is symmetric positive-definite; this can be seen from the identity
-\[
-b(u_i,v_{u_j}) = \LRp{v_{u_i},v_{u_j}}_V = \LRp{v_{u_j},v_{u_i}}_V = b(u_j,v_{u_i}).
-\]
-Positive-definiteness is again a natural consequence of the minimum-residual nature of DPG.  
-\end{enumerate}
-
-\subsection{Broken test spaces}
-
-To determine test functions under DPG, we must invert the Riesz map by determining $R_V^{-1} B\delta u$, which is done by solving the auxiliary variational problem
-\begin{equation}
-\label{aux}
-(v,\delta v)_V = b\LRp{\delta u,\delta v}, \quad \forall \delta v\in V.  
-\end{equation}
-Unfortunately, this amounts to both an infinite-dimensional and global problem if $V$ is not chosen carefully.
-For example, if $V = H^1(\Omega)$ and $\LRp{\cdot, \cdot }_V$ corresponded to the $H^1$ Sobolev inner product  $\LRp{v,\delta v}_{L^2(\Omega)} + \LRp{\grad v,\grad \delta v}_{L^2(\Omega)}$, solving for a single optimal test function would be equivalent to solving the Poisson equation exactly over the entire domain.
-However, we can both localize and make solving Problem~(\ref{aux}) computationally feasible by choosing for $V$ a \textit{broken} test space and by approximating the solution to (\ref{aux}) using a discrete space $V_h\subset V$.
-
-We begin by assuming we are given some triangulation $\Omega_h$ of $\Omega$ such that $\bar{\Omega} = \bigcup_{K\in \Omega_h}\bar{K}$.  We can adopt for $V$ the broken test space
-\[
-V(\Oh) = \bigoplus_{K\in \Omega_h}V(K).
-\]
-If we further assume that the inner product and norm on $V$ are localizable\footnote{A localizable norm $\nor{v}_{V(\Oh)}$ can be written in the form 
-$$\nor{v}_{V(\Oh)}^2 = \sum_{K\in\Oh} \nor{v}_{V(K)}^2,$$ where $\nor{v}_{V(K)}$ is a norm over the element $K$.}, the solution to \eqref{aux} (corresponding to the inversion of the Riesz map) can now be determined locally over each element.
-In practice, these solutions are approximated by solving (\ref{aux}) over a locally conforming space $V_h$ over each element $K$, where $\dim(V_h) > \dim(U_h)$ elementwise.
-Typically, if $U_h$ is of order $p$, $V_h$ is chosen to be the corresponding $H^1$ or $H({\rm div})$ conforming space of order $p + \del p$, where $\del p \geq n$, the spatial dimension \cite{practicalDPG}.
-For this reason, we refer to $V_h$ as the \textit{enriched} space.
-We refer to this approximated test space under $V_h$ as the approximate optimal test space $V_{{\rm opt},h}$.
-\begin{remark}
-All properties of DPG carry over if $V=V_h$, the discrete inner product space, and if Problem~(\ref{aux}) is well-approximated under $V_h$, then the solution to our variational problem (\ref{variational}) over the approximate optimal test space will deliver very similar results to the solution of (\ref{variational}) over the exact optimal test space.
-\end{remark}
-
-\subsection{The ultra-weak variational formulation}
-
-Up to now, the variational formulation has been left unspecified.
-For several reasons, we've chosen to use the \textit{ultra-weak formulation}, which results from writing the PDE as a first-order system, integrating all derivatives by parts, and identifying boundary traces as independent unknowns, similarly to hybridized DG methods.
-The formulation is given as follows: let $$\Gh = \bigcup_{K\in \Oh} \partial K$$ be the \textit{mesh skeleton}, comprising of the union of all element boundaries.
-Let $Au=f$ represents the strong form of a first-order system of PDEs; the ultra-weak formulation is then
-\begin{equation}
-\label{variationalProblem}
-b\LRp{\LRp{u,\uh},v} = \LRp{u,A_h^*v}_{\Oh} + \sum_{K \in \Oh} \LRa{\uh,v}_{\partial K} = \LRp{f,v}_{\Omega},
-\end{equation}
-where $u \in \L$, and $A_h^*$ is the formal adjoint of $A$ acting elementwise on a broken test space, and $\LRa{\uh,v}_{\partial K}$ is the duality pairing between the trace unknown $\uh$ and the trace of the test function $v$ on an element boundary.
-Under proper regularity assumptions, we have that
-$$\sum_{K \in \Oh} \LRa{\uh,v}_{\partial K} = \LRa{\uh,\jump{v}}_{\Gh}.$$    %so $\uh \in \gamma(D\LRp{A})$, the trace space of the domain of the strong operator $A$.  
-Finally, $\uh$ represents the trace of the conforming solution to $Au=f$ on the mesh skeleton $\Gh$; if we define the graph space $H_A \coloneqq \LRc{u \in U: Au\in \L},$ then $\uh$ comes from $ \widehat{H}_A(\Gh)$, the trace space of $H_A$ on $\Gh$
-\[
-\widehat{H}_A(\Gh) \coloneqq \LRc{ \left.u\right|_{\Gh}: u\in H_A}.
-\]
-
-Combining this variational formulation with the concept of DPG optimal test functions yields a conforming method for $u$, the field variable, and $\uh$, the trace variable.
-Optimal test functions are all determined locally, and optimal test functions corresponding to traces defined on the element boundary $\partial K$ have support over each element adjacent to $\partial K$.
-The degrees of freedom are thus coupled together globally through the optimal test functions for trace variables.
-
-\begin{remark}
-\label{remarkDahmen}
-It is possible to apply the same minimum-residual method behind DPG in an alternative fashion by casting the normal equations as a saddle-point problem, which is the approach taken by Dahmen et al.\ in \cite{DahmenVariationalStabilization}.
-This method requires the solution of a larger global linear system than the DPG method, but can be directly applied to arbitrary variational formulations and conforming discretizations of $V$.
-\end{remark}
-
-\subsection{The graph test norm}
-
-We have not yet specified the inner product $\LRp{v,\delta v}_V$, which induces the norm defining the space $V$.
-Here, we derive two important ``canonical" test norms for the ultra-weak variational formulation.
-We begin first with the canonical norm in $U$.
-Since $\uh \in \widehat{H}_A(\Gh)$, the standard norm for $\uh$ is the so-called minimum energy extension norm defined as
-\begin{equation*}
-\|\widehat{u}\| = \inf_{w\in \widehat{H}_A(\Gamma_h),
-  \left.w\right|_{\Gh}=\widehat{u}} \|w\|_{\widehat{H}_A}.
-\end{equation*}
-The canonical norm for the group variable $\LRp{u,\uh}$ is then given by
-\[
-\|\left(u,\widehat{u}\right)\|_U^2 = \|u\|^2_{\L} + \|\widehat{u}\|^2.
-\]
-If we define the norm $\nor{v}_{V,U}$  through
-\[
-\nor{v}_{V,U}^2 = \|A_h^*v\|_{\L}^2
-+\left(\sup_{\widehat{u} \in \widehat{H}_A(\Gamma_h)} \frac{\LRa{ \widehat{u},
-  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2, 
-\]
-it has been shown in \cite{Bui-ThanhDemkowiczGhattas11a, ChanHeuerBui-ThanhDemkowicz12} that the canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ induces (generates) the norm $\nor{v}_{V,U}$ in $V$; in other words, the energy norm in which DPG is optimal is equal to the canonical norm $\nor{\LRp{u,\uh}}_U$ if we choose for a test norm on $\nor{v}_{V,U}$.
-
-The canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ provides an optimal balance between the standard norms on the field $u$ and the flux $\uh$ \cite{DPG4}.
-As a result, if the induced norm $\nor{v}_{V,U}$ (namely, the optimal test norm) is used to compute optimal test functions in (\ref{aux}), the finite element error in the canonical norm is the best in the norm $\nor{u}_{U}$.
-Unfortunately, the optimal test norm is non-localizable due to the presence of the jump term $\jump{v}$.
-Since the jump terms couple elements together, the evaluation of the jump terms requires contributions from all the elements in the mesh.
-Consequently, solving for an optimal test function amounts to inverting the Riesz map over the entire mesh $\Oh$, making the optimal test norm impractical.
-
-On the other hand, since $A^*_h v \in \L$, we can use as a test norm for $v$ the broken graph test norm: 
-\[
-\nor{v}_V^2 =  \|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2,
-\]
-where we have regularized the seminorm $\nor{A_h^*v}_{\L}^2$ by adding to it the $L^2$ norm of $v$.
-
-The norm $\nor{v}_V$ can be considered as a localization of $\nor{v}_{V,U}$ to allow for the solution of optimal test functions on an element-by-element basis, and can be considered to be the canonical norm on $V$.
-In the DPG literature \cite{DPG4}, $\nor{v}_{V,U}$ is known as the {\em optimal test norm}, while $\nor{v}_{V}$ is known as the quasi-optimal or {\em graph} test norm.
-The DPG method was first shown to be well-posed under the graph test norm for the Poisson and convection-diffusion equations in \cite{analysisDPG}.
-This analysis was later extended to the large class of Friedrichs' systems in \cite{Bui-ThanhDemkowiczGhattas11b} and to Stokes in \cite{stokesDPG}.
-
-It has also been shown in \cite{stokesDPG} that $\nor{v}_{V,U}$ and $\nor{v}_V$ are equivalent norms; if the operator $A$ is bounded below such that $\nor{Au}_{\L} \geq \gamma\nor{v}_{\L}$, then the equivalence constants between $\nor{v}_{V,U}$ and $\nor{v}_V$ are $O(\gamma)$.
-This is important in context of \textit{singular perturbation problems}, which typically depend on some parameter $k\rightarrow 0$ or $k\rightarrow \infty$; if the constant $\gamma$ associated with the problem is independent of $k$, then the DPG method under the graph test norm is \textit{robust}, or equivalent to the $\L$-projection with constants independent of $k$.
-Robustness is discussed more in Section~\ref{sec:robust} in context of the convection-diffusion equation.
-
-\section{The ultra-weak formulation and globally conforming test spaces}
-
-Though DPG test functions are determined locally on an element-by-element basis, it is the global properties of the test space that determine the performance of the method.
-We motivate this statement first by deriving global conditions for the test space under which the ultra-weak variational formulation recovers an $L^2$ optimal solution, using the specific example of the convection-diffusion equation.
-
-\subsection{The convection-diffusion equation}
-
-The convection-diffusion problem models the concentration $u$ of some solvent in a convection field $\beta$ subject to diffusion of some magnitude $\epsilon > 0$ in some domain $\Omega$ with boundary $\Gamma$.
+%\subsection{The convection-diffusion equation}
+%
+%The convection-diffusion problem models the concentration $u$ of some solvent in a convection field $\beta$ subject to diffusion of some magnitude $\epsilon > 0$ in some domain $\Omega$ with boundary $\Gamma$.
 We decompose the boundary as follows:
-\begin{align*}
-\Gamma_{\rm in} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\}, \quad {\rm
-(inflow)}\\ 
-\Gamma_{\rm out} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\},
-\quad {\rm (outflow)}\\
-\Gamma_{0} &\coloneqq \{x\in \Gamma;\beta_n(x) = 0\},
-\end{align*}
-where $\beta_n \coloneqq \beta \cdot n$.
-
-The problem is typically written in as
-\begin{align*}
-\div\LRp{\beta u - \epsilon \grad u} &= f, \quad \text{in } \Omega \\
-u &= u_{0}, \quad \text{on } \Gamma.
-\end{align*}
-The problem is especially of interest as a prototypical problem for boundary layer problems in computational fluid dynamics, as solutions to the convection-diffusion problem can, for certain boundary conditions, develop strong boundary layers of width $\epsilon$ at the outflow boundary $\Gamma_{\rm out}$.
-
-We can further write it as a system of first-order equations
-\begin{align*}
-\div\LRp{\beta u - \sigma} &= f\\
-\frac{1}{\epsilon}\sigma - \grad u &= 0.
-\end{align*}
-This first order system is the starting point for the ultra-weak variational formulation, which, under the convection-diffusion equation and prior to the application of boundary data, is given as 
-\begin{align*}
-b\LRp{\LRp{u,\sigma, \uh, \fnh}, \LRp{v,\tau}} &=\LRa{\uh,\tau_n}_{\Gh} + \LRa{\fnh,v}_{\Gh} + \\ & \LRp{u, \Grad_h\cdot \tau - \beta\cdot \Grad_h v}_{\L} + \LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad_h v}_{\L}.
-\end{align*}
-where $\fnh \coloneqq \beta_n u - \sigma_n$.  Trial and test spaces are specified to be 
-\begin{align*}
-\LRp{u,\sigma} \in \L, \fnh \in H^{-1/2}(\Gh), \uh \in H^{1/2}(\Gh)&,\\ 
-v \in H^1(\Oh), \tau \in H\LRp{\rm div, \Oh}&,
-\end{align*}
-where $H^1(\Oh)$ and $H\LRp{\rm div, \Oh}$ represent the broken $H^1$ and $H(\rm div)$ spaces over $\Oh$.
+%\begin{align*}
+%\Gamma_{\rm in} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\}, \quad {\rm
+%(inflow)}\\ 
+%\Gamma_{\rm out} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\},
+%\quad {\rm (outflow)}\\
+%\Gamma_{0} &\coloneqq \{x\in \Gamma;\beta_n(x) = 0\},
+%\end{align*}
+%where $\beta_n \coloneqq \beta \cdot n$.
+%
+%The problem is typically written in as
+%\begin{align*}
+%\div\LRp{\beta u - \epsilon \grad u} &= f, \quad \text{in } \Omega \\
+%u &= u_{0}, \quad \text{on } \Gamma.
+%\end{align*}
+%The problem is especially of interest as a prototypical problem for boundary layer problems in computational fluid dynamics, as solutions to the convection-diffusion problem can, for certain boundary conditions, develop strong boundary layers of width $\epsilon$ at the outflow boundary $\Gamma_{\rm out}$.
+%
+%We can further write it as a system of first-order equations
+%\begin{align*}
+%\div\LRp{\beta u - \sigma} &= f\\
+%\frac{1}{\epsilon}\sigma - \grad u &= 0.
+%\end{align*}
+%This first order system is the starting point for the ultra-weak variational formulation, which, under the convection-diffusion equation and prior to the application of boundary data, is given as 
+%\begin{align*}
+%b\LRp{\LRp{u,\sigma, \uh, \fnh}, \LRp{v,\tau}} &=\LRa{\uh,\tau_n}_{\Gh} + \LRa{\fnh,v}_{\Gh} + \\ & \LRp{u, \Grad_h\cdot \tau - \beta\cdot \Grad_h v}_{\L} + \LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad_h v}_{\L}.
+%\end{align*}
+%where $\fnh \coloneqq \beta_n u - \sigma_n$.  Trial and test spaces are specified to be 
+%\begin{align*}
+%\LRp{u,\sigma} \in \L, \fnh \in H^{-1/2}(\Gh), \uh \in H^{1/2}(\Gh)&,\\ 
+%v \in H^1(\Oh), \tau \in H\LRp{\rm div, \Oh}&,
+%\end{align*}
+%where $H^1(\Oh)$ and $H\LRp{\rm div, \Oh}$ represent the broken $H^1$ and $H(\rm div)$ spaces over $\Oh$.
 This is discussed in more detail for the convection-diffusion equation in \cite{DPGrobustness, ChanHeuerBui-ThanhDemkowicz12}.
-
-For the case of boundary data $\uh = u_0$ on the entire boundary $\Gamma$, our variational formulation becomes
-\begin{align*}
-\LRa{\uh,\tau_n}_{\Gh^0} + \LRa{\fnh,v}_{\Gh} + \LRp{u, \Grad_h\cdot \tau - \beta\cdot \Grad_h v} + \LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad_h v} = \LRp{f,v} + \LRa{u_0,\tau_n}_{\Gamma}, 
-\end{align*}
-where $\Gh^0 = \Gh\setminus \Gamma$ is the union of all internal element edges, and is referred to as the internal skeleton, and $\Grad_h$ and $\Grad_h\cdot$ are understood to be the broken gradient and divergence, taken over each individual element.
+%
+%For the case of boundary data $\uh = u_0$ on the entire boundary $\Gamma$, our variational formulation becomes
+%\begin{align*}
+%\LRa{\uh,\tau_n}_{\Gh^0} + \LRa{\fnh,v}_{\Gh} + \LRp{u, \Grad_h\cdot \tau - \beta\cdot \Grad_h v} + \LRp{\sigma, \frac{1}{\epsilon}\tau + \Grad_h v} = \LRp{f,v} + \LRa{u_0,\tau_n}_{\Gamma}, 
+%\end{align*}
+%where $\Gh^0 = \Gh\setminus \Gamma$ is the union of all internal element edges, and is referred to as the internal skeleton, and $\Grad_h$ and $\Grad_h\cdot$ are understood to be the broken gradient and divergence, taken over each individual element.
 We have also dropped the subscript for $\LRp{\cdot,\cdot}_{L^2(\Omega)}$ and, for the rest of the paper, simply refer to the $L^2$ inner product using the notation $\LRp{\cdot,\cdot}$.
@@
 \[
-\nor{v}_{V_{\rm graph}}^2 = \nor{\grad_h\cdot\tau - \beta \cdot \grad_h v}_{L^2(\Omega)}^2 + \nor{{\epsilon}^{-1} \tau -  \grad_h v}_{L^2(\Omega)}^2 + \nor{v}_{L^2(\Omega)}^2
+\nor{\LRp{v,\tau}}_{V_{\rm graph}}^2 = \nor{\grad_h\cdot\tau - \beta \cdot \grad_h v}_{L^2(\Omega)}^2 + \nor{{\epsilon}^{-1} \tau -  \grad_h v}_{L^2(\Omega)}^2 + \nor{v}_{L^2(\Omega)}^2, 
 \]
-where $\grad_h$ and $\div_h$ are understood to act elementwise.\footnote{Since $\nor{A^*_hv}$ is not positive definite on its own, we typically add an $L^2$ term for all components of the test function; however, here the $L^2$ norm of $\tau$ is neglected as it is not required to preserve positive-definiteness of the norm.}
+where $\grad_h$ and $\grad_h\cdot$ are understood to act elementwise.\footnote{Since $\nor{A^*_hv}$ is not positive definite on its own, we typically add an $L^2$ term for all components of the test function; however, here the $L^2$ norm of $\tau$ is neglected as it is not required to preserve positive-definiteness of the norm.}
 
@@
 \[
-\left.A_h^*v\right|_K = \LRp{\div\tau - \beta \cdot \grad v, {\epsilon}^{-1} \tau -  \grad v}, \quad \text{on } K \in \Oh.
+\left.A_h^*v\right|_K = \LRp{\div\tau - \beta \cdot \grad v, {\epsilon}^{-1} \tau -  \grad v} \quad \text{on } K \in \Oh.
 \]
@@
 \begin{align*}
-b\LRp{\LRp{u,\uh},v} &\coloneqq \LRa{\uh,v} + \LRp{u,A^*_h v}_{\L} \\
+b\LRp{\LRp{u,\uh},v} &\coloneqq \LRa{\uh,\jump{v}} + \LRp{u,A^*_h v}_{\L} \\
 \nor{v}_V^2 &\coloneqq \nor{A_h^*v}_{\L}^2 + \nor{v}_{\L}^2
@@
 Note that in these definitions, we have chosen both trial and test functions from the fully conforming spaces $H({\rm div};\Omega)$ and $H^1(\Omega)$ over $\Omega$.
-Let us define the spaces ${U} = {V} = H^1(\Omega) \times H({\rm div};\Omega)$ as the \textit{conforming} spaces for which the inter-element jumps $\LRa{\uh,\tau_n}_{\Gh^0}$ and $\LRa{\fnh,v}_{\Gh^0}$ both vanish.
+Let us define the spaces ${U} = {V} = H^1(\Omega) \times H({\rm div};\Omega)$ as the \textit{conforming} spaces for which the inter-element jumps $\LRa{\uh,\jump{\tau_n}}_{\Gh^0}$ and $\LRa{\fnh,\jump{v}}_{\Gh^0}$ both vanish.
 If we again overload notation by defining ${u} \coloneqq \LRp{u,\sigma}^T\in {U}$ and ${v} \coloneqq \LRp{v,\tau} \in {V}$, and define the operator $A$ and its adjoint $A^*$ through
@@
 \begin{align*}
-\div \tau - \beta\cdot \Grad v &= u_i\\
-\frac{1}{\epsilon}\tau + \Grad v &= \sigma_i\\
-v &= 0, \quad \text{on } \Gamma,
+\div \tau - \beta\cdot \Grad v &= u_i,\\
+\frac{1}{\epsilon}\tau + \Grad v &= \sigma_i,\\
+v &= 0 \quad \text{on } \Gamma,
 \end{align*}
@@
 
-%
-%%For boundary data $\uh_0$ enforced on $\Gamma_0 \subset \Gamma$, our corresponding variational formulation is 
-%\begin{equation*}
-%b\LRp{\LRp{u,\uh},v} = \LRp{u,A_h^*v}_{\Omega} + \LRa{\uh,\jump{v}}_{\Gh} = \LRp{f,v}_{\Omega}.
-%\end{equation*}
-%We introduce the operator $C_{\rm BC}$, which is defined such that $C_{\rm BC}\uh$ is the quantity on which boundary conditions $C_{\rm BC}\uh = Cu_0$ are to be applied.
-We can then define a second operator $C$ such that $\LRa{C\uh,\jump{v}}_{\Gamma} = \LRa{\uh,\jump{v}}_{\Gamma} - \LRa{C_{\rm BC}\uh,\jump{v}}_{\Gamma}$, and our formulation becomes
-%\begin{equation*}
-%b\LRp{\LRp{u,\uh},v} = \LRp{u,A_h^*v}_{\Omega} + \LRa{\uh,\jump{v}}_{\Gh^0} + \LRa{\uh,C'\jump{v}}_{\Gamma}= \LRp{f,v}_{\Omega} - \LRa{Cu_0,v}_{\Gamma}.
-%\end{equation*}
-%where $C'$ is the adjoint of $C$ under the duality pairing $\LRa{\cdot,\cdot}$, and $\Gh^0$ is the internal skeleton, or the mesh skeleton minus the domain boundary.
-The goal of this above notation is to allow for a generalized treatment of boundary conditions, where $\LRa{C_{\rm BC}\uh,\jump{v}}_{\Gamma}$ can represent operations such as the extraction of a component of a vector-valued $\uh$ or the restriction of to a section of the boundary.
-For a more rigorous and detailed exposition of the above notation, see \cite{stokesDPG,overviewDPG}.
-%
-%We define the subspace $V_0 \subset V$ as elements of $V$ for which the remaining boundary term $\LRa{\uh,C'\jump{v}}_{\Gamma}$ vanishes: 
-%\[
-%V_0 = \{v\in V : \LRa{\uh,C'\jump{v}}_{\Gamma}= 0, \forall (\uh,0)\in U\}.
-%\]
-%For standard Galerkin formulations, this space is analogous to the homogenous space (the complement of the lift space) for essential boundary conditions.  
-%
-%Suppose now that our test functions come from a \textit{conforming} subspace of $V_0$ - in other words, that
-%\begin{align*}
-%\LRa{\uh,\jump{v}}_{\Gh^0} &= 0, \quad \forall \uh \in \gamma(D(A))
-%%\LRa{\uh,\jump{v}}_{\Gh\setminus \Gamma_0} = 0, \quad \forall \uh \in \gamma(D(A))
-%\end{align*}
-%is additionally satisfied over the internal skeleton ${\Gh^0}$.  
-%%is satisfied over $\Gh\setminus \Gamma_0$.  
-%In this case, the inter-element boundary terms vanish, $A^*_h v$ becomes $A^*v$, and the variational formulation becomes
-%\begin{align*}
-%%b\LRp{\LRp{u,\uh},v} = \LRp{u,A^*v}_{\Omega} + \LRa{\uh,\jump{v}}_{\Gamma \setminus \Gamma_0} = \LRp{f,v}_{\Omega} - \LRa{\widehat{u}_0,\jump{v}}_{\Gamma_0}.
-%%b\LRp{\LRp{u,\uh},v} = \LRp{u,A^*v}_{\Omega} = \LRp{f,v}_{\Omega} - \LRa{\widehat{u}_0,\jump{v}}_{\Gamma_0}.
-%b\LRp{\LRp{u,\uh},v} = \LRp{u,A^*v}_{\Omega} = \LRp{f,v}_{\Omega}.
-%\end{align*}
-%Let $\bar{V}$ be a conforming subspace of $V_0$ such that 
-%%$\bar{V} = \{\bar{v}\in V: \LRa{\uh,\jump{\bar{v}}}_{\Gh\setminus\Gamma_0} = 0, \forall \LRp{0,\uh}\in U\}$.  
-%$\bar{V} = \{\bar{v}\in V_0: \LRa{\uh,\jump{\bar{v}}}_{\Gh^0} = 0, \forall \LRp{0,\uh}\in U\}$.  
-%If we seek $u_h \in U_h$ and if our discrete test space is chosen to be 
-%\[
-%\bar{V}_{\rm opt} = \{\bar{v}_{\delta u} \in \bar{V}: A^*\bar{v}_{\delta u} = \delta u, \forall \delta u \in U_h\},
-%\]
-%%\[
-%%\bar{V}_{\rm opt} = \{\bar{v}_{\delta u} \in \bar{V}: \delta u \in U_h\},
-%%\]
-%%where each test function $v_{\delta u}$ satisfies the following adjoint equation 
-%%\begin{align*}
-%%A^*v_{\delta u} &= \delta u, \\
-%%\left.v_{\delta u}\right |_{\Gamma\setminus\Gamma_0} &= 0,
-%%\end{align*}
-%then our variational problem reduces to
-%\[
-%\LRp{u_h,\delta u}_{\Omega} = \LRp{f,v}_{\Omega} = \LRp{u,\delta u}_{\Omega}, \quad \forall \delta u \in U_h
-%\]
-%and the solution $u_h$ is the $L^2$ projection of the exact solution $u$ onto $U_h$.
-
-\section{Globally conforming DPG test spaces}
+\subsection{Globally conforming DPG test spaces}
 
 As noted above, $L^2$ optimality is achieved when the test space possesses certain \textit{global} properties.
-An obvious question concerning DPG is how much non-local information can be gleaned from locally generated test spaces.\footnote{Global properties of the test norm are related to the adjoint equation, as shown in \cite{DPGrobustness, ChanHeuerBui-ThanhDemkowicz12}.
+An obvious question concerning DPG is how much non-local information can be gleaned from locally generated test spaces.\footnote{Global properties of the test norm are related to the adjoint equation, as shown in \cite{DPGrobustness}.
 However, global properties of the test space have not been explored specifically in these prior works.}
@@
 be the space of optimal test functions determined \textit{globally} over the weakly conforming space $\tilde{V}$.
-In other words, the optimal test functions that span $\tilde{V}_{\rm opt}$ are the result of the inversion of the Riesz operator \textit{globally}, over the entire mesh (the idea is not new - the concept of globally optimal test functions was first introduced in \cite{DPG3pub} to prove mesh-independence).
-The following lemma concerning the test space spanned by the locally computed optimal test functions of DPG was proven first by Demkowicz and Gopalakrishnan in \cite{overviewDPG}, which we reproduce briefly here:
+In other words, the optimal test functions that span $\tilde{V}_{\rm opt}$ are the result of the inversion of the Riesz operator \textit{globally}, over the entire mesh (the idea is not new -- the concept of globally optimal test functions was first introduced in \cite{DPG3} to prove mesh-independence).
+The following lemma concerning the test space spanned by the locally computed optimal test functions of DPG was proven first by Demkowicz and Gopalakrishnan in \cite{overviewDPG}, which we reproduce briefly here.
 \begin{lemma}
@@
 \[
-\LRp{v_{\uh},v_{\rm opt}^\perp}_{V(\Oh)} = \LRa{\uh,\jump{v_{\rm opt}^\perp}}_{\Gh^0} = 0,
+\LRp{v_{\uh},v_{\rm opt}^\perp}_{V(\Oh)} = \LRa{\uh,\jump{v_{\rm opt}^\perp}}_{\Gh^0} = 0.
 \]
@@
 
-Lemma~\ref{lemma1} has an immediate consequence concerning DPG solutions under weakly conforming test spaces: 
+Lemma~\ref{lemma1} has an immediate consequence concerning DPG solutions under weakly conforming test spaces.
 \begin{lemma}
@@
 \begin{proof}
-This can be shown by taking the variational problem (\ref{variational}) for $u$ and $\widehat{u}$; since $\tilde{V}_{\rm opt} \subseteq V_{\rm opt}$, we can substitute in for $v$ the weakly conforming optimal test functions spanning $\tilde{V}_{\rm opt}$.
-Doing so reduces (\ref{variational}) to the problem for $\tilde{u}$.
+This can be shown by taking the variational problem $b(\LRp{u,\uh},v)=l(v)$ for $u$ and $\widehat{u}$; since $\tilde{V}_{\rm opt} \subseteq V_{\rm opt}$, we can substitute in for $v$ the weakly conforming optimal test functions spanning $\tilde{V}_{\rm opt}$.
+Doing so reduces $b(\LRp{u,\uh},v)=l(v)$ to the problem for $\tilde{u}$.
 \end{proof}
@@
 
-Finally, DPG can also be viewed as a non-conforming method over $V$ under another perspective: as mentioned in Remark~\ref{remarkDahmen}, work by Dahmen et al.\ in \cite{DahmenVariationalStabilization} uses the same functional setting as DPG; however, their starting point is to view the above problem into a saddle point system.
-Defining the error $e = R_V^{-1}\LRp{l-Bu} \in V'$, Problem (\ref{dualNormal}) can be written as follows: solve for $\LRp{e,u_h}$ such that
+Finally, DPG can also be viewed as a non-conforming method over $V$ under another perspective: work by Dahmen et al.\ in \cite{DahmenVariationalStabilization} uses the same functional setting as DPG; however, their starting point is to view the above problem into a saddle point system.
+Defining the error $e = R_V^{-1}\LRp{l-Bu} \in V'$, the variational problem with optimal test functions can be written as follows: solve for $\LRp{e,u_h}$ such that
 \begin{align*}
-\LRp{e,\delta v}_V + b(u_h,\delta v)&= l(\delta v),\quad \delta v \in V\\
-b(\delta u, e) &= 0, \quad \delta u \in U_h
+\LRp{e,\delta v}_V + b(u_h,\delta v)&= l(\delta v),\quad \delta v \in V,\\
+b(\delta u, e) &= 0, \quad \delta u \in U_h.
 \end{align*}
@@
 \begin{align*}
-\LRp{e,\delta v}_{V(K)} + \LRp{u_h,A^*_h\delta v}_{L^2{\Omega}} + \LRa{\uh_h,v}_{\Gh}- l(\delta v) &= 0, \quad \delta v \in V(K),\,\, \quad \forall K\in \Oh\\
-\LRp{\delta u, A_h^*e}_{L^2(K)} &= 0, \quad \LRp{\delta u,0} \in U_h, \quad \forall K\in \Oh\\
-\LRa{\widehat{\delta u}, \jump{e}}_{\Gh} &= 0, \quad \LRp{0,\widehat{\delta u}} \in U_h
+\LRp{e,\delta v}_{V(K)} + \LRp{u_h,A^*_h\delta v}_{L^2{\Omega}} + \LRa{\uh_h,v}_{\Gh}- l(\delta v) &= 0, \quad \delta v \in V(K),\,\, \quad \forall K\in \Oh,\\
+\LRp{\delta u, A_h^*e}_{L^2(K)} &= 0, \quad \LRp{\delta u,0} \in U_h, \quad \forall K\in \Oh,\\
+\LRa{\widehat{\delta u}, \jump{e}}_{\Gh} &= 0, \quad \LRp{0,\widehat{\delta u}} \in U_h.
 \end{align*}
@@
 
-Recall that an operator is invertible only if it is bounded below; thus, for our problem $Au=f$ to have a solution, we require $\nor{Au}_{\L} > \gamma\nor{u}_{\L}$ for some constant $\gamma > 0$ and some arbitrary $u$.
+Recall that a linear operator is continuously invertible only if it is bounded below; thus, for our problem $Au=f$ to have a solution, we require $\nor{Au}_{\L} > \gamma\nor{u}_{\L}$ for some constant $\gamma > 0$ and some arbitrary $u$.
 Classical theory gives that the adjoint is bounded below as well with the same constant
@@
 It can be demonstrated that the optimal test functions generated under the graph test norm for convection-diffusion problems develop strong boundary layers of width $\epsilon$.
-Figure~\ref{fig:optTestBoundary} shows the result of 2D numerical experiments where a fine mesh was used to resolve an optimal test function resulting from (\ref{aux}), demonstrating the presence of strong boundary layers at the element inflow boundary $\partial K_{\rm in}$.
+Figure~\ref{fig:optTestBoundary} shows the result of 2D numerical experiments where a fine mesh was used to resolve an optimal test function resulting from the auxiliary problem \eqnref{optvVar}, demonstrating the presence of strong boundary layers at the element inflow boundary $\partial K_{\rm in}$.
 All figures of optimal test functions are produced using the FEniCS codebase \cite{LoggMardalEtAl2012a}.
@@
 
-Under the graph norm for convection-diffusion, Problem~(\ref{aux}) over a single element is given as
+Under the graph norm for convection-diffusion, the variational problem for test functions over a single element is given as
 \begin{align*}
@@
 For severely underresolved meshes where $h \gg \epsilon$, this makes the approximation of optimal test functions using a simple $p$-enriched space very difficult, though specially designed $hp$-Shishkin subgrid meshes have been used to resolve such test functions with some success in \cite{DBLP:journals/procedia/NiemiCC11} (these are discussed further in Section~\ref{ShishkinSection}).
-The construction of alternative test norms in \cite{DPGrobustness, ChanHeuerBui-ThanhDemkowicz12} was motivated by the computational difficulty in applying the graph test norm to heavily convection-dominated regimes where $\epsilon \ll 1$.
+The construction of alternative test norms in \cite{DPGrobustness} was motivated by the computational difficulty in applying the graph test norm to heavily convection-dominated regimes where $\epsilon \ll 1$.
 
-Consider now globally optimal test functions under the test norm, where Problem~(\ref{aux}) is solved using the weakly conforming space $\tilde{V}$.
+Consider now globally optimal test functions under the test norm, where Problem~\eqnref{optvVar} is solved using the weakly conforming space $\tilde{V}$.
 By the same scaling argument, strong boundary layers appear, but only at the global inflow boundary $\Gamma_{\rm in}$.
@@
 We investigate now non-local effects present in the DPG optimal test spaces for convection-diffusion under the test norm.
-In particular, we focus on the resolution of boundary layers in optimal test functions for DPG and their effect on \textit{robustness} of discrete solutions with respect to $\epsilon$.
-Under fully resolved optimal test functions under the graph test norm, we expect the DPG method to be robust in $\epsilon$, and for non-robustness to be attributed to approximation error of test functions.
+In particular, we focus on the resolution of boundary layers in optimal test functions for DPG and their effect on the \textit{robustness} of the method with respect to $\epsilon$.
+Under fully resolved optimal test functions under the graph test norm, we expect the DPG method to be robust in $\epsilon$, and that any observed non-robustness can be attributed to approximation error in computed test functions.
 
@@
 \subsection{Adaptivity and adjoint boundary layers}
-
+\seclab{sec:inflowRefinements}
 %\	textcolor{red}{Make note on how refinements are seen at the inflow.
@@
 
-We adopt a modification of a problem first proposed by Eriksson and Johnson in \cite{Eriksson1993} and later used in \cite{DPGrobustness, ChanHeuerBui-ThanhDemkowicz12} to determine the robustness of DPG with respect to the diffusion parameter $\epsilon$.
+We adopt a modification of a problem first proposed by Eriksson and Johnson in \cite{Eriksson1993} and later used in \cite{DPGrobustness} to determine the robustness of DPG with respect to the diffusion parameter $\epsilon$.
 For the choice of $\Omega = (0,1)^2$, $f=0$, and $\beta = (1,0)^T$, the convection diffusion equation reduces to
@@
 \begin{align*}
-u-\sigma_x &= u_0-\sigma_{x,0}, \quad x=0,\\
+u &= u_0, \quad x=0,\\
+%u-\sigma_x &= u_0-\sigma_{x,0}, \quad x=0,\\
 \sigma_y &=  0, \quad y=0,1,\\
@@
 \end{align*}
-%The constants $C_n$ depend on a given inflow condition $u_0$ at $x=0$ via the formula
-%\[
-%C_n = \int_0^1 u_0(y) \cos(n\pi y).
-%\]
-%We begin with the solution taken to be the first non-constant term of the above series.
+The constants $C_n$ depend on a given inflow condition $u_0$ at $x=0$ via the formula
+\[
+C_n = \int_0^1 u_0(y) \cos(n\pi y).
+\]
+We begin with the solution taken to be the first non-constant term of the above series.
 We set the inflow boundary condition to be exactly the value of $u-\sigma_x$ corresponding to the exact solution.
@@
 \subfigure{
-\includegraphics[scale=.37]{figs/wallBC_exact_u.png}
+\includegraphics[scale=.345]{figs/wallBC_exact_u.png}
 }
 \subfigure{
-\includegraphics[scale=.37]{figs/wallBC_exact_sigx.png}
+\includegraphics[scale=.345]{figs/wallBC_exact_sigx.png}
 }
 \subfigure{
-\includegraphics[scale=.37]{figs/wallBC_exact_sigy.png}
+\includegraphics[scale=.345]{figs/wallBC_exact_sigy.png}
 }
@@
 The left figure shows the trial solution $u$ under a test norm introduced in \cite{DPGrobustness}, which is shown to induce a DPG method whose solutions which do not degenerate as $\epsilon\rightarrow 0$.
-The presence of refinements at the inflow under the naive test norm illuminates an interesting heuristic observation concerning DPG for convection-diffusion problems; if the form of your test norm neglects to account for boundary layers in optimal test functions, their effects will show up in the energy error, and the method will still seek to resolve the optimal test space through minimization of error via adaptive mesh refinement.
+We speculate that the presence of refinements at the inflow under the naive test norm illuminates an interesting heuristic observation concerning DPG for convection-diffusion problems; if the form of your test norm neglects to account for boundary layers in optimal test functions, their effects will show up in the energy error, and the method will still seek to resolve the optimal test space through minimization of error via adaptive mesh refinement.
 
@@
 \subfigure[$H^1 \times H({\rm div})$ test norm]{\includegraphics[width=7.5cm]{figs/nonRobust.png}}
-\caption{An example of automatic mesh refinement under both a robust test norm (left) and a naively chosen non-robust test norm (right).
+\caption{An example of automatic mesh refinement under both a robust test norm (left) and a naively chosen non-robust test norm (right) for $\epsilon = .001$.
 The naively chosen test norm exhibits both degeneration of the solution and extraneous refinements at the inflow boundary.
@@
 Under the graph test norm, we expect such globally determined test functions to exhibit strong boundary layers, but only at the inflow boundary.
-Recalling Lemma~\ref{lemma1}, we have that the weakly conforming globally optimal test space is a proper subset of the direct sum of locally optimal test spaces over each element; thus, \textit{a-priori} refinements of the mesh that anticipate the presence of an inflow boundary layer should allow for a better resolution of the global optimal test space and improve approximation properties.
+Recalling Lemma~\ref{lemma1}, we have that the weakly conforming globally optimal test space is a proper subset of the direct sum of locally optimal test spaces over each element; thus, \textit{a-priori} refinements of the mesh that anticipate the presence of an inflow boundary layer in computed test functions should allow for a better resolution of the global optimal test space and improve approximation properties.
 Additionally, since the solution is relatively smooth near $x=0$, we do not expect additional mesh resolution near the inflow to significantly affect the best approximation error.
@@
 \centering
-\subfigure{\includegraphics[width=8cm]{figs/errorInflow.png}}
-\subfigure{\includegraphics[width=8cm]{figs/ratioInflow.png}}
+\subfigure{\includegraphics[width=7.55cm]{figs/errorInflow.png}}
+\subfigure{\includegraphics[width=7.55cm]{figs/ratioInflow.png}}
 \caption{The effects of increased mesh resolution at the inflow boundary on $L^2$ and energy error (left) and their ratio (right).
@@
 \]
-induces a strong problem with boundary conditions $\gamma(A^*_h v) = \LRa{\uh, v}$, where $\gamma(A^*_hv)$ is the trace resulting from integration by parts of the operator $A^*_h$.
-For the convection-diffusion equation, this translates to a boundary condition of
+and induces a strong problem with a specific load.
+The corresponding strong form of the problem has boundary conditions $\gamma(A^*_h v) = \LRa{u, v} - \LRa{\uh,v}$, where $\gamma(A^*_hv)$ is the trace resulting from integration by parts of the operator $A^*_h$.
+For the convection-diffusion equation, this translates to the boundary conditions
 \begin{align*}
-\tau_n - \beta_n v  &= \fnh\\
-\frac{1}{\epsilon}\tau_n + \pd{v}{n} &= \uh.
+\LRp{\frac{1}{\epsilon}\tau_n + \pd{v}{n}} - \beta_n\LRp{\div \tau - \beta\cdot \grad v} &= \fnh - (\beta_n u -\sigma_n)\\
+\div \tau - \beta\cdot \grad v &= \uh - u.
 \end{align*}
-where $\fnh$ and $\uh$ are the trace and flux variables for the convection-diffusion equation under the ultra-weak variational formulation.
-The presence of the $\frac{1}{\epsilon}$ term in the boundary condition further increases the strength of the boundary layer when the auxiliary problem~(\ref{aux}) is loaded with a non-zero $\uh$.
+where $u$ and $\sigma$ are field variables, and $\fnh$ and $\uh$ are the trace and flux variables for the convection-diffusion equation under the ultra-weak variational formulation.
+Reducing these two equations into one, we have
+\[
+\frac{1}{\epsilon}\tau_n + \pd{v}{n}= \fnh - (\beta_n u -\sigma_n) + \beta_n\LRp{\uh-u}
+\]
+The presence of the $\frac{1}{\epsilon}$ term in the boundary condition further increases the strength of the boundary layer when the auxiliary problem for a test function~\eqnref{optvVar} is loaded with a non-zero $\uh$.
 
@@
 \centering
-\subfigure[$128\times 128$ mesh]{\includegraphics[height=4.7cm]{figs/uhat_graph_tau_128.pdf}}
-\subfigure[$256 \times 128$ mesh]{\includegraphics[height=4.7cm]{figs/uhat_graph_tau_256.pdf}}
-\subfigure[$512\times 128$ mesh]{\includegraphics[height=4.7cm]{figs/uhat_graph_tau_512.pdf}}
+\subfigure[$128\times 128$ mesh]{\includegraphics[height=4.35cm]{figs/uhat_graph_tau_128.pdf}}
+\subfigure[$256 \times 128$ mesh]{\includegraphics[height=4.35cm]{figs/uhat_graph_tau_256.pdf}}
+\subfigure[$512\times 128$ mesh]{\includegraphics[height=4.35cm]{figs/uhat_graph_tau_512.pdf}}
 \caption{Magnitudes of the vector-valued component $\tau$ of the optimal test functions corresponding to the flux $\widehat{u}=y(1-y)$ on the boundary $x = 0$ for $\epsilon = 0.01$ over the reference element.
@@
 The result of this under-resolution of optimal test functions having to do with traces on the inflow boundary is an underestimation of the inflow boundary term $\LRa{\uh,\jump{v}}_{\Gamma_{\rm in}}$, which leads to the underestimation of the solution in experiments \cite{shishkinDPG}, and explains the fine mesh resolution on the inflow boundary necessary to restore robustness to the DPG method in Figure~\ref{fig:robustness}.
-
-\section{Conclusions}
-
-In this paper, we show how DPG's locally constructed test space can be interpreted as a non-conforming approximation of a weakly-conforming global test space.
-Furthermore, the field solutions and trace solutions on the boundary $\Gamma$ are shown to depend \textit{only} upon properties of the non-conforming global test space; thus, when considering approximation error in test functions, resolution of global approximation error (as opposed to local approximation error) can be sufficient to produce a stable method.
-
-Additionally, global properties of test spaces are given under which the ultra-weak formulation delivers the best $L^2$-approximation to the exact solution.
-A connection is made to DPG through the graph test norm, which can be viewed as a regularization of the graph seminorm through the addition of an $L^2$ term of magnitude $\delta$.
-As the regularization parameter $\delta \rightarrow 0$, DPG under this version of the graph test norm is shown to converge to a weakly-conforming approximation to the $L^2$-optimal test space.
-
-Finally, viewing DPG as an approximation to globally optimal test functions allows the construction of test spaces that focus on resolution of global features as opposed to local features.
-We illustrate this with the convection-diffusion problem, where we show that it is possible to restore robustness with respect to the diffusion parameter $\epsilon$ by neglecting the resolution of boundary layers on the element-local level and focusing on the resolution of global boundary layers in optimal test spaces.
-
-%\section{Acknowledgements}
-%
-%The authors thanks John Evans for several helpful discussions on the ideas and philosophy behind Variational Multiscale finite element methods.
-
-\bibliographystyle{plain}
-\bibliography{paper}
-
-\end{document}
-
-%\subsection{The strong form of the trial-to-test operator}
-%
-%Under the graph test norm 
-%\[
-%\LRp{v,\delta v}_{V(K)} = \LRp{A_h^*v,A_h^*\delta v}_{L^2(K)} + (v,\delta v)_{L^2(K)},
-%\]
-%element-local test functions are induced as solutions of 
-%\[
-%\LRp{v,\delta v}_{V(K)} = (u,A_h^*\delta v)_K + \LRa{\uh,\delta v}_{\partial K}
-%\]
-%Under proper regularity assumptions, this variational problem corresponds to the strong problem
-%\begin{align*}
-%A_hA_h^*v + v &= A_hu, \quad \text{on $K$}\\
-%\gamma\LRp{A_h^*v} &= \uh.
-%\end{align*}

### 2013-07-22 docs/Jesse/Dissertation/H1DPG.tex
updating confusion, dissertation, and NS

--- 2013-05-17 docs/Jesse/Confusion Notes/H1DPG.tex
@@
-%&pdflatex
-\documentclass[final,leqno]{siamltex}
-%\documentclass[10pt,onecolumn]{article}
-\usepackage[top=2cm,bottom=3cm,left=3.5cm,right=3.5cm]{geometry}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath,amssymb,amsfonts,mathrsfs}
-\let\proof\relax 
-\let\endproof\relax
-\usepackage{amsthm}
-\usepackage{amssymb}
-\usepackage{amscd}
-\usepackage{listings}
-\usepackage{array}
-\usepackage{mathtools}
-\usepackage{dsfont}
-\usepackage{graphicx}
-\usepackage{pdfpages}
-\usepackage[textsize=footnotesize,color=green]{todonotes}
-\usepackage{algorithm, algorithmic}
-\usepackage{array}
-\usepackage{bm}
-\usepackage{tikz}
-\usepackage{subfigure}
-\usepackage[normalem]{ulem}
-
-\newcommand{\bs}[1]{\boldsymbol{#1}}
-
-\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}
-
-\newcommand{\tablab}[1]{\label{tab:#1}}
-\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
-
-\newcommand{\theolab}[1]{\label{theo:#1}}
-\newcommand{\theoref}[1]{\ref{theo:#1}}
-\newcommand{\eqnlab}[1]{\label{eq:#1}}
-\newcommand{\eqnref}[1]{\eqref{eq:#1}}
-\newcommand{\seclab}[1]{\label{sec:#1}}
-\newcommand{\secref}[1]{\ref{sec:#1}}
-\newcommand{\lemlab}[1]{\label{lem:#1}}
-\newcommand{\lemref}[1]{\ref{lem:#1}}
-
-\newcommand{\mb}[1]{\mathbf{#1}}
-\newcommand{\mbb}[1]{\mathbb{#1}}
-\newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\nor}[1]{\left\| #1 \right\|}
-\newcommand{\snor}[1]{\left| #1 \right|}
-\newcommand{\LRp}[1]{\left( #1 \right)}
-\newcommand{\LRs}[1]{\left[ #1 \right]}
-\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
-\newcommand{\LRc}[1]{\left\{ #1 \right\}}
-\newcommand{\LRb}[1]{\left| #1 \right|}
-
-\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
-\newcommand{\Grad} {\ensuremath{\nabla}}
-\newcommand{\Div} {\ensuremath{\nabla\cdot}}
-\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
-\newcommand{\jump}[1] {\ensuremath{\LRs{\!\left[#1\right]\!}}}
-\newcommand{\uh}{\widehat{u}}
-\newcommand{\fnh}{\widehat{f}_n}
-\renewcommand{\L}{L^2\LRp{\Omega}}
-\newcommand{\pO}{\partial\Omega}
-\newcommand{\Gh}{\Gamma_h}
-\newcommand{\Gm}{\Gamma_{-}}
-\newcommand{\Gp}{\Gamma_{+}}
-\newcommand{\Go}{\Gamma_0}
-\newcommand{\Oh}{\Omega_h}
-
-\newcommand{\eval}[2][\right]{\relax
-  \ifx#1\right\relax \left.\fi#2#1\rvert}
-
-\def\etal{{\it et al.~}}
-
-\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
-\newcommand{\tensor}[1]{\underline{\vect{#1}}}
-\newcommand{\del}{\Delta}
-\let\grad\relax
-\newcommand{\grad}{\nabla}
-\newcommand{\curl}{\grad \times}
-\renewcommand{\div}{\grad \cdot}
-\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
-\newcommand{\eip}[1]{a\left( #1 \right)}
-\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
-\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
-
-\newcommand{\circone}{\ding{192}}
-\newcommand{\circtwo}{\ding{193}}
-\newcommand{\circthree}{\ding{194}}
-\newcommand{\circfour}{\ding{195}}
-\newcommand{\circfive}{\ding{196}}
-
-\def\arr#1#2#3#4{\left[
-\begin{array}{cc}
-#1 & #2\\
-#3 & #4\\
-\end{array}
-\right]}
-\def\vecttwo#1#2{\left[
-\begin{array}{c}
-#1\\
-#2\\
-\end{array}
-\right]}
-\def\vectthree#1#2#3{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-\end{array}
-\right]}
-\def\vectfour#1#2#3#4{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-#4\\
-\end{array}
-\right]}
-
-%\newtheorem{proposition}{Proposition}
-%\newtheorem{corollary}{Corollary}
-%\newtheorem{theorem}{Theorem}
-%\newtheorem{lemma}{Lemma}
-
-\newcommand{\G} {\Gamma}
-\newcommand{\Gin} {\Gamma_{in}}
-\newcommand{\Gout} {\Gamma_{out}}
-
-\newtheorem{remark}{Remark}
-
-\title{A minimum-residual finite element method for the convection-dominated diffusion equation}
-\author{Jesse Chan, John A. Evans}
-\date{}
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-We present a minimum-residual finite element method for convection-dominated diffusion problems in a higher order, adaptive, continuous Galerkin setting.
-The method borrows concepts from both the Discontinuous Petrov-Galerkin (DPG) method by Demkowicz et al.\ \cite{DPG2} and the method of variational stabilization by Dahmen et al.\ \cite{DahmenVariationalStabilization}, and it can also be interpreted as a variational multiscale method in which the fine-scales are defined through a dual-orthogonality condition.
-A key ingredient in the method is the proper choice of norm used to measure the residual, and we present two alternatives which are observed to be robust in both convection and diffusion-dominated regimes.
-Numerically obtained convergence rates are given in 2D, and benchmark numerical examples in all space dimensions are shown to illustrate the behavior of the method.
-\end{abstract}
-
-%\tableofcontents
-%\begin{keywords}\end{keywords}
-%\begin{AMS}\end{AMS}
-
 \section{Introduction}
@@
 \[
-\langle Bu,v\rangle_V \coloneqq b(u,v), \quad u\in U, v\in V
+\langle Bu,v\rangle_{V' \times V} \coloneqq b(u,v), \quad u\in U, v\in V
 \]
@@
 \]
-where $L = \LRb{\Omega}^{\frac{1}{d}}$ is the length measure of $\Omega$ in $d$ spatial dimensions, $\LRb{\beta} = \max_\Omega \nor{\beta}_{l^2}$, and we have introduced the scaling $\frac{L}{\LRb{\beta}}$ on the streamline diffusion term for unit consistency\footnote{In all problems considered, $\frac{L}{\LRb{\beta}} = O(1)$}.
+where $L = \LRb{\Omega}^{\frac{1}{d}}$ is the length measure of $\Omega$ in $d$ spatial dimensions, $\LRb{\beta} = \max_\Omega \nor{\beta}_{l^2}$, and we have introduced the scaling $\frac{L}{\LRb{\beta}}$ on the streamline diffusion term for unit consistency\footnote{In all problems considered, $\frac{L}{\LRb{\beta}} = O(1)$.}.
 $\alpha \geq 0$ is a user-specified constant with units of inverse time\footnote{In the case where $\alpha = 0$, the seminorm remains a norm due to equivalence with the $H^1$ seminorm, which is norm on $H^1_0$.
@@
 \end{itemize}
-\newpage
-\bibliographystyle{unsrt}
-\bibliography{paper}
 
-\end{document}
+%\bibliographystyle{unsrt}
+%\bibliography{paper}
+%\end{document}

### 2013-07-22 docs/Jesse/NavierStokes paper/Conclusions.tex
updating confusion, dissertation, and NS

\section{Conclusions and future work}

The goal of this work has been to explore the behavior of the Discontinuous Petrov-Galerkin (DPG) method as a method for the discretization and solution of convection-dominated diffusion problems, and to produce both theory and numerical results for model problems in this area.  We begin by introducing the DPG method for linear problems; the concept of problem-dependent optimal test functions is derived through equivalence with the minimization of a specific residual, and discontinuous test functions are introduced in order to localize the determination of such optimal test functions to a single element.

The DPG framework is then extended to nonlinear problems, and equivalence is shown between the DPG method and a Gauss-Newton minimization scheme for the nonlinear residual.  An anisotropic refinement scheme is implemented to more effectively capture lower-dimensional behavior of solutions of convection-diffusion problems, such as boundary layers.  We extrapolate the DPG method to a nonlinear viscous Burgers' equation, and conclude by applying the DPG method to systems of equations and to the solution of two model problems in viscous compressible flow.

In particular, we demonstrate for both the flat plate and compression ramp problem in supersonic/hypersonic in compressible flow that the DPG method is able to begin from a highly underresolved meshes (two elements for the Carter plate problem, and 12 elements for the Holden ramp problem), and resolve physical features of the solution through automatic adaptivity, without the aid of artificial diffusivity or shock capturing terms.  We believe this indicates both the robustness of the method on coarse grids and the effectiveness of the DPG error indicator for adaptive refinement.

As is the case with any research, much work remains to be done.  We have chosen the classical variables in which to cast the compressible Navier-Stokes equations; however, investigation of alternative sets of variables may have merit, as different choices of variables yield differing linearizations with their own advantages (for example, all derivatives in time are linear with respect to the momentum variables, and the entropy variables of Hughes both symmetrize the Navier-Stokes equations and yield solutions obeying second law of thermodynamics for standard $H^1$ formulations \cite{Hughes1986223}).

We also hope to investigate artificial viscosity methods as regularization for problems in viscous compressible flow.  We present an analysis of the 1D Burgers' equation demonstrating that the exact solutions under Newton linearization contain large oscillations.  While these oscillations are not the result of the stability of the spatial discretization, their presence can cause density and temperature to become non-physically negative, which can stall the convergence of the nonlinear solver.  Our goal in incorporating artificial viscosity would not be to provide additional stabilization mechanisms for the discrete spatial discretization, but to provide regularization with which to suppress the presence of large oscillations in the linearized solution.

Finally, though the method is inf-sup stable for arbitrary meshes, our experiments have focused on meshes of uniform $p$.  We hope to implement a true $hp$-adaptive DPG method in the future.

### 2013-07-22 docs/Jesse/NavierStokes paper/NSNotes.tex
updating confusion, dissertation, and NS

\section{The compressible Navier-Stokes equations}

We briefly review the 2D compressible Navier-Stokes equations and formulate DPG for the nonlinear system. 
\begin{itemize}
\item \textbf{Conservation equations}
\begin{align*}
\div \vecttwo{\rho u_1 }{\rho u_2} &= 0\\
\div \vecttwo{\rho u_1^2+p }{\rho u_1 u_2} &= \div\left(\vec{\sigma_{i1}}\right)\\
\div \vecttwo{\rho u_1 u_2}{\rho u_2^2+p } &= \div\left(\vec{\sigma_{i2}}\right)\\
\div\vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2} &= \div\left[\boldsymbol\sigma \boldsymbol u + \vec{q}\right],
\end{align*}
where $\boldsymbol \sigma$ is the stress tensor whose $ij$th term is $\sigma_{ij}$, and $\boldsymbol u$ is the vector $(u_1,u_2)^T$.

\item \textbf{Newtonian fluid laws}

We represent $\boldsymbol\sigma$ using the Newtonian fluid law
\[
\sigma_{ij} = \mu(u_{i,j} + u_{j,i}) + \lambda u_{k,k} \delta_{ij}
\]
where $\mu$ is viscosity and $\lambda$ is bulk viscosity. 
%Following elasticity, a general formula for the stress tensor is 
%\[
%\sigma_{ij} = 2\mu \epsilon_{ij} + \lambda \epsilon_{kk} \delta_{ij}
%\]
We can invert the stress tensor under isotropic and plane strain assumptions to get
\[
\frac{1}{2}\left(\grad  \boldsymbol u + \grad ^T  \boldsymbol u\right) = \frac{1}{2\mu} \sigma_{ij} - \frac{\lambda}{4\mu (\mu + \lambda)} \sigma_{kk}\delta_{ij}
\]
We also have
\[
\frac{1}{2}\left(\grad  \boldsymbol u + \grad ^T  \boldsymbol u\right) = \grad  \boldsymbol u - \boldsymbol \omega
\]
where $\boldsymbol \omega$ is the antisymmetric part of the infinitesimal strain tensor:
\[
\boldsymbol \omega = \frac{1}{2}\left(\grad  \boldsymbol u - \grad ^T  \boldsymbol u\right).
\]
Thus our final form is
\begin{align*}
\grad  \boldsymbol u - \boldsymbol \omega = \frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I.
\end{align*}
Notice that $\boldsymbol \omega$ is implicitly defined to be the antisymmetric part of $\grad u$ by taking the symmetric part of the above equation.

We note that, though this is a standard approach in solid mechanics, it is nonstandard compared to the usual finite element and DG approaches to the viscous stresses. We adopt such an approach to better mirror our experiences with the convection-diffusion equation \cite{DPGrobustness,DPGrobustness2}.

\item \textbf{Fourier's heat conduction law}

We assume Fourier's law 
\begin{align*}
\vec{q} &= \kappa \grad T,
\end{align*}
%where $\kappa$ is generally a function of temperature. 
We introduce here the Prandtl number here as well
\[
{\rm Pr} = \frac{\gamma c_v \mu}{\kappa}.
\]
In this case, we assume a constant Prandlt number, which implies that the heat conductivity $\kappa$ is proportional to viscosity $\mu$.

\end{itemize}

\subsection{Nondimensionalization}
To nondimensionalize our equations, we introduce nondimensional quantities for length, density, velocity, temperature, and viscosity. 
\[
\boldsymbol x^* = \frac{\boldsymbol x}{L}, \qquad \rho^* = \frac{\rho}{\rho_{\infty}}, \qquad u_1^* = \frac{u_1}{V_\infty}, \qquad u_2^* = \frac{u_2}{V_\infty}, \qquad T^* = \frac{T}{T_\infty}, \qquad \mu^* = \frac{\mu}{\mu_\infty}
\]
Pressure, internal energy, and bulk viscosity are then nondimensionalized with respect to the above variables
\[
p^* = \frac{p}{\rho_\infty V_\infty^2}, \qquad \iota^* = \frac{\iota}{V_\infty^2}, \qquad \lambda^* = \frac{\lambda}{\mu_\infty}
\]
We introduce, for convenience, the Reynolds number
\[
\Reyn = \frac{\rho_\infty V_\infty L}{\mu_\infty} 
\]
and the reference (free stream) Mach number
\[
M_\infty = \frac{V_\infty}{\sqrt{\gamma(\gamma-1)c_vT_\infty}}
\]
Note that 
\[
a = \sqrt{\frac{\gamma p_\infty}{\rho_\infty}} = \sqrt{{\gamma p_\infty}} = \sqrt{\gamma(\gamma-1)c_vT_\infty}
\]
The equations take the same form as before after nondimensionalization, so long as we define new material constants
\[
\tilde{\mu} = \frac{\mu^*}{\Reyn}, \qquad \tilde{\lambda} = \frac{\lambda^*}{\Reyn}, \qquad \tilde{c}_v = \frac{1}{\gamma(\gamma-1)M_\infty^2}, \qquad \tilde{\kappa} = \frac{\gamma\tilde{c}_v\tilde{\mu}}{\rm Pr}
\]
From here on, we drop the $^*$ superscript and assume all variables refer to their nondimensionalized quantities.

To summarize, our system of equations in the classical variables is now
\begin{align*}
\div \vecttwo{\rho u_1 }{\rho u_2} &= 0\\
\div \left(\vecttwo{\rho u_1^2+p }{\rho u_1 u_2} - \boldsymbol \sigma_{1}\right) &=0\\
\div \left(\vecttwo{\rho u_1 u_2}{\rho u_2^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
\div \left(\vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2} - \boldsymbol\sigma \mathbf{u} - \vec{q}\right) &=0\\
\frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I &= \grad \mathbf{u} - \Reyn \, {\boldsymbol \omega}\\
\frac{1}{\kappa}\vec{q} &= \grad T
\end{align*}
We strongly enforce symmetry of the stress tensor $\boldsymbol \sigma$ by setting $\sigma_{21} = \sigma_{12}$. Additionally, we have scaled the antisymmetric tensor $\boldsymbol \omega$ by the Reynolds number to ensure that $\boldsymbol \omega = O(1)$ for all ranges of $\Reyn$.

\subsection{Linearization}

As the equations for viscous compressible flow are nonlinear and cannot be solved exactly, we linearize the equations and adopt an iterative procedure for approximating the nonlinear solution.\footnote{We note that it is possible to linearize the strong form of the equations and then derive a linearized weak form, instead of linearizing the weak form of the nonlinear equations, which is done here.  The two formulations are equivalent; however, extraneous linearization of the fluxes is avoided using the latter approach.}  We outline the linearization of both the conservation and stress laws in this section.

\subsubsection{Conservation laws}

The Navier-Stokes conservation laws can be written as 
\begin{align*}
\div \vecttwo{\rho u_1 }{\rho u_2} &= 0\\
\div \left(\vecttwo{\rho u_1^2+p }{\rho u_1 u_2} - \boldsymbol \sigma_{1}\right) &=0\\
\div \left(\vecttwo{\rho u_1 u_2}{\rho u_2^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
\div \left(\vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2} - \boldsymbol \sigma_1 \cdot \boldsymbol u- \boldsymbol \sigma_2 \cdot \boldsymbol u - \vec{q}\right) &=0,
\end{align*}
where $\boldsymbol \sigma_1$ is the $i$th column or row of $\boldsymbol \sigma$, or more generally, if we group our Eulerian and stress variables into the vector variables $\boldsymbol U$ and $\boldsymbol \Sigma$, respectively
\[
\div (F_i(\boldsymbol U)-G_i(\boldsymbol U,\boldsymbol \Sigma) = 0, \qquad i = 1,\ldots, 4,
\]
where $F_i$and $G_i$ are given as
\begin{align*}
F_1 = \vecttwo{\rho u_1 }{\rho u_2}, \quad &G_1 = 0\\
F_2 = \vecttwo{\rho u_1^2+p }{\rho u_1 u_2},\quad &G_2 = \boldsymbol \sigma_{1}\\
F_3 = \vecttwo{\rho u_1 u_2}{\rho u_2^2+p }, \quad &G_3 = \boldsymbol \sigma_{2}\\
F_4 = \vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2}, \quad &G_4 = \boldsymbol \sigma_1 \cdot \boldsymbol u + \boldsymbol \sigma_2 \cdot \boldsymbol u + \vec{q}
\end{align*}
The variational form restricted to a single element gives
\[
\langle \widehat{F}_i\cdot n, v\rangle - \int_K  (F(\boldsymbol U)-G_i(\boldsymbol U,\boldsymbol \Sigma)) \cdot \grad v_i = 0 , \qquad i = 1,\ldots, 4
\]
and the variational form over the entire domain is given by summing up the element-wise contributions.

The presence of terms such as $\boldsymbol \sigma_i \cdot \boldsymbol u$ means that we will need to linearize in the stress variables $\sigma_ij$ in addition to our Eulerian quantities. Since fluxes and traces are linear functions of the unknowns, we do not need to linearize them. Instead, fluxes $\widehat{F}_{i,n}$ and traces $\widehat{u},\widehat{v},\widehat{T}$ will represent normal traces and traces of the accumulated nonlinear solution. The linearized variational formulation is thus
\begin{align*}
\langle \widehat{F}_i\cdot n, v\rangle &- \int_K  \left(F_{i,\boldsymbol U}(\boldsymbol U)\cdot \Delta \boldsymbol U -G_{i,\boldsymbol U}(\boldsymbol U, \boldsymbol \Sigma)\cdot \Delta \boldsymbol U - G_{i,\boldsymbol \Sigma}(\boldsymbol U, \boldsymbol \Sigma)\cdot \Delta \boldsymbol \Sigma \right)\cdot \grad v_i \\
&= \int_K  \left(F_i(\boldsymbol U)-G_i(\boldsymbol U)\right) \cdot \grad v_i \\
\qquad i &= 1,\ldots, 4
\end{align*}
where $F^i_{j,\boldsymbol U}$, $G^i_{j,\boldsymbol U}$, and $G^i_{j,\boldsymbol \Sigma}$ are the Eulerian and two viscous Jacobians (linearized w.r.t.\ the Eulerian/viscous variables), respectively.
%where
%\begin{align*}
%F^1_{1,\boldsymbol U} &= \{u,\rho ,0,0\} \\
%F^2_{1,\boldsymbol U} &= \{v,0,\rho ,0\} \\
%F^1_{2,\boldsymbol U} &=\left\{c_v T (\gamma -1)+u^2,2 u \rho ,0,c_v (\gamma -1) \rho \right\}\\
%F^2_{2,\boldsymbol U} &=\{u v,v \rho ,u \rho ,0\}\\
%F^1_{3,\boldsymbol U} &=\{u v,v \rho ,u \rho ,0\}\\
%F^2_{3,\boldsymbol U} &=\left\{c_v T (\gamma -1)+v^2,0,2 v \rho ,c_v (\gamma -1) \rho \right\}\\
%F^1_{4,\boldsymbol U} &=\left\{\frac{1}{2} u \left(2 c_v T (2 \gamma -1)+u^2+v^2\right),\frac{1}{2} \rho  \left(2 c_v T (2 \gamma -1)+3 u^2+v^2\right),u v \rho ,c_v u (2 \gamma -1) \rho \right\}\\
%F^2_{4,\boldsymbol U} &=\left\{\frac{1}{2} v \left(2 c_v T (2 \gamma -1)+u^2+v^2\right),u v \rho ,\frac{1}{2} \rho  \left(2c_v T (2 \gamma -1)+u^2+3 v^2\right),c_v v (2 \gamma -1) \rho \right\}
%\end{align*}
%The viscous Jacobians become (when linearized with respect to $\{\sigma_{11},\sigma_{12}, \sigma_{22}\}$)
%\begin{align*}
%G^1_{2,\boldsymbol \sigma} &= \{1,0,0\}\\
%G^2_{2,\boldsymbol \sigma} &= \{0,1,0\}\\
%G^1_{3,\boldsymbol \sigma} &= \{0,1,0\}\\
%G^2_{3,\boldsymbol \sigma} &= \{0,0,1\}\\
%G^1_{4,\boldsymbol \sigma} &= \{u_1,u_2,0\}\\
%G^2_{4,\boldsymbol \sigma} &= \{0,u_1,u_2\}
%\end{align*}
%and (when linearized with respect to the Eulerian variables)
%\begin{align*}
%G^1_{4,\boldsymbol U} &= \{0,\sigma_{11},\sigma_{12},0\}\\
%G^2_{4,\boldsymbol U} &= \{0,\sigma_{12},\sigma_{22},0\}
%\end{align*}

\subsubsection{Viscous equations}
We have two equations left to linearize - the constitutive laws defining our viscous stresses and heat flux terms. 
\begin{align*}
\frac{1}{2\mu}{\boldsymbol \sigma}- \frac{\lambda}{4\mu(\mu+\lambda)}{\rm tr}({\boldsymbol \sigma}){\boldsymbol I} + \Reyn {\boldsymbol \omega} &= 
\grad
\left[\begin{array}{c}
u_1\\
u_2
\end{array}
\right]\\
\frac{1}{\kappa}
\left[\begin{array}{c}
q_1\\
q_2
\end{array}\right] &=
\grad T
\end{align*}

We treat the first tensor equation as two vector equations by considering each column:
\begin{align*}
\frac{1}{2\mu} \vecttwo{\sigma_{11}}{\sigma_{12}} - \frac{\lambda}{4\mu(\mu+\lambda)}\vecttwo{\sigma_{11}+\sigma_{22}}{0} + \Reyn\vecttwo{0}{-\omega} - \grad u_1&= 0 \\
\frac{1}{2\mu} \vecttwo{\sigma_{12}}{\sigma_{22}} - \frac{\lambda}{4\mu(\mu+\lambda)}\vecttwo{0}{\sigma_{11}+\sigma_{22}} + \Reyn\vecttwo{\omega}{0} - \grad u_2 &= 0
\end{align*}
%These equations are linear in $\sigma_{ij}$, so the linearization is simple. 
Since all equations are linear in variables $q_1, q_2, w$ for all combinations of variables, we do not need to linearize any equations in $q_1, q_2, w$.  We do not linearize the viscosities $\mu$ and $\lambda$, but instead set them based on the power law and the solution at the previous timestep for simplicity.

\subsection{Test norm}

%Recall the convection-diffusion problem 
%\begin{align*}
%\div \left(\beta u - \sigma\right) &= f\\
%\frac{1}{\epsilon}\sigma - \grad u &= 0.
%\end{align*}
%On domain $\Omega$, with mesh $\Oh$ and mesh skeleton $\Gh$, the DPG variational formulation is
%\begin{align*}
%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
%\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
%v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh} - \LRa{
%\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n,
%  \jump{v} }_{\Gh}.
%\end{align*}
%with $v\in H^1$ and $\tau \in H({\rm div},\Oh)$. The test norm adopted for convection-diffusion in \cite{DPGrobustness2} is defined elementwise on $K$ as
%\[
%\|\left(v,\tau\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau-\beta\cdot\grad v\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
%\]
%This test norm both delivers robust control of the error in the $L^2$ variables $u$ and $\sigma$ and avoids boundary layers in the computation of local test functions.

Recall that the test norm adopted for convection-diffusion is defined elementwise as
\[
\|\left(v,\tau\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau-\beta\cdot\grad v\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
\]
This test norm is extrapolated to the Navier-Stokes equations as follows: we denote the vector of $H^1$ test functions as $\boldsymbol V=\{v_1,v_2,v_3,v_4\}$, and similarly for $\boldsymbol W = \{\tau_1,\tau_2,\tau_3\}$. If $R_{\rm Euler}(\boldsymbol U,\boldsymbol \Sigma)$ and $R_{\rm visc}(\boldsymbol U,\boldsymbol \Sigma)$ are Eulerian and viscous nonlinear residuals, our formulation for the linearized Navier-Stokes equations can be written as
\begin{align*}
\div \left(A_{\rm Euler}\boldsymbol \delta U - A_{\rm visc}\boldsymbol \delta \Sigma\right) &= R_{\rm Euler}(\boldsymbol U,\boldsymbol \Sigma)\\
E_{\rm visc}\boldsymbol  \delta \Sigma - \grad \boldsymbol \delta U &= R_{\rm visc}(\boldsymbol U,\boldsymbol \Sigma)
\end{align*}
with variational formulation
\begin{align*}
\LRa{\widehat{F}_n,\boldsymbol V}_{\Gh} + \left(\boldsymbol \delta U,\div \boldsymbol W - A_{\rm Euler}^T\grad \boldsymbol  V\right) + \LRa{\widehat{\boldsymbol U},\boldsymbol W\cdot n}_{\Gh} + \left(\boldsymbol \delta \Sigma,E_{\rm visc}^T\boldsymbol W - A_{\rm visc}^T\grad \boldsymbol  V\right) &= 
\\ \LRa{R_{\rm Euler}(\boldsymbol U,\boldsymbol \Sigma),\boldsymbol V} + \LRa{R_{\rm visc}(\boldsymbol U,\boldsymbol \Sigma),\boldsymbol W}
\end{align*}
Identifying vector-valued terms in the Navier-Stokes formulation with equivalent scalar terms in the convection-diffusion equation allows us to extrapolate our test norm to systems of equations
\begin{align*}
\|\left(\boldsymbol V,\boldsymbol W\right)\|_{V, K}^2 =& \|\boldsymbol V\|^2 + \frac{1}{\Reyn} \|A_{\rm visc}^T\grad \boldsymbol V\|^2 + \|A_{\rm Euler}^T \grad \boldsymbol V\|^2 \\
& + \| \div \boldsymbol W - A_{\rm Euler}^T \grad \boldsymbol V\|^2 + \min\left\{\Reyn,\frac{1}{|K|}\right\}\|E_{\rm visc}^T\boldsymbol W\|^2.
\end{align*}
An advantage of this extrapolation approach is that the incompletely parabolic nature of the Navier-Stokes equation is taken into account; there is no diffusive term present in the mass conservation equation, and the test norm reflects that by requesting only limited regularity of $v_1$, the test function for the conservation equation.\footnote{The situation is analogous to using the full $H^1(\Oh)$ norm for the pure convection equation --- the optimal test norm $\nor{v}_V = \nor{\beta\cdot \grad v} + \nor{v}$ implies only streamline regularity, whereas taking $\nor{v}_V = \nor{\grad v} + \nor{v}$ implies stronger regularity on the test space $V$ than the graph norm. Consequently, convergence is suboptimal for DPG applied to the convection problem under the $H^1(\Oh)$ test norm.}

\subsection{Boundary conditions}

As a consequence of the ultra-weak variational formulation, our solution is linear in the flux and trace variables. Thus, the nonlinear boundary conditions can be applied directly to our fluxes $\widehat{f}_{i,n}, i = 1,\ldots,4$, and traces $\widehat{u}_1$, $\widehat{u}_2$, and $\widehat{T}$. Additionally, inflow boundary conditions are applied not directly to the trace variables $\widehat{u}_1$, $\widehat{u}_2$, and $\widehat{T}$, but to the fluxes $\widehat{f}_{i,n}$. Extrapolating from the convection-diffusion problem, this allows us to use a stronger test norm without experiencing adverse effects for smaller diffusion/higher Reynolds numbers, as described in Section~\secref{sec:testNormSec} and \cite{DPGrobustness,DPGrobustness2}.

\section{Nonlinear solver}

For our nonlinear solver, we use a pseudo-time stepping approach to iterate to a steady state solution, along with a greedy refinement scheme to eliminate spatial discretization error.  We cover briefly the details of the pseudo-timestepping method in this section.  
%Though we have not yet implemented adaptive timestepping, we are able to take large enough uniform timesteps over a coarse mesh such that convergence occurs sufficiently quickly.

\subsection{Pseudo-timestepping}

The solution of the compressible Navier-Stokes equations can be quite challenging; as mentioned previously, the direct application of a Newton algorithm often will not converge, especially for high Reynolds numbers.  Typically, a pseudo-timestepping algorithm is used in lieu of a full nonlinear Newton algorithm. The pseudo-timestep proceeds as follows: given the transient terms present in the conservation laws of compressible flow
\begin{align*}
\pd{\rho}{t} + \ldots \\
\pd{\LRp{\rho u}}{t} + \ldots \\
\pd{\LRp{\rho v}}{t} + \ldots \\
\pd{\LRp{\rho e}}{t} + \ldots,
\end{align*}
we discretize each time derivative using an implicit timestepping method.  Though second order time discretizations have been shown to be effective \cite{Demkowicz1990275, BenKirk}, we choose a first order backwards Euler discretization for simplicity.  Due to the fact that we've chosen to solve the Navier-Stokes equations under primitive variables $\rho, u, v$, and $T$, the time terms are nonlinear as well, and must be linearized.  After time discretization and linearization, we are left with a coupled system of reaction terms in the problem for our solution update at every timestep
\begin{align*}
A_{\rm time}\boldsymbol \delta U_i + \div \left(A_{\rm Euler}\boldsymbol \delta U_i - A_{\rm visc}\boldsymbol \delta \Sigma_i\right) &= R_{\rm Euler}(\boldsymbol U_i,\boldsymbol \Sigma_i) + R_{\rm time}(\boldsymbol U_{i-1},\boldsymbol U_i)\\
E_{\rm visc} \boldsymbol \Sigma_i - \grad \boldsymbol U_i &= R_{\rm visc}(\boldsymbol U_i,\boldsymbol \Sigma_i),
\end{align*}
where $R_{\rm time}(\boldsymbol U_{i-1},\boldsymbol U_i)$ is the transient residual.  Including the transient terms in our test norm as well, our final test norm is 
\begin{align*}
\|\left(\boldsymbol V,\boldsymbol W\right)\|_{V,K}^2 =& \nor{A_{\rm time}^T\boldsymbol V} + \|\boldsymbol V\|^2 + \frac{1}{\Reyn} \|A_{\rm visc}^T\grad \boldsymbol V\|^2 + \|A_{\rm Euler}^T \grad \boldsymbol V\|^2 \\
& + \| \div \boldsymbol W - A_{\rm Euler}^T \grad \boldsymbol V\|^2 + \min\left\{\Reyn,\frac{1}{|K|}\right\}\|E_{\rm visc}^T\boldsymbol W\|^2.
\end{align*}
Finally, convergence of the pseudo-timestepping method is determined by measuring the transient residual in the energy norm; in other words, we measure $\nor{e_{\rm time}}_V$, where
\[
\LRp{\LRp{\boldsymbol V,\boldsymbol W},\LRp{\boldsymbol dV,\boldsymbol dW}}_V = \LRp{R_{\rm time}(\boldsymbol U_{i-1},\boldsymbol U_i),\boldsymbol V}_{\L}, \quad \forall \LRp{\boldsymbol dV,\boldsymbol dW} \in V.
\]
The energy norm thus provides a consistent measure in which convergence of the nonlinear iteration at each timestep, convergence of the pseudo-timestepping algorithm to steady state, and nonlinear residual can all be assessed.

\subsubsection{Dependence of solution on $dt$}

A surprising feature of pseudo-timestepping schemes for DPG is that, under the problem-dependent minimum-residual nature of the method, convergence to steady state can yield qualitatively slightly different solutions under different size timesteps.  We illustrate this using a ``plate'' example for convection-diffusion.  We consider the transient form of the conservation equation for convection-diffusion
\[
\pd{u}{t} + \div \LRp{\beta u - \sigma} = f, 
\]
where the stress law remains unchanged.  Applying a backwards Euler time discretization, at each timestep, we will solve for the current solution $u_i$ (as well as the current stress $\sigma_i$) given the previous timestep solution $u_{i-1}$ under
\[
\frac{u_i}{dt} + \div \LRp{\beta u_i - \sigma_i} = f + \frac{u_{i-1}}{dt}.
\]
The conserved flux $\beta_n u - \sigma_n$ is set to freestream values on the inflow, and 0 on the top boundary $y = 1$ and half of the bottom boundary $x < .5, y = 0$.  We set $u = 1$ for the boundary $x \in (.5,1), y = 0$. For this example, $\beta = (1,0)$ and $\epsilon = 10^{-3}$.  
\begin{figure}
\centering
\subfigure[$dt = .1$]{\includegraphics[width=2.5in]{dt10.png}}
\subfigure[$dt = .01$]{\includegraphics[width=2.5in]{dt100.png}}
\caption{Comparison of pseudo-timestepping to steady state for a convection-diffusion problem under two different sizes of timestep.}
\label{fig:dtComparison}
\end{figure}
This can be understood as the consequence of solving a ``moving target'' optimization problem -- our variational formulation and test norm for this problem are
\begin{align*}
\LRp{u_{i}, \frac{1}{dt}v}_{\L} + b\LRp{u_i,v} &= l(v) + \LRp{u_{i-1},\frac{1}{dt}v}_{\L}\\
\nor{\LRp{\tau,v}}_{V,dt}^2 &= \frac{1}{dt}\nor{v}_{\L}^2 + \nor{v}_V^2,
\end{align*}
where $\nor{\LRp{\tau,v}}_{V}$ is the test norm introduced in Section~\secref{sec:testNormSec}, and $b(u,v)$ and $l(v)$ are the bilinear form and load for the steady state form of the convection diffusion equation.  DPG solutions minimize the functional 
\[
J(u_i) = \sup_{v\in V} \frac{\LRp{u_{i}-u_{i-1}, \frac{1}{dt}v}_{\L} + b(u_i,v) - l(v)}{\LRp{\frac{1}{dt}\nor{v}_{\L}^2 + \nor{v}_V^2}^{\frac{1}{2}}}
\]
over a given mesh.  As $u_{i-1}\rightarrow u_{i}$, which we expect to happen as the pseudo-timestepping algorithm converges to steady state, the minimized functional becomes
\[
J(u_i) = \sup_{v\in V} \frac{b(u_i,v) - l(v)}{\LRp{\frac{1}{dt}\nor{v}_{\L}^2 + \nor{v}_V^2}^{\frac{1}{2}}}.
\]
While the transient portion of the residual disappears, a factor of $\frac{1}{dt}$ is still present in the test norm.\footnote{While the solution under smaller $dt$ appears to give visually higher quality results, we stress that simply adding the term $\frac{1}{dt}\nor{v}_{\L}$ to the test norm under the steady state version of the convection-diffusion equations does not achieve the same effect.  We are able to add this term without negative consequence due to the inclusion of the $\frac{u_i}{dt}$ term present in the variational formulation (see \cite{DPGrobustness,DPGrobustness2} for mathematical details).  Numerical experiments indicate that including $\alpha\nor{v}_{\L}$ in the test norm, where $\alpha > \frac{1}{dt}$, converges much more slowly to a fine-mesh reference solution than if $\alpha = \frac{1}{dt}$.}  Thus, we can expect that the nature of the steady state solution achieved through convergence of the pseudo-time algorithm can depend on the timestep $dt$.  We observe the same phenomena for analogous problems in compressible flow as well.

\subsubsection{Adaptive time thresholding}

Adaptive timestepping (also known as pseudo-transient continuation) has been implemented successfully for problems in compressible flow \cite{BenKirk}. Typical adaptive time-stepping schemes modify the time-step based on some notion of the transient residual $R_i$ at timestep $i$, such that
\[
dt_{i+k} = \LRp{\frac{R_{i+k}}{R_i}}^r dt_i,
\]
where $r > 1$ dictates the rate of change of the timestep based on residual reduction, and $k$ indicates an integer interval at which to modify the timestep.  However, the minimum-residual nature of the DPG method and the ``moving target'' problem make the effectiveness of adaptive time-stepping schemes questionable.

For our current experiments, we implement instead an adaptive time thresholding, where we adaptive decrease our convergence criterion based on the spatial energy error.  Recall that, under convergence of the pseudo-timestepping algorithm, the DPG energy error converges to the measure of the nonlinear residual in the dual norm.  We set convergence criterion for the pseudo-timestepping algorithm to be such that 
\[
\nor{e_{\rm time}}_V < \max \{\epsilon_t,\epsilon_{t,k}\},
\]
where $\epsilon_{t,k}$ is the tolerance at the $k$th refinement iteration, and $\epsilon_t < \epsilon_{t,k}$ is an absolute tolerance.  We initialize $\epsilon_{t,k}$ to $\epsilon_{t}$, then based on the energy error $\nor{u-u_h}_E$, we set 
\[
\epsilon_{t,k} = \alpha_t \nor{u-u_h}_E.
\]
Since the linearized error at a single timestep is composed of a sum of the linearization error, transient residual, and nonlinear residual, if the transient residual and linearization error are small, we expect that the nonlinear residual at that point will be sufficient to be an effective error indicator with which to drive adaptive mesh refinement.  In the following numerical experiments, $\alpha_t$ is set to $.005$.

The aim of this adaptive thresholding is to relax the convergence criteria for solution of the nonlinear system at each refinement step such that the same refinement pattern is achieved with or without the use of adaptive time thresholding.  Numerical experiments seem to indicate that the same refinement pattern is produced with or without the implementation of this simple adaptive thresholding scheme, though wall-clock convergence times under adaptive thresholding are faster.  We hope to investigate both DPG-specific adaptive timestepping schemes and more advanced methods of balancing convergence criterion in the future.

\subsection{Linear solver}

A clear choice for a linear solver under the ultra-weak variational formulation is static condensation, or the Schur-complement method. Given a block matrix structure of a stiffness matrix $K$, we can view the DPG system as
\[
Ku = \arr{A}{B}{B^T}{D}\vecttwo{u_{\rm flux}}{u_{\rm field}} = \vecttwo{f}{g} = l
\]
where $D$ has a block-diagonal structure, and $A$ and $D$ are both square matrices with $\dim{A} < \dim{D}$. This is due to the fact that, for the ultra-weak variational formulation (and for all HDG methods), the interior field degrees of freedom can be condensed out to yield a problem posed solely in terms of the coupled flux and trace degrees of freedom.  The system can be reduced to yield the condensed system
\[
\left(A-B D^{-1} B^T\right)u_{\rm flux} = f - B D^{-1} g
\]
where $D^{-1}$ can be inverted block-wise. Once the globally coupled flux and trace degrees of freedom are solved for, the field degrees of freedom can be reconstructed locally. An additional advantage of the above approach is that the Schur complement maintains the same sparsity pattern implied by the connectivity of the globally coupled flux and trace degrees of freedom.  Since the condensation process can be done locally, we can save memory by avoiding constructing the full stiffness matrix.

It has been shown that, unlike standard least-squares methods, DPG generates for the Poisson matrix a stiffness matrix with condition number $O(h^{-2})$ \cite{practicalDPG}. It is well known that, under standard finite element methods, if the condition number of the global stiffness matrix $K$ is $O(h^{-2})$, the condition number of the Schur complement is $O(h^{-1})$. Additionally, through either diagonal preconditioning or matrix equilibration, the condition number of the Schur complement can often be made significantly smaller than $O(h^{-1})$, and the positive-definiteness of the resulting system allows the use of iterative solvers in solving the condensed system.  Initial experiments indicate that, at least for quasi-uniform and low-order meshes, both algebraic multigrid and preconditioned conjugate gradients are able to solve the condensed system fairly rapidly.  We hope to experiment further with solvers for the condensed system, and to develop multigrid methods and preconditioners for adaptive and higher order meshes under DPG.

\section{Test problems}

We applied the DPG method to two test problems in compressible flow -- flow over a flate plate, and flow over a compression ramp.  While the physics of both problems are fairly simple, they nonetheless display several features (shocks, singularities, boundary layers) that are computationally difficult to resolve without adaptivity.  Furthermore, the problems themselves are not usually solved without the aid of artificial or numerical diffusion and/or shock-capturing terms, which we eschew in our application of DPG to these model problems.

The numerical parameters used are as follows for:
\begin{itemize}
\item{DPG parameters:} $p = 2$ and $\Delta p = 2$ uniformly across the mesh. 
\item{Adaptivity parameters:} Energy threshold $\alpha$ for refinements is $\alpha = .4$ for the Carter flat plate example and $\alpha = .5$ for the Holden ramp example.  
\item{Time-stepping parameters:} Initial timestep $\Delta t = .1$, and initial tolerance for transient residual $\epsilon_t = 1e-7$.
\end{itemize}

Numerical experiments were run on a small cluster with 16 CPUs and 8GB memory, as well as on the Lonestar machine at the Texas Advanced Computing Center (TACC), using a varying number of cores, from 48 to 120 depending on problem geometry and parameters.  Experiments were done using the Camellia library \cite{Camellia}.
%Elements were partitioned using the Zoltan library of Trilinos \cite{ZoltanOverviewArticle}, using either a Hilbert space-filling curve or the REFTREE \cite{REFTREE} algorithm.

\subsection{Numerical experiments: Carter flat plate}

The first problem of interest is the Carter flat plate problem \cite{Carter}. An infinitesmally thin flat plate disrupts a free stream flow, causing a shock to form at the tip of the plate, and a boundary layer forms and widens along the length of the plate.

\begin{figure}
\centering
\includegraphics[width=3.5in]{flat_plate_BCs.pdf}
\caption{Carter flat plate problem.}
\end{figure}

\begin{enumerate}
\item \textbf{Symmetry boundary conditions:} $u_n = q_n = \pd{u_s}{n} = 0$. Here, this implies $u_2 = q_2 = \sigma_{12} = 0$. We impose the stress condition by noting that, for the flat plate geometry, if $u_2 = 0$, then at the top and bottom, with $n = (0,1)$, $\widehat{f}_{2,n} = \sigma_{12}$, and $\widehat{f}_{4,n} = q_2$ if $\sigma_{12}$ and $u_2 = 0$. They are applied here to the bottom free-stream boundary.
\item \textbf{Flat plate boundary conditions:} $u_1 = u_2 = 0$, and $T = T_w = \left[1+(\gamma-1)M_\infty^2/2\right] T_\infty = 2.8T_\infty$ (for Mach 3 flow). We impose these strongly on the trace variables $\widehat{u}_1, \widehat{u}_2, \widehat{T}$. 
\item \textbf{Symmetry boundary conditions} are applied also to the top free-stream boundary.
\item \textbf{Inflow boundary conditions:} free stream conditions are applied here to all four fluxes $\widehat{f}_{i,n}$.
\item \textbf{Outflow boundary conditions:} the exact boundary conditions to enforce here are not universally agreed on.  Many enforce $\pd{u_1}{n}=\pd{u_2}{n}=0$ and $\pd{T}{n} = 0$, while others enforce an outflow boundary condition only in regions where the flow is subsonic \cite{Demkowicz:1990:NFE:112271.112276}.  
We adopt a ``no boundary condition'' outflow condition, mimicing what is done in \cite{Shakib1991141}.%first introduced in \cite{FLD:FLD1650140506}. %A mathematical analysis and explanation of this boundary condition for standard $H^1$ elements is given in \cite{FLD:FLD505}. 
%An alternative boundary condition would be as follows: since $u_1$ and $u_2$ are not expected to be zero at these points, we can set $\widehat{f}_{2,n}$ and $\widehat{f}_{4,n}$ to their represented quantities using either the field variables from the background flow, or (in the case of pseudo-time stepping) the previous timestep's flux and field quantities. 
\end{enumerate}

We initialize our solution to
\[
\rho = 1,\qquad u_1= 1,\qquad u_2 = 0, \qquad T = 1%\frac{1}{\gamma(\gamma-1){\rm Ma}^2}
\]
which, we also take as the freestream values for the above variables, and is consistent with what was done by Demkowicz, Oden, and Rachowicz in \cite{Demkowicz1990275}. Stresses are set uniformly to zero.  We take the computational domain to be $\Omega = [0,2]\times[0,1]$. Under Dirichlet wall boundary conditions for all 3 traces $u_1$, $u_2$, and $T$, the solution develops a singularity in the density $\rho$ at the plate beginning, and both $T$ and $u_1$ form a boundary layer along the leading edge of the plate.

\begin{figure}
\centering
\subfigure[$T$]{\includegraphics[width=2.5in]{T0.png}}
\subfigure[$u_1$]{\includegraphics[width=2.5in]{u0.png}}
\caption{Converged solution on 2 cells.}
\label{fig:Re1000_2cells}
\end{figure}

We perform 10 steps of adaptive mesh refinement, beginning with a mesh of only two square elements.  The solution on this coarsest mesh is given in Figure~\ref{fig:Re1000_2cells}, and the final solutions after 10 refinement steps are given in Figure~\ref{fig:Re1000}.  For this specific example, we use only isotropic refinements.

\begin{figure}
\centering
\subfigure[$\rho$]{\includegraphics[width=2.8in]{rho.png}}
\subfigure[$u_1$]{\includegraphics[width=2.8in]{u1.png}}
\subfigure[$u_2$]{\includegraphics[width=2.8in]{u2.png}}
\subfigure[$T$]{\includegraphics[width=2.8in]{T.png}}
\caption{Solutions after twelve refinements for $p=2$ and $\Reyn = 1000$, starting from a mesh of 2 elements.}
\label{fig:Re1000}
\end{figure}

Typical coarse meshes for adaptive CFD computations aim to resolve, at least to some degree, the features of the solution; often, physical features such as high gradients are used to drive refinement.  For feature-based adaptivity to be effective, coarse mesh solutions must be of sufficiently high quality to resolve basic solution features.  Often, artificial diffusion and shock capturing must also be applied in order to produce visually clean solutions on underresolved meshes.  In contrast to this, the residual-based approach of DPG is able to place refinements accurately and efficiently despite the underresolution of solution features.

Figure~\ref{fig:Re1000_midRefs} shows snapshots of the third and sixth steps of adaptive mesh refinement.  The main contribution to energy error is at the plate tip -- due to the change in boundary condition across the point $(.5,0)$, the viscous stresses are singular at this point (this is analogous to the convection-diffusion plate example given earlier).  Underresolution of the stresses at this point results in some pollution effects slightly upstream of the beginning of the plate; however, once $h\approx {\rm Re}^{-1}$ near the plate edge, these pollution effects disappear.  We observe numerically that decreasing $dt$ also limits how far upstream of the plate edge this pollution effect travels.

\begin{figure}
\centering
\subfigure[Mesh, 4th refinement]{\includegraphics[width=2.85in]{mesh4.png}}
\subfigure[$T$, 4th refinement]{\includegraphics[width=2.85in]{T4.png}}
\subfigure[Mesh, 8th refinement]{\includegraphics[width=2.85in]{mesh8.png}}
\subfigure[$T$, 8th refinement]{\includegraphics[width=2.85in]{T8.png}}
\caption{Snapshots of adaptive meshes and solutions for two different steps of adaptivity $\Reyn = 1000$.}
\label{fig:Re1000_midRefs}
\end{figure}

We observe numerically that $\rho$ also behaves singularly at the plate tip -- due to the presence of this strong singularity, the coloring of the wide range of values for $\rho$ in Figure~\ref{fig:Re1000} causes the solution to appears largely uniform, save for a flare up at the tip of the plate.  To better visualize density, $\rho$ is rescaled such that the features of the solution away from the singularity, as well as the final mesh after 10 refinement steps, are visible in Figure~\ref{fig:rhoScaled}.

\begin{figure}
\centering
\subfigure[$\rho$]{\includegraphics[width=2.8in]{rhoRescaled.png}}
\subfigure[Mesh]{\includegraphics[width=2.8in]{mesh12.png}}
\caption{Rescaled solution for $\rho$ in the range $[\rho_{\min},2]$ and adaptive mesh after 12 refinement steps.}
\label{fig:rhoScaled}
\end{figure}

We can also zoom in on the plate tip to view the solution quality at the singular point.  Figure~\ref{fig:Re1000_zoom} demonstrates that the solution remains smooth and well-resolved at the plate tip, despite the presence of a singularity in the viscous stresses.%, and the fact that high order methods do not tend to resolve singularities as efficiently as low order methods \cite{hp1}.\cite{Optimal $hp$-adaptive strategies for elliptic problems with singularities result in meshes of lowest

\begin{figure}
\centering
\subfigure[$\rho$]{\includegraphics[scale=.23]{rhoZoom.png}}
\subfigure[$u_1$]{\includegraphics[scale=.23]{u1Zoom.png}}
\subfigure[$u_2$]{\includegraphics[scale=.23]{u2Zoom.png}}
\subfigure[$T$]{\includegraphics[scale=.23]{TZoom.png}}
\caption{Zoom of solutions at the beginning of the plate for $p=2$ and $\Reyn = 1000$.}
\label{fig:Re1000_zoom} 
\end{figure}

We increased the Reynolds number to $10,000$ to assess the behavior of DPG for higher Reynolds numbers.  However, we found it necessary to modify the method in several ways in order to achieve satisfactory results.

First, we implemented a line search algorithm to enforce positivity of both temperature and density, which are physically defined to be positive quantities.  Given updates $\triangle \rho$ and $\triangle T$, we update our previous solution by setting 
\begin{align*}
\rho \coloneqq \rho + \alpha_{\rm line}\triangle \rho \\
T \coloneqq T + \alpha_{\rm line}\triangle T,
\end{align*}
where $\alpha_{\rm line}$ is chosen, for some $\delta > 0$, such that
\begin{align*}
\rho + \alpha_{\rm line}\triangle \rho - \delta = 0\\
T + \alpha_{\rm line}\triangle T  - \delta = 0.
\end{align*}
Since the addition of a line search can slow the convergence of a nonlinear algorithm, we incorporate also a Newton iteration at each timestep to effectively solve the nonlinear system at each timestep.  We consider $\nor{\triangle U}_E < \epsilon_{\rm Newton}$ to be our condition for convergence of the Newton iteration, though we also limit the number of allowed Newton steps for computational efficiency.  The full solver algorithm is given in Algorithm~\ref{fig:algorithm}.  
\begin{algorithm}                      % enter the algorithm environment
\caption{Calculate $y = x^n$}          % give the algorithm a caption
\label{alg1}                           % and a label for \ref{} commands later in the document
\begin{algorithmic}                    % enter the algorithmic environment
\FOR{ number of refinement steps } 
    \WHILE{ $R_{\rm time} > \epsilon_t$}
        \STATE k = 0
        \WHILE{$\nor{\triangle U}_E > \epsilon_{\rm Newton}$ and $k <$ maximum Newton steps}
            \STATE Solve for $\triangle U$, determine $\alpha_{\rm line}$.  
            \STATE $U \coloneqq U + \alpha_{\rm line}\triangle U$.  
            \STATE k = k+1
        \ENDWHILE
        \STATE Increment timestep.  
    \ENDWHILE
    \STATE Compute energy error and refine based on a greedy refinement algorithm.
    \STATE Set $\epsilon_t = \alpha_t \nor{u-u_h}_E$.    
\ENDFOR
\end{algorithmic}
\caption{Pseudo-timetepping adaptive algorithm with line search.}
\label{fig:algorithm}
\end{algorithm}
For higher Reynolds numbers and highly refined meshes, the solution update exhibits large oscillations, such that the solution at a timestep can become negative, under which the pseudo-timestepping algorithm can stall or even diverge.\footnote{We note that these large oscillations mimic experiences in 1D as well, where the linearized solution was shown to exhibit sharp gradients near shocks that did not disappear, even with additional mesh refinement, indicating that the presence of such overshoots and undershoots is a consequence of the linearization, as opposed to the stability of the discretization \cite{NS_DPG1D}. This is discussed in more detail in Section~\secref{sec:oscillations}.

We note also that theory developed in \cite{DPGrobustness2} for the convection-diffusion problem assumes a smooth convection field.  However, under linearization of the Burgers' and Navier-Stokes equations, the solution around which we linearize dictates the convection field, and can display large gradients.  While we have not observed issues in the Burgers' equation related to this, we hope to revisit the analysis done in \cite{DPGrobustness2} and generalize it for convection fields with large gradients.}.  However, we have observed that requiring a strictly positive solution appears to be too restrictive a constraint for some meshes; the use of line search does not appear to be necessary for convergence of the pseudo-timestepping algorithm on coarser meshes (until the 10th refinement iteration, or $h< .001$).

Finally, we implement an ``effective'' CFL number; though implicit time integration schemes are unconditionally stable (compared to explicit schemes), a CFL condition relating the size of the time increment to the (minimum) mesh size is often still used in practice to improve convergence speed and stability of the numerical scheme \cite{Shakib1991141}.   Our CFL number is chosen to be 64.  We note that this CFL number is implemented for non-standard reasons.  In fact, DPG is able to solve the steady-state system directly without the use of pseudo-timestepping (direct Newton iteration).  However, as noted previously, the size of the timestep under which pseudo-timestepping converges greatly affects the qualitative nature of the solution.  Figure~\ref{fig:dtCompare} demonstrates the difference between convergence at large and small timesteps -- for $dt$ large relative to the mesh size, the solution experiences upstream ``pollution'' effects.  
\begin{figure}
\centering
\subfigure[$dt = \infty$ (Direct Newton)]{\includegraphics[width=2.8in]{dtInf.png}}
\subfigure[$dt = 1.0$]{\includegraphics[width=2.8in]{dtOne.png}}
\subfigure[$dt = .1$]{\includegraphics[width=2.8in]{dtTenth.png}}
\caption{Steady state solutions for ${\rm Re} = 10,000$ under three different timesteps on a $16\times 8$ uniform mesh.}
\label{fig:dtCompare}
\end{figure}
Due to the upstream ``pollution'' present in the solution for $dt \geq 1$, the adaptive mesh refinement algorithm tends to add extraneous refinements on elements adjacent to the boundary $y = 0$, $x\in (0,1)$.  Decreasing the timestep alleviates this issue somewhat; however, an overly small timestep requires a large number of iterations to converge.  The implementation of an effective CFL number aims to balance the size of the timestep with the mesh size.\footnote{An additional reason for the implementation of an effective CFL number is the conditioning of the local problem, which was discussed for the convection-dominated diffusion problem in \cite{DPG3}.  The main problem concerning conditioning of local problems is the way that different test terms behave as a function of local element size.  We illustrate this using the element Sobolev norm $\nor{v}_{H^1(K)} = \nor{v}_{\L} + \nor{\grad v}_{\L}$ -- $\nor{v}_{\L} = O(h^2)$ (where $h$ is the element size), while $\nor{\grad v}_{\L} = O(1)$.  Thus, as $h\rightarrow 0$, the Sobolev norm over a single element approaches the Sobolev seminorm and loses positive definiteness, resulting in a highly ill-conditioned system to solve.  The addition of a first-order pseudo-timestepping term allows us to increase the relative magnitude of $\nor{v}_{\L}$ with respect to $\nor{\grad v}_{\L}$ and avoid conditioning issues while maintaining robustness of the method.}

We note that, even with all of the above modifications, the pseudo-timetepping adaptive algorithm with line search would sometimes failed to converge below $\epsilon_t$ for ${\rm Re} \geq 10,000$.  Figure~\ref{fig:nonconvergence} shows a plot of the transient residual after the 14th refinement step; while the residual initially decreases, it stalls at about $R_{\rm time} \approx 10^{-4}$.  
\begin{figure}
\centering
\subfigure[Non-convergence]{\includegraphics[width=2.5in]{oscillations1.pdf}}
\subfigure[Recovery of convergence]{\includegraphics[width=2.5in]{oscillations2.pdf}}
\caption{Stalling and recovery of the pseudo-timestep iteration for $\Reyn = 10000$.}
\label{fig:nonconvergence}
\end{figure}
An examination of the difference in the solutions between the final and $125$th timesteps shows that the nonconvergence of the transient residual is due to oscillations in the solution (primarily in $\rho$) slightly upstream to the plate edge.  Visually, the solution converges everywhere else, save for this area.  Such behavior is also observed in \cite{BenKirk}, where, at the change in boundary conditions between the free stream and flat plate, an oscillation was observed in the solution which prevented convergence of his pseudo-time algorithm.  His oscillations are of smaller magnitude ($O\LRp{10^{-6}}$ as opposed to $O\LRp{10^{-4}}$), which may be the result of several differences between the methods presented.\footnote{Apart from the use of a standard Galerkin (continuous as opposed to discontinuous Galerkin) formulation, Kirk's approach differed from ours in the use of linear elements and the addition of artificial diffusion shock-capturing terms, both of which could explain the lower point at which error stagnates. Reasons for this loss of convergence in the pre-asymptotic range should be explored further.}  However, we note that, under additional refinements and increased resolution of the solution, the transient residual once again decreases in a smooth monotonic fashion, as shown in Figure~\ref{fig:nonconvergence}.

\begin{figure}
\centering
\subfigure[$\rho$]{\includegraphics[width=2.8in]{rhoRe4Plate.png}}
\subfigure[$u_1$]{\includegraphics[width=2.8in]{u1Re4Plate.png}}
\subfigure[$u_2$]{\includegraphics[width=2.8in]{u2Re4Plate.png}}
\subfigure[$T$]{\includegraphics[width=2.8in]{TRe4Plate.png}}
\caption{Solutions after 18 refinements for $p=2$ and $\Reyn = 10000$.}
\label{fig:Re10000}
\end{figure}

For additional computational efficiency, we also implemented an anisotropic refinement scheme.  In 2D, the boundary layer is a primarily 1D phenomena, which we expect to be far better resolved by anisotropic refinement than by isotropic refinement.  We experimented first using the scheme described in Section~\secref{sec:aniso} as an anisotropy indicator; however, the anisotropic scheme appeared to be too conservative near the boundary layer, placing primarily isotropic refinements.  We modified our scheme in two ways -- first, we incorporated spatially variable thresholding.  Typically, anisotropic refinement in the $x$ direction is chosen if $e_{x,K} > \epsilon_r e_{y,K}$ (and vice versa for anisotropic refinement in the $y$-direction), where $e_{x_i,K}$ is the error in the $x_i$ direction.  We set $\epsilon_r = \epsilon_{r,K}$; in other words, we allow our anisotropic threshold to vary element-by-element, and decrease it from $\epsilon_r= 10$ to $\epsilon_{r,K} = 2.5$ for elements adjacent to the wall upon which the boundary layer forms.  Additionally, since the boundary layer typically displays rapid variation in the $y$-direction (the direction orthogonal to the wall), we relax the condition under which a vertically cut anisotropic refinement occurs to
\[
2 e_{y,K} > \epsilon_{r,K} e_{x,K}.
\]
Despite the artificial modification of the anisotropic refinement scheme, the resulting meshes still resolve boundary layer solutions more efficiently than isotropic refinements.  We hope to investigate reasons for the ineffectiveness of the pure anisotropic scheme for the compressible Navier-Stokes equations in future research.

\begin{figure}
\centering
\subfigure[$\rho$]{\includegraphics[width=2.8in]{rhoRescaledRe4Plate.png}}
\subfigure[Mesh]{\includegraphics[width=2.8in]{meshRe4Plate.png}}
\caption{Rescaled solution for $\rho$ in the range $[\rho_{\min},2]$ and adapted mesh.}
\label{fig:rhoScaled}
\end{figure}

\begin{figure}
\centering
\subfigure[$\rho$]{\includegraphics[width=2.8in]{rhoZoomRe4Plate.png}}
\subfigure[$u_1$]{\includegraphics[width=2.8in]{u1ZoomRe4Plate.png}}
\subfigure[$u_2$]{\includegraphics[width=2.8in]{u2ZoomRe4Plate.png}}
\subfigure[$T$]{\includegraphics[width=2.8in]{TZoomRe4Plate.png}}
\caption{Zoom of solutions at the beginning of the plate for $p=2$ and $\Reyn = 10000$.}
\label{fig:Re1e4Zoom}
\end{figure}

We note that the resolution of the solution near the plate edge in Figure~\ref{fig:Re1e4Zoom} for Reynolds number 10000 is qualitatively rougher than that for Reynolds 1000 in Figure~\ref{fig:Re1000_zoom}; this is due to the greedy refinement algorithm emphasizing refinements most strongly at the singular point and not in shock resolution, as well as the fact that at a higher Reynolds number, the shock width is thinner and more difficult to resolve.  Further refinement steps improve resolution of the shock features.

%\begin{figure}[!h]
%\centering
%\subfigure[${\rm Re} = 1000$]{\includegraphics[scale=.5]{figs/Re1000p2/heatflux.png}}
%\subfigure[${\rm Re} = 10000$]{\includegraphics[scale=.3]{figs/Re1e5/q2line.png}}
%\caption{Heat flux at the bottom boundary.}
%\end{figure}

\subsection{Holden ramp problem}

Our second problem is a modified version of the Holden ramp problem, which models supersonic/hypersonic flow over a compression corner (the geometry of which is given in Figure~\ref{fig:holdenCartoon}).  Similarly to the Carter flat plate problem, a flat plate disrupts the flow and forms a weak shock at the plate tip due to viscous effects and no-slip boundary conditions.  The boundary layer grows down the plate edge, deflecting upwards due to the presence of the compression corner.  A stronger shock forms slightly upstream of the compression corner in order to deflect the incoming supersonic flow, and is a common test problem for adaptive finite element methods for compressible flow \cite{Rachowicz1997231,Barter,BenKirk}.

\begin{figure}
\centering
\includegraphics[width=4in]{holden.pdf}
\caption{A modification of the Holden ramp/compression corner problem.}
\label{fig:holdenCartoon}
\end{figure}

The original plate length is given to be .442, while the ramp length is given to be .269. We have modified the problem slightly in order to exactly represent the boundary conditions on a coarse mesh while keeping the ratio of plate length to ramp length roughly the same. Similarly to the Carter flat plate, we start out with a very coarse $2 \times 3$ mesh of 6 elements.  We initialize our solution to the freestream values
\[
\rho_{\infty} = 1,\qquad u_{1,\infty}= 1,\qquad u_{2,\infty} = 0, \qquad T_{\infty} = 1
\]
and again set stresses uniformly to zero.

\begin{figure}
\centering
\subfigure[$\rho$ rescaled]{\includegraphics[width = 2.9in]{rhoRescaledMa6Ramp.png}}
\subfigure[$u_1$]{\includegraphics[width = 2.9in]{u1Ma6Ramp.png}}
\subfigure[$u_2$]{\includegraphics[width = 2.9in]{u2Ma6Ramp.png}}
\subfigure[$T$]{\includegraphics[width = 2.9in]{TMa6Ramp.png}}
\subfigure[Mesh]{\includegraphics[width = 5.5in]{meshMa6Ramp.png}}
\caption{Solutions and adaptive mesh for ${\rm Ma} = 6$ and $\Reyn = 10000$.}
\label{fig:holdenMa6}
\end{figure}

We first solve under Mach 6 flow.\footnote{The increase in Mach number is to change the angle of the shock; under the current setup, Mach 3 flow produced a shock which reflected off the top boundary $y = 1$  We note that the effect of Mach number under our nondimensionalization of choice is to decrease the thermal diffusivity constant $\kappa$ relative to the viscosities $\mu$ and $\lambda$.} and Reynolds number of 10,000, or a Reynolds number of 33,936 if measured with respect to the original plate length of .442.  The wall temperature is set to $T_{w} = 2.8T_{\infty}$, identically to the flat plate problem.  24 mesh refinements were performed, resulting in a final mesh of 1858 elements.  Figure~\ref{fig:holdenMa6} shows both solution values and final adaptive mesh.  Due to a large maximum value of $\rho_{\max} = 14.1538$ at the plate tip, the resulting solution for $\rho$ is scaled to better show qualitative features of the flow.  The presence of the second shock deflecting the incoming supersonic flow at the ramp is clearly seen in both the solutions and the adaptive mesh refinements.

\begin{figure}
\centering
\subfigure[Initial mesh]{\includegraphics[width = 2.9in]{rampMesh0.png}}
\subfigure[6 refinements]{\includegraphics[width = 2.9in]{rampMesh6.png}}
\subfigure[12 refinements]{\includegraphics[width = 2.9in]{rampMesh12.png}}
\subfigure[18 refinements]{\includegraphics[width = 2.9in]{rampMesh18.png}}
\caption{Sequence of adaptive meshes for ${\rm Ma} = 6$ and $\Reyn = 10000$.}
\label{fig:holdenMa6Meshes}
\end{figure}

We can examine the sequence of adaptive meshes generated by the DPG method.  Figure~\ref{fig:holdenMa6Meshes} shows the initial mesh, as well as the 6th, 12th, and 18th subsequent refinements generated automatically by the DPG method.  Unlike the previous sequence of meshes generated by the flat plate example, refinements tend to be placed most heavily near the shock at the outflow ramp.  By the 18th refinement, the adaptive mesh looks qualitatively very similar to the final mesh of 24 refinements, and further refinements focus on the resolution of the shocks originating at the plate edge and at the ramp outflow.

\begin{figure}
\centering
\subfigure[$\rho$ rescaled]{\includegraphics[width = 2.9in]{rhoRescaledshockMa6Ramp.png}}
\subfigure[$T$]{\includegraphics[width = 2.9in]{TshockMa6Ramp.png}}
\subfigure[Mesh]{\includegraphics[width = 4in]{shockMeshMa6Ramp.png}}
\caption{Zoom of solutions and adaptive mesh around shock. }
\label{fig:holdenMa6Zoom}
\end{figure}

Figure~\ref{fig:holdenMa6Zoom} shows a zoom of the second stronger shock that develops near the ramp outflow.  Refinements are placed very heavily near the shock, which we expect due to the fact that a shock forms a stronger gradient than a boundary layer.  We note that our residual-driven adaptivity scheme places mesh refinements in a very precise manner; refinements on ramp boundary are placed slightly more heavily upstream than downstream.  We believe this is due to the fact that solution gradients are slightly higher in $\rho$ at the upstream section of the ramp.

\begin{figure}
\centering
\subfigure[$\rho$ rescaled]{\includegraphics[width = 2.9in]{rhoRescaledMa11Ramp.png}}
\subfigure[$u_1$]{\includegraphics[width = 2.9in]{u1Ma11Ramp.png}}
\subfigure[$u_2$]{\includegraphics[width = 2.9in]{u2Ma11Ramp.png}}
\subfigure[$T$]{\includegraphics[width = 2.9in]{TMa11Ramp.png}}
\subfigure[Mesh]{\includegraphics[width = 5.5in]{meshMa11Ramp.png}}
\caption{Solutions and adaptive mesh for ${\rm Ma} = 11.68$ and $\Reyn = 16442.4$.}
\label{fig:holdenMa11}
\end{figure}

The second set of conditions under which we solve are under Mach 11.68 flow and Reynolds number of 16,4	42.4, or 55,800 if measured with respect to original plate length, with the wall temperature set to $T_{w} = 4.6T_{\infty}$.  24 automatic mesh refinements are performed under an energy threshold of $.5$, resulting in a final mesh of 2385 elements.

Figure~\ref{fig:holdenMa11} shows the resulting solution and final adaptive mesh.  The increased Mach number changes again the angle of the weak shock resulting from the change in boundary conditions at the plate edge.  Compared to the previous case of Mach 6 flow, where only 18 refinements steps were performed, 24 refinements were performed for the Mach 11.68 case, leading to a more highly resolved solution, especially near the plate tip.  Due to a large maximum value of $\rho_{\max} = 50.1805$ at the plate tip, the resulting solution for $\rho$ is scaled to better show qualitative features of the flow.

%We note that, under a higher Mach number, the placement of adaptive mesh refinements appears to improve.  The element size adjacent to the plate tip for the Mach $6$ case is $h = O\LRp{10^{-4}}$, while the size of elements adjacent to the plate tip in the Mach 11 case is $h = O\LRp{10^{-5}}$.  For the Mach $6$ and Reynolds $10,000$ case of the ramp problem, several extraneous refinements were placed slightly upstream of the plate tip, corresponding to the location of large gradients in the Newton solution update.  More study is necessary to determine the reasons for the difference in behavior of the automatic adaptivity algorithm.
%
%\begin{figure}[!h]
%\centering
%%\subfigure[$\rho$]{\includegraphics[width = 2.9in]{rhoshock.png}}
%%\subfigure[$T$]{\includegraphics[width = 2.9in]{Tshock.png}}
%\subfigure[Mach 6]{\includegraphics[width = 2.75in]{plateMesh.png}}
%\subfigure[Mach 11]{\includegraphics[width = 2.75in]{plateMesh.png}}
%\caption{Zoom of solutions and adaptive mesh around the plate tip.}
%\label{fig:plateComparison}
%\end{figure}

\begin{figure}
\centering
\subfigure[$\rho$ rescaled]{\includegraphics[width = 2.9in]{rhoshockMa11Ramp.png}}
\subfigure[$T$]{\includegraphics[width = 2.9in]{TshockMa11Ramp.png}}
\subfigure[Mesh]{\includegraphics[width = 4in]{shockMeshMa11Ramp.png}}
\caption{Zoom of solutions and adaptive mesh around shock. }
\label{fig:holdenMa11Zoom}
\end{figure}

Compared to the Mach 6 case, where 18 refinements were performed, the resolution of the mesh near the shock at the ramp outflow for Mach 11.68 flow and 18 refinements is qualitatively similar.  Further refinement steps increase resolution of the mesh near the shock, as shown in Figure~\ref{fig:holdenMa11Zoom}.

Finally, we plot the normal heat flux over the plate and ramp for both Holden problems in Figure~\ref{fig:heatFlux}.  The normal heat flux over the flat plate is indicated by the blue line, while the dotted brown line indicates the heat flux over the ramp, and both are plotted against the x-coordinate along the plate/ramp boundary.  The normal heat flux is given by the normal trace of the conserved quantity in the energy equation
\[
\widehat{f}_{4,n} = (\rho e+p)u_n - \boldsymbol n\cdot \boldsymbol \sigma\cdot \boldsymbol u + q_n.
\]
Recognizing that $u_1 = u_2 = 0$ reduces the above to $\widehat{f}_{4,n} = q_n$.

The heat flux develops a strong singularity at the point $(-.5,0)$, where the boundary condition changes from a Neumann/stress boundary condition to a Dirichlet/no-slip boundary condition.\footnote{Figure~\ref{fig:heatFlux} cuts off this singularity in order to show the qualitative behavior of $q_n$ over the remainder of the boundary.  The maximum visualized values in the singular portion of $q_n$ are .35 for Mach 6 flow and 1.268 for Mach 11.68 flow.}  It can be shown that the Laplace equation develops a singularity in stress at under any such change in boundary conditions, and the same phenomena is observed for a similar setup under convection-diffusion \cite{localConservationDPG}.

\begin{figure}
\centering
\subfigure[Mach 6, Reynolds 10,000]{\includegraphics[width=2.9in]{heatFluxMa6Ramp.png}}
\subfigure[Mach 11.68, Reynolds 16,442.4]{\includegraphics[width=2.9in]{heatFluxMa11Ramp.png}}
\caption{Normal heat flux $q_n$ over plate and ramp for the Holden problem.  The blue line indicates $q_n$ over the flat plate, while the brown line indicates $q_n$ over the ramp. }
\label{fig:heatFlux}
\end{figure}

\subsection{Higher Reynolds numbers}
\seclab{sec:oscillations}
For higher Reynolds number, the pseudo-timestepping, we have encountered difficulties which have made it difficult to converge to a steady-state solution, even under the addition of an effective CFL number and line search to enforce positivity of density $\rho$ and temperature $T$.  However, we believe these difficulties to be related to the nature of the equations, rather than the robustness of the method.  We illustrate this with a simple example.

Let us consider the 1D steady state viscous Burgers' equation on $[-\infty,\infty]$
\[
u\pd{u}{x} - \epsilon \pdd{u}{x} = 0.
\]
The exact solution to this equation under boundary conditions
\begin{align*}
u(-\infty) &= 1\\
u(\infty) &= -1
\end{align*}
can be easily derived (see \cite{Barter} for a simple derivation), and the solution and its first two derivatives are
\[
u(x) = \frac{1-e^{\frac{x}{\epsilon}}}{1+e^\frac{x}{\epsilon}}, \qquad u'(x) = \frac{-2e^{\frac{x}{\epsilon}}}{\LRp{1+e^{\frac{x}{\epsilon}}}^2\epsilon}, \qquad u''(x) = \frac{-2e^{\frac{x}{\epsilon}}\LRp{e^{\frac{x}{\epsilon}}-1}}{\LRp{1+e^{\frac{x}{\epsilon}}}^3\epsilon^2}
\]
\begin{figure}
\centering
\subfigure[$u(x)$]{\includegraphics[width = 1.8in]{u.pdf}}
\subfigure[$u'(x)$]{\includegraphics[width = 1.8in]{du.pdf}}
\subfigure[$u''(x)$]{\includegraphics[width = 1.8in]{ddu.pdf}}
\caption{$u(x)$ and its derivative and second derivative for $\epsilon = .01$.}
\label{fig:burgersSoln100}
\end{figure} 
Figure~\ref{fig:burgersSoln100} shows each of these functions for $\epsilon = .01$.  From the form of $u'(x)$ and $u''(x)$, we know these oscillations will grow rapidly as $\epsilon$ decreases.  Consider now the linearized Burgers' equation
\[
\pd{u\Delta u}{x} - \epsilon \pdd{\Delta u}{x} = - r(x)
\]
where $r(x) = u\pd{u}{x} - \epsilon \pdd{u}{x}$ is the strong form of the nonlinear residual.  Recall that for a pure Newton iteration, $u(x)$ is assumed to be known, and the linearized problem is driven by the residual.  The solution $u(x)$ is updated $u \coloneqq u + \Delta u$, and is repeated until $\Delta u$ and $r(x)$ are both approximately zero.

Let $u_\epsilon(x)$ be the exact solution for a particular viscosity $\epsilon$, and consider the setting of $u(x) = u_{\alpha \epsilon}(x)$, with $\alpha > 1$.  In other words, the initial guess for the Newton iteration is taken to be the exact solution for the viscous Burgers' equation under a larger viscosity (a less sharp shock), a method known as continuation (specifically, continuation in viscosity $\epsilon$).\footnote{We note that continuation in Reynolds number was attempted for the Navier-Stokes equations; however, the presence of large oscillations in the Newton update on highly adapted meshes caused the line search to return a near-zero step length, which stalled the nonlinear iteration prior to convergence to a steady state solution.}

\begin{figure}
\centering
\subfigure[$\epsilon = .01$]{\includegraphics[width = 2.5in]{residual100.pdf}}
\subfigure[$\epsilon = .001$]{\includegraphics[width = 2.5in]{residual1000.pdf}}
\caption{Residual for Burgers' equation with viscosity $\epsilon$ under the exact solution for ${2\epsilon}$.}
\label{fig:burgersResidual}
\end{figure}

We plot $r(x)$ for $u(x) = u_{2\epsilon}(x)$ in Figure~\ref{fig:burgersResidual}.  While the form of the exact linearized solution $\Delta u$ is unknown, we see that the forcing term in the above equation develops oscillations that grow in magnitude and decrease in support as $\epsilon$ decreases.  We have observed similar behaviors for discretized solutions to the Burgers' and Navier Stokes equations -- the discrete linearized solution will develop gradients as well, though their magnitude will be limited by the resolution of the mesh.  However, additional refinements near shocks will introduce additional oscillations, which are subsequently damped by additional Newton iterations.

In other words, not all oscillations are related to the method of discretization -- the exact linearized solution itself contains large oscillations, which are picked up more and more strongly in a discrete scheme as the mesh resolution approaches the viscous length scale $\epsilon$ (see \cite{DPGspacetime, DPGNS_1d} for additional numerical examples).  We note that these large oscillations are not an issue for the viscous Burgers' equation, as there is no positivity constraint on $u$.  However, as noted previously, the convergence of the nonlinear iteration for the compressible Navier-Stokes equations can stall or even diverge for sufficiently negative values of $\rho$ and $T$, which happens easily in the presence of large oscillations.  When a line search is implemented to enforce a strictly positive solution, the nonlinear iteration can stall, and numerical experiments have generated cases in which the line search length goes to zero, returning an under-converged solution.

There are several approaches to controlling the magnitude of oscillations in the linearized solution -- a simple option is decreasing the size of the timestep; however, doing so can cause the number of iterations required for convergence to greatly increase.  The application of artificial diffusion near sharp gradients is another way in which to control such oscillations; however, this results in a modified set of equations, and, though solutions with contemporary artificial viscosity methods can produce solutions with expected qualitative features, there is a wide range of choices for artificial diffusion, and it was not clear in the scope of this paper which artificial viscosity method would be quantifiably superior, or most suitable for use with the DPG method.

### 2013-07-22 docs/Jesse/NavierStokes paper/NonlinDPG.tex
updating confusion, dissertation, and NS

--- 2013-05-15 docs/Jesse/Dissertation/NonlinDPG.tex
@@
 \section{DPG for nonlinear problems}
-
+\seclab{sec:nonlinDPG}
 In this chapter, we extend DPG to the nonlinear setting and apply it to two problems in computational fluid dynamics.  We take as our starting point a nonlinear variational formulation
@@
 This procedure is then repeated for the next timestep $t_{i+1}$ until the transient residual decreases such that $\nor{u(t_i) - u(t_{i-1})}_{L^2(\Omega)} = \nor{\Delta u(t_i)}_{L^2(\Omega)} \leq tol$.\footnote{Strictly speaking, seeking the solution at each timestep involves the solution of a nonlinear problem, requiring a Newton-type iteration to solve for $u(t_i)$.
-However, for most applications, it is sufficient to approximate the nonlinear solution using a single Newton solve at each time step.}
+For most applications, it is sufficient to approximate the nonlinear solution using a single Newton solve at each time step.}
 \end{itemize}
 
-In practice, most compressible flow solvers opt for the pseudo-time step method over the direct Newton iteration due to the difficulty of convergence and sensitivity of the Newton iteration to initial guess\cite{libMeshPaper}.
+In practice, most compressible flow solvers opt for the pseudo-time step method over the direct Newton iteration due to the difficulty of convergence and sensitivity of the Newton iteration to initial guess\cite{libMeshPaper, gunzburger1989finite}.
 Though the convergence of the pseudo-time step is slower, the addition of the zero-order transient terms ``regularizes" the problem and makes it less difficult to solve.\footnote{The addition of a zero-order term ``regularizes" an equation by adding to it a positive-definite $L^2$ projection operator.
@@
 Since DPG allows for the formulation of a discrete nonlinear residual, it is possible to formulate the nonlinear DPG problem as a minimization problem and use an optimization method to solve the discrete nonlinear problem.
-This approach has been successfully implemented by Peraire et al.\ in solving compressible gas dynamics problems on uniform grids using a modified version of the ultra-weak variational formulation \cite{MITDPG}.
+This approach has been successfully implemented in solving compressible gas dynamics problems on uniform grids using a modified version of the ultra-weak variational formulation \cite{MITDPG, optDPG}.
 An additional advantage of such an approach would be the more direct enforcement of physical constraints, which are treated in an ad-hoc manner in most compressible Navier-Stokes solvers.
@@
 \]
+We note that, under convergence of any of the nonlinear iterations described above, the converged DPG solution does in fact satisfy the above minimization problem \cite{MITDPG}, and that the DPG energy error converges to the nonlinear residual.
+However, it is theoretically possible to accelerate convergence of a nonlinear iteration to the minimizer $u_h$, using the same minimum residual framework DPG is based upon.
+
 Similarly to the linear case, we can take the Gate\'aux derivative to arrive at a necessary condition for $u_h$ to minimize $J(u_h)$ 
@@
 We note that we have not implemented this Hessian-based nonlinear solver in the numerical experiments to follow, and instead plan to do so in future work.
+
+\subsection{DPG as a Gauss-Newton approximation}
+
+The above Hessian-based nonlinear DPG method essentially replaces a simple linearization of with a higher-order expansion of the residual $J(u_h)$.
+However, the application of DPG to the linearized equations actually yields a Gauss-Newton method for minimizing $J(u_h)$.
+
+Recall that the discrete DPG method applied to a linear problem solves
+\[
+{B}^T{R_V}^{-1}{B}u - {B}^T{R_V}^{-1}l  = 0
+\]
+where ${B}$ is the rectangular matrix of size $m\times n$ resulting from the variational form $b(u,v)$ (where $m = \dim(U_h)$ and $n = \dim(V_h)$), and ${R_V}$ is the Gram matrix of dimension $n\times n$ resulting from choice of norm $\nor{\cdot}_V$ and inner product on $V$.
+If we have the nonlinear equation ${B}(u_h)-{l}$ and linearize it, we have ${B}_u\triangle u_h = {r}(u_h)$, where $r(u_h) = l-B(u_h)$ is the residual.
+The solution of the linearized equation by DPG minimizes then $\nor{r(u_h) - B_u\triangle u_h}_{V'}^2$, which we can recognize as linear least squares equations from which the Gauss-Newton method is derived \cite{Nocedal2006NO}.
+
+Initial experiments with Hessian-based nonlinear DPG under Burgers' equation indicate that eigenvalues of the stiffness matrix can become negative if the Hessian is applied.
+While the Gauss-Newton iteration may not converge as rapidly as the Hessian-based version of DPG, it does guarantee positive eigenvalues of the stiffness matrix, such that $\Delta u_h$ is always a descent direction.

### 2013-07-22 docs/Jesse/NavierStokes paper/confusionSummary.tex
updating confusion, dissertation, and NS

\section{DPG for convection-diffusion}

The convection-diffusion problem can be given as a first order system: 
\begin{align*}
\div \left(\beta u - \sigma\right) &= f\\
\frac{1}{\epsilon}\sigma - \grad u &= 0,
\end{align*}
with inflow boundary conditions $\left.u\right|_{\Gamma_{\rm in}} = u_{\rm in}$, and outflow boundary conditions $\left.u\right|_{\Gamma_{\rm out}} = u_{\rm out}$.  The inflow and outflow boundaries are defined
\begin{align*}
\Gamma_{\rm in} &\coloneqq \{x\in \Gamma; \beta_n(x) \leq 0\}, \quad {\rm (inflow)}\\ 
\Gamma_{\rm out} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\}, \quad {\rm (outflow)}
%\Gamma_{0} &\coloneqq \{x\in \Gamma; \beta_n(x) = 0\},
\end{align*}
On domain $\Omega$, with mesh $\Oh$ and mesh skeleton $\Gh$, the ultra-weak variational formulation for convection-diffusion is
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),\left( v, \tau \right)\right) &= 
\left(u,\div \tau - \beta \cdot \grad v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh} 
- \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n, \jump{v} }_{\Gh}.
\end{align*}
with $v\in H^1$ and $\tau \in H({\rm div},\Oh)$.

\subsection{Inflow boundary condition and choice of test norm}
\seclab{sec:testNormSec}

Given the above properties of DPG, we can see that the choice of test norm will determine the behavior of DPG; however, the proper choice of test norm can be unclear.  There exists a canonical graph norm for the ultra-weak variational formulation under which well-posedness can be proven for a large class of problems, and near-optimality is observed in numerical experiments \cite{DPG4, Bui-ThanhDemkowiczGhattas11b, stokesDPG}.  However, for the specific problem of convection-diffusion, the resolution of optimal test functions resulting from the graph norm prove very difficult to approximate \cite{globalLocalDPG}.  In \cite{DPGrobustness}, Demkowicz and Heuer introduced guidelines for the construction of alternative test norms based on energy estimates for the adjoint equation. We follow \cite{DPGrobustness2}, where, in addition to constructing an alternative test norm, a new inflow boundary condition is introduced in order to regularize the adjoint equation.

Typical boundary conditions for the convection-diffusion problem enforce a Dirichlet condition on both inflow and outflow.  We adopt instead a``conserved flux'' inflow boundary condition, 
\[
\beta_nu - \epsilon\pd{u}{n} \approx u_{\rm in}.
\]
This corresponds to the imposition of a boundary condition on the conserved flux $\fnh = \beta_nu - \sigma_n$.  For small $\epsilon$ and most problems of interest, both $\pd{u}{n}$ and $\epsilon$ tend to be small, such that the above is a good approximation of $\left.u\right|_{\Gamma_{\rm in}} = u_{\rm in}$.

Under this boundary condition, the adjoint problem is regularized such that its solutions are smoother, which in turn improves the stability of the DPG method \cite{DPGrobustness2}.  We illustrate this improvement with a simple numerical experiment; Figure~\ref{fig:confusion1D} demonstrates the behavior of the DPG method under both the standard Dirichlet and the new conserved flux boundary conditions.  In both cases, the test norm used is the 1D Sobolev norm $\nor{\LRp{v,\tau}}_V\coloneqq \nor{v}_{H^1} + \nor{\tau}_{H^1}$.  The left figure shows the behavior of DPG under a Dirichlet boundary condition; degeneration of the solution is observed as $\epsilon$ decreases.  In contrast, under the new conserved flux boundary condition, as $\epsilon$ decreases, the solution converges to the $L^2$ projection of the exact solution onto our trial space.

\begin{figure}
\centering
\subfigure[Dirichlet boundary condition $u(0) = 1$]{\includegraphics[width=2.75in]{dirichletBC.png}}
\subfigure[``Conserved flux'' boundary condition $u(0) - \epsilon u'(0) = 1$]{\includegraphics[width=2.75in]{newBC.png}}
\caption{Behavior of the 1D DPG method for convection diffusion under both standard Dirichlet and conserved flux boundary conditions.}
\label{fig:confusion1D}
\end{figure}

The test norm for convection-diffusion in multiple dimensions is defined elementwise on $K$ as
\[
\|\left(v,\tau\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau-\beta\cdot\grad v\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
\]
DPG under $\nor{\cdot}_V$ both delivers robust control of the $L^2$ error in the variables $u$ and $\sigma$ and minimizes approximation error in the solution of \eqnref{optvVar}.

\subsection{Anisotropic refinement}
\seclab{sec:aniso}
Isotropic adaptive mesh refinement has shown itself to be an effective way to resolve isolated solution features with large gradients, such as point singularities \cite{hp1,hp3}. However, for the resolution of phenomena such as shocks or boundary layers, anisotropic mesh refinement can resolve solution features for a much lower cost per degree-of-freedom, due to the fact that boundary layers in $n$-dimensions are primarily phenomena supported over $n-1$ dimensions.

As a least squares method, DPG already includes a natural error indicator with which to drive adaptive mesh refinement.  To introduce anisotropic refinements, we need to introduce an anisotropy indicator in order to detect in which direction solution features are aligned.  In general, a test norm can be expressed as the sum of normed quantities, both scalar and vector valued.  If we restrict ourselves to quadrilateral elements for the moment, a general anisotropy indicator for DPG can be constructed by evaluating the $\L$ norms of the individual components of vector valued terms in the test norm.

Under the robust test norm derived in this chapter for the convection-dominated diffusion problem, we can define $x$ and $y$ error contributions over a single element
\begin{align*}
e_{x,K} &= \epsilon \nor{\pd{v}{x}}_{L^2(K)}^2 + \nor{\tau_x}_{L^2(K)}^2 \\
e_{y,K} &= \epsilon \nor{\pd{v}{y}}_{L^2(K)}^2 + \nor{\tau_y}_{L^2(K)}^2.
\end{align*}
We define the anisotropy indicator as the ratio $r_K = \frac{e_{x,K}}{e_{y,K}}$, and implement a simple refinement scheme following \cite{DPG3}.  Given some anisotropic threshold $\epsilon_r$, if $r_K>\epsilon_r$, then we can conclude that the error in the $x$ direction is large compared to the $y$ direction, and we anisotropically refine the element along the $x$-axis.  Likewise, if $r_K < \frac{1}{\epsilon_r}$, this implies that the opposite is true, and we refine the element anisotropically along the $y$-axis.

%We note that it is possible to compute the discrete system without needing much additional integration.  Recall that if we let $G$ be the symmetric positive-definite Gram matrix representing the inner product $\LRp{v,\delta v}_V$ on $V_h$, we solve for degrees of freedom $c_e$ representing our error representation function $e$.  
%
%For both the graph and robust test norms, we can decompose the inner product that induces the test norm into 
%\[
%\LRp{v,\delta v}_V = \sum_i \LRp{v,\delta v}_{V,x_i} + \LRp{v,\delta v}_{V,{\rm scalar}}
%\]
%such that $\LRp{v,\delta v}_{V,x_i}$ is a seminorm containing the $i$th coordinate component of a vector-valued test term, and $\LRp{v,\delta v}_{V,{\rm scalar}}$ is simply the non-vector portions of the test norm.  For example, if we take the $H^1(\Omega)$ Sobolev norm
%\[
%\LRp{v,\delta v}_V = \LRp{v,\delta v}_{\L} + \LRp{\grad v,\grad \delta v}_{\L}
%\]
%then $\LRp{v,\delta v}_{V,x_i} = \LRp{\pd{v}{x_i},\pd{\delta v}{x_i}}_{\L}$, and $\LRp{v,\delta v}_{V,{\rm scalar}} = \LRp{v,\delta v}_{\L}$.  Each bilinear term $\LRp{v,\delta v}_{V,x_i}$ induces a symmetric positive-semidefinite matrix $G_{x_i}$, such that 
%\[
%c_e^TG_{x_i}c_e = \nor{e}^2_{V,x_i}.
%\]
%By storing $G$ as the sum of $G_{\rm scalar}$ and $G_{x_i}$, we can then cheaply compute the anisotropic error indicators once we have the degrees of freedom corresponding to our error representation function.

### 2013-07-22 docs/Jesse/NavierStokes paper/outline.tex
updating confusion, dissertation, and NS

--- 2012-07-16 docs/Jesse/Proposal/outline.tex
@@
-\documentclass{report}
-
-\usepackage{utproposal}  		% Dissertation package style file.
+%&pdflatex
+\documentclass{elsarticle}
 
 \usepackage{array}
-\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
-\usepackage[utf8]{inputenc}
-\usepackage{listings}
+\usepackage{amsmath,amssymb,amsfonts,amsthm}
 \usepackage{mathtools}
-\usepackage{dsfont}
-\usepackage{pdfpages}
-\usepackage[textsize=footnotesize,color=green]{todonotes}
 \usepackage{algorithm, algorithmic}
-\usepackage{bm}
-\usepackage{tikz}
-\usepackage[normalem]{ulem}
-
 \usepackage{graphicx}
@@
 \usepackage[colorlinks = true, filecolor = red, urlcolor = blue, linkcolor = black]{hyperref}
-\usepackage{pdflscape}
-\usepackage{pifont}
-%\usepackage{fullpage}
+
 \setlength\textwidth{6in}
@@
 
-\newcommand{\circone}{\ding{192}}
-\newcommand{\circtwo}{\ding{193}}
-\newcommand{\circthree}{\ding{194}}
-\newcommand{\circfour}{\ding{195}}
-\newcommand{\circfive}{\ding{196}}
-
 \newcommand{\Reyn}{\rm Re}
@@
 \newcommand{\tabref}[1]{Table~\ref{tab:#1}}
+
+\newtheorem{remark}{Remark}
 
@@
 \newcommand{\LRc}[1]{\left\{ #1 \right\}}
-\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
+\newcommand{\LRb}[1]{\left| #1 \right|}
+
 \newcommand{\Grad} {\ensuremath{\nabla}}
@@
 %%%%%%%%%%%%%%% End def of new commands %%%%%%%%%%%%%%%%%%%
-
-\author{Jesse Chan}
-\address{910 E. 32nd St, Apt.\ 101\\ Austin, Texas 78705}  % Required
-
-\title{A DPG method for compressible flow problems}
-
-\supervisor
-	[Leszek Demkowicz]
-	{Robert Moser}
-
-\committeemembers
-	[Todd Arbogast]
-	[Omar Ghattas]
-	{Venkat Raman}
-
-\previousdegrees{B.A.}
-
-\oneandonehalfspacequote
-
-\topmargin 0.125in
-
-\makeindex
-
 %%%%%%%%%%%%%%% Start of thesis %%%%%%%%%%%%%%%%%%%
@@
 \begin{document}
-%\copyrightpage          % Produces the copyright page.
-%\commcertpage           % Produces the Committee Certification
-\titlepage
+\begin{frontmatter}
 
-\tableofcontents   % Table of Contents will be automatically
-                   % generated and placed here.
+\author{Jesse Chan\corref{cor1}}
+\ead{jchan@ices.utexas.edu}
+\cortext[cor1]{Principal Corresponding Author, Institute for Computational Engineering and Sciences, The University of Texas at Austin}
+\cortext[affil]{Institute for Computational Engineering and Sciences, The University of Texas at Austin}
+\author{Leszek Demkowicz\corref{affil}}
+\ead{leszek@ices.utexas.edu}
+\author{Robert Moser\corref{affil}}
+\ead{rmoser@ices.utexas.edu}
 
-%\listoftables      % List of Tables and List of Figures will be placed
-%\listoffigures     % here, if applicable.
+\title{A DPG method for steady viscous compressible flow}
 
-\chapter{Introduction}
+\begin{abstract}
+The Discontinuous Petrov-Galerkin (DPG) method is a class of novel higher order adaptive finite element methods derived from the minimization of the residual of the variational problem \cite{DPG2}, and has been shown to deliver a method for convection-diffusion that is provably robust in the diffusion parameter \cite{DPGrobustness,DPGrobustness2}.
+In this work, the DPG method is extrapolated to nonlinear systems, and applied to several problems in fluid dynamics whose solutions exhibit boundary layers or singularities in stresses.
+In particular, the effectiveness of DPG as a numerical method for compressible flow is assessed with the application of DPG to two model problems over a range of Mach numbers and laminar Reynolds numbers using automatic adaptivity for higher order elements, beginning with highly under-resolved coarse initial meshes.
+\end{abstract}
 
-\input{proposalIntro}
+\end{frontmatter}
 
-\chapter{Range of problems}
+%\maketitle
 
-\input{problemRange}
+%\tableofcontents
 
-\chapter{Discontinuous Petrov-Galerkin: a minimum residual method for linear problems}
+\input{paperIntro}
 
 \input{DPGtheory}
-
-\chapter{A robust DPG method for convection-diffusion}
-
-\input{DPGrobustness}
-
-\chapter{Proposed work}
+\input{confusionSummary}
 
@@
 \input{NSNotes}
-\input{areaReq}
 
-\bibliographystyle{plain}
-\bibliography{CFD_intro,DPG_old,paper,LitRev,NSNotes}
+\input{Conclusions}
 
-%\chapter{Appendix}
-\appendix
-\input{paper_appendix.tex}
-%\input{hyperbolicDPG.tex}
+%\bibliographystyle{plain}
+\bibliographystyle{unsrt}
+\bibliography{paper,NSNotes,DPGarticles}
 

### 2013-07-22 docs/Jesse/NavierStokes paper/problemRange.tex
updating confusion, dissertation, and NS

--- 2013-05-15 docs/Jesse/Dissertation/problemRange.tex
@@
 \centering
-\includegraphics[scale=.45]{figs/CFD_tree.pdf}
+\includegraphics[scale=.475]{figs/CFD_tree.pdf}
 \caption{A diagram of common CFD problems and their simplifying assumptions.}
@@
 
-In 2D, the classical form of the Navier-Stokes equations involve the fluid density $\rho$, velocity in the $x$ and $y$ directions $u$ and $v$ (or $u_1$ and $u_2$), respectively, temperature $T$, energy per unit mass $e$, and stress and heat flux vectors $\boldsymbol \sigma_i$ and $\vec{q}$.
+In 2D, the classical form of the Navier-Stokes equations involve the fluid density $\rho$, velocity in the $x$ and $y$ directions $u_1$ and $u_2$, respectively, temperature $T$, energy per unit mass $e$, and stress and heat flux vectors $\boldsymbol \sigma_i$ and $\vec{q}$.
 The equations are as follows:
@@
 \begin{align*}
-\pd{\rho}{t} + \div \vecttwo{\rho u }{\rho v} &= 0
+\pd{\rho}{t} + \div \vecttwo{\rho u_1 }{\rho u_2} &= 0
 \end{align*}
@@
 \begin{align*}
-\pd{\rho u_1}{t} + \div \left(\vecttwo{\rho u^2+p }{\rho u v} - \boldsymbol \sigma_{1}\right) &=0\\
-\pd{\rho u_2}{t} + \div \left(\vecttwo{\rho u v}{\rho v^2+p } - \boldsymbol \sigma_{2}\right) &=0
+\pd{\rho u_1}{t} + \div \left(\vecttwo{\rho u_1^2+p }{\rho u_1 u_2} - \boldsymbol \sigma_{1}\right) &=0\\
+\pd{\rho u_2}{t} + \div \left(\vecttwo{\rho u_1 u_2}{\rho u_2^2+p } - \boldsymbol \sigma_{2}\right) &=0
 \end{align*}
@@
 \begin{align*}
-\pd{\rho e}{t} + \div \left(\vecttwo{((\rho e)+p)u}{((\rho e)+p)v} - \boldsymbol \sigma_1 \cdot \boldsymbol u- \boldsymbol \sigma_2 \cdot \boldsymbol u + \vec{q}\right) &=0
+\pd{\rho e}{t} + \div \left(\vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2} - \boldsymbol \sigma_1 \cdot \boldsymbol u- \boldsymbol \sigma_2 \cdot \boldsymbol u + \vec{q}\right) &=0
 \end{align*}
@@
 
-The scope of this dissertation will not deal with these two equations --- the Stokes equations are treated in \cite{stokesDPG}, and the incompressible Navier-Stokes are covered in an upcoming dissertation.
+The scope of this dissertation will not deal with these two equations --- the Stokes equations are treated in \cite{stokesDPG}, and the incompressible Navier-Stokes are covered in the upcoming dissertation of Nathan Roberts.
 
@@
 A feature of the Burgers' equation not present in convection-diffusion is that, due to the presence of the nonlinear term, it can develop shock discontinuities in its solutions in finite time.
-The Burgers' equation has also been used to study the phenomenon of turbulence; however, the Burgers equation does not exhibit the chaotic nature and sensitivity to initial conditions that characterizes turbulence as observed in the full and incompressible Navier-Stokes equations.
+The Burgers' equation has also been used to study the phenomenon of turbulence; however, the Burgers' equation does not exhibit the chaotic nature and sensitivity to initial conditions that characterizes turbulence as observed in the full and incompressible Navier-Stokes equations.
 
 The Burgers' equation is also the simplest nonlinear extension of the linear convection-diffusion equation, and exact solutions can sometimes be found using the method of characteristics.
-In the scope of this dissertation proposal, Burgers shall be used as to test the extension of our numerical method to nonlinear problems.
+In the scope of this dissertation, Burgers shall be used as to test the extension of our numerical method to nonlinear problems.
 
@@
 \centering
-\includegraphics[scale = .22]{figs/convCirc.png}
+\includegraphics[scale = .3]{figs/convCirc.png}
 \caption{Setup for the vortex problem.}
@@
 Formally speaking, the solution to the vortex problem is taken to be the solution to the convection-diffusion equation (with appropriate outflow boundary conditions) as the viscosity tends towards zero, in which case, the solution in the interior would be uniformly zero (this technique is referred to in mathematical literature as the ``vanishing viscosity" method, and is used to define unique solutions in the inviscid limit).
-This motivates the need for \emph{artificial viscosity} methods with which to regularize inviscid solutions.
+This motivates the need for \emph{artificial viscosity} methods with which to regularize inviscid problems.
 The topic is expansive, and we direct the reader towards \cite{Barter} for a more detailed discussion of past and present artificial viscosity methods.

### 2013-07-30 docs/Jesse/Dissertation/Conclusions.tex

The goal of this work has been to explore the behavior of the Discontinuous Petrov-Galerkin (DPG) method as a method for the discretization and solution of convection-dominated diffusion problems, and produce both theory and numerical results using this method applied to model problems in this area.  We begin in Chapter~\secref{chap:intro} by describing convection-diffusion problems in fluid dynamics and the issues faced by naive methods in the convective limit, with particular emphasis on the \textit{robustness} of the method, and give a brief survey of numerical methods tailored for convection-dominated diffusion problems.  In Chapter~\secref{chap:problemRange}, we introduce the range of problems we are interested in addressing.  Specifically, we are interested in the convection-diffusion class of singular perturbation problems in computational fluid dynamics, and discuss the compressible Navier-Stokes equations, as well as the simpler model problems of Burgers' equation and the linear convection-diffusion equation, upon which we develop our numerical method.

In Chapter~\secref{chap:introDPG}, we introduce the DPG method for linear problems.  The concept of problem-dependent optimal test functions is derived through equivalence with the minimization of a specific residual, and discontinuous test functions are introduced in order to localize the determination of such optimal test functions to a single element.  The approximation of such test functions using a high order spectral method is discussed, and conclude the chapter by introducing the ultra-weak variational formulation with which the concept of optimal test functions is paired and its corresponding energy spaces.

In Chapter~\secref{chap:graphNorm}, we show how DPG's locally constructed test space can be interpreted as a non-conforming approximation of a weakly-conforming global test space under the ultra-weak formulation.  Furthermore, the field solutions and trace solutions on the boundary $\Gamma$ are shown to depend \textit{only} upon properties of the non-conforming global test space; thus, when considering approximation error in test functions, resolution of global approximation error (as opposed to local approximation error) can be sufficient to produce a stable method.  Additionally, global properties of test spaces are given under which the ultra-weak formulation delivers the best $L^2$-approximation to the exact solution.  A connection is made to DPG through the graph test norm, which can be viewed as a regularization of the graph seminorm through the addition of an $L^2$ term of magnitude $\delta$. As the regularization parameter $\delta \rightarrow 0$, DPG under this version of the graph test norm is shown to converge to a weakly-conforming approximation to the $L^2$-optimal test space.  Finally, viewing DPG as an approximation to globally optimal test functions allows the construction of test spaces that focus on resolution of global features as opposed to local features.  We illustrate this with the convection-diffusion problem, where we show that it is possible to restore robustness with respect to the diffusion parameter $\epsilon$ by neglecting the resolution of boundary layers on the element-local level and focusing on the resolution of global boundary layers in optimal test spaces.

In Chapter~\secref{chap:robustDPG}, we presented the analysis of a non-canonical test norm and its corresponding DPG energy norm for the convection-diffusion equation in the small-diffusion limit for solutions with strong boundary layers. Additionally, we have introduced a non-standard inflow boundary condition, and have explored the difference between between this and the standard Dirichlet inflow boundary condition. Both a definition and proof of robustness are given, and approximation of test functions is addressed.  Numerical results are presented in order to verify the results derived in this paper. However, at least for our model problem, numerical experiments appear to demonstrate results that are stronger than our proofs indicate, delivering solutions for $u$ and $\sigma$ that are extremely close to their best $L^2$ projections.   Finally, the test norm is modified to address problems with singularities.  A model problem using Laplace's equation is formulated to illustrate the presence of singular solutions to the convection-diffusion equation, and difficulties in control of singularities under the previously developed test norm are demonstrated.  Numerical experiments demonstrate that the new test norm resolves previous issues, and is effective in controlling singularities in solutions of the convection-diffusion equation.

In the final chapter Chapter~\secref{chap:nonlinDPG}, we extend the methodology for linear problems to two model nonlinear problems.  We describe several common methods for the solution of nonlinear equations, and describe the application of the DPG method to each of them.   We demonstrate the effectiveness of DPG for nonlinear problems on a model Burgers problem with a shock solution, and then apply the DPG method to solving two model problems in supersonic/hypersonic compressible flow under different Reynolds numbers.  In particular, we demonstrate for both the flat plate and compression ramp problem in supersonic/hypersonic in compressible flow that the DPG method is able to begin from a highly underresolved meshes (two elements for the Carter plate problem, and 12 elements for the Holden ramp problem), and through automatic adaptivity, is able to resolve physical features of the solution without the aid of artificial diffusivity or shock capturing terms.  We believe this indicates both the robustness of the method on coarse grids and the effectiveness of the DPG error indicator for adaptive refinement.

In conclusion, we have examined carefully the application of the DPG method to linear convection-dominated diffusion problem, where Galerkin test functions are computed automatically based on a choice of basis functions and the variational formulation.  We have introduced a novel variational formulation -- the ``ultra-weak'' variational formulation -- and have analyzed the nature of test functions resulting from a ``canonical'' choice of test norm.  After showing that such test functions display strong boundary layers, we concluded that resolution of the such test functions was infeasible, and developed a version of the DPG method for linear convection-dominated diffusion problems whose behavior does not degenerate as $\epsilon \rightarrow 0$.  The end goal of such an analysis was to present a method which could adaptively solve a heavily convection-dominated diffusion problem despite beginning with a highly under-resolved initial mesh.  We extrapolated such a method to a nonlinear Burgers equation and two model problems in viscous compressible flow and demonstrated its usefulness by using an automatic adaptivity scheme to fully capture features of the flow, starting with a mesh requiring no prior knowledge of the solution or physics of the simulation.

\section{Accomplishments}

In the theoretical scope of this dissertation, I have developed and proven the robustness of a Discontinuous Petrov-Galerkin method for convection-diffusion problems.  In particular, I have introduced an alternative inflow boundary condition and demonstrated its regularizing affect on the adjoint problem, allowing for the use of a stronger test norm.  Additionally, I have developed theory detailing the global nature of the DPG test space, and have shown that, for a specific series of test norms, the global DPG test space converges to a weakly-conforming approximation of the global test space under which the ultra-weak variational formulation yields the $L^2$-best approximation.  Finally, I have extended the DPG framework to nonlinear problems, demonstrating the equivalence of the DPG method to a Gauss-Newton minimization scheme for the nonlinear residual.

In the numerical and computational scope of this dissertation, I have confirmed numerically the robustness of the DPG method for convection-diffusion problems in the convective limit under arbitrary high-order adaptive meshes.  I have implemented an anisotropic refinement scheme to more effectively capture lower-dimensional behavior of solutions of convection-diffusion problems, such as boundary layers.  Finally, I have contributed to the development of the parallel $hp$-adaptive DPG codebase Camellia\cite{Camellia}, under which the results in this dissertation were produced.

Finally, this dissertations includes the application of the DPG method to several model convection-diffusion problems.  Convergence of the method is demonstrated under an exact solution to the scalar convection-diffusion problem, and the method is extrapolated to a nonlinear viscous Burgers' equation.  Finally, the DPG method is extrapolated to systems of equations and used to solve the flat plate and compression ramp problems in supersonic/hypersonic compressible flow.

\section{Future work}

As is the case with any research, much work remains to be done.  We outline here several areas of work which we hope to pursue in the future.
\begin{itemize}
\item \textbf{Nonlinear DPG --} as described in Section~\secref{sec:nonlinDPG}, there is a natural Hessian-based version of the DPG method which provides a second-order approximation to the nonlinear equation instead of the first-order one afforded by Newton-Raphson linearization.  Unfortunately, under this Hessian-based version of DPG, the stiffness matrix may no longer be positive definite, which can lead to non-descent search directions.  We hope to avoid such issues through the use of Newton-CG methods\cite{Nocedal2006NO}, which avoid negative search directions by terminating the CG iteration in the presence of negative curvature.  
\item \textbf{Navier-Stokes --} We have chosen the classical variables in which to cast the compressible Navier-Stokes equations; however, investigation of alternative sets of variables may have merit, as different choices of variables yield differing linearizations with their own advantages (for example, all derivatives in time are linear with respect to the momentum variables, and the entropy variables of Hughes both symmetrize the Navier-Stokes equations and yield solutions obeying second law of thermodynamics for standard $H^1$ formulations \cite{Hughes1986223}).

We also hope to investigate artificial viscosity methods as regularization for problems in viscous compressible flow.  We present an analysis of the 1D Burgers' equation demonstrating that the exact solutions under Newton linearization contain large oscillations.  While these oscillations are not the result of the stability of the spatial discretization, their presence can cause density and temperature to become non-physically negative, which can stall the convergence of the nonlinear solver.  We hope to investigate artificial viscosity not as a stabilization mechanism of the discrete spatial discretization, but as a regularization of the strong problem with which to suppress the presence of large oscillations in the linearized solution.

Finally, though the method is inf-sup stable for arbitrary meshes, most of our experiments have focused on meshes of uniform $p$.  We hope to implement a true $hp$-adaptive DPG method for the compressible Navier-Stokes equations in the future.  
\item \textbf{Alternative discretizations --} Recent works (see \cite{DahmenVariationalStabilization, broersenStevenson, primalDPG, H1DPG}) have applied the same minimum residual methodology behind DPG to alternative discretizations, as well as the use of \textit{continuous} test functions.\footnote{We note that the use of continuous test functions does not imply the computation of such test functions over the entire mesh; it is shown that the minimum residual method can be formulated instead as a saddle point problem, which is equivalent to computing optimal test functions.  See \cite{DahmenVariationalStabilization, H1DPG} for more details.}  We hope to investigate the behavior of the minimum residual method under both continuous test functions and different variational formulations. 
\item \textbf{Alternative architectures --} For an efficient implementation of DPG, massively parallel low memory architectures are required.  In this work, we have focused on an MPI implementation of DPG.  However, future access to extremely large MPI-based clusters may be limited to those who can afford the cost of petascale -- namely, government-sponsored projects and large engineering companies.  We hope to experiment with the GPU implementation of DPG as a lower-cost, highly parallel HPC alternative.  
\end{itemize}

### 2013-07-30 docs/Jesse/Dissertation/DPGrobustness.tex

--- 2013-04-29 docs/Jesse/HeuerPaper/paperForCAMWA.tex
@@
-%&pdflatex
-\documentclass[11pt,onecolumn]{scrartcl}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
-\usepackage[top=2cm,bottom=3cm,left=2.5cm,right=2cm]{geometry}
-\usepackage{amssymb}
-\usepackage{listings}
-\usepackage{array}
-\usepackage{mathtools}
-\usepackage{dsfont}
-\usepackage{graphicx}
-\usepackage{pdfpages}
-\usepackage[textsize=footnotesize,color=green]{todonotes}
-\usepackage{algorithm, algorithmic}
-\usepackage{array}
-\usepackage{bm}
-\usepackage{tikz}
-\usepackage{subfigure}
-\usepackage[normalem]{ulem}
-\usepackage{epstopdf}
-
-\newcommand{\bs}[1]{\boldsymbol{#1}}
-\DeclareMathOperator{\diag}{diag}
-
-\newcommand{\equaldef}{\stackrel{\mathrm{def}}{=}}
-
-\newcommand{\tablab}[1]{\label{tab:#1}}
-\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
-
-\newcommand{\theolab}[1]{\label{theo:#1}}
-\newcommand{\theoref}[1]{\ref{theo:#1}}
-\newcommand{\eqnlab}[1]{\label{eq:#1}}
-\newcommand{\eqnref}[1]{\eqref{eq:#1}}
-\newcommand{\seclab}[1]{\label{sec:#1}}
-\newcommand{\secref}[1]{\ref{sec:#1}}
-\newcommand{\lemlab}[1]{\label{lem:#1}}
-\newcommand{\lemref}[1]{\ref{lem:#1}}
-
-\newcommand{\mb}[1]{\mathbf{#1}}
-\newcommand{\mbb}[1]{\mathbb{#1}}
-\newcommand{\mc}[1]{\mathcal{#1}}
-\newcommand{\nor}[1]{\left\| #1 \right\|}
-\newcommand{\snor}[1]{\left| #1 \right|}
-\newcommand{\LRp}[1]{\left( #1 \right)}
-\newcommand{\LRs}[1]{\left[ #1 \right]}
-\newcommand{\LRa}[1]{\left\langle #1 \right\rangle}
-\newcommand{\LRc}[1]{\left\{ #1 \right\}}
-\newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
-\newcommand{\Grad} {\ensuremath{\nabla}}
-\newcommand{\Div} {\ensuremath{\nabla\cdot}}
-\newcommand{\Nel} {\ensuremath{{N^\text{el}}}}
-\newcommand{\jump}[1] {\ensuremath{\LRs{\![#1]\!}}}
-\newcommand{\uh}{\widehat{u}}
-\newcommand{\fnh}{\widehat{f}_n}
-\renewcommand{\L}{L^2\LRp{\Omega}}
-\newcommand{\pO}{\partial\Omega}
-\newcommand{\Gh}{\Gamma_h}
-\newcommand{\Gm}{\Gamma_{-}}
-\newcommand{\Gp}{\Gamma_{+}}
-\newcommand{\Go}{\Gamma_0}
-\newcommand{\Oh}{\Omega_h}
-
-\newcommand{\eval}[2][\right]{\relax
-  \ifx#1\right\relax \left.\fi#2#1\rvert}
-
-\def\etal{{\it et al.~}}
-
-\newcommand{\vect}[1]{\ensuremath\boldsymbol{#1}}
-\newcommand{\tensor}[1]{\underline{\vect{#1}}}
-\newcommand{\del}{\Delta}
-\newcommand{\grad}{\nabla}
-\newcommand{\curl}{\grad \times}
-\renewcommand{\div}{\grad \cdot}
-\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
-\newcommand{\eip}[1]{a\left( #1 \right)}
-\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
-\newcommand{\pdd}[2]{\frac{\partial^2#1}{\partial#2^2}}
-
-\newcommand{\circone}{\ding{192}}
-\newcommand{\circtwo}{\ding{193}}
-\newcommand{\circthree}{\ding{194}}
-\newcommand{\circfour}{\ding{195}}
-\newcommand{\circfive}{\ding{196}}
-
-\def\arr#1#2#3#4{\left[
-\begin{array}{cc}
-#1 & #2\\
-#3 & #4\\
-\end{array}
-\right]}
-\def\vecttwo#1#2{\left[
-\begin{array}{c}
-#1\\
-#2\\
-\end{array}
-\right]}
-\def\vectthree#1#2#3{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-\end{array}
-\right]}
-\def\vectfour#1#2#3#4{\left[
-\begin{array}{c}
-#1\\
-#2\\
-#3\\
-#4\\
-\end{array}
-\right]}
-
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-
-\newcommand{\G} {\Gamma}
-\newcommand{\Gin} {\Gamma_{in}}
-\newcommand{\Gout} {\Gamma_{out}}
-
-\author{Jesse Chan\textsuperscript{a}, Norbert Heuer\textsuperscript{b}, Tan Bui-Thanh\textsuperscript{a}, and Leszek Demkowicz\textsuperscript{a}}
-
-%\title{$\epsilon$-explicit analysis of DPG for convection-dominated diffusion}
-\title{A robust DPG method for convection-dominated diffusion problems II: adjoint boundary conditions and mesh-dependent test norms.}
-\date{}
-\begin{document}
-
-%\tableofcontents
-\maketitle
-\begin{center}
-\textsuperscript{a} Institute for Computational Engineering and Sciences, \\University of Texas at Austin, \\Austin, TX 78712, USA\\
-\end{center}
-
-\begin{center}
-\textsuperscript{b} Facultad de Matem\'aticas, \\Pontificia Universidad Cat\'olica de Chile,\\
-Avenida Vicu\~na Mackenna 4860, Santiago, Chile
-\end{center}
-
-\section{Introduction}
-
-\subsection{Singular perturbation problems and robustness}
-
-The finite element/Galerkin method has been widely utilized in engineering to solve partial differential equations governing the behavior of physical phenomena in engineering problems.
-The method relates the solution of a partial differential equation (PDE) to the solution of a corresponding variational problem.
-The finite element method itself provides several advantages --- a framework for systematic mathematical analysis of the behavior of the method, weaker regularity constraints on the solution than implied by the strong form of the equations, and applicability to very general physical domains and geometries.
-
-Historically, the Galerkin method has been very successfully applied to a broad range of problems in solid mechanics, for which the variational problems resulting from the PDE are symmetric and coercive (positive-definite).
-It is well known that the finite element method produces optimal or near-optimal results for such problems, with the finite element solution matching or coming close to the best approximation of the solution in the finite element space.
-However, standard Bubnov-Galerkin methods tend to perform poorly for the class of PDEs known as singular perturbation problems.
-These problems are often characterized by a parameter that may be either very small or very large in the context of physical problems.
-An additional complication of singular perturbation problems is that very often, in the limiting case of the parameter blowing up or decreasing to zero, the PDE itself will change types (e.g.\ from elliptic to hyperbolic).
-
-\subsubsection{Convection-diffusion}
-
-A canonical example of a singularly perturbed problem is the convection-diffusion equation.
-%The equation models the convection of fluid along a direction $\beta$ with a viscous dissipation of magnitude $\epsilon$.
-In the limit as $\epsilon\rightarrow 0$, the convection-diffusion equation transforms from a parabolic to a hyperbolic partial differential equation.
-In 1D, the convection-diffusion equation is
-\begin{align*}
-\beta u'-\epsilon u'' &= f.
-\end{align*}
-The equation represents the change in the concentration $u$ of a quantity in a given medium, taking into account both convective and diffusive effects.
-$\beta$ represents the speed of convection, while the singular perturbation parameter $\epsilon$ represents the diffusivity of the medium.
-In the limit of an inviscid medium as $\epsilon\rightarrow 0$, the equation changes types, from elliptic to hyperbolic, and from second order to first order.
-For Dirichlet boundary conditions $u(0)=u_0$ and $u(1)= u_1$, the solution can develop sharp boundary layers of width $\epsilon$ near the outflow.
-
-%The finite element method has performed notoriously poorly for this example, as well as for many other singularly perturbed problems.
-This poor performance is captured by the error bound for the finite element method applied to the convection-diffusion equation - under the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}
-The poor performance of the finite element method for this problem is reflected in the bound on the error in the finite element solution --- under the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}:
-\[
-\|u-u_h\|_\epsilon \leq C \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
-\]
-for $\|u\|_\epsilon^2 \coloneqq \|u\|_{L^2}^2 + \epsilon \|u'\|_{L^2}^2$, with $C$ independent of $\epsilon$. An alternative formulation of the above bound is 
-\[
-\|u-u_h\|_{H^1(0,1)} \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
-\]
-where $C(\epsilon)$ grows as $\epsilon\rightarrow 0$.
-The dependence of the constant $C$ on $\epsilon$ is referred to as a \textit{loss of robustness} --- as the singular perturbation parameter $\epsilon$ decreases, our finite element error is bounded more and more loosely by the best approximation error.
-As a consequence, the finite element solution can diverge significantly from the best finite element approximation of the solution for very small values of $\epsilon$.
-For example, on a coarse mesh, and for small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation with a boundary layer develops spurious oscillations everywhere in the domain, even where the best approximation error is small.
-These oscillations grow in magnitude as $\epsilon \rightarrow 0$, eventually polluting the entire solution.
-
-%, allowing for more and more error in the finite element solution for as $\epsilon$ shrinks. 
-%Intuitively, a non-robust method will perform increasingly worse as $\epsilon$ decreases.
-
-\subsubsection{Wave propagation}
-
-Another example of a singular perturbation problem which experiences loss of robustness is high frequency wave propagation, in which the singular perturbation parameter is the wavenumber $k$, where $k\rightarrow \infty$.
-The loss of robustness in this case manifests as ``pollution" error, a phenomenon in which the finite element solution degrades over many wavelengths for high wavenumbers (commonly manifesting as a phase error between the FE solution and the exact solution).
-
-\subsubsection{Stabilization terms}
-
-Traditionally, instability/loss of robustness has been dealt with using residual-based stabilization techniques.
-Given some variational form, the problem is modified by adding to the bilinear form the strong form of the residual, weighted by a test function and scaled by a stabilization constant $\tau$.
-The most well-known example of this technique is the streamline-upwind Petrov-Galerkin (SUPG) method, which is a stabilized method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.
-In the 1D case, SUPG stabilization not only removes the spurious oscillations from the finite element solution of the convection-diffusion equation, but delivers the best finite element approximation in the $H^1$ norm.
-An important difference between residual-based stabilization techniques and other stabilizations is the idea of \textit{consistency} --- by adding stabilization terms based on the residual, the exact solution still satisfies the same variational problem (i.e.\ Galerkin orthogonality still holds).\footnote{Contrast this to an artificial diffusion method, where a specific amount of additional viscosity is added based on the magnitude of the convection and diffusion parameters.
-The exact solution to the original equation no longer satisfies the new stabilized formulation.}
-
-The addition of residual-based stabilization terms has also been interpreted as a modification of the test functions --- in other words, stabilization can be achieved by changing the test space for a given problem.
-We approach the idea of stabilization through the construction of \textit{optimal test functions} to achieve optimal approximation properties.
-
-%\textcolor{red}{add bit about SUPG/residual-based stabilization terms and test functions}
-
-\subsection{Discontinuous Petrov-Galerkin methods with optimal test functions}
-\seclab{optimalTest} Petrov-Galerkin methods, in which the test space
-differs from the trial space, have been explored for over 30 years,
-beginning with the approximate symmetrization method of Barrett and
-Morton~\cite{BARRETT01101981}. The idea was continued with the SUPG
-method of Hughes, and the characteristic Petrov-Galerkin approach of
-Demkowicz and Oden~\cite{Demkowicz1986188}, which introduced the
-idea of tailoring the test space to change the norm in which a finite
-element method would converge.
-
-The idea of optimal test functions was introduced by Demkowicz and
-Gopalakrishnan in \cite{DPG2}.  Conceptually, these optimal test
-functions are the natural result of the minimization of a residual
-corresponding to the operator form of a variational equation. The
-connection between stabilization and least squares/minimum residual
-methods has been observed previously \cite{GLS}. However, the method in \cite{DPG2} distinguishes itself
-by measuring the residual of the natural \textit{operator form of the equation}, which is posed in the dual space, and measured with the dual norm, as we now discuss.
-
-Throughout the paper, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U'$ and $V'$ as the respective topological dual spaces.
-Let $U_h \subset U$ and $V_h\subset V$ be finite dimensional subsets.
-We are interested in the following problem
-\begin{equation}
-\eqnlab{variationEq}
-\left\{
-  \begin{array}{l}
-    \text{Given } l \in V', \text{ find } u_h \in U_h  \text{ such that} \\ 
-    b(u_h,v_h) = l(v_h), \quad \forall v_h\in V_h,
-  \end{array}
-  \right.
-\end{equation}
-where $b\LRp{\cdot,\cdot}: U \times V \to \mbb{R}$ is a continuous
-bilinear form.  $U_h$ is chosen to be some trial space of approximating functions, but $V_h$ is as of yet unspecified.
-
-Throughout the paper, we suppose the variational
-problem \eqnref{variationEq} to be well-posed. In that case, we can
-identify a unique operator $B:U\rightarrow V'$ such that
-\[
-\langle Bu,v\rangle_V \coloneqq b(u,v), \quad u\in U, v\in V
-\]
-with $\LRa{\cdot, \cdot}_V$ denoting the duality pairing between $V'$ and $V$, to obtain the operator form of the continuous variational problem
-\begin{equation}
-\eqnlab{dualEq}
-Bu = l \quad \text{in } V'.
-\end{equation}
-In other words, we can represent the continuous form of our variational equation
-\eqnref{variationEq} equivalently as the operator equation \eqnref{dualEq} with values in the
-dual space $V'$.  This motivates us to consider the conditions under which the solution to \eqnref{variationEq} is the solution to the minimum residual problem in $V'$ 
-\[
-u_h = \underset{u_h\in U_h}{\arg\min}\, J(u_h),
-\]
-where $J(w)$ is defined for $w\in U$ as 
-\[
-J(w) = \frac{1}{2}\|Bw-l\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(w,v)-l(v)|^2}{\nor{v}_V^2}.
-\]
-For convenience in writing, we will abuse the notation $\sup_{v \in V}$ to denote $\sup_{v\in V\setminus\{0\}}$ for the remainder of the paper.
-
-Let us define $R_V: V \to V'$ as the Riesz map, which identifies
-elements of $V$ with elements of $V'$ by 
-\[
-\langle R_V v,\delta
-v\rangle_V \coloneqq(v, \delta v)_V, \quad \forall \delta v \in V.
-\]
-Here, $(\cdot, \cdot)_V$ denotes the
-inner product in $V$. As $R_V$ and its inverse, $R_V^{-1}$, are both
-isometries, e.g.\ $\|f\|_{V'} = \|R_V^{-1} f\|_V, \forall f \in V'$, we
-have
-\begin{equation}
-\eqnlab{minimization}
-\min_{u_h\in U_h} J(u_h) = \frac{1}{2}\left\|Bu_h-l\right\|_{V'}^2 =  \frac{1}{2}\left\|R_V^{-1}(Bu_h-l)\right\|_V^2.
-\end{equation}
-The first order optimality condition for \eqnref{minimization} requires
-the G\^ateaux derivative to be zero in all directions $\delta u \in
-U_h$, i\.e\.,
-\begin{align*}
-\left(R_V^{-1}(Bu_h-l),R_V^{-1}B\delta u\right)_V = 0, \quad \forall \delta u \in U. 
-\end{align*}
-We define, for a given $\delta u \in U$, the corresponding {\em optimal test function} $v_{\delta u}$
-\begin{equation}
-\eqnlab{optv}
-v_{\delta u} \coloneqq R_V^{-1}B\delta u \quad  \text{in } V.
-\end{equation} 
-The optimality condition then becomes
-\[
- \langle Bu_h-l, v_{\delta u}\rangle_V = 0, \quad \forall \delta u \in U
-\]
-which is exactly the standard variational equation in
- \eqnref{variationEq} with $v_{\delta u}$ as the test functions.
-We can define the optimal test space $V_{\rm opt} \coloneqq \{v_{\delta u} \text{ s.t.
-} \delta u\in U\}$.
-Thus, the solution of the variational problem \eqnref{variationEq} with test space $V_h = V_{\rm opt}$ minimizes the residual in the dual norm $\nor{Bu_h-l}_{V'}$.
-This is the key idea behind the concept of optimal test functions.
-
-Since $U_h \subset U$ is spanned by a finite number of basis functions $\LRc{\varphi_i}_{i=1}^N$, \eqnref{optv} allows us to compute (for each basis function) a corresponding optimal test function $v_{\varphi_i}$.
-The collection $\LRc{v_{\varphi_i}}_{i = 1}^N$ of optimal test functions then forms a basis for the optimal test space.
-In order to express optimal test functions defined in \eqnref{optv} in a more familiar form, we take  $\delta u = \varphi$, a generic basis function in $U_h$, and rewrite \eqnref{optv} as
-\[
-R_Vv_{\varphi} = B\varphi, \quad \text{in } V',
-\]
-which is, by definition, equivalent to
-\[
-\LRp{v_\varphi,\delta v}_V = \LRa{R_Vv_\varphi,\delta v}_{V}=
-\LRa{B\varphi, \delta v}_V = b\LRp{\varphi,\delta v}, \quad
-\forall \delta v \in V.
-\]
-%% Now, let us define the \textit{trial-to-test} operator $T =
-%% R_V^{-1}B$, which, by \eqnref{optv}, maps a trial function $\delta u$
-%% to its corresponding \textit{optimal} test function $v = T\delta u$.
-%% On the other hand,
-As a result, optimal test functions can be determined by solving the auxiliary
-variational problem
-\begin{equation}
-\eqnlab{optvVar}
-\left(v_\varphi,\delta v\right)_V = b(\varphi,\delta v), \quad \forall
-\delta v \in V.
-\end{equation}
-However, in general, for standard $H^1$ and $H({\rm div})$-conforming finite element methods, test functions are continuous over the entire domain, and hence solving variational problem \eqnref{optvVar} for each optimal test function requires a global operation over the entire mesh, rendering the method impractical.
-A breakthrough came through the development of discontinous Galerkin (DG) methods, for which basis functions are discontinuous over elements.
-In particular, the use of discontinuous test functions $\delta v$ and a \textit{localizable} norm $\nor{\cdot}_V$\footnote{A localizable norm $\nor{v}_{V(\Oh)}$ can be written in the form
-$$\nor{v}_{V(\Oh)}^2 = \sum_{K\in\Oh} \nor{v}_{V(K)}^2,$$ where $\nor{v}_{V(K)}$ is a norm over the element $K$.} reduces the problem of determining global optimal test functions in \eqnref{optvVar} to local problems that can be solved in an element-by-element fashion.
-
-We note that solving \eqnref{optvVar} on each element exactly is infeasible since it amounts to inverting the Riesz map $R_V$ exactly.
-Instead, optimal test functions are approximated using the standard Bubnov-Galerkin method on an ``enriched" subspace $\tilde{V} \subset V$ such that $\dim(\tilde{V}) > \dim(U_h)$ elementwise \cite{DPG1, DPG2}.
-In this paper, we assume the error in approximating the optimal test functions is negligible, and refer to the work in \cite{practicalDPG} for estimating the effects of approximation error on the performance of DPG.
-
-It is now well known that the DPG method delivers the best approximation error in the ``energy norm" --- that is \cite{Bui-ThanhDemkowiczGhattas11a, DPG2,DPG4} 
-\begin{equation}
-\eqnlab{optimalError}
-\nor{u-u_h}_{U,E} = \inf_{w\in U_h} \nor{u-w}_{U,E},
-\end{equation}
-where the energy norm $\|\cdot \|_{U,E}$ is defined for a function $\varphi \in U$ as
-\begin{equation}
-\eqnlab{energyNorm} \|\varphi\|_{U,E} \coloneqq \sup_{v\in V}
-\frac{b(\varphi,v)}{\|v\|_V} = \sup_{\nor{v}_V = 1} b(\varphi,v) =
-\sup_{\nor{v}_V = 1} \LRa{B\varphi,v}_V = \nor{B\varphi}_{V'} =
-\nor{v_\varphi}_V,
-\end{equation}
-where the last equality holds due to the isometry of the Riesz map
-$R_V$ (or directly from \eqnref{optvVar} by taking the supremum). An
-additional consequence of adopting such an energy norm is that,
-without knowing the exact solution, the energy error $\|u-u_h\|_{U,E}  = \nor{Bu - Bu_h}_{V'} = \nor{R_V^{-1}\LRp{l-Bu_h}}_{V}$ can
-be determined by computing the \textit{error representation function} $e \coloneqq R_V^{-1}\LRp{l-Bu_h}$ through
-\[
-\left(e,\delta v\right)_V = b(u-u_h,\delta v) = l\LRp{\delta v} - b(u_h,\delta v)
-\]
-and measuring its norm $\|e\|_V$.
-This is simply a consequence of the least-squares nature of DPG; the energy error is simply the norm of the residual in $V'$.
-Under the assumption of a localizable norm on $V$, we can compute the squared norm over the entire domain $\nor{e}_{V(\Oh)}^2$ as the sum of individual element contributions $\sum_{K\in \Oh} \nor{e}_{V(K)}^2$.
-We define $e_K^2 \coloneqq \nor{e}_{V(K)}^2$ as a local error indicator with which we can drive adaptive mesh refinement.
-
-Practically speaking, this implies that the DPG method is discretely stable on any mesh.
-In particular, DPG is unconditionally stable for higher order adaptive meshes, where discrete stability is often an issue.
-
-\subsection{Duality between trial and test norms (energy norm pairings)}
-%\subsection{Abstract energy norm pairings}
-\seclab{energyPair}
-A clear property of the energy norm defined by \eqnref{energyNorm} is that the trial norm $\nor{\cdot}_{U,E}$ is induced by a given test norm.
-However, the reverse relationship holds as well; for any trial norm, the test norm that induces such a norm is recoverable through duality.
-We have a result, Lemma 2.5 in \cite{Bui-ThanhDemkowiczGhattas11a}: assuming, for simplicity, that the bilinear form $b(u,v)$ is definite\footnote{By definite, we mean that \begin{align*}b(u,v) &= 0, \forall v\in V \Rightarrow u = 0\\ b(u,v)&=0, \forall u\in U \Rightarrow v = 0,\end{align*}  which imply injectivity of the bilinear operator $B$ and its transpose $B'$, defined such that $\LRa{Bu,v} = \LRa{u,B'v}$.
-These conditions imply solvability of the variational problem.}, given any norm $\nor{\cdot}_{U}$ on the trial space $U$, for $\varphi \in U$, we can represent $\nor{\varphi}_{U}$ via
-\[
-\nor{\varphi}_{U} = \sup_{v \in V}\frac{b\LRp{w,v}}{\nor{v}_{V,U}}.
-\]
-where $\nor{v}_{V,U}$ is defined through
-\[
-\nor{v}_{V,U} = \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U}}.
-\]
-%In other words, the norm $\nor{\cdot}_V$ in $V$ can be recovered using the energy norm $\nor{\cdot}_{U,E}$ in $U$, and vice versa.
-
-In particular, given two arbitrary norms $\nor{\cdot}_{U,1}$ and $\nor{\cdot}_{U,2}$ in $U$
-such that $\nor{\cdot}_{U,1} \le c \nor{\cdot}_{U,2}$ for some constant
-$c$, they generate two norms $\nor{\cdot}_{V,U,1}$ and
-$\nor{\cdot}_{V,U,2}$ in $V$ defined by
-\[
-\nor{v}_{V,U,1} \coloneqq \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U,1}}, \quad
-\text{and }\nor{v}_{V,U,2} \coloneqq \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U,2}},
-\]
-such that $\nor{\cdot}_{V,U,1}$ and $\nor{\cdot}_{V,U,2}$ induce
-$\nor{\cdot}_{U,1}$ and $\nor{\cdot}_{U,2}$ as energy
-norms in $U$, respectively. That is,
-\[
-\|\varphi\|_{U,1} = \sup_{v\in V}
-\frac{b(\varphi,v)}{\|v\|_{V,U,1}}, \quad \text{and }\|\varphi\|_{U,2} = \sup_{v\in V}
-\frac{b(\varphi,v)}{\|v\|_{V,U,2}}.
-\]
-
-A question that remains to be addressed is to establish the relationship
-between $\nor{\cdot}_{V,U,1}$ and $\nor{\cdot}_{V,U,2}$, given that
-$\nor{\cdot}_{U,1} \le c \nor{\cdot}_{U,2}$. But this is
-straightforward since we have
-\begin{align*}
- \| v \|_{V,U,2} = \sup_{u \in U} \frac{b\left(w,v\right)}{\left\|
-  w \right\|_{U,2}} \le c\sup_{w \in U} \frac{b\left(w,v\right)}{\left\| w
-  \right\|_{U,1}} = c\| v \|_{V,U,1}.
-\end{align*}
-Consequently, a stronger energy norm in $U$ will generate a weaker
-norm in $V$ and vice versa. In other words, to show that an
-energy norm $\nor{\cdot}_{U,1}$ is weaker than another energy norm
-$\nor{\cdot}_{U,2}$ in $U$, one simply needs to show the reverse inequality on the
-corresponding norms in $V$, that is, $\nor{\cdot}_{V,U,1}$ is stronger
-than $\nor{\cdot}_{V,U,2}$.
-
-%From now on, unless otherwise stated, we will refer to  $\nor{\cdot}_{V,U,1}$, $\nor{\cdot}_{V,U,2}$, and $\nor{\cdot}_{V}$ as the test norms which induce $\nor{\cdot}_{U,1}$, $\nor{\cdot}_{U,2}$, and $\nor{\cdot}_{U,E}$ and vice versa, in the sense discussed above.
-From now on, unless otherwise stated, we will refer to $\nor{\cdot}_{V,U}$ as the test norm that induces a given norm $\nor{\cdot}_U$.
-Likewise, we will refer $\nor{\cdot}_{U,V}$ as the trial norm induced by a given test norm $\nor{\cdot}_V$.
-In this paper, for simplicity of exposition, we shall call a pair of norms in $U$ and $V$ that induce each other as an {\em energy norm pairing}.
-
-\subsection{Discontinuous Petrov-Galerkin methods with the ultra-weak formulation}
-\seclab{abstractUweak}
-
-The naming of the discontinuous Petrov-Galerkin method refers to the fact that the method is a Petrov-Galerkin method, and that the test functions are specified to be discontinuous across element boundaries.
-There is no specification of the regularity of the trial space, and we stress that the idea of DPG is not inherently tied to a single variational formulation \cite{Bui-ThanhDemkowiczGhattas11a}.
-Additionally, Cohen, Dahmen and Welper simultaneously extend the minimum residual concept behind DPG to general variational settings and avoid the use of discontinuous test functions by formulating the minimum residual method as a saddle-point problem \cite{DahmenVariationalStabilization}.
-
-In most of the DPG literature, however, the discontinuous Petrov-Galerkin method refers to the combination of the concept of locally computable optimal test functions in Section \secref{optimalTest} with the so-called ``ultra-weak formulation" \cite{DPG1,DPG2,DPG3,DPG4,DPGElas,DBLP:journals/procedia/NiemiCC11}.
-Unlike the previous two sections in which we studied the general equation \eqnref{variationEq} given by abstract bilinear and linear forms, we now consider a concrete instance of \eqnref{variationEq} resulting from an ultra-weak formulation for an abstract first-order system of PDEs $Au = f$.
-Additionally, from this section onwards, we will refer to DPG as the pairing of the ultra-weak variational formulation with the concept of locally computable optimal test functions.
-
-We begin by partitioning the domain of interest $\Omega$ into $\Nel$ non-overlapping elements $K_j, j = 1,\hdots,\Nel$ such that $\Oh = \cup_{j=1}^\Nel K_j$ and $\overline{\Omega} = \overline{\Omega}_h$.
-Here, $h$ is defined as $h= \max_{j\in \LRc{1,\hdots,\Nel}}\text{diam}\LRp{K_j}$.
-We denote the mesh ``skeleton" by $\Gh = \cup_{j=1}^\Nel \partial K_j$; the set of all faces/edges $e$, each of which comes with a normal vector ${n}_e$.
-The internal skeleton is then defined as $\Gamma^0_h = \Gh \setminus \partial \Omega$.
-If a face/edge $e \in \Gh$ is the intersection of $\partial K_i$ and $\partial K_j$, $i \ne j$, we define the following jumps:
-\[
-\jump{v} = \text{sgn} \LRp{{n}^-}v^- + \text{sgn} \LRp{{n}^+}v^+, \quad
-\jump{\tau \cdot n} = {n}^-\cdot \tau^- + {n}^+\cdot\tau^+,
-\]
-where
-\[
-\text{sgn}\LRp{{n}^{\pm}} =
-\left\{
-\begin{array}{ll}
-1 & \text{if } {n}^{\pm} = {n}_e \\
--1 & \text{if } {n}^\pm = -{n}_e
-\end{array}
-\right..
-\]
-For $e$ belonging to the domain boundary $\partial \Omega$, we define
-\[
-\jump{v} = v, \quad
-\jump{\tau \cdot n} = {n}_e\cdot \tau.
-\]
-Note that we allow arbitrariness in assigning ``-'' and ``+'' quantities to the adjacent elements $K_i$ and $K_j$.
-%For the rest of the paper, we will use the same notation for both a function and its trace (if it is well-defined) when there is no ambiguity.
-
-The ultra-weak formulation for $Au = f$ on $\Oh$, ignoring boundary
-conditions for now, reads
-\begin{equation}
-\eqnlab{uweak}
-b\left(\left(u, \widehat{u}\right),v\right) \coloneqq \langle \widehat{u}, \jump{v}
-\rangle_{\Gh} - (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh},
-\end{equation}
-where we have denoted $\LRa{\cdot,\cdot}_{\Gh}$ as the duality
-pairing on $\Gh$, $\LRp{\cdot,\cdot}_{\Oh}$ the $L^2$-inner
-product over $\Oh$, and $A_h^*$ the formal adjoint resulting from
-element-wise integration by parts.  Occasionally, for simplicity in
-writing, we will ignore the subscripts in the duality pairing and
-$L^2$-inner product if they are $\Gh$ and $\Oh$. Both the
-inner product and formal adjoint are understood to be taken
-element-wise. Using the ultra-weak formulation, the regularity
-requirement on solution variable $u$ is relaxed, that is, $u$ is now
-square integrable for the ultra-weak formulation \eqnref{uweak} to be
-meaningful, instead of being (weakly) differentiable.  The trade-off
-is that $u$ does not admit a trace on $\Gh$ even though it did
-originally. Consequently, we need to introduce an additional new
-``trace'' variable $\widehat{u}$ in \eqnref{uweak}, that is defined only on
-$\Gh$.
-
-The energy setting is now clear; namely,
-\[
-u\in L^2\LRp{\Oh} \equiv L^2(\Omega), \quad v\in V=D(A^*_h), \quad
-\widehat{u}\in \gamma(D(A)),
-\]
-where $D(A_h^*)$ denotes the broken graph space corresponding to $A_h^*$,
-and $\gamma(D(A))$ the trace space (assumed to exist) of the graph space of
-operator $A$.
-The first discussion of the well-posedness of DPG with the ultra-weak formulation can be found in \cite{analysisDPG}, where the proof is presented for the Poisson and convection-diffusion equations.
-A more comprehensive discussion of the abstract setting for DPG with the ultra-weak formulation using the graph space, as well as a more general proof of well-posedness, can be consulted in \cite{Bui-ThanhDemkowiczGhattas11b}.
-
-%\subsection{Optimal and quasi-optimal test norms}
-\subsection{A canonical energy norm pairing for ultra-weak formulation}
-
-From the discussion in Section~\secref{energyPair} of energy norm and test norm pairings, we know that specifying either a test norm or trial norm is sufficient to define an energy pairing.
-%In this section, we derive and discuss two important energy norm pairings, the first of which begins by specifying the canonical norm in $U$ and inducing a test norm on $V$.
-The second pairing begins instead by specifying the canonical norm on $V$ under the ultra-weak formulation \eqnref{uweak} and inducing an energy norm on the trial space $U$.
-In this section, we derive and discuss an important energy norm pairing which specifies the canonical norm in $U$ and induces a test norm on $V$.
-%The second pairing begins instead by specifying the canonical norm on $V$ under the ultra-weak formulation \eqnref{uweak} and inducing an energy norm on the trial space $U$.
-
-We begin first with the canonical norm in $U$. Since $\uh \in \gamma\LRp{D\LRp{A}}$, the standard norm for $\uh$ is
-the so-called minimum energy extension norm defined as
-\begin{equation}
-\eqnlab{MEnorm}
-\|\widehat{u}\| = \inf_{w\in D\LRp{A},
-  \left.w\right|_{\Gh}=\widehat{u}} \|w\|_{D\LRp{A}}.
-\end{equation}
-The canonical norm for the group variable $\LRp{u,\uh}$ is then given by
-\[
-\|\left(u,\widehat{u}\right)\|_U^2 = \|u\|^2_{\L} + \|\widehat{u}\|^2.
-\]
-Applying the Cauchy-Schwarz inequality, we arrive at
-\[
-b\LRp{\LRp{u,\uh},v} \le \nor{\LRp{u,\uh}}_U \nor{v}_{V,U},
-\]
-where
-\[
-\nor{v}_{V,U}^2 = \|A_h^*v\|_{\L}^2
-+\left(\sup_{\widehat{u} \in \gamma\LRp{D\LRp{A}}} \frac{\LRa{ \widehat{u},
-  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2.
-\]
-
-%On the other hand, since $v \in D\LRp{A^*_h}$, the canonical norm for
-%$v$ is the broken graph norm: 
+An obvious choice for the test norm would have been the quasi-optimal norm described in the previous chapter; it is the canonical test norm, and DPG has been shown to be well-posed and robust under such an optimal test norm for a large class of problems \cite{DPGrobustness,Bui-ThanhDemkowiczGhattas11b, stokesDPG}.
+However, as was demonstrated, computations with the quasi-optimal test norm for convection-diffusion problems turn out to be quite problematic for small diffusion and coarse meshes.
+
+%For convection-diffusion, the quasi-optimal test norm is 
 %\[
-%\nor{v}_V^2 =  \|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2.
+%\|\left(v,\tau\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v
+%\|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 +
+%\|v\|_{L^2}^2 + \|\tau\|_{L^2}^2.
 %\]
-%Using the Cauchy-Schwarz inequality again, we obtain
-%\[
-%b\LRp{\LRp{u,\uh},v} \le \nor{\LRp{u,\uh}}_{U,V} \nor{v}_{V},
-%\]
-%where
-%\begin{equation}
-%\eqnlab{inducedQuasi}
-%\nor{\LRp{u,\uh}}_{U,V}^2 = \nor{u}_{\L}^2
-%+\sup_{v \in D\LRp{A_h^*}} \frac{\LRa{\widehat{u},
-%  \jump{v}}_{\Gh}^2}{\|v\|_V^2},
-%\end{equation}
-
-Using the framework developed in \cite{Bui-ThanhDemkowiczGhattas11a}, one can show that $\LRp{\nor{\LRp{u,\uh}}_U,  \nor{v}_{V,U}}$ is an energy norm pairing in the sense discussed in Section \secref{energyPair}.
-That is, the canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ induces (generates) the norm $\nor{v}_{V,U}$ in $V$.
-
-The canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ provides an optimal balance between the standard norms on the field $u$ and the flux $\uh$ \cite{DPG4}.
-As a result, if the induced norm $\nor{v}_{V,U}$ (namely, the optimal test norm) is used to compute  optimal test functions in \eqnref{optvVar}, the finite element error in the canonical norm is the best in the sense of \eqnref{optimalError}.
-Unfortunately, the optimal test norm is non-localizable due to the presence of the jump term $\jump{v}$.
-Since the jump terms couple elements together, the evaluation of the jump terms requires contributions from all the elements in the mesh.
-Consequently, solving for an optimal test function amounts to inverting the Riesz map over the entire mesh $\Oh$, making the optimal test norm impractical.
-
-On the other hand, since $v \in D\LRp{A^*_h}$, we can use as a test norm for $v$ the broken graph norm: 
-\[
-\nor{v}_V^2 =  \|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2.
-\]
-This norm is a localization of $\nor{v}_{V,U}$ to allow for the solution of optimal test functions on an element-by-element basis, and is considered to be the canonical norm on $V$.
-In the DPG literature \cite{DPG4}, $\nor{v}_{V,U}$ is known as the {\em optimal test norm}, while $\nor{v}_{V}$ is known as the {\em quasi-optimal} or {\em graph test norm}.
-
-%Using the framework developed in \cite{Bui-ThanhDemkowiczGhattas11a}, one can show that both pairs $\LRp{\nor{\LRp{u,\uh}}_U,  \nor{v}_{V,U}}$ and $\LRp{\nor{\LRp{u,\uh}}_{U,V}, \nor{v}_{V}}$ are energy norm pairings in the sense discussed in Section \secref{energyPair}.
-That is, the canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ induces (generates) the norm $\nor{v}_{V,U}$ in $V$, while the canonical norm $\nor{v}_V$ in $V$ induces (generates) the energy norm $\nor{\LRp{u,\uh}}_{U,V}$ in $U$.
-In the DPG literature \cite{DPG4}, $\nor{v}_{V,U}$ is known as the {\em optimal test norm}, while $\nor{v}_{V}$ is known as the {\em quasi-optimal test norm}.
-
-%\begin{figure}[!h]
-%\centering
-%\begin{tabular}{l c c}
-%Trial norm & & Test norm \\
-%\hline
-%$\boxed{\|u\|^2_{\L} + \|\widehat{u}\|^2}$ & $\Longrightarrow$  & $\|A_h^*v\|_{\L}^2
-%+\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},
-%  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2$ \\
-%%\hline
-%%Quasi-optimal trial norm & & Canonical test norm \\
-%%\hline
-%$\nor{u}_{\L}^2+\sup_{v } \left(\frac{\LRa{\widehat{u},
-%  \jump{v}}_{\Gh}}{\|v\|_V}\right)^2$ &  $\Longleftarrow$ & $\boxed{\|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2}$
-%\end{tabular}
-%\caption{A summary of the derivation of test/trial norm pairings; we begin with the boxed norm on either the trial or test space, and induce the norm on the other space through duality.
-The optimal \textit{test} norm is naturally derived by beginning with the canonical norm on the trial space, while the quasi-optimal \textit{trial} norm is derived from beginning with the canonical norm on the test space.}
-%\end{figure}
-
-%The canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ provides an optimal balance between the standard norms on the field $u$ and the flux $\uh$ \cite{DPG4}.
-As a result, if the induced norm $\nor{v}_{V,U}$ (namely, the optimal test norm) is used to compute  optimal test functions in \eqnref{optvVar}, the finite element error in the canonical norm is the best in the sense of \eqnref{optimalError}.
+%Use of this norm for the convection-diffusion problem is difficult --- since the problem \eqnref{optvVar} for optimal test functions is local, we can transform the problem over a single element $K$ to the reference element $\widehat{K}$ and show that it is equivalent to a reaction-diffusion system, with diffusion parameter $\frac{\epsilon}{|K|}$, where $|K|$ is the element measure \cite{DBLP:journals/procedia/NiemiCC11}.
+We refer to the inverse of this parameter $\frac{|K|}{\epsilon}$ as the element Peclet number $\rm Pe$.
+For a coarse mesh and small diffusion parameter $\epsilon$, we will have a large element Peclet number, and optimal test functions under the quasi-optimal test norm will develop strong boundary layers of width $\rm Pe$, as seen in Figure~\ref{fig:optTestBoundary}.
 %
-%Unfortunately, the optimal test norm is non-localizable due to the presence of the jump term $\jump{v}$.
-Since the jump terms couple elements together, the evaluation of the jump terms requires contributions from all the elements in the mesh.
-Consequently, solving for an optimal test function amounts to inverting the Riesz map over the entire mesh $\Oh$, making the optimal test norm impractical.
-
-%On the other hand, the quasi-optimal test norm $\nor{v}_V$, namely the canonical norm in $V$, \textit{is} localizable, and hence practical.
-However, it's worth noting the difference between the induced energy norm $\nor{\LRp{u,\uh}}_{U,V}$ and the canonical norm in $U$; under the induced norm $\nor{\LRp{u,\uh}}_{U,V}$ there is no natural interpretation for the norm in which the error in the flux variable $\uh$ is measured.
-
-Using variants of the quasi-optimal test norm, numerical results show that the DPG method appears to provide a ``pollution-free" method without phase error for the Helmholtz equation \cite{DPG4}, and analysis of the pollution-free nature of DPG is currently under investigation.
-Similar results have also been obtained in the context of elasticity \cite{DPGElas} and the linear Stokes equations \cite{Camellia}.
-On the theoretical side, the quasi-optimal test norm has been shown to yield a well-posed DPG methodology for the Poisson and convection-diffusion equations \cite{analysisDPG}.
-More recently, this theory has been generalized to show the well-posedness of DPG for the large class of PDEs of Friedrichs' type \cite{Bui-ThanhDemkowiczGhattas11b}.
-
-\section{Model problem and robustness}
-\seclab{sec:modelSec}
-The remainder of the paper focuses on a convection-diffusion model problem using the abstract theory that we
-have discussed so far.
-In particular, we shall use the DPG method based on the ultra-weak formulation with optimal test functions to solve the model problem and analyze its behavior with respect to $\epsilon$.
-Our goal is to show the robustness of the method with respect to $\epsilon$, and demonstrate its usefulness as  a numerical approach to solving singular-perturbed problems.
-
-We consider the following model convection-diffusion problem on a domain
-$\Omega \subset \mathbb{R}^d$ with boundary $\pO \equiv \Gamma$
-\begin{equation}
-\div (\beta u) - \epsilon\Delta u = f  \in \L \label{primal},
-\end{equation}
-which can be cast into the first order form on the group variable
-$\LRp{u,\sigma}$ as
-\begin{equation}
-\eqnlab{CDstrong}
-A \LRp{u,\sigma} \coloneqq \LRs {
-\begin{array}{c}
-\div (\beta u - \sigma) \\ \frac{1}{\epsilon}\sigma - \grad u
-\end{array}} = \LRs{
-\begin{array}{c}
-f \\ 0
-\end{array}
-}.
-\end{equation}
-Using the abstract ultra-weak formulation developed in Section
-\secref{abstractUweak} for the first order system of PDEs \eqnref{CDstrong} we
-obtain
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh} - \LRa{
-\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n,
-  \jump{v} }_{\Gh},
-\end{align*}
-where $\LRp{v, \tau}$ is the group test function. It should be pointed
-out that the divergence and gradient operators are understood to act
-element-wise on test functions $\LRp{v, \tau}$ in the broken graph
-space $ D\LRp{A_h^*} \coloneqq  H^1(\Oh) \times H({\rm div}, \Oh)$, but
-globally as usual on conforming test functions, i.e.\ $ \LRp{v, \tau}
-\in  H^1(\Omega) \times H({\rm div}, \Omega)$. It follows that the
-canonical norm on this test space can be written as
-\[
-\|\left(v, \tau\right)\|_V^2 = \|\left(v, \tau\right)\|_{H^1(\Oh) \times H({\rm div},\Oh)}^2
-= \sum_{K\in \Oh} \|\left(v, \tau\right)\|_{H^1(K) \times H({\rm
-    div},K)}^2,
-\]
-where
-\[
-\|\left(v, \tau \right)\|_{H^1(K) \times H({\rm div},K)}^2 =
-\|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2 + \|\tau\|_{L^2(K)}^2 +
-\|\div \tau\|_{L^2(K)}^2.
-\]
-
-In order to define the proper norm on the trial space, boundary
-conditions need to be specified. We begin by splitting the boundary
-$\Gamma$ as follows
-\begin{align*}
-\Gamma_{-} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\}, \quad {\rm
-  (inflow)}\\ \Gamma_{+} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\},
-\quad {\rm (outflow)}\\ \Gamma_{0} &\coloneqq \{x\in \Gamma;
-\beta_n(x) = 0\},
-\end{align*}
-where $\beta_n \coloneqq \beta \cdot n$.
-Previous work in \cite{DPGrobustness} adopted Dirichlet boundary
-conditions everywhere on $\Gamma$.  
-%and we could obtain the robustness only with special weighted norms in which the weight varied spatially. 
-In this paper, we employ the inflow
-condition of Hesthaven \etal \cite{Hesthaven96astable}, where we set
+In the application of DPG in \cite{DPG1,DPG2,DPG3,DPG4}, the approximation of optimal test functions is done using polynomial enrichment.
+We search for the solution to \eqnref{optvVar} in the enriched test space $\tilde{V} \approx \prod_{K} P^{p+\Delta p}(K)$, where $p$ is the polynomial order of the trial space on a given element $K$.\footnote{$V$ is only \emph{approximately} equal to the space $\prod_{K} P^{p+\Delta p}(K)$.
+In practice, $V$ is constructed using locally $H^1$-conforming and Raviart-Thomas elements of appropriate order.}  In other words, optimal test functions are approximated element-by-element using polynomials whose order is $\Delta p$ more than the local order of approximation.
+Under this scheme, the error in approximation of test functions is tied to the effectiveness of the $p$-method.
+Unfortunately, for problems with boundary layers --- including the approximation of test functions under the quasi-optimal test norm --- the $p$-method performs very poorly.
+As a result of this poor approximation, the numerical solutions of the convection-dominated diffusion equation under DPG using the quasi-optimal test norm tend to be of poor quality, and do not exhibit all the proven properties of DPG (for example, the energy error may increase after mesh refinement, even though, by virtue of DPG delivering a best approximation, the energy error for a coarse mesh must be greater than or equal to the energy error for a finer mesh).
+We conclude that the error in approximation of optimal test functions using simple polynomial enrichment pollutes and ruins the performance of DPG under the quasi-optimal test norm.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[scale=.3]{figs/opt.png}
+\caption{$v$ and $\tau$ components of the 1D optimal test functions corresponding to the flux $\widehat{f}_n$ on the right-hand side of a unit element for $\epsilon = 0.01$.
+The solution has been obtained using automatic $hp$-adaptivity driven by the test norm with the error tolerance set at 1\%.}
+\label{fig:optTestBoundary}
+\end{figure}
+
+%The difficulty in using the quasi-optimal test norm for convection-diffusion is perplexing at first, considering that the quasi-optimal norm has yielded excellent results for the Helmholtz equation and other wave propagation problems.
+The difference between the two problems lies in the fact that, for wave propagation problems, the mesh size tends to be on the order of the wavenumber $k$ --- the singular perturbation parameter.
+Transforming the variational problem using the quasi-optimal test norm for wave propagation yields smooth optimal test functions that are approximated much more accurately using only polynomials over the reference element.
+Typically, the wavenumbers $k$ of physical interest are $O(100)$ with respect to a unit domain.
+The corresponding finite element problems will typically be solved on meshes containing approximately $O\!\left(k^d\right)$ elements in $\mathbb{R}^d$, well within the range of a computationally tractable simulation.
+However, for convection diffusion problems, the relevant range of $\epsilon$ for physical problems can be as small as $1e-7$.
+Solving on under-resolved meshes is thus unavoidable, and the approximability of optimal test functions must be addressed in order to take advantage of the properties of DPG.
+
+%Resolving such boundary layers present in test functions under the quasi-optimal test norm has been investigated numerically using specially designed (Shishkin) subgrid meshes by Niemi, Collier, and Calo in
+%\cite{DBLP:journals/procedia/NiemiCC11}.
+However, even with Shishkin meshes, the approximation of optimal test functions under the quasi-optimal norm is far more expensive and complex to implement than approximation of test functions using a simple $p$-enriched space for $V$.
+We therefore aim instead to design a test norm that does not induce boundary layers, but still delivers good approximation results over a range of $\epsilon$.
+
+\section{A new inflow boundary condition}
+
+We are interested in computing DPG optimal test functions for the convection-diffusion equation with very small values of $\epsilon$; due to the difficulty of approximating optimal test functions, we conclude that the use of the quasi-optimal test norm is infeasible towards this goal.
+
+However, if we naively choose a test norm that does not generate boundary layers, the performance of DPG may be adversely affected.
+For example, if $\|\left(v,\tau\right)\|_V^2 = \|v\|_{H^1(\Omega_h)}^2 + \|\tau\|^2_{H({\rm div},\Omega_h)}$, the $H^1(\Omega_h)\times H({\rm div},\Omega_h)$ norm, then the corresponding test functions will be smooth and free of boundary layers; however, the performance of DPG will provide approximations which worsen in quality as $\epsilon$ becomes very small \cite{DPG3,DPGrobustness}.
+
+Our goal is to construct a test norm that compromises between performance of DPG and approximability of test functions.
+This test norm should not produce boundary layers in the optimal test functions, but still induce an energy norm that yields good approximation properties for small $\epsilon$.
+We note that, even under the quasi-optimal norm, the norms on the flux and trace variables will likely depend on $\epsilon$.
+Thus, we aim to construct a test norm for which the DPG method will be robust in $\epsilon$ with respect to the \emph{field variables}.
+
+For now, we discuss the steps necessary to analyze the performance of DPG with respect to a non-canonical test norm.
+We require a priori that the test norm has separable $\tau$ and $v$ components --- in other words, that there are no terms in the test norm that couple $\tau$ and $v$ together.
+Problem \eqnref{optvVar} then decouples, such that the components of the vector-valued test function $\left(v,\tau\right)$ can be solved for independently of each other.
+The decoupled variational problems are no longer systems but scalar equations in $\tau$ and $v$, for which it is easier to conclude whether or not there are boundary layers in the solutions (the avoidance of boundary layers in the test norm will be discussed in more detail in Section~\ref{sec:num_exp}, which describes our numerical experiments).
+This will ensure that the resulting DPG method does not suffer from approximation errors in the optimal test functions.
+
+We also adopt a new inflow boundary condition in this chapter.
+Previous work in \cite{DPGrobustness} adopted Dirichlet boundary conditions everywhere on $\Gamma$.
+We employ the inflow condition of Hesthaven \etal \cite{Hesthaven96astable}, where we set
 \[
@@
 
-On the outflow boundary, we apply standard homogeneous Dirichlet boundary conditions
-\[
-u = 0, \quad \text{on } \Gp.
-\]
-This paper is intended to act as an extension of work presented by Heuer and Demkowicz in \cite{DPGrobustness}.
-The primary focus of the paper is to analyze the DPG method and extend previous results under this new choice of inflow boundary conditions.
-The difference in the performance of DPG under both new and old boundary conditions is connected to the difference in the adjoint problems induced under each boundary condition.
-The secondary contribution of this paper will be to analyze the performance of DPG under a new mesh-dependent test norm.
-
 \subsection{Norms on $U$}
 
-With the above boundary conditions at hand, the ultra-weak formulation
-\eqnref{uweak} can be fitted in the abstract form \eqnref{variationEq}
+With the above boundary conditions at hand, we can specify norms on both trial and test spaces which we will use to perform a rigorous mathematical analysis of the DPG method under a given test norm.
+The ultra-weak formulation \eqnref{uweak} can be fitted in the abstract form \eqnref{variationEq}
 as
@@
 \end{align*}
-which, after using the setting in Section \secref{abstractUweak},
-suggests the following trial space (see \cite{analysisDPG, Bui-ThanhDemkowiczGhattas11b} for details):
+which, after using the setting in Section \secref{abstractUweak}, suggests the following trial space (see \cite{analysisDPG, Bui-ThanhDemkowiczGhattas11b} for details):
 \begin{align*}
@@
 %We will denote $\|\cdot \| = \|\cdot\|_{L^2}$ for all functions defined on $\Oh$. 
-As $\tau \in H({\rm div},\Oh)$ and $v \in H^1(\Oh)$, we will
-construct norms on $v$ and $\tau$ 
-which are equivalent to the canonical $H^1(K) \times H({\rm div},K)$
-norm over a single element
+As $\tau \in H({\rm div},\Oh)$ and $v \in H^1(\Oh)$, we will construct norms on $v$ and $\tau$ which are equivalent to the canonical $H^1(K) \times H({\rm div},K)$ norm over a single element
 \[
@@
 
-\subsection{Approximability of the quasi-optimal test norm}
-%\textcolor{blue}{need to define what we mean by robustness. perharps the best place is in the introduction}
-An obvious choice for the test norm would be the quasi-optimal norm; it is the canonical test norm, and DPG has been shown to be well-posed and robust under such an optimal test norm for a large class of problems \cite{DPGrobustness,Bui-ThanhDemkowiczGhattas11b, stokesDPG}.
-However, computations with the quasi-optimal test norm for convection-diffusion problems turn out to be quite problematic for small diffusion and coarse meshes.
-
-For convection-diffusion, the quasi-optimal test norm is 
-\[
-\|\left(v,\tau\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v
-\|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 +
-\|v\|_{L^2}^2 + \|\tau\|_{L^2}^2.
-\]
-%We note that the optimal test norm will automatically guarantee the
-%robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.
-Use of this norm for the convection-diffusion problem is difficult --- since the problem \eqnref{optvVar} for optimal test functions is local, we can transform the problem over a single element $K$ to the reference element $\widehat{K}$ and show that it is equivalent to a reaction-diffusion system, with diffusion parameter $\frac{\epsilon}{|K|}$, where $|K|$ is the element measure \cite{DBLP:journals/procedia/NiemiCC11}.
-We refer to the inverse of this parameter $\frac{|K|}{\epsilon}$ as the element Peclet number $\rm Pe$.
-For a coarse mesh and small diffusion parameter $\epsilon$, we will have a large element Peclet number, and optimal test functions under the quasi-optimal test norm will develop strong boundary layers of width $\rm Pe$, as seen in Figure~\ref{fig:optTestBoundary}.
-
-In the application of DPG in \cite{DPG1,DPG2,DPG3,DPG4}, the approximation of optimal test functions is done using polynomial enrichment.
-We search for the solution to \eqnref{optvVar} in the enriched test space $\tilde{V} \approx \prod_{K} P^{p+\Delta p}(K)$, where $p$ is the polynomial order of the trial space on a given element $K$.\footnote{$V$ is only \emph{approximately} equal to the space $\prod_{K} P^{p+\Delta p}(K)$.
-In practice, $V$ is constructed using locally $H^1$-conforming and Raviart-Thomas elements of appropriate order.}  In other words, optimal test functions are approximated element-by-element using polynomials whose order is $\Delta p$ more than the local order of approximation.
-Under this scheme, the error in approximation of test functions is tied to the effectiveness of the $p$-method.
-Unfortunately, for problems with boundary layers --- including the approximation of test functions under the quasi-optimal test norm --- the $p$-method performs very poorly.
-As a result of this poor approximation, the numerical solutions of the convection-dominated diffusion equation under DPG using the quasi-optimal test norm tend to be of poor quality, and do not exhibit all the proven properties of DPG (for example, the energy error may increase after mesh refinement, even though, by virtue of DPG delivering a best approximation, the energy error for a coarse mesh must be greater than or equal to the energy error for a finer mesh).
-We conclude that the error in approximation of optimal test functions using simple polynomial enrichment pollutes and ruins the performance of DPG under the quasi-optimal test norm.
-
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.25]{opt.png}
-\caption{$v$ and $\tau$ components of the 1D optimal test functions corresponding to the flux $\widehat{f}_n$ on the right-hand side of a unit element for $\epsilon = 0.01$.
-The solution has been obtained using automatic $hp$-adaptivity driven by the test norm with the error tolerance set at 1\%.}
-\label{fig:optTestBoundary}
-\end{figure}
-
-The difficulty in using the quasi-optimal test norm for convection-diffusion is perplexing at first, considering that the quasi-optimal norm has yielded excellent results for the Helmholtz equation and other wave propagation problems.
-The difference between the two problems lies in the fact that, for wave propagation problems, the mesh size tends to be on the order of the wavenumber $k$ --- the singular perturbation parameter.
-Transforming the variational problem using the quasi-optimal test norm for wave propagation yields smooth optimal test functions that are approximated much more accurately using only polynomials over the reference element.
-Typically, the wavenumbers $k$ of physical interest are $O(100)$ with respect to a unit domain.
-The corresponding finite element problems will typically be solved on meshes containing approximately $O\!\left(k^d\right)$ elements in $\mathbb{R}^d$, well within the range of a computationally tractable simulation.
-However, for convection diffusion problems, the relevant range of $\epsilon$ for physical problems can be as small as $1e-7$.
-Solving on under-resolved meshes is thus unavoidable, and the approximability of optimal test functions must be addressed in order to take advantage of the properties of DPG.
-
-Resolving such boundary layers present in test functions under the quasi-optimal test norm has been investigated numerically using specially designed (Shishkin) subgrid meshes by Niemi, Collier, and Calo in
-\cite{DBLP:journals/procedia/NiemiCC11}.
-However, even with Shishkin meshes, the approximation of optimal test functions under the quasi-optimal norm is far more expensive and complex to implement than approximation of test functions using a simple $p$-enriched space for $V$.
-We therefore aim instead to design a test norm that does not induce boundary layers, but still delivers good approximation results over a range of $\epsilon$.
-
-\section{Analysis of a DPG test norm}
+\subsection{Analysis of a robust test norm}
 \seclab{sec:testNormSec}
-We are interested in computing DPG optimal test functions for the convection-diffusion equation with very small values of $\epsilon$; due to the difficulty of approximating optimal test functions, we conclude that the use of the quasi-optimal test norm is infeasible towards this goal.
-
-However, if we naively choose a test norm that does not generate boundary layers, the performance of DPG may be adversely affected.
-For example, if $\|\left(v,\tau\right)\|_V^2 = \|v\|_{H^1(\Omega_h)}^2 + \|\tau\|^2_{H({\rm div},\Omega_h)}$, the $H^1(\Omega_h)\times H({\rm div},\Omega_h)$ norm, then the corresponding test functions will be smooth and free of boundary layers; however, the performance of DPG will provide approximations which worsen in quality as $\epsilon$ becomes very small \cite{DPG3,DPGrobustness}.
-
-Our goal is to construct a test norm that compromises between performance of DPG and approximability of test functions.
-This test norm should not produce boundary layers in the optimal test functions, but still induce an energy norm that yields good approximation properties for small $\epsilon$.
-We note that, even under the quasi-optimal norm, the norms on the flux and trace variables will likely depend on $\epsilon$.
-Thus, we aim to construct a test norm for which the DPG method will be robust in $\epsilon$ with respect to the \emph{field variables}.
-
-For now, we discuss the steps necessary to analyze the performance of DPG with respect to a non-canonical test norm.
-We require a priori that the test norm has separable $\tau$ and $v$ components --- in other words, that there are no terms in the test norm that couple $\tau$ and $v$ together.
-Problem \eqnref{optvVar} then decouples, such that the components of the vector-valued test function $\left(v,\tau\right)$ can be solved for independently of each other.
-The decoupled variational problems are no longer systems but scalar equations in $\tau$ and $v$, for which it is easier to conclude whether or not there are boundary layers in the solutions (the avoidance of boundary layers in the test norm will be discussed in more detail in Section~\ref{sec:num_exp}, which describes our numerical experiments).
-This will ensure that the resulting DPG method does not suffer from approximation errors in the optimal test functions.
-
-We begin with the following test norm:
+Under this new boundary condition, we adopt the test norm:
 \[
@@
 The use of this norm is problematic for practical computations; we will discuss the reasons why and present a modification of it in Section~\secref{sec:meshDep}.
+This work is intended to act as an extension of work presented by Heuer and Demkowicz in \cite{DPGrobustness}.
+The primary focus of the work is to analyze the DPG method and extend previous results under this new choice of inflow boundary conditions.
+The difference in the performance of DPG under both new and old boundary conditions is connected to the difference in the adjoint problems induced under each boundary condition.
+The secondary contribution of this work will be to analyze the performance of DPG under a new mesh-dependent test norm.
 
@@
 Roughly speaking, necessary conditions for the performance of DPG to not degenerate as $\epsilon \rightarrow 0$ are derived through analysis of specific test functions.
-For example, if $u$ is the first $L^2$ component of the solution to the variational problem defined in Section~\secref{sec:modelSec}, by choosing $(v,\tau) \in H^1(\Omega) \times H({\rm div},\Omega)$ such that
+For example, if $u$ is the first $L^2$ component of the solution, by choosing $(v,\tau) \in H^1(\Omega) \times H({\rm div},\Omega)$ such that
 \begin{align*}
@@
 \end{align*}
-we have
+and that boundary terms vanish, we have
 \[
@@
 For this analysis, it will be necessary to assume certain technical conditions on $\beta$.
-For each proof, we require $\beta \in C^2(\bar{\Omega})$ and $\beta, \div \beta = O(1)$.
-Additionally, we will assume that some or all of the following assumptions hold
-\footnote{These assumptions correspond to convection fields which are divergence-free \eqref{c_req}, curl-free \eqref{a_req}, bounded away from zero \eqref{a_req}, and of bounded variation \eqref{b_req}.
+For each proof, we require $\beta \in C^2(\bar{\Omega})$ and $\beta, \div \beta = O(1)$ with respect to $\LRb{\Omega}$, the size of the domain.
+Additionally, we will assume that some or all of the following assumptions hold:\footnote{These assumptions correspond to convection fields which are divergence-free \eqref{c_req}, curl-free \eqref{a_req}, bounded away from zero \eqref{a_req}, and of bounded variation \eqref{b_req}.
 However, these are merely sufficient conditions; numerical experiments indicate that they may not be strictly necessary.}
-:
 \begin{align}
@@
 \centering
-\subfigure{\includegraphics[scale=.22]{mesh1.png}}
-\subfigure{\includegraphics[scale=.22]{sol1.png}}
+\subfigure{\includegraphics[scale=.2125]{figs/mesh1.png}}
+\subfigure{\includegraphics[scale=.2125]{figs/sol1.png}}
 \caption{The $v$ component of the optimal test function corresponding to flux $\widehat{u} = x(1-x)$ on the bottom side of a unit element for $\epsilon = 0.01$.
@@
 Similarly, we scale the $L^2$ contributions of $\tau$ by $C_\tau(K)$ such that $\frac{C_\tau(K)}{\epsilon} \|\tau\|^2$ and $\|\div \tau\|^2$ are of the same magnitude as well.
-For this paper, we consider only isotropic refinements on quadrilateral elements in 2D.
+For now, we consider only isotropic refinements on quadrilateral elements in 2D.
 
@@
 
-The main theoretical result of this paper can now be given:
+The main theoretical result of this chapter can now be given:
 \begin{lemma}
@@
 \centering
-\includegraphics[scale=.5]{testBoundary1D.pdf}
+\includegraphics[scale=.65]{figs/testBoundary1D.eps}
 \caption{$v_1(x) = \frac{e^{-\frac{x}{\epsilon}}}{e^{\frac{1}{\epsilon}}-1}\left(e^{\frac{1}{\epsilon}}\left(e^{\frac{x}{\epsilon}}-1\right) + \left(e^{\frac{1}{\epsilon}}-1\right)e^{\frac{x}{\epsilon}}x\right)$, the solution to the adjoint equation for $f=0$ and constant $\beta$ and load $g$ for $\epsilon = .01$.}
@@
 Thus, we cannot conclude $\|\beta v'\| \lesssim \|g\|$ when $g$ is a constant,\footnote{Unlike the case of Dirichlet boundary conditions, the inflow condition on $ \widehat{f}_n = u(0)-\epsilon u'(0)$ induces an adjoint boundary condition $\tau(0)=0$, or equivalently $v'(0) = 0$, removing the non-robust term from the estimate.} and as a consequence cannot conclude that the robust error bound $\|u-u_h\|_{L^2} \lesssim \|(u,\sigma,\widehat{u},\widehat{f}_n)-(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h})\|_E$ holds for the solution $u_h$.
-More detailed 1D error bounds for Dirichlet boundary conditions are provided in \cite{DPG3}, and indicate the same lack of robustness under the test norm derived in this paper.\footnote{Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
+More detailed 1D error bounds for Dirichlet boundary conditions are provided in \cite{DPG3}, and indicate the same lack of robustness under the test norm derived in this work.\footnote{Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
 \[
@@
 \centering
-\subfigure[Primal problem, Dirichlet inflow BC]{\includegraphics[scale=.375]{primalDir.pdf}}
-\subfigure[Adjoint problem, Dirichlet inflow BC]{\includegraphics[scale=.375]{adjointDir.pdf}}
-\subfigure[Primal problem, new inflow BC]{\includegraphics[scale=.375]{primal.pdf}}
-\subfigure[Adjoint problem, new inflow BC]{\includegraphics[scale=.375]{adjoint.pdf}}
+\subfigure[Primal problem, Dirichlet inflow BC]{\includegraphics[scale=.425]{figs/primalDir.eps}}
+\subfigure[Adjoint problem, Dirichlet inflow BC]{\includegraphics[scale=.425]{figs/adjointDir.eps}}
+\subfigure[Primal problem, new inflow BC]{\includegraphics[scale=.425]{figs/primal.eps}}
+\subfigure[Adjoint problem, new inflow BC]{\includegraphics[scale=.425]{figs/adjoint.eps}}
 \caption{Comparison of primal and adjoint problems under both the standard Dirichlet and the new inflow boundary condition.
@@
 
-Recall our strategy for analysis was to decompose of $(v,\tau)$ into continuous and discontinuous portions.
-Mathematically speaking, the use of Dirichlet boundary conditions on the primal problem introduces strong boundary layers into the solution $v$ of the adjoint equation --- in other words, boundary layers are introduced into the continuous portions of our decomposition of $(v,\tau)$.\footnote{The boundary conditions do not introduce boundary layers into the actual computed test functions.
-However, an interesting phenomenon observed is that, for small $\epsilon$, a lack of robustness can manifest itself during numerical experiments as additional refinements near the inflow boundary, precisely where the continuous parts of the decomposition of $(v,\tau)$ develop boundary layers.} The new inflow boundary condition on the primal problem relaxes the wall boundary condition induced on the adjoint/dual problem with a boundary condition that does not generate boundary layers, resulting in stronger stability estimates for the adjoint, and a better result for the primal problem.
-
-%\begin{figure}[h]
-%\centering
-%\subfigure[Primal problem]{\includegraphics[scale=.3]{primal.png}}
-%\subfigure[Adjoint problem]{\includegraphics[scale=.3]{adjoint.png}}
-%\caption{Comparison of primal and adjoint problems for convection-diffusion under the standard Dirichlet outflow boundary condition and the new inflow boundary condition.
-Notice the replacement of a wall-stop boundary condition with a Neumann stress boundary condition at the outflow boundary of the adjoint problem.
-}
-%\end{figure}
+Recall our strategy for analysis was to decompose $(v,\tau)$ into continuous and discontinuous portions.
+Mathematically speaking, the use of Dirichlet boundary conditions on the primal problem introduces strong boundary layers into the solution $v$ of the adjoint equation --- in other words, boundary layers are introduced into the continuous portions of our decomposition of $(v,\tau)$.\footnote{We note that the boundary conditions do not introduce boundary layers into the actual computed test functions.
+However, an interesting phenomenon observed is that, for small $\epsilon$, a lack of robustness can manifest itself during numerical experiments as additional refinements near the inflow boundary, precisely where the continuous parts of the decomposition of $(v,\tau)$ develop boundary layers.
+Please refer to the earlier discussion in Section~\secref{sec:inflowRefinements}.} The new inflow boundary condition on the primal problem relaxes the wall boundary condition induced on the adjoint/dual problem with a boundary condition that does not generate boundary layers, resulting in stronger stability estimates for the adjoint, and a better result for the primal problem.
 
@@
 
-To confirm our theoretical results, we adopt a modification of a problem first proposed by Eriksson and Johnson in \cite{Eriksson1993}.
+To confirm our theoretical results, we use again the problem of Eriksson and Johnson \cite{Eriksson1993} introduced in the previous chapter.
+This problem yields an exact solution with a boundary layer for the convection-diffusion problem with a forcing term independent of $\epsilon$.
+%
+%To confirm our theoretical results, we adopt a modification of a problem first proposed by Eriksson and Johnson in \cite{Eriksson1993}.
 For the choice of $\Omega = (0,1)^2$, $f=0$, and $\beta = (1,0)^T$, the convection diffusion equation reduces to
-\[
-\pd{u}{x} - \epsilon \left(\pdd{u}{x}+ \pdd{u}{y}\right) = 0,
-\]
-which has an exact solution by separation of variables, allowing us to analyze convergence of DPG for a wide range of $\epsilon$.
-For boundary conditions, we impose $u=0$ on $\Gamma_+$ and $\beta_n u - \sigma_n$ on $\Gamma_-$, which reduces to
+%\[
+%\pd{u}{x} - \epsilon \left(\pdd{u}{x}+ \pdd{u}{y}\right) = 0,
+%\]
+%which has an exact solution by separation of variables, allowing us to analyze convergence of DPG for a wide range of $\epsilon$.
+
+Unlike our previous experiments using the Eriksson-Johnson problem, which enforced Dirichlet boundary conditions on $u$ on both inflow and outflow, we impose boundary conditions on $u=0$ on $\Gamma_+$ and $\beta_n u - \sigma_n$ on $\Gamma_-$, which reduces to
 \begin{align*}
@@
 \sigma_y &=  0, \quad y=0,1,\\
-u &= 0, \quad x=1.\\
-\end{align*}
-In this case, our exact solution is the series
+u &= 0, \quad x=1.
+\end{align*}
+The exact solution is the series
 \[
@@
 \]
-where
-\begin{align*}
-r_{1,2} &= \frac{1 \pm \sqrt{1 + 4 \epsilon\lambda_n}}{2 \epsilon},\\
-\lambda_n &= n^2\pi^2 \epsilon.
-\end{align*}
-The constants $C_n$ depend on a given inflow condition $u_0$ at $x=0$ via the formula
+%where
+%\begin{align*}
+%r_{1,2} &= \frac{1 \pm \sqrt{1 + 4 \epsilon\lambda_n}}{2 \epsilon},\\
+%\lambda_n &= n^2\pi^2 \epsilon.
+%\end{align*}
+where $r_{1,2}$ are specified previously in Section~\secref{sec:inflowRefinements}, and the constants $C_n$ depend on a given inflow condition $u_0$ at $x=0$ via the formula
 \[
@@
 \]
-
 All computations have been done using the adaptive DPG code Camellia, built on the Sandia toolbox Trilinos \cite{Camellia}.
@@
 \subfigure{
-\includegraphics[scale=.37]{wallBC_exact_u.png}
-}
-\subfigure{
-\includegraphics[scale=.37]{wallBC_exact_sigx.png}
-}
-\subfigure{
-\includegraphics[scale=.37]{wallBC_exact_sigy.png}
-}
-\caption{Solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
+\includegraphics[scale=.65]{figs/wallBC_exact_u.png}
+}
+\caption{Solution for $u$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\subfigure{
+\includegraphics[scale=.45]{figs/wallBC_exact_sigx.png}
+}
+\subfigure{
+\includegraphics[scale=.45]{figs/wallBC_exact_sigy.png}
+}
+\caption{Solution for $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
 \end{figure}
 In each case, we begin with a square 2 by 2 mesh of quadrilateral elements with order $p=3$.
-We choose $\Delta p = 5$, though we note that the behavior of DPG is nearly identical for any $\Delta p \leq 3$, and qualitatively the same for $\Delta p = 2$.
+We choose $\Delta p = 5$, though we note that the behavior of DPG is nearly identical for any $\Delta p \geq 3$, and qualitatively the same for $\Delta p = 2$.
 $h$-refinements are executed using a greedy refinement algorithm, where the element energy error $e_K^2$ is computed for all elements $K$, and elements such that $e_K^2 \leq \alpha^2 \max_K e_K^2$ are refined.
@@
 \centering
-\includegraphics[scale=.4]{u_pointdiff_wallBC.png}
+\includegraphics[scale=.5]{figs/u_pointdiff_wallBC.png}
 \caption{Adapted mesh and pointwise error for $\epsilon=.01$}
@@
 \subfigure{
-\includegraphics[scale=.38]{errorrates_wallBC.pdf}
-}
-\subfigure{
-\includegraphics[scale=.38]{L2energyratio_wallBC.pdf}
+\includegraphics[scale=.4]{figs/errorrates_wallBC.eps}
+}
+\subfigure{
+\includegraphics[scale=.4]{figs/L2energyratio_wallBC.eps}
 }
@@
 \subfigure{
-\includegraphics[scale=.38]{roundoff_rates.pdf}
-}
-\subfigure{
-\includegraphics[scale=.38]{roundoff_ratio.pdf}
+\includegraphics[scale=.4]{figs/roundoff_rates.eps}
+}
+\subfigure{
+\includegraphics[scale=.4]{figs/roundoff_ratio.eps}
 }
@@
 \subfigure{
-\includegraphics[scale=.38]{rates_noSigma.pdf}
-}
-\subfigure{
-\includegraphics[scale=.38]{ratio_noSigma.pdf}
+\includegraphics[scale=.4]{figs/rates_noSigma.eps}
+}
+\subfigure{
+\includegraphics[scale=.4]{figs/ratio_noSigma.eps}
 }
@@
 \subfigure{
-\includegraphics[scale=.38]{disc_hat.png}
-}
-\subfigure{
-\includegraphics[scale=.38]{disc_hat_surf.png}
+\includegraphics[scale=.4]{figs/disc_hat.png}
+}
+\subfigure{
+\includegraphics[scale=.4]{figs/disc_hat_surf.png}
 }
@@
 \subfigure{
-\includegraphics[scale=.38]{rates_disc.pdf}
-}
-\subfigure{
-\includegraphics[scale=.38]{ratio_disc.pdf}
+\includegraphics[scale=.4]{figs/rates_disc.eps}
+}
+\subfigure{
+\includegraphics[scale=.4]{figs/ratio_disc.eps}
 }
@@
 However, the ratios still remain bounded as predicted by theory, and similarly to the previous problem with a smooth inflow condition, the ratios are close to $1$ for $\epsilon$ varying over two orders of magnitude.
-
-\section{Conclusions}
-
-We have presented in this paper the analysis of a non-canonical test norm and its corresponding DPG energy norm for the convection-diffusion equation in the small-diffusion limit.
-Additionally, we have introduced a non-standard inflow boundary condition, and have explored the difference between between this and the standard Dirichlet inflow boundary condition.
-
-Numerical results are presented in order to verify the results derived in this paper.
-However, at least for our model problem, numerical experiments appear to demonstrate results that are stronger than our proofs indicate, delivering solutions for $u$ and $\sigma$ that are extremely close to their best $L^2$ projections.
-
-The theory presented in this paper have been successfully extrapolated to nonlinear singular perturbation problems and systems of equations, and has been applied in context of the Burgers and Navier-Stokes equations.
-These results will be presented in an upcoming paper.
-
-\section{Acknowledgements}
-
-The authors would like to acknowledge the help of Nathan Roberts with software development and Dr Robert Moser for fruitful discussions and perspective.
-Chan and Demkowicz were supported by the Department of Energy [National Nuclear Security Administration] under Award Number [DE-FC52-08NA28615].
-Heuer was supported through the project "Fondecyt-Chile 1110324" and by the "J Tinsley Oden Faculty Research Fellowship" of the Institute of Computational Engineering and Sciences (ICES).
-
-%None yet.  Ideas:
-%\begin{itemize}
-%\item Explanation of choice of boundary condition and why it impacts stability
-%\item Interpretation of weight as allowing diffusion to work on the boundary.  
-%\item Note results have worked for Burgers, and mention the extension to Navier-Stokes
-%\end{itemize}
-
-\bibliographystyle{plain}
-\bibliography{paper}
-
-\input{paper_appendix.tex}
-
-\end{document}

### 2013-07-30 docs/Jesse/Dissertation/NSNotes.tex

--- 2012-07-16 docs/Jesse/Proposal/NSNotes.tex
@@
 \div \vecttwo{\rho u_1 u_2}{\rho u_2^2+p } &= \div\left(\vec{\sigma_{i2}}\right)\\
-\div\vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2} &= \div\left[\boldsymbol\sigma U + \vec{q}\right],
+\div\vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2} &= \div\left[\boldsymbol\sigma \boldsymbol u + \vec{q}\right],
 \end{align*}
-where $\boldsymbol \sigma$ is the stress tensor whose $ij$th term is $\sigma_{ij}$.
+where $\boldsymbol \sigma$ is the stress tensor whose $ij$th term is $\sigma_{ij}$, and $\boldsymbol u$ is the vector $(u_1,u_2)^T$.
 
@@
 \[
-\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \frac{1}{2\mu} \sigma_{ij} - \frac{\lambda}{4\mu (\mu + \lambda)} \sigma_{kk}\delta_{ij}
+\frac{1}{2}\left(\grad  \boldsymbol u + \grad ^T  \boldsymbol u\right) = \frac{1}{2\mu} \sigma_{ij} - \frac{\lambda}{4\mu (\mu + \lambda)} \sigma_{kk}\delta_{ij}
 \]
@@
 \[
-\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \grad  U - \boldsymbol \omega
+\frac{1}{2}\left(\grad  \boldsymbol u + \grad ^T  \boldsymbol u\right) = \grad  \boldsymbol u - \boldsymbol \omega
 \]
@@
 \[
-\boldsymbol \omega = \frac{1}{2}\left(\grad  U - \grad ^T  U\right).
+\boldsymbol \omega = \frac{1}{2}\left(\grad  \boldsymbol u - \grad ^T  \boldsymbol u\right).
 \]
@@
 \begin{align*}
-\grad  U - \boldsymbol \omega = \frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I.
+\grad  \boldsymbol u - \boldsymbol \omega = \frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I.
 \end{align*}
-Notice that $\boldsymbol \omega$ is implicitly defined to be the symmetric part of $\grad u$ by taking the symmetric part of the above equation.
+Notice that $\boldsymbol \omega$ is implicitly defined to be the antisymmetric part of $\grad u$ by taking the symmetric part of the above equation.
 
@@
 \begin{align*}
-\div \vecttwo{\rho u }{\rho v} &= 0\\
-\div \left(\vecttwo{\rho u^2+p }{\rho u v} - \boldsymbol \sigma_{1}\right) &=0\\
-\div \left(\vecttwo{\rho u v}{\rho v^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
-\div \left(\vecttwo{((\rho e)+p)u}{((\rho e)+p)v} - \boldsymbol\sigma \mathbf{u} + \vec{q}\right) &=0\\
+\div \vecttwo{\rho u_1 }{\rho u_2} &= 0\\
+\div \left(\vecttwo{\rho u_1^2+p }{\rho u_1 u_2} - \boldsymbol \sigma_{1}\right) &=0\\
+\div \left(\vecttwo{\rho u_1 u_2}{\rho u_2^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
+\div \left(\vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2} - \boldsymbol\sigma \mathbf{u} - \vec{q}\right) &=0\\
 \frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I &= \grad \mathbf{u} - \Reyn \, {\boldsymbol \omega}\\
@@
 
+As the equations for viscous compressible flow are nonlinear and cannot be solved exactly, we linearize the equations and adopt an iterative procedure for approximating the nonlinear solution.\footnote{We note that it is possible to linearize the strong form of the equations and then derive a linearized weak form, instead of linearizing the weak form of the nonlinear equations, which is done here.
+The two formulations are equivalent; however, extraneous linearization of the fluxes is avoided using the latter approach.}  We outline the linearization of both the conservation and stress laws in this section.
+
 \subsubsection{Conservation laws}
@@
 \begin{align*}
-\div \vecttwo{\rho u }{\rho v} &= 0\\
-\div \left(\vecttwo{\rho u^2+p }{\rho u v} - \boldsymbol \sigma_{1}\right) &=0\\
-\div \left(\vecttwo{\rho u v}{\rho v^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
-\div \left(\vecttwo{((\rho e)+p)u}{((\rho e)+p)v} - \boldsymbol \sigma_1 \cdot \boldsymbol u- \boldsymbol \sigma_2 \cdot \boldsymbol u + \vec{q}\right) &=0
+\div \vecttwo{\rho u_1 }{\rho u_2} &= 0\\
+\div \left(\vecttwo{\rho u_1^2+p }{\rho u_1 u_2} - \boldsymbol \sigma_{1}\right) &=0\\
+\div \left(\vecttwo{\rho u_1 u_2}{\rho u_2^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
+\div \left(\vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2} - \boldsymbol \sigma_1 \cdot \boldsymbol u- \boldsymbol \sigma_2 \cdot \boldsymbol u - \vec{q}\right) &=0,
 \end{align*}
-or generally, 
+where $\boldsymbol \sigma_1$ is the $i$th column or row of $\boldsymbol \sigma$, or more generally, if we group our Eulerian and stress variables into the vector variables $\boldsymbol U$ and $\boldsymbol \Sigma$, respectively
 \[
-\div (F_i(\boldsymbol U)-G_i(\boldsymbol U,\boldsymbol \sigma) = 0, \qquad i = 1,\ldots, 4
+\div (F_i(\boldsymbol U)-G_i(\boldsymbol U,\boldsymbol \Sigma) = 0, \qquad i = 1,\ldots, 4,
 \]
+where $F_i$and $G_i$ are given as
+\begin{align*}
+F_1 = \vecttwo{\rho u_1 }{\rho u_2}, \quad &G_1 = 0\\
+F_2 = \vecttwo{\rho u_1^2+p }{\rho u_1 u_2},\quad &G_2 = \boldsymbol \sigma_{1}\\
+F_3 = \vecttwo{\rho u_1 u_2}{\rho u_2^2+p }, \quad &G_3 = \boldsymbol \sigma_{2}\\
+F_4 = \vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2}, \quad &G_4 = \boldsymbol \sigma_1 \cdot \boldsymbol u + \boldsymbol \sigma_2 \cdot \boldsymbol u + \vec{q}
+\end{align*}
 The variational form restricted to a single element gives
 \[
-\langle \widehat{F}_i\cdot n, v\rangle - \int_K  (F(\boldsymbol U)-G_i(\boldsymbol U,\boldsymbol \sigma)) \cdot \grad v_i = 0 , \qquad i = 1,\ldots, 4
+\langle \widehat{F}_i\cdot n, v\rangle - \int_K  (F(\boldsymbol U)-G_i(\boldsymbol U,\boldsymbol \Sigma)) \cdot \grad v_i = 0 , \qquad i = 1,\ldots, 4
 \]
@@
 The presence of terms such as $\boldsymbol \sigma_i \cdot \boldsymbol u$ means that we will need to linearize in the stress variables $\sigma_ij$ in addition to our Eulerian quantities.
-Since fluxes and traces are linear, we do not need to linearize them.
+Since fluxes and traces are linear functions of the unknowns, we do not need to linearize them.
 Instead, fluxes $\widehat{F}_{i,n}$ and traces $\widehat{u},\widehat{v},\widehat{T}$ will represent normal traces and traces of the accumulated nonlinear solution.
@@
 \begin{align*}
-\langle \widehat{F}_i\cdot n, v\rangle &- \int_K  \left(F_{i,\boldsymbol U}(\boldsymbol U)\cdot \Delta \boldsymbol U -G_{i,\boldsymbol U}(\boldsymbol U, \boldsymbol \sigma)\cdot \Delta \boldsymbol U - G_{i,\boldsymbol \sigma}(\boldsymbol U, \boldsymbol \sigma)\cdot \Delta \boldsymbol \sigma \right)\cdot \grad v_i \\
+\langle \widehat{F}_i\cdot n, v\rangle &- \int_K  \left(F_{i,\boldsymbol U}(\boldsymbol U)\cdot \Delta \boldsymbol U -G_{i,\boldsymbol U}(\boldsymbol U, \boldsymbol \Sigma)\cdot \Delta \boldsymbol U - G_{i,\boldsymbol \Sigma}(\boldsymbol U, \boldsymbol \Sigma)\cdot \Delta \boldsymbol \Sigma \right)\cdot \grad v_i \\
 &= \int_K  \left(F_i(\boldsymbol U)-G_i(\boldsymbol U)\right) \cdot \grad v_i \\
@@
 \end{align*}
-where $F^i_{j,\boldsymbol U}$, $G^i_{j,\boldsymbol U}$, and $G^i_{j,\boldsymbol \sigma}$ are the Eulerian and two viscous Jacobians (linearized w.r.t.\ the Eulerian/viscous variables), respectively.
+where $F^i_{j,\boldsymbol U}$, $G^i_{j,\boldsymbol U}$, and $G^i_{j,\boldsymbol \Sigma}$ are the Eulerian and two viscous Jacobians (linearized w.r.t.\ the Eulerian/viscous variables), respectively.
 %where
@@
 \[
-\|\left(v,\tau\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
+\|\left(v,\tau\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau-\beta\cdot\grad v\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
 \]
@@
 
-Our test norm is extrapolated to the Navier-Stokes equations as follows: we denote the vector of $H^1$ test functions as $v=\{v_1,v_2,v_3,v_4\}$, and similarly for $W = \{\tau_1,\tau_2,\tau_3\}$.
-Similarly, we group our Eulerian and stress variables into the vector variables $U$ and $\Sigma$, respectively.
-If $R_{\rm Euler}(U,\Sigma)$ and $R_{\rm visc}(U,\Sigma)$ are Eulerian and viscous nonlinear residuals, our formulation for the linearized Navier-Stokes equations can be written as
+This test norm is extrapolated to the Navier-Stokes equations as follows: we denote the vector of $H^1$ test functions as $\boldsymbol V=\{v_1,v_2,v_3,v_4\}$, and similarly for $\boldsymbol W = \{\tau_1,\tau_2,\tau_3\}$.
+If $R_{\rm Euler}(\boldsymbol U,\boldsymbol \Sigma)$ and $R_{\rm visc}(\boldsymbol U,\boldsymbol \Sigma)$ are Eulerian and viscous nonlinear residuals, our formulation for the linearized Navier-Stokes equations can be written as
 \begin{align*}
-\div \left(A_{\rm Euler}U - A_{\rm visc}\Sigma\right) &= R_{\rm Euler}(U,\Sigma)\\
-E_{\rm visc} \Sigma - \grad U &= R_{\rm visc}(U,\Sigma)
+\div \left(A_{\rm Euler}\boldsymbol \delta U - A_{\rm visc}\boldsymbol \delta \Sigma\right) &= R_{\rm Euler}(\boldsymbol U,\boldsymbol \Sigma)\\
+E_{\rm visc}\boldsymbol  \delta \Sigma - \grad \boldsymbol \delta U &= R_{\rm visc}(\boldsymbol U,\boldsymbol \Sigma)
 \end{align*}
@@
 \begin{align*}
-\LRa{\widehat{F}_n,V}_{\Gh} + \left(U,\div W - A_{\rm Euler}^T\grad  V\right) + \LRa{\widehat{U},W\cdot n}_{\Gh} + \left(\Sigma,E_{\rm visc}^TW - A_{\rm visc}^T\grad  V\right) &= 0
+\LRa{\widehat{F}_n,\boldsymbol V}_{\Gh} + \left(\boldsymbol \delta U,\div \boldsymbol W - A_{\rm Euler}^T\grad \boldsymbol  V\right) + \LRa{\widehat{\boldsymbol U},\boldsymbol W\cdot n}_{\Gh} + \left(\boldsymbol \delta \Sigma,E_{\rm visc}^T\boldsymbol W - A_{\rm visc}^T\grad \boldsymbol  V\right) &=
+\\ \LRa{R_{\rm Euler}(\boldsymbol U,\boldsymbol \Sigma),\boldsymbol V} + \LRa{R_{\rm visc}(\boldsymbol U,\boldsymbol \Sigma),\boldsymbol W}
 \end{align*}
@@
 \begin{align*}
-\|\left(V,W\right)\|_{V,K}^2 =& \min\left\{\frac{\Reyn}{|K|},1\right\}\|v\|^2 + \frac{1}{\Reyn} \|A_{\rm visc}^T\grad v\|^2 + \|A_{\rm Euler}^T \grad v\|^2 \\
-& + \| \div W\|^2 + \min\left\{\Reyn,\frac{1}{|K|}\right\}\|E_{\rm visc}^T\tau\|^2.
+\|\left(\boldsymbol V,\boldsymbol W\right)\|_{V, K}^2 =& \|\boldsymbol V\|^2 + \frac{1}{\Reyn} \|A_{\rm visc}^T\grad \boldsymbol V\|^2 + \|A_{\rm Euler}^T \grad \boldsymbol V\|^2 \\
+& + \| \div \boldsymbol W - A_{\rm Euler}^T \grad \boldsymbol V\|^2 + \min\left\{\Reyn,\frac{1}{|K|}\right\}\|E_{\rm visc}^T\boldsymbol W\|^2.
 \end{align*}
-An advantage of this extrapolation approach is that the incompletely parabolic nature of the Navier-Stokes equation is taken into account; there is no diffusive term present in the mass conservation equation, and the test norm reflects that by requesting only limited regularity of $v_1$.\footnote{The situation is analogous to using the full $H^1(\Oh)$ norm for the pure convection equation --- the optimal test norm $\nor{v}_V = \nor{\beta\cdot \grad v} + \nor{v}$ implies only streamline regularity, whereas taking $\nor{v}_V = \nor{\grad v} + \nor{v}$ implies stronger regularity on the test space $V$ than the graph norm.
+An advantage of this extrapolation approach is that the incompletely parabolic nature of the Navier-Stokes equation is taken into account; there is no diffusive term present in the mass conservation equation, and the test norm reflects that by requesting only limited regularity of $v_1$, the test function for the conservation equation.\footnote{The situation is analogous to using the full $H^1(\Oh)$ norm for the pure convection equation --- the optimal test norm $\nor{v}_V = \nor{\beta\cdot \grad v} + \nor{v}$ implies only streamline regularity, whereas taking $\nor{v}_V = \nor{\grad v} + \nor{v}$ implies stronger regularity on the test space $V$ than the graph norm.
 Consequently, convergence is suboptimal for DPG applied to the convection problem under the $H^1(\Oh)$ test norm.}
@@
 
+\section{Nonlinear solver}
+
+For our nonlinear solver, we use a pseudo-time stepping approach to iterate to a steady state solution, along with a greedy refinement scheme to eliminate spatial discretization error.
+We cover briefly the details of the pseudo-timestepping method in this section.
+%Though we have not yet implemented adaptive timestepping, we are able to take large enough uniform timesteps over a coarse mesh such that convergence occurs sufficiently quickly.
+
+\subsection{Pseudo-timestepping}
+
+The solution of the compressible Navier-Stokes equations can be quite challenging; as mentioned previously, the direct application of a Newton algorithm often will not converge, especially for high Reynolds numbers.
+Typically, a pseudo-timestepping algorithm is used in lieu of a full nonlinear Newton algorithm.
+The pseudo-timestep proceeds as follows: given the transient terms present in the conservation laws of compressible flow
+\begin{align*}
+\pd{\rho}{t} + \ldots \\
+\pd{\LRp{\rho u}}{t} + \ldots \\
+\pd{\LRp{\rho v}}{t} + \ldots \\
+\pd{\LRp{\rho e}}{t} + \ldots,
+\end{align*}
+we discretize each time derivative using an implicit timestepping method.
+Though second order time discretizations have been shown to be effective \cite{Demkowicz1990275, BenKirk}, we choose a first order backwards Euler discretization for simplicity.
+Due to the fact that we've chosen to solve the Navier-Stokes equations under primitive variables $\rho, u, v$, and $T$, the time terms are nonlinear as well, and must be linearized.
+After time discretization and linearization, we are left with a coupled system of reaction terms in the problem for our solution update at every timestep
+\begin{align*}
+A_{\rm time}\boldsymbol \delta U_i + \div \left(A_{\rm Euler}\boldsymbol \delta U_i - A_{\rm visc}\boldsymbol \delta \Sigma_i\right) &= R_{\rm Euler}(\boldsymbol U_i,\boldsymbol \Sigma_i) + R_{\rm time}(\boldsymbol U_{i-1},\boldsymbol U_i)\\
+E_{\rm visc} \boldsymbol \Sigma_i - \grad \boldsymbol U_i &= R_{\rm visc}(\boldsymbol U_i,\boldsymbol \Sigma_i),
+\end{align*}
+where $R_{\rm time}(\boldsymbol U_{i-1},\boldsymbol U_i)$ is the transient residual.  Including the transient terms in our test norm as well, our final test norm is 
+\begin{align*}
+\|\left(\boldsymbol V,\boldsymbol W\right)\|_{V,K}^2 =& \nor{A_{\rm time}^T\boldsymbol V} + \|\boldsymbol V\|^2 + \frac{1}{\Reyn} \|A_{\rm visc}^T\grad \boldsymbol V\|^2 + \|A_{\rm Euler}^T \grad \boldsymbol V\|^2 \\
+& + \| \div \boldsymbol W - A_{\rm Euler}^T \grad \boldsymbol V\|^2 + \min\left\{\Reyn,\frac{1}{|K|}\right\}\|E_{\rm visc}^T\boldsymbol W\|^2.
+\end{align*}
+Finally, convergence of the pseudo-timestepping method is determined by measuring the transient residual in the energy norm; in other words, we measure $\nor{e_{\rm time}}_V$, where
+\[
+\LRp{\LRp{\boldsymbol V,\boldsymbol W},\LRp{\boldsymbol dV,\boldsymbol dW}}_V = \LRp{R_{\rm time}(\boldsymbol U_{i-1},\boldsymbol U_i),\boldsymbol V}_{\L}, \quad \forall \LRp{\boldsymbol dV,\boldsymbol dW} \in V.
+\]
+The energy norm thus provides a consistent measure in which convergence of the nonlinear iteration at each timestep, convergence of the pseudo-timestepping algorithm to steady state, and nonlinear residual can all be assessed.
+
+\subsubsection{Dependence of solution on $dt$}
+
+A surprising feature of pseudo-timestepping schemes for DPG is that, under the problem-dependent minimum-residual nature of the method, convergence to steady state can yield qualitatively slightly different solutions under different size timesteps.
+We illustrate this using the plate example for convection-diffusion, which we described first in Section~\secref{sec:confusionPlate}.
+We consider the transient form of the conservation equation for convection-diffusion
+\[
+\pd{u}{t} + \div \LRp{\beta u - \sigma} = f, 
+\]
+where the stress law remains unchanged.
+Applying a backwards Euler time discretization, at each timestep, we will solve for the current solution $u_i$ (as well as the current stress $\sigma_i$) given the previous timestep solution $u_{i-1}$ under
+\[
+\frac{u_i}{dt} + \div \LRp{\beta u_i - \sigma_i} = f + \frac{u_{i-1}}{dt}.
+\]
+The conserved flux $\beta_n u - \sigma_n$ is set to freestream values on the inflow, and 0 on the top boundary $y = 1$ and half of the bottom boundary $x < .5, y = 0$.
+We set $u = 1$ for the boundary $x \in (.5,1), y = 0$.
+For this example, $\beta = (1,0)$ and $\epsilon = 10^{-3}$.
+\begin{figure}
+\centering
+\subfigure[$dt = .1$]{\includegraphics[scale=.35]{figs/confusionDtFigs/dt10.png}}
+\subfigure[$dt = .01$]{\includegraphics[scale=.35]{figs/confusionDtFigs/dt100.png}}
+\caption{Comparison of pseudo-timestepping to steady state for a convection-diffusion problem under two different sizes of timestep.}
+\label{fig:dtComparison}
+\end{figure}
+This can be understood as the consequence of solving a ``moving target'' optimization problem -- our variational formulation and test norm for this problem are
+\begin{align*}
+\LRp{u_{i}, \frac{1}{dt}v}_{\L} + b\LRp{u_i,v} &= l(v) + \LRp{u_{i-1},\frac{1}{dt}v}_{\L}\\
+\nor{\LRp{\tau,v}}_{V,dt}^2 &= \frac{1}{dt}\nor{v}_{\L}^2 + \nor{v}_V^2,
+\end{align*}
+where $\nor{\LRp{\tau,v}}_{V}$ is the coupled test norm introduced in Section~\secref{sec:testNormSec}, and $b(u,v)$ and $l(v)$ are the bilinear form and load for the steady state form of the convection diffusion equation.
+DPG solutions minimize the functional
+\[
+J(u_i) = \sup_{v\in V} \frac{\LRp{u_{i}-u_{i-1}, \frac{1}{dt}v}_{\L} + b(u_i,v) - l(v)}{\LRp{\frac{1}{dt}\nor{v}_{\L}^2 + \nor{v}_V^2}^{\frac{1}{2}}}
+\]
+over a given mesh.  As $u_{i-1}\rightarrow u_{i}$, which we expect to happen as the pseudo-timestepping algorithm converges to steady state, the minimized functional becomes
+\[
+J(u_i) = \sup_{v\in V} \frac{b(u_i,v) - l(v)}{\LRp{\frac{1}{dt}\nor{v}_{\L}^2 + \nor{v}_V^2}^{\frac{1}{2}}}.
+\]
+While the transient portion of the residual disappears, a factor of $\frac{1}{dt}$ is still present in the test norm.\footnote{While the solution under smaller $dt$ appears to give visually higher quality results, we stress that simply adding the term $\frac{1}{dt}\nor{v}_{\L}$ to the test norm under the steady state version of the convection-diffusion equations does not achieve the same effect.
+We are able to add this term without negative consequence due to the inclusion of the $\frac{u_i}{dt}$ term present in the variational formulation (see Chapter~\secref{chap:robustDPG} and Appendix~\secref{appendix:timesteppingConfusion} for mathematical details).
+Numerical experiments indicate that including $\alpha\nor{v}_{\L}$ in the test norm, where $\alpha > \frac{1}{dt}$, converges much more slowly to a fine-mesh reference solution than if $\alpha = \frac{1}{dt}$.}  Thus, we can expect that the nature of the steady state solution achieved through convergence of the pseudo-time algorithm can depend on the timestep $dt$.
+We observe the same phenomena for analogous problems in compressible flow as well.
+
+\subsubsection{Adaptive time thresholding}
+
+Adaptive timestepping (also known as pseudo-transient continuation) has been implemented successfully for problems in compressible flow \cite{BenKirk}.
+Typical adaptive time-stepping schemes modify the time-step based on some notion of the transient residual $R_i$ at timestep $i$, such that
+\[
+dt_{i+k} = \LRp{\frac{R_{i+k}}{R_i}}^r dt_i,
+\]
+where $r > 1$ dictates the rate of change of the timestep based on residual reduction, and $k$ indicates an integer interval at which to modify the timestep.
+However, the minimum-residual nature of the DPG method and the ``moving target'' problem make the effectiveness of adaptive time-stepping schemes questionable.
+
+For our current experiments, we implement instead an adaptive time thresholding, where we adaptive decrease our convergence criterion based on the spatial energy error.
+Recall that, under convergence of the pseudo-timestepping algorithm, the DPG energy error converges to the measure of the nonlinear residual in the dual norm.
+We set convergence criterion for the pseudo-timestepping algorithm to be such that
+\[
+\nor{e_{\rm time}}_V < \max \{\epsilon_t,\epsilon_{t,k}\},
+\]
+where $\epsilon_{t,k}$ is the tolerance at the $k$th refinement iteration, and $\epsilon_t < \epsilon_{t,k}$ is an absolute tolerance.
+We initialize $\epsilon_{t,k}$ to $\epsilon_{t}$, then based on the energy error $\nor{u-u_h}_E$, we set
+\[
+\epsilon_{t,k} = \alpha_t \nor{u-u_h}_E.
+\]
+Since the linearized error at a single timestep is composed of a sum of the linearization error, transient residual, and nonlinear residual, if the transient residual and linearization error are small, we expect that the nonlinear residual at that point will be sufficient to be an effective error indicator with which to drive adaptive mesh refinement.
+In the following numerical experiments, $\alpha_t$ is set to $.01$.
+
+The aim of this adaptive thresholding is to relax the convergence criteria for solution of the nonlinear system at each refinement step such that the same refinement pattern is achieved with or without the use of adaptive time thresholding.
+Numerical experiments seem to indicate that the same refinement pattern is produced with or without the implementation of this simple adaptive thresholding scheme, though wall-clock convergence times under adaptive thresholding are faster.
+We hope to investigate both DPG-specific adaptive timestepping schemes and more advanced methods of balancing convergence criterion in the future.
+
+\subsection{Linear solver}
+
+A clear choice for a linear solver under the ultra-weak variational formulation is static condensation, or the Schur-complement method.
+Given a block matrix structure of a stiffness matrix $K$, we can view the DPG system as
+\[
+Ku = \arr{A}{B}{B^T}{D}\vecttwo{u_{\rm flux}}{u_{\rm field}} = \vecttwo{f}{g} = l
+\]
+where $D$ has a block-diagonal structure, and $A$ and $D$ are both square matrices with $\dim{A} < \dim{D}$.
+This is due to the fact that, for the ultra-weak variational formulation (and for all HDG methods), the interior field degrees of freedom can be condensed out to yield a problem posed solely in terms of the coupled flux and trace degrees of freedom.
+The system can be reduced to yield the condensed system
+\[
+\left(A-B D^{-1} B^T\right)u_{\rm flux} = f - B D^{-1} g
+\]
+where $D^{-1}$ can be inverted block-wise.
+Once the globally coupled flux and trace degrees of freedom are solved for, the field degrees of freedom can be reconstructed locally.
+An additional advantage of the above approach is that the Schur complement maintains the same sparsity pattern implied by the connectivity of the globally coupled flux and trace degrees of freedom.
+Since the condensation process can be done locally, we can save memory by avoiding constructing the full stiffness matrix.
+
+It has been shown that, unlike standard least-squares methods, DPG generates for the Poisson matrix a stiffness matrix with condition number $O(h^{-2})$ \cite{practicalDPG}.
+It is well known that, under standard finite element methods, if the condition number of the global stiffness matrix $K$ is $O(h^{-2})$, the condition number of the Schur complement is $O(h^{-1})$.
+Additionally, through either diagonal preconditioning or matrix equilibration, the condition number of the Schur complement can often be made significantly smaller than $O(h^{-1})$, and the positive-definiteness of the resulting system allows the use of iterative solvers in solving the condensed system.
+Initial experiments indicate that, at least for quasi-uniform and low-order meshes, both algebraic multigrid and preconditioned conjugate gradients are able to solve the condensed system fairly rapidly.
+We hope to experiment further with solvers for the condensed system, and to develop multigrid methods and preconditioners for adaptive and higher order meshes under DPG.
+
+\section{Test problems}
+
+We applied the DPG method to two test problems in compressible flow -- flow over a flate plate, and flow over a compression ramp.
+While the physics of both problems are fairly simple, they nonetheless display several features (shocks, singularities, boundary layers) that are computationally difficult to resolve without adaptivity.
+Furthermore, the problems themselves are not usually solved without the aid of artificial or numerical diffusion and/or shock-capturing terms, which we eschew in our application of DPG to these model problems.
+
+The numerical parameters used are as follows for:
+\begin{itemize}
+\item{DPG parameters:} $p = 2$ and $\Delta p = 2$ uniformly across the mesh. 
+\item{Adaptivity parameters:} Energy threshold for refinements is $\alpha = .4$ for the Carter flat plate example and $\alpha = .5$ for the Holden ramp example.  
+\item{Time-stepping parameters:} Initial timestep $\Delta t = .1$, and initial tolerance for transient residual $\epsilon_t = 1e-7$.
+\end{itemize}
+
+Numerical experiments were run on a small cluster with 16 CPUs and 8GB memory, as well as on the Lonestar machine at the Texas Advanced Computing Center (TACC), using a varying number of cores, from 48 to 120 depending on problem geometry and parameters.
+Elements were partitioned using the Zoltan library of Trilinos \cite{ZoltanOverviewArticle}, using either a Hilbert space-filling curve or the REFTREE \cite{REFTREE} algorithm.
+
 \subsection{Numerical experiments: Carter flat plate}
 
-For our solver, we use a standard pseudo-time solver and greedy refinement scheme.
-Though we have not yet implemented adaptive timestepping, we are able to take large enough uniform timesteps over a coarse mesh such that convergence occurs sufficiently quickly.
+The first problem of interest is the Carter flat plate problem\cite{Carter}.
+An infinitesmally thin flat plate disrupts a free stream flow, causing a shock to form at the tip of the plate, and a boundary layer forms and widens along the length of the plate.
 
-The numerical parameters used are as follows:
-\begin{itemize}
-\item{DPG parameters:} $p = 2$ and $\Delta p = 2$ uniformly across the mesh. 
-\item{Adaptivity parameters:} Energy threshold for refinements is $\alpha = .2$ or $\alpha = .15$. 
-\item{Time-stepping parameters:} $\Delta t = .1$, and tolerance for transient residual $\epsilon_t = 5e-7$.
-\end{itemize}
-
-Our problem of interest is the Carter flat plate problem. An infinitesmally thin flat plate disrupts a free stream flow and causes a shock to form at the tip of the plate.
-
-\begin{figure}[!h]
+\begin{figure}
 \centering
-\includegraphics[scale=.5]{figs/flat_plate_BCs.pdf}
+\includegraphics[scale=.7]{figs/flat_plate_BCs.pdf}
 \caption{Carter flat plate problem.}
@@
 
-\begin{itemize}
-\item \textbf{Inflow boundary conditions:} free stream conditions are applied here to all four fluxes $\widehat{f}_{i,n}$.
+\begin{enumerate}
 \item \textbf{Symmetry boundary conditions:} $u_n = q_n = \pd{u_s}{n} = 0$.
@@
 We impose the stress condition by noting that, for the flat plate geometry, if $u_2 = 0$, then at the top and bottom, with $n = (0,1)$, $\widehat{f}_{2,n} = \sigma_{12}$, and $\widehat{f}_{4,n} = q_2$ if $\sigma_{12}$ and $u_2 = 0$.
+They are applied here to the bottom free-stream boundary.
 \item \textbf{Flat plate boundary conditions:} $u_1 = u_2 = 0$, and $T = T_w = \left[1+(\gamma-1)M_\infty^2/2\right] T_\infty = 2.8T_\infty$ (for Mach 3 flow).
 We impose these strongly on the trace variables $\widehat{u}_1, \widehat{u}_2, \widehat{T}$.
+\item \textbf{Symmetry boundary conditions} are applied also to the top free-stream boundary.
+\item \textbf{Inflow boundary conditions:} free stream conditions are applied here to all four fluxes $\widehat{f}_{i,n}$.
 \item \textbf{Outflow boundary conditions:} the exact boundary conditions to enforce here are not universally agreed on.
@@
 A mathematical analysis and explanation of this boundary condition for standard $H^1$ elements is given in \cite{FLD:FLD505}.
-
 %An alternative boundary condition would be as follows: since $u_1$ and $u_2$ are not expected to be zero at these points, we can set $\widehat{f}_{2,n}$ and $\widehat{f}_{4,n}$ to their represented quantities using either the field variables from the background flow, or (in the case of pseudo-time stepping) the previous timestep's flux and field quantities.
-
-\end{itemize}
+\end{enumerate}
 
@@
 \[
-\rho = 1,\qquad u_1= 1,\qquad u_2 = 0, \qquad T = 1
+\rho = 1,\qquad u_1= 1,\qquad u_2 = 0, \qquad T = 1%\frac{1}{\gamma(\gamma-1){\rm Ma}^2}
 \]
-which is consistent with what was done in Demkowicz and Oden in \cite{Demkowicz:1990:NFE:112271.112276}. Stresses are set uniformly to zero.
+which, we also take as the freestream values for the above variables, and is consistent with what was done by Demkowicz, Oden, and Rachowicz in \cite{Demkowicz1990275}.
+Stresses are set uniformly to zero.
+We take the computational domain to be $\Omega = [0,2]\times[0,1]$.
+Under Dirichlet wall boundary conditions for all 3 traces $u_1$, $u_2$, and $T$, the solution develops a singularity in the density $\rho$ at the plate beginning, and both $T$ and $u_1$ form a boundary layer along the leading edge of the plate.
 
-We take the computational domain to be $\Omega = [0,2]\times[0,1]$.
-We begin with a mesh of 8 by 16 elements.
-Under Dirichlet wall boundary conditions for all 3 traces $u_1$, $u_2$, and $T$, the solution develops a singularity in the density $\rho$ at the plate beginning, and both $T$ and $u_1$ form a boundary layer along the leading edge of the plate.
-Due to the presence of the singularity, the solution for $\rho$ is scaled such that the features of the solution away from the singularity are visible in Figure~\ref{fig:rhoScaled}.
-
-\begin{figure}[!h]
+\begin{figure}
 \centering
-\subfigure[$\rho$]{\includegraphics[scale=.21]{figs/Re1000p2/rhoUnscaled.png}}
-\subfigure[$u_1$]{\includegraphics[scale=.21]{figs/Re1000p2/u1.png}}
-\subfigure[$u_2$]{\includegraphics[scale=.21]{figs/Re1000p2/u2.png}}
-\subfigure[$T$]{\includegraphics[scale=.21]{figs/Re1000p2/T.png}}
-\caption{Solutions after seven refinements for $p=2$ and $\Reyn = 1000$.}
-\label{fig:Re500}
+\subfigure[$T$]{\includegraphics[scale=.3]{figs/propMovie/T0.png}}
+\subfigure[$u_1$]{\includegraphics[scale=.3]{figs/propMovie/u0.png}}
+\caption{Converged solution on 2 cells.}
+\label{fig:Re1000_2cells}
 \end{figure}
 
-\begin{figure}[!h]
+We perform 10 steps of adaptive mesh refinement, beginning with a mesh of only two square elements.
+The solution on this coarsest mesh is given in Figure~\ref{fig:Re1000_2cells}, and the final solutions after 10 refinement steps are given in Figure~\ref{fig:Re1000}.
+For this specific example, we use only isotropic refinements.
+
+Typical coarse meshes for adaptive CFD computations aim to resolve, at least to some degree, the features of the solution; often, physical features such as high gradients are used to drive refinement.
+For feature-based adaptivity to be effective, coarse mesh solutions must be of sufficiently high quality to resolve basic solution features.
+Often, artificial diffusion and shock capturing must also be applied in order to produce visually clean solutions on underresolved meshes.
+In contrast to this, the residual-based approach of DPG is able to place refinements accurately and efficiently despite the underresolution of solution features.
+
+\begin{figure}
 \centering
-\subfigure[$\rho$]{\includegraphics[scale=.25]{figs/Re1000p2/rhoScaled.png}}
-\subfigure[Mesh]{\includegraphics[scale=.57]{figs/Re1000p2/mesh6.png}}
-\caption{Rescaled solution for $\rho$ in the range $[0,3]$ and adaptive mesh after seven refinements.}
+\subfigure[$\rho$]{\includegraphics[width=2.8in]{figs/FlowFigs/PlateFigFiles/Re3/rho.png}}
+\subfigure[$u_1$]{\includegraphics[width=2.8in]{figs/FlowFigs/PlateFigFiles/Re3/u1.png}}
+\subfigure[$u_2$]{\includegraphics[width=2.8in]{figs/FlowFigs/PlateFigFiles/Re3/u2.png}}
+\subfigure[$T$]{\includegraphics[width=2.8in]{figs/FlowFigs/PlateFigFiles/Re3/T.png}}
+\caption{Solutions after twelve refinements for $p=2$ and $\Reyn = 1000$, starting from a mesh of 2 elements.}
+\label{fig:Re1000}
+\end{figure}
+
+Figure~\ref{fig:Re1000_midRefs} shows snapshots of the third and sixth steps of adaptive mesh refinement.
+The main contribution to energy error is at the plate tip -- due to the change in boundary condition across the point $(.5,0)$, the viscous stresses are singular at this point (this is analogous to the convection-diffusion plate example given in Section~\secref{sec:confusionPlate}).
+Underresolution of the stresses at this point results in some pollution effects slightly upstream of the beginning of the plate; however, once $h\approx {\rm Re}^{-1}$ near the plate edge, these pollution effects disappear.
+We observe numerically that decreasing $dt$ also limits how far upstream of the plate edge this pollution effect travels.
+
+\begin{figure}
+\centering
+\subfigure[Mesh, 4th refinement]{\includegraphics[width=2.85in]{figs/FlowFigs/PlateFigFiles/Re3/mesh4.png}}
+\subfigure[$T$, 4th refinement]{\includegraphics[width=2.85in]{figs/FlowFigs/PlateFigFiles/Re3/T4.png}}
+\subfigure[Mesh, 8th refinement]{\includegraphics[width=2.85in]{figs/FlowFigs/PlateFigFiles/Re3/mesh8.png}}
+\subfigure[$T$, 8th refinement]{\includegraphics[width=2.85in]{figs/FlowFigs/PlateFigFiles/Re3/T8.png}}
+\caption{Snapshots of adaptive meshes and solutions for two different steps of adaptivity $\Reyn = 1000$.}
+\label{fig:Re1000_midRefs}
+\end{figure}
+
+We observe numerically that $\rho$ also behaves singularly at the plate tip -- due to the presence of this strong singularity, the coloring of the wide range of values for $\rho$ in Figure~\ref{fig:Re1000} causes the solution to appears largely uniform, save for a flare up at the tip of the plate.
+To better visualize density, $\rho$ is rescaled such that the features of the solution away from the singularity, as well as the final mesh after 10 refinement steps, are visible in Figure~\ref{fig:rhoScaled}.
+
+\begin{figure}
+\centering
+\subfigure[$\rho$]{\includegraphics[width=2.8in]{figs/FlowFigs/PlateFigFiles/Re3/rhoRescaled.png}}
+\subfigure[Mesh]{\includegraphics[width=2.8in]{figs/FlowFigs/PlateFigFiles/Re3/mesh12.png}}
+\caption{Rescaled solution for $\rho$ in the range $[\rho_{\min},2]$ and adaptive mesh after 12 refinement steps.}
 \label{fig:rhoScaled}
@@
 
-\begin{figure}[!h]
+We can also zoom in on the plate tip to view the solution quality at the singular point.
+Figure~\ref{fig:Re1000_zoom} demonstrates that the solution remains smooth and well-resolved at the plate tip, despite the presence of a singularity in the viscous stresses.%, and the fact that high order methods do not tend to resolve singularities as efficiently as low order methods \cite{hp1}.\cite{Optimal $hp$-adaptive strategies for elliptic problems with singularities result in meshes of lowest
+
+\begin{figure}
 \centering
-\subfigure[$\rho$]{\includegraphics[scale=.23]{figs/Re1000p2/rhoUnscaledzoom.png}}
-\subfigure[$u_1$]{\includegraphics[scale=.23]{figs/Re1000p2/u1zoom.png}}
-\subfigure[$u_2$]{\includegraphics[scale=.23]{figs/Re1000p2/u2zoom.png}}
-\subfigure[$T$]{\includegraphics[scale=.23]{figs/Re1000p2/Tzoom.png}}
+\subfigure[$\rho$]{\includegraphics[scale=.23]{figs/FlowFigs/PlateFigFiles/Re3/rhoZoom.png}}
+\subfigure[$u_1$]{\includegraphics[scale=.23]{figs/FlowFigs/PlateFigFiles/Re3/u1Zoom.png}}
+\subfigure[$u_2$]{\includegraphics[scale=.23]{figs/FlowFigs/PlateFigFiles/Re3/u2Zoom.png}}
+\subfigure[$T$]{\includegraphics[scale=.23]{figs/FlowFigs/PlateFigFiles/Re3/TZoom.png}}
 \caption{Zoom of solutions at the beginning of the plate for $p=2$ and $\Reyn = 1000$.}
+\label{fig:Re1000_zoom} 
 \end{figure}
 
-\begin{figure}[!h]
+We increased the Reynolds number to $10,000$ to assess the behavior of DPG for higher Reynolds numbers.
+However, we found it necessary to modify the method in several ways in order to achieve satisfactory results.
+
+First, we implemented a line search algorithm to enforce positivity of both temperature and density, which are physically defined to be positive quantities.
+Given updates $\triangle \rho$ and $\triangle T$, we update our previous solution by setting
+\begin{align*}
+\rho \coloneqq \rho + \alpha_{\rm line}\triangle \rho \\
+T \coloneqq T + \alpha_{\rm line}\triangle T,
+\end{align*}
+where $\alpha_{\rm line}$ is chosen, for some $\delta > 0$, such that
+\begin{align*}
+\rho + \alpha_{\rm line}\triangle \rho - \delta = 0\\
+T + \alpha_{\rm line}\triangle T  - \delta = 0.
+\end{align*}
+Since the addition of a line search can slow the convergence of a nonlinear algorithm, we incorporate also a Newton iteration at each timestep to effectively solve the nonlinear system at each timestep.
+We consider $\nor{\triangle U}_E < \epsilon_{\rm Newton}$ to be our condition for convergence of the Newton iteration, though we also limit the number of allowed Newton steps for computational efficiency.
+The full solver algorithm is given in Algorithm~\ref{fig:algorithm}.
+\begin{algorithm}                      % enter the algorithm environment
+\caption{Calculate $y = x^n$}          % give the algorithm a caption
+\label{alg1}                           % and a label for \ref{} commands later in the document
+\begin{algorithmic}                    % enter the algorithmic environment
+\FOR{ number of refinement steps } 
+    \WHILE{ $R_{\rm time} > \epsilon_t$}
+        \STATE k = 0
+        \WHILE{$\nor{\triangle U}_E > \epsilon_{\rm Newton}$ and $k <$ maximum Newton steps}
+            \STATE Solve for $\triangle U$, determine $\alpha_{\rm line}$.  
+            \STATE $U \coloneqq U + \alpha_{\rm line}\triangle U$.  
+            \STATE k = k+1
+        \ENDWHILE
+        \STATE Increment timestep.  
+    \ENDWHILE
+    \STATE Compute energy error and refine based on a greedy refinement algorithm.
+    \STATE Set $\epsilon_t = \alpha_t \nor{u-u_h}_E$.    
+\ENDFOR
+\end{algorithmic}
+\caption{Pseudo-timetepping adaptive algorithm with line search.}
+\label{fig:algorithm}
+\end{algorithm}
+For higher Reynolds numbers and highly refined meshes, the solution update exhibits large oscillations, such that the solution at a timestep can become negative, under which the pseudo-timestepping algorithm can stall or even diverge\footnote{We note that these large oscillations mimic experiences in 1D as well, where the linearized solution was shown to exhibit sharp gradients near shocks that did not disappear, even with additional mesh refinement, indicating that the presence of such overshoots and undershoots is a consequence of the linearization, as opposed to the stability of the discretization \cite{NS_DPG1D}.
+This is discussed in more detail in Section~\secref{sec:oscillations}.
+
+We note also that theory developed in Chapter~\secref{chap:robustDPG} for the convection-diffusion problem assumes a smooth convection field.
+However, under linearization of the Burgers' and Navier-Stokes equations, the solution around which we linearize dictates the convection field, and can display large gradients.
+While we have not observed issues in the Burgers' equation related to this, we hope to revisit the analysis done in Chapter~\secref{chap:robustDPG} and generalize it for convection fields with large gradients.}.
+However, we have observed that requiring a strictly positive solution appears to be too restrictive a constraint for some meshes; the use of line search does not appear to be necessary for convergence of the pseudo-timestepping algorithm on coarser meshes (until the 10th refinement iteration, or $h< .001$).
+
+Finally, we implement an ``effective'' CFL number; though implicit time integration schemes are unconditionally stable (compared to explicit schemes), a CFL condition relating the size of the time increment to the (minimum) mesh size is often still used in practice to improve convergence speed and stability of the numerical scheme \cite{Shakib1991141}.
+Our CFL number is chosen to be 64.
+We note that this CFL number is implemented for non-standard reasons.
+In fact, DPG is able to solve the steady-state system directly without the use of pseudo-timestepping (direct Newton iteration).
+However, as noted previously, the size of the timestep under which pseudo-timestepping converges greatly affects the qualitative nature of the solution.
+Figure~\ref{fig:dtCompare} demonstrates the difference between convergence at large and small timesteps -- for $dt$ large relative to the mesh size, the solution experiences upstream ``pollution'' effects.
+\begin{figure}
 \centering
-\includegraphics[scale=.45]{figs/Re1000p2/heatflux.png}
-\caption{Heat flux at the bottom boundary.}
+\subfigure[$dt = \infty$ (Direct Newton)]{\includegraphics[width=2.8in]{figs/FlowFigs/dtComparison/dtInf.png}}
+\subfigure[$dt = 1.0$]{\includegraphics[width=2.8in]{figs/FlowFigs/dtComparison/dtOne.png}}
+\subfigure[$dt = .1$]{\includegraphics[width=2.8in]{figs/FlowFigs/dtComparison/dtTenth.png}}
+\caption{Steady state solutions for ${\rm Re} = 10,000$ under three different timesteps on a $16\times 8$ uniform mesh.}
+\label{fig:dtCompare}
 \end{figure}
+Due to the upstream ``pollution'' present in the solution for $dt \geq 1$, the adaptive mesh refinement algorithm tends to add extraneous refinements on elements adjacent to the boundary $y = 0$, $x\in (0,1)$.
+Decreasing the timestep alleviates this issue somewhat; however, an overly small timestep requires a large number of iterations to converge.
+The implementation of an effective CFL number aims to balance the size of the timestep with the mesh size.\footnote{An additional reason for the implementation of an effective CFL number is the conditioning of the local problem, which was discussed for the convection-dominated diffusion problem in \cite{DPG3}.
+The main problem concerning conditioning of local problems is the way that different test terms behave as a function of local element size.
+We illustrate this using the element Sobolev norm $\nor{v}_{H^1(K)} = \nor{v}_{\L} + \nor{\grad v}_{\L}$ -- $\nor{v}_{\L} = O(h^2)$ (where $h$ is the element size), while $\nor{\grad v}_{\L} = O(1)$.
+Thus, as $h\rightarrow 0$, the Sobolev norm over a single element approaches the Sobolev seminorm and loses positive definiteness, resulting in a highly ill-conditioned system to solve.
+The addition of a first-order pseudo-timestepping term allows us to increase the relative magnitude of $\nor{v}_{\L}$ with respect to $\nor{\grad v}_{\L}$ and avoid conditioning issues while maintaining robustness of the method (see Appendix~\secref{appendix:timesteppingConfusion} for the proof of robustness).}
+
+We note that, even with all of the above modifications, the pseudo-timetepping adaptive algorithm with line search would sometimes failed to converge below $\epsilon_t$ for ${\rm Re} \geq 10,000$.
+Figure~\ref{fig:nonconvergence} shows a plot of the transient residual after the 14th refinement step; while the residual initially decreases, it stalls at about $R_{\rm time} \approx 10^{-4}$.
+\begin{figure}
+\centering
+\subfigure[Non-convergence]{\includegraphics[width=2.5in]{figs/FlowFigs/PlateFigFiles/oscillations1.eps}}
+\subfigure[Recovery of convergence]{\includegraphics[width=2.5in]{figs/FlowFigs/PlateFigFiles/oscillations2.eps}}
+\caption{Stalling and recovery of the pseudo-timestep iteration for $\Reyn = 10000$.}
+\label{fig:nonconvergence}
+\end{figure}
+An examination of the difference in the solutions between the final and $125$th timesteps shows that the nonconvergence of the transient residual is due to oscillations in the solution (primarily in $\rho$) slightly upstream to the plate edge.
+Visually, the solution converges everywhere else, save for this area.
+Such behavior is also observed in \cite{BenKirk}, where, at the change in boundary conditions between the free stream and flat plate, an oscillation was observed in the solution which prevented convergence of his pseudo-time algorithm.
+His oscillations are of smaller magnitude ($O\LRp{10^{-6}}$ as opposed to $O\LRp{10^{-4}}$), which may be the result of several differences between the methods presented.\footnote{Apart from the use of a standard Galerkin (continuous as opposed to discontinuous Galerkin) formulation, Kirk's approach differed from ours in the use of linear elements and the addition of artificial diffusion shock-capturing terms, both of which could explain the lower point at which error stagnates.
+Reasons for this loss of convergence in the pre-asymptotic range should be explored further.}  However, we note that, under additional refinements and increased resolution of the solution, the transient residual once again decreases in a smooth monotonic fashion, as shown in Figure~\ref{fig:nonconvergence}.
+
+\begin{figure}
+\centering
+\subfigure[$\rho$]{\includegraphics[width=2.8in]{figs/FlowFigs/PlateFigFiles/Re4/rho.png}}
+\subfigure[$u_1$]{\includegraphics[width=2.8in]{figs/FlowFigs/PlateFigFiles/Re4/u1.png}}
+\subfigure[$u_2$]{\includegraphics[width=2.8in]{figs/FlowFigs/PlateFigFiles/Re4/u2.png}}
+\subfigure[$T$]{\includegraphics[width=2.8in]{figs/FlowFigs/PlateFigFiles/Re4/T.png}}
+\caption{Solutions after 18 refinements for $p=2$ and $\Reyn = 10000$.}
+\label{fig:Re10000}
+\end{figure}
+
+For additional computational efficiency, we also implemented an anisotropic refinement scheme.
+In 2D, the boundary layer is a primarily 1D phenomena, which we expect to be far better resolved by anisotropic refinement than by isotropic refinement.
+We experimented first using the scheme described in Section~\secref{sec:aniso} as an anisotropy indicator; however, the anisotropic scheme appeared to be too conservative near the boundary layer, placing primarily isotropic refinements.
+We modified our scheme in two ways -- first, we incorporated spatially variable thresholding.
+Typically, anisotropic refinement in the $x$ direction is chosen if $e_{x,K} > \epsilon_r e_{y,K}$ (and vice versa for anisotropic refinement in the $y$-direction), where $e_{x_i,K}$ is the error in the $x_i$ direction.
+We set $\epsilon_r = \epsilon_{r,K}$; in other words, we allow our anisotropic threshold to vary element-by-element, and decrease it from $\epsilon_r= 10$ to $\epsilon_{r,K} = 2.5$ for elements adjacent to the wall upon which the boundary layer forms.
+Additionally, since the boundary layer typically displays rapid variation in the $y$-direction (the direction orthogonal to the wall), we relax the condition under which a vertically cut anisotropic refinement occurs to
+\[
+2 e_{y,K} > \epsilon_{r,K} e_{x,K}.
+\]
+Despite the artificial modification of the anisotropic refinement scheme, the resulting meshes still resolve boundary layer solutions more efficiently than isotropic refinements.
+We hope to investigate reasons for the ineffectiveness of the pure anisotropic scheme for the compressible Navier-Stokes equations in future research.
+
+\begin{figure}
+\centering
+\subfigure[$\rho$]{\includegraphics[width=2.8in]{figs/FlowFigs/PlateFigFiles/Re4/rhoRescaled.png}}
+\subfigure[Mesh]{\includegraphics[width=2.8in]{figs/FlowFigs/PlateFigFiles/Re4/mesh.png}}
+\caption{Rescaled solution for $\rho$ in the range $[\rho_{\min},2]$ and adapted mesh.}
+\label{fig:rhoScaled}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[$\rho$]{\includegraphics[width=2.8in]{figs/FlowFigs/PlateFigFiles/Re4/rhoZoom.png}}
+\subfigure[$u_1$]{\includegraphics[width=2.8in]{figs/FlowFigs/PlateFigFiles/Re4/u1Zoom.png}}
+\subfigure[$u_2$]{\includegraphics[width=2.8in]{figs/FlowFigs/PlateFigFiles/Re4/u2Zoom.png}}
+\subfigure[$T$]{\includegraphics[width=2.8in]{figs/FlowFigs/PlateFigFiles/Re4/TZoom.png}}
+\caption{Zoom of solutions at the beginning of the plate for $p=2$ and $\Reyn = 10000$.}
+\label{fig:Re1e4Zoom}
+\end{figure}
+
+We note that the resolution of the solution near the plate edge in Figure~\ref{fig:Re1e4Zoom} for Reynolds number 10000 is qualitatively rougher than that for Reynolds 1000 in Figure~\ref{fig:Re1000_zoom}; this is due to the greedy refinement algorithm emphasizing refinements most strongly at the singular point and not in shock resolution, as well as the fact that at a higher Reynolds number, the shock width is thinner and more difficult to resolve.
+Further refinement steps improve resolution of the shock features.
+
+%\begin{figure}[!h]
+%\centering
+%\subfigure[${\rm Re} = 1000$]{\includegraphics[scale=.5]{figs/Re1000p2/heatflux.png}}
+%\subfigure[${\rm Re} = 10000$]{\includegraphics[scale=.3]{figs/Re1e5/q2line.png}}
+%\caption{Heat flux at the bottom boundary.}
+%\end{figure}
+
+\subsection{Holden ramp problem}
+
+Our second problem is a modified version of the Holden ramp problem, which models supersonic/hypersonic flow over a compression corner (the geometry of which is given in Figure~\ref{fig:holdenCartoon}).
+Similarly to the Carter flat plate problem, a flat plate disrupts the flow and forms a weak shock at the plate tip due to viscous effects and no-slip boundary conditions.
+The boundary layer grows down the plate edge, deflecting upwards due to the presence of the compression corner.
+A stronger shock forms slightly upstream of the compression corner in order to deflect the incoming supersonic flow, and is a common test problem for adaptive finite element methods for compressible flow \cite{Rachowicz1997231,Barter,BenKirk}.
+
+\begin{figure}
+\centering
+\includegraphics[width=4in]{figs/holden.eps}
+\caption{A modification of the Holden ramp/compression corner problem.}
+\label{fig:holdenCartoon}
+\end{figure}
+
+The original plate length is given to be .442, while the ramp length is given to be .269.
+We have modified the problem slightly in order to exactly represent the boundary conditions on a coarse mesh while keeping the ratio of plate length to ramp length roughly the same.
+Similarly to the Carter flat plate, we start out with a very coarse $2 \times 3$ mesh of 6 elements.
+We initialize our solution to the freestream values
+\[
+\rho_{\infty} = 1,\qquad u_{1,\infty}= 1,\qquad u_{2,\infty} = 0, \qquad T_{\infty} = 1
+\]
+and again set stresses uniformly to zero.
+
+\begin{figure}
+\centering
+\subfigure[$\rho$ rescaled]{\includegraphics[width = 2.9in]{figs/FlowFigs/RampFigFiles/Ma6Re4/rhoRescaled.png}}
+\subfigure[$u_1$]{\includegraphics[width = 2.9in]{figs/FlowFigs/RampFigFiles/Ma6Re4/u1.png}}
+\subfigure[$u_2$]{\includegraphics[width = 2.9in]{figs/FlowFigs/RampFigFiles/Ma6Re4/u2.png}}
+\subfigure[$T$]{\includegraphics[width = 2.9in]{figs/FlowFigs/RampFigFiles/Ma6Re4/T.png}}
+\subfigure[Mesh after 24 refinements]{\includegraphics[width = 5.5in]{figs/FlowFigs/RampFigFiles/Ma6Re4/mesh.png}}
+\caption{Solutions and adaptive mesh for ${\rm Ma} = 6$ and $\Reyn = 10000$.}
+\label{fig:holdenMa6}
+\end{figure}
+
+We first solve under Mach 6 flow\footnote{The increase in Mach number is to change the angle of the shock; under the current setup, Mach 3 flow produced a shock which reflected off the top boundary $y = 1$.
+We note that the effect of Mach number under our nondimensionalization of choice is to decrease the thermal diffusivity constant $\kappa$ relative to the viscosities $\mu$ and $\lambda$.} and Reynolds number of 10,000, or a Reynolds number of 33,936 if measured with respect to the original plate length of .442.
+The wall temperature is set to $T_{w} = 2.8T_{\infty}$, identically to the flat plate problem.
+24 mesh refinements were performed, resulting in a final mesh of 1858 elements.
+Figure~\ref{fig:holdenMa6} shows both solution values and final adaptive mesh.
+Due to a large maximum value of $\rho_{\max} = 14.1538$ at the plate tip, the resulting solution for $\rho$ is scaled to better show qualitative features of the flow.
+The presence of the second shock deflecting the incoming supersonic flow at the ramp is clearly seen in both the solutions and the adaptive mesh refinements.
+
+\begin{figure}
+\centering
+\subfigure[Initial mesh]{\includegraphics[width = 2.9in]{figs/FlowFigs/RampFigFiles/mesh0.png}}
+\subfigure[6 refinements]{\includegraphics[width = 2.9in]{figs/FlowFigs/RampFigFiles/mesh6.png}}
+\subfigure[12 refinements]{\includegraphics[width = 2.9in]{figs/FlowFigs/RampFigFiles/mesh12.png}}
+\subfigure[18 refinements]{\includegraphics[width = 2.9in]{figs/FlowFigs/RampFigFiles/mesh18.png}}
+\caption{Sequence of adaptive meshes for ${\rm Ma} = 6$ and $\Reyn = 10000$.}
+\label{fig:holdenMa6Meshes}
+\end{figure}
+
+We can examine the sequence of adaptive meshes generated by the DPG method.
+Figure~\ref{fig:holdenMa6Meshes} shows the initial mesh, as well as the 6th, 12th, and 18th subsequent refinements generated automatically by the DPG method.
+Unlike the previous sequence of meshes generated by the flat plate example, refinements tend to be placed most heavily near the shock at the outflow ramp.
+By the 18th refinement, the adaptive mesh looks qualitatively very similar to the final mesh of 24 refinements, and further refinements focus on the resolution of the shocks originating at the plate edge and at the ramp outflow.
+
+\begin{figure}
+\centering
+\subfigure[$\rho$ rescaled]{\includegraphics[width = 2.9in]{figs/FlowFigs/RampFigFiles/Ma6Re4/rhoRescaledshock.png}}
+\subfigure[$T$]{\includegraphics[width = 2.9in]{figs/FlowFigs/RampFigFiles/Ma6Re4/Tshock.png}}
+\subfigure[Mesh]{\includegraphics[width = 4in]{figs/FlowFigs/RampFigFiles/Ma6Re4/shockMesh.png}}
+\caption{Zoom of solutions and adaptive mesh around shock. }
+\label{fig:holdenMa6Zoom}
+\end{figure}
+
+Figure~\ref{fig:holdenMa6Zoom} shows a zoom of the second stronger shock that develops near the ramp outflow.
+Refinements are placed very heavily near the shock, which we expect due to the fact that a shock forms a stronger gradient than a boundary layer.
+We note that our residual-driven adaptivity scheme places mesh refinements in a very precise manner; refinements on ramp boundary are placed slightly more heavily upstream than downstream.
+We believe this is due to the fact that solution gradients are slightly higher in $\rho$ at the upstream section of the ramp.
+
+\begin{figure}
+\centering
+\subfigure[$\rho$ rescaled]{\includegraphics[width = 2.9in]{figs/FlowFigs/RampFigFiles/Ma11Re4/rhoRescaled.png}}
+\subfigure[$u_1$]{\includegraphics[width = 2.9in]{figs/FlowFigs/RampFigFiles/Ma11Re4/u1.png}}
+\subfigure[$u_2$]{\includegraphics[width = 2.9in]{figs/FlowFigs/RampFigFiles/Ma11Re4/u2.png}}
+\subfigure[$T$]{\includegraphics[width = 2.9in]{figs/FlowFigs/RampFigFiles/Ma11Re4/T.png}}
+\subfigure[Mesh]{\includegraphics[width = 5.5in]{figs/FlowFigs/RampFigFiles/Ma11Re4/mesh.png}}
+\caption{Solutions and adaptive mesh for ${\rm Ma} = 11.68$ and $\Reyn = 16442.4$.}
+\label{fig:holdenMa11}
+\end{figure}
+
+The second set of conditions under which we solve are under Mach 11.68 flow and Reynolds number of 16,4	42.4, or 55,800 if measured with respect to original plate length, with the wall temperature set to $T_{w} = 4.6T_{\infty}$.
+24 automatic mesh refinements are performed under an energy threshold of $.5$, resulting in a final mesh of 2385 elements.
+
+Figure~\ref{fig:holdenMa11} shows the resulting solution and final adaptive mesh.
+The increased Mach number changes again the angle of the weak shock resulting from the change in boundary conditions at the plate edge.
+Compared to the previous case of Mach 6 flow, where only 18 refinements steps were performed, 24 refinements were performed for the Mach 11.68 case, leading to a more highly resolved solution, especially near the plate tip.
+Due to a large maximum value of $\rho_{\max} = 50.1805$ at the plate tip, the resulting solution for $\rho$ is scaled to better show qualitative features of the flow.
+
+%We note that, under a higher Mach number, the placement of adaptive mesh refinements appears to improve.
+The element size adjacent to the plate tip for the Mach $6$ case is $h = O\LRp{10^{-4}}$, while the size of elements adjacent to the plate tip in the Mach 11 case is $h = O\LRp{10^{-5}}$.
+For the Mach $6$ and Reynolds $10,000$ case of the ramp problem, several extraneous refinements were placed slightly upstream of the plate tip, corresponding to the location of large gradients in the Newton solution update.
+More study is necessary to determine the reasons for the difference in behavior of the automatic adaptivity algorithm.
+%
+%\begin{figure}[!h]
+%\centering
+%%\subfigure[$\rho$]{\includegraphics[width = 2.9in]{figs/FlowFigs/RampFigFiles/Ma11Re4/rhoshock.png}}
+%%\subfigure[$T$]{\includegraphics[width = 2.9in]{figs/FlowFigs/RampFigFiles/Ma11Re4/Tshock.png}}
+%\subfigure[Mach 6]{\includegraphics[width = 2.75in]{figs/FlowFigs/RampFigFiles/Ma6Re4/plateMesh.png}}
+%\subfigure[Mach 11]{\includegraphics[width = 2.75in]{figs/FlowFigs/RampFigFiles/Ma11Re4/plateMesh.png}}
+%\caption{Zoom of solutions and adaptive mesh around the plate tip.}
+%\label{fig:plateComparison}
+%\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[$\rho$ rescaled]{\includegraphics[width = 2.9in]{figs/FlowFigs/RampFigFiles/Ma11Re4/rhoshock.png}}
+\subfigure[$T$]{\includegraphics[width = 2.9in]{figs/FlowFigs/RampFigFiles/Ma11Re4/Tshock.png}}
+\subfigure[Mesh]{\includegraphics[width = 4in]{figs/FlowFigs/RampFigFiles/Ma11Re4/shockMesh.png}}
+\caption{Zoom of solutions and adaptive mesh around shock. }
+\label{fig:holdenMa11Zoom}
+\end{figure}
+
+Compared to the Mach 6 case, where 18 refinements were performed, the resolution of the mesh near the shock at the ramp outflow for Mach 11.68 flow and 18 refinements is qualitatively similar.
+Further refinement steps increase resolution of the mesh near the shock, as shown in Figure~\ref{fig:holdenMa11Zoom}.
+
+Finally, we plot the normal heat flux over the plate and ramp for both Holden problems in Figure~\ref{fig:heatFlux}.
+The normal heat flux over the flat plate is indicated by the blue line, while the dotted brown line indicates the heat flux over the ramp, and both are plotted against the x-coordinate along the plate/ramp boundary.
+The normal heat flux is given by the normal trace of the conserved quantity in the energy equation
+\[
+\widehat{f}_{4,n} = (\rho e+p)u_n - \boldsymbol n\cdot \boldsymbol \sigma\cdot \boldsymbol u + q_n.
+\]
+Recognizing that $u_1 = u_2 = 0$ reduces the above to $\widehat{f}_{4,n} = q_n$.
+
+The heat flux develops a strong singularity at the point $(-.5,0)$, where the boundary condition changes from a Neumann/stress boundary condition to a Dirichlet/no-slip boundary condition.\footnote{Figure~\ref{fig:heatFlux} cuts off this singularity in order to show the qualitative behavior of $q_n$ over the remainder of the boundary.
+The maximum visualized values in the singular portion of $q_n$ are .35 for Mach 6 flow and 1.268 for Mach 11.68 flow.}  Section~\secref{sec:confusionPlate} proves that the Laplace equation develops a singularity in stress at under any such change in boundary conditions, and the same phenomena is observed for a similar setup under the convection-diffusion equation (see also \cite{localConservationDPG}).
+
+\begin{figure}
+\centering
+\subfigure[Mach 6, Reynolds 10,000]{\includegraphics[width=2.9in]{figs/FlowFigs/RampFigFiles/Ma6Re4/heatFlux.png}}
+\subfigure[Mach 11.68, Reynolds 16,442.4]{\includegraphics[width=2.9in]{figs/FlowFigs/RampFigFiles/Ma11Re4/heatFlux.png}}
+\caption{Normal heat flux $q_n$ over plate and ramp for the Holden problem.  The blue line indicates $q_n$ over the flat plate, while the brown line indicates $q_n$ over the ramp. }
+\label{fig:heatFlux}
+\end{figure}
+
+\subsection{Higher Reynolds numbers}
+\seclab{sec:oscillations}
+For higher Reynolds number, the pseudo-timestepping, we have encountered difficulties which have made it difficult to converge to a steady-state solution, even under the addition of an effective CFL number and line search to enforce positivity of density $\rho$ and temperature $T$.
+However, we believe these difficulties to be related to the nature of the equations, rather than the robustness of the method.
+We illustrate this with a simple example.
+
+Let us consider the 1D steady state viscous Burgers' equation on $[-\infty,\infty]$
+\[
+u\pd{u}{x} - \epsilon \pdd{u}{x} = 0.
+\]
+The exact solution to this equation under boundary conditions
+\begin{align*}
+u(-\infty) &= 1\\
+u(\infty) &= -1
+\end{align*}
+can be easily derived (see \cite{Barter} for a simple derivation), and the solution and its first two derivatives are
+\[
+u(x) = \frac{1-e^{\frac{x}{\epsilon}}}{1+e^\frac{x}{\epsilon}}, \qquad u'(x) = \frac{-2e^{\frac{x}{\epsilon}}}{\LRp{1+e^{\frac{x}{\epsilon}}}^2\epsilon}, \qquad u''(x) = \frac{-2e^{\frac{x}{\epsilon}}\LRp{e^{\frac{x}{\epsilon}}-1}}{\LRp{1+e^{\frac{x}{\epsilon}}}^3\epsilon^2}
+\]
+\begin{figure}
+\centering
+\subfigure[$u(x)$]{\includegraphics[width = 1.8in]{figs/Burgers1DPlots/u.eps}}
+\subfigure[$u'(x)$]{\includegraphics[width = 1.8in]{figs/Burgers1DPlots/du.eps}}
+\subfigure[$u''(x)$]{\includegraphics[width = 1.8in]{figs/Burgers1DPlots/ddu.eps}}
+\caption{$u(x)$ and its derivative and second derivative for $\epsilon = .01$.}
+\label{fig:burgersSoln100}
+\end{figure} 
+Figure~\ref{fig:burgersSoln100} shows each of these functions for $\epsilon = .01$.
+From the form of $u'(x)$ and $u''(x)$, we know these oscillations will grow rapidly as $\epsilon$ decreases.
+Consider now the linearized Burgers' equation
+\[
+\pd{u\Delta u}{x} - \epsilon \pdd{\Delta u}{x} = - r(x)
+\]
+where $r(x) = u\pd{u}{x} - \epsilon \pdd{u}{x}$ is the strong form of the nonlinear residual.
+Recall that for a pure Newton iteration, $u(x)$ is assumed to be known, and the linearized problem is driven by the residual.
+The solution $u(x)$ is updated $u \coloneqq u + \Delta u$, and is repeated until $\Delta u$ and $r(x)$ are both approximately zero.
+
+Let $u_\epsilon(x)$ be the exact solution for a particular viscosity $\epsilon$, and consider the setting of $u(x) = u_{\alpha \epsilon}(x)$, with $\alpha > 1$.
+In other words, the initial guess for the Newton iteration is taken to be the exact solution for the viscous Burgers' equation under a larger viscosity (a less sharp shock), a method known as continuation (specifically, continuation in viscosity $\epsilon$).\footnote{We note that continuation in Reynolds number was attempted for the Navier-Stokes equations; however, the presence of large oscillations in the Newton update on highly adapted meshes caused the line search to return a near-zero step length, which stalled the nonlinear iteration prior to convergence to a steady state solution.}
+
+\begin{figure}
+\centering
+\subfigure[$\epsilon = .01$]{\includegraphics[width = 2.75in]{figs/Burgers1DPlots/residual100.eps}}
+\subfigure[$\epsilon = .001$]{\includegraphics[width = 2.75in]{figs/Burgers1DPlots/residual1000.eps}}
+\caption{Residual for Burgers' equation with viscosity $\epsilon$ under the exact solution for ${2\epsilon}$.}
+\label{fig:burgersResidual}
+\end{figure}
+
+We plot $r(x)$ for $u(x) = u_{2\epsilon}(x)$ in Figure~\ref{fig:burgersResidual}.
+While the form of the exact linearized solution $\Delta u$ is unknown, we see that the forcing term in the above equation develops oscillations that grow in magnitude and decrease in support as $\epsilon$ decreases.
+We have observed similar behaviors for discretized solutions to the Burgers' and Navier Stokes equations -- the discrete linearized solution will develop gradients as well, though their magnitude will be limited by the resolution of the mesh.
+However, additional refinements near shocks will introduce additional oscillations, which are subsequently damped by additional Newton iterations.
+
+In other words, not all oscillations are related to the method of discretization -- the exact linearized solution itself contains large oscillations, which are picked up more and more strongly in a discrete scheme as the mesh resolution approaches the viscous length scale $\epsilon$ (see \cite{DPGspacetime, DPGNS_1d} for additional numerical examples).
+We note that these large oscillations are not an issue for the viscous Burgers' equation, as there is no positivity constraint on $u$.
+However, as noted previously, the convergence of the nonlinear iteration for the compressible Navier-Stokes equations can stall or even diverge for sufficiently negative values of $\rho$ and $T$, which happens easily in the presence of large oscillations.
+When a line search is implemented to enforce a strictly positive solution, the nonlinear iteration can stall, and numerical experiments have generated cases in which the line search length goes to zero, returning an under-converged solution.
+
+There are several approaches to controlling the magnitude of oscillations in the linearized solution -- a simple option is decreasing the size of the timestep; however, doing so can cause the number of iterations required for convergence to greatly increase.
+The application of artificial diffusion near sharp gradients is another way in which to control such oscillations; however, this results in a modified set of equations, and, though solutions with contemporary artificial viscosity methods can produce solutions with expected qualitative features, there is a wide array of choices for artificial diffusion, and it was not clear in the scope of this dissertation which artificial viscosity method would be quantifiably superior, or most suitable for use with the DPG method.

### 2013-07-30 docs/Jesse/Dissertation/acknowledgements.tex

This dissertation represents five years of work and study, which seem to have simply flown by much quicker than I expected.  First and foremost, I have to thank my advisor (and self-designated local parent figure during my time in Austin) Leszek Demkowicz.  Your insight, experience, and most of all, your drive to think outside the box were irreplaceable in building up both my work and my understanding throughout these last 5 years.  I have very much enjoyed all the fruitful discussions I have had with you, and have relished the fact that as I've mature mathematically, I've been able to contribute my own share into those discussions as well.  My experience in Austin would not have been nearly as pleasant without your kindness as well; your hospitality and warmth are something all of your students appreciate greatly.

None of the work in this thesis would have been possible without the help and expertise of fellow graduate student Nate Roberts, who almost singlehandedly built and maintains the parallel $hp$-adaptive DPG codebase Camellia, with which I ran all numerical experiments in this thesis.  Thanks for teaching me software design, for your help in debugging my code, for helpful discussions on each of our mathematical problems, and for good conversations and company in and outside of the ACES (now POB) building.

I'm grateful to the members of my committee -- Professors Robert Moser, Todd Arbogast, Omar Ghattas, and Venkat Raman -- for helpful discussions and feedback in evaluating my work, as well as for perspective on how my thesis work fits into the larger scheme of computational science and engineering.

To my co-authors on several papers, thank you for all your help in pushing me further along the path to this doctoral degree.  To Norbert Heuer, your mathematical insight has greatly advanced our understanding of the DPG method.  To Tan Bui, thanks for your emphasis on mathematical rigor, and for your incredible understanding of both application areas and numerical methods and their mathematics.  ICES is lucky to have you as a faculty member.  To Jay Gopalakrishnan, thanks for our communications, and for keeping me updated with your own insights on DPG.  Your interest and excitement in this area are contagious, and your students and colleagues all agree that you are one of the most kind and gracious professors they have ever worked with.  To John Evans, congratulations on your new position -- it was a pleasure to be able to write a paper with you, to hear your insights, and connect our two separate areas together.

For helpful discussions on both the mathematical and physical nature of my problem, I'm grateful to a host of folks at ICES.  To Ivo Babu\v{s}ka, thanks for allowing me to host the ICES Forum with you for 3 years, and for sharing your wealth of knowledge on $hp$ methods and singularities with me.  To Rhys Ulerich, thanks for discussions and answers to all of the strangest and most esoteric questions concerning compilers, linking, and all things code-based in general.  To Todd Oliver, thanks for the discussions on nondimensionalization and boundary conditions.  Roy Stogner and Paul Baumann thanks for giving me some of PECOS' vast perspective on common problems in fluid dynamics simulations using finite elements.  Paul Tsuji, thanks for the discussions on conditioning and Schur complement systems.  Truman Ellis and Jamie Bramwell, thanks for listening to me talk on DPG and mathematics -- when working on such a new topic, I am grateful for any colleagues who also understand it, with whom to share both successes and failures.

The Texas Advanced Computing Center (TACC) at The University of Texas at Austin has been very generous in providing HPC resources that have contributed to the research results reported within this paper, as well as consultation for whenever I experienced issues on their machines.  Thanks also to Chris Simmons and Karl Schulz for helping me figure out some of the tricks of the trade when it came to modern software engineering.

To my friends at ICES, thanks for making all the long hours spent in this building enjoyable.  Fred Qiu, it was great having you both as a roommate and colleague.  John Hawkins, thanks for your hospitality, and for the fun nights of bike building and conversation with you and Christa.  Chris Mirabito, Paul Tsuji, Henry Chang, Omar Al Hinai, Prapti Neupane, and the rest of the cribbage crowd -- may your fifteens be numerous.  Jeff Hussman, Jesse Kelly, it was fun to have someone with whom I could share both my math and my music.  Fred Nugen, it was great biking with you (you still owe me for those rims, by the way).  To so many folks at ICES -- Jessica, Lindley, Hamid, Vikram, Michele, Nick, James, and still so many more -- thanks for all the good conversation and camaraderie over these last few years.

To my community at Vox Veniae, you have been a pillar of support for the last 5 years of my life.  To list all the incredible people who have made an impact on my life would take almost the entire length of this acknowledgment section all over again.

Thanks to my family -- my parents Henry and Wendy, and my brother David -- thanks for the support throughout the last 5 years, and for always welcoming me home whenever I needed a break.  I love you all so much.

I would be remiss if I did not acknowledge the financial support I received during the course of this project.  This work was made possible by the CAM Fellowship at ICES and by
the Department of Energy [National Nuclear Security Administration] under Award Number [DE-FC52-08NA28615].

### 2013-07-30 docs/Jesse/Dissertation/confusionDPGIntro.tex

--- 2012-06-20 docs/Jesse/Proposal/DPGrobustness.tex
@@
 In particular, we shall use the DPG method based on the ultra-weak formulation with optimal test functions to solve this model problem and analyze its behavior as $\epsilon\rightarrow 0$.
-Our goal is to show the robustness of the method with respect to $\epsilon$, and demonstrate its usefulness as a numerical method for solving singular-perturbed problems.
+Our goal is to show the robustness of the method with respect to $\epsilon$ (for a given test norm), and demonstrate its usefulness as a numerical method for solving singular-perturbed problems.
+In particular, we will examine three different choices of test norms on $V$ -- an ideal norm (which returns good results, but whose test functions are difficult to approximate), a robust norm (which is easy to approximate and computationally efficient to assemble but still returns good results over a range of $\epsilon$), and finally, a coupled, robust test norm that borrows ideas from both the ideal and robust norm.\footnote{This third test norm is motivated by observed numerical difficulties; the precise shortcomings of the previous robust test norm are not completely understood, though a possible explanation is offered for both the issues encountered by the robust norm and the success of the coupled robust test norm in overcoming these issues.}
 
@@
 
-\seclab{sec:modelSec}
-
-The convection-diffusion problem is given on a domain
+We consider the following model convection-diffusion problem on a domain
 $\Omega \subset \mathbb{R}^d$ with boundary $\pO \equiv \Gamma$
@@
 \begin{align*}
-\Gamma_{-} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\}, \quad {\rm
-  (inflow)}\\ \Gamma_{+} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\},
-\quad {\rm (outflow)}\\ \Gamma_{0} &\coloneqq \{x\in \Gamma;
+\Gamma_{-} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\} \quad {\rm
+  (inflow)},\\ 
+  \Gamma_{+} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\}
+\quad {\rm (outflow)},\\ 
+\Gamma_{0} &\coloneqq \{x\in \Gamma;
 \beta_n(x) = 0\},
@@
 where $\beta_n \coloneqq \beta \cdot n$.
-Previous work in \cite{DPGrobustness} adopted Dirichlet boundary
-conditions everywhere on $\Gamma$.  
-%and we could obtain the robustness only with special weighted norms in which the weight varied spatially. 
-We employ instead the inflow
-condition of Hesthaven \etal \cite{Hesthaven96astable}, where we set
-\[
-\beta_n u - \sigma_n  = u_0, \quad \text{on } \Gm,
-\]
-instead of $\beta_n u = u_0$. The former resembles the latter
-as $\epsilon$ approaches zero\footnote{For our model problem, as for many problems of interest in computational fluid dynamics, we expect $\grad u$ to be small near the inflow, and that the solutions to \eqref{primal} using $\beta_n u - \sigma_n = f_n = u_0$ on $\Gamma_-$ will converge to that using $u=u_0$ on $\Gamma_-$  for sufficiently small $\epsilon$.}; however, the latter induces a more ``well-behaved" adjoint problem than the former, which, as we will discuss, affects the performance of DPG.
-
-On the outflow boundary, we apply standard homogeneous Dirichlet boundary conditions
+On the inflow boundary, we apply the inflow boundary condition $$u = u_{\rm in} \quad \text{on }\Gm.$$  On the outflow boundary, we apply standard homogeneous Dirichlet boundary conditions
 \[
@@
 \]
-This work is intended to act as an extension of work presented by Heuer and Demkowicz in \cite{DPGrobustness}.
-The primary focus of this chapter is to analyze the DPG method and extend previous results under this new choice of inflow boundary conditions.
-The difference in the performance of DPG under both new and old boundary conditions is connected to the difference in the adjoint problems induced under each boundary condition.
-The secondary contribution of this work will be to analyze the performance of DPG under a new mesh-dependent test norm.
-
-\subsection{Norms on $U$}
-
-With the above boundary conditions at hand, the ultra-weak formulation
-\eqnref{uweak} can be fitted in the abstract form \eqnref{variationEq}
-as
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right), \left( v,
-\tau\right)\right) &= \left(u,\div \tau - \beta \cdot \grad
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad
-v\right)_{\Oh} \\
-&- \LRa{ \jump{\tau\cdot n}, \widehat{u} }_{\Gh
-  \setminus \Gp} + \LRa{ \widehat{f}_n, \jump{v} }_{\Gamma_h \setminus
-  \Gm} =  \left(f, v\right) -
-\LRa{ u_0, v }_{\Gamma_-} = l\left(\left(v, \tau\right)\right),
-\end{align*}
-which, after using the setting in Section \secref{abstractUweak},
-suggests the following trial space (see \cite{analysisDPG, Bui-ThanhDemkowiczGhattas11b} for details):
-\begin{align*}
-u, \sigma \in \L, \quad \text{and } \LRp{\uh,\fnh} \in
-\gamma\LRp{D\LRp{A}} \subset \gamma\LRp{  H^1(\Omega) \times
-H({\rm div}, \Omega)} = H^{\frac{1}{2}}\left(\Gh\right) \times H^{-\frac{1}{2}}\left(\Gh\right).
-\end{align*}
-The space for $u$ and $\sigma$ are simply scalar and vector $L^2$ spaces over $\Omega$, while the space for $\left(\uh,\fnh\right)$ is the trace space of the graph space of the operator $A$ subject to the boundary conditions.
-
-The minimum energy extension norm \eqnref{MEnorm} now reads
-\begin{align*}
-\|\widehat{u}\| &= \inf_{w\in H^1(\Omega),
-  \left.w\right|_{\Gamma_+}=0, \left.w\right |_{\Gh\setminus
-    \Gamma_+ } = \widehat{u}} \|w\|_{H^1(\Omega)}, \\ \|\widehat{f}_n\|
-&= \inf_{q\in H({\rm div},\Omega), \left.q\cdot n\right|_{\Gamma_-}=
-  0, \left. q\cdot n \right |_{\Gh\setminus
-    \Gamma_-} = \widehat{f}_n}
-\|q\|_{H({\rm div},\Omega)}.
-\end{align*}
-As a result, the canonical norm on $U$ is given by
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U^2 = 
-\|u\|_{L^2(\Oh)}^2 + \|\sigma\|_{L^2(\Oh)}^2 +
-\|\widehat{u}\|^2 + \|\widehat{f}_n\|^2.
-\]
-
-\subsection{Norms on $V$}
-
-%We will denote $\|\cdot \| = \|\cdot\|_{L^2}$ for all functions defined on $\Oh$. 
-As $\tau \in H({\rm div},\Oh)$ and $v \in H^1(\Oh)$, we will
-construct norms on $v$ and $\tau$ 
-which are equivalent to the canonical $H^1(K) \times H({\rm div},K)$
-norm over a single element
-\[
-\|\left(v,\tau\right)\|_{H^1(K) \times H({\rm div},K)}^2 =
-\|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2 + \|\tau\|_{L^2(K)}^2 +
-\|\div \tau\|_{L^2(K)}^2.
-\]
-The squared norm over the entire triangulation $\Oh$ is defined to be the squared sum of contributions from each element
-\[
-\|\left(v,\tau\right)\|_{H^1(\Oh) \times H({\rm div},\Oh)}^2
-= \sum_{K\in \Oh} \|\left(v,\tau\right)\|_{H^1(K) \times H({\rm
-    div},K)}^2.
-\]
-The exact norms that we will specify on $V$ will be determined later.
-
-The norms on the skeleton $\Gh$ for $v$ and $\tau$ are defined by duality from the bilinear form
-\begin{align*}
-\left\|\jump{\tau\cdot n}\right\| &= \left\|\jump{\tau\cdot n}\right\|_{\Gh \setminus \Gamma_+} \coloneqq \sup_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+} = 0} \frac{\langle \jump{\tau \cdot n}, w\rangle}{\|w\|_{H^1(\Omega)}},\\
-\left\|\jump{v}\right\|&=\left\|\jump{v}\right\|_{\Gh^0 \cup \Gamma_+} \coloneqq \sup_{\eta\in H({\rm div},\Omega), \left.\eta\cdot n\right|_{\Gamma_- \cup \Gamma_0} = 0} \frac{\langle \jump{v}, \eta\cdot n\rangle}{\|\eta\|_{H({\rm div},\Omega)}}.
-\end{align*}
-
-\subsection{Approximability of the quasi-optimal test norm}
-%\textcolor{blue}{need to define what we mean by robustness. perharps the best place is in the introduction}
-An obvious choice for the test norm would be the quasi-optimal norm; it is the canonical test norm, and DPG has been shown to be well-posed and robust under such an optimal test norm for a large class of problems \cite{DPGrobustness,Bui-ThanhDemkowiczGhattas11b, stokesDPG}.
-However, computations with the quasi-optimal test norm for convection-diffusion problems turn out to be quite problematic for small diffusion and coarse meshes.
-
-For convection-diffusion, the quasi-optimal test norm is 
-\[
-\|\left(v,\tau\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v
-\|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 +
-\|v\|_{L^2}^2 + \|\tau\|_{L^2}^2.
-\]
-%We note that the optimal test norm will automatically guarantee the
-%robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.
-Use of this norm for the convection-diffusion problem is difficult --- since the problem \eqnref{optvVar} for optimal test functions is local, we can transform the problem over a single element $K$ to the reference element $\widehat{K}$ and show that it is equivalent to a reaction-diffusion system, with diffusion parameter $\frac{\epsilon}{|K|}$, where $|K|$ is the element measure \cite{DBLP:journals/procedia/NiemiCC11}.
-We refer to the inverse of this parameter $\frac{|K|}{\epsilon}$ as the element Peclet number $\rm Pe$.
-For a coarse mesh and small diffusion parameter $\epsilon$, we will have a large element Peclet number, and optimal test functions under the quasi-optimal test norm will develop strong boundary layers of width $\rm Pe$, as seen in Figure~\ref{fig:optTestBoundary}.
-
-In the application of DPG in \cite{DPG1,DPG2,DPG3,DPG4}, the approximation of optimal test functions is done using polynomial enrichment.
-We search for the solution to \eqnref{optvVar} in the enriched test space $\tilde{V} \approx \prod_{K} P^{p+\Delta p}(K)$, where $p$ is the polynomial order of the trial space on a given element $K$.\footnote{$V$ is only \emph{approximately} equal to the space $\prod_{K} P^{p+\Delta p}(K)$.
-In practice, $V$ is constructed using locally $H^1$-conforming and Raviart-Thomas elements of appropriate order.}  In other words, optimal test functions are approximated element-by-element using polynomials whose order is $\Delta p$ more than the local order of approximation.
-Under this scheme, the error in approximation of test functions is tied to the effectiveness of the $p$-method.
-Unfortunately, for problems with boundary layers --- including the approximation of test functions under the quasi-optimal test norm --- the $p$-method performs very poorly.
-As a result of this poor approximation, the numerical solutions of the convection-dominated diffusion equation under DPG using the quasi-optimal test norm tend to be of poor quality, and do not exhibit all the proven properties of DPG (for example, the energy error may increase after mesh refinement, even though, by virtue of DPG delivering a best approximation, the energy error for a coarse mesh must be greater than or equal to the energy error for a finer mesh).
-We conclude that the error in approximation of optimal test functions using simple polynomial enrichment pollutes and ruins the performance of DPG under the quasi-optimal test norm.
-
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.25]{figs/opt.png}
-\caption{$v$ and $\tau$ components of the 1D optimal test functions corresponding to the flux $\widehat{f}_n$ on the right-hand side of a unit element for $\epsilon = 0.01$.
-The solution has been obtained using automatic $hp$-adaptivity driven by the test norm with the error tolerance set at 1\%.}
-\label{fig:optTestBoundary}
-\end{figure}
-
-The difficulty in using the quasi-optimal test norm for convection-diffusion is perplexing at first, considering that the quasi-optimal norm has yielded excellent results for the Helmholtz equation and other wave propagation problems.
-The difference between the two problems lies in the fact that, for wave propagation problems, the mesh size tends to be on the order of the wavenumber $k$ --- the singular perturbation parameter.
-Transforming the variational problem using the quasi-optimal test norm for wave propagation yields smooth optimal test functions that are approximated much more accurately using only polynomials over the reference element.
-Typically, the wavenumbers $k$ of physical interest are $O(100)$ with respect to a unit domain.
-The corresponding finite element problems will typically be solved on meshes containing approximately $O\!\left(k^d\right)$ elements in $\mathbb{R}^d$, well within the range of a computationally tractable simulation.
-However, for convection diffusion problems, the relevant range of $\epsilon$ for physical problems can be as small as $1e-7$.
-Solving on under-resolved meshes is thus unavoidable, and the approximability of optimal test functions must be addressed in order to take advantage of the properties of DPG.
-
-Resolving such boundary layers present in test functions under the quasi-optimal test norm has been investigated numerically using specially designed (Shishkin) subgrid meshes by Niemi, Collier, and Calo in
-\cite{DBLP:journals/procedia/NiemiCC11}.
-However, even with Shishkin meshes, the approximation of optimal test functions under the quasi-optimal norm is far more expensive and complex to implement than approximation of test functions using a simple $p$-enriched space for $V$.
-We therefore aim instead to design a test norm that does not induce boundary layers, but still delivers good approximation results over a range of $\epsilon$.
-
-\subsection{Analysis of a DPG test norm}
-\seclab{sec:testNormSec}
-We are interested in computing DPG optimal test functions for the convection-diffusion equation with very small values of $\epsilon$; due to the difficulty of approximating optimal test functions, we conclude that the use of the quasi-optimal test norm is infeasible towards this goal.
-
-However, if we naively choose a test norm that does not generate boundary layers, the performance of DPG may be adversely affected.
-For example, if $\|\left(v,\tau\right)\|_V^2 = \|v\|_{H^1(\Omega_h)}^2 + \|\tau\|^2_{H({\rm div},\Omega_h)}$, the $H^1(\Omega_h)\times H({\rm div},\Omega_h)$ norm, then the corresponding test functions will be smooth and free of boundary layers; however, the performance of DPG will provide approximations which worsen in quality as $\epsilon$ becomes very small \cite{DPG3,DPGrobustness}.
-
-Our goal is to construct a test norm that compromises between performance of DPG and approximability of test functions.
-This test norm should not produce boundary layers in the optimal test functions, but still induce an energy norm that yields good approximation properties for small $\epsilon$.
-We note that, even under the quasi-optimal norm, the norms on the flux and trace variables will likely depend on $\epsilon$.
-Thus, we aim to construct a test norm for which the DPG method will be robust in $\epsilon$ with respect to the \emph{field variables}.
-
-For now, we discuss the steps necessary to analyze the performance of DPG with respect to a non-canonical test norm.
-We require a priori that the test norm has separable $\tau$ and $v$ components --- in other words, that there are no terms in the test norm that couple $\tau$ and $v$ together.
-Problem \eqnref{optvVar} then decouples, such that the components of the vector-valued test function $\left(v,\tau\right)$ can be solved for independently of each other.
-The decoupled variational problems are no longer systems but scalar equations in $\tau$ and $v$, for which it is easier to conclude whether or not there are boundary layers in the solutions (the avoidance of boundary layers in the test norm will be discussed in more detail in Section~\ref{sec:num_exp}, which describes our numerical experiments).
-\textbf{This will ensure that the resulting DPG method does not suffer from approximation errors in the optimal test functions}.
-
-We begin with the following test norm:
-\[
-\left\|\left(v,\tau\right)\right\|^2_V \coloneqq \|v\|_{L^2}^2 + \epsilon\|\grad v\|_{L^2}^2 + \|\beta \cdot \grad v\|_{L^2}^2  + \frac{1}{\epsilon}\|\tau\|_{L^2}^2 + \|\div \tau\|_{L^2}^2.
-\]
-The use of this norm is problematic for practical computations; we will discuss the reasons why and present a modification of it in Section~\secref{sec:meshDep}.
-
-We can see how this norm will differ from the canonical $H^1(\Omega_h)\times H({\rm div},\Omega_h)$ norm: the clearest difference is the fact that the gradient in the streamline direction is $O(1)$, while the full gradient is $O(\sqrt{\epsilon})$, so that, in our test norm, the streamline gradient of $v$ will be emphasized over the full gradient of $v$ for small $\epsilon$.
-
-The choice of this test norm is implied by the mathematics of the adjoint problem.
-Roughly speaking, necessary conditions for the performance of DPG to not degenerate as $\epsilon \rightarrow 0$ are derived through analysis of specific test functions.
-For example, if $u$ is the first $L^2$ component of the solution to the variational problem defined in Section~\secref{sec:modelSec}, by choosing $(v,\tau) \in H^1(\Omega) \times H({\rm div},\Omega)$ such that
-\begin{align*}
-\div \tau - \beta \cdot \grad v &= u \\
-\frac{1}{\epsilon} \tau - \grad v &= 0,
-\end{align*}
-we have
-\[
- \nor{u}_{L^2}^2 = b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(v,\tau\right)\right) \leq \nor{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)}_{U,V} \nor{\left(v,\tau\right)}_V,
-\]
-and we recover the $L^2$ norm of $u$ from the bilinear form.
-
-Let $\|a\| \lesssim \|b\|$ denote an $\epsilon$-independent bound; specifically, that $\|a\| \leq C\|b\|$ for a constant $C$ independent of $\epsilon$.
-Consequently, if for any $u\in L^2(\Oh)$, $\nor{\left(v,\tau\right)}_V\lesssim \nor{u}_{L^2}$, then dividing through by $\nor{u}_{L^2}$ gives the bound
-\[
- \nor{u}_{L^2} \lesssim \nor{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)}_E.
-\]
-In other words, there is the guarantee that the $L^2$ error in $u$ is at least robustly bounded from above by the energy error.
-Then, if the energy error (which DPG minimizes) approaches zero, the $L^2$ error in $u$ will as well.
-The same exercise can be repeated for the stress $\sigma$, as well as the flux variables $\widehat{u}$, $\widehat{f}_n$.
-
-This methodology gives constraints on the quantities found in the test norm; any quantity present in $\nor{\left(v,\tau\right)}_V$ must be shown to be bounded from above independently of $\epsilon$ by the load of the adjoint problem.
-However, showing this simply amounts to showing \textit{standard energy estimates} for $H^1$ and $H({\rm div})$-conforming finite elements.
-A more detailed discussion on the reasoning behind the construction of test norms can be found in \cite{DPGrobustness}.
-
-The second step will be to \textbf{show the equivalence of the energy norm to explicit norms on $U$}.
-Since we do not generally have a closed form expression for the DPG energy norm, we seek to understand the behavior of DPG by finding a norm on $U$ to which the DPG energy norm is equivalent.
-Since $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U$ is a group variable from a tensor product space, we construct norms on $U$ through the combination of norms on $u$, $\sigma$, $\widehat{u}$, and $\widehat{f}_n$.
-Specifically, we use the norm on $U$
-\begin{equation}
-\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U}^2 \coloneqq \|u\|^2 + \|\sigma\|^2 + \left\|\widehat{u}\right\|^2 + \left\|\widehat{f}_n\right\|^2.
-\end{equation}
-For equivalence between norms, two constants are specified.
-However, since this norm on $U$ is a norm on four separate variables, we can specify not just two but eight equivalence constants.\footnote{Sharper estimates are attainable if these constants are allowed to vary over the mesh $\Oh$.
-See Section~\ref{sec:main_bounds} for a discussion.} In order to simplify analysis, we phrase this equivalence statement in an alternative form.
-
-Let $\nor{\cdot}_E \coloneqq \nor{\cdot}_{U,V}$, the energy norm induced by the test norm described above. We seek the bound of $\nor{\cdot}_E$ from above and below:
-\[
-\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2},
-\]
-where both $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ are defined as scaled combinations of the norms on $u, \sigma, \widehat{u}$, and $\widehat{f}_n$
-\begin{equation}
-\eqnlab{uNorms}
-\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,i}^2 \coloneqq \left(C_u^i\|u\|\right)^2 + \left(C_\sigma^i\|\sigma\|\right)^2 + \left(C_{\widehat{u}}^i\|\widehat{u}\|\right)^2 + \left(C_{\widehat{f}_n}^i\|\widehat{f}_n\|\right)^2,\quad i = 1,2
-\end{equation}
-Our goal is to explicitly derive the equivalence constants 
-%$C^1_u,\ldots, C^1_{\widehat{f}_n}$ and $C^2_u,\ldots, C^2_{\widehat{f}_n}$ 
-that define the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ respectively, taking into account any dependency on $\epsilon$.
-To do so, we need a relation between trial norms on $U$ and test norms on $V$.
-
-Recall from Section~\secref{energyPair} that every test norm induces a corresponding trial norm, and vice versa.
-Let $\|\cdot\|_{U,1} \simeq \|\cdot\|_{U,2}$ mean that the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ are equivalent, with equivalence constants independent of $\epsilon$.
-By equivalence of finite dimensional norms and the discussion in Section~\secref{energyPair} on the duality between test norms/energy norms, the norms \eqnref{uNorms} on $U$ induce the equivalent test norms on $\left(v,\tau\right) \in H^1(\Oh)\times H({\rm div},\Oh)$
-\begin{align*}
-\left\|\left(v,\tau\right)\right\|_{V,{U,i}} &\simeq \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(v,\tau\right)\right)}{C_u^i\|u\| + C_\sigma^i\|\sigma\| + C_{\widehat{u}}^i\|\widehat{u}\|+ C_{\widehat{f}_n}^i\|\widehat{f}_n\|}\\
-&= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \jump{\tau_n}, \widehat{u} \rangle_{\Gamma_-\cup \Gh^0} + \langle \widehat{f}_n, \jump{v} \rangle_{\Gamma_+ \cup \Gh^0}}{C_u^i\|u\| + C_\sigma^i\|\sigma\| + C_{\widehat{u}}^i\|\widehat{u}\|+ C_{\widehat{f}_n}^i\|\widehat{f}_n\|}\\
-& \simeq \frac{1}{C_u^i}\|g\| + \frac{1}{C_\sigma^i}\|f\| + \frac{1}{C_{\widehat{u}}^i}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle \jump{\tau\cdot n}, \widehat{u}\rangle}{\|\widehat{u}\|} +\frac{1}{C_{\widehat{f}_n}^i}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, \jump{v}\rangle}{\|\widehat{f}_n\|},
-\end{align*}
-where $f$ and $g$ are defined element-wise over $\Oh$ as 
-\begin{align*}
-g &\coloneqq \div \tau - \beta \cdot \grad v\\
-f &\coloneqq \epsilon^{-1}\tau + \grad v.
-\end{align*}
-By definition of the norms on the quantities defined on the skeleton $\Gh$, this gives the characterization of the induced test norm 
-\[
-\|\left(v,\tau\right)\|_{V,{U,i}} \simeq \frac{1}{C_u^i}\|g\| + \frac{1}{C_\sigma^i}\|f\| + \frac{1}{C_{\widehat{u}}^i}\|\jump{\tau\cdot n}\| + \frac{1}{C_{\widehat{f}_n}^i}\|\jump{v}\|, \quad i = 1,2.
-\]
-We can now use this relation to compare different norms on $U$ by comparing their induced norms on $V$ (recall that showing a robust inequality between two norms on $U$ is equivalent to showing the robust \textit{reverse} inequality in the induced norms on $V$).
-Namely, we can show the bound of $\nor{\cdot}_{U,1} \lesssim \nor{\cdot}_E$ by showing the bound $\nor{\left(v,\tau\right)}_{V,U,1} \gtrsim \nor{\left(v,\tau\right)}_{V}$, and likewise for $\nor{\cdot}_E \lesssim \nor{\cdot}_{U,2}$.
-
-Since the techniques used to show such bounds are more involved, we break the procedure up into two steps:
-\begin{enumerate}
-\item{}Decompose test functions $(v,\tau)$ into three separate, more easily analyzable components (Section~\ref{sec:strategy2}).
-\item{}Derive adjoint estimates (Section~\ref{sec:strategy3}).
-\end{enumerate}
-
-\subsubsection{Decomposition into analyzable components}
-\label{sec:strategy2}
-
-Having reduced the problem of comparing norms on $U$ to the comparison of norms on $V$, we break the analysis of $\left(v,\tau\right) \in V$ into the analysis of three subproblems.
-Define the decomposition
-\[
-\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right),
-\]
-where $\left(v_1,\tau_1\right)$ satisfies 
-\begin{align*}
-\epsilon^{-1}\tau_1 + \grad v_1 &= 0 ,\\
-\div \tau_1 - \beta\cdot \grad v_1 &=  \div \tau - \beta\cdot \grad v = g, 
-\end{align*} 
-and $\left(v_2,\tau_2\right)$ satisfies
-\begin{align*}
-\epsilon^{-1}\tau_2 + \grad v_2 &= \epsilon^{-1}\tau + \grad v = f, \\
-\div \tau_2 - \beta\cdot \grad v_2 &= 0.
-\end{align*}
-Both $(v_1,\tau_1), (v_2,\tau_2) \in H({\rm div}; \Omega)\times H^1(\Omega)$ are understood to satisfy these relations in a conforming sense over the domain $\Omega$; however, the divergence of $\tau$ and gradient of $v$ on the right hand side are still understood to be taken in an element-wise fashion.
-
-We will additionally require both $\left(v_1,\tau_1\right), \left(v_2,\tau_2\right)$ to satisfy the adjoint homogeneous boundary conditions
-\begin{align}
-\tau_i\cdot n &= 0, \quad \text{on }\Gamma_- \label{bc_1}\\
-v_i &= 0, \quad \text{on } \Gamma_+ \label{bc_2}
-\end{align}
-for $i = 1, 2$.
-The selection of $H({\rm div}, \Omega)\times H^1(\Omega)$ conforming test functions satisfying the specific boundary conditions above removes the contribution of the jump terms over the skeleton $\Gh$ in the bilinear form, allowing us to analyze field terms in the induced test norms separately from  the boundary/jump terms.
-
-Finally, by construction, $\left(v_0,\tau_0\right) \in H^1(\Oh) \times H({\rm div},\Oh)$ must satisfy 
-\begin{align*}
-\epsilon^{-1}\tau_0 + \grad v_0 &= 0\\
-\div \tau_0 - \beta\cdot \grad v_0 &= 0
-\end{align*}
-with jumps
-\begin{align*}
-\jump{v_0} &= \jump{v}, \quad \text{on }\Gh^0\\
-\jump{\tau_0 \cdot n} &= \jump{\tau \cdot n}, \quad \text{on }\Gh^0.
-\end{align*}
-and boundary conditions
-\begin{align*}
-v_0 &= v, \quad \text{on } \Gamma_+ \\
-\tau_0 \cdot n &= \tau \cdot n, \quad \text{on } \Gamma_-\cup \Gamma_0. 
-\end{align*}
-Notice that the evaluation the bilinear form $b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(v,\tau\right)\right)$ with each specific test functions returns only one part of the bilinear form.
-Furthermore, by choosing the proper loads $g = u$ and $f=\sigma$, we can recover from the bilinear form the norms of $u$ and $\sigma$ (as described in Section~\secref{sec:testNormSec}), as well as the norms on $\widehat{u}$, and $\widehat{f}_n$.\footnote{To recover the norms on $\widehat{u}$, and $\widehat{f}_n$, the loads $f$, and $g$ must be zero, and the jumps of the test function $(v,\tau)$ must be chosen specifically.}
-
-We have now decomposed an arbitrary test function $\left(\tau,v\right)$ into a discontinuous contribution and two continuous contributions.
-Recall that our goal is to show the robust bound from above and below of the DPG energy norm by $\|\cdot \|_{U,1}$ and $\|\cdot \|_{U,2}$:
-\[
-\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}.
-\]
-
-Under the duality of trial and test norms and the decomposition of test functions $\left(\tau,v\right) \in V$ into $\left(\tau_0,v_0\right), \left(\tau_1,v_1\right)$, and $\left(\tau_2,v_2\right)$, the above bound is equivalent to bounding each component
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,U,1} &\gtrsim \sum_{i=0}^2\|\left(v_{i},\tau_{i}\right)\|_V \gtrsim \|\left(v,\tau\right)\|_{V,U,2}.
-%\|\left(v,\tau\right)\|_{V,1} &\lesssim \|\left(v_{1},\tau_{1}\right)\|_V \lesssim \|\left(v,\tau\right)\|_{V,2}\\
-%\|\left(v,\tau\right)\|_{V,1} &\lesssim \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|\left(v,\tau\right)\|_{V,2}
-\end{align*}
-Bounding $\|\left(v_0,\tau_0\right)\|$ requires the use of techniques first developed in \cite{analysisDPG} and adapted to convection-diffusion in \cite{analysisDPG} and \cite{DPGrobustness}.
-However, since $\left(\tau,v\right) \in H({\rm div}, \Omega)\times H^1(\Omega)$, the bound from above of test functions $\|\left(v_{1},\tau_{1}\right)\|_V$ and $\|\left(v_{2},\tau_{2}\right)\|_V$ is reduced to proving classical error estimates for the adjoint equations
-\begin{align*}
-\epsilon^{-1}\tau_1 + \grad {v_1} &= 0 \\
-\div {\tau_1} - \beta\cdot \grad {v_1} &=  g, \\
-\left.\tau_1\cdot n\right|_{\Gamma_-} &= 0, \\
-\left.v_1\right|_{\Gamma_+} &= 0.
-\end{align*} 
-and 
-\begin{align*}
-\epsilon^{-1}\tau_2 + \grad {v_2} &= f \\
-\div {\tau_2} - \beta\cdot \grad {v_2} &= 0, \\
-\left.\tau_2\cdot n\right|_{\Gamma_-} &= 0, \\
-\left.v_2\right|_{\Gamma_+} &= 0.
-\end{align*} 
-More generally, we can analyze the adjoint equations
-\begin{align}
-\epsilon^{-1}\tau + \grad {v} &= f \label{adjoint1}\\
-\div {\tau} - \beta\cdot \grad {v} &= g, \label{adjoint2}
-\end{align}
-for arbitrary data $f, g\in L^2({\Omega})$ and boundary conditions $\jump{\tau\cdot n}_{\Gamma_-} = 0$ and $\jump{v}_{\Gamma_+} = 0$.
-In other words, we want to analyze the stability properties of the adjoint equations by deriving bounds of the form $\|\left(v_1,\tau_1\right)\|_V\lesssim \|g\|_{L^2}$ and $\|\left(v_2,\tau_2\right)\|_V \lesssim \|f\|_{L^2}$.
-
-%An alternate interpretation of the above decomposition is that each component $(v_i,\tau_i)$ of the decomposition corresponds to a term in the bilinear form.
-For example, .
-If we evaluating our bilinear form with $(v,\tau) = (v_1,\tau_1)$ delivers
-%\[
-%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-%\left( v_1, \tau_1 \right)\right) = (u,g)_{L^2} 
-%\]
-%By choosing $g = u$,
-
-\subsubsection{Adjoint estimates}
-\label{sec:strategy3}
-
-The final step to estimating the induced norm on $U$ by a selected localizable test norm on $V$ is to derive adjoint stability estimates on $\tau$ and $v$ in terms of localizable normed quantities.
-We will construct complete test norms on $V$ through combinations of these normed quantities.%, where each normed quantity on $\tau$ or $v$ will correspond roughly to $\|u\|_{L^2}$, $\|\sigma\|_{L^2}$, $\|\widehat{u}\|$, or $\|\widehat{f}_n\|$.
-
-We introduce first the bounds derived; the proofs will be given later.
-For this analysis, it will be necessary to assume certain technical conditions on $\beta$.
-For each proof, we require $\beta \in C^2(\bar{\Omega})$ and $\beta, \div \beta = O(1)$.
-Additionally, we will assume that some or all of the following assumptions hold:
-\begin{align}
-&\curl \beta = 0, \quad 0<C \leq \left | \beta\right |^2 + \frac{1}{2}\div \beta, \quad C = O(1) \label{a_req},\\
-&\grad \beta + \grad \beta ^T - \div \beta I = O(1) \label{b_req},\\
-&\div \beta = 0 \label{c_req}.
-\end{align}
-Under proper assumptions on $\beta$, we have the robust bounds, which are proved in the Appendix. 
-\begin{itemize}
-\item \textbf{Lemma \ref{lemma_stream}}: \textit{For $\beta$ satisfying \eqref{a_req} and \eqref{b_req}, %$f=0$ 
-and $v_1 \in H^1(\Omega)$, satisfying equations \eqref{adjoint1} and \eqref{adjoint2} with $f=0$, and with boundary conditions \eqref{bc_1} and \eqref{bc_2}},
-\begin{align*}
-\|\beta \cdot \grad v_1 \| &\lesssim \| g\|.
-\end{align*}
-Similarly, from $\div \tau_1 - \beta\cdot \grad v_1 = g$, we get $\|\div \tau_1\| \lesssim \|g\|$ as well.  
-\item \textbf{Lemma \ref{lemma_grad}}: \textit{For $\beta$ satisfying \eqref{a_req}, and $v \in H^1(\Omega)$ satisfying equations \eqref{adjoint1} and \eqref{adjoint2} and boundary conditions \eqref{bc_1} and \eqref{bc_2}, and for sufficiently small $\epsilon$},
-\[
-\epsilon \|\grad v\|^2 + \|v\|^2 \lesssim \|g\|^2 + \epsilon \|f\|^2.
-\]
-We can characterize both $v_1$ and $v_2$ in the above decompositions using this theorem by setting either $f=0$ or $g=0$. 
-%\begin{align*}
-%\epsilon \|\grad v_1\|^2 + \|v_1\|^2 &\lesssim \|g\|^2\\
-%\epsilon \|\grad v_2\|^2 + \|v_2\|^2 &\lesssim \epsilon \| f\|^2.
-%\end{align*}
-%By the triangle inequality, this implies for any $w$ of the form $w=v_1+v_2$
-%\begin{align*}
-%\epsilon \|\grad w\|^2 + \|w\|^2 &\lesssim \|g\|^2 + \epsilon \| f\|^2
-%\end{align*}
-\item \textbf{Lemma \ref{lemma_boundary}}: \textit{For $\beta$ satisfying \eqref{a_req}, \eqref{c_req}, and solutions $v_0 \in H^1(\Oh)$ and $\tau_0 \in H({\rm div},\Oh)$ of equations \eqref{adjoint1} and \eqref{adjoint2} with $f=g=0$,}
-\begin{align*}
-\|\grad v_0\| = \frac{1}{\epsilon}\|\tau_0\| &\lesssim \frac{1}{\epsilon} \| \jump{\tau_0\cdot n}\|_{\Gh \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| \jump{v_0}\|_{\Gh^0 \cup \Gamma_+}.
-\end{align*}
-\end{itemize}
-We are interested in showing the equivalence of the DPG energy norm with norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$, respectively.
-We will show this by bounding $\|\cdot \|_V$ from below by $\|\cdot\|_{V,U,1}$ and from above by $\|\cdot\|_{V,U,2}$ (the induced test norms for $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$, respectively).
-
-%We will use Lemmas \ref{lemma_stream}, \ref{lemma_grad}, and \ref{lemma_boundary} to prove such bounds on our yet-unspecified test norm $\|(\tau,v)\|_V$.
-
-%Together, these estimates will be sufficient to construct a complete norm on $V$ and demonstrate bounds on induced test norms for different scalings of norms on $U$.  
-%\tanbui{}{again, using the same notation
-%  $(v, \tau)$ for all three problems is not a good idea. Why don't we
-%  use $(v_i,\tau_i)$ introduced above? Things are much clearer this
-%  way?}
-\subsubsection{A mesh-dependent test norm}
-\seclab{sec:meshDep}
-Ideally, we would be interested in the use of the test norm 
-\[
-\|\left(v,\tau\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2
-\]
-for practical computations.
-However, the presence of the term $\|v\|$ together with $\sqrt{\epsilon}\|\grad v\|$ (and similarly $\|\div \tau\|$ and $\frac{1}{\sqrt{\epsilon}}\|\tau\|$ terms) induces boundary layers in the optimal test functions for under-resolved meshes.
-We can see this by recovering the strong form of the variational problem defining test functions.
-We first note that the variational problems for the $v$ and $\tau$ components of optimal test functions decouple from each other under this test norm.
-Then, examining the variational problem for the $v$ component only of an optimal test function, and assuming $\div \beta = 0$ for illustrative purposes, we have
-\begin{align*}
-\left(\left(v,0\right),\left(\delta v,\delta\tau\right)\right)_{V} &= (v,\delta v) + \epsilon \left(\grad v,\grad \delta v\right) + \left(\beta \cdot \grad v, \beta \cdot \grad \delta v\right)\\
-&= \left(v - \epsilon \Delta v - \div \left(\left(\beta \otimes \beta\right) \grad v\right), \delta v\right)_{L^2} + \langle \epsilon \grad v\cdot n, \delta v\rangle + \langle n\cdot \left(\beta\otimes\beta\right) \grad v , \delta v\rangle.
-\end{align*}
-After integration by parts, we recover the strong form of the operator $L$ inducing such a variational problem 
-\[
-Lv \coloneqq v - \epsilon \Delta v - \div \left(\left(\beta \otimes \beta\right) \grad v\right),
-\]
-where we neglect the resulting boundary terms from integration by parts for now.
-
-The streamline direction $\beta$ induces an anisotropic diffusion, while the $\sqrt{\epsilon}\|\grad v\|_{L^2}$ term induces a small isotropic diffusion contribution everywhere.
-Since any vector in the cross-stream direction is in the null space of the anisotropic diffusion tensor, in the cross-stream directions, the optimal test function is governed only by the cross-stream part of the operator $L$
-\[
-L_{\rm \beta^\perp} \coloneqq v - \epsilon \Delta v,
-\]
-and can develop boundary layers in those directions.
-The presence of boundary layers has been verified through numerical computation as well; using an $H^1$-conforming finite element code with $hp$-adaptivity \cite{demkowicz2006computing}, the solution to the variational problem defining the optimal test function under the above test norm was computed.
-Figure~\ref{fig:boundaryTest} shows the result of such a computation for the $v$ component of an optimal test function under the above test norm.
-\begin{figure}[!h]
-\centering
-\subfigure{\includegraphics[scale=.2]{figs/mesh1.png}}
-\subfigure{\includegraphics[scale=.2]{figs/sol1.png}}
-\caption{The $v$ component of the optimal test function corresponding to flux $\widehat{u} = x(1-x)$ on the bottom side of a unit element for $\epsilon = 0.01$.
-The corresponding $hp$-mesh used to compute the solution is displayed to the left.}
-\label{fig:boundaryTest}
-\end{figure}
-To avoid boundary layers in the optimal test functions, we follow \cite{DPGrobustness} in scaling the $L^2$ contributions of $v$ by $C_v(K)$, such that, when transformed to the reference element, both $C_v(K)\|v\|^2$ and $\epsilon\|\grad v\|^2$ are of the same magnitude.
-Similarly, we scale the $L^2$ contributions of $\tau$ by $C_\tau(K)$ such that $\frac{C_\tau(K)}{\epsilon} \|\tau\|^2$ and $\|\div \tau\|^2$ are of the same magnitude as well.
-For this work, we consider only isotropic refinements on quadrilateral elements in 2D.
-
-Our test norm, as defined over a single element $K$, is now
-\[
-\|\left(v,\tau\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
-\]
-This modified test norm avoids boundary layers in the locally computed optimal test functions, but for adaptive meshes, provides additional stability in areas of heavy refinement, where the best approximation error tends to be large and stronger robustness is most necessary.
-This leads to a test norm which produces easily approximable optimal test functions, but still provides \textit{asymptotically} the strongest test norm and tightest robustness results in the areas of highest error.
-
-\subsubsection{Equivalence of energy norm with $\nor{\cdot}_U$}
-%\subsection{Relations between trial and test constants}
-\label{sec:main_bounds}
-
-The main theoretical result of this work can now be given:
-\begin{lemma}
-Under the mesh-dependent test norm
-\[
-\|\left(v,\tau\right)\|_{V,\Oh}^2 = \|C_vv\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \|C_\tau\tau\|^2,
-\]
-where $C_v, C_{\tau}\in L^2(\Omega)$ are defined elementwise through
-\begin{align*}
-\left.C_v\right |_K &= \min\left\{\sqrt{\frac{\epsilon}{|K|}},1\right\}\\
-\left.C_{\tau}\right |_K &= \min\left\{\frac{1}{\sqrt{\epsilon}},\frac{1}{\sqrt{|K|}}\right\}.
-\end{align*}
-If $\beta$ satisfies \eqref{a_req}, \eqref{b_req}, and \eqref{c_req}, the DPG energy norm $\nor{\cdot}_E$ satisfies the following equivalence relations
-\begin{align*}
-\nor{u}_{L^2} + \nor{\sigma}_{L^2} + \epsilon\nor{\widehat{u}} + \sqrt{\epsilon}\nor{\widehat{f}_n} 
-&\lesssim \nor{\left(u,\sigma, \widehat{u},\widehat{f}_n\right)}_E \\ 
-%\nor{\left(u,\sigma, \widehat{u},\widehat{f}_n\right)}_E &\lesssim \nor{u}_{L^2} + \nor{C_\sigma \sigma}_{L^2} + \frac{1}{\sqrt{\epsilon}} \left(\nor{\widehat{u}} + \nor{\widehat{f}_n}\right),
-\nor{\left(u,\sigma, \widehat{u},\widehat{f}_n\right)}_E &\lesssim \nor{u}_{L^2} + \nor{\frac{1}{\epsilon C_\tau} \sigma}_{L^2} + \frac{1}{\sqrt{\epsilon}} \left(\nor{\widehat{u}} + \nor{\widehat{f}_n}\right).
-\end{align*}
-%where $C_\sigma \in L^2(\Omega)$ is defined elementwise through $\left.C_\sigma\right|_K  = \max\left\{ \frac{1}{\sqrt{\epsilon}} , \frac{\sqrt{|K|}}{\epsilon} \right\}$.
-\end{lemma}
-
-\begin{proof}
-We begin by proving the bound from below.
-As a consequence of the duality of norms discussed in Section~\secref{energyPair}, we know that the norm $\left\| u \right\|_{U,1}$ is induced by a specific test norm $\| v  \|_{V,U,1}$.
-To bound $\|\cdot\|_E$ robustly from above or below by a given norm $\left\| u \right\|_{U,2}$ on $U$ now only requires the robust bound in the opposite direction of $\| v \|_{V,U,1}$ by $\|v\|_{V,U,2}$.
-
-For $f$ and $g$ defined in \eqref{adjoint1} and \eqref{adjoint2},
-\begin{align*}
-f &= \epsilon^{-1}\tau + \grad v  \\
-g &=\div \tau - \beta\cdot \grad v,
-\end{align*} 
-we can characterize the test norm for 
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,1}^2 = \|u\|^2 + \|\sigma\|^2 + \epsilon\|\widehat{u}\|^2+ \sqrt{\epsilon}\|\widehat{u}\|^2
-\]
-through the equivalence relation
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,U,1} &\simeq \sup_{u,\sigma,\widehat{u},\widehat{f}_n}\frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\|u\| + \|\sigma\| + \epsilon\|\widehat{u}\|+ \sqrt{\epsilon}\|\widehat{u}\|}\\
-& \simeq \|g\| + \|f\| + \frac{1}{\epsilon}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle \jump{\tau\cdot n}, \widehat{u}\rangle}{\|\widehat{u}\|} + \frac{1}{\sqrt{\epsilon}}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, \jump{v}\rangle}{\|\widehat{f}\|},
-\end{align*}
-which, by definition of the boundary norms, is 
-\[
-\|\left(v,\tau\right)\|_{V,U,1} \simeq \|g\| + \|f\| + \frac{1}{\epsilon}\|\jump{\tau\cdot n}\| + \frac{1}{\sqrt{\epsilon}}\|\jump{v}\|.
-\]
-We wish to show the bound
-\[
-\nor{\left(v,\tau\right)}_{V,\Oh} \lesssim \|g\| + \|f\| + \frac{1}{\epsilon}\|\jump{\tau\cdot n}\| + \frac{1}{\sqrt{\epsilon}}\|\jump{v}\|.
-\]
-By noting that both 
-\begin{align*}
-\nor{C_vv_0} &\leq \nor{v_0},\\
-\nor{C_\tau\tau_0} &\leq \frac{1}{\sqrt{\epsilon}}\nor{\tau_0},
-\end{align*}
-we have that $\nor{\left(v,\tau\right)}_{V,\Oh} \leq \nor{\left(v,\tau\right)}_{V}$, so it suffices to prove the bound for the mesh-independent test norm 
-\[
-\|\left(v,\tau\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2.
-\]
-
-We will bound $\|\left(v,\tau\right)\|_V$ for all $\left(v,\tau\right)$ by decomposing $\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right)$ as described in Section~\ref{sec:strategy2}.
-
-By the triangle inequality, robustly bounding $\|\left(v,\tau\right)\|_V$ from above reduces to robustly bounding each component 
-\[
-\|\left(v_{0},\tau_{0}\right)\|_V, \|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|g\| + \|f\| + \frac{1}{\epsilon}\|\jump{\tau\cdot n}\| + \frac{1}{\sqrt{\epsilon}}\|\jump{v}\|.
-\]
-
-%Roughly speaking, Lemma \ref{lemma_grad} concerns the robust control of $u$ by the energy error; Lemmas \ref{lemma_stream} and \ref{lemma_boundary} concern the robust control of field variable $\sigma$ and flux/trace variables, respectively.
-
-\begin{itemize}
-\item \textbf{Bound on $\|\left(v_{0},\tau_{0}\right)\|_V$}
-
-Lemma \ref{lemma_boundary} gives control over $\sqrt{\epsilon}\|\grad v_0\| + \frac{1}{\epsilon}\|\tau_0\|$ through
-\[
-\|\grad v_0\| = \frac{1}{\epsilon}\|\tau_0\| \lesssim \frac{1}{\epsilon} \nor{\jump{\tau_0\cdot n}}_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \nor{\jump{v_0}}_{\Gamma_h^0 \cup \Gamma_+} = \frac{1}{\epsilon} \nor{ \jump{\tau\cdot n}}_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \nor{ \jump{v}}_{\Gamma_h^0 \cup \Gamma_+}.
-\]
-Lemma 4.2 of \cite{analysisDPG} gives us the Poincare inequality for discontinuous functions
-\[
-\|v_0\| \lesssim \|\grad v_0\| + \|\jump{v}\|.
-\]
-%Since $f=0$, by Lemma 2, $\|\beta\cdot \grad v_0\|  \lesssim \|g\| = 0$.  
-Since $g = 0$, $\| \div \tau_0\| = \|\beta\cdot \grad v_0\|\lesssim \|\grad v_0\|$, which we now have control over as well.
-
-\item \textbf{Bound on $\|\left(v_{1},\tau_{1}\right)\|_V$}
-
-With $f = 0$, Lemma \ref{lemma_stream} provides the bound
-\[
-\|\beta \cdot \grad v_1 \| \lesssim \| g\|.
-\]
-Noting that $\div \tau_1 = g+\beta\cdot \grad v_1$ gives $\|\div \tau_1 \| \lesssim \|g\|$ as well.  Lemma \ref{lemma_grad} gives
-\[
-\epsilon \|\grad v_1\|^2 + \|v_1\|^2 \lesssim \|g\|^2,
-\]
-and noting that $\epsilon^{-1/2}\tau_1 = \epsilon^{1/2}\grad v_1$ gives $\epsilon\|\grad v_1\|^2 = \epsilon^{-1}\|\tau_1\|^2 \lesssim \|g\|^2$ as well.
-
-\item \textbf{Bound on $\|\left(v_{2},\tau_{2}\right)\|_V$}
-
-Lemma \ref{lemma_grad} provides, for $\epsilon$ sufficiently small, 
-\[
-\epsilon \|\grad v_2\|^2 + \|v_2\|^2 \lesssim  \epsilon \| f\|^2 \leq \|f\|^2.
-\]
-We have $\epsilon^{-1}\tau_2 = f - \grad v_2$, so $\epsilon^{-1} \|\tau_2\| \lesssim \|f\| + \|\grad v_2\|$.
-Lemma~\ref{lemma_grad} implies $\|\grad v_2\|^2  \lesssim  \| f\|^2$, so for $\epsilon \leq 1$, we have $\epsilon^{-1/2}\|\tau_2\| \leq \epsilon^{-1}\|\tau_2\| \lesssim \|f\|$.
-The remaining terms can be bounded by noting that, with $g = 0$, $\|\div \tau_2\| = \|\beta\cdot \grad v_2\| \lesssim \|\grad v_2\| \lesssim \|f\| $.
-\end{itemize}
-
-We have shown the robust bound of the norm $\|\cdot \|_{U,1}$ on $U$ by the energy norm; for a full equivalence statement, we require a bound from above on the energy norm by the norm $\|\cdot \|_{U,2}$ on $U$.
-By the duality of the energy and test norm, this is equivalent to bounding the test norm from below by the test norm induced by $\|\cdot \|_{U,2}$.
-For a norm on $U$ of the form
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,2}^2 = \|u\|^2 + \nor{C_\sigma \sigma}^2 + \frac{1}{{\epsilon}}\left( \|\widehat{u}\|^2 + \|\widehat{f}_n\|^2\right),
-\]
-the induced test norm is equivalent to
-\begin{align*}
-\| \left(\tau,v\right) \|_{V,U,2} &\simeq \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E} \\
-&\simeq \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \jump{\tau_n}, \widehat{u} \rangle + \langle \widehat{f}_n, \jump{v} \rangle
-}{\|u\| + \nor{\left(\epsilon C_\tau\right)^{-1}\sigma} + \frac{1}{\sqrt{\epsilon}}\left(  \|\widehat{u}\| + \|\widehat{f}_n\| \right)} \\
-&\simeq \|g\| + \nor{\epsilon C_\tau f} + {\sqrt{\epsilon}}\left(\sup_{\widehat{u},\widehat{f}_n \neq 0}\frac{\langle \jump{\tau_n}, \widehat{u} \rangle + \langle \widehat{f}_n, \jump{v} \rangle}{\|\widehat{u}\| + \|\widehat{f}_n\|}\right),
-\end{align*}
-where $f$ and $g$ are 
-\begin{align*}
-f &= \frac{1}{\epsilon}\tau + \grad v\\
-g &= \div \tau - \beta \cdot \grad v,
-\end{align*}
-the loads of the adjoint problem defined in \eqref{adjoint1}, \eqref{adjoint2}.
-
-Note that $\epsilon C_\tau \leq \sqrt{\epsilon}$. Then, by the triangle inequality, we have the bounds
-\begin{align*}
-%\sqrt{\epsilon} \|f \| &\leq \epsilon^{-1/2} \| \tau\| + \sqrt{\epsilon} \|\grad v\| \lesssim \|\\
-\|\epsilon C_\tau f \| &\leq C_\tau \nor{ \tau} + \epsilon C_\tau \nor{\grad v} \lesssim \| \left(\tau,v\right)\|_{V,\Oh}\\
-\|g \| &\leq \|\div \tau\| +  \|\beta \cdot \grad v\| \lesssim \| \left(\tau,v\right)\|_{V,\Oh}
-\end{align*}
-We estimate the supremum on the jumps of $\left(\tau,v\right)$ by following \cite{DPGrobustness}; we begin by choosing $\eta \in H({\rm div}; \Omega)$, $w\in H^1(\Omega)$, such that $\left.\left(\eta-\beta w \right)\cdot n\right |_{\Gamma_+} = 0$ and $\left.w\right |_{\Gamma_-\cup\Gamma_0} = 0$, and integrating the boundary pairing by parts to get
-\begin{align*}
-\langle \jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle &= (\tau,\grad w) + (\div \tau, w) + \left(\eta - \beta w, \grad v\right) +  \left(\div \left(\eta - \beta w\right), v\right)\\
-&\lesssim \|C_\tau\tau\| \nor{ \frac{1}{C_\tau}\grad w} + \|\div \tau\| \|w\| \\
-&\left.\hspace{.3cm}\right. + \sqrt{\epsilon}\| \grad v \|\frac{1}{\sqrt{\epsilon}}\|\eta\| +  \|\beta \cdot \grad v\| \| w\|\\
-&\left.\hspace{.3cm}\right. + \|C_vv\|\nor{\frac{1}{C_v}\div \eta} + \| C_vv\| \nor{\frac{1}{C_v}w} \\
-&\left.\hspace{.3cm}\right. + \|C_v v\| \nor{\frac{1}{C_v} \grad w},
-\end{align*}
-where we have used that $\epsilon < 1$, $\div \beta = O(1)$, and that $\|\beta\cdot \grad w\|\lesssim \|\grad w\|$.
-
-Without loss of generality, assume the problem is scaled such that $\max_{K\in\Oh}|K| \leq 1$.
-Then, $\frac{1}{C_\tau^2}\leq \frac{1}{C_v^2} \leq \frac{1}{\epsilon}$, and an application of discrete Cauchy-Schwarz gives us
-\begin{align*}
-\langle \jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle &\lesssim \|\left(\tau,v\right)\|_{V,\Oh}\frac{1}{\sqrt{\epsilon}}\left(\nor{\eta}_{H({\rm div},\Omega)} + \nor{w}_{H^1(\Omega)}\right),\\
-&\lesssim \|\left(\tau,v\right)\|_{V,\Oh}\frac{1}{\sqrt{\epsilon}}\left(\nor{\eta-\beta w}_{H({\rm div},\Omega)} + \nor{w}_{H^1(\Omega)}\right),
-\end{align*}
-since $\|\eta\|_{H({\rm div},\Omega)} = \|\eta - \beta w + \beta w\|_{H({\rm div},\Omega)} \leq \|\eta - \beta w\|_{H({\rm div},\Omega)} + \|\beta w\|_{H({\rm div},\Omega)} \lesssim \|\eta-\beta w\|_{H({\rm div},\Omega)} + \|w\|_{H^1(\Omega)}$.
-Dividing through and taking the supremum gives
-\[
-\sup_{w,\eta \neq 0} \frac{\langle\jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle}{\left(\nor{\eta-\beta w}_{H({\rm div},\Omega)} + \nor{w}_{H^1(\Omega)}\right)} \lesssim \|\left(\tau,v\right)\|_{V,\Oh}\frac{1}{\sqrt{\epsilon}}.
-\]
-To finish the proof, define $\rho \in H^{1/2}(\Gamma_h)$ and $\phi \in H^{-1/2}(\Gamma_h)$ such that $\rho = \left.w\right|_{\Gamma_h}$ and $\phi = \left.(\eta-\beta w)\cdot n\right|_{\Gamma_h}$, and note that, from \cite{analysisDPG}, by the definition of the trace norms on $\jump{\tau\cdot n}$ and $\jump{v}$
-\begin{align*}
-\sup_{\rho,\phi \neq 0} \frac{\langle \jump{\tau\cdot n},\rho\rangle + \langle \jump{v},\phi \rangle}{\|\rho\|_{H^{1/2}(\Gamma_h)}+\|\phi\|_{H^{-1/2}(\Gamma_h)}} &= \sup_{w,\eta \neq 0} \frac{\langle \jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle}{ \|w\|_{H^1(\Omega)}+\|\eta-\beta w\|_{H({\rm div},\Omega)}}.
-\end{align*}
-Together, the bounds on the jump terms and the bounds on $\|g\|$ and $\|f\|$ imply $\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{E} \lesssim \left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,2}$.
-\end{proof}
-
-\subsubsection{Comparison of boundary conditions}
-
-It is worth addressing the effect of boundary conditions on stability.
-Specifically, a test norm that provides stability for one set of boundary conditions may perform poorly for another set.
-Take, for example, the test norm defined in Section~\ref{sec:main_bounds} and the convection-diffusion problem with Dirichlet boundary conditions.
-
-The bilinear form for the case of Dirichlet boundary conditions is 
-\[
-b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(v,\tau\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) + \langle \widehat{u}, \jump{\tau \cdot n} \rangle_{\Gh^0} + \langle \widehat{f}_n, \jump{v} \rangle_{\Gh}.
-\]
-Notice that the boundary terms in the final bilinear form are different; hence, the adjoint problems associated with Section~\ref{sec:strategy3} will now carry different boundary conditions as well.
-Likewise, the stability properties proven previously will not hold under a different set of boundary conditions.
-%We note that 
-%\begin{align*}
-%b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gh^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gh}
-%&= \| u \|^2_{L^2}
-%\end{align*}
-%for the specific continuous test functions $\tau$ and $v$ satisfying
-%\begin{align*}
-%\div \tau - \beta \cdot \grad v &= u \\
-%\frac{1}{\epsilon}\tau + \grad v &= 0
-%\end{align*}
-%with boundary condition $\left.v\right|_\Gamma = 0$.
-Choosing a continuous conforming test function $v$ removes the contribution of the term $\langle \widehat{f}_n, \left[v\right] \rangle$ on the mesh skeleton, while the boundary conditions remove the contribution of boundary terms from the bilinear form.
-Then, for this specific choice of $\left(\tau, v\right)$,
-%\begin{align*}
-%\|u\|_{L^2}^2 &= b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right)}{\|\left(\tau, v\right)\|_V}\|\left(\tau, v\right)\|_V \leq \|u\|_E \|\left(\tau, v\right)\|_V
-%\end{align*}
-%At minimum, we want $\|u\|_{L^2} \lesssim \|u\|_E$, which requires 
-%\[
-%\|\left(\tau, v\right)\|_V \lesssim \| u \|_{L^2}
-%\]
-%for any choice of $u \in L^2$ (dividing through by $\|u\|_{L^2}$ gives the desired result).
-This can be considered a ``sanity check"; at the minimum, we at least want control over the behavior of the single field variable $u$.
-However, we are unable to prove this in the case of Dirichlet boundary conditions.
-
-As it turns out, the robust bounds given in Section~\ref{sec:main_bounds} hold in $\mathbb{R}^d$ for arbitrary $d$; however, we can show that for the case of Dirichlet boundary conditions, the same results do not hold, even in 1D.
-%In 1D, the problem reduces to 
-%\begin{align*}
-%\frac{1}{\epsilon}\sigma - u' &= 0\\
-%\left(u - \epsilon \sigma \right)' &=f
-%\end{align*}
-%with bilinear form
-%\begin{align*}
-%b\left(\left(u,\sigma,\widehat{u},\widehat{f}\right),\left(\tau,v\right)\right) &= \sum_{k=1}^N \left(\left.\widehat{u}(x) \tau(x)\right |^{x_k}_{x_{k-1}} + \left.\widehat{f}(x) v(x)\right |^{x_k}_{x_{k-1}}\right) \\
-%&+ \left(\sigma,\epsilon^{-1}\tau\right)_{\Oh} + (u,\tau')_{\Oh}- \left(u - \epsilon \sigma,v'\right)_{\Oh}
-%\end{align*}
-%where $\widehat{u}(x), \widehat{f}(x) \in \mathbb{R}$ are now point values defined on mesh points $x_k$ for $k=1,\ldots,N$, where $N$ is the number of elements.
-We can assume without loss of generality that $\Oh$ is the unit interval $(0,1)$.
-%
-%Let us first provide an interpretation of Lemma~\ref{lemma_stream}. Recall the bilinear form 
-%\begin{align*}
-%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-%\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
-%v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh} - \LRa{
-%\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n,
-%  \jump{v} }_{\Gh},
-%\end{align*}
-%By choosing $(v,\tau)$ such that
-%\begin{align*}
-%\div \tau - \beta \cdot \grad v &= u \\
-%\frac{1}{\epsilon} \tau + \grad v &= 0
-%\end{align*}
-%we will have 
-%\[
-%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-%\left( v, \tau \right)\right) =\|u\|_{L^2}^2 
-%\]
-%Given this, we can use the definition of the energy norm \eqnref{energyNorm} to bound
-%\[
-%\|u\|_{L^2}^2 = b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-%\left( v, \tau \right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-%\left( v, \tau \right)\right)}{\|(v,\tau)\|_V}\|(v,\tau)\|_V \lesssim \|u\|_E \|(v,\tau)\|_V
-%\]
-%If we can show that $\|(v,\tau)\|_V \lesssim \|u\|_{L^2}$ for $(v,\tau)$ as defined above, then this implies 
-%\[
-%\|u\|_{L^2} \lesssim \|u\|_E
-%\]
-%By the fact that 
-Consider now the 1D analogue of the estimate given by Lemma~\ref{lemma_stream}.  In 1D, $\|\beta\cdot\grad v_1\| \lesssim \|g\|$ reduces to the inequality 
-\[
-\|\beta v_1'\|\lesssim \|g\|, \quad g\in L^2\!\left(\Oh\right).
-\]
-Without this inequality, we are unable to prove the robust bound on the $L^2$ error $\|u-u_h\|_{L^2} \lesssim \nor{(u,\sigma,\widehat{u},\widehat{f}_n)-(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h})}_E$.
-
-The adjoint problem corresponding to Lemma~\ref{lemma_stream} in Section~\ref{sec:strategy3} is likewise reduced in 1D to the scalar equation
-\begin{align}
-\epsilon v_1'' + \beta v_1' &= -g \label{adjoint_1D}
-\end{align}
-with $v_1\in H^1_0\left((0,1)\right)$.  After multiplying this equation by $\beta v_1'$ and integrate by parts over $\Oh$, we can apply Young's inequality to get
-%\[
-%\int_0^1 \epsilon v_1'' \beta v_1' + \|\beta v_1'\|_{L^2}^2 = -\int_0^1 g \beta v_1'.\
-%]
-%Integrating by parts and Young's inequality gives
-\begin{align*}
-\left.\frac{\epsilon}{2} \beta v_1'^2\right|_0^1 + \|\beta v_1'\|_{L^2}^2 &\leq \frac{1}{2}\|g\|^2 + \frac{1}{2}\|\beta v_1'\|^2,
-\end{align*}
-implying that
-\begin{align*}
-\|\beta v_1'\|_{L^2}^2 & \lesssim \|g\|^2 + {\beta \epsilon} v_1'(0)^2.
-\end{align*}
-Let us restrict ourselves to the cases where $v_1$ is sufficiently smooth for $v'(0)$ to be well defined.
-Taking $g=1$ (corresponding to a piecewise constant approximation) we can solve \eqref{adjoint_1D} exactly.
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.5]{figs/testBoundary1D.png}
-\caption{$v_1(x) = \frac{e^{-\frac{x}{\epsilon}}}{e^{\frac{1}{\epsilon}}-1}\left(e^{\frac{1}{\epsilon}}\left(e^{\frac{x}{\epsilon}}-1\right) + \left(e^{\frac{1}{\epsilon}}-1\right)e^{\frac{x}{\epsilon}}x\right)$, the solution to the adjoint equation for $f=0$ and constant $\beta$ and load $g$ for $\epsilon = .01$.}
-\label{fig:testBoundary1D}
-\end{figure}
-The solution $v_1$ is plotted in Figure~\ref{fig:testBoundary1D}, where we can see that $v_1(x)$ develops strong boundary layers of width $\epsilon$ near the inflow boundary $x=0$.
-Consequently, $\frac{\epsilon}{2} v_1'(0)^2 \approx \epsilon^{-1}$.
-Thus, we cannot conclude $\|\beta v'\| \lesssim \|g\|$ when $g$ is a constant,\footnote{Unlike the case of Dirichlet boundary conditions, the inflow condition on $ \widehat{f}_n = u(0)-\epsilon u'(0)$ induces an adjoint boundary condition $\tau(0)=0$, or equivalently $v'(0) = 0$, removing the non-robust term from the estimate.} and as a consequence cannot conclude that the robust error bound $\|u-u_h\|_{L^2} \lesssim \|(u,\sigma,\widehat{u},\widehat{f}_n)-(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h})\|_E$ holds for the solution $u_h$.
-More detailed 1D error bounds for Dirichlet boundary conditions are provided in \cite{DPG3}, and indicate the same lack of robustness under the test norm used thus far.\footnote{Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
-\[
-\|\left(\tau, v\right)\|_{V,w}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\|_{w+\epsilon} + \| \div \tau\|_{w+\epsilon} + \frac{1}{\epsilon}\|\tau\|_{w+\epsilon}
-\]
-where $\|\cdot \|_{w+\epsilon}$ is a weighted $L^2$ norm, where the weight $w \in (0,1)$ is required to vanish on $\Gamma_-$ and satisfy $\grad w = O(1)$.
-The need for this weight is necessary to account for the loss of robustness at the inflow.}
-
-\begin{figure}[h!]
-\centering
-\subfigure[Primal problem, Dirichlet inflow BC]{\includegraphics[scale=.3]{figs/primalDir.png}}
-\subfigure[Adjoint problem, Dirichlet inflow BC]{\includegraphics[scale=.3]{figs/adjointDir.png}}
-\subfigure[Primal problem, new inflow BC]{\includegraphics[scale=.3]{figs/primal.png}}
-\subfigure[Adjoint problem, new inflow BC]{\includegraphics[scale=.3]{figs/adjoint.png}}
-\caption{Comparison of primal and adjoint problems under both the standard Dirichlet and the new inflow boundary condition.
-The outflow boundary for each problem is denoted in red.
-For the standard Dirichlet inflow condition, the solution to the adjoint problem can develop strong boundary layers at the outflow of the adjoint problem.
-Notice, under the new inflow conditions, the relaxation of a wall-stop boundary condition with a zero-stress condition at the outflow boundary of the adjoint problem.}
-\end{figure}
-
-In higher dimensions, the adjoint problem is of the same form as the primal problem with the direction of convection reversed.
-However, the primal problem determines adjoint boundary conditions on $\Gamma_-$ and $\Gamma_+$.
-Thus, wheareas for the primal problem, data is convected from the inflow to the outflow, in the adjoint problem, data is convected from the outflow to the inflow boundary instead.
-
-We can intuitively explain the loss of robustness under our derived test norm by the presence of the Dirichlet boundary condition on $v$ at the inflow boundary.
-Since the direction of convection is reversed in the adjoint equation, we can interpret the adjoint as representing the convection of a concentration $v$ from the outflow to the inflow boundary.
-In the presence of a Dirichlet boundary condition at the inflow, $v$ can develop strong boundary layers at the inflow.
-As a consequence, the quantities $\|\beta\cdot \grad v\|$ and $\sqrt{\epsilon}\|\grad v\|$ are no longer robustly bounded by $\|f\|$ and $\|g\|$, and we can no longer derive robust bounds on the error $\|u-u_h\|_{L^2}$ by the error in the energy norm.
-
-Recall our strategy for analysis was to decompose of $(v,\tau)$ into continuous and discontinuous portions.
-Mathematically speaking, the use of Dirichlet boundary conditions on the primal problem introduces strong boundary layers into the solution $v$ of the adjoint equation --- in other words, boundary layers are introduced into the continuous portions of our decomposition of $(v,\tau)$.\footnote{The boundary conditions do not introduce boundary layers into the actual computed test functions.
-However, an interesting phenomenon observed is that, for small $\epsilon$, a lack of robustness can manifest itself during numerical experiments as additional refinements near the inflow boundary, precisely where the continuous parts of the decomposition of $(v,\tau)$ develop boundary layers.} The new inflow boundary condition on the primal problem relaxes the wall boundary condition induced on the adjoint/dual problem with a boundary condition that does not generate boundary layers, resulting in stronger stability estimates for the adjoint, and a better result for the primal problem.
-
-%\begin{figure}[h]
-%\centering
-%\subfigure[Primal problem]{\includegraphics[scale=.3]{figs/primal.png}}
-%\subfigure[Adjoint problem]{\includegraphics[scale=.3]{figs/adjoint.png}}
-%\caption{Comparison of primal and adjoint problems for convection-diffusion under the standard Dirichlet outflow boundary condition and the new inflow boundary condition.
-Notice the replacement of a wall-stop boundary condition with a Neumann stress boundary condition at the outflow boundary of the adjoint problem.
-}
-%\end{figure}
-
-\section{Numerical experiments: Eriksson-Johnson problem}
-\label{sec:num_exp}
-
-In each numerical experiment, we vary $\epsilon = .01, .001, .0001$ in order to demonstrate robustness over a range of $\epsilon$.
-This is intended to mirror the experience with roundoff effects in numerical experiments \cite{DPGrobustness}; for ``worst-case" linear solvers, such as LU decomposition without pivoting, the effect of roundoff error becomes evident in the solving of optimal test functions for $\epsilon \leq O(1e-5)$.
-The roundoff itself comes from the conditioning of the Gram matrix under certain test norms; for example, if the weighted $H({\rm div};\Omega)\times H^1(\Omega)$ norm is used for the test norm $\|\left(\tau,v\right)\|_V$ (as was done in \cite{DPG2}), for an element of size $h$, $\|v\|_{L^2}^2 = O(h)$, while $\|\grad v\|_{L^2}^2 = O(h^{-1})$.
-As $h\rightarrow 0$, the seminorm portion of the test norm dominates the Gram matrix, leading to a near-singular and ill-conditioned system.
-
-The effect of roundoff error is often characterized by an increase in the energy error, which (assuming negligible error in the approximation of test functions) is proven to decrease for any series of refined meshes.
-These roundoff effects are dependent primarily on the mesh, appearing when trying to fully resolve very thin boundary layers by introducing elements of size $\epsilon$ through adaptivity.
-The effects of roundoff error were successfully treated in \cite{DPG3} by dynamically rescaling the test norms based on element size, a practical remedy not covered yet by the present analysis.
-
-To confirm our theoretical results, we adopt a modification of a problem first proposed by Eriksson and Johnson in \cite{Eriksson1993}.
-For the choice of $\Omega = (0,1)^2$, $f=0$, and $\beta = (1,0)^T$, the convection diffusion equation reduces to
-\[
-\pd{u}{x} - \epsilon \left(\pdd{u}{x}+ \pdd{u}{y}\right) = 0,
-\]
-which has an exact solution by separation of variables, allowing us to analyze convergence of DPG for a wide range of $\epsilon$.
-For boundary conditions, we impose $u=0$ on $\Gamma_+$ and $\beta_n u - \sigma_n$ on $\Gamma_-$, which reduces to
-\begin{align*}
-u-\sigma_x &= u_0-\sigma_{x,0}, \quad x=0,\\
-\sigma_y &=  0, \quad y=0,1,\\
-u &= 0, \quad x=1.\\
-\end{align*}
-In this case, our exact solution is the series
-\[
-u(x,y) = C_0 + \sum_{n=1}^\infty C_n \frac{\exp(r_2(x-1)-\exp(r_1(x-1)))}{r_1\exp(-r2) - r_2\exp(-r1)}\cos(n\pi y),
-\]
-where
-\begin{align*}
-r_{1,2} &= \frac{1 \pm \sqrt{1 + 4 \epsilon\lambda_n}}{2 \epsilon},\\
-\lambda_n &= n^2\pi^2 \epsilon.
-\end{align*}
-The constants $C_n$ depend on a given inflow condition $u_0$ at $x=0$ via the formula
-\[
-C_n = \int_0^1 u_0(y) \cos(n\pi y).
-\]
-
-All computations have been done using the adaptive DPG code Camellia, built on the Sandia toolbox Trilinos \cite{Camellia}.
-
-\subsection{Solution with $C_1 = 1, C_{n\neq 1} = 0$}
-
-We begin with the solution taken to be the first non-constant term of the above series.
-We set the inflow boundary condition to be exactly the value of $u-\sigma_x$ corresponding to the exact solution.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.37]{figs/wallBC_exact_u.png}
-}
-\subfigure{
-\includegraphics[scale=.37]{figs/wallBC_exact_sigx.png}
-}
-\subfigure{
-\includegraphics[scale=.37]{figs/wallBC_exact_sigy.png}
-}
-\caption{Solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
-\end{figure}
-In each case, we begin with a square 4 by 4 mesh of quadrilateral elements with order $p=3$.
-We choose $\Delta p = 5$, though we note that the behavior of DPG is nearly identical for any $\Delta p \leq 3$, and qualitatively the same for $\Delta p = 2$.
-$h$-refinements are executed using a greedy refinement algorithm, where element energy error $e_K^2$ is computed for all elements $K$, and elements such that $e_K^2 \leq \alpha \max_K e_K^2$ are refined.
-We make the arbitrary choice of taking $\alpha = .2$ for each of these experiments.
-
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=.4]{figs/u_pointdiff_wallBC.png}
-\caption{Adapted mesh and pointwise error for $\epsilon=.01$}
-\end{figure}
-We are especially interested in the ratio of energy error and total $L^2$ error in both $\sigma$ and $u$, which we denote as $\|u-u_h\|_{L^2}$.
-The bounds on $\nor{\cdot}_E$ presented in Section~\ref{sec:main_bounds} imply that, using the above test norm, $\|u-u_h\|_{L^2} / \|u-u_h\|_E \leq C$ independent of $\epsilon$.
-Figure~\ref{ratios_simple}, which plots the ratio of $L^2$ to energy error, seems to imply that (at least for this model problem) $C=O(1)$.
-Additionally, while we do not have a robust lower bound ($\|u-u_h\|_{L^2} / \|u-u_h\|_E$ can approach $0$ as $\epsilon \rightarrow 0$), our numerical results appear to indicate the existence of an $\epsilon$-independent lower bound.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{figs/errorrates_wallBC.png}
-}
-\subfigure{
-\includegraphics[scale=.38]{figs/L2energyratio_wallBC.png}
-}
-\caption{$L^2$ and energy errors, and their ratio for $\epsilon=.01$, $\epsilon=.001$, $\epsilon=.0001$}
-\label{ratios_simple}
-\end{figure}
-The effect of a mesh dependent scalings on the $\|v\|^2$ and $\|\tau\|^2$ terms in the test norm can be seen in the ratios of $L^2$ to energy error; as the mesh is refined, the constants in front of the $L^2$ terms for $v$ and $\tau$ converge to stationary values (providing the full robustness implied by our adjoint energy estimates), and the ratio of $L^2$ to energy error transitions from a smaller to a larger value.
-The transition point happens later for smaller $\epsilon$, which we expect, since the transition of the ratio corresponds to the introduction of elements whose size is of order $\epsilon$ through mesh refinement.
-
-We examined how small $\epsilon$ needed to be in order to encounter roundoff effects as well.
-In \cite{DPGrobustness}, the smallest resolvable $\epsilon$ using only double precision arithmetic was $1e-4$.
-The solution of optimal test functions is now done using both pivoting and equilibration, improving conditioning.
-Roundoff effects still appear, but at smaller values of $\epsilon$.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.36]{figs/roundoff_rates.png}
-}
-\subfigure{
-\includegraphics[scale=.36]{figs/roundoff_ratio.png}
-}
-\caption{Energy error and $L^2$/energy error ratio for $\epsilon=1e-5$, $\epsilon=1e-6$, $\epsilon=1e-7$.
-Non-monotonic behavior of the energy error indicates conditioning issues and roundoff effects.}
-\label{roundoff_figures}
-\end{figure}
-
-Without anisotropic refinements, it still becomes computationally difficult to fully resolve the solution for $\epsilon$ smaller than $1e-5$.
-Regardless, for all ranges of $\epsilon$, DPG does not lose robustness, as indicated by the rates and ratio between $L^2$ and energy error in Figure~\ref{roundoff_figures} remaining bounded from both above and below.
-For $\epsilon = 1e-5$, we observe that the ratio of $L^2$ error increases, corresponding to the scaling of the test norm with mesh size (the transition in test norm occurs after 8 refinements, which, for an initial $4\times 4$ mesh, implies a minimum element size of about $1.5e-05$.
-At this point, rescaled test norm allows us to take advantage of the full magnitude of the $L^2$ term for $\|v\|$ and $\|\tau\|$ implied by our adjoint estimates).
-By analogy, for smaller $\epsilon = 1e-6, 1e-7$, the transition period should begin near the 10th and 11th refinement iterations; however, we do not observe such behavior, possibly due to roundoff effects.
-For $\epsilon=1e-6$, the ratio simply remains constant, but for $\epsilon=1e-7$, we observe definite roundoff effects, as the energy error increases at the 11th refinement.
-Since DPG is optimal in the energy norm for a mesh-independent test norm\footnote{While the test norm changes with the mesh, it increases monotonically.
-A strictly stronger test norm implies $\frac{b(u,v)}{\|v\|_1} \geq \frac{b(u,v)}{\|v\|_2}$ for any $\|v\|_1 \leq \|v\|_2$}, we expect monotonic decrease of the energy error with mesh refinement.
-Non-monotonic behavior indicates either approximation or roundoff error, and as we observed no qualitative difference between using $\Delta p = 5$ and $\Delta p = 6$ for these experiments, we expect that the approximation error is negligible and conclude roundoff effects are at play when these phenomena are observed.
-
-It is worth noting that for $\epsilon \leq 1e-5$, we do not perform enough refinements to completely resolve the boundary layer, so $|K| \geq \epsilon$ for all $K\in \Oh$.
-Thus, any roundoff effects observed are not due to the conditioning issues associated with the differing scales of the $\nor{v}_{L^2(K)}$ and $\nor{\grad v}_{L^2(K)}$ terms discussed previously.
-
-\subsection{Neglecting $\sigma_n$}
-
-In practice, we will not have prior knowledge of $\sigma_n$ at the inflow, and will have to set $\beta_n u - \sigma_n = u_0$, ignoring the viscous contribution to the boundary condition.
-The hope is that for small $\epsilon$, this omission will be negligible.
-Figure~\ref{ratios_noSigma} indicates that, between $\epsilon = .005$ and $\epsilon = .001$, the omission of $\sigma_n$ in the boundary condition becomes negligible, and both our error rates and ratios of $L^2$ to energy error become identical to the case where $\sigma_n$ is explicitly accounted for in the inflow condition.
-For large $\epsilon = .01$, the $L^2$ error stagnates around $1e-3$, or about $7\%$ relative error.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{figs/rates_noSigma.png}
-}
-\subfigure{
-\includegraphics[scale=.38]{figs/ratio_noSigma.png}
-}
-\caption{$L^2$ and energy errors and their ratio when neglecting $\sigma_n$ at the inflow.}
-\label{ratios_noSigma}
-\end{figure}
-
-\subsection{Discontinuous inflow data}
-
-We note also that an additional advantage of selecting this new boundary condition is a relaxation of regularity requirements: as $\widehat{f}_n \in H^{-1/2}(\Gh)$, strictly discontinuous inflow boundary conditions are no longer ``variational crimes".
-We consider the discontinuous inflow condition
-\[
-u_0(y) = \begin{cases}
-(y-1)^2, \quad &y>.5\\
--y^2, \quad &y\leq .5 
-\end{cases}
-\]
-as an example of a more difficult test case.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{figs/disc_hat.png}
-}
-\subfigure{
-\includegraphics[scale=.38]{figs/disc_hat_surf.png}
-}
-\caption{Solution variables $u$ and $\widehat{u}$ with discontinuous inflow data $u_0$ for $\epsilon = .01$.}
-\label{disc_sol}
-\end{figure}
-Figure~\ref{disc_sol} shows the solution $u$ and overlaid trace variable $\widehat{u}$, which both demonstrate the regularizing effect of viscosity on the discontinuous boundary condition at $x=0$.
-However, we do not have a closed-form solution with which to compare results for a stricly discontinuous $u_0$.
-In order to analyze convergence, we approximate $u_0$ with 20 terms of a Fourier series, giving a near-discontinuity for $u_0$.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.36]{figs/rates_disc.png}
-}
-\subfigure{
-\includegraphics[scale=.36]{figs/ratio_disc.png}
-}
-\caption{$L^2$ and energy errors, and their ratio for $\epsilon=.01$, $\epsilon=.001$, $\epsilon=.0001$, with discontinuous $u_0$ approximated by a Fourier expansion. }
-\label{disc_sol_fourier}
-\end{figure}
-
-The ratios of $L^2$ to energy error are now less predictable than for the previous example, in part due to the difficulty in approximating highly oscillatory boundary conditions.
-The numerical experiments were originally performed by applying boundary conditions via interpolation; the result was that the highly oscillatory inflow boundary condition was not sampled enough to be properly resolved, causing the solution to converge to a solution different than the exact solution.
-The experiments were repeated using the penalty method to enforce inflow conditions; however, we note that the proper way to do so is to use an $L^2$ projection at the boundary.
-Even when using the penalty method, however, the ratios still remain bounded and close to $1$ for $\epsilon$ varying over two orders of magnitude, as predicted by theory.

### 2013-07-30 docs/Jesse/Dissertation/coupledRobust.tex

\section{A coupled, robust test norm}

In the course of our numerical experiments, we encountered unforeseen difficulties for certain problems under our current robust test norm.  We illustrate in this section the observed issue using a second model problem with a singular solution, offer possible explanations for the phenomena observed, and propose a modification of the robust test norm presented previously, which we demonstrate eliminates the issues observed in numerical experiments.

\subsection{A second model problem}
\seclab{sec:confusionPlate}
We begin by first examining a different problem than convection-diffusion -- we examine admissible solutions for the homogeneous Laplace's equation over the $y > 0$ half-plane under boundary conditions 
\begin{align*}
u &= 0 \text{ on } x > 0\\
\pd{u}{n} &= 0 \text{ on } x < 0.
\end{align*}
Let us consider the 2D case - a simple separation of variables argument in polar coordinates shows that the solution is of the form
\[
u(r,\theta) = \sum_{n=0}^\infty R_n(r) \sin(\lambda_n \theta),
\]
where $\lambda_n = n + \frac{1}{2}$, and $R_n(r) = C_{1,n}x^{\lambda_n} + C_{2,n}x^{-\lambda_n}$.  By requiring $u(0,\theta) < \infty$, we have $R_n(r) = C_n x^{\lambda_n}$.  We have now that solutions to this problem include $u$ of the form
\[
u = \sum_{n=0} x^{n+\frac{1}{2}} \sin\LRp{\LRp{n+\frac{1}{2}}\theta}.
\]
Note that, for the lowest-order term, the gradient of $u$ displays a singularity at $r = 0$.  It is well known that, for smooth boundary data, solutions to Laplace's equation can be decomposed into the linear combination of smooth and singular contributions; the above analysis implies that, when boundary conditions change from Dirichlet to Neumann on the half-plane, the Laplace's equation will always develop a singularity in the stresses.

Consider now Laplace's equation $\del u = f$ on the box domain $\Omega = [0,1]^2$ with boundary conditions
\begin{align*}
u &= 0 \text{ on } x > .5\\
\pd{u}{n} &= 0 \text{ on } x < .5.
\end{align*}
with forcing term $f=1$.  
\begin{figure}[!h]
\centering
\subfigure{\includegraphics[scale=.375]{figs/LaplaceFigs/LaplacePlate.png}}
\caption{Solution of Laplace's equation on the unit quad with $f=1$.}
\label{fig:laplace}
\end{figure}
Extrapolating the results from the half-plane example to a finite domain, we expect the solution of Laplace's equation to be bounded, but to have a singularity in its gradient.  Figures~\ref{fig:laplace} and \ref{fig:laplaceStresses} are finite element solutions of the above problem under a quadratic $h$-refined mesh.  Figure~\ref{fig:laplace} confirms that $u$ is bounded, while Figure~\ref{fig:laplaceStresses} confirms that singularities in the gradient appear at the point $(.5,0)$, where the boundary condition changes from Neumann to Dirichlet.

\begin{figure}[!h]
\centering
\subfigure{\includegraphics[scale=.275]{figs/LaplaceFigs/LaplacePlateSigma1.png}}
\subfigure{\includegraphics[scale=.275]{figs/LaplaceFigs/LaplacePlateSigma2.png}}
\caption{$x$ and $y$ components of the $\Grad u$ for $u$ solving Laplace's equation with a change in boundary conditions.  Both components develop singularities at the point where the boundary condition changes type.}
\label{fig:laplaceStresses}
\end{figure}

We consider now the convection-diffusion problem, under a similar setup as before.  We consider the domain $\Omega = [0,1]^2$, with boundary conditions
\begin{align*}
u &= 0,\quad \text{ on } x = 0\\
\pd{u}{n} &= 0,\quad \text{ on } x = 1, y = 1, \text{ and } y = 0, x < .5\\
u &= 1,\quad \text{ on } .5 < x \leq 1.
\end{align*}
The problem is meant to simulate the transport of $u$ over a domain with a ``plate'' boundary $x \in [.5,1]$.  For small $\epsilon$, the problem develops a boundary layer over the plate, as well as a singularity at the plate tip $(x,y) = (.5,0)$.\footnote{This problem is meant to mimic the Carter flat plate problem -- a common early benchmark problem in viscous compressible flow problems -- which can be shown to also exhibit a singularity in stress at the point $(.5,0)$.}  Unlike the Laplace example, we swap the Dirichlet boundary condition at the outflow $x=1$ with an outflow boundary condition.\footnote{The outflow ``boundary condition'' is simply the absence of an applied boundary condition, and is analyzed in more detail in \cite{FLD:FLD505}.  This outflow condition appears to work well for convection-diffusion problems in the convective regime, and is the outflow condition we will use in our extension of DPG to a model problem in viscous compressible flow.  Though the well-posedness of the problem under this boundary condition is questionable, we can still effectively illustrate the issues present under the robust test norm using this problem setup.  }

The above convection-diffusion problem is related back to the earlier Laplace/diffusion problem with a singularity -- in most of the domain, convective effects dominate; however, if we  localize the behavior of Laplace's equation to a circle of $\epsilon$ around $(.5,0)$, then we again see a discontinuity in the stresses.  Asymptotic expansion techniques indicate that singularities in solutions are determined primarily by the highest order differential operator present in the equation -- in other words, the addition of a convective term to a scaled Laplacian (to recover the convection-diffusion equation) will not alter the presence of a singularity in the solution.

\begin{figure}[!h]
\centering
\subfigure{\includegraphics[scale=.275]{figs/LaplaceFigs/confusion1e2h1e2.png}}
\subfigure{\includegraphics[scale=.275]{figs/LaplaceFigs/confusion1e2h1e3.png}}
\caption{Solution $u$ for $\epsilon = .01$ under the robust test norm.  The solution oscillates strongly at the plate edge, growing in magnitude under additional refinements despite the absence of a singularity in $u$ at that point.}
\label{fig:plateOsc}
\end{figure}

Figures~\ref{fig:plateOsc} and \ref{fig:plateOscZoom} demonstrate the behavior of the DPG method under the robust test norm for the plate problem.  The diffusion is taken to be fairly large ($\epsilon = 10^{-2}$), and automatic refinements are done until the element size $h$ is at or below the diffusion scale.  Due to the singular nature of the solution, refinements are clustered around $(.5,0)$, and the order is set to be uniform with $p=2$.  While there should be no singularity in $u$, the magnitude of $u$ grows as $h \rightarrow 0$, so long as $h\leq \epsilon$.

\begin{figure}[!h]
\centering
\includegraphics[scale=.375]{figs/LaplaceFigs/confusion1e2h1e3uZoom.png}
\caption{Zoomed solution $u$ and adaptive mesh for $\epsilon = .01$ after over-resolution of the diffusion scale. }
\label{fig:plateOscZoom}
\end{figure}

We note that the appearance of this non-physical singularity in $u$ is allowed under the theory underlying the robust test norm; the error in the $\L$-norm of the solution is guaranteed to be robustly bounded; however, the $\L$ norm does allow for the presence of weak singularities (singularities of order $x^{-\frac{1}{2}}$).  Apart from the oscillation of $u$ at the singular point, the solution is well-behaved, and the stress $\sigma = \epsilon \Grad u$ is very well represented, as indicated in Figure~\ref{fig:plateStresses}.

\begin{figure}[!h]
\centering
\subfigure{\includegraphics[scale=.275]{figs/LaplaceFigs/confusion1e2h1e3Sigma1.png}}
\subfigure{\includegraphics[scale=.275]{figs/LaplaceFigs/confusion1e2h1e3Sigma2.png}}
\caption{Viscous stresses for the plate problem.  }
\label{fig:plateStresses}
\end{figure}

\subsection{A modification of the robust test norm}

While oscillations of this sort in a solution near a singular point may be acceptable in certain simulations, it is a large problem for the methods in compressible flow simulations -- physical constraints require several solution variables to remain positive throughout simulation.\footnote{Apart from returning a non-physical solution, the violation of positivity constraints typically results in non-convergence of nonlinear solvers.}  We propose a modification of the robust test norm that appears to remedy this issue, which we refer to as 
\[
\nor{\LRp{v,\tau}}_V^2 \coloneqq \nor{v}^2_{\L} + \epsilon \nor{\grad v}^2_{\L} + \nor{\beta\cdot \Grad v}_{\L}^2 + \nor{\div \tau - \beta\cdot\Grad v}_{\L}^2 + \nor{C_\tau\tau}_{\L}^2,
\]
where $C_\tau$ is defined as before.\footnote{We note that we have dropped the mesh-dependent scaling on $\nor{v}_{\L}$ from the robust norm; this is related to recent insights into the nature of DPG test spaces and explained in more detail in Appendix~\secref{appendix:globalLocal}.}  We note that, under the theory developed in Section~\secref{sec:testNormSec}, the above test norm is trivially provably robust using the same theory.\footnote{This is due to the fact that $\nor{\div \tau - \beta\cdot\Grad v}_{\L}^2$ is robustly bounded by $\nor{\div \tau}_{\L}$ and $\nor{\beta\cdot\Grad v}_{\L}$.  Alternatively, we can note that $\nor{\div \tau - \beta\cdot\Grad v}_{\L}^2 = \nor{g}_{\L}^2$, where $g$ is a load of the adjoint problem related to robustness described in Section~\secref{sec:testNormSec}.}

While not rigorously understood, the author believes the issues related to the appearance of non-physical singularities to be related to the uncoupled nature of the test norm.  Previous example problems exhibited boundary layers and sharp gradients in the stress $\sigma$, but not singularities, which contribute significantly more error.  We expect that the oscillations observed in $u$ are a sort of \textit{pollution error}, where error in $u$ is tied to error in $\sigma$.  If we consider the ultra-weak variational formulation for convection-diffusion
\[
\LRp{u,\div \tau - \beta\cdot \grad v}_{\L} + \LRp{\sigma,\frac{1}{\epsilon} \tau + \grad v}_{\L} + \ldots,
\]
we can see that it is a combination of test functions that corresponds to both $u$ and $\sigma$.  Recall from the previous section that, by choosing $\tau$ and $v$ such that they satisfy the adjoint equation with forcing terms $u$ and $\sigma$, we recover the best $L^2$ approximation.  In other words, achieving optimality in the $L^2$ norm requires coupling between $v$ and $\tau$, which is achieved under the graph norm, but not the robust norm derived in the previous section.  If coupling of the test terms delivers optimality in $u$ and $\sigma$ independently, we expect that decoupling $v$ and $\tau$ from each other in a test norm from each other will have the effect of coupling error in $\sigma$ to error in $u$, which would explain the spurious oscillations in $u$ in the presence of singularities in $\sigma$.\footnote{Similar results have been observed in the Stokes equations, where error in $u$ is coupled to the behavior of the pressure variable \cite{FLD:FLD582}.}

The drawback to using the above test norm is that the resulting local system for test functions is now completely coupled, whereas using the previous test norm, the system was block diagonal due to the decoupling in $v$ and $\tau$ and could be constructed and inverted more efficiently.  We hope to explore the difference between these two norms in more rigor and detail in the future; however, experiments in \cite{localConservationDPG} indicate that this new norm performs equivalently or better than the robust test norm derived in the previous chapter for a large range of numerical examples.

\begin{figure}[!h]
\centering
\subfigure{\includegraphics[scale=.275]{figs/LaplaceFigs/coupled1e2h1e2.png}}
\subfigure{\includegraphics[scale=.275]{figs/LaplaceFigs/coupled1e2h1e3.png}}
\caption{$\epsilon = 10^{-2}$ without $h$-resolving diffusion scale, and with $h$-resolution of diffusion scale.}
\label{fig:newNorm}
\end{figure}

Figure~\ref{fig:newNorm} shows the solution for $\epsilon = .01$, where the diffusion scale is both underresolved and resolved by $h$-adaptivity.  In both cases, there are no additional oscillations near the plate tip -- Figure~\ref{fig:newNormZoom} shows a zoomed image of the solution $u$ at the point $(.5,0)$.  The stress is resolved similarly to the previous case; however, the solution $u$ does not display spurious oscillations in either the underresolved or resolved cases.  Figure~\ref{fig:newNormSmallEps} displays the same quantities, but for $\epsilon = 10^{-4}$, in order to demonstrate that the new test norm removes spurious oscillations in $u$ (in the presence of singularities in $\sigma$) independently of $\epsilon$.

\begin{figure}[!h]
\centering
%\subfigure{\includegraphics[scale=.25]{figs/LaplaceFigs/coupled1e2h1e3u.png}}
%\subfigure{\includegraphics[scale=.251]{figs/LaplaceFigs/coupled1e2h1e3uZoom.png}}
\includegraphics[scale=.3]{figs/LaplaceFigs/coupled1e2h1e3uZoom.png}
\caption{Zoom of solution $u$ at the plate tip for $\epsilon = 10^{-2}$.}
\label{fig:newNormZoom}
\end{figure}

\begin{figure}[!h]
\centering
\subfigure{\includegraphics[scale=.25]{figs/LaplaceFigs/coupled1e4h1e5.png}}
\subfigure{\includegraphics[scale=.227]{figs/LaplaceFigs/coupled1e4h1e5Zoom.png}}
\caption{14 refinements for $\epsilon = 10^{-4}$, min $h$ is $O(10^{-5})$.}
\label{fig:newNormSmallEps}
\end{figure}

\section{Anisotropic refinement}
\seclab{sec:aniso}
Isotropic adaptive mesh refinement has shown itself to be an effective way to resolve isolated solution features with large gradients, such as point singularities \cite{hp1,hp3}. However, for the resolution of phenomena such as shocks or boundary layers, anisotropic mesh refinement can resolve solution features for a much lower cost per degree-of-freedom, due to the fact that boundary layers in $n$-dimensions are primarily phenomena supported over $n-1$ dimensions.

As a least squares method, DPG already includes a natural error indicator with which to drive adaptive mesh refinement.  To introduce anisotropic refinements, we need to introduce an anisotropy indicator in order to detect in which direction solution features are aligned.  In general, a test norm can be expressed as the sum of normed quantities, both scalar and vector valued.  If we restrict ourselves to quadrilateral elements for the moment, a general anisotropy indicator for DPG can be constructed by evaluating the $\L$ norms of the individual components of vector valued terms in the test norm.

Under the robust test norm derived in this chapter for the convection-dominated diffusion problem, we can define $x$ and $y$ error contributions over a single element
\begin{align*}
e_{x,K} &= \epsilon \nor{\pd{v}{x}}_{L^2(K)}^2 + \nor{\tau_x}_{L^2(K)}^2 \\
e_{y,K} &= \epsilon \nor{\pd{v}{y}}_{L^2(K)}^2 + \nor{\tau_y}_{L^2(K)}^2.
\end{align*}
We define the anisotropy indicator as the ratio $r_K = \frac{e_{x,K}}{e_{y,K}}$, and implement a simple refinement scheme following \cite{DPG3}.  Given some anisotropic threshold $\epsilon_r$, if $r_K>\epsilon_r$, then we can conclude that the error in the $x$ direction is large compared to the $y$ direction, and we anisotropically refine the element along the $x$-axis.  Likewise, if $r_K < \frac{1}{\epsilon_r}$, this implies that the opposite is true, and we refine the element anisotropically along the $y$-axis.

We note that it is possible to compute the discrete system without needing much additional integration.  Recall that if we let $G$ be the symmetric positive-definite Gram matrix representing the inner product $\LRp{v,\delta v}_V$ on $V_h$, we solve for degrees of freedom $c_e$ representing our error representation function $e$.

For both the graph and robust test norms, we can decompose the inner product that induces the test norm into 
\[
\LRp{v,\delta v}_V = \sum_i \LRp{v,\delta v}_{V,x_i} + \LRp{v,\delta v}_{V,{\rm scalar}}
\]
such that $\LRp{v,\delta v}_{V,x_i}$ is a seminorm containing the $i$th coordinate component of a vector-valued test term, and $\LRp{v,\delta v}_{V,{\rm scalar}}$ is simply the non-vector portions of the test norm.  For example, if we take the $H^1(\Omega)$ Sobolev norm
\[
\LRp{v,\delta v}_V = \LRp{v,\delta v}_{\L} + \LRp{\grad v,\grad \delta v}_{\L}
\]
then $\LRp{v,\delta v}_{V,x_i} = \LRp{\pd{v}{x_i},\pd{\delta v}{x_i}}_{\L}$, and $\LRp{v,\delta v}_{V,{\rm scalar}} = \LRp{v,\delta v}_{\L}$.  Each bilinear term $\LRp{v,\delta v}_{V,x_i}$ induces a symmetric positive-semidefinite matrix $G_{x_i}$, such that 
\[
c_e^TG_{x_i}c_e = \nor{e}^2_{V,x_i}.
\]
By storing $G$ as the sum of $G_{\rm scalar}$ and $G_{x_i}$, we can then cheaply compute the anisotropic error indicators once we have the degrees of freedom corresponding to our error representation function.

%\textcolor{red}{Add examples of anisotropic refinement for plate/boundary layers}

### 2013-07-30 docs/Jesse/Dissertation/dissPres.tex

--- 2012-08-08 docs/Jesse/Proposal/proposalPres.tex
@@
 \let\newblock\relax 
-
 \institute[ICES]{Institute for Computational Engineering and Sciences}
 
-\title[A DPG method for Compressible Flow]{A Discontinuous Petrov-Galerkin method for compressible flow problems}
-\date{August 8, 2012}
+\title[DPG for convection-diffusion]{A Discontinuous Petrov-Galerkin method for convection-diffusion problems}
+\date{July 17, 2013}
 \author[J. Chan, L. Demkowicz, R. Moser]{Jesse Chan \\ Supervisors: Leszek Demkowicz, Robert Moser \\ Committee: Todd Arbogast, Omar Ghattas, Venkat Raman}
@@
 
+\begin{frame}
+\frametitle{Acknowledgements}
+\begin{columns}[c]
+\begin{column}{.03\textwidth}
+\end{column}
+\begin{column}{.33\textwidth}
+
+Omar Al-Hinai
+
+Ivo Babu\v{s}ka
+
+Paul Baumann
+
+Tan Bui
+
+Henry Chang
+
+Truman Ellis
+
+John Evans
+
+\end{column}
+\begin{column}{.33\textwidth}
+
+Jay Gopalakrishnan
+
+Courtney Grymonprez
+
+John Hawkins
+
+Norbert Heuer
+
+Jessica Meixner
+
+Steve Mattis
+
+Todd Oliver
+
+\end{column}
+\begin{column}{.33\textwidth}
+
+Weifeng Qiu
+
+Nate Roberts
+
+Karl Schulz
+
+Chris Simmons
+
+Roy Stogner
+
+Paul Tsuji
+
+Rhys Ulerich
+
+\end{column}
+
+\end{columns}
+\vspace{1cm}
+\begin{center}
+\ldots and many more.
+\end{center}
+\end{frame}
+
 \section{Introduction/Literature review}
@@
 Compressible flow plays an important role in the aerospace and energy industries - transonic and supersonic aircraft, combustion engines, etc. 
-
 }
@@
 \item{} Shocks
-\item{} Boundary layers - resolution needed for drag/load
+\item{} Boundary layers
 \item{} Turbulence (non-localized)
@@
 }
+
+\begin{frame}{Outline}
+  \tableofcontents[currentsection]
+\end{frame}
+
 \frame{
@@
 \includegraphics[scale=.35]{figs/GalerkinOscTight.png}
-\caption{Solution for $f=1$. Oscillations in the standard Galerkin method for large Peclet numbers ${\rm Pe} \coloneqq \frac{h}{\epsilon}$.}
+\caption{Solution for $f=1$. Oscillations in the Galerkin method for large Peclet numbers ${\rm Pe} \coloneqq \frac{h}{\epsilon}$.}
 \end{figure}
@@
 \end{columns}
-\footnotetext{\bibentry{SUPG}}
+\footnotetext{\tiny\bibentry{SUPG}}
 }
@@
 \section{The DPG Method}
+\begin{frame}{Outline}
+  \tableofcontents[currentsection]
+\end{frame}
+
 \frame{
@@
 \begin{frame}
-Let $R_V: V \to V'$ be the isometric Riesz map st.\
+Let $R_V: V \to V'$ be the Riesz map (an isometry):\
 \[
@@
 \end{align*}
+Summary: select test functions \textcolor{red}{$v_{\delta u} \coloneqq R_V^{-1}B\delta u$} to \textcolor{red}{minimize residuals}.  
 \end{frame}
 
-\frame{
-\frametitle{Summary: select test functions to minimize residuals}
-For $\delta u \in U_h$, define the \textcolor{red}{optimal test function} $v_{\delta u}$. 
-\begin{equation*}
-v_{\delta u} \coloneqq R_V^{-1}B\delta u.
-\end{equation*} 
-Then, the residual $J(u_h) = \frac{1}{2}\left\|Bu_h-\ell\right\|_{V'}^2$ is minimized by the solution of
-\[
-b\LRp{u_h,v_{\delta u}} = \ell\LRp{v_{\delta u}}, \quad \forall \delta u \in U_h.
-\]
-}
+%\frame{
+%\frametitle{Summary: select test functions to minimize residuals}
+%For $\delta u \in U_h$, define the \textcolor{red}{optimal test function} $v_{\delta u}$. 
+%\begin{equation*}
+%v_{\delta u} \coloneqq R_V^{-1}B\delta u.
+%\end{equation*} 
+%Then, the residual $J(u_h) = \frac{1}{2}\left\|Bu_h-\ell\right\|_{V'}^2$ is minimized by the solution of
+%\[
+%b\LRp{u_h,v_{\delta u}} = \ell\LRp{v_{\delta u}}, \quad \forall \delta u \in U_h.
+%\]
+%}
 
@@
 \item By choosing a \textcolor{red}{broken} test space $V$ and \textcolor{red}{localizable} norm $\nor{v}_V^2 = \sum_K \nor{v}_{V(K)}^2$, test functions can be determined locally.
-\item In practice, we use an \textcolor{red}{enriched space} $V_h \subset V$, where $\dim(V_h) > \dim(U_h)$ elementwise, and \textcolor{red}{optimal test functions} are approximated by computing $v_{\delta u} \coloneqq R_{V_h}^{-1}B\delta u \in V_h$ through\footnote{\bibentry{DPG2}}
+\item In practice, we use an \textcolor{red}{enriched space} $V_h \subset V$, where $\dim(V_h) > \dim(U_h)$ elementwise, and \textcolor{red}{optimal test functions} are approximated by computing $v_{\delta u} \coloneqq R_{V_h}^{-1}B\delta u \in V_h$ through\footnote{\tiny\bibentry{DPG2}}
 \[
@@
 \]
-Typically, if $U_h = \mathcal{P}^p(\mathbb{R}^n)$, $V_h = \mathcal{P}^{p+\triangle p}(\mathbb{R}^n)$, where $\triangle p \geq n$.\footnote{\bibentry{practicalDPG}} 
-\end{itemize}
-%\footnotetext{\bibentry{DPG2}}
+Typically, if $U_h = \mathcal{P}^p(\mathbb{R}^n)$, $V_h = \mathcal{P}^{p+\triangle p}(\mathbb{R}^n)$, where $\triangle p \geq n$.\footnote{\tiny\bibentry{practicalDPG}} 
+\end{itemize}
+\let\thefootnote\relax\footnotetext{\tiny\bibentry{DPG2}}
 }
@@
 \[
-\nor{u-u_h}_E = \nor{B(u-u_h)}_{V'} = \nor{R_V^{-1}(l-Bu_h)}_V = \nor{e}_V
+\nor{u-u_h}_E = \nor{B(u-u_h)}_{V'} = \nor{R_V^{-1}(\ell-Bu_h)}_V = \nor{e}_V
 \]
@@
 \end{itemize}
-\footnotetext{\bibentry{DPG3pub}}
-}
-
-%\frame{
-%\frametitle{Duality of norms}
-%Duality of norms: for any trial norm $\nor{u}_U$,
-%\[
-%\nor{u}_{U} = \sup_{v \in V}\frac{b\LRp{u,v}}{\nor{v}_{V,U}}, \quad \nor{v}_{V,U} = \sup_{u \in U}\frac%{b\LRp{u,v}}{\nor{u}_{U}}.
-%\]
-%Likewise, for any test norm $\nor{v}_V$, 
-%\[
-%\nor{v}_{V} = \sup_{u \in U}\frac{b\LRp{u,v}}{\nor{U}_{U,V}}, \quad \nor{u}_{U,V} = \sup_{v \in V}\frac%{b\LRp{u,v}}{\nor{v}_{V}}.
-%\]
-%
-%}
+\footnotetext{\tiny\bibentry{DPG3}}
+}
 
@@
 \]
-where $D(A_h^*)$ is the broken graph space of the formal adjoint $A_h^*$, and $\gamma(D(A))$ the trace space of the graph space of operator $A$.\footnote{\bibentry{analysisDPG}}
+where $D(A_h^*)$ is the broken graph space of the formal adjoint $A_h^*$, and $\gamma(D(A))$ the trace space of the graph space of operator $A$.\footnote{\tiny\bibentry{analysisDPG}}
 }
@@
 \[
-\nor{\LRp{u,\widehat{u}}}_U \coloneqq \|u\|^2_{\L} + \|\widehat{u}\|^2
+\nor{\LRp{u,\widehat{u}}}_U^2 \coloneqq \|u\|^2_{\L} + \|\widehat{u}\|_{\dag}^2
 \] 
@@
 \[
-\nor{v}_{V_{\rm opt}} \coloneqq \|A_h^*v\|_{\L}^2 +\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},\jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2.
-\]
-This norm is not localizable, so we instead substitute the jump terms for an $L^2$ term, giving us the \emph{graph norm}\footnote{\bibentry{Bui-ThanhDemkowiczGhattas11b}}
-\[
-\nor{v}_V \coloneqq \|A_h^*v\|_{\L}^2 + \nor{v}_{L^2}.
-\]
-}
-
-\frame{
-\frametitle{Goal: robust higher order adaptive methods}
+\nor{v}_{V_{\rm opt}}^2 \coloneqq \|A_h^*v\|_{\L}^2 +\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},\jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2.
+\]
+This norm is not localizable, so we instead substitute an $L^2$ term for the jump terms, giving us the (equivalent) \textcolor{red}{graph norm}\footnote{\tiny\bibentry{Bui-ThanhDemkowiczGhattas11b}}
+\[
+\nor{v}_V^2 \coloneqq \|A_h^*v\|_{\L}^2 + \nor{v}_{L^2}^2.
+\]
+\let\thefootnote\relax\footnotetext{\tiny{\dag: This norm has a marvelous technical definition for which this footnote is too small to contain.}}
+}
+
+\frame{
+\frametitle{Global properties of test spaces: $L^2$-best approximations}
+
+Under the ultra-weak formulation for $Au = f$.  
+\[
+b(\LRp{u,\uh},v) = \LRa{\widehat{u},\jump{v}}_{\Gh} + (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh},
+\]
+we recover the \textcolor{red}{$L^2$-projection} for \textcolor{red}{conforming} test functions that satisfy the adjoint equation:
+\[
+A_h^*v = \delta u, \quad \forall \delta u \in U_h. %v\in V^r = \LRc{v \in V(\Oh): \LRa{\uh,\jump{v}}_{\Gh} = 0, \quad \forall \LRp{0,\widehat{\delta u}} \in U}.
+\]
+
+For $\nor{v}_{\rm graph}^2 = \nor{A_h^*v}_{\L}^2 + \delta\nor{v}_{\L}^2$ as $\delta \rightarrow 0$; test functions solve
+\[
+\LRp{A_h^*v,A_h^*\delta v}_{L^2(K)} = (u,A_h^*\delta v)_{L^2(K)}.
+\]
+What can we say about \textcolor{red}{global properties} of local test functions?
+}
+
+\frame{
+\frametitle{Global properties of DPG test spaces}
+If we define $V^r_{{\rm opt}}$ as the optimal test space constructed using $V^r_p$, the \textcolor{red}{weakly conforming} space $\LRc{v \in V, \LRa{\widehat{\delta u},\jump{v}}_{\Gh} = 0, \quad \forall \LRp{0,\widehat{\delta u}} \in U_h}$,
+\[
+V^r_{{\rm opt}} = \LRc{ R_{V^r_p}^{-1}B \delta u, \quad \forall \delta u \in U_h},
+\]
+we have the following theorem\footnote{\tiny\bibentry{globalLocalDPG}}
+\begin{theorem}
+$V^r_{{\rm opt}} \subset V_{{\rm opt}}$.  Furthermore, the \textbf{field solutions} $u$ of $b(\LRp{u,\uh},v)=l(v)$ over $V_{{\rm opt}}$ and ${V}^r_{\rm opt}$ coincide.
+\end{theorem}
+\begin{itemize}
+\item Locally determined test functions approximate global test functions.
+\item Under a variant of the graph norm, \textcolor{red}{DPG approximates test functions which deliver $L^2$ optimality}.
+\end{itemize}
+}
+
+%\frame{
+%\frametitle{DPG as a non-conforming DG method on $V$}
+%For DPG using the ultra-weak variational formulation
+%\[
+%b\left(\left(u, \widehat{u}\right),v\right) \coloneqq \LRa{\widehat{u},\jump{v}}_{\Gh} + (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh},
+%\]
+%under the graph test norm $\nor{v}_{\rm graph} = \nor{A_h^*v}_{\L} + \delta\nor{v}_{\L}$, as $\delta\rightarrow 0$, weakly conforming optimal test functions $\tilde{v}\in \tilde{V}$ satisfy 
+%\[
+%\LRp{A_h^*\tilde{v},A_h^*\tilde{\delta v}}_{\L} = (u,A_h^*\tilde{\delta v})_{\Oh}
+%\]
+%which yields a global \textcolor{red}{non-conforming least squares} method for $A_h^*v = u$.
+%%\[
+%%b\left(\left(u, \widehat{u}\right),\tilde{v}\right) = (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh}.
+%%\]
+%}
+
+%\frame{%}
+
+\subsection{A Robust DPG Method for Convection-Diffusion}
+\begin{frame}{Outline}
+  \tableofcontents[currentsection]
+\end{frame}
+
+\frame{
+\frametitle{Ultra-weak formulation for convection-diffusion}
+\vspace{-.25cm}
 \begin{columns}
-\begin{column}{.45\textwidth}
-Our aim is to design an adaptive method for compressible laminar flows that is 
-\begin{itemize}
-\item robust in Reynolds number
-\item stable for arbitrary elements
-\end{itemize}
-
-This proposal will outline
-\begin{enumerate}
-\item a robust DPG method for convection-diffusion,
-\item extension to nonlinear problems and systems,
-\item proposed work.
-\end{enumerate}
-
-\end{column}
-\begin{column}{.54\textwidth}
-\begin{figure}
-\centering
-\subfigure{\includegraphics[scale=.23]{figs/Re1000p2/u2_full.png}}
-\subfigure{\includegraphics[scale=.37]{figs/Re1000p2/mesh6.png}}
-\caption{$u_2$ and $p=2$ mesh for $\Reyn = 1000$.}
-\end{figure}
-\end{column}
-\end{columns}
-}
-
-\section{A Robust DPG Method for Convection-Diffusion}
-
-\frame{
-\frametitle{Ultra-weak formulation for convection-diffusion}
-In first order form, the convection-diffusion equation is
+\begin{column}{.67\textwidth}
+Convection-diffusion as a first order system is
 \[
@@
 \]
+\end{column}
+\begin{column}{.32\textwidth}
+\begin{figure}[!h]
+\centering
+\includegraphics[width = 1.25in]{figs/hybridDGnodes.pdf}
+\end{figure}
+\end{column}
+\end{columns}
+\vspace{-.25cm}
 The variational formulation is
@@
 \]
-Problem with this test norm: approximability of test functions.
+Problem with this test norm: approximability of test functions.\footnote{\tiny\bibentry{globalLocalDPG}}
 \vspace{-.3cm}
@@
 \centering
-\includegraphics[scale=.175]{figs/opt.png}
-\caption{$v$ and $\tau$ components of the 1D optimal test functions for flux $\widehat{f}_n$ on the \emph{right-hand} side of a unit element for $\epsilon = 0.01$. }
+\subfigure[Element $\tau$]{\includegraphics[width=1.1in]{figs/u_graph_tau_mag_K.pdf}}
+\subfigure[Element $v$]{\includegraphics[width=1.1in]{figs/u_graph_v_K.pdf}}
+\subfigure[Global $\tau$]{\includegraphics[width=1.1in]{figs/u_graph_tau_mag.pdf}}
+\subfigure[Global $v$]{\includegraphics[width=1.1in]{figs/u_graph_v.pdf}}
+\caption{$v$ and $\tau$ components of optimal test functions for $u = 1$ on $K$, for $\beta = (1,0)$ and $\epsilon = 0.01$. }
 \label{fig:optTestBoundary}
@@
 \end{align*}
-We recover $\nor{u}^2_{L^2(\Omega)}$ by choosing conforming $\LRp{v,\tau}$ satisfying the \emph{adjoint equations}
+We recover $\nor{\LRp{u,\sigma}}^2_{L^2(\Omega)}$ by choosing conforming $\LRp{v,\tau}$ satisfying the \emph{adjoint equations}
 \begin{align*}
 \div\tau - \beta \cdot \grad v   &= u\\
-\frac{1}{\epsilon}\tau + \grad v &= 0
+\frac{1}{\epsilon}\tau + \grad v &= \sigma
 \end{align*}
@@
 \[
-\nor{u}^2_{L^2(\Omega)} = b\LRp{{\boldsymbol U},\LRp{v,\tau}} = \frac{b\LRp{{\boldsymbol U},\LRp{v,\tau}}}{\nor{\LRp{v,\tau}}_V} \nor{\LRp{v,\tau}}_V \leq \nor{\boldsymbol U}_E \nor{\LRp{v,\tau}}_V
-\]
-Let $\lesssim$ denote a robust bound - \textcolor{red}{if $ \nor{\LRp{v,\tau}}_V \lesssim \|u\|_{L^2(\Omega)}$}, then we have that
-\[
-\nor{u}_{L^2(\Omega)} \lesssim \nor{\boldsymbol U}_E
+\nor{\LRp{u,\sigma}}^2_{L^2(\Omega)} = b\LRp{{\boldsymbol U},\LRp{v,\tau}} = \frac{b\LRp{{\boldsymbol U},\LRp{v,\tau}}}{\nor{\LRp{v,\tau}}_V} \nor{\LRp{v,\tau}}_V \leq \nor{\boldsymbol U}_E \nor{\LRp{v,\tau}}_V
+\]
+Let $\lesssim$ denote a robust bound - \textcolor{red}{if $ \nor{\LRp{v,\tau}}_V \lesssim \nor{\LRp{u,\sigma}}_{\L}$}, then we have that
+\[
+\nor{\LRp{u,\sigma}}_{\L} \lesssim \nor{\boldsymbol U}_E
 \]
@@
 \item{} The standard choice of inflow boundary condition: $u = u_0$.
-\item{} We impose the non-standard inflow condition: $\widehat{f}_n \coloneqq \beta_n u - \sigma_n \approx \beta_n u_0$ on $\Gamma_{\rm in}$.
+\item{} We impose a new ``conserved flux'' inflow condition: $\widehat{f}_n \coloneqq \beta_n u - \sigma_n \approx \beta_n u_0$ on $\Gamma_{\rm in}$.
 \end{itemize}
@@
 \includegraphics[scale=.23]{figs/primal.png}
-\caption{Non-standard inflow.}
+\caption{Non-standard ``conserved flux'' inflow.}
 \end{figure}
@@
 \end{columns}
-When $\sigma_n \approx 0$ near the inflow, condition on $\widehat{f}_n$ approximates condition on $u$.
-
+When $\sigma_n \approx 0$ near the inflow (i.e.\ most problems of interest where $\epsilon \ll 1$), condition on $\widehat{f}_n$ approximates condition on $u$. 
 }
@@
 \frame{
-\frametitle{New inflow boundary condition on $\widehat{f}_n$}
+\frametitle{``Conserved flux'' inflow boundary condition on $\widehat{f}_n$}
 Non-standard choice of boundary condition: $\widehat{f}_n = \beta_n u_0$ on $\Gamma_{\rm in}$, induces smoother adjoint problems, \textcolor{red}{$\nor{\beta\cdot \grad v}_{L^2} = O(1)$}.
@@
 \subfigure[Dirichlet inflow]{\includegraphics[scale=.35]{figs/dirichletBC.png}}
-\subfigure[``Convection'' inflow]{\includegraphics[scale=.35]{figs/newBC.png}}
-\caption{DPG solutions to convection-diffusion for both inflow conditions using an $H^1$ test norm.}
+\subfigure[``Conserved flux'' inflow]{\includegraphics[scale=.35]{figs/newBC.png}}
+\caption{DPG solutions to convection-diffusion for both inflow conditions using the $H^1$ test norm $\nor{\LRp{v,\tau}}_V \coloneqq \nor{v}_{H^1(\Omega)} + \nor{\tau}_{H^1(\Omega)}$.}
 \end{figure}
@@
 %}
-\frame{
-\frametitle{Adjoint estimates, or ``norm building blocks''}
-For solutions $(v,\tau)$ of the adjoint equations, the following quantities are robustly bounded from above by $\nor{u}_{L^2(\Omega)}$.  
-\begin{align*}
-&\|v\|, \sqrt{\epsilon} \|\grad v\|, \|\beta \cdot \grad v\| \\
-&\| \div \tau\|, \frac{1}{\sqrt{\epsilon}}\|\tau\|.
-\end{align*}
-We will construct a test norm through a combination of the above quantities, such that
-\begin{itemize}
-\item $v$ and $\tau$ decoupled (no systems).
-\item Coefficients are of equal order after transforming to the unit element (no boundary layers).
-\end{itemize}
-}
-\frame{
-\frametitle{Mesh-scaled test norms}
+%\frame{
+%\frametitle{Adjoint estimates, or ``norm building blocks''}
+%For solutions $(v,\tau)$ of the adjoint equations, the following quantities are robustly bounded from above by $\nor{u}_{L^2(\Omega)}$.  
+%\begin{align*}
+%&\|v\|, \sqrt{\epsilon} \|\grad v\|, \|\beta \cdot \grad v\| \\
+%&\| \div \tau\|, \frac{1}{\sqrt{\epsilon}}\|\tau\|.
+%\end{align*}
+%We will construct a test norm through a combination of the above quantities, such that
+%\begin{itemize}
+%\item $v$ and $\tau$ decoupled (no systems).
+%\item Coefficients are of equal order after transforming to the unit element (no boundary layers).
+%\end{itemize}
+%}
+
+\frame{
+\frametitle{A mesh-scaled test norm}
 Our test norm, as defined over a single element $K$, is now
 \begin{align*}
-\|\left(v,\tau\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 +&\\
-\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2&.
-\end{align*}
-which induces the proven \emph{robust} bound\footnote{\bibentry{DPGrobustness2}}
+\|\left(v,\tau\right)\|_{V,K}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 &\\
++\| \div \tau - \beta\cdot \grad v\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2&.
+\end{align*}
+which induces the proven \emph{robust} bound\footnote{\tiny\bibentry{DPGrobustness2}}\textsuperscript{,}\footnote{\tiny\bibentry{localConservationDPG}}
 \[
@@
 %Separation of variables gives an analytic solution. 
-All numerical experiments done using Camellia codebase.\footnote{\bibentry{Camellia}}
+All numerical experiments done using Camellia codebase.\footnote{\tiny\bibentry{Camellia}}
 %\[
@@
 \subfigure{
-\includegraphics[scale=.23]{figs/wallBC_exact_u.png}
+\includegraphics[width=1.4in]{figs/wallBC_exact_u.png}
 }
 \subfigure{
-\includegraphics[scale=.23]{figs/wallBC_exact_sigx.png}
+\includegraphics[width=1.4in]{figs/wallBC_exact_sigx.png}
 }
 \subfigure{
-\includegraphics[scale=.23]{figs/wallBC_exact_sigy.png}
+\includegraphics[width=1.4in]{figs/wallBC_exact_sigy.png}
 }
@@
 \frame{
-\frametitle{Error rates}
+\frametitle{Error rates: numerical robustness}
 \begin{figure}
@@
 \subfigure{
-\includegraphics[scale=.33]{figs/errorrates_wallBC.png}
+\includegraphics[width=2.275in]{figs/errorrates_wallBC.eps}
 }
 \subfigure{
-\includegraphics[scale=.33]{figs/L2energyratio_wallBC.png}
+\includegraphics[width=2.275in]{figs/L2energyratio_wallBC.eps}
 }
@@
 
-%\frame{
-%\frametitle{Regularization}
-%Discontinuous inflow conditions on $\widehat{f_n}$, out of alignment with mesh. Boundary condition $\epsilon \grad u \cdot n = 0$ at outflow.
-%\begin{figure}
-%\centering
-%\subfigure{
-%\includegraphics[scale=.33]{figs/discontinuous.png}
-%}
-%\subfigure{
-%\includegraphics[scale=.305]{figs/discontinuousL2rates.png}
-%}
-%\caption{Discontinuous hat inflow data with $\epsilon = 1e-5$, convection solution errors.}
-%\end{figure}
-%}
-
-\frame{
-\frametitle{Regularization}
-For $\beta = (-y,x)^T$ on $\Omega = [-1,1]^2$. Ill posed in the convection setting. Similar tests have been done with discontinuous data.
-
-\begin{figure}
-\centering
-\subfigure{
-\includegraphics[scale=.21]{figs/vortex.png}
-}
-\subfigure{
-\includegraphics[scale=.2015]{figs/vortexMesh.png}
-}
-\caption{Steady vortex problem with $\epsilon = 1e-4$, using a variant of the test norm.}
-\end{figure}
-\vspace{-.25cm}
-}
-
-\section{DPG for nonlinear problems}
+\section{DPG for stationary nonlinear problems}
+\begin{frame}{Outline}
+  \tableofcontents[currentsection]
+\end{frame}
+
 \frame{
 \frametitle{DPG for nonlinear problems}
-
 Given some linearization technique (typically Newton-Raphson and pseudo-timestepping linearization), we measure 
@@
 \end{itemize}
-Preliminary experiments were done in 1D\footnote{\bibentry{DPGNS_1d}} and space-time.\footnote{\bibentry{DPGspacetime}}
+Preliminary experiments were done in 1D\footnote{\tiny\bibentry{DPGNS_1d}} and space-time.\footnote{\tiny\bibentry{DPGspacetime}}
 }
@@
 \begin{columns}
-\begin{column}{.48\textwidth}
+\begin{column}{.45\textwidth}
 \vspace{-.5cm}
@@
 \end{column}
-\begin{column}{.48\textwidth}
+\begin{column}{.52\textwidth}
 \begin{figure}[!h]
 \centering
-\includegraphics[scale = .22]{figs/burgers.png}
-\caption{Shock solution for Burgers' equation, $\epsilon = 1e-4$, using Newton-Raphson.}
+\includegraphics[width = 2.15in]{figs/burgers.png}
+\caption{Shock solution for a Burgers' equation with $\epsilon = 10^{-4}$ using Newton-Raphson.}
 \end{figure}
@@
 \subfigure{\includegraphics[scale=.2]{figs/burgersZoom.png}}
-\caption{Adaptive mesh after 9 refinements, and zoom view at point (.5,.5) with shock formation and $1e-3$ width line for reference.}
+\caption{Adaptive mesh after 9 refinements, and zoom view at point (.5,.5) with shock formation and $10^{-3}$ width line for reference.}
 \end{figure}
@@
 \div \left(\vecttwo{\rho u_1 u_2}{\rho u_2^2+p } - \boldsymbol \sigma_{2}\right) &=0\\
-\div \left(\vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2} - \boldsymbol\sigma \mathbf{u} + \vec{q}\right) &=0\\
+\div \left(\vecttwo{((\rho e)+p)u_1}{((\rho e)+p)u_2} - \boldsymbol\sigma \mathbf{u} - \vec{q}\right) &=0\\
 \frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I &= \grad \mathbf{u} - \Reyn \, \boldsymbol \omega \\
@@
 \end{align*}
-}
-
-\frame{
-\frametitle{Stress law}
-$\boldsymbol\sigma$ for a Newtonian fluid: $\sigma_{ij} = \mu(u_{i,j} + u_{j,i}) + \lambda u_{k,k} \delta_{ij}$.
-%We can invert the stress tensor under isotropic and plane strain assumptions to get
-\[
-\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \frac{1}{2\mu} \sigma_{ij} - \frac{\lambda}{4\mu (\mu + \lambda)} \sigma_{kk}\delta_{ij}
-\]
-The symmetric part of the gradient is
-\[
-\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \grad  U - \boldsymbol \omega
-\]
-%where $\boldsymbol \omega$ is the antisymmetric part of the infinitesimal strain tensor:
-%\[
-%\boldsymbol \omega = \frac{1}{2}\left(\grad  U - \grad ^T  U\right).
-%\]
-Our final form is
-\begin{align*}
-\grad  U - \boldsymbol \omega = \frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I.
-\end{align*}
-By enforcing strong symmetry of $\boldsymbol \sigma$, taking the antisymmetric part implicitly defines $\boldsymbol \omega$ to be the antisymmetric part of $\grad u$. 
 }
@@
 \end{align*}
-Navier-Stokes: defining vector variables $U = \{\rho,u_1,u_2,T\}$ and $\Sigma = \{{\boldsymbol \sigma},\mathbf{q},\omega\}$,
-\begin{align*}
-\div \left(A_{\rm invisc}U - A_{\rm visc}\Sigma\right) &= R_{\rm conserv}(U,\Sigma)\\
-E_{\rm visc} \Sigma - \grad U &= R_{\rm constit}(U,\Sigma)
+Navier-Stokes: defining vector variables $U = \{\rho,u_1,u_2,T\}$ and $\Sigma = \{{\boldsymbol \sigma},\mathbf{q},\omega\}$ and their linearized updates $\delta U, \delta \Sigma$,
+\begin{align*}
+\div \left(A_{\rm invisc}\delta U - A_{\rm visc}\delta\Sigma\right) &= R_{\rm conserv}(U,\Sigma)\\
+E_{\rm visc} \delta\Sigma - \grad \delta U &= R_{\rm constit}(U,\Sigma)
 \end{align*}
@@
 
-\frame{
-\frametitle{Test norms over one element}
-Convection-diffusion:
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,K}^2 =& \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \|\beta \cdot \grad v\|^2 + \epsilon \|\grad v\|^2  \\
-&+\| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
-\end{align*}
-
-Navier-Stokes: let $V$ and $W$ be vectors of test functions $v_i$ and $\tau_i$.
-\begin{align*}
-\|\left(V,W\right)\|_{V,K}^2 =& \min\left\{\frac{1}{\Reyn|K|},1\right\}\nor{V}^2  + \nor{A_{\rm invisc}^T \grad V}^2 + \frac{1}{\Reyn} \nor{A_{\rm visc}^T\grad V}^2 \\
-& + \nor{\div W}^2 + \min\left\{1,\frac{1}{\Reyn|K|}\right\}\nor{E_{\rm visc}^TW}^2.
-\end{align*}
-}
+%\frame{
+%\frametitle{Test norms over one element}
+%Convection-diffusion:
+%\begin{align*}
+%\|\left(v,\tau\right)\|_{V,K}^2 =& \|v\|^2 + \|\beta \cdot \grad v\|^2 + \epsilon \|\grad v\|^2  \\
+%&+\| \div \tau- \beta\cdot \grad v\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
+%\end{align*}
+%
+%Navier-Stokes: let $V$ and $W$ be vectors of test functions $v_i$ and $\tau_i$.
+%\begin{align*}
+%\|\left(V,W\right)\|_{V,K}^2 =& \nor{V}^2  + \nor{A_{\rm invisc}^T \grad V}^2 + \frac{1}{\Reyn} \nor{A_{\rm visc}^T\grad V}^2 \\
+%& + \nor{\div W-A_{\rm invisc}^T \grad V}^2 + \min\left\{1,\frac{1}{\Reyn|K|}\right\}\nor{E_{\rm visc}^TW}^2.
+%\end{align*}
+%}
 
@@
 \item{} Inflow: conserved quantities specified using far-field values.
-\item{} No outflow condition set.
+\item{} No outflow condition set.\footnotemark
 \end{enumerate}
@@
 \end{columns}
-}
-
-\frame{
-\frametitle{Refinement level 0}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u0.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T0.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh0.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 1}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u1.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T1.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh1.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 2}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u2.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T2.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh2.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 3}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u3.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T3.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh3.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 4}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u4.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T4.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh4.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 5}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u5.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T5.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh5.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 6}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u6.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T6.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh6.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 7}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u7.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T7.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh7.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 8}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u8.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T8.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh8.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 9}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u9.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T9.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh9.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Refinement level 10}
-\begin{figure}
-\centering
-\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u10.png}}
-\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T10.png}}
-\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh10.png}}
-\end{figure}
-}
-\setcounter{subfigure}{0}
-
-\frame{
-\frametitle{Zoomed solutions at plate/stagnation point}
-\begin{figure}
-\centering
-\subfigure[$\rho$]{\includegraphics[scale = .12]{figs/Re1000p2/rhoUnscaledzoom.png}}
-\subfigure[$u_1$]{\includegraphics[scale = .12]{figs/Re1000p2/u1zoom.png}}
-\subfigure[$u_2$]{\includegraphics[scale = .12]{figs/Re1000p2/u2zoom.png}}
-\subfigure[$T$]{\includegraphics[scale = .12]{figs/Re1000p2/Tzoom.png}}
-\subfigure[$q_n$]{\includegraphics[scale = .23]{figs/Re1000p2/heatflux.png}}
-\end{figure}
-}
-
-\section{Proposed work}
-\subsection{Area A}
-\frame{
-\frametitle{Proposed work: Area A}
-\begin{itemize}
-\item{\textbf{Completed: Prove robustness of DPG method for the scalar convection-diffusion problem.}}
-
-We have introduced a test norm under which the DPG method robustly bounds the $L^2$ error in the field variables $u$ and the scaled stress $\sigma$.
-Numerical results confirm the theoretical bounds given.
-
-\item{\textbf{\textcolor{red}{Proposed}: Attempt analysis of the linearized Navier-Stokes system.}}
-
-We hope to analyze the linearized Navier-Stokes equations to determine an optimal extrapolation of the test norm for the scalar convection-diffusion problem to systems.
-
-\end{itemize}
-}
-
-\subsection{Area B}
-
-\frame{
-\frametitle{Proposed work: Area B}
-\begin{itemize}
-\item{\textbf{Completed: Collaborative work with Nathan Roberts on the higher order parallel adaptive DPG code Camellia.}}
-
-Numerical experiments use the higher-order adaptive codebase Camellia, built by Nathan Roberts upon the Trilinos library.
-%The framework for arbitrary-irregularity anisotropic refinements in both $h$ and $p$ is in place, and the code is partially parallelized.
-
-\item{\textbf{\textcolor{red}{Proposed}: Anisotropic refinements and $hp$-schemes.}}
-
-The error representation function drives refinement effectively, and we hope to generalize its use to anisotropic adaptive schemes. 
-\begin{figure}
-\centering
-\subfigure{\includegraphics[scale = .175]{figs/anisotropy/b5.png}}
-\subfigure{\includegraphics[scale = .18]{figs/anisotropy/v6.png}}
-\caption{Anisotropic mesh for a convection-diffusion boundary layer.}
-\end{figure}
-\end{itemize}
-}
-
-\frame{
-\textbf{\textcolor{red}{Proposed}: Distributed iterative static condensation.}
+\footnotetext{\tiny\bibentry{Shakib1991141}}
+\let\thefootnote\relax\footnotetext{\tiny\bibentry{Carter}}
+}
+
+%\frame{
+%\frametitle{Refinement level 0}
+%\begin{figure}
+%\centering
+%\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u0.png}}
+%\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T0.png}}
+%\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh0.png}}
+%\end{figure}
+%}
+%\setcounter{subfigure}{0}
+%
+%
+%\frame{
+%\frametitle{Refinement level 1}
+%\begin{figure}
+%\centering
+%\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u1.png}}
+%\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T1.png}}
+%\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh1.png}}
+%\end{figure}
+%}
+%\setcounter{subfigure}{0}
+%
+%
+%\frame{
+%\frametitle{Refinement level 2}
+%\begin{figure}
+%\centering
+%\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u2.png}}
+%\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T2.png}}
+%\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh2.png}}
+%\end{figure}
+%}
+%\setcounter{subfigure}{0}
+%
+%
+%\frame{
+%\frametitle{Refinement level 3}
+%\begin{figure}
+%\centering
+%\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u3.png}}
+%\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T3.png}}
+%\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh3.png}}
+%\end{figure}
+%}
+%\setcounter{subfigure}{0}
+%
+%
+%
+%\frame{
+%\frametitle{Refinement level 4}
+%\begin{figure}
+%\centering
+%\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u4.png}}
+%\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T4.png}}
+%\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh4.png}}
+%\end{figure}
+%}
+%\setcounter{subfigure}{0}
+%
+%
+%
+%\frame{
+%\frametitle{Refinement level 5}
+%\begin{figure}
+%\centering
+%\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u5.png}}
+%\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T5.png}}
+%\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh5.png}}
+%\end{figure}
+%}
+%\setcounter{subfigure}{0}
+%
+%\frame{
+%\frametitle{Refinement level 6}
+%\begin{figure}
+%\centering
+%\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u6.png}}
+%\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T6.png}}
+%\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh6.png}}
+%\end{figure}
+%}
+%\setcounter{subfigure}{0}
+%
+%
+%
+%\frame{
+%\frametitle{Refinement level 7}
+%\begin{figure}
+%\centering
+%\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u7.png}}
+%\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T7.png}}
+%\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh7.png}}
+%\end{figure}
+%}
+%\setcounter{subfigure}{0}
+%
+%
+%\frame{
+%\frametitle{Refinement level 8}
+%\begin{figure}
+%\centering
+%\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u8.png}}
+%\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T8.png}}
+%\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh8.png}}
+%\end{figure}
+%}
+%\setcounter{subfigure}{0}
+%
+%\frame{
+%\frametitle{Refinement level 9}
+%\begin{figure}
+%\centering
+%\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u9.png}}
+%\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T9.png}}
+%\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh9.png}}
+%\end{figure}
+%}
+%\setcounter{subfigure}{0}
+%
+%
+%\frame{
+%\frametitle{Refinement level 10}
+%\begin{figure}
+%\centering
+%\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u10.png}}
+%\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T10.png}}
+%\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh10.png}}
+%\end{figure}
+%}
+%\setcounter{subfigure}{0}
+
+\frame{
+\frametitle{Reynolds number $\Reyn ={\rho_\infty V_\infty L_{\rm plate}}/{\mu_\infty} = 1000$, $p=2$}
+\begin{figure}
+\centering
+\subfigure[$\rho$]{\includegraphics[width=2.25in]{figs/FlowFigs/PlateFigFiles/Re3/rho.png}}
+\subfigure[$u_1$]{\includegraphics[width=2.25in]{figs/FlowFigs/PlateFigFiles/Re3/u1.png}}
+\subfigure[$u_2$]{\includegraphics[width=2.25in]{figs/FlowFigs/PlateFigFiles/Re3/u2.png}}
+\subfigure[$T$]{\includegraphics[width=2.25in]{figs/FlowFigs/PlateFigFiles/Re3/T.png}}
+\end{figure}
+}
+
+\frame{
+\frametitle{Reynolds number $1000$: adapted mesh}
+\begin{figure}
+\centering
+\subfigure[Rescaled $\rho$]{\includegraphics[width=2.25in]{figs/FlowFigs/PlateFigFiles/Re3/rhoRescaled.png}}
+\subfigure[Adapted mesh]{\includegraphics[width=2.25in]{figs/FlowFigs/PlateFigFiles/Re3/mesh12.png}}
+\caption{Adapted $p=2$ mesh and rescaled density $\rho$ for Reynolds number $1000$.}
+\end{figure}
+}
+
+\frame{
+\frametitle{Reynolds number $1000$: solutions at stagnation point}
+\begin{figure}
+\centering
+\subfigure[$\rho$]{\includegraphics[width=2in]{figs/FlowFigs/PlateFigFiles/Re3/rhoZoom.png}}
+\subfigure[$u_1$]{\includegraphics[width=2in]{figs/FlowFigs/PlateFigFiles/Re3/u1Zoom.png}}
+\subfigure[$u_2$]{\includegraphics[width=2in]{figs/FlowFigs/PlateFigFiles/Re3/u2Zoom.png}}
+\subfigure[$T$]{\includegraphics[width=2in]{figs/FlowFigs/PlateFigFiles/Re3/TZoom.png}}
+\end{figure}
+}
+
+\frame{
+\frametitle{Reynolds number 10,000: 18 mesh refinements}
+\begin{figure}[!h]
+\centering
+\subfigure[$\rho$]{\includegraphics[width=2.25in]{figs/FlowFigs/PlateFigFiles/Re4/rho.png}}
+\subfigure[$u_1$]{\includegraphics[width=2.25in]{figs/FlowFigs/PlateFigFiles/Re4/u1.png}}
+\subfigure[$u_2$]{\includegraphics[width=2.25in]{figs/FlowFigs/PlateFigFiles/Re4/u2.png}}
+\subfigure[$T$]{\includegraphics[width=2.25in]{figs/FlowFigs/PlateFigFiles/Re4/T.png}}
+\label{fig:Re10000}
+\end{figure}
+}
+
+\frame{
+\frametitle{Reynolds number 10,000: adapted mesh}
+\begin{figure}
+\centering
+\subfigure[Rescaled $\rho$]{\includegraphics[width=2.25in]{figs/FlowFigs/PlateFigFiles/Re4/rhoRescaled.png}}
+\subfigure[Adapted mesh]{\includegraphics[width=2.25in]{figs/FlowFigs/PlateFigFiles/Re4/mesh.png}}
+\caption{Adapted mesh and rescaled density $\rho$ for Reynolds number 10,000.}
+\end{figure}
+}
+
+\frame{
+\frametitle{Reynolds number 10,000: solutions at stagnation point}
+\begin{figure}
+\centering
+\subfigure[$\rho$]{\includegraphics[width=1.9in]{figs/FlowFigs/PlateFigFiles/Re4/rhoZoom.png}}
+\subfigure[$u_1$]{\includegraphics[width=1.9in]{figs/FlowFigs/PlateFigFiles/Re4/u1Zoom.png}}
+\subfigure[$u_2$]{\includegraphics[width=1.9in]{figs/FlowFigs/PlateFigFiles/Re4/u2Zoom.png}}
+\subfigure[$T$]{\includegraphics[width=1.9in]{figs/FlowFigs/PlateFigFiles/Re4/TZoom.png}}
+\end{figure}
+}
+
+\frame{
+\frametitle{Solver upgrades for $\Reyn = $10,000}
+\begin{itemize}
+\item Static condensation: the DPG ultra-weak formulation yields 
 \[
@@
 \]
-where $D$ has a block-diagonal structure. The system can be reduced to yield the condensed system
-\[
-\left(A-B D^{-1} B^T\right)u_{\rm flux} = f - B D^{-1} g
-\]
-where $D^{-1}$ can be inverted block-wise.
-For FE stiffness matrices under the Laplace equation, the Schur complement has reduced condition number of $O(h^{-1})$ as opposed to $O(h^{-2})$.\footnote{\bibentry{schurComplement}}
-}
-
-\frame{  
-\textbf{\textcolor{red}{Proposed}: a Nonlinear Hessian-based DPG method.}
-Given a nonlinear variational problem $b(u,v) = \ell(v)$, linear in $v$ but not in $u$, beginning with the \textit{nonlinear} dual residual 
-\[
-J(u_h) = \frac{1}{2}\|B(u_h)-\ell\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(u_h,v)-\ell(v)|^2}{\nor{v}_V^2}.
-\]
-produces a Hessian-based DPG method, which solves
-\[
-b_u(\Delta u,v) + b''(\Delta u, \delta u, v_{R(u)}) = \ell(v) - b(u,v) = r(u,v),
-\]
-and aims to minimize the nonlinear dual residual instead of the linearized problem residual. 
-}
-
-\subsection{Area C}
-\frame{
-\frametitle{Proposed work: Area C}
+where $D$ is block-diagonal. The system can be reduced to $\left(A-B D^{-1} B^T\right)u_{\rm flux} = f - B D^{-1} g$ with improved conditioning.\footnote{\tiny\bibentry{schurComplement}}
+\item Anisotropic refinements using the error representation function\footnote{\tiny\bibentry{DPG3}}.
+\item Line search to enforce positivity of $\rho$ and $T$.
+%\[
+%\rho \coloneqq \rho + \alpha \Delta \rho = \delta > 0, \qquad T \coloneqq T + \alpha \Delta T = \delta > 0
+%\]
+\item ``Effective'' CFL number: constraining $dt$ by $h_{\min}$.\footnote{\tiny\bibentry{Shakib1991141}}
+\end{itemize}
+}
+
+\frame{
+\frametitle{Holden ramp problem}
 \begin{columns}
-\begin{column}{.48\textwidth}
-\begin{itemize}
-\item{\textbf{Completed: convection-dominated diffusion, Burgers, and a model problem for Navier-Stokes.}}
-\item{\textbf{\textcolor{red}{Proposed}: Range of Reynolds/Mach numbers.}}
-\item{\textbf{\textcolor{red}{Proposed}: Flow over a bump, Holden's ramp problem (shock-boundary layer interaction).}}
-\item{\textbf{\textcolor{red}{Proposed (time permitting)}: airfoils, regularized Euler.}}
-\end{itemize}
-\end{column}
-\begin{column}{.5\textwidth}
-\begin{figure}
-\centering
-\includegraphics[scale = .275]{figs/ramp.png}
-\end{figure}
+\begin{column}{.49\textwidth}
+\begin{figure}[!h]
+\centering
+\includegraphics[width=2.25in]{figs/holden.eps}
+\caption{Holden ramp problem on domain $[-1,2]\times[0,1]$. Plate begins at $x=-.5$.}
+\end{figure}
+\end{column}
+\begin{column}{.49\textwidth}
+\begin{itemize}
+\item{} Prescribed temperature and wall stagnation conditions on plate and ramp.
+\item{} Symmetry boundary conditions.
+\item{} Inflow: conserved quantities specified using far-field values.
+\item{} No outflow condition set.
+\end{itemize}
 \end{column}
 \end{columns}
+Stress/heat flux boundary conditions are set in terms of the momentum and energy fluxes. 
+\let\thefootnote\relax\footnotetext{\tiny\bibentry{Carter}}
+}
+
+\frame{
+\frametitle{Holden ramp problem - Mach 6, Reynolds 10,000}
+\begin{figure}
+\centering
+\subfigure[$\rho$ rescaled]{\includegraphics[width=2.25in]{figs/FlowFigs/RampFigFiles/Ma6Re4/rhoRescaled.png}}
+\subfigure[$u_1$]{\includegraphics[width=2.25in]{figs/FlowFigs/RampFigFiles/Ma6Re4/u1.png}}
+\subfigure[$u_2$]{\includegraphics[width=2.25in]{figs/FlowFigs/RampFigFiles/Ma6Re4/u2.png}}
+\subfigure[$T$]{\includegraphics[width=2.25in]{figs/FlowFigs/RampFigFiles/Ma6Re4/T.png}}
+\caption{Solutions of Holden ramp problem for Mach 6 and Reynolds number 10,000 (approximately 34,000 with respect to plate length).}
+\end{figure}
+}
+
+\frame{
+\frametitle{Mach 6, Reynolds 10,000: solutions at shock}
+\begin{figure}
+\centering
+\subfigure[Adapted mesh]{\includegraphics[width=3.25in]{figs/FlowFigs/RampFigFiles/Ma6Re4/mesh.png}}
+\subfigure[Zoom of mesh at shock]{\includegraphics[width=2.25in]{figs/FlowFigs/RampFigFiles/Ma6Re4/shockMesh.png}}
+%\subfigure[Zoom of $T$ at shock]{\includegraphics[width=2.25in]{figs/FlowFigs/RampFigFiles/Ma6Re4/Tshock.png}}
+\subfigure[Zoom of rescaled $\rho$ at shock]{\includegraphics[width=2.25in]{figs/FlowFigs/RampFigFiles/Ma6Re4/rhoRescaledshock.png}}
+\end{figure}
+}
+
+\frame{
+\frametitle{Holden ramp problem - Mach 11.68, Reynolds 16,442.4}
+\begin{figure}
+\centering
+\subfigure[$\rho$ rescaled]{\includegraphics[width=2.25in]{figs/FlowFigs/RampFigFiles/Ma11Re4/rhoRescaled.png}}
+\subfigure[$u_1$]{\includegraphics[width=2.25in]{figs/FlowFigs/RampFigFiles/Ma11Re4/u1.png}}
+\subfigure[$u_2$]{\includegraphics[width=2.25in]{figs/FlowFigs/RampFigFiles/Ma11Re4/u2.png}}
+\subfigure[$T$]{\includegraphics[width=2.25in]{figs/FlowFigs/RampFigFiles/Ma11Re4/T.png}}
+\caption{Solutions of Holden ramp problem for Mach 11.68 and Reynolds number 16,442.4 (approximately 55,800 with respect to plate length).}
+\end{figure}
+\let\thefootnote\relax\footnotetext{\tiny\bibentry{BenKirk}}
+}
+
+\frame{
+\frametitle{Mach 11.68, Reynolds 16,442.4: solutions at shock}
+\begin{figure}
+\centering
+\subfigure[Adapted mesh]{\includegraphics[width=3.25in]{figs/FlowFigs/RampFigFiles/Ma11Re4/mesh.png}}
+\subfigure[Zoom of mesh at shock]{\includegraphics[width=2.25in]{figs/FlowFigs/RampFigFiles/Ma11Re4/shockMesh.png}}
+%\subfigure[Zoom of $T$ at shock]{\includegraphics[width=2.25in]{figs/FlowFigs/RampFigFiles/Ma11Re4/Tshock.png}}
+\subfigure[Zoom of rescaled $\rho$ at shock]{\includegraphics[width=2.25in]{figs/FlowFigs/RampFigFiles/Ma11Re4/rhoshock.png}}
+\end{figure}
+}
+
+\frame{
+\frametitle{Normal heat flux for Holden flow}
+\begin{figure}
+\centering
+\subfigure[Mach 6, Reynolds 10,000]{\includegraphics[width=2.25in]{figs/FlowFigs/RampFigFiles/Ma6Re4/heatFlux.png}}
+\subfigure[Mach 11.68, Reynolds 16,442.4]{\includegraphics[width=2.25in]{figs/FlowFigs/RampFigFiles/Ma11Re4/heatFlux.png}}
+\caption{Normal heat flux $q_n$ over plate and ramp for the Holden problem (\textcolor{blue}{blue} is heat flux over the plate, while \textcolor{brown}{brown} is heat flux over the ramp, plotted against the $x$-coordinate along the ramp).}
+\end{figure}
+}
+
+\frame{
+\frametitle{Summary of work}
+\begin{itemize}
+\item \textbf{Area A:}
+\begin{itemize}
+\item Developed a provably robustness DPG method and theory on global properties of DPG test spaces for convection-diffusion problems.
+\item Developed theory for extension of DPG to nonlinear problems.  
+\end{itemize}
+\item \textbf{Area B:}
+\begin{itemize}
+\item Contributions to parallel $hp$-adaptive Camellia\footnote{\tiny\bibentry{Camellia}} (anisotropic refinements, Schur-complement linear solver).
+\item Construction of a higher order adaptive Navier-Stokes solver.
+\end{itemize}
+\item \textbf{Area C:}
+\begin{itemize}
+\item Solution of 2D convection-diffusion and viscous Burgers' equation.
+\item Solution of 2D compressible Navier-Stokes equations for the Carter flat plate and Holden compression ramp problems.
+\end{itemize}
+\end{itemize}
+}
+
+\frame{
+\frametitle{Future directions}
+\begin{itemize}
+\item Navier-Stokes: non-primitive variables, artificial diffusion methods.
+\item Scalability: GPU architectures, preconditioners and multigrid solvers. 
+\item Alternative discretizations: saddle point formulation\footnote{\tiny\bibentry{H1DPG}}
+\begin{figure}
+\centering
+\subfigure[Problem setup]{\includegraphics[width=1.3in]{figs/discForcing.eps}}
+\subfigure[$p=2$ mesh]{\includegraphics[width=1.3in]{figs/discontinuousForcing.png}}
+\subfigure[Solution]{\includegraphics[width=1.3in]{figs/discontinuousForcingMesh.png}}
+\caption{Results using FEniCS for convection-diffusion under a $C_0$ basis.}
+\end{figure}
+\end{itemize}
 }
@@
 Thank you!\\
-\vspace{1cm}
+\vspace{.5cm}
 Questions?
 \end{center}
-}
-
-\section{Extended slides}
-
-\frame{
-\frametitle{Extended literature review}
-\begin{itemize}
-\item Finite difference/volume methods, upwind stencils, monotonicity, ENO/WENO. 
-\item Artificial diffusion, flux limiters/discontinuity-capturing operators.
-\item DG fluxes can be interpreted as residual-based stabilizations similar to SUPG.\footnote{\bibentry{Brezzi20063293}}
-\item Hybridized DG (HDG) methods introduce independent unknowns for numerical traces. Fluxes are defined in terms of DG fluxes and the numerical trace.\footnote{\bibentry{hybridDG}}
-\end{itemize}
-}
-
-\frame{
-\frametitle{Specifics of the ultra-weak formulation}
-
-Given a first order system $Au = f$, multiply by test function $v$ and integrate 
-\[
-\LRp{Au,v} = \LRa{\gamma\LRp{Au},v} + \LRp{u,A^*_hv} = \LRp{f,v}
-\]
-If $u \in L^2\LRp{\Omega}$, the trace of $u$ is undefined, so we identify boundary terms $\LRa{\gamma\LRp{Au},v}_{\Gh} = \LRa{\widehat{u},v}_{\Gh}$ as unknowns $\widehat{u}$ on $\Gh$.
+\begin{figure}
+\centering
+\subfigure[3D slice]{\includegraphics[width=1.75in]{figs/3DSlice.png}}
+\subfigure[3D mesh slice]{\includegraphics[width=1.75in]{figs/3DMeshSlice.png}}
+\caption{An adaptive convection-diffusion experiment in FEniCS with $\epsilon = 10^{-6}$ and a $C_0$ basis.}
+\end{figure}
+}
+
+\frame{
+\frametitle{Extended slides: Oscillations for nonlinear shock problems}
+1D linearized Burgers': $\LRp{u\Delta  u}_{,x} - \epsilon \Delta u_{,xx} = -r(u) = -\LRp{\LRp{\frac{u^2}{2}}_{,x} - \epsilon u_{,xx}}$
+%: $\LRp{\frac{u^2}{2}}_{,x} - \epsilon u_{,xx} = f$.   is
+\begin{figure}
+\centering
+\subfigure[$u_{\epsilon}(x)$ for $\epsilon = .01$]{\includegraphics[width=1.5in]{figs/Burgers1DPlots/u.eps}}
+\subfigure[$r(u_{2\epsilon})$ for $\epsilon = .01$]{\includegraphics[width=1.5in]{figs/Burgers1DPlots/residual100.eps}}
+\subfigure[$r(u_{2\epsilon})$ for $\epsilon = .001$]{\includegraphics[width=1.5in]{figs/Burgers1DPlots/residual1000.eps}}
+\caption{Nonlinear residual/forcing term $r(u_{2\epsilon})$.  Linearization is done around the exact solution for $2\epsilon$.}
+\end{figure}
+}
+
+\frame{
+\frametitle{Extended slides: Navier-Stokes stress law}
+$\boldsymbol\sigma$ for a Newtonian fluid: $\sigma_{ij} = \mu(u_{i,j} + u_{j,i}) + \lambda u_{k,k} \delta_{ij}$.
+%We can invert the stress tensor under isotropic and plane strain assumptions to get
+\[
+\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \frac{1}{2\mu} \sigma_{ij} - \frac{\lambda}{4\mu (\mu + \lambda)} \sigma_{kk}\delta_{ij}
+\]
+The symmetric part of the gradient is
+\[
+\frac{1}{2}\left(\grad  U + \grad ^T  U\right) = \grad  U - \boldsymbol \omega
+\]
+%where $\boldsymbol \omega$ is the antisymmetric part of the infinitesimal strain tensor:
+%\[
+%\boldsymbol \omega = \frac{1}{2}\left(\grad  U - \grad ^T  U\right).
+%\]
+Our final form is
+\begin{align*}
+\grad  U - \boldsymbol \omega = \frac{1}{2\mu} \boldsymbol \sigma - \frac{\lambda}{4\mu (\mu + \lambda)} { \rm tr}(\boldsymbol \sigma) \boldsymbol I.
+\end{align*}
+By enforcing strong symmetry of $\boldsymbol \sigma$, taking the antisymmetric part implicitly defines $\boldsymbol \omega$ to be the antisymmetric part of $\grad u$. 
+}
+
+%\frame{
+%\frametitle{Extended literature review}
+%\begin{itemize}
+%\item Finite difference/volume methods, upwind stencils, monotonicity, ENO/WENO. 
+%\item Artificial diffusion, flux limiters/discontinuity-capturing operators.
+%\item DG fluxes can be interpreted as residual-based stabilizations similar to SUPG.\footnote{\tiny\bibentry{Brezzi20063293}}
+%\item Hybridized DG (HDG) methods introduce independent unknowns for numerical traces. Fluxes are defined in terms of DG fluxes and the numerical trace.\footnote{\tiny\bibentry{hybridDG}}
+%\end{itemize}
+%}
+
+%\frame{
+%\frametitle{Specifics of the ultra-weak formulation}
+%
+%Given a first order system $Au = f$, multiply by test function $v$ and integrate 
+%\[
+%\LRp{Au,v} = \LRa{\gamma\LRp{Au},v} + \LRp{u,A^*_hv} = \LRp{f,v}
+%\]
+%If $u \in L^2\LRp{\Omega}$, the trace of $u$ is undefined, so we identify boundary terms $\LRa{\gamma\LRp{Au},v}_{\Gh} = \LRa{\widehat{u},v}_{\Gh}$ as unknowns $\widehat{u}$ on $\Gh$.
 For convection-diffusion,
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-\left( v, \tau \right)\right) = \left(u,\grad_h\cdot \tau - \beta \cdot \grad_h
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad_h v\right)_{\Oh}&\\
-  - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
-\end{align*}
-where 
-\begin{align*}
-\widehat{f}_n \coloneqq \beta_n u - \sigma_n \in H^{-1/2}(\Gh), \quad \widehat{u} \in H^{1/2}(\Gh)
-\end{align*}
-with the minimum energy extension norm on $\Gh$. We note that $H^{\pm 1/2}(\Gh)$ are \emph{closed} subspaces of $\prod_K H^{\pm 1/2}(\partial K)$. 
-}
-
-\frame{
-\frametitle{Inviscid equations}
-Issue: consider pure convection, $\div \beta u = f$. The ultra-weak variational formulation is
-\[
-\LRa{\widehat{f}_n,v}-\LRp{u,\beta\cdot \grad v} = \LRp{f,v},
-\]
-where $\widehat{f}_n \coloneqq \beta_n u$.
-When $\beta_n = 0$, $v$ has only a streamline derivative, and $\widehat{f}_n$ becomes an ill-defined trace in the cross-stream direction.
-For hyperbolic \emph{systems}, this issue manifests as \emph{sonic lines}.
-\begin{figure}
-\centering
-\includegraphics[scale=.25]{figs/sonicLines.pdf}
-\caption{Sonic lines ($u_n - c = 0$) appear for linearized Euler.}
-\end{figure}
-}
+%\begin{align*}
+%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
+%\left( v, \tau \right)\right) = \left(u,\grad_h\cdot \tau - \beta \cdot \grad_h
+%v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad_h v\right)_{\Oh}&\\
+%  - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}&,
+%\end{align*}
+%where 
+%\begin{align*}
+%\widehat{f}_n \coloneqq \beta_n u - \sigma_n \in H^{-1/2}(\Gh), \quad \widehat{u} \in H^{1/2}(\Gh)
+%\end{align*}
+%with the minimum energy extension norm on $\Gh$. We note that $H^{\pm 1/2}(\Gh)$ are \emph{closed} subspaces of $\prod_K H^{\pm 1/2}(\partial K)$. 
+%}
 
 \bibliographystyle{plain}
-{\scriptsize
-\bibliography{CFD_intro,DPG_old,paper,LitRev,NSNotes}
+{\scriptsize\bibliography{paper,NSNotes,DPGarticles}
 }

### 2013-07-30 docs/Jesse/Dissertation/problemRange.tex

@@
 However, since the effect of bulk viscosity can become important for compressible flows, we treat both coefficients separately.
-In general, $\mu$ and $\lambda$ are functions of temperature, obeying the power law
+In general, $\mu$ and $\lambda$ are functions of temperature.
+One method of modeling temperature dependence is through the power law
 \[
@@
 Mathematically speaking, the linearized Navier-Stokes equations are the results of the linearization of the full equations with respect to a specific background flow.
-The linearized NS equations are frequently referred to as an ``acoustic problem'', as they are used to study sound propagation.
+%The linearized NS equations are frequently referred to as an ``acoustic problem'', as they are used to study sound propagation.
 

### 2013-07-30 docs/Jesse/NavierStokes paper/BurgersNotes.tex

--- 2013-05-15 docs/Jesse/Dissertation/BurgersNotes.tex
@@
-\section{The viscous Burgers equation}
+\subsection{A viscous Burgers equation}
 
@@
 Notice that the nonlinear term is only dependent on $u$, and thus there is no need to linearize in the variables $\sigma$, $\widehat{u}$, and $\widehat{f}_n$.
+Since the linearized Burgers' equation is of the form of a convection-diffusion problem with non-homogeneous load, we adopt the test norm described in Section~\secref{sec:testNormSec} with convection vector $\beta = (u,1)$.
 
-Since the linearized Burgers' equation is of the form of a convection-diffusion problem with non-homogeneous load, we adopt the test norm described in Section~\secref{sec:testNormSec} with convection vector $\beta = (u,1)$.
+%\begin{figure}
+%\centering
+%\caption{Shock solution for Burgers' equation with $\epsilon = 10^{-4}$.} 
+%\label{fig:BurgersShock}
+%\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[Solution $u$]{\includegraphics[height=2in]{burgers.png}}
+\subfigure[Adaptive mesh]{\includegraphics[height=2in]{burgersMesh.png}}
+\subfigure[Zoomed solution at the shock]{\includegraphics[height=2in]{burgersZoom.png}}
+\caption{Solution and adaptive mesh after 9 refinements, and zoom view at point (.5,.5) with shock formation and $1e-3$ width line for reference.}
+\label{fig:BurgersShock}
+\end{figure}
 
@@
 The results of an adaptive simulation are shown in Figure~\ref{fig:BurgersShock} for $\epsilon = 1e-4$.
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.4]{figs/burgers.png}
-\caption{Shock solution for Burgers' equation with $\epsilon = 10^{-4}$.} 
-\label{fig:BurgersShock}
-\end{figure}
 
 For the solution of Burgers' equation, adaptivity began on a cubic $4\times 4$ mesh.
-9 iterations of adaptive mesh refinement were performed, and the resulting mesh and zoomed solution are displayed in Figure~\ref{fig:BurgersShockZoom}, demonstrating a fully resolved smooth transition of the solution into a smeared shock.
-
-\begin{figure}[!h]
-\centering
-\subfigure{\includegraphics[scale=.275]{figs/burgersZoom.png}}
-\subfigure{\includegraphics[scale=.275]{figs/burgersMesh.png}}
-\caption{Adaptive mesh after 9 refinements, and zoom view at point (.5,.5) with shock formation and $1e-3$ width line for reference.}
-\label{fig:BurgersShockZoom}
-\end{figure}
+9 iterations of adaptive mesh refinement were performed, and the resulting mesh and zoomed solution are also displayed in Figure~\ref{fig:BurgersShock}, demonstrating a fully resolved smooth transition of the solution into a smeared shock.

### 2013-07-30 docs/Jesse/NavierStokes paper/CoverLetter.tex

--- 2012-06-13 docs/Jesse/HeuerPaper/paper.tex
@@
-%&pdflatex
-\documentclass[11pt,onecolumn]{scrartcl}
+%\documentclass[11pt,onecolumn]{scrartcl}
+\documentclass{letter}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{tikz}
-\usepackage{subfigure}
+%\usepackage{subfigure}
 \usepackage[normalem]{ulem}
@@
 
-\author{Jesse Chan\textsuperscript{a}, Norbert Heuer\textsuperscript{b}, Tan Bui-Thanh\textsuperscript{a}, and Leszek Demkowicz\textsuperscript{a}}
-
-%\title{$\epsilon$-explicit analysis of DPG for convection-dominated diffusion}
-\title{Robust DPG method for convection-dominated diffusion problems II: a natural inflow condition}
-\date{}
+\signature{Jesse Chan, John A. Evans}
+\address{201 East 24th St, Stop C0200\\
+Austin, Texas 78712-1229}
 \begin{document}
+\begin{letter}{Drs  Chunlei Liang, Krzysztof Fidkowski, Per-Olof Persson, and Peter Vincent\\Computers and Fluids Co-guest editors\\Special Issue:12th USNCCM}
 
 %\tableofcontents
-\maketitle
+%\maketitle
+
+\opening{Dear Dr. Liang, Dr. Fidkowski, Dr. Persson, and Dr Vincent.,}
+
+Please find enclosed our manuscript, 
 \begin{center}
-\textsuperscript{a} Institute for Computational Engineering and Sciences, \\University of Texas at Austin, \\Austin, TX 78712, USA\\
+Jesse Chan, Leszek Demkowicz, Robert Moser\\
+\textit{A DPG method for steady viscous compressible flow},
 \end{center}
+which we would like to submit for publication as an original research article in the 12th USNCCM special issue of Computers and Fluids.
+We believe this is the first report describing the application of the Discontinuous Petrov-Galerkin method of Demkowicz and Gopalakrishnan to the higher order adaptive solution of problems with shocks and boundary layers in viscous compressible flow.
+The method and results of this paper have been accepted for presentation at the minisymposium on \textit{Higher order methods for CFD} at the 12th USNCCM conference, and we believe that the method and results discussed in this manuscript would appeal to the readership of Computers and Fluids.
 
-\begin{center}
-\textsuperscript{b} Facultad de Matem\'aticas, \\Pontificia Universidad Cat\'olica de Chile,\\
-Avenida Vicu\~na Mackenna 4860, Santiago, Chile
-\end{center}
+All authors have approved the manuscript and agree with its submission, and we confirm that this manuscript has not been published elsewhere and is not under consideration by another journal.
+We look forward to hearing from you at your earliest convenience.
 
-\section{Introduction}
+\closing{Best regards}
 
-\subsection{Singular perturbation problems and robustness}
-
-The finite element/Galerkin method has been widely utilized in engineering to solve partial differential equations governing the behavior of physical phenomena in engineering problems.
-The method relates the solution of a partial differential equation (PDE) to the solution of a corresponding variational problem.
-The finite element method itself provides several advantages --- a framework for systematic mathematical analysis of the behavior of the method, weaker regularity constraints on the solution than implied by the strong form of the equations, and applicability to very general physical domains and geometries.
-
-Historically, the Galerkin method has been very successfully applied to a broad range of problems in solid mechanics, for which the variational problems resulting from the PDE are symmetric and coercive (positive-definite).
-It is well known that the finite element method produces optimal or near-optimal results for such problems, with the finite element solution matching or coming close to the best approximation of the solution in the finite element space.
-However, standard Bubnov-Galerkin methods tend to perform poorly for the class of PDEs known as singular perturbation problems.
-These problems are often characterized by a parameter that may be either very small or very large in the context of physical problems.
-An additional complication of singular perturbation problems is that very often, in the limiting case of the parameter blowing up or decreasing to zero, the PDE itself will change types (e.g.\ from elliptic to hyperbolic).
-
-\subsubsection{Convection-diffusion}
-
-A canonical example of a singularly perturbed problem is the convection-diffusion equation.
-%The equation models the convection of fluid along a direction $\beta$ with a viscous dissipation of magnitude $\epsilon$.
-In the limit as $\epsilon\rightarrow 0$, the convection-diffusion equation transforms from a parabolic to a hyperbolic partial differential equation.
-In 1D, the convection-diffusion equation is
-\begin{align*}
-\beta u'-\epsilon u'' &= f.
-\end{align*}
-The equation represents the change in the concentration $u$ of a quantity in a given medium, taking into account both convective and diffusive effects.
-$\beta$ represents the speed of convection, while the singular perturbation parameter $\epsilon$ represents the diffusivity of the medium.
-In the limit of an inviscid medium as $\epsilon\rightarrow 0$, the equation changes types, from elliptic to hyperbolic, and from second order to first order.
-For Dirichlet boundary conditions $u(0)=u_0$ and $u(1)= u_1$, the solution can develop sharp boundary layers of width $\epsilon$ near the outflow.
-
-%The finite element method has performed notoriously poorly for this example, as well as for many other singularly perturbed problems.
-This poor performance is captured by the error bound for the finite element method applied to the convection-diffusion equation - under the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}
-The poor performance of the finite element method for this problem is reflected in the bound on the error in the finite element solution --- under the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}:
-\[
-\|u-u_h\|_\epsilon \leq C \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
-\]
-for $\|u\|_\epsilon^2 \coloneqq \|u\|_{L^2}^2 + \epsilon \|u'\|_{L^2}^2$, with $C$ independent of $\epsilon$. An alternative formulation of the above bound is 
-\[
-\|u-u_h\|_{H^1(0,1)} \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
-\]
-where $C(\epsilon)$ grows as $\epsilon\rightarrow 0$.
-The dependence of the constant $C$ on $\epsilon$ is referred to as a \textit{loss of robustness} --- as the singular perturbation parameter $\epsilon$ decreases, our finite element error is bounded more and more loosely by the best approximation error.
-As a consequence, the finite element solution can diverge significantly from the best finite element approximation of the solution for very small values of $\epsilon$.
-For example, on a coarse mesh, and for small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation with a boundary layer develops spurious oscillations everywhere in the domain, even where the best approximation error is small.
-These oscillations grow in magnitude as $\epsilon \rightarrow 0$, eventually polluting the entire solution.
-
-%, allowing for more and more error in the finite element solution for as $\epsilon$ shrinks. 
-%Intuitively, a non-robust method will perform increasingly worse as $\epsilon$ decreases.
-
-\subsubsection{Wave propagation}
-
-Another example of a singular perturbation problem which experiences loss of robustness is high frequency wave propagation, in which the singular perturbation parameter is the wavenumber $k$, where $k\rightarrow \infty$.
-The loss of robustness in this case manifests as ``pollution" error, a phenomenon in which the finite element solution degrades over many wavelengths for high wavenumbers (commonly manifesting as a phase error between the FE solution and the exact solution).
-
-\subsubsection{Stabilization terms}
-
-Traditionally, instability/loss of robustness has been dealt with using residual-based stabilization techniques.
-Given some variational form, the problem is modified by adding to the bilinear form the strong form of the residual, weighted by a test function and scaled by a stabilization constant $\tau$.
-The most well-known example of this technique is the streamline-upwind Petrov-Galerkin (SUPG) method, which is a stabilized method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.
-SUPG stabilization not only removes the spurious oscillations from the finite element solution of the convection-diffusion equation, but delivers the best finite element approximation in the $H^1$ norm.
-An important difference between residual-based stabilization techniques and other stabilizations is the idea of \textit{consistency} --- by adding stabilization terms based on the residual, the exact solution still satisfies the same variational problem (i.e.\ Galerkin orthogonality still holds).\footnote{Contrast this to an artificial diffusion method, where a specific amount of additional viscosity is added based on the magnitude of the convection and diffusion parameters.
-The exact solution to the original equation no longer satisfies the new stabilized formulation.}
-
-The addition of residual-based stabilization terms can also be interpreted as a modification of the test functions --- in other words, stabilization can be achieved by changing the test space for a given problem.
-We approach the idea of stabilization through the construction of \textit{optimal test functions} to achieve optimal approximation properties.
-
-%\textcolor{red}{add bit about SUPG/residual-based stabilization terms and test functions}
-
-\subsection{Discontinuous Petrov-Galerkin methods with optimal test functions}
-\seclab{optimalTest} Petrov-Galerkin methods, in which the test space
-differs from the trial space, have been explored for over 30 years,
-beginning with the approximate symmetrization method of Barrett and
-Morton~\cite{BARRETT01101981}. The idea was continued with the SUPG
-method of Hughes, and the characteristic Petrov-Galerkin approach of
-Demkowicz and Oden~\cite{Demkowicz1986188}, which introduced the
-idea of tailoring the test space to change the norm in which a finite
-element method would converge.
-
-The idea of optimal test functions was introduced by Demkowicz and
-Gopalakrishnan in \cite{DPG2}.  Conceptually, these optimal test
-functions are the natural result of the minimization of a residual
-corresponding to the operator form of a variational equation. The
-connection between stabilization and least squares/minimum residual
-methods has been observed previously \cite{GLS}. However, the method in \cite{DPG2} distinguishes itself
-by measuring the residual of the natural \textit{operator form of the equation}, which is posed in the dual space, and measured with the dual norm, as we now discuss.
-
-Throughout the paper, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U'$ and $V'$ as the respective topological dual spaces.
-Let $U_h \subset U$ and $V_h\subset V$ be finite dimensional subsets.
-We are interested in the following problem
-\begin{equation}
-\eqnlab{variationEq}
-\left\{
-  \begin{array}{l}
-    \text{Given } l \in V', \text{ find } u_h \in U_h  \text{ such that} \\ 
-    b(u_h,v_h) = l(v_h), \quad \forall v_h\in V_h,
-  \end{array}
-  \right.
-\end{equation}
-where $b\LRp{\cdot,\cdot}: U \times V \to \mbb{R}$ is a continuous
-bilinear form.  $U$ is chosen to be some trial space of approximating functions, but $V_h$ is as of yet unspecified.
-
-Throughout the paper, we suppose the variational
-problem \eqnref{variationEq} to be well-posed. In that case, we can
-identify a unique operator $B:U\rightarrow V'$ such that
-\[
-\langle Bu,v\rangle_V \coloneqq b(u,v), \quad u\in U, v\in V
-\]
-with $\LRa{\cdot, \cdot}_V$ denoting the duality pairing between $V'$ and $V$, to obtain the operator form of the continuous variational problem
-\begin{equation}
-\eqnlab{dualEq}
-Bu = l \quad \text{in } V'.
-\end{equation}
-In other words, we can represent the continuous form of our variational equation
-\eqnref{variationEq} equivalently as the operator equation \eqnref{dualEq} with values in the
-dual space $V'$.  This motivates us to consider the conditions under which the solution to \eqnref{variationEq} is the solution to the minimum residual problem in $V'$ 
-\[
-u_h = \underset{u_h\in U_h}{\arg\min}\, J(u_h),
-\]
-where $J(w)$ is defined for $w\in U$ as 
-\[
-J(w) = \frac{1}{2}\|Bw-l\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(w,v)-l(v)|^2}{\nor{v}_V^2}.
-\]
-For convenience in writing, we will abuse the notation $\sup_{v \in V}$ to denote $\sup_{v\in V\setminus\{0\}}$ for the remainder of the paper.
-
-Let us define $R_V: V \to V'$ as the Riesz map, which identifies
-elements of $V$ with elements of $V'$ by 
-\[
-\langle R_V v,\delta
-v\rangle_V \coloneqq(v, \delta v)_V, \quad \forall \delta v \in V.
-\]
-Here, $(\cdot, \cdot)_V$ denotes the
-inner product in $V$. As $R_V$ and its inverse, $R_V^{-1}$, are both
-isometries, e.g.\ $\|f\|_{V'} = \|R_V^{-1} f\|_V, \forall f \in V'$, we
-have
-\begin{equation}
-\eqnlab{minimization}
-\min_{u_h\in U_h} J(u_h) = \frac{1}{2}\left\|Bu_h-l\right\|_{V'}^2 =  \frac{1}{2}\left\|R_V^{-1}(Bu_h-l)\right\|_V^2.
-\end{equation}
-The first order optimality condition for \eqnref{minimization} requires
-the G\^ateaux derivative to be zero in all directions $\delta u \in
-U_h$, i\.e\.,
-\begin{align*}
-\left(R_V^{-1}(Bu_h-l),R_V^{-1}B\delta u\right)_V = 0, \quad \forall \delta u \in U. 
-\end{align*}
-We define, for a given $\delta u \in U$, the corresponding {\em optimal test function} $v_{\delta u}$
-\begin{equation}
-\eqnlab{optv}
-v_{\delta u} \coloneqq R_V^{-1}B\delta u \quad  \text{in } V.
-\end{equation} 
-The optimality condition then becomes
-\[
- \langle Bu_h-l, v_{\delta u}\rangle_V = 0, \quad \forall \delta u \in U
-\]
-which is exactly the standard variational equation in
- \eqnref{variationEq} with $v_{\delta u}$ as the test functions.
-We can define the optimal test space $V_{\rm opt} \coloneqq \{v_{\delta u} \text{ s.t.
-} \delta u\in U\}$.
-Thus, the solution of the variational problem \eqnref{variationEq} with test space $V_h = V_{\rm opt}$ minimizes the residual in the dual norm $\nor{Bu_h-l}_{V'}$.
-This is the key idea behind the concept of optimal test functions.
-
-Since $U_h \subset U$ is spanned by a finite number of basis functions $\LRc{\varphi_i}_{i=1}^N$, \eqnref{optv} allows us to compute (for each basis function) a corresponding optimal test function $v_{\varphi_i}$.
-The collection $\LRc{v_{\varphi_i}}_{i = 1}^N$ of optimal test functions then forms a basis for the optimal test space.
-In order to express optimal test functions defined in \eqnref{optv} in a more familiar form, we take  $\delta u = \varphi$, a generic basis function in $U_h$, and rewrite \eqnref{optv} as
-\[
-R_Vv_{\varphi} = B\varphi, \quad \text{in } V',
-\]
-which is, by definition, equivalent to
-\[
-\LRp{v_\varphi,\delta v}_V = \LRa{R_Vv_\varphi,\delta v}_{V}=
-\LRa{B\varphi, \delta v}_V = b\LRp{\varphi,\delta v}, \quad
-\forall \delta v \in V.
-\]
-%% Now, let us define the \textit{trial-to-test} operator $T =
-%% R_V^{-1}B$, which, by \eqnref{optv}, maps a trial function $\delta u$
-%% to its corresponding \textit{optimal} test function $v = T\delta u$.
-%% On the other hand,
-As a result, optimal test functions can be determined by solving the auxiliary
-variational problem
-\begin{equation}
-\eqnlab{optvVar}
-\left(v_\varphi,\delta v\right)_V = b(\varphi,\delta v), \quad \forall
-\delta v \in V.
-\end{equation}
-However, in general, for standard $H^1$ and $H({\rm div})$-conforming finite element methods, test functions are continuous over the entire domain, and hence solving variational problem \eqnref{optvVar} for each optimal test function requires a global operation over the entire mesh, rendering the method impractical.
-A breakthrough came through the development of
-discontinous Galerkin (DG) methods, for which basis functions are
-discontinuous over elements. In particular, the use of discontinuous
-test functions $\delta v$ reduces the problem of determining global 
-optimal test functions
-in \eqnref{optvVar} to local problems that can be solved in an
-element-by-element fashion.
-
-We note that solving \eqnref{optvVar} on each element exactly is
-infeasible since it amounts to inverting the Riesz map $R_V$ exactly.
-Instead, optimal test functions are approximated using the standard
-Bubnov-Galerkin method on an ``enriched" subspace $\tilde{V} \subset
-V$ such that $\dim(\tilde{V}) > \dim(U_h)$ elementwise \cite{DPG1, DPG2}. In this
-paper, we assume the error in approximating the optimal test functions
-is negligible, and refer to the work in \cite{practicalDPG} for
-estimating the effects of approximation error on the performance of DPG.
-
-It is now well known that the DPG method
-delivers the best approximation error in the ``energy norm" --- that is
-\cite{Bui-ThanhDemkowiczGhattas11a, DPG2,DPG4} 
-\begin{equation}
-\eqnlab{optimalError}
-\nor{u-u_h}_{U,E} = \inf_{w\in U_h} \nor{u-w}_{U,E},
-\end{equation}
-where the energy norm $\|\cdot \|_{U,E}$ is defined for a function $\varphi \in U$ as
-\begin{equation}
-\eqnlab{energyNorm} \|\varphi\|_{U,E} \coloneqq \sup_{v\in V}
-\frac{b(\varphi,v)}{\|v\|_V} = \sup_{\nor{v}_V = 1} b(\varphi,v) =
-\sup_{\nor{v}_V = 1} \LRa{B\varphi,v}_V = \nor{B\varphi}_{V'} =
-\nor{v_\varphi}_V,
-\end{equation}
-where the last equality holds due to the isometry of the Riesz map
-$R_V$ (or directly from \eqnref{optvVar} by taking the supremum). An
-additional consequence of adopting such an energy norm is that,
-without knowing the exact solution, the energy error $\|u-u_h\|_{U,E}$ can
-be determined by computing $\|v_{u-u_h}\|_V$ from the following
-identity
-\[
-\left(v_{u-u_h},\delta v\right)_V = b(u-u_h,\delta v) = l\LRp{\delta
-v} - b(u_h,\delta v).
-\]
-This is simply a consequence of the least-squares nature of DPG; the energy error is simply the norm of the  residual in $V'$.
-
-Practically speaking, this implies that the DPG method is discretely stable on any mesh.
-In particular, DPG is unconditionally stable for higher order adaptive meshes, where discrete stability is often an issue.
-
-\subsection{Duality between trial and test norms (energy norm pairings)}
-%\subsection{Abstract energy norm pairings}
-\seclab{energyPair}
-A clear property of the energy norm defined by \eqnref{energyNorm} is that the trial norm $\nor{\cdot}_{U,E}$ is induced by a given test norm.
-However, the reverse relationship holds as well; for any trial norm, the test norm that induces such a norm is recoverable through duality.
-We have a result, proved in \cite{Bui-ThanhDemkowiczGhattas11a}: assuming, for simplicity, that the bilinear form $b(u,v)$ is definite, given any norm $\nor{\cdot}_{U}$ on the trial space $U$, for $\varphi \in U$, we can represent $\nor{\varphi}_{U}$ via
-\[
-\nor{\varphi}_{U} = \sup_{v \in V}\frac{b\LRp{w,v}}{\nor{v}_{V,U}}.
-\]
-where $\nor{v}_{V,U}$ is defined through
-\[
-\nor{v}_{V,U} = \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U}}.
-\]
-%In other words, the norm $\nor{\cdot}_V$ in $V$ can be recovered using the energy norm $\nor{\cdot}_{U,E}$ in $U$, and vice versa.
-
-In particular, given two arbitrary norms $\nor{\cdot}_{U,1}$ and $\nor{\cdot}_{U,2}$ in $U$
-such that $\nor{\cdot}_{U,1} \le c \nor{\cdot}_{U,2}$ for some constant
-$c$, they generate two norms $\nor{\cdot}_{V,U,1}$ and
-$\nor{\cdot}_{V,U,2}$ in $V$ defined by
-\[
-\nor{v}_{V,U,1} \coloneqq \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U,1}}, \quad
-\text{and }\nor{v}_{V,U,2} \coloneqq \sup_{w \in U}\frac{b\LRp{w,v}}{\nor{w}_{U,2}},
-\]
-such that $\nor{\cdot}_{V,U,1}$ and $\nor{\cdot}_{V,U,2}$ induce
-$\nor{\cdot}_{U,1}$ and $\nor{\cdot}_{U,2}$ as energy
-norms in $U$, respectively. That is,
-\[
-\|\varphi\|_{U,1} = \sup_{v\in V}
-\frac{b(\varphi,v)}{\|v\|_{V,U,1}}, \quad \text{and }\|\varphi\|_{U,2} = \sup_{v\in V}
-\frac{b(\varphi,v)}{\|v\|_{V,U,2}}.
-\]
-
-A question that remains to be addressed is to establish the relationship
-between $\nor{\cdot}_{V,U,1}$ and $\nor{\cdot}_{V,U,2}$, given that
-$\nor{\cdot}_{U,1} \le c \nor{\cdot}_{U,2}$. But this is
-straightforward since we have
-\begin{align*}
- \| v \|_{V,U,2} = \sup_{u \in U} \frac{b\left(w,v\right)}{\left\|
-  w \right\|_{U,2}} \le c\sup_{w \in U} \frac{b\left(w,v\right)}{\left\| w
-  \right\|_{U,1}} = c\| v \|_{V,U,1}.
-\end{align*}
-Consequently, a stronger energy norm in $U$ will generate a weaker
-norm in $V$ and vice versa. In other words, to show that an
-energy norm $\nor{\cdot}_{U,1}$ is weaker than another energy norm
-$\nor{\cdot}_{U,2}$ in $U$, one simply needs to show the reverse inequality on the
-corresponding norms in $V$, that is, $\nor{\cdot}_{V,U,1}$ is stronger
-than $\nor{\cdot}_{V,U,2}$.
-
-%From now on, unless otherwise stated, we will refer to  $\nor{\cdot}_{V,U,1}$, $\nor{\cdot}_{V,U,2}$, and $\nor{\cdot}_{V}$ as the test norms which induce $\nor{\cdot}_{U,1}$, $\nor{\cdot}_{U,2}$, and $\nor{\cdot}_{U,E}$ and vice versa, in the sense discussed above.
-From now on, unless otherwise stated, we will refer to $\nor{\cdot}_{V,U}$ as the test norm that induces a given norm $\nor{\cdot}_U$.
-Likewise, we will refer $\nor{\cdot}_{U,V}$ as the trial norm induced by a given test norm $\nor{\cdot}_V$.
-In this paper, for simplicity of exposition, we shall call a pair of norms in $U$ and $V$ that induce each other as an {\em energy norm pairing}.
-
-\subsection{Discontinuous Petrov-Galerkin methods with the ultra-weak formulation}
-\seclab{abstractUweak}
-
-The naming of the discontinuous Petrov-Galerkin method refers to the fact that the method is a Petrov-Galerkin method, and that the test functions are specified to be discontinuous across element boundaries.
-There is no specification of the regularity of the trial space, and we stress that the idea of DPG is not inherently tied to a single variational formulation \cite{Bui-ThanhDemkowiczGhattas11a}.
-
-In most of the DPG literature, however, the discontinuous Petrov-Galerkin method refers to the combination of the concept of locally computable optimal test functions in Section \secref{optimalTest} with the so-called ``ultra-weak formulation" \cite{DPG1,DPG2,DPG3,DPG4,DPGElas,DBLP:journals/procedia/NiemiCC11}.
-Unlike the previous two sections in which we studied the general equation \eqnref{variationEq} given by abstract bilinear and linear forms, we now consider a concrete instance of \eqnref{variationEq} resulting from an ultra-weak formulation for an abstract first-order system of PDEs $Au = f$.
-Additionally, from this section onwards, we will refer to DPG as the pairing of the ultra-weak variational formulation with the concept of locally computable optimal test functions.
-
-We begin by partitioning the domain of interest $\Omega$ into $\Nel$ non-overlapping elements $K_j, j = 1,\hdots,\Nel$ such that $\Oh = \cup_{j=1}^\Nel K_j$ and $\overline{\Omega} = \overline{\Omega}_h$.
-Here, $h$ is defined as $h= \max_{j\in \LRc{1,\hdots,\Nel}}\text{diam}\LRp{K_j}$.
-We denote the mesh ``skeleton" by $\Gh = \cup_{j=1}^\Nel \partial K_j$; the set of all faces/edges $e$, each of which comes with a normal vector ${n}_e$.
-The internal skeleton is then defined as $\Gamma^0_h = \Gh \setminus \partial \Omega$.
-If a face/edge $e \in \Gh$ is the intersection of $\partial K_i$ and $\partial K_j$, $i \ne j$, we define the following jumps:
-\[
-\jump{v} = \text{sgn} \LRp{{n}^-}v^- + \text{sgn} \LRp{{n}^+}v^+, \quad
-\jump{\tau \cdot n} = {n}^-\cdot \tau^- + {n}^+\cdot\tau^+,
-\]
-where
-\[
-\text{sgn}\LRp{{n}^{\pm}} =
-\left\{
-\begin{array}{ll}
-1 & \text{if } {n}^{\pm} = {n}_e \\
--1 & \text{if } {n}^\pm = -{n}_e
-\end{array}
-\right..
-\]
-For $e$ belonging to the domain boundary $\partial \Omega$, we define
-\[
-\jump{v} = v, \quad
-\jump{\tau \cdot n} = {n}_e\cdot \tau.
-\]
-Note that we allow arbitrariness in assigning ``-'' and ``+'' quantities to the adjacent elements $K_i$ and $K_j$.
-%For the rest of the paper, we will use the same notation for both a function and its trace (if it is well-defined) when there is no ambiguity.
-
-The ultra-weak formulation for $Au = f$ on $\Oh$, ignoring boundary
-conditions for now, reads
-\begin{equation}
-\eqnlab{uweak}
-b\left(\left(u, \widehat{u}\right),v\right) \coloneqq \langle \widehat{u}, \jump{v}
-\rangle_{\Gh} - (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh},
-\end{equation}
-where we have denoted $\LRa{\cdot,\cdot}_{\Gh}$ as the duality
-pairing on $\Gh$, $\LRp{\cdot,\cdot}_{\Oh}$ the $L^2$-inner
-product over $\Oh$, and $A_h^*$ the formal adjoint resulting from
-element-wise integration by parts.  Occasionally, for simplicity in
-writing, we will ignore the subscripts in the duality pairing and
-$L^2$-inner product if they are $\Gh$ and $\Oh$. Both the
-inner product and formal adjoint are understood to be taken
-element-wise. Using the ultra-weak formulation, the regularity
-requirement on solution variable $u$ is relaxed, that is, $u$ is now
-square integrable for the ultra-weak formulation \eqnref{uweak} to be
-meaningful, instead of being (weakly) differentiable.  The trade-off
-is that $u$ does not admit a trace on $\Gh$ even though it did
-originally. Consequently, we need to introduce an additional new
-``trace'' variable $\widehat{u}$ in \eqnref{uweak}, that is defined only on
-$\Gh$.
-
-The energy setting is now clear; namely,
-\[
-u\in L^2\LRp{\Oh} \equiv L^2(\Omega), \quad v\in V=D(A^*_h), \quad
-\widehat{u}\in \gamma(D(A)),
-\]
-where $D(A_h^*)$ denotes the broken graph space corresponding to $A_h^*$,
-and $\gamma(D(A))$ the trace space (assumed to exist) of the graph space of
-operator $A$.
-The first discussion of the well-posedness of DPG with the ultra-weak formulation can be found in \cite{analysisDPG}, where the proof is presented for the Poisson and convection-diffusion equations.
-A more comprehensive discussion of the abstract setting for DPG with the ultra-weak formulation using the graph space, as well as a more general proof of well-posedness, can be consulted in \cite{Bui-ThanhDemkowiczGhattas11b}.
-
-%\subsection{Optimal and quasi-optimal test norms}
-\subsection{Canonical energy norm pairings for ultra-weak formulation}
-
-From the discussion in Section~\secref{energyPair} of energy norm and test norm pairings, we know that specifying either a test norm or trial norm is sufficient to define an energy pairing.
-In this section, we derive and discuss two important energy norm pairings, the first of which begins by specifying the canonical norm in $U$ and inducing a test norm on $V$.
-The second pairing begins instead by specifying the canonical norm on $V$ under the ultra-weak formulation \eqnref{uweak} and inducing an energy norm on the trial space $U$.
-
-We begin first with the canonical norm in $U$. Since $\uh \in \gamma\LRp{D\LRp{A}}$, the standard norm for $\uh$ is
-the so-called minimum energy extension norm defined as
-\begin{equation}
-\eqnlab{MEnorm}
-\|\widehat{u}\| = \inf_{w\in D\LRp{A},
-  \left.w\right|_{\Gh}=\widehat{u}} \|w\|_{D\LRp{A}}.
-\end{equation}
-The canonical norm for the group variable $\LRp{u,\uh}$ is then given by
-\[
-\|\left(u,\widehat{u}\right)\|_U^2 = \|u\|^2_{\L} + \|\widehat{u}\|^2,
-\]
-Applying the Cauchy-Schwarz inequality, we arrive at
-\[
-b\LRp{\LRp{u,\uh},v} \le \nor{\LRp{u,\uh}}_U \nor{v}_{V,U},
-\]
-where
-\[
-\nor{v}_{V,U}^2 = \|A_h^*v\|_{\L}^2
-+\left(\sup_{\widehat{u} \in \gamma\LRp{D\LRp{A}}} \frac{\LRa{ \widehat{u},
-  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2.
-\]
-
-On the other hand, since $v \in D\LRp{A^*_h}$, the canonical norm for
-$v$ is the broken graph norm: 
-\[
-\nor{v}_V^2 =  \|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2.
-\]
-Using the Cauchy-Schwarz inequality again, we obtain
-\[
-b\LRp{\LRp{u,\uh},v} \le \nor{\LRp{u,\uh}}_{U,V} \nor{v}_{V},
-\]
-where
-\begin{equation}
-\eqnlab{inducedQuasi}
-\nor{\LRp{u,\uh}}_{U,V}^2 = \nor{u}_{\L}^2
-+\sup_{v \in D\LRp{A_h^*}} \frac{\LRa{\widehat{u},
-  \jump{v}}_{\Gh}^2}{\|v\|_V^2},
-\end{equation}
-
-Using the framework developed in \cite{Bui-ThanhDemkowiczGhattas11a},
-one can show that both pairs $\LRp{\nor{\LRp{u,\uh}}_U,
-  \nor{v}_{V,U}}$ and $\LRp{\nor{\LRp{u,\uh}}_{U,V}, \nor{v}_{V}}$ are
-energy norm pairings in the sense discussed in Section
-\secref{energyPair}. That is, the canonical norm $\nor{\LRp{u,\uh}}_U$
-in $U$ induces (generates) the norm $\nor{v}_{V,U}$ in $V$, while the
-canonical norm $\nor{v}_V$ in $V$ induces (generates) the energy norm
-$\nor{\LRp{u,\uh}}_{U,V}$ in $U$. In the DPG literature \cite{DPG4}, $\nor{v}_{V,U}$ is known as the {\em optimal test norm},
-while $\nor{v}_{V}$ is known as the {\em quasi-optimal test norm}.
-
-\begin{figure}[!h]
-\centering
-\begin{tabular}{l c c}
-Trial norm & & Test norm \\
-\hline
-$\boxed{\|u\|^2_{\L} + \|\widehat{u}\|^2}$ & $\Longrightarrow$  & $\|A_h^*v\|_{\L}^2
-+\left(\sup_{\widehat{u}} \frac{\LRa{ \widehat{u},
-  \jump{v} }_{\Gh}}{\|\widehat{u}\|}\right)^2$ \\
-%\hline
-%Quasi-optimal trial norm & & Canonical test norm \\
-%\hline
-$\nor{u}_{\L}^2+\sup_{v } \left(\frac{\LRa{\widehat{u},
-  \jump{v}}_{\Gh}}{\|v\|_V}\right)^2$ &  $\Longleftarrow$ & $\boxed{\|A_h^*v\|_{\L}^2 + \nor{v}_{\L}^2}$
-\end{tabular}
-\caption{A summary of the derivation of test/trial norm pairings; we begin with the boxed norm on either the trial or test space, and induce the norm on the other space through duality.
-The optimal \textit{test} norm is naturally derived by beginning with the canonical norm on the trial space, while the quasi-optimal \textit{trial} norm is derived from beginning with the canonical norm on the test space.}
-\end{figure}
-
-The canonical norm $\nor{\LRp{u,\uh}}_U$ in $U$ provides a good
-balance between the standard norms on the field $u$ and the flux
-$\uh$ \cite{DPG4}. As a result, if the induced norm $\nor{v}_{V,U}$ (namely, the
-optimal test norm) is used to compute  optimal test functions in
-\eqnref{optvVar}, the finite element error in the canonical norm is the
-best in the sense of \eqnref{optimalError}.
-
-Unfortunately, the optimal test norm is non-localizable due to the presence of the jump term $\jump{v}$.\footnote{A localizable norm $\nor{v}_{V(\Oh)}$ can be written in the form
-$$\nor{v}_{V(\Oh)} = \sum_{K\in\Oh} \nor{v}_{V(K)},$$ where $\nor{v}_{V(K)}$ is a norm over the element $K$.} Since the jump terms couple elements together, the evaluation of the jump terms requires contributions from all the elements in the mesh.
-Consequently, solving for an optimal test function
-amounts to inverting the Riesz map %, defined on the left sideof \eqnref{optvVar}, 
-over the entire mesh $\Oh$, making the optimal test norm impractical.
-
-On the other hand, the quasi-optimal test norm $\nor{v}_V$, namely the canonical norm in $V$, \textit{is} localizable, and hence practical.
-However, it's worth noting the difference between the induced energy norm $\nor{\LRp{u,\uh}}_{U,V}$ and the canonical norm in $U$; under the induced norm $\nor{\LRp{u,\uh}}_{U,V}$ there is no natural interpretation for the norm in which the error in the flux variable $\uh$ is measured.
-
-Using a variant of the quasi-optimal test norm, numerical results show that the DPG method appears to provide a ``pollution-free" method without phase error for the Helmholtz equation \cite{DPG4}, and analysis of the pollution-free nature of DPG is currently under investigation.
-Similar results have also been obtained in the context of elasticity \cite{DPGElas} and the linear Stokes equations \cite{Camellia}.
-On the theoretical side, the quasi-optimal test norm has been shown to yield a well-posed DPG methodology for the Poisson and convection-diffusion equations \cite{analysisDPG}.
-More recently, this theory has been generalized to show the well-posedness of DPG for the large class of PDEs of Friedrichs' type \cite{Bui-ThanhDemkowiczGhattas11b}.
-
-\section{Model problem and robustness}
-\seclab{sec:modelSec}
-The remainder of the paper focuses on a convection-diffusion model problem using the abstract theory that we
-have discussed so far.
-In particular, we shall use the DPG method based on the ultra-weak formulation with optimal test functions to solve the model problem and analyze its behavior with respect to $\epsilon$.
-Our goal is to show the robustness of the method with respect to $\epsilon$, and demonstrate its usefulness as  a numerical approach to solving singular-perturbed problems.
-
-We consider the following model convection-diffusion problem on a domain
-$\Omega \subset \mathbb{R}^d$ with boundary $\pO \equiv \Gamma$
-\begin{equation}
-\div (\beta u) - \epsilon\Delta u = f  \in \L \label{primal},
-\end{equation}
-which can be cast into the first order form on the group variable
-$\LRp{u,\sigma}$ as
-\begin{equation}
-\eqnlab{CDstrong}
-A \LRp{u,\sigma} \coloneqq \LRs {
-\begin{array}{c}
-\div (\beta u - \sigma) \\ \frac{1}{\epsilon}\sigma - \grad u
-\end{array}} = \LRs{
-\begin{array}{c}
-f \\ 0
-\end{array}
-}.
-\end{equation}
-Using the abstract ultra-weak formulation developed in Section
-\secref{abstractUweak} for the first order system of PDEs \eqnref{CDstrong} we
-obtain
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh} - \LRa{
-\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n,
-  \jump{v} }_{\Gh},
-\end{align*}
-where $\LRp{v, \tau}$ is the group test function. It should be pointed
-out that the divergence and gradient operators are understood to act
-element-wise on test functions $\LRp{v, \tau}$ in the broken graph
-space $ D\LRp{A_h^*} \coloneqq  H^1(\Oh) \times H({\rm div}, \Oh)$, but
-globally as usual on conforming test functions, i.e.\ $ \LRp{v, \tau}
-\in  H^1(\Omega) \times H({\rm div}, \Omega)$. It follows that the
-canonical test norm can be written as
-\[
-\|\left(v, \tau\right)\|_V^2 = \|\left(v, \tau\right)\|_{H^1(\Oh) \times H({\rm div},\Oh)}^2
-= \sum_{K\in \Oh} \|\left(v, \tau\right)\|_{H^1(K) \times H({\rm
-    div},K)}^2,
-\]
-where
-\[
-\|\left(v, \tau \right)\|_{H^1(K) \times H({\rm div},K)}^2 =
-\|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2 + \|\tau\|_{L^2(K)}^2 +
-\|\div \tau\|_{L^2(K)}^2.
-\]
-
-In order to define the proper norm on the trial space, boundary
-conditions need to be specified. We begin by splitting the boundary
-$\Gamma$ as follows
-\begin{align*}
-\Gamma_{-} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\}, \quad {\rm
-  (inflow)}\\ \Gamma_{+} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\},
-\quad {\rm (outflow)}\\ \Gamma_{0} &\coloneqq \{x\in \Gamma;
-\beta_n(x) = 0\},
-\end{align*}
-where $\beta_n \coloneqq \beta \cdot n$.
-Previous work in \cite{DPGrobustness} adopted Dirichlet boundary
-conditions everywhere on $\Gamma$.  
-%and we could obtain the robustness only with special weighted norms in which the weight varied spatially. 
-In this paper, we employ the inflow
-condition of Hesthaven \etal \cite{Hesthaven96astable}, where we set
-\[
-\beta_n u - \sigma_n  = u_0, \quad \text{on } \Gm,
-\]
-instead of $\beta_n u = u_0$. The former resembles the latter
-as $\epsilon$ approaches zero\footnote{For our model problem, as for many problems of interest in computational fluid dynamics, we expect $\grad u$ to be small near the inflow, and that the solutions to \eqref{primal} using $\beta_n u - \sigma_n = f_n = u_0$ on $\Gamma_-$ will converge to that using $u=u_0$ on $\Gamma_-$  for sufficiently small $\epsilon$.}; however, the latter induces a more ``well-behaved" adjoint problem than the former, which, as we will discuss, affects the performance of DPG.
-
-On the outflow boundary, we apply standard homogeneous Dirichlet boundary conditions
-\[
-u = 0, \quad \text{on } \Gp.
-\]
-This paper is intended to act as an extension of work presented by Heuer and Demkowicz in \cite{DPGrobustness}.
-The primary focus of the paper is to analyze the DPG method and extend previous results under this new choice of inflow boundary conditions.
-The difference in the performance of DPG under both new and old boundary conditions is connected to the difference in the adjoint problems induced under each boundary condition.
-The secondary contribution of this paper will be to analyze the performance of DPG under a new mesh-dependent test norm.
-
-\subsection{Norms on $U$}
-
-With the above boundary conditions at hand, the ultra-weak formulation
-\eqnref{uweak} can be fitted in the abstract form \eqnref{variationEq}
-as
-\begin{align*}
-b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right), \left( v,
-\tau\right)\right) &= \left(u,\div \tau - \beta \cdot \grad
-v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad
-v\right)_{\Oh} \\
-&- \LRa{ \jump{\tau\cdot n}, \widehat{u} }_{\Gh
-  \setminus \Gp} + \LRa{ \widehat{f}_n, \jump{v} }_{\Gamma_h \setminus
-  \Gm} =  \left(f, v\right) -
-\LRa{ u_0, v }_{\Gamma_-} = l\left(\left(v, \tau\right)\right),
-\end{align*}
-which, after using the setting in Section \secref{abstractUweak},
-suggests the following trial space (see \cite{analysisDPG, Bui-ThanhDemkowiczGhattas11b} for details):
-\begin{align*}
-u, \sigma \in \L, \quad \text{and } \LRp{\uh,\fnh} \in
-\gamma\LRp{D\LRp{A}} \subset \gamma\LRp{  H^1(\Omega) \times
-H({\rm div}, \Omega)} = H^{\frac{1}{2}}\left(\Gh\right) \times H^{-\frac{1}{2}}\left(\Gh\right).
-\end{align*}
-The space for $u$ and $\sigma$ are simply scalar and vector $L^2$ spaces over $\Omega$, while the space for $\left(\uh,\fnh\right)$ is the trace space of the graph space of the operator $A$ subject to the boundary conditions.
-
-The minimum energy extension norm \eqnref{MEnorm} now reads
-\begin{align*}
-\|\widehat{u}\| &= \inf_{w\in H^1(\Omega),
-  \left.w\right|_{\Gamma_+}=0, \left.w\right |_{\Gh\setminus
-    \Gamma_+ } = \widehat{u}} \|w\|_{H^1(\Omega)}, \\ \|\widehat{f}_n\|
-&= \inf_{q\in H({\rm div},\Omega), \left.q\cdot n\right|_{\Gamma_-}=
-  0, \left. q\cdot n \right |_{\Gh\setminus
-    \Gamma_-} = \widehat{f}_n}
-\|q\|_{H({\rm div},\Omega)}.
-\end{align*}
-As a result, the canonical norm on $U$ is given by
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U^2 = 
-\|u\|_{L^2(\Oh)}^2 + \|\sigma\|_{L^2(\Oh)}^2 +
-\|\widehat{u}\|^2 + \|\widehat{f}_n\|^2.
-\]
-
-\subsection{Norms on $V$}
-
-%We will denote $\|\cdot \| = \|\cdot\|_{L^2}$ for all functions defined on $\Oh$. 
-As $\tau \in H({\rm div},\Oh)$ and $v \in H^1(\Oh)$, we will
-construct norms on $v$ and $\tau$ 
-which are equivalent to the canonical $H^1(K) \times H({\rm div},K)$
-norm over a single element
-\[
-\|\left(v,\tau\right)\|_{H^1(K) \times H({\rm div},K)}^2 =
-\|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2 + \|\tau\|_{L^2(K)}^2 +
-\|\div \tau\|_{L^2(K)}^2.
-\]
-The squared norm over the entire triangulation $\Oh$ is defined to be the squared sum of contributions from each element
-\[
-\|\left(v,\tau\right)\|_{H^1(\Oh) \times H({\rm div},\Oh)}^2
-= \sum_{K\in \Oh} \|\left(v,\tau\right)\|_{H^1(K) \times H({\rm
-    div},K)}^2.
-\]
-The exact norms that we will specify on $V$ will be determined later.
-
-The norms on the skeleton $\Gh$ for $v$ and $\tau$ are defined by duality from the bilinear form
-\begin{align*}
-\left\|\jump{\tau\cdot n}\right\| &= \left\|\jump{\tau\cdot n}\right\|_{\Gh \setminus \Gamma_+} \coloneqq \sup_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+} = 0} \frac{\langle \jump{\tau \cdot n}, w\rangle}{\|w\|_{H^1(\Omega)}},\\
-\left\|\jump{v}\right\|&=\left\|\jump{v}\right\|_{\Gh^0 \cup \Gamma_+} \coloneqq \sup_{\eta\in H({\rm div},\Omega), \left.\eta\cdot n\right|_{\Gamma_- \cup \Gamma_0} = 0} \frac{\langle \jump{v}, \eta\cdot n\rangle}{\|\eta\|_{H({\rm div},\Omega)}}.
-\end{align*}
-
-\subsection{Approximability of the quasi-optimal test norm}
-%\textcolor{blue}{need to define what we mean by robustness. perharps the best place is in the introduction}
-An obvious choice for the test norm would be the quasi-optimal norm; it is the canonical test norm, and DPG has been shown to be well-posed and robust under such an optimal test norm for a large class of problems \cite{DPGrobustness,Bui-ThanhDemkowiczGhattas11b, stokesDPG}.
-However, computations with the quasi-optimal test norm for convection-diffusion problems turn out to be quite problematic for small diffusion and coarse meshes.
-
-For convection-diffusion, the quasi-optimal test norm is 
-\[
-\|\left(v,\tau\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v
-\|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 +
-\|v\|_{L^2}^2 + \|\tau\|_{L^2}^2.
-\]
-%We note that the optimal test norm will automatically guarantee the
-%robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.
-Use of this norm for the convection-diffusion problem is difficult --- since the problem \eqnref{optvVar} for optimal test functions is local, we can transform the problem over a single element $K$ to the reference element $\widehat{K}$ and show that it is equivalent to a reaction-diffusion system, with diffusion parameter $\frac{\epsilon}{|K|}$, where $|K|$ is the element measure \cite{DBLP:journals/procedia/NiemiCC11}.
-We refer to the inverse of this parameter $\frac{|K|}{\epsilon}$ as the element Peclet number $\rm Pe$.
-For a coarse mesh and small diffusion parameter $\epsilon$, we will have a large element Peclet number, and optimal test functions under the quasi-optimal test norm will develop strong boundary layers of width $\rm Pe$, as seen in Figure~\ref{fig:optTestBoundary}.
-
-In the application of DPG in \cite{DPG1,DPG2,DPG3,DPG4}, the approximation of optimal test functions is done using polynomial enrichment.
-We search for the solution to \eqnref{optvVar} in the enriched test space $\tilde{V} \approx \prod_{K} P^{p+\Delta p}(K)$, where $p$ is the polynomial order of the trial space on a given element $K$.\footnote{$V$ is only \emph{approximately} equal to the space $\prod_{K} P^{p+\Delta p}(K)$.
-In practice, $V$ is constructed using locally $H^1$-conforming and Raviart-Thomas elements of appropriate order.}  In other words, optimal test functions are approximated element-by-element using polynomials whose order is $\Delta p$ more than the local order of approximation.
-Under this scheme, the error in approximation of test functions is tied to the effectiveness of the $p$-method.
-Unfortunately, for problems with boundary layers --- including the approximation of test functions under the quasi-optimal test norm --- the $p$-method performs very poorly.
-As a result of this poor approximation, the numerical solutions of the convection-dominated diffusion equation under DPG using the quasi-optimal test norm tend to be of poor quality, and do not exhibit all the proven properties of DPG (for example, the energy error may increase after mesh refinement, even though, by virtue of DPG delivering a best approximation, the energy error for a coarse mesh must be greater than or equal to the energy error for a finer mesh).
-We conclude that the error in approximation of optimal test functions using simple polynomial enrichment pollutes and ruins the performance of DPG under the quasi-optimal test norm.
-
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.25]{figs/opt.png}
-\caption{$v$ and $\tau$ components of the 1D optimal test functions corresponding to the flux $\widehat{f}_n$ on the right-hand side of a unit element for $\epsilon = 0.01$.
-The solution has been obtained using automatic $hp$-adaptivity driven by the test norm with the error tolerance set at 1\%.}
-\label{fig:optTestBoundary}
-\end{figure}
-
-The difficulty in using the quasi-optimal test norm for convection-diffusion is perplexing at first, considering that the quasi-optimal norm has yielded excellent results for the Helmholtz equation and other wave propagation problems.
-The difference between the two problems lies in the fact that, for wave propagation problems, the mesh size tends to be on the order of the wavenumber $k$ --- the singular perturbation parameter.
-Transforming the variational problem using the quasi-optimal test norm for wave propagation yields smooth optimal test functions that are approximated much more accurately using only polynomials over the reference element.
-Typically, the wavenumbers $k$ of physical interest are $O(100)$ with respect to a unit domain.
-The corresponding finite element problems will typically be solved on meshes containing approximately $O\!\left(k^d\right)$ elements in $\mathbb{R}^d$, well within the range of a computationally tractable simulation.
-However, for convection diffusion problems, the relevant range of $\epsilon$ for physical problems can be as small as $1e-7$.
-Solving on under-resolved meshes is thus unavoidable, and the approximability of optimal test functions must be addressed in order to take advantage of the properties of DPG.
-
-Resolving such boundary layers present in test functions under the quasi-optimal test norm has been investigated numerically using specially designed (Shishkin) subgrid meshes by Niemi, Collier, and Calo in
-\cite{DBLP:journals/procedia/NiemiCC11}.
-However, even with Shishkin meshes, the approximation of optimal test functions under the quasi-optimal norm is far more expensive and complex to implement than approximation of test functions using a simple $p$-enriched space for $V$.
-We therefore aim instead to design a test norm that does not induce boundary layers, but still delivers good approximation results over a range of $\epsilon$.
-
-\section{Analysis of a DPG test norm}
-\seclab{sec:testNormSec}
-We are interested in computing DPG optimal test functions for the convection-diffusion equation with very small values of $\epsilon$; due to the difficulty of approximating optimal test functions, we conclude that the use of the quasi-optimal test norm is infeasible towards this goal.
-
-However, if we naively choose a test norm that does not generate boundary layers, the performance of DPG may be adversely affected.
-For example, if $\|\left(v,\tau\right)\|_V^2 = \|v\|_{H^1(\Omega_h)}^2 + \|\tau\|^2_{H({\rm div},\Omega_h)}$, the $H^1(\Omega_h)\times H({\rm div},\Omega_h)$ norm, then the corresponding test functions will be smooth and free of boundary layers; however, the performance of DPG will provide approximations which worsen in quality as $\epsilon$ becomes very small \cite{DPG3,DPGrobustness}.
-
-Our goal is to construct a test norm that compromises between performance of DPG and approximability of test functions.
-This test norm should not produce boundary layers in the optimal test functions, but still induce an energy norm that yields good approximation properties for small $\epsilon$.
-We note that, even under the quasi-optimal norm, the norms on the flux and trace variables will likely depend on $\epsilon$.
-Thus, we aim to construct a test norm for which the DPG method will be robust in $\epsilon$ with respect to the \emph{field variables}.
-
-For now, we discuss the steps necessary to analyze the performance of DPG with respect to a non-canonical test norm.
-We require a priori that the test norm has separable $\tau$ and $v$ components --- in other words, that there are no terms in the test norm that couple $\tau$ and $v$ together.
-Problem \eqnref{optvVar} then decouples, such that the components of the vector-valued test function $\left(v,\tau\right)$ can be solved for independently of each other.
-The decoupled variational problems are no longer systems but scalar equations in $\tau$ and $v$, for which it is easier to conclude whether or not there are boundary layers in the solutions (the avoidance of boundary layers in the test norm will be discussed in more detail in Section~\ref{sec:num_exp}, which describes our numerical experiments).
-\textbf{This will ensure that the resulting DPG method does not suffer from approximation errors in the optimal test functions}.
-
-We begin with the following test norm:
-\[
-\left\|\left(v,\tau\right)\right\|^2_V \coloneqq \|v\|_{L^2}^2 + \epsilon\|\grad v\|_{L^2}^2 + \|\beta \cdot \grad v\|_{L^2}^2  + \frac{1}{\epsilon}\|\tau\|_{L^2}^2 + \|\div \tau\|_{L^2}^2.
-\]
-The use of this norm is problematic for practical computations; we will discuss the reasons why and present a modification of it in Section~\secref{sec:meshDep}.
-
-We can see how this norm will differ from the canonical $H^1(\Omega_h)\times H({\rm div},\Omega_h)$ norm: the clearest difference is the fact that the gradient in the streamline direction is $O(1)$, while the full gradient is $O(\sqrt{\epsilon})$, so that, in our test norm, the streamline gradient of $v$ will be emphasized over the full gradient of $v$ for small $\epsilon$.
-
-The choice of this test norm is implied by the mathematics of the adjoint problem.
-Roughly speaking, necessary conditions for the performance of DPG to not degenerate as $\epsilon \rightarrow 0$ are derived through analysis of specific test functions.
-For example, if $u$ is the first $L^2$ component of the solution to the variational problem defined in Section~\secref{sec:modelSec}, by choosing $(v,\tau) \in H^1(\Omega) \times H({\rm div},\Omega)$ such that
-\begin{align*}
-\div \tau - \beta \cdot \grad v &= u \\
-\frac{1}{\epsilon} \tau - \grad v &= 0,
-\end{align*}
-we have
-\[
- \nor{u}_{L^2}^2 = b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(v,\tau\right)\right) \leq \nor{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)}_{U,V} \nor{\left(v,\tau\right)}_V,
-\]
-and we recover the $L^2$ norm of $u$ from the bilinear form.
-
-Let $\|a\| \lesssim \|b\|$ denote an $\epsilon$-independent bound; specifically, that $\|a\| \leq C\|b\|$ for a constant $C$ independent of $\epsilon$.
-Consequently, if for any $u\in L^2(\Oh)$, $\nor{\left(v,\tau\right)}_V\lesssim \nor{u}_{L^2}$, then dividing through by $\nor{u}_{L^2}$ gives the bound
-\[
- \nor{u}_{L^2} \lesssim \nor{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)}_E.
-\]
-In other words, there is the guarantee that the $L^2$ error in $u$ is at least robustly bounded from above by the energy error.
-Then, if the energy error (which DPG minimizes) approaches zero, the $L^2$ error in $u$ will as well.
-The same exercise can be repeated for the stress $\sigma$, as well as the flux variables $\widehat{u}$, $\widehat{f}_n$.
-
-This methodology gives constraints on the quantities found in the test norm; any quantity present in $\nor{\left(v,\tau\right)}_V$ must be shown to be bounded from above independently of $\epsilon$ by the load of the adjoint problem.
-However, showing this simply amounts to showing \textit{standard energy estimates} for $H^1$ and $H({\rm div})$-conforming finite elements.
-A more detailed discussion on the reasoning behind the construction of test norms can be found in \cite{DPGrobustness}.
-
-The second step will be to \textbf{show the equivalence of the energy norm to explicit norms on $U$}.
-Since we do not generally have a closed form expression for the DPG energy norm, we seek to understand the behavior of DPG by finding a norm on $U$ to which the DPG energy norm is equivalent.
-Since $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U$ is a group variable from a tensor product space, we construct norms on $U$ through the combination of norms on $u$, $\sigma$, $\widehat{u}$, and $\widehat{f}_n$.
-Specifically, we use the norm on $U$
-\begin{equation}
-\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U}^2 \coloneqq \|u\|^2 + \|\sigma\|^2 + \left\|\widehat{u}\right\|^2 + \left\|\widehat{f}_n\right\|^2.
-\end{equation}
-For equivalence between norms, two constants are specified.
-However, since this norm on $U$ is a norm on four separate variables, we can specify not just two but eight equivalence constants.\footnote{Sharper estimates are attainable if these constants are allowed to vary over the mesh $\Oh$.
-See Section~\ref{sec:main_bounds} for a discussion.} In order to simplify analysis, we phrase this equivalence statement in an alternative form.
-
-Let $\nor{\cdot}_E \coloneqq \nor{\cdot}_{U,V}$, the energy norm induced by the test norm described above. We seek the bound of $\nor{\cdot}_E$ from above and below:
-\[
-\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2},
-\]
-where both $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ are defined as scaled combinations of the norms on $u, \sigma, \widehat{u}$, and $\widehat{f}_n$
-\begin{equation}
-\eqnlab{uNorms}
-\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,i}^2 \coloneqq \left(C_u^i\|u\|\right)^2 + \left(C_\sigma^i\|\sigma\|\right)^2 + \left(C_{\widehat{u}}^i\|\widehat{u}\|\right)^2 + \left(C_{\widehat{f}_n}^i\|\widehat{f}_n\|\right)^2,\quad i = 1,2
-\end{equation}
-Our goal is to explicitly derive the equivalence constants 
-%$C^1_u,\ldots, C^1_{\widehat{f}_n}$ and $C^2_u,\ldots, C^2_{\widehat{f}_n}$ 
-that define the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ respectively, taking into account any dependency on $\epsilon$.
-To do so, we need a relation between trial norms on $U$ and test norms on $V$.
-
-Recall from Section~\secref{energyPair} that every test norm induces a corresponding trial norm, and vice versa.
-Let $\|\cdot\|_{U,1} \simeq \|\cdot\|_{U,2}$ mean that the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ are equivalent, with equivalence constants independent of $\epsilon$.
-By equivalence of finite dimensional norms and the discussion in Section~\secref{energyPair} on the duality between test norms/energy norms, the norms \eqnref{uNorms} on $U$ induce the equivalent test norms on $\left(v,\tau\right) \in H^1(\Oh)\times H({\rm div},\Oh)$
-\begin{align*}
-\left\|\left(v,\tau\right)\right\|_{V,{U,i}} &\simeq \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(v,\tau\right)\right)}{C_u^i\|u\| + C_\sigma^i\|\sigma\| + C_{\widehat{u}}^i\|\widehat{u}\|+ C_{\widehat{f}_n}^i\|\widehat{f}_n\|}\\
-&= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \jump{\tau_n}, \widehat{u} \rangle_{\Gamma_-\cup \Gh^0} + \langle \widehat{f}_n, \jump{v} \rangle_{\Gamma_+ \cup \Gh^0}}{C_u^i\|u\| + C_\sigma^i\|\sigma\| + C_{\widehat{u}}^i\|\widehat{u}\|+ C_{\widehat{f}_n}^i\|\widehat{f}_n\|}\\
-& \simeq \frac{1}{C_u^i}\|g\| + \frac{1}{C_\sigma^i}\|f\| + \frac{1}{C_{\widehat{u}}^i}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle \jump{\tau\cdot n}, \widehat{u}\rangle}{\|\widehat{u}\|} +\frac{1}{C_{\widehat{f}_n}^i}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, \jump{v}\rangle}{\|\widehat{f}_n\|},
-\end{align*}
-where $f$ and $g$ are defined element-wise over $\Oh$ as 
-\begin{align*}
-g &\coloneqq \div \tau - \beta \cdot \grad v\\
-f &\coloneqq \epsilon^{-1}\tau + \grad v.
-\end{align*}
-By definition of the norms on the quantities defined on the skeleton $\Gh$, this gives the characterization of the induced test norm 
-\[
-\|\left(v,\tau\right)\|_{V,{U,i}} \simeq \frac{1}{C_u^i}\|g\| + \frac{1}{C_\sigma^i}\|f\| + \frac{1}{C_{\widehat{u}}^i}\|\jump{\tau\cdot n}\| + \frac{1}{C_{\widehat{f}_n}^i}\|\jump{v}\|, \quad i = 1,2.
-\]
-We can now use this relation to compare different norms on $U$ by comparing their induced norms on $V$ (recall that showing a robust inequality between two norms on $U$ is equivalent to showing the robust \textit{reverse} inequality in the induced norms on $V$).
-Namely, we can show the bound of $\nor{\cdot}_{U,1} \lesssim \nor{\cdot}_E$ by showing the bound $\nor{\left(v,\tau\right)}_{V,U,1} \gtrsim \nor{\left(v,\tau\right)}_{V}$, and likewise for $\nor{\cdot}_E \lesssim \nor{\cdot}_{U,2}$.
-
-Since the techniques used to show such bounds are more involved, we break the procedure up into two steps:
-\begin{enumerate}
-\item{}Decompose test functions $(v,\tau)$ into three separate, more easily analyzable components (Section~\ref{sec:strategy2}).
-\item{}Derive adjoint estimates (Section~\ref{sec:strategy3}).
-\end{enumerate}
-
-\subsection{Decomposition into analyzable components}
-\label{sec:strategy2}
-
-Having reduced the problem of comparing norms on $U$ to the comparison of norms on $V$, we break the analysis of $\left(v,\tau\right) \in V$ into the analysis of three subproblems.
-Define the decomposition
-\[
-\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right),
-\]
-where $\left(v_1,\tau_1\right)$ satisfies 
-\begin{align*}
-\epsilon^{-1}\tau_1 + \grad v_1 &= 0 ,\\
-\div \tau_1 - \beta\cdot \grad v_1 &=  \div \tau - \beta\cdot \grad v = g, 
-\end{align*} 
-and $\left(v_2,\tau_2\right)$ satisfies
-\begin{align*}
-\epsilon^{-1}\tau_2 + \grad v_2 &= \epsilon^{-1}\tau + \grad v = f, \\
-\div \tau_2 - \beta\cdot \grad v_2 &= 0.
-\end{align*}
-Both $(v_1,\tau_1), (v_2,\tau_2) \in H({\rm div}; \Omega)\times H^1(\Omega)$ are understood to satisfy these relations in a conforming sense over the domain $\Omega$; however, the divergence of $\tau$ and gradient of $v$ on the right hand side are still understood to be taken in an element-wise fashion.
-
-We will additionally require both $\left(v_1,\tau_1\right), \left(v_2,\tau_2\right)$ to satisfy the adjoint homogeneous boundary conditions
-\begin{align}
-\tau_i\cdot n &= 0, \quad \text{on }\Gamma_- \label{bc_1}\\
-v_i &= 0, \quad \text{on } \Gamma_+ \label{bc_2}
-\end{align}
-for $i = 1, 2$.
-The selection of $H({\rm div}, \Omega)\times H^1(\Omega)$ conforming test functions satisfying the specific boundary conditions above removes the contribution of the jump terms over the skeleton $\Gh$ in the bilinear form, allowing us to analyze field terms in the induced test norms separately from  the boundary/jump terms.
-
-Finally, by construction, $\left(v_0,\tau_0\right) \in H^1(\Oh) \times H({\rm div},\Oh)$ must satisfy 
-\begin{align*}
-\epsilon^{-1}\tau_0 + \grad v_0 &= 0\\
-\div \tau_0 - \beta\cdot \grad v_0 &= 0
-\end{align*}
-with jumps
-\begin{align*}
-\jump{v_0} &= \jump{v}, \quad \text{on }\Gh^0\\
-\jump{\tau_0 \cdot n} &= \jump{\tau \cdot n}, \quad \text{on }\Gh^0.
-\end{align*}
-and boundary conditions
-\begin{align*}
-v_0 &= v, \quad \text{on } \Gamma_+ \\
-\tau_0 \cdot n &= \tau \cdot n, \quad \text{on } \Gamma_-\cup \Gamma_0. 
-\end{align*}
-Notice that the evaluation the bilinear form $b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(v,\tau\right)\right)$ with each specific test functions returns only one part of the bilinear form.
-Furthermore, by choosing the proper loads $g = u$ and $f=\sigma$, we can recover from the bilinear form the norms of $u$ and $\sigma$ (as described in Section~\secref{sec:testNormSec}), as well as the norms on $\widehat{u}$, and $\widehat{f}_n$.\footnote{To recover the norms on $\widehat{u}$, and $\widehat{f}_n$, the loads $f$, and $g$ must be zero, and the jumps of the test function $(v,\tau)$ must be chosen specifically.}
-
-We have now decomposed an arbitrary test function $\left(\tau,v\right)$ into a discontinuous contribution and two continuous contributions.
-Recall that our goal is to show the robust bound from above and below of the DPG energy norm by $\|\cdot \|_{U,1}$ and $\|\cdot \|_{U,2}$:
-\[
-\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}.
-\]
-
-Under the duality of trial and test norms and the decomposition of test functions $\left(\tau,v\right) \in V$ into $\left(\tau_0,v_0\right), \left(\tau_1,v_1\right)$, and $\left(\tau_2,v_2\right)$, the above bound is equivalent to bounding each component
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,U,1} &\gtrsim \sum_{i=0}^2\|\left(v_{i},\tau_{i}\right)\|_V \gtrsim \|\left(v,\tau\right)\|_{V,U,2}.
-%\|\left(v,\tau\right)\|_{V,1} &\lesssim \|\left(v_{1},\tau_{1}\right)\|_V \lesssim \|\left(v,\tau\right)\|_{V,2}\\
-%\|\left(v,\tau\right)\|_{V,1} &\lesssim \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|\left(v,\tau\right)\|_{V,2}
-\end{align*}
-Bounding $\|\left(v_0,\tau_0\right)\|$ requires the use of techniques first developed in \cite{analysisDPG} and adapted to convection-diffusion in \cite{analysisDPG} and \cite{DPGrobustness}.
-However, since $\left(\tau,v\right) \in H({\rm div}, \Omega)\times H^1(\Omega)$, the bound from above of test functions $\|\left(v_{1},\tau_{1}\right)\|_V$ and $\|\left(v_{2},\tau_{2}\right)\|_V$ is reduced to proving classical error estimates for the adjoint equations
-\begin{align*}
-\epsilon^{-1}\tau_1 + \grad {v_1} &= 0 \\
-\div {\tau_1} - \beta\cdot \grad {v_1} &=  g, \\
-\left.\tau_1\cdot n\right|_{\Gamma_-} &= 0, \\
-\left.v_1\right|_{\Gamma_+} &= 0.
-\end{align*} 
-and 
-\begin{align*}
-\epsilon^{-1}\tau_2 + \grad {v_2} &= f \\
-\div {\tau_2} - \beta\cdot \grad {v_2} &= 0, \\
-\left.\tau_2\cdot n\right|_{\Gamma_-} &= 0, \\
-\left.v_2\right|_{\Gamma_+} &= 0.
-\end{align*} 
-More generally, we can analyze the adjoint equations
-\begin{align}
-\epsilon^{-1}\tau + \grad {v} &= f \label{adjoint1}\\
-\div {\tau} - \beta\cdot \grad {v} &= g, \label{adjoint2}
-\end{align}
-for arbitrary data $f, g\in L^2({\Omega})$ and boundary conditions $\jump{\tau\cdot n}_{\Gamma_-} = 0$ and $\jump{v}_{\Gamma_+} = 0$.
-In other words, we want to analyze the stability properties of the adjoint equations by deriving bounds of the form $\|\left(v_1,\tau_1\right)\|_V\lesssim \|g\|_{L^2}$ and $\|\left(v_2,\tau_2\right)\|_V \lesssim \|f\|_{L^2}$.
-
-%An alternate interpretation of the above decomposition is that each component $(v_i,\tau_i)$ of the decomposition corresponds to a term in the bilinear form.
-For example, .
-If we evaluating our bilinear form with $(v,\tau) = (v_1,\tau_1)$ delivers
-%\[
-%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-%\left( v_1, \tau_1 \right)\right) = (u,g)_{L^2} 
-%\]
-%By choosing $g = u$,
-
-\subsection{Adjoint estimates}
-\label{sec:strategy3}
-
-The final step to estimating the induced norm on $U$ by a selected localizable test norm on $V$ is to derive adjoint stability estimates on $\tau$ and $v$ in terms of localizable normed quantities.
-We will construct complete test norms on $V$ through combinations of these normed quantities.%, where each normed quantity on $\tau$ or $v$ will correspond roughly to $\|u\|_{L^2}$, $\|\sigma\|_{L^2}$, $\|\widehat{u}\|$, or $\|\widehat{f}_n\|$.
-
-We introduce first the bounds derived; the proofs will be given later.
-For this analysis, it will be necessary to assume certain technical conditions on $\beta$.
-For each proof, we require $\beta \in C^2(\bar{\Omega})$ and $\beta, \div \beta = O(1)$.
-Additionally, we will assume that some or all of the following assumptions hold:
-\begin{align}
-&\curl \beta = 0, \quad 0<C \leq \left | \beta\right |^2 + \frac{1}{2}\div \beta, \quad C = O(1) \label{a_req},\\
-&\grad \beta + \grad \beta ^T - \div \beta I = O(1) \label{b_req},\\
-&\div \beta = 0 \label{c_req}.
-\end{align}
-Under proper assumptions on $\beta$, we have the robust bounds, which are proved in the Appendix. 
-\begin{itemize}
-\item \textbf{Lemma \ref{lemma_stream}}: \textit{For $\beta$ satisfying \eqref{a_req} and \eqref{b_req}, %$f=0$ 
-and $v_1 \in H^1(\Omega)$, satisfying equations \eqref{adjoint1} and \eqref{adjoint2} with $f=0$, and with boundary conditions \eqref{bc_1} and \eqref{bc_2}},
-\begin{align*}
-\|\beta \cdot \grad v_1 \| &\lesssim \| g\|.
-\end{align*}
-Similarly, from $\div \tau_1 - \beta\cdot \grad v_1 = g$, we get $\|\div \tau_1\| \lesssim \|g\|$ as well.  
-\item \textbf{Lemma \ref{lemma_grad}}: \textit{For $\beta$ satisfying \eqref{a_req}, and $v \in H^1(\Omega)$ satisfying equations \eqref{adjoint1} and \eqref{adjoint2} and boundary conditions \eqref{bc_1} and \eqref{bc_2}, and for sufficiently small $\epsilon$},
-\[
-\epsilon \|\grad v\|^2 + \|v\|^2 \lesssim \|g\|^2 + \epsilon \|f\|^2.
-\]
-We can characterize both $v_1$ and $v_2$ in the above decompositions using this theorem by setting either $f=0$ or $g=0$. 
-%\begin{align*}
-%\epsilon \|\grad v_1\|^2 + \|v_1\|^2 &\lesssim \|g\|^2\\
-%\epsilon \|\grad v_2\|^2 + \|v_2\|^2 &\lesssim \epsilon \| f\|^2.
-%\end{align*}
-%By the triangle inequality, this implies for any $w$ of the form $w=v_1+v_2$
-%\begin{align*}
-%\epsilon \|\grad w\|^2 + \|w\|^2 &\lesssim \|g\|^2 + \epsilon \| f\|^2
-%\end{align*}
-\item \textbf{Lemma \ref{lemma_boundary}}: \textit{For $\beta$ satisfying \eqref{a_req}, \eqref{c_req}, and solutions $v_0 \in H^1(\Oh)$ and $\tau_0 \in H({\rm div},\Oh)$ of equations \eqref{adjoint1} and \eqref{adjoint2} with $f=g=0$,}
-\begin{align*}
-\|\grad v_0\| = \frac{1}{\epsilon}\|\tau_0\| &\lesssim \frac{1}{\epsilon} \| \jump{\tau_0\cdot n}\|_{\Gh \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| \jump{v_0}\|_{\Gh^0 \cup \Gamma_+}.
-\end{align*}
-\end{itemize}
-We are interested in showing the equivalence of the DPG energy norm with norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$, respectively.
-We will show this by bounding $\|\cdot \|_V$ from below by $\|\cdot\|_{V,U,1}$ and from above by $\|\cdot\|_{V,U,2}$ (the induced test norms for $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$, respectively).
-
-%We will use Lemmas \ref{lemma_stream}, \ref{lemma_grad}, and \ref{lemma_boundary} to prove such bounds on our yet-unspecified test norm $\|(\tau,v)\|_V$.
-
-%Together, these estimates will be sufficient to construct a complete norm on $V$ and demonstrate bounds on induced test norms for different scalings of norms on $U$.  
-%\tanbui{}{again, using the same notation
-%  $(v, \tau)$ for all three problems is not a good idea. Why don't we
-%  use $(v_i,\tau_i)$ introduced above? Things are much clearer this
-%  way?}
-\subsection{A mesh-dependent test norm}
-\seclab{sec:meshDep}
-Ideally, we would be interested in the use of the test norm 
-\[
-\|\left(v,\tau\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2
-\]
-for practical computations.
-However, the presence of the term $\|v\|$ together with $\sqrt{\epsilon}\|\grad v\|$ (and similarly $\|\div \tau\|$ and $\frac{1}{\sqrt{\epsilon}}\|\tau\|$ terms) induces boundary layers in the optimal test functions for under-resolved meshes.
-We can see this by recovering the strong form of the variational problem defining test functions.
-We first note that the variational problems for the $v$ and $\tau$ components of optimal test functions decouple from each other under this test norm.
-Then, examining the variational problem for the $v$ component only of an optimal test function, and assuming $\div \beta = 0$ for illustrative purposes, we have
-\begin{align*}
-\left(\left(v,0\right),\left(\delta v,\delta\tau\right)\right)_{V} &= (v,\delta v) + \epsilon \left(\grad v,\grad \delta v\right) + \left(\beta \cdot \grad v, \beta \cdot \grad \delta v\right)\\
-&= \left(v - \epsilon \Delta v - \div \left(\left(\beta \otimes \beta\right) \grad v\right), \delta v\right)_{L^2} + \langle \epsilon \grad v\cdot n, \delta v\rangle + \langle n\cdot \left(\beta\otimes\beta\right) \grad v , \delta v\rangle.
-\end{align*}
-After integration by parts, we recover the strong form of the operator $L$ inducing such a variational problem 
-\[
-Lv \coloneqq v - \epsilon \Delta v - \div \left(\left(\beta \otimes \beta\right) \grad v\right),
-\]
-where we neglect the resulting boundary terms from integration by parts for now.
-
-The streamline direction $\beta$ induces an anisotropic diffusion, while the $\sqrt{\epsilon}\|\grad v\|_{L^2}$ term induces a small isotropic diffusion contribution everywhere.
-Since any vector in the cross-stream direction is in the null space of the anisotropic diffusion tensor, in the cross-stream directions, the optimal test function is governed only by the cross-stream part of the operator $L$
-\[
-L_{\rm \beta^\perp} \coloneqq v - \epsilon \Delta v,
-\]
-and can develop boundary layers in those directions.
-The presence of boundary layers has been verified through numerical computation as well; using an $H^1$-conforming finite element code with $hp$-adaptivity \cite{demkowicz2006computing}, the solution to the variational problem defining the optimal test function under the above test norm was computed.
-Figure~\ref{fig:boundaryTest} shows the result of such a computation for the $v$ component of an optimal test function under the above test norm.
-\begin{figure}[!h]
-\centering
-\subfigure{\includegraphics[scale=.22]{figs/mesh1.png}}
-\subfigure{\includegraphics[scale=.22]{figs/sol1.png}}
-\caption{The $v$ component of the optimal test function corresponding to flux $\widehat{u} = x(1-x)$ on the bottom side of a unit element for $\epsilon = 0.01$.
-The corresponding $hp$-mesh used to compute the solution is displayed to the left.}
-\label{fig:boundaryTest}
-\end{figure}
-To avoid boundary layers in the optimal test functions, we follow \cite{DPGrobustness} in scaling the $L^2$ contributions of $v$ by $C_v(K)$, such that, when transformed to the reference element, both $C_v(K)\|v\|^2$ and $\epsilon\|\grad v\|^2$ are of the same magnitude.
-Similarly, we scale the $L^2$ contributions of $\tau$ by $C_\tau(K)$ such that $\frac{C_\tau(K)}{\epsilon} \|\tau\|^2$ and $\|\div \tau\|^2$ are of the same magnitude as well.
-For this paper, we consider only isotropic refinements on quadrilateral elements in 2D.
-
-Our test norm, as defined over a single element $K$, is now
-\[
-\|\left(v,\tau\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
-\]
-This modified test norm avoids boundary layers in the locally computed optimal test functions, but for adaptive meshes, provides additional stability in areas of heavy refinement, where the best approximation error tends to be large and stronger robustness is most necessary.
-This leads to a test norm which produces easily approximable optimal test functions, but still provides \textit{asymptotically} the strongest test norm and tightest robustness results in the areas of highest error.
-
-\subsection{Equivalence of energy norm with $\nor{\cdot}_U$}
-%\subsection{Relations between trial and test constants}
-\label{sec:main_bounds}
-
-The main theoretical result of this paper can now be given:
-\begin{lemma}
-Under the mesh-dependent test norm
-\[
-\|\left(v,\tau\right)\|_{V,\Oh}^2 = \|C_vv\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \|C_\tau\tau\|^2,
-\]
-where $C_v, C_{\tau}\in L^2(\Omega)$ are defined elementwise through
-\begin{align*}
-\left.C_v\right |_K &= \min\left\{\sqrt{\frac{\epsilon}{|K|}},1\right\}\\
-\left.C_{\tau}\right |_K &= \min\left\{\frac{1}{\sqrt{\epsilon}},\frac{1}{\sqrt{|K|}}\right\}.
-\end{align*}
-If $\beta$ satisfies \eqref{a_req}, \eqref{b_req}, and \eqref{c_req}, the DPG energy norm $\nor{\cdot}_E$ satisfies the following equivalence relations
-\begin{align*}
-\nor{u}_{L^2} + \nor{\sigma}_{L^2} + \epsilon\nor{\widehat{u}} + \sqrt{\epsilon}\nor{\widehat{f}_n} 
-&\lesssim \nor{\left(u,\sigma, \widehat{u},\widehat{f}_n\right)}_E \\ 
-%\nor{\left(u,\sigma, \widehat{u},\widehat{f}_n\right)}_E &\lesssim \nor{u}_{L^2} + \nor{C_\sigma \sigma}_{L^2} + \frac{1}{\sqrt{\epsilon}} \left(\nor{\widehat{u}} + \nor{\widehat{f}_n}\right),
-\nor{\left(u,\sigma, \widehat{u},\widehat{f}_n\right)}_E &\lesssim \nor{u}_{L^2} + \nor{\frac{1}{\epsilon C_\tau} \sigma}_{L^2} + \frac{1}{\sqrt{\epsilon}} \left(\nor{\widehat{u}} + \nor{\widehat{f}_n}\right).
-\end{align*}
-%where $C_\sigma \in L^2(\Omega)$ is defined elementwise through $\left.C_\sigma\right|_K  = \max\left\{ \frac{1}{\sqrt{\epsilon}} , \frac{\sqrt{|K|}}{\epsilon} \right\}$.
-\end{lemma}
-
-\begin{proof}
-We begin by proving the bound from below.
-As a consequence of the duality of norms discussed in Section~\secref{energyPair}, we know that the norm $\left\| u \right\|_{U,1}$ is induced by a specific test norm $\| v  \|_{V,U,1}$.
-To bound $\|\cdot\|_E$ robustly from above or below by a given norm $\left\| u \right\|_{U,2}$ on $U$ now only requires the robust bound in the opposite direction of $\| v \|_{V,U,1}$ by $\|v\|_{V,U,2}$.
-
-For $f$ and $g$ defined in \eqref{adjoint1} and \eqref{adjoint2},
-\begin{align*}
-f &= \epsilon^{-1}\tau + \grad v  \\
-g &=\div \tau - \beta\cdot \grad v,
-\end{align*} 
-we can characterize the test norm for 
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,1}^2 = \|u\|^2 + \|\sigma\|^2 + \epsilon\|\widehat{u}\|^2+ \sqrt{\epsilon}\|\widehat{u}\|^2
-\]
-through the equivalence relation
-\begin{align*}
-\|\left(v,\tau\right)\|_{V,U,1} &\simeq \sup_{u,\sigma,\widehat{u},\widehat{f}_n}\frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\|u\| + \|\sigma\| + \epsilon\|\widehat{u}\|+ \sqrt{\epsilon}\|\widehat{u}\|}\\
-& \simeq \|g\| + \|f\| + \frac{1}{\epsilon}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle \jump{\tau\cdot n}, \widehat{u}\rangle}{\|\widehat{u}\|} + \frac{1}{\sqrt{\epsilon}}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, \jump{v}\rangle}{\|\widehat{f}\|},
-\end{align*}
-which, by definition of the boundary norms, is 
-\[
-\|\left(v,\tau\right)\|_{V,U,1} \simeq \|g\| + \|f\| + \frac{1}{\epsilon}\|\jump{\tau\cdot n}\| + \frac{1}{\sqrt{\epsilon}}\|\jump{v}\|.
-\]
-We wish to show the bound
-\[
-\nor{\left(v,\tau\right)}_{V,\Oh} \lesssim \|g\| + \|f\| + \frac{1}{\epsilon}\|\jump{\tau\cdot n}\| + \frac{1}{\sqrt{\epsilon}}\|\jump{v}\|.
-\]
-By noting that both 
-\begin{align*}
-\nor{C_vv_0} &\leq \nor{v_0},\\
-\nor{C_\tau\tau_0} &\leq \frac{1}{\sqrt{\epsilon}}\nor{\tau_0},
-\end{align*}
-we have that $\nor{\left(v,\tau\right)}_{V,\Oh} \leq \nor{\left(v,\tau\right)}_{V}$, so it suffices to prove the bound for the mesh-independent test norm 
-\[
-\|\left(v,\tau\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2.
-\]
-
-We will bound $\|\left(v,\tau\right)\|_V$ for all $\left(v,\tau\right)$ by decomposing $\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right)$ as described in Section~\ref{sec:strategy2}.
-
-By the triangle inequality, robustly bounding $\|\left(v,\tau\right)\|_V$ from above reduces to robustly bounding each component 
-\[
-\|\left(v_{0},\tau_{0}\right)\|_V, \|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|g\| + \|f\| + \frac{1}{\epsilon}\|\jump{\tau\cdot n}\| + \frac{1}{\sqrt{\epsilon}}\|\jump{v}\|.
-\]
-
-%Roughly speaking, Lemma \ref{lemma_grad} concerns the robust control of $u$ by the energy error; Lemmas \ref{lemma_stream} and \ref{lemma_boundary} concern the robust control of field variable $\sigma$ and flux/trace variables, respectively.
-
-\begin{itemize}
-\item \textbf{Bound on $\|\left(v_{0},\tau_{0}\right)\|_V$}
-
-Lemma \ref{lemma_boundary} gives control over $\sqrt{\epsilon}\|\grad v_0\| + \frac{1}{\epsilon}\|\tau_0\|$ through
-\[
-\|\grad v_0\| = \frac{1}{\epsilon}\|\tau_0\| \lesssim \frac{1}{\epsilon} \nor{\jump{\tau_0\cdot n}}_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \nor{\jump{v_0}}_{\Gamma_h^0 \cup \Gamma_+} = \frac{1}{\epsilon} \nor{ \jump{\tau\cdot n}}_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \nor{ \jump{v}}_{\Gamma_h^0 \cup \Gamma_+}.
-\]
-Lemma 4.2 of \cite{analysisDPG} gives us the Poincare inequality for discontinuous functions
-\[
-\|v_0\| \lesssim \|\grad v_0\| + \|\jump{v}\|.
-\]
-%Since $f=0$, by Lemma 2, $\|\beta\cdot \grad v_0\|  \lesssim \|g\| = 0$.  
-Since $g = 0$, $\| \div \tau_0\| = \|\beta\cdot \grad v_0\|\lesssim \|\grad v_0\|$, which we now have control over as well.
-
-\item \textbf{Bound on $\|\left(v_{1},\tau_{1}\right)\|_V$}
-
-With $f = 0$, Lemma \ref{lemma_stream} provides the bound
-\[
-\|\beta \cdot \grad v_1 \| \lesssim \| g\|.
-\]
-Noting that $\div \tau_1 = g+\beta\cdot \grad v_1$ gives $\|\div \tau_1 \| \lesssim \|g\|$ as well.  Lemma \ref{lemma_grad} gives
-\[
-\epsilon \|\grad v_1\|^2 + \|v_1\|^2 \lesssim \|g\|^2,
-\]
-and noting that $\epsilon^{-1/2}\tau_1 = \epsilon^{1/2}\grad v_1$ gives $\epsilon\|\grad v_1\|^2 = \epsilon^{-1}\|\tau_1\|^2 \lesssim \|g\|^2$ as well.
-
-\item \textbf{Bound on $\|\left(v_{2},\tau_{2}\right)\|_V$}
-
-Lemma \ref{lemma_grad} provides, for $\epsilon$ sufficiently small, 
-\[
-\epsilon \|\grad v_2\|^2 + \|v_2\|^2 \lesssim  \epsilon \| f\|^2 \leq \|f\|^2.
-\]
-We have $\epsilon^{-1}\tau_2 = f - \grad v_2$, so $\epsilon^{-1} \|\tau_2\| \lesssim \|f\| + \|\grad v_2\|$.
-Lemma~\ref{lemma_grad} implies $\|\grad v_2\|^2  \lesssim  \| f\|^2$, so for $\epsilon \leq 1$, we have $\epsilon^{-1/2}\|\tau_2\| \leq \epsilon^{-1}\|\tau_2\| \lesssim \|f\|$.
-The remaining terms can be bounded by noting that, with $g = 0$, $\|\div \tau_2\| = \|\beta\cdot \grad v_2\| \lesssim \|\grad v_2\| \lesssim \|f\| $.
-\end{itemize}
-
-We have shown the robust bound of the norm $\|\cdot \|_{U,1}$ on $U$ by the energy norm; for a full equivalence statement, we require a bound from above on the energy norm by the norm $\|\cdot \|_{U,2}$ on $U$.
-By the duality of the energy and test norm, this is equivalent to bounding the test norm from below by the test norm induced by $\|\cdot \|_{U,2}$.
-For a norm on $U$ of the form
-\[
-\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,2}^2 = \|u\|^2 + \nor{C_\sigma \sigma}^2 + \frac{1}{{\epsilon}}\left( \|\widehat{u}\|^2 + \|\widehat{f}_n\|^2\right),
-\]
-the induced test norm is equivalent to
-\begin{align*}
-\| \left(\tau,v\right) \|_{V,U,2} &\simeq \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_E} \\
-&\simeq \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right) \in U\setminus \{0\}} \frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \jump{\tau_n}, \widehat{u} \rangle + \langle \widehat{f}_n, \jump{v} \rangle
-}{\|u\| + \nor{\left(\epsilon C_\tau\right)^{-1}\sigma} + \frac{1}{\sqrt{\epsilon}}\left(  \|\widehat{u}\| + \|\widehat{f}_n\| \right)} \\
-&\simeq \|g\| + \nor{\epsilon C_\tau f} + {\sqrt{\epsilon}}\left(\sup_{\widehat{u},\widehat{f}_n \neq 0}\frac{\langle \jump{\tau_n}, \widehat{u} \rangle + \langle \widehat{f}_n, \jump{v} \rangle}{\|\widehat{u}\| + \|\widehat{f}_n\|}\right),
-\end{align*}
-where $f$ and $g$ are 
-\begin{align*}
-f &= \frac{1}{\epsilon}\tau + \grad v\\
-g &= \div \tau - \beta \cdot \grad v,
-\end{align*}
-the loads of the adjoint problem defined in \eqref{adjoint1}, \eqref{adjoint2}.
-
-Note that $\epsilon C_\tau \leq \sqrt{\epsilon}$. Then, by the triangle inequality, we have the bounds
-\begin{align*}
-%\sqrt{\epsilon} \|f \| &\leq \epsilon^{-1/2} \| \tau\| + \sqrt{\epsilon} \|\grad v\| \lesssim \|\\
-\|\epsilon C_\tau f \| &\leq C_\tau \nor{ \tau} + \epsilon C_\tau \nor{\grad v} \lesssim \| \left(\tau,v\right)\|_{V,\Oh}\\
-\|g \| &\leq \|\div \tau\| +  \|\beta \cdot \grad v\| \lesssim \| \left(\tau,v\right)\|_{V,\Oh}
-\end{align*}
-We estimate the supremum on the jumps of $\left(\tau,v\right)$ by following \cite{DPGrobustness}; we begin by choosing $\eta \in H({\rm div}; \Omega)$, $w\in H^1(\Omega)$, such that $\left.\left(\eta-\beta w \right)\cdot n\right |_{\Gamma_+} = 0$ and $\left.w\right |_{\Gamma_-\cup\Gamma_0} = 0$, and integrating the boundary pairing by parts to get
-\begin{align*}
-\langle \jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle &= (\tau,\grad w) + (\div \tau, w) + \left(\eta - \beta w, \grad v\right) +  \left(\div \left(\eta - \beta w\right), v\right)\\
-&\lesssim \|C_\tau\tau\| \nor{ \frac{1}{C_\tau}\grad w} + \|\div \tau\| \|w\| \\
-&\left.\hspace{.3cm}\right. + \sqrt{\epsilon}\| \grad v \|\frac{1}{\sqrt{\epsilon}}\|\eta\| +  \|\beta \cdot \grad v\| \| w\|\\
-&\left.\hspace{.3cm}\right. + \|C_vv\|\nor{\frac{1}{C_v}\div \eta} + \| C_vv\| \nor{\frac{1}{C_v}w} \\
-&\left.\hspace{.3cm}\right. + \|C_v v\| \nor{\frac{1}{C_v} \grad w},
-\end{align*}
-where we have used that $\epsilon < 1$, $\div \beta = O(1)$, and that $\|\beta\cdot \grad w\|\lesssim \|\grad w\|$.
-
-Without loss of generality, assume the problem is scaled such that $\max_{K\in\Oh}|K| \leq 1$.
-Then, $\frac{1}{C_\tau^2}\leq \frac{1}{C_v^2} \leq \frac{1}{\epsilon}$, and an application of discrete Cauchy-Schwarz gives us
-\begin{align*}
-\langle \jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle &\lesssim \|\left(\tau,v\right)\|_{V,\Oh}\frac{1}{\sqrt{\epsilon}}\left(\nor{\eta}_{H({\rm div},\Omega)} + \nor{w}_{H^1(\Omega)}\right),\\
-&\lesssim \|\left(\tau,v\right)\|_{V,\Oh}\frac{1}{\sqrt{\epsilon}}\left(\nor{\eta-\beta w}_{H({\rm div},\Omega)} + \nor{w}_{H^1(\Omega)}\right),
-\end{align*}
-since $\|\eta\|_{H({\rm div},\Omega)} = \|\eta - \beta w + \beta w\|_{H({\rm div},\Omega)} \leq \|\eta - \beta w\|_{H({\rm div},\Omega)} + \|\beta w\|_{H({\rm div},\Omega)} \lesssim \|\eta-\beta w\|_{H({\rm div},\Omega)} + \|w\|_{H^1(\Omega)}$.
-Dividing through and taking the supremum gives
-\[
-\sup_{w,\eta \neq 0} \frac{\langle\jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle}{\left(\nor{\eta-\beta w}_{H({\rm div},\Omega)} + \nor{w}_{H^1(\Omega)}\right)} \lesssim \|\left(\tau,v\right)\|_{V,\Oh}\frac{1}{\sqrt{\epsilon}}.
-\]
-To finish the proof, define $\rho \in H^{1/2}(\Gamma_h)$ and $\phi \in H^{-1/2}(\Gamma_h)$ such that $\rho = \left.w\right|_{\Gamma_h}$ and $\phi = \left.(\eta-\beta w)\cdot n\right|_{\Gamma_h}$, and note that, from \cite{analysisDPG}, by the definition of the trace norms on $\jump{\tau\cdot n}$ and $\jump{v}$
-\begin{align*}
-\sup_{\rho,\phi \neq 0} \frac{\langle \jump{\tau\cdot n},\rho\rangle + \langle \jump{v},\phi \rangle}{\|\rho\|_{H^{1/2}(\Gamma_h)}+\|\phi\|_{H^{-1/2}(\Gamma_h)}} &= \sup_{w,\eta \neq 0} \frac{\langle \jump{\tau\cdot n},w\rangle + \langle \jump{v},\left(\eta - \beta w\right)\cdot n\rangle}{ \|w\|_{H^1(\Omega)}+\|\eta-\beta w\|_{H({\rm div},\Omega)}}.
-\end{align*}
-Together, the bounds on the jump terms and the bounds on $\|g\|$ and $\|f\|$ imply $\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{E} \lesssim \left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,2}$.
-\end{proof}
-
-\subsection{Comparison of boundary conditions}
-
-It is worth addressing the effect of boundary conditions on stability.
-Specifically, a test norm that provides stability for one set of boundary conditions may perform poorly for another set.
-Take, for example, the test norm defined in Section~\ref{sec:main_bounds} and the convection-diffusion problem with Dirichlet boundary conditions.
-
-The bilinear form for the case of Dirichlet boundary conditions is 
-\[
-b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(v,\tau\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) + \langle \widehat{u}, \jump{\tau \cdot n} \rangle_{\Gh^0} + \langle \widehat{f}_n, \jump{v} \rangle_{\Gh}.
-\]
-Notice that the boundary terms in the final bilinear form are different; hence, the adjoint problems associated with Section~\ref{sec:strategy3} will now carry different boundary conditions as well.
-Likewise, the stability properties proven previously will not hold under a different set of boundary conditions.
-%We note that 
-%\begin{align*}
-%b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gh^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gh}
-%&= \| u \|^2_{L^2}
-%\end{align*}
-%for the specific continuous test functions $\tau$ and $v$ satisfying
-%\begin{align*}
-%\div \tau - \beta \cdot \grad v &= u \\
-%\frac{1}{\epsilon}\tau + \grad v &= 0
-%\end{align*}
-%with boundary condition $\left.v\right|_\Gamma = 0$.
-Choosing a continuous conforming test function $v$ removes the contribution of the term $\langle \widehat{f}_n, \left[v\right] \rangle$ on the mesh skeleton, while the boundary conditions remove the contribution of boundary terms from the bilinear form.
-Then, for this specific choice of $\left(\tau, v\right)$,
-%\begin{align*}
-%\|u\|_{L^2}^2 &= b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right)}{\|\left(\tau, v\right)\|_V}\|\left(\tau, v\right)\|_V \leq \|u\|_E \|\left(\tau, v\right)\|_V
-%\end{align*}
-%At minimum, we want $\|u\|_{L^2} \lesssim \|u\|_E$, which requires 
-%\[
-%\|\left(\tau, v\right)\|_V \lesssim \| u \|_{L^2}
-%\]
-%for any choice of $u \in L^2$ (dividing through by $\|u\|_{L^2}$ gives the desired result).
-This can be considered a ``sanity check"; at the minimum, we at least want control over the behavior of the single field variable $u$.
-However, we are unable to prove this in the case of Dirichlet boundary conditions.
-
-As it turns out, the robust bounds given in Section~\ref{sec:main_bounds} hold in $\mathbb{R}^d$ for arbitrary $d$; however, we can show that for the case of Dirichlet boundary conditions, the same results do not hold, even in 1D.
-%In 1D, the problem reduces to 
-%\begin{align*}
-%\frac{1}{\epsilon}\sigma - u' &= 0\\
-%\left(u - \epsilon \sigma \right)' &=f
-%\end{align*}
-%with bilinear form
-%\begin{align*}
-%b\left(\left(u,\sigma,\widehat{u},\widehat{f}\right),\left(\tau,v\right)\right) &= \sum_{k=1}^N \left(\left.\widehat{u}(x) \tau(x)\right |^{x_k}_{x_{k-1}} + \left.\widehat{f}(x) v(x)\right |^{x_k}_{x_{k-1}}\right) \\
-%&+ \left(\sigma,\epsilon^{-1}\tau\right)_{\Oh} + (u,\tau')_{\Oh}- \left(u - \epsilon \sigma,v'\right)_{\Oh}
-%\end{align*}
-%where $\widehat{u}(x), \widehat{f}(x) \in \mathbb{R}$ are now point values defined on mesh points $x_k$ for $k=1,\ldots,N$, where $N$ is the number of elements.
-We can assume without loss of generality that $\Oh$ is the unit interval $(0,1)$.
-%
-%Let us first provide an interpretation of Lemma~\ref{lemma_stream}. Recall the bilinear form 
-%\begin{align*}
-%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-%\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
-%v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh} - \LRa{
-%\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n,
-%  \jump{v} }_{\Gh},
-%\end{align*}
-%By choosing $(v,\tau)$ such that
-%\begin{align*}
-%\div \tau - \beta \cdot \grad v &= u \\
-%\frac{1}{\epsilon} \tau + \grad v &= 0
-%\end{align*}
-%we will have 
-%\[
-%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-%\left( v, \tau \right)\right) =\|u\|_{L^2}^2 
-%\]
-%Given this, we can use the definition of the energy norm \eqnref{energyNorm} to bound
-%\[
-%\|u\|_{L^2}^2 = b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-%\left( v, \tau \right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
-%\left( v, \tau \right)\right)}{\|(v,\tau)\|_V}\|(v,\tau)\|_V \lesssim \|u\|_E \|(v,\tau)\|_V
-%\]
-%If we can show that $\|(v,\tau)\|_V \lesssim \|u\|_{L^2}$ for $(v,\tau)$ as defined above, then this implies 
-%\[
-%\|u\|_{L^2} \lesssim \|u\|_E
-%\]
-%By the fact that 
-Consider now the 1D analogue of the estimate given by Lemma~\ref{lemma_stream}.  In 1D, $\|\beta\cdot\grad v_1\| \lesssim \|g\|$ reduces to the inequality 
-\[
-\|\beta v_1'\|\lesssim \|g\|, \quad g\in L^2\!\left(\Oh\right).
-\]
-Without this inequality, we are unable to prove the robust bound on the $L^2$ error $\|u-u_h\|_{L^2} \lesssim \nor{(u,\sigma,\widehat{u},\widehat{f}_n)-(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h})}_E$.
-
-The adjoint problem corresponding to Lemma~\ref{lemma_stream} in Section~\ref{sec:strategy3} is likewise reduced in 1D to the scalar equation
-\begin{align}
-\epsilon v_1'' + \beta v_1' &= -g \label{adjoint_1D}
-\end{align}
-with $v_1\in H^1_0\left((0,1)\right)$.  After multiplying this equation by $\beta v_1'$ and integrate by parts over $\Oh$, we can apply Young's inequality to get
-%\[
-%\int_0^1 \epsilon v_1'' \beta v_1' + \|\beta v_1'\|_{L^2}^2 = -\int_0^1 g \beta v_1'.\
-%]
-%Integrating by parts and Young's inequality gives
-\begin{align*}
-\left.\frac{\epsilon}{2} \beta v_1'^2\right|_0^1 + \|\beta v_1'\|_{L^2}^2 &\leq \frac{1}{2}\|g\|^2 + \frac{1}{2}\|\beta v_1'\|^2,
-\end{align*}
-implying that
-\begin{align*}
-\|\beta v_1'\|_{L^2}^2 & \lesssim \|g\|^2 + {\beta \epsilon} v_1'(0)^2.
-\end{align*}
-Let us restrict ourselves to the cases where $v_1$ is sufficiently smooth for $v'(0)$ to be well defined.
-Taking $g=1$ (corresponding to a piecewise constant approximation) we can solve \eqref{adjoint_1D} exactly.
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.5]{figs/testBoundary1D.png}
-\caption{$v_1(x) = \frac{e^{-\frac{x}{\epsilon}}}{e^{\frac{1}{\epsilon}}-1}\left(e^{\frac{1}{\epsilon}}\left(e^{\frac{x}{\epsilon}}-1\right) + \left(e^{\frac{1}{\epsilon}}-1\right)e^{\frac{x}{\epsilon}}x\right)$, the solution to the adjoint equation for $f=0$ and constant $\beta$ and load $g$ for $\epsilon = .01$.}
-\label{fig:testBoundary1D}
-\end{figure}
-The solution $v_1$ is plotted in Figure~\ref{fig:testBoundary1D}, where we can see that $v_1(x)$ develops strong boundary layers of width $\epsilon$ near the inflow boundary $x=0$.
-Consequently, $\frac{\epsilon}{2} v_1'(0)^2 \approx \epsilon^{-1}$.
-Thus, we cannot conclude $\|\beta v'\| \lesssim \|g\|$ when $g$ is a constant,\footnote{Unlike the case of Dirichlet boundary conditions, the inflow condition on $ \widehat{f}_n = u(0)-\epsilon u'(0)$ induces an adjoint boundary condition $\tau(0)=0$, or equivalently $v'(0) = 0$, removing the non-robust term from the estimate.} and as a consequence cannot conclude that the robust error bound $\|u-u_h\|_{L^2} \lesssim \|(u,\sigma,\widehat{u},\widehat{f}_n)-(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h})\|_E$ holds for the solution $u_h$.
-More detailed 1D error bounds for Dirichlet boundary conditions are provided in \cite{DPG3}, and indicate the same lack of robustness under the test norm derived in this paper.\footnote{Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
-\[
-\|\left(\tau, v\right)\|_{V,w}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\|_{w+\epsilon} + \| \div \tau\|_{w+\epsilon} + \frac{1}{\epsilon}\|\tau\|_{w+\epsilon}
-\]
-where $\|\cdot \|_{w+\epsilon}$ is a weighted $L^2$ norm, where the weight $w \in (0,1)$ is required to vanish on $\Gamma_-$ and satisfy $\grad w = O(1)$.
-The need for this weight is necessary to account for the loss of robustness at the inflow.}
-
-\begin{figure}[h!]
-\centering
-\subfigure[Primal problem, Dirichlet inflow BC]{\includegraphics[scale=.3]{figs/primalDir.png}}
-\subfigure[Adjoint problem, Dirichlet inflow BC]{\includegraphics[scale=.3]{figs/adjointDir.png}}
-\subfigure[Primal problem, new inflow BC]{\includegraphics[scale=.3]{figs/primal.png}}
-\subfigure[Adjoint problem, new inflow BC]{\includegraphics[scale=.3]{figs/adjoint.png}}
-\caption{Comparison of primal and adjoint problems under both the standard Dirichlet and the new inflow boundary condition.
-The outflow boundary for each problem is denoted in red.
-For the standard Dirichlet inflow condition, the solution to the adjoint problem can develop strong boundary layers at the outflow of the adjoint problem.
-Notice, under the new inflow conditions, the relaxation of a wall-stop boundary condition with a zero-stress condition at the outflow boundary of the adjoint problem.}
-\end{figure}
-
-In higher dimensions, the adjoint problem is of the same form as the primal problem with the direction of convection reversed.
-However, the primal problem determines adjoint boundary conditions on $\Gamma_-$ and $\Gamma_+$.
-Thus, wheareas for the primal problem, data is convected from the inflow to the outflow, in the adjoint problem, data is convected from the outflow to the inflow boundary instead.
-
-We can intuitively explain the loss of robustness under our derived test norm by the presence of the Dirichlet boundary condition on $v$ at the inflow boundary.
-Since the direction of convection is reversed in the adjoint equation, we can interpret the adjoint as representing the convection of a concentration $v$ from the outflow to the inflow boundary.
-In the presence of a Dirichlet boundary condition at the inflow, $v$ can develop strong boundary layers at the inflow.
-As a consequence, the quantities $\|\beta\cdot \grad v\|$ and $\sqrt{\epsilon}\|\grad v\|$ are no longer robustly bounded by $\|f\|$ and $\|g\|$, and we can no longer derive robust bounds on the error $\|u-u_h\|_{L^2}$ by the error in the energy norm.
-
-Recall our strategy for analysis was to decompose of $(v,\tau)$ into continuous and discontinuous portions.
-Mathematically speaking, the use of Dirichlet boundary conditions on the primal problem introduces strong boundary layers into the solution $v$ of the adjoint equation --- in other words, boundary layers are introduced into the continuous portions of our decomposition of $(v,\tau)$.\footnote{The boundary conditions do not introduce boundary layers into the actual computed test functions.
-However, an interesting phenomenon observed is that, for small $\epsilon$, a lack of robustness can manifest itself during numerical experiments as additional refinements near the inflow boundary, precisely where the continuous parts of the decomposition of $(v,\tau)$ develop boundary layers.} The new inflow boundary condition on the primal problem relaxes the wall boundary condition induced on the adjoint/dual problem with a boundary condition that does not generate boundary layers, resulting in stronger stability estimates for the adjoint, and a better result for the primal problem.
-
-%\begin{figure}[h]
-%\centering
-%\subfigure[Primal problem]{\includegraphics[scale=.3]{figs/primal.png}}
-%\subfigure[Adjoint problem]{\includegraphics[scale=.3]{figs/adjoint.png}}
-%\caption{Comparison of primal and adjoint problems for convection-diffusion under the standard Dirichlet outflow boundary condition and the new inflow boundary condition.
-Notice the replacement of a wall-stop boundary condition with a Neumann stress boundary condition at the outflow boundary of the adjoint problem.
-}
-%\end{figure}
-
-\section{Numerical experiments}
-\label{sec:num_exp}
-
-In each numerical experiment, we vary $\epsilon = .01, .001, .0001$ in order to demonstrate robustness over a range of $\epsilon$.
-This is intended to mirror the experience with roundoff effects in numerical experiments \cite{DPGrobustness}; for ``worst-case" linear solvers, such as LU decomposition without pivoting, the effect of roundoff error becomes evident in the solving of optimal test functions for $\epsilon \leq O(1e-5)$.
-The roundoff itself comes from the conditioning of the Gram matrix under certain test norms; for example, if the weighted $H({\rm div};\Omega)\times H^1(\Omega)$ norm is used for the test norm $\|\left(\tau,v\right)\|_V$ (as was done in \cite{DPG2}), for an element of size $h$, $\|v\|_{L^2}^2 = O(h)$, while $\|\grad v\|_{L^2}^2 = O(h^{-1})$.
-As $h\rightarrow 0$, the seminorm portion of the test norm dominates the Gram matrix, leading to a near-singular and ill-conditioned system.
-
-The effect of roundoff error is often characterized by an increase in the energy error, which (assuming negligible error in the approximation of test functions) is proven to decrease for any series of refined meshes.
-These roundoff effects are dependent primarily on the mesh, appearing when trying to fully resolve very thin boundary layers by introducing elements of size $\epsilon$ through adaptivity.
-The effects of roundoff error were successfully treated in \cite{DPG3} by dynamically rescaling the test norms based on element size, a practical remedy not covered yet by the present analysis.
-
-\subsection{Eriksson-Johnson model problem}
-
-To confirm our theoretical results, we adopt a modification of a problem first proposed by Eriksson and Johnson in \cite{Eriksson1993}.
-For the choice of $\Omega = (0,1)^2$, $f=0$, and $\beta = (1,0)^T$, the convection diffusion equation reduces to
-\[
-\pd{u}{x} - \epsilon \left(\pdd{u}{x}+ \pdd{u}{y}\right) = 0,
-\]
-which has an exact solution by separation of variables, allowing us to analyze convergence of DPG for a wide range of $\epsilon$.
-For boundary conditions, we impose $u=0$ on $\Gamma_+$ and $\beta_n u - \sigma_n$ on $\Gamma_-$, which reduces to
-\begin{align*}
-u-\sigma_x &= u_0-\sigma_{x,0}, \quad x=0,\\
-\sigma_y &=  0, \quad y=0,1,\\
-u &= 0, \quad x=1.\\
-\end{align*}
-In this case, our exact solution is the series
-\[
-u(x,y) = C_0 + \sum_{n=1}^\infty C_n \frac{\exp(r_2(x-1)-\exp(r_1(x-1)))}{r_1\exp(-r2) - r_2\exp(-r1)}\cos(n\pi y),
-\]
-where
-\begin{align*}
-r_{1,2} &= \frac{1 \pm \sqrt{1 + 4 \epsilon\lambda_n}}{2 \epsilon},\\
-\lambda_n &= n^2\pi^2 \epsilon.
-\end{align*}
-The constants $C_n$ depend on a given inflow condition $u_0$ at $x=0$ via the formula
-\[
-C_n = \int_0^1 u_0(y) \cos(n\pi y).
-\]
-
-All computations have been done using the adaptive DPG code Camellia, built on the Sandia toolbox Trilinos \cite{Camellia}.
-
-\subsubsection{Solution with $C_1 = 1, C_{n\neq 1} = 0$}
-
-We begin with the solution taken to be the first non-constant term of the above series.
-We set the inflow boundary condition to be exactly the value of $u-\sigma_x$ corresponding to the exact solution.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.37]{figs/wallBC_exact_u.png}
-}
-\subfigure{
-\includegraphics[scale=.37]{figs/wallBC_exact_sigx.png}
-}
-\subfigure{
-\includegraphics[scale=.37]{figs/wallBC_exact_sigy.png}
-}
-\caption{Solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
-\end{figure}
-In each case, we begin with a square 4 by 4 mesh of quadrilateral elements with order $p=3$.
-We choose $\Delta p = 5$, though we note that the behavior of DPG is nearly identical for any $\Delta p \leq 3$, and qualitatively the same for $\Delta p = 2$.
-$h$-refinements are executed using a greedy refinement algorithm, where element energy error $e_K^2$ is computed for all elements $K$, and elements such that $e_K^2 \leq \alpha \max_K e_K^2$ are refined.
-We make the arbitrary choice of taking $\alpha = .2$ for each of these experiments.
-
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=.4]{figs/u_pointdiff_wallBC.png}
-\caption{Adapted mesh and pointwise error for $\epsilon=.01$}
-\end{figure}
-We are especially interested in the ratio of energy error and total $L^2$ error in both $\sigma$ and $u$, which we denote as $\|u-u_h\|_{L^2}$.
-The bounds on $\nor{\cdot}_E$ presented in Section~\ref{sec:main_bounds} imply that, using the above test norm, $\|u-u_h\|_{L^2} / \|u-u_h\|_E \leq C$ independent of $\epsilon$.
-Figure~\ref{ratios_simple}, which plots the ratio of $L^2$ to energy error, seems to imply that (at least for this model problem) $C=O(1)$.
-Additionally, while we do not have a robust lower bound ($\|u-u_h\|_{L^2} / \|u-u_h\|_E$ can approach $0$ as $\epsilon \rightarrow 0$), our numerical results appear to indicate the existence of an $\epsilon$-independent lower bound.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{figs/errorrates_wallBC.png}
-}
-\subfigure{
-\includegraphics[scale=.38]{figs/L2energyratio_wallBC.png}
-}
-\caption{$L^2$ and energy errors, and their ratio for $\epsilon=.01$, $\epsilon=.001$, $\epsilon=.0001$}
-\label{ratios_simple}
-\end{figure}
-The effect of a mesh dependent scalings on the $\|v\|^2$ and $\|\tau\|^2$ terms in the test norm can be seen in the ratios of $L^2$ to energy error; as the mesh is refined, the constants in front of the $L^2$ terms for $v$ and $\tau$ converge to stationary values (providing the full robustness implied by our adjoint energy estimates), and the ratio of $L^2$ to energy error transitions from a smaller to a larger value.
-The transition point happens later for smaller $\epsilon$, which we expect, since the transition of the ratio corresponds to the introduction of elements whose size is of order $\epsilon$ through mesh refinement.
-
-We examined how small $\epsilon$ needed to be in order to encounter roundoff effects as well.
-In \cite{DPGrobustness}, the smallest resolvable $\epsilon$ using only double precision arithmetic was $1e-4$.
-The solution of optimal test functions is now done using both pivoting and equilibration, improving conditioning.
-Roundoff effects still appear, but at smaller values of $\epsilon$.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{figs/roundoff_rates.png}
-}
-\subfigure{
-\includegraphics[scale=.38]{figs/roundoff_ratio.png}
-}
-\caption{Energy error and $L^2$/energy error ratio for $\epsilon=1e-5$, $\epsilon=1e-6$, $\epsilon=1e-7$.
-Non-monotonic behavior of the energy error indicates conditioning issues and roundoff effects.}
-\label{roundoff_figures}
-\end{figure}
-
-Without anisotropic refinements, it still becomes computationally difficult to fully resolve the solution for $\epsilon$ smaller than $1e-5$.
-Regardless, for all ranges of $\epsilon$, DPG does not lose robustness, as indicated by the rates and ratio between $L^2$ and energy error in Figure~\ref{roundoff_figures} remaining bounded from both above and below.
-For $\epsilon = 1e-5$, we observe that the ratio of $L^2$ error increases, corresponding to the scaling of the test norm with mesh size (the transition in test norm occurs after 8 refinements, which, for an initial $4\times 4$ mesh, implies a minimum element size of about $1.5e-05$.
-At this point, rescaled test norm allows us to take advantage of the full magnitude of the $L^2$ term for $\|v\|$ and $\|\tau\|$ implied by our adjoint estimates).
-By analogy, for smaller $\epsilon = 1e-6, 1e-7$, the transition period should begin near the 10th and 11th refinement iterations; however, we do not observe such behavior, possibly due to roundoff effects.
-For $\epsilon=1e-6$, the ratio simply remains constant, but for $\epsilon=1e-7$, we observe definite roundoff effects, as the energy error increases at the 11th refinement.
-Since DPG is optimal in the energy norm for a mesh-independent test norm\footnote{While the test norm changes with the mesh, it increases monotonically.
-A strictly stronger test norm implies $\frac{b(u,v)}{\|v\|_1} \geq \frac{b(u,v)}{\|v\|_2}$ for any $\|v\|_1 \leq \|v\|_2$}, we expect monotonic decrease of the energy error with mesh refinement.
-Non-monotonic behavior indicates either approximation or roundoff error, and as we observed no qualitative difference between using $\Delta p = 5$ and $\Delta p = 6$ for these experiments, we expect that the approximation error is negligible and conclude roundoff effects are at play when these phenomena are observed.
-
-It is worth noting that for $\epsilon \leq 1e-5$, we do not perform enough refinements to completely resolve the boundary layer, so $|K| \geq \epsilon$ for all $K\in \Oh$.
-Thus, any roundoff effects observed are not due to the conditioning issues associated with the differing scales of the $\nor{v}_{L^2(K)}$ and $\nor{\grad v}_{L^2(K)}$ terms discussed previously.
-
-\subsubsection{Neglecting $\sigma_n$}
-
-In practice, we will not have prior knowledge of $\sigma_n$ at the inflow, and will have to set $\beta_n u - \sigma_n = u_0$, ignoring the viscous contribution to the boundary condition.
-The hope is that for small $\epsilon$, this omission will be negligible.
-Figure~\ref{ratios_noSigma} indicates that, between $\epsilon = .005$ and $\epsilon = .001$, the omission of $\sigma_n$ in the boundary condition becomes negligible, and both our error rates and ratios of $L^2$ to energy error become identical to the case where $\sigma_n$ is explicitly accounted for in the inflow condition.
-For large $\epsilon = .01$, the $L^2$ error stagnates around $1e-3$, or about $7\%$ relative error.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{figs/rates_noSigma.png}
-}
-\subfigure{
-\includegraphics[scale=.38]{figs/ratio_noSigma.png}
-}
-\caption{$L^2$ and energy errors and their ratio when neglecting $\sigma_n$ at the inflow.}
-\label{ratios_noSigma}
-\end{figure}
-
-\subsubsection{Discontinuous inflow data}
-
-We note also that an additional advantage of selecting this new boundary condition is a relaxation of regularity requirements: as $\widehat{f}_n \in H^{-1/2}(\Gh)$, strictly discontinuous inflow boundary conditions are no longer ``variational crimes".
-We consider the discontinuous inflow condition
-\[
-u_0(y) = \begin{cases}
-(y-1)^2, \quad &y>.5\\
--y^2, \quad &y\leq .5 
-\end{cases}
-\]
-as an example of a more difficult test case.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{figs/disc_hat.png}
-}
-\subfigure{
-\includegraphics[scale=.38]{figs/disc_hat_surf.png}
-}
-\caption{Solution variables $u$ and $\widehat{u}$ with discontinuous inflow data $u_0$ for $\epsilon = .01$.}
-\label{disc_sol}
-\end{figure}
-Figure~\ref{disc_sol} shows the solution $u$ and overlaid trace variable $\widehat{u}$, which both demonstrate the regularizing effect of viscosity on the discontinuous boundary condition at $x=0$.
-However, we do not have a closed-form solution with which to compare results for a stricly discontinuous $u_0$.
-In order to analyze convergence, we approximate $u_0$ with 20 terms of a Fourier series, giving a near-discontinuity for $u_0$.
-
-\begin{figure}[h!]
-\centering
-\subfigure{
-\includegraphics[scale=.38]{figs/rates_disc.png}
-}
-\subfigure{
-\includegraphics[scale=.38]{figs/ratio_disc.png}
-}
-\caption{$L^2$ and energy errors, and their ratio for $\epsilon=.01$, $\epsilon=.001$, $\epsilon=.0001$, with discontinuous $u_0$ approximated by a Fourier expansion. }
-\label{disc_sol_fourier}
-\end{figure}
-
-The ratios of $L^2$ to energy error are now less predictable than for the previous example, in part due to the difficulty in approximating highly oscillatory boundary conditions.
-The numerical experiments were originally performed by applying boundary conditions via interpolation; the result was that the highly oscillatory inflow boundary condition was not sampled enough to be properly resolved, causing the solution to converge to a solution different than the exact solution.
-The experiments were repeated using the penalty method to enforce inflow conditions; however, we note that the proper way to do so is to use an $L^2$ projection at the boundary.
-Even when using the penalty method, however, the ratios still remain bounded and close to $1$ for $\epsilon$ varying over two orders of magnitude, as predicted by theory.
-
-\section{Conclusions}
-
-We have presented in this paper the analysis of a non-canonical test norm and its corresponding DPG energy norm for the convection-diffusion equation in the small-diffusion limit.
-Additionally, we have introduced a non-standard inflow boundary condition, and have explored the difference between between this and the standard Dirichlet inflow boundary condition.
-
-Numerical results are presented in order to verify the results derived in this paper.
-However, at least for our model problem, numerical experiments appear to demonstrate results that are stronger than our proofs indicate, delivering solutions for $u$ and $\sigma$ that are extremely close to their best $L^2$ projections.
-
-The theory presented in this paper have been successfully extrapolated to nonlinear singular perturbation problems and systems of equations, and has been applied in context of the Burgers and Navier-Stokes equations.
-These results will be presented in an upcoming paper.
-
-\section{Acknowledgements}
-
-The authors would like to acknowledge the help of Nathan Roberts with software development and Dr Robert Moser for fruitful discussions and perspective.
-Chan and Demkowicz were supported by the Department of Energy [National Nuclear Security Administration] under Award Number [DE-FC52-08NA28615].
-Heuer was supported through the project "Fondecyt-Chile 1110324" and by the "J Tinsley Oden Faculty Research Fellowship" of the Institute of Computational Engineering and Sciences (ICES).
-
-%None yet.  Ideas:
-%\begin{itemize}
-%\item Explanation of choice of boundary condition and why it impacts stability
-%\item Interpretation of weight as allowing diffusion to work on the boundary.  
-%\item Note results have worked for Burgers, and mention the extension to Navier-Stokes
-%\end{itemize}
-
-\bibliographystyle{plain}
-\bibliography{paper}
-
-\input{paper_appendix.tex}
-
+\end{letter}
 \end{document}

### 2013-07-30 docs/Jesse/NavierStokes paper/DPGtheory.tex

\section{DPG as a minimum-residual method}
\seclab{optimalTest}

%Petrov-Galerkin methods, in which the test space differs from the trial space, have been explored for over 30 years, beginning with the approximate symmetrization method of Barrett and Morton~\cite{BARRETT01101981}. The idea was continued with the SUPG method of Hughes, and the characteristic Petrov-Galerkin approach of Demkowicz and Oden~\cite{Demkowicz1986188}, which introduced the idea of tailoring the test space to change the norm in which a finite element method would converge.
%The idea of optimal test functions was introduced by Demkowicz and Gopalakrishnan in \cite{DPG2}.  Conceptually, these optimal test functions are the natural result of the minimization of a residual corresponding to the operator form of a variational equation. The connection between stabilization and least squares/minimum residual
%methods has been observed previously \cite{GLS}. However, the method in \cite{DPG2} distinguishes itself by measuring the residual of the natural \textit{operator form of the equation}, posed in the dual space and measured with the dual norm.

Our starting point is the minimization of some measure of error over a finite-dimensional space, given an abstract variational formulation 
\begin{equation}
\eqnlab{variationEq}
\left\{
  \begin{array}{l}
    \text{Given } l \in V^*, \text{ find } u \in U  \text{ such that} \\ 
    b(u,v) = l(v), \quad \forall v\in V,
  \end{array}
  \right.
\end{equation}
where $b\LRp{\cdot,\cdot}: U \times V \to \mbb{R}$ is a continuous bilinear form.  Throughout the paper, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U^*$ and $V^*$ as the respective topological dual spaces.  Throughout the paper, we suppose the variational problem \eqnref{variationEq} to be well-posed in the inf-sup sense. We can then identify a unique operator $B:U\rightarrow V^*$ such that 
\[
\langle Bu,v\rangle_{V^* \times V} \coloneqq b(u,v), \quad u\in U, v\in V
\]
with $\LRa{\cdot, \cdot}_{V^*\times V}$ denoting the duality pairing between $V^*$ and $V$, to obtain the operator form of the our variational problem
\begin{equation}
\eqnlab{dualEq}
Bu = l \quad \text{in } V^*.
\end{equation}
We are interested in minimizing the residual over the discrete approximating subspace $U_h \subset U$
\[
u_h = \underset{u_h\in U_h}{\arg\min}\, J(u_h) \coloneqq \frac{1}{2}\|l-Bu_h\|_{V^*}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| l(v)- b(u_h,v)|^2}{\nor{v}_V^2}.
\]
For convenience in writing, we will abuse the notation $\sup_{v \in V}$ to denote $\sup_{v\in V\setminus\{0\}}$ for the remainder of the paper.  If we define the problem-dependent \textit{energy norm} 
\[
\nor{u}_E \coloneqq \nor{Bu}_{V^*},
\]
then we can equate the minimization of $J(u_h)$ with the minimization of error in $\nor{\cdot}_E$.

The first order optimality condition for minimization of the quadratic functional $J(u_h)$ requires the G\^ateaux derivative to be zero in all directions $\delta u \in U_h$,
\begin{align}
\left(l-Bu_h,B\delta u\right)_{V^*} = 0, \quad \forall \delta u \in U,
\label{orthog}
\end{align}
which is nothing more than the least-squares condition enforcing orthogonality of error with respect to the inner product on $V$.

The difficulty in working with the first-order optimality condition~\eqref{orthog} is that the inner product $\LRp{\cdot,\cdot}_{V^*}$ cannot be evaluated explicitly.  However, we have that 
\begin{align}
\left(l-Bu_h,B\delta u\right)_{V^*} = \left(R_V^{-1}(l-Bu_h),R_V^{-1}B\delta u\right)_{V},
\label{rieszOrthog}
\end{align}
where $R_V: V\rightarrow V^*$ is the Riesz map mapping elements of a Hilbert space $V$ to elements of the dual $V^*$ defined by
\[
\LRa{R_Vv,\delta v}_{V^*\times V} \coloneqq \LRp{v,\delta v}_V.
\]
Furthermore, the Riesz operator is an isometry, such that $J(u_h) = \frac{1}{2}\nor{l-Bu_h}^2_{V^*} = \frac{1}{2}\nor{R_V^{-1}(l-Bu_h)}^2_{V}$.  Thus, satisfaction of~\eqref{rieszOrthog} is exactly equivalent to satisfaction of the original optimality conditions~\eqref{orthog}.

\subsection{Optimal test functions}

%Throughout this dissertation, we assume that the trial space $U$ and test space $V$ are real Hilbert spaces, and denote $U'$ and $V'$ as the respective topological dual spaces. Let $U_h \subset U$ and $V_h\subset V$ be finite dimensional subsets. We are interested in the following problem  
%\begin{equation}
%\eqnlab{variationEq}
%\left\{
%  \begin{array}{l}
%    \text{Given } l \in V', \text{ find } u_h \in U_h  \text{ such that} \\ 
%    b(u_h,v_h) = l(v_h), \quad \forall v_h\in V_h,
%  \end{array}
%  \right.
%\end{equation}
%where $b\LRp{\cdot,\cdot}: U \times V \to \mbb{R}$ is a continuous
%bilinear form.  $U_h$ is chosen to be some trial space of approximating functions, but $V_h$ is as of yet unspecified. 
%
%Throughout the dissertation, we suppose the variational
%problem \eqnref{variationEq} to be well-posed. In that case, we can
%identify a unique operator $B:U\rightarrow V'$ such that
%\[
%\langle Bu,v\rangle_V \coloneqq b(u,v), \quad u\in U, v\in V
%\]
%with $\LRa{\cdot, \cdot}_V$ denoting the duality pairing between $V'$ and $V$, to obtain the operator form of the continuous variational problem
%\begin{equation}
%\eqnlab{dualEq}
%Bu = l \quad \text{in } V'.
%\end{equation}
%In other words, we can represent the continuous form of our variational equation
%\eqnref{variationEq} equivalently as the operator equation \eqnref{dualEq} with values in the
%dual space $V'$.  This motivates us to consider the conditions under which the solution to \eqnref{variationEq} is the solution to the minimum residual problem in $V'$ 
%\[
%u_h = \underset{u_h\in U_h}{\arg\min}\, J(u_h),
%\]
%where $J(w)$ is defined for $w\in U$ as 
%\[
%J(w) = \frac{1}{2}\|Bw-l\|_{V'}^2 \coloneqq\frac{1}{2} \sup_{v\in V\setminus\{0\}} \frac{| b(w,v)-l(v)|^2}{\nor{v}_V^2}.
%\]
%For convenience in writing, we will abuse the notation $\sup_{v \in V}$ to denote $\sup_{v\in V\setminus\{0\}}$ for the remainder of the dissertation.
%
%Let us define $R_V: V \to V'$ as the Riesz map, which identifies
%elements of $V$ with elements of $V'$ by 
%\[
%\langle R_V v,\delta
%v\rangle_V \coloneqq(v, \delta v)_V, \quad \forall \delta v \in V.
%\]
%Here, $(\cdot, \cdot)_V$ denotes the
%inner product in $V$. As $R_V$ and its inverse, $R_V^{-1}$, are both
%isometries, e.g.\ $\|f\|_{V'} = \|R_V^{-1} f\|_V, \forall f \in V'$, we
%have
%\begin{equation}
%\eqnlab{minimization}
%\min_{u_h\in U_h} J(u_h) = \frac{1}{2}\left\|Bu_h-l\right\|_{V'}^2 =  \frac{1}{2}\left\|R_V^{-1}(Bu_h-l)\right\|_V^2.
%\end{equation}
%The first order optimality condition for \eqnref{minimization} requires
%the G\^ateaux derivative to be zero in all directions $\delta u \in
%U_h$, i\.e\.,
%\begin{align*}
%\left(R_V^{-1}(Bu_h-l),R_V^{-1}B\delta u\right)_V = 0, \quad \forall \delta u \in U. 
%\end{align*}
We define, for a given trial function $\delta u \in U$, the corresponding {\em optimal test function} $v_{\delta u}$
\begin{equation}
\eqnlab{optv}
v_{\delta u} \coloneqq R_V^{-1}B\delta u \quad  \text{in } V.
\end{equation} 
By definition of the Riesz inverse, the optimality condition~(\ref{rieszOrthog}) becomes
\[
 \langle Bu_h-l, v_{\delta u}\rangle_V = 0, \quad \forall \delta u \in U
\]
which is exactly the standard variational equation in \eqnref{variationEq} with $v_{\delta u}$ as the test functions. By defining the optimal test space $V_{\rm opt} \coloneqq \{v_{\delta u} \text{ s.t. } \delta u\in U\}$, the solution of the discrete variational problem \eqnref{variationEq} with test space $V_h = V_{\rm opt}$ minimizes the residual in the dual norm $\nor{Bu_h-l}_{V'}$.

%Since $U_h \subset U$ is spanned by a finite number of basis functions $\LRc{\varphi_i}_{i=1}^N$, \eqnref{optv} allows us to compute (for each basis function) a corresponding optimal test function $v_{\varphi_i}$. The collection $\LRc{v_{\varphi_i}}_{i = 1}^N$ of optimal test functions then forms a basis for the optimal test space.  In order to express optimal test functions defined in \eqnref{optv} in a more familiar form, we take  $\delta u = \varphi$, a generic basis function in $U_h$, and rewrite \eqnref{optv} as
%\[
%R_Vv_{\varphi} = B\varphi, \quad \text{in } V',
%\]
%which is, by definition, equivalent to
%\[
%\LRp{v_\varphi,\delta v}_V = \LRa{R_Vv_\varphi,\delta v}_{V}=
%\LRa{B\varphi, \delta v}_V = b\LRp{\varphi,\delta v}, \quad
%\forall \delta v \in V.
%\]
The inversion of the Riesz operator required to determine optimal test functions is done through the solution of the auxiliary variational problem
\begin{equation}
\eqnlab{optvVar}
\left(v_{\delta u},\delta v\right)_V = b({\delta u},\delta v), \quad \forall \delta v \in V.
\end{equation}
In general, for conforming finite element methods, test functions are continuous over the entire domain, and hence solving variational problem \eqnref{optvVar} for each optimal test function is a global operation over the entire mesh, rendering the method impractical. The development of discontinous Galerkin (DG) methods allows us to avoid this by adopting basis functions which are discontinuous over elements. In particular, the use of discontinuous test functions $\delta v$ and a \textit{localizable} norm $\nor{v}_{V(\Oh)}^2 = \sum_{K\in\Oh} \nor{v}_{V(K)}^2$, (where $\nor{v}_{V(K)}$ is a norm over the element $K$), reduces the problem of determining global optimal test functions in \eqnref{optvVar} to local problems that can be solved in an element-by-element fashion.

We note that solving \eqnref{optvVar} on each element exactly is still impossible since it amounts to inverting the infinite-dimensional Riesz map $R_V$. Instead, optimal test functions are approximated using the standard Bubnov-Galerkin method on an ``enriched" subspace $\tilde{V} \subset V$ such that $\dim(\tilde{V}) > \dim(U_h)$ elementwise \cite{DPG1, DPG2}. We assume in this paper that the approximation error in optimal test functions is negligible, and refer to \cite{practicalDPG} for estimating the effects of approximation error on DPG.

Finally, the DPG method boasts several attractive properties: 
\begin{itemize}
\item DPG provides a symmetric positive-definite stiffness matrix. Let $\{\phi_j\}_{j=1}^m$ be a basis for $U_h$, and $\{v_i\}_{i=1}^n$ a basis for $V_h$, such that $n>m$. Then, for $B_{ji} = b(\phi_j,v_i)$ and $l_i = \ell(v_i)$, DPG solves the ``internally preconditioned'' algebraic least squares system for degrees of freedom $u$
\begin{align*}
\LRp{B^T R_V^{-1}B} u  &= \LRp{B^T R_V^{-1}} l,
\end{align*}
where, under a localizable norm and discontinuous test functions, $R_V^{-1}$ is block diagonal.
\item DPG delivers the best approximation error in the ``energy norm" \cite{Bui-ThanhDemkowiczGhattas11a, DPG2, DPG4} 
\begin{equation}
\eqnlab{optimalError}
\nor{u-u_h}_{E} = \inf_{w\in U_h} \nor{u-w}_{E},
\end{equation}
where the energy norm $\nor{u}_{E}$ is defined 
\begin{equation}
\eqnlab{energyNorm} \nor{u}_{E} \coloneqq \nor{Bu}_{V'} = \sup_{v\in V}\frac{b(u,v)}{\nor{v}_V}.
\end{equation}
\item DPG inherits the natural property of minimum-residual methods that the energy error can be determined without knowing the exact solution --  $\|u-u_h\|_{U,E}  = \nor{Bu - Bu_h}_{V'} = \nor{R_V^{-1}\LRp{l-Bu_h}}_{V}$ shows that the energy error is simply the residual measured in a specific norm.  The energy error for DPG can be determined by computing the \textit{error representation function} $e \coloneqq R_V^{-1}\LRp{l-Bu_h}$ through
\[
\left(e,\delta v\right)_V = b(u-u_h,\delta v) = l\LRp{\delta v} - b(u_h,\delta v)
\]
and measuring $\|e\|_V$.  %This is simply a consequence of the least-squares nature of DPG; the energy error is simply the norm of the residual in $V'$.  
We can compute the squared norm over the domain $\nor{e}_{V(\Oh)}^2$ as the sum of element contributions $\sum_{K\in \Oh} \nor{e}_{V(K)}^2$, and we define $e_K^2 \coloneqq \nor{e}_{V(K)}^2$ as a local error indicator with which we can drive adaptive mesh refinement.  
\end{itemize}

\subsection{The ultra-weak variational formulation}
\seclab{abstractUweak}

We note that the above theory holds for any variational formulation that allows for discontinuous test functions.  Though alternative discretizations have been successful \cite{primalDPG}, we focus primarily on the ultra-weak variational formulation.

The ultra-weak variational formulation begins with a first order system $Au = f$.  After multiplying by a test function $v$, we integrate all equations by parts, such that over one element, we have
\[
\LRp{Au,v}_{L^2(K)} = \LRp{u,A_h^*v}_{L^2(K)} + \LRa{\uh,v}_{\partial K}.
\]
$A_h^*v$ is the broken formal adjoint, which corresponds to the adjoint operator acting element-wise on $v$.  In traditional DG methods, the numerical flux $\uh$ is constructed as some function of solution values on elements adjacent to $\partial K$.  Under the ultra-weak formulation, these numerical fluxes are identified as additional unknowns, akin to hybridized discontinuous Galerkin (HDG) methods \cite{hybridDG}.\footnote{While the boundary term resulting from integration by parts of a gradient (the numerical trace), is typically identified as an additional unknown, the boundary term resulting from integration by parts of a divergence (the numerical flux) is not, and is approximated using a DG flux.  The ultra-weak variational formulation identifies both as independent unknowns.}

We define the mesh $\Oh$ as the partitioning of $\Omega$ into non-overlapping elements $K_j, j = 1,\hdots,\Nel$ through $\Oh = \cup_{j=1}^\Nel K_j$.  We define also the mesh ``skeleton" by $\Gh = \cup_{j=1}^\Nel \partial K_j$; the set of all element faces/edges. The ultra weak formulation is given as the sum of the independent element contributions in the mesh $\Oh$, which, under proper regularity assumptions, yields the bilinear form $b\LRp{\LRp{u,\uh},v}$ 
\[
b\LRp{\LRp{u,\uh},v} = \sum_{K\in \Oh} \LRp{u,A_h^*v}_{L^2(K)} + \LRa{\uh,v}_{\partial K} = \LRp{u,A^*_h v}_{\L} + \LRa{\uh,\jump{v}}_{\Gh},
\]
where $\jump{v}$ is the jump of $v$ across all edges that make up the skeleton $\Gh$.  We refer to \cite{analysisDPG, Bui-ThanhDemkowiczGhattas11b, stokesDPG} for a detailed discussion of the proper energy setting and spaces for each variable, as well as detailed analysis of well-posedness of the ultra-weak variational formulation for a large range of problems.

%The \cite{globalLocalDPG} for mortar/global test space connections.

%The naming of the discontinuous Petrov-Galerkin method refers to the fact that the method is a Petrov-Galerkin method, and that the test functions are specified to be discontinuous across element boundaries. There is no specification of the regularity of the trial space, and we stress that the idea of DPG is not inherently tied to a single variational formulation \cite{Bui-ThanhDemkowiczGhattas11a}. Additionally, Cohen, Dahmen and Welper simultaneously extended the minimum residual concept behind DPG to general variational settings and avoid the use of discontinuous test functions by formulating the minimum residual method as a saddle-point problem \cite{DahmenVariationalStabilization}.  
%
%In most of the DPG literature, however, the discontinuous Petrov-Galerkin method refers to the combination of the concept of locally computable optimal test functions introduced in Section \secref{optimalTest} with the so-called ``ultra-weak formulation" \cite{DPG1,DPG2,DPG3,DPG4,DPGElas,DBLP:journals/procedia/NiemiCC11}. Unlike the previous two sections in which we studied the general equation \eqnref{variationEq} given by abstract bilinear and linear forms, we now consider a concrete instance of \eqnref{variationEq} resulting from an ultra-weak formulation for an abstract first-order system of PDEs $Au = f$. Additionally, from this section onwards, we will refer to DPG as the pairing of the ultra-weak variational formulation with the concept of locally computable optimal test functions. 
%
%We begin by partitioning the domain of interest $\Omega$ into $\Nel$ non-overlapping elements $K_j, j = 1,\hdots,\Nel$ such that $\Oh = \cup_{j=1}^\Nel K_j$ and $\overline{\Omega} = \overline{\Omega}_h$. Here, $h$ is defined as $h= \max_{j\in \LRc{1,\hdots,\Nel}}\text{diam}\LRp{K_j}$.  We denote the mesh ``skeleton" by $\Gh = \cup_{j=1}^\Nel \partial K_j$; the set of all faces/edges $e$, each of which come with a normal vector ${n}_e$. The internal skeleton is then defined as $\Gamma^0_h = \Gh \setminus \partial \Omega$. If a face/edge $e \in \Gh$ is the intersection of $\partial K_i$ and $\partial K_j$, $i \ne j$, we define the following jumps:
%\[
%\jump{v} = \text{sgn} \LRp{{n}^-}v^- + \text{sgn} \LRp{{n}^+}v^+, \quad
%\jump{\tau \cdot n} = {n}^-\cdot \tau^- + {n}^+\cdot\tau^+,
%\]
%where
%\[
%\text{sgn}\LRp{{n}^{\pm}} =
%\left\{
%\begin{array}{ll}
%1 & \text{if } {n}^{\pm} = {n}_e \\
%-1 & \text{if } {n}^\pm = -{n}_e
%\end{array}
%\right..
%\]
%For $e$ belonging to the domain boundary $\partial \Omega$, we define
%\[
%\jump{v} = v, \quad
%\jump{\tau \cdot n} = {n}_e\cdot \tau.
%\]
%Note that we allow arbitrariness in assigning ``-'' and ``+'' quantities to the adjacent elements $K_i$ and $K_j$.
%%For the rest of the paper, we will use the same notation for both a function and its trace (if it is well-defined) when there is no ambiguity.
%
%The ultra-weak formulation for $Au = f$ on $\Oh$, ignoring boundary
%conditions for now, reads
%\begin{equation}
%\eqnlab{uweak}
%b\left(\left(u, \widehat{u}\right),v\right) \coloneqq \langle \widehat{u}, \jump{v}
%\rangle_{\Gh} - (u,A_h^*v)_{\Oh}= \LRp{f,v}_{\Oh},
%\end{equation}
%where we have denoted $\LRa{\cdot,\cdot}_{\Gh}$ as the duality
%pairing on $\Gh$, $\LRp{\cdot,\cdot}_{\Oh}$ the $L^2$-inner
%product over $\Oh$, and $A_h^*$ the formal adjoint resulting from
%element-wise integration by parts.  Occasionally, for simplicity in
%writing, we will ignore the subscripts in the duality pairing and
%$L^2$-inner product if they are $\Gh$ and $\Oh$. Both the
%inner product and formal adjoint are understood to be taken
%element-wise. Using the ultra-weak formulation, the regularity
%requirement on solution variable $u$ is relaxed, that is, $u$ is now
%square integrable for the ultra-weak formulation \eqnref{uweak} to be
%meaningful, instead of being (weakly) differentiable.  The trade-off
%is that $u$ does not admit a trace on $\Gh$ even though it did
%originally. Consequently, we need to introduce an additional new
%``trace'' variable $\widehat{u}$ in \eqnref{uweak}, that is defined only on
%$\Gh$.
%
%The energy setting is now clear; namely,
%\[
%u\in L^2\LRp{\Oh} \equiv L^2(\Omega), \quad v\in V=D(A^*_h), \quad
%\widehat{u}\in \gamma(D(A)),
%\]
%where $D(A_h^*)$ denotes the broken graph space corresponding to $A_h^*$,
%and $\gamma(D(A))$ the trace space (assumed to exist) of the graph space of
%operator $A$. The first discussion of the well-posedness of DPG with the ultra-weak formulation can be found in \cite{analysisDPG}, where the proof is presented for the Poisson and convection-diffusion equations. A more comprehensive discussion of the abstract setting for DPG with the ultra-weak formulation using the graph space, as well as a more general proof of well-posedness, can be consulted in \cite{Bui-ThanhDemkowiczGhattas11b}.

### 2013-07-30 docs/Jesse/NavierStokes paper/paperIntro.tex

--- 2013-07-22 docs/Jesse/Dissertation/proposalIntro.tex
@@
-\section{Motivations}
-
-Over the last three decades, Computational Fluid Dynamics (CFD) simulations have become commonplace as a tool in the engineering and design of high-speed aircraft.
-Wind tunnel experiments are often complemented by computational simulations, and CFD technologies have proved very useful in both the reduction of aircraft development cycles and the simulation of experimentally difficult conditions.
-Great advances have been made in the field since its introduction, especially in areas of meshing, computer architecture, and solution strategies.
-Despite this, there still exist many computational limitations in existing CFD methods:
-\begin{itemize}
-\item \textbf{Higher order methods :} Higher order methods stand to offer large computational savings through a more efficient use of discrete degrees of freedom.
-However, there are very few working higher-order CFD codes in existence, and most higher order methods tend to degrade to first-order accuracy near shocks.
-The use of higher order codes to solve the steady state equations is even rarer, where convergence of discrete nonlinear steady equations is a tricky issue \cite{BoeingHigherOrder}.
-\item \textbf{Automatic adaptivity :} The use of adaptive meshes is crucial to many CFD applications, where the solution can exhibit very localized sharp gradients and shocks.
-Good resolution for such problems under uniform meshes is computationally prohibitive and impractical for most physical regimes of interest.
-However, the construction of ``good" meshes is a difficult task, usually requiring a-priori knowledge of the form of the solution \cite{andersonCFDBook}.
-An alternative set of strategies are automatically adaptive schemes; such methods usually begin with a coarse mesh and refine based on the minimization of some error.
-However, this task is difficult, as the convergence of numerical methods for problems in CFD is notoriously sensitive to mesh quality.
-Additionally, the use of adaptivity becomes even more difficult in the context of higher order and $hp$ methods \cite{BoeingHigherOrder}.
-\end{itemize}
-Both of these issues are tied to the notion of \emph{robustness}.
-We define robustness loosely as the degradation of the quality of numerical solutions with respect to a given problem parameter.
-In the context of CFD simulations, the parameter of interest is the Reynolds number (the nondimensional equivalent of the inverse of the viscosity) --- for typical physical conditions of interest for the compressible Navier-Stokes equations, the Reynolds number is extremely high, on the order of 1e7, yielding solutions with two vastly different scales - inviscid phenomena at an $O(1)$ scale, and $O(1e-7)$ viscous phenomena.
-
-The full Navier-Stokes equations are not well understood in a mathematical sense --- in order to more clearly illustrate the issue of robustness for problems in CFD, we will study first the important model problem of convection-dominated diffusion.
-
-\subsection{Singular perturbation problems and robustness}
-
-%Historically, the Galerkin method has been very successfully applied to a broad range of problems in solid mechanics, for which the variational problems resulting from the PDE are symmetric and coercive (positive-definite).
-It is well known that the finite element method produces optimal or near-optimal results for such problems, with the finite element solution matching or coming close to the best approximation of the solution in the finite element space.
-However,
+\section{Introduction}
 
@@
 
-We will illustrate the issues associated with numerical methods for this equation using one dimensional examples.  In 1D, the convection-diffusion equation is
-\begin{align*}
-\beta u'-\epsilon u'' &= f.
-\end{align*}
-For Dirichlet boundary conditions $u(0)=u_0$ and $u(1)= u_1$, the solution can develop sharp boundary layers of width $\epsilon$ near the outflow boundary $x=1$.
-
-\begin{figure}[!h]
-\centering
-\includegraphics[scale=.5]{figs/GalerkinOscTight.png}
-\caption{Oscillations in the 1D finite element solution of the convection-diffusion equation for small diffusion \cite{GalerkinOsc}.
+%We will illustrate the issues associated with numerical methods for this equation using one dimensional examples.  In 1D, the convection-diffusion equation is
+%\begin{align*}
+%\beta u'-\epsilon u'' &= f.
+%\end{align*}
+%For Dirichlet boundary conditions $u(0)=u_0$ and $u(1)= u_1$, the solution 
+%can develop sharp boundary layers of width $\epsilon$ near the outflow boundary.
+%\begin{figure}[!h]
+%\centering
+%\includegraphics[width=2.5in]{figs/GalerkinOscTight.png}
+%\caption{Oscillations in the 1D finite element solution of the convection-diffusion equation for small diffusion \cite{GalerkinOsc}.
 Standard finite volume and finite difference methods exhibit similar behavior.}
-\label{fig:GalerkinOsc}
-\end{figure}
-We consider for now the Galerkin finite element method as applied to convection-dominated diffusion.
-Standard finite element methods (as well as standard finite volume and finite difference methods) perform poorly for the case of small $\epsilon$.
-The poor performance of the finite element method for this problem is reflected in the bound on the error in the finite element solution --- under the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}:
-\[
-\|u-u_h\|_\epsilon \leq C \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
-\]
-for $\|u\|_\epsilon^2 \coloneqq \|u\|_{L^2}^2 + \epsilon \|u'\|_{L^2}^2$, with $C$ independent of $\epsilon$. An alternative formulation of the above bound is 
-\[
-\|u-u_h\|_{H^1(0,1)} \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
-\]
-where $C(\epsilon)$ grows as $\epsilon\rightarrow 0$.
+%\label{fig:GalerkinOsc}
+%\end{figure}
+The standard finite element method applied to the convection-dominated diffusion problem can perform very poorly for the case of small $\epsilon$.\footnote{This is especially true in the presence of boundary layers in the solution \cite{roos2008robust}.}  This poor performance can be observed numerically -- as the singular perturbation parameter $\epsilon$ decreases, the finite element solution can diverge significantly from the best finite element approximation of the solution.
+%The poor performance of the finite element method for this problem is reflected in the bound on the error in the finite element solution --- under the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}:
+%\[
+%\|u-u_h\|_\epsilon \leq C \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
+%\]
+%for $\|u\|_\epsilon^2 \coloneqq \|u\|_{L^2}^2 + \epsilon \|u'\|_{L^2}^2$, with $C$ independent of $\epsilon$. An alternative formulation of the above bound is 
+%\[
+%\|u-u_h\|_{H^1(0,1)} \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
+%\]
+%where $C(\epsilon)$ grows as $\epsilon\rightarrow 0$.
 The dependence of the constant $C$ on $\epsilon$ is what we refer to as a \textit{loss of robustness} --- as the singular perturbation parameter $\epsilon$ decreases, our finite element error is bounded more and more loosely by the best approximation error.
 As a consequence, the finite element solution can diverge significantly from the best finite element approximation of the solution for very small values of $\epsilon$.
-For example, Figure~\ref{fig:GalerkinOsc} shows an example of how, on a coarse mesh, and for small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation with a boundary layer develops spurious oscillations everywhere in the domain, even where the best approximation error is small.
+For example, it is well known that, on a fixed coarse mesh and for small values of $\epsilon$ (or a large Peclet number, the ratio $h/\epsilon$), the Galerkin approximation of the solution to the convection-diffusion equation with a boundary layer develops spurious oscillations everywhere in the domain, even where the best approximation error is small.
 These oscillations grow in magnitude as $\epsilon \rightarrow 0$, eventually polluting the entire solution.\footnote{For nonlinear shock problems, the solution often exhibits sharp gradients or discontinuities, around which the solution would develop spurious Gibbs-type oscillations.
@@
 
-\section{Goal}
+Traditionally, instability/loss of robustness in finite element methods has been dealt with using residual-based stabilization techniques.
+Given some variational form, the problem is modified by adding to the bilinear form the strong form of the residual, weighted by a test function and scaled by a stabilization constant $\tau$.
+The most well-known example of this technique is the streamline-upwind Petrov-Galerkin (SUPG) method, which is a stabilized FE method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.
+SUPG stabilization not only removes the spurious oscillations from the finite element solution of the convection-diffusion equation, but delivers the best finite element approximation in the $H^1$ norm in 1D.
 
@@
 This requires that both the method and the refinement scheme to perform adequately on coarse meshes with high Peclet numbers -- in other words, that the adaptive method is robust in the diffusion parameter.
-We construct such a method in this work -- in particular, we present a method for which automatic adaptivity can be applied to problems in compressible flow, beginning with very coarse meshes which do not reflect additional knowledge about the problem.
-The goal of this dissertation will be to develop a mathematical theory demonstrating the robustness in $\epsilon$ of our method for singularly perturbed convection-diffusion problems, and to demonstrate its feasibility as a CFD solver by applying it to several benchmark problems.
-
-%We construct such a method in this paper as follows: we begin by deriving the DPG method for linear problems, then constructing a DPG method for the scalar convection-diffusion equation that is robust for very small viscosities.
+We construct such a method in this paper as follows: we begin by deriving the DPG method for linear problems, then constructing a DPG method for the scalar convection-diffusion equation that is robust for very small viscosities.
 Unlike common adaptive methods in computational fluid dynamics, which often refine based on physical features (such as high gradients in the solution), adaptivity under this method is driven by the minimization of a residual, which measures error accurately even for highly underresolved meshes.
@@
 Numerical experiments are given, demonstrating the robustness of the method and the effectiveness of automatic adaptivity for two model problems in viscous compressible flow.
-
-%From the perspective of the full Navier-Stokes equations, this loss of robustness is doubly problematic.
-Not only will any nonlinear solution suffer from similar non-physical oscillations, but nonlinear solvers themselves may fail to yield a solution due to such instabilities.
-A nonlinear solution is almost always computed by solving a series of linear problems whose solutions will converge to the nonlinear solution under appropriate assumptions, and the presence of such oscillations in each linear problem can cause the solution convergence to slow significantly or even diverge.
-%
-%Our aim is to develop a \emph{stable, higher order, automatically adaptive scheme} for the steady compressible laminar Navier-Stokes equations in transonic/supersonic regimes that is \emph{robust for very small viscosity}.
-In particular, we hope to present a method for which automatic adaptivity can be applied to problems in compressible flow, beginning with very coarse meshes which do not reflect additional knowledge about the problem.
-The goal of this dissertation will be to develop a mathematical theory demonstrating the robustness in $\epsilon$ of our method for singularly perturbed convection-diffusion problems, and to demonstrate its feasibility as a CFD solver by applying it to several benchmark problems.
-
-\section{Literature review}
-
-For the past half-century, problems in CFD have been solved using a multitude of methods, many of which are physically motivated, and thus applicable only to a small number of problems and geometries.
-We consider more general methods, whose framework is applicable to a larger set of problems; however, our specific focus will be on the problems of compressible aerodynamics involving small-scale viscous phenomena (i.e.\ boundary layers and, if present, shock waves).
-Broadly speaking, the most popular general methods include (in historical order) finite difference methods, finite volume methods, and finite element methods.
-
-\subsection{Finite difference and finite volume methods}
-
-For linear problems, finite difference (FD) methods approximate derivatives based on interpolation of pointwise values of a function.
-In the context of conservation laws, FD methods were popularized first by Lax, who introduced the concepts of the monotone scheme and numerical flux.
-For the conservation laws governing compressible aerodynamics, FD methods approximate the conservation law, using some numerical flux to reconstruct approximations to the derivative at a point.
-Finite volume (FV) methods are similar to finite difference methods, but approximate the integral version of a conservation law as opposed to the differential form.
-FD and FV have roughly the same computational cost/complexity; however, the advantage of FV methods over FD is that FV methods can be used on a much larger class of problems and geometries than FD methods, which require uniform or smooth structured meshes.
-
-Several ideas were introduced to deal with oscillations in the solution near a sharp gradient or shock: artificial diffusion, total variation diminishing (TVD) schemes, and slope limiters.
-However, each method had its drawback, either in terms of loss of accuracy, dimensional limitations, or problem-specific parameters to be tuned \cite{Shu:Lectures}.
-Harten, Enquist, Osher and Chakravarthy introduced the essentially non-oscillatory (ENO) scheme in 1987 \cite{ENO}, which was improved upon with the weighted essentially non-oscillatory (WENO) scheme in \cite{WENO}.
-WENO remains a popular choice today for both finite volume and finite difference schemes.
-Most of these methods can be interpreted as adding some specific artificial diffusion to the given numerical scheme, which vanishes as the mesh size $h\rightarrow 0$.
-%We refer to such schemes as \emph{modified equation} methods, as the exact solution no longer satisfies the discrete system due to the presence of additional artificial diffusion terms.
-
-Historically, finite volumes and finite difference methods have been the numerical discretizations of choice for CFD applications; the simplicity of implementation of the finite difference method allows for quick turnaround time, and the finite volume method is appealing due to its locally conservative nature and flexibility.
-More recently, the finite element (FE) method has gained popularity as a discretization method for CFD applications for its stability properties and rigorous mathematical foundations.
-Early pioneers of the finite element method for CFD included Zienkiewicz, Oden, Karniadakis, and Hughes \cite{ChungCFDBook}.
-
-\subsection{Stabilized finite element methods}
-
-The finite element/Galerkin method has been widely utilized in engineering to solve partial differential equations governing the behavior of physical phenomena in engineering problems.
-The method relates the solution of a partial differential equation (PDE) to the solution of a corresponding variational problem.
-The finite element method itself provides several advantages --- a framework for systematic mathematical analysis of the behavior of the method, weaker regularity constraints on the solution than implied by the strong form of the equations, and applicability to very general physical domains and geometries for arbitrary orders of approximation.
-
-Historically, the Galerkin method has been very successfully applied to a broad range of problems in solid mechanics, for which the variational problems resulting from the PDE are often symmetric and coercive (positive-definite).
-It is well known that the finite element method produces optimal or near-optimal results for such problems, with the finite element solution matching or coming close to the best approximation of the solution in the finite element space.
-However, standard Galerkin methods tend to perform poorly for singular perturbation problems, developing instabilities when the singular perturbation parameter is very small.
-
-Traditionally, instability/loss of robustness in finite element methods has been dealt with using residual-based stabilization techniques.
-Given some variational form, the problem is modified by adding to the bilinear form the strong form of the residual, weighted by a test function and scaled by a stabilization constant $\tau$.
-The most well-known example of this technique is the streamline-upwind Petrov-Galerkin (SUPG) method, which is a stabilized FE method for solving the convection-diffusion equation using piecewise linear continuous finite elements \cite{SUPG}.
-SUPG stabilization not only removes the spurious oscillations from the finite element solution of the convection-diffusion equation, but delivers the best finite element approximation in the $H^1$ norm in 1D.
-
-\subsubsection{SUPG}
-
-All Galerkin methods involve both trial (approximating) and test (weighting) functions.
-Standard Galerkin methods, where these trial and test functions are taken from the same space, are referred to as Bubnov-Galerkin methods.
-Petrov-Galerkin methods refer most often to methods where test and trial functions \emph{differ}, leading to differing test and trial spaces.\footnote{Hughes takes the more general definition of a Petrov-Galerkin method to be any Galerkin method other than a classical Bubnov-Galerkin method.}  The Streamline Upwind Petrov Galerkin (SUPG) method is a stabilization method for $H^1$-conforming finite elements, the idea of which was originally motivated by artificial diffusion techniques in finite differences.
-In particular, for the homogeneous 1D convection-diffusion equation, it is possible to recover, under a finite difference method, the exact solution at nodal points by adding an ``exact" artificial diffusion based on the mesh size $h$ and the magnitudes of the convection $\beta$ and the viscosity $\epsilon$.
-The idea of ``exact" artificial viscosity was adapted to finite elements not through the direct modification of the equations, but through the \emph{test} functions and weighting of the residual.
-\footnote{Finite element and Galerkin methods are often referred to as ``weighted residual" methods, since the starting point of both is to multiply the residual by a particular test, or weighting, function.
-Standard Bubnov-Galerkin methods simply choose these weighting functions to be the same as the the basis functions used to approximate the solution.
-}
-
-We will introduce the SUPG method at the abstract level for illustrative purposes only.
-Further details and perspectives on the SUPG method can be found in \cite{SUPG}, as well as in an upcoming book by Hughes.
-The convection-diffusion equation can be written as follows:
-\[
-Lu = \left(L_{\rm adv} + L_{\rm diff} \right) u = f,
-\]
-where $L_{\rm adv}u \coloneqq \div \left(\beta u\right)$ is the first order advective operator, and $L_{\rm diff}u \coloneqq \epsilon \Delta u$ is the second-order diffusive operator.
-Let us assume $u$ to be a linear combination of piecewise-linear basis functions $\phi_i, i = 0,\ldots,N$ (then, within each element, $L_{\rm diff} u = 0$).
-If $b(u,v)$ and $l(v)$ are the bilinear form and load for the standard Galerkin method (resulting from multiplying by a test function $v$ and integrating both convective and diffusion terms by parts), the SUPG method is then to solve $b_{\rm SUPG}(u,v) = l_{\rm SUPG}(v)$, where $b_{\rm SUPG}(u,v)$ and $l_{\rm SUPG}(v)$ are defined as
-\begin{align*}
-b_{\rm SUPG}(u,v) &= b(u,v)+ \sum_{K} \int_{K} \tau \LRp{L_{\rm adv} v} \LRp{L u - f} \\
-l_{\rm SUPG}(v) &= l(v) + \sum_{K} \int_{K} \tau \LRp{L_{\rm adv}v} f
-\end{align*}
-for where $\tau$ is the SUPG parameter.
-For uniform meshes in 1D, $\tau$ is chosen such that, for $f=0$, the matrix system resulting from SUPG is exactly equal to the finite difference system under ``exact" artificial diffusion.
-However, unlike exact artificial diffusion, for $f\neq 0$, the SUPG method still delivers optimal stabilization.
-In fact, the SUPG finite element solution in 1D is nothing less than the nodal interpolant and the best $H^1_0$ approximation of the exact solution, as seen in Figure~\ref{fig:SUPG}.
-
-\begin{figure}[!h]
-\centering
-\subfigure[SUPG and standard FEM solutions]{\includegraphics[scale=.475]{figs/SUPG.png}}
-\subfigure[SUPG test function]{\includegraphics[scale=.25]{figs/SUPGtest.png}}
-\caption{SUPG and standard Bubnov-Galerkin solutions to the 1D convection-dominated diffusion equation, and a modified SUPG test function (in black) corresponding to a linear basis ``hat" function (in red).
-The upwind portion of the element is emphasized, while the downwind portion is decreased.
-The magnitude of the discontinuity between the upwind and downwind portion is controlled by the intrinsic timescale parameter $\tau$.
-}
-\label{fig:SUPG}
-\end{figure}
-
-The idea of emphasizing the upwind portion of a test function is an older idea, introduced in 1977 by Zienkiewicz et al.\ in \cite{zienkUpwind}.
-However, the precise amount of upwinding,\footnote{Insufficient upwinding results in a method which still exhibits oscillations and instabilities, while excessive upwinding leads to an overly diffusive method.} as well as the connection to residual-based stabilization methods, were novel to SUPG.
-
-For appropriately chosen $\tau$, the method can be generalized for higher order elements as well.
-In higher dimensions, the SUPG solution is very close to, but no longer the $H^1_0$ best approximation for 2D and 3D problems \cite{HughesSangalliSUPG}.
-Since its inception, SUPG is and has been the most popular stabilization method of choice for convection-diffusion type problems, in both academic and industry applications.
-
-An important feature of SUPG and other residual-based stabilization techniques that separates it from modified equation methods is the idea of \textit{consistency} --- by adding stabilization terms based on the residual, the exact solution still satisfies the same variational problem (i.e.\ Galerkin orthogonality still holds with $b(u-u_h,v) = 0$ for all $v\in V$).
-This addition of residual-based stabilization can be interpreted as a modification of the test functions.
-For SUPG, the formulation can equivalently be written as
-\[
-b\LRp{u,\tilde{v}_{i}} = l\LRp{\tilde{v}_{i}}, \quad \forall i = 1,\ldots,N-1
-\]
-where the SUPG test function $\tilde{v}_{i}$ is defined elementwise as
-\[
-\tilde{v}_{i} = \phi_i(x) + \tau L_{\rm adv} \phi_i.  
-\]
-In other words, the test functions $\tilde{v}_{i}$ is a perturbation of the basis function $\phi_i$ by a scaled advective operator applied to $\phi_i$.
-For a linear $C^0$ basis function (the ``hat" function), this naturally leads to a bias in the upwind or streamline direction of the flow $\beta$, as seen in Figure~\ref{fig:SUPG}.
-
-An important connection can now be made --- stabilization can be achieved by changing the test space for a given problem.
-We will discuss in Section~\secref{optimalTest} approaching the idea of stabilization through the construction of \textit{optimal test functions} to achieve optimal approximation properties.
-
-\subsubsection{DG methods}
-
-Discontinuous Galerkin (DG) methods form a subclass of FEM; first introduced by Reed and Hill in \cite{Reed:73}.
-These methods were later analyzed Raviart et al \cite{DGRaviart} and later by Johnson et al \cite{DGJohnson}, who contributed a mathematical analysis of the original method of Reed and Hill, as well as by Cockburn and Shu \cite{CockburnShu:DG}, who solved the Euler equations by applying concept of Lax's numerical flux within the context of DG.
-
-Advantages of DG methods include the local conservation property, easily modified local orders of approximation, ease of adaptivity in both $h$ and $p$, and efficient parallelizability.
-Rather than having a continuous basis where the basis function support spans multiple element cells, DG opts instead for a discontinuous, piecewise polynomial basis, where, like FV schemes, a \emph{numerical flux} facilitates communication between neighboring elements (unlike FV methods, however, there is no need for a reconstruction step).
-
-The formal definition of the numerical flux (attributed to Peter Lax) on an element boundary is some function of the values on the edges of both the neighboring elements.
-An additional reason for the popularity of DG methods is that they can be interpreted as stabilized FE methods (and vice versa) through appropriate choices of this numerical flux \cite{Brezzi20063293}.
-We will illustrate this with the steady convection equation in 1D:
-\begin{align*}
-\pd{\left(\beta(x) u\right)}{x} = f, \quad u(0) &= u_0.
-\end{align*}
-The DG formulation is derived by multiplying by a test function $v$ with support only on a single element $K = [x_K,x_{K+1}]$ and integrating by parts.
-The boundary term is left alone, such that the local formulation is
-\[
-\left.\beta u v\right|_{x_K}^{x_{K+1}} + \int_K -\beta u \pd{v}{x} = \int_K f v,
-\]
-and the global formulation is recovered by summing up all element-wise local formulations.
-However, the boundary term in the local formulation is presently ill-defined, as both $u$ and $v$ are dual-valued over element boundaries.
-Consequently, we make the choice to define the values of $u$ on the boundary (the \emph{traces} of $u$) as
-\begin{align*}
-u(x_K) \coloneqq u(x_K^-), \quad u(x_{K+1}) \coloneqq u(x_{K+1}^-),
-\end{align*}
-where $u(x_K^-)$ is the value of $u$ at $x_K$ as seen from the left, and $u(x_K^+)$ the value as seen from the right. Similarly, the traces of $v$ are defined to be
-\begin{align*}
-v(x_K) \coloneqq v(x_K^+), \quad v(x_{K+1}) \coloneqq v(x_{K+1}^-),
-\end{align*}
-For $\beta$ positive, $v(x_K^+)$ is the \emph{upwind} value of $v(x_K)$, and we refer to DG under this specific choice of traces as upwind DG.
-This specific choice of $v(x_K)$ as the upwind value is crucial; similarly to SUPG, the upwind DG emphasizes the test function in the direction of convection and changes the way the residual is measured.
-As it turns out, the performance of DG for convection-type problems is closely tied to this upwinding --- choosing the value of $v(x_K)$ to be the downwind value $v(x_K^-)$ leads to an unstable method, while choosing $v(x_K)$ to be the average of the upwind and downwind values leads to a DG method with suboptimal stability properties, similar to an $H^1$-conforming continuous Galerkin approximation\cite{Brezzi20063293}.\footnote{For second-order convection-diffusion problems with small diffusion, the additional regularity imparted by choice of the DG numerical flux is often insufficient, and SUPG-type stabilization is also applied.}
-
-Another perspective on the use of the numerical flux in DG methods is that the selection of specific DG fluxes imparts \emph{additional regularity} where needed.
-For example, for the pure convection problem, the solution has a distributional derivative in the streamline direction, but is only $L^2$ in the crosswind direction.
-As a consequence of the regularity of the solution, the boundary trace of the solution is defined only in the direction of convection.
-The upwind DG method addresses the above issue by choosing the numerical flux to be the upwind flux; in this case, the DG numerical flux can be viewed as imparting additional regularity to the discrete solution than is implied by the continuous setting \cite{DPG1,DPG3}.
-
-\subsubsection{HDG}
-
-A more recent development in DG methods is the idea of \emph{hybridized} DG (HDG), introduced by Cockburn, Gopalakrishnan and Lazarov \cite{hybridDG}.
-The hybridized DG framework identifies degrees of freedom with support only on element edges, which can be interpreted as Lagrange multipliers enforcing weak continuity of the trial space.
-HDG methods treat numerical \emph{traces} and numerical \emph{fluxes} differently depending on the form of the boundary term resulting from integration by parts.
-The numerical trace (the result of integrating by parts the gradient) in HDG methods is chosen to be an unknown, while the numerical flux (the result of integrating by parts the divergence) is chosen to be an appropriate function of both function values on neighboring elements and the numerical trace.
-
-By a careful choice of the numerical flux, the global HDG formulation can be reduced to a single equation involving only the numerical trace degrees of freedom, referred to as the \emph{global} problem.
-Once the global problem is solved, interior degrees of freedom can be recovered in parallel through so-called \emph{local} problems \cite{HDGprojection}.
-
-HDG methods are an active topic of current research, since they address several criticisms of common DG methods (large number of globally coupled degrees of freedom, complicated/inefficient implementation procedures, suboptimal convergence of approximate fluxes).
-Note that HDG methods still fall under the category of stabilized methods --- stabilization techniques are employed through the choice of the HDG numerical flux, which involves some stabilization parameter $\tau$.
-
-\section{Scope}
-
-This dissertation will proceed in four main parts.
-We will begin by introducing the abstract Discontinuous Petrov-Galerkin (DPG) method as a minimum residual method for linear problems and highlighting some important properties of the method.
-Our next step will be to formulate and prove the robustness of a DPG method (with respect to $\epsilon$) for the model problem of convection-dominated diffusion.
-Finally, we will extend and apply the DPG method to singularly perturbed nonlinear problems in CFD, presenting results for the Burgers and compressible Navier-Stokes equations.

### 2013-11-04 docs/Truman/LocalConservation/paper/paper.tex
Updated paper with Hemker diffusion
Updated paper

@@
 Hilbert space for a well-posed variational problem $b(u,v)=l(v)$. In operator
-form this is $Bu=l$, where $B:U\rightarrow V'$. We seek to minimize the
+form this is $Bu=l$, where $B:U\rightarrow V'$ and $\LRa{Bu,v}=b(u,v)$. We seek to minimize the
 residual for the discrete space $U_h\subset U$:
@@
 Primal DPG\cite{PrimalDPG} method presents an alternative with
-continuous test functions). Thus, we seek field variables $u\in L^2(K)$ and
+continuous trial functions). Thus, we seek field variables $u\in L^2(K)$ and
 $\bsigma\in\mb{L^2}(K)$. Mathematically, this leaves their traces on element
@@
 &=\underbrace{\:(f,v)_K\genfrac{}{}{0pt}{}{}{}}_{l(\mathbf{v})} &\text{in }\Omega \\
-u&=0 &\text{on }\Gamma
+\hat u&=0 &\text{on }\Gamma
 \end{align}
@@
 b(\bs u_h,T(\delta\bs u_h))-\sum_K\lambda_K b(\bs u_h,(1_K,\bs0))
-&=(f,T(\delta\bs u_h)) & \forall\delta\bs u_h\in\bs U_h\\
-b(\bs u_h,(1_K,\bs0)) &=(f,(1_K,\bs0)) & \forall K\,,
+&=l(T(\delta\bs u_h)) & \forall\delta\bs u_h\in\bs U_h\\
+b(\bs u_h,(1_K,\bs0)) &=l((1_K,\bs0)) & \forall K\,,
 \end{array}
@@
 
-Since the trial-to-test operator selectively produces test functions in
-$H^1(\Omega_h)$ and $\bs H(\text{div},\Omega_h)$, denote the result
-$v_{\delta\bs u_h}$ when $T(\delta u_h)\in H^1(\Omega_h)$ and
-$\btau_{\delta\bs u_h}$ when $T(\delta u_h)\in \bs H(\text{div},\Omega_h)$.
 Then, putting \eqref{eq:conservativeSystem} into more concrete terms for
@@
 &=(f,\vdeltau) & \forall\delta\bs u_h\in\bs U_h\\
-\langle\hat t,(1_K,\bs0)\rangle &=(f,(1_K,\bs0)) & \forall K\,.
+\langle\hat t,(1_K,\bs0)\rangle &=(f,1_K) & \forall K\,.
 \end{array}
@@
 
-We can decompose the discrete flux space $\hat F_h$ into equilibriated fluxes
-(zero net flux over each element) and some algebraic complement:
-\begin{equation}
-\hat F_h=\hat F_h^e\oplus\hat F_h^{ne}\,,\quad\hat 
-F_h^{e}:=\{\hat t:\langle\hat t,(1_K,\bs0)\rangle=0\quad\forall K\}\,.
-\label{eq:decomposition}
-\end{equation}
-In theory, we could accomplish this by employing for fluxes in $\hat F_h^{e}$
-traces of curls, $\nabla\times\phi$, but we don't do this in practice.
-
-\textcolor{red}{
-In practice, we solve \eqref{eq:conservativeConfusionSystem} as a fully
-coupled system of equations, but for didactic purposes, we can examine it one
-piece at a time. If we restrict \eqref{eq:conservativeConfusionSystem}$_1$ to
-$\delta\hat t\in\hat F_h^{ne}$, the Lagrange multiplier term drops out and we
-are left with a system that we can solve for $u_h$, $\bsigma_h$, $\hat u_h$,
-and $\hat t_h^e\in\hat F^e_h$.
-}
-
-\textcolor{red}{
-Restricting ourselves to $\delta\hat t\in\hat
-F_h^{e}$ in \eqref{eq:conservativeConfusionSystem}$_1$, we obtain a system  of
-equations that can be solved for $u_h$, $\bsigma_h$, $\hat u$, and $\hat
-t\in\hat F_h^e$. The remaining fluxes, $\hat t\in\hat F_h^{ne}$ are determined
-from \eqref{eq:conservativeConfusionSystem}$_2$. Finally, testing with $\hat
-t\in\hat F_h^{ne}$ in \eqref{eq:conservativeConfusionSystem}$_1$, we obtain a
-system of equations that can be solved for Lagrange multipliers $\lambda_K$.
-}
-
-\subsection{\textcolor{red}{Proof of Convergence}}
-In the following discussion, we do not account for the error in approximating
-the optimal test functions because $\dots$ (Need explanation).
-We cannot directly use Brezzi's theorem, but we can reproduce his argument.
-First of all, variational formulation \eqref{eq:variationalFormulation} is
-equivalent to:
-
-Find $\bs u\in\bs U$ such that
-\begin{equation}
-b(\bs u,T(\delta\bs u))=(f,T(\delta\bs u))\quad\forall\bs v\in\bs V\,.
-\label{eq:bilinearForm}
-\end{equation}
-This is because the trial-to-test operator $T=R_V^{-1}B$ is an isomorphism.
-
-Restricting ourselves to $\delta\hat t_h\in\hat F_h^e$, and subtracting
-\eqref{eq:bilinearForm} from \eqref{eq:conservativeConfusionSystem}, we have
-the Galerkin orthogonality condition:
-\begin{align}
-\label{eq:galerkinOrthogonality}
-\frac{1}{\epsilon}(\bsigma_h-\bsigma,\taudeltau)
-&+(u_h-u,\nabla\cdot\taudeltau)
--\langle\hat u_h-\hat u,\taudeltau\cdot\bs n\rangle
-\nonumber\\
-&-(\bbeta(u_h-u)-(\bsigma_h-\bsigma),\nabla\vdeltau)
-+\langle\hat t_h-\hat t,\vdeltau\rangle
-\\
-&\hspace{25ex}\forall(\delta u_h,\delta\bsigma_h,\delta\hat u_h,\delta\hat t_h)
-\in U_h\times\bs S_h\times\hat U_h\times\hat F_h^e\,.
-\nonumber
-\end{align}
-
-We begin with an equivalent of Brezzi's \emph{discrete inf-sup in kernel
-condition}.
-\begin{lemma}
-\label{lemma:infsuplemma}
-The following condition holds:
-\begin{align}
-\sup_{\stackrel{
-(\delta u_h,\delta\bsigma_h,\delta\hat u,\delta\hat t)\in}
-{U_h\times\bs S_h\times\hat U_h\times\hat F_h^e}
-}
-\frac{\snorm{
-b((u_h,\bsigma_h,\hat u_h,\hat t_h), (\vdeltau,\taudeltau))
-% \frac{1}{\epsilon}(\bsigma_h,\taudeltau)
-% +(u_h,\nabla \cdot\taudeltau)
-% -\langle\hat u_h,\taudeltau\cdot\bs n\rangle
-% -(\bbeta u_h-\bsigma_h,\nabla\vdeltau)
-% +\langle\hat t_h,\vdeltau\rangle
-}}
-{\norm{(\vdeltau,\taudeltau)}}
-\ge\alpha\norm{(u_h,\bsigma_h,\hat u_h,\hat t_h)}\quad\nonumber\\
-\forall(u_h,\bsigma_h,\hat u_h,\hat t_h)
-\in U_h\times\bs S_h\times\hat U_h\times\hat F_h^e\,.
-\label{eq:infsup}
-\end{align}
-
-\end{lemma}
-\begin{proof}
-By the very construction of the trial-to-test operator, the supremum on the
-left is equal to
-\begin{equation}
-\norm{T(u_h,\bsigma_h,\hat u_h,\hat t_h)}_{V}
-=\norm{R_V^{-1}B(u_h,\bsigma_h,\hat u_h, \hat t_h)}_{V}
-=\norm{B(u_h,\bsigma_h,\hat u_h, \hat t_h)}_{V'}
-\label{eq:infsupproof}
-\end{equation}
-The condition follows now from the fact that operator $B$ is bounded below,
-i.e. bilinear form \linebreak$b((u_h,\bsigma_h,\hat u_h, \hat t_h),(v,\btau))$ satisfies
-the inf-sup condition.
-\end{proof}
-
-Assume additionally that flux decomposition \eqref{eq:decomposition} is
-orthogonal. We begin by decomposing $\hat t_h$,
-\begin{equation}
-\hat t_h=\hat t_h^{e}+\hat t_h^{ne}\,.
-\label{eq:fluxdecomposition}
-\end{equation}
-Next, we use the triangle inequality,
-\begin{align}
-\label{eq:triangle}
-\norm{(u-u_h,\bsigma-\bsigma_h,\hat u-\hat u_h, \hat t-\hat t_h)}&=
-\norm{(u-u_h,\bsigma-\bsigma_h,\hat u-\hat u_h, \hat t-(\hat t_h^e+\hat t_h^{ne}))}\nonumber\\
-&\le\norm{(u-w_h,\bsigma-\bs s_h,\hat u-\hat w_h, \hat t-(\hat r_h^e+\hat t_h^{ne}))}\\
-&\hspace{3ex}+\norm{(w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h, \hat r_h^e-\hat t_h^e)}\nonumber
-\end{align}
-where $w_h\in U_h$, $\bs s_h\in\bs S_h$, $\hat w_h\in\hat U_h$, and $\hat
-r_h^{e}\in\hat F_h$ are arbitrary. The inf-sup in kernel condition now
-implies:
-\begin{align}
-\label{eq:estimate}
-&\norm{(w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h, \hat r_h^e-\hat t_h^e)}\\
-&\hspace{8ex}\le\frac{1}{\alpha}
-\sup_{\stackrel{
-(\delta u_h,\delta\bsigma_h,\delta\hat u,\delta\hat t)\in}
-{U_h\times\bs S_h\times\hat U_h\times\hat F_h^e}
-}
-\frac{\snorm{
-b( (w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h,\hat r_h^e-\hat t_h^e),
-(\vdeltau,\taudeltau))
-}}
-{\norm{(\vdeltau,\taudeltau)}}\nonumber\\
-&\hspace{8ex}\le\frac{1}{\alpha}
-\sup_{\stackrel{
-(\delta u_h,\delta\bsigma_h,\delta\hat u,\delta\hat t)\in}
-{U_h\times\bs S_h\times\hat U_h\times\hat F_h^e}
-}
-\frac{\snorm{
-b( (w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h,\hat r_h^e+\hat t_h^{ne}-\hat t),
-(\vdeltau,\taudeltau))
-}}
-{\norm{(\vdeltau,\taudeltau)}}\nonumber\\
-&\hspace{8ex}\le\frac{1}{\alpha}
-\norm{(w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h,\hat t-(\hat r_h^e+\hat
-t_h^{ne}))}
-\end{align}
-% \frac{1}{\epsilon}(\bs s_h-\bsigma_h,\taudeltau)
-% +(w_h-u_h,\nabla \cdot\taudeltau)
-% -\langle\hat w_h-\hat u_h,\taudeltau\cdot\bs n\rangle
-% -(\bbeta (w_h-u_h)-(\bs s_h-\bsigma_h),\nabla\vdeltau)
-% +\langle\hat r_h^e-\hat t_h^e,\vdeltau\rangle
-where the second step follows from the Galerkin orthogonality condition
-\eqref{eq:galerkinOrthogonality}, and the last step is a consequence of the
-minimum energy extension norm for fluxes. Combining with \eqref{eq:triangle},
-we get the final stability result:
-\begin{equation}
-\norm{(u-u_h,\bsigma-\bsigma_h,\hat u-\hat u_h,\hat t-\hat t_h)}
-\leq\left(1+\frac{1}{\alpha}\right)
-\inf_{\stackrel{
-(w_h,\bs s_h,\hat w,\hat r_h^e)\in}
-{U_h\times\bs S_h\times\hat U_h\times\hat F_h^e}
-}
-\norm{(u-w_h,\bsigma-\bs s_h,\hat u-\hat w,\hat t-(\hat r_h^e+\hat t_h^{ne}))}
-\,.
-\label{eq:stability}
-\end{equation}
-
-\section{A coupled, robust test norm}
+% We can decompose the discrete flux space $\hat F_h$ into equilibriated fluxes
+% (zero net flux over each element) and some algebraic complement:
+% \begin{equation}
+% \hat F_h=\hat F_h^e\oplus\hat F_h^{ne}\,,\quad\hat
+% F_h^{e}:=\{\hat t:\langle\hat t,(1_K,\bs0)\rangle=0\quad\forall K\}\,.
+% \label{eq:decomposition}
+% \end{equation}
+% In theory, we could accomplish this by employing for fluxes in $\hat F_h^{e}$
+% traces of curls, $\nabla\times\phi$, but we don't do this in practice.
+%
+% \textcolor{red}{
+% In practice, we solve \eqref{eq:conservativeConfusionSystem} as a fully
+% coupled system of equations, but for didactic purposes, we can examine it one
+% piece at a time. If we restrict \eqref{eq:conservativeConfusionSystem}$_1$ to
+% $\delta\hat t\in\hat F_h^{ne}$, the Lagrange multiplier term drops out and we
+% are left with a system that we can solve for $u_h$, $\bsigma_h$, $\hat u_h$,
+% and $\hat t_h^e\in\hat F^e_h$.
+% }
+%
+% \textcolor{red}{
+% Restricting ourselves to $\delta\hat t\in\hat
+% F_h^{e}$ in \eqref{eq:conservativeConfusionSystem}$_1$, we obtain a system  of
+% equations that can be solved for $u_h$, $\bsigma_h$, $\hat u$, and $\hat
+% t\in\hat F_h^e$. The remaining fluxes, $\hat t\in\hat F_h^{ne}$ are determined
+% from \eqref{eq:conservativeConfusionSystem}$_2$. Finally, testing with $\hat
+% t\in\hat F_h^{ne}$ in \eqref{eq:conservativeConfusionSystem}$_1$, we obtain a
+% system of equations that can be solved for Lagrange multipliers $\lambda_K$.
+% }
+%
+% \subsection{\textcolor{red}{Proof of Convergence}}
+% In the following discussion, we do not account for the error in approximating
+% the optimal test functions because $\dots$ (Need explanation).
+% We cannot directly use Brezzi's theorem, but we can reproduce his argument.
+% First of all, variational formulation \eqref{eq:variationalFormulation} is
+% equivalent to:
+%
+% Find $\bs u\in\bs U$ such that
+% \begin{equation}
+% b(\bs u,T(\delta\bs u))=(f,T(\delta\bs u))\quad\forall\bs v\in\bs V\,.
+% \label{eq:bilinearForm}
+% \end{equation}
+% This is because the trial-to-test operator $T=R_V^{-1}B$ is an isomorphism.
+%
+% Restricting ourselves to $\delta\hat t_h\in\hat F_h^e$, and subtracting
+% \eqref{eq:bilinearForm} from \eqref{eq:conservativeConfusionSystem}, we have
+% the Galerkin orthogonality condition:
+% \begin{align}
+% \label{eq:galerkinOrthogonality}
+% \frac{1}{\epsilon}(\bsigma_h-\bsigma,\taudeltau)
+% &+(u_h-u,\nabla\cdot\taudeltau)
+% -\langle\hat u_h-\hat u,\taudeltau\cdot\bs n\rangle
+% \nonumber\\
+% &-(\bbeta(u_h-u)-(\bsigma_h-\bsigma),\nabla\vdeltau)
+% +\langle\hat t_h-\hat t,\vdeltau\rangle
+% \\
+% &\hspace{25ex}\forall(\delta u_h,\delta\bsigma_h,\delta\hat u_h,\delta\hat t_h)
+% \in U_h\times\bs S_h\times\hat U_h\times\hat F_h^e\,.
+% \nonumber
+% \end{align}
+%
+% We begin with an equivalent of Brezzi's \emph{discrete inf-sup in kernel
+% condition}.
+% \begin{lemma}
+% \label{lemma:infsuplemma}
+% The following condition holds:
+% \begin{align}
+% \sup_{\stackrel{
+% (\delta u_h,\delta\bsigma_h,\delta\hat u,\delta\hat t)\in}
+% {U_h\times\bs S_h\times\hat U_h\times\hat F_h^e}
+% }
+% \frac{\snorm{
+% b((u_h,\bsigma_h,\hat u_h,\hat t_h), (\vdeltau,\taudeltau))
+% % \frac{1}{\epsilon}(\bsigma_h,\taudeltau)
+% % +(u_h,\nabla \cdot\taudeltau)
+% % -\langle\hat u_h,\taudeltau\cdot\bs n\rangle
+% % -(\bbeta u_h-\bsigma_h,\nabla\vdeltau)
+% % +\langle\hat t_h,\vdeltau\rangle
+% }}
+% {\norm{(\vdeltau,\taudeltau)}}
+% \ge\alpha\norm{(u_h,\bsigma_h,\hat u_h,\hat t_h)}\quad\nonumber\\
+% \forall(u_h,\bsigma_h,\hat u_h,\hat t_h)
+% \in U_h\times\bs S_h\times\hat U_h\times\hat F_h^e\,.
+% \label{eq:infsup}
+% \end{align}
+%
+% \end{lemma}
+% \begin{proof}
+% By the very construction of the trial-to-test operator, the supremum on the
+% left is equal to
+% \begin{equation}
+% \norm{T(u_h,\bsigma_h,\hat u_h,\hat t_h)}_{V}
+% =\norm{R_V^{-1}B(u_h,\bsigma_h,\hat u_h, \hat t_h)}_{V}
+% =\norm{B(u_h,\bsigma_h,\hat u_h, \hat t_h)}_{V'}
+% \label{eq:infsupproof}
+% \end{equation}
+% The condition follows now from the fact that operator $B$ is bounded below,
+% i.e. bilinear form \linebreak$b((u_h,\bsigma_h,\hat u_h, \hat t_h),(v,\btau))$ satisfies
+% the inf-sup condition.
+% \end{proof}
+%
+% Assume additionally that flux decomposition \eqref{eq:decomposition} is
+% orthogonal. We begin by decomposing $\hat t_h$,
+% \begin{equation}
+% \hat t_h=\hat t_h^{e}+\hat t_h^{ne}\,.
+% \label{eq:fluxdecomposition}
+% \end{equation}
+% Next, we use the triangle inequality,
+% \begin{align}
+% \label{eq:triangle}
+% \norm{(u-u_h,\bsigma-\bsigma_h,\hat u-\hat u_h, \hat t-\hat t_h)}&=
+% \norm{(u-u_h,\bsigma-\bsigma_h,\hat u-\hat u_h, \hat t-(\hat t_h^e+\hat t_h^{ne}))}\nonumber\\
+% &\le\norm{(u-w_h,\bsigma-\bs s_h,\hat u-\hat w_h, \hat t-(\hat r_h^e+\hat t_h^{ne}))}\\
+% &\hspace{3ex}+\norm{(w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h, \hat r_h^e-\hat t_h^e)}\nonumber
+% \end{align}
+% where $w_h\in U_h$, $\bs s_h\in\bs S_h$, $\hat w_h\in\hat U_h$, and $\hat
+% r_h^{e}\in\hat F_h$ are arbitrary. The inf-sup in kernel condition now
+% implies:
+% \begin{align}
+% \label{eq:estimate}
+% &\norm{(w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h, \hat r_h^e-\hat t_h^e)}\\
+% &\hspace{8ex}\le\frac{1}{\alpha}
+% \sup_{\stackrel{
+% (\delta u_h,\delta\bsigma_h,\delta\hat u,\delta\hat t)\in}
+% {U_h\times\bs S_h\times\hat U_h\times\hat F_h^e}
+% }
+% \frac{\snorm{
+% b( (w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h,\hat r_h^e-\hat t_h^e),
+% (\vdeltau,\taudeltau))
+% }}
+% {\norm{(\vdeltau,\taudeltau)}}\nonumber\\
+% &\hspace{8ex}\le\frac{1}{\alpha}
+% \sup_{\stackrel{
+% (\delta u_h,\delta\bsigma_h,\delta\hat u,\delta\hat t)\in}
+% {U_h\times\bs S_h\times\hat U_h\times\hat F_h^e}
+% }
+% \frac{\snorm{
+% b( (w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h,\hat r_h^e+\hat t_h^{ne}-\hat t),
+% (\vdeltau,\taudeltau))
+% }}
+% {\norm{(\vdeltau,\taudeltau)}}\nonumber\\
+% &\hspace{8ex}\le\frac{1}{\alpha}
+% \norm{(w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h,\hat t-(\hat r_h^e+\hat
+% t_h^{ne}))}
+% \end{align}
+% % \frac{1}{\epsilon}(\bs s_h-\bsigma_h,\taudeltau)
+% % +(w_h-u_h,\nabla \cdot\taudeltau)
+% % -\langle\hat w_h-\hat u_h,\taudeltau\cdot\bs n\rangle
+% % -(\bbeta (w_h-u_h)-(\bs s_h-\bsigma_h),\nabla\vdeltau)
+% % +\langle\hat r_h^e-\hat t_h^e,\vdeltau\rangle
+% where the second step follows from the Galerkin orthogonality condition
+% \eqref{eq:galerkinOrthogonality}, and the last step is a consequence of the
+% minimum energy extension norm for fluxes. Combining with \eqref{eq:triangle},
+% we get the final stability result:
+% \begin{equation}
+% \norm{(u-u_h,\bsigma-\bsigma_h,\hat u-\hat u_h,\hat t-\hat t_h)}
+% \leq\left(1+\frac{1}{\alpha}\right)
+% \inf_{\stackrel{
+% (w_h,\bs s_h,\hat w,\hat r_h^e)\in}
+% {U_h\times\bs S_h\times\hat U_h\times\hat F_h^e}
+% }
+% \norm{(u-w_h,\bsigma-\bs s_h,\hat u-\hat w,\hat t-(\hat r_h^e+\hat t_h^{ne}))}
+% \,.
+% \label{eq:stability}
+% \end{equation}
+
+\section{Robust test norms}
 The optimal test functions are determined by solving local problems determined
@@
 
-\subsection{A second model problem}
+\subsection{A model problem}
 \seclab{sec:confusionPlate}
 We begin by first examining a different problem than convection-diffusion.
-We look at admissible solutions for the homogeneous Laplace's equation over
+We look at admissible solutions for the homogeneous Laplace's equation
+(convection diffusion with $\bbeta=\bs 0$) over
 the $y > 0$ half-plane under boundary conditions
@@
 \ref{fig:laplaceStresses} are finite element solutions of the above problem
-under a quadratic $h$-refined mesh.  Figure~\ref{fig:laplace} confirms that
+obtained with a quadratic $h$-refined mesh.  Figure~\ref{fig:laplace} confirms that
 $u$ is bounded, while Figure~\ref{fig:laplaceStresses} confirms that
@@
 We consider now the convection-diffusion problem, under a similar setup as
-before.  We consider the domain $\Omega = [0,1]^2$, with boundary conditions
+before.  We consider the domain $\Omega = [0,1]^2$ with advection vector
+$\bbeta=(1,0)$ and boundary conditions
 \begin{align*}
@@
 boundary, $\hat t=0$ on the top and bottom edges, and $\hat u=1$ on the
-cylinder.
+cylinder. We run with $\epsilon=10^{-3}$.
 

### 2013-11-07 docs/Truman/LocalConservation/paper/paper.tex

@@
 \def\btau{\boldsymbol\tau}
+\def\bftau{\boldsymbol\tau}
 \def\bsigma{\boldsymbol\sigma}
@@
 \newcommand{\bfsig}{\mbox{\boldmath $\sigma$}}
+\newcommand{\bfv}{\boldsymbol v}
+\newcommand{\bfu}{\boldsymbol u}
+\newcommand{\bfpsi}{\boldsymbol\psi}
+\newcommand{\bflambda}{\boldsymbol\lambda}
 \newcommand{\bfn}{\mbox{\boldmath $n$}}
@@
 
-% We can decompose the discrete flux space $\hat F_h$ into equilibriated fluxes
-% (zero net flux over each element) and some algebraic complement:
-% \begin{equation}
-% \hat F_h=\hat F_h^e\oplus\hat F_h^{ne}\,,\quad\hat
-% F_h^{e}:=\{\hat t:\langle\hat t,(1_K,\bs0)\rangle=0\quad\forall K\}\,.
-% \label{eq:decomposition}
-% \end{equation}
-% In theory, we could accomplish this by employing for fluxes in $\hat F_h^{e}$
-% traces of curls, $\nabla\times\phi$, but we don't do this in practice.
-%
-% \textcolor{red}{
-% In practice, we solve \eqref{eq:conservativeConfusionSystem} as a fully
-% coupled system of equations, but for didactic purposes, we can examine it one
-% piece at a time. If we restrict \eqref{eq:conservativeConfusionSystem}$_1$ to
-% $\delta\hat t\in\hat F_h^{ne}$, the Lagrange multiplier term drops out and we
-% are left with a system that we can solve for $u_h$, $\bsigma_h$, $\hat u_h$,
-% and $\hat t_h^e\in\hat F^e_h$.
-% }
-%
-% \textcolor{red}{
-% Restricting ourselves to $\delta\hat t\in\hat
-% F_h^{e}$ in \eqref{eq:conservativeConfusionSystem}$_1$, we obtain a system  of
-% equations that can be solved for $u_h$, $\bsigma_h$, $\hat u$, and $\hat
-% t\in\hat F_h^e$. The remaining fluxes, $\hat t\in\hat F_h^{ne}$ are determined
-% from \eqref{eq:conservativeConfusionSystem}$_2$. Finally, testing with $\hat
-% t\in\hat F_h^{ne}$ in \eqref{eq:conservativeConfusionSystem}$_1$, we obtain a
-% system of equations that can be solved for Lagrange multipliers $\lambda_K$.
-% }
-%
-% \subsection{\textcolor{red}{Proof of Convergence}}
-% In the following discussion, we do not account for the error in approximating
-% the optimal test functions because $\dots$ (Need explanation).
-% We cannot directly use Brezzi's theorem, but we can reproduce his argument.
-% First of all, variational formulation \eqref{eq:variationalFormulation} is
-% equivalent to:
-%
-% Find $\bs u\in\bs U$ such that
-% \begin{equation}
-% b(\bs u,T(\delta\bs u))=(f,T(\delta\bs u))\quad\forall\bs v\in\bs V\,.
-% \label{eq:bilinearForm}
-% \end{equation}
-% This is because the trial-to-test operator $T=R_V^{-1}B$ is an isomorphism.
-%
-% Restricting ourselves to $\delta\hat t_h\in\hat F_h^e$, and subtracting
-% \eqref{eq:bilinearForm} from \eqref{eq:conservativeConfusionSystem}, we have
-% the Galerkin orthogonality condition:
-% \begin{align}
-% \label{eq:galerkinOrthogonality}
-% \frac{1}{\epsilon}(\bsigma_h-\bsigma,\taudeltau)
-% &+(u_h-u,\nabla\cdot\taudeltau)
-% -\langle\hat u_h-\hat u,\taudeltau\cdot\bs n\rangle
-% \nonumber\\
-% &-(\bbeta(u_h-u)-(\bsigma_h-\bsigma),\nabla\vdeltau)
-% +\langle\hat t_h-\hat t,\vdeltau\rangle
-% \\
-% &\hspace{25ex}\forall(\delta u_h,\delta\bsigma_h,\delta\hat u_h,\delta\hat t_h)
-% \in U_h\times\bs S_h\times\hat U_h\times\hat F_h^e\,.
-% \nonumber
-% \end{align}
-%
-% We begin with an equivalent of Brezzi's \emph{discrete inf-sup in kernel
-% condition}.
-% \begin{lemma}
-% \label{lemma:infsuplemma}
-% The following condition holds:
-% \begin{align}
-% \sup_{\stackrel{
-% (\delta u_h,\delta\bsigma_h,\delta\hat u,\delta\hat t)\in}
-% {U_h\times\bs S_h\times\hat U_h\times\hat F_h^e}
-% }
-% \frac{\snorm{
-% b((u_h,\bsigma_h,\hat u_h,\hat t_h), (\vdeltau,\taudeltau))
-% % \frac{1}{\epsilon}(\bsigma_h,\taudeltau)
-% % +(u_h,\nabla \cdot\taudeltau)
-% % -\langle\hat u_h,\taudeltau\cdot\bs n\rangle
-% % -(\bbeta u_h-\bsigma_h,\nabla\vdeltau)
-% % +\langle\hat t_h,\vdeltau\rangle
-% }}
-% {\norm{(\vdeltau,\taudeltau)}}
-% \ge\alpha\norm{(u_h,\bsigma_h,\hat u_h,\hat t_h)}\quad\nonumber\\
-% \forall(u_h,\bsigma_h,\hat u_h,\hat t_h)
-% \in U_h\times\bs S_h\times\hat U_h\times\hat F_h^e\,.
-% \label{eq:infsup}
-% \end{align}
-%
-% \end{lemma}
-% \begin{proof}
-% By the very construction of the trial-to-test operator, the supremum on the
-% left is equal to
-% \begin{equation}
-% \norm{T(u_h,\bsigma_h,\hat u_h,\hat t_h)}_{V}
-% =\norm{R_V^{-1}B(u_h,\bsigma_h,\hat u_h, \hat t_h)}_{V}
-% =\norm{B(u_h,\bsigma_h,\hat u_h, \hat t_h)}_{V'}
-% \label{eq:infsupproof}
-% \end{equation}
-% The condition follows now from the fact that operator $B$ is bounded below,
-% i.e. bilinear form \linebreak$b((u_h,\bsigma_h,\hat u_h, \hat t_h),(v,\btau))$ satisfies
-% the inf-sup condition.
-% \end{proof}
-%
-% Assume additionally that flux decomposition \eqref{eq:decomposition} is
-% orthogonal. We begin by decomposing $\hat t_h$,
-% \begin{equation}
-% \hat t_h=\hat t_h^{e}+\hat t_h^{ne}\,.
-% \label{eq:fluxdecomposition}
-% \end{equation}
-% Next, we use the triangle inequality,
-% \begin{align}
-% \label{eq:triangle}
-% \norm{(u-u_h,\bsigma-\bsigma_h,\hat u-\hat u_h, \hat t-\hat t_h)}&=
-% \norm{(u-u_h,\bsigma-\bsigma_h,\hat u-\hat u_h, \hat t-(\hat t_h^e+\hat t_h^{ne}))}\nonumber\\
-% &\le\norm{(u-w_h,\bsigma-\bs s_h,\hat u-\hat w_h, \hat t-(\hat r_h^e+\hat t_h^{ne}))}\\
-% &\hspace{3ex}+\norm{(w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h, \hat r_h^e-\hat t_h^e)}\nonumber
-% \end{align}
-% where $w_h\in U_h$, $\bs s_h\in\bs S_h$, $\hat w_h\in\hat U_h$, and $\hat
-% r_h^{e}\in\hat F_h$ are arbitrary. The inf-sup in kernel condition now
-% implies:
-% \begin{align}
-% \label{eq:estimate}
-% &\norm{(w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h, \hat r_h^e-\hat t_h^e)}\\
-% &\hspace{8ex}\le\frac{1}{\alpha}
-% \sup_{\stackrel{
-% (\delta u_h,\delta\bsigma_h,\delta\hat u,\delta\hat t)\in}
-% {U_h\times\bs S_h\times\hat U_h\times\hat F_h^e}
-% }
-% \frac{\snorm{
-% b( (w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h,\hat r_h^e-\hat t_h^e),
-% (\vdeltau,\taudeltau))
-% }}
-% {\norm{(\vdeltau,\taudeltau)}}\nonumber\\
-% &\hspace{8ex}\le\frac{1}{\alpha}
-% \sup_{\stackrel{
-% (\delta u_h,\delta\bsigma_h,\delta\hat u,\delta\hat t)\in}
-% {U_h\times\bs S_h\times\hat U_h\times\hat F_h^e}
-% }
-% \frac{\snorm{
-% b( (w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h,\hat r_h^e+\hat t_h^{ne}-\hat t),
-% (\vdeltau,\taudeltau))
-% }}
-% {\norm{(\vdeltau,\taudeltau)}}\nonumber\\
-% &\hspace{8ex}\le\frac{1}{\alpha}
-% \norm{(w_h-u_h,\bs s_h-\bsigma_h,\hat w_h-\hat u_h,\hat t-(\hat r_h^e+\hat
-% t_h^{ne}))}
-% \end{align}
-% % \frac{1}{\epsilon}(\bs s_h-\bsigma_h,\taudeltau)
-% % +(w_h-u_h,\nabla \cdot\taudeltau)
-% % -\langle\hat w_h-\hat u_h,\taudeltau\cdot\bs n\rangle
-% % -(\bbeta (w_h-u_h)-(\bs s_h-\bsigma_h),\nabla\vdeltau)
-% % +\langle\hat r_h^e-\hat t_h^e,\vdeltau\rangle
-% where the second step follows from the Galerkin orthogonality condition
-% \eqref{eq:galerkinOrthogonality}, and the last step is a consequence of the
-% minimum energy extension norm for fluxes. Combining with \eqref{eq:triangle},
-% we get the final stability result:
-% \begin{equation}
-% \norm{(u-u_h,\bsigma-\bsigma_h,\hat u-\hat u_h,\hat t-\hat t_h)}
-% \leq\left(1+\frac{1}{\alpha}\right)
-% \inf_{\stackrel{
-% (w_h,\bs s_h,\hat w,\hat r_h^e)\in}
-% {U_h\times\bs S_h\times\hat U_h\times\hat F_h^e}
-% }
-% \norm{(u-w_h,\bsigma-\bs s_h,\hat u-\hat w,\hat t-(\hat r_h^e+\hat t_h^{ne}))}
-% \,.
-% \label{eq:stability}
-% \end{equation}
+%%%%%%%%%%% Begin Demkowicz Section %%%%%%%%%%%%
+\subsection{Stability Analysis}
+
+In the following analysis, we neglect the error due to the approximation of optimal test functions.
+We follow the classical Brezzi's theory \cite{Brezzi1974,DBB05} for an abstract
+mixed problem:
+\begin{equation}
+\left\{
+\begin{array}{lll}
+u \in V, p \in Q\\
+a(u,v) + c(p,v) & = l(v) & \forall v \in V \\
+c(q,u) & = g(q) & \forall q \in Q
+\end{array}
+\right.
+\end{equation}
+where $V,Q$ are Hilbert spaces, and $a,c,l,q$ denote the appropriate
+bilinear and linear forms.
+
+The choice of norm for the Lagrange multipliers $\lambda_K$ is implied
+by the quotient norm used for $H^{-1/2}(\Gamma_h)$ and continuity
+bound for form $c(p,v)$ representing the constraint.
+\begin{equation}
+\begin{array}{lll}
+\vert b((u,\bfsig,\hat{u},\hat{t}),\sum_K \lambda_K (1_K,{\bf 0})) \vert
+& = \vert \sum_K \lambda_K \langle \hat{t}, 1_K \rangle_{\ptl K} \vert \\[8pt]
+& = \vert \sum_K \lambda_K \langle v_n , 1_K \rangle_{\ptl K} \vert \\[8pt]
+& = \vert \sum_K \lambda_K \int_K \text{div} \bfv \: 1_K  \vert \\[8pt]
+& \leq \sum_K  \lambda_K \Vert \text{div} \bfv \Vert_{L^2(K)} \mu(K)^{1/2} \\[8pt]
+& \leq (\sum_K \mu(K) \lambda_K^2)^{1/2} \: (\sum_K \Vert \text{div} \bfv \Vert_{L^2(K)}^2 )^{1/2} \\[8pt]
+& \leq \underbrace{(\sum_K \mu(K) \lambda_K^2)^{1/2}}_{=: \Vert \bflambda \Vert} \Vert \hat{t} \Vert_{H^{-1/2}(\Gamma_h)}
+\end{array}
+\end{equation}
+Above, function $\bfv$ denotes the $H(\text{div},\Omega)$ extension of flux $\hat{t}$
+that realizes the minimum in the definition of the quotient (minimum energy extension) norm,
+and $\mu(K)$ stands for the area (measure) of element $K$.
+
+We proceed now with the discussion of the discrete inf-sup stability constants. We skip
+index $h$ in the notation.
+
+\paragraph{Inf Sup Condition} relating spaces $V$ and $Q$ reads as follows,
+\begin{equation}
+\sup_{v \in V} \frac{\vert c(p,v) \vert}{\Vert v \Vert_V} \geq \beta \Vert p \Vert_Q
+\end{equation}
+Let
+\begin{equation}
+R\, : \, L^2(\Omega) \ni q \to \bfv \in \bfH(\text{div},\Omega) \cap \bfH^1(\Omega)
+\end{equation}
+be
+the continuous right inverse of the divergence operator constructed by
+Costabel and McIntosh in \cite{CostabelMcIntosh}.
+Let $\bfv_h$ denote the classical, lowest order Raviart-Thomas (RT) interpolant of
+function
+\begin{equation}
+\bfv = R (\sum_K \lambda_K 1_K) \: .
+\end{equation}
+Note that $\text{div} \bfv_h = \text{div} \bfv = \lambda_K$ in element $K$.
+
+Classical $h$-interpolation interpolation error estimate for the lowest error
+Raviart-Thomas elements and continuity of operator $R$ imply the stability estimate:
+\begin{equation}
+\begin{array}{lll}
+\Vert \bfv_h \Vert & \leq \Vert \bfv_h - \bfv \Vert + \Vert \bfv \Vert\\[8pt]
+&\leq C h \Vert \bfv \Vert_{H^1} +  \Vert \bfv \Vert \\[8pt]
+& \leq C \Vert \text{div} \bfv \Vert = C (\sum_K \mu(K) \lambda_K^2)^{1/2}
+\end{array}
+\label{eq:stab}
+\end{equation}
+Above, $C$ is a generic, mesh independent constant incorporating constant from
+the interpolation error estimate and continuity constant of $R$.
+Let $\hat{t}$ be now the trace of $\bfv_h$. We have then,
+\begin{equation}
+\sup_{\hat{t} \in H^{-1/2}(\Gamma_h)} \frac{\vert  \sum_K \lambda_K \langle \hat{t},1_K \rangle_{\ptl K} \vert}{\Vert \hat{t} \Vert_{H^{-1/2}(\Gamma_h)}}
+\geq \frac{\vert \sum_K \lambda_K \int_K \text{div} \bfv_h \: 1_K  \vert}
+{\Vert \bfv_h \Vert_{H(\text{div},\Omega)}}
+\geq \frac{1}{C} (\sum_K \mu(K) \lambda_K^2)^{1/2}
+\end{equation}
+where $C$ is the constant from stability estimate~(\ref{eq:stab}).
+
+Notice that we have considered traces of lowest order Raviart-Thomas elements for the
+discretization of flux $\hat{t}$. The inf-sup condition for the lowest order RT spaces implies
+automatically the analogous condition for elements of arbitrary order; increasing
+space $V$ makes only the discrete inf-sup constant bigger.
+
+\paragraph{Inf Sup in Kernel Condition} is satisfied automatically due to the use of optimal
+test functions. First of all, we characterize the ``kernel'' space:
+\begin{equation}
+\begin{array}{rl}
+V_0  := & \{ v \in V \, : \, c(v,u) = 0 \: \forall q \in Q\} \\[8pt]
+ = &\{ (u,\bfsig,\hat{u},\hat{t}) \, : \, \langle \hat{t},1_T \rangle = 0 \, \forall K \}
+\end{array}
+\end{equation}
+In other words, the kernel space contains only the equilibriated fluxes.
+With $u \in V_0$, we have then:
+\begin{equation}
+\sup_{v \in V_0} \frac{\vert a(u,v) \vert}{\Vert v \Vert_V }
+ \geq \frac{\vert b(\bfu,T \bfu) \vert}{\Vert T \bfu \Vert}
+= \sup_{(v,\bftau)}
+\frac{\vert b((u,\bfsig,\hat{u},\hat{t}), (v,\bftau)) \vert}{\Vert (v,\bftau) \Vert}
+\geq \gamma \Vert (u,\bfsig,\hat{u},\hat{t}) \Vert
+\end{equation}
+where $\gamma$ is the stability constant for the standard continuous DPG formulation.
+
+With both discrete inf-sup constants in place, we have the standard result: the FE error
+is bounded by the best approximation error. Notice that the exact Lagrange multipliers
+are zero, so the best approximation error involves only solution $(u,\bfsig,\hat{u},\hat{t})$.
+
+\subsubsection{Robustness Analysis}
+
+Recall the main line of analysis in \cite{} leading to the construction of robust
+test norms. With the robust test norms, we have
+\begin{equation}
+\begin{array}{ll}
+\Vert u - u_h \Vert, \Vert \bfsig - \bfsig_h \Vert
+& \lesssim \Vert (u - u_h, \bfsig - \bfsig_h, \hat{u} - \hat{u}_h, \hat{t} - \hat{t}_h \Vert_E \\[8pt]
+&= \inf_{(v_h,\bftau_h,\hat{v},\hat{r}_h)}
+\Vert (u - v_h, \bfsig - \bftau_h, \hat{u} - \hat{v}_h, \hat{t} - \hat{r}_h \Vert_E
+\end{array}
+\end{equation}
+The last equality follows from the fact that DPG method delivers the best approximation
+error in the energy norm (minimizes the residual). This is not longer true for the
+conservative version. So, can we claim the robustness in the sense of the inequality above
+for the conservative version as well ?
+
+One possible way to attack the problem is to switch to the energy norm in the Brezzi's stability
+analysis. Dealing with the ``inf-sup in kernel'' condition is simple. Upon replacing
+the original norm of solution $u$ with the energy norm, both constant $\gamma$ and continuity
+constant become unity. In order to investigate the robustness of inf-sup  constant $\beta$,
+we need to realize first what the energy norm of flux $\hat{t}$ is. Given an element $K$,
+we solve for the optimal test functions corresponding to flux $\hat{t}$,
+\begin{equation}
+\left\{
+\begin{array}{ll}
+v_K \in H^1(K),\, \bftau_K \in \bfH(\text{div},K)\\[8pt]
+((v_K,\bftau_K), (\delta v,\delta \bftau)_V = \langle \hat{t},\delta v\rangle_{\ptl K}
+\quad \forall \delta v \in H^1(K), \delta \bftau \in \bfH(\text{div},K)
+\end{array}
+\right.
+\label{eq:local_problem}
+\end{equation}
+The energy norm of $\hat{t}$ is then equal to:
+\begin{equation}
+\Vert \hat{t} \Vert_E^2 = \sum_K \Vert (v_K,\bftau_K) \Vert_V^2
+\end{equation}
+We need to establish sufficient conditions under which inf-sup and continuity constants for
+the bilinear form representing the constraint are independent of viscosity $\epsilon$.
+
+Let us start with the inf-sup condition,
+\begin{equation}
+\sup_{\hat{t}} \frac{\vert \sum_K \lambda_K \langle \hat{t},1_K \rangle \vert}{\Vert \hat{t} \Vert_E}
+\geq  \beta (\sum_K \mu(K) \lambda_K^2)^{1/2}
+\end{equation}
+As in the previous analysis, we select for $\hat{t}$ the trace of Raviart-Thomas
+interpolant $\bfpsi_h$ of $\bfpsi = R (\sum_K \lambda_K 1_K)$ where $R$ is the right-inverse
+of the divergence operator constructed by Costabel and Mac Intosh. The only change compared
+with the previous analysis, is the evaluation of norm of $\hat{t}_h$. For this, we need
+to solve the local problems:
+\begin{equation}
+((v,\bftau), (\delta v, \delta \bftau)_V = \langle \hat{t}, \delta v \rangle_{\ptl K}
+= \int_K \text{div} \bfpsi_h \, \delta v = \int_K \text{div} \bfpsi \, \delta v = \int_K \lambda_K \delta v
+= \lambda_K (1_K,\delta v)_K  \quad \forall \delta v \in H^1(K)
+\label{eq:local}
+\end{equation}
+We need then an upper bound of the energy norm of $\bfv_h$:
+$$
+(\sum_K \Vert (v,\bftau) \Vert_V^2)^{1/2}
+$$
+Substituting $v$ for $\delta v$ in~(\ref{eq:local}), we get,
+\begin{equation}
+\Vert (v,\bftau) \Vert_V^2 = \lambda_K (1_K, v_K)
+\end{equation}
+If we have a robust stability estimate:
+\begin{equation}
+(1_K, v_K) \leq C \mu(K)^{1/2} \Vert (v,\bftau) \Vert_K
+\end{equation}
+(i.e. constant $C$ is independent of $\epsilon$) then
+\begin{equation}
+\Vert  (v,\bftau) \Vert_V \leq C \mu(K)^{1/2} \vert \lambda_K \vert
+\end{equation}
+and, eventually, as needed,
+\begin{equation}
+\sum_K \Vert (v,\bftau) \Vert_V^2  \leq C^2 \sum_K \mu(K) \lambda_K^2
+\end{equation}
+which leads to the robust estimate of inf-sup constant $\beta$. For example, it is sufficient if
+\begin{equation}
+\Vert v \Vert_{L^2(K)} \leq \Vert v \Vert_V \, .
+\label{eq:robust_est1}
+\end{equation}
+Notice that the stability analysis with the energy norm was, in a sense, easier than
+with the quotient norm. Only the divergence of the interpolant $\bfpsi_h$ enters~(\ref{eq:local})
+and it coincides with the divergence of $\bfpsi$.
+
+We arrive at a similar situation in the continuity estimate of
+$$
+\sum_K \lambda_K \langle \hat{t}, 1_K \rangle
+$$
+Testing with $(1_K,{\bf 0})$ in the local problem~(\ref{eq:local_problem}), we obtain,
+\begin{equation}
+((v,\bftau),(1_K,{\bf 0}))_V = \langle \hat{t}, 1_K \rangle_{\ptl K}
+\label{eq:local2}
+\end{equation}
+If we have a robust estimate,
+\begin{equation}
+\vert ((v,\bftau),(1_K,{\bf 0}))_V \vert \leq C \mu(K)^{1/2} \, \Vert (v,\bftau) \Vert_V
+\label{eq:robust_est2}
+\end{equation}
+then
+\begin{equation}
+\vert \sum_K \lambda_K \langle \hat{t}, 1_K \rangle \vert \leq C (\sum_K \mu(K) \lambda_K^2)^{1/2}
+\, (\sum_K \Vert (v,\bftau) \Vert_V^2)^{1/2}
+= C (\sum_K \mu(K) \lambda_K^2)^{1/2}  \Vert \hat{t} \Vert_E
+\end{equation}
+as needed.
+
+For instance, condition~(\ref{eq:robust_est2}) will be satisfied if the test inner product
+in~(\ref{eq:local2}) reduces to the $L^2$ term only,
+\begin{equation}
+((v,\bftau),(1_K,{\bf 0}))_V = (v,1_K)_{L^2(K)} \: .
+\end{equation}
+With the robust stability and continuity constants for the mixed problem, the energy error
+of solution $(u,\bfsig,\hat{u},\hat{t})$ (and Lagrange multipliers $\lambda_K$ as well)
+is bounded robustly by the {\em best approximation error} of  $(u,\bfsig,\hat{u},\hat{t})$
+measured in the energy norm. We arrive thus at the same situation as in the standard
+DPG method.
+
+% %%%%%%%%%%% End Demkowicz Section %%%%%%%%%%%%
 

### 2013-11-11 docs/Truman/LocalConservation/paper/paper.tex
Commented out irrelevant local conservation problems

--- 2013-11-04 docs/Truman/LocalConservation/paper/paper.tex
@@
 
-\subsubsection{Skewed Convection-Diffusion Problem}
-This is a standard convection-diffusion problem with a skewed convection
-vector relative to the mesh. We take $\bbeta=(2,1)$, and on the left and
-bottom inflow boundaries we impose $\hat t=1-x-y$ while the right and top
-boundaries have $\hat u=0$. We solve for $\epsilon=10^{-4}$.
-
-\begin{figure}[p]
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Confusion/modified8nc.png}
-\includegraphics[width=\textwidth]{figs/Confusion/modified8nc_mesh.png}
-\caption{Nonconservative}
-\label{fig:confusionModified8nc}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Confusion/modified8c.png}
-\includegraphics[width=\textwidth]{figs/Confusion/modified8c_mesh.png}
-\caption{Conservative}
-\label{fig:confusionModified8c}
-\end{subfigure}
-\caption{Skewed convection-diffusion problem after 8 refinements}
-\label{fig:confusion}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=0.8\textwidth]{figs/Confusion/modifiedFlux.pdf}
-\caption{Flux imbalance in skewed convection-diffusion solutions}
-\label{fig:confusionFlux}
-\end{figure}
-
-\subsubsection{Double Glazing Problem}
-This nominal problem definition takes the same unit square domain with
-\[
-\bbeta=\binom{2(2y-1)(1-(2x-1)^2)}{-2(2x-1)(1-(2y-1)^2)}\,;\quad
-\hat u=
-\begin{cases}
-1 & \mbox{on }\Gamma_{right}\\
-0 & \mbox{else }
-\end{cases}\,,
-\]
-except that this definition for the boundary is not legal for $\hat u\in
-H^{\frac{1}{2}}(\Gamma_h)$ which is continuous. Therefore we use a ramp of
-width $\sqrt{\epsilon}$ on the right edge to go from 0 to 1. The
-results are for $\epsilon=10^{-2}$.
-
-\begin{figure}[p]
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/DoubleGlazing/modified5nc.png}
-\caption{Nonconservative}
-\label{fig:doubleglazingGraph6c}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/DoubleGlazing/modified5c.png}
-\caption{Conservative}
-\label{fig:doubleglazingRobust6c}
-\end{subfigure}
-\caption{Double glazing problem after 5 refinements}
-\label{fig:doubleglazing}
-\end{figure}
-
-\begin{figure}[p]
-\centering
-\includegraphics[width=0.8\textwidth]{figs/DoubleGlazing/modifiedFlux.pdf}
-\caption{Flux imbalance in double glazing problem}
-\label{fig:doubleglazingFlux}
-\end{figure}
+% \subsubsection{Skewed Convection-Diffusion Problem}
+% This is a standard convection-diffusion problem with a skewed convection
+% vector relative to the mesh. We take $\bbeta=(2,1)$, and on the left and
+% bottom inflow boundaries we impose $\hat t=1-x-y$ while the right and top
+% boundaries have $\hat u=0$. We solve for $\epsilon=10^{-4}$.
+%
+% \begin{figure}[p]
+% \centering
+% \begin{subfigure}[t]{0.45\textwidth}
+% \centering
+% \includegraphics[width=\textwidth]{figs/Confusion/modified8nc.png}
+% \includegraphics[width=\textwidth]{figs/Confusion/modified8nc_mesh.png}
+% \caption{Nonconservative}
+% \label{fig:confusionModified8nc}
+% \end{subfigure}
+% \begin{subfigure}[t]{0.45\textwidth}
+% \centering
+% \includegraphics[width=\textwidth]{figs/Confusion/modified8c.png}
+% \includegraphics[width=\textwidth]{figs/Confusion/modified8c_mesh.png}
+% \caption{Conservative}
+% \label{fig:confusionModified8c}
+% \end{subfigure}
+% \caption{Skewed convection-diffusion problem after 8 refinements}
+% \label{fig:confusion}
+% \end{figure}
+%
+% \begin{figure}[h!]
+% \centering
+% \includegraphics[width=0.8\textwidth]{figs/Confusion/modifiedFlux.pdf}
+% \caption{Flux imbalance in skewed convection-diffusion solutions}
+% \label{fig:confusionFlux}
+% \end{figure}
+%
+% \subsubsection{Double Glazing Problem}
+% This nominal problem definition takes the same unit square domain with
+% \[
+% \bbeta=\binom{2(2y-1)(1-(2x-1)^2)}{-2(2x-1)(1-(2y-1)^2)}\,;\quad
+% \hat u=
+% \begin{cases}
+% 1 & \mbox{on }\Gamma_{right}\\
+% 0 & \mbox{else }
+% \end{cases}\,,
+% \]
+% except that this definition for the boundary is not legal for $\hat u\in
+% H^{\frac{1}{2}}(\Gamma_h)$ which is continuous. Therefore we use a ramp of
+% width $\sqrt{\epsilon}$ on the right edge to go from 0 to 1. The
+% results are for $\epsilon=10^{-2}$.
+%
+% \begin{figure}[p]
+% \centering
+% \begin{subfigure}[t]{0.45\textwidth}
+% \centering
+% \includegraphics[width=\textwidth]{figs/DoubleGlazing/modified5nc.png}
+% \caption{Nonconservative}
+% \label{fig:doubleglazingGraph6c}
+% \end{subfigure}
+% \begin{subfigure}[t]{0.45\textwidth}
+% \centering
+% \includegraphics[width=\textwidth]{figs/DoubleGlazing/modified5c.png}
+% \caption{Conservative}
+% \label{fig:doubleglazingRobust6c}
+% \end{subfigure}
+% \caption{Double glazing problem after 5 refinements}
+% \label{fig:doubleglazing}
+% \end{figure}
+%
+% \begin{figure}[p]
+% \centering
+% \includegraphics[width=0.8\textwidth]{figs/DoubleGlazing/modifiedFlux.pdf}
+% \caption{Flux imbalance in double glazing problem}
+% \label{fig:doubleglazingFlux}
+% \end{figure}
 
@@
 
-\subsubsection{Wedge Problem}
-We devised this problem to examine some of the issues we were having blow up
-of the solution under the robust test norm. The domain is a rectangle
-$[-0.5,0.5]\times[-1,0.5]$ where the triangle connecting the bottom edges with
-the origin at $(0,0)$ is removed. The convection vector $\bbeta=(1,0)^T$,
-$\epsilon=10^{-1}$, and we apply boundary conditions $\hat t=0$ on the left
-inflow edge, $\hat u=0$ on the top edge, $\bbeta\cdot\mathbf{n}\cdot\hat
-u-\hat t=\sigma_n=0$ on the right outflow edge, $\hat u=1$ on the leading edge
-of the wedge, and $\hat t=\bbeta\cdot\mathbf{n}\cdot 1$ on the trailing edge
-of the wedge.
-
-\begin{figure}[p]
-\centering
-\begin{subfigure}[t]{0.4\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Wedge/modified16nc.png}
-\includegraphics[width=\textwidth]{figs/Wedge/modified16nc_mesh.png}
-\caption{Nonconservative}
-\label{fig:wedgeGraph16nc}
-\end{subfigure}
-\begin{subfigure}[t]{0.4\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Wedge/modified16c.png}
-\includegraphics[width=\textwidth]{figs/Wedge/modified16c_mesh.png}
-\caption{Conservative}
-\label{fig:wedgeRobust16nc}
-\end{subfigure}
-\caption{Wedge problem after 16 refinements}
-\label{fig:wedge}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=0.8\textwidth]{figs/Wedge/modifiedFlux.pdf}
-\caption{Flux imbalance in wedge solutions}
-\label{fig:wedge_flux}
-\end{figure}
-
-\subsubsection{Inner Layer Problem}
-In this problem, $\bbeta=(\frac{\sqrt{3}}{2},\frac{1}{2})^T$ and we have a
-discontinuous flux inflow condition where $\hat t=0$ if $y\le0.2$ and $\hat
-t=\bbeta\cdot\mathbf{n}$ if $y>0.2$. On the outflow, $\hat u=0$. We use a very
-small diffusion scale of $\epsilon=10^{-6}$ which creates a very thin inner
-layer.
-% Nonconservative solution in range $[-0.38, 1.34]$.
-% Conservative solution in range $[-0.39, 1.38]$.
-
-\begin{figure}[p]
-\centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/InnerLayer/modified8nc.png}
-\includegraphics[width=\textwidth]{figs/InnerLayer/modified8nc_mesh.png}
-\caption{Nonconservative}
-\label{fig:innerlayer8nc}
-\end{subfigure}
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/InnerLayer/modified8c.png}
-\includegraphics[width=\textwidth]{figs/InnerLayer/modified8c_mesh.png}
-\caption{Conservative}
-\label{fig:innerlayer8c}
-\end{subfigure}
-\caption{Inner layer problem after 8 refinements}
-\label{fig:innerlayer}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=0.8\textwidth]{figs/InnerLayer/modifiedFlux.pdf}
-\caption{Flux imbalance in inner layer solutions}
-\label{fig:innerlayer_flux}
-\end{figure}
+% \subsubsection{Wedge Problem}
+% We devised this problem to examine some of the issues we were having blow up
+% of the solution under the robust test norm. The domain is a rectangle
+% $[-0.5,0.5]\times[-1,0.5]$ where the triangle connecting the bottom edges with
+% the origin at $(0,0)$ is removed. The convection vector $\bbeta=(1,0)^T$,
+% $\epsilon=10^{-1}$, and we apply boundary conditions $\hat t=0$ on the left
+% inflow edge, $\hat u=0$ on the top edge, $\bbeta\cdot\mathbf{n}\cdot\hat
+% u-\hat t=\sigma_n=0$ on the right outflow edge, $\hat u=1$ on the leading edge
+% of the wedge, and $\hat t=\bbeta\cdot\mathbf{n}\cdot 1$ on the trailing edge
+% of the wedge.
+%
+% \begin{figure}[p]
+% \centering
+% \begin{subfigure}[t]{0.4\textwidth}
+% \centering
+% \includegraphics[width=\textwidth]{figs/Wedge/modified16nc.png}
+% \includegraphics[width=\textwidth]{figs/Wedge/modified16nc_mesh.png}
+% \caption{Nonconservative}
+% \label{fig:wedgeGraph16nc}
+% \end{subfigure}
+% \begin{subfigure}[t]{0.4\textwidth}
+% \centering
+% \includegraphics[width=\textwidth]{figs/Wedge/modified16c.png}
+% \includegraphics[width=\textwidth]{figs/Wedge/modified16c_mesh.png}
+% \caption{Conservative}
+% \label{fig:wedgeRobust16nc}
+% \end{subfigure}
+% \caption{Wedge problem after 16 refinements}
+% \label{fig:wedge}
+% \end{figure}
+%
+% \begin{figure}[h!]
+% \centering
+% \includegraphics[width=0.8\textwidth]{figs/Wedge/modifiedFlux.pdf}
+% \caption{Flux imbalance in wedge solutions}
+% \label{fig:wedge_flux}
+% \end{figure}
+%
+% \subsubsection{Inner Layer Problem}
+% In this problem, $\bbeta=(\frac{\sqrt{3}}{2},\frac{1}{2})^T$ and we have a
+% discontinuous flux inflow condition where $\hat t=0$ if $y\le0.2$ and $\hat
+% t=\bbeta\cdot\mathbf{n}$ if $y>0.2$. On the outflow, $\hat u=0$. We use a very
+% small diffusion scale of $\epsilon=10^{-6}$ which creates a very thin inner
+% layer.
+% % Nonconservative solution in range $[-0.38, 1.34]$.
+% % Conservative solution in range $[-0.39, 1.38]$.
+%
+% \begin{figure}[p]
+% \centering
+% \begin{subfigure}[t]{0.45\textwidth}
+% \centering
+% \includegraphics[width=\textwidth]{figs/InnerLayer/modified8nc.png}
+% \includegraphics[width=\textwidth]{figs/InnerLayer/modified8nc_mesh.png}
+% \caption{Nonconservative}
+% \label{fig:innerlayer8nc}
+% \end{subfigure}
+% \begin{subfigure}[t]{0.45\textwidth}
+% \centering
+% \includegraphics[width=\textwidth]{figs/InnerLayer/modified8c.png}
+% \includegraphics[width=\textwidth]{figs/InnerLayer/modified8c_mesh.png}
+% \caption{Conservative}
+% \label{fig:innerlayer8c}
+% \end{subfigure}
+% \caption{Inner layer problem after 8 refinements}
+% \label{fig:innerlayer}
+% \end{figure}
+%
+% \begin{figure}[h!]
+% \centering
+% \includegraphics[width=0.8\textwidth]{figs/InnerLayer/modifiedFlux.pdf}
+% \caption{Flux imbalance in inner layer solutions}
+% \label{fig:innerlayer_flux}
+% \end{figure}
 
@@
 
-\subsubsection{Hemker Problem}
-The Hemker problem is defined on a domain
-$\Omega=\{[-3,9]\times[-3,3]\}\setminus\{(x,y):x^2+y^2<1\}$, essentially a simplified
-model of flow past an infinite cylinder. We start with the initial mesh shown
-in Figure~\ref{fig:hemkerInitial} in which we approximate the circle by 8
-fifth order curvilinear polynomial segments. As we refine, the new elements are
-fitted to better approximate an exact circle.The boundary conditions are $\hat
-t=\bbeta\cdot\mathbf{n}\cdot 1$ on the left inflow boundary,
-$\bbeta\cdot\mathbf{n}\cdot\hat u-\hat t=\sigma_n=0$ on the right outflow
-boundary, $\hat t=0$ on the top and bottom edges, and $\hat u=1$ on the
-cylinder. We run with $\epsilon=10^{-3}$.
-
-\begin{figure}[p]
-\centering
-\includegraphics[width=0.8\textwidth]{figs/Hemker/initial_mesh.png}
-\caption{Initial mesh for the Hemker problem}
-\label{fig:hemkerInitial}
-\end{figure}
-
-\begin{figure}[p]
-\centering
-\centering
-\includegraphics[width=0.8\textwidth]{figs/Hemker/modifiedFlux.pdf}
-\caption{Flux imbalance in Hemker problem}
-\label{fig:hemkerFlux}
-\end{figure}
-
-\begin{figure}[p]
-\centering
-\begin{subfigure}[t]{0.6\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Hemker/modified8nc.png}
-\end{subfigure}
-\begin{subfigure}[t]{0.6\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Hemker/modified8nc_mesh.png}
-\caption{Nonconservative}
-\label{fig:hemkerModified8nc}
-\end{subfigure}
-\begin{subfigure}[t]{0.6\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Hemker/modified8c.png}
-\end{subfigure}
-\begin{subfigure}[t]{0.6\textwidth}
-\centering
-\includegraphics[width=\textwidth]{figs/Hemker/modified8c_mesh.png}
-\caption{Conservative}
-\label{fig:hemkerModified8c}
-\end{subfigure}
-\caption{Hemker problem after 8 refinements}
-\label{fig:hemker8}
-\end{figure}
+% \subsubsection{Hemker Problem}
+% The Hemker problem is defined on a domain
+% $\Omega=\{[-3,9]\times[-3,3]\}\setminus\{(x,y):x^2+y^2<1\}$, essentially a simplified
+% model of flow past an infinite cylinder. We start with the initial mesh shown
+% in Figure~\ref{fig:hemkerInitial} in which we approximate the circle by 8
+% fifth order curvilinear polynomial segments. As we refine, the new elements are
+% fitted to better approximate an exact circle.The boundary conditions are $\hat
+% t=\bbeta\cdot\mathbf{n}\cdot 1$ on the left inflow boundary,
+% $\bbeta\cdot\mathbf{n}\cdot\hat u-\hat t=\sigma_n=0$ on the right outflow
+% boundary, $\hat t=0$ on the top and bottom edges, and $\hat u=1$ on the
+% cylinder. We run with $\epsilon=10^{-3}$.
+%
+% \begin{figure}[p]
+% \centering
+% \includegraphics[width=0.8\textwidth]{figs/Hemker/initial_mesh.png}
+% \caption{Initial mesh for the Hemker problem}
+% \label{fig:hemkerInitial}
+% \end{figure}
+%
+% \begin{figure}[p]
+% \centering
+% \centering
+% \includegraphics[width=0.8\textwidth]{figs/Hemker/modifiedFlux.pdf}
+% \caption{Flux imbalance in Hemker problem}
+% \label{fig:hemkerFlux}
+% \end{figure}
+%
+% \begin{figure}[p]
+% \centering
+% \begin{subfigure}[t]{0.6\textwidth}
+% \centering
+% \includegraphics[width=\textwidth]{figs/Hemker/modified8nc.png}
+% \end{subfigure}
+% \begin{subfigure}[t]{0.6\textwidth}
+% \centering
+% \includegraphics[width=\textwidth]{figs/Hemker/modified8nc_mesh.png}
+% \caption{Nonconservative}
+% \label{fig:hemkerModified8nc}
+% \end{subfigure}
+% \begin{subfigure}[t]{0.6\textwidth}
+% \centering
+% \includegraphics[width=\textwidth]{figs/Hemker/modified8c.png}
+% \end{subfigure}
+% \begin{subfigure}[t]{0.6\textwidth}
+% \centering
+% \includegraphics[width=\textwidth]{figs/Hemker/modified8c_mesh.png}
+% \caption{Conservative}
+% \label{fig:hemkerModified8c}
+% \end{subfigure}
+% \caption{Hemker problem after 8 refinements}
+% \label{fig:hemker8}
+% \end{figure}
 

### 2013-11-15 docs/Truman/LocalConservation/paper/paper.tex
Updates to local conservation paper

--- 2013-11-07 docs/Truman/LocalConservation/paper/paper.tex
@@
 \usepackage{subcaption}
+\usepackage{morefloats}
+\usepackage{pgf,tikz}
+\usetikzlibrary{arrows}
 
@@
 \def\bftau{\boldsymbol\tau}
-\def\bsigma{\boldsymbol\sigma}
+\def\bfsigma{\boldsymbol\sigma}
 \def\bbeta{\boldsymbol\beta}
@@
 \newcommand{\bfu}{\boldsymbol u}
+\newcommand{\bff}{\boldsymbol f}
+\newcommand{\bft}{\boldsymbol t}
 \newcommand{\bfpsi}{\boldsymbol\psi}
@@
 \right]}
-\def\vecttwo#1#2{\left[
+\def\vecttwo#1#2{\left(
 \begin{array}{c}
@@
 \end{array}
-\right]}
+\right)}
 \def\vectthree#1#2#3{\left[
@@
 
-\renewcommand{\arraystretch}{2.0}
+% \renewcommand{\arraystretch}{2.0}
 
@@
 \begin{aligned}
--(\bbeta u-\bsigma,\nabla v)_K+((\bbeta
-u-\bsigma)\cdot\mathbf{n},v)_{\partial K}&=(f,v)_K\\
-\frac{1}{\epsilon}(\bsigma,\btau)_K+(u,\nabla\cdot\btau)_K
+-(\bbeta u-\bfsigma,\nabla v)_K+((\bbeta
+u-\bfsigma)\cdot\mathbf{n},v)_{\partial K}&=(f,v)_K\\
+\frac{1}{\epsilon}(\bfsigma,\btau)_K+(u,\nabla\cdot\btau)_K
 -(u,\tau_n)_{\partial K}&=0\,.
@@
 continuous trial functions). Thus, we seek field variables $u\in L^2(K)$ and
-$\bsigma\in\mb{L^2}(K)$. Mathematically, this leaves their traces on element
+$\bfsigma\in\mb{L^2}(K)$. Mathematically, this leaves their traces on element
 boundaries undefined, and in a manner similar to the hybridized discontinuous
@@
 Find
-$\bs u:=(u,\bsigma,\hat u,\hat t)
+$\bs u:=(u,\bfsigma,\hat u,\hat t)
 \in\bs U:=L^2(\Omega_h)\times \bs L^2(\Omega_h)\times H^{1/2}(\Gamma_h)\times H^{-1/2}(\Gamma_h)$
@@
 \label{eq:variationalFormulation}
-\underbrace{-(\bbeta u-\bsigma,\nabla v)_K+(\hat t,v)_{\partial K}
-+ \frac{1}{\epsilon}(\bsigma,\btau)_K
+\underbrace{-(\bbeta u-\bfsigma,\nabla v)_K+(\hat t,v)_{\partial K}
++ \frac{1}{\epsilon}(\bfsigma,\btau)_K
 +(u,\nabla\cdot\btau)_K
@@
 L^2(\Omega_h)\times H^{\frac{1}{2}}(\Gamma_h)\times H^{-\frac{1}{2}}(\Gamma_h)$
-be a finite-dimensional subspace, and let $\bs u_h:=(u_h.\bsigma_h,\hat
+be a finite-dimensional subspace, and let $\bs u_h:=(u_h.\bfsigma_h,\hat
 u_h\hat t_h)\in\bs U_h$ be a group variable. The element conservative DPG scheme is
@@
 \begin{array}[c]{rll}
--(\bbeta u-\bsigma,\nabla \vdeltau)+\langle\hat t,\vdeltau\rangle
-+ \frac{1}{\epsilon}(\bsigma,\taudeltau)
+-(\bbeta u-\bfsigma,\nabla \vdeltau)+\langle\hat t,\vdeltau\rangle
++ \frac{1}{\epsilon}(\bfsigma,\taudeltau)
 +(u,\nabla\cdot\taudeltau)
@@
 
-\section{Robust test norms}
+\subsection{Robust test norms}
 The optimal test functions are determined by solving local problems determined
@@
 
-\subsection{A model problem}
+\subsubsection{A model problem}
 \seclab{sec:confusionPlate}
@@
 $x^{-\frac{1}{2}}$).  Apart from the oscillation of $u$ at the singular point,
-the solution is well-behaved, and the stress $\bsigma = \epsilon \Grad u$ is
+the solution is well-behaved, and the stress $\bfsigma = \epsilon \Grad u$ is
 very well represented, as indicated in Figure~\ref{fig:plateStresses}.
@@
 
-\subsection{A modification of the robust test norm}
+\subsubsection{A modification of the robust test norm}
 
@@
 of the test norm.  Previous example problems exhibited boundary layers and
-sharp gradients in the stress $\bsigma$, but not singularities, which
+sharp gradients in the stress $\bfsigma$, but not singularities, which
 contribute significantly more error.  We expect that the oscillations observed
 in $u$ are a sort of \textit{pollution error}, where error in $u$ is tied to
-error in $\bsigma$.  If we consider the ultra-weak variational formulation for
+error in $\bfsigma$.  If we consider the ultra-weak variational formulation for
 convection-diffusion
 \[
-\LRp{u,\div \btau - \bbeta\cdot \grad v}_{\L} + \LRp{\bsigma,\frac{1}{\epsilon}
+\LRp{u,\div \btau - \bbeta\cdot \grad v}_{\L} + \LRp{\bfsigma,\frac{1}{\epsilon}
 \btau + \grad v}_{\L} + \ldots,
@@
 we can see that it is a combination of test functions that corresponds to both
-$u$ and $\bsigma$.  Referring to \cite{ChanHeuerThanhDemkowicz2012}, we note
+$u$ and $\bfsigma$.  Referring to \cite{ChanHeuerThanhDemkowicz2012}, we note
 that, by choosing $\btau$
 and $v$ such that they satisfy the adjoint equation with forcing terms $u$ and
-$\bsigma$, we recover the best $L^2$ approximation.  In other words, achieving
+$\bfsigma$, we recover the best $L^2$ approximation.  In other words, achieving
 optimality in the $L^2$ norm requires coupling between $v$ and $\btau$, which
@@
 previous section.
-If coupling of the test terms delivers optimality in $u$ and $\bsigma$
+If coupling of the test terms delivers optimality in $u$ and $\bfsigma$
 independently, we expect that decoupling
 $v$ and $\btau$ from each other in a test norm will have the
-effect of coupling error in $\bsigma$ to error in $u$, which would explain the
-spurious oscillations in $u$ in the presence of singularities in $\bsigma$.
+effect of coupling error in $\bfsigma$ to error in $u$, which would explain the
+spurious oscillations in $u$ in the presence of singularities in $\bfsigma$.
 Similar results have been observed in the Stokes equations, where error in $u$
@@
 that the new test norm removes spurious oscillations in $u$ (in the presence
-of singularities in $\bsigma$) independently of $\epsilon$.
+of singularities in $\bfsigma$) independently of $\epsilon$.
 
@@
 
-\subsection{Adaptation for a Locally Conservative Formulation}
+\subsubsection{Adaptation for a Locally Conservative Formulation}
 With this choice of test norm, our local problem now becomes:
@@
 
+\section{Application to Other Fluid Model Problems}
+Extension of these ideas to other fluid flow problems is relatively trivial.
+For the following problems, we just use the graph norm for the local problems.
+
+\subsection{Inviscid Burgers' Equation}
+The inviscid Burger's equation is
+\[
+\frac{\partial u}{\partial t}+u\frac{\partial u}{\partial x}=f\,.
+\]
+Define the space-time gradient: $\Grad_{xt}=\LRp{\frac{\partial}{\partial
+x},\frac{\partial}{\partial t}}^T$. We can now rewrite this as
+\[
+\vecttwo{u}{1}\cdot\Grad_{xt}u=0\,.
+\]
+Multiplying by a test function $v$, and integrating by parts:
+\[
+-\LRp{\vecttwo{u}{1}u,\Grad_{xt}v}+\LRa{\hat t,v}=\LRp{f,v}\,,
+\]
+where $\hat t$ is the trace of $\vecttwo{u^2}{u}\cdot\mathbf{n}_{xt}$ on
+element boundaries, and $\mathbf{n}_{xt}$ is the space-time normal vector.
+As in convection-diffusion, local conservation implies that
+$\int_{\partial K}\hat t=\int_Kf$ for all elements, $K$.
+
+In order to solve this nonlinear problem, we linearize and do a simple Newton iteration
+until the solution converges. The results follow in Section \ref{sec:inviscidBurgers}.
+
+\subsection{Stokes Flow}
+We start with the VGP (velocity, gradient pressure) Stokes formulation:
+\begin{align*}
+   \mu\Delta \bfu+\Grad p&=\bff\\
+   \Div\bfu&=0\,,
+\end{align*}
+where $\bfu$ is the velocity vector field.
+% For the following discussion, we let $\mu=1$, though this is by no means
+% essential.
+As a first order system of equations, this is
+\begin{align*}
+   \frac{1}{\mu}\bfsigma-\Grad\bfu&=0\\
+   \Div\bfsigma+\Grad p&=\bff\\
+   \Div\bfu&=0\,,
+\end{align*}
+where $\bfsigma$ is a tensor valued stress field.
+Multiplying by test functions $\bftau$ (tensor valued), $\bfv$ (vector
+valued), and $q$ (scalar valued), and integrating by parts:
+\begin{align*}
+   \LRp{\frac{1}{\mu}\bfsigma,\bftau}+\LRp{\bfu,\Div\bftau}-\LRa{\hat
+   \bfu,\bftau\cdot\mathbf{n}}&=0\\
+   -\LRp{\bfsigma,\Grad\bfv}-\LRp{p,\Div\bfv}+\LRa{\hat \bft,\bfv}&=\LRp{\bff,\bfv}\\
+   -\LRp{\bfu,\Grad q}+\LRa{\hat\bfu\cdot\mathbf{n},q}&=0\,,
+\end{align*}
+where $\hat\bfu$ is the trace of $\bfu$, and $\hat\bft$ is the trace of
+$\LRp{\bfsigma+p\mathbf{I}}\cdot\mathbf{n}$. The solve for $p$ is only unique
+up to a constant, so we also impose a zero mean condition, $\int_\Omega p=0$.
+Local conservation for Stokes flow means that over each element,
+$\int_K\hat\bfu\cdot\mathbf{n}=0$. Results follow in Sections
+\ref{sec:stokesCylinder} and \ref{sec:stokesStep}.
+
 \section{Numerical Experiments}
@@
 \ref{sec:problemAnalysis} we discuss the solution properties in general. We
-solve with second order field variables and flux ($u$, $\bsigma$, and $\hat
+solve with second order field variables and flux ($u$, $\bfsigma$, and $\hat
 t$), third order traces ($\hat t$), and fifth order test functions ($v$ and
@@
 Unless otherwise noted, the problem domain is $\Omega=[0,1]^2$ and $f=0$. Also
-note that except for the discontinuous source problem, for all of the
+note that unless otherwise noted, for all of the
 pseudo-color plots, blue corresponds to $0$ and red to $1$ with a linear
-scaling in between. Also, all plots are of the field variable $u$.
+scaling in between. Also, all convection-diffusion plots are of the field variable $u$.
+Inviscid Burgers' and Stokes results will be dealt with individually.
 
@@
 \label{fig:hemker8}
+\end{figure}
+
+\subsubsection{Inviscid Burgers' Equation}\label{sec:inviscidBurgers}
+
+\subsubsection{Stokes Flow Around a Cylinder}\label{sec:stokesCylinder}
+This is a common problem used to stress-test local conservation properties of
+least squares finite element methods. Since DPG can be viewed as a generalized
+least squares methods\cite{DPGOverview}, we might expect it to struggle with
+this problem as well. The problem domain is detailed in
+Figure~\ref{fig:stokesCylinderDomain} with inlet and outlet velocity profiles
+\[
+\bfu_{in}=\bfu_{out}=\vecttwo{(1-y)(1+y)}{0}\,,
+\]
+and zero flow on the cylinder and at the top and bottom walls. We use $\mu=$
+with both Stokes problems.
+
+We measure mass loss much more directly in these two Stokes problems. Because
+fluid enters and leaves the domain only through the inlet and outlet
+boundaries, we should be able to integrate the mass flux over any
+cross-section of the mesh and get the same value. Unfortunately, it's not
+mathematically kosher to take line integrals of our field variables which only
+live in $L^2$. We can, however, integrate the flux over element boundaries.
+This carries the unfortunate limitation that we can only measure mass loss
+where there is a clear vertical mesh line. We therefore pick integration lines
+from the initial coarse mesh and measure the mass flux after each adaptive refinement
+step. The percent mass loss is thus
+\[
+\%m_{loss}=\frac{\int_{\Gamma_{in}}\bfu\cdot\bfn_{in}d\ell-\int_S\bfu\cdot\bfn_Sd\ell}
+{\int_{\Gamma_{in}}\bfu\cdot\bfn_{in}d\ell}\times100.
+\]
+
+\begin{figure}[p]
+\centering
+\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=2.5cm,y=2.5cm]
+\clip(-1.97,-1.48) rectangle (3.39,1.55);
+\draw(0,0) circle (1.5cm);
+\draw (-1,-1)-- (3,-1);
+\draw (3,1)-- (3,-1);
+\draw (-1,1)-- (3,1);
+\draw (-1,1)-- (-1,-1);
+\draw (0,0)-- (.3,0.5196);
+\draw (0.12,0.29) node[anchor=north west] {r};
+\draw (-1.3,-1.0) node[anchor=north west] {-1.0};
+\draw (-1.3,1.15) node[anchor=north west] {1.0};
+\draw (-1.3,0.0) node[anchor=north west] {$u_{in}$};
+\draw (0.6,0.0) node[anchor=north west] {$u_{cyl}$};
+\draw (3.0,-1.0) node[anchor=north west] {3.0};
+\draw (3.0,0.0) node[anchor=north west] {$u_{out}$};
+\draw (0.9,-1.03) node[anchor=north west] {$u_{wall}$};
+\draw (0.9,1.17) node[anchor=north west] {$u_{wall}$};
+\end{tikzpicture}
+\caption{Stokes cylinder domain}
+\label{fig:stokesCylinderDomain}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\begin{subfigure}[t]{0.5\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/StokesCylinder/umag9_NC0.png}
+\caption{Nonconservative on initial mesh}
+\end{subfigure}
+\begin{subfigure}[t]{0.5\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/StokesCylinder/umag9_C0.png}
+\caption{Conservative on initial mesh}
+\end{subfigure}
+\begin{subfigure}[t]{0.5\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/StokesCylinder/umag9_NC6.png}
+\caption{Nonconservative after 6 refinement steps}
+\label{fig:stokesCylinderNC}
+\end{subfigure}
+\begin{subfigure}[t]{0.5\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/StokesCylinder/umag9_C6.png}
+\caption{Conservative after 6 refinement steps}
+\label{fig:stokesCylinderC}
+\end{subfigure}
+\caption{Stokes flow around a cylinder - velocity magnitude}
+\label{fig:stokesCylinder}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/StokesCylinder/MassLoss9_NC.pdf}
+\caption{Mass loss in Stokes flow around a cylinder - nonconservative DPG}
+\label{fig:stokesCylinderMassLossNC}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/StokesCylinder/MassLoss9_C.pdf}
+\caption{Mass loss in Stokes flow around a cylinder - conservative DPG}
+\label{fig:stokesCylinderMassLossC}
+\end{figure}
+
+\subsubsection{Stokes Flow Over a Backward Facing Step}\label{sec:stokesStep}
+Similarly, least squares methods have historically performed very poorly when
+calculating Stokes flow over a backward facing step. The stress singularity at
+the reentrant corner, in particular, seems to destroy local conservation. We
+assign parabolic inlet and outlet velocity boundary conditions
+\[
+\bfu_{in}=\vecttwo{8(y-0.5)(1-y)}{0}
+\quad\text{ and }\quad
+\bfu_{out}=\vecttwo{y(1-y)}{0}
+\]
+and zero velocity on all other boundaries.
+
+\begin{figure}[p]
+\centering
+\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1.3cm,y=1.3cm]
+\clip(-0.5,-0.3) rectangle (10.67,5);
+\draw [line width=1.0pt] (0,0.5)-- (2,0.5);
+\draw [line width=1.0pt] (2,0.5)-- (2,0);
+\draw [line width=1.0pt] (10,0)-- (2,0);
+\draw [line width=1.0pt] (10,1)-- (10,0);
+\draw [line width=1.0pt] (0,1)-- (10,1);
+\draw [line width=1.0pt] (0,0.5)-- (0,1);
+\draw (-0.6,0.6) node[anchor=north west] {0.5};
+\draw (-0.6,1.3) node[anchor=north west] {1.0};
+\draw (1.4,0.2) node[anchor=north west] {2.0};
+\draw (10.0,0.2) node[anchor=north west] {10.0};
+\draw (0.0,0.92) node[anchor=north west] {$u_{in}$};
+\draw (10.0,0.7) node[anchor=north west] {$u_{out}$};
+\draw (5.0,0.0) node[anchor=north west] {$u_{wall}$};
+\draw (5.0,1.35) node[anchor=north west] {$u_{wall}$};
+\end{tikzpicture}
+\caption{Stokes step domain}
+\label{fig:stokesStepDomain}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\begin{subfigure}[t]{0.8\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/StokesStep/Quartic_NC0.png}
+\caption{Nonconservative on initial mesh}
+\end{subfigure}
+\begin{subfigure}[t]{0.8\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/StokesStep/Quartic_C0.png}
+\caption{Conservative on initial mesh}
+\end{subfigure}
+\begin{subfigure}[t]{0.8\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/StokesStep/Quartic_NC8.png}
+\caption{Nonconservative after 8 refinement steps}
+\label{fig:stokesStepNC}
+\end{subfigure}
+\begin{subfigure}[t]{0.8\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/StokesStep/Quartic_C8.png}
+\caption{Conservative after 8 refinement steps}
+\label{fig:stokesStepC}
+\end{subfigure}
+\caption{Stokes backward facing step - velocity magnitude}
+\label{fig:stokesStep}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/StokesStep/MassLoss_NC.pdf}
+\caption{Mass loss in Stokes backward facing step - nonconservative DPG}
+\label{fig:stokesStepMassLossNC}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/StokesStep/MassLoss_C.pdf}
+\caption{Mass loss in Stokes backward facing step - conservative DPG}
+\label{fig:stokesStepMassLossC}
 \end{figure}

### 2013-11-18 docs/Truman/LocalConservation/paper/paper.tex
Added Stokes and Burgers results to local conservation paper.

@@
 \end{quote}
+There are also some mathematically attractive reasons to pursue local
+conservation. The Lax-Wendroff theorem guarantees that a convergent numerical
+solution to a system of hyperbolic conservation laws will converge to the
+correct weak solution.
 
@@
 \subsection{Inviscid Burgers' Equation}
+We include the inviscid Burgers' equation in our suite of tests because, being
+a nonlinear hyperbolic conservation law, it
+falls under the purvue of the Lax-Wendroff theorem.
 The inviscid Burger's equation is
@@
 \[
-\vecttwo{u}{1}\cdot\Grad_{xt}u=0\,.
+\Grad_{xt}\cdot\vecttwo{u^2/2}{u}=0\,.
 \]
@@
 \[
--\LRp{\vecttwo{u}{1}u,\Grad_{xt}v}+\LRa{\hat t,v}=\LRp{f,v}\,,
-\]
-where $\hat t$ is the trace of $\vecttwo{u^2}{u}\cdot\mathbf{n}_{xt}$ on
+-\LRp{\vecttwo{u^2/2}{u},\Grad_{xt}v}+\LRa{\hat t,v}=\LRp{f,v}\,,
+\]
+where $\hat t$ is the trace of $\vecttwo{u^2/2}{u}\cdot\mathbf{n}_{xt}$ on
 element boundaries, and $\mathbf{n}_{xt}$ is the space-time normal vector.
@@
 In order to solve this nonlinear problem, we linearize and do a simple Newton iteration
-until the solution converges. The results follow in Section \ref{sec:inviscidBurgers}.
+until the solution converges. The linearized equation is
+\[
+-\LRp{\vecttwo{u}{1}\Delta u,\Grad_{xt}v}+\LRa{\hat t,v}=\LRp{f,v}
++\LRp{\vecttwo{u^2/2}{u},\Grad_{xt}v} \,,
+\]
+where $u$ is the previous solution iteration and $\Delta u$ is the update.
+The results follow in Section \ref{sec:inviscidBurgers}.
 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{figs/Erickson/graphFlux.pdf}
+\includegraphics[width=0.8\textwidth]{figs/Erickson/modifiedFlux.pdf}
 \caption{Flux imbalance in Erickson-Johnson solutions}
@@
 \centering
-\includegraphics[width=\textwidth]{figs/Discontinuous/graph8nc.png}
+\includegraphics[width=\textwidth]{figs/Discontinuous/modified8nc.png}
 \caption{Nonconservative}
@@
 \centering
-\includegraphics[width=\textwidth]{figs/Discontinuous/robust8nc.png}
+\includegraphics[width=\textwidth]{figs/Discontinuous/modified8c.png}
 \caption{Conservative}
@@
 \subsubsection{Inviscid Burgers' Equation}\label{sec:inviscidBurgers}
+This is a standard test problem for Burgers' equation. The domain is a unit
+square. We assign boundary conditions $\hat t=-(1-2x)$ on the bottom, $\hat
+t=-1/2$ on the left, while $\hat t=1/2$ on the right. Since this is a
+hyperbolic equation, there is no need to set a boundary condition on the top.
+
+\begin{figure}[p]
+\centering
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Burgers/graph8nc.png}
+\caption{Nonconservative}
+\label{fig:burgers8nc}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/Burgers/graph8c.png}
+\caption{Conservative}
+\label{fig:burgers8c}
+\end{subfigure}
+\caption{Burgers' problem after 8 refinements}
+\label{fig:burgers}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/Burgers/graphFlux.pdf}
+\caption{Flux imbalance in Burgers' solutions}
+\label{fig:burgers_flux}
+\end{figure}
 
@@
 and zero flow on the cylinder and at the top and bottom walls. We use $\mu=$
-with both Stokes problems.
+with both Stokes problems and set velocity boundary conditions on $\hat\bfu$.
+
+Bochev \etal~\cite{Bochev2010} run this test with both $r=0.6$ and $r=0.9$; we
+repeat the same experiments with standard and locally conservative DPG methods
+starting from the very coarse meshes shown in Figure~\ref{fig:stokesMesh}
+while adaptively refining toward a resolved solution. The extreme pressure
+gradient in the $r=0.9$ case obviously makes local conservation more
+challenging.
 
@@
 mathematically kosher to take line integrals of our field variables which only
-live in $L^2$. We can, however, integrate the flux over element boundaries.
+live in $L^2$. We can, however, integrate the trace and flux variables over element boundaries.
 This carries the unfortunate limitation that we can only measure mass loss
@@
 \%m_{loss}=\frac{\int_{\Gamma_{in}}\bfu\cdot\bfn_{in}d\ell-\int_S\bfu\cdot\bfn_Sd\ell}
-{\int_{\Gamma_{in}}\bfu\cdot\bfn_{in}d\ell}\times100.
-\]
+{\int_{\Gamma_{in}}\bfu\cdot\bfn_{in}d\ell}\times100,
+\]
+where $S$ is some vertical mesh line.
 
@@
 \centering
+\begin{subfigure}[t]{0.6\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/StokesCylinder/mesh6_0.png}
+\caption{Mesh for $r=0.6$}
+\label{fig:stokesMesh6}
+\end{subfigure}
+\begin{subfigure}[t]{0.6\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/StokesCylinder/mesh9_0.png}
+\caption{Mesh for $r=0.9$}
+\label{fig:stokesMesh9}
+\end{subfigure}
+\caption{Initial mesh for Stokes flow over a cylinder}
+\label{fig:stokesMesh}
+\end{figure}
+
+\begin{figure}[p]
+\centering
 \begin{subfigure}[t]{0.5\textwidth}
 \centering
-\includegraphics[width=\textwidth]{figs/StokesCylinder/umag9_NC0.png}
-\caption{Nonconservative on initial mesh}
+\includegraphics[width=\textwidth]{figs/StokesCylinder/umag6_NC6.png}
+\caption{Nonconservative with $r=0.6$}
+\label{fig:stokesCylinderNC6}
 \end{subfigure}
@@
 \centering
-\includegraphics[width=\textwidth]{figs/StokesCylinder/umag9_C0.png}
-\caption{Conservative on initial mesh}
+\includegraphics[width=\textwidth]{figs/StokesCylinder/umag6_C6.png}
+\caption{Conservative with $r=0.6$}
+\label{fig:stokesCylinderC6}
 \end{subfigure}
@@
 \includegraphics[width=\textwidth]{figs/StokesCylinder/umag9_NC6.png}
-\caption{Nonconservative after 6 refinement steps}
-\label{fig:stokesCylinderNC}
+\caption{Nonconservative with $r=0.9$}
+\label{fig:stokesCylinderNC9}
 \end{subfigure}
@@
 \includegraphics[width=\textwidth]{figs/StokesCylinder/umag9_C6.png}
-\caption{Conservative after 6 refinement steps}
-\label{fig:stokesCylinderC}
-\end{subfigure}
-\caption{Stokes flow around a cylinder - velocity magnitude}
-\label{fig:stokesCylinder}
-\end{figure}
-
-\begin{figure}[p]
-\centering
-\includegraphics[width=0.8\textwidth]{figs/StokesCylinder/MassLoss9_NC.pdf}
-\caption{Mass loss in Stokes flow around a cylinder - nonconservative DPG}
-\label{fig:stokesCylinderMassLossNC}
-\end{figure}
-
-\begin{figure}[p]
-\centering
-\includegraphics[width=0.8\textwidth]{figs/StokesCylinder/MassLoss9_C.pdf}
-\caption{Mass loss in Stokes flow around a cylinder - conservative DPG}
-\label{fig:stokesCylinderMassLossC}
+\caption{Conservative with $r=0.9$}
+\label{fig:stokesCylinderC9}
+\end{subfigure}
+\caption{Stokes flow around a cylinder after 6 refinement steps - velocity magnitude}
+\label{fig:stokesCylinder9}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\begin{subfigure}[t]{0.8\textwidth}
+\includegraphics[width=\textwidth]{figs/StokesCylinder/MassLoss6_NC.pdf}
+\caption{Nonconservative}
+\label{fig:stokesCylinder6MassLossNC}
+\end{subfigure}
+\begin{subfigure}[t]{0.8\textwidth}
+\includegraphics[width=\textwidth]{figs/StokesCylinder/MassLoss6_C.pdf}
+\caption{Conservative}
+\label{fig:stokesCylinder6MassLossC}
+\end{subfigure}
+\caption{Mass loss in Stokes flow around a cylinder of radius $0.6$}
+\label{fig:stokesCylinder6MassLoss}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\begin{subfigure}[t]{0.8\textwidth}
+\includegraphics[width=\textwidth]{figs/StokesCylinder/MassLoss9_NC.pdf}
+\caption{Nonconservative}
+\label{fig:stokesCylinder9MassLossNC}
+\end{subfigure}
+\begin{subfigure}[t]{0.8\textwidth}
+\includegraphics[width=\textwidth]{figs/StokesCylinder/MassLoss9_C.pdf}
+\caption{Conservative}
+\label{fig:stokesCylinder9MassLossC}
+\end{subfigure}
+\caption{Mass loss in Stokes flow around a cylinder of radius $0.9$}
+\label{fig:stokesCylinder9MassLoss}
 \end{figure}
@@
 \]
-and zero velocity on all other boundaries.
+and zero velocity on all other boundaries. In this problem, we solve with
+fourth order field and flux variables, fifth order traces, and sixth order
+test functions.
 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{figs/StokesStep/MassLoss_NC.pdf}
-\caption{Mass loss in Stokes backward facing step - nonconservative DPG}
+\begin{subfigure}[t]{0.8\textwidth}
+\includegraphics[width=\textwidth]{figs/StokesStep/MassLoss_NC.pdf}
+\caption{Nonconservative DPG}
 \label{fig:stokesStepMassLossNC}
-\end{figure}
-
-\begin{figure}[p]
-\centering
-\includegraphics[width=0.8\textwidth]{figs/StokesStep/MassLoss_C.pdf}
-\caption{Mass loss in Stokes backward facing step - conservative DPG}
+\end{subfigure}
+\begin{subfigure}[t]{0.8\textwidth}
+\includegraphics[width=\textwidth]{figs/StokesStep/MassLoss_C.pdf}
+\caption{Conservative DPG}
 \label{fig:stokesStepMassLossC}
+\end{subfigure}
+\caption{Mass loss in Stokes backward facing step}
+\label{fig:stokesStepMassLoss}
 \end{figure}
@@
 \subsection{Analysis of Results}\label{sec:problemAnalysis}
+\subsubsection{Convection-Diffusion Results}
 % Solution quality
 The general trend we see looking at the results is that the solution quality
-of the conservative and nonconservative formulations is nearly identical. This
+of the conservative and nonconservative formulations is nearly identical once
+sufficiently resolved. This
 is ideal, as we wish to preserve the attractive features of DPG --
@@
 Another measure of solution quality is to look at the magnitude of overshoots
-and undershoots in the solution. In most of the problems considered (barring
+and undershoots in the solution. In most of the convection-diffusion problems considered (barring
 the discontinuous source problem) the exact solution would range exactly
@@
 nonconservative formulation, the solution range for $u$ was $[-0.392,1.342]$,
-while the conservative solution range was $[0.389,1.378]$. This difference is
+while the conservative solution range was $[-0.389,1.378]$. This difference is
 easily accounted for by the differences in refinement patterns between the two
@@
 
+\subsubsection{Burgers' Results}
+Standard and locally conservative DPG perform nearly identically for the
+inviscid Burgers' problem. It's obvious that the Lax-Wendroff condition of
+local conservation is a sufficient, but not necessary condition for numerical
+solutions to hyperbolic conservation laws. We see the same behavior with the
+flux imbalance plots that was so common with convection-diffusion.
+
+\subsubsection{Stokes Results}
+The two Stokes problems are the first ones we encounter that really stress the local
+conservation property of standard DPG. With a cylinder radius of $0.6$,
+standard DPG loses nearly 30\% of the mass post-cylinder, but quickly recovers
+most of that with further refinement. As we increase the cylinder radius to
+$0.9$, the problem only exacerbates. Nearly 100\% of the mass is lost in the
+constricted region on coarse meshes. It takes a much higher level of
+resolution to recover the mass loss. The stress singularity at the reentrant
+corner of the backward facing step causes issues for standard DPG on coarse
+meshes. It seems that the error in approximating the singularity outweighs the
+error of missed mass conservation. If we focus refinements at the singularity,
+the error eventually drops far enough for the method to become nearly
+conservative.
+The small amount of mass loss for the conservative method is clearly due to
+accumulation of floating point error.
+
 \section{Conclusions}
 We've developed a locally conservative formulation of DPG by leveraging
-Lagrange multipliers. While the formulation is provably convergent, it does
+Lagrange multipliers. While the formulation is provably convergent and robust, it does
 increase the number of unkowns in the system and changes the structure from
@@
 indicate that the method delivers what it promises with local flux imbalances
-hovering close to machine precision, but they also indicate that for the
+hovering close to machine precision, but they also indicate that for most of the
 problems considered, standard DPG is close to conservative and becomes more so
-with refinements. Probably the most encouraging result of these experiments is
+with refinements. For the Stokes problems, standard DPG suffered similar mass
+loss as standard least squares on coarse meshes, but made up the lost mass with further
+resolution.
+Probably the most encouraging result of these experiments is
 that enforcing local conservation did not change the nature of the solutions
 too significantly. Standard DPG has a lot of attractive features, and we wish
-to preserve thoes.
-
-Mass conservation is probably the foremost issue facing the class of Least
-Squares Finite Element Methods. And there are several benchmark problems in the
-literature where these methods have performed very poorly, particularly Stokes
-flow over a cylinder and the backward facing step problem. Extending our locally
-conservative formulation of DPG to these kinds of problems should be
-relatively straightforward. The real test of whether local conservation is
-worth it for DPG will come when we start doing more realistic problems.
+to preserve those.
+
+% Mass conservation is probably the foremost issue facing the class of Least
+% Squares Finite Element Methods. And there are several benchmark problems in the
+% literature where these methods have performed very poorly, particularly Stokes
+% flow over a cylinder and the backward facing step problem. Extending our locally
+% conservative formulation of DPG to these kinds of problems should be
+% relatively straightforward. The real test of whether local conservation is
+% worth it for DPG will come when we start doing more realistic problems.
 

### 2013-11-19 docs/Truman/LocalConservation/paper/paper.tex
adding robustness paragraph by jesse

@@
 
+% jesse robustness section
+
+We note that, for convection-diffusion problems, we are particularly interested in designing a \textit{robust} DPG method.
+Specifically, we are interested in designing methods whose behavior does not change as the diffusion parameter $\epsilon$ becomes very small.
+Naive Galerkin methods for convection-diffusion tend to suffer from a lack of robustness; specifically, the finite element error is bounded by a constant factor of the best approximation error, but the constant is often proportional to $\epsilon^{-1}$.
+Our aim is to design a DPG method with this in mind.
+We follow the methodology introduced by Heuer and Demkowicz in \cite{DemkowiczHeuer}: the ultra-weak variational formulation for convection-diffusion can be refactored as
+\[
+b\LRp{\LRp{u,\sigma,\uh,\fnh},\LRp{\tau,v}} = \sum_{K\in \Oh}\LRs{\LRa{\fnh,v}_{\delta K} + \LRa{\uh,\tau_n}_{\delta K} + \LRp{u,\div \tau - \beta\cdot\grad v}_{L^2(K)} + \LRp{\sigma,\frac{1}{\epsilon} \tau + \grad v}_{L^2(K)}},
+\]
+modulo application of boundary data.  If we choose specific \textit{conforming} test functions satisfying the adjoint equations
+\begin{align*}
+\div \tau - \beta \cdot \grad v &= u,\\
+\frac{1}{\epsilon} \tau + \grad v &= \sigma,
+\end{align*}
+then evaluating $b\LRp{\LRp{u,\sigma,\uh,\fnh},\LRp{\tau,v}}$ at these specific test functions returns back $\norm{u}^2 + \norm{\sigma}^2$, the $L^2$ norm of our field variables.
+Multiplying and dividing through by the test norm $\norm{v}_V$, we have
+\[
+\norm{u}_{\L}^2 + \norm{\sigma}_{\L}^2 = b\LRp{\LRp{u,\sigma,\uh,\fnh},\LRp{\tau,v}} = \frac{b\LRp{\LRp{u,\sigma,\uh,\fnh},\LRp{\tau,v}}}{\norm{v}_V}\norm{v}_V \leq \norm{u,\sigma,\uh,\fnh}_E\norm{v}_V,
+\]
+where 
+\[
+\norm{u,\sigma,\uh,\fnh}_E = \sup_{v\in V\setminus\LRc{0}}\frac{b\LRp{\LRp{u,\sigma,\uh,\fnh},\LRp{\tau,v}}}{\norm{v}_V}
+\]
+is the DPG energy norm.
+If we can robustly bound the test norm $\norm{v}_V \lesssim \LRp{\norm{u}_{\L}^2+\norm{\sigma}^2_{\L}}^{1/2}$ (i.e.
+derive a bound from above with a constant independent of $\epsilon$), then we can divide through to get
+\[
+\LRp{\norm{u}_{\L}^2 + \norm{\sigma}_{\L}^2}^{\frac{1}{2}} \lesssim \norm{u,\sigma,\uh,\fnh}_E.
+\]
+In other words, the energy norm in which DPG is optimal bounds independently of $\epsilon$ the $L^2$ norm; as we drive our energy error down to zero, we can expect that the $L^2$ error will also decrease regardless of $\epsilon$.
+
+We note that the construction of the test norm $\norm{v}_V$ for a robust DPG method depends on two things: the test norm, as well as the adjoint equation.
+In \cite{DemkowiczHeuer}, the standard problem with Dirichlet conditions enforced over the entire boundary was considered; in \cite{ChanHeuerThanhDemkowicz2012}, boundary conditions were chosen for the forward problem such that the induced adjoint problem was regularized and contained no strong boundary layers, allowing for the construction of a stronger test norm on $V$.
+We adopt a slight modification of the test norm introduced in \cite{ChanHeuerThanhDemkowicz2012} for numerical experiments here, which is motivated and explained in more detail in Section~\secref{sec:confusionPlate}.
+
+Having reviewed and laid the foundation for DPG methods, we can now formulate our conservative DPG scheme.  % added by Jesse
 Let $\bs U_h:=U_h\times\bs S_h\times\hat U_h\times\hat F_h\subset L^2(\Omega_h)\times\bs

### 2013-11-19 docs/Truman/LocalConservation/paper/paper.tex
More updates to local conservation paper

--- 2013-11-18 docs/Truman/LocalConservation/paper/paper.tex
@@
 show that standard DPG, while not guaranteed to be conservative, is nearly
-conservative for the benchmarks considered. The new method preserves many of
+conservative for many of the benchmarks considered. The new method preserves many of
 the attractive features of DPG, but turns the normally symmetric
@@
 both methods share similar negative of transforming a minimization method to a
-saddle-point problem.
+saddle-point problem. In the interest of crediting Chang and Nelson's
+restricted LSFEM, we call the following locally conservative DPG method the
+restricted DPG method (RDPG).
 
@@
 be a finite-dimensional subspace, and let $\bs u_h:=(u_h.\bfsigma_h,\hat
-u_h\hat t_h)\in\bs U_h$ be a group variable. The element conservative DPG scheme is
+u_h\hat t_h)\in\bs U_h$ be the group variable. The element conservative DPG scheme is
 derived from the Lagrangian:
@@
 
+Denote $T(\delta\bfu_h)=\LRp{\vdeltau,\taudeltau}\in
+H^1(\Omega_h)\times\bfH(div,\Omega_h)$.
 Then, putting \eqref{eq:conservativeSystem} into more concrete terms for
@@
 R\, : \, L^2(\Omega) \ni q \to \bfv \in \bfH(\text{div},\Omega) \cap \bfH^1(\Omega)
+=\bfH^1
 \end{equation}
@@
 \sup_{v \in V_0} \frac{\vert a(u,v) \vert}{\Vert v \Vert_V }
- \geq \frac{\vert b(\bfu,T \bfu) \vert}{\Vert T \bfu \Vert}
+ \geq \frac{\vert b(\bfu,T \bfu) \vert}{\Vert \bfu \Vert}
 = \sup_{(v,\bftau)}
 \frac{\vert b((u,\bfsig,\hat{u},\hat{t}), (v,\bftau)) \vert}{\Vert (v,\bftau) \Vert}
-\geq \gamma \Vert (u,\bfsig,\hat{u},\hat{t}) \Vert
+\geq \gamma^2 \Vert (u,\bfsig,\hat{u},\hat{t}) \Vert
 \end{equation}
@@
 
-Recall the main line of analysis in \cite{} leading to the construction of robust
+Recall the main line of analysis in {\color{red}(supposed to be Brezzi?)}\cite{} leading to the construction of robust
 test norms. With the robust test norms, we have
@@
 \begin{array}{ll}
-\Vert u - u_h \Vert, \Vert \bfsig - \bfsig_h \Vert
+   \LRp{\Vert u - u_h \Vert^2+ \Vert \bfsig - \bfsig_h
+   \Vert^2}^{\frac{1}{2}}
 & \lesssim \Vert (u - u_h, \bfsig - \bfsig_h, \hat{u} - \hat{u}_h, \hat{t} - \hat{t}_h \Vert_E \\[8pt]
@@
 error in the energy norm (minimizes the residual). This is not longer true for the
-conservative version. So, can we claim the robustness in the sense of the inequality above
-for the conservative version as well ?
+restricted version. So, can we claim the robustness in the sense of the inequality above
+for the restricted version as well?
 
@@
 $$
-Substituting $v$ for $\delta v$ in~(\ref{eq:local}), we get,
+Substituting $(v,\bftau)$ for $(\delta v,\delta\bftau)$ in~(\ref{eq:local}), we get,
 \begin{equation}
@@
 \begin{equation}
-\Vert v \Vert_{L^2(K)} \leq \Vert v \Vert_V \, .
+\Vert v \Vert_{L^2(K)} \leq \Vert (v,\bftau) \Vert_V \, .
 \label{eq:robust_est1}
@@
 Bochev \etal~\cite{Bochev2010} run this test with both $r=0.6$ and $r=0.9$; we
-repeat the same experiments with standard and locally conservative DPG methods
+repeat the same experiments with standard and restricted DPG methods
 starting from the very coarse meshes shown in Figure~\ref{fig:stokesMesh}
@@
 Similarly, least squares methods have historically performed very poorly when
-calculating Stokes flow over a backward facing step. The stress singularity at
-the reentrant corner, in particular, seems to destroy local conservation. We
+calculating Stokes flow over a backward facing step shown in
+Figure~\ref{fig:stokesStepDomain}. The stress singularity at
+the reentrant corner seems to destroy local conservation. We
 assign parabolic inlet and outlet velocity boundary conditions
@@
 \includegraphics[width=\textwidth]{figs/StokesStep/MassLoss_NC.pdf}
-\caption{Nonconservative DPG}
+\caption{Nonconservative}
 \label{fig:stokesStepMassLossNC}
@@
 \includegraphics[width=\textwidth]{figs/StokesStep/MassLoss_C.pdf}
-\caption{Conservative DPG}
+\caption{Conservative}
 \label{fig:stokesStepMassLossC}
@@
 The general trend we see looking at the results is that the solution quality
-of the conservative and nonconservative formulations is nearly identical once
+of the standard and restricted formulations is nearly identical once
 sufficiently resolved. This
@@
 get overshoots and undershoots along the separation line. For the
-nonconservative formulation, the solution range for $u$ was $[-0.392,1.342]$,
-while the conservative solution range was $[-0.389,1.378]$. This difference is
+standard formulation, the solution range for $u$ was $[-0.392,1.342]$,
+while the restricted solution range was $[-0.389,1.378]$. This difference is
 easily accounted for by the differences in refinement patterns between the two
@@
 determine which elements to adaptively refine). Standard DPG minimizes the
-error in the energy norm, but the Lagrange multipliers in the conservative
+error in the energy norm, but the Lagrange multipliers in the restricted
 formulation shift the solution slightly. So we should see somewhat higher
@@
 test norm also plays into this calculation of the error representation
-function. As discussed earlier, the conservative formulation allows us to
+function. As discussed earlier, the restricted formulation allows us to
 throw away the $L^2$ term on $v$. The inclusion of this term required certain
 assumptions on $\bbeta$ \cite{ChanHeuerThanhDemkowicz2012} that break down for
-the vortex problem. Here we see the nonconservative method needlessly refines
-in the center of the domain where the solution is constant. The conservative
+the vortex problem. Here we see the standard method needlessly refines
+in the center of the domain where the solution is constant. The restricted
 scheme is more discerning about refinements and focuses them where
@@
 % Mass conservation
-It shouldn't come as a surprise that the conservative and nonconservative
-solutions match each other so closely. The conservative formulation
+It shouldn't come as a surprise that the standard and restricted
+solutions match each other so closely. The restricted formulation
 enforces local conservation more strictly, but if we examine the flux
@@
 own -- and appears to become more conservative with refinement. The flux
-imbalance of the conservative methods appears to bounce around close to the
+imbalance of the restricted methods appears to bounce around close to the
 machine epsilon (plus a few orders of magnitude). The level of enforcement
@@
 \subsubsection{Burgers' Results}
-Standard and locally conservative DPG perform nearly identically for the
+Standard and restricted DPG perform nearly identically for the
 inviscid Burgers' problem. It's obvious that the Lax-Wendroff condition of
@@
 conservative.
-The small amount of mass loss for the conservative method is clearly due to
+The small amount of mass loss for the restricted method is clearly due to
 accumulation of floating point error.

### 2013-11-19 docs/Truman/LocalConservation/paper/paper.tex
Fixed some references in local conservation paper

@@
 
-We note that, for convection-diffusion problems, we are particularly interested in designing a \textit{robust} DPG method.
-Specifically, we are interested in designing methods whose behavior does not change as the diffusion parameter $\epsilon$ becomes very small.
-Naive Galerkin methods for convection-diffusion tend to suffer from a lack of robustness; specifically, the finite element error is bounded by a constant factor of the best approximation error, but the constant is often proportional to $\epsilon^{-1}$.
-Our aim is to design a DPG method with this in mind.
-We follow the methodology introduced by Heuer and Demkowicz in \cite{DemkowiczHeuer}: the ultra-weak variational formulation for convection-diffusion can be refactored as
+We note that, for convection-diffusion problems, we are particularly
+interested in designing a \textit{robust} DPG method.  Specifically, we are
+interested in designing methods whose behavior does not change as the
+diffusion parameter $\epsilon$ becomes very small.  Naive Galerkin methods for
+convection-diffusion tend to suffer from a lack of robustness; specifically,
+the finite element error is bounded by a constant factor of the best
+approximation error, but the constant is often proportional to
+$\epsilon^{-1}$.  Our aim is to design a DPG method with this in mind.  We
+follow the methodology introduced by Heuer and Demkowicz in
+\cite{DemkowiczHeuer}: the ultra-weak variational formulation for
+convection-diffusion can be refactored as
 \[
@@
 Laplace/diffusion problem with a singularity -- in most of the domain,
-convective effects dominate; however, if we  localizing the behavior of
-Laplace's equation to a circle of $\epsilon$ around $(.5,0)$, then we again
+convective effects dominate; however, localizing the behavior of
+Laplace's equation to a circle of $\epsilon$ around $(.5,0)$, we again
 see a discontinuity in the stresses.  Asymptotic expansion techniques indicate
@@
 +\epsilon(\nabla\vdeltau,\nabla \delta v)_K
-+\frac{1}{|K|}\int_K\vdeltau\int_K\delta v
++\frac{1}{|K|^2}\int_K\vdeltau\int_K\delta v
 \label{eq:localSolveMod}
@@
 where the $\frac{1}{|K|^2}$ coefficient is needed to make the zero mean term
-scale correctly with $h$. Numerically this helps with the condition
+scale correctly since $\int_K\vdeltau$ and $\int_K\delta v$ both scale like
+$|K|$. Numerically this helps with the condition
 numbers of the local solve.
@@
 \end{equation}
-Taking $\epsilon=10^{-2}$, $C_1=1$, and $C_{n\neq1}=0$, the exact solution looks
-like Figure \ref{fig:erickson}.
+The exact solution for $\epsilon=10^{-2}$, $C_1=1$, and $C_{n\neq1}=0$ is
+shown in Figure \ref{fig:erickson}.
 
@@
 of the standard and restricted formulations is nearly identical once
-sufficiently resolved. This
-is ideal, as we wish to preserve the attractive features of DPG --
-namely that it minimizes error in the energy norm. In particular, when we
-examine the error convergence plots for the Erickson-Johnson problem, the
-energy levels for the two methods lie nearly right on top of each other. This
-seems to indicate at the least that enforcing local conservation doesn't hurt
-DPG too much.
+sufficiently resolved.
 

### 2013-11-19 docs/Truman/LocalConservation/paper/paper.tex
Minor updates to bibliography

@@
 The last equality follows from the fact that DPG method delivers the best approximation
-error in the energy norm (minimizes the residual). This is not longer true for the
-restricted version. So, can we claim the robustness in the sense of the inequality above
+error in the energy norm (minimizes the residual). This is no longer true for the
+restricted version. So, can we claim robustness in the sense of the inequality above
 for the restricted version as well?

### 2013-11-20 docs/Truman/LocalConservation/paper/paper.tex
Updated notation in local conservation paper

@@
 \documentclass[letterpaper]{article}
+%TODO: check for periods after equations
+%TODO: bold face proper variables
 \usepackage[margin=1.0in]{geometry}
@@
 \def\bfsigma{\boldsymbol\sigma}
+\def\bfvarsigma{\boldsymbol\varsigma}
 \def\bbeta{\boldsymbol\beta}
@@
 \newcommand{\bfu}{\boldsymbol u}
+\newcommand{\bfU}{\boldsymbol U}
+\newcommand{\bfV}{\boldsymbol V}
+\newcommand{\bfw}{\boldsymbol w}
 \newcommand{\bff}{\boldsymbol f}
@@
 H^\frac{1}{2}(\Gamma_h) & := \left\{ \hat{v} = \{\hat{v}_K \} \in \prod_K H^{1/2}(\ptl K) \: :
-\: \exists v \in H^1(\Omega) : v\vert_{\ptl K} = \hat{v}_K \right\}, \\[8pt]
+\: \exists v \in H^1(\Omega) : v|_{\ptl K} = \hat{v}_K \right\}, \\[8pt]
 H^{-\frac{1}{2}}(\Gamma_h) & := \left\{ {\hat{\sigma}}_n = \{ {\hat{\sigma}}_{Kn} \}\in \prod_K H^{-1/2}(\ptl K) \: : \: \exists \bfsig \in \bfH(\text{div},\Omega)
-: {\hat{\sigma}}_{Kn} = (\bfsig \cdot \bfn)\vert_{\ptl K} \right\},
+: {\hat{\sigma}}_{Kn} = (\bfsig \cdot \bfn)|_{\ptl K} \right\},
 \end{array}
@@
 \[
-b\LRp{\LRp{u,\sigma,\uh,\fnh},\LRp{\tau,v}} = \sum_{K\in \Oh}\LRs{\LRa{\fnh,v}_{\delta K} + \LRa{\uh,\tau_n}_{\delta K} + \LRp{u,\div \tau - \beta\cdot\grad v}_{L^2(K)} + \LRp{\sigma,\frac{1}{\epsilon} \tau + \grad v}_{L^2(K)}},
-\]
-modulo application of boundary data.  If we choose specific \textit{conforming} test functions satisfying the adjoint equations
+b\LRp{\LRp{u,\bfsigma,\uh,\hat t},\LRp{\bftau,v}} =
+\sum_{K\in \Oh}\LRs{\LRa{\hat t,v}_{\delta K}
++\LRa{\uh,\tau_n}_{\delta K} + \LRp{u,\div \bftau
+-\bbeta\cdot\grad v}_{L^2(K)}
++\LRp{\bfsigma,\frac{1}{\epsilon} \bftau + \grad v}_{L^2(K)}},
+\]
+modulo application of boundary data.  If we choose specific
+\textit{conforming} test functions satisfying the adjoint equations
 \begin{align*}
-\div \tau - \beta \cdot \grad v &= u,\\
-\frac{1}{\epsilon} \tau + \grad v &= \sigma,
+\div \bftau - \bbeta \cdot \grad v &= u,\\
+\frac{1}{\epsilon} \bftau + \grad v &= \bfsigma,
 \end{align*}
-then evaluating $b\LRp{\LRp{u,\sigma,\uh,\fnh},\LRp{\tau,v}}$ at these specific test functions returns back $\norm{u}^2 + \norm{\sigma}^2$, the $L^2$ norm of our field variables.
-Multiplying and dividing through by the test norm $\norm{v}_V$, we have
-\[
-\norm{u}_{\L}^2 + \norm{\sigma}_{\L}^2 = b\LRp{\LRp{u,\sigma,\uh,\fnh},\LRp{\tau,v}} = \frac{b\LRp{\LRp{u,\sigma,\uh,\fnh},\LRp{\tau,v}}}{\norm{v}_V}\norm{v}_V \leq \norm{u,\sigma,\uh,\fnh}_E\norm{v}_V,
+then evaluating $b\LRp{\LRp{u,\bfsigma,\uh,\fnh},\LRp{\bftau,v}}$ at these
+specific test functions returns back $\norm{u}^2 + \norm{\bfsigma}^2$, the $L^2$
+norm of our field variables.  Multiplying and dividing through by the test
+norm $\norm{v}_V$, we have
+\[
+\norm{u}_{\L}^2 + \norm{\bfsigma}_{\L}^2 =
+b\LRp{\LRp{u,\bfsigma,\uh,\fnh},\LRp{\bftau,v}} =
+\frac{b\LRp{\LRp{u,\bfsigma,\uh,\fnh},\LRp{\bftau,v}}}{\norm{v}_V}\norm{v}_V
+\leq \norm{u,\bfsigma,\uh,\fnh}_E\norm{v}_V,
 \]
@@
 \[
-\norm{u,\sigma,\uh,\fnh}_E = \sup_{v\in V\setminus\LRc{0}}\frac{b\LRp{\LRp{u,\sigma,\uh,\fnh},\LRp{\tau,v}}}{\norm{v}_V}
-\]
-is the DPG energy norm.
-If we can robustly bound the test norm $\norm{v}_V \lesssim \LRp{\norm{u}_{\L}^2+\norm{\sigma}^2_{\L}}^{1/2}$ (i.e.
-derive a bound from above with a constant independent of $\epsilon$), then we can divide through to get
-\[
-\LRp{\norm{u}_{\L}^2 + \norm{\sigma}_{\L}^2}^{\frac{1}{2}} \lesssim \norm{u,\sigma,\uh,\fnh}_E.
-\]
-In other words, the energy norm in which DPG is optimal bounds independently of $\epsilon$ the $L^2$ norm; as we drive our energy error down to zero, we can expect that the $L^2$ error will also decrease regardless of $\epsilon$.
-
-We note that the construction of the test norm $\norm{v}_V$ for a robust DPG method depends on two things: the test norm, as well as the adjoint equation.
-In \cite{DemkowiczHeuer}, the standard problem with Dirichlet conditions enforced over the entire boundary was considered; in \cite{ChanHeuerThanhDemkowicz2012}, boundary conditions were chosen for the forward problem such that the induced adjoint problem was regularized and contained no strong boundary layers, allowing for the construction of a stronger test norm on $V$.
-We adopt a slight modification of the test norm introduced in \cite{ChanHeuerThanhDemkowicz2012} for numerical experiments here, which is motivated and explained in more detail in Section~\secref{sec:confusionPlate}.
+\norm{u,\bfsigma,\uh,\fnh}_E = \sup_{v\in
+V\setminus\LRc{0}}\frac{b\LRp{\LRp{u,\bfsigma,\uh,\fnh},\LRp{\bftau,v}}}{\norm{v}_V}
+\]
+is the DPG energy norm.  If we can robustly bound the test norm $\norm{v}_V
+\lesssim \LRp{\norm{u}_{\L}^2+\norm{\bfsigma}^2_{\L}}^{1/2}$ (i.e. derive a
+bound from above with a constant independent of $\epsilon$), then we can
+divide through to get
+\begin{equation}
+\LRp{\norm{u}_{\L}^2 + \norm{\bfsigma}_{\L}^2}^{\frac{1}{2}} \lesssim
+\norm{u,\bfsigma,\uh,\fnh}_E.
+\label{eq:robustBound}
+\end{equation}
+In other words, the energy norm in which DPG is optimal bounds independently
+of $\epsilon$ the $L^2$ norm; as we drive our energy error down to zero, we
+can expect that the $L^2$ error will also decrease regardless of $\epsilon$.
+
+We note that the construction of the test norm $\norm{v}_V$ for a robust DPG
+method depends on two things: the test norm, as well as the adjoint equation.
+In \cite{DemkowiczHeuer}, the standard problem with Dirichlet conditions
+enforced over the entire boundary was considered; in
+\cite{ChanHeuerThanhDemkowicz2012}, boundary conditions were chosen for the
+forward problem such that the induced adjoint problem was regularized and
+contained no strong boundary layers, allowing for the construction of a
+stronger test norm on $V$.  We adopt a slight modification of the test norm
+introduced in \cite{ChanHeuerThanhDemkowicz2012} for numerical experiments
+here, which is motivated and explained in more detail in
+Section~\secref{sec:confusionPlate}.
 
@@
 \begin{array}{lll}
-u \in V, p \in Q\\
-a(u,v) + c(p,v) & = l(v) & \forall v \in V \\
-c(q,u) & = g(q) & \forall q \in Q
+\bfu \in \bfU, p \in Q\\
+a(\bfu,\bfw) + c(p,\bfw) & = l(\bfw) & \forall \bfw \in \bfU \\
+c(q,\bfu) & = g(q) & \forall q \in Q
 \end{array}
@@
 \end{equation}
-where $V,Q$ are Hilbert spaces, and $a,c,l,q$ denote the appropriate
-bilinear and linear forms.
+where $\bfU,Q$ are Hilbert spaces, and $a,c,l,q$ denote the appropriate
+bilinear and linear forms. Note that $a(\bfu,\bfw)=b(\bfu,T\bfw)=(T\bfu,T\bfw)_V$ in
+the notation from the previous section.
 
@@
 by the quotient norm used for $H^{-1/2}(\Gamma_h)$ and continuity
-bound for form $c(p,v)$ representing the constraint.
+bound for form $c(p,\bfw)$ representing the constraint.
 \begin{equation}
 \begin{array}{lll}
-\vert b((u,\bfsig,\hat{u},\hat{t}),\sum_K \lambda_K (1_K,{\bf 0})) \vert
-& = \vert \sum_K \lambda_K \langle \hat{t}, 1_K \rangle_{\ptl K} \vert \\[8pt]
-& = \vert \sum_K \lambda_K \langle v_n , 1_K \rangle_{\ptl K} \vert \\[8pt]
-& = \vert \sum_K \lambda_K \int_K \text{div} \bfv \: 1_K  \vert \\[8pt]
-& \leq \sum_K  \lambda_K \Vert \text{div} \bfv \Vert_{L^2(K)} \mu(K)^{1/2} \\[8pt]
-& \leq (\sum_K \mu(K) \lambda_K^2)^{1/2} \: (\sum_K \Vert \text{div} \bfv \Vert_{L^2(K)}^2 )^{1/2} \\[8pt]
-& \leq \underbrace{(\sum_K \mu(K) \lambda_K^2)^{1/2}}_{=: \Vert \bflambda \Vert} \Vert \hat{t} \Vert_{H^{-1/2}(\Gamma_h)}
+| c(\sum_K \lambda_K (1_K,{\bf 0}),(u,\bfsig,\hat{u},\hat{t})) |
+& = | \sum_K \lambda_K \langle \hat{t}, 1_K \rangle_{\ptl K} | \\[8pt]
+& = | \sum_K \lambda_K \langle v_n , 1_K \rangle_{\ptl K} | \\[8pt]
+& = | \sum_K \lambda_K \int_K \text{div} \bfpsi \: 1_K  | \\[8pt]
+& \leq \sum_K  \lambda_K | \text{div} \bfpsi |_{L^2(K)} \mu(K)^{1/2} \\[8pt]
+& \leq (\sum_K \mu(K) \lambda_K^2)^{1/2} \: (\sum_K | \text{div} \bfpsi |_{L^2(K)}^2 )^{1/2} \\[8pt]
+& \leq \underbrace{(\sum_K \mu(K) \lambda_K^2)^{1/2}}_{=: | \bflambda |} | \hat{t} |_{H^{-1/2}(\Gamma_h)}
 \end{array}
 \end{equation}
-Above, function $\bfv$ denotes the $H(\text{div},\Omega)$ extension of flux $\hat{t}$
+Above, function $\bfpsi$ denotes the $H(\text{div},\Omega)$ extension of flux $\hat{t}$
 that realizes the minimum in the definition of the quotient (minimum energy extension) norm,
@@
 
-\paragraph{Inf Sup Condition} relating spaces $V$ and $Q$ reads as follows,
-\begin{equation}
-\sup_{v \in V} \frac{\vert c(p,v) \vert}{\Vert v \Vert_V} \geq \beta \Vert p \Vert_Q
+\paragraph{Inf Sup Condition} relating spaces $\bfU$ and $Q$ reads as follows,
+\begin{equation}
+   \sup_{\bfw \in \bfU} \frac{| c(p,\bfw) |}{| \bfw |_{\bfU}} \geq \beta | p |_Q
 \end{equation}
@@
 \begin{equation}
-R\, : \, L^2(\Omega) \ni q \to \bfv \in \bfH(\text{div},\Omega) \cap \bfH^1(\Omega)
-=\bfH^1
+R\, : \, L^2(\Omega) \ni q \to \bfpsi \in \bfH(\text{div},\Omega) \cap \bfH^1(\Omega)
+=\bfH^1(\Omega)
 \end{equation}
@@
 Costabel and McIntosh in \cite{CostabelMcIntosh}.
-Let $\bfv_h$ denote the classical, lowest order Raviart-Thomas (RT) interpolant of
+Let $\bfpsi_h$ denote the classical, lowest order Raviart-Thomas (RT) interpolant of
 function
 \begin{equation}
-\bfv = R (\sum_K \lambda_K 1_K) \: .
-\end{equation}
-Note that $\text{div} \bfv_h = \text{div} \bfv = \lambda_K$ in element $K$.
+\bfpsi = R (\sum_K \lambda_K 1_K) \: .
+\end{equation}
+Note that $\text{div} \bfpsi_h = \text{div} \bfpsi = \lambda_K$ in element $K$.
 
@@
 \begin{array}{lll}
-\Vert \bfv_h \Vert & \leq \Vert \bfv_h - \bfv \Vert + \Vert \bfv \Vert\\[8pt]
-&\leq C h \Vert \bfv \Vert_{H^1} +  \Vert \bfv \Vert \\[8pt]
-& \leq C \Vert \text{div} \bfv \Vert = C (\sum_K \mu(K) \lambda_K^2)^{1/2}
+| \bfpsi_h | & \leq | \bfpsi_h - \bfpsi | + | \bfpsi |\\[8pt]
+&\leq C h | \bfpsi |_{H^1} +  | \bfpsi | \\[8pt]
+& \leq C | \text{div} \bfpsi | = C (\sum_K \mu(K) \lambda_K^2)^{1/2}
 \end{array}
@@
 the interpolation error estimate and continuity constant of $R$.
-Let $\hat{t}$ be now the trace of $\bfv_h$. We have then,
-\begin{equation}
-\sup_{\hat{t} \in H^{-1/2}(\Gamma_h)} \frac{\vert  \sum_K \lambda_K \langle \hat{t},1_K \rangle_{\ptl K} \vert}{\Vert \hat{t} \Vert_{H^{-1/2}(\Gamma_h)}}
-\geq \frac{\vert \sum_K \lambda_K \int_K \text{div} \bfv_h \: 1_K  \vert}
-{\Vert \bfv_h \Vert_{H(\text{div},\Omega)}}
+Let $\hat{t}$ be now the trace of $\bfpsi_h$. We have then,
+\begin{equation}
+\sup_{\hat{t} \in H^{-1/2}(\Gamma_h)} \frac{|  \sum_K \lambda_K \langle \hat{t},1_K \rangle_{\ptl K} |}{| \hat{t} |_{H^{-1/2}(\Gamma_h)}}
+\geq \frac{| \sum_K \lambda_K \int_K \text{div} \bfpsi_h \: 1_K  |}
+{| \bfpsi_h |_{H(\text{div},\Omega)}}
 \geq \frac{1}{C} (\sum_K \mu(K) \lambda_K^2)^{1/2}
@@
 automatically the analogous condition for elements of arbitrary order; increasing
-space $V$ makes only the discrete inf-sup constant bigger.
+space $U$ only makes the discrete inf-sup constant bigger.
 
@@
 \begin{array}{rl}
-V_0  := & \{ v \in V \, : \, c(v,u) = 0 \: \forall q \in Q\} \\[8pt]
- = &\{ (u,\bfsig,\hat{u},\hat{t}) \, : \, \langle \hat{t},1_T \rangle = 0 \, \forall K \}
+\bfU_0  := & \{ \bfw \in \bfU \, : \, c(q,\bfw) = 0 \quad \forall q \in Q\} \\[8pt]
+ = &\{ (u,\bfsig,\hat{u},\hat{t}) \, : \, \langle \hat{t},1_K \rangle = 0
+ \quad \forall K \}
 \end{array}
@@
 In other words, the kernel space contains only the equilibriated fluxes.
-With $u \in V_0$, we have then:
-\begin{equation}
-\sup_{v \in V_0} \frac{\vert a(u,v) \vert}{\Vert v \Vert_V }
- \geq \frac{\vert b(\bfu,T \bfu) \vert}{\Vert \bfu \Vert}
+With $\bfu \in \bfU_0$, we have then:
+\begin{equation}
+   \sup_{\bfw \in \bfU_0} \frac{| a(\bfu,\bfw) |}{| \bfw |_{\bfU} }
+ \geq \frac{| b(\bfu,T \bfu) |}{| \bfu |}
 = \sup_{(v,\bftau)}
-\frac{\vert b((u,\bfsig,\hat{u},\hat{t}), (v,\bftau)) \vert}{\Vert (v,\bftau) \Vert}
-\geq \gamma^2 \Vert (u,\bfsig,\hat{u},\hat{t}) \Vert
+\frac{| b((u,\bfsig,\hat{u},\hat{t}), (v,\bftau)) |}{| (v,\bftau) |}
+\geq \gamma^2 | (u,\bfsig,\hat{u},\hat{t}) |
 \end{equation}
@@
 
-Recall the main line of analysis in {\color{red}(supposed to be Brezzi?)}\cite{} leading to the construction of robust
-test norms. With the robust test norms, we have
+Recall the line of analysis leading to the construction of robust
+test norms allowing us to bound the $L^2$ error of the field variables by the
+energy error, Equation \ref{eq:robustBound}. With robust test norms, we have
 \begin{equation}
 \begin{array}{ll}
-   \LRp{\Vert u - u_h \Vert^2+ \Vert \bfsig - \bfsig_h
-   \Vert^2}^{\frac{1}{2}}
-& \lesssim \Vert (u - u_h, \bfsig - \bfsig_h, \hat{u} - \hat{u}_h, \hat{t} - \hat{t}_h \Vert_E \\[8pt]
-&= \inf_{(v_h,\bftau_h,\hat{v},\hat{r}_h)}
-\Vert (u - v_h, \bfsig - \bftau_h, \hat{u} - \hat{v}_h, \hat{t} - \hat{r}_h \Vert_E
+   \LRp{| u - u_h |^2+ | \bfsig - \bfsig_h
+   |^2}^{\frac{1}{2}}
+& \lesssim | (u - u_h, \bfsig - \bfsig_h, \hat{u} - \hat{u}_h, \hat{t} - \hat{t}_h |_E \\[8pt]
+&= \inf_{(w_h,\bfvarsigma_h,\hat{w},\hat{r}_h)}
+| (u - w_h, \bfsig - \bfvarsigma_h, \hat{u} - \hat{w}_h, \hat{t} - \hat{r}_h |_E\,.
 \end{array}
@@
 analysis. Dealing with the ``inf-sup in kernel'' condition is simple. Upon replacing
-the original norm of solution $u$ with the energy norm, both constant $\gamma$ and continuity
+the original norm of solution $\bfu$ with the energy norm, both constant $\gamma$ and continuity
 constant become unity. In order to investigate the robustness of inf-sup  constant $\beta$,
@@
 v_K \in H^1(K),\, \bftau_K \in \bfH(\text{div},K)\\[8pt]
-((v_K,\bftau_K), (\delta v,\delta \bftau)_V = \langle \hat{t},\delta v\rangle_{\ptl K}
-\quad \forall \delta v \in H^1(K), \delta \bftau \in \bfH(\text{div},K)
+((v_K,\bftau_K), (\delta v,\delta \bftau))_V = \langle \hat{t},\delta v\rangle_{\ptl K}
+\quad \forall \delta v \in H^1(K), \delta \bftau \in \bfH(\text{div},K)\,.
 \end{array}
@@
 \end{equation}
-The energy norm of $\hat{t}$ is then equal to:
-\begin{equation}
-\Vert \hat{t} \Vert_E^2 = \sum_K \Vert (v_K,\bftau_K) \Vert_V^2
-\end{equation}
-We need to establish sufficient conditions under which inf-sup and continuity constants for
+The energy norm of $\hat{t}$ is then equal to
+\begin{equation}
+| \hat{t} |_E^2 = \sum_K | (v_K,\bftau_K) |_V^2\,.
+\end{equation}
+We need to establish sufficient conditions under which the inf-sup and continuity constants for
 the bilinear form representing the constraint are independent of viscosity $\epsilon$.
@@
 \begin{equation}
-\sup_{\hat{t}} \frac{\vert \sum_K \lambda_K \langle \hat{t},1_K \rangle \vert}{\Vert \hat{t} \Vert_E}
-\geq  \beta (\sum_K \mu(K) \lambda_K^2)^{1/2}
+\sup_{\hat{t}} \frac{| \sum_K \lambda_K \langle \hat{t},1_K \rangle |}{| \hat{t} |_E}
+\geq  \beta \LRp{\sum_K \mu(K) \lambda_K^2}^{1/2}\,.
 \end{equation}
@@
 interpolant $\bfpsi_h$ of $\bfpsi = R (\sum_K \lambda_K 1_K)$ where $R$ is the right-inverse
-of the divergence operator constructed by Costabel and Mac Intosh. The only change compared
+of the divergence operator constructed by Costabel and McIntosh. The only change compared
 with the previous analysis, is the evaluation of norm of $\hat{t}_h$. For this, we need
@@
 \end{equation}
-We need then an upper bound of the energy norm of $\bfv_h$:
+We need then an upper bound of the energy norm of $(v_h,\bftau_h)$:
 $$
-(\sum_K \Vert (v,\bftau) \Vert_V^2)^{1/2}
+\LRp{\sum_K | (v,\bftau) |_V^2}^{1/2}\,.
 $$
@@
 \begin{equation}
-\Vert (v,\bftau) \Vert_V^2 = \lambda_K (1_K, v_K)
+| (v,\bftau) |_V^2 = \lambda_K (1_K, v_K)
 \end{equation}
@@
 \begin{equation}
-(1_K, v_K) \leq C \mu(K)^{1/2} \Vert (v,\bftau) \Vert_K
+(1_K, v_K) \leq C \mu(K)^{1/2} | (v,\bftau) |_K
 \end{equation}
@@
 \begin{equation}
-\Vert  (v,\bftau) \Vert_V \leq C \mu(K)^{1/2} \vert \lambda_K \vert
+|  (v,\bftau) |_V \leq C \mu(K)^{1/2} | \lambda_K |
 \end{equation}
@@
 \begin{equation}
-\sum_K \Vert (v,\bftau) \Vert_V^2  \leq C^2 \sum_K \mu(K) \lambda_K^2
+\sum_K | (v,\bftau) |_V^2  \leq C^2 \sum_K \mu(K) \lambda_K^2
 \end{equation}
@@
 \begin{equation}
-\Vert v \Vert_{L^2(K)} \leq \Vert (v,\bftau) \Vert_V \, .
+| v |_{L^2(K)} \leq | (v,\bftau) |_V \, .
 \label{eq:robust_est1}
@@
 $$
-\sum_K \lambda_K \langle \hat{t}, 1_K \rangle
+\sum_K \lambda_K \langle \hat{t}, 1_K \rangle\,.
 $$
@@
 \begin{equation}
-\vert ((v,\bftau),(1_K,{\bf 0}))_V \vert \leq C \mu(K)^{1/2} \, \Vert (v,\bftau) \Vert_V
+| ((v,\bftau),(1_K,{\bf 0}))_V | \leq C \mu(K)^{1/2} \, | (v,\bftau) |_V
 \label{eq:robust_est2}
@@
 \begin{equation}
-\vert \sum_K \lambda_K \langle \hat{t}, 1_K \rangle \vert \leq C (\sum_K \mu(K) \lambda_K^2)^{1/2}
-\, (\sum_K \Vert (v,\bftau) \Vert_V^2)^{1/2}
-= C (\sum_K \mu(K) \lambda_K^2)^{1/2}  \Vert \hat{t} \Vert_E
+| \sum_K \lambda_K \langle \hat{t}, 1_K \rangle | \leq C (\sum_K \mu(K) \lambda_K^2)^{1/2}
+\, (\sum_K | (v,\bftau) |_V^2)^{1/2}
+= C (\sum_K \mu(K) \lambda_K^2)^{1/2}  | \hat{t} |_E
 \end{equation}
@@
 \norm{\LRp{v,\btau}}_{V,K}^2 &\coloneqq
-\min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\norm{\btau}_K^2,
+\min\left\{\frac{1}{\epsilon},\frac{1}{\mu(K)}\right\}\norm{\btau}_K^2,
 + \norm{\div \btau - \bbeta\cdot\Grad v}_K^2 \\
@@
 \begin{align}
-\min&\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}(\taudeltau,\delta\btau)_K
+\min&\left\{\frac{1}{\epsilon},\frac{1}{\mu(K)}\right\}(\taudeltau,\delta\btau)_K
 +(\nabla\cdot\taudeltau-\bbeta\cdot\nabla
@@
 +\epsilon(\nabla\vdeltau,\nabla \delta v)_K
-+\frac{1}{|K|^2}\int_K\vdeltau\int_K\delta v
++\frac{1}{\mu(K)^2}\int_K\vdeltau\int_K\delta v
 \label{eq:localSolveMod}
 \end{align}
-where the $\frac{1}{|K|^2}$ coefficient is needed to make the zero mean term
+where the $\frac{1}{\mu(K)^2}$ coefficient is needed to make the zero mean term
 scale correctly since $\int_K\vdeltau$ and $\int_K\delta v$ both scale like
-$|K|$. Numerically this helps with the condition
+$\mu(K)$. Numerically this helps with the condition
 numbers of the local solve.

### 2013-11-22 docs/Truman/LocalConservation/paper/paper.tex
Fixed norms in local conservation paper

@@
 
+Let function $\bfpsi$ denote the $H(\text{div},\Omega)$ extension of flux $\hat{t}$
+that realizes the minimum in the definition of the quotient (minimum energy
+extension) norm.
 The choice of norm for the Lagrange multipliers $\lambda_K$ is implied
 by the quotient norm used for $H^{-1/2}(\Gamma_h)$ and continuity
-bound for form $c(p,\bfw)$ representing the constraint.
+bound for form $c(p,\bfw)$ representing the constraint:
 \begin{equation}
@@
 & = | \sum_K \lambda_K \int_K \text{div} \bfpsi \: 1_K  | \\[8pt]
-& \leq \sum_K  \lambda_K | \text{div} \bfpsi |_{L^2(K)} \mu(K)^{1/2} \\[8pt]
-& \leq (\sum_K \mu(K) \lambda_K^2)^{1/2} \: (\sum_K | \text{div} \bfpsi |_{L^2(K)}^2 )^{1/2} \\[8pt]
-& \leq \underbrace{(\sum_K \mu(K) \lambda_K^2)^{1/2}}_{=: | \bflambda |} | \hat{t} |_{H^{-1/2}(\Gamma_h)}
+& \leq \sum_K  \lambda_K || \text{div} \bfpsi ||_{L^2(K)} \mu(K)^{1/2} \\[8pt]
+& \leq (\sum_K \mu(K) \lambda_K^2)^{1/2} \: (\sum_K || \text{div} \bfpsi ||_{L^2(K)}^2 )^{1/2} \\[8pt]
+& \leq \underbrace{(\sum_K \mu(K) \lambda_K^2)^{1/2}}_{=: || \bflambda ||} ||
+\hat{t} ||_{H^{-1/2}(\Gamma_h)}
 \end{array}
 \end{equation}
-Above, function $\bfpsi$ denotes the $H(\text{div},\Omega)$ extension of flux $\hat{t}$
-that realizes the minimum in the definition of the quotient (minimum energy extension) norm,
-and $\mu(K)$ stands for the area (measure) of element $K$.
+where $\mu(K)$ stands for the area (measure) of element $K$.
 
@@
 \begin{equation}
-   \sup_{\bfw \in \bfU} \frac{| c(p,\bfw) |}{| \bfw |_{\bfU}} \geq \beta | p |_Q
+   \sup_{\bfw \in \bfU} \frac{| c(p,\bfw) |}{|| \bfw ||_{\bfU}} \geq \beta ||
+   p ||_Q
 \end{equation}
@@
 \begin{array}{lll}
-| \bfpsi_h | & \leq | \bfpsi_h - \bfpsi | + | \bfpsi |\\[8pt]
-&\leq C h | \bfpsi |_{H^1} +  | \bfpsi | \\[8pt]
-& \leq C | \text{div} \bfpsi | = C (\sum_K \mu(K) \lambda_K^2)^{1/2}
+|| \bfpsi_h || & \leq || \bfpsi_h - \bfpsi || + || \bfpsi ||\\[8pt]
+&\leq C h || \bfpsi ||_{H^1} +  || \bfpsi || \\[8pt]
+& \leq C || \text{div} \bfpsi || = C (\sum_K \mu(K) \lambda_K^2)^{1/2}
 \end{array}
@@
 \begin{equation}
-\sup_{\hat{t} \in H^{-1/2}(\Gamma_h)} \frac{|  \sum_K \lambda_K \langle \hat{t},1_K \rangle_{\ptl K} |}{| \hat{t} |_{H^{-1/2}(\Gamma_h)}}
+\sup_{\hat{t} \in H^{-1/2}(\Gamma_h)} \frac{|  \sum_K \lambda_K \langle
+\hat{t},1_K \rangle_{\ptl K} |}{|| \hat{t} ||_{H^{-1/2}(\Gamma_h)}}
 \geq \frac{| \sum_K \lambda_K \int_K \text{div} \bfpsi_h \: 1_K  |}
-{| \bfpsi_h |_{H(\text{div},\Omega)}}
+{|| \bfpsi_h ||_{H(\text{div},\Omega)}}
 \geq \frac{1}{C} (\sum_K \mu(K) \lambda_K^2)^{1/2}
@@
 \begin{equation}
-   \sup_{\bfw \in \bfU_0} \frac{| a(\bfu,\bfw) |}{| \bfw |_{\bfU} }
- \geq \frac{| b(\bfu,T \bfu) |}{| \bfu |}
+   \sup_{\bfw \in \bfU_0} \frac{| a(\bfu,\bfw) |}{|| \bfw ||_{\bfU} }
+ \geq \frac{| b(\bfu,T \bfu) |}{|| \bfu ||}
 = \sup_{(v,\bftau)}
-\frac{| b((u,\bfsig,\hat{u},\hat{t}), (v,\bftau)) |}{| (v,\bftau) |}
-\geq \gamma^2 | (u,\bfsig,\hat{u},\hat{t}) |
+\frac{| b((u,\bfsig,\hat{u},\hat{t}), (v,\bftau)) |}{|| (v,\bftau) ||}
+\geq \gamma^2 || (u,\bfsig,\hat{u},\hat{t}) ||
 \end{equation}
@@
 \begin{array}{ll}
-   \LRp{| u - u_h |^2+ | \bfsig - \bfsig_h
-   |^2}^{\frac{1}{2}}
-& \lesssim | (u - u_h, \bfsig - \bfsig_h, \hat{u} - \hat{u}_h, \hat{t} - \hat{t}_h |_E \\[8pt]
+   \LRp{|| u - u_h ||^2+ || \bfsig - \bfsig_h ||^2}^{\frac{1}{2}}
+& \lesssim || (u - u_h, \bfsig - \bfsig_h, \hat{u} - \hat{u}_h, \hat{t} - \hat{t}_h ||_E \\[8pt]
 &= \inf_{(w_h,\bfvarsigma_h,\hat{w},\hat{r}_h)}
-| (u - w_h, \bfsig - \bfvarsigma_h, \hat{u} - \hat{w}_h, \hat{t} - \hat{r}_h |_E\,.
+|| (u - w_h, \bfsig - \bfvarsigma_h, \hat{u} - \hat{w}_h, \hat{t} - \hat{r}_h ||_E\,.
 \end{array}
@@
 \begin{equation}
-| \hat{t} |_E^2 = \sum_K | (v_K,\bftau_K) |_V^2\,.
+|| \hat{t} ||_E^2 = \sum_K || (v_K,\bftau_K) ||_V^2\,.
 \end{equation}
@@
 \begin{equation}
-\sup_{\hat{t}} \frac{| \sum_K \lambda_K \langle \hat{t},1_K \rangle |}{| \hat{t} |_E}
+\sup_{\hat{t}} \frac{| \sum_K \lambda_K \langle \hat{t},1_K \rangle |}{|| \hat{t} ||_E}
 \geq  \beta \LRp{\sum_K \mu(K) \lambda_K^2}^{1/2}\,.
@@
 $$
-\LRp{\sum_K | (v,\bftau) |_V^2}^{1/2}\,.
+\LRp{\sum_K || (v,\bftau) ||_V^2}^{1/2}\,.
 $$
@@
 \begin{equation}
-| (v,\bftau) |_V^2 = \lambda_K (1_K, v_K)
+|| (v,\bftau) ||_V^2 = \lambda_K (1_K, v_K)
 \end{equation}
@@
 \begin{equation}
-(1_K, v_K) \leq C \mu(K)^{1/2} | (v,\bftau) |_K
+(1_K, v_K) \leq C \mu(K)^{1/2} || (v,\bftau) ||_K
 \end{equation}
@@
 \begin{equation}
-|  (v,\bftau) |_V \leq C \mu(K)^{1/2} | \lambda_K |
+||  (v,\bftau) ||_V \leq C \mu(K)^{1/2} | \lambda_K |
 \end{equation}
@@
 \begin{equation}
-\sum_K | (v,\bftau) |_V^2  \leq C^2 \sum_K \mu(K) \lambda_K^2
+\sum_K || (v,\bftau) ||_V^2  \leq C^2 \sum_K \mu(K) \lambda_K^2
 \end{equation}
@@
 \begin{equation}
-| v |_{L^2(K)} \leq | (v,\bftau) |_V \, .
+|| v ||_{L^2(K)} \leq || (v,\bftau) ||_V \, .
 \label{eq:robust_est1}
@@
 \begin{equation}
-| ((v,\bftau),(1_K,{\bf 0}))_V | \leq C \mu(K)^{1/2} \, | (v,\bftau) |_V
+| ((v,\bftau),(1_K,{\bf 0}))_V | \leq C \mu(K)^{1/2} \, || (v,\bftau) ||_V
 \label{eq:robust_est2}
@@
 | \sum_K \lambda_K \langle \hat{t}, 1_K \rangle | \leq C (\sum_K \mu(K) \lambda_K^2)^{1/2}
-\, (\sum_K | (v,\bftau) |_V^2)^{1/2}
-= C (\sum_K \mu(K) \lambda_K^2)^{1/2}  | \hat{t} |_E
+\, (\sum_K || (v,\bftau) ||_V^2)^{1/2}
+= C (\sum_K \mu(K) \lambda_K^2)^{1/2}  || \hat{t} ||_E
 \end{equation}

### 2013-11-22 docs/Truman/LocalConservation/paper/paper.tex
Added coarse stokes cylinder results to lc paper

@@
    \geq \frac{| b(\bfu,T \bfu) |}{|| \bfu ||}
-= \sup_{(v,\bftau)}
-\frac{| b((u,\bfsig,\hat{u},\hat{t}), (v,\bftau)) |}{|| (v,\bftau) ||}
+   = \frac{| b(\bfu,T \bfu) |}{|| T\bfu ||}\frac{||T\bfu||}{||\bfu||}
+   = \sup_{(v,\bftau)}\frac{| b((u,\bfsig,\hat{u},\hat{t}), (v,\bftau)) |}{|| (v,\bftau) ||}
+   \frac{||T\bfu||}{||\bfu||}
    \geq \gamma^2 || (u,\bfsig,\hat{u},\hat{t}) ||
@@
 where $\gamma$ is the stability constant for the standard continuous DPG formulation.
+The first inequality follows as we plug in the definition for $a$ and pick
+$\bfw=\bfu$. The second equality is trivial, while the next one follows by definition of the optimal test
+functions given through the trial-to-test operator $T$. The finally inequality
+springs from the fact that
+$\sup_{\bfv}\frac{|b(\bfu,\bfv)|}{||\bfv||}\geq\gamma||\bfu||$ and
+$||T\bfu||_V=||R_V^{-1}B\bfu||_V=||B\bfu||_{V'}\geq\gamma||u||$.
 
@@
 \centering
-\begin{subfigure}[t]{0.5\textwidth}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/StokesCylinder/umag6_NC0.png}
+\caption{Nonconservative on initial mesh with $r=0.6$}
+\label{fig:stokesCylinder6NC0}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/StokesCylinder/umag6_C0.png}
+\caption{Conservative on initial mesh with $r=0.6$}
+\label{fig:stokesCylinder6C0}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
 \centering
 \includegraphics[width=\textwidth]{figs/StokesCylinder/umag6_NC6.png}
-\caption{Nonconservative with $r=0.6$}
-\label{fig:stokesCylinderNC6}
-\end{subfigure}
-\begin{subfigure}[t]{0.5\textwidth}
+\caption{Nonconservative after 6 refinements with $r=0.6$}
+\label{fig:stokesCylinder6NC6}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
 \centering
 \includegraphics[width=\textwidth]{figs/StokesCylinder/umag6_C6.png}
-\caption{Conservative with $r=0.6$}
-\label{fig:stokesCylinderC6}
-\end{subfigure}
-\begin{subfigure}[t]{0.5\textwidth}
+\caption{Conservative after 6 refinements with $r=0.6$}
+\label{fig:stokesCylinder6C6}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/StokesCylinder/umag9_NC1.png}
+\caption{Nonconservative after 1 refinement with $r=0.9$}
+\label{fig:stokesCylinder9NC1}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
+\centering
+\includegraphics[width=\textwidth]{figs/StokesCylinder/umag9_C1.png}
+\caption{Conservative after 1 refinement with $r=0.9$}
+\label{fig:stokesCylinder9C1}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
 \centering
 \includegraphics[width=\textwidth]{figs/StokesCylinder/umag9_NC6.png}
-\caption{Nonconservative with $r=0.9$}
-\label{fig:stokesCylinderNC9}
-\end{subfigure}
-\begin{subfigure}[t]{0.5\textwidth}
+\caption{Nonconservative after 6 refinements with $r=0.9$}
+\label{fig:stokesCylinder9NC6}
+\end{subfigure}
+\begin{subfigure}[t]{0.45\textwidth}
 \centering
 \includegraphics[width=\textwidth]{figs/StokesCylinder/umag9_C6.png}
-\caption{Conservative with $r=0.9$}
-\label{fig:stokesCylinderC9}
-\end{subfigure}
-\caption{Stokes flow around a cylinder after 6 refinement steps - velocity magnitude}
-\label{fig:stokesCylinder9}
+\caption{Conservative after 6 refinements with $r=0.9$}
+\label{fig:stokesCylinder9C6}
+\end{subfigure}
+\caption{Stokes flow around a cylinder - velocity magnitude}
+\label{fig:stokesCylinder}
 \end{figure}

### 2013-11-22 docs/Truman/LocalConservation/paper/paper.tex
Added discussion of coarse results

@@
 
+The most significant benefit of enforcing local conservation for these
+problems is that it allows us to recover the essential flow features with much
+coarser meshes. On the $r=0.6$ cylinder problem, the peak velocity magnitude
+of the conservative solution is fairly close on the coarsest mesh, while the
+nonconservative solution severely underpredicts the peak. With the $r=0.9$
+cylinder, this problem is only exacerbated. After just one adaptive
+refinement, the conservative solution nails the peak velocity. The
+nonconservative solution is completely useless at this point. We see the same
+thing with the backward facing step problem. The conservative solution is
+great on the coarsest mesh, while standard DPG needs a lot more resolution
+before it even starts to look right.
+
 \section{Conclusions}
@@
 loss as standard least squares on coarse meshes, but made up the lost mass with further
-resolution.
+resolution. On problems where local conservation was really stressed,
+restricted DPG was able to deliver reasonable solutions with much less
+resolution than standard DPG.
 Probably the most encouraging result of these experiments is

### 2013-12-03 docs/Truman/LocalConservation/paper/paper.tex
Small changes to local conservation paper

--- 2013-11-22 docs/Truman/LocalConservation/paper/paper.tex
@@
 %TODO: bold face proper variables
+%TODO: Make sure titles have consistent case
 \usepackage[margin=1.0in]{geometry}
@@
 \newcommand{\LRc}[1]{\left\{ #1 \right\}}
+\newcommand{\LRl}[1]{\left| #1 \right|}
 \newcommand{\tanbui}[2]{\textcolor{blue}{\sout{#1}} \textcolor{red}{#2}}
@@
 
-\section{Intoduction}
+\section{Introduction}
 The discontinuous Petrov-Galerkin (DPG) method with optimal test functions has
@@
 \subsubsection{Robustness Analysis}
+\label{sec:robustnessAnalysis}
 
@@
 to solve the local problems:
-\begin{equation}
-((v,\bftau), (\delta v, \delta \bftau)_V = \langle \hat{t}, \delta v \rangle_{\ptl K}
-= \int_K \text{div} \bfpsi_h \, \delta v = \int_K \text{div} \bfpsi \, \delta v = \int_K \lambda_K \delta v
-= \lambda_K (1_K,\delta v)_K  \quad \forall \delta v \in H^1(K)
+\begin{align}
+((v,\bftau), (\delta v, \delta \bftau)_V &= \langle \hat{t}, \delta v \rangle_{\ptl K}
+= \int_K \text{div} \bfpsi_h \, \delta v = \int_K \text{div} \bfpsi \, \delta v
+\nonumber\\
+&= \int_K \lambda_K \delta v
+= \lambda_K (1_K,\delta v)_K  \quad \forall \delta v \in
+H^1(K)\,\forall\delta\bftau\in\bfH(\text{div},K)
 \label{eq:local}
-\end{equation}
+\end{align}
 We need then an upper bound of the energy norm of $(v_h,\bftau_h)$:
@@
 (1_K, v_K) \leq C \mu(K)^{1/2} || (v,\bftau) ||_K
+\label{eq:robustEst1}
 \end{equation}
@@
 \begin{align}
+\label{eq:localSolveMod}
 \min&\left\{\frac{1}{\epsilon},\frac{1}{\mu(K)}\right\}(\taudeltau,\delta\btau)_K
@@
 +\epsilon(\nabla\vdeltau,\nabla \delta v)_K
-+\frac{1}{\mu(K)^2}\int_K\vdeltau\int_K\delta v
-\label{eq:localSolveMod}
++\frac{1}{\mu(K)}\int_K\vdeltau\int_K\delta v
 \end{align}
-where the $\frac{1}{\mu(K)^2}$ coefficient is needed to make the zero mean term
-scale correctly since $\int_K\vdeltau$ and $\int_K\delta v$ both scale like
-$\mu(K)$. Numerically this helps with the condition
-numbers of the local solve.
+where the $\frac{1}{\mu(K)}$ coefficient is an arbitrary scaling condition
+that doesn't make a difference mathematically, but can affect the condition
+number of the actual solve. In practice, we use $\frac{1}{\mu(K)^2}$
+since $\int_K\vdeltau$ and $\int_K\delta v$ both scale like
+$\mu(K)$, but $\frac{1}{\mu(K)}$ is more convenient more the analysis in the
+next section.
 It is convenient to be able to take $\alpha\rightarrow0$ as we will see in
 some later numerical experiments.
+
+\subsubsection{Proof of Robust Stability Estimate}
+In the robustness analysis in Section~\ref{sec:robustnessAnalysis}, we argued
+that if we have a robust stability estimate:
+\begin{equation}
+(1_K, v_K) \leq C \mu(K)^{1/2} || (v,\bftau) ||_K
+\tag{\ref{eq:robustEst1}}
+\end{equation}
+and
+\begin{equation}
+| ((v,\bftau),(1_K,{\bf 0}))_V | \leq C \mu(K)^{1/2} \, || (v,\bftau) ||_V\,.
+\tag{\ref{eq:robust_est2}}
+\end{equation}
+We now proceed to show that the robust norms we are using satisfy this
+requirement.
+Consider the inner product from Equation~(\ref{eq:localSolve}), with
+$\alpha=1$. We wish to
+verify condition (\ref{eq:robustEst1}) with the norm derived from this inner
+product on the right hand side. By Cauchy-Schwarz
+\begin{equation}
+   \int_K v\cdot
+   1\leq\mu(K)^{1/2}\norm{v}_{L^2(K)}\leq\mu(K)^{1/2}\norm{(v,\btau)}_K
+   \label{eq:robustProof}
+\end{equation}
+where $\norm{(v,\btau)}_K$ is the norm derived from the inner product.
+Condition~\ref{eq:robust_est2} comes out the same since
+$$|(
+(v,\btau),(1_K,{\bf0}))| =
+\sum_K|(1_K,v_K)|\leq\sum_K\mu(K)^{1/2}\norm{v,\btau}_K
+$$
+element-wise.
+
+Now we wish the perform the same analysis for the modified inner product in
+Equation~(\ref{eq:localSolveMod}). In this case,
+condition~(\ref{eq:robustEst1}) follows even more naturally as
+\begin{equation}
+   \int_K v\cdot1\leq\mu(K)^{1/2}\frac{1}{\mu(K)^{1/2}}\LRl{\int_Kv}
+   \leq\norm{(v,\btau)}_K
+   \label{eq:robustProof2}
+\end{equation}
+where $\norm{(v,\btau)}$ now refers to the norm generated by inner product
+(\ref{eq:localSolveMod}). Condition~(\ref{eq:robust_est2}) follows by the same
+reasoning.
 

### 2013-12-04 docs/Truman/LocalConservation/paper/paper.tex
Spelling fixes for LC paper

@@
 %TODO: Make sure titles have consistent case
+%TODO: Make sure figures work in gray-scale
 \usepackage[margin=1.0in]{geometry}
@@
 the attractive features of DPG, but turns the normally symmetric
-positive-difinite DPG system into a saddlepoint problem.
+positive-definite DPG system into a saddle point problem.
 \end{abstract}
@@
 least squares finite elements for a long time. Several approaches have been
-used to try to adress this. Bochev \etal\cite{Bochev2010} accomplish local
+used to try to address this. Bochev \etal\cite{Bochev2010} accomplish local
 conservation by using a pointwise divergence free velocity space in the Stokes
@@
 both methods share similar negative of transforming a minimization method to a
-saddle-point problem. In the interest of crediting Chang and Nelson's
+saddle point problem. In the interest of crediting Chang and Nelson's
 restricted LSFEM, we call the following locally conservative DPG method the
@@
 \cite{DPGStokes}. We follow his derivation of the standard DPG method as a
-minumum residual method. Let $U$ be the trial Hilbert space and $V$ the test
+minimum residual method. Let $U$ be the trial Hilbert space and $V$ the test
 Hilbert space for a well-posed variational problem $b(u,v)=l(v)$. In operator
@@
 \end{equation}
-where $\bfU,Q$ are Hilbert spaces, and $a,c,l,q$ denote the appropriate
+where $\bfU,Q$ are Hilbert spaces, and $a,c,l,g$ denote the appropriate
 bilinear and linear forms. Note that $a(\bfu,\bfw)=b(\bfu,T\bfw)=(T\bfu,T\bfw)_V$ in
@@
 & \leq (\sum_K \mu(K) \lambda_K^2)^{1/2} \: (\sum_K || \text{div} \bfpsi ||_{L^2(K)}^2 )^{1/2} \\[8pt]
-& \leq \underbrace{(\sum_K \mu(K) \lambda_K^2)^{1/2}}_{=: || \bflambda ||} ||
+& \leq \underbrace{\left(\sum_K \mu(K) \lambda_K^2\right)^{1/2}}_{=: || \bflambda ||} ||
 \hat{t} ||_{H^{-1/2}(\Gamma_h)}
@@
 the interpolation error estimate and continuity constant of $R$.
-Let $\hat{t}$ be now the trace of $\bfpsi_h$. We have then,
+Let $\hat{t}$ be the trace of $\bfpsi_h$. We have then,
 \begin{equation}
@@
 \end{equation}
-In other words, the kernel space contains only the equilibriated fluxes.
+In other words, the kernel space contains only the equilibrated fluxes.
 With $\bfu \in \bfU_0$, we have then:
@@
 test norms allowing us to bound the $L^2$ error of the field variables by the
-energy error, Equation \ref{eq:robustBound}. With robust test norms, we have
+energy error, Equation~(\ref{eq:robustBound}). With robust test norms, we have
 \begin{equation}
@@
 
-\subsection{Robust test norms}
+\subsection{Robust Test Norms}
 The optimal test functions are determined by solving local problems determined
@@
 
-\subsubsection{A model problem}
+\subsubsection{A Model Problem}
 \seclab{sec:confusionPlate}
@@
 
-\subsubsection{A modification of the robust test norm}
+\subsubsection{A Modification of the Robust Test Norm}
 
@@
 Figure~\ref{fig:newNorm} shows the solution for $\epsilon = .01$, where the
-diffusion scale is both underresolved and resolved by $h$-adaptivity.  In both
+diffusion scale is both under-resolved and resolved by $h$-adaptivity.  In both
 cases, there are no oscillations near the plate tip --
@@
 however, the solution $u$ does not display spurious oscillations in either the
-underresolved or resolved cases.  Figure~\ref{fig:newNormSmallEps} displays
+under-resolved or resolved cases.  Figure~\ref{fig:newNormSmallEps} displays
 the same quantities, but for $\epsilon = 10^{-4}$, in order to demonstrate
@@
 
-\subsubsection{Proof of Robust Stability Estimate}
+\subsubsection{Verification of Robust Stability Estimate}
 In the robustness analysis in Section~\ref{sec:robustnessAnalysis}, we argued
-that if we have a robust stability estimate:
+that if we have robust stability estimates:
 \begin{equation}
 (1_K, v_K) \leq C \mu(K)^{1/2} || (v,\bftau) ||_K
-\tag{\ref{eq:robustEst1}}
+\tag{\ref{eq:robustEst1} revisted}
 \end{equation}
@@
 | ((v,\bftau),(1_K,{\bf 0}))_V | \leq C \mu(K)^{1/2} \, || (v,\bftau) ||_V\,.
-\tag{\ref{eq:robust_est2}}
-\end{equation}
+\tag{\ref{eq:robust_est2} revisted}
+\end{equation}
+then the restricted DPG method is robust.
+
 We now proceed to show that the robust norms we are using satisfy this
@@
 a nonlinear hyperbolic conservation law, it
-falls under the purvue of the Lax-Wendroff theorem.
+falls under the purview of the Lax-Wendroff theorem.
 The inviscid Burger's equation is
@@
 Lagrange multipliers. While the formulation is provably convergent and robust, it does
-increase the number of unkowns in the system and changes the structure from
-symmetric positive-definite to a saddlepoint problem. Numerical results
+increase the number of unknowns in the system and changes the structure from
+symmetric positive-definite to a saddle point problem. Numerical results
 indicate that the method delivers what it promises with local flux imbalances

### 2013-12-04 docs/Truman/LocalConservation/paper/paper.tex
Added punctuation after equations in LC paper

@@
 used to try to address this. Bochev \etal\cite{Bochev2010} accomplish local
-conservation by using a pointwise divergence free velocity space in the Stokes
+conservation by using a point-wise divergence free velocity space in the Stokes
 formulation.  Chang and Nelson\cite{ChangNelson1997} developed the
@@
 \LRp{v_{\delta u_h},\delta v}_V=\LRa{R_Vv_{\delta u_h},\delta v}
-=\LRa{B\delta u_h,\delta v}=b(\delta u_h,\delta v)\,,\quad\forall\delta v\in V.
+=\LRa{B\delta u_h,\delta v}=b(\delta u_h,\delta v)\quad\forall\delta v\in V.
 \label{eq:optimaltestproblem}
@@
 & \leq \underbrace{\left(\sum_K \mu(K) \lambda_K^2\right)^{1/2}}_{=: || \bflambda ||} ||
-\hat{t} ||_{H^{-1/2}(\Gamma_h)}
+\hat{t} ||_{H^{-1/2}(\Gamma_h)}\,,
 \end{array}
@@
 
-\paragraph{Inf Sup Condition} relating spaces $\bfU$ and $Q$ reads as follows,
+\paragraph{Inf Sup Condition} relating spaces $\bfU$ and $Q$ reads as follows:
 \begin{equation}
    \sup_{\bfw \in \bfU} \frac{| c(p,\bfw) |}{|| \bfw ||_{\bfU}} \geq \beta ||
-   p ||_Q
+   p ||_Q\,.
 \end{equation}
@@
 &\leq C h || \bfpsi ||_{H^1} +  || \bfpsi || \\[8pt]
-& \leq C || \text{div} \bfpsi || = C (\sum_K \mu(K) \lambda_K^2)^{1/2}
+& \leq C || \text{div} \bfpsi || = C (\sum_K \mu(K) \lambda_K^2)^{1/2}\,.
 \end{array}
@@
 {|| \bfpsi_h ||_{H(\text{div},\Omega)}}
-\geq \frac{1}{C} (\sum_K \mu(K) \lambda_K^2)^{1/2}
+\geq \frac{1}{C} (\sum_K \mu(K) \lambda_K^2)^{1/2}\,,
 \end{equation}
@@
  = &\{ (u,\bfsig,\hat{u},\hat{t}) \, : \, \langle \hat{t},1_K \rangle = 0
- \quad \forall K \}
+ \quad \forall K \}\,.
 \end{array}
@@
    \frac{||T\bfu||}{||\bfu||}
-   \geq \gamma^2 || (u,\bfsig,\hat{u},\hat{t}) ||
+   \geq \gamma^2 || (u,\bfsig,\hat{u},\hat{t}) ||\,,
 \end{equation}
@@
 = \lambda_K (1_K,\delta v)_K  \quad \forall \delta v \in
-H^1(K)\,\forall\delta\bftau\in\bfH(\text{div},K)
+H^1(K)\,\forall\delta\bftau\in\bfH(\text{div},K)\,.
 \label{eq:local}
@@
 \begin{equation}
-|| (v,\bftau) ||_V^2 = \lambda_K (1_K, v_K)
+|| (v,\bftau) ||_V^2 = \lambda_K (1_K, v_K)\,.
 \end{equation}
@@
 \end{equation}
-(i.e. constant $C$ is independent of $\epsilon$) then
+(i.e. constant $C$ is independent of $\epsilon$), then
 \begin{equation}
@@
 \end{equation}
-and, eventually, as needed,
-\begin{equation}
-\sum_K || (v,\bftau) ||_V^2  \leq C^2 \sum_K \mu(K) \lambda_K^2
+and, eventually as needed,
+\begin{equation}
+\sum_K || (v,\bftau) ||_V^2  \leq C^2 \sum_K \mu(K) \lambda_K^2\,,
 \end{equation}
@@
 \begin{equation}
-((v,\bftau),(1_K,{\bf 0}))_V = \langle \hat{t}, 1_K \rangle_{\ptl K}
+((v,\bftau),(1_K,{\bf 0}))_V = \langle \hat{t}, 1_K \rangle_{\ptl K}\,.
 \label{eq:local2}
@@
 \begin{equation}
-| ((v,\bftau),(1_K,{\bf 0}))_V | \leq C \mu(K)^{1/2} \, || (v,\bftau) ||_V
+| ((v,\bftau),(1_K,{\bf 0}))_V | \leq C \mu(K)^{1/2} \, || (v,\bftau) ||_V\,,
 \label{eq:robust_est2}
@@
 \, (\sum_K || (v,\bftau) ||_V^2)^{1/2}
-= C (\sum_K \mu(K) \lambda_K^2)^{1/2}  || \hat{t} ||_E
+= C (\sum_K \mu(K) \lambda_K^2)^{1/2}  || \hat{t} ||_E\,,
 \end{equation}
@@
 + \epsilon\norm{\Grad v}_K^2
-+ \norm{v}^2_K
++ \norm{v}^2_K\,,
 \end{align}
@@
 +\epsilon(\nabla\vdeltau,\nabla \delta v)_K
-+\frac{1}{\mu(K)}\int_K\vdeltau\int_K\delta v
++\frac{1}{\mu(K)}\int_K\vdeltau\int_K\delta v\,,
 \end{align}
@@
    \int_K v\cdot
-   1\leq\mu(K)^{1/2}\norm{v}_{L^2(K)}\leq\mu(K)^{1/2}\norm{(v,\btau)}_K
+   1\leq\mu(K)^{1/2}\norm{v}_{L^2(K)}\leq\mu(K)^{1/2}\norm{(v,\btau)}_K\,,
    \label{eq:robustProof}
@@
 where $\norm{(v,\btau)}_K$ is the norm derived from the inner product.
-Condition~\ref{eq:robust_est2} comes out the same since
+Condition~(\ref{eq:robust_est2}) comes out the same since
 $$|(
@@
    \int_K v\cdot1\leq\mu(K)^{1/2}\frac{1}{\mu(K)^{1/2}}\LRl{\int_Kv}
-   \leq\norm{(v,\btau)}_K
+   \leq\norm{(v,\btau)}_K\,,
    \label{eq:robustProof2}

### 2013-12-04 docs/Truman/LocalConservation/paper/paper.tex
Fixed some equation parenthesis in LC paper

@@
 \end{equation}
-where $C$ is the constant from stability estimate~(\ref{eq:stab}).
+where $C$ is the constant from stability estimate~\eqref{eq:stab}.
 
@@
 test norms allowing us to bound the $L^2$ error of the field variables by the
-energy error, Equation~(\ref{eq:robustBound}). With robust test norms, we have
+energy error, \eqref{eq:robustBound}. With robust test norms, we have
 \begin{equation}
@@
 $$
-Substituting $(v,\bftau)$ for $(\delta v,\delta\bftau)$ in~(\ref{eq:local}), we get,
+Substituting $(v,\bftau)$ for $(\delta v,\delta\bftau)$ in~\eqref{eq:local}, we get,
 \begin{equation}
@@
 Notice that the stability analysis with the energy norm was, in a sense, easier than
-with the quotient norm. Only the divergence of the interpolant $\bfpsi_h$ enters~(\ref{eq:local})
+with the quotient norm. Only the divergence of the interpolant $\bfpsi_h$
+enters~\eqref{eq:local}
 and it coincides with the divergence of $\bfpsi$.
@@
 $$
-Testing with $(1_K,{\bf 0})$ in the local problem~(\ref{eq:local_problem}), we obtain,
+Testing with $(1_K,{\bf 0})$ in the local problem~\eqref{eq:local_problem}, we obtain,
 \begin{equation}
@@
 
-For instance, condition~(\ref{eq:robust_est2}) will be satisfied if the test inner product
-in~(\ref{eq:local2}) reduces to the $L^2$ term only,
+For instance, condition~\eqref{eq:robust_est2} will be satisfied if the test inner product
+in~\eqref{eq:local2} reduces to the $L^2$ term only,
 \begin{equation}
@@
 requirement.
-Consider the inner product from Equation~(\ref{eq:localSolve}), with
+Consider the inner product from \eqref{eq:localSolve}, with
 $\alpha=1$. We wish to
-verify condition (\ref{eq:robustEst1}) with the norm derived from this inner
+verify condition \eqref{eq:robustEst1} with the norm derived from this inner
 product on the right hand side. By Cauchy-Schwarz
@@
 where $\norm{(v,\btau)}_K$ is the norm derived from the inner product.
-Condition~(\ref{eq:robust_est2}) comes out the same since
+Condition~\eqref{eq:robust_est2} comes out the same since
 $$|(
@@
 Now we wish the perform the same analysis for the modified inner product in
-Equation~(\ref{eq:localSolveMod}). In this case,
-condition~(\ref{eq:robustEst1}) follows even more naturally as
+\eqref{eq:localSolveMod}. In this case,
+condition~\eqref{eq:robustEst1} follows even more naturally as
 \begin{equation}
@@
 where $\norm{(v,\btau)}$ now refers to the norm generated by inner product
-(\ref{eq:localSolveMod}). Condition~(\ref{eq:robust_est2}) follows by the same
+\eqref{eq:localSolveMod}. Condition~\eqref{eq:robust_est2} follows by the same
 reasoning.

### 2013-12-10 docs/Truman/LocalConservation/paper/paper.tex

--- 2013-12-04 docs/Truman/LocalConservation/paper/paper.tex
@@
 %TODO: Make sure titles have consistent case
-%TODO: Make sure figures work in gray-scale
 \usepackage[margin=1.0in]{geometry}
@@
 the attractive features of DPG, but turns the normally symmetric
-positive-definite DPG system into a saddle point problem.
+positive-difinite DPG system into a saddlepoint problem.
 \end{abstract}
@@
 \cite{DPG1, DPG2, DPG3, DPG5, DemkowiczHeuer, ChanHeuerThanhDemkowicz2012,
-MoroNguyenPeraire11}. In this paper, we develop a theory for the locally conservative
-formulation of DPG for convection-diffusion type equations and supplement this
-with extensive numerical results.
+MoroNguyenPeraire11}. In this paper, we develop a theory for the locally
+conservative formulation of DPG for convection-diffusion type equations
+(including Burgers' Equation and Stokes flow) and supplement this with
+extensive numerical results.
 
@@
 norm, while DPG seeks the minimization in a dual norm realized through the
-inverse Riesz map. Exact mass conservation has been an issue that has plagued
-least squares finite elements for a long time. Several approaches have been
-used to try to address this. Bochev \etal\cite{Bochev2010} accomplish local
+inverse Riesz map. Exact mass conservation has been an issue that has long plagued
+least squares finite elements. Several approaches have been
+used to try to adress this. Bochev \etal\cite{Bochev2010} accomplish local
 conservation by using a pointwise divergence free velocity space in the Stokes
@@
 \emph{restricted LSFEM}\cite{ChangNelson1997} by augmenting the least squares
-equations with a Lagrange multiplier explicitly enforcing mass conservation
+equations with Lagrange multipliers explicitly enforcing mass conservation
 element-wise. Our conservative formulation of DPG takes a similar approach and
-both methods share similar negative of transforming a minimization method to a
-saddle point problem. In the interest of crediting Chang and Nelson's
+both methods similarly share the disadvantage of transforming a minimization method to a
+saddle-point problem. In the interest of crediting Chang and Nelson's
 restricted LSFEM, we call the following locally conservative DPG method the
@@
 \cite{DPGStokes}. We follow his derivation of the standard DPG method as a
-minimum residual method. Let $U$ be the trial Hilbert space and $V$ the test
+minumum residual method. Let $U$ be the trial Hilbert space and $V$ the test
 Hilbert space for a well-posed variational problem $b(u,v)=l(v)$. In operator
@@
 infinite-dimensional Riesz map, but approximating $V$ by a finite
-dimensional $V_h$ which is of a higher polynomial degree than $U_h$ (hence
+dimensional space, $V_h$, which is of a higher polynomial degree than $U_h$ (hence
 ``enriched space'') works well in practice.
@@
 \end{align*}
-If we then multiply the top equation by some scalar test function $v$ and the
+If we then multiply the first equation by some scalar test function $v$ and the
 bottom equation by some vector-valued test function $\btau$, we can integrate by
@@
 trial space. It does not specify our choice of trial space. Nevertheless, many
-considerations of DPG in the literature (convection-diffusion \cite{DPG6},
+versions of DPG in the literature (convection-diffusion \cite{DPG6},
 linear elasticity \cite{BramwellDemkowiczGopalakrishnanQiu11}, linear
@@
 \end{equation}
-where $\bfU,Q$ are Hilbert spaces, and $a,c,l,g$ denote the appropriate
+where $\bfU,Q$ are Hilbert spaces, and $a,c,l,q$ denote the appropriate
 bilinear and linear forms. Note that $a(\bfu,\bfw)=b(\bfu,T\bfw)=(T\bfu,T\bfw)_V$ in
@@
 & \leq (\sum_K \mu(K) \lambda_K^2)^{1/2} \: (\sum_K || \text{div} \bfpsi ||_{L^2(K)}^2 )^{1/2} \\[8pt]
-& \leq \underbrace{\left(\sum_K \mu(K) \lambda_K^2\right)^{1/2}}_{=: || \bflambda ||} ||
+& \leq \underbrace{(\sum_K \mu(K) \lambda_K^2)^{1/2}}_{=: || \bflambda ||} ||
 \hat{t} ||_{H^{-1/2}(\Gamma_h)}
@@
 
-Classical $h$-interpolation interpolation error estimate for the lowest error
+Classical $h$-interpolation interpolation error estimates for the lowest error
 Raviart-Thomas elements and continuity of operator $R$ imply the stability estimate:
@@
 the interpolation error estimate and continuity constant of $R$.
-Let $\hat{t}$ be the trace of $\bfpsi_h$. We have then,
+Let $\hat{t}$ be now the trace of $\bfpsi_h$. We have then,
 \begin{equation}
@@
 
-Notice that we have considered traces of lowest order Raviart-Thomas elements for the
-discretization of flux $\hat{t}$. The inf-sup condition for the lowest order RT spaces implies
-automatically the analogous condition for elements of arbitrary order; increasing
-space $U$ only makes the discrete inf-sup constant bigger.
+Notice that we have considered traces of lowest order Raviart-Thomas elements
+for the discretization of flux $\hat{t}$. The inf-sup condition for the lowest
+order RT spaces implies automatically the analogous condition for elements of
+arbitrary order; increasing the dimension of space $U$ only makes the discrete
+inf-sup constant bigger.
 
@@
 \end{equation}
-In other words, the kernel space contains only the equilibrated fluxes.
+In other words, the kernel space contains only the equilibriated fluxes.
 With $\bfu \in \bfU_0$, we have then:
@@
 test norms allowing us to bound the $L^2$ error of the field variables by the
-energy error, Equation~(\ref{eq:robustBound}). With robust test norms, we have
+energy error, Equation \ref{eq:robustBound}. With robust test norms, we have
 \begin{equation}
@@
 
-\subsection{Robust Test Norms}
+\subsection{Robust test norms}
 The optimal test functions are determined by solving local problems determined
@@
 
-\subsubsection{A Model Problem}
+\subsubsection{A model problem}
 \seclab{sec:confusionPlate}
@@
 \]
-Note that even in the lowest-order term, the gradient of $u$ displays a
+Note that in the lowest-order term, the gradient of $u$ displays a
 singularity at $r = 0$. It is well known that, for smooth boundary data,
@@
 
-\subsubsection{A Modification of the Robust Test Norm}
+\subsubsection{A modification of the robust test norm}
 
@@
 Figure~\ref{fig:newNorm} shows the solution for $\epsilon = .01$, where the
-diffusion scale is both under-resolved and resolved by $h$-adaptivity.  In both
+diffusion scale is both underresolved and resolved by $h$-adaptivity.  In both
 cases, there are no oscillations near the plate tip --
@@
 however, the solution $u$ does not display spurious oscillations in either the
-under-resolved or resolved cases.  Figure~\ref{fig:newNormSmallEps} displays
+underresolved or resolved cases.  Figure~\ref{fig:newNormSmallEps} displays
 the same quantities, but for $\epsilon = 10^{-4}$, in order to demonstrate
@@
 
-\subsubsection{Verification of Robust Stability Estimate}
+\subsubsection{Proof of Robust Stability Estimate}
 In the robustness analysis in Section~\ref{sec:robustnessAnalysis}, we argued
-that if we have robust stability estimates:
+that if we have a robust stability estimate:
 \begin{equation}
 (1_K, v_K) \leq C \mu(K)^{1/2} || (v,\bftau) ||_K
-\tag{\ref{eq:robustEst1} revisted}
+\tag{\ref{eq:robustEst1}}
 \end{equation}
@@
 | ((v,\bftau),(1_K,{\bf 0}))_V | \leq C \mu(K)^{1/2} \, || (v,\bftau) ||_V\,.
-\tag{\ref{eq:robust_est2} revisted}
-\end{equation}
-then the restricted DPG method is robust.
-
+\tag{\ref{eq:robust_est2}}
+\end{equation}
 We now proceed to show that the robust norms we are using satisfy this
@@
 a nonlinear hyperbolic conservation law, it
-falls under the purview of the Lax-Wendroff theorem.
+falls under the purvue of the Lax-Wendroff theorem.
 The inviscid Burger's equation is
@@
 solve with second order field variables and flux ($u$, $\bfsigma$, and $\hat
-t$), third order traces ($\hat t$), and fifth order test functions ($v$ and
+t$), third order traces ($\hat u$), and fifth order test functions ($v$ and
 $\btau$).
@@
 \subsubsection{Wedge Problem}
-We devised this problem to examine some of the issues we were having blow up
-of the solution under the robust test norm. The domain is a rectangle
-$[-0.5,0.5]\times[-1,0.5]$ where the triangle connecting the bottom edges with
-the origin at $(0,0)$ is removed. The convection vector $\bbeta=(1,0)^T$,
-$\epsilon=10^{-1}$, and we apply boundary conditions $\hat t=0$ on the left
-inflow edge, $\hat u=0$ on the top edge, $\bbeta\cdot\mathbf{n}\cdot\hat
-u-\hat t=\sigma_n=0$ on the right outflow edge, $\hat u=1$ on the leading edge
-of the wedge, and $\hat t=\bbeta\cdot\mathbf{n}\cdot 1$ on the trailing edge
-of the wedge.
+We devised this problem to examine some of the issues we were having with the
+singularity in the solution under the robust test norm. The domain is a
+rectangle $[-0.5,0.5]\times[-1,0.5]$ where the triangle connecting the bottom
+edges with the origin at $(0,0)$ is removed. The convection vector
+$\bbeta=(1,0)^T$, $\epsilon=10^{-1}$, and we apply boundary conditions $\hat
+t=0$ on the left inflow edge, $\hat u=0$ on the top edge,
+$\bbeta\cdot\mathbf{n}\cdot\hat u-\hat t=\sigma_n=0$ on the right outflow
+edge, $\hat u=1$ on the leading edge of the wedge, and $\hat
+t=\bbeta\cdot\mathbf{n}\cdot 1$ on the trailing edge of the wedge.
 
@@
 boundaries, we should be able to integrate the mass flux over any
-cross-section of the mesh and get the same value. Unfortunately, it's not
+cross-section of the mesh and get the same value. Unfortunately, it is not
 mathematically kosher to take line integrals of our field variables which only
@@
 Lagrange multipliers. While the formulation is provably convergent and robust, it does
-increase the number of unknowns in the system and changes the structure from
-symmetric positive-definite to a saddle point problem. Numerical results
+increase the number of unkowns in the system and changes the structure from
+symmetric positive-definite to a saddlepoint problem. Numerical results
 indicate that the method delivers what it promises with local flux imbalances

### 2013-12-10 docs/Truman/LocalConservation/paper/paper.tex
mods of paper, mostly typos and language

@@
 the attractive features of DPG, but turns the normally symmetric
-positive-difinite DPG system into a saddlepoint problem.
+positive-definite DPG system into a saddle-point problem.
 \end{abstract}
@@
 singularity at $r = 0$. It is well known that, for smooth boundary data,
-solutions to Laplace’s equation can be decomposed into the linear combination
+solutions to Laplace's equation can be decomposed into the linear combination
 of smooth and singular contributions; the above analysis implies that, when
 boundary conditions change from Dirichlet to Neumann on the half-plane, the
-Laplace’s equation will always develop a singularity in the stresses.
+Laplace's equation will always develop a singularity in the stresses.
 
@@
 a nonlinear hyperbolic conservation law, it
-falls under the purvue of the Lax-Wendroff theorem.
+falls under the scope of the Lax-Wendroff theorem. %replaced purvue with purview, but I think scope might be more easily understood -JC
 The inviscid Burger's equation is
@@
 \subsubsection{Wedge Problem}
-We devised this problem to examine some of the issues we were having with the
+We devised this problem to examine the issues we were having with the
 singularity in the solution under the robust test norm. The domain is a
@@
 cross-section of the mesh and get the same value. Unfortunately, it is not
-mathematically kosher to take line integrals of our field variables which only
+%mathematically kosher to take line integrals of our field variables which only
+mathematically well-defined to take line integrals of our field variables which only
 live in $L^2$. We can, however, integrate the trace and flux variables over element boundaries.
@@
 % Solution quality
-The general trend we see looking at the results is that the solution quality
+The general trend we observe from the results is that the solution quality
 of the standard and restricted formulations is nearly identical once
@@
 error in the energy norm, but the Lagrange multipliers in the restricted
-formulation shift the solution slightly. So we should see somewhat higher
+formulation shift the solution slightly, so we should see somewhat higher
 error and different elements will get chosen for refinement. The choice of
@@
 assumptions on $\bbeta$ \cite{ChanHeuerThanhDemkowicz2012} that break down for
-the vortex problem. Here we see the standard method needlessly refines
+the vortex problem, where $\snorm{\bbeta}\rightarrow 0$ in the center of the domain. 
+Here, we see the standard method needlessly refines
 in the center of the domain where the solution is constant. The restricted
@@
 % Mass conservation
-It shouldn't come as a surprise that the standard and restricted
+It should not come as a surprise that the standard and restricted
 solutions match each other so closely. The restricted formulation
@@
 Standard and restricted DPG perform nearly identically for the
-inviscid Burgers' problem. It's obvious that the Lax-Wendroff condition of
+inviscid Burgers' problem. It is obvious that the Lax-Wendroff condition of
 local conservation is a sufficient, but not necessary condition for numerical
@@
 \subsubsection{Stokes Results}
-The two Stokes problems are the first ones we encounter that really stress the local
+The two Stokes problems are the first ones we encounter that stress the local
 conservation property of standard DPG. With a cylinder radius of $0.6$,
@@
 nonconservative solution is completely useless at this point. We see the same
-thing with the backward facing step problem. The conservative solution is
-great on the coarsest mesh, while standard DPG needs a lot more resolution
-before it even starts to look right.
+thing with the backward facing step problem. The conservative solution preserves
+qualitative features even on the coarsest mesh, while standard DPG requires far higher resolution
+to achieve a similar solution.
 
 \section{Conclusions}
-We've developed a locally conservative formulation of DPG by leveraging
+We have developed a locally conservative formulation of DPG by leveraging
 Lagrange multipliers. While the formulation is provably convergent and robust, it does
-increase the number of unkowns in the system and changes the structure from
-symmetric positive-definite to a saddlepoint problem. Numerical results
+increase the number of unknowns in the system and changes the structure from
+symmetric positive-definite to a saddle-point problem. Numerical results
 indicate that the method delivers what it promises with local flux imbalances
@@
 loss as standard least squares on coarse meshes, but made up the lost mass with further
-resolution. On problems where local conservation was really stressed,
+resolution. For problems where local conservation was stressed,
 restricted DPG was able to deliver reasonable solutions with much less

### 2013-12-13 docs/Truman/LocalConservation/paper/paper.tex
Minor changes to LC paper

--- 2013-12-04 docs/Truman/LocalConservation/paper/paper.tex
@@
 
-Let function $\bfpsi$ denote the $H(\text{div},\Omega)$ extension of flux $\hat{t}$
+Let function $\bfpsi$ denote the $\bfH(\text{div},\Omega)$ extension of flux $\hat{t}$
 that realizes the minimum in the definition of the quotient (minimum energy
@@
 
-One possible way to attack the problem is to switch to the energy norm in the Brezzi's stability
+One possible way to attack the problem is to switch to the energy norm in the Brezzi stability
 analysis. Dealing with the ``inf-sup in kernel'' condition is simple. Upon replacing
@@
 \begin{align}
-((v,\bftau), (\delta v, \delta \bftau)_V &= \langle \hat{t}, \delta v \rangle_{\ptl K}
+((v,\bftau), (\delta v, \delta \bftau))_V &= \langle \hat{t}, \delta v \rangle_{\ptl K}
 = \int_K \text{div} \bfpsi_h \, \delta v = \int_K \text{div} \bfpsi \, \delta v
